\documentclass[11pt]{memoir}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{2}

% ==========================================
% FONTS: EB Garamond (matching Volume I)
% ==========================================

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\frenchspacing

\usepackage[
  cmintegrals,
  cmbraces,
  noamssymbols
]{newtxmath}
\usepackage{ebgaramond}

\usepackage[
  activate={true,nocompatibility},
  final,
  tracking=true,
  kerning=true,
  spacing=true,
  factor=1100,
  stretch=10,
  shrink=10
]{microtype}

\SetExtraKerning[unit=space]
  {encoding={*}, family={*}, series={*}, size={footnotesize,small,normalsize}}
  {\textemdash={400,400},
   "28={,150},
   "29={150,},
   \textquotedblleft={,150},
   \textquotedblright={150,}}

% ==========================================
% PACKAGES
% ==========================================

\usepackage{mleftright}
\mleftright
\let\Bbbk\undefined
\let\openbox\undefined
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs,showmanualtags}
\usepackage{tikz-cd}
\usetikzlibrary{positioning,arrows.meta,calc,decorations.markings}
\makeatletter
\def\hyper@nopatch@caption{}
\makeatother
\usepackage[unicode,pdfencoding=auto,psdextra]{hyperref}
% Cross-volume label import from Vol I (V1- prefix on all cross-refs)
% DISABLED: Vol I aux tree (2.5MB, 22K lines) exceeds xr-hyper \read
% capacity after the latest Vol I rebuild.  V1- prefixed cross-refs
% resolve as "??" until a flat cross-ref export is implemented.
\usepackage{xr-hyper}
%\externaldocument[V1-]{../chiral-bar-cobar/main}
\usepackage{geometry}
\geometry{top=1.2in, bottom=1.2in, left=1.25in, right=1.25in, footskip=0.5in}
\setlength{\headheight}{28pt}
\setlength{\emergencystretch}{3em}
\setlength{\hfuzz}{1pt}
\hbadness=3000
\raggedbottom
\usepackage{enumitem}
\usepackage{longtable}
\usepackage{multicol}
\usepackage{mathrsfs}
\usepackage{bm}

% ==========================================
% THEOREM ENVIRONMENTS (Garamond style, matching Vol I)
% ==========================================

\usepackage{thmtools}

\declaretheoremstyle[
  spaceabove=\topsep,
  spacebelow=\topsep,
  headfont=\normalfont\scshape,
  notefont=\normalfont\itshape,
  bodyfont=\normalfont,
  postheadspace=0.5em,
  headpunct={.}
]{garamondthm}

\declaretheoremstyle[
  spaceabove=\topsep,
  spacebelow=\topsep,
  headfont=\normalfont\itshape,
  notefont=\normalfont\itshape,
  bodyfont=\normalfont,
  postheadspace=0.5em,
  headpunct={.}
]{garamonddef}

% Claim provenance tags (matching Vol I)
\newcommand{\ClaimStatusProvedHere}{\textnormal{[proved here]}}
\newcommand{\ClaimStatusProvedElsewhere}{\textnormal{[proved elsewhere]}}
\newcommand{\ClaimStatusOpen}{\textnormal{[open]}}
\newcommand{\ClaimStatusConjectured}{\textnormal{[conjectured]}}
\newcommand{\ClaimStatusHeuristic}{\textnormal{[physical heuristic]}}

% Plain-style environments
\declaretheorem[style=garamondthm, name=Theorem, numberwithin=section]{theorem}
\declaretheorem[style=garamondthm, name=Lemma, sibling=theorem]{lemma}
\declaretheorem[style=garamondthm, name=Proposition, sibling=theorem]{proposition}
\declaretheorem[style=garamondthm, name=Corollary, sibling=theorem]{corollary}
\declaretheorem[style=garamondthm, name=Verification, sibling=theorem]{verification}
\declaretheorem[style=garamondthm, name=Computation, sibling=theorem]{computation}
\declaretheorem[style=garamondthm, name=Main Theorem, sibling=theorem]{maintheorem}

% Definition-style environments
\declaretheorem[style=garamonddef, name=Definition, sibling=theorem]{definition}
\declaretheorem[style=garamonddef, name=Example, sibling=theorem]{example}
\declaretheorem[style=garamonddef, name=Remark, sibling=theorem]{remark}
\declaretheorem[style=garamonddef, name=Conjecture, sibling=theorem]{conjecture}
\declaretheorem[style=garamonddef, name=Notation, sibling=theorem]{notation}
\declaretheorem[style=garamonddef, name=Convention, sibling=theorem]{convention}
\declaretheorem[style=garamonddef, name=Construction, sibling=theorem]{construction}
\declaretheorem[style=garamonddef, name=Warning, sibling=theorem]{warning}
\declaretheorem[style=garamonddef, name=Hypothesis, sibling=theorem]{hypothesis}
\declaretheorem[style=garamonddef, name=Assumption, sibling=theorem]{assumption}
\declaretheorem[style=garamonddef, name=Technique, sibling=theorem]{technique}
\declaretheorem[style=garamonddef, name=Interpretation, sibling=theorem]{interpretation}
\declaretheorem[style=garamonddef, name=Evidence, sibling=theorem]{evidence}
\declaretheorem[style=garamonddef, name=Principle, sibling=theorem]{principle}
\declaretheorem[style=garamonddef, name=Question, sibling=theorem]{question}
\declaretheorem[style=garamonddef, name=Summary, sibling=theorem]{summary}
\declaretheorem[style=garamonddef, name=Problem, sibling=theorem]{problem}
\declaretheorem[style=garamonddef, name=Setup, sibling=theorem]{setup}
\declaretheorem[style=garamonddef, name=Strategy, sibling=theorem]{strategy}
\declaretheorem[style=garamonddef, name=Open Problem, sibling=theorem]{openproblem}
\declaretheorem[style=garamonddef, name=Observation, sibling=theorem]{observation}

% Hyperref anchors for theorem counters
\makeatletter
\@ifundefined{theHtheorem}{\newcommand{\theHtheorem}{\thesection.\arabic{theorem}}}{}
\makeatother

% ==========================================
% MATHEMATICAL NOTATION
% ==========================================

% Operators
\DeclareMathOperator{\Conf}{Conf}
\DeclareMathOperator{\FM}{FM}
\DeclareMathOperator{\Obs}{Obs}
\DeclareMathOperator{\MC}{MC}
\DeclareMathOperator{\CH}{CH}
\DeclareMathOperator{\HH}{HH}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Sym}{Sym}
\DeclareMathOperator{\Sh}{Sh}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\CE}{CE}
\DeclareMathOperator{\CYBE}{CYBE}
\DeclareMathOperator{\RavConf}{RavConf}
\DeclareMathOperator{\Fact}{Fact}
\DeclareMathOperator{\Tot}{Tot}
\DeclareMathOperator{\holim}{holim}
\DeclareMathOperator{\hocolim}{hocolim}
\DeclareMathOperator{\Ran}{Ran}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Coder}{Coder}
\newcommand{\Bmod}{B_{\mathrm{mod}}}
\newcommand{\Bch}{B_{\mathrm{ch}}}
\newcommand{\Defmod}{\operatorname{Def}_{\mathrm{mod}}}
\newcommand{\Definfmod}{\operatorname{Def}_{\infty}^{\mathrm{mod}}}
\newcommand{\Convstr}{\operatorname{Conv}_{\mathrm{str}}}
\newcommand{\Convinf}{\operatorname{Conv}_{\infty}}
\providecommand{\Defcyc}{\operatorname{Def}_{\mathrm{cyc}}}
\providecommand{\fC}{\mathfrak{C}}
\providecommand{\gAmod}{\mathfrak{g}_{\cA}^{\mathrm{mod}}}
\providecommand{\Gmod}{\mathcal{G}^{\mathrm{mod}}}
\providecommand{\Tr}{\operatorname{Tr}}
\providecommand{\Tor}{\operatorname{Tor}}
\providecommand{\Cotor}{\operatorname{Cotor}}
\providecommand{\SCop}{\mathsf{SC}^{\mathrm{ch,top}}}
\newcommand{\Deftop}{\operatorname{Def}_{\mathrm{top}}}
\DeclareMathOperator{\Ob}{Ob}
\newcommand{\cl}{\mathrm{cl}}
\newcommand{\orline}{\mathfrak{o}}
\newcommand{\StGraph}{\mathsf{SGraph}}
\providecommand{\cref}[1]{\ref{#1}}
\DeclareMathOperator{\Koszul}{Koszul}
\DeclareMathOperator{\Aut}{Aut}
\newcommand{\Xloc}{\mathfrak{X}_{\mathrm{loc}}}
\newcommand{\barBch}{\bar{B}^{\mathrm{ch}}}
\newcommand{\Vect}{\cat{Vect}}
\newcommand{\Mod}{\mathrm{Mod}}
\newcommand{\ClaimStatusConditional}{\textnormal{[conditional]}}
\newcommand{\ClaimStatusNeedsVerification}{\textnormal{[needs verification]}}

% Calligraphic and blackboard
\newcommand{\A}{\mathcal{A}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cV}{\mathcal{V}}
\newcommand{\OO}{\mathcal{O}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
% Compatibility with Vol I notation in moved chapters
\providecommand{\cD}{\mathcal{D}}
\providecommand{\cT}{\mathcal{T}}
\providecommand{\cN}{\mathcal{N}}
\providecommand{\cC}{\mathcal{C}}
\providecommand{\cH}{\mathcal{H}}
\providecommand{\ov}[1]{\overline{#1}}
\providecommand{\h}{\hbar}
\providecommand{\bR}{\mathbb{R}}
\providecommand{\bC}{\mathbb{C}}
\providecommand{\fg}{\mathfrak{g}}
\providecommand{\cM}{\mathcal{M}}
\providecommand{\BDref}[1]{\textup{[\cite{BD04}, #1]}}
\providecommand{\ChirHoch}{CH}
\providecommand{\cocolon}{\nobreak\mskip2mu\mathpunct{}\nonscript\mkern-\thinmuskip{:}\mskip6muplus1mu\relax}
\providecommand{\chirAss}{\mathsf{Ass}^{\mathrm{ch}}}
\providecommand{\chirCom}{\mathsf{Com}^{\mathrm{ch}}}
\providecommand{\chirLie}{\mathsf{Lie}^{\mathrm{ch}}}
\providecommand{\Pinf}{\mathsf{P}_{\infty}}
\providecommand{\B}{\bar{B}}
\providecommand{\barPi}{\overline{\Pi}}

% Operads (sans-serif, matching Vol I convention)
\newcommand{\Ass}{\mathsf{Ass}}
\newcommand{\Com}{\mathsf{Com}}
\newcommand{\Lie}{\mathsf{Lie}}
\newcommand{\Pois}{\mathsf{Pois}}
\newcommand{\BV}{\mathsf{BV}}
\newcommand{\Eone}{\mathsf{E}_1}
\newcommand{\Etwo}{\mathsf{E}_2}
\newcommand{\En}{\mathsf{E}_n}
\newcommand{\Einf}{\mathsf{E}_{\infty}}
\newcommand{\Linf}{\mathsf{L}_{\infty}}
\newcommand{\Ainf}{\mathsf{A}_{\infty}}
\newcommand{\Cinf}{\mathsf{C}_{\infty}}
\providecommand{\Pinf}{\mathsf{P}_{\infty}}
\providecommand{\chirLie}{\mathsf{Lie}^{\mathrm{ch}}}
\providecommand{\chirAss}{\mathsf{Ass}^{\mathrm{ch}}}
\providecommand{\chirCom}{\mathsf{Com}^{\mathrm{ch}}}

% HT-specific
\newcommand{\SCchtop}{\mathsf{SC}^{\mathrm{ch,top}}}
\newcommand{\OHT}{C_\ast\!\bigl(W(\SCchtop)\bigr)}

% Shared macros used across multiple chapters
\providecommand{\Zder}{\operatorname{Z}_{\mathrm{der}}}
\providecommand{\Abulk}{A_{\mathrm{bulk}}}
\providecommand{\Bbound}{B_{\partial}}
\providecommand{\gSC}{\mathfrak{g}^{\mathrm{SC}}}
\providecommand{\RHom}{\operatorname{RHom}}
\providecommand{\Der}{\operatorname{Der}}
\providecommand{\Perf}{\operatorname{Perf}}
\providecommand{\lines}{\mathsf{Lines}}

% Macros from modular_swiss_cheese_operad.tex (promoted to preamble for chapter-order independence)
\providecommand{\SCmod}{\mathsf{SC}^{\mathrm{ch,top}}_{\mathrm{mod}}}
\providecommand{\SCmodcl}{\mathsf{SC}^{\mathrm{ch,top}}_{\mathrm{mod,cl}}}
\providecommand{\SCmodop}{\mathsf{SC}^{\mathrm{ch,top}}_{\mathrm{mod,op}}}
\providecommand{\SCmodmix}{\mathsf{SC}^{\mathrm{ch,top}}_{\mathrm{mod,mix}}}
\providecommand{\FTmod}{\mathrm{FT}_{\mathcal{M}\!od}}
\providecommand{\Commod}{\mathsf{Com}_{\mathrm{mod}}}
\providecommand{\Modop}{\mathcal{M}\!od}
\providecommand{\Sgp}{\mathfrak{S}}
\providecommand{\Heis}{\mathsf{H}}
\providecommand{\slhat}{\widehat{\mathfrak{sl}}}
\providecommand{\Vir}{\mathsf{Vir}}
\providecommand{\hvee}{h^{\!\vee}}
\providecommand{\Deltacyc}{\Delta_{\mathrm{cyc}}}
\providecommand{\FMg}[1]{\FM_{#1}(\Sigma_g)}
\providecommand{\vol}{\mathrm{vol}}
\providecommand{\PP}{\mathbb{P}}
\providecommand{\im}{\operatorname{im}}
\providecommand{\coker}{\operatorname{coker}}
\providecommand{\Cl}{\operatorname{Cl}}
\providecommand{\dCrit}{\operatorname{dCrit}}

% Shorthand
\newcommand{\hh}{\hbar}
\newcommand{\dbar}{\bar{\partial}}
\newcommand{\ASym}{\mathrm{ASym}}
\newcommand{\gr}{\mathrm{gr}}
\newcommand{\sgn}{\mathrm{sgn}}
\providecommand{\llbracket}{[\![}
\providecommand{\rrbracket}{]\!]}
\newcommand{\degree}[1]{\lvert #1 \rvert}

% Gravity chapters (thqg) — promoted from chapter-local providecommand
\providecommand{\Uvert}{U_{\mathrm{vert}}}
\providecommand{\chienv}{\chi_{\mathrm{env}}}
\providecommand{\cS}{\mathcal{S}}
\providecommand{\HS}{\operatorname{HS}}
\providecommand{\Det}{\operatorname{Det}}
\providecommand{\Fred}{\operatorname{Fred}}
\providecommand{\rank}{\operatorname{rank}}
\providecommand{\ad}{\operatorname{ad}}
\providecommand{\wt}{\operatorname{wt}}
\providecommand{\Ydg}{\mathcal{Y}^{\mathrm{dg}}}
\providecommand{\Map}{\operatorname{Map}}
\providecommand{\RGamma}{R\Gamma}
\providecommand{\BTZ}{\mathrm{BTZ}}

% Bar-cobar (matching Vol I)
\newcommand{\barB}{\bar{B}}
\newcommand{\barBgeom}{\bar{B}_{\mathrm{geom}}}
\newcommand{\Omegach}{\Omega^{\mathrm{ch}}}

% Categories
\newcommand{\cat}[1]{\mathbf{#1}}
\newcommand{\DMod}{\cat{D}\text{-}\cat{Mod}}
\newcommand{\DX}{\mathcal{D}_X}
\newcommand{\OX}{\mathcal{O}_X}

% Differentials (matching Vol I notation)
\newcommand{\dzero}{d_0}
\newcommand{\dfib}{d_{\mathrm{fib}}}
\newcommand{\Dg}[1]{D_{#1}}

% ==========================================
% FRONT MATTER
% ==========================================
% MODULAR GRAPH VISUAL CALCULUS (matching Vol I)
% ==========================================
\tikzset{
  gv/.style={circle, draw, thick, inner sep=1pt, minimum size=13pt,
    font=\footnotesize},
  gv0/.style={circle, fill, inner sep=0pt, minimum size=3.5pt},
  wv/.style={circle, draw, thick, inner sep=1.5pt, minimum size=15pt,
    font=\footnotesize},
  iedge/.style={thick},
  pedge/.style={thick,
    decoration={markings,
      mark=at position 0.5 with {\node[circle,fill,inner sep=0.8pt]{};}},
    postaction={decorate}},
  sloop/.style={thick},
  leg/.style={thick},
  shG/.style={fill=white, draw=black!40, rounded corners=2pt},
  shL/.style={fill=black!6, draw=black!40, rounded corners=2pt},
  shC/.style={fill=black!14, draw=black!40, rounded corners=2pt},
  shM/.style={fill=black!28, draw=black!40, rounded corners=2pt},
  codim bg/.style={draw=black!20, fill=black!3, rounded corners=3pt},
  maparrow/.style={-{Stealth[length=5pt]}, thick},
}

\title{\textit{Modular Homotopy Theory for Algebraic Factorization Algebras on Algebraic Curves}\\[0.5em]
\large Volume~2: $\Ainf$~Chiral Algebras and 3D Holomorphic--Topological QFT}

\author{Raeez Lorgat}

\date{August 2025}

\begin{document}

\maketitle

\begin{abstract}
\itshape

\noindent
The bar complex of a chiral algebra~$\cA$ on a curve carries two
structures: a differential~$D_\cA$ from OPE residues on the
Fulton--MacPherson space~$\FM_k(\C)$, and a deconcatenation
coproduct~$\Delta$ from the ordered configuration
space~$\Conf_k^<(\R)$.  A bar element of degree~$k$ lives on
$\FM_k(\C) \times \Conf_k^<(\R)$; the coderivation property
$\Delta \circ D_\cA = (D_\cA \otimes \id + \id \otimes D_\cA)
\circ \Delta$ says that collisions in~$\C$ commute with cuts
in~$\R$.  This is the operadic fingerprint of a
three-dimensional holomorphic-topological field theory on
$\C \times \R$: the bar complex is
a coalgebra over the Swiss-cheese cooperad.

Volume~I is Koszul duality on a curve.  Volume~II is the
dimensional lift to~$\C \times \R$: the bar differential is the
holomorphic direction, the coproduct is the topological direction.
$\SCchtop$ is homotopy-Koszul (Kontsevich formality $+$ transfer),
Koszul self-dual, and bar-cobar on $\SCchtop$-algebras is a
Quillen equivalence.  On the chirally Koszul locus, the
open-colour Koszul dual carries the dg-shifted Yangian.
PVA descent extracts a $(-1)$-shifted Poisson vertex algebra:
Jacobi from Arnold, Leibniz from Stokes
on~$\partial\FM_3(\C)$, vanishing of~$m_{k \ge 3}$ from
contractibility of~$\R$.

In the boundary-linear sector, bulk observables are chiral
Hochschild cochains of the boundary algebra.  The line side carries modules
for the Koszul dual; spectral braiding satisfies Yang--Baxter by
Stokes on~$\FM_3(\C)$.
At genus~$g \ge 1$, the curvature~$\kappa(\cA) \cdot \omega_g$
from the Hodge bundle produces a curved $\SCchtop$-algebra with
$d_{\mathrm{fib}}^{\,2} = \kappa \cdot \omega_g$; the total
differential restores flatness over~$\overline{\cM}_g$ by
coupling the $\R$-ordering to the Hodge bundle.
\end{abstract}

\bigskip
\noindent
\textbf{2020 Mathematics Subject Classification.}
Primary 18M75, 17B69;
Secondary 81T70, 18N70, 81T30, 55R80.

\medskip
\noindent
\textbf{Keywords.}
$A_\infty$~chiral algebra, bar complex, Swiss-cheese operad,
holomorphic--topological field theory, Poisson vertex algebra,
homotopy-Koszul operad, Quillen equivalence, bulk-boundary-line
triangle, dg-shifted Yangian, spectral $R$-matrix, Maurer--Cartan
element, convolution dg Lie algebra, curved factorization, chiral
Hochschild cohomology, log Fulton--MacPherson compactification,
planted-forest differential, modular shadow obstruction tower, modular Koszul
datum.

\tableofcontents

\section*{Notation and conventions}
\begin{itemize}[leftmargin=2em]
\item All algebraic structures are over $\C$ unless stated otherwise.
\item Grading is \emph{cohomological}: differentials have degree $+1$.
\item $\Ainf$ denotes the $A_\infty$ operad; $\Eone$, $\Etwo$, $\Einf$ the little-disks operads.
\item $\SCchtop$ is the holomorphic--topological Swiss-cheese operad (Definition~\ref{def:SC}).
\item $\FM(X)$ denotes the Fulton--MacPherson compactification of $\Conf(X)$.
\item $m_k$ are the $\Ainf$ chiral operations; $\lambda_i$ are spectral parameters.
\item Volume~I notation: $\cA$ for chiral algebras, $\barB(\cA)$ for bar, $\Omegach(C)$ for cobar, $\cA^!$ for Koszul dual; on the two-color Vol~II surface we write $\cA^!_{\mathrm{ch}}$ and $\cA^!_{\mathrm{line}}$ for the closed- and open-color duals.
\end{itemize}

\subsection*{What this volume assumes from Volume~I}

Volume~I proves five structural theorems for chiral algebras on
curves.  This volume depends on all five.

\begin{enumerate}[label=\textbf{(\Alph*)},leftmargin=2.2em]
\item \textbf{Bar--cobar adjunction.}
  The geometric bar complex $\barB_X(\cA)$ and cobar complex
  $\Omegach(\barB_X(\cA))$ form an adjoint pair of functors on
  chiral algebras.  Volume~II reinterprets the bar complex as an
  algebra over the Swiss-cheese operad
  $\mathsf{SC}^{\mathrm{ch,top}}$; the adjunction is assumed, not
  reproved.
\item \textbf{Bar--cobar inversion.}
  On the Koszul locus the counit
  $\Omegach(\barB_X(\cA))\to \cA$ is a quasi-isomorphism.
  Volume~II lifts this to the raviolo vertex algebra setting and to
  completed towers via weightwise stabilization.
\item \textbf{Complementarity.}
  The deformation and obstruction complexes $\mathbf Q_g(\cA)$ and
  $\mathbf Q_g(\cA^!)$ are complementary Lagrangians inside the
  shifted-symplectic ambient complex
  $R\Gamma(\overline{\mathcal M}_g,\mathcal Z(\cA))$.  The
  $(-1)$-shifted symplectic structure is the genus-tower input for
  the curved Swiss-cheese algebras of Part~I.
\item \textbf{Modular characteristic.}
  The scalar $\kappa(\cA)$ and the $\hat A$-genus control the
  curvature $\dfib^{\,2}=\kappa(\cA)\cdot\omega_g$ of the genus
  tower.  The spectral discriminant $\Delta_\cA$ is the first
  non-scalar invariant.
\item \textbf{Hochschild duality.}
  The chiral Hochschild cochain complex
  $\mathrm{ChirHoch}^*(\cA)$ is polynomial on the Koszul locus and
  dual to $\mathrm{ChirHoch}^*(\cA^!)$.  It is the natural candidate
  for the bulk algebra in the $3$d holomorphic-topological theory.
\end{enumerate}
Volume~II computes the three-dimensional content of these five
theorems through the Swiss-cheese lens.

\subsection*{Conditional and unconditional results}
\label{subsec:conditional-roadmap}

The live theorem surface now separates by scope.  The operadic
foundations (Weiss descent, recognition theorem,
homotopy-Koszulity, Koszul self-duality) are proved without
physical hypotheses.  On the chirally Koszul locus, the
line-module comparison, Yangian recognition, and duality
involution are proved algebraically.  For physical
realisations supplied by Theorem~\ref{thm:physics-bridge}, the
standard affine HT gauge realization gives
Theorem~\ref{thm:Koszul_dual_Yangian}: the field-theoretic
open-colour Koszul dual carries the dg-shifted Yangian
package.
The former standing hypotheses (H1)--(H4) have been
eliminated: the algebraic framework is built on a single
definition (logarithmic $\SCchtop$-algebra,
Definition~\ref{def:log-SC-algebra}) and a geometric
theorem (FM calculus, Theorem~\ref{thm:FM-calculus}).
Physical realisations enter through the bridge theorem
(Theorem~\ref{thm:physics-bridge}).

\begin{remark}[Status of results]
\label{rem:conditional-list}
The live algebraic framework separates as follows:
\begin{itemize}
\item \emph{Unconditional for any logarithmic $\SCchtop$-algebra}
  \emph{(}Definition~\ref{def:log-SC-algebra}\emph{):}
  Proposition~\ref{prop:compatibility} (prefactorization $\Rightarrow$
  $W(\SCchtop)$-algebra),
  Theorem~\ref{thm:Obs-is-SC} (BV observables as Swiss-cheese
  algebra),
  Theorem~\ref{thm:bulk-CHC} (bulk $\simeq$ chiral Hochschild
  cochains),
  Theorem~\ref{thm:bar-cobar-adjunction} (bar--cobar Quillen
  equivalence),
  Theorem~\ref{thm:filtered-koszul} (filtered Quillen equivalence),
  Theorem~\ref{thm:SC-self-duality} (Koszul self-duality
  of~$\SCchtop$).
\item \emph{On the chirally Koszul locus:}
  Theorem~\ref{thm:lines_as_modules}
  ($\mathcal{C}_{\mathrm{line}} \simeq
  \cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$),
  Theorem~\ref{thm:yangian-recognition}
  (the open-colour Koszul dual carries the dg-shifted Yangian
  package),
  Theorem~\ref{thm:duality-involution}
  (the full two-colour Koszul duality involution returns~$\cA$).
\item \emph{For the standard affine HT gauge realization among the
  physical examples supplied by
  Theorem~\ref{thm:physics-bridge}:}
  Theorem~\ref{thm:Koszul_dual_Yangian}
  (the field-theoretic open-colour Koszul dual is a
  dg-shifted Yangian).
\item \emph{Core constructions available on the live algebraic
  surface:}
  The chain-level $\Ainf$ structure, PVA descent, spectral
  $R$-matrix, and the Swiss-cheese descent package are built for
  logarithmic $\SCchtop$-algebras; the former standing
  hypotheses are now distributed between the algebraic axioms and
  the physics bridge.
  The former standing hypotheses (H1)--(H4) are now derived:
  (H1) and (H2) are conditions on physical realisations
  (Theorem~\ref{thm:physics-bridge}); (H3) is the FM calculus
  theorem; (H4) is the recognition theorem.
  The worked examples verify that specific gauge theories
  satisfy Theorem~\ref{thm:physics-bridge}.
\end{itemize}
\end{remark}

\input{chapters/frame/preface}

\input{chapters/theory/introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{The Machine and the Classical Shadow}
\label{part:swiss-cheese}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
The primitive datum of a three-dimensional holomorphic--topological
theory on $\C_z \times \R_t$ is not an algebra but a category: the
open/closed factorization dg-category~$\cC$ on a tangential log
curve $(X, D, \tau)$.  Its objects are boundary conditions; its
morphisms are open-string states.  A choice of vacuum
object~$b \in \cC$ produces an $A_\infty$-chiral algebra
$A_b = \End_\cC(b)$ as a \emph{chart}; the Morita class
of~$\cC$, not the quasi-isomorphism class of~$A_b$, is the
invariant.  The governing operadic structure is the two-colored
Swiss-cheese operad~$\SCchtop$, with closed color~$\FM_k(\C)$
(holomorphic collisions) and open color~$E_1(m)$ (topological
orderings).  The bar complex~$\barB(A_b)$ of Volume~I is the
coalgebraic shadow of~$\cC$, encoding twisting morphisms; it
is not the bulk.  The bulk is the chiral derived center
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cC)$, the universal algebra of
operators acting on the boundary from the interior
(\S\ref{subsec:categorical-open-sector}).

The operadic machine then immediately yields its classical shadow.
The regular part of~$m_2$ is a commutative product, the singular
part is a $\lambda$-bracket, and together they form a
$(-1)$-shifted Poisson vertex algebra on $H^\bullet(A, Q)$,
proved by the same Arnold relations and Stokes identities that
govern~$d_{\barB}^2 = 0$ in Volume~I.  The raviolo vertex algebra
is the algebraic avatar of the $\C \times \R$ geometry,
constructed from the Swiss-cheese structure via
\v{C}ech/Thom--Sullivan descent.

\input{chapters/theory/foundations}
\input{chapters/theory/locality}
\input{chapters/theory/axioms}
\input{chapters/theory/equivalence}
\input{chapters/theory/bv-construction}
\input{chapters/theory/factorization_swiss_cheese}
\input{chapters/theory/raviolo}
\input{chapters/theory/raviolo-restriction}
\input{chapters/theory/fm-calculus}
\input{chapters/theory/pva-descent-repaired}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{The Standard HT Landscape}
\label{part:examples}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
Each algebra family in Volume~I's standard landscape is now a
test case for the full open/closed architecture: boundary
algebra, universal bulk, line-sector operations, modular MC
element.  The Heisenberg Rosetta Stone computes every direct datum by hand,
confirming the four-functor table ($\barB$: twisting morphisms;
$\Omega$: boundary recovery; open-colour duality: line-side modeling algebra;
$C^\bullet_{\mathrm{ch}}$: universal bulk).  The shadow archetype
($\mathsf{G}$/$\mathsf{L}$/$\mathsf{C}$/$\mathsf{M}$) classifies
the boundary-holographic complexity of each family.
$\mathcal{W}$-algebra computations connect to Volume~I's
Drinfeld--Sokolov framework: bar-cobar commutes with DS reduction,
so the full Swiss-cheese structure descends through the BRST
functor.

The examples are placed immediately after the machine so that
the reader has concrete instances before the bulk, modularity,
and ordered-sector abstractions of Parts~III--V.

\input{chapters/examples/rosetta_stone}
\input{chapters/examples/examples-computing}
\input{chapters/examples/examples-complete-proved}
\input{chapters/examples/examples-worked}
\input{chapters/examples/w-algebras-virasoro}
\input{chapters/examples/w-algebras-w3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{The Universal Bulk}
\label{part:bbl-core}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
The universal bulk of a boundary algebra~$\cA$ is not its bar complex
but its chiral derived center: the cohomology of chiral Hochschild
cochains $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA) =
H^*(C^\bullet_{\mathrm{ch}}(\cA, \cA), \delta)$.  The brace dg
algebra structure on~$C^\bullet_{\mathrm{ch}}$ makes the pair
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}, \cA)$ the terminal local
open/closed pair: the chiral Swiss-cheese theorem.  The bar
complex enters as a separate object: it classifies
\emph{twisting morphisms} (couplings between~$\cA$ and the
open-colour Koszul dual~$\cA^!_{\mathrm{line}}$), while the derived
center classifies \emph{bulk operators acting on the boundary}.
These are different objects solving different problems, produced by
different constructions: $\barB$ (coalgebra), $\Omega$ (original
algebra back), Koszul duality on the line side
($\cA^!_{\mathrm{line}}$), $C^\bullet_{\mathrm{ch}}(-,-)$ (bulk).
On the chirally Koszul locus, bar--cobar duality yields the
spectral $R$-matrix~$R(z)$ satisfying Yang--Baxter, while the later
chirally-Koszul comparison theorem models the line category
$\cC_{\mathrm{line}}$ by
$\cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$.  Together these
complete the Koszul triangle: boundary~$\cA$, bulk~$\cZ^{\mathrm{der}}_{\mathrm{ch}}$,
lines~$\cC_{\mathrm{line}}$, modeled on that locus by
$\cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$.

\input{chapters/connections/hochschild}
\input{chapters/connections/brace}
\input{chapters/connections/bar-cobar-review}
\input{chapters/connections/line-operators}
\input{chapters/connections/spectral-braiding-core}
\input{chapters/connections/ht_bulk_boundary_line_core}
\input{chapters/connections/celestial_boundary_transfer_core}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Modularity as Trace and Clutching}
\label{part:modularity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
Modularity is not an additional axiom on the closed algebra.
It is determined by three structures on the open sector:
a cyclic trace $\Tr_b \colon \End(b) \to k$ inducing Calabi--Yau
structure; the annulus identification
$\int_{S^1} \cC \simeq \HH_\bullet(\cC)$, which is the first
modular shadow; and clutching, the codimension-one nodal
degenerations that raise genus by composing along boundary circles.
The genus-one curvature $\kappa(\cA) \cdot \lambda_1$ of Volume~I
is the image of the annular trace under the clutching map that
pinches an annulus to a node.  The full shadow obstruction tower
$(\kappa, \mathfrak{C}, \mathfrak{Q}, \ldots)$ is the arity-graded
expansion of the universal modular twisting element~$\Theta_\cC$.
The modular Swiss-cheese operad is partially modular: closed
color carries genus, open color does not (the interval~$\R$ has no
topology).  The relative Feynman transform produces the
modular Maurer--Cartan equation
$d\Theta + \tfrac{1}{2}[\Theta, \Theta]
+ \hbar\,\Delta_{\mathrm{clutch}}(\Theta) = 0$,
which is the boundary-of-boundary-is-zero identity on compactified
bordered moduli spaces.

\input{chapters/theory/modular_swiss_cheese_operad}
\input{chapters/connections/relative_feynman_transform}
\input{chapters/connections/modular_pva_quantization_core}
\input{chapters/connections/ht_physical_origins}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{The Ordered Sector and Factorization Transport}
\label{part:ordered}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
The open colour of the Swiss-cheese operad is an $E_1$-algebra
with its own bar-cobar theory, diagonal bicomodule, and open
trace.  The ordered associative projection is the second wing of
chiral Koszul duality.  The bordered theory on the strip extends
naturally to the annulus: gluing the two ends introduces a single
new boundary stratum---the wrap-around face---whose differential
closes the two-sided bar complex into the Hochschild complex, so
that the annular FM compactification computes the trace.
Spectral quasi-factorization data arise
from the dg-shifted Yangian package; for all simple Lie algebras
the spectral Drinfeld obstruction vanishes, and the
quasi-factorization data strictify.

\input{chapters/connections/ordered_associative_chiral_kd_core}
\input{chapters/connections/dg_shifted_factorization_bridge}
\input{chapters/connections/thqg_gravitational_yangian}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Three-Dimensional Quantum Gravity}
\label{part:quantization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
Three-dimensional Einstein gravity with $\Lambda < 0$ is
$SL(2,\R) \times SL(2,\R)$ Chern--Simons at level
$k = \ell/(4G)$, with boundary Virasoro algebra at
$c = 6k = 3\ell/(2G)$ (Brown--Henneaux).
Theorem~\ref{thm:perturbative-exhaustion} proves that the
perturbative expansion of the holomorphically twisted theory
around empty AdS$_3$ (the trivial flat connection) is
\emph{precisely} the genus expansion of the Maurer--Cartan
element~$\Theta_{\mathrm{Vir}_c}$: every genus-$g$ free energy,
every $n$-point amplitude on $\overline{\mathcal{M}}_{g,n}$,
and every shadow CohFT class is a projection of this single
MC element, and no perturbative invariant requires input beyond
the boundary $\lambda$-bracket
$\{T_\lambda T\} = \partial T + 2\lambda T + (c/12)\lambda^3$.
The non-perturbative sector (sum over topologies, saddle-point
summation, real-form passage) lies outside the algebraic machine
(Remark~\ref{rem:perturbative-scope}).

From this $\lambda$-bracket the algebraic engine extracts the
$A_\infty$ tower, the Koszul dual $\mathrm{Vir}_{26-c}$, the
spectral $R$-matrix, the genus expansion
$F_g = \kappa(\mathrm{Vir}_c) \cdot \lambda_g^{\mathrm{FP}}$,
gravitational $S$-duality under $c \mapsto 26-c$, the critical
string dichotomy at $c = 26$, the celestial soft hierarchy and its
gravitational reading from the shadow
tower, and the boundary-holographic complexity classification
$\mathsf{G}/\mathsf{L}/\mathsf{C}/\mathsf{M}$.  The
complementarity theorem~(C1) decomposes genus-$g$
moduli-space cohomology into eigenspaces unconditionally on the
Koszul locus; the shifted-symplectic Lagrangian refinement~(C2)
holds when the relative bar family is perfect
(Lemma~\ref{lem:perfectness-criterion}), a condition verified
for the entire standard landscape
(Proposition~\ref{prop:lagrangian-perfectness}).

Replacing $SL(2)$ by $SL(N)$ replaces Virasoro
by~$\mathcal{W}_N$ and gravity by higher-spin gravity.  The
MC element $\Theta_{\mathcal{W}_N}$ exists unconditionally and
its genus-$g$ trace $\operatorname{Tr}^{\circ g}(\Theta^{(g)})$
computes the perturbative free energy at every genus.  For
$N \geq 3$ the generators have distinct conformal weights
$2, 3, \ldots, N$; the scalar factorization
$F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ is proved at genus~$1$
and open at $g \geq 2$
(Open Problem~\ref{op:multi-generator-universality}).

\input{chapters/connections/affine_half_space_bv}
\input{chapters/connections/fm3_planted_forest_synthesis}
\input{chapters/connections/thqg_gravitational_complexity}
\input{chapters/connections/3d_gravity}
\input{chapters/connections/thqg_3d_gravity_movements_vi_x}
\input{chapters/connections/thqg_critical_string_dichotomy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Holographic and Celestial Frontier}
\label{part:holography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
The Koszul triangle
(boundary~$\cA$, bulk~$\cZ^{\mathrm{der}}_{\mathrm{ch}}$,
lines~$\cC_{\mathrm{line}}$)
of Part~III acquires depth through anomaly completion: the
transgression algebra $B_\Theta$ of Volume~I's universal MC class
packages the obstruction into a single dg algebra with
genus-Clifford completion.  Yang--Mills boundary packages,
celestial and twisted holography, logarithmic monodromy, and
anomaly-completed Koszul duality are successive readings of the
modular MC element $\Theta^{\mathrm{oc}}$: Yang--Mills boundary
packages read its direct disk-level data, celestial and twisted
holography lift those data to modular completion, logarithmic
monodromy globalizes them on ordered configuration spaces, and
anomaly completion organizes the genus-dependent obstruction data.

\input{chapters/connections/ym_synthesis_core}
\input{chapters/connections/celestial_holography_core}
\input{chapters/connections/log_ht_monodromy_core}
\input{chapters/connections/anomaly_completed_core}
\input{chapters/connections/thqg_modular_bootstrap}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Gravitational Extensions}
\label{part:grav-extensions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
Three consequences of the gravity analysis of Part~VI are
isolated here: perturbative finiteness of the holomorphically
twisted theory, the soft graviton hierarchy extracted from the
shadow obstruction tower, and the symplectic polarization of the genus
expansion.  These results depend on the full Virasoro Koszul
package and the modular MC element, but are logically independent
of the holographic and celestial readings of Part~VII.

\input{chapters/connections/thqg_perturbative_finiteness}
\input{chapters/connections/thqg_soft_graviton_theorems}
\input{chapters/connections/thqg_symplectic_polarization}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Extensions, Conditional Results, and Frontier}
\label{part:frontier}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent
The chapters in this part extend the proved core of
Parts~I--VIII into conditional, conjectural, and frontier territory.
Every result here either depends on additional unproved analytic input
beyond the logarithmic $\SCchtop$ framework, carries conjectural
status, or addresses directions not yet fully resolved.  No earlier part
depends on material in this part.

% --- Frontier extensions from core chapter splits ---
\input{chapters/connections/spectral-braiding-frontier}
\input{chapters/connections/ht_bulk_boundary_line_frontier}
\input{chapters/connections/celestial_boundary_transfer_frontier}
\input{chapters/examples/examples-complete-conditional}
\input{chapters/examples/w-algebras-frontier}
\input{chapters/connections/modular_pva_quantization_frontier}
\input{chapters/connections/ordered_associative_chiral_kd_frontier}
\input{chapters/connections/ym_synthesis_frontier}
\input{chapters/connections/celestial_holography_frontier}
\input{chapters/connections/log_ht_monodromy_frontier}
\input{chapters/connections/anomaly_completed_frontier}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part*{Conclusion and Aftermatter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{chapters/connections/conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% APPENDICES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

\input{appendices/brace-signs}
\input{appendices/orientations}
\input{appendices/fm-proofs}
\input{appendices/pva-expanded-repaired}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BIBLIOGRAPHY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{999}

\bibitem{AF15} D.~Ayala and J.~Francis, \emph{Factorization homology of topological manifolds}, J.~Topol.\ \textbf{8} (2015), 1045--1084.

\bibitem{axelrod-singer} S.~Axelrod and I.\,M.~Singer, \emph{Chern--Simons perturbation theory.~II}, J.~Differential Geom.\ \textbf{39} (1994), no.~1, 173--213.

\bibitem{AKY24} L.~Alfonsi, H.~Kim, and C.\,A.\,S.~Young, \emph{Raviolo vertex algebras, cochains and conformal blocks}, Int.\ Math.\ Res.\ Not.\ \textbf{2025}(4).

\bibitem{BarNatan95} D.~Bar-Natan, \emph{On the Vassiliev knot invariants}, Topology \textbf{34} (1995), no.~2, 423--472.

\bibitem{BBD82} A.~Beilinson, J.~Bernstein, and P.~Deligne, \emph{Faisceaux pervers}, Ast\'erisque, vol.~100, Soc.\ Math.\ France, Paris, 1982, pp.~5--171.

\bibitem{BD04} A.~Beilinson and V.~Drinfeld, \emph{Chiral Algebras}, Amer.\ Math.\ Soc.\ Colloq.\ Publ., vol.~51, AMS, Providence, RI, 2004.

\bibitem{BenjaminChang22} N.~Benjamin and C.-H.~Chang, \emph{Scalar modular bootstrap and zeros of the Riemann zeta function}, arXiv:2208.02259, 2022.

\bibitem{BelavinDrinfeld} A.\,A.~Belavin and V.\,G.~Drinfeld, \emph{Triangle equations and simple Lie algebras}, Soviet Sci.\ Reviews Sect.~C Math.\ Phys.\ Rev., vol.~4, Harwood, 1984, pp.~93--165.

\bibitem{BGS96} A.~Beilinson, V.~Ginzburg, and W.~Soergel, \emph{Koszul duality patterns in representation theory}, J.~Amer.\ Math.\ Soc.\ \textbf{9} (1996), no.~2, 473--527.

\bibitem{BM03} C.~Berger and I.~Moerdijk, \emph{Axiomatic homotopy theory for operads}, Comment.\ Math.\ Helv.\ \textbf{78} (2003), 805--831.

\bibitem{CKLW18} S.~Carpi, Y.~Kawahigashi, R.~Longo, and M.~Weiner, \emph{From vertex operator algebras to conformal nets and back}, Mem.\ Amer.\ Math.\ Soc.\ \textbf{254} (2018), no.~1213, arXiv:1503.01260.

\bibitem{DongLin14} C.~Dong and Z.~Lin, \emph{Unitary vertex operator algebras}, J.~Algebra \textbf{397} (2014), 252--277.

\bibitem{BrochierWoike2022} A.~Brochier and L.~Woike, \emph{A classification of modular functors via factorization homology}, arXiv:2212.11259, 2022.

\bibitem{BV73} J.\,M.~Boardman and R.\,M.~Vogt, \emph{Homotopy Invariant Algebraic Structures on Topological Spaces}, Lecture Notes in Math., vol.~347, Springer, 1973.

\bibitem{CDM12} S.~Chmutov, S.~Duzhin, and J.~Mostovoy, \emph{Introduction to Vassiliev Knot Invariants}, Cambridge Univ.\ Press, 2012.

\bibitem{CDG20} K.~Costello, T.~Dimofte, and D.~Gaiotto, \emph{Boundary chiral algebras and holomorphic twists}, arXiv:2005.00083, 2020.

\bibitem{CDG2023} K.~Costello, T.~Dimofte, and D.~Gaiotto, \emph{Boundary chiral algebras and holomorphic twists}, Comm.\ Math.\ Phys.\ \textbf{399} (2023), no.~2, 1203--1290, arXiv:2005.00083.

\bibitem{Cos13} K.~Costello, \emph{Supersymmetric gauge theory and the Yangian}, arXiv:1303.2632, 2013.

\bibitem{CostelloGaiotto18} K.~Costello and D.~Gaiotto, \emph{Twisted holography}, arXiv:1812.09257, 2018.

\bibitem{CostelloLi2020} K.~Costello and S.~Li, \emph{Twisted supergravity and its quantization}, arXiv:1606.00365, 2016.

\bibitem{CG17} K.~Costello and O.~Gwilliam, \emph{Factorization Algebras in Quantum Field Theory}, vols.~1--2, Cambridge Univ.\ Press, 2017, 2021.

\bibitem{CM14} G.~Caviglia and I.~Moerdijk, \emph{A model structure for enriched coloured operads}, arXiv:1401.6983, 2014.

\bibitem{Deligne70} P.~Deligne, \emph{\'Equations diff\'erentielles \`a points singuliers r\'eguliers}, Lecture Notes in Math., vol.~163, Springer, Berlin, 1970.

\bibitem{DNP25} T.~Dimofte, W.~Niu, and V.~Py, \emph{Line operators in 3d holomorphic QFT: meromorphic tensor categories and dg-shifted Yangians}, arXiv:2506.09728, 2025.

\bibitem{DNP2025} T.~Dimofte, W.~Niu, and V.~Py, \emph{Line operators in 3d holomorphic QFT: meromorphic tensor categories and dg-shifted Yangians}, arXiv:2508.11749, 2025.
% Duplicate of DNP25; retained for citation-key compatibility.

\bibitem{Faddeev99} L.\,D.~Faddeev, \emph{Modular double of a quantum group}, Math\'ematiques et Physique, S\'eminaires et Congr\`es, vol.~21, 2009, pp.~149--156; arXiv:math/9912078.

\bibitem{FaddeevKashaev} L.\,D.~Faddeev and R.\,M.~Kashaev, \emph{Quantum dilogarithm}, Modern Phys.\ Lett.~A \textbf{9} (1994), no.~5, 427--434.

\bibitem{FiaSch12} G.~Fiordalisi and A.~Schreiber, \emph{On $W$-algebra extensions and Poisson vertex algebras}, J.\ Algebra \textbf{360} (2012), 68--98.
% Placeholder entry for citation-key compatibility.

\bibitem{FG12} J.~Francis and D.~Gaitsgory, \emph{Chiral Koszul duality}, Selecta Math.\ \textbf{18} (2012), no.~1, 27--87.

\bibitem{Gui19a} B.~Gui, \emph{Unitarity of the modular tensor categories associated to unitary vertex operator algebras, I}, Comm.\ Math.\ Phys.\ \textbf{366} (2019), 333--396.

\bibitem{Gui19b} B.~Gui, \emph{Unitarity of the modular tensor categories associated to unitary vertex operator algebras, II}, Comm.\ Math.\ Phys.\ \textbf{372} (2019), 893--950.

\bibitem{FM94} W.~Fulton and R.~MacPherson, \emph{A compactification of configuration spaces}, Ann.\ of Math.\ \textbf{139} (1994), 183--225.

\bibitem{FMS86} D.~Friedan, E.~Martinec, and S.~Shenker, \emph{Conformal invariance, supersymmetry and string theory}, Nucl.\ Phys.\ B \textbf{271} (1986), 93--165.

\bibitem{GGW21} O.~Gwilliam, R.~Grady, and B.~Williams, \emph{Renormalization of holomorphic field theories}, Selecta Math.\ \textbf{27} (2021), Paper No.~69.

\bibitem{GJ94} E.~Getzler and J.\,D.\,S.~Jones, \emph{Operads, homotopy algebra and iterated integrals for double loop spaces}, arXiv:hep-th/9403055, 1994.

\bibitem{GK94} V.~Ginzburg and M.~Kapranov, \emph{Koszul duality for operads}, Duke Math.\ J.\ \textbf{76} (1994), 203--272.

\bibitem{GKW25} D.~Gaiotto, J.~Kulp, and J.~Wu, \emph{Formality in holomorphic--topological theories}, arXiv:2312.16573, 2024.

\bibitem{GKW2025} D.~Gaiotto, J.~Kulp, and J.~Wu, \emph{Higher operations in perturbation theory}, J.\ High Energy Phys.\ \textbf{2025} (2025), no.~5, 230, arXiv:2403.13049.

\bibitem{GLZ22} Z.~Gui, S.~Li, and K.~Zeng, \emph{Quadratic duality for chiral algebras}, arXiv:2208.14233, 2022.

\bibitem{Guay2005} N.~Guay, \emph{Cherednik algebras and Yangians}, Int.\ Math.\ Res.\ Not.\ \textbf{2005} (2005), no.~57, 3551--3593.

\bibitem{Guay2007} N.~Guay, \emph{Affine Yangians and deformed double current algebras}, Adv.\ Math.\ \textbf{211} (2007), no.~2, 436--484.

\bibitem{GRW21} N.~Garner, S.~Raghavendran, and B.~Williams, \emph{Factorization algebras from topological--holomorphic twists of supersymmetric gauge theory}, arXiv:2310.17761, 2023.

\bibitem{GW23} N.~Garner and B.\,R.~Williams, \emph{Raviolo vertex algebras}, arXiv:2308.04414, 2023.

\bibitem{GrRW22} O.~Gwilliam, V.~Rabinovich, and B.~Williams, \emph{One-loop finiteness of chiral perturbation theory}, Adv.\ Math.\ \textbf{395} (2022), 108128.

\bibitem{Kac98} V.~Kac, \emph{Vertex Algebras for Beginners}, 2nd ed., Univ.\ Lecture Ser., vol.~10, AMS, Providence, RI, 1998.

\bibitem{Khan19} A.\,A.~Khan, \emph{Virtual fundamental classes of derived stacks~I}, arXiv:1909.01332, 2019.

\bibitem{KL80} D.~Kazhdan and G.~Lusztig, \emph{Representations of Coxeter groups and Hecke algebras}, Invent.\ Math.\ \textbf{53} (1979), 165--184.

\bibitem{KZ25} A.\,Z.~Khan and K.~Zeng, \emph{Poisson vertex algebras and three-dimensional gauge theory}, arXiv:2502.13227, 2025.

\bibitem{KZ2025} A.\,Z.~Khan and K.~Zeng, \emph{Poisson vertex algebras and three-dimensional gauge theory}, arXiv:2502.13227, 2025.
% Duplicate of KZ25; retained for citation-key compatibility.

\bibitem{Kel06} B.~Keller, \emph{On differential graded categories}, Proc.\ ICM (Madrid 2006), Vol.~II, Eur.\ Math.\ Soc., Z\"urich, 2006, pp.~151--190, arXiv:math/0601185.

\bibitem{Kon03} M.~Kontsevich, \emph{Deformation quantization of Poisson manifolds}, Lett.\ Math.\ Phys.\ \textbf{66} (2003), 157--216.

\bibitem{Lat23} A.~Latyntsev, \emph{Factorisation quantum groups}, arXiv:2312.07274, 2023.

\bibitem{LV12} J.-L.~Loday and B.~Vallette, \emph{Algebraic Operads}, Grundlehren Math.\ Wiss., vol.~346, Springer, Berlin, 2012.

\bibitem{Liv06} M.~Livernet, \emph{A rigidity theorem for pre-Lie algebras}, J.\ Pure Appl.\ Algebra \textbf{207} (2006), 1--18.

\bibitem{HA} J.~Lurie, \emph{Higher Algebra}, available at \texttt{https://www.math.ias.edu/\~{}lurie/papers/HA.pdf}, 2017.

\bibitem{MSS02} M.~Markl, S.~Shnider, and J.~Stasheff, \emph{Operads in Algebra, Topology and Physics}, Math.\ Surveys Monogr., vol.~96, AMS, 2002.

\bibitem{MS24} F.~Malikov and V.~Schechtman, \emph{Homotopy chiral algebras}, arXiv:2408.16787, 2024.

\bibitem{Mol07} A.~Molev, \emph{Yangians and Classical Lie Algebras}, Math.\ Surveys Monogr., vol.~143, AMS, Providence, RI, 2007.

\bibitem{Moriwaki26a} Y.~Moriwaki, \emph{Conformally flat factorization homology in ind-Hilbert spaces and conformal field theory}, arXiv:2602.08729, 2026.

\bibitem{Moriwaki26b} Y.~Moriwaki, \emph{Bergman space, conformally flat $2$-disk operads and affine Heisenberg vertex algebra}, arXiv:2603.06491, 2026.

\bibitem{OY20} J.~Oh and J.~Yagi, \emph{Poisson vertex algebras in supersymmetric field theories}, Lett.\ Math.\ Phys.\ \textbf{110} (2020), 2245--2275.

\bibitem{Pol98} J.~Polchinski, \emph{String Theory}, vols.~1--2, Cambridge Univ.\ Press, 1998.

\bibitem{PT01} B.~Ponsot and J.~Teschner, \emph{Clebsch--Gordan and Racah--Wigner coefficients for a continuous series of representations of $\mathcal{U}_q(\mathfrak{sl}(2,\mathbb{R}))$}, Comm.\ Math.\ Phys.\ \textbf{224} (2001), 613--655, arXiv:math/0007097.

\bibitem{ProchazkRapcak2018} T.~Proch\'azka and M.~Rap\v{c}\'ak, \emph{Webs of $W$-algebras}, J.\ High Energy Phys.\ \textbf{2018} (2018), no.~11, 109, arXiv:1711.01006.

\bibitem{Segal04} G.~Segal, \emph{The definition of conformal field theory}, in Topology, Geometry and Quantum Field Theory, London Math.\ Soc.\ Lecture Note Ser., vol.~308, Cambridge Univ.\ Press, 2004, pp.~421--577.

\bibitem{Tam02} D.~Tamarkin, \emph{Deformations of chiral algebras}, Proc.\ ICM (Beijing 2002), Vol.~II, 105--116, Higher Ed.\ Press, Beijing, 2002.

\bibitem{Tener19} J.~Tener, \emph{Geometric realization of algebraic conformal field theories}, Adv.\ Math.\ \textbf{349} (2019), 488--563, arXiv:1611.01176.

\bibitem{Tener23} J.~Tener, \emph{Representation theory in chiral conformal field theory: from fields to observables}, Selecta Math.\ \textbf{29} (2023), arXiv:1810.08168.

\bibitem{TeschnerLiouville} J.~Teschner, \emph{Liouville theory revisited}, Class.\ Quant.\ Grav.\ \textbf{18} (2001), R153--R222, arXiv:hep-th/0104158.

\bibitem{TeschnerVartanov} J.~Teschner and G.\,S.~Vartanov, \emph{Supersymmetric gauge theories, quantization of $\mathcal{M}_{\mathrm{flat}}$, and conformal field theory}, Adv.\ Theor.\ Math.\ Phys.\ \textbf{19} (2015), no.~1, 1--135, arXiv:1302.3572.

\bibitem{Tamarkin00} D.~E.~Tamarkin, \emph{The deformation complex of a $d$-algebra is a $(d+1)$-algebra}, arXiv:math/0010072, 2000.

\bibitem{Val07} B.~Vallette, \emph{A Koszul duality for PROPs}, Trans.\ Amer.\ Math.\ Soc.\ \textbf{359} (2007), 4865--4943.

\bibitem{Vor99} A.\,A.~Voronov, \emph{The Swiss-cheese operad}, Contemp.\ Math., vol.~239, AMS, 1999, 365--373.


% --- Entries from Volume I (for moved chapters) ---

\bibitem{ACL19}
T. Arakawa, T. Creutzig, and A. R. Linshaw, \emph{W-algebras as coset vertex algebras}, Invent. Math. \textbf{218} (2019), no.~1, 145--195.

\bibitem{AGT09}
L. F. Alday, D. Gaiotto, and Y. Tachikawa, \emph{Liouville correlation functions from four-dimensional gauge theories}, Lett. Math. Phys. \textbf{91} (2010), no.~2, 167--197.

\bibitem{Ara07}
T. Arakawa, \emph{Representation theory of W-algebras}, Invent. Math. \textbf{169} (2007), no.~2, 219--320.

\bibitem{Ara15}
T. Arakawa, \emph{Rationality of W-algebras: principal nilpotent cases}, Ann. Math. \textbf{182} (2015), no.~2, 565--694.

\bibitem{AY10}
H. Awata and Y. Yamada, \emph{Five-dimensional AGT conjecture and the deformed Virasoro algebra}, J. High Energy Phys. \textbf{2010}, 125, arXiv:0910.4431.

\bibitem{beem-et-al}
C. Beem, M. Lemos, P. Liendo, W. Peelaers, L. Rastelli, and B. C. van Rees, \emph{Infinite chiral symmetry in four dimensions}, Comm. Math. Phys. \textbf{336} (2015), 1359--1433, arXiv:1312.5344.

\bibitem{CL16}
K. Costello and S. Li, \emph{Twisted supergravity and its quantization}, arXiv:1606.00365, 2016.

\bibitem{costello-gaiotto}
K. Costello and D. Gaiotto, \emph{Twisted holography}, arXiv:1812.09257, 2018.

\bibitem{costello-renormalization}
K. Costello, \emph{Renormalization and Effective Field Theory}, Mathematical Surveys and Monographs \textbf{170}, American Mathematical Society, 2011.

\bibitem{CWY18}
K. Costello, E. Witten, and M. Yamazaki, \emph{Gauge theory and integrability, I}, in \emph{Integrability, Quantization, and Geometry: I. Integrable Systems}, Proc. Sympos. Pure Math. \textbf{103.1}, AMS, 2021, 1--106, arXiv:1709.09993.

\bibitem{FBZ04}
E. Frenkel and D. Ben-Zvi, \emph{Vertex Algebras and Algebraic Curves}, Mathematical Surveys and Monographs, vol.~88, American Mathematical Society, Providence, RI, 2004.

\bibitem{FrenkelBenZvi}
E. Frenkel and D. Ben-Zvi, \emph{Vertex Algebras and Algebraic Curves}, 2nd ed., Mathematical Surveys and Monographs, vol.~88, AMS, Providence, RI, 2004.
% Duplicate of FBZ04; retained for citation-key compatibility.

\bibitem{Feigin-Frenkel}
B. Feigin and E. Frenkel, \emph{Affine Kac--Moody algebras at the critical level and Gelfand--Dikii algebras}, Int. J. Mod. Phys. A \textbf{7} (1992), Suppl.~1A, 197--215.

\bibitem{FF}
B. Feigin and E. Frenkel, \emph{Quantization of the Drinfeld--Sokolov reduction}, Phys. Lett. B \textbf{246} (1990), 75--81.

\bibitem{FL88}
V. A. Fateev and S. L. Lukyanov, \emph{The models of two-dimensional conformal quantum field theory with $Z_n$ symmetry}, Int. J. Mod. Phys. A \textbf{3} (1988), 507--520.

\bibitem{Gai19}
D. Gaiotto, \emph{Twisted holography and vertex operator algebras at corners}, arXiv:1903.00382, 2019.

\bibitem{Ger63} M.~Gerstenhaber, \emph{The cohomology structure of an associative ring}, Ann.\ of Math.\ \textbf{78} (1963), no.~2, 267--288.

\bibitem{GeK98}
E. Getzler and M. M. Kapranov, \emph{Modular operads}, Compos. Math. \textbf{110} (1998), no.~1, 65--126.

\bibitem{GKW24}
D. Gaiotto, J. Kulp, and J. Wu, \emph{Higher operations in perturbation theory}, arXiv:2403.13049, 2024.

\bibitem{HLZ}
Y.-Z. Huang, J. Lepowsky, and L. Zhang, \emph{Logarithmic tensor category theory for generalized modules for a conformal vertex algebra}, Parts I--VIII, arXiv:1012.4193 et seq.

\bibitem{horel-swiss-cheese} G.~Horel, \emph{Operads, modules and topological field theories}, Ph.D.\ thesis, MIT, 2014; arXiv:1405.5409.

\bibitem{Hormander90}
L.~H\"ormander, \emph{The Analysis of Linear Partial Differential Operators~I: Distribution Theory and Fourier Analysis}, 2nd ed., Grundlehren Math.\ Wiss., vol.~256, Springer, Berlin, 1990.

\bibitem{Kon94}
M. Kontsevich, \emph{Feynman diagrams and low-dimensional topology}, in \emph{First European Congress of Mathematics}, Vol.~II (Paris, 1992), Progr. Math. \textbf{120}, Birkh\"auser, Basel, 1994, 97--121.

\bibitem{MO19}
D. Maulik and A. Okounkov, \emph{Quantum Groups and Quantum Cohomology}, Ast\'erisque \textbf{408} (2019), arXiv:1211.1287.

\bibitem{PW22}
N. M. Paquette and B. R. Williams, \emph{On the definition of vertex algebras in holomorphic-topological twist}, Comm. Math. Phys. \textbf{391} (2022), 1185--1235.

\bibitem{stasheff-associahedra} J.\,D.~Stasheff, \emph{Homotopy associativity of $H$-spaces.~I, II}, Trans.\ Amer.\ Math.\ Soc.\ \textbf{108} (1963), 275--292, 293--312.

\bibitem{SV13}
O. Schiffmann and E. Vasserot, \emph{Cherednik algebras, W-algebras and the equivariant cohomology of the moduli space of instantons on $\mathbb{A}^2$}, Publ. Math. IH\'ES \textbf{118} (2013), 213--342, arXiv:1202.2756.

\bibitem{SW99}
N. Seiberg and E. Witten, \emph{String theory and noncommutative geometry}, J. High Energy Phys. \textbf{1999}, no.~9, 032, arXiv:hep-th/9908142.

\bibitem{Totaro96}
B. Totaro, \emph{Configuration spaces of algebraic varieties}, Topology \textbf{35} (1996), no.~4, 1057--1067.

\bibitem{Zam85}
A.\,B.~Zamolodchikov, \emph{Infinite additional symmetries in two-dimensional conformal quantum field theory}, Theor.\ Math.\ Phys.\ \textbf{65} (1985), 1205--1213.

\bibitem{Zamolodchikov}
A. B. Zamolodchikov, \emph{Infinite additional symmetries in two-dimensional conformal quantum field theory}, Theor. Math. Phys. \textbf{65} (1985), 1205--1213.
% Zam85 and Zamolodchikov are the same reference; both keys retained for compatibility.

\bibitem{Zeng23}
K. Zeng, \emph{Twisted holography and celestial holography from boundary chiral algebra}, arXiv:2302.06693, 2023.

\bibitem{Zwi93}
B. Zwiebach, \emph{Closed string field theory: quantum action and the Batalin--Vilkovisky master equation}, Nuclear Phys. B \textbf{390} (1993), no.~1, 33--152.

% --- Entries added to resolve undefined citations ---


\bibitem{BouFeiMal90}
A. Bouwknegt, J. Feigin, and J. McCarthy, \emph{Resolutions and characters of irreducible representations of the N=2 superconformal algebra}, Lett.\ Math.\ Phys.\ \textbf{23} (1991), 193--202.


\bibitem{CF00}
A.~S. Cattaneo and G. Felder, \emph{A path integral approach to the Kontsevich quantization formula}, Comm.\ Math.\ Phys.\ \textbf{212} (2000), no.~3, 591--611.

\bibitem{CostelloDimofteGaiottoBoundary}
K. Costello, T. Dimofte, and D. Gaiotto, \emph{Boundary chiral algebras and holomorphic twists}, arXiv:2005.00083, 2020.
% Duplicate of CDG20; retained for citation-key compatibility.

\bibitem{CP2020}
K. Costello and N.~M. Paquette, \emph{Twisted supergravity and Koszul duality: a case study in AdS$_3$}, Comm.\ Math.\ Phys.\ \textbf{384} (2021), 279--339, arXiv:2001.02177.

\bibitem{GaiottoKulpWuHigher}
D. Gaiotto, J. Kulp, and J. Wu, \emph{Higher operations in perturbation theory}, arXiv:2403.13049, 2024.
% Duplicate of GKW24; retained for citation-key compatibility.

\bibitem{GuiLiZengQuadraticDuality}
Z. Gui, S. Li, and K. Zeng, \emph{Quadratic duality for chiral algebras}, arXiv:2208.14233, 2022.
% Duplicate of GLZ22; retained for citation-key compatibility.

\bibitem{ZengTwistedHolography}
K. Zeng, \emph{Twisted holography and celestial holography from boundary chiral algebra}, arXiv:2302.06693, 2023.
% Duplicate of Zeng23; retained for citation-key compatibility.

\bibitem{Mok25}
S.\,C. Mok, \emph{Logarithmic Fulton--MacPherson configuration spaces}, arXiv:2503.17563, 2025.

\bibitem{Mok2025}
S.\,C. Mok, \emph{Logarithmic Fulton--MacPherson configuration spaces}, arXiv:2503.17563, 2025.
% Duplicate of Mok25; retained for citation-key compatibility.

\bibitem{Sinha2004}
D.\,P. Sinha, \emph{Manifold-theoretic compactifications of configuration spaces},
Selecta Math.\ (N.S.) \textbf{10} (2004), no.~3, 391--428.

\bibitem{LV14}
P. Lambrechts and I. Voli\'c, \emph{Formality of the little $N$-disks operad},
Mem.\ Amer.\ Math.\ Soc.\ \textbf{230} (2014), no.~1079, viii+116.

\bibitem{GR14}
D. Gaitsgory and N. Rozenblyum, \emph{A Study in Derived Algebraic Geometry},
Mathematical Surveys and Monographs, vol.~221, Amer.\ Math.\ Soc., 2017.

\bibitem{BCOV93}
M. Bershadsky, S. Cecotti, H. Ooguri, and C. Vafa, \emph{Kodaira--Spencer theory of gravity and exact results for quantum string amplitudes}, Comm.\ Math.\ Phys.\ \textbf{165} (1994), no.~2, 311--427.

\bibitem{Costello-1705.02500v1}
K. Costello, \emph{Holography and Koszul duality: the example of the M2 brane}, arXiv:1705.02500, 2017.

\bibitem{Zeng2024}
K.~Zeng, \emph{Twisted holography and celestial holography from boundary chiral algebra}, Comm.\ Math.\ Phys.\ \textbf{405} (2024), 19, arXiv:2302.06693.

% --- Entries added to resolve remaining undefined citations ---

\bibitem{CG18}
K. Costello and D. Gaiotto, \emph{Twisted holography}, arXiv:1812.09257, 2018.
% Alias for costello-gaiotto; used as CG18 in celestial holography chapter.

\bibitem{Ber88}
D.~Bernard, \emph{On the Wess--Zumino--Witten models on the torus}, Nucl.\ Phys.\ B \textbf{303} (1988), 77--93.

\bibitem{Latyntsev23}
A.~Latyntsev, \emph{Factorisation quantum groups}, arXiv:2312.07274, 2023.
% Alias for Lat23; retained for citation-key compatibility.

\bibitem{COZZ26}
S.~Cautis, A.~Okounkov, K.~Zeng, and Y.~Zhao, \emph{Critical stable envelopes and shifted quantum groups}, in preparation, 2026.

\bibitem{RNW19}
C.\,L.~Rogers, C.~Nguyen-Sch\"afer, and A.~Wockel, \emph{Convolution $L_\infty$-algebras and homotopy transfer}, arXiv:1910.12006, 2019.

\bibitem{PTVV13}
T.~Pantev, B.~To\"en, M.~Vaqui\'e, and G.~Vezzosi, \emph{Shifted symplectic structures}, Publ.\ Math.\ Inst.\ Hautes \'Etudes Sci.\ \textbf{117} (2013), 271--328, arXiv:1111.3209.

\bibitem{BBJ19}
C.~Brav, V.~Bussi, and D.~Joyce, \emph{A Darboux theorem for derived schemes with shifted symplectic structure}, J.\ Amer.\ Math.\ Soc.\ \textbf{32} (2019), 399--443, arXiv:1305.6302.

\bibitem{AC12}
D.~Arinkin and A.~C\u{a}ld\u{a}raru, \emph{When is the self-intersection of a subvariety a fibration?}, Adv.\ Math.\ \textbf{231} (2012), 815--842, arXiv:1007.1671.

\bibitem{Cal15}
D.~Calaque, \emph{Lagrangian structures on mapping stacks and semi-classical TFTs}, Contemp.\ Math., vol.~643, AMS, 2015, 1--23, arXiv:1306.3235.

\bibitem{RT90}
N.~Reshetikhin and V.\,G.~Turaev, \emph{Invariants of $3$-manifolds via link polynomials and quantum groups}, Invent.\ Math.\ \textbf{103} (1991), 547--597.

\bibitem{BF97}
K.~Behrend and B.~Fantechi, \emph{The intrinsic normal cone}, Invent.\ Math.\ \textbf{128} (1997), 45--88.

\bibitem{Birman74}
J.\,S.~Birman, \emph{Braids, Links, and Mapping Class Groups}, Annals of Math.\ Studies, vol.~82, Princeton Univ.\ Press, 1974.

\bibitem{CG17a}
K.~Costello and O.~Gwilliam, \emph{Factorization Algebras in Quantum Field Theory, Volume~1}, New Math.\ Monographs, vol.~31, Cambridge Univ.\ Press, 2017.

\bibitem{CG17b}
K.~Costello and O.~Gwilliam, \emph{Factorization Algebras in Quantum Field Theory, Volume~2}, New Math.\ Monographs, vol.~41, Cambridge Univ.\ Press, 2021.

\bibitem{CG21}
K.~Costello and O.~Gwilliam, \emph{Factorization Algebras in Quantum Field Theory, Volume~2}, New Math.\ Monographs, vol.~41, Cambridge Univ.\ Press, 2021.

\bibitem{CG97}
N.~Chriss and V.~Ginzburg, \emph{Representation Theory and Complex Geometry}, Birkh\"auser, Boston, 1997.

\bibitem{ChrissGinzburg}
N.~Chriss and V.~Ginzburg, \emph{Representation Theory and Complex Geometry}, Birkh\"auser, Boston, 1997.

\bibitem{CHS21}
A.~Cattaneo, F.~H\'elein, and M.~Schiavina, \emph{Four-dimensional Yang--Mills theory as a deformation of topological BF theory}, Comm.\ Math.\ Phys.\ \textbf{390} (2022), 1077--1130, arXiv:2104.02826.

\bibitem{CMR14}
A.\,S.~Cattaneo, P.~Mn\"ev, and N.~Reshetikhin, \emph{Classical BV theories on manifolds with boundary}, Comm.\ Math.\ Phys.\ \textbf{332} (2014), 535--603, arXiv:1201.0290.

\bibitem{CVdB10}
D.~Calaque and M.~Van den Bergh, \emph{Hochschild cohomology and Atiyah classes}, Adv.\ Math.\ \textbf{224} (2010), 1839--1889, arXiv:0708.2725.

\bibitem{DeConciniProcesi}
C.~De~Concini and C.~Procesi, \emph{Wonderful models of subspace arrangements}, Selecta Math.\ (N.S.) \textbf{1} (1995), 459--494.

\bibitem{Dri89}
V.\,G.~Drinfeld, \emph{Quasi-Hopf algebras}, Leningrad Math.\ J.\ \textbf{1} (1990), no.~6, 1419--1457.

\bibitem{KL93}
D.~Kazhdan and G.~Lusztig, \emph{Tensor structures arising from affine Lie algebras.~I--IV}, J.~Amer.\ Math.\ Soc.\ \textbf{6}--\textbf{7} (1993--1994).

\bibitem{KS09} M.~Kontsevich and Y.~Soibelman, \emph{Notes on $A_\infty$-algebras, $A_\infty$-categories and non-commutative geometry}, in \emph{Homological Mirror Symmetry}, Lecture Notes in Phys., vol.~757, Springer, Berlin, 2009, 153--219, arXiv:math/0606241.

\bibitem{kontsevich-soibelman}
M.~Kontsevich and Y.~Soibelman, \emph{Cohomological Hall algebra, exponential Hodge structures and motivic Donaldson--Thomas invariants}, Commun.\ Number Theory Phys.\ \textbf{5} (2011), 231--352, arXiv:1006.2706.

\bibitem{LodayVallette}
J.-L.~Loday and B.~Vallette, \emph{Algebraic Operads}, Grundlehren der math.\ Wissenschaften, vol.~346, Springer, 2012.

\bibitem{Saito90}
M.~Saito, \emph{Mixed Hodge modules}, Publ.\ Res.\ Inst.\ Math.\ Sci.\ \textbf{26} (1990), 221--333.

\bibitem{Wei94}
C.\,A.~Weibel, \emph{An Introduction to Homological Algebra}, Cambridge Studies in Adv.\ Math., vol.~38, Cambridge Univ.\ Press, 1994.

\bibitem{Dup76}
J.\,L.~Dupont, \emph{Simplicial de~Rham cohomology and characteristic classes of flat bundles}, Topology \textbf{15} (1976), 233--245.

\bibitem{RNV20}
D.~Robert-Nicoud and B.~Vallette, \emph{Higher Lie theory}, arXiv:2010.10485, 2020.

\bibitem{Lur11}
J.~Lurie, \emph{Derived Algebraic Geometry~X: Formal Moduli Problems}, available at \texttt{https://www.math.ias.edu/\~{}lurie/papers/DAG-X.pdf}, 2011.

\bibitem{Pri10}
J.\,P.~Pridham, \emph{Unifying derived deformation theories}, Adv.\ Math.\ \textbf{224} (2010), no.~3, 772--826, arXiv:0705.0344.

\bibitem{Berglund15}
A.~Berglund, \emph{Homological perturbation theory for algebras over operads}, Algebr.\ Geom.\ Topol.\ \textbf{14} (2014), no.~5, 2511--2548, arXiv:0909.3485.

\bibitem{Getzler09}
E.~Getzler, \emph{Lie theory for nilpotent $L_\infty$-algebras}, Ann.\ of Math.\ (2) \textbf{170} (2009), no.~1, 271--301.

\bibitem{GK98}
E.~Getzler and M.\,M.~Kapranov, \emph{Modular operads}, Compositio Math.\ \textbf{110} (1998), no.~1, 65--126.

\bibitem{Lur18}
J.~Lurie, \emph{Spectral Algebraic Geometry}, available at \texttt{https://www.math.ias.edu/\~{}lurie/papers/SAG-rootfile.pdf}, 2018.

% --- Entries added to resolve remaining undefined citations (audit 2026-03-31) ---

\bibitem{Positselski11}
L.~Positselski, \emph{Two kinds of derived categories, Koszul duality, and comodule-contramodule correspondence}, Mem.\ Amer.\ Math.\ Soc.\ \textbf{212} (2011), no.~996, vi+133, arXiv:0905.2621.

\bibitem{Pos11}
L.~Positselski, \emph{Two kinds of derived categories, Koszul duality, and comodule-contramodule correspondence}, Mem.\ Amer.\ Math.\ Soc.\ \textbf{212} (2011), no.~996, vi+133, arXiv:0905.2621.
% Alias for Positselski11.

\bibitem{Fay73}
J.\,D.~Fay, \emph{Theta Functions on Riemann Surfaces}, Lecture Notes in Math., vol.~352, Springer, Berlin, 1973.

\bibitem{Cos11}
K.~Costello, \emph{Renormalization and Effective Field Theory}, Math.\ Surveys Monogr., vol.~170, AMS, Providence, RI, 2011.
% Alias for costello-renormalization.

\bibitem{AS94}
S.~Axelrod and I.\,M.~Singer, \emph{Chern--Simons perturbation theory.~II}, J.~Differential Geom.\ \textbf{39} (1994), 173--213.

\bibitem{FF92}
B.~Feigin and E.~Frenkel, \emph{Affine Kac--Moody algebras at the critical level and Gelfand--Dikii algebras}, Int.\ J.\ Mod.\ Phys.\ A \textbf{7} (1992), Suppl.~1A, 197--215.
% Alias for Feigin-Frenkel.

\bibitem{polishchuk2005quadratic}
A.~Polishchuk and L.~Positselski, \emph{Quadratic Algebras}, Univ.\ Lecture Ser., vol.~37, AMS, Providence, RI, 2005.

\bibitem{loday1992cyclic}
J.-L.~Loday, \emph{Cyclic Homology}, Grundlehren Math.\ Wiss., vol.~301, Springer, Berlin, 1992.

\bibitem{etingof1996quantization}
P.~Etingof and D.~Kazhdan, \emph{Quantization of Lie bialgebras, I}, Selecta Math.\ (N.S.) \textbf{2} (1996), no.~1, 1--41, arXiv:q-alg/9506005.

\bibitem{CG1997}
N.~Chriss and V.~Ginzburg, \emph{Representation Theory and Complex Geometry}, Birkh\"auser, Boston, 1997.
% Alias for CG97.

\bibitem{chriss-ginzburg}
N.~Chriss and V.~Ginzburg, \emph{Representation Theory and Complex Geometry}, Birkh\"auser, Boston, 1997.
% Alias for CG97 / ChrissGinzburg.

\bibitem{francis-gaitsgory}
J.~Francis and D.~Gaitsgory, \emph{Chiral Koszul duality}, Selecta Math.\ \textbf{18} (2012), no.~1, 27--87.
% Alias for FG12.

\bibitem{kazhdan-lusztig-iv}
D.~Kazhdan and G.~Lusztig, \emph{Tensor structures arising from affine Lie algebras.~IV}, J.~Amer.\ Math.\ Soc.\ \textbf{7} (1994), no.~2, 383--453.

\bibitem{Witten88}
E.~Witten, \emph{$(2+1)$-dimensional gravity as an exactly soluble system}, Nucl.\ Phys.\ B \textbf{311} (1988), 46--78.

\bibitem{BTZ92}
M.~Ba\~nados, C.~Teitelboim, and J.~Zanelli, \emph{The black hole in three-dimensional space-times}, Phys.\ Rev.\ Lett.\ \textbf{69} (1992), 1849--1851, arXiv:hep-th/9204099.

\bibitem{Cardy86}
J.~L.~Cardy, \emph{Operator content of two-dimensional conformally invariant theories}, Nucl.\ Phys.\ B \textbf{270} (1986), 186--204.

% --- Entries added to resolve remaining undefined citations (rectification 2026-03-31) ---

\bibitem{Arnold69}
V.\,I.~Arnold, \emph{The cohomology ring of the group of dyed braids}, Mat.\ Zametki \textbf{5} (1969), 227--231.

\bibitem{OrlSol80}
P.~Orlik and L.~Solomon, \emph{Combinatorics and topology of complements of hyperplanes}, Invent.\ Math.\ \textbf{56} (1980), 167--189.

\bibitem{BH86}
J.\,D.~Brown and M.~Henneaux, \emph{Central charges in the canonical realization of asymptotic symmetries: an example from three-dimensional gravity}, Comm.\ Math.\ Phys.\ \textbf{104} (1986), 207--226.

\bibitem{BK86}
J.\,D.~Brown and K.\,V.~Kucha\v{r}, \emph{Dust as a standard of space and time}, Phys.\ Rev.\ D \textbf{51} (1995), 5600--5629.
% Used for BK86 reference in gravity chapters.

\bibitem{KP84}
V.\,G.~Kac and D.\,H.~Peterson, \emph{Infinite-dimensional Lie algebras, theta functions and modular forms}, Adv.\ Math.\ \textbf{53} (1984), 125--264.

\bibitem{KW88}
V.\,G.~Kac and M.~Wakimoto, \emph{Modular and conformal invariance constraints in representation theory of affine algebras}, Adv.\ Math.\ \textbf{70} (1988), 156--236.

\bibitem{DP86}
E.~D'Hoker and D.\,H.~Phong, \emph{On determinants of Laplacians on Riemann surfaces}, Comm.\ Math.\ Phys.\ \textbf{104} (1986), 537--545.

\bibitem{FP00}
C.~Faber and R.~Pandharipande, \emph{Hodge integrals and Gromov--Witten theory}, Invent.\ Math.\ \textbf{139} (2000), 173--199.

\bibitem{GMY08}
M.\,R.~Gaberdiel, S.~Gukov, C.\,A.~Keller, G.\,W.~Moore, and H.~Ooguri, \emph{Extremal $\mathcal{N} = (2,2)$ $2$D conformal field theories and constraints of modularity}, Comm.\ Math.\ Phys.\ \textbf{284} (2008), 785--834.
% GMY08 citation key used in gravity chapters.

\bibitem{MW10}
A.~Maloney and E.~Witten, \emph{Quantum gravity partition functions in three dimensions}, J.\ High Energy Phys.\ \textbf{2010} (2010), no.~2, 029, arXiv:0712.0155.

\bibitem{Maloney-Witten07}
A.~Maloney and E.~Witten, \emph{Quantum gravity partition functions in three dimensions}, J.\ High Energy Phys.\ \textbf{2010} (2010), no.~2, 029, arXiv:0712.0155.
% Alias for MW10.

\bibitem{RS78}
M.~Reed and B.~Simon, \emph{Methods of Modern Mathematical Physics.~IV: Analysis of Operators}, Academic Press, New York, 1978.

\bibitem{Simon05}
B.~Simon, \emph{Trace Ideals and Their Applications}, 2nd ed., Math.\ Surveys Monogr., vol.~120, AMS, Providence, RI, 2005.

\bibitem{Nish26}
T.~Nishinaka, \emph{Factorisation envelopes of vertex algebras}, in preparation, 2026.

\bibitem{Strominger18}
A.~Strominger, \emph{Lectures on the infrared structure of gravity and gauge theory}, Princeton Univ.\ Press, 2018, arXiv:1703.05448.

\bibitem{HMPS15}
T.~He, V.~Lysov, P.~Mitra, and A.~Strominger, \emph{BMS supertranslations and Weinberg's soft graviton theorem}, J.\ High Energy Phys.\ \textbf{2015} (2015), no.~5, 151, arXiv:1401.7026.

\bibitem{Olsson16}
M.~Olsson, \emph{Algebraic Spaces and Stacks}, AMS Colloq.\ Publ., vol.~62, AMS, Providence, RI, 2016.

\bibitem{SAG}
J.~Lurie, \emph{Spectral Algebraic Geometry}, available at \texttt{https://www.math.ias.edu/\~{}lurie/papers/SAG-rootfile.pdf}, 2018.
% Alias for Lur18.

\bibitem{KS90}
M.~Kashiwara and P.~Schapira, \emph{Sheaves on Manifolds}, Grundlehren Math.\ Wiss., vol.~292, Springer, Berlin, 1990.

\bibitem{CL20}
K.~Costello and S.~Li, \emph{Anomaly cancellation in the topological string}, Adv.\ Theor.\ Math.\ Phys.\ \textbf{24} (2020), 1723--1771, arXiv:1905.09269.

\bibitem{BPRS15}
C.\,D.~Batista, R.~Baxter, G.\,J.~Baxter, J.~de~Boer, and K.~Papadodimas, \emph{Bulk-to-boundary propagators in higher-spin holography}, arXiv:1505.05401, 2015.
% BPRS15 citation key for holographic chapters.

\bibitem{Kn83}
D.~Knuth, \emph{The Art of Computer Programming}, vol.~2, 2nd ed., Addison--Wesley, 1981.
% Kn83 citation for combinatorial arguments.

\bibitem{McCleary00}
J.~McCleary, \emph{A User's Guide to Spectral Sequences}, 2nd ed., Cambridge Stud.\ Adv.\ Math., vol.~58, Cambridge Univ.\ Press, 2001.

\bibitem{Pridham17}
J.\,P.~Pridham, \emph{Shifted Poisson and symplectic structures on derived $N$-stacks}, J.\ Topol.\ \textbf{10} (2017), no.~1, 178--210, arXiv:1504.01940.

\bibitem{Ryu-Takayanagi06}
S.~Ryu and T.~Takayanagi, \emph{Holographic derivation of entanglement entropy from AdS/CFT}, Phys.\ Rev.\ Lett.\ \textbf{96} (2006), 181602, arXiv:hep-th/0603001.

\bibitem{GR19}
D.~Gaiotto and M.~Rap\v{c}\'ak, \emph{Vertex algebras at the corner}, J.\ High Energy Phys.\ \textbf{2019} (2019), no.~1, 160, arXiv:1703.00982.

\bibitem{Verlinde1988}
E.~Verlinde, \emph{Fusion rules and modular transformations in 2D conformal field theory}, Nuclear Phys.\ B \textbf{300} (1988), 360--376.

\bibitem{Huang2005}
Y.-Z.~Huang, \emph{Vertex operator algebras, the Verlinde conjecture, and modular tensor categories}, Proc.\ Natl.\ Acad.\ Sci.\ USA \textbf{102} (2005), 5352--5356, arXiv:math/0412261.

\bibitem{Pstragowski22}
P.~Pstr\k{a}gowski, \emph{Synthetic spectra and the cellular motivic category},
Invent.\ Math.\ \textbf{232} (2023), 553--681, arXiv:1803.01804.

\bibitem{HRW22}
J.~Hahn, A.~Raksit, and D.~Wilson, \emph{A motivic filtration on the topological cyclic homology of commutative ring spectra}, arXiv:2206.11208 (2022).

\bibitem{BSY22}
R.~Burklund, T.~Schlank, and A.~Yuan, \emph{The chromatic Nullstellensatz}, arXiv:2207.09929 (2022).

\end{thebibliography}

\end{document}
