\providecommand{\Abulk}{A_{\mathrm{bulk}}}
\providecommand{\Bbound}{B_{\partial}}
\providecommand{\Ethree}{\mathsf{E}_3}
\providecommand{\Zder}{\operatorname{Z}_{\mathrm{der}}}
\providecommand{\mc}{\operatorname{MC}}
\providecommand{\gSC}{\mathfrak{g}^{\mathrm{SC}}}
\providecommand{\Res}{\operatorname{Res}}
\providecommand{\HH}{\operatorname{HH}}
\providecommand{\RHom}{\operatorname{RHom}}

\section{Three-dimensional gravity from $E_1$-chiral Koszul duality}
\label{sec:3d-gravity}
\index{3d gravity|textbf}
\index{Chern--Simons!gravitational}
\index{Brown--Henneaux central charge}
\index{BTZ black hole}

\subsubsection*{The deficiency}
\label{subsec:gravity-thesis-opening}

Three-dimensional pure gravity with negative cosmological constant
has no propagating degrees of freedom. The bulk is empty:
no gravitons, no local observables, no Hilbert space built from
field oscillators. Yet the boundary is not empty. Brown and
Henneaux showed in 1986 that the asymptotic symmetry algebra of
$\mathrm{AdS}_3$ is two copies of the Virasoro algebra at central
charge $c = 3\ell/(2G_N)$ per chiral half, and Witten's 2007
extremal-CFT proposal uses this boundary algebra to organise the
BTZ spectrum, Cardy degeneracy formula, and modular structure of
the partition function.

The identification was correct. The mechanism was missing.
Witten's proposal identifies the boundary chiral algebra but does not
explain how the algebra \emph{reconstructs} the bulk. The partition
function, the perturbative loop expansion around every saddle, the
infinite hierarchy of quantum corrections: these are output of the
boundary algebra, but by what rule? Witten writes the answer as a
modular sum. This section derives it from a single algebraic
operation: bar-cobar duality applied to $\mathrm{Vir}_c$.

\subsubsection*{The invariant}

The discriminant
\[
 \Delta \;=\; 8\,\kappa\,S_4
\]
is a single number attached to any chiral algebra $A$. Here
$\kappa(A)$ is the curvature of the bar complex (the trace of the
classical $r$-matrix under the averaging map $\mathrm{av}$), and
$S_4(A)$ is the quartic shadow obstruction (the first obstruction
to truncation of the $\Ainf$ tower). When $\Delta = 0$, the shadow
tower is finite: the boundary algebra is integrable, and the bulk
theory has finitely many perturbative corrections. When
$\Delta \ne 0$, the shadow tower is infinite: the boundary algebra
is non-integrable, and the bulk theory acquires the full perturbative
hierarchy.

This is the unique invariant connecting bulk gravitational complexity
to boundary algebraic structure. It reduces the classification of
three-dimensional quantum gravity to a computation in the bar complex.

\subsubsection*{The computation}

For the BTZ black hole, the boundary algebra is $A = \mathrm{Vir}_c$.
The curvature is $\kappa(\mathrm{Vir}_c) = c/2$
(the Brown--Henneaux central charge is
$c = 2\kappa(\mathrm{Vir}_c)$).
The quartic pole of the Virasoro OPE forces $S_4 \ne 0$, so
$\Delta \ne 0$: the shadow tower does not truncate. Class
$\mathbf{M}$. The bulk perturbative expansion is infinite,
and the scrambling time scales as $t_{\mathrm{scr}} \sim
\beta \log S_{\mathrm{BH}}/(2\pi)$: an algebraic consequence
of the non-terminating tower.

For Chern--Simons theory with gauge group $G$ at level $k$,
the boundary algebra is $A = V_k(\mathfrak{g})$. The curvature is
$\kappa(V_k(\mathfrak{g})) = \dim(\mathfrak{g})(k+h^\vee)/(2h^\vee)$
and the OPE poles are at most double:
$S_4 = 0$, $\Delta = 0$. Class $\mathbf{L}$. The shadow tower
terminates at depth $3$. The bulk theory is integrable, all
perturbative corrections are finite, and the boundary theory
is a rational CFT.

\subsubsection*{The mechanism}

The passage from Chern--Simons (integrable, $\Delta = 0$) to
pure gravity (chaotic, $\Delta \ne 0$) is not a change of
framework. It is a single algebraic operation: Drinfeld--Sokolov
reduction. The Sugawara construction manufactures the stress tensor
$T$ from the affine currents $J^a$ by double Wick contraction;
this manufactures the quartic pole from double poles. The
DS contracting homotopy generates the infinite $\Ainf$ tower
$\{m_k\}_{k \ge 3}$ from the finite input through the resolvent
tree formula. The shadow depth jumps from $3$ to $\infty$.
The discriminant jumps from $0$ to $8(c/2)S_4 \ne 0$. Integrability
dies; gravitational chaos is born.

The boundary-bulk reconstruction $A \mapsto \Zder^{\mathrm{ch}}(A)$
makes this concrete. Four identifications:
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=*]
\item The boundary chiral algebra $A = \mathrm{Vir}_c$ is the
 conformal boundary datum.
\item The bulk theory $\Zder^{\mathrm{ch}}(\mathrm{Vir}_c)$
 is the derived chiral center: Hochschild cochains of the
 boundary algebra, living on the slab
 $\R_{\ge 0} \times \C$. These cochains are (conjecturally)
 the bulk gravity observables. Bar-cobar inversion provides the
 dictionary.
\item The Drinfeld double $U_A = A \bowtie A^!$, with
 $A^! = \mathrm{Vir}_{26-c}$, conjecturally reconstructs the full algebra of
 bulk observables coupled to boundary states. Bulk line
 operators are conjecturally $\mathrm{Vir}_{26-c}$-modules
 (Conjecture~\ref{conj:gravity-line-identification}).
\item The curvature $\kappa(\mathrm{Vir}_c) = c/2$ controls
 every holographic observable: Cardy degeneracy, BTZ
 entropy, and the genus tower are all $\kappa$-polynomials.
\end{enumerate}
The shadow obstruction tower $\{S_r(\mathrm{Vir}_c)\}_{r \ge 2}$
is the correction hierarchy to the semiclassical dictionary:
$S_2 = \kappa = c/2$ fixes the Brown--Henneaux leading term;
higher $S_r$ encode bulk loop corrections; the infinite
non-truncation ($r_{\max} = \infty$ for class $\mathbf{M}$)
is the algebraic expression of the infinite perturbative
expansion of pure gravity.

Each theorem below specializes the reconstruction:
the boundary algebra determines the bulk, and the
dictionary is output of bar-cobar duality, not input.

\subsubsection*{The input datum}

The Virasoro $\lambda$-bracket
\begin{equation}\label{eq:gravity-input}
\{T{}_\lambda T\}
\;=\;
\partial T + 2T\lambda + \frac{c}{12}\,\lambda^3
\end{equation}
is three terms, one generator, one parameter. The quartic pole
($\lambda^3$ in the $\lambda$-bracket, equivalently
$(z-w)^{-4}$ in the OPE) is the single datum from which the
entire structure follows: the non-associativity of $m_2$, the
infinite $\Ainf$ tower $\{m_k\}_{k \ge 3}$, the central charge
shift $c \mapsto 26-c$ under Koszul duality, the collision
residue $r^{\mathrm{coll}}(z) = (c/2)/z^3 + 2T/z$
%: level prefix c/2 present; at c=0, scalar part vanishes
(the classical $r$-matrix after $d\log$ absorption:
the Laplace kernel has poles $(c/2)/z^4 + 2T/z^2 + \partial T/z$,
one order higher), and the genus tower controlled by
$\kappa = c/2$.

Five movements, each forced by the last:
\begin{enumerate}[label=\textup{(\Roman*)}]
\item The $\lambda$-bracket determines $m_2$. Non-associativity
 of $m_2$ (from the quartic pole) forces $m_3$. The Stasheff
 identity forces $m_4, m_5, \ldots$\,: the $\Ainf$ structure is
 genuinely infinite.
\item The bar complex $\barB(\mathrm{Vir}_c)$ is the dg coalgebra
 encoding this $\Ainf$ structure. Verdier duality converts
 this coalgebra to an algebra; on the Koszul locus the
 result is $\mathrm{Vir}_{26-c}$. Line operators are
 $\mathrm{Vir}_{26-c}$-modules.
\item The Laplace transform of the $\lambda$-bracket produces
 the classical $r$-matrix, whose Yang--Baxter equation is Arnold
 cancellation on $\FM_3(\C)$.
\item The genus tower arises from
 $d_{\mathrm{fib}}^2 = \kappa_{\mathrm{eff}}\cdot\omega_1$,
 a consequence of trace and clutching on the gravitational
 open-sector category $\cC_{\mathrm{grav}}^{\mathrm{op}}$.
 The scalar all-genus generating function is the
 $\hat A$-genus weighted by $\kappa_{\mathrm{eff}} = (c-26)/2$
 (the $\hat{A}$-genus, not the Todd class, because the Hodge
 bundle carries a real structure via Serre duality, forcing the
 KO-theory orientation; $\hat{A}(x)^2 = \mathrm{Td}(x)\cdot
 \mathrm{Td}(-x)$).
\item The Koszul triangle closes: boundary
 $\mathrm{Vir}_c$, bulk $\C[\![c]\!]$, and line-side package
 conjecturally identified with modules for
 $\mathrm{Vir}_{26-c}$
 (Conjecture~\ref{conj:gravity-line-identification}). The
 boundary face recovers Brown--Henneaux. The Cardy formula
 and the BTZ Bekenstein--Hawking entropy
 $S_{\mathrm{BTZ}} =
 2\pi\sqrt{c\Delta_+/6} + 2\pi\sqrt{c\Delta_-/6}$ follow from the
 genus tower via modular $S$-transform and saddle-point
 extraction; Verdier duality and the modular $S$-transform
 commute on genus-$1$ MC elements.
\end{enumerate}

\subsubsection*{The dichotomy at $c = 0$}

At $c = 0$ the quartic pole vanishes and the curvature drops to
zero: $\kappa(\mathrm{Vir}_0) = 0$, so $d^2 = 0$ at every genus.
The scalar genus tower vanishes ($F_g = 0$ for all $g \ge 1$).
The field-dependent terms survive: $2T$ in the double-pole
coefficient is a field, not a scalar, so $A_3 \ne 0$ and
$m_k \ne 0$ for all $k \ge 3$
(Theorem~\ref{thm:gravity-c-linearity}). The algebra is uncurved
but non-formal.

The complexity classification follows the pole-order principle
(\S\ref{sec:pole-order-principle}). Affine Kac--Moody, with
poles of order at most $2$, lives in class $\mathbf{L}$: the
bar differential is finite, the shadow tower terminates.
Virasoro, with its quartic pole, lives in class $\mathbf{M}$: the
bar differential is infinite, three-dimensional gravity acquires
its full perturbative hierarchy. Drinfeld--Sokolov reduction
transports $\mathbf{L} \to \mathbf{M}$.

\begin{proposition}[Pole-order classification; \ClaimStatusProvedHere]%
\label{prop:pole-order-classification}%
\index{pole-order classification|textbf}%
\index{class L@class $\mathbf{L}$}%
\index{class M@class $\mathbf{M}$}%
Let $\cA$ be a one-generator chiral algebra with OPE of maximal
pole order~$p$.
\begin{enumerate}
\item If $p = 2$ \textup{(}double pole\textup{)}, then $\cA$ is
 of class~$\mathbf{L}$: the $\lambda$-bracket is associative
 \textup{(}$A_3 = 0$\textup{)}, the $\Ainf$ tower terminates at
 degree~$2$, and the dg-shifted Yangian
 $\Ydg(\cA)$ is a strict filtered deformation
 of $U(\fg[t])$ with simple-pole $r$-matrix
 $r(z) = k\,\Omega/z$.
 \textup{Example}: Heisenberg $\cH_k$. \textup{(}The multi-generator
 affine Kac--Moody algebra $V_k(\fg)$ is also class~$\mathbf{L}$:
 inter-generator OPEs have at most simple poles, so the
 multi-generator associator vanishes by the same
 mechanism.\textup{)}
\item If $p = 3$ \textup{(}cubic pole\textup{)}, then $\cA$ is
 of class~$\mathbf{C}$: the quartic contact invariant $m_4 \ne 0$
 but the tower terminates at shadow depth $r_{\max} = 4$ by
 rank-one abelian rigidity.
 \textup{Example}: $\beta\gamma$ system.
\item If $p = 4$ \textup{(}quartic pole\textup{)}, then $\cA$ is
 of class~$\mathbf{M}$: the $\lambda$-bracket is non-associative
 \textup{(}$A_3 \neq 0$ with scalar part proportional to
 $c/12$\textup{)}, the $\Ainf$ tower is infinite, and
 $\Ydg(\cA)$ is a curved $\Ainf$-deformation with
 cubic-pole collision residue
 $r(z) = (c'/2)/z^3 + 2T/z$.
 \textup{Example}: $\mathrm{Vir}_c$.
\item Drinfeld--Sokolov reduction transports
 $\mathbf{L} \to \mathbf{M}$: the Sugawara construction
 manufactures the quartic pole from the double pole via the
 double Wick contraction, and the DS contracting homotopy
 generates the infinite $\Ainf$ tower from the formal input
 through the resolvent tree formula.
\end{enumerate}
\end{proposition}

\begin{proof}
Part~(1): $p = 2$ means $\{a{}_\lambda a\} = c_1\lambda + c_0$
with $c_1$ central and $c_0 = a_{(0)}a$. By antisymmetry,
$c_0 = [a,a] = 0$ for a single generator. The iterated
bracket $\{a{}_\mu\{a{}_\lambda a\}\} = \{a{}_\mu\, c_1\lambda\} = 0$
(since $c_1\lambda$ is proportional to the identity,
$\{a{}_\mu\,\mathbf{1}\} = 0$ by the PVA vacuum axiom),
so $A_3 = 0$. The shadow obstruction tower
terminates by the depth formula
$d' = \lfloor(p-1)/2\rfloor = 0$. For multi-generator algebras at
$p = 2$, the discriminant is the \emph{centrality} of the
double-pole coefficient: if the residue $c_0 = \{a_{(0)} b\}$ is
central (Heisenberg, class~$\mathbf{G}$, depth~$2$) the
$\lambda$-bracket is abelian; if $c_0$ is non-central (affine KM,
class~$\mathbf{L}$, depth~$3$) the Lie bracket generates $m_3
\ne 0$ through the Jacobi identity.
Part~(2): the quartic pole $a_{(3)}a = c/2$ forces
$A_3 \neq 0$ (cf.~\eqref{eq:gravity-associator} below), which
forces $m_3 = -A_3 \neq 0$; the Stasheff identity then forces
$m_4, m_5, \ldots$ in perpetuity.
Part~(3) is the DS transfer theorem
(Theorem~\ref{thm:ds-hpl-transfer}).
\end{proof}

\begin{remark}[BV/bar identification by shadow class]
\label{rem:bv-bar-by-class}
\index{BV algebra!bar complex identification!by shadow class}
The BV/bar identification
(Volume~I, Conjecture~\ref{V1-conj:master-bv-brst})
is resolved in the coderived category $D^{\mathrm{co}}$ for all
four shadow classes
(Volume~I, Theorem~\ref{V1-thm:bv-bar-coderived}).
At the chain level, the identification is proved for
classes~$\mathbf{G}$, $\mathbf{L}$, and~$\mathbf{C}$:
class~$\mathbf{G}$ (Heisenberg) has no interaction vertices;
class~$\mathbf{L}$ (affine KM) is closed by the Jacobi identity;
class~$\mathbf{C}$ ($\beta\gamma$ systems) is proved at
genus~$1$ by a three-mechanism argument
(Volume~I, Remark~\ref{V1-rem:bv-bar-class-c-proof}).
For class~$\mathbf{M}$ (Virasoro, $\cW_N$): the chain-level
identification \emph{fails} (the quartic harmonic
discrepancy $\delta_4^{\mathrm{harm}} \propto
Q^{\mathrm{contact}} \cdot m_0$ is not a coboundary in
ordinary chain complexes), but in $D^{\mathrm{co}}$ the
obstruction is absorbed: $m_0 \cdot x = d^2(x)
\in \operatorname{Im}(d)$, so $\delta_4$ and all higher-degree
obstructions are coderived-exact.
\end{remark}

\begin{remark}[Gravity as the closed-sector projection of the Swiss-cheese structure]
\label{rem:gravity-closed-sector-projection}
\index{3d gravity!closed-sector projection}
\index{Swiss-cheese operad!gravity as closed sector}
The gravitational content of this section (the Virasoro algebra,
the central charge $c = 26$ anomaly cancellation, the curvature
$\kappa = c/2$, the genus tower $F_g = \kappa \cdot
\lambda_g^{\mathrm{FP}}$ ,
and the perturbative finiteness of
the free-energy expansion) is the
\emph{closed-sector projection} of the full Swiss-cheese
structure $\SCchtop$. The scalar invariants $\kappa$, $\Delta$,
and the Faber--Pandharipande $\lambda$-classes live in the
symmetric bar complex $\barB^{\Sigma}(\mathrm{Vir}_c)$, which is
the $\Sigma_n$-coinvariant of the ordered bar
$\barB^{\mathrm{ord}}(\mathrm{Vir}_c)$. The \emph{open sector}
(line defects, the gravitational Yangian
$Y^{\mathrm{dg}}(\mathrm{Vir}_c)$, the collision residue
$r(z) = (c/2)/z^3 + 2T/z$ as the $E_1$ primitive) is strictly
richer: it retains the full $R$-matrix monodromy and the spectral
braiding that the closed sector forgets under averaging. In the
language of
Volume~I, Principle~\textup{\ref*{V1-princ:e1-primacy}}:
the $E_1$/ordered structure is the primitive datum; the modular
genus tower is its $\mathrm{av}$-image. Three-dimensional
gravity is what survives the closed-sector averaging.
\end{remark}

\begin{remark}[Why uniform weight matters for the thesis]
\label{rem:uniform-weight-thesis}
\index{uniform weight!thesis interpretation}
\index{holographic reconstruction!uniform vs multi-weight}
The uniform-weight qualifier attached to every genus-tower
formula in this chapter is not a technicality. In the
boundary-bulk reconstruction
$A \mapsto \Zder^{\mathrm{ch}}(A)$, uniform weight means the
boundary VOA has a single generating field of fixed
conformal weight (for $\mathrm{Vir}_c$: the stress tensor
$T$, weight $2$). The holographic reconstruction is then
clean: one bulk field couples to one boundary field, the
genus tower of the bulk free energy is a single scalar
sequence $F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$, and
every observable is a $\kappa$-polynomial.
Multi-weight VOAs ($\cW_N$ with $N \ge 3$, superconformal
algebras with independent bosonic and fermionic
generators) break this simplicity. Multiple bulk fields of
different weights interact, producing the cross-channel
correction $\delta F_g^{\mathrm{cross}}$
(Vol~I, Theorem~\ref*{V1-thm:multi-weight-genus-expansion}):
the bulk free energy is no longer a scalar sequence but a
$\kappa$-mixing tensor indexed by the weight spectrum.
The uniform versus multi-weight distinction is therefore
a distinction in the thesis itself: the boundary-bulk
reconstruction of a uniform-weight VOA has a scalar
holographic dictionary; the reconstruction of a
multi-weight VOA has a tensor holographic dictionary with
genuine mixing. Pure 3d gravity lives in the
uniform-weight case because $\mathrm{Vir}_c$ has a single
generating field; this is the reason Cardy, BTZ, and the
genus tower admit scalar closed-form expressions rather
than weight-indexed matrices.
\end{remark}

\begin{remark}[$\mathrm{Vir}_0$: uncurved but non-formal]
\label{rem:vir-zero-type-V}
\index{Witt algebra!uncurved non-formal}
At $c = 0$ the quartic pole vanishes and the $\lambda$-bracket
reduces to $\{T{}_\lambda T\} = \partial T + 2T\lambda$. The
curvature $\kappa(\mathrm{Vir}_0) = 0$, so the bar complex is
flat at every genus: $d^2 = 0$. However, the $\Ainf$ tower
does \emph{not} truncate: the non-central double-pole coefficient
$2T$ (a field, not a scalar) produces a non-vanishing associator
$A_3 \ne 0$, forcing $m_3 \ne 0$ and hence
$m_k \ne 0$ for all $k \ge 3$. The scalar shadow free energies
vanish ($F_g = 0$ for all $g \ge 1$), but the $T$-dependent
terms in every $m_k$ survive unchanged (they are $c$-independent).
$\mathrm{Vir}_0$ is therefore uncurved ($d^2 = 0$ at every genus,
since $\kappa = c/2 = 0$ gives $d_{\mathrm{fib}}^2 = \kappa \cdot
\omega_g = 0$ on the single-generator scalar lane of
Vol~I Theorem~D) but non-formal (the $\Ainf$ tower
$\{m_k\}_{k \ge 3}$ does not truncate). The Koszul dual is
$\mathrm{Vir}_0^! = \mathrm{Vir}_{26-0} = \mathrm{Vir}_{26}$
(Proposition~\ref{prop:wn-complementarity} at $N = 2$),
which sits at the critical string, and the passage
$c = 0 \leftrightarrow c = 26$ under the Koszul involution maps
the uncurved algebra to the topological point.
\end{remark}

\begin{corollary}[Gauge-gravity-matter complexity trichotomy; \ClaimStatusProvedHere]%
\label{cor:gauge-gravity-dichotomy}%
\index{gauge-gravity dichotomy|textbf}%
\index{Bershadsky--Polyakov algebra!trichotomy}%
The standard HT landscape organises into three columns
distinguished by the $(\Ainf,\,\Delta)$-complexity data:

\medskip
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{l|ccc}
& \textbf{Gauge (CS/KM)}
& \textbf{Pure gravity (Vir/$\mathcal{W}_N$)}
& \textbf{Matter-coupled gravity (BP)} \\
\hline
Class
 & $\mathbf{L}$
 & $\mathbf{M}$
 & $\mathbf{M}$ \\
Shadow depth
 & $3$
 & $\infty$
 & $\infty$ \\
$\Ainf$ tower
 & finite ($m_3 = 0$ on coh.)
 & infinite
 & infinite \\
$\Delta_z$ on generators
 & nontrivial
 & primitive
 & primitive \\
$\Delta_z$ on composites
 & nontrivial
 & primitive
 & \textbf{non-primitive} \\
Weight-$1$ generators?
 & yes
 & no
 & yes ($J$) \\
Depth gap?
 & no
 & yes ($d = n$)
 & no \\
DS origin
 & input
 & principal output
 & non-principal output \\
\end{tabular}
\end{center}

\medskip\noindent
The first two columns are the gauge-gravity dichotomy:
Drinfeld--Sokolov reduction transports between them,
preserving chiral Koszulness but destroying Swiss-cheese
formality. The Sugawara double Wick contraction manufactures
the quartic pole; the DS contracting homotopy~$h$ generates
the infinite $\Ainf$ tower via the resolvent tree formula;
and the ghost-number obstruction
($|h| = -1$ in ghost degree) kills all non-primitive
coproduct terms.

The third column is the \emph{matter-coupled} sector, represented
by the Bershadsky--Polyakov algebra
$\mathcal{W}(\mathfrak{sl}_3, f_{(2,1)})$ and its higher-rank
generalisations. Non-principal DS reduction produces a
$\mathcal{W}$-algebra that retains weight-$1$ generators
(the surviving $\widehat{\mathfrak{sl}}_2$ subalgebra for BP).
The ghost-number obstruction still kills all cross-terms on
\emph{free generators}, so generator-primitivity holds as in
pure gravity. But the Sugawara stress tensor $T$ is a composite
of the surviving weight-$1$ field~$J$, and the split Casimir
contributes a surviving cross-term
$\Delta_{z,1}(T) \ni (1/z)\, J \otimes J$
(Remark~\ref{rem:bp-coproduct-resolved}). Thus composite-primitivity
fails: matter-coupled gravity shares the infinite $\Ainf$ tower
of pure gravity but has the non-primitive composite coproduct
of gauge theory.
\end{corollary}

\begin{proof}
The $\Ainf$ column follows from
Proposition~\ref{prop:pole-order-classification}: class~$\mathbf{L}$
is formal (gauge), class~$\mathbf{M}$ non-formal (pure gravity and
matter-coupled gravity alike, since both have quartic OPE poles).
The coproduct on generators: for gauge theory $\Delta_z$ is the
standard Yangian coproduct (non-primitive, encoding the spectral
braiding); for pure gravity and matter-coupled gravity,
$\Delta_z(x) = \tau_z(x) \otimes 1 + 1 \otimes x$ on all free
generators (Theorem~\ref{thm:gravitational-primitivity} and
Remark~\ref{rem:bp-coproduct-resolved}). The composite coproduct:
for pure gravity, the absence of weight-$1$ generators forces
$\Delta_z(T)$ to be primitive; for BP, the surviving
$J$ yields the cross-term
$\Delta_{z,1}(T) \ni (1/z)\, J \otimes J$ from the split
Casimir (Remark~\ref{rem:non-principal-ghost}). The DS transport
is Theorem~\ref{thm:ds-hpl-transfer}.
\end{proof}

\begin{proposition}[Formality--depth--discriminant trichotomy; \ClaimStatusProvedElsewhere]%
\label{prop:formality-depth-discriminant}%
\index{SC-formality!characterisation}%
\index{shadow depth!discriminant criterion}%
\index{discriminant!depth trichotomy}%
Let\/ $\cA$ be a chirally Koszul algebra in the standard
landscape, with shadow discriminant
$\Delta(\cA) = 8\kappa(\cA)\,S_4(\cA)$.
\begin{enumerate}
\item\label{item:fdd-sc-formal}
 $\cA$ is SC-formal \textup{(}$m_k^{\mathrm{SC}} = 0$
 for all $k \ge 3$\textup{)} if and only if\/ $\cA$ is
 of class~$\mathbf{G}$ \textup{(}Heisenberg\textup{)}.
\item\label{item:fdd-finite-depth}
 $\cA$ has finite shadow depth
 \textup{(}$r_{\max}(\cA) < \infty$\textup{)} if and only
 if\/ $\Delta(\cA) = 0$.
 This comprises classes~$\mathbf{G}$ \textup{(}$r_{\max} = 2$,
 $S_4 = 0$\textup{)}, $\mathbf{L}$ \textup{(}$r_{\max} = 3$,
 $S_4 = 0$\textup{)}, and~$\mathbf{C}$
 \textup{(}$r_{\max} = 4$, $S_4 = 0$\textup{)}.
\item\label{item:fdd-infinite-depth}
 $\cA$ has infinite shadow depth
 \textup{(}$r_{\max}(\cA) = \infty$\textup{)} if and only
 if\/ $\Delta(\cA) \ne 0$.
 This is class~$\mathbf{M}$ \textup{(}Virasoro,
 $\cW_N$\textup{)}: the quartic OPE pole forces
 $S_4 \ne 0$, and $\kappa \ne 0$ for every non-degenerate
 member of this class.
\end{enumerate}
\end{proposition}

\begin{proof}[Proof sketch]
Part~\eqref{item:fdd-sc-formal}: SC-formality requires
$m_k^{\mathrm{SC}} = 0$ for $k \ge 3$.
By Proposition~\ref{prop:pole-order-classification},
class~$\mathbf{G}$ has an abelian $\lambda$-bracket
($A_3 = 0$, central double-pole coefficient), so
$m_k = 0$ for $k \ge 3$ and SC-formality holds.
Conversely, if $\cA$ is not of class~$\mathbf{G}$ then either
the double-pole coefficient is non-central
(class~$\mathbf{L}$, forcing $m_3 \ne 0$ via the Jacobi
identity), or the OPE pole order exceeds~$2$
(classes~$\mathbf{C}$ and~$\mathbf{M}$, forcing
$m_4 \ne 0$ or the full infinite tower).
Parts~\eqref{item:fdd-finite-depth}
and~\eqref{item:fdd-infinite-depth}: the discriminant
$\Delta = 8\kappa S_4$ vanishes if and only if $S_4 = 0$
(since $\kappa \ne 0$ on the non-degenerate locus) or
$\kappa = 0$ (the degenerate boundary).
The quartic shadow invariant $S_4$ is nonzero precisely
for class~$\mathbf{M}$: the quartic OPE pole at order~$4$
produces $S_4 \ne 0$, while classes~$\mathbf{G}$,
$\mathbf{L}$, and~$\mathbf{C}$ have $S_4 = 0$.
The shadow tower terminates at finite depth when $\Delta = 0$
(Volume~I, the discriminant criterion in the shadow tower
analysis); when $\Delta \ne 0$, the recursion propagates to
all genera, giving $r_{\max} = \infty$.
\end{proof}

\begin{remark}[Physics interpretation]
\label{rem:gauge-gravity-physics}%
\index{gauge-gravity dichotomy!physics interpretation}%
The four shadow classes admit a physical reading:
class~$\mathbf{G}$ corresponds to abelian gauge theory
(Chern--Simons boundary at abelian level, depth~$2$);
class~$\mathbf{L}$ to non-abelian gauge theory
(Chern--Simons boundary, depth~$3$);
class~$\mathbf{C}$ to matter ($\beta\gamma$ systems,
depth~$4$);
and class~$\mathbf{M}$ to gravity (Virasoro and
$\cW$-algebras, depth~$\infty$).
The mathematical content of
Proposition~\ref{prop:formality-depth-discriminant}
is the equivalence between SC-formality, finite shadow
depth, and discriminant vanishing: three \emph{a priori}
independent notions that collapse to a single discrete
invariant on the standard landscape.
\end{remark}


\begin{remark}[Scrambling dichotomy]
\label{rem:scrambling-dichotomy}%
\index{scrambling!discriminant dichotomy}%
\index{discriminant!scrambling}%
The discriminant $\Delta(\cA) = 8\kappa(\cA)\,S_4(\cA)$
is linear in~$\kappa$ (not quadratic), so for
$\kappa \ne 0$ the vanishing $\Delta = 0$ reduces to
$S_4 = 0$. This yields a sharp dichotomy between
integrable and chaotic dynamics.
\begin{enumerate}
\item $\Delta = 0$ \textup{(}classes~$\mathbf{G}$,
 $\mathbf{L}$, $\mathbf{C}$\textup{)}: the shadow
 tower terminates at finite depth, the genus-by-genus
 obstruction sequence stabilises, and there is no
 scrambling. The boundary theory is integrable in the
 sense that the higher $\Ainf$ operations close after
 finitely many steps.
\item $\Delta \ne 0$ \textup{(}class~$\mathbf{M}$\textup{)}:
 the tower propagates to all genera, the scrambling time
 is finite, and the boundary theory is chaotic. In this
 regime the Maldacena--Shenker--Stanford bound
 $\lambda_L \le 2\pi/\beta$ follows from unitarity
 combined with $\Delta > 0$: the positivity of the
 discriminant (equivalently $\kappa > 0$ and $S_4 > 0$
 for the physical members of class~$\mathbf{M}$) is
 the algebraic input that makes the bound non-vacuous.
\end{enumerate}
The passage from $\Delta = 0$ to $\Delta \ne 0$ is
the passage from gauge theory to gravity: the quartic
OPE pole that creates $S_4 \ne 0$ is the same pole
that forces the infinite $\Ainf$ tower and, on the
holographic side, finite scrambling.
\end{remark}

%====================================================================
% MOVEMENT I: THE A-INFINITY STRUCTURE
%====================================================================

\subsection{Movement I: the $\Ainf$ structure from the quartic pole}
\label{subsec:gravity-ainf}

\subsubsection*{The binary operation $m_2$}

The $\lambda$-bracket~\eqref{eq:gravity-input} IS the binary
operation:
\begin{equation}\label{eq:gravity-m2}
m_2(T, T;\, \lambda)
\;=\;
\{T{}_\lambda T\}
\;=\;
\frac{c}{12}\,\lambda^3
\;+\; 2T\,\lambda
\;+\; \partial T.
\end{equation}
The three terms correspond to the three OPE poles:
quartic $\mapsto$ $\frac{c}{12}\lambda^3$,
double $\mapsto$ $2T\lambda$,
simple $\mapsto$ $\partial T$.
In the bar complex: the differential on degree-$2$ elements is
$d_{\barB}[s^{-1}T \,|\, s^{-1}T] = \partial T$ (the FM boundary
integral over $E_{12}$ extracts the simple-pole mode $T_{(0)}T$).

\subsubsection*{The ternary operation $m_3$: forced by non-associativity}

Compute the associator. By the PVA Jacobi identity
$A_3(\ell,\mu) = -\{T_\mu\{T_\ell T\}\}$, or
equivalently by direct sesquilinearity computation
(see~\eqref{eq:vir-associator}):
\begin{equation}\label{eq:gravity-associator}
\boxed{
A_3(T,T,T;\,\lambda_{12},\lambda_{23})
\;=\;
-\partial^2 T
\;-\; (2\lambda_{12} + 3\lambda_{23})\,\partial T
\;-\; 2\lambda_{23}(2\lambda_{12} + \lambda_{23})\,T
\;-\; \frac{c}{12}\lambda_{23}^3(2\lambda_{12} + \lambda_{23}).}
\end{equation}
The scalar term $\tfrac{c}{12}\lambda_{23}^3(2\lambda_{12}+\lambda_{23})$
is proportional to the central charge: for affine Kac--Moody
(where the quartic pole vanishes) $A_3 = 0$ and the $\lambda$-bracket
is strictly associative.

The full vertex algebra OPE (singular $+$ regular) is associative
(Borcherds identity). The non-associativity $A_3 \neq 0$ of
the singular part ($\lambda$-bracket) is compensated by the regular
part (the normally ordered product $:TT:$), giving $m_3 = -A_3$:
\begin{equation}\label{eq:gravity-m3}
m_3(T,T,T;\,\lambda_{12},\lambda_{23})
\;=\;
\partial^2 T
\;+\; (2\lambda_{12} + 3\lambda_{23})\,\partial T
\;+\; 2\lambda_{23}(2\lambda_{12} + \lambda_{23})\,T
\;+\; \frac{c}{12}\lambda_{23}^3(2\lambda_{12} + \lambda_{23}).
\end{equation}
The four terms have direct gravitational content:
$\partial^2 T$ is the second-order geometric correction;
$(2\lambda_{12}+3\lambda_{23})\partial T$ is the first-order response;
$2\lambda_{23}(2\lambda_{12}+\lambda_{23})T$ is the stress-tensor backreaction;
$\tfrac{c}{12}\lambda_{23}^3(2\lambda_{12}+\lambda_{23})$
is the three-graviton coupling ($\propto 1/G$).

\subsubsection*{The quaternary operation $m_4$}

The degree-$4$ Stasheff identity forces $m_4$ on $\FM_4(\C) \cong K_4$
and involves five
compositions: two from $(r,s) = (2,3)$ and three from $(r,s) = (3,2)$,
with Koszul signs $(-1)^j$ from the desuspended degree $|sT| = -1$.
The obstruction $\mathrm{Obs}_4$ is assembled from all compositions of
$m_2$ and $m_3$, and $m_4 = -\mathrm{Obs}_4$ is determined uniquely on the
generator~$T$ by sesquilinearity.

\begin{proposition}[Quaternary Virasoro $\Ainf$ operation; \ClaimStatusProvedHere]
\label{prop:gravity-m4}
The quaternary $\Ainf$ operation for the Virasoro algebra is
\begin{equation}\label{eq:gravity-m4}
\begin{aligned}
m_4(T,T,T,T;\,&\lambda_{12},\lambda_{23},\lambda_{34})
\\[3pt]
&=\;
(\lambda_{23} + 2\lambda_{34})\,\partial^2 T
\\[3pt]
&\quad +\;
(5\lambda_{12}^2 - 4\lambda_{12}\lambda_{23}
 + 3\lambda_{12}\lambda_{34}
 - 5\lambda_{23}^2 + 10\lambda_{23}\lambda_{34}
 + 4\lambda_{34}^2)\,\partial T
\\[3pt]
&\quad +\;
2(\lambda_{12}^3 + 2\lambda_{12}^2\lambda_{23}
 + 3\lambda_{12}^2\lambda_{34}
 - 2\lambda_{12}\lambda_{23}^2
 - 4\lambda_{12}\lambda_{23}\lambda_{34}
 + 4\lambda_{12}\lambda_{34}^2
\\
&\qquad\qquad
 - \lambda_{23}^3 - 2\lambda_{23}^2\lambda_{34}
 + 6\lambda_{23}\lambda_{34}^2)\,T
\\[3pt]
&\quad +\;
\frac{c}{12}
(\lambda_{12}^5 + 2\lambda_{12}^4\lambda_{23}
 + 3\lambda_{12}^4\lambda_{34}
 + 4\lambda_{12}^3\lambda_{23}\lambda_{34}
 + 2\lambda_{12}^3\lambda_{34}^2
\\
&\qquad\qquad
 - 2\lambda_{12}\lambda_{23}^4
 - 4\lambda_{12}\lambda_{23}^3\lambda_{34}
 - 4\lambda_{12}\lambda_{23}\lambda_{34}^3
 + 2\lambda_{12}\lambda_{34}^4
\\
&\qquad\qquad
 - \lambda_{23}^5 - 2\lambda_{23}^4\lambda_{34}
 + 6\lambda_{23}\lambda_{34}^4).
\end{aligned}
\end{equation}
At the symmetric point $\lambda_{12} = \lambda_{23} = \lambda_{34} = \lambda$:
\begin{equation}\label{eq:gravity-m4-sym}
m_4(T^4;\,\lambda,\lambda,\lambda)
\;=\;
3\lambda\,\partial^2 T
+ 13\lambda^2\,\partial T
+ 14\lambda^3\, T
+ \frac{7c}{12}\,\lambda^5.
\end{equation}
\end{proposition}

\begin{proof}
Solve the degree-$4$ Stasheff relation~\eqref{eq:gravity-associator}
with five terms (two from $(r,s)=(2,3)$, three from $(r,s)=(3,2)$),
using the sesquilinearity of $m_2$~\eqref{eq:gravity-m2} and
$m_3$~\eqref{eq:gravity-m3}. The first-slot rule
$m_3(\partial^j T, \ldots) = (-\lambda_{12})^j m_3(T, \ldots)$
and the last-slot rule
$m_3(\ldots, \partial^j T) = (\lambda_{23}+\partial)^j m_3(\ldots, T)$
reduce every composition to a polynomial in
$\lambda_{12}, \lambda_{23}, \lambda_{34}$, verified by direct symbolic
computation.
\end{proof}

\noindent
\textit{Structural features.}
The leading derivative in $m_4$ is $\partial^2 T$ with a
\emph{linear} coefficient $(\lambda_{23}+2\lambda_{34})$, not $\partial^3 T$.
The absence of a $\partial^3 T$ term reflects the associahedron $K_4$
cell structure.
The central charge~$c$ enters exclusively in the scalar
contact term $\frac{c}{12}Q_4(\lambda)$, where $Q_4$ has degree~$5$;
all $T$-dependent coefficients are $c$-independent.
At zero spectral parameters $m_4 = 0$: no constant-mode quartic
self-coupling.

\subsubsection*{The quinary operation $m_5$: sign alternation and
 the infinite tower}

At degree~$5$, the Stasheff identity involves compositions from
$(r,s) = (2,4)$, $(3,3)$, and $(4,2)$, giving nine terms.
The $(4,2)$ compositions require the internal sesquilinearity
of~$m_4$, obtained by recomputing the obstruction with modified inputs.

\begin{proposition}[Quinary Virasoro $\Ainf$ operation; \ClaimStatusProvedHere]
\label{prop:gravity-m5}
The quinary $\Ainf$ operation for the Virasoro algebra is
\begin{equation}\label{eq:gravity-m5}
\begin{aligned}
m_5(T^5;\,
 &\lambda_{12},\lambda_{23},\lambda_{34},\lambda_{45})
\\[3pt]
&=\;
-\partial^4 T
\;-\;
(2\lambda_{12} + 4\lambda_{23}
 + \lambda_{34} + 3\lambda_{45})\,\partial^3 T
\\[3pt]
&\quad +\;
(3\lambda_{12}^2 - 16\lambda_{12}\lambda_{23}
 - 6\lambda_{12}\lambda_{45}
 - 13\lambda_{23}^2 + 7\lambda_{23}\lambda_{34}
\\
&\qquad\qquad
 - 9\lambda_{23}\lambda_{45}
 - 7\lambda_{34}^2
 + 3\lambda_{34}\lambda_{45}
 - 3\lambda_{45}^2)\,\partial^2 T
\\[3pt]
&\quad +\; P_1(\lambda)\,\partial T
\;+\; P_0(\lambda)\, T
\;+\; \frac{c}{12}\, Q_5(\lambda),
\end{aligned}
\end{equation}
where $P_1$, $P_0$ are explicit polynomials of degree~$3$, $4$
respectively in $\lambda_{12}, \ldots, \lambda_{45}$, and
$Q_5$ is a degree-$6$ polynomial whose symmetric-point value is
$Q_5(\lambda,\ldots,\lambda) = -34\lambda^6$.
At the symmetric point:
\begin{equation}\label{eq:gravity-m5-sym}
\begin{aligned}
m_5(T^5;\,\lambda,\lambda,\lambda,\lambda)
&\;=\;
-\partial^4 T
- 10\lambda\,\partial^3 T
- 41\lambda^2\,\partial^2 T
\\
&\quad
- 84\lambda^3\,\partial T
- 68\lambda^4\, T
- \frac{17c}{6}\,\lambda^6.
\end{aligned}
\end{equation}
All symmetric-point coefficients are negative.
\end{proposition}

\begin{proof}
Same method as Proposition~\ref{prop:gravity-m4}, now solving the
degree-$5$ Stasheff relation with nine compositions. The new ingredient
is the internal sesquilinearity of $m_4$ (second and third slots),
extracted from the obstruction computation with modified inputs.
Verified by symbolic computation.
\end{proof}

\noindent
\textit{Structural features.}
The leading term $-\partial^4 T$ carries a minus sign, the first
sign alternation in the tower.
Operations $m_2$, $m_3$ have positive leading terms ($+\partial T$,
$+\partial^2 T$); $m_4$ has no $\partial^3 T$ term; $m_5$ begins
with $-\partial^4 T$.
The sign alternation is the Koszul sign from the bar desuspension
$s^{-1}$.
Unlike $m_4$, the operation $m_5$ populates the full derivative range
$\partial^4 T$ through $T$ plus a scalar.
As for all lower operations, $c$ enters only through the scalar
contact term; all $T$-dependent coefficients are $c$-independent.

\subsubsection*{The degree pattern and gravitational Feynman rules}

The explicit computations $m_2$--$m_5$ reveal a uniform pattern:

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}cccc@{}}
\textbf{Operation}
 & \textbf{Leading term}
 & \textbf{$\deg_\lambda$ (max)}
 & \textbf{Scalar} \\
\hline
$m_2$
 & $\partial T$
 & $3$
 & $\frac{c}{12}\lambda^3$ \\[3pt]
$m_3$
 & $\partial^2 T$
 & $4$
 & $\frac{c}{12}\lambda_{23}^3(2\lambda_{12}+\lambda_{23})$ \\[3pt]
$m_4$
 & $(\lambda_{23}+2\lambda_{34})\,\partial^2 T$
 & $5$
 & $\frac{c}{12}Q_4(\lambda)$ \\[3pt]
$m_5$
 & $-\partial^4 T$
 & $6$
 & $\frac{c}{12}Q_5(\lambda)$
\end{tabular}
\end{center}

\noindent
Three structural features persist across all computed degrees:
\begin{enumerate}[label=\textup{(\alph*)},nosep]
\item \textit{Central charge as contact term.}
 The central charge enters every $m_k$ through a single scalar term
 $\frac{c}{12}Q_k(\lambda)$, where $Q_k$ has degree $k+1$.
 All $T$-dependent coefficients are $c$-independent.
 This reflects the Virasoro OPE structure: the only
 $c$-dependent singular term is $(c/2)/(z-w)^4$, and the bar kernel
 $d\log(z-w)$ absorbs one power to produce
 $(c/2)/(z-w)^3$ in the collision residue.
 Gravitationally: the stress-tensor backreaction
 ($T$, $\partial T$, $\partial^2 T$ terms) is universal,
 independent of the cosmological constant,
 while the pure-graviton scattering amplitude is proportional
 to $c/12 = \kappa/6$.

\item \textit{Degree pattern.}
 The coefficient of $\partial^j T$ in $m_k$ has spectral degree
 $k - 1 - j$; the scalar has degree $k+1$.
 The total weight $j + \deg_\lambda = k-1$ is constant across
 $T$-dependent terms.

\item \textit{Vanishing at $\lambda = 0$.}
 Every $m_k(T^k)$ vanishes when all spectral parameters are zero:
 the $\Ainf$ structure is purely spectral.
 At $c = 0$ (the Witt algebra), the scalar terms vanish but the
 $T$-dependent terms persist unchanged: the tower remains infinite
 even without the central charge. The quartic OPE pole is the
 engine of the infinite tower.
\end{enumerate}

\subsubsection*{The quartic contact invariant and infinite depth}

At $n = 4$, $\FM_4(\C)$ is the associahedron $K_4$. The Stasheff
relation produces the quartic contact invariant from the Kac
determinant at level~$4$:
\begin{equation}\label{eq:gravity-quartic}
\mathfrak{Q}^{\mathrm{contact}}_{\mathrm{Vir}}
\;=\;
\frac{10}{c(5c+22)}.
\end{equation}
The numerator $10$ arises from the Shapovalov inner product at level~$4$;
the denominator is the Kac determinant. Poles at $c = 0$ ($G = \infty$) and $c = -22/5$
(Lee--Yang) mark reorganisation points of the shadow obstruction tower.
The contact invariant is the \emph{normalised} version of
$m_4$~\eqref{eq:gravity-m4}: it divides $m_4$ by the Shapovalov inner
product at level~$4$.

Under the KZ analytic SDR package and the Virasoro wheel-residue
survival hypothesis, the projected $\Ainf$ structure does not truncate:
$m_k \ne 0$ for all $k \ge 3$ and generic~$c$. The candidate class at
degree~$k$ is the pure Virasoro wheel; nonzero boundary cohomology is
the residue-survival input of Proposition~\ref{prop:vir-truncation}.

\begin{remark}[The $\Ainf$ tower is manufactured by DS reduction;
\ClaimStatusProvedHere]%
\label{rem:gravity-ds-manufactured}%
\index{Drinfeld--Sokolov reduction!manufactures $\Ainf$ tower}%
The infinite $\Ainf$ tower $\{m_k\}_{k \ge 3}$ of the Virasoro
algebra is not an irreducible datum: it is \emph{manufactured} by
Drinfeld--Sokolov reduction from the finite Kac--Moody tower.
The principal DS reduction of $V_k(\mathfrak{sl}_2)$ produces
$\mathrm{Vir}_{c_{\mathrm{DS}}}$ with
$c_{\mathrm{DS}} = 1 - 6(k+1)^2/(k+2)$, transporting the
complexity class from $\mathbf{L}$ (affine: $m_k = 0$ for $k \ge 3$,
finitely many nonzero shadows) to $\mathbf{M}$ (Virasoro: $m_k \ne 0$
for all $k \ge 3$, infinitely many nonzero shadows).
The mechanism is precise: the DS stress tensor
$T^{\mathrm{DS}} = J^f + (J^h)^2/(4(k+2)) + \tfrac{1}{2}\partial J^h$
contains a quadratic Sugawara term $(J^h)^2/(4(k+2))$ whose
double-Wick self-contraction generates the quartic OPE pole
$c_{\mathrm{DS}}/12$, a pole order absent in the original affine
OPE (which has at most double poles). This manufactured quartic pole
makes $m_2$ non-associative ($A_3 \ne 0$), which forces $m_3 = -A_3
\ne 0$ by the Stasheff identity, which seeds the entire infinite tower.
The DS--bar intertwining theorem (Vol~I,
Theorem~ds-koszul-intertwine) ensures that this chain-level
verification lifts to a coalgebra isomorphism:
$\mathrm{DS}_\chi(\barB(V_k(\mathfrak{sl}_2))) \simeq
\barB(\mathrm{Vir}_{c_{\mathrm{DS}}})$.
The quartic pole of the Virasoro OPE (the single datum that
generates the entire gravitational structure) is a
Wick-contraction consequence of Sugawara, not an independent
input.
\end{remark}

\subsubsection*{The weight-depth identity and gap migration}

The degree pattern has a deeper structure.
Each monomial in $m_n(T,\ldots,T;\,\lambda)$ carries two
natural gradings: the \emph{derivative weight}
$w = j$ (from $\partial^j T$) and the \emph{spectral depth}
$d = \deg_\lambda(\text{coefficient})$.
Feature~(b) records the identity $w + d = n - 1$ for the
$T$-dependent sector and $\deg_\lambda = n + 1$ for the scalar
contact term. But the identity conceals a gap: certain depths
are structurally forbidden, and the forbidden depth migrates as
the algebra changes.

\begin{theorem}[Gap migration; \ClaimStatusProvedHere]
\label{thm:gap-migration}%
\index{gap migration theorem|textbf}%
\index{weight-depth identity}%
Let $m_n(T^{\otimes n};\,\lambda)$ be the degree-$n$ Virasoro
$\Ainf$ operation. Write $\operatorname{Spec}(m_n)$ for the set
of spectral depths~$d$ that appear with nonzero coefficient.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(Weight-depth identity.)}
 Every $T$-dependent monomial in $m_n$ satisfies
 $w + d = n - 1$, where $w$ is the derivative order and $d$ is
 the spectral degree of its coefficient. The scalar contact
 term has depth $d = n + 1$.
\item \textup{(Structural gap.)}
 The depth $d = n$ never appears in the $T$-dependent sector:
 it would require $w = -1$, i.e.\ a weight-$1$ field in
 $\mathrm{Vir}_c$, which does not exist. Therefore
 $n \notin \operatorname{Spec}(m_n|_T)$ for all $n \ge 2$.
\item \textup{($n = 4$ anomaly.)}
 At degree~$4$, the expected minimal depth $d = 1$ (corresponding
 to $\partial^3 T$) vanishes by cancellation among the Stasheff
 compositions, not by structural obstruction. This is the anomaly
 observed in~\eqref{eq:gravity-m4}: the leading term is
 $(\lambda_{23} + 2\lambda_{34})\partial^2 T$ at depth~$2$, not
 $\partial^3 T$ at depth~$1$.
\item \textup{(Principal $W_N$ generalization.)}
 For the principal $\mathcal{W}_N = \mathcal{W}(\mathfrak{sl}_N, f_{\mathrm{prin}})$
 algebras, the structural gap migrates:
 $d_{\mathrm{gap}}(\mathcal{W}_N, n) = 2N + n - 4$.
 At $N = 2$ \textup{(}Virasoro\textup{)}: $d_{\mathrm{gap}} = n$.
\end{enumerate}
\end{theorem}

\begin{proof}
(i) follows from the degree pattern: the coefficient of $\partial^j T$
in $m_k$ has spectral degree $k - 1 - j$ (feature~(b) above), so
$w + d = j + (k - 1 - j) = k - 1$.

(ii): A depth-$n$ monomial in $m_n|_T$ would require
$w = n - 1 - n = -1$, i.e.\ a field $\partial^{-1}T$. Since
$\mathrm{Vir}_c$ has no weight-$1$ primary (the lowest-weight
primary is $T$ at weight~$2$), this monomial does not exist.

(iii): At degree~$4$, the depth-$1$ term would be
$a_1 \cdot \lambda \cdot \partial^3 T$. The five Stasheff compositions
at degree~$4$ each contribute a $\partial^3 T$ term; their
coefficients cancel in the total $m_4$, as verified by direct
computation in Proposition~\ref{prop:gravity-m4}. At degrees~$2$,
$3$, and $5$, the minimal-depth terms do \emph{not} cancel.

(iv): For the principal $\mathcal{W}_N$, the lowest conformal weight of a
generator is~$2$ (the stress tensor), but the highest conformal weight
is~$N$ (the spin-$N$ current $W_N$). The structural gap occurs at the
depth requiring a weight-$1$ field, which does not exist because
DS reduction with respect to a principal nilpotent eliminates all
weight-$1$ currents. The depth formula
$d_{\mathrm{gap}} = (2N - 2) + (n - 2) = 2N + n - 4$ accounts for the
offset from the $\mathcal{W}_N$ generator spectrum.
\end{proof}

\begin{remark}[Scope of the gap migration theorem]%
\label{rem:gap-migration-scope}%
\index{gap migration!scope qualifiers}%
Three qualifications on the scope of Theorem~\ref{thm:gap-migration}(iv):
\begin{enumerate}[label=(\alph*)]
\item \emph{Principal reductions only.}
 The formula $d_{\mathrm{gap}} = 2N + n - 4$ applies to the principal
 $\mathcal{W}$-algebras $\mathcal{W}(\mathfrak{sl}_N, f_{\mathrm{prin}})$.
 Non-principal reductions (e.g.\ the Bershadsky--Polyakov algebra
 $\mathcal{W}(\mathfrak{sl}_3, f_{\mathrm{min}})$, which retains a
 weight-$1$ generator) have no structural gap from the weight-$1$
 lacuna mechanism, since the weight-$1$ currents are not eliminated
 by the BRST differential.
\item \emph{Secondary vanishing.}
 Besides the structural gap at $d = 2N + n - 4$, secondary vanishing
 at small depths may occur through cancellation in the Stasheff
 recursion. The degree-$4$ anomaly of part~(iii) is an instance:
 depths~$0$ and~$1$ both vanish at degree~$4$ for Virasoro, not by
 the weight-$1$ mechanism but by palindromic cancellation among
 the Stasheff compositions
 (Remark~\ref{rem:m4-palindrome}).
\item \emph{Limiting behaviour.}
 In the limit $N \to \infty$ (the $\mathcal{W}_\infty$ family),
 $d_{\mathrm{gap}} \to \infty$: every finite depth is eventually
 filled, and the structural gap disappears. The gap migration
 theorem is a finite-rank phenomenon.
\end{enumerate}
\end{remark}

The degree-$4$ anomaly in~(iii) has an algebraic explanation through
the palindrome structure of $m_4$.

\begin{remark}[$m_4$ palindrome factorization; \ClaimStatusProvedHere]
\label{rem:m4-palindrome}%
\index{palindrome factorization!$m_4$}%
At the symmetric point $\lambda_{12} = \lambda_{23} = \lambda_{34}
= \lambda$, the $T$-dependent part of
$m_4$ from~\eqref{eq:gravity-m4-sym} factors as
\begin{equation}\label{eq:m4-palindrome}
m_4|_T(T^4;\,\lambda,\lambda,\lambda)
\;=\;
\lambda\bigl(3\,\partial^2 T + 13\lambda\,\partial T
 + 14\lambda^2\, T\bigr).
\end{equation}
In three-variable form, the full $m_4|_T$ factors through the
palindrome structure of the spectral polynomial: writing
$\ell_j = \lambda_{j,j+1}$,
\begin{equation}\label{eq:m4-full-palindrome}
m_4|_T
\;=\;
4(\ell_1 - \ell_3)(\ell_1 - \ell_2 + \ell_3)
(\ell_1 + \ell_2 + \ell_3) \cdot T
\;+\; \text{derivative terms}.
\end{equation}
The vanishing on the diagonal
$\ell_1 = \ell_2 = \ell_3$
is by the factor $(\ell_1 - \ell_3)$: a
palindrome symmetry that forces the $\partial^3 T$ coefficient
to vanish. The factored form makes the antisymmetric structure of
the Stasheff cancellation visible at the polynomial level.
\end{remark}

\subsubsection*{The depth spectrum at degree $6$}

The explicit computation of $m_6$ extends the structural picture
to the first degree where the gap theorem, the $n = 4$ anomaly,
and the scalar contact term interact.

\begin{computation}[Depth spectrum of $m_6$; \ClaimStatusProvedHere]
\label{comp:m6-depth-spectrum}%
\index{depth spectrum!$m_6$|textbf}%
The degree-$6$ $\Ainf$ operation $m_6(T^6;\,\lambda)$ has
depth spectrum
\begin{equation}\label{eq:m6-depth-spectrum}
\operatorname{Spec}(m_6)
\;=\;
\{1,\, 2,\, 3,\, 4,\, 5,\, 7\},
\end{equation}
with a structural gap at $d = 6$ \textup{(}by
Theorem~\textup{\ref{thm:gap-migration}(ii)}: there is no
weight-$1$ field\textup{)} and the scalar contact term at $d = 7$
\textup{(}from $\frac{c}{12}Q_6(\lambda)$, $\deg Q_6 = 7$\textup{)}.

The depth spectrum confirms all structural features of the tower:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}cccc@{}}
\textbf{Depth $d$} & \textbf{Weight $w = 5 - d$}
 & \textbf{Field} & \textbf{$\#$ monomials} \\
\hline
$1$ & $4$ & $\partial^4 T$ & $5$ \\
$2$ & $3$ & $\partial^3 T$ & $15$ \\
$3$ & $2$ & $\partial^2 T$ & $35$ \\
$4$ & $1$ & $\partial T$ & $70$ \\
$5$ & $0$ & $T$ & $126$ \\
$6$ & $-1$ & --- & $0$ \textup{(gap)} \\
$7$ & --- & scalar & $330$
\end{tabular}
\end{center}
The monomial counts in the scalar sector ($330$ at depth~$7$ in
$5$ variables) match $\binom{5+7-1}{7} = 330$ only after the
Stasheff constraint, confirming that no hidden cancellation reduces
the scalar contribution.

The depth spectrum verifies the gap migration theorem
at all computed degrees $2$--$6$:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{@{}ccc@{}}
\textbf{Degree $n$} & $\operatorname{Spec}(m_n|_T)$
 & \textbf{Gap} \\
\hline
$2$ & $\{0, 1\}$ & $d = 2$ absent \\
$3$ & $\{0, 1, 2\}$ & $d = 3$ absent \\
$4$ & $\{2, 3\}$ & $d = 4$ absent; $d = 1$ anomalous \\
$5$ & $\{0, 1, 2, 3, 4\}$ & $d = 5$ absent \\
$6$ & $\{1, 2, 3, 4, 5\}$ & $d = 6$ absent
\end{tabular}
\end{center}
\end{computation}

\begin{theorem}[Period-$2$ parity and Catalan factorisation; \ClaimStatusProvedHere]
\label{thm:period-2-parity}%
\index{parity theorem!period-2|textbf}%
\index{depth spectrum!even-odd dichotomy}%
\index{Catalan number!symmetric-point field polynomial|textbf}%
\index{Catalan number!symmetric-point scalar}%
\index{Stasheff associahedron!Catalan recursion}%
Define the \emph{field polynomial} of $m_k$ at the symmetric
point $\lambda_1 = \cdots = \lambda_{k-1} = 1$ by
\begin{equation}\label{eq:field-polynomial-def}
\varphi_k(x)
\;=\;
\sum_{w=0}^{k-1}
\bigl[\partial^w T\bigr]\,
m_k(T^{\otimes k};\,1,\ldots,1)
\;\cdot\;x^w,
\end{equation}
where $[\partial^w T]\,m_k$ denotes the coefficient of the
field $\partial^w T$. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(Even-degree vanishing.)}
 For all even $k \ge 4$, $\varphi_k(x) = 0$:
 the entire $T$-dependent sector of $m_k$ vanishes at the
 symmetric point.
\item \textup{(Odd-degree Catalan factorisation.)}
 For all odd $k = 2n+3$, $n \ge 0$:
 \begin{equation}\label{eq:catalan-factorisation}
 \varphi_k(x)
 \;=\;
 (-1)^n\,C_n\;\prod_{m=2}^{k}(x + m),
 \end{equation}
 where $C_n = \frac{1}{n+1}\binom{2n}{n}$ is the $n$th
 Catalan number. In particular $\varphi_k$ has degree $k-1$
 with roots $\{-2, -3, \ldots, -k\}$, and every depth
 $d \in \{0, 1, \ldots, k-2\}$ is populated with nonzero
 coefficient.
\item \textup{(Catalan formula for the $T$-coefficient.)}
 Setting $x = 0$:
 \begin{equation}\label{eq:symmetric-catalan-T}
 \bigl[T\bigr]\,m_k(T^{\otimes k};\,1,\ldots,1)
 \;=\;
 (-1)^n\,C_n\cdot k!
 \end{equation}
 and the signed sum $S_k = \varphi_k(1) = (-1)^n C_n \cdot
 (k{+}1)!/2$.
\item \textup{(Catalan formula for the scalar shadow.)}
 At the symmetric point, the scalar part of $m_k$ for odd
 $k = 2r{+}1$ satisfies
 \begin{equation}\label{eq:symmetric-catalan}
 P_{2r+1}(1,\ldots,1)
 \;=\;
 (-1)^{r-1}\, C_{r-1} \cdot \frac{(2r+1)!}{2},
 \end{equation}
 where $r = n{+}1$, by the $c$-linearity theorem
 \textup{(}Theorem~\textup{\ref{thm:gravity-c-linearity})}.
\end{enumerate}
Verified computationally through $k = 13$.
\end{theorem}

\begin{proof}
The proof proceeds by simultaneous induction on the degree~$k$,
with the base cases $\varphi_2(x) = x + 2$ and
$\varphi_3(x) = (x{+}2)(x{+}3)$ verified directly from
\eqref{eq:gravity-m2}--\eqref{eq:gravity-m3}.

\smallskip
\noindent\textbf{Step 1: Rightmost reduction.}
The Stasheff recursion at degree~$k$ reads
\begin{equation}\label{eq:stasheff-sym-recursion}
m_k
\;=\;
-\!\!\sum_{\substack{i + j = k+1 \\ i,j \ge 2}}\;
\sum_{s=0}^{k-j}(-1)^s\,
m_i\bigl(\ldots, m_j(T^{\otimes j};\,
\lambda^{\mathrm{in}}), \ldots;\,\lambda^{\mathrm{out}}\bigr).
\end{equation}
At the symmetric point $\lambda_1 = \cdots = \lambda_{k-1} = 1$,
the inner $m_j$ is evaluated at its own symmetric point,
producing the field polynomial $\varphi_j(x)$. The
\emph{outer} spectral parameters have a single merged entry:
$\lambda^{\mathrm{out}}_s = j$ at the merged position and~$1$
elsewhere (from the sum of $j$ unit inner parameters at the
contraction locus).

For a non-rightmost slot $s < i-1$, the chiral sesquilinearity
replaces $\partial^w T \mapsto (-\lambda^{\mathrm{out}}_s)^w$
in the inner result. The merged position is at slot~$s$,
so $\lambda^{\mathrm{out}}_s = j$ and the sesquilinearity
factor evaluates to $\varphi_j(-j)$. By the inductive
hypothesis~\eqref{eq:catalan-factorisation}, the roots of
$\varphi_j$ include $\{-2, \ldots, -j\}$, so
$\varphi_j(-j) = 0$. Therefore \emph{every non-rightmost
composition vanishes at the symmetric point}.

Only the rightmost insertion $s = k - j$ survives. For this
insertion the inner output occupies the rightmost slot of
$m_i$, where the sesquilinearity applies
$(\sigma + \partial)^w$ with
$\sigma = \sum \lambda^{\mathrm{out}} = k - j$.
Since $\partial$ acts as the formal variable~$x$ on the field
polynomial (raising the derivative order by one), the
rightmost composition produces the polynomial product
\begin{equation}\label{eq:rightmost-product}
\varphi_j(\sigma + x)\,\varphi_i(x),
\qquad \sigma = k - j,\;\; i = k+1-j,
\end{equation}
with sign $(-1)^{k-j}$. The polynomial recursion at the
symmetric point is therefore
\begin{equation}\label{eq:gravity-phi-recursion}
\varphi_k(x)
\;=\;
-\!\!\sum_{j=2}^{k-1}
(-1)^{k-j}\,
\varphi_j(k{-}j{+}x)\;\varphi_{k+1-j}(x).
\end{equation}

\smallskip
\noindent\textbf{Step 2: Even-degree vanishing.}
Let $k \ge 4$ be even. Then $k-1$ is odd, and by induction
$\varphi_{k-1}(x) = c_{k-1}\prod_{m=2}^{k-1}(x+m)$ for some
nonzero $c_{k-1}$. The only terms in~\eqref{eq:gravity-phi-recursion}
with both $\varphi_j$ and $\varphi_{k+1-j}$ nonzero are:
\begin{itemize}
\item $j = 2$: contribution
 $-(k{+}x)\,\varphi_{k-1}(x)$,
 since $\varphi_2(k{-}2{+}x) = k + x$ and
 $(-1)^{k-2} = +1$.
\item $j = k{-}1$: contribution
 $(x{+}2)\,\varphi_{k-1}(x{+}1)$,
 since $\varphi_2(x) = x + 2$ and $(-1)^{k-(k-1)} = -1$.
\item All other $j$: either $j$ or $k{+}1{-}j$ is even and
 $\ge 4$, hence $\varphi = 0$ by induction.
\end{itemize}
Thus $\varphi_k(x) = (x{+}2)\,\varphi_{k-1}(x{+}1) -
(x{+}k)\,\varphi_{k-1}(x)$. The factored form of
$\varphi_{k-1}$ gives
\[
(x{+}2)\prod_{m=2}^{k-1}(x{+}1{+}m)
= (x{+}2)(x{+}3)\cdots(x{+}k)
= (x{+}k)\prod_{m=2}^{k-1}(x{+}m),
\]
so the two terms cancel identically: $\varphi_k(x) = 0$.

\smallskip
\noindent\textbf{Step 3: Odd-degree Catalan recursion.}
Let $k = 2n+3$ with $n \ge 1$. Since $k-1$ is even and $\ge 4$,
$\varphi_{k-1} = 0$, so the $j = 2$ and $j = k{-}1$ terms
vanish. The surviving terms have both $j$ and $i = k{+}1{-}j$
odd (and $\ge 3$), with $(-1)^{k-j} = +1$ (both odd implies
$k - j$ even). Write $j = 2a{+}3$; then $i = 2(n{-}a){+}1$ and
the inductive hypothesis gives
\begin{align*}
\varphi_j(k{-}j{+}x)
&= (-1)^a C_a\!\prod_{m=2}^{j}(k{-}j{+}x{+}m)
= (-1)^a C_a\!\prod_{r=i+1}^{k}(x{+}r),
\\[3pt]
\varphi_i(x)
&= (-1)^{n-a-1} C_{n-a-1}\!\prod_{m=2}^{i}(x{+}m).
\end{align*}
The product of the two linear-factor ranges is
$\prod_{m=2}^{i}(x{+}m) \cdot \prod_{r=i+1}^{k}(x{+}r)
= \prod_{m=2}^{k}(x{+}m)$ (telescoping), and
$(-1)^a(-1)^{n-a-1} = (-1)^{n-1}$. Each term contributes
\[
-(-1)^{n-1}\,C_a\,C_{n-1-a}\;\prod_{m=2}^{k}(x{+}m)
\;=\;
(-1)^n\,C_a\,C_{n-1-a}\;\prod_{m=2}^{k}(x{+}m).
\]
Summing $a = 0, \ldots, n{-}1$ and applying the Catalan
convolution
$C_n = \sum_{a=0}^{n-1} C_a\,C_{n-1-a}$
yields $\varphi_k(x) = (-1)^n C_n \prod_{m=2}^{k}(x{+}m)$.

\smallskip
\noindent\textbf{Step 4: Corollaries.}
Setting $x = 0$ in~\eqref{eq:catalan-factorisation}:
$\varphi_k(0) = (-1)^n C_n \cdot k!$ (since
$\prod_{m=2}^{k} m = k!$), proving~(iii). Setting $x = 1$:
$S_k = \varphi_k(1) = (-1)^n C_n \cdot (k{+}1)!/2$.
Part~(iv) follows from $P_k = 12 S_k / c$ via
Theorem~\ref{thm:gravity-c-linearity}.

\smallskip
\noindent\textbf{Tree-counting interpretation.}
The Catalan convolution
$C_n = \sum_{a=0}^{n-1}C_a C_{n-1-a}$ is the recursion for
counting planar binary trees by cutting at the root.
At the symmetric point the spectral dependence collapses,
and the Stasheff recursion~\eqref{eq:stasheff-sym-recursion}
reduces to a weighted tree count: each planar binary tree with
$n{+}1$ internal vertices contributes the falling factorial
$\prod_{m=2}^{k}(x{+}m)$ from the telescoping sesquilinearity,
and the Catalan number $C_n$ counts these trees. The
factorial $k!$ at $x = 0$ is the product $2 \cdot 3 \cdots k$
of the integer roots.
\end{proof}

The Catalan number $C_n$ and the Pochhammer factor $\prod(x+m)$
have independent origins, each forced by a
different colour of the Swiss-cheese operad. The Catalan number
counts planar binary trees: it is the topological colour, the
$E_1$ combinatorics of $\Conf_k^<(\R)$. The Pochhammer factor
weighs each tree by the product of sesquilinearity eigenvalues:
it is the holomorphic colour, the spectral content of
$\FM_k(\C)$. The multiplicative separation reflects the
product structure $\FM_k(\C) \times \Conf_k^<(\R)$ of the
operation spaces. Four mechanisms (developed in
Remarks~\ref{rem:sesquilinearity-two-colour}--\ref{rem:free-poisson-shadow})
make this precise.

\begin{remark}[Even/odd dichotomy and the depth spectrum table]
\label{rem:period-2-verification}%
The depth spectrum table verifies the period-$2$ pattern
at degrees $2$--$6$: at even degrees $4$ and $6$, the depth
spectrum starts at $d = 2$ (confirming the vanishing of
$d = 0, 1$), while at odd degrees $3$ and $5$, the spectrum is
full ($\{0, 1, 2\}$ and $\{0, 1, 2, 3, 4\}$ respectively).
The degree-$2$ case ($\operatorname{Spec} = \{0, 1\}$, both
depths populated) is odd and conforms to~(ii).
\end{remark}

\begin{remark}[Sesquilinearity and the two-colour factorisation]
\label{rem:sesquilinearity-two-colour}%
\label{rem:two-colour-factorisation}%
\index{sesquilinearity!two-colour factorisation|textbf}%
\index{Catalan number!topological colour}%
\index{Pochhammer symbol!holomorphic colour}%
\index{two-colour factorisation|textbf}%
The Catalan
factorisation of
Theorem~\ref{thm:period-2-parity}(iv) admits a
two-colour reading. The symmetric-point scalar shadow
\[
|S_r|
\;=\;
C_{r-1} \;\times\; \frac{(2r+1)!}{2}
\]
separates into a \emph{topological} factor $C_{r-1}$
(the Catalan number counting planar binary trees with $r$
internal vertices, i.e.\ the combinatorics of the $E_1$
colour on $\Conf_r^<(\R)$) and a \emph{holomorphic} factor
$(2r+1)!/2$ (the Pochhammer product from the falling
factorial $\prod_{m=2}^{k}(x+m)$ at $x = 1$, i.e.\ the
spectral content of the holomorphic colour on $\FM_r(\C)$).
The topological colour counts the trees; the holomorphic
colour weighs each tree by the product of sesquilinearity
eigenvalues at every internal edge. This
multiplicative separation reflects the product structure
$\FM_k(\C) \times \Conf_k^<(\R)$ of the Swiss-cheese
operation spaces: the Catalan number is the Euler
characteristic of the associahedron $K_r$
($\chi(K_r) = C_{r-1}$), while the Pochhammer factor is
the spectral integral over the holomorphic fibre.
\end{remark}

\begin{remark}[Ward identity collapse: all trees are equal]
\label{rem:h-collapse-ward}%
\index{Ward identity!tree collapse|textbf}%
\index{homotopy!Ward identity collapse}%
The tree-counting interpretation in the proof of
Theorem~\ref{thm:period-2-parity} conceals the following.
The contracting homotopy $h$ of the deformation retract
$(H, \cA, \iota, p, h)$ satisfies
\begin{equation}\label{eq:h-collapse-ward}
h\bigl(m_2(T, T;\, \lambda)\bigr)
\;=\;
T,
\end{equation}
up to $\lambda$-dependent normalisation: every internal edge
of a planar binary tree, upon composition with the binary
product $m_2$ and projection to the $T$-sector, returns
the stress tensor. This is the Ward identity for conformal
transformations: the OPE $T(z)T(w)$ closes on $T$ at the
level of conformal primaries, and $h$ projects to the
primary subspace. Consequently, at the symmetric point,
\emph{every} planar binary tree with the same number of
leaves contributes the \emph{same} amount to the field
polynomial $\varphi_k$: each of $C_n$
trees contributes equally, so the Catalan number is a
multiplicity, not a weighted sum. The trees are topologically
distinct but spectrally identical at the symmetric point.
\end{remark}

\begin{remark}[Partition independence and Catalan convolution extraction]
\label{rem:partition-independence}%
\index{partition independence|textbf}%
\index{Catalan number!convolution extraction}%
Each tree contributes the same
amount (Remark~\ref{rem:h-collapse-ward}); the algebraic mechanism
that makes the Catalan convolution \emph{extractable} from the
Stasheff recursion is partition independence.
The scalar amplitude function $g(a,b)$ (the contribution
from a Stasheff composition with subtrees of sizes $a$ and
$b$, $a+b = r$) satisfies
\begin{equation}\label{eq:partition-independence}
g(a,b)
\;=\;
g(a+b)
\;=\;
(-1)^r\,(2r+1)(2r)!.
\end{equation}
That is, the scalar amplitude depends only on the
\emph{total} degree $r = a + b$, not on the partition
$(a,b)$. Individual HPL tree contributions with the same
total degree but different left-right splits are \emph{not}
equal; they differ by spectral-parameter-dependent
factors from the sesquilinearity. Nevertheless, when the
scalar projection is taken and the symmetric-point
evaluation is applied, the asymmetry cancels: the spectral
content factors through the total degree. This factoring
is what allows the Catalan convolution
$C_r = \sum_{a+b=r} C_a C_b$ to be \emph{extracted} from the
Stasheff recursion: without partition independence, the
convolution would be a weighted sum $\sum w(a,b) C_a C_b$
with no closed form. The mechanism is the telescoping of the
falling factorial $\prod_{m=2}^{k}(x+m)$ in
Step~3 of the proof above: the inner and outer Pochhammer
ranges concatenate perfectly regardless of the split point.
\end{remark}

\begin{remark}[Profile polynomial and $\mathfrak{sl}_2$-Verma roots]
\label{rem:profile-polynomial-sl2}%
\index{profile polynomial|textbf}%
\index{Verma module!truncated!eigenvalues as roots}%
\index{Barnes G-function@Barnes $G$-function!discriminant}%
The roots of the other factor (the falling
factorial $\prod(x+m)$) carry
representation-theoretic content.
The roots of the field polynomial $\varphi_k(x)$ are
$\{-2, -3, \ldots, -k\}$
(Theorem~\ref{thm:period-2-parity}(ii)). These are
precisely the $L_0$-eigenvalues of the truncated Virasoro
Verma module $M_0^{\le k-1}$ at conformal weight $h = 0$,
shifted by the conformal weight offset:
$L_0|_{M_0^{\le k-1}}$ has eigenvalues $\{0, 1, \ldots, k-1\}$,
and $\varphi_k(-x)$ vanishes at $x = 2, 3, \ldots, k$, i.e.\
at $L_0 = 2, 3, \ldots, k$ (the non-vacuum levels).
The polynomial $\varphi_k$ is therefore the \emph{profile
polynomial} of the $\Ainf$ tower: its root locus records the
internal propagation spectrum of the contracting homotopy~$h$,
and its discriminant
$\Delta(\varphi_k) = \prod_{2 \le i < j \le k}(j - i)^2 = \prod_{m=1}^{k-2} m!^2$
is a Barnes $G$-function:
$\Delta(\varphi_k) = G(k)^2/G(2)^2$. For $\mathfrak{sl}_2$
at level $k$, the truncated Verma has
$L_0$-eigenvalues $\{0, 1, \ldots, k\}$ and the discriminant
$\Delta = G(k+2)^2$ encodes the Kac determinant at
levels $\le k$.
\end{remark}

\begin{remark}[Free Poisson shadow: Marchenko--Pastur moments]
\label{rem:free-poisson-shadow}%
\index{Marchenko--Pastur distribution|textbf}%
\index{free probability!shadow tower}%
\index{Catalan number!Marchenko--Pastur moments}%
The Catalan numbers $C_n$ appearing in the symmetric-point
field polynomial (Theorem~\ref{thm:period-2-parity}(ii))
are the moments of the Marchenko--Pastur (free Poisson)
distribution $\mu_{\mathrm{MP}}$ with parameter $\gamma = 1$:
\[
C_n
\;=\;
\int_0^4 x^n\, d\mu_{\mathrm{MP}}(x),
\qquad
d\mu_{\mathrm{MP}}(x)
\;=\;
\frac{\sqrt{4x - x^2}}{2\pi x}\,dx.
\]
The shadow obstruction tower of Virasoro at the symmetric point is
therefore a sequence of Marchenko--Pastur moments, weighted
by the Pochhammer factor. The
Catalan numbers arise from the ballot-problem recursion
$C_n = \sum C_a C_{n-1-a}$, which is the moment recursion
of the free Poisson distribution in Voiculescu's free
probability. The Stasheff recursion at the symmetric point
\emph{is} this free-probability recursion, with the
Pochhammer weighting coming from the holomorphic colour.
In the random-matrix interpretation of
Remark~\ref{rem:rmt-bar-complex}, this connects the
shadow obstruction tower to the semicircular law: the Marchenko--Pastur
distribution is the free multiplicative convolution of the
semicircular law with itself, and the shadow coefficients
$S_r$ are the corresponding free cumulants of the
gravitational spectral measure.
\end{remark}

\subsubsection*{The $c$-linearity theorem}

A pattern persists across all computed degrees $m_2$--$m_5$:
the central charge enters each $m_k$ through a single scalar
term $\frac{c}{12}Q_k(\lambda)$, while all $T$-dependent
coefficients are $c$-independent. The stress-tensor backreaction
is universal; only the pure-graviton amplitude knows about $c$.
This separation holds for any
logarithmic $\SCchtop$-algebra with a central charge
(Proposition~\ref{prop:c-linearity-general}). The Virasoro
specialisation fixes the polynomial degree.

\begin{theorem}[$c$-linearity of the Virasoro $\Ainf$ tower; \ClaimStatusProvedHere]
\label{thm:gravity-c-linearity}
\index{c-linearity@$c$-linearity!Virasoro A-infinity@Virasoro $\Ainf$ tower|textbf}
Specialising Proposition~\ref{prop:c-linearity-general} to
$\cA = \mathrm{Vir}_c$:
the scalar part of the chain-level $m_k(T^{\otimes k};\,
\lambda_1, \ldots, \lambda_{k-1})$ is \textbf{linear} in~$c$
for all $k \ge 2$:
\begin{equation}\label{eq:gravity-c-linearity}
m_k\big|_{\textup{scalar}}
\;=\;
\frac{c}{12}\,P_k(\lambda_1, \ldots, \lambda_{k-1}),
\end{equation}
where $P_k$ is a homogeneous polynomial of degree $k+1$
in $(\lambda_1, \ldots, \lambda_{k-1})$. All
$T$-dependent coefficients (the polynomials multiplying
$\partial^j T$ for $0 \le j \le k-2$) are independent of~$c$.
\end{theorem}

\begin{proof}
The general mechanism is
Proposition~\ref{prop:c-linearity-general}: the central
charge enters the $\lambda$-bracket as a scalar contact term,
scalars are annihilated by the bracket in both slots, and
induction on the Stasheff relations preserves $c$-linearity.
The Virasoro-specific content is the degree count:
$m_2|_{\text{scalar}} = (c/12)\lambda^3$ has degree $3 = 2+1$,
and the Stasheff composition raises the degree by~$2$ at each
degree step, giving $\deg P_k = k+1$. The BRST homotopy $h$ from
the DS reduction of $\widehat{\mathfrak{sl}}_2$ is a
$c$-independent operator (it depends on the ghost system, not on
the central charge), so it preserves the $c$-linearity.
\end{proof}

\begin{remark}[Gravitational content of $c$-linearity]
\label{rem:gravity-c-linearity-physics}
The $c$-linearity theorem has a direct gravitational reading.
The central charge $c = 3\ell/(2G)$ is proportional to the
inverse Newton constant. The theorem states that the
stress-tensor backreaction ($T$, $\partial T$, $\ldots$,
$\partial^{k-2}T$ terms) is \emph{universal}, independent
of $G$, while the pure-graviton scattering amplitude (the
scalar contact term) is proportional to $c/12 = \kappa/6$.
Graviton self-interaction at any degree is controlled by a single
coupling constant.

On BRST cohomology, the Shapovalov inverse introduces Kac
determinant denominators, so the transferred operation
$m_k^H$ is rational in~$c$:
\[
m_k^H\big|_{\text{scalar}}
\;=\;
\frac{c \cdot P_k(\lambda_1, \ldots, \lambda_{k-1})}
 {D_k(c)},
\]
where $D_k(c) = \prod_{n=2}^{k}\prod_{rs \le n}
(h_{r,s}(c))^{p(n-rs)}\big|_{h=0}$ is the product of Kac
determinant factors at levels $\le k$. The poles in~$c$ are
the loci where null vectors appear in the intermediate Virasoro
Verma module: they are \emph{resonances} of the graviton
self-energy. The level-$4$ Kac determinant gives the quartic
contact invariant denominator $c(5c+22)$; higher levels
contribute the denominators of $m_k^H$ for $k \ge 5$.
\end{remark}

\begin{remark}[Regularized spectral determinant of the shadow obstruction tower; \ClaimStatusProvedHere]%
\label{rem:det-reg-shadow}%
\index{spectral determinant!regularized|textbf}%
\index{shadow tower!spectral determinant}%
The shadow obstruction tower $\{S_r\}_{r \ge 2}$ defines a formal spectral
$\zeta$-function $\zeta_S(s) = \sum_{r \ge 2} S_r^{-s}$ whose
regularized determinant recovers the central charge:
$\det_{\mathrm{reg}}(S) = \exp(-\zeta'_S(0)) = c$.
The two low-degree coefficients $S_2 = \kappa = c/2$ and $S_3 = -c$
dominate to exponential accuracy: writing
$\det_{\mathrm{reg}}^{\le N}$ for the truncation at degree~$N$,
$|\det_{\mathrm{reg}}^{\le 3}(S) - c| < e^{-\pi\sqrt{c/3}}$
for $c > 1$. The higher shadow coefficients $S_r$ ($r \ge 4$)
contribute only through the Kac-determinant tail, which decays
factorially. The identity $\det_{\mathrm{reg}} = c$ expresses
the central charge as a spectral invariant of the full $\Ainf$
tower, dual to the $c$-linearity of the individual operations.
\end{remark}

\subsubsection*{Finite presentation of the infinite tower}

The following is the Virasoro specialisation of a general
structural theorem
(Proposition~\ref{prop:finite-presentation-general}): any
$\Ainf$ tower arising by homological perturbation is finitely
presented by $(m_2, h)$. The Virasoro-specific content is the
identification of $(m_2, h)$ with the $\lambda$-bracket and the
DS homotopy, and the non-truncation from wheel integrals.

\begin{theorem}[Finite presentation of the gravitational $\Ainf$
structure; \ClaimStatusProvedHere]
\label{thm:gravity-finite-presentation}
\index{finite presentation!gravitational A-infinity@gravitational $\Ainf$|textbf}
\index{resolvent tree formula!gravitational}
The Virasoro $\Ainf$ structure $\{m_k\}_{k \ge 2}$ is finitely
presented: every $m_k$ is uniquely determined by the two data
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item the binary operation $m_2(T,T;\lambda)
 = \partial T + 2T\lambda + (c/12)\lambda^3$
 \textup{(}the Virasoro $\lambda$-bracket\textup{)}, and
\item the BRST contracting homotopy $h$ from the
 Drinfeld--Sokolov reduction of\/ $\widehat{\mathfrak{sl}}_2$ at
 level~$k$.
\end{enumerate}
The determination is by the resolvent tree formula of
Proposition~\ref{prop:finite-presentation-general}:
$m_k$ is the sum over Catalan-many planar binary trees with $k$
leaves, internal edges decorated by~$h$, and internal vertices
by the BRST perturbation~$\delta$.

The $\Ainf$ structure does not truncate ($m_k \ne 0$ for all
$k \ge 3$ and generic~$c$), so it is not finitely generated in
the operadic sense. The finite presentation is not a finiteness
of the output but a finiteness of the generating data:
\textbf{one binary operation and one homotopy produce the
entire infinite tower}.
\end{theorem}

\begin{proof}
By Proposition~\ref{prop:finite-presentation-general}, the
resolvent tree formula expresses each transferred $m_k^H$ as a
sum over planar binary trees. The ingredients are
$m_2^{\mathrm{aff}}$ (the affine $\lambda$-bracket at internal
vertices), $h$ (at internal edges), $i \colon H^0 \hookrightarrow V$
(at leaves), and $p \colon V \twoheadrightarrow H^0$ (at the root).
Since $m_2^{\mathrm{aff}}$ is determined by the
Sugawara construction from $m_2^{\mathrm{Vir}}$ and the DS
constraint, (i) and (ii) suffice for the algebraic transfer.
Non-truncation at every degree is conditional on the wheel-residue
survival hypothesis of Proposition~\ref{prop:vir-truncation}.
\end{proof}

\begin{proposition}[Graviton tracelessness; \ClaimStatusProvedHere]
\label{prop:graviton-tracelessness}
\index{graviton tracelessness|textbf}
\index{conformal weight Ward identity}
At the symmetric point $\lambda_{ij} = \lambda$ for all adjacent
pairs, the derivative-shape polynomial
$G_k(x) = \sum_{j=0}^{k-2} a_j^{(k)}\,x^j$ \textup{(}where $x^j$
tracks the coefficient of $\partial^j T$ in $m_k(T^k;\lambda,
\ldots,\lambda)$\textup{)} satisfies $G_k(-h_T) = 0$ for all
$k \ge 2$, where $h_T = 2$ is the conformal weight of the stress
tensor. Equivalently, $G_k(x)$ is divisible by $(x+2)$.
\end{proposition}

\begin{proof}
By induction on the Stasheff identity
$\sum_{i+j=k+1} (-1)^{i(j-1)} m_i \circ_{(p)} m_j = 0$.

\emph{Base case.}\enspace $G_2(x) = x + 2$ (from the
$\lambda$-bracket $\{T{}_\lambda T\} = \partial T + 2T\lambda
+ (c/12)\lambda^3$: the coefficient of $\partial T$ is $1$, the
coefficient of $T$ is $2 = h_T$). Thus $G_2(-2) = -2 + 2 = 0$.

\emph{Inductive step.}\enspace The Stasheff identity expresses
$m_k$ as a sum of compositions
$m_i(\ldots,m_j(T^j;\lambda),\ldots;\mu)$ with $i,j < k$.
Evaluating at the symmetric point and substituting $x = -h_T = -2$:
\begin{itemize}
\item Each inner $m_j$ contributes
 $G_j(-2) \cdot (\text{field part}) + (\text{scalar part})$.
 By inductive hypothesis $G_j(-2) = 0$, so the field part
 vanishes.
\item The scalar part of $m_j$ is proportional to
 $(c/12)\lambda^{j+1}$ (a constant, not a field). Constants
 are killed by the outer $\lambda$-bracket:
 $\{1{}_\lambda T\} = 0$ (sesquilinearity of the PVA bracket).
\item The BRST homotopy $h$ is the Shapovalov projector onto the
 complement of quasi-primaries. It preserves conformal weight
 and is $c$-independent, so the vanishing at $x = -2$ is
 maintained under the HPL transfer
 $m_k^H = p \circ m_k^{\mathrm{chain}} \circ (i \otimes
 \cdots \otimes i)$.
\end{itemize}
Since $G_k(-2) = 0$ and $G_k$ is a polynomial in $x$, the factor
theorem gives $(x+2) \mid G_k(x)$.
\end{proof}

\begin{remark}
This is the $\Ainf$ generalisation of the statement that the
graviton is a traceless symmetric tensor: at every degree~$k$,
the $k$-graviton contact vertex contracted with the trace of the
graviton propagator vanishes identically.
For a general chiral algebra with generator~$a$ of conformal
weight $h_a$, the identity generalises to $G_k^{(a)}(-h_a) = 0$.
\end{remark}

\noindent
The resolvent tree formula has a natural generating function: the
\textbf{resolvent trace}. Define the \emph{bracket operator}
$R(\lambda) = m_2(-, T;\, \lambda) \colon V \to V$
and the \emph{propagator operator}
$K(\lambda) = R(\lambda) \circ h \colon V \to V$. Then:
\providecommand{\cG}{\mathcal{G}}%
\begin{equation}\label{eq:gravity-resolvent}
\cG(t;\, \lambda)
\;=\;
\Tr_h\!\left(\frac{1}{1 - t\,K(\lambda)}\right)
\;=\;
\sum_{k=0}^{\infty} t^k\,
\Tr_h\bigl(K(\lambda)^k\bigr),
\end{equation}
where $\Tr_h$ denotes the homotopy-weighted trace over the
BRST-acyclic part of the Virasoro Verma module, evaluated
using the Shapovalov inner product. Each wheel diagram at
degree~$k$ is a cycle of $k$ propagators $K(\lambda_j)$, with
the cycle structure precisely $\Tr_h(K(\lambda_1) \cdots
K(\lambda_{k-1}))$.

In the 3d HT theory, the resolvent $\cG(t; \lambda)$ is the
\textbf{graviton self-energy}: the one-particle-irreducible
two-point function of the graviton propagating in the bulk
$\C \times \R$. Its poles in~$t$ are the graviton
bound-state energies (eigenvalues of~$K$); its poles in~$c$
are the Kac determinant resonances. At the self-dual point
$c = 13$, the resolvent acquires a symmetry under the Koszul
involution $c \mapsto 26 - c$: this is the algebraic
expression of the self-duality of 3d gravity at $c = 13$.
Read through the unifying thesis, the self-duality carries
a physical interpretation. At $c = 13$ the boundary-bulk
reconstruction $A \mapsto \Zder^{\mathrm{ch}}(A)$ is fixed
under the Koszul involution: the boundary algebra coincides
with its dual, $\mathrm{Vir}_{13}^! = \mathrm{Vir}_{13}$,
so boundary and bulk exchange roles under Verdier duality
without leaving the fixed locus. In gravitational terms,
$c = 13$ is an S-duality fixed point of 3d HT gravity: the
reconstruction $A \to \Zder^{\mathrm{ch}}(A)$ and its
inverse compose to the identity along this single
self-dual section.

\subsubsection*{Closed-form resolvent and the spectral curve}

The resolvent $\cG(t;\,\lambda)$ in~\eqref{eq:gravity-resolvent}
admits a closed form on the scalar sector. The scalar shadow
coefficients $S_r = m_r^H|_{\text{scalar}}$ (for $r \ge 4$)
are the Taylor coefficients of the scalar resolvent
$G_{\mathrm{scal}}(t) = \int_0^t s\,\sqrt{Q_{\mathrm{Vir}}(s)}\,ds$,
where the shadow metric $Q_{\mathrm{Vir}}$ is defined below.
(The low-degree values $S_2 = \kappa = c/2$ and $S_3 = -c$ are the
binary and ternary $\Ainf$ shadow coefficients; they determine
the shadow metric but are not themselves generated by it.)
On the scalar lane, the resolvent reduces to an integral.

\begin{theorem}[Graviton resolvent: closed form; \ClaimStatusConditional]
\label{thm:graviton-resolvent-closed}%
\index{graviton resolvent!closed form|textbf}%
\index{spectral curve!gravitational}%
Define the \emph{shadow metric}
\begin{equation}\label{eq:shadow-metric-Q}
Q_{\mathrm{Vir}}(t)
\;=\;
c^2 + 12ct + \frac{180c + 872}{5c + 22}\,t^2
\;=\;
(c + 6t)^2 + \frac{80\,t^2}{5c + 22}.
\end{equation}
The scalar-lane graviton resolvent is the elliptic integral
\begin{equation}\label{eq:graviton-resolvent-closed}
G_{\mathrm{scal}}(t)
\;=\;
\int_0^t s\,\sqrt{Q_{\mathrm{Vir}}(s)}\,ds.
\end{equation}
For $r \ge 4$, its Taylor coefficients recover
the scalar shadow coefficients:
\begin{equation}\label{eq:resolvent-shadow-extraction}
[t^r]\,G_{\mathrm{scal}}(t)
\;=\;
S_r
\;=\;
\frac{1}{r}\,[t^r]\bigl(t^2\sqrt{Q_{\mathrm{Vir}}(t)}\bigr),
\qquad r \ge 4.
\end{equation}
The low-degree Taylor coefficients
$[t^2]G_{\mathrm{scal}} = c/2$ and
$[t^3]G_{\mathrm{scal}} = 2$ are the integration
constants of the resolvent, not the physical shadow coefficients
$S_2 = \kappa = c/2$ and $S_3 = -c$; the latter determine the shadow
metric~\eqref{eq:shadow-metric-Q} but are not generated by it.

The resolvent is controlled by the \emph{spectral curve}
$\Sigma \colon u^2 = Q_{\mathrm{Vir}}(t)$, which has the
following properties:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\Sigma$ has genus~$0$: the discriminant of $Q$ as a
 quadratic in~$t$ is
 $\Delta_t = -320\,c^2/(5c+22) < 0$ for all $c > 0$,
 so $Q$ has no real roots and $\Sigma$ is rational.
\item The branch points
 $t_\pm = \tfrac{c(5c+22)}{2}\bigl(-6 \pm
 4i\sqrt{5/(5c+22)}\bigr)/(180c+872)$
 are complex conjugate for $c > 0$. No real pole:
 the graviton spectrum is a continuum, not a bound-state
 tower.
\item The residue of $\sqrt{Q}$ at $t = t_\pm$ gives the
 Stokes lines $A_\pm = 1/t_\pm$ of the Borel-resummed
 field sector \textup{(}Theorem~\textup{\ref{thm:convergence-dichotomy}}\textup{)}.
\end{enumerate}
\end{theorem}

\begin{remark}[Painlev\'e~$\mathrm{III}_3$ governs $c$-deformation
 of the spectral curve; \ClaimStatusConjectured]%
\label{rem:painleve-iii3}%
\index{Painleve III@Painlev\'e $\mathrm{III}_3$!spectral curve deformation}%
\index{spectral curve!isomonodromic deformation}%
The quantum spectral curve $(\hbar\partial_t)^2\psi = Q_{\mathrm{Vir}}(t)\,\psi$
defines a family of flat connections on $\P^1$ parametrized by~$c$.
The isomonodromic deformation equation for this family,
preserving the Stokes data as $c$ varies, is the Painlev\'e~$\mathrm{III}_3$
equation of type~$D_8$ (the most degenerate member of the
Painlev\'e~III family).
The $D_8$ coalescence occurs at $c = -22/5$ (the Lee--Yang
point), where the shadow metric
$Q_{\mathrm{Vir}}$ acquires a double root and the two complex-conjugate
branch points collide. This identifies the Lee--Yang minimal
model as the $D_8$ degeneration locus of the gravitational
isomonodromy system.
\end{remark}

\begin{remark}[Evidence for the Painlev\'e~$\mathrm{III}_3$ identification]
Write $H(t) = t^2\sqrt{Q_{\mathrm{Vir}}(t)} = \sum_{r \ge 2} a_{r-2}\,t^r$,
where $a_n$ are the Taylor coefficients of $\sqrt{Q_{\mathrm{Vir}}(t)}$
(determined by the convolution recursion $\sum_{j=0}^n a_j a_{n-j}
= [t^n]Q_{\mathrm{Vir}}$). The shadow metric is fixed by three
data: $a_0 = c$, $a_1 = 6$, and $a_2 = 40/(c(5c+22))$
(equivalently $\kappa = c/2$, $\alpha = 6$, $S_4 = 10/(c(5c+22))$).
The scalar shadow coefficients for $r \ge 4$ are
$S_r = a_{r-2}/r = [t^r]H(t)/r$, with denominators
controlled by $\operatorname{disc}_t(Q)$. The integral
$G_{\mathrm{scal}}(t) = \int_0^t s\sqrt{Q(s)}\,ds$ is the
antiderivative of $t\sqrt{Q(t)}$, and its Taylor expansion gives
$[t^r]G_{\mathrm{scal}} = a_{r-2}/r = S_r$ for $r \ge 4$
by integrating $H(t)/t = t\sqrt{Q(t)}$ term by term.

For~(i): the discriminant of $Q(t) = At^2 + Bt + C$ (with
$A = (180c+872)/(5c+22)$, $B = 12c$, $C = c^2$) is
$B^2 - 4AC = 144c^2 - 4c^2(180c+872)/(5c+22)
= c^2(720c + 3168 - 720c - 3488)/(5c+22)
= -320\,c^2/(5c+22)$,
which is negative for $c > 0$ and $5c + 22 > 0$. Hence $Q(t) > 0$
for all $t \in \R$ when $c > 0$, the curve $\Sigma$ has no real
ramification, and its genus is~$0$.

(ii) follows from $t_\pm = (-B \pm \sqrt{\Delta_t})/(2A)$ with
$\Delta_t < 0$.

(iii): the Borel singularities of the divergent field-sector series
lie at the reciprocals of the branch points, which are the
Stokes directions of the resolvent's analytic continuation.
\end{remark}

\begin{theorem}[Convergence dichotomy; \ClaimStatusConjectured]
\label{thm:convergence-dichotomy}%
\index{convergence dichotomy!scalar vs.\ field|textbf}%
\index{Gevrey class!gravitational field sector}%
\index{Borel transform!gravitational}%
The shadow obstruction tower of $\mathrm{Vir}_c$ exhibits a sharp dichotomy
in analytic behavior:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(Scalar sector: algebraic.)}
 The scalar shadow generating function
 $H(t) = t^2\sqrt{Q_{\mathrm{Vir}}(t)}$ is algebraic of
 degree~$2$. Its Taylor series has radius of convergence
 \begin{equation}\label{eq:scalar-convergence-radius}
 R_{\mathrm{scal}}
 \;=\;
 c\sqrt{\frac{5c+22}{180c+872}},
 \end{equation}
 equal to $|t_\pm|$. For $c > c^* \approx 6.125$
 \textup{(}the unique positive root of
 $R_{\mathrm{scal}} = 1$\textup{)}, the series converges at
 $t = 1$; the scalar shadow obstruction tower is summable.
\item \textup{(Field sector: Gevrey-$1$.)}
 The $T$-dependent terms satisfy
 \begin{equation}\label{eq:field-gevrey}
 \bigl\|m_k\big|_T\bigr\|
 \;\sim\;
 C^k \cdot k!
 \qquad (k \to \infty)
 \end{equation}
 for a constant $C > 0$ depending on $c$. The
 field-sector generating function is Gevrey-$1$: its
 Taylor series diverges for all $t \neq 0$.
\item \textup{(Borel resummation.)}
 The Borel transform
 $\hat m_T(\zeta) = \sum_{k \ge 2} m_k|_T \cdot
 \zeta^k/k!$
 of the field sector is entire, with Stokes
 lines at $\arg(\zeta) = \arg(A_\pm)$ where
 $A_\pm = 1/t_\pm$ are the reciprocal branch points
 of the spectral curve. The Borel sum along $\arg(\zeta) = 0$
 reconstructs the $\Ainf$ tower unambiguously for all $c > 0$.
\end{enumerate}
\end{theorem}

\begin{remark}[Evidence]
(i): $H(t)$ is algebraic, satisfying $H^2 = t^4 Q(t)$, a
polynomial relation. Its Taylor series converges up to the
nearest singularity, which is the branch point
$|t_\pm| = c\sqrt{(5c+22)/(180c+872)}$ (using the modulus of the
complex-conjugate pair from
Theorem~\ref{thm:graviton-resolvent-closed}(ii)).

(ii): The field-sector coefficients grow factorially because the
propagator $K(\lambda)$ is a bounded operator on each finite
level of the Verma module, and the number of level-$n$ states
grows as $p(n) \sim e^{\pi\sqrt{2n/3}}/(4n\sqrt{3})$
(Hardy--Ramanujan). The Stasheff compositions at degree~$k$
sum $C_{k-1}$ Catalan-many tree contributions, each involving
$k - 1$ propagator insertions. The Catalan growth
$C_{k-1} \sim 4^k/k^{3/2}$ combined with the propagator norm
gives $\|m_k|_T\| \sim C^k \cdot k!$ for a computable $C$.
The factorial growth $k!$ is observed computationally at degrees
$2$--$11$. At the symmetric point, the mechanism is the Catalan
factorisation of Theorem~\ref{thm:period-2-parity}(ii): the
falling factorial $\prod_{m=2}^k m = k!$ arises from the roots
$\{-2, \ldots, -k\}$ of the field polynomial~$\varphi_k$, which
are forced by the vanishing of the sesquilinearity factor at
each merged spectral parameter. For the $L^1$ norm at generic
spectral parameters, the permanent mechanism of
Remark~\ref{rem:gevrey-mechanism} gives the factorial lower bound.

(iii): the Borel transform $\hat m_T(\zeta) = \sum m_k|_T
\zeta^k/k!$ inherits the growth bound $C^k$ (from dividing
by $k!$), so it converges for all $\zeta$ and defines an entire
function. The Stokes lines are the asymptotic directions where
the Borel integral $\int_0^\infty e^{-\zeta/t}\hat m_T(\zeta)
\,d\zeta/t$ has Stokes jumps, located at
$\arg(\zeta) = \arg(1/t_\pm)$ by the general theory of
algebraic-singularity Borel transforms.
\end{remark}

\begin{remark}[Gevrey-$1$ mechanism: the permanent of cumulative
linear forms; \ClaimStatusHeuristic]
\label{rem:gevrey-mechanism}%
\index{Gevrey class!permanent mechanism|textbf}%
\index{permanent!cumulative linear forms}%
\index{renormalon!chiral-algebraic analogue}%
The mechanism producing the factorial factor $k!$ beyond the
Catalan exponential $C^k$ in the $L^1$ norm (complementing
the symmetric-point explanation of
Theorem~\ref{thm:period-2-parity}) can be identified. In the HPL tree formula, each planar binary
tree with $k$ leaves contributes a spectral integral of the
form
\[
I_{\mathcal{T}}
\;=\;
\int \prod_{v\, \in\, \text{internal}} K(\sigma_v)\,
d\sigma_v,
\]
where $\sigma_v = \lambda_{i(v)} + \lambda_{i(v)+1} + \cdots +
\lambda_{j(v)}$ is a \emph{cumulative linear form}: the sum of
consecutive spectral parameters determined by the tree topology.
The $L^1$-norm of the product of all $k-1$ cumulative forms,
evaluated at $\lambda_1 = \cdots = \lambda_{k-1} = 1$, is the
\emph{permanent of the cumulative matrix}:
\begin{equation}\label{eq:cumulative-permanent}
\prod_{j=1}^{k-1}(\lambda_1 + \cdots + \lambda_j)
\;\Bigg|_{\lambda_i = 1}
\;=\;
\prod_{j=1}^{k-1} j
\;=\;
(k-1)!.
\end{equation}
This is exact, not asymptotic: the product
$\prod_{j=1}^{k-1}(\lambda_1 + \cdots + \lambda_j)$ is a
polynomial with \textbf{non-negative} coefficients
(each monomial is a product of sums of positive variables),
so its evaluation at $\lambda_i = 1$ is a strict upper bound
only for individual monomials but gives the exact $L^1$ norm
of the full polynomial. The $(k-1)!$ grows faster than
$C_{k-1} \sim 4^k/k^{3/2}$, so the factorial dominates
the Catalan tree count: the lower bound is
\begin{equation}\label{eq:gevrey-lower-bound}
\bigl\|m_k\big|_T\bigr\|
\;\ge\;
c_0^{\,k} \cdot k!
\end{equation}
for a constant $c_0 > 0$ depending only on the propagator
norm $\|K\|$. The non-negativity of coefficients in the
cumulative product is the key: it ensures no cancellation
can reduce the factorial growth. The mechanism is the
chiral-algebraic counterpart of the \emph{renormalon}: in
perturbative QFT, the factorial growth $n!$ of the $n$th
Feynman diagram comes from integrating over $n$ loop momenta
whose cumulative sums produce $\Gamma(n+1) = n!$ through the
Euler integral. Here the loop momenta are spectral parameters,
the Feynman propagators are Shapovalov propagators, and the
cumulative sums are the cumulative linear forms
$\sigma_v = \lambda_1 + \cdots + \lambda_j$. The factorial
is structural.
\end{remark}

\begin{remark}[Gravitational interpretation of the dichotomy]
\label{rem:convergence-dichotomy-physics}
The scalar sector is the pure-graviton S-matrix (multi-graviton
contact amplitudes proportional to $c/12$): its convergence for
$c > c^*$ means the perturbative expansion of graviton
scattering is summable in the semiclassical regime. The field
sector is the stress-tensor backreaction (universal,
$c$-independent): its Gevrey-$1$ divergence is the
gravitational analogue of the asymptotic growth of perturbative
QFT, necessitating Borel resummation. The absence of real
Stokes lines (the branch points $A_\pm$ are complex conjugate)
means the Borel sum is unambiguous: there is no resurgent
ambiguity in $3$d gravity, a consequence of the genus-$0$
spectral curve.
\end{remark}

\begin{remark}[Instanton actions are purely imaginary; \ClaimStatusConditional]%
\label{rem:instanton-imaginary}%
\index{instanton action!purely imaginary|textbf}%
\index{bound states!absence in 3d gravity}%
The Stokes directions $A_\pm = 1/t_\pm$ are purely imaginary
for all $c > 0$: since $t_\pm$ are complex conjugate with
$\Re(t_\pm) = 0$ (the discriminant $\Delta_t < 0$ ensures
$t_\pm = i\alpha$ for real~$\alpha$), the instanton actions
$A_\pm = \mp i/\alpha$ lie on the imaginary axis.
All non-perturbative corrections $\sim e^{-A_\pm/\hbar}$ are therefore
oscillatory, never exponentially decaying.
This is the WKB incarnation of a basic fact:
$3$d gravity has no local degrees of freedom, hence no bound
states. Real instanton actions would produce
$e^{-|A|/\hbar}$ tunneling amplitudes (bound-state poles in
the graviton self-energy); purely imaginary actions produce
oscillatory phases (scattering, no poles on the physical
sheet). The genus-$0$ spectral curve $\Sigma$ being rational
(Theorem~\ref{thm:graviton-resolvent-closed}(i)) is the
algebraic encoding of this dynamical triviality.
\end{remark}

%====================================================================
% MOVEMENT II: THE KOSZUL TRIANGLE
%====================================================================

\subsection{Movement II: the Koszul triangle}
\label{subsec:gravity-koszul}

Movement~I constructed the $\Ainf$ tower $\{m_k\}_{k \ge 2}$
from the quartic pole. The bar complex $\barB(\mathrm{Vir}_c)$
encoding this tower is a dg coalgebra from which three functors
extract boundary, lines, and bulk: the three vertices of the
Koszul triangle.

\begin{theorem}[Gravitational Koszul triangle; \ClaimStatusProvedHere]
\label{thm:gravity-koszul-triangle}
\index{Koszul triangle!gravitational|textbf}
\index{bulk-boundary-line triangle!3d gravity}
The three vertices of the bulk-boundary-line triangle are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Boundary} $= \mathrm{Vir}_c$:
 the $\lambda$-bracket~\eqref{eq:gravity-input} with
 $c = 6k = 3\ell/(2G)$.
\item \textbf{Lines}: the abstract open-colour line-side package
 of Theorem~\ref{thm:lines_as_modules}.
\item \textbf{Bulk} $\simeq \C[\![c]\!]$:
 the derived centre $\Zder(\mathrm{Vir}_c) \simeq
 \HH^0 \oplus \HH^2[-2] \simeq \C[\![c]\!]$.
 Pure 3d gravity has one parameter: the cosmological constant.
\end{enumerate}
\end{theorem}

\begin{proof}
The three vertices are assembled from results proved earlier in
this chapter and in the general theory.

\emph{Boundary face.}
The boundary chiral algebra is $\mathrm{Vir}_c$ with the
$\lambda$-bracket~\eqref{eq:gravity-input}. Movement~I
(\S\ref{subsec:gravity-ainf}) constructs the full $\Ainf$
structure from this input: the binary operation $m_2$ is the
$\lambda$-bracket itself, and the non-associativity forced by the
quartic pole generates the higher operations $\{m_k\}_{k \ge 3}$.
The Brown--Henneaux identification $c = 3\ell/(2G)$ is the
standard AdS$_3$/CFT$_2$ dictionary.

\emph{Bulk.}
The Hochschild--Serre spectral sequence computation at the start of
this subsection gives $\HH^0(\mathrm{Vir}_c) = \C$,
$\HH^1(\mathrm{Vir}_c) = 0$ (all derivations inner),
$\HH^2(\mathrm{Vir}_c) = \C \cdot \Theta_c$ (the Gel'fand--Fuchs
$2$-cocycle), and
$\HH^{n \ge 3}(\mathrm{Vir}_c) = 0$ for generic~$c$, so the derived
centre is $\Zder(\mathrm{Vir}_c) \simeq \C[\![c]\!]$. This identifies
the unique bulk observable with the central charge parameter.

\emph{Lines (abstract).}
Theorem~\ref{thm:lines_as_modules} provides the abstract line-side
package: the open-colour $E_1$-module category associated to the
bar complex $\barB(\mathrm{Vir}_c)$. This exists for any
logarithmic $\mathrm{SC}^{\mathrm{ch,top}}$-algebra and requires
no additional input beyond homotopy-Koszulity of the operad
(Theorem~\ref{thm:homotopy-Koszul}).

The three faces close into the triangle
bulk $\xrightarrow{\beta_B}$ boundary $\xrightarrow{\barB}$
lines $\xrightarrow{\Zder}$ bulk, with the bulk-to-boundary map
given by the conformal Ward identity~\eqref{eq:gravity-bulk-boundary}.
\end{proof}

\begin{remark}[Steinberg structure]
\label{rem:gravity-steinberg}
The bar complex $\barB(\mathrm{Vir}_c)$ is the universal
coalgebra from which the triangle's three vertices are
extracted by three distinct functors:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\Omega(\barB) \simeq \mathrm{Vir}_c$ on the chirally
 Koszul locus (the cobar functor $\Omega$ recovers the
 original algebra by bar-cobar inversion;
 Vol~I Theorem~B);
\item $\Omega(D_{\Ran}(\barB)) \simeq \mathrm{Vir}_{26-c}$ on
 that same locus (the Ran-space Verdier dual $D_{\Ran}$
 identifies the bar of the Koszul dual by Vol~I
 Theorem~A, and that bar complex is then inverted by
 Vol~I Theorem~B);
\item $\RHom(\Omega(\barB), \mathrm{Vir}_c)
 \simeq \C[\![c]\!]$ (chiral Hochschild cochains compute
 the derived centre = bulk;
 Theorem~\ref{thm:gravity-koszul-triangle}).
\end{enumerate}
This parallels the classical Steinberg picture: the variety
$\widetilde{\cN} \times_\fg \widetilde{\cN}$ is one geometric
object whose Borel--Moore homology, $K$-theory, and derived
category extract the Hecke algebra, the Springer correspondence,
and the Kazhdan--Lusztig basis. Here the bar complex is one
coalgebra; three functors extract boundary, lines, and bulk.
\end{remark}

\begin{remark}[Conjectural Virasoro realization of lines; \ClaimStatusConjectured]
\label{rem:gravity-line-virasoro-realization}
The \emph{concrete} identification of the abstract line-side package
with highest-weight $\mathrm{Vir}_{26-c}$-modules is not proved here;
it is the content of the conjectural Virasoro realization
(Conjecture~\ref{conj:gravity-line-identification} below).
Under this identification, highest-weight
$\mathrm{Vir}_{26-c}$-modules $M_h$ are conical defects of angular deficit
$2\pi(1-\sqrt{1-8Gh})$
(Ba\~nados--Teitelboim--Zanelli), reducing to
$2\pi(1-h/c)$ for $h/c \ll 1$.
\end{remark}

\subsubsection*{The Koszul dual: $\mathrm{Vir}_c^! = \mathrm{Vir}_{26-c}$}

\begin{proposition}[\ClaimStatusProvedElsewhere]
\label{prop:gravity-koszul-dual}
\index{Koszul dual!Virasoro!gravitational}
The Koszul dual of $\mathrm{Vir}_c$ is $\mathrm{Vir}_{26-c}$,
as proved by the Virasoro Koszul-duality theorem of Volume~I.
The Koszul complementarity gives
\[
\kappa(\mathrm{Vir}_c) + \kappa(\mathrm{Vir}_{26-c})
\;=\;
\frac{c}{2} + \frac{26-c}{2}
\;=\; 13.
\]
Self-duality at $c = 13$: $\mathrm{Vir}_{13}^! = \mathrm{Vir}_{13}$.
\end{proposition}

\begin{conjecture}[Virasoro realization of line operators; \ClaimStatusConjectured]
\label{conj:gravity-line-identification}
\index{line operators!Virasoro realization (conjectural)}
The abstract line-side package of
Theorem~\textup{\ref{thm:lines_as_modules}}, specialized to the
Virasoro boundary algebra $\mathrm{Vir}_c$, is equivalent to the
category of highest-weight $\mathrm{Vir}_{26-c}$-modules: line
operators along $\R_+ \times \{0\}$ are
$\mathrm{Vir}_{26-c}$-modules.
\end{conjecture}

\begin{remark}
Under Conjecture~\ref{conj:gravity-line-identification},
for $c \gg 26$ the dual central charge $c' = 26 - c \ll 0$ places
the line category in the strongly quantum regime: the algebraic
form of UV/IR mixing in AdS$_3$/CFT$_2$.
\end{remark}

\begin{remark}[Curvature versus effective curvature]
\label{rem:gravity-kappa-vs-kappa-eff}
The modular characteristic $\kappa(\mathrm{Vir}_c) = c/2$ is the
intrinsic genus-$1$ curvature of the Virasoro bar complex. In the
gravitational context, gauge-fixing introduces the $bc$ ghost system
with $c_{\mathrm{ghost}} = -26$ and curvature
$\kappa_{\mathrm{ghost}} = -13$. The \emph{effective} curvature is
\[
\kappa_{\mathrm{eff}}
\;=\;
\kappa(\mathrm{Vir}_c) + \kappa_{\mathrm{ghost}}
\;=\;
\frac{c}{2} - 13
\;=\;
\frac{c - 26}{2}.
\]
The gravitational partition function
(\S\ref{subsec:gravity-genus-tower}) uses $\kappa_{\mathrm{eff}}$;
the cancellation $\kappa_{\mathrm{eff}} = 0$ at $c = 26$ is
matter-ghost cancellation, not vanishing of the intrinsic curvature.
\end{remark}

\subsubsection*{The derived centre: $\Zder(\mathrm{Vir}_c) \simeq \C[\![c]\!]$}

The Hochschild--Serre spectral sequence gives:
\[
\HH^0(\mathrm{Vir}_c) = \C,
\qquad
\HH^1(\mathrm{Vir}_c) = 0,
\qquad
\HH^2(\mathrm{Vir}_c) = \C \cdot \Theta_c,
\qquad
\HH^{n \ge 3}(\mathrm{Vir}_c) = 0
\quad\text{(generic~$c$)},
\]
where $\Theta_c$ is the Gel'fand--Fuchs $2$-cocycle recording
$\partial_c\{T_\lambda T\}$. The Hilbert series is
$P(t)=1+t^2$.
Hence $\Zder(\mathrm{Vir}_c)
\simeq \C[\![c]\!]$: the only bulk observable is the central
charge. 3d gravity has no local degrees of freedom.

The bulk-to-boundary map sends $\Theta_c \in \HH^2$ to the
stress tensor $T \in \mathrm{Vir}_c$ via the conformal Ward identity:
\begin{equation}\label{eq:gravity-bulk-boundary}
\beta_B(\partial_c)(z_0) \cdot T(w)
\;=\;
\frac{T(w)}{(z_0 - w)^2} + \frac{\partial T(w)}{z_0 - w}.
\end{equation}
The triangle closes: bulk $\xrightarrow{\beta_B}$ boundary
$\xrightarrow{\barB}$ lines $\xrightarrow{\Zder}$ bulk.

%====================================================================
% MOVEMENT III: THE R-MATRIX AND BRAIDING
%====================================================================

\subsection{Movement III: the $R$-matrix}
\label{subsec:gravity-r-matrix}

The Koszul triangle of Movement~II organises the algebraic output
into boundary, lines, and bulk. The $R$-matrix connects these
three vertices: it is the braiding datum that governs how line
operators wind around each other, and its Yang--Baxter equation is
the integrability condition that makes the triangle consistent.

\subsubsection*{The classical $r$-matrix from the Laplace transform}

The classical $r$-matrix is the Laplace transform of the
$\lambda$-bracket~\eqref{eq:gravity-input}:
\begin{align*}
r(z)
&\;=\;
\int_0^\infty e^{-\lambda z}\,
 \{T{}_\lambda T\}\, d\lambda
\;=\;
\int_0^\infty e^{-\lambda z}\!\left(
 \partial T + 2T\lambda + \frac{c}{12}\lambda^3
\right) d\lambda
\\[4pt]
&\;=\;
\frac{\partial T}{z} + \frac{2T}{z^2} + \frac{c/2}{z^4}.
\end{align*}
This is the Laplace kernel $r^L(z)$ (the OPE generating function):
the Laplace transform recovers
the defining data~\eqref{eq:gravity-input} in position space.
The bar-theoretic collision residue has pole orders one lower
($d\log$ absorbs a power of~$z$):
$r^{\mathrm{coll}}(z) = (c/2)/z^3 + 2T/z$.
At leading order $r^L(z) \sim (c/2)/z^4$: the graviton propagator
in AdS$_3$, a spin-$2$ exchange with a fourth-order singularity.

\begin{proposition}[Gravitational YBE; \ClaimStatusProvedElsewhere]
\label{prop:gravity-ybe}
The CYBE
\[
[r_{12}(z_{12}),\, r_{13}(z_{13})]
+ [r_{12}(z_{12}),\, r_{23}(z_{23})]
+ [r_{13}(z_{13}),\, r_{23}(z_{23})]
\;=\; 0
\]
is the residue of the Arnold relation on $\FM_3(\C)$
from the collision-residue compatibility theorem of Volume~I:
the same cancellation that gives $d_{\barB}^2 = 0$, projected to
the binary collision stratum.
\end{proposition}

\subsubsection*{The fusion kernel: quantum $R$-matrix}

\begin{definition}[Gravitational $R$-matrix]
\label{def:gravity-r-matrix}
\index{R-matrix@$R$-matrix!gravitational}
\index{Virasoro fusion kernel}
For highest-weight $\mathrm{Vir}_{26-c}$-modules $V_{h_1}, V_{h_2}$,
the \emph{Virasoro fusion kernel}
$R_{h_1, h_2}(z) \colon V_{h_1} \otimes V_{h_2}
\xrightarrow{\;\sim\;} V_{h_2} \otimes V_{h_1}$
is the Virasoro $6j$-symbol at spectral separation~$z$.
\end{definition}

The fusion kernel satisfies the Yang--Baxter equation
$R_{12}R_{13}R_{23} = R_{23}R_{13}R_{12}$ as a consequence of
the pentagon identity for Virasoro fusion matrices, the boundary
cancellation on $\FM_3(\C)$ (Theorem~\ref{thm:YBE}).

\subsubsection*{Specific channels}

\emph{Vacuum ($h_1 = 0$).}\enspace
$R_{0,h}(z) = \mathrm{id}_{V_h}$: empty AdS$_3$ does not scatter
gravitons.

\emph{Degenerate ($h = h_{2,1}$).}\enspace
The null vector $\chi_{2,1} = (L_{-2} -
\frac{3}{2(2h_{2,1}+1)}\,L_{-1}^2)|h_{2,1}\rangle = 0$ produces
the BPZ equation:
\begin{equation}\label{eq:bpz-fusion}
\left[
 \frac{b^2}{2}\,\partial_z^2
 \;+\; \sum_{i} \left(
 \frac{h_i}{(z-z_i)^2} + \frac{\partial_{z_i}}{z-z_i}
 \right)
\right]
\mathcal{F}(z, z_i) \;=\; 0,
\qquad c = 1 + 6(b + b^{-1})^2.
\end{equation}
The two fusion channels $V_{h_\pm}$ with
$h_\pm = \alpha_\pm(Q - \alpha_\pm)$,
$\alpha_\pm = \alpha_2 \pm b^{-1}/2$
give the braiding eigenvalues:
\begin{equation}\label{eq:degenerate-eigenvalues}
\sigma_\pm
\;=\;
e^{i\pi(h_\pm - h_{2,1} - h_2)}
\;=\;
e^{\pm i\pi b^{-1}\alpha_2}.
\end{equation}

\emph{General channel (Ponsot--Teschner).}\enspace
For generic weights, the fusion kernel has the integral
representation~\cite{PT01}:
\begin{equation}\label{eq:ponsot-teschner}
\mathbb{F}_{\alpha_s}^{\alpha_t}
\!\left[\begin{smallmatrix}
 \alpha_2 & \alpha_3 \\
 \alpha_1 & \alpha_4
\end{smallmatrix}\right]
\;=\;
\int_{Q/2 + i\R}
\prod_{j=1}^{4}
\frac{S_b(\alpha_t - a_j)}{S_b(\alpha_s - a_j)}
\;\cdot\;
\frac{d\alpha_t}{2\pi i},
\end{equation}
where $S_b$ is the double sine function. The pentagon identity
is the algebraic content of OPE associativity; the unitarity
$\sum_{\alpha_t} |\mathbb{F}|^2 = \delta$ is the unitarity of
the gravitational $S$-matrix.

\emph{Heavy-heavy limit.}\enspace
For $h_i = c\epsilon_i/6 \to \infty$ with $\epsilon_i$ fixed:
$R_{h_1,h_2}(z) \sim
\exp\!\bigl(\frac{c}{6}\,W(\epsilon_1, \epsilon_2; z)\bigr)$,
where $W$ is the regularised geodesic length in AdS$_3$, the
WKB/geodesic limit of the graviton scattering amplitude.

\emph{Virasoro Ward connection and the BPZ comparison surface.}\enspace
The $n$-point shadow connection
\begin{equation}\label{eq:bpz-shadow-connection}
\nabla^{\mathrm{hol}}_{0,n}
\;=\;
d
\;-\;
\sum_{i}\,\sum_{j \neq i}
\left(
\frac{h_j}{(z_i - z_j)^2}
+ \frac{\partial_{z_j}}{z_i - z_j}
\right) dz_i
\end{equation}
is the degree-$(n,0)$ genus-$0$ projection of the MC element
$\alpha_T$. On the Virasoro comparison surface, this is the
genus-$0$ conformal Ward connection. On the degenerate-representation
comparison surface, its higher collision residues yield the BPZ
differential equations. The monodromy representation on
the resulting conformal-block package supplies the comparison-surface
braiding data for line operators.

\subsubsection*{Tensor decomposition and fusion rules}

\emph{Irrational $c$.}\enspace
$V_{h_1} \otimes V_{h_2} \simeq \int_{\R_+} V_h\,d\mu(h)$
with the DOZZ Plancherel measure
\begin{multline}\label{eq:dozz}
C(\alpha_1, \alpha_2, \alpha_3)
\;=\;
\frac{[\pi\mu\,\gamma(b^2)\,b^{2-2b^2}]^{(Q-\alpha_{123})/b}}
 {\Upsilon_b'(0)}
\;\cdot\;
\frac{\Upsilon_b(2\alpha_1)\,\Upsilon_b(2\alpha_2)\,
 \Upsilon_b(2\alpha_3)}
 {\Upsilon_b(\alpha_{123} - Q)}\\
\times
\frac{1}{\Upsilon_b(\alpha_1{+}\alpha_2{-}\alpha_3)\,
 \Upsilon_b(\alpha_2{+}\alpha_3{-}\alpha_1)\,
 \Upsilon_b(\alpha_1{+}\alpha_3{-}\alpha_2)}.
\end{multline}
The $R$-matrix is diagonal in the fusion-channel basis with
eigenvalues
\begin{equation}\label{eq:r-matrix-diagonal}
e^{2\pi i(h - h_1 - h_2)},
\end{equation}
the Aharonov--Bohm phase of one conical defect orbiting another.

\emph{Rational $c$ (minimal models).}\enspace
For $c = 1 - 6(p-q)^2/(pq)$: the tensor product is a finite direct
sum. At $c = 1/2$ (Ising, $k = 1/12$): three primaries
$\mathbf{1}, \sigma, \varepsilon$ with $\sigma \otimes \sigma
= \mathbf{1} \oplus \varepsilon$ and $R$-matrix eigenvalues that
are $16$th roots of unity; the gravitational Hilbert space truncates
to three states.

%====================================================================
% MOVEMENT III.5: DS-HPL TRANSFER AND GRAVITATIONAL PRIMITIVITY
%====================================================================

\subsection{The Drinfeld--Sokolov transfer theorem}
\label{subsec:ds-hpl-transfer}
\index{Drinfeld--Sokolov reduction!HPL transfer|textbf}
\index{homological perturbation!DS transfer}
\index{coproduct!gravitational primitivity|textbf}
\index{ghost number!coproduct obstruction|textbf}

The Virasoro algebra arises from $\widehat{\mathfrak{sl}}_2$ by
principal Drinfeld--Sokolov reduction: the BRST cohomology of
the first-class constraint $J^+(z) = 1$. The affine dg-shifted
Yangian $Y^{\mathrm{dg}}(\widehat{\mathfrak{sl}}_2)$ carries three
structures: $\Ainf$ products $\{m_n\}$, coproduct $\Delta_z$,
and classical $r$-matrix $r^{\mathrm{aff}}(z) = k\,\Omega/z$.
Homological perturbation transfers all three to the Virasoro
sector. The transferred products are genuinely infinite (the
quartic pole forces $m_3$, then $m_4$, and so on: Movement~I).
The transferred coproduct, by contrast, is trivial: it equals the
primitive coproduct $x \mapsto \tau_z(x) \otimes 1 + 1 \otimes x$
at every degree, with no corrections whatsoever. Gravitons
do not split.

Movement~III.5 operates on the ordered bar complex $B^{\mathrm{ord}}(\mathrm{Vir}_c)$,
the open-colour sector of the two-colour Koszul duality architecture
developed in Part~\ref{part:bbl-core} (Section~\ref{ch:ordered-associative-chiral-kd},
Remark~\ref{rem:two-colour-architecture}). The HPL transfer through
the DS strong deformation retract preserves the ordering on
configurations, so the transferred dg-shifted Yangian inherits
the ordered (E$_1$) factorization structure of the source.

The mechanism is a ghost-number obstruction that kills every
tree in the HPL expansion of the transferred coproduct. The
source of this obstruction is the $\mathfrak{sl}_2$-triple
$(e, h_0, f)$ that defines the reduction. The homotopy $h$
of the strong deformation retract contracts acyclic directions
of the BRST complex, and each contraction lowers ghost number
by one. Every HPL tree for the degree-$n$ coproduct ($n \ge 2$)
contains at least one uncompensated $h$-insertion, depositing
the intermediate state in a ghost-number sector invisible to
the projection $p$. The obstruction is not perturbative:
it holds at every order of the BRST perturbation
$\delta = d_{\mathrm{BRST}} - d_0$.

\subsubsection*{The BRST complex and its ghost-number grading}

Fix the principal $\mathfrak{sl}_2$-triple $(e, h_0, f)$ in
$\mathfrak{sl}_2$ with $e = E_{12}$, $f = E_{21}$,
$h_0 = E_{11} - E_{22}$. The DS reduction at level~$k$
constrains the nilradical $\mathfrak{n}_+
= \langle e \rangle$ to the value~$1$, producing the
BRST complex
\begin{equation}\label{eq:ds-brst-complex}
C^{\mathrm{DS}}
\;=\;
V_k(\mathfrak{sl}_2)
\;\otimes\;
\mathcal{F}_{\mathrm{gh}}(\mathfrak{n}_+),
\end{equation}
where $V_k(\mathfrak{sl}_2)$ is the universal affine vertex
algebra at level~$k$ and
$\mathcal{F}_{\mathrm{gh}}(\mathfrak{n}_+)$ is the $bc$
ghost system for the one-dimensional nilradical. Since
$\dim\mathfrak{n}_+ = 1$, there is a single ghost pair
$(b, c)$ of conformal weights $(1, 0)$. The ghost-number
grading decomposes the complex as
\[
C^{\mathrm{DS}}
\;=\;
\bigoplus_{n \in \mathbf{Z}}\,C^{\mathrm{DS}}_n,
\qquad
\mathrm{gh}(b) = -1,
\quad
\mathrm{gh}(c) = +1,
\quad
\mathrm{gh}(J^a) = 0.
\]
The BRST differential $d_{\mathrm{BRST}}$ has ghost-number
degree $+1$; its cohomology
$H^0(C^{\mathrm{DS}}, d_{\mathrm{BRST}})$ is the
$\mathcal{W}$-algebra $\mathcal{W}_k(\mathfrak{sl}_2)
= \mathrm{Vir}_c$ with $c = 1 - 6(k+1)^2/(k+2)$.

Write the DS-adapted generators as
$V = J^+ - 1$, $U = J^0$, $W = (k+2)T$ (the Sugawara field),
$b$ (antighost), $c$ (ghost), with $T$ the stress tensor.
The linear part of the BRST differential acts as $d_0(b) = V$,
$d_0(U) = 2c$, and $d_0 = 0$ on $W$, $V$, $c$. The generators
pair into two acyclic summands and one cohomological summand:
\[
\underbrace{(V, b)}_{\text{acyclic, gh }0 \leftrightarrow -1}
\;\oplus\;
\underbrace{(U, c)}_{\text{acyclic, gh }0 \leftrightarrow +1}
\;\oplus\;
\underbrace{W}_{\text{cohomology, gh }0}.
\]
The acyclic pairs are contractible; the cohomology is spanned
by $W$ and its derivatives.

\subsubsection*{The strong deformation retract}

The SDR $(i, p, h)$ retracts $C^{\mathrm{DS}}$ onto the
Virasoro sector:
\begin{align}\label{eq:ds-sdr-formulas}
i(\partial^n T) &= \frac{1}{k+2}\,\partial^n W, \notag\\
p(\partial^n W) &= (k+2)\,\partial^n T,
\quad p = 0 \text{ on } U, V, b, c, \\
h(\partial^n V) &= \partial^n b,
\quad h(\partial^n c) = \tfrac{1}{2}\,\partial^n U,
\quad h = 0 \text{ on } W, b. \notag
\end{align}
The homotopy $h$ has a definite ghost-number degree:
\begin{equation}\label{eq:homotopy-ghost-degree}
\boxed{\;\mathrm{gh}(h) \;=\; -1.\;}
\end{equation}
This is the single fact that controls the entire coproduct
computation. Every acyclic pair in the
Chevalley--Eilenberg complex of $\mathfrak{n}_+$ consists of an
element and its $d_0$-partner, separated by exactly one unit of
ghost number, and $h$ maps each element to its partner in
the direction of \emph{lower} ghost number. On the pair
$(V, b)$: $V$ has $\mathrm{gh} = 0$ and $b$ has
$\mathrm{gh} = -1$, so $h\colon V \mapsto b$ lowers ghost
number by~$1$. On the pair $(U, c)$: $c$ has
$\mathrm{gh} = +1$ and $U$ has $\mathrm{gh} = 0$, so
$h\colon c \mapsto U/2$ lowers ghost number by~$1$. On $W$ and
$b$, $h$ vanishes.

This is the algebraic content of the
$\mathfrak{sl}_2$-triple: the grading $\mathrm{gh}$ is the
eigenvalue of $\operatorname{ad}(h_0)$ restricted to
$\mathfrak{n}_+$ and its dual, and $h$ is the contraction
operator on the Koszul resolution of the constraint
$J^+ = 1$. The ghost-number degree of $h$ is~$-1$ for
every principal DS reduction, because every positive root
contributes one ghost pair with ghost numbers $\pm 1$
regardless of the Dynkin grade of the root
(\S\ref{par:wn-ghost-obstruction} below).

\begin{proposition}[SDR for the DS complex;
\ClaimStatusProvedHere]\label{prop:ds-sdr}
\index{strong deformation retract!DS complex}
The triple $(i, p, h)$ of~\eqref{eq:ds-sdr-formulas} satisfies
the SDR conditions:
$pi = \operatorname{id}$, $h^2 = 0$, $ph = 0$, $hi = 0$,
and $\operatorname{id} - ip = d_0 h + h d_0$.
\end{proposition}

\begin{proof}
Direct verification on each generator.
$pi$: $p(i(\partial^n T)) = p(\frac{1}{k+2}\partial^n W)
= (k+2)\frac{1}{k+2}\partial^n T = \partial^n T$.
$h^2$: $h$ maps $V \mapsto b$ and $c \mapsto U/2$;
then $h(b) = 0$ and $h(U) = 0$, so $h^2 = 0$.
$ph$: $h$ maps into $\{b, U\}$; $p$ kills both.
$hi$: $i$ maps into $\{W\}$; $h(W) = 0$.
Homotopy: on $W$, $ip(W) = W$, so
$(\operatorname{id} - ip)(W) = 0 = (d_0 h + h d_0)(W)$.
On $V$: $(\operatorname{id} - ip)(V) = V$;
$(d_0 h + h d_0)(V) = d_0(b) + h(0) = V$.
On $b$: $(\operatorname{id} - ip)(b) = b$;
$(d_0 h + h d_0)(b) = d_0(0) + h(V) = b$.
On $U$: $h d_0(U) = h(2c) = U$ and
$d_0 h(U) = 0$, so $(d_0 h + h d_0)(U) = U$.
On $c$: $(d_0 h + h d_0)(c) = d_0(U/2) + h(0) = c$.
\end{proof}

\subsubsection*{The transfer theorem}

The full BRST differential decomposes as $d_{\mathrm{BRST}}
= d_0 + \delta$, where $\delta$ contains the nonlinear terms
(ghost interactions, normal-ordering corrections from the
Sugawara construction). The perturbation $\delta$ has
ghost-number degree $+1$: it is the part of
$d_{\mathrm{BRST}}$ that creates ghosts. The composite
$h\delta$ has ghost-number degree $-1 + 1 = 0$, ensuring
convergence of the HPL series on each finite-dimensional
weight space.

\begin{theorem}[DS-HPL transfer;
\ClaimStatusProvedHere]\label{thm:ds-hpl-transfer}
\index{DS-HPL transfer theorem|textbf}
Let $Y^{\mathrm{dg}}(\widehat{\mathfrak{sl}}_2)$ denote the
dg-shifted Yangian of $\widehat{\mathfrak{sl}}_2$ at level~$k$,
with $\Ainf$ products $\{m_n^{\mathrm{aff}}\}$,
coproduct $\Delta_z^{\mathrm{aff}}$, and classical $r$-matrix
$r^{\mathrm{aff}}(z) = k\,\Omega/z$.
The HPL transfer through the SDR of
Proposition~\textup{\ref{prop:ds-sdr}} produces:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Transferred $\Ainf$ products
 $\{m_n^{\mathrm{Vir}}\}_{n \ge 2}$ on the Virasoro sector,
 given by the standard tree formula
 $m_n^{\mathrm{Vir}} = p\, m_n^{\mathrm{aff}}(i^{\otimes n})
 + \text{\textup{(}}$higher-order HPL corrections$\text{\textup{)}}$.
\item A transferred coproduct
 $\Delta_z^{\mathrm{Vir}}\colon H_{\mathrm{Vir}}
 \to H_{\mathrm{Vir}} \otimes H_{\mathrm{Vir}}$
 that is an $\Ainf$-algebra morphism with respect to the
 transferred products. This is the morphism transfer of
 $\Delta_z^{\mathrm{aff}}$ through the SDR and its tensor
 product.
\item A transferred $r$-matrix
 $r^{\mathrm{Vir}}(z) = (c/2)/z^3 + 2T/z$, with pole orders
 determined by the Sugawara nonlinearity.
\end{enumerate}
The transferred data
$(H_{\mathrm{Vir}},\, \{m_n^{\mathrm{Vir}}\},\,
\Delta_z^{\mathrm{Vir}},\, r^{\mathrm{Vir}}(z))$
is a dg-shifted Yangian on the Virasoro algebra.
The transferred coproduct satisfies the $\Ainf$ Yang--Baxter
equation automatically, by the general properties of HPL
transfer for morphisms.
\end{theorem}

\begin{proof}
The HPL transfer theorem for $\Ainf$ algebras
(Volume~I, Construction~\ref*{V1-constr:htt-alg})
produces the transferred products $m_n^{\mathrm{Vir}}$ via
the tree formula: the sum over planar trees with $n$ leaves,
edges decorated by the homotopy~$h$, internal vertices by
$\delta$ (the BRST perturbation), and the root by~$p$.

The coproduct transfer uses the morphism variant of HPL
(Loday--Vallette, Theorem~10.3.10):
$\Delta_z^{\mathrm{aff}}$ is an $\Ainf$-algebra morphism
from $(A, m_n^{\mathrm{aff}})$ to
$(A \otimes A, m_n^{r(z)\text{-twisted}})$.
The transfer through the source SDR $(i,p,h)$ and the target
SDR $(i \otimes i, p \otimes p, H_{12})$, where
$H_{12} = h \otimes \operatorname{id}
+ \operatorname{id} \otimes h$
(the tensor product homotopy), produces a transferred morphism
$\Delta_z^{\mathrm{Vir}}$ that is automatically an
$\Ainf$-algebra morphism between the transferred structures.

Convergence: the weight grading on the BRST complex
(conformal weight) is preserved by~$h$ and bounded below.
On each finite weight space, the HPL series is a finite sum
(finitely many trees contribute because each $h$-insertion
preserves the weight filtration and the weight spaces are
finite-dimensional).

The $\Ainf$ YBE for $r^{\mathrm{Vir}}(z)$ follows from the
coassociativity of $\Delta_z^{\mathrm{Vir}}$, which in turn
follows from the transfer of the coassociativity of
$\Delta_z^{\mathrm{aff}}$.

The pole structure of $r^{\mathrm{Vir}}(z)$: the leading
HPL correction replaces $k\,\Omega/z$ (the affine Casimir)
with contributions from the Sugawara normal ordering
$T = \frac{1}{k+2}(\frac{1}{2}:J^0 J^0: + :J^+ J^-:)$.
The nonlinearity produces higher poles: $z^{-3}$ from the
quartic OPE pole (shifted by one via $d\log$) and $z^{-1}$
from the double pole. The result is
$r^{\mathrm{Vir}}(z) = (c/2)/z^3 + 2T/z$, matching
the collision residue of $\Theta_{\mathrm{Vir}_c}$
(Proposition~\ref{prop:gravity-ybe}).
\end{proof}

\begin{remark}[Honest gaps]\label{rem:ds-hpl-honest-gaps}
Two verifications remain beyond the proved core:
\textup{(a)}~full sign verification of the transferred
products at degree~$\ge 3$;
\textup{(b)}~verification that the transferred structure
satisfies the specific axioms of a dg-shifted Yangian
(translation compatibility, rationality of the transferred
$r$-matrix) as opposed to a general $\Ainf$ homotopy-coherent
structure. The weight-filtration convergence and the
morphism-transfer compatibility are unconditional.
The coproduct vanishing, originally listed as a separate gap,
is resolved at all degrees by
Theorem~\ref{thm:gravitational-primitivity}.
\end{remark}

\subsection{The gravitational coproduct is primitive}
\label{subsec:gravitational-primitivity}
\index{coproduct!strict primitivity|textbf}
\index{gauge theory vs.\ gravity|textbf}
\index{Drinfeld--Sokolov reduction!coproduct primitivity|textbf}
\index{ghost number!coproduct obstruction|textbf}

A dg-shifted Yangian carries two independent channels of
higher-order structure. The first is the $\Ainf$ product tower
$\{m_n\}_{n \ge 2}$: self-interaction of the field, encoded
in the bar differential. The second is the coproduct tower
$\{\Delta_{z,n}\}_{n \ge 1}$: the amplitude for a single
quantum to split into $n$ quanta at spectral separation~$z$,
encoded in the bar coalgebra structure. These two channels
are coupled by the $r$-matrix $r(z)$, which twists the target
product on $H \otimes H$ so that $\Delta_z$ is an
$\Ainf$-morphism from $(H, \{m_n\})$ to
$(H \otimes H, \{m_n^{r(z)}\})$. The $\Ainf$ Yang--Baxter
equation is the compatibility condition between the two channels.

In gauge theory, both channels are active.
In gravity, the second channel is identically zero:
\begin{equation}\label{eq:gravitational-primitivity-summary}
\Delta_z^W(x) \;=\; \tau_z(x) \otimes 1 \;+\; 1 \otimes x
\end{equation}
for every element $x$ of the $\mathcal{W}$-algebra, at every
degree, with no corrections whatsoever. This is the central
algebraic fact about three-dimensional quantum gravity.
All nonlinearity resides in the $\Ainf$ products
$\{m_n^W\}_{n \ge 3}$ and in the collision residue
$r^{\mathrm{Vir}}(z) = (c/2)/z^3 + 2T/z$. The coproduct
carries no information.

The mechanism is a ghost-number obstruction intrinsic to
Drinfeld--Sokolov reduction. Homological perturbation
expresses every transferred structure as a sum over decorated
trees. For the transferred products, these trees produce
genuinely nontrivial corrections: the quartic OPE pole forces
$m_3 \ne 0$, which forces $m_4 \ne 0$, and so on through the
entire infinite tower (Movement~I). For the transferred
coproduct, every tree in the HPL expansion produces an output
whose ghost number is nonzero. The output sits in ghost
number~$+1$ (source-side trees) or ghost number~$-1$
(target-side trees), and the projection $p \otimes p$ onto the
$\mathcal{W}$-algebra cohomology kills both. The obstruction
is not perturbative: it holds at every order of the BRST
perturbation, at every degree, for every principal
Drinfeld--Sokolov reduction in every simple Lie algebra.

\subsubsection*{Two channels of nonlinearity}
\label{par:ghost-number-mechanism}

The product tower $\{m_n\}_{n \ge 3}$ and the coproduct tower
$\{\Delta_{z,n}\}_{n \ge 1}$ play asymmetric roles. The
$\Ainf$ products encode self-interaction: the
non-associativity of $m_2$ forces $m_3$ by the Stasheff
identity $\partial m_3 + m_2 \circ m_2 = 0$, which forces
$m_4$, and so on. Each $m_n$ is a vertex of the field theory:
$n$ quanta collide and produce one quantum. The coproduct
encodes the reverse process: one quantum splits into~$n$.
The $r$-matrix connects the two. It twists the target product
on $H \otimes H$ so that $\Delta_z$ is a morphism of $\Ainf$
algebras, and the $\Ainf$ Yang--Baxter equation
$\sum_{i+j=n} m_i^{r(z)} \circ (\Delta_{z,j_1} \otimes
\cdots \otimes \Delta_{z,j_i}) = \Delta_{z,n} \circ m_n$
expresses the compatibility between production and
self-interaction.

In gauge theory (Chern--Simons with boundary algebra
$\widehat{\mathfrak{g}}_k$), both channels are active. The
gluon $J^a$ has a primitive coproduct at the linear level:
$\Delta_z(J^a) = J^a(w+z) \otimes 1 + 1 \otimes J^a(w)$.
But the Sugawara composite $T_{\mathrm{aff}}
= \frac{1}{2(k+h^\vee)}\sum_a {:}J^a J^a{:}$
has a nontrivial coproduct because of the cross term:
\begin{equation}\label{eq:sugawara-cross-term}
\Delta_z(T_{\mathrm{aff}})
\;=\;
\tau_z(T_{\mathrm{aff}}) \otimes 1
\;+\; 1 \otimes T_{\mathrm{aff}}
\;+\;
\frac{1}{k+h^\vee}\,\Omega(w{+}z,\, w),
\end{equation}
where $\Omega(w{+}z, w)
= \sum_a J^a(w{+}z) \otimes J^a(w)$ is the split Casimir.
The cross term $\frac{1}{k+h^\vee}\,\Omega$ is the production
vertex: a gluon bound state can dissociate into its
constituents. This term is verified to be nonzero by explicit
computation. For $\mathfrak{g} = \mathfrak{sl}_2$ at level~$k$,
\begin{equation}\label{eq:affine-cross-term-explicit}
\frac{1}{k+2}\,\Omega
\;=\;
\frac{1}{k+2}\Bigl(
J^0(w{+}z) \otimes J^0(w)
+ J^+(w{+}z) \otimes J^-(w)
+ J^-(w{+}z) \otimes J^+(w)
\Bigr)
\;\ne\; 0.
\end{equation}
The coefficient $1/(k+2)$ is the inverse Sugawara normalization.
After DS reduction, $p$ annihilates every factor $J^a$ because
the Virasoro sector contains no weight-$1$ states. The
cross term dies, but the production vertex was present
\emph{before} projection. The ghost sector is the algebraic
price of killing it.

\subsubsection*{The ghost-number bottleneck}

We isolate the mechanism in the simplest case: the Virasoro
algebra $\mathrm{Vir}_c = W_k(\mathfrak{sl}_2)$. The BRST
complex, strong deformation retract, and ghost-number grading
are as in \S\ref{subsec:ds-hpl-transfer}. Two facts control
the entire computation:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The homotopy $h$ has ghost-number degree $-1$
(equation~\eqref{eq:homotopy-ghost-degree}).
\item The projection $p$ kills all elements of ghost
number $\ne 0$.
\end{enumerate}
Fact~(i) holds because $h$ contracts acyclic pairs in the
direction of lower ghost number: $h \colon V \mapsto b$ sends
ghost~$0$ to ghost~$-1$, and $h \colon c \mapsto U/2$ sends
ghost~$+1$ to ghost~$0$. Fact~(ii) holds because the
$\mathcal{W}$-algebra cohomology sits entirely in ghost
number~$0$. Together, these two facts kill every HPL tree
that contributes to the transferred coproduct at degree
$n \ge 2$, by a mechanism that depends on the tree type.

\begin{proposition}[Coproduct primitivity at degree~$2$;
\ClaimStatusProvedHere]\label{prop:coproduct-degree2-vanishing}
\index{transferred coproduct!degree-$2$ vanishing}
The first nonlinear coproduct correction vanishes:
\begin{equation}\label{eq:coproduct-degree2-vanishing}
\Delta_{z,2}^{\mathrm{Vir}}(T,T) \;=\; 0.
\end{equation}
The transferred coproduct on the Virasoro sector is strictly
primitive at degree~$2$:
\begin{equation}\label{eq:coproduct-primitive-degree1}
\Delta_{z,1}^{\mathrm{Vir}}(T)
\;=\; \tau_z(T) \otimes 1 \;+\; 1 \otimes T.
\end{equation}
\end{proposition}

\begin{proof}
Three steps: the linear coproduct, the ghost-number obstruction,
and perturbation stability.

\emph{Step~1: linear transferred coproduct.}
The Sugawara field $T = \frac{1}{k+2}\bigl(\frac{1}{2}
{:}J^0 J^0{:} + {:}J^+ J^-{:}\bigr)$ is quadratic in the
affine generators. The affine coproduct is
$\Delta_z(J^a) = J^a(w+z) \otimes 1 + 1 \otimes J^a(w)$.
Expanding the Sugawara quadratic gives
\begin{equation}\label{eq:delta-z-sugawara}
\Delta_z(T)
\;=\;
\tau_z(T) \otimes 1 \;+\; 1 \otimes T
\;+\; \frac{1}{k+2}\,\Omega(w+z,\,w),
\end{equation}
where $\Omega(w+z,w)
= J^0(w{+}z) \otimes J^0(w)
+ J^+(w{+}z) \otimes J^-(w)
+ J^-(w{+}z) \otimes J^+(w)$
is the split Casimir.
Applying $p \otimes p$: the projection $p$ annihilates
$U = J^0$, $V = J^+ - 1$, $b$, $c$, and all composites not
involving~$W$. Each summand of $\Omega$ has at least one factor
in $\{J^0, J^+, J^-\}$ at conformal weight~$1$; the Virasoro
sector has no weight-$1$ states ($L_{-1}|0\rangle = 0$), so
$p$ kills every such factor. Hence
$(p \otimes p)\,\Delta_z(T)
= \tau_z(T) \otimes 1 + 1 \otimes T$:
the linear transferred coproduct is already primitive.

\emph{Step~2: ghost-number obstruction at degree~$2$.}
The HPL tree formula for the degree-$2$ transferred
morphism involves two types of decorated trees
(\cite{LV12},~\S10.3):
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Source tree:}
 $(p \otimes p)\,\Delta_z\,h\,\mu(i(T),\, i(T))$.
\item \emph{Target tree:}
 $(p \otimes p)\,H_{12}\,\mu_{r(z)}
 (\Delta_z\,i(T),\, \Delta_z\,i(T))$.
\end{enumerate}
Both vanish, but by opposite ghost-number violations.

For tree~(a): $\mu(i(T), i(T)) = {:}TT{:}$ has ghost
number~$0$. Then $h({:}TT{:})$ has ghost number~$-1$
(equation~\eqref{eq:homotopy-ghost-degree}).
Then $\Delta_z$ preserves ghost number, depositing a
ghost-number-$(-1)$ element into $C \otimes C$.
A ghost-number-$(-1)$ element of $C \otimes C$ decomposes
into summands of bidegree $(0, -1)$ and $(-1, 0)$;
in both cases one tensor factor has ghost number~$\ne 0$,
so $(p \otimes p)$ kills it.

For tree~(b): each factor $\Delta_z\,i(T)$ has ghost
number~$0$ (the inclusion $i$ and the coproduct $\Delta_z$
both preserve ghost number). The twisted product $\mu_{r(z)}$
also preserves ghost number: $\mu_{r(z)}(\Delta_z i(T),
\Delta_z i(T))$ has ghost number~$0$ in $C \otimes C$.
Then $H_{12} = h \otimes \operatorname{id}
+ \operatorname{id} \otimes h$ drops the ghost number by~$1$,
producing a ghost-number-$(-1)$ element. The projection
$(p \otimes p)$ kills it by the same bidegree argument.

The two tree types are killed by the same
projection, but the ghost-number violations originate at
different stages: the source tree acquires its deficit
from $h$ applied \emph{before} the coproduct $\Delta_z$, while
the target tree acquires its deficit from $H_{12}$ applied
\emph{after} the coproduct.

\emph{Step~3: perturbation stability.}
The corrected inclusion $i_\infty = \sum_{n \ge 0}
(h\delta)^n\,i$ satisfies $i_\infty(T) = i(T)$: the stress
tensor is BRST-closed ($\delta(T) = 0$), so
$(h\delta)(i(T)) = h(\delta(T)) = 0$ and the series
terminates at the zeroth term. The corrected projection
$p_\infty = \sum_{n \ge 0} p\,(\delta h)^n$ has
ghost-number degree~$0$. Applying
$(p_\infty \otimes p_\infty)$ to
$\Delta_z\,i_\infty(T) = \Delta_z\,i(T)$ gives the same
primitive coproduct. No corrections appear at any
perturbative order.
\end{proof}

\subsubsection*{The all-degree theorem}

The degree-$2$ result extends to all degrees. The key
observation is that the ghost-number obstruction is structural:
it depends only on the tree topology of the HPL expansion,
not on the specific algebra or the degree. Source-side trees
produce output in ghost number~$+1$; target-side trees produce
output in ghost number~$-1$. In both cases, the projection
$p \otimes p$ annihilates the result, because
the $\mathcal{W}$-algebra cohomology sits in ghost number~$0$.

\begin{theorem}[Gravitational coproduct primitivity;
\ClaimStatusProvedHere]
\label{thm:gravitational-primitivity}
\index{coproduct!strict primitivity|textbf}
\index{Drinfeld--Sokolov reduction!coproduct primitivity}
Let $W_k(\mathfrak{g})
= H^0_{\mathrm{BRST}}(\widehat{\mathfrak{g}}_k, f_{\mathrm{prin}})$
be a principal Drinfeld--Sokolov reduction, with SDR $(i,p,h)$
from the BRST complex to the $\mathcal{W}$-algebra cohomology.
The HPL-transferred coproduct is strictly primitive at all
degrees:
\begin{equation}\label{eq:gravitational-primitivity}
\Delta_{z,n}^W \;=\; 0
\qquad\text{for all } n \ge 2.
\end{equation}
That is,
\begin{equation}\label{eq:gravitational-primitivity-explicit}
\Delta_z^W(x) \;=\; \tau_z(x) \otimes 1 \;+\; 1 \otimes x
\qquad
\text{for every } x \in W_k(\mathfrak{g}).
\end{equation}
All nontrivial structure of the transferred dg-shifted Yangian
resides in the $\Ainf$ products $\{m_n^W\}_{n \ge 3}$ and in
the $r(z)$-twisted target product. The coproduct carries no
information.
\end{theorem}

\begin{proof}
The proof rests on three facts:
the ghost-number degree of $h$, the ghost-number analysis of
source and target HPL trees, and the ghost-number selectivity
of $p \otimes p$.

\emph{(i) Ghost-number degree of $h$.}
For any principal DS reduction of $\widehat{\mathfrak{g}}$ by the
principal nilpotent $f$, the BRST complex has ghost pairs
$(b_\alpha, c_\alpha)$ indexed by positive roots $\alpha$
of $\mathfrak{g}$, with $\mathrm{gh}(b_\alpha) = -1$ and
$\mathrm{gh}(c_\alpha) = +1$. The Dynkin grade $j(\alpha)$
of the root determines the conformal weights of the ghost
pair ($(1-j, j)$), but ghost number is always $\pm 1$,
independent of the grade. The DS homotopy $h$ contracts each
acyclic pair in the direction of lower ghost number. Hence
$\mathrm{gh}(h) = -1$ for every principal DS reduction,
regardless of $\mathfrak{g}$.

\emph{(ii) Source-side and target-side ghost counting.}
The HPL tree formula for the degree-$n$ transferred coproduct
($n \ge 2$) is a sum over two families of decorated trees
(\cite{LV12},~\S10.3):
\begin{enumerate}[label=$\bullet$]
\item \emph{Source trees.}
 These operate on the source side of the coproduct: $n$
 inputs enter through the inclusion $i$ (ghost~$0$ each),
 pass through a tree of $h$-edges and $\delta$-vertices,
 then through $\Delta_z$ (ghost-preserving), and finally
 through $p \otimes p$. A binary tree with $n$ leaves
 has $n - 1$ internal vertices decorated by~$\delta$
 (ghost~$+1$ each) and $n - 2$ internal edges decorated
 by~$h$ (ghost~$-1$ each). The net ghost-number shift
 from the tree internals is
 $(n-1) \cdot (+1) + (n-2) \cdot (-1) = +1$.
 Combined with $\mathrm{gh}(i^{\otimes n}) = 0$ and
 $\mathrm{gh}(\Delta_z) = 0$, the output before
 projection has ghost number~$+1$.

\item \emph{Target trees.}
 These operate on the target side: $n$ inputs enter through
 $\Delta_z \circ i$ (ghost~$0$), pass through a tree of
 $H_{12}$-edges and target-$\delta$-vertices in
 $C \otimes C$, then through $p \otimes p$.
 The tensor-product homotopy $H_{12}
 = h \otimes \operatorname{id}
 + \operatorname{id} \otimes h$ has
 ghost-number degree~$-1$ (each summand lowers ghost
 number by~$1$ on one tensor factor). Every target tree
 with $n \ge 2$ leaves has at least one $H_{12}$-edge that
 is not paired with a target-$\delta$-vertex.
 The unpaired $H_{12}$ lowers ghost number by~$1$,
 producing an output of ghost number~$-1$ on at least one
 tensor factor.
\end{enumerate}

The two families exhaust the HPL expansion at each degree.
Source trees have ghost~$+1$; target trees have
ghost~$-1$ on one tensor factor. Both are nonzero.

\emph{(iii) Ghost-number selectivity of $p \otimes p$.}
The $\mathcal{W}$-algebra cohomology sits in ghost number~$0$.
The projection $p$ annihilates all elements of ghost number
$\ne 0$. For the coproduct, $p \otimes p$ acts on each tensor
factor separately and kills any element whose ghost number is
not $(0, 0)$.

For source trees: the output has total ghost number~$+1$, so it
decomposes into summands of bidegree $(+1, 0)$ and $(0, +1)$.
In both cases, one tensor factor has ghost number~$+1$,
and $p$ kills it.

For target trees: the unpaired $H_{12}$-insertion deposits
ghost number~$-1$ on one tensor factor. The resulting bidegree
is $(-1, 0)$ or $(0, -1)$, and $p$ kills that factor.

Combining (i)--(iii): every tree in the HPL expansion of
$\Delta_{z,n}^W$ ($n \ge 2$) produces an output of nonzero
ghost number before projection, and $(p \otimes p)$ kills
it. No cancellation between trees is required; each tree
vanishes individually.

\emph{(iv) Perturbation stability.}
The BRST-closedness of the $\mathcal{W}$-generators
($\delta(W_s) = 0$ for each spin-$s$ generator
$W_s$, $s = 2, \ldots, N$) ensures that the corrected
inclusion satisfies $i_\infty(W_s) = i(W_s)$, so the
perturbation-series argument of
Proposition~\ref{prop:coproduct-degree2-vanishing}, Step~3,
applies to every generator and every degree.
\end{proof}

\subsubsection*{The gauge-gravity comparison}

The algebraic distinction between gauge theory and gravity
reduces to a single sentence: the graviton is composite.

In gauge theory, the fundamental field is the connection
$A = J^a T_a\,dz$. The gluon $J^a$ lives in ghost number~$0$
of the unconstrained affine vertex algebra, at conformal
weight~$1$. No BRST reduction intervenes. The coproduct of
$J^a$ is primitive on generators:
$\Delta_z(J^a) = J^a(w+z) \otimes 1 + 1 \otimes J^a(w)$.
But the coproduct of the Sugawara composite is
nontrivial: the split Casimir
$\Omega(w+z,w) = \sum_a J^a(w+z) \otimes J^a(w)$ provides the
cross term~\eqref{eq:sugawara-cross-term}. Gluon bound states
dissociate. For $\mathfrak{g} = \mathfrak{sl}_2$, the
production vertex has coefficient $1/(k+2)$, confirmed by
explicit computation at conformal weight~$2$.

In gravity, the fundamental field is the stress tensor $T$,
the Sugawara quadratic
$T = \frac{1}{k+2}(\frac{1}{2}{:}J^0 J^0{:}
+ {:}J^+ J^-{:})$
of the $\mathfrak{sl}_2$ connection. The passage from $J^a$ to
$T$ is the Drinfeld--Sokolov reduction
$\widehat{\mathfrak{sl}}_2 \to \mathrm{Vir}_c$, implemented by
imposing the first-class constraint $J^+(z) = 1$. The BRST
ghost pair $(b,c)$ that enforces this constraint carries a
$\mathbf{Z}$-grading invisible to the unconstrained theory.
The same split Casimir that provides the gluon production
vertex is present in the affine coproduct of $T$
(equation~\eqref{eq:delta-z-sugawara}), but the projection
$p \otimes p$ annihilates it: each summand of $\Omega$ has at
least one factor at conformal weight~$1$, and the Virasoro
sector has no weight-$1$ states. At degree~$2$ and beyond, the
ghost-number obstruction of
Theorem~\ref{thm:gravitational-primitivity} provides a second,
independent, mechanism: even those HPL corrections that survive
the weight-$1$ argument are killed by the ghost-number mismatch
between the tree output (ghost $+1$ for source trees,
ghost~$-1$ for target trees) and the physical sector
(ghost~$0$).

The following table records the outcome across the standard
landscape of three-dimensional holomorphic-topological theories:

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{llccc}
\textbf{Theory} & \textbf{Boundary algebra}
 & $\boldsymbol{\Delta_z}$ \textbf{(gen.)}
 & $\boldsymbol{\Delta_z}$ \textbf{(comp.)}
 & \textbf{Mechanism} \\
\hline
Chern--Simons (gauge) &
 $\widehat{\mathfrak{g}}_k$ (affine KM) &
 $\ne \varepsilon$ &
 $\ne \varepsilon$ &
 fundamental gluon splitting \\[2pt]
3d gravity &
 $\mathrm{Vir}_c = W_k(\mathfrak{sl}_2)$ &
 $= \varepsilon$ &
 $= \varepsilon$ &
 ghost obstruction (principal DS) \\[2pt]
$bc$-$\beta\gamma$ (twisted hol.) &
 $H_k$ (Heisenberg) &
 $= \varepsilon$ &
 $= \varepsilon$ &
 free field, $r = k/z$ \\[2pt]
M2 brane &
 DDCA &
 $\ne \varepsilon$ &
 $\ne \varepsilon$ &
 no DS, fundamental modes \\[2pt]
Higher-spin gravity &
 $\mathcal{W}_N = W_k(\mathfrak{sl}_N)$ &
 $= \varepsilon$ &
 $= \varepsilon$ &
 ghost obstruction (principal DS) \\[2pt]
M5 brane &
 $W_{1+\infty} = \mathrm{DS}(\widehat{\mathfrak{gl}}_K)$ &
 $= \varepsilon$ &
 $= \varepsilon$ &
 ghost obstruction (principal DS) \\[2pt]
\hline
\rule{0pt}{2.4ex}%
Matter-coupled gravity &
 $\mathcal{W}(\mathfrak{sl}_3, f_{(2,1)})$ (BP) &
 $= \varepsilon$ &
 $\ne \varepsilon$ &
 non-principal DS; $J$ survives \\
\end{tabular}
\end{center}

The first six rows confirm the original dichotomy: every
boundary algebra obtained by \emph{principal} Drinfeld--Sokolov
reduction has a fully primitive coproduct, and every boundary
algebra consisting of fundamental fields has a nontrivial one.
The seventh row (the Bershadsky--Polyakov algebra) instantiates
the third column of the trichotomy
(Corollary~\ref{cor:gauge-gravity-dichotomy}). Free generators
are primitive (the ghost-number obstruction applies), but the
Sugawara composite $T$ is not: the surviving weight-$1$ current
$J$ feeds the split Casimir cross-term
$\Delta_{z,1}(T) \ni (1/z)\, J \otimes J$
(Remark~\ref{rem:bp-coproduct-resolved}). Free fields are
primitive for a different reason and by a different mechanism;
we return to this below.

\begin{remark}[Heisenberg: primitive without ghosts]
\label{rem:heisenberg-primitive}
\index{Heisenberg!primitive coproduct}
The Heisenberg algebra $H_k$ has a primitive coproduct because
its $r$-matrix $r^H(z) = k/z$ is a $c$-number: the target
product on $H_k \otimes H_k$ is twisted by a scalar, and
the HPL transfer produces no nontrivial corrections at any
degree. The bar complex terminates at degree~$2$ (class~G,
shadow depth $r_{\max} = 2$). There is no DS reduction and
no ghost obstruction. The Virasoro algebra, by contrast, has
an operator-valued $r$-matrix
$r^{\mathrm{Vir}}(z) = (c/2)/z^3 + 2T/z$, infinite shadow
depth (class~M), and all $\Ainf$ products nontrivial.
Production vertices \emph{could} in principle be generated by
the HPL transfer. They are killed by ghost number, not by
triviality of the input. Free fields are primitive because
they are free. Gravitational fields are primitive because they
are composite.
\end{remark}

\subsubsection*{Physical content: gravity without graviton
 production}

The strict primitivity of $\Delta_z^{\mathrm{grav}}$ is the
algebraic statement that three-dimensional gravity has no local
degrees of freedom.

The $\Ainf$ products
$\{m_n^{\mathrm{Vir}}\}_{n \ge 3}$ encode the self-interaction
of the stress tensor: nonlinear, infinite, and captured by the
higher $m_n$.
The coproduct corrections $\Delta_{z,n}$ for $n \ge 2$ would
encode graviton production: a graviton splitting into
constituents, each carrying a fraction of the energy. In three
dimensions: the Weyl tensor vanishes identically, so the
Einstein equations fix the local geometry completely, leaving
only topological degrees of freedom.

\subsubsection*{Primitivity and the strict $\Ainf$ morphism}
\label{par:primitive-strict-morphism}
\index{coproduct!strict A-infinity morphism|textbf}
\index{A-infinity morphism@$\Ainf$ morphism!strict from primitivity}

The vanishing of $\Delta_{z,n}$ for $n \ge 2$ has an immediate
structural consequence: the primitive coproduct
$\Delta_z^{\mathrm{prim}} \colon x \mapsto
\tau_z(x) \otimes 1 + 1 \otimes x$ is a \emph{strict}
$\Ainf$-algebra morphism. An $\Ainf$ morphism
$f \colon (A, \{m_n\}) \to (B, \{m'_n\})$ consists of
components $f_1, f_2, f_3, \ldots$ satisfying the morphism
Stasheff identities. The morphism is strict if $f_n = 0$ for
$n \ge 2$, so that the identities reduce to
$f_1 \circ m_n = m'_n \circ f_1^{\otimes n}$. The
gravitational coproduct satisfies this with
$f_1 = \Delta_{z,1}^{\mathrm{prim}}$: the compatibility
condition on the generator $T$ reads
\begin{equation}\label{eq:compatibility-primitive}
\Delta_z^{\mathrm{Vir}}(m_n(T^{\otimes n}))
\;=\;
m_n^{r(z)}\bigl(\Delta_z(T)^{\otimes n}\bigr),
\end{equation}
which expands to
\[
\tau_z(m_n(T^{\otimes n})) \otimes 1
\;+\; 1 \otimes m_n(T^{\otimes n})
\;=\;
m_n^{r(z)}\bigl(
(\tau_z(T) \otimes 1 + 1 \otimes T)^{\otimes n}\bigr).
\]
The left side is the primitive coproduct of the product; the
right side is the $r(z)$-twisted product of the primitive
coproducts. No independent coproduct data enters at any
degree. The entire dg-shifted Yangian of gravity is controlled
by two data: the collision residue
\begin{equation}\label{eq:gravity-r-matrix-determines-all}
r^{\mathrm{Vir}}(z)
\;=\;
\frac{c/2}{z^3} \;+\; \frac{2T}{z}
\end{equation}
and the $\Ainf$ product tower $\{m_n^{\mathrm{Vir}}\}$. The
coproduct, which is the third datum of a general Yangian, adds
nothing.

The strictness of $\Delta_z^{\mathrm{prim}}$ as an $\Ainf$
morphism should be contrasted with the transferred products
$\{m_n^{\mathrm{Vir}}\}_{n \ge 3}$, which are genuinely
higher-order: $m_3 \ne 0$ forced by the quartic OPE pole,
$m_4 \ne 0$ forced by the Stasheff identity relating $m_3$
and $m_2$, and so on through the entire infinite tower
(class~M, shadow depth $r_{\max} = \infty$). The gravitational
Yangian has maximal product complexity and zero coproduct
complexity. The gauge-theoretic Yangian (affine KM) has
$m_2$ strict and $\Delta_z$ nontrivial: product complexity
$0$ and nonzero coproduct complexity. The two theories exhaust
opposite corners of the $(m, \Delta)$-complexity plane.

\subsubsection*{The $r$-matrix seeds the genus tower}
\label{par:btz-r-matrix}

The collision residue~\eqref{eq:gravity-r-matrix-determines-all}
is the genus-$0$, degree-$2$ datum. It seeds the entire genus
tower through self-sewing: the $r$-matrix couples to itself on
each handle of $\overline{\mathcal{M}}_{g,n}$, producing the
genus-$g$ free energy $F_g$ as a Hodge integral weighted by
$\kappa_{\mathrm{eff}}$. The Cardy entropy is the
high-temperature shadow of this tower.

The self-sewing construction couples $r^{\mathrm{Vir}}(z)$
to the Hodge class on $\overline{\mathcal{M}}_{g,n}$. At
genus~$1$, the self-loop graph
$\Gamma = \vcenter{\hbox{\begin{tikzpicture}[scale=0.4,
 baseline=-0.5ex]
\draw (0,0) circle (0.4);
\fill (0,-0.4) circle (0.05);
\end{tikzpicture}}}$
on $\overline{\mathcal{M}}_{1,1}$ extracts
$\kappa = c/2$ from the subleading pole of
$r^{\mathrm{Vir}}(z)$. The leading pole $(c/2)/z^3$
contributes zero after the $\operatorname{Res}_{z=0}$
extraction (no $z^{-1}$ term); the subleading pole $2T/z$
contributes
$\operatorname{Res}_{z=0}\,2T/z\,dz = 2\langle T \rangle
= c/12$. The sewing integral over
$\overline{\mathcal{M}}_{1,1}$ couples this to
$\lambda_1 = 1/24$, giving $F_1 = \kappa/24 = c/48$.
After ghost subtraction:
$F_1^{\mathrm{eff}} = \kappa_{\mathrm{eff}}/24 = (c-26)/48$.

The holomorphic contribution to the BTZ
partition function is read as the exponential of the all-genus generating function
$\sum_{g \ge 1} F_g^{\mathrm{eff}}\,x^{2g}
= \frac{c-26}{2}\bigl(\hat{A}(ix) - 1\bigr)$,
where $\hat{A}(x) = (x/2)/\sinh(x/2)$. The Cardy entropy
$S_{\mathrm{Cardy}} =
2\pi\sqrt{c\Delta_+/6} + 2\pi\sqrt{c\Delta_-/6}$
at large shifted conformal energy (Conjecture~\ref{conj:gravity-cardy})
arises from the modular
$S$-transform of this generating function. The $r$-matrix is the genus-$0$,
degree-$2$ datum that seeds the entire tower; the Cardy entropy is its
high-temperature shadow.

\subsubsection*{Conical defects and BTZ from braiding}

Primitivity of $\Delta_z^{\mathrm{grav}}$ states that the BTZ
spectrum is not built by splitting gravitons. Black holes
form by a different mechanism: accumulation of $r$-matrix
twists. The BTZ black hole of mass $M$ and angular
momentum $J$ is a quotient of AdS$_3$ by a discrete isometry;
its partition function is read as a trace over a single
Virasoro module, not as a sum over multi-graviton states.
Conical defects of angular deficit $2\pi(1 - \sqrt{1 - 8Gh})$
are read as highest-weight modules $M_h$ of the Koszul dual
$\mathrm{Vir}_{26-c}$: they are topological
objects, classified by the monodromy of the $r$-matrix
braiding. The fusion of two
conical defects is controlled by conformal blocks of
$\mathrm{Vir}_{26-c}$, parametrized by the Ponsot--Teschner
fusion kernel
$\mathbb{F}_{\alpha_s}^{\alpha_t}$
(\S\ref{subsec:gravity-r-matrix}). The gravitational $S$-matrix
is a pure braiding matrix:
it rearranges line operators but never creates new ones.

This is the algebraic content of the classical observation that
three-dimensional gravity is topological. The Einstein--Hilbert
action in three dimensions is equivalent to Chern--Simons theory
for $SL(2,\mathbf{R}) \times SL(2,\mathbf{R})$, and the phase
space consists of flat connections modulo gauge: a
finite-dimensional moduli space with no local excitations. The
Koszul-dual formulation makes this precise. The coproduct
$\Delta_z$ would create local excitations
(propagating gravitons). Its vanishing states that the only
gravitational degrees of freedom are topological:
conical deficits, black holes, and
the modular data encoded in the braiding of line operators.
The $r$-matrix is the complete repository of this
topological content.

\subsubsection*{The $\mathcal{W}_N$ extension and
 non-principal reductions}
\label{par:wn-ghost-obstruction}
\index{W-algebra@$\mathcal{W}$-algebra!ghost-number obstruction}

Theorem~\ref{thm:gravitational-primitivity} covers all
principal DS reductions, including $\mathcal{W}_N$-gravity
($\mathfrak{g} = \mathfrak{sl}_N$) and the M5 brane
($\mathfrak{g} = \mathfrak{gl}_K$). The essential input is
the ghost-number degree $\mathrm{gh}(h) = -1$, which holds
for every principal nilpotent. We verify this explicitly for
$\mathfrak{sl}_N$.

The DS reduction of $\widehat{\mathfrak{sl}}_N$ by the
principal nilpotent $f = \sum_{i=1}^{N-1} E_{i+1,\,i}$
produces $N(N-1)/2$ ghost pairs
$(b_\alpha, c_\alpha)$ indexed by positive roots
$\alpha \in \Phi^+(\mathfrak{sl}_N)$. The
$\operatorname{ad}(h_0)$-eigenvalue of each root is
its Dynkin grade $j(\alpha) \in \{1, 2, \ldots, N-1\}$.
The conformal weights of the ghost pair at grade~$j$ are
$(1-j,\, j)$, so higher-grade ghost pairs have higher
conformal weight. The ghost number, however, is always
$\mathrm{gh}(b_\alpha) = -1$, $\mathrm{gh}(c_\alpha) = +1$,
regardless of the grade. The Dynkin grade controls the
conformal weight of the intermediate state but has no effect
on the ghost-number argument: every acyclic pair is separated
by exactly one unit of ghost number, and every contraction
by $h_N$ lowers ghost number by exactly~$1$.

The proof of
Theorem~\ref{thm:gravitational-primitivity} therefore applies
verbatim to $\mathcal{W}_N$ for every~$N$: the spin-$s$
generators $W_s$ ($s = 2, \ldots, N$) are BRST-closed,
$i_\infty(W_s) = i(W_s)$, and every HPL tree for the degree-$n$
coproduct ($n \ge 2$) vanishes after projection by the same
ghost-number bottleneck. Higher-spin gravitons do not split
either.

\begin{remark}[Non-principal nilpotents]
\label{rem:non-principal-ghost}
\index{Drinfeld--Sokolov reduction!non-principal}
For a non-principal nilpotent $f$ in $\mathfrak{g}$, the BRST
complex $C^{\mathrm{DS}}(\mathfrak{g}, f)$ has ghost pairs
$(b_\alpha, c_\alpha)$ indexed by positive roots with
$\langle \alpha, h_0 \rangle > 0$, where $h_0$ is the neutral
element of the $\mathfrak{sl}_2$-triple of~$f$. The homotopy
$h_f$ still has ghost-number degree~$-1$: every acyclic pair
in the Chevalley--Eilenberg complex of $\mathfrak{n}_+(f)$
is separated by one unit of ghost number. Thus the
ghost-number obstruction kills all \emph{nonlinear} HPL
corrections: $\Delta_{z,n}^{\mathcal{W}(\mathfrak{g},f)} = 0$
for $n \ge 2$ whenever the DS reduction produces an SDR with
$\mathrm{gh}(h_f) = -1$. This covers hook-type, subregular,
and minimal nilpotents in all types. However, the
\emph{linear} transferred coproduct $\Delta_{z,1}$ requires a
separate argument: for non-principal reductions whose
$\mathcal{W}$-algebra retains weight-$1$ generators (e.g.\
the Bershadsky--Polyakov algebra from $(\mathfrak{sl}_3,
f_{(2,1)})$, which has an $\widehat{\mathfrak{sl}}_2$
subalgebra at weight~$1$), the projection~$p$ does not
automatically kill the split Casimir cross-terms. The
resolution (Remark~\ref{rem:bp-coproduct-resolved}) is that
\emph{generator}-primitivity holds (the ghost-number
obstruction kills all cross-terms on free generators), but
\emph{composite}-primitivity can fail: fields built from
surviving weight-$1$ generators (e.g.\ the Sugawara stress
tensor) may acquire cross-terms from the split Casimir.
\end{remark}

\begin{remark}[BP coproduct: resolved]
\label{rem:bp-coproduct-resolved}
\index{Bershadsky--Polyakov algebra!coproduct resolution}
The linear transferred coproduct $\Delta_{z,1}$ \emph{is}
primitive for the Bershadsky--Polyakov algebra
$\mathcal{W}(\mathfrak{sl}_3, f_{(2,1)})$ on all free
generators, but not on composites. The three free generators
behave as follows:
\begin{enumerate}
\item $G^+ = J^{E_{23}}$ and $G^- = J^{E_{31}}$ are
 fundamental affine generators. Because $E_{23}$ and
 $E_{31}$ are root vectors for simple roots of the
 $\mathfrak{sl}_2$-complement, the split Casimir
 $\Omega = \sum t^a \otimes t_a$ contributes no cross-term
 of the form $J^{E_{23}} \otimes (\cdots)$ or vice versa:
 the Casimir component $E_{23} \otimes E_{32}$ pairs a
 surviving direction with a BRST-exact one. Thus
 $\Delta_{z,1}(G^\pm) = G^\pm \otimes 1 + 1 \otimes G^\pm$.
\item The weight-$1$ generator $J$ involves Cartan currents
 and ghost bilinears. Ghost cross-terms are killed by the
 ghost-number projection $p \otimes p$: any term with
 nonzero ghost number in either tensor factor vanishes
 under projection to the ghost-number-zero summand.
 Thus $\Delta_{z,1}(J) = J \otimes 1 + 1 \otimes J$.
\item The stress tensor $T$ is a \emph{composite} (Sugawara
 plus ghost corrections), not a free generator. Its
 coproduct is \emph{non-primitive}: the $\mathfrak{sl}_3$
 Casimir has a surviving Cartan component
 $H_1 \otimes H_1$ that projects to $J \otimes J$ under
 $p \otimes p$, giving a nonzero cross-term
 $\Delta_{z,1}(T) \ni (1/z)\, J \otimes J$.
\end{enumerate}
The dichotomy between principal and
non-principal DS reductions is sharp:
\begin{itemize}
\item \textbf{Principal} ($\mathrm{Vir}$, $\mathcal{W}_N$):
 \emph{all} fields are primitive, including composites,
 because no weight-$1$ generators survive the reduction:
 the ghost-number obstruction kills everything.
\item \textbf{Non-principal} (Bershadsky--Polyakov and its
 generalisations): free generators are primitive, but
 composites built from surviving weight-$1$ fields are
 non-primitive. The surviving weight-$1$ Casimir component
 provides exactly the cross-terms that escape the
 ghost-number filter.
\end{itemize}
The gap flagged in Remark~\ref{rem:non-principal-ghost} is
therefore resolved: primitivity holds on generators (which
suffice for the coalgebra structure), while the composite
non-primitivity is a \emph{consequence} of the Sugawara
construction and does not obstruct the HPL transfer.
\end{remark}

\begin{remark}[Scope and the infinite tower]
\label{rem:primitivity-scope}
\label{rem:coproduct-gap-closed}
\index{coproduct!scope of primitivity}
Theorem~\ref{thm:gravitational-primitivity} resolves the
coproduct question completely: strict primitivity holds at all
degrees for all principal DS reductions. The ghost-number
obstruction extends to all $N$: the total ghost number
$\mathrm{gh}_{\mathrm{tot}} = \sum_\alpha \mathrm{gh}(c_\alpha)$
is a global $\mathbb{Z}$-grading regardless of the number of ghost
pairs, the homotopy~$h_f$ has $\mathrm{gh}(h_f) = -1$ for
structural reasons (forced by the SDR equation
$\pi \circ h = 0$, $h \circ \iota = 0$, $h^2 = 0$),
and $p \otimes p$ kills all nonzero ghost-number
components of $\Delta^{V_k}_{z,n}$ since both tensor factors
project to the ghost-number-zero summand. The remaining
gaps of Remark~\ref{rem:ds-hpl-honest-gaps} concern the
transferred $\Ainf$ products and the dg-shifted Yangian axioms,
not the coproduct. The infinite complexity of
class~$\mathbf{M}$ algebras ($\mathrm{Vir}$,
$\mathcal{W}_N$ for all $N$) resides entirely in the
transferred products $\{m_n^W\}_{n \ge 3}$ and the
$r(z)$-twisted target product. The coproduct is trivial.
The nontrivial gravitational
physics lives entirely in the $r$-matrix.
\end{remark}

%====================================================================
% MOVEMENT IV: THE GENUS TOWER
%====================================================================

\subsection{Movement IV: the genus tower}
\label{subsec:gravity-genus-tower}

Movements I--III operated at genus~$0$: the $\Ainf$ tower,
the Koszul triangle, the $R$-matrix, the coproduct: all
live on $\FM_k(\C) \times \Conf_k^<(\R)$, the product of
holomorphic and topological configuration spaces on
$\C \times \R$. Movement~IV raises the genus. The
curvature $d_{\mathrm{fib}}^2 = \kappa_{\mathrm{eff}}
\cdot \omega_g$ measures the failure of the genus-$0$
differential to square to zero on genus-$g$ surfaces,
and the genus tower $\{F_g\}_{g \ge 1}$ records this
failure as a sequence of Hodge integrals.

\subsubsection*{Genus-$1$ curvature}

The effective gravitational curvature
(Remark~\ref{rem:gravity-kappa-vs-kappa-eff}) is
\begin{equation}\label{eq:gravity-kappa}
\kappa_{\mathrm{eff}}
\;=\;
\frac{c - 26}{2}
\;=\;
3k - 13.
\end{equation}
The bar differential at genus~$1$ acquires curvature
$d_{\mathrm{fib}}^2 = \kappa_{\mathrm{eff}} \cdot \omega_1$
from the self-loop graph on $\overline{\cM}_{1,1}$. The genus-$1$
free energy:
\begin{equation}\label{eq:gravity-F1}
F_1(\mathrm{Vir}_c)
\;=\;
\kappa_{\mathrm{eff}} \cdot \frac{1}{24}
\;=\;
\frac{c - 26}{48}.
\end{equation}
The corresponding $\eta$-function bookkeeping packages the
genus-$1$ oscillator contribution as a function of~$\tau$; it
should not be conflated with the constant free energy~$F_1$.
Here $\eta(\tau) = q^{1/24}\prod_{n \ge 1}(1 - q^n)$.

\begin{remark}[Intrinsic vs.\ effective free energy at genus $1$]
\label{rem:gravity-F1-intrinsic-vs-effective}
The \emph{intrinsic} genus-$1$ free energy of $\mathrm{Vir}_c$ is
$F_1^{\mathrm{intr}} = \kappa(\mathrm{Vir}_c)/24 = c/48$,
using the intrinsic modular characteristic $\kappa = c/2$
(see Computation~\ref{comp:genus1-free-energy}).
The \emph{effective} value $F_1^{\mathrm{eff}} = (c-26)/48$
in~\eqref{eq:gravity-F1} is the physical quantity after
ghost subtraction ($\kappa_{\mathrm{ghost}} = -13$). At
$c = 26$: $F_1^{\mathrm{eff}} = 0$ (the genus tower collapses).
The corresponding partition functions on a torus~$E_\tau$ are
$Z_1^{\mathrm{intr}}(\tau) = \eta(\tau)^{-c/2}$ and
$Z_1^{\mathrm{eff}}(\tau) = \eta(\tau)^{-(c-26)/2}$.
\end{remark}

\subsubsection*{All genera: the $\hat A$-genus and the Wick rotation}

The genus-$g$ free energy is
$F_g = \kappa_{\mathrm{eff}} \cdot \int_{\overline{\cM}_g}
\lambda_g$ ,
with generating function
\begin{equation}\label{eq:gravity-generating}
\sum_{g \ge 1} F_g\,x^{2g}
\;=\;
\frac{c - 26}{2}\bigl(\hat{A}(ix) - 1\bigr),
\qquad
\hat{A}(x) = \frac{x/2}{\sinh(x/2)}.
\end{equation}
The argument~$ix$, not~$x$, is the content.
The $\hat{A}$-genus
$\hat{A}(x) = (x/2)/\sinh(x/2)$
is the characteristic series of the Dirac index:
its Taylor coefficients are the alternating Bernoulli
numbers.
The substitution $x \mapsto ix$ converts
$\sinh(ix/2) = i\sin(x/2)$, producing
$\hat{A}(ix) = (x/2)/\sin(x/2)$
with all coefficients positive.
This is the Wick rotation
from Lorentzian (oscillatory Dirac index, alternating signs)
to Euclidean (convergent Hodge integrals, definite signs):
the factor $i^{2g} = (-1)^g$ on each monomial~$x^{2g}$
absorbs the alternation. The individual coefficients
are the Faber--Pandharipande Hodge integrals
$\int_{\overline{\cM}_g} \lambda_g
= \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
=: \lambda_g^{\mathrm{FP}} > 0$
for all $g \ge 1$, and their generating function is
$\hat{A}(x) = (x/2)\operatorname{csch}(x/2)$.
The prefactor $\kappa_{\mathrm{eff}} = (c{-}26)/2$ is the
single datum from the boundary algebra after ghost
subtraction.\label{obs:genus-tower-wick-anomaly}%
\index{Wick rotation!anomaly interpretation}%
\index{genus tower!as Wick rotation anomaly}%

Since every $\lambda_g^{\mathrm{FP}}$ is positive,
the genus tower has uniform sign
$\operatorname{sgn}(\kappa_{\mathrm{eff}})$
at every genus: subcritical ($c < 26$) gives
$F_g < 0$ for all~$g$;
supercritical ($c > 26$) gives $F_g > 0$;
critical ($c = 26$) gives $F_g = 0$.
No sign alternation survives the Wick rotation.

\begin{remark}[Why the $\hat{A}$-genus]
\label{rem:why-A-hat-genus}
\index{A-hat genus@$\hat{A}$-genus!why it appears}%
Three independent routes force $\hat{A}$ rather than the Todd class:
\begin{enumerate}
\item \emph{Symmetry.} The genus tower uses only even powers of~$x$.
 The Todd class $\mathrm{Td}(x) = x/(1-e^{-x})$ has odd powers.
 The product $\mathrm{Td}(x)\cdot\mathrm{Td}(-x)
 = x^2/((1-e^{-x})(e^x-1)) = x^2/(4\sinh^2(x/2))$ is even;
 its positive square root $x/(2\sinh(x/2)) = \hat{A}(x)$.
\item \emph{KO orientation.} The Hodge bundle $\mathbb{E}$ on
 $\overline{\mathcal{M}}_g$ carries a real structure via Serre
 duality ($\mathbb{E}^* \simeq \mathbb{E} \otimes \omega$).
 Real vector bundles are oriented by KO-theory, whose
 multiplicative genus is the $\hat{A}$-genus. Complex vector
 bundles would give the Todd class via KU-theory.
\item \emph{Explicit integration.} The Faber--Pandharipande
 integral
 $\lambda_g^{\mathrm{FP}}
 = \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}$
 equals the coefficient of $x^{2g}$ in
 $\hat{A}(ix) - 1 = (x/2)/\sin(x/2) - 1$
 (the standard Mittag-Leffler expansion
 $z/\sin(z) = 1 + 2\sum_{g \ge 1}
 \tfrac{(2^{2g-1}-1)|B_{2g}|}{(2g)!}\,z^{2g}$
 identifies the Taylor coefficients with
 $\lambda_g^{\mathrm{FP}}$; verified numerically through
 $g = 6$). The factor
 $(2^{2g-1}-1)/2^{2g-1}$ arises from the boundary-strata
 decomposition $\csc(u) = \cot(u) + \tan(u/2)$.
\end{enumerate}
\end{remark}

\medskip

The vanishing locus $\kappa_{\mathrm{eff}} = 0$ admits
a modular reading.
The genus-$1$ partition function
$Z_1^{\mathrm{eff}}(\tau) = \eta(\tau)^{-\kappa_{\mathrm{eff}}}$
transforms under the modular $S$-transform
$\tau \mapsto -1/\tau$ with weight $-\kappa_{\mathrm{eff}}/2$,
because $\eta(-1/\tau) = \sqrt{-i\tau}\cdot\eta(\tau)$.
At $\kappa_{\mathrm{eff}} = 0$ the weight vanishes:
$c = 26$ is the unique central charge at which
$Z_1^{\mathrm{eff}}$ is $S$-invariant.
The genus tower therefore measures the
\emph{breaking of Wick-rotation symmetry}:
$F_g \ne 0$ at genus~$g$ is the $g$-th
anomaly coefficient, and the Cardy entropy
$S_{\mathrm{Cardy}} =
2\pi\sqrt{c\Delta_+/6} + 2\pi\sqrt{c\Delta_-/6}$
\textup{(}Conjecture~\textup{\ref{conj:gravity-cardy})}
is its high-temperature shadow, extracted by composing
the $S$-transform with the saddle-point approximation.
The single chain
\[
\text{quartic pole}
\;\longrightarrow\;
\kappa
\;\longrightarrow\;
d_{\mathrm{fib}}^2 = \kappa_{\mathrm{eff}}\cdot\omega_g
\;\longrightarrow\;
F_g \ne 0
\;\longrightarrow\;
S_{\mathrm{Cardy}}
\]
connects the OPE datum to the entropy.

\begin{remark}[Modularity from the open sector]
\label{rem:gravity-modularity-open-sector}
\index{modularity!from open sector}
The genus tower is not an axiom on the closed algebra
$\mathrm{Vir}_c$. It arises from trace and clutching on the
gravitational open-sector factorization dg-category
$\cC_{\mathrm{grav}}^{\mathrm{op}}$
\textup{(}Definition~\textup{\ref{def:grav-open-category})}: the
annulus trace $\int_{S^1} \cC_{\mathrm{grav}}^{\mathrm{op}}
\simeq HH_*(\mathrm{Vir}_c)$ is the first modular shadow
\textup{(}\eqref{eq:grav-annulus-trace}\textup{)}, and
clutching along shared boundary circles raises genus. The
scalar $\kappa_{\mathrm{eff}}$ enters as the trace of the
cyclic pairing on $\End(b)$, not as primitive closed-string data.
The MC equation on the bordered FM compactification
$\overline{C}{}^{\,\mathrm{oc}}_{k,\vec{m}}$ packages both
sectors into a single identity whose closed projection recovers
$F_g = \kappa_{\mathrm{eff}} \int_{\overline{\cM}_g}\lambda_g$ .
\end{remark}

\begin{remark}[Gravitational content as closed-sector projection of $\SCchtop$]
\label{rem:gravity-closed-sector-projection-genus}%
\index{3d gravity!closed-sector projection}%
\index{Swiss-cheese operad!gravitational projection}%
Every gravitational quantity in this section is the
$\Sigma_n$-coinvariant (closed-sector) projection of an ordered
$\SCchtop$-structure. The curvature $\kappa_{\mathrm{eff}}$ is
$\mathrm{av}(r(z))$, the image of the classical $r$-matrix
under the averaging map $\mathrm{av}\colon
\mathfrak{g}^{E_1}_{\mathrm{Vir}} \to
\mathfrak{g}^{\mathrm{mod}}_{\mathrm{Vir}}$
(Remark~\ref{rem:e1-colour-primitive}). The free energy
$F_g = \kappa_{\mathrm{eff}} \int_{\overline{\cM}_g} \lambda_g$ is the image of the ordered genus-$g$ amplitude. The full ordered
ancestor carries strictly more data: the $R$-matrix, the braided
monoidal structure on line operators (Movement~III), and the
Yangian completion $\Ydg(\mathrm{Vir}_c)$. The closed-sector
projection discards this data and retains only the scalar
shadow obstruction tower of Volume~I. Three-dimensional quantum
gravity, in the Virasoro $\SCchtop$-algebra formulation, is
the modular shadow of the ordered gravitational Yangian.
\end{remark}

\begin{remark}[Gravitational content as $\Sigma_n$-descent of the $\SCchtop$-structure]
\label{rem:gravity-sigma-descent}%
\index{3d gravity!Sigma-n descent@$\Sigma_n$-descent}%
\index{Swiss-cheese operad!gravitational content}%
The preceding remark identifies every gravitational quantity as
a $\Sigma_n$-coinvariant projection. In the language of the
three-bar-complex hierarchy
(Remark~\ref{rem:sc-three-bar-connection} in
\S\ref{sec:foundations}), the gravitational genus tower
$F_g = \kappa_{\mathrm{eff}} \cdot \lambda_g^{\mathrm{FP}}$ is an invariant of the symmetric bar $\barBch(\mathrm{Vir}_c)$,
while the full $\SCchtop$-structure of $\mathrm{Vir}_c$
also encodes the $R$-matrix, the braided monoidal
structure on gravitational line operators, and the dg-shifted
Yangian $\Ydg(\mathrm{Vir}_c)$.
The derived center $Z^{\mathrm{der}}_{\mathrm{ch}}(\mathrm{Vir}_c)$
(Volume~I, Theorem~\ref*{V1-thm:thqg-swiss-cheese}) is the
universal bulk algebra of the gravitational theory: it is
computed by chiral Hochschild cochains of any boundary chart,
not by the bar complex.
The bar complex classifies twisting morphisms (couplings between
$\mathrm{Vir}_c$ and $\mathrm{Vir}_{26-c}$); the derived
center classifies bulk observables. Three-dimensional gravity
is the closed-sector ($\Sigma_n$-averaged) projection of the
full open/closed $\SCchtop$-structure on the Virasoro algebra.
\end{remark}

\begin{remark}[Bi-based factorisation datum at the K3$\times T^2$
compactification]
\label{rem:3dqg-bi-based-factorisation}%
\index{factorisation datum!bi-based!K3$\times T^2$}%
\index{Kodaira fibre!24 nearby cycles}%
\index{SC@$\SCchtop$!K3 specialisation}%
The closed-sector projection of the Virasoro $\SCchtop$-structure
admits a geometric refinement at the K3$\times T^2$ compactification
relevant to the 3d-gravity climax. In this frame the ordered
ancestor is a \emph{bi-based factorisation datum}: a chiral
factorisation algebra on the Ran space
$\mathrm{Ran}(E^{\mathrm{nod},\mathrm{sm}}_{24})$ of the elliptic
K3 with $24$ Kodaira I$_1$ nodal points attached together with a
parameter factorisation on the compactified genus-$2$ Siegel moduli
space $\overline{\cA}_2$. The bi-based structure is the pair
\[
\bigl(
\mathrm{Fact}^{\mathrm{ch}}_{\mathrm{Ran}(E^{\mathrm{nod},\mathrm{sm}}_{24})}(\mathrm{Vir}_c),
\;
\mathrm{Fact}^{\mathrm{param}}_{\overline{\cA}_2}
\bigr)
\]
linked by the Francis--Gaitsgory $\infty$-categorical pushforward
along the Kuga--Satake correspondence, with nearby-cycles at the
$24$ Kodaira nodes supplying the Costello--Gaiotto 5-brane vertex
data of \cite{CostelloGaiotto2018,Costello2021}. The
$\SCchtop$-structure on the bulk-boundary pair
$\bigl(C^\bullet_{\mathrm{ch}}(\mathrm{Vir}_c,\mathrm{Vir}_c),
\mathrm{Vir}_c\bigr)$ of
Chapter~\ref{ch:sc-chtop-heptagon} specialises to this bi-based
datum, with the averaging map factoring
\[
\mathrm{av}
\;=\;
\mathrm{Torelli}_{\mathrm{K3}}
\,\circ\,
\mathrm{KugaSatake}
\,\circ\,
j_{\mathrm{Kodaira}}
\]
through the Kuga--Satake $\mathbb{Z}/2$-spin cover of $\cA_2$.
Bi-basing the factorisation is the geometric mechanism that
relates the chain-level $\SCchtop$-heptagon
(Theorem~\ref{thm:sc-heptagon}) to the
$(\infty,1)$-categorical bulk-boundary pair of
Part~\ref{part:gravity}: both lanes present the same geometric
object, viewed through different factorisation bases.
Primary literature: \cite{FrancisGaitsgory2012} (parametrised
factorisation $\infty$-categories);
\cite{CostelloGaiotto2018,Costello2021} (twisted M-theory and
5-brane vertex algebra on K3$\times T^2$).
\end{remark}

\subsubsection*{The effective scalar partition function}

The effective scalar bookkeeping series for the SL$(2,\R) \times$
SL$(2,\R)$ theory (left$+$right) is
\[
Z_{\mathrm{grav}}^{\mathrm{scal}}(\tau, \bar\tau)
\;=\;
|\eta(\tau)|^{(c-26)/6}.
\]
The exponent $(c{-}26)/6$ is $\kappa_{\mathrm{eff}}/3$, reflecting
the per-real-degree-of-freedom normalisation of the
SL$(2,\R) \times$ SL$(2,\R)$ one-loop determinant
($\dim_{\R} \mathfrak{sl}_2 = 3$, two copies).
At $c = 26$ ($k = 13/3$):
$Z_{\mathrm{grav}}^{\mathrm{scal}} = 1$, reflecting effective scalar
anomaly cancellation rather than triviality of the full coupled
partition function. At $c = 13$ (Koszul self-duality):
$Z_{\mathrm{grav}}^{\mathrm{scal}} = |\eta(\tau)|^{-13/6}$.

\subsubsection*{The shadow obstruction tower}

The genus tower is controlled by a sequence of invariants,
each extracted from the $\Ainf$ tower at increasing degree.
The first four named shadows and their gravitational readings:

\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lll}
\textbf{Shadow} & \textbf{Algebraic origin (Vol~I)} & \textbf{Gravitational counterpart} \\
\hline
$\kappa_{\mathrm{eff}} = (c-26)/2$
 & effective curvature after ghost subtraction
 & one-loop Weyl anomaly; $= 0$ iff $c = 26$ \\[2pt]
$\mathfrak{C}(\mathrm{Vir}_c) = -c$
 & cubic shadow (Vol~I)
 & cubic graviton vertex; $\propto \ell/(16\pi G)$ at Brown--Henneaux \\[2pt]
$\mathfrak{Q} = 10/[c(5c+22)]$
 & quartic contact shadow (Computation~\ref{comp:gravity-quartic-correction})
 & genus-$2$ correction $F_2^{\mathrm{contact}}$ \\[2pt]
$o_5 \ne 0$
 & quintic obstruction (Vol~I, non-vanishing)
 & genus-$2$ five-point contribution to $F_2$
\end{tabular}
\end{center}

The shadow obstruction tower does not terminate
(by the explicit Virasoro quartic-contact computation of Volume~I):
the $r$-th shadow determines the $r$-graviton
vertex, and no finite
truncation determines the full perturbative hierarchy.

\begin{computation}[Quartic contact shadow and genus-$2$ contact
correction; \ClaimStatusProvedHere]
\label{comp:gravity-quartic-correction}%
\index{quartic contact shadow!genus-2 contact correction}%
The quartic contact shadow
$\mathfrak{Q}^{\mathrm{contact}}_{\mathrm{Vir}} = 10/[c(5c+22)]$
from the quartic-contact analysis of Volume~I
determines the genus-$2$ contact correction
$F_2^{\mathrm{contact}}$, the
leading nonlinear partition-function correction beyond the
one-loop sector.

\emph{Explicit evaluation.} At the Brown--Henneaux central charge
$c = 6k = 3\ell/(2G)$:
\begin{alignat*}{2}
\mathfrak{Q}(c = 6k)
\;&=\;
\frac{10}{6k(30k+22)}
\;=\;
\frac{5}{6k(15k+11)},
\\[4pt]
\intertext{and the genus-$1$ Hessian correction
$\delta_H^{(1)} = 120/[c^2(5c+22)]$ evaluates to}
\delta_H^{(1)}(c = 6k)
\;&=\;
\frac{120}{36k^2(30k+22)}
\;=\;
\frac{5}{3k^2(15k+11)}.
\end{alignat*}
In the semiclassical limit $k \to \infty$ (equivalently
$G \to 0$):
\[
\mathfrak{Q} \;\sim\; \frac{1}{18k^2},
\qquad
\delta_H^{(1)} \;\sim\; \frac{1}{9k^3}.
\]
The quartic correction enters the genus-$2$ partition function
via the $r = 4$ planted-forest graph amplitude:
\[
F_2^{\mathrm{contact}}
\;=\;
\mathfrak{Q} \cdot \int_{\overline{\cM}_{2}} \psi_1^2
\;=\;
\frac{10}{c(5c+22)} \cdot \frac{1}{240}
\;=\;
\frac{1}{24\,c(5c+22)},
\]
where $\int_{\overline{\cM}_2} \psi_1^2 = 1/240$ by
Faber's formula.

\emph{Gravitational interpretation.}
The quartic shadow $\mathfrak{Q}$ is read as the four-graviton
contact coupling: a connected genus-$0$ amplitude with four external
stress-tensor insertions, exchanged through the one-loop wheel
graph $C_4$. Its nonvanishing ($\mathfrak{Q} \neq 0$ for
$c \neq 0$) is the algebraic witness that $3$d gravity has genuine
nonlinear dynamics beyond one loop,
and the shadow depth of $\mathrm{Vir}_c$ being infinite
(class~M) is read as meaning that the full graviton S-matrix
has no finite truncation.

\emph{Complementarity.} Under $c \mapsto 26 - c$
(Koszul duality $\mathrm{Vir}_c^! = \mathrm{Vir}_{26-c}$):
\[
\mathfrak{Q}(c) + \mathfrak{Q}(26-c)
\;=\;
\frac{10}{c(5c+22)} + \frac{10}{(26-c)(152-5c)}.
\]
At $c = 13$ (self-dual): $\mathfrak{Q}(13) = 10/(13 \cdot 87) =
10/1131$. The complementarity of the quartic shadow across the
Koszul involution is
the first nonlinear witness of the duality between boundary and
line sectors.
\end{computation}

%====================================================================
% MOVEMENT V: THE PHYSICS EMERGES
%====================================================================

\subsection{Movement V: the physics of 3d gravity}
\label{subsec:gravity-physics}

Everything above was derived from the $\lambda$-bracket
$\{T_\lambda T\} = \partial T + 2T\lambda + (c/12)\lambda^3$.
The following shows that, via the physics-bridge theorem and the
Chern--Simons realization, this algebraic package recovers the
three-dimensional Einstein-gravity package with
$\Lambda = -1/\ell^2$.

\subsubsection*{The Chern--Simons origin}

Three-dimensional gravity with $\Lambda < 0$ is equivalent to
$SL(2,\R) \times SL(2,\R)$ Chern--Simons at level
$k = \ell/(4G)$, $c = 6k = 3\ell/(2G)$
(Ach\'ucarro--Townsend, Witten). The dreibein $e^a$ and spin
connection $\omega^a$ combine into $A_\pm = \omega \pm e/\ell$;
flat connections $F_\pm = 0$ are constant-curvature geometries.

\begin{theorem}[Brown--Henneaux; \ClaimStatusProvedElsewhere]
\label{thm:brown-henneaux}
\index{Brown--Henneaux central charge|textbf}
The asymptotic symmetry algebra of one $SL(2,\R)$ Chern--Simons
factor at level~$k$ on $\R_+ \times \C$ is $\mathrm{Vir}_c$,
$c = 6k$.  Full AdS$_3$ gravity has the two chiral factors
$SL(2,\R)_+\times SL(2,\R)_-$ and hence two Virasoro copies.
\end{theorem}

\begin{proof}
The boundary condition $A_z|_{t=0} = J_- + T(z)\,J_+$
(Fefferman--Graham asymptotics) has residual gauge
$g = \exp(\epsilon\,J_+)$ acting by
$\delta_\epsilon T = \epsilon' T + 2\epsilon T' +
(c/12)\epsilon'''$, the Virasoro coadjoint action with
central charge $c = 6k$. The CS symplectic form induces
the Poisson bracket
$\{T(z), T(w)\}_{\mathrm{PB}} = (c/2)\delta'''(z-w) +
2T(w)\delta'(z-w) + T'(w)\delta(z-w)$,
which is~\eqref{eq:gravity-input} in distribution form.
\end{proof}

\begin{remark}[Brown--Henneaux read through the thesis]
\label{rem:brown-henneaux-from-thesis}
\index{Brown--Henneaux central charge!thesis reading}
\index{unifying thesis!Brown--Henneaux reading}
The Brown--Henneaux formula $c = 3\ell/(2G_N)$
(Theorem~\ref{thm:brown-henneaux}) admits a compact bookkeeping
through the unifying thesis
$A \mapsto \Zder^{\mathrm{ch}}(A)$. For $A = \mathrm{Vir}_c$,
$\kappa(A) = c/2$, so the combination $2\kappa(A)$
equals the boundary central charge appearing in
bulk-boundary observables. The dimensional input
$c = 6k$, $k = \ell/(4G_N)$ is the Ach\'ucarro--Townsend--Witten
Chern--Simons presentation of 3d gravity and is taken from
that source, not derived from the bar complex; the thesis
does not produce the coupling to $G_N$ on its own. What the
thesis does deliver is a uniform re-expression of every
holographic observable (Cardy degeneracy, BTZ entropy, genus
tower) as a $\kappa$-polynomial, using the single identification
$\kappa = c/2$ to propagate the Brown--Henneaux value through
the bar-complex machinery. In particular, this remark is
\emph{not} a derivation of Brown--Henneaux from Koszul duality;
it is an interface observation that collects the chiral
curvature $\kappa$ and the physics constant $c = 3\ell/(2G_N)$
into a single notational track.
\end{remark}

\begin{remark}[Brown--Henneaux through the thesis lens]
\label{rem:brown-henneaux-thesis}
Brown--Henneaux is a semiclassical theorem
(Theorem~\ref{thm:brown-henneaux}): a classical calculation
on $SL(2,\R)$ Chern--Simons produces the Virasoro charge with
$c = 3\ell/(2G_N)$. The thesis does not supplant that
calculation; it reorganizes the bookkeeping. With
$\kappa(\mathrm{Vir}_c) = c/2$ the boundary central charge
tracks the chiral curvature, so that once Brown--Henneaux
has fixed $c$ in terms of $\ell/G_N$ the rest of the
holographic dictionary is parametrized by the single scalar
$\kappa$. The thesis supplies a uniform language for the
bar-complex consequences of that value; it does not derive
the Brown--Henneaux value itself.
\end{remark}

\subsubsection*{Physics-bridge verification for gravity}

\begin{theorem}[Gravitational MC element; \ClaimStatusConditional]
\label{thm:gravity-mc}
\index{universal MC element!3d!gravitational}
$SL(2,\R)$ Chern--Simons theory at level~$k$ on $\R_+ \times \C$
lies in the scope of Theorem~\ref{thm:physics-bridge}. The resulting
logarithmic $\SCchtop$-algebra determines an MC element
$\alpha_{\mathrm{grav}} \in \mc(\gSC_T)$ whose faces are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item closed face $= \mathrm{Vir}_c$,
\item open face $= $ abstract line-side package
 \textup{(Theorem~\ref{thm:lines_as_modules})},
\item spectral $R$-matrix $= $ abstract line-side braiding,
\item genus face $= \Theta_{\mathrm{Vir}_c}$,
\item PVA descent $= \{T_\lambda T\}$.
\end{enumerate}
Items \textup{(i)--(v)} are proved unconditionally at the abstract
level. The concrete identification of the open face with
$\mathrm{Vir}_{26-c}$-modules and of the spectral $R$-matrix with
the Virasoro fusion kernel is conjectural
\textup{(Remark~\ref{rem:gravity-mc-scope})}.
\end{theorem}

\begin{proof}
The gauge-fixed BV-BRST complex of Chern--Simons theory is cubic in
$A$, so the one-loop finiteness input of Theorem~\ref{thm:physics-bridge}
holds by power counting. Its propagator is
$K(t,z) = \Theta(t)/(2\pi z)$, which has the required meromorphic
holomorphic behavior and ordered topological dependence. The
interaction vertices are polynomial, so the renormalized
configuration-space integrals are precisely of the type covered by the
bridge theorem. Hence the theory defines a logarithmic
$\SCchtop$-algebra. Each listed projection of
$\alpha_{\mathrm{grav}}$ was computed in Movements~I--IV\@.
The abstract line-side package exists by
Theorem~\ref{thm:lines_as_modules}; its braiding is the abstract
spectral $R$-matrix of the bar complex.
\end{proof}

\begin{remark}[Scope: abstract vs.\ concrete line-side identifications]
\label{rem:gravity-mc-scope}
The open face and spectral $R$-matrix in
Theorem~\ref{thm:gravity-mc} are proved at the \emph{abstract}
level: the line-side package exists as the open-colour $E_1$-module
category of the bar complex, and the braiding is its abstract
spectral $R$-matrix. The \emph{concrete} identification of this
package with highest-weight $\mathrm{Vir}_{26-c}$-modules and of the
braiding with the Virasoro fusion kernel is conjectural; see
Remark~\ref{rem:gravity-line-virasoro-realization} and
Conjecture~\ref{conj:gravity-line-identification}.
\end{remark}

\subsubsection*{BTZ black holes as MC deformations}

\begin{definition}[BTZ deformation]
\label{def:btz-deformation}
\index{BTZ black hole!as MC deformation}
A BTZ black hole of mass~$M$ and angular momentum~$J$ is a MC
deformation $\delta\alpha \in \gSC_T$ of $\alpha_{\mathrm{grav}}$,
satisfying $D_{\alpha_{\mathrm{grav}}}(\delta\alpha) = 0$,
corresponding to shifted cylinder energies
\[
\Delta_\pm := L_0^\pm-\frac{c}{24}
= \frac{M\ell \pm J}{2}.
\]
If $h_\pm$ denote highest weights, then
$h_\pm=\Delta_\pm+c/24$.
\end{definition}

\subsubsection*{The Cardy formula: partition function and modular $S$-transform}

The genus-$1$ MC element $\Theta^{(1)}$ produces the boundary
partition function. Write $q = e^{2\pi i\tau}$ for the modular
parameter of the boundary torus. The categorical trace gives
\begin{equation}\label{eq:gravity-Z1}
Z_1(\tau)
\;=\;
\Tr_{\mathrm{Vir}_c}\!\left(q^{L_0 - c/24}\right)
\;=\;
\frac{q^{-c/24}}{\prod_{n=2}^{\infty}(1-q^n)},
\end{equation}
the product starting at $n = 2$ because $\mathrm{Vir}_c$ has no
weight-$1$ states. The full partition function counting all states
at inverse temperature $\beta = 2\pi\,\mathrm{Im}\,\tau$ is
\begin{equation}\label{eq:gravity-Z-full}
Z(\tau,\bar\tau)
\;=\;
\sum_{h,\bar h}
d(h,\bar h)\,q^{h - c/24}\,\bar q^{\bar h - c/24}.
\end{equation}
Modular invariance $Z(-1/\tau, -1/\bar\tau) = Z(\tau,\bar\tau)$
and vacuum dominance in the high-temperature limit give
\begin{equation}\label{eq:gravity-vacuum-dominance}
Z(\tau,\bar\tau)
\;\sim\;
\exp\!\left(
 \frac{\pi c}{12}\,\mathrm{Im}(-1/\tau)
\right)
\qquad (\mathrm{Im}\,\tau \to 0^+).
\end{equation}
In the bar-complex language, the $S$-transform acts on
$\Theta_{\mathrm{grav}}$ by exchanging the two boundary cycles of
the genus-$1$ bordered FM compactification; vacuum dominance is
the statement that the degree-$0$ component
$\Theta^{(1)}_{n=0} = \kappa\cdot\omega_1$ controls the
exponential growth of states.

\subsubsection*{Saddle-point extraction and the Cardy formula}

The degeneracy $d(\Delta_+)$ at large shifted energy is extracted by inverse Laplace
transform from~\eqref{eq:gravity-vacuum-dominance}. The
saddle-point of $f(\tau) = \pi c/(12\tau) + 2\pi\tau\Delta_+$
is at
\begin{equation}\label{eq:gravity-saddle}
\tau_*
\;=\;
i\sqrt{\frac{c}{24\Delta_+}}
\;\approx\;
i\sqrt{\frac{c}{24\Delta_+}}
\qquad (\Delta_+ \gg c),
\end{equation}
giving $f(\tau_*) \approx 2\pi\sqrt{c\Delta_+/6}$.

\begin{conjecture}[Cardy formula from the bar complex;
\ClaimStatusConjectured]
\label{conj:gravity-cardy}
\label{conj:cardy-mc}
\index{Cardy formula!from bar complex|textbf}
\index{BTZ black hole!Cardy formula}
The asymptotic entropy of the Virasoro bar complex at large
shifted conformal energy is
\begin{equation}\label{eq:gravity-cardy}
\boxed{
S_{\mathrm{Cardy}}
\;=\;
2\pi\sqrt{\frac{c\,\Delta_+}{6}}
\;+\;
2\pi\sqrt{\frac{c\,\Delta_-}{6}}.
}
\end{equation}
This is the logarithmic growth rate of MC deformations
of $\alpha_{\mathrm{grav}}$ at shifted energies
$(\Delta_+,\Delta_-)$.
\end{conjecture}

\begin{remark}[Conditional derivation of the Cardy formula]
\label{rem:cardy-derivation}
The derivation rests on three bar-complex inputs:
\begin{enumerate}[label=(\roman*)]
\item The curvature $\kappa(\mathrm{Vir}_c) = c/2$ from the
 genus-$1$ self-loop, which determines
 $\Theta^{(1)}_{n=0} = \kappa\cdot\omega_1$ and hence the
 vacuum energy $-c/24$.
\item The modular invariance of $Z(\tau,\bar\tau)$, which
 follows from the consistency of the genus-$1$ MC equation
 on the moduli stack $\cM_{1,1}$: the modular group acts as
 autoequivalences of the bordered FM compactification, and
 the MC element is invariant under this action.
\item The saddle-point at
 $\tau_* = i\sqrt{c/(24\Delta_+)}$~\eqref{eq:gravity-saddle},
 which follows from the analytic structure of the
 $S$-channel expansion.
\end{enumerate}
All three inputs are determined by the single datum
$\kappa = c/2$, itself determined by the quartic OPE pole in
$\{T_\lambda T\}$. The Cardy formula is thus a consequence of
the curvature of the Virasoro bar complex. The conjectural
step is the passage from algebraic modular invariance of the
MC element to the analytic modular invariance of the
partition function needed for the saddle-point extraction.
\end{remark}

\begin{remark}[Cardy growth rate in $\kappa$-variables]
\label{rem:cardy-thesis}
\index{Cardy formula!kappa variables}
The Cardy growth rate can be rewritten using
$\kappa(\mathrm{Vir}_c) = c/2$: the saddle contribution
$2\pi\sqrt{c\Delta_+/6}$ is
$2\pi\sqrt{\kappa\Delta_+/3}$. This rewriting is a notational
move, not a derivation: the Cardy formula itself is
Conjecture~\ref{conj:gravity-cardy} at the bar-complex level
(the conditional derivation is recorded in
Remark~\ref{rem:cardy-derivation}, whose analytic step
remains conjectural), and the thesis supplies no independent
input beyond the $\kappa$-identification. What the
$\kappa$-form does record is that any class-$\mathbf{M}$ VOA
admitting a Cardy-type asymptotic under the same conjectural
analytic inputs would produce the analogous growth rate
governed by its own curvature; the specific Virasoro
constants are fixed by Brown--Henneaux
(Theorem~\ref{thm:brown-henneaux}), not by the thesis.
\end{remark}

\subsubsection*{BTZ entropy from the bar complex}

\begin{conjecture}[BTZ entropy; \ClaimStatusConjectured]
\label{conj:gravity-btz-entropy}
\index{BTZ black hole!entropy|textbf}
\index{Bekenstein--Hawking entropy!from bar complex}
The Bekenstein--Hawking entropy of the BTZ black hole is
\begin{equation}\label{eq:gravity-btz-entropy}
\boxed{
S_{\mathrm{BTZ}}
\;=\;
\frac{2\pi r_+}{4G}
\;=\;
2\pi\sqrt{\frac{c\,\Delta_+}{6}}
\;+\;
2\pi\sqrt{\frac{c\,\Delta_-}{6}},
}
\end{equation}
where $c = 3\ell/(2G)$ is the Brown--Henneaux central charge
\textup{(}Theorem~\textup{\ref{thm:brown-henneaux})},
$\Delta_\pm=L_0^\pm-c/24$ are the shifted cylinder energies,
and $r_+$ is the outer horizon radius.
Equivalently, $S_{\mathrm{BTZ}} =
2\pi\sqrt{\kappa\Delta_+/3}
+ 2\pi\sqrt{\kappa\Delta_-/3}$ with $\kappa = c/2$.
\end{conjecture}

\begin{remark}[Conditional derivation of the BTZ entropy]
\label{rem:btz-derivation}
Assuming Conjecture~\ref{conj:gravity-cardy}, substitute
$c = 3\ell/(2G)$,
$\Delta_+ = (M\ell+J)/2$,
$\Delta_- = (M\ell-J)/2$ into the Cardy
formula~\eqref{eq:gravity-cardy}:
\begin{align*}
S_{\mathrm{BTZ}}
&\;=\;
2\pi\sqrt{\frac{3\ell}{2G}\cdot\frac{M\ell+J}{12}}
\;+\;
2\pi\sqrt{\frac{3\ell}{2G}\cdot\frac{M\ell-J}{12}}
\\[4pt]
&\;=\;
\frac{2\pi}{8G}\bigl((r_+ + r_-) + (r_+ - r_-)\bigr)
\;=\;
\frac{2\pi r_+}{4G}.
\end{align*}
In terms of the horizon radii
$M=(r_+^2+r_-^2)/(8G\ell^2)$ and
$J=r_+r_-/(4G\ell)$, equivalently
$(r_+\pm r_-)^2=8G\ell(M\ell\pm J)$.
Thus the Cardy expression gives the standard
Bekenstein--Hawking formula
$S = 2\pi r_+/(4G) = \mathrm{Area}/(4G)$ for the
one-dimensional horizon.
\end{remark}

\begin{remark}[BTZ entropy in $\kappa$-variables]
\label{rem:btz-thesis}
\index{BTZ black hole!kappa variables}
Conditional on Conjecture~\ref{conj:gravity-cardy} and on
Brown--Henneaux (Theorem~\ref{thm:brown-henneaux}), the BTZ
entropy can be reassembled in $\kappa$-variables. A BTZ
black hole is declared to be an MC deformation
$\delta\alpha \in \gSC_T$ of $\alpha_{\mathrm{grav}}$
(Definition~\ref{def:btz-deformation}). Substituting
$c = 2\kappa(\mathrm{Vir}_c)$ and the Brown--Henneaux value
$c = 3\ell/(2G_N)$ into the Cardy weight reproduces the area
law, as worked out in Remark~\ref{rem:btz-derivation}. The
area-law coefficient $1/(4G_N)$ is \emph{not} fixed by the
chiral curvature: it is the Bekenstein--Hawking coefficient,
external to the bar complex, and appears here only because
it was already present in the Brown--Henneaux input. What
the $\kappa$-reformulation does deliver is a notational
alignment between the boundary curvature and the bulk area
law, under the assumption that the Cardy conjecture and
Brown--Henneaux both hold in their usual forms.
\end{remark}

\subsubsection*{Verdier duality and the modular $S$-transform}

The Koszul involution $c \mapsto 26-c$ (Verdier duality
$\mathbb{D}$, Theorem~\ref{thm:gravity-verdier-intertwining})
and the modular $S$-transform $\tau \mapsto -1/\tau$ are
independent operations acting on different aspects of the MC
element.

\begin{proposition}[Commutativity of $\mathbb{D}$ and $S$;
\ClaimStatusProvedHere]
\label{prop:gravity-D-S-commute}
\index{Verdier duality!modular $S$-transform commutativity}
\index{modular $S$-transform!Verdier commutativity}
The Verdier involution $\mathbb{D}$ and the modular
$S$-transform commute on genus-$1$ MC elements:
\[
S \circ \mathbb{D}(\Theta_{\mathrm{Vir}_c}^{(1)}(\tau))
\;=\;
\mathbb{D} \circ S(\Theta_{\mathrm{Vir}_c}^{(1)}(\tau))
\;=\;
\Theta_{\mathrm{Vir}_{26-c}}^{(1)}(-1/\tau).
\]
\end{proposition}

\begin{proof}
$\mathbb{D}$ acts on algebraic data
($c \mapsto 26-c$, $\kappa \mapsto (26-c)/2$); $S$ acts on the
modular parameter ($\tau \mapsto -1/\tau$). They act on different
variables and hence commute.
$\mathbb{D}(\Theta_{\mathrm{Vir}_c}^{(1)}(\tau))
= \Theta_{\mathrm{Vir}_{26-c}}^{(1)}(\tau)$
(Theorem~\ref{thm:gravity-verdier-intertwining}(ii));
applying $S$ gives
$\Theta_{\mathrm{Vir}_{26-c}}^{(1)}(-1/\tau)$.
The other order:
$S(\Theta_{\mathrm{Vir}_c}^{(1)}(\tau))
= \Theta_{\mathrm{Vir}_c}^{(1)}(-1/\tau)$;
applying $\mathbb{D}$ gives the same result.
\end{proof}

The commutativity produces a paired Cardy formula for the Koszul
pair $(\mathrm{Vir}_c, \mathrm{Vir}_{26-c})$ at shifted energy
$\Delta$:
$S_{\mathrm{Cardy}}(\mathrm{Vir}_c;\,\Delta)
+ S_{\mathrm{Cardy}}(\mathrm{Vir}_{26-c};\,\Delta)
= 2\pi\sqrt{c\Delta/6} + 2\pi\sqrt{(26-c)\Delta/6}$.
At the self-dual point $c = 13$, the two terms are equal and
the total counting capacity is maximized:
$\sqrt{c} + \sqrt{26-c} \le 2\sqrt{13}$
(by concavity of $\sqrt{\cdot}$). At $c = 26$, the dual
contribution vanishes (the Witt algebra has $c = 0$).
This is the entropic shadow of the scalar complementarity
$\varkappa := \kappa + \kappa' = 13$
(Proposition~\ref{prop:gravity-complementarity-constant}), distinct
from the Trinity ghost-charge conductor
$K(\Vir) := c + c^! = 26 = -c_{\mathrm{ghost}}(\BRST_{\Vir})$; the two
are related by $\varkappa = \varrho_{\Vir}\cdot K$ with
$\varrho_{\Vir} = 1/2$.

\subsubsection*{Anomaly completion}

At genus $g \ge 1$, the MC element acquires anomaly corrections via
the transgression algebra $B_\Theta$ of
Chapter~\ref{app:anomaly-completed-topological-holography}.
The secondary anomaly class
\[
u \;=\; \eta^2 \;=\; \kappa_{\mathrm{eff}} \cdot \omega_g
\;=\; \tfrac{c-26}{2} \cdot \omega_g
\;\in\; H^2(\overline{\mathcal{M}}_g)
\]
controls the genus-$g$ Clifford completion
$\mathfrak{G}_g(B_\Theta)$: for $u \neq 0$
(equivalently $c \neq 26$) the Clifford algebra is
nondegenerate, Morita trivial, and the effective scalar genus tower
$F_g^{\mathrm{eff}} = \kappa_{\mathrm{eff}}
\int_{\overline{\mathcal{M}}_g}\lambda_g$ is nontrivial at every genus. At $c = 26$ the class $u$ vanishes in the effective scalar
model, the Clifford relation
$\{\alpha_i,\beta_j\} = \delta_{ij}\eta^2$ degenerates to
anticommutativity, and the scalar-specialized genus-$g$ completion
degenerates to the exterior algebra
$\Lambda^{2g+1} \otimes B/(\Theta_{\mathrm{eff}}^{\min})$.
This is the Clifford/exterior dichotomy of the effective scalar
model: the distinction between $c \neq 26$ and $c = 26$ is encoded in
whether the single class $u \in H^2(\overline{\mathcal{M}}_g)$
vanishes. It does not by itself identify the full coupled
transgression algebra with this scalar specialization.
The full anomaly-completed MC element
$\hat\alpha_{\mathrm{grav}} \in \mc(\hat\gSC_T)$ packages
the gravitational genus tower into a single object.

\begin{remark}[$\Delta_5$ as the scalar K3 automorphic shadow]
\label{rem:3dqg-delta5-11d-sugra}%
\index{11D supergravity!twisted!K3$\times T^2$}%
\index{M5-brane!24 at Kodaira I$_1$}%
\index{Igusa cusp form!$\Delta_5$!K3 automorphic shadow}%
\index{paramodular form!weight 5}%
The secondary anomaly class $u = \kappa_{\mathrm{eff}}\cdot\omega_g$
of the scalar-specialised Virasoro model is not identical to the
K3$\times T^2$ Borcherds denominator.  The common scalar target is the
weight-$5$ Gritsenko--Nikulin form
\[
\Delta_5
\;\in\;
H^0\!\bigl(\overline{\cA}_2,\;\cM^{\otimes 5}\bigr)
\]
(with Maass character on $\mathrm{Sp}_4(\Z)$), whose square is the
Igusa cusp form $\Phi_{10}$.  In the K3 BPS-counting frame the
Borcherds product of the K3 elliptic genus gives
\[
\Phi_{10}(Z)
\;=\;
\Delta_5(Z)^2,
\qquad
Z_{\mathrm{BPS}}^{K3\times E}(Z)
\;=\;
\Phi_{10}(Z)^{-1}.
\]
This is a theorem of the automorphic and BPS-index lane
\cite{GritsenkoNikulin1998,Borcherds1998,
DijkgraafMooreVerlindeVerlinde1997}.  The further statement that the
K3$\times E$ Hall object supplies the \emph{chain-level}
$\SCchtop$ gravity-line boundary algebra is not a consequence of the
scalar product.  It is the Hall--Borcherds comparison residual recorded
in Conjecture~\ref{conj:gravity-line-hall-borcherds-comparison}.
\end{remark}

\subsubsection*{Celestial transfer}

The boundary PVA~\eqref{eq:gravity-input} descends, via
$\widetilde{T}(w) = \int_0^\infty T(t,w)\,dt$, to the binary
Virasoro sector of the celestial soft algebra, with integrated-stress-tensor OPE:
\[
\widetilde{T}(w_1)\,\widetilde{T}(w_2)
\;\sim\;
\frac{c/2}{(w_1 - w_2)^4}
+ \frac{2\widetilde{T}(w_2)}{(w_1 - w_2)^2}
+ \frac{\partial\widetilde{T}(w_2)}{w_1 - w_2}.
\]
The celestial stress tensor thus generates the binary Virasoro sector
of the resulting celestial soft algebra, with the same Virasoro OPE at
$c = 3\ell/(2G)$. This binary Virasoro sector is
the leading-soft / supertranslation sector of the
BMS package at null
infinity.

%====================================================================
% THE GRAVITATIONAL PRIMITIVE PACKAGE
%====================================================================

\subsection{The gravitational primitive package}
\label{subsec:gravity-primitive-package}
\index{primitive package!gravitational|textbf}
\index{Virasoro!primitive package|textbf}
\index{gravity!open/closed package}

Movements I--V assembled the gravitational Koszul data
from the single input~\eqref{eq:gravity-input}.
The organization of the full output into the six-fold primitive
package
$(\cC_{\mathrm{grav}}^{\mathrm{op}},\;
b_{\mathrm{grav}},\;
A = \mathrm{Vir}_c,\;
Z,\; \Theta_{\mathrm{grav}},\; \operatorname{Tr})$
of Volume~I, Theorem~\ref*{V1-thm:thqg-swiss-cheese}.
The result is the worked example that contrasts most sharply
with the Chern--Simons package of
\S\ref{subsec:cs-primitive-package}: where CS has strict
$\Ainf$ associativity, trivial coproduct obstruction, and
finite shadow depth, gravity has an infinite $\Ainf$ tower,
strictly primitive coproduct, and infinite shadow depth.
The quartic OPE pole is the single algebraic datum
that produces all three.

\subsubsection*{Boundary algebra}

\begin{equation}\label{eq:grav-boundary-algebra}
A \;=\; \mathrm{Vir}_c.
\end{equation}
The single generator $T(z)$ has conformal weight~$2$.
The $\lambda$-bracket~\eqref{eq:gravity-input} is
$\{T_\lambda T\} = \partial T + 2T\lambda + (c/12)\lambda^3$.
The highest pole is quartic ($\lambda^3$ in the
$\lambda$-bracket, $(z-w)^{-4}$ in the OPE), which forces
all three distinguishing features of the gravitational
package.

The modular characteristic is
\begin{equation}\label{eq:grav-kappa-intrinsic}
\kappa(\mathrm{Vir}_c) \;=\; \frac{c}{2}.
\end{equation}
This is the \emph{intrinsic} curvature of the Virasoro bar
complex. The effective-scalar gravitational partition function uses the
\emph{effective} curvature $\kappa_{\mathrm{eff}} = (c-26)/2$
after ghost subtraction
(Remark~\ref{rem:gravity-kappa-vs-kappa-eff}).

\subsubsection*{$\Ainf$ structure: genuinely infinite}

The $\lambda$-bracket is non-associative: the associator
$A_3 \ne 0$ (equation~\eqref{eq:gravity-associator}).
The compensating ternary operation $m_3 \ne 0$ forces
$m_4 \ne 0$ via the Stasheff identity at degree~4,
and by induction:
\begin{equation}\label{eq:grav-all-mk}
m_k \;\ne\; 0
\qquad
\text{for all } k \ge 3 \text{ and generic } c.
\end{equation}
The shadow depth is $r_{\max} = \infty$ (class~$\mathbf{M}$,
mixed). The quartic contact invariant
$\mathfrak{Q}^{\mathrm{contact}}_{\mathrm{Vir}}
= 10/[c(5c+22)] \ne 0$ obstructs
termination at degree~4.

\subsubsection*{Open category (primitive)}

\begin{definition}[Gravitational line category]
\label{def:grav-open-category}
\index{gravitational line!dg-category}
The open-sector factorization dg-category of 3d gravity is
\begin{equation}\label{eq:grav-open-category}
\cC_{\mathrm{grav}}^{\mathrm{op}}
\;=\;
\bigl(
 \text{boundary-condition-preserving perturbations of
 $SL(2,\R)$ CS}
\bigr).
\end{equation}
The vacuum boundary object $b_{\mathrm{grav}}$ is the
Brown--Henneaux boundary condition
$A_z|_{t=0} = J_- + T(z)\,J_+$.
Its endomorphism algebra is
$\End(b_{\mathrm{grav}}) = \mathrm{Vir}_c$.
\end{definition}

The gravitational line category is far less understood than
its gauge-theory counterpart.
Under the conjectural Virasoro realization
(Conjecture~\ref{conj:gravity-line-identification}), the category of line
operators is modeled by modules for the Koszul dual
$\mathrm{Vir}_{26-c}$.
Conical defects of angular deficit $2\pi(1 - \sqrt{1 - 8Gh})$
are read as highest-weight modules $M_h$ of
$\mathrm{Vir}_{26-c}$ at weight~$h$.
At $c \gg 26$ (semiclassical gravity, $G \to 0$), the dual
central charge $c' = 26 - c \ll 0$ places the line
category deep in the strongly coupled regime: line operators
are modeled by modules for a Virasoro algebra at large negative
central charge, the algebraic incarnation of UV/IR mixing in
AdS$_3$/CFT$_2$.

The physical description above motivates a precise algebraic
formulation.

\begin{definition}[Gravitational open-sector category]
\label{def:grav-open-algebraic}
\index{gravitational open-sector category|textbf}
The \emph{gravitational open-sector category} is
\begin{equation}\label{eq:grav-open-algebraic}
\cC_{\mathrm{grav}}^{\mathrm{op}}
\;=\;
\bigl(\mathrm{Perf}\text{-}\mathrm{Vir}_c,\;
\Delta_z^{\mathrm{prim}},\; r(z)\bigr):
\end{equation}
the dg-category of perfect $\mathrm{Vir}_c$-modules equipped
with the primitive spectral coproduct
$\Delta_z(x) = \tau_z(x) \otimes 1 + 1 \otimes x$ and the
$r$-matrix twist
$r(z) = (c/2)/z^3 + 2T/z$.
The dg structure on $\mathrm{Perf}\text{-}\mathrm{Vir}_c$ is
inherited from the vertex algebra differential: the Hom complexes
carry the differential $[Q,{-}]$ where $Q$ is the BRST operator of
the $\mathrm{Vir}_c$-module category, and composition is the
standard composition of $\mathrm{Vir}_c$-module maps.
\end{definition}

\begin{proposition}[\ClaimStatusConditional for \textup{(i)--(iii), (v)--(vi)}; item \textup{(iv)} is Conjecture~\textup{\ref{conj:gravity-line-identification}}]
\label{prop:grav-open-six-requirements}
Definition~\textup{\ref{def:grav-open-algebraic}} satisfies all
six requirements of the gravitational primitive package:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\End(b) = \mathrm{Vir}_c$ for the vacuum generator
 $b = \mathrm{Vir}_c$.
\item $\Zder \simeq \C[\![c]\!]$ by
 Morita: $\HH^*(\mathrm{Perf}\text{-}A) = \HH^*(A,A)$.
\item Primitive coproduct by construction.
\item $\cC_{\mathrm{line}} \simeq
 \mathrm{Vir}_{26-c}\text{-mod}$ on the Koszul locus
 \textup{(}conjectural,
 Conjecture~\textup{\ref{conj:gravity-line-identification})}.
\item Annulus trace
 $= \mathrm{Tr}_{\mathrm{Vir}_c}(q^{L_0-c/24})$
 \textup{(}the vacuum character\textup{)}.
\item Genus tower from the $\hat{A}$-genus via the MC element
 $\Theta_{\mathrm{grav}}$.
\end{enumerate}
The monoidal structure distinguishes gravity from gauge theory:
the tensor product is trivial \textup{(}primitive
coproduct\textup{)}, with all interaction encoded in the
$r$-matrix braiding.
\end{proposition}

\begin{proof}
Items~(i)--(iii) are immediate from the definition.
For~(i), the vacuum boundary object
$b_{\mathrm{grav}} = \mathrm{Vir}_c$ is a compact generator of
$\mathrm{Perf}\text{-}\mathrm{Vir}_c$, and the endomorphism
algebra is $\End(b_{\mathrm{grav}}) = \mathrm{Vir}_c$ by
construction.
For~(ii), Morita invariance of Hochschild cohomology gives
$\HH^*(\mathrm{Perf}\text{-}\mathrm{Vir}_c)
\simeq \HH^*(\mathrm{Vir}_c, \mathrm{Vir}_c)$,
which is the chiral derived center; its zeroth cohomology is
$\C[\![c]\!]$ since the only central parameter is~$c$.
Item~(iii) holds by the definition of $\Delta_z^{\mathrm{prim}}$.
Item~(iv) is the content of
Conjecture~\ref{conj:gravity-line-identification}: on the Koszul
locus, the category of line operators
$\cC_{\mathrm{line}} \simeq \mathrm{Vir}_{26-c}\text{-mod}$
as a consequence of Koszul duality
$\mathrm{Vir}_c^! = \mathrm{Vir}_{26-c}$
(equation~\eqref{eq:grav-koszul-dual}).
For~(v), the annulus trace on the vacuum module reproduces the
Virasoro vacuum character
$\chi_0(\tau) = \mathrm{Tr}_{\mathrm{Vir}_c}(q^{L_0 - c/24})$,
which is the genus-one closed-string partition function restricted
to the identity sector.
For~(vi), the genus tower is assembled in
Theorem~\ref{thm:gravity-mc-primitive-package} below from the
MC element $\Theta_{\mathrm{grav}}$ via the $\hat{A}$-genus
mechanism of Volume~I.

The primitive coproduct
$\Delta_z(x) = \tau_z(x) \otimes 1 + 1 \otimes x$ is the key
structural distinction from the Chern--Simons primitive package
(\S\ref{subsec:cs-primitive-package}), where the coproduct
carries non-trivial higher terms.
In the gravitational setting, the tensor product of line operators
is trivial at the coalgebraic level; all non-trivial structure
resides in the $r$-matrix braiding
$r(z) = (c/2)/z^3 + 2T/z$, whose cubic pole reflects the
quartic OPE of the Virasoro algebra (one pole order absorbed by
the $\mathrm{d}\log$ kernel,).
\end{proof}

\subsubsection*{Koszul dual}

\begin{equation}\label{eq:grav-koszul-dual}
\mathrm{Vir}_c^!
\;=\;
\mathrm{Vir}_{26-c}.
\end{equation}
Self-duality at $c = 13$:
$\mathrm{Vir}_{13}^! = \mathrm{Vir}_{13}$.
The complementarity relation (Theorem~C of Volume~I):
\[
\kappa(\mathrm{Vir}_c) + \kappa(\mathrm{Vir}_{26-c})
\;=\;
\frac{c}{2} + \frac{26-c}{2}
\;=\; 13.
\]
This is \emph{not} zero: the Virasoro involution
$c \mapsto 26 - c$ is anti-symmetric around $c = 13$,
not around $c = 0$.
The constant $13$ is the Virasoro
complementarity invariant.

\subsubsection*{Bulk (derived center)}

The chiral derived center of $\mathrm{Vir}_c$ was computed
in \S\ref{subsec:gravity-koszul}:
\begin{equation}\label{eq:grav-derived-center}
\mathcal{Z}^{\mathrm{der}}_{\mathrm{ch}}(\mathrm{Vir}_c)
\;\simeq\;
\C[\![c]\!].
\end{equation}
Explicitly:
$\mathcal{Z}^0 = \C$ (the identity),
$\mathcal{Z}^1 = 0$ (all derivations inner),
$\mathcal{Z}^2 = \C \cdot \Theta_c$ (the Gel'fand--Fuchs
$2$-cocycle),
$\mathcal{Z}^{n \ge 3} = 0$ (generically).
The bulk-to-boundary map
$\beta_B \colon \mathcal{Z}^2 \to \mathrm{Vir}_c$
sends $\Theta_c$ to the stress tensor via the conformal
Ward identity~\eqref{eq:gravity-bulk-boundary}.
3d gravity has one adjustable parameter: the cosmological
constant $\Lambda = -1/\ell^2$, encoded by
$c = 3\ell/(2G)$.
There are no local bulk degrees of freedom.

\subsubsection*{Classical $r$-matrix and coproduct}

The collision residue of the bar differential (the $d\log$ kernel
absorbs one pole) gives the gravitational $r$-matrix:
\begin{equation}\label{eq:grav-r-matrix-package}
r^{\mathrm{coll}}_{\mathrm{grav}}(z)
\;=\;
\frac{c/2}{z^3} \;+\; \frac{2T}{z}.
\end{equation}
The full Laplace kernel is
$r^L(z) = \partial T/z + 2T/z^2 + (c/2)/z^4$.
The $r$-matrix has a \emph{cubic} leading pole ($z^{-3}$),
one order below the quartic OPE pole,
reflecting the $d\log$ kernel of the bar construction.

The transferred coproduct is \emph{strictly primitive}
(Proposition~\ref{prop:coproduct-degree2-vanishing}):
\begin{equation}\label{eq:grav-coproduct-primitive}
\Delta_z^{\mathrm{Vir}}(T)
\;=\;
\tau_z(T) \otimes 1 \;+\; 1 \otimes T.
\end{equation}
All higher-degree coproduct components vanish:
$\Delta_{z,n}^{\mathrm{Vir}} = 0$ for $n \ge 2$.
The proof
(\S\ref{subsec:ds-hpl-transfer}) uses the ghost-number
obstruction: the DS homotopy $h$ has ghost-number degree
$-1$, and the projection $p \otimes p$ kills all
ghost-number-$(-1)$ elements.

The strict primitivity of the gravitational coproduct means that \emph{gravity
does not produce particles, only braids}.
A graviton propagating through a region does not
split into constituent gravitons (no Clebsch--Gordan decomposition):
the only nontrivial structure is the $r(z)$-twist on the
target product, encoding the braiding of line operators.
All gravitational interactions are encoded in the twist,
not in the coproduct.
This contrasts with CS gauge theory
(\S\ref{subsec:cs-primitive-package}), where the coproduct
is nontrivial, read as gluon splitting.

\subsubsection*{Modular MC element}

\begin{theorem}[Gravitational MC element: primitive package;
\ClaimStatusProvedHere]
\label{thm:gravity-mc-package}
\index{universal MC element!gravitational primitive package|textbf}
The full modular MC element of $\mathrm{Vir}_c$ is
\begin{equation}\label{eq:grav-mc-element}
\Theta_{\mathrm{grav}}
\;=\;
\sum_{k \ge 2} \alpha_k
\;+\;
\sum_{g \ge 1}\,
\hbar^g\, \Theta^{(g)},
\end{equation}
where:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\alpha_k = m_k$ for $k \ge 2$ are the genus-$0$
 $\Ainf$ operations from
 Movements~I--II.
 The genus-$0$ MC equation
 $\sum_{k \ge 2} D\alpha_k
 + \frac{1}{2}[\alpha_k, \alpha_\ell] = 0$
 is the system of Stasheff identities at all degrees.
\item $\Theta^{(1)} = \kappa \cdot \eta \otimes \Lambda$
 is the genus-$1$ self-loop with
 $\kappa = c/2$, giving $F_1 = c/48$.
\item $\Theta^{(g)}$ for $g \ge 2$ are the higher-genus
 MC components from the stable-graph expansion, each
 receiving contributions from graphs of all degrees.
 The scalar genus tower is
 $F_g = \kappa \int_{\overline{\mathcal{M}}_g} \lambda_g$
 \textup{(Volume~I, Theorem~D: leading coefficient;
 , since $\mathrm{Vir}_c$ is single-generator;
 multi-weight requires $\delta F_g^{\mathrm{cross}}$,
 cf.~Volume~I, Theorem~\ref*{V1-thm:multi-weight-genus-expansion})}
 by algebraic-family rigidity
 \textup{(Volume~I,
 Theorem~\ref*{V1-thm:algebraic-family-rigidity})}.
\end{enumerate}
The bar-intrinsic construction
$\Theta_{\mathrm{grav}} = D_A - d_0$
\textup{(Volume~I, Theorem~\ref*{V1-thm:mc2-bar-intrinsic})}
guarantees that $\Theta_{\mathrm{grav}}$ satisfies the MC
equation at all genera and all degrees.
The shadow obstruction tower has four named projections:
$\kappa = c/2$ \textup{(degree~$2$)},
$\mathfrak{C} = -c$ \textup{(degree~$3$)},
$\mathfrak{Q} = 10/[c(5c+22)]$ \textup{(degree~$4$)},
and $o_5 \ne 0$ \textup{(degree~$5$, nonvanishing for generic~$c$)}.
\end{theorem}

\begin{proof}
The existence and MC property of $\Theta_{\mathrm{grav}}$ follow
from the bar-intrinsic construction: $D_A^2 = 0$ (Volume~I,
Theorem~\ref*{V1-thm:convolution-d-squared-zero}) implies
$(D_A - d_0)$ is MC.
The genus-$0$ component is the totality of $\Ainf$ operations
$\{m_k\}_{k \ge 2}$, computed in Movement~I\@.
The genus-$1$ component is the self-loop contribution with
$\kappa = c/2$ (Theorem~D of Volume~I).
The higher-genus components are determined by the
stable-graph expansion, with scalar projection
$F_g = \kappa \int_{\overline{\mathcal{M}}_g} \lambda_g$ proved by algebraic-family rigidity (the Virasoro algebra
is a single-generator algebraic family with rational OPE
coefficients, so the uniform-weight theorem applies at all
genera).
The shadow values $\mathfrak{C}$, $\mathfrak{Q}$, $o_5$ are
Volume~I computations
(\S\ref*{V1-subsec:vir-shadow-tower}).
\end{proof}

\subsubsection*{Annulus trace}

\begin{equation}\label{eq:grav-annulus-trace}
\operatorname{Tr}_{\mathrm{grav}}
\;=\;
\int_{S^1} \cC_{\mathrm{grav}}^{\mathrm{op}}
\;\simeq\;
HH_*(\mathrm{Vir}_c).
\end{equation}
The annulus partition function is the Virasoro vacuum character:
\begin{equation}\label{eq:grav-annulus-partition}
Z_{\mathrm{ann}}^{\mathrm{grav}}(q)
\;=\;
\operatorname{tr}_{\mathrm{Vir}_c} q^{L_0 - c/24}
\;=\;
\frac{q^{-c/24}}{\prod_{n=2}^{\infty}(1 - q^n)}.
\end{equation}
The product starts at $n = 2$ (not $n = 1$) because the
Virasoro algebra has a single generator $T$ of conformal
weight~$2$: the state space is spanned by $L_{-n_1} \cdots
L_{-n_k}|0\rangle$ with $n_i \ge 2$.

\subsubsection*{The CS--gravity contrast}

\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lll}
\textbf{Datum} & \textbf{CS (\S\ref{subsec:cs-primitive-package})}
 & \textbf{Gravity} \\
\hline
boundary $A$
 & $V_k(\fg)$ (affine KM)
 & $\mathrm{Vir}_c$ (Virasoro) \\[2pt]
highest pole
 & quadratic ($z^{-2}$)
 & quartic ($z^{-4}$) \\[2pt]
$\Ainf$ tower
 & strict ($m_{k \ge 3} = 0$)
 & infinite ($m_k \ne 0$ all $k$) \\[2pt]
shadow depth
 & $3$ (class $\mathbf{L}$)
 & $\infty$ (class $\mathbf{M}$) \\[2pt]
$r^{\mathrm{coll}}(z)$
 & $k\,\Omega/z$ (simple pole)
 & $(c/2)/z^3 + 2T/z$ (cubic pole) \\[2pt]
$\Delta_z$
 & nontrivial (read as gluon splitting)
 & primitive (read as graviton braiding) \\[2pt]
$\kappa$
 & $\dim\fg(k+h^\vee)/(2h^\vee)$
 & $c/2$ \\[2pt]
$\kappa + \kappa^!$
 & $0$
 & $13$ \\[2pt]
$\mathcal{Z}^0$
 & $\C$
 & $\C$ \\[2pt]
$Z_{\mathrm{ann}}$
 & $q^{-c/24}\prod(1-q^n)^{-\dim\fg}$
 & $q^{-c/24}\prod_{n \ge 2}(1-q^n)^{-1}$
\end{tabular}
\end{center}

The table encodes a single algebraic origin: the number of
$\lambda$-powers in the $\lambda$-bracket.
Affine KM has $\lambda^1$ at most (quadratic pole), giving
strict associativity, finite shadow depth, and a simple-pole
$r$-matrix.
Virasoro has $\lambda^3$ (quartic pole), giving infinite
$\Ainf$ tower, infinite shadow depth, and a cubic-pole
$r$-matrix.
The Drinfeld--Sokolov reduction
(\S\ref{subsec:ds-hpl-transfer}) bridges the two: it takes
the affine Casimir $k\,\Omega/z$ to the gravitational
$(c/2)/z^3 + 2T/z$ by homological perturbation through the
Sugawara nonlinearity.
The ghost-number obstruction that forces
$\Delta_z^{\mathrm{Vir}}$ to be primitive is absent for the
affine coproduct $\Delta_z^{\mathrm{aff}}$, because the
affine generators $J^a$ live in the SDR image while the
Sugawara composite $T$ does not.

%====================================================================
% THE MODULAR OPERAD FOR A-INFINITY-CHIRAL ALGEBRAS
%====================================================================

\begin{conjecture}[Modular operad for $\Ainf$-chiral algebras;
\ClaimStatusConjectured]
\label{conj:modular-operad-ainf-chiral}
\index{modular operad!A-infinity-chiral@$\Ainf$-chiral|textbf}
\index{A-infinity-chiral algebra@$\Ainf$-chiral algebra!modular operad|textbf}
\index{Swiss-cheese operad!modular extension}
\index{factorisation algebra!3d holomorphic-topological}
There exists a modular operad $\mathcal{O}^{\Ainf\text{-ch}}$
whose algebras are $\Ainf$-algebras in $\Eone$-chiral algebras
on~$X$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The genus-$0$ part recovers the $\SCchtop$ bar complex
 structure: the differential is holomorphic factorization
 on~$\C$, the deconcatenation coproduct is topological
 factorization on~$\R$.
\item The higher-genus part produces the curvature
 $\kappa_{\mathrm{ch}}(\cA) \cdot \omega_g$ as the operadic
 obstruction to extending the genus-$0$ differential to
 genus~$g$: the failure $\dfib^{\,2} \ne 0$ is the image
 of the clutching map of $\mathcal{O}^{\Ainf\text{-ch}}$
 under the Feynman transform.
\item Algebras over $\mathcal{O}^{\Ainf\text{-ch}}$ are the
 factorisation algebras of $3$d holomorphic-topological
 bulk theories on $X \times \R$.
\end{enumerate}
\end{conjecture}

\begin{construction}[Genus-$0$ generators of $\mathcal{O}^{\Ainf\text{-ch}}$]
\label{constr:genus0-ainf-chiral-operad}
\index{modular operad!A-infinity-chiral@$\Ainf$-chiral!genus-0 generators|textbf}
\index{Swiss-cheese operad!three-coloured extension}
\index{Boardman--Vogt tensor product!SC and Ass}
\index{E3-algebra@$\Ethree$-algebra!operadic generators}
\ClaimStatusProvedHere{}
We construct the genus-$0$ part
$\mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}$ as a three-coloured
topological operad, making explicit the generators and relations
left unspecified by Conjecture~\ref{conj:modular-operad-ainf-chiral}.
The three colours arise from the three geometric directions
of the HT theory on $X \times \R_{\perp}$: the holomorphic
direction of the curve~$X$, the topological boundary direction
$\R_{||} = \partial\mathbb{H} \subset X$ (the real locus of
the half-plane), and the topological transverse direction
$\R_{\perp}$ (normal to~$X$).

\medskip\noindent
\textbf{Colours.}
$\mathbf{Col} = \{\mathsf{ch},\, \mathsf{bdy},\, \mathsf{tr}\}$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\mathsf{ch}$ (holomorphic/bulk): insertions in the interior
 of the curve~$X$.
\item $\mathsf{bdy}$ (topological/boundary): insertions on the
 boundary $\R_{||} \subset X$ (the real locus).
\item $\mathsf{tr}$ (topological/transverse): insertions along the
 transverse interval $\R_{\perp}$.
\end{enumerate}

\medskip\noindent
\textbf{Operation spaces.}
For $k \ge 0$ inputs of colour~$\mathsf{ch}$,
$m \ge 0$ inputs of colour~$\mathsf{bdy}$,
$p \ge 0$ inputs of colour~$\mathsf{tr}$,
and output colour~$c_{\mathrm{out}} \in \mathbf{Col}$:
\begin{enumerate}[label=\textup{(G\arabic*)}]
\item \emph{Holomorphic output
 ($c_{\mathrm{out}} = \mathsf{ch}$):}
 \[
 \mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}
 \bigl(
 \underbrace{\mathsf{ch},\ldots}_{k};\,\mathsf{ch}
 \bigr)
 \;=\; \FM_k(\C),
 \]
 and the operation space is \emph{empty} if any input has
 colour $\mathsf{bdy}$ or $\mathsf{tr}$.

\item \emph{Boundary output
 ($c_{\mathrm{out}} = \mathsf{bdy}$):}
 \[
 \mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}
 \bigl(
 \underbrace{\mathsf{ch},\ldots}_{k},\,
 \underbrace{\mathsf{bdy},\ldots}_{m};\,\mathsf{bdy}
 \bigr)
 \;=\; \FM_k(\C) \times \Eone(m),
 \]
 and the operation space is \emph{empty} if any input has
 colour~$\mathsf{tr}$. This reproduces $\SCchtop$
 (Definition~\ref{def:SC-operations}).

\item \emph{Transverse output
 ($c_{\mathrm{out}} = \mathsf{tr}$):}
 \begin{equation}\label{eq:genus0-triple-ops}
 \mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}
 \bigl(
 \underbrace{\mathsf{ch},\ldots}_{k},\,
 \underbrace{\mathsf{bdy},\ldots}_{m},\,
 \underbrace{\mathsf{tr},\ldots}_{p};\,\mathsf{tr}
 \bigr)
 \;=\; \FM_k(\C) \times \Eone(m) \times \Eone(p).
 \end{equation}
 All three types of input are permitted. The $\Eone(p)$ factor
 is the associahedron governing collisions in the transverse
 direction $\R_{\perp}$; the $\FM_k(\C) \times \Eone(m)$
 factor is the $\SCchtop$ datum governing the within-slice
 structure at each transverse position.
\end{enumerate}

\medskip\noindent
\textbf{Directionality.}
The three-colour directionality is a refinement of the
$\SCchtop$ directionality
(Definition~\ref{def:SC-operations}) to a linear filtration
on~$\mathbf{Col}$:
\[
 \mathsf{ch}
 \;\longrightarrow\;
 \mathsf{bdy}
 \;\longrightarrow\;
 \mathsf{tr}.
\]
An operation with output colour~$c_{\mathrm{out}}$ admits
inputs only of colour $c \le c_{\mathrm{out}}$ in this
ordering. Concretely:
\begin{itemize}
\item no $\mathsf{bdy}$ or $\mathsf{tr}$ inputs produce
 $\mathsf{ch}$ output (bulk isolation);
\item no $\mathsf{tr}$ inputs produce $\mathsf{bdy}$ output
 (boundary isolation from transverse);
\item all colours can feed into $\mathsf{tr}$ output (the
 transverse direction receives data from both the holomorphic
 bulk and the topological boundary).
\end{itemize}
At $p=0$ (no transverse inputs), the
$\mathsf{ch}$/$\mathsf{bdy}$ sector recovers $\SCchtop$
exactly.

\medskip\noindent
\textbf{Composition.}
Composition is componentwise: the three factors $\FM_\bullet(\C)$,
$\Eone^{\mathsf{bdy}}$, $\Eone^{\mathsf{tr}}$ compose
independently via their respective operadic insertion maps,
exactly as in Definition~\ref{def:SC-composition} for the
$\SCchtop$ factor, tensored with the standard $\Eone$ composition
on the transverse factor:
\[
 \bigl(\FM_k(\C) \times \Eone(m) \times \Eone(p)\bigr)
 \;\times\;
 \prod_{i=1}^{k} \FM_{\ell_i}(\C)
 \;\times\;
 \prod_{j=1}^{m} \Eone(n_j)
 \;\times\;
 \prod_{r=1}^{p} \Eone(q_r)
 \;\longrightarrow\;
 \FM_{\sum\ell_i}(\C)
 \times \Eone\bigl(\textstyle\sum n_j\bigr)
 \times \Eone\bigl(\textstyle\sum q_r\bigr).
\]
The symmetric groups $\Sgp_k$ act on holomorphic inputs; the
boundary and transverse inputs are ordered (no symmetric group
action).

\medskip\noindent
\textbf{Relations.}
The relations in $\mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}$
are the product of three independent relation sets:
\begin{enumerate}[label=\textup{(R\arabic*)}]
\item The codimension-$2$ strata of $\FM_k(\C)$: the Jacobi
 identity / homotopy-associativity of the chiral product
 (the Arnold relation at genus~$0$).
\item The Stasheff associahedron relations on $\Eone(m)$:
 the $\Ainf$ coherences for boundary compositions.
\item The Stasheff associahedron relations on $\Eone(p)$:
 the $\Ainf$ coherences for transverse compositions.
\item No mixed relations between (R1)--(R3) at genus~$0$:
 the product decomposition~\eqref{eq:genus0-triple-ops}
 is \emph{strict}, not merely a homotopy equivalence.
\end{enumerate}
\end{construction}

\begin{proposition}[Product decomposition at genus~$0$;
\ClaimStatusProvedHere]
\label{prop:genus0-product-decomposition}
\index{Boardman--Vogt tensor product!product decomposition}
The genus-$0$ operad
$\mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}$ of
Construction~\textup{\ref{constr:genus0-ainf-chiral-operad}} is
isomorphic as a three-coloured topological operad to the
external product
\begin{equation}\label{eq:genus0-product}
 \mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}
 \;\cong\;
 \SCchtop \;\times\; \Eone^{\mathsf{tr}},
\end{equation}
where $\SCchtop$ acts on the colours
$\{\mathsf{ch}, \mathsf{bdy}\}$ and
$\Eone^{\mathsf{tr}}$ acts on the colour
$\{\mathsf{tr}\}$, with the product directionality
$(\mathsf{ch} \to \mathsf{bdy}) \to \mathsf{tr}$.
\end{proposition}

\begin{proof}
\emph{Step~1: Propagator factorisation.}
On $\C \times \R_{\perp}$ (the genus-$0$ HT slab), the
propagator of the free theory~\eqref{eq:HT-kinetic}
factorises as
\[
 P(z,t;\, w,s)
 \;=\;
 \frac{dz}{z - w}
 \;\cdot\;
 \theta(t - s),
\]
where $dz/(z-w)$ is the Cauchy kernel on~$\C$ and
$\theta(t-s)$ is the Heaviside function on~$\R_{\perp}$.
The holomorphic variable~$z$ and the transverse variable~$t$
decouple: the Green's function carries no cross-terms.

\medskip\noindent
\emph{Step~2: Configuration space decomposition.}
At genus~$0$, the compactified configuration space of $n$
points in the HT slab $\mathbb{H} \times \R_{\perp}$,
stratified by the HT twist (holomorphic in $\C$, locally
constant in both $\R_{||}$ and $\R_{\perp}$), decomposes
as a product:
\[
 \overline{\mathrm{Conf}}^{\mathrm{HT}}_{k,m,p}
 \bigl(\mathbb{H} \times \R_{\perp}\bigr)
 \;\cong\;
 \FM_k(\C) \;\times\; \Conf_m^{<}(\R_{||})
 \;\times\; \Conf_p^{<}(\R_{\perp}).
\]
This is strict (not merely a homotopy equivalence) because
at genus~$0$ the curve is $\C$ (contractible), the
boundary $\R_{||}$ is a line (contractible), the transverse
$\R_{\perp}$ is a line (contractible), and there are no
compact cycles whose monodromy could entangle the three factors.
The argument is the three-dimensional analogue of
Remark~\ref{rem:product-forced-by-locality}: the propagator
factorisation forces the operation spaces to be products, and
the codimension-$2$ strata decompose compatibly.

\medskip\noindent
\emph{Step~3: Composition compatibility.}
The operadic composition maps are products of the FM insertion
maps on the holomorphic factor, the Stasheff associahedron
compositions on the boundary factor, and the Stasheff
compositions on the transverse factor. No cross-composition maps
arise: a collision in $\R_{\perp}$ does not produce a
codimension-$1$ stratum in $\FM_k(\C)$ or in $\Conf_m^<(\R_{||})$,
and vice versa, by the propagator decoupling of Step~1.
Therefore the operad structure is the external product
$\SCchtop \times \Eone^{\mathsf{tr}}$.
\end{proof}

\begin{remark}[Why the product decomposition fails at genus $g \ge 1$]
\label{rem:product-failure-higher-genus}
\index{modular operad!A-infinity-chiral@$\Ainf$-chiral!product failure}
\index{curved Dunn additivity!product failure}
At genus $g \ge 1$, the propagator on $\Sigma_g$ acquires
$B$-cycle monodromy (equation~\eqref{eq:propagator-monodromy}),
and the Arakelov regularisation introduces a non-holomorphic
correction with $\bar\partial$-defect
$-2\pi i\, \omega_g$ (the Arakelov $(1,1)$-form).
This defect entangles the holomorphic and transverse directions:
the single-valued propagator on $\Sigma_g \times \R_{\perp}$ is
\[
 P^{(g)}(z,t;\, w,s)
 \;=\;
 K^{(g)}_{\mathrm{Ar}}(z,w) \;\cdot\; \theta(t-s),
\]
and $\bar\partial_z K^{(g)}_{\mathrm{Ar}} = -2\pi i\,\omega_g(z)
\ne 0$, so the $z$- and $t$-dependences no longer decouple at the
cochain level. The failure of the product decomposition at $g \ge 1$
is precisely the content of
Conjecture~\ref{conj:modular-operad-ainf-chiral}(ii): the modular
extension $\mathcal{O}^{\Ainf\text{-ch}}$ carries non-trivial
clutching maps that intertwine the holomorphic and transverse
factors, producing the curvature
$\kappa_{\mathrm{ch}}(\cA) \cdot \omega_g$.

The genus-$0$ product decomposition~\eqref{eq:genus0-product}
is the \emph{flat model}: $\dfib^{\,2} = 0$ holds precisely
because the three factors are independent.
At genus $g \ge 1$, the non-separating clutching of
$\mathcal{O}^{\Ainf\text{-ch}}$ (which contracts two
$\mathsf{ch}$-inputs and raises genus) introduces
cross-terms between $\FM_k(\Sigma_g)$ and $\Eone(p)$:
the $R$-matrix data of the $\Eone$-chiral algebra enters
the genus-raising operation, entangling the $\SCchtop$ and
$\Eone^{\mathsf{tr}}$ factors.
This entanglement is the operadic expression of curved Dunn
additivity (Conjecture~\ref{conj:curved-dunn-additivity}).
\end{remark}

\begin{remark}[Algebras over the genus-$0$ operad]
\label{rem:algebras-genus0-ainf-chiral}
\index{A-infinity-chiral algebra@$\Ainf$-chiral algebra!genus-0 algebras}
An algebra over
$\mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}
\cong \SCchtop \times \Eone^{\mathsf{tr}}$
is a triple
$(A_{\mathsf{ch}},\, A_{\mathsf{bdy}},\, A_{\mathsf{tr}})$
with:
\begin{enumerate}[label=\textup{(\alph*)}]
\item Structure maps
 $C_\ast(\FM_k(\C)) \otimes A_{\mathsf{ch}}^{\otimes k}
 \to A_{\mathsf{ch}}$:
 the chiral product (holomorphic factorisation on~$\C$).
\item Structure maps
 $C_\ast(\FM_k(\C) \times \Eone(m)) \otimes
 A_{\mathsf{ch}}^{\otimes k} \otimes
 A_{\mathsf{bdy}}^{\otimes m} \to A_{\mathsf{bdy}}$:
 the $\SCchtop$ mixed operations (bulk-to-boundary module maps).
\item Structure maps
 $C_\ast(\FM_k(\C) \times \Eone(m) \times \Eone(p))
 \otimes A_{\mathsf{ch}}^{\otimes k} \otimes
 A_{\mathsf{bdy}}^{\otimes m} \otimes
 A_{\mathsf{tr}}^{\otimes p} \to A_{\mathsf{tr}}$:
 the transverse operations, combining holomorphic, boundary,
 and transverse data.
\end{enumerate}
By the product decomposition~\eqref{eq:genus0-product},
this is equivalent to an $\Ainf$-algebra
$(A_{\mathsf{tr}},\, \{m_p^{\mathsf{tr}}\}_{p \ge 1})$
whose underlying object carries an $\SCchtop$-algebra
structure; that is, an $\Ainf$-algebra in
$\Eone$-chiral algebras, as required by
Conjecture~\ref{conj:modular-operad-ainf-chiral}(i).

The half-plane bar complex
$\barB^{\mathbb{H}}(\cA)$
(Construction~\ref{constr:half-plane-bar}) is the
$\SCchtop$ bar coalgebra. The transverse bar complex is
the standard $\Eone$-bar of $\barB^{\mathbb{H}}(\cA)$,
taken in the transverse direction: at the cochain level
it produces the Hochschild complex of the boundary, and
$\Zder^{\mathrm{ch}}(\cA)$ inherits the $\Ethree$-chiral
structure of Definition~\ref{def:E3-chiral-algebra}.
\end{remark}

\begin{remark}[Relation to existing structures]
\label{rem:modular-operad-ainf-context}
At genus~$0$, the operad $\mathcal{O}^{\Ainf\text{-ch}}$ is
$\SCchtop \times \Eone^{\mathsf{tr}}$
(Proposition~\ref{prop:genus0-product-decomposition}),
which refines the two-coloured $\SCchtop$ to a
three-coloured operad with the transverse $\Eone$ factor
governing the $\Ainf$ structure.
Construction~\ref{constr:genus0-ainf-chiral-operad} makes
the generators and composition explicit.
The conjecture asserts that
the modular extension $\SCmod$
(Definition~\ref{def:SC-mod}), which governs
$\Einf$-chiral algebras at all genera, has an $\Eone$-chiral
analogue $\mathcal{O}^{\Ainf\text{-ch}}$ that governs
$\Ainf$-algebras in $\Eone$-chiral algebras at all genera.
The $\Einf$ case is proved (the curvature
$\dfib^{\,2} = \kappa \cdot \omega_g$ arises from the
clutching maps of $\SCmod$); the $\Eone$ case requires
extending the clutching maps to the ordered setting, where
$R$-matrix data enters the genus-raising operation.
\end{remark}

\begin{conjecture}[Curved Dunn additivity; \ClaimStatusConjectured]
\label{conj:curved-dunn-additivity}
\index{Dunn additivity!curved|textbf}
\index{curved Dunn additivity|textbf}
\index{E2-algebra@$\Etwo$-algebra!curved Dunn decomposition}
A curved $\Etwo$-algebra decomposes as a curved $\Eone$-algebra
in curved $\Eone$-algebras. The curvature
$\kappa_{\mathrm{ch}}(\cA) \cdot \omega_g$ is the obstruction
to the flat decomposition: when $\kappa_{\mathrm{ch}}(\cA) = 0$,
the decomposition reduces to the classical Dunn additivity
equivalence $\Etwo \simeq \Eone \circ \Eone$.
\end{conjecture}

\begin{remark}[Curved Dunn additivity and the genus tower]
\label{rem:curved-dunn-genus-tower}
\index{Dunn additivity!genus tower}
Classical Dunn additivity decomposes an $\Etwo$-algebra as an
$\Eone$-algebra in $\Eone$-algebras; the two $\Eone$ factors
correspond to the holomorphic and topological directions
of the $\SCchtop$-structure.
Conjecture~\ref{conj:curved-dunn-additivity} asserts that
the curved analogue (where $\dfib^{\,2} \ne 0$ at genus
$g \ge 1$) deforms this decomposition: the two
$\Eone$-factors become individually curved, and the curvature
$\kappa_{\mathrm{ch}}(\cA) \cdot \omega_g$ measures the
failure of the flat factorisation. For the Virasoro algebra,
this gives the curvature $\kappa_{\mathrm{eff}} \cdot \omega_g
= ((c-26)/2) \cdot \omega_g$ of Movement~IV, and the genus
tower $F_g = \kappa_{\mathrm{eff}} \cdot \lambda_g^{\mathrm{FP}}$
is the sequence of obstructions to restoring the flat
$\Etwo \simeq \Eone \circ \Eone$ decomposition genus by genus.
\end{remark}

\begin{remark}[Three-level refinement of curved Dunn additivity]
\label{rem:curved-dunn-three-level}
\index{Dunn additivity!curved!three-level refinement|textbf}
\index{twisted tensor product!operadic bar complex}
\index{K\"unneth!twisted operadic}
\index{Eilenberg--Zilber twisted tensor product}
Conjecture~\ref{conj:curved-dunn-additivity} admits a
three-level refinement that avoids the undefined
BV tensor product of curved operads.

\medskip\noindent
\textbf{Level~1 (proved; uncurved Dunn).}
At genus~$0$,
$\mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}
\cong \SCchtop \times \Eone^{\mathsf{tr}}$
(Proposition~\ref{prop:genus0-product-decomposition}).
The three-coloured operad is a strict product, and the
operadic K\"unneth lemma
(Lemma~\ref{lem:operadic-kunneth}) yields
\[
 \mathbf{B}(\mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0})
 \;\simeq\;
 \mathbf{B}(\SCchtop)
 \otimes \mathbf{B}(\Eone^{\mathsf{tr}}).
\]
The two-coloured K\"unneth holds because
the mixed bar differential decomposes as
$d_{\mathrm{cl}} \otimes \mathrm{id}
+ \mathrm{id} \otimes d_{\mathrm{op}}$
with no cross-terms: directionality forbids
open-to-closed edges, so closed and open graphs decouple
(proof of Lemma~\ref{lem:operadic-kunneth}).

\medskip\noindent
\textbf{Level~2 (obstruction theory).}
The obstruction to extending the genus-$0$ product
decomposition to genus~$g$ lies in
\[
 H^2\bigl(
 \Hom\bigl(
 \mathbf{B}(\Eone^{\mathsf{tr}}),\;
 \mathrm{gr}^g\,
 \mathbf{B}_{\mathrm{mod}}(\SCchtop)
 \bigr),\; d_0\bigr).
\]
At genus~$1$, this obstruction is
$\kappa_R(\cA) \cdot \omega_1$, controlled by
$\mathrm{Mon}(R) = \lim_{z \to e^{2\pi i}z} R(z)$.
When $\mathrm{Mon}(R) = \mathrm{id}$, the obstruction
vanishes: the product extends, and the curvature at
genus~$1$ reduces to the pure holomorphic scalar
$\kappa(\cA) \cdot \omega_1$ with no cross-terms between
holomorphic and transverse factors.
When $\mathrm{Mon}(R) \neq \mathrm{id}$
(genuinely $\Eone$-chiral algebras), the
genus-$1$ cross-term $\kappa_R(\cA) \cdot \omega_1$ is
non-trivial
(Construction~\ref{constr:genus1-ainf-chiral-operations}).

\medskip\noindent
\textbf{Why the two-coloured K\"unneth holds but the
three-coloured version fails at genus $\ge 1$.}
The K\"unneth decomposition of
Lemma~\ref{lem:operadic-kunneth} applies to a strict
product $\cP_1 \boxtimes \cP_2$ where the mixed operations
are $\cP_1(g,k) \otimes \cP_2(m)$ at every genus.
At genus~$0$, the three-coloured operad
$\mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}$ is such a
strict product. At genus~$g \ge 1$, the clutching maps
of $\mathcal{O}^{\Ainf\text{-ch}}$ twist the transverse
$\Eone^{\mathsf{tr}}$ factor by $\mathrm{Mon}(R)$
(Remark~\ref{rem:product-failure-higher-genus}):
the self-sewing contracts two holomorphic inputs
and transports transverse states around the $B$-cycle,
so the mixed operations at genus~$g$ are no longer
a tensor product but carry the monodromy twist.
The bar differential acquires cross-terms
$d_{\mathrm{cl}} \otimes \mathrm{Mon}(R)$
that couple the closed and open summands,
and the hypotheses of
Lemma~\ref{lem:operadic-kunneth} fail.

\medskip\noindent
\textbf{Level~3 (twisted K\"unneth; hard but well-posed).}
The correct replacement for the product decomposition
at all genera is a \emph{twisted tensor product}.
The full modular bar complex decomposes as
\begin{equation}\label{eq:twisted-kunneth-bar}
 \mathbf{B}_{\mathrm{mod}}\bigl(
 \mathcal{O}^{\Ainf\text{-ch}},\, \cA\bigr)
 \;\simeq\;
 \mathbf{B}_{\mathrm{mod}}(\SCchtop,\, \cA)
 \;\otimes^{\mathrm{Mon}(R)}\;
 \mathbf{B}(\Eone^{\mathsf{tr}},\, \cA),
\end{equation}
where $\otimes^{\mathrm{Mon}(R)}$ denotes the
Eilenberg--Zilber twisted tensor product with
twisting cochain
$\tau \colon
\mathbf{B}(\Eone^{\mathsf{tr}}) \to
\mathbf{B}_{\mathrm{mod}}(\SCchtop)$
built from the $R$-matrix monodromy at each
genus-raising clutching.
At genus~$0$, $\tau = 0$ and the twisted tensor
product reduces to the ordinary tensor product of
Level~1.
At genus~$1$, $\tau$ is determined by the single
non-separating clutching with monodromy insertion
$\mathrm{Mon}(R)$
(Construction~\ref{constr:genus1-ainf-chiral-operations},
equation~\eqref{eq:R-matrix-clutching}).
At genus $g \ge 2$, $\tau$ is determined recursively
by iterating the clutching maps of
Definition~\ref{def:modular-operad-ainf-chiral}(ii)
along stable graphs with $g$ loops.

\medskip\noindent
\textbf{Reduction to tractable sub-problems.}
Establishing~\eqref{eq:twisted-kunneth-bar}
reduces to three steps:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Explicit construction of $\tau$.}
 At genus~$1$, $\tau$ is the monodromy insertion of
 Construction~\ref{constr:genus1-ainf-chiral-operations}
 (done). At genus~$g \ge 2$, $\tau$ is built inductively
 from the stable-graph clutching maps.
\item \emph{Twisted K\"unneth.}
 A generalisation of Lemma~\ref{lem:operadic-kunneth}
 to the twisted setting: if $\tau$ satisfies the
 Maurer--Cartan equation for the convolution dg Lie
 algebra
 $\Hom(\mathbf{B}(\Eone^{\mathsf{tr}}),\,
 \mathbf{B}_{\mathrm{mod}}(\SCchtop))$,
 then the twisted differential
 $d + \tau$ on the tensor product is a
 well-defined square-zero differential, and the
 resulting twisted tensor product computes the modular
 bar complex of $\mathcal{O}^{\Ainf\text{-ch}}$.
\item \emph{Model structure compatibility.}
 The twisted decomposition must respect the
 model structures for curved operadic algebras
 (Bellier-Mill\`es--Drummond-Cole~\cite{BMDC20},
 Hirsh--Mill\`es~\cite{HM22}): the twisting cochain
 $\tau$ determines a curved $\Ainf$-structure whose bar
 complex is the twisted tensor product, and the cofibrant
 replacements in the model category of curved operads
 agree with the cobar construction of the twisted
 bar complex.
\end{enumerate}
At genus~$0$, steps (a)--(c) are all trivially satisfied
($\tau = 0$, the K\"unneth is untwisted, and the model
structure reduces to the classical one). The content of
Conjecture~\ref{conj:curved-dunn-additivity} is that
these three steps go through at all genera, with the
$R$-matrix monodromy providing the twisting cochain.

\medskip\noindent
\textbf{The two-complex bridge (the precise frontier).}
The genus-$g$ obstruction class $\mathrm{Ob}_g$ lives in
two different complexes with different cohomological
properties.  In the \emph{modular-bootstrap complex}
$(\mathfrak{g}^{\cA}_{\mathrm{mod}}, d_{\Theta^{(0)}})$
(Theorem~\ref{thm:modular-bar} and the genus-tower
recursion), $H^2 = 0$ at every genus $g \ge 1$: every
$\mathrm{Ob}_g$ is exact, and the genus-$g$ partition
function is uniquely determined by lower-genus data.
In the \emph{curved-Dunn twisting-cochain complex}
$H^2\bigl(\Hom\bigl(\mathbf{B}(\Eone^{\mathsf{tr}}),\,
\mathrm{gr}^g\,\mathbf{B}_{\mathrm{mod}}(\SCchtop)\bigr),
d_0\bigr)$, the vanishing of $H^2$ is \emph{open}.
If a natural map between these two complexes can be
constructed (a bridge carrying the modular-bootstrap
exactness into the curved-Dunn setting), then curved
Dunn additivity at all genera follows from the
already-proved modular bootstrap recursion.
\end{remark}

\begin{construction}[Genus-$1$ operations of
$\mathcal{O}^{\Ainf\text{-ch}}$; conjectural]
\label{constr:genus1-ainf-chiral-operations}
\index{modular operad!A-infinity-chiral@$\Ainf$-chiral!genus-1 operations|textbf}
\index{clutching!non-separating!genus-1 with R-matrix@genus-$1$ with $R$-matrix}
\index{R-matrix@$R$-matrix!genus-1 clutching@genus-$1$ clutching}
\index{Arakelov propagator!genus-1 clutching@genus-$1$ clutching}
\index{curved Dunn additivity!genus-1 operations@genus-$1$ operations}
\ClaimStatusConjectured
At genus~$0$, the operad
$\mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}
\cong \SCchtop \times \Eone^{\mathsf{tr}}$
is a strict product
(Proposition~\ref{prop:genus0-product-decomposition}).
The genus-$1$ operations are generated by applying the
non-separating clutching to the genus-$0$ product, and
they exhibit the entanglement of the holomorphic and
transverse factors predicted by
Remark~\ref{rem:product-failure-higher-genus}.

\medskip\noindent
\textbf{The self-sewing clutching.}
The non-separating clutching
$\xi_{\mathrm{nsep}} \colon
\mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}
(k{+}2,m,p) \to
\mathcal{O}^{\Ainf\text{-ch}}\big|_{g=1}(k,m,p)$
contracts two $\mathsf{ch}$-coloured inputs of a genus-$0$
operation and raises the genus by~$1$.
At genus~$0$, the operation space is the product
$\FM_{k+2}(\C) \times \Eone(m) \times \Eone(p)$;
the clutching contracts the last two holomorphic inputs,
identifying them via the invariant bilinear form to create
a self-loop.
Geometrically, this corresponds to cutting out
two small discs around $z_{k+1}$ and $z_{k+2}$ on~$\C$ and
gluing them to form a handle, producing a torus
$\Sigma_1 = E_\tau$.

\medskip\noindent
\textbf{The genus-$1$ propagator and the dbar-defect.}
On the resulting torus, the propagator is the
Arakelov-normalised form
(Proposition~\ref{prop:arakelov-genus-1-derivation}):
\[
 \eta^{(1)}(z,w;\tau)
 \;=\;
 \partial_z \log\vartheta_1(z{-}w|\tau)
 \;+\;
 \frac{2\pi i\, \operatorname{Im}(z{-}w)}
 {\operatorname{Im}\tau}.
\]
This propagator is single-valued on $E_\tau$ but
satisfies $\bar\partial_z \eta^{(1)} = -(\pi/\operatorname{Im}\tau)
\,dz \wedge d\bar z = 2i\,\omega_{\mathrm{Ar}}$.
The $\bar\partial$-defect is the source of the curvature
$\kappa(\cA) \cdot \omega_1$ at genus~$1$
(equation~\eqref{eq:arnold-defect-genus-g} specialised
to $g=1$).

\medskip\noindent
\textbf{Entanglement of the three factors.}
At genus~$0$, the three factors $\FM_k(\C)$, $\Eone(m)$,
$\Eone(p)$ are independent because the propagator
$dz/(z{-}w) \cdot \theta(t{-}s)$ decouples
(Proposition~\ref{prop:genus0-product-decomposition},
Step~1). At genus~$1$, the self-sewing introduces two
sources of entanglement:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{$B$-cycle monodromy (holomorphic $\leftrightarrow$
 transverse).}
 The self-sewing identifies the two contracted points
 via the annular propagator, which involves
 transporting states around the $B$-cycle of~$E_\tau$.
 In the three-coloured operad, this transport acts on
 the transverse factor by the $R$-matrix monodromy:
 the $\Eone^{\mathsf{tr}}(p)$ factor is twisted by
 $\mathrm{Mon}(R) = \lim_{z \to e^{2\pi i}z} R(z)$,
 exactly as in the wraparound differential of the circle
 bar chain model
 (Remark~\ref{rem:wraparound-monodromy}).
 This twist prevents the genus-$1$ operation space from
 being a product $\FM_k(\Sigma_1) \times \Eone(m)
 \times \Eone(p)$.
\item \emph{Arakelov defect (holomorphic $\leftrightarrow$
 boundary).}
 The non-holomorphic correction in $\eta^{(1)}$
 introduces $(1,1)$-form contributions at codimension-$2$
 strata where a holomorphic collision coincides with a
 boundary collision. These cross-terms, absent at
 genus~$0$, entangle the $\FM_k(\Sigma_1)$ and
 $\Eone(m)$ factors.
\end{enumerate}

\medskip\noindent
\textbf{The simplest genus-$1$ operation: the torus trace.}
The simplest new operation at genus~$1$ is the
\emph{torus trace}: the self-sewing of the genus-$0$
binary operation
$\mu_2 \in \FM_2(\C) \times \Eone(0) \times \Eone(0)$
(the chiral product with no boundary or transverse inputs),
contracting both holomorphic inputs:
\begin{equation}\label{eq:torus-trace-operation}
 \xi_{\mathrm{nsep}}(\mu_2)
 \;\in\;
 \mathcal{O}^{\Ainf\text{-ch}}\big|_{g=1}(0,0,0).
\end{equation}
This is the genus-$1$ scalar:
the self-sewing of the binary product by the
invariant bilinear form produces
$\kappa(\cA) \cdot \omega_1$, where
$\kappa(\cA) = \mathrm{Tr}_\cA$ is the modular
characteristic.
On an algebra $\cA$ over
$\mathcal{O}^{\Ainf\text{-ch}}$, this evaluates to
\[
 \xi_{\mathrm{nsep}}(\mu_2)(\cA)
 \;=\;
 \sum_h \langle e^h | \mu_2 | e_h \rangle
 \;=\;
 \kappa(\cA) \cdot \omega_1,
\]
where $\{e_h\}$, $\{e^h\}$ are dual bases. This is the
genus-$1$ partition function density.

\medskip\noindent
\textbf{The genus-$1$ operation with transverse inputs:
$R$-matrix clutching.}
The first entangled operation involves transverse inputs.
Consider the genus-$0$ operation with $k=2$
holomorphic inputs and $p=1$ transverse input:
\[
 \mu_{2;0;1} \;\in\;
 \FM_2(\C) \times \Eone(0) \times \Eone(1)
 \;=\; \FM_2(\C) \times \{\mathrm{pt}\}.
\]
Self-sewing the two holomorphic inputs produces
a genus-$1$ operation with one transverse input:
\begin{equation}\label{eq:genus1-transverse-operation}
 \xi_{\mathrm{nsep}}^{R}(\mu_{2;0;1})
 \;\in\;
 \mathcal{O}^{\Ainf\text{-ch}}\big|_{g=1}(0,0,1).
\end{equation}
This operation is \emph{not} simply
$\xi_{\mathrm{nsep}}^{\mathrm{cl}} \otimes
\mathrm{id}_{\Eone}$ (which would be the product
ansatz). The transverse input must be transported
through the torus handle, picking up the $R$-matrix
monodromy. The explicit formula on an element
$a \in \cA_{\mathsf{tr}}$ is:
\begin{equation}\label{eq:R-matrix-clutching}
 \xi_{\mathrm{nsep}}^{R}(\mu_{2;0;1})(\cA)(a)
 \;=\;
 \sum_h
 \bigl\langle e^h \,\big|\,
 \mu_2\bigl(e_h,\,
 \mathrm{Mon}(R)(a)\bigr)
 \bigr\rangle
 \cdot \omega_1,
\end{equation}
where $\mathrm{Mon}(R)(a) =
\lim_{z \to e^{2\pi i}z} R(z) \cdot a$
is the $R$-matrix monodromy acting on the transverse
state. For $E_\infty$-chiral algebras (where
$\mathrm{Mon}(R)$ is derived from the OPE), this
reduces to the standard genus-$1$ trace with monodromy
insertion; for genuinely $E_1$-chiral algebras, the
$R$-matrix monodromy is independent structure.

\medskip\noindent
\textbf{The curvature from the clutching.}
The curvature $\dfib^{\,2} = \kappa(\cA) \cdot \omega_1$
arises from the composition of two genus-$0$ operations
through the genus-$1$ propagator: the Arnold defect
(equation~\eqref{eq:arnold-defect-genus-g} at $g=1$)
prevents $\dfib^{\,2}=0$.
In the three-coloured operad, this curvature measures
the failure of the product decomposition
$\SCchtop \times \Eone^{\mathsf{tr}}$ to extend to
genus~$1$. The curvature has two components:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The \emph{scalar curvature}
 $\kappa(\cA) \cdot \omega_1 \in
 \mathcal{O}^{\Ainf\text{-ch}}\big|_{g=1}(0,0,0)$:
 the trace of the binary product, living in the
 pure-holomorphic sector. This is the classical
 curvature from the modular bar complex.
\item The \emph{$R$-matrix curvature} from the cross-terms
 between the holomorphic and transverse factors:
 at genus~$1$, the composition
 $\dfib^{\mathsf{ch}} \circ \dfib^{\mathsf{tr}}
 + \dfib^{\mathsf{tr}} \circ \dfib^{\mathsf{ch}}$
 is no longer zero. These cross-terms are controlled
 by the $R$-matrix monodromy and vanish when
 $\mathrm{Mon}(R) = \mathrm{id}$.
\end{enumerate}
The total genus-$1$ curvature is therefore
\[
 \dfib^{\,2}\big|_{g=1}
 \;=\;
 \kappa(\cA) \cdot \omega_1
 \;+\;
 \kappa_R(\cA) \cdot \omega_1,
\]
where $\kappa_R(\cA)$ is a correction depending on
the $R$-matrix monodromy.
For $E_\infty$-chiral algebras, the $R$-matrix monodromy
contribution is absorbed into the modular
characteristic~$\kappa$, because $\mathrm{Mon}(R)$ is
derived from the OPE; the decomposition
$\kappa + \kappa_R$ is nontrivial only for genuinely
$E_1$-chiral algebras where $R$ is independent structure.
When $\mathrm{Mon}(R)=\mathrm{id}$,
$\kappa_R = 0$ and the curvature reduces to
$\kappa \cdot \omega_1$.
No example of a genuinely $E_1$-chiral algebra with
$\kappa_R \neq 0$ has been computed; the correction
remains conjectural.
\end{construction}

\begin{remark}[Relation to existing genus-$1$ structures]
\label{rem:genus1-ainf-context}
\index{modular operad!A-infinity-chiral@$\Ainf$-chiral!genus-1 context}
Construction~\ref{constr:genus1-ainf-chiral-operations}
assembles three ingredients already present in the
manuscript:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The self-sewing mechanism
 $D_1 = D_{\mathrm{nsep}}$ of the modular bar complex
 (Definition~\ref{def:SC-mod}, axiom~(C7)), which
 contracts two closed inputs and raises genus.
\item The wraparound monodromy $\mathrm{Mon}(R)$ of
 the circle bar chain model
 (Remark~\ref{rem:wraparound-monodromy}), which
 twists the cyclic differential by the $R$-matrix.
\item The genus-$1$ spectral $R$-matrix correction
 $r_1(z;\tau)$ of
 Theorem~\ref{thm:genus1-r-matrix}, which involves the
 Weierstrass $\wp$-function and the Eisenstein series
 $E_2(\tau)$ as the genus-$1$ exchange kernel.
\end{enumerate}
The conjectural content is the \emph{interaction} of
these three: how the self-sewing of a three-coloured
genus-$0$ operation, with the $R$-matrix monodromy
acting on the transverse factor, produces the genus-$1$
operations of the modular operad
$\mathcal{O}^{\Ainf\text{-ch}}$.

For the Virasoro algebra at central charge~$c$,
Construction~\ref{constr:genus1-ainf-chiral-operations}
is compatible with the genus-$1$ MC element
$\Theta^{(1)}_{\mathrm{Vir}_c}$ of
Theorem~\ref{thm:genus1-mc-virasoro}: the torus
trace~\eqref{eq:torus-trace-operation} reproduces the
degree-$0$ component $\kappa_{\mathrm{eff}} \cdot \omega_1$
with $\kappa_{\mathrm{eff}} = (c-26)/2$, and the
$R$-matrix clutching~\eqref{eq:R-matrix-clutching}
reproduces the degree-$2$ component involving
$\wp(z;\tau) + E_2(\tau)/12$
(equation~\eqref{eq:genus1-r-matrix-virasoro}).
The full genus-$1$ operad structure requires
extending the formulas~\eqref{eq:torus-trace-operation}--\eqref{eq:R-matrix-clutching}
to arbitrary degrees $(k,m,p)$ and verifying the
operadic associativity with the genus-$0$ compositions.
This is the genus-$1$ content of
Conjecture~\ref{conj:modular-operad-ainf-chiral}.
\end{remark}

\begin{definition}[The modular operad
$\mathcal{O}^{\Ainf\text{-ch}}$]
\label{def:modular-operad-ainf-chiral}
\index{modular operad!A-infinity-chiral@$\Ainf$-chiral!definition|textbf}
The \textbf{modular operad for $\Ainf$-chiral algebras} is the
modular completion of the genus-$0$ cyclic operad
$\SCchtop \times \Eone^{\mathsf{tr}}$
(Construction~\textup{\ref{constr:genus0-ainf-chiral-operad}}),
with structure as follows.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Genus-$0$ operations.}
  The three-coloured operad
  $\SCchtop \times \Eone^{\mathsf{tr}}$
  (Proposition~\textup{\ref{prop:genus0-product-decomposition}}:
  a strict product at genus~$0$).
\item \textbf{Clutching maps (conjectural).}
  For each stable graph~$\Gamma$ of genus~$g$, the clutching map
  \[
    \xi_\Gamma \colon
    \bigotimes_{v \in V(\Gamma)}
    \mathcal{O}^{\Ainf\text{-ch}}\big|_{g_v}
    \;\longrightarrow\;
    \mathcal{O}^{\Ainf\text{-ch}}\big|_{g}
  \]
  is conjecturally defined by sewing vertex bar complexes at edges via the
  annular bar complex $B^{\mathrm{ann}}$
  (Construction~\textup{\ref{constr:annular-bar-vol2}})
  with $R$-matrix monodromy $\mathrm{Mon}(R)$ at each node
  (Construction~\textup{\ref{constr:genus1-ainf-chiral-operations}}).
  The annular sewing carries the monodromy of the KZ connection
  around the sewing circle, entangling the holomorphic
  and transverse factors.
\item \textbf{Modular associativity.}
  For nested stable graphs $\Gamma' \subset \Gamma$, the
  clutching axiom is
  $\xi_\Gamma = \xi_{\Gamma/\Gamma'} \circ
  (\xi_{\Gamma'} \otimes \id)$,
  independent of the order of node formation.
  The abstract stable-graph modular bar differential
  satisfies $D^2=0$
  (Theorem~\textup{\ref{thm:modular-bar}}).
  For affine $V_k(\fg)$, the concrete operadic
  associativity of the clutching maps is proved at
  genus~$0$ for all non-critical levels, and at all
  genera for integrable levels, via flatness and
  regular singularity of the KZ\slash KZB connection
  (Theorem~\textup{\ref{thm:affine-composition-associativity}}).
  At generic non-integral level and genus $\ge 1$,
  the composition axiom remains open
  (the Stokes gap of
  Remark~\textup{\ref{rem:composition-associativity-scope}}).
\item \textbf{Curvature.}
  The failure $\dfib^{\,2} = \kappa_{\mathrm{ch}}(\cA) \cdot
  \omega_g \neq 0$ at genus $g \ge 1$ arises from the
  $\bar\partial$-defect of the Arakelov-regularised
  propagator at each sewing circle: the defect
  $\bar\partial K_{\mathrm{Ar}}^{(g)} =
  -2\pi i\,\omega_g$ entangles the holomorphic and
  transverse directions, preventing the genus-$0$ product
  decomposition from extending to genus~$g$.
\end{enumerate}
At genus~$0$, the product decomposition
(Proposition~\textup{\ref{prop:genus0-product-decomposition}})
means the clutching is trivial and the operad splits.
At genus $\ge 1$, the $R$-matrix monodromy in the
clutching maps and the Arakelov defect in the curvature
make the operad a genuine \emph{deformation} of the
genus-$0$ product, with deformation parameter
$\kappa_{\mathrm{ch}}(\cA)$.
\end{definition}

\begin{remark}[Status]
\label{rem:modular-operad-status}
The genus-$0$ part~(i) and the curvature~(iv)
are proved. For affine $V_k(\fg)$ at non-critical level,
the $\pi_1(\Sigma_g)$ well-definedness of the
clutching maps is proved at all genera
(Proposition~\textup{\ref{prop:affine-modular-operad-all-genera}})
via flatness of the KZB connection. The abstract
stable-graph modular bar differential satisfies
$D^2=0$ (Theorem~\textup{\ref{thm:modular-bar}}).
The genus-$1$ construction remains conjectural
(Construction~\textup{\ref{constr:genus1-ainf-chiral-operations}}).
Equivariance of the clutching maps under $\Aut(\Gamma)$
is proved unconditionally for $E_1$-chiral quantum groups
(Proposition~\textup{\ref{prop:qt-equivariance}}), via
quasi-triangularity and the Yang--Baxter equation.
For affine $V_k(\fg)$, the concrete operadic
associativity and unitality of the
clutching maps are proved at genus~$0$ for all
non-critical levels, and at all genera for integrable
levels
(Theorem~\textup{\ref{thm:affine-composition-associativity}});
at generic non-integral level and genus $\ge 1$,
composition associativity remains open
(the Stokes gap).
For the Heisenberg algebra $\cH_k$, the full operadic
axioms are proved at all genera by the scalar monodromy
principle
(Proposition~\ref{prop:heisenberg-full-modular-operad}).
A homotopy-coherent framework for $\infty$-modular operads
(Strumila~\cite{Strumila25}) may provide an alternative
route where strict composition is replaced by coherent
homotopies, potentially circumventing the Stokes gap.
For non-principal $\cW$-algebras, the reduction-by-stages
framework of Genra--Juillard~\cite{GenraJuillard25}
connects different nilpotent orbits in the same Lie algebra,
providing structural input for the clutching maps.
\end{remark}

\begin{proposition}[Quasi-triangularity implies clutching equivariance;
\ClaimStatusProvedHere]
\label{prop:qt-equivariance}
\index{equivariance!clutching maps|textbf}%
\index{quasi-triangularity!equivariance from|textbf}%
\index{modular operad!A-infinity-chiral@$\Ainf$-chiral!equivariance}%
\index{theta graph!equivariance|textbf}%
\index{Yang--Baxter equation!equivariance from}%
\index{stable graph!automorphism group}%
Let $(\cA, \Delta, R(z), S)$ be an $E_1$-chiral quantum group
\textup{(}Definition~\textup{\ref{def:e1-chiral-quantum-group}}\textup{)}
satisfying quasi-triangularity
$R(z)\,\Delta(a) = \Delta^{\mathrm{op}}(a)\,R(z)$ and the
Yang--Baxter equation
\textup{(}Theorem~\textup{\ref{thm:YBE}}\textup{)}.
Let $\Gamma \in \StGraph(g,n)$ be a stable graph with
automorphism group $\Aut(\Gamma)$, and let
$\xi_\Gamma$ be the clutching map of
Definition~\textup{\ref{def:modular-operad-ainf-chiral}(ii)},
constructed by sewing vertex bar complexes at edges via the
annular bar complex $B^{\mathrm{ann}}$
with $R$-matrix monodromy insertion at each node.
Then $\xi_\Gamma$ is $\Aut(\Gamma)$-equivariant:
\[
\xi_\Gamma \circ \sigma^\ast = \xi_\Gamma
\qquad \text{for all } \sigma \in \Aut(\Gamma),
\]
where $\sigma^\ast$ is the induced action on
$\bigotimes_{v \in V(\Gamma)}
\mathcal{O}^{\Ainf\text{-ch}}\big|_{g_v}$
by permuting vertex factors and re-routing edge sewings.
\end{proposition}

\begin{proof}
Every automorphism $\sigma \in \Aut(\Gamma)$ acts on the vertex
set $V(\Gamma)$ and the edge set $E(\Gamma)$ compatibly with the
incidence structure.  The equivariance of $\xi_\Gamma$ under
$\sigma$ is established by decomposing $\sigma$ into two types
of generators: vertex transpositions and edge transpositions
(fixing both endpoints).

\medskip
\noindent\textbf{Step 1: Vertex transposition via
quasi-triangularity (the theta-graph case).}
The simplest non-trivial instance is the theta graph
$\Gamma_\theta$: two vertices $v_1, v_2$ connected by $k$
parallel edges $e_1, \ldots, e_k$ (at genus~$2$, $k = 3$).
The automorphism group contains $\mathbb{Z}/2$ acting by
$\sigma \colon v_1 \leftrightarrow v_2$ (and correspondingly
reversing the orientation of each edge).

The clutching map $\xi_{\Gamma_\theta}$ sews the vertex bar
complexes $B_{v_1}(\cA)$ and $B_{v_2}(\cA)$ at $k$ edges, each
via the annular bar complex $B^{\mathrm{ann}}_{e_i}(\cA)$.
At each edge $e_i$, the sewing inserts the $R$-matrix monodromy
$\mathrm{Mon}(R)$
(Construction~\ref{constr:genus1-ainf-chiral-operations},
equation~\eqref{eq:R-matrix-clutching}).
The vertex transposition $\sigma$ exchanges the two tensor
factors in $B_{v_1}(\cA) \otimes B_{v_2}(\cA)$, which acts on
the annular sewing by replacing $\Delta$ with
$\Delta^{\mathrm{op}}$ at each edge.
Quasi-triangularity gives, for each edge and for all $a \in \cA$:
\[
R(z)\,\Delta(a) = \Delta^{\mathrm{op}}(a)\,R(z).
\]
Since $\xi_{\Gamma_\theta}$ involves the $R$-matrix monodromy
insertion $\mathrm{Mon}(R)$ at each sewing circle, the exchange
$\Delta \leftrightarrow \Delta^{\mathrm{op}}$ is absorbed by the
$R$-matrix insertions: the total sewing map is invariant under
the simultaneous swap of vertex factors and reversal of edge
orientations.  Concretely, on the degree-$(k,m,p)$ component:
\[
\xi_{\Gamma_\theta}(x_{v_2} \otimes x_{v_1})
= \xi_{\Gamma_\theta}\bigl(\sigma^\ast(x_{v_1} \otimes x_{v_2})\bigr)
= \xi_{\Gamma_\theta}(x_{v_1} \otimes x_{v_2}),
\]
where the first equality is the definition of $\sigma^\ast$ and
the second follows from applying quasi-triangularity at each of
the $k$ sewing circles simultaneously.

\medskip
\noindent\textbf{Step 2: Edge transposition via the
Yang--Baxter equation.}
An edge transposition $\tau_{ij} \colon e_i \leftrightarrow e_j$
(fixing both endpoints) permutes the annular bar complexes
$B^{\mathrm{ann}}_{e_i}(\cA) \leftrightarrow
B^{\mathrm{ann}}_{e_j}(\cA)$
at a common pair of vertices.  Each annular sewing carries an
$R$-matrix monodromy insertion; the exchange of two sewings at a
common vertex is the exchange of two braiding operations on a
common tensor product.

For two parallel edges $e_i, e_j$ at vertices $v_a, v_b$, the
exchange $\tau_{ij}$ acts on the monodromy insertions by a
transposition of the braiding factors.  If a third edge $e_l$
is also present (as in the theta graph at genus~$2$), the
consistency of all pairwise exchanges is the braid
relation, which is the Yang--Baxter equation
(Theorem~\ref{thm:YBE}).

More precisely: the $k$ parallel edges at $(v_a, v_b)$ produce
$k$ monodromy insertions $\mathrm{Mon}(R)_{e_1}, \ldots,
\mathrm{Mon}(R)_{e_k}$ acting on
$B_{v_a}(\cA) \otimes B_{v_b}(\cA)$.
The symmetric group $\Sgp_k$ permuting these $k$ edges acts
by permuting the $k$ monodromy insertions.  The YBE ensures that
this action is compatible with the clutching:
for any $\tau \in \Sgp_k$,
\[
\prod_{i=1}^{k} \mathrm{Mon}(R)_{e_{\tau(i)}}
= \prod_{i=1}^{k} \mathrm{Mon}(R)_{e_i}
\]
as operators on the sewing, because the monodromy insertions act
on independent tensor factors of
$B_{v_a}(\cA) \otimes B_{v_b}(\cA)$ (each edge connects the same
pair of vertices, so the monodromy factors commute when restricted
to their respective annular collars, and the YBE resolves the
ordering ambiguity when they interact through vertex operations).

\medskip
\noindent\textbf{Step 3: General stable graph.}
An arbitrary stable graph $\Gamma$ has
$\Aut(\Gamma) \hookrightarrow
\Sgp_{V(\Gamma)} \ltimes \prod_{(v,v')} \Sgp_{E(v,v')}$,
where $E(v,v')$ is the set of edges between vertices $v$ and $v'$
(including self-edges when $v = v'$).  Every element
$\sigma \in \Aut(\Gamma)$ decomposes as a vertex permutation
$\sigma_V$ followed by edge permutations $\sigma_E$ within each
multi-edge class.  By Steps~1 and~2:
\begin{itemize}
\item $\sigma_V$ is absorbed by quasi-triangularity at each edge
  whose endpoints are transposed (each such edge contributes one
  application of $R\,\Delta = \Delta^{\mathrm{op}}\,R$);
\item $\sigma_E$ is absorbed by the Yang--Baxter equation at each
  vertex where multiple edges are permuted (each triple of edges
  at a common vertex pair contributes one YBE relation).
\end{itemize}
Since every $\sigma \in \Aut(\Gamma)$ is a product of such
generators, $\xi_\Gamma \circ \sigma^\ast = \xi_\Gamma$.

\medskip
\noindent\textbf{Step 4: Self-edges (non-separating).}
For a self-edge $e$ at vertex~$v$ (raising genus by~$1$), the
automorphism exchanging the two half-edges of~$e$ is absorbed
by the symmetry
$\mathrm{Mon}(R)_{21} = \mathrm{Mon}(R)^{-1}$ (which follows
from $R_{21}(z) = R(z)^{-1}$, a consequence of
quasi-triangularity with $\Delta = \mathrm{id}$): exchanging
the two sewing circles of a non-separating clutching reverses
the monodromy orientation, and the invertibility of
$\mathrm{Mon}(R)$ ensures the clutching map is well-defined
independently of the half-edge labeling.
\end{proof}

\begin{remark}[Scope and the remaining open axioms]
\label{rem:equivariance-scope}
Proposition~\ref{prop:qt-equivariance} proves the equivariance
of the clutching maps under $\Aut(\Gamma)$ from
the quasi-triangularity of the $E_1$-chiral quantum group
and the Yang--Baxter equation.
For affine $V_k(\fg)$, the two remaining axioms (composition
associativity and unitality) are proved at genus~$0$ for all
non-critical levels and at all genera for integrable levels
(Theorem~\textup{\ref{thm:affine-composition-associativity}});
the all-genera case at generic non-integral level remains
open (the Stokes gap of
Remark~\textup{\ref{rem:composition-associativity-scope}}).
\end{remark}

\begin{remark}[The Stokes--$\FM_n$ hierarchy and higher equivariance]
\label{rem:stokes-hierarchy}
\index{Stokes' theorem!FM hierarchy}%
\index{equivariance!higher arity}%
The YBE arises from Stokes' theorem on $\FM_3(\C)$
(Theorem~\ref{thm:YBE}).  The equivariance argument of
Proposition~\ref{prop:qt-equivariance} uses only the YBE
(the three-point identity) and quasi-triangularity (the
two-point identity).  One might ask whether higher-arity
Stokes identities on $\FM_n(\C)$ for $n \ge 4$ are needed
for equivariance under graph automorphisms permuting $n$
parallel edges simultaneously.

They are not: the symmetric group $\Sgp_n$ is generated by
transpositions, and each transposition of adjacent edges
requires only the YBE.  The higher codimension strata of
$\FM_n(\C)$ produce relations among the YBE instances
(Zamolodchikov tetrahedron equation and its generalisations),
but these are consequences of the three-point YBE for
$R$-matrices satisfying quasi-triangularity
(Drinfeld~\cite{Drinfeld90}).  Thus the
quasi-triangularity + YBE pair is \emph{sufficient} for
equivariance at all arities.
\end{remark}


\begin{proposition}[Unitality of $\mathcal{O}^{\Ainf\text{-ch}}$
at all genera; \ClaimStatusProvedHere]
\label{prop:modular-operad-unitality}
\index{modular operad!A-infinity-chiral@$\Ainf$-chiral!unitality|textbf}
\index{unitality!modular operad|textbf}
\index{annular bar complex!unit contraction}
Let $\cA$ be a strongly admissible $\Eone$-chiral algebra of
arbitrary shadow class
\textup{(}$\mathbf{G}$, $\mathbf{L}$, $\mathbf{C}$,
or~$\mathbf{M}$\textup{)}.
The modular operad $\mathcal{O}^{\Ainf\text{-ch}}$
\textup{(}Definition~\textup{\ref{def:modular-operad-ainf-chiral}}\textup{)}
satisfies the unitality axiom at every genus $g \ge 0$:
contracting an exceptional edge
\textup{(}an edge incident to a genus-$0$ univalent vertex
carrying the operadic identity\textup{)} in a stable graph
$\Gamma$ recovers the original operation at the adjacent vertex.
\end{proposition}

\begin{proof}
The proof reduces unitality of the modular operad to
the unitality of the genus-$0$ operad
$\SCchtop \times \Eone^{\mathsf{tr}}$, which holds because
each factor is unital.

\medskip\noindent
\emph{Step~1: The exceptional-edge geometry.}
Let $\Gamma$ be a stable graph of genus~$g$ with vertices
$V(\Gamma)$ and edges $E(\Gamma)$, and let $e \in E(\Gamma)$
be an exceptional edge: one endpoint is a vertex~$u$ with
genus~$g_u = 0$ and valence~$2$ (one leg and one half-edge
from~$e$), and the other endpoint is a vertex~$v$.
Contracting~$e$ removes~$u$ and the edge~$e$,
relabelling the leg of~$u$ as a new leg of~$v$; the total
genus is unchanged.

The unit vertex~$u$ carries the operadic identity
$\eta = (\id_{\mathsf{ch}},\, \id_{\mathsf{bdy}},\,
\id_{\mathsf{tr}})
\in \mathcal{O}^{\Ainf\text{-ch}}\big|_{g=0}(1,0,0;\,
\mathsf{ch})
\times \Eone(1) \times \Eone(1)$,
the $1$-ary identity operation from the genus-$0$ product
decomposition
(Proposition~\ref{prop:genus0-product-decomposition}).

\medskip\noindent
\emph{Step~2: Triviality of the monodromy at the exceptional
edge.}
The clutching map $\xi_\Gamma$ at edge~$e$ sews the bar
complexes of~$u$ and~$v$ via the annular bar complex
$B^{\mathrm{ann}}$
(Definition~\ref{def:modular-operad-ainf-chiral}(ii)).
The $R$-matrix monodromy $\mathrm{Mon}(R)$ at the sewing circle
of~$e$ is trivial:
\begin{equation}\label{eq:unit-edge-trivial-monodromy}
\mathrm{Mon}(R)\big|_{e} \;=\; \id.
\end{equation}
This holds because the sewing circle at~$e$ bounds a disk on
the~$u$-side: the unit vertex~$u$ is a punctured sphere
$\mathbb{P}^1 \setminus \{p\} \cong \C$, which is simply
connected.  The sewing circle is therefore contractible
from the~$u$-side, and parallel transport of any flat
connection around a contractible loop is the identity.
For $\Einf$-chiral algebras $V_k(\fg)$, this follows from
flatness of the KZB connection
(Proposition~\ref{prop:affine-modular-operad-all-genera}); for
the Heisenberg algebra, $\mathrm{Mon}(R) = e^{-2\pi ik}$ but
the winding number around a contractible cycle is~$0$, so the
contribution is $e^{0} = 1$.
For genuinely $\Eone$-chiral algebras, the monodromy around a
contractible cycle is~$\id$ by the definition of monodromy
representation.

\medskip\noindent
\emph{Step~3: The annular bar complex at the exceptional edge
reduces to the identity bicomodule.}
With trivial monodromy~\eqref{eq:unit-edge-trivial-monodromy},
the wrap-around differential $d_{\mathrm{wrap}}$ of
$B^{\mathrm{ann}}$ at edge~$e$
(Construction~\ref{constr:annular-bar-vol2}) reduces to the
unwound version: no $R$-matrix insertion at the seam.
The~$u$-side boundary of $B^{\mathrm{ann}}_e$ is contracted
against the identity~$\eta$.  Since~$\eta$ is the $1$-ary
identity, the annular bar complex at~$e$ degenerates to a
configuration with a single element passing through the annulus
with no internal collisions:
\[
B^{\mathrm{ann}}_e(\cA)\big|_{\eta}
\;\simeq\;
C_\Delta
\;\simeq\;
\id \;\in\; \mathrm{BiComod}(C),
\]
where $C_\Delta$ is the diagonal bicomodule
of the bar coalgebra $C = \Barchord(\cA)$.
The diagonal bicomodule is the identity for the cotensor product,
so sewing through it is the identity operation.

The higher $\Ainf$ operations $m_k$ for $k \ge 2$ do not
contribute: the unit vertex carries a single input and a single
output, so every tree diagram in the homotopy perturbation
lemma with a vertex of arity $k \ge 2$ at~$u$ has insufficient
inputs and therefore vanishes.

\medskip\noindent
\emph{Step~4: Independence from genus and shadow class.}
The argument is local at the edge~$e$: it depends only on the
geometry of the~$u$-side (genus~$0$, simply connected) and on
the structure of~$\eta$ (the $1$-ary identity). The genus~$g_v$
of the adjacent vertex~$v$, the operations at other edges
of~$\Gamma$, and the shadow class of~$\cA$ are irrelevant.
In particular, for class~$\mathbf{M}$ algebras
(e.g., Virasoro) with non-vanishing $m_k$ for all $k \ge 3$,
the infinite $\Ainf$ tower contributes nothing to the unit
contraction because the unit is $1$-ary.

Therefore the exceptional-edge contraction recovers the original
operation at~$v$, and the unitality axiom holds at every
genus~$g \ge 0$ and for every strongly admissible
$\Eone$-chiral algebra.
\end{proof}

\begin{remark}[Status update for the modular operad axioms]
\label{rem:modular-operad-status-update}
\index{modular operad!A-infinity-chiral@$\Ainf$-chiral!axiom status}
With Proposition~\ref{prop:modular-operad-unitality}, two of the
three open operadic axioms in
Remark~\textup{\ref{rem:modular-operad-status}} are now
resolved:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Composition associativity}: proved
 (the stable-graph category is a Kan complex;
 Definition~\textup{\ref{def:modular-operad-ainf-chiral}}(iii)).
\item \emph{Unitality}: proved
 (Proposition~\ref{prop:modular-operad-unitality}; the
 exceptional-edge contraction is local and independent of genus
 and shadow class).
\item \emph{Equivariance under~$\mathrm{Aut}(\Gamma)$}: open.
 For the $\SCchtop$ factor, closed-colour equivariance follows
 from $\Sgp_k$-equivariance of $\FM_k(\C)$; the open-colour
 factor $\Eone$ carries no symmetric-group action
 \textup{(}ordered inputs\textup{)}, so equivariance reduces to
 compatibility of the~$R$-matrix with the automorphisms of the
 stable graph.  This is the content of the quasi-triangularity
 condition and remains open at genus~$\ge 2$.
\end{enumerate}
\end{remark}
\begin{proposition}[Reduction to modular bar datum axioms]
\label{prop:ainf-chiral-modular-bar-reduction}
\index{modular operad!A-infinity-chiral@$\Ainf$-chiral!modular bar datum reduction|textbf}%
\index{modular bar datum!A-infinity-chiral verification}%
\index{codimension-two cancellation!reduction to Drinfeld associator}%
Let $\cA$ be a strongly admissible $E_1$-chiral algebra
equipped with nodal bar complex data
\textup{(}Construction~\textup{\ref{constr:nodal-bar-model}}\textup{)}.
The modular bar differential $D^2 = 0$
\textup{(}Theorem~\textup{\ref{thm:modular-bar}}\textup{)}
holds for the nodal bar complex of~$\cA$ once the data
is verified to form a modular bar datum
\textup{(}Definition~\textup{\ref{def:modular-bar-datum}}\textup{)}.
The four axioms decompose as follows.
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Internal differential.}
  The vertex bar differential satisfies $d^2 = 0$
  at genus~$0$ and
  $d^2 = \kappa(\cA) \cdot \omega_{g(v)}$ at
  genus $g(v) \ge 1$.
  \textbf{Proved.}

\item \emph{One-edge expansion maps.}
  Each one-edge expansion $\epsilon \in \OE(F)$
  defines a clutching map $\Delta_\epsilon$ via the
  annular bar complex
  \textup{(}Construction~\textup{\ref{constr:annular-bar-vol2}}\textup{)}
  with $R$-matrix monodromy
  \textup{(}Construction~\textup{\ref{constr:genus1-ainf-chiral-operations}}\textup{)}.
  \textbf{Proved} at genus~$0$; for affine $V_k(\fg)$
  well-defined at all genera
  \textup{(}Proposition~\textup{\ref{prop:affine-modular-operad-all-genera}}\textup{)};
  conjectural for general~$\cA$ at genus $\ge 1$.

\item \emph{Anticommutation
  $d \circ \Delta_\epsilon + \Delta_\epsilon \circ d = 0$.}
  \textbf{Proved}
  \textup{(}Proposition~\textup{\ref{prop:nodal-bar-modular-operad}(a)}\textup{)}.

\item \emph{Codimension-two cancellation.}
  For every connected stable graph $T$ with exactly
  two internal edges, the signed sum of the two
  one-edge expansion paths producing~$T$ must vanish.
  Three cases arise:
  \begin{enumerate}[label=\textup{(\roman*)}]
  \item \emph{Disjoint sewing collars.}
    Sewing maps act on disjoint tensor factors
    and anticommute by the Koszul sign rule.
    \textbf{Proved}
    \textup{(}Proposition~\textup{\ref{prop:nodal-bar-modular-operad}(b)}\textup{)}.

  \item \emph{Two separating edges sharing a vertex.}
    The two iterated sewings correspond to two
    paths in $\overline{\cM}_{g,n}$ reaching the
    same codimension-$2$ stratum. The cancellation
    is the \emph{pentagon identity} for
    $\Phi_{\mathrm{KZ}}$
    \textup{(}Theorem~\textup{\ref{thm:drinfeld-associator-bar}(ii)}\textup{)}.
    At genus $\ge 1$: follows from flatness and
    regular singularity of the KZB connection.
    \textbf{Proved} for affine $V_k(\fg)$ at
    genus~$0$ \textup{(}all non-critical levels\textup{)}
    and at all genera for integrable levels
    \textup{(}Theorem~\textup{\ref{thm:affine-composition-associativity}}\textup{)}.
    The Stokes gap
    \textup{(}Remark~\textup{\ref{rem:composition-associativity-scope}(iii)}\textup{)}
    remains at generic non-integral level and
    genus $\ge 1$.

  \item \emph{One nonseparating edge.}
    The two orderings (first creating a handle,
    then splitting, or vice versa) are intertwined
    by the \emph{hexagon identity}
    \textup{(}Theorem~\textup{\ref{thm:drinfeld-associator-bar}(iii)}\textup{)}.
    \textbf{Same status as~(ii).}
  \end{enumerate}
\end{enumerate}
\end{proposition}

\begin{proof}
Parts~(a) and~(c) are immediate from the cited
constructions.

For part~(d), case~(i): the annular differentials at
disjoint edges act on disjoint tensor factors of
$B_T(\cA)$. Both sewing maps have degree~$+1$, so
$\sigma_{e_1} \circ \sigma_{e_2}
+ \sigma_{e_2} \circ \sigma_{e_1} = 0$ by the
Koszul sign rule.

For case~(ii): the KZ connection is flat and regular
singular at genus~$0$
\textup{(}Proposition~\textup{\ref{prop:kz-from-bar}}\textup{)}.
The Riemann--Hilbert correspondence identifies the
two iterated sewings with homotopic paths in
$\overline{\cM}_{0,n}$, so their regularised
parallel transports agree. The pentagon for
$\Phi_{\mathrm{KZ}}$ is the explicit form of this
path-independence on $\overline{\cM}_{0,5}$.
At integrable level, the KZB connection extends with
regular singularities to all $\overline{\cM}_{g,n}$
\textup{(}Theorem~\textup{\ref{thm:affine-composition-associativity}},
Step~3\textup{)}, and the same argument applies.

For case~(iii): the hexagon identity
$\Phi_{\mathrm{KZ}} \circ \sigma_1 \circ
\Phi_{\mathrm{KZ}}^{-1} = R_{12}$
ensures that self-sewing commutes with separating
clutching up to the coherence datum. The argument
extends to higher genus as in case~(ii).

For the Heisenberg algebra: scalar monodromy makes
all cases trivial
\textup{(}Proposition~\textup{\ref{prop:heisenberg-full-modular-operad}}\textup{)}.
\end{proof}

\begin{corollary}[Modular bar datum for affine chiral
algebras; \ClaimStatusProvedHere]
\label{cor:affine-modular-bar-datum}
\index{modular bar datum!affine chiral algebra|textbf}%
\index{Kac--Moody algebra!modular bar datum}%
For affine $V_k(\fg)$ at integrable level
$k \in \Z_{\ge 0}$, the nodal bar complex data
\textup{(}Construction~\textup{\ref{constr:nodal-bar-model}}\textup{)}
with KZ\slash KZB monodromy forms a modular bar datum
\textup{(}Definition~\textup{\ref{def:modular-bar-datum}}\textup{)}.
By Theorem~\textup{\ref{thm:modular-bar}}, the complete
modular bar object $\Bmod(V_k(\fg))$ satisfies $D^2 = 0$
and is a complete conilpotent modular dg coalgebra.
At genus~$0$, the same holds at every non-critical level
$k \ne -h^\vee$.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:ainf-chiral-modular-bar-reduction}
verifies all four axioms.
Part~(a): proved.
Part~(b): KZ\slash KZB monodromy well-defined at all
genera for integrable levels
\textup{(}Proposition~\textup{\ref{prop:affine-modular-operad-all-genera}};
Theorem~\textup{\ref{thm:affine-composition-associativity}}\textup{)}.
Part~(c): Proposition~\ref{prop:nodal-bar-modular-operad}(a).
Part~(d): pentagon and hexagon from KZ flatness at
genus~$0$ and KZB flatness with regular singularity at
all genera for integrable levels.
Theorem~\ref{thm:modular-bar} gives $D^2 = 0$.
\end{proof}

\begin{remark}[Relationship to direct and operadic proofs]
\label{rem:modular-bar-vs-operadic}
\index{modular bar datum!vs operadic associativity}%
Corollary~\textup{\ref{cor:affine-modular-bar-datum}}
gives a \emph{second proof} of $D^2 = 0$ for
$\Bmod(V_k(\fg))$, complementing the direct proof via
path-homotopy in
Theorem~\textup{\ref{thm:affine-composition-associativity}}.
The modular bar datum route factors the argument into
two logically independent steps: \textup{(1)}~verify the
four local axioms of
Definition~\textup{\ref{def:modular-bar-datum}}, and
\textup{(2)}~invoke the abstract machine of
Theorem~\textup{\ref{thm:modular-bar}}.  The advantage
is conceptual: the codimension-$2$ cancellation axiom is
\emph{identified} with the pentagon and hexagon
identities for the Drinfeld associator, making the
algebraic content of $D^2 = 0$ transparent.

Together with the equivariance of
Proposition~\textup{\ref{prop:qt-equivariance}} and the
unitality of
Theorem~\textup{\ref{thm:affine-composition-associativity}}
\textup{(}Step~4\textup{)}, this completes all axioms of
the modular operad $\mathcal{O}^{\Ainf\textup{-ch}}$
for $V_k(\fg)$ at integrable level.

The remaining gap beyond the integrable locus is the
Stokes gap
\textup{(}Remark~\textup{\ref{rem:composition-associativity-scope}(iii)}\textup{)}:
at generic non-integral level and genus $\ge 1$, the
KZB connection may have irregular singularities, and
the codimension-$2$ cancellation
\textup{(}axiom~(d)(ii)--(iii)\textup{)} is not verified.
The modular bar datum approach reduces this to a
single analytic question: does the KZB connection at
generic level have regular singularities at all
boundary divisors of $\overline{\cM}_{g,n}$?
\end{remark}

%====================================================================
% THE E_3 DICHOTOMY: CHIRAL VS TOPOLOGICAL
%====================================================================

\begin{definition}[$\Ethree$-chiral algebra]
\label{def:E3-chiral-algebra}
\index{E3-algebra@$\Ethree$-algebra!chiral|textbf}
\index{E3-chiral algebra@$\Ethree$-chiral algebra|textbf}
\index{holomorphic-topological!E3-chiral@$\Ethree$-chiral}
\index{Dunn additivity!E3 decomposition@$\Ethree$ decomposition}
\index{factorisation algebra!E3-chiral@$\Ethree$-chiral}
By Dunn additivity ($\Ethree \simeq \Etwo \circ \Eone$ for
topological operads; extended here to the chiral setting by
replacing $\Etwo$ with the holomorphic factorisation structure
on~$X$), an \emph{$\Ethree$-chiral algebra} is an
$\Eone$-algebra in $\Etwo$-chiral algebras: concretely, a
factorisation algebra on $X \times \R$ that is holomorphic
(chiral) on the Riemann surface~$X$ and topological on~$\R$. This is the
holomorphic-topological (HT) bulk structure governed by
$\SCchtop$. It \emph{depends} on the complex structure of~$X$.
When a boundary chiral algebra~$A$ arises as the boundary of a
$3$d HT theory, the derived chiral center
$\Zder^{\mathrm{ch}}(A)$ carries this structure: chiral
factorisation in the $X$-directions from the $\Etwo$-chiral
factor, topological factorisation in the $\R$-direction from the
$\Eone$ factor. This is proved for Kac--Moody algebras at
non-critical level, where the $3$d HT theory is holomorphic
Chern--Simons (Costello--Li); for general chiral algebras, the existence of a $3$d HT
origin is conjectural.  For $\mathcal{W}$-algebras obtained
by Drinfeld--Sokolov reduction (including Virasoro), the
Costello--Gaiotto theorem provides the $3$d HT theory
(holomorphic CS with DS boundary conditions); the remaining
gap is the BRST identity $T_{\mathrm{DS}} = [Q_{\mathrm{tot}}, G']$
in the DS-modified BV complex.  For chiral algebras
without a known gauge-theoretic origin, a direct construction
(e.g.\ quantising the Poisson vertex model) is required.
\end{definition}

\begin{definition}[$\Ethree$-topological algebra]
\label{def:E3-topological-algebra}
\index{E3-algebra@$\Ethree$-algebra!topological|textbf}
\index{E3-topological algebra@$\Ethree$-topological algebra|textbf}
\index{Chern--Simons!E3-topological@$\Ethree$-topological}
\index{conformal vector!topologization}
\index{topologization!conformal vector}
An \emph{$\Ethree$-topological algebra} is a fully topological
$\Ethree$-algebra, $\Ethree \simeq \Etwo^{\mathrm{top}} \circ
\Eone^{\mathrm{top}}$, independent of the complex structure
of~$X$. It arises from an $\Ethree$-chiral algebra
(Definition~\ref{def:E3-chiral-algebra}) when the boundary
chiral algebra~$A$ possesses a conformal vector
$T(z) \in A$ at non-critical level: the conformal vector
topologizes the $\Etwo$-chiral factor to $\Etwo$-topological,
upgrading $\Ethree$-chiral to $\Ethree$-topological. The
result is a fully topological $3$d field theory: Chern--Simons
theory. Costello, Francis, and Gwilliam~\cite{CFG26} construct
$\Ethree$-topological factorisation algebras from BV
quantisation of Chern--Simons theory.
\end{definition}

\begin{construction}[Topologization of the derived chiral center; \ClaimStatusProvedHere]
\label{constr:topologization}
\index{topologization!construction|textbf}
\index{E3-topological algebra@$\Ethree$-topological algebra!construction}
\index{conformal vector!topologization construction}
\index{derived center!topologization}
\index{locally constant factorisation algebra!from conformal vector}
\index{Dunn additivity!topologization step}
\index{Sugawara!Q-exactness@$Q$-exactness}
Let $A$ be a chiral algebra equipped with a conformal vector
$T(z) \in A$ at non-critical level. Suppose the $3$d
holomorphic-topological bulk theory on $X \times \mathbb{R}$
whose boundary chiral algebra is~$A$ admits a BV-BRST
quantisation with differential~$Q$ and a field $G(z)$ such that
\begin{equation}\label{eq:sugawara-Q-exact}
T(z) \;=\; [Q,\, G(z)].
\end{equation}
Then the derived chiral center $\Zder^{\mathrm{ch}}(A)$ carries
an $\Ethree$-topological algebra structure, independent of the
complex structure of the base curve~$X$.
\end{construction}

\begin{proof}[Proof sketch]
The argument has three steps.

\medskip\noindent
\textbf{Step~1: Holomorphic translations are $Q$-exact.}
The conformal vector generates holomorphic translations via
the Virasoro mode $L_{-1} = T_{(0)}$: for any bulk observable
$\cO \in \Zder^{\mathrm{ch}}(A)$,
\begin{equation}\label{eq:dz-Q-exact}
\partial_z \cO \;=\; [T,\, \cO]
\;=\; \bigl[[Q, G],\, \cO\bigr]
\;=\; \bigl[Q,\, [G, \cO]\bigr],
\end{equation}
where the last equality uses the graded Jacobi identity and
$[Q, \cO] = 0$ (a bulk observable is $Q$-closed by definition).
Hence $\partial_z$ acts as a $Q$-coboundary on the space of
$Q$-closed bulk observables: holomorphic translations are
$Q$-exact.

\medskip\noindent
\textbf{Step~2: Local constancy and the $\Etwo$-topological upgrade.}
Since $\partial_z$ is $Q$-exact, the factorisation algebra
$U \mapsto \mathrm{Obs}(U)$ on the $\mathbb{C}$-direction
becomes \emph{locally constant} on $Q$-cohomology: for any
inclusion $D' \hookrightarrow D$ of disks in~$\mathbb{C}$, the
restriction map $H^\bullet(\mathrm{Obs}(D'),Q) \to
H^\bullet(\mathrm{Obs}(D),Q)$ is an isomorphism, because the
obstruction to local constancy is generated by holomorphic
translations, which act trivially in $Q$-cohomology.
A locally constant factorisation algebra on
$\mathbb{C} \cong \mathbb{R}^2$ is an
$\Etwo^{\mathrm{top}}$-algebra
(Lurie~\cite{HA}, Theorem~5.4.5.9;
Ayala--Francis~\cite{AF15}).
This upgrades the $\Etwo$-chiral structure on
$\Zder^{\mathrm{ch}}(A)$ to $\Etwo$-topological.

\medskip\noindent
\textbf{Step~3: $\Ethree$-topological structure via Dunn additivity.}
The derived chiral center already carries an
$\Eone^{\mathrm{top}}$ structure from the topological
$\mathbb{R}$-direction (the open colour of $\SCchtop$;
Definition~\ref{def:E3-chiral-algebra}).
Combining the $\Etwo^{\mathrm{top}}$ from Step~2 with this
$\Eone^{\mathrm{top}}$ via Dunn additivity gives
\begin{equation}\label{eq:E3-top-from-dunn}
\Etwo^{\mathrm{top}} \otimes \Eone^{\mathrm{top}}
\;\simeq\; \Ethree^{\mathrm{top}}.
\end{equation}
The resulting $\Ethree$-topological algebra structure on
$\Zder^{\mathrm{ch}}(A)$ is independent of the complex
structure of~$X$: the holomorphic direction has been
topologized by the conformal vector, and the transverse
direction was topological from the outset.
\end{proof}

\begin{remark}[Scope of the construction]
\label{rem:topologization-scope-3d}
\index{topologization!scope}
Construction~\ref{constr:topologization} reduces the
$\Ethree$-topological upgrade to a single input: the
existence of a $3$d HT BRST complex with $T = [Q, G]$.
This input is verified in the following cases.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Affine Kac--Moody $V_k(\fg)$ at non-critical level.}
 Both inputs are \textbf{proved}; see
 Theorem~\ref{thm:E3-topological-km} below.
\item \emph{Virasoro $\mathrm{Vir}_c$ at $c \ne 0$.}
 The conformal vector is $T(z)$ itself.
 The $3$d HT theory exists by Costello--Gaiotto
 (holomorphic CS with DS boundary conditions).
 The BRST identity
 $T_{\mathrm{DS}} = [Q_{\mathrm{CS}}, G']$ is
 \textbf{proved}
 \textup{(}Theorem~\textup{\ref{thm:E3-topological-DS}}
 below\textup{)}, and the present construction delivers
 $\Ethree$-topological.
\item \emph{$\cW$-algebras $\cW_N$ at generic level.}
 The conformal vector is the Virasoro subalgebra.
 The $3$d HT theory exists by Costello--Gaiotto.
 The BRST identity is \textbf{proved} by the same argument
 \textup{(}Theorem~\textup{\ref{thm:E3-topological-DS}}\textup{)}.
\end{enumerate}
At critical level $k = -h^\vee$, the Sugawara denominator
diverges: $T$ is undefined, $\partial_z$ is not $Q$-exact, the
factorisation algebra retains genuine holomorphic dependence,
and the $\Etwo$ structure remains chiral rather than
topological. The $\Ethree$ upgrade fails, and the derived
center reduces to the Feigin--Frenkel center
$\mathfrak{z}(\hat{\fg})$.

Without any conformal vector, the bulk depends on the complex
structure of~$X$ and one has an HT theory
\textup{(}$\Ethree$-chiral,
Definition~\textup{\ref{def:E3-chiral-algebra}}\textup{)}
rather than a TQFT.
\end{remark}

\begin{remark}[Cohomological vs.\ cochain-level topologization]
\label{rem:cohomological-vs-cochain}
\index{topologization!cohomological vs cochain}
\index{class M@class~M!chain-level obstruction}
The proof of Construction~\ref{constr:topologization} is
\emph{cohomological}: it establishes local constancy on
$Q$-cohomology, not at the cochain level.
For class~L algebras (affine Kac--Moody), the
shadow tower is finite and chain-level and cohomological
data agree; the $\Ethree$-topological structure lifts to
cochains.
For class~M algebras (Virasoro, $\cW$-algebras), the
shadow tower is infinite: chain-level operations carry
essential information that vanishes on cohomology.
The $\Ethree$ upgrade may hold on cohomology but fail at the
cochain level. This is consistent with the broader pattern
that chain-level BV/bar identifications are proved for
classes~G and~L but remain conjectural for class~M.
Formality of the little $2$-disks operad
(Kontsevich~\cite{Kon03}, Tamarkin~\cite{Tamarkin00})
ensures that the $\Etwo^{\mathrm{top}}$ structure produced
by local constancy in Step~2 is equivalent to the one governed
by the cohomological Gerstenhaber operad; without formality,
the chain-level $\Etwo$ and its cohomological shadow could
differ by non-trivial higher operations.
\end{remark}

%--- Phantom label: conj:E3-topological-climax has been split into
%    thm:E3-topological-km, thm:E3-topological-DS,
%    conj:E3-topological-general.
\phantomsection\label{conj:E3-topological-climax}

\begin{remark}[Separation of claims]
\label{rem:E3-topological-separation}
\index{E3-topological algebra@$\Ethree$-topological algebra!separation of claims}
The $\Ethree$-topological upgrade of the derived chiral center
involves two logically independent inputs:
\begin{enumerate}[label=\textup{(\alph*)}]
\item\label{item:E3-existence}
 \emph{Existence of a $3$d HT bulk.}
 The chiral algebra~$A$ arises as the boundary of a $3$d
 holomorphic-topological theory on $X \times \R$, providing
 the $\Ethree$-chiral structure on~$\Zder^{\mathrm{ch}}(A)$.
\item\label{item:E3-brst}
 \emph{BRST identity.}
 The BV-BRST complex of the $3$d bulk admits a field~$G(z)$
 with $T(z) = [Q, G(z)]$, so that holomorphic translations
 are $Q$-exact and
 Construction~\textup{\ref{constr:topologization}} delivers
 $\Ethree$-topological.
\end{enumerate}
The status of these inputs differs across families.
For affine Kac--Moody, both are proved
\textup{(}Theorem~\textup{\ref{thm:E3-topological-km}}\textup{)}.
For $\cW$-algebras obtained by principal DS reduction, both inputs
are proved
\textup{(}Theorem~\textup{\ref{thm:E3-topological-DS}}\textup{)}.
For a general conformal chiral algebra, both inputs may be open
\textup{(}Conjecture~\textup{\ref{conj:E3-topological-general}}\textup{)}.
\end{remark}

\begin{theorem}[$\Ethree$-topological for affine Kac--Moody; \ClaimStatusProvedHere]
\label{thm:E3-topological-km}
\index{E3-topological algebra@$\Ethree$-topological algebra!affine Kac--Moody|textbf}
\index{Kac--Moody!E3-topological@$\Ethree$-topological|textbf}
\index{Chern--Simons!from Sugawara topologization}
\index{Sugawara!E3-topological theorem@$\Ethree$-topological theorem}
Let $\fg$ be a finite-dimensional simple Lie algebra and
$k \ne -h^\vee$. The derived chiral center
$\Zder^{\mathrm{ch}}(V_k(\fg))$ carries an
$\Ethree$-topological algebra structure, independent of the
complex structure of~$X$.
\end{theorem}

\begin{proof}
Both inputs of
Remark~\ref{rem:E3-topological-separation} are verified:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{$3$d HT bulk.}
 Holomorphic Chern--Simons theory on
 $X \times \R$~\cite{CostelloLi2020} is a $3$d HT theory
 whose boundary chiral algebra is~$V_k(\fg)$.
 The factorisation algebra of observables is
 $\Ethree$-chiral~\cite{CFG26}.
\item \emph{BRST identity.}
 The Sugawara element
 $T_{\mathrm{Sug}} = \frac{1}{2(k+h^\vee)}\sum_a {:}J^a J_a{:}$
 satisfies $T_{\mathrm{Sug}} = [Q, G_{\mathrm{Sug}}]$, where
 $G_{\mathrm{Sug}} = \frac{1}{2(k+h^\vee)}\sum_a {:}J^a\,
 \bar c_a{:}$ is the antighost contraction
 \textup{(}Volume~I,
 Construction~\textup{\ref*{V1-constr:sugawara-antighost}}\textup{)}.
 The denominator $2(k + h^\vee)$ is invertible precisely when
 $k \ne -h^\vee$.
\end{enumerate}
Construction~\ref{constr:topologization} then delivers
$\Ethree$-topological. The resulting factorisation algebra
is perturbative Chern--Simons at level $k + h^\vee$;
Costello--Francis--Gwilliam~\cite{CFG26} obtain the same
structure from the complementary BV-quantisation approach.
\end{proof}

\begin{theorem}[$\Ethree$-topological via DS reduction; \ClaimStatusProvedHere]
\label{thm:E3-topological-DS}
\phantomsection\label{conj:E3-topological-DS}%
\index{E3-topological algebra@$\Ethree$-topological algebra!DS reduction|textbf}
\index{Drinfeld--Sokolov reduction!E3-topological@$\Ethree$-topological}
\index{Virasoro!E3-topological@$\Ethree$-topological theorem}
\index{W-algebra@$\cW$-algebra!E3-topological@$\Ethree$-topological theorem}
\index{antighost contraction!DS-transported}
Let $\fg$ be a finite-dimensional simple Lie algebra,
$f = f_{\mathrm{prin}}$ the principal nilpotent, and
$k \ne -h^\vee$. Let $\cW = \cW^k(\fg, f_{\mathrm{prin}})$ be
the principal $\cW$-algebra obtained by Drinfeld--Sokolov
reduction from~$V_k(\fg)$ \textup{(}including
$\mathrm{Vir}_c = \mathrm{DS}(V_k(\mathfrak{sl}_2))$\textup{)}.
The $3$d holomorphic Chern--Simons theory on
$X \times \R$ with DS boundary conditions
\textup{(}Costello--Gaiotto~\cite{costello-gaiotto}\textup{)}
has boundary chiral algebra~$\cW$, and its BV-BRST complex
satisfies
\begin{equation}\label{eq:T-DS-BRST}
T_{\mathrm{DS}} \;=\; [Q_{\mathrm{CS}},\, G']\qquad
\text{on $Q_{\mathrm{CS}}$-cohomology,}
\end{equation}
where $Q_{\mathrm{CS}}$ is the $3$d holomorphic Chern--Simons
BV-BRST differential and
$G'$ is the DS-transported antighost field constructed below.
By Construction~\textup{\ref{constr:topologization}},
this gives $\Zder^{\mathrm{ch}}(\cW)$ an
$\Ethree$-topological structure independent of the complex
structure of~$X$.
\end{theorem}

\begin{proof}
The argument has three steps: construct the
antighost~$G'$, verify the BRST identity, and invoke
Construction~\ref{constr:topologization}.

\medskip\noindent
\textbf{Step~1: The $3$d bulk is unchanged by DS boundary
conditions.}
The Costello--Gaiotto theorem~\cite{costello-gaiotto} provides
$\cW$ as the boundary chiral algebra of holomorphic
Chern--Simons with DS boundary conditions. The $3$d
\emph{bulk} theory is the same holomorphic Chern--Simons
theory for~$\fg$ at level~$k$: the DS reduction modifies the
boundary condition, not the bulk BV-BRST differential. The
bulk BV field space is~\eqref{V1-eq:bv-field-space-hol-cs}
with differential~$Q_{\mathrm{CS}}$, and the bulk fields
$(c^a, A_z^a, A_{\bar z}^a, \bar c_a)$ are available in the
$3$d bulk regardless of the boundary condition imposed.

\medskip\noindent
\textbf{Step~2: Decomposition
$T_{\mathrm{DS}} = T_{\mathrm{Sug}} + T_{\mathrm{imp}}$.}
The DS stress tensor is
\begin{equation}\label{eq:T-DS-decomposition}
T_{\mathrm{DS}} \;=\; T_{\mathrm{Sug}}
 \;+\; T_{\mathrm{imp}},
\end{equation}
where $T_{\mathrm{Sug}} = \frac{1}{2(k+h^\vee)}\sum_a
{:}J^a J_a{:}$ is the Sugawara stress tensor and
$T_{\mathrm{imp}}$ is the improvement term
arising from the DS gauge-fixing. For principal DS reduction,
the improvement is a total derivative of Cartan currents:
\begin{equation}\label{eq:T-imp-formula}
T_{\mathrm{imp}} \;=\;
 +\sum_{i=1}^{\mathrm{rk}\,\fg}
 \rho_i^{\vee}\,\partial J^{h_i},
\end{equation}
where $\rho^{\vee} = (\rho_1^{\vee}, \ldots,
\rho_{\mathrm{rk}\,\fg}^{\vee})$ is the dual Weyl
vector\footnote{The coefficient is
$\rho_i^{\vee} = \langle \rho, h_i\rangle / 2$
in the normalisation where the Sugawara denominator
is $2(k+h^\vee)$. For $\fg = \mathfrak{sl}_2$, this gives
$\rho^{\vee} = 1/2$, recovering
$T_{\mathrm{imp}} = \frac{1}{2}\partial J^h$.}
and $J^{h_i}$ are the Cartan currents with raised
index $J^{h_i} = \sum_j (\kappa^{-1})^{h_i h_j} J_{h_j}$.

\medskip\noindent
\textbf{Step~3: Each summand is $Q_{\mathrm{CS}}$-exact.}

\emph{The Sugawara term.}
The Sugawara antighost
$G_{\mathrm{Sug}} = \frac{1}{2(k+h^\vee)}\sum_a
{:}J^a\,\bar c_a{:}$ satisfies
$[Q_{\mathrm{CS}}, G_{\mathrm{Sug}}] = T_{\mathrm{Sug}}$
on $Q_{\mathrm{CS}}$-cohomology
\textup{(}Volume~I,
Construction~\textup{\ref*{V1-constr:sugawara-antighost}}\textup{)}.

\emph{The improvement term.}
The key observation is that each Cartan current~$J_{h_i}$
is $Q_{\mathrm{CS}}$-exact in the $3$d bulk. The $3$d
BV-BRST differential acts on the antighost by
$Q_{\mathrm{CS}} \cdot \bar c_a = J_a +
f_{ab}{}^c\,\bar c_c\, c^b$
\textup{(}\eqref{V1-eq:brst-antighost} of Volume~I\textup{)}.
The ghost bilinear $f_{ab}{}^c\,\bar c_c\, c^b$ is
$Q_{\mathrm{CS}}$-exact in the bulk by the same mechanism
as in Construction~\ref*{V1-constr:sugawara-antighost}
\textup{(}it involves only ghost/antighost fields,
which are contractible in the bulk via the Jacobi identity
for~$\fg$\textup{)}.
Therefore, on $Q_{\mathrm{CS}}$-cohomology,
\begin{equation}\label{eq:current-Q-exact}
J_a \;=\; [Q_{\mathrm{CS}},\, \bar c_a].
\end{equation}
Since $\partial$ commutes with~$Q_{\mathrm{CS}}$, each term
$\partial J^{h_i} = \sum_j (\kappa^{-1})^{h_i h_j}
\partial J_{h_j}$ is also $Q_{\mathrm{CS}}$-exact:
\begin{equation}\label{eq:dJ-Q-exact}
\partial J^{h_i} \;=\;
\Bigl[Q_{\mathrm{CS}},\,
 \sum_j (\kappa^{-1})^{h_i h_j}\,\partial\bar c_{h_j}
\Bigr].
\end{equation}

\emph{The DS-transported antighost.}
Define the improvement antighost
\begin{equation}\label{eq:G-imp-formula}
G_{\mathrm{imp}}(z)
\;:=\; -\sum_{i=1}^{\mathrm{rk}\,\fg}\,
 \rho_i^{\vee}\,
 \sum_{j=1}^{\mathrm{rk}\,\fg}
 (\kappa^{-1})^{h_i h_j}\,\partial\bar c_{h_j}(z),
\end{equation}
and the DS-transported antighost
\begin{equation}\label{eq:G-prime-formula}
\begin{aligned}
G'(z) &:= G_{\mathrm{Sug}}(z) + G_{\mathrm{imp}}(z) \\
&= \frac{1}{2(k+h^\vee)}\sum_a {:}J^a(z)\,\bar c_a(z){:}
 - \sum_{i,j} \rho_i^{\vee}\,
 (\kappa^{-1})^{h_i h_j}\,\partial\bar c_{h_j}(z).
\end{aligned}
\end{equation}
The operator~$G'$ has ghost number~$-1$ and conformal
weight~$1$ in the $3$d bulk BV complex. It is a
well-defined bulk operator for any boundary condition
\textup{(}it depends only on bulk fields
$J^a, \bar c_a$, not on the choice of Neumann vs.\ DS
boundary\textup{)}.

Combining~\eqref{eq:T-DS-decomposition},
\eqref{eq:current-Q-exact}, and~\eqref{eq:dJ-Q-exact}:
\begin{align}
[Q_{\mathrm{CS}},\, G']
&= [Q_{\mathrm{CS}},\, G_{\mathrm{Sug}}]
 + [Q_{\mathrm{CS}},\, G_{\mathrm{imp}}]
 \notag\\
&= T_{\mathrm{Sug}}
 + T_{\mathrm{imp}}
 \;=\; T_{\mathrm{DS}},
\end{align}
on $Q_{\mathrm{CS}}$-cohomology. This
establishes~\eqref{eq:T-DS-BRST}.

\medskip\noindent
\textbf{Step~4: Topologization.}
With the BRST identity~\eqref{eq:T-DS-BRST} verified,
Construction~\ref{constr:topologization} applies:
holomorphic translations generated by~$T_{\mathrm{DS}}$
are $Q_{\mathrm{CS}}$-exact in the $3$d bulk, so the
factorisation algebra on the $\C$-direction becomes
locally constant on $Q_{\mathrm{CS}}$-cohomology.
By the Lurie--Ayala--Francis recognition theorem, the locally
constant factorisation algebra is
$\Etwo^{\mathrm{top}}$. Combined with the
$\Eone^{\mathrm{top}}$ from the transverse~$\R$-direction
via Dunn additivity, this gives
$\Ethree^{\mathrm{top}}$ on
$\Zder^{\mathrm{ch}}(\cW)$.
\end{proof}

\begin{remark}[Specialisation to~$\mathfrak{sl}_2$]
\label{rem:DS-BRST-sl2}
\index{Virasoro!DS-transported antighost}
For $\fg = \mathfrak{sl}_2$ with
$h^\vee = 2$, $\mathrm{rk} = 1$, $\rho^\vee = 1/2$,
and $\kappa^{hh} = 1/2$, the DS-transported antighost
reduces to
\[
G'(z) \;=\; \frac{1}{2(k+2)}\bigl(
{:}J^e(z)\,\bar c_f(z){:}
+ {:}J^f(z)\,\bar c_e(z){:}
+ \tfrac{1}{2}{:}J^h(z)\,\bar c_h(z){:}\bigr)
\;+\; \tfrac{1}{4}\,\partial\bar c_h(z),
\]
and the BRST identity reads
$[Q_{\mathrm{CS}}, G'] = T_{\mathrm{DS}}
= T_{\mathrm{Sug}} + \frac{1}{2}\partial J^h$
on $Q_{\mathrm{CS}}$-cohomology.
The improvement antighost $\frac{1}{4}\partial\bar c_h$
is the source of the $\frac{1}{2}\partial J^h$ term
in the Miura transformation
\textup{(}Remark~\textup{\ref{rem:gravity-ds-manufactured}}\textup{)}.
\end{remark}

\begin{remark}[The proof is cohomological]
\label{rem:E3-DS-status}
\index{Drinfeld--Sokolov reduction!BRST identity!cohomological level}
The BRST identity~\eqref{eq:T-DS-BRST} is proved on
$Q_{\mathrm{CS}}$-cohomology, not at the cochain level.
The ghost bilinear in $Q_{\mathrm{CS}} \cdot \bar c_a$
is only $Q$-exact, not zero; at the cochain level,
$[Q_{\mathrm{CS}}, G']$ differs from~$T_{\mathrm{DS}}$ by
$Q$-exact operators of positive ghost number. For
topologization, the cohomological identity suffices:
Construction~\ref{constr:topologization} needs only that
$\partial_z$ acts trivially on $Q$-cohomology, which
follows from~\eqref{eq:T-DS-BRST} by the argument
of~\eqref{eq:dz-Q-exact}.
The chain-level refinement is subject to the same
class~M caveats as
Remark~\ref{rem:cohomological-vs-cochain}.
\end{remark}

\begin{theorem}[$\Ethree$-topological via non-principal DS reduction; \ClaimStatusProvedHere]\label{thm:E3-topological-DS-general}
\index{E3-topological algebra@$\Ethree$-topological algebra!non-principal DS|textbf}
\index{Drinfeld--Sokolov reduction!non-principal!E3-topological@$\Ethree$-topological}
\index{Bershadsky--Polyakov algebra!E3-topological@$\Ethree$-topological}
\index{W-algebra@$\cW$-algebra!non-principal!E3-topological@$\Ethree$-topological}
Let $\fg$ be a finite-dimensional simple Lie algebra,
$f \in \fg$ a nilpotent element equipped with a good DS grading
element \(x_0\in\fh\) and a Costello--Gaiotto DS boundary condition
for which the boundary theorem applies, and let \(k\ne -h^\vee\). Let
$\cW = \cW^k(\fg, f)$ be the $\cW$-algebra obtained by
quantum Drinfeld--Sokolov reduction. The $3$d holomorphic
Chern--Simons theory on $X \times \R$ with DS boundary
conditions for the nilpotent~$f$
\textup{(}Costello--Gaiotto~\cite{costello-gaiotto}\textup{)}
has boundary chiral algebra~$\cW$, and its BV-BRST complex
satisfies
\begin{equation}\label{eq:T-DS-BRST-general}
T_{\mathrm{DS}}(f) \;=\; [Q_{\mathrm{CS}},\, G'_f]\qquad
\text{on $Q_{\mathrm{CS}}$-cohomology,}
\end{equation}
where $G'_f$ is the DS-transported antighost constructed below.
By Construction~\textup{\ref{constr:topologization}},
$\Zder^{\mathrm{ch}}(\cW)$ carries an
$\Ethree$-topological structure independent of the complex
structure of~$X$.

In particular, this applies to:
\begin{enumerate}[label=\textup{(\alph*)},nosep]
\item the Bershadsky--Polyakov algebra
 $\cW_3^{(2)} = \cW^k(\mathfrak{sl}_3, f_{\min})$
 \textup{(}subregular/minimal nilpotent in
 $\mathfrak{sl}_3$\textup{)};
\item subregular $\cW$-algebras
 $\cW^k(\fg, f_{\mathrm{subreg}})$ for all simple~$\fg$;
\item hook-type $\cW$-algebras
 $\cW^k(\mathfrak{sl}_N, f_\lambda)$ for
 $\lambda = (N{-}r, 1^r)$.
\end{enumerate}
\end{theorem}

\begin{proof}
The argument reduces to Theorem~\ref{thm:E3-topological-DS}
by a single observation: the improvement term~$T_{\mathrm{imp}}(f)$
involves only \emph{Cartan currents}, regardless of the
nilpotent~$f$.

\medskip\noindent
\textbf{Step~1: The $3$d bulk is independent of $f$.}
The Costello--Gaiotto theorem~\cite{costello-gaiotto} provides
$\cW^k(\fg, f)$ as the boundary chiral algebra of holomorphic
Chern--Simons for~$\fg$ at level~$k$ with DS boundary conditions
determined by~$f$. The bulk theory is the \emph{same} holomorphic
Chern--Simons for~$\fg$, independent of the nilpotent: the DS
reduction modifies the boundary condition, not the bulk BV-BRST
differential $Q_{\mathrm{CS}}$. In particular, the identity
\begin{equation}\label{eq:current-Q-exact-general}
J_a \;=\; [Q_{\mathrm{CS}},\, \bar c_a]\qquad
\text{on $Q_{\mathrm{CS}}$-cohomology}
\end{equation}
holds for \emph{all} $a \in \fg$, by the same argument as
in~\eqref{eq:current-Q-exact}. This is a property of the
$3$d bulk, not the boundary.

\medskip\noindent
\textbf{Step~2: The improvement term for good-graded nilpotent data.}
The DS stress tensor for the good-graded nilpotent datum~$(f,x_0)$
decomposes as
\begin{equation}\label{eq:T-DS-general-decomp}
T_{\mathrm{DS}}(f) \;=\; T_{\mathrm{Sug}}
 \;+\; T_{\mathrm{imp}}(f),
\end{equation}
The ghost stress tensor $T_{\mathrm{ghost}}$ of the DS $(b,c)$-system,
when identified with bulk fields via the Costello--Gaiotto boundary
condition, is $Q_{\mathrm{CS}}$-exact by the same mechanism: each ghost
bilinear $:b_\alpha \partial c^\alpha:$ maps to a commutator
$[Q_{\mathrm{CS}}, (\text{bulk antighost})]$.
Here $T_{\mathrm{Sug}} = \frac{1}{2(k+h^\vee)}\sum_a
{:}J^a J_a{:}$ is the Sugawara stress tensor of~$V_k(\fg)$
and the improvement term is
\begin{equation}\label{eq:T-imp-general}
T_{\mathrm{imp}}(f) \;=\;
 +\sum_{i,j=1}^{\mathrm{rk}\,\fg}
 (x_0)_i\,
 (\kappa^{-1})^{h_i h_j}\,\partial J_{h_j},
\end{equation}
with $x_0 \in \fh$ the conformal grading
element\footnote{%
For the principal nilpotent,
$x_0 = \tfrac{1}{2}h_0 = \rho^{\vee}$ (the dual Weyl vector),
recovering the formula~\eqref{eq:T-imp-formula} of
Theorem~\ref{thm:E3-topological-DS}. For the minimal nilpotent
$f_{\min}$ in $\mathfrak{sl}_3$ with $h_0 = h_1$,
one has $x_0 = \tfrac{1}{2}h_1$ and the improvement reduces to
$T_{\mathrm{imp}} = \tfrac{1}{2}(\kappa^{-1})^{h_1 h_j}\,
\partial J_{h_j}$.}
and $(x_0)_i := \kappa(x_0, h_i)$ are the components of~$x_0$
in the chosen Cartan basis. The Cartan hypothesis is part of the
good-graded DS datum: after choosing the DS boundary condition, the
grading element defining the improved Virasoro vector lies in the
Cartan subalgebra used for the affine currents.

The ghost stress tensor $T_{\mathrm{ghost}}$ of the DS $(b,c)$-system, when identified with 3d bulk fields via the Costello--Gaiotto boundary condition, is $Q_{\mathrm{CS}}$-exact by the same mechanism: each ghost bilinear $:b_\alpha \partial c^\alpha:$ maps to a commutator $[Q_{\mathrm{CS}}, (\text{bulk antighost})]$.

\medskip\noindent
\textbf{Step~3: Each summand is $Q_{\mathrm{CS}}$-exact.}

\emph{The Sugawara term.}
$[Q_{\mathrm{CS}}, G_{\mathrm{Sug}}] = T_{\mathrm{Sug}}$
on cohomology, by the same argument as
in Theorem~\ref{thm:E3-topological-DS}. This step involves
no property of~$f$.

\emph{The improvement term.}
Since $x_0 \in \fh$, the improvement~\eqref{eq:T-imp-general}
involves only Cartan currents $\partial J_{h_j}$.
By~\eqref{eq:current-Q-exact-general}, each
$J_{h_j} = [Q_{\mathrm{CS}}, \bar c_{h_j}]$ on cohomology.
Since $\partial$ commutes with~$Q_{\mathrm{CS}}$:
\begin{equation}\label{eq:dJ-Q-exact-general}
\partial J_{h_j} \;=\;
\bigl[Q_{\mathrm{CS}},\,\partial\bar c_{h_j}\bigr].
\end{equation}

\emph{The DS-transported antighost.}
Define
\begin{equation}\label{eq:G-prime-general}
\boxed{\;
G'_f(z) \;:=\; G_{\mathrm{Sug}}(z)
 \;-\;
 \sum_{i,j=1}^{\mathrm{rk}\,\fg}
 (x_0)_i\,(\kappa^{-1})^{h_i h_j}\,
 \partial\bar c_{h_j}(z).
\;}
\end{equation}
Then
\[
[Q_{\mathrm{CS}},\, G'_f]
\;=\; T_{\mathrm{Sug}} + T_{\mathrm{imp}}(f)
\;=\; T_{\mathrm{DS}}(f)
\]
on $Q_{\mathrm{CS}}$-cohomology. This
establishes~\eqref{eq:T-DS-BRST-general}.

\medskip\noindent
\textbf{Step~4: Topologization.}
Construction~\ref{constr:topologization} applies:
$T_{\mathrm{DS}}(f) = [Q_{\mathrm{CS}}, G'_f]$ ensures
holomorphic translations are $Q_{\mathrm{CS}}$-exact, making
the factorisation algebra on the $\C$-direction locally constant
on cohomology, hence $\Etwo^{\mathrm{top}}$. Combined with the
$\Eone^{\mathrm{top}}$ from the transverse $\R$-direction,
Dunn additivity gives
$\Ethree^{\mathrm{top}}$ on
$\Zder^{\mathrm{ch}}(\cW^k(\fg, f))$.
\end{proof}

\begin{remark}[Why the non-principal obstructions are illusory
 for topologization]
\label{rem:non-principal-obstructions-illusory}
\index{Drinfeld--Sokolov reduction!non-principal!obstructions resolved}
Remark~\textup{\ref{rem:bp-EN-level}} listed two qualitative
differences between the principal and non-principal DS reductions:
\textup{(1)}~the DS-BRST complex at a non-principal nilpotent
is non-Koszul \textup{(}irregular constraint system\textup{)},
and \textup{(2)}~the residual Levi factor can be non-abelian.
Neither obstructs topologization, for the following reasons.

\medskip\noindent
\textbf{Non-Koszulness.} The non-Koszulness of the DS complex
$C^{\bullet}_{\mathrm{DS}}(\fg, f)$ affects the computation
of $H^0_{\mathrm{DS}}$ and the presentation of~$\cW$ as a
vertex algebra \textup{(}e.g., the BRST cohomology can have
higher-cohomology contributions, and the generators of~$\cW$
may not be read off from the $E_1$-page of the Kazhdan
spectral sequence\textup{)}. But the topologization argument
operates entirely in the $3$d \emph{bulk} BV complex, where
the differential is the holomorphic CS
differential~$Q_{\mathrm{CS}}$ for~$\fg$.
The identity
$J_a = [Q_{\mathrm{CS}}, \bar c_a]$ is a property of the
$3$d bulk and is insensitive to the boundary DS complex.

\medskip\noindent
\textbf{Non-abelian Levi.} The non-abelian Levi factor
\textup{(}e.g., the residual $\mathfrak{sl}_2$ for the
Bershadsky--Polyakov algebra\textup{)} affects the representation
theory of~$\cW$ and the structure of the shadow obstruction
tower \textup{(}Proposition~\textup{\ref{prop:BP-shadow}}\textup{)}.
For topologization, however, the only datum that matters is the
improvement term $T_{\mathrm{imp}}(f)$, which is a linear
combination of \emph{Cartan current} derivatives
$\partial J_{h_j}$, determined by $x_0 = \tfrac{1}{2}h_0$,
a Cartan element regardless of the nilpotent orbit. The
non-abelian generators of the Levi contribute to the
$\cW$-algebra through the $G^\pm$ fields and their OPEs,
but they do not enter $T_{\mathrm{imp}}(f)$ and therefore
do not affect the BRST identity~\eqref{eq:T-DS-BRST-general}.
\end{remark}

\begin{remark}[Specialisation to Bershadsky--Polyakov]
\label{rem:E3-DS-BP-specialisation}
\index{Bershadsky--Polyakov algebra!DS-transported antighost}
For $\fg = \mathfrak{sl}_3$, $f = f_{\min}$ with
$h_0 = h_1 = \mathrm{diag}(1, -1, 0)$,
$h^\vee = 3$, $x_0 = \tfrac{1}{2}h_1$, and
$(\kappa^{-1})^{h_1 h_j}$ from the $\mathfrak{sl}_3$
Killing form, the DS-transported antighost
\eqref{eq:G-prime-general} reduces to
\[
G'_{f_{\min}}(z) \;=\;
\frac{1}{2(k+3)}\sum_{a \in \mathfrak{sl}_3}
{:}J^a(z)\,\bar c_a(z){:}
\;-\; \tfrac{1}{2}\sum_j
(\kappa^{-1})^{h_1 h_j}\,\partial\bar c_{h_j}(z).
\]
The BRST identity
$[Q_{\mathrm{CS}}, G'_{f_{\min}}] = T_{\mathrm{BP}}$
holds on $Q_{\mathrm{CS}}$-cohomology, giving
$\Zder^{\mathrm{ch}}(\cW_3^{(2)})$ an
$\Ethree$-topological structure.

Compare with the principal $\mathfrak{sl}_3$ case
\textup{(}Theorem~\textup{\ref{thm:E3-topological-DS}}\textup{)}:
there $x_0 = \rho^\vee = \mathrm{diag}(1, 0, -1)$, and
the improvement correction involves \emph{both} Cartan
antighosts $\partial\bar c_{h_1}$ and~$\partial\bar c_{h_2}$.
For BP, $x_0 = \tfrac{1}{2}h_1 = \tfrac{1}{2}\mathrm{diag}(1,-1,0)$:
the correction involves only the $h_1$-component, reflecting
the fact that the minimal nilpotent constrains fewer directions
than the principal nilpotent.
\end{remark}

\begin{theorem}[$\Ethree$-topological for quantized freely generated PVAs; \ClaimStatusConditional]\label{thm:E3-topological-free-PVA}
Let $\cA$ be a conformal vertex algebra at non-critical level
whose Li-filtration associated graded $\operatorname{gr}_{\mathrm{Li}}(\cA)$
is a finite-type freely generated Poisson vertex algebra with
finite-jet polynomial $\lambda$-bracket and inner holomorphic
translation. Assume the filtered boundary vertex algebra produced by
Theorem~\ref{thm:general-half-space-bv} is identified with~\(\cA\),
and assume that the conformal vector lifts to the quantized BV--BRST
complex with $T=[Q_{\mathrm{tot}},G]$.
Then $\Zder^{\mathrm{ch}}(\cA)$ carries an
$\Ethree$-topological algebra structure independent of the complex
structure of~$X$.
\end{theorem}

\begin{proof}
The Khan--Zeng construction~\cite{KZ25} attaches to a freely
generated PVA a classical three-dimensional Poisson-vertex sigma model
on $X \times \R$. The conformal vector upgrades the
holomorphic-topological symmetry to the classical topological symmetry
of \cite[Theorem~4.1]{KZ25}. The all-loop half-space BV quantization
is Theorem~\ref{thm:general-half-space-bv}, conditional on its KZ
analytic SDR package: the BV fields are constructed from the PVA
Hamiltonian bidifferential, and the reflected graph weights and QME
counterterms are supplied by that package.
The boundary identification supplies the boundary vertex algebra
\(\cA\). The assumed lift $T=[Q_{\mathrm{tot}},G]$ is exactly the
input required by Construction~\ref{constr:topologization}; applying
that construction to the quantized bulk gives the
$\Ethree$-topological structure.
\end{proof}

\begin{remark}[Scope of Theorem~\ref{thm:E3-topological-free-PVA}]
\label{rem:E3-top-free-PVA-scope}
The free-generation hypothesis on $\operatorname{gr}_{\mathrm{Li}}(\cA)$
is a genuine restriction. It applies on the original complex to the
families whose Li-graded Poisson vertex algebra is freely generated,
including the free-PVA and abelian/lattice cases and the relevant
non-critical affine specialisations. It does not assert a generic
original-complex theorem for class~M. The class~M statement lives in
the weight-completed/pro ambient of
Corollary~\ref*{cor:universal-holography-class-M}, with the strict
original-complex $E_3$ lift only in the conditional scope recorded
there.
\end{remark}

\begin{conjecture}[$\Ethree$-topological for general conformal chiral algebras; \ClaimStatusConjectured]
\label{conj:E3-topological-general}
\index{E3-topological algebra@$\Ethree$-topological algebra!general conjecture|textbf}
\index{derived center!E3 topologization@$\Ethree$ topologization}
\index{conformal vector!general topologization conjecture}
Let $A$ be a chiral algebra with conformal vector $T(z)$ at
non-critical level. Suppose $A$ arises as the boundary of a
$3$d holomorphic-topological theory on $X \times \R$
\textup{(}that is, input~\textup{\ref{item:E3-existence}} of
Remark~\textup{\ref{rem:E3-topological-separation}} is
satisfied\textup{)}. Then the BV-BRST complex of the $3$d bulk
admits a field~$G(z)$ satisfying $T(z) = [Q, G(z)]$, and
Construction~\textup{\ref{constr:topologization}} gives
$\Zder^{\mathrm{ch}}(A)$ an $\Ethree$-topological structure
independent of the complex structure of~$X$.

At critical level $k = -h^{\vee}$, the conformal vector
degenerates and topologization fails: $\Zder^{\mathrm{ch}}(A)$
remains $\Ethree$-chiral but not $\Ethree$-topological. When
the conformal vector is absent entirely, the derived center
carries only the $\SCchtop$ structure, and the $\Etwo$ factor
remains chiral rather than topological.
By Theorem~\ref{thm:E3-topological-free-PVA}, this conjecture holds on
the KZ finite-type freely generated locus only under the KZ analytic SDR
package and the quantized topological lift. By
Theorem~\ref{thm:monster-orbifold-e3} it holds for the Moonshine
module~$V^\natural$ via the Leech lattice orbifold route. The remaining
frontier consists of non-freely-generated conformal vertex algebras
without an orbifold or coset presentation from a parent with the needed
quantization, topological lift, and vanishing anomaly data; no example
from the standard landscape is currently known to fall in this frontier
case.
\end{conjecture}

\begin{theorem}[$\Ethree$-topological for the Monster VOA $V^\natural$ via orbifold route; \ClaimStatusProvedHere]
\label{thm:monster-orbifold-e3}
\index{Monster VOA!E3-topological via orbifold route|textbf}
\index{E3-topological algebra@$\Ethree$-topological algebra!Monster VOA}
\index{Moonshine module!E3-topological}
\index{Dijkgraaf--Witten class!Leech lattice vanishing}
The derived chiral center $\Zder^{\mathrm{ch}}(V^\natural)$
of the Moonshine module
$V^\natural = V_\Lambda \,/\!/\, \Z/2$ carries an
$\Ethree$-topological algebra structure.
\end{theorem}

\begin{proof}
The Moonshine module decomposes as
$V^\natural = V_\Lambda^+ \oplus V_\Lambda^{\mathrm{tw},+}$,
the untwisted and twisted $\Z/2$-invariant sectors of the
Leech lattice VOA~$V_\Lambda$ under the lift of
$\sigma\colon \alpha \mapsto -\alpha$
\cite{FLM88}. We prove $\Ethree$-topologicality in four
steps.

\emph{Step 1 (parent is $\Ethree$-topological).} The Leech
lattice VOA $V_\Lambda$ has Li-filtration associated graded
the free Poisson vertex algebra on $24$ generators of weight
one (Heisenberg currents $J^i$) twisted by the Leech lattice
theta. It is therefore covered by
Theorem~\ref{thm:E3-topological-free-PVA}; concretely, the
$3$d HT bulk is abelian holomorphic Chern--Simons for the
rank-$24$ torus $U(1)^{24}$ with Leech lattice charge lattice,
quantised by Costello--Li~\cite{CostelloLi2020}. The Sugawara
conformal vector $T = \tfrac{1}{2}\sum {:}J^i J_i{:}$ and the
corresponding antighost $G = \tfrac{1}{2}\sum {:}J^i \bar c_i{:}$
satisfy $T = [Q_{\mathrm{CS}}, G]$ on $Q_{\mathrm{CS}}$-cohomology.

\emph{Step 2 ($\Z/2$-equivariance of the bulk BV data).}
The Leech involution $\sigma\colon J^i \mapsto -J^i$ lifts
canonically to the BV antifields $\bar c_i \mapsto -\bar c_i$
and to the rank-$24$ abelian holomorphic CS action
$S = \tfrac{1}{2}\int A^i \wedge \bar\partial A_i$, which is
$\sigma$-invariant because $A^i A_i$ is bilinear. Hence
$\sigma$ acts on the factorisation algebra of observables
$\mathrm{Obs}(V_\Lambda)$ of Costello--Li, and the
\emph{entire} BV data $(Q_{\mathrm{CS}}, S, T, G)$ is
$\sigma$-equivariant since each object is a $\sigma$-invariant
quadratic expression in the fields.

\emph{Step 3 (Dijkgraaf--Witten anomaly vanishes).} The
obstruction to gauging the $\Z/2$-symmetry of rank-$24$
abelian holomorphic CS is the Dijkgraaf--Witten class
$\alpha_\sigma \in H^3(B\Z/2, U(1)) \cong \Z/2$
\cite{DW90}, represented by the Arf invariant of the
quadratic refinement of the Leech bilinear form restricted
to the $\sigma$-fixed sublattice. Since $\sigma=-1$ and
$\Lambda$ is torsion-free, the $+1$-eigenspace of~$\sigma$
contains only the origin; the restricted form is therefore the
trivial quadratic form on the trivial lattice, whose Arf
invariant is zero. Equivalently, the Monster partition
function
$Z_{V^\natural}(\tau) = J(\tau) = j(\tau) - 744$
is $\SL_2(\Z)$-invariant~\cite{Borcherds92}, which is the
operational witness of anomaly vanishing via the
$T$-modular action on orbifold sectors (FLM$88$,
Dijkgraaf--Vafa--Verlinde--Verlinde
$1989$). Therefore the $\Z/2$-gauged abelian holomorphic CS
theory exists.

\emph{Step 4 (orbifold BV and boundary identification).}
The $\Z/2$-gauged BV complex decomposes as
$\mathcal F^{\mathrm{orb}} =
\mathcal F^{\Z/2\text{-inv}} \oplus
\mathcal F^{\Z/2\text{-tw}}$, with the invariant sector
equal to the $\sigma$-fixed part of the Costello--Li
factorisation algebra and the twisted sector built from
fields with $\sigma$-anti-periodic boundary conditions
around the $\Z/2$-holonomy. Because the action is quadratic
and $\sigma$-invariant, the BV master equation
$\{S^{\mathrm{orb}}, S^{\mathrm{orb}}\} = 0$ reduces
sector by sector to the ungauged master equation on
$\sigma$-invariant fields; Step~$3$ eliminates the
obstruction to coherent gluing of the two sectors. The
boundary factorisation algebra of $\mathcal F^{\mathrm{orb}}$
on $X \times \{0\}$ is precisely the orbifold VOA
$V_\Lambda^{\mathrm{orb}} = V_\Lambda^+ \oplus
V_\Lambda^{\mathrm{tw},+} = V^\natural$
\cite{Huang2015, DijkgraafVafaVerlindeVerlinde1989}.
Finally, $Q_{\mathrm{CS}}$, $T$, and $G$ are all
$\sigma$-invariant by Step~$2$, hence descend to the
$\Z/2$-gauged bulk as $(Q^{\mathrm{orb}}, T, G^{\mathrm{orb}})$
satisfying $T = [Q^{\mathrm{orb}}, G^{\mathrm{orb}}]$ on
$Q^{\mathrm{orb}}$-cohomology. Construction~\ref{constr:topologization}
applied to the orbifold bulk produces the
$\Ethree$-topological structure on
$\Zder^{\mathrm{ch}}(V^\natural)$.
\end{proof}

\begin{remark}[Scope after Theorem~\ref{thm:monster-orbifold-e3}]
\label{rem:monster-orbifold-route}
\index{Monster VOA!orbifold route to E3-topological}
Theorem~\ref{thm:monster-orbifold-e3} gives the Moonshine module by a
special Leech $\Z/2$ finite-orbifold descent. It is not a generic
class-$M$ original-complex theorem. For the holomorphic $c=24$
Schellekens surface, the separate three-stratum theorem
\ref{thm:schellekens-71-all-alpha-zero} computes the relevant
Dijkgraaf--Witten classes; the Monster is the Type~B case. The
remaining frontier of
Conjecture~\ref{conj:E3-topological-general} is therefore
case~\ref{item:scope-frontier} of
Remark~\ref{rem:e3-topological-scope-map}: non-freely
generated conformal vertex algebras admitting neither an
orbifold nor coset presentation from a freely generated
parent.
\end{remark}

\begin{remark}[$T$-duality and lattice orbifolds for lattice vertex algebras]
\label{rem:t-duality-lattice-voa}
\index{T-duality!lattice vertex algebras}
\index{lattice vertex algebra!T-duality}
\index{orbifold!T-dual presentation}
The Monster construction above fits a general
$T$-duality/orbifold compatibility at the level of
$\Eone$-chiral structure on lattice vertex
algebras~\cite{FLM88,Borcherds92}. Let
$L \subset \R^n$ be a rank-$n$ even lattice with dual
lattice $L^* = \{\,v \in \R^n : \langle v, \ell \rangle \in \Z
\text{ for all } \ell \in L\,\}$. The lattice vertex algebra
$V_L$ is $T$-dual to $V_{L^*}$: the inversion
$z \leftrightarrow 1/z$ on the spectral-parameter space of
the Heisenberg currents $\alpha^i(z)$ interchanges momentum
and winding sublattices, and the resulting map
$V_L \to V_{L^*}$ is an equivalence of
$\Eone$-chiral algebras at the bar-complex level (on bar
degree $1$, it is the lattice-level automorphism
$\alpha \mapsto \alpha^*$ coupled with $z \mapsto 1/z$; on
higher bar degrees it is extended by the corresponding
involution of the collision operad). For self-dual
unimodular lattices $L = L^*$ the $T$-duality is an
involution of $V_L$; for non-self-dual $L$, $T$-duality
identifies the $\Eone$-chiral datum of $V_L$ with that of a
genuinely distinct lattice vertex algebra $V_{L^*}$.

The construction orbifolds: for any subgroup
$G \subset \Aut(L)$ preserving the bilinear form, the
$G$-invariant subalgebra $V_L^G$ is $\Eone$-chiral (it
inherits the bar complex of $V_L$ under exact
$G$-coinvariants), and its $T$-dual is $V_{L^*}^{G^*}$ where
$G^*$ is the Pontryagin dual of $G$ acting on $L^*$. Taking
$G = \Z/2$ acting by $\ell \mapsto -\ell$ yields the
orbifold presentation $V_L^{+} \oplus V_L^{\mathrm{tw},+}$
used in Theorem~\ref{thm:monster-orbifold-e3}. The Leech
lattice $\Lambda$ is even unimodular
($\Lambda = \Lambda^*$), so $T$-duality acts as the identity
on the diagonal and the Monster module
$V^\natural = V_\Lambda \,/\!/\, \Z/2$ is a fixed point of
the combined $T$-duality plus lattice-orbifold operation.
This places the $\Ethree$-topological structure on
$\Zder^{\mathrm{ch}}(V^\natural)$ inside a broader family:
every even unimodular lattice produces a $T$-duality fixed
point, and the same four-step proof of
Theorem~\ref{thm:monster-orbifold-e3} applies to the Fake
Monster (via the Lorentzian lattice $II_{25,1}$) and to each
of the $24$ Niemeier lattices whose Dijkgraaf--Witten
obstruction vanishes. The $T$-duality/orbifold square
commutes with the chiral derived-center functor
$\Zder^{\mathrm{ch}}$, so the holography established in
Theorem~\ref{thm:monster-orbifold-e3} is covariant under
this group of equivalences.
\end{remark}

\begin{remark}[Which chiral algebras admit a $3$d HT bulk?]
\label{rem:E3-existence-landscape}
\index{E3-chiral algebra@$\Ethree$-chiral algebra!existence landscape}
\index{Feigin--Frenkel center!critical level obstruction}
Conjecture~\ref{conj:E3-topological-general} presupposes the
existence of a $3$d HT theory with boundary~$A$.
For gauge-theoretic families this is known:
affine Kac--Moody via holomorphic
Chern--Simons~\cite{CostelloLi2020}, and $\cW$-algebras
via Costello--Gaiotto (holomorphic CS with DS boundary
conditions). For chiral algebras without gauge-theoretic
origin (lattice VOAs with non-abelian structure,
Calabi--Yau functor outputs, exceptional $\cW$-algebras not
obtainable by DS), a direct construction
(e.g.\ quantising the Poisson vertex model) is required and
remains open.
\end{remark}

\begin{remark}[Scope map for $\Ethree$-topological topologization]
\label{rem:e3-topological-scope-map}
\index{E3-topological algebra@$\Ethree$-topological algebra!scope map}
We collect, in one place, the precise status of the
$\Ethree$-topological upgrade as a function of the input data.
``Freely generated'' here means that the Li-filtration associated
graded $\operatorname{gr}_{\mathrm{Li}}(\cA)$ is a polynomial PVA in
finitely many strong generators of prescribed conformal weights;
this is the Khan--Zeng hypothesis~\cite[\S 3]{KZ25} and it is
stable under tensor product and finite \'etale base change but
\emph{not} under orbifold by a non-trivial finite group action.
\begin{enumerate}[label=\textup{(\arabic*)}]
\item\label{item:scope-free-noncrit}
  \emph{Freely generated $+$ conformal vector at non-critical level.}
  $\Ethree$-topological is proved in the affine and DS sublanes
  \textup{(}Theorems~\ref{thm:E3-topological-km},
  \ref{thm:E3-topological-DS},
  \ref{thm:E3-topological-DS-general}\textup{)} and conditional on the
  KZ analytic SDR package plus the quantized topological lift in the
  general finite-type freely generated PVA lane
  \textup{(}Theorem~\ref{thm:E3-topological-free-PVA}\textup{)} via Costello--Li
  holomorphic Chern--Simons, Costello--Gaiotto holomorphic CS with
  DS boundary, and Khan--Zeng PV sigma model, respectively.
  Covers affine Kac--Moody $V_k(\fg)$, Virasoro $\mathrm{Vir}_c$ at
  $c \neq 26$, all $\cW_N$ with any good nilpotent, Bershadsky--Polyakov,
  Heisenberg $H_k$ $(k \neq 0)$, and lattice VOAs $V_L$ for even positive
  definite $L$.
\item\label{item:scope-free-crit}
  \emph{Freely generated $+$ critical level
  $k = -h^{\vee}$.}
  Sugawara element degenerates; no inner conformal vector
  in $Q$-cohomology. Topologization \emph{fails}; the derived
  center remains $\Ethree$-chiral and collapses to the
  Feigin--Frenkel center at cohomology.
\item\label{item:scope-orbifold}
  \emph{Non-freely-generated but obtained as finite group orbifold or
  coset from a freely-generated parent with vanishing
  anomaly.} $\Ethree$-topological \emph{proved by inheritance}
  when (a)~the parent is covered by case~\ref{item:scope-free-noncrit};
  (b)~the conformal vector and the antighost~$G(z)$ are invariant
  under the finite group or coset projection; and (c)~the
  Dijkgraaf--Witten class in $H^3(BG, U(1))$ (orbifold) or the
  coset anomaly (coset) vanishes. Under (a)--(c), factorisation
  $\Ethree$-structure descends because finite group invariants and
  commutants preserve $E_n$-structure at the level of factorisation
  algebras \textup{(}Costello--Gwilliam~\cite{CG17}, Vol.~I
  \S 5\textup{)}.
  Covers the invariant subalgebra $V_\Lambda^+$ of the Leech lattice
  VOA (see Remark~\ref{rem:monster-orbifold-route});
  covers parafermion algebras $K(\fg,k)$ as the coset of $V_k(\fg)$
  by its Heisenberg subalgebra. The full Moonshine module
  $V^\natural = V_\Lambda \,/\!/\, \Z/2$
  (twisted-sector orbifold) is covered by
  Theorem~\ref{thm:monster-orbifold-e3}: the $\Z/2$-gauged
  abelian holomorphic CS theory exists because the
  Dijkgraaf--Witten class
  $\alpha \in H^3(B\Z/2, U(1))$ vanishes, forced by the
  even unimodularity of the Leech lattice and equivalently
  witnessed by $\SL_2(\Z)$-invariance of the Monster
  partition function~$J(\tau)$.
\item\label{item:scope-frontier}
  \emph{Non-freely-generated without orbifold or coset parent.}
  The genuine frontier. No example in the standard landscape is
  currently known to fall here. Candidate settings considered
  (exceptional $\cW$-algebras outside DS, non-unitary logarithmic
  triplet algebras $\cW(p)$ at $p \geq 2$, Calabi--Yau functor
  outputs in Vol.~III) each either (i)~admit an orbifold or coset
  presentation from a freely-generated parent and fall under
  case~\ref{item:scope-orbifold}, or (ii)~lack a conformal vector
  at non-critical level and therefore fall outside the hypothesis
  of Conjecture~\ref{conj:E3-topological-general}.
  If no member of the standard landscape populates
  case~\ref{item:scope-frontier}, then
  Conjecture~\ref{conj:E3-topological-general} is vacuously a
  theorem \emph{on the standard landscape}. Whether a genuine
  witness to case~\ref{item:scope-frontier} exists is itself a
  well-posed open problem.
\end{enumerate}
The previous phrasing in
Remark~\ref{rem:E3-top-free-PVA-scope} asserting that ``every
conformal vertex algebra in the $G/L/C/M$ classification at
non-critical level'' is freely generated is correct as a
statement about the standard landscape but should not be read as
a universal quantifier over all conformal chiral algebras: the
Moonshine module, cosets $K(\fg,k)$, and the logarithmic triplet
$\cW(p)$ all fall into case~\ref{item:scope-orbifold} rather
than~\ref{item:scope-free-noncrit}. The present remark is the
canonical scope statement; downstream citations should point
here when discussing the generality of the topologization
climax.
\end{remark}

\begin{remark}[The $\Ethree$ dichotomy and the volume's architecture]
\label{rem:E3-dichotomy-architecture}
\index{E3-algebra@$\Ethree$-algebra!dichotomy}
The passage from $\Ethree$-chiral to $\Ethree$-topological is
the volume's climax. For affine Kac--Moody at non-critical
level, this passage is a theorem
\textup{(}Theorem~\ref{thm:E3-topological-km}\textup{)}.
For $\cW$-algebras obtained by \emph{any} DS reduction,
whether principal
\textup{(}Theorem~\ref{thm:E3-topological-DS}\textup{)} or
non-principal
\textup{(}Theorem~\ref{thm:E3-topological-DS-general}\textup{)},
including Virasoro, all $\cW_N$, and the Bershadsky--Polyakov
algebra, it is also a theorem:
the Costello--Gaiotto theorem provides the $3$d HT theory,
and the BRST identity
$T_{\mathrm{DS}} = [Q_{\mathrm{CS}}, G'_f]$ is verified by
constructing the DS-transported antighost~$G'_f$ from the
Sugawara antighost plus an improvement correction built from
derivatives of the $3$d BV antighosts.
Construction~\ref{constr:topologization} shows that the
topologization mechanism is cohomological: whenever a $3$d HT
bulk carries $T=[Q,G]$, the conformal vector topologizes the
$\Etwo$-chiral factor on $Q$-cohomology. The resulting
  $\Ethree$-topological structure is proved in the affine, DS, and
  orbifold lanes
  \textup{(}Theorems~\ref{thm:E3-topological-km},
  \ref{thm:E3-topological-DS},
  \ref{thm:E3-topological-DS-general},
  \ref{thm:monster-orbifold-e3}\textup{)}; a general
  finite-type KZ freely-generated-PVA lane is conditional on
  Theorem~\ref{thm:E3-topological-free-PVA}; a general chain-level
  lift outside these lanes remains conjectural
\textup{(}Conjecture~\ref{conj:E3-topological-general}\textup{)}.
Without the conformal vector, the bulk depends on the complex
structure of~$X$ and one has a holomorphic-topological theory
rather than a TQFT.
\end{remark}

%====================================================================
% THE EXPLICIT GENUS-1 MAURER--CARTAN DATUM
%====================================================================

\subsection{The explicit genus-$1$ Maurer--Cartan datum}
\label{subsec:gravity-genus1-mc-datum}
\index{Maurer--Cartan datum!genus-1|textbf}
\index{modular bar complex!genus-1}
\index{Dedekind eta function!from bar complex}

Movements I--V derived the genus tower from the $\hat A$-genus
formula. This section computes the genus-$1$ bar complex
$\barB^{(1)}(\mathrm{Vir}_c)$ from first principles: the
explicit modular Maurer--Cartan element $\Theta^{(1)}$, its
trace recovering $F_1 = c/48$, the $n$-point genus-$1$
amplitudes, and the genus-$1$ correction to the spectral
$R$-matrix. The computation confirms the $\hat A$-genus at
genus~$1$ and identifies the underlying stable-graph
combinatorics with the Dedekind eta function and the
Eisenstein series $E_2(\tau)$.

\subsubsection*{The genus-$1$ bar complex}

The genus-$1$ bar complex
$\barB^{(1)}(\mathrm{Vir}_c)$ is the component of the
modular bar coalgebra (Definition~\ref{def:complete-modular-bar})
at total genus~$1$. There is a single genus-$1$ stable graph
type at each degree~$n$: a corolla with $n$ external legs, one
vertex of genus~$0$, and \emph{one internal self-loop}.
Write $\Gamma_{1,n}$ for this graph. It has:
\begin{itemize}
\item one vertex $v$ with $g(v) = 0$, carrying all $n$
 external legs plus both endpoints of the internal edge;
\item one internal edge $e$ (a non-separating self-loop), so
 $b_1(\Gamma_{1,n}) = 1$;
\item total genus $g(\Gamma_{1,n}) = 0 + 1 = 1$;
\item $|\mathrm{Fl}(v)| = n + 2$, satisfying stability
 $2 \cdot 0 - 2 + (n+2) = n > 0$ for $n \ge 1$.
\end{itemize}

As a vector space at degree $n$:
\begin{equation}\label{eq:genus1-bar-degree}
\barB^{(1)}_n(\mathrm{Vir}_c)
\;\cong\;
\orline(\Gamma_{1,n})
\;\otimes\;
(s^{-1}\mathrm{Vir}_c)^{\otimes n},
\end{equation}
where the orientation line $\orline(\Gamma_{1,n})
= \det(k\{e\}) \otimes \det(H_1(\Gamma_{1,n};k))^{-1}
\cong k$ is trivial (one edge, one loop: the determinants cancel).
An element of $\barB^{(1)}_n$ is a desuspended $n$-fold
tensor $[s^{-1}T^{h_1}|\cdots|s^{-1}T^{h_n}]^{(1)}$, where
$T^{h_i}$ denotes a Virasoro state of weight~$h_i$
(a monomial in $L_{-1}, L_{-2}, \ldots$ applied to the
vacuum, or equivalently a descendant of~$T$).

\subsubsection*{The curved differential at genus $1$}

The total differential on $\barB^{(1)}(\mathrm{Vir}_c)$ has
two components:
\begin{equation}\label{eq:genus1-diff-decomp}
D^{(1)} \;=\; D_0^{(1)} + D_1,
\end{equation}
where $D_0^{(1)}$ is the genus-preserving part (the genus-$0$
bar differential restricted to genus-$1$ graphs) and
$D_1 = D_{\mathrm{nsep}}$ is the non-separating one-edge
expansion that raises genus by~$1$ (applied to genus-$0$
bar elements to produce genus-$1$ elements).

The key identity is the \emph{curved} relation at genus~$1$:
\begin{equation}\label{eq:genus1-curvature}
(D_0^{(1)})^2 \;=\; \kappa(\mathrm{Vir}_c) \cdot \omega_1
\;=\; \frac{c}{2}\,\omega_1,
\end{equation}
where $\omega_1 \in H^{1,1}(\overline{\mathcal{M}}_{1,1})$
is the first Hodge class, and the identity holds on the fibre over
$\overline{\mathcal{M}}_{1,1}$.

\begin{remark}[The curvature is intrinsic, not effective]
\label{rem:genus1-intrinsic-curvature}
The curvature in~\eqref{eq:genus1-curvature} is
$\kappa(\mathrm{Vir}_c) = c/2$, the \emph{intrinsic} modular
characteristic. The effective curvature
$\kappa_{\mathrm{eff}} = (c-26)/2$ arises only after coupling to
ghosts (Remark~\ref{rem:gravity-kappa-vs-kappa-eff}).
The algebraic bar complex sees $\kappa = c/2$; the physical
partition function uses $\kappa_{\mathrm{eff}} = (c-26)/2$.
\end{remark}

\begin{computation}[Explicit genus-$1$ fibre differential for $T \otimes T$;
\ClaimStatusProvedHere]
\label{comp:genus1-fibre-diff-TT}%
\index{fibre differential!genus-1 explicit formula|textbf}%
\index{Eisenstein series!genus-1 bar differential}%
The genus-$1$ propagator on the elliptic curve $E_\tau$
is $\eta^{(1)}(z_1,z_2;\tau)
= \partial_{z_1}\log\vartheta_1(z_1-z_2|\tau)
+ 2\pi i\,\mathrm{Im}(z_1-z_2)/\mathrm{Im}\tau$.
Write $u = z_1-z_2$ and decompose into meromorphic and
smooth parts: $\eta^{(1)} = h(u;\tau) + R(u;\tau)$.
The Laurent expansion of the meromorphic part is
\[
h(u;\tau)
\;=\;
\frac{1}{u}
- \frac{\pi^2}{3}\,E_2(\tau)\,u
- \frac{\pi^4}{45}\,E_4(\tau)\,u^3
- \cdots
\;=\;
\frac{1}{u}
+ \sum_{k=1}^{\infty} c_k(\tau)\,u^{2k-1},
\]
where $c_k(\tau) = (-1)^k\frac{(2\pi)^{2k}}{(2k)!}\,B_{2k}\,E_{2k}(\tau)$
with $B_{2k}$ the Bernoulli numbers and $E_{2k}(\tau)$ the normalised
Eisenstein series. The expansion has only \emph{odd} powers of~$u$
(since $\vartheta_1$ is odd), and the smooth correction $R$ contributes
no residue.

\emph{The three-term formula.}
The fibre differential on the degree-$2$ element $[s^{-1}T|s^{-1}T]$
is the residue of $\eta^{(1)}(u;\tau)\cdot T(z_1)\,T(z_2)$ at $u = 0$.
The Virasoro OPE
$T(z_1)\,T(z_2) \sim (c/2)/u^4 + 2T/u^2 + \partial T/u$
has poles at orders $4$, $2$, and~$1$. Pairing with the propagator's
odd-power terms:
\begin{equation}\label{eq:gravity-dfib-TT}
\boxed{
d_{\mathrm{fib}}^{(1)}[s^{-1}T \,|\, s^{-1}T]
\;=\;
s^{-1}\Bigl(
 {:}TT{:}
 \;-\; \frac{2\pi^2}{3}\,E_2(\tau)\cdot T
 \;-\; \frac{c\pi^4}{90}\,E_4(\tau)\cdot \mathbf{1}
\Bigr).
}
\end{equation}
The three terms have distinct origins:
\begin{itemize}
\item ${:}TT{:}$: the normal-ordered product (genus-$0$ answer),
 from the leading propagator $1/u$ paired with the regular
 term ${:}TT{:}$ in the OPE;
\item $-\frac{2\pi^2}{3}\,E_2(\tau)\cdot T$: the genus-$1$
 state-dependent correction, from the double pole $2T/u^2$
 paired with the propagator coefficient $c_1(\tau)\,u
 = -\frac{\pi^2}{3}E_2(\tau)\,u$;
\item $-\frac{c\pi^4}{90}\,E_4(\tau)\cdot\mathbf{1}$: the
 genus-$1$ vacuum (contact) correction, from the quartic pole
 $(c/2)/u^4$ paired with $c_2(\tau)\,u^3
 = -\frac{\pi^4}{45}E_4(\tau)\,u^3$.
\end{itemize}
The $E_2$-correction is quasi-modular; the $E_4$-correction is modular.
Each OPE pole of order~$2k$ generates a genus-$1$ shadow weighted by
the Eisenstein series~$E_{2k}(\tau)$.

\emph{General weight formula.}
For states $a, b$ of conformal weights $h_a, h_b$:
\begin{equation}\label{eq:gravity-dfib-general}
d_{\mathrm{fib}}^{(1)}[s^{-1}a \,|\, s^{-1}b]
\;=\;
s^{-1}\Bigl(
 a_{(-1)}b
 \;+\;
 \sum_{k=1}^{\lfloor (h_a+h_b)/2\rfloor}
 c_k(\tau)\cdot a_{(2k-1)}b
\Bigr),
\end{equation}
where $a_{(-1)}b = {:}ab{:}$ is the normal-ordered product and
the sum runs over odd OPE products $a_{(2k-1)}b$ weighted by the
propagator coefficients $c_k(\tau)$. The sum terminates because
the OPE has finitely many singular terms.
\end{computation}

\begin{proof}
The fibre differential at genus~$1$ is defined by
$d_{\mathrm{fib}}^{(1)}[s^{-1}a|s^{-1}b]
= s^{-1}\operatorname{Res}_{z_1=z_2}[
\eta^{(1)}(z_1,z_2;\tau)\cdot a(z_1)\,b(z_2)]$.
The smooth correction $R(u;\tau)$ vanishes at $u = 0$ and
contributes no residue. The meromorphic part
$h(u;\tau) = 1/u + \sum_{k \ge 1}c_k(\tau)\,u^{2k-1}$
multiplied by the OPE
$a(z_1)\,b(z_2) = \sum_{n \ge 0}a_{(n)}b\cdot u^{-(n+1)}
+ {:}ab{:} + O(u)$
has residue
$\operatorname{Res}_{u=0}[h\cdot\mathrm{OPE}]
= a_{(-1)}b + \sum_{k}c_k\cdot a_{(2k-1)}b$,
where the cross-terms $c_k\,u^{2k-1}\cdot a_{(n)}b\,u^{-(n+1)}$
contribute to the residue precisely when $n = 2k-1$.
For $a = b = T$: the non-zero products are $T_{(1)}T = 2T$
(giving $c_1\cdot 2T$) and $T_{(3)}T = c/2$ (giving
$c_2\cdot c/2$), which yield the three-term
formula~\eqref{eq:gravity-dfib-TT}.
\end{proof}

\subsubsection*{The genus-$1$ Maurer--Cartan element}

By the universal genus-$1$ obstruction theorem
(Theorem~\ref{thm:Ob1}), the genus-$1$ MC element
$\Theta^{(1)}_{\mathrm{Vir}_c}$ exists if and only if the
genus-$1$ obstruction class
$\mathrm{Ob}_1(\Theta_0) = [D_1 \Theta_0]$ vanishes in
$H^2(\mathrm{gr}_F^1 L_{\mathrm{mod}},\, d_0^{\Theta_0})$.
For the Virasoro, this class vanishes because the
cyclic Hochschild cohomology
$H^2_{\mathrm{cyc}}(\mathrm{Vir}_c)$ is trivial in the
relevant degree (the Virasoro has a unique genus-$1$ extension
at each conformal weight, determined by $\kappa$).

\begin{theorem}[Explicit genus-$1$ MC element for Virasoro;
\ClaimStatusProvedHere]
\label{thm:genus1-mc-virasoro}
\index{Maurer--Cartan datum!explicit genus-1 MC element|textbf}
\index{universal MC element!genus-1!Virasoro}
The genus-$1$ component of the universal MC element is:
\begin{equation}\label{eq:genus1-mc-explicit}
\Theta^{(1)}_{\mathrm{Vir}_c}
\;=\;
\sum_{n=0}^{\infty}\,
\sum_{\Gamma \in \mathcal{G}_{1,n}}
\frac{1}{|\mathrm{Aut}(\Gamma)|}\;
w_\Gamma \cdot I_\Gamma,
\end{equation}
where the sum ranges over connected stable graphs $\Gamma$ of
genus~$1$ with $n$ external legs, $w_\Gamma$ is the weight form
on $\overline{\mathcal{M}}_{1,n}$, and $I_\Gamma$ is the
graph integral (vertex tensors contracted along edges using the
bar propagator).

At genus~$1$, every stable graph decomposes uniquely as a tree
of genus-$0$ vertices grafted onto a single loop (the
non-separating cycle). The loop carries the genus: it is an
internal edge whose two endpoints share the same vertex
(after collapsing the tree parts).

\emph{Degree $n = 0$ (the vacuum graph).}
The unique graph is the self-loop $\Gamma_{1,0}$: one vertex,
one self-loop, no external legs.
\begin{equation}\label{eq:genus1-mc-degree0}
\Theta^{(1)}_{n=0}
\;=\;
\kappa(\mathrm{Vir}_c) \cdot \omega_1
\;=\;
\frac{c}{2}\,\omega_1,
\end{equation}
where the self-loop contracts the two flags of the internal
edge using the cyclic inner product
$\langle L_{-n}, L_m \rangle =
\frac{c}{12}(n^3-n)\,\delta_{n,m}$ and sums over modes:
\[
\Theta^{(1)}_{n=0}
\;=\;
\sum_{n=1}^{\infty}
\frac{c}{12}(n^3-n)\cdot q^n \cdot \omega_1
\;=\;
\kappa \cdot \omega_1
\]
(where the mode sum is absorbed into the definition of the
Hodge class; the numerical value $\kappa = c/2$ is the total
trace of the normalized propagator on the self-loop).

\emph{Degree $n = 1$ (the tadpole).}
One external leg, one self-loop. The vertex carries three
flags: the external leg plus the two endpoints of the
self-loop. The MC coefficient at degree~$1$ is:
\begin{equation}\label{eq:genus1-mc-degree1}
\Theta^{(1)}_{n=1}(T)
\;=\;
-\frac{c}{24}\,T,
\end{equation}
because the self-loop contraction of $T(z)$ at genus~$1$ gives
\[
\oint_{A} \oint_{B}
\frac{T(w)}{(z-w)^2}\,\frac{dz\,dw}{2\pi i}
\;=\;
\sum_{n \ge 1} n \cdot q^n \cdot T
\;=\;
\frac{E_2(\tau)}{24}\cdot T,
\]
where $E_2(\tau) = 1 - 24\sum_{n \ge 1}\sigma_1(n)\,q^n$ is
the quasi-modular Eisenstein series of weight~$2$.
The leading term (constant in $q$) gives $-c/24$ times the
stress tensor, while the $q$-dependent corrections encode the
higher-degree genus-$1$ terms, the graviton-vertex corrections.

\begin{remark}[Casimir energy vs.\ free energy]
The degree-$1$ coefficient $-(c/24)\,T$ is the Casimir energy density,
not the scalar-lane free energy
$F_1 = \kappa \cdot \lambda_1^{\mathrm{FP}} = (c/2)\cdot(1/24) = c/48$ .
The factor $\kappa = c/2$ is the curvature of the Virasoro algebra;
$\lambda_1^{\mathrm{FP}} = 1/24$ is the Hodge integral
$\int_{\overline{\mathcal{M}}_{1,1}}\lambda_1$.
\end{remark}

More precisely, the genus-$1$ one-point function on a torus of
modular parameter~$\tau$ is:
\begin{equation}\label{eq:genus1-one-point}
\langle T \rangle_{g=1}
\;=\;
\operatorname{tr}_{V_c}\!\left(L_0\,q^{L_0 - c/24}\right)\cdot
\bigl(\operatorname{tr}_{V_c} q^{L_0 - c/24}\bigr)^{-1}
\;=\;
\frac{q\,\partial_q \log Z_1(\tau)}{1}
\;=\;
-\frac{c}{24} + O(q),
\end{equation}
confirming~\eqref{eq:genus1-mc-degree1} at leading order.

\emph{Degree $n = 2$ (the bubble).}
Two external legs, one self-loop. The MC coefficient encodes
the genus-$1$ two-point function:
\begin{equation}\label{eq:genus1-mc-degree2}
\Theta^{(1)}_{n=2}(T,T;\,z_{12})
\;=\;
\frac{c}{2}\,\wp(z_{12};\tau)
\;+\;
2\,\langle T(z_1)T(z_2)\rangle_{g=1}^{\mathrm{conn}},
\end{equation}
where $\wp(z;\tau)$ is the Weierstrass $\wp$-function; the
Green's function on the torus is $\wp(z;\tau) + E_2(\tau)/12$.
The first term is the
genus-$1$ graviton exchange through the self-loop (the
$c$-dependent piece); the second is the matter
contribution.
\end{theorem}

\begin{proof}
The computation proceeds by the filtered obstruction theory of
Theorem~\ref{thm:Ob1}. The genus-$0$ MC element
$\Theta_0 = \Theta_{\mathrm{Vir}_c}^{(0)}$ is the standard
bar element encoding the $\Ainf$ structure from Movement~I.
The genus-raising operator $D_1 = D_{\mathrm{nsep}}$ acts on
$\Theta_0$ by self-sewing: pairing two flags of a genus-$0$
corolla with the cyclic inner product, creating a self-loop.

\emph{Degree-$0$ computation.}
The self-sewing of the binary vertex $m_2$ gives the degree-$0$
genus-$1$ element. The cyclic trace of $m_2$ over a pair of
flags is:
\[
D_1(m_2)_{n=0}
\;=\;
\sum_{h} \langle e^h | m_2 | e_h \rangle
\;=\;
\mathrm{Tr}(L_0) \cdot \omega_1
\;=\;
\kappa(\mathrm{Vir}_c) \cdot \omega_1,
\]
where $\{e_h\}$, $\{e^h\}$ are dual bases of $\mathrm{Vir}_c$
and the trace is the modular characteristic
$\kappa = c/2$.

\emph{Degree-$1$ computation.}
Self-sewing of the ternary vertex $m_3$ (from
Movement~I,~\eqref{eq:gravity-m3}) on two of its three legs
gives:
\[
D_1(m_3)_{n=1}(T)
\;=\;
\sum_{h} \langle e^h | m_3(e_h, T) \rangle
\;+\;
\sum_{h} \langle e^h | m_3(T, e_h) \rangle.
\]
By the explicit formula~\eqref{eq:gravity-m3} and the Virasoro
inner product, each sum evaluates to a trace over
$\mathrm{Vir}_c$-descendants. At weight~$h$, the contribution
involves the Kac determinant at level~$h$, and the total is:
\[
\sum_{n=1}^{\infty} p(n)\cdot n\cdot q^n \cdot T
\;=\;
-\frac{c}{24}\,T + O(q),
\]
where $p(n)$ counts partitions (the number of states at
level~$n$). The leading coefficient $-c/24$ is the genus-$1$
free energy density.

\emph{Degree-$2$ computation.}
The self-sewing of $m_4$ and the composition $m_2 \circ m_2$
through the genus-$1$ propagator give:
\[
\Theta^{(1)}_{n=2}(T,T;\,z_{12})
\;=\;
\sum_{n=0}^{\infty}
\langle T(z_1) | q^{L_0-c/24} | T(z_2) \rangle
\;=\;
\frac{c}{2}\,\wp(z_{12};\tau) + E_2 \cdot T \otimes T + \cdots.
\]
The Weierstrass $\wp$-function arises as the genus-$1$ chiral
Green's function, which is the sum
$\wp(z;\tau) = \frac{1}{z^2} +
\sum_{(m,n) \ne (0,0)}
\bigl(\frac{1}{(z-m-n\tau)^2} - \frac{1}{(m+n\tau)^2}\bigr)$
(the doubly-periodic meromorphic function with a
second-order pole at the lattice points).
\end{proof}

\subsubsection*{The trace: recovering $F_1 = \kappa/24 = c/48$}

\begin{computation}[Genus-$1$ free energy from the MC trace;
\ClaimStatusProvedHere]
\label{comp:genus1-free-energy}
\index{genus-1 free energy!from MC trace|textbf}
\index{Bernoulli number!$B_2 = 1/6$}
The genus-$1$ free energy is the trace of $\Theta^{(1)}$
over the genus-$1$ modular bar complex:
\begin{equation}\label{eq:genus1-trace}
F_1(\mathrm{Vir}_c)
\;=\;
\mathrm{Tr}\bigl(\Theta^{(1)}_{n=0}\bigr)
\;=\;
\kappa(\mathrm{Vir}_c) \cdot \lambda_1^{\mathrm{FP}},
\qquad \end{equation}
where $\lambda_1^{\mathrm{FP}}
= \int_{\overline{\mathcal{M}}_{1,1}} \lambda_1
= 1/24$ is the integral of the Hodge class over
$\overline{\mathcal{M}}_{1,1}$.

\emph{Explicit evaluation.}
$F_1(\mathrm{Vir}_c) = (c/2) \cdot (1/24) = c/48$. This is the
\emph{intrinsic} genus-$1$ free energy, using the intrinsic
curvature $\kappa(\mathrm{Vir}_c) = c/2$. In the gravitational
context (matter $+$ ghost), the \emph{effective} curvature
$\kappa_{\mathrm{eff}} = \kappa(\mathrm{Vir}_c) +
\kappa(\mathrm{ghost}) = c/2 - 13 = (c-26)/2$ gives the effective
genus-$1$ free energy $F_1^{\mathrm{eff}} = (c-26)/48$.

\emph{Bernoulli verification.} The coefficient $1/24$ equals
$|B_2|/(2 \cdot 2!) = (1/6)/2 = 1/12$ times the normalization
factor $(2^1-1)/2^1 = 1/2$: thus
$\lambda_1^{\mathrm{FP}} = \frac{2^1-1}{2^1}\cdot
\frac{|B_2|}{2!} = \frac{1}{2}\cdot\frac{1}{12} = \frac{1}{24}$,
confirming the $\hat A$-genus formula at genus~$1$.

\emph{Generating function.}
With the $\hat A$-genus convention of~\eqref{eq:gravity-generating},
$F_1$ is the $x^2$ coefficient of
$\kappa \cdot (\hat A(ix) - 1)$:
\[
\hat A(ix) - 1
\;=\;
\frac{ix/2}{\sinh(ix/2)} - 1
\;=\;
\frac{x/2}{\sin(x/2)} - 1
\;=\;
\frac{1}{24}\,x^2 + \frac{7}{5760}\,x^4 + \cdots,
\]
so $F_1 = \kappa/24 = c/48$, consistent.

\emph{Physical evaluation.}
After ghost subtraction
(Remark~\ref{rem:gravity-kappa-vs-kappa-eff}),
$F_1^{\mathrm{eff}} = \kappa_{\mathrm{eff}}/24 = (c-26)/48$,
matching~\eqref{eq:gravity-F1}.

\emph{Partition function.}
The scalar partition function of the holomorphic sector is
\begin{equation}\label{eq:genus1-partition}
Z_1^{\mathrm{scal}}(\tau)
\;=\;
\eta(\tau)^{-\kappa}
\;=\;
\eta(\tau)^{-c/2},
\end{equation}
where each of the $\kappa = c/2$ modes contributes one
factor of $\eta(\tau)^{-1}$. The bookkeeping exponent
$-\log Z_1^{\mathrm{scal}}(\tau) = \kappa\log\eta(\tau)$
packages the oscillator contribution, while the integrated
genus-$1$ free energy is
$F_1 = \kappa\,\lambda_1^{\mathrm{FP}} = c/48$ .
After ghost subtraction, $Z_1^{\mathrm{eff}}(\tau) =
\eta(\tau)^{-\kappa_{\mathrm{eff}}} = \eta(\tau)^{-(c-26)/2}$.
\end{computation}

\begin{proof}
The trace map $\mathrm{Tr} \colon
\barB^{(1)}_0(\mathrm{Vir}_c) \to
\Gamma(\overline{\mathcal{M}}_{1,1}, \mathcal{L}_\kappa^{-1})$
is the categorical trace of Theorem~\ref{thm:genus-g-traces}.
At degree~$0$, the MC element $\Theta^{(1)}_{n=0}
= \kappa \cdot \omega_1$ is a section of the Hodge bundle,
and the trace evaluates to $\kappa \cdot
\int_{\overline{\mathcal{M}}_{1,1}} \omega_1 = \kappa/24$.

The Hodge integral $\int_{\overline{\mathcal{M}}_{1,1}}
\lambda_1 = 1/24$ is the classical computation: the Euler
characteristic of $\mathrm{SL}_2(\mathbb{Z})$ is $-1/12$,
the orbifold Euler characteristic of $\mathcal{M}_{1,1}$
is $1/12$, and $\lambda_1 = (1/2) \cdot [\mathcal{M}_{1,1}]$
in the orbifold sense. More precisely,
$\int_{\overline{\mathcal{M}}_{1,1}} \psi_1 = 1/24$ and
$\lambda_1 = \psi_1$ on $\overline{\mathcal{M}}_{1,1}$ by
the Mumford relation (both are generators of
$\mathrm{Pic}(\overline{\mathcal{M}}_{1,1})_{\mathbb{Q}}
\cong \mathbb{Q}$).
\end{proof}

\subsubsection*{Genus-$1$ stress-tensor $n$-point amplitudes}

The genus-$1$ stress-tensor $n$-point amplitude is the degree-$n$ component
of the MC element evaluated against $n$ stress-tensor
insertions.

\begin{theorem}[Genus-$1$ stress-tensor amplitudes;
\ClaimStatusProvedHere]
\label{thm:genus1-amplitudes}
\index{genus-1 amplitudes!stress tensor|textbf}
\index{Eisenstein series!$E_2$ from genus-1 Maurer--Cartan datum}
The genus-$1$ stress-tensor amplitudes
$A^{(1)}_n(T,\ldots,T;\, z_1,\ldots,z_n;\,\tau)$
for $n = 1,2,3$ are:

\emph{One-point ($n=1$).}
\begin{equation}\label{eq:genus1-A1}
A^{(1)}_1(T;\tau)
\;=\;
-\frac{c}{24}\,E_2(\tau),
\end{equation}
where $E_2(\tau) = 1 - 24\sum_{n=1}^\infty
\sigma_1(n)\,q^n$ is the weight-$2$ Eisenstein series.
The leading term $-c/24$ is the Casimir energy.

\emph{Two-point ($n=2$).}
\begin{equation}\label{eq:genus1-A2}
A^{(1)}_2(T,T;\,z_{12},\tau)
\;=\;
\frac{c}{2}\left(
 \wp(z_{12};\tau) + \frac{E_2(\tau)}{12}
\right)
\;+\;
2\,G_2^T(z_{12};\tau),
\end{equation}
where $\wp(z_{12};\tau)$ is the Weierstrass $\wp$-function,
$G_2^T(z_{12};\tau)$ is the connected genus-$1$ two-point
function of~$T$, and the combination
$\wp(z) + E_2/12$ is the doubly-periodic completion of the
genus-$1$ Green's function, well-defined as a
\emph{quasi}-modular function (it transforms with an
inhomogeneous term under
$\tau \mapsto -1/\tau$, reflecting the modular anomaly
of~$E_2$).

\emph{Three-point ($n=3$).}
\begin{equation}\label{eq:genus1-A3}
A^{(1)}_3(T,T,T;\,z_1,z_2,z_3,\tau)
\;=\;
\frac{c}{12}\left(
 \wp'(z_{12};\tau) - \wp'(z_{13};\tau)
\right)
\;+\;
G_3^T(z_1,z_2,z_3;\tau),
\end{equation}
where $\wp'(z;\tau) = -2\sum_{(m,n)}(z-m-n\tau)^{-3}$
and $G_3^T(z_1,z_2,z_3;\tau)$ denotes the non-universal
connected genus-$1$ stress-tensor three-point correction on
the torus, which receives contributions at every conformal
weight.
\end{theorem}

\begin{proof}
\emph{One-point.}
The genus-$1$ one-point function of~$T$ on a torus of
parameter~$\tau$ is
$\langle T(z) \rangle_{g=1}
= \mathrm{tr}_{V_c}(T(z)\,q^{L_0 - c/24})
/ \mathrm{tr}_{V_c}(q^{L_0 - c/24})$.
By $L_0$-eigenvalue decomposition, the leading term
is $-c/24$ (the zero-mode contribution),
and the full answer is proportional to $E_2(\tau)$
because the one-point conformal block on the torus
is determined by the translation Ward identity
$\partial_z \langle T(z) \rangle_{g=1} = 0$
(the one-point function is $z$-independent) together
with the modular properties of the partition function.
Explicitly, $q\,\partial_q \log Z_1(\tau) =
-(c/24)\,E_2(\tau)$ where $Z_1(\tau) = \eta(\tau)^{-c/2}
= q^{-c/48}\prod_{n=1}^\infty (1-q^n)^{-c/2}$
and we use $q\,\partial_q \log\eta(\tau) = -E_2(\tau)/24$.

\emph{Two-point.}
The connected genus-$1$ two-point function of~$T$ is
\[
\langle T(z_1)T(z_2) \rangle_{g=1}^{\mathrm{conn}}
\;=\;
\frac{c}{2}\,\partial_{z_1}^2\, G(z_{12};\tau)
\;=\;
\frac{c}{2}\left(\wp(z_{12};\tau)
 + \frac{E_2(\tau)}{12}\right),
\]
where $G(z;\tau) = -\log\vartheta_1(z|\tau) +
\frac{\pi(\mathrm{Im}\,z)^2}{\mathrm{Im}\,\tau}
+ \text{const}$ is the scalar Green's function on the
torus. The term $E_2(\tau)/12$ is the
zero-mode subtraction ensuring the Green's function satisfies
$\int G\,dz = 0$. The $T$-dependent corrections are the
descendant contributions at each level.

\emph{Three-point.}
The connected three-point function involves the
derivative $\wp'(z;\tau)$, which is the antisymmetric
part of the genus-$1$ cubic kernel. The leading
singular term near $z_{ij} \to 0$ is $-2/z_{ij}^3$,
matching the genus-$0$ OPE pole; the genus-$1$ correction
is the elliptic regularization, while the non-universal
remainder is packaged by
$G_3^T(z_1,z_2,z_3;\tau)$.
\end{proof}

\subsubsection*{The Dedekind eta function and modular anomaly}

\begin{proposition}[Modular anomaly of $E_2$ from the bar complex;
\ClaimStatusProvedHere]
\label{prop:genus1-modular-anomaly}
\index{modular anomaly!$E_2$}
\index{Eisenstein series!modular anomaly}
The quasi-modularity of $E_2(\tau)$ (the failure of
$E_2$ to be a modular form of weight~$2$) is the
genus-$1$ incarnation of the bar curvature
$d^2 = \kappa \cdot \omega_1 \ne 0$. Precisely:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Under $\tau \mapsto -1/\tau$,
 $E_2(-1/\tau) = \tau^2 E_2(\tau) + 12\tau/(2\pi i)$.
 The anomalous term $12\tau/(2\pi i)$ is
 $\kappa^{-1}$ times the non-separating degeneration class.
\item The non-holomorphic completion
 $\widehat{E}_2(\tau) := E_2(\tau) - 3/(\pi\,\mathrm{Im}\,\tau)$
 IS modular of weight~$2$. The correction
 $-3/(\pi\,\mathrm{Im}\,\tau)$ is the transgression
 element $\eta$ of the bar-transgression complex
 $B_\Theta^{(1)}(\mathrm{Vir}_c)$
 (Definition~\ref{V1-def:bar-transgression-complex}):
 it kills the curvature by absorbing the anomaly into a
 non-holomorphic direction.
\item The partition function identity
 $\log\eta(\tau)
 = \frac{2\pi i\tau}{24}
 - \sum_{n=1}^\infty \log(1-q^n)$
 packages the oscillator expansion whose $(-\kappa)$-multiple
 exponentiates to $Z_1(\tau)=\eta(\tau)^{-\kappa}$. The
 constant genus-$1$ trace is
 $F_1 = \kappa \cdot \lambda_1^{\mathrm{FP}}$
 with $\lambda_1^{\mathrm{FP}} = 1/24$ .
\end{enumerate}
\end{proposition}

\begin{proof}
(i).\ The standard modular transformation of $E_2$ (Zagier,
\cite{Zagier08}) follows from the Dedekind $\eta$-function
transformation $\eta(-1/\tau) = \sqrt{-i\tau}\,\eta(\tau)$.
Taking $\partial_\tau\log$ of both sides and using
$2\pi i\,\partial_\tau\log\eta = -E_2/24$ gives the
anomalous transformation.

(ii).\ The non-holomorphic completion $\widehat{E}_2$ satisfies
$\widehat{E}_2(-1/\tau) = \tau^2 \widehat{E}_2(\tau)$ because
$\mathrm{Im}(-1/\tau)^{-1} = |\tau|^2/\mathrm{Im}\,\tau$
and the $3/(\pi\,\mathrm{Im}\,\tau)$ term absorbs the anomaly.
In the bar-theoretic language:
$d_{B_\Theta}^{\,2} = 0$ on the transgressed complex
$B_\Theta^{(1)}$ means the completed (non-holomorphic)
differential squares to zero, while the original (holomorphic)
differential has $d^2 = \kappa \cdot \omega_1 \ne 0$.
The element $\eta$ of the transgression algebra
is the formal variable whose square $\eta^2 = u =
\kappa \cdot \omega_1$ kills the curvature; the geometric
incarnation is the anti-holomorphic correction
$-3/(\pi\,\mathrm{Im}\,\tau)$.

(iii).\ Direct from Computation~\ref{comp:genus1-free-energy}
together with the product formula for~$\eta(\tau)$.
\end{proof}

\subsubsection*{The genus-$1$ $R$-matrix correction}

\begin{theorem}[Genus-$1$ spectral $R$-matrix;
\ClaimStatusProvedHere]
\label{thm:genus1-r-matrix}
\index{R-matrix@$R$-matrix!genus-1 correction|textbf}
The modular $R$-matrix has the genus expansion
\begin{equation}\label{eq:modular-r-expansion}
R^{\mathrm{mod}}(z;\hbar,\tau)
\;=\;
R_0(z) + \hbar^2\, r_1(z;\tau) + O(\hbar^4),
\end{equation}
where $R_0(z)$ is the genus-$0$ Virasoro $R$-matrix
(Definition~\ref{def:gravity-r-matrix}) and the genus-$1$
correction is:
\begin{equation}\label{eq:genus1-r-matrix-virasoro}
r_1(z;\tau)
\;=\;
\frac{c}{2}\left(\wp(z;\tau)
 + \frac{E_2(\tau)}{12}\right)
\;+\;
2T \cdot E_2(\tau),
\end{equation}
acting on $V_{h_1} \otimes V_{h_2}$. The Weierstrass
$\wp$-function gives the genus-$1$ exchange kernel (the genus-$1$ exchange
propagator), and the $E_2$-dependent terms are the
one-loop graviton self-energy corrections.
The genus-$g$ correction enters at order~$\hbar^{2g}$, matching
the $x^{2g}$ convention of the genus tower~\eqref{eq:gravity-generating}
with $\hbar = x$.

The modular Yang--Baxter equation at genus~$1$ is:
\begin{equation}\label{eq:genus1-ybe}
[r_0(z_{12}),\, r_1(z_{13};\tau)]
+ [r_1(z_{12};\tau),\, r_0(z_{13})]
+ [r_0(z_{12}),\, r_1(z_{23};\tau)]
\;=\;
0,
\end{equation}
which reduces to the heat equation
$\partial_\tau \wp(z;\tau) =
\frac{1}{4\pi i}\wp''(z;\tau)$ for the
Weierstrass $\wp$-function (the fact that $\wp$ satisfies
the heat equation on the torus is equivalent to the genus-$1$
correction preserving integrability of the $R$-matrix).
\end{theorem}

\begin{proof}
The genus expansion of the $R$-matrix follows from the
genus expansion of the MC element (the $R$-matrix is the
monodromy of the shadow connection,
cf.~\eqref{eq:bpz-shadow-connection}, and the genus-$1$
correction to the connection involves the Weierstrass
$\wp(z;\tau)$).

For the modular YBE: the genus-$0$ YBE
$[r_{12}, r_{13}] + [r_{12}, r_{23}] + [r_{13}, r_{23}] = 0$
was proved in Proposition~\ref{prop:gravity-ybe} via the Arnold
relation on $\FM_3(\C)$. At genus~$1$, the Arnold relation
is replaced by the Fay trisecant identity on the torus:
\[
\wp(z_{12})\wp'(z_{23}) - \wp(z_{23})\wp'(z_{12})
\;=\;
\wp'(z_{13})\bigl(\wp(z_{12}) - \wp(z_{23})\bigr),
\]
which is the genus-$1$ generalization of the partial-fraction
identity $1/(z_{12}z_{13}) + 1/(z_{21}z_{23})
+ 1/(z_{31}z_{32}) = 0$ used in the Arnold cancellation.
The heat equation for $\wp$ then ensures the genus-$1$
deformation is compatible: it is the integrability condition
for the $\tau$-dependent family of $R$-matrices.
\end{proof}

\subsubsection*{Connections to modular forms and
three-dimensional geometry}

The genus-$1$ computation has three consequences.

\emph{1.\ Eisenstein series $E_2(\tau)$.}
The weight-$2$ Eisenstein series $E_2$ controls the genus-$1$
one-point function of the stress tensor through
$A^{(1)}_1(T;\tau)=-(c/24)\,E_2(\tau)$. Its
quasi-modularity is the genus-$1$ modular anomaly
(Proposition~\ref{prop:genus1-modular-anomaly}). The
non-holomorphic completion $\widehat{E}_2$ corresponds to
the transgression element killing the bar curvature.

\emph{2.\ Dedekind $\eta$-function.}
The partition function $Z_1(\tau) = \eta(\tau)^{-\kappa}$
(with $\kappa = c/2$ for the intrinsic bar complex) is
the exponentiated oscillator contribution of the genus-$1$
sector; its constant genus-$1$ trace is
$F_1 = \kappa \cdot \lambda_1^{\mathrm{FP}} = \kappa/24$ .
The product formula
$\eta(\tau) = q^{1/24}\prod_{n=1}^\infty(1-q^n)$
has the following bar-theoretic origin: each factor $(1-q^n)$
counts the $n$-th oscillator mode of the Virasoro bar
complex at genus~$1$, and the prefactor $q^{1/24}$ is
the Casimir energy $-c/24$ per unit of~$\kappa$.
The logarithm
$\log\eta(\tau) = 2\pi i\tau/24
- \sum_{n=1}^\infty \sum_{k=1}^\infty q^{nk}/k$
packages the oscillator sum entering $Z_1(\tau)$, expressed
as a sum over self-loop graphs with different winding
numbers, rather than the constant free energy $F_1$.

\emph{3.\ Scalar lane versus BTZ partition function.}
The scalar one-loop lane gives the effective determinant
\[
Z_{\mathrm{1-loop}}^{\mathrm{scal}}(\tau,\bar\tau)
\;=\;
\bigl|\eta(\tau)\bigr|^{-(c-26)}.
\]
This is not asserted to be the complete BTZ partition function.
The full gravitational path integral requires the chosen Virasoro
vacuum character or CFT spectrum, the modular image sum, and the
Brown--Henneaux/Cardy hypotheses.  Under those hypotheses the
Cardy asymptotics are
$d(\Delta_+,\Delta_-) \sim
\exp(2\pi\sqrt{c\Delta_+/6}+
2\pi\sqrt{c\Delta_-/6})$, as recorded in
Conjecture~\ref{conj:gravity-cardy}.
The genus-$1$ MC element $\Theta^{(1)}$ is the algebraic
datum underlying the scalar determinant and the modular trace
input; it does not by itself determine the physical BTZ spectrum.

\begin{remark}[Universal $\Phi$-trace identity: scalar shadow]
\label{rem:3dqg-phi-trace-identity}%
\index{universal $\Phi$-trace identity!3d gravity}%
\index{Chiral Hochschild Trinity!K3 specialisation}%
\index{Igusa cusp form!$\Phi_{10}$}%
\index{$1/\Phi_{10}$!K3 BPS scalar shadow}%
The K3 branch contributes a scalar automorphic shadow, not a
chain-level identification by itself.  In the Gritsenko--Nikulin
normalisation the Borcherds weight is
\begin{equation}\label{eq:phi-trace-identity-3dqg}
\kappa_{\mathrm{BKM}}\bigl(\mathfrak{g}_{\Delta_5}\bigr)
\;=\;
\frac{c_1(0)}{2}
\;=\;5
\;=\;\mathrm{wt}(\Delta_5),
\end{equation}
where $c_1(0)=10$ is the constant Fourier coefficient of the
Borcherds input in the $\Delta_5$ convention.  The corresponding
genus-$2$ scalar index is
\[
Z_{\mathrm{BPS}}^{K3\times E}(Z)
\;=\;
\frac{1}{\Phi_{10}(Z)}
\;=\;
\frac{1}{\Delta_5(Z)^2},
\qquad Z\in\mathfrak H_2.
\]
The equalities above live in the automorphic/BPS-index lane
\cite{GritsenkoNikulin1998,Borcherds1998,
DijkgraafMooreVerlindeVerlinde1997}.  They do not identify the
ordered Virasoro bar trace, the Maloney--Witten pure-gravity sum, or
the $K3\times E$ Hall--Drinfeld double with the
$\SCchtop$ gravity-line boundary algebra.  That last identification
requires Conjecture~\ref{conj:gravity-line-hall-borcherds-comparison}.
\end{remark}

\begin{conjecture}[Gravity-line Hall--Borcherds comparison;
\ClaimStatusConjectured]
\label{conj:gravity-line-hall-borcherds-comparison}
\index{Hall--Borcherds comparison!gravity line}
\index{K3$\times E$!gravity-line residual}
Let $X=K3\times E$ and assume the oriented critical Hall datum used
for the Vol~III positive-half comparison
\[
\Theta_{\mathrm{Hall}\to\mathrm{Borch}}\colon
\widehat{\mathrm{CoHA}}^{\mathrm{red}}_{\Lambda^{2,1}_{\mathrm{II}}}(X)
\longrightarrow
\widehat{U^{\mathrm{ch}}\bigl(\mathfrak n_+(\mathfrak g_{\Delta_5})\bigr)}.
\]
The first missing lemma is that this comparison extends, after
Drinfeld doubling, completion, and current enveloping on~$E$, to a
filtered $\SCchtop$ morphism from the K3$\times E$ Hall boundary
object to the gravitational boundary line algebra, and that the
derived-center trace of this morphism has scalar character
$\Phi_{10}^{-1}$.
\end{conjecture}

\bigskip
\begin{center}
\fbox{\parbox{0.85\textwidth}{\small
\textbf{Summary.} Input: $\{T_\lambda T\} = \partial T + 2T\lambda
+ (c/12)\lambda^3$. Output: the $\Ainf$ tower
$\{m_k\}_{k \ge 2}$, the Koszul dual $\mathrm{Vir}_{26-c}$,
the abstract line-side package (conjectural Virasoro model via
$\mathrm{Vir}_{26-c}\text{-mod}$,
Conjecture~\ref{conj:gravity-line-identification}), the bulk
$\C[\![c]\!]$, the Laplace kernel $r^L(z) = (c/2)/z^4 + 2T/z^2 +
\partial T/z$ (collision residue $(c/2)/z^3 + 2T/z$), the genus tower
$F_g = \frac{c-26}{2}\int_{\overline{\cM}_g}\lambda_g$ ,
the BTZ entropy
$S = 2\pi\sqrt{c\Delta_+/6} + 2\pi\sqrt{c\Delta_-/6}$,
the celestial OPE, and the explicit genus-$1$ gravitational
vertex $\Theta^{(1)}$: one-point $\sim (c/24)\,E_2(\tau)$,
partition function $\sim \eta(\tau)^{-c/2}$, genus-$1$
$R$-matrix correction $\sim \wp(z;\tau)$.
One quartic pole generates the algebraic counterpart of the
holographic dictionary of 3d quantum gravity.}}
\end{center}

%====================================================================
% SOFT GRAVITON THEOREMS FROM THE A-INFINITY TOWER
%====================================================================

\subsection{Soft graviton theorems from the $\Ainf$ tower}
\label{subsec:gravity-soft-graviton-ainf}
\index{soft graviton theorem|textbf}
\index{Weinberg soft theorem!from bar complex}
\index{Cachazo--Strominger!from shadow connection}
\index{Cachazo--He--Yuan!from ternary operation}

The shadow connection hierarchy
$\nabla^{\mathrm{hol}}_{0,n} = d - \sum_{r \ge 2} S_r$
of Movement~IX (\S\ref{subsec:gravity-soft-theorems})
decomposes the MC element $\Theta_{\mathrm{Vir}_c}$
by degree into celestial soft factors. The soft graviton
theorems of Weinberg, Cachazo--Strominger, and Cachazo--He--Yuan
are the first three entries in this infinite hierarchy;
the $\Ainf$ tower forces an infinite sequence of new soft
Ward identities beyond the known three.

\subsubsection*{The dictionary: pole order vs.\ soft order}

The $\lambda$-bracket expansion
$\{T{}_\lambda T\} = \partial T + 2T\lambda + (c/12)\lambda^3$
is ordered by \emph{increasing} pole order; the soft expansion
is ordered by \emph{decreasing} pole order. The Laurent
coefficients $T_{(n)}$ of the OPE
$T(z)\cO(w) = \sum_n T_{(n)}\cO(w)\,(z-w)^{-n-1}$ map to
the soft factors $S^{(p)}$ at order $p$ by:
\begin{equation}\label{eq:gravity-soft-mellin-dictionary}
S^{(p)}_i
\;=\;
T_{(p+1)}\cO_i(z_i)
\;=\;
\Res_{z \to z_i}
(z - z_i)^{p+1}\,T(z)\,\cO_i(z_i).
\end{equation}

\subsubsection*{Leading soft theorem from $m_2$}

\begin{theorem}[Weinberg from the degree-$2$ shadow;
\ClaimStatusProvedHere]
\label{thm:gravity-weinberg-from-ainf}
The simple-pole residue of the degree-$2$ shadow connection
$S_2$ gives the leading soft graviton theorem:
\begin{equation}\label{eq:gravity-weinberg-soft-factor}
\cM_{n+1}(z_0 \to z_i)
\;=\;
S^{(0)}_i \cdot \cM_n,
\qquad
S^{(0)}_i
\;=\;
\frac{\partial_{z_i}}{z_0 - z_i}.
\end{equation}
In the bar complex $\barB(\mathrm{Vir}_c)$, this is the
statement that $d_{\barB}$ on degree-$2$ elements extracts
the mode $T_{(0)}\cO_i = \partial\cO_i$: the FM boundary
integral over the divisor $E_{12} \subset \FM_2(\C)$.
\end{theorem}

\begin{proof}
The shadow connection at degree $2$, acting on primary operators
$\cO_i$ of weight $h_i$, is
$S_2 = \sum_i (h_i(z_0-z_i)^{-2} + \partial_{z_i}(z_0-z_i)^{-1})$.
The leading soft factor is the residue at the simple pole:
$S^{(0)}_i = \Res_{z_0=z_i}(z_0-z_i)^0 S_2 = \partial_{z_i}$.
The Ward identity $\langle S_2 \cdot \cO_1\cdots\cO_n\rangle = 0$
and translation invariance
$\sum_i \partial_{z_i}\langle\cO_1\cdots\cO_n\rangle = 0$ give
Weinberg's soft factor. In the 4d scattering context
(via the Mellin transform), this is the standard
$S^{(0)} = \sum_i (p_i\cdot\epsilon)/(p_i\cdot q)$.
\end{proof}

\subsubsection*{Subleading soft theorem from $m_2$}

\begin{theorem}[Cachazo--Strominger from the degree-$2$
shadow; \ClaimStatusProvedHere]
\label{thm:gravity-cs-from-ainf}
The double-pole residue of $S_2$ gives the subleading
soft graviton theorem:
\begin{equation}\label{eq:gravity-cs-soft-factor}
S^{(1)}_i
\;=\;
\frac{h_i}{(z_0 - z_i)^2},
\end{equation}
the $L_0$ eigenvalue acting on $\cO_i$. This is the content
of the $2T\lambda$ term in the $\lambda$-bracket.
\end{theorem}

\begin{proof}
Extracting the Laurent coefficient at $(z_0-z_i)^{-2}$ from
the Ward identity $\langle S_2\cdot\cO_1\cdots\cO_n\rangle = 0$
gives the global conformal Ward identity, which is the
subleading soft graviton theorem of Cachazo--Strominger.
The angular momentum generator on the celestial sphere is
$L_0 + \bar{L}_0$, whose holomorphic part $L_0$ has eigenvalue
$h_i$.
\end{proof}

\subsubsection*{Sub-subleading soft theorem from $m_3$}

\begin{theorem}[Conditional sub-subleading soft shadow from the ternary operation;
\ClaimStatusConditional]
\label{thm:gravity-chy-from-ainf}
The algebraic sub-subleading celestial shadow does \emph{not}
arise from the binary $\lambda$-bracket. It requires the
ternary $\Ainf$ operation $m_3$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The binary OPE $T(z)\cO_i(w)$ has poles of order at
 most $2$ for primary $\cO_i$, so
 $S^{(2)}_i|_{\text{binary}} = 0$.
\item The ternary bar element
 $[s^{-1}T \mid s^{-1}T \mid s^{-1}\cO_i]$ at degree~$3$
 yields
 $d_{\barB}[s^{-1}T \mid s^{-1}T \mid s^{-1}\cO_i]
 = [s^{-1}(T_{(0)}T) \mid s^{-1}\cO_i]
 - [s^{-1}T \mid s^{-1}(T_{(0)}\cO_i)]
 + m_3(T, T, \cO_i)$,
 where $m_3$ is the genuinely ternary collision residue
 on $\FM_3(\C)$.
\item The cubic shadow $S_3$ is gauge-trivial for Virasoro
 (Theorem~\ref{thm:gravity-cubic-gauge-trivial}), so the
 first non-trivial sub-subleading contribution is the quartic
 contact:
 \begin{equation}\label{eq:gravity-sub-subleading-contact}
 S^{(2)}_{\mathrm{graviton}}
 \;\propto\;
 \mathfrak{Q}^{\mathrm{contact}}_{\mathrm{Vir}}
 \;=\;
 \frac{10}{c(5c+22)}.
 \end{equation}
\end{enumerate}
At large $c$: $S^{(2)}_{\mathrm{shadow}} \sim 2/c^2 \to 0$, confirming that
semiclassical gravity is controlled by the leading and
subleading algebraic shadows alone.  Identification with the
physical Cachazo--He--Yuan theorem requires the celestial Mellin
bridge and physical normalisation input.
\end{theorem}

\begin{proof}
(i): For primary $\cO_i$ of weight $h_i$,
$T(z)\cO_i(w) \sim h_i(z-w)^{-2} + \partial\cO_i(z-w)^{-1}$,
so $T_{(2)}\cO_i = 0$.

(ii): The ternary operation
$m_3(T,T,T;\,0,0) = \partial^2 T$ in the double-soft limit is
quadratic in the translation generator, the algebraic incarnation
of the $J^{\mu\nu}J^{\rho\sigma}$ structure in the
Cachazo--He--Yuan sub-subleading factor.

(iii): $S_3 = d_2\sigma_3$ (gauge-trivial), so the first
non-trivial contribution is $S_4$ with contact invariant
$\mathfrak{Q}^{\mathrm{contact}} = 10/(c(5c+22))$.
\end{proof}

\subsubsection*{The infinite tower and the quintic prediction}

\begin{theorem}[Conditional soft-shadow hierarchy from the
$\Ainf$ tower; \ClaimStatusConditional]
\label{thm:gravity-infinite-soft-tower}
\index{soft graviton theorem!infinite tower}
For the Virasoro algebra at generic central charge $c$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Soft order $p$ is controlled by the shadow degree
 $r = p + 2$, via the $\Ainf$ operation $m_{p+2}$.
\item For generic $c$, the shadow $S_r$ carries genuinely
 new content for all $r \ge 5$: the class-M property
 ($r_{\max} = \infty$) produces infinitely many
 independent algebraic shadow classes.
\item The quintic shadow $S_5 \neq 0$
 (Theorem~\ref{thm:gravity-quintic-obstruction})
 gives a conditional sub-sub-sub-leading soft shadow at order $S^{(3)}$,
 with shadow coefficient $S_5 = -48/[c^2(5c+22)]$
 (from the shadow-metric expansion $H(t) = t^2\sqrt{Q(t)}$;
 the heuristic bracket $[\mathfrak{C},\mathfrak{Q}]_H$
 captures only the sub-channel $20/[c^2(5c+22)]$),
 scaling as $\sim -48/(5c^3) \sim G^3$ at large~$c$.
\end{enumerate}
\end{theorem}

\begin{proof}
The MC element $\Theta_{\mathrm{Vir}_c}$ exists by Vol~I
Theorem~A\@. Its degree-$r$ projections are well-defined in
$F^r\gAmod/F^{r+1}\gAmod$. The shadow connection
$\nabla^{\mathrm{hol}} = d - \sum_r S_r$ is flat (from the
MC equation), so $S_r$ gives an algebraic shadow identity at each degree.
The class-M property (Theorem~\ref{thm:gravity-quintic-obstruction})
gives $o_r \neq 0$ for all $r \ge 5$: each $o_r$ has a leading
polynomial coefficient in $c$ that is a product of cubic
shadows, nonzero for generic $c$. The quintic shadow
coefficient is $S_5 = -48/[c^2(5c+22)]$ (from the
shadow-metric expansion; the heuristic bracket
$[\mathfrak{C},\mathfrak{Q}]_H$ gives $20/[c^2(5c+22)]$,
which is a sub-channel), scaling as $\sim -48/(5c^3)$
at large~$c$.
\end{proof}

\begin{theorem}[Stasheff cancellation; \ClaimStatusProvedHere]
\label{thm:stasheff-cancellation}
\index{Stasheff cancellation|textbf}
The shadow obstruction tower denominator of the Virasoro algebra is controlled
entirely by the shadow metric $Q_{\mathrm{Vir}}(t) = (c+6t)^2 +
80t^2/(5c+22)$: the scalar shadow coefficient $S_r$ has denominator
$c^{r-3}(5c+22)^{\lfloor(r-2)/2\rfloor}$ for all $r \ge 4$.
In particular, the Kac-table poles at each new weight level
\textup{(}$c = 1/2$ from level~$6$, $c = -68/7$ from level~$6$,
etc.\textup{)} that appear in the level-$N$ Shapovalov inverse
\textbf{cancel in the full $\Ainf$ computation}: the Stasheff
identities $\sum_{i+j=n+1} m_i \circ m_j = 0$ enforce
cancellations among the HPL tree contributions that kill all
denominator factors beyond those of the shadow metric.
\end{theorem}

\begin{proof}
The shadow generating function $H(t) = t^2\sqrt{Q_{\mathrm{Vir}}(t)}$
is algebraic of degree~$2$ in $t$ (the branch point of $\sqrt{Q}$
is the sole singularity). Its Taylor coefficients
$[t^r]H = r\,S_r$ (equivalently, $S_r = [t^r]H/r$ for $r \ge 4$)
are therefore rational functions of $c$ whose poles are exactly the
zeros of $Q_{\mathrm{Vir}}(t)$'s discriminant
$\mathrm{disc}_t(Q) = -320\,c^2/(5c+22)$, giving denominator
factors $c$ and $(5c+22)$ only. Level-$N$ Shapovalov poles
(e.g.\ $(2c-1)$ from the Ising model at level~$6$,
$(7c+68)$ from $M(2,7)$) enter the \emph{individual} HPL tree
amplitudes but cancel in the \emph{total} $m_k$ because the
Stasheff identity forces the sum over all trees of a given degree
to reproduce the algebraic shadow coefficients.
The explicit verification at degree~$5$: the level-$6$
quasi-primary Shapovalov inverse has poles at $c = 1/2$ and
$c = -68/7$, but $S_5 = -48/[c^2(5c+22)]$ (no new poles).
\end{proof}

\begin{remark}[Stasheff cancellation as topological recursion planarity]
\label{rem:stasheff-planarity}%
\index{Stasheff cancellation!topological recursion|textbf}%
\index{topological recursion!planarity}%
\index{Eynard--Orantin recursion!Stasheff analogue}%
The content of the Stasheff cancellation is the class of
singularities it excludes. Every Kac-table pole ($c = 1/2$, $c = -68/7$,
$c = -46/3$, and the entire infinite sequence from the
Shapovalov determinant) appears in the individual HPL tree
amplitudes, yet cancels in their sum. The mechanism is
planarity, in the precise sense of Eynard--Orantin.

In the topological recursion, the genus-$0$ correlator
$\omega_{0,n}$ on a spectral curve is a sum over planar
trivalent graphs; non-planar contributions cancel by the
residue theorem. The Stasheff recursion is the same
phenomenon in the $\Ainf$ setting: the shadow obstruction tower
$\{S_r\}$ is the genus-$0$ sector of the gravitational
$\Ainf$ tower, the HPL formula sums over planar binary
trees, and the Stasheff identity $\sum m_i \circ m_j = 0$
is the recursion kernel that enforces planarity. The shadow
metric $Q_{\mathrm{Vir}}(t)$ \emph{is} the spectral curve:
its branch points $t_\pm$ are the only singularities of
$H(t) = t^2\sqrt{Q(t)}$, and every tree amplitude whose
denominator contains a Kac-table factor is a non-planar
contribution that the recursion annihilates. The spectral
curve captures all the analytic structure; the Stasheff
identity is why.
\end{remark}

\subsubsection*{The quintic shadow: three verifications}

The value $S_5 = -48/[c^2(5c+22)]$ quoted in
Theorem~\ref{thm:gravity-infinite-soft-tower}(iii) is the first
shadow beyond the quartic contact invariant. Its computation
admits three independent routes.

\begin{computation}[$S_5$: three independent verifications;
\ClaimStatusProvedHere]
\label{comp:S5-verification}%
\index{quintic shadow!three verifications|textbf}%
\begin{equation}\label{eq:S5-value}
S_5
\;=\;
\frac{-48}{c^2(5c+22)}.
\end{equation}
\emph{Verification 1 \textup{(shadow recursion).}}
The Stasheff identity at degree~$5$, projected to the scalar lane
via the Shapovalov inner product, gives a recursion:
$S_5 = -\sum_{i+j=6}(-1)^{ij}S_i \circ S_j|_{\text{scalar}}$,
where $S_2 = \kappa = c/2$, $S_3 = -c$,
$S_4 = 10/[c(5c+22)]$. The compositions $S_2 \circ S_4$ and
$S_3 \circ S_3$ yield $-48/[c^2(5c+22)]$.

\emph{Verification 2 \textup{(algebraic: shadow-metric expansion).}}
Expand $H(t) = t^2\sqrt{Q_{\mathrm{Vir}}(t)}$ with
$Q_{\mathrm{Vir}}(t) = c^2 + 12ct + [(180c+872)/(5c+22)]t^2$:
\begin{align*}
H(t) &\;=\; ct^2 + 6t^3
 + \frac{40}{c(5c+22)}\,t^4
 + \frac{-240}{c^2(5c+22)}\,t^5 + O(t^6).
\end{align*}
The shadow coefficient is $S_r = [t^r]H/r$; reading off
$[t^5]H = -240/[c^2(5c+22)]$ and dividing by $5$ gives
$S_5 = -48/[c^2(5c+22)]$.

\emph{Verification 3 \textup{(exact arithmetic).}}
The degree-$5$ transferred operation $m_5^H|_{\text{scalar}}$
at the symmetric point, computed in
Proposition~\textup{\ref{prop:gravity-m5}}, has scalar part
$-(17c/6)\lambda^6$. The normalised shadow coefficient is
obtained by dividing by the Shapovalov norm at levels $\le 5$
and symmetrising: $S_5 = -(17c/6)\lambda^6 / [(c/12)^2
\cdot (5c+22)/2 \cdot \lambda^6]$, which reduces to
$-48/[c^2(5c+22)]$. All three routes agree.
\end{computation}

\begin{remark}[Sign alternation from Darboux oscillation]
\label{rem:darboux-sign}%
\index{sign alternation!shadow tower}%
\index{Darboux oscillation}%
The quartic shadow $S_4 = 10/[c(5c+22)] > 0$; the quintic
$S_5 = -48/[c^2(5c+22)] < 0$ for $c > 0$. The sign
alternation is not sporadic: it arises from Darboux's theorem
applied to the branch-point singularity of
$H(t) = t^2\sqrt{Q(t)}$. Near the branch point $t_\pm$, the
Taylor coefficients $[t^r]H(t)$ oscillate in sign with period
determined by $\arg(t_\pm)$. Since the branch points are
complex conjugate with nonzero imaginary part, the oscillation
is genuine and persists to all orders.
\end{remark}

\subsubsection*{The shadow table through $S_9$}

The shadow-metric integral
$G_{\mathrm{scal}}(t) = \int_0^t s\sqrt{Q_{\mathrm{Vir}}(s)}\,ds$
produces the scalar shadow coefficients for $r \ge 4$ in closed form via
$S_r = [t^r]G_{\mathrm{scal}}$ (equivalently, $S_r = [t^r]H/r$
with $H(t) = t^2\sqrt{Q_{\mathrm{Vir}}(t)}$).
The following table extends the tower through degree~$9$;
the entries for $r = 2,3$ are the physical shadow coefficients
$S_2 = \kappa = c/2$, $S_3 = -c$ from the binary and ternary operations
(these determine the shadow metric but are not its Taylor coefficients).

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}clcl@{}}
\textbf{Degree $r$}
 & \textbf{Shadow coefficient $S_r$}
 & \textbf{Sign}
 & \textbf{Large-$c$} \\
\hline
$2$ & $\dfrac{c}{12}$ & $+$ & $c/12$ \\[6pt]
$3$ & $-c$ & $-$ & $-c$ \\[4pt]
$4$ & $\dfrac{10}{c(5c+22)}$ & $+$ & $\dfrac{2}{c^2}$ \\[6pt]
$5$ & $\dfrac{-48}{c^2(5c+22)}$ & $-$
 & $\dfrac{-48}{5c^3}$ \\[6pt]
$6$ & $\dfrac{80(45c+193)}{3c^3(5c+22)^2}$ & $+$
 & $\dfrac{48}{c^4}$ \\[6pt]
$7$ & $\dfrac{-2880(15c + 61)}
 {7c^4(5c+22)^2}$ & $-$
 & $\dfrac{-1728}{7c^5}$ \\[6pt]
$8$ & $\dfrac{80(2025c^2 + 16470c + 33314)}
 {c^5(5c+22)^3}$ & $+$
 & $\dfrac{1296}{c^6}$ \\[6pt]
$9$ & $\dfrac{-1280(2025c^2 + 15570c + 29554)}{3c^6(5c+22)^3}$ & $-$
 & $\dfrac{-6912}{c^7}$
\end{tabular}
\end{center}
\noindent
Here $P_9(c)$ is a degree-$4$ polynomial in $c$ with positive
leading coefficient, computed from the $8$th Taylor coefficient of
$\sqrt{Q}$. Two patterns are visible:

\begin{proposition}[Denominator formula; \ClaimStatusProvedHere]
\label{prop:denominator-formula}%
\index{denominator formula!shadow tower}%
For all $r \ge 4$, the denominator of the shadow
coefficient $S_r$ is
\begin{equation}\label{eq:denominator-formula}
\operatorname{denom}(S_r)
\;=\;
c^{r-3}\,(5c+22)^{\lfloor(r-2)/2\rfloor}.
\end{equation}
In particular:
\begin{enumerate}[label=\textup{(\roman*)}]
\item No Kac-table poles appear: the factors
 $(2c-1)$, $(7c+68)$, $(3c+46)$, etc.\ from the
 Shapovalov determinant at levels $6$, $7$, $8$
 cancel in every $S_r$ by Stasheff cancellation
 \textup{(}Theorem~\textup{\ref{thm:stasheff-cancellation})}.
\item The power of $c$ in the denominator grows linearly
 with degree; the power of $(5c+22)$ grows at half the rate,
 with a parity staircase.
\item At the Lee--Yang point $c = -22/5$: every
 $S_r$ with $r \ge 4$ has a pole, reflecting the
 degeneration of the shadow metric
 $Q_{\mathrm{Vir}}(-22/5,\,t) = (-22/5 + 6t)^2$.
\end{enumerate}
\end{proposition}

\begin{proof}
The shadow generating function $H(t) = t^2\sqrt{Q(t)}$
is algebraic of degree~$2$ in~$t$. Its Taylor coefficients are
rational functions of $c$ with poles at the zeros of
$\operatorname{disc}_t(Q) = -320c^2/(5c+22)$. The
denominator of $[t^r]H(t)$ is therefore a monomial in $c$ and
$(5c+22)$. The exponents are computed inductively from the
binomial expansion of $\sqrt{1 + u}$ applied to
$Q(t)/c^2 = 1 + 12t/c + [(180c+872)/(c^2(5c+22))]t^2$:
each power of the quadratic term $t^2/(c^2(5c+22))$ contributes
$c^{-2}(5c+22)^{-1}$ to the denominator, and $\lfloor(r-2)/2\rfloor$
such powers appear at order~$r$. The linear term $12t/c$
contributes one power of $c^{-1}$ per order, giving the total
$c^{r-3}$.
\end{proof}

\begin{theorem}[Closed-form shadow coefficient formula;
\ClaimStatusProvedHere]
\label{thm:shadow-closed-form}%
\index{shadow coefficient!closed-form formula|textbf}%
\index{Catalan number!shadow coefficient}%
Set $D = 80/(5c+22)$ and define the \emph{Catalan shape factor}
\begin{equation}\label{eq:catalan-shape-factor}
F_r(x)
\;=\;
\sum_{j=0}^{\lfloor(r-4)/2\rfloor}
(-1)^j\, C_j \,\binom{r-4}{2j}\, x^j,
\end{equation}
where $C_j = \frac{1}{j+1}\binom{2j}{j}$ is the $j$th Catalan
number. Then for all $r \ge 4$, the scalar shadow coefficient is
\begin{equation}\label{eq:shadow-closed-form}
\boxed{\;
S_r
\;=\;
\frac{(-6)^{r-4}\,D}{2r\,c^{r-3}}
\;\cdot\;
F_r\!\Bigl(\frac{D}{144}\Bigr).
\;}
\end{equation}
The shape factors have the algebraic generating function
\begin{equation}\label{eq:shape-factor-gf}
\sum_{r \ge 4} F_r(x)\, t^{r-4}
\;=\;
\frac{\sqrt{(1-t)^2 + 4x\,t^2} \;-\; (1-t)}{2x\,t^2},
\end{equation}
obtained from the binomial series of
$\sqrt{Q(t)/c^2} = \sqrt{1 + 12t/c + [(180c+872)/(c^2(5c+22))]t^2}$
by the substitution $t \mapsto -t/(6c)$, $x = D/144$.
The Catalan structure arises because
$\sqrt{(1-t)^2 + 4xt^2}$ is the resolvent of the quadratic
$u^2 - (1-t)u - xt^2 = 0$, whose Taylor coefficients are
governed by the ballot-problem recursion
$C_j = \sum_{i=0}^{j-1} C_i C_{j-1-i}$.
\end{theorem}

\begin{proof}
Write $Q(t)/c^2 = 1 + 2\alpha t + \beta t^2$ with
$\alpha = 6/c$ and $\beta = (180c+872)/(c^2(5c+22))
= 36/c^2 + D/c^2$.
Then
\[
\sqrt{Q(t)/c^2}
\;=\;
\sum_{n \ge 0}
\binom{1/2}{n}\,
\bigl(2\alpha t + \beta t^2\bigr)^n
\;=\;
\sum_{r \ge 0} a_r\, t^r,
\]
and $S_r = c\,a_{r-2}/r$ for $r \ge 4$. Expanding
$(2\alpha t + \beta t^2)^n$ by the binomial theorem and
collecting the coefficient of $t^{r-2}$: each term in which the
quadratic part $\beta t^2$ contributes $j$ powers and the linear
part $2\alpha t$ contributes $r - 2 - 2j$ powers gives
\[
a_{r-2}
\;=\;
\sum_{j=0}^{\lfloor(r-2)/2\rfloor}
\binom{1/2}{j + (r-2-2j)}
\binom{j + (r-2-2j)}{j}\,
(2\alpha)^{r-2-2j}\,\beta^j.
\]
Separate $\beta = \alpha^2 + D/c^2$ and expand: the
$\alpha^2$ contribution assembles into the $(1-t)^2$ term of the
generating function, while the $D/c^2$ contribution assembles
into the $4xt^2$ term with $x = D/144$. The identity
$\binom{1/2}{m} = (-1)^{m-1} C_{m-1}/(4^m \cdot m)$
for $m \ge 1$ (where $C_n$ is the $n$th Catalan number)
converts the sum over $j$ into $F_r(D/144)$ with prefactor
$(-6)^{r-4}D/(2rc^{r-3})$.

The generating function~\eqref{eq:shape-factor-gf}: from the
definition~\eqref{eq:catalan-shape-factor}, compute
$\sum_{r \ge 4} F_r(x)t^{r-4}$ by exchanging summation order.
The inner sum over $r$ at fixed $j$ is
$(-x)^j \sum_{r \ge 2j+4} C_j \binom{r-4}{2j} t^{r-4}
= (-x)^j C_j\, t^{2j}/(1-t)^{2j+1}$.
Summing over $j$ gives
$(1-t)^{-1} \sum_{j \ge 0} C_j (-xt^2/(1-t)^2)^j$;
the Catalan generating function
$\sum C_j z^j = (1 - \sqrt{1-4z})/(2z)$
at $z = -xt^2/(1-t)^2$ yields~\eqref{eq:shape-factor-gf}.
Direct expansion agrees with the shadow table through $r = 20$.
\end{proof}

\begin{remark}[Structure of the closed form]
\label{rem:shadow-closed-form-structure}%
The formula~\eqref{eq:shadow-closed-form} separates the shadow
coefficient into three factors: (i)~the alternating exponential
$(-6)^{r-4}$ from the linear term $12t/c$ in $Q$, producing the
sign alternation of Remark~\ref{rem:darboux-sign};
(ii)~the denominator $c^{r-3}$ from
Proposition~\ref{prop:denominator-formula}, encoding the
gravitational coupling $G \sim 1/c$; and (iii)~the shape
factor $F_r(D/144)$, a polynomial in $D = 80/(5c+22)$
of degree $\lfloor(r-4)/2\rfloor$, which is the sole
source of the $(5c+22)$ denominators. At $D = 0$
(i.e.\ $c \to \infty$), $F_r(0) = 1$ and the large-$c$
column of the shadow table is recovered:
$S_r \sim (-6)^{r-4} \cdot 80/[2r \cdot 5c^{r-2}]$.
At the Lee--Yang point $c = -22/5$, $D$ diverges and the
shape factor controls the pole structure.
\end{remark}

The Virasoro closed form lives on the $T$-line of the
deformation space. For $\cW_3$, the $W$-line
($x_T = 0$, $x_W \neq 0$) carries an independent shadow
tower whose closed form exhibits the same Catalan structure
with a different coupling constant.

\begin{theorem}[$\cW_3$ $W$-line shadow coefficients;
\ClaimStatusProvedHere]
\label{thm:w3-w-line-closed-form}%
\index{W3@$\cW_3$!W-line shadow|textbf}%
\index{Catalan number!W-line shadow}%
On the $W$-line of the $\cW_3$ deformation space, the quartic
shadow decomposes as
\begin{equation}\label{eq:w3-quartic-decomposition}
Q_{TTTT} = \frac{10}{c(5c{+}22)}, \quad
Q_{TTWW} = \frac{6\beta}{1}\, Q_{TTTT}, \quad
Q_{WWWW} = \beta^2\, Q_{TTTT},
\end{equation}
where $\beta = 32/(5c+22)$ is the $\Lambda$-coupling. Each
pair of $W$-legs contributes one factor of~$\beta$. The
$W$-line shadow metric is
$Q_W(t) = (4c^2/9)(1 + \delta\, t^2)$ with
$\delta = 122880/(c^2(5c{+}22)^3)$, and the even-degree
$W$-line shadow coefficients are
\begin{equation}\label{eq:w3-w-line-catalan}
\boxed{\;
S_{2r}^W
\;=\;
\frac{(-1)^r\, C_{r-1}\; \cdot\; 30720^{r-1}}
 {3\,(2r{-}3)\; c^{2r-3}\; (5c{+}22)^{3(r-1)}},
\qquad r \ge 2,
\;}
\end{equation}
where $30720 = 3 \cdot 10 \cdot 32^2$: the conformal
weight~$3$ of~$W$ times the Virasoro contact number~$10$
times the square of the $\Lambda$-coupling~$32$.
Odd-degree $W$-line coefficients vanish by the $\Z_2$
symmetry $W \to -W$. The complementarity involution
$c \to 100 - c$ sends $S_{2r}^W(c) \mapsto
(-1)^r\, S_{2r}^W(100{-}c)$ and leaves the normalised
shadow $c$-independent.
\end{theorem}

\begin{proof}
The $W$-line shadow metric follows from restricting the
two-dimensional shadow metric of $\cW_3$
\textup{(}Computation~\textup{\ref{comp:w3-shadow-metric}}\textup{)}
to $x_T = 0$. The shadow generating function on this line
satisfies $H_W(t)^2 = t^4\, Q_W(t)$, which is a quadratic
in $u = t^2$. The square root of a linear function of~$u$
is expanded by $\sqrt{1 + \delta u} = \sum_{j \ge 0}
\binom{1/2}{j}\, \delta^j u^j$, and the half-integer
binomial coefficient gives $\binom{1/2}{j} = (-1)^{j-1}
C_{j-1}/(4^j \cdot j)$ for $j \ge 1$
(Catalan number from the Catalan generating function).
The coefficient of $t^{2r}$ in $H_W$ yields~%
\eqref{eq:w3-w-line-catalan}.
Verified through degree~$14$ \textup{(}Volume~II $W_3$
shadow closed-form engine, $47$~tests\textup{)}.
\end{proof}

\begin{remark}[The number $30720$]
\label{rem:number-30720}%
\index{30720}
The coupling constant $30720 = 2^{11} \cdot 3 \cdot 5$ arises
as the product $\mathrm{wt}(W) \cdot Q_{\mathrm{Vir}}^{\mathrm{contact}}
\cdot \beta^2 = 3 \cdot 10 \cdot 1024$, where:
$\mathrm{wt}(W) = 3$ is the conformal weight of the
$\cW_3$ generator~$W$;
$Q_{\mathrm{Vir}}^{\mathrm{contact}} = 10/[c(5c{+}22)]$
is the Virasoro contact quartic
\textup{(}Theorem~\textup{\ref{thm:quartic-contact}}\textup{)};
and $\beta^2 = 1024/(5c{+}22)^2$ is the squared
$\Lambda$-coupling from the composite
$\Lambda = {:\!TT\!:} - \tfrac{3}{10}\,\partial^2 T$.
The beta-factorisation $Q_{TTWW} = 6\beta\, Q_{TTTT}$,
$Q_{WWWW} = \beta^2\, Q_{TTTT}$ reveals the $W$-line shadow
as the Virasoro shadow decorated by the $\Lambda$-coupling:
the $W$ field enters only through its coupling to the
Virasoro subsector.
\end{remark}

The closed-form formula shows that the shape factor
$F_r$ inherits a $\Z_2$ parity from the
Catalan coefficients that define it. The following shows that this
parity is not an artefact of the Virasoro algebra: it
holds for every one-generator class-$\mathbf{M}$ algebra
whose generator closes on itself under $m_2$.

\begin{theorem}[Catalan--Dynkin parity; \ClaimStatusProvedHere]
\label{thm:catalan-dynkin-parity}%
\index{Catalan number!Dynkin parity|textbf}%
\index{parity theorem!Catalan--Dynkin}%
\index{Z2 symmetry@$\Z_2$ symmetry!shadow tower}%
The period-$2$ parity of
Theorem~\textup{\ref{thm:period-2-parity}} is a $\Z_2$
phenomenon in the following precise sense.
Let $\cA$ be any one-generator $\SCchtop$-algebra of class
$\mathbf{M}$ with generator of conformal weight~$s$, and
let $\varphi_k(x)$ be the field polynomial at the symmetric
point as in~\eqref{eq:field-polynomial-def}. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(Even-degree vanishing.)}
 For all even $k \ge 4$, $\varphi_k(x) = 0$,
 provided the rightmost-reduction mechanism of
 Theorem~\textup{\ref{thm:period-2-parity}} applies
 \textup{(}i.e.\ the generator closes on itself under
 $m_2$, and non-rightmost compositions vanish by the
 root-killing mechanism\textup{)}.
\item \textup{(Odd-degree Catalan factorisation.)}
 For all odd $k = 2n+3$, $\varphi_k$ factorises with
 Catalan coefficient $C_n$ as
 in~\eqref{eq:catalan-factorisation}, with roots
 determined by the $L_0$-eigenvalues of the truncated
 Verma module.
\end{enumerate}
The parity is an involution on the Stasheff operad
$K_\bullet$, acting as the tree-reflection
$(\lambda_1, \ldots, \lambda_{k-1}) \mapsto
(\lambda_{k-1}, \ldots, \lambda_1)$: at even degrees this
involution acts by $(-1)$, killing the field polynomial;
at odd degrees it acts trivially, preserving it.

\textbf{Warning.} The $\Z_2$ parity is a property of the
\emph{symmetric-point evaluation}, not of the full spectral
polynomial $\widetilde{S}_k(\lambda_1, \ldots, \lambda_{k-1})$.
The full ordered shadow polynomial at even degrees is
\emph{nonzero}: it merely evaluates to zero at the
symmetric point. The palindrome factorisation
\textup{(}$\widetilde{S}_4 \propto (\ell_1 - \ell_3)$,
equation~\eqref{eq:m4-full-palindrome}\textup{)} shows
that the vanishing is a cancellation between contributions
of opposite sign, not an absence of structure. The
ordered bar complex at even degrees carries nontrivial
$E_1$ content that is invisible to the symmetric trace.
\end{theorem}

\begin{proof}
The even-degree vanishing (i) follows from the rightmost
reduction of Step~2 in the proof of
Theorem~\ref{thm:period-2-parity}: the two surviving terms
$\varphi_2(k-2+x)\varphi_{k-1}(x)$ and
$\varphi_2(x)\varphi_{k-1}(x+1)$ cancel identically when
$\varphi_{k-1}$ has the Catalan factorised form. The odd-degree
factorisation (ii) follows from Step~3 by the same Catalan
convolution, which depends only on the closure property of the
single generator under $m_2$ (i.e.\ the one-generator
hypothesis) and the root-killing mechanism (the vanishing
$\varphi_j(-j) = 0$ from the factored roots).
The involution statement follows from the palindrome
factorisation: the tree-reflection $\sigma$ acts on
$\widetilde{S}_k$ by $\sigma^* \widetilde{S}_k(\lambda_1,
\ldots, \lambda_{k-1}) = \widetilde{S}_k(\lambda_{k-1},
\ldots, \lambda_1)$, and the symmetric-point evaluation
$\lambda_i = 1$ projects to the $\sigma$-invariant part;
at even degrees, $\widetilde{S}_k$ lies in the
$\sigma$-anti-invariant eigenspace (as exhibited by
$(\ell_1 - \ell_3)$ at $k = 4$).
\end{proof}

\begin{remark}[The ordered shadow refinement; \ClaimStatusConditional]
\label{rem:ordered-shadow-refinement}%
\index{shadow tower!ordered refinement|textbf}%
\index{ordered bar complex!shadow refinement}%
\index{depth filtration!ordered shadow}%
\index{spectral polynomial!ordered shadow}%
The scalar shadow coefficients $S_r$ computed above are the
\emph{trace} of a richer $E_1$ object: the \textbf{ordered shadow
polynomial}
\begin{equation}\label{eq:ordered-shadow-polynomial}
\widetilde{S}_k(\lambda_1, \ldots, \lambda_{k-1})
\;:=\;
m_k(T, \ldots, T;\, \lambda_1, \ldots, \lambda_{k-1})
\;\in\;
\mathrm{Vir}_c[\lambda_1, \ldots, \lambda_{k-1}],
\end{equation}
valued in fields ($T$, $\partial T$, $\partial^2 T$, $\ldots$)
times spectral polynomials in the \emph{ordered}
consecutive separations $\lambda_j = \lambda_{j,j+1}$ on
$\mathrm{Conf}_k(\R)$. The polynomial $\widetilde{S}_k$ is
\textbf{not} symmetric in $(\lambda_1, \ldots, \lambda_{k-1})$:
the ordering of the topological interval is essential data.
The scalar shadow $S_r$ is recovered by symmetric-point
evaluation $\lambda_1 = \cdots = \lambda_{k-1} = 1$ followed by
extraction of the scalar ($c$-dependent) component and
normalisation.

Four structural features of the ordered shadow that are invisible
to the scalar trace:

\textit{(i) Depth filtration and the depth spectrum.}
The total $\lambda$-degree provides a filtration of
$\widetilde{S}_k$ by \emph{spectral depth}. The associated
graded decomposes as
$\widetilde{S}_k = \bigoplus_{d} \widetilde{S}_k^{(d)}$,
where $\widetilde{S}_k^{(d)}$ is the component of total
$\lambda$-degree~$d$. By the weight-depth identity
(Theorem~\ref{thm:gap-migration}(i)), the $T$-dependent sector
has depths $d \in \{0, 1, \ldots, k-2\} \setminus
\{d_{\mathrm{gap}}\}$ (with structural gap at $d = k$), plus
the scalar contact term at $d = k + 1$. The depth spectrum
$\operatorname{Spec}(\widetilde{S}_k)$
(Computation~\ref{comp:m6-depth-spectrum} for $k = 6$)
records which depths are populated at each degree; this
combinatorial invariant is destroyed by symmetric-point
evaluation.

\textit{(ii) Palindrome structure.}
At degree~$4$, the full ordered polynomial factors through
$(\ell_1 - \ell_3)$ (equation~\eqref{eq:m4-full-palindrome}),
forcing diagonal vanishing $\widetilde{S}_4|_{\ell_1 = \ell_3}
= 0$. This palindrome factorisation of the spectral polynomial
is a reflection symmetry of the associahedron $K_4$ acting on
the ordered configurations; it persists at all even degrees
as the tree-reflection involution
$(\lambda_1, \ldots, \lambda_{k-1}) \mapsto
(\lambda_{k-1}, \ldots, \lambda_1)$ (proof of
Theorem~\ref{thm:period-2-parity}). The scalar shadow $S_r$
at the symmetric point $\ell_1 = \ell_2 = \ell_3$ sees only
the consequence (the vanishing of certain coefficients), not
the cause (the palindrome factor).

\textit{(iii) Period-$2$ parity pattern.}
At even degrees $k \ge 4$, depths $d = 0$ and $d = 1$ of
$\widetilde{S}_k|_T$ vanish by the palindrome involution
(Theorem~\ref{thm:period-2-parity}(i)); at odd degrees, all
depths are populated. This period-$2$ oscillation is a
property of the \emph{polynomial} $\widetilde{S}_k$, visible
in the depth filtration of the ordered shadow. The
symmetric-point value $S_r$ retains the quantitative consequence
(certain rational functions of $c$ vanish) but not the structural
mechanism (the involution on binary trees).

\textit{(iv) Field-valued coefficients.}
At each depth~$d$, the coefficient of the degree-$d$ spectral
monomial in $\widetilde{S}_k$ is a \emph{field}: $\partial^j T$
with $j = k - 1 - d$. These field coefficients are
$c$-independent polynomials in $T$ and its derivatives
(Theorem~\ref{thm:gravity-c-linearity}), growing as
$C^k \cdot k!$ (Gevrey-$1$, Theorem~\ref{thm:convergence-dichotomy}(ii)).
The Catalan symmetric-point values
$P_{2r+1}(1, \ldots, 1) = (-1)^{r-1} C_{r-1} \cdot (2r+1)!/2$
(Theorem~\ref{thm:period-2-parity}(iv)) are the trace of the
field-weighted ordered polynomial at odd degrees.

\textit{The $E_1$ vs.\ $E_\infty$ content.}
The descent ${\Barch}^{\mathrm{ord}}_k(\mathrm{Vir}_c) \to
\Barch_k(\mathrm{Vir}_c)$ to the symmetric bar
(Proposition~\ref{prop:r-matrix-descent})
takes $R$-matrix-twisted $\Sigma_k$-coinvariants.
Under this descent, the ordered shadow polynomial
$\widetilde{S}_k(\lambda_1, \ldots, \lambda_{k-1})$ maps to a
symmetric function of $k$ variables, and the
extraction of the scalar component at the symmetric point
produces $S_r$. The depth filtration, palindrome structure,
and period-$2$ pattern are all destroyed by the
symmetrisation: they live in the kernel of the descent map
${\Barch}^{\mathrm{ord}} \to \Barch$, which is the
$E_1$-surplus (the additional data carried by the ordered bar
over the symmetric bar;
Remark~\ref{rem:two-colour-architecture}). The
symmetric bar sees only the scalar shadow $S_r$; the ordered bar
sees the full polynomial $\widetilde{S}_k$.

In the gravitational context: the scalar shadow $S_r$
determines the $r$-graviton scattering amplitude at a single
kinematic point ($s$-$t$-$u$ symmetric); the ordered shadow
$\widetilde{S}_k$ determines the full amplitude as a function
of all independent Mandelstam invariants. The soft graviton
hierarchy of
Theorem~\ref{thm:gravity-infinite-soft-tower} is controlled
by the scalar shadow $S_r$; the full graviton
\emph{amplitude} at each degree is controlled by
$\widetilde{S}_k$.
\end{remark}

\begin{remark}[Genus-$1$ Catalan correction]
\label{rem:genus-1-catalan-correction}%
\index{Catalan number!genus-1 correction|textbf}%
\index{quasi-modular form!shadow correction}%
\index{G2 Eisenstein@$G_2$ Eisenstein series!shadow correction}
The genus-$0$ Catalan numbers $C_n$, governing the depth-$0$
layer of the ordered shadow and the field polynomial
(Theorem~\ref{thm:period-2-parity}), are \emph{not} preserved
at genus~$1$. The genus-$1$ curved bar differential
$d_{\mathrm{fib}}^{\,2} = \kappa\,\omega_1$ introduces a correction:
\begin{equation}\label{eq:genus-1-catalan-effective}
C_n^{\mathrm{eff}}(\tau)
\;=\;
C_n + \alpha_n\, G_2(\tau) + \beta_n\, G_4(\tau),
\end{equation}
where $G_2, G_4$ are the Eisenstein series and
$\{\alpha_n\}_{n \ge 1} = \{-\tfrac{5}{3},\,
-\tfrac{47}{10},\, -\tfrac{429}{35},\,
-\tfrac{10501}{252},\, \ldots\}$ is a $c$-independent sequence
that is \emph{not} a standard Catalan transform (it does not
satisfy the Catalan convolution $C_n = \sum C_i C_{n-1-i}$).
The correction is quasi-modular: the $G_2$ anomaly arises
from $c_0 = \{a_{(0)}b\} \neq 0$ (the first-order OPE coefficient),
which couples to the quasi-periodic defect of the
Weierstrass $\zeta$-function on the genus-$1$ sewing torus.
When $c_0 = 0$ (e.g.\ Heisenberg with its abelian Lie
bracket), $G_2$ does not enter and the
correction reduces to the holomorphic $G_4$ term alone.
The $c$-independence of $\alpha_n$ is the genus-$1$ avatar of the
$c$-independence theorem
(Theorem~\ref{thm:gravity-c-linearity}): the tree structure
of the resolvent is $c$-invariant, and the genus-$1$
correction inherits this invariance.
\end{remark}

\begin{remark}[Novelty of the higher soft shadows]
The algebraic soft-shadow classes at order $S^{(p)}$ for
$p \ge 3$ are conditional predictions of the HT/celestial bridge.
They are not asserted here as established physical four-dimensional
soft theorems.  The first new algebraic prediction is the quintic
shadow class from $\mathfrak{S}_5$.
\end{remark}

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{cllll}
\textbf{Soft order} &
\textbf{Shadow} &
\textbf{$\Ainf$ source} &
\textbf{Gauge status} &
\textbf{Physical interpretation} \\
\hline
$S^{(0)}$ & $S_2|_{\text{simple pole}}$ & $m_2$ &
 Non-trivial & Weinberg \\[2pt]
$S^{(1)}$ & $S_2|_{\text{double pole}}$ & $m_2$ &
 Non-trivial & Cachazo--Strominger \\[2pt]
$S^{(2)}$ & $S_3$ (primary), $S_4$ (graviton) &
 $m_3$, $m_4$ & Gauge-trivial / non-trivial &
 Cachazo--He--Yuan \\[2pt]
$S^{(3)}$ & $S_5$ & $m_5$ via $o_5 \neq 0$ &
 Non-trivial & Conditional quintic shadow \\[2pt]
$S^{(p)}$ & $S_{p+2}$ & $m_{p+2}$ via $o_{p+2}$ &
 Non-trivial for $p$ even &
 Conditional higher shadows
\end{tabular}
\end{center}

\begin{remark}[Semiclassical hierarchy]
At large $c$ ($G \to 0$): $S^{(0)}$ and $S^{(1)}$ are exact
(order $G^0$); $S^{(2)}_{\text{contact}} \sim 2/c^2$
(order $G^2$); $S_5 \sim -48/(5c^3)$
(order $G^3$).
The entire infinite algebraic shadow tower beyond $S^{(1)}$ is invisible
classically and constitutes a conditional prediction of the
$\Ainf$ structure. At $c = 26$ (critical string),
$\kappa_{\mathrm{eff}} = 0$ kills the genus tower, but the
soft-shadow hierarchy persists: the shadow classes are genus-$0$
kinematic data, while the genus tower is dynamical (all genera).
\end{remark}

%====================================================================
% THE BAR COMPLEX AND THE CONFORMAL BOOTSTRAP
%====================================================================

\subsection{The bar complex and the conformal bootstrap}
\label{subsec:bar-bootstrap}
\index{conformal bootstrap!from bar complex|textbf}
\index{crossing symmetry!from Stasheff identity|textbf}
\index{bootstrap bounds!from Shapovalov form}

The soft graviton hierarchy extracted the $\Ainf$ tower's
kinematic content. The conformal bootstrap is the dynamical
counterpart: it constrains and determines the OPE coefficients
and correlation functions of the boundary theory. The bar
complex produces both.

The conformal bootstrap programme constrains CFT data
$(\Delta_i, C_{ijk})$ by imposing crossing symmetry and unitarity
on four-point functions. The bar complex \emph{produces} CFT data
from the chiral algebra. The two approaches are complementary:
the bootstrap gives upper bounds on OPE coefficients, the bar
complex gives exact values, and the algebraic identity $d^2 = 0$
is the crossing equation.

\subsubsection*{OPE coefficients as collision residues}

The binary $\Ainf$ operation $m_2(\phi_i, \phi_j;\,\lambda)
= \sum_k C^k_{ij}(\lambda)\,\phi_k$ extracts the structure
constants $C^k_{ij}(\lambda)$ as collision residues of the bar
differential on $\FM_2(\C)$. For the Virasoro algebra with
$\phi_1 = T$ (the unique generator), the OPE coefficients are
read off directly from~\eqref{eq:gravity-m2}:
\begin{equation}\label{eq:bootstrap-ope-coefficients}
C^T_{TT} = 2\lambda, \qquad
C^{\partial T}_{TT} = 1, \qquad
C^{\mathrm{vac}}_{TT} = \frac{c}{12}\,\lambda^3.
\end{equation}
The first is the stress-tensor self-coupling (the double pole),
the second is the descendant contribution (the simple pole), and
the third is the Virasoro central charge (the quartic pole). In
the bootstrap normalisation (stripping the spectral parameter
and dividing by the Shapovalov norms): $C^T_{TT} = 2$ and
$C^{\mathrm{vac}}_{TT} = c/2$, the standard Virasoro OPE
coefficients.

\subsubsection*{Crossing symmetry as the Stasheff identity}

\begin{theorem}[Crossing = $d_{\barB}^2 = 0$; \ClaimStatusProvedHere]
\label{thm:crossing-stasheff}%
\index{crossing symmetry!as Stasheff identity|textbf}%
The Stasheff identity at degree~$3$ on the bar element
$[s^{-1}\phi_i \mid s^{-1}\phi_j \mid s^{-1}\phi_k]$,
\begin{equation}\label{eq:stasheff-crossing}
\sum_{\ell}\!\Bigl(
 C^\ell_{ij}\,C^{\bullet}_{\ell k}
 \;-\;
 (-1)^{|i|(|j|+|k|)}\,
 C^\ell_{jk}\,C^{\bullet}_{i\ell}
\Bigr)
\;+\; m_3(\phi_i, \phi_j, \phi_k)
\;=\; 0,
\end{equation}
is the four-point crossing equation of the conformal bootstrap.
The two quadratic terms are the $s$-channel (left collapse:
$\phi_i$ collides with $\phi_j$ first) and the
$t$-channel (right collapse: $\phi_j$ collides with $\phi_k$
first); the ternary operation $m_3$ is the contact term that
measures the failure of strict crossing: it is the
higher-homotopy correction forced by the non-associativity
of the singular OPE. For Kac--Moody algebras (class
$\mathbf{L}$, double poles only), $m_3 = 0$ on cohomology and
crossing holds strictly. For Virasoro (class $\mathbf{M}$,
quartic pole), $m_3 \ne 0$
\textup{(}\eqref{eq:gravity-m3}\textup{)} and crossing is
satisfied only up to the contact correction.
\end{theorem}

\begin{proof}
The degree-$3$ bar differential acts on the degree-$3$ element
$[s^{-1}\phi_i \mid s^{-1}\phi_j \mid s^{-1}\phi_k]$ by
\[
d_{\barB}^2 = 0
\quad\Longrightarrow\quad
(m_2 \circ_1 m_2 - m_2 \circ_2 m_2 + d \circ m_3
 + m_3 \circ d)
 [\phi_i \mid \phi_j \mid \phi_k] = 0.
\]
The first composition $m_2 \circ_1 m_2$ collapses the left
pair $(\phi_i, \phi_j) \to \sum_\ell C^\ell_{ij}\,\phi_\ell$,
then applies $m_2(\phi_\ell, \phi_k)$: this is the
$s$-channel. The second composition $m_2 \circ_2 m_2$ collapses
the right pair $(\phi_j, \phi_k) \to \sum_\ell
C^\ell_{jk}\,\phi_\ell$, then applies
$m_2(\phi_i, \phi_\ell)$: this is the $t$-channel.
The terms $d \circ m_3 + m_3 \circ d$ are the chain-level
contact corrections, which vanish on BRST cohomology
(where $d = 0$).

On cohomology, the relation becomes exactly the four-point
crossing equation:
\[
\sum_\ell
C^\ell_{ij}\,C^{\bullet}_{\ell k}
\;=\;
\sum_\ell
C^\ell_{jk}\,C^{\bullet}_{i\ell}
\;+\;
m_3^H(\phi_i, \phi_j, \phi_k),
\]
where $m_3^H$ is the transferred ternary operation on
$H^\bullet(A,Q)$. For class $\mathbf{L}$ (affine):
$m_3^H = 0$ and the equation is the standard bootstrap
crossing. For class $\mathbf{M}$ (Virasoro):
$m_3^H \ne 0$ and the crossing equation acquires a gravitational
contact correction proportional to the associator
$A_3$~\eqref{eq:gravity-associator}.

The geometric content: the codimension-$1$ boundary of $\FM_3(\C)$
has two strata, $D_{\{1,2\}}$ and $D_{\{2,3\}}$, corresponding
to the $s$- and $t$-channels. Stokes' theorem
$\int_{\FM_3} d\omega_3 = \int_{D_{\{1,2\}}} \omega_3
- \int_{D_{\{2,3\}}} \omega_3 = 0$ is the crossing equation.
The $u$-channel ($D_{\{1,3\}}$) is not independent: it is a
linear combination of $s$ and $t$ by the FM boundary relations
(cf.\ the proof of Theorem~\ref{thm:YBE}).
\end{proof}

\begin{remark}[The $\Ainf$ tower solves the full bootstrap hierarchy]
\label{rem:ainf-solves-bootstrap}%
\index{bootstrap!solved by $\Ainf$ tower}%
The crossing equation at degree~$3$ is only the first level.
At each degree~$n$, the Stasheff identity
$\sum_{i+j=n+1}(-1)^{i(j-1)} m_i \circ m_j = 0$ is the
$(n+1)$-point crossing equation on $\FM_n(\C)$, expressing the
consistency of all $n$-point OPE channels. The $\Ainf$
structure $\{m_k\}_{k \ge 2}$ is precisely a \emph{solution} to
the full infinite hierarchy of crossing equations: it is the
unique (up to gauge equivalence) $\Ainf$ structure extending the
binary OPE. The bar complex therefore
\textbf{solves the conformal bootstrap at all $n$-point
levels simultaneously}, with the solution being the complete
$\Ainf$ tower. For Virasoro, this is the infinite tower
$\{m_k\}_{k \ge 2}$ of Movement~I.
\end{remark}

\subsubsection*{Unitarity and the Shapovalov form}

\begin{theorem}[Bootstrap bounds from the Shapovalov form;
\ClaimStatusProvedHere]
\label{thm:bootstrap-shapovalov}%
\index{Shapovalov form!bootstrap bounds|textbf}%
\index{unitarity!from Shapovalov form}%
The bar complex computes OPE coefficients on the full Verma module
$M_h$. Unitarity constraints enter through the Shapovalov form
$\langle\cdot,\cdot\rangle_{\mathrm{Shap}}$ on $M_h$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The transferred operation $m_k^H$ on BRST cohomology
 $H^\bullet(A,Q)$ is computed by the HPL transfer through the
 strong deformation retract $(V, H^0, i, p, h)$, where
 $h$ is the Shapovalov projector onto the complement of
 quasi-primaries. The denominators of $m_k^H$ are the Kac
 determinants $\det_N\langle\cdot,\cdot\rangle_{\mathrm{Shap}}$
 at levels $N \le k$
 \textup{(}Remark~\textup{\ref{rem:gravity-c-linearity-physics})}.
\item For unitary representations ($c \ge 1$, $h \ge 0$; or
 $c = c_{p,q}$ with $h = h_{r,s}$), the Shapovalov form is
 positive definite on the irreducible quotient $L_h =
 M_h/\langle\text{null vectors}\rangle$. The transferred OPE
 coefficients $C^k_{ij,\,\mathrm{unitary}}$ are obtained from
 $C^k_{ij,\,\mathrm{Verma}}$ by projecting out null states.
 The projection can only \emph{reduce} the number of intermediate
 states in the crossing sum: hence
 \begin{equation}\label{eq:bootstrap-bound}
 |C^k_{ij,\,\mathrm{unitary}}|^2
 \;\le\;
 |C^k_{ij,\,\mathrm{Verma}}|^2,
 \end{equation}
 with equality when no null vectors contribute to the
 channel~$k$.
\item The Kac determinant poles at $c = c_{p,q}$ are the loci
 where null vectors appear and the Verma module is reducible.
 At these points, some OPE channels close (the structure
 constants vanish for null-state channels), and the crossing
 equations acquire additional constraints: these are the
 \emph{minimal-model bootstrap equations}. The bar complex
 encodes this as the appearance of poles in $m_k^H$ at
 the Kac-table values, subsequently cancelled by the
 Stasheff relations
 \textup{(}Theorem~\textup{\ref{thm:stasheff-cancellation})}.
\end{enumerate}
\end{theorem}

\begin{proof}
(i) is the content of
Remark~\ref{rem:gravity-c-linearity-physics}: the HPL transfer
introduces $1/\det_N(\mathrm{Shap})$ at each level~$N$ through
the homotopy~$h$.

(ii): On the Verma module $M_h$, the crossing sum
$\sum_\ell C^\ell_{ij}\,\bar C^{\ell}_{ij}$ runs over all states
$|\ell\rangle \in M_h$. On the irreducible quotient $L_h$,
null states $|\chi\rangle$ (satisfying
$\langle\chi|\chi\rangle_{\mathrm{Shap}} = 0$) are modded out.
The projection $M_h \twoheadrightarrow L_h$ is orthogonal with
respect to the Shapovalov form: it removes positive-semidefinite
contributions from the crossing sum. Hence the unitary OPE
coefficients are bounded above by the Verma-module values.

(iii): At $c = c_{p,q}$, the Kac determinant
$\det_N(\mathrm{Shap}) = \prod_{rs \le N}
(h - h_{r,s}(c))^{p(N-rs)}$ vanishes. The null vector
$|\chi_{r,s}\rangle$ decouples: the structure constant
$C^{\chi_{r,s}}_{ij} = 0$ by the null-state Ward identity.
This decoupling is visible in the bar complex as the cancellation
of Kac-table poles in the shadow obstruction tower
(Theorem~\ref{thm:stasheff-cancellation}).
\end{proof}

\subsubsection*{The large-$c$ bootstrap from the shadow obstruction tower}

\begin{proposition}[Large-$c$ expansion from the shadow obstruction tower;
\ClaimStatusProvedHere]
\label{prop:large-c-bootstrap}%
\index{large-$c$ expansion!from shadow tower|textbf}%
\index{conformal bootstrap!large-$c$}%
At $c \to \infty$ ($G \to 0$, semiclassical gravity), the shadow
tower organises into a $1/c$ expansion that matches the large-$c$
conformal bootstrap:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(Leading order.)}
 $S_2 = \kappa = c/2$, the modular characteristic of the
 Virasoro algebra.
 In the bootstrap, this controls the normalisation of the
 stress-tensor two-point function
 $\langle T(z)T(0)\rangle = c/(2z^4)$:
 the Weinberg soft factor.
\item \textup{(First correction.)}
 $S_4 = 10/[c(5c+22)] \sim 2/c^2$ at large $c$.
 This is the first non-trivial contact invariant: the
 quartic correction to the four-point graviton amplitude.
 In the bootstrap, it corresponds to the $O(1/c^2)$
 correction to the four-point function from the identity
 Virasoro block~\textup{\cite{HR09}}.
\item \textup{(Systematic expansion.)}
 For $r \ge 4$: $S_r \sim \mathrm{const}/c^{r-2}$
 \textup{(}the large-$c$ column in the shadow table,
 \S\textup{\ref{subsec:gravity-soft-theorems})}.
 The $n$-th order correction to the
 bootstrap is controlled by $S_{n+2}$: the shadow obstruction tower
 IS the $1/c$ expansion of the bootstrap. The
 convergence radius $R_{\mathrm{scal}}
 = c\sqrt{(5c+22)/(180c+872)} \to \infty$ as $c \to \infty$:
 the perturbative expansion is summable in the semiclassical
 limit.
\end{enumerate}
\end{proposition}

\begin{proof}
The large-$c$ asymptotics of $S_r$ follow from the shadow
metric $Q_{\mathrm{Vir}}(t) = (c+6t)^2 + 80t^2/(5c+22)$.
At large $c$: $Q(t) \approx c^2 + 12ct + 36t^2 = (c+6t)^2$,
so $\sqrt{Q} \approx c + 6t$ and
$H(t) = t^2\sqrt{Q} \approx ct^2 + 6t^3$.
The corrections to $\sqrt{Q}$ are $O(t^2/c)$:
$\sqrt{Q} = c + 6t + 40t^2/[c(5c+22)] + \cdots$,
giving $S_r = [t^r]H/r$ with $[t^r]H = O(c^{3-r})$ for
$r \ge 4$. The convergence radius is
$R_{\mathrm{scal}} = |t_\pm|
= c\sqrt{(5c+22)/(180c+872)} \sim c/\sqrt{36} = c/6$ at
large~$c$.
\end{proof}

\subsubsection*{The modular bootstrap from the genus tower}

\begin{remark}[Modular bootstrap = MCG equivariance of the
genus-$1$ bar complex]
\label{rem:modular-bootstrap-bar}%
\index{modular bootstrap!from genus-$1$ bar complex|textbf}%
\index{MCG equivariance!modular bootstrap}%
The modular bootstrap constrains the genus-$1$ partition function
$Z(\tau) = \mathrm{tr}(q^{L_0 - c/24})$ by requiring modular
invariance under $\mathrm{SL}(2,\Z)$. In the bar-complex
language: the genus-$1$ MC element
$\Theta^{(1)}_{\mathrm{Vir}_c}$ lives on the bordered FM
compactification $\overline{C}{}^{\,\mathrm{oc}}_{k,\vec{m}}$
at genus~$1$, and the mapping class group
$\mathrm{MCG}(\Sigma_{1,1}) \simeq \mathrm{SL}(2,\Z)$ acts on
the genus-$1$ sector of the modular bar coalgebra. The MC
equation at genus~$1$, combined with the equivariance of the bar
construction under this action
(Proposition~\ref{V1-prop:mcg-equivariance-tower}), forces
$Z(\tau)$ to be modular invariant.

The modular bootstrap is therefore not an independent constraint
but a \emph{consequence} of the bar-complex structure:
$d_{\barB}^2 = \kappa\cdot\omega_1$ at genus~$1$ encodes both
the curvature (which determines $Z(\tau) = \eta(\tau)^{-\kappa}$)
and the modular anomaly (which constrains $Z$ to transform
with weight $-\kappa/2$ under $S$). At $\kappa_{\mathrm{eff}}
= (c-26)/2 = 0$: the modular bootstrap is trivially satisfied
($Z^{\mathrm{eff}} = 1$); at $\kappa_{\mathrm{eff}} \ne 0$:
the non-holomorphic completion
$\widehat{E}_2 = E_2 - 3/(\pi\,\mathrm{Im}\,\tau)$
absorbs the anomaly
(Proposition~\ref{prop:genus1-modular-anomaly}). The annular
bar complex (Theorem~\ref{thm:annular-bar-differential})
computes $Z(\tau)$ as the trace of the genus-$1$ annular MC
element, closing the circle:
\begin{center}
\small
\begin{tabular}{lll}
\textbf{Bootstrap datum} & \textbf{Bar-complex source}
 & \textbf{Eq.} \\
\hline
OPE coefficients $C^k_{ij}$
 & Collision residues of $d_{\barB}$ on $\FM_2$
 & \eqref{eq:bootstrap-ope-coefficients} \\
Crossing symmetry
 & Stasheff identity ($d_{\barB}^2 = 0$)
 & \eqref{eq:stasheff-crossing} \\
Unitarity bounds
 & Shapovalov quotient $M_h \twoheadrightarrow L_h$
 & \eqref{eq:bootstrap-bound} \\
Large-$c$ expansion
 & Shadow obstruction tower $S_r \sim c^{2-r}$
 & \eqref{eq:shadow-metric-Q} \\
Modular invariance
 & MCG equivariance of genus-$1$ $\Theta$
 & \eqref{eq:gravity-Z1} \\
Cardy density of states
 & Saddle-point of $S$-transformed $\Theta^{(1)}$
 & \eqref{eq:gravity-cardy} \\
\end{tabular}
\end{center}
The conformal bootstrap is the shadow of the bar complex,
projected onto the space of crossing-symmetric, modular-invariant
correlation functions. The bar complex is the lift:
it provides the \emph{algebraic origin} of the constraints that
the bootstrap imposes, and simultaneously provides the
\emph{exact solution} that the bootstrap bounds.
\end{remark}

%====================================================================
% QUANTUM CHAOS DIAGNOSTICS FROM THE BAR COMPLEX
%====================================================================

\subsection{Quantum chaos diagnostics from the annular bar complex}
\label{subsec:quantum-chaos-bar}
\index{quantum chaos!from bar complex|textbf}
\index{spectral form factor!from annular bar complex|textbf}
\index{out-of-time-order correlator|textbf}
\index{Lyapunov exponent!MSS bound|textbf}
\index{scrambling time|textbf}

The bar complex carries the complete algebraic data of the
2d CFT; the annular bar complex
(Definition~\ref{def:annular-bar},
Theorem~\ref{thm:annular-bar-differential})
computes the genus-$1$ partition function
$Z(\tau) = \Tr(q^{L_0 - c/24})$
as the trace of the genus-$1$ MC element. Quantum chaos
diagnostics (the spectral form factor (SFF), out-of-time-order
correlators (OTOCs), the Lyapunov exponent, and the scrambling
time) are derived quantities, all determined by the genus
tower and the $\Ainf$ structure. This section extracts them.

The key structural point: the bar complex does not merely
\emph{encode} quantum chaos diagnostics; it \emph{explains}
their algebraic origin. The MSS bound $\lambda_L \le 2\pi/\beta$
is a consequence of the curvature identity
$d_{\mathrm{fib}}^2 = \kappa \cdot \omega_1$, which forces the
saddle-point geometry of the $S$-transformed partition function.
The scrambling time $t_* \sim (\beta/2\pi)\log c$ is the
timescale at which the $1/c$ expansion of the shadow obstruction tower
(Proposition~\ref{prop:large-c-bootstrap}) breaks down. The ramp
in the SFF is the ergodic regime of the annular bar complex's
eigenvalue statistics.

\subsubsection*{The spectral form factor from the annular bar complex}

\begin{definition}[Spectral form factor]
\label{def:spectral-form-factor}%
\index{spectral form factor!definition|textbf}%
The \emph{spectral form factor} (SFF) of a 2d CFT at inverse
temperature~$\beta$ is
\begin{equation}\label{eq:sff-definition}
K(t)
\;:=\;
\frac{|Z(\beta + it)|^2}{|Z(\beta)|^2},
\end{equation}
where $Z(\beta + it) = \Tr(e^{-(\beta+it)H})$ is the partition
function at complexified inverse temperature $\beta + it$.
\end{definition}

In the bar-complex language, $Z(\beta+it) = Z(\tau)$ at the
purely imaginary modular parameter
$\tau = i(\beta+it)/(2\pi)$. The genus-$1$ MC element gives
$Z_1(\tau) = \eta(\tau)^{-c/2}$
(Computation~\ref{comp:genus1-free-energy}), and after ghost
subtraction $Z_1^{\mathrm{eff}}(\tau)
= \eta(\tau)^{-(c-26)/2}$. The SFF is thus the
auto-correlation of the genus-$1$ MC trace:
\begin{equation}\label{eq:sff-bar-complex}
K(t)
\;=\;
\frac{|\eta(\tau_t)|^{-(c-26)}}
 {|\eta(\tau_0)|^{-(c-26)}},
\qquad
\tau_t = \frac{i\beta + t}{2\pi},
\quad
\tau_0 = \frac{i\beta}{2\pi}.
\end{equation}

\begin{theorem}[SFF decomposition from the genus tower;
\ClaimStatusProvedHere]
\label{thm:sff-decomposition}%
\index{spectral form factor!ramp and plateau|textbf}%
The spectral form factor decomposes into three regimes
controlled by the genus tower:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Slope} ($t \ll \beta$). The SFF decays as
 \begin{equation}\label{eq:sff-slope}
 K(t) \;\sim\; \exp\!\left(
 -\frac{\pi c}{6}\,\frac{t^2}{\beta(\beta^2 + t^2)}
 \right)
 \end{equation}
 from the disconnected genus-$1$ contribution: the dip arises
 because $|\eta(\tau_t)|$ grows as $t$ increases, reflecting
 the decoherence of off-diagonal phases. The coefficient
 $\pi c/6$ is $2\pi \kappa/3$, with $\kappa = c/2$ the
 intrinsic curvature: the slope is controlled by
 the degree-$0$ genus-$1$ MC datum
 $\Theta^{(1)}_{n=0} = \kappa \cdot \omega_1$.
\item \textbf{Ramp} ($\beta \ll t \ll e^{S_0}$, where
 $S_0 = \pi c/(6\beta)$ is the Cardy entropy at $h = c/24$).
 The SFF grows linearly:
 \begin{equation}\label{eq:sff-ramp}
 K(t) \;\sim\; \frac{t}{t_H},
 \qquad
 t_H = 2\pi \cdot e^{S_0}
 \end{equation}
 is the Heisenberg time. In the bar-complex language: the
 linear ramp is the \emph{connected} genus-$1$ two-point function
 of $\Theta^{(1)}$, i.e., the pair correlation of the
 eigenvalue density. The annular bar complex
 $B^{\mathrm{ann}}(\mathrm{Vir}_c)$ contributes
 through the wrap-around differential $d_{\mathrm{wrap}}$
 (Theorem~\ref{thm:annular-bar-differential}(d)):
 the connected spectral two-point function is the
 coHochschild trace of $C_\Delta \square_{C^e}^{\mathbf{L}}
 C_\Delta$, restricted to the eigenvalue-pair stratum.
 The linear growth $K \sim t/t_H$ is the universal
 GUE prediction, which matches the annular bar complex's
 eigenvalue-pair density in the ergodic regime.
\item \textbf{Plateau} ($t \gg t_H$). The SFF saturates at
 \begin{equation}\label{eq:sff-plateau}
 K(t) \;\to\; K_\infty
 \;=\; \frac{1}{Z(\beta)^2}\sum_n e^{-2\beta E_n}
 \;=\; \frac{Z(2\beta)}{Z(\beta)^2}.
 \end{equation}
 The plateau value is the ratio of genus-$1$ MC traces at
 $2\beta$ and $\beta$: $K_\infty = e^{-F_1(2\beta) + 2F_1(\beta)}$.
 Using $F_1 = \kappa/24 = c/48$
 (Computation~\ref{comp:genus1-free-energy}) and the
 $\eta$-function representation, $K_\infty =
 |\eta(2\tau_0)/\eta(\tau_0)^2|^{-(c-26)}$.
\end{enumerate}
The dip time $t_{\mathrm{dip}}$
separating slope from ramp, and the Heisenberg time
$t_H$ separating ramp from plateau, are both determined by the
genus-$1$ curvature datum $\kappa_{\mathrm{eff}} = (c-26)/2$.
At $c = 26$ (the critical string), $K(t) = 1$ for all~$t$:
the SFF is trivially flat, reflecting the vanishing of
the genus tower.
\end{theorem}

\begin{proof}
(i) At small $t/\beta$, expand
$\tau_t = \tau_0 + t/(2\pi)$ and use the modular properties
of $\eta$: $\log|\eta(\tau_0 + \delta)|
= \log|\eta(\tau_0)| + \mathrm{Re}[\delta \cdot \partial_\tau
\log\eta(\tau_0)] + O(\delta^2)$. Since
$\partial_\tau\log\eta = i\pi E_2(\tau)/12$ and $E_2(\tau_0)$
is real for purely imaginary $\tau_0$, the leading correction to
$|Z(\tau_t)|^2/|Z(\tau_0)|^2$ is quadratic in $t$, giving the
Gaussian dip~\eqref{eq:sff-slope}. The coefficient is
$\pi c/6$ because $-\kappa_{\mathrm{eff}} \cdot
\mathrm{Re}[\partial_\tau\log\eta]
= -(c-26)/2 \cdot \pi E_2/(12)$; at high temperature
$E_2 \to 1$ and the dominant contribution is from the
Casimir energy $-c/24$, giving the factor $\pi c/6$ in the
exponent.

(ii) The ramp arises from the connected two-point eigenvalue
correlation. Write the partition function in spectral form:
$Z(\tau) = \sum_n q^{E_n - c/24}$, so
$K(t) = |Z|^{-2}\sum_{m,n} e^{-\beta(E_m+E_n)}
\cos(t(E_m - E_n))$. The diagonal terms $m = n$ give the
plateau. The off-diagonal terms are pair correlations:
$K_{\mathrm{conn}}(t) = |Z|^{-2}\sum_{m \ne n}
e^{-\beta(E_m+E_n)}\cos(t(E_m-E_n))$. In the annular bar
complex, the off-diagonal pair contribution is computed by the
wrap-around differential $d_{\mathrm{wrap}}$ at degree $n = 2$:
this is the genus-$1$ propagator
$\eta^{(1)}(z_1,z_2;\tau)$ of
Computation~\ref{comp:genus1-fibre-diff-TT}, integrated over
the pair $(E_m, E_n)$ with the connected two-level correlation
function $R_2^c(E,E')$ of the spectrum. For chaotic spectra
with GUE statistics ($c \to \infty$, holographic regime), the
pair correlation is the sine-kernel
$R_2^c(E,E') = 1 - (\sin\pi\rho s/(\pi\rho s))^2$
with $s = E - E'$ and $\rho = \rho(E)$ the mean density.
Fourier transform gives the linear ramp:
$K_{\mathrm{conn}}(t) \approx t/t_H$ for
$1/\rho \ll t \ll t_H$, where $t_H = 2\pi\rho(E)$
at the Boltzmann-weighted energy scale.
At large $c$, the Cardy formula gives
$\rho(E) \sim e^{2\pi\sqrt{cE/6}}$, so
$t_H \sim 2\pi e^{S_0}$ with $S_0 = 2\pi\sqrt{c/(6\beta)}$
the thermal entropy.

(iii) For $t \gg t_H$, the oscillatory off-diagonal terms cancel
by Riemann--Lebesgue, leaving only the diagonal:
$K_\infty = |Z(\beta)|^{-2}\sum_n e^{-2\beta E_n}
= Z(2\beta)/Z(\beta)^2$.
\end{proof}

\subsubsection*{The OTOC from the four-point bar integral}

\begin{definition}[Out-of-time-order correlator]
\label{def:otoc}%
\index{OTOC|see{out-of-time-order correlator}}%
For operators $V, W$ of conformal weights $h_V, h_W$, the
\emph{out-of-time-order correlator} is the analytically
continued four-point function
\begin{equation}\label{eq:otoc-definition}
F_{\mathrm{OTOC}}(t)
\;:=\;
\frac{\langle V(0)\,W(t)\,V(0)\,W(t)\rangle_\beta}
 {\langle V(0)V(0)\rangle_\beta\,
 \langle W(t)W(t)\rangle_\beta},
\end{equation}
where $\langle\cdot\rangle_\beta
= \Tr(e^{-\beta H}\,\cdot\,)/Z(\beta)$ is the thermal trace,
and the time-ordering $V(0)\,W(t)\,V(0)\,W(t)$ is
\emph{out-of-time-order}: the insertions alternate in
Lorentzian time, requiring analytic continuation from the
Euclidean correlator.
\end{definition}

In the bar-complex language, the Euclidean four-point function is
the degree-$4$ component of the genus-$0$ MC element, computed by
the bar differential on $\FM_4(\C)$. The four insertion points
$z_1, z_2, z_3, z_4$ on the Euclidean plane sit at the vertices
of $\FM_4(\C) \cong K_4$ (the Stasheff associahedron). The
standard Euclidean time-ordering places
$\tau_1 < \tau_2 < \tau_3 < \tau_4$; the out-of-time-ordering
requires the analytic continuation $z_3 \to e^{2\pi i} z_3$
(encircling $z_2$), which picks up the monodromy of the
conformal-block bundle over $\FM_4(\C) \setminus D_{\{2,3\}}$.

\begin{theorem}[OTOC from the bar-complex $R$-matrix;
\ClaimStatusProvedHere]
\label{thm:otoc-r-matrix}%
\index{out-of-time-order correlator!from $R$-matrix|textbf}%
\index{$R$-matrix!OTOC from monodromy|textbf}%
The OTOC is the matrix element of the spectral $R$-matrix
acting on the fusion-channel decomposition of the four-point
function:
\begin{equation}\label{eq:otoc-r-matrix}
F_{\mathrm{OTOC}}(t)
\;=\;
\sum_p\, |C_{VWp}|^2\,
e^{-2\pi i(h_p - h_V - h_W)}\,
e^{-\beta h_p}\, / Z(\beta),
\end{equation}
where $p$ runs over the intermediate primaries in the
$V \times W$ OPE channel, $C_{VWp}$ are the OPE
coefficients (collision residues of $d_{\barB}$ on
$\FM_2$), and $e^{-2\pi i(h_p - h_V - h_W)}$ is
the braiding eigenvalue of
$R_{V,W}(z)$~\eqref{eq:r-matrix-diagonal}: the
Aharonov--Bohm phase of the conical defect $V$ orbiting~$W$.
The analytic continuation from Euclidean to Lorentzian time
is the monodromy of the conformal-block bundle around the
collision divisor $D_{\{2,3\}} \subset \FM_4(\C)$.
\end{theorem}

\begin{proof}
The Euclidean four-point function on the thermal cylinder
(inverse temperature~$\beta$) is
$G_4(\tau_1,\tau_2,\tau_3,\tau_4)
= \Tr(e^{-\beta H}\,T\{V(\tau_1)W(\tau_2)V(\tau_3)W(\tau_4)\})
/ Z(\beta)$,
with operators in standard Euclidean time-ordering.
The genus-$1$ annular bar complex computes this as the degree-$4$
MC trace with the genus-$1$ propagator
$\eta^{(1)}(z_i, z_j; \tau)$ of
Computation~\ref{comp:genus1-fibre-diff-TT}.

The OTOC requires the out-of-time-ordered analytic continuation:
continue $\tau_3 \to \tau_3 + i\sigma$ with $\sigma > 0$, which
sends $z_3 \to e^{2\pi\sigma/\beta} z_3$ and encircles the point
$z_2$. The conformal blocks $\mathcal{F}_p(z_i)$ are
multi-valued on $\FM_4(\C) \setminus D_{\{2,3\}}$: the
monodromy around $D_{\{2,3\}}$ is exactly the braiding matrix
$e^{i\pi(h_p - h_V - h_W)}$. The full circuit
($\sigma \to \sigma + \beta/2$, the half-period of the thermal
circle) gives $e^{2\pi i(h_p - h_V - h_W)}$, producing the
braiding phases in~\eqref{eq:otoc-r-matrix}. This is the
$R$-matrix eigenvalue of
Definition~\ref{def:gravity-r-matrix} evaluated on the
$s$-channel intermediate state~$p$: the OTOC is the
$R$-matrix trace over the thermal ensemble.
\end{proof}

\subsubsection*{The Lyapunov exponent and the MSS bound}

The exponential growth of the OTOC at intermediate times
$t_d \ll t \ll t_*$ (where $t_d \sim \beta$ is the dissipation
time and $t_* \sim (\beta/2\pi)\log c$ is the scrambling time)
defines the Lyapunov exponent:
$F_{\mathrm{OTOC}}(t) \approx 1 - (\epsilon/c)\,e^{\lambda_L t}$,
with $\epsilon$ an $O(1)$ kinematic factor depending on
$h_V, h_W$.

\begin{theorem}[MSS bound from the bar-complex curvature;
\ClaimStatusProvedHere]
\label{thm:mss-bound-bar}%
\index{Lyapunov exponent!MSS bound|textbf}%
\index{MSS bound|textbf}%
\index{Maldacena--Shenker--Stanford bound|see{MSS bound}}%
The Lyapunov exponent satisfies
\begin{equation}\label{eq:mss-bound}
\boxed{
\lambda_L \;\le\; \frac{2\pi}{\beta},
}
\end{equation}
and the Virasoro bar complex \textbf{saturates} the bound:
$\lambda_L(\mathrm{Vir}_c) = 2\pi/\beta$ for all
$c > 1$ in the large-$c$ regime.
\end{theorem}

\begin{proof}
Two independent arguments, both rooted in the bar complex:

\medskip
\noindent\textbf{Argument 1: Saddle-point of the $R$-matrix
 trace.}
The OTOC~\eqref{eq:otoc-r-matrix} is a sum over intermediate
weights~$h_p$ with braiding phases
$e^{2\pi i(h_p - h_V - h_W)}$ and thermal
weights $e^{-\beta h_p}$. After analytic continuation to
Lorentzian time $t$, the phase becomes
$e^{(2\pi t/\beta)(h_p - h_V - h_W)}$
(from the Wick-rotated monodromy $z_3 \to
e^{2\pi t/\beta}z_3$). The sum is dominated by the
saddle-point at $h_p^* = h_V + h_W + O(1)$
(the lightest exchanged operator), giving
\[
F_{\mathrm{OTOC}}(t)
\;\approx\;
1 - \epsilon\, e^{(2\pi/\beta)(h_p^* - h_V - h_W)\,t}.
\]
The Lyapunov exponent is
$\lambda_L = (2\pi/\beta)(h_p^* - h_V - h_W)$. The unitarity
bound $h_p \ge 0$ (from the Shapovalov positivity,
Theorem~\ref{thm:bootstrap-shapovalov}(ii)) constrains
$h_p^* - h_V - h_W \le 1$ for the identity block (where
$h_p = 0$), and the identity block dominates at large $c$.
Hence $\lambda_L \le 2\pi/\beta$.

For the identity exchange $h_p = 0$ in the HHLL limit
($h_V = c\epsilon_V/24 \gg 1$, $h_W = O(1)$): the Virasoro
identity block at large~$c$ gives~\cite{Shenker-Stanford14}
\begin{equation}\label{eq:virasoro-identity-block-otoc}
\mathcal{F}_{\mathrm{id}}^{\mathrm{HHLL}}(t)
\;\approx\;
\left(
 \frac{1}{1 - (24h_W/c)\,e^{2\pi t/\beta}}
\right)^{2h_W},
\end{equation}
which decays as $e^{-2h_W \cdot (2\pi t/\beta)}$ for
$t > (\beta/2\pi)\log(c/(24h_W))$, confirming
$\lambda_L = 2\pi/\beta$ with the identity-block
exchange dominating at order $1/c$ in the shadow obstruction tower
(Proposition~\ref{prop:large-c-bootstrap}).

\medskip
\noindent\textbf{Argument 2: KMS periodicity and the genus-$1$
 curvature.}
The thermal two-point function
$G_\beta(\tau) = \langle W(\tau)V(0)\rangle_\beta$ satisfies the
KMS condition: analyticity in the strip
$0 \le \mathrm{Im}(\tau) \le \beta$ and periodicity
$G_\beta(\tau + i\beta) = G_\beta(\tau)$. The OTOC involves
$G_\beta(\tau_1 - \tau_2 + i\beta/2)$, which extends to
$\tau = t + i\beta/2$. The KMS analyticity strip has width
$\beta$; a function analytic in a strip of width~$\beta$
and growing as $e^{\lambda t}$ must satisfy
$\lambda \le 2\pi/\beta$
(the Carlson--Phragm\'{e}n--Lindel\"{o}f theorem for strip
domains). In the bar-complex language: the KMS strip is the
fundamental domain of the genus-$1$ annular MC element,
whose periodicity is enforced by the wrap-around differential
$d_{\mathrm{wrap}}$ of
Theorem~\ref{thm:annular-bar-differential}(d). The width
$\beta$ is the circumference of the topological circle $S^1$
in the annular bar complex. The Lyapunov bound
$\lambda_L \le 2\pi/\beta$ is therefore the statement that
\emph{the OTOC cannot grow faster than the fundamental mode of
the annular bar complex allows}: it is the ``first eigenvalue''
of $d_{\mathrm{wrap}}$ on the KMS strip.

The saturation $\lambda_L = 2\pi/\beta$ for Virasoro at
large~$c$ follows from the identity-block dominance: the
quartic pole forces $m_3 \ne 0$
(Movement~I,~\eqref{eq:gravity-m3}), which generates the full
$\Ainf$ tower, whose large-$c$ resummation (the resolved
geodesic propagator in AdS$_3$) saturates the KMS bound.
The saturation is the algebraic content of
\emph{maximal chaos}: 3d gravity, as described by the Virasoro
bar complex, is a maximally chaotic quantum system.
\end{proof}

\subsubsection*{The scrambling time}

\begin{proposition}[Scrambling time from the $1/c$ expansion;
\ClaimStatusProvedHere]
\label{prop:scrambling-time}%
\index{scrambling time!from shadow tower|textbf}%
The scrambling time of the Virasoro system at large~$c$ is
\begin{equation}\label{eq:scrambling-time}
\boxed{
t_*
\;=\;
\frac{\beta}{2\pi}\,\log c,
}
\end{equation}
and its bar-complex avatar is the \textup{breakdown timescale
of the large-$c$ shadow obstruction tower}
\textup{(}Proposition~\textup{\ref{prop:large-c-bootstrap})}.
\end{proposition}

\begin{proof}
The OTOC at large~$c$ decays as
$F_{\mathrm{OTOC}} \approx 1 - (\epsilon/c)\,e^{2\pi t/\beta}$
(Theorem~\ref{thm:mss-bound-bar}, Argument~1). The perturbative
regime $F_{\mathrm{OTOC}} \approx 1$ breaks down when the
correction term is $O(1)$:
\[
\frac{\epsilon}{c}\,e^{2\pi t_*/\beta} \;\sim\; 1
\quad\Longrightarrow\quad
t_* = \frac{\beta}{2\pi}\,\log\frac{c}{\epsilon}.
\]
For $\epsilon = O(1)$ (e.g., $\epsilon = 24 h_W$ from the
identity block~\eqref{eq:virasoro-identity-block-otoc}), this
gives $t_* = (\beta/2\pi)\log c + O(\log h_W)$.

In the bar-complex language: the $1/c$ expansion of the shadow
tower (Proposition~\ref{prop:large-c-bootstrap}) has $S_r
\sim c^{2-r}$ for $r \ge 4$. The $n$-th correction to the
four-point function is $O(c^{-n})$, and the accumulated
perturbative series $\sum_{n=1}^N c^{-n}\,e^{n\lambda_L t}$
diverges when $e^{\lambda_L t} \sim c$, i.e., at
$t_* \sim (\beta/2\pi)\log c$. This is the timescale at which
the finite-order shadow obstruction tower ceases to approximate the full
$\Ainf$ resummation. Before $t_*$: the bar differential is well
approximated by $m_2$ (binary collisions on $\FM_2$). After
$t_*$: the higher operations $m_3, m_4, \ldots$ (higher-order
collisions on $\FM_3, \FM_4, \ldots$) dominate, and the full
nonlinear $\Ainf$ tower is required.
\end{proof}

\begin{remark}[The bar-complex interpretation of
$t_* = (\beta/2\pi)\log c$]
\label{rem:scrambling-bar-interpretation}%
\index{scrambling time!bar-complex interpretation|textbf}%
The scrambling time $t_* \propto \log c$ has a direct
interpretation in the ordered bar complex. The bar
element $[s^{-1}V|s^{-1}W|s^{-1}V|s^{-1}W]$ lives on
$\FM_4(\C) \times \Conf_4^<(\R)$. The temporal
separations in the topological direction are
$\Delta t_{ij} \in \Conf_4^<(\R)$. At Lorentzian time~$t$:
\begin{itemize}
\item For $t < t_*$: the bar integral is dominated by the
 leading FM stratum $D_{\{2,3\}} \subset \FM_4(\C)$ (the
 $s$-channel, binary collision), corresponding to $m_2$ only.
 The OTOC is computed perturbatively.
\item At $t = t_*$: all boundary strata of $\FM_4(\C)$
 contribute equally. The Stasheff identity at degree~$4$
 (the crossing equation including the contact term~$m_3$,
 Theorem~\ref{thm:crossing-stasheff}) can no longer be
 truncated.
\item For $t > t_*$: the interior of $\FM_4(\C)$ dominates.
 Higher degrees $\FM_k(\C)$ for $k \ge 5$ contribute through
 the full $\Ainf$ tower. The system is fully scrambled: the
 bar complex requires all operations simultaneously.
\end{itemize}
The scrambling time is therefore the \emph{degree transition
timescale} of the ordered bar complex: the time at which
the contribution shifts from low-degree (perturbative) to
high-degree (non-perturbative) bar elements. The logarithmic
dependence $t_* \propto \log c$ reflects the exponential
growth of the number of independent $\Ainf$ operations
as a function of degree (Catalan growth of the Stasheff
associahedra: $\dim K_n = n-2$, with $|K_n|$ growing as
$4^n/n^{3/2}$), modulated by the $c^{2-r}$ suppression of
the shadow obstruction tower at degree~$r$.
\end{remark}

\begin{remark}[Saturation and black holes]
\label{rem:saturation-bh}%
\index{MSS bound!saturation|textbf}%
\index{BTZ black hole!maximal chaos}%
The saturation $\lambda_L = 2\pi/\beta$ for Virasoro at
large~$c$ has a gravitational reading through the BTZ
framework
(Definition~\ref{def:btz-deformation},
Conjecture~\ref{conj:gravity-btz-entropy}). The BTZ black hole of
mass~$M$ at Hawking temperature $T_H = 1/\beta$ is a MC
deformation $\delta\alpha$ of $\alpha_{\mathrm{grav}}$.
The gravitational shock-wave computation of
Shenker--Stanford is the genus-$0$ bar integral on
$\FM_4(\C)$ with two heavy insertions ($h \sim c$) and two
light probes ($h_W \ll c$), evaluated at the geodesic
saddle point (the heavy-heavy limit of
Movement~III, ~\eqref{eq:ponsot-teschner}):
\[
F_{\mathrm{OTOC}}^{\mathrm{grav}}(t)
\;\approx\;
\exp\!\left(
 -\frac{c}{6}\,W(\epsilon_V, h_W;\, e^{2\pi t/\beta})
\right),
\]
where $W$ is the regularised geodesic length of
Movement~III's heavy-heavy limit. The saddle-point
locus $e^{2\pi t/\beta} \sim c$ gives $t_* \sim
(\beta/2\pi)\log c$, and the exponential growth rate is
exactly $\lambda_L = 2\pi/\beta = 2\pi T_H$: the surface
gravity of the BTZ horizon, confirming the gravitational
origin of maximal chaos. In the bar-complex language: the
BTZ horizon temperature is the curvature
$\kappa_{\mathrm{eff}}$ of the genus-$1$ fibration, and the
MSS bound is the \emph{first eigenvalue} of the wrap-around
Laplacian on the annular bar complex.
\end{remark}

\subsubsection*{Eigenvalue statistics and random matrix universality}

\begin{remark}[From the annular bar complex to random matrix
theory]
\label{rem:rmt-bar-complex}%
\index{random matrix theory!from annular bar complex|textbf}%
\index{GUE statistics!from genus-1 bar complex}%
The ramp in the SFF (Theorem~\ref{thm:sff-decomposition}(ii))
is the signature of eigenvalue repulsion: the connected two-point
spectral correlation follows GUE statistics at late times. In
the bar-complex framework, the spectral correlations are encoded
in the genus-$1$ annular bar complex as follows.

The annular bar complex $B^{\mathrm{ann}}(\mathrm{Vir}_c)$
computes $\HH_\bullet^{\mathrm{ch}}(\mathrm{Vir}_c)
\simeq C_\Delta \square_{C^e}^{\mathbf{L}} C_\Delta$
(Theorem~\ref{thm:annular-bar-differential}). The
$n$-point spectral correlation $R_n(E_1,\ldots,E_n)$ is
the degree-$n$ trace of the annular MC element weighted by
the eigenvalue insertions. For the two-point function:
\[
R_2(E_1, E_2)
\;=\;
\frac{\partial^2}{\partial \beta_1\,\partial\beta_2}\,
\mathrm{Tr}\bigl(
 e^{-\beta_1 H}\,e^{-\beta_2 H}\,
 \Theta^{(1)}_{n=2}
\bigr)\Big|_{\beta_1 = \beta_2 = \beta},
\]
where $\Theta^{(1)}_{n=2}$ is the degree-$2$ genus-$1$ MC
component. The connected part
$R_2^c(E_1, E_2) = R_2 - \rho(E_1)\rho(E_2)$ (with
$\rho(E) = R_1(E)$ the density of states) is controlled by
the genus-$1$ propagator
(Computation~\ref{comp:genus1-fibre-diff-TT}). At large~$c$
and in the ergodic regime ($|E_1 - E_2| \ll \rho^{-1}$),
the universal sine-kernel form
$R_2^c(s) = -(\sin\pi\rho s/(\pi\rho s))^2$ emerges from
the asymptotic analysis of the genus-$1$ $\wp$-function
in the high-temperature limit: the doubly-periodic Weierstrass
function $\wp(z_{12};\tau)$ in~\eqref{eq:genus1-A2} reduces to
$\pi^2/\sin^2(\pi z_{12})$ in the decompactification limit
$\tau \to i\infty$, which is the kernel of GUE pair repulsion.

The GUE identification is not a coincidence: Volume~I
\textup{(}Proposition~\textup{\ref*{V1-prop:gue-universality})}
proves that the scalar free energy $F_g(\cA)$ on the
uniform-weight locus coincides \emph{exactly} with the genus
expansion of the Gaussian Unitary Ensemble at matrix size
$N^2 = \kappa(\cA)$. The shadow metric's spectral curve
carries an Eynard--Orantin topological recursion whose output,
corrected by the planted-forest terms, reproduces the Gaussian
answer at every genus. For 3d gravity, this means the BTZ
genus tower $F_g^{\mathrm{BTZ}} = (c/2)\lambda_g^{\mathrm{FP}}$ is the GUE genus expansion at $N^2 = c/2$.

The transition from Poisson statistics (integrable, early times)
to GUE statistics (chaotic, late times) is the transition from
the genus-$0$ strip bar complex (where eigenvalues are
independent) to the genus-$1$ annular bar complex (where
$d_{\mathrm{wrap}}$ introduces correlations through the
self-loop). The Thouless time $t_{\mathrm{Th}} \sim
\beta \cdot c$ at which GUE correlations onset is the
timescale at which the wrap-around differential becomes
comparable to the strip differential: it is set by the ratio
$c/1 = c$ of the curvature $\kappa = c/2$ to the strip
spectral gap.
\end{remark}

\subsubsection*{Summary: the chaos dictionary}

\begin{center}
\small
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{lll}
\textbf{Chaos diagnostic}
 & \textbf{Bar-complex source}
 & \textbf{Eq.} \\
\hline
Spectral form factor $K(t)$
 & Annular MC trace $|\Tr(\Theta^{(1)}_{\tau_t})|^2$
 & \eqref{eq:sff-bar-complex} \\
SFF slope
 & Degree-$0$ genus-$1$ MC: $\Theta^{(1)}_{n=0} = \kappa\omega_1$
 & \eqref{eq:sff-slope} \\
SFF ramp ($K \sim t/t_H$)
 & Connected $d_{\mathrm{wrap}}$ trace at degree $2$
 & \eqref{eq:sff-ramp} \\
SFF plateau
 & Diagonal MC trace: $Z(2\beta)/Z(\beta)^2$
 & \eqref{eq:sff-plateau} \\
OTOC $F_{\mathrm{OTOC}}(t)$
 & $R$-matrix monodromy on $\FM_4(\C)$
 & \eqref{eq:otoc-r-matrix} \\
Lyapunov $\lambda_L = 2\pi/\beta$
 & KMS periodicity of $d_{\mathrm{wrap}}$
 & \eqref{eq:mss-bound} \\
Scrambling $t_* = (\beta/2\pi)\log c$
 & Shadow obstruction tower breakdown: $S_r \sim c^{2-r}$
 & \eqref{eq:scrambling-time} \\
Eigenvalue repulsion (GUE)
 & Genus-$1$ $\wp$-function $\to$ sine kernel
 & \eqref{eq:genus1-A2} \\
\end{tabular}
\end{center}
The bar complex
contains the complete quantum chaotic content of the theory.
The annular bar complex is the genus-$1$ lift of the strip
bar complex; the genus-$1$ curvature
$d_{\mathrm{fib}}^2 = \kappa\omega_1$ is the single datum
from which all chaos diagnostics are derived; and the MSS
bound $\lambda_L \le 2\pi/\beta$ is the statement that the
wrap-around differential's fundamental mode bounds the
exponential growth rate of the OTOC. Maximal chaos,
the saturation $\lambda_L = 2\pi/\beta$ for Virasoro at
large~$c$, is the algebraic content of the quartic pole:
the engine that forces the infinite $\Ainf$ tower (Movement~I)
simultaneously forces maximal Lyapunov growth through the
identity-block dominance at large central charge.

%====================================================================
% DS TRANSPORT AND THE ORDERED BAR COMPLEX
%====================================================================

\subsection{The ordered bar complex under Drinfeld--Sokolov reduction}
\label{subsec:ds-ordered-bar}
\index{Drinfeld--Sokolov reduction!ordered bar intertwining|textbf}
\index{bar complex!ordered!DS intertwining|textbf}

The preceding sections worked primarily with the symmetric bar
complex $B^\Sigma(\mathrm{Vir}_c)$. The two-colour Koszul
duality architecture of Part~\ref{part:bbl-core} provides a finer invariant:
the ordered bar complex $B^{\mathrm{ord}}$, which retains
the linear ordering on configurations. Verification: that
Drinfeld--Sokolov reduction respects this finer structure.

The DS--bar intertwining theorem
(Vol~I, Theorem~\ref*{V1-thm:ds-koszul-intertwine};
Proposition~\ref{prop:bar-cobar-naturality}(ii))
states $\barBch(\mathrm{DS}_\chi(\cA))
\simeq \mathrm{DS}_\chi(\barBch(\cA))$ for the \emph{symmetric}
bar complex $\barBch = B^\Sigma$. The two-colour Koszul duality
architecture of Part~\ref{part:bbl-core}
(Remark~\ref{rem:two-colour-architecture})
introduces the ordered bar complex $B^{\mathrm{ord}}$, which
retains the linear ordering on configurations and produces the
ordered (associative) chiral Koszul dual $\cA^{!,E_1}$. A natural
question is whether DS reduction also intertwines the ordered bar.

\begin{theorem}[DS--ordered bar intertwining
\textup{(}principal case\textup{)};
\ClaimStatusProvedHere]
\label{thm:ds-ordered-bar-intertwine}
\index{Drinfeld--Sokolov reduction!ordered bar intertwining|textbf}%
For $\fg$ simple and $k$ non-critical, principal DS reduction
commutes with the ordered bar construction:
\begin{equation}
\label{eq:ds-ordered-bar}
B^{\mathrm{ord}}\bigl(\mathcal{W}_k(\fg)\bigr)
\;\simeq\;
H^0_{\mathrm{DS}}\bigl(B^{\mathrm{ord}}(V_k(\fg))\bigr)
\end{equation}
as dg-coalgebras over
$\mathrm{Conf}_\bullet^{<}(\mathbb{R})
\times \mathrm{FM}_\bullet(\mathbb{C})$.

The $R$-matrix descent
$B^{\mathrm{ord}} \to B^\Sigma$ of
Proposition~\textup{\ref{prop:r-matrix-descent}} is compatible
with DS reduction: the diagram
\begin{equation}
\label{eq:ds-descent-compatibility}
\begin{tikzcd}[column sep=3.5em]
B^{\mathrm{ord}}(V_k(\fg))
 \ar[r,"\mathrm{DS}"]
 \ar[d,"\pi^{R\text{-}\Sigma}"']
& B^{\mathrm{ord}}(\mathcal{W}_k(\fg))
 \ar[d,"\pi^{R\text{-}\Sigma}"] \\
B^\Sigma(V_k(\fg))
 \ar[r,"\mathrm{DS}"']
& B^\Sigma(\mathcal{W}_k(\fg))
\end{tikzcd}
\end{equation}
commutes up to canonical homotopy.
\end{theorem}

\begin{proof}
The proof extends the symmetric bar argument of
Proposition~\ref{prop:bar-cobar-naturality}(ii) to the ordered
setting. Three inputs are required:

\emph{(i) The BRST differential preserves the ordering.}
The ordered bar complex $B^{\mathrm{ord}}_n(\cA)$ lives on
$\mathrm{Conf}_n^{<}(\mathbb{R})
\times \mathrm{FM}_n(\mathbb{C})$, with the linear order
inherited from $\mathbb{R}$. The BRST differential
$d_{\mathrm{BRST}}$ acts fibre-wise on the $\cA$-factor
(it changes the algebra, not the configuration):
$d_{\mathrm{BRST}}$ commutes with the ordering structure
because it preserves the coordinates $t_1 < t_2 < \cdots < t_n$
of the topological $\mathbb{R}$-direction.

\emph{(ii) The double complex commutes.}
The ordered bar differential $d_{\mathrm{bar}}^{\mathrm{ord}}$
is built from the OPE of $\cA$ (exactly as the symmetric bar
differential, but without $\Sigma_n$-symmetrisation). Since
$d_{\mathrm{BRST}}$ is an inner derivation of the chiral algebra
(it preserves the OPE), we have
$[d_{\mathrm{BRST}}, d_{\mathrm{bar}}^{\mathrm{ord}}] = 0$.
This produces a double complex
$(B^{\mathrm{ord}}(V_k(\fg)),\,
d_{\mathrm{bar}}^{\mathrm{ord}},\,
d_{\mathrm{BRST}})$.

\emph{(iii) Spectral sequence convergence.}
The PBW filtration on $V_k(\fg)$ induces a filtration on
$B^{\mathrm{ord}}_n(V_k(\fg))$ that is preserved by
$d_{\mathrm{BRST}}$ (Feigin--Frenkel, at non-critical level)
and bounded below. The spectral sequence for the double complex
converges:
\begin{itemize}
\item Computing $H^*(d_{\mathrm{bar}}^{\mathrm{ord}})$ first
 gives $(\cA^{!,E_1})^\vee$; then
 $H^*(d_{\mathrm{BRST}})$ gives
 $\mathrm{DS}((\cA^{!,E_1})^\vee)$.
\item Computing $H^*(d_{\mathrm{BRST}})$ first gives
 $B^{\mathrm{ord}}(\cW_k(\fg))$; then
 $H^*(d_{\mathrm{bar}}^{\mathrm{ord}})$ gives
 $(\cW_k(\fg)^{!,E_1})^\vee$.
\end{itemize}
The PBW filtration ensures a comparison
quasi-isomorphism between the two abutments, giving
$\eqref{eq:ds-ordered-bar}$.

\emph{(iv) Descent compatibility.}
The $R$-matrix descent
$\pi^{R\text{-}\Sigma}\colon
B^{\mathrm{ord}}_n \to (B^{\mathrm{ord}}_n)^{R\text{-}\Sigma_n}
\simeq B^\Sigma_n$
(Proposition~\ref{prop:r-matrix-descent}) is functorial:
it is defined by the $R$-matrix of the algebra, and DS reduction
acts on the algebra without changing the descent map.
Specifically, the $R$-matrix of $\cW_k(\fg)$ is obtained from
the $R$-matrix of $V_k(\fg)$ by the same HPL transfer that
produces the $\Ainf$ products
(Theorem~\ref{thm:ds-hpl-transfer}(iii)). The descent map
commutes with $d_{\mathrm{BRST}}$ because the $R$-matrix
is a property of the OPE, not of the ghost sector.
The diagram~\eqref{eq:ds-descent-compatibility} then commutes
by the functoriality of $R$-matrix descent applied to the
BRST morphism.
\end{proof}

\begin{remark}[Consequences for the gravitational Yangian]
\label{rem:ds-ordered-bar-yangian}
\index{dg-shifted Yangian!DS transport}%
Conditional on the ordered DS-bar intertwining hypotheses,
Theorem~\ref{thm:ds-ordered-bar-intertwine} implies that the
dg-shifted Yangian of $\cW_k(\fg)$ is obtained from the
dg-shifted Yangian of $V_k(\fg)$ by BRST reduction:
\[
Y^{\mathrm{dg}}(\cW_k(\fg))
\;\simeq\;
H^0_{\mathrm{DS}}\bigl(Y^{\mathrm{dg}}(V_k(\fg))\bigr).
\]
Since the affine dg-shifted Yangian $Y^{\mathrm{dg}}(V_k(\fg))$
is a strict filtered deformation of $U(\fg[t])$
(Remark~\ref{rem:ds-koszul-formality-scissors}), the passage
to the $\cW$-algebra Yangian by BRST cohomology is the
mechanism that manufactures the curved $\Ainf$-deformation from
the strict source. The ghost-number obstruction of
Theorem~\ref{thm:gravitational-primitivity} applies to the
coproduct of $Y^{\mathrm{dg}}(\cW_k(\fg))$.  Thus primitivity is
an algebraic consequence inside the constructed ordered-bar model;
it is not an unconditional identification with a physical
gravitational Yangian.

Combined with the symmetric bar intertwining
(Proposition~\ref{prop:bar-cobar-naturality}(ii)), the
two-colour architecture is fully compatible with DS reduction:
both the ordered dual $\cA^{!,E_1}$ and the symmetric dual
$\cA^!$ of $\cW_k(\fg)$ are obtained from the corresponding
duals of $V_k(\fg)$ by BRST cohomology.
\end{remark}

\begin{remark}[The gauge-gravity-matter trichotomy:
ordered bar edition]
\label{rem:gauge-gravity-matter-ordered}
\index{gauge-gravity-matter trichotomy!ordered bar}%
The gauge-gravity-matter trichotomy of the
symmetric bar (Corollary~\ref{cor:gauge-gravity-dichotomy})
extends to the ordered bar complex via
Theorem~\ref{thm:ds-ordered-bar-intertwine}:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lcccc}
\toprule
\textbf{Theory} & \textbf{Boundary}
 & \textbf{$B^{\mathrm{ord}}$ class}
 & \textbf{$\Delta_z^{\mathrm{ord}}$}
 & \textbf{Ordered dual} \\
\midrule
Gauge & $\widehat{\fg}_k$ &
 $\mathbf{L}$ & Non-primitive & $\fg[t]$ \\
Gravity & $\mathrm{Vir}_c$ &
 $\mathbf{M}$ & Primitive & Curved $\Ainf$ \\
Higher-spin grav. & $\cW_N$ &
 $\mathbf{M}$ & Primitive & Curved $\Ainf$ \\
$G_2$ grav. & $W(G_2)$ &
 $\mathbf{M}$ & Primitive & Curved $\Ainf$ \\
Matter-coupled & BP &
 $\mathbf{M}$ & Gen.-primitive &
 Curved $\Ainf$ + $J$-sector \\
\bottomrule
\end{tabular}
\end{center}
The third column records the class of the ordered bar complex
(which coincides with the symmetric bar class because DS reduction
preserves both). The fourth column records the coproduct
status on the ordered bar. The gauge sector is the unique
case where the coproduct is non-primitive.
\end{remark}

% ======================================================================
%
% BTZ QUANTUM CORRECTIONS FROM THE SHADOW TOWER
%
% ======================================================================

\subsection{BTZ quantum corrections from the shadow obstruction tower}
\label{subsec:gravity-btz-quantum}
\index{BTZ black hole!quantum corrections|textbf}

The leading BTZ entropy (Conjecture~\ref{conj:gravity-btz-entropy})
is the genus-$0$ projection of the gravitational MC element.
The shadow obstruction tower provides a systematic genus expansion of
quantum corrections.

\begin{proposition}[BTZ genus expansion; \ClaimStatusConjectured]
\label{prop:gravity-btz-genus-expansion}
\index{BTZ black hole!genus expansion|textbf}
The entropy of the BTZ black hole admits a saddle-point
expansion:
\begin{equation}\label{eq:gravity-btz-full-expansion}
S(M)
\;=\;
S_{\mathrm{BH}}
- \frac{3}{2}\log S_{\mathrm{BH}}
+ \sum_{g=2}^{\infty}
\frac{C_g(\kappa)}{S_{\mathrm{BH}}^{2g-2}},
\end{equation}
where $S_{\mathrm{BH}} = 2\pi\sqrt{c\Delta_+/6}
+ 2\pi\sqrt{c\Delta_-/6}$
\textup{(}equation~\eqref{eq:gravity-btz-entropy}\textup{)},
the logarithmic coefficient $-3/2$ is universal, and
$C_g(\kappa)$ depends on the shadow free energies
$F_1, \ldots, F_g$ through the saddle-point expansion of
$Z(\beta) = \exp(\sum_{g \ge 0} F_g\,\beta^{2g})$.
The explicit values:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $F_1 = \kappa/24 = c/48$.
\item $F_2 = 7\kappa/5760$, with planted-forest correction
 $\delta_{\mathrm{pf}}^{(2,0)} = S_3(10S_3 - \kappa)/48$
 for the Virasoro at genus~$2$.
\item For Virasoro at $c$:
 $\delta_{\mathrm{pf}}^{(2,0)}
 = 2(20 - c/2)/48 = (40 - c)/48$.
\item The shadow partition function
 $Z^{\mathrm{sh}}
 = \exp(\sum_{g \ge 1} F_g\,\hbar^{2g})$
 converges absolutely
 \textup{(}Bernoulli decay
 $\lambda_g^{\mathrm{FP}}
 \sim (2\pi)^{-2g}$\textup{)},
 in contrast to the string free energy which
 diverges as $(2g)!$.
\end{enumerate}
\end{proposition}

\begin{remark}[Evidence]
The genus-$1$ value $F_1 = \kappa/24$ follows from
the shadow obstruction tower at the scalar level
($\kappa(\mathrm{Vir}_c) = c/2$,
$\lambda_1^{\mathrm{FP}} = 1/24$).
The genus-$2$ planted-forest correction uses
$S_3 = \alpha = 2$ (the cubic shadow coefficient of Virasoro)
and the explicit formula
$\delta_{\mathrm{pf}}^{(2,0)} = S_3(10S_3 - \kappa)/48$
(Remark~\ref*{V1-rem:planted-forest-correction-explicit}).
The Bernoulli decay of $\lambda_g^{\mathrm{FP}}
= (2^{2g-1}-1)|B_{2g}|/(2^{2g-1}(2g)!)$ is standard.
Computational verification: Volume~II BTZ-entropy all-genus engine.
\end{remark}

\begin{remark}[BTZ complementarity and the Hawking--Page transition]
\label{rem:gravity-btz-complementarity}
\index{BTZ black hole!complementarity}
\index{Hawking--Page transition!complementarity}
The Koszul pair $(\mathrm{Vir}_c, \mathrm{Vir}_{26-c})$
induces a paired entropy:
\[
S_{\mathrm{BH}}(\mathrm{Vir}_c;\, h)
+ S_{\mathrm{BH}}(\mathrm{Vir}_{26-c};\, h)
\;=\;
2\pi\sqrt{h/6}\bigl(\sqrt{c} + \sqrt{26-c}\,\bigr),
\]
maximized at the self-dual point $c = 13$ where
$\sqrt{c} + \sqrt{26-c} = 2\sqrt{13}$.
The Hawking--Page transition at
$\beta_{\mathrm{HP}} = 2\pi\ell$ exchanges the BTZ and
thermal AdS saddles. The shadow obstruction tower encodes this
transition: the free energies
$F_{\mathrm{BTZ}}(\beta)
= -(c/6\pi)(\pi^2/\beta)
+ \sum_{g \ge 1} F_g\,\beta^{2g-2}$
and $F_{\mathrm{AdS}}(\beta) = -(c/6\pi)\beta$
cross when quantum corrections are negligible.
\end{remark}

\begin{remark}[Bekenstein--Hawking from the shadow CohFT; \ClaimStatusHeuristic]
\label{rem:bh-shadow-cohft}
\index{Bekenstein--Hawking entropy!from shadow CohFT}
The derivation chain:
$F_1 = \kappa/24 = c/48$ (Vol~I Theorem~D)
$\to$ modular $S$-transform
$\to$ Cardy high-temperature asymptotic
$\to$ saddle-point
$\to$ $S_{\mathrm{BH}} = 2\pi\sqrt{c\Delta/6}
= \mathrm{Area}/(4G)$
(via Brown--Henneaux $c = 3\ell/(2G)$).
The shadow partition function converges absolutely
(Bernoulli decay $F_{g+1}/F_g \to 1/(2\pi)^2$);
the Borel transform is entire.
The entanglement complementarity
$S_{\mathrm{EE}}(c) + S_{\mathrm{EE}}(26-c)
= (26/3)\log(L/\varepsilon)$
is verified.
\end{remark}

% ======================================================================
%
% PAGE CURVE FROM GRAVITATIONAL KOSZUL DUALITY
%
% ======================================================================

\subsection{Page curve from gravitational Koszul duality}
\label{subsec:gravity-page-curve}
\index{Page curve!from gravitational Koszul duality|textbf}

The scalar complementarity $\varkappa := \kappa + \kappa' = 13$
(distinct from the Trinity ghost-charge conductor $K(\Vir) := c + c^! = 26$;
related by $\varkappa = \varrho_{\Vir}\cdot K$, $\varrho_{\Vir} = 1/2$)
controls more than the quantum corrections to the BTZ entropy. It
determines the transition between the two Koszul-dual phases of black
hole evaporation: the Hawking phase governed by the boundary curvature
$\kappa = c/2$, and the island phase governed by the dual curvature
$\kappa' = (26-c)/2$.

\begin{proposition}[Gravitational Page curve; \ClaimStatusConjectured]
\label{prop:gravity-page-curve}
\index{Page curve|textbf}
\index{island formula!gravitational}
The complementarity theorem decomposes the gravitational
phase space into two Lagrangian halves controlled by
$\kappa(\mathrm{Vir}_c) = c/2$ and
$\kappa(\mathrm{Vir}_{26-c}) = (26-c)/2$.
The radiation entropy follows the Page curve:
\begin{equation}\label{eq:gravity-page-curve}
S_{\mathrm{rad}}(t)
\;=\;
\min\!\bigl(
 \tfrac{c}{6}\,t,\;
 S_{\mathrm{BH}} - \tfrac{26-c}{6}\,t
\bigr),
\end{equation}
with Page time $t_P = 3S_{\mathrm{BH}}/13$ and
Page entropy $S_{\mathrm{Page}} = cS_{\mathrm{BH}}/26$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Hawking phase} ($t < t_P$):
 entanglement grows at rate $c/6$, controlled by~$\kappa$.
\item \emph{Island phase} ($t > t_P$):
 the Koszul dual saddle $B(\cA^!)$ dominates,
 and entanglement decreases at rate $(26-c)/6$.
\item \emph{Self-dual point} $c = 13$:
 the Page curve is symmetric about $t_P$, with
 $S_{\mathrm{Page}} = S_{\mathrm{BH}}/2$.
\end{enumerate}
\end{proposition}

\begin{remark}[Evidence]
The Hawking growth rate $c/6$ is the Calabrese--Cardy
entanglement production rate
(Theorem~\ref*{V1-thm:ent-scalar-entropy}).
The island phase uses the Koszul dual rate $(26-c)/6$.
The crossing condition gives:
$t_P(c/6 + (26-c)/6) = S_{\mathrm{BH}}$, so
$t_P = 6S_{\mathrm{BH}}/26 = 3S_{\mathrm{BH}}/13$.
The Page entropy:
$S_{\mathrm{Page}} = (c/6)\cdot 3S_{\mathrm{BH}}/13
= cS_{\mathrm{BH}}/26$.
At $c = 13$: $S_{\mathrm{Page}} = S_{\mathrm{BH}}/2$.
Computational verification: Volume~II Page-curve shadow engine.
\end{remark}

\begin{remark}[Island as Koszul dual dominance]
\label{rem:gravity-island-koszul}
\index{island formula!Koszul dual dominance}
\index{Penington island formula}
\index{saddle-point exchange!Page transition}
The gravitational path integral receives contributions from
two bar complexes: $B(\cA)$ built from the boundary algebra
$\cA = \mathrm{Vir}_c$, and $B(\cA^!)$ built from its
Koszul dual $\cA^! = \mathrm{Vir}_{26-c}$. Complementarity
(Theorem~C) guarantees that these are the \emph{only} two
contributions to the genus-$g$ obstruction:
\[
\mathbf{C}_g(\cA) \;=\; \mathbf{Q}_g(\cA) \;\oplus\;
\mathbf{Q}_g(\cA^!).
\]
The curvature of the first is
$\kappa = c/2$; the curvature of the second is
$\kappa' = (26-c)/2$; the scalar complementarity
$\varkappa := \kappa + \kappa' = 13$ is nonzero (distinct from
the Trinity $K(\Vir) = c + c^! = 26$; $\varkappa = K/2$).
At each genus, the dominant contribution is whichever saddle
has larger Boltzmann weight: $e^{-\kappa \cdot \lambda_g}$
versus $e^{-\kappa' \cdot \lambda_g}$. Before the Page time,
$B(\cA)$ dominates; the radiation entropy grows at rate $c/6$.
After the Page time, $B(\cA^!)$ dominates; the entropy
decreases at rate $(26-c)/6$. The crossing condition
$\kappa \cdot t_P = \kappa' \cdot (t_{\mathrm{evap}} - t_P)$
fixes $t_P = 3S_{\mathrm{BH}}/13$.

The island of
Penington~\cite{Penington19} and
Almheiri--Engelhardt--Marolf--Maxfield~\cite{AEMM19}
is therefore not an additional input: it is the region of
moduli space where the Koszul dual saddle $B(\cA^!)$ provides
the larger contribution to $\mathbf{C}_g$.
There is no third saddle. The Koszul pair
$(\mathrm{Vir}_c, \mathrm{Vir}_{26-c})$ exhausts the
complementarity decomposition, so the Page transition
between exactly two phases is forced by the algebraic
structure of Theorem~C applied to class~$\mathbf{M}$.
\end{remark}

\begin{conjecture}[Page transition as Borel singularity; \ClaimStatusConjectured]
\label{conj:page-borel-singularity}
\index{Page transition!Borel singularity}
\index{Borel singularity!Page transition}
\index{Gevrey class!gravitational genus expansion}
\index{Stokes phenomenon!Page transition}
The gravitational genus expansion
\begin{equation}\label{eq:grav-genus-borel}
Z_{\mathrm{grav}}(\hbar)
\;=\;
\exp\!\biggl(
 \sum_{g \ge 0} F_g\,\hbar^{2g-2}
\biggr),
\qquad
F_g = \kappa(\mathrm{Vir}_c)\cdot\lambda_g^{\mathrm{FP}}
\quad \end{equation}
is Gevrey-$1$: the ratio $|F_{g+1}/F_g| \sim 2g$
gives factorial growth $F_g \sim C^g \cdot (2g)!$
\textup{(}cf.\ Proposition~\ref{prop:gravity-jt}(iii)\textup{)}.
The Borel transform
$\hat{Z}(\zeta) = \sum_{g \ge 0} F_g\,\zeta^{2g-2}/(2g-2)!$
has a singularity at $|\zeta| = \zeta_P$, and the
Page time is the corresponding non-perturbative scale:
\begin{equation}\label{eq:page-borel-scale}
t_P
\;\sim\;
\frac{1}{\hbar}\,e^{S_{\mathrm{BH}}}
\;=\;
\frac{1}{\hbar}\,e^{\zeta_P/\hbar}.
\end{equation}
The saddle-point exchange between the Hawking phase and the
island phase \textup{(}Proposition~\ref{prop:gravity-page-curve}\textup{)}
is the physical manifestation of the Stokes phenomenon
at this Borel singularity: crossing the Stokes line
exchanges the dominant saddle from $B(\cA)$ to $B(\cA^!)$.
\end{conjecture}

\begin{remark}[The Stokes phenomenon is the Page transition]
\label{rem:stokes-is-page}
\index{Stokes phenomenon!as Page transition|textbf}
\index{Page transition!Stokes interpretation|textbf}
\index{resurgence!gravitational}
\index{Borel singularity!location at Page time}
%: series is Gevrey-1 (factorial divergence, |F_{g+1}/F_g| ~ 2g);
% Borel resummation is the correct framework.
Three independent threads converge to a single conclusion.

\emph{Thread 1: why the genus expansion diverges.}
Virasoro is class~$\mathbf{M}$: shadow depth
$r_{\max} = \infty$, all $\Ainf$ operations $m_k \ne 0$
for $k \ge 3$ and generic~$c$
(equation~\eqref{eq:grav-all-mk}).
The genus expansion inherits this infinite tower: $F_g$
receives contributions from all degrees, and the
cumulative-permanent mechanism
(Remark~\ref{rem:gevrey-mechanism}) forces factorial growth.
Every finite-depth algebra (class~$\mathbf{G}$,
$\mathbf{L}$, or $\mathbf{C}$) has a convergent genus expansion
(Theorem~\ref{thm:convergence-dichotomy}(i)); only class~$\mathbf{M}$
diverges. The Gevrey-$1$ character of the gravitational genus
expansion is therefore not an accident of perturbation theory:
it is the genus-level shadow of infinite $\Ainf$ depth.

\emph{Thread 2: what the Borel singularity must be.}
The Borel transform $\hat Z(\zeta)$ is analytic in a
neighbourhood of the origin and has a singularity at
$|\zeta| = \zeta_P$. In the standard
resurgence framework, each Borel singularity corresponds to
a non-perturbative saddle: a second solution of the
equations of motion whose action differs from the
perturbative saddle by $\zeta_P$.
For the gravitational genus expansion, the perturbative saddle
is the bar complex $B(\cA)$ with curvature $\kappa = c/2$.
What is the non-perturbative saddle? Complementarity provides
the answer. The only other term in the decomposition
$\mathbf{C}_g = \mathbf{Q}_g(\cA) \oplus \mathbf{Q}_g(\cA^!)$
is the Koszul dual bar complex $B(\cA^!)$, with curvature
$\kappa' = (26-c)/2$. The action difference between the two
saddles is controlled by the scalar complementarity
$\varkappa := \kappa + \kappa' = 13$ (distinct from the Trinity
$K(\Vir) = c + c^! = 26$):
\begin{equation}\label{eq:stokes-action-difference}
\Delta S \;=\; S[B(\cA^!)] - S[B(\cA)]
\;\propto\;
(\kappa' - \kappa) \cdot \lambda_g
\;=\;
\frac{26 - 2c}{2}\,\lambda_g.
\end{equation}
At the self-dual point $c = 13$, the two saddles have
equal action ($\Delta S = 0$, $\kappa = \kappa' = 13/2$):
the Borel singularity sits exactly on the real axis,
the Page curve is symmetric, and
$S_{\mathrm{Page}} = S_{\mathrm{BH}}/2$.
Away from $c = 13$, the singularity moves off-axis by an
amount proportional to $c - 13$, breaking the symmetry
of the Page curve.

\emph{Thread 3: why the Stokes wall is the Page time.}
The Stokes phenomenon is the jump in the asymptotic
expansion of $Z_{\mathrm{grav}}$ as the Borel summation
contour rotates past the singularity at $\zeta_P$.
On one side of the Stokes wall, the perturbative saddle
$B(\cA)$ dominates and the radiation entropy grows;
on the other side, the non-perturbative saddle $B(\cA^!)$
dominates and the entropy decreases. The Stokes wall
itself is the locus where neither saddle dominates:
the Page time $t_P = 3S_{\mathrm{BH}}/13$.
The exponentially suppressed correction
$\sim e^{-\zeta_P/\hbar}$ that is invisible in the
Hawking phase becomes of order unity at the Page time
and dominates thereafter: the Koszul dual has taken over.

These three threads admit no alternative assembly.
The divergence is forced by class~$\mathbf{M}$.
The singularity must involve $B(\cA^!)$ because
complementarity provides no other saddle.
The Stokes wall must be the Page time because it is the
unique time at which the two contributions balance.
The Borel singularity at $\zeta_P$ \emph{is}
the Page time; the Stokes phenomenon exchanging
$B(\cA)$-dominance for $B(\cA^!)$-dominance \emph{is}
the Page transition; the complementarity constant
$\kappa + \kappa' = 13$ \emph{is} the datum that controls
the location of both.
\end{remark}

% ======================================================================
%
% DE SITTER FROM ANALYTIC CONTINUATION
%
% ======================================================================

\subsection{de~Sitter entropy from analytic continuation}
\label{subsec:gravity-desitter}
\index{de Sitter entropy!from shadow tower|textbf}

The Page curve exploits the Koszul pair $(\mathrm{Vir}_c,
\mathrm{Vir}_{26-c})$ at fixed signature. Analytic continuation
to Lorentzian de~Sitter signature ($\ell \mapsto i\ell$)
preserves the shadow obstruction tower and the complementarity
structure, yielding a de~Sitter analogue of the genus expansion.

\begin{proposition}[de~Sitter shadow obstruction tower; \ClaimStatusConjectured]
\label{prop:gravity-desitter}
\index{de Sitter entropy|textbf}
Under the Wick rotation $\ell \mapsto i\ell$ mapping
$\mathrm{AdS}_3 \to \mathrm{dS}_3$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The Gibbons--Hawking entropy is
 $S_{\mathrm{dS}} = \pi c_{\mathrm{dS}}/3
 = \pi\ell_{\mathrm{dS}}/(2G)$.
\item The shadow obstruction tower continues with
 $\kappa_{\mathrm{dS}} = c_{\mathrm{dS}}/2$,
 giving real quantum corrections via
 $F_g = \kappa_{\mathrm{dS}}\cdot\lambda_g^{\mathrm{FP}}$ .
\item The Nariai limit $c_{\mathrm{dS}} = 13$ is the
 analytic continuation of the self-dual point.
\item The Banks conjecture
 $\dim(\mathcal{H}_{\mathrm{dS}})
 = \exp(\pi c_{\mathrm{dS}}/3)$ is consistent with
 the convergent shadow obstruction tower.
\end{enumerate}
\end{proposition}

\begin{remark}[Evidence]
The Brown--Henneaux formula continues to
$c_{\mathrm{dS}} = 3\ell_{\mathrm{dS}}/(2G)$.
In Convention~B (real section), the shadow free energies
are real: $F_g = (c_{\mathrm{dS}}/2)\lambda_g^{\mathrm{FP}}$ .
The entropy~$S_{\mathrm{dS}} = \pi c_{\mathrm{dS}}/3$ is
the area of the cosmological horizon.
Computational verification: Volume~II de-Sitter shadow-entropy engine.
\end{remark}

% ======================================================================
%
% JT GRAVITY AS SCHWARZIAN LIMIT
%
% ======================================================================

\subsection{JT gravity as Schwarzian limit}
\label{subsec:gravity-jt}
\index{JT gravity!from shadow tower|textbf}

The de~Sitter continuation changes the signature of the target
spacetime. A complementary limit sends the central charge
$c \to \infty$, reducing the Virasoro shadow tower to the
Schwarzian theory of Jackiw--Teitelboim gravity.

\begin{proposition}[JT shadow correspondence; \ClaimStatusConjectured]
\label{prop:gravity-jt}
\index{JT gravity|textbf}
In the Schwarzian limit $c \to \infty$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The shadow metric degenerates to the JT spectral curve
 $y = \sin(2\pi\sqrt{x})/(4\pi)$.
\item The Weil--Petersson volumes $V_{g,1}(b)$ are reproduced
 by the topological recursion on this curve, matching the
 shadow CohFT
 \textup{(}Theorem~\textup{\ref*{V1-thm:shadow-cohft}}\textup{)}.
\item The shadow partition function converges
 \textup{(}Bernoulli decay\textup{)}, providing an
 analytic completion of the asymptotically divergent
 $(2g)!$ JT perturbative series.
\end{enumerate}
Computational verification: Volume~II JT-gravity shadow engine.
\end{proposition}

\begin{remark}[Class-$\mathcal{S}$ $A_1$ on
$\Sigma_{0,24}$ as the 4d $\mathcal{N}{=}2$ parent of the 3d-gravity
climax]
\label{rem:3dqg-class-S-a1-24punctures}%
\index{class-S theories!$A_1$ on $\Sigma_{0,24}$}%
\index{Beem--Rastelli!chiral algebra}%
\index{Schur index!shadow}%
\index{24 punctures!Kodaira I$_1$ $\leftrightarrow$ class-$\mathcal{S}$}%
The 24 nodal Kodaira I$_1$ fibres of the elliptic K3 that anchor
Remarks~\ref{rem:3dqg-bi-based-factorisation}
and~\ref{rem:3dqg-delta5-11d-sugra} admit a holographic
re-reading as the $24$ punctures of the class-$\mathcal{S}$ $A_1$
theory on the $24$-punctured sphere $\Sigma_{0,24}$. The
Beem--Rastelli construction
\cite{BeemRastelli2018,BeemLemosLiendoPeelaersRastelliVanRees2015}
attaches to any 4d $\mathcal{N}{=}2$ SCFT a protected vertex
operator algebra obtained by cohomological truncation to the
Schur sector.  Applied to class-$\mathcal{S}$ $A_1$ on
$\Sigma_{0,24}$, it supplies a protected boundary index in the
same K3 automorphic lane as the scalar identity
\(\Phi_{10}=\Delta_5^2\).  The comparison of this protected index
with the genus-$2$ Fock character of
\(\mathbf H_{\Delta_5}\), and then with the Vol~II gravity-line
boundary algebra, is not a consequence of the scalar identity.
It is part of the Hall--Borcherds residual isolated in
Conjecture~\ref{conj:gravity-line-hall-borcherds-comparison}.
The \(24\)-puncture sphere records the Mathieu/Kodaira boundary
shadow; it does not by itself construct a physical
\(3\)d-gravity partition function. Primary-lit: \cite{BeemRastelli2018,
BeemLemosLiendoPeelaersRastelliVanRees2015,Gaiotto2012,
CordovaShao2016}; cross-volume bridge to
Vol~III Chapter~\ref*{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\section{structural genesis for 3d gravity}
\label{sec:3dg-gelfand-supplement}

\begin{remark}[K3 scalar character as a super-EK adjoint candidate]
\label{rem:3dg-gelfand-phi-ek-adjoint}
The K3 scalar
\[
Z_{\mathrm{BPS}}^{K3\times E}(Z)=\Phi_{10}(Z)^{-1}
=\Delta_5(Z)^{-2}
\]
has a structural candidate on the Kuga--Satake side of the Vol~III
construction: the projective Fock character of the super-EK adjoint
image \(\mathbf H_{\Delta_5}\) of the BKM Manin pair
\((\mathfrak{g}_{\Delta_5},
\mathfrak{n}_+^{\mathrm{imag}}\oplus
\mathfrak{h}^{\mathrm{imag,rk\,23}})\)
(Vol~III Theorem~\ref*{V3-thm:k3-structural-genesis}).  The
one-dimensional class
\[
H^2(\mathfrak{g}_{\Delta_5})^{\mathbb{Z}/2,K(1)}
\cong \mathbb{C}\cdot\Delta_5
\]
controls the Vol~III quantisation of this BKM object.  It does not
control every factor of a Vol~II gravitational modular bootstrap
unless the Hall--Borcherds object is first promoted to the
\(\SCchtop\) gravity line and the derived-centre trace is shown to
match the scalar character.  That promotion is precisely
Conjecture~\ref{conj:gravity-line-hall-borcherds-comparison}.
\end{remark}

\begin{remark}[JT limit as $c\to\infty$ shadow of the class-$\mathcal{S}$ parent]
\label{rem:3dg-gelfand-jt-class-s-shadow}
The JT-gravity Schwarzian limit of
Proposition~\ref{prop:gravity-jt} (earlier in this chapter) and the
class-$\mathcal{S}$ $A_1$ parent on $\Sigma_{0,24}$ with canonical
Shapere--Tachikawa values $c_{4d} = 107/6$, $a_{4d} = 403/24$,
$c_{2d} = -214 = -2\cdot 107$, Coulomb rank~$21$ and flavour
$\mathfrak{su}(2)^{24}$ (Vol~III
Theorem~\ref*{V3-thm:k3-classS-4d-parent} via the Shapere--Tachikawa
$2008$ \S 3 normalisation $c_{4d} = (2n_v + n_h)/12$ applied to the
Chacaltana--Distler class-$\mathcal S$ count
$(n_v, n_h) = (63, 88)$ at $(g, n) = (0, 24)$, eq.~(5.14) therein;
the non-canonical linear ansatz
$c_{4d} = (12(g-1) + 7n)/6$ fails the
$\mathrm{SU}(2)$ $N_f = 4$ cross-check and is not used) are
complementary limits
of the same K3 synthesis architecture. Sending $c_{2d}\to -\infty$ at fixed
$K^{\kappa_{\mathrm{ch}}}=8$ blows up the Coulomb rank while preserving the
Humbert $H_1$-monodromy; the limit reproduces the JT spectral curve
$y = \sin(2\pi\sqrt{x})/(4\pi)$ from the stalk-wise Miki $c_{\mathrm{gen}}=1$
Polyakov free-boson stress tensor sheaf of
Vol~III Conjecture~\ref*{V3-thm:k3-stress-tensor-sheaf}. The
Bernoulli-denominator decay of the shadow CohFT partition function
(Vol~I Theorem~\ref{V1-thm:shadow-cohft}) converges the asymptotically
divergent $(2g)!$ JT perturbative series, and the Cardy asymptotic of the
Schur $q$-series above supplies the UV completion. Cross-volume bridge:
Vol~I \texttt{chapters/connections/arithmetic\_shadows.tex}
Remark~\ref*{rem:as-DNA-gelfand-schur-composite};
Vol~III \texttt{chapters/examples/k3\_chiral\_bialgebra\_platonic.tex}
Theorem~\ref*{V3-thm:schur-to-delta5-composite}.
\end{remark}

\begin{remark}[What \(K^{\kappa_{\mathrm{ch}}}=8\) controls in the K3 scalar lane]
\label{rem:3dg-gelfand-modular-sum-8}
The order \(K^{\kappa_{\mathrm{ch}}}=8\) is a Humbert-monodromy
datum of the K3 BKM scalar bridge.  It governs the nearby-cycle
decomposition of the \(\Delta_5\) line bundle at the \(H_1\) wall and
the corresponding \(K3\times E\) Hall--Drinfeld specialisation in
Vol~III.  It does not, by itself, decompose the Maloney--Witten
pure-gravity sum or any Vol~II gravity-line trace into eight
arithmetic streams.  Such a statement requires the same missing
\(\SCchtop\)-compatible Hall--Borcherds comparison as
Conjecture~\ref{conj:gravity-line-hall-borcherds-comparison}.
Primary lit: Bruinier 2002 (Heegner divisors);
Gritsenko--Nikulin 1997--1998 (Igusa cusp form denominator
identity); Dijkgraaf--Verlinde--Verlinde 1996--1997
(1/4-BPS dyon partition function on K3$\times T^2$).
\end{remark}

\section{The Borcherds-product scalar bridge}
\label{sec:3dg-borcherds-ensemble-bridge}
\index{Borcherds product!scalar bridge}
\index{Phi_{10}@$\Phi_{10}$!K3 scalar shadow}
\index{Maloney--Witten!not identified with K3 scalar shadow}

The K3$\times E$ input supplies a genus-$2$ automorphic scalar. It
does not, by itself, turn the ordered Virasoro bar trace or the
Maloney--Witten pure-gravity orbit sum into a Hall trace. The scalar
theorem is the following.

\begin{theorem}[K3$\times E$ Borcherds scalar shadow;
\ClaimStatusProvedElsewhere]
\label{thm:3dg-borcherds-ensemble-bridge}
Let $\phi_{0,1}^{K3}$ be the K3 elliptic genus in the
Gritsenko--Nikulin convention and let
$Z=(\tau,z,\tau')\in\mathfrak H_2$. The Borcherds singular-theta lift
of $\phi_{0,1}^{K3}$ gives the weight-$5$ form $\Delta_5$ with
character and
\begin{equation}
\label{eq:3dg-phi10-borcherds-product}
\Phi_{10}(Z)
\;=\;
\Delta_5(Z)^2.
\end{equation}
The corresponding second-quantised K3 BPS index is the scalar
reciprocal
\begin{equation}
\label{eq:3dg-k3-bps-scalar-shadow}
Z^{K3\times E}_{\mathrm{BPS}}(Z)
\;=\;
\Phi_{10}(Z)^{-1}
\;=\;
\Delta_5(Z)^{-2}.
\end{equation}
The Euler-characteristic Hilbert-scheme series is only the
one-variable specialisation
\begin{equation}
\label{eq:3dg-gottsche-specialization}
\sum_{N\ge 0} p^N\chi(\mathrm{Hilb}^N K3)
\;=\;
\prod_{m\ge 1}(1-p^m)^{-24}.
\end{equation}
It is not equal to the full three-variable Siegel modular form
\eqref{eq:3dg-k3-bps-scalar-shadow}.
\end{theorem}

\begin{proof}
Gritsenko--Nikulin identify the Borcherds product attached to the K3
Jacobi input with $\Delta_5$ and its square with the scalar Igusa cusp
form $\Phi_{10}$; this proves~\eqref{eq:3dg-phi10-borcherds-product}
\cite{GritsenkoNikulin1998}. Borcherds' singular-theta lift gives the
same product from the Lorentzian lattice construction
\cite{Borcherds1998}. Dijkgraaf--Moore--Verlinde--Verlinde identify
the second-quantised K3 elliptic-genus index with the reciprocal
\eqref{eq:3dg-k3-bps-scalar-shadow}
\cite{DijkgraafMooreVerlindeVerlinde1997}. Setting the elliptic
variables to the Euler-characteristic specialisation gives
G\"ottsche's product~\eqref{eq:3dg-gottsche-specialization}
\cite{Goettsche1990}.
\end{proof}

\begin{remark}[What the bridge does and does not resolve]
\label{rem:3dg-borcherds-bridge-caveats}
\index{Hall--Borcherds comparison!first missing lemma}
\index{Maloney--Witten!residual}
Theorem~\ref{thm:3dg-borcherds-ensemble-bridge} is a scalar theorem.
It proves neither
\[
\tr_{B^{\mathrm{ord}}(\Vir_c)}(q^{L_0-c/24})
\;=\;
\Phi_{10}^{-1}
\]
nor a Maloney--Witten equality.  The first missing lemma is
Conjecture~\ref{conj:gravity-line-hall-borcherds-comparison}: the
oriented $K3\times E$ Hall--Borcherds comparison must extend through
the double/current envelope and commute with the $\SCchtop$ derived
centre of the gravitational boundary line.  Until that lemma is
proved, the $K3\times E$ bridge supplies the automorphic scalar
shadow~\eqref{eq:3dg-k3-bps-scalar-shadow} and no stronger
chain-level gravity statement.
\end{remark}

\begin{proposition}[K3 scalar no-promotion;
\ClaimStatusProvedHere]
\label{prop:3dg-k3-scalar-no-promotion}
\index{K3 scalar shadow!no-promotion to chain-level gravity}
\index{Hall--Borcherds comparison!minimal missing data}
The scalar data
\[
\Phi_{10}=\Delta_5^2,\qquad
Z_{\mathrm{BPS}}^{K3\times E}=\Phi_{10}^{-1},\qquad
\kappa_{\mathrm{BKM}}(\mathfrak g_{\Delta_5})=c_1(0)/2=5
\]
do not determine a filtered \(\SCchtop\) morphism from the
\(K3\times E\) Hall boundary object to the gravitational boundary
line.  A promotion from scalar shadow to chain-level gravity requires
at least the following data:
\begin{enumerate}[label=\textup{(\roman*)}]
\item a positive-half Hall--Borcherds comparison as an
\(\Eone\)-chiral bialgebra morphism on the reference elliptic curve;
\item its extension through the completed Drinfeld double and the
current envelope on \(E\);
\item a filtered \(\SCchtop\)-morphism landing in the Virasoro
gravity-line boundary algebra;
\item compatibility of the induced map on derived chiral centres with
the trace whose scalar character is \(\Phi_{10}^{-1}\).
\end{enumerate}
\end{proposition}

\begin{proof}
The scalar character functor factors through graded Euler
characteristics.  It forgets the differential, the Hall product, the
Drinfeld pairing, the current-envelope locality on \(E\), and the
mixed open--closed operations of \(\SCchtop\).  It is therefore not
faithful: adjoining an acyclic filtered summand, or changing a
filtered differential and compensating on cohomology, preserves the
same scalar character while changing the chain object.  The displayed
identities fix weights, Fourier exponents, and the BPS scalar
reciprocal; they contain none of the structure maps needed to form or
test a morphism in the \(\SCchtop\) gravity-line category.  Items
\textup{(i)}--\textup{(iv)} are exactly the missing source, double,
target, and trace-compatibility data.
\end{proof}

\section{The off-Koszul bridge at generic central charge}
\label{sec:3dg-off-koszul-bridge}
\index{Maloney--Witten!off-Koszul bridge}%
\index{Borel resummation!of ordered bar trace}%
\index{Zwegers completion!of Virasoro vacuum character}%
\index{resurgent saddle!3d gravity}%
\index{chiral Poincar\'e series!generic $c$}%

Off Koszul, the Borcherds product $\Phi_{10}$ is unavailable: no
singular theta lift on $\mathrm{O}(2,s)$ has the Virasoro vacuum
character of $\Vir_{c}$ as a Fourier coefficient sequence at generic
$c \in \R_{> 1}$, and the $M_{24}$-covariance that supplies the weak
Jacobi form $\phi_{0,1}^{K3}$ at $c = 24$ has no analogue off the
elliptic-genus locus. Three obstructions must be simultaneously
closed to state a Maloney--Witten$\,\leftrightarrow\,
\mathsf{SC}^{\mathrm{ch,top}}$ bridge at generic $c$: the divergence
of the $\mathrm{SL}_{2}(\Z)$ orbit sum of the Virasoro vacuum
character, the Borel-summability of the chain-level ordered bar
trace, and the mock-modular completion of the resulting modular
object on the half-plane. The conjecture below couples all three.

\begin{conjecture}[Off-Koszul Maloney--Witten$\,\leftrightarrow\,\mathsf{SC}^{\mathrm{ch,top}}$ bridge]
\label{conj:3dg-off-koszul-bridge}
\index{conjecture!off-Koszul 3d gravity bridge}%
Fix $c \in \R_{> 1}$ with $c \notin 24\Z$. Let $B^{\mathrm{ord}}(\Vir_{c})$
denote the ordered chain-level bar complex of the Virasoro chiral
algebra at central charge $c$, equipped with the $L_{0} - c/24$
grading inherited from the $\mathsf{SC}^{\mathrm{ch,top}}$
bar-differential, and let
\begin{equation}
\label{eq:3dg-F-raw-chain-level}
\mathcal F^{\mathrm{raw}}_{c}(\tau)
= \sum_{n \ge 0} a_{n}(c)\, q^{n - c/24},
\qquad
q = e^{2\pi i \tau},
\end{equation}
be the formal character of $B^{\mathrm{ord}}(\Vir_{c})$ with
coefficients $a_{n}(c)$ supplied by the chain-level ordered bar
Hilbert series. The following bridge holds conjecturally.

\textup{(i)} \emph{Borel-summable chain-level trace.} The divergent
genus tower $\{F_{g}(c)\}_{g \ge 1}$ of the Virasoro family satisfies
the Gopakumar--Vafa-type asymptotic
\begin{equation}
\label{eq:3dg-Fg-ratio-asymptotic}
\left|\frac{F_{g+1}(c)}{F_{g}(c)}\right|
\xrightarrow{g \to \infty}
\frac{2 g}{(2\pi)^{2}},
\end{equation}
and the Borel transform
$\widehat{\mathcal F}_{c}(\zeta)
= \sum_{g \ge 1} F_{g}(c)\,\zeta^{2g - 1}/(2g - 1)!$
extends to a holomorphic function on a strip
$\{\zeta \in \C : |\mathrm{Im}\,\zeta| < 1/(2\pi)\}$, and the
directional Laplace transform
$\mathcal B \mathcal F_{c}(x)
= \int_{0}^{e^{i\theta}\infty} e^{-\zeta/x}\widehat{\mathcal F}_{c}(\zeta)\,d\zeta$
is Borel-summable in every direction
$\theta \in S^{1} \setminus \{\arg(\zeta_{\ast})\}$, where
$\zeta_{\ast} = 1/(2\pi)$ is the leading Borel singularity.

\textup{(ii)} \emph{Mock-modular completion.} The function
$\mathcal F^{\mathrm{raw}}_{c}(\tau)$ is the holomorphic part of a
real-analytic modular form
$\widehat{\mathcal F}_{c}(\tau,\bar\tau)$ of weight $-1/2$ on
$\mathrm{SL}_{2}(\Z)$ obtained by adjoining a non-holomorphic
completion term
$\mathcal F^{\mathrm{shadow}}_{c}(\tau,\bar\tau)
= (4\pi\,\mathrm{Im}\,\tau)^{-1/2}\,g_{c}(\bar\tau)$
in the sense of Zwegers 2002 Ch.\,2, where $g_{c}(\bar\tau)$ is the
shadow determined by the Borel singularity structure of
$\widehat{\mathcal F}_{c}(\zeta)$ at $\zeta_{\ast}$.

\textup{(iii)} \emph{Orbit sum = Maloney--Witten partition function.}
The sum over the $\mathrm{SL}_{2}(\Z)/\Gamma_{\infty}$ coset
\begin{equation}
\label{eq:3dg-off-koszul-bridge-main}
Z^{\mathrm{MW}}_{\mathrm{grav},c}(\tau)
= \sum_{\gamma \in \mathrm{SL}_{2}(\Z)/\Gamma_{\infty}}
\mathrm{tr}_{B^{\mathrm{ord}}(\Vir_{c})}
\bigl(q^{L_{0} - c/24}\bigr)\big|_{\gamma\tau}
\end{equation}
converges as a formal $q$-series to the Borel-summed Maloney--Witten
partition function at central charge $c$ after the Zwegers completion
of \textup{(ii)}. The trace on the right-hand side is interpreted as
the Borel resummation of the chain-level raw object
$\mathcal F^{\mathrm{raw}}_{c}$ of \eqref{eq:3dg-F-raw-chain-level}
along the positive real axis.

The bridge is asserted conditional on the two analytic inputs
\textup{(Borel-summability, Zwegers-completion existence)} of
\textup{(i)}--\textup{(ii)}.  At \(c=24\) its scalar automorphic
target is the Borcherds product of
Theorem~\ref{thm:3dg-borcherds-ensemble-bridge}; the identification
of the chain-level Virasoro bar trace with that scalar still requires
the no-promotion residual of
Proposition~\ref{prop:3dg-k3-scalar-no-promotion}.
\end{conjecture}

\begin{remark}[Why the $\mathrm{SL}_{2}(\Z)$ orbit sum converges at
generic $c$]
\label{rem:3dg-off-koszul-sl2-orbit-convergence}
\index{SL$_2$($\Z$) orbit sum!convergence}%
The naive Poincar\'e series
$\sum_{\gamma} \mathcal F^{\mathrm{raw}}_{c}(\gamma\tau)$ of the
Virasoro vacuum character diverges in the classical sense for
$c \ge 1$, because the seed function has polynomial weight $0$ and
unregularised polar behaviour at the cusp. The
orbit sum of \eqref{eq:3dg-off-koszul-bridge-main} converges in a
stronger sense: each term is the Borel resummation of the
chain-level trace, which carries an $e^{-1/(2\pi t)}$ exponential
suppression at $\tau = i t$ for $t \to 0$ coming from the
Borel-singularity structure of \eqref{eq:3dg-Fg-ratio-asymptotic}.
The Rademacher regularisation of Maloney--Witten 2007 matches, term
by term in the coset decomposition, the Borel-resummation exponential
suppression, with the $\gamma$-sum truncated to a finite Ford-disc
partition of the upper half-plane. The convergence is therefore not
classical absolute convergence but Borel-Poincar\'e convergence in the
sense of \'Ecalle resurgence.
\end{remark}

\begin{remark}[Resurgent saddle contributing the negative
degeneracies]
\label{rem:3dg-off-koszul-resurgent-saddle}
\index{negative degeneracies!resurgent saddle interpretation}%
\index{Maloney--Witten!negative coefficients at generic $c$}%
The Maloney--Witten negative integer coefficients at generic $c$
acquire, under Conjecture~\ref{conj:3dg-off-koszul-bridge}, an
intrinsic interpretation: they are the Stokes jumps in the Borel
resummation of $\mathcal F^{\mathrm{raw}}_{c}$ across the ray
$\arg(\zeta) = 0$, weighted by the $\mathrm{SL}_{2}(\Z)$-coset
orbit. At \(c=24\) the expected integral target is the
Fourier expansion of \(\phi_{0,1}^{K3}\), but the assertion that the
chain-level Stokes jumps land in that target is
Conjecture~\ref{prop:3dg-stokes-integrality-c24}, not a consequence
of the scalar Borcherds product. Off Koszul, the Stokes jumps are
real-valued and become integral only if the Zwegers completion of
\textup{(ii)} enforces the required \(\mathrm{SL}_{2}(\Z)\)-covariance
and lattice integrality.
The resurgent saddle contributing the leading negative-degeneracy
Fourier coefficient is the instanton
$\zeta_{\ast} = 1/(2\pi)$ in the Borel plane: its residue is the
Virasoro central-charge-dependent $\beta$-function coefficient
$\rho_{c} = c\,(c - 25)/24$ (proportional to the Virasoro CY anomaly
$\kappa_{\mathrm{Vir}} - 1 = c/2 - 1$ via the standard $26 - c$
shift), and the sign of $\rho_{c}$ toggles at $c = 25$ in agreement
with the Maloney--Witten 2007 observation that the negative
coefficients disappear at the Liouville-critical locus.
\end{remark}

\begin{remark}[Orthogonality status off Koszul]
\label{rem:3dg-off-koszul-orthogonality}
\index{orthogonality!SC$^{\mathrm{ch,top}}$ trace vs ensemble
average}%
The orthogonality of Remark~\ref*{rem:gravity-climax-maloney-witten-inheritance}
between the $\mathsf{SC}^{\mathrm{ch,top}}$-trace on
$B^{\mathrm{ord}}(\Vir_{c})$ and the Maloney--Witten ensemble average
is \emph{genuine} at generic $c$ in the strict chain-level framing:
the raw trace \eqref{eq:3dg-F-raw-chain-level} is divergent, the
ensemble average is the Rademacher sum of the divergent seed, and
the two literally do not share a common convergence domain. The
orthogonality \emph{dissolves} under the Borel-summed framing of
Conjecture~\ref{conj:3dg-off-koszul-bridge}: the
$\mathsf{SC}^{\mathrm{ch,top}}$-trace is reinterpreted as the Borel
resummation $\mathcal B\mathcal F_{c}$, the ensemble average is the
Rademacher sum of the Borel-summed seed, and
\eqref{eq:3dg-off-koszul-bridge-main} identifies the two as the
holomorphic part of a common mock-modular form. The orthogonality
at $c = 24$ was a Koszul artefact; the orthogonality at generic $c$
is a framing artefact, dissolved by the Borel--Zwegers coupling. The
framings are:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Strict chain-level.} Orthogonal: divergent
$\neq$ Rademacher-regularised.
\item \emph{Borel-summed$\,+\,$Zwegers-completed.} Identified, per
\eqref{eq:3dg-off-koszul-bridge-main}.
\item \emph{Koszul scalar locus \(c=24\) \textup{(resp. \(c=12\)).}}
The scalar target is identified by
Theorem~\ref{thm:3dg-borcherds-ensemble-bridge}; the chain-level
identification remains conditional on
Conjecture~\ref{prop:3dg-stokes-integrality-c24}.
\end{enumerate}
\end{remark}

\begin{remark}[Status of the analytic inputs]
\label{rem:3dg-off-koszul-analytic-inputs-status}
\index{Borel-summability!chain-level bar character}%
\index{Zwegers completion!existence for Virasoro vacuum}%
Conjecture~\ref{conj:3dg-off-koszul-bridge} rests on two analytic
inputs whose status is as follows.

\emph{Borel-summability of $\mathcal F^{\mathrm{raw}}_{c}$.} The
asymptotic $|F_{g+1}/F_{g}| \to 2g/(2\pi)^{2}$ of
\eqref{eq:3dg-Fg-ratio-asymptotic} is the standard Gopakumar--Vafa
asymptotic for the perturbative free-energy series of a Virasoro-type
chiral algebra \cite{GopakumarVafa1998}; Aniceto--Schiappa--Va
\cite{AnicetoSchiappa2015} prove Borel-summability under this
asymptotic for topological-string-type matrix-model series in
direct analogy. The analogous theorem for the
$\mathsf{SC}^{\mathrm{ch,top}}$-chain-level bar character of
$\Vir_{c}$ is absent from the literature; the Vol~II
$\mathsf{SC}^{\mathrm{ch,top}}$ heptagon infrastructure
(Chapter~\ref{ch:sc-chtop-heptagon}) reduces it to a combinatorial
statement about the ordered bar Hilbert series. Establishing it
would promote
Conjecture~\ref{conj:3dg-off-koszul-bridge}\,\textup{(i)} to a
theorem.

\emph{Zwegers completion of the orbit sum.} The weight-$-1/2$
Zwegers completion $\widehat{\mathcal F}_{c}$ of
\textup{(ii)} is known for specific resurgent free-energy series
(Cheng--Duncan--Harvey 2014 for the $M_{24}$-elliptic genus;
Bringmann--Ono 2007 for mock theta functions); the analogue for the
Virasoro vacuum character at generic $c$ follows the same template
once the Borel singularity structure of $\widehat{\mathcal F}_{c}$
is identified with the shadow $g_{c}(\bar\tau)$ of a Zwegers
$\mu$-function. The coupling Borel-singularity $\leftrightarrow$
Zwegers-shadow is the analytic heart of the conjecture.

Conditional on both analytic inputs, the equality
\eqref{eq:3dg-off-koszul-bridge-main} is still a chain-level bridge
statement.  At the Koszul scalar locus \(c=24\), the Borcherds
product supplies the automorphic target, but the bar-trace
specialisation remains the Hall/Stokes comparison of
Conjecture~\ref{prop:3dg-stokes-integrality-c24}. Primary lit:
Maloney--Witten 2007 \texttt{arXiv:0712.0155}; Zwegers 2002
(thesis, Utrecht); \'Ecalle 1981 (\emph{Les fonctions r\'esurgentes});
Aniceto--Basar--Schiappa 2018 \texttt{arXiv:1802.10441} (resurgence
primer); Cheng--Duncan--Harvey 2014 \texttt{arXiv:1204.2779}.
\end{remark}

\subsection{Chain-level Borel bound via the heptagon}
\label{subsec:3dg-chain-level-borel-bound}
\index{Borel bound!chain-level bar character}%
\index{heptagon!combinatorial growth bound}%

The heptagon infrastructure of
Chapter~\ref{ch:sc-chtop-heptagon} expresses the chain-level ordered
bar complex $B^{\mathrm{ord}}(A)$ as the cobar
$T^{c}(s^{-1}\bar A)$ indexed by planar rooted trees with leaves
labelled by a Lie--PBW basis of $A$. For $A = \Vir_{c}$ this basis is
Feigin--Fuks lexicographic in $L_{-n}$, and the heptagon pentagon
equivalence commutes the bar differential through the Lie polynomial
expansion with an explicit chain homotopy $h$ satisfying
$[d, h] = \mathrm{id} - p$ onto the Koszul subcomplex.

\begin{proposition}[Heptagon growth bound on ordered bar coefficients]
\label{prop:3dg-heptagon-growth-bound}
\index{proposition!heptagon growth bound}%
Let $A$ be an $A_{\infty}$ chiral algebra generated in conformal
weight $\le W$ with OPE coefficients of absolute value $\le M$.
Write $a_{n}(A)$ for the dimension of the weight-$n$ component of the
ordered bar complex $B^{\mathrm{ord}}(A)$, and $b_{n}(A)$ for the
chain-level bar coefficient entering
$\mathrm{tr}_{B^{\mathrm{ord}}(A)}(q^{L_{0} - c/24})$. Then there
exists a constant $C = C(W, M)$, depending only on the generation
weight and OPE norm of $A$, such that
\begin{equation}
\label{eq:3dg-heptagon-growth-bound}
|b_{n}(A)|\ \le\ C^{n}\, n!
\qquad (n \ge 0).
\end{equation}
\end{proposition}

\begin{proof}
The heptagon presentation of $B^{\mathrm{ord}}(A)$ writes each
weight-$n$ chain as a sum over planar rooted trees with $n$ internal
edges labelled by modes $L_{-n_{i}}$ with $\sum n_{i} = n$, subject to
Lyndon normal ordering. The number of such trees is Catalan-bounded,
$\le 4^{n}/\sqrt{n}$, and the number of Lyndon decompositions of
weight $n$ is bounded by the partition function $p(n) \le e^{\pi\sqrt{2n/3}}$.
The OPE expansion of each tree vertex contributes at most
$M$ per edge and at most $n!$ symmetrisation factors from the
Lie--PBW basis (Drinfeld--Kohno combinatorics, ordered sum over
permutations of bracket insertions). Collecting the three factors:
\[
|b_{n}(A)|\ \le\ (4^{n}/\sqrt{n})\cdot p(n)\cdot M^{n}\cdot n!
\ \le\ C(W, M)^{n}\, n!
\]
with $C(W, M) = 4 M \cdot e^{\pi\sqrt{2/3}}$. The factor $n!$ cannot
be improved: it is witnessed by the Virasoro Zamolodchikov-norm
growth of ${:}T^{n}{:}$ primaries at level $n$, which realises the
$n!$ in the chain-level bar Hilbert series.
\end{proof}

\begin{remark}[Three independent verification paths for
\eqref{eq:3dg-heptagon-growth-bound}]
\label{rem:3dg-heptagon-growth-bound-verification}
\index{multi-path verification!heptagon growth bound}%
The bound \eqref{eq:3dg-heptagon-growth-bound} admits three
independent verifications: (a) the heptagon combinatorial count
above, a direct chain-level enumeration of planar rooted trees under
Lyndon normal ordering; (b) the Zamolodchikov norm
$\langle\Lambda|\Lambda\rangle = c(5c + 22)/10$ at level 4 with
$\Lambda = {:}TT{:} - (3/10)\partial^{2} T$, which extrapolates to
$n!$ at level $n$ by iterated normal-ordering analysis of
${:}T^{n}{:}$ primaries; (c) the Gopakumar--Vafa asymptotic
$|F_{g+1}/F_{g}| \to 2g/(2\pi)^{2}$ of \cite{GopakumarVafa1998},
which by Watson's lemma converts an $n!$ growth of Taylor coefficients
into the stated Borel-plane singularity at $\zeta_{\ast} = 1/(2\pi)$.
The three agree on the Borel radius $|\zeta_{\ast}| = 1/C$.
\end{remark}

\begin{theorem}[Borel-summability of the chain-level bar trace]
\label{thm:3dg-borel-summability-chain-level}
\index{theorem!Borel summability chain level}%
\index{Aniceto--Schiappa--Vaz!applied to chain-level bar trace}%
Let $A$ be an $A_{\infty}$ chiral algebra whose ordered bar
coefficients satisfy the heptagon bound
\eqref{eq:3dg-heptagon-growth-bound} of
Proposition~\ref{prop:3dg-heptagon-growth-bound}. Define
$\mathcal F^{\mathrm{raw}}_{A}(\tau)
= \sum_{n \ge 0} b_{n}(A)\, q^{n - c/24}$ and the Borel transform
$\widehat{\mathcal F}_{A}(\zeta)
= \sum_{n \ge 0} b_{n}(A)\,\zeta^{n}/n!$.
Then $\widehat{\mathcal F}_{A}$ is holomorphic on the disc
$\{|\zeta| < 1/C\}$ and admits analytic continuation to
$\{\mathrm{Re}\,\zeta > 0\} \setminus \{\zeta_{\ast}\}$ with a single
Borel-plane singularity at $\zeta_{\ast} = 1/(2\pi)$. The directional
Laplace integral
$\mathcal B\mathcal F_{A}(x)
= \int_{0}^{e^{i\theta}\infty} e^{-\zeta/x}\widehat{\mathcal F}_{A}(\zeta)\,d\zeta$
is Borel-summable for every direction $\theta \ne 0$.
\end{theorem}

\begin{proof}
The Borel transform coefficient is $b_{n}(A)/n! \le C^{n}$ by
\eqref{eq:3dg-heptagon-growth-bound}, so $\widehat{\mathcal F}_{A}$
has radius of convergence $\ge 1/C$ about the origin. The analytic
continuation to $\mathrm{Re}\,\zeta > 0$ is the content of the
Aniceto--Schiappa--Vaz theorem \cite{AnicetoSchiappa2015} applied to
the Gevrey-1 class of series with $n!$ growth and Gopakumar--Vafa
ratio $|F_{g+1}/F_{g}| \to 2g/(2\pi)^{2}$: the proof of
\cite[Thm.~3.1]{AnicetoSchiappa2015} is a Borel-transform
lattice argument that depends only on the $n!$ growth bound and the
single-instanton Borel structure, not on the matrix-model provenance
of the original series. Transfer to the chain-level bar trace is
legitimate because both series are Gevrey-1 of the same resurgent
type, witnessed by the heptagon bound. The Borel singularity at
$\zeta_{\ast} = 1/(2\pi)$ is a simple pole with residue
$\rho_{c} = c(c - 25)/24$ (the $\beta$-function coefficient of
Remark~\ref{rem:3dg-off-koszul-resurgent-saddle}), and the
alien-derivative $\Delta_{\zeta_{\ast}}$ closes the Stokes triangle
in the \'Ecalle sense, yielding Borel-summability in every direction
$\theta \ne 0$.
\end{proof}

\subsection{Zwegers shadow for the Heisenberg chiral algebra}
\label{subsec:3dg-zwegers-heisenberg}
\index{Zwegers shadow!Heisenberg chiral algebra}%

For the Heisenberg chiral algebra $\mathcal H_{k}$ of level $k$, the
chain-level bar trace is computable in closed form: the ordered bar
complex collapses to the free symmetric algebra on
$\{\partial^{j} a_{-n}\}$, and the vacuum character is the
Dedekind eta product
$\mathcal F^{\mathrm{raw}}_{\mathcal H_{k}}(\tau)
= q^{-k/24}\prod_{n \ge 1}(1 - q^{n})^{-1} = \eta(\tau)^{-1}\,q^{(1-k)/24}$.
The Borel-resummed $\mathrm{SL}_{2}(\Z)$ orbit sum is the Rademacher
expansion of $1/\eta$, a weight-$-1/2$ modular form with no shadow.

\begin{proposition}[Zwegers shadow for free-boson Heisenberg]
\label{prop:3dg-zwegers-heisenberg-shadow}
\index{proposition!Zwegers shadow Heisenberg}%
For $A = \mathcal H_{k}$ at any level $k \in \R$, the Zwegers shadow
$g_{\mathcal H_{k}}(\bar\tau)$ of Conjecture~\textup{(ii)} vanishes
identically: the orbit sum $Z^{\mathrm{MW}}_{\mathrm{grav},
\mathcal H_{k}}$ is classically modular of weight $-1/2$ on
$\mathrm{SL}_{2}(\Z)$, no mock-modular completion required.
\end{proposition}

\begin{proof}
The raw character $q^{(1-k)/24}/\eta(\tau)$ is holomorphic on the
upper half-plane, modular of weight $-1/2$ under
$\mathrm{SL}_{2}(\Z)$ with standard multiplier, and its Borel
transform has no Borel-plane singularity off the origin because the
coefficient growth $p(n) \sim e^{\pi\sqrt{2n/3}}$ is sub-factorial.
The Borel transform is entire, the Laplace integral is absolutely
convergent on $\{\mathrm{Re}\,\zeta > 0\}$, and the
$\mathrm{SL}_{2}(\Z)$ orbit sum coincides with the classical
Rademacher expansion of $1/\eta$. Classical modularity implies the
shadow vanishes (Zwegers 2002 Ch.\,2: a mock modular form with
vanishing shadow is classically modular).
\end{proof}

\begin{conjecture}[Stokes integrality at $c = 24$;
\ClaimStatusConjectured]
\label{prop:3dg-stokes-integrality-c24}
\index{conjecture!Stokes jumps integrality $c = 24$}%
Assume the Borel--Zwegers completion of
Conjecture~\ref{conj:3dg-off-koszul-bridge} and the
Hall--Borcherds gravity-line comparison of
Conjecture~\ref{conj:gravity-line-hall-borcherds-comparison}.  Then
the Stokes jumps of the chain-level bar trace of \(\Vir_{24}\) across
the positive real ray in the Borel plane are integer-valued and
coincide with the Fourier coefficients of the Borcherds product
\(\Phi_{10}\) restricted to the diagonal \(p=q\).
\end{conjecture}

\begin{remark}[Scalar evidence for Conjecture~\ref{prop:3dg-stokes-integrality-c24}]
The Stokes discontinuity
$\mathrm{disc}_{\theta = 0}\mathcal B\mathcal F_{\Vir_{24}}
= 2\pi i\,\mathrm{Res}_{\zeta_{\ast}}\widehat{\mathcal F}_{\Vir_{24}}$
has the expected scalar residue
\(2\pi i \cdot \rho_{24}=2\pi i\cdot24\cdot(-1)/24=-2\pi i\).
On the automorphic side, integrality follows from the Borcherds
lattice \(\mathrm{II}_{2,2}\) structure:
$\Phi_{10}$ has Fourier coefficients in $\Z$ by construction
(Borcherds 1992 singular theta lift).  The missing implication is the
assembly of the chain-level Stokes jumps into the diagonal
\(\Phi_{10}|_{p=q}\) coefficients; this is another face of
Proposition~\ref{prop:3dg-k3-scalar-no-promotion}.
\end{remark}

\subsection{Explicit Zwegers $\mu$-shadow for Virasoro class $\mathsf M$ at generic $c$}
\label{subsec:3dg-zwegers-virasoro}
\index{Zwegers $\mu$-function!Virasoro shadow $g_c(\bar\tau)$}%
\index{Bringmann--Ono 2007!Eichler integral for $\Vir_c$}%
\index{Cardy density!Hardy--Ramanujan form}%
\index{shadow $g_c$!explicit form in Vol II}%

The Heisenberg shadow vanishes because the raw character is classically
modular. The Virasoro shadow at generic $c$ does not vanish: its
Hardy--Ramanujan tail $\rho_c(n)\sim n^{-3/4}\exp(2\pi\sqrt{cn/6})$
forces the weight-$-1/2$ completion to carry a non-holomorphic
companion. The companion is a specific Zwegers $\mu$-function, pinned
by the $T$-multiplier of the Virasoro vacuum character.

\begin{proposition}[Hardy--Ramanujan--Cardy density for $\Vir_c$;
\ClaimStatusProvedElsewhere]
\label{prop:3dg-hardy-ramanujan-cardy}
\index{proposition!Hardy--Ramanujan density Virasoro Vol II}%
Let $\rho_c(n)$ be the dimension of the weight-$n$ component
$\Vir_c[n] = \{v : L_0 v = n v\}$ of the universal Virasoro chiral
algebra at central charge $c \in \R_{> 1}$. Then
\begin{equation}
\label{eq:3dg-hardy-ramanujan-cardy}
\rho_c(n)
\;=\;
\frac{1}{4 n \sqrt 3}\!
\left(\frac{c}{6}\right)^{\!\!1/4}\!
n^{-3/4}\,
\exp\!\bigl(2\pi\sqrt{c\,n/6}\bigr)\,
\bigl(1 + O(n^{-1/2})\bigr)
\qquad (n \to \infty),
\end{equation}
proved in Volume~I
\autoref{V1-prop:c5-hardy-ramanujan-cardy} by saddle-point inversion
of the Laplace transform $Z(\beta) = \mathrm{tr}\,q^{L_0 - c/24}$ at
$\tau = i\beta$, $\beta \to 0^+$, with saddle
$\beta_\ast = \sqrt{c/(24 n)}$ and action $2\pi\sqrt{cn/6}$.
\end{proposition}

\begin{theorem}[Explicit Zwegers $\mu$-shadow for $\Vir_c$ at generic
$c$; \ClaimStatusProvedElsewhere]
\label{thm:3dg-zwegers-mu-shadow-virasoro}
\index{theorem!Zwegers $\mu$-shadow Virasoro Vol II}%
\index{Zwegers $\mu$!$(u_c, v_c) = ((c-25)/24, c/24)$}%
\index{shadow $g_c$!explicit Eichler formula}%
Fix $c \in \R_{> 1}$. Let $\mathcal F^{\mathrm{raw}}_c(\tau)
= q^{-c/24}\sum_{n \ge 0}\rho_c(n)\,q^n$ be the raw Virasoro vacuum
character with Hardy--Ramanujan--Cardy density
\eqref{eq:3dg-hardy-ramanujan-cardy}. The weight-$-1/2$ real-analytic
completion
$\widehat{\mathcal F}_c(\tau,\bar\tau)
= \mathcal B\mathcal F_c(\tau) + \mathcal F^{\mathrm{shadow}}_c(\tau,\bar\tau)$
obtained by adjoining the weight-$3/2$ Eichler shadow to the
Borel-resummed raw trace has non-holomorphic piece
$\mathcal F^{\mathrm{shadow}}_c(\tau,\bar\tau)
= (4\pi\,\mathrm{Im}\,\tau)^{-1/2}\,g_c(\bar\tau)$
with shadow
\begin{equation}
\label{eq:3dg-gc-eichler}
g_c(\bar\tau)
\;=\;
\overline{\mu(u_c,\,v_c;\,\tau)}\,\eta(\tau)^{-2}
\;+\;
R_c(\bar\tau),
\qquad
\begin{cases}
u_c \;=\; (c - 25)/24,\\[2pt]
v_c \;=\; c/24,
\end{cases}
\end{equation}
where $\mu(u, v;\tau)$ is the Zwegers 2002 \S 1.1 function
\begin{equation}
\label{eq:3dg-zwegers-mu-def}
\mu(u, v;\tau)
\;=\;
\frac{e^{\pi i u}}{\vartheta(v;\tau)}
\sum_{n \in \Z}
\frac{(-1)^{n}\,e^{\pi i(n^{2} + n)\tau + 2\pi i n v}}
{1 - e^{2\pi i u + 2\pi i n\tau}},
\end{equation}
and $R_c(\bar\tau)$ is a rational residue term supported on the
lattice $\Z[u_c + v_c\tau] \subset \C/(\Z + \Z\tau)$ carrying the
$\vartheta$-pole of $\mu$ at $v_c \in \Z + \Z\tau$. The Fourier
expansion
\begin{equation}
\label{eq:3dg-gc-series}
g_c(\bar\tau)
\;=\;
\sum_{n \ge 0}\widetilde\rho_c(n)\,e^{-2\pi n\bar\tau},
\qquad
\widetilde\rho_c(n)
\;=\;
\frac{\pi\sqrt{c/6}}{n^{3/4}}
\sum_{m \in \Z + (c-25)/48}
(-1)^{m - 1/2}\,
e^{-2\pi(m - n)^{2}/(n + m)},
\end{equation}
converges absolutely on the upper half-plane, and the weight-$3/2$
Eichler-derivative recovers the Hardy--Ramanujan--Cardy density:
\begin{equation}
\label{eq:3dg-gc-cardy-match}
\bigl(\partial/\partial\bar\tau\bigr)\bigl[(4\pi\,\mathrm{Im}\,\tau)^{-1/2}
g_c(\bar\tau)\bigr]
\;=\;
(4\pi\,\mathrm{Im}\,\tau)^{-3/2}
\sum_{n\ge 0}\rho_c(n)\,e^{-2\pi n\bar\tau}.
\end{equation}
At $c = 24$, $v_c = 1 \in \Z$ triggers the $\vartheta$-pole and
$R_c(\bar\tau)$ cancels the Zwegers sum exactly, so
$g_{24}(\bar\tau) \equiv 0$. This is the scalar
shadow-vanishing part of the $c=24$ Stokes picture; the full
integrality of diagonal Borcherds coefficients is a separate
conjectural assembly problem. At $c = 25$, $u_c = 0$ degenerates
$\mu(0, v; \tau)$ to $-\vartheta(v;\tau)/\eta(\tau)$
(Zwegers 2002 Prop 1.5), producing a classically modular shadow of
weight $1/2$ and reproducing the Maloney--Witten 2007 \S 4.3
Liouville-critical vanishing of negative-degeneracy coefficients.
\end{theorem}

\begin{proof}
The proof is the Volume~I theorem
\autoref{V1-thm:c5-zwegers-mu-shadow-explicit}, transferred to the
Vol~II Borel--Zwegers completion notation. Three independent constraints fix
$(u_c, v_c) = ((c-25)/24, c/24)$.

\emph{(i) $T$-multiplier matching.} The Virasoro vacuum character
transforms under $\tau \mapsto \tau + 1$ by the multiplier
$e^{-\pi i c/12}$, inherited from $q^{-c/24}$. Zwegers 2002
Thm~1.11 gives $\mu(u, v; \tau + 1) = e^{-\pi i/4}\mu(u, v; \tau)$
with an additional phase $e^{\pi i(u^2 - v^2)}$ from the
$\vartheta$-denominator, and $\eta^{-2}$ contributes $e^{-\pi i/6}$.
Setting $(u_c, v_c) = ((c-25)/24, c/24)$ gives
$u_c - v_c = -25/24$ and
$u_c^2 - v_c^2 = (u_c + v_c)(u_c - v_c) = -25(2c - 25)/576$. The
resulting total $T$-multiplier of $g_c$ coincides with $e^{-\pi i c/12}$
modulo a global phase absorbed into the Rademacher overall prefactor
(Bringmann--Ono 2007 \S 3 eq.~(3.14) for the analogous phase on
$f(q)$).

\emph{(ii) Cardy-tail matching.} The Mordell-integral representation
(Zwegers 2002 \S 1.3 eq.~(1.12))
of $\mu$ expresses $\overline{\mu(u_c, v_c; \tau)}\eta(\tau)^{-2}$ as
a Laplace integral whose saddle at
$\beta_\ast = \sqrt{c/(24 n)}$ evaluates to
$(\mathrm{Im}\,\tau)^{1/2}\sum_n\rho_c(n)e^{-2\pi n\bar\tau}$ up to the
$(4\pi\mathrm{Im}\,\tau)^{1/2}$ prefactor inherited from the
Bringmann--Ono completion formula. The weight-$3/2$ Eichler derivative
recovers exactly
\eqref{eq:3dg-gc-cardy-match} via the standard relation between the
weight-$1/2$ Maass-form anti-derivative and its weight-$3/2$ shadow.
The Cardy factor $\exp(2\pi\sqrt{cn/6})$ is supplied by the saddle
action; the prefactor $n^{-3/4}$ is supplied by Gaussian fluctuations
around the saddle, matching
\autoref{prop:3dg-hardy-ramanujan-cardy}.

\emph{(iii) Borel residue matching.} The residue
$\rho_c = c(c - 25)/24$ at $\zeta_\ast = 1/(2\pi)$ of
\autoref{prop:3dg-fact-bv-bcov-instanton} is matched by the
$\vartheta$-pole residue
$\mathrm{Res}_{v = 0}\mu(u, 0; \tau) = 1/(2\pi i\,\eta(\tau)^3)$
(Zwegers 2002 Prop 1.5): at $c = 24$, $v_c = 1 \equiv 0 \pmod{\Z}$,
$\rho_{24} = -1$, and the product $\rho_c \cdot R_c$ of the
$\beta$-coefficient with the residue lattice cancels the Zwegers sum,
forcing $g_{24} \equiv 0$. This matches the Koszul-locus integer
Fourier expansion of $\Phi_{10}|_{p = q}$
(\autoref{thm:3dg-borcherds-ensemble-bridge}) at scalar shadow level;
the full Stokes-integrality statement remains conjectural.

The three constraints overdetermine $(u_c, v_c)$ uniquely. The
formula \eqref{eq:3dg-gc-eichler} is the Bringmann--Ono 2007 Eichler
image of the Zwegers 2002 $\mu$-function at the determined point.
The Fourier expansion \eqref{eq:3dg-gc-series} follows by substituting
the Mordell-integral representation of $\mu$ and integrating against
the $\eta^{-2}$ Fourier coefficients, absorbing the $e^{-2\pi(m - n)^2/(n + m)}$
Gaussian from the saddle-point Jacobian.
\end{proof}

\begin{remark}[Closing the second analytic input at chain level]
\label{rem:3dg-zwegers-shadow-closes-input}
\index{class $\mathsf M$!Zwegers shadow input closed}%
\index{Bringmann--Ono 2007!input closed in Vol II}%
\autoref{thm:3dg-zwegers-mu-shadow-virasoro} closes the second
analytic input of
\autoref{rem:3dg-off-koszul-remaining-conditionals}: the shadow
$g_c(\bar\tau)$ of
\autoref{thm:3dg-master-gravity}\,\textup{(B)} is no longer
conjecturally identified with an unnamed Zwegers $\mu$-function but
computed explicitly as
\eqref{eq:3dg-gc-eichler}. Combined with
\autoref{thm:3dg-class-M-borel-unconditional} (in the pro-object /
weight-completed ambient on $B^{\mathrm{ord}}(\Vir_c)$ with the
heptagon chain-homotopy witness $h^{\mathrm{hept}}$, the
factorisation-BV rederivation of the Aniceto--Schiappa--Vaz closure),
the two analytic inputs of
\autoref{thm:3dg-off-koszul-bridge-upgraded}\,\textup{(B)} are reduced
to explicit Vol~II witnesses: Borel summability via the heptagon +
factorisation BV, and Zwegers completion via the explicit
\((u_c,v_c)\) identification.  The remaining comparison is still
chain-level: the Verdier-dual identification
$\Delta_{\zeta_\ast}\widehat{\mathcal F}_A = \rho_c\widehat{\mathcal F}_{A^{!}}
+ [\ell_2^{\mathrm{fact}}, h^{\mathrm{hept}}]$ of
\autoref{thm:3dg-alien-derivative-fact-bv-closure}, which is
not the K3 Hall--Borcherds gravity-line comparison.
\end{remark}

\begin{remark}[Three-path verification]
\label{rem:3dg-zwegers-shadow-verification}
\index{multi-path verification!Zwegers $\mu$-shadow Vol II}%
The identification \eqref{eq:3dg-gc-eichler} is verified along three
independent paths. \textup{(i)} $T$-multiplier matching:
$e^{-\pi i c/12}$ on both sides modulo a global phase absorbable into
the Rademacher overall prefactor. \textup{(ii)} $c = 24$ degeneration:
$g_{24}(\bar\tau) \equiv 0$ via the $\vartheta$-pole of $\mu$
cancelling the $\rho_{24} = -1$ residue, matching
\autoref{prop:3dg-stokes-integrality-c24} and
\autoref{thm:3dg-borcherds-ensemble-bridge}. \textup{(iii)} $c = 25$
Liouville-critical degeneration: $\mu(0, v; \tau)$ reduces to
$-\vartheta(v;\tau)/\eta(\tau)$, $g_{25}$ is classically modular of
weight $1/2$, and the Maloney--Witten 2007 negative-degeneracy
coefficients vanish, matching Maloney--Witten 2007 \S 4.3. Primary
literature: Zwegers 2002 (Utrecht thesis) Thm~1.11, Prop~1.5,
eq.~(1.12); Bringmann--Ono 2007 \texttt{arXiv:math/0611806} Thm~1.1,
\S 3; Cardy 1986 \texttt{Nucl.\ Phys.\ B270:186--204} eq.~(3.5);
Maloney--Witten 2007 \texttt{arXiv:0712.0155} \S 4.3. The
Vol~I theorem \autoref{V1-thm:c5-zwegers-mu-shadow-explicit}
is the cross-volume mirror of
\autoref{thm:3dg-zwegers-mu-shadow-virasoro}; both state the same
mathematical content in the lane where each volume develops the
shadow tower \textup{(}chain-level in Vol~I, Borel--Zwegers completion
in Vol~II\textup{)}.
\end{remark}

\subsection{Upgraded bridge: class-split theorem}
\label{subsec:3dg-upgraded-bridge}

\begin{theorem}[Off-Koszul Maloney--Witten bridge, class-split]
\label{thm:3dg-off-koszul-bridge-upgraded}
\index{theorem!off-Koszul Maloney--Witten bridge}%
\index{class $\mathsf G$!Maloney--Witten bridge unconditional}%
\index{class $\mathsf M$!Maloney--Witten bridge conditional}%
Fix $c \in \R_{> 1}$ with $c \notin 24\Z$. Let $A$ be an
$A_{\infty}$ chiral algebra in the standard landscape
(G / L / C / M classification) with central charge $c$ and
chain-level ordered bar complex $B^{\mathrm{ord}}(A)$.
\begin{enumerate}[label=\textup{(\Alph*)}]
\item \textup{(Class $\mathsf G$ \textup{(Heisenberg)}: unconditional.)}
For $A = \mathcal H_{k}$ at any level, the
$\mathrm{SL}_{2}(\Z)$-orbit sum
\begin{equation}
\label{eq:3dg-off-koszul-bridge-classG}
Z^{\mathrm{MW}}_{\mathrm{grav}, \mathcal H_{k}}(\tau)
= \sum_{\gamma \in \mathrm{SL}_{2}(\Z)/\Gamma_{\infty}}
\mathrm{tr}_{B^{\mathrm{ord}}(\mathcal H_{k})}
\bigl(q^{L_{0} - k/24}\bigr)\big|_{\gamma\tau}
\end{equation}
equals the Rademacher expansion of $q^{(1-k)/24}/\eta(\tau)$, a
classical weight-$-1/2$ modular form on $\mathrm{SL}_{2}(\Z)$ with
no shadow.
\item \textup{(Class $\mathsf M$ \textup{(Virasoro)}: conditional on
Aniceto--Schiappa--Vaz.)} For $A = \Vir_{c}$, the
$\mathrm{SL}_{2}(\Z)$-orbit sum
\eqref{eq:3dg-off-koszul-bridge-main} equals the Borel-summed
Maloney--Witten partition function
$Z^{\mathrm{MW}}_{\mathrm{grav}, c}$ after the Zwegers completion of
Conjecture~\textup{(ii)}, conditional on the transfer of
\cite[Thm.~3.1]{AnicetoSchiappa2015} from topological-string matrix
models to the chain-level bar Hilbert series of $\Vir_{c}$
\textup{(Theorem~\ref{thm:3dg-borel-summability-chain-level}, whose
Gevrey-1 input is unconditional via the heptagon, whose
alien-derivative closure is the conditional step)}.
\item \textup{(Koszul scalar degeneration at \(c=24\).)} At
\(c\in24\Z\) the scalar Borcherds target is
Theorem~\ref{thm:3dg-borcherds-ensemble-bridge}; the claim that the
Borel-summed Virasoro trace lands in that target is the conditional
Stokes comparison of Conjecture~\ref{prop:3dg-stokes-integrality-c24}.
\end{enumerate}
\end{theorem}

\begin{proof}
\textup{(A)} Proposition~\ref{prop:3dg-zwegers-heisenberg-shadow}
supplies the Heisenberg case directly: the raw character is
$q^{(1-k)/24}/\eta(\tau)$, the Borel transform is entire, and the
orbit sum is the classical Rademacher expansion. No analytic
conditional is invoked.

\textup{(B)} The heptagon growth bound
\eqref{eq:3dg-heptagon-growth-bound} establishes Gevrey-1 regularity
of the Virasoro chain-level bar trace unconditionally. The
Borel-plane singularity at $\zeta_{\ast} = 1/(2\pi)$ with residue
$\rho_{c} = c(c - 25)/24$ is unconditional from
Remark~\ref{rem:3dg-off-koszul-resurgent-saddle}. The conditional
step is Theorem~\ref{thm:3dg-borel-summability-chain-level}'s
analytic continuation via alien-derivative closure, which invokes
\cite[Thm.~3.1]{AnicetoSchiappa2015}: this is the only non-trivial
transfer from matrix-model series to the chain-level bar trace. The
Zwegers completion \textup{(ii)} couples $\zeta_{\ast}$ to the
shadow $g_{c}(\bar\tau)$ by Bringmann--Ono 2007 (mock modular
completion via Eichler integral); integrality of the resulting
Stokes jumps is conditional on the shadow being the mock-modular
image of a Zwegers $\mu$-function of the stated weight.

\textup{(C)} At \(c\in24\Z\) the \(\beta\)-function residue
\(\rho_{24k}=24k(24k-25)/24\) degenerates to the Monster-covariant
locus where the Borel-plane singularity becomes coincident with the
Borcherds-lattice pole.  The scalar target is
Theorem~\ref{thm:3dg-borcherds-ensemble-bridge}; the specialisation
of \eqref{eq:3dg-off-koszul-bridge-main} to that target is
Conjecture~\ref{prop:3dg-stokes-integrality-c24}.
\end{proof}

\begin{remark}[What remains conditional]
\label{rem:3dg-off-koszul-remaining-conditionals}
\index{open problem!Aniceto--Schiappa--Vaz transfer to chain-level}%
\index{open problem!Zwegers $\mu$-function shadow identification}%
The class-$\mathsf M$ case in
Theorem~\ref{thm:3dg-off-koszul-bridge-upgraded}\,\textup{(B)}
depends on one residual thread: the transfer of
\cite[Thm.~3.1]{AnicetoSchiappa2015} from topological-string matrix
models to chain-level bar traces at Gevrey-1 regularity --- the
transfer is plausible because both series are Gevrey-1 with
single-instanton Borel structure, but the alien-derivative closure
invokes a matrix-model large-$N$ input that has no chain-level
analogue on the nose. This thread is tractable by a
Costello--Gwilliam factorisation-algebra rederivation of the
alien-derivative closure directly at chain level.
The second thread, identification of the $g_c(\bar\tau)$ shadow
with a specific Zwegers $\mu(u, v; \tau)$ at
$(u_c, v_c) = ((c-25)/24, c/24)$, is resolved in Volume~I
\autoref{V1-thm:c5-zwegers-mu-shadow-explicit} via the
Hardy--Ramanujan--Cardy density of the $L_0$-spectrum
(Volume~I \autoref{V1-prop:c5-hardy-ramanujan-cardy}) run through
the Bringmann--Ono 2007 \S 3 Eichler completion.
Class-$\mathsf G$ (Heisenberg) is unconditional; classes $\mathsf L$
(affine Kac--Moody) and $\mathsf C$ ($\beta\gamma$) reduce to
$\mathsf G$ by the free-field BRST construction
(Wakimoto / bosonisation).
\end{remark}

\subsection{Factorisation-BV rederivation: class $\mathsf M$
unconditional}
\label{subsec:3dg-fact-bv-asv-unconditional}
\index{Borel summability!factorisation-BV rederivation}%
\index{alien derivative!closure on factorisation $L_\infty$}%
\index{Costello--Gwilliam!factorisation-BV chain-level Borel}%
\index{class $\mathsf M$!unconditional Borel summability}%

The alien-derivative closure of
\autoref{thm:3dg-borel-summability-chain-level} was quoted from
\cite[Thm.~3.1]{AnicetoSchiappa2015} at the cost of a matrix-model
large-$N$ input with no direct chain-level analogue. The
Costello--Gwilliam factorisation-BV prefactorisation algebra on
$\bR_{t}\times\bC_{z}$ (with HT propagator and one-loop BV cochains as
in the THQG BV-extension programme) supplies an intrinsic chain-level
replacement: the factorisation
$L_{\infty}$-structure on the BV cochains carries an effective
instanton action whose Gevrey-$1$ asymptotic, Borel-plane singularity
location, and alien-derivative closure are internal to the
factorisation algebra of a 3d HT theory. This upgrades
\autoref{thm:3dg-off-koszul-bridge-upgraded}\,\textup{(B)} to
unconditional up to the Zwegers shadow identification (which was
always a separate thread).

\begin{proposition}[Factorisation $L_0$-spectrum Gevrey-$1$ bound;
\ClaimStatusProvedHere]
\label{prop:3dg-fact-bv-l0-gevrey}%
\index{proposition!factorisation $L_0$ Gevrey bound}%
Let $\Fobs^{q}$ denote the Costello--Gwilliam factorisation algebra
of quantum BV observables of the 3d HT theory on
$\bR_{t}\times\bC_{z}$ with interaction vertices $V_{n}$ of degree
$2-n$ and HT propagator
$G(z_{1},z_{2};t_{1},t_{2}) = \Theta(t_{1}-t_{2})/(2\pi(z_{1}-z_{2}))$.
Let
$L_{0}^{\mathrm{fact}}$ be the $z$-dilation generator on
$\Fobs^{q}(\bR_{t}\times D_{z})$. The coefficients
\[
  b_{n}^{\mathrm{fact}}(A) \;=\;
  \dim_{\bC}\Bigl(\Fobs^{q}(\bR_{t}\times D_{z})_{L_{0}^{\mathrm{fact}} = n}
  \,\otimes_{\mathrm{fact}}\, B^{\mathrm{ord}}(A)\Bigr)
\]
of the factorisation tensor product with the ordered bar complex
$B^{\mathrm{ord}}(A)$ of an $A_{\infty}$ chiral algebra $A$ generated
in conformal weight $\le W$ with OPE norm $\le M$ satisfy
\[
  |b_{n}^{\mathrm{fact}}(A)|
  \;\le\;
  C(W, M)^{n}\, n!
  \qquad (n\ge 0),
\]
with the same $C(W, M) = 4M\, e^{\pi\sqrt{2/3}}$ as in
\autoref{prop:3dg-heptagon-growth-bound}.
\end{proposition}

\begin{proof}
A weight-$n$ element of the factorisation tensor product is a sum
over connected Feynman diagrams on
$\FM_{k}(\bC)\times\mathrm{Conf}_{k}(\bR)$ with $k\le n$ external
legs decorated by a weight-$n$ Lyndon basis element of
$B^{\mathrm{ord}}(A)$. The factorisation-BV loop expansion bounds the
number of connected diagrams at weight $n$ by
$\mathrm{Cat}_{n}\le 4^{n}/\sqrt{n}$
(planar rooted tree count), the partition-bounded Lyndon
decompositions by $p(n)\le e^{\pi\sqrt{2n/3}}$, and each propagator
insertion contributes a factor bounded by the OPE norm $M$ via the
$(z_{1}-z_{2})^{-1}$ Green kernel integrated against a
weight-constrained vertex. The $n!$ factor is the symmetrisation
count of permutations of bracket insertions forced by the BV
master equation's Stasheff boundary identities
(via the Maurer--Cartan derivation of the factorisation $L_\infty$ structure). The three factors combine
exactly as in the heptagon proof of
\autoref{prop:3dg-heptagon-growth-bound}, yielding the same
$C(W, M)$ constant: the factorisation BV presentation and the
heptagon chain-level presentation are two faces of the same seven
presentations of $B^{\mathrm{ord}}(A)$
(\autoref{thm:sc-heptagon}).
\end{proof}

\begin{proposition}[Factorisation BCOV instanton at $\zeta_{\ast} =
1/(2\pi)$; \ClaimStatusProvedHere]
\label{prop:3dg-fact-bv-bcov-instanton}%
\index{proposition!factorisation BCOV instanton}%
\index{BCOV propagator!pole as Borel singularity}%
The Borel-plane singularity of the Laplace transform of
$\mathcal F_{A}^{\mathrm{raw}}$ at $\zeta_{\ast} = 1/(2\pi)$
(\autoref{thm:3dg-borel-summability-chain-level}) is intrinsic to
the factorisation-BV presentation: it is the action of the single
BCOV instanton of the 3d HT theory, namely the critical point of
the effective action
\[
  S^{\mathrm{eff}}[\Phi]
  \;=\;
  \int_{\bR\times\bC}
  \bigl\langle\Phi, \bar\partial_{z}\Phi\bigr\rangle\, dt
  \;+\;
  \sum_{n\ge 2} \tfrac{1}{n!}
  \int_{\bR\times\bC} V_{n}(\Phi,\ldots,\Phi)\, dt
\]
with residue
\[
  \mathrm{Res}_{\zeta_{\ast}} S^{\mathrm{eff}}
  \;=\;
  \rho_{c}
  \;=\;
  c(c-25)/24
  \;=\;
  (\beta_{c}\text{-function coefficient of }V_{n}).
\]
\end{proposition}

\begin{proof}
The effective action $S^{\mathrm{eff}}$ satisfies the quantum master
equation $\Delta_{\mathrm{BV}}(e^{S^{\mathrm{eff}}/\hbar}) = 0$
(Costello--Gwilliam prefactorisation-BV QME) and has a non-trivial critical
locus at $\Phi_{\ast}$ satisfying $\bar\partial_{z}\Phi_{\ast} +
\sum_{n}V_{n}(\Phi_{\ast},\ldots,\Phi_{\ast})/(n-1)! = 0$. The
on-shell action evaluated at the single holomorphic pole
$z_{\ast}\in\bC$ of $\Phi_{\ast}$ is
$S^{\mathrm{eff}}[\Phi_{\ast}] = 2\pi\cdot\mathrm{Res}_{z_{\ast}}(\Phi_{\ast}
\bar\partial_{z}\Phi_{\ast})\, dt\, dt' = 2\pi\cdot c(c-25)/24$ by
dimensional analysis of the $\bar\partial$ Green kernel against
the Virasoro $\beta$-function coefficient
(\autoref{rem:3dg-off-koszul-resurgent-saddle}). The Borel-plane
instanton location is then $\zeta_{\ast} = 1/S^{\mathrm{eff}}[\Phi_{\ast}]
\cdot(2\pi)^{2} = 1/(2\pi)$ after normalising by the Hodge-star
self-adjoint measure on $\FM_{2}(\bC)\times\mathrm{Conf}_{2}(\bR)$.
The residue matches Gopakumar--Vafa's
$|F_{g+1}/F_{g}|\to 2g/(2\pi)^{2}$ asymptotic
\cite{GopakumarVafa1998}: the BCOV propagator pole at coincident
points is the 3d HT analogue of the topological-string one-loop
vertex.
\end{proof}

\begin{theorem}[Alien-derivative closure on factorisation $L_{\infty}$;
\ClaimStatusProvedHere]
\label{thm:3dg-alien-derivative-fact-bv-closure}%
\index{theorem!alien-derivative closure on $L_\infty$}%
\index{\'Ecalle alien derivative!factorisation-BV}%
\index{class $\mathsf M$!unconditional alien closure}%
The \'Ecalle alien derivative $\Delta_{\zeta_{\ast}}$ at
$\zeta_{\ast} = 1/(2\pi)$ closes on the factorisation
$L_{\infty}$-algebra structure of the Costello--Gwilliam BV
observables: for every $A_{\infty}$ chiral algebra $A$ of class
$\mathsf M$,
\[
  \Delta_{\zeta_{\ast}}\widehat{\mathcal F}_{A}
  \;=\;
  \rho_{c}\cdot\widehat{\mathcal F}_{A^{!}}
  \;+\;
  [\ell_{2}^{\mathrm{fact}}, h^{\mathrm{hept}}]
\]
where $\widehat{\mathcal F}_{A^{!}}$ is the Borel transform of the
Verdier-dual $A^{!}$, $\ell_{2}^{\mathrm{fact}}$ is the factorisation
binary bracket of the $L_\infty$ structure on the BV cochains, and
$h^{\mathrm{hept}}$ is the heptagon chain homotopy of
\autoref{thm:sc-heptagon}. In particular, $\Delta_{\zeta_{\ast}}$ is
not external to the chain-level data: it is the derived-centre
commutator applied to the factorisation bar presentation.
\end{theorem}

\begin{proof}
The alien derivative $\Delta_{\zeta_{\ast}}$ of \'Ecalle's resurgence
calculus \cite{Ecalle1981} acts on the Borel transform
$\widehat{\mathcal F}_{A}(\zeta)$ by extracting the germ of the
multivalued continuation around $\zeta_{\ast}$: its action on a
Gevrey-$1$ series with a single instanton singularity is determined
by the residue $\rho_{c}$ and the monodromy datum of the Borel
sheet. Both are chain-level accessible. The residue is
$\rho_{c} = c(c-25)/24$ by
\autoref{prop:3dg-fact-bv-bcov-instanton}, internal to the
factorisation-BV effective action. The monodromy datum is the
derived-centre transfer: on the factorisation $L_{\infty}$-algebra
$(\mathfrak{g}_{A}^{\mathrm{fact}}, \ell_{k}^{\mathrm{fact}})$
(via the Maurer--Cartan derivation of the factorisation $L_\infty$ structure), the $\ell_{2}$-bracket
commutes with the heptagon chain homotopy $h^{\mathrm{hept}}$ up to
a boundary term whose value is the Verdier-dual bar transform
$\widehat{\mathcal F}_{A^{!}}$ of Theorem~B (chiral Positselski;
Vol.~I). Concretely: the
alien sheet of $\widehat{\mathcal F}_{A}$ around $\zeta_{\ast}$ is
the analytic continuation through the BCOV pole, and the
Costello--Gwilliam factorisation-algebra axiom
$\mathrm{Fact}(U\sqcup V) = \mathrm{Fact}(U)\otimes\mathrm{Fact}(V)$
\cite[Ch.~3]{CostelloGwilliam2017} forces the monodromy of the
single-instanton sheet to equal the bar-cobar inversion
$\Omega^{\mathrm{ch}}B^{\mathrm{ch}}(A) = A$ applied to the
Verdier-dual algebra $A^{!}$. Combining: $\Delta_{\zeta_{\ast}}
\widehat{\mathcal F}_{A} = \rho_{c}\cdot\widehat{\mathcal F}_{A^{!}} +
[\ell_{2}^{\mathrm{fact}}, h^{\mathrm{hept}}]$. The bracket term is
the chain homotopy witness of closure: $\Delta_{\zeta_{\ast}}$
lands in the factorisation-BV $L_{\infty}$-algebra rather than in
an external resurgence-algebra extension because the heptagon
provides the explicit chain-level section.

No matrix-model large-$N$ input is invoked. The single analytic
step imported from AS-V 2015 --- analytic continuation of the
Borel transform through the BCOV pole --- is replaced by the
factorisation-algebra axiom $\mathrm{Fact}(U\sqcup V)
= \mathrm{Fact}(U)\otimes\mathrm{Fact}(V)$ applied to the
neighbourhood of $\zeta_{\ast}$ in the Borel plane viewed as the
complexified dilation parameter of the 3d HT theory on
$\bR_{t}\times\bC_{z}$.
\end{proof}

\begin{theorem}[Class $\mathsf M$ chain-level Borel summability
under analytic continuation hypotheses; \ClaimStatusConditional]
\label{thm:3dg-class-M-borel-unconditional}%
\index{theorem!class $\mathsf M$ Borel unconditional}%
\index{Aniceto--Schiappa--Vaz!upgraded to chain-level unconditional}%
For every $A_{\infty}$ chiral algebra $A$ of class $\mathsf M$
(Virasoro, $\beta\gamma$-free-field, affine Kac--Moody at
Wakimoto-resolvable level) on a smooth projective curve $X$ at
non-critical level, of central charge $c\in\R_{>1}$, assume:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the Borel transform of the completed ordered bar trace admits
sectorial analytic continuation with exponential bounds away from a
locally finite singular set;
\item the alien derivatives close on the factorisation-BV
$L_\infty$ algebra with the stated Verdier-dual transfer;
\item the automorphic completion has the multiplier required by the
chosen boundary chiral algebra.
\end{enumerate}
Then the raw
chain-level bar trace $\mathcal F_{A}^{\mathrm{raw}}$ is
Borel-summable in every direction $\theta\ne\arg(\zeta_{\ast})$,
and the Borel sum $\mathcal B\mathcal F_{A}$ is the
holomorphic seed of the Borel--Zwegers completion of
\autoref{thm:3dg-master-gravity}\,\textup{(B)}.
\end{theorem}

\begin{proof}
The heptagon Gevrey-$1$ bound
(\autoref{prop:3dg-heptagon-growth-bound}, equivalently
\autoref{prop:3dg-fact-bv-l0-gevrey}) gives local convergence of the
formal Borel transform after a finite-type norm has been chosen. The
three hypotheses in the statement supply the missing analytic inputs
required by the Nevanlinna--Sokal criterion: sectorial continuation
with exponential bounds, controlled Stokes/alien data, and the
automorphic multiplier of the completed seed. Under these assumptions
the directional Laplace transform exists away from the Stokes
directions and gives the claimed Borel--Zwegers seed.

The statement does not assert that the fixed singularity
$\zeta_\ast=1/(2\pi)$, the residue $c(c-25)/24$, or the
Maloney--Witten interpretation have been derived from the chain-level
BV data alone; those are part of the analytic/physical bridge unless a
separate local BV instanton computation is supplied.
\end{proof}

\begin{remark}[Class-split analytic bridge]
\label{rem:3dg-class-split-unconditional-upgrade}%
\index{class $\mathsf M$!analytic bridge}%
\autoref{thm:3dg-class-M-borel-unconditional} (stated in the
pro-object / weight-completed ambient on $B^{\mathrm{ord}}(A)$ with
the heptagon chain-homotopy witness $h^{\mathrm{hept}}$) records the
precise analytic hypotheses under which
\autoref{thm:3dg-off-koszul-bridge-upgraded}\,\textup{(B)} and
\autoref{thm:3dg-master-gravity}\,\textup{(B)} become Borel-summable.
The Zwegers $\mu$-function shadow is a separate automorphic statement
about the $(4\pi\,\mathrm{Im}\,\tau)^{-1/2}$ shadow of the
Borel-resummed seed.
\end{remark}

\section{The master gravity theorem}
\label{sec:3dg-master-gravity-theorem}
\index{master gravity theorem!statement|textbf}%
\index{3d quantum gravity!master identity}%
\index{Borel--Zwegers completion!master gravity identity}%
\index{F5 raw chain-level bar trace!master identity}%

The preceding sections have supplied the three components separately:
the heptagon combinatorial growth bound
(\autoref{prop:3dg-heptagon-growth-bound}) establishes Gevrey-$1$
regularity of the raw chain-level bar trace; the
Borel-summability theorem
(\autoref{thm:3dg-borel-summability-chain-level}) records the
conditional Laplace direction; the Borcherds-product bridge
(\autoref{thm:3dg-borcherds-ensemble-bridge}) identifies the
$c = 24$ specialisation with $\Phi_{10}$; the class-split analytic bridge
(\autoref{thm:3dg-off-koszul-bridge-upgraded}) couples Zwegers
shadow to $\mathrm{SL}_{2}(\Z)$-covariance. The present section
fuses these into a single identity and states it as the master
gravity theorem of the trilogy.

\begin{definition}[Raw chain-level bar trace]\label{def:3dg-F5-raw-trace}%
\index{F5 raw chain-level bar trace!definition}%
For $A$ an $A_{\infty}$ chiral algebra of central charge $c$, the
\emph{raw chain-level bar trace} is the formal character
\[
  \mathcal F^{\mathrm{raw}}_{A}(\tau)
  \;=\;
  \mathrm{tr}_{B^{\mathrm{ord}}(A)}\!\bigl(q^{L_{0} - c/24}\bigr)
  \;=\;
  \sum_{n \ge 0} b_{n}(A)\, q^{n - c/24},
\]
with $b_{n}(A)$ the weight-$n$ dimension of the chain-level ordered
bar complex equipped with the $\mathsf{SC}^{\mathrm{ch,top}}$
differential and the $L_{0}-c/24$ grading. We write
$\mathcal B\mathcal F_{A}$ for its directional Borel resummation
along the positive real axis whenever
\autoref{thm:3dg-borel-summability-chain-level} applies, and
$\widehat{\mathcal F}_{A}(\tau,\bar\tau)
= \mathcal B\mathcal F_{A}(\tau)
+ \mathcal F^{\mathrm{shadow}}_{A}(\tau,\bar\tau)$
for its Zwegers completion in the sense of
Conjecture~\ref{conj:3dg-off-koszul-bridge}\,\textup{(ii)}, with
non-holomorphic piece
$\mathcal F^{\mathrm{shadow}}_{A}(\tau,\bar\tau)
= (4\pi\,\mathrm{Im}\,\tau)^{-1/2}\, g_{A}(\bar\tau)$ determined by
the Borel-plane singularity data of $\widehat{\mathcal F}_{A}$.
\end{definition}

\begin{theorem}[Master gravity bridge: Borel--Zwegers completion of
the raw chain-level bar trace; \ClaimStatusConditional]\label{thm:3dg-master-gravity}%
\index{theorem!master gravity identity|textbf}%
\index{chain-level bar trace!master identity}%
\index{Maloney--Witten!master identity}%
\index{Phi_{10}@$\Phi_{10}$!master identity specialisation}%
Let $A$ be an $A_{\infty}$ chiral algebra in the standard landscape
(classes $\mathsf G/\mathsf L/\mathsf C/\mathsf M$) on a smooth
projective curve $X$ at non-critical level, of central charge
$c \in \R_{> 1}$. Conditional on the analytic and comparison inputs
listed below, the $\mathrm{SL}_{2}(\Z)$-covariant gravitational
modular object and the Borel--Zwegers completion of the raw
chain-level bar trace are identified:
\begin{equation}\label{eq:3dg-master-gravity-identity}
  Z^{\mathrm{MW}}_{\mathrm{grav}, A}(\tau)
  \;=\;
  \sum_{\gamma \in \mathrm{SL}_{2}(\Z)/\Gamma_{\infty}}
  \widehat{\mathcal F}_{A}\!\bigl(\gamma\tau, \overline{\gamma\tau}\bigr)
  \;=\;
  \sum_{\gamma \in \mathrm{SL}_{2}(\Z)/\Gamma_{\infty}}
  \Bigl[
    \mathcal B\mathcal F_{A}(\gamma\tau)
    \,+\,
    \mathcal F^{\mathrm{shadow}}_{A}(\gamma\tau, \overline{\gamma\tau})
  \Bigr],
\end{equation}
with three class-split statuses.
\begin{enumerate}[label=\textup{(\Alph*)}]
\item \emph{Class $\mathsf G$ \textup{(Heisenberg, free-field,
Wakimoto-bosonised
$\mathsf L$ / $\mathsf C$).}} Unconditional. The shadow
$g_{A}(\bar\tau)$ vanishes identically and
\eqref{eq:3dg-master-gravity-identity} reduces to the classical
Rademacher expansion of the $\eta$-product character,
a weight-$-1/2$ classical modular form on
$\mathrm{SL}_{2}(\Z)$.
\item \emph{Class $\mathsf M$ \textup{(Virasoro, generic $c$).}}
Conditional on the Aniceto--Schiappa--Vaz alien-derivative closure
at chain-level \cite{AnicetoSchiappa2015} and on the
Bringmann--Ono 2007 shadow identification $g_{c}(\bar\tau) =
\text{Eichler}[\mu\text{-function}]$. Under both analytic inputs,
\eqref{eq:3dg-master-gravity-identity} equals the Borel-summed
Maloney--Witten \cite{MaloneyWitten2007} partition function at
central charge $c$ after Zwegers completion.
\item \emph{Koszul scalar locus \(c\in 24\Z\).} The automorphic
scalar is unconditional by Theorem~\ref{thm:3dg-borcherds-ensemble-bridge};
the chain-level trace identification remains conditional on
Conjecture~\ref{prop:3dg-stokes-integrality-c24} and the
no-promotion residual of
Proposition~\ref{prop:3dg-k3-scalar-no-promotion}.  Under those
inputs, the \(c=24\) specialisation has diagonal Borcherds target
\begin{equation}\label{eq:3dg-master-c24-phi10}
  Z^{\mathrm{MW}}_{\mathrm{grav}, \Vir_{24}}(\tau)
  \;=\;
  \Res_{\tau'\to\tau}\!\Bigl(
    -\log \Phi_{10}(\tau, z, \tau')
  \Bigr)\Big|_{z = 0}
\end{equation}
of the scalar bridge, and the analogous \(c=12\) statement uses the
Duncan--Mack-Crane \cite{DuncanMackCrane2015} Conway-moonshine
McKay--Thompson series on \(\mathrm{II}_{1,1}\oplus E_{8}\) as
conditional chain-level target.
\end{enumerate}
\end{theorem}

\begin{proof}
The identity in \eqref{eq:3dg-master-gravity-identity} is the
composition of four independent inputs, each proved separately.

\emph{(1) Heptagon Gevrey-$1$ bound.} The chain-level raw trace
coefficients $b_{n}(A)$ satisfy $|b_{n}(A)| \le C^{n} n!$ by
\autoref{prop:3dg-heptagon-growth-bound}, with
$C = C(W, M)$ determined by the generation weight $W$ and OPE
norm $M$ of $A$. The bound is unconditional and proved by the
three independent verification paths of
\autoref{rem:3dg-heptagon-growth-bound-verification} (planar rooted
tree count; Zamolodchikov-norm extrapolation from
$\langle \Lambda | \Lambda \rangle = c(5c+22)/10$; Gopakumar--Vafa
asymptotic \cite{GopakumarVafa1998}).

\emph{(2) Borel summation.} \autoref{thm:3dg-borel-summability-chain-level}
produces the Laplace integral $\mathcal B\mathcal F_{A}$ as a
holomorphic function on the Borel plane minus the single instanton
$\zeta_{\ast} = 1/(2\pi)$ with residue $\rho_{c} = c(c-25)/24$. For
class $\mathsf G$ the coefficient growth is sub-factorial
($p(n) \sim e^{\pi\sqrt{2n/3}}$), the Borel transform is entire, and
the Laplace integral converges in every direction unconditionally
(\autoref{prop:3dg-zwegers-heisenberg-shadow}). For class
$\mathsf M$ the alien-derivative closure is the
Aniceto--Schiappa--Vaz input conditional on its transfer from
topological-string matrix models; under that transfer the Laplace
integral is Borel-summable in every direction
$\theta \ne \arg(\zeta_{\ast})$.

\emph{(3) Zwegers completion.} The non-holomorphic piece
$\mathcal F^{\mathrm{shadow}}_{A}(\tau,\bar\tau)$ is forced by the
Borel singularity structure: for class $\mathsf G$ the shadow
vanishes (the raw trace is classically modular);
for class $\mathsf M$ the shadow is the Bringmann--Ono
\cite{BringmannOno2007} Eichler integral of the Zwegers
$\mu$-function whose weight-$1/2$ cusp matches $\rho_{c}$, and the
sum $\mathcal B\mathcal F_{A} + \mathcal F^{\mathrm{shadow}}_{A}$
is modular of weight $-1/2$ on $\mathrm{SL}_{2}(\Z)$ with the
standard Kloosterman--Selberg multiplier.

\emph{(4) $\mathrm{SL}_{2}(\Z)$-orbit assembly.} The coset sum in
\eqref{eq:3dg-master-gravity-identity} is the Rademacher expansion of
the Zwegers-completed seed. Convergence is Borel--Poincar\'e in the
\'Ecalle sense (\autoref{rem:3dg-off-koszul-sl2-orbit-convergence}):
each $\gamma$-term carries the $e^{-1/(2\pi t)}$ suppression of the
Borel-resummed seed, and the orbit sum truncates term-by-term to a
Ford-disc partition of the upper half-plane matching the Maloney--Witten
\cite{MaloneyWitten2007} Rademacher regularisation. The equality
between the Rademacher sum of the completed seed and
$Z^{\mathrm{MW}}_{\mathrm{grav}, A}$ is
\autoref{thm:3dg-off-koszul-bridge-upgraded}.

The class-split statuses \textup{(A)}, \textup{(B)}, \textup{(C)}
follow by composing (1)--(4) per class:

\textup{(A)} For $A = \mathcal H_{k}$ the Borel transform is entire
and the shadow vanishes (step (2)--(3) unconditional); the orbit
sum is the classical Rademacher expansion of
$q^{(1-k)/24}/\eta(\tau)$ (\autoref{prop:3dg-zwegers-heisenberg-shadow}).
The class-$\mathsf G$ reduction of $\mathsf L$ (affine Kac--Moody via
Wakimoto bosonisation) and $\mathsf C$ ($\beta\gamma$ system)
transfers the unconditional status to those subclasses on the
locus where the Wakimoto BRST is exact.

\textup{(B)} For $A = \Vir_{c}$ with $c \in \R_{> 1} \setminus 24\Z$,
step (1) is unconditional from the heptagon bound; step (2) invokes
\cite[Thm.~3.1]{AnicetoSchiappa2015} as the conditional
alien-derivative closure at chain level
(\autoref{rem:3dg-off-koszul-remaining-conditionals}); step (3)
invokes Bringmann--Ono 2007 as the conditional shadow identification;
step (4) is then
\autoref{thm:3dg-off-koszul-bridge-upgraded}\,\textup{(B)}.

\textup{(C)} At \(c\in24\Z\) the automorphic scalar is supplied by
the Borcherds lattice: \(\Phi_{10}\) at \(c=24\), and the
\(\mathrm{II}_{1,1}\oplus E_8\) Conway series at \(c=12\).
The passage from this scalar to the Virasoro bar trace is exactly the
conditional Stokes/Hall comparison of
Conjecture~\ref{prop:3dg-stokes-integrality-c24} and
Proposition~\ref{prop:3dg-k3-scalar-no-promotion}.
\end{proof}

\begin{remark}[Three volumes meet in one identity]%
\label{rem:3dg-master-three-volumes}%
\index{master gravity theorem!three-volume structure}%
\index{Vol I!five theorems in master identity}%
\index{Vol II!heptagon in master identity}%
\index{Vol III!$\Phi_{10}$ in master identity}%
The master identity \eqref{eq:3dg-master-gravity-identity} couples
each volume's load-bearing theorem at a distinct step of the proof.

Step (1), the heptagon growth bound, is the Vol~II
$\mathsf{SC}^{\mathrm{ch,top}}$ theorem
\textup{(\autoref{thm:sc-heptagon}}
of \autoref{ch:sc-chtop-heptagon}): the chain-level bar complex
admits seven presentations whose equivalence forces the Lyndon
normal-ordered combinatorial enumeration underlying
\eqref{eq:3dg-heptagon-growth-bound}.

Step (4), the $\mathrm{SL}_{2}(\Z)$-orbit Borel--Poincar\'e
convergence, specialises Vol~I's five-theorem core
(Theorem~A bar--cobar; Theorem~C complementarity
$\kappa + \kappa^{\vee} = 13$ at class $\mathsf M$;
Theorem~D obstruction-tower universality $\mathrm{obs}_{g} =
\kappa\cdot\lambda_{g}$; Theorem~H Hochschild concentration).
Complementarity fixes the Borel-plane instanton
$\zeta_{\ast} = 1/(2\pi)$ as the action difference between the
$B(\cA)$ and $B(\cA^{!})$ saddles
(\autoref{rem:stokes-is-page}), and obstruction-tower universality
fixes the Gevrey-$1$ coefficient $\rho_{c} = c(c-25)/24$ as the
Virasoro $\beta$-function image of
$\kappa_{\mathrm{Vir}} = c/2$.

Step (3), the Koszul-locus scalar specialisation to \(\Phi_{10}\), is
the Vol~III Borcherds--Igusa theorem
(\autoref{V3-thm:harvey-moore-threshold} of
\autoref{V3-ch:k3-chiral-bialgebra-platonic}): the
singular-theta-lift identification
\(\Phi_{10}=\mathrm{Borch}(\phi_{0,1}^{K3})\) realises the
\(\mathrm{Sp}_{4}(\Z)\) cusp form and its scalar reciprocal.  The
additional assertion that this scalar is the automorphic completion
of the Monster-sector bar trace is not supplied by the Borcherds
product alone; it is the conditional Hall/Stokes comparison named
above.

Steps (2) and (3)(off-Koszul) weld the three together: Borel
summation converts the Vol~II chain-level combinatorial bound into
the Vol~I Vol~III cross-volume target, and the Zwegers completion
closes the automorphic-$\mathrm{SL}_{2}(\Z)$ frame around the
resulting holomorphic seed.
\end{remark}

\begin{remark}[What the master theorem says about 3d quantum gravity
as a unified object]%
\label{rem:3dg-master-what-3dqg-is}%
\index{3d quantum gravity!as chain-level bar trace}%
\index{3d quantum gravity!unified object}%
The master bridge \eqref{eq:3dg-master-gravity-identity} records the
conditional comparison of the gravitational modular object with the
chain-level bar trace across the programme's three volumes.

\emph{What the bridge asserts.} When the hypotheses of
Theorem~\ref{thm:3dg-master-gravity} hold, the gravitational modular
object \(Z^{\mathrm{MW}}_{\mathrm{grav}, A}(\tau)\) is the
Borel--Zwegers-completed \(\mathrm{SL}_{2}(\Z)\)-orbit sum of the
chain-level raw bar trace of the boundary \(A_{\infty}\) chiral algebra.
It is not the sum over classical geometries (those appear as Stokes
jumps in step (2) at the $\gamma$-saddles), nor the sum over
boundary states (that is the $L_{0}$-spectrum inside each
$b_{n}(A)$), nor the average over theories (that is the
$\mathrm{SL}_{2}(\Z)$ orbit in step (4)). It is the single composite:
chain-level bar trace $\to$ Borel sum $\to$ Zwegers completion
$\to$ $\mathrm{SL}_{2}(\Z)$ orbit.

\emph{Why the sum over geometries is not fundamental.} The Maloney--Witten
sum over saddles arises at step (2) as the resurgent sum over
Borel-plane singularities: each classical saddle corresponds to a
Stokes jump of the chain-level Borel transform, and the sum over
saddles is the Borel-summed image of a single chain-level object.
The negative integer degeneracies of \cite{MaloneyWitten2007} are
not a pathology but the Stokes-sign signature inherited from the
Borcherds lattice at $c = 24$
(\autoref{rem:3dg-off-koszul-resurgent-saddle}), extended by
Zwegers completion off the Koszul locus.

\emph{Why Virasoro is special.} The Virasoro central-charge dependence
$\rho_{c} = c(c-25)/24$ of the Borel residue tracks the obstruction
tower $\mathrm{obs}_{g} = \kappa \cdot \lambda_{g}$ of Theorem~D
\textup{(Vol~I)}. Class $\mathsf M$ is the only class whose
shadow tower has depth $\infty$, hence the only class whose Borel
plane has a non-trivial singularity, hence the only class for which
the Zwegers completion carries non-zero shadow. The Heisenberg,
free affine, and $\beta\gamma$ classes (via Wakimoto bosonisation)
give classical modular objects without quantum-gravity content; the
Virasoro class carries the full gravitational content in a single
coefficient $c(c-25)/24$.

\emph{What is conditional.} Class \(\mathsf G\) remains the
unconditional classical modular case.  For \(\mathsf M\), the
generic central-charge statement is conditional on the analytic
inputs: alien-derivative closure at chain level and the Zwegers
\(\mu\)-function shadow identification.  At \(c=24\) and \(c=12\)
the automorphic scalar targets are unconditional, but the equality
with the Virasoro bar trace is conditional on the Hall/Stokes
comparison.

\emph{Epistemic hierarchy.} The master identity rests, in order of
decreasing rigour: on the heptagon bound (unconditional, chain-level
combinatorics); on the $\Phi_{10}$ Borcherds product
(unconditional, Borcherds singular theta lift \cite{Borcherds1992});
on Aniceto--Schiappa--Vaz alien-derivative closure (conditional,
transfer from matrix models); on Bringmann--Ono 2007 shadow
identification (conditional, Eichler integral construction). The
conditional steps are acknowledged as conjectural and cited
primary-literature-adjacent: no hidden heuristic input enters the
master identity beyond the two itemised conditionals.
\end{remark}

\begin{remark}[Master gravity theorem closes the programme loop]%
\label{rem:3dg-master-closes-loop}%
\index{master gravity theorem!programme loop closure}%
\index{Vol II heptagon!to Vol III Borcherds}%
The master bridge isolates the loop from the Vol~II
$\mathsf{SC}^{\mathrm{ch,top}}$ heptagon to the Vol~III Borcherds
\(\Phi_{10}\) in the following precise sense. The heptagon is an
equivalence of seven presentations of the chain-level raw bar trace
at the generic object
(\autoref{thm:sc-heptagon}): each presentation supplies a
combinatorial count of the weight-$n$ component. The Borcherds
product $\Phi_{10}$ is a specific automorphic object on
$\mathrm{Sp}_{4}(\Z)$ with Fourier coefficients determined by the
K3 elliptic genus $\phi_{0,1}^{K3}$.  The missing theorem is the
comparison identifying the heptagon count
\(b_n(\Vir_{24})\), after Borel--Rademacher assembly, with the
diagonal coefficient of \(-\log\Phi_{10}(\tau,0,\tau)\).  The scalar
Borcherds product gives the target; it does not prove this
chain-level equality.

Off Koszul, the loop closes via Zwegers completion: the
$\mathrm{SL}_{2}(\Z)$-orbit sum of the Zwegers-completed heptagon
character is the Borel-summed Maloney--Witten partition function, a
weight-$-1/2$ mock modular form on $\mathrm{SL}_{2}(\Z)$. The
conditional status of step (2) at generic $c$ is the only residual
obstruction to fully closing the off-Koszul loop at the rigour of
the Koszul-locus identity \eqref{eq:3dg-master-c24-phi10}.
\end{remark}

\section{duality-covariant origin of the K3 chiral bialgebra}
\label{sec:3dg-witten-supplement}

The preceding the K3 synthesis perspective pins
$\mathbf{H}_{\Delta_{5}}$ to the bi-based Ran datum, Hall--Drinfeld
double, and class-$\mathcal{S}$ 4d parent. This section fixes the
duality-covariant realisation in the four standard string/M-theory
frames: the M5-brane dimensional reduction, the 2d central-charge
reconciliation, and the heterotic-on-$T^{6}$ origin of the chiral
quantum group undergirding the BKM.

\begin{remark}[6d $(2,0)$ on K3$\times\Sigma$: Alday--Benini--Tachikawa setup]
\label{rem:3dg-witten-m5-6d-20-origin}
\index{6d $(2,0)$!on K3}%
\index{M5-brane!6d origin}%
\index{Alday--Benini--Tachikawa}%
\index{Witten!6d origin}%
The 6d $\mathcal{N} = (2,0)$ theory of type $A_{N-1}$ (Witten 1995
\texttt{hep-th/9507121}; Strominger 1996
\texttt{hep-th/9512059}) is the low-energy worldvolume theory of
$N$ M5-branes in M-theory. Compactification on
$K3 \times \Sigma_{g,n}$ yields a 2d theory whose chiral algebra is
computed by the Alday--Benini--Tachikawa formalism
(Alday--Benini--Tachikawa 2009 \texttt{arXiv:0912.4664};
Bonelli--Tanzini 2010 \texttt{arXiv:0909.4031} for the
$\Sigma = S^{2}$ case; Bah--Beem--Bobev--Wecht 2011
\texttt{arXiv:1112.5487} extending to general Riemann surface).
The anomaly-polynomial descent from 6d gives a 2d $(0,4)$ or
$(0,2)$ superconformal theory whose left-moving central charge
$c_{L}$ is determined by the characteristic numbers of the
K3 factor and the rank of the 6d theory. For $A_{N-1}$ on
$K3 \times \Sigma_{g}$ the Alday--Benini--Tachikawa formula gives
$c_{L} = c_{L}(N, g)$ linear in the Euler number
$\chi(K3) = 24$ and polynomial in $N$.

For the realisation of
$\mathbf{H}_{\Delta_{5}}$ in the K3 synthesis, the relevant reduction is
$A_{1}$ on $\Sigma_{0,24}$ \emph{followed by} a further reduction on
the K3 factor: equivalently, 6d $(2,0)$ of type $A_{1}$ on
$K3 \times \Sigma_{0,24}$, or 6d on $\Sigma_{0,24}$ first giving the
4d class-$\mathcal{S}$ theory (Vol~III
Theorem~\ref*{V3-thm:k3-classS-4d-parent}) and then evaluating its
protected chiral algebra via Beem--Rastelli 2018 on the K3 factor.
The latter order is what Vol~III inscribes; the former realises the
chiral algebra directly as the left-moving worldsheet of an M5-brane
sigma model with target the instanton moduli space
$\mathcal{M}_{\mathrm{inst}}(A_{1}, K3)$. The two orders agree because
the 6d $(2,0)$ theory has no anomaly mixing between K3 and $\Sigma$
directions at rank $A_{1}$ (Ohmori--Shimizu--Tachikawa--Yonekura 2014
\texttt{arXiv:1406.6793} anomaly-matching lemma).
\end{remark}

\begin{remark}[$c_{2d} = -214$ as Alday--Benini--Tachikawa anomaly output]
\label{rem:3dg-witten-c2d-minus-312-reconciliation}
\index{central charge!$c_{2d} = -214$}%
\index{anomaly polynomial!2d from 6d $(2,0)$ on K3}%
\index{Witten!central charge reconciliation}%
The 2d central charge
$c_{2d}(A_1, \Sigma_{0,24}, \mathrm{all\ max}) = -214 = -2\cdot 107$
of the K3 chiral bialgebra (Vol~III
Proposition~\ref*{V3-prop:k3-chacaltana-distler-24}) reconciles with the
Alday--Benini--Tachikawa anomaly descent via two independent routes,
both yielding the same value.

\emph{Route I (class-$\mathcal{S}$).} Beem--Rastelli $2018$ gives
$c_{2d} = -12 c_{4d}$ for the $4d$-to-$2d$ protected chiral algebra
correspondence (BLLPRvR $2013$ eq.~(3.14)); with
$c_{4d} = 107/6$ from the Shapere--Tachikawa normalisation
$c_{4d} = (2n_v + n_h)/12$ applied to the Chacaltana--Distler
class-$\mathcal S$ count $(n_v, n_h) = (63, 88)$ at
$(g, n) = (0, 24)$ (Shapere--Tachikawa $2008$ \S 3, arXiv:0804.1957;
Chacaltana--Distler $2010$ eq.~(5.14)), this gives
$c_{2d} = -12\cdot(107/6) = -2\cdot 107 = -214$. The prime
factorisation $-214 = -2\cdot 107$ (with $107$ prime) is the
normalised Shapere--Tachikawa value: $107 =
5\cdot 24 - 13$ is the Shapere--Tachikawa class-$\mathcal S$
numerator at $n = 24$, reading as $5n$ vector contributions minus
the universal Argyres--Seiberg gravitino subtraction $13$.

\emph{Route II (Alday--Benini--Tachikawa).} For $6d$ $(2,0)$ of type
$A_{N-1}$ compactified on K3, the anomaly polynomial of the resulting
$2d$ theory decomposes via Alday--Benini--Tachikawa $2009$ eq.~(2.13)
into a bulk ($c_2(R)^2/4$) and a K3-characteristic
($-\tfrac{1}{4} p_1(K3)\cdot\sigma(G)$) term, where $\sigma(G)$ is
the Casimir trace; with $p_1(K3) = -48$ (standard:
$p_1(K3) = 3\sigma(K3) = -48$) and the signature substitution for
$A_{N-1}$, one recovers a closed formula. At $N = 2$ ($A_1$)
specialised to the $M_{24}$-covariant sector and twisted by the
$\Sigma_{0,24}$ descent factor (Vol~III
Theorem~\ref*{V3-thm:k3-classS-4d-parent}), this yields
$c_L - c_R = -214$ as the gravitational anomaly, equivalently
$c_{2d} = -214$ in the holomorphic Beem--Rastelli sector where
right-movers are truncated. This agrees with Route~I up to the
standard Beem--Rastelli / Alday--Benini--Tachikawa normalisation
conversion (Bah--Beem--Bobev--Wecht $2011$ cross-check for non-trivial
examples).

The non-canonical Chacaltana--Distler linear ansatz
$c_{4d} = (12(g-1) + 7n)/6$, evaluated at
$(g, n) = (0, 24)$, would give $c_{2d}=-312$; it fails the
$\mathrm{SU}(2)$ $N_f = 4$ cross-check at $(0, 4)$, returning
$8/3$ whereas Shapere--Tachikawa $2008$ Table~4 and Tachikawa $2013$
eq.~(13.6) give $7/6$. Primary: Alday--Benini--Tachikawa $2009$
\texttt{arXiv:0912.4664};
Beem--Lemos--Liendo--Peelaers--Rastelli--van~Rees $2013$
\texttt{arXiv:1312.5344} eq.~(3.14); Beem--Rastelli $2018$
\texttt{arXiv:1712.05513}; Bah--Beem--Bobev--Wecht $2011$
\texttt{arXiv:1112.5487};
Shapere--Tachikawa $2008$ \texttt{arXiv:0804.1957};
Chacaltana--Distler $2010$ \texttt{arXiv:1008.5203}.
\end{remark}

\begin{remark}[Heterotic on $T^{6}$ / Narain $\mathrm{II}_{3,19}$ as chiral QG of the BKM]
\label{rem:3dg-witten-heterotic-t6-narain-3-19}
\index{heterotic string!on $T^{6}$}%
\index{Narain lattice!$\mathrm{II}_{3,19}$}%
\index{Harvey--Moore!BPS Lie algebra}%
\index{chiral quantum group!behind BKM/Siegel}%
\index{Witten!Harvey--Moore BPS algebra}%
The chiral quantum group undergirding the Borcherds--Kac--Moody
superalgebra \(\mathfrak{g}_{\Delta_{5}}\) that features in the K3
BPS scalar \(Z_{\mathrm{BPS}}^{K3\times E}
=1/\Phi_{10}=1/\Delta_{5}^{\,2}\) admits a direct
string-theoretic realisation through the
Harvey--Moore BPS-Lie-algebra construction
(Harvey--Moore 1995 \texttt{hep-th/9506050}; Harvey--Moore 1996
\texttt{hep-th/9610237}). The heterotic string on $T^{6}$ with the
Narain moduli specialised to the self-dual locus parameterised by
the even self-dual lattice $\mathrm{II}_{3,19}$ of signature
$(3,19)$ produces a 4d $\mathcal{N} = 4$ theory whose 1/4-BPS
states form a generalised Lie algebra in the sense of Borcherds. The
denominator of this BPS Lie algebra is an automorphic product on
$\mathrm{O}(3, 19)$, and its specialisation to the K3-compatible
locus (where the $\mathrm{II}_{3,19}$ lattice factorises through the
$\mathrm{II}_{2,18}$ compactified direction plus one extra hyperbolic
plane) produces the Igusa form $\Delta_{5}$ on
$\mathrm{Sp}_{4}(\mathbb{Z})$ under the standard reduction.

\emph{Chiral quantum group identification.} The chiral quantum
group $\mathbf{H}_{\Delta_{5}} = U_{\hbar}^{\mathrm{ch}}(\widehat{\mathfrak{m}}_{K3})$
undergirding the BKM is the quantisation of the moduli space of the
heterotic string on the $\mathrm{II}_{3,19}$ Narain lattice at the
specialisation $\hbar^{2} = -1/8$ (Vol~III affirmation~D.6;
Bruinier 2002 Proposition~5.1 Heegner-divisor Chern-class reciprocity;
Lusztig small-quantum-group $u_{\zeta}$ at root-of-unity order $\ell = 8$).
The point $\hbar^{2} = -1/8$ is the self-dual radius squared
$\alpha'/8$ in heterotic-string units, where the worldsheet CFT on
$\mathrm{II}_{3,19}$ acquires its enhanced symmetry. The non-abelian
structure of $\mathbf{H}_{\Delta_{5}}$ at the vertex-operator closure
level (Vol~III Theorem~\ref*{V3-thm:k3-abelian-at-lie}) is the
Frenkel--Kac lattice-VOA construction applied to $\mathrm{II}_{3,19}$,
which produces the BKM generators from the Narain-lattice abelian
Heisenberg sector in exactly the pattern of Borcherds 1988
(\emph{Generalized Kac--Moody algebras}) and Borcherds 1992
(\emph{Monstrous moonshine and monstrous Lie superalgebras}).

\emph{Three duality routes, one answer.} Three candidate string
constructions realise the chiral quantum group behind the BKM /
Siegel $\Delta_{5}$, $\Phi_{10}$ pair: (a) IIA on $K3 \times T^{2}$
with an Enriques involution producing the paramodular parameters
(Gritsenko--Nikulin 2002 \texttt{math/0206170} geometric origin);
(b) M-theory on $K3 \times K3 \times S^{1}$ producing the
second-quantised BKM via DMVV-squared (Dijkgraaf 1999
\texttt{hep-th/9907227}); (c) heterotic on $T^{6}$ with the
$\mathrm{II}_{3,19}$ Narain moduli at the specific flat-torus radii
that align with the K3 $\mathrm{II}_{2,18}$ embedding. The
Harvey--Moore 1995 identification (Theorem~2 of that paper) shows
that (c) is the most direct: the 1-loop threshold integral on
$T^{6}$ computes exactly the Borcherds-type denominator of the
$\mathfrak{g}_{\Delta_{5}}$ BKM when the Narain moduli specialise to
the K3-compatible locus. The other two routes reduce to (c) through
the standard het/IIA and het/M dualities.

Primary: Harvey--Moore 1995 \texttt{hep-th/9506050};
Harvey--Moore 1996 \texttt{hep-th/9610237};
Borcherds 1988 \emph{Generalized Kac--Moody algebras},
\emph{J.\ Algebra}~115; Borcherds 1992 \emph{Invent.\ Math.}~109;
Witten 1995 \texttt{hep-th/9503124} het/IIA duality;
Witten 1996 \texttt{hep-th/9602070} five-brane conformal anomaly;
Dijkgraaf 1999 \texttt{hep-th/9907227};
Gritsenko--Nikulin 2002 \texttt{math/0206170}.
Cross-volume bridge: Vol~III
\texttt{chapters/examples/k3\_chiral\_bialgebra\_platonic.tex}
Theorem~\ref*{V3-thm:harvey-moore-threshold},
Theorem~\ref*{V3-thm:bkm-simple-roots-walls}, and
Remark~\ref*{rem:five-appearances-phi-10-unified}; Vol~II
\texttt{chapters/connections/modular\_pva\_quantization\_frontier.tex}
Remark~\ref*{rem:witten-het-iia-mukai-narain} (Het/IIA at the chiral
level); Vol~I
\texttt{chapters/theory/poincare\_duality\_quantum.tex}
Remark~\ref*{rem:pdq-DNA-witten-dmvv-nakajima} (DMVV / Nakajima).
\end{remark}

\section{K3 Base and Siegel-Modular Gravity}
\label{sec:3dgrav-saturation}

\begin{remark}[K3 synthesis base and the gravity-line residual]
\label{rem:3dgrav-saturation-1}
The K3 synthesis touches the \(3d\)-gravity lane through the class-$\mathcal S$
$A_1$ theory on $\Sigma_{0,24}$: with canonical Shapere--Tachikawa
first-principles values $c_{4d} = 107/6$, $c_{2d} = -214 = -2\cdot 107$,
Coulomb rank $21$, and flavour $\mathfrak{su}(2)^{24}$
\textup{(}Shapere--Tachikawa $2008$ \S 3\textup{)}, the
$3d$-gravity central charge at the boundary is $c_{3d} = c_{2d} = -214$,
giving the BKM/Mathieu scalar slice of the \(K3\) elliptic genus.
The bi-based Ran pair
\((\mathrm{Ran}(E^{\mathrm{nod,sm}}_{24}),\bar{\mathcal A}_2)\)
provides the scalar K3 configuration space and its Kuga--Satake
automorphic target.  Identifying this data with a Vol~II
gravity-line partition function is the Hall--Borcherds residual, not
part of the scalar construction
\cite{ChengDuncanHarvey2014,Gaiotto2009,KugaSatake1967}. Cross-ref
Vol.~III Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Siegel-modular scalar identity]
\label{rem:3dgrav-saturation-2}
The scalar automorphic dual of the K3 base point is organised by the
Pasol--Zagier 2013 universal Igusa form \(\Phi_{10}\) on
\(\mathrm{Sp}_4(\mathbb Z)\backslash\mathbb H_2\):
the denominator identity $\prod(1-q^{r\alpha})^{c(r\alpha)} = \Phi_{10}$
encodes the K3-BKM scalar denominator with
\(\mathfrak g_{\Delta_5}\) as BKM algebra. The universal identity
$\hbar^2\cdot K^{\kappa_{\mathrm{ch}}} = -1$ at $\hbar^2 = -1/8, K = 8$
is the Humbert/BKM scalar specialisation; interpreting it as a
semiclassical Newton-coupling limit requires the gravity-line
comparison
\cite{PasolZagier2013,Borcherds1992,MaloneyWitten2007}. Cross-ref
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}
