\chapter{Higher-spin celestial corrections from $W$-type Poisson vertex algebras}
\label{ch:celestial-boundary-transfer-frontier}

\section{$W$-type Poisson vertex algebras and higher-spin celestial data}
\label{sec:cbt-w-type}

For $W$-type PVAs in the sense of Khan--Zeng~\cite{KZ25}, the obstruction theory specializes to higher-spin invariants.

\subsection{The lowest-nonlinearity principle for $W$-type PVAs}
\label{sec:cbt-abstract-w-type}

Theorem~\ref{thm:cbt-lowest-nonlinearity} controls the first nonlinear celestial invariant of a PVA by the lowest nonlinear homogeneous part of the generator $\lambda$-brackets. For $W$-type PVAs in the sense of~\cite{KZ25}, that lowest part is quadratic.

\begin{corollary}[first higher-spin correction for quadratic $W$-type PVAs]
\label{cor:cbt-w-type-quadratic}
\ClaimStatusConditional
Let $V$ be a freely generated $W$-type PVA, and assume:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2em]
\item the boundary/celestial tree-level transfer exists and respects the composite filtration;
\item the first nonlinear homogeneous term in the generator $\lambda$-brackets is quadratic.
\end{enumerate}
Then the first nonlinear obstruction class $\operatorname{Ob}_1$ of the associated boundary/celestial $\Ainf$-algebra depends only on the linearized Lie conformal structure and the quadratic part of the $\lambda$-brackets. No cubic or higher homogeneous term can affect $\operatorname{Ob}_1$.
\end{corollary}

\begin{proof}
This is the case $q=2$ of Theorem~\ref{thm:cbt-lowest-nonlinearity}.
\end{proof}

\subsection{The classical \texorpdfstring{$W_3$}{W3} Poisson vertex algebra}
\label{sec:cbt-w3-example}

The classical $W_3$ PVA~\cite{KZ25} is generated by a spin-$2$ field $T$ and a spin-$3$ field $W$ with $\lambda$-brackets
\[
\{T_\lambda T\}=\partial T+2T\lambda+\frac{c}{12}\lambda^3,
\]
\[
\{T_\lambda W\}=\partial W+3W\lambda,
\]
and
\[
\{W_\lambda W\}
=
\frac{c}{360}\lambda^5
+\frac13 T\lambda^3
+\frac12(\partial T)\lambda^2
+\left(\frac{3}{10}\partial^2T+\frac{16}{22+5c}T^2\right)\lambda
+\frac1{15}\partial^3T
+\frac{16}{22+5c}T\,\partial T.
\]
The lowest nonlinear part is quadratic in $T$.

\begin{corollary}[first higher-spin obstruction for the classical \texorpdfstring{$W_3$}{W3} PVA]
\label{cor:cbt-w3-obstruction}
\ClaimStatusConditional
Assuming the tree-level filtered boundary transfer exists for the $W_3$ PVA and respects composite degree, the first nonlinear celestial/boundary obstruction class is controlled entirely by the linear Virasoro-$W$ sector together with the quadratic terms
\[
\frac{16}{22+5c}T^2\lambda
\qquad\text{and}\qquad
\frac{16}{22+5c}T\,\partial T
\]
in $\{W_\lambda W\}$. No higher nonlinear correction can influence the first obstruction.
\end{corollary}

\begin{proof}
The $W_3$ bracket displayed above has first nonlinear homogeneous degree $2$. Apply Corollary~\ref{cor:cbt-w-type-quadratic}.
\end{proof}

\begin{remark}[universal first higher-spin celestial correction]
\label{rem:cbt-universal-first-correction}
The first obstruction is determined by the pair (linear conformal algebra, first quadratic nonlinear term) once the tree-level filtered transfer exists.
\end{remark}

\begin{remark}[$W_n$ and $W_\infty$ extensions]
\label{rem:cbt-beyond-w3}
The Khan--Zeng construction~\cite{KZ25} extends to $W_n$ and $W_\infty$. Conditional on the tree-level filtered transfer, Corollary~\ref{cor:cbt-w-type-quadratic} fixes a hierarchy of first nonlinear higher-spin celestial invariants before explicit transfer formulas appear.
\end{remark}

\section{Three projections of the boundary/celestial $\Ainf$-algebra}
\label{sec:cbt-synthesis}

The boundary/celestial $\Ainf$-algebra of a PVA $V$ admits three projections, each isolating one structural layer: the wedge quotient, the bar-filtered tower, and the highest-weight restriction.

\subsection*{I. The wedge projection}
Quotient by composites. The wedge $\Ainf$-algebra $\mathbb{W}(C)$ is the single-particle shadow of the boundary/celestial algebra.

\subsection*{II. The bar-filtered projection}
Composites organized by filtration produce the obstruction tower
\[
\operatorname{Ob}_1,\operatorname{Ob}_2,\operatorname{Ob}_3,\dots
\]
and the composite spectral sequence. The classes $\operatorname{Ob}_r$ are the nonlinear curvature of the celestial algebra relative to its wedge sector.

\subsection*{III. The highest-weight projection}
Restriction to exactly solvable weight sectors makes the transfer explicit: simplex integrals, simplex summation laws, double factorials, exact $\pi_n$ coefficients, the one-dimensional Airy--Witt normal form.

The boundary/celestial algebra is a filtered cotangent deformation; the wedge quotient is its linear shadow; the obstruction classes are its nonlinear curvature; the highest-weight ladders are its integrable geodesics.

\section{Open problems}
\label{sec:cbt-open-problems}

\begin{enumerate}[leftmargin=2.2em]
\item \textbf{Even-mode closure for the Poisson ladder.}
Theorem~\ref{thm:cbt-airy-witt} computes the odd positive modes. The missing even modes inside the full transferred $\Linf$ algebra on $T^*[1]\operatorname{Ham}(\mathbb{C}^2)$ remain to be identified.

\item \textbf{Central extensions on the ladder.}
The higher Kac--Moody algebra admits central extensions~\cite{Zeng25}. The transfer of the cocycle to the highest-weight ladder produces central higher brackets.

\item \textbf{Explicit $W_3$ transfer.}
An explicit contraction for the $W_3$ PVA, together with $\operatorname{Ob}_1$ and the first ladder sector.

\item \textbf{Homotopy invariance of the higher ladder sectors.}
The all-degree formulas hold for the canonical transferred model. Identification of the gauge-invariant higher obstructions inside this canonical structure.

\item \textbf{Quantum corrections.}
Combination of the exact tree-level formulas with loop corrections; in the Poisson-vertex setting, deformation quantization of the boundary algebra.
\end{enumerate}

\subsection{Notation concordance}
\label{sec:cbt-notation-concordance}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.27\textwidth}>{\raggedright\arraybackslash}p{0.67\textwidth}}
\toprule
\textbf{Notation here} & \textbf{Meaning / relation to the source papers}\\
\midrule
$\mathbb{W}(C)$ & Wedge or single-particle $\Ainf$-algebra $H/F^1H$ of a filtered celestial/boundary $\Ainf$-algebra.\\
$\operatorname{Ob}_r$ & $r$th nonlinear obstruction class of the filtered bar coderivation.\\
$A_{\mathrm{BF}}$ & Transferred minimal $\Ainf$-algebra on $H_b^{0,\bullet}(S^3)$ for holomorphic BF.\\
$L_n$ & Transferred $\Linf$ bracket $\{\cdot,\dots,\cdot\}_{\bar\pi,n}$ in Zeng's notation.\\
$\eta_b$ or $v_b$ & Highest-weight anti-holomorphic basis vector $\bar w_2^b\epsilon \in H_b^{0,1}(S^3)$.\\
$L_a$ & Highest-weight holomorphic monomial $w_1^a$.\\
$\xi_m$ & Renormalized odd ladder generator $\dfrac{(-1)^m}{(2m+1)!!}w_1^{2m+1}$.\\
$R_m$ & $(m+1)$-linear operator $L_{m+2}(\xi_m,-,\dots,-)$ on the odd ladder sector.\\
$D_m$ & First-order differential operator $-\partial_t\circ M_{t^{2m+2}}$ representing $R_m$.\\
$\mathfrak c^L_{r,s},\mathfrak c^R_{r,s}$ & Unit-projected left and right cubic coefficients of $m_3$ in holomorphic BF.\\
$\Delta_{r,s}$ & Cubic asymmetry invariant $\mathfrak c^L_{r,s}-\mathfrak c^R_{r,s}$.\\
$(\pi_n)$ & Zeng's normalized coefficient package for the transferred Poisson brackets.\\
\bottomrule
\end{longtable}

\subsection{The wedge--obstruction--ladder triple of $W$-type celestial transfer}
\label{sec:cbt-inventory}

The three projections of \S\ref{sec:cbt-synthesis} carry, on a
$W$-type PVA, three independent layers of celestial data. The wedge
projection delivers the single-particle transfer
$\mathbb{W}(C)$ and reduces composite curvature to its linear
shadow. The obstruction tower
$\operatorname{Ob}_1,\operatorname{Ob}_2,\operatorname{Ob}_3,\ldots$
of the bar-filtered projection, generated by the recursive
linearisation criterion of
Theorem~\ref{thm:cbt-lowest-nonlinearity} and realised by the
composite spectral sequence, measures the failure of strictification;
its first class, on quadratic $W$-type PVAs, depends only on the
linear conformal datum and the quadratic part of the
$\lambda$-brackets, with the $W_3$ instance of
Corollary~\ref{cor:cbt-w3-obstruction} as the principal example. The
highest-weight projection, evaluated on the holomorphic BF and
Poisson BF transfers, produces the cubic asymmetry invariant
$\Delta_{r,s}$ that obstructs strictification, the exact
highest-weight ladder theorems with their simplex integrals and
double factorials, the all-order higher Kac--Moody ladder brackets
and the Poisson $\pi_n$ ladder coefficients, and the Airy--Witt
normal form of the odd highest-weight sector of the transferred
deformation of $T^*[1]\operatorname{Ham}(\mathbb{C}^2)$.
