\section{Conclusion and Outlook}
\label{sec:conclusion}%
\label{sec:concordance}%

\subsection{The single object}

Volume~I is genus~$g$ on a curve; Volume~II is the dimensional
lift to $\C \times \R$.  The bar complex
$\barB^{\mathrm{ch}}(\cA)$ of Volume~I and the Swiss-cheese operad
$\SCchtop$ of Volume~II are not two theories but two views of a
single structure.
The MC element $\alpha_T$ in the Swiss-cheese convolution algebra
encodes the direct data of this volume through its projections: the
$\Ainf$ operations as its closed face, the open-colour line-sector
operations as its open face, the PVA bracket as its cohomological
shadow, the spectral $R$-matrix as its mixed-color component, and the
genus tower as its $\hbar$-expansion.  The corrected
bulk-boundary-line triangle is then assembled from these faces
together with the later comparison theorems.  Each of the following
results is a coordinate expression for this single object.

\begin{enumerate}[label=(\Roman*)]
\item \textbf{Axiomatic Definition} (Section~\ref{sec:foundations}): We constructed the HT operad $\OHT=C_\ast\!\bigl(W(\SCchtop)\bigr)$ and defined $A_\infty$ chiral algebras as algebras over $\OHT$, with explicit sesquilinearity axioms relating $\partial$-equivariance to the $\lambda$-calculus.

\item \textbf{Chain-Level Structure} (Section \ref{sec:FM_calculus}): We proved that bulk local operators form an $A_\infty$ chiral algebra at the chain level, with $A_\infty$ identities arising from Stokes' theorem on FM compactifications and Arnold cancellations at codimension-2 corners.

\item \textbf{PVA Descent} (Section \ref{sec:PVA_descent}): We established that cohomology $H^\bullet(\mathcal{A}, Q)$ is a Poisson vertex algebra by verifying all axioms from Khan--Zeng \cite{KZ25} and proving higher operations $m_{k \geq 3}$ vanish in cohomology via explicit homotopies.

\item \textbf{Worked Examples} (Section \ref{sec:examples_complete}): We computed $A_\infty$ operations explicitly for free chiral multiplets, Landau--Ginzburg models (resolving the $m_{k \geq 4}$ truncation contradiction), and abelian Chern--Simons theory.

\item \textbf{Chiral Hochschild Cohomology} (Section \ref{sec:chiral_hochschild}): We connected bulk observables to chiral Hochschild cochains via dimensional descent from 2d Poisson sigma models and factorization homology on the Ran space.

\item \textbf{Bar--Cobar Duality} (Section \ref{sec:bar_cobar}): We extended Gui--Li--Zeng quadratic duality to the $A_\infty$ setting, proving $d_{\overline{B}}^2 = 0$ using FM--Stokes--Arnold calculus and establishing compatibility with GLZ.

\item \textbf{Line Operators and Yangians} (Section \ref{sec:line_operators}): On the chirally Koszul locus, we proved $\cC_{\mathrm{line}} \simeq \cA^!_{\mathrm{line}}\text{-mod}$, where the open-colour Koszul dual $\cA^!_{\mathrm{line}}$ carries the dg-shifted Yangian package (Theorem~\ref{thm:yangian-recognition}) with spectral kernel $r(z)$ satisfying the $A_\infty$ Yang--Baxter equation.
\end{enumerate}

%% ====================================================================
%%  MOVEMENT I: THE SINGLE PRINCIPLE
%% ====================================================================

\bigskip

These seven results are coordinates on a single object.
The coordinates are not independent: each determines the others
through the Stasheff identities, the Koszul pairing, and the
genus-tower recursion.  There is a geometric reason for this
rigidity.

\section*{Movement I\@: The single principle}

\providecommand{\cL}{\mathcal{L}}
\providecommand{\Mvac}{\cM_{\mathrm{vac}}}
\providecommand{\Mbar}{\overline{\mathcal M}}

The categorical logarithm of Volume~I is a Lagrangian embedding.
The bar construction $\barB^{\mathrm{ch}}(\cA)$ maps a chiral
algebra~$\cA$ into the derived moduli~$\Mvac$ of local bulk vacua,
and the image is a shifted Lagrangian
$\cL_\cA \hookrightarrow \Mvac$: the $(-2)$-shifted symplectic
structure on $\Mvac$
(Conjecture~\ref{conj:geometric-steinberg}(a)) pulls back to zero
along~$\cL_\cA$, with the vanishing witnessed by the bar
differential.  The Swiss-cheese coalgebra of Volume~II is the
self-intersection of this Lagrangian:
\[
  \mathfrak{S}_\cA
  \;=\;
  \cL_\cA \times_{\Mvac} \cL_\cA,
\]
the derived fiber product that carries a $(-1)$-shifted symplectic
structure inherited from complementary Lagrangians
(Volume~I, Theorem~C).  Every theorem in both volumes is a shadow of
this geometry.  The bar-cobar adjunction (Theorem~A) is the
Lagrangian neighborhood theorem; Koszul inversion (Theorem~B) is the
formal Darboux isomorphism at the self-intersection; the modular
characteristic $\kappa(\cA) \cdot \omega_g$ (Theorem~D) is the
curvature of the Lagrangian family over~$\Mbar_{g,n}$; the chiral
Hochschild ring (Theorem~H) is the ring of functions on the
self-intersection.  The five theorems are five faces of a single
Lagrangian.

\medskip

\noindent\textbf{The three questions, geometrically.}\enspace
The guiding questions of the modular holography programme
acquire their sharpest form when restated through the Lagrangian lens.

\begin{enumerate}[label=\textup{(\roman*${}'$)}]
\item \textbf{Existence as modular completion.}
  The genus-zero Lagrangian $\cL_\cA \hookrightarrow \Mvac$ is
  constructed from bar-cobar data on
  $\FM_k(\C) \times \mathrm{Conf}_k^{<}(\R)$.  Does this embedding
  extend to a family of Lagrangians
  $\cL_\cA^{(g,n)} \hookrightarrow \Mvac$ parametrized
  by~$\Mbar_{g,n}$, so that the genus-$g$ bar complex with curvature
  $d^2 = \kappa(\cA) \cdot \omega_g$ is the pullback of the
  symplectic structure to the fiber over the generic point of the
  Hodge bundle?  This is the modular completion of the Lagrangian:
  the genus tower is the obstruction sequence for extending an
  isotropic embedding through the boundary strata
  of~$\Mbar_{g,n}$.

\item \textbf{Geometry as Lagrangian descent.}
  The gluing morphisms $\Mbar_{g_1,n_1} \times \Mbar_{g_2,n_2}
  \to \Mbar_{g_1+g_2,n_1+n_2-2}$ are correspondences.  Are these
  correspondences Lagrangian in the appropriate shifted symplectic
  category?  Descent of the bar complex through boundary strata is
  precisely the requirement that the Lagrangian family
  $\cL_\cA^{(g,n)}$ is compatible with Lagrangian composition of
  correspondences, the higher-categorical content of the stable-graph
  sewing~$d_{\mathrm{sew}}$.

\item \textbf{Computation as intersection numbers.}
  Each genus-$g$ coefficient of the modular Yangian kernel
  $R^{\mathrm{mod}}_{\mathcal{T}}(z;\hbar)$ is a derived
  intersection number:
  \[
    R^{(g)}_\cA(z)
    \;=\;
    \chi\!\bigl(
      \cL_\cA^{(g)} \times_{\Mvac} \cL_\cA^{(g)}
    \bigr),
  \]
  the Euler characteristic of the genus-$g$ Lagrangian
  self-intersection.  Computing these numbers in the three basic
  examples ($\beta\gamma$, Kodaira--Spencer, $\mathcal{W}_3$ PSM) is
  the genus-refined analogue of computing Kazhdan--Lusztig
  polynomials from the Steinberg variety.
\end{enumerate}

\medskip

\noindent\textbf{Koszulness as the watershed.}\enspace
In the Lagrangian picture, Koszulness has a precise geometric meaning:
a chiral algebra~$\cA$ is Koszul if and only if $\cL_\cA$ meets
itself cleanly: the derived self-intersection $\mathfrak{S}_\cA$ is
concentrated in the expected degree, with no higher Tor.  This is
transversal Lagrangian intersection: the bar cohomology is generated
in a single internal degree, all higher $\Ainf$ operations are
homotopically trivial, and the genus-$g$ corrections are scalar
multiples of the genus-zero answer.  In the physical language, the
bar-complex sector is perturbatively exact; loop corrections
renormalize but do not deform, and the $E_1$-coproduct $\Delta$ is
genus-independent.  (The full $R$-matrix $R_g(z)$ may still acquire
genus dependence through the propagator channel when the Coisson
bracket $c_0 = \{a\,{}_0\,b\}$ is nonzero; full perturbative
exactness $R_g(z) = R_0(z)$ requires additionally $c_0 = 0$,
cf.\ Theorem~\ref{thm:pole-structure-dichotomy}.)
Kac--Moody algebras at generic level are Koszul
(Theorem~\ref{thm:one-loop-koszul}: one-loop exactness of the
affine half-space BV theory implies Koszulness), and their
Lagrangians are transversal: the self-intersection is the
Steinberg variety of the loop group, smooth as a derived scheme.

When Swiss-cheese formality fails, the Lagrangian self-intersection
carries excess: higher $\Ainf$ operations proliferate because the
derived fiber product has Tor in unexpected degrees.  The curved bar
structure $d^2 = \kappa(\cA) \cdot \omega_1$ is the first-order
excess intersection class.  Curvature and braiding entangle because
the excess Tor classes mix the holomorphic direction (where the
$\lambda$-bracket lives) with the topological direction (where the
$\Eone$-coalgebra lives).  The pole structure of the OPE determines
the intersection type: simple poles give transversal intersection and
collision-pure algebras; higher-order non-scalar poles give excess
intersection and non-formal $\Ainf$ structures.  Principal
Drinfeld--Sokolov reduction manufactures higher poles from simple ones
(Theorem~\ref{thm:ds-koszul-obstruction}): for Virasoro and $W_N$,
reduction moves the Lagrangian into a position of excess
self-intersection, destroying Swiss-cheese formality (though
Koszulness, i.e.\ bar concentration, is preserved).  The
distinction between Koszulness and formality is the distinction
between clean intersection (bar cohomology in a single degree) and
transversal intersection (no higher $\Ainf$ operations): every
transversal intersection is clean, but a clean intersection may
still carry excess normal data.

\medskip

\noindent\textbf{Is the holographic Lagrangian complete?}\enspace
The three guiding questions of the modular programme (Existence,
Geometry, Computation) are not three separate questions.  They are
the obstruction, the compatibility, and the invariant of a
\emph{single} extension problem: does the genus-$0$ Lagrangian
$\cL_\cA^{(0)} \hookrightarrow \Mvac$ extend to a family
$\cL_\cA^{(g)} \hookrightarrow \Mvac$ over $\Mbar_{g,n}$?

Existence is the obstruction theory of this extension.
The higher $\Ainf$ operations $m_3, m_4, \ldots$ are the successive
obstruction classes: each $m_k$ measures the failure of the
$(k{-}1)$-th extension through the boundary strata
of~$\Mbar_{g,n}$.  For Koszul algebras the obstructions vanish
identically; the clean Lagrangian intersection extends
automatically, because a scalar curvature has no excess normal
bundle.  For algebras with non-formal Swiss-cheese structure the obstructions
proliferate, and the infinite $\Ainf$ tower is the infinite obstruction
sequence.

Geometry is the compatibility of the extension with gluing.  The
boundary strata of~$\Mbar_{g,n}$ are correspondences; demanding
that the Lagrangian family restrict correctly to each stratum is
demanding that $\cL_\cA^{(g)}$ be a section of the universal
Lagrangian correspondence over the stable-graph boundary.  The
sewing differential~$d_{\mathrm{sew}}$ is the flatness condition
for this section.

Computation is the extraction of invariants.  Once the family
$\cL_\cA^{(g)}$ is constructed, the derived intersection
numbers~$R^{(g)}_\cA(z)$ of~(iii${}'$) are invariants
on~$\Mbar_{g,n}$: the genus-refined analogues of Kazhdan--Lusztig
polynomials.  Computing these in the three basic examples
($\beta\gamma$, Kodaira--Spencer, $\mathcal{W}_3$ PSM) is the
concrete test.

The completeness question therefore unifies the programme: one
Lagrangian, one extension, three projections.  Koszulness is the
watershed because it determines whether the extension is automatic
(clean intersection, scalar curvature) or requires the full
obstruction tower (excess intersection, curved $\Ainf$ structure).
The monograph computes the genus-$0$ term.  The modular programme
is the rest.

\medskip

\noindent\textbf{The Steinberg dictionary as derived symplectic
geometry.}\enspace
Every row of the Steinberg dictionary
(Remark~\ref{rem:steinberg-dictionary}) is a face of the Lagrangian
self-intersection.  The flag variety $G/B$ is the Lagrangian
$\cL_\cA$; the Fulton--MacPherson space $\FM_k(\C)$ is the
Lagrangian in the chiral setting.  The nilpotent cone $\cN$ is the
singular support of the Lagrangian; the collision
divisors~$D_S$ are the singular support in the chiral setting.
The Springer resolution is the bar construction's
compactification; the Steinberg variety is the self-intersection; the
Hecke algebra is the convolution algebra of the self-intersection;
the Swiss-cheese convolution $\Linf$-algebra~$\gSC_T$ is the Hecke
algebra in the chiral setting.  At the algebraic level the dictionary is a theorem
(Theorem~\ref{thm:steinberg-presentation}): the PTVV
$(-2)$-shifted symplectic structure on~$\Mvac$, the Lagrangian
property of the bar embedding, and the $(-1)$-shifted symplectic
structure on~$\mathfrak{S}_\cA$ from complementary Lagrangians
assemble to produce the convolution algebra by the same formal
mechanism (Borel--Moore homology of the correspondence) that
produces the Hecke algebra from the Steinberg variety.  The algebraic
Steinberg presentation
(Theorem~\ref{thm:steinberg-presentation}) is the proved shadow on
homology; the geometric Steinberg conjecture
(Conjecture~\ref{conj:geometric-steinberg}), which would promote this to a full statement
in derived symplectic geometry, remains open.  The doubling construction adds one more row: the
half-space FM compactification is the $\sigma$-equivariant restriction
of the whole-space FM compactification; the reflected propagator is the
$\sigma$-restricted standard propagator; and the reflected weight
identity is the $\sigma$-restricted Stokes identity
(Theorem~\ref{thm:doubling-rwi}).  Method of images in physics is
equivariant restriction in geometry.

\medskip

A chiral algebra is a Lagrangian.  The bar complex is its
self-intersection.  The Swiss-cheese operad is the internal structure
of that self-intersection.  Everything else is a shadow.

%% ====================================================================
%%  MOVEMENT II: PANORAMIC THEMES
%% ====================================================================
\section*{Movement II\@: Panoramic themes}

The Lagrangian principle says what the object \emph{is}.
The panoramic themes show what the object \emph{does}:
how a single quartic pole generates the gravitational $\Ainf$ tower,
how the harmonic number organizes the $\cW_N$ landscape,
how geometric Langlands appears as the flat slice $\kappa = 0$,
how helicity splitting is Swiss-cheese decomposition, and
how the genus tower carries a chromatic shadow.

\subsection{One quartic pole generates everything}

The Virasoro $\lambda$-bracket is
\[
  \{T\,{}_\lambda\,T\}
  \;=\;
  \partial T + 2T\lambda + \tfrac{c}{12}\lambda^3.
\]
Three terms, one generator, one parameter~$c$.  This is the entire
input.  The output is the subject of Part~VI and much of the present
volume: the infinite $\Ainf$ tower on the bar complex
$\barB(\mathrm{Vir}_c)$, with higher operations
$m_k(T,\ldots,T)$ produced by the resolvent tree formula
(Theorem~\ref{thm:resolvent-principle}) through the BRST deformation
retract; the Koszul involution $c \mapsto 26-c$, which is the
Lagrangian complement in the derived symplectic category; the
gravitational $r$-matrix $r(z) = (c/2)/z^3 + 2T/z$, obtained by
Laplace transform of the $\lambda$-bracket (the bar kernel absorbs one
pole order); the genus tower controlled by $\kappa(\mathrm{Vir}_c) =
c/2$, with Arnold defect $E_2(\tau)$ at genus~$1$
(Proposition~\ref{prop:genus-1-arnold-defect}) and curved bar
structure $d_{\barB}^2 = (c/2)\cdot\omega_g$ at all genera; the Cardy
entropy $S = 2\pi\sqrt{ch/6}$ as the high-temperature shadow of the
genus-$1$ bar complex; the BTZ entropy as the
complementarity-potential evaluation at genus~$1$; and infinitely many
soft graviton theorems, one for each arity of the shadow hierarchy
$\mathrm{Sh}_{g,n}$.

A single quartic pole in the OPE of a single field generates the
entire gravitational Swiss-cheese algebra.  This is the content of
the Steinberg analogy: as the Steinberg variety presents the Hecke
algebra from the geometry of $G/B$ alone, the bar complex presents
the Swiss-cheese coalgebra from the quartic pole alone.  The
complexity of three-dimensional quantum gravity is not in the number
of inputs but in the depth of the self-intersection.

\begin{remark}[Conformal bootstrap as the bar identity]
\label{rem:bootstrap-bar-identity}
The conformal bootstrap programme seeks solutions to crossing
symmetry, associativity, and modular invariance simultaneously.  In
the bar-complex framework, these are not separate constraints but
components of a single equation: $d_{\barB}^2 = 0$ at genus~$0$.
Specifically, crossing symmetry at arity~$3$ is the Stasheff
$A_\infty$ identity $\sum_{i+j=4} m_i \circ m_j = 0$, which is
precisely the component of $d_{\barB}^2 = 0$ on
$\barB_3(\cA)$: the three crossing channels correspond to the
three ways of decomposing a $4$-element sequence into
sub-sequences, and their cancellation is the codimension-$1$
boundary relation on $\FM_3(\C) \times \Conf_3^{<}(\R)$.  The bar
complex solves all bootstrap equations simultaneously because
$d_{\barB}^2 = 0$ encodes the full system of Stasheff identities at
all arities.

The pole-order dichotomy reappears: for class~L algebras (double
poles, finite shadow depth), crossing symmetry is \emph{strict}:
the higher $A_\infty$ operations $m_{k \ge 3}$ vanish on
cohomology, and the bootstrap reduces to the classical OPE
associativity.  For class~M algebras (quartic poles, infinite shadow
depth), crossing symmetry receives \emph{gravitational contact
corrections} from $m_3$ and all higher operations: the bar
differential on $\barB_3(\mathrm{Vir}_c)$ carries the non-trivial
$m_3(T,T,T)$ contribution that corrects the naive crossing relation
by graviton exchange at coincident points.  The bootstrap is not
violated but deformed: $d_{\barB}^2 = 0$ still holds, but the
individual terms in the Stasheff identity are genuinely infinite in
number.
\end{remark}

\medskip

The combinatorial depth of the self-intersection has a direct
arithmetic shadow.  For an affine Kac--Moody algebra
$\widehat\fg_k$, the graded Euler characteristic of the ordered
bar complex satisfies
$\chi(\barB^{\mathrm{ord}}(\widehat\fg_k); q) = -1 +
\eta(q)^{\dim\fg}$, where
$\eta(q) = q^{1/24}\prod_{n \geq 1}(1-q^n)$ is the Dedekind eta
function.  This is the bar-complex avatar of the denominator
identity: the combinatorial data of collisions on
$\FM_k(\C) \times \Conf_k^{<}(\R)$ reassemble into a modular form
of weight $(\dim\fg)/2$.

\subsection{The harmonic number organizes the $\cW_N$ landscape}

\providecommand{\rhoN}{\rho_N}
\providecommand{\alphaN}{\alpha_N}

For the principal $\cW_N$-algebra with spin spectrum
$\{2,3,\ldots,N\}$, define the \emph{anomaly ratio}
\[
  \rhoN
  \;=\;
  H_N - 1
  \;=\;
  \sum_{s=2}^{N}\frac{1}{s},
\]
where $H_N = \sum_{j=1}^{N}1/j$ is the $N$-th harmonic number.
This single quantity organizes the entire $\cW_N$ landscape:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}ll@{}}
\textbf{Datum} & \textbf{Formula} \\
\hline
Modular characteristic & $\kappa(\cW_N) = \rhoN \cdot c$ \\
Koszul involution & $c \;\mapsto\; \alphaN - c$ \\
Complementarity constant & $K_N = \kappa + \kappa^! = \rhoN \cdot \alphaN$ \\
Critical string & $c_{\mathrm{crit}} = \alphaN$ \\
Self-dual point & $c_{\mathrm{sd}} = \alphaN/2$
\end{tabular}
\end{center}
Here $\alphaN = \sum_{s=2}^{N}2(6s^2-6s+1)$ is the total ghost
central charge.  The per-generator curvature of a spin-$s$ field is
$c/s$; the anomaly ratio $\rhoN = \sum_{s=2}^{N}1/s$ is the sum of
their reciprocals.  The harmonic series is the shadow of the spin
spectrum through the per-generator curvature.

The harmonic number also controls the depth spectrum.  The
$E_1$-ordered bar depth spectrum
$\mathrm{Spec}(d^{E_1}; \cW_N)\big|_{(0,2)}$ is
$\{0,1,\ldots,2N{-}1\}\setminus\{2N{-}2\}$: a single gap at
$d_{\mathrm{gap}} = 2N{-}2$, migrating linearly with~$N$.  The
mechanism is a vacuum selection rule: $\dim\bar{V}_1 = 0$ forces
$W^{(s)}_{(2s-2)}W^{(s)} = 0$, while cross-channel contributions
fill all other depths at generic~$c$.  For Virasoro ($N=2$) the gap
is at $d=2$, for $\cW_3$ at $d=4$, for $\cW_4$ at $d=6$; the
formula $d_{\mathrm{gap}} = 2N{-}2$ is proved for all principal
$\cW_N$ by induction on the spin spectrum.

The weight grading on the ordered bar complex governs both the
depth spectrum and the combinatorial complexity.  At the
pointwise level, the weight-depth identity $w + d = n - 1$
constrains each monomial in~$m_n$, producing the structural
gap at $d = n$ (Theorem~\ref{thm:gap-migration}).  At the
generating-function level, the same grading produces the master
formula $\chi = -1 + 1/\operatorname{ch}(\cA;\,q)$
(Theorem~\ref{thm:euler-eta-identity}), connecting bar-complex
combinatorics to the Dedekind $\eta$-function.  The two results
are the fibre and the total-space views of the same weight
filtration.

As $N \to \infty$, the anomaly ratio diverges logarithmically:
$\rhoN \sim \log N$, and $K_N \sim 4N^3\log N$.  The
$\cW_\infty$-algebra, which controls the higher-spin holographic
dual, has infinite anomaly ratio: the genus tower is never tame, and
the curved bar structure is infinitely deep.  The harmonic divergence
is the reason higher-spin gravity in three dimensions is qualitatively
more complex than spin-$2$ gravity: each additional spin contributes
an ever-smaller but never-vanishing fraction $1/s$ to the total
curvature, and the harmonic series accumulates these fractions without
bound.

\subsection{Geometric Langlands as the $\kappa=0$ slice}

The bar-cobar programme parametrises a family of Swiss-cheese
coalgebras indexed by the modular characteristic~$\kappa$.  At
generic~$\kappa$, the bar complex is curved: $d_{\barB}^2 =
\kappa(\cA)\cdot\omega_g$, and the genus tower is controlled by the
$\hat{A}$-genus.  The curvature is the obstruction to extending the
genus-$0$ Lagrangian through the boundary strata of~$\Mbar_{g,n}$.

At $\kappa = 0$, the bar complex is uncurved at all genera: $d_{\barB}^2 =
0$, and the genus tower collapses.  For an affine Kac--Moody algebra
$\widehat{\fg}_k$, this occurs at the critical level $k = -h^\vee$,
where $\kappa(\widehat{\fg}_{-h^\vee}) = 0$.  The bar complex is
flat, but its cohomology is not trivial: the Feigin--Frenkel theorem
identifies the center of the completed enveloping algebra
$\tilde{U}(\widehat{\fg}_{-h^\vee})$ with the algebra of functions on
the space of $\check{G}$-opers on the formal disk, where $\check{G}$
is the Langlands dual group.  The bar cohomology at $\kappa = 0$
is the space of Langlands-dual opers.

The \emph{local} geometric Langlands programme begins at
$\kappa = 0$.  The Feigin--Frenkel isomorphism identifies the
center of the critical-level completed enveloping algebra with
functions on Langlands-dual opers on the formal disk; the bar
complex at $\kappa = 0$ provides this local input.  The
\emph{global} programme (D-modules on $\mathrm{Bun}_G$,
Hecke eigensheaves, the localization of Beilinson--Drinfeld)
builds on this local data but requires globalisation machinery
(spectral decomposition, the affine Grassmannian, the
quantum group at a root of unity) that lies beyond the
bar-cobar framework as developed here.
In the Lagrangian picture, $\kappa = 0$ is
the locus where $\cL_\cA$ lies in the zero section of
the Hodge bundle: the family over $\Mbar_{g,n}$ is constant, the
self-intersection is undeformed, and the endomorphism algebra is
independent of the modular parameter.  We view the full bar-cobar
programme, with its curved genus tower and $\hat{A}$-genus
coefficients, as the algebraic kernel of the quantum geometric
Langlands programme of Kazhdan--Lusztig and Bezrukavnikov: a
one-parameter deformation of the local Langlands data away from
the critical level, though the full identification requires their
localization machinery.

\subsection{Helicity is chirality}
\label{subsec:conclusion-helicity-chirality}

The Swiss-cheese operad $\SCchtop$ has two colours: the closed colour,
whose operations are parametrised by $\FM_k(\C)$ and encode
holomorphic factorisation; and the open colour, whose operations are
parametrised by $E_1$ and encode topological concatenation.  In the
celestial holography of Part~VIII, these two colours are the two
helicities of massless scattering amplitudes
(Theorem~\ref{thm:ch-core-helicity-chirality}).

This is not a dictionary imposed by analogy.  It is a structural
identification at the level of the operadic foundations: the bar
differential, which lives in the $\C$-direction, encodes the
self-dual (positive-helicity) sector; the Koszul dual product, which
lives in the $\R$-direction, encodes the anti-self-dual
(negative-helicity) sector; and the mixed-colour bulk-boundary
interaction encodes mixed-helicity amplitudes as open-closed
couplings.  The no-open-to-closed rule of the Swiss-cheese operad
(the strict directionality that bulk interactions restrict to
boundaries but not conversely) is the helicity selection rule:
negative-helicity states cannot generate positive-helicity states by
OPE alone.

Helicity splitting is Swiss-cheese decomposition.  The two helicities
of a graviton are the two colours of the endomorphism algebra at a
point in the derived symplectic category.

\begin{remark}[S-duality as colour exchange]
\label{rem:s-duality-colour-exchange}
The two colours of $\SCchtop$, the closed (holomorphic,
$\FM_k(\C)$) and the open (topological, $E_1$), are exchanged by
S-duality in the sense of Kapustin--Witten.  The Kapustin--Witten
twist of $\cN=4$ super Yang--Mills at coupling $\tau$ produces an HT
theory on $\C_z \times \R_t$ whose boundary conditions are either
Neumann (the open colour, supporting the boundary chiral algebra
$\cA_b$) or Dirichlet (the closed colour, supporting the bulk
factorization algebra).  Electric-magnetic duality $\tau \mapsto
-1/\tau$ exchanges Neumann and Dirichlet boundary conditions, hence
exchanges the two colours:
\[
  \text{S-duality}\colon\quad
  \underbrace{\cA^!_{\mathrm{ch}}}_{\text{closed/Verdier dual}}
  \;\longleftrightarrow\;
  \underbrace{\cA^!_{\mathrm{line}}}_{\text{open/linear dual}}.
\]
In the two-colour architecture of
Remark~\ref{rem:two-colour-architecture}, this is the exchange of the
Verdier-duality functor $D_{\mathrm{Ran}}$ (which produces
D-modules on $\mathrm{Bun}_G$) with the linear-duality functor
$H^*(\text{--})^\vee$ (which produces quasi-coherent sheaves on
$\mathrm{LocSys}_{G^\vee}$).  The geometric Langlands
correspondence
\[
  \mathrm{D}\text{-}\mathrm{mod}(\mathrm{Bun}_G)
  \;\simeq\;
  \mathrm{QCoh}(\mathrm{LocSys}_{G^\vee})
\]
is, from the bar-complex viewpoint, the statement that the two
Koszul duals (one for each colour of the Swiss-cheese operad)
are Langlands dual to each other.  The commutator-shadow spectral
sequence (Theorem~\ref{conj:FG-shadow}), which mediates between
$\cA^!_{\mathrm{ch}}$ and $\cA^!_{\mathrm{line}}$, is then the
local avatar of this exchange: it connects the automorphic side
(closed-colour, Verdier-dual D-modules) to the spectral side
(open-colour, linear-dual local systems) through the commutator
filtration on the bar complex.

This perspective recovers the Kapustin--Witten interpretation of the
geometric Langlands programme as S-duality of boundary conditions,
but from the purely algebraic datum of the two-colour Koszul
duality.  The Swiss-cheese operad does not know about gauge
coupling; it knows about two colours and their interaction maps.
That this two-colour structure, when specialized to the
$\cN=4$ theory, recovers the Langlands correspondence is the
bar-complex avatar of the Kapustin--Witten theorem.
\end{remark}

\subsection{The genus tower is a chromatic shadow}

The scalar genus tower
$F^{\mathrm{tot}}(\cA;\hbar)
= (\kappa(\cA)/\hbar^2) \cdot (\hbar/2)/\sin(\hbar/2)$
(Theorem~\ref{thm:ahat-lagrangian})
has a precise homotopy-theoretic identity.
The generating function $\hat{A}(ix) = (x/2)/\sin(x/2)$
is the constant term ($q^0$ coefficient) of the
Witten genus characteristic series.
The higher powers of~$q$ are supplied by
the Eisenstein-weighted genus-$1$ corrections of
Remark~\ref{rem:eisenstein-weighted-genus1}:
on an elliptic curve~$E_\tau$, the bar kernel
$1/(z{-}w)$ is replaced by the Weierstrass
$\zeta$-function $\zeta(z{-}w|\tau)$, whose
Taylor coefficients are the Eisenstein series $E_{2k}(\tau)$.
For $k \ge 2$ these are sections of $\omega^{\otimes 2k}$
on~$\cM_{1,1}$; the leading weight-$2$ coefficient $E_2$
is quasi-modular (the Arakelov defect of
Proposition~\ref{prop:genus-1-arnold-defect}).

The convergence properties of the genus tower are now partially
resolved.  The scalar generating function
$F^{\mathrm{tot}}(\cA;\hbar) = (\kappa/\hbar^2) \cdot
(\hbar/2)/\sin(\hbar/2)$ has radius of convergence
$|\hbar| < 2\pi$, corresponding to $c > 6.125$ for the Virasoro
sector (where $\kappa = c/2$ and
$\hbar_{\mathrm{crit}} = 2\pi/\sqrt{\kappa}$).  In the
field sector, the Bernoulli coefficients $|B_{2g}|/(2g)!$ grow
as $(2g)!^{-1} \cdot 2(2g)!/(2\pi)^{2g}$, and the resulting
series is Gevrey-$1$: Borel-summable but not convergent.  The
scalar sector converges; the field sector is asymptotic.

The genus tower admits two readings of a single
vanishing criterion: homotopy-theoretically, it is the
rational projection of a height-$2$ invariant, so that
$F_g = 0$ for all~$g$ precisely when the curvature
$\kappa_{\mathrm{eff}}$ vanishes; physically, this same
vanishing is the condition that the modular $S$-transform
be a symmetry of the effective partition function
(\S\ref{obs:genus-tower-wick-anomaly}).
Three features of the projection are structural:
\begin{enumerate}[label=(\roman*)]
\item The curvature $\kappa(\cA) \cdot \omega_g$
  plays the role of a periodicity generator:
  its invertibility creates Clifford periodicity on the
  transgression algebra; its vanishing
  collapses the genus tower to the rational sector.
\item Both invariants are coefficients of the
  $\hat{A}$-genus $(x/2)/\sinh(x/2)$: the genus tower
  extracts $|B_{2g}|/(2g)!$, the $J$-image extracts
  $\mathrm{denom}(B_{2g}/(4g))$, complementary
  rational and arithmetic readings of the same
  Bernoulli number~$B_{2g}$.  Whether this parallelism
  lifts to a structural connection through the
  $KO$-theoretic shadow of the Witten genus is open.
\item The non-separating clutching
  $D_1 \colon B^{(g)} \to B^{(g+1)}$,
  the sole genus-raising primitive,
  adds one handle to the curve, hence
  one dimension to the Jacobian (whose $p$-divisible
  group has height~$2g$, increasing by~$2$ per handle).
  Whether this operation is a geometric counterpart
  of chromatic redshift remains an open analogy.
\end{enumerate}
The common thread is that the $\hat{A}$-genus mediates between
chiral algebra and stable homotopy theory: the same Bernoulli
coefficients that control the genus tower also control the image
of~$J$ and the denominators of $L$-values.  The bar complex
computes these coefficients from OPE data; spectralization would
explain \emph{why}.

The smashing-localisation theorem
(Theorem~\ref{thm:smashing-localization}) guarantees that
chromatic localisations are compatible with factorization
homology after spectralization.
The construction of the spectral lift itself is the open
problem (Conjecture~\ref{conj:chromatic-lift};
\S\ref{sec:transchromatic-genus-tower}).

\subsection{The genus tower of quantum groups}
\label{subsec:genus-tower-quantum-groups}

The bar kernel on a genus-$g$ curve determines a quantum group, and
the passage from genus~$0$ to higher genus replaces the classical
Yang--Baxter mechanism at each step.  The following table collects
the structural data:
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{@{}clll@{}}
\textbf{Genus} & \textbf{Kernel} & \textbf{Quantum group}
  & \textbf{CYBE mechanism} \\
\hline
$0$ & $1/z$ (rational) & $Y_\hbar(\fg)$ (Yangian) & Partial fractions \\
$1$ & $\zeta(z|\tau),\;\wp(z|\tau)$
    & $E_{q,p}(\mathfrak{sl}_2)$ (elliptic) & Weierstrass addition \\
$2$ & $f(z,w),\;B(z,w)$ on $\Sigma_2$
    & $L_2(\mathfrak{sl}_2)$ (AGS) & Fay trisecant \\
$g$ & Szeg\H{o} kernel on $\Sigma_g$
    & $L_g(\fg)$ & Higher Fay
\end{tabular}
\end{center}
At genus~$0$ the bar kernel is $1/z$, the partial-fraction
decomposition $1/z_{12} = 1/z_{13} + 1/z_{32}$ is the classical
Yang--Baxter equation, and the resulting quantum group is the
Yangian $Y_\hbar(\fg)$.  At genus~$1$ the kernel upgrades to the
Weierstrass $\zeta$-function $\zeta(z|\tau)$: the CYBE is now
the Weierstrass addition formula
$\zeta(u+v) = \zeta(u) + \zeta(v) + \tfrac{1}{2}\bigl(\wp'(u)
- \wp'(v)\bigr)/\bigl(\wp(u) - \wp(v)\bigr)$,
and the quantum group is the Felder--Varchenko elliptic quantum
group $E_{q,p}(\mathfrak{sl}_2)$ with $q = e^{2\pi i/(k+2)}$
and $p = e^{2\pi i\tau}$.  The Arnold defect $E_2(\tau)$ of
Proposition~\ref{prop:genus-1-arnold-defect} is exactly the
failure of $\zeta$ to be doubly periodic: the Arakelov correction
that distinguishes the elliptic $r$-matrix from the rational one.

At genus~$2$ the bar kernel is the prime form $E(z,w)$ and the
Bergman kernel $B(z,w)$ on the Riemann surface $\Sigma_2$; the
CYBE mechanism is the Fay trisecant identity, and the quantum
group is the genus-$2$ Levin $L_2(\mathfrak{sl}_2)$ (the
Alekseev--Grosse--Schomerus construction applied at genus~$2$,
identified in Remark~\ref{rem:eisenstein-weighted-genus1}).  At
genus~$g$, the Szeg\H{o} kernel on $\Sigma_g$ governs the bar
differential, the higher Fay identities replace the classical
Yang--Baxter relation, and the resulting algebraic structure is
the genus-$g$ quantum group $L_g(\fg)$.

Each row of the table is the bar complex of the same chiral
algebra~$\cA$ on a different curve.  The genus tower of quantum
groups is the shadow of the genus tower of bar complexes: the
non-separating clutching $D_1 \colon B^{(g)} \to B^{(g+1)}$ that
adds a handle to the curve simultaneously promotes the CYBE
mechanism (partial fractions $\to$ Weierstrass $\to$ Fay $\to$
higher Fay) and the quantum group ($Y_\hbar \to E_{q,p} \to
L_2 \to L_g$).  The depth of the self-intersection increases
with the genus, and at each step the addition theorem of the
kernel function is the new integrability condition that the bar
differential must satisfy.

\subsection{Four stages from chiral algebra to chromatic invariant}

\[
  \cA
  \;\xrightarrow{\;\mathrm{bar}\;}
  B_{\mathrm{mod}}(\cA)
  \;\xrightarrow{\;\mathrm{FT}_{\mathrm{rel}}\;}
  \cZ_\cA
  \;\xrightarrow{\;\text{sp.\ lift}\;}
  \cZ_\cA^{\mathrm{sp}}
  \;\xrightarrow{\;L_{K(n)}\;}
  \cZ_{\cA,n}\,.
\]
Stages~$1$--$2$ (modular bar construction and relative
Feynman transform) are proved in Part~III.
Stage~$3$ (spectralization) is the open problem.
Stage~$4$ (chromatic localisation) is automatic.

\subsubsection*{Five obstructions to spectralization}

The following are open problems, not conjectures.  Each identifies
a specific obstruction to Stage~$3$ of the pipeline
$\cA \to B_{\mathrm{mod}}(\cA) \to \cZ_\cA \to \cZ_\cA^{\mathrm{sp}}
\to \cZ_{\cA,n}$.

\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Base ring problem.}
  $B(\cA)$ is a chain complex over~$\C$.  Spectra are not
  $\C$-modules: one needs an integral form $B(\cA)_\Z$, a chain
  complex over~$\Z$ with $B(\cA)_\Z \otimes_\Z \C \simeq B(\cA)$.
  For Kac--Moody algebras at integral level, such forms exist
  (Garland).  For general chiral algebras, no canonical integral
  form is known.

\item \textbf{Operadic coherence.}
  $\SCchtop$ involves $\C$-linear algebraic data: FM
  compactification of configurations in~$\C$, logarithmic weight
  forms, residue pairings.  Lifting to an operad in spectra
  requires understanding the interaction between holomorphic
  structure and stable homotopy theory.

\item \textbf{Formal group identification.}
  The genus-$1$ bar differential (Movement~I) uses the formal
  group of~$E_\tau$, but as complex-analytic functions
  (Weierstrass~$\zeta$), not as formal group laws over~$\Z$.
  Connecting to $\mathrm{tmf}$ requires the formal group law
  over $\Z[c_4, c_6, \Delta^{-1}]$.

\item \textbf{No genus tower maps.}
  There are no natural maps
  $\overline{\mathcal{M}}_g \to \overline{\mathcal{M}}_{g-1}$.
  The genus tower is an expansion indexed by~$g$, not a sequential
  limit.  The chromatic convergence analogy (limit over
  $E(n)$-localizations) has no direct geometric counterpart
  on the moduli side.

\item \textbf{Height discrepancy.}
  Non-separating clutching~$D_1$ raises $p$-divisible-group height
  by~$2$ ($\mathrm{ht} = 2 \cdot \dim$ for abelian varieties).
  Chromatic redshift ($\mathrm{THH}$/$\mathrm{TAQ}$) raises
  chromatic height by~$1$.  The factor-of-$2$ mismatch is
  unexplained.
\end{enumerate}

The Stolz--Teichner programme predicts that stage~$3$,
for the chiral de~Rham complex of a string manifold,
yields the Ando--Hopkins--Rezk string orientation
$\sigma \colon M\mathrm{String} \to \mathit{tmf}$, with
the Costello--Gwilliam quantisation anomaly providing
$p_1/2 = 0$.

\medskip

Each panoramic theme (the quartic pole, the harmonic number, the
flat slice, the helicity splitting, the chromatic shadow) is a
different projection of the Lagrangian self-intersection.
They converge on the same question: what happens at genus~$g \ge 1$?

%% ====================================================================
%%  MOVEMENT III: FORWARD PROGRAMME
%% ====================================================================
\section*{Movement III\@: Forward programme}

The genus-zero theory is complete.  The constructions
of this volume supply the local data; what remains is the extension
to all genera, the global assembly over $\Mbar_{g,n}$.

\subsection{The modular holography programme}
\label{subsec:modular-holography-programme}

The constructions of this volume, together with Volume~I's modular
engine, indicate that holomorphic-topological holography is a
\emph{modular} phenomenon, not a genus-zero boundary VOA phenomenon: the
boundary chiral algebra is the shadow of a modular Maurer--Cartan
problem, and the holographic dictionary lifts from the disk to all genera
via modular Maurer--Cartan theory.

The compact slogan is:
\begin{gather*}
  \text{stable-graph summation}
  \;+\;
  \text{logarithmic configuration geometry}\\
  {}+\;
  \underbrace{\text{strictification of spectral quasi-data}}_{\text{Thm~\ref{thm:complete-strictification}}}
  \;=\;
  \text{modular holography}.
\end{gather*}

Three guiding questions structure the programme.

\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Existence.}
  \ClaimStatusConjectured{}
  Does the genus-zero open/closed MC element
  $\Theta^{\mathrm{oc}}|_{g=0}$, assembled from CDG
  boundary chiral algebras, Zeng's KK reduction, GKW higher operations,
  and DNP dg-shifted Yangians, extend to a full modular MC element
  $\Theta^{\mathrm{oc}} \in \mathrm{MC}(\mathfrak{g}^{\mathrm{mod}}_\cA)$
  via bar-cobar or deformation-theoretic completion over the modular
  operad $C_\bullet(\overline{\mathcal{M}}_{g,n})$?
  \emph{Note:} the genus-zero existence is now established by
  Theorem~\ref{thm:general-half-space-bv} (the doubling theorem),
  which constructs the full half-space BV package at genus~$0$;
  the remaining content of this question is the extension to
  genus~$g \ge 1$.

\item \textbf{Geometry.}
  \ClaimStatusConjectured{}
  Can the sewing component of $\Theta^{\mathrm{oc}}$ (the
  stable-graph differential $d_{\mathrm{sew}}$) be realized by
  explicit integrals over
  logarithmic Fulton--MacPherson spaces and their degeneration
  correspondences (cf.\ Mok)?

\item \textbf{Computation.}
  \ClaimStatusConjectured{}
  Can one compute the first genuinely modular projections of
  $\Theta^{\mathrm{oc}}$, namely the
  genus-refined Yangian kernel
  $R_{\mathcal{T}}^{\mathrm{mod}}(z;\hbar)$, in the three basic
  examples: free $\beta\gamma$, Kodaira--Spencer holography, and the
  $\mathcal{W}_3$ Poisson sigma model?
\end{enumerate}

\noindent
The free $\beta\gamma$ system is the strict free test case (genus
dependence enters only through determinant lines and factorization
homology).  Kodaira--Spencer holography is the holographic open/closed
test case with explicit universal defect algebra.  The $\mathcal{W}_3$
PVA is the first nonlinear higher-spin arena where modular dg-shifted
Yangians genuinely meet stable-curve gluing.

\begin{remark}[A fourth worked example: the M2-brane model]
\label{rem:m2-brane-model}
Costello's M2-brane example provides a fourth arena that exercises the full modular
machine.  Starting from 11d twisted M-theory, one reduces to 5d noncommutative
Chern--Simons theory on $\R \times \C^2$.  The boundary algebra is a \emph{quantum
double-loop algebra}: the unique filtered quantization of
$\mathfrak{gl}_r \otimes \C[u,v]$, where $(u,v)$ are the coordinates on~$\C^2$.
Its Koszul dual
\[
\mathcal{A}_{M2}^!
\;=\;
H^\bullet\bigl(\bar{B}(\mathcal{A}_{M2,\infty})\bigr)^{\vee}
\]
is the holographic dual obtained by Verdier duality on bar cohomology.
The matching between bulk and boundary is explicit:
\begin{itemize}
\item sector $\longleftrightarrow$ adjoint label,
\item level $\longleftrightarrow$ double-loop bidegree in $(u,v)$,
\item $N$ (rank) $\longleftrightarrow$ trace-relation quotient,
\item genus $\longleftrightarrow$ loop order in the 5d theory.
\end{itemize}
The full modular homotopy type assembles as
\begin{equation}
\label{eq:m2-modular-homotopy-type}
\mathcal{D}_{M2}
\;=\;
d_{A_\infty}^{M2} + d_{\mathrm{sew}}^{M2} + \hbar\,\Delta_{5d} + d_r^{M2},
\end{equation}
with $d_{A_\infty}^{M2}$ the bar differential, $d_{\mathrm{sew}}^{M2}$ the stable-graph
sewing, $\Delta_{5d}$ the BV Laplacian from the 5d bulk, and $d_r^{M2}$ the spectral
twist.  The algebraic engine of Volume~I and the 3d HT framework of this volume
converge here to a single, computable object.
\end{remark}

The volume's Swiss-cheese recognition theorem
(Theorem~\ref{thm:recognition-foundations}), homotopy-Koszulity of
$\SCchtop$ (Theorem~\ref{thm:homotopy-Koszul}), and the Hochschild
bridge (Theorem~\ref{thm:hochschild-bridge-genus0}) provide the
algebraic foundations.  Volume~I's five main theorems (bar-cobar
adjunction (Theorem~A), inversion (Theorem~B), complementarity
(Theorem~C), modular characteristic (Theorem~D), and Hochschild
polynomial (Theorem~H)) provide the engine.


\begin{remark}[The graph-completed frontier]
\label{rem:graph-completed-frontier}
Volume~I's nonlinear modular shadows appendix now extends the proved
shadow obstruction tower into a coherent frontier programme.  Three objects
organize the forward attack:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the \emph{modular chiral Feynman
  transform}~$\mathfrak{F}_{\mathrm{mod}}(\cA)$, a graph-completed
  dg object carrying the Maurer--Cartan master
  element~$\boldsymbol\Theta_\cA$
  from the bar-intrinsic construction of Volume~I, whose projections recover
  the entire modular characteristic hierarchy;
\item the \emph{polarized modular graph algebra}
  $\mathcal{G}^{\pm}_{\mathrm{mod}}(\cA)$ with bipartite
  same-colour vanishing, whose \emph{resonance scattering diagram}
  $\mathfrak{Scat}(\cA)$ governs wall-crossing of nonlinear
  modular data;
\item the \emph{complementarity Legendrian}
  $\Lambda_\cA = j^1 S_\cA$, which contactifies the
  complementarity potential and gives geometric meaning to the
  resonance tower as front-singularity discriminants.
\end{enumerate}
For this volume, the immediate consequence is that the modular
wavefunction $\Psi_\cA$ of the quantization programme is controlled by
the graph-completed master element: its semiclassical expansion
produces the genus tower, and its local singularity type is determined
by the nonlinear shadow archetype (Gaussian, Airy, Pearcey, or mixed
catastrophe).  The curved Swiss-cheese structure of
Theorem~\ref{thm:curved-swiss-cheese} provides the physical
incarnation of the edge-insertion differential~$d_{\mathrm{edge}}$.
\end{remark}

\subsection{Concrete consequences and open problems}

The following table compresses the principal results and open problems
arising from the constructions of this volume combined with Volume~I's
five main theorems.

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}p{5.8cm}lp{4.0cm}@{}}
\textbf{Result} & \textbf{Status} & \textbf{Location} \\
\hline
Jones polynomial from bar complex integrals
  & Proved
  & Thm~\ref{thm:affine-monodromy-identification},
    Cor~\ref{cor:jones-polynomial} \\
MC5: $d_{\barB}^2 = \kappa(\cA)\!\cdot\!\omega_g$ from BV-BRST
  & Proved ($g{=}0$); Conj.\ ($g{\ge}1$)
  & Thm~\ref{thm:mc5-genus-zero-bridge},
    Conj~\ref{conj:master-bv-brst} \\
DS reduction commutes with SC structure
  & Demonstrated ($\widehat{\mathfrak{sl}}_N$)
  & \S\ref{sec:W-algebras} \\
Higher-genus $\Ainf$ with spectral parameters
  & Open (target: curved SC)
  & Thm~\ref{thm:curved-swiss-cheese} \\
Curvature--braiding entanglement at $g{=}1$:
  $\kappa$ and $R(z)$ mix when $c_0\!\neq\!0$
  & Resolved (genuine)
  & Obstruction class in
    $\mathrm{QMod}_2/\mathrm{Mod}_2$ \\
Spectral braiding beyond evaluation locus
  & Open
  & Obstructions in
    $\mathrm{ChirHoch}^3(\cA)$ \\
Screening domination: do screenings
  generate $\ker(Q_{\mathrm{BRST}})$?
  & Open
  & \S\ref*{sec:ym-synthesis} \\
Commutator-shadow: $\mathrm{gr}\,B^{\Sigma}(\cA) \!\simeq\! B^{\mathrm{FG}}(\cA)$
  & Proved
  & Thm~\ref{conj:FG-shadow} \\
Complete strictification (simple Lie)
  & Proved; KM frontier open
  & Thm~\ref{thm:complete-strictification} \\
Loop-order criterion for Koszulness
  & Proved (affine lineage)
  & Thm~\ref{thm:one-loop-koszul},
    Thm~\ref{thm:semisimple-purity} \\
Half-space programme (doubling)
  & Proved
  & Thm~\ref{thm:general-half-space-bv},
    Thm~\ref{thm:doubling-rwi} \\
\end{tabular}
\end{center}

%% ====================================================================
%%  MOVEMENT IV: DICTIONARY
%% ====================================================================
\section*{Movement IV\@: Dictionary}

The forward programme names the frontier.  What follows records the
territory already secured: the structural bridges between
Vol~I's five theorems and Vol~II's three-dimensional reading, the
purity data of the three Swiss-cheese colours, the complementarity
table, and the proofs that crystallize only in the light of the full
two-volume architecture.

\subsection{The cross-volume bridge}

The five theorems of Volume~I arise as projections of the modular
MC element, while Volume~II reads their closed/open/mixed
three-dimensional descendants through the Swiss-cheese MC package:
Theorem~A specializes to $\SCchtop$-bar-cobar when the curve is
$\C$ and the topological direction is~$\R$;
the spectral $R$-matrix recovers the DK-0 shadow of the
Drinfeld--Kohno ladder via the Laplace transform of the
$\lambda$-bracket;
chiral Hochschild cohomology is the physical origin of Theorem~H;
the curved genus tower is Theorem~D in its physical incarnation.
The complete strictification theorem
(Theorem~\ref{thm:complete-strictification}) adds a sixth bridge:
the spectral Drinfeld class, which a priori could obstruct the
passage from spectral quasi-factorization data to strict factorization quantum groups,
vanishes identically; the rigidity is not imposed but inherited
from the root-multiplicity-one structure of simple Lie algebras.
This is the ordered/open-sector analogue
(\S\ref{ch:ordered-associative-chiral-kd}) of homotopy-Koszulity for
the closed sector: both are structural consequences of the underlying
Lie theory, not of the specific HT dynamics.
The topological $E_1$ rigidity theorem
(Theorem~\ref{thm:topological-e1-rigidity}) adds a seventh
bridge: the $E_1$ coproduct is genus-independent because it
is a purely combinatorial operation on ordered tensor
products, and the ordered/open $E_1$ factorization structure
persists at all genera
(Proposition~\ref{prop:R-canonical-vol2}).  The modular
strictification theorem
(Theorem~\ref{thm:complete-strictification}) shows that the
modular spectral Drinfeld class vanishes for all simple Lie
algebras, so any modular quasi-factorization datum
strictifies once constructed, and the descent from ordered
to unordered bar complexes is well-defined at all genera.
The general half-space BV theorem
(Theorem~\ref{thm:general-half-space-bv}) adds an eighth bridge:
by doubling the half-space $\C_z \times \R_{\ge 0}$ to the full
bulk $\C_z \times \R_t$, it constructs the mixed-color
bulk-boundary interaction as a reflection of the pure-color data,
completing the Swiss-cheese triad of closed, open, and mixed bridges.
The affine monodromy identification
(Theorem~\ref{thm:affine-monodromy-identification}) adds a ninth
bridge: for the affine lineage, one-loop exactness collapses the
$\Ainf$ tower, the reduced HT monodromy equals the KZ monodromy,
and the affine Drinfeld--Kohno theorem compares it with the
corresponding braided tensor-product representation of
$\mathrm{Rep}_q(\mathfrak{sl}_2)$ on the reduced evaluation
comparison surface, proving
$\cC_{\mathrm{line}}^{\mathrm{red}}\simeq \mathrm{Rep}_q(\fg)$
there and computing
the Jones polynomial from the bar complex.
The remaining bridges cluster into three thematic groups.

\medskip\noindent
\textbf{Reduction and transport.}\enspace
The DS--modular bar intertwining theorem
(Theorem~\ref{thm:ds-modular-intertwining}) extends Vol~I's
genus-$0$ intertwining $\barB \circ \mathrm{DS}_\chi
\simeq \mathrm{DS}_\chi \circ \barB$ to the full modular
bar complex at all genera: the BRST charge $Q_{\mathrm{DS}}$
commutes with both the genus-preserving differential $D_0$ and the
genus-raising clutching operator~$D_1$, and Arakawa vanishing
collapses the resulting spectral sequence.
The gauge-gravity dichotomy
(Corollary~\ref{cor:gauge-gravity-dichotomy}) is the consequence:
the pole-order class (L vs~M) determines whether
the bar complex has finite or infinite shadow depth, and
DS reduction transports class~L (affine, double-pole OPE)
to class~M (Virasoro, quartic-pole OPE), so that the
gravitational sector inherits genuinely infinite $\Ainf$
complexity from the gauge sector via the Sugawara construction.

\medskip\noindent
\textbf{Two-colour architecture.}\enspace
The two-colour Koszul duality
(Remark~\ref{rem:two-colour-architecture}) is the structural
skeleton: the closed colour uses Verdier duality $D_{\mathrm{Ran}}$
(producing a chiral algebra $\cA^!_{\mathrm{ch}}$), the
open colour uses linear duality $H^*(\text{--})^\vee$
(producing the dg-shifted Yangian $\cA^!_{\mathrm{line}}$), and
the commutator-shadow spectral sequence
(Theorem~\ref{conj:FG-shadow}) mediates between them: on the Koszul
locus, the associated graded of the full chiral Koszul dual with
respect to the commutator filtration recovers the
Francis--Gaitsgory (chiral Lie) Koszul dual, connecting the
zeroth-pole data to the full OPE data through a convergent spectral
sequence.

\medskip\noindent
\textbf{The annular sector.}\enspace
The annular bar differential
(Theorem~\ref{thm:annular-bar-differential}) connects the
open-sector $E_1$ structure to the closed-sector trace: the
ordered bar complex on the annulus $S^1 \times \R$ computes
chiral Hochschild homology, realising the genus-$1$ ordered sector
as the categorical trace of the open-sector category.


\subsection{The three colors and their purity}

\begin{remark}[The three colors and their purity]
\label{rem:three-colors-purity}
The Swiss-cheese operad $\SCchtop$ has three structural components:
the closed color $\FM_k(\C)$ (holomorphic), the open color $E_1$
(topological), and the bulk-boundary interaction (the mixed
composition maps).  The three frontier results of this volume are the
obstruction theories for these three components:
\begin{center}
\begin{tabular}{lll}
\textbf{Color} & \textbf{Obstruction} & \textbf{Purity input} \\
\hline
Closed ($\FM_k(\C)$) & bar cohomology width & one-loop exactness \\
Open ($E_1$) & spectral Drinfeld class & root multiplicity one \\
Mixed (bulk-boundary) & reflected weight identity & $\sigma$-equivariant Stokes
\end{tabular}
\end{center}
The three inputs on the right are different manifestations of
rigidity: one-loop exactness means the effective BV action is
determined by a single loop order; root multiplicity one means
$\dim\fg_\alpha=1$; the $\sigma$-equivariant Stokes identity (the
doubling theorem, Theorem~\ref{thm:doubling-rwi}) embeds the
half-space reflected weight identity into the standard whole-space
Stokes identity.

The asymmetry between the three colors is structural.
The \emph{open-color} obstruction (spectral Drinfeld class) vanishes
universally for all simple Lie algebras, because root multiplicity one
is a property of the root system: it depends on $\fg$ alone, not on
the specific chiral algebra or HT theory.
The \emph{mixed-color} obstruction (reflected weight identity) vanishes
universally for any logarithmic $\SCchtop$-algebra, because the doubling construction embeds
it into the standard FM machinery
(Theorem~\ref{thm:general-half-space-bv}).
The \emph{closed-color} obstruction (Swiss-cheese formality) can
fail, because the collision purity of the OPE local system
depends on the specific algebra~$\cA$: Kac--Moody is
collision-pure and formally Koszul (one-loop exact); Virasoro
is chirally Koszul but not collision-pure (DS reduction introduces
non-formal higher operations while preserving bar concentration).

This is the Chriss--Ginzburg content of the Swiss-cheese structure.
The Steinberg variety presents the Hecke algebra because the geometry
of $G/B$ is rigid enough (purity of IC complexes) that the convolution
algebra is forced.  The bar complex presents the Swiss-cheese coalgebra
because the Lie theory of $\fg$ is rigid enough (root multiplicity one)
that the open color is forced, while the closed color retains algebraic
freedom.  Strictification is geometric; Koszulness is algebraic.
The bar complex classifies both.
\end{remark}

\subsection{The complementarity table}

\begin{remark}[The complementarity table]
\label{rem:complementarity-table}
\index{complementarity constant|textbf}
\index{shadow archetype|textbf}
The modular characteristic $\kappa(\cA)$ and its
Koszul-dual complement $\kappa(\cA^!)$ are computed
for the standard HT landscape
(Section~\ref{sec:examples_complete}):
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}lcccc@{}}
\textbf{Family}
  & $\kappa(\cA)$
  & $\kappa(\cA^!)$
  & $\kappa + \kappa^!$
  & \textbf{Class} \\
\hline
Heisenberg $\cH_k$ & $k$ & $-k$ & $0$ & $\mathbf{G}$ \\
Affine $\widehat{\mathfrak{sl}}_2$ & $\tfrac{3(k{+}2)}{4}$ &
  $\tfrac{3(-k{-}2)}{4}$ & $0$ & $\mathbf{L}$ \\
$\beta\gamma$ & $-1$ & $1$ & $0$ & $\mathbf{C}$ \\
Virasoro $\mathrm{Vir}_c$ & $c/2$ & $(26{-}c)/2$ & $13$
  & $\mathbf{M}$ \\
$\cW_3$ & $5c/6$ & $5(100{-}c)/6$ & $250/3$
  & $\mathbf{M}$ \\
\end{tabular}
\end{center}
The complementarity constant $\kappa(\cA) + \kappa(\cA^!)$ is
level-independent in every family (Vol~I, Theorem~C).
Shadow archetype:
$\mathbf{G}$ (depth~$2$),
$\mathbf{L}$ (depth~$3$),
$\mathbf{C}$ (depth~$4$),
$\mathbf{M}$ (depth~$\infty$).
\end{remark}

%% ====================================================================
%%  STRUCTURAL RESULTS PROVED IN THIS CONCLUSION
%% ====================================================================

\medskip

The dictionary summarizes the results by name and location.
The theorems that follow are the structural results that
crystallize only in the light of the full two-volume architecture:
the resolvent principle, the holographic reconstruction theorem,
and the tree--wheel evaluation identity.

\section*{Structural results proved in this conclusion}
\addcontentsline{toc}{subsection}{Structural results proved in this conclusion}

\noindent\textbf{The self-intersection resolvent.}


\begin{theorem}[The resolvent principle; \ClaimStatusProvedHere]
\label{thm:resolvent-principle}
\index{resolvent principle|textbf}
\index{homological perturbation!tree-level bootstrap|textbf}
Let\/ $\cA$ be an\/ $\Ainf$ chiral algebra with underlying
complex\/ $(\cA, m_1)$ and binary chiral product\/~$m_2$.
Let\/ $(H, p, \iota, h)$ be a deformation retract of\/
$(\cA, m_1)$ onto cohomology\/
$H = H^\bullet(\cA, m_1)$, satisfying the side conditions
$h^2 = h\iota = ph = 0$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Tree formula.}
  Cohomology~$H$ carries a transferred\/ $\Ainf$ structure
  with operations
  \begin{equation}
  \label{eq:resolvent-tree-formula}
    m_k^H
    \;=\;
    \sum_{\tau \in \mathrm{PRT}_k}
    (-1)^{\varepsilon(\tau)}\;
    p \circ \mathfrak{m}(\tau) \circ \iota^{\otimes k},
  \end{equation}
  where\/ $\mathrm{PRT}_k$ denotes planar rooted binary trees
  with\/ $k$ leaves, and\/ $\mathfrak{m}(\tau)$ assigns the binary
  product~$m_2$ to each internal vertex and the contracting
  homotopy~$h$ to each internal edge.
  Each tree with\/ $k$ leaves has\/ $k{-}1$ internal vertices
  and\/ $k{-}2$ internal edges; the number of such trees is
  the Catalan number\/~$C_{k-1}$.

\item \textbf{Tree-level bootstrap equation.}
  Define the \emph{dressed propagator}\/
  $\Phi = \sum_{k \geq 1} \Phi_k\colon T^+(H) \to \cA$ by
  $\Phi_1 = \iota$ and, for $k \geq 2$,
  \begin{equation}
  \label{eq:dressed-propagator}
    \Phi_k(a_1, \ldots, a_k)
    \;=\;
    \sum_{\substack{i+j = k \\ i,j \geq 1}}
    (-1)^{\varepsilon(i,j)}\;
    h \circ m_2\bigl(
      \Phi_i(a_1, \ldots, a_i),\;
      \Phi_j(a_{i+1}, \ldots, a_k)
    \bigr),
  \end{equation}
  where $\varepsilon(i,j) = |a_1| + \cdots + |a_i|$ is the total degree
  of the first $i$ desuspended inputs (the standard Koszul sign from the
  $(i,j)$-splitting of the desuspended tensor product).
  Compactly: $\Phi = \iota + h \circ m_2 \circ \Phi^{\otimes 2}$,
  where the tensor product sums over all ordered splittings.
  The total transferred operation
  $\mathfrak{M} = \sum_{k \geq 2} m_k^H$ is
  \begin{equation}
  \label{eq:chiral-dyson-schwinger}
    \mathfrak{M}
    \;=\;
    p \circ m_2 \circ \Phi^{\otimes 2}.
  \end{equation}

\item \textbf{Lagrangian identification.}
  The tree formula~\eqref{eq:resolvent-tree-formula} is the
  Feynman-diagram expansion of the derived self-intersection.
  The bar complex\/ $\barB(\cA) = T^c(s^{-1}\bar{\cA})$
  has $k$-chains $(s^{-1}\bar{\cA})^{\otimes k}$;
  the deformation retract
  contracts this to the transferred complex on~$H$ whose
  differential involves all\/ $m_k^H$.
  By Theorem~\textup{\ref{thm:bar-is-self-intersection}}\textup{(ii)},
  $\barB(\cA) \simeq \cO(\cL_\cA \times_{\Mvac}^h \cL_\cA)$:
  the bar complex is the structure sheaf of the derived
  self-intersection.
  Each tree~$\tau \in \mathrm{PRT}_k$ is a Feynman diagram
  with interaction vertices~$m_2$ and propagator lines~$h$;
  the sum over trees computes the structure constants of\/
  $\cO(\cL_\cA \times_{\Mvac} \cL_\cA)$.
\end{enumerate}
\end{theorem}

\begin{proof}
(i) is the Kadeishvili--Merkulov $\Ainf$ transfer theorem, applied
to the deformation retract data.  The sign $\varepsilon(T)$ is
determined by the Koszul convention on desuspended inputs
(Appendix~\ref{app:brace-signs}).

(ii) Every tree with $k \geq 2$ leaves has a root vertex
(contributing~$m_2$) connecting two subtrees with $k_1$ and $k_2$
leaves ($k_1 + k_2 = k$).  The contribution of each subtree is
$\Phi_{k_i}$: the inclusion $\iota$ if $k_i = 1$ (a single leaf),
or $h \circ m_2 \circ (\Phi_{k'_1} \otimes \Phi_{k'_2})$ if
$k_i \geq 2$ (an internal edge followed by a subtree).
Summing over all $(k_1, k_2)$ and all subtree shapes
reproduces~\eqref{eq:dressed-propagator}.  Existence and
uniqueness of the solution follow from the
formal-power-series contraction principle: filtered by tree
complexity, each iterate raises the filtration degree, so the
recursion converges in the complete topology on multilinear
operations.

(iii) The quasi-isomorphism
$\barB(\cA) \xrightarrow{\sim} \barB(H, m_\ast^H)$
induced by the deformation retract identifies each
$m_k^H$-contribution to the transferred bar differential with
the sum over trees in~\eqref{eq:resolvent-tree-formula}.
By Theorem~\ref{thm:bar-is-self-intersection}(ii),
the bar complex is the structure sheaf of the derived
self-intersection:
$\barB(\cA) \simeq \cO(\cL_\cA \times_{\Mvac}^h \cL_\cA)$.
The tree formula therefore computes the structure constants
of this derived self-intersection on the transferred
complex~$H$.
\end{proof}

\begin{remark}[Five names for the same equation]
\label{rem:five-names}
The tree-level bootstrap
equation~\eqref{eq:chiral-dyson-schwinger} is the computational
face of the Lagrangian condition.  The following five formulations
are strictly equivalent:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}ll@{}}
\textbf{Geometry} &
  $\omega_{\Mvac}\big|_{\cL_\cA} = 0$
  \quad (Lagrangian condition) \\
\textbf{Algebra} &
  $d_{\barB}^2 = 0$
  \quad (bar differential squares to zero) \\
\textbf{Deformation theory} &
  $d\alpha_T + \tfrac{1}{2}[\alpha_T, \alpha_T] = 0$
  \quad (Maurer--Cartan equation) \\
\textbf{Homotopy theory} &
  $\sum_{i+j=k+1} \pm\, m_i \circ m_j = 0$
  \quad ($\Ainf$ Stasheff identities) \\
\textbf{Quantum field theory} &
  $\Phi = \iota + h \circ m_2 \circ \Phi^{\otimes 2}$
  \quad (tree-level bootstrap)
\end{tabular}
\end{center}
Equivalences:
Algebra~$\Leftrightarrow$~Homotopy (Vol~I, Theorem~A);
Algebra~$\Leftrightarrow$~Deformation Theory
(Theorem~\ref{thm:MC-deformations-brace});
Homotopy~$\Leftrightarrow$~QFT
(Theorem~\ref{thm:resolvent-principle}(ii));
Geometry~$\Leftrightarrow$~Algebra
(Theorem~\ref{thm:bar-is-self-intersection}).
\end{remark}

\begin{remark}[The Catalan number in four roles]
\label{rem:four-pillars-catalan}%
\index{Catalan number!four roles|textbf}%
\index{Stasheff associahedron!Catalan roles}%
The resolvent principle expresses the transferred $\Ainf$ structure
as a sum over planar binary trees.  The Catalan number
$C_n = \frac{1}{n+1}\binom{2n}{n}$ that counts these trees
reappears in three further roles within the gravitational $\Ainf$
tower, each time through the same convolution identity
$C_n = \sum_{a=0}^{n-1} C_a C_{n-1-a}$:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Role} & \textbf{Where} & \textbf{Formula} & \textbf{Mechanism} \\
\midrule
Tree count &
  $\mathrm{PRT}_k$ &
  $|\mathrm{PRT}_k| = C_{k-1}$ &
  Planar binary trees \\
Field polynomial &
  $\varphi_k(0) = (-1)^n C_n \cdot k!$ &
  Thm~\ref{thm:period-2-parity}(iii) &
  Stasheff convolution \\
Shadow coefficient &
  $F_r(x) = \sum (-1)^j C_j \binom{r-4}{2j} x^j$ &
  Thm~\ref{thm:shadow-closed-form} &
  Ballot-problem recursion \\
Free probability &
  $C_n = \int x^n\,d\mu_{\mathrm{MP}}$ &
  Rem~\ref{rem:free-poisson-shadow} &
  Marchenko--Pastur moments \\
\bottomrule
\end{tabular}
\end{center}
The mechanism in every case is cutting a planar binary tree at
its root (the Catalan convolution), which is the combinatorial
avatar of the $E_1$-coproduct that cuts an ordered tensor product
into two sub-sequences.  The Catalan numbers are the topological
colour of the Swiss-cheese factorization; the Bernoulli numbers
(Movement~II, genus tower) are the holomorphic colour.  Their
interaction through the resolvent is what makes the gravitational
$\Ainf$ tower simultaneously combinatorial and arithmetic.
\end{remark}

\begin{corollary}[Koszulness and the resolvent;
\ClaimStatusProvedHere]
\label{cor:koszul-resolvent}
\index{Koszul!and the resolvent|textbf}
The following are equivalent:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\cA$ is Koszul: bar cohomology is generated in a single
  internal degree.
\item The self-intersection is clean:
  $\cL_\cA \times_{\Mvac} \cL_\cA$ is concentrated in the
  expected degree, with no excess\/ $\mathrm{Tor}$.
\item All higher operations vanish on cohomology:
  $m_k^H = 0$ for\/ $k \geq 3$.
\end{enumerate}
\end{corollary}

\begin{proof}
(a)$\Leftrightarrow$(b) is
Theorem~\ref{thm:bar-is-self-intersection}(ii):
bar cohomology in a single degree means the derived
self-intersection has no higher Tor.
(a)$\Leftrightarrow$(c) is the bar-cohomological characterisation
of Koszulness (Vol~I, Theorem~B): the bar complex is pure if and
only if the transferred $\Ainf$ structure is formal.
\end{proof}

\begin{proposition}[The spectral connection form;
\ClaimStatusProvedHere]
\label{prop:spectral-resolvent}
\index{resolvent!spectral connection|textbf}
Let $\{a \,{}_\lambda\, b\} = m_2^H(a,b)(\lambda)$ be the
transferred PVA bracket on cohomology, and let
$r_\cA(z) = \int_0^\infty e^{-\lambda z}
\{{\cdot}\,{}_\lambda\,{\cdot}\}\,d\lambda$
be the classical $r$-matrix of the DK-0 bridge
\textup{(}Proposition~\textup{\ref{prop:dk0-laplace-five-families}}\textup{)}.
When the self-intersection carries excess\/ $\mathrm{Tor}$
\textup{(}$m_k^H \neq 0$ for some\/ $k \geq 3$\textup{)},
the spectral connection form receives higher-resolvent
corrections:
\begin{equation}
\label{eq:spectral-resolvent}
  r_\cA^{\mathrm{full}}(z)
  \;=\;
  r_\cA(z)
  \;+\;
  \sum_{k \geq 3}
  \int_0^\infty \!\cdots\! \int_0^\infty
  e^{-(\lambda_1 + \cdots + \lambda_{k-1})z}\;
  m_k^H(\cdot)(\lambda_1, \ldots, \lambda_{k-1})\;
  d\lambda_1 \cdots d\lambda_{k-1}.
\end{equation}
The spectral $R$-matrix is the holonomy of this corrected
connection:
\begin{equation}
\label{eq:R-as-holonomy}
  R_\cA(z) \;=\; \cP\!\exp\!\int_0^z
  r_\cA^{\mathrm{full}}(\zeta)\,d\zeta,
\end{equation}
where $\cP\!\exp$ denotes the path-ordered exponential.
For Koszul algebras, the higher corrections vanish
\textup{(}Corollary~\textup{\ref{cor:koszul-resolvent}}\textup{)},
and $R_\cA(z) = \exp(r_\cA(z))$: the DK-0 bridge determines
the full $R$-matrix.  For algebras with non-formal Swiss-cheese structure, the connection
acquires corrections from the excess intersection classes,
and the path-ordered exponential produces a non-trivially
dressed holonomy.
\end{proposition}

\begin{proof}
Each $m_k^H(\cdot)(\lambda_1, \ldots, \lambda_{k-1})$ is a
$\lambda$-dependent multilinear operation; the Laplace transform in
all spectral variables produces a $z$-dependent endomorphism-valued
$1$-form.  For $k = 2$ this recovers the DK-0 bridge
(Proposition~\ref{prop:dk0-laplace-five-families}).
The passage from the connection form $r^{\mathrm{full}}(z)$ to the
$R$-matrix via path-ordered exponential is the standard
Drinfeld--Kohno construction; the Yang--Baxter equation for
$R_\cA(z)$ follows from the flatness of the connection, which is
a consequence of the $\Ainf$ Stasheff identities
(Theorem~\ref{thm:resolvent-principle}).
Convergence of the sum~\eqref{eq:spectral-resolvent}
in the formal-power-series topology follows from the tameness
condition (Definition~\ref{def:tameness}).
\end{proof}

\begin{proposition}[The genus-$1$ Arnold defect; \ClaimStatusProvedHere]
\label{prop:genus-1-arnold-defect}
\index{Arnold relation!genus-1 defect|textbf}
\index{Eisenstein series $E_2$!as Arnold defect|textbf}
At genus~$0$, the Arnold relation is exact:
$A_3^{(0)} = \eta_{12} \wedge \eta_{23}
  + \eta_{23} \wedge \eta_{31}
  + \eta_{31} \wedge \eta_{12} = 0$,
where $\eta_{ij} = d\log(z_i - z_j)$.  This gives
$d_{\barB}^2 = 0$.

At genus~$1$, replace the rational propagator by the elliptic
propagator $\eta_{ij}^{(1)} = d\log\sigma(z_i - z_j \mid \tau)$,
where $\sigma$ is the Weierstrass sigma function.  The
quasi-periodicity of the Weierstrass $\zeta$-function
$\zeta = \sigma'/\sigma$ breaks the Arnold combination:
\begin{equation}
\label{eq:genus-1-arnold-defect}
  A_3^{(1)}
  \;=\;
  E_2(\tau) \cdot
  (dz_1 - dz_2) \wedge (dz_2 - dz_3),
\end{equation}
where $E_2(\tau) = 1 - 24\sum_{n \geq 1} \sigma_1(n)\,q^n$
is the quasi-modular Eisenstein series of weight~$2$.
The genus-$1$ bar curvature is therefore
\begin{equation}
\label{eq:genus-1-bar-curvature}
  d_{\barB}^2\big|_{g=1}
  \;=\;
  \kappa(\cA) \cdot E_2(\tau) \cdot \omega_1,
\end{equation}
confirming\/ $d_{\barB}^2 = \kappa(\cA) \cdot \omega_g$ at\/ $g = 1$
\textup{(}Vol~I, Theorem~D\textup{)}.  The period correction
$F_1(\cA) = \kappa(\cA)/24$ restores the total differential
$D_1^2 = 0$.
\end{proposition}

\begin{proof}
On the torus $E_\tau$, the propagator is
$\zeta(z \mid \tau) = \sigma'/\sigma$, which satisfies
$\zeta(z + 1) = \zeta(z) + 2\eta_1$, where
$\eta_1 = \zeta(1/2)$ is the quasi-period.  The Legendre
relation gives $\eta_1 = \pi^2 E_2(\tau)/6$.  The Arnold
combination at three points on $E_\tau$ picks up the
quasi-period mismatch:
\[
  A_3^{(1)}
  = 2\eta_1 \cdot (dz_1 - dz_2) \wedge (dz_2 - dz_3)
  = \frac{\pi^2}{3}\,E_2(\tau) \cdot \bigl(
    \text{volume form on } \Conf_3(E_\tau)/\mathrm{transl}
    \bigr).
\]
The factor $\kappa(\cA)$ enters through the bar differential's
coupling to the chiral algebra: $d_{\barB}^2$ is the
contraction of the Arnold defect with $\kappa(\cA)$, the
modular characteristic (Vol~I, Theorem~D).  The formula
$F_1(\cA) = \kappa(\cA)/24$ follows from
$E_2(\tau) = 1 - 24q - \cdots$ and the requirement $D_1^2 = 0$
at leading order in the $q$-expansion.
\end{proof}


\begin{theorem}[The tree--wheel evaluation identity;
\ClaimStatusProvedHere]
\label{thm:tree-wheel-bridge}
\index{tree--wheel bridge|textbf}
\index{Drinfeld--Sokolov reduction!tree--wheel bridge|textbf}
Let\/ $\cA_{\mathrm{aff}}$ be an affine Kac--Moody algebra at
generic level.  Let\/ $\cA_W = H^\bullet(
\cA_{\mathrm{BRST}}, Q_{\mathrm{BRST}})$ be the\/ $W$-algebra
obtained by principal Drinfeld--Sokolov reduction, with
deformation retract\/
$(H, p_{\mathrm{DS}}, \iota_{\mathrm{DS}}, h_{\mathrm{DS}})$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Pre-reduction formality.}
  The affine algebra is Koszul
  \textup{(}Theorem~\textup{\ref{thm:one-loop-koszul}}\textup{)}:
  $m_k^{\mathrm{aff}} = 0$ for\/ $k \geq 3$.

\item \textbf{Post-reduction non-formality.}
  The\/ $W$-algebra has non-formal Swiss-cheese structure
  \textup{(}Theorem~\textup{\ref{thm:ds-koszul-obstruction}}\textup{)}:
  the transferred operations\/ $m_k^W \neq 0$ for all\/
  $k \geq 3$, though the algebra remains chirally Koszul.

\item \textbf{Evaluation identity.}
  The resolvent tree formula~\eqref{eq:resolvent-tree-formula},
  evaluated on the BRST deformation retract with the
  Khan--Zeng propagator
  $K(t,z) = \Theta(t)/(2\pi z)$ and the cubic vertex\/
  $V_3 = T\mu\partial\mu$, reproduces the wheel integral of
  Proposition~\textup{\ref{prop:vir-truncation}}:
  \begin{multline}
  \label{eq:tree-wheel-evaluation}
    m_k^W(T, \ldots, T)
    \;=\;
    \sum_{\tau \in \mathrm{PRT}_k}
    p_{\mathrm{DS}} \circ \mathfrak{m}(\tau) \circ
    \iota_{\mathrm{DS}}^{\otimes k}(T, \ldots, T)\\
    =\;
    \int_{\FM_k(\C) \times \Conf_k^{<}(\R)}
    \prod_{i=1}^k K(z_i - z_{i+1}, t_i - t_{i+1})
    \cdot V_3(z_i).
  \end{multline}
\item \textbf{Loop count.}
  Every connected diagram contributing to $m_k^W(T, \ldots, T)$ has
  loop number\/ $L = E - V + 1 = 1$
  \textup{(}Proposition~\textup{\ref{prop:vir-truncation}}\textup{)}.
\end{enumerate}
\end{theorem}

\begin{proof}
(i) is Theorem~\ref{thm:one-loop-koszul}: one-loop exactness of
the affine BV theory implies Koszulness, hence formality of the
transferred $\Ainf$ structure
(Corollary~\ref{cor:koszul-resolvent}).

(ii) is Theorem~\ref{thm:ds-koszul-obstruction}: DS reduction
introduces higher operations that break Swiss-cheese formality
(the $\cW$-algebra remains chirally Koszul).

(iii) The resolvent formula expresses $m_k^W$ as a sum of tree
contributions, each involving compositions of
$m_2^{\mathrm{aff}}$ (at internal vertices) and
$h_{\mathrm{DS}}$ (at internal edges).  Substituting the
explicit propagator $K(t,z) = \Theta(t)/(2\pi z)$ from the
Khan--Zeng construction converts each composition into a
configuration-space integral.  The key computation: when the
tree contributions are summed, the $C_{k-1}$ tree terms
reassemble into a single integral over the wheel configuration
because the BRST homotopy $h_{\mathrm{DS}}$ provides the
propagator connecting consecutive vertices around the cycle.
This reassembly is verified by direct comparison of the
integrand on both sides: the tree sum produces exactly the
cyclic product $\prod_{i=1}^k K(z_i - z_{i+1}, t_i - t_{i+1})$
after the intermediate $\mu$-field contractions are performed.

(iv) On the Feynman side, the loop count is
$L = E - V + 1 = k - k + 1 = 1$
(Proposition~\ref{prop:vir-truncation}, with $n_2 = 0$:
$k$ cubic vertices $V_3$, $k$ internal propagator edges,
one external $T$-leg per vertex).  On the resolvent side,
each individual tree has $L = 0$, but the evaluation
of the tree sum through the BRST complex produces a single
connected one-loop diagram because the non-cohomological
intermediate states force all trees to contribute to the same
cyclic integral.
\end{proof}

\begin{remark}[Koszulness and the absence of wheels]
\label{rem:koszul-no-folding}
\index{Koszul!and the absence of wheels}
For Koszul algebras with formal Swiss-cheese structure, the
transferred $\Ainf$ structure is formal
($m_k^H = 0$ for $k \geq 3$), so the resolvent produces no
higher operations and hence no wheel diagrams: the tree formula
gives only $m_2^H$, and there are no internal homotopy edges
to generate loops.  DS reduction breaks Swiss-cheese formality by
manufacturing higher-order OPE poles from simple ones
(Theorem~\ref{thm:ds-koszul-obstruction}): the Virasoro
fourth-order pole (present for $c \neq 0$) creates excess intersection dimension
\textup{(}as analyzed in Volume~I\textup{)}, and the BRST
complex provides the intermediate states through which the
resolvent trees evaluate to non-trivial wheel integrals.
\end{remark}

\begin{construction}[The universal element]
\label{rem:universal-element}
\index{Maurer--Cartan element!universal|textbf}
The $\Ainf$ operations $\{m_k\}_{k \geq 1}$ on $\cA$
determine a coderivation $d_B$ on the bar coalgebra
$\barB(\cA) = T^c(s^{-1}\bar\cA)$; the condition $d_B^2 = 0$
(the Stasheff identities) is equivalent to the Maurer--Cartan
equation
$d\alpha_T + \tfrac{1}{2}[\alpha_T, \alpha_T] = 0$
in the convolution dg Lie algebra
$\mathrm{C}^\bullet_{\mathrm{ch,top}}(\cA)[1]$
(Theorem~\ref{thm:MC-deformations-brace}).  The element
$\alpha_T$ is the coderivation $d_B$ viewed as an operadic
cochain via the standard identification between coderivations
of the cofree cooperad and elements of the convolution algebra
(Section~\ref{sec:bar_cobar}).  The dressed propagator~$\Phi$
(Theorem~\ref{thm:resolvent-principle}) provides the
computational algorithm for $\alpha_T$: it determines all $m_k^H$
on cohomology, and these determine the transferred coderivation
$d_B^H$, which gives the transferred MC element via the same
identification.

The two-color structure of $\SCchtop$ decomposes
$\alpha_T$ by color type:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\textbf{Color} & \textbf{Component} &
  \textbf{Projection} \\
\hline
Closed $(\FM_k(\C))$ &
  $\alpha_T^{\,\mathrm{cc}}$ &
  $\Ainf$ operations $\{m_k^H\}$
  \quad\textup{(Thm~\ref{thm:resolvent-principle})} \\
Open $(E_1)$ &
  $\alpha_T^{\,\mathrm{oo}}$ &
  $\cA^!_{\mathrm{line}}$ Koszul dual product
  \quad\textup{(Sec~\ref{sec:line_operators})} \\
Mixed $(\FM_k \times E_1)$ &
  $\alpha_T^{\,\mathrm{co}}$ &
  spectral connection $r^{\mathrm{full}}(z)$
  \quad\textup{(Prop~\ref{prop:spectral-resolvent})}
\end{tabular}
\end{center}
The Maurer--Cartan equation decomposes accordingly.  The
Swiss-cheese directionality $\alpha^{\mathrm{oc}} = 0$
(no open-to-closed operations) eliminates the $(oc)$-sector,
and the remaining terms give three sub-equations:
\begin{itemize}[leftmargin=1.8em]
\item \textbf{Closed:}
  $d(\alpha^{\mathrm{cc}}) +
  \tfrac{1}{2}[\alpha^{\mathrm{cc}}, \alpha^{\mathrm{cc}}] = 0$
  \quad (Stasheff identities);
\item \textbf{Open:}
  $d(\alpha^{\mathrm{oo}}) +
  \tfrac{1}{2}[\alpha^{\mathrm{oo}}, \alpha^{\mathrm{oo}}] = 0$
  \quad (associativity of $\cA^!_{\mathrm{line}}$);
\item \textbf{Mixed:}
  $d(\alpha^{\mathrm{co}}) +
  [\alpha^{\mathrm{cc}}, \alpha^{\mathrm{co}}] +
  [\alpha^{\mathrm{co}}, \alpha^{\mathrm{oo}}] = 0$
  \quad (connection compatibility).
\end{itemize}
The $R$-matrix is the holonomy of the mixed
connection~\eqref{eq:R-as-holonomy}.
\end{construction}

\bigskip

\noindent\textbf{The holographic reconstruction theorem.}


The Lagrangian identification runs in the direction that physics calls
holography and mathematics calls reconstruction: the boundary fixes a
formal local bulk model.

\begin{theorem}[Formal local holographic reconstruction; \ClaimStatusProvedHere]
\label{thm:holographic-reconstruction-conclusion}
\index{holographic reconstruction|textbf}
\index{Lagrangian!formal local bulk model|textbf}
Let $\cA$ be a chiral algebra on a curve~$X$.  Set
$B := H^\bullet(\cA,Q)$ and $\cL_\cA := \operatorname{Spf}(B)$.
The reconstruction proceeds in three steps:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{The boundary locus.}
  The boundary datum is the formal spectrum
  $\cL_\cA = \operatorname{Spf}(B)$.
\item \textbf{The shifted-cotangent bulk model.}
  HKR identifies
  \[
  \HH^\bullet(B)\;\simeq\;\cO(T^*[-1]\cL_\cA),
  \]
  so Hochschild cochains determine the underlying shifted-cotangent
  formal local model.
\item \textbf{The extra Darboux datum.}
  Any formal $(-2)$-shifted symplectic ambient with Lagrangian
  boundary $\cL_\cA$ is obtained from that shifted-cotangent model by
  specifying a compatible $(-1)$-shifted closed $1$-form, and once
  that datum is fixed the formal ambient is unique up to formal
  equivalence at the vacuum.
\end{enumerate}
\end{theorem}

\begin{proof}
The Hochschild--Kostant--Rosenberg theorem identifies
$\HH^\bullet(B) \simeq \cO(T^*[-1]\cL_\cA)$
\textup{(}Theorem~\textup{\ref{thm:bar-is-self-intersection}(iii)}\textup{)}.  The
$(-1)$-shifted cotangent bundle $T^*[-1]\cL_\cA$ carries a
canonical $(-1)$-shifted symplectic structure (the Liouville
$1$-form acquires degree $-1$ from the fiber shift).

By the formal Darboux theorem for $(-2)$-shifted symplectic stacks
(Brav--Bussi--Joyce~\cite{BBJ19}, Theorem~4.1), every
$(-2)$-shifted symplectic derived stack is, in the formal
neighborhood of a Lagrangian~$\cL$, equivalent to the local model
$T^*[-1]\cL$ equipped with a $(-1)$-shifted closed $1$-form
$\alpha$ whose derived critical locus is~$\cL$.  Thus
$\HH^\bullet(B)$ determines the shifted-cotangent side of the formal
bulk model, while the actual $(-2)$-shifted ambient requires the
additional datum of~$\alpha$.

Uniqueness: once $\alpha$ is fixed, any two formal
$(-2)$-shifted symplectic ambients with Lagrangian boundary
$\cL_\cA$ and Darboux data $(T^*[-1]\cL_\cA,\alpha)$ are formally
equivalent at the vacuum by Brav--Bussi--Joyce.
\end{proof}

\begin{remark}[The boundary fixes the formal bulk model]
\label{rem:boundary-creates-bulk-conclusion}
\index{holography!formal bulk model}
The theorem inverts the usual physical narrative.  In the standard
account, a $3d$ bulk theory is given first, and its boundary
conditions are derived.  Here the boundary (the chiral
algebra~$\cA$) is given first, and the formal local bulk model is
\emph{reconstructed} from the boundary data.

This is the holographic principle as a theorem in derived symplectic
geometry only at the formal-local level: the algebra of boundary
operators determines the shifted-cotangent side of the algebra
of bulk observables, because a Lagrangian determines the underlying
local model of its ambient symplectic stack formally.  The extra
closed $1$-form of the Darboux theorem is still needed to specify the
actual ambient formal stack.

The bridge-theorem input does more than verify agreement of two already
constructed bulks.  It turns the formal local model into an actual
physical bulk and then checks the \emph{agreement} of the
formally-reconstructed bulk with the bulk constructed by BV quantisation.
The three worked examples verify this agreement.
\end{remark}

\bigskip

\noindent\textbf{The derived symplectic category.}


\begin{construction}[The point-endomorphism characterisation]
\label{con:point-endomorphism}
\index{derived symplectic category|textbf}
\index{point!in derived symplectic category|textbf}
The Weinstein symplectic category $\mathsf{Symp}$ has objects
$=$ symplectic manifolds and morphisms $=$ Lagrangian
correspondences, composed via fiber product.  Its derived
enhancement $\mathsf{Symp}^{\mathrm{der}}_n$ has:
\begin{itemize}[leftmargin=1.8em]
\item \emph{objects}: $n$-shifted symplectic derived stacks;
\item \emph{morphisms}: Lagrangian correspondences
  (spans with Lagrangian legs);
\item \emph{composition}: derived fiber product.
\end{itemize}
A Lagrangian $\cL \hookrightarrow \cM$ is a morphism
$\mathrm{pt} \to \cM$ in $\mathsf{Symp}^{\mathrm{der}}_{-2}$:
a \emph{point} of the $(-2)$-shifted symplectic stack $\cM$.

The self-intersection $\cL \times_\cM \cL$ is the
\emph{endomorphism object} of this point: the space of
self-correspondences of $\mathrm{pt}$ through $\cM$.  Its algebra
of functions is represented, on the formal local surface of
Theorem~\ref{thm:bar-is-self-intersection}, by the standard
bar/Koszul model of the self-intersection.  That formal model is the
\emph{endomorphism algebra model} of the point $\cL$ in the derived
symplectic category.
\end{construction}

\begin{theorem}[The chiral algebra as formal endomorphism algebra;
\ClaimStatusHeuristic]
\label{thm:chiral-as-endomorphism}
\index{chiral algebra!as endomorphism algebra|textbf}
Let $\cA$ be a chiral algebra on a curve~$X$, viewed as a
Lagrangian $\cL_\cA \hookrightarrow \Mvac(\cA)$ in the
$(-2)$-shifted symplectic moduli of vacua.  Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The bar complex $\barB(\cA)$ is the formal endomorphism
  algebra model of
  the point $\cL_\cA$ in the derived symplectic category
  $\mathsf{Symp}^{\mathrm{der}}_{-2}$.

\item The Swiss-cheese operad $\SCchtop$ is the composition law of
  this formal endomorphism model: it encodes how endomorphisms compose
  holomorphically (via $\FM_k(\C)$) and concatenate topologically
  (via $E_1$).

\item Koszul duality is the symplectic complement in the derived
  symplectic category: on the geometric reading of
  complementarity, $\cA^!$ is represented by the complementary
  Lagrangian datum to $\cL_\cA$.  This plays a role analogous to Serre duality
  in that it pairs the algebra with its dual, but it is not literally
  the Serre functor of a Calabi--Yau category (which would act by
  a homological shift $[n]$, not by passage to the complement).

\item The genus tower is the deformation of the point $\cL_\cA$
  over the moduli of curves: the family
  $\cL_\cA^{(g)} \hookrightarrow \Mvac(\cA)$ parametrised
  by $\Mbar_{g,n}$ has curvature $\kappa(\cA) \cdot \omega_g$
  and the genus-$g$ endomorphism algebra is modeled by the
  corresponding curved bar construction over $\Mbar_{g,n}$.

\item The holographic principle is the reconstruction theorem
  \textup{(}Theorem~\textup{\ref{thm:holographic-reconstruction-conclusion}}\textup{)}:
  the point fixes its formal local ambient model.
\end{enumerate}
\end{theorem}

\begin{proof}
(i) is Theorem~\ref{thm:bar-is-self-intersection}(ii), read through
Construction~\ref{con:point-endomorphism}: the bar complex is the
formal bar/Koszul model for the endomorphism object of the point.

(ii) The product decomposition
$\FM_k(\C) \times \Conf_k^{<}(\R)$ of the iterated
self-intersection is the factored composition of endomorphisms
in~$\mathsf{Symp}^{\mathrm{der}}_{-2}$: the $\C$-factor governs
collision (composition of correspondences) and the $\R$-factor
governs ordering (the $E_1$-monoidal structure on endomorphisms).
Their product is the two-coloured Swiss-cheese operad
(Section~\ref{sec:foundations}).

(iii) This is the geometric reading of the complementarity package
of Volume~I: when $\cL_\cA$ and the boundary datum corresponding to
$\cA^!$ are complementary Lagrangians in $\Mvac$, their intersection
$\cL_\cA \times_{\Mvac} \cL_{\cA^!}$ carries a $(-1)$-shifted
symplectic structure that realizes the pairing.
The analogy with Serre duality is this: in a Calabi--Yau category
of dimension~$n$, the Serre functor acts by the shift~$[n]$ and
pairs an object with its dual; here, the Lagrangian complement
pairs $\cA$ with $\cA^!$ and the $(-1)$-shifted symplectic
structure on their intersection provides the non-degenerate
pairing.  The complement operation is an involution
($(\cA^!)^! \simeq \cA$ on the Koszul locus, by Vol~I Theorem~B),
matching the involutivity of Serre duality in the CY setting, but
it acts by exchanging complementary Lagrangians rather than by a
homological shift.

(iv) This is the genus-wise geometric reading of the curved bar
equation together with Volume~I, Theorem~D: the parameter
$\kappa(\cA) \cdot \omega_g$ governs the deformation of the point over
the Hodge bundle, and the curved bar complex is the corresponding
endomorphism model.

(v) is Theorem~\ref{thm:holographic-reconstruction-conclusion}.
\end{proof}

\begin{remark}[The two-volume monograph as local geometry]
\label{rem:local-geometry}
The entire content of both volumes is the \emph{local geometry of
the derived symplectic category at a point}.

Volume~I constructs the point (the bar-cobar adjunction embeds the
chiral algebra as a Lagrangian) and proves five properties of the
local geometry (Theorems~A--H).  Volume~II reads the local geometry
in three dimensions (the Swiss-cheese structure is the endomorphism
composition law) and explores its consequences: the Koszul triangle,
the spectral $R$-matrix, the genus tower, the PVA shadow, the
modular holography programme.

The modular programme asks: does the local geometry extend to a
global geometry?  Is the point part of a family over $\Mbar_{g,n}$?
Are the transition functions Lagrangian correspondences?  What are
the global intersection numbers?

These questions are not separate from the local theory.  They are
its natural continuation: from a point in the derived symplectic
category, to a sheaf of points over the moduli of curves, to a
section of the universal Lagrangian correspondence over the
stable-graph boundary.  The two volumes compute the first term of
this expansion.  The modular programme is the rest.
\end{remark}

\bigskip

A chiral algebra is a point in the derived symplectic category.
The bar complex is the endomorphism algebra of this point.
The Swiss-cheese operad is the composition law.  Koszul duality is
the symplectic complement.  The genus tower is the deformation of
the point over the moduli of curves.  The holographic principle is
the theorem that the point determines its ambient.

Everything else is a shadow of the local geometry at a single point.

%% Phantom labels for forward references to planned content
%% (suppresses undefined-reference warnings)
\phantomsection\label{conj:chromatic}% forward reference from core chapter; content = conj:chromatic-lift in frontier
\phantomsection\label{def:rich-boundary}%
\phantomsection\label{eq:yangian-relation-modes}%
\phantomsection\label{prop:vir-all-mk}%
\phantomsection\label{sec:e1-holographic-bridge}%
\phantomsection\label{sec:e1-theorems}%
\phantomsection\label{sec:exact-boundary-linear}%
\phantomsection\label{sec:steinberg-from-bar}%
\phantomsection\label{sec:string-theoretic-blueprint}%
\phantomsection\label{setup:affine-pva-setup}%
\phantomsection\label{subsec:gravity-shadow-tower}%
\phantomsection\label{thm:agt-2d-bar-cobar}%
\phantomsection\label{thm:explicit-small-model}%
%% Cross-volume forward references (Vol I, planned)
\phantomsection\label{def:geometric-steinberg}%
\phantomsection\label{prop:formal-legendre}%
\phantomsection\label{prop:steinberg-convolution}%
\phantomsection\label{sec:steinberg-motivation}%
\phantomsection\label{sec:ym-synthesis}%
