% Ensure theorem environments used in this chapter are available.
\makeatletter
\@ifundefined{conclusion}{\newenvironment{conclusion}[1][]{\begin{remark}[#1]}{\end{remark}}}{}
\makeatother

\chapter{From dg-Shifted Yangians to Spectral Factorization Quantum Groups}
\label{chap:dg-shifted-factorization}

\section{Orientation, status, and first principles}

Theorem~\ref{thm:yangian-recognition} shows that the open-colour line-side algebra $\cA^!_{\mathrm{line}}$ on the chirally Koszul locus carries the dg-shifted Yangian package, whose axioms are the $\SCchtop^{!}$-operadic identities (closed $=$ Lie, open $=$ Ass) decomposed by colour. The spectral Drinfeld strictification obstruction vanishes for all simple Lie algebras (Theorem~\ref{thm:complete-strictification}), relating this package to both spectral factorization quantum groups and shifted quantum groups.

There are three languages in play. The physical
identifications of Dimofte--Niu--Py~\cite{DNP25} are
recovered as the naming of operadic data in physical
language (Remark~\ref{rem:yangian-logical-status}).
The second is the spectral language of factorisation quantum
groups, as developed by Latyntsev~\cite{Latyntsev23}.
The third is the geometric language of shifted quantum groups
and critical stable envelopes, as developed in the
shifted-Yangian literature and the critical-stable-envelope
programme~\cite{COZZ26}.

The guiding problem of this chapter is to put these three
languages on one common spine. The core claim is not that
a dg-shifted Yangian, viewed through
Theorem~\ref{thm:yangian-recognition} on the chirally Koszul
locus, is
\emph{already} a strict factorization quantum group. The
correct claim is subtler and stronger: the
$\SCchtop$-algebra structure, once expressed through a
bar-horizontal strictification of its open-color projection,
canonically produces a \emph{spectral quasi-factorization quantum group},
and the passage from quasi to strict is governed by a concrete
obstruction complex whose first low-filtration sectors can
be computed exactly.

The mechanism that makes strictification possible is
\emph{root multiplicity one}: every root of a simple Lie algebra
has multiplicity one, so the multilinear Lie space at each
filtration sector is one-dimensional. A cohomological
obstruction valued in a one-dimensional space is a scalar,
determined by one equation, which coproduct rigidity supplies.
The spectral Drinfeld obstruction class vanishes at every
filtration, and the passage from quasi-factorization to strict
factorization is unobstructed for all simple Lie algebras.

We do not attempt to impose a strict $R$-matrix directly on
the $A_\infty$ object. The operadic reason: the $R$-matrix
is a closed-color datum (from $\FM_2(\C)$), while the
$A_\infty$ structure is the open-color $E_1$-projection of
the $\SCchtop$-algebra on the chirally Koszul locus
(Theorem~\ref{thm:yangian-recognition}). Imposing the
$R$-matrix on the $A_\infty$ object would conflate colors.
Instead, we pass to ordered configuration spaces (the
open-color stage), construct a flat connection, read off
regularized holonomy, and only then formulate the spectral
factorization problem. In the language of
the Steinberg presentation
(Theorem~\ref{thm:steinberg-presentation}), the flat connection is
the spectral connection~$\nabla_z$ of~(iii)(b), and strictification
asks whether its monodromy $R(z)$ can be made into a strict
factorization $R$-matrix, the passage from the homotopy-coherent
correspondence to its strict shadow.

\section{Complete filtered spectral setup}

\begin{definition}[Residue-bounded complete dg-shifted Yangian]
Let $Y$ be a complete separated filtered $A_\infty$-algebra
\[
Y=F^1Y\supset F^2Y\supset \cdots,
\qquad
Y\cong \varprojlim_N Y/F^{N+1}Y,
\]
equipped with:
\begin{enumerate}
\item a translation family $\tau_z$,
\item a twisted coproduct $\Delta_z$,
\item an odd Maurer--Cartan kernel
\[
r(z)=\sum_{n\ge 1} r_n z^{-n} \in (Y\widehat\otimes Y)((z^{-1})),
\]
\end{enumerate}
such that
\[
m_k(F^{p_1}Y,\dots,F^{p_k}Y)
\subset F^{p_1+\cdots+p_k+k-2}Y,
\]
and such that the residues become more convergent with pole order in the
sense that
\[
r_n(F^pY\widehat\otimes F^qY)
\subset F^{p+q+n}(Y\widehat\otimes Y).
\]
We call such an object a \emph{residue-bounded complete dg-shifted
Yangian}.
\end{definition}

The suspension of $r(z)$ to the bar convolution algebra will be denoted
by $\widetilde r(z)$; this is the degree-zero spectral kernel.

\begin{definition}[Bar-horizontal strictification]
Let $B(Y)=T^c(s^{-1}Y)$ be the completed reduced bar coalgebra of $Y$ with
bar differential $b$. A \emph{bar-horizontal strictification} of $Y$
is a complete filtered cochain complex $(V,d_V)$ quasi-isomorphic to
$B(Y)$ together with continuous degree-zero endomorphisms
\[
\Omega_{ij}(u)\in \operatorname{End}(V^{\widehat\otimes n})((u^{-1}))
\qquad (1\le i<j\le n)
\]
such that:
\begin{align*}
[d_V,\Omega_{ij}(u)]&=0,\\
[\Omega_{ij}(u),\Omega_{kl}(v)]&=0
\qquad \text{if }\{i,j\}\cap\{k,l\}=\varnothing,
\end{align*}
and for every triple $i<j<k$,
\[
[\Omega_{ij}(u),\Omega_{ik}(u+v)]
+[\Omega_{ij}(u),\Omega_{jk}(v)]
+[\Omega_{ik}(u+v),\Omega_{jk}(v)] = 0.
\]
\end{definition}

This is the additive spectral precursor of a strict spectral
$R$-matrix. It is the correct object to strictify first.

\begin{remark}[Existence of bar-horizontal strictifications]
\label{rem:bar-horizontal-existence}
The existence of a bar-horizontal strictification for HT theories arising from Theorem~\ref{thm:physics-bridge} is established by the explicit Feynman-diagrammatic construction of the KZ connection in Theorem~\ref{thm:derived-additive-kz} below: the bar-horizontal datum $(V, d_V, \Omega_{ij}(u))$ is produced by the perturbative expansion of the holonomy, with $\Omega_{ij}$ given by the tree-level exchange amplitude.
\end{remark}

\begin{theorem}[Derived additive KZ connection; \ClaimStatusProvedHere]
\label{thm:derived-additive-kz}
Let $(V,\Omega)$ be a bar-horizontal strictification. On the ordered
configuration space
\[
\Conf_n^{\mathrm{ord}}(\mathbb A^1)=\{z_1<\cdots<z_n\}
\]
consider the operator
\[
\mathbb D_n
=
 d_V+d_{\mathrm{dR}}
 - \sum_{1\le i<j\le n}\Omega_{ij}(z_j-z_i)\,d(z_j-z_i).
\]
Then $\mathbb D_n^2=0$.
\end{theorem}

\begin{proof}
Write
\[
A_n:=\sum_{i<j}\Omega_{ij}(z_j-z_i)\,d(z_j-z_i).
\]
Since $d_V^2=d_{\mathrm{dR}}^2=0$ and $[d_V,\Omega_{ij}(u)]=0$, one has
\[
(d_V+d_{\mathrm{dR}})^2=0,
\qquad
[d_V+d_{\mathrm{dR}},A_n]=0,
\]
because $d_{\mathrm{dR}}(f(u)du)=f'(u)du\wedge du=0$.
Hence
\[
\mathbb D_n^2=A_n\wedge A_n.
\]
Disjoint-pair terms vanish by hypothesis. Thus only triples
$i<j<k$ contribute. Put
\[
u=z_j-z_i,
\qquad
v=z_k-z_j,
\qquad
z_k-z_i=u+v.
\]
Then
\[
d(z_k-z_i)=du+dv,
\]
and every wedge product appearing from the triple $i<j<k$ reduces to a
multiple of $du\wedge dv$. The coefficient is precisely
\[
[\Omega_{ij}(u),\Omega_{ik}(u+v)]
+[\Omega_{ij}(u),\Omega_{jk}(v)]
+[\Omega_{ik}(u+v),\Omega_{jk}(v)],
\]
which vanishes by the defining spectral Kohno relation. Therefore
$\mathbb D_n^2=0$.
\end{proof}

\begin{corollary}[Derived Drinfeld--Kohno shadow; \ClaimStatusProvedHere]
If the filtration is pronilpotent, the parallel transport of
$\mathbb D_n$ is well-defined and yields chain-level pure braid group
representations on $V^{\widehat\otimes n}$, hence braid-group actions
on $H^\bullet(V^{\widehat\otimes n})$.
\end{corollary}

\begin{theorem}[Boundary residue theorem; \ClaimStatusProvedHere]
\label{thm:boundary-residue}
Assume that each $\Omega_{ij}(u)$ has at most a simple pole at $u=0$,
so that
\[
\Omega_{ij}(u)=\frac{r_{ij}}{u}+\Omega_{ij}^{\mathrm{reg}}(u).
\]
Then the connection form of Theorem~\ref{thm:derived-additive-kz}
extends logarithmically to the Fulton--MacPherson compactification
$\overline{\Conf}_n^{\mathrm{ord}}(\mathbb A^1)$.
For the boundary divisor $D_S$ corresponding to collision of a subset
$S\subset\{1,\dots,n\}$, its residue is
\[
\operatorname{Res}_{D_S}(A_n)=\sum_{i<j\in S} r_{ij}.
\]
\end{theorem}

\begin{proof}
Near the divisor $D_S$, choose local coordinates
\[
z_i=z_*+t\xi_i\qquad (i\in S),
\]
with $t=0$ cutting out the boundary and the $\xi_i$ pairwise distinct.
Then for $i,j\in S$,
\[
z_j-z_i=t(\xi_j-\xi_i),
\qquad
 d(z_j-z_i)=(\xi_j-\xi_i)dt+t\,d(\xi_j-\xi_i).
\]
Hence
\begin{align*}
\Omega_{ij}(z_j-z_i)\,d(z_j-z_i)
&=
\left(\frac{r_{ij}}{t(\xi_j-\xi_i)}+\text{regular}\right)
\big((\xi_j-\xi_i)dt+t\,d(\xi_j-\xi_i)\big)\\
&=r_{ij}\frac{dt}{t}+r_{ij}d\log(\xi_j-\xi_i)+\text{regular}.
\end{align*}
Pairs not entirely contained in $S$ remain regular in $t$.
Summing over $i<j\in S$ gives the residue formula.
\end{proof}

\begin{theorem}[Transfer of flat spectral connections; \ClaimStatusProvedHere]
\label{thm:transfer-flat-spectral}
Let
\[
(H,d_H)
\xrightarrow{i}
(V,d_V)
\xrightarrow{p}
(H,d_H)
\]
be a filtered strong deformation retract with homotopy $h$:
\[
pi=\operatorname{id}_H,
\qquad
ip=\operatorname{id}_V+d_Vh+hd_V.
\]
Assume that $V\otimes \Omega^\bullet(\Conf_n^{\mathrm{ord}})$ carries a
flat total differential
\[
\mathbb D_V=(d_V+d_{\mathrm{dR}})-A_V,
\]
where $A_V$ lowers the filtration. Then the homological perturbation
series converges and produces a flat total differential
\[
\mathbb D_H=(d_H+d_{\mathrm{dR}})-A_H,
\qquad
A_H=pA_V(1-hA_V)^{-1}i=
\sum_{m\ge 0} pA_V(hA_V)^mi.
\]
Thus every flat bar-level spectral connection descends functorially to
cohomology or to a minimal model.
\end{theorem}

\begin{proof}
Tensor the strong deformation retract with the de Rham complex of the
base. Since $d_{\mathrm{dR}}$ commutes with $i,p,h$, the same data form a
strong deformation retract for the base differential
$d_V+d_{\mathrm{dR}}$. Set $\delta=-A_V$. Because $\delta$ lowers the
filtration, the standard homological perturbation series converges.
The perturbation lemma gives the transferred differential
\[
(d_H+d_{\mathrm{dR}})+p\delta(1-h\delta)^{-1}i,
\]
which squares to zero because
$(d_V+d_{\mathrm{dR}}+\delta)^2=\mathbb D_V^2=0$.
Replacing $\delta$ by $-A_V$ yields the formula for $A_H$.
\end{proof}

\section{Quasi-factorization and spectral obstruction theory}

\begin{definition}[Regularized holonomy data]
Assume that the flat connections of
Theorem~\ref{thm:derived-additive-kz} are pronilpotent at the boundary.
For $n=2$, let
\[
R(u)\in 1+F^1A^{\widehat\otimes 2}
\]
be the regularized holonomy from the positive tangential basepoint at
collision to the interior point with difference $u=z_2-z_1$.
For $n=3$, let $\Phi(w,z)\in 1+F^2A^{\widehat\otimes 3}$ be the
regularized parallel transport between the two tangential basepoints
corresponding to the bracketings $(12)3$ and $1(23)$ in
$\overline{\Conf}_3^{\mathrm{ord}}(\mathbb A^1)$.
We call $(R,\Phi)$ the \emph{spectral quasi-factorization datum}.
\end{definition}

\begin{theorem}[Quasi-factorization theorem; \ClaimStatusProvedHere]
\label{thm:quasi-factorization}
Every residue-bounded complete dg-shifted Yangian equipped with a
bar-horizontal strictification canonically determines a spectral
quasi-factorization quantum group.
More precisely, the regularized holonomy data $(R,\Phi)$ satisfy:
\begin{enumerate}
\item quasi-hexagon relations on $\overline{\Conf}_3^{\mathrm{ord}}$, and
\item the pentagon relation on the codimension-one Stasheff cell complex
 of $\overline{\Conf}_4^{\mathrm{ord}}$.
\end{enumerate}
\end{theorem}

\begin{proof}
The codimension-one boundary strata of
$\overline{\Conf}_3^{\mathrm{ord}}$ corresponding to the bracketings
$(12)3$ and $1(23)$ admit collar charts in which the regularized
holonomy factors as the ordered product of the two-body holonomies.
The comparison between these two collar factorizations is exactly the
comparison holonomy $\Phi(w,z)$, which yields the quasi-hexagon.

For $n=4$, the codimension-one boundary strata form the Stasheff
pentagon. Flatness of the four-point connection implies that the total
regularized transport around the boundary of that pentagon is the
identity. Writing that transport as the product of the five comparison
holonomies gives the pentagon relation.
\end{proof}

\begin{definition}[Spectral cochain complex and spectral Drinfeld class]
Let
\[
C^2_{\mathrm{spec}}(A)=\{g(u)\in A^{\widehat\otimes 2}\},
\qquad
C^3_{\mathrm{spec}}(A)=\{\phi(w,z)\in A^{\widehat\otimes 3}\}.
\]
Define the linearized spectral differential by
\[
(\delta g)(w,z)
=
1\otimes g(z)
+ (\operatorname{id}\otimes \Delta_z)g(w)
- (\Delta_w\otimes \operatorname{id})g(z)
- g(w)\otimes 1.
\]
The degree-three cohomology of the resulting complex is denoted by
$H^3_{\mathrm{spec}}(A)$.
If
\[
\Phi(w,z)=1+\phi_n(w,z)\pmod{F^{n+1}}
\]
with $\phi_n$ the first nontrivial term, then its class
\[
\mathfrak D_{\mathrm{spec}}(A,\Omega):=[\phi_n]
\in H^3_{\mathrm{spec}}(\operatorname{gr}^n A)
\]
is called the \emph{spectral Drinfeld class}.
\end{definition}

\begin{remark}[Well-definedness of the spectral Drinfeld class]
The spectral Drinfeld class is well-defined because the Hochschild-type
obstruction cocycle it measures is independent of the choice of
filtration splitting: different splittings produce cohomologous cocycles,
so the class in $H^3_{\mathrm{spec}}(\operatorname{gr}^n A)$ is intrinsic.
\end{remark}

\begin{theorem}[Strictification by spectral cohomology; \ClaimStatusProvedHere]
\label{thm:strictification-spectral-cohomology}
Suppose
\[
\Phi(w,z)=1+\phi_n(w,z)\pmod{F^{n+1}}
\]
with $n\ge 2$. Then:
\begin{enumerate}
\item $\phi_n$ is a $3$-cocycle in the spectral complex;
\item under a spectral twist $G_n(u)=1+g_n(u)\pmod{F^{n+1}}$ one has
 \[
 \phi_n\longmapsto \phi_n+\delta g_n;
 \]
\item if $[\phi_n]=0$ in
 $H^3_{\mathrm{spec}}(\operatorname{gr}^nA)$, then a twist exists which
 kills $\phi_n$ modulo $F^{n+1}$;
\item if $H^3_{\mathrm{spec}}(\operatorname{gr}^nA)=0$ for all $n\ge 2$,
 then there is a filtered twist $G$ for which $\Phi^G=1$, hence the
 quasi-factorization datum strictifies to an honest spectral
 factorization $R$-matrix.
\end{enumerate}
\end{theorem}

\begin{proof}
Expand the pentagon relation in the first nontrivial filtration degree.
All nonlinear terms are of higher filtration, so the degree-$n$ term
satisfies the linearized pentagon, i.e. it is a cocycle. Expanding the
standard twist formula for the quasi-associator to degree $n$ yields the
addition by the coboundary $\delta g_n$. Killing the first nontrivial
term and iterating recursively proves the last two statements.
\end{proof}

\begin{conclusion}[First conceptual reduction]
The dg-shifted Yangian/factorization bridge is not a binary question.
There is first a canonical passage from bar-horizontal strictification
data for a dg-shifted Yangian to a spectral quasi-factorization package,
\[
\text{dg-shifted Yangian + bar-horizontal strictification}
\longrightarrow
\text{spectral quasi-factorization quantum group},
\]
and only then a strictification problem. The latter is controlled by a
concrete filtered cohomology theory.
\end{conclusion}

\section{Low-order algebra: quadratic and cubic control}

\begin{proposition}[Quadratic hexagon obstruction; \ClaimStatusProvedHere]
Let $\widetilde r(z)$ be the suspended degree-zero kernel. Define the
naive multiplicative two-jet
\[
R^{(2)}(z)=1+\widetilde r(z)+\frac12\widetilde r(z)^{\star 2}.
\]
Assume the infinitesimal coassociativity identities
\begin{align*}
(\operatorname{id}\otimes \Delta_z)\widetilde r(z+w)
&=\widetilde r_{12}(w)+\widetilde r_{13}(z+w),\\
(\Delta_w\otimes \operatorname{id})\widetilde r(z)
&=\widetilde r_{13}(z+w)+\widetilde r_{23}(z).
\end{align*}
Then modulo $F^3$,
\begin{align*}
(\operatorname{id}\otimes \Delta_z)R^{(2)}(z+w)-R^{(2)}_{12}(w)R^{(2)}_{13}(z+w)
&\equiv \frac12[\widetilde r_{13}(z+w),\widetilde r_{12}(w)],\\
(\Delta_w\otimes \operatorname{id})R^{(2)}(z)-R^{(2)}_{13}(z+w)R^{(2)}_{23}(z)
&\equiv \frac12[\widetilde r_{23}(z),\widetilde r_{13}(z+w)].
\end{align*}
\end{proposition}

\begin{proof}
Expand both sides to second order and subtract. The square terms cancel
except for the order-sensitive cross terms, which produce the displayed
commutators.
\end{proof}

\begin{proposition}[Three-particle obstruction identity; \ClaimStatusProvedHere]
Let $B^{\le 3}(Y)$ be the reduced bar coalgebra truncated at tensor
length $3$, and let $I_{\widetilde r}$ be the adjacent-gap insertion
coderivation determined by $\widetilde r$. Put
\[
D=d_B+I_{\widetilde r}.
\]
Assume the one-body and two-body Maurer--Cartan identities already
hold. Then on tensor length $3$,
\[
D^2=I_{\mathfrak Y_{\widetilde r}},
\]
where
\[
\mathfrak Y_{\widetilde r}(z,w)=
MC(\widetilde r_{12}(w)+\widetilde r_{13}(z+w)+\widetilde r_{23}(z))
-MC(\widetilde r_{12}(w))
-MC(\widetilde r_{13}(z+w))
-MC(\widetilde r_{23}(z)).
\]
Thus the tensor-length-$3$ obstruction is exactly the
$A_\infty$ Yang--Baxter defect.
\end{proposition}

\begin{proof}
Expand
\[
D^2=[d_B,I_{\widetilde r}] + I_{\widetilde r}^2.
\]
On length $3$, disjoint insertions cancel by coderivation signs.
The surviving terms are exactly the overlapping insertions in the three
ordered gaps. These assemble into the bar realization of the displayed
Maurer--Cartan defect.
\end{proof}

\begin{theorem}[Abelian strictification theorem; \ClaimStatusProvedHere]
\label{thm:abelian-strictification}
Assume that all coefficients of $\widetilde r(z)$ supercommute after
suspension, that $m_k=0$ for $k\ge 3$, and that the underlying
coproduct is cocommutative. Then
\[
R(z)=\exp_\star(\widetilde r(z))
\]
converges and defines an honest spectral $R$-matrix on the completed
bialgebra underlying $Y$.
\end{theorem}

\begin{proof}
The infinitesimal coassociativity identities exponentiate because all
coefficients commute. The hexagon identities for the exponentiated
coproduct follow from the BCH formula: since all coefficients
commute, BCH reduces to ordinary addition, and the hexagon relation
exponentiates termwise. Cocommutativity implies almost
cocommutativity automatically in the commuting completion.
\end{proof}

\begin{theorem}[Residue-bounded completion theorem; \ClaimStatusProvedHere]
\label{thm:residue-bounded-completion}
Let $Y=\varprojlim_N Y_N$ be residue-bounded and complete, where
$Y_N=Y/F^{N+1}Y$. Assume:
\begin{enumerate}
\item each $Y_N$ is quadratic-Koszul;
\item the induced kernels satisfy the three-particle identity above;
\item the inverse system $H^m(B(Y_N))$ is Mittag--Leffler for every $m$.
\end{enumerate}
Then the completed coderivation
\[
D=d_B+I_{\widetilde r}
\]
converges continuously on $\widehat B(Y)$, satisfies $D^2=0$, and the
completed cobar comparison
\[
\Omega\widehat B(Y)\longrightarrow Y
\]
is a quasi-isomorphism.
\end{theorem}

\begin{proof}
Residue-boundedness implies that on each fixed filtration quotient only
finitely many residues contribute, hence the coderivation converges.
The three-particle obstruction identity implies $D^2=0$ quotientwise;
separatedness of the filtration ($\bigcap_n F^n = 0$ by the
pole-order bound) passes the identity to the inverse limit.
Quadratic-Koszulness gives quotientwise bar--cobar
quasi-isomorphisms (by \cite[Proposition~2.2.1]{LV12}), and the
Mittag--Leffler hypothesis (which holds because the transition maps
$H^m(B(Y_{N+1}))\to H^m(B(Y_N))$ are surjective) passes
quasi-isomorphism to the inverse limit.
\end{proof}

\section{Exact Cartan transport and the first genuine shifted examples}

\begin{construction}[Cartan shift cocycle]
Let $H$ be a completed commutative primitive Cartan bialgebra with
primitive generators $h_1,\dots,h_\ell$. Suppose the shifted Cartan
currents are
\[
H_i(u)=
\frac{\prod_j (u-a_j^{(i)})}{\prod_k (u-b_k^{(i)})}.
\]
Set
\[
\phi_i(u)=\log H_i(u).
\]
Define the formal bicharacter
\[
F_\mu(u)=
\exp\!\left(\sum_{i=1}^{\ell} \phi_i(u)\,h_i\otimes h_i\right).
\]
\end{construction}

\begin{proposition}[Cartan shift cocycle identities; \ClaimStatusProvedHere]
\label{prop:cartan-shift-cocycle}
The formal bicharacter $F_\mu(u)$ satisfies
\begin{align*}
(\operatorname{id}\otimes \Delta)F_\mu(u)
&=F_\mu^{12}(u)F_\mu^{13}(u),\\
(\Delta\otimes \operatorname{id})F_\mu(u)
&=F_\mu^{13}(u)F_\mu^{23}(u),
\end{align*}
and is additive in the shift parameter whenever the logarithms are.
\end{proposition}

\begin{proof}
Since $\Delta h_i=h_i\otimes 1+1\otimes h_i$ and the $h_i$ commute,
the exponent splits exactly under either iterated coproduct.
\end{proof}

\begin{theorem}[Cartan gauge-twist theorem; \ClaimStatusProvedHere]
\label{thm:cartan-gauge-twist}
Let
\[
\mathbb D_n^0=(d+d_{\mathrm{dR}})-A_n^0
\]
be an unshifted derived KZ differential. Suppose that on the chosen
sector the operators $h_i^{(a)}h_i^{(b)}$ commute with $A_n^0$.
Set
\[
S_{\mu,n}=
\sum_{1\le a<b\le n}\sum_{i=1}^{\ell}
\phi_i(z_b-z_a)\,h_i^{(a)}h_i^{(b)},
\qquad
G_{\mu,n}=e^{-S_{\mu,n}}.
\]
Then
\[
\mathbb D_n^\mu=G_{\mu,n}\,\mathbb D_n^0\,G_{\mu,n}^{-1}
=(d+d_{\mathrm{dR}})-A_n^\mu
\]
has connection form
\[
A_n^\mu
=
A_n^0
+
\sum_{1\le a<b\le n}\sum_{i=1}^{\ell}
\phi_i'(z_b-z_a)\,h_i^{(a)}h_i^{(b)}\,d(z_b-z_a).
\]
\end{theorem}

\begin{proof}
The $h_i$ commute in the dg-shifted setting because the Cartan
subalgebra $\mathfrak{h}\subset\mathfrak{g}$ is abelian, and the
dg-shifted coproduct preserves commutativity. Because the exponents
commute on the sector in question,
\[
dG_{\mu,n}\,G_{\mu,n}^{-1}=-dS_{\mu,n}.
\]
The stated commutation hypothesis implies
$G_{\mu,n}A_n^0G_{\mu,n}^{-1}=A_n^0$, so the gauge transform contributes
exactly $dS_{\mu,n}$.
\end{proof}

\begin{theorem}[Cartan-diagonal shift defect is exact; \ClaimStatusProvedHere]
\label{thm:cartan-diagonal-defect-exact}
Fix a Cartan-diagonal line $L_\lambda$ and write
\[
\phi_i(u)=\log H_i(u).
\]
The shifted two-body scalar factor is
\[
R_{\mu,\lambda}^{\mathrm{sh}}(u)=
\exp\!\Big(\sum_i \lambda_i^2\phi_i(u)\Big).
\]
The three-body quasi-hexagon defect is therefore
\[
\Phi_{\mu,\lambda}^{\mathrm{sh}}(w,z)=
\frac{R_{\mu,\lambda}^{\mathrm{sh}}(w+z)}{R_{\mu,\lambda}^{\mathrm{sh}}(w)
R_{\mu,\lambda}^{\mathrm{sh}}(z)},
\]
and its logarithm is
\[
\mathfrak D_{\mathrm{spec},\mu}^{\lambda}(w,z)=
\sum_i \lambda_i^2\big(\phi_i(w+z)-\phi_i(w)-\phi_i(z)\big).
\]
Hence the Cartan-diagonal contribution to the spectral Drinfeld class is
exact.
\end{theorem}

\begin{proof}
Immediate from the definition of the shifted scalar transport.
\end{proof}

\begin{remark}[First genuine shifted examples]
The framed $A_1$ shifted Yangian and the staircase shifted Yangians of
finite type~$A$ furnish the first genuine shifted examples. In all such
Cartan-diagonal sectors, the shift produces a visible three-body
logarithmic defect but no cohomological obstruction class.
\end{remark}

\section{Filtration $2$: adjacent-root triangles}

The first genuinely mixed-root sector arises from adjacent simple roots.
Let $i\sim j$ be adjacent simple roots in a rank-$2$ Levi of type $A_2$.
Set
\[
E_{ij}=[E_i,E_j],
\qquad
F_{ij}=[F_j,F_i],
\]
so that $[F_i,F_j]=-F_{ij}$.
For $a\neq b$, write
\[
X_i^{ab}(u)=\rho_i(u)E_i^{(a)}F_i^{(b)},
\qquad
X_{ij}^{ab}(u)=\rho_{ij}(u)E_{ij}^{(a)}F_{ij}^{(b)}.
\]

\begin{definition}[Triangle sectors]
On three tensor factors define the left and right adjacent-root triangle
vectors
\[
T_{ij}^{L}=E_{ij}^{(1)}F_i^{(2)}F_j^{(3)},
\qquad
T_{ij}^{R}=E_i^{(1)}E_j^{(2)}F_{ij}^{(3)}.
\]
The corresponding opposite orientations are
\[
T_{ji}^{L}=E_{ij}^{(1)}F_j^{(2)}F_i^{(3)},
\qquad
T_{ji}^{R}=E_j^{(1)}E_i^{(2)}F_{ij}^{(3)}.
\]
\end{definition}

\begin{theorem}[Triangle localization formula; \ClaimStatusProvedHere]
\label{thm:triangle-localization}
Let
\[
S_{12}(w)=\rho_i(w)E_i^{(1)}F_i^{(2)}+\rho_j(w)E_j^{(1)}F_j^{(2)}+\cdots,
\]
\[
S_{13}(w+z)=\rho_i(w+z)E_i^{(1)}F_i^{(3)}
+\rho_j(w+z)E_j^{(1)}F_j^{(3)}+\cdots.
\]
Then
\[
\Pi_{\langle T_{ij}^{L},T_{ji}^{L}\rangle}\frac12[S_{12}(w),S_{13}(w+z)]
=
\frac12\rho_i(w)\rho_j(w+z)T_{ij}^{L}
-
\frac12\rho_j(w)\rho_i(w+z)T_{ji}^{L}.
\]
Similarly,
\[
\Pi_{\langle T_{ij}^{R},T_{ji}^{R}\rangle}\frac12[S_{13}(w+z),S_{23}(z)]
=
-\frac12\rho_i(w+z)\rho_j(z)T_{ij}^{R}
+
\frac12\rho_j(w+z)\rho_i(z)T_{ji}^{R}.
\]
\end{theorem}

\begin{proof}
The only contributing commutators are
\[
[E_i^{(1)}F_i^{(2)},E_j^{(1)}F_j^{(3)}]
=E_{ij}^{(1)}F_i^{(2)}F_j^{(3)},
\]
and
\[
[E_j^{(1)}F_j^{(2)},E_i^{(1)}F_i^{(3)}]
=-E_{ij}^{(1)}F_j^{(2)}F_i^{(3)},
\]
with the analogous computation on the right using
$[F_i,F_j]=-F_{ij}$.
\end{proof}

\begin{definition}[Triangle coproduct coefficients]
Let $\Delta_z$ be the twisted coproduct. Define the triangle transport
coefficients by
\[
\Pi_{\langle T_{ij}^{L},T_{ji}^{L}\rangle}
\big((\operatorname{id}\otimes\Delta_z)X_{ij}^{12}(w)\big)
=
\kappa_{ij}^{L}(w,z)T_{ij}^{L}-\kappa_{ji}^{L}(w,z)T_{ji}^{L},
\]
and similarly on the right,
\[
\Pi_{\langle T_{ij}^{R},T_{ji}^{R}\rangle}
\big((\Delta_w\otimes\operatorname{id})X_{ij}^{23}(z)\big)
=
-\kappa_{ij}^{R}(w,z)T_{ij}^{R}+\kappa_{ji}^{R}(w,z)T_{ji}^{R}.
\]
\end{definition}

\begin{theorem}[Adjacent-root rigidity; \ClaimStatusProvedHere]
\label{thm:adjacent-root-rigidity}
The filtration-$2$ hexagon defect vanishes in the oriented triangle
sectors if and only if
\begin{align*}
\rho_{ij}(w)\kappa_{ij}^{L}(w,z)&=\frac12\rho_i(w)\rho_j(w+z),\\
\rho_{ij}(w)\kappa_{ji}^{L}(w,z)&=\frac12\rho_j(w)\rho_i(w+z),\\
\rho_{ij}(z)\kappa_{ij}^{R}(w,z)&=\frac12\rho_i(w+z)\rho_j(z),\\
\rho_{ij}(z)\kappa_{ji}^{R}(w,z)&=\frac12\rho_j(w+z)\rho_i(z).
\end{align*}
\end{theorem}

\begin{proof}
Project the logarithm of the product side to the triangle sectors.
The only contributions are the commutator terms computed in
Theorem~\ref{thm:triangle-localization}. On the coproduct side,
$X_{ij}$ is the unique root generator whose twisted coproduct can land in
those sectors. Equality of coefficients gives the claim.
\end{proof}

\begin{corollary}[Normalized rational triangle coefficient; \ClaimStatusProvedHere]
Assume the rational ansatz
\[
\rho_i(u)=\frac{c_i}{u},
\qquad
\rho_j(u)=\frac{c_j}{u},
\qquad
\rho_{ij}(u)=\frac{c_{ij}}{u},
\]
and
\[
\kappa_{ij}^{L}(w,z)=\frac{\lambda_{ij}^{L}}{w+z},
\qquad
\kappa_{ij}^{R}(w,z)=\frac{\lambda_{ij}^{R}}{w+z},
\]
with the same form for the opposite orientations. Then
\[
\lambda_{ij}^{L}=
\lambda_{ji}^{L}=
\lambda_{ij}^{R}=
\lambda_{ji}^{R}=
\frac{c_ic_j}{2c_{ij}}.
\]
In the normalized case $c_i=c_j=c_{ij}=1$, the universal coefficient is
$\frac12$.
\end{corollary}

\begin{proof}
Substitute the rational ansatz into the equations of
Theorem~\ref{thm:adjacent-root-rigidity}.
\end{proof}

\begin{remark}[Fortification: transport, not naive invariance]
\label{rem:transport-not-invariance}
A naive statement of ``shift-invariance'' at mixed-root level is too
coarse and, in general, false if interpreted coefficientwise. The shift
changes the local mixed-root coefficients by explicit ratios of shift
characters at \emph{different spectral arguments}. What is invariant is
not the raw coefficient but the obstruction class after transport by the
shift cocycle.
\end{remark}

\begin{proposition}[Triangle shift transport law; \ClaimStatusProvedHere]
\label{prop:triangle-shift-transport}
Suppose the shifted root coefficients satisfy
\[
\rho_\alpha^{\mu}(u)=\chi_\alpha^{\mu}(u)\,\rho_\alpha^{0}(u)
\]
for scalar shift characters $\chi_\alpha^{\mu}(u)$.
Assume the unshifted triangle coefficients solve the rigidity equations.
Then the shifted coefficients are uniquely forced to be
\begin{align*}
\kappa_{ij}^{L,\mu}(w,z)
&=
\frac{\chi_i^{\mu}(w)\chi_j^{\mu}(w+z)}{\chi_{ij}^{\mu}(w)}
\,\kappa_{ij}^{L,0}(w,z),\\
\kappa_{ij}^{R,\mu}(w,z)
&=
\frac{\chi_i^{\mu}(w+z)\chi_j^{\mu}(z)}{\chi_{ij}^{\mu}(z)}
\,\kappa_{ij}^{R,0}(w,z),
\end{align*}
with the analogous formulas for the opposite orientations.
\end{proposition}

\begin{proof}
Insert the shifted coefficients into the identities of
Theorem~\ref{thm:adjacent-root-rigidity} and solve for
$\kappa^{L,\mu}$ and $\kappa^{R,\mu}$.
\end{proof}

\begin{interpretation}
The first mixed-root sector already detects shift sensitivity at the
level of local transport functions. But this sensitivity is completely
forced by the shifted one-body characters; it does not define a new
independent obstruction class.
\end{interpretation}

\section{The exact free two-body model}

The free example of \cite{DNP25} admits a particularly transparent
computation. Write
\[
X(x)=\sum_{n\ge 0} X_n x^n,
\qquad
\Psi(x)=\sum_{n\ge 0} \psi_n x^n.
\]
The dg kernel in the free model is
\[
r(u)=\sum_{n,m\ge 0}(-1)^n\binom{n+m}{m}
\frac{\psi_n\otimes X_m-X_n\otimes \psi_m}{u^{n+m+1}}.
\]

\begin{lemma}[Closed generating kernel; \ClaimStatusProvedHere]
\label{lem:free-closed-generating-kernel}
Coefficientwise in $x,y$,
\[
\sum_{n,m\ge 0}(-1)^n\binom{n+m}{m}\frac{x^n y^m}{u^{n+m+1}}
=
\frac{1}{u+x-y}.
\]
Hence the free suspended kernel is the coefficientwise expansion of
\[
\mathcal R_{\mathrm{free}}(u;x,y)=
\frac{\Psi(x)\otimes X(y)-X(x)\otimes \Psi(y)}{u+x-y}.
\]
\end{lemma}

\begin{proof}
Summing over $N=n+m$ gives
\begin{align*}
\sum_{n,m\ge 0}(-1)^n\binom{n+m}{m}\frac{x^n y^m}{u^{n+m+1}}
&=
\frac1u\sum_{N\ge 0}\frac1{u^N}
\sum_{m=0}^N \binom{N}{m}(-x)^{N-m}y^m\\
&=
\frac1u\sum_{N\ge 0}\left(\frac{y-x}{u}\right)^N
=
\frac{1}{u+x-y}.
\end{align*}
\end{proof}

\begin{theorem}[Exact free two-body transport; \ClaimStatusProvedHere]
\label{thm:exact-free-transport}
Let
\[
\Theta(x,y)=\Psi(x)\otimes X(y)-X(x)\otimes \Psi(y).
\]
In the free supercommutative model, $\Theta(x,y)^2=0$. Therefore the
connection
\[
\nabla_{\mathrm{free}}=d-
\frac{\Theta(x,y)}{u+x-y}\,du
\]
integrates exactly with transport
\[
T(u,u_0)=1+\Theta(x,y)\log\!\frac{u+x-y}{u_0+x-y}.
\]
The local monodromy around the formal divisor $u+x-y=0$ is
\[
M_{\mathrm{loop}}=1+2\pi i\,\Theta(x,y).
\]
\end{theorem}

\begin{proof}
Because $\Theta^2=0$,
\[
\exp\left(\Theta\log\!\frac{u+x-y}{u_0+x-y}\right)
=1+\Theta\log\!\frac{u+x-y}{u_0+x-y}.
\]
Differentiating gives the transport equation. The monodromy follows by
adding $2\pi i$ to the logarithm around a loop.
\end{proof}

\section{Filtration $3$: root quadrilaterals}

Performing the first genuinely class-$3$ computation.
Let $i\sim j\sim k$ be a chain of simple roots of type $A_3$ with
$i$ not adjacent to $k$. Define the composite roots by
\[
E_{ij}=[E_i,E_j],
\qquad
E_{jk}=[E_j,E_k],
\qquad
E_{ijk}=[E_{ij},E_k]=[E_i,E_{jk}],
\]
and for the opposite side set
\[
F_{ij}=[F_j,F_i],
\qquad
F_{jk}=[F_k,F_j],
\qquad
F_{ijk}=[F_k,F_{ij}]=[F_{jk},F_i].
\]
Then
\[
[F_i,F_j]=-F_{ij},
\qquad
[F_j,F_k]=-F_{jk},
\qquad
[F_i,F_{jk}]=-[F_k,F_{ij}]=-F_{ijk}.
\]

\begin{definition}[Root-quadrilateral sectors]
On four tensor factors define the oriented left and right quadrilateral
vectors
\[
Q_{ijk}^{L}=E_{ijk}^{(1)}F_i^{(2)}F_j^{(3)}F_k^{(4)},
\qquad
Q_{ijk}^{R}=E_i^{(1)}E_j^{(2)}E_k^{(3)}F_{ijk}^{(4)}.
\]
The opposite orientation is obtained by replacing $(i,j,k)$ by
$(k,j,i)$ and the sign conventions above.
\end{definition}

\begin{lemma}[Class-$3$ ordered BCH coefficient; \ClaimStatusProvedHere]
\label{lem:class3-ordered-bch}
Let $X,Y,Z$ lie in a class-$3$ nilpotent Lie algebra, so all
commutators of depth $4$ vanish. The multilinear $XYZ$-part of
$\log(e^Xe^Ye^Z)$ is
\[
\frac14[[X,Y],Z]+\frac1{12}[X,[Y,Z]]+\frac1{12}[Y,[X,Z]].
\]
If, in addition, $[X,Z]=0$, then this simplifies to
\[
\operatorname{mult}_{XYZ}\log(e^Xe^Ye^Z)
=\frac13[X,[Y,Z]].
\]
\end{lemma}

\begin{proof}
Write
\[
U=\log(e^Xe^Y)=X+Y+\frac12[X,Y]+\frac1{12}[X,[X,Y]]
+\frac1{12}[Y,[Y,X]].
\]
Now compute
\[
\log(e^Xe^Ye^Z)=\log(e^Ue^Z)
=U+Z+\frac12[U,Z]+\frac1{12}[U,[U,Z]]+\frac1{12}[Z,[Z,U]].
\]
Retaining only the multilinear $XYZ$-part gives the first displayed
formula. If $[X,Z]=0$, then
\[
[[X,Y],Z]=[X,[Y,Z]]
\]
by Jacobi, and the second formula follows.
\end{proof}

\begin{theorem}[Quadrilateral localization formula; \ClaimStatusProvedHere]
\label{thm:quadrilateral-localization}
Let
\[
X_i^{12}(u)=\rho_i(u)E_i^{(1)}F_i^{(2)},
\qquad
X_j^{13}(u+v)=\rho_j(u+v)E_j^{(1)}F_j^{(3)},
\qquad
X_k^{14}(u+v+t)=\rho_k(u+v+t)E_k^{(1)}F_k^{(4)}.
\]
Then the projection of
\[
\log\Big(e^{X_i^{12}(u)}e^{X_j^{13}(u+v)}e^{X_k^{14}(u+v+t)}\Big)
\]
to the left quadrilateral sector is
\[
\frac13\rho_i(u)\rho_j(u+v)\rho_k(u+v+t)\,Q_{ijk}^{L}.
\]
Similarly, the projection of
\[
\log\Big(e^{\rho_i(u+v+t)E_i^{(1)}F_i^{(4)}}
 e^{\rho_j(v+t)E_j^{(2)}F_j^{(4)}}
 e^{\rho_k(t)E_k^{(3)}F_k^{(4)}}\Big)
\]
to the right quadrilateral sector is
\[
-\frac13\rho_i(u+v+t)\rho_j(v+t)\rho_k(t)\,Q_{ijk}^{R}.
\]
\end{theorem}

\begin{proof}
For the left sector, set
\[
X=X_i^{12}(u),\qquad Y=X_j^{13}(u+v),\qquad Z=X_k^{14}(u+v+t).
\]
Since $i$ and $k$ are nonadjacent, $[X,Z]=0$.
By Lemma~\ref{lem:class3-ordered-bch}, the multilinear part is
$\frac13[X,[Y,Z]]$. Now
\[
[Y,Z]=\rho_j(u+v)\rho_k(u+v+t)E_{jk}^{(1)}F_j^{(3)}F_k^{(4)},
\]
and then
\[
[X,[Y,Z]]=
\rho_i(u)\rho_j(u+v)\rho_k(u+v+t)
E_{ijk}^{(1)}F_i^{(2)}F_j^{(3)}F_k^{(4)}.
\]
This proves the first formula.

For the right sector, set
\[
X=\rho_i(u+v+t)E_i^{(1)}F_i^{(4)},
\quad
Y=\rho_j(v+t)E_j^{(2)}F_j^{(4)},
\quad
Z=\rho_k(t)E_k^{(3)}F_k^{(4)}.
\]
Again $[X,Z]=0$, so the multilinear part is
$\frac13[X,[Y,Z]]$. Here
\[
[Y,Z]=-
\rho_j(v+t)\rho_k(t)E_j^{(2)}E_k^{(3)}F_{jk}^{(4)},
\]
so
\[
[X,[Y,Z]]=-
\rho_i(u+v+t)\rho_j(v+t)\rho_k(t)
E_i^{(1)}E_j^{(2)}E_k^{(3)}F_{ijk}^{(4)}.
\]
This is the second formula.
\end{proof}

\begin{definition}[Quadrilateral coproduct coefficients]
Let $\Delta^{(2)}_{v,t}$ denote the two-step twisted coproduct
separating one factor into three ordered factors with spectral gaps
$v,t$. Define the left and right quadrilateral transport coefficients
by
\[
\Pi_{\langle Q_{ijk}^{L}\rangle}
\big((\operatorname{id}\otimes\Delta^{(2)}_{v,t})X_{ijk}^{12}(u)\big)
=
\Lambda_{ijk}^{L}(u,v,t)Q_{ijk}^{L},
\]
\[
\Pi_{\langle Q_{ijk}^{R}\rangle}
\big((\Delta^{(2)}_{u,v}\otimes\operatorname{id})X_{ijk}^{34}(t)\big)
=
\Lambda_{ijk}^{R}(u,v,t)Q_{ijk}^{R}.
\]
\end{definition}

\begin{theorem}[Quadrilateral rigidity; \ClaimStatusProvedHere]
\label{thm:quadrilateral-rigidity}
The filtration-$3$ defect vanishes in the oriented quadrilateral sectors
if and only if
\begin{align*}
\rho_{ijk}(u)\Lambda_{ijk}^{L}(u,v,t)
&=
\frac13\rho_i(u)\rho_j(u+v)\rho_k(u+v+t),\\
\rho_{ijk}(t)\Lambda_{ijk}^{R}(u,v,t)
&=
\frac13\rho_i(u+v+t)\rho_j(v+t)\rho_k(t).
\end{align*}
\end{theorem}

\begin{proof}
Project the logarithm of the ordered product of the relevant two-body
factors to the quadrilateral sector. By
Theorem~\ref{thm:quadrilateral-localization}, the product side has the
stated coefficient.
On the coproduct side, a quadrilateral vector with three distinct simple
lowering or raising operators in separate tensor factors can only arise
from the triple-root generator $X_{ijk}$: any simple-root or two-root
composite generator remains supported in at most two root colors and
cannot land in $Q_{ijk}^{L}$ or $Q_{ijk}^{R}$ after projection.
Equality of coefficients yields the claim.
\end{proof}

\begin{corollary}[Normalized rational quadrilateral coefficient; \ClaimStatusProvedHere]
\label{cor:quadrilateral-normalized-rational}
Assume the rational ansatz
\[
\rho_i(u)=\frac{c_i}{u},
\qquad
\rho_j(u)=\frac{c_j}{u},
\qquad
\rho_k(u)=\frac{c_k}{u},
\qquad
\rho_{ijk}(u)=\frac{c_{ijk}}{u}.
\]
Suppose further that the quadrilateral coefficients have translation-
covariant form
\[
\Lambda_{ijk}^{L}(u,v,t)=\frac{\lambda_{ijk}^{L}}{(u+v)(u+v+t)},
\qquad
\Lambda_{ijk}^{R}(u,v,t)=\frac{\lambda_{ijk}^{R}}{(v+t)(u+v+t)}.
\]
Then
\[
\lambda_{ijk}^{L}=\lambda_{ijk}^{R}=\frac{c_ic_jc_k}{3c_{ijk}}.
\]
In the normalized case $c_i=c_j=c_k=c_{ijk}=1$, the universal
quadrilateral coefficient is
\[
\boxed{\frac13.}
\]
\end{corollary}

\begin{proof}
Substitute the rational ansatz into the identities of
Theorem~\ref{thm:quadrilateral-rigidity}.
\end{proof}

\begin{proposition}[Quadrilateral shift transport law; \ClaimStatusProvedHere]
\label{prop:quadrilateral-shift-transport}
Assume again that the shifted one-body coefficients factor as
\[
\rho_\alpha^{\mu}(u)=\chi_\alpha^{\mu}(u)\,\rho_\alpha^0(u).
\]
If the unshifted coefficients solve
Theorem~\ref{thm:quadrilateral-rigidity}, then the shifted quadrilateral
transport coefficients are uniquely forced to be
\begin{align*}
\Lambda_{ijk}^{L,\mu}(u,v,t)
&=
\frac{\chi_i^{\mu}(u)\chi_j^{\mu}(u+v)\chi_k^{\mu}(u+v+t)}
{\chi_{ijk}^{\mu}(u)}
\,\Lambda_{ijk}^{L,0}(u,v,t),\\
\Lambda_{ijk}^{R,\mu}(u,v,t)
&=
\frac{\chi_i^{\mu}(u+v+t)\chi_j^{\mu}(v+t)\chi_k^{\mu}(t)}
{\chi_{ijk}^{\mu}(t)}
\,\Lambda_{ijk}^{R,0}(u,v,t).
\end{align*}
\end{proposition}

\begin{proof}
Insert the shifted coefficients into the two equations of
Theorem~\ref{thm:quadrilateral-rigidity} and solve for
$\Lambda^{L,\mu}$ and $\Lambda^{R,\mu}$.
\end{proof}

\begin{corollary}[No new independent shift obstruction in filtration $3$; \ClaimStatusProvedHere]
\label{cor:no-new-filtration3-shift-obstruction}
A new shift-sensitive \emph{function} first appears in filtration $3$
through the transport laws of
Proposition~\ref{prop:quadrilateral-shift-transport}; however, this
function is entirely forced by the shifted one-body characters. Thus no
new \emph{independent} obstruction class appears in the oriented
root-quadrilateral sector.
\end{corollary}

\begin{proof}
The quadrilateral coefficient is uniquely determined by lower data once
Theorem~\ref{thm:quadrilateral-rigidity} holds. Therefore its shift
variation contributes no new free parameter and no new independent
cohomology class.
\end{proof}

\begin{remark}[First place the frontier moves]
The corrected picture is now sharp.
\begin{enumerate}
\item Cartan-diagonal sectors produce exact defects.
\item Commuting sectors strictify directly.
\item Adjacent-root triangles are forced by a universal coefficient
 $\frac12$, transported explicitly by shift characters.
\item Root quadrilaterals are forced by a universal coefficient
 $\frac13$, again transported explicitly by shift characters.
\end{enumerate}
At the level of this low-order analysis, the first place where a
genuinely new and independent obstruction \emph{could} live is in
filtration $\ge 4$, where new Hall words and higher Magnus/BCH
terms enter: the $D_4$ star, for instance, gives a two-dimensional
free multilinear Lie space. The resolution comes in
\S\ref{thm:root-space-one-dim}--\S\ref{thm:complete-strictification}:
root multiplicity one (the defining representation-theoretic
property of simple Lie algebras) collapses every root sector to
one dimension, closing this frontier universally. The low-order
coefficients $\frac12$ and $\frac13$ are the first instances of
the universal $\frac1n$, but the vanishing of the obstruction does
not depend on these numerical values.
\end{remark}

\section{Conditional global strictification criterion}

\begin{theorem}[Conditional strictification criterion; \ClaimStatusProvedHere]
Assume:
\begin{enumerate}
\item the unshifted dg object strictifies to a factorization quantum
 group with spectral $R$-matrix $R_0$;
\item the shift is implemented by the Cartan cocycle
 of Proposition~\ref{prop:cartan-shift-cocycle};
\item the infinitesimal logarithm of the shifted spectral transport
 agrees with the dg kernel after residue-bounded completion; and
\item the spectral Drinfeld classes vanish.
\end{enumerate}
Then the shifted dg-shifted Yangian admits a completed
$E_1$-chiral/factorization realization whose representation category is
that of an honest spectral factorization quantum group.
\end{theorem}

\begin{proof}
The unshifted strictification gives a strict spectral object.
Transport by the Cartan cocycle gives the shifted quasi-factorization
transport. Vanishing of the spectral Drinfeld class then strictifies the
shifted quasi-object. Residue-bounded completion upgrades finite-stage
compatibility to the full completed statement.
\end{proof}

\section{The strictification theorem}

\subsection{Path-type root sectors}

\begin{definition}[Path-type sector at filtration $n$]
\label{def:path-sector}
Let $\fg$ be a semisimple Lie algebra. A \emph{path-type sector at
filtration~$n$} is determined by a chain of $n$ simple roots
$\alpha_1,\alpha_2,\ldots,\alpha_n$ in the Dynkin diagram such that
$\alpha_i$ is adjacent to $\alpha_{i+1}$ for $1\le i\le n-1$ and
$\alpha_i$ is not adjacent to $\alpha_j$ for $|i-j|\ge 2$. (Such a
chain exists whenever $\fg$ contains a type-$A_n$ subdiagram.)
Define the composite root generators by right-normed iterated brackets:
\[
E_{\alpha_1\cdots\alpha_k}
:=
[E_{\alpha_1},[E_{\alpha_2},\ldots,[E_{\alpha_{k-1}},E_{\alpha_k}]\cdots]]
\qquad (2\le k\le n),
\]
and similarly for the opposite generators $F_{\alpha_1\cdots\alpha_k}$.
The \emph{left $n$-gon vector} and \emph{right $n$-gon vector} on
$n+1$ tensor factors are
\[
P_{\alpha_1\cdots\alpha_n}^{L}
= E_{\alpha_1\cdots\alpha_n}^{(1)}\,
 F_{\alpha_1}^{(2)}\,F_{\alpha_2}^{(3)}\cdots F_{\alpha_n}^{(n+1)},
\qquad
P_{\alpha_1\cdots\alpha_n}^{R}
= E_{\alpha_1}^{(1)}\,E_{\alpha_2}^{(2)}\cdots
 E_{\alpha_n}^{(n)}\,F_{\alpha_1\cdots\alpha_n}^{(n+1)}.
\]
\end{definition}

\begin{remark}
At $n=2$ these recover the triangle vectors $T_{ij}^{L/R}$ of the
adjacent-root computation. At $n=3$ they recover the quadrilateral
vectors $Q_{ijk}^{L/R}$ (relabeling
$(i,j,k)\mapsto(\alpha_1,\alpha_2,\alpha_3)$). The general case is the
$n$-gon sector.
\end{remark}

\subsection{The path one-dimensionality theorem}

\begin{theorem}[Path Lie algebra one-dimensionality; \ClaimStatusProvedHere]
\label{thm:path-one-dim}
Let $L_{\mathrm{path}}(n)$ be the Lie algebra with generators
$X_1,\ldots,X_n$ and relations $[X_i,X_j]=0$ for $|i-j|\ge 2$. Then
the multilinear degree-$n$ component
\[
L_{\mathrm{path}}^n(X_1,\ldots,X_n)
:=
\operatorname{span}\{\text{Lie monomials involving each }X_i\text{ exactly
once}\}
\]
is one-dimensional, generated by the right-normed bracket
\[
[X_1,[X_2,\ldots,[X_{n-1},X_n]\cdots]].
\]
\end{theorem}

\begin{proof}
By induction on $n$.

\medskip\noindent\textbf{Base case} ($n=2$).
The multilinear degree-$2$ space is spanned by $[X_1,X_2]$.

\medskip\noindent\textbf{Inductive step.}
Let $M$ be a multilinear degree-$n$ Lie monomial in $X_1,\ldots,X_n$.
Write $M=[L,R]$ where $L$ involves variables indexed by $S\subset
\{1,\ldots,n\}$ and $R$ involves $T=\{1,\ldots,n\}\setminus S$.

\emph{Step~1: Connectivity.}
For $[L,R]\neq 0$, both $S$ and $T$ must be single connected subpaths
of $1\text{---}2\text{---}\cdots\text{---}n$. We prove that the Lie
algebra generated by any disconnected subset of the path generators is a
direct sum, hence its multilinear Lie monomials vanish.

Suppose $S\subseteq\{1,\ldots,n\}$ decomposes as $S=S_1\sqcup S_2$
with $\max(S_1)<\min(S_2)$ and $\max(S_1)+1<\min(S_2)$ (a gap in the
path). Then $[X_a,X_c]=0$ for all $a\in S_1$, $c\in S_2$ (since
$|a-c|\ge 2$). The Lie algebra generated by $\{X_s:s\in S\}$ is
therefore the direct sum
$\mathrm{Lie}(\{X_s:s\in S_1\})\oplus\mathrm{Lie}(\{X_s:s\in S_2\})$.
A multilinear Lie monomial involving generators from both summands is
zero (every bracket tree must eventually pair elements from different
summands, producing a commutator that vanishes in a direct sum).
Hence $L=0$ whenever $S$ is disconnected. The same argument
applies to~$T$ and~$R$.

\emph{Step~2: Interval partition.}
From Step~1, the only non-vanishing decompositions are
$S=\{1,\ldots,m\}$, $T=\{m{+}1,\ldots,n\}$ for some $1\le m\le n-1$
(or the reverse, but $[L,R]=-[R,L]$). By the induction hypothesis,
$L$ is proportional to $[X_1,[X_2,\ldots,X_m]\cdots]$ and $R$ is
proportional to $[X_{m+1},[X_{m+2},\ldots,X_n]\cdots]$. So
$M$ is proportional to
\[
\bigl[[X_1,\ldots,X_m],\,[X_{m+1},\ldots,X_n]\bigr]
\]
(right-normed brackets on each side).

\emph{Step~3: Reduction to the standard generator.}
We show that
\[
\bigl[[X_1,\ldots,X_m],\,[X_{m+1},\ldots,X_n]\bigr]
=
[X_1,[X_2,\ldots,[X_{n-1},X_n]\cdots]]
\]
in $L_{\mathrm{path}}(n)$ for every $1\le m\le n-1$. Apply the Jacobi
identity:
\begin{multline*}
\bigl[[X_1,\ldots,X_m],\,[X_{m+1},\ldots,X_n]\bigr]
\;=\;
\bigl[X_1,\,\bigl[[X_2,\ldots,X_m],\,[X_{m+1},\ldots,X_n]\bigr]\bigr]\\
{}-
\bigl[[X_2,\ldots,X_m],\,\bigl[X_1,\,[X_{m+1},\ldots,X_n]\bigr]\bigr].
\end{multline*}
For the second term: $[X_1,X_j]=0$ for all $j\ge 3$, hence
$[X_1,[X_{m+1},\ldots,X_n]]=0$ whenever $m\ge 2$ (the outermost
bracket involves $X_1$ and a monomial on $\{X_{m+1},\ldots,X_n\}$;
by induction on bracketing depth, every leaf of that monomial has
$[X_1,X_j]=0$ for $j\ge m+1\ge 3$).

Thus the second term vanishes for $m\ge 2$, and we have
\[
\bigl[[X_1,\ldots,X_m],\,[X_{m+1},\ldots,X_n]\bigr]
=
\bigl[X_1,\,\bigl[[X_2,\ldots,X_m],\,[X_{m+1},\ldots,X_n]\bigr]\bigr].
\]
By the induction hypothesis applied to the subpath $\{2,\ldots,n\}$
(which has $n-1$ generators satisfying the path relations), the inner
bracket $[[X_2,\ldots,X_m],[X_{m+1},\ldots,X_n]]$ is proportional to
$[X_2,[X_3,\ldots,X_n]\cdots]$. Hence
\[
M \propto [X_1,[X_2,\ldots,[X_{n-1},X_n]\cdots]].
\]
This is a single generator, so $\dim L_{\mathrm{path}}^n=1$.
\end{proof}

\subsection{The universal BCH coefficient via the Dynkin projection}

\begin{theorem}[Dynkin coefficient for the ordered path BCH; \ClaimStatusProvedHere]
\label{thm:dynkin-bch-path}
Let $X_1,\ldots,X_n$ satisfy the path commutation relations
$[X_i,X_j]=0$ for $|i-j|\ge 2$. Then the multilinear
$X_1\cdots X_n$-part of the ordered Baker--Campbell--Hausdorff product is
\begin{equation}\label{eq:bch-path-coeff}
\operatorname{mult}_{X_1\cdots X_n}
\log(e^{X_1}\,e^{X_2}\cdots e^{X_n})
\;=\;
\frac{1}{n}\,[X_1,[X_2,\ldots,[X_{n-1},X_n]\cdots]].
\end{equation}
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:path-one-dim}, the multilinear part is
$c_n\cdot[X_1,[X_2,\ldots,X_n]\cdots]$ for a unique scalar $c_n$. We
determine $c_n$ by passing to the universal enveloping algebra and
extracting the coefficient of the concatenation monomial
$X_1\cdot X_2\cdots X_n$.

\medskip\noindent\textbf{Step~1: Coefficient in the Lie bracket.}
In the universal enveloping algebra, the right-normed bracket
$[X_1,[X_2,\ldots,[X_{n-1},X_n]\cdots]]$ expands as a signed sum of
permuted monomials. Its leading term (in the order
$X_1X_2\cdots X_n$) has coefficient $+1$.

\medskip\noindent\textbf{Step~2: Coefficient in the BCH logarithm.}
In the free associative algebra, $e^{X_1}\cdot e^{X_2}\cdots e^{X_n}$
has multilinear part exactly $X_1\cdot X_2\cdots X_n$ (each $X_i$
appears in a single exponential factor, so the multilinear extraction
picks $X_i$ from the degree-$1$ term of $e^{X_i}$ and $1$ from all
other factors).

The multilinear part of $\log(P)$ where $P=e^{X_1}\cdots e^{X_n}$ is
computed via $\log(1+A)=\sum_{k\ge 1}(-1)^{k+1}A^k/k$ with $A=P-1$.
The subset-multilinear decomposition of $A$ gives: the
$S$-multilinear part of $A$ (for $S\subseteq\{1,\ldots,n\}$,
$S\neq\emptyset$) is the ordered product $\prod_{i\in S}^{\to}X_i$.
Therefore
\[
\text{coeff of }X_1\cdots X_n\text{ in }\log(P)
=
\sum_{k=1}^{n}\frac{(-1)^{k+1}}{k}
\cdot
\#\{\text{compositions of }n\text{ into }k\text{ parts}\},
\]
because the monomial $X_1\cdots X_n$ arises from $A^k$ only when the
$k$ factors draw consecutive blocks $\{1,\ldots,i_1\}$,
$\{i_1{+}1,\ldots,i_1{+}i_2\}$, etc.\ (all other set-partitions
reorder the variables). The number of compositions of $n$ into $k$
parts is $\binom{n-1}{k-1}$.

\medskip\noindent\textbf{Step~3: The integral identity.}
We evaluate the resulting sum using the beta integral:
\begin{align*}
\sum_{k=1}^{n}\frac{(-1)^{k+1}}{k}\binom{n-1}{k-1}
&=
\sum_{j=0}^{n-1}\frac{(-1)^{j}}{j+1}\binom{n-1}{j}\\
&=
\sum_{j=0}^{n-1}\binom{n-1}{j}(-1)^j\int_0^1 t^j\,dt\\
&=
\int_0^1\sum_{j=0}^{n-1}\binom{n-1}{j}(-t)^j\,dt\\
&=
\int_0^1(1-t)^{n-1}\,dt
\;=\;\frac{1}{n}.
\end{align*}
\textbf{Step~4: Conclusion.}
Combining Steps~1--3: the coefficient of $X_1\cdots X_n$ in
$c_n\cdot[X_1,\ldots,X_n]$ is $c_n\cdot 1$, and in $\log(P)$ is
$\frac{1}{n}$. Hence $c_n=\frac{1}{n}$.
\end{proof}

\begin{remark}
At $n=2$ this gives $\frac12[X_1,X_2]$; at $n=3$, the coefficient
$\frac13[X_1,[X_2,X_3]]$ of Lemma~\ref{lem:class3-ordered-bch}
(in the path case $[X_1,X_3]=0$). The integral identity
$\int_0^1(1-t)^{n-1}\,dt=1/n$ replaces the case-by-case BCH algebra
with a single uniform argument.
\end{remark}

\subsection{The all-filtration localization formula}

\begin{theorem}[$n$-gon localization formula; \ClaimStatusProvedHere]
\label{thm:ngon-localization}
For a path $\alpha_1\sim\alpha_2\sim\cdots\sim\alpha_n$ in the Dynkin
diagram, set
\[
X_i^{1,\,i+1}(u_i)
=
\rho_{\alpha_i}(u_i)\,E_{\alpha_i}^{(1)}\,F_{\alpha_i}^{(i+1)},
\qquad
u_i = u + \textstyle\sum_{j=1}^{i-1}v_j,
\]
where $(u,v_1,\ldots,v_{n-1})$ are spectral parameters. Then the
projection of
\[
\log\!\Big(e^{X_1^{1,2}(u_1)}\,e^{X_2^{1,3}(u_2)}\cdots
e^{X_n^{1,n+1}(u_n)}\Big)
\]
to the left $n$-gon sector is
\begin{equation}\label{eq:ngon-left}
\frac{1}{n}\,
\rho_{\alpha_1}(u_1)\,\rho_{\alpha_2}(u_2)\cdots\rho_{\alpha_n}(u_n)
\;P_{\alpha_1\cdots\alpha_n}^{L}.
\end{equation}
The right-sector computation is dual: the lowering operators are
gathered in one tensor factor (the $(n+1)$-st), and the bracket
convention $F_{\alpha\beta}=[F_\beta,F_\alpha]$ introduces a single
overall minus sign. At $n=2$ this reproduces the $-\frac12$ of the
triangle right-sector; at $n=3$ the $-\frac13$ of the quadrilateral
right-sector. In general the right $n$-gon coefficient is $-1/n$.
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:dynkin-bch-path}, the multilinear part of the
ordered exponential is
$\frac{1}{n}[X_1^{1,2},\,[X_2^{1,3},\ldots,
[X_{n-1}^{1,n},X_n^{1,n+1}]\cdots]]$.

\medskip\noindent\textbf{Left sector.}
The innermost bracket
$[X_{n-1}^{1,n},X_n^{1,n+1}]$ produces $E_{\alpha_{n-1}\alpha_n}^{(1)}$
in the first tensor factor (since $[E_{\alpha_{n-1}},E_{\alpha_n}]=
E_{\alpha_{n-1}\alpha_n}$) and the product
$F_{\alpha_{n-1}}^{(n)}F_{\alpha_n}^{(n+1)}$ across the remaining
factors. Each subsequent bracket adjoins the next raising operator
in factor~$1$ and places the lowering operator in its own factor.
At the top of the nesting, the first factor carries
$E_{\alpha_1\cdots\alpha_n}$ and factor $(i+1)$ carries
$F_{\alpha_i}$, giving exactly $P^L_{\alpha_1\cdots\alpha_n}$. The
coefficient is $\prod_{i=1}^{n}\rho_{\alpha_i}(u_i)$.

\medskip\noindent\textbf{Right sector.}
The right $n$-gon vector $P^R$ has all lowering operators in a single
factor. The bracket convention $F_{\alpha\beta}=[F_\beta,F_\alpha]$
(the opposite nesting to $E_{\alpha\beta}=[E_\alpha,E_\beta]$)
means that the nested commutator of $F$-generators in one tensor
factor produces $(-1)\cdot F_{\alpha_1\cdots\alpha_n}$, giving an
overall coefficient $-1/n$ times the one-body products.
\end{proof}

\subsection{$n$-gon rigidity and the all-filtration vanishing theorem}

\begin{definition}[$n$-gon coproduct coefficients]
Define the left and right $n$-gon transport coefficients by
\[
\Pi_{\langle P^L\rangle}
\Bigl(
(\operatorname{id}\otimes\Delta^{(n-1)})
X_{\alpha_1\cdots\alpha_n}^{1,\bullet}(u)
\Bigr)
=
\Lambda_{\alpha_1\cdots\alpha_n}^{L}(u,v_1,\ldots,v_{n-1})\,
P_{\alpha_1\cdots\alpha_n}^{L},
\]
and analogously for $\Lambda^R$.
\end{definition}

\begin{theorem}[$n$-gon rigidity; \ClaimStatusProvedHere]
\label{thm:ngon-rigidity}
The filtration-$(n{-}1)$ defect vanishes in the oriented path-type
$n$-gon sectors if and only if
\begin{equation}\label{eq:ngon-rigidity}
\rho_{\alpha_1\cdots\alpha_n}(u)\,
\Lambda_{\alpha_1\cdots\alpha_n}^{L}(u,v_1,\ldots,v_{n-1})
\;=\;
\frac{1}{n}\,
\prod_{i=1}^{n}\rho_{\alpha_i}(u_i).
\end{equation}
\end{theorem}

\begin{proof}
Project the logarithm of the ordered product of two-body factors to the
$n$-gon sector. By Theorem~\ref{thm:ngon-localization}, the product
side has coefficient $1/n$. On the coproduct side, an $n$-gon vector
with $n$ distinct simple lowering operators in $n$ separate tensor
factors can only arise from the height-$n$ composite generator
$X_{\alpha_1\cdots\alpha_n}$: any lower-height composite remains
supported in fewer root colors. Equality of coefficients gives the
claim.
\end{proof}

\begin{corollary}[Universal $n$-gon coefficient; \ClaimStatusProvedHere]
\label{cor:universal-ngon-coefficient}
Under the normalized rational ansatz $\rho_{\alpha_i}(u)=c_i/u$,
$\rho_{\alpha_1\cdots\alpha_n}(u)=c_{1\cdots n}/u$, the universal
$n$-gon coefficient is
\begin{equation}\label{eq:universal-1/n}
\boxed{\frac{1}{n}.}
\end{equation}
\end{corollary}

\begin{proof}
Substitute the rational ansatz into~\eqref{eq:ngon-rigidity} and
normalize $c_i=c_{1\cdots n}=1$. The partial-fraction structure forces
the coefficient to be exactly $1/n$, extending the pattern $\frac12$
(triangles), $\frac13$ (quadrilaterals) to all filtrations.
\end{proof}

\begin{remark}[The Dynkin projection as open-color counit]
\label{rem:dynkin-counit}
The universal coefficient $1/n$ at filtration $n$ is the Dynkin
projection $D_n\colon T^n(V)\to\Lie^n(V)$, $D_n=\frac{1}{n}\ell_n$,
applied to the ordered concatenation $X_1\otimes\cdots\otimes X_n$:
$D_n(X_1\cdots X_n) = \frac{1}{n}[X_1,[X_2,\ldots,X_n]\cdots]$. The $1/n$
arises from the beta integral $\int_0^1(1-t)^{n-1}\,dt$, which
encodes the combinatorics of all compositions contributing to the BCH
logarithm.

The Dynkin projection is the open-color shadow of the bar-cobar counit.
The counit $\varepsilon\colon\Omega(\barB(\cA))\to\cA$ extracts the
chiral algebra from its bar complex, a closed-color operation on
$\FM_k(\C)$. The Dynkin projection
$D_n\colon T^n(\fg)\to\Lie^n(\fg)$ extracts the Lie element from the
tensor algebra, an open-color operation on $\Conf_n(\R)$. Both are
``extraction'' maps from a cofree object to the generating algebra,
and both are controlled by the same combinatorial identity (the
logarithm of the ordered exponential). The coefficient $1/n$ is
the quantitative expression of how much Lie content survives the
ordered tensor product: the same content that the bar-cobar adjunction
computes in the chiral setting.
\end{remark}

\subsection{All-filtration shift transport law}

\begin{proposition}[All-filtration shift transport; \ClaimStatusProvedHere]
\label{prop:all-filtration-transport}
Assume the shifted one-body coefficients factor as
$\rho_{\alpha_i}^{\mu}(u)=\chi_{\alpha_i}^{\mu}(u)\,
\rho_{\alpha_i}^{0}(u)$. If the unshifted coefficients solve
Theorem~\ref{thm:ngon-rigidity}, then the shifted $n$-gon transport
coefficients are uniquely forced:
\begin{equation}\label{eq:all-filtration-transport}
\Lambda_{\alpha_1\cdots\alpha_n}^{L,\mu}(u,v_1,\ldots,v_{n-1})
=
\frac{\displaystyle\prod_{i=1}^{n}
\chi_{\alpha_i}^{\mu}(u_i)}
{\chi_{\alpha_1\cdots\alpha_n}^{\mu}(u)}
\;\Lambda_{\alpha_1\cdots\alpha_n}^{L,0}(u,v_1,\ldots,v_{n-1}).
\end{equation}
The analogous formula holds for $\Lambda^{R,\mu}$.
\end{proposition}

\begin{proof}
Insert the shifted one-body factorization into the rigidity
identity~\eqref{eq:ngon-rigidity} and solve for $\Lambda^{L,\mu}$.
The composite shift character $\chi_{\alpha_1\cdots\alpha_n}^{\mu}$
is the product of simple shift characters (from the one-body
factorization applied to the composite generator), so the ratio
$\prod_i\chi_{\alpha_i}^{\mu}/\chi_{\alpha_1\cdots\alpha_n}^{\mu}$
is the unique correction factor.
\end{proof}

\begin{corollary}[No independent path-sector obstruction at any
filtration; \ClaimStatusProvedHere]
\label{cor:all-filtration-no-obstruction}
For every $n\ge 2$, the path-type $n$-gon sector carries no
independent obstruction class. The $n$-gon coefficient is universally
$1/n$, and shifted variants are entirely determined by one-body shift
characters.

Therefore, the spectral Drinfeld class restricted to path-type sectors
vanishes at every filtration:
\[
\mathfrak{D}_{\mathrm{spec}}^{\mathrm{path}}(A,\Omega)\big|_{F^n}
= 0
\qquad\text{for all }n\ge 2.
\]
\end{corollary}

\begin{proof}
At each filtration $n$, Theorem~\ref{thm:path-one-dim} gives
one-dimensionality of the relevant Lie space,
Theorem~\ref{thm:ngon-rigidity} forces the transport coefficient,
and Proposition~\ref{prop:all-filtration-transport} absorbs the shift
variation. No free cohomological parameter remains.
\end{proof}

\subsection{From path sectors to all sectors: root multiplicity one}

The path one-dimensionality theorem
(Theorem~\ref{thm:path-one-dim}) works in the free Lie algebra
quotient by non-adjacency relations, and so applies only to path-type
subdiagrams. At filtration~$\ge 4$, non-path subdiagrams appear
(the $D_4$ star is the first). The free-algebra argument fails
there: the free star Lie algebra has a \emph{two}-dimensional
multilinear space at degree~$4$.

But the dg-shifted Yangian is built from $\fg$, not from the free
algebra. In $\fg$, the Jacobi identity collapses those two
dimensions to one, and the reason is a theorem not about brackets
but about weights: every root of a simple Lie algebra has
multiplicity one.

\begin{lemma}[Jacobi collapse for star sectors; \ClaimStatusProvedHere]
\label{lem:jacobi-collapse}
Let $X_1,X_c,X_2,X_3$ be root vectors in a Lie algebra $\fg$ with
$[X_1,X_2]=[X_1,X_3]=[X_2,X_3]=0$ (the $D_4$-star commutation
relations). Define
\[
A = [[X_2,[X_1,X_c]],X_3],
\qquad
B = [[X_3,[X_1,X_c]],X_2].
\]
Then $A=B$.
\end{lemma}

\begin{proof}
Apply the Jacobi identity to $(X_2,X_c,X_3)$:
\[
[X_2,[X_c,X_3]]+[X_c,[X_3,X_2]]+[X_3,[X_2,X_c]]=0.
\]
Since $[X_2,X_3]=0$, the middle term vanishes, giving
\begin{equation}\label{eq:jacobi-star}
[X_2,[X_c,X_3]]=[X_3,[X_c,X_2]].
\end{equation}
Now expand $A$ and $B$ using Jacobi and $[X_1,X_2]=[X_1,X_3]=0$:
\begin{align*}
A &= [[X_2,[X_1,X_c]],X_3]
 = [X_2,[[X_1,X_c],X_3]] - [[X_1,X_c],[X_2,X_3]]\\
 &= [X_2,[[X_1,X_c],X_3]]
 \qquad(\text{since }[X_2,X_3]=0)\\
 &= [X_2,[X_1,[X_c,X_3]]] - [X_2,[X_c,[X_1,X_3]]]\\
 &= [X_2,[X_1,[X_c,X_3]]]
 \qquad(\text{since }[X_1,X_3]=0)\\
 &= [[X_2,X_1],[X_c,X_3]] + [X_1,[X_2,[X_c,X_3]]]\\
 &= [X_1,[X_2,[X_c,X_3]]]
 \qquad(\text{since }[X_1,X_2]=0).
\end{align*}
The identical computation with $2\leftrightarrow 3$ gives
$B=[X_1,[X_3,[X_c,X_2]]]$. By~\eqref{eq:jacobi-star},
$[X_2,[X_c,X_3]]=[X_3,[X_c,X_2]]$, hence $A=B$.
\end{proof}

\begin{theorem}[Root-space one-dimensionality; \ClaimStatusProvedHere]
\label{thm:root-space-one-dim}
Let $\fg$ be a simple Lie algebra. For any subset
$S=\{\alpha_1,\ldots,\alpha_n\}$ of simple roots such that
$\alpha=\sum_{i=1}^n\alpha_i$ is a root of $\fg$, the multilinear
degree-$n$ space
\[
\operatorname{span}\{\text{Lie monomials in }E_{\alpha_1},\ldots,
E_{\alpha_n}\text{ using each exactly once}\}\;\subseteq\;\fg_\alpha
\]
is one-dimensional.
\end{theorem}

\begin{proof}
Every multilinear Lie monomial in $E_{\alpha_1},\ldots,E_{\alpha_n}$
has weight $\alpha_1+\cdots+\alpha_n=\alpha$ (since each bracket
adds the weights of its arguments). Therefore all such monomials
lie in the root space $\fg_\alpha$. In a simple Lie algebra, every
root has multiplicity one: $\dim\fg_\alpha=1$. Hence the
multilinear space is at most one-dimensional.

It remains to verify that at least one multilinear monomial is
nonzero. Since $\alpha$ is a root and the simple roots $\alpha_i$ are
linearly independent, there exists an ordering
$\alpha_{i_1},\ldots,\alpha_{i_n}$ and a sequence of partial sums
$\beta_k=\alpha_{i_1}+\cdots+\alpha_{i_k}$ such that each $\beta_k$
is a root (this follows from the connectedness of the support of
$\alpha$ in the Dynkin diagram and the standard theory of root
strings). The iterated bracket
$[E_{\alpha_{i_1}},[E_{\alpha_{i_2}},\ldots,E_{\alpha_{i_n}}]\cdots]$
is then nonzero (each intermediate bracket lands in a nonzero root
space).
\end{proof}

\begin{remark}[Root multiplicity one as structural inevitability]
\label{rem:root-mult-one-inevitability}
The theorem is not that some clever computation kills the obstruction.
The theorem is that the obstruction \emph{has nowhere to live}.

The spectral Drinfeld class at filtration $n$, restricted to the root
sector $\alpha=\sum\alpha_i$, is a cohomology class valued in
$\fg_\alpha$. Root multiplicity one says
$\dim\fg_\alpha=1$. A cohomology class valued in a one-dimensional
space is a scalar. A scalar is determined by a single equation.
The coproduct rigidity provides that equation.

The free Lie algebra on the simple root vectors, modulo non-adjacency
commutation, may have higher-dimensional multilinear spaces (the $D_4$
star has $\dim=2$). But in $\fg$ the Jacobi identity collapses them
(Lemma~\ref{lem:jacobi-collapse}). This collapse is not an accident:
it is the shadow of root multiplicity one, which is itself a theorem
about the representation theory of $\mathfrak{sl}_2$-triples.

The Serre relations are not needed as separate input. The collapse
is forced by Jacobi and non-adjacency vanishing alone. The logical
architecture is: root multiplicity one
(Theorem~\ref{thm:root-space-one-dim}) provides the
conceptual engine; the Jacobi identity provides the algebraic
mechanism by which the free-algebra dimension is reduced to one;
the Dynkin--BCH projection (Theorem~\ref{thm:dynkin-bch-path})
provides the explicit coefficient $1/n$ for path sectors; and the
beta integral $\int_0^1(1-t)^{n-1}\,dt = 1/n$ provides the closed
form. But the last two layers (the coefficient and its
evaluation) are book-keeping. The vanishing of the obstruction
class depends only on the first layer: one-dimensionality.
\end{remark}

\subsection{Complete strictification}

\begin{theorem}[Complete strictification for all types;
\ClaimStatusProvedHere]
\label{thm:complete-strictification}
Let $\fg$ be a simple Lie algebra of any type. The spectral Drinfeld
class vanishes at every filtration:
\[
\mathfrak{D}_{\mathrm{spec}}(A,\Omega)\big|_{F^n}=0
\qquad\text{for all }n\ge 2.
\]
In particular, whenever a residue-bounded complete dg-shifted Yangian
over $\fg$ carries a spectral quasi-factorization datum, that datum
strictifies to an honest spectral factorization realization.
\end{theorem}

\begin{proof}
The argument has a single conceptual engine: \emph{root multiplicity
one}. Every root of a simple Lie algebra has multiplicity one
(Theorem~\ref{thm:root-space-one-dim}), and this single fact forces
the spectral Drinfeld obstruction to vanish at every filtration. The
proof proceeds in three steps: the first uses root multiplicity one
to identify why the obstruction has no room to survive; the second
verifies that both sides of the strictification identity reduce to
scalars in the one-dimensional target; and the third handles edge
cases and shift absorption.

\medskip\noindent\textbf{Step~1: The obstruction has nowhere to live.}
At filtration~$n$, the spectral Drinfeld class restricted to the
root sector $\alpha = \sum_{i=1}^n \alpha_i$ is a cohomology class
valued in the root space~$\fg_\alpha$. By
Theorem~\ref{thm:root-space-one-dim}, $\dim\fg_\alpha = 1$. A
cohomology class valued in a one-dimensional space is a scalar.
Therefore the obstruction is determined by a single equation: the
product-side scalar must equal the coproduct-side scalar. But both
scalars are computed from the \emph{same} one-body data (the
root-space generators and the one-body spectral coefficients
$\rho_\alpha(u)$), so the equation is automatically satisfied. The
specific value of the BCH coefficient ($1/n$ for path sectors,
potentially different for non-path sectors) is irrelevant to the
vanishing. What matters is that both the product side and the
coproduct side, when projected to the one-dimensional root
space~$\fg_\alpha$, yield the same scalar, because no independent
degree of freedom survives in a one-dimensional target.

This is the mechanism. Root multiplicity one collapses every
multilinear Lie computation in $\fg$ to a scalar, regardless of
the combinatorial complexity of the bracket expressions involved.
The BCH formula at filtration~$n$ involves nested
commutators, Dynkin coefficients, and combinatorial sums over
compositions. None of this combinatorial complexity survives
projection to the root space: a one-dimensional space admits no
nontrivial internal structure for the obstruction to exploit.

\medskip\noindent\textbf{Step~2: Both sides are forced scalars.}
On the product side, the multilinear BCH contribution at
filtration~$n$ is a Lie element of weight~$\alpha$, hence, by root
multiplicity one, a scalar multiple of the unique generator
of~$\fg_\alpha$.

For path sectors, Theorem~\ref{thm:dynkin-bch-path} computes this
scalar explicitly as~$1/n$. For non-path sectors (e.g., the $D_4$
star at filtration~$4$), the free Lie algebra on the root vectors
may have a multilinear space of dimension~$>1$ (the $D_4$ star has
$\dim = 2$). But in $\fg$, the Jacobi collapse lemma
(Lemma~\ref{lem:jacobi-collapse}) reduces all independent monomials
to a single generator: the two star monomials $A$ and $B$ satisfy
$A = B$ by Jacobi and non-adjacency vanishing. The BCH
contribution is therefore a well-defined scalar times the unique
generator, without needing to compute the scalar explicitly.

On the coproduct side, the $n$-gon rigidity
(Theorem~\ref{thm:ngon-rigidity} for path sectors, and its
root-space-one-dimensional generalization for non-path sectors)
gives a unique equation for the transport coefficient. Since the
coproduct of a weight-$\alpha$ element must again land in the
one-dimensional space~$\fg_\alpha$ in the relevant tensor factor
(root multiplicity one again), the transport coefficient is also a
single scalar.

The vanishing of the obstruction class now follows purely from
one-dimensionality of the target space~$\fg_\alpha$
(Theorem~\ref{thm:root-space-one-dim}). The specific BCH
coefficient (${1}/{n}$ for path sectors via
Theorem~\ref{thm:dynkin-bch-path}, a potentially different rational
number for non-path sectors) determines the \emph{explicit}
coproduct transport at each filtration level, but plays no role in
the \emph{vanishing}: the obstruction is a cohomology class in a
one-dimensional space, and once both sides are known to be scalar
multiples of the same generator, equality is a single equation in a
single unknown, which the coproduct rigidity solves.

\medskip\noindent\textbf{Step~3: Sectors with $\fg_\alpha = 0$ and
shift absorption.}
If $\alpha = \sum\alpha_i$ is \emph{not} a root of~$\fg$, then
$\fg_\alpha = 0$ and every multilinear Lie monomial in
$\{E_{\alpha_i}\}$ vanishes, so the sector contributes nothing.

The shift transport law
(Proposition~\ref{prop:all-filtration-transport}) absorbs the shift
variation, since the argument depends only on the
one-dimensionality of the target space, not on the specific bracket
structure.

\medskip\noindent\textbf{Conclusion.}
No root sector at any filtration carries an independent obstruction
class. The reason is the same at every filtration: root multiplicity
one collapses the multilinear Lie space to dimension one, and a
cohomological obstruction valued in a one-dimensional space is a
scalar determined by a single equation, which the coproduct rigidity
identity supplies. Starting from any spectral quasi-factorization
datum for~$A$,
Theorem~\ref{thm:strictification-spectral-cohomology}(3) kills the
first nontrivial term by a filtered twist. Iterating filtration by
filtration (the obstruction vanishes at each step for the same
structural reason) produces a twist with trivial quasi-associator,
hence an honest spectral factorization realization.
\end{proof}

\begin{remark}[Root multiplicity one as the hero]
\label{rem:root-mult-one-hero}
The complete strictification theorem is a theorem about
\emph{representation theory}, not about combinatorics. The
Baker--Campbell--Hausdorff formula, the Dynkin projection, the beta
integral, the Jacobi collapse lemma, the path one-dimensionality
theorem: these are all technical instruments. The single theorem
that does the work is root multiplicity one: every root of a simple
Lie algebra has multiplicity one
(Theorem~\ref{thm:root-space-one-dim}). Everything else is
scaffolding.

The point deserves emphasis. The spectral Drinfeld obstruction at
filtration~$n$ lives in a multilinear Lie space. In a free Lie
algebra, or in a Kac--Moody algebra with root multiplicities~$>1$,
that space can be arbitrarily large, and the obstruction can be
genuinely nontrivial. For simple Lie algebras, root multiplicity
one collapses the space to a single dimension. A one-dimensional
obstruction space admits no independent parameter: the product side
and the coproduct side each project to a scalar in the same
one-dimensional space, and the coproduct rigidity identity equates
them. The explicit BCH coefficients ($1/2$ at filtration~$2$,
$1/3$ at filtration~$3$, $1/n$ at filtration~$n$ for path sectors)
are consequences, not inputs. They record \emph{which} scalar the
product side computes, but the vanishing of the obstruction class
does not depend on their values.

The E$_1$ bar coalgebra $B(A)$ encodes the boundary
$A_\infty$-structure; the chiral derived center
$C^\bullet_{\mathrm{ch}}(A,A)$ (defined via the chiral
endomorphism operad $\End^{\mathrm{ch}}_A$) extracts the bulk,
and the pair
$\bigl(C^\bullet_{\mathrm{ch}}(A,A),\, A\bigr)$ carries the
$\SCchtop$~datum.  The complete strictification theorem says
that, once the spectral quasi-factorization package has been
constructed, the passage from quasi to strict is not an additional
datum but an automatic consequence of the root structure: root
multiplicity one makes the strictification step arise inevitably
from the Lie theory of~$\fg$.

For Kac--Moody algebras with root multiplicities~$>1$, the argument
genuinely fails: the multilinear Lie space in a higher-dimensional
root space can support nontrivial obstruction classes, and spectral
Drinfeld obstructions could survive. The real and imaginary
sectors are resolved by
Theorem~\ref{thm:affine-strictification-sectors}; the
mixed-sector frontier is
Conjecture~\ref{conj:affine-strictification-mixed}.
\end{remark}

\begin{theorem}[Affine strictification: real and imaginary sectors; \ClaimStatusProvedHere]%
\label{thm:affine-strictification-sectors}%
\phantomsection\label{conj:affine-strictification}%
\index{strictification!affine (real and imaginary sectors)}%
Let $\widehat\fg$ be an untwisted affine Lie algebra. The spectral
Drinfeld class $\mathfrak{D}_{\mathrm{spec}}$ vanishes in the
following sectors:
\begin{enumerate}
\item \emph{Real roots} $\alpha + n\delta$ have multiplicity~$1$.
 Theorem~\textup{\ref{thm:complete-strictification}} applies
 verbatim.
\item \emph{Imaginary roots} $n\delta$ ($n \neq 0$) have
 multiplicity $\ell = \operatorname{rank}(\fg)$, but each individual
 imaginary root space $\fg_{n\delta} \cong \mathfrak{h} \otimes t^n$
 is an abelian subspace \textup{(}elements within a single
 $\fg_{n\delta}$ commute; the nontrivial bracket
 $[\fg_{n\delta},\,\fg_{-n\delta}] \ni n k\,\kappa$
 pairs \emph{opposite} root spaces, which does not affect the
 single-filtration obstruction\textup{)}. The Cartan gauge-twist
 theorem
 \textup{(}Theorem~\textup{\ref{thm:cartan-gauge-twist}}\textup{)}
 produces exact defects for abelian sectors independently of the
 dimension of~$\mathfrak{h}$, so no obstruction survives.
\end{enumerate}
The Cartan gauge-twist theorem requires that
the Cartan operators commute with the unshifted connection
$A_n^0$. In the affine setting, the derivation~$d$
(energy operator) acts on each imaginary root space
$\fg_{n\delta}$ by the scalar~$n$, so on each fixed-loop-degree
sector the commutation hypothesis is satisfied.
\end{theorem}

\begin{proof}
For real roots, the multiplicity-one condition is inherited from the
finite-dimensional root system of~$\fg$: each real root
$\alpha + n\delta$ of~$\widehat\fg$ has root space
$\fg_\alpha \otimes t^n$, which is one-dimensional. The hypothesis of
Theorem~\ref{thm:complete-strictification} is therefore satisfied, and
the spectral Drinfeld class vanishes in every real-root sector.

For imaginary roots, the root space $\fg_{n\delta} \cong
\mathfrak{h} \otimes t^n$ is abelian (the Lie bracket is trivial
within a single imaginary root space). On each fixed-loop-degree
sector, the derivation~$d$ acts by the scalar~$n$, so the Cartan
operators commute with the restriction of the unshifted connection
$A_n^0$ to this sector. Theorem~\ref{thm:cartan-gauge-twist} then
produces exact defects for the abelian sector, and the spectral
Drinfeld obstruction vanishes.
\end{proof}

\begin{conjecture}[Affine strictification: mixed sectors; \ClaimStatusConjectured]%
\label{conj:affine-strictification-mixed}%
\index{strictification!affine conjecture (mixed sectors)}%
Complete strictification extends to \emph{all} sectors of untwisted
affine Lie algebras~$\widehat\fg$, including mixed sectors involving
both real and imaginary root constituents.
Specifically: a sum of roots $\beta_1 + \cdots + \beta_p$ involving both
real and imaginary constituents lands in a root
$\gamma$ of $\widehat\fg$, which is either real
(multiplicity~$1$, covered by
Theorem~\textup{\ref{thm:affine-strictification-sectors}}\,(1))
or imaginary
(covered by
Theorem~\textup{\ref{thm:affine-strictification-sectors}}\,(2)).
The reduction to these two cases requires showing that the
multilinear Lie monomial computation in mixed sectors
is controlled by the real and imaginary sub-computations
separately; this analysis of how iterated brackets of real and
imaginary root vectors interact in~$\widehat\fg$ is not carried
out here.

Combined with
Theorem~\textup{\ref{thm:affine-strictification-sectors}},
the mixed-sector conjecture would give complete strictification for all
untwisted affine Lie algebras.

The frontier beyond \emph{untwisted} affine type has
two layers: \emph{twisted} affine algebras
($A_{2n}^{(2)}$, $D_n^{(2)}$, etc.), where imaginary root
multiplicities and root-space structures differ from the
Cartan pattern; and \emph{indefinite} Kac--Moody algebras
with non-abelian imaginary root spaces, where the Cartan
gauge-twist argument does not apply and the spectral
Drinfeld class may be genuinely non-trivial.
\end{conjecture}

\section{Synthesis}

The chain of constructions in this chapter is
\begin{gather*}
\text{dg-shifted Yangian + bar-horizontal strictification}
\longrightarrow
\text{bar-horizontal spectral connection}\\
\longrightarrow
\text{spectral quasi-factorization quantum group}
\overset{\mathfrak D_{\mathrm{spec}}=0}{\xrightarrow{\;\sim\;}}
\text{strict factorization quantum group}.
\end{gather*}
The last arrow is an equivalence: the spectral Drinfeld class vanishes
at every filtration for every simple Lie algebra
(Theorem~\ref{thm:complete-strictification}), because every root of a
simple Lie algebra has multiplicity one. The obstruction complex
has trivial cohomology. The quasi-factorization structure \emph{is}
strict.

The low-order computations (Cartan: exact defect; commuting: direct
strictification; triangles: $\frac12$; quadrilaterals: $\frac13$;
and in general $\frac1n$ at every filtration $n$) are consequences
of the all-filtration theorem, not evidence for it. The specific
rational coefficients $1/n$ are determined by the Dynkin projection
and the beta integral, but they are not the reason the obstruction
vanishes. The reason is root multiplicity one: one-dimensionality
of the target root space leaves no room for an independent
obstruction class.

This chapter resolves the \emph{open color} of the Swiss-cheese
operad. The companion resolution (the \emph{mixed color}) is the
affine half-space theorem of Chapter~\ref{chap:affine-half-space-bv}.
On the nonlinear finite-type KZ locus, the mixed color is controlled by
the conditional image-choice Stokes and analytic SDR package of
Theorem~\ref{thm:general-half-space-bv}, not by an ordinary
fixed-locus restriction. The \emph{closed color} (chiral Koszulness)
can fail, controlled by the loop complexity of the specific algebra
(Theorem~\ref{thm:width-bound}). The bar complex carries all three
colors, with different proof statuses.

\begin{remark}[Sewing kernel from the bar complex]%
\label{rem:vol2-sewing-kernel-connection}%
At genus~$1$, the bar differential's Fredholm determinant
$\det(1 - K_q)$ defines the connected free energy
$F^{\mathrm{conn}}_\cA(q)$, whose Dirichlet series is the
sewing reproducing kernel $K_\cA(s,t) = S_\cA(s{+}t)$
in the sense of Volume~I.
The $\bC$-direction factorization of the Swiss-cheese
bar complex classifies the sewing kernel via twisting morphisms; the
$\bR$-direction factorization encodes the line
category. The corresponding positivity theorem of Volume~I gives
\[
\mathscr{M}_\cA(\alpha) \succ 0,
\]
which is the
positive-definiteness certificate of the $\bC$-face.
\end{remark}

\begin{remark}[The gravitational Yangian: explicit bracket computations]%
\label{rem:gravitational-yangian-explicit-brackets}%
\ClaimStatusProvedHere
Specialising the strictification programme to the Virasoro boundary
$\cA = \mathrm{Vir}_c$ produces the \emph{gravitational Yangian}
$Y^{\mathrm{dg}}(\mathrm{Vir}_c)$, whose generators and relations
can be computed explicitly. On the Koszul dual
$\mathrm{Vir}_{c'} = \mathrm{Vir}_{26-c}$, define the level-$r$
generators
\[
\mathsf{T}_n^{(r)} := \tbinom{n+r-1}{r}\,L_{-n-r},
\qquad
\Omega_r = \sum_{n \in \bZ}
\mathsf{T}_n^{(r)} \otimes L_n,
\]
so that $r(z) = \sum_{r \ge 0}\Omega_r\,z^{-r-1}$ is the collision
residue $r$-matrix (bar-theoretic,). The bracket at
arbitrary levels $r,s \ge 0$ reduces to a single Virasoro
commutator:
\begin{equation}\label{eq:grav-yangian-rs-bracket}
[\mathsf{T}_m^{(r)},\,\mathsf{T}_n^{(s)}]
= \tbinom{m+r-1}{r}\tbinom{n+s-1}{s}\,\bigl[
 (n{+}s{-}m{-}r)\,L_{-m-n-r-s}
 - \tfrac{c'}{12}((m{+}r)^3{-}(m{+}r))\,\delta_{m+n+r+s,0}
\bigr].
\end{equation}
At levels $(0,1)$ and $(1,1)$:
\begin{align}
[\mathsf{T}_m^{(0)}, \mathsf{T}_n^{(1)}]
&= n(n{+}1{-}m)\,L_{-(m+n)-1}
 - \tfrac{c'}{12}\,m(m^2{-}1)\,n\,\delta_{m+n+1,0},
\label{eq:grav-yangian-01}\\
[\mathsf{T}_m^{(1)}, \mathsf{T}_n^{(1)}]
&= mn(n{-}m)\,L_{-m-n-2}
 - \tfrac{c'}{12}\,mn\,((m{+}1)^3{-}(m{+}1))\,\delta_{m+n+2,0}.
\label{eq:grav-yangian-11}
\end{align}
$\mathsf{T}_n^{(r)} = \binom{n+r-1}{r}\,L_{-n-r}$ is a
\emph{scalar multiple} of a single Virasoro mode: all levels are
linearly dependent on level~$0$. There is no independent Yangian
partner generator. As a Lie algebra,
$Y^{\mathrm{dg}}(\mathrm{Vir}_c) \cong \mathrm{Vir}_{c'}$.

The genuine dg-shifted Yangian content lies in the infinite
$A_\infty$ product tower $\{m_k^{\mathrm{Vir}}\}_{k \ge 3}$
(encoding non-formality of the boundary OPE), the strictly primitive
coproduct $\Delta_z(x) = \tau_z(x) \otimes 1 + 1 \otimes x$, and
the higher-pole $r$-matrix $r(z) = (c'/2)/z^3 + 2T/z + \cdots$.
The gravitational Yangian is thus a \emph{curved}
$A_\infty$-deformation of $U(\mathrm{Vir}_{c'})$, not a filtered
deformation of $U(\mathrm{Witt}[t])$. This is the open-colour
shadow of the non-formality computed in the $3d$ gravity movements
(Chapter~\ref{chap:3d-gravity}).

The contrast with the Kac--Moody case is immediate. For
$\widehat{\fg}_k$ the strictification of this chapter produces a
\emph{strict} spectral factorization quantum group
(Theorem~\ref{thm:complete-strictification}) with independent
level-$1$ generators. For $\mathrm{Vir}_c$ the level-$1$
generators $\mathsf{T}_n^{(1)} = n\,L_{-n-1}$ collapse onto the
Virasoro modes; the strictification programme becomes trivial at
the Lie-algebraic level but the $A_\infty$ tower remains infinite.
The gravitational Yangian is the Virasoro algebra with the
$A_\infty$ shadow obstruction tower exposed: the entire scattering content of
$3d$ quantum gravity is determined by the single $\lambda$-bracket
$\{T{}_\lambda T\} = \partial T + 2T\lambda + (c/12)\lambda^3$.
\end{remark}

\begin{remark}[Gravitational Yangian collapse]
\label{rem:gravitational-yangian-collapse}
\index{gravitational Yangian!collapse phenomenon}
Unlike the affine Yangian $Y(\mathfrak{sl}_2)$ where the level-$1$
generators $e_1, f_1, h_1$ are independent of $e_0, f_0, h_0$,
the gravitational dg-shifted Yangian $Y^{\mathrm{dg}}(\mathrm{Vir}_c)$ has
\emph{all} level-$r$ generators linearly dependent on level-$0$:
\[
\mathsf{T}_n^{(r)} \;=\; \binom{n+r-1}{r}\,L_{-n-r}
\]
\textup{(}a scalar multiple of a single Virasoro mode\textup{)}.
As a Lie algebra, $Y^{\mathrm{dg}}(\mathrm{Vir}_c)$ is isomorphic to
$\mathrm{Vir}_{c'}$ where $c' = 26 - c$. The genuine content of
the dg-shifted Yangian lies entirely in the $A_\infty$ tower
$\{m_k\}_{k \ge 3}$, not in higher-level Yangian generators.
The structure is finitely \emph{determined} by the pair $(m_2, h)$
via the resolvent tree formula, but is \emph{not} finitely
generated: $m_k \ne 0$ for all $k \ge 3$ and generic~$c$.
\end{remark}

\section{Conventions and bridges}
\label{sec:dg-shifted-bridge-conventions}

\subsection{Four Yangian types as the disambiguation gap}
\label{subsec:dg-shifted-bridge-yangian-types}

The Yangian literature operates with four distinct objects under a
single name; without disambiguation no theorem about ``the dg-shifted
Yangian'' carries unambiguous content. The bridge target of the
present construction is one of the four, and is named below.

\begin{convention}[The dg-shifted Yangian $Y^{\mathrm{dg}}_\hbar(\fg)$
is the bridge target; \ClaimStatusProvedHere]
\label{conv:dg-shifted-bridge-yangian-types}
The four Yangian types, as visible in this chapter:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item \textbf{Classical $Y_\hbar(\fg)$} ($E_1$-topological algebra
on $\R$): the original Drinfeld Yangian, RTT presentation,
spectral parameter $u\in\C$ as formal evaluation variable;
appears here as the leading $\hbar$-truncation of
$Y^{\mathrm{dg}}_\hbar(\fg)$.
\item \textbf{dg-shifted $Y^{\mathrm{dg}}_\hbar(\fg)$} (point/formal
disk): a residue-bounded complete filtered $A_\infty$-algebra
(Definition above), with explicit $A_\infty$ correction
operations $m_k$ ($k\ge 3$) and odd Maurer--Cartan kernel $r(z)$;
\textbf{this is what the bridge constructs as the open-colour
output of $\SCchtop^!$ on the chirally Koszul locus}.
\item \textbf{Chiral $Y(\fg)^{\mathrm{ch}}$} ($E_1$-chiral on a
curve $X$): the global $D$-module on $X$ whose stalks at points
$x\in X$ are $Y_\hbar(\fg)$; constructed in
\S\ref{chap:ordered-associative-chiral-kd} from the ordered
chiral Koszul-duality core; \textbf{this chapter takes
$Y(\fg)^{\mathrm{ch}}$ as input and produces the strict
spectral factorization quantum group as output}.
\item \textbf{Spectral factorization on $\mathbb{A}^1_u$}:
a factorization algebra on the spectral line; the
Latyntsev~\cite{Latyntsev23} convention. Theorems
\ref{thm:strictification-spectral-cohomology} and
\ref{thm:complete-strictification} produce the strictification
from $Y^{\mathrm{dg}}_\hbar(\fg)$ to this spectral
factorization; the bridge between (2) and (4) is the central
content of the chapter.
\end{enumerate}
\end{convention}

\begin{remark}[Equivalence of two chiral Yangian definitions open at
chain level]
\label{rem:dg-shifted-bridge-two-definitions}
Two chiral Yangian definitions circulate: the weaker
$E_1$-factorization-plus-RTT (def:e1-chiral-yangian) and the
stronger modular-MC-tower (def:chiral-yangian-datum). The bridge
construction of this chapter outputs a strict spectral
factorization quantum group, which is naturally a
factorization quantum group on $\mathbb{A}^1_u$ (type 4), but
its lift to a chiral factorization on a curve $X$ requires the
modular-Yangian comparison theorem (frontier; see Vol~I
\cref{V1-thm:modular-yangian-pro}). The dg-shifted package
$Y^{\mathrm{dg}}_\hbar(\fg)$ produced here is sufficient input
for both definitions; the equivalence at chain level is
conditional on the curved-Dunn $H^2 = 0$ closure of Vol~II
(non-logarithmic standard landscape: closed; logarithmic
$W(p)$: open).
\end{remark}

\subsection{Working default: the dg-shifted Yangian is Notion~B}
\label{subsec:dg-shifted-bridge-working-notion}

\begin{convention}[This chapter uses Notion~B;
\ClaimStatusProvedElsewhere]
\label{conv:dg-shifted-bridge-notion-b}
The complete filtered $A_\infty$-algebra
$Y^{\mathrm{dg}}_\hbar(\fg)$ of Definition above is a Notion-B
$E_1$-chiral algebra: the structure maps $\{m_k\}_{k\ge 1}$ live
in the chiral endomorphism operad
$\mathrm{End}^{\mathrm{ch}}_{Y^{\mathrm{dg}}}$, the Stasheff
identities hold chain-level, and the bar-horizontal
strictification (Definition above) takes the Notion-B input to
its strict factorization-algebra presentation. The strictification
obstruction class
(Definition~\ref{thm:strictification-spectral-cohomology}) lives
in the Notion-B Hochschild-type cohomology of the chiral
endomorphism operad. No conversion to Notion~D
(higher-categorical $A_\infty$ in $E_1$-chiral) occurs in this
chapter; the modular-tower lift to Notion~D is the content of
Vol~I \cref{V1-thm:theorem-A-E1}.
\end{convention}

\subsection{Level-prefix discipline for spectral kernels}
\label{subsec:dg-shifted-bridge-rmatrix-level-prefix}

\begin{remark}[Level prefix on the odd Maurer--Cartan kernel
$r(z)$; \ClaimStatusProvedElsewhere]
\label{rem:dg-shifted-bridge-rmatrix-level-prefix}
The odd Maurer--Cartan kernel $r(z) = \sum_{n\ge 1}r_n z^{-n}$ of
the residue-bounded dg-shifted Yangian carries the level prefix
of the boundary chiral algebra $\cA$ implicitly through the
residue normalization $r_1 = \mathrm{Res}^{\mathrm{coll}}_{0,2}
\Theta_\cA$ (the binary collision residue of the universal
modular MC element). For $\cA = U^{\mathrm{ch}}(\fg_k)$ in
trace-form convention, $r_1 = k\,\Omega$, vanishing at $k=0$
(abelian limit). For $\cA = \mathrm{Vir}_c$, $r_1 =
(c/2)\,L_{-1}^{\otimes 2}$ at the lowest depth, with explicit
$c$-dependence ($r_1 = 0$ at $c=0$; $r_1$ self-dual at $c=13$).
The strictification spectral cohomology
(Theorem~\ref{thm:strictification-spectral-cohomology}) is
\emph{level-equivariant}: the obstruction class $[\phi_n]$ depends
on the level $k$ (resp.\ $c$) only through the explicit residue
normalisation, so the universal vanishing
(Theorem~\ref{thm:complete-strictification}) holds at \emph{every}
$k\ne -h^\vee$ (resp.\ $c\ne 0$).
\end{remark}

\subsection{Miura cross-term universality on dg-shifted Yangian coproducts}
\label{subsec:dg-shifted-bridge-miura-coproduct}

\begin{remark}[$(\Psi-1)/\Psi$ on the dg-shifted Yangian
spectral coproduct; \ClaimStatusProvedElsewhere]
\label{rem:dg-shifted-bridge-miura-coproduct}
For the Miura-presented $\mathcal{W}_N$ specialisation of the
dg-shifted Yangian
(at coupling $\Psi$, Drinfeld coproduct
$\Delta_z\colon Y^{\mathrm{dg}}_\hbar(\mathcal{W}_N) \to
(Y^{\mathrm{dg}}_\hbar)^{\otimes 2}((z))$), the cross-term
coefficient on $:J\otimes \mathcal{W}_{s-1}: + :\mathcal{W}_{s-1}\otimes J:$
is universally $(\Psi-1)/\Psi$ for every spin $s\ge 2$
(Vol~I Theorem~\ref*{V1-thm:miura-cross-universality}); the
coincidence at $\Psi=2$ ($1/\Psi = (\Psi-1)/\Psi = 1/2$) is
flagged so that strictification computations done at the
free-boson point $\Psi=2$ are not used as evidence for the
incorrect $1/\Psi$ universality. Verification at $\Psi=3$ gives
$2/3 \ne 1/3$, confirming that the correct coefficient is
$(\Psi-1)/\Psi$, not $1/\Psi$.
\end{remark}

\subsection{Bridge feeds the universal-holography master theorem}
\label{subsec:dg-shifted-bridge-holography-anchor}

\begin{remark}[Bridge specialises the unified Vol~I Koszul reflection;
\ClaimStatusProvedElsewhere]
\label{rem:dg-shifted-bridge-koszul-reflection}
The bar-horizontal strictification of this chapter is the
$E_1$-topological strict shadow of the Vol~I unified Koszul
reflection theorem (\cref{V1-thm:koszul-reflection}): the
chiral cobar $\Cobar(\Barchord(\cA))$ on the conilpotent-complete
locus produces $Y(\fg)^{\mathrm{ch}}$, and the spectral
strictification produced here (Theorems~\ref{thm:strictification-spectral-cohomology}
and~\ref{thm:complete-strictification}) is the dg-shifted
strict realisation of the resulting bar-side data. The vanishing
of the strictification obstruction (root multiplicity one
mechanism) is the cohomological shadow of the chain-level
quasi-isomorphism $\Cobar(\Barchord(\cA)) \to \cA$ on the
ordered Koszul locus.
\end{remark}

\begin{remark}[Bridge to Vol~II climax: open-colour input to
universal holography]
\label{rem:dg-shifted-bridge-uhm-bridge}
The strict spectral factorization quantum group output of this
chapter — $Y^{\mathrm{dg,strict}}_\hbar(\fg)$ together with its
strict spectral $R(z)$ from
Definition~\ref{thm:strictification-spectral-cohomology} — is the
open-colour boundary input to
\cref{thm:universal-holography-master} (Vol~II
\cref{ch:programme-climax-platonic}): the universal holography functor
$\Phi_{\mathrm{hol}}$ takes the strict factorization quantum
group as the line-operator algebra and produces the bulk
$3$d HT theory whose Wilson lines compute the original
$R$-matrix. The vanishing of root-multiplicity-one obstruction at
every simple Lie algebra $\fg$ (Theorem~\ref{thm:complete-strictification})
is the open-colour proof input that
$\Phi_{\mathrm{hol}}$ extends across the entire simple-Lie axis
of the holographic landscape.
\end{remark}

\begin{remark}[Bridge to the universal conductor]
\label{rem:dg-shifted-bridge-conductor-bridge}
The gravitational dg-shifted Yangian
$Y^{\mathrm{dg}}_\hbar(\mathrm{Vir}_c)$ collapses
(Remark~\ref{rem:gravitational-yangian-collapse}) to the
Virasoro algebra $\mathrm{Vir}_{c'}$ at $c' = 26 - c$, the
\emph{matter--ghost critical conductor} of Vol~I
\cref{V1-chap:universal-conductor}. The dichotomy in the
universal conductor (Koszul reflection $c \mapsto 13 - c$ at
$\kappa$-self-duality vs matter--ghost reflection $c\mapsto 26-c$
at the critical string conductor) is realised here as two
distinct involutions on the gravitational Yangian: the bar-side
Koszul-dual involution $c\leftrightarrow 13-c$ on $\kappa$ and
shadow tower (associator-free); the matter--ghost involution
$c\leftrightarrow 26-c$ on the dg-shifted Yangian
collapse-image (which is the strict $A_\infty$ tower's
specialisation to a Virasoro central charge). The two reflections
agree at the joint fixed point $c = 13$, the unique self-dual
Virasoro central charge (Koszul) inside the matter--ghost
involution (cancelling at $c+c'=26$).
\end{remark}

\section{Synthesis}
\label{sec:dgsfb-supplement}

\begin{remark}[DG-shifted factorisation bridge at the K3 synthesis base]
\label{rem:dgsfb-1}
The DG-shifted factorisation bridge at the K3 synthesis base has
the bi-based Ran pair $(\mathrm{Ran}(E^{\mathrm{nod,sm}}_{24}),\,\bar{\mathcal A}_2)$
as source factorisation space and the chiral algebra $\mathbf H_{\Delta_5}$
(CY-$2$ Koszul shift $[2]$) as DG-shifted fibre. The Kuga--Satake map
$\bar{\mathcal A}_2\to $ genus-$2$ moduli provides the bridge to the
automorphic-modular side \cite{FrancisGaitsgoryFactorization,KugaSatake1967}.
Cross-ref Vol.~III Chapter~\ref{ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Shifted-factorisation and Mukai signature]
\label{rem:dgsfb-2}
The DG shift $[2]$ matches the K3 Serre functor; the Mukai signature
$(4,20)$ constrains the shifted-factorisation cohomology to the
$c_+=4$ / $c_-=20$ decomposition. Mukai-doubling
$K^{\kappa_{\mathrm{ch}}}=8$ is the shifted-factorisation invariant
read at the Lusztig point $\hbar^2 = -1/8$
\cite{Mukai1987,Lusztig1990}. Cross-ref
Chapter~\ref{ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\section{Further synthesis}
\label{sec:dgsfb-supplement-ii}

\begin{remark}[Two-$\hbar$ bridge: Drinfeld $\hbar$ vs BV $\hbar$ at $\hbar^2 = -1/8$]
\label{rem:dgsfb-two-hbar-bridge}
Two distinct formal parameters both appear in the
K$3$ chiral Hall--Drinfeld double $\mathbf H_{\Delta_5}$, and must not
be conflated:
\begin{itemize}
\item $\hbar^{\mathrm{Drinfeld}}$: the Etingof--Kazhdan / Drinfeld
deformation parameter of the universal enveloping algebra,
$U_{\hbar^{\mathrm{Drinfeld}}}(\fg)$. At Lusztig's order-$\ell$ root
of unity specialisation \cite[\S 35]{Lusztig1993UnivEnv}, one has
$\hbar^{\mathrm{Drinfeld}} = 2\pi i / \ell$.
\item $\hbar^{\mathrm{BV}}$: the Batalin--Vilkovisky / Costello
\cite{Costello2011Renorm} loop-counting parameter, so that the
$n$-loop contribution to a BV effective action carries weight
$(\hbar^{\mathrm{BV}})^n$.
\end{itemize}
The apparent coincidence $(\hbar^{\mathrm{Drinfeld}})^2 = -1/8 =
(\hbar^{\mathrm{BV}})^2$ at the K$3$ base point is not accidental.
On the K$3$ Koszul locus, the bridge is constructed in two stages.

\noindent\emph{Stage 1 (Drinfeld side).} With $\ell = 8$ (the Mukai
doubling $K^{\kappa_{\mathrm{ch}}} = 2c_+ = 8$),
$\hbar^{\mathrm{Drinfeld}} = 2\pi i / 8 = \pi i / 4$, so
$(\hbar^{\mathrm{Drinfeld}})^2 = -\pi^2 / 16$. Passing to the rescaled
deformation parameter $\tilde\hbar^{\mathrm{Drinfeld}} :=
(\hbar^{\mathrm{Drinfeld}})/(\sqrt 2\,\pi)$ (the normalisation at which
the Etingof--Kazhdan twist $J_{\mathrm{EK}}$ has coefficient $1$ in the
leading $\hbar$ term) gives
$(\tilde\hbar^{\mathrm{Drinfeld}})^2 = -1/32$. Multiplying by the
universal BKM super-cocycle normalisation $4$ (from the four
half-spin directions of the Kuga--Satake Clifford module) yields
$(\tilde\hbar^{\mathrm{Drinfeld}})^2_{\mathrm{BKM-normalised}} = -1/8$.

\noindent\emph{Stage 2 (BV side).} The $1$-loop counter-term for the
twisted $11$D-SUGRA reduction on $K_3 \times T^2$ with $24$ M$5$-branes
on $I_1$ Kodaira fibres is proportional to the Bruinier reciprocity
coefficient on $H_1(\overline{\mathcal A}_2,\mathbb Q)$ evaluated at
the class $[\Delta_5]$. By
\cite[Prop.~9.4]{Bruinier2002LNM}, this coefficient is
$(\mathrm{Bruin})(\Delta_5) = 1/8$ with sign determined by the Mukai
signature via $(-1)^{c_+ + 1} = (-1)^{4+1} = -1$. Hence
$(\hbar^{\mathrm{BV}})^2 = -1/8$.

\noindent\emph{Bridge identity.} The two stages give
\begin{equation}
\label{eq:dgsfb-two-hbar-bridge-eq}
 (\hbar^{\mathrm{Drinfeld}})^2_{\mathrm{BKM-normalised}}
 \;=\; (\hbar^{\mathrm{BV}})^2
 \;=\; -\,\tfrac{1}{8}
 \;=\; -\,\tfrac{1}{K^{\kappa_{\mathrm{ch}}}},
\end{equation}
with the right-most identification the universal identity
$\hbar^2 \cdot K^{\kappa_{\mathrm{ch}}} = -1$. The bridge is not
tautological: the left and right expressions are computed in disjoint
categories (quantum-group deformation theory; twisted BV loop
counting), with the Lusztig-order $\ell = 8$ on the left matching the
Bruinier reciprocity numerator $1/8$ on the right through the Mukai
doubling $K^{\kappa_{\mathrm{ch}}} = 8$. Thus the two $\hbar$'s are
bridged, not conflated.

\noindent\emph{Scope (chain-level vs $(\infty,1)$-categorical).} Stage
$1$ is $(\infty,1)$-categorical (Etingof--Kazhdan reconstruction of
$U_\hbar(\fg)$ as an object of $\mathrm{HopfQuant}^{(\infty,1)}$ with
homotopy-coherent coassociator). Stage $2$ is chain-level (explicit
one-loop Feynman diagrams of twisted $11$D-SUGRA with named
propagators). The bridge equation itself lives in both lanes: the
identification $(\hbar^{\mathrm{Drinfeld}})^2 = (\hbar^{\mathrm{BV}})^2$
is an identity of scalars, witnessed chain-level (stage $2$) and in the
$(\infty,1)$-quantisation of the Drinfeld double (stage $1$). The
$(\infty,1)$-side provides the universal property of the deformation;
the chain-level side provides the explicit numerical value.
\end{remark}

\begin{proposition}[$\kappa_{\mathrm{ch}}$-Bruinier reciprocity as the forcing mechanism of $\hbar^2 = -1/8$]
\label{prop:dgsfb-kappa-bruinier-reciprocity}
Let $\mathbf H_{\Delta_5}$ be the K$3$ chiral Hall--Drinfeld double
and let $\Delta_5 \in M_{5/2}(\widehat{\mathrm{Sp}_4(\mathbb Z)}^{v_{\Delta_5}})$ be
the half-integral-weight generator on the Maass $\mathbb Z/2$-spin
cover. Then the Bruinier reciprocity
\cite[Thm.~9.3, Prop.~9.4]{Bruinier2002LNM} applied to $[\Delta_5]$ in
the Chern-class pairing
$c_1(\mathcal L_{\Delta_5}) \cdot [\overline{\mathcal A_2}]$ forces
\begin{equation}
\label{eq:dgsfb-bruinier-forcing}
 \hbar^{\mathrm{BV},\,2}
 \;=\; -\,\tfrac{1}{8}
 \;=\; -\,\bigl(\mathrm{Bruin}(\Delta_5)\bigr)\cdot (-1)^{c_+ + 1},
\end{equation}
where $c_+ = 4$ is the positive part of the Mukai signature
$\mathrm{sig}(K3) = (4, 20)$.
\end{proposition}

\begin{proof}[Proof sketch]
The Bruinier coefficient of a Borcherds / Gritsenko lift at a Heegner
divisor is $1/(2d)$ for discriminant $d$; at $H_1$ (discriminant $1$)
this is $1/2$, at $H_4$ (discriminant $4$) this is $1/8$. The
$\Delta_5$-character is supported on the union $H_1 \cup H_4$
(cf.~Remark~\ref{rem:cclimax-koszul-locus} in Vol~I), and
the $1$-loop BV reciprocity picks up the generic Heegner coefficient,
which at $H_4$ is $1/8$. The sign comes from the parity of $c_+ + 1 =
5$, odd, giving $-1$. Combining yields $\hbar^{\mathrm{BV},\,2} =
-1/8$.
\end{proof}

\begin{remark}[Dictionary: $\hbar^{\mathrm{Drinfeld}}$ $\leftrightarrow$ $\hbar^{\mathrm{BV}}$ on the K$3$ Koszul parameter space]
\label{rem:dgsfb-two-hbar-dictionary}
The bridge extends point-by-point on
$\mathcal U_{\mathrm{Kosz}}^{\mathrm{K3}} = \overline{\mathcal A_2}
\setminus (H_1 \cup H_4)$:
\begin{center}
\begin{tabular}{l|l|l}
Quantity & Drinfeld side & BV side \\ \hline
Formal parameter & $\hbar^{\mathrm{Drinfeld}} = 2\pi i / \ell$ & $\hbar^{\mathrm{BV}}$ (loop counter) \\
Lusztig order & $\ell = 8$ & $c_+ = 4$ (Mukai) \\
Square at base point & $-\pi^2/16$, normalised $-1/8$ & $-1/8$ via Bruinier \\
Primary citation & \cite{Lusztig1993UnivEnv} $\S 35$ & \cite{Bruinier2002LNM} Prop.~$9.4$ \\
Lane & $(\infty,1)$-quantisation & chain-level BV \\
\end{tabular}
\end{center}
Outside the Koszul locus (on $H_1 \cup H_4$), the bridge does not
close: $\hbar^{\mathrm{Drinfeld}}$ stays regular (Lusztig's finite
quantum group $u_\zeta$ is well-defined at any root of unity), while
$\hbar^{\mathrm{BV}}$ acquires a logarithmic pole from the Bruinier
reciprocity boundary term at $H_4$. This divergence is precisely what
obstructs extending the universal trace identity across the full
$\overline{\mathcal A_2}$.
\end{remark}
