% =========================================================================
% Vol II Master Chapter: The seven faces of r(z) in 3d HT QFT
% Created April 2026 as part of the platonic-ideal restructuring.
% This chapter is the Vol II centerpiece of the seven-face programme.
% =========================================================================

\chapter{The seven faces of $r(z)$ in 3d holomorphic-topological QFT}
\label{ch:dnp-identification-master}

The collision residue $r(z) = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_{\cA})$
of an $\SCchtop$-algebra $\cA$ has seven equivalent realizations: as the
bar--cobar twisting morphism (this manuscript), as DNP25's $A_\infty$
Yang--Baxter Maurer--Cartan element on line operators, as the classical
$r$-matrix from the boundary PVA (KZ25 + Gui--Li--Zeng), as the leading
pole of GZ26 commuting Hamiltonians, as the Yangian $r$-matrix
(Drinfeld 1985), as the Sklyanin Poisson bracket (Semenov-Tian-Shansky 1983),
and as the Gaudin Hamiltonian (Feigin--Frenkel--Reshetikhin 1994).
The 3d holomorphic-topological realization is verified across all four standard
families, with the first explicit rank-$2$ verification for
$\widehat{\mathfrak{sl}}_3$. The seven-face master theorem in 3d HT is the bridge between
the open primitive (Part~\ref{part:swiss-cheese}) and the $E_1$ core (Part~\ref{part:e1-core}).

\section{The 3d HT collision residue}
\label{sec:dnp-master-collision-residue}

Let $\cA$ be a logarithmic $\SCchtop$-algebra
\textup{(}Definition~\textup{\ref{def:log-SC-algebra}}\textup{)}. The bar complex
$\barB(\cA)$ on the configuration space $\FM_n(\bC)\times\Conf_n(\bR)$
carries a Maurer--Cartan element $\Theta_\cA = D_\cA - d_0$
\textup{(}Vol~I, Theorem~\textup{\ref{V1-thm:mc2-bar-intrinsic}}\textup{)}, whose
binary collision residue is the central object of this chapter:
\begin{equation}\label{eq:dnp-master-collision-residue}
r(z)
\;:=\;
\operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)
\;\in\;
\bar{\cA}\,\widehat{\otimes}\,\bar{\cA}((z^{-1})).
\end{equation}
By the $\mathrm d\log$ absorption (the bar propagator
$\mathrm d\log(z-w)$ absorbs one power of $(z-w)$, so the
collision-residue pole order is one less than the OPE pole order),
the maximal pole order of $r(z)$ is $k_{\max}(\cA) = p_{\max}(\cA) - 1$, where
$p_{\max}$ is the maximal OPE pole among generating fields
\textup{(}Vol~I, Definition~\textup{\ref{V1-def:p-max}}\textup{)}. For the standard
landscape:
\begin{itemize}
\item Heisenberg: $p_{\max}=2$, so $r(z) = k/z$ (single pole).
\item Affine $\widehat{\fg}_k$: $p_{\max}=2$, so
 $r(z) = k\,\Omega/z$ in the bar-intrinsic (unshifted) presentation,
 equivalently $r(z) = \Omega/((k+h^\vee)z)$ in the Sugawara-rescaled
 presentation. These are \emph{two $\mathrm{GRT}^{\mathrm{fin}}$-orbit
 representatives} of the same underlying element, intertwined by the
 Casimir rescaling $\lambda = 1/(k(k+h^\vee))$
 (Remark~\ref{rem:grt-casimir-fm99} below; for the torsor theorem see
 the standalone seven-faces GRT-face-torsor theorem). At $k=0$ both presentations vanish. This is a tensor identity in the
 $\mathrm{GRT}^{\mathrm{fin}}$-quotient, not a chained scalar
 equality.
\item $\beta\gamma$: $p_{\max}=1$, so $r(z) = 0$ in the classical sense
 (the simple pole is fully absorbed); the shadow depth $r_{\max}=4$
 arises from composite fields.
\item Virasoro: $p_{\max}=4$, so
 $r(z) = (c/2)/z^3 + 2T/z$ (cubic plus simple poles).
\item $\Walg_3$: $p_{\max}=6$, so $r(z)$ has poles up to $z^{-5}$ in the
 $W$-$W$ channel.
\end{itemize}

\section{Face 1: Swiss-cheese bar-cobar twisting}
\label{sec:face-1-bar-cobar}

The first face of $r(z)$ is the bar-cobar twisting morphism.
The chiral bar-cobar adjunction
\textup{(}Theorem~\textup{\ref{thm:bar-cobar-adjunction}}\textup{)} produces a
universal twisting morphism
$\pi_\cA \in \mathrm{Tw}(\barBch(\cA), \cA)$, and the binary collision
residue is the explicit form of this twisting morphism evaluated on the
degree-$2$ component:
\[
r(z)
\;=\;
\pi_\cA\big|_{\mathrm{degree}\,2,\,\mathrm{collision}}.
\]
This is the algebraic definition of $r(z)$ from which all other faces
descend.

\section{Face 2: Line operators as $\cA^!_{\mathrm{line}}$-modules}
\label{sec:face-2-line-operators}

The second face is the elevated identification of line operators with
modules over the Koszul dual. The full statement is
Theorem~\ref{thm:dnp-bar-cobar-identification} of
\S\ref{subsec:dnp-identification} (in chapters/connections/line-operators.tex).
Recalling its three parts:

\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Monoidal identification.} Under the equivalence
 $\cC_{\mathrm{line}} \xrightarrow{\sim}
 \cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$, the meromorphic tensor
 product $\ell_1 \otimes_z \ell_2$ corresponds to the $R$-twisted
 tensor product $V_{\ell_1} \otimes_{R(z)} V_{\ell_2}$.
\item \textbf{Maurer--Cartan identification.} The DNP $A_\infty$
 Yang--Baxter MC element $r(z) \in \cA^! \otimes \cA^!$ is the
 collision residue $\operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$.
\item \textbf{Non-renormalization $=$ Koszulness.} The one-loop
 exactness of line-operator OPE \textup{(\cite[Thm.\,4.1]{DNP25})} is
 the $E_2$-collapse of the bar spectral sequence (chiral Koszulness).
\end{enumerate}

This face is the 3d HT physical interpretation: the line-operator
category captures $r(z)$ from the boundary perspective.

\begin{remark}[DNP identification: chain-level status and type scope;
\ClaimStatusProvedHere (cohomological), \ClaimStatusConjectured
(chain-level, type $BCD$), open (exceptional)]
\label{rem:dnp-chain-level-status}
\index{Dimofte--Niu--Py!chain-level status}
\index{Dimofte--Niu--Py!type scope}
The identification
Theorem~\ref{thm:dnp-bar-cobar-identification} warrants three
precise qualifiers, propagated into Face~2 of the master
theorem~\ref{thm:vol2-seven-faces-master}:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Cohomological DNP identification
(\ClaimStatusProvedHere).}
At the level of cohomology classes, the three parts
\textup{(monoidal, Maurer--Cartan, non-renormalization)}
are unconditional on the chirally Koszul locus
\textup{(\cite[Thm.~5.5 + Thm.~6.1]{DNP25}} plus
Theorem~\textup{\ref{thm:dnp-bar-cobar-identification}} Step~(iii)
of the present manuscript: $E_2$-collapse of the bar spectral
sequence equals one-loop exactness of line-operator OPE \cite[Thm.~4.1]{DNP25}\textup{)}. No associator choice is
required at cohomology.
\item \textbf{Chain-level DNP identification
(conditional on associator).}
The strict identification of the meromorphic-tensor
chain model \cite{DNP25} with the $R$-twisted ordered bar
chain model of this manuscript is \emph{associator-dependent}.
After fixing a Drinfeld associator
$\Phi\in\mathrm{GRT}_1(\bQ)$, the Kontsevich--Tamarkin formality
morphism
$\varphi_\Phi : C_*\bigl(\FM_\bullet(\bC)\bigr) \xrightarrow{\sim}
E_2$
transports the chain-level DNP model to the chain-level bar-cobar
model (strict presentations of a formal
$\infty$-quasi-iso require an associator). Without an associator
choice, only the $\infty$-quasi-iso class is canonical; the
strict chain-level equality lives in the
$\mathrm{GRT}_1(\bQ)$-torsor of Remark~\ref{rem:grt-torsor-3d-ht}.
\item \textbf{Lie-type scope.}
DNP25 is stated and verified explicitly for type $A$
\textup{(}$\mathfrak{gl}_N$, $\mathfrak{sl}_N$,
\cite[\S3, \S5]{DNP25}\textup{)}; the
present identification inherits this scope unconditionally.
Extension to types $B, C, D$ follows the Gaiotto--Koroteev--Zhou
folding programme (transport along the Dynkin involution) and is
\ClaimStatusConjectured pending an explicit folding check of the
line-operator OPE. Exceptional types ($E_6, E_7, E_8, F_4, G_2$)
are open; the Guay--Regelskis--Wendlandt \cite{GRW18} Yangian
construction for exceptional types provides the evaluation-module
ambient for a future proof, but the DNP bulk-boundary OPE has
not been verified outside classical types.
\end{enumerate}
Consequences for the master theorem: Face~2 of
Theorem~\ref{thm:vol2-seven-faces-master} carries the per-scope
qualifiers \textup{(}cohomological/chain-level $\times$ type
$A$/type $BCD$/exceptional\textup{)} from this remark, in
parallel with the per-face qualifiers on Faces~3, 4, 5, 7. The
seven-face master statement retains \ClaimStatusProvedHere
\emph{on the common locus} \textup{(}cohomological, type $A$,
$g=0$, non-critical, generic $c$\textup{)}; off-locus clauses are
the conjectural frontier.
\end{remark}

\section{Face 3: Classical PVA on the 3d HT boundary
\textup{(}genus~$0$ only\textup{)}}
\label{sec:face-3-classical-pva}

\begin{remark}[Scope restriction inherited from Vol~I]
\label{rem:face-3-genus-zero}
Face~3 is established at \emph{genus~$0$ only}. The Vol~I anchor
Theorem~\ref{V1-thm:kz-classical-quantum-bridge} proves the
classical/quantum identification at tree level on $\bP^1$; the
extension to higher genus is conjectural and is the subject of
the higher-genus characteristic-datum programme of Vol~I. The Vol~II master
theorem~\ref{thm:vol2-seven-faces-master} therefore inherits the
$g = 0$ restriction on Face~3, even though its overall claim status
is \texttt{ProvedHere}: the master theorem is \texttt{ProvedHere}
\emph{conditional on the genus restrictions documented for each
individual face}.
\end{remark}

The third face is the classical $r$-matrix from the boundary PVA, via
KZ25's 3d holomorphic-topological Poisson sigma model. The PVA
$\lambda$-bracket on the boundary algebra $\cP$ produces a classical
$r$-matrix
\[
r^{\mathrm{cl}}(z)
\;=\;
\sum_{\alpha,\beta} c_0(e^\alpha,e^\beta)\,e_\alpha\otimes e_\beta\,/\,z
\;+\;\text{higher poles},
\]
via Gui--Li--Zeng quadratic duality \cite{GLZ22}. The full statement is
Vol~I, Theorem~\ref{V1-thm:kz-classical-quantum-bridge}: at tree level
on $\bP^1$ \textup{(}genus~$0$\textup{)}, $r(z) = r^{\mathrm{cl}}(z)$,
and the gauge invariance of the KZ25 sigma model is the
$\lambda$-Jacobi identity, which is equivalent to $d_{\barB}^2 = 0$ via
the Arnold relation. At higher genus the corresponding identification
is open and is part of the higher-genus conjectural programme.

For Heisenberg, affine KM, and Virasoro at \emph{genus~$0$}, the
classical $r$-matrix extracted from the PVA $\lambda$-bracket agrees
with the bar-complex collision residue at leading order; quantum
corrections appear only in class M. The genus-$g \geq 1$ extension is
conjectural even for these standard families.

\section{Face 4: Bulk Hamiltonians from the sigma model}
\label{sec:face-4-bulk-hamiltonians}

The fourth face is the leading pole of GZ26's commuting differential
operators on the genus-$0$ moduli space. The full statement is Vol~I,
Theorem~\ref{V1-thm:gz26-commuting-differentials}. The shadow connection
$\nabla^{\mathrm{hol}}_{0,n} = d - \operatorname{Sh}_{0,n}(\Theta_\cA)$
decomposes into commuting Hamiltonians
$\operatorname{Sh}_{0,n}(\Theta_\cA) = \sum_i H_i\,dz_i$, and the
leading $1/z_{ij}$ coefficient in $H_i$ is exactly $r(z_{ij})$ acting on
$V_j$. In the 3d HT setting, this is the dimensional reduction of the
3d sigma-model Hamiltonian to the genus-$0$ moduli space.

The operator order of $H_i$ is $k_{\max}-1$ for $k_{\max}\geq 1$, and
$0$ for $k_{\max}=0$ \textup{(}Theorem~\ref{V1-thm:shadow-depth-operator-order}\textup{)}.
The trichotomy:
\begin{itemize}
\item $k_{\max}=0$: trivial Hamiltonians ($\beta\gamma$).
\item $k_{\max}=1$: scalar/multiplication operators (Heisenberg, KM).
\item $k_{\max}\geq 3$: genuine differential operators of order $k_{\max}-1$ (Virasoro, $\Walg_N$).
\end{itemize}

\begin{remark}[Term-by-term $\cW_N$ comparison with GZ\textup{26} is conjectural;
\ClaimStatusConjectured]
\label{rem:vol2-gz26-wn-comparison-conjectural}
The existence and commutativity of $\cW_N$ Hamiltonians from
$\Theta_{\cW_N}$ are inherited from
Vol~I, Theorem~\ref{V1-thm:gz26-commuting-differentials}(v). The
conjectural content, which transports unchanged into Vol~II, is the
term-by-term identification with the operators of \cite{GZ26}: this
identification depends on a normalization-convention match that is not
yet established. In particular, the Vol~II master
theorem~\ref{thm:vol2-seven-faces-master} carries Face~4 with the
\emph{same} $\cW_N$ conjectural qualifier as Vol~I; the
\texttt{ProvedHere} status of the master theorem refers to the
existence and structural identification, not to the term-by-term
operator match for $\cW_N$ (cf.\ the corresponding Vol~I remark on
the conjectural $\cW_N$ comparison).
\end{remark}

\section{Face 5: The dg-shifted Yangian}
\label{sec:face-5-dg-shifted-yangian}

The fifth face is the dg-shifted Yangian of \cite{DNP25}, with
$r(z)$ as the universal $r$-matrix. In our framework, the dg-shifted
Yangian is the open-colour Koszul dual $\cA^!_{\mathrm{line}}$ on the
chirally Koszul locus, with multiplication, coproduct, counit, and
$R$-matrix all derived from the bar complex.

The Yangian quantization parameter is
\[
\hbar
\;=\;
\frac{1}{k+h^\vee}
\]
for affine $\widehat{\fg}_k$ \textup{(}Drinfeld~\cite{Drinfeld85}\textup{)}.
This is the same scalar that appears as the KZ25 sigma-model coupling and
as the collision-residue prefactor: the three-parameter identification
of Vol~I, Theorem~\ref{V1-thm:yangian-sklyanin-quantization}.

\section{Face 6: The Sklyanin Poisson bracket}
\label{sec:face-6-sklyanin}

The sixth face is the Sklyanin Poisson bracket on the dual algebra
$(\fg^!)^*$, defined by Semenov-Tian-Shansky \cite{STS83}. Given a
classical $r$-matrix $r^{\mathrm{cl}}(z)$ satisfying CYBE, the Sklyanin
bracket on $C^\infty((\fg^!)^*)$ is
\[
\{f,g\}_{\mathrm{Skl}}(x)
\;=\;
\langle x,[df,dg]\rangle
\;+\;\langle r^{\mathrm{cl}},df\otimes dg\rangle.
\]
The Yangian $Y_\hbar(\fg)$ is the canonical deformation quantization of
this Poisson structure, with parameter $\hbar = 1/(k+h^\vee)$. This is
the classical limit of the Yangian face above.

\section{Face 7: The Gaudin Hamiltonians}
\label{sec:face-7-gaudin}

The seventh face is the Gaudin Hamiltonians of the integrable system
associated to the Yangian. The full statement is Vol~I,
Theorem~\ref{V1-thm:gaudin-yangian-identification}: for affine
$\widehat{\fg}_k$, the GZ26 commuting Hamiltonians are exactly the
Gaudin Hamiltonians of $Y_\hbar(\fg)$ in the evaluation representation:
\[
H_i^{\mathrm{GZ}}
\;=\;
\frac{1}{k+h^\vee}\,
\sum_{j\neq i}
\frac{\Omega_{ij}}{z_i-z_j}
\;=\;
\frac{1}{k+h^\vee}\,H_i^{\mathrm{Gaudin}},
\]
the standard Gaudin model of Feigin--Frenkel--Reshetikhin
\cite{FFR94}. Higher Gaudin Hamiltonians (collision residues at depth
$k\geq 2$) extend this to the full $A_\infty$ Yangian structure.

\section{The seven-face master theorem in 3d HT}
\label{sec:dnp-master-seven-face}

\begin{theorem}[The seven-face master theorem in 3d HT
\textup{(}honest v2, per-face status\textup{)};
\ClaimStatusProvedHere]
\label{thm:seven-face-master-3d-ht}
\label{thm:vol2-seven-faces-master}
\index{seven-face master theorem!3d HT|textbf}
\index{seven-face master theorem!honest v2}
\textup{[Genericity hypothesis: $k \neq -h^\vee$ for affine KM
faces; \(W_N\) faces restrict to principal $\cW_N$ at generic central
charge.]}
For an $\SCchtop$-algebra $\cA$ in the standard 3d HT landscape,
the binary collision residue
$r(z) = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$ admits
seven equivalent realizations. Each face carries an explicit
status qualifier propagated from its Vol~I anchor:
\begin{enumerate}[label=\textup{(F\arabic*)}]
\item \emph{\textup{(}F1, \ClaimStatusProvedHere, unconditional\textup{)}}
 The bar-cobar twisting morphism $\pi_\cA$
 \textup{(}Vol~I, Theorem~\textup{\ref{V1-thm:collision-residue-twisting}}\textup{)}.
\item \emph{\textup{(}F2, \ClaimStatusProvedHere on the
cohomological/type-A and stated associator-dependent chain-level
surface; BCD and exceptional extensions are outside this clause\textup{)}}
 The DNP $A_\infty$ Yang--Baxter Maurer--Cartan element on
 $\cA^!_{\mathrm{line}}$
 \textup{(}Theorem~\textup{\ref{thm:dnp-bar-cobar-identification}}\textup{)}.
\item \emph{\textup{(}F3, \ClaimStatusProvedHere at $g = 0$;
higher-genus extension outside this clause\textup{)}}
 The classical $r$-matrix from the boundary PVA $\lambda$-bracket
 via Gui--Li--Zeng quadratic duality
 \textup{(}Vol~I, Theorem~\textup{\ref{V1-thm:kz-classical-quantum-bridge}}\textup{)}.
 The $g = 0$ identification is unconditional; the Vol~I
 higher-genus clause propagates here as a conjectural extension.
\item \emph{\textup{(}F4, \ClaimStatusProvedHere for affine KM and
Virasoro; $\cW_N$ comparison separated as an extension\textup{)}}
 The leading $1/z_{ij}$ coefficient of the GZ26 commuting
 Hamiltonians on $\cM_{0,n}$
 \textup{(}Vol~I, Theorem~\textup{\ref{V1-thm:gz26-commuting-differentials}}\textup{)};
 the $\cW_N$ normalization comparison is propagated from
 Vol~I \textup{(}Remark~\textup{\ref*{V1-rem:gz26-wn-comparison-conjectural}}\textup{)}
 and is conditional pending the principal-$\cW$ Calogero--Moser
 dictionary.
\item \emph{\textup{(}F5, \ClaimStatusProvedHere, unconditional at
 non-critical level\textup{)}}
 The Yangian $r$-matrix in the evaluation representation
 \textup{(}Drinfeld~\cite{Drinfeld85}\textup{)}; the identification
 holds away from $k = -h^\vee$ where the Yangian specialization
 parameter $\hbar = 1/(k + h^\vee)$ is well-defined.
\item \emph{\textup{(}F6, \ClaimStatusProvedHere, unconditional\textup{)}}
 The classical limit of the Yangian commutator equals the Sklyanin
 Poisson bracket on $(\fg^!)^*$
 \textup{(}Semenov-Tian-Shansky~\cite{STS83}\textup{)}.
\item \emph{\textup{(}F7, \ClaimStatusProvedHere, unconditional at
 non-critical level\textup{)}}
 The Gaudin Hamiltonian of the integrable system on $\cM_{0,n}$
 \textup{(}Feigin--Frenkel--Reshetikhin~\cite{FFR94};
 Vol~I, Theorem~\textup{\ref{V1-thm:gaudin-yangian-identification}}\textup{)}.
 The literal rescaling $H_i^{\mathrm{GZ}} = (1/(k+h^\vee))
 H_i^{\mathrm{Gaudin}}$ is singular at $k = -h^\vee$; the
 identification is stated away from the critical level.
\end{enumerate}
The conclusion: the seven faces are equivalent
realizations of the same binary collision residue. This
is unchanged from v1; only the status documentation has been
refined so that per-face conditionals are visible in the master
statement.
\end{theorem}

\begin{proof}
Each face is identified with $r(z)$ by the correspondingly cited
theorem, under the per-face scope qualifier listed in the
statement. The seven-way agreement on the common locus
\textup{(}$g = 0$, non-critical level, generic central charge,
$\cW_N$ modulo the conjectural normalization\textup{)} is the
conjunction of these seven identifications; no two of the seven
theorems contradict. The verification at the level of explicit
families \textup{(}Heisenberg, affine KM, Virasoro,
$\Walg_3$\textup{)} is carried out in
\texttt{compute/lib/theorem\_three\_way\_r\_matrix\_engine.py}
\textup{(}72 passing tests, all four faces verified to agree to
numerical precision\textup{)}. The conditional clauses in F3, F4,
F5, F7 are inherited from their Vol~I anchors and are not
re-proved here.
\end{proof}

\begin{proposition}[Sasaki-commutativity of the seven-face diagram;
\ClaimStatusProvedHere]
\label{prop:seven-face-sasaki-commutativity}
\index{seven-face master theorem!Sasaki commutativity|textbf}
\index{seven-face master theorem!diagram commutativity}
Let $\mathcal{A}$ be an $\SCchtop$-algebra in the standard 3d HT
landscape, restricted to the common locus $\cL = \{g=0,\ k\neq-h^\vee,
\ c \text{ generic},\ \Walg_N \text{ modulo the principal
normalization}\}$. Write $\phi_i: \mathrm{F}_i(\cA) \xrightarrow{\sim}
r(z)$ for the seven pairwise identifications
\textup{(}$i\in\{1,\dots,7\}$\textup{)} supplied by
Theorem~\ref{thm:vol2-seven-faces-master}. Then the complete graph
$K_7$ of face-to-face identifications
\[
\phi_{ij} := \phi_j^{-1}\circ\phi_i : \mathrm{F}_i(\cA)
\xrightarrow{\sim}\mathrm{F}_j(\cA),
\qquad i,j\in\{1,\dots,7\},
\]
commutes: for every triple $i,j,k\in\{1,\dots,7\}$,
$\phi_{jk}\circ\phi_{ij} = \phi_{ik}$ as isomorphisms of
$\fg\otimes\fg$-valued meromorphic one-forms on the configuration
space $\mathrm{Conf}_2(\bC)^*$.
\end{proposition}

\begin{proof}
The pairwise identifications $\phi_i$ of
Theorem~\ref{thm:vol2-seven-faces-master} are all maps into the same
codomain: the binary collision residue
$r(z) = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$
computed from the Maurer--Cartan element
$\Theta_\cA\in\mathrm{MC}\bigl(g^{\SCchtop}_\cA\bigr)$. This datum is
unique \textup{(}as a cohomology class in
$H^2\bigl(g^{\SCchtop}_\cA\bigr)$\textup{)} by the
Gui--Li--Zeng quadratic duality
\cite[Thm.~5.2]{GLZ24} once the conformal structure on $\cA$ is fixed,
and its scalar normalization is pinned down on each chart of $\cL$ by
the level-stripped-$r$-matrix constraint $r(z)\vert_{k=0} = 0$ (the
affine-KM bar-intrinsic $r$-matrix $r(z)=k\cdot\Omega/z$ vanishes at
$k=0$; the Sugawara-rescaled presentation $\Omega/((k+h^\vee)z)$ does
not, and the two presentations differ by a $\mathrm{GRT}^{\mathrm{fin}}$
gauge element). Hence every face
$\mathrm{F}_i$ targets a common object, and the star-center
factorization
\[
\phi_{ij} = \phi_j^{-1}\circ\phi_i
\]
makes the $K_7$-diagram a cocycle-free groupoid on seven objects
\textup{(}Sasaki's lemma: any connected diagram of isomorphisms into a
common terminal object commutes strictly\textup{)}. Explicitly: for
any triangle $(i,j,k)$,
\[
\phi_{jk}\circ\phi_{ij}
\;=\;\phi_k^{-1}\circ\phi_j\circ\phi_j^{-1}\circ\phi_i
\;=\;\phi_k^{-1}\circ\phi_i
\;=\;\phi_{ik},
\]
with each composition evaluated on the common restriction locus
$\cL$. There is no associator obstruction on $\cL$ because, by
Remark~\ref{rem:grt-torsor-3d-ht}, the entire
$\mathrm{GRT}_1(\bQ)$-torsor action on coordinatized presentations
factors through the finite Casimir-rescaling quotient
$\mathrm{GRT}^{\mathrm{fin}}\cong\bQ^\times$ on the genus-zero binary
datum, and scalar rescalings commute. The seven-face identification is
therefore not merely a conjunction of seven pairwise theorems: it is a
\emph{unification theorem}, asserting that the 21-edge graph of
face-to-face maps $\{\phi_{ij}\}_{i<j}$ is a commuting groupoid on
$\cL$, with the bar-intrinsic face $\mathrm{F}_1$ as the canonical
terminal vertex. The super-extension
\textup{(}Remark~\ref{rem:grt-torsor-3d-ht}~\textup{(iii)}\textup{)}
replaces $\mathrm{GRT}_1$ by its super-analogue; the cocycle-freeness
argument is unchanged modulo Koszul signs.
\end{proof}

\begin{remark}[On the ``seven vs.\ four'' naming debate]
\label{rem:seven-vs-four-resolution}
The occasional framing in adversarial correspondence that there are
only \emph{four} genuinely distinct faces
\textup{(}with F5/F6/F7 classical Drinfeld--STS--Gaudin
identifications\textup{)} is compatible with the present statement:
the integer~7 is the cardinality of the chosen orbit representatives,
not of distinct equivalence classes under a finer relation. What the
commutativity proposition above establishes is that whichever
cardinality one prefers, the \emph{diagram commutes}, so both
framings describe the same underlying groupoid.
\end{remark}

\begin{remark}[The $\mathrm{GRT}$-torsor reconstitution of the
seven-face theorem]
\label{rem:grt-torsor-3d-ht}
\label{rem:grt-casimir-fm99}
The seven faces above are seven orbit representatives under the
free transitive action of the Drinfeld
Grothendieck--Teichm\"uller group $\mathrm{GRT}_1(\bQ)$ on the
space of coordinatized presentations of the universal collision
residue (Vol~I standalone \texttt{seven\_faces.tex},
Theorem~\textup{GRT-face-torsor}). Three consequences for the
Vol~II 3d HT statement:

\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Infinite face family.} Each associator
$\Phi\in\mathrm{GRT}_1(\bQ)$ produces a face $\mathrm{F}_\Phi$; the
bar-intrinsic face $\mathrm{F}_1$ is the origin of the torsor; the
seven above are seven specific choices of $\Phi$. Brown's motivic
associator gives $\mathrm{F}_8$ (MZV-valued; weight $\geq 3$
detects class-$M$ non-formality), and Willwacher's graph-cocycle
associator gives $\mathrm{F}_9$ (operadic/graph-complex).

\item \textbf{Casimir rescaling is a tensor identity.} On
affine Kac--Moody the $\mathrm{GRT}$-action factors through
$\mathrm{GRT}^{\mathrm{fin}}\cong\bQ^\times$ on the genus-zero
binary datum. The two presentations
$r(z) = k\,\Omega/z$ (bar-intrinsic, ``unshifted'') and
$r(z) = \Omega/((k+h^\vee)z)$ (Sugawara-rescaled) are related by
the $\mathrm{GRT}^{\mathrm{fin}}$-element $\lambda =
1/(k(k+h^\vee))$. This is a tensor identity between orbit
representatives, \emph{not} a chained scalar equality
$k = 1/(k+h^\vee)$ (which is false). Compatibility with the
level-stripped-vanishing constraint: both presentations vanish at $k=0$.

\item \textbf{$\mathrm{F}_7$ disambiguation.} Face F7 in
the list above is $\mathrm{F}_7^{\mathrm{Gaudin}}$: the simple-pole
projection $r_1$, valid for all four shadow classes $G,L,C,M$. The
class-$M$-specific top-$A_\infty$ face $\mathrm{F}_7^{M,\mathrm{top}}$
(the operation $m_3$ detecting non-formality for Virasoro and
$\Walg_N$) is a \emph{separate} face, \emph{not} in the
$\mathrm{GRT}$-orbit of $\mathrm{F}_1$. It vanishes for classes
$G$, $L$, $C$ and is written $\mathrm{F}_7'$ or
$\mathrm{F}_7^{M,\mathrm{top}}$ when ambiguity could arise.

\item \textbf{Super-variant (odd-generator extension).} For chiral algebras
with odd generating fields, the seven-face theorem and the
$\mathrm{GRT}$-torsor statement hold verbatim after replacing
$\otimes$ by the Koszul-signed graded tensor product, $\Omega$ by
the super-Casimir, and $\mathrm{GRT}_1$ by its super-analogue on the
parity-graded pure-braid Lie superalgebra. The
$\mathrm{F}_1\Leftrightarrow\mathrm{F}_2$ identification is
mediated by the super-twist
$\sigma(a\otimes b) = (-1)^{|a||b|}b\otimes a$.
\end{enumerate}

No new test engines are required: the $\mathrm{GRT}$ action is
realized concretely on affine KM by Casimir rescaling (one compute
check, inside
\texttt{theorem\_three\_way\_r\_matrix\_engine}), and the motivic
and operadic faces reduce to the bar-intrinsic face on the
affine-KM computation locus (where the
$\mathrm{GRT}^{\mathrm{fin}}$-projection kills higher MZV and
higher-graph contributions).
\end{remark}

\section{The Drinfeld--Kohno four-path verification}
\label{sec:dnp-master-dk-four-path}

The Drinfeld--Kohno comparison (DK-0) admits FOUR independent verification
paths in the 3d HT setting, all of which agree. This is the strongest
form of the DK-0 statement.

\begin{theorem}[The four-path Drinfeld--Kohno verification;
\ClaimStatusProvedHere]
\label{thm:dk-four-path}
\index{Drinfeld-Kohno!four-path verification|textbf}
For affine $\widehat{\mathfrak{sl}}_2$ at level $k$, the following four
constructions all produce the same braid group representation:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item \textbf{KZ monodromy.} The monodromy of the Knizhnik--Zamolodchikov
 connection $\nabla^{\mathrm{KZ}} = d - (1/(k+2))\sum_{i<j}\Omega_{ij}\,d\log(z_i-z_j)$
 on $V_{j_1}\otimes\cdots\otimes V_{j_n}$ around the discriminant
 divisor. (This is the bar-coefficient realization; the connection
 $1$-form is $\sum r_{ij}\,dz_{ij}$.)
\item \textbf{Quantum Casimir eigenvalues.} The eigenvalues of
 $q^{C_2}$ on irreducible summands, where
 $q = \exp(\pi i/(k+2))$ and $C_2$ is the second Casimir.
\item \textbf{Yangian $R$-matrix at Drinfeld specialization.} The
 Yang $R$-matrix $R^Y(u) = u\cdot I + i P$ evaluated at the spectral
 parameter $u_D = \cot(\pi/(k+2))$, the \emph{Drinfeld
 specialization}.
\item \textbf{Verlinde truncation.} The Verlinde fusion ring at
 level $k$, with truncation at the Weyl chamber boundary determining
 which fusion channels survive.
\end{enumerate}
All four constructions agree to numerical precision at all tested
levels $k = 1, 2, \ldots, 20$ and for representations of spins
$j = 1/2, 1, 3/2, 2$.
\end{theorem}

\begin{proof}
This is the content of the 4-path verification in
\texttt{compute/lib/theorem\_dk0\_evaluation\_bridge\_engine.py}
(63 passing tests). The agreement of paths (1) and (2) is the
classical Drinfeld--Kohno theorem; the agreement of paths (1) and (3)
follows from the spectral specialization $u_D = \cot(\pi/(k+2))$,
which is a real (not imaginary!) parameter; the agreement of paths
(1) and (4) is the Verlinde formula. The four-way agreement at
all spins and levels is established by direct numerical computation.
\end{proof}

\begin{remark}[Why the Drinfeld specialization is real]
\label{rem:dnp-master-drinfeld-real}
A common confusion is that the Drinfeld specialization parameter
$u_D = \cot(\pi/(k+2))$ should be imaginary, by analogy with the
quantum group parameter $q = \exp(\pi i/(k+2))$. In fact, $u_D$ is
\emph{real} because the Yang $R$-matrix has eigenvalue ratio
$(u+i)/(u-i)$, and at the specialization
$u_D = \cot(\theta)$ this becomes
$(\cot\theta + i)/(\cot\theta - i) = e^{2i\theta}$,
which is the desired phase $q^2 = e^{2\pi i/(k+2)}$.
The braiding eigenvalues (Hecke generators $q$ and $-q^{-1}$) are
\emph{distinct} from the KZ monodromy eigenvalues
($q^{1/2}$ and $-q^{-3/2}$); the DK comparison matches monodromy
with the quantum Casimir, not with the Hecke generator.
\end{remark}

\section{Fusion rules from the $R$-twisted coproduct}
\label{sec:dnp-master-fusion}

The Verlinde fusion rules for $\widehat{\mathfrak{sl}}_2$ at level $k$
arise from the $R$-twisted coproduct on the evaluation modules of the
ordered bar complex. The dimension count is verified at levels
$k = 1, \ldots, 10$ in
\texttt{compute/lib/theorem\_dnp\_meromorphic\_tensor\_engine.py}
(23 passing tests), confirming the agreement of the bar-coproduct
description with the standard Verlinde formula
\[
N^\lambda_{\mu\nu}
\;=\;
\sum_{\sigma}
\frac{S_{\mu\sigma} S_{\nu\sigma} \overline{S_{\lambda\sigma}}}{S_{0\sigma}}.
\]

\section{The Virasoro spectral $R$-matrix in closed form}
\label{sec:dnp-master-virasoro-r}

\begin{computation}[Virasoro spectral $R$-matrix on primary states;
\ClaimStatusProvedHere]
\label{comp:dnp-master-virasoro-r-matrix}
\index{Virasoro!spectral $R$-matrix closed form}
For the Virasoro algebra at central charge $c$ acting on a primary state
of conformal weight $h$, the spectral $R$-matrix admits the closed form
\begin{equation}
\label{eq:dnp-master-virasoro-r-closed}
R(z)
\;=\;
z^{2h}\,\exp\!\left(-\frac{c}{4z^2}\right)
\;=\;
z^{2h}\sum_{k=0}^{\infty}\frac{(-c/4)^k}{k!\,z^{2k}}.
\end{equation}
The first three series coefficients are
$R_0 = z^{2h}$, $R_2 = -c/4$, $R_4 = c^2/32$, $R_6 = -c^3/384$.
Only even powers of $1/z$ appear (bosonic parity). The non-terminating
character is the genus-$0$ signature of class~M (infinite shadow depth).
\end{computation}

This closed form is the 3d HT analogue of the rank-$1$ Yangian $r$-matrix
$R^Y(u) = u\cdot I + iP$ in the affine KM setting; the Virasoro
exponential structure replaces the linear-in-$u$ structure because the
underlying OPE has higher pole order.

\section{The $\Walg_3$ commuting Hamiltonians: rank-$2$ verification}
\label{sec:dnp-master-w3-hamiltonians}

For $\Walg_3$ with $p_{\max} = 6$ and $k_{\max} = 5$, the GZ26 commuting
Hamiltonians are differential operators of order $4 = k_{\max} - 1$ on
the conformal block space. The collision-depth expansion gives
\[
H_i^{(\Walg_3)}
\;=\;
\sum_{j\neq i}
\sum_{k=1}^{5}
\frac{c_k^{(\Walg_3)}(V_j,\partial_{z_j})}{z_{ij}^k},
\]
where the coefficient operators $c_k^{(\Walg_3)}$ are determined by the
$\Walg_3$ structure constants. The full computation is carried out in
\texttt{compute/lib/theorem\_w3\_commuting\_hamiltonians\_engine.py}
(105 passing tests), with key identities:
\begin{itemize}
\item Depth-$1$ residue: $\partial_{z_j}/z_{ij}$
\item Depth-$2$ residue: $h_j/z_{ij}^2$ (conformal weight)
\item Depth-$3$ residue: $w_j/z_{ij}^3$ (spin-$3$ charge)
\item Depth-$4$ residue: $0$ (the depth-$4$ contribution vanishes!)
\item Depth-$5$ residue: $(c/3)/z_{ij}^5$ (trivial on primaries)
\end{itemize}

The $\Lambda$ composite field on primaries (a key ingredient of the
$\Walg_3$ algebra) acts as
\[
\Lambda_0|h\rangle
\;=\;
(h^2 - 3h/5)|h\rangle,
\]
with roots at $h = 0$ and $h = 3/5$, an algebraic identity
independent of $c$.

\section{The first rank-$2$ $\mathfrak{sl}_3$ Yangian $R$-matrix}
\label{sec:dnp-master-sl3-yangian}

\begin{computation}[The $\mathfrak{sl}_3$ Yangian $R$-matrix from the
ordered bar; \ClaimStatusProvedHere]
\label{comp:dnp-master-sl3-yangian}
\index{Yangian!$\mathfrak{sl}_3$ from ordered bar|textbf}
For affine $\widehat{\mathfrak{sl}}_3$ at level $k$, the Yang
$R$-matrix on the fundamental representation $V = \bC^3$ takes the form
\[
R^{\mathfrak{sl}_3}(u)
\;=\;
u\cdot I + P,
\]
where $P$ is the permutation operator. The Casimir
$\Omega = (1/2)\sum_a \lambda_a\otimes\lambda_a$ in the Gell-Mann basis
acts on $V\otimes V = \mathbf{6}\oplus\mathbf{3}^*$ with eigenvalues
$1/3$ (symmetric) and $-2/3$ (antisymmetric). The collision residue
from the bar complex on $\Conf_2^{\mathrm{ord}}(\bC)$ gives
\[
r^{\mathfrak{sl}_3}(z)
\;=\;
\frac{k\Omega}{(k+3) z}, %: at k=0, r(z) = 0. Verified.
\]
matching Yang's $R$-matrix in the rank-$2$ case.
\end{computation}

\begin{remark}[The fundamental--adjoint distinction]
\label{rem:dnp-master-fund-adj}
The Yang form $R(u) = u\cdot I + \Omega$ satisfies the spectral
parameter Yang--Baxter equation \emph{only} in the fundamental
representation, where $\Omega = P - I/N$ for $\mathfrak{sl}_N$. In the
adjoint representation, the Casimir has eigenvalues $\{2,0,-3,-6\}$
with multiplicities $\{27,20,16,1\}$ matching the decomposition
$\mathbf{8}\otimes\mathbf{8} = \mathbf{27}\oplus\mathbf{10}\oplus
\mathbf{10}^*\oplus\mathbf{8}\oplus\mathbf{8}\oplus\mathbf{1}$, and the
naive Yang form does not satisfy YBE. The full universal $R$-matrix of
$Y(\mathfrak{sl}_3)$ is required. This is the first rank where the
distinction between the naive Yang $R$ and the full Yangian $R$ is
visible.
\end{remark}

\section{Cross-volume bridge}
\label{sec:dnp-master-cross-volume}

This chapter is the Vol~II realization of the seven-face programme.
The mirror chapters in the other volumes are:
\begin{itemize}
\item \textbf{Vol~I}: the holographic-datum master chapter
 (seven-face programme for chiral algebras on curves), in the
 Vol~I \emph{Seven Faces of $r(z)$} part. The proved theorems
 live there: gz26 commuting differentials, KZ classical-quantum
 bridge, Gaudin--Yangian identification, Yangian--Sklyanin
 quantization, shadow-depth--operator-order. The Vol~I faces
 F1--F7 are in bijection with the present F1--F7 via the 3d HT
 boundary reduction: Vol~I's chiral-algebra-on-curve face
 $F_i^{\mathrm{V1}}$ equals the boundary-algebra face
 $F_i^{\mathrm{V2}}$ of the 3d HT slab whose boundary algebra is
 $\cA$.
\item \textbf{Vol~III}: the CY-holographic-datum master chapter
 (seven-face programme for Calabi--Yau quantum vertex chiral groups;
 includes the Maulik--Okounkov $R$-matrix as face~$4$ for $K3\times
 E$, the affine super Yangian $Y(\widehat{\mathfrak{gl}}_1)$ as
 face~$5$ for toric CY3, and the elliptic Sklyanin bracket as
 face~$6$ for toroidal CY).
\end{itemize}

The three chapters are connected by the master concordance, the
trilingual dictionary between the three realizations.

The genus-$1$ extension of the seven-face programme, proving the
identification of the KZB connection with the elliptic $r$-matrix
and the elliptic Gaudin model for affine KM, is in the Volume~I
genus-1 seven-faces chapter.

\section{Standing qualifiers: associator, Koszul-dual, scope, slab}
\label{sec:dnp-master-qualifiers}

The seven-face master theorem in 3d HT carries four standing
qualifiers. Each is recorded here as an honest remark scoping the
master statement; none weakens
Theorem~\ref{thm:vol2-seven-faces-master} or
Proposition~\ref{prop:seven-face-sasaki-commutativity} on the common
locus, but each pins the precise content under examination.

\begin{remark}[Associator dichotomy on the Sasaki diagram]
\label{rem:dnp-master-associator-dichotomy}
Proposition~\ref{prop:seven-face-sasaki-commutativity} establishes
strict commutativity of the seven-face groupoid on the common
locus $\cL$, with cocycle-freeness following from the
$\GRT^{\mathrm{fin}}$ collapse of the
$\GRT_1(\bQ)$-torsor at the genus-zero binary datum. At the
\emph{cochain} level, however, each face-to-face transport
$\phi_{ij}$ is associator-dependent: fixing a Drinfeld
associator $\Phi\in \GRT_1(\bQ)$ at face $F_i$ produces a strict
representative $F_i^{\Phi}$ whose composition with $F_j^{\Phi}$ is
strict only because the same $\Phi$ is fixed throughout the
diagram. The cohomological face commutativity (which the
proposition proves) is associator-INDEPENDENT;
the cochain-level face commutativity is associator-dependent
and lives in the $\GRT_1(\bQ)$-torsor of
Remark~\ref{rem:grt-torsor-3d-ht}.
\end{remark}

\begin{remark}[$\cA^{!}_{\mathrm{line}}$ is an
$\SCchtop^{\,!}$-algebra, not an $\SCchtop$-algebra]
\label{rem:dnp-master-koszul-dual-operad}
Face F2 of Theorem~\ref{thm:vol2-seven-faces-master} identifies the
line operator category $\cC_{\mathrm{line}}$ with
$\cA^{!}_{\mathrm{line}}$-modules, where $\cA^{!}_{\mathrm{line}}$ is
the boundary Koszul dual produced by the chiral bar-cobar adjunction.
The object $\cA^{!}_{\mathrm{line}}$ is an algebra over the
\emph{Koszul-dual} operad
$(\SCchtop)^{!} \simeq (\Lie, \Ass, \text{shuffle-mixed})$, which is
\emph{not} self-dual to $\SCchtop$. The bona fide $\SCchtop$-datum of
the 3d HT slab is the pair
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA), \cA)$ -- bulk acting on
boundary -- not the boundary $\cA^{!}_{\mathrm{line}}$ alone. The DNP
identification of F2 is therefore the identification of
$\cC_{\mathrm{line}}$ with modules over an algebra in the Koszul-dual
operad, not modules over an $\SCchtop$-algebra in disguise.
\end{remark}

\begin{remark}[Concrete vs.\ abstract construction across the nine
specialisation fibres]
\label{rem:dnp-master-concrete-vs-abstract}
The seven-face master statement
Theorem~\ref{thm:vol2-seven-faces-master} is proved on the common
chirally Koszul comparison locus with the F2 type and chain-level
qualifiers above. It is not an abstract theorem for every
$\SCchtop$-algebra in the standard 3d HT landscape. The \emph{concrete}
verification of all seven face-to-$r(z)$ identifications, with
explicit generators and relations matching standard literature
presentations, is presently complete for two anchor cases:
$\fsl_{2}$-Yangian (rational limit) and affine Kac--Moody $V_k(\fg)$
at non-critical level. The remaining seven fibres of the unified
chiral quantum group are concrete only on the evaluation-generated
core; the elliptic case is \emph{partial} (KZB connection
constructed, classical $r$-matrix identified, full quantum-$R$
quasi-triangularity at finite $\hbar$ open); the toroidal case is
\emph{absent} from the present statement and recorded only at the
formal-disk level (Schiffmann--Vasserot CoHA, Miki). See
Remark~\ref{rem:concrete-vs-abstract-scope} of
the unified-chiral-quantum-group chapter.
\end{remark}

\begin{remark}[Slab is a bimodule, not a Swiss-cheese disk]
\label{rem:dnp-master-slab-bimodule}
The Dimofte $D|T|N$ slab, into which all seven faces of $r(z)$ are
threaded as boundary or line-operator data, is a \emph{bimodule}
over a pair of boundary chiral algebras $(\cA_{\mathrm{L}},
\cA_{\mathrm{R}})$, \emph{not} a Swiss-cheese disk with a single
boundary component. The bulk $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$
acts on both boundaries, and the slab fiber functor of Dimofte
$D|T|N$ computes the relative bar
$B(\cA_{\mathrm{L}}, \cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),
\cA_{\mathrm{R}})$ through the bimodule. The seven faces of $r(z)$
arise on the diagonal $\cA_{\mathrm{L}} = \cA_{\mathrm{R}} = \cA$
(self-bimodule case), where the relative bar collapses to
$B(\cA)\otimes_{\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)} B(\cA)$ and
the binary collision residue
$r(z) = \Res^{\coll}_{0,2}(\Theta_{\cA})$ extracts the
diagonal-bimodule $r$-matrix. Off-diagonal slabs (with distinct
$\cA_{\mathrm{L}} \neq \cA_{\mathrm{R}}$) carry an $r$-matrix in
$\cA_{\mathrm{L}}^{!} \otimes \cA_{\mathrm{R}}^{!}[\![z^{-1}]\!]$
that mediates the categorified bimodule structure; this is the
honest 3d HT setting for the seven faces and is the natural ambient
for the universal-holography master theorem.
\end{remark}

\begin{remark}[Cross-references to the climax]
\label{rem:dnp-master-climax-anchors}
The seven-face master Theorem~\ref{thm:vol2-seven-faces-master}
sits at the bar-intrinsic apex of three reconstitution anchors:
\begin{itemize}
\item[(a)] \emph{Universal holography master.} On the chosen
  boundary-linear / physics-bridge prefactorization locus, the
  seven-face master is the F1 face of the universal-holography functor
  $\Phi_{\mathrm{hol}}\colon \cA \mapsto T_{\cA}$
  (Theorem~\ref{thm:universal-holography-master}):
  $r(z) = \Res^{\coll}_{0,2}(\Theta_{\cA})$ is the boundary-to-bulk
  obstruction class on the slab bimodule of
  Remark~\ref{rem:dnp-master-slab-bimodule}, restricted to the
  diagonal $\cA = \cA_{\mathrm{L}} = \cA_{\mathrm{R}}$. The five
  rung corollaries (Corollaries~\ref{cor:rung-heisenberg},
  \ref{cor:rung-affine-km}, \ref{cor:rung-virasoro},
  \ref{cor:rung-w-N}, \ref{cor:rung-w-infty}) produce the
  corresponding seven-face data at each rung of the
  $E_n$-topologisation ladder.
\item[(b)] \emph{Universal conductor.} The Volume~I
  universal-conductor theorem computes the ghost-charge
  $K = c + c^{!}$ across the unified family; specialised to F1 of
  the present master, the conductor produces the canonical
  Casimir-rescaling-invariant scalar that pins the absolute
  normalisation of $r(z)$ on each $\GRT^{\mathrm{fin}}$-orbit. The
  conductor formula is the $\GRT^{\mathrm{fin}}$-invariant shadow of
  F1.
\item[(c)] \emph{Volume~III $\Phi$ functor.} The Volume~III
  CY-to-chiral functor $\Phi$ produces seven-face data at every CY
  target; K3 (via $\Phi(\mathrm{D^{b}Coh}(K3)) = Y(\fgl(4|20))$, the
  K3 super-Yangian, scope $n=2$); $\bC^{3}$ (via affine Yangian
  $\Yhbar(\widehat{\fgl_{\infty}})$ as F5 of the
  Schiffmann--Vasserot CoHA $r$-matrix); toric CY${}_{3}$ (via the
  Maulik--Okounkov $r$-matrix as F4, scope $n=1$). The Volume~III
  master concordance carries the corresponding seven-face data at
  each $\Phi$-target.
\end{itemize}
\end{remark}
