
The bar complex looks like a Feynman expansion. The differential
is a sum over trees weighted by propagators $\eta_{ij} = d\log(z_i - z_j)$,
the degree counts vertices, and iterated residues on
Fulton--MacPherson boundary strata play the role of UV divergences.
The similarity is striking enough to demand an answer: is the bar
complex a literal reformulation of perturbative QFT, or only a
structural analogy?

The honest answer distinguishes two regimes. For the Heisenberg
algebra $\mathcal{H}_{\kappa^{\mathrm{Heis}}}$, the bar complex
reproduces the free-boson residue calculus exactly, and
Conjecture~\ref{conj:bar-cobar-path-integral-heisenberg} records the
expected all-genera path-integral identification. For interacting
theories, Volume~I proves only the
genus-$0$ algebraic BRST/bar comparison on the Kac--Moody locus and
the local binary/ternary reduction package; the general perturbative
comparison remains conjectural
\textup{(}Conjecture~\ref{conj:bar-cobar-path-integral}\textup{)}.
The Feynman--bar mnemonic (Remark~\ref{rem:feynman-bar-bridge})
identifies propagator $= \eta_{ij}$, vertex $=$ collision residue,
and UV divergence $=$ FM boundary stratum; it does \emph{not}
establish a general equality between perturbative complexes and the
bar complex, nor a literal loop$=$genus identity. What the
mnemonic does establish is a canonical bijection between bar
differential terms and tree-level stable graphs: the Feynman
transform of the commutative modular operad decomposes $\Theta_\cA$
as a stable-graph sum, and the free boson case is verified at each
genus below. The gap between analogy and equivalence is the gap
between the Gaussian base case and the nonlinear locus; closing it
is the content of the seven faces of the collision residue.

\begin{construction}[Feynman transform as stable-graph MC decomposition]
\label{constr:feynman-stable-graph}
\index{Feynman transform!stable-graph decomposition|textbf}
\index{stable graph!MC decomposition|textbf}
\index{MC element!stable-graph sum}
The Feynman transform $\mathrm{FT}(\mathrm{FCom})$ of the commutative modular operad decomposes the MC element $\Theta_\cA$ as a stable-graph sum:
\[
\Theta_\cA^{(g,n)} = \sum_{\Gamma \in \mathsf{Gr}^{\mathrm{st}}_{g,n}} \frac{1}{|\mathrm{Aut}(\Gamma)|} \cdot W_\Gamma(\cA),
\]
where $W_\Gamma(\cA)$ is the $\Gamma$-amplitude (Construction~\ref{V1-constr:stable-graph-decomposition}). Feynman diagrams in physical QFT are the genus-$0$ tree-level truncation of this sum; loop corrections are the higher-genus contributions. The MC equation $D\Theta + \tfrac{1}{2}[\Theta,\Theta] = 0$ is the codimension-$2$ face cancellation in $\overline{\mathcal{M}}_{g,n}$ (Remark~\ref{V1-rem:mc-codimension-two}).
\end{construction}

\section{The free boson at genus~\texorpdfstring{$0$}{0}}

The Heisenberg vertex algebra $\mathcal{H}_{\kappa^{\mathrm{Heis}}}$ has OPE
$a(z)\,a(w) \sim \kappa^{\mathrm{Heis}}\,(z-w)^{-2}$. The Feynman rules are:
propagator $G(z,w) = \kappa^{\mathrm{Heis}}/(z-w)^2$; no vertices (free theory);
each insertion of $a(z_i)$ is an external leg.

\begin{center}
\begin{tikzpicture}
\node at (0,0) {$z_1$};
\node at (3,0) {$z_2$};
\draw[thick] (0.3,0) -- (2.7,0);
\node at (1.5, 0.3) {$\frac{\kappa^{\mathrm{Heis}}}{(z_1-z_2)^2}$};
\end{tikzpicture}
\end{center}

The genus-$0$ bar complex is
$\bar{B}^{(0)}_n = \int_{C_n(\mathbb{P}^1)} \omega \otimes a(z_1) \otimes \cdots \otimes a(z_n)$,
with differential computing tree-level factorization.
The bar differential uses the logarithmic propagator
$\eta_{12} = d\log(z_1 - z_2)$, which is the unique conformally invariant
1-form with a simple pole along the diagonal (Remark~\ref{V1-rem:why-log-forced}).
It does \emph{not} combine multiplicatively with the OPE propagator
$G(z_1,z_2)=\kappa^{\mathrm{Heis}}(z_1-z_2)^{-2}$; the two objects play distinct roles.
The bar differential acts by residue extraction via $\eta_{12}$:
\begin{equation}
d^{(0)}[a \otimes a \otimes \eta_{12}]
= \operatorname{Res}_{D_{12}}\bigl(\eta_{12} \cdot a(z_1)\,a(z_2)\bigr)
= \kappa^{\mathrm{Heis}} \cdot \mathbf{1},
\end{equation}
where the residue is $\kappa^{\mathrm{Heis}}$ because $a(z_1)a(z_2) \sim \kappa^{\mathrm{Heis}}(z_1-z_2)^{-2}$
and $\eta_{12} = d\log(z_1-z_2)$ absorbs one pole order, leaving a simple pole
whose residue is $\kappa^{\mathrm{Heis}}$
(Example~\ref{V1-ex:ope-to-residue} and Proposition~\ref{V1-prop:pole-decomposition}).
The QFT propagator $G(z,w)=\kappa^{\mathrm{Heis}}/(z-w)^2$ is a separate bookkeeping device
for Wick contractions; it does not enter the bar differential.

\section{The free boson at genus~\texorpdfstring{$1$}{1}}

The tadpole diagram (self-contraction on an elliptic curve
$E_\tau = \mathbb{C}/(\mathbb{Z} + \tau\mathbb{Z})$) gives:
\begin{equation}
A_{\text{tadpole}}^{(E_\tau)} = \kappa^{\mathrm{Heis}} \sideset{}{'}\sum_{(n,m) \in \mathbb{Z}^2} \frac{1}{(n + m\tau)^2}
= \kappa^{\mathrm{Heis}} \cdot E_2(\tau),
\end{equation}
up to normalization. The modular anomaly
$E_2(-1/\tau) = \tau^2 E_2(\tau) + 6\tau/(\pi i)$
is the one-loop quantum correction to modularity, proportional
to~$\kappa^{\mathrm{Heis}}$.

\begin{center}
\begin{tikzpicture}[scale=1.2]
\node at (0,0) {$\bullet$};
\draw[thick] (0,0) arc (180:540:0.5);
\node at (0.5, -1.2) {tadpole};
\end{tikzpicture}
\end{center}

The tadpole corresponds to $[\text{Tr}(a \otimes a)]^{(1)} \in \bar{B}^{(1)}_1$,
with $d^{(0)}[\text{Tr}(a \otimes a)]^{(1)} = \kappa^{\mathrm{Heis}} \cdot [1]^{(1)}$.

\subsection{Loop-genus correspondence}

\begin{theorem}[Loop-genus correspondence; \ClaimStatusProvedElsewhere{} \cite{costello-renormalization}]
\label{thm:loop-genus-correspondence}
A connected Feynman diagram $\Gamma$ with $V$ vertices, $E$ edges,
and $F$ faces has loop number $L = E - V + 1$. The genus of the
ribbon graph satisfies
$\chi = V - E + F = 2 - 2g$, hence $g = (L + 1 - F)/2 \leq L/2$,
with equality when $F = 1$.
\end{theorem}

The free boson correlation function expands as
$\langle a(z_1) \cdots a(z_n) \rangle_{\text{all genera}}
= \sum_{g=0}^\infty (\kappa^{\mathrm{Heis}})^{n/2+g-1}
\langle a(z_1) \cdots a(z_n) \rangle^{(g)}_{\text{conn.}}$,
and the bar filtration weights genus~$g$ by $(\kappa^{\mathrm{Heis}})^g$.

\section{One-loop partition function}

The Gaussian path integral on $E_\tau$ gives
$Z_{E_\tau} = (\mathrm{Im}\,\tau)^{-1/2} |\eta(\tau)|^{-2}$,
which is modular invariant as a density on
$\mathcal{M}_{1,0}$. The bar complex interpretation:
$Z_{E_\tau} = H_0(\bar{B}^{(1)})$; the modular anomaly
is the scalar trace
$\kappa(\cA)\cdot\deg(\lambda_1) = \kappa(\cA)/24$
(Theorems~\ref{thm:genus-universality}
and~\ref{thm:explicit-theta}).

\section{Path integral = bar complex}

\begin{conjecture}[Bar complex = path integral for the free boson; \ClaimStatusConjectured]\label{conj:bar-cobar-path-integral-heisenberg}
For the Heisenberg vertex algebra $\mathcal{H}_{\kappa^{\mathrm{Heis}}}$
\textup{(}free boson at nonzero Heisenberg level\textup{)} on a
compact Riemann surface $\Sigma_g$ of genus~$g \geq 0$:
\begin{equation}\label{eq:bar-partition-heisenberg}
Z_g^{\mathcal{H}_{\kappa^{\mathrm{Heis}}}}(\Sigma_g)
= H^0(\bar{B}^{(g)}(\mathcal{H}_{\kappa^{\mathrm{Heis}}})) = \mathbb{C}
\end{equation}
\begin{equation}\label{eq:bar-npoint-heisenberg}
\langle \alpha(z_1) \cdots \alpha(z_n) \rangle_{\Sigma_g}
= H^n(\bar{B}^{(g)}(\mathcal{H}_{\kappa^{\mathrm{Heis}}}))
/ H^0(\bar{B}^{(g)}(\mathcal{H}_{\kappa^{\mathrm{Heis}}}))
\end{equation}
\end{conjecture}

\begin{remark}[Evidence]
\emph{Step~1: Bar complex cohomology.}
By Theorem~\ref{V1-thm:heisenberg-higher-genus}, the bar complex
cohomology of $\mathcal{H}_{\kappa^{\mathrm{Heis}}}$ on~$\Sigma_g$ is:
\[
H^n(\bar{B}^{(g)}(\mathcal{H}_{\kappa^{\mathrm{Heis}}})) = \begin{cases}
\mathbb{C} & n = 0, \\
\mathbb{C}^{2g} & n = 1, \\
\mathbb{C} \oplus \mathbb{C} \cdot c_{\kappa^{\mathrm{Heis}}}^{(g)} & n = 2, \\
0 & n > 2.
\end{cases}
\]

\emph{Step~2: Free boson path integral.}
The path integral is Gaussian with normalized partition function
$Z_g = 1$ (zero-mode volume removed), matching
$H^0 = \mathbb{C}$. By Wick's theorem:
$H^1 \cong H^1(\Sigma_g, \mathbb{C})$ (zero modes);
the $2$-point function has residue $\kappa^{\mathrm{Heis}}$ matching the bar
differential; $H^n = 0$ for $n > 2$ (free theory).

\emph{Step~3: Factorization homology.}
By Theorem~\ref{V1-thm:verdier-AF-compat},
$H^*(\bar{B}^{(g)}(\mathcal{H}_{\kappa^{\mathrm{Heis}}}))$ computes the
factorization homology $\int_{\Sigma_g}\mathcal{H}_{\kappa^{\mathrm{Heis}}}$,
which for the free boson equals the Gaussian BV
cohomology~\cite{CG17}.
\end{remark}

\begin{conjecture}[Bar-cobar as worldsheet path integral: general case; \ClaimStatusConjectured]\label{conj:bar-cobar-path-integral}
For a general chiral algebra $\cA$ on $\Sigma_g$, the generating functional of correlation functions is classified by the bar complex:
\begin{equation}
\exp\left( \sum_{g,n} \frac{1}{n!} \int_{C_n(\Sigma_g)} \langle a(z_1) \cdots a(z_n) \rangle_g \right) = \det(\mathbf{1} + \bar{B}(\cA))
\end{equation}
where the right side is the Fredholm determinant of the bar complex.
Evidence is strongest for $\mathcal{H}_{\kappa^{\mathrm{Heis}}}$ at all genera
\textup{(}Conjecture~\textup{\ref{conj:bar-cobar-path-integral-heisenberg})};
conjectural for interacting $\cA$.
Contributing to Conjecture~\ref{conj:v1-master-bv-brst}.
\end{conjecture}

\begin{remark}[Shadow depth decomposition in the Feynman picture]
\label{rem:feynman-depth-decomposition}
The loop-genus correspondence (Theorem~\ref{thm:loop-genus-correspondence})
underlies the depth decomposition $d = 1 + d_{\mathrm{arith}} + d_{\mathrm{alg}}$
of Theorem~\ref{V1-thm:depth-decomposition} (Chapter~\ref{V1-chap:arithmetic-shadows}):
$d_{\mathrm{arith}}$ counts critical lines of the spectral $L$-function
(Feynman-integral periods) and $d_{\mathrm{alg}}$ records the OPE vertex
complexity visible as higher-loop skeleton subdivergences.
\end{remark}

\begin{remark}[Scope of the bar-path-integral comparison]\label{rem:bar-path-integral-scope}
Conjecture~\ref{conj:bar-cobar-path-integral-heisenberg} records
the expected bar-complex/path-integral identification for
$\mathcal{H}_{\kappa^{\mathrm{Heis}}}$ at all genera. For interacting chiral algebras $\cA$, only the
genus-$0$ algebraic BRST/bar comparison on the Kac--Moody locus and
the local binary/ternary reduction package are proved in this volume
(Theorem~\ref{thm:brst-bar-genus0}); the all-genera comparison is
Conjecture~\ref{conj:bar-cobar-path-integral}.
\end{remark}
