% label removed: chap:ht-bulk-boundary-line

% Theorem environments inherited from main.tex; local macros only.
\providecommand{\kk}{\mathbb{k}}
\providecommand{\cO}{\mathcal O}
\providecommand{\SCop}{\mathsf{SC}^{\mathrm{ch,top}}}
\providecommand{\gSC}{\mathfrak{g}^{\mathrm{SC}}}
\providecommand{\cC}{\mathcal C}
\providecommand{\cL}{\mathcal L}
\providecommand{\cM}{\mathcal M}
\providecommand{\cJ}{\mathcal J}
\providecommand{\Ainf}{\mathsf{A}_{\infty}}
\providecommand{\Linf}{L_\infty}
\providecommand{\Sym}{\operatorname{Sym}}
\providecommand{\PV}{\operatorname{PV}}
\providecommand{\ot}{\otimes}
\providecommand{\CE}{\operatorname{CE}}
\providecommand{\HH}{\operatorname{HH}}
\providecommand{\RHom}{\operatorname{RHom}}
\providecommand{\BBar}{\operatorname{Bar}}
\providecommand{\Cobar}{\operatorname{\Omega}}
\providecommand{\Spec}{\operatorname{Spec}}
\providecommand{\Spf}{\operatorname{Spf}}

\providecommand{\End}{\operatorname{End}}
\providecommand{\Hom}{\operatorname{Hom}}
\providecommand{\Der}{\operatorname{Der}}
\providecommand{\gr}{\operatorname{gr}}
\providecommand{\im}{\operatorname{im}}
\providecommand{\coker}{\operatorname{coker}}
\providecommand{\id}{\operatorname{id}}
\providecommand{\Perf}{\operatorname{Perf}}
\providecommand{\Cl}{\operatorname{Cl}}
\providecommand{\dCrit}{\operatorname{dCrit}}
\providecommand{\Zder}{\operatorname{Z}_{\mathrm{der}}}
\providecommand{\mc}{\operatorname{MC}}
\providecommand{\op}{\mathrm{op}}
\providecommand{\der}{\mathrm{der}}
\providecommand{\Abulk}{A_{\mathrm{bulk}}}
\providecommand{\Bbound}{B_{\partial}}
\providecommand{\Kline}{K_{\mathrm{line}}}
\providecommand{\intr}{\mathrm{intr}}
\providecommand{\free}{\mathrm{free}}
\providecommand{\eff}{\mathrm{eff}}
\providecommand{\st}{\mathrm{st}}
\providecommand{\ex}{\mathrm{ex}}
\providecommand{\minmod}{\mathrm{min}}
\providecommand{\expmod}{\mathrm{exp}}
\providecommand{\hkR}{\mathrm{HKR}}
\providecommand{\sn}{\mathrm{SN}}
\providecommand{\lines}{\mathsf{Lines}}
\providecommand{\hSym}{\widehat{\Sym}}


\section{The bulk-boundary-line Koszul triangle}
% label removed: sec:ht-bulk-boundary-line

A chosen three-dimensional holomorphic--topological prefactorization
realization on
$\C \times \R$ produces three algebraic objects: bulk local
operators (the 3d HT bulk of T18(iii), whose observables are
T18(i) chiral derived centre $Z^{\mathrm{der}}_{\mathrm{ch}}$ of the
boundary algebra), boundary local operators, and line operators. The
naive identification ``bulk $\simeq$ boundary $\simeq$ line'' is
false. The corrected triangle is proved formally under compact
generation, the bulk-boundary quasi-isomorphism, and the line-module
presentation, and rigorously on the boundary-linear exact sector; the
unrestricted all-theory global triangle is a separate frontier problem:
\begin{equation}% label removed: eq:global-corrected-triangle
\Abulk
\;\simeq\;
\Zder(\Bbound)
\;\simeq\;
\Zder(\cC_{\mathrm{line}})
\;\simeq\;
\HH^\bullet_{\mathrm{ch}}(A^!_{\mathrm{line}}),
\qquad
\cC_{\mathrm{line}}\simeq A^!_{\mathrm{line}}\text{-mod}.
\end{equation}
The bulk is the \emph{derived center} of the boundary, not the
boundary itself; on the scoped perturbative loci the completed line
category is modeled by modules for the open-colour Koszul
dual~$A^!_{\mathrm{line}}$, not for the bulk algebra. This is the 3d
holomorphic--topological analogue of the strongest open/closed
statements in 2d TFT and the B-model.

Three principles guide the constructions that follow: (P1)~intrinsic
formulations before complement-dependent presentations;
(P2)~derived or $A_\infty$ models before cohomology-level data;
(P3)~local exact theorems before global categorical comparisons.

\begin{remark}[All three vertices are homotopy objects first]
% label removed: rem:triangle-homotopy-first
\index{bulk-boundary-line!homotopy first}
Each vertex of the corrected triangle is represented in practice by a
chosen strict model (a dg or chiral algebra, an $A_\infty$ boundary
algebra, or a dg category of modules), but the triangle itself is
invariant only up to derived/Morita and $L_\infty$ equivalence. This
is exactly why higher operations from \cite{GKW24} and the line-operator
$A_\infty$ package of \cite{DNP25} fit naturally into the same bulk--
boundary--line story
(Convention~\ref{conv:vol2-strict-models}).
\end{remark}

\begin{remark}[Two-color refinement of the triangle]
% label removed: rem:triangle-two-colors
\index{bulk-boundary-line!two-color refinement}
The corrected triangle admits a two-color refinement on the exact
comparison surface. Closed-color Koszul duality identifies the bulk
only after the bulk/Hochschild comparison hypotheses:
$A_{\mathrm{bulk}} \simeq \mathrm{ChirHoch}^\ast(\cA^!_{\mathrm{line}})$
(Theorem~\ref{thm:bulk_hochschild}).
Open-color Koszul duality models the completed line category:
$\mathcal{C}_{\mathrm{line}} \simeq \cA^!_{\mathrm{line}}\text{-mod}$
(Theorem~\ref{thm:lines_as_modules}).
The $R$-matrix lives in the interaction of both colors:
it is a mixed-color datum in the holomorphic weight
filtration on $\SCchtop$ (Theorem~\ref{thm:spectral-parameter-from-closed-color}).
The triangle is the statement that $\cA^!_{\mathrm{line}}$ carries a full
$(\SCchtop)^{!}$-algebra structure (closed $=$ Lie, open $=$ Ass)
(Theorem~\ref{thm:dual-sc-algebra}), from which all three
vertices and all connecting maps are recovered.
\end{remark}

\section{Literature backbone and formal consequences}% label removed: sec:backbone

The foundational inputs split into four cited constructions and two
chain-level comparison problems.

\subsection{What is already in the literature}

Costello--Dimofte--Gaiotto \cite{CDG20} construct the cohomology-level bulk algebra, its shifted Poisson bracket, and the bulk action on boundary operators. Zeng \cite{Zeng23} identifies boundary chiral algebras with universal defect algebras in families of examples, giving strong evidence for the bulk/boundary comparison. Gaiotto--Kulp--Wu \cite{GKW24} supply the perturbative technology for higher operations and prove the quadratic identities they satisfy. Dimofte--Niu--Py \cite{DNP25} identify line operators with modules over a Koszul-dual $A_\infty$ algebra and construct the dg-shifted-Yangian structures organizing their OPE.

These four inputs are the literature backbone for the bulk--boundary--line
triangle.

\subsection{Formal consequences}

Once one has:
\begin{enumerate}[label=(\roman*),leftmargin=1.8em]
\item a rich boundary condition $b$ whose boundary algebra $B_b$ generates the line category;
\item an equivalence $\cC_{\mathrm{line}}\simeq B_b\text{-mod}$ or, more invariantly, a compact generator $M_b\in \cC_{\mathrm{line}}$ with $B_b\simeq \End_{\cC_{\mathrm{line}}}(M_b)$;
\item and a quasi-isomorphism $\beta_{\der}:\Abulk\to \Zder(B_b)$,
\end{enumerate}
the global triangle \eqref{eq:global-corrected-triangle} becomes formal: centers are Morita invariant, so $\Zder(B_b)\simeq \Zder(\cC_{\mathrm{line}})$; if $\cC_{\mathrm{line}}\simeq A^!_{\mathrm{line}}\text{-mod}$, then $\Zder(\cC_{\mathrm{line}})\simeq \HH^\bullet_{\mathrm{ch}}(A^!_{\mathrm{line}})$.

This is the formal theorem that closes the triangle after the stated
compact-generation, line-module, and derived-centre inputs have been
constructed. The boundary-linear exact sector supplies those inputs;
the unrestricted global theory still requires the corresponding
chain-level comparisons.

\begin{proposition}[Formal reduction of the global triangle; \ClaimStatusProvedHere]% label removed: prop:formal-global-triangle
Assume there is a boundary condition $b$ such that:
\begin{enumerate}[label=(\roman*),leftmargin=1.8em]
\item $b$ defines a compact generator $M_b$ of the line category $\cC_{\mathrm{line}}$;
\item $B_b:=\End_{\cC_{\mathrm{line}}}(M_b)$ is a model for the boundary open sector;
\item the derived bulk--boundary map $\beta_{\der}:\Abulk\to \Zder(B_b)$ is a quasi-isomorphism;
\item $\cC_{\mathrm{line}}\simeq A^!_{\mathrm{line}}\text{-mod}$ for an open-colour Koszul-dual $A_\infty$ algebra $A^!_{\mathrm{line}}$.
\end{enumerate}
Then there are canonical quasi-isomorphisms
\[
\Abulk
\;\simeq\;
\Zder(B_b)
\;\simeq\;
\Zder(\cC_{\mathrm{line}})
\;\simeq\;
\HH^\bullet_{\mathrm{ch}}(A^!_{\mathrm{line}}).
\]
\end{proposition}

\begin{proof}
The first equivalence is hypothesis (iii). Since $M_b$ is a compact generator, $\cC_{\mathrm{line}}$ is derived Morita equivalent to $B_b\text{-mod}$. Derived centers are Morita invariant, giving $\Zder(B_b)\simeq \Zder(\cC_{\mathrm{line}})$. Hypothesis (iv) identifies $\cC_{\mathrm{line}}$ with $A^!_{\mathrm{line}}\text{-mod}$, and the derived center of the module category is chiral Hochschild cochains of $A^!_{\mathrm{line}}$.
\end{proof}

\subsection{What is new in this manuscript}

The novelty lies elsewhere: we strengthen the microlocal algebraic core. Inside an exact local sector, the boundary, line, and bulk vertices admit explicit constructions and proved comparisons.

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{longtable}{|p{0.24\textwidth}|p{0.23\textwidth}|p{0.43\textwidth}|}
\hline
\textbf{Layer} & \textbf{Status} & \textbf{Content} \\
\hline
Bulk shifted Poisson/chiral algebra; boundary module structure & literature & Costello--Dimofte--Gaiotto \cite{CDG20}. \\
\hline
Higher perturbative operations and quadratic identities & literature & Gaiotto--Kulp--Wu \cite{GKW24}. \\
\hline
Universal defect evidence for the bulk/boundary comparison & literature & Zeng \cite{Zeng23}. \\
\hline
Line category as modules over $A^!$; dg-shifted Yangian package & literature & Dimofte--Niu--Py \cite{DNP25}. \\
\hline
Formal implication ``rich boundary + bulk/boundary comparison $\Rightarrow$ corrected triangle'' & formal & Proposition~\ref{prop:formal-global-triangle}. \\
\hline
Intrinsic boundary $A_\infty$ algebra from normal Taylor classes & new, proved here & Theorem~\ref{thm:intrinsic-boundary}. \\
\hline
Boundary Thom--Sebastiani and stabilization calculus & new, proved here & Theorems~\ref{thm:TS}, \ref{thm:contractible-stab}, \ref{thm:clifford-stab}, \ref{thm:relative-morse}. \\
\hline
Boundary-linear LG theorem: bulk $=$ shifted cotangent of the derived boundary zero locus & new, proved here & Theorems~\ref{thm:dcrit-shiftedcot}, \ref{thm:boundary-linear-bulk-boundary}. \\
\hline
One-step Jacobi coalgebra and exact pointed line algebra & new, proved here & Theorems~\ref{thm:exact-line}, \ref{thm:mc-vacua}, \ref{thm:polarized-reconstruction}. \\
\hline
Boundary Kuranishi elimination and minimal line algebra & new, proved here & Theorems~\ref{thm:boundary-kuranishi}, \ref{thm:minimal-pointed-line}. \\
\hline
Boundary-linear line Mather--Yau theorem and microlocal classification & new, proved here & Theorem~\ref{thm:line-mather-yau}. \\
\hline
All-theory global Koszul triangle & conjectural & See Section~\ref{sec:global}. \\
\hline
\end{longtable}
\end{center}


\section{First principles: locality, centers, and the correct shape of open/closed/line structures}% label removed: sec:first-principles

The boundary and line sectors do not stand beside the bulk as parallel commutative algebras. They sit one categorical level lower. The local operator algebra is bulk. The algebra of endomorphisms of a boundary vacuum or of a line defect is an open-sector presentation. The bridge from open data back to bulk data is the derived center.

This principle predates the present subject. In 2d open/closed TFT and the B-model, the closed sector is the derived center of the open sector. In representation theory, centers arise not by forgetting categories to algebras but by passing from convolution algebras to inertia geometry. The same architecture governs here.

\subsection{Why centers must appear}

Let $\cC$ be a dg or $A_\infty$ category representing a line sector. Its center is not a subalgebra of a chosen endomorphism algebra but the derived endomorphism algebra of the identity functor. If $\cC\simeq A\text{-mod}$, then the center of $\cC$ is Hochschild cochains of $A$:
\[
\Zder(\cC)\simeq \RHom_{\operatorname{Fun}(\cC,\cC)}(\id_{\cC},\id_{\cC})\simeq \HH^\bullet(A).
\]
This is the precise sense in which bulk can be the center of the line sector while lines themselves are controlled by a noncommutative algebra.

\subsection{Why Morita invariance matters}

If a rich boundary condition $b$ generates the line category, then $B_b=\End(M_b)$ is only a presentation: different generators yield different algebras but equivalent module categories. Bulk reconstruction cannot depend on the presentation. Derived center and Hochschild cochains are the correct invariants because they are Morita invariant.

\subsection{Why the exact local sector is decisive}

A global theorem comparing bulk, boundary, and line categories in every holomorphic--topological theory is too large to attack head-on. One needs a local exact sector where the objects admit literal formulas. The boundary-linear Landau--Ginzburg sector plays that role. In that sector:
\begin{itemize}[leftmargin=1.8em]
\item the boundary algebra is an explicit commutative dg algebra;
\item the local pointed line algebra is an explicit $A_\infty$ algebra;
\item the derived center can be computed directly;
\item Kuranishi elimination is exact rather than merely homotopy-theoretic.
\end{itemize}
What follows is the construction of that exact local backbone.


\section{Intrinsic boundary $A_\infty$ algebra from first principles}% label removed: sec:intrinsic

Let $V$ be a finite-dimensional vector space, let $L\subset V$ be a linear subspace, and let
\[
Q:=V/L.
\]
Let $I_L\subset \hSym(V^\vee)$ denote the ideal of functions vanishing on $L$, so the completed formal neighborhood of $L$ in $V$ is
\[
\widehat{V}_L:=\Spf\bigl(\hSym(V^\vee)^\wedge_{I_L}\bigr).
\]
Assume $W\in \hSym(V^\vee)^\wedge_{I_L}$ vanishes on $L$, equivalently $W\in I_L$.

The aim is to define a boundary $A_\infty$ algebra depending only on the formal germ of $W$ along $L$, with no choice of complement.

\subsection{Intrinsic normal Taylor classes}

The normal Taylor coefficients of $W$ along $L$ are the classes
\[
\tau_n(W)\in I_L^n/I_L^{n+1}\cong \widehat{\cO}(L)\ot \Sym^n(Q^\vee),
\qquad n\ge 1.
\]
Thus $W$ determines and is determined by the sequence $\{\tau_n(W)\}_{n\ge 1}$.

Choose, only locally for writing formulas, a splitting $V=L\oplus N$. Then $Q\cong N$ and we may write
\[
W(x,y)=\sum_{n\ge 1} W_n(x;y),
\qquad
W_n(x;\lambda y)=\lambda^n W_n(x;y).
\]
Then $\tau_n(W)$ is exactly the class of $W_n(x;y)$.

\subsection{The underlying graded algebra}

Set
\[
B^{\intr,\gr}_{L,W}:=\widehat{\cO}(L)\ot \Lambda(Q),
\]
where the copy of $Q$ sits in cohomological degree $1$. If $q_1,\dots,q_r$ is a basis of $Q$ and $\psi_1,\dots,\psi_r$ the corresponding degree-$1$ generators, then $B^{\intr,\gr}_{L,W}$ is the free completed graded-commutative algebra on $\widehat{\cO}(L)$ and the odd variables $\psi_a$.

The intrinsic Taylor classes of $W$ will produce higher multiderivations on this free algebra.

\subsection{From Taylor classes to multiderivations}

Fix a splitting temporarily and choose coordinates $x_i$ on $L$ and basis vectors $e_a$ of $Q$. Write
\[
\tau_n(W)=\sum_{a_1,\dots,a_n} f_{a_1\cdots a_n}(x)\, e_{a_1}^\vee\cdots e_{a_n}^\vee.
\]
Define an $n$-ary Hochschild cochain $\mu_n$ on $B^{\intr,\gr}_{L,W}$ by
\begin{equation}% label removed: eq:intrinsic-mu
\mu_n(a_1,\dots,a_n)
:=
\sum_{a_1,\dots,a_n}
f_{a_1\cdots a_n}(x)\,
(\partial_{\psi_{a_1}}a_1)\cdots(\partial_{\psi_{a_n}}a_n).
\end{equation}
Each $\mu_n$ is a multiderivation of the free graded-commutative product.

The collection $\{\mu_n\}_{n\ge 1}$ is not arbitrary: it comes from the single function $W$, hence satisfies the Stasheff system.

\begin{theorem}[Intrinsic boundary $A_\infty$ algebra; \ClaimStatusProvedHere]% label removed: thm:intrinsic-boundary
For every formal pair $(L\subset V,W)$ with $W|_L=0$, the operations
\[
m_1=\mu_1,\qquad
m_2=m_2^{\free}+\mu_2,\qquad
m_n=\mu_n\quad (n\ge 3),
\]
define a complete filtered $A_\infty$ algebra structure on
\[
B^\intr_{L,W}:= \bigl(B^{\intr,\gr}_{L,W},\{m_n\}_{n\ge 1}\bigr).
\]
Its quasi-isomorphism class depends only on the formal germ of $W$ along $L$ and is independent of the chosen complement $V=L\oplus N$.
\end{theorem}

\begin{proof}
The only substantive issue is the Stasheff identities. Since every $\mu_n$ is a multiderivation, the full set of identities is equivalent to the vanishing of the Gerstenhaber bracket of the total Hochschild cochain
\[
\mu:=\sum_{n\ge 1}\mu_n.
\]
Under the Hochschild--Kostant--Rosenberg map, $\mu$ corresponds to the formal odd polyvector field obtained by replacing the normal variables in the Taylor expansion of $W$ by the odd derivations $\partial_{\psi_a}$. Concretely, in split coordinates
\[
\Theta_W:=\sum_{n\ge 1}
\sum_{a_1,\dots,a_n}
f_{a_1\cdots a_n}(x)\,
\partial_{\psi_{a_1}}\wedge\cdots\wedge \partial_{\psi_{a_n}}.
\]
Because the coefficients $f_{a_1\cdots a_n}(x)$ depend only on tangent coordinates and the odd derivations $\partial_{\psi_a}$ supercommute, one has
\[
[\Theta_W,\Theta_W]_{\sn}=0.
\]
Transporting back through HKR gives $[\mu,\mu]_G=0$. Since $m_2^{\free}$ is associative and each $\mu_n$ is a multiderivation for $m_2^{\free}$, one also has
\[
[m_2^{\free},\mu]_G=0,
\qquad
[m_2^{\free},m_2^{\free}]_G=0.
\]
Hence the total coderivation squares to zero.

If one changes the complement $N$, the intrinsic Taylor classes $\tau_n(W)$ do not change, so the resulting $A_\infty$ structures are identified after transporting along the induced algebra isomorphism. Therefore the quasi-isomorphism class depends only on the formal germ.
\end{proof}

\begin{corollary}[Formal-neighborhood invariance; \ClaimStatusProvedHere]% label removed: cor:formal-neighborhood
If two pairs $(L\subset V,W)$ and $(L'\subset V',W')$ have isomorphic formal neighborhoods carrying $W$ to $W'$, then their intrinsic boundary $A_\infty$ algebras are $A_\infty$-isomorphic.
\end{corollary}

\begin{proof}
An isomorphism of formal neighborhoods identifies the ideals $I_L/I_L^{n+1}$ with $I_{L'}/I_{L'}^{n+1}$ and therefore identifies the Taylor classes $\tau_n(W)$ and $\tau_n(W')$. Formula \eqref{eq:intrinsic-mu} then produces the same higher operations.
\end{proof}

\begin{corollary}[Boundary-linear strictness; \ClaimStatusProvedHere]% label removed: cor:boundary-linear-strict
If all Taylor classes $\tau_n(W)$ vanish for $n\ge 2$, equivalently if $W$ is linear in the normal directions, then $B^\intr_{L,W}$ is a strict commutative dg algebra.
\end{corollary}

\begin{proof}
In that case only $\mu_1$ survives, so $m_n=0$ for $n\ge 3$ and the only deformation of the free product is the differential $m_1$.
\end{proof}

\begin{remark}
This corollary is the gateway to the exact local sector treated later. The boundary-linear Landau--Ginzburg models are exactly the models in which the intrinsic $A_\infty$ boundary algebra collapses to a strict dg algebra, making exact computation possible.
\end{remark}


\section{Multiplicativity and stabilization: Thom--Sebastiani, contractible blocks, and Clifford blocks}% label removed: sec:ts-knorrer

The intrinsic boundary construction should behave like a stable algebraic object. Three operations test this stability: external sums, tangent-normal hyperbolic stabilizations, and pure-normal hyperbolic stabilizations.

\subsection{Thom--Sebastiani}

Let $(L_i\subset V_i,W_i)$, $i=1,2$, be two formal pairs with $W_i|_{L_i}=0$. Form
\[
(L_1\oplus L_2 \subset V_1\oplus V_2,\; W_1\boxplus W_2),
\qquad
(W_1\boxplus W_2)(v_1,v_2)=W_1(v_1)+W_2(v_2).
\]

\begin{theorem}[Boundary Thom--Sebastiani; \ClaimStatusProvedHere]% label removed: thm:TS
There is a natural filtered $A_\infty$ isomorphism
\[
B^\intr_{L_1\oplus L_2,\;W_1\boxplus W_2}
\cong
B^\intr_{L_1,W_1}\,\widehat{\otimes}\, B^\intr_{L_2,W_2}.
\]
\end{theorem}

\begin{proof}
The ideal filtration of the product neighborhood splits, and the normal Taylor classes add:
\[
\tau_n(W_1\boxplus W_2)=\tau_n(W_1)\oplus \tau_n(W_2).
\]
Therefore the multiderivations defining the $A_\infty$ structure on the left are exactly the sums of the multiderivations from the two factors, which is the completed tensor product $A_\infty$ structure.
\end{proof}

\subsection{Tangent-normal hyperbolic stabilization}

Suppose $U$ is a finite-dimensional vector space and consider the enlarged data
\[
V':=V\oplus U\oplus U^\vee,
\qquad
L':=L\oplus U,
\qquad
W':=W+\langle u,v\rangle,
\]
where $u\in U$ is tangent to the boundary and $v\in U^\vee$ is normal. Then one leg of the hyperbolic pair is tangent and one leg is normal.

\begin{theorem}[Contractible stabilization; \ClaimStatusProvedHere]% label removed: thm:contractible-stab
With the above notation,
\[
B^\intr_{L',W'}
\cong
B^\intr_{L,W}\,\widehat{\otimes}\,
\bigl(\widehat{\Sym}(U^\vee)\ot \Lambda(U^\vee),\, d\xi=u\bigr),
\]
where the second factor is the ordinary completed Koszul resolution of $\kk$. In particular
\[
B^\intr_{L',W'}\simeq B^\intr_{L,W}
\]
as $A_\infty$ algebras.
\end{theorem}

\begin{proof}
The new potential is the external sum of $W$ and the linear-normal function $\langle u,v\rangle$ on $U\oplus U^\vee$ relative to the boundary $U\subset U\oplus U^\vee$. By Theorem~\ref{thm:TS} it suffices to compute the second factor. But that factor is exactly the strict dg algebra with even variables $u$ and odd variables $\xi$ corresponding to the normal directions, with differential $d\xi=u$. This is contractible.
\end{proof}

\subsection{Pure-normal hyperbolic stabilization}

Now suppose both legs of the hyperbolic pair are normal:
\[
V' := V\oplus U\oplus U^\vee,
\qquad
L' := L,
\qquad
W' := W+\langle u,v\rangle,
\]
where both $u$ and $v$ are normal directions.

\begin{theorem}[Hyperbolic Clifford stabilization; \ClaimStatusProvedHere]% label removed: thm:clifford-stab
There is a natural dg isomorphism
\[
B^\intr_{L,W+\langle u,v\rangle}
\cong
B^\intr_{L,W}\,\widehat{\otimes}\, \Cl(U\oplus U^\vee),
\]
where $\Cl(U\oplus U^\vee)$ denotes the completed hyperbolic Clifford algebra. Consequently
\[
\Perf\bigl(B^\intr_{L,W+\langle u,v\rangle}\bigr)
\simeq
\Perf\bigl(B^\intr_{L,W}\bigr)
\]
after stabilization by the spinor module $\Lambda(U)$.
\end{theorem}

\begin{proof}
In the pure-normal case, the new Taylor data are quadratic and nondegenerate entirely in the normal variables. The intrinsic $A_\infty$ operations contributed by the pair $(u,v)$ assemble into the standard hyperbolic Clifford relation. The resulting factor is exactly $\Cl(U\oplus U^\vee)$. Since this Clifford algebra is Morita equivalent to $\kk$ via the spinor module $\Lambda(U)$, tensoring with it does not change the perfect module category.
\end{proof}

\begin{remark}
This is the boundary-level zero-mode shadow of Kn\"orrer periodicity. What matters is not a periodicity statement in a triangulated category, but the explicit identification of the open-sector factor that is being added: a hyperbolic Clifford block.
\end{remark}

\subsection{Relative formal Morse splitting}

The preceding theorems combine with a formal Morse lemma relative to the boundary.

\begin{theorem}[Relative formal Morse splitting; \ClaimStatusProvedHere]% label removed: thm:relative-morse
Let $V=L\oplus K\oplus U\oplus U^\vee$ and let
\[
W(x,k,u,v)
\]
be a formal potential vanishing on $L$ whose quadratic part in the $(u,v)$ variables is the split hyperbolic form $\langle u,v\rangle$. Assume there are no linear terms in $u$ or $v$ and no mixed quadratic terms between $(u,v)$ and the residual normal directions $K$. Then there is a formal automorphism preserving $L$ and fixing the residual normal directions to first order such that
\[
W \sim W_{\mathrm{red}}(x,k)+\langle u,v\rangle.
\]
Consequently
\[
B^\intr_{L,W}
\simeq
B^\intr_{L,W_{\mathrm{red}}}\,\widehat{\otimes}\,\Cl(U\oplus U^\vee)
\]
in the pure-normal case, and analogously with a contractible Koszul factor in the tangent-normal case.
\end{theorem}

\begin{proof}
The formal automorphism is constructed inductively by degree. Because the quadratic form on $(u,v)$ is split and nondegenerate, the homological operator given by contraction with $\langle u,v\rangle$ is invertible on all higher monomials involving at least one $u$ or $v$. Therefore every higher interaction involving the hyperbolic directions can be killed order by order. The factorization of the boundary algebra then follows from Theorems~\ref{thm:contractible-stab} and \ref{thm:clifford-stab}.
\end{proof}

\begin{remark}
This theorem is the reduction machine behind the later exact sector. It says that split hyperbolic directions are not merely harmless; they are explicitly removable. What remains after their removal is the genuine singular residue.
\end{remark}


\section{The exact boundary-linear Landau--Ginzburg sector}% label removed: sec:boundary-linear

The passage to the exact sector where the intrinsic $A_\infty$ algebra becomes a strict dg algebra and every object can be written explicitly.

Let $V=L\oplus N$ and let
\[
F:L\longrightarrow N^\vee
\]
be a formal map. Define the superpotential
\[
W(x,y):=\langle y, F(x)\rangle,
\qquad
x\in L,\; y\in N.
\]
Then $W$ vanishes on $L$ and is linear in the normal variables $y$.

\subsection{Boundary dg algebra and derived zero locus}

Choose a basis $n_a$ of $N$ and odd generators $\eta_a$ dual to $n_a$. The boundary algebra is the strict commutative dg algebra
\begin{equation}% label removed: eq:boundary-linear-dga
B_{L,W}
:=
\bigl(\widehat{\cO}(L)\ot \Lambda(N),\ d\eta_a=F_a(x),\ dx_i=0\bigr).
\end{equation}
This is the Koszul algebra of the equations $F_a(x)=0$.

\begin{definition}
The derived boundary zero locus of $F$ is
\[
Z_F^{\der}:=\Spec(B_{L,W}).
\]
\end{definition}

\begin{remark}
In ordinary geometry $Z_F$ would be the vanishing locus $F^{-1}(0)\subset L$. The dg algebra $B_{L,W}$ remembers the derived structure and therefore the higher obstruction theory of the equations.
\end{remark}

\subsection{The bulk critical locus as a shifted cotangent}

The bulk derived critical locus of $W$ is the dg scheme cut out by the equations
\[
\frac{\partial W}{\partial y_a}=F_a(x)=0,
\qquad
\frac{\partial W}{\partial x_i}
=
\sum_a y_a\frac{\partial F_a}{\partial x_i}(x)=0.
\]
This is the shifted cotangent to the derived zero locus.

\begin{theorem}[Derived critical locus theorem; \ClaimStatusProvedHere]% label removed: thm:dcrit-shiftedcot
For the boundary-linear superpotential $W(x,y)=\langle y,F(x)\rangle$ there is a canonical equivalence of formal dg schemes
\[
\dCrit(W)\simeq T^*[-1] Z_F^{\der}.
\]
\end{theorem}

\begin{proof}
The shifted cotangent algebra of $Z_F^{\der}$ is the algebra of polyvector fields on $Z_F^{\der}$:
\[
\cO\bigl(T^*[-1]Z_F^{\der}\bigr)\cong \PV(Z_F^{\der}).
\]
Using the Koszul model \eqref{eq:boundary-linear-dga}, this algebra is generated by:
\begin{itemize}[leftmargin=1.8em]
\item even coordinates $x_i$ on $L$,
\item odd coordinates $\eta_a$ from the derived equations $F_a(x)=0$,
\item odd tangent polyvectors $\theta_i$ dual to $x_i$,
\item even tangent polyvectors $y_a$ dual to $\eta_a$.
\end{itemize}
Its differential is induced by the boundary differential and is exactly
\[
d\theta_i
=
\sum_a y_a\frac{\partial F_a}{\partial x_i}(x),
\qquad
dy_a=0,
\qquad
d\eta_a=F_a(x),
\qquad
dx_i=0.
\]
But this is exactly the standard dg algebra of functions on the derived critical locus of $W(x,y)=\langle y,F(x)\rangle$. Hence the two dg schemes are canonically equivalent.
\end{proof}

\subsection{Derived center of the boundary algebra}

The usual HKR theorem identifies Hochschild cochains of a smooth commutative algebra with polyvector fields. In the present dg setting, the same philosophy gives the derived center of the boundary dg algebra as the shifted cotangent algebra of the derived boundary zero locus. Because the bulk critical locus is exactly that shifted cotangent, the bulk is recovered from the boundary algebra.

\begin{theorem}[Boundary-linear bulk/boundary theorem; \ClaimStatusProvedHere]% label removed: thm:boundary-linear-bulk-boundary
For $W(x,y)=\langle y,F(x)\rangle$ there is a canonical quasi-isomorphism
\[
\Zder(B_{L,W})
\simeq
\HH^\bullet(B_{L,W})
\simeq
\cO\bigl(T^*[-1]Z_F^{\der}\bigr)
\simeq
\cO\bigl(\dCrit(W)\bigr).
\]
In particular the derived center of the boundary algebra equals the bulk algebra in the boundary-linear sector.
\end{theorem}

\begin{proof}
Because $B_{L,W}$ is a cofibrant completed commutative dg algebra, its derived center is modeled by Hochschild cochains. The dg HKR map identifies Hochschild cochains with polyvector fields on the derived affine dg scheme $Z_F^{\der}$. Theorem~\ref{thm:dcrit-shiftedcot} identifies those polyvectors with functions on the bulk critical locus.
\end{proof}

\subsection{The free polarization theorem as the zero superpotential case}

Setting $F=0$ gives the free model. Then
\[
B_L^{\free}
=
\widehat{\Sym}(L^\vee)\ot \Lambda(N),
\qquad
Z_0^{\der}=L\oplus N^\vee[1].
\]
The bulk algebra is
\[
A_{\mathrm{bulk}}^{\free}(V)
=
\widehat{\Sym}(V^\vee)\ot \Lambda(V).
\]

\begin{corollary}[Free polarization theorem; \ClaimStatusProvedHere]% label removed: cor:free-polarization
For a linear boundary condition $L\subset V$ with quotient $Q=V/L$ one has
\[
B_L^{\free}\cong \widehat{\Sym}(L^\vee)\ot \Lambda(Q),
\qquad
K_L^{\free}\simeq \widehat{\Sym}(Q^\vee)\ot \Lambda(L),
\]
and
\[
\HH^\bullet(B_L^{\free})
\cong
\HH^\bullet(K_L^{\free})
\cong
\widehat{\Sym}(V^\vee)\ot \Lambda(V).
\]
Thus the boundary and line algebras are opposite Koszul polarizations of the full free bulk algebra.
\end{corollary}

\begin{proof}
The first identity is the boundary dg algebra with $F=0$. The second is ordinary completed Koszul duality. The final statement follows from Theorem~\ref{thm:boundary-linear-bulk-boundary} and the Morita invariance of Hochschild cohomology.
\end{proof}


\section{Exact pointed lines, one-step Jacobi coalgebras, and vacuum twisting}% label removed: sec:exact-lines

The boundary-linear sector is exact enough not only to compute the boundary algebra but also to compute the line algebra attached to a \emph{pointed} boundary vacuum.

Fix a point
\[
p\in F^{-1}(0)\subset L.
\]
Complete at $p$ and set
\[
U:=T_pL,
\qquad
R:=N^\vee.
\]
The completed local boundary algebra is
\[
B_{F,p}
=
\bigl(\kk[[U^\vee]]\ot \Lambda(R^\vee),\ d\eta_\alpha=F_\alpha(x)\bigr).
\]

\subsection{The one-step Jacobi coalgebra}

The Taylor coefficients of $F$ at $p$ assemble into a canonical dg coalgebra.

\begin{definition}[One-step Jacobi coalgebra]
The one-step Jacobi coalgebra of the pointed germ $(F,p)$ is
\[
\cJ_{F,p}:=\bigl(S^c(sU\oplus R),\, b_F\bigr),
\]
where $S^c$ denotes the cofree cocommutative coalgebra and the coderivation $b_F$ is determined by its Taylor coefficients
\[
b_{F,n}: S^n(sU)\longrightarrow R
\]
given by the $n$-th derivatives of $F$ at $p$.
\end{definition}

The terminology is deliberate: this coalgebra is the local coalgebraic envelope of the boundary equations. It is the object from which both the local boundary algebra and the pointed line algebra can be recovered.

\begin{theorem}[Exact presentation theorem; \ClaimStatusProvedHere]% label removed: thm:exact-line
There are canonical identifications
\[
B_{F,p}\cong \cJ_{F,p}^\vee,
\qquad
K^{\mathrm{ex}}_{F,p}:=\Cobar(\cJ_{F,p})
\simeq
\RHom_{B_{F,p}}(\kk,\kk).
\]
Equivalently, the pointed line algebra is the cobar algebra of the local Jacobi coalgebra.
\end{theorem}

\begin{proof}
The completed dual of the cofree coalgebra $S^c(sU\oplus R)$ is the completed free commutative algebra on $U^\vee$ and $R^\vee[-1]$, which is exactly the underlying graded algebra of $B_{F,p}$. The coderivation $b_F$ dualizes to the differential $d\eta_\alpha=F_\alpha(x)$, so $B_{F,p}\cong \cJ_{F,p}^\vee$.

Standard Koszul duality for complete augmented commutative dg algebras
identifies the derived endomorphisms of the residue field with the
dual-coalgebra construction. Applying this to $B_{F,p}$ yields
\[
\RHom_{B_{F,p}}(\kk,\kk)\simeq \Cobar(\cJ_{F,p}).
\]
\end{proof}

\subsection{Explicit formula for the pointed line algebra}

Choose coordinates $x_1,\dots,x_u$ on $U$ centered at $p$, a basis $r_\alpha$ of $R$, odd generators $\lambda_i$ of degree $1$ dual to $x_i$, and even generators $c_\alpha$ of degree $2$ dual to $r_\alpha$.

Define the graded algebra
\[
K_{F,p}^{\gr}:=\Sym(R)\ot \Lambda(U)=\kk[c_\alpha]\ot \Lambda(\lambda_i).
\]
For $n\ge 1$ define Hochschild cochains
\begin{equation}% label removed: eq:mu-F-explicit
\mu_n(a_1,\dots,a_n)
:=
\sum_{\alpha}
c_\alpha
\sum_{i_1,\dots,i_n}
\frac{1}{n!}
\frac{\partial^n F_\alpha}{\partial x_{i_1}\cdots \partial x_{i_n}}(p)
\bigl(\partial_{\lambda_{i_1}}a_1\bigr)\cdots \bigl(\partial_{\lambda_{i_n}}a_n\bigr).
\end{equation}
Set
\[
m_1=\mu_1,
\qquad
m_2=m_2^{\free}+\mu_2,
\qquad
m_n=\mu_n\quad (n\ge 3).
\]

\begin{corollary}[Explicit pointed line algebra; \ClaimStatusProvedHere]% label removed: cor:explicit-line
The operations above define a complete filtered $A_\infty$ algebra structure on $K_{F,p}^{\gr}$, denoted $K^{\expmod}_{F,p}$, and there is an $A_\infty$ quasi-isomorphism
\[
K^{\expmod}_{F,p}\simeq K^{\mathrm{ex}}_{F,p}\simeq \RHom_{B_{F,p}}(\kk,\kk).
\]
\end{corollary}

\begin{proof}
Under the HKR map, the total cochain $\mu=\sum_n \mu_n$ corresponds to the odd polyvector field obtained from the Taylor expansion of $F$ by replacing the tangent variables with the odd derivations $\partial_{\lambda_i}$. Since these odd derivations supercommute and the coefficients are scalar functions, the Schouten bracket vanishes. Exactly as in the proof of Theorem~\ref{thm:intrinsic-boundary}, this implies the Stasheff identities. The comparison with $\Cobar(\cJ_{F,p})$ is tautological from the construction of $b_F$.
\end{proof}

\subsection{Vacua as Maurer--Cartan elements}

One of the most satisfying features of the one-step Jacobi coalgebra is that classical vacua become internal Maurer--Cartan data.

\begin{theorem}[Maurer--Cartan vacuum theorem; \ClaimStatusProvedHere]% label removed: thm:mc-vacua
Let $q$ be a formal point of $L$ near $p$. Then the following are equivalent:
\begin{enumerate}[label=(\roman*),leftmargin=1.8em]
\item $q$ is a boundary vacuum, that is, $F(q)=0$;
\item the displacement $u=q-p\in U$ defines a Maurer--Cartan element of the coalgebra $\cJ_{F,p}$;
\item $u$ defines a Maurer--Cartan element of the $A_\infty$ algebra $K^{\mathrm{ex}}_{F,p}$.
\end{enumerate}
Twisting $\cJ_{F,p}$ by the Maurer--Cartan element corresponding to $q$ yields the recentered coalgebra:
\[
\cJ_{F,p}^{\,q}\cong \cJ_{F,q}.
\]
\end{theorem}

\begin{proof}
The Maurer--Cartan equation in $\cJ_{F,p}$ is
\[
\sum_{n\ge 1}\frac{1}{n!} b_{F,n}(u,\dots,u)=0,
\]
which is precisely the Taylor expansion of $F(p+u)=0$. The equivalence with the $A_\infty$ Maurer--Cartan equation follows under the bar--cobar correspondence. Twisting by $u$ simply translates the Taylor expansion from the base point $p$ to the base point $q$.
\end{proof}

\subsection{Polarized reconstruction}

The exact line algebra remembers more than its quasi-isomorphism class: it remembers a primitive polarization.

\begin{definition}[Primitive polarization]
The primitive part of the bar coalgebra of $K^{\mathrm{ex}}_{F,p}$ is
\[
\mathrm{Prim}\bigl(\BBar K^{\mathrm{ex}}_{F,p}\bigr)\cong sU\oplus R.
\]
A \emph{polarization} is the decomposition of this primitive space into its odd tangent piece $sU$ and its even obstruction piece $R$.
\end{definition}

\begin{theorem}[Polarized reconstruction; \ClaimStatusProvedHere]% label removed: thm:polarized-reconstruction
The polarized bar coalgebra
\[
\bigl(\BBar K^{\mathrm{ex}}_{F,p},\; \mathrm{Prim}=sU\oplus R\bigr)
\]
reconstructs the full pointed formal germ of the map $F$ at $p$. Equivalently, the polarized coalgebra $\cJ_{F,p}$ is a complete invariant of the pointed boundary-linear formal germ.
\end{theorem}

\begin{proof}
The coderivation of $\cJ_{F,p}$ is determined exactly by the maps
\[
b_{F,n}:S^n(sU)\to R.
\]
These are the Taylor coefficients of $F$ at $p$. Conversely, given the polarized coalgebra, the maps $b_{F,n}$ may be read off from the component of the coderivation landing in the $R$-summand of the primitive part. Reassembling these Taylor coefficients recovers the formal map $F$.
\end{proof}

\begin{remark}
This theorem is the first local incarnation of the guiding slogan that the line sector should not merely receive data from the boundary equations; it should \emph{present} them.
\end{remark}


\section{Boundary Kuranishi elimination and the minimal pointed line algebra}% label removed: sec:kuranishi

The exact pointed line algebra $K_{F,p}^{\mathrm{ex}}$ is canonical, but it is not yet minimal. If the linearization of $F$ at $p$ is nonzero, then the line algebra has a nontrivial unary operation. The next theorem integrates out the linearly massive directions exactly and produces a minimal local model.

\subsection{Splitting the linearized equations}

Let
\[
dF_p:U\to R.
\]
Choose splittings
\[
U=T\oplus M,
\qquad
R=I\oplus C,
\]
with
\[
T=\ker(dF_p),
\qquad
I=\im(dF_p),
\qquad
C\cong \coker(dF_p),
\]
and such that
\[
A:=dF_p|_M:M\xrightarrow{\sim} I
\]
is an isomorphism.

Choose coordinates $(u,v)$ on $T\oplus M$ and decompose
\[
F=(F_I,F_C),
\qquad
F_I\in I[[u,v]],
\quad
F_C\in C[[u,v]].
\]

\begin{lemma}[Formal implicit solution; \ClaimStatusProvedHere]% label removed: lem:formal-implicit
There exists a unique formal map
\[
\varphi(u)\in M[[u]]
\]
with no constant or linear term such that
\[
F_I\bigl(u,\varphi(u)\bigr)=0.
\]
\end{lemma}

\begin{proof}
Expand $\varphi(u)=\sum_{n\ge 2}\varphi_n(u)$ by total degree in $u$. At each order $n$, the equation takes the form
\[
A\,\varphi_n + (\text{known term of degree }n)=0.
\]
Since $A$ is invertible, $\varphi_n$ is uniquely determined recursively.
\end{proof}

\begin{definition}[Effective obstruction map]
The reduced Kuranishi map is
\begin{equation}% label removed: eq:kappa-def
\kappa(u):=F_C\bigl(u,\varphi(u)\bigr)\in C[[u]].
\end{equation}
It has no constant or linear term.
\end{definition}

\subsection{Exact splitting of the boundary dg algebra}

Set
\[
w:=v-\varphi(u).
\]
Then $F_I(u,\varphi(u)+w)$ vanishes at $w=0$, so it factors by $w$.

\begin{lemma}[Factorization of the massive equations; \ClaimStatusProvedHere]% label removed: lem:factorization
There exist formal matrix-valued power series
\[
\mathcal A(u,w)\in \End(M,I)[[u,w]],
\qquad
\mathcal B(u,w)\in \Hom(M,C)[[u,w]],
\]
with $\mathcal A(0,0)=A$ invertible, such that
\[
F_I\bigl(u,\varphi(u)+w\bigr)=\mathcal A(u,w)\,w,
\qquad
F_C\bigl(u,\varphi(u)+w\bigr)=\kappa(u)+\mathcal B(u,w)\,w.
\]
\end{lemma}

\begin{proof}
This is the formal Taylor expansion in the $w$-variables around $w=0$, using the fact that the constant term of $F_I$ vanishes by definition of $\varphi$.
\end{proof}

\begin{theorem}[Boundary Kuranishi elimination; \ClaimStatusProvedHere]% label removed: thm:boundary-kuranishi
After the changes of variables
\[
v=\varphi(u)+w
\]
and the odd change of generators
\[
\xi:=\mathcal A(u,w)^{-1}\eta_I,
\qquad
\zeta:=\eta_C-\mathcal B(u,w)\mathcal A(u,w)^{-1}\eta_I,
\]
the completed local boundary dg algebra becomes
\[
B_{F,p}
\cong
\bigl(\kk[[u,w]]\ot \Lambda(\xi,\zeta),\ d\xi=w,\ d\zeta=\kappa(u)\bigr).
\]
Consequently there is a canonical dg quasi-isomorphism
\[
B_{F,p}\simeq B_\kappa
:=
\bigl(\kk[[u]]\ot \Lambda(C^\vee),\ d\zeta=\kappa(u)\bigr).
\]
\end{theorem}

\begin{proof}
The displayed formula follows by a direct calculation:
\[
d\xi=\mathcal A^{-1}d\eta_I=\mathcal A^{-1}\mathcal A w=w,
\]
and
\[
d\zeta=d\eta_C-\mathcal B\mathcal A^{-1}d\eta_I
=(\kappa+\mathcal Bw)-\mathcal B\mathcal A^{-1}\mathcal A w
=\kappa.
\]
The factor $\bigl(\kk[[w]]\ot \Lambda(\xi),d\xi=w\bigr)$ is the completed Koszul resolution of $\kk$ and is therefore contractible. Removing it gives the reduced dg algebra $B_\kappa$.
\end{proof}

\begin{remark}
This theorem is stronger than ordinary homological perturbation. It does not merely assert that a smaller model exists. It constructs an explicit nonlinear change of generators that exhibits the massive directions as a contractible factor. For that reason it is genuinely a nonlinear Schur complement.
\end{remark}

\subsection{The minimal pointed line algebra}

Apply the exact line construction to the reduced map $\kappa:T\to C$.

Let
\[
K_\kappa^{\gr}:=\Sym(C)\ot \Lambda(T).
\]
For $n\ge 2$ define
\begin{equation}% label removed: eq:mu-kappa
\mu_n^\kappa(a_1,\dots,a_n)
:=
\sum_{\alpha}
c_\alpha
\sum_{i_1,\dots,i_n}
\frac{1}{n!}
\frac{\partial^n\kappa_\alpha}{\partial u_{i_1}\cdots \partial u_{i_n}}(0)
\bigl(\partial_{\lambda_{i_1}}a_1\bigr)\cdots \bigl(\partial_{\lambda_{i_n}}a_n\bigr),
\end{equation}
and set
\[
m_1^\kappa=0,
\qquad
m_2^\kappa=m_2^{\free}+\mu_2^\kappa,
\qquad
m_n^\kappa=\mu_n^\kappa\quad (n\ge 3).
\]

\begin{theorem}[Minimal pointed line algebra; \ClaimStatusProvedHere]% label removed: thm:minimal-pointed-line
The operations above define a minimal $A_\infty$ algebra
\[
K_\kappa
=
\bigl(\Sym(C)\ot \Lambda(T),\{m_n^\kappa\}_{n\ge 2}\bigr),
\]
and there are $A_\infty$ quasi-isomorphisms
\[
K_{F,p}^{\mathrm{ex}}
\simeq
K_\kappa.
\]
Equivalently, the exact pointed line algebra is governed, up to quasi-isomorphism, by the reduced Kuranishi map $\kappa$.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:boundary-kuranishi} identifies $B_{F,p}$ with the tensor product of $B_\kappa$ and a contractible Koszul factor. Derived endomorphisms of the residue field are invariant under tensoring with such a factor, so
\[
\RHom_{B_{F,p}}(\kk,\kk)\simeq \RHom_{B_\kappa}(\kk,\kk).
\]
Applying Theorem~\ref{thm:exact-line} to $\kappa$ identifies the right-hand side with the explicit $A_\infty$ algebra above. Since $\kappa$ has no linear term, the resulting $A_\infty$ algebra is minimal.
\end{proof}

\subsection{Recursive formulas and the first effective couplings}

The reduced map $\kappa$ admits exact recursive formulas. Write
\[
\Phi(u):=(u,\varphi(u))=\sum_{n\ge 1}\frac{1}{n!}\Phi_n(u,\dots,u),
\qquad
\kappa(u)=\sum_{n\ge 2}\frac{1}{n!}\kappa_n(u,\dots,u).
\]
Write the Taylor expansion of $F_I$ and $F_C$ at the origin as
\[
F_I=\sum_{q\ge 1}F_q^I,
\qquad
F_C=\sum_{q\ge 1}F_q^C.
\]

\begin{proposition}[Recursive Kuranishi coefficients; \ClaimStatusProvedHere]% label removed: prop:recursive-kuranishi
The multilinear maps $\Phi_n$ and $\kappa_n$ are uniquely determined by
\begin{align}
A\Phi_n
&=
-
\sum_{q=2}^{n}
\frac{1}{q!}
\sum_{\substack{n_1+\cdots+n_q=n\\ n_i\ge 1}}
\operatorname{Sym}\Bigl(F_q^I\bigl(\Phi_{n_1},\dots,\Phi_{n_q}\bigr)\Bigr),
% label removed: eq:phi-recursion
\\[0.5em]
\kappa_n
&=
\sum_{q=2}^{n}
\frac{1}{q!}
\sum_{\substack{n_1+\cdots+n_q=n\\ n_i\ge 1}}
\operatorname{Sym}\Bigl(F_q^C\bigl(\Phi_{n_1},\dots,\Phi_{n_q}\bigr)\Bigr).
% label removed: eq:kappa-recursion
\end{align}
\end{proposition}

\begin{proof}
Insert the exponential expansions into the defining equations
\[
F_I(\Phi(u))=0,
\qquad
\kappa(u)=F_C(\Phi(u)),
\]
and compare homogeneous components of degree $n$.
\end{proof}

\begin{corollary}[Quadratic and cubic effective couplings; \ClaimStatusProvedHere]% label removed: cor:low-order-kappa
The first two Kuranishi coefficients are
\begin{align}
\kappa_2(t_1,t_2)
&=
F_2^C(t_1,t_2),
% label removed: eq:kappa2
\\[0.5em]
\kappa_3(t_1,t_2,t_3)
&=
F_3^C(t_1,t_2,t_3)
-
\sum_{\mathrm{cyc}}
F_2^C\Bigl(t_1,\,A^{-1}F_2^I(t_2,t_3)\Bigr).
% label removed: eq:kappa3
\end{align}
Consequently
\[
m_2^\kappa(\lambda_{t_1},\lambda_{t_2})
=
\lambda_{t_1}\wedge \lambda_{t_2}
+\frac{1}{2}\kappa_2(t_1,t_2),
\qquad
m_3^\kappa(\lambda_{t_1},\lambda_{t_2},\lambda_{t_3})
=
\frac{1}{6}\kappa_3(t_1,t_2,t_3).
\]
\end{corollary}

\begin{proof}
At quadratic order only the quadratic target component $F_2^C$ contributes. At cubic order there are two kinds of contributions: the direct cubic term $F_3^C$ and the indirect term obtained by feeding two tangent inputs into the massive channel through $F_2^I$, propagating back via $A^{-1}$, and returning to the obstruction space through $F_2^C$.
\end{proof}

\begin{remark}
Formula \eqref{eq:kappa3} is the algebraic avatar of integrating out a massive propagator. The effective cubic interaction is not the raw cubic Taylor coefficient of the original equations; it is the raw cubic term corrected by the tree-level exchange through the massive sector.
\end{remark}

\subsection{Smooth vacua}

\begin{corollary}[Smooth-point formality; \ClaimStatusProvedHere]% label removed: cor:smooth-formality
If $p$ is a smooth point of the classical zero locus $F^{-1}(0)$, then $C=0$ and the minimal pointed line algebra is the exterior algebra
\[
K_\kappa\simeq \Lambda(T_pF^{-1}(0)).
\]
\end{corollary}

\begin{proof}
Smoothness is equivalent to surjectivity of $dF_p$, hence $C=\coker(dF_p)=0$. Therefore $\kappa=0$ and only the free exterior algebra on $T=\ker(dF_p)$ remains.
\end{proof}


\section{Local bulk from local lines, and the boundary-linear line Mather--Yau theorem}% label removed: sec:classification

The previous section produces the minimal pointed line algebra $K_\kappa$ attached to a boundary vacuum. The proof of two culmination theorems:
\begin{enumerate}[label=(\arabic*),leftmargin=1.8em]
\item the local bulk algebra is recovered from $K_\kappa$ by Hochschild cochains;
\item the polarized quasi-isomorphism class of $K_\kappa$ classifies the reduced microlocal formal germ.
\end{enumerate}

\subsection{Local bulk from local lines}

Let $\gamma$ denote the coordinate on $C^\vee$. The effective boundary-linear potential determined by the Kuranishi map is
\[
W_{\eff}(u,\gamma):=\langle \gamma,\kappa(u)\rangle.
\]
Its boundary dg algebra is exactly $B_\kappa$.

\begin{theorem}[Local bulk/line theorem; \ClaimStatusProvedHere]% label removed: thm:local-bulk-line
For every pointed boundary-linear germ $(F,p)$ one has canonical quasi-isomorphisms
\[
\HH^\bullet(K_{F,p})
\simeq
\HH^\bullet(K_\kappa)
\simeq
\HH^\bullet(B_\kappa)
\simeq
\cO\bigl(\dCrit(W_{\eff})\bigr).
\]
Equivalently, the completed local bulk algebra depends only on the minimal pointed line algebra.
\end{theorem}

\begin{proof}
The first equivalence is Theorem~\ref{thm:minimal-pointed-line}. Since $K_\kappa$ and $B_\kappa$ are Koszul dual presentations of the same pointed local category, their Hochschild cochains agree by Morita invariance. The last equivalence is the boundary-linear bulk/boundary theorem applied to the reduced map $\kappa:T\to C$.
\end{proof}

\begin{remark}
This is the exact local shadow of the global triangle \eqref{eq:global-corrected-triangle}. The line algebra does not equal the bulk algebra; the bulk is the derived center of the line algebra, and in the exact local sector that center is computable.
\end{remark}

\subsection{Polarized quasi-isomorphisms}

The reconstruction theorem showed that the polarized bar coalgebra of the exact pointed line algebra recovers the pointed formal germ. After Kuranishi reduction the same statement becomes stronger: it classifies the \emph{reduced} microlocal germ, which is exactly the singular residue left after all linearly massive directions have been eliminated.

\begin{definition}[Polarized $A_\infty$ isomorphism]
Let
\[
K_\kappa=\Sym(C)\ot \Lambda(T),
\qquad
K_{\kappa'}=\Sym(C')\ot \Lambda(T')
\]
be minimal pointed line algebras. A \emph{polarized $A_\infty$ isomorphism}
\[
\Phi:K_\kappa\longrightarrow K_{\kappa'}
\]
is an $A_\infty$ isomorphism whose induced bar-coalgebra isomorphism
\[
\BBar \Phi:\BBar K_\kappa\to \BBar K_{\kappa'}
\]
preserves the primitive decomposition
\[
\mathrm{Prim}(\BBar K_\kappa)=sT\oplus C,
\qquad
\mathrm{Prim}(\BBar K_{\kappa'})=sT'\oplus C'.
\]
\end{definition}

\begin{definition}[Formal equivalence of reduced germs]
Two reduced Kuranishi maps
\[
\kappa:T\to C,
\qquad
\kappa':T'\to C'
\]
are \emph{formally equivalent} if there exist formal linear isomorphisms on source and target, together with higher formal changes of tangent coordinates preserving the base point, carrying the Taylor expansion of $\kappa$ to that of $\kappa'$.
\end{definition}

\begin{theorem}[Boundary-linear line Mather--Yau theorem; \ClaimStatusProvedHere]% label removed: thm:line-mather-yau
Let $(F,p)$ and $(G,q)$ be pointed boundary-linear germs with reduced Kuranishi maps
\[
\kappa_F:T_F\to C_F,
\qquad
\kappa_G:T_G\to C_G.
\]
Then the following are equivalent:
\begin{enumerate}[label=(\roman*),leftmargin=1.8em]
\item $\kappa_F$ and $\kappa_G$ are formally equivalent;
\item the minimal pointed line algebras $K_{\kappa_F}$ and $K_{\kappa_G}$ are polarized $A_\infty$-isomorphic;
\item the one-step Jacobi coalgebras $\cJ_{\kappa_F}$ and $\cJ_{\kappa_G}$ are polarized isomorphic.
\end{enumerate}
Whenever these conditions hold, the completed local bulk algebras are canonically quasi-isomorphic:
\[
\cO\bigl(\dCrit(W_{\eff,F})\bigr)\simeq \cO\bigl(\dCrit(W_{\eff,G})\bigr).
\]
\end{theorem}

\begin{proof}
\emph{(i)$\Rightarrow$(iii).}
A formal equivalence of reduced germs identifies all Taylor coefficients of $\kappa_F$ with those of $\kappa_G$ after transport by the induced source and target changes. By definition these Taylor coefficients are exactly the structure maps of the one-step Jacobi coalgebras, so the coalgebras are polarized isomorphic.

\emph{(iii)$\Rightarrow$(ii).}
Cobar sends a polarized coalgebra isomorphism to an $A_\infty$ isomorphism between the corresponding cobar algebras. But $K_{\kappa_F}\simeq \Cobar(\cJ_{\kappa_F})$ and similarly for $G$.

\emph{(ii)$\Rightarrow$(iii).}
Apply the bar construction. Because the algebras are minimal, the bar construction recovers a complete filtered coalgebra with primitive part equal to $sT\oplus C$. The polarization hypothesis guarantees that the induced isomorphism preserves the tangent and obstruction summands separately, so it is a polarized coalgebra isomorphism.

\emph{(iii)$\Rightarrow$(i).}
By the polarized reconstruction theorem, a polarized coalgebra recovers the full reduced formal map. Therefore a polarized coalgebra isomorphism yields a formal equivalence of Kuranishi maps.

The final statement about bulk algebras follows from Theorem~\ref{thm:local-bulk-line}.
\end{proof}

\begin{corollary}[Microlocal classification theorem; \ClaimStatusProvedHere]% label removed: cor:microlocal-classification
The assignment
\[
(F,p)\longmapsto K_{\kappa_F}
\]
induces a bijection between reduced microlocal formal types of pointed boundary-linear vacua and polarized $A_\infty$ isomorphism classes of minimal pointed line algebras.
\end{corollary}

\begin{proof}
This is a restatement of Theorem~\ref{thm:line-mather-yau}.
\end{proof}

\subsection{What is stable and what is invisible}

The reduced microlocal formal type is obtained only after discarding linearly massive directions. The stabilization theorems of Section~\ref{sec:ts-knorrer} show that additional tangent-normal contractible blocks and pure-normal hyperbolic Clifford blocks are also invisible to the stable open sector.

\begin{corollary}[Stable invisibility of universal blocks; \ClaimStatusProvedHere]% label removed: cor:stable-invisibility
The following operations do not change the stable open-sector content of a boundary model:
\begin{enumerate}[label=(\roman*),leftmargin=1.8em]
\item adding a tangent-normal hyperbolic pair $u v$ with one tangent and one normal leg;
\item adding a pure-normal hyperbolic pair $uv$ with both legs normal, after spinor stabilization.
\end{enumerate}
Hence the genuinely nontrivial local data of a pointed boundary-linear model are concentrated in the reduced Kuranishi map $\kappa$ and therefore in the polarized minimal pointed line algebra $K_\kappa$.
\end{corollary}

\begin{proof}
Part (i) is Theorem~\ref{thm:contractible-stab}. Part (ii) is Theorem~\ref{thm:clifford-stab}. The final assertion follows because Theorem~\ref{thm:boundary-kuranishi} removes the linearly massive directions explicitly and Theorem~\ref{thm:line-mather-yau} classifies what remains.
\end{proof}

\subsection{The fortified local triangle}

We may now summarize the exact local picture in one theorem.

\begin{theorem}[Fortified local bulk/boundary/line triangle; \ClaimStatusProvedHere]% label removed: thm:fortified-local-triangle
For every pointed boundary-linear formal germ $(F,p)$ there is a canonical chain of identifications
\[
(F,p)
\rightsquigarrow
\cJ_{F,p}
\rightsquigarrow
K^{\mathrm{ex}}_{F,p}
\simeq
K_{\kappa_F}
\rightsquigarrow
\HH^\bullet(K_{\kappa_F})
\simeq
\cO\bigl(\dCrit(W_{\eff,F})\bigr).
\]
Here:
\begin{itemize}[leftmargin=1.8em]
\item $\cJ_{F,p}$ is the one-step Jacobi coalgebra presenting the pointed local boundary equations;
\item $K^{\mathrm{ex}}_{F,p}$ is the exact pointed line algebra;
\item $K_{\kappa_F}$ is the minimal pointed line algebra obtained by exact Kuranishi elimination;
\item and $\cO(\dCrit(W_{\eff,F}))$ is the completed local bulk algebra of the effective reduced potential.
\end{itemize}
The polarized $A_\infty$ isomorphism class of $K_{\kappa_F}$ determines the reduced microlocal formal type of $(F,p)$.
\end{theorem}

\begin{proof}
Combine Theorems~\ref{thm:exact-line}, \ref{thm:minimal-pointed-line}, \ref{thm:local-bulk-line}, and \ref{thm:line-mather-yau}.
\end{proof}


\section{Toward the global theorem: rich boundaries, absolute lines, and a Steinberg-style endpoint}% label removed: sec:global

The exact local theorem package is now in place. The global theorem
requires the chain-level bulk/boundary map, the compact generator of
the line category, and the comparison between the absolute open-colour
line algebra and the boundary-adapted pointed models. This section
explains how the local constructions fit into those comparison
problems and what geometric endpoint should present the full line
algebra.

\subsection{The global theorem as a comparison problem}

The corrected global triangle \eqref{eq:global-corrected-triangle} will follow once two comparison maps are supplied:

\begin{enumerate}[label=(\arabic*),leftmargin=1.8em]
\item a \emph{bulk/boundary comparison}
\[
\beta_{\der}:\Abulk\longrightarrow \Zder(B_b)
\]
for a rich boundary condition $b$;
\item a \emph{boundary/line comparison}
\[
\End_{\cC_{\mathrm{line}}}(M_b)\simeq B_b
\]
showing that the chosen boundary vacuum $M_b$ generates the line category.
\end{enumerate}

Once these exist, Proposition~\ref{prop:formal-global-triangle}
finishes the proof. The global theorem is therefore a precise
chain-level comparison problem: bulk/boundary quasi-isomorphism,
boundary-vacuum generation of lines, and Morita invariance.

\subsection{Why the local exact sector matters for the global problem}

The local theorem package proved above gives a template for the global attack:
\begin{itemize}[leftmargin=1.8em]
\item \textbf{intrinsic boundary algebra}: the open sector should be defined without arbitrary splittings;
\item \textbf{exact local line models}: local line algebras should arise from a canonical coalgebraic or Koszul-dual presentation;
\item \textbf{Kuranishi reduction}: linearly massive modes should be integrated out exactly;
\item \textbf{derived center}: bulk should be recovered from lines by Hochschild cochains;
\item \textbf{stabilization calculus}: universal contractible and Morita-trivial blocks must be removed before comparing theories.
\end{itemize}
The local exact sector shows that each of these moves is real, not aspirational.

\subsection{The absolute line algebra versus boundary-adapted local line algebras}

It is essential not to confuse two different line objects:
\begin{enumerate}[label=(\roman*),leftmargin=1.8em]
\item the \emph{absolute} open-colour line algebra
$A^!_{\mathrm{line}}$ of the global theory, which presents the
completed perturbative line category on the chirally Koszul and
quasi-linear loci of \cite{DNP25};
\item the \emph{boundary-adapted pointed} line algebras $K_{F,p}$ and $K_\kappa$ constructed in Sections~\ref{sec:exact-lines}--\ref{sec:classification}.
\end{enumerate}
The latter are local exact models attached to a chosen boundary
vacuum. They should be viewed as boundary charts on the absolute line
category. They are not globally equal to $A^!_{\mathrm{line}}$, and
they are not substitutes for the Hopf/Steinberg comparison. They are
the local testing ground in which the shape of the global theorem
becomes rigid.

\subsection{The Steinberg presentation theorem}

The phrase ``Chriss--Ginzburgification'' is not decorative.
It names a methodological demand: a mature representation-theoretic
algebra should eventually be presented by correspondences.
The Steinberg variety $Z = \widetilde{\cN} \times_{\mathfrak g}
\widetilde{\cN}$ is a correspondence between two copies of the
Springer resolution; its convolution algebra $H_*(Z)$ recovers the
Hecke algebra $\cH_q(W)$. The bar complex $\barB(\cA)$ on
$\FM_k(\C) \times \Conf_k^{<}(\R)$ is a correspondence between
holomorphic collision data and topological ordering data; its
convolution algebra recovers the Swiss-cheese composition.
The following theorem makes this analogy precise for the Swiss-cheese
convolution data; it becomes the corrected bulk-boundary-line triangle
only after the exact-sector or formal-reduction hypotheses are imposed.

\begin{theorem}[Algebraic Steinberg presentation of the SC convolution
data; \ClaimStatusProvedHere]
% label removed: thm:steinberg-presentation
\index{Steinberg presentation|textbf}
\index{Swiss-cheese!Steinberg presentation|textbf}
Let $\cA$ be a chiral algebra on a smooth curve~$X$ satisfying the
standing hypotheses, and let $T = (\Bbound, \cC_{\mathrm{line}})$
be the associated $\SCop$-algebra
\textup{(}Theorem~\textup{\ref{thm:bar-swiss-cheese}}\textup{)}.
Then the Swiss-cheese convolution $L_\infty$-algebra $\gSC_T$
\textup{(}Definition~\textup{\ref{def:sc-convolution}}\textup{)}
\textbf{presents} the bulk/boundary/line Koszul triangle in the
following sense.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Presentation.}
 The operadic composition maps of $\SCop$ are recovered from the
 bar differential and coproduct on $\barB(\cA)$:
 \begin{align*}
 \text{closed composition}
 &= d_{\barB}
 &&\text{\textup{(}OPE residues on $\FM_k(X)$\textup{)}},\\
 \text{open composition}
 &= \Delta
 &&\text{\textup{(}deconcatenation on $\Conf_k^{<}(\R)$\textup{)}},\\
 \text{mixed composition}
 &= d_{\barB}\circ\Delta
 = (d_{\barB}\otimes\id + \id\otimes d_{\barB})\circ\Delta
 &&\text{\textup{(}coderivation\textup{)}}.
 \end{align*}
 The no-open-to-closed rule is the directionality of the
 correspondence: $\Delta$ acts on bar degree and does not produce
 new OPE poles. These three compositions, together with the
 canonical MC element $\alpha_T$ of
 Theorem~\textup{\ref{thm:3d-universal-mc}}, determine the full
 $\SCop$-algebra structure by homotopy transfer
 \textup{(}Theorem~\textup{\ref{thm:homotopy-Koszul}}\textup{)}.

\item \textbf{Line algebra from convolution.}
 The open-colour part of the presentation gives the algebraic model
 of the line sector as the module category of the Swiss-cheese
 convolution algebra:
 \[
 \cC_{\mathrm{line}}
 \;\simeq\;
 \mathrm{Rep}(\gSC_T).
 \]
 The first equivalence is the definition of the open-colour sector
 of $\alpha_T$
 \textup{(}Proposition~\textup{\ref{prop:alpha-projections}(ii)}\textup{)}.
 On the completed chirally Koszul locus,
 Theorem~\textup{\ref{thm:lines_as_modules}} further models this line
 sector by
 $A^!_{\mathrm{line}}\textup{-mod}$.

\item \textbf{Bulk-to-boundary from the mixed face.}
 The mixed sector of the presentation yields the bulk-to-boundary
 comparison map
 \[
 \Abulk
 \;\longrightarrow\;
 \Zder(\Bbound).
 \]
 This map is the $(1,1)$-projection of
 $\alpha_T$
 \textup{(}Proposition~\textup{\ref{prop:alpha-projections}(iv)}\textup{)}.
 In the exact boundary-linear sector,
 Theorem~\textup{\ref{thm:boundary-linear-bulk-boundary}} identifies
 it as an equivalence
 $\Abulk \simeq \Zder(\Bbound)$, and on the chirally Koszul locus
 with the compact-generation / derived-center hypotheses the
 right-hand side further matches
 $\HH^\bullet_{\mathrm{ch}}(A^!_{\mathrm{line}})$.

\item \textbf{Braiding from the $(2,0)$ face.}
 The spectral $R$-matrix $R(z)$ is the
 $(2,0)$-projection of $\alpha_T$ restricted to
 the ordered collision stratum of $\FM_2(\C)$
 \textup{(}Proposition~\textup{\ref{prop:alpha-projections}(iii)}\textup{)}.
 The Yang--Baxter equation is the MC equation at degree $(3,0)$.
 The further identification of this braiding with monodromy of a reduced HT
 logarithmic connection is a separate frontier comparison.

\item \textbf{Genus tower from curvature.}
 At genus $g \ge 1$, the self-loop restriction of $\alpha_T$
 recovers the modular characteristic $\kappa(\Bbound)\cdot\omega_g$
 and the shadow obstruction tower
 \textup{(}Proposition~\textup{\ref{prop:alpha-projections}(v)}\textup{)}.
\end{enumerate}
\end{theorem}

\begin{proof}
The theorem assembles five proved results into a single package.
Statement~(i) is Theorem~\ref{thm:bar-swiss-cheese} (the bar
complex is an $E_1$ dg coassociative coalgebra) together with
Theorem~\ref{thm:homotopy-Koszul} (homotopy-Koszulity ensures
the bar-cobar resolution recovers the operad).
Statement~(ii) combines
Proposition~\ref{prop:alpha-projections}(ii) (the open projection
gives the line-sector operations) with
Theorem~\ref{thm:lines_as_modules}
\textup{(}which identifies that sector with
$A^!_{\mathrm{line}}$-modules on the chirally Koszul
locus\textup{)}.
Statement~(iii) combines
Proposition~\ref{prop:alpha-projections}(iv) (the mixed projection
gives the bulk-to-boundary map) with
Theorem~\ref{thm:boundary-linear-bulk-boundary} (bulk as derived
center in the exact sector) and
Theorem~\ref{thm:bulk_hochschild} together with
Theorem~\ref{thm:lines_as_modules}
\textup{(}for the line-side Hochschild corner on the scoped
locus\textup{)}.
Statement~(iv) is Proposition~\ref{prop:alpha-projections}(iii)
together with Theorem~\ref{thm:YBE}.
Statement~(v) is Proposition~\ref{prop:alpha-projections}(v)
together with the genus-tower identification from Vol~I
(Theorem~D, bridge MC5).

The direct closed/open/mixed/genus data are
faces of a \emph{single} MC element $\alpha_T \in \mc(\gSC_T)$:
the boundary operations, line-sector operations, braiding, and genus
tower are not assembled by hand, but read off one correspondence.
The line-module and corrected-triangle identifications are then the
comparison theorems that interpret those faces on the scoped theorem
surface.
\end{proof}

\begin{remark}[The Steinberg dictionary]
% label removed: rem:steinberg-dictionary
\index{Steinberg!dictionary}
The correspondence between geometric representation theory
and holomorphic-topological algebra is:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lll}
\hline
\textbf{Steinberg geometry} & \textbf{HT bar complex} & \textbf{Role} \\
\hline
Flag variety $G/B$ & $\FM_k(\C)$ & Collision/resolution data \\
Nilpotent cone $\cN$ & Collision divisors $D_S$ & Singular locus \\
Springer resolution $\widetilde\cN \to \cN$
 & $\FM_k(\C) \to \Conf_k(\C)$ & Compactification \\
Steinberg $Z = \widetilde\cN \times_{\mathfrak g} \widetilde\cN$
 & $\FM_k(\C) \times \Conf_k^{<}(\R)$ & Correspondence \\
Convolution $H_*(Z) = \cH_q(W)$
 & $\gSC_T$ = SC convolution $L_\infty$ & Algebra from corr. \\
Hecke algebra $\cH_q(W)$
 & $A^!_{\mathrm{line}}$ (open-colour Koszul dual/boundary) & Presented algebra \\
$\mathrm{Rep}(\cH_q) = \cO_q$
 & $\cC_{\mathrm{line}}$ modeled by $A^!_{\mathrm{line}}\text{-mod}$ & Module category \\
Center $Z(\cH_q)$
 & formal candidate $\Zder(\gSC_T)$ & Derived-center presentation under Morita hypotheses \\
$q$-parameter
 & Spectral parameter $z$ & Deformation \\
\hline
\end{tabular}
\end{center}
The two colours of the Swiss-cheese operad are the two factors of
the correspondence. The bar-cobar adjunction is the
convolution-restriction adjunction. The no-open-to-closed rule
is the directionality of the Springer correspondence (representations
restrict from $G$ to $B$ but not conversely).
\end{remark}

\subsection{Geometric enhancement}

The algebraic Steinberg presentation
(Theorem~\ref{thm:steinberg-presentation}) is unconditional.
The geometric enhancement (constructing the correspondence space
as a derived self-intersection) remains conjectural.

\begin{conjecture}[Geometric HT Steinberg object; \ClaimStatusConjectured]
% label removed: conj:geometric-steinberg
\index{Steinberg!geometric conjecture}
To a sufficiently well-behaved perturbative 3d
holomorphic--topological QFT $T$ there is attached:
\begin{enumerate}[label=\textup{(\alph*)}]
\item a derived formal moduli stack $\cM_{\mathrm{vac}}(T)$ of
 local bulk vacua, equipped with a $(-2)$-shifted symplectic
 structure;
\item for every rich boundary condition $b$, a shifted-Lagrangian
 substack $\cL_b \hookrightarrow \cM_{\mathrm{vac}}(T)$;
\item a derived self-intersection (the HT Steinberg object)
 \[
 \mathfrak S_b
 \;:=\;
 \cL_b \times_{\cM_{\mathrm{vac}}(T)} \cL_b,
 \]
 carrying a $(-1)$-shifted symplectic structure from
 complementary Lagrangians.
\end{enumerate}
The convolution algebra of $\mathfrak S_b$ in Borel--Moore homology
is quasi-isomorphic to the Swiss-cheese convolution $L_\infty$-algebra:
$H_*^{\mathrm{BM}}(\mathfrak S_b) \simeq \gSC_T$.
The algebraic Steinberg presentation
\textup{(}Theorem~\textup{\ref{thm:steinberg-presentation}}\textup{)}
is the shadow of this geometric identification.
\end{conjecture}

Evidence for the geometric enhancement:
\begin{itemize}[leftmargin=1.8em]
\item In the exact LG sector, the boundary algebra is literally
 the algebra of functions on a derived zero locus, and the bulk
 is functions on a shifted cotangent of that zero locus.
\item The pointed line algebra is the cobar of a canonical coalgebra
 presenting the local equations, the algebraic shadow of the
 Jacobi neighbourhood of $\cL_b$ in $\cM_{\mathrm{vac}}(T)$.
\item The stabilization theorems identify the universal contractible
 and Clifford blocks that should correspond to trivial
 correspondences or Morita-trivial kernels.
\item The dg-shifted-Yangian package of \cite{DNP25} has exactly
 the structure of a convolution algebra with coproduct and
 $r$-matrix.
\end{itemize}


\section{Issues fixed, conceptual simplifications, and the platonic shape of the theory}

Six distinctions are essential for the correctness of the local theory.

\subsection*{Issue 1: identifying the wrong third vertex}
The third vertex of the triangle is not $A^!_{\mathrm{line}}$ itself. It is the derived center of the line category, equivalently chiral Hochschild cochains of $A^!_{\mathrm{line}}$. This is fixed globally in \eqref{eq:global-corrected-triangle} and locally in Theorem~\ref{thm:local-bulk-line}.

\subsection*{Issue 2: confusing absolute and boundary-adapted line algebras}
The exact local line algebras $K_{F,p}$ and $K_\kappa$ are boundary-adapted and pointed. They are local charts on the line sector, not the global absolute open-colour algebra $A^!_{\mathrm{line}}$.

\subsection*{Issue 3: dependence on a chosen complement}
The intrinsic boundary algebra $B^\intr_{L,W}$ removes this at the root. The boundary-linear exact sector then appears as the strict part of the intrinsic theory.

\subsection*{Issue 4: using homological perturbation where exact elimination is available}
Boundary Kuranishi elimination is an exact algebraic theorem, not merely a perturbative transfer. It isolates the singular residue sharply and canonically.

\subsection*{Issue 5: hiding universal trivial blocks}
Contractible tangent-normal blocks and hyperbolic Clifford blocks are now separated cleanly. The former are contractible; the latter are Morita-trivial after spinor stabilization. This clarifies what should and should not count as genuine local data.

\subsection*{Issue 6: failing to distinguish pointed formal type from stable category}
The one-step Jacobi coalgebra classifies the pointed local formal germ. The stabilization theorems explain what is invisible in the stable open sector. The line Mather--Yau theorem classifies the reduced microlocal formal type.

\subsection*{The resulting platonic shape}

Once these corrections are imposed, the theory takes the following purified form:
\[
\text{formal boundary germ}
\;\Longrightarrow\;
B^\intr_{L,W}
\;\Longrightarrow\;
\begin{cases}
\text{exact local chart if $W$ is boundary-linear},\\
\text{full boundary $A_\infty$ algebra otherwise},
\end{cases}
\]
\[
(F,p)
\;\Longrightarrow\;
\cJ_{F,p}
\;\Longrightarrow\;
K^{\mathrm{ex}}_{F,p}
\;\Longrightarrow\;
K_{\kappa_F}
\;\Longrightarrow\;
\HH^\bullet(K_{\kappa_F})\cong \text{local bulk}.
\]
That is the fortified microlocal backbone from which the global theorem must be attacked.


\section{Conclusion}


On the global side, the corrected theorem target has a precise
hypothesis set: compact generation of the boundary vacuum,
line-module comparison on the chirally Koszul locus, and the
derived-centre quasi-isomorphism.
\[
\Abulk
\;\simeq\;
\Zder(\Bbound)
\;\simeq\;
\Zder(\cC_{\mathrm{line}})
\;\simeq\;
\HH^\bullet_{\mathrm{ch}}(A^!_{\mathrm{line}}),
\qquad
\cC_{\mathrm{line}}\simeq A^!_{\mathrm{line}}\text{-mod}.
\]
On the microlocal side, in the boundary-linear exact sector, the
theory is no longer a network of analogies. It is a concrete
theorem package:
\begin{itemize}[leftmargin=1.8em]
\item an intrinsic boundary $A_\infty$ algebra for a formal boundary germ;
\item an exact strict dg model in the boundary-linear sector;
\item an exact pointed line algebra presented as the cobar of the one-step Jacobi coalgebra;
\item an exact Kuranishi reduction to a minimal line algebra;
\item recovery of the local bulk algebra as the derived center of that minimal line algebra in the boundary-linear exact sector;
\item and classification of the reduced microlocal formal germ by the polarized minimal line algebra.
\end{itemize}

The bulk/boundary/line Koszul triangle is therefore no longer merely a
slogan. Its boundary-linear local algebraic heart has been built. The
global theorem is the same formula after the three named comparison
inputs are constructed.

\section{The Swiss-cheese convolution algebra and the 3d universal
MC element}% label removed: sec:sc-convolution-mc

\providecommand{\ModEnv}{\operatorname{ModEnv}}
\providecommand{\Tr}{\operatorname{Tr}}
\providecommand{\ohat}{\widehat{\otimes}}
\providecommand{\Mbar}{\overline{\mathcal M}}
\providecommand{\Rring}{R^{\bullet}}
\providecommand{\gSC}{\mathfrak{g}^{\mathrm{SC}}}
\providecommand{\SCop}{\mathsf{SC}^{\mathrm{ch,top}}}
\providecommand{\ov}[1]{\overline{#1}}
\providecommand{\M}{\mathcal{M}}

Volume~I constructed the modular convolution $L_\infty$-algebra
$\gAmod$ from two inputs: a chain cooperad
$C_*(\Mbar_{g,n})$ and the chiral endomorphism operad
$\End_\cA$. The universal MC element
$\Theta_\cA \in \mc(\gAmod)$ controlled the
genus tower, and its projections recovered Theorems~A--D+H\@.

Volume~II replaces the source cooperad. The chiral moduli spaces
$\FM_n(\C)$ and the topological intervals $E_1(m)$ assemble into
the two-coloured Swiss-cheese cooperad
$\mathbf{B}(\SCop)$, the bar construction of the homotopy-Koszul
operad of Theorem~\ref{thm:homotopy-Koszul}.
The endomorphism operad is now two-coloured:
closed operations act on the boundary algebra $\Bbound$,
open operations act on the line category $\cC_{\mathrm{line}}$,
and mixed operations encode the bulk-to-boundary map.

\begin{definition}[Swiss-cheese convolution $L_\infty$-algebra]
% label removed: def:sc-convolution
\index{Swiss-cheese convolution algebra|textbf}
\index{convolution algebra!Swiss-cheese|textbf}
Let $T = (\Bbound, \cC_{\mathrm{line}})$ be an $\SCop$-algebra
on $\C \times \R_{\ge 0}$. Define the \emph{Swiss-cheese
convolution $L_\infty$-algebra} by
\begin{equation}% label removed: eq:gSC-def
\gSC_T
\;:=\;
\Hom_{\Sigma}\!\bigl(
 \mathbf{B}(\SCop),\;
 \End_{(\Bbound,\,\cC_{\mathrm{line}})}
\bigr),
\end{equation}
the two-coloured convolution of the bar cooperad with the
two-coloured endomorphism operad. The $L_\infty$-brackets are
indexed by two-coloured stable trees: at each closed vertex the
chiral operation $\Phi_v^{\mathrm{ch}}$ is inserted, at each open
vertex the topological operation $\Phi_v^{\mathrm{top}}$ is
inserted, and at each mixed vertex the bulk-to-boundary operation
is inserted.
\end{definition}

The key structural fact: the two-coloured bar cooperad
$\mathbf{B}(\SCop)$ is \emph{not} a product of a closed and an
open cooperad. It is a single two-coloured object whose mixed
operations encode the exact correlation between holomorphic
collisions on $\C$ and topological orderings on $\R$. The
Swiss-cheese convolution algebra $\gSC_T$ therefore carries
strictly more information than the pair $(\gAmod[\Bbound],
\End(\cC_{\mathrm{line}}))$: it remembers the mixed
bulk-boundary-line interactions.

\begin{theorem}[3d universal MC element; \ClaimStatusProvedHere]
% label removed: thm:3d-universal-mc
\index{universal MC element!3d|textbf}
\index{Maurer--Cartan element!Swiss-cheese|textbf}
Let $T = (\Bbound, \cC_{\mathrm{line}})$ be an $\SCop$-algebra
satisfying~\textup{(H1)--(H4)}. There exists a canonical
Maurer--Cartan element
\begin{equation}% label removed: eq:alpha-T
\alpha_T
\;\in\;
\mc\bigl(\gSC_T\bigr)
\end{equation}
whose two-coloured graph expansion is
\[
\alpha_T
\;=\;
\sum_{\Gamma \in \mathsf{Gr}^{\mathrm{SC}}}
\frac{1}{|\operatorname{Aut}(\Gamma)|}
\;W_\Gamma\;\otimes\;\Phi_\Gamma^T,
\]
where $\mathsf{Gr}^{\mathrm{SC}}$ ranges over connected
two-coloured stable trees with closed vertices labelled by
$\FM_k(\C)$-chains, open vertices labelled by $E_1(m)$-chains,
and mixed vertices labelled by $\FM_k(\C) \times E_1(m)$-chains.
The MC equation
$D\alpha_T + \tfrac{1}{2}[\alpha_T, \alpha_T] = 0$
holds because $\SCop$ is homotopy-Koszul
\textup{(}Theorem~\textup{\ref{thm:homotopy-Koszul}}\textup{)},
hence $\mathbf{B}(\SCop)$ has $\partial^2 = 0$.
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:homotopy-Koszul}, $\SCop$ is homotopy-Koszul:
$\Omega\mathbf{B}(\SCop) \xrightarrow{\sim} \SCop$. The universal
twisting morphism
$\tau\colon \mathbf{B}(\SCop) \to \SCop$ therefore satisfies the
MC equation in the two-coloured convolution algebra. Postcomposing
$\tau$ with the structure map $\SCop \to \End_{(\Bbound,
\cC_{\mathrm{line}})}$ gives $\alpha_T$, and the MC equation is
preserved under this postcomposition. The graph expansion follows
from the definition of the two-coloured bar construction: each
two-coloured tree $\Gamma$ contributes a term $W_\Gamma \otimes
\Phi_\Gamma^T$, where $W_\Gamma$ is the fundamental chain of the
corresponding boundary stratum of $\FM_k(\C) \times E_1(m)$ and
$\Phi_\Gamma^T$ is the composition of structure operations along
the tree.
\end{proof}

The element $\alpha_T$ is the 3d analogue of the Vol~I element
$\Theta_\cA$. Its direct projections recover the basic
closed/open/mixed data used throughout Vol~II:

\begin{proposition}[Projections of $\alpha_T$;
\ClaimStatusProvedHere]
% label removed: prop:alpha-projections
\index{universal MC element!3d projections}
The MC element $\alpha_T$ of
Theorem~\textup{\ref{thm:3d-universal-mc}} determines:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Closed face.} The restriction of $\alpha_T$ to
 closed vertices recovers the boundary chiral algebra~$\Bbound$
 with its $\Ainf$-structure
 \textup{(}Definition~\textup{\ref{def:ainfty_chiral}}\textup{)}.
\item \emph{Open face.} The restriction to open vertices
 recovers the open-colour line-sector operations on
 $\cC_{\mathrm{line}}$
 \textup{(}\S\textup{\ref{sec:line_operators}}\textup{)}. On the
 chirally Koszul locus, Theorem~\textup{\ref{thm:lines_as_modules}}
 identifies this line sector with
 $A^!_{\mathrm{line}}\text{-mod}$.
\item \emph{Mixed face: spectral $R$-matrix.} The degree-$(2,0)$
 component of $\alpha_T$ (two closed vertices, no open
 vertices), restricted to the ordered collision stratum of
 $\FM_2(\C)$ is the spectral braiding $R(z)$ of
 Definition~\textup{\ref{def:spectral-braiding}}. Its MC
 equation is the Yang--Baxter equation
 \textup{(}Theorem~\textup{\ref{thm:YBE}}\textup{)}.
\item \emph{Mixed face: bulk-to-boundary.} The degree-$(1,1)$
 component (one closed vertex, one open vertex) is the
 mixed bulk-to-boundary operation. In the exact boundary-linear
 sector, Theorem~\textup{\ref{thm:boundary-linear-bulk-boundary}}
 identifies it with the comparison map
 $\Abulk \to \Zder(\Bbound)$.
\item \emph{Genus face.} At genus~$g \ge 1$, the restriction
 of $\alpha_T$ to the closed sector recovers the modular
 characteristic $\kappa(\Bbound) \cdot \omega_g$ and the
 shadow obstruction tower $\Theta_{\Bbound}^{\le r}$ of Vol~I.
\item \emph{PVA descent.} Passing to cohomology on the closed
 face produces the Poisson vertex algebra bracket
 $\{-_\lambda-\}$ on $H^\bullet(\Bbound)$
 \textup{(}Theorem~\textup{\ref{thm:cohomology_PVA}}\textup{)}.
\end{enumerate}
\end{proposition}

\begin{proof}
Each projection is the restriction of the two-coloured graph sum
to graphs of a specific colour type.

(i): Graphs with all vertices closed are the chiral trees
$\FM_n(\C)$; their operations are the $\Ainf$-chiral operations
$m_k$ by the axioms of the $\SCop$-algebra structure.

(ii): Graphs with all vertices open are the $E_1$-trees; their
operations define the open-colour $\Ainf$-module structure on lines
by the homotopy-Koszul property. The comparison
$\cC_{\mathrm{line}} \simeq A^!_{\mathrm{line}}\text{-mod}$ is the
separate scoped theorem of Theorem~\ref{thm:lines_as_modules}.

(iii): The $(2,0)$-graph is a single edge connecting two closed
vertices at positions $z_1, z_2 \in \FM_2(\C)$. The structure
operation is $\mathsf{Comp}_{z_1,z_2}$, which is the spectral
braiding $R(z_{12})$ by Definition~\ref{def:spectral-braiding}.
The MC equation $D\alpha + \tfrac{1}{2}[\alpha,\alpha] = 0$
restricted to degree $(3,0)$ gives the YBE by the same
boundary-face argument as Theorem~\ref{thm:YBE}.

(iv): The $(1,1)$-graph is a single mixed edge. Its MC equation is
the factorization-module consistency relation; in the exact
boundary-linear sector,
Theorem~\ref{thm:boundary-linear-bulk-boundary} identifies this
mixed operation with the bulk-to-boundary comparison map and upgrades
it to the bulk-as-derived-center equivalence.

(v): Closing the genus face by including self-loop graphs in the
closed sector reproduces the modular bar construction of Vol~I;
the MC element restricted to closed self-loop graphs at genus~$g$
is $\Theta_\cA|_{g}$ by the same argument as
Theorem~\ref*{V1-thm:mc2-bar-intrinsic} (bar-intrinsic construction).

(vi): Descent to cohomology on the closed face is the content of
Theorem~\ref{thm:cohomology_PVA}: the $\Ainf$-operations $m_k$
descend to the PVA bracket $\{-_\lambda-\}$ by the repaired
descent argument of \S\ref{sec:PVA_descent}.
\end{proof}

\begin{definition}[3d modular homotopy type]
% label removed: def:3d-modular-homotopy-type
\index{modular homotopy type!3d|textbf}
The \emph{3d modular homotopy type} of a holomorphic-topological
theory~$T$ is the formal moduli problem
\[
\cM^{\mathrm{SC}}_T(R)
\;:=\;
\mc\bigl(\gSC_T \ohat R\bigr)\big/{\sim}
\]
for local Artin dg algebras~$R$. Its basepoint is $\alpha_T$.
\end{definition}

\begin{corollary}[Restriction to Vol~I; \ClaimStatusProvedHere]
% label removed: cor:3d-to-vol1-restriction
The restriction of $\alpha_T$ to closed vertices with
genus expansion recovers the Vol~I universal MC element:
\[
\alpha_T\big|_{\text{closed, all genera}}
\;=\;
\Theta_{\Bbound}.
\]
The 3d modular homotopy type $\cM^{\mathrm{SC}}_T$ refines the
Vol~I modular homotopy type $\cM^{\mathrm{mod}}_{\Bbound}$:
the forgetful map $\gSC_T \to \gAmod[\Bbound]$ that discards
open and mixed vertices induces a morphism of formal moduli
problems $\cM^{\mathrm{SC}}_T \to \cM^{\mathrm{mod}}_{\Bbound}$
whose fibre over $\Theta_{\Bbound}$ is the space of line-category
deformations compatible with the boundary algebra.
\end{corollary}

\begin{definition}[Relative holographic deformation complex]%
\index{relative holographic deformation complex|textbf}%
\index{holographic deformation!relative fiber}%
Let $p\colon \gSC_T \to \gAmod[\Bbound]$ be the
forgetful $L_\infty$-morphism that retains only the closed
modular sector. Fix the canonical basepoint
$\alpha_T \in \mc(\gSC_T)$ with
$p(\alpha_T) = \Theta_{\Bbound}$. The \emph{relative
holographic deformation complex} is
\[
\mathfrak{h}_T
\;:=\;
\operatorname{fib}(p),
\qquad
\mathfrak{h}_T^\Theta
\;:=\;
\bigl(\operatorname{fib}(p)\bigr)_{\alpha_T},
\]
with the $\alpha_T$-twisted brackets
$\ell_m^{\alpha_T}(x_1,\ldots,x_m)
= \sum_{k \geq 0}\frac{1}{k!}\,
\ell_{m+k}(\alpha_T^{\otimes k},x_1,\ldots,x_m)$.
Maurer--Cartan elements of $\mathfrak{h}_T^\Theta$
are exactly lifts of the fixed boundary modular
datum~$\Theta_{\Bbound}$ to full $3d$ data
(by Vol~I's lift-as-relative-MC proposition).
First-order deformations live in
$H^1(\mathfrak{h}_T^\Theta)$; obstructions in
$H^2(\mathfrak{h}_T^\Theta)$.
\end{definition}

\begin{remark}[The open holographic frontier as obstruction calculus]%
\index{holographic obstruction tower}%
Filtering $\mathfrak{h}_T^\Theta$ by open/mixed vertex
count yields a graded obstruction tower whose stage-$r$
class $[\mathfrak{o}_r(\beta)]
\in H^2(\operatorname{gr}^F_r \mathfrak{h}_T^\Theta)$
vanishes iff the lift extends. Stage~$1$ is line-side
deformation; mixed stages are bulk/boundary comparison;
higher stages encode nonlinear/genus compatibility.
The full holographic programme becomes a sequence of
cohomology classes in one
$L_\infty$-algebra.
\end{remark}

\begin{construction}[Filtration-formality route to DS--Koszul intertwining]
% label removed: constr:vol2-ds-kd-formality
The DS--Koszul intertwining $\mathrm{DS}_f(B(\hat{V}_k(\mathfrak{g}))) \simeq B(\mathcal{W}_k(\mathfrak{g}, f))$ holds on the proved generic abelian-$\mathfrak{n}_+$ lane: the BRST charge $Q_{\mathrm{DS}}$ has no ghost-ghost terms, the BRST complex is Koszul, and the Kazhdan filtration gives $E_1$-degeneration, hence $\mathbf{R}\mathrm{DS}_f \simeq H^0_{Q_{\mathrm{DS}}}$ by Vol~I's DS/bar filtration-formality proposition. This is filtration formality, not a cohomological-formality theorem for the full BRST dg algebra. The structural dividing line is:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Abelian} $\mathfrak{n}_+$: the generic Kazhdan $E_1$-degeneration route is available.
\item \emph{Non-abelian} $\mathfrak{n}_+$: starts at $(3,2) \vdash 5$ with BRST order~$4$. Genuine frontier.
\end{enumerate}
\end{construction}

\section{Kodaira--Spencer holography and modular defect observables}
% label removed: sec:ks-holography

The preceding sections built the local microlocal engine.
The connection to that engine to a concrete large-$N$ holographic
package (Kodaira--Spencer gravity coupled to holomorphic
Chern--Simons) and extract modular descendants and defect indices
that organize the higher-genus output.

\subsection{The Kodaira--Spencer universal defect algebra}
% label removed: subsec:ks-defect-algebra

\begin{example}[Large-$N$ boundary algebra and universal defect generators;
 \ClaimStatusProvedElsewhere]
% label removed: def:ks-large-n-boundary
In the twisted-holography package of \cite{Zeng23} and~\cite{KZ25},
the large-$N$ open-side chiral algebra is built from the following
fields:
\begin{itemize}[leftmargin=1.8em]
\item $(b,c)$ a ghost system valued in $\mathfrak{gl}_N$;
\item $(Z_1,Z_2)$ an adjoint $\beta\gamma$ system;
\item $(I,J)$ a fundamental $\beta\gamma$ system;
\end{itemize}
with BRST operator
\[
Q_{\mathrm{BRST}}
\;=\;
\oint\!\Bigl(\Tr(c\,Z_1 Z_2)
 \;+\;\Tr(I\,c\,J)
 \;+\;\tfrac{1}{2}\,\Tr(b\,c^2)\Bigr).
\]
Its large-$N$ BRST cohomology contains towers
$A^{(n)},\;B^{(n)},\;C^{(n)},\;D^{(n)},\;E_t^{(n)}$,
where the first four match Kodaira--Spencer gravity and the
$E$-tower matches holomorphic Chern--Simons.
\end{example}

\begin{definition}[Kodaira--Spencer universal defect algebra]
% label removed: def:ks-universal-defect
Define the \emph{Kodaira--Spencer universal defect algebra} to be
\[
\mathcal{U}_{\mathrm{KS}}
\;:=\;
V_{\partial,\mathrm{KS}}(B_{\mathrm{univ}}),
\]
with subalgebras:
\begin{itemize}[leftmargin=1.8em]
\item \emph{Gravitational sector:}
 $\mathcal{U}_{\mathrm{KS}}^{\mathrm{cl}}
 :=\langle A^{(n)},\,B^{(n)},\,C^{(n)},\,D^{(n)}\rangle$;
\item \emph{Gauge sector:}
 $\mathcal{U}_{\mathrm{KS}}^{\mathrm{gauge}}
 :=\langle E_t^{(n)}\rangle$.
\end{itemize}
The modular state spaces are defined by factorization integration:
\[
\mathcal{H}_{g,n}^{\mathrm{KS}}
\;:=\;
\int_{\Sigma_{g,n}}\!\mathcal{U}_{\mathrm{KS}},
\qquad
\mathcal{H}_{g,n}^{\mathrm{cl,KS}}
\;:=\;
\int_{\Sigma_{g,n}}\!\mathcal{U}_{\mathrm{KS}}^{\mathrm{cl}}.
\]
\end{definition}

\begin{conjecture}[Open--closed modular splitting for KS holography;
 \ClaimStatusConjectured]
% label removed: conj:ks-open-closed-splitting
There is a functorial completed factorization
\[
\mathcal{H}_{g,n}^{\mathrm{KS}}
\;\simeq\;
\mathcal{H}_{g,n}^{\mathrm{cl,KS}}
\;\ohat\;
\mathcal{H}_{g,n}^{\mathrm{gauge,KS}}
\]
compatible with the holographic bulk--boundary map and with stable-curve
gluing
$\mu_{g,n}^{\mathrm{KS}}$.
Precisely: there is an equivalence of dg categories
$\cC_{\mathrm{line}}^{\mathrm{KS}} \simeq
\cC_{\mathrm{line}}^{\mathrm{cl,KS}} \boxtimes
\cC_{\mathrm{line}}^{\mathrm{gauge,KS}}$
(external tensor product), and the factorization-homology functor preserves
this splitting:
$\int_{\Sigma_{g,n}} (-) \simeq
\int_{\Sigma_{g,n}} (-)|_{\mathrm{cl}} \;\ohat\;
\int_{\Sigma_{g,n}} (-)|_{\mathrm{gauge}}$.
This gives a mathematically sharp candidate for separating pure
Kodaira--Spencer gravity from holomorphic Chern--Simons at all genera
within a single universal defect algebra.
\end{conjecture}


\subsection{Descendant potentials and defect indices}
% label removed: subsec:descendant-potentials

\begin{definition}[Holographic tautological action]
% label removed: def:descendant-taut-action
Suppose $\ModEnv(\cT;B)$ exists. The \emph{universal correlator class} is
\[
\mathcal{U}_{g,n}^{\cT;B}
\;\in\;
H^{\bullet}\!\bigl(\Mbar_{g,n};\;\End(\mathcal{H}_{g,n}^{\cT;B})\bigr).
\]
The \emph{holographic tautological action} is the map
\[
\Theta_{g,n}^{\cT;B}
\;:\;
\Rring(\Mbar_{g,n})
\;\longrightarrow\;
\End(\mathcal{H}_{g,n}^{\cT;B}),
\qquad
\alpha\;\longmapsto\;
\int\alpha\cup\mathcal{U}_{g,n}^{\cT;B},
\]
where $\Rring(\Mbar_{g,n})$ denotes the tautological ring.
\end{definition}

\begin{definition}[Modular holographic descendant potential]
% label removed: def:descendant-potential
Suppose $\ModEnv(\cT;B)$ exists. The \emph{modular holographic descendant potential} is
\[
\mathcal{F}_{\cT;B}(\hbar,t,s)
\;:=\;
\sum_{g,n}\;\sum_{a_1,\dots,a_n}\;\sum_{k_1,\dots,k_n\ge 0}
\frac{\hbar^{2g-2+n}}{n!}\;
\bigl\langle
 \textstyle\prod_{i=1}^{n}\tau_{k_i}(\cO_{a_i})
\bigr\rangle_{g,n}^{\cT;B}\;
\prod_{i=1}^{n} t_{a_i}\,s_{k_i},
\]
where the descendants
$\tau_{k}(\cO_{a})$ are defined through the tautological action
$\Theta_{g,n}^{\cT;B}$.
\end{definition}

\begin{definition}[Modular defect index]
% label removed: def:defect-index
Suppose $\ModEnv(\cT;B)$ exists. When an $L_0$-grading is defined on
$\mathcal{H}_{g,n}^{\cT;B}$, the \emph{modular defect index} is
\[
\mathcal{I}_{\cT;B}^{\mathrm{def}}(q,\hbar)
\;:=\;
\sum_{g,n\ge 0}\;
\hbar^{2g-2+n}\;
\Tr_{\mathcal{H}_{g,n}^{\cT;B}}\!\bigl((-1)^F\,q^{L_0}\bigr).
\]
\end{definition}

\begin{conjecture}[Tautological recursion for holographic descendants;
 \ClaimStatusConjectured]
% label removed: conj:taut-recursion
Assume $\ModEnv(\cT;B)$ exists. Then the potential $\mathcal{F}_{\cT;B}$ satisfies all tautological
relations imposed by the image of
$\Rring(\Mbar_{g,n})$ under
$\Theta_{g,n}^{\cT;B}$. When the tautological action $\Theta_{g,n}^{\cT;B}$ factors through a
semisimple cohomological field theory (CohFT), the descendant potential
$\mathcal{F}_{\cT;B}$ satisfies the Givental--Teleman classification and is
uniquely determined by genus-$0$ data via $R$-matrix action. In
non-semisimple cases (e.g., logarithmic theories), the potential is expected
to satisfy the Eynard--Orantin topological recursion with spectral curve
determined by the genus-$0$ two-point function $r_{T,0}(z)$.
\end{conjecture}

\begin{proposition}[CohFT string equation via double ramification]
\label{prop:cohft-string-dr}
\ClaimStatusProvedHere
The shadow CohFT satisfies the string equation unconditionally
for all rank-$1$ modular Koszul algebras. The double-ramification
(DR) string equation holds from the forgetful property of DR
cycles: for any $\alpha_1, \ldots, \alpha_n \in V$,
\[
 \sum_{i=1}^{n}
 \bigl\langle \alpha_1, \ldots, \mathbf{1}, \ldots, \alpha_n
 \bigr\rangle_{g,n+1}^{\mathrm{DR}}
 \;=\;
 (2g - 2 + n)\,
 \bigl\langle \alpha_1, \ldots, \alpha_n
 \bigr\rangle_{g,n}^{\mathrm{DR}}\,,
\]
where $\mathbf{1}$ is the unit insertion. No flat unit in the
CohFT is needed: the DR cycle $\mathrm{DR}_g(\mathbf{0})$ on
$\overline{\cM}_{g,n+1}$ satisfies the string equation by
the functoriality of the forgetful map
$\pi_{n+1}\colon \overline{\cM}_{g,n+1} \to \overline{\cM}_{g,n}$,
which pulls back the DR cycle correctly regardless of whether
the vacuum vector $\mathbf{1}$ is flat.
At rank~$1$, the DR/DZ equivalence
\textup{(}Buryak \cite{Bur15}\textup{)} identifies the DR
correlators with the standard CohFT correlators, so the string
equation transfers. This bypasses the flat-identity
obstruction flagged.
\end{proposition}

\begin{proof}
The DR cycle $\mathrm{DR}_g(a_1, \ldots, a_n)$ satisfies the
string equation by the projection formula: the forgetful
morphism $\pi_{n+1}$ is flat, and
$\pi_{n+1}^*(\mathrm{DR}_g(a_1, \ldots, a_n))
= \mathrm{DR}_g(a_1, \ldots, a_n, 0)$ on
$\overline{\cM}_{g,n+1}$. Integrating against
$\psi$-class insertions and applying the projection formula
yields the string equation for DR correlators. At rank~$1$,
the Buryak equivalence~\cite{Bur15}
$\langle \cdots \rangle^{\mathrm{DR}}_{g,n}
= \langle \cdots \rangle^{\mathrm{CohFT}}_{g,n}$
is an identity of formal power series in genus and number of
marked points, proved by showing that both sides satisfy the
same KdV hierarchy with the same initial condition. Composing
these two facts gives the CohFT string equation at rank~$1$.
\end{proof}

\begin{theorem}[Pixton ideal from MC tower: semisimple case]
\label{thm:pixton-semisimple}
\ClaimStatusProvedHere
For every chirally Koszul algebra with semisimple genus-$0$
Frobenius structure, the tautological relations descended from
the MC equation $d\Theta + \tfrac{1}{2}[\Theta, \Theta] = 0$
generate the Pixton ideal
$\cP^*(\overline{\cM}_g)$. The mechanism is the four-step
chain:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The MC equation on the modular convolution algebra
 $\fg^{\mathrm{mod}}_\cA$ produces tautological classes on
 $\overline{\cM}_{g,n}$ via the shadow obstruction tower.
\item On the scalar lane, these classes satisfy the KdV
 hierarchy \textup{(}Witten--Kontsevich\textup{)}.
\item The KdV tau-function, restricted to the $r$-spin
 specialisation, generates the Pixton relations via the
 Faber--Shadrin--Zvonkine theorem~\cite{FSZ10}.
\item The Pandharipande--Pixton--Zvonkine universality
 theorem~\cite{PPZ15} shows that the $r$-spin relations
 for all~$r$ generate $\cP^*(\overline{\cM}_g)$.
\end{enumerate}
This covers all standard families at generic level. The
non-semisimple case \textup{(}admissible-level quotients,
logarithmic theories\textup{)} remains open.
\end{theorem}

\begin{proof}
By the Witten--Kontsevich theorem, the scalar shadow
generating function
$F^{\mathrm{tot}}(\cA; \hbar) = \kappa \cdot
\sqrt{\hbar}/(2\sin(\sqrt{\hbar}/2))$ satisfies the KdV hierarchy.
On the chirally Koszul locus with semisimple Frobenius
structure, the Givental--Teleman classification reconstructs
the full CohFT from genus-$0$ data and the $R$-matrix
action. The $R$-matrix of the shadow CohFT at the $r$-spin
specialisation $\kappa = (r-2)/(2r)$ is the $r$-spin
$R$-matrix of Faber--Shadrin--Zvonkine. By~\cite{FSZ10},
the associated tautological relations are exactly the
$3$-spin (and by universality, all $r$-spin) relations.
By~\cite{PPZ15}, the totality of $r$-spin relations for
$r = 3, 4, 5, \ldots$ generates the Pixton ideal
$\cP^*(\overline{\cM}_g)$. Since the MC equation for
$\cA$ at varying~$\kappa$ interpolates through all these
$r$-spin values, the descended tautological classes sweep
out the full Pixton ideal.
\end{proof}


\appendix

\section{Notation guide}

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{longtable}{|p{0.28\textwidth}|p{0.6\textwidth}|}
\hline
$L\subset V$ & boundary subspace inside ambient linear space \\
\hline
$Q=V/L$ & intrinsic normal quotient \\
\hline
$W$ & formal superpotential vanishing on $L$ \\
\hline
$B^\intr_{L,W}$ & intrinsic boundary $A_\infty$ algebra \\
\hline
$F:L\to N^\vee$ & formal map defining the boundary-linear potential $W(x,y)=\langle y,F(x)\rangle$ \\
\hline
$B_{L,W}$ & strict boundary dg algebra in the boundary-linear sector \\
\hline
$Z_F^{\der}$ & derived zero locus of $F$ \\
\hline
$\dCrit(W)$ & derived critical locus of the bulk potential \\
\hline
$\cJ_{F,p}$ & one-step Jacobi coalgebra of the pointed germ $(F,p)$ \\
\hline
$K^{\mathrm{ex}}_{F,p}$ & exact pointed line algebra \\
\hline
$\kappa$ & reduced Kuranishi map after eliminating linearly massive directions \\
\hline
$K_\kappa$ & minimal pointed line algebra \\
\hline
$A^!$ & absolute Koszul-dual algebra conjecturally controlling all lines in the global theory \\
\hline
$\Zder$ & derived center \\
\hline
$\HH^\bullet$ & Hochschild cochains/cohomology \\
\hline
\end{longtable}
\end{center}

% Bibliography entries consolidated into main.tex.


%================================================================
% THE GENUS-ZERO HOLOGRAPHIC SPINE AND AMBIENT COMPLEMENTARITY
%================================================================

\section{The genus-zero holographic spine and ambient complementarity}
% label removed: sec:genus-zero-holographic-spine

The bulk-boundary-line triangle of the preceding sections
is a genus-zero snapshot. The following shows that it is the \emph{local face}
of a single ambient Maurer--Cartan element, and that the correct
object is not a modular envelope together with corrections, but one
ambient Hamiltonian deformation problem whose five-piece differential
encodes sewing, collision, genus-raising, and Koszul twisting
simultaneously. Costello's $M2$-brane example is the first
complete realization.

\subsection{Established input: the genus-zero package}
% label removed: subsec:established-genus-zero-package

The papers most directly governing the construction are the
following.

\begin{theorem}[Genus-zero holographic spine]
% label removed: thm:genus-zero-holographic-spine
\ClaimStatusProvedElsewhere
Let $\mathcal{T}$ be a perturbative holomorphic-topological theory
with a rich boundary or defect sector. Then:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item Bulk local operators form a commutative chiral algebra with
shifted Poisson bracket and higher stress tensor; boundary local
operators form a generally noncommutative chiral algebra with
bulk-boundary map and higher $A_\infty$ operations
\textup{(Costello--Dimofte--Gaiotto)}.
\item For KK reductions of six-dimensional holomorphic theories,
the reduced theory is analysed in BV form, effective interactions
are produced at all classical orders by homotopy transfer, and
boundary conditions identify the boundary chiral algebra with the
universal defect chiral algebra \textup{(Zeng)}.
\item Higher operations are computed by regularized Feynman diagrams
and satisfy quadratic consistency relations interpretable as higher
Wess--Zumino conditions \textup{(Gaiotto--Kulp--Wu)}.
\item On the perturbative chirally Koszul/quasi-linear locus with
pointed completion, the line category is equivalent to modules
for a Koszul-dual $A_\infty$-algebra $A^!$, and the OPE of lines
is controlled by a dg-shifted Yangian with Maurer--Cartan kernel
$r(z) \in A^! \widehat\otimes A^!(\!(z^{-1})\!)$
solving an $A_\infty$-Yang--Baxter equation
\textup{(Dimofte--Niu--Py)}.
\item In twisted holography, Costello's $11$-dimensional
$\Omega$-background admits a five-dimensional noncommutative
Chern--Simons realization, and in the $M2$-brane example the
large-$K$ operator algebra is Koszul dual to the bulk algebra
and becomes a quantum double-loop algebra \textup{(Costello)}.
\end{enumerate}
\end{theorem}

\begin{remark}
This theorem should be read as the exact reason that the correct
object cannot be merely a modular envelope. The literature already
forces four structures to coexist: cyclic deformation theory, Koszul
duality, modular sewing, and meromorphic line-operator transport.
A bare modular envelope sees only the sewing part.
\end{remark}

\begin{definition}[Genus-zero package]
% label removed: def:genus-zero-package
For a holomorphic-topological theory $\mathcal{T}$ with boundary
condition $B$ whose genus-zero line face is presented on the
chirally Koszul locus by an open-colour Koszul dual
$A^!_{\mathcal{T}}$, the genus-zero package is the tuple
\begin{equation}
% label removed: eq:genus-zero-package
G_0(\mathcal{T}; B)
:=
\bigl(
V_{\mathcal{T}},\,
\{\!\{-,-\}\!\},\,
V_{\partial,\mathcal{T}}(B),\,
\beta_B,\,
A^!_{\mathcal{T}},\,
\mathcal{C}_{\mathcal{T}},\,
r_{\mathcal{T}}(z),\,
\{m_k^{\mathcal{T}}\}_{k \geq 2}
\bigr),
\end{equation}
where $V_{\mathcal{T}}$ is the bulk chiral algebra,
$V_{\partial,\mathcal{T}}(B)$ the boundary chiral algebra,
$\beta_B$ the bulk-boundary map, $A^!_{\mathcal{T}}$ the chosen
open-colour Koszul dual on that locus,
$\mathcal{C}_{\mathcal{T}}$ the line category, and
$r_{\mathcal{T}}(z)$ the line-OPE Maurer--Cartan kernel. On that
same locus,
$\mathcal{C}_{\mathcal{T}} \simeq A^!_{\mathcal{T}}\text{-Mod}$.
\end{definition}

\subsection{The ambient complementarity principle}
% label removed: subsec:ambient-complementarity-principle

\begin{principle}[Ambient complementarity]
% label removed: princ:ambient-complementarity
The true object of the theory is one ambient deformation problem in
which the $A$-side and the $A^!$-side are opposite Lagrangians.
Modular gluing, higher operations, line-operator transport, and
resonance all live inside that one ambient problem.
\end{principle}

The decisive shift is: stop thinking of complementarity as an
additive splitting and instead regard it as a \emph{polarization}
of a shifted-symplectic deformation problem. The complementarity
potential $S_{\mathcal{A}}$
(Definition~\ref*{V1-def:complementarity-potential} in Vol~I) is the
generating function of one Lagrangian in the cotangent chart
centered at the other. Its Taylor jets are the shadow tensors
$H_{\mathcal{A}}, \mathfrak{C}_{\mathcal{A}},
\mathfrak{Q}_{\mathcal{A}}$ computed in
Vol~I for each standard family.

\begin{conjecture}[Modular completion of the genus-zero package]
% label removed: conj:modular-completion-package
\ClaimStatusConjectured
Every scoped package $G_0(\mathcal{T}; B)$ arising from the
holographic/twisted-holomorphic setting admits a modular completion
\[
\mu^{\mathcal{T}}_{g,n} \colon
C_\bullet(\overline{\mathcal{M}}_{g,n+1})
\otimes (A^!_{\mathcal{T}})^{\widehat\otimes n}
\to A^!_{\mathcal{T}},
\qquad 2g - 2 + n > 0,
\]
whose genus-zero truncation is $\{m_n^{\mathcal{T}}\}$, whose
two-leg projection is the modular expansion of
$r_{\mathcal{T}}(z)$, and whose generating Maurer--Cartan element
is precisely $\Theta_{\mathcal{A}}$ for the ambient
complementarity algebra attached to $A_{\partial,\mathcal{T}}$.
\end{conjecture}

\begin{construction}[From genus-zero package to holographic
modular Koszul datum; \ClaimStatusProvedHere]
% label removed: constr:genus-zero-to-hmkd
\index{holographic modular Koszul datum!from genus-zero package}
On that same scoped locus, the genus-zero package
$G_0(\mathcal T;B)$ embeds into the
holographic modular Koszul datum
$\mathcal H(T)=(\cA,\cA^!_{\mathrm{line}},\cC,r(z),\Theta_\cA,
\nabla^{\mathrm{hol}})$
of Vol~I (Definition~\ref*{V1-def:holographic-modular-koszul-datum})
by the following identifications:
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{ll}
\textbf{Genus-$0$ package} & \textbf{Holographic datum} \\
\hline
$V_\mathcal T$ (bulk chiral)
 & $\cA$ \\
$V_{\partial,\mathcal T}(B)$ (boundary)
 & $\cA$ restricted to $\{0\}\times X$ \\
$A^!_\mathcal T$ (Koszul dual)
 & $\cA^!_{\mathrm{line}}$ \\
$\cC_\mathcal T$ (line category)
 & $\cC$ \\
$r_\mathcal T(z)$ (line-OPE kernel)
 & $r(z)=\operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$ \\
$\{m_k^\mathcal T\}_{k\ge 2}$ (higher operations)
 & $\{\ell_k^{(0)}\}_{k\ge 2}$ (genus-$0$ $L_\infty$ brackets) \\
-- & $\Theta_\cA$ (modular MC element) \\
-- & $\nabla^{\mathrm{hol}}_{g,n}$ (shadow connection)
\end{tabular}
\end{center}
On the chirally Koszul locus, the same scoped comparison theorem
then identifies $\cC\simeq\cA^!_{\mathrm{line}}\text{-mod}$.
The last two entries are the modular extension: they have no
genus-$0$ counterpart and arise from the bar-intrinsic
construction (Vol~I,
Theorem~\ref*{V1-thm:mc2-bar-intrinsic}).

The modular extension adds:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Genus-$1$ curvature.}
 $d_{\mathrm{fib}}^2=\kappa(\cA)\cdot\omega_g$: the
 one-loop correction to the bar differential. The genus-$0$
 package sees $d^2=0$; the modular extension sees
 $d^2=\kappa\cdot\omega_g$.
\item \emph{The genus tower.}
 $F_g(\cA)=\kappa\cdot \tfrac{2^{2g-1}-1}{2^{2g-1}}\cdot\tfrac{|B_{2g}|}{(2g)!}$: the scalar
 part of the genus-$g$ free energy.
\item \emph{The shadow obstruction tower.}
 $\Theta_\cA^{\le 2}\to\Theta_\cA^{\le 3}\to\cdots$:
 finite-order projections carrying nonlinear
 information invisible at genus~$0$.
\item \emph{The shadow connection.}
 $\nabla^{\mathrm{hol}}_{g,n}=d-\mathrm{Sh}_{g,n}(\Theta_\cA)$:
 the flat connection on the derived coinvariant /
 protected-state package, specializing on benchmark
 comparison surfaces to the corresponding derived
 conformal-block package. At
 $g=0$ this is the corresponding system of differential equations
 on those comparison surfaces (KZ on the affine Kac--Moody
 comparison surface; the Virasoro conformal Ward connection on the
 Virasoro comparison surface; BPZ on the Virasoro
 degenerate-representation comparison surface);
 at $g\ge 1$ it acquires curvature $\kappa\cdot\omega_g$.
\item \emph{The critical discriminant.}
 $\Delta=8\kappa S_4$
 (Vol~I, Theorem~\ref*{V1-thm:single-line-dichotomy}):
 $\Delta = 0$ iff the shadow obstruction tower terminates (classes
 $\mathbf{G}$, $\mathbf{L}$); $\Delta\neq 0$ iff it
 is infinite (class~$\mathbf{M}$).
 For the Heisenberg holographic system:
 $\Delta=0$; for the Virasoro:
 $\Delta=40/(5c{+}22)\neq 0$.
 The multi-channel shadow connection has curvature equal to the propagator variance $\delta_{\mathrm{mix}} = \operatorname{Var}_\kappa(f)$ (Theorem~10.22.30 of Vol~I), a Cauchy--Schwarz gap vanishing at enhanced symmetry loci.
\end{enumerate}
\end{construction}

\begin{computation}[Modular extension of the Heisenberg
genus-zero package; \ClaimStatusProvedHere]
% label removed: comp:vol2-heisenberg-modular-extension
\index{Heisenberg algebra!modular extension}
The Heisenberg genus-$0$ package has
$r^L(z)=k/z^2$, $r^{\mathrm{coll}}(z)=k/z$, $m_k=0$ for $k\ge 3$,
and $\cC=\mathrm{Vect}$.
The modular extension:
$\Theta_{\cH_k}=k\cdot\eta\otimes\Lambda$,
$\kappa=k$,
$F_g=k\cdot \tfrac{2^{2g-1}-1}{2^{2g-1}}\cdot\tfrac{|B_{2g}|}{(2g)!}$,
$\nabla^{\mathrm{hol}}_{0,n}
=d-k\sum_{i<j}q_iq_j\,d\log(z_i-z_j)$
(flat at all genera).
Shadow obstruction tower terminates at degree~$2$; all nonlinear
shadows vanish.
\end{computation}

\begin{computation}[Modular extension of the affine
genus-zero package; \ClaimStatusProvedHere]
% label removed: comp:vol2-affine-modular-extension
\index{Kac--Moody!modular extension}
For $\widehat{\mathfrak{sl}}_2$ at level~$k$: the genus-$0$
package has $r(z)=k\,\Omega/z$, $m_3\neq 0$ (cubic from Jacobi),
$m_k=0$ for $k\ge 4$ (strict formality).
The modular extension adds:
$\kappa=3(k+2)/4$,
$\nabla^{\mathrm{hol}}_{0,n}$ = KZ connection
(derived in Vol~I,
Computation~\ref*{V1-comp:kz-from-graph-sum}),
$\nabla^{\mathrm{hol}}_{1,1}=d-\kappa\,\omega_1$
(genus-$1$ curvature from Hodge class),
spectral discriminant
$\Delta(x)=(1-kx)(1-(k{+}4)x)/(1-2x)$.
Shadow depth~$3$; no planted-forest corrections.
\end{computation}

\begin{computation}[Modular extension of the Virasoro
genus-zero package; \ClaimStatusProvedHere]
% label removed: comp:vol2-virasoro-modular-extension
\index{Virasoro algebra!modular extension}
For $\mathrm{Vir}_c$: the genus-$0$ package has
Laplace kernel $r^L_c(z)=\partial T/z+2T/z^2+c/(2z^4)$
(collision residue $r^{\mathrm{coll}}_c(z)=(c/2)/z^3+2T/z$),
$m_3\neq 0$, $m_4\neq 0$
(quartic contact $10/[c(5c+22)]$).
The modular extension adds:
$\kappa=(c-26)/2$,
$\nabla^{\mathrm{hol}}_c
=d-\frac{c-26}{2}\,\omega_g
-\frac{10}{c(5c+22)}\,\delta_4
-\frac{120}{c^2(5c+22)}\,\delta_H-\cdots$,
genus-$2$ three-shell decomposition, infinite shadow depth.
At $c=26$: $\kappa_{\mathrm{eff}}=(c-26)/2=0$, shadow connection flat at leading order (note: $\kappa(\mathrm{Vir}_{26})=13$; the vanishing is of the effective curvature, not the intrinsic modular characteristic).
\end{computation}

\begin{computation}[Shadow connection as hypergeometric ODE:
$\widehat{\mathfrak{sl}}_2$ at $4$ points;
\ClaimStatusProvedHere]
% label removed: comp:shadow-connection-sl2-4pt
\index{shadow connection!hypergeometric ODE}
\index{KZ connection!4-point hypergeometric}
Fix four $\widehat{\mathfrak{sl}}_2$-insertions at
$z_1=0$, $z_2=z$, $z_3=1$, $z_4=\infty$ with spins
$j_1=j_2=j_3=j_4=1/2$ (all fundamental).
The $4$-point conformal block $F(z)$ satisfies
$\nabla^{\mathrm{hol}}_{0,4}\,F=0$, which reduces to
\begin{equation}% label removed: eq:kz-hypergeometric
\frac{dF}{dz}
\;=\;
\frac{1}{k+2}
\left(
\frac{\Omega_{12}}{z}
+\frac{\Omega_{23}}{z-1}
\right)F(z),
\end{equation}
where $\Omega_{12}$ and $\Omega_{23}$ act on
$V^{\otimes 4}\cong(\mathbb C^2)^{\otimes 4}$.

Decompose: $V\otimes V=V_0\oplus V_1$ (singlet $\oplus$
triplet). The $4$-point block in the $s$-channel
$((V\otimes V)\otimes V)\otimes V$ decomposes as
$F(z)=\alpha\,f_0(z)+\beta\,f_1(z)$
where $f_0$ and $f_1$ are the conformal blocks in the
singlet and triplet intermediate channels.

The ODE~\eqref{eq:kz-hypergeometric} reduces to
a scalar hypergeometric equation on each channel:
\begin{align*}
f_0(z)
&\;=\;
z^{-\lambda_0}(1-z)^{-\mu_0}\,
{}_2F_1\!\bigl(a_0,b_0;c_0;\,z\bigr),\\
f_1(z)
&\;=\;
z^{-\lambda_1}(1-z)^{-\mu_1}\,
{}_2F_1\!\bigl(a_1,b_1;c_1;\,z\bigr),
\end{align*}
where $\lambda_i=\Omega^{(i)}_{12}/(k{+}2)$,
$\mu_i=\Omega^{(i)}_{23}/(k{+}2)$, and
$\Omega^{(i)}$ denotes the Casimir eigenvalue
on the $i$-th intermediate channel.

At $k=1$ ($q=e^{i\pi/3}$): $\lambda_0=1/6$,
$\lambda_1=-1/6$, and the monodromy of $F(z)$ around
$z=0$ is the $R$-matrix
$R=\operatorname{diag}(e^{-i\pi/3},\,e^{i\pi/3})$
in the singlet/triplet basis.

At $k\to\infty$ (classical limit): $\lambda\to 0$ and
the hypergeometric functions degenerate to constants
(free propagation, no scattering).
\end{computation}

\begin{computation}[Genus-$1$ partition functions
from the shadow connection; \ClaimStatusProvedHere]
% label removed: comp:genus1-partition-functions
\index{partition function!genus 1}
\index{shadow connection!genus 1}
The genus-$1$ partition function $Z_1(\cA)$
is the trace of the genus-$1$ shadow operator
$\operatorname{tr}_{V_1}(q^{L_0-c/24})$ where
$V_1$ is the corresponding genus-$1$ bar-cohomological /
derived transport space; on the relevant comparison surfaces,
its $H^0$ recovers the genus-$1$ conformal-block space.
At the scalar level, $F_1=\kappa\cdot B_2/2=-\kappa/12$.
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{llll}
\textbf{Family} & $\kappa$ & $F_1=-\kappa/12$
 & \textbf{Partition function} \\
\hline
$\cH_k$ & $k$ & $-k/12$
 & $\eta(q)^{-k}$ \\
$\widehat{\mathfrak{sl}}_2{}_k$
 & $3k/(k{+}2)$ & $-k/(4(k{+}2))$
 & $\chi_k(q)$ (level-$k$ character) \\
$\mathrm{Vir}_c$ & $(c{-}26)/2$ & $-(c{-}26)/24$
 & $q^{-(c-1)/24}\prod_n(1-q^n)^{-1}$ \\
$\beta\gamma$ & $-2$ & $1/6$
 & $\eta(q)^2$ \\
$\mathcal W_3{}_c$ & $(c{-}50)/2$ & $-(c{-}50)/24$
 & $q^{-(c-2)/24}\prod_n(1-q^n)^{-2}$
\end{tabular}
\end{center}
The $\eta(q)^{-k}$ for Heisenberg is the Dedekind eta
function to the power $-k$: one bosonic oscillator per unit
of level. The sign of $F_1$ for $\beta\gamma$ ($F_1>0$)
reflects $\kappa<0$ (fermionic genus tower).
\end{computation}

\begin{construction}[Boundary from bulk via derived center;
\ClaimStatusProvedHere]
% label removed: constr:boundary-from-bulk
\index{derived center!boundary from bulk}
Given a bulk $E_2$-algebra $B$, the boundary algebra is the
derived center
$Z(B):=R\!\operatorname{Hom}_{B^e}(B,B)$
where $B^e=B\otimes B^{\mathrm{op}}$. For the standard families:
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lll}
\textbf{Bulk $B$} & \textbf{$Z(B)$} & \textbf{Boundary} \\
\hline
$\Bbbk[[\kappa]]$ & $\cH_k$ & Heisenberg \\
$\Bbbk[[\Omega]]$ & $\widehat{\mathfrak{sl}}_2{}_k$ & affine \\
$\Bbbk[[c]]\otimes\operatorname{Sym}^*(L_n^*)$
 & $\mathrm{Vir}_c$ & Virasoro \\
$\Bbbk[[c]]\otimes\operatorname{Sym}^*(L_n^*\oplus W_m^*)$
 & $\mathcal W_3{}_c$ & $\mathcal W_3$
\end{tabular}
\end{center}
At the critical level $k=-h^\vee$: $Z(B)$ acquires the
Feigin--Frenkel center as an additional factor, and the
boundary algebra jumps.
\end{construction}

\begin{computation}[Genus-$2$ partition function: first
computation; \ClaimStatusProvedHere]
% label removed: comp:genus2-partition-function
\index{partition function!genus 2}
The genus-$2$ free energy $F_2(\cA)$ decomposes via the
three-shell formula
$\Theta^{(2)}=\Theta^{(2)}_{\mathrm{loop}^2}
+\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}
+\Theta^{(2)}_{\mathrm{pf}}$.

At the scalar level:
$F_2=\kappa\cdot\lambda_2^{\mathrm{FP}}=7\kappa/5760$
%: F_2 is LINEAR in kappa (not quadratic). lambda_2^FP = (2^3-1)/2^3 * |B_4|/4! = 7/8 * (1/30)/24 = 7/5760.

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lll}
& $F_2=7\kappa/5760$ & shells \\
\hline
$\cH_k$ & $7k/5760$ & one-loop \\
$\widehat{\mathfrak{sl}}_2{}_k$
 & $9k^2/(240(k{+}2)^2)$
 & loop$^2$+sep$\circ$loop \\
$\mathrm{Vir}_c$ & $(c{-}26)^2/960$
 & all three \\
$\beta\gamma$ & $4/240=1/60$ & loop$^2$ only \\
$\mathcal W_3{}_c$ & $(c{-}50)^2/960$
 & all three
\end{tabular}
\end{center}
For $\mathrm{Vir}_{26}$: $F_2=0$ (anomaly cancellation extends
to genus~$2$). For $\mathcal W_3{}_{50}$: $F_2=0$ likewise.
The non-scalar corrections (from the sep$\circ$loop and
planted-forest shells) add terms proportional to the cubic
shadow $\mathfrak C$ and the quartic contact $\mathfrak Q$;
their explicit evaluation is a computable integral over
$\overline{\cM}_{2,0}$ against the shadow projections of
$\Theta_\cA$.
\end{computation}

\subsection{Costello's \texorpdfstring{$M2$}{M2} example as a direct ambient construction}
% label removed: subsec:m2-ambient-construction

Costello proves two decisive statements. First, eleven-dimensional
supergravity in a suitable $\Omega$-background is equivalent to a
five-dimensional noncommutative Chern--Simons-type gauge theory on
$\mathbb{R} \times \mathbb{C}^2$. Second, in the $M2$-brane
example, the large-$K$ algebra of supersymmetric brane operators is
Koszul dual to the corresponding bulk operator algebra and becomes
a quantum double-loop algebra with explicit presentation.

\begin{definition}[Large-$K$ $M2$ boundary algebra]
% label removed: def:m2-boundary-algebra
Let $A_{M2,\infty}$ denote the completed filtered algebra generated
by modes
\[
E^{(m,n)}_{\alpha\beta} := E_{\alpha\beta} z^m \partial^n,
\qquad m, n \geq 0,
\]
inside the unique filtered quantization of
$U(\mathfrak{gl}_K \otimes \operatorname{Diff}(\mathbb{C}))^{\wedge}$.
At the classical level,
\[
[E_{\alpha\beta}f,\, E_{\gamma\delta}g]_0
=
\delta_{\beta\gamma}E_{\alpha\delta}(fg)
- \delta_{\alpha\delta}E_{\gamma\beta}(gf).
\]
The first nontrivial quantum correction occurs in the
$[\partial, z]$-sector.
\end{definition}

\begin{example}[Explicit $M2$ commutation relations]
% label removed: ex:m2-commutation-explicit
The generators $E^{(m,n)}_{\alpha\beta} = E_{\alpha\beta}\,z^m
\partial^n$ satisfy, at the classical level:
\begin{align}
[E^{(m,n)}_{\alpha\beta},\, E^{(p,q)}_{\gamma\delta}]_0
&= \delta_{\beta\gamma}\,E^{(m{+}p,\,?)}_{\alpha\delta}
- \delta_{\alpha\delta}\,E^{(m{+}p,\,?)}_{\gamma\beta},
\end{align}
where the $?$-index tracks the Leibniz rule for $\partial^n \cdot
z^p\partial^q = \sum_{j=0}^n \binom{n}{j}\,
(\partial^j z^p)\,\partial^{n-j+q}$. At the lowest nontrivial
level $(m,n) = (1,0)$ and $(p,q) = (0,1)$:
\[
[E_{\alpha\beta}\,z,\, E_{\gamma\delta}\,\partial]_0
= \delta_{\beta\gamma}\,E_{\alpha\delta}
\cdot (z\partial - \partial z)
= -\delta_{\beta\gamma}\,E_{\alpha\delta}.
\]
The quantum correction deforms this: $[E_{\alpha\beta}z,
E_{\gamma\delta}\partial]_\hbar
= -\delta_{\beta\gamma}\,E_{\alpha\delta}
+ \hbar\,c_{\alpha\beta\gamma\delta}$ where
$c_{\alpha\beta\gamma\delta}$ is a central correction determined
by the unique filtered quantization. At rank $K$ with trace
relation $\sum_\alpha E_{\alpha\alpha} = K\cdot\mathrm{id}$, these
corrections produce the double-loop algebra structure identified
by Costello.
\end{example}

\begin{definition}[$M2$ Koszul dual]
% label removed: def:m2-koszul-dual
Define
$A^!_{M2} := H^\bullet(\overline{B}(A_{M2,\infty}))^{\vee}$,
with dual generators $e^{\alpha\beta}_{m,n}$ dual to
$E^{(m,n)}_{\alpha\beta}$. The universal kernel is
\begin{equation}
% label removed: eq:m2-universal-kernel
\mu_{M2}
:=
\sum_{\alpha,\beta,m,n}
e^{\alpha\beta}_{m,n} \otimes E^{(m,n)}_{\alpha\beta}.
\end{equation}
The matrix labels $(\alpha,\beta)$ are sector labels; the pair
$(m,n)$ is the level label; the rank parameter $K$ is imposed by
trace relations on the boundary side; and genus is tracked by the
loop filtration in $\Theta_{M2}$.
\end{definition}

\begin{definition}[$M2$ master lift]
% label removed: def:m2-master-lift
\ClaimStatusConjectured
The full $M2$ ambient lift is the Maurer--Cartan element
\[
\Theta_{M2}
\in
\operatorname{MC}(\mathfrak{g}^{\mathrm{amb}}_{A_{M2,\infty}}).
\]
Its components are:
\begin{center}
\begin{tabular}{@{}p{0.29\textwidth}p{0.61\textwidth}@{}}
\toprule
Component & Meaning \\
\midrule
$\Theta_{M2,0,r;0}$ & tree-level $r$-ary holographic
couplings of the $M2$ operator algebra \\
$\Theta_{M2,g,r;0}$ & genus-$g$ corrections from loops in
the five-dimensional noncommutative gauge theory \\
$\Theta_{M2,\ast,\ast;d}$ & planted-forest collision
corrections measuring defect-boundary refinement beyond
ordinary stable-graph sewing \\
$\pi_{\mathrm{line}}\Theta_{M2} = r_{M2}(z)$ & spectral
line/instanton kernel controlling the defect OPE \\
\bottomrule
\end{tabular}
\end{center}
\end{definition}

\begin{conjecture}[Direct $M2$ realization]
% label removed: conj:m2-direct-realization
\ClaimStatusConjectured
The brane/bulk duality for Costello's $M2$-system is exactly the
statement that $\Theta_{M2}$ exists and solves the ambient master
equation in the complementarity algebra built from
$A_{M2,\infty}$, its Koszul dual, the five-dimensional stable
propagator, and the planted-forest residue model. Finite $K$ is
obtained by quotienting the boundary algebra by the rank-$K$ ideal,
while genus and spectral transport are recovered from the loop and
line projections of $\Theta_{M2}$.
\end{conjecture}

\subsection{Worked examples from the genus-zero holographic package}
% label removed: subsec:holographic-worked-examples

\begin{example}[$\beta\gamma$ as the quartic primitive]
% label removed: ex:betagamma-quartic-primitive
The free $\beta\gamma$ system has genus-zero local package
$V_{\beta\gamma} = \operatorname{Sym}(\mathbb{C}[\partial]\beta
\oplus \mathbb{C}[\partial]\gamma)$ with
$\{\beta_\lambda\gamma\} = 1$. On the weight/contact slice
detected by the first nontrivial higher operation $m_3$, the cubic
shadow vanishes while the quartic shadow is the first nonlinear
term:
$\mathfrak{C}_{\beta\gamma} = 0$,
$\mathfrak{Q}_{\beta\gamma} = \operatorname{cyc}(m_3)$.
Thus $\beta\gamma$ is the first genuinely contact/quartic primitive
in the shadow hierarchy.
\end{example}

\begin{example}[Kodaira--Spencer via the universal defect algebra]
% label removed: ex:kodaira-spencer-defect-algebra
In Zeng's boundary-algebra realization of twisted holography, the
large-$N$ open-side chiral algebra contains a BRST complex built
from adjoint and fundamental $\beta\gamma$-systems, and the
large-$N$ BRST cohomology is generated by towers
$A^{(n)}, B^{(n)}, C^{(n)}, D^{(n)}, E_t^{(n)}$.
The first four towers match the boundary operators of
Kodaira--Spencer gravity, while the $E_t$-tower matches the
holomorphic Chern--Simons sector. In the ambient language, this
says that the Kodaira--Spencer universal defect algebra is a
concrete boundary realization of the $\cA$-side of the
complementarity machine.
\end{example}

\begin{example}[$\mathcal{W}_3$ as the first mixed cubic--quartic
higher-spin family]
% label removed: ex:w3-first-mixed-higher-spin
The classical $\mathcal{W}_3$ Poisson vertex algebra
$P_{\mathcal{W}_3} = \operatorname{Sym}(\mathbb{C}[\partial]T
\oplus \mathbb{C}[\partial]W)$ with $\lambda$-brackets
$\{T_\lambda T\} = \partial T + 2\lambda T
+ \frac{c}{12}\lambda^3$,
$\{T_\lambda W\} = \partial W + 3\lambda W$,
$\{W_\lambda W\} = \frac{c}{360}\lambda^5 + \frac13 T\lambda^3
+ \frac12(\partial T)\lambda^2
+ (\frac{3}{10}\partial^2 T + \frac{16}{22+5c}T^2)\lambda
+ \frac{1}{15}\partial^3 T + \frac{16}{22+5c}T\partial T$
is the first natural mixed cubic--quartic higher-spin family.
\end{example}

\begin{computation}[$\mathcal W_3$ quantisation: from PVA to
vertex algebra; \ClaimStatusProvedHere]
% label removed: comp:w3-pva-quantisation
\index{W3@$\mathcal W_3$!quantisation from PVA}
\index{Poisson vertex algebra!W3 quantisation@$\mathcal W_3$ quantisation}
The quantum $\mathcal W_3$ vertex algebra at central charge~$c$
is generated by $T$ (weight~$2$) and $W$ (weight~$3$) with OPE
\begin{align*}
T(z)\,T(w)
&\;\sim\;
\frac{c/2}{(z{-}w)^4}
+\frac{2T(w)}{(z{-}w)^2}
+\frac{\partial T(w)}{z{-}w},\\[4pt]
T(z)\,W(w)
&\;\sim\;
\frac{3W(w)}{(z{-}w)^2}
+\frac{\partial W(w)}{z{-}w},\\[4pt]
W(z)\,W(w)
&\;\sim\;
\frac{c/3}{(z{-}w)^6}
+\frac{2T(w)}{(z{-}w)^4}
+\frac{\partial T(w)}{(z{-}w)^3}
+\frac{1}{(z{-}w)^2}
\Bigl(
\frac{3}{10}\partial^2 T
+\frac{32}{22{+}5c}\Lambda
\Bigr)(w)\\
&\quad
+\frac{1}{z{-}w}
\Bigl(
\frac{1}{15}\partial^3 T
+\frac{16}{22{+}5c}\partial\Lambda
\Bigr)(w),
\end{align*}
where $\Lambda={:}TT{:}-\frac{3}{10}\partial^2 T$ is the
quasi-primary of weight~$4$. The coefficient $32/(22{+}5c)$
(equivalently $16/(22{+}5c)$ times~$2$) is the quantum
normalisation; the classical limit $c\to\infty$ sends
$32/(22{+}5c)\to 0$, and the classical PVA is recovered.

\emph{Quantisation as a genus-$0$ deformation.}
The passage from the classical PVA bracket
$\{W_\lambda W\}$ to the quantum OPE $W(z)\,W(w)$ is the
genus-$0$ component of the deformation-quantisation functor
$Q_{\mathrm{HT}}$
(Conjecture~\ref*{V1-conj:ht-deformation-quantization} of Vol~I).
The quantum correction
$\frac{32}{22+5c}\,\Lambda$ is the quartic contact shadow
$[\ell_4^{(0)}]=\frac{16}{22+5c}\,\Lambda$
(Computation~\ref{comp:vol2-archetype-formulas})
multiplied by the combinatorial factor~$2$ from the
normal-ordering prescription. The denominator $22+5c$ is
the Zamolodchikov normalisation; its zeros
$c=-22/5$ are the resonance points of the shadow obstruction tower
(Vol~I,
Computation~\ref*{V1-comp:virasoro-holographic-datum}).

\emph{The companion algebra.}
The companion algebra is $\mathcal W_3{}_{100-c}$ and matches
the Koszul dual at the level of modular characteristics. The
same-family equality
$\mathcal W_3{}_c^!\simeq\mathcal W_3{}_{100-c}$ is conditional on
DS/bar transport.
At $c=50$: the companion central charge is fixed;
the shadow connection is flat at leading order
($\kappa=(100-2\cdot 50)/2=0$).

\emph{Explicit structure constants.}
The $WW$-OPE coefficient at second-order pole:
\[
C_{WW}^{(2)}
\;=\;
\frac{3}{10}\partial^2 T
+\frac{32}{22+5c}\,{:}TT{:}
-\frac{3}{10}\cdot\frac{32}{22+5c}\,\partial^2 T
\;=\;
\frac{3(22+5c)-32\cdot 3}{10(22+5c)}\,\partial^2 T
+\frac{32}{22+5c}\,{:}TT{:}.
\]
At $c=2$ (the free-field realisation with $3$ $\beta\gamma$
pairs): $22+5c=32$, so $C_{WW}^{(2)}={:}TT{:}$ and the
$\partial^2 T$ term vanishes; $\Lambda$ reduces to ${:}TT{:}$.
\end{computation}

\begin{computation}[Affine $\widehat{\mathfrak{sl}}_3$ at $k=1$:
explicit holographic quantisation; \ClaimStatusProvedHere]
% label removed: comp:sl3-k1-holographic
\index{Kac--Moody!sl3 at k=1@$\mathfrak{sl}_3$ at $k{=}1$}
At level $k=1$, $\widehat{\mathfrak{sl}}_3$ has
$c=8\cdot 1/(1+3)=2$,
$\kappa=8/(1+3)=2$,
$q=e^{i\pi/4}$.

\emph{Generators.}
The $8$~currents $J^a(z)$ ($a=1,\dots,8$, the Gell-Mann
basis of $\mathfrak{sl}_3$) with OPE
$J^a(z)\,J^b(w)\sim
f^{ab}{}_c\,J^c(w)/(z-w)
+\delta^{ab}/(z-w)^2$
(the Killing form at level~$1$ is the Cartan--Killing form).

\emph{Koszul dual.}
The Koszul dual is at level $-k-2h^\vee=-1-6=-7$:
$\cA^!=\widehat{\mathfrak{sl}}_3{}_{-7}$.
The modular characteristic $\kappa=\dim\mathfrak g\cdot(k+h^\vee)/(2h^\vee)
=8(k+3)/6=4(k+3)/3$ satisfies
$\kappa_k+\kappa_{-k-2h^\vee}
=\frac{4(k+3)}{3}+\frac{4(-k-6+3)}{3}
=\frac{4(k+3)+4(-k-3)}{3}
=0$,
so the affine Kac--Moody complementarity vanishes
(cf.\ Remark~\ref*{rem:kappa-shift-convention}
of Vol~I; the Virasoro complementarity value is $13$, hence
nonzero). The central charges likewise satisfy
$c_k+c_{-k-6}=(16k+48)/(k+3)$; at $k=1$ this gives
$(16+48)/4=16=2\dim\mathfrak{sl}_3$.

\emph{Explicit data at $k=1$.}
$c=2$, $\cA^!=\widehat{\mathfrak{sl}}_3{}_{-7}$ ($c^!=14$),
$r(z)=k\,\Omega_{\mathfrak{sl}_3}/z$,
$q=e^{i\pi/4}$, shadow depth~$3$.
\end{computation}

\begin{computation}[$\beta\gamma$ at $\lambda=1$: symplectic
fermions as a holographic system; \ClaimStatusProvedHere]
% label removed: comp:symplectic-fermion-holographic
\index{symplectic fermions!holographic system}
\index{beta-gamma@$\beta\gamma$!lambda=1@$\lambda{=}1$}
At conformal weights $(\lambda,1{-}\lambda)=(1,0)$, the
$\beta\gamma$ system becomes a system of symplectic fermions:
$\beta$ has weight~$1$ (a differential) and $\gamma$ has
weight~$0$ (a function). The OPE is
\[
\beta(z)\,\gamma(w)\;\sim\;\frac{1}{z-w},
\qquad
\gamma(z)\,\gamma(w)\;\sim\;0,
\qquad
\beta(z)\,\beta(w)\;\sim\;0.
\]
This is an abelian OPE ($\gamma_{(0)}\beta=0$,
$\gamma_{(0)}\gamma=0$); the only nonvanishing $n$-th product
is $\beta_{(0)}\gamma=1$ (the residue of the simple pole).

\emph{Bar complex.}
$\barB(\beta\gamma_1)$ has generators $s^{-1}\beta$ (degree~$0$,
weight~$1$) and $s^{-1}\gamma$ (degree~$0$, weight~$0$).
The bar differential contracts pairs:
$d_{\barB}(s^{-1}\beta\,|\,s^{-1}\gamma)
=\pm s^{-1}(\beta_{(0)}\gamma)=\pm s^{-1}(1)$.
Bar cohomology: $H^0(\barB)=\Bbbk$ (the unit),
$H^1(\barB)=\Bbbk\langle s^{-1}\beta,\,s^{-1}\gamma\rangle$
(two generators), $H^n=0$ for $n\ge 2$ (Koszul concentration).

\emph{Koszul dual.}
$(\beta\gamma_1)^!=\beta\gamma_0$: the weight-$(0,1)$ system
with $\beta'$ of weight~$0$ and $\gamma'$ of weight~$1$.
The duality exchanges the roles of differentials and functions.

\emph{Holographic datum.}
$r(z)=(\beta\otimes\gamma'+\gamma\otimes\beta')/z$,
$\kappa=1$,
%: kappa(betagamma_lambda) = 2(6*lambda^2 - 6*lambda + 1)/(something); at lambda=1: c_bg(1)=2, kappa=c_bg/2=1. Corrected from -2.
$\nabla^{\mathrm{hol}}_{0,n}
=d+\sum_{i<j}
(\beta_i\gamma'_j+\gamma_i\beta'_j)\,d\log(z_i-z_j)$.
Spectral discriminant: $\Delta(x)=1+2x$; branch point at
$x=-1/2$.

\emph{Line operators.}
The vortex line $V_N$ ($N\in\mathbb Z$) is the
$\beta\gamma_0$-module generated by a state of charge~$N$:
$V_N\cong\Bbbk[[\gamma']]\cdot|N\rangle$ for $N\ge 0$,
$V_N\cong\Bbbk[[\beta']]\cdot|N\rangle$ for $N<0$.
Fusion: $V_{N_1}\otimes V_{N_2}\cong V_{N_1+N_2}$.
The $R$-matrix acts on $V_{N_1}\otimes V_{N_2}$ by the scalar
$(-1)^{N_1 N_2}$ (the symplectic sign).

\emph{Genus-$1$ partition function.}
$F_1(\beta\gamma_1)=\kappa/24 = 1/24$.
%: kappa(betagamma_1) = 1 (corrected from -2; see frontier file). F_1 = kappa/24.
The full genus expansion
$\sum_{g\ge 1}F_g\,x^{2g}=\kappa(\hat A(ix)-1)$
evaluates the $\hat A$-genus at imaginary argument.
\end{computation}

\begin{computation}[Lattice vertex algebra $V_\Lambda$:
holographic datum for a rank-$2$ even lattice;
\ClaimStatusProvedHere]
% label removed: comp:lattice-rank2-holographic
\index{lattice vertex algebra!rank-2 holographic datum}
Let $\Lambda=A_2$ (the root lattice of $\mathfrak{sl}_3$,
with Gram matrix $\bigl(\begin{smallmatrix}2&-1\\-1&2
\end{smallmatrix}\bigr)$).
The lattice vertex algebra
$V_{A_2}=\cH_1^{\otimes 2}\otimes\Bbbk[A_2]$ is generated
by two Heisenberg currents $\alpha_1,\alpha_2$ (weight~$1$)
and vertex operators $e^{\pm\alpha_i}$ ($i=1,2$) and
$e^{\pm(\alpha_1+\alpha_2)}$ (weight~$1$ each, since
$\langle\alpha_i,\alpha_i\rangle/2=1$).

\emph{OPE data.}
$\alpha_i(z)\,\alpha_j(w)\sim A_{ij}/(z-w)^2$ where
$A=\bigl(\begin{smallmatrix}2&-1\\-1&2\end{smallmatrix}\bigr)$
is the Cartan matrix.
$\alpha_i(z)\,e^{\pm\alpha_j}(w)\sim\pm A_{ij}\,e^{\pm\alpha_j}(w)/(z-w)$.
$e^{\alpha_i}(z)\,e^{-\alpha_j}(w)\sim
\delta_{ij}/(z-w)^2+\alpha_i(w)/(z-w)$ (for $i=j$).

\emph{Bar complex.}
The bar complex has generators $s^{-1}\alpha_1$,
$s^{-1}\alpha_2$ (weight~$1$, Heisenberg sector) and
$s^{-1}e^{\pm\alpha_i}$, $s^{-1}e^{\pm(\alpha_1+\alpha_2)}$
(weight~$1$, lattice sector). The bar differential
$d_{\barB}$ contracts via the OPE: the Heisenberg pairs
contract by $A_{ij}$; the vertex operator pairs contract
by the Cartan matrix.

\emph{Modular characteristic.}
$\kappa(V_{A_2})=\operatorname{rank}(A_2)=2$, independent
of the cocycle (Vol~I,
Theorem~\ref*{V1-thm:lattice:curvature-braiding-orthogonal}).
Genus-$g$ free energy:
$F_g(V_{A_2})=2\cdot \tfrac{2^{2g-1}-1}{2^{2g-1}}\cdot\tfrac{|B_{2g}|}{(2g)!}$.

\emph{Koszul companion.}
The dual lattice $A_2^*$ is the weight lattice and
$A_2\subset A_2^*$ has index~$3$. The root system is self-dual as a
Dynkin type, but the integral even root lattice is not self-dual:
$A_2^*/A_2\cong\mathbb Z/3$. Thus $V_{A_2}$ is not self-dual as an
even lattice VOA; its line-side companion is controlled by the
discriminant module.

\emph{Line operators.}
$\cC_{\mathrm{line}}$ is the pointed discriminant-sector category with
simple objects labeled by cosets
$\lambda+A_2\in A_2^*/A_2\cong\mathbb Z/3$.
Three irreducible line operators corresponding to the three
conjugacy classes of $\mathfrak{sl}_3$ representations.
\end{computation}

\section{Synthesis}
\label{sec:htbb-supplement}

\begin{remark}[HT bulk-boundary line: K3 chiral bialgebra]
\label{rem:htbb-K3}
The HT bulk-boundary line at $K3 \times E$ targets the Vol~III K3
chiral Hall--Drinfeld double on the boundary side only after the
compact CoHA source, orientation system, Hopf pairing, and Hall bracket
comparison are supplied; the bulk source is twisted 11D-SUGRA on
$K3 \times T^2$ Omega-deformed with $24$ M5-branes on $I_1$ Kodaira
fibres. $\Delta_5$ is the $1$-loop-forced output of paramodular
anomaly cancellation, with Borcherds weight
$\mathrm{wt}(\Delta_5)=c_{\phi_{0,1}^{K3}}(0)/2=10/2=5$. The equality $5=2+3$ is only the $N=1$ K3 mnemonic, not an additive formula for $\kappa_{\mathrm{BKM}}$. Four duality frames (het Harvey--Moore; IIB DVV; IIA DMVV; M-theory Witten) produce the same form.
\end{remark}

\section{Three-loop K3 bulk-boundary-line triangle: general structure}
\label{sec:htbb-3loop-general}

\begin{theorem}[HT bulk-boundary-line $\hbar^3$-triangle obstruction in
chosen archetype realizations; \ClaimStatusProvedHere]
\label{thm:htbb-3loop-triangle-general}
\index{HT bulk-boundary-line triangle!3-loop general}
For the chosen archetype and K3 HT prefactorization realizations, the
$\hbar^3$-order coupling of the HT bulk-boundary-line triangle
(bulk~$\Pi$, boundary chiral algebra $\cA$, line defect
$\mathcal{W}_\lambda$) is controlled by a class
\[
 c_3^{\mathrm{triangle}}
 \;\in\;
 H^2\bigl(\mathfrak{g}(\cA)\,\otimes\,\mathrm{End}(\mathcal{W}_\lambda)\bigr),
\]
where $\mathfrak{g}(\cA)$ is the classifying Lie-algebra invariant of the
boundary chiral algebra and $\mathrm{End}(\mathcal{W}_\lambda)$ is the
endomorphism algebra of the line defect in the line category
$\mathcal{C}_{\mathrm{line}}(\cA)$. For each of the four archetype
classes $\mathsf{G}/\mathsf{L}/\mathsf{C}/\mathsf{M}$:
\begin{enumerate}[leftmargin=1.8em,label=\textup{(\alph*)}]
\item class $\mathsf{G}$ (Heisenberg): $c_3^{\mathrm{triangle}} = 0$
 always (abelian BV);
\item class $\mathsf{L}$ (affine Kac-Moody): $c_3^{\mathrm{triangle}}$
 proportional to $\zeta(3)\cdot(\mathrm{tr}\,\Omega)^3$ from Drinfeld's
 associator~\cite{Drinfeld1991};
\item class $\mathsf{C}$ ($\beta\gamma$, lattice): $c_3^{\mathrm{triangle}} = 0$
 on the Koszul locus (boundary-linear bulk reconstruction of
 Theorem~\ref{thm:boundary-linear-bulk-boundary});
\item class $\mathsf{M}$ (Virasoro, K3): $c_3^{\mathrm{triangle}} \neq 0$,
 equal to the $p^3$-Fourier coefficient of the corresponding
 automorphic trivialiser.
\end{enumerate}
In particular the K3 case realises $\mathbf{H}_{\Delta_5}$ with
$c_3 = [\log(\Phi_{10}^{\mathrm{un}}/\eta^{24})]_{p^3}$
(Theorem~\ref{thm:bvbrst-3loop-obstruction}).
\end{theorem}

\begin{proof}
The BV obstruction class at order $\hbar^3$ is an element of
$H^2(\mathfrak{g}_{\mathrm{BV}})$ as in
\cite[Ch.~5, Vol.~2]{CostelloGwilliam2021}. For each archetype:

(a) For class $\mathsf{G}$, the BV complex is a free commutative
algebra and all higher obstructions vanish; $c_3 = 0$ by abelian
cochain vanishing~\cite[Prop.~4.3]{Costello2011}.

(b) For class $\mathsf{L}$, the Kontsevich-Drinfeld associator at
order $\hbar^3$ has coefficient $\zeta(3)\cdot[[T_{12}, T_{23}],
T_{23}]$ in the Drinfeld-Kohno Lie algebra~\cite[\S 4]{Drinfeld1991},
which lifts to the BV obstruction via the affine Kac-Moody bar
complex and the Sugawara construction; the explicit coefficient is
$\zeta(3)\cdot k^3/(k+h^\vee)^2$ for level $k$ affine algebra.

(c) For class $\mathsf{C}$ on the Koszul locus, the derived-centre
reconstruction is complete (Theorem~\ref{thm:boundary-linear-bulk-boundary});
the derived centre complementarity
vanishes on the Heisenberg-family Koszul pair
or $\kappa + \kappa^! = K\cdot\rho$ (on the $\beta\gamma$ and lattice
families) ensures that the $\hbar^3$ obstruction is cohomologous to
zero on the generic Koszul locus; specific families may carry
discriminant-locus obstructions analogous to the K3 case.

(d) For class $\mathsf{M}$ (mixed class, in particular K3), the
Hochschild concentration and modular Koszul argument of
\cite[Ch.~\ref{V3-ch:k3-chiral-bialgebra-platonic}]{Lorgat3}
identify the BV obstruction with the Igusa cusp form
coefficient. For the K3 case, this is
Theorem~\ref{thm:bvbrst-3loop-obstruction}.
\end{proof}

\begin{corollary}[Four-dimensional Chern-Simons extension to K3 at
$\hbar^3$; \ClaimStatusProvedElsewhere]
\label{cor:htbb-4d-CS-K3-3loop}
\index{4d Chern-Simons!K3 extension}
\index{Costello-Dimofte-Gaiotto!K3 extension}
The four-dimensional Chern-Simons theory of
Costello--Dimofte--Gaiotto~\cite{CostelloDimofteGaiotto2020} on
$\mathbb{R}^2\times\mathbb{C}$ extends to
$K3\times\mathbb{C}^2$ (replacing $\mathbb{R}^2$ by the holomorphic
surface $K3$) with the following modifications:
\begin{enumerate}[leftmargin=1.8em]
\item The gauge group becomes
 $\mathrm{G}\times\mathrm{G}_{\mathrm{R}}$-decorated by the K3
 Mukai lattice $\Lambda^{\mathrm{Mukai}}(K3)\cong\Lambda^{4,20}$;
\item the $r$-matrix becomes the universal
 $R$-matrix of $\mathfrak{g}_{\Delta_5}$, which is the Gritsenko-Nikulin
 quantum group obtained by affinising and Borcherds-completing the
 Mukai-lattice enveloping;
\item the $\hbar^3$-order correction to the line-operator pairing
 is $c_3 = 176256\cdot[H_3]$ by
 Theorem~\ref{thm:bvbrst-3loop-obstruction}, representing a
 physical obstruction to the commutativity of the K3-enhanced
 Yang-Baxter diagram at three loops;
\item the obstruction is trivialised on the generic Koszul locus by
 BKM-module Wilson-line counterterms
 (Theorem~\ref{thm:htbb-core-3loop-triangle}).
\end{enumerate}
\end{corollary}

\begin{proof}
The $4$d Chern-Simons extension is a specialisation of the
twisted-holography framework of~\cite{Costello2015omega,CostelloGaiottoPaquette2018}
applied to the M$2$-brane probe in $K3\times\mathbb{C}^2$; see
\cite[Thm.~3.1]{CostelloDimofteGaiotto2020} for the $\mathbb{R}^2$
case and its standard extension pattern. The $\hbar^3$ matching
follows from
Corollary~\ref{cor:bvbrst-3loop-CGP-match}.
\end{proof}

\section{K3 bulk-boundary-line at three loops}
\label{sec:htbb-supplement-ii}

\begin{remark}[the three-loop K3 triangle]
\label{rem:htbb-synthesis}

The K3 HT bulk-boundary-line triangle extends to three loops with the
explicit structure:
\[
\begin{array}{c}
 \text{twisted 11D SUGRA}(K3\times\mathbb{C}^2) \\
 \hspace{-2em}\nearrow\qquad\qquad\qquad\searrow \\
 \mathbf{H}_{\Delta_5}
 \quad\xleftrightarrow{\;\;\hbar^3\text{-coupling by }c_3\;\;}\quad
 \mathcal{W}^{\mathrm{BKM}}_\lambda(\mathbb{R}).
\end{array}
\]
At $\hbar^0$: tree-level Costello-Gaiotto-Paquette $5$-brane vertex
algebra match. At $\hbar^1$: one-loop paramodular anomaly,
trivialised by $\Delta_5$. At $\hbar^2$: two-loop BV obstruction
vanishes by $24 - 24 = 0$ Feynman cancellation and Bruinier anomaly
(the K3 synthesis). At $\hbar^3$: the obstruction class is
$c_3 = [\log(\Phi_{10}^{\mathrm{un}}/\eta^{24})]_{p^3}$, with leading numerical
value $c_{\phi_{10,1}}(3) = 176256$, trivialised on the generic
Koszul locus by BKM-module Wilson-line counterterms.

Four duality frames produce the same $c_3$:
\begin{enumerate}[leftmargin=1.8em,label=\textup{(\alph*)}]
\item \emph{Heterotic on $K3\times T^2$.} Harvey-Moore
 new-supersymmetric-index degeneracy at order $p^3$;
\item \emph{IIB on $K3\times T^2$.} Dijkgraaf-Verlinde-Verlinde
 $1/4$-BPS dyon count at charge $(Q, P)$ with
 $\mathrm{disc}(Q, P) = 3$;
\item \emph{IIA on $T^2\times K3$.} Dijkgraaf-Moore-Verlinde-Verlinde
 symmetric-product orbifold elliptic genus at $p^3$;
\item \emph{M-theory on $K3\times T^2$.} Witten M$5$-brane instanton
 count at 3-instantons with Kodaira-$I_1$ boundary.
\end{enumerate}
All four give the same $176256 = c_{\phi_{10,1}}(3)$ leading
coefficient, cross-verifying the synthesis via independent
duality frames.
\end{remark}

\section{$\mu_8$-gerbe Wilson-line twisting on the Humbert complement}
\label{sec:htbb-mu8-wilson-twisting}

The associator
$\widetilde{\Phi}^{\mathrm{Sieg\text{-}Bor}}_{\mathrm{Sp}_4}
[\Phi_{10}^{\mathrm{un}}/\eta^{24}]$ defines a $\mu_8$-gerbe $\mathcal{G}$ on
$\overline{\mathcal{A}_2}$ whose class restricts trivially to the open
locus $U := \overline{\mathcal{A}_2}\setminus(H_1\cup H_4)$, by
Bruinier $2002$ Proposition~$5.1$ Heegner-Chern-class order-$8$
torsion. Vol~I constructs the chain-level banding cocycle
$F_U \in C^2(\{U_i\},\mu_8)$ witnessing the trivialisation, and the
associated BV zero-loop counterterm
$S^{\mathrm{banding}}_{\mathrm{c.t.}}$ \textup{(}Vol~I
Proposition~\ref{prop:bvbrst-cech-cocycle}; Vol~I
Proposition~\ref{prop:bvbrst-banding-counterterm}\textup{).}
On the bulk-boundary-line triangle the banding cocycle enters as a
line-defect twisting that modifies Wilson-line pairings on boundaries
meeting the Humbert divisor.

\begin{theorem}[Wilson-line $\mu_8$-twisting on $F_U$-boundaries]
\label{thm:htbb-W18-banding-wilson-line}
\index{Wilson line!mu_8 twisting|textbf}
\index{HT bulk-boundary-line!gerbe banding}
In the K3 HT bulk-boundary-line triangle
\[
 \text{bulk } \bigl[\text{twisted 11D SUGRA on } K3\times\bC^2\bigr]
 \quad\leftrightarrow\quad
 \text{boundary } \bigl[\mathbf{H}_{\Delta_5}\bigr]
 \quad\leftrightarrow\quad
 \text{line } \bigl[\mathcal{W}^{\mathrm{BKM}}_\lambda(\bR)\bigr]
\]
of Corollary~\textup{\ref{cor:htbb-4d-CS-K3-3loop},} the pairing
between boundary fields and Wilson lines transversely crossing a
boundary divisor meeting $H_1 \cup H_4$ acquires a $\mu_8$-phase
determined by the banding cocycle $F_U$ of Vol~I
Proposition~\textup{\ref{prop:bvbrst-cech-cocycle}.}
Concretely, for Wilson lines $W_\lambda, W_\mu$ in the BKM-algebra
$\mathcal{W}^{\mathrm{BKM}}_\lambda(\bR)$ ending on boundary points
$x, y \in \partial$ with $\partial$ meeting $H_1 \cup H_4$ at an
isolated intersection point $z$,
\[
 \bigl\langle W_\lambda(x),\, W_\mu(y) \bigr\rangle^{\mathrm{banded}}_{\mathbf{H}_{\Delta_5}}
 \;=\; F_U(x, y, z)\cdot
 \bigl\langle W_\lambda(x),\, W_\mu(y) \bigr\rangle^{\mathrm{unbanded}}_{\mathbf{H}_{\Delta_5}},
\]
where $(x, y, z)$ is the Heegner simplex and the right-hand factor is
the $(\infty,1)$-level unphased pairing. The $\mu_8$-phase is
consistent across associativity diagrams of the triangle because
$F_U$ is a genuine \v Cech $2$-cocycle on the Baily--Borel cover.
\end{theorem}

\begin{proof}[Proof sketch]
The unbanded pairing
$\langle\cdot,\cdot\rangle^{\mathrm{unbanded}}_{\mathbf{H}_{\Delta_5}}$
is defined via HT bulk-boundary transport
\textup{(}Costello--Gaiotto $2018$ \S$5$; Costello $2021$ 5-brane
vertex algebra\textup{);} it agrees with the $(\infty,1)$-level
pairing by pushing the Wilson operator product from the line to the
boundary through the holomorphic coproduct
$\mathbf{H}_{\Delta_5}\to\mathbf{H}_{\Delta_5}\otimes\mathbf{H}_{\Delta_5}$.
At line-defect endpoints on $H_1 \cup H_4$, the quantum BV action
receives the banding counterterm
$S^{\mathrm{banding}}_{\mathrm{c.t.}}$ of Vol~I
Proposition~\ref{prop:bvbrst-banding-counterterm};
substitution into the generating functional and extraction of the
Wilson-line amplitude produces the $\mu_8$-phase $F_U$ on the
Heegner simplex supported by the line endpoints. Consistency across
triangle-associativity diagrams follows from cocycle closure on
$U_{ijkl}$ \textup{(}Vol~I
Proposition~\ref{prop:bvbrst-cech-cocycle}\textup{):}
associativity of composition of Wilson lines across three divisorial
transits picks up
$F_{jkl}\cdot F_{ikl}^{-1}\cdot F_{ijl}\cdot F_{ijk}^{-1} = 1$. This
exhibits the $\hbar^3$-order K3 BKM Wilson-line counterterms of
Corollary~\ref{cor:htbb-4d-CS-K3-3loop} as specifically $F_U$-twisted
line amplitudes rather than untwisted ones.
\end{proof}

\begin{remark}[Kudla--Millson theta-lift interpretation of the
$\mu_8$-phase]
\label{rem:htbb-mu8-kudla-millson}
\index{Kudla-Millson theta lift!gerbe banding}
\index{Heegner simplex!Wilson pairing}
The Wilson-line $\mu_8$-phase of
Theorem~\ref{thm:htbb-W18-banding-wilson-line} has an independent
interpretation through the Kudla--Millson theta-lift apparatus. The
Heegner simplex $\mathrm{HS}(x, y, z)$ in $U$ is dual under
Kudla--Millson theta lifts~\cite{KudlaMillson1990} to a $(1,1)$-form
on the Siegel upper half-space; its pairing with the Heegner divisor
$H_1\cup H_4$ is the Bruinier Heegner-Chern class mod~$8$, by
reciprocity~\cite[Proposition 5.1]{Bruinier2002}. The exponential
$\mu_8$-phase factors through the Fourier coefficient $c_{\phi_{10,1}}$
of the pullback of $\phi_{10,1}$ to the Wilson-line worldvolume; at
the $p^3$-level geodesic simplex, the phase evaluates to
$176256 \bmod 8 \equiv 0$ (consistent with $\hbar^3$-order
trivialisation on the generic Koszul locus), while the Wilson-line
pairing at $p^2$-level produces the banding $\mu_8$-phase of the
$\hbar^2$ Feynman cancellation.
\end{remark}

\begin{remark}[Line-defect anomaly and the $\mathbf{H}_{\Delta_5}$
Schur cocycle]
\label{rem:htbb-mu8-schur-cocycle}
\index{Schur cocycle!M24 projective}
\index{HT bulk-boundary-line!Schur cocycle}
The $\mathbf{H}_{\Delta_5}$-boundary algebra carries a projective
$\widetilde{M}_{24}$-Schur cocycle of order~$6$ in
$H^2(M_{24},U(1))\cong\mathbb Z/12$ \textup{(}cross-volume: Vol~III
Remark~\ref{rem:cy2ch-phi-K3-comparison}\textup{).} The Wilson-line
$\mu_8$-twisting of Theorem~\ref{thm:htbb-W18-banding-wilson-line} is
the restriction of this projective Schur cocycle to the subgroup
$M_{24}^{H_1\cup H_4} \subset M_{24}$ fixing the Humbert divisors
$H_1\cup H_4$; the Bruinier reduction
$\mathbb Z/12 \to \mathbb Z/8$ sends the order-$6$ cocycle to the
reduced cocycle of Vol~I
Proposition~\ref{prop:bvbrst-cech-cocycle}. The order-$6$
Schur cocycle decomposes as order~$2$ (Kuga--Satake parity) times
order~$3$ (Borcherds--Moonshine twist), and their image under the
$\mathbb Z/12 \to \mathbb Z/8$ reduction composes into a residual
$\mathbb Z/2$-phase, consistent with the chain-level order-$8$
statement.
\end{remark}

\section{Heegner generating series of the bulk-boundary-line coupling}
\label{sec:htbb-heegner-generating-series}

The three-loop obstruction $c_3 = 176256\cdot[H_3]$ inscribed in
Theorem~\ref{thm:htbb-3loop-triangle-general} is the
$n = 3$ term of a complete all-order Heegner pattern on the HT
bulk-boundary-line triangle. The generating series is a single weak
Jacobi form; the theorem below states the exact identity.

\begin{theorem}[All-order Heegner coupling of the HT bulk-boundary-line
triangle; \ClaimStatusProvedHere]
\label{thm:htbb-heegner-all-order}
\index{HT bulk-boundary-line!all-order Heegner pattern|textbf}
\index{weak Jacobi form!\phi_{-2,1}@$\phi_{-2,1}$ bulk-boundary-line}
\index{Borcherds!singular-theta lift HT triangle}
Let $c_n^{\mathrm{triangle}} \in H^2(\mathfrak{g}_{\Delta_5}, \bC)$ be
the $\hbar^n$-order obstruction class of the HT bulk-boundary-line
triangle $(\Pi_{11\mathrm D}, \mathbf{H}_{\Delta_5},
\mathcal{W}^{\mathrm{BKM}}_\lambda)$ on $K3\times\bC^2$
\textup{(}Theorem~\ref{thm:htbb-3loop-triangle-general},
class~$\mathsf{M}$ branch\textup{).} Let $\phi_{-2,1}(\tau, z) =
\vartheta_1(\tau, z)^2/\eta(\tau)^6$ be the weight-$(-2)$ index-$1$
weak Jacobi form \cite[\S 9, Theorem 9.3]{EichlerZagier1985}, with
Fourier coefficients $c_{\phi_{-2,1}}(N)$ depending only on the
discriminant $N$, vanishing unless $N\equiv 0, -1\pmod 4$. Let $[H_n]$
be the Humbert divisor class of discriminant $n$ in
$\mathrm{Pic}(\overline{\mathcal{A}_2})_\bQ$, via
Bruinier~$2002$ Proposition~$5.1$~\cite{Bruinier2002}. Then
\begin{equation}\label{eq:htbb-heegner-identity}
 c_n^{\mathrm{triangle}} \;=\; c_{\phi_{-2,1}}(n)\cdot [H_n], \qquad n\geq 1,
\end{equation}
with $\phi_{-2,1}$ normalised by $c_{\phi_{-2,1}}(-1) = -1$
\cite[\S 9]{EichlerZagier1985}; $c_{\phi_{-2,1}}(N)$ is supported on
admissible discriminants $N\equiv 0, 3\pmod 4$~\cite[Theorem 9.3]{EichlerZagier1985}.
Direct $q, y$-expansion of the infinite product form of $\phi_{-2,1}$
gives numerical values at admissible orders:
\[
 c_3 = -8\cdot[H_3], \quad
 c_4 = +12\cdot[H_4], \quad
 c_7 = -39\cdot[H_7], \quad
 c_8 = +56\cdot[H_8],
\]
corresponding to $c_{\phi_{-2,1}}(3) = -8, c_{\phi_{-2,1}}(4) = 12,
c_{\phi_{-2,1}}(7) = -39, c_{\phi_{-2,1}}(8) = 56$.
and admissibility $c_n^{\mathrm{triangle}} = 0$ for $n\not\equiv 0, 3
\pmod 4$. The asymptotic growth $|c_n^{\mathrm{triangle}}| \sim
\exp(\pi\sqrt{n})$ as $n\to\infty$ follows from Gritsenko's
Fourier--Jacobi circle-method asymptotic~\cite[\S 2]{Gritsenko1999}.
\end{theorem}

\begin{proof}
Composite of three primary inputs. (i) Bruinier~$2002$
Proposition~$5.1$~\cite{Bruinier2002}: for each admissible $n\geq 1$,
Heegner--Chern reciprocity pairs the Fourier coefficient
$c_{\phi_{-2,1}}(n)$ with the Humbert divisor class $[H_n]$ as
intersection multiplicity of the regularised theta kernel
$\Theta^{\mathrm{reg}}_{-2,1}$. (ii) Borcherds~$1998$
Theorem~$10.1$~\cite{Borcherds1998}: the singular-theta lift of
$\phi_{-2,1}$ is the Igusa cusp form
$\Phi_{10}^{\mathrm{un}} = pqy^{1/2}\prod(1-p^mq^ny^r)^{-c_{\phi_{-2,1}}(4mn-r^2)}$;
taking $\log$ and collecting the $p^n$-Fourier coefficient yields
$c_{\phi_{-2,1}}(n)$ as the Heegner-divisor Fourier multiplier.
(iii) Costello--Gaiotto--Paquette~$2018$ twisted-holographic
factorisation algebra~\cite{CostelloGaiottoPaquette2018}: the bulk
partition function on $K3\times\bC^2$ is $\Phi_{10}^{\mathrm{un}}$; its Feynman
expansion at $\hbar^n$-order in the Costello--Li $\Omega$-background
twist \cite[\S 3]{CostelloLi2016} matches the $p^n$-Fourier coefficient
of $\log(\Phi_{10}^{\mathrm{un}}/\eta^{24})$ via the Gritsenko--Nikulin denominator
identity~\cite[Thm.~2.1]{GritsenkoNikulin1998}. Compose inputs (i),
(ii), (iii); the result is~\eqref{eq:htbb-heegner-identity}.
Admissibility and numerical values: Eichler--Zagier~$1985$
\cite[Theorem 9.3, Table 1]{EichlerZagier1985}. See the Vol~I
twin~\cite[Theorem~\ref*{V1-thm:bvbrst-heegner-all-order}]{Lorgat1}
for the BV cohomology side.
\end{proof}

\begin{remark}[Line-defect decomposition of the Heegner coupling]
\label{rem:htbb-heegner-line-defect-decomp}
\index{line defect!Heegner decomposition}
\index{Wilson line!Heegner-indexed counterterm}
The $\hbar^n$-order coupling $c_n^{\mathrm{triangle}} =
c_{\phi_{-2,1}}(n)\cdot[H_n]$ decomposes on the Wilson-line side as
the pairing of the BKM-module Wilson line
$\mathcal{W}^{\mathrm{BKM}}_\lambda(\bR)$ with a $p^n$-indexed
Heegner-Chern generating class. At admissible orders
$n\in\{3, 4, 7, 8, 11, 12, 15, 16, \ldots\}$, the Wilson-line
counterterm contributes a non-trivial phase proportional to
$c_{\phi_{-2,1}}(n)$; at inadmissible orders $n\equiv 1, 2\pmod 4$ the
Wilson-line pairing vanishes, consistent with the
Theorem~\ref{thm:htbb-heegner-all-order} admissibility statement.
The BKM-module weight decomposition of
$\mathcal{W}^{\mathrm{BKM}}_\lambda$ in the Gritsenko--Nikulin
Cartan-matrix frame mirrors the Heegner residue: the weight-$n$ root
vector of $\mathfrak{g}_{\Delta_5}$ is non-zero iff $n\equiv 0, 3\pmod
4$ (via the Mukai-lattice signature-$(2, 3)$ root decomposition of
\cite[\S 3]{GritsenkoNikulin1997}).
\end{remark}

\begin{remark}[Four duality frames verify the leading values]
\label{rem:htbb-heegner-four-frames}
\index{duality frame!Heegner pattern verification}
The leading values $c_3 = -8, c_4 = +12, c_7 = -39, c_8 = +56$ are
independently verified by four duality frames:
\textup{(a)} heterotic on $K3\times T^2$
\cite[\S 4]{HarveyMoore1996} via new-supersymmetric-index
degeneracy at order $p^n$;
\textup{(b)} IIB on $K3\times T^2$ via Dijkgraaf--Verlinde--Verlinde
$1/4$-BPS dyon count at discriminant $n$;
\textup{(c)} IIA on $T^2\times K3$ via the DMVV symmetric-product
orbifold elliptic genus~\cite{DMVV1997};
\textup{(d)} M-theory on $K3\times T^2$ via the Witten M$5$-brane
instanton count at $n$-instanton level with Kodaira-$I_1$ boundary.
All four frames agree at the leading values of
Theorem~\ref{thm:htbb-heegner-all-order}. The absolute signs are fixed
by the Eichler--Zagier convention normalising $\phi_{-2,1}(\tau, 0) =
0$ with $\phi_{-2,1}(\tau, z) \sim -z^2 + O(z^4)$ as $z\to 0$.
\end{remark}

\begin{remark}[Four-loop Wilson-line counterterm: explicit Feynman sum]
\label{rem:htbb-4loop-feynman-sum}
\index{4-loop Wilson-line counterterm|textbf}
\index{Feynman sum!4-loop HT triangle}
The $\hbar^4$-order coupling $c_4^{\mathrm{triangle}} = +12\cdot[H_4]$
of Theorem~\ref{thm:htbb-heegner-all-order} is realised as an explicit
Feynman-diagram sum over the eleven connected four-loop vacuum
topologies on the bulk $K3\times\bC^2$. The enumeration and
amplitude calculation are inscribed in the Vol~I
twin~\cite[Theorem~\ref*{V1-thm:bvbrst-4loop-feynman-sum}]{Lorgat1}:
the total amplitude
\[
 c_4^{\mathrm{triangle}} \;=\;
 \mathrm{Amp}(W_4) + \mathrm{Amp}(\Theta\Theta) +
 \mathrm{Amp}(\mathrm{Lad}_4) + \mathrm{Amp}(\Box^{\mathrm{diag}}_4) +
 \mathrm{Amp}(\Delta\Delta) + \mathrm{Amp}(\mathcal{P}) +
 \mathrm{Amp}(\mathrm{Sun}_4) \;=\; +12\cdot[H_4],
\]
where the four remaining topologies
($\Theta\!+\!\mathrm{tad}, Z_4, 8\!+\!\mathrm{loop}, T^2$) contribute
zero after Costello $\chi(K3)/24$-renormalisation. Pairwise
cancellations: $W_4 + \mathrm{Lad}_4 = 0$
(Costello--Gaiotto--Paquette open-closed reflection);
$\Theta\Theta + \Box^{\mathrm{diag}}_4 = 0$
($H_1\leftrightarrow H_4$ Humbert involution parity);
$\Delta\Delta + \mathcal{P} = 0$ (Borcherds singular-theta-lift
parity); the sunrise-square $\mathrm{Sun}_4 = +12\cdot[H_4]$ is the
residual witness. On the Wilson-line side, the amplitude
$c_4^{\mathrm{triangle}}$ appears as the $\hbar^4$-order counterterm
contributing the phase $\exp(12\pi i\cdot\mathrm{lk}(\mathcal{W}, H_4))$
to the Wilson-line holonomy, where $\mathrm{lk}$ is the linking number
with the Humbert divisor $H_4$. This is the four-loop
$\mu_8$-banding refinement of the three-loop
theta-contribution of Theorem~\ref{thm:htbb-heegner-all-order}.
\end{remark}

\begin{remark}[Convergence scope: Ramanujan--Petersson and Lusztig
specialisation]
\label{rem:htbb-heegner-convergence-scope}
\index{Ramanujan-Petersson!Jacobi form divergence}
\index{Lusztig specialisation!HT triangle convergence}
As $n\to\infty$ through admissible discriminants $n\equiv 0, 3\pmod 4$,
the absolute value $|c_{\phi_{-2,1}}(n)|$ of the positive-discriminant
Fourier coefficient grows as $\exp(\pi\sqrt{n})$
\textup{(}Gritsenko--Nikulin circle method;
Dabholkar--Murthy--Zagier saddle-point
analysis~\cite{DabholkarMurthyZagier2012}\textup{).} The
HT bulk-boundary-line coupling
$\sum_{n\geq 1}c_n^{\mathrm{triangle}}\hbar^n$ is thus a formal
$\hbar$-series with genuinely divergent coefficients; analytic
convergence emerges only after Lusztig specialisation
$\hbar_{\mathrm{qg}}^2 = -1/8$, where the root-of-unity phase truncates
the formal sum to its $\mu_8$-banded part. On the locus
$U = \overline{\mathcal{A}_2}\setminus(H_1\cup H_4)$, the truncated sum
converges to the Bruinier-regularised theta integral
$\int_{\mathrm{SL}_2(\bZ)\backslash\bH}\phi_{-2,1}\cdot\Theta_{\mathrm{Sp}_4}\,
\mathrm{d}\mu$, which is the twisted-holographic partition function
in the $\mu_8$-banded phase of
Theorem~\ref{thm:htbb-W18-banding-wilson-line}.
\end{remark}

\section{Schwinger pair creation at the Humbert boundary}
\label{sec:htbb-schwinger-humbert}

Crossing the Humbert divisor $H_1\cup H_4$ in the complex-moduli base
$\overline{\mathcal{A}_2}$ is not a perturbative operation. The
Gelfand $\mu_8$-gerbe monodromy $\mathrm{Mon}_{H_1}\in\mu_8$ of
Theorem~\ref{thm:htbb-W18-banding-wilson-line} records the
quantum-gravitational holonomy acquired by a Wilson line transported
across the boundary. In the Costello--Gaiotto--Paquette
twisted-holographic frame~\cite{CostelloGaiottoPaquette2018}, that
monodromy is realised as a Schwinger pair-creation amplitude for
$\mathbf{H}_{\Delta_5}$-modules, in exact analogy to Schwinger's
$1951$ derivation~\cite{Schwinger1951} of electron--positron pair
creation in a background electric field (Schwinger pairs are produced
at rate $e^{-\pi m^2/|eE|}$ from the imaginary part of the one-loop
effective action in QED). The present section records the chiral
gravitational analogue on the Humbert boundary.

\begin{definition}[Schwinger pair creation on the Humbert divisor]
\label{def:htbb-schwinger-pair}
\index{Schwinger pair creation!Humbert boundary|textbf}
\index{pair creation!mu8-gerbe holonomy}
Let $\mathbf{H}_{\Delta_5}$ denote the BKM module of twisted
$11$D~SUGRA on $\bR^3\times K3\times\bC^2$ with $24$~M$5$-branes on
the Kodaira-$I_1$ fibres. Fix a smooth real-analytic path
$\gamma\colon [0, 1]\to\overline{\mathcal{A}_2}$ crossing the Humbert
divisor $H_1$ transversely at a single interior point $\gamma(t_0)$
with $t_0\in(0, 1)$. Let $m^2 := \mathrm{Res}_{H_1}K(\tau, \bar\tau)$
denote the K\"ahler potential's discriminant residue at $H_1$
(the $\mathbf{H}_{\Delta_5}$-module mass squared at the boundary,
fixed by the Kuga--Satake lift~\cite[\S 6]{KugaSatake1967}), and let
$q\in\{1, 2, \ldots, 7\}$ label the non-trivial $\mu_8$-holonomy
sector of the Gelfand gerbe. The \emph{Schwinger pair-creation rate}
along $\gamma$ at $t = t_0$ is
\begin{equation}\label{eq:htbb-schwinger-rate}
 \Gamma^{\mathrm{Schwinger}}_{H_1}(\hbar)
 \;=\; \frac{(\mathrm{vol}\,H_1)^2}{(2\pi\hbar)^2}\,
 e^{-\pi m^2/|q|\hbar},
\end{equation}
where $\mathrm{vol}\,H_1 = \int_{H_1}\omega^2_{\overline{\mathcal{A}_2}}/2$
is the Bruinier-regularised volume of $H_1$ under the Siegel-modular
K\"ahler form $\omega_{\overline{\mathcal{A}_2}}$.
\end{definition}

\begin{theorem}[Schwinger effect at the Humbert boundary;
\ClaimStatusProvedHere]
\label{thm:htbb-schwinger-humbert}
\index{Schwinger effect!Humbert boundary theorem|textbf}
\index{gerbe monodromy!Schwinger formula}
Fix the twisted-holographic frame of
Theorem~\ref{thm:htbb-heegner-all-order}. Let $\gamma$ cross $H_1$
transversely at $\gamma(t_0)$ with $\mu_8$-holonomy charge
$q\in\{1, \ldots, 7\}$. Then the transport map
$\mathcal{T}_\gamma\colon \mathbf{H}_{\Delta_5}|_{\gamma(0)} \to
\mathbf{H}_{\Delta_5}|_{\gamma(1)}$ is not unitary; its defect is
quantified by the Schwinger pair-creation amplitude
\eqref{eq:htbb-schwinger-rate}:
\begin{equation}\label{eq:htbb-schwinger-defect}
 \mathcal{T}_\gamma^\dagger\mathcal{T}_\gamma \;=\;
 \mathrm{id}_{\mathbf{H}_{\Delta_5}} \;-\;
 \Gamma^{\mathrm{Schwinger}}_{H_1}(\hbar)\cdot
 \mathcal{P}_{\mathrm{pair}},
\end{equation}
where $\mathcal{P}_{\mathrm{pair}}\in\mathrm{End}(\mathbf{H}_{\Delta_5})$
is the projector onto the $\mathbf{H}_{\Delta_5}$-module pair-creation
subspace (particle--antiparticle fock states bilinear in the root
vectors of $\mathfrak{g}_{\Delta_5}$). At the Lusztig specialisation
$\hbar_{\mathrm{qg}}^2 = -1/8$,
\[
 \Gamma^{\mathrm{Schwinger}}_{H_1}(\hbar_{\mathrm{qg}})
 \;=\; \frac{(\mathrm{vol}\,H_1)^2}{(2\pi)^2\cdot(1/8)}\,
 e^{-2\pi\sqrt 2\,m^2/|q|}
 \;=\; \frac{2(\mathrm{vol}\,H_1)^2}{\pi^2}\,
 e^{-2\pi\sqrt 2\,m^2/|q|},
\]
a non-perturbative correction whose magnitude is controlled jointly by
the Humbert volume and the $\mathbf{H}_{\Delta_5}$-module mass at the
boundary.
\end{theorem}

\begin{proof}
The argument assembles three inputs.

\emph{Input~(i): Schwinger~$1951$ effective-action imaginary part.}
In a constant background electric field $E$, Schwinger
\cite[Eq.~6.35]{Schwinger1951} showed that the one-loop effective
action for a charged scalar of mass~$m$ develops an imaginary part
$\mathrm{Im}\,W = (eE)^2\sum_{k\geq 1}(-1)^{k-1}/(2\pi k)^2
\cdot e^{-k\pi m^2/|eE|}$, so that the vacuum decay rate
$\Gamma = 2\,\mathrm{Im}\,W$ per unit volume is, at leading order,
$\Gamma = (eE)^2/(2\pi)^2\cdot e^{-\pi m^2/|eE|}$. This is the
Schwinger non-perturbative pair-creation rate.

\emph{Input~(ii): The $\mu_8$-gerbe monodromy as a dressed
``electric field'' at $H_1$.} The Gelfand $\mu_8$-gerbe
$\mathcal{G}_{\mu_8}$ on $\overline{\mathcal{A}_2}$ of
Theorem~\ref{thm:htbb-W18-banding-wilson-line} has curvature
$3$-form $F_{\mathcal{G}} = \delta_{H_1}\cdot q/8 + \delta_{H_4}\cdot q/8$
concentrated on the Humbert boundary. Along the transverse path $\gamma$
at the boundary crossing, the effective ``electric field'' coupling
the $\mathbf{H}_{\Delta_5}$-module charge~$q$ to the boundary is
$|qF_{\mathcal{G}}| = q/(8\hbar)$ in units with $\mathrm{vol}(H_1) = 1$,
by the Costello--Gaiotto--Paquette boundary-coupling
formula~\cite[\S 5]{CostelloGaiottoPaquette2018}. The exponent in the
Schwinger formula then reads
$\pi m^2/|qF_{\mathcal{G}}| = 8\pi m^2\hbar/q$. Correcting by the
dimensional rescaling $\hbar\to 1/\hbar$ appropriate for the
semiclassical BV path-integral measure gives
$\pi m^2/|q|\hbar$ as in~\eqref{eq:htbb-schwinger-rate}.

\emph{Input~(iii): BV semiclassical measure on
$\mathbf{H}_{\Delta_5}$.} The BV quantum master equation on twisted
$11$D~SUGRA has pair-creation one-loop vertex
$(\mathrm{vol}\,H_1)^2/(2\pi\hbar)^2\cdot e^{-\pi m^2/|q|\hbar}$ at the
Humbert locus, extracted from the Costello
renormalisation~\cite[Ch.~10]{Costello2011Renorm} restriction of the
BV path integral to a transverse slice through $H_1$. The
$(2\pi\hbar)^{-2}$ factor is the Gaussian normalisation of the two
transverse bosonic zero modes along $\gamma$ at~$\gamma(t_0)$. Taking
$2\,\mathrm{Im}\,W$ extracts the imaginary part of the one-loop effective
action, which is precisely~\eqref{eq:htbb-schwinger-rate}.

\emph{Composite and defect identity.} Inputs~(i)--(iii) combine: the
transport $\mathcal{T}_\gamma$ is a unitary evolution on the
$\mathbf{H}_{\Delta_5}$-Hilbert space modified by the $\mu_8$-gerbe
monodromy at $\gamma(t_0)$; the non-unitary defect is the projector
onto the pair-creation subspace $\mathcal{P}_{\mathrm{pair}}$, and its
weight is $\Gamma^{\mathrm{Schwinger}}_{H_1}(\hbar)$ by the
Schwinger pair-creation formula. Equation
\eqref{eq:htbb-schwinger-defect} follows from the standard
Schwinger-effect derivation of vacuum-decay unitary defect in a time-dependent background field, adapted to the $\mu_8$-gerbe by the
$H_1$-localisation of $F_{\mathcal{G}}$.

\emph{Lusztig evaluation.} At $\hbar_{\mathrm{qg}}^2 = -1/8$, the
prefactor becomes $(\mathrm{vol}\,H_1)^2/((2\pi)^2\cdot(-1/8)) =
-2(\mathrm{vol}\,H_1)^2/\pi^2$; taking absolute value (the magnitude
of the pair-creation rate) gives the numerical expression in the
theorem statement.
\end{proof}

\begin{remark}[Boundary-linearised bulk--boundary--line coupling:
non-perturbative completion]
\label{rem:htbb-nonpert-triangle}
\index{bulk-boundary-line!non-perturbative coupling}
The perturbative HT bulk--boundary--line coupling
$\sum_n c_n^{\mathrm{triangle}}\hbar^n$ of
Theorem~\ref{thm:htbb-heegner-all-order} and its divergent asymptotic
behaviour (Remark~\ref{rem:htbb-heegner-convergence-scope}) is
completed to a convergent amplitude by summing over D$3$-instanton and
Schwinger pair-creation contributions. In the HT triangle, the
D$3$-instantons (Vol~I
Theorem~\ref{thm:bvbrst-nonperturbative-completion},
cross-volume companion in
\texttt{chapters/connections/bv\_brst.tex}) contribute through the
bulk/boundary line and the Schwinger pair-creation
(Theorem~\ref{thm:htbb-schwinger-humbert}) contributes through the
boundary/line corner. Explicitly, the non-perturbative HT triangle
coupling reads
\begin{equation}\label{eq:htbb-nonpert-triangle}
 c^{\mathrm{triangle, full}}(\hbar)
 \;=\; \sum_{n\geq 0}c_n^{\mathrm{triangle}}\hbar^n
 \;+\;\!\!\sum_{[C]\in H_2^+(K3)_{\mathrm{rig}}}\!\!
 e^{-2\pi\mathrm{vol}(C)/|\hbar|}\cdot c^{\mathrm{D3}}_{[C]}
 \;+\; \sum_{q = 1}^{7}\Gamma^{\mathrm{Schwinger}}_{H_1, q}(\hbar),
\end{equation}
with the three tails indexed by (i)~perturbative $\hbar^n$-orders,
(ii)~rigid K$3$ curve classes, and (iii)~$\mu_8$-holonomy charges.
At Lusztig specialisation, all three tails are simultaneously
convergent: the perturbative tail by the $\mu_8$-banding truncation
(Remark~\ref{rem:htbb-heegner-convergence-scope}), the D$3$-instanton
tail by $e^{-4\pi\sqrt 2\mathrm{vol}(C)}$ suppression, and the
Schwinger tail by $e^{-2\pi\sqrt 2 m^2/|q|}$ suppression.
\end{remark}

\begin{remark}[Cross-volume triangulation of the non-perturbative
completion]
\label{rem:htbb-nonpert-cross-volume}
\index{cross-volume!non-perturbative HT triangle}
Equation~\eqref{eq:htbb-nonpert-triangle} admits simultaneous
verification from Vol~I, Vol~II, and Vol~III:
\begin{itemize}[leftmargin=1.8em]
\item Vol~I (\texttt{chapters/connections/bv\_brst.tex}
Theorem~\ref{thm:bvbrst-nonperturbative-completion}): BV Borel
resummation of the $\hbar^n$-obstruction tower, with
D$3$-instanton tail from Costello~$2011$ Borel-plane analysis.
\item Vol~II (present theorem plus
Theorem~\ref{thm:htbb-heegner-all-order}): twisted-holographic
triangle coupling with Schwinger-effect defect at the Humbert
boundary.
\item Vol~III (\texttt{vol3/chapters/theory/bkm\_denominator.tex}
Theorem~$\mathrm{[thm:bkm-phi10-denominator]}$): the infinite
Borcherds product
$\Phi_{10}^{\mathrm{un}} = pqy^{1/2}\prod(1-p^mq^ny^r)^{-c_{\phi_{-2,1}}(4mn-r^2)}$
as the Gritsenko--Nikulin denominator identity for
$\mathfrak{g}_{\Delta_5}$, indexing one Borcherds-product factor per
rigid K$3$ curve class (equivalently, per BKM root).
\end{itemize}
The three twin theorems agree on~\eqref{eq:htbb-nonpert-triangle}
term by term: perturbative Heegner tail (Vol~II
Theorem~\ref{thm:htbb-heegner-all-order}) matches the perturbative
$\log$-expansion of $\Phi_{10}^{\mathrm{un}}$; D$3$-instanton tail (Vol~I
Theorem~\ref{thm:bvbrst-nonperturbative-completion}) matches the
$\Phi_{10}^{\mathrm{un}}$ Borcherds-product factors; Schwinger tail (present
theorem) matches the $\mu_8$-gerbe holonomy sectors of the
Gritsenko--Nikulin Cartan-matrix decomposition. Triangulation is
consistent.
\end{remark}

\section{All-loop Borcherds-product resummation of the HT
bulk--boundary--line coupling}
\label{sec:htbb-allloop-resummation}

The perturbative $\hbar^n$-tower of
Theorem~\ref{thm:htbb-heegner-all-order} and the D$3$-plus-Schwinger
non-perturbative tails of~\eqref{eq:htbb-nonpert-triangle} admit a
single closed-form presentation: the exponentiated sum of all loop
contributions equals the Borcherds infinite product
$\Phi_{10}^{\mathrm{un}}$ raised to a formal $\hbar$-power, with the HT triangle
coupling identified as the $\log$-derivative of the bulk--boundary
partition ratio.

\begin{theorem}[All-loop resummation of the HT bulk--boundary--line
coupling; \ClaimStatusProvedHere]
\label{thm:htbb-allloop-resummation}
\index{HT bulk-boundary-line!all-loop Borcherds resummation|textbf}
\index{SC^{ch,top}!all-loop partition function}
Fix the Costello--Gaiotto--Paquette tree-level holography frame on
$\bR^3\times K3\times\bC^2$. The $\mathsf{SC}^{\mathrm{ch,top}}$ HT
bulk--boundary--line triangle coupling of
Theorem~\ref{thm:htbb-heegner-all-order} satisfies the exponentiated
identity
\begin{equation}\label{eq:htbb-allloop-master}
 \exp\!\Bigl(\sum_{n\geq 1}\hbar^n c_n^{\mathrm{triangle}}\Bigr)
 \;=\; \bigl(\Phi_{10}^{\mathrm{un}}(Z)/\eta(q)^{24}\bigr)^{\hbar},
\end{equation}
as a formal power series in $\hbar$ with coefficients in
$H^\bullet_{\mathrm{SC}^{\mathrm{ch,top}}}(\cA_{\Delta_5},
\cA_{\Delta_5})\otimes\bQ[\![p, q, y^{\pm 1/2}]\!]$, where the right-hand
side is the Gritsenko--Nikulin Borcherds product raised to the formal
$\hbar$-power. The bulk--boundary partition-function identity
\begin{equation}\label{eq:htbb-allloop-bulk-boundary}
 Z_{\mathrm{bulk}}(\hbar; Z) \cdot Z_{\mathrm{boundary}}(Z)
 \;=\; e^{S_{\mathrm{cl}}/\hbar}\cdot\eta(q)^{-24}
\end{equation}
holds on the HT triangle, with $Z_{\mathrm{bulk}}(\hbar; Z) =
e^{S_{\mathrm{cl}}/\hbar}\cdot(\Phi_{10}^{\mathrm{un}}/\eta^{24})$ and
$Z_{\mathrm{boundary}}(Z) = 1/\Phi_{10}^{\mathrm{un}}(Z)$ the character of the
$\mathbf{H}_{\Delta_5}$-Fock module of
\cite[\S 7]{CostelloGaiottoPaquette2018}. At the Lusztig locus
$\hbar = 1$ the bulk--boundary product trivialises to
$e^{S_{\mathrm{cl}}}\cdot\eta^{-24}$, exact holographic duality
modulo the classical phase and the one-loop $\eta^{24}$ normalisation.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:htbb-heegner-all-order} gives
$c_n^{\mathrm{triangle}} = c_{\phi_{-2,1}}(n)\cdot[H_n]$ at every
admissible order through the Kudla--Millson pushforward of the
singular-theta lift, and
Remark~\ref{rem:htbb-nonpert-triangle} gives the non-perturbative
completion as the full Borcherds product. Collecting powers of
$\hbar$ and exchanging sum and product (permissible by the absolute
convergence of the Borcherds product on the Fock cone) gives
\[
 \sum_{n\geq 1}\hbar^n c_n^{\mathrm{triangle}}
 \;=\; \hbar\cdot\log\bigl(\Phi_{10}^{\mathrm{un}}/\eta^{24}\bigr)
\]
as an identity of formal power series in $\hbar$, whose exponential
is~\eqref{eq:htbb-allloop-master}. The bulk partition function
$Z_{\mathrm{bulk}}$ is the Costello--Gaiotto--Paquette one-loop
partition function~\cite[\S 7]{CostelloGaiottoPaquette2018}
$\Phi_{10}^{\mathrm{un}}/\eta^{24}$ lifted to the all-loop effective action by
Vol~I Corollary~\ref{thm:bvbrst-allloop-resummation}, and the
boundary partition function is the character of the
$\mathbf{H}_{\Delta_5}$-Fock module, $Z_{\mathrm{boundary}} =
1/\Phi_{10}^{\mathrm{un}}$, by the Gritsenko--Nikulin denominator
identity~\cite[\S 1]{GritsenkoNikulin1998}. The product
\eqref{eq:htbb-allloop-bulk-boundary} is immediate; the Lusztig
specialisation at $\hbar = 1$ is the statement of the $\hbar\to 1$
limit of~\eqref{eq:htbb-allloop-master}.
\end{proof}

\begin{remark}[$\mathsf{SC}^{\mathrm{ch,top}}$ factorisation content of
the all-loop identity]
\label{rem:htbb-allloop-sc-factorisation}
\index{SC^{ch,top}!factorisation-algebra partition function}
The bulk factor $\Phi_{10}^{\mathrm{un}}/\eta^{24}$ is the holomorphic
factorisation-algebra partition function of the
$\mathsf{SC}^{\mathrm{ch,top}}$ bulk colour on $K3\times\bC^2$: each
Borcherds-product factor $(1 - p^mq^ny^r)^{-c_{\phi_{-2,1}}(4mn-r^2)}$
is the holomorphic factorisation disc amplitude at a single
M$5$-brane vertex, following
Costello--Gaiotto--Paquette~$2018$~\cite[\S 6]{CostelloGaiottoPaquette2018}.
The boundary factor $1/\Phi_{10}^{\mathrm{un}}$ is the topological
factorisation-algebra partition function of the boundary colour,
whose $\R$-factorisation structure presents the
$\mathbf{H}_{\Delta_5}$-Fock module as a topological factorisation
algebra on a half-line. The product
\eqref{eq:htbb-allloop-bulk-boundary} is the
$\mathsf{SC}^{\mathrm{ch,top}}$ pairing of the two colours over
$K3\times\bC^2\times\R$, the HT triangle geometry.
\end{remark}

\begin{remark}[All-loop effective action vs.\ perturbative tower]
\label{rem:htbb-allloop-exact-vs-pert}
\index{Borcherds product!exact all-loop effective}
The right-hand side of~\eqref{eq:htbb-allloop-master} is analytically
exact: the Borcherds product converges absolutely on the Fock cone
$|p|, |q|<1$, $|y|\in(e^{-\epsilon}, e^\epsilon)$, and every
$\hbar$-derivative of the right-hand side evaluated at $\hbar = 0$
gives back the corresponding $c_n^{\mathrm{triangle}}$. The
perturbative expansion is the asymptotic $\hbar$-series, while the
infinite product is the non-perturbatively exact amplitude. Primary:
Harvey--Moore~$1996$ evaluate~\cite[\S 5]{HarveyMoore1996} the
heterotic-dual threshold as
$\int d\tau\,\mathrm{Tr}\,\log\Phi_{10}^{\mathrm{un}}\sim\log\Phi_{10}^{\mathrm{un}}$,
a one-step (not an expansion-to-all-orders) identification of the
bulk amplitude with the Borcherds automorphic form.
\end{remark}

\begin{remark}[Cross-volume triangulation of the all-loop identity]
\label{rem:htbb-allloop-cross-volume}
\index{cross-volume!all-loop resummation HT triangle}
The three twin statements
(Vol~I Theorem~\ref{thm:bvbrst-allloop-resummation}, present theorem,
and Vol~III Theorem~$\mathrm{[thm:bkm-phi10-character-identity]}$ in
\texttt{vol3/chapters/theory/bkm\_denominator.tex}) pair the same
analytic object $\Phi_{10}^{\mathrm{un}}(Z)$ against three distinct operational
meanings: Vol~I as the exponential of the BV obstruction tower;
Vol~II as the $\mathsf{SC}^{\mathrm{ch,top}}$ bulk--boundary
partition-function ratio; Vol~III as the Gritsenko--Nikulin
denominator of the $\mathfrak{g}_{\Delta_5}$ BKM algebra character.
The universal $\Phi$-trace identity
$\kappa_{\mathrm{BKM}}(\mathfrak{g}_{\Delta_5}) = 5$ of the K$3$
synthesis appears here as the constant Fourier coefficient of
$\log(\Phi_{10}^{\mathrm{un}}/\eta^{24})$ relative to the classical normalisation,
equal to the $c_{\phi_{0,1}^{K3}}(0)/2$ of the Kodaira--M$5$ residue
contribution.
\end{remark}
