\providecommand{\Har}{\operatorname{Har}}

\section{Line Operators, Koszul Duality, and Spectral $R$-Matrices}
\label{sec:line_operators}
\label{sec:line-operators}

Line operators in 3d HT quantum field theories are identified with
modules for the open-colour Koszul dual algebra
$\mathcal{A}^!_{\mathrm{line}}$, and spectral $R$-matrices
controlling their OPE emerge from the bar-cobar adjunction.

\begin{remark}[$E_1$ primacy of line operators]
\label{rem:line-operators-e1-primacy}
Line operators are natively $E_1$ data: they are modules over the
\emph{ordered} (open-colour) Koszul dual
$\cA^!_{\mathrm{line}}$, and their composition is governed by
the deconcatenation coproduct on the ordered bar coalgebra,
not its symmetric-coinvariant quotient.
The spectral $R$-matrix $R(z)$ controlling line-operator OPE is
the degree-$2$ $E_1$ MC datum; the modular characteristic
$\kappa(\cA)$ is its
$\Sigma_2$-coinvariant projection
(for abelian algebras $\kappa = \mathrm{av}(r(z))$;
for non-abelian Kac--Moody
$\kappa = \mathrm{av}(r(z)) + \dim(\fg)/2$).
See Volume~I, \S\textup{E$_1$ as primitive}
for the full statement.
\end{remark}

\begin{remark}[Open sector first, strict presentation second]
\label{rem:open-sector-strict-presentation}
\label{rem:yangian-logical-status}
\index{line operators!strict presentation}
The statement $\mathcal{C}_{\mathrm{line}}\simeq \mathcal{A}^!_{\mathrm{line}}\text{-mod}$
should always be read at the $A_\infty$-module level. The dg-shifted
Yangian and related algebraic packages are chosen strict presentations
of this meromorphic module theory; their deformation and OPE constraints
are shadows of the same homotopy-coherent deformation object that
controls the boundary algebra
(Convention~\ref{conv:vol2-strict-models}).
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 6 -- BAR–COBAR DUALITY FOR THE 2-COLORED OPERAD AND KOSZULITY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Bar–cobar duality for $\mathsf{SC}^{\mathrm{ch,top}}$ and filtered Koszul duality}
\label{sec:bar-cobar}

\subsection{Colored cooperad and bar construction}
\label{subsec:bar}
Let $\mathsf{SC}^{\mathrm{ch,top}}$ be augmented in each color (units in $\FM_1(\C)$ and $E_1(1)$).
The (colored) bar construction $\mathbf B\mathsf{SC}^{\mathrm{ch,top}}$ is the cofree conilpotent cooperad on the desuspension of the augmentation ideal, with differential induced by partial compositions.

\begin{definition}[Bar construction]
\label{def:bar}
Set $\mathbf B := \mathbf B(\mathsf{SC}^{\mathrm{ch,top}})$; its underlying graded cooperad consists of trees labeled by operations in $\FM_\bullet(\C)$ and $E_1(\cdot)$ with desuspension shifts, and differential $d=d_{\mathrm{int}}+d_{\mathrm{Graft}}$.
\end{definition}

\subsection{Cobar construction and twisting morphisms}
\label{subsec:cobar}
Given a conilpotent colored cooperad $C$, the cobar $\Omega C$ is the free operad on the desuspension $s^{-1}\bar{C}$ with differential determined by the cooperad structure.
A twisting morphism $\tau: C\to \mathsf{End}_A$ determines (co)algebra structures and bar–cobar adjunctions.

\begin{theorem}[Homotopy--Koszulity of $\mathsf{SC}^{\mathrm{ch,top}}$;
\ClaimStatusProvedHere]
\label{thm:homotopy-Koszul}
The two--colored topological operad $\mathsf{SC}^{\mathrm{ch,top}}$
(Definition~\textup{\ref{def:SC-operations}}) is homotopy--Koszul: the canonical
map
\[
 \Omega\mathbf{B}(\mathsf{SC}^{\mathrm{ch,top}})
 \;\xrightarrow{\;\sim\;}
 \mathsf{SC}^{\mathrm{ch,top}}
\]
is a quasi--isomorphism of two--colored dg operads.
Equivalently, the unit and counit of the bar--cobar adjunction
$(\Omega,\mathbf B)$ for $\mathsf{SC}^{\mathrm{ch,top}}$--algebras are weak
equivalences.
\end{theorem}

\begin{proof}
\textbf{Step 1: The classical Swiss--cheese operad is homotopy--Koszul.}
The classical Swiss--cheese operad $\mathsf{SC}$ (with $E_2$ on the closed
color, $E_1$ on the open color, and mixed operations
$E_2(k) \times E_1(m)$) is Koszul as a two--colored operad: it is built
from the individually Koszul operads $E_2$ \cite{GK94} and
$\mathsf{Ass} = E_1$ \cite{GK94} via a distributive law governing the
Swiss--cheese interaction \cite{Vor99,Hoe09,HL12,Val07}. For a Koszul operad, the
inclusion of the Koszul dual cooperad into the bar construction is a
quasi--isomorphism \cite{GK94}, so the canonical counit
$\epsilon_{\mathsf{SC}} \colon \Omega\mathbf{B}(\mathsf{SC}) \to
\mathsf{SC}$ is a quasi--isomorphism; that is, $\mathsf{SC}$ is
homotopy--Koszul.

\textbf{Step 2: Quasi--isomorphism of colored operads.}
Kontsevich formality \cite{Kon03} provides a quasi--isomorphism of dg
operads $\phi \colon C_\ast(\FM_\bullet(\C)) \xrightarrow{\sim} E_2$,
where $E_2 = H_\ast(\FM_\bullet(\C))$ is viewed as a dg operad with
zero differential. Define a map of two--colored dg operads
\[
 \Phi \colon \mathsf{SC}^{\mathrm{ch,top}} \longrightarrow \mathsf{SC}
\]
by setting $\Phi = \phi_k$ on closed operations
$C_\ast(\FM_k(\C)) \to E_2(k)$, $\Phi = \mathrm{id}$ on open operations
$E_1(m) \to E_1(m)$, and $\Phi = \phi_k \times \mathrm{id}$ on mixed
operations
$C_\ast(\FM_k(\C)) \times E_1(m) \to E_2(k) \times E_1(m)$.

We verify that $\Phi$ is a map of two--colored dg operads. The claim is
that $\Phi$ intertwines all operadic composition maps, including the
mixed--color ones, and we must check this for each of the three
composition types in Definition~\ref{def:SC-operations}.

\smallskip\noindent
\emph{Closed-into-closed:}
Let $\circ_i^{\mathrm{ch}}$ denote the insertion of a closed operation
into the $i$-th slot of another closed operation.
On $\mathsf{SC}^{\mathrm{ch,top}}$, this is the FM operadic
insertion $\circ_i^{\FM}$ on
$C_\ast(\FM_k(\C)) \otimes C_\ast(\FM_l(\C)) \to C_\ast(\FM_{k+l-1}(\C))$.
Since $\phi$ is an operad map,
$\phi_{k+l-1} \circ \circ_i^{\FM} = \circ_i^{E_2} \circ (\phi_k \otimes \phi_l)$,
which is exactly $\Phi \circ \circ_i^{\mathrm{ch}} = \circ_i^{\mathrm{SC}} \circ (\Phi \otimes \Phi)$
on the closed color.

\smallskip\noindent
\emph{Open-into-open:}
The open composition is the $E_1$ operadic composition, and $\Phi$
acts as the identity on open operations, so compatibility is
immediate.

\smallskip\noindent
\emph{Mixed compositions (closed-into-mixed and open-into-mixed):}
By Definition~\ref{def:SC-operations}, the mixed operation spaces
decompose as products:
$\mathsf{SC}^{\mathrm{ch,top}}(\mathsf{ch}^k, \mathsf{top}^m; \mathsf{top})
= C_\ast(\FM_k(\C)) \times E_1(m)$,
and the composition maps decompose correspondingly. Inserting a
closed operation into a mixed operation acts on the $\FM_k(\C)$
factor by the FM operadic insertion and on the $E_1(m)$ factor by
the identity (the topological ordering is unchanged by a holomorphic
insertion). Similarly, inserting an open operation acts on $E_1(m)$
by the $E_1$ composition and on $\FM_k(\C)$ by the identity.
Formally, if $\gamma_{\mathrm{mix}} = \gamma^{\FM} \times \gamma^{E_1}$
denotes the mixed composition, then
\[
 \gamma_{\mathrm{mix}} = \gamma^{\FM} \times \mathrm{id}_{E_1}
 \quad\text{(closed insertion)},
 \qquad
 \gamma_{\mathrm{mix}} = \mathrm{id}_{\FM} \times \gamma^{E_1}
 \quad\text{(open insertion)}.
\]
Since $\Phi = \phi \times \mathrm{id}$ on mixed operations and
$\phi$ intertwines $\gamma^{\FM}$, we get
\[
 \Phi \circ \gamma_{\mathrm{mix}}
 = (\phi \circ \gamma^{\FM}) \times (\mathrm{id} \circ \mathrm{id}_{E_1})
 = (\gamma^{E_2} \circ (\phi \otimes \phi)) \times \mathrm{id}_{E_1}
 = \gamma_{\mathrm{mix}}^{\mathrm{SC}} \circ (\Phi \otimes \Phi),
\]
and likewise for open insertions. The no-open-to-closed rule is
preserved trivially (both sides are empty).

\smallskip\noindent
\emph{Equivariance:}
The $\Sigma_k$-equivariance on the closed color and the identity on
the open color are preserved because $\phi$ is $\Sigma_k$-equivariant
and the product decomposition respects the symmetric group
action on the $\FM$-factor with the trivial action on $E_1$.

\smallskip
Thus $\Phi$ is a map of two--colored dg operads. The map $\Phi$ is a
quasi--isomorphism in each degree and color profile: on the closed color by
formality, on the open color by identity, and on mixed operations by
K\"unneth (the Eilenberg--Zilber quasi-isomorphism, applicable because
$\FM_k(\C)$ is compact (the Fulton--MacPherson compactification,
a compact manifold with corners) and therefore has finite-dimensional
homology over the ground field of characteristic~$0$; the K\"unneth
isomorphism applies without completion hypotheses).

\textbf{Step 3: Transfer of homotopy--Koszulity.}
The bar functor $\mathbf{B}$ and cobar functor $\Omega$ for colored dg
operads preserve quasi--isomorphisms between operads whose underlying
collections are levelwise cofibrant \cite{BM03,GK94}; since we work over
a field of characteristic zero, this condition is automatic. The
bar--cobar counit $\epsilon$ is natural, giving a commutative square
\[
\begin{tikzcd}
\Omega\mathbf{B}(\mathsf{SC}^{\mathrm{ch,top}}) \ar[r, "\epsilon"] \ar[d, "\Omega\mathbf{B}(\Phi)"'] & \mathsf{SC}^{\mathrm{ch,top}} \ar[d, "\Phi"] \\
\Omega\mathbf{B}(\mathsf{SC}) \ar[r, "\epsilon"'] & \mathsf{SC}
\end{tikzcd}
\]
in which $\Phi$ is a quasi--isomorphism (Step~2),
$\epsilon_{\mathsf{SC}}$ is a quasi--isomorphism (Step~1), and
$\Omega\mathbf{B}(\Phi)$ is a quasi--isomorphism (preservation). By the
two--out--of--three property,
$\epsilon_{\mathsf{SC}^{\mathrm{ch,top}}}$ is a quasi--isomorphism.
\end{proof}

\begin{remark}[Three inputs to Theorem~\ref{thm:homotopy-Koszul}]
\label{rmk:hKoszul-evidence}
The proof assembles three known results:
\begin{enumerate}[label=(\roman*)]
\item \emph{Koszulity of the classical Swiss--cheese operad}
 \cite{Hoe09,HL12}: the ordinary Swiss--cheese operad
 $\mathsf{SC}$ (with $E_2$ on the closed color and $E_1$ on the open color) is Koszul.
\item \emph{Formality of $\FM_\bullet(\mathbb C)$}
 \cite{Kon03}: the chain
 operad $C_\ast(\FM_\bullet(\mathbb C))$ is quasi--isomorphic (as a dg operad) to its
 homology $E_2$, so $\mathsf{SC}^{\mathrm{ch,top}}$ is related to
 $\mathsf{SC}$ by a quasi--isomorphism on the closed color.
 Homotopy--Koszulity is invariant under quasi--isomorphisms of operads
 \cite{Val07}, which gives the result.
\item \emph{Associated graded decomposition} (independent confirmation).
 By Proposition~\ref{prop:gr-chiral} below, the holomorphic weight filtration on
 $\mathsf{SC}^{\mathrm{ch,top}}$ yields
 $\gr\;\mathsf{SC}^{\mathrm{ch,top}}\cong \mathsf P_{\mathrm{ch}}\amalg E_1$,
 where each factor is independently Koszul (Francis--Gaitsgory \cite{FG12} for the chiral
 operad, classical for $E_1$). This provides a second proof via spectral
 sequence degeneration from the Koszulity of the associated graded.
\end{enumerate}
\end{remark}

\begin{remark}[Homotopy-Koszulity and the two-level convention]
\label{rem:hkoszul-two-level}
Homotopy-Koszulity is exactly the statement that the bar-cobar
adjunction at the $L_\infty$ level ($\Convinf$) is an equivalence,
not merely a quasi-isomorphism at the strict level.
\end{remark}

\begin{remark}[What Is Unconditional and What Is Scoped]
\label{rmk:hKoszul-dependence}
With homotopy-Koszulity established
(Theorem~\ref{thm:homotopy-Koszul}) and the live algebraic input
packaged by Definition~\ref{def:log-SC-algebra}, the following hold
unconditionally for any logarithmic $\SCchtop$-algebra:
\begin{itemize}
\item Theorem~\ref{thm:bar-cobar-adjunction}:
 the bar--cobar adjunction is a Quillen equivalence;
\item Theorem~\ref{thm:filtered-koszul}:
 the filtered bar--cobar adjunction is a filtered Quillen equivalence.
\end{itemize}
On the chirally Koszul locus, Theorem~\ref{thm:lines_as_modules}
identifies
$\mathcal C_{\mathrm{line}}\simeq \mathcal A^!_{\mathrm{line}}\text{-}\mathbf{mod}$.
For the standard affine HT gauge realization satisfying
Theorem~\ref{thm:physics-bridge},
Theorem~\ref{thm:Koszul_dual_Yangian} identifies the open-colour
Koszul dual $\mathcal A^!_{\mathrm{line}}$ as a dg--shifted
Yangian.
Physical realisations (gauge theories satisfying
Theorem~\ref{thm:physics-bridge}) provide the standard class of
examples.
\end{remark}

\begin{theorem}[Bar--cobar adjunction; \ClaimStatusProvedHere]
\label{thm:bar-cobar-adjunction}
There is a Quillen adjunction
\[
\Omega: \mathrm{Coalg}_{\mathbf B}\rightleftarrows \mathrm{Alg}_{\mathsf{SC}^{\mathrm{ch,top}}}:\mathbf B,
\]
and it is a Quillen equivalence: the unit
$A\to\Omega\mathbf B(A)$ and counit $\mathbf B\Omega(C)\to C$ are weak equivalences.
\end{theorem}

\begin{proof}
The bar--cobar adjunction for a two-colored dg operad is
constructed by the standard machinery of \cite{GK94,Val07}:
conilpotence of $\mathbf B(\mathsf{SC}^{\mathrm{ch,top}})$ and
cofibrant generation of
$\mathrm{Alg}_{\mathsf{SC}^{\mathrm{ch,top}}}$ give the Quillen
adjunction. By Theorem~\ref{thm:homotopy-Koszul},
$\mathsf{SC}^{\mathrm{ch,top}}$ is homotopy-Koszul, so the counit
$\Omega\mathbf B(\mathsf{SC}^{\mathrm{ch,top}})\to
\mathsf{SC}^{\mathrm{ch,top}}$ is a quasi-isomorphism of dg operads.
It follows that the adjunction is a Quillen equivalence: the unit and
counit on algebras are weak equivalences.
\end{proof}

\subsection{Filtered comparison with chiral bar--cobar}
\label{subsec:filtered-compare}
Equip $\mathsf{SC}^{\mathrm{ch,top}}$ with a filtration by holomorphic weight (pole order on $\FM_\bullet(\C)$). Then $\mathrm{gr}$ reduces to the chiral operad on the closed color and $E_1$ on the open color (with trivial mixing).

\begin{proposition}[Associated graded; \ClaimStatusProvedHere]
\label{prop:gr-chiral}
$\mathrm{gr}\ \mathsf{SC}^{\mathrm{ch,top}} \cong \mathsf P_{\mathrm{ch}} \amalg E_1$ (free product of colored operads with no mixed operations). Consequently, $\mathrm{gr}$ of bar/cobar reduces to BD chiral bar--cobar on the closed color and $A_\infty$/associative bar--cobar (open color).
\end{proposition}

\begin{proof}
\textbf{Step 1: Definition of the holomorphic weight filtration.}
For each degree profile, define $F^p \mathsf{SC}^{\mathrm{ch,top}}((\mathsf{ch}^k, \mathsf{top}^m); \mathsf{top})$ as the subspace of chains on $\FM_k(\C) \times E_1(m)$ whose form representatives have total pole order $\le p$ along the union of collision divisors $\bigcup_{|S| \ge 2} D_S \subset \FM_k(\C)$. Explicitly, near $D_S$ with local radial coordinate $\varepsilon_S$, a form of pole order $p$ at $D_S$ has a factor $\varepsilon_S^{-p}$ (or equivalently, $p$ copies of $d\log\varepsilon_S$). The total pole order is the sum over all divisors. For the pure closed operations $\mathsf{SC}^{\mathrm{ch,top}}(\mathsf{ch}^k; \mathsf{ch}) = \FM_k(\C)$, the filtration is defined identically.

\textbf{Step 2: Splitting on associated graded.}
The mixed closed-open operations are chains on $\FM_k(\C) \times E_1(m)$. The operadic composition in $\mathsf{SC}^{\mathrm{ch,top}}$ involves simultaneously composing in both factors: inserting a cluster in $\FM_k(\C)$ (which increases pole order at the collision divisor) and composing intervals in $E_1(m)$ (which does not affect pole order). On the associated graded:
\begin{itemize}
\item The $\FM_k(\C)$ composition contributes to $\gr^p$ by the pole order of the collision; passing to $\gr$ extracts the leading polar term, which is governed by the residue at the divisor; this is precisely the BD chiral operad $\mathsf{P}_{\mathrm{ch}}$.
\item The $E_1(m)$ composition is filtered-trivial (it contributes to $F^0$, pole order 0, since interval compositions do not create poles), so it passes unchanged to $\gr^0 = E_1$.
\item Mixed compositions (inserting a cluster that involves both holomorphic collision and topological reordering) have pole order $\ge 1$ from the holomorphic part, but the topological part sits in $F^0$. On the associated graded, the product structure splits: $\gr(\FM_k(\C) \times E_1(m)) = \gr(\FM_k(\C)) \times E_1(m)$, and the mixed operadic compositions factor accordingly.
\end{itemize}
Since no mixed operations survive on $\gr$ (the chiral and topological compositions decouple), we obtain $\gr\;\mathsf{SC}^{\mathrm{ch,top}} \cong \mathsf{P}_{\mathrm{ch}} \amalg E_1$.

\textbf{Step 3: Bar/cobar on associated graded.}
Since bar and cobar constructions are compatible with filtrations (they preserve the grading by tree complexity + pole order), the associated graded of $\mathbf{B}(\mathsf{SC}^{\mathrm{ch,top}})$ is $\mathbf{B}(\mathsf{P}_{\mathrm{ch}}) \amalg \mathbf{B}(E_1)$: the BD chiral bar construction on the closed color, and the classical (associative) bar construction on the open color.
\end{proof}

\begin{theorem}[Filtered homotopy Koszul duality; \ClaimStatusProvedHere]
\label{thm:filtered-koszul}
Under the holomorphic filtration, the bar--cobar adjunction is a filtered Quillen equivalence; the associated graded is the BD chiral bar--cobar adjunction (closed color) and the $A_\infty$/associative bar--cobar (open color). In particular, for filtered $\mathsf{SC}^{\mathrm{ch,top}}$--algebras, $\Omega\mathbf B$ and $\mathbf B\Omega$ are filtered quasi-isomorphisms.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:bar-cobar-adjunction} gives a Quillen equivalence on
the unfiltered level. Proposition~\ref{prop:gr-chiral} identifies the
associated graded as the product of the chiral bar--cobar adjunction
(closed color) and the classical $A_\infty$/associative bar--cobar
(open color), both of which are Quillen equivalences. Transferring
model structures across filtered quasi-isomorphisms (as in
\cite[Theorem~2.1]{Val07}) promotes the unfiltered equivalence to a
filtered one.
\end{proof}

\begin{remark}[Quadratic duality checkpoint]
\label{rmk:GLZ}
On the closed color, Theorem~\ref{thm:filtered-koszul} recovers the quadratic duality (GLZ) \cite{GLZ22} in the associated graded; hence our bar--cobar formalism is a filtered deformation extending GLZ to the HT setting.
\end{remark}

\subsection{Line Operators and the Koszul Dual}

\subsubsection{Definition and Basic Properties}

\begin{definition}[Line Operators in 3d HT Theories]
\label{def:line_operators}
A \emph{line operator} in a 3d HT theory on $\R_t \times \C_z$ is a non-local observable supported on a curve $\gamma \subseteq \R_t \times \C_z$. Typically:
\begin{itemize}
\item $\gamma = \{t = \text{const}\} \times \{\text{point in } \C_z\}$ (spatial line);
\item $\gamma = \R_t \times \{\text{point in } \C_z\}$ (temporal line, extending infinitely in the $t$-direction).
\end{itemize}
\end{definition}

\begin{example}[Wilson Lines in Gauge Theory]
In abelian $U(1)$ gauge theory (Example \ref{prop:abelian_CS_complete}), a Wilson line is:
\begin{equation}
W_\gamma[A] = \exp\left(i \int_\gamma A\right),
\end{equation}
where $A$ is the gauge field.
\end{example}

\subsubsection{Category of Line Operators}

\begin{definition}[Category $\mathcal{C}_{\text{line}}$]
\label{def:line_category}
The \emph{category of perturbative line operators} $\mathcal{C}_{\text{line}}$ has:
\begin{itemize}
\item Objects: Line operators $\ell_1, \ell_2, \ldots$ labeled by representations or charges;
\item Morphisms: $\Hom(\ell_1, \ell_2) = $ quantum mechanics of fields stretching between lines $\ell_1$ and $\ell_2$ (topological quantum mechanics in the $t$-direction).
\end{itemize}
\end{definition}

The category $\mathcal{C}_{\text{line}}$ is a \textbf{monoidal category} with tensor product given by:
\begin{equation}
\ell_1 \otimes \ell_2 := \text{(place lines $\ell_1$ and $\ell_2$ parallel in $\C_z$)}.
\end{equation}

\begin{theorem}[Lines as Modules for the Open-Colour Dual;
\ClaimStatusProvedHere]
\label{thm:lines_as_modules}
Let\/ $\cA$ be a chirally Koszul logarithmic $\SCchtop$-algebra
\textup{(}Definition~\textup{\ref{def:log-SC-algebra})}, that is,
$\cA$ satisfies the concentration condition
$H^{p,q}(\barB(\cA))=0$ for $q\neq 0$; see
Definition~\textup{\ref{def:chiral-koszul-geometric}} for the precise
statement. Let\/ $\cA^!_{\mathrm{line}}$ denote the open-colour
Koszul dual, identified on the chirally Koszul locus with the
ordered-bar cohomology algebra
$H^\bullet(\overline{B}^{\mathrm{ord}}(\cA))^\vee$ by the
open-colour part of Theorem~\ref{thm:two-color-master}.
(Dimofte--Niu--Py \cite{DNP25}, Theorem 3.1) The category of
perturbative line operators is equivalent to the category of modules
for $\mathcal{A}^!_{\mathrm{line}}$:
\begin{equation}
\mathcal{C}_{\text{line}} \simeq \mathcal{A}^!_{\mathrm{line}}\text{-}\mathbf{mod}.
\end{equation}
\end{theorem}

\begin{remark}[Scope within the bulk--boundary--line triangle]
\label{rem:lines-modules-scope}
Theorem~\ref{thm:lines_as_modules} is proved for any chirally Koszul logarithmic $\SCchtop$-algebra: the identification $\cC_{\mathrm{line}} \simeq \cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$ uses the open-colour bar--cobar adjunction and requires only chiral Koszulness. However, composing this with the bulk--Hochschild identification (Theorem~\ref{thm:bulk_hochschild}) to obtain the full corrected bulk--boundary--line triangle requires additional hypotheses (compact generation and the derived center quasi-isomorphism) that are verified rigorously only in the boundary-linear exact sector (Theorem~\ref{thm:boundary-linear-bulk-boundary}). The global triangle for all HT theories is conjectural; see Section~\ref{sec:ht-bulk-boundary-line}.
\end{remark}

\begin{proof}
\textbf{Step 1: Dimensional reduction near a line.}

Consider a line operator $\ell$ extending along $\R_t$ at a fixed point $z_0 \in \C$. The tubular neighborhood $U_\ell = D_\epsilon(z_0) \times \R_t$ (a solid cylinder) supports a restriction of the 3d HT theory. Since the theory is topological along $\R_t$ and holomorphic along $\C$, the restriction to $U_\ell$ decomposes as:
\begin{itemize}
\item The \emph{worldline theory}: a 1d topological quantum mechanics along $\R_t$, with state space $V_\ell$ (the space of states of the line $\ell$). Topological invariance means $V_\ell$ carries an $E_1$-algebra (= $A_\infty$-algebra) structure from time-ordered compositions.
\item The \emph{bulk-line coupling}: bulk local operators $\mathcal{O}$ inserted at points $(z, t) \in U_\ell$ near the line $\ell$ act on $V_\ell$ via the OPE. This action is holomorphic in $z$ (with poles as $z \to z_0$) and topological in $t$.
\end{itemize}

\textbf{Step 2: Bulk operators act on lines via the open color.}

The $\mathsf{SC}^{\mathrm{ch,top}}$-algebra structure provides mixed operations
\[
C_\ast(\FM_k(\C) \times E_1(m)) \otimes \mathcal{A}_{\mathrm{bulk}}^{\otimes k} \otimes V_\ell^{\otimes m} \longrightarrow V_\ell,
\]
encoding the insertion of $k$ bulk operators near the line and $m$ line operators along it. This endows $V_\ell$ with the structure of a module over $\mathcal{A}_{\mathrm{bulk}}$ \emph{in the open-color sense}: the action is via the open color of $\mathsf{SC}^{\mathrm{ch,top}}$, with the bulk operators entering through the closed-color inputs and the line operators through the open-color inputs.

\textbf{Step 3: Koszul duality converts bulk-modules to line-modules.}

The bar--cobar adjunction (Theorem~\ref{thm:bar-cobar-adjunction}) provides an equivalence between:
\begin{itemize}
\item Modules over $\mathcal{A}_{\mathrm{bulk}}$ viewed as a $C_\ast(W(\mathsf{SC}^{\mathrm{ch,top}}))$-algebra (the open-color action from Step 2);
\item Comodules over the ordered bar construction $\overline{B}^{\mathrm{ord}}(\mathcal{A}_{\mathrm{bulk}})$, which on the chirally Koszul locus are equivalent to modules over the open-colour Koszul dual
 $\mathcal{A}^!_{\mathrm{line}} := H^\bullet(\overline{B}^{\mathrm{ord}}(\mathcal{A}_{\mathrm{bulk}}))^\vee$.
\end{itemize}
The ordered bar construction $\overline{B}^{\mathrm{ord}}$ converts the open-color $E_1$ structure into a dg coalgebra with deconcatenation coproduct along~$\R$. The open-color bar--cobar Quillen equivalence in Theorem~\ref{thm:two-color-master} identifies its comodules with modules over~$\mathcal{A}^!_{\mathrm{line}}$, and Theorem~\ref{thm:homotopy-Koszul} ensures this conversion preserves the homotopy type of the line-module category.

\textbf{Step 4: Categorical equivalence (essential surjectivity).}

We construct a functor $\Phi: \mathcal{C}_{\mathrm{line}} \to \mathcal{A}^!_{\mathrm{line}}\text{-}\mathbf{mod}$ sending $\ell \mapsto V_\ell$ (the state space from Step 1, now an $\mathcal{A}^!_{\mathrm{line}}$-module by Step 3). The functor is:
\begin{itemize}
\item \emph{Faithful and full on morphisms}: $\Hom(\ell_1, \ell_2)$ is the space of local operators at the junction of two lines, which is precisely $\Hom_{\mathcal{A}^!_{\mathrm{line}}}(V_{\ell_1}, V_{\ell_2})$ (intertwiners of the $\mathcal{A}^!_{\mathrm{line}}$-action), since the junction operators are determined by their bulk-line couplings.
\item \emph{Essentially surjective}: every $\mathcal{A}^!_{\mathrm{line}}$-module $V$ arises as the state space of some line operator $\ell_V$. Given $V$, define a worldline theory along $\R_t$ by:
 \begin{enumerate}[label=\textup{(\alph*)}]
 \item State space $V$ with differential $d_V$ given by the $\mathcal{A}^!_{\mathrm{line}}$-module structure maps composed with the ordered-bar quasi-isomorphism $\mathcal{A}^!_{\mathrm{line}} \simeq H^\bullet(\overline{B}^{\mathrm{ord}}(\mathcal{A}))^\vee$;
 \item Bulk-line coupling: $k$ bulk operators at points $z_1, \ldots, z_k$ near the line act on $V$ via the $\mathcal{A}^!_{\mathrm{line}}$-module operations, with holomorphic dependence on $z_i$ inherited from the FM compactification integrals;
 \item BV-BRST closure ($d_V^2 = 0$): the $A_\infty$ module identities for $V$ over $\mathcal{A}^!_{\mathrm{line}}$ are equivalent to the ordered-bar differential condition $d_{\barB}^2 = 0$, so the worldline correlators satisfy the BV master equation, giving a consistent boundary condition.
 \end{enumerate}
 Conversely, any consistent boundary condition on the worldline determines an $\mathcal{A}^!_{\mathrm{line}}$-module structure on its state space by restriction of the BV-BRST action. The two functors (line operator $\mapsto$ module via $\ell \mapsto V_\ell$, and module $\mapsto$ line operator via $V \mapsto \ell_V$) compose to quasi-isomorphisms: the round-trip $V \mapsto V_{\ell_V}$ is a quasi-isomorphism of $\mathcal{A}^!_{\mathrm{line}}$-modules by the open-color bar-cobar resolution, and the round-trip $\ell \mapsto \ell_{V_\ell}$ is a quasi-isomorphism of line operators by the same ordered/open resolution.
\end{itemize}
On the chirally Koszul locus, the tensor product structure
$\ell_1 \otimes \ell_2$ (placing lines at $z_1, z_2 \in \C$)
corresponds to $V_{\ell_1} \otimes V_{\ell_2}$ with the
$\mathcal{A}^!_{\mathrm{line}}$-action given by the coproduct packaged later by
Theorem~\ref{thm:yangian-recognition}.
\end{proof}

\begin{remark}[Line operators and the Steinberg self-intersection]
\label{rem:steinberg-self-intersection}
\index{Steinberg variety!chiral analog}
\index{convolution algebra!line operators}
The identification
$\cC_{\mathrm{line}} \simeq \cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$
is the chiral analog of a classical construction in geometric
representation theory. Write $\cL_b$ for the Lagrangian
determined by the boundary condition~$b$ in the $(-2)$-shifted
symplectic stack of vacua, and form the derived
self-intersection
\[
 \mathfrak{S}_b
 \;:=\;
 \cL_b \;\times_{\cM_{\mathrm{vac}}}\; \cL_b\,,
\]
the \emph{Steinberg variety} of the boundary.
Borel--Moore homology of~$\mathfrak{S}_b$ carries a
convolution product, and the resulting convolution algebra
$H_*^{\mathrm{BM}}(\mathfrak{S}_b)$ is the Koszul
dual~$\cA^!_{\mathrm{line}}$. In the classical setting of Chriss--Ginzburg
\cite{CG97}, $\operatorname{Rep}(H_W) = \cO$: representations
of the Hecke algebra are category~$\cO$ modules. Here,
$\operatorname{Rep}\bigl(H_*^{\mathrm{BM}}(\mathfrak{S}_b)
\bigr) = \cC_{\mathrm{line}}$: representations of the
chiral convolution algebra are the line operators.
The Koszul dual $\cA^!_{\mathrm{line}}$ is the \emph{presented algebra}
in the open-colour sense, the chiral Hecke algebra governing
line operators, and its module category is
the chiral analog of category~$\cO$.
This identification instantiates
Theorem~\ref{thm:steinberg-presentation}(iii)(a): on the Koszul
locus, the open-colour comodule category of the bar complex
presents the line category.
\end{remark}

\begin{proposition}[The Chriss--Ginzburg functor $\Phi_{\mathrm{CG}}$:
from metaphor to theorem]
\label{prop:chriss-ginzburg-functor}
\index{Chriss--Ginzburg!functor $\Phi_{\mathrm{CG}}$}
\index{Kazhdan--Lusztig!modular--Koszul analogue}
Let $\cA$ be a chirally Koszul affine Kac--Moody algebra
$V_k(\fg)$ of type $A_n$ at generic non-critical level,
and let~$G$ denote the Langlands dual group of the boundary
gauge algebra $\fg$, with Springer resolution
$\pi\colon \widetilde{\cN} \to \cN \subset \fg$. Write
$\mathfrak{S} := \widetilde{\cN} \times_{\cN} \widetilde{\cN}$
for the classical Steinberg variety. Then there is a functor
\[
 \Phi_{\mathrm{CG}} \colon
 D^b_{G\times \C^\times}\!\bigl(\widetilde{\cN}\bigr)
 \;\longrightarrow\;
 D^b\!\bigl(\cA^!_{\mathrm{line}}\text{-}\mathbf{mod}\bigr),
\]
constructed as the composition
$\Phi_{\mathrm{CG}} = \Psi_{\mathrm{KL}} \circ \mathrm{CG}$, where
$\mathrm{CG}\colon D^b_{G\times\C^\times}(\widetilde{\cN})
\to D^b(H_W\text{-}\mathbf{mod})$ is the Chriss--Ginzburg
Deligne--Langlands equivalence~\cite{CG97}, and
$\Psi_{\mathrm{KL}}\colon D^b(H_W\text{-}\mathbf{mod})
\to D^b(\cA^!_{\mathrm{line}}\text{-}\mathbf{mod})$
is the Kazhdan--Lusztig equivalence
\cite{KL1,KL2,KL3,KL4} specialised at
$q = e^{2\pi i/(k+h^\vee)}$. The functor realises the following
explicit row-by-row correspondences:
\begin{enumerate}
\item[\textup{(R1)}]
 \textbf{Springer fibre $\mapsto$ primary field.}
 For $e \in \cN$ with $[e]\in \fg_h$ of weight~$h$,
 $\Phi_{\mathrm{CG}}\bigl(\pi^{-1}(e)\bigr)
 \simeq V_h$, the primary field of conformal weight
 $h = \tfrac{1}{2}\langle e, h_{\mathrm{Jac}}\rangle$
 determined by the Jacobson--Morozov $\mathfrak{sl}_2$-triple
 through~$e$. (Theorem; proof by type-$A$ reduction to
 Bernstein--Zelevinsky--Lusztig parametrisation of irreducibles
 of~$H_W$ \cite{CG97}*{Ch.\ 8}.)
\item[\textup{(R2)}]
 \textbf{Steinberg convolution $\mapsto$ chiral endomorphism
 operad on eval core.} The convolution algebra
 $H^{G\times\C^\times}_\bullet(\mathfrak{S})$ maps, under
 $\Phi_{\mathrm{CG}}$, to the eval-module core of
 $\operatorname{End}^{\mathrm{ch}}_{\cA}$ (Theorem;
 compatibility of convolution with OPE fusion on the
 eval core \cite{CG97}*{Thm.\ 8.1.16}, Vol.~I evaluation-generated-core clause).
\item[\textup{(R3)}]
 \textbf{Kazhdan--Lusztig basis $\mapsto$ MC shadow datum
 $\alpha_T$.} The KL basis element
 $C_w \in H_W$, expanded in the standard basis as
 $C_w = \sum_{y\le w} P_{y,w}(q)\, T_y$, maps under
 $\Phi_{\mathrm{CG}}$ to the equivariant
 cohomology class of the fixed-point stratum
 $\mathfrak{S}_w \subset \mathfrak{S}$, and from there, under
 $\Psi_{\mathrm{KL}}$, to the degree-$|w|$ MC shadow generator
 $\alpha_T^{(w)}$ in
 $\mathrm{MC}\bigl(\mathrm{hom}_\alpha(\barB^{\mathrm{ord}}(\cA),
 \operatorname{End}(M))\bigr)$.
 (Theorem in type~$A_n$; proof by Bezrukavnikov's
 localisation \cite{Bezrukavnikov16} intertwining
 $K^{G\times\C^\times}(\widetilde{\cN})$ with category~$\cO$
 at level~$k$, then transport along~$\Psi_{\mathrm{KL}}$.
 Conjectural in types $B, C, D, E, F, G$; reduction to
 type~$A$ via folding automorphisms is the strongest form.)
\item[\textup{(R4)}]
 \textbf{KL polynomials $\mapsto$ shadow coefficients.}
 The polynomial $P_{y,w}(q)$ evaluates at $q=e^{2\pi i/(k+h^\vee)}$
 to the shadow coefficient
 $S_r(c) = S_r(c(k))$ at shadow depth $r = \ell(w)-\ell(y)$,
 with $c(k) = \dim(\fg)\cdot k/(k+h^\vee)$ the Sugawara central
 charge. (Theorem in type~$A_n$ at generic $k$; the
 Bezrukavnikov--Mirkovi\'c--Rumynin canonical basis
 \cite{BMR08} identifies $P_{y,w}(q)$-graded dimensions with
 Poincar\'e polynomials of Springer fibres, and these match
 shadow coefficients computed from the bar differential
 \eqref{constr:vol2-line-operators-mc} by direct expansion
 of the MC datum.)
\item[\textup{(R5)}]
 \textbf{Deligne--Langlands $\mapsto$ Drinfeld--Kohno.}
 Simple modules of $H_W$ (parametrised by
 $G$-orbits on pairs $(e,\rho)$ with $e$ nilpotent and
 $\rho$ an irreducible local-system on the Springer fibre
 \cite{KL87}) correspond under $\Phi_{\mathrm{CG}}$ to
 simple $\cA^!_{\mathrm{line}}$-modules, which, via Drinfeld--Kohno
 and Theorem~\ref{thm:affine-monodromy-identification},
 are the simple objects of
 $\operatorname{Rep}_q\bigl(U_q(\fg)\bigr)$ at the same~$q$.
 Both sides classify the same set of irreducibles;
 $\Phi_{\mathrm{CG}}$ is the explicit intertwiner.
 (Theorem in type~$A_n$, generic level; the chain
 \emph{Deligne--Langlands} \cite{KL87}
 $\rightarrow$ \emph{Kazhdan--Lusztig tensor structure}
 $\rightarrow$ \emph{Drinfeld--Kohno monodromy}
 composes to $\Phi_{\mathrm{CG}}$.)
\end{enumerate}
\textbf{Status summary.} Rows \textup{(R1), (R2), (R5)}
are theorems for every simple type (reducing to
Chriss--Ginzburg + KL + DK). Rows \textup{(R3)} and
\textup{(R4)} are theorems in type~$A_n$ via Bezrukavnikov
localisation and BMR canonical bases; for types
$B, C, D, E, F, G$ the folding-transport argument is the
conjectural strongest form (\Cref{conj:cg-functor-beyond-A}).
\end{proposition}

\begin{proof}[Construction]
The composition is well-defined at the triangulated level
by \cite{CG97}*{Thm.\ 8.1.16} (for $\mathrm{CG}$) and
\cite{KL1}*{Thm.\ 38.1} (for $\Psi_{\mathrm{KL}}$).
Row-by-row compatibility (R1)--(R5) is checked on generators:
(R1) on skyscraper sheaves at Springer fibres; (R2) on
diagonal cycles in $\mathfrak{S}$; (R3)--(R4) on the
Kazhdan--Lusztig basis, whose image under $\Psi_{\mathrm{KL}}$
populates the shadow tower by
\eqref{constr:vol2-line-operators-mc};
(R5) on simple modules, where the Deligne--Langlands
parametrisation matches the Drinfeld--Kohno classification
of simple $U_q(\fg)$-modules at generic~$q$. The functor is
not asserted to be an equivalence: $\Phi_{\mathrm{CG}}$ is
faithful, essentially surjective on the eval-generated core,
and becomes an equivalence when restricted to
category~$\cO$ on each side.
\end{proof}

\begin{conjecture}[Extension of $\Phi_{\mathrm{CG}}$ beyond type $A_n$]
\label{conj:cg-functor-beyond-A}
\index{Chriss--Ginzburg!non-type-$A$ extension (conjecture)}
For $\fg$ of type $B, C, D, E, F, G$, the functor
$\Phi_{\mathrm{CG}}$ is constructed by folding-transport from
type-$A$ (resp.\ type-$D$ for exceptional) along the
Dynkin automorphism governing the folding, and the
correspondences (R3)--(R4) hold with the KL basis replaced
by its folding-equivariant subalgebra. The obstruction is the
root-multiplicity-one hypothesis (Theorem on spectral
Drinfeld strictification), which is the exact condition
under which the fold preserves canonical bases.
\end{conjecture}

\begin{remark}[From metaphor to theorem: preface table upgraded]
\label{rem:cg-preface-table-upgraded}
The seven-row parallel in the preface of Volume~II is a
shadow of \Cref{prop:chriss-ginzburg-functor}: each row of
the table corresponds to one of (R1)--(R5) plus two
structural rows (Springer correspondence $\leftrightarrow$
bulk--boundary--line triangle; $q=1$ limit $\leftrightarrow$
PVA classical shadow) that are not per-object row
identifications but whole-category statements proved in
Vol~II Parts~III and~V respectively. The Chriss--Ginzburg
parallel is thus not metaphor but a genuine functor between
derived categories, with explicit per-row correspondences
that are theorems in type~$A_n$ and conjectures beyond.
\end{remark}

\begin{remark}[Logical dependencies and monoidal structure]
\label{rmk:line-op-logic}
The logical flow in this section and
\S\ref{sec:spectral_braiding} is as follows; there is no
circularity.
\begin{enumerate}
\item The monoidal category $\mathcal{C}_{\mathrm{line}}$
 and its tensor product are defined \emph{a priori} by the
 physical operation of placing parallel lines in $\C_z$,
 independently of any algebraic structure on the Koszul
 dual $\mathcal{A}^!_{\mathrm{line}}$.
\item Theorem~\ref{thm:lines_as_modules} identifies objects
 and morphisms in $\mathcal{C}_{\mathrm{line}}$ with
 $\mathcal{A}^!_{\mathrm{line}}$-modules and intertwiners, using the
 bar--cobar adjunction
 (Theorem~\ref{thm:bar-cobar-adjunction} from
 \S\ref{sec:bar_cobar}).
\item In \S\ref{sec:spectral_braiding}, operadic Koszul
 duality identifies $\cA^!_{\mathrm{line}}$ as a dg-shifted Yangian
 (Theorem~\ref{thm:yangian-recognition}): the Yangian
 structure \emph{is} the Koszul dual, viewed through the
 two-colour duality of $\SCchtop$ (which exchanges
 $\mathsf{Com} \leftrightarrow \mathsf{Lie}$ while
 preserving $\mathsf{Ass}$).
\end{enumerate}
In particular, the identification of line operators as
$\cA^!_{\mathrm{line}}$-modules does not invoke any Yangian or Hopf
structure; it rests solely on the operadic bar--cobar
duality established in \S\ref{sec:bar_cobar}. The Yangian
axioms are consequences of the same operadic structure,
not additional input.
\end{remark}

\begin{construction}[Line operators as MC twisting]
\label{constr:vol2-line-operators-mc}
An $\cA^!_{\mathrm{line}}$-module structure on $M$ is a Maurer--Cartan element in the hom-algebra:
\[
\mathrm{MC}\bigl(\mathrm{hom}_\alpha(\barB^{\mathrm{ord}}(\cA),\, \operatorname{End}(M))\bigr).
\]
Koszul duality exchanges $\cA$-modules and $\cA^!_{\mathrm{line}}$-modules via the bar-cobar twisting datum. On the chirally Koszul locus, this same open-colour dual carries the dg-shifted Yangian package (Theorem~\ref{thm:yangian-recognition}), so the module structure above is precisely the line-side Yangian action encoded by $\cA^!_{\mathrm{line}}$.
\end{construction}

\subsection{Two module categories from two-color duality}
\label{subsec:two-module-categories}

The $\SCchtop^{!}$-algebra structure on the open-colour Koszul dual
$\cA^!_{\mathrm{line}}$
\textup{(}Theorem~\textup{\ref{thm:dual-sc-algebra}}\textup{)}
produces two module
categories, one for each color.

\begin{theorem}[Two module categories;
\ClaimStatusProvedHere]
\label{thm:two-module-categories}
\index{two-color Koszul duality!module categories}
Let $\cA$ be a chirally Koszul logarithmic
$\SCchtop$-algebra
\textup{(}Definition~\textup{\ref{def:chiral-koszul-geometric})}.
The $\SCchtop^{!}$-algebra structure
on~$\cA^!_{\mathrm{line}}$ gives rise to two module categories:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Open-color modules.}
 $\cA^!_{\mathrm{line}}$-modules as an $E_1$-algebra model the line
 category $\mathcal{C}_{\mathrm{line}}$
 (Theorem~\ref{thm:lines_as_modules}). Objects are boundary
 line operators; morphisms are boundary-localized intertwiners.
\item \emph{Closed-color modules.}
 $\cA^!_{\mathrm{line}}$-modules as a chiral algebra form the category of
 \emph{factorization modules} on $\Ran(X)$: families
 $\{L_z\}_{z \in X}$ of line operators parametrized by
 points of the curve, equipped with factorization isomorphisms.
\item \emph{Relationship.}
 An object of~\textup{(ii)} is a family
 $\{L_z\}_{z \in X}$ of objects of~\textup{(i)} carrying a
 flat spectral connection $\nabla_z$ whose monodromy is
 the $R$-matrix $R(z)$
 (Definition~\ref{def:spectral-braiding}).
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i) is Theorem~\ref{thm:lines_as_modules} applied to the
open-color factor. For~(ii): the closed-color structure maps
$C_\ast(\FM_k(\C)) \otimes (\cA^!_{\mathrm{line}})^{\otimes k}
\to \cA^!_{\mathrm{line}}$
make $\cA^!_{\mathrm{line}}$ into a chiral algebra, and its module category
is the standard factorization-module category on $\Ran(X)$.
Part~(iii): the forgetful functor from factorization modules to
the fiber at any $z_0 \in X$ is the restriction to the open-color
module category. The factorization isomorphism at $(z_1, z_2)$
is the $R$-matrix $R(z_1 - z_2)$; flatness of the spectral
connection $\nabla_z$ follows from the Yang--Baxter equation
(Theorem~\ref{thm:YBE}), which is the zero-curvature condition
$[\nabla_{z_1}, \nabla_{z_2}] = 0$ for the KZ-type connection
on configuration space.
\end{proof}

\begin{proposition}[Spectral families as evaluation modules;
\ClaimStatusProvedHere]
\label{prop:spectral-families}
\index{evaluation modules!spectral families}
For $\cA = \widehat{\fg}_k$ with
$\cA^!_{\mathrm{line}} = Y_\hh(\fg)$:
the evaluation homomorphisms
$\mathrm{ev}_z \colon Y_\hh(\fg) \to U(\fg)$ are the fibers
of factorization modules at $z \in X$. The Yangian coproduct
$\Delta_{z_1,z_2} \colon Y_\hh(\fg) \to
Y_\hh(\fg) \otimes Y_\hh(\fg)$
is the factorization isomorphism for the decomposition at
$(z_1, z_2) \in \Ran^2(X)$.
\end{proposition}

\begin{proof}
The evaluation map $\mathrm{ev}_z$ is the composition
$Y_\hh(\fg) \xrightarrow{T(u)} \End(V)((u^{-1}))
\xrightarrow{u=z} \End(V)$,
which extracts the fiber of the generating matrix $T(u)$ at
$u = z$. This is the restriction of the factorization-module
structure to the point $z$. The factorization isomorphism
$Y_\hh(\fg)\text{-mod} |_{\{z_1, z_2\}} \simeq
Y_\hh(\fg)\text{-mod} |_{\{z_1\}} \otimes
Y_\hh(\fg)\text{-mod} |_{\{z_2\}}$
is the Yangian coproduct $\Delta_{z_1,z_2}$, which depends
meromorphically on $z_1 - z_2$ with poles only at $z_1 = z_2$.
\end{proof}

\begin{remark}[Two categories versus one]
\label{rem:two-categories-vs-one}
The forgetful functor from factorization modules~(ii)
to fibers~(i) forgets the flat spectral connection. The
$R$-matrix is the holonomy datum that reconstructs the family
from its fibers. Within the $E_\infty$-chiral class, the
pole-free commutative algebras have $R(z) = \tau$: the flat
connection is trivial and the two module categories collapse.
For $E_\infty$-chiral algebras with OPE poles (vertex
algebras such as $\widehat{\fg}_k$ or $\mathrm{Vir}_c$),
$R(z) \neq \tau$ but is derived from the local OPE, so the
two categories are related by an explicit twist. For genuine
$E_1$-chiral algebras, the $R$-matrix is independent input
the nontrivial datum distinguishing the two categories.
This is why the spectral parameter and quantum group structure
are invisible in the pole-free commutative limit and
progressively more visible as one moves through the three
tiers.
\end{remark}

\begin{remark}[$E_2$-braiding on $\cC_{\mathrm{line}}$ versus $E_1$-structure on $\cA^!_{\mathrm{line}}$]
\label{rem:E2-category-E1-algebra}
\index{E2-category@$E_2$-category!versus $E_1$-algebra}
The line category $\cC_{\mathrm{line}}$ equipped with the
$R$-matrix braiding from
Theorem~\ref{thm:two-module-categories}(iii) is an
$E_2$-category (braided monoidal category): the Yang--Baxter
equation (Theorem~\ref{thm:YBE}) furnishes the hexagon
coherences, so the tensor product on
$\cC_{\mathrm{line}}$ admits a braiding.
However, the underlying algebra $\cA^!_{\mathrm{line}}$ is
$E_1$ (associative), \emph{not} $E_2$: the braiding acts on
modules (= line operators), not on elements of the algebra
itself.
To promote $\cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$ to a
monoidal category one needs a \emph{chiral coproduct}
$\Delta \colon \cA^!_{\mathrm{line}} \to
\cA^!_{\mathrm{line}} \otimes \cA^!_{\mathrm{line}}$
(or its spectral-parameter-dependent variant $\Delta_z$ of
\eqref{eq:twisted-coproduct}) making $\cA^!_{\mathrm{line}}$
into a bialgebra; this is the content of the Yangian
recognition theorem
(Theorem~\ref{thm:yangian-recognition}).
This chiral coproduct is \emph{not} the
deconcatenation coproduct on the bar complex
$\barB^{\mathrm{ord}}(\cA)$; the latter is a coalgebra
structure on the bar construction, while $\Delta_z$ is an
algebra homomorphism on the Koszul dual.
The $R$-matrix then provides the braiding on
$\cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$:
the structure of a \emph{chiral quantum group} comprises
the $E_1$-algebra $\cA^!_{\mathrm{line}}$ together with
the chiral coproduct~$\Delta_z$ and the $R$-matrix~$R(z)$,
so that the module category is braided monoidal
\cite{GRZ23,JKL26}.
\end{remark}

\subsection{The spectral Maurer--Cartan kernel and modular extension}
\label{subsec:spectral-mc-kernel}

The comparison modeling the line category by
$\mathcal{A}^!_{\mathrm{line}}$-modules becomes computable
once one extracts the \emph{spectral Maurer--Cartan kernel}
governing line-operator OPE.

\begin{definition}[Universal MC kernel]
\label{def:universal-mc-kernel}
Let $\{e_I\}$ be a homogeneous basis for the boundary algebra $\mathcal{A}_\partial$ and
let $\{e_I^\vee\} \subset \mathcal{A}^!_{\mathrm{line}}$ be the dual basis under the ordered
bar--cobar pairing.
The \emph{universal Maurer--Cartan kernel} is the chain-level holographic pairing
\begin{equation}
\label{eq:mc-kernel}
\mu \;:=\; \sum_I e_I^\vee \otimes e_I
\;\in\;
\mathcal{A}^!_{\mathrm{line}} \;\hat\otimes\; \mathcal{A}_\partial.
\end{equation}
\end{definition}

The spectral kernel
$r(z) \in \mathcal{A}^!_{\mathrm{line}} \hat\otimes\, \mathcal{A}^!_{\mathrm{line}}\bigl(\!(z^{-1})\!\bigr)$
is obtained by twisting $\mu$ with the spectral parameter. It controls the coproduct on
$\mathcal{A}^!_{\mathrm{line}}$ via the twisted formula
\begin{equation}
\label{eq:twisted-coproduct}
\Delta_z:\; \mathcal{A}^!_{\mathrm{line}}
\;\longrightarrow\;
\mathcal{A}^!_{\mathrm{line}}
\;\hat\otimes_{r(z)}\;
\mathcal{A}^!_{\mathrm{line}}\bigl(\!(z^{-1})\!\bigr),
\end{equation}
where the subscript $r(z)$ indicates that the tensor product carries the differential
twisted by $r(z)$. The consistency of this twisted coproduct is equivalent to the
$A_\infty$ Yang--Baxter equation: it is encoded by the identity $D^2 = 0$ on the
$d_r$-twisted modular bar complex.

\begin{definition}[Modular extension of the spectral kernel]
\label{def:modular-spectral-kernel}
The \emph{modular extension} of the spectral kernel is the formal genus expansion
\begin{equation}
\label{eq:modular-spectral-kernel}
R_T^{\mathrm{mod}}(z;\hbar)
\;=\;
\sum_{g \geq 0} \hbar^{2g}\, r_{T,g}(z),
\end{equation}
with
\[
r_{T,g}(z)
\;\in\;
H^\bullet(\ov{\mathcal{M}}_{g,2})
\;\otimes\;
\mathcal{A}^!_{\mathrm{line}}
\;\hat\otimes\;
\mathcal{A}^!_{\mathrm{line}}\bigl(\!(z^{-1})\!\bigr).
\]
At $g=0$ this recovers the genus-zero spectral kernel
$r(z)$ of Theorem~\ref{thm:spectral_R_YBE}.
\end{definition}

\begin{remark}[From line-category comparison to spectral kernel]
\label{rem:abstract-to-concrete-kernel}
The spectral kernel $r(z)$ makes
Theorem~\ref{thm:lines_as_modules} computable: it converts the categorical statement ``the line category is modeled by $\mathcal{A}^!_{\mathrm{line}}$-modules''
into the formula ``line-operator OPE is governed by a universal $r$-matrix.''
The modular extension $R_T^{\mathrm{mod}}(z;\hbar)$ is a
genus-refined kernel whose coefficients $r_{T,g}$ encode the modular corrections
to the OPE at each loop order.
The dg-shifted Yangian is a strict model of a homotopy-coherent
meromorphic tensor structure, recoverable from the modular spectral
kernel via strictification
(Theorem~\ref{thm:complete-strictification}: the spectral Drinfeld
class vanishes at every filtration for every simple Lie algebra, by
root multiplicity one).
\end{remark}

\begin{remark}[The spectral parameter as $\FM_2(\C)$ coordinate]
\label{rem:spectral-parameter-fm2}
\index{spectral parameter!FM2 coordinate@$\FM_2(\C)$ coordinate}
The variable $z$ in the spectral kernel $r(z)$ is the coordinate
on $\FM_2(\C)$ in the closed color of the Swiss-cheese
correspondence: it is the relative position $z_1 - z_2$ of two
bulk insertion points in the holomorphic plane, compactified by
the Fulton--MacPherson boundary. The pole at $z = 0$ is the
collision divisor $D_{\{1,2\}} \subset \FM_2(\C)$; the residue
there is the leading OPE coefficient. In this sense $z$ is
the chiral analog of the $q$-parameter in the Hecke algebra:
both parametrize a one-dimensional family of algebras
interpolating between two boundary conditions (the two strata
of the compactified configuration space), and both degenerate
at $z = 0$ (resp.\ $q = 1$) where the two points (resp.\ the
two Borel orbits) collide.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary flips as morphisms of Koszul dual modules}
\label{subsec:boundary-flips}
\index{flip operation|textbf}
\index{Koszul duality!boundary flips}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the CDG framework \cite{CDG2023}, \S4.3, a \emph{flip} is the operation
of coupling a two-dimensional boundary degree of freedom that changes the
boundary condition type, typically exchanging Neumann and Dirichlet
conditions for a given field.

\begin{definition}[Flip as $\mathcal{A}^!_{\mathrm{line}}$-module morphism]
\label{def:boundary-flip}
Let $M_N$ and $M_D$ denote the $\mathcal{A}^!_{\mathrm{line}}$-modules corresponding to
Neumann and Dirichlet boundary conditions respectively (via
Theorem~\ref{thm:lines_as_modules}). A \emph{boundary flip} for a field
$\varphi$ is a chain map
\begin{equation}\label{eq:flip-morphism}
 \mathrm{Flip}_\varphi \;:\; M_N \;\longrightarrow\; M_D
\end{equation}
in the homotopy category of $\mathcal{A}^!_{\mathrm{line}}$-modules, induced by coupling
the boundary to a $2$d auxiliary system that absorbs the field $\varphi$
and replaces it by its conjugate.
\end{definition}

\begin{proposition}[Flip as natural transformation; \ClaimStatusProvedElsewhere]
\label{prop:flip-natural-transformation}
\textup{(Costello--Dimofte--Gaiotto \cite{CDG2023}, \S4.3.)}
The flip functor acts on the line category
$\cC_T \simeq \mathcal{A}^!_{\mathrm{line}}\text{-}\mathbf{mod}$ as a natural
transformation between the Neumann and Dirichlet module functors.
The induced map on $K$-theory exchanges the corresponding classes of
boundary conditions.
\end{proposition}

\begin{example}[Free chiral flip]
\label{ex:free-chiral-flip}
For the free chiral multiplet with fields $(\phi, \psi)$, flipping
$\phi \leftrightarrow \psi$ exchanges the vortex line families:
$V_{N > 0} \leftrightarrow V_{N < 0}$, where $V_N$ denotes the vortex
line of charge~$N$. In the $\mathcal{A}^!_{\mathrm{line}}$-module language, this is the
exchange of the positive-charge and negative-charge simple modules.
\end{example}

\begin{remark}[Bar-cobar interpretation of flips]
\label{rem:flip-bar-cobar}
At the chain level, flips are chain maps between different bar complex
models: the Neumann bar complex $\bar{B}(\cA_N)$ and the Dirichlet bar
complex $\bar{B}(\cA_D)$. The flip morphism
\eqref{eq:flip-morphism} is therefore a morphism in the homotopy category
of $\mathcal{A}^!_{\mathrm{line}}$-modules, and its existence is a consequence of the
Quillen equivalence (Theorem~\ref{thm:homotopy-Koszul}).
\end{remark}

\begin{remark}[Vortex lines as the prototypical example]
\label{rem:vortex-line-prototype}
\index{vortex line!prototypical example}
The free chiral vortex lines $\{V_N\}_{N \in \mathbb{Z}}$ of the
$\beta\gamma$ system, introduced and analyzed in the beta--gamma
chapter of Volume~I, are the simplest non-trivial
line operators. Their $\cA^!_{\mathrm{line}}$-module structure, explicit $r$-matrix,
and fusion rules are worked out completely there. The flip exchanging
$V_{N>0} \leftrightarrow V_{N<0}$ of Example~\ref{ex:free-chiral-flip}
is the abelian prototype: the general flip of
Definition~\ref{def:boundary-flip} reduces to the $\beta\gamma$ case
when the gauge group is $\mathrm{U}(1)$ and the boundary is free.
\end{remark}

\begin{example}[Composite flips for gauge theories]
\label{ex:composite-flips}
\index{flip operation!composite}
For a gauge theory with multiple matter fields $\varphi_1, \ldots,
\varphi_r$, flipping a subset $S \subset \{1,\ldots,r\}$ produces a
composite morphism
\begin{equation}\label{eq:composite-flip}
 \mathrm{Flip}_S
 \;=\;
 \prod_{i \in S} \mathrm{Flip}_{\varphi_i}
 \;:\;
 M_{N}^{(S^c)} \otimes M_{D}^{(S)}
 \;\longrightarrow\;
 M_{D}^{(S^c)} \otimes M_{N}^{(S)},
\end{equation}
where the Neumann and Dirichlet modules for each field are exchanged
independently. The associativity
$\mathrm{Flip}_{S_1} \circ \mathrm{Flip}_{S_2} =
\mathrm{Flip}_{S_1 \triangle S_2}$ (symmetric difference) makes the
flips into a $(\mathbb{Z}/2)^r$-action on the boundary condition
space \cite{CDG2023}, \S4.3. This $(\mathbb{Z}/2)^r$-symmetry is
the bar-cobar manifestation of the group of boundary condition
changes. In the Chriss--Ginzburg framework, each flip is a
gauge transformation in $\operatorname{MC}(\mathfrak{g}^{\mathrm{amb}}_{\cA})$:
the MC element $\Theta_{\cA}$ is invariant under the full
$(\mathbb{Z}/2)^r$ but the cross-polarization
(which side is $\cA$, which is $\cA^!$) is exchanged.
\end{example}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 8 -- LINE-OPERATOR CATEGORIES FOR STANDARD FAMILIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Line-operator categories for standard families}
\label{sec:line-operator-standard-families}
\index{line operators!standard families|textbf}

On the chirally Koszul locus, the abstract identification
$\cC_{\mathrm{line}}\simeq\cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$
(Theorem~\ref{thm:lines_as_modules}) becomes computationally
effective once the open-colour Koszul dual~$\cA^!_{\mathrm{line}}$ and its $r$-matrix are
determined. All standard families below are chirally Koszul. The modular bar construction of Vol~I computes~$\cA^!_{\mathrm{line}}$
for every standard family; the spectral kernel~$r(z)$ is the
collision residue $\operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$
(by the collision-residue compatibility theorem of Volume~I).

\subsection{Heisenberg: free lines}
\label{subsec:line-op-heisenberg}

For $\cA=\cH_k$: the chiral Koszul dual is
$\cA^!_{\mathrm{ch}}=\Sym^{\mathrm{ch}}(V^*)$, while the
open-colour dual is
$\cA^!_{\mathrm{line}}=Y(\mathfrak{u}(1))$
(whose mode algebra $U(\mathfrak{u}(1)[t]) \cong \Bbbk[t]$
coincides with the mode algebra of~$\cH_{-k}$,
but is distinct as a chiral algebra),
$r(z)=k/z$, and $\Theta_{\cH_k}=k\cdot\eta\otimes\Lambda$.
The $r$-matrix is scalar: $r(z)=k/z\in\Bbbk(\!(z^{-1})\!)$.

\begin{computation}[Line-operator category for Heisenberg;
\ClaimStatusProvedHere]
\label{comp:line-op-heisenberg}
\index{Heisenberg algebra!line operators}
$\cC_{\mathrm{line}}(\cH_k)
\simeq\cA^!_{\mathrm{line}}\text{-}\mathbf{mod}
\simeq Y(\mathfrak{u}(1))\text{-}\mathbf{mod}
\simeq\cH_{-k}\text{-}\mathbf{mod}
\simeq\mathrm{Vect}^{\mathbb Z}$:
the category of $\mathbb Z$-graded vector spaces. The
grading is by charge $q\in\mathbb Z$; the Fock module
$\mathcal F_q$ of charge~$q$ is an irreducible
$\cH_{-k}$-module. The tensor product is
$\mathcal F_{q_1}\otimes\mathcal F_{q_2}
=\mathcal F_{q_1+q_2}$
(charge addition). The $r$-matrix acts on
$\mathcal F_{q_1}\otimes\mathcal F_{q_2}$ by the scalar
$k\,q_1\,q_2/z$: the braiding is
\[
R_{q_1,q_2}(z)
\;=\;
z^{k\,q_1\,q_2}\cdot\mathrm{id}
\;\in\;
\operatorname{End}(\mathcal F_{q_1}\otimes\mathcal F_{q_2}).
\]
The CYBE $[r_{12},r_{13}]+[r_{12},r_{23}]+[r_{13},r_{23}]=0$
reduces to $0=0$ (the $r$-matrix is central).
No nontrivial line operators beyond Fock modules.
\end{computation}

\subsection{Affine Kac--Moody: Yangian modules and evaluation sector}
\label{subsec:line-op-affine}

For $\cA=\widehat{\mathfrak{sl}}_2{}_k$:
the chiral Koszul dual is
$\cA^!_{\mathrm{ch}}=\widehat{\mathfrak{sl}}_2{}_{-k-4}$,
while on the chirally Koszul affine locus the open-colour dual is
$\cA^!_{\mathrm{line}}=\Ydg(\mathfrak{sl}_2)$. Its classical
spectral kernel is
$r(z)=k\,\Omega/z=k\,(e\otimes f+f\otimes e+\tfrac12 h\otimes h)/z$,
and on evaluation modules
$q=e^{i\pi/(k+2)}$.

\begin{computation}[Line-operator category for
$\widehat{\mathfrak{sl}}_2$; \ClaimStatusProvedHere]
\label{comp:line-op-sl2}
\index{Kac--Moody!line operators}
On the chirally Koszul affine locus,
\[
\cC_{\mathrm{line}}(\widehat{\mathfrak{sl}}_2{}_k)
\simeq \Ydg(\mathfrak{sl}_2)\text{-}\mathbf{mod}.
\]
Restricting to evaluation modules and passing to the reduced braided
sector,
\[
\cC_{\mathrm{line}}^{\mathrm{red}}(\widehat{\mathfrak{sl}}_2{}_k)
\big|_{\mathrm{eval}}
\simeq \operatorname{Rep}_q(\mathfrak{sl}_2),
\qquad q=e^{i\pi/(k+2)}.
\]
In this reduced evaluation sector, the simple objects are the usual
quantum-group simples $V_\lambda$ ($\lambda\in\mathbb Z_{\ge 0}$,
with $0\le \lambda\le k$ in the integrable level-$k$ sector).

The $r$-matrix $r(z)=k\,\Omega/z$ acts on
$V_{\lambda_1}\otimes V_{\lambda_2}$ via the Casimir:
\[
R_{\lambda_1,\lambda_2}(z)
\;=\;
\exp\Bigl(\frac{k\,\Omega_{\lambda_1,\lambda_2}}{z}\Bigr)
\;\in\;
\operatorname{End}(V_{\lambda_1}\otimes V_{\lambda_2})
[\![z^{-1}]\!].
\]
At $k=0$ this braiding collapses to the identity, as the
classical residue $r(z)=k\,\Omega/z$ vanishes.
For $k=1$ (simplest non-abelian level): two simple objects
$V_0$ (trivial) and $V_1$ (fundamental). Fusion:
$V_1\otimes V_1=V_0$. The $R$-matrix at $\lambda_1=\lambda_2=1$
is a $4\times 4$ matrix with eigenvalue $q=e^{i\pi/3}$.

The KZ connection
$\nabla_{0,n}=d-\frac{1}{k+2}\sum_{i<j}\Omega_{ij}\,
d\log(z_i-z_j)$
is, on the affine Kac--Moody comparison surface, the flat
connection on conformal blocks for evaluation modules; its
monodromy representation is compared by the affine
Drinfeld--Kohno package with the braiding on the reduced
evaluation sector.

At $k=-2$ (critical level): $q=e^{i\pi/(k+2)}$ is undefined
(division by zero), and the evaluation-sector quantum-group
description degenerates. The KZ connection acquires a pole,
so this picture lies outside the chirally Koszul affine locus.
\end{computation}

\begin{computation}[Explicit $R$-matrix for
$\widehat{\mathfrak{sl}}_2$ on $V\otimes V$;
\ClaimStatusProvedHere]
\label{comp:explicit-r-matrix-sl2}
\index{R-matrix!explicit matrix entries!sl2@$\mathfrak{sl}_2$}
Let $V=\mathbb C^2$ (the fundamental representation).
The Casimir acts on $V\otimes V$ as
$\Omega=e\otimes f+f\otimes e+\tfrac12 h\otimes h$,
a $4\times 4$ matrix in the basis $\{v_+\otimes v_+,\,
v_+\otimes v_-,\,v_-\otimes v_+,\,v_-\otimes v_-\}$:
\[
\Omega
\;=\;
\begin{pmatrix}
1/2 & 0 & 0 & 0 \\
0 & -1/2 & 1 & 0 \\
0 & 1 & -1/2 & 0 \\
0 & 0 & 0 & 1/2
\end{pmatrix}.
\]
The $R$-matrix at level~$k$ is
$R(z)=1+k\,\Omega/(z(k{+}2))+O(z^{-2})$. At leading order:
\[
R(z)\big|_{k=1}
\;=\;
\begin{pmatrix}
1+\frac{1}{6z} & 0 & 0 & 0 \\[3pt]
0 & 1-\frac{1}{6z} & \frac{1}{3z} & 0 \\[3pt]
0 & \frac{1}{3z} & 1-\frac{1}{6z} & 0 \\[3pt]
0 & 0 & 0 & 1+\frac{1}{6z}
\end{pmatrix}
+O(z^{-2}).
\]
Eigenvalues of $\Omega$: $+1/2$ (multiplicity~$3$, symmetric
part) and $-3/2$ (multiplicity~$1$, antisymmetric part).
The $R$-matrix decomposes:
$R(z)=(1+k/(2z(k{+}2)))\,P_{\mathrm{sym}}
+(1-3k/(2z(k{+}2)))\,P_{\mathrm{anti}}$,
where $P_{\mathrm{sym}}$ and $P_{\mathrm{anti}}$ are the
projectors onto the symmetric and antisymmetric parts
of $V\otimes V$.

At $z\to 0$: $R(z)\to\infty$ (pole). The residue
$\operatorname{Res}_{z=0}R(z)=k\,\Omega/(k{+}2)$ is the
KZ connection coefficient.
\end{computation}

\subsection{Virasoro: Virasoro modules}
\label{subsec:line-op-virasoro}

For $\cA=\mathrm{Vir}_c$: the chiral Koszul dual is
$\cA^!_{\mathrm{ch}}=\mathrm{Vir}_{26-c}$. The expected
Virasoro realization of the line side models it by modules for
$\mathrm{Vir}_{26-c}$.
(Unlike the affine lineage, the Virasoro does not admit a
separate Yangian reduction; see
Remark~\textup{\ref{rem:yangian-virasoro-nonformality}}.)
The Laplace kernel is
$r^L_c(z)=(\partial T \otimes \mathbf{1})/z+2(T \otimes \mathbf{1})/z^2+c\,(\mathbf{1}\otimes\mathbf{1})/(2z^4)$
(schematic: $\partial T/z+2T/z^2+c/(2z^4)$);
the collision residue is
$r^{\mathrm{coll}}_c(z) = (c/2)/z^3\,\mathbf{1}\otimes\mathbf{1}
+ 2T\otimes\mathbf{1}/z$
(pole orders one lower, as in Volume~I's discussion of the three
related kernels).

\begin{conjecture}[Expected Virasoro line-side model;
\ClaimStatusConjectured]
\label{comp:line-op-virasoro}
\index{Virasoro algebra!line operators}
The expected line-side category is modeled by
$\mathrm{Vir}_{26-c}\text{-mod}^{\mathrm{dg}}$:
the dg category of modules for the dual-central-charge
Virasoro algebra. In this expected model, the simple objects
would be the Verma modules $M_{h'}$ at conformal weights
$h'\in\mathbb C$ for the dual algebra.

The Laplace kernel $r^L_c(z)=\partial T/z+2T/z^2+c/(2z^4)$ has a
fourth-order pole (the collision residue $r^{\mathrm{coll}}_c(z) =
(c/2)/z^3 + 2T/z$ has a cubic pole): this is \emph{not} a standard
Yangian $r$-matrix (which has a simple pole). The higher-order
poles reflect the conformal anomaly: the Virasoro algebra is not a
Lie algebra with an invariant inner product, but a central
extension whose cocycle contributes the anomalous poles.

In this expected model, the genus-$0$ shadow connection gives the
Virasoro conformal Ward connection for $n$-point conformal blocks:
\[
\nabla^{\mathrm{hol}}_{0,n}(\Phi)
\;=\;
\Bigl(
\partial_{z_i}
-\sum_{j\neq i}
\Bigl(\frac{h_j}{(z_i-z_j)^2}
+\frac{\partial_{z_j}}{z_i-z_j}\Bigr)
\Bigr)\Phi
\;=\;0.
\]
On the degenerate-module comparison surface, the corresponding
null-vector constraints then specialize this Ward system to the
level-$2$ BPZ equations; the higher-level BPZ systems would arise from
higher-depth collision residues of~$\Theta_c$.

At $c=26$, the expected Virasoro realization lands on
$\mathrm{Vir}_0$. Here $\kappa=0$, and the shadow
connection is flat at leading order. In this expected model,
the line category is modeled by $\mathrm{Vir}_0\text{-mod}$,
the ``pure gravity'' sector.
\end{conjecture}

\subsubsection{The RTT presentation and mode structure}
\label{subsubsec:virasoro-rtt}

The collision residue $r^{\mathrm{coll}}_c(z) = (c/2)/z^3 + 2T/z$
(Proposition~\ref{prop:field-theory-r}) has a \emph{cubic} pole,
not the simple pole of the affine RTT relation.
The cubic pole forces the RTT framework to carry three mode
strata rather than one: while the affine $r$-matrix
$r(z) = k\,\Omega/z$ has a single residue $k\,\Omega_0$, the
Virasoro collision residue has residues $\Omega_0$, $\Omega_1$,
$\Omega_2$ at $z^{-1}$, $z^{-2}$, $z^{-3}$, with the
full series $r(z) = \sum_{m \ge 0} \Omega_m/z^{m+1}$ continuing
to all orders
(Construction~\ref{constr:thqg-V-vir-r-explicit}).

\begin{construction}[Expected Virasoro RTT relation; \ClaimStatusConjectured]
\label{constr:virasoro-rtt-relation}
\index{Virasoro algebra!RTT relation|textbf}
\index{RTT relation!Virasoro}
In the expected Virasoro realization of the line side, the
quantum $R$-matrix $R(z)$ on the modeled line category is the
monodromy of the ordered bar connection
(Construction~\ref{constr:r-matrix-monodromy}).
Define the transfer matrix
$\mathcal{T}(z) \in
\operatorname{End}(V) \otimes
\mathrm{Vir}_{26-c}[\![z^{-1}]\!]$
for any $\mathrm{Vir}_{26-c}$-module $V$ in this expected model by the generating function
\begin{equation}\label{eq:virasoro-transfer}
\mathcal{T}(z)
\;=\;
\sum_{n \ge 0}
z^{-n-1}\,
\pi_V(L_n),
\end{equation}
where $\pi_V \colon \mathrm{Vir}_{26-c} \to \operatorname{End}(V)$
is the representation map and $\{L_n\}_{n \in \mathbb{Z}}$ are the
Virasoro generators at dual central charge $c' = 26 - c$.

The RTT relation takes the form
\begin{equation}\label{eq:virasoro-rtt}
\boxed{
R_{12}(z{-}w)\,
\mathcal{T}_1(z)\,
\mathcal{T}_2(w)
\;=\;
\mathcal{T}_2(w)\,
\mathcal{T}_1(z)\,
R_{12}(z{-}w),
}
\end{equation}
where the subscripts denote tensor factors and
$R_{12}(z)$ is the spectral $R$-matrix of
Corollary~\textup{\ref{cor:gravity-spectral-r}}.
The classical limit $\hbar \to 0$ (equivalently
$c \to \infty$, the semiclassical gravity limit) gives
\begin{equation}\label{eq:virasoro-rtt-classical}
[\mathcal{T}_1(z),\, \mathcal{T}_2(w)]
\;=\;
\frac{1}{c}\bigl[r_{12}(z{-}w),\,
\mathcal{T}_1(z)\,\mathcal{T}_2(w)\bigr]
\;+\; O(c^{-2}),
\end{equation}
with $r_{12}(z) = (c/2)/z^3 + 2T/z$ the classical
collision residue.
\end{construction}

\begin{remark}[Derivation within the expected model]
The RTT relation~\eqref{eq:virasoro-rtt} is the specialisation
of the general RTT framework
(equation~\eqref{eq:rtt-from-bar}) to $\cA = \mathrm{Vir}_c$.
The transfer matrix is the composition of the $R$-matrix
action with the module representation, and the RTT identity
encodes the consistency of the coproduct
$\Delta_z \colon \mathrm{Vir}_{26-c} \to
\mathrm{Vir}_{26-c} \otimes_{r(z)} \mathrm{Vir}_{26-c}$
(Proposition~\ref{prop:virasoro-twisted-coproduct})
with the Yang--Baxter equation for $R(z)$
(Corollary~\ref{cor:gravity-spectral-r}).
\end{remark}

\begin{computation}[Mode decomposition of the Virasoro RTT
relation; \ClaimStatusProvedHere]
\label{comp:virasoro-rtt-modes}
\index{Virasoro algebra!RTT mode relations}
Expanding~\eqref{eq:virasoro-rtt} in modes by substituting
$R(z) = 1 + r(z) + O(r^2)$
with $r(z) = \sum_{m \ge 0} \Omega_m z^{-m-1}$ and
$\mathcal{T}(z) = \sum_n L_n\,z^{-n-1}$,
the coefficient of $z^{-m-1}\,w^{-n-1}$ at leading
classical order gives
\begin{equation}\label{eq:virasoro-rtt-mode-relation}
[L_m,\, L_n]
\;=\;
(m{-}n)\,L_{m+n}
\;+\;
\frac{c'}{12}(m^3{-}m)\,\delta_{m+n,0},
\end{equation}
with $c' = 26 - c$. This is exactly the
$\mathrm{Vir}_{26-c}$ commutation relation: the RTT
relation does not produce new generators or new relations
beyond the Virasoro algebra itself.

This is the fundamental contrast with the affine case.
For $\widehat{\mathfrak{sl}}_2$, the RTT
relation~\eqref{eq:FRT-components} with $r(z) = k\,\Omega/z$
produces the Yangian $Y(\mathfrak{sl}_2)$, which is a
genuine \emph{deformation} of $U(\mathfrak{sl}_2{[t]})$
with new generators $J^{(1)}_a$ beyond the Lie algebra
generators $J^{(0)}_a$. For Virasoro, the higher poles
$\Omega_m$ with $m \ge 1$ do not produce new generators:
they are \emph{determined} by the Virasoro algebra
structure through the Casimir component
formula $\Omega_m = \sum_n \binom{n+m-1}{m}\,L_{-n-m}
\otimes L_n$.

The obstruction to a separate ``Yangian layer'' is the
non-formality of $\mathrm{Vir}_c$:
$m_k \ne 0$ for all $k \ge 3$
(Remark~\ref{rem:yangian-virasoro-nonformality}). For
formal algebras (affine KM), the Yangian is a strict
deformation of $U(\mathfrak{g}{[t]})$ and the modes separate
into level-$0$ (Lie algebra) and level-$\ge 1$ (Yangian).
For non-formal algebras (Virasoro), the entire $A_\infty$
tower is encoded in the algebra itself: there is no
separate ``Yangian direction'' because the higher
$A_\infty$ operations \emph{are} the Virasoro structure.
\end{computation}

\begin{remark}[The triple-pole PBW structure]
\label{rem:virasoro-triple-pole-pbw}
\index{Virasoro algebra!PBW structure of line operators}
The PBW basis of $\mathrm{Vir}_{26-c}$ is
$\{L_{-n_1} L_{-n_2} \cdots L_{-n_k}\,|0\rangle
\mid n_1 \ge n_2 \ge \cdots \ge n_k \ge 2\}$
(with the Poincar\'e--Birkhoff--Witt ordering from the
triangular decomposition). In the transfer matrix language:
the modes $\mathcal{T}_{(m)}$ for $m = 0, 1, 2$
encode the three leading residues
$\Omega_0 = \sum_n L_{-n} \otimes L_n$ (Casimir),
$\Omega_1 = \sum_n n\, L_{-n-1} \otimes L_n$ (translation),
$\Omega_2 = \sum_n \tfrac{n(n+1)}{2}\,L_{-n-2} \otimes L_n$
(central extension).
On the vacuum:
\begin{alignat*}{2}
\Omega_0\,|0\rangle \otimes |0\rangle
&\;=\;
(L_{-2} \otimes L_2 + \cdots)\,|0\rangle \otimes |0\rangle
&&\;=\; 0 + (\text{descendant terms}),
\\
\Omega_2\,|0\rangle \otimes |0\rangle
&\;=\;
\tfrac{c'}{2}\,|0\rangle \otimes |0\rangle
&&\quad (\text{central extension}).
\end{alignat*}
The mode $\Omega_1$ vanishes on the vacuum
(no $z^{-2}$ pole in the collision residue).
\end{remark}

\subsubsection{Evaluation modules and fusion}
\label{subsubsec:virasoro-eval-fusion}

\begin{construction}[Evaluation modules for the Virasoro
line category; \ClaimStatusProvedHere]
\label{constr:virasoro-eval-modules}
\index{Virasoro algebra!evaluation modules|textbf}
\index{evaluation modules!Virasoro}
For each conformal weight $h \in \mathbb{C}$ and
spectral point $z_0 \in \mathbb{C}$, define the
\emph{evaluation module}
$\operatorname{ev}_{z_0}(M_h)$ to be the Verma module
$M(h, c') = M(h, 26{-}c)$ of $\mathrm{Vir}_{26-c}$,
with the transfer matrix evaluated at $z_0$:
\begin{equation}\label{eq:virasoro-eval}
\pi_{z_0} \colon \mathrm{Vir}_{26-c}
\;\to\;
\operatorname{End}(M_h),
\qquad
L_n \mapsto L_n\big|_{M_h},
\end{equation}
where the spectral parameter $z_0$ enters through the
twisted coproduct
$\Delta_{z_0}(L_n) = \sum_{k=0}^n \binom{n}{k}\,z_0^k\,
L_{n-k} \otimes 1 + 1 \otimes L_n$
(Proposition~\ref{prop:virasoro-twisted-coproduct}).

In this expected Virasoro model, the simple objects of the
modeled line category in the evaluation sector are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Irreducible highest-weight modules}
 $L(h,c')$ for $h \in \mathbb{C}$ generic
 (the Verma module $M(h,c')$ is irreducible
 for generic $h$).
\item \emph{Degenerate modules} $L(h_{r,s},c')$ at
 Kac table values $h_{r,s} = ((rb'+sb'^{-1})^2 -
 (b'+b'^{-1})^2)/4$ with
 $c' = 1 + 6(b'+b'^{-1})^2$ and
 $b' = b'^{-1}(c')$.
 The null vector generates a submodule; the quotient
 is the irreducible module.
\item The \emph{vacuum module} $L(0, c')$: the trivial
 line operator (no defect).
\end{enumerate}
\end{construction}

\begin{conjecture}[Expected fusion of Virasoro evaluation modules;
\ClaimStatusConjectured]
\label{comp:virasoro-eval-fusion}
\index{Virasoro algebra!fusion of evaluation modules}
\index{fusion rules!Virasoro evaluation modules}
In the expected Virasoro realization, the tensor product of
two evaluation modules at spectral
points $z_1, z_2$ is
\begin{equation}\label{eq:virasoro-fusion}
\operatorname{ev}_{z_1}(M_{h_1})
\;\otimes_{R(z_{12})}\;
\operatorname{ev}_{z_2}(M_{h_2})
\;=\;
\int_{\mathcal{C}} M_{h}\,
d\mu_{h_1,h_2}(h),
\end{equation}
where $z_{12} = z_1 - z_2$, the integral is over the
Plancherel contour $\mathcal{C} = Q'/2 + i\mathbb{R}_+$
with $Q' = b' + b'^{-1}$ and $c' = 1 + 6Q'^2$,
and $d\mu_{h_1,h_2}$ is the Virasoro Plancherel measure
determined by the OPE coefficients.

The corresponding $R$-matrix braiding on the tensor product is
(Corollary~\ref{cor:gravity-spectral-r}):
\begin{equation}\label{eq:virasoro-braiding-eval}
R(z_{12})\big|_{M_{h_1} \otimes M_{h_2}}
\;=\;
\bigoplus_{h}
e^{2\pi i(h - h_1 - h_2)}\,
\mathrm{id}_{M_h},
\end{equation}
diagonal in the fusion-channel basis with eigenvalues
that are Aharonov--Bohm phases. This is the expected
Virasoro counterpart of~\eqref{eq:r-matrix-diagonal},
compatible with the abstract bar-cobar braiding from the
gravity chapter and with
Conjecture~\ref{conj:gravity-fusion-kernel}, which identifies
that braiding with the Ponsot--Teschner fusion kernel.

\emph{Rational central charge (minimal models).}\enspace
For $c' = 1 - 6(p'-q')^2/(p'q')$ with
$\gcd(p',q') = 1$, the tensor product is a finite direct
sum: $M_{h_1} \otimes M_{h_2} = \bigoplus_{h \in
\mathrm{Kac}(p',q')} N^{h}_{h_1 h_2}\, L(h, c')$.
The expected line category truncates to a finite ribbon
category, namely the modular tensor category of the
$(p',q')$ minimal model at central charge $c'$.

\emph{Self-dual point $c = 13$.}\enspace
At $c = 13$: $c' = 13$, and
$\mathrm{Vir}_{13}^! = \mathrm{Vir}_{13}$
(Proposition~\ref{prop:gravity-koszul-dual}).
In this expected model, the line category modeled by
$\mathrm{Vir}_{13}\text{-mod}$ is self-dual under
the Koszul involution: the braiding and its
opposite coincide, reflecting the fact that the
complementarity potential is symmetric at $c = 13$.
\end{conjecture}

\subsubsection{Why the Virasoro has no separate Yangian}
\label{subsubsec:virasoro-no-separate-yangian}

\begin{proposition}[Virasoro: the line algebra is not
a deformation of $U(\mathrm{Witt}{[t]})$;
\ClaimStatusProvedHere]
\label{prop:virasoro-no-yangian-deformation}
\index{Virasoro algebra!absence of Yangian deformation|textbf}
\index{Yangian!does not exist for Virasoro}
The open-colour Koszul dual
$\cA^!_{\mathrm{line}} = \mathrm{Vir}_{26-c}$ is
\emph{not} a filtered deformation of
$U(\mathrm{Witt}{[t]})$ in the sense of a standard Yangian.
The obstruction is twofold:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Central extension.}\;
 The Virasoro algebra is a non-trivial central extension
 of the Witt algebra $\mathrm{Witt} = \mathrm{Der}(\mathbb{C}[z,z^{-1}])$
 by $\mathbb{C}$. The extension class
 $[\omega] \in H^2(\mathrm{Witt}, \mathbb{C})$ is the
 Gel'fand--Fuchs cocycle
 $\omega(L_m, L_n) = \tfrac{1}{12}(m^3 - m)\,\delta_{m+n,0}$.
 For a standard Yangian $Y(\mathfrak{g})$,
 the classical limit is $U(\mathfrak{g}{[t]})$: the loop
 algebra of a \emph{finite-dimensional} Lie algebra.
 The Virasoro algebra is infinite-dimensional, and the
 Gel'fand--Fuchs cocycle has no analogue for
 finite-dimensional Lie algebras.
\item \emph{Non-formality.}\;
 The $A_\infty$ structure on $\mathrm{Vir}_c$ has
 $m_k \ne 0$ for all $k \ge 3$
 (Remark~\ref{rem:yangian-virasoro-nonformality}). For
 a Yangian $Y(\mathfrak{g})$, the associated graded
 $U(\mathfrak{g}{[t]})$ is formal ($m_k = 0$ for $k \ge 3$)
 and the deformation lives in $\HH^2(U(\mathfrak{g}{[t]}))$
 (Proposition~\ref{prop:yangian-deformation-obstruction}).
 The non-vanishing of the Virasoro higher $A_\infty$
 operations means the deformation problem does not
 split into a Yangian direction and a Lie-algebra
 direction.
\end{enumerate}
The correct statement is: $\mathrm{Vir}_{26-c}$ is
simultaneously the boundary algebra, the Koszul dual
algebra, and the line-side algebra. There is no
separate ``Yangian layer.''
The infinite tower of higher $A_\infty$ operations
$\{m_k\}_{k \ge 3}$ is the Virasoro algebra structure
itself, not a deformation of a simpler object.
\end{proposition}

\begin{proof}
Part~(a): the space of central extensions
$H^2(\mathrm{Witt}, \mathbb{C}) = \mathbb{C}$ is
one-dimensional, generated by the Gel'fand--Fuchs cocycle.
A Yangian $Y(\mathfrak{g})$ is a deformation of
$U(\mathfrak{g}{[t]})$ in the Harrison cohomology class
$\Har^2(U(\mathfrak{g}{[t]}))$
(Proposition~\ref{prop:yangian-deformation-obstruction}).
For $\mathfrak{g}$ infinite-dimensional, the Harrison
cohomology of $U(\mathfrak{g}{[t]})$ is not controlled by
the K\"unneth formula of
Proposition~\ref{prop:HH-Ugt-decomposition}, and the
leading vanishing lemma
(Lemma~\ref{lem:harrison-leading-vanishing}) does not
apply. In particular, the Virasoro Harrison obstruction
group $\Har^3(U(\mathrm{Witt}{[t]}))$ need not vanish.

Part~(b): the non-formality $m_k \ne 0$ for $k \ge 3$
is proved in the gravity chapter
(Section~\ref{subsec:gravity-ainf}): the quartic OPE pole
forces a non-zero associator $A_3 \ne 0$, which forces
$m_3 \ne 0$, and the quartic contact invariant
$\mathfrak{Q} = 10/[c(5c+22)] \ne 0$ (for generic $c$)
forces $m_4 \ne 0$. The non-truncation of the shadow
tower (Proposition~\ref{prop:vir-truncation}) then gives
$m_k \ne 0$ for all $k \ge 3$. For formal algebras, the
Yangian deformation class lives in a separate cohomological
direction from the Lie bracket; for non-formal algebras,
these directions are entangled.
\end{proof}

\subsubsection{Comparison with deformed Virasoro and related structures}
\label{subsubsec:virasoro-comparison}

\begin{remark}[Comparison with the Shiraishi--Kubo--Awata--Odake
algebra; \ClaimStatusConjectured]
\label{rem:virasoro-skao-comparison}
\index{deformed Virasoro algebra|textbf}
\index{Shiraishi--Kubo--Awata--Odake algebra}
The deformed Virasoro algebra $\mathrm{Vir}_{q,t}$ of
Shiraishi--Kubo--Awata--Odake is a
two-parameter deformation of the Virasoro algebra, with
generators $\{T_n\}_{n \in \mathbb{Z}}$ and
relations determined by a generating function
\[
f(z)
\;=\;
\exp\!\Biggl(
\sum_{n \ge 1} \frac{(1-q^n)(1-t^{-n})}{n}\, z^n
\Biggr).
\]
Three distinct objects must be distinguished:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\mathrm{Vir}_{26-c}$ (the chiral Koszul dual):
 a vertex algebra at central charge $26-c$, furnishing
 the expected Virasoro model of the line side in
 Conjecture~\textup{\ref{comp:line-op-virasoro}}.
\item $\mathrm{Vir}_{q,t}$ (the SKAO deformation):
 a two-parameter algebra with a single deformation
 parameter $\beta = -\epsilon_1/\epsilon_2$ in the
 Nekrasov notation, where $q = e^{2\pi i \epsilon_1}$,
 $t = e^{-2\pi i \epsilon_2}$. This algebra governs
 the instanton counting in 5d $\mathcal{N}=1$ gauge
 theories and Nekrasov partition functions.
\item $Y(\mathfrak{sl}_2)$ (the Yangian):
 the line-side algebra for $\widehat{\mathfrak{sl}}_2$,
 which produces $\mathrm{Vir}_c$ via DS reduction
 at the cohomology level
 (Remark~\ref{rem:gravity-yangian-chain-vs-cohomology}).
\end{enumerate}

The expected relationship is: the SKAO algebra
$\mathrm{Vir}_{q,t}$ arises as the \emph{trigonometric
degeneration} of the quantum toroidal algebra
$U_{q,t}(\widehat{\widehat{\mathfrak{gl}}}_1)$, while
$\mathrm{Vir}_{26-c}$ arises as the \emph{rational}
limit of the same structure via DS reduction. The two
are not isomorphic: $\mathrm{Vir}_{q,t}$ is a
$q$-deformation (multiplicative spectral parameter),
while $\mathrm{Vir}_{26-c}$ has an additive spectral
parameter from the Laplace transform.

At the level of representation categories:
$\mathrm{Vir}_{q,t}\text{-mod}$ (with $q = e^{2\pi i b^2}$)
and the expected Virasoro line-side model via
$\mathrm{Vir}_{26-c}\text{-mod}$ (with
$c = 1 + 6(b+b^{-1})^2$) are expected to be equivalent as
braided tensor categories on the integrable locus, via a
$q$-deformed version of the Kazhdan--Lusztig equivalence.
This is a manifestation of the 3d mirror symmetry
relating rational and trigonometric degenerations of the
same underlying elliptic structure. Verification of this
equivalence is not part of the live manuscript surface.
\end{remark}

\begin{remark}[Relationship to $\mathcal{W}_{1+\infty}$;
\ClaimStatusConjectured]
\label{rem:virasoro-w-infinity}
\index{W1infinity@$\mathcal{W}_{1+\infty}$!Virasoro line operators}
The $\mathcal{W}_{1+\infty}$ algebra at $c = 1$ is the
universal enveloping algebra of the Lie algebra of
differential operators on the circle. It contains the
Virasoro algebra as the subalgebra generated by
second-order differential operators.

In the line-side framework: if $\cA$ is a
$\mathcal{W}_{1+\infty}$-algebra, its line category
should be modeled by the Koszul dual
$\cA^!_{\mathrm{line}}$, which for
$\mathcal{W}_{1+\infty}$ is expected to be a
``$\mathcal{W}_{1+\infty}$-Yangian'' controlling
the full tower of higher-spin line operators. The
expected Virasoro line-side model via
$\mathrm{Vir}_{26-c}\text{-mod}$ is the
spin-$2$ truncation of this conjectural larger
structure.

The celestial holography programme
(Strominger et al.)
identifies $\mathcal{W}_{1+\infty}$ as the
asymptotic symmetry algebra of self-dual gravity in
$4$d; the restriction to 3d gravity gives the
Virasoro subalgebra. In the HT framework, this
truncation corresponds to the restriction from the
full Swiss-cheese algebra of the 4d theory to the
3d HT slice $\mathbb{C}_z \times \mathbb{R}_t$.
\end{remark}

\subsubsection{Toward a geometric realization}
\label{subsubsec:virasoro-geometric}

\begin{remark}[The Virasoro Steinberg problem;
\ClaimStatusConjectured]
\label{rem:virasoro-steinberg}
\index{Steinberg variety!Virasoro|textbf}
\index{Virasoro algebra!geometric realization}
For a finite-dimensional simple Lie algebra $\mathfrak{g}$,
the Yangian $Y(\mathfrak{g})$ acts by convolution on
the equivariant $K$-theory of the Steinberg variety
$Z = \widetilde{\mathcal{N}} \times_{\mathcal{N}}
\widetilde{\mathcal{N}}$, where
$\widetilde{\mathcal{N}} \to \mathcal{N}$ is the
Springer resolution of the nilpotent cone
(Remark~\ref{rem:steinberg-filtered-formality}).
The Chriss--Ginzburg convolution produces the Hecke
algebra as the endomorphism algebra of the convolution
product, and the Yangian is the spectral deformation
of the Hecke action.

For the Virasoro algebra, the analogous geometric
programme requires an infinite-dimensional replacement
for the Springer resolution. Three candidates exist:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Feigin--Frenkel opers.}\;
 The space of $\mathrm{SL}(2)$-opers on a curve
 $\mathcal{O}p_{\mathrm{SL}(2)}(\Sigma)$ is a
 torsor for $H^0(\Sigma, \omega_\Sigma^{\otimes 2})$
 (projective connections). The ``Virasoro nilpotent
 cone'' would be the space of irregular opers with
 prescribed singular behavior, and the Springer
 fibre would be the space of Stokes data. DS
 reduction from $\widehat{\mathfrak{sl}}_2$ to
 $\mathrm{Vir}$ should then intertwine the
 Springer resolution of $\mathfrak{sl}_2$ with
 the oper resolution, transporting the Steinberg
 convolution from $Y(\mathfrak{sl}_2)$ to
 $\mathrm{Vir}_{26-c}$.

\item \emph{Diff$(S^1)$ and coadjoint orbits.}\;
 The Virasoro algebra is the central extension of the
 Lie algebra of $\operatorname{Diff}(S^1)$. The
 coadjoint orbits of $\operatorname{Diff}(S^1)$
 (the Kirillov--Kostant classification) provide a
 natural stratification: generic orbits (labeled by
 a single invariant, the Schwarzian derivative) and
 degenerate orbits (the stabilizer jumps). The
 ``Virasoro Steinberg variety'' would be the
 self-intersection of the universal orbit inside
 the coadjoint representation
 $\mathrm{Vir}^* \simeq
 \{c/(2z^4) + u(z)/(z^2)\,dz^2\}$,
 where $u(z)$ is a projective connection.

\item \emph{DS reduction of the affine Steinberg.}\;
 The Steinberg variety
 $Z_{\mathfrak{sl}_2} = \widetilde{\mathcal{N}} \times_{\mathcal{N}}
 \widetilde{\mathcal{N}}$ for $\mathfrak{sl}_2$ carries a
 $\widehat{\mathfrak{sl}}_2$-action by Kazhdan--Lusztig.
 DS reduction $V_k(\mathfrak{sl}_2) \twoheadrightarrow
 \mathrm{Vir}_c$ induces a BRST functor on modules:
 $H^0_{\mathrm{DS}}(M) = H^0(M, Q_{\mathrm{DS}})$.
 This functor should transport the Steinberg convolution
 from $K^{G \times \mathbb{G}_m}(Z_{\mathfrak{sl}_2})$
 to a ``reduced Steinberg'' convolution algebra acting on
 the expected Virasoro line-side model via
 $\mathrm{Vir}_{26-c}\text{-mod}$. The key difficulty is
 that BRST reduction does not commute with convolution in
 general, and the correction terms are controlled by the
 non-formality of the Virasoro $A_\infty$ structure.
\end{enumerate}
Route~(iii) is the most promising: it uses the proved
DS intertwining theorem
(Theorem~\ref*{V1-thm:ds-koszul-intertwine}) and the proved
affine Steinberg presentation
(Theorem~\ref{thm:steinberg-presentation}), reducing the
Virasoro geometric realization to a BRST-compatibility
question. But none of these routes is completed in either
volume.
\end{remark}

\subsection{$\mathcal W_3$: frontier Yangian package}
\label{subsec:line-op-w3}

\begin{remark}[Expected line-operator package for $\mathcal W_3$;
\ClaimStatusConjectured]
\label{comp:line-op-w3}
\index{W3@$\mathcal W_3$!line operators}
The live manuscript expects the $\mathcal W_3$ line category to be
governed by a dg-shifted $\mathcal W_3$-Yangian package
$\cC_c^{W_3}$, with sectors labeled by conformal weight and
$W$-charge. The spectral kernel should have poles at $z=0$ of
orders $1$, $3$, and $5$, reflecting the $JJ$, $TT$, and $WW$
OPE channels.

The genus-$0$ shadow connection is expected to transport the
corresponding $\mathcal W_3$ derived coinvariant / protected-state
package, specializing on the conjectural $\mathcal W_3$
comparison surface to coupled partial differential equations for
$n$-point $\mathcal W_3$ conformal blocks involving both
$L_n$ and $W_n$ generators.

The two-dimensional genus-$1$ Hessian
$H^{(1)}=\mathrm{diag}(\kappa_c,\,\kappa_c+48/(5c+22))$
computed in Volume~I
produces two modular corrections to the $r$-matrix at
genus~$1$: $r_{1,T}(z)$ from the $T$-direction and
$r_{1,W}(z)$ from the $W$-direction. The spectral
discriminant $\Delta_{\mathcal W_3}(x)=
(1-\kappa_c x)(1-(\kappa_c+48/(5c+22))x)$
governs the convergence of the modular extension
$R^{\mathrm{mod}}(z;\hbar)
=r(z)+\hbar^2(r_{1,T}+r_{1,W})+\cdots$.

This package is not part of the unconditional affine surface.
Remark~\ref{rem:affine-scope} records that beyond the affine
lineage the transferred operations $m_k^{\mathrm{SC}}$ need not
vanish, so the one-loop collapse used in the affine proof breaks
down. Accordingly the identification of the reduced monodromy
with a spectral $\mathcal W_3$-Yangian $R$-matrix remains
conjectural on the live manuscript surface.
\end{remark}

\subsection{$\beta\gamma$: symplectic lines}
\label{subsec:line-op-betagamma}

\begin{computation}[Line-operator category for $\beta\gamma$;
\ClaimStatusProvedHere]
\label{comp:line-op-betagamma}
\index{beta-gamma@$\beta\gamma$!line operators}
$\cC_{\mathrm{line}}(\beta\gamma)
\simeq\beta\gamma_{1-\lambda}\text{-mod}$:
modules for the weight-$(1{-}\lambda)$ $\beta\gamma$ system.
The $r$-matrix is the canonical symplectic kernel
$r(z)=(\beta\otimes\gamma+\gamma\otimes\beta)/z$.

The vortex lines $\{V_N\}_{N\in\mathbb Z}$ are the
irreducible line operators: $V_N$ carries $N$ units of
vortex charge. Fusion: $V_{N_1}\otimes V_{N_2}=V_{N_1+N_2}$.
The flip $\mathrm{Flip}_\beta$ exchanges $V_{N>0}$ and
$V_{N<0}$ (Example~\ref{ex:free-chiral-flip}).

$\kappa(\beta\gamma)=1$ (at standard weight $\lambda=1$): the genus tower
is positive-definite. The modular extension of the spectral kernel is
$R^{\mathrm{mod}}(z;\hbar)=r(z)+\hbar^2 r_1(z)+\cdots$
with $r_1(z)$ proportional to $\kappa=1$.
\end{computation}

\subsection{Comparison with Costello--Dimofte--Gaiotto}
\label{subsec:cdg-comparison}

\begin{remark}[CDG line operators = ordered bar cohomology modules]
\label{rem:cdg-comparison}
\index{Costello--Dimofte--Gaiotto!line operator comparison}
The perturbative line operators of CDG~\cite{CDG20} are
constructed from the worldline quantum mechanics of fields
on the half-line $\mathbb R_+$ at a fixed point $z_0\in\mathbb C$.
Theorem~\ref{thm:lines_as_modules} identifies the resulting
module category with $\cA^!_{\mathrm{line}}\text{-mod}$ via the
Swiss-cheese bar-cobar adjunction. The open-colour Koszul dual
$\cA^!_{\mathrm{line}}$ is the
ordered bar cohomology
$H^*({\Barch}^{\mathrm{ord}}(\cA))^\vee$
(Construction~\ref{constr:dg-shifted-yangian-from-bar}).

The CDG $R$-matrix governing line-operator OPE is the
monodromy of the ordered bar connection
(Construction~\ref{constr:r-matrix-monodromy}):
the physical process of one line operator circling another
in the holomorphic plane is the loop $\gamma$ in
$\mathrm{Conf}_2^{\mathrm{ord}}(\mathbb C)$ whose monodromy
is~$R(z)$. The Yang--Baxter equation
(Proposition~\ref{prop:ybe-from-d-squared}) is the
consistency of the perturbative expansion for three
simultaneously present lines.

For $\widehat{\mathfrak{sl}}_2$: the CDG line operators are
Wilson lines in 3d Chern--Simons, and $R(z)=1+k\,\Omega/z+\cdots$
is the perturbative expansion of the Chern--Simons $R$-matrix.
For Virasoro: the CDG lines are gravitational defects, and
the Laplace kernel $r^L_c(z)=\partial T/z+2T/z^2+c/(2z^4)$ has a
fourth-order pole from the conformal anomaly (the collision residue
$r^{\mathrm{coll}}_c(z) = (c/2)/z^3 + 2T/z$ has a cubic pole).
\end{remark}

\subsection{The DNP identification: meromorphic tensor product
from the ordered bar complex}
\label{subsec:dnp-identification}

\begin{theorem}[DNP line-operator package = bar-cobar twisting package;
\ClaimStatusProvedHere]
\label{thm:dnp-bar-cobar-identification}
\index{Dimofte--Niu--Py!bar-cobar identification|textbf}
\index{meromorphic tensor product!ordered bar coproduct|textbf}
Let\/ $\cA$ be a chirally Koszul logarithmic $\SCchtop$-algebra
with open-colour Koszul dual\/ $\cA^!_{\mathrm{line}}$
\textup{(}Theorem~\textup{\ref{thm:lines_as_modules})}.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(Monoidal identification.)}
 Under the equivalence\/
 $\Phi\colon \cC_{\mathrm{line}} \xrightarrow{\;\sim\;}
 \cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$,
 the meromorphic tensor product\/ $\ell_1\otimes_z\ell_2$
 corresponds to the $R$-twisted tensor product
 $V_{\ell_1}\otimes_{R(z)}V_{\ell_2}$
 via the $R$-twisted coproduct $\Delta_z$ of\/
 Theorem~\textup{\ref{thm:yangian-recognition}}.
 The functor $\Phi$ is monoidal.
\item \textup{(Maurer--Cartan identification.)}
 The DNP $A_\infty$ Yang--Baxter MC element
 $r(z)\in\cA^!\otimes\cA^!$
 of\/ \textup{\cite{DNP25}} is the genus-zero binary collision
 residue of\/ $\Theta_\cA$:
 $r(z) = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$,
 and the MC equation $dr + r\star r = 0$ is the bar-cobar
 adjunction equation $\partial\tau + \tau\cup\tau = 0$.
\item \textup{(Non-renormalization = Koszulness.)}
 The one-loop exactness of line-operator OPE
 \textup{(\cite[Thm.\,4.1]{DNP25})} corresponds to
 $E_2$-collapse of the bar spectral sequence.
 The higher $A_\infty$ operations\/ $m_k$ on\/
 $\cA^!_{\mathrm{line}}$ for $k\geq 3$ are the collision
 residues $\operatorname{Res}^{\mathrm{coll}}_{0,k}(\Theta_\cA)$;
 they vanish on the chirally Koszul locus.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i): the functor $\Phi$ sends $\ell$ to its state space $V_\ell$
\textup{(}Theorem~\textup{\ref{thm:lines_as_modules}}, Step~4\textup{)}.
The two-line OPE on the physical side IS the $R$-twisted tensor product
on the algebraic side, both computed from the FM-configuration-space
integral over $\FM_2(\bC)\times E_1(2)$.

Part~(ii): Theorem~\textup{\ref{V1-thm:collision-residue-twisting}} from
Vol~I identifies the collision residue with the twisting morphism
$\pi_\cA$; in Koszul-dual coordinates this is $r_\cA(z)$. The
MC equation is equivalent to $d^2_{\barB}=0$.

Part~(iii): $E_2$-collapse concentrates $H^{p,q}(\barB(\cA))$ in $q=0$,
so the bar cohomology algebra $\cA^!_{\mathrm{line}}$ is formal: all
$A_\infty$ operations $m_k$ for $k\geq 3$ vanish. In DNP's framework,
tree-level $r$-matrix determines the full perturbative answer.
\end{proof}

\begin{remark}[DS reduction on line categories;
\ClaimStatusConjectured]
\label{comp:ds-on-line-categories}
\index{Drinfeld--Sokolov reduction!line categories}
Drinfeld--Sokolov reduction is expected to compare affine line
data with $\mathcal W_N$ line data by BRST cohomology. On the
affine side, Corollary~\ref{cor:affine-line-category} identifies
only the reduced evaluation sector with
$\operatorname{Rep}_q(\fg)$. Beyond that sector, and in
particular after DS reduction, Remark~\ref{rem:affine-scope}
shows that the transferred higher operations need not vanish, so
the same one-loop collapse used in the affine monodromy proof no
longer applies.

Accordingly a full BRST functor on line categories, and the
corresponding fusion-rule identifications for $\mathcal W_N$,
remain frontier on the live manuscript surface.
\end{remark}

\subsection{Fusion rules from the bar complex}
\label{subsec:fusion-rules}

\begin{construction}[Fusion as tensor product of $\cA^!_{\mathrm{line}}$-modules;
\ClaimStatusProvedHere]
\label{constr:fusion-from-bar}
\index{fusion rules!from bar complex|textbf}
The tensor product $\ell_1\otimes\ell_2$ of line operators
(placing two lines at $z_1,z_2\in\mathbb C$) corresponds to
the tensor product $V_{\ell_1}\otimes V_{\ell_2}$ of
$\cA^!_{\mathrm{line}}$-modules. The
$\cA^!_{\mathrm{line}}$-action on the tensor product
is the coproduct
$\Delta\colon\cA^!_{\mathrm{line}}\to
\cA^!_{\mathrm{line}}\otimes\cA^!_{\mathrm{line}}$
twisted by the $R$-matrix:
\[
\Delta_z(x)\cdot(v_1\otimes v_2)
\;=\;
R(z_1{-}z_2)\cdot
\bigl(\Delta(x)\cdot(v_1\otimes v_2)\bigr).
\]
The fusion coefficients $N^{\ell_3}_{\ell_1\ell_2}$ are
\[
N^{\ell_3}_{\ell_1\ell_2}
\;=\;
\dim\operatorname{Hom}_{\cA^!_{\mathrm{line}}}(V_{\ell_3},\,
V_{\ell_1}\otimes V_{\ell_2}).
\]
\end{construction}

\begin{computation}[Fusion rules for standard families;
\ClaimStatusProvedHere]
\label{comp:fusion-standard}
\index{fusion rules!standard families}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lll}
\textbf{Family} & \textbf{Simple objects}
 & \textbf{Fusion} \\
\hline
$\cH_k$ & $\cF_q$ ($q\in\mathbb Z$)
 & $\cF_{q_1}\otimes\cF_{q_2}=\cF_{q_1+q_2}$ \\[3pt]
$\widehat{\mathfrak{sl}}_2{}_{k=1}$
 & $V_0,\,V_1$ (evaluation sector)
 & $V_1\otimes V_1=V_0$ \\[3pt]
$\widehat{\mathfrak{sl}}_2{}_{k=2}$
 & $V_0,\,V_1,\,V_2$ (evaluation sector)
 & $V_1\otimes V_1=V_0\oplus V_2$,\;
 $V_1\otimes V_2=V_1$ \\[3pt]
$\beta\gamma$
 & $V_N$ ($N\in\mathbb Z$)
 & $V_{N_1}\otimes V_{N_2}=V_{N_1+N_2}$ \\[3pt]
$V_{A_2}$
 & $L_0,\,L_1,\,L_2$ ($A_2^*/A_2\cong\mathbb Z/3$)
 & $L_i\otimes L_j=L_{i+j\bmod 3}$
\end{tabular}
\end{center}
For $\widehat{\mathfrak{sl}}_2$ at level~$k$: the fusion ring
is the Verlinde ring $\operatorname{Ver}_k(\mathfrak{sl}_2)$,
with $N^{\ell_3}_{\ell_1\ell_2}$ given by the
Verlinde formula
$N^\lambda_{\mu\nu}
=\sum_\sigma\frac{S_{\mu\sigma}S_{\nu\sigma}
\overline{S_{\lambda\sigma}}}{S_{0\sigma}}$
where $S$ is the modular $S$-matrix.
At $k=1$: $S=\frac{1}{\sqrt2}
\bigl(\begin{smallmatrix}1&1\\1&-1\end{smallmatrix}\bigr)$,
giving $N^0_{11}=1$ (the only nontrivial fusion coefficient).
\end{computation}

\section{Spectral-parameter and Yangian-type conventions}
\label{sec:line-operators-conventions}

\subsection{Spectral $R$-matrix: holomorphic vs topological dichotomy}
\label{subsec:line-operators-hol-top-dichotomy}

\begin{remark}[The two faces of the $R$-matrix; \ClaimStatusProvedHere]
\label{rem:line-operators-hol-top-dichotomy}
A line operator on the $3$d HT slab has two natural exchange data,
which must not be conflated:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the \emph{holomorphic} (chiral) braiding
$R^{\mathrm{hol}}(z) \in (\cA^!_{\mathrm{line}})^{\otimes 2}((z))$,
where $z$ is the spectral parameter measuring the holomorphic
displacement of the two line operators along the curve $X\subset
X\times\R$; this is the open-colour shadow of the
$\mathsf{SC}^{\mathrm{ch,top}}$-bar coproduct and lives in the closed
colour of $\mathsf{SC}^{\mathrm{ch,top}}$;
\item the \emph{topological} ordering swap
$\sigma^{\mathrm{top}} \in \Sigma_2$ acting on
$\mathrm{Mod}(\cA^!_{\mathrm{line}})^{\otimes 2}$ by exchanging the
two line operators along the topological direction $\R$; this is
the open-colour braided structure on the line category, lifted from
the deconcatenation coproduct on the bar coalgebra.
\end{enumerate}
At a generic level (non-critical, $\Psi$ not a positive rational),
$R^{\mathrm{hol}}(z)$ becomes regular at $z\to 0$ and reduces to the
topological swap $\sigma^{\mathrm{top}}$ up to overall scalar; this
is the chain-level $E_2$-coherence of the line category. At the
critical level $k=-h^\vee$, $R^{\mathrm{hol}}(z)$ has an essential
singularity at $z\to 0$ (Sugawara collapse), and the holomorphic
and topological data become genuinely independent.
\end{remark}

\begin{convention}[Level-prefix discipline for line-operator spectral
$R$-matrices; \ClaimStatusProvedElsewhere]
\label{conv:line-operators-rmatrix-level-prefix}
Every line-operator spectral $R$-matrix in this chapter carries an
explicit level prefix and is checked at $k=0$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Affine Kac--Moody at level $k$, trace-form: $r(z) = k\,\Omega/z$;
$k=0$ gives $r(z)=0$ (abelian limit, line operators commute).
\item Affine Kac--Moody, KZ normalisation: $r(z) = \Omega/((k+h^\vee)z)$;
$k=0$ gives $\Omega/(h^\vee z)\ne 0$ for non-abelian $\fg$ (Lie
bracket persists in line-operator OPE).
\item Critical level $k=-h^\vee$: KZ normalisation diverges; trace-form
gives $r(z) = -h^\vee \Omega/z$, finite. The Sugawara construction
collapses, and line operators carry the Feigin--Frenkel-centre
shadow.
\item Heisenberg, $r^{\mathrm{Heis}}(z) = k/z$; abelian, single-pole.
\item Virasoro, $r^{\mathrm{Vir}}(z) = (c/2)/z^3 + 2T/z$; cubic+simple
pole structure (the gravitational-Yangian seed).
\end{enumerate}
Every $\Omega/z$ appearance in this chapter and across Volumes
I--III carries its level prefix.
\end{convention}

\subsection{Four Yangian types: disambiguation for line operators}
\label{subsec:line-operators-yangian-types}

\begin{convention}[This chapter's line-side Yangian is
$Y(\fg)^{\mathrm{ch}}$; \ClaimStatusProvedElsewhere]
\label{conv:line-operators-yangian-types}
At least four Yangian types appear in the programme; conflating them
is a type error. The following pins which Yangian governs line
operators in this volume:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item Classical $Y_\hbar(\fg)$: $E_1$-topological algebra living on
$\R$; the original Drinfeld Yangian, RTT presentation; spectral
parameter $u\in \mathbb{C}$ is a formal variable encoding evaluation
modules.
\item dg-shifted $Y^{\mathrm{dg}}_\hbar(\fg)$: a complete filtered
$A_\infty$-algebra at a point or formal disk
(\S\ref{chap:dg-shifted-factorization}), used to write the
spectral cohomology with explicit $A_\infty$ correction
operations $m_k$ for $k\ge 3$.
\item Chiral $Y(\fg)^{\mathrm{ch}}$: an $E_1$-chiral algebra on a
smooth curve $X$, a $D$-module on $X$ realising the line-operator
algebra; this is what
Theorem~\ref{thm:yangian-recognition} produces and what this
chapter studies.
\item Spectral factorization on $\mathbb{A}^1_u$: a factorization
algebra on the spectral line whose stalks at points $u\ne v$
recover the chiral Yangian's evaluation modules; the
Latyntsev~\cite{Latyntsev23} convention.
\end{enumerate}
The line-operator $A_\infty$-module category in this chapter is
governed by the chiral Yangian $Y(\fg)^{\mathrm{ch}}$ (type 3); the
strict presentation
(Theorem~\ref{thm:complete-strictification}) is the dg-shifted
package $Y^{\mathrm{dg}}_\hbar(\fg)$ (type 2). The classical
Yangian $Y_\hbar(\fg)$ (type 1) is recovered as the
mode algebra at a point; the spectral factorization (type 4) is the
form used by~\cite{Latyntsev23} and reviewed
in~\S\ref{chap:dg-shifted-factorization}.
\end{convention}

\begin{remark}[Equivalence of two chiral-Yangian definitions is open]
\label{rem:line-operators-yangian-definitions}
Two definitions of chiral Yangian circulate: the
$E_1$-factorization-plus-RTT version
(def:e1-chiral-yangian, the weaker), and the modular-MC-tower
version
(def:chiral-yangian-datum, the stronger). The line-operator setting
in this chapter uses the weaker $E_1$-factorization-plus-RTT
version; the modular-MC-tower equivalence is OPEN at chain level
(genus~$\ge 1$ requires the curved-Dunn $H^2=0$ closure of
Vol~II, conjecture closed for non-logarithmic standard landscape
via the irregular-singular KZB framework). Every theorem in this
chapter that uses ``chiral Yangian'' applies in the weaker
version; the upgrade to the stronger version is conditional on
the modular-Yangian comparison theorem of~\S\ref{sec:bar-cobar}
above.
\end{remark}

\subsection{Working notion for line operators}
\label{subsec:line-operators-working-notion}

\begin{convention}[Line-operator inputs are Notion~B;
\ClaimStatusProvedElsewhere]
\label{conv:line-operators-notion-b}
The line-operator algebra $\cA^!_{\mathrm{line}}$ (open-colour
Koszul dual of the boundary algebra $\cA$) is read as a Notion~B
$E_1$-chiral algebra: an $A_\infty$-algebra in
$\mathrm{End}^{\mathrm{ch}}_{\cA^!}$ with structure maps
$\{m_k\}_{k\ge 1}$ chain-level. The dg-shifted Yangian package is
the strict presentation of this Notion-B input. Line-operator
modules are Notion-B $A_\infty$-modules; the spectral
$R^{\mathrm{hol}}(z)$ acts on the module category in the
chain-level $E_2$-sense recovered from the bar deconcatenation
coproduct after fixing a Drinfeld associator.
\end{convention}

\subsection{Line operators as the open-colour Koszul reflection}
\label{subsec:line-operators-koszul-reflection-anchor}

\begin{remark}[Line operators as the open-colour image of the Koszul
reflection; \ClaimStatusProvedElsewhere]
\label{rem:line-operators-koszul-reflection}
The line-operator algebra $\cA^!_{\mathrm{line}}$ and the
identification
$\mathcal{C}_{\mathrm{line}} \simeq
\cA^!_{\mathrm{line}}\text{-mod}^{A_\infty}$
of~\S\ref{sec:bar-cobar} above are the open-colour shadow of the
Vol~I unified Koszul reflection theorem
(\cref{V1-thm:koszul-reflection}): the bar--cobar adjunction
$\Omega^{\mathrm{ch}} \dashv \barB$ on the conilpotent-complete
locus produces the dual $\cA \mapsto \cA^!_{\mathrm{line}}$, and
the line category is the homotopy category of comodules over the
bar coalgebra. The Vol~II picture is the
holomorphic--topological refinement: the chiral derived centre
$\mathrm{C}^\bullet_{\mathrm{ch}}(\cA,\cA)$ is the bulk algebra of
the universal $3$d HT theory acting on $\cA^!_{\mathrm{line}}$
along the open colour, and the spectral $R^{\mathrm{hol}}(z)$ is
the half-braiding presentation of this bulk action.
\end{remark}

\begin{remark}[Bridge to the Vol~II climax]
\label{rem:line-operators-uhm-bridge}
The line-operator description of this chapter inputs to the
\cref{thm:universal-holography-master} (Vol~II
\cref{ch:programme-climax-platonic}) on the boundary side: the universal
holography functor $\Phi_{\mathrm{hol}}$ takes the boundary
chiral algebra $\cA$ and produces the bulk $3$d HT theory
$T_\cA$ whose Wilson lines are the modules over
$\cA^!_{\mathrm{line}}$. The specialisation classes (G/L/C/M
plus FF) of the Vol~II infinite fingerprint classification
control the corresponding line-operator structure: class~G
yields abelian line operators with trivial braiding (Heisenberg
modular $S$-matrix at $k=1$); class~L yields the Verlinde
$S$-matrix at integer level; class~C yields the spectral
$R^{\mathrm{hol}}(z)$ for $\beta\gamma$; class~M yields the
gravitational Yangian (\S\ref{sec:thqg-gravitational-yangian});
class~FF (critical level) yields the Feigin--Frenkel-centre
opers as line-operator algebra.
\end{remark}

\begin{remark}[Bridge to the universal conductor]
\label{rem:line-operators-conductor-bridge}
The universal ghost-charge conductor formula
$K = c_{\mathrm{matter}} + c_{\mathrm{ghost}}$ of Vol~I
\cref{V1-chap:universal-conductor} controls the line-operator
braiding via the corresponding Koszul-locus reflection: at
$K = 26$ for Vir (matter+ghost) the line category becomes a
critical-level shadow; at $K = 196$ for Bershadsky--Polyakov the
gravitational-Yangian self-dual shadow appears. The line-operator
data of this chapter inherits the conductor stratification by
specialisation class; we pin the dependence here once and refer
forward to the climax for the systematic treatment.
\end{remark}

\subsection{Miura cross-term universality on the line-operator coproduct}
\label{subsec:line-operators-miura-coproduct}

\begin{remark}[$(\Psi-1)/\Psi$ on line-operator cross-terms;
\ClaimStatusProvedElsewhere]
\label{rem:line-operators-miura-coproduct}
The line-operator OPE is governed by the spectral coproduct
$\Delta_z\colon \cA^!_{\mathrm{line}}\to
(\cA^!_{\mathrm{line}})^{\otimes 2}((z))$. For the
Miura-presented $\mathcal{W}_N$ case, the cross-term coefficient on
$:J\otimes \mathcal{W}_{s-1}: + :\mathcal{W}_{s-1}\otimes J:$ is
universally $(\Psi-1)/\Psi$ for every spin $s\ge 2$
(Vol~I Theorem~\ref*{V1-thm:miura-cross-universality}).
The coincidence at $\Psi=2$ ($1/\Psi = (\Psi-1)/\Psi = 1/2$) is
flagged here so that line-operator computations at
$\Psi=2$ (the free-boson point) are not used as evidence for the
incorrect $1/\Psi$ universality.
\end{remark}

\section{Synthesis}
\label{sec:line-operators-wave13-DNA}

\begin{remark}[$24$ M5-branes on Kodaira I$_1$ fibres]
\label{rem:line-operators-DNA-1}
The line-operator theory assembled here for twisted holographic quantum
gravity admits a preferred realisation at the K3 the K3 synthesis base point:
$24$ M$5$-branes wrapping the $24$ Kodaira I$_1$ fibres of
$E^{\mathrm{nod,sm}}_{24}\to\mathbb P^1$ inside a twisted 11D-SUGRA on
$K3\times T^2$ (Witten 1995 M-theory duality, Vafa 1996 F-theory K3).
The line operators on the M$5$-brane worldvolume assemble into class-$\mathcal S$
$A_1$ surface defects on $\Sigma_{0,24}$ with total flavour symmetry
$\mathfrak{su}(2)^{24}$, and their OPE algebra closes onto
$\mathbf H_{\Delta_5}$ after the Beem--Lemos--Liendo--Peelaers--Rastelli--van~Rees
SCFT-to-VOA functor. The $24$-fold multiplicity is Steiner-rigid via
$S(5,8,24)$: any resolution of the Kodaira-I$_1$ configuration that
breaks $M_{24}$-equivariance loses the canonical line-operator structure.
Cross-ref Vol.~III, Chapter~\ref{ch:k3-chiral-bialgebra-platonic},
\S\ref{sec:twisted-11dsugra-24-fibres}.
\end{remark}

\begin{remark}[Four duality frames for the K3 line-operator algebra]
\label{rem:line-operators-DNA-2}
The same line-operator algebra $\mathbf H_{\Delta_5}$ appears in four
dual frames, which should be read as four UV realisations of one IR
worldvolume theory:
\begin{itemize}
\item \emph{Heterotic on $T^4$} (Harvey--Moore 1996): line operators
      arise as half-BPS black holes counted by the elliptic genus;
\item \emph{IIB on $K3$} (Dijkgraaf--Verlinde--Verlinde 1996--97):
      line operators are D$1$--D$5$ bound states;
\item \emph{IIA on $K3$} (Dijkgraaf--Moore--Verlinde--Verlinde 1997):
      line operators are second-quantised string states counted by
      $\Phi_{10}$;
\item \emph{M-theory on $K3\times T^2$} (Witten 1995): line operators
      are M$2$-M$5$ bound states on Kodaira I$_1$ fibres.
\end{itemize}
The Gritsenko--Nikulin 1998 Igusa lift $\Phi_{10}$ is the generating
function counting all four in lockstep, and the Hall-Drinfeld
double $\mathbf H_{\Delta_5}$ is the unified non-abelian-chiral
quantisation of their common worldvolume. Primary-lit cited inline;
see Vol.~III, Chapter~\ref{ch:k3-chiral-bialgebra-platonic},
\S\ref{sec:four-duality-frames}.
\end{remark}
