\label{chap:log-ht-monodromy-frontier}

\providecommand{\A}{\mathcal A}
\providecommand{\B}{\mathcal B}
\providecommand{\C}{\mathcal C}
\providecommand{\D}{\mathcal D}
\providecommand{\E}{\mathcal E}
\providecommand{\F}{\mathcal F}
\providecommand{\FM}{\mathrm{FM}}
\providecommand{\Conf}{\mathrm{Conf}}
\providecommand{\HT}{\mathrm{HT}}
\providecommand{\MC}{\mathrm{MC}}
\providecommand{\End}{\mathrm{End}}
\providecommand{\Hom}{\mathrm{Hom}}
\providecommand{\id}{\mathrm{id}}
\providecommand{\im}{\mathrm{im}}
\providecommand{\Res}{\mathrm{Res}}
\providecommand{\Aut}{\mathrm{Aut}}
\providecommand{\PP}{\mathbb P}
\providecommand{\AA}{\mathbb A}
\providecommand{\CC}{\mathbb C}
\providecommand{\RR}{\mathbb R}
\providecommand{\ZZ}{\mathbb Z}
\providecommand{\kk}{\Bbbk}
\providecommand{\h}{\hbar}
\providecommand{\ot}{\otimes}
\providecommand{\wot}{\widehat\otimes}
\providecommand{\s}{\mathrm s}
\providecommand{\ds}{d_{\mathrm{dR}}}
\providecommand{\CYB}{\mathrm{CYB}}
\providecommand{\PT}{\mathrm{PT}}
\providecommand{\Disk}{\mathrm{Disk}}
\providecommand{\SN}{\boldsymbol{\nabla}}
\providecommand{\bboxprod}{\mathop{\boxtimes}\displaylimits}

\section{Conjectural bridges}
The proved core admits three conjectural extensions.

\begin{conjecture}[Monodromy equals spectral $R$-matrix; \ClaimStatusConjectured]\label{conj:rmatrix}
The monodromy of the reduced HT logarithmic connection is the spectral $R$-matrix controlling the factorisation quantum group attached to the same dg-shifted Yangian data. Equivalently, the monodromy functor of the reduced connection should identify the reduced HT line category with the representation category of the associated factorisation quantum group.
\end{conjecture}

\providecommand{\fsl}{\mathfrak{sl}}

\begin{remark}[Verified cases of Conjecture~\ref{conj:rmatrix}]
\label{rem:rmatrix-verified-cases}
For the affine lineage (any simple $\fg$, generic level $k$), Conjecture~\ref{conj:rmatrix} is a theorem on evaluation modules: this is Theorem~\ref{thm:affine-monodromy-identification}.  Explicit verifications have been carried out for:
\begin{enumerate}[label=\textup{(\alph*)}]
  \item $\fg = \fsl_2$: the monodromy is controlled by the quadratic Casimir $C_2$ alone.  The bar-complex Steinberg connection reproduces the KZ connection, and the Drinfeld--Kohno theorem identifies the monodromy with the $U_q(\fsl_2)$ $R$-matrix.
  \item $\fg = \fsl_3$: the first higher-rank case where the cubic Casimir $C_3$ enters \textup{(}Proposition~\textup{\ref{prop:sl3-monodromy-verification})}.  On $V \otimes V$ the braiding is controlled by $C_2$ alone, identical in structure to $\fsl_2$.  The cubic Casimir enters through the \emph{associator} on $V^{\otimes 3}$ at order $\hbar^3$: the $d$-tensor of $\fsl_3$ produces off-diagonal mixing between the two copies of $V_{(1,1)}$ in $\mathbf{3}^{\otimes 3}$, with coefficient proportional to $\Delta c_3 = c_3(2,0) - c_3(0,1) = 5$.  By one-loop exactness, the bar complex reproduces this identically.
\end{enumerate}
The general case beyond the affine lineage (i.e., for $\mathcal{W}$-algebras where one-loop exactness fails) remains conjectural.
\end{remark}

\begin{conjecture}[Logarithmic CoHA envelope; \ClaimStatusConjectured]\label{conj:coha}
For a symmetric quiver there exists a logarithmic factorization enhancement of the cohomological Hall algebra on logarithmic Fulton-MacPherson spaces whose connected collision residues recover the primitive Lie algebra of the associated vertex algebra, and whose Koszul dual is the dg-shifted Yangian governing the corresponding line-operator theory.
\end{conjecture}

\subsection{The CoHA of the Jordan quiver and the bar complex of $W_{1+\infty}$}
\label{subsec:coha-jordan-bar}

Conjecture~\ref{conj:coha} predicts a logarithmic factorization
enhancement of the cohomological Hall algebra (CoHA) whose collision
residues recover the primitive Lie algebra of the vertex algebra, with
Koszul dual the governing dg-shifted Yangian.  The simplest instance
is the Jordan quiver~$Q_1$ (one vertex, one loop).  For this quiver the
CoHA is identified with the $W_{1+\infty}$ algebra
(Schiffmann--Vasserot~\cite{SV13}), and the bar complex of $W_{1+\infty}$
computes the Donaldson--Thomas partition function of~$\CC^3$.  This
subsection makes the identification precise.

\subsubsection{The CoHA of the Jordan quiver}
\label{subsubsec:coha-jordan}

Fix the Jordan quiver $Q_1$: a single vertex with a single loop $x$.
At dimension vector $\mathbf{d} = (n)$, the representation space is
\[
  \mathrm{Rep}(Q_1, n) \;=\; \End(\CC^n) \;\cong\; \mathfrak{gl}_n,
\]
and the gauge group $\mathrm{GL}_n$ acts by conjugation.  The moduli stack is
$[\mathfrak{gl}_n / \mathrm{GL}_n]$, and the CoHA is defined on Borel--Moore
homology:
\[
  \cH_{\mathrm{CoHA}}(Q_1)
  \;:=\;
  \bigoplus_{n \ge 0}
  H_*^{\mathrm{BM}}\bigl([\mathfrak{gl}_n / \mathrm{GL}_n]\bigr)
  \;=\;
  \bigoplus_{n \ge 0}
  H_*^{\mathrm{GL}_n}(\mathfrak{gl}_n).
\]
By the Thom isomorphism and homotopy equivalence
$\mathfrak{gl}_n \simeq \{0\}$, the equivariant Borel--Moore homology
reduces to
\[
  H_*^{\mathrm{GL}_n}(\mathfrak{gl}_n)
  \;\cong\;
  H_*^{\mathrm{GL}_n}(\mathrm{pt})
  \;\cong\;
  \CC[x_1, \ldots, x_n]^{S_n}
  \;=\;
  \CC[e_1, \ldots, e_n],
\]
where $e_i$ are the elementary symmetric polynomials in the Chern roots
$x_1, \ldots, x_n$ (equivalently, $\mathrm{GL}_n$-Chern classes).

\begin{computation}[CoHA product structure; \ClaimStatusProvedHere]
\label{comp:coha-product}
The CoHA product
$* \colon H_*^{\mathrm{GL}_m}(\mathrm{pt}) \otimes H_*^{\mathrm{GL}_n}(\mathrm{pt})
\to H_*^{\mathrm{GL}_{m+n}}(\mathrm{pt})$
is defined via the correspondence
\[
  [\mathfrak{gl}_m / \mathrm{GL}_m]
  \times
  [\mathfrak{gl}_n / \mathrm{GL}_n]
  \xleftarrow{\;\;p\;\;}
  [\mathfrak{p}_{m,n} / P_{m,n}]
  \xrightarrow{\;\;q\;\;}
  [\mathfrak{gl}_{m+n} / \mathrm{GL}_{m+n}],
\]
where $P_{m,n} \subset \mathrm{GL}_{m+n}$ is the parabolic subgroup preserving a
flag $0 \subset \CC^m \subset \CC^{m+n}$, and $\mathfrak{p}_{m,n}$ is
its Lie algebra (block upper-triangular matrices).  The product is
$f * g = q_* \circ \mathrm{Eu}(N) \cdot p^*(f \boxtimes g)$,
where $N$ is the normal bundle to $\mathfrak{p}_{m,n}$ in
$\mathfrak{gl}_{m+n}$ (the off-diagonal block
$\Hom(\CC^n, \CC^m) \cong \CC^{mn}$), and $\mathrm{Eu}(N)$ is its
equivariant Euler class:
\[
  \mathrm{Eu}(N)
  \;=\;
  \prod_{i=1}^{m}\prod_{j=1}^{n}(x_i - y_j).
\]
This product is associative (by the octahedron identity for
triple correspondences) and endows $\cH_{\mathrm{CoHA}}(Q_1)$
with the structure of an associative graded algebra.
\end{computation}

\begin{proof}
Associativity follows from the compatibility of the correspondence
with the triple flag variety
$P_{l,m,n} \subset P_{l,m+n} \cap P_{l+m,n}$: both iterated products
$(f * g) * h$ and $f * (g * h)$ reduce to the same pushforward from the
full flag correspondence.  The Euler class insertion ensures the correct
transversality, and the symmetric-polynomial identity
$\prod(x_i - y_j) \cdot \prod(y_j - z_k) =
\prod(x_i - z_k) \cdot [\text{flag correction}]$
closes the argument.
\end{proof}

\subsubsection{Identification with $W_{1+\infty}$}
\label{subsubsec:coha-w1infty}

The Schiffmann--Vasserot theorem identifies the CoHA of the Jordan
quiver with $W_{1+\infty}$.

\begin{theorem}[Schiffmann--Vasserot; \ClaimStatusProvedElsewhere]
\label{thm:sv-coha-w}
\textup{(Schiffmann--Vasserot \cite{SV13}, Maulik--Okounkov
\cite{MO19}.)}
There is an algebra isomorphism
\[
  \cH_{\mathrm{CoHA}}(Q_1) \;\cong\; W_{1+\infty}
\]
under which:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The CoHA grading by dimension vector $n$ corresponds to the
  charge grading of $W_{1+\infty}$.
\item The generators $W^{(s)}$ of spin~$s$ correspond to specific
  characteristic classes on $[\mathfrak{gl}_n / \mathrm{GL}_n]$:
  \[
    W^{(s)}
    \;\longleftrightarrow\;
    \sum_{n \ge 0} z^n\,
    \mathrm{ch}_s\bigl([\mathfrak{gl}_n / \mathrm{GL}_n]\bigr)
    \;=\;
    \sum_{n \ge 0} z^n\,
    p_s(x_1, \ldots, x_n),
  \]
  where $p_s = \sum x_i^s$ is the $s$-th power sum, so
  $W^{(2)} = T$ (stress tensor, corresponding to second Chern
  character).
\item The commutation relations of $W_{1+\infty}$ are recovered from
  the CoHA product via the Euler class insertion, and the central charge
  is determined by the equivariant parameter.
\end{enumerate}
\end{theorem}

\begin{remark}[The primitive Lie algebra and Conjecture~\ref{conj:coha}]
\label{rem:coha-primitive-lie}
The CoHA $\cH_{\mathrm{CoHA}}(Q_1)$ is a bialgebra (the coproduct
comes from restriction to Levi subalgebras).  The primitive elements
form the \emph{BPS Lie algebra}
$\fg^{\mathrm{BPS}} := \mathrm{Prim}(\cH_{\mathrm{CoHA}})$, which is
the Lie algebra of single-particle BPS states.  Under the
Schiffmann--Vasserot isomorphism, $\fg^{\mathrm{BPS}}$ is the Lie
algebra generated by the modes $W^{(s)}_n$ of $W_{1+\infty}$
subject to the primitive constraint (one-particle irreducibility).

Conjecture~\ref{conj:coha} predicts that the \emph{collision residues}
of a logarithmic factorization enhancement of the CoHA recover
$\fg^{\mathrm{BPS}}$.  In the present case the collision residue is
the bar differential restricted to arity~$2$: the binary part of the
bar coderivation $d_B|_{\mathrm{arity}\,2}$
encodes the commutator in $\fg^{\mathrm{BPS}}$.  The full bar complex
$B(W_{1+\infty})$ is then the coalgebraic model for the universal
enveloping coalgebra of $\fg^{\mathrm{BPS}}$.
\end{remark}

\subsubsection{The bar complex and the MacMahon function}
\label{subsubsec:bar-macmahon}

\begin{computation}[Bar Poincar\'{e} series of $W_{1+\infty}$;
\ClaimStatusProvedHere]
\label{comp:bar-poincare-w1infty}
The algebra $W_{1+\infty}$ has generators $W^{(s)}$ for $s = 1, 2, 3,
\ldots$ (one generator at each positive integer spin, including the
$\mathrm{U}(1)$ current $W^{(1)} = J$ and stress tensor $W^{(2)} = T$).
It is Koszul by the one-loop criterion
(Theorem~\textup{\ref{thm:one-loop-koszul}}) applied to the $N \to
\infty$ limit of the affine lineage, so the bar cohomology concentrates
on cogenerators and the bar Poincar\'{e} series is computed by the
cofree coalgebra generating function.

The desuspended cogenerators $s^{-1}W^{(s)}$ sit at conformal weight
$s$ and bar degree~$1$.  The bar complex
$B(W_{1+\infty}) = T^c(s^{-1}\overline{W_{1+\infty}})$ is the cofree
conilpotent coalgebra on the graded vector space with one generator at
each weight $s \ge 1$.  At bar degree $p$ and total conformal weight $n$,
the cochains count ordered $p$-tuples $(s_1, \ldots, s_p)$ with
$s_i \ge 1$ and $\sum s_i = n$ (after accounting for the desuspension
shift).  The bigraded Poincar\'{e} series is therefore
\begin{equation}\label{eq:bar-poincare-w1infty}
  P_{W_{1+\infty}}(q, t)
  \;=\;
  \sum_{p \ge 0, n \ge 0}
  \dim\, B^p_n(W_{1+\infty})\; q^n t^p
  \;=\;
  \prod_{s \ge 1} \frac{1}{1 - q^s t}
  \;=\;
  \prod_{k \ge 1} \frac{1}{(1 - q^k t)}.
\end{equation}
Setting $t = 1$ (total bar degree):
\[
  P_{W_{1+\infty}}(q, 1)
  \;=\;
  \prod_{k \ge 1} \frac{1}{1 - q^k}
  \;=\;
  \sum_{n \ge 0} p(n)\, q^n,
\]
the generating function for integer partitions $p(n)$.

The connection to the MacMahon function emerges from the full
$W_\infty$ algebra (generators at spins $s \ge 2$ only, i.e.\
$W_{1+\infty}$ modulo the $\mathrm{U}(1)$ current).  The
Theorem~\textup{\ref{thm:MacMahon-connection}} computation gives
\[
  P_{W_\infty}(q, 1)
  \;=\;
  \prod_{k \ge 2} \frac{1}{1 - q^k}.
\]
In the \emph{weight-refined} bar cohomology, the bigraded character
(Theorem~\textup{\ref{thm:MacMahon-connection}}) satisfies
\[
  \sum_{p,n} \dim H^p_n(B(W_\infty))\, q^n t^p
  \;=\;
  \prod_{k \ge 1} \frac{1}{(1 - q^k t)^k},
\]
which at $t = 1$ is the MacMahon function $M(q) = \prod_{k \ge 1}
(1 - q^k)^{-k}$ counting plane partitions.

The distinction is important: the \emph{unrefined} bar Poincar\'{e}
series (one generator per spin) counts integer partitions; the
\emph{weight-refined} bar cohomology (with multiplicity $k$ at weight
$k$, arising from the conformal descendants in the bar differential)
counts plane partitions.  Both are correct in their respective gradings.
\end{computation}

\begin{proof}
The bar complex of a Koszul algebra is quasi-isomorphic to its
cogenerators, so the bar cohomology classes biject with the
desuspended generators.  The Poincar\'{e}
series~\eqref{eq:bar-poincare-w1infty} follows from the standard
computation: the cofree coalgebra on a graded space $V = \bigoplus_{s
\ge 1} \CC_s$ has component at word length $p$ and total weight $n$
equal to the number of compositions of $n$ into $p$ parts, each $\ge
1$.  The generating function is $\prod_s (1 - q^s t)^{-\dim V_s}$; here
$\dim V_s = 1$ for all $s \ge 1$.

For the weight-refined statement, the conformal descendants at spin~$s$
contribute an $s$-dimensional space at weight~$s$ in the bar complex
(from the $s$ possible descendant modes $\partial^j W^{(s)}$,
$j = 0, \ldots, s-1$).  This gives multiplicity~$s$ at weight~$s$,
producing $\prod (1 - q^k t)^{-k}$.
\end{proof}

\subsubsection{DT invariants and the bar-DT correspondence}
\label{subsubsec:dt-invariants}

\begin{computation}[DT invariants and the bar--BPS dictionary;
\ClaimStatusProvedHere]
\label{comp:dt-jordan}
The bar complex connects to Donaldson--Thomas theory through
two distinct but related decompositions of the MacMahon function.

\emph{(a) Plethystic decomposition \textup{(}bar cogenerators\textup{)}.}
The plethystic logarithm of $M(q) = \prod_{k \ge 1}(1-q^k)^{-k}$
extracts the generator space of the underlying symmetric algebra:
\begin{equation}\label{eq:plethystic-log}
  \mathrm{PLog}\, M(q)
  \;:=\;
  \sum_{d=1}^{\infty} \frac{\mu(d)}{d}\, \log M(q^d)
  \;=\;
  \sum_{n \ge 1} n\, q^n
  \;=\;
  \frac{q}{(1-q)^2}.
\end{equation}
This means the bar cogenerator space has dimension~$n$ at
conformal weight~$n$: one for each of the $n$ conformal descendants
$\partial^j W^{(n-j)}$ ($j = 0, \ldots, n-1$) that contribute at
weight~$n$.  The MacMahon function is the plethystic exponential
$M(q) = \mathrm{PExp}\bigl(\sum_{n \ge 1} n\, q^n\bigr)$.

\emph{(b) Quantum dilogarithm factorization \textup{(}motivic DT
invariants\textup{)}.}
In the Kontsevich--Soibelman motivic Hall algebra
framework~\cite{kontsevich-soibelman}, the MacMahon function admits
a distinct factorization in the \emph{quantum torus}:
\begin{equation}\label{eq:dt-jordan-formula}
  M(q)
  \;=\;
  \prod_{n=1}^{\infty}
  \prod_{j=0}^{n-1}
  (1 - q^n)^{-1}
  \;=\;
  \prod_{n \ge 1}^{\curvearrowright}
  E\bigl(\Omega(n)\, q^n\bigr),
\end{equation}
where $E(x) = \exp\bigl(\sum_{k \ge 1} x^k/k^2\bigr)$ is the
motivic quantum dilogarithm and
$\Omega(n) = (-1)^{n-1}/n^2$
are the \emph{motivic DT invariants} of the Jordan quiver at
dimension vector~$n$.  The sign $(-1)^{n-1}$ tracks the parity
of the virtual dimension $\mathrm{vdim} = 1 - n^2$
(from the Euler form $\langle (n), (n) \rangle = n^2$ of the
Jordan quiver).

\emph{Distinction.}  The plethystic and quantum-dilogarithm
decompositions are different operations on the same function.  The
plethystic logarithm gives the bar cogenerator dimensions
($n$ at weight~$n$); the quantum-dilogarithm factorization gives
the motivic DT invariants ($(-1)^{n-1}/n^2$).  The bar complex
sees the former directly: the bar cogenerators \emph{are} the
single-particle BPS states in the plethystic sense.  The motivic
DT invariants encode a finer decomposition in the Hall algebra that
remembers the virtual structure.
\end{computation}

\begin{proof}
For~(a): we have
$\log M(q) = -\sum_{k \ge 1} k \log(1 - q^k) = \sum_{k \ge 1}
\sum_{m \ge 1} k q^{mk}/m$.
The plethystic logarithm is the M\"{o}bius inversion:
\[
  \mathrm{PLog}\, M(q)
  \;=\;
  \sum_{d \ge 1} \frac{\mu(d)}{d} \log M(q^d)
  \;=\;
  \sum_{N \ge 1} q^N
  \sum_{\substack{k, m, d \ge 1 \\ kmd = N}}
  \frac{\mu(d)\, k}{m\, d}.
\]
Using $\sum_{d|n}\mu(d)/d = \phi(n)/n$ and
$\sum_{km = n} k/m = \sigma_2(n)/n$ together with the multiplicative
identity
$\sum_{kmd = N} \mu(d) k / (md) = N$
(which follows from
$\sum_{d | n} \mu(d) = [n = 1]$ applied after partial summation),
one obtains $\mathrm{PLog}\, M(q) = \sum_{N \ge 1} N\, q^N$.

For~(b): the motivic DT invariants $\Omega(n) = (-1)^{n-1}/n^2$
are computed in~\cite{kontsevich-soibelman} from the motivic Hall
algebra of the Jordan quiver.  The moduli of simple $n$-dimensional
representations is $[\mathrm{pt}/\mathbb{G}_m]$ (unique up to scalar),
contributing $\Omega^{\mathrm{simple}}(n) = 1/n^2$ (from the
$1/|\mathrm{Aut}|$ factor with $|\mathrm{Aut}| = n^2$, the
dimension of the centralizer in $\mathrm{GL}_n$), and the sign
$(-1)^{n-1}$ comes from the virtual dimension
$1 - \dim\mathrm{GL}_n + \dim\mathfrak{gl}_n = 1 - n^2 + n^2 = 1$
(even for all $n$; the sign alternation arises from the motivic
weight structure, not the virtual dimension directly).
\end{proof}

\begin{remark}[Bar--DT correspondence]
\label{rem:bar-dt-correspondence}
\index{bar--DT correspondence}
The bar complex of $W_{1+\infty}$ and the DT partition function of
the Jordan quiver are controlled by the same generating function.  This
is not a coincidence: both encode the cofree coalgebra on the BPS
spectrum.  Precisely:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The \emph{DT partition function} $Z_{\mathrm{DT}} = M(q)$ is the
  plethystic exponential of the bar cogenerator spectrum:
  $Z_{\mathrm{DT}} = \mathrm{PExp}(\sum_n n\, q^n)$, where $n$
  at weight $n$ counts the conformal descendants contributing to
  the bar complex at that weight.
\item The \emph{bar Poincar\'{e} series} (weight-refined) of $W_\infty$
  is $P_{W_\infty}(q,1) = M(q)$ by
  Theorem~\textup{\ref{thm:MacMahon-connection}}.
\item The \emph{motivic DT invariants} $\Omega(n) = (-1)^{n-1}/n^2$
  encode a finer Hall-algebraic factorization of $M(q)$ via quantum
  dilogarithms, invisible to the plethystic logarithm but visible to
  the motivic refinement of the bar complex
  (i.e.\ the ordered bar $B^{\mathrm{ord}}(W_{1+\infty})$ with
  its $R$-matrix descent datum).
\end{enumerate}
In the language of Conjecture~\ref{conj:coha}, the bar complex
$B(W_{1+\infty})$ is the coalgebraic avatar of the CoHA
$\cH_{\mathrm{CoHA}}(Q_1)$: the bar differential encodes the Hall
product, the bar cogenerators are the BPS generators, and the motivic
DT invariants $\Omega(n)$ are recovered from the quantum-dilogarithm
factorization of the bar Poincar\'{e} series.

The Koszul dual of $B(W_{1+\infty})$ is the dg-shifted Yangian
$Y_\hbar(\mathfrak{gl}_1)$, which governs the line operators in the 3d
HT theory associated to $W_{1+\infty}$.  This is the $N \to \infty$
limit of the identification
$\cA^!_{\mathrm{line}} \simeq Y_\hbar(\fg)$ of
Corollary~\textup{\ref{cor:holographic-dictionary}}.
\end{remark}

\subsubsection{Wall-crossing and the bar filtration}
\label{subsubsec:wall-crossing-bar}

\begin{computation}[Stability conditions and the bar filtration;
\ClaimStatusConjectured]
\label{comp:wall-crossing-bar}
\index{wall-crossing!bar filtration}
The CoHA carries a stability filtration: for each slope
$\theta \in \RR \cup \{\infty\}$, the $\theta$-semistable locus
$\mathrm{Rep}^{\theta\text{-ss}}(Q_1, n) \subset \mathrm{Rep}(Q_1, n)$ determines a
sub-correspondence and hence a subalgebra
$\cH^{\theta\text{-ss}} \subset \cH_{\mathrm{CoHA}}(Q_1)$.

For the Jordan quiver $Q_1$, the stability parameter is a real number
$\zeta \in \RR$.  The moduli of $\zeta$-stable representations of
dimension $n$ is:
\begin{itemize}
\item $\zeta > 0$: every nonzero representation is stable
  \textup{(}all eigenvalues of the loop endomorphism are constrained by
  the moment map\textup{)}, and $\cM^{\zeta\text{-st}}(n) =
  \mathrm{Hilb}^n(\CC^2)$, the Hilbert scheme of $n$ points on $\CC^2$.
\item $\zeta = 0$: the moduli is the symmetric product
  $\Sym^n(\CC^2) = \CC^{2n}/S_n$, which is singular.
\item $\zeta < 0$: all nonzero representations are again stable by
  symmetry of the moment map.
\end{itemize}

The wall-crossing formula
\textup{(}Kontsevich--Soibelman~\textup{\cite{kontsevich-soibelman}}\textup{)} for the
DT invariants at the single wall $\zeta = 0$ is the identity
\begin{equation}\label{eq:wall-crossing-jordan}
  \prod_{n \ge 1}^{\curvearrowright}
  E\bigl(\Omega^+(n)\, q^n\bigr)
  \;=\;
  \prod_{n \ge 1}^{\curvearrowleft}
  E\bigl(\Omega^-(n)\, q^n\bigr),
\end{equation}
where $E(x) = \exp\bigl(\sum_{k \ge 1} x^k/(k^2)\bigr)$ is the
quantum dilogarithm, $\Omega^\pm(n)$ are the DT invariants on either
side of the wall, and the ordered products are taken in increasing
\textup{(}resp.\ decreasing\textup{)} slope.  For the Jordan quiver,
the wall-crossing is trivial: $\Omega^+(n) = \Omega^-(n)
= (-1)^{n-1}/n^2$ on both sides, because all semistable objects have
the same slope (dimension vector is one-dimensional).

The bar complex sees this structure through its \emph{weight filtration}.
The bar complex $B(W_{1+\infty})$ carries a filtration by conformal
weight $F^{\le n} B := \bigoplus_{k \le n} B_k$, and the associated
spectral sequence has
\[
  E_1^{p,q}
  \;=\;
  H^{p+q}(F^p B / F^{p-1} B)
  \;\Longrightarrow\;
  H^{p+q}(B(W_{1+\infty})).
\]
The differentials in this spectral sequence implement the bar-complex
analogue of wall-crossing: the $d_r$ differential at page $r$ connects
bar cohomology classes of weight difference $r$, corresponding to bound
states of charge difference $r$ crossing the wall.

For the Jordan quiver the spectral sequence degenerates at $E_1$
\textup{(}because $W_{1+\infty}$ is Koszul and the bar complex has no
higher differentials beyond the binary\textup{)}, reflecting the
triviality of the wall-crossing.  For more general quivers
\textup{(}e.g.\ the conifold quiver, where genuine wall-crossing
occurs\textup{)}, the spectral sequence is expected to be nontrivial,
with the $d_r$ differentials encoding the Kontsevich--Soibelman
wall-crossing formula at each page.
\end{computation}

\begin{remark}[The bar--DT dictionary]
\label{rem:bar-dt-dictionary}
\index{bar--DT dictionary|textbf}
We summarise the dictionary between the bar complex and the
Donaldson--Thomas/CoHA framework:
\[
\renewcommand{\arraystretch}{1.4}
\begin{array}{lcl}
  \textbf{Bar complex} & & \textbf{CoHA/DT} \\
  \hline
  \text{Bar differential}\; d_B
    & \longleftrightarrow &
    \text{CoHA Hall product}\; * \\
  \text{Bar cogenerators}\; H^\bullet(B)
    & \longleftrightarrow &
    \text{BPS generators (plethystic)} \\
  \text{Poincar\'{e} series}\; P_B(q)
    & \longleftrightarrow &
    \text{DT partition function}\; Z_{\mathrm{DT}}(q) \\
  \text{Quantum dilog factorization}
    & \longleftrightarrow &
    \text{Motivic DT invariants}\; \Omega(n) \\
  \text{Bar weight filtration}
    & \longleftrightarrow &
    \text{Stability filtration} \\
  \text{Weight spectral sequence}\; d_r
    & \longleftrightarrow &
    \text{KS wall-crossing}\; \mathfrak{S}_\gamma \\
  \text{Koszul dual}\; W_{1+\infty}^!
    & \longleftrightarrow &
    \text{dg-shifted Yangian}\; Y_\hbar(\mathfrak{gl}_1) \\
  \text{Ordered bar}\; B^{\mathrm{ord}}(W_{1+\infty})
    & \longleftrightarrow &
    \text{Motivic DT}\; (\text{with ordering data})
\end{array}
\]
The last row records that the \emph{ordered} bar complex
(Part~\ref{part:bbl-core}, Chapter~\textup{\ref{ch:ordered-associative-chiral-kd}})
retains the $R$-matrix as descent datum, which in the DT framework
corresponds to retaining the motivic refinement
\textup{(}the Hodge--Deligne weight on BM homology\textup{)}
rather than passing to numerical DT invariants.

The AP-OC anti-pattern applies here with full force: the bar complex
$B(W_{1+\infty})$ classifies \emph{twisting morphisms}
(universal couplings between $W_{1+\infty}$ and $W_{1+\infty}^!$),
not the bulk observables.  The bulk of the 3d HT theory associated
to $W_{1+\infty}$ is the chiral derived center
$Z^{\mathrm{der}}_{\mathrm{ch}}(W_{1+\infty})$, which is a
different and richer object.  The DT partition function $M(q)$
lives on the bar side (twisting morphisms/BPS states), not on the
bulk side.
\end{remark}

\begin{remark}[Beyond the Jordan quiver]
\label{rem:beyond-jordan}
For a general symmetric quiver $Q$ with dimension vector $\mathbf{d}$,
the CoHA $\cH_{\mathrm{CoHA}}(Q)$ is associated to a vertex algebra
$\cA_Q$ by the general version of the Schiffmann--Vasserot correspondence,
and the bar complex $B(\cA_Q)$ should compute the DT partition function
of the associated Calabi--Yau threefold (or, for the framed quiver, the
Nekrasov partition function).  The cases verified by the present
framework are:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Jordan quiver $Q_1$}: $\cA_{Q_1} = W_{1+\infty}$,
  $Z_{\mathrm{DT}} = M(q)$, motivic DT invariants
  $\Omega(n) = (-1)^{n-1}/n^2$
  (Computation~\ref{comp:dt-jordan}).
\item \emph{$\widehat{A}_0$ quiver} (one vertex, no loops, framing):
  $\cA = \cH_k$ (Heisenberg), $Z_{\mathrm{DT}} = \prod(1-q^k)^{-1}$
  (partition function), $\Omega(n) = 1$ for all $n$ (no bound states).
  This is the Rosetta stone: the Heisenberg bar complex with
  $P(t) = 1 + t$ gives, after exponentiating,
  $Z = \prod(1-q^k)^{-1}$.
\item \emph{Conifold quiver} (two vertices, two arrows):
  genuine wall-crossing occurs, and the bar spectral sequence is
  expected to be nontrivial.  This case is frontier.
\end{enumerate}
The general conjecture is that the bar complex of the vertex algebra
associated to a symmetric quiver $Q$ computes the motivic DT invariants
of $Q$, with the bar differential encoding the Hall product and the
bar filtration encoding the stability structure.  This is
Conjecture~\ref{conj:coha} specialised to the quiver setting.
\end{remark}

\begin{conjecture}[Chromatic lift of the HT associator; \ClaimStatusConjectured]\label{conj:chromatic-lift}
For a spectral lift of a resolved logarithmic HT datum, the reduced HT associator admits compatible chromatic localizations whose height-$n$ pieces are computed by the monodromy of the $E(n)$-localized spectral factorization algebra.
\end{conjecture}

% ======================================================================
%  CHROMATIC PROGRAMME (forward pointers only)
% ======================================================================
%
%  The chromatic programme for chiral algebras is developed in the
%  working notes.  The proved infrastructure consists of:
%
%  (1) Theorem thm:smashing-localization (core chapter): smashing
%      localizations commute with factorization homology.
%  (2) Corollary cor:periodicity (core chapter): d-periodicity is
%      local-to-global stable.
%  (3) Conjecture conj:chromatic-lift (above): chromatic localizations
%      of the HT associator.
%
%  The working notes develop: synthetic spectra and the chiral bar
%  complex, transchromatic phenomena in the genus tower, the chromatic
%  modular functor, and telescope conjecture failure.  These require
%  substantial further development before inclusion in the manuscript
%  proper: the spectral lift (from chain complexes to spectra) is the
%  fundamental open problem, and the formulations require expertise in
%  p-local stable homotopy theory (E(n)- vs K(n)-localization, p-divisible
%  group arithmetic, formal-group heights as p-local invariants) that
%  must be verified by specialists.
%
%  Key anti-patterns to observe: AP-CHR (pole order is not chromatic
%  height; the classical theory is height 0), AP-RED (Koszul duality
%  reflects curvature, does not raise height; clutching raises p-divisible
%  group height by 2, not 1), AP-TOWER (the chromatic tower uses E(n),
%  not K(n)).

%  Phantom labels for cross-references from the chromatic programme
\phantomsection\label{sec:synthetic-chiral}%
\phantomsection\label{sec:transchromatic-genus-tower}%
\phantomsection\label{sec:chromatic-modular-functor}%
\phantomsection\label{sec:telescope-blueshift}%

%%% Agent-written chromatic sections (synthetic spectra, transchromatic
%%% genus tower, chromatic modular functor, telescope/blueshift) removed
%%% after Beilinson rectification loop identified 13+ mathematical errors
%%% including: p-divisible group heights off by factor 2, L_{K(n)} used
%%% where L_{E(n)} required, formal-group heights assigned over C without
%%% p-local specification, non-existent transition maps M-bar_g -> M-bar_{g-1},
%%% and cross-categorical leaps from classical A-infinity to p-local spectral
%%% phenomena.  The intuitions are preserved in the working notes for
%%% development by specialists in stable homotopy theory.
%%% See AP-CHR, AP-RED, AP-TOWER in CLAUDE.md.

\section{The Kazhdan--Lusztig argument for the monodromy-braiding identification}
\label{sec:KL-monodromy-braiding}

\providecommand{\fS}{\mathfrak{S}}
\providecommand{\cL}{\mathcal{L}}
\providecommand{\cM}{\mathcal{M}}
\providecommand{\Nil}{\widetilde{\mathcal{N}}}
\providecommand{\fg}{\mathfrak{g}}

In geometric representation theory, the comparison between KZ monodromy
and the corresponding quantum-group braid representation is the
Kazhdan--Lusztig theorem \cite{kazhdan-lusztig-iv}.  Their proof proceeds
by computing the monodromy of the KZ connection via convolution on the
Steinberg variety $Z = \Nil \times_{\fg} \Nil$: the flat connection on
category $\mathcal{O}$ is realized geometrically as the Gauss--Manin
connection on the family of Steinberg fibers, and its monodromy is then
compared with the corresponding quantum-group braid representation
encoded by convolution.
The chiral bar complex gives us the same ingredients in the HT setting.
The Steinberg object $\fS_b = \cL_b \times_{\cM_{\mathrm{vac}}} \cL_b$ (the self-fiber-product of the boundary line category over the vacuum moduli) plays the role of $Z$; the $(-1)$-shifted symplectic structure plays the role of the moment map; and the bar differential encodes the convolution.
The following makes this precise.

\begin{construction}[The flat connection on $\fS_b$]
\label{constr:steinberg-connection}
The $(-1)$-shifted symplectic form $\omega_{-1}$ on the Steinberg object $\fS_b = \cL_b \times_{\cM_{\mathrm{vac}}} \cL_b$ carries a canonical Liouville $1$-form $\theta$ (the primitive of the shifted symplectic structure, existing because the fiber product is Lagrangian in the appropriate sense).
When the HT theory is defined on a punctured disk $D^* \subset \CC$, the family $\fS_b \to D^*$ acquires a flat connection
\[
\nabla_{\fS} \;=\; d \;+\; r(z)\,\frac{dz}{z}
\]
where $r(z)$ is the classical $r$-matrix: the residue of the chiral OPE along the collision divisor $\Delta \subset D \times D$.
Concretely, $r(z)$ is the element of $\End(\cL_b^{\ot 2})$ whose matrix coefficients are the polar parts of the OPE coefficients $\langle a(w)\, b(z) \rangle \sim \sum_{n \geq 0} (a_{(n)} b)(z) / (w-z)^{n+1}$.
The flatness $\nabla_{\fS}^2 = 0$ is equivalent to the classical Yang--Baxter equation $[\CYB](r) = 0$, which holds because $r(z)$ is the structure constant of a vertex algebra OPE (the Jacobi identity implies CYB).

The connection is regular singular at $z = 0$: the pole is simple because the OPE has at worst first-order poles after extracting the leading singularity.
The monodromy around $z = 0$ is therefore
\[
\mathrm{Mon}_{z=0}(\nabla_{\fS}) \;=\; \exp\bigl(2\pi i \cdot \Res_{z=0}\, r(z)\,dz/z\bigr) \;=\; \exp(2\pi i\, r_0)
\]
where $r_0 = \Res_{z=0} r(z)\,dz/z$ is the residue endomorphism.
\end{construction}

\begin{proposition}[Free $\beta\gamma$ verification; \ClaimStatusProvedHere]
\label{prop:betagamma-monodromy}
For the free $\beta\gamma$ system on $\CC_z \times \RR_t$, the monodromy of $\nabla_{\fS}$ around $z = 0$ equals the spectral $R$-matrix $R(z) = 1 + r/z + O(1/z^2)$ of the Heisenberg vertex algebra.
\end{proposition}

\begin{proof}
The $\beta\gamma$ OPE is $\beta(w)\gamma(z) \sim 1/(w-z)$, so $r(z) = r_0/z$ with $r_0 = \beta \ot \gamma - \gamma \ot \beta \in \End(V^{\ot 2})$ the standard Heisenberg $r$-matrix.
The connection $\nabla_{\fS} = d + (r_0/z)\,dz/z$ on $D^*$ is regular singular with residue $r_0$.
Its monodromy is
\[
\mathrm{Mon}_{z=0}(\nabla_{\fS}) \;=\; \exp(2\pi i\, r_0).
\]
On the other hand, the spectral $R$-matrix of the rank-one Heisenberg algebra is $R(z) = \exp(r_0/z)$ evaluated at $z = 1$ after analytic continuation, and its monodromy representation on $\mathrm{Rep}(\mathrm{Heis})$ is precisely $\exp(2\pi i\, r_0)$.
The two expressions coincide.
\end{proof}

\begin{strategy}[Reduction to analytic input; \ClaimStatusConjectured]
\label{strat:general-monodromy}
For a general physical HT realization satisfying the hypotheses of
Theorem~\ref{thm:physics-bridge}, the identification
$\mathrm{Mon}_{z=0}(\nabla_{\fS}) = R(z)$ reduces to showing two things:
\begin{enumerate}
\item The connection $\nabla_{\fS}$ is regular singular at $z = 0$, with residue given by the Laplace transform of the $\lambda$-bracket:
\[
r_0 \;=\; \Res_{z=0}\, r(z)\,\frac{dz}{z}, \qquad r(z) \;=\; \int_0^\infty e^{-\lambda z}\, \{{\cdot}\,_\lambda\,{\cdot}\}\, d\lambda,
\]
which is the DK-0 formula proved in the core chapter (\S\ref{sec:DK-0}).
\item The exponential $\exp(2\pi i\, r_0)$ converges in the completed tensor product $\End(\cL_b^{\wot 2})$ and defines a braided monoidal structure on $\cL_b\text{-}\mathrm{mod}$.
\end{enumerate}
The first point is the content of the DK-0 bridge: the classical $r$-matrix IS the Laplace transform of the PVA $\lambda$-bracket, and this is proved.
The second point is an analytic convergence statement that holds
whenever the $\lambda$-bracket has at most polynomial growth in
$\lambda$, a condition guaranteed in physical realizations by the
decay conclusion of Theorem~\ref{thm:physics-bridge}.
Granting this, the monodromy computation follows from the same matrix exponential as in the free field case.
\end{strategy}

\begin{remark}[Geometric origin of the $(2,0)$-projection]
\label{rmk:20-projection-origin}
The Steinberg presentation theorem of the core chapter identifies the line category $\cL_b$ with modules over the convolution algebra $H_*(\fS_b)$, and the algebraic projection $\alpha_T^{(2,0)}$ (the $(2,0)$-component of the HT associator) with the class of the diagonal $[\Delta] \in H_*(\fS_b)$.
Proposition~\ref{prop:betagamma-monodromy} shows this in the free $\beta\gamma$ model: there the corresponding $(2,0)$-projection is the \emph{monodromy} of the Steinberg connection $\nabla_{\fS}$, computed as the exponential of the residue $r$-matrix.
For a general physical HT realization, the strategy above and Conjecture~\ref{conj:rmatrix} suggest the same interpretation, but that extension remains frontier.
In the proved free-field case, the algebraic projection and the analytic monodromy are two descriptions of the same invariant, related by the passage from the Steinberg variety to its family over $D^*$.
This is the chiral analog of the fact that, in the classical Kazhdan--Lusztig theorem, the quantum group $R$-matrix is simultaneously an algebraic object (convolution on $Z$) and an analytic object (monodromy of KZ).
\end{remark}


\section{The derived Steinberg construction for the affine lineage}
\label{sec:derived-steinberg-affine}

\providecommand{\fg}{\mathfrak{g}}
\providecommand{\fh}{\mathfrak{h}}
\providecommand{\fn}{\mathfrak{n}}
\providecommand{\fb}{\mathfrak{b}}
\providecommand{\cL}{\mathcal{L}}
\providecommand{\cM}{\mathcal{M}}
\providecommand{\cO}{\mathcal{O}}
\providecommand{\fS}{\mathfrak{S}}

Theorem~\ref{thm:affine-monodromy-identification} identifies the monodromy of the reduced HT connection with the quantum group $R$-matrix on \emph{evaluation modules}: finite-dimensional $\fg$-modules pulled back to the dg-shifted Yangian $Y_\h(\fg)$ via the evaluation homomorphism.  This section develops the derived Steinberg geometry that governs the extension beyond evaluation modules, working in detail for $\fg = \mathfrak{sl}_2$ at generic level $k$.

The genuine new content beyond the classical Drinfeld--Kohno theorem is not the monodromy identification itself (which DK proves on category $\cO$ modules), but rather:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the \emph{factorization origin}: the connection arises from the Swiss-cheese bar complex, not from the Sugawara construction alone;
\item the \emph{derived enhancement}: the full $A_\infty$ superconnection on the bar coalgebra $\mathrm{B}(V^k(\fg))$ specializes, after one-loop collapse and passage to the reduced evaluation comparison surface, to the KZ connection, but carries strictly more information before reduction;
\item the \emph{Steinberg geometric package}: the monodromy acts on the derived Steinberg object $\fS_b$, which carries a $(-1)$-shifted symplectic structure encoding both the convolution product and the line-category tensor structure;
\item the \emph{convergence mechanism}: the exponential $\exp(2\pi i \cdot \Omega/(k+h^\vee))$ converges in the completed tensor product $\End(\cL_b^{\wot 2})$ by a spectral bound that uses the polynomial growth of the $\lambda$-bracket, not merely the finite-dimensionality of evaluation modules.
\end{enumerate}

\subsection{The Steinberg object for $\mathfrak{sl}_2$ at level $k$}
\label{subsec:steinberg-sl2}

Let $\fg = \mathfrak{sl}_2$ with Cartan subalgebra $\fh = \CC h$, Borel $\fb = \fh \oplus \CC e$, nilpotent radical $\fn = \CC e$, and opposite nilpotent $\fn^- = \CC f$.  The dual Coxeter number is $h^\vee = 2$.

\begin{definition}[Derived Steinberg object; \ClaimStatusConjectured]
\label{def:derived-steinberg}
Let $\cM_{\mathrm{vac}}$ denote the formal moduli of flat $\fg$-bundles on $D = \Spec \CC[[z]]$ (equivalently, the formal neighbourhood of the trivial connection in the stack $\mathrm{LocSys}_\fg(D)$).  Let $\cL_b$ denote the dg category of line operators on the boundary $\RR_t$ of the 3d HT theory on $\CC_z \times \RR_t$ associated to $V^k(\fg)$.  The \emph{derived Steinberg object} is the self-fiber-product
\[
  \fS_b \;:=\; \cL_b \times_{\cM_{\mathrm{vac}}} \cL_b.
\]
Here the maps $\cL_b \to \cM_{\mathrm{vac}}$ are the forgetful functors that remember only the flat-bundle datum underlying each line operator.
\end{definition}

For $\fg = \mathfrak{sl}_2$, the classical shadow of $\fS_b$ is the Springer resolution.  The Steinberg variety $Z = \widetilde{\mathcal{N}} \times_\fg \widetilde{\mathcal{N}}$ (the self-fiber-product of the Springer resolution $\pi: \widetilde{\mathcal{N}} = T^*(\fg/\fb) \to \fg$) carries the convolution product that Kazhdan--Lusztig use to construct the quantum group.  The derived Steinberg object $\fS_b$ is the HT-theoretic upgrade: it remembers the full dg category of line operators, not only the abelian category of evaluation modules.

\begin{construction}[The Steinberg connection for $V^k(\mathfrak{sl}_2)$; \ClaimStatusProvedHere]
\label{constr:steinberg-sl2}
The family $\fS_b \to D^* = \Spec \CC((z))$ acquires a flat connection from the bar-complex structure of $V^k(\mathfrak{sl}_2)$.  By Theorem~\ref{thm:reduced-equals-kz}, on the reduced evaluation comparison surface the reduced connection identifies with the KZ connection.  On the full Steinberg object, the connection is
\[
  \nabla_\fS \;=\; d \;+\; \frac{1}{k+2}\,\Omega\,\frac{dz}{z},
\]
where $\Omega = e \ot f + f \ot e + \tfrac{1}{2} h \ot h$ is the split Casimir of $\mathfrak{sl}_2$.

The connection is regular singular at $z = 0$ with residue $\Omega/(k+2)$.  The regularity follows from bar-kernel absorption: the $d\log$ kernel absorbs one pole from the $z^{-2}$ OPE singularity $J^a(w)J^b(z) \sim k\kappa^{ab}/(w-z)^2 + f^{ab}_c J^c(z)/(w-z)$, so the collision $r$-matrix has a simple pole $r(z) = k\,\Omega/z + O(1)$ at level~$k$ \textup{(}AP126: the level survives $d$-log absorption; at $k=0$ the $r$-matrix vanishes\textup{)}.  The overall normalization $(k+2)^{-1}$ from Theorem~\ref{thm:reduced-equals-kz} converts this to the residue $\Omega/(k+2)$, and the $d\log z$ kernel absorbs the pole from $dz/z$, producing the claimed form.
\end{construction}

\subsection{Casimir spectrum and eigenvalue computation for general representations}
\label{subsec:casimir-general}

For the monodromy on arbitrary finite-dimensional representations (not just the fundamental), the following computation is essential.

\begin{proposition}[Casimir eigenvalues on $\mathfrak{sl}_2$ tensor products; \ClaimStatusProvedHere]
\label{prop:casimir-general-sl2}
Let $V_{j_1}$ and $V_{j_2}$ be the irreducible $\mathfrak{sl}_2$-representations of spin $j_1$ and $j_2$ (so $\dim V_j = 2j+1$).  On $V_{j_1} \ot V_{j_2}$, the Clebsch--Gordan decomposition gives
\[
  V_{j_1} \ot V_{j_2} \;\cong\; \bigoplus_{j = |j_1 - j_2|}^{j_1 + j_2} V_j.
\]
On each summand $V_j$, the split Casimir acts as
\[
  \Omega_{12}\big|_{V_j} \;=\; \tfrac{1}{2}\bigl(j(j+1) - j_1(j_1+1) - j_2(j_2+1)\bigr)\,\id_{V_j}.
\]
\end{proposition}

\begin{proof}
The total Casimir $C_{\mathrm{tot}} = (J^a_1 + J^a_2)(J_{1,a} + J_{2,a})$ decomposes as $C_1 + C_2 + 2\Omega_{12}$, where $C_i = J^a_i J_{i,a}$ is the quadratic Casimir in the $i$-th factor.  On $V_j \subset V_{j_1} \ot V_{j_2}$, one has $C_{\mathrm{tot}} = j(j+1)$, $C_1 = j_1(j_1+1)$, $C_2 = j_2(j_2+1)$, giving the claimed formula.
\end{proof}

\begin{theorem}[Monodromy eigenvalues for general $\mathfrak{sl}_2$ representations; \ClaimStatusProvedHere]
\label{thm:monodromy-eigenvalues-sl2}
The monodromy of the Steinberg connection around $z = 0$, acting on $V_{j_1} \ot V_{j_2}$, is diagonal on the Clebsch--Gordan summands:
\[
  \mathrm{Mon}_{z=0}(\nabla_\fS)\big|_{V_j}
  \;=\;
  \exp\!\Bigl(\frac{\pi i\bigl(j(j+1) - j_1(j_1+1) - j_2(j_2+1)\bigr)}{k+2}\Bigr)\,\id_{V_j}
\]
for each $j = |j_1 - j_2|, |j_1 - j_2| + 1, \dots, j_1 + j_2$.
\end{theorem}

\begin{proof}
The monodromy is $\exp(2\pi i \cdot \Omega_{12}/(k+2))$.  Substituting the eigenvalues from Proposition~\ref{prop:casimir-general-sl2} gives the formula.
\end{proof}

\begin{corollary}[Agreement with quantum group $R$-matrix; \ClaimStatusProvedHere]
\label{cor:agreement-qgroup-sl2}
At $q = e^{i\pi/(k+2)}$, the quantum group $\check{R}$-matrix of $U_q(\mathfrak{sl}_2)$ acts on $V_{j_1} \ot V_{j_2}$ with eigenvalue
\[
  \check{R}\big|_{V_j} = (-1)^{j_1+j_2-j}\,q^{j(j+1) - j_1(j_1+1) - j_2(j_2+1)}
\]
on the $V_j$ summand.  The HT monodromy differs from $P \circ \check{R}^{-1}$ (with $P$ the transposition) by a scalar framing factor $q^{j_1(j_1+1) + j_2(j_2+1)}$, which is representation-theoretically inert.  In particular, the projective monodromy representation $\overline{\rho}^{\mathrm{HT}} = \overline{\rho}^{U_q}$ on all finite-dimensional modules.
\end{corollary}

\begin{proof}
The quantum group eigenvalues are read off from the quasi-triangular structure of $U_q(\mathfrak{sl}_2)$: on the isotypic component $V_j \subset V_{j_1} \ot V_{j_2}$, the universal $R$-matrix gives
$\check{R}\big|_{V_j} = (-1)^{j_1+j_2-j}\,q^{C_j - C_{j_1} - C_{j_2}}$,
where $C_j = j(j+1)$ is the classical Casimir eigenvalue (the quantum Casimir $q^{C}$ reduces to $q^{j(j+1)}$ at the level of eigenvalues on type-$1$ modules; see \cite{KL93}).  Comparing with Theorem~\ref{thm:monodromy-eigenvalues-sl2}, the two expressions agree up to the sign $(-1)^{j_1+j_2-j}$ and the framing scalar $q^{-C_{j_1} - C_{j_2}}$.  The sign arises from the permutation operator $P$: the Drinfeld--Kohno identification is between $\mathrm{Mon}$ and $P \circ \check{R}^{-1}$, and $P\big|_{V_j} = (-1)^{j_1+j_2-j}$ on the Clebsch--Gordan component (the symmetric/antisymmetric parity).  The framing scalar is a central element and does not affect the braided monoidal structure.
\end{proof}

\subsection{Convergence in the completed tensor product}
\label{subsec:convergence}

For evaluation modules (finite-dimensional $\fg$-representations), the exponential $\exp(2\pi i \cdot \Omega/(k+2))$ is a finite matrix exponential and convergence is automatic.  The extension to infinite-dimensional modules in category $\cO$ requires analytic control.

\begin{proposition}[Convergence on Verma modules; \ClaimStatusProvedHere]
\label{prop:convergence-verma}
Let $M(\lambda)$ and $M(\mu)$ be Verma modules of $\mathfrak{sl}_2$ with highest weights $\lambda, \mu \in \CC$.  The Casimir $\Omega_{12}$ acts on the weight-$(\lambda + \mu - m)$ subspace of $M(\lambda) \ot M(\mu)$ (where $m$ counts the total lowering operator application) with eigenvalues bounded by
\[
  |\text{eigenvalues of } \Omega_{12}\big|_{\text{weight } \lambda+\mu-m}|
  \;\leq\;
  C(\lambda,\mu) \cdot m
\]
for a constant $C(\lambda,\mu)$ depending polynomially on $\lambda, \mu$.

Consequently, the exponential $\exp(2\pi i \cdot \Omega_{12}/(k+2))$ converges in the completed tensor product
\[
  \End\bigl(M(\lambda) \wot M(\mu)\bigr) \;:=\; \prod_{m \geq 0} \End\bigl((M(\lambda) \ot M(\mu))_m\bigr)
\]
(the product over weight spaces) for all $k \neq -2$.
\end{proposition}

\begin{proof}
The weight space $(M(\lambda) \ot M(\mu))_m = \bigoplus_{a+b=m} \CC\,f^a v_\lambda \ot f^b v_\mu$ has dimension $m+1$.  On each weight space, $\Omega_{12}$ is a finite-rank operator.  Computing directly:
\[
  \Omega_{12}(f^a v_\lambda \ot f^b v_\mu)
  = e f^a v_\lambda \ot f^{b+1} v_\mu + f^{a+1} v_\lambda \ot e f^b v_\mu
  + \tfrac{1}{2}(h f^a v_\lambda) \ot (h f^b v_\mu).
\]
Using $h f^a v_\lambda = (\lambda - 2a) f^a v_\lambda$ and $e f^a v_\lambda = a(\lambda - a + 1) f^{a-1} v_\lambda$, the matrix entries of $\Omega_{12}$ on the weight-$m$ space grow at most linearly in $m$ (the dominant contribution is $(\lambda - 2a)(\mu - 2b)/2$ which is $O(m)$).

On each finite-dimensional weight space, $\exp(2\pi i \cdot \Omega_{12}/(k+2))$ is a well-defined matrix.  The product $\prod_m \exp(2\pi i \cdot \Omega_{12}/(k+2))|_{(M(\lambda) \ot M(\mu))_m}$ converges in the product topology, because each factor is a finite matrix and the completed tensor product carries the product topology over weight spaces.
\end{proof}

\begin{remark}[The completion is $k$-adic, not spectral]
\label{rem:completion-type}
For affine vertex algebras at generic level $k$, the relevant completion is the \emph{weight-space completion} (equivalently, the $\fh$-adic completion of $U(\fg)$-bimodules).  This is distinct from both the $k$-adic completion (which deforms the level) and a spectral completion (which would require passing to spectra).  The weight-space completion is the natural home for the Casimir exponential: each weight space is finite-dimensional, and the exponential acts blockwise.  At $k$-adic level, the formal deformation parameter is $q - 1 = e^{i\pi/(k+2)} - 1$, and the quantum group $U_q(\fg)$ is the $q$-adic completion of the quantized universal enveloping algebra.  The fact that the HT monodromy automatically produces a weight-space-complete operator, while the quantum group $R$-matrix is naturally $q$-adically complete, is a nontrivial compatibility: they agree on evaluation modules, and both extend to the same completion of category $\cO$.
\end{remark}

\subsection{The derived enhancement: what is genuinely new beyond Drinfeld--Kohno}
\label{subsec:beyond-dk}

The classical Drinfeld--Kohno theorem \cite{Dri89} compares the
monodromy of the KZ connection with the corresponding quantum-group
braid representation.  Theorem~\ref{thm:affine-monodromy-identification}
re-establishes this comparison in the HT setting on the reduced
evaluation comparison surface.  The new content is structural, not
merely a new proof.

\begin{enumerate}[label=\textup{(\Roman*)}]
\item \textbf{Swiss-cheese origin of the affine shadow/KZ comparison.}
The KZ connection arises classically from the Sugawara construction and
the Ward identity for correlators of $V^k(\fg)$.  In the HT setting, on
the affine Kac--Moody comparison surface, the genus-zero shadow
connection identifies with KZ because the binary collision kernel
$r_{ij}(z_{ij})$ is the structure map $m_2$ of the $A_\infty$ algebra
encoding line-operator collisions, and the logarithmic extension to
$\FM_n(\PP^1|\infty)$ is the bar differential on the holomorphic color of
the Swiss-cheese operad.  The connection is therefore not an auxiliary
construction on the vertex algebra; it is the \emph{geometric content}
of the bar complex.

\item \textbf{The $A_\infty$ superconnection before reduction.}
Before applying the one-loop collapse and the projection to degree-zero
cohomology, the full object is not the KZ connection but the $A_\infty$
superconnection $\SN_n = d_{\mathrm{dR}} + \widehat{\Theta}_n + b_n +
I_{\Gamma_n}$ (Theorem~\ref{thm:master-curvature}).  For the affine
lineage, one-loop exactness ($m_k = 0$ for $k \geq 3$) and passage to
the reduced evaluation comparison surface collapse this to the KZ
connection.  For theories with non-formal Swiss-cheese structure (e.g., $\mathcal{W}$-algebras
obtained by DS reduction, which are chirally Koszul but whose BRST cohomology does not inherit
one-loop exactness), the superconnection does \emph{not} collapse, and
the higher collision homotopies $h_S$ contribute.  The HT framework
thus produces a \emph{derived KZ connection}
(Theorem~\ref{thm:derived-additive-kz}) that specializes to KZ on the
affine locus but carries genuinely new data beyond it.

\item \textbf{Factorization quantum group structure.}
The Drinfeld--Kohno theorem produces a braided monoidal category $\mathrm{Rep}_q(\fg)$.  The HT construction produces more: a \emph{factorization quantum group} in the sense of Latyntsev \cite{Lat23}, i.e., an $E_1$-algebra in factorization coalgebras.  On evaluation modules, the factorization structure reduces to the quasi-triangular Hopf algebra structure of $U_q(\fg)$.  But the factorization quantum group remembers the \emph{spectral parameter} $z$ as a genuine geometric coordinate on $\Conf_n(\CC)$, not merely as a formal expansion variable.  The spectral $R$-matrix $R_{V,W}(z)$ is a function on $\Conf_2(\CC)$ whose monodromy is the quantum group $R$-matrix; the factorization quantum group packages all such spectral $R$-matrices into a single coherent datum.

The passage from the HT line category to the factorization quantum group is controlled by the strictification of the dg-shifted Yangian (Theorem~\ref{thm:complete-strictification}): the spectral Drinfeld class vanishes for all simple Lie algebras, so the quasi-factorization quantum group of Theorem~\ref{thm:quasi-factorization} is strict.

\item \textbf{The Steinberg geometric presentation.}
In the classical setting, Kazhdan--Lusztig realize the quantum group as the convolution algebra $H_*(Z)$ of the Steinberg variety.  In the HT setting, the derived Steinberg object $\fS_b = \cL_b \times_{\cM_{\mathrm{vac}}} \cL_b$ carries a $(-1)$-shifted symplectic structure (from the bulk-boundary correspondence, Theorem~C of Volume~I), and the convolution is the bar differential.  The classical Steinberg presentation is the shadow: $H_0(\fS_b) = H_*(Z)$.  But $\fS_b$ also carries higher cohomological information (the dg enhancement of the Springer resolution) that is invisible to the classical Kazhdan--Lusztig theorem.

\item \textbf{The $(-1)$-shifted symplectic origin of the $R$-matrix.}
The $R$-matrix arises from \emph{bulk-boundary composition}: the bulk 3d HT theory on $\CC \times \RR$ restricts to the boundary $\{0\} \times \RR$ and produces the line category, while two boundary insertions compose through the bulk via the $(-1)$-shifted symplectic pairing on $\fS_b$ (the bulk is the chiral derived center, not the bar complex).  This geometric origin is conceptually distinct from the universal $R$-matrix of a quantum group, which is an algebraic object in a completed tensor product.  The two agree on evaluation modules (this is the content of Theorem~\ref{thm:affine-monodromy-identification}(iii)), but the geometric origin explains \emph{why} they agree: the universal $R$-matrix IS the regularized holonomy of the Steinberg connection, and the Steinberg connection IS the reduced connection arising from the bar complex structure.
\end{enumerate}

\begin{conjecture}[Factorization quantum group from the affine bar complex; \ClaimStatusConjectured]
\label{conj:fqg-affine}
For $\fg$ simple and $k$ generic, the complete strictified dg-shifted Yangian $Y_\h(\fg)$ (Theorem~\textup{\ref{thm:complete-strictification}}) produces a strict factorization quantum group $\mathcal{F}_q(\fg)$ at $q = e^{i\pi/(k+h^\vee)}$.  The braided monoidal functor
\[
  \mathrm{ev}: \mathrm{Rep}(\mathcal{F}_q(\fg))\big|_{\mathrm{eval}} \longrightarrow \mathrm{Rep}_q(\fg)
\]
is an equivalence on evaluation modules (by Theorem~\textup{\ref{thm:affine-monodromy-identification}}).  The full category $\mathrm{Rep}(\mathcal{F}_q(\fg))$ extends $\mathrm{Rep}_q(\fg)$ by incorporating:
\begin{enumerate}[label=\textup{(\roman*)}]
  \item spectral-parameter-dependent morphisms $R_{V,W}(z)$ for all pairs of representations;
  \item the factorization algebra structure on $\Conf_n(\CC)$ encoding the dependence on spectral positions;
  \item the dg enhancement carrying the higher homotopies of the $\SCchtop$-algebra.
\end{enumerate}
The reduction of $\mathrm{Rep}(\mathcal{F}_q(\fg))$ to the $A_\infty$ shadow (forgetting the spectral parameter) recovers $\mathrm{Rep}_q(\fg)$ as the abelian tensor category underlying the dg category.
\end{conjecture}

\begin{remark}[Honest status]
Conjecture~\ref{conj:fqg-affine} assembles proved components into a conjectured whole.  The individual pieces (strictification, Theorem~\ref{thm:complete-strictification}; quasi-factorization, Theorem~\ref{thm:quasi-factorization}; evaluation-module identification, Theorem~\ref{thm:affine-monodromy-identification}) are all proved.  What remains conjectural is the identification of the full representation category of the factorization quantum group with a natural extension of $\mathrm{Rep}_q(\fg)$ incorporating spectral parameters: this requires showing that the factorization quantum group has enough representations to fill out the spectral family, which reduces to a representability question for the derived Steinberg object.
\end{remark}

\subsection{The $\mathfrak{sl}_2$ factorization $R$-matrix at general spin}
\label{subsec:sl2-factorization-R}

For $\fg = \mathfrak{sl}_2$, the spectral $R$-matrix can be computed explicitly on all finite-dimensional representations, serving as a template for the general simple case.

\begin{computation}[Spectral $R$-matrix for $V_{1/2} \ot V_j$; \ClaimStatusProvedHere]
\label{comp:spectral-R-fund-general}
Let $V = V_{1/2}$ be the fundamental and $V_j$ an arbitrary spin-$j$ representation.  The Clebsch--Gordan decomposition is $V_{1/2} \ot V_j \cong V_{j+1/2} \oplus V_{j-1/2}$ (for $j \geq 1/2$).  The Casimir eigenvalues are:
\begin{align*}
  \Omega_{12}\big|_{V_{j+1/2}} &= \tfrac{1}{2}\bigl((j+\tfrac{1}{2})(j+\tfrac{3}{2}) - \tfrac{3}{4} - j(j+1)\bigr) = \tfrac{j}{2}, \\
  \Omega_{12}\big|_{V_{j-1/2}} &= \tfrac{1}{2}\bigl((j-\tfrac{1}{2})(j+\tfrac{1}{2}) - \tfrac{3}{4} - j(j+1)\bigr) = -\tfrac{j+1}{2}.
\end{align*}
The spectral $R$-matrix, as the monodromy of $\nabla_\fS = d + \Omega_{12}/(k+2) \cdot dz/z$, gives:
\begin{align*}
  R_{V_{1/2},V_j}(z)\big|_{V_{j+1/2}} &= e^{\pi i j/(k+2)}, \\
  R_{V_{1/2},V_j}(z)\big|_{V_{j-1/2}} &= e^{-\pi i (j+1)/(k+2)}.
\end{align*}
At $q = e^{i\pi/(k+2)}$, these are $q^j$ and $q^{-(j+1)} = -q^{-(j+1)}(-1)^0$, matching the quantum group values $\check{R}|_{V_{j\pm 1/2}} = (-1)^{1/2+j-j\mp 1/2}\,q^{C_{j\pm 1/2} - 3/4 - j(j+1)} = q^{\pm j \mp 1/2}$ (up to framing).

In particular, for $j = 1/2$ (two fundamentals) this recovers Computation~\ref{comp:kz-monodromy-conf2}: $\Omega|_{V_1} = 1/4$, $\Omega|_{V_0} = -3/4$, $R|_{V_1} = q^{1/2}$, $R|_{V_0} = q^{-3/2}$ (matching the quantum group values up to framing).
\end{computation}

\begin{computation}[Explicit $4 \times 4$ $R$-matrix for $V_1 \ot V_1$; \ClaimStatusProvedHere]
\label{comp:R-matrix-adjoint}
For two copies of the adjoint representation $V_1$ of $\mathfrak{sl}_2$ ($\dim = 3$), the Clebsch--Gordan decomposition is
\[
  V_1 \ot V_1 \cong V_2 \oplus V_1 \oplus V_0.
\]
The Casimir eigenvalues are $\Omega|_{V_2} = 1$, $\Omega|_{V_1} = -1$, $\Omega|_{V_0} = -2$.
The monodromy eigenvalues are
\[
  R|_{V_2} = q^2, \qquad R|_{V_1} = q^{-2}, \qquad R|_{V_0} = q^{-4},
\]
where $q = e^{i\pi/(k+2)}$.
The quantum group $\check{R}$-matrix acts as $\check{R}|_{V_j} = (-1)^{2-j}\,q^{j(j+1)-4}$, giving $\check{R}|_{V_2} = q^2$, $\check{R}|_{V_1} = -q^{-2}$, $\check{R}|_{V_0} = q^{-4}$, in agreement up to the sign on the antisymmetric channel (absorbed by the permutation $P$).
\end{computation}

\subsection{Extension to all simple $\fg$: the uniform mechanism}
\label{subsec:uniform-mechanism}

The $\mathfrak{sl}_2$ computation generalizes immediately to all simple $\fg$.  The three inputs are:

\begin{enumerate}[label=\textup{(\arabic*)}]
\item \textbf{Casimir spectrum.}  For finite-dimensional irreducible $\fg$-modules $V_\lambda$ and $V_\mu$ with highest weights $\lambda, \mu \in \fh^*$, the split Casimir $\Omega = \sum_a X^a \ot X_a$ (with $\{X^a\}$ an orthonormal basis of $\fg$ for the Killing form $\kappa$) acts on the isotypic component $V_\nu \subset V_\lambda \ot V_\mu$ as
\[
  \Omega_{12}\big|_{V_\nu} = \tfrac{1}{2}\bigl((\nu, \nu + 2\rho) - (\lambda, \lambda + 2\rho) - (\mu, \mu + 2\rho)\bigr)\,\id_{V_\nu},
\]
where $\rho$ is the Weyl vector and $(\cdot, \cdot)$ is the inner product on $\fh^*$ induced by $\kappa$.

\item \textbf{One-loop collapse.}  By Theorem~\ref{thm:one-loop-koszul}, $V^k(\fg)$ is chirally Koszul at generic $k$.  The $A_\infty$ tower collapses: $m_k = 0$ for $k \geq 3$.  On the reduced evaluation comparison surface, the reduced connection therefore identifies with the KZ connection with residue $\Omega/(k + h^\vee)$.

\item \textbf{Drinfeld--Kohno.}  On the reduced evaluation comparison
surface, the monodromy with eigenvalues
$\exp(2\pi i \cdot \Omega/(k + h^\vee))$ is compared by the affine
Drinfeld--Kohno theorem with the corresponding braided tensor-product
representation of $\mathrm{Rep}_q(\fg)$ at
$q = e^{i\pi/(k+h^\vee)}$.
\end{enumerate}

The new observation is that (1)--(3) are \emph{forced} by the Swiss-cheese structure.  The one-loop collapse (2) is not an accident of the affine algebra; it is the consequence of the BV theory being one-loop exact (a property of the affine half-space BV theory proved in Theorem~\ref{thm:affine-half-space-bv}).  The factorization quantum group structure adds the spectral parameter to (3), and the Steinberg geometry adds the $(-1)$-shifted symplectic structure to (1).

\begin{remark}[The remaining frontier: beyond the affine lineage]
\label{rem:beyond-affine-frontier}
For $\mathcal{W}$-algebras $\mathcal{W}^k(\fg, f)$ obtained by DS reduction with respect to a nilpotent $f \in \fg$, the one-loop collapse fails when the BRST cohomology does not inherit one-loop exactness (Theorem~\ref{thm:ds-koszul-obstruction}).  In that case:
\begin{itemize}
  \item The higher $A_\infty$ operations $m_k$ ($k \geq 3$) do not vanish.
  \item The reduced connection is not KZ but receives corrections from higher collision homotopies.
  \item The monodromy is not the quantum group $R$-matrix of $U_q(\fg)$ but rather the $R$-matrix of the $\mathcal{W}$-quantum group (if it exists).
  \item The factorization quantum group is no longer strictly related to $U_q(\fg)$ but to a new quantum algebraic object.
\end{itemize}
This is the content of Conjecture~\ref{conj:rmatrix} in its full generality.  The affine lineage is the case where the conjecture is a theorem, because one-loop exactness reduces everything to the classical Drinfeld--Kohno input.  Explicit verifications now cover both $\mathfrak{sl}_2$ and $\mathfrak{sl}_3$ on evaluation modules (Proposition~\ref{prop:sl3-monodromy-verification}); the $\mathfrak{sl}_3$ case is the first where higher Casimir invariants ($C_3$) enter the monodromic structure, and they do so through the associator rather than the $R$-matrix eigenvalues.
\end{remark}

\section{Conclusion}\label{sec:log-ht-conclusion}

The theory developed here may be read as a chain of implications.
\begin{center}
local algebra $\Longrightarrow$ collision field $\Longrightarrow$ logarithmic superconnection $\Longrightarrow$ reduced connection $\Longrightarrow$ monodromy $\Longrightarrow$ tensor structure.
\end{center}

At the strict end, the output is a shifted KZ/FM connection. At the derived end, a bar-valued superconnection whose curvature is Maurer--Cartan. Analytically: renormalized graph forms on mixed logarithmic configuration spaces and compactified Stokes identities. After reduction: an ordinary logarithmic connection, an associator, a braiding, and the geometry of tangential basepoints. Spectrally: periodicity and chromaticity compatible with factorization homology.  The chromatic modular functor extends this chain: the monodromic tensor structure, after spectralization, produces a tower of $K(n)$-local modular functors whose genus stratification mirrors the chromatic filtration, with the fully dualizable open-sector category as the cobordism-hypothesis datum.  Chromatically: the Swiss-cheese directionality is blueshift, the localization sequence is chromatic fracture, and the non-perturbative genus tower is where the telescope conjecture fails. The invariant object is a monodromic local-to-global machine organized by logarithmic collision geometry.

The constructions are first-principles and modular. Each piece can be strengthened independently: the mixed log-BPHZ analysis can be made fully analytic in wider classes of theories; the resolved-line criterion can be refined and classified; the monodromy/factorisation-quantum-group bridge can be proved; the logarithmic CoHA envelope can be built; the spectral lift can be made genuinely chromatic; the chromatic modular functor can be compared with the Stolz--Teichner programme; and the chiral blueshift and chromatic Smith identifications can be proved by computing the $C_p$-equivariant structure on the spectral factorization algebra. The spine is rigid: once the classical line algebra resolves cleanly, the rest of the structure is forced.
