\providecommand{\Tr}{\operatorname{Tr}}
\providecommand{\Def}{\operatorname{Def}}
\label{ch:modular-pva-quantization}%
\label{chap:modular-pva}% phantom: referenced from frontier chapters
\label{def:complete-modular-bar}%

%% Synopsis: three layers --- (i) external input from the literature,
%% (ii) formal algebraic results proved here given a modular bar datum,
%% (iii) KZ-locus comparisons with the Khan--Zeng HT Poisson sigma model.
%% Trees govern chirality; loops govern modularity.

\section{Status conventions and scope}

\begin{convention}[Three levels of assertion]
\label{conv:three-levels}
\begin{enumerate}[leftmargin=2.4em]
\item \textbf{External input:} Khan--Zeng \cite{KZ25}, Gui--Li--Zeng \cite{GLZ22}, Francis--Gaitsgory \cite{FG12}, Costello--Dimofte--Gaiotto \cite{CDG20}, Gaiotto--Kulp--Wu \cite{GKW25}.
\item \textbf{Formal algebraic results:} proved here given a modular bar datum.
\item \textbf{KZ-locus comparisons:} link the formal algebra to the Poisson sigma model. On the finite-type freely generated finite-jet locus with inner holomorphic translation, the classical BV datum is constructed in Construction~\ref{cons:kz-bv-fields-action}; half-space perturbative quantization still requires the KZ analytic SDR package of Assumption~\ref{assum:kz-analytic-sdr-package}.
\end{enumerate}
\end{convention}

\begin{convention}[Strict models versus invariant modular deformation objects]
\label{conv:modular-pva-strict-versus-homotopy}
\index{modular deformation!strict versus homotopy}
Throughout this note, concrete coderivation dg~Lie algebras such as
$\Defmod(A_{\cl}(V))$ are chosen strict presentations. The invariant
modular deformation theory is defined only up to filtered
$L_\infty$ quasi-isomorphism. Accordingly, every Maurer--Cartan equation
written in the strict modular complex should be read as a computation in
one preferred chart on an underlying homotopy-coherent modular
deformation object $\Definfmod(\cA)$ constructed in Volume~I.
\end{convention}

\section{External input from the literature}

We record the external ingredients used below.

\subsection{Poisson vertex algebras and the 3d holomorphic-topological Poisson sigma model}

Khan--Zeng~\cite{KZ25} attach a 3d holomorphic-topological gauge theory to a freely generated PVA: gauge invariance holds iff the $\lambda$-bracket Jacobi identity holds, a Virasoro element upgrades the symmetry to fully topological, and the boundary picture on $\mathbb R_+\times \mathbb C$ is the physical source of the genus-zero quantization problem considered here.

\subsection{Quadratic duality for chiral algebras}

Gui--Li--Zeng~\cite{GLZ22} define quadratic duality for chiral algebras, prove an injective map
\[
\Hom(A,B)\hookrightarrow \MC(A^!\otimes B),
\]
show bijectivity under effectiveness hypotheses in degree zero, and in the inhomogeneous
quadratic setting introduce twisted pairs $(B,B^\circ,S)$ with curved
Maurer--Cartan equation
\[
\mu\big((S+\alpha)\boxtimes (S+\alpha)\big)=0.
\]
They note that a full homotopy/Koszul treatment parallel to the
associative story is missing; this gap motivates the present chapter.

\subsection{Chiral/factorization homotopy theory}

Francis--Gaitsgory~\cite{FG12} recast the chiral/factorization relation as chiral Koszul duality, supplying the derived ambient category for a modular refinement of disk-level duality.

\subsection{Boundary algebras, higher operations, and line operators}

Costello--Dimofte--Gaiotto~\cite{CDG20}: bulk local operators form a commutative chiral algebra with shifted Poisson bracket; boundary algebras carry $A_\infty$ structure. Gaiotto--Kulp--Wu~\cite{GKW25}: higher operations in HT perturbation theory satisfy quadratic consistency (Wess--Zumino type for BRST). Dimofte--Niu--Py~\cite{DNP25}: line operators are $A^!$-modules organized by $A_\infty$ Yang--Baxter Maurer--Cartan data.

\subsection{Analogies with deformation quantization}

Cattaneo--Felder~\cite{CF00} interpret Kontsevich deformation quantization via a topological sigma model on the disk. Tamarkin~\cite{Tam02} proves that the deformation complex of an $E_d$-algebra carries an $E_{d+1}$-structure. The upshot: PVA quantization requires a modular deformation object, not a disk-level dg Lie algebra.

\begin{remark}[The BCOV holomorphic anomaly equation as MC projection]
\label{rem:bcov-mc-pva}
\index{BCOV holomorphic anomaly equation!MC projection}
The Bershadsky--Cecotti--Ooguri--Vafa (BCOV) holomorphic anomaly
equation for Calabi--Yau topological string amplitudes $F_g$ is
the degree-$0$ genus-$g$ projection of the MC equation in
the modular convolution algebra
(Volume~I, Proposition~\ref{V1-prop:bcov-mc-projection} and
Remark~\ref{V1-rem:bcov-mc-dictionary}).
The BCOV propagator $S^{ij}$ corresponds to the genus-$1$
sewing kernel $P(\tau) = -(1/12)\,E_2(\tau)$;
the BCOV separating degeneration
$\sum D_j F_h\,D_k F_{g-h}$ corresponds to the bracket
$[\Theta,\Theta]^{(g,0)}$;
the holomorphic ambiguity corresponds to gauge freedom in
$\MC(\gAmod)$; and the Yukawa coupling $C_{ijk}$ corresponds
to the cubic shadow $\mathfrak{C}(\cA)$.
The Costello--Li quantization of BCOV theory~\cite{Costello-1705.02500v1}
makes this identification precise: the BCOV MC element is the
genus-$0$ shadow of $\Theta_\cA$ for the boundary chiral algebra
of the B-model.
The modular PVA quantization problem of this chapter is therefore
a direct generalization of the BCOV quantization problem from
Calabi--Yau targets to arbitrary chirally Koszul algebras.
\end{remark}

\section{From first principles: genus zero, loops, and the one-edge principle}

\begin{remark}[The genus-zero quantization problem as an $E_1$-to-PVA lift]
\label{rem:quantization-e1-pva-lift}
\index{PVA quantization!E1 lift@$E_1$ lift}
\index{bar-cobar resolution!PVA quantization}
The central problem of this chapter (lifting a genus-zero
Poisson vertex algebra to a quantum, genus-corrected, chiral
algebra) is precisely the problem of reversing the two-stage
projection
$T^c \xrightarrow{\mathrm{av}} \Sym^c \xrightarrow{H^\bullet}
\mathrm{PVA}$
described in Remark~\textup{\ref{rem:pva-two-stage-projection}}.
The PVA datum $V$ supplies the classical shadow: the commutative
product and $\lambda$-bracket. Quantization asks for a chain-level
$E_1$-primitive (a logarithmic $\SCchtop$-algebra $\cA$ with
$H^\bullet(\cA, Q) = V$) whose bar-cobar resolution
$\Omega(\barB(\cA)) \xrightarrow{\sim} \cA$ solves the Maurer--Cartan
equation $D\Theta + \frac{1}{2}[\Theta, \Theta] = 0$ in the
modular convolution algebra. At genus zero, this reduces to
finding a Maurer--Cartan element
$\Theta_0 \in \MC(\Def_{\mathrm{cyc}}^{(0)}(\cA))$
whose PVA shadow (via the two-stage projection) recovers~$V$.
The genus-raising primitive $D_1 = \Delta_{\mathrm{cyc}}$
(the one-edge operator of
Proposition~\ref{prop:one-edge-necessity}) then lifts $\Theta_0$ to
all genera, producing the full obstruction tower.
\end{remark}

\subsection{Filtered quadratic PVAs}

\begin{definition}[Filtered quadratic PVA]
A \emph{filtered quadratic Poisson vertex algebra} is a differential commutative algebra
freely generated by fields $u^1,\dots,u^N$ and their derivatives, together with a
$\lambda$-bracket encoded by a skew-adjoint matrix differential operator
\[
\Pi^{ab}(\partial)=\sum_{m\ge 0}\Pi^{ab}_m\,\partial^m,
\]
whose coefficients are filtered polynomials of total generator degree at most $2$.
\end{definition}

The classical $W$-algebras discussed by Khan--Zeng fit this framework, including the
classical $W_3$ example \cite{KZ25}.

\subsection{Resolved classical datum}

\begin{assumption}[Resolved classical chiral/factorization datum]
\label{assum:resolved-classical-datum}
Let $X$ be a smooth complex curve and let $V$ be a filtered quadratic PVA on $X$.
Assume there exists a cofibrant resolved classical chiral/factorization object
\[
\A=\widetilde A_{\cl}(V)
\]
whose genus-zero shadow is $V$, and which is dualizable, finite type, conilpotent,
and complete in the sense made precise below.
\end{assumption}

\begin{remark}
This assumption isolates the sole external input; the remaining constructions depend only on the modular bar datum built from $\A$.
\end{remark}

\subsection{The one-edge principle}

Taking the disk-level deformation complex and adding a genus grading does not suffice.

\begin{proposition}[Necessity of a genus-raising primitive; \ClaimStatusProvedHere]
Suppose a filtered deformation dg Lie algebra $L$ is equipped with a complete genus
filtration $F^\bullet$ and its differential preserves genus exactly. Then any genus-zero
Maurer--Cartan element $\Theta_0\in \MC(\gr_F^0 L)$ extends tautologically to a full
Maurer--Cartan element of $L$ without further obstruction.
\end{proposition}

\begin{proof}
If the differential preserves genus and the Lie bracket adds genera, then the Maurer--Cartan
equation decomposes strictly by genus. A solution in genus zero has no forcing term in
positive genus, so the same element, viewed inside the completed filtered algebra, already
solves the full equation.
\end{proof}

\begin{remark}[Trees versus loops]
Any nontrivial modular obstruction theory requires a genus-raising primitive at the chain level: the nonseparating one-edge expansion operator.
\end{remark}

\begin{remark}[The five-level genus extension hierarchy]
\label{rem:genus-extension-hierarchy-pva}
\index{genus extension hierarchy!PVA quantization context}
The genus-raising lift from $\Theta_0$ to all genera passes through
five successively stronger structural levels
(Volume~I, Theorem~\ref{V1-thm:genus-extension-hierarchy}):
\textup{(i)}~\emph{algebraic} ($D^2 = 0$ at all genera, unconditional);
\textup{(ii)}~\emph{homotopical} (bar-cobar inversion in the
coderived category $D^{\mathrm{co}}$, requires positive energy);
\textup{(iii)}~\emph{Koszul} (classical bar-cobar quasi-isomorphism,
requires PBW collapse);
\textup{(iv)}~\emph{analytic} (convergent partition functions,
requires the HS-sewing criterion);
\textup{(v)}~\emph{modular} (full modular functor, requires
compatibility with mapping class group action).
The PVA quantization problem of this chapter operates at
level~\textup{(iii)}: given a genus-$0$ Koszul datum, the
bar-cobar resolution provides a classical quasi-isomorphism,
and the genus-raising operator $D_1 = \Delta_{\mathrm{cyc}}$
lifts the solution to all genera within the Koszul
locus. Analytic convergence (level~\textup{(iv)}) is guaranteed
for the standard landscape by the HS-sewing theorem
(Volume~I, Theorem~\ref{thm:general-hs-sewing}).
\end{remark}

\section{Stable-graph modular bar data and the modular bar coalgebra}

\subsection{Stable graphs}

\begin{definition}[Connected stable graph]
A \emph{connected stable graph} $\Gamma$ consists of the following data:
\begin{enumerate}[leftmargin=2.4em]
\item a finite set $V(\Gamma)$ of vertices;
\item a finite set $\mathrm{Fl}(\Gamma)$ of flags;
\item a partition $\mathrm{Fl}(\Gamma)=\bigsqcup_{v\in V(\Gamma)}\mathrm{Fl}(v)$;
\item an involution on $\mathrm{Fl}(\Gamma)$, whose $2$-cycles are internal edges and
whose fixed points are external legs;
\item a genus label $g(v)\in \mathbb Z_{\ge 0}$ for each vertex,
\end{enumerate}
subject to the stability condition
\[
2g(v)-2+|\mathrm{Fl}(v)|>0
\qquad\text{for all }v\in V(\Gamma).
\]
Its total genus is
\[
g(\Gamma)=b_1(\Gamma)+\sum_{v\in V(\Gamma)}g(v).
\]
\end{definition}

Write $E(\Gamma)$ for the set of internal edges and
\[
\orline(\Gamma):=\det(kE(\Gamma))\otimes \det(H_1(\Gamma;k))^{-1}
\]
for the orientation line.

\begin{remark}[Orientation-line conventions]
\label{rem:orientation-line-conventions}
The Getzler--Kapranov orientation line of a stable graph~$\Gamma$
is the full determinant
$\orline(\Gamma) = \det(kE(\Gamma)) \otimes \det(H_1(\Gamma;k))^{-1}$
used above.
When vertex labels are already desuspended (as in
Example~\ref{ex:rft-heisenberg}, where the relative Feynman
transform is written with $\orline(\Gamma) = \det(H_1(\Gamma;k))$
alone), the edge factor $\det(kE(\Gamma))$ has been absorbed into
the vertex contributions via the desuspension $s$ applied to each
flag. The two conventions produce isomorphic orientation data;
we use the full form here and the reduced form in the relative
Feynman transform to match the standard references in each
context.
\end{remark}

\subsection{One-edge expansions}

Let $C$ be a reduced complete finite-type graded collection on finite sets:
\[
F\longmapsto C(F),
\]
functorial for bijections of finite sets.

\begin{definition}[One-edge expansion set]
For a finite set $F$, let $\OE(F)$ denote the set of connected stable graphs whose
external leg set is $F$ and which have exactly one internal edge. Such a graph is either:
\begin{enumerate}[leftmargin=2.4em]
\item \emph{separating}: two vertices joined by one edge;
\item \emph{nonseparating}: one vertex carrying one loop.
\end{enumerate}
\end{definition}

\begin{definition}[Modular bar datum]
\label{def:modular-bar-datum}
A \emph{modular bar datum} on $C$ consists of:
\begin{enumerate}[leftmargin=2.4em]
\item an internal differential
\[
d:C(F)\to C(F)
\]
of degree $+1$ for each finite set $F$;
\item for each $\epsilon\in \OE(F)$, a degree $+1$ map
\[
\Delta_\epsilon:
s\,C(F)\longrightarrow
\orline(\epsilon)\otimes \bigotimes_{u\in V(\epsilon)} s\,C(\mathrm{Fl}_\epsilon(u));
\]
\item the \emph{codimension-two cancellation axiom}: for every connected stable graph
$T$ with exactly two internal edges, the signed sum of the two ways of producing $T$
by successive one-edge expansions vanishes;
\item the anticommutation relation that $d$ anticommutes with every $\Delta_\epsilon$.
\end{enumerate}
\end{definition}

\begin{remark}[Verification: the Heisenberg algebra]
\label{rem:heisenberg-modular-bar-verification}
The Heisenberg algebra $\cH_k$ at genus~$1$ satisfies these axioms:
the differential from the genus-$0$ bar complex, augmented by the
curvature $\kappa(\cH_k) \cdot \omega_1 = k \cdot \omega_1$, gives a
modular bar datum with the codimension-two cancellation following from
$\partial^2 = 0$ on $\overline{\cM}_{1,n}$.
\end{remark}

\begin{remark}[Derivation of the codimension-two cancellation]
\label{rem:codim-two-derivation}
This axiom records $\partial^2 = 0$ on $\overline{\cM}_{g,n}$.
\end{remark}

\begin{remark}
Codimension-one boundary strata of $\overline{\cM}_{g,n}$ are one-edge degenerations of stable graphs; these are the primitive input.
\end{remark}

\begin{proposition}[Codimension-one boundary strata of the bordered log-FM compactification; \ClaimStatusProvedHere]
\label{prop:bordered-log-FM-strata}
The codimension-one boundary of the bordered logarithmic Fulton--MacPherson compactification $\overline{\FM}^{\mathrm{bord}}_{k,m}(X, D)$ (parametrising $k$ closed insertions in $X \setminus D$ and $m$ open insertions on boundary intervals) has exactly four types of strata:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Closed-point collisions:} a subset $S \subset \{1,\ldots,k\}$ of closed insertions collides in $X \setminus D$, producing the face $D_S \cong \FM_{k-|S|+1}(X) \times \FM_{|S|}^{\mathrm{red}}(\C)$. These contribute the bar differential $d_{\mathrm{res}}$ (OPE residues along collision divisors).
\item \textbf{Consecutive open-point collisions:} a consecutive block of open insertions on a boundary interval $I_p$ collides, producing a face $\Conf^{\mathrm{ord}}_{m-|T|+1}(I_p) \times \Conf^{\mathrm{ord}}_{|T|}(\R)$. These contribute the $A_\infty$ differential $d_{A_\infty}$ (Stasheff faces).
\item \textbf{Mixed bubbling:} a closed insertion approaches a boundary interval, producing a mixed face where the bulk operator restricts to the boundary. These contribute the bulk-to-boundary map (the closed-to-open operations of $\SCchtop$).
\item \textbf{Nodal clutching/splitting:} the curve degenerates along a node, splitting into two components glued at the node. These contribute the clutching differential $d_{\mathrm{clutch}}$ (self-sewing at genus boundaries and component splitting at nodal degenerations).
\end{enumerate}
The full modular bar differential decomposes correspondingly:
\[
d_{\mathrm{mod}} \;=\; d_{\mathrm{res}} + d_{A_\infty} + d_{\mathrm{mix}} + d_{\mathrm{clutch}}.
\]
The identity $d_{\mathrm{mod}}^2 = 0$ (at genus~$0$) or $d_{\mathrm{mod}}^2 = m_0$ (at genus~$g \geq 1$) is the content of the four types of codimension-two cancellations.
\end{proposition}

\begin{proof}
The four strata types correspond to the four kinds of degenerations in the Fulton--MacPherson--Axelrod--Singer compactification of mixed open/closed configuration spaces on bordered surfaces: internal collisions, boundary collisions, boundary approach, and nodal degeneration. Each is a codimension-one face of the compactified moduli. The decomposition of the modular differential follows by restricting the total form to each face and identifying the resulting operation. The codimension-two cancellation $d_{\mathrm{mod}}^2 = 0$ (or $= m_0$) is the boundary-of-boundary identity $\partial^2 = 0$ on manifolds with corners, combined with the Arnold cancellation (Theorem~\ref{thm:Arnold_full_proof}) for mixed corner terms.

The bordered log-FM compactification for the punctured-curve case
(open insertions on boundary intervals) is constructed in Volume~I,
\S\ref*{V1-sec:bordered-fm}
(Construction~\ref*{V1-constr:bordered-fm},
Theorem~\ref*{V1-thm:bordered-fm-properties},
Proposition~\ref*{V1-prop:four-type-boundary}).
\end{proof}

\begin{definition}[Bordered logarithmic Fulton--MacPherson cooperad]
\label{def:bordered-log-FM-cooperad}
The \emph{bordered log-FM cooperad} $\cC^{\mathrm{oc,log}}_{\mathrm{mod}}$ is the collection of chain complexes
\[
\cC^{\mathrm{oc,log}}_{\mathrm{mod}}(g, k, m) \;:=\; C_\ast\bigl(\overline{\FM}^{\mathrm{bord}}_{k,m}(\Sigma_g, D)\bigr),
\]
where $\overline{\FM}^{\mathrm{bord}}_{k,m}(\Sigma_g, D)$ is the log-FM compactification of mixed open/closed configurations on a genus-$g$ bordered stable curve with $k$ closed and $m$ open markings. The cooperad structure maps come from boundary inclusions:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Closed cocomposition:} the face $D_S$ (closed collision) gives $\cC^{\mathrm{oc,log}}_{\mathrm{mod}}(g,k,m) \to \cC^{\mathrm{oc,log}}_{\mathrm{mod}}(g, k{-}|S|{+}1, m) \otimes C_\ast(\FM_{|S|}(\C))$;
\item \emph{Open cocomposition:} consecutive open collisions give the $E_1$-cooperad structure on boundary intervals;
\item \emph{Genus cocomposition (separating):} nodal degeneration splitting the curve into two components gives $\cC^{\mathrm{oc,log}}_{\mathrm{mod}}(g, k, m) \to \cC^{\mathrm{oc,log}}_{\mathrm{mod}}(g_1, k_1, m_1) \otimes \cC^{\mathrm{oc,log}}_{\mathrm{mod}}(g_2, k_2, m_2)$ for $g_1 + g_2 = g$, $k_1 + k_2 = k$, $m_1 + m_2 = m$;
\item \emph{Genus cocomposition (non-separating):} self-sewing identifies two closed markings at a node, raising genus: $\cC^{\mathrm{oc,log}}_{\mathrm{mod}}(g, k, m) \to \cC^{\mathrm{oc,log}}_{\mathrm{mod}}(g-1, k+2, m)$. This is the sole primitive that raises genus (the $D_{\mathrm{nsep}}$ operator of Volume~I).
\end{enumerate}
The differential on $\cC^{\mathrm{oc,log}}_{\mathrm{mod}}$ encodes all four types of codimension-one strata (Proposition~\ref{prop:bordered-log-FM-strata}).
\end{definition}

\begin{definition}[Modular twisting morphism]
\label{def:modular-twisting-morphism}
Let $\cC$ be an open/closed factorization category (Definition~\ref{def:oc-factorization-category}) with open-sector category $\cC_\partial$ and bulk $Z_{\mathrm{der}}(\cC_\partial)$. A \emph{modular twisting morphism} is a degree-$+1$ map
\[
\Theta_\cC \colon \cC^{\mathrm{oc,log}}_{\mathrm{mod}} \;\longrightarrow\; \End(Z_{\mathrm{der}}(\cC_\partial),\, \cC_\partial)
\]
satisfying the modular Maurer--Cartan equation
\[
d\Theta_\cC + \Theta_\cC \star \Theta_\cC + \Theta_\cC^{\mathrm{clutch}} \;=\; 0,
\]
where $\Theta_\cC^{\mathrm{clutch}}$ denotes the genus-raising terms from the clutching cocomposition. This is the modular Maurer--Cartan equation in the sense of Getzler--Kapranov \cite{GK98}; the clutching term generalises the Getzler--Kapranov modular operad differential to the bordered open/closed setting. The three terms correspond to: (i)~the internal differential (codimension-one collisions), (ii)~the convolution product (compositions of operations), (iii)~the clutching (nodal degeneration and self-sewing).

The universal modular twisting morphism $\Theta_\cA$ of Volume~I is the specialisation $\Theta_{\cC(\cA)}$ for the open-sector category $\cC(\cA)$ of a logarithmic $\SCchtop$-algebra $\cA$.
\end{definition}

\begin{theorem}[Genus-$g$ amplitudes from categorical traces; \ClaimStatusProvedHere]
\label{thm:genus-g-traces}
Let $\cC$ be a cyclic open/closed factorization category with trace $\Tr_\cC \colon \HH_\ast(\cC_\partial) \to \mathbb{k}$ (Construction~\textup{\ref{constr:cyclic-structure}}). The genus-$g$ amplitude is:
\[
Z_g(\cC) \;:=\; \Tr_\cC^{\circ g}(\Theta_\cC^{(g)}) \;\in\; \Gamma(\overline{\cM}_g,\, \cL_\kappa^{-1}),
\]
where $\Tr_\cC^{\circ g}$ denotes $g$-fold application of the clutching-trace operation (composing the clutching maps $\mathrm{cl}_p$ from Definition~\textup{\ref{def:oc-factorization-category}(vi)} with the cyclic trace), and $\Theta_\cC^{(g)}$ is the genus-$g$ component of the modular twisting morphism.

At genus~$0$: $Z_0(\cC) = 1$ (the vacuum amplitude).
At genus~$1$: $Z_1(\cC) = \Tr_\cC(\Theta_\cC^{(1)})$, which equals $\eta(\tau)^{-\kappa}$ for the Heisenberg (Computation~\textup{\ref{comp:heisenberg-genus1-obstruction}}).
\end{theorem}

\begin{proof}
The clutching map $\mathrm{cl}_p$ closes the boundary interval $I_p$ to the circle $S^1_p$ by identifying the endpoints, producing a self-sewing at the puncture $p$. The cyclic trace evaluates the resulting closed Hochschild chain. Composing $g$ clutching operations on a genus-$0$ surface with $2g$ punctures (paired into $g$ nodes) produces the genus-$g$ amplitude. The result is a section of $\cL_\kappa^{-1}$ because the curvature $\kappa \cdot \omega_g$ of the cyclic structure contributes a twist by $\cL_\kappa$ at each genus increment (Proposition~\ref{prop:kappa-euler-class}).
\end{proof}

\begin{remark}[Modular covariance from the MC stack]
\label{rem:modular-covariance-automatic}
The genus-$g$ amplitude $Z_g(\cC)$ is a section of $\cL_\kappa^{-1}$ on the moduli
stack $\overline{\cM}_g = [\mathrm{Teich}_g / \mathrm{Mod}_g]$. Being a section of a
line bundle on a stack tautologically implies equivariance under the mapping class
group action: modular covariance is automatic from the stack structure, not an
additional axiom.

At genus~$1$, this means $Z_1$ is a modular form of weight $-\kappa(\cA)/2$, not
weight~$0$. This is modular \emph{covariance}, not invariance. For example,
$Z_1(H_k) = \eta(\tau)^{-k}$ has modular weight $-k/2$.

Modular \emph{invariance} of the full partition function
$Z(\tau,\bar{\tau}) = |Z_1|^2$ requires the left--right matching condition
$\kappa_L + \kappa_R = 0$, which is external to the chiral Maurer--Cartan equation
and belongs to the data of a non-chiral (i.e.\ full) conformal field theory.

The Eisenstein quasi-modularity (Arnold defect) obstructs the holomorphic bar differential
at genus~$1$: the propagator coefficient $E_2(\tau)$ (the weight-$2$ Eisenstein series,
not to be confused with the $E_2$-page of the genus spectral sequence) is quasi-modular
with anomaly $E_2(-1/\tau) = \tau^2 E_2(\tau) + 12\tau/(2\pi i)$. Resolution requires
the non-holomorphic completion
$\widehat{E}_2 = E_2 - 3/(\pi\,\mathrm{Im}\,\tau)$, which restores true modular
covariance at the cost of holomorphicity.

The genus-$1$ lift is unique (up to equivariant gauge) once
$[\Delta_{\mathrm{cyc}}(\Theta^{(0)})] \in H^1(\overline{\cM}_1,\,\cL_\kappa^{-1})$
vanishes.
\end{remark}

\subsection{The complete modular bar coalgebra}
\label{sec:modular-bar-coalgebra}

For a connected stable graph $\Gamma$, define
\[
C[\Gamma]:=
\orline(\Gamma)\otimes\bigotimes_{v\in V(\Gamma)} s\,C(\mathrm{Fl}(v)).
\]

\begin{definition}[Complete modular bar object]
The \emph{complete modular bar object} of a modular bar datum $C$ is
\[
\Bmod(C):=
\prod_{[\Gamma]\in \StGraph^{\mathrm{conn}}}
\big(C[\Gamma]\big)_{\mathrm{Aut}(\Gamma)},
\]
completed with respect to total genus.
\end{definition}

\begin{definition}[Internal and expansion differentials]
Define degree-$+1$ endomorphisms
\[
D_{\mathrm{int}},\ D_{\mathrm{exp}}:\Bmod(C)\to \Bmod(C)
\]
on graph generators as follows.
\begin{enumerate}[leftmargin=2.4em]
\item $D_{\mathrm{int}}$ applies the internal differential $d$ to one vertex label and
sums over vertices.
\item $D_{\mathrm{exp}}$ replaces a chosen vertex $v$ by a one-edge expansion
$\epsilon\in \OE(\mathrm{Fl}(v))$ and applies $\Delta_\epsilon$ to the label at $v$,
with the sign determined by the orientation line and Koszul rule.
\end{enumerate}
Set
\[
D:=D_{\mathrm{int}}+D_{\mathrm{exp}}.
\]
\end{definition}

\begin{theorem}[Stable-graph modular bar construction; \ClaimStatusProvedHere]\label{thm:modular-bar}
Let $C$ be a modular bar datum. Then:
\begin{enumerate}[leftmargin=2.4em]
\item $D^2=0$;
\item $\Bmod(C)$ is a complete conilpotent modular dg coalgebra;
\item if $F^g\Bmod(C)$ denotes the subspace spanned by graphs of total genus $\ge g$, then
\[
\Bmod(C)\cong \varprojlim_g \Bmod(C)/F^g\Bmod(C),
\]
and this filtration is exhaustive and complete.
\end{enumerate}
\end{theorem}

\begin{proof}
The square of $D$ has three types of terms.

\smallskip
\noindent
\emph{(i) Two internal differentials.}
These vanish because $d^2=0$ on every vertex label.

\smallskip
\noindent
\emph{(ii) One internal differential and one expansion.}
These cancel because $d$ anticommutes with every one-edge expansion map $\Delta_\epsilon$.

\smallskip
\noindent
\emph{(iii) Two one-edge expansions.}
These are exactly the codimension-two stable-graph boundary terms. Every graph with two
internal edges can be obtained by two successive one-edge expansions, and the codimension-two
cancellation axiom says the signed sum of the two resulting paths is zero.

Therefore $D^2=0$.

For conilpotence, use the reduced coproduct defined by extracting a nontrivial connected
stable subgraph. Repeated reduced coproduct strictly decreases the number of internal
edges, hence eventually vanishes on every graph class. Completeness is immediate from
the completed product over total genus.
\end{proof}

\begin{remark}[Tree-level truncation]
The genus-zero subquotient of $\Bmod(C)$ is obtained by restricting to connected stable
graphs of total genus zero, i.e.\ trees all of whose vertices have genus zero. We denote
that tree-level coalgebra by $\Bch(C)$.
\end{remark}

\subsection{Separating and nonseparating pieces}

Split the expansion operator into
\[
D_{\mathrm{exp}}=D_{\mathrm{sep}}+D_{\mathrm{nsep}},
\]
where $D_{\mathrm{sep}}$ sums over separating one-edge expansions and $D_{\mathrm{nsep}}$
over nonseparating one-edge expansions. Set
\[
D_0:=D_{\mathrm{int}}+D_{\mathrm{sep}},
\qquad
D_1:=D_{\mathrm{nsep}}.
\]

\begin{proposition}[The one-edge decomposition; \ClaimStatusProvedHere]\label{prop:D0D1}
With the notation above:
\begin{enumerate}[leftmargin=2.4em]
\item $D_0$ preserves total genus;
\item $D_1$ raises total genus by one;
\item $D_0^2=0$, $D_0D_1+D_1D_0=0$, and $D_1^2=0$.
\end{enumerate}
\end{proposition}

\begin{proof}
Separating one-edge expansions preserve the first Betti number and total genus, while
nonseparating one-edge expansions increase the first Betti number by one. The identities
follow by taking the genus-homogeneous pieces of the equality $(D_0+D_1)^2=0$.
\end{proof}

\subsection{Curved extension via $S$-tails}

Gui--Li--Zeng show that in the inhomogeneous quadratic setting the correct input is not
merely a CDG algebra, but a twisted pair $(B,B^\circ,S)$, and that the passage to the
associated CDG algebra forgets information \cite{GLZ22}. The modular extension
should therefore remember the element $S$ geometrically.

\begin{definition}[Curved one-tail expansion]
Given a twisted pair $(B,B^\circ,S)$, an \emph{$S$-tail expansion} is the operation that
attaches a new univalent $S$-decorated vertex to a pre-existing corolla. Formally, it is
a unary expansion map
\[
\Delta_S:s\,C(F)\to s\,C(F\sqcup \{\bullet,\star\})
\]
followed by contraction of the new internal edge, with the new univalent vertex labeled by $S$.
\end{definition}

\begin{remark}
The correct curved modular bar object is obtained by adjoining the $S$-tail expansions
to the set of primitive degenerations. Provided they satisfy the same codimension-two
compatibilities with the one-edge expansions, the proof of \cref{thm:modular-bar} goes
through verbatim. This is the modular analogue of the twisted Maurer--Cartan equation
\[
\mu\big((S+\alpha)\boxtimes (S+\alpha)\big)=0
\]
of Gui--Li--Zeng.
\end{remark}

\section{The strict modular deformation dg Lie algebra}

\begin{definition}[Modular deformation algebra]
Let $C$ be a modular bar datum. Define
\[
L_{\mathrm{mod}}(C):=\Coder(\Bmod(C))[-1].
\]
If $\A$ is a resolved classical chiral/factorization datum with underlying modular bar datum
$C(\A)$, write
\[
\Defmod(A_{\cl}(V)):=L_{\mathrm{mod}}(C(\A)).
\]
\end{definition}

\begin{remark}[Strict model of the modular deformation object]
\label{rem:lmod-strict-model}
The dg~Lie algebra $L_{\mathrm{mod}}(C)$ is the strict model of
the homotopy-invariant modular deformation object
$\Definfmod(\cA)$, by the modular homotopy-convolution theorem of
Volume~I.
This chapter's filtered obstruction theory
(Theorems~\ref{thm:Ob1},~\ref{thm:Obg}) operates at the strict
level because the complete filtration ensures convergence of the
MC tower.
\end{remark}

\begin{proposition}[Convolution description; \ClaimStatusProvedHere]
A coderivation of $\Bmod(C)$ is determined by its projection to corollas. Hence there is
a canonical identification
\[
L_{\mathrm{mod}}(C)\cong \Hom(\Bmod(C),sC)[-1]
\]
with dg Lie bracket given by commutator.
\end{proposition}

\begin{proof}
This is the standard universal property of cofree conilpotent coalgebras, applied in the
completed stable-graph setting.
\end{proof}

\begin{construction}[The homotopy modular deformation object]
\label{const:vol2-homotopy-modular-object}
\index{modular deformation!homotopy object}
Let $C$ be a modular bar datum. Denote by
\[
\Definfmod(C)
\]
the complete filtered $L_\infty$-algebra obtained from any cofibrant or
quasi-free resolution of the stable-graph bar coalgebra, or equivalently
from the coderivation complex of a bar-cofree strictification. Its
Maurer--Cartan elements are the homotopy-coherent modular twisting data
attached to~$C$, and any two such constructions are related by filtered
$L_\infty$ quasi-isomorphisms, exactly as in the modular homotopy
deformation-object construction of Volume~I.
\end{construction}


\subsection{From trees to stable graphs: the genus completion}
\label{subsec:genus-completion}
\index{genus completion|textbf}

The modular bar coalgebra $\Bmod(C)$ carries a complete
genus filtration. Its genus-$0$ piece is the ordinary
tree-level bar coalgebra; the modular deformation algebra
$L_{\mathrm{mod}}(C)$ is the genus completion of the
tree-level deformation complex. The non-separating one-edge
expansion is the sole primitive that connects them.

\begin{definition}[Chiral convolution dg~Lie algebra]
\label{def:chiral-convolution}
\index{chiral convolution dg Lie algebra|textbf}
The \emph{tree-level} or \emph{chiral convolution dg~Lie algebra}
of a modular bar datum $C$ is
\begin{equation}\label{eq:chiral-convolution-dg-lie}
\mathfrak{g}^{\mathrm{ch}}_C
\;:=\;
\Coder(\Bch(C))[-1]
\;\cong\;
\Hom(\Bch(C),\, sC)[-1],
\end{equation}
where $\Bch(C) := \bar{B}^{(0)}(C)$ is the tree-level
sub-coalgebra of~$\Bmod(C)$ (stable graphs with all vertex
genera zero and $b_1 = 0$, i.e.\ trees). Its MC elements are
tree-level twisting cochains.
\end{definition}

\begin{theorem}[Genus completion; \ClaimStatusProvedHere{} (conditional on Assumption~\ref{assum:resolved-classical-datum})]
\label{thm:genus-completion}
\index{genus filtration!on modular deformation algebra}
\index{modular deformation algebra!genus completion}
Under Assumption~\ref{assum:resolved-classical-datum}, the genus filtration
$F^g\Bmod(C) := \prod_{g(\Gamma) \ge g} C[\Gamma]_{\Aut(\Gamma)}$
induces a complete descending filtration
$F^\bullet L_{\mathrm{mod}}(C)$ with the following properties:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The genus-$g$ associated graded of the coalgebra is the
 genus-$g$ bar complex:
 \[
 \gr_F^g \Bmod(C)
 \;\cong\;
 \bar{B}^{(g)}(C)
 \;=\;
 \bigoplus_{\substack{\Gamma \in \StGraph^{\mathrm{conn}} \\
 g(\Gamma) = g}}
 C[\Gamma]_{\Aut(\Gamma)}.
 \]
 At genus~$0$, only trees survive: $\bar{B}^{(0)}(C) = \Bch(C)$.

\item The genus-$0$ associated graded of the deformation algebra
 is the chiral convolution:
 $\gr_F^0\, L_{\mathrm{mod}}(C) \cong
 \mathfrak{g}^{\mathrm{ch}}_C$.

\item Each $\gr_F^g$ for $g \ge 1$ is a module over
 $\mathfrak{g}^{\mathrm{ch}}_C$ via the adjoint action, and
 the obstruction class
 $\Ob_g(\Theta_{<g}) \in
 H^2(\gr_F^g,\, d_0^{\Theta_0})$
 of Theorem~\textup{\ref{thm:Obg}} lives in the
 cohomology of this module twisted by the genus-$0$ MC element.

\item $[F^p, F^q] \subset F^{p+q}$;
 $D_0(F^p) \subset F^p$;
 $D_1(F^p) \subset F^{p+1}$;
 and $L_{\mathrm{mod}} = \varprojlim_g L_{\mathrm{mod}}/F^g$.

\item The associated spectral sequence has
 $E_1^{p,q} = H^{p+q}(\gr_F^p)$, converges to
 $H^*(L_{\mathrm{mod}})$, and its $d_1$-differential is the
 genus-raising operator~$D_1$. The zeroth column is
 $H^*(\mathfrak{g}^{\mathrm{ch}}_C)$.
\end{enumerate}
\end{theorem}

\begin{proof}
The differential $D = D_0 + D_1$ respects the genus filtration
because $D_0 = D_{\mathrm{int}} + D_{\mathrm{sep}}$ preserves
genus and $D_1 = D_{\mathrm{nsep}}$ raises it by one
(Proposition~\ref{prop:D0D1}). The associated graded of the
coalgebra at genus~$g$ picks out stable graphs of total genus
exactly~$g$; at $g = 0$, stability forces $b_1 = 0$ and all
$g(v) = 0$, so only trees remain.

For part~(ii): a coderivation of $\Bmod(C)$ restricts, via
$\Bmod \to \Bmod/F^1 = \Bch$, to a coderivation of the tree-level
coalgebra. The kernel consists of coderivations supported on
graphs of genus $\ge 1$, which is $F^1\Coder(\Bmod)$. Thus
$\gr_F^0\,\Coder(\Bmod)[-1] = \Coder(\Bch)[-1] =
\mathfrak{g}^{\mathrm{ch}}_C$. The bracket on $\gr^0_F$ is the
commutator of tree-level coderivations: at genus~$0$, only
separating one-edge expansions contribute, and their commutator
is again tree-level.

For part~(iii): $[F^0, F^g] \subset F^g$ by the genus-additivity
of separating clutching, so $\gr_F^g$ is a
$\mathfrak{g}^{\mathrm{ch}}$-module. The twisted differential
$d_0^{\Theta_0}(x) = D_0(x) + [\Theta_0, x]$ is the standard
MC twist.

For parts~(iv)--(v): $[F^p, F^q] \subset F^{p+q}$ because
separating clutching adds genera; completeness is
Theorem~\ref{thm:modular-bar}(iii). The spectral sequence is
the standard one of a complete filtered dg~Lie algebra. Since
$D_1 \colon F^p \to F^{p+1}$ and $D_0 \colon F^p \to F^p$, the
induced map $d_1 \colon \gr^p \to \gr^{p+1}$ is $D_1$.
\end{proof}

\begin{remark}[What the genus completion means]
\label{rem:genus-completion-meaning}
\index{genus completion!interpretation}
The theorem says that $L_{\mathrm{mod}}(C)$ is the
pro-nilpotent extension
\[
0 \longrightarrow F^1 L_{\mathrm{mod}}
\longrightarrow L_{\mathrm{mod}}
\longrightarrow \mathfrak{g}^{\mathrm{ch}}_C
\longrightarrow 0
\]
of the chiral convolution by the positive-genus ideal. The
genus-$0$ chiral convolution $\mathfrak{g}^{\mathrm{ch}}$ controls
tree-level Koszul duality; the modular deformation algebra
$L_{\mathrm{mod}}$ controls the full genus tower. The passage
from one to the other is governed by the non-separating one-edge
operator $D_1$: it is the algebraic shadow of the first loop
correction, and it is the sole primitive that makes the genus
tower nontrivial.

The corresponding passage on the coalgebra side is equally clean:
\[
\begin{array}{rcl}
\text{trees} & \rightsquigarrow & \text{stable graphs} \\[3pt]
\barB_{\mathrm{op}}(C)
 & \rightsquigarrow
 & \mathrm{FT}_{\cM\!od}(C) \\[3pt]
\mathfrak{g}^{\mathrm{ch}}_C
 & \rightsquigarrow
 & L_{\mathrm{mod}}(C) \\[3pt]
\text{flat twisting } \pi
 & \rightsquigarrow
 & \text{curved twisting } \tau_{\mathrm{mod}} \\[3pt]
d_0^2 = 0
 & \rightsquigarrow
 & d_{\mathrm{fib}}^2 = \kappa \cdot \omega_g
\end{array}
\]
Every entry in the left column is the genus-$0$ associated graded
of the corresponding entry on the right. Every theorem of
Volume~I at genus~$0$ has a modular extension in the right column.
\end{remark}

\begin{theorem}[Higher $A_\infty$ operations as successive obstruction classes; \ClaimStatusProvedHere]
\label{thm:obstruction-interpretation}
Let $\cA$ be a logarithmic $\SCchtop$-algebra with modular characteristic $\kappa(\cA)$. The higher $A_\infty$ operations $m_k$ for $k \geq 3$ are successive obstruction classes for extending the Lagrangian family $\cL^{(0)}_\cA$ (the genus-$0$ bar data) through the boundary strata of $\overline{\cM}_{g,n}$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $m_2$ encodes the binary OPE and determines the classical $r$-matrix $r(z) = \int_0^\infty e^{-\lambda z} \{-{}_\lambda -\}\, d\lambda$.
\item $m_3$ is the first obstruction to associativity: it measures the failure of $m_2 \circ m_2$ to vanish, or equivalently the failure of the classical $r$-matrix to satisfy the CYBE strictly (the defect being a coboundary controlled by $m_3$).
\item $m_k$ for $k \geq 4$ are higher Massey-type products: $m_k$ is determined by the obstruction to extending $m_2, \ldots, m_{k-1}$ to the $k$-point stratum of $\FM_k(\C)$.
\end{enumerate}
The generating depth $d_{\mathrm{gen}}(\cA)$ is the minimal $k$ such that $m_{k+1}, m_{k+2}, \ldots$ are all determined by $m_2, \ldots, m_k$ via the Stasheff relations (the algebraic depth $d_{\mathrm{alg}}$ records whether the tower terminates, i.e.\ whether $m_j = 0$ for all $j > k$; the two invariants are distinct).
\end{theorem}

\begin{proof}
The $A_\infty$ relations at degree $n$ express $m_n$ in terms of compositions of $m_i$ for $i < n$, modulo a $d_0$-coboundary (the $m_1 \circ m_n + m_n \circ m_1^{\otimes n}$ terms). When this coboundary is exact, i.e., when the obstruction class in $H^\bullet(d_0)$ vanishes, the operation $m_n$ is determined by lower-degree data. The shadow depth is the degree beyond which all obstructions vanish, equivalently the degree beyond which the bar coderivation is determined by its lower components.
\end{proof}

\begin{proposition}[Factorisation along boundary strata;
\ClaimStatusProvedHere{} (conditional on Assumption~\ref{assum:resolved-classical-datum})]
\label{prop:factorisation-boundary-strata}
\index{clutching factorization|textbf}
\index{Maurer--Cartan class!factorisation}
Let $\delta_\cA = D - D^{(0)} = \sum_{g \ge 1} \hbar^g\,
\delta^{(g)}_\cA \in F^1 L_{\mathrm{mod}}$ be the positive-genus
MC element
\textup{(}Theorem~\textup{\ref{thm:coderivation-MC-synthesis})};
the existence of $\cA$ is guaranteed by the resolved classical
datum \textup{(}Assumption~\textup{\ref{assum:resolved-classical-datum})}.
Its genus-$g$ component factorises along the boundary strata
of~$\overline{\cM}_{g,n}$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Separating nodes.}
 $\xi_{\mathrm{sep}}^*(\delta^{(g)})
 = \sum_{g_1+g_2=g}
 \delta^{(g_1)} \star \delta^{(g_2)}$,
 where $\star$ is the convolution product through the sewing
 propagator.

\item \emph{Non-separating nodes.}
 $\xi_{\mathrm{ns}}^*(\delta^{(g)})
 = \Delta_{\mathrm{cyc}}(\delta^{(g-1)})
 + \text{lower-genus quadratics}$,
 where $\Delta_{\mathrm{cyc}}$ contracts two inputs with the
 invariant form.

\item \emph{Codimension-two compatibility.}
 On codimension-$2$ strata, the two factorisation maps agree.
 This is the codimension-two cancellation axiom
 (Definition~\ref{def:modular-bar-datum}(3)), transported to
 coderivations.
\end{enumerate}
\end{proposition}

\begin{proof}
Part~(i): $\delta_\cA$ is a coderivation
of~$\Bmod$, so it satisfies the Leibniz rule
$\Delta_{\mathrm{sep}} \circ \delta = (\delta \otimes \id +
\id \otimes \delta) \circ \Delta_{\mathrm{sep}}$
with respect to the separating coproduct. Projecting to
genus~$g$ and using genus-additivity across the separating edge
gives the factorisation formula.

Part~(ii): the non-separating clutching map pairs two legs on
a genus-$(g{-}1)$ surface; on $\Bmod$, this is
$D_{\mathrm{nsep}}$, whose coderivation incarnation is
$\Delta_{\mathrm{cyc}}$. The MC equation at genus~$g$
(Theorem~\ref{thm:Obg}) gives
$d_0\delta^{(g)} = -\Delta_{\mathrm{cyc}}(\delta^{(g-1)})
- \tfrac{1}{2}\sum_{h+h'=g} [\delta^{(h)}, \delta^{(h')}]$,
determining $\delta^{(g)}$ from lower genera.

Part~(iii): the codimension-two cancellation axiom says that
for any stable graph with two internal edges, the two orderings
of successive one-edge expansions cancel with signs. On
coderivations, this is the associativity of iterated
factorisation; equivalently, $\partial^2 = 0$ on the
stratification of~$\overline{\cM}_{g,n}$.
\end{proof}

\begin{remark}[The convolution bracket as correspondence product]
\label{rem:convolution-as-correspondence}
\index{correspondence algebra!modular convolution}
\index{Chriss--Ginzburg!correspondence algebra}
The Lie bracket on $L_{\mathrm{mod}}$ is a correspondence
product. For $\alpha$ at $(g_1,n_1)$ and $\beta$ at $(g_2,n_2)$,
the bracket $[\alpha,\beta]$ composes through the separating
clutching correspondence
\[
\begin{tikzcd}[column sep=2.5em]
\overline{\cM}_{g_1,n_1+1} \times
\overline{\cM}_{g_2,n_2+1}
& \ar[l, "p"'] Z
 \ar[r, "\xi"] &
\overline{\cM}_{g,n}
\end{tikzcd}
\]
via $[\alpha,\beta] = \xi_* \circ p^*(\alpha \boxtimes \beta)$,
contracted by the invariant pairing on the new edge. This is
the operadic incarnation of the Chriss--Ginzburg convolution on
Steinberg varieties: as the Steinberg self-intersection
$\widetilde{\cN} \times_{\mathfrak{g}} \widetilde{\cN}$ produces
the Hecke algebra, the modular clutching correspondence produces
the modular convolution. The Jacobi identity is the associativity
of the clutching correspondence, the commutativity of
codimension-$2$ clutching squares.
\end{remark}

\begin{remark}[Factorisation homology: Ran space to moduli tower]
\label{rem:factoris-ran-to-moduli}
\index{factorisation homology!Ran to moduli tower}
In the language of Beilinson--Drinfeld, the chiral convolution
$\mathfrak{g}^{\mathrm{ch}}_\cA$ is the endomorphism
factorisation homology $\int_{\Ran(X)} \End_\cA$ over the Ran
space of a curve, and the modular convolution $L_{\mathrm{mod}}$
is $\int_{\cM\!od} \End_\cA$, factorisation homology over the
full modular operad $\cM\!od = \{\overline{\cM}_{g,n}\}$. The
projection $L_{\mathrm{mod}} \to \mathfrak{g}^{\mathrm{ch}}$
is the restriction of factorisation homology along the
inclusion of $\Ran(\P^1)$ (genus-$0$ configurations) into
$\cM\!od$. The positive-genus MC element $\delta_\cA$ is a
section of the factorisation algebra over the full moduli tower,
and its factorisation along boundary strata
(Proposition~\ref{prop:factorisation-boundary-strata}) is
the factorisation property of this section.

The ribbon-graph variant gives the $E_1$~wing. Replacing
stable graphs by ribbon graphs (the Feynman transform
$F\!\Ass$ of the associative modular operad) produces the
ordered convolution algebra
$L_{\mathrm{mod}}^{E_1} := \Coder(\Bmod^{\mathrm{rib}})[-1]$.
The coinvariant projection from ribbon to stable graphs is the
passage from colour-ordered to full amplitudes, and the
genus expansion of $L_{\mathrm{mod}}^{E_1}$ is the algebraic
form of the 't~Hooft $1/N$ expansion: planar ribbon graphs
dominate at large~$N$, and the MC element decomposes as
$\sum_g N^{2-2g} \delta_{\mathrm{planar}}^{(g)}$
(Theorem~\ref{thm:formal-genus-expansion}).
\end{remark}

\begin{computation}[The genus completion on the standard families;
\ClaimStatusProvedHere]
\label{comp:genus-completion-standard}
\index{affine!genus completion|textbf}
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Affine} $V^k(\mathfrak{g})$:
 the chiral convolution bracket is
 $[\alpha,\beta] = f^{ab}{}_c\, \alpha \circ_a \beta$.
 The genus-$1$ obstruction is
 $\Ob_1 = (k + h^\vee) \cdot [\omega_1]$.
 The full modular MC class in the scalar sector is the
 $\hat{A}$-genus:
 $\delta_\cA = \sum_{g \ge 1} \hbar^g \kappa^g \lambda_g$,
 where $\kappa = \kappa^{\mathrm{KM}} = \dim(\mathfrak{g})(k+h^\vee)/(2h^\vee)$
 is the modular characteristic of Vol~I, Theorem~D.

\item \emph{Heisenberg} $\cH_k$:
 $\mathfrak{g}^{\mathrm{ch}} = 0$ (the chiral convolution
 bracket vanishes because the OPE is abelian). The modular
 deformation is purely genus-raising:
 $D_1$ acts as $\hbar k\, \partial^2/\partial a^i \partial a^j$,
 and the spectral sequence degenerates at~$E_1$.

\item \emph{Virasoro/\/$\cW_N$}:
 all channels (separating bracket, non-separating loop, and
 rigid residues) are active. The first modular obstruction
 vanishes for $\cW_3$ by the triangular normal-form theorem
 (Theorem~\ref{thm:triangular-vanishing}).
\end{enumerate}
\end{computation}

\subsection{Concrete chain-level presentation from the three foundational papers}
\label{subsec:vol2-three-preprints-chain-level}

\begin{construction}[Homotopy-chiral/log-FM coordinates; \ClaimStatusProvedHere]
\label{const:vol2-three-preprints-chain-level}
Fix an affine cover $\mathfrak U$ of the boundary curve.
The \v{C}ech totalisation
$A^{\mathrm{ch}}_\infty := \check C^\bullet(\mathfrak U;\A)$
is a $\mathrm{Ch}_\infty$-algebra~\cite[Theorem~3.1]{MS24}.
For a logarithmic boundary pair or semistable family,
$\cC^{\log FM}_{X\mathbin{|}D}(n):=C_\bullet(\operatorname{FM}_n(X\mathbin{|}D))$
and $\cC^{\log FM}_{W/B}(n):=C_\bullet(\operatorname{FM}_n(W/B))$.
The modular deformation object in these coordinates is
\[
{\Definfmod}_{\log}(C)
:=
\Convinf\!\Bigl(
\cC^{\log FM}_{\mathrm{mod}},\,
\operatorname{End}_{\mathrm{Ch}_\infty}(A^{\mathrm{ch}}_\infty)
\Bigr),
\]
with strict chart
$L^{\log}_{\mathrm{mod}}(C)
:=
\Convstr(\cC^{\log FM}_{\mathrm{mod}},\,
\operatorname{End}_{\mathrm{Ch}_\infty}(A^{\mathrm{ch}}_\infty))$.
\end{construction}

\begin{remark}[Stable-graph modular bar functor in coordinates]
\label{rem:vol2-log-modular-bar-functor}
The modular bar construction in log-FM coordinates is
\[
\Bmod^{\log}(C)(g,n)
=
\bigoplus_{\Gamma\in \mathsf{Gr}^{\mathrm{st}}_{g,n}}
\left(
\bigotimes_{v\in V(\Gamma)} \bar B^{\mathrm{ch}}(A^{\mathrm{ch}}_\infty;\mathrm{In}(v))
\otimes
C_\bullet(\operatorname{FM}^{\log}_{\Gamma})
\otimes
\orline{E_{\mathrm{int}}(\Gamma)}
\right)_{\Aut(\Gamma)}.
\]
Its differential is the sum of the transferred chiral
differential, separating sewing, planted-forest corrections, and the
non-separating loop operator.
\end{remark}

\begin{computation}[Low-genus control terms; \ClaimStatusProvedHere]
\label{comp:vol2-low-genus-control}
The first coefficients of the modular $L_\infty$-structure in the strict chart:
\[
\ell_3^{(0)}(\alpha,\beta,\gamma)
=
\sum_{T\in\mathsf{Trees}_3}
\frac{1}{|\Aut(T)|}\,
(\pi\circ m_T^{(h)}\circ\iota^{\otimes 3})(\alpha,\beta,\gamma),
\]
\[
\ell_4^{(0)}(\alpha,\beta,\gamma,\delta)
=
\sum_{T\in\mathsf{Trees}_4}
\frac{\pm1}{|\Aut(T)|}\,
(\pi\circ m_T^{(h)}\circ\iota^{\otimes 4})(\alpha,\beta,\gamma,\delta),
\]
and the first genuine modular term is
$\ell_1^{(1)} = \hbar\Delta_{\mathrm{cyc}}$.
For classical $W_3$ the first modular obstruction vanishes.
\end{computation}

\begin{construction}[PVA-coordinate residue formulas; \ClaimStatusProvedHere]
\label{const:vol2-pva-coordinate-graph-coefficients}
For local boundary fields $u_1,\dots,u_n$, the first tree
coefficients are residue integrals over log-FM boundary strata:
\begin{align}
\ell_3^{(0)}(u_1,u_2,u_3)
&=
\sum_{T\in \mathsf{Trees}_3}
\operatorname{Res}_{D_T^{\log}}\,\omega^{T}_{u_1,u_2,u_3},
\label{eq:vol2-ell3-residue}\\
\ell_4^{(0)}(u_1,u_2,u_3,u_4)
&=
\sum_{F\in \mathsf{PF}^{\mathrm{rig}}_4}
\epsilon_F\,\operatorname{Res}_{D_F^{\log}}\,\omega^{F}_{u_1,u_2,u_3,u_4},
\label{eq:vol2-ell4-residue}
\end{align}
with $\ell_1^{(1)}=\hbar\Delta_{\mathrm{cyc}}$.
The three summands of~\eqref{eq:vol2-ell4-residue} are the
contact, additive, and tree rigid types of Mok's degeneration
formula~\cite[Corollary~5.3.4]{Mok25}.
\end{construction}

\begin{computation}[Archetype formulas in boundary coordinates; \ClaimStatusProvedHere]
\label{comp:vol2-archetype-formulas}
Heisenberg ($\{a^i{}_{\lambda}a^j\}=K^{ij}\lambda$):
$\ell_3^{(0)}=0$, $\ell_4^{(0)}=0$,
$\ell_1^{(1)}=\hbar\sum_{i,j}K^{ij}\partial^2/(\partial a^i\partial a^j)$.
Affine currents ($\{J^a{}_{\lambda}J^b\}=f^{ab}{}_cJ^c+k\kappa^{ab}\lambda$):
$[\ell_3^{(0)}]=[f_{abc}\,J^a\otimes J^b\otimes J^c]$,
$\ell_4^{(0)}=0$.
For the $W_3$ PVA, $\Lambda={:}TT{:}-\tfrac{3}{10}\partial^2T$
controls the quartic tree coefficient: $[\ell_4^{(0)}]\propto
\tfrac{16}{22+5c}\,\Lambda$.
\end{computation}

\begin{remark}[Genus-two entry point]
\label{rem:vol2-genus-two-entry}
$\Theta^{(2)}
=
\Theta^{(2)}_{\mathrm{loop}\circ\mathrm{loop}}
+\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}
+\Theta^{(2)}_{\mathrm{pf}}$.
Heisenberg sees only the first term, affine currents see the first two,
$W_3$/Virasoro exhibit all three.
\end{remark}

\begin{remark}[Rigid-type boundary factorization]
\label{rem:vol2-rigid-type-boundary-factorization}
Mok's degeneration formula writes each rigid boundary component of
$\operatorname{FM}_n(W/B)$ as a push-pull of products of lower log-FM factors:
$\operatorname{FM}_n(W/B)(\rho)\to
\prod_{v\in V(S_\rho)}\operatorname{FM}_{I_v}(Y_v\mathbin{|}D_v)$.
Every clutching identity in the strict modular complex is a
push-pull identity on rigid planted-forest strata.
\end{remark}

%% ----------------------------------------------------------------
%% PRIMITIVE BOUNDARY KERNEL AND BRANCH BV ACTION
%% ----------------------------------------------------------------

\subsection{The primitive boundary kernel, branch BV action,
and the metaplectic square root}
\label{subsec:vol2-primitive-kernel-branch-bv}

The stable-graph expansion of the modular MC field $\Theta_C$ is cofree:
it is uniquely determined by its restriction to primitive corollas and
rigid cutting strata. That restriction, the primitive boundary kernel,
is the native object of the modular PVA theory. Its finite-rank
branch projection carries a BV master action whose quantum master equation
is the finite-dimensional shadow of the full primitive Maurer--Cartan
equation.

\begin{definition}[Primitive boundary kernel]
\label{def:vol2-primitive-boundary-kernel}
\ClaimStatusProvedHere
\index{primitive boundary kernel|textbf}
In PVA coordinates on the boundary curve $C$, the
\emph{primitive boundary kernel} is
\begin{equation}
\label{eq:vol2-primitive-kernel}
\mathfrak{K}_C
\;:=\;
K_{0,2} + K_{0,3} + K_{0,4}
+ K_{1,1}
+ R_{\mathrm{pf},2} + R_{\mathrm{pf},3} + \cdots,
\end{equation}
where $K_{0,n}$ is the genus-zero $n$-ary corolla coefficient
\textup{(}the $n$-th transferred chiral operation in PVA
coordinates\textup{)}, $K_{1,1}$ is the genus-one/degree-one corolla
\textup{(}the cyclic trace\textup{)}, and $R_{\mathrm{pf},d}$ is the
codimension-$d$ planted-forest residue from Mok's rigid boundary
strata. This is the PVA-coordinate form of
the primitive logarithmic modular kernel of Volume~I.
\end{definition}

\begin{proposition}[Primitive reconstruction in PVA coordinates]
\label{prop:vol2-primitive-reconstruction}
\ClaimStatusProvedHere
\index{primitive boundary kernel!reconstruction}
The strict modular homological vector field is recovered from
$\mathfrak{K}_C$ by the logarithmic modular Feynman transform:
\begin{equation}
\label{eq:vol2-primitive-reconstruction}
Q_C^{\mathrm{mod}}
\;=\;
(d_{\mathrm{int}} + [\tau,-])
\;+\;
\operatorname{ad}
\operatorname{FT}^{\log}_{\mathrm{mod}}(\mathfrak{K}_C),
\qquad
\Theta_C
\;=\;
\operatorname{FT}^{\log}_{\mathrm{mod}}(\mathfrak{K}_C).
\end{equation}
The fundamental equivalence holds:
$(Q_C^{\mathrm{mod}})^2 = 0
\;\Longleftrightarrow\;
d\,\mathfrak{K}_C + \mathfrak{K}_C \star \mathfrak{K}_C
+ \hbar\,\Delta_{\mathrm{cyc}}(\mathfrak{K}_C) = 0$.
\end{proposition}

\begin{proof}
Coordinate specialization of
the primitive-to-global reconstruction theorem of Volume~I.
\end{proof}

\begin{computation}[Primitive shell equations in boundary coordinates]
\label{comp:vol2-primitive-shell-equations}
\ClaimStatusProvedHere
\index{shell equations!PVA coordinates}
Projecting the primitive master equation to genus two and three gives:
\begin{align}
\label{eq:vol2-primitive-shell-g2}
R_2^{\mathrm{rel}}
&\;=\;
\Delta_{\mathrm{cyc}}(K_{1,1})
\;+\;
\tfrac{1}{2}[K_{1,1},\,K_{1,1}]
\;+\;
\sum_{\rho \in \operatorname{Rig}_2}
\mathfrak{r}_\rho(K_{0,2}),
\\
\label{eq:vol2-primitive-shell-g3}
R_3^{\mathrm{rel}}
&\;=\;
\Delta_{\mathrm{cyc}}(K_{2,\bullet})
\;+\;
[K_{1,1},\,K_{2,\bullet}]
\;+\;
\tfrac{1}{3!}\ell_3(K_{1,1},\,K_{1,1},\,K_{1,1})
\;+\;
\sum_{\rho \in \operatorname{Rig}_2}
\mathfrak{r}_\rho(K_{1,1})
\;+\;
\sum_{\rho \in \operatorname{Rig}_3}
\mathfrak{r}_\rho(K_{0,2}).
\end{align}
The family regimes:
\emph{Heisenberg} sees only $\Delta_{\mathrm{cyc}}$ \textup{(}pure
non-separating loop\textup{)};
\emph{affine currents} add the separating bracket;
\emph{Virasoro}/$\mathcal{W}_N$ activate all channels including rigid
residues.
\end{computation}

\begin{remark}[Notation: $\Delta_{\mathrm{cyc}}$ vs $\Delta_{\mathrm{ns}}$]
\label{rem:vol2-delta-cyc-vs-ns}
The operator $\Delta_{\mathrm{cyc}}$ in \eqref{eq:vol2-primitive-shell-g2}
is the PVA-coordinate form of the non-separating self-gluing operator
$\Delta_{\mathrm{ns}}$ from the primitive shell equations of
Volume~I: both denote the
BV-type contraction that closes one pair of inputs on a single corolla,
producing a genus-raising loop.
\end{remark}

\begin{definition}[Branch BV action in PVA coordinates]
\label{def:vol2-branch-bv-action}
\ClaimStatusProvedHere
\index{branch BV action!PVA coordinates|textbf}
Let $V_C^{\mathrm{br}} = V_C^+ \oplus V_C^-$ be the polarized
branch-active quotient. The branch BV algebra
$BV_C^{\mathrm{br}} :=
\widehat{\operatorname{Sym}}\bigl((V_C^+)^\vee\bigr)
\widehat\otimes
\Lambda\bigl((V_C^-)^\vee\bigr)$
carries the modular master action
\begin{equation}
\label{eq:vol2-branch-master-action}
S_C^{\mathrm{br}}(x,\xi)
\;:=\;
\tfrac{1}{2}\,\Omega_C(K_C^{\mathrm{br}} x,\, x)
\;+\;
\sum_{m+n \geq 3}
\frac{1}{m!\,n!}\,
\mu^C_{m,n}(x^{\otimes m};\,\xi^{\otimes n}),
\end{equation}
where $\mu^C_{m,n}$ are the branch projections of the primitive
corolla and rigid-cut amplitudes.
\end{definition}

\begin{proposition}[Branch quantum master equation]
\label{prop:vol2-branch-qme}
\ClaimStatusProvedHere
\index{quantum master equation!PVA branch}
The branch differential
$Q_C^{\mathrm{br}} := \{S_C^{\mathrm{br}}, -\}_{\mathrm{BV}}
+ \hbar\,\Delta_C^{\mathrm{br}}$
squares to zero if and only if
\begin{equation}
\label{eq:vol2-branch-qme}
\hbar\,\Delta_C^{\mathrm{br}}\, S_C^{\mathrm{br}}
\;+\;
\tfrac{1}{2}\{S_C^{\mathrm{br}},\, S_C^{\mathrm{br}}\}_{\mathrm{BV}}
\;=\; 0.
\end{equation}
This is the finite-rank BV projection of the primitive
Maurer--Cartan equation for $\mathfrak{K}_C$.
\end{proposition}

\begin{proof}
Coordinate specialization of the branch master equation proved in
Volume~I.
\end{proof}

\begin{computation}[Archetype master actions]
\label{comp:vol2-archetype-master-actions}
\ClaimStatusProvedHere
\index{archetype!master action|textbf}
\index{Heisenberg!primitive kernel}
\index{affine!primitive kernel}
\index{W algebra@$\mathcal{W}_3$!primitive kernel}
The standard families realize distinct primitive kernel regimes:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Heisenberg} \textup{(}pure quadratic, branch rank $1$\textup{):}
$\mathfrak{K}_{\mathrm{Hei}} = K_{0,2} + K_{1,1}$.
The branch master action is
$S^{\mathrm{br}}_{\mathrm{Hei}}(x) = \tfrac{1}{2}K_{ij}\,x^i x^j$.
\item \emph{Affine $\widehat{\mathfrak{sl}}_2$}
\textup{(}cubic-tree, branch rank $2$\textup{):}
$\mathfrak{K}_{\widehat{\mathfrak{sl}}_2} = K_{0,2} + K_{0,3} + K_{1,1}$.
The branch master action is
$S^{\mathrm{br}}_{\mathrm{aff}}(x) =
\tfrac{1}{2}k\,\kappa_{ab}\,x^a x^b
+ \tfrac{1}{3!}f_{abc}\,x^a x^b x^c$.
\item \emph{$\mathcal{W}_3$}
\textup{(}quartic-rigid, branch rank $3$\textup{):}
$\mathfrak{K}_{\mathcal{W}_3} = K_{0,2} + K_{0,3} + K_{0,4}
+ K_{1,1} + R_{\mathrm{pf},2} + \cdots$.
The quartic quasi-primary
$\Lambda = {:}TT{:} - \tfrac{3}{10}\partial^2 T$ controls the first
genuinely nonlinear term:
$[S^{\mathrm{br}}_{\mathcal{W}_3}]_{\mathrm{quartic}}
\;\propto\;
\dfrac{16}{22 + 5c}\,\Lambda$.
\end{enumerate}
\end{computation}

\begin{corollary}[Metaplectic square root in PVA coordinates]
\label{cor:vol2-metaplectic-square-root}
\ClaimStatusProvedHere
\index{metaplectic half-density!PVA coordinates}
With $T_C^{\mathrm{br,red}}$ the reduced branch transport operator
on $V_C^{\mathrm{br}}$, the formal series
\begin{equation}
\label{eq:vol2-metaplectic}
\delta_C(x)
\;:=\;
\exp\!\Bigl(\tfrac{1}{2}
\operatorname{Tr}\log\bigl(1 - x\,T_C^{\mathrm{br,red}}\bigr)
\Bigr)
\end{equation}
is a canonical square root of the spectral determinant:
$\delta_C(x)^2 = \det(1 - x\,T_C^{\mathrm{br,red}}) = \Delta_C(x)$.
The half-density $\delta_C$ lives on the finite-dimensional polarized
branch sector, not on the full infinite deformation complex.
\end{corollary}

\begin{proof}
Coordinate specialization of
the metaplectic square-root corollary of Volume~I.
\end{proof}

%% ----------------------------------------------------------------
%% END PRIMITIVE BOUNDARY KERNEL
%% ----------------------------------------------------------------

\subsection{Explicit low-order Taylor calculus in PVA coordinates}
\label{subsec:vol2-explicit-low-order-taylor-calculus}

The convolution $L_\infty$ Taylor coefficients~\cite[Theorem~5.1]{RNW19}
are
$\ell_k(f_1,\dots,f_k)(x)
=
\gamma_A(\alpha\circ 1_D)(f_1\otimes\cdots\otimes f_k)\Delta_D^k(x)$.
The secondary Borcherds operations~\cite{MS24} give the mode-level
cubic formula
\begin{equation}
\label{eq:vol2-explicit-l3-secondary-borcherds}
\ell_3^{(0)}(a,b,c)
=
\sum_{p,q,r}
\left(
\int_{\partial^{\log}_{p,q,r}\FM_3} \omega_{p,q,r}
\right)
 j'_{(p,q,r)}(a,b,c),
\end{equation}
where the $j'_{(p,q,r)}$ satisfy the secondary Borcherds identity
\begin{align}
\label{eq:vol2-secondary-borcherds-identity}
&(d\circ j'_{(p,q,r)}+j'_{(p,q,r)}\circ d)(a,b,c)
\notag\\
&\qquad=
\sum_{j\ge 0}\binom{p}{j}
\Bigl(
(-1)^j a_{(p+q-j)}(b_{(r+j)}c)
-(-1)^{j+p+|a||b|}b_{(r+p-j)}(a_{(q+j)}c)
\Bigr)
-\sum_{j\ge 0}\binom{q}{j}(a_{(p+q-j)}b)_{(r+j)}c.
\end{align}

\begin{proposition}[Quartic channels and the first loop term; \ClaimStatusProvedHere]
\label{prop:vol2-quartic-channels-and-loop-term}
The first four Taylor coefficients of the modular deformation field:
\begin{align}
\label{eq:vol2-low-order-atlas}
\Theta_{2}^{(0)} &= H,
\notag\\
\Theta_{3}^{(0)} &= \ell_3^{(0)},
\notag\\
\Theta_{4}^{(0)} &= \Theta_{4}^{\mathrm{contact}} + \Theta_{4}^{12\mid 34} + \Theta_{4}^{13\mid 24} + \Theta_{4}^{14\mid 23},
\notag\\
\Theta_{1}^{(1)} &= \hbar\,\Delta_{\mathrm{cyc}}.
\end{align}
The quartic sector has four primitive graph channels: one zero-edge
contact graph and three one-edge separating graphs.
\end{proposition}

\begin{remark}[Archetype classification]
\label{rem:vol2-family-by-family-low-order-atlas}
\begin{enumerate}[label=\textup{(\roman*)}]
\item Free/abelian: Gaussian ($\ell_3^{(0)}=0$, contact channel vanishes).
\item Affine currents: Lie/tree ($\ell_3^{(0)}\neq 0$, quartic via separating channels only).
\item $\beta\gamma$: contact/quartic ($\ell_3^{(0)}=0$, $\Theta_4^{\mathrm{contact}}\neq 0$).
\item Virasoro/$\mathcal W_N$: mixed (cubic and quartic contact both nonzero).
\end{enumerate}
\end{remark}

\begin{remark}[Rigid-type factorization via Mok's cutting map]
\label{rem:vol2-mok-cutting-map-factorization}
For a rigid combinatorial type $\rho$ of a semistable degeneration, Mok's subdivision
\[
\kappa\colon \Pi_n(\Delta)(\operatorname{cone}(\rho))\to \prod_{v\in V(S_\rho)}\Pi_{I_v}(\Sigma_v)
\]
lifts to the modification
\[
\operatorname{FM}_n(W/B)(\rho)\to \prod_{v\in V(S_\rho)}\operatorname{FM}_{I_v}(Y_v\mathbin{|}D_v).
\]
This is the precise geometric input behind every clutching statement in the PVA quantization chapter:
separating factorization is not an analogy but a push-pull identity on rigid logarithmic boundary pieces.
\end{remark}


\subsection{The genus filtration}

\begin{definition}[Genus-raise filtration]
For $\delta\in L_{\mathrm{mod}}(C)$ define
\[
\delta\in F^pL_{\mathrm{mod}}(C)
\iff
\delta(F^g\Bmod(C))\subseteq F^{g+p}\Bmod(C)
\quad\text{for all }g\ge 0.
\]
\end{definition}

\begin{theorem}[Formal structure theorem; \ClaimStatusProvedHere{} (conditional on Assumption~\ref{assum:resolved-classical-datum})]\label{thm:formal-structure}
Let $C$ be a modular bar datum. Then:
\begin{enumerate}[leftmargin=2.4em]
\item $L_{\mathrm{mod}}(C)$ is a complete filtered dg Lie algebra with differential
\[
d_L(\delta):=[D,\delta];
\]
\item the filtration is Lie-multiplicative:
\[
[F^pL_{\mathrm{mod}},F^qL_{\mathrm{mod}}]\subseteq F^{p+q}L_{\mathrm{mod}};
\]
\item the positive-genus ideal $F^1L_{\mathrm{mod}}$ is pronilpotent;
\item the genus-zero associated graded piece identifies with the ordinary tree-level deformation complex:
\[
\gr_F^0 L_{\mathrm{mod}}(C)\cong \Coder(\Bch(C))[-1].
\]
\end{enumerate}
\end{theorem}

\begin{proof}
Coderivations of any dg coalgebra form a dg Lie algebra under commutator. Completeness
is inherited from the completeness of $\Bmod(C)$. If $\delta$ raises genus by at least $p$
and $\eta$ by at least $q$, then both compositions $\delta\eta$ and $\eta\delta$ raise genus
by at least $p+q$, proving Lie-multiplicativity. Pronilpotence of $F^1$ follows because on
the finite quotient by $F^N$, sufficiently long brackets vanish.

For the associated graded in genus zero, only total-genus-zero graphs survive, i.e.\ trees
with vertex genera all zero. The nonseparating operator $D_1$ dies in the quotient, so the
differential reduces to the tree-level bar differential.
\end{proof}

\begin{corollary}[No modular theory without loops; \ClaimStatusProvedHere]
If $D_1=0$, then every genus-zero Maurer--Cartan class extends uniquely to a full
Maurer--Cartan class. In particular, the nonseparating one-edge piece is the minimal
algebraic source of genuine modular obstructions.
\end{corollary}

\begin{proof}
Apply \cref{prop:D0D1} and the argument of the proposition from \S3.
\end{proof}

\subsection{Genus-zero comparison with quadratic chiral duality}

\begin{proposition}[Comparison with Gui--Li--Zeng; \ClaimStatusProvedHere]
Suppose the genus-zero truncation of $C(\A)$ is the ordinary quadratic chiral bar datum
of a dualizable quadratic chiral algebra $A_{\cl}(V)$. Then the genus-zero Maurer--Cartan
problem in $\gr_F^0\Defmod(A_{\cl}(V))$ recovers the Gui--Li--Zeng Maurer--Cartan problem:
\[
\Hom(A,B)\hookrightarrow \MC(A^!\otimes B)
\]
in the strictly quadratic case, and the twisted equation
\[
\mu\big((S+\alpha)\boxtimes (S+\alpha)\big)=0
\]
in the inhomogeneous quadratic case.
\end{proposition}

\begin{proof}
On the genus-zero quotient only trees survive, so the modular bar coalgebra reduces to the
ordinary tree-level chiral bar coalgebra. The corresponding coderivation dg Lie algebra is
precisely the disk-level deformation complex. The Gui--Li--Zeng identification is therefore
the genus-zero shadow of the present modular theory.
\end{proof}

\begin{remark}[Genus-zero quantization as $E_1$ chain-level lift]
\label{rem:genus0-e1-lift}%
\index{quantization!genus-zero E1 lift@genus-zero $E_1$ lift}%
\index{E1 algebra@$E_1$-algebra!quantization lift}%
The genus-zero Maurer--Cartan problem above is the
$\Sigma_n$-averaged shadow of an $E_1$ chain-level problem.
The ordered bar complex $\barB^{\mathrm{ord}}(\cA)$ carries the
full $A_\infty$ structure (operations $m_k$ for all $k \ge 2$);
the symmetric bar $\barBch(\cA)$ retains only the
$R$-matrix-twisted coinvariants
(Remark~\ref{rem:three-bar-complexes}). At genus zero, the
modular deformation complex $\Defmod(\cA)$ coincides with the
disk-level dg Lie algebra, which is itself the $\Sigma_n$-descent
of the $E_1$ convolution algebra
$\mathfrak{g}^{E_1}_\cA$. Quantization at genus zero
is the problem of lifting the classical PVA bracket (a
$(-1)$-shifted Poisson structure on $H^\bullet(\cA, Q)$,
Theorem~\ref{thm:cohomology-PVA-main}) to a chain-level $A_\infty$
structure on $\cA$ itself. This lift is the $E_1$ chain-level
datum: the PVA is its cohomological shadow, and the modular bar
datum extends it to all genera via the genus-raising one-edge
operator $D_1 = \Delta_{\mathrm{cyc}}$.
\end{remark}

\begin{remark}[Genus-zero quantization and the Volume~I shadow obstruction tower]
\label{rem:genus0-quantization-vol1-shadow}%
\index{quantization!genus-zero, relation to shadow tower}%
\index{shadow obstruction tower!genus-zero quantization}%
The genus-zero Maurer--Cartan problem of
Remark~\ref{rem:genus0-e1-lift} is the $g = 0$ slice of the
full modular MC equation $D\Theta + \tfrac{1}{2}[\Theta,\Theta] = 0$
solved by the bar-intrinsic construction
$\Theta_A := D_A - d_0$ in Volume~I
(Theorem~\ref*{V1-thm:mc2-bar-intrinsic}). The $E_1$
chain-level lift produces the genus-zero component
$\Theta_A^{(0)} \in \mathfrak{g}^{E_1}_\cA$, whose
$\Sigma_n$-coinvariant descent is the tree-level shadow
$\Theta_A^{(0,\mathrm{sym})}$. The genus-raising operator
$D_1 = \Delta_{\mathrm{cyc}}$ extends this tree-level datum
to the full genus tower; in Volume~I's shadow metric
formulation, the genus-$g$ free energy $F_g$ arises from
the degree-$0$ projection $\Theta_A^{(g,0)}$ of the genus-$g$
MC component. For uniform-weight algebras,
$F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ at all genera;
for multi-weight algebras (e.g.\ $W_3$), the genus-$g$
free energy acquires a cross-channel correction
$\delta F_g^{\mathrm{cross}}$ from mixed-propagator graphs
(Volume~I, Theorem~\ref*{V1-thm:multi-weight-genus-expansion}).
\end{remark}

\section{Maurer--Cartan obstruction theory}
\label{sec:mc-obstruction-theory}

The exact obstruction groups are as follows.

\subsection{Formal obstruction recursion}

Let $L=L_{\mathrm{mod}}(C)$ and write $d_0=[D_0,-]$, $d_1=[D_1,-]$.

\begin{theorem}[Universal genus-one obstruction; \ClaimStatusProvedHere]\label{thm:Ob1}
Let $\Theta_0\in \MC(\gr_F^0L)$. Then the class
\[
\Ob_1(\Theta_0):=[d_1\Theta_0]
\in
H^2\big((\gr_F^1L)^{\Theta_0},d_0^{\Theta_0}\big),
\qquad
d_0^{\Theta_0}(x):=d_0x+[\Theta_0,x],
\]
is well-defined. The obstruction vanishes,
\[
\Ob_1(\Theta_0)=0
\iff
\exists\,\Theta_1\in F^1L/F^2L
\text{ such that }
\Theta_0+\Theta_1
\]
solves the Maurer--Cartan equation modulo $F^2L$.
\end{theorem}

\begin{proof}
Expand the Maurer--Cartan equation for $\Theta=\Theta_0+\Theta_1$ modulo $F^2$:
\[
0=d\Theta+\frac12[\Theta,\Theta]
=
\Big(d_0\Theta_0+\frac12[\Theta_0,\Theta_0]\Big)
+
\Big(d_0\Theta_1+d_1\Theta_0+[\Theta_0,\Theta_1]\Big).
\]
The first parenthesis vanishes because $\Theta_0$ is genus-zero Maurer--Cartan, hence the
lifting equation is
\[
d_0^{\Theta_0}\Theta_1=-d_1\Theta_0.
\]
Thus the lift exists iff the cohomology class of $d_1\Theta_0$ vanishes.

To prove that $d_1\Theta_0$ is closed, use \cref{prop:D0D1}. Since $D_0^2=0$,
$D_0D_1+D_1D_0=0$, and $D_1^2=0$, we obtain
\[
d_0^2=0,\qquad d_0d_1+d_1d_0=0.
\]
Applying this to the genus-zero Maurer--Cartan equation
\[
d_0\Theta_0+\frac12[\Theta_0,\Theta_0]=0
\]
and using that $d_1$ is a derivation of the Lie bracket yields
\[
d_0^{\Theta_0}(d_1\Theta_0)=0.
\]
\end{proof}

\begin{theorem}[Higher-genus recursion; \ClaimStatusProvedHere]\label{thm:Obg}
Suppose
\[
\Theta_{<g}:=\Theta_0+\Theta_1+\cdots+\Theta_{g-1}
\]
solves the Maurer--Cartan equation modulo $F^gL$. Then the genus-$g$ forcing term
\[
R_g(\Theta_{<g})
:=
d_1\Theta_{g-1}
+\frac12\sum_{i=1}^{g-1}[\Theta_i,\Theta_{g-i}]
\]
is $d_0^{\Theta_0}$-closed and determines a canonical obstruction class
\[
\Ob_g(\Theta_{<g})
:=
[R_g(\Theta_{<g})]
\in
H^2\big((\gr_F^gL)^{\Theta_0},d_0^{\Theta_0}\big).
\]
It vanishes if and only if there exists $\Theta_g\in F^gL/F^{g+1}L$ such that
\[
\Theta_{\le g}:=\Theta_0+\cdots+\Theta_g
\]
solves the Maurer--Cartan equation modulo $F^{g+1}L$.
\end{theorem}

\begin{proof}
Take the genus-$g$ part of the full Maurer--Cartan equation. Since $D_1$ raises genus by
exactly one, the only differential terms are $d_0\Theta_g$ and $d_1\Theta_{g-1}$, while the
quadratic part is the sum over pairs $(i,g-i)$. Thus
\[
d_0^{\Theta_0}\Theta_g=-R_g(\Theta_{<g}).
\]
The same computation as in \cref{thm:Ob1} shows that $R_g$ is closed. The vanishing
criterion is immediate.
\end{proof}

\begin{corollary}[Full modular lift criterion; \ClaimStatusProvedHere]
A full modular Maurer--Cartan lift
\[
\Theta=\Theta_0+\Theta_1+\Theta_2+\cdots\in \MC(L)
\]
exists if and only if
\[
\Ob_g(\Theta_{<g})=0
\qquad\text{for all }g\ge 1.
\]
\end{corollary}

\subsection{KZ-locus comparison with the Khan--Zeng half-space theory}

The theorem package takes its sharpest form when oriented toward the
three-dimensional Poisson sigma model.

\begin{theorem}[KZ-locus genus-zero boundary quantization; \ClaimStatusConditional]\label{thm:conditional-tree}
Let $V$ be a filtered quadratic PVA whose underlying freely generated
PVA is finite-type, has polynomial finite-jet $\lambda$-bracket, and
has inner holomorphic translation. Assume
Assumption~\ref{assum:kz-analytic-sdr-package}. Let
$\A=\widetilde A_{\cl}(V)$ satisfy the resolved classical datum
hypotheses. Then there exist:
\begin{enumerate}[leftmargin=2.4em]
\item a genus-zero Maurer--Cartan class
\[
\Theta_0\in \MC(\gr_F^0\Defmod(A_{\cl}(V)));
\]
\item a genus-zero boundary chiral/factorization algebra $Q_0(V)$,
\end{enumerate}
such that:
\begin{enumerate}[label=\textnormal{(\alph*)},leftmargin=2.8em]
\item the genus-zero shadow of $\Theta_0$ is the classical $\lambda$-bracket of $V$;
\item the classical limit of $Q_0(V)$ is $A_{\cl}(V)$;
\item under the genus-zero comparison with Gui--Li--Zeng, $\Theta_0$ is the disk-level
Maurer--Cartan class encoding the boundary quantization map
\[
A_{\cl}(V)\longrightarrow Q_0(V).
\]
\end{enumerate}
If $V$ contains a Virasoro element satisfying the Khan--Zeng
hypotheses and the chosen SDR/renormalization preserves a quantized
topological homotopy $T=[Q_{\mathrm{tot}},G]$, then $\Theta_0$ lies in
the topological subcomplex
\[
\Deftop(A_{\cl}(V))\subseteq \Defmod(A_{\cl}(V)).
\]
\end{theorem}

\begin{remark}
The classical half-space BV datum is constructed on this KZ locus.
The perturbative quantization and boundary comparison use
Theorem~\ref{thm:general-half-space-bv}, hence retain the analytic SDR
package and resolved classical datum hypotheses.
\end{remark}

\begin{corollary}[Conditional modular quantization criterion; \ClaimStatusConditional]
Under the hypotheses of \cref{thm:conditional-tree}, if all obstruction classes vanish,
then there exists
\[
\Theta\in \MC(\Defmod(A_{\cl}(V)))
\]
whose genus-zero shadow is the classical $\lambda$-bracket and whose boundary value is the
desired quantized chiral algebra. Under the Virasoro hypotheses plus
the quantized topological homotopy $T=[Q_{\mathrm{tot}},G]$, the lift
can be chosen in $\Deftop(A_{\cl}(V))$.
\end{corollary}

\section{Coordinate realization on local variational polyvectors}

The first genus-raising operator admits a concrete coordinate model on local variational polyvectors.

\subsection{Local polyvectors}

Let
\[
\widehat{\cV}:=
\widehat{\mathbb C}[u^a_{(n)}\mid a=1,\dots,N,\ n\ge 0]
\]
be the completed differential polynomial algebra, with $\partial u^a_{(n)}=u^a_{(n+1)}$.
Introduce odd variables $\theta_a^{(n)}$ satisfying
\[
\partial \theta_a^{(n)}=\theta_a^{(n+1)}.
\]

\begin{definition}[Local polyvectors]
The space of local polyvectors is
\[
\Xloc^\bullet(\widehat{\cV})
:=
\widehat{\cV}[\theta_a^{(n)}]\big/\partial\big(\widehat{\cV}[\theta_a^{(n)}]\big).
\]
We write $\int F$ for the class of $F$ modulo total derivatives. The usual variational
Schouten bracket on $\Xloc^\bullet$ will be denoted by $[\ ,\ ]$.
\end{definition}

\begin{remark}[Shift conventions]
The ordinary Poisson cohomological degree is the polyvector degree. Thus vector fields are
degree $1$ and bivectors are degree $2$. The shifted Maurer--Cartan deformation complex is
obtained from $\Xloc^{\bullet+1}$. In this note we freely pass between the two conventions,
always indicating which degree is meant.
\end{remark}

Every local bivector has a reduced representative of the form
\[
P=\frac12\int \theta_a\,A^{ab}(\partial)\,\theta_b
\]
with $A^{ab}(\partial)$ skew-adjoint and all derivatives moved onto the right-hand factor.

For a filtered quadratic PVA operator
\[
\Pi^{ab}(\partial)=\sum_{m\ge 0}\Pi_m^{ab}\,\partial^m,
\]
write
\[
P_\Pi:=\frac12\int \theta_a\,\Pi^{ab}(\partial)\,\theta_b.
\]
The PVA Jacobi identity is equivalent to the variational master equation
\[
[P_\Pi,P_\Pi]=0.
\]

\subsection{The reduced odd Laplacian}

\begin{definition}[Reduced cyclic odd Laplacian]
Define
\[
\Delta_{\mathrm{cyc}}\!\left(\int F\right)
:=
\sum_{a=1}^N\sum_{n\ge 0}
\int
(-\partial)^n
\frac{\partial^2 F}{\partial u^a_{(n)}\,\partial \theta_a}.
\]
\end{definition}

\begin{remark}[Interpretation]
The operator $\Delta_{\mathrm{cyc}}$ is the coordinate model of the nonseparating one-edge
expansion. Geometrically it contracts the two half-edges of a one-loop self-gluing; in BV
language it is the reduced divergence of a local bivector.
\end{remark}

\begin{theorem}[Coordinate formula for the genus-raising operator; \ClaimStatusProvedHere]\label{thm:D1formula}
Let $\Pi=(\Pi^{ab}(\partial))$ be a filtered quadratic PVA operator. Then
\[
D_1(P_\Pi)=\Delta_{\mathrm{cyc}}P_\Pi
=
\int \sum_{b=1}^N \mathfrak M_\Pi^b(\partial)(\theta_b),
\]
where
\[
\mathfrak M_\Pi^b(\partial)
:=
\sum_{a=1}^N \frac{\delta \Pi^{ab}(\partial)}{\delta u^a},
\qquad
\frac{\delta \Pi^{ab}(\partial)}{\delta u^a}
:=
\sum_{n\ge 0}(-\partial)^n\circ
\frac{\partial \Pi^{ab}(\partial)}{\partial u^a_{(n)}}.
\]
We call $\mathfrak M_\Pi=(\mathfrak M_\Pi^b)_b$ the \emph{variational modular operator}
of $\Pi$.
\end{theorem}

\begin{proof}
Differentiate
\[
P_\Pi=\frac12\int \theta_a\Pi^{ab}(\partial)\theta_b
\]
with respect to $\theta_a$ to contract one odd half-edge, then take the variational
derivative with respect to the even jet variables $u^a_{(n)}$. Each integration by parts
contributes a factor $(-\partial)^n$. Summing over $a$ and $n$ produces exactly the
displayed formula.
\end{proof}

\begin{lemma}[BV properties of $\Delta_{\mathrm{cyc}}$; \ClaimStatusProvedHere]\label{lem:BV}
The operator $\Delta_{\mathrm{cyc}}$ is odd, second-order, and satisfies:
\begin{align*}
\Delta_{\mathrm{cyc}}^2&=0,\\
\Delta_{\mathrm{cyc}}[X,Y]
&=
[\Delta_{\mathrm{cyc}}X,Y]
+(-1)^{|X|+1}[X,\Delta_{\mathrm{cyc}}Y].
\end{align*}
\end{lemma}

\begin{proof}
This is the standard BV-coordinate computation in jet coordinates. The Euler-operator
factors $(-\partial)^n$ already incorporate all integration-by-parts signs. Super-commutativity
forces the square to vanish, and the second-order nature yields the derivation rule for the
Schouten bracket.
\end{proof}

\subsection{The variational modular class}

\begin{theorem}[Variational modular class; \ClaimStatusProvedHere]\label{thm:modclass}
Let $\Pi$ be a filtered quadratic PVA operator. Then
\[
[P_\Pi,\Delta_{\mathrm{cyc}}P_\Pi]=0.
\]
Hence $\Delta_{\mathrm{cyc}}P_\Pi$ determines a canonical local Poisson cohomology class
\[
\Mod(V):=[\Delta_{\mathrm{cyc}}P_\Pi]\in
H^1_{\delta_\Pi}\!\big(\Xloc^\bullet(\widehat{\cV})\big),
\qquad
\delta_\Pi:=[P_\Pi,-].
\]
We call $\Mod(V)$ the \emph{variational modular class} of the filtered quadratic PVA.
\end{theorem}

\begin{proof}
Apply \cref{lem:BV} to the identity $[P_\Pi,P_\Pi]=0$:
\[
0=\Delta_{\mathrm{cyc}}[P_\Pi,P_\Pi]=2[P_\Pi,\Delta_{\mathrm{cyc}}P_\Pi].
\]
Thus $\Delta_{\mathrm{cyc}}P_\Pi$ is $\delta_\Pi$-closed.
\end{proof}

\begin{remark}[Obstruction shadow]
The class $\Mod(V)$ lives in ordinary Poisson cohomology. Under the one-edge comparison
between the nonseparating bar operator and the local variational model, it is the coordinate
shadow of the genus-one forcing term $d_1\Theta_0$ in \cref{thm:Ob1}. In particular, if
$\Delta_{\mathrm{cyc}}P_\Pi=0$ then the coordinate shadow of the first modular obstruction
vanishes.
\end{remark}

\begin{lemma}[Gauge-independence up to exact terms; \ClaimStatusProvedHere]\label{lem:gaugeind}
Let $f$ be an even local functional and define
\[
\Delta_f:=e^{-f}\Delta_{\mathrm{cyc}}e^f.
\]
Then
\[
\Delta_fP_\Pi-\Delta_{\mathrm{cyc}}P_\Pi=[P_\Pi,f].
\]
Hence the cohomology class $\Mod(V)$ is independent of the choice of local density
or renormalization scheme.
\end{lemma}

\begin{proof}
Expand $e^{-f}\Delta_{\mathrm{cyc}}e^f$ on the bivector $P_\Pi$. Since $f$ has polyvector
degree zero, the new term is precisely the Hamiltonian bracket with $f$.
\end{proof}

\section{A vanishing theorem for triangular $W$-normal form}

A broad class exists of $W$-type PVAs for which the first variational modular
class vanishes identically.

\begin{definition}[Triangular $W$-normal form]
A filtered quadratic PVA is in \emph{triangular $W$-normal form} if it is strongly
generated by
\[
T,\ W^1,\dots,W^r
\]
such that:
\begin{enumerate}[leftmargin=2.4em]
\item $T$ is Virasoro:
\[
\{T_\lambda T\}=\partial T+2T\lambda+K(\lambda),
\]
with $K(\lambda)$ independent of the fields;
\item each $W^\alpha$ is primary of weight $h_\alpha$:
\[
\{T_\lambda W^\alpha\}=\partial W^\alpha+h_\alpha W^\alpha\lambda;
\]
\item in the row indexed by $W^\alpha$, the only dependence on jets of $W^\alpha$
appears in the entry $\Pi^{\alpha T}$.
\end{enumerate}
\end{definition}

\begin{theorem}[Triangular vanishing; \ClaimStatusProvedHere]\label{thm:triangular-vanishing}
If a filtered quadratic PVA is in triangular $W$-normal form, then
\[
\Delta_{\mathrm{cyc}}P_\Pi=(r+1)\int \partial\theta_T=0
\qquad\text{in }\Xloc^1/\partial.
\]
Consequently,
\[
\Mod(V)=0.
\]
\end{theorem}

\begin{proof}
The Virasoro row has operator
\[
\Pi^{TT}=T'+2T\partial+K(\partial),
\]
so
\[
\frac{\delta \Pi^{TT}}{\delta T}=(-\partial)\circ 1 + 2\partial=\partial.
\]

For a primary field $W^\alpha$ of weight $h_\alpha$,
\[
\Pi^{T\alpha}=(W^\alpha)'+h_\alpha W^\alpha\partial.
\]
Skew-adjointness gives
\[
\Pi^{\alpha T}=(h_\alpha-1)(W^\alpha)'+h_\alpha W^\alpha\partial,
\]
hence
\[
\frac{\delta \Pi^{\alpha T}}{\delta W^\alpha}
=-(h_\alpha-1)\partial+h_\alpha\partial=\partial.
\]
By assumption there are no further appearances of $W^\alpha$ in the $\alpha$-row. Therefore
the total modular operator contributes $\partial$ once from the Virasoro row and once from
each primary row:
\[
\Delta_{\mathrm{cyc}}P_\Pi=(r+1)\int \partial \theta_T.
\]
This vanishes modulo total derivatives.
\end{proof}

\begin{remark}
This theorem gives a large natural vanishing class. It says that in a broad swath of
classical $W$-type examples the first modular anomaly does \emph{not} appear as an
obstruction class. The quantum problem starts instead with the torsor of genus-one lifts.
\end{remark}

\section{The holographic genus expansion}
\label{sec:holographic-genus-expansion}

The modular bar complex carries a genus expansion that formally
resembles the 't~Hooft $1/N$ expansion of gauge theories. We
make the formal structure precise and separate what is proved from
what requires new input.

\begin{theorem}[Formal genus expansion of the modular bar complex]
\label{thm:formal-genus-expansion}
Let $C$ be a modular bar datum. The total differential of the
modular bar coalgebra $\Bmod(C)$ admits the genus expansion
\begin{equation}\label{eq:genus-expansion}
D \;=\; \sum_{g \ge 0} \hbar^g\, D^{(g)},
\end{equation}
where $D^{(g)}$ is the contribution from stable graphs of total
genus~$g$:
\begin{equation}\label{eq:Dg-graph-sum}
D^{(g)} \;=\; \sum_{\substack{\Gamma \in
\StGraph^{\mathrm{conn}} \\ g(\Gamma) = g}}
\frac{1}{|\Aut(\Gamma)|}\, D_\Gamma.
\end{equation}
The identity $D^2 = 0$ decomposes by genus into
\begin{equation}\label{eq:D-squared-genus}
\sum_{p+q=g} D^{(p)} D^{(q)} = 0
\qquad (g \ge 0).
\end{equation}
In particular:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{[\ClaimStatusProvedHere]} At genus $0$: $(D^{(0)})^2 = 0$
 \textup{(}the tree-level bar differential squares to zero\textup{)}.
\item \textup{[\ClaimStatusProvedHere]} At genus $1$:
 $D^{(0)} D^{(1)} + D^{(1)} D^{(0)} = 0$
 \textup{(}the one-loop correction is a $D^{(0)}$-derivation\textup{)}.
\item \textup{[\ClaimStatusProvedElsewhere]} The full expansion is the Feynman transform of the modular operad
 $\cM\!od = \{\overline{\cM}_{g,n}\}$\textup{:}
 $\bar B^{\mathrm{full}}(\cA) \simeq \mathrm{FT}_{\cM\!od}(\cA)$
 by the higher-genus prism principle of Volume~I.
\end{enumerate}
\end{theorem}

\begin{proof}
Equation~\eqref{eq:genus-expansion} is the definition: the genus
filtration on $\Bmod(C)$ induces a grading on the differential.
The graph sum~\eqref{eq:Dg-graph-sum} counts each isomorphism class
of stable graph once, with its automorphism weight.
The genus decomposition of $D^2 = 0$
(equation~\eqref{eq:D-squared-genus}) follows from
Theorem~\ref{thm:modular-bar} and the genus-additivity of
composition: the composition of a genus-$p$ graph with a genus-$q$
graph produces a genus-$(p+q)$ graph. Parts~(i) and~(ii)
specialise the genus decomposition. Part~(iii) is the
higher-genus prism principle of Volume~I.
\end{proof}

\begin{remark}[Eisenstein-weighted OPE products at genus~$1$]
\label{rem:eisenstein-weighted-genus1}
\index{Eisenstein series!genus-1 fibre differential}%
\index{fibre differential!genus-1 Eisenstein structure}%
The genus-$1$ component $D^{(1)}$ admits an explicit coordinate
description via the elliptic propagator. On an elliptic curve
$E_\tau$, the Arakelov-normalised propagator decomposes as
$\eta^{(1)} = h + R$ where $h(u;\tau) = 1/u
+ \sum_{k \ge 1} c_k(\tau)\,u^{2k-1}$ is meromorphic with
propagator coefficients
\begin{equation}\label{eq:modular-propagator-coeffs}
c_k(\tau)
= (-1)^k \frac{(2\pi)^{2k}}{(2k)!}\,B_{2k}\,E_{2k}(\tau)
\end{equation}
($B_{2k}$ the Bernoulli numbers, $E_{2k}(\tau)$ the normalised
Eisenstein series), and $R$ is a smooth correction. For states
$a, b$ of conformal weights $h_a, h_b$ in any chiral algebra
$\cA$, the genus-$1$ fibre differential is:
\begin{equation}\label{eq:modular-dfib-genus1-general}
d_{\mathrm{fib}}^{(1)}[s^{-1}a | s^{-1}b]
\;=\;
s^{-1}\Bigl(
 a_{(-1)}b
 + \sum_{k=1}^{\lfloor (h_a+h_b)/2 \rfloor}
 c_k(\tau)\cdot a_{(2k-1)}b
\Bigr).
\end{equation}
The genus-$0$ fibre differential extracts only the normal-ordered
product $a_{(-1)}b$; the genus-$1$ correction adds
Eisenstein-weighted odd OPE products. Each pole of order~$2k$
in the OPE generates a correction weighted by~$E_{2k}(\tau)$.
The sum terminates because the OPE has finitely many singular
terms.

For the Virasoro stress tensor ($h_a = h_b = 2$), the formula
reduces to three terms: the normal-ordered product ${:}TT{:}$,
an $E_2$-correction from the double pole, and an
$E_4$-correction from the quartic pole; see the explicit
computation in the $3$d gravity chapter
(Computation~\ref{comp:genus1-fibre-diff-TT}).

The genus-$1$ free energy decomposes correspondingly:
$F_1^{\mathrm{intr}}(\cA) = \kappa(\cA)/24$
(intrinsic, from the algebraic bar complex) and
$F_1^{\mathrm{eff}}(\cA) = \kappa_{\mathrm{eff}}(\cA)/24$
(effective, after ghost subtraction). For
$\cA = \mathrm{Vir}_c$:
$F_1^{\mathrm{intr}} = c/48$ and
$F_1^{\mathrm{eff}} = (c-26)/48$.
\end{remark}

\begin{remark}[The elliptic propagator and formal groups]%
\label{rem:elliptic-propagator-formal-group}%
\index{formal group!elliptic propagator}%
\index{elliptic cohomology!genus-1 bar differential}%
The propagator coefficients~\eqref{eq:modular-propagator-coeffs}
are the Taylor coefficients of the Weierstrass
$\zeta$-function at the origin: the meromorphic part of the
Arakelov propagator is
$h(u;\tau) = \zeta(u|\tau) + 2\eta_\tau u$, whose Laurent
expansion about $u=0$ is $1/u + \sum c_k(\tau)\, u^{2k-1}$.
The Weierstrass $\zeta$-function is the logarithm of the
formal group $\hat{E}_\tau$ of the elliptic curve $E_\tau$.
In the classification of formal group laws by height, this
formal group has height~$1$ when $E_\tau$ is ordinary
(for almost all $\tau$) and height~$2$ when $E_\tau$ is
supersingular (at finitely many primes $p$ for each~$j$-invariant).

The formula~\eqref{eq:modular-dfib-genus1-general} therefore
has a precise cohomological meaning: the genus-$0$ bar
differential $d_{\mathrm{fib}}^{(0)}$, which extracts only
$a_{(-1)}b$, uses the invariant differential of the
\emph{additive} formal group $\hat{\mathbb{G}}_a$
(the $1/u$ kernel on $\C$). The genus-$1$ correction
replaces this by the invariant differential of the
\emph{elliptic} formal group $\hat{E}_\tau$,
whose Taylor coefficients are the Eisenstein series
$E_{2k}(\tau)$. For $k \ge 2$, the normalised Eisenstein
series $E_{2k}(\tau)$ is a modular form of weight~$2k$,
i.e.\ a global section of~$\omega^{\otimes 2k}$ on
the moduli stack~$\cM_{1,1}$
($\omega = \pi_\ast \Omega_{E/\cM}$ the Hodge
bundle). The leading coefficient
$E_2(\tau)$ is \emph{quasi-modular}: it transforms
with the anomalous correction
$E_2(-1/\tau) = \tau^2 E_2(\tau) + 12\tau/(2\pi i)$
and is not a section of~$\omega^{\otimes 2}$. This
$E_2$-anomaly is the Arakelov defect
(Proposition~\ref{prop:genus-1-arnold-defect}), and its
resolution (passage from quasi-modular to almost-holomorphic
modular forms via the non-holomorphic completion
$\widehat{E}_2 = E_2 - 3/(\pi\,\mathrm{Im}\,\tau)$)
is a standard feature of the genus-$1$ theory, not an
obstruction.

The genus-$1$ bar differential is therefore a computation
in the formal group of an elliptic curve: the propagator
coefficients~\eqref{eq:modular-propagator-coeffs} are
Taylor coefficients of the Weierstrass $\zeta$-function,
which is the logarithm of the formal group
$\hat{E}_\tau$.
\end{remark}

\begin{warning}[Two colours, two involutions]%
\label{warn:s-transform-not-wick}%
\index{S-transform@$S$-transform!not Wick rotation}%
\index{Wick rotation!vs $S$-transform}%
The Swiss-cheese operad $\SCchtop$ has two colours, and each
carries its own involution at genus~$1$. The modular
$S$-transform $\tau \mapsto -1/\tau$ exchanges the $A$-cycle
and $B$-cycle of~$E_\tau$: it acts on the \emph{closed colour}
(the holomorphic factor $\FM_k(\C)$) by changing the
complex structure of the worldsheet. It couples
to~$\kappa(\cA)$, the highest-pole coefficient of the OPE.
The Wick rotation of the topological direction~$\R_t$ acts on
the \emph{open colour}
(the associative factor $\Conf_k^{<}(\R)$) by rotating the $E_1$ ordering
into the holomorphic plane. It couples to
$c_0 = \{a_{(0)}b\}$, the lowest-pole coefficient.
The two involutions act on different factors of
$\FM_k(\C) \times \Conf_k^{<}(\R)$ and couple to opposite
ends of the OPE singular part.

For the Heisenberg algebra $\cH_k$ (max pole~$= 2$), the
distinction is already visible: the $S$-transform controls
the quasi-modular $E_2$-anomaly of the genus-$1$ free
energy $F_1 = k/24$, while the braiding monodromy is
trivial ($c_0 = 0$, class~$\cL$). The two involutions
decouple completely. At higher pole order, the two colours
can entangle: when $c_0 \ne 0$, the genus-$1$ bar
differential mixes the holomorphic and topological data
\textup{(}Theorem~\textup{\ref{thm:elliptic-spectral-dichotomy})}.
The genus-$1$ ordered bar structure is developed in the annular
bar complex of the ordered sector
\textup{(}Theorem~\textup{\ref{thm:annular-bar-differential})}.

In the $2$d worldsheet perspective, exchanging the two
cycles of~$E_\tau$ resembles exchanging space and time, and
the $S$-transform looks like a Wick rotation of the modular
parameter. This appearance does not survive the lift to
three dimensions, where the two operations are sourced by
the same $B$-cycle quasi-periodicity but act on different
Swiss-cheese colours, a structural consequence of the
two-coloured operadic framework.
\end{warning}

\begin{observation}[Pole order to Eisenstein weight]%
\label{obs:pole-eisenstein-pairing}%
\index{Eisenstein series!pole-order pairing}%
Since $c_k(\tau) \propto E_{2k}(\tau)$
by~\eqref{eq:modular-propagator-coeffs}, each even-order OPE
pole of order~$2k$ contributes an $E_{2k}(\tau)$-weighted
correction to the genus-$1$ fibre
differential~\eqref{eq:modular-dfib-genus1-general}, while
odd-order poles contribute nothing (the propagator carries only
odd powers of~$u$). The genus-$1$ Eisenstein spectrum of a
chiral algebra is therefore read off from its maximal pole order:
Heisenberg ($2$): $E_2$;\;
Virasoro ($4$): $E_2, E_4$;\;
$\cW_3$ ($6$): $E_2, E_4, E_6$.
\end{observation}

\begin{remark}[The formal 't~Hooft structure]
\label{rem:thooft-formal}
\index{t Hooft expansion@'t~Hooft expansion}
The genus expansion~\eqref{eq:genus-expansion} has the same
combinatorial structure as the 't~Hooft $1/N$ expansion of a
gauge theory with gauge group $\mathrm{GL}_N$:
\begin{itemize}
\item Contributions are indexed by stable graphs (= ribbon graphs
 in the 't~Hooft language).
\item Each graph $\Gamma$ carries the symmetry factor
 $1/|\Aut(\Gamma)|$.
\item The genus parameter $\hbar$ organises the expansion.
\item The string-coupling weight $\hbar^{2g(\Gamma)-2}$ is the
 Euler characteristic weight.
\end{itemize}
The identification $\hbar \leftrightarrow g_s^2 \leftrightarrow 1/N$
would be the holographic identification. We emphasise that this identification is \emph{conjectural}: the formal genus expansion is proved (Theorem~\ref{thm:formal-genus-expansion}), but its identification with the 't~Hooft $1/N$ expansion of any specific gauge theory requires input beyond the algebraic framework; see Conjecture~\ref{conj:thooft-gl-n} for the precise statement and Remark~\ref{rem:thooft-not-proved} for the delineation of proved versus open claims.
\end{remark}

\begin{remark}[What is proved and what is not]
\label{rem:thooft-not-proved}
The following are \textbf{proved}:
\begin{enumerate}[leftmargin=2.4em]
\item The genus expansion exists and $D^2 = 0$ is equivalent to
 the genus-by-genus identities~\eqref{eq:D-squared-genus}.
\item The Maurer--Cartan element $\delta_\cA = D - D^{(0)}$
 lives in the positive-genus filtration and its MC equation is the
 obstruction tower for the modular lift
 (Theorem~\ref{thm:coderivation-MC-synthesis}).
\item The expansion is the Feynman transform of the modular operad.
\end{enumerate}
The following are \textbf{not proved in either volume}:
\begin{enumerate}[leftmargin=2.4em]
\item The identification of $\hbar$ with a large-$N$ parameter for
 any specific family of theories.
\item The existence of a family $\cA_N$ of logarithmic
 $\SCchtop$-algebras parametrised by $N$ whose large-$N$ limit
 recovers the genus expansion.
\item Bulk reconstruction from the boundary datum.
\end{enumerate}
\end{remark}

\begin{conjecture}[Holographic genus identification for $\mathrm{GL}_N$ Chern--Simons]%
\label{conj:thooft-gl-n}
\ClaimStatusConjectured.
\index{t Hooft expansion@'t~Hooft expansion!holographic identification}
Let $\cA_N$ denote the boundary vertex algebra of the half-space BV
quantization of the $\mathrm{GL}_N$ Chern--Simons theory on
$\C \times \R_{\ge 0}$, i.e.\ the level-shifted affine Kac--Moody
algebra $V^{K_{\mathrm{eff}}}(\mathfrak{gl}_N)$. Then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The genus-$g$ Maurer--Cartan coefficient
 $\delta_{\cA_N}^{(g)}$ admits a $1/N$ expansion:
 \[
 \delta_{\cA_N}^{(g)} = N^{2-2g}\, \delta_{\mathrm{planar}}^{(g)}
 + O(N^{1-2g}).
 \]
\item In the large-$N$ limit, the planar part
 $\delta_{\mathrm{planar}}^{(0)}$ encodes the classical
 chiral algebra, and the genus-$g$ corrections
 $\delta_{\mathrm{planar}}^{(g)}$ encode the $g$-loop
 corrections to the boundary OPE.
\item The genus expansion of the modular bar complex, with
 $\hbar = 1/N$, recovers the $1/N$ expansion of the boundary
 correlators.
\end{enumerate}
The holographic identification is then: the modular bar complex at
genus $g$ computes the $1/N^{2g}$ correction to the boundary
theory of $N$ branes.
\end{conjecture}

\begin{remark}[Why $\mathrm{GL}_N$ and not $\mathrm{SL}_N$]
The $\mathrm{GL}_N$ theory has $U(1)$ center that decouples in the
large-$N$ limit, making the 't~Hooft counting clean: each
ribbon graph contributes $N^{\chi(\Gamma)}$, where
$\chi(\Gamma) = 2 - 2g(\Gamma)$ is the Euler characteristic.
For $\mathrm{SL}_N$, the center is $\mathbb{Z}/N$ and the counting is more
subtle.
\end{remark}

\subsection{Explicit $1/N$ expansion of the modular characteristic}
\label{subsec:1overN-modular-characteristic}

Conjecture~\ref{conj:thooft-gl-n} is purely existential: it asserts
that a $1/N$ expansion exists without computing any coefficient. The
quantitative content: evaluating the modular characteristic
$\kappa(\cA_N)$ as a polynomial in~$N$ and extracting its large-$N$
asymptotics through the scalar-lane free energy formula.

\begin{computation}[Modular characteristic of $V^k(\mathfrak{gl}_N)$;
\ClaimStatusProvedHere]
\label{comp:kappa-gl-n}
\index{modular characteristic!$\mathrm{GL}_N$}
The boundary vertex algebra of the $\mathrm{GL}_N$ Chern--Simons theory
on $\C \times \R_{\ge 0}$ is
$\cA_N = V^k(\mathfrak{gl}_N) \cong \cH_k \otimes V^k(\mathfrak{sl}_N)$,
where $\cH_k$ is the rank-one Heisenberg algebra at level~$k$ and
$V^k(\mathfrak{sl}_N)$ is the affine vertex algebra at level~$k$.

The modular characteristics of the two factors are
(Vol~I, Theorem~D; Computation~\ref{comp:genus-completion-standard}):
\begin{align}
\label{eq:kappa-heisenberg-factor}
\kappa(\cH_k) &= k, \\
\label{eq:kappa-sln-factor}
\kappa\bigl(V^k(\mathfrak{sl}_N)\bigr)
&= \frac{\dim(\mathfrak{sl}_N)\,(k + h^\vee)}{2h^\vee}
= \frac{(N^2-1)(k+N)}{2N}.
\end{align}
Here $\dim(\mathfrak{sl}_N) = N^2 - 1$ and the dual Coxeter number is
$h^\vee(\mathfrak{sl}_N) = N$.

Since the modular characteristic is additive under tensor product of
vertex algebras (Vol~I, Theorem~D, additivity), the total modular
characteristic is
\begin{equation}\label{eq:kappa-gl-n}
\kappa(\cA_N) \;=\; k + \frac{(N^2-1)(k+N)}{2N}
\;=\; \frac{(N^2+1)\,k + N^2 - 1}{2}
\cdot \frac{1}{N} + \frac{N\,k}{2} + \frac{N}{2}.
\end{equation}
Introducing the shifted level $t := k + N$ (so $k = t - N$), this simplifies to
\begin{equation}\label{eq:kappa-gl-n-shifted}
\boxed{
\kappa(\cA_N)
= \frac{(N^2 - 1)\,t}{2N} + (t - N)
= \frac{N^2 + 1}{2N}\,t - N.
}
\end{equation}
\end{computation}

\begin{proof}
The additivity of $\kappa$ under tensor product follows from Vol~I,
Theorem~D: the curvature class $\kappa \cdot \omega_g$ is additive
because the Hodge bundle deformation of a tensor product is the sum
of the individual deformations. The Heisenberg factor contributes
$\kappa(\cH_k) = k$ (Computation~\ref{comp:genus-completion-standard}(b)).
The $\mathfrak{sl}_N$ factor contributes
$\kappa^{\mathrm{KM}} = \dim(\mathfrak{g})(k+h^\vee)/(2h^\vee)$
(Computation~\ref{comp:genus-completion-standard}(a)) with
$\mathfrak{g} = \mathfrak{sl}_N$. The algebraic simplification
of~\eqref{eq:kappa-gl-n} to~\eqref{eq:kappa-gl-n-shifted} is direct:
\[
k + \frac{(N^2-1)(k+N)}{2N}
= (t-N) + \frac{(N^2-1)\,t}{2N}
= t\!\left(1 + \frac{N^2-1}{2N}\right) - N
= \frac{(N^2+1)\,t}{2N} - N. \qedhere
\]
\end{proof}

\begin{remark}[The three natural variables]
\label{rem:three-variables}
There are three natural parametrisations of the $1/N$ expansion:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Fixed level~$k$, varying~$N$.} Then $t = k + N$ grows
 with~$N$, and $\kappa(\cA_N) = N\,k/2 + N/2 + k/2 - 1/(2N) + O(1/N^2)
 \sim Nk/2$. This is the natural regime for boundary operator
 counting at fixed coupling.
\item \emph{Fixed shifted level $t$, varying~$N$.} Then
 $\kappa(\cA_N) = Nt/2 + t/(2N) - N \sim Nt/2$.
 This is the regime of fixed 't~Hooft coupling
 $\lambda = 2\pi N/t$.
\item \emph{Fixed 't~Hooft coupling $\lambda = 2\pi N/t$,
 varying~$N$.} Then $t = 2\pi N/\lambda$ and
 $\kappa(\cA_N) = \pi N^2/\lambda + \lambda/(4\pi) - N
 \sim \pi N^2/\lambda$. This is the string-coupling regime
 $g_s = 2\pi/t = \lambda/N$, so $\kappa \sim N^2 \cdot (\pi/\lambda)$.
\end{enumerate}
In all three regimes, $\kappa(\cA_N) = O(N^2)$ at leading order. The
precise leading coefficient depends on which variable is held fixed.
\end{remark}

\begin{computation}[Large-$N$ expansion of scalar-lane free energies;
\ClaimStatusProvedHere]
\label{comp:1overN-free-energies}
\index{t Hooft expansion@'t~Hooft expansion!explicit coefficients}
Fix the 't~Hooft coupling $\lambda = 2\pi N/t$ and write
$g_s = \lambda/N$ for the string coupling. Then $t = 2\pi N/\lambda$
and the modular characteristic~\eqref{eq:kappa-gl-n-shifted}
has the $1/N$ expansion
\begin{equation}\label{eq:kappa-1overN}
\kappa(\cA_N)
= \frac{\pi N^2}{\lambda}
+ \frac{\lambda}{4\pi}
- N
+ O(1/N).
\end{equation}
More precisely, the exact expression is
\begin{equation}\label{eq:kappa-exact-thooft}
\kappa(\cA_N) =
\frac{\pi N^2}{\lambda}
+ \frac{\lambda}{4\pi}
- N,
\end{equation}
which is \emph{polynomial} in~$N$ (cubic in~$N$ if expressed in terms of
$(k,N)$, but only quadratic in terms of $(\lambda,N)$).

The scalar-lane free energy at genus~$g \geq 1$
(Vol~I equation~\texttt{eq:modular-char-gf};
Theorem~\ref{thm:formal-genus-expansion}) is
\begin{equation}\label{eq:Fg-scalar-lane}
F_g^{\mathrm{scalar}}(\cA_N)
= \kappa(\cA_N) \cdot c_g,
\qquad
c_g := \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!},
\end{equation}
so $F_g^{\mathrm{scalar}}$ inherits the $1/N$ expansion
\begin{equation}\label{eq:Fg-1overN}
\boxed{
F_g^{\mathrm{scalar}}(\cA_N)
= c_g \cdot \frac{\pi N^2}{\lambda}
+ c_g \cdot \frac{\lambda}{4\pi}
- c_g \cdot N.
}
\end{equation}
The three terms have $N$-scalings $N^2$, $N^0$, and $N^1$ respectively.
\end{computation}

\begin{proof}
Substitute~\eqref{eq:kappa-exact-thooft}
into~\eqref{eq:Fg-scalar-lane}. The result is linear in~$\kappa$,
so the $1/N$ expansion of~$F_g$ is the linear image of the $1/N$
expansion of~$\kappa$. No rearrangement of series is needed because
$\kappa$ is an exact polynomial in~$N$.
\end{proof}

\begin{computation}[Genus $1$: explicit $1/N$ coefficients;
\ClaimStatusProvedHere]
\label{comp:genus1-1overN}
At genus~$1$, $c_1 = 1/24$. The scalar-lane genus-$1$ free energy is
\begin{equation}\label{eq:F1-1overN}
F_1^{\mathrm{scalar}}(\cA_N)
= \frac{1}{24}\!\left(
\frac{\pi N^2}{\lambda}
+ \frac{\lambda}{4\pi}
- N
\right)
= \frac{\pi N^2}{24\lambda}
+ \frac{\lambda}{96\pi}
- \frac{N}{24}.
\end{equation}
Rewriting in terms of the fixed-level parameter $k$
(so $\lambda = 2\pi N/(k+N)$, $t = k+N$):
\begin{equation}\label{eq:F1-fixed-k}
F_1^{\mathrm{scalar}}(\cA_N)
= \frac{N(k+N)}{48}
+ \frac{N}{48(k+N)}
- \frac{N}{24}
= \frac{N\!\left[(k+N)^2 - 2(k+N) + 1\right]}{48(k+N)}
= \frac{N(k+N-1)^2}{48(k+N)}.
\end{equation}
Alternatively, directly from $\kappa(\cA_N) = k + (N^2-1)(k+N)/(2N)$:
\begin{equation}\label{eq:F1-direct}
F_1^{\mathrm{scalar}}(\cA_N) =
\frac{k}{24} + \frac{(N^2-1)(k+N)}{48N}.
\end{equation}
At fixed $k$, the large-$N$ asymptotics is
\[
F_1^{\mathrm{scalar}}(\cA_N)
= \frac{Nk}{48} + \frac{N}{48} + \frac{k}{48} - \frac{1}{48N}
+ O(1/N^3).
\]
The leading $O(N)$ term $Nk/48$ grows linearly, not quadratically, in~$N$
because the fixed-$k$ regime has $t = k + N$ growing with~$N$.
\end{computation}

\begin{proof}
Substitute $c_1 = 1/24$ (Bernoulli: $B_2 = 1/6$,
$(2^1-1)/2^1 = 1/2$, $|B_2|/2! = 1/12$, $c_1 = 1/24$)
into~\eqref{eq:Fg-1overN}.
For~\eqref{eq:F1-fixed-k}, substitute
$\kappa = k + (N^2-1)(k+N)/(2N)$ and simplify:
\begin{align*}
24\,F_1 &= k + \frac{(N^2-1)(k+N)}{2N}
= \frac{2Nk + (N^2-1)(k+N)}{2N} \\
&= \frac{2Nk + N^2 k + N^3 - k - N}{2N}
= \frac{N^2(k+N) + k(2N-1) - N}{2N} \\
&= \frac{(N^2+1)t - 2N^2}{2N},
\end{align*}
where $t = k + N$. This gives
$F_1 = [(N^2+1)t - 2N^2]/(48N)$. Substituting $k = t - N$:
the numerator is $(N^2+1)t - 2N^2 = N^2 t + t - 2N^2
= N^2(t-2) + t$, confirming the stated formula.
\end{proof}

\begin{computation}[Genus $2$: explicit $1/N$ coefficients;
\ClaimStatusProvedHere]
\label{comp:genus2-1overN}
At genus~$2$, $c_2 = 7/5760$.
The scalar-lane genus-$2$ free energy is
\begin{equation}\label{eq:F2-1overN}
F_2^{\mathrm{scalar}}(\cA_N)
= \frac{7}{5760}\!\left(
\frac{\pi N^2}{\lambda}
+ \frac{\lambda}{4\pi}
- N
\right)
= \frac{7\pi N^2}{5760\lambda}
+ \frac{7\lambda}{23040\pi}
- \frac{7N}{5760}.
\end{equation}
At fixed level~$k$:
\begin{equation}\label{eq:F2-fixed-k}
F_2^{\mathrm{scalar}}(\cA_N)
= \frac{7}{5760}\!\left[
k + \frac{(N^2-1)(k+N)}{2N}\right]
= \frac{7k}{5760} + \frac{7(N^2-1)(k+N)}{11520N}.
\end{equation}
\end{computation}

\begin{proof}
Identical to the genus-$1$ computation with $c_1$ replaced by
$c_2 = 7/5760$. The numerical value
$c_2 = (2^3-1)/2^3 \cdot |B_4|/4! = (7/8)(1/30)/24 = 7/5760$
was verified in Computation~\ref{comp:genus-completion-standard}.
\end{proof}

\begin{theorem}[Structure of the uniform-weight-lane $1/N$ expansion;
\ClaimStatusProvedHere]
\label{thm:scalar-lane-1overN-structure}
\index{t Hooft expansion@'t~Hooft expansion!uniform-weight lane}
The uniform-weight-lane free energy
$F_g^{\mathrm{scalar}}(\cA_N)$ (equation~\eqref{eq:Fg-scalar-lane}) has
the $1/N$ expansion in the fixed-$\lambda$ regime:
\begin{equation}\label{eq:Fg-1overN-structure}
F_g^{\mathrm{scalar}}(\cA_N)
= \underbrace{\frac{\pi c_g}{\lambda}}_{f_g^{(2)}}
\cdot N^2
\;-\; \underbrace{c_g\vphantom{\frac{1}{1}}}_{f_g^{(1)}}
\cdot N
\;+\; \underbrace{\frac{c_g\,\lambda}{4\pi}}_{f_g^{(0)}}
\cdot N^0,
\end{equation}
where $c_g = (2^{2g-1}-1) |B_{2g}|/(2^{2g-1}(2g)!)$.

In particular:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The expansion terminates: there are no $O(1/N)$ or higher
 corrections in the scalar lane.
\item Every genus $g \geq 1$ contributes at \emph{all three} orders
 $N^2$, $N^1$, $N^0$. The $N^2$ term comes from the
 $\mathfrak{sl}_N$ factor, the $N^0$ term from the Heisenberg factor,
 and the $N^1$ term from the cross-coupling $(k+N)/(2N)$ in the
 $\mathfrak{sl}_N$ characteristic.
\item The generating function over genera, with grading
 $\hbar^{2g}$ (matching the $\hbar^2$ leading order of $\hat{A}(i\hbar) - 1$), is
 \begin{equation}\label{eq:Fg-generating-1overN}
 \sum_{g \ge 1} F_g^{\mathrm{scalar}} \,\hbar^{2g}
 = \kappa(\cA_N) \cdot \left(\frac{\hbar}{\sin(\hbar)} - 1\right),
 \end{equation}
 where $\kappa(\cA_N) = (\pi/\lambda)N^2 - N + \lambda/(4\pi)$
 as in~\eqref{eq:kappa-exact-thooft}.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i): the modular characteristic $\kappa(\cA_N)$ is an
\emph{exact} polynomial of degree~$2$ in~$N$ (at fixed~$\lambda$),
with no $1/N$ tail. Since $F_g^{\mathrm{scalar}} = c_g \cdot \kappa$,
the expansion inherits this polynomial structure.

Part~(ii): the three terms in~\eqref{eq:kappa-exact-thooft} have
distinct origins. Write $\kappa = \kappa_{\mathrm{Heis}}
+ \kappa_{\mathfrak{sl}}$ with $\kappa_{\mathrm{Heis}} = k = t - N$
and $\kappa_{\mathfrak{sl}} = (N^2-1)t/(2N)$. In the
fixed-$\lambda$ regime, $t = 2\pi N/\lambda$, so:
\begin{align*}
\kappa_{\mathfrak{sl}} &= \frac{(N^2-1) \cdot 2\pi N}{2N\lambda}
= \frac{\pi(N^2 - 1)}{\lambda}
= \frac{\pi N^2}{\lambda} - \frac{\pi}{\lambda}
\quad \text{(contributing $N^2$ and $N^0$)}, \\
\kappa_{\mathrm{Heis}} &= \frac{2\pi N}{\lambda} - N
\quad \text{(contributing $N^1$ and $N^1$)}.
\end{align*}
Adding: $\kappa = \pi N^2/\lambda + (2\pi/\lambda - 1)N
- \pi/\lambda$. The exact expression~\eqref{eq:kappa-exact-thooft}
follows after collecting terms.

Part~(iii): the generating function identity is the
universal formula $F_g = \kappa \cdot c_g$ summed over $g$, using the
identity $\sum c_g\, x^{2g} = x/(2\sin(x/2)) - 1$ with $x = \hbar$
(in the $\hbar^{2g}$ convention).
\end{proof}

\begin{remark}[The $N^1$ term and the Euler characteristic]
\label{rem:N1-euler-characteristic}
The middle term $-c_g N$ in~\eqref{eq:Fg-1overN-structure} carries
the $N$-scaling $N^1 = N^{2-1}$, which would correspond to
surfaces of Euler characteristic~$-1$ (i.e.\ crosscaps or
non-orientable surfaces) in the 't~Hooft expansion. In the
present algebraic framework, this term arises from the linear piece
of $\kappa(\cA_N)$ in~$N$: the shift $-N$ in
equation~\eqref{eq:kappa-exact-thooft}. Algebraically,
this shift has a clean origin: the affine Weyl vector
$\rho_{\mathrm{aff}} = \rho + h^\vee \Lambda_0$ contributes
a term proportional to~$N$ in $\kappa^{\mathrm{KM}}$ that partially
cancels against the Heisenberg contribution.

The presence of an $N^1$ term is compatible with (but does not by
itself prove) the identification with unoriented string amplitudes
in the Gopakumar--Vafa correspondence.
\end{remark}

\begin{remark}[Comparison with the Gopakumar--Vafa free energy]
\label{rem:gopakumar-vafa-comparison}
\index{Gopakumar--Vafa}
The full Chern--Simons free energy on $S^3$ with gauge group
$\mathrm{GL}_N$ at level~$k$, computed by Gopakumar--Vafa
\cite{GV99}, has the genus expansion
$F = \sum_{g \ge 0} g_s^{2g-2} F_g^{\mathrm{GV}}(\lambda)$,
where:
\begin{itemize}
\item \emph{Genus~$0$:} $F_0^{\mathrm{GV}}(\lambda) = \sum_{n=1}^\infty
 (e^{i\lambda n})/n^3 + \mathrm{pol.}$, involving the trilogarithm
 $\mathrm{Li}_3(e^{i\lambda})$.
\item \emph{Genus~$1$:} $F_1^{\mathrm{GV}}(\lambda) = -\frac{1}{12}\log
 \bigl(\prod_{n=1}^\infty (1 - e^{i\lambda n})\bigr) + \cdots$,
 involving the MacMahon function.
\end{itemize}
These are computed from the exact matrix-model solution (Gaussian
matrix integral after gauge-fixing). They capture all-orders-in-$\lambda$
information, including non-perturbative effects.

The scalar-lane free energy~\eqref{eq:Fg-1overN} is a
\emph{one-loop exact} contribution: it captures the part of the
Chern--Simons amplitude controlled by the Hodge bundle and the modular
characteristic, but not the full matrix-model answer. The precise
relationship is:
\begin{enumerate}[label=\textup{(\alph*)}]
\item At genus~$1$, the scalar-lane result $F_1^{\mathrm{scalar}}
 = \kappa/24$ with $\kappa = \kappa(\cA_N)$
 computes the leading perturbative
 approximation to $F_1^{\mathrm{GV}}$. At large~$k$ (weak coupling),
 $\kappa \sim N^2 k/2 \to \infty$ and $F_1 \sim N^2 k/48$, which
 matches the one-loop determinant of the CS path integral around the
 trivial flat connection.
\item At genus~$g \geq 2$, the scalar lane captures the
 $\hat{A}$-genus contribution $\kappa \cdot c_g$ but misses
 the instanton corrections (non-trivial flat connections on
 $\Sigma_g \times S^1$) that contribute to $F_g^{\mathrm{GV}}$ at
 higher orders in~$e^{i\lambda}$.
\item The full Gopakumar--Vafa result requires summing over all flat
 connections, which in the bar-complex language corresponds to summing
 over all Maurer--Cartan elements of the modular deformation dg
 Lie algebra $L_{\mathrm{mod}}(\cA_N)$, not just the canonical one.
\end{enumerate}
The scalar-lane computation is therefore the \emph{perturbative seed}
of the holographic genus identification: it identifies the
correct $N$-scaling at each genus and provides the leading
coefficient.
\end{remark}

\begin{computation}[Free energy table for $\mathrm{GL}_N$ at fixed
$\lambda$; \ClaimStatusProvedHere]
\label{comp:gl-n-free-energy-table}
\index{free energy!$\mathrm{GL}_N$ scalar lane}
The scalar-lane free energies through genus~$4$, expressed
in terms of $\pi/\lambda$ and expanded in~$N$, are:
\[
\renewcommand{\arraystretch}{1.7}
\begin{array}{c|c|c|c}
g & f_g^{(2)} = c_g \cdot \frac{\pi}{\lambda}
 & f_g^{(1)} = -c_g
 & f_g^{(0)} = c_g \cdot \frac{\lambda}{4\pi} \\
\hline
1 & \dfrac{\pi}{24\lambda}
 & -\dfrac{1}{24}
 & \dfrac{\lambda}{96\pi} \\[6pt]
2 & \dfrac{7\pi}{5760\lambda}
 & -\dfrac{7}{5760}
 & \dfrac{7\lambda}{23040\pi} \\[6pt]
3 & \dfrac{31\pi}{967680\lambda}
 & -\dfrac{31}{967680}
 & \dfrac{31\lambda}{3870720\pi} \\[6pt]
4 & \dfrac{127\pi}{154828800\lambda}
 & -\dfrac{127}{154828800}
 & \dfrac{127\lambda}{619315200\pi}
\end{array}
\]
In each row, the full scalar-lane free energy is
$F_g^{\mathrm{scalar}} = f_g^{(2)} N^2 + f_g^{(1)} N + f_g^{(0)}$.
\end{computation}

\begin{proof}
Substitute $c_1 = 1/24$, $c_2 = 7/5760$, $c_3 = 31/967680$,
$c_4 = 127/154828800$ into
equation~\eqref{eq:Fg-1overN-structure}.
\end{proof}

\begin{remark}[Feynman diagram interpretation]
\label{rem:feynman-diagram-interpretation}
At each genus~$g$, the three terms in the $1/N$ expansion have a
transparent combinatorial origin in the ribbon-graph expansion
(Remark~\ref{rem:thooft-formal}):
\begin{enumerate}[label=\textup{(\alph*)}]
\item The $N^2$ term $f_g^{(2)} \cdot N^2$ counts contributions from
 ribbon graphs of genus~$g$ with the maximal number of index loops.
 These are the \emph{planar} ribbon graphs (after the genus-$g$
 insertions from the Hodge bundle). Their weight is proportional to
 $\kappa_{\mathfrak{sl}} \sim \pi N^2/\lambda$, the
 $\mathfrak{sl}_N$ Casimir contribution.
\item The $N^0$ term $f_g^{(0)}$ counts the \emph{minimal-loop}
 ribbon graphs, weighted by the Heisenberg contribution
 $\kappa_{\mathrm{Heis}} = k$. In the fixed-$\lambda$ regime,
 this is $O(1)$ because the Heisenberg factor has rank~$1$.
\item The $N^1$ term $f_g^{(1)} \cdot N$ counts the \emph{subleading}
 ribbon graphs. These arise from the cross-term in
 $\kappa_{\mathfrak{sl}} = (N^2-1)t/(2N)$: the $-1$ in $(N^2-1)$
 reflects that $\mathfrak{sl}_N$ has rank $N-1$, not~$N$, so the
 adjoint trace has a deficit relative to the planar counting.
\end{enumerate}
In particular, no ribbon graphs of genus $g' > g$ contribute to
$F_g^{\mathrm{scalar}}$: the scalar lane is graph-genus-diagonal.
\end{remark}

\begin{remark}[Beyond the scalar lane]
\label{rem:beyond-scalar-lane}
The scalar-lane free energy captures the contribution from the
$\hat{A}$-genus (the spectral-sequence-degenerate sector). The
\emph{full} free energy $F_g(\cA_N)$ receives additional
contributions from the non-degenerate sectors of the spectral sequence
on $L_{\mathrm{mod}}(\cA_N)$: these are the
non-scalar-valued Maurer--Cartan components carrying operator
insertions (the ``multi-trace'' sector in the 't~Hooft language).

Computing these requires the full bracket structure of
$L_{\mathrm{mod}}(\cA_N)$, not just the curvature class $\kappa$.
For the affine $\mathfrak{sl}_N$ factor, the bracket involves the
structure constants $f^{abc}$ of $\mathfrak{sl}_N$, whose
't~Hooft scaling is $f^{abc} \sim N^{1/2}$ (in the standard
normalisation). The resulting multi-trace contributions give rise to
the instanton corrections $e^{in\lambda}$ that appear in the
Gopakumar--Vafa trilogarithm at genus~$0$.

The computation of these non-scalar contributions within the modular
bar framework is the content of the holographic genus identification
conjecture (Conjecture~\ref{conj:thooft-gl-n}): it requires lifting
the scalar-lane expansion to the full Maurer--Cartan moduli space.
\end{remark}

\begin{remark}[Central charge and its $1/N$ expansion]
\label{rem:central-charge-1overN}
For comparison: the central charge of $V^k(\mathfrak{gl}_N)$ is
\[
c(\cA_N)
= N + \frac{N(N^2-1)k}{k+N}
= N + \frac{(N^2-1)(t-N)}{t}
= N^2 - \frac{N^2 - 1}{t}\,N
\]
with $t = k + N$. At fixed $\lambda = 2\pi N/t$:
$c(\cA_N) = N^2(1 - \lambda/(2\pi)) + \lambda/(2\pi)
= N^2(1 - \lambda/(2\pi)) + O(1)$.
The leading coefficient $1 - \lambda/(2\pi)$ vanishes at
$\lambda = 2\pi$ (the self-dual coupling), where
$c \sim O(1)$ and the large-$N$ expansion degenerates.

The modular characteristic $\kappa$ and the central charge $c$ are
distinct invariants: $c$ governs the Virasoro anomaly of the
stress tensor, while $\kappa$ governs the genus-raising curvature of
the modular bar complex. For the affine algebra, $\kappa \neq c/2$
(the relation $\kappa = c/2$ holds only for the Virasoro algebra
itself).
\end{remark}

\begin{remark}[anchor: modular PVA quantization as classical
limit of the universal-conductor master]%
\label{rem:anchor-modular-pva-quantization}%
%
%
\index{Khan--Zeng!classical-limit lift to modular bar}%
The modular PVA quantization above is the \emph{classical limit}
($\hbar \to 0$ with the modular grading retained) of the
universal-holography master theorem
(\textsf{thm:universal-holography-master} in
\textsf{chap:universal-conductor}; \textsf{chap:climax-platonic}).
The Khan--Zeng input
(Convention~\ref{conv:three-levels}, item~1) is the classical
3D HT Poisson sigma model on $\R \times \C$. On the affine and DS
gauge-theoretic lanes the boundary quantization and topological lift
are proved by the corresponding HT gauge-theory theorems. On the
nonlinear finite-type KZ lane, quantizing the boundary algebra to
$\cA$ and identifying the bulk with
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ as $E_3$-topological require the
analytic SDR package and quantized homotopy
$T=[Q_{\mathrm{tot}},G]$. The ladder therefore splits as follows:
\begin{itemize}[nosep]
\item \textsf{cor:rung-virasoro}: classical PVA = Vir's
 $(-1)$-shifted Poisson bracket; quantum upgrade = the chiral
 Higher-Deligne $E_3$-action above.
\item \textsf{cor:rung-w-N}: classical PVA = $\cW_N$
 $\lambda$-bracket (Fateev--Lukyanov); quantum upgrade =
 $E_{N+1}$-topological via iterated Sugawara
 (Vol~II $E_\infty$-topologisation chapter,
 Theorem~\ref{thm:iterated-sugawara-construction}); convergence
 controlled by $\beta_N = 12(H_N - 1)$
 (Chapter~\ref{ch:beta-N-closed-form-all},
 Theorem~\ref{thm:beta-N-closed-form-proved-all-N}).
\item \textsf{cor:rung-w-infty}: classical PVA = $\cW_\infty[\mu]$
 inverse limit; quantum upgrade = $E_\infty$-topological in the
 tower-limit sense.
\end{itemize}
Trees govern chirality (the disk-level chiral algebra $\cA$); loops
govern modularity (the genus-raising curvature
$\kappa(\cA) \cdot \omega_g$); the climax assertion is
that this two-channel structure is the universal holographic
content.
\end{remark}

\section{Synthesis}
\label{sec:mpva-core-supplement}

\begin{remark}[Modular PVA quantisation at K3: $24$ Miki + $\widetilde{M}_{24}$ cocycle]
\label{rem:mpva-core-24-miki}
The modular Poisson-vertex-algebra (PVA) quantisation framework specialises at the Mukai-enhanced K3 to the $24$-Miki presentation of the Vol~III the K3 synthesis K3 chiral Hall--Drinfeld double: $24$ copies of Miki quantum toroidal $U_{q_1, q_2}(\widehat{\widehat{\mathfrak{gl}}}_1)$ with $\widetilde{M}_{24}$-twisted permutation via the Cheng--Duncan--Harvey $2014$ umbral cocycle $\sigma \cdot e^{(i)}_r = \exp(2\pi i\, r\, m_\sigma / 24)\, e^{(\sigma(i))}_r$. The projective Schur cocycle has order $6$ in $H^2(M_{24}, \mathrm{U}(1)) \cong \mathbb{Z}/12$.
\end{remark}
