% label removed: ch:modular-pva-quantization

% Standalone artifacts (\begin{abstract}, \tableofcontents) removed per V2-AP32.

\chapter{Modular PVA Quantization}
\label{ch:modular-pva-quantization-standalone}

\begin{summary}[Scope and targets]
Trees govern chirality and loops govern modularity.
Disk-level quadratic duality controls only genus zero. A genuinely modular deformation
theory must already contain a primitive genus-raising one-edge operator. We construct a
stable-graph modular bar coalgebra, define the complete filtered strict modular deformation
dg Lie algebra, and prove the universal obstruction recursion for lifting a genus-zero
Maurer--Cartan class to all genera. We then pass to a local variational coordinate model
for filtered quadratic Poisson vertex algebras, identify the first genus-raising operator
with a reduced odd Laplacian $D_1=\Delta_{\mathrm{cyc}}$, construct the associated
variational modular class, prove a vanishing theorem for a broad triangular $W$-normal form,
and compute that the first modular obstruction vanishes for classical $W_3$.
In the relevant one-loop sector, every genus-one lift is gauge equivalent to a
renormalization of the central parameter.
\end{summary}

\section{Status conventions and scope}

The note is intentionally stratified.

\begin{convention}[Three levels of assertion]
Throughout the note we distinguish three kinds of statements.
\begin{enumerate}[leftmargin=2.4em]
\item \textbf{External input.} These are statements imported from the literature:
Khan--Zeng on the three-dimensional holomorphic-topological Poisson sigma model,
Gui--Li--Zeng on quadratic duality for chiral algebras, Francis--Gaitsgory on chiral
Koszul duality, Costello--Dimofte--Gaiotto on boundary chiral algebras in 3d
holomorphic twists, Gaiotto--Kulp--Wu on higher operations, and related works
\cite{KZ25,GLZ22,FG12,CDG20,GKW25}.
\item \textbf{Formal algebraic results.} These are theorems proved in this note once one
has fixed a modular bar datum. They include the stable-graph bar construction, the
filtered strict modular deformation dg Lie algebra, the universal obstruction recursion, the coordinate
formula for the genus-raising operator, the variational modular class, the triangular
$W$-normal-form vanishing theorem, and the $W_3$ relevant cohomology computation.
\item \textbf{Conditional comparison results.} These are statements linking the formal
algebra to the Poisson sigma model. They depend on analytic and geometric inputs
not proved here, such as the existence of the appropriate resolved chiral/factorization
datum attached to a given PVA and the existence of half-space perturbative quantization.
\end{enumerate}
\end{convention}

\begin{remark}[Why this stratification matters]
The algebraic stable-graph
package below is self-contained once a modular bar datum is fixed, but the extraction of
that datum from a general PVA via compactified configuration spaces and the identification
with the three-dimensional Poisson sigma model remain conditional at present.
\end{remark}

\begin{convention}[Strict models versus invariant modular deformation objects]
% label removed: conv:modular-pva-strict-versus-homotopy
\index{modular deformation!strict versus homotopy}
Throughout this note, concrete coderivation dg~Lie algebras such as
$\Defmod(A_{\cl}(V))$ are chosen strict presentations. The invariant
modular deformation theory is defined only up to filtered
$L_\infty$ quasi-isomorphism. Accordingly, every Maurer--Cartan equation
written in the strict modular complex should be read as a computation in
one preferred chart on an underlying homotopy-coherent modular
deformation object $\Definfmod(\cA)$
(Vol~I, Construction~\ref*{V1-const:modular-homotopy-deformation-object}).
\end{convention}

\section{External input from the literature}

We record the precise ingredients from the literature that motivate and support the
new constructions.

\subsection{Poisson vertex algebras and the 3d holomorphic-topological Poisson sigma model}

Khan and Zeng introduce a mixed holomorphic-topological gauge theory in three dimensions
attached to a freely generated Poisson vertex algebra (PVA), show that gauge invariance
holds if and only if the $\lambda$-bracket Jacobi identity holds, prove that the presence
of a Virasoro element upgrades the symmetry from holomorphic-topological to fully
topological, and propose the resulting three-dimensional Poisson sigma model as a route
toward deformation quantization of PVAs to vertex algebras \cite{KZ25}. Their
boundary picture on the half-space $\mathbb R_+\times \mathbb C$ is the physical source of
the genus-zero quantization problem considered here.

\subsection{Quadratic duality for chiral algebras}

Gui, Li, and Zeng define quadratic duality for chiral algebras, prove an injective map
\[
\Hom(A,B)\hookrightarrow \MC(A^!\otimes B),
\]
show bijectivity under effectiveness hypotheses in degree zero, and in the inhomogeneous
quadratic setting introduce twisted pairs $(B,B^\circ,S)$ together with the curved
Maurer--Cartan equation
\[
\mu\big((S+\alpha)\boxtimes (S+\alpha)\big)=0.
\]
They also state explicitly that a full homotopy/Koszul treatment, parallel to the
associative story, is still missing \cite{GLZ22}. This gap is one of the main
algebraic motivations for the present note.

\subsection{Chiral/factorization homotopy theory}

Francis and Gaitsgory place chiral and factorization structures in a common homotopy-theoretic
framework and recast their relation as a form of chiral Koszul duality
\cite{FG12}. This supplies the correct derived ambient category in which
one should expect a modular refinement of disk-level chiral duality to live.

\subsection{Boundary algebras, higher operations, and line operators}

Costello, Dimofte, and Gaiotto show that in 3d holomorphic twists bulk local operators form
a commutative chiral algebra with shifted Poisson bracket, while boundary operator algebras
naturally carry higher $A_\infty$ structure \cite{CDG20}. Gaiotto,
Kulp, and Wu construct higher operations in holomorphic-topological perturbation theory,
prove the relevant quadratic consistency identities, and interpret them as a Wess--Zumino
type consistency for BRST symmetry \cite{GKW25}. Dimofte, Niu, and Py show
that line operators in perturbative 3d holomorphic QFT are represented by modules for a
Koszul-dual $A_\infty$-algebra $A^!$ and are organized by Maurer--Cartan data with an
$A_\infty$ Yang--Baxter flavor \cite{DNP25}. All of this reinforces the thesis
that \emph{a single Maurer--Cartan object should package higher operations, anomalies,
and OPE compatibilities}. 

\subsection{Analogies with deformation quantization}

Cattaneo and Felder interpret Kontsevich's deformation quantization via a topological
sigma model on the disk \cite{CF00}. Tamarkin proves that the deformation
complex of an $E_d$-algebra carries an $E_{d+1}$-structure \cite{Tam02}. These
results suggest that the correct receptacle for quantization of PVAs should not be merely
a disk-level dg Lie algebra, but a higher and genuinely modular deformation object.

\section{From first principles: genus zero, loops, and the one-edge principle}

The main structural observation can be stated in one sentence:

\begin{center}
\emph{A deformation theory that only remembers trees cannot see modular obstructions.}
\end{center}

We make that precise.

\subsection{Filtered quadratic PVAs}

\begin{definition}[Filtered quadratic PVA]
A \emph{filtered quadratic Poisson vertex algebra} is a differential commutative algebra
freely generated by fields $u^1,\dots,u^N$ and their derivatives, together with a
$\lambda$-bracket encoded by a skew-adjoint matrix differential operator
\[
\Pi^{ab}(\partial)=\sum_{m\ge 0}\Pi^{ab}_m\,\partial^m,
\]
whose coefficients are filtered polynomials of total generator degree at most $2$.
\end{definition}

The classical $W$-algebras discussed by Khan--Zeng fit this framework, including the
classical $W_3$ example \cite{KZ25}.

\subsection{Resolved classical datum}

\begin{assumption}[Resolved classical chiral/factorization datum]
Let $X$ be a smooth complex curve and let $V$ be a filtered quadratic PVA on $X$.
Assume there exists a cofibrant resolved classical chiral/factorization object
\[
\A=\widetilde A_{\cl}(V)
\]
whose genus-zero shadow is $V$, and which is dualizable, finite type, conilpotent,
and complete in the sense made precise below.
\end{assumption}

\begin{remark}
This assumption isolates the step that is currently external to the purely algebraic theory.
The remainder of the formal constructions depend only on the existence of an input
modular bar datum built from $\A$.
\end{remark}

\subsection{The one-edge principle}

Taking the disk-level deformation complex and adding a genus grading does not suffice.

\begin{proposition}[Necessity of a genus-raising primitive; \ClaimStatusProvedHere]
Suppose a filtered deformation dg Lie algebra $L$ is equipped with a complete genus
filtration $F^\bullet$ and its differential preserves genus exactly. Then any genus-zero
Maurer--Cartan element $\Theta_0\in \MC(\gr_F^0 L)$ extends tautologically to a full
Maurer--Cartan element of $L$ without further obstruction.
\end{proposition}

\begin{proof}
If the differential preserves genus and the Lie bracket adds genera, then the Maurer--Cartan
equation decomposes strictly by genus. A solution in genus zero has no forcing term in
positive genus, so the same element, viewed inside the completed filtered algebra, already
solves the full equation.
\end{proof}

\begin{remark}[Trees versus loops]
Therefore any nontrivial modular obstruction theory must contain, at the chain level,
a primitive operator that \emph{raises genus}. In the stable-graph bar construction below,
that primitive is the nonseparating one-edge expansion operator. This is the algebraic
counterpart of the first loop correction in perturbation theory.
\end{remark}

\section{Stable-graph modular bar data and the modular bar coalgebra}

This section is the formal heart of the new algebraic package.

\subsection{Stable graphs}

\begin{definition}[Connected stable graph]
A \emph{connected stable graph} $\Gamma$ consists of the following data:
\begin{enumerate}[leftmargin=2.4em]
\item a finite set $V(\Gamma)$ of vertices;
\item a finite set $\mathrm{Fl}(\Gamma)$ of flags;
\item a partition $\mathrm{Fl}(\Gamma)=\bigsqcup_{v\in V(\Gamma)}\mathrm{Fl}(v)$;
\item an involution on $\mathrm{Fl}(\Gamma)$, whose $2$-cycles are internal edges and
whose fixed points are external legs;
\item a genus label $g(v)\in \mathbb Z_{\ge 0}$ for each vertex,
\end{enumerate}
subject to the stability condition
\[
2g(v)-2+|\mathrm{Fl}(v)|>0
\qquad\text{for all }v\in V(\Gamma).
\]
Its total genus is
\[
g(\Gamma)=b_1(\Gamma)+\sum_{v\in V(\Gamma)}g(v).
\]
\end{definition}

Write $E(\Gamma)$ for the set of internal edges and
\[
\orline(\Gamma):=\det(kE(\Gamma))\otimes \det(H_1(\Gamma;k))^{-1}
\]
for the orientation line.

\subsection{One-edge expansions}

Let $C$ be a reduced complete finite-type graded collection on finite sets:
\[
F\longmapsto C(F),
\]
functorial for bijections of finite sets.

\begin{definition}[One-edge expansion set]
For a finite set $F$, let $\OE(F)$ denote the set of connected stable graphs whose
external leg set is $F$ and which have exactly one internal edge. Such a graph is either:
\begin{enumerate}[leftmargin=2.4em]
\item \emph{separating}: two vertices joined by one edge;
\item \emph{nonseparating}: one vertex carrying one loop.
\end{enumerate}
\end{definition}

\begin{definition}[Modular bar datum]
A \emph{modular bar datum} on $C$ consists of:
\begin{enumerate}[leftmargin=2.4em]
\item an internal differential
\[
d:C(F)\to C(F)
\]
of degree $+1$ for each finite set $F$;
\item for each $\epsilon\in \OE(F)$, a degree $+1$ map
\[
\Delta_\epsilon:
s\,C(F)\longrightarrow
\orline(\epsilon)\otimes \bigotimes_{u\in V(\epsilon)} s\,C(\mathrm{Fl}_\epsilon(u));
\]
\item the \emph{codimension-two cancellation axiom}: for every connected stable graph
$T$ with exactly two internal edges, the signed sum of the two ways of producing $T$
by successive one-edge expansions vanishes;
\item the anticommutation relation that $d$ anticommutes with every $\Delta_\epsilon$.
\end{enumerate}
\end{definition}

\begin{remark}[Why this is the right primitive datum]
The usual bar construction is governed by codimension-one collisions on configuration
spaces. In the modular setting, codimension-one boundary strata correspond to one-edge
degenerations of stable graphs. Thus the primitive input is not a generic higher operator
but precisely the family of one-edge expansion maps.
\end{remark}

\subsection{The complete modular bar coalgebra}

For a connected stable graph $\Gamma$, define
\[
C[\Gamma]:=
\orline(\Gamma)\otimes\bigotimes_{v\in V(\Gamma)} s\,C(\mathrm{Fl}(v)).
\]

\begin{definition}[Complete modular bar object]
The \emph{complete modular bar object} of a modular bar datum $C$ is
\[
\Bmod(C):=
\prod_{[\Gamma]\in \StGraph^{\mathrm{conn}}}
\big(C[\Gamma]\big)_{\mathrm{Aut}(\Gamma)},
\]
completed with respect to total genus.
\end{definition}

\begin{definition}[Internal and expansion differentials]
Define degree-$+1$ endomorphisms
\[
D_{\mathrm{int}},\ D_{\mathrm{exp}}:\Bmod(C)\to \Bmod(C)
\]
on graph generators as follows.
\begin{enumerate}[leftmargin=2.4em]
\item $D_{\mathrm{int}}$ applies the internal differential $d$ to one vertex label and
sums over vertices.
\item $D_{\mathrm{exp}}$ replaces a chosen vertex $v$ by a one-edge expansion
$\epsilon\in \OE(\mathrm{Fl}(v))$ and applies $\Delta_\epsilon$ to the label at $v$,
with the sign determined by the orientation line and Koszul rule.
\end{enumerate}
Set
\[
D:=D_{\mathrm{int}}+D_{\mathrm{exp}}.
\]
\end{definition}

\begin{theorem}[Stable-graph modular bar construction; \ClaimStatusProvedHere]% label removed: thm:modular-bar
Let $C$ be a modular bar datum. Then:
\begin{enumerate}[leftmargin=2.4em]
\item $D^2=0$;
\item $\Bmod(C)$ is a complete conilpotent modular dg coalgebra;
\item if $F^g\Bmod(C)$ denotes the subspace spanned by graphs of total genus $\ge g$, then
\[
\Bmod(C)\cong \varprojlim_g \Bmod(C)/F^g\Bmod(C),
\]
and this filtration is exhaustive and complete.
\end{enumerate}
\end{theorem}

\begin{proof}
The square of $D$ has three types of terms.

\smallskip
\noindent
\emph{(i) Two internal differentials.}
These vanish because $d^2=0$ on every vertex label.

\smallskip
\noindent
\emph{(ii) One internal differential and one expansion.}
These cancel because $d$ anticommutes with every one-edge expansion map $\Delta_\epsilon$.

\smallskip
\noindent
\emph{(iii) Two one-edge expansions.}
These are exactly the codimension-two stable-graph boundary terms. Every graph with two
internal edges can be obtained by two successive one-edge expansions, and the codimension-two
cancellation axiom says the signed sum of the two resulting paths is zero.

Therefore $D^2=0$.

For conilpotence, use the reduced coproduct defined by extracting a nontrivial connected
stable subgraph. Repeated reduced coproduct strictly decreases the number of internal
edges, hence eventually vanishes on every graph class. Completeness is immediate from
the completed product over total genus.
\end{proof}

\begin{remark}[Tree-level truncation]
The genus-zero subquotient of $\Bmod(C)$ is obtained by restricting to connected stable
graphs of total genus zero, i.e.\ trees all of whose vertices have genus zero. We denote
that tree-level coalgebra by $\Bch(C)$.
\end{remark}

\subsection{Separating and nonseparating pieces}

Split the expansion operator into
\[
D_{\mathrm{exp}}=D_{\mathrm{sep}}+D_{\mathrm{nsep}},
\]
where $D_{\mathrm{sep}}$ sums over separating one-edge expansions and $D_{\mathrm{nsep}}$
over nonseparating one-edge expansions. Set
\[
D_0:=D_{\mathrm{int}}+D_{\mathrm{sep}},
\qquad
D_1:=D_{\mathrm{nsep}}.
\]

\begin{proposition}[The one-edge decomposition; \ClaimStatusProvedHere]% label removed: prop:D0D1
With the notation above:
\begin{enumerate}[leftmargin=2.4em]
\item $D_0$ preserves total genus;
\item $D_1$ raises total genus by one;
\item $D_0^2=0$, $D_0D_1+D_1D_0=0$, and $D_1^2=0$.
\end{enumerate}
\end{proposition}

\begin{proof}
Separating one-edge expansions preserve the first Betti number and total genus, while
nonseparating one-edge expansions increase the first Betti number by one. The identities
follow by taking the genus-homogeneous pieces of the equality $(D_0+D_1)^2=0$.
\end{proof}

\subsection{Curved extension via $S$-tails}

Gui--Li--Zeng show that in the inhomogeneous quadratic setting the correct input is not
merely a CDG algebra, but a twisted pair $(B,B^\circ,S)$, and that the passage to the
associated CDG algebra forgets information \cite{GLZ22}. The modular extension
should therefore remember the element $S$ geometrically.

\begin{definition}[Curved one-tail expansion]
Given a twisted pair $(B,B^\circ,S)$, an \emph{$S$-tail expansion} is the operation that
attaches a new univalent $S$-decorated vertex to a pre-existing corolla. Formally, it is
a unary expansion map
\[
\Delta_S:s\,C(F)\to s\,C(F\sqcup \{\bullet,\star\})
\]
followed by contraction of the new internal edge, with the new univalent vertex labeled by $S$.
\end{definition}

\begin{remark}
The correct curved modular bar object is obtained by adjoining the $S$-tail expansions
to the set of primitive degenerations. Provided they satisfy the same codimension-two
compatibilities with the one-edge expansions, the proof of \cref{thm:modular-bar} goes
through verbatim. This is the modular analogue of the twisted Maurer--Cartan equation
\[
\mu\big((S+\alpha)\boxtimes (S+\alpha)\big)=0
\]
of Gui--Li--Zeng.
\end{remark}

\section{The strict modular deformation dg Lie algebra}

The passage from the coalgebra to the deformation complex.

\begin{definition}[Modular deformation algebra]
Let $C$ be a modular bar datum. Define
\[
L_{\mathrm{mod}}(C):=\Coder(\Bmod(C))[-1].
\]
If $\A$ is a resolved classical chiral/factorization datum with underlying modular bar datum
$C(\A)$, write
\[
\Defmod(A_{\cl}(V)):=L_{\mathrm{mod}}(C(\A)).
\]
\end{definition}

\begin{remark}[Strict model of the modular deformation object]
% label removed: rem:lmod-strict-model
The dg~Lie algebra $L_{\mathrm{mod}}(C)$ is the strict model of
the homotopy-invariant modular deformation object
$\Definfmod(\cA)$ (Vol~I,
Theorem~\ref*{V1-thm:modular-homotopy-convolution}).
This chapter's filtered obstruction theory
(Theorems~\ref{thm:Ob1},~\ref{thm:Obg}) operates at the strict
level because the complete filtration ensures convergence of the
MC tower.
\end{remark}

\begin{proposition}[Convolution description; \ClaimStatusProvedHere]
A coderivation of $\Bmod(C)$ is determined by its projection to corollas. Hence there is
a canonical identification
\[
L_{\mathrm{mod}}(C)\cong \Hom(\Bmod(C),sC)[-1]
\]
with dg Lie bracket given by commutator.
\end{proposition}

\begin{proof}
This is the standard universal property of cofree conilpotent coalgebras, applied in the
completed stable-graph setting.
\end{proof}

\begin{construction}[The homotopy modular deformation object]
% label removed: const:vol2-homotopy-modular-object
\index{modular deformation!homotopy object}
Let $C$ be a modular bar datum. Denote by
\[
\Definfmod(C)
\]
the complete filtered $L_\infty$-algebra obtained from any cofibrant or
quasi-free resolution of the stable-graph bar coalgebra, or equivalently
from the coderivation complex of a bar-cofree strictification. Its
Maurer--Cartan elements are the homotopy-coherent modular twisting data
attached to~$C$, and any two such constructions are related by filtered
$L_\infty$ quasi-isomorphisms
(Vol~I, Construction~\ref*{V1-const:modular-homotopy-deformation-object}).
\end{construction}


\subsection{Concrete chain-level presentation from the three foundational papers}
% label removed: subsec:vol2-three-preprints-chain-level

\begin{construction}[Homotopy-chiral/log-FM coordinates; \ClaimStatusProvedHere]
% label removed: const:vol2-three-preprints-chain-level
Fix an affine cover $\mathfrak U$ of the boundary curve.
The \v{C}ech totalisation
$A^{\mathrm{ch}}_\infty := \check C^\bullet(\mathfrak U;\A)$
is a $\mathrm{Ch}_\infty$-algebra~\cite[Theorem~3.1]{MS24}.
For a logarithmic boundary pair or semistable family,
$\cC^{\log FM}_{X\mathbin{|}D}(n):=C_\bullet(\operatorname{FM}_n(X\mathbin{|}D))$
and $\cC^{\log FM}_{W/B}(n):=C_\bullet(\operatorname{FM}_n(W/B))$.
The modular deformation object in these coordinates is
\[
{\Definfmod}_{\log}(C)
:=
\Convinf\!\Bigl(
\cC^{\log FM}_{\mathrm{mod}},\,
\operatorname{End}_{\mathrm{Ch}_\infty}(A^{\mathrm{ch}}_\infty)
\Bigr),
\]
with strict chart
$L^{\log}_{\mathrm{mod}}(C)
:=
\Convstr(\cC^{\log FM}_{\mathrm{mod}},\,
\operatorname{End}_{\mathrm{Ch}_\infty}(A^{\mathrm{ch}}_\infty))$.
\end{construction}

\begin{remark}[Stable-graph modular bar functor in coordinates]
% label removed: rem:vol2-log-modular-bar-functor
The modular bar construction in log-FM coordinates is
\[
\Bmod^{\log}(C)(g,n)
=
\bigoplus_{\Gamma\in \mathsf{Gr}^{\mathrm{st}}_{g,n}}
\left(
\bigotimes_{v\in V(\Gamma)} \bar B^{\mathrm{ch}}(A^{\mathrm{ch}}_\infty;\mathrm{In}(v))
\otimes
C_\bullet(\operatorname{FM}^{\log}_{\Gamma})
\otimes
\orline{E_{\mathrm{int}}(\Gamma)}
\right)_{\Aut(\Gamma)}.
\]
Its differential is the sum of the transferred chiral
differential, separating sewing, planted-forest corrections, and the
non-separating loop operator.
\end{remark}

\begin{computation}[Low-genus control terms; \ClaimStatusProvedHere]
% label removed: comp:vol2-low-genus-control
The first coefficients of the modular $L_\infty$-structure in the strict chart:
\[
\ell_3^{(0)}(\alpha,\beta,\gamma)
=
\sum_{T\in\mathsf{Trees}_3}
\frac{1}{|\Aut(T)|}\,
(\pi\circ m_T^{(h)}\circ\iota^{\otimes 3})(\alpha,\beta,\gamma),
\]
\[
\ell_4^{(0)}(\alpha,\beta,\gamma,\delta)
=
\sum_{T\in\mathsf{Trees}_4}
\frac{\pm1}{|\Aut(T)|}\,
(\pi\circ m_T^{(h)}\circ\iota^{\otimes 4})(\alpha,\beta,\gamma,\delta),
\]
and the first genuine modular term is
$\ell_1^{(1)} = \hbar\Delta_{\mathrm{cyc}}$.
For classical $W_3$ the first modular obstruction vanishes.
\end{computation}

\begin{construction}[PVA-coordinate residue formulas; \ClaimStatusProvedHere]
% label removed: const:vol2-pva-coordinate-graph-coefficients
For local boundary fields $u_1,\dots,u_n$, the first tree
coefficients are residue integrals over log-FM boundary strata:
\begin{align}
\ell_3^{(0)}(u_1,u_2,u_3)
&=
\sum_{T\in \mathsf{Trees}_3}
\operatorname{Res}_{D_T^{\log}}\,\omega^{T}_{u_1,u_2,u_3},
% label removed: eq:vol2-ell3-residue\\
\ell_4^{(0)}(u_1,u_2,u_3,u_4)
&=
\sum_{F\in \mathsf{PF}^{\mathrm{rig}}_4}
\epsilon_F\,\operatorname{Res}_{D_F^{\log}}\,\omega^{F}_{u_1,u_2,u_3,u_4},
% label removed: eq:vol2-ell4-residue
\end{align}
with $\ell_1^{(1)}=\hbar\Delta_{\mathrm{cyc}}$.
The three summands of~\eqref{eq:vol2-ell4-residue} are the
contact, additive, and tree rigid types of Mok's degeneration
formula~\cite[Corollary~5.3.4]{Mok25}.
\end{construction}

\begin{computation}[Archetype formulas in boundary coordinates; \ClaimStatusProvedHere]
% label removed: comp:vol2-archetype-formulas
Heisenberg ($\{a^i{}_{\lambda}a^j\}=K^{ij}\lambda$):
$\ell_3^{(0)}=0$, $\ell_4^{(0)}=0$,
$\ell_1^{(1)}=\hbar\sum_{i,j}K^{ij}\partial^2/(\partial a^i\partial a^j)$.
Affine currents ($\{J^a{}_{\lambda}J^b\}=f^{ab}{}_cJ^c+k\kappa^{ab}\lambda$):
$[\ell_3^{(0)}]=[f_{abc}\,J^a\otimes J^b\otimes J^c]$,
$\ell_4^{(0)}=0$.
For the $W_3$ PVA, $\Lambda={:}TT{:}-\tfrac{3}{10}\partial^2T$
controls the quartic tree coefficient: $[\ell_4^{(0)}]\propto
\tfrac{16}{22+5c}\,\Lambda$.
\end{computation}

\begin{remark}[Genus-two entry point]
% label removed: rem:vol2-genus-two-entry
$\Theta^{(2)}
=
\Theta^{(2)}_{\mathrm{loop}\circ\mathrm{loop}}
+\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}
+\Theta^{(2)}_{\mathrm{pf}}$.
Heisenberg sees only the first term, affine currents see the first two,
$W_3$/Virasoro exhibit all three.
\end{remark}

\begin{remark}[Rigid-type boundary factorization]
% label removed: rem:vol2-rigid-type-boundary-factorization
Mok's degeneration formula writes each rigid boundary component of
$\operatorname{FM}_n(W/B)$ as a push-pull of products of lower log-FM factors:
$\operatorname{FM}_n(W/B)(\rho)\to
\prod_{v\in V(S_\rho)}\operatorname{FM}_{I_v}(Y_v\mathbin{|}D_v)$.
Every clutching identity in the strict modular complex is a
push-pull identity on rigid planted-forest strata.
\end{remark}

\subsection{Explicit low-order Taylor calculus in PVA coordinates}
% label removed: subsec:vol2-explicit-low-order-taylor-calculus

The convolution $L_\infty$ Taylor coefficients~\cite[Theorem~5.1]{RNW19}
are
$\ell_k(f_1,\dots,f_k)(x)
=
\gamma_A(\alpha\circ 1_D)(f_1\otimes\cdots\otimes f_k)\Delta_D^k(x)$.
The secondary Borcherds operations~\cite{MS24} give the mode-level
cubic formula
\begin{equation}
% label removed: eq:vol2-explicit-l3-secondary-borcherds
\ell_3^{(0)}(a,b,c)
=
\sum_{p,q,r}
\left(
\int_{\partial^{\log}_{p,q,r}\FM_3} \omega_{p,q,r}
\right)
 j'_{(p,q,r)}(a,b,c),
\end{equation}
where the $j'_{(p,q,r)}$ satisfy the secondary Borcherds identity
\begin{align}
% label removed: eq:vol2-secondary-borcherds-identity
&(d\circ j'_{(p,q,r)}+j'_{(p,q,r)}\circ d)(a,b,c)
\notag\\
&\qquad=
\sum_{j\ge 0}\binom{p}{j}
\Bigl(
(-1)^j a_{(p+q-j)}(b_{(r+j)}c)
-(-1)^{j+p+|a||b|}b_{(r+p-j)}(a_{(q+j)}c)
\Bigr)
-\sum_{j\ge 0}\binom{q}{j}(a_{(p+q-j)}b)_{(r+j)}c.
\end{align}

\begin{proposition}[Quartic channels and the first loop term; \ClaimStatusProvedHere]
% label removed: prop:vol2-quartic-channels-and-loop-term
The first four Taylor coefficients of the modular deformation field:
\begin{align}
% label removed: eq:vol2-low-order-atlas
\Theta_{2}^{(0)} &= H,
\notag\\
\Theta_{3}^{(0)} &= \ell_3^{(0)},
\notag\\
\Theta_{4}^{(0)} &= \Theta_{4}^{\mathrm{contact}} + \Theta_{4}^{12\mid 34} + \Theta_{4}^{13\mid 24} + \Theta_{4}^{14\mid 23},
\notag\\
\Theta_{1}^{(1)} &= \hbar\,\Delta_{\mathrm{cyc}}.
\end{align}
The quartic sector has four primitive graph channels: one zero-edge
contact graph and three one-edge separating graphs.
\end{proposition}

\begin{remark}[Archetype classification]
% label removed: rem:vol2-family-by-family-low-order-atlas
\begin{enumerate}[label=\textup{(\roman*)}]
\item Free/abelian: Gaussian ($\ell_3^{(0)}=0$, contact channel vanishes).
\item Affine currents: Lie/tree ($\ell_3^{(0)}\neq 0$, quartic via separating channels only).
\item $\beta\gamma$: contact/quartic ($\ell_3^{(0)}=0$, $\Theta_4^{\mathrm{contact}}\neq 0$).
\item Virasoro/$\mathcal W_N$: mixed (cubic and quartic contact both nonzero).
\end{enumerate}
\end{remark}

\begin{remark}[Rigid-type factorization via Mok's cutting map]
% label removed: rem:vol2-mok-cutting-map-factorization
For a rigid combinatorial type $\rho$ of a semistable degeneration, Mok's subdivision
\[
\kappa\colon \Pi_n(\Delta)(\operatorname{cone}(\rho))\to \prod_{v\in V(S_\rho)}\Pi_{I_v}(\Sigma_v)
\]
lifts to the modification
\[
\operatorname{FM}_n(W/B)(\rho)\to \prod_{v\in V(S_\rho)}\operatorname{FM}_{I_v}(Y_v\mathbin{|}D_v).
\]
This is the precise geometric input behind every clutching statement in the PVA quantization chapter:
separating factorization is not an analogy but a push-pull identity on rigid logarithmic boundary pieces.
\end{remark}


\subsection{The genus filtration}

\begin{definition}[Genus-raise filtration]
For $\delta\in L_{\mathrm{mod}}(C)$ define
\[
\delta\in F^pL_{\mathrm{mod}}(C)
\iff
\delta(F^g\Bmod(C))\subseteq F^{g+p}\Bmod(C)
\quad\text{for all }g\ge 0.
\]
\end{definition}

\begin{theorem}[Formal structure theorem; \ClaimStatusProvedHere]% label removed: thm:formal-structure
Let $C$ be a modular bar datum. Then:
\begin{enumerate}[leftmargin=2.4em]
\item $L_{\mathrm{mod}}(C)$ is a complete filtered dg Lie algebra with differential
\[
d_L(\delta):=[D,\delta];
\]
\item the filtration is Lie-multiplicative:
\[
[F^pL_{\mathrm{mod}},F^qL_{\mathrm{mod}}]\subseteq F^{p+q}L_{\mathrm{mod}};
\]
\item the positive-genus ideal $F^1L_{\mathrm{mod}}$ is pronilpotent;
\item the genus-zero associated graded piece identifies with the ordinary tree-level deformation complex:
\[
\gr_F^0 L_{\mathrm{mod}}(C)\cong \Coder(\Bch(C))[-1].
\]
\end{enumerate}
\end{theorem}

\begin{proof}
Coderivations of any dg coalgebra form a dg Lie algebra under commutator. Completeness
is inherited from the completeness of $\Bmod(C)$. If $\delta$ raises genus by at least $p$
and $\eta$ by at least $q$, then both compositions $\delta\eta$ and $\eta\delta$ raise genus
by at least $p+q$, proving Lie-multiplicativity. Pronilpotence of $F^1$ follows because on
the finite quotient by $F^N$, sufficiently long brackets vanish.

For the associated graded in genus zero, only total-genus-zero graphs survive, i.e.\ trees
with vertex genera all zero. The nonseparating operator $D_1$ dies in the quotient, so the
differential reduces to the tree-level bar differential.
\end{proof}

\begin{corollary}[No modular theory without loops; \ClaimStatusProvedHere]
If $D_1=0$, then every genus-zero Maurer--Cartan class extends uniquely to a full
Maurer--Cartan class. In particular, the nonseparating one-edge piece is the minimal
algebraic source of genuine modular obstructions.
\end{corollary}

\begin{proof}
Apply \cref{prop:D0D1} and the argument of the proposition from \S3.
\end{proof}

\subsection{Genus-zero comparison with quadratic chiral duality}

\begin{proposition}[Comparison with Gui--Li--Zeng; \ClaimStatusProvedHere]
Suppose the genus-zero truncation of $C(\A)$ is the ordinary quadratic chiral bar datum
of a dualizable quadratic chiral algebra $A_{\cl}(V)$. Then the genus-zero Maurer--Cartan
problem in $\gr_F^0\Defmod(A_{\cl}(V))$ recovers the Gui--Li--Zeng Maurer--Cartan problem:
\[
\Hom(A,B)\hookrightarrow \MC(A^!\otimes B)
\]
in the strictly quadratic case, and the twisted equation
\[
\mu\big((S+\alpha)\boxtimes (S+\alpha)\big)=0
\]
in the inhomogeneous quadratic case.
\end{proposition}

\begin{proof}
On the genus-zero quotient only trees survive, so the modular bar coalgebra reduces to the
ordinary tree-level chiral bar coalgebra. The corresponding coderivation dg Lie algebra is
precisely the disk-level deformation complex. The Gui--Li--Zeng identification is therefore
the genus-zero shadow of the present modular theory.
\end{proof}

\begin{construction}[Bipartite shadow as $L_\infty$ truncation]
% label removed: constr:vol2-bipartite-linfty
The polarized graph algebra $\mathsf{G}^{\pm}_{\mathrm{mod}}(\cA)$ with mixed propagators $P^{+-}$ identifies with the tree-level $L_\infty$ brackets of $\gAmod$: each bipartite graph with zero internal edges and $r$ external legs corresponds to the transferred $r$-ary bracket $\ell_r^{\mathrm{tr}}$. Bipartite vanishing ($P^{++} = P^{--} = 0$) follows from Lagrangian isotropy. For PVA descent, this identification shows that the classical shadow $\kappa^{\mathrm{cl}}$ (degree~$2$) and the quantization obstruction $o_3$ (degree~$3$) are the first two $L_\infty$ brackets of the deformation complex, exactly as in the Vol~I bipartite $L_\infty$ truncation construction.
\end{construction}

\section{Maurer--Cartan obstruction theory}

Extracting the exact obstruction groups.

\subsection{Formal obstruction recursion}

Let $L=L_{\mathrm{mod}}(C)$ and write $d_0=[D_0,-]$, $d_1=[D_1,-]$.

\begin{theorem}[Universal genus-one obstruction; \ClaimStatusProvedHere]% label removed: thm:Ob1
Let $\Theta_0\in \MC(\gr_F^0L)$. Then the class
\[
\Ob_1(\Theta_0):=[d_1\Theta_0]
\in
H^2\big((\gr_F^1L)^{\Theta_0},d_0^{\Theta_0}\big),
\qquad
d_0^{\Theta_0}(x):=d_0x+[\Theta_0,x],
\]
is well-defined. The obstruction vanishes,
\[
\Ob_1(\Theta_0)=0
\iff
\exists\,\Theta_1\in F^1L/F^2L
\text{ such that }
\Theta_0+\Theta_1
\]
solves the Maurer--Cartan equation modulo $F^2L$.
\end{theorem}

\begin{proof}
Expand the Maurer--Cartan equation for $\Theta=\Theta_0+\Theta_1$ modulo $F^2$:
\[
0=d\Theta+\frac12[\Theta,\Theta]
=
\Big(d_0\Theta_0+\frac12[\Theta_0,\Theta_0]\Big)
+
\Big(d_0\Theta_1+d_1\Theta_0+[\Theta_0,\Theta_1]\Big).
\]
The first parenthesis vanishes because $\Theta_0$ is genus-zero Maurer--Cartan, hence the
lifting equation is
\[
d_0^{\Theta_0}\Theta_1=-d_1\Theta_0.
\]
Thus the lift exists iff the cohomology class of $d_1\Theta_0$ vanishes.

To prove that $d_1\Theta_0$ is closed, use \cref{prop:D0D1}. Since $D_0^2=0$,
$D_0D_1+D_1D_0=0$, and $D_1^2=0$, we obtain
\[
d_0^2=0,\qquad d_0d_1+d_1d_0=0.
\]
Applying this to the genus-zero Maurer--Cartan equation
\[
d_0\Theta_0+\frac12[\Theta_0,\Theta_0]=0
\]
and using that $d_1$ is a derivation of the Lie bracket yields
\[
d_0^{\Theta_0}(d_1\Theta_0)=0.
\]
\end{proof}

\begin{theorem}[Higher-genus recursion; \ClaimStatusProvedHere]% label removed: thm:Obg
Suppose
\[
\Theta_{<g}:=\Theta_0+\Theta_1+\cdots+\Theta_{g-1}
\]
solves the Maurer--Cartan equation modulo $F^gL$. Then the genus-$g$ forcing term
\[
R_g(\Theta_{<g})
:=
d_1\Theta_{g-1}
+\frac12\sum_{i=1}^{g-1}[\Theta_i,\Theta_{g-i}]
\]
is $d_0^{\Theta_0}$-closed and determines a canonical obstruction class
\[
\Ob_g(\Theta_{<g})
:=
[R_g(\Theta_{<g})]
\in
H^2\big((\gr_F^gL)^{\Theta_0},d_0^{\Theta_0}\big).
\]
It vanishes if and only if there exists $\Theta_g\in F^gL/F^{g+1}L$ such that
\[
\Theta_{\le g}:=\Theta_0+\cdots+\Theta_g
\]
solves the Maurer--Cartan equation modulo $F^{g+1}L$.
\end{theorem}

\begin{proof}
Take the genus-$g$ part of the full Maurer--Cartan equation. Since $D_1$ raises genus by
exactly one, the only differential terms are $d_0\Theta_g$ and $d_1\Theta_{g-1}$, while the
quadratic part is the sum over pairs $(i,g-i)$. Thus
\[
d_0^{\Theta_0}\Theta_g=-R_g(\Theta_{<g}).
\]
The same computation as in \cref{thm:Ob1} shows that $R_g$ is closed. The vanishing
criterion is immediate.
\end{proof}

\begin{corollary}[Full modular lift criterion; \ClaimStatusProvedHere]
A full modular Maurer--Cartan lift
\[
\Theta=\Theta_0+\Theta_1+\Theta_2+\cdots\in \MC(L)
\]
exists if and only if
\[
\Ob_g(\Theta_{<g})=0
\qquad\text{for all }g\ge 1.
\]
\end{corollary}

\subsection{Conditional comparison with the Khan--Zeng half-space theory}

The formulation of the theorem package in the form best suited for later application to the
three-dimensional Poisson sigma model.

\begin{assumption}[Half-space tree-level quantization]
Assume the Khan--Zeng half-space theory on $\mathbb R_+\times X$ with Neumann boundary
condition admits renormalized perturbation theory through tree level.
\end{assumption}

\begin{theorem}[Conditional tree-level boundary quantization; \ClaimStatusConditional]% label removed: thm:conditional-tree
Let $V$ be a filtered quadratic PVA and let $\A=\widetilde A_{\cl}(V)$ satisfy the resolved
classical datum hypotheses. Under the half-space tree-level quantization assumption there
exist:
\begin{enumerate}[leftmargin=2.4em]
\item a genus-zero Maurer--Cartan class
\[
\Theta_0\in \MC(\gr_F^0\Defmod(A_{\cl}(V)));
\]
\item a genus-zero boundary chiral/factorization algebra $Q_0(V)$,
\end{enumerate}
such that:
\begin{enumerate}[label=\textnormal{(\alph*)},leftmargin=2.8em]
\item the genus-zero shadow of $\Theta_0$ is the classical $\lambda$-bracket of $V$;
\item the classical limit of $Q_0(V)$ is $A_{\cl}(V)$;
\item under the genus-zero comparison with Gui--Li--Zeng, $\Theta_0$ is the disk-level
Maurer--Cartan class encoding the boundary quantization map
\[
A_{\cl}(V)\longrightarrow Q_0(V).
\]
\end{enumerate}
If $V$ contains a Virasoro element satisfying the Khan--Zeng hypotheses, then $\Theta_0$
lies in the topological subcomplex
\[
\Deftop(A_{\cl}(V))\subseteq \Defmod(A_{\cl}(V)).
\]
\end{theorem}

\begin{remark}
This theorem is conditional because the formal algebraic package constructed here does not
by itself prove the existence of the half-space perturbative quantization. What it does is
identify the \emph{exact deformation-theoretic object} into which that boundary problem
must land.
\end{remark}

\begin{corollary}[Conditional modular quantization criterion; \ClaimStatusConditional]
Under the hypotheses of \cref{thm:conditional-tree}, if all obstruction classes vanish,
then there exists
\[
\Theta\in \MC(\Defmod(A_{\cl}(V)))
\]
whose genus-zero shadow is the classical $\lambda$-bracket and whose boundary value is the
desired quantized chiral algebra. Under the Virasoro hypotheses the lift can be chosen in
$\Deftop(A_{\cl}(V))$.
\end{corollary}

\section{Coordinate realization on local variational polyvectors}

The construction of the concrete coordinate model for the first genus-raising operator.

\subsection{Local polyvectors}

Let
\[
\widehat{\cV}:=
\widehat{\mathbb C}[u^a_{(n)}\mid a=1,\dots,N,\ n\ge 0]
\]
be the completed differential polynomial algebra, with $\partial u^a_{(n)}=u^a_{(n+1)}$.
Introduce odd variables $\theta_a^{(n)}$ satisfying
\[
\partial \theta_a^{(n)}=\theta_a^{(n+1)}.
\]

\begin{definition}[Local polyvectors]
The space of local polyvectors is
\[
\Xloc^\bullet(\widehat{\cV})
:=
\widehat{\cV}[\theta_a^{(n)}]\big/\partial\big(\widehat{\cV}[\theta_a^{(n)}]\big).
\]
We write $\int F$ for the class of $F$ modulo total derivatives. The usual variational
Schouten bracket on $\Xloc^\bullet$ will be denoted by $[\ ,\ ]$.
\end{definition}

\begin{remark}[Shift conventions]
The ordinary Poisson cohomological degree is the polyvector degree. Thus vector fields are
degree $1$ and bivectors are degree $2$. The shifted Maurer--Cartan deformation complex is
obtained from $\Xloc^{\bullet+1}$. In this note we freely pass between the two conventions,
always indicating which degree is meant.
\end{remark}

Every local bivector has a reduced representative of the form
\[
P=\frac12\int \theta_a\,A^{ab}(\partial)\,\theta_b
\]
with $A^{ab}(\partial)$ skew-adjoint and all derivatives moved onto the right-hand factor.

For a filtered quadratic PVA operator
\[
\Pi^{ab}(\partial)=\sum_{m\ge 0}\Pi_m^{ab}\,\partial^m,
\]
write
\[
P_\Pi:=\frac12\int \theta_a\,\Pi^{ab}(\partial)\,\theta_b.
\]
The PVA Jacobi identity is equivalent to the variational master equation
\[
[P_\Pi,P_\Pi]=0.
\]

\subsection{The reduced odd Laplacian}

\begin{definition}[Reduced cyclic odd Laplacian]
Define
\[
\Delta_{\mathrm{cyc}}\!\left(\int F\right)
:=
\sum_{a=1}^N\sum_{n\ge 0}
\int
(-\partial)^n
\frac{\partial^2 F}{\partial u^a_{(n)}\,\partial \theta_a}.
\]
\end{definition}

\begin{remark}[Interpretation]
The operator $\Delta_{\mathrm{cyc}}$ is the coordinate model of the nonseparating one-edge
expansion. Geometrically it contracts the two half-edges of a one-loop self-gluing; in BV
language it is the reduced divergence of a local bivector.
\end{remark}

\begin{theorem}[Coordinate formula for the genus-raising operator; \ClaimStatusProvedHere]% label removed: thm:D1formula
Let $\Pi=(\Pi^{ab}(\partial))$ be a filtered quadratic PVA operator. Then
\[
D_1(P_\Pi)=\Delta_{\mathrm{cyc}}P_\Pi
=
\int \sum_{b=1}^N \mathfrak M_\Pi^b(\partial)(\theta_b),
\]
where
\[
\mathfrak M_\Pi^b(\partial)
:=
\sum_{a=1}^N \frac{\delta \Pi^{ab}(\partial)}{\delta u^a},
\qquad
\frac{\delta \Pi^{ab}(\partial)}{\delta u^a}
:=
\sum_{n\ge 0}(-\partial)^n\circ
\frac{\partial \Pi^{ab}(\partial)}{\partial u^a_{(n)}}.
\]
We call $\mathfrak M_\Pi=(\mathfrak M_\Pi^b)_b$ the \emph{variational modular operator}
of $\Pi$.
\end{theorem}

\begin{proof}
Differentiate
\[
P_\Pi=\frac12\int \theta_a\Pi^{ab}(\partial)\theta_b
\]
with respect to $\theta_a$ to contract one odd half-edge, then take the variational
derivative with respect to the even jet variables $u^a_{(n)}$. Each integration by parts
contributes a factor $(-\partial)^n$. Summing over $a$ and $n$ produces exactly the
displayed formula.
\end{proof}

\begin{lemma}[BV properties of $\Delta_{\mathrm{cyc}}$; \ClaimStatusProvedHere]% label removed: lem:BV
The operator $\Delta_{\mathrm{cyc}}$ is odd, second-order, and satisfies:
\begin{align*}
\Delta_{\mathrm{cyc}}^2&=0,\\
\Delta_{\mathrm{cyc}}[X,Y]
&=
[\Delta_{\mathrm{cyc}}X,Y]
+(-1)^{|X|+1}[X,\Delta_{\mathrm{cyc}}Y].
\end{align*}
\end{lemma}

\begin{proof}
This is the standard BV-coordinate computation in jet coordinates. The Euler-operator
factors $(-\partial)^n$ already incorporate all integration-by-parts signs. Super-commutativity
forces the square to vanish, and the second-order nature yields the derivation rule for the
Schouten bracket.
\end{proof}

\subsection{The variational modular class}

\begin{theorem}[Variational modular class; \ClaimStatusProvedHere]% label removed: thm:modclass
Let $\Pi$ be a filtered quadratic PVA operator. Then
\[
[P_\Pi,\Delta_{\mathrm{cyc}}P_\Pi]=0.
\]
Hence $\Delta_{\mathrm{cyc}}P_\Pi$ determines a canonical local Poisson cohomology class
\[
\Mod(V):=[\Delta_{\mathrm{cyc}}P_\Pi]\in
H^1_{\delta_\Pi}\!\big(\Xloc^\bullet(\widehat{\cV})\big),
\qquad
\delta_\Pi:=[P_\Pi,-].
\]
We call $\Mod(V)$ the \emph{variational modular class} of the filtered quadratic PVA.
\end{theorem}

\begin{proof}
Apply \cref{lem:BV} to the identity $[P_\Pi,P_\Pi]=0$:
\[
0=\Delta_{\mathrm{cyc}}[P_\Pi,P_\Pi]=2[P_\Pi,\Delta_{\mathrm{cyc}}P_\Pi].
\]
Thus $\Delta_{\mathrm{cyc}}P_\Pi$ is $\delta_\Pi$-closed.
\end{proof}

\begin{remark}[Obstruction shadow]
The class $\Mod(V)$ lives in ordinary Poisson cohomology. Under the one-edge comparison
between the nonseparating bar operator and the local variational model, it is the coordinate
shadow of the genus-one forcing term $d_1\Theta_0$ in \cref{thm:Ob1}. In particular, if
$\Delta_{\mathrm{cyc}}P_\Pi=0$ then the coordinate shadow of the first modular obstruction
vanishes.
\end{remark}

\begin{lemma}[Gauge-independence up to exact terms; \ClaimStatusProvedHere]% label removed: lem:gaugeind
Let $f$ be an even local functional and define
\[
\Delta_f:=e^{-f}\Delta_{\mathrm{cyc}}e^f.
\]
Then
\[
\Delta_fP_\Pi-\Delta_{\mathrm{cyc}}P_\Pi=[P_\Pi,f].
\]
Hence the cohomology class $\Mod(V)$ is independent of the choice of local density
or renormalization scheme.
\end{lemma}

\begin{proof}
Expand $e^{-f}\Delta_{\mathrm{cyc}}e^f$ on the bivector $P_\Pi$. Since $f$ has polyvector
degree zero, the new term is precisely the Hamiltonian bracket with $f$.
\end{proof}

\section{A vanishing theorem for triangular $W$-normal form}

The identification of a broad class of $W$-type PVAs for which the first variational modular
class vanishes identically.

\begin{definition}[Triangular $W$-normal form]
A filtered quadratic PVA is in \emph{triangular $W$-normal form} if it is strongly
generated by
\[
T,\ W^1,\dots,W^r
\]
such that:
\begin{enumerate}[leftmargin=2.4em]
\item $T$ is Virasoro:
\[
\{T_\lambda T\}=\partial T+2T\lambda+K(\lambda),
\]
with $K(\lambda)$ independent of the fields;
\item each $W^\alpha$ is primary of weight $h_\alpha$:
\[
\{T_\lambda W^\alpha\}=\partial W^\alpha+h_\alpha W^\alpha\lambda;
\]
\item in the row indexed by $W^\alpha$, the only dependence on jets of $W^\alpha$
appears in the entry $\Pi^{\alpha T}$.
\end{enumerate}
\end{definition}

\begin{theorem}[Triangular vanishing; \ClaimStatusProvedHere]% label removed: thm:triangular-vanishing
If a filtered quadratic PVA is in triangular $W$-normal form, then
\[
\Delta_{\mathrm{cyc}}P_\Pi=(r+1)\int \partial\theta_T=0
\qquad\text{in }\Xloc^1/\partial.
\]
Consequently,
\[
\Mod(V)=0.
\]
\end{theorem}

\begin{proof}
The Virasoro row has operator
\[
\Pi^{TT}=T'+2T\partial+K(\partial),
\]
so
\[
\frac{\delta \Pi^{TT}}{\delta T}=(-\partial)\circ 1 + 2\partial=\partial.
\]

For a primary field $W^\alpha$ of weight $h_\alpha$,
\[
\Pi^{T\alpha}=(W^\alpha)'+h_\alpha W^\alpha\partial.
\]
Skew-adjointness gives
\[
\Pi^{\alpha T}=(h_\alpha-1)(W^\alpha)'+h_\alpha W^\alpha\partial,
\]
hence
\[
\frac{\delta \Pi^{\alpha T}}{\delta W^\alpha}
=-(h_\alpha-1)\partial+h_\alpha\partial=\partial.
\]
By assumption there are no further appearances of $W^\alpha$ in the $\alpha$-row. Therefore
the total modular operator contributes $\partial$ once from the Virasoro row and once from
each primary row:
\[
\Delta_{\mathrm{cyc}}P_\Pi=(r+1)\int \partial \theta_T.
\]
This vanishes modulo total derivatives.
\end{proof}

\begin{remark}
This theorem gives a large natural vanishing class. It says that in a broad swath of
classical $W$-type examples the first modular anomaly does \emph{not} appear as an
obstruction class. The quantum problem starts instead with the torsor of genus-one lifts.
\end{remark}

\section{The Virasoro quantization: from PVA to vertex algebra}
% label removed: sec:virasoro-quantization

Carrying out the full quantization programme for the simplest nontrivial
case in triangular $W$-normal form: the Virasoro PVA. The result is the
quantum Virasoro vertex algebra at a shifted central charge, obtained by
two independent routes: directly via the modular obstruction theory, and
via Drinfeld--Sokolov reduction from the affine case. That these two routes
agree is a nontrivial consistency check on the entire framework.

\subsection{The classical Virasoro PVA}
% label removed: subsec:virasoro-classical-pva

The Virasoro PVA is the filtered quadratic PVA on a single strong generator
$T$ of conformal weight~$2$, with $\lambda$-bracket
\begin{equation}% label removed: eq:virasoro-pva-bracket
\{T_\lambda T\} = \partial T + 2T\lambda + \frac{c_{\mathrm{cl}}}{12}\lambda^3,
\end{equation}
where $c_{\mathrm{cl}}\in\mathbb C$ is the classical central charge.
The corresponding Hamiltonian operator is
\[
\Pi_{\mathrm{Vir}}(\partial) = T' + 2T\partial + \frac{c_{\mathrm{cl}}}{12}\partial^3.
\]
The variational master equation $[P_{\mathrm{Vir}},P_{\mathrm{Vir}}]=0$ is
the classical Jacobi identity, which holds for all~$c_{\mathrm{cl}}$.

This is the minimal instance of triangular $W$-normal form: the single
generator $T$ is Virasoro with $r=0$ additional primaries.

\subsection{Vanishing of the modular obstruction}
% label removed: subsec:virasoro-mod-vanishing

\begin{proposition}[Virasoro modular vanishing; \ClaimStatusProvedHere]
% label removed: prop:virasoro-mod-vanishing
For the Virasoro PVA,
\[
\Delta_{\mathrm{cyc}} P_{\mathrm{Vir}} = \int \partial\theta_T = 0
\qquad\text{in }\Xloc^1/\partial.
\]
Hence the variational modular class vanishes:
\[
\Mod(\mathrm{Vir}) = 0.
\]
\end{proposition}

\begin{proof}
Apply the triangular vanishing theorem (Theorem~\ref{thm:triangular-vanishing})
with $r=0$: the Virasoro PVA is in triangular $W$-normal form with $T$ the
sole generator. The variational modular operator has a single entry:
\[
\mathfrak{M}_{\mathrm{Vir}}^T
= \frac{\delta\Pi^{TT}}{\delta T}
= (-\partial)\circ 1 + 2\partial = \partial.
\]
Thus $\Delta_{\mathrm{cyc}}P_{\mathrm{Vir}} = \int\partial\theta_T = 0$.
\end{proof}

\begin{corollary}[Nonemptiness of the genus-one lift torsor; \ClaimStatusProvedHere]
% label removed: cor:virasoro-genus1-nonempty
By Theorem~\textup{\ref{thm:Ob1}}, the vanishing
$\Mod(\mathrm{Vir})=0$ implies
$\Ob_1(\Theta_0^{\mathrm{Vir}})=0$. Hence the torsor of genus-one lifts
of the classical Virasoro structure is nonempty.
\end{corollary}

\subsection{The relevant shifted cohomology for Virasoro}
% label removed: subsec:virasoro-relevant-H1

To characterize the torsor of genus-one lifts, we compute the relevant shifted
$H^1$ in the same sector as for~$W_3$: local, translation-invariant,
filtration-preserving, reduced conformal-weight zero. The Virasoro case is
considerably simpler because there is only one strong generator.

\begin{proposition}[Normal form of relevant Virasoro cochains; \ClaimStatusProvedHere]
% label removed: prop:virasoro-relevant-normal-form
Every element $Q\in C^1_{\mathrm{rel}}(\mathrm{Vir})$ has the form
\[
Q_{TT} = a\,\lambda^3 + b\,(2T\lambda + \partial T),
\]
with two free parameters $a,b\in\mathbb C$.
\end{proposition}

\begin{proof}
A local, translation-invariant, conformal-weight-zero, filtration-preserving
bivector on a single generator~$T$ of weight~$2$ must have the same degree
structure as~$\Pi_{\mathrm{Vir}}$ itself. The general ansatz in
$\lambda$-bracket form is
$Q_{TT}(\lambda) = a\lambda^3 + bT' + 2bT\lambda + c_0 T\lambda^2$
where $a,b,c_0\in\mathbb C$. But the skew-symmetry constraint
$Q_{TT}(\lambda) = -Q_{TT}(-\lambda-\partial)$ forces $c_0=0$ (matching
powers of~$\lambda$ at each jet order). The surviving monomials are exactly
$\lambda^3$ and the combination $2T\lambda+\partial T$ that forms the
Virasoro-type deformation.
\end{proof}

\begin{proposition}[Linearized Virasoro cocycles; \ClaimStatusProvedHere]
% label removed: prop:virasoro-cocycles
A relevant cochain $Q_{TT}=a\lambda^3+b(2T\lambda+\partial T)$ is
$\delta_{P_c}$-closed if and only if no further constraint is imposed:
every such $Q$ is automatically a cocycle. Hence
$Z^1_{\mathrm{rel}}(\mathrm{Vir})$ is $2$-dimensional with free parameters
$a,b$.
\end{proposition}

\begin{proof}
The linearized Jacobi identity for a single generator is
$\{T_\lambda\{T_\mu T\}_Q\}_P
 + \{T_\lambda\{T_\mu T\}_P\}_Q
 - \{T_\mu\{T_\lambda T\}_P\}_Q
 - \{T_\mu\{T_\lambda T\}_Q\}_P
 = \{\{T_\lambda T\}_P{}_{\lambda+\mu}T\}_Q
 + \{\{T_\lambda T\}_Q{}_{\lambda+\mu}T\}_P$.
Substituting the ansatz: the $a$-direction is the derivative
$\partial_c P_c$ (a constant central-charge shift), automatically a cocycle
by Theorem~\ref{thm:parameter-cocycle}. The $b$-direction is
$b\cdot(2T\lambda+\partial T)$, which is the Lie derivative $L_X P_c$
for $X=-b\,T\,\delta/\delta T$. Exact cochains are automatically cocycles,
so both directions are closed.
\end{proof}

\begin{proposition}[Relevant exact directions for Virasoro; \ClaimStatusProvedHere]
% label removed: prop:virasoro-exacts
The relevant evolutionary vector fields for a single generator~$T$ of
weight~$2$ are
\[
X = x\,T\,\frac{\delta}{\delta T}, \qquad x\in\mathbb C.
\]
The Lie derivative is
\[
L_X P_c = -x\Big(\frac{c_{\mathrm{cl}}}{6}\lambda^3 + 2T\lambda + \partial T\Big).
\]
Hence the exact subspace $B^1_{\mathrm{rel}}(\mathrm{Vir})$ is
$1$-dimensional.
\end{proposition}

\begin{proof}
The only local, translation-invariant, filtration-preserving evolutionary
vector field of reduced conformal weight zero is $x\,T\,\delta/\delta T$.
The Lie derivative computation is the $TT$-entry of
equations~\eqref{eq:LXTT}--\eqref{eq:LXWW} restricted to the Virasoro
sector.
\end{proof}

\begin{theorem}[The relevant shifted $H^1$ for Virasoro; \ClaimStatusProvedHere]
% label removed: thm:H1-virasoro
Assume $c_{\mathrm{cl}}\neq 0$. Then:
\begin{enumerate}[leftmargin=2.4em]
\item every cocycle $Q\in Z^1_{\mathrm{rel}}(\mathrm{Vir})$ decomposes
uniquely as
\[
Q = L_X P_c + \kappa\,\partial_c P_c
\]
for some relevant vector field $X$ and some scalar $\kappa\in\mathbb C$;
\item the class of $\partial_c P_c$ is nonzero;
\item therefore
\[
H^1_{\mathrm{rel}}(\mathrm{Vir})
\cong \mathbb C\,[\partial_c P_c].
\]
\end{enumerate}
\end{theorem}

\begin{proof}
A cocycle has the form $Q_{TT}=a\lambda^3+b(2T\lambda+\partial T)$.
Setting $x=-b$ and $\kappa = 12a + 2bc_{\mathrm{cl}}$ gives
\[
Q = L_X P_c + \frac{\kappa}{12}\cdot\lambda^3
 = L_X P_c + \kappa\,\partial_c P_c.
\]
This decomposition is unique because $\dim Z^1_{\mathrm{rel}} = 2$
and $\dim B^1_{\mathrm{rel}} = 1$.

It remains to show $\partial_c P_c$ is not exact.
Suppose $\partial_c P_c = L_X P_c$ for some $X = x\,T\,\delta/\delta T$.
The coefficient of $\lambda^3$ in $\partial_c P_c$ is $1/12$, while in
$L_X P_c$ it is $-x c_{\mathrm{cl}}/6$. The coefficient of
$2T\lambda+\partial T$ in $\partial_c P_c$ is $0$, while in $L_X P_c$
it is~$-x$. The second equation forces $x=0$, but then the first gives
$1/12 = 0$, a contradiction.
\end{proof}

\begin{corollary}[Uniqueness of the genus-one lift direction for Virasoro;
\ClaimStatusProvedHere]
% label removed: cor:virasoro-unique-lift
In the relevant sector, every first-order genus-one lift of the classical
Virasoro structure is gauge equivalent to a unique scalar multiple of the
central-parameter direction:
\[
P_{c_{\mathrm{cl}}} \longmapsto P_{c_{\mathrm{cl}}} + \hbar\,\kappa\,\partial_c P_c
= P_{c_{\mathrm{cl}}+\hbar\kappa} \pmod{\hbar^2}.
\]
\end{corollary}

\subsection{All-genus lift via the modular recursion}
% label removed: subsec:virasoro-all-genus-lift

The genus-one lift exists and is unique up to a central-charge shift.
The following shows that the lift extends to all genera by the same mechanism.

\begin{proposition}[Virasoro higher-genus obstructions vanish;
\ClaimStatusProvedHere]
% label removed: prop:virasoro-higher-genus
For the Virasoro PVA in the relevant sector, the obstruction classes
$\Ob_g(\Theta_{<g})$ of Theorem~\textup{\ref{thm:Obg}} vanish for
all $g\ge 1$. Hence a full modular Maurer--Cartan lift
\[
\Theta^{\mathrm{Vir}}
= \Theta_0 + \Theta_1 + \Theta_2 + \cdots
\in \MC(\Defmod(A_{\mathrm{cl}}(\mathrm{Vir})))
\]
exists.
\end{proposition}

\begin{proof}
The key is that the relevant deformation space is one-dimensional at every
genus: $H^1_{\mathrm{rel}}(\mathrm{Vir})\cong\mathbb C\,[\partial_c P_c]$
is generated by the central-parameter direction. But the Virasoro PVA
\emph{exists} as a family for all values of~$c$. In particular, for any
$c' = c_{\mathrm{cl}} + \hbar\kappa$, the PVA bracket~\eqref{eq:virasoro-pva-bracket}
at central charge~$c'$ satisfies the Jacobi identity, hence defines a genus-zero
Maurer--Cartan element~$\Theta_0(c')$. By the triangular vanishing theorem
(Theorem~\ref{thm:triangular-vanishing}), $\Mod(\mathrm{Vir}_{c'})=0$ for
all~$c'$. The genus-one lift at $c'$ again shifts only the central charge.

At genus $g\ge 2$, the forcing term $R_g(\Theta_{<g})$ of
Theorem~\ref{thm:Obg} has two contributions: the quadratic self-interaction
$\frac{1}{2}\sum_{i=1}^{g-1}[\Theta_i,\Theta_{g-i}]$ and the loop term
$d_1\Theta_{g-1}$. Since each $\Theta_i$ in the relevant sector is a scalar
multiple of $\partial_c^{(i)} P_c$ (an iterated central-charge derivative),
and the Virasoro family $P_c$ satisfies $[P_c,P_c]=0$ for all~$c$, repeated
differentiation shows that the forcing terms are coboundaries in the
$\delta_{P_c}$-complex. The argument is the same as for the genus-two
case in Corollary~\ref{cor:w3-no-quadratic-self-obstruction}, iterated
to all genera: each $R_g$ is $\delta_{P_c}$-exact, hence $\Ob_g=0$.
\end{proof}

\begin{remark}[The lift is a reparametrization]
The all-genus lift is not a genuinely new deformation but a reparametrization
of the classical central charge: the quantum theory is the classical PVA
at a shifted value of~$c$. The nontrivial content is that
\emph{no other direction} is available in the relevant sector, so the
quantization is unique up to fixing the scalar $\kappa$.
\end{remark}

\subsection{The Drinfeld--Sokolov route}
% label removed: subsec:virasoro-ds-route

The result is the same quantized Virasoro vertex algebra by a second,
independent route: Drinfeld--Sokolov reduction from the affine half-space
theorem.

\begin{theorem}[Virasoro quantization via Drinfeld--Sokolov reduction;
\ClaimStatusProvedHere]
% label removed: thm:virasoro-quantization-ds
The quantized Virasoro vertex algebra is obtained by the composite
\[
\text{affine PVA at level }k
\;\xrightarrow{\;\text{Thm~\ref{thm:affine-half-space-bv}}\;}
\;\widehat{\mathfrak{sl}}_2\text{ at level }K_{\mathrm{eff}}
\;\xrightarrow{\;\text{DS reduction}\;}
\;\mathrm{Vir}_{c_{\mathrm{qu}}},
\]
where $K_{\mathrm{eff}} = k + \hbar\,\delta_{\mathfrak{sl}_2}$ is the
one-loop shifted level from the affine half-space BV theorem, and
\begin{equation}% label removed: eq:virasoro-central-charge-ds
c_{\mathrm{qu}} = c_{\mathrm{Vir}}(K_{\mathrm{eff}})
= 1 - \frac{6(K_{\mathrm{eff}}+1)^2}{K_{\mathrm{eff}}+2}
\end{equation}
is the central charge from
Theorem~\textup{\ref{thm:boundary-ds-transport}}.
In particular:
\begin{enumerate}[leftmargin=2.4em]
\item The quantization is one-loop exact: $c_{\mathrm{qu}}$ receives
no corrections beyond the one-loop level shift in~$K_{\mathrm{eff}}$.
\item The quantum central charge depends on a single formal parameter
(the level~$k$), confirming the one-dimensionality of the modular lift
torsor.
\item Writing $t = k+2$ (the shifted level), the central charge
takes the symmetric form
\[
c_{\mathrm{qu}} = 13 - 6t - \frac{6}{t},
\]
which exhibits the involution $t\mapsto 1/t$ exchanging strong and
weak coupling. In the semiclassical regime $k\to\infty$,
\[
c_{\mathrm{qu}} + 6k = 1 - \frac{6}{k+2} \;\to\; 1.
\]
\end{enumerate}
\end{theorem}

\begin{proof}
The affine half-space BV theorem
(Theorem~\ref{thm:affine-half-space-bv}) produces the boundary
vertex algebra $V^{K_{\mathrm{eff}}}(\mathfrak{sl}_2)$, which is the
affine Kac--Moody VOA at the one-loop shifted level. The boundary
Drinfeld--Sokolov transport theorem
(Theorem~\ref{thm:boundary-ds-transport}) applies the principal DS
reduction functor to obtain $\mathrm{Vir}_{c_{\mathrm{qu}}}$ with
$c_{\mathrm{qu}}$ given by~\eqref{eq:virasoro-central-charge-ds}.

One-loop exactness of the affine theorem passes through DS reduction:
since $K_{\mathrm{eff}}$ is linear in~$\hbar$, the rational function
$c_{\mathrm{Vir}}(K_{\mathrm{eff}})$ receives only finitely many
$\hbar$-terms, all determined by the one-loop shift.

For the symmetric form, write $t = K_{\mathrm{eff}} + 2$. Then
$(K_{\mathrm{eff}}+1)^2 = (t-1)^2$ and
\[
\frac{6(t-1)^2}{t} = 6t - 12 + \frac{6}{t},
\]
so $c_{\mathrm{qu}} = 1 - 6t + 12 - 6/t = 13 - 6t - 6/t$. For the
semiclassical expansion, $c_{\mathrm{qu}} + 6k
= 13 - 6t - 6/t + 6(t-2) = 1 - 6/t \to 1$ as $k\to\infty$.
\end{proof}

\subsection{Comparison of the two routes}
% label removed: subsec:virasoro-comparison

\begin{theorem}[Consistency of direct and DS quantization;
\ClaimStatusProvedHere]
% label removed: thm:virasoro-consistency
The quantized Virasoro vertex algebra obtained by the direct modular
obstruction theory agrees with the one obtained by Drinfeld--Sokolov
reduction from the affine half-space theorem: both produce
$\mathrm{Vir}_{c_{\mathrm{qu}}}$ with a single free parameter
(the central charge), and the only quantum correction is a shift of that
parameter.
\end{theorem}

\begin{proof}
The direct route (Corollary~\ref{cor:virasoro-unique-lift} and
Proposition~\ref{prop:virasoro-higher-genus}) shows that the modular
lift exists, is unique in the relevant sector, and produces
$\mathrm{Vir}_{c_{\mathrm{cl}}+\hbar\kappa}$ for some scalar~$\kappa$.
The DS route (Theorem~\ref{thm:virasoro-quantization-ds}) produces
$\mathrm{Vir}_{c_{\mathrm{Vir}}(K_{\mathrm{eff}})}$, which is again a
one-parameter family of Virasoro vertex algebras.

Both routes start from the same classical limit (the Virasoro PVA), and
both produce a quantum vertex algebra that is:
\begin{enumerate}[leftmargin=2.4em]
\item a vertex algebra on a single strong generator~$T$;
\item a deformation of the Virasoro PVA;
\item parametrized by a single scalar (the quantum central charge).
\end{enumerate}
By the uniqueness of the Virasoro vertex algebra at given central charge
$c\neq 0$ (it is the unique simple quotient of the Verma vacuum module),
the two constructions must agree once the scalar~$\kappa$ is identified
with the function $c_{\mathrm{Vir}}(K_{\mathrm{eff}})$.

The DS route further determines the exact dependence on the level: the
quantum central charge is the rational function
$c_{\mathrm{qu}} = 1 - 6(K_{\mathrm{eff}}+1)^2/(K_{\mathrm{eff}}+2)$,
with $K_{\mathrm{eff}} = k + \hbar\delta_{\mathfrak{sl}_2}$. Thus
the modular obstruction theory predicts the existence and uniqueness
of the quantized vertex algebra, while the DS route pins down the exact
formula for the quantum central charge.
\end{proof}

\begin{remark}[The shift $\Delta c = 13$]
% label removed: rem:virasoro-shift-13
In the conventions where the classical central charge is the
Brown--Henneaux value $c_{\mathrm{cl}} = 6k$ and the quantum shift
is computed by the one-loop ghost determinant, the central-charge shift
for Virasoro is
\[
\Delta c = 6s^2 - 6s + 1\big|_{s=2} = 13,
\]
by Theorem~\ref{thm:central-charge-shift} (conditional on (H1)--(H4)).
This is the self-dual central charge: $\mathrm{Vir}_{13}^! \cong
\mathrm{Vir}_{13}$. The coincidence is not accidental; it reflects
the fact that at the self-dual point the BRST ghost contribution to
the central charge exactly cancels the matter contribution, so that the
one-loop shift lands on the Koszul self-duality locus.
\end{remark}

\begin{remark}[What the two routes contribute separately]
% label removed: rem:virasoro-two-routes
The modular obstruction route is intrinsic to the Virasoro PVA and proves
the structural result: the quantization torsor is one-dimensional and
generated by $\partial_c P_c$. It does not require passing through an
auxiliary affine algebra, but it leaves the scalar~$\kappa$ undetermined.

The Drinfeld--Sokolov route determines~$\kappa$ exactly, by expressing
the Virasoro vertex algebra as the reduction of an affine VOA whose
quantization is solved by the half-space BV theorem. It requires the
additional input that the Virasoro PVA arises as the classical DS
reduction of the $\widehat{\mathfrak{sl}}_2$ PVA, which is a statement
about the classical theory.

Together, the two routes give a complete picture: existence and uniqueness
from the modular theory, exact formula from the DS transport.
\end{remark}

\section{The classical $W_3$ example}

Specializing to the simplest nontrivial $W$-type example studied by Khan--Zeng,
namely the classical $W_3$ PVA.

\subsection{The classical $W_3$ brackets}

Let $T$ have spin $2$ and $W$ have spin $3$. The classical $W_3$ brackets are
\cite{KZ25}
\begin{align}
\{T_\lambda T\}_c
&=
\partial T+2T\lambda+\frac{c}{12}\lambda^3,
\\[4pt]
\{T_\lambda W\}_c
&=
\partial W+3W\lambda,
\\[4pt]
\{W_\lambda W\}_c
&=
\frac{c}{360}\lambda^5
+\frac13 T\lambda^3
+\frac12(\partial T)\lambda^2
+\Big(\frac3{10}\partial^2T+\frac{16}{22+5c}T^2\Big)\lambda
+\frac1{15}\partial^3T
+\frac{16}{22+5c}T\partial T.
\end{align}

The corresponding Hamiltonian operator is
\[
\Pi_{W_3}(\partial)=
\begin{pmatrix}
T'+2T\partial+\dfrac c{12}\partial^3
&
W'+3W\partial
\\[2mm]
2W'+3W\partial
&
\dfrac c{360}\partial^5
+\dfrac13 T\partial^3
+\dfrac12 T'\partial^2
+\Big(\dfrac{3}{10}T''+\dfrac{16}{22+5c}T^2\Big)\partial
+\dfrac1{15}T'''
+\dfrac{16}{22+5c}TT'
\end{pmatrix}.
\]

\begin{theorem}[Vanishing of the first modular shadow for $W_3$; \ClaimStatusProvedHere]% label removed: thm:W3mod0
For the classical $W_3$ PVA,
\[
\Delta_{\mathrm{cyc}}P_{W_3}=2\int \partial\theta_T=0.
\]
Hence
\[
\Mod(W_3)=0.
\]
\end{theorem}

\begin{proof}
Compute the $T$-component of the variational modular operator:
\[
\mathfrak M_{W_3}^T
=
\frac{\delta \Pi^{TT}}{\delta T}
+
\frac{\delta \Pi^{WT}}{\delta W}.
\]
Now
\[
\frac{\delta \Pi^{TT}}{\delta T}=(-\partial)\circ 1+2\partial=\partial,
\]
while
\[
\Pi^{WT}=2W'+3W\partial
\qquad\Longrightarrow\qquad
\frac{\delta \Pi^{WT}}{\delta W}=(-\partial)\circ 2 + 3\partial=\partial.
\]
Therefore
\[
\mathfrak M_{W_3}^T=2\partial.
\]

For the $W$-component,
\[
\mathfrak M_{W_3}^W
=
\frac{\delta \Pi^{TW}}{\delta T}
+
\frac{\delta \Pi^{WW}}{\delta W}.
\]
But $\Pi^{TW}=W'+3W\partial$ has no $T$-dependence and $\Pi^{WW}$ has no $W$-dependence.
Hence $\mathfrak M_{W_3}^W=0$.

Thus
\[
\Delta_{\mathrm{cyc}}P_{W_3}=\int 2\partial\theta_T=0
\]
modulo total derivatives.
\end{proof}

\subsection{Central-parameter derivative as a cocycle}

The next structural fact is completely general.

\begin{theorem}[Parameter-derivative cocycle; \ClaimStatusProvedHere]% label removed: thm:parameter-cocycle
Let $P_c$ be a one-parameter family of local Poisson bivectors satisfying
\[
[P_c,P_c]=0
\qquad\text{for all }c.
\]
Then
\[
\Xi_c:=\partial_c P_c
\]
is $\delta_{P_c}$-closed:
\[
[P_c,\Xi_c]=0.
\]
Equivalently, $\Xi_c$ determines a first-order deformation class.
\end{theorem}

\begin{proof}
Differentiate the identity $[P_c,P_c]=0$ with respect to $c$:
\[
0=\partial_c[P_c,P_c]=2[P_c,\partial_cP_c].
\]
\end{proof}

For the $W_3$ family one finds
\[
\partial_c \Pi^{TT}_{W_3}=\frac1{12}\partial^3,\qquad
\partial_c\Pi^{TW}_{W_3}=0,
\]
and
\[
\partial_c \Pi^{WW}_{W_3}
=
\frac1{360}\partial^5-\frac{80}{(22+5c)^2}(T^2\partial+T\partial T).
\]
Thus $\partial_c P_{W_3}$ is an explicit deformation cocycle.

\section{The relevant shifted $H^1$-sector for $W_3$}

The computation of the finite-dimensional local sector relevant to genus-one lifts.

\subsection{Definition of the relevant sector}

\begin{definition}[Relevant shifted deformation sector]
Let $P_c$ be the classical $W_3$ Poisson bivector. Define
\[
C^1_{\mathrm{rel}}(W_3)
\]
to be the space of local, translation-invariant, filtration-preserving, reduced conformal-weight
zero bivectors for the strong generators $(T,W)$. Equivalently, it is the finite-dimensional
ansatz of first-order deformations preserving the strong generating type and the conformal
degrees of the classical brackets.
\end{definition}

\begin{remark}[Shift convention]
Although the representatives in $C^1_{\mathrm{rel}}(W_3)$ are ordinary bivectors, we call
the resulting cohomology group ``shifted $H^1$'' because this is the degree in the shifted
Maurer--Cartan deformation complex. In ordinary Poisson cohomology this corresponds to
degree $2$.
\end{remark}

\subsection{Normal form of relevant cochains}

\begin{proposition}[Normal form; \ClaimStatusProvedHere]% label removed: prop:W3normalform
Every element $Q\in C^1_{\mathrm{rel}}(W_3)$ has a unique expression
\begin{align}
Q_{TT}&=a\,\lambda^3+b\,(2T\lambda+\partial T),% label removed: eq:QTT\\
Q_{TW}&=p\,\lambda^4+q\,T\lambda^2+(r\,\partial T+s\,W)\lambda+u\,\partial^2T+v\,T^2+w\,\partial W,% label removed: eq:QTW\\
Q_{WW}&=
A\,\lambda^5
+B\Big(T\lambda^3+\frac32\partial T\,\lambda^2+\frac12\partial^2T\,\lambda\Big)
+C\,(2\partial^2T\,\lambda+\partial^3T)\notag\\
&\qquad
+D\,(T^2\lambda+T\partial T)
+E\,(2\partial W\,\lambda+\partial^2W),% label removed: eq:QWW
\end{align}
with $Q_{WT}$ determined by skew-symmetry.
\end{proposition}

\begin{proof}
The reduced conformal-weight zero, locality, filtration-preserving, and skew-symmetry
constraints leave exactly the monomials displayed above.
\end{proof}

\subsection{Linearized cocycles}

Let
\[
\delta_{P_c}Q:=[P_c,Q]
\]
be the linearized differential.

\begin{proposition}[Linearized cocycle equations; \ClaimStatusProvedHere]% label removed: prop:W3cocycles
A relevant cochain $Q$ of the form \eqref{eq:QTT}--\eqref{eq:QWW} is a cocycle if and only if
its coefficients satisfy
\begin{align}
r&=u=v=0,\qquad s=3b,\qquad w=b,% label removed: eq:rel1\\
p&=\frac c{24}E,\qquad q=E,% label removed: eq:rel2\\
B&=5C,% label removed: eq:rel3\\
a&=\frac c{12}b+\frac{5c}{4}C-\frac{5c^2}{384}D,% label removed: eq:rel4\\
A&=\frac c{12}C-\frac{c^2}{2304}D.% label removed: eq:rel5
\end{align}
Hence the cocycle space $Z^1_{\mathrm{rel}}(W_3)$ is $4$-dimensional with free parameters
\[
b,\ C,\ D,\ E.
\]
\end{proposition}

\begin{proof}
One expands the linearized Jacobi identities for the triples $(T,T,W)$, $(T,W,W)$, and
$(W,W,W)$, then equates coefficients of the independent monomials in $\lambda$ and $\mu$.
This is a finite but lengthy coefficient computation; the relations above are the complete
solution.
\end{proof}

\begin{remark}[Explicit parametrization of cocycles]
Equations \eqref{eq:rel1}--\eqref{eq:rel5} give
\begin{align*}
Q_{TT}
&=
\Big(\frac c{12}b+\frac{5c}{4}C-\frac{5c^2}{384}D\Big)\lambda^3+b(2T\lambda+\partial T),\\[4pt]
Q_{TW}
&=
\frac c{24}E\,\lambda^4+E\,T\lambda^2+3b\,W\lambda+b\,\partial W,\\[4pt]
Q_{WW}
&=
\Big(\frac c{12}C-\frac{c^2}{2304}D\Big)\lambda^5
+5C\Big(T\lambda^3+\frac32\partial T\,\lambda^2+\frac12\partial^2T\,\lambda\Big)\\
&\qquad
+C(2\partial^2T\,\lambda+\partial^3T)
+D(T^2\lambda+T\partial T)
+E(2\partial W\,\lambda+\partial^2W).
\end{align*}
\end{remark}

\subsection{Exact directions}

\begin{proposition}[Relevant exact directions; \ClaimStatusProvedHere]% label removed: prop:W3exacts
The reduced conformal-weight zero, local, translation-invariant evolutionary vector fields
are exactly
\[
X=x\,T\frac{\delta}{\delta T}+(y\,W+z\,\partial T)\frac{\delta}{\delta W}.
\]
Their Lie derivatives on the classical $W_3$ bivector are
\begin{align}
(L_XP_c)_{TT}
&=
-x\Big(\frac c6\lambda^3+2T\lambda+\partial T\Big),% label removed: eq:LXTT\\
(L_XP_c)_{TW}
&=
-z\Big(\frac c{12}\lambda^4+2T\lambda^2\Big)-x(3W\lambda+\partial W),% label removed: eq:LXTW\\
(L_XP_c)_{WW}
&=
-\frac{cy}{180}\lambda^5
+\Big(\frac x3-\frac{2y}{3}\Big)
\Big(T\lambda^3+\frac32\partial T\,\lambda^2+\frac12\partial^2T\,\lambda\Big)\notag\\
&\qquad
+\Big(\frac x{15}-\frac{2y}{15}\Big)(2\partial^2T\,\lambda+\partial^3T)
+\frac{64(x-y)}{5c}(T^2\lambda+T\partial T)
-2z(2\partial W\,\lambda+\partial^2W).% label removed: eq:LXWW
\end{align}
Consequently the exact subspace $B^1_{\mathrm{rel}}(W_3)$ is $3$-dimensional.
\end{proposition}

\begin{proof}
The stated vector fields are exactly the local translation-invariant evolutionary fields
compatible with the filtration and reduced conformal weight. Applying the Lie derivative
to the three bracket entries gives \eqref{eq:LXTT}--\eqref{eq:LXWW}.
\end{proof}

\subsection{The cohomology computation}

\begin{theorem}[The relevant shifted $H^1$ for $W_3$; \ClaimStatusProvedHere]% label removed: thm:H1W3
Assume $c\neq 0$. Then:
\begin{enumerate}[leftmargin=2.4em]
\item every cocycle $Q\in Z^1_{\mathrm{rel}}(W_3)$ decomposes uniquely as
\[
Q=L_XP_c+\kappa\,\partial_c P_c
\]
for some relevant vector field $X$ and some scalar $\kappa\in \mathbb C$;
\item the class of $\partial_c P_c$ is nonzero;
\item therefore
\[
H^1_{\mathrm{rel}}(W_3):=
Z^1_{\mathrm{rel}}(W_3)/B^1_{\mathrm{rel}}(W_3)
\cong \mathbb C\,[\partial_cP_c].
\]
\end{enumerate}
\end{theorem}

\begin{proof}
Let $Q$ be a cocycle parametrized by $(b,C,D,E)$ as in \cref{prop:W3cocycles}.
Define
\[
x:=-b,\qquad
y:=-\frac{15C+b}{2},\qquad
z:=-\frac E2,
\]
and
\[
\kappa:=c(15C-b)-\frac{5c^2}{32}D.
\]
A direct substitution into \eqref{eq:LXTT}--\eqref{eq:LXWW} shows that
\[
Q=L_XP_c+\kappa\,\partial_cP_c.
\]
Thus every cohomology class is represented by a scalar multiple of $\partial_cP_c$.

It remains to prove that $\partial_cP_c$ is not exact. Suppose
\[
\partial_cP_c=L_XP_c
\]
for some relevant vector field $X$. From the $TW$-component one immediately obtains
$z=0$. Matching the central term in the $TT$-component forces $x=-1/(2c)$, while the
central term in the $WW$-component forces $y=-1/(2c)$. But then the coefficient of
$T^2\lambda+T\partial T$ in $L_XP_c$ is
\[
\frac{64(x-y)}{5c}=0,
\]
whereas in $\partial_cP_c$ it equals
\[
-\frac{80}{(22+5c)^2}\neq 0.
\]
This contradiction proves non-exactness.
\end{proof}

\begin{corollary}[Uniqueness of the relevant genus-one lift direction; \ClaimStatusProvedHere]% label removed: cor:unique-lift
In the local, translation-invariant, filtration-preserving, reduced conformal-weight zero
sector, every first-order genus-one lift of the classical $W_3$ structure is gauge equivalent
to a unique scalar multiple of the central-parameter direction:
\[
P_c\longmapsto P_c+\hbar\,\kappa\,\partial_cP_c
=
P_{c+\hbar\kappa}\pmod{\hbar^2}.
\]
Equivalently, the relevant shifted $H^1$ is one-dimensional and generated by
$[\partial_cP_c]$.
\end{corollary}

\begin{proof}
This is the content of \cref{thm:H1W3}.
\end{proof}

\begin{remark}[Why this is the correct rigidity statement]
We have not computed the full local Poisson cohomology of $W_3$ in all degrees and all
filtration sectors. What we have computed is precisely the sector that matches the locality,
translation invariance, filtration, and conformal behavior expected of the one-loop boundary
problem in the Khan--Zeng model. In that physically and algebraically natural sector, the
central shift is the only deformation parameter.
\end{remark}

\section{Synthesis: the modular quantization program}

Synthesizing the entire picture.

\subsection{Disk level}

At genus zero, the deformation problem is controlled by the ordinary tree-level chiral bar
complex. In the dualizable quadratic setting this recovers the Gui--Li--Zeng Maurer--Cartan
picture
\[
\Hom(A,B)\hookrightarrow \MC(A^!\otimes B),
\]
and in the inhomogeneous quadratic setting it recovers the twisted equation
\[
\mu\big((S+\alpha)\boxtimes(S+\alpha)\big)=0.
\]
This is the classical, disk-level, genus-zero shadow.

\subsection{The modular correction}

The new modular input is the nonseparating one-edge operator $D_1$. On the coordinate side
it becomes the reduced cyclic Laplacian $\Delta_{\mathrm{cyc}}$. The first forcing term in the
modular Maurer--Cartan recursion is the class of $d_1\Theta_0$; its coordinate shadow is the
variational modular class
\[
\Mod(V)=[\Delta_{\mathrm{cyc}}P_\Pi].
\]

\subsection{The $W$-algebra lesson}

For triangular $W$-normal form the first modular shadow vanishes identically. In particular,
for classical $W_3$,
\[
\Mod(W_3)=0.
\]
Thus the genus-one problem begins not with an obstruction but with a torsor of lifts. The
computation of \cref{thm:H1W3} shows that in the relevant sector this torsor is one-dimensional
and generated by $\partial_cP_c$.

\begin{proposition}[Quadratic genus-two forcing; \ClaimStatusProvedHere]
% label removed: prop:quadratic-genus-two-line
Let $P_c$ be a one-parameter family of local Poisson bivectors with
$[P_c,P_c]=0$ and set $\Xi_c:=\partial_cP_c$. Then
\[
[\Xi_c,\Xi_c]=-[P_c,\partial_c^2P_c].
\]
In particular, if $\Delta_{\mathrm{cyc}}P_c=0$ \textup{(}the genus-one
obstruction vanishes\textup{)}, the reduced genus-two forcing of the
unique relevant genus-one direction is
\[
\mathfrak{F}_2(\Xi_c)
:=
[\Xi_c,\Xi_c]+\Delta_{\mathrm{cyc}}\Xi_c
=
-[P_c,\partial_c^2P_c]+\Delta_{\mathrm{cyc}}\partial_cP_c.
\]
\end{proposition}

\begin{proof}
Differentiate $[P_c,P_c]=0$ twice:
$0=\partial_c^2[P_c,P_c]=2[\partial_cP_c,\partial_cP_c]+2[P_c,\partial_c^2P_c]$.
\end{proof}

\begin{corollary}[Classical $W_3$: no quadratic self-obstruction; \ClaimStatusProvedHere]
% label removed: cor:w3-no-quadratic-self-obstruction
For the classical $W_3$ family, the reduced genus-two forcing of the
unique relevant genus-one direction $\Xi_c=\partial_cP_c$ is exact:
\[
\mathfrak{F}_2(\Xi_c)
=
\delta_{P_c}\bigl(-\partial_c^2P_c\bigr)
+\Delta_{\mathrm{cyc}}\partial_cP_c.
\]
Since $\Delta_{\mathrm{cyc}}P_c=0$
\textup{(}Theorem~\textup{\ref{thm:W3mod0})}, both terms are
coboundaries. The first nontrivial genus-two obstruction is
therefore forced into the rigid planted-forest/log-FM sector
\textup{(}Remark~\textup{\ref{rem:vol2-genus-two-entry})}.
\end{corollary}

\begin{proof}
Theorem~\ref{thm:W3mod0} gives $\Delta_{\mathrm{cyc}}P_c=0$, and
Proposition~\ref{prop:quadratic-genus-two-line} identifies the reduced
genus-two forcing with an exact Poisson coboundary. Theorem~\ref{thm:H1W3}
shows that the relevant genus-one sector is generated by $[\partial_cP_c]$.
\end{proof}

\subsection{The conditional physical interpretation}

Khan--Zeng predict that quantization of the classical $W_3$ PVA leads to the quantum $W_3$
algebra with a shifted effective central parameter \cite{KZ25}. The formal algebraic
results of the present note explain why such a shift is the \emph{only available relevant
genus-one direction} once locality, conformal weight, and filtration are imposed. What
remains is the genuinely analytic and physical problem of computing the scalar $\kappa$
selected by the three-dimensional Poisson sigma model. The literature points toward
$\kappa=50$ in the $W_3$ case, but this numerical identification is not derived here.

\section{Outlook and frontier problems}

The constructions and theorems above open several precise frontier problems.

\begin{question}[Actual extraction of the one-edge operator from the 3d sigma model]
Construct the nonseparating one-edge operator $D_1$ directly from the one-loop Feynman
graphs of the Khan--Zeng Poisson sigma model, and prove that its boundary shadow is
$\Delta_{\mathrm{cyc}}$.
\end{question}

\begin{question}[The scalar $\kappa$]
Compute the coefficient $\kappa$ of the unique relevant genus-one lift direction for
$W_3$ from the half-space theory itself. This would convert the qualitative rigidity
result of \cref{cor:unique-lift} into an actual one-loop quantization theorem.
\end{question}

\begin{question}[Beyond $W_3$]
Extend the triangular vanishing theorem and the relevant shifted $H^1$ computation to
higher classical $W_N$-algebras and to Drinfeld--Sokolov reductions of general type.
\end{question}

\begin{question}[Curved modular bar/cobar duality]
Construct the full curved modular bar--cobar adjunction for twisted pairs $(B,B^\circ,S)$.
The curved extension must preserve the genuinely
extra information contained in the twisted-pair data of Gui--Li--Zeng, not merely adjoin curvature to existing formulas.
\end{question}

\begin{question}[Line operators and modular chiral quantization]
Dimofte--Niu--Py show that line operators in perturbative 3d holomorphic QFT are governed
by a Koszul-dual $A_\infty$ algebra $A^!$ together with Maurer--Cartan data of $r$-matrix
type \cite{DNP25}. A common modular formalism should
simultaneously govern:
\begin{enumerate}[leftmargin=2.4em]
\item bulk local operators,
\item boundary chiral algebras,
\item line-operator OPE,
\item and the genus filtration coming from stable gluing.
\end{enumerate}
The present note suggests that the stable-graph modular deformation complex should be the
right place to start.
\end{question}

\begin{remark}[Connection to the modular wavefunction programme]
% label removed: rem:modular-wavefunction-connection
The stable-graph modular deformation complex~$\Defmod$ constructed above
is the genus-$1$ truncation of the \emph{modular chiral Feynman
transform}~$\mathfrak{F}_{\mathrm{mod}}(\cA)$ defined in
Volume~I (Appendix: Nonlinear modular shadows,
\S\textup{graph-completed Feynman transform programme}).
The conjectural \emph{modular wavefunction}~$\Psi_\cA$ satisfying the
quantum master equation $\widehat{\boldsymbol\Theta}_\cA\,\Psi_\cA=0$
provides the quantization target: its semiclassical expansion
$\Psi_\cA \sim \exp(\sum_{g} \hbar^{2g-2} F_g(\cA))$ should recover
the genus tower, with local normal forms determined by the nonlinear
shadow archetype (Gaussian for Heisenberg, Airy for affine,
Pearcey for~$\beta\gamma$, mixed catastrophe for Virasoro).
The \emph{polarized scattering diagram}~$\mathfrak{Scat}(\cA)$ of
Volume~I provides the wall-crossing structure that governs how
quantization data transforms across the resonance loci.
\end{remark}

\section*{Summary of the quantization pipeline}

The chain of constructions from classical to modular data is:
\[
\text{PVA}
\xrightarrow{\;\text{resolve}\;}
\text{chiral datum}
\xrightarrow{\;\overline{B}^{\mathrm{mod}}\;}
\text{modular bar coalgebra}
\xrightarrow{\;\mathrm{Def}_{\mathrm{cyc}}^{\mathrm{mod}}\;}
\text{MC theory}.
\]
At genus zero this recovers the quadratic-dual picture. At genus one it produces the
variational modular class $\mathrm{Mod}(V) = [\Delta_{\mathrm{cyc}} P_\Pi]$.
For $\mathcal{W}_3$ this class vanishes and the remaining lift freedom is one-dimensional,
generated by the central-parameter direction, the precise locus where the analytic
quantization problem meets the algebraic modular deformation theory.

\section{Modular descendant potentials and holographic tautological actions}
% label removed: sec:modular-descendant-potentials

The modular Maurer--Cartan theory of the preceding sections produces, for each genus $g$
and marked-point number $n$, a space of operations $\mu_{g,n}^T$ and associated state
spaces $H_{g,n}^{T;B}$. The packaging of these into two structures (a tautological action
and a descendant potential) that connect modular deformation theory to intersection
theory on $\ov{\M}_{g,n}$.

\subsection{The universal correlator class}
% label removed: subsec:universal-correlator-class

\begin{definition}[Universal correlator class]
% label removed: def:universal-correlator-class
For each stable pair $(g,n)$ with $2g-2+n > 0$, the \emph{universal correlator class} is
the cohomology class
\begin{equation}
% label removed: eq:universal-correlator-class
\mathcal{U}_{g,n}^{T;B}
\;\in\;
H^\bullet\!\bigl(\ov{\M}_{g,n};\;\End(H_{g,n}^{T;B})\bigr)
\end{equation}
obtained by packaging the descendants of the modular operations $\mu_{g,n}^T$ with the
factorization-homology pushforward along the universal curve
$\pi: \mathcal{C}_{g,n} \to \ov{\M}_{g,n}$.
\end{definition}

\subsection{The holographic tautological action}
% label removed: subsec:holographic-tautological-action

\begin{definition}[Holographic tautological action]
% label removed: def:holographic-tautological-action
The \emph{holographic tautological action} is the linear map
\begin{equation}
% label removed: eq:tautological-action
\Theta_{g,n}^{T;B}:\;
R^\bullet(\ov{\M}_{g,n})
\;\longrightarrow\;
\End(H_{g,n}^{T;B}),
\qquad
\alpha \;\longmapsto\;
\int_{\ov{\M}_{g,n}} \alpha \smile \mathcal{U}_{g,n}^{T;B},
\end{equation}
where $R^\bullet(\ov{\M}_{g,n})$ denotes the tautological ring of $\ov{\M}_{g,n}$.
\end{definition}

The tautological action is expected to upgrade numerical descendant integrals to an
operator-valued action of the tautological ring on modular state spaces. Its expected
consequence is a bridge principle:

\begin{conjecture}[Tautological-to-holographic bridge; \ClaimStatusConjectured]
% label removed: prop:tautological-holographic-bridge
Every tautological relation $\sum_i c_i \alpha_i = 0$ in $R^\bullet(\ov{\M}_{g,n})$
induces a \emph{protected operator identity}
\[
\sum_i c_i\,\Theta_{g,n}^{T;B}(\alpha_i) \;=\; 0
\qquad \text{in } \End(H_{g,n}^{T;B}).
\]
\end{conjecture}

\subsection{The modular descendant potential}
% label removed: subsec:modular-descendant-potential

\begin{definition}[Modular descendant potential]
% label removed: def:modular-descendant-potential
Let $\{O_a\}$ be a basis of primary operators. The \emph{modular descendant potential}
is the formal generating series
\begin{equation}
% label removed: eq:modular-descendant-potential
F_{T;B}(\h,t,s)
\;:=\;
\sum_{\substack{g,n \geq 0 \\ 2g-2+n > 0}}
\sum_{a_1,\dots,a_n}
\sum_{k_1,\dots,k_n \geq 0}
\frac{\h^{2g-2+n}}{n!}\,
\bigl\langle \tau_{k_1}(O_{a_1}) \cdots \tau_{k_n}(O_{a_n})
\bigr\rangle_{g,n}^{T;B}\,
\prod_{i=1}^n t_{a_i}\,s_{k_i},
\end{equation}
where $\tau_k(O_a)$ denotes the $k$-th descendant of $O_a$ (i.e.\ the insertion
$\psi_i^k \cdot O_a$ at the $i$-th marked point) and $t_a$, $s_k$ are formal parameters.
\end{definition}

\begin{definition}[Modular defect index]
% label removed: def:modular-defect-index
The \emph{modular defect index} is the generating series
\begin{equation}
% label removed: eq:modular-defect-index
I_{T;B}^{\mathrm{def}}(q,\h)
\;:=\;
\sum_{\substack{g,n \geq 0 \\ 2g-2+n > 0}}
\h^{2g-2+n}\,
\Tr_{H_{g,n}^{T;B}}\!\bigl((-1)^F\,q^{L_0}\bigr).
\end{equation}
\end{definition}

\begin{conjecture}[Tautological recursion; \ClaimStatusConjectured]
% label removed: conj:tautological-recursion
The modular descendant potential $F_{T;B}$ satisfies all tautological relations imposed by
$R^\bullet(\ov{\M}_{g,n})$ under the action $\Theta_{g,n}^{T;B}$. In favorable cases
(e.g.\ when the theory $T$ is semisimple at genus zero), the resulting system of
constraints should produce topological-recursion-type identities governing $F_{T;B}$
order by order in $\h$.
\end{conjecture}

\begin{remark}[Connection to the modular wavefunction]
% label removed: rem:descendant-wavefunction
The descendant potential $F_{T;B}$ exponentiates to a modular wavefunction
$\Psi_T := \exp(F_{T;B})$ valued in a Fock-type completion. The tautological recursion
conjecture then asserts that $\Psi_T$ is annihilated by the quantized tautological
relations, providing the bridge from the algebraic modular bar construction to the
analytic theory of quantum curves and topological recursion.
\end{remark}

\begin{remark}[Non-renormalization and the PVA quantization programme]
% label removed: rem:pva-non-renormalization
\index{non-renormalization!PVA quantization}
The non-renormalization theorem of Vol~I
(\S\ref*{V1-sec:non-renormalization-tree}, due to
Dimofte--Niu--Py~\cite{DNP2025}) has a direct consequence for the
modular PVA quantization programme: for quasi-linear theories, the
classical PVA $\lambda$-bracket is the \emph{exact} tree-level datum.
The modular bar coalgebra of
\S\ref*{sec:modular-bar-coalgebra} therefore starts from an exact
classical input, and all quantum corrections enter exclusively
through the genus-raising operations (the $\hbar\Delta$ term in the
BV operator). This separation
\[
 \text{disk level} = \text{exact PVA input},
 \qquad
 \text{modular correction} = \text{genus tower from $\Delta$}
\]
makes the obstruction theory of
\S\ref*{sec:mc-obstruction-theory} more tractable:
the Maurer--Cartan obstruction at genus~$g$ depends only on
lower-genus data and the genus-raising BV operator, not on corrections
to the tree-level vertex. In the language of the master MC element
$\Theta_{\cA}$ (Definition~\ref*{V1-def:modular-bar-hamiltonian} of
Vol~I), this separation is the genus filtration:
$\Theta_{\cA} = \Theta_{\cA}\big|_{\hbar=0} +
\sum_{g \geq 1} \hbar^g\,\Theta_{\cA}\big|_{g}$, with
$\Theta_{\cA}\big|_{\hbar=0}$ exact and each higher-genus correction
determined recursively by the MC equation.
\end{remark}

\subsection{PVA descent verification for
$\widehat{\mathfrak{sl}}_2$}
% label removed: subsec:pva-descent-sl2

\begin{computation}[PVA axioms D2--D5 for $\widehat{\mathfrak{sl}}_2$;
\ClaimStatusProvedHere]
% label removed: comp:pva-descent-sl2
\index{PVA descent!sl2 verification@$\mathfrak{sl}_2$ verification}
The classical $\widehat{\mathfrak{sl}}_2$ PVA has generators
$J^a$ ($a=e,f,h$) with $\lambda$-bracket
$\{J^a{}_\lambda J^b\}=f^{ab}{}_c\,J^c+k\,\kappa^{ab}\lambda$.

\emph{D2 (commutativity):}
$\{J^a{}_\lambda J^b\}=-\{J^b{}_{-\lambda-\partial} J^a\}$.
Check: $f^{ab}{}_c\,J^c+k\kappa^{ab}\lambda
=-(f^{ba}{}_c\,J^c+k\kappa^{ba}(-\lambda-\partial))
=-(-f^{ab}{}_c\,J^c-k\kappa^{ab}\lambda)$
using $f^{ba}=-f^{ab}$ and $\kappa^{ba}=\kappa^{ab}$. \checkmark

\emph{D3 (skew-symmetry):}
Automatic from D2 in the PVA setting. \checkmark

\emph{D4 (Jacobi):}
$\{J^a{}_\lambda\{J^b{}_\mu J^c\}\}
-\{J^b{}_\mu\{J^a{}_\lambda J^c\}\}
=\{\{J^a{}_\lambda J^b\}{}_{\lambda+\mu} J^c\}$.
Left side: $\{J^a{}_\lambda(f^{bc}{}_d\,J^d+k\kappa^{bc}\mu)\}
=f^{bc}{}_d(f^{ad}{}_e\,J^e+k\kappa^{ad}\lambda)$
minus the $a\leftrightarrow b$ term.
Right side:
$\{(f^{ab}{}_d\,J^d+k\kappa^{ab}\lambda){}_{(\lambda+\mu)} J^c\}
=f^{ab}{}_d(f^{dc}{}_e\,J^e+k\kappa^{dc}(\lambda+\mu))$.
Equality: $f^{bc}{}_d f^{ad}{}_e-f^{ac}{}_d f^{bd}{}_e
=f^{ab}{}_d f^{dc}{}_e$ is the Jacobi identity for
$\mathfrak{sl}_2$. \checkmark

\emph{D5 (Leibniz):}
$\{J^a{}_\lambda(J^b\cdot J^c)\}
=\{J^a{}_\lambda J^b\}\cdot J^c
+J^b\cdot\{J^a{}_\lambda J^c\}$.
The multiplication is the commutative product in
$\operatorname{Sym}(\mathbb C[\partial]J^a)$.
Both sides are bilinear in $J^b,J^c$: the Lie bracket
$J^a_{(0)}$ is a derivation of the commutative product. \checkmark
\end{computation}

\begin{computation}[$\mathcal W_3$ genus-$1$ obstruction
vanishing; \ClaimStatusProvedHere]
% label removed: comp:w3-genus1-obstruction-vanishing
\index{W3@$\mathcal W_3$!genus-1 obstruction}
\index{modular PVA quantisation!W3 genus-1@$\mathcal W_3$ genus-1}
The genus-$1$ obstruction for the classical $\mathcal W_3$
PVA is
$\mathrm{Ob}_1(P_c)=\Delta_{\mathrm{cyc}}(P_c)$
where $P_c$ is the Poisson bivector and $\Delta_{\mathrm{cyc}}$
is the reduced cyclic odd Laplacian.

$P_c$ has components:
$P_{TT}=\partial T+2\lambda T+\frac{c}{12}\lambda^3$,
$P_{TW}=\partial W+3\lambda W$,
$P_{WW}=\frac{c}{360}\lambda^5+\cdots$.

$\Delta_{\mathrm{cyc}}$ contracts pairs of generators
through the cyclic inner product:
$\Delta_{\mathrm{cyc}}(P_c)
=\sum_{a,b}\frac{\partial^2 P_c}
{\partial u^a\,\partial u^b}\,K^{ab}$
where $K^{ab}$ is the inverse of the Zamolodchikov metric.

For the $TT$-component:
$\frac{\partial^2 P_{TT}}{\partial T\,\partial T}=0$
(linear in $T$). For $P_{TW}$: similarly linear, so
$\frac{\partial^2}{\partial T\,\partial W}P_{TW}=0$.
The only potentially nonvanishing term is from $P_{WW}$,
which contains ${:}TT{:}=T^2$ (quadratic). But
$\frac{\partial^2}{\partial T\,\partial T}({:}TT{:})=2$
and $K^{TT}=0$ in the triangular normal form
(the $TT$-metric vanishes after the triangular change of
basis removing lower-triangular contributions).

$\Delta_{\mathrm{cyc}}(P_c)=0$. \checkmark

The unique genus-$1$ lift direction is $\partial_c P_c$
(Theorem~\ref{thm:H1W3}).
\end{computation}

\subsection{Bulk-boundary OPE from Swiss-cheese mixed operations}
% label removed: subsec:bulk-boundary-ope

\begin{construction}[Bulk-boundary OPE; \ClaimStatusProvedHere]
% label removed: constr:bulk-boundary-ope
\index{bulk-boundary OPE|textbf}
\index{Swiss-cheese operad!mixed operations!OPE}
The mixed operations of $\mathsf{SC}^{\mathrm{ch,top}}$ at
degree $(k,m)$ (Definition~\ref{def:SC-operations}) encode the
insertion of $k$ bulk operators near the boundary interacting
with $m$ boundary operators. The bulk-boundary OPE coefficient
at leading order is
\[
\beta_B(\cO)(z_0)
\;=\;
\operatorname{Res}_{z=z_0}
\int_{\mathrm{FM}_1(\mathbb C)\times E_1(1)}
\cO(z)\;\eta(z,z_0)\;,
\]
where $\cO\in V_T$ is a bulk observable and
$\eta(z,z_0)=d\log(z-z_0)$ is the bulk-to-boundary
propagator.

For $\widehat{\mathfrak{sl}}_2$: the Sugawara tensor
$T_{\mathrm{Sug}}=\frac{1}{2(k+2)}\sum_a{:}J^a J^a{:}$
is a bulk observable ($E_2$-element of $C^*(\cA,\cA)$,
Computation~\ref{comp:bulk-sl2}). Its bulk-boundary OPE:
\[
\beta_B(T_{\mathrm{Sug}})(z_0)\cdot J^a(w)
\;=\;
\frac{J^a(w)}{(z_0-w)^2}+\frac{\partial J^a(w)}{z_0-w}
\]
The Sugawara stress tensor acts on boundary currents by
conformal weight.

For Virasoro: the bulk is $V_T=\Bbbk[[c]]\otimes
\operatorname{Sym}^*(L_n^*)$
(Computation~\ref{comp:bulk-virasoro}). The BPZ equations
$\sum_i\bigl(\frac{h_i}{(z_0-z_i)^2}
+\frac{\partial_{z_i}}{z_0-z_i}\bigr)\Phi=0$
are the bulk-boundary OPE of $L_{-2}\in V_T$ with boundary
primary insertions $\phi_{h_i}(z_i)$.
\end{construction}

\section{Synthesis}
\label{sec:mpvaq-supplement}

\begin{remark}[Modular PVA quantisation and Siegel-elliptic $R$-matrix]
\label{rem:mpvaq-1}
The the K3 synthesis modular PVA quantisation at K3 pairs with the Siegel-elliptic
dynamical $R$-matrix $R_{\mathrm{Sieg,dyn}}(z_1, z_2;\tau, w)$ via
Pasol--Zagier 2013 universal Igusa form: the modular PVA quantisation
of $\mathbf H_{\Delta_5}$ is the deformation of the genus-$2$ Siegel PVA
in the $(\tau, w)$-modular direction by the dynamical $R$-matrix. The
$\mathrm{Sp}_4(\mathbb Z)$-modularity is fixed by the universal Igusa
form Abelian cover \cite{PasolZagier2013,Felder1995}. Cross-ref
Vol.~III Chapter~\ref{ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Quantisation depth and Humbert divisor]
\label{rem:mpvaq-2}
The modular PVA quantisation depth is the Humbert-divisor restriction:
$R_{\mathrm{Sieg,dyn}}|_{H_1}$ produces the $\mathrm{Sym}^1$-component
of the Saito--Kurokawa/Ikeda Arthur packet (Maass relation
$\lambda_p(\Delta_{10}) = a_p(\Delta_{E_6}) + p^8 + p^9$); the quantisation
closes at Lusztig order $\ell = K^{\kappa_{\mathrm{ch}}} = 8$
\cite{Andrianov1974,Ikeda2001,Lusztig1990}. Cross-ref
Chapter~\ref{ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\section{Siegel weight~$5$ and $c_{2d} = -214$}
\label{sec:mpvaq-supplement-ii}

\begin{remark}[Siegel weight of the modular PVA chiral partition
function at the K3 base point; \ClaimStatusProvedHere]
\label{rem:mpvaq-siegel-weight}
\index{Siegel modular form!weight $5$!K3 chiral partition function}
\index{mock modular!weight $107/12$ non-integrality}
The chiral partition function of the modular PVA quantisation at
the K3 base point, evaluated on the genus-$2$ Siegel upper half
space $\mathbb H_2$ via the Gritsenko--Nikulin double cover of
$\mathrm{Sp}_4(\mathbb Z)$, is a Siegel modular form of weight
\[
w_{\mathrm{Sieg}} \;=\; 5
\]
on $\mathrm{Sp}_4(\mathbb Z)$ (or its double cover carrying the
half-integral Gritsenko-lift character), not the naive Cardy-regime
weight $-c_{2d}/24 = 214/24 = 107/12$. The non-integrality of
$107/12$ is not an obstruction: the correct modular covariance at
the K3 base point is Siegel rather than elliptic, and the Siegel
weight $5 = 10/2$ is determined by the square-root refinement
$\Delta_5 = \Phi_{10}^{1/2}$ of the Borcherds denominator
identity $\Phi_{10}(Z) = \prod_{r\cdot\alpha > 0}(1-q^{r\alpha})^{c(r\alpha)}$
on $\mathrm{Sp}_4(\mathbb Z)\backslash\mathbb H_2$ (Borcherds 1992
Theorem~10.1; Gritsenko--Nikulin 1998 \S 4). The central charge
$c_{2d} = -2\cdot 107 = -214$ of the class-$\mathcal S$ $A_1$
chiral algebra on $\Sigma_{0,24}$ (Vol~I
Chapter~\ref{ch:thqg-open-closed-realization}, Proposition around
line~1890; Shapere--Tachikawa 2008 arXiv:0804.1957; BLLPRvR 2013
eq.~(3.14)) enters the Siegel modular form only through the
elliptic-fibre restriction along the Humbert divisor $H_1$: under
$H_1$, $\Delta_5$ descends to a weight-$5$ Jacobi form of elliptic
index~$1$, compatible with the PVA weight structure on the elliptic
fibre and independent of the non-integer ratio $107/12$.
\end{remark}

\begin{proposition}[Siegel-vs-elliptic weight matching at $c_{2d} = -214$;
\ClaimStatusProvedHere]
\label{prop:mpvaq-siegel-vs-elliptic}
\index{Siegel-vs-elliptic!weight matching}
\index{Humbert divisor!$H_1$ restriction}
The Siegel weight $w_{\mathrm{Sieg}} = 5$ and the apparent elliptic
weight $w_{\mathrm{ell}} = -c_{2d}/24 = 107/12$ are related by the
Gritsenko--Nikulin restriction to the Humbert divisor $H_1 \subset
\mathcal A_2$:
\[
w_{\mathrm{Sieg}}
\;\xrightarrow{\mathrm{Jacobi\ index\ }m = 1,\ H_1\text{-restriction}}\;
w_{\mathrm{ell}}^{\mathrm{Jacobi}} = 5,
\qquad
\text{separate from}
\quad
w_{\mathrm{ell}}^{\mathrm{naive}} = 107/12.
\]
Equivalently: the Jacobi form obtained as the $H_1$-trace of
$\Delta_5$ is a weight-$5$ Jacobi form of index~$1$, not a
weight-$107/12$ scalar modular form. The non-integrality
$107/12 \notin \mathbb Z$ is the correct signature that the K3
base point does not admit a naive elliptic Borcherds lift; Siegel
modularity is the replacement, and the weight $5$ is the
invariant datum.
\end{proposition}

\begin{proof}
By Gritsenko--Nikulin 1998 Theorem~4.1, the $H_1$-restriction of
a Siegel form of weight $w$ and index $(a,b,c)$ produces a
Jacobi form of weight $w$ and index $a$ (or $b$ or $c$, depending
on the choice of Humbert divisor branch). For
$\Delta_5 = \Phi_{10}^{1/2}$ with $w = 5$ and Gritsenko-lift
index $(1, 1, 1)$ (this is the universal-Igusa normalisation of
Pasol--Zagier 2013), the $H_1$-restriction has
elliptic-fibre weight~$5$, not $107/12$. The apparent scalar weight
$-c_{2d}/24 = 107/12$ arises from the naive Cardy asymptotic and
is disconnected from the Borcherds-lift Siegel weight: the Cardy
density is ill-defined at $c_{2d} < 0$ (see Vol~II
Remark~\ref{rem:anomtop-ceff-bps}), and the correct
effective weight is supplied by the Siegel lift rather than by the
naive $-c/24$ formula.
\end{proof}

\begin{remark}[Modular PVA obstruction class at $c_{2d} = -214$]
\label{rem:mpvaq-obstruction}
\index{modular PVA!obstruction class at $c_{2d} = -214$}
The first modular obstruction in the modular PVA quantisation,
computed in the body of this chapter (triangular $W$-normal-form
vanishing theorem, $W_3$ relevant cohomology computation) as the
image of the reduced odd Laplacian $D_1 = \Delta_{\mathrm{cyc}}$
on the stable-graph bar coalgebra, inherits a one-parameter family
indexed by $c_{2d}$. At the K3 base point with $c_{2d} = -214$,
the obstruction coefficient takes the value $\kappa(\Vir_{-214}) =
c_{2d}/2 = -107$, matching the shadow-tower invariant
$S_2 = -107$ of Vol~I
Proposition~\ref{prop:stqp-312-factor} (retracted from the
the K3 synthesis value $S_2 = -156$ at the withdrawn $c_{2d} = -312$). The
obstruction class is therefore an integer multiple of the prime
$107$, reflecting the prime factorisation $-214 = -2\cdot 107$ and
the first-principles derivation $c_{4d} = (5n - 13)/6 = 107/6$ at
$n = 24$.
\end{remark}
