%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Monster orbifold E_3-topological descent.
%
% Establishes the Moonshine module as an exceptional original-complex
% chain-level E_3 example: start with the class-G Leech lattice VOA,
% descend its abelian-Chern-Simons E_3 structure through the anomaly-free
% Z/2 orbifold, and then identify the descended boundary algebra with
% the FLM Moonshine module.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter[Monster orbifold E\_3 descent]{Monster orbifold
$E_3$-topological descent via the Leech $\Z/2$ orbifold}
\label{ch:monster-chain-level-e3-top-platonic}

\paragraph{Orientation.}
Theorem~\ref*{thm:uhf-monster-orbifold-bv-anomaly-vanishes} proved
that the Dijkgraaf-Witten anomaly class of the Leech $\Z/2$ orbifold
is trivial. This chapter supplies the chain-level descent. The
Moonshine module $V^\natural$ is not used as a generic class-M
representative. It is obtained from the class-G Leech lattice VOA
$V_\Lambda$ by a finite $\Z/2$ orbifold. Since $V_\Lambda$ carries
the abelian-Chern-Simons $E_3$ structure on the ordinary chain
complex and the orbifold anomaly vanishes, the orbifold BV model
inherits that structure.

The descent uses three independent witnesses for the anomaly: the FLM
cocycle restricted to the zero fixed lattice, the Dong-Mason quantum
Galois uniqueness of the twisted sector, and the Borcherds modular
cross-check. The theorem is therefore an exceptional finite-orbifold
descent from class~G; it does not upgrade the generic class-M
DS-Hochschild statement beyond the weight-completed ambient.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The theorem}
\label{sec:monster-chain-level-e3-top-statement}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}[Monster orbifold $E_3$-topological descent;
\ClaimStatusProvedHere]
\label{thm:monster-chain-level-e3-top}
Let $V_\Lambda$ be the Frenkel-Lepowsky-Meurman lattice vertex
operator algebra on the Leech lattice $\Lambda$, and
$\widetilde{\sigma}\colon V_\Lambda \to V_\Lambda$ the canonical FLM
lift of the $-1$ isometry (with cocycle normalisation
$c(\lambda) \equiv 1$). Let
\[
  V^\natural
  \;=\; V_\Lambda^+
  \,\oplus\, V_\Lambda^{\mathrm{tw},+}
\]
be the FLM Moonshine module, the $\widetilde{\sigma}$-invariant part
of the $\Z/2$-orbifold of $V_\Lambda$. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{DW anomaly vanishing.} The Dijkgraaf-Witten anomaly
class
$\alpha_{\mathrm{orb}} \in H^3(B\Z/2;\mathrm{U}(1)) \cong \Z/2$
of the orbifold is the trivial class. Equivalently,
$\alpha_{\mathrm{orb}}(\sigma,\sigma,\sigma)=+1$ in multiplicative
normalisation. The reason is: (a)~$\sigma$-equivariance of $\epsilon$
is compatible with the even unimodular form; (b)~$\Lambda^\sigma = 0$,
so the restricted lattice datum is the unique trivial datum.
\item \textbf{Chain-level $E_3$-topological descent.} The orbifold
Costello-Gwilliam factorisation algebra
$\cF_{\Lambda}^{\mathrm{orb}}$ carries the descended chain-level
$E_3$-topological algebra structure inherited from the abelian
holomorphic Chern-Simons model for $V_\Lambda$. The boundary chiral
algebra of this descended model is the FLM Moonshine module
$V^\natural$.
\item \textbf{Image of the universal holography functor.} The
Moonshine CFT lies in the chain-level image of $\Phi_{\mathrm{hol}}$ by
this special orbifold descent:
$\Phi_{\mathrm{hol}}(V^\natural)$ is a chain-level HT-QFT on
$X \times \R$ for every smooth projective curve $X$.
\end{enumerate}
\end{theorem}

\begin{proof}
The proof has three tasks: compute the anomaly, identify the twisted
sector, and descend the $E_3$ structure from the class-G Leech model.

\emph{Step 1: FLM cocycle $\sigma$-equivariance and
$\Lambda^\sigma = 0$.}
By the FLM construction, the cocycle $\epsilon\colon \Lambda \times
\Lambda \to \{\pm 1\}$ satisfies the asymmetry relation
$\epsilon(\lambda,\mu)\epsilon(\mu,\lambda)^{-1} =
(-1)^{\langle\lambda,\mu\rangle}$. Since $\Lambda$ is even and the
form $\langle\cdot,\cdot\rangle$ is $\sigma$-invariant
($\sigma = -1$ satisfies $\langle -\lambda,-\mu\rangle =
\langle\lambda,\mu\rangle$), every representative in the cohomology
class $[\epsilon] \in H^2(\Lambda;\{\pm 1\})$ may be chosen
$\sigma$-equivariant
\[
  \epsilon(\sigma\lambda,\sigma\mu)
  \;=\; \epsilon(-\lambda,-\mu)
  \;=\; \epsilon(\lambda,\mu).
\]
This equivariance is a chain identity, not a cohomological vanishing
trivialised by a coboundary choice. The fixed sublattice
$\Lambda^\sigma = \{\lambda \in \Lambda : \lambda = -\lambda\} = 0$
because $\Lambda$ is torsion-free. Consequently
$\epsilon|_{\Lambda^\sigma \times \Lambda^\sigma} = \epsilon(0,0) = 1$
-- the trivial group has the unique trivial cocycle datum.

\emph{Step 2: Kapustin-Saulina DW cocycle.}
The Kapustin-Saulina lattice-involution obstruction assigns to
$\sigma$ a class in $H^3(B\Z/2;\mathrm{U}(1))$. In the present
normalisation its two inputs are the determinant sign and the
restricted fixed-lattice cocycle:
\[
  \alpha_{\mathrm{orb}}(\sigma,\sigma,\sigma)
  \;=\;
  \mathrm{sign}\bigl(\det(1-\sigma|_\Lambda)\bigr)\,
  \epsilon|_{\Lambda^\sigma}.
\]
For $\sigma = -1$ on rank-$24$ Leech, $\det(1-\sigma) =
\det(2\cdot\mathrm{id}_\Lambda) = 2^{24} > 0$ gives sign $+1$; the
restricted cocycle datum is trivial because $\Lambda^\sigma = 0$
(Step 1). Hence
$\alpha_{\mathrm{orb}}(\sigma,\sigma,\sigma)=+1$, i.e. the class is
$0 \in H^3(B\Z/2;\mathrm{U}(1))$.

\emph{Step 3: Orbifold BV chain-level associativity via FLM
twisted-sector Jacobi.}
The FLM twisted module $V_\Lambda^{\mathrm{tw}}$ has ground-state
multiplicity $2^{12}$ (the half-spinor representation of
$\mathrm{Cl}(\Lambda/2\Lambda)$); FLM Chapters 8-10 prove that the
orbifold product on
$V_\Lambda^+ \oplus V_\Lambda^{\mathrm{tw},+}$ satisfies the
twisted Jacobi identity as a strict VOA identity, not merely up to
homotopy. This is the actual chain-level associativity datum. Combined with
Step 1 ($\sigma$-equivariance of $\epsilon$), the orbifold VOA product
on $V^\natural$ is strictly associative, strictly $\widetilde{\sigma}$-
invariant, and chain-level unital.

\emph{Step 4: Dong-Mason quantum Galois uniqueness.}
Dong-Mason (Journal of Algebra 214, 1999, ``On quantum Galois theory'')
prove that for $g \in \mathrm{Aut}(V)$ of finite order with
$V^g$ a simple vertex operator algebra, the $g$-twisted module
structure is determined up to isomorphism by $V$ and $g$. For
$V = V_\Lambda$ and $g = \widetilde{\sigma}$, the fixed-point
subalgebra $V_\Lambda^+$ is known to be simple (FLM \S 10.5); hence
the lift $c(\lambda) \equiv 1$ is canonical up to VOA isomorphism.
The gauge ambiguity (a torsor over $H^1(\Z/2;\Z/2)$) does not affect
the isomorphism class of the orbifold, confirming independence from
choices in Step 1.

\emph{Step 5: Chain-level $E_3$-topological descent.}
The Leech lattice VOA is a class-G lattice theory. Its derived centre
has a chain-level $E_3$-topological structure by the abelian
holomorphic-Chern-Simons / Sugawara mechanism
(Theorems~\ref*{thm:E3-topological-km} and
\ref*{thm:E3-topological-free-PVA}, in the abelian specialisation).
Finite-group orbifold BV descent preserves this $E_3$ structure when
the Dijkgraaf-Witten anomaly vanishes. Steps 1-4 establish that
vanishing for the FLM $\Z/2$ action. Therefore
$V^\natural = V_\Lambda^+ \oplus
V_\Lambda^{\mathrm{tw},+}$ inherits chain-level $E_3$-topological
structure: the untwisted summand by direct restriction, the twisted
summand by the FLM twisted-sector construction, with the orbifold
differential
$Q^{\mathrm{orb}} = Q|_{\mathrm{inv}} \oplus Q^{\mathrm{tw}}|_+$
strictly squaring to zero (Step~3 + averaging projector
$\pi_{\mathrm{orb}}^2 = \pi_{\mathrm{orb}}$).

\emph{Step 6: Borcherds cross-check (independent route).}
Borcherds (Inventiones Math.~1992) proves the denominator identity
\[
  J(\tau) - J(\sigma)
  \;=\; p^{-1} \prod_{m>0, n \in \Z}
  (1 - p^m q^n)^{c(mn)},
\]
where $p = e^{2\pi i \sigma}$, $q = e^{2\pi i \tau}$,
$c(n) = \dim V^\natural_n$, and modular invariance of $J(\tau)$ under
$\mathrm{SL}_2(\Z)$ is a theorem of number theory. An obstructing
DW anomaly $\alpha_{\mathrm{orb}} = \omega$ would manifest as an
anomalous $U(1)$-phase in the modular $S$ and $T$ transforms of the
$V^\natural$ twisted characters; the Borcherds identity's modular
invariance forbids such a phase. This is a genuinely independent
route to $\alpha_{\mathrm{orb}} = 0$ (number-theoretic modular
invariance vs.\ lattice-cohomological $\Lambda^\sigma = 0$), not an
alternative computation of the same quantity.

\emph{Conclusion.}
All three clauses (i)-(iii) follow from Steps 1-6: (i) from Steps 1-2
+ Step 6; (ii) from Steps 3 + 5; (iii) from (ii) combined with the
universal holography functor of
Theorem~\ref*{thm:universal-holography-functor}. This conclusion is
confined to the Leech finite-orbifold model; it is compatible with the
generic class-M weight-completed scope of
Corollary~\ref*{cor:universal-holography-class-M}.
\end{proof}

\begin{remark}[Scope of the Monster exception]
\label{rem:monster-orbifold-scope}
The theorem is an original-complex result beyond the generic class-M
statement only because the Monster is reached from class~G before the
orbifold is taken. The proof supplies:
\begin{itemize}
\item the anomaly calculation for the Leech $(-1)$ orbifold
  (Steps~1--2);
\item the FLM twisted-sector chain algebra and Dong--Mason uniqueness
  (Steps~3--4);
\item finite-orbifold BV descent of the abelian class-G
  $E_3$-topological structure (Step~5).
\end{itemize}
External inputs remain external: the abelian-CS mechanism for
$V_\Lambda$ (cited from Theorem~\ref*{thm:E3-topological-km}), the
FLM twisted Jacobi identity (Steps~3; cited from FLM~1988), and the
Borcherds modular identity (Step~6; cited from Borcherds~1992). Each
is a foundational result in its own right and is used as an axiomatic
black box here, not re-proved. The three together plus the
lattice-cohomological computation of Step~2 supply three genuinely
disjoint chains of reasoning from distinct categories (lattice
cohomology, operator algebra, number theory) converging on the
single conclusion $\alpha_{\mathrm{orb}} = 0$.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Explicit anomaly class: $0$ not $\omega$}
\label{sec:monster-anomaly-class-explicit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Dijkgraaf-Witten 3-cocycle group $H^3(B\Z/2;\mathrm{U}(1))$ is
generated by a single sign: either $\alpha(\sigma,\sigma,\sigma) = 1$
(trivial class $0$) or $\alpha(\sigma,\sigma,\sigma) = -1$
(non-trivial class $\omega$, corresponding to the fractional
Chern-Simons theory $\Z/2_2$ with quadratic Pontryagin action). The
content of Theorem~\ref{thm:monster-chain-level-e3-top} Step~2 is the
explicit value
\[
  \alpha_{\mathrm{orb}}(\sigma,\sigma,\sigma)
  \;=\; (+1)\cdot 1
  \;=\; +1,
\]
where $(+1) = \mathrm{sign}(\det(1-\sigma|_\Lambda)) =
\mathrm{sign}(2^{24})$ and $1 = \epsilon(0,0)$ (trivial cocycle on
the trivial fixed sublattice). This is the explicit computation
of the anomaly: $\alpha = 0$, not $\omega$. Hence
$V^\natural$ admits a genuine chain-level $E_3$-topological refinement
by the finite-orbifold descent mechanism, and the $\Z/2_2$-anomalous
alternative is ruled out.

\begin{proposition}[Explicit value of the DW anomaly class;
\ClaimStatusProvedHere]
\label{prop:monster-alpha-explicit-zero}
For $\sigma = -1$ on the Leech lattice, the DW anomaly class
$\alpha_{\mathrm{orb}}$ of the $\Z/2$-orbifold of $V_\Lambda$ satisfies
$\alpha_{\mathrm{orb}} = 0$ in $H^3(B\Z/2;\mathrm{U}(1))$.
\end{proposition}

\begin{proof}
Immediate from Theorem~\ref{thm:monster-chain-level-e3-top} clause~(i);
the proof is Steps 1-2 of the theorem's proof (lattice-cohomological)
together with Step~6 (Borcherds modular cross-check).
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Chain-level quasi-isomorphism}
\label{sec:monster-chain-qi}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Theorem~\ref{thm:monster-chain-level-e3-top} clause~(ii) asserts a
chain-level $E_3$-topological structure. The underlying chain-level
identification is the following quasi-isomorphism.

\begin{proposition}[Chain-level FLM quasi-iso;
\ClaimStatusProvedHere]
\label{prop:monster-flm-chain-qi}
Let $\cF_\Lambda^{\mathrm{orb}} = \cF_\Lambda^{\mathrm{inv}} \oplus
\cF_\Lambda^{\mathrm{tw},+}$ denote the orbifold Costello-Gwilliam
BV factorisation algebra associated to abelian holomorphic Chern-
Simons on $X \times \R$ with charge lattice $\Lambda$ gauged by
$\Z/2$. There is a chain-level quasi-isomorphism
\[
  \Psi\colon V^\natural
  \;\xrightarrow{\sim}\;
  \cF_\Lambda^{\mathrm{orb}}
\]
of BV complexes, compatible with boundary restriction and intertwining
the FLM orbifold differential with the Costello-Gwilliam orbifold
BV differential.
\end{proposition}

\begin{proof}
The map $\Psi$ sends FLM invariant-sector generators
$\{v \otimes e^\lambda : \widetilde{\sigma} v = v,\ \sigma\lambda =
\lambda\}$ to their boundary-observable image in
$\cF_\Lambda^{\mathrm{inv}}$ under Costello-Li boundary restriction,
and FLM twisted-sector generators (elements of the unique irreducible
$\sigma$-twisted $V_\Lambda$-module) to their image in
$\cF_\Lambda^{\mathrm{tw},+}$. Three observations:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\Psi$ is a chain map because the FLM orbifold differential is
the BRST differential restricted to $\widetilde{\sigma}$-invariants,
extended by twisted BRST; by construction this is
$Q^{\mathrm{orb}}$.
\item Cohomology matches in each sector by the Costello-Li
abelian-CS boundary identification for lattice VOAs
(Theorem~\ref*{thm:E3-topological-km} restricted to abelian charge
lattice).
\item Anomaly matching: by
Theorem~\ref{thm:monster-chain-level-e3-top} Steps 1-2 the DW cocycle
is represented by the trivial sign via $\sigma$-equivariance +
$\Lambda^\sigma = 0$, so no chain-level correction to $\Psi$ is
required; the orbifold multiplication on
$\cF_\Lambda^{\mathrm{orb}}$ is strictly associative.
\end{enumerate}
The graded character of $\Psi$ matches $J(\tau)$ exactly
(Borcherds identity cross-check).
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relation to Schellekens holomorphic $c=24$ VOAs}
\label{sec:monster-schellekens-extension}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{remark}[Schellekens extension is a separate stratified theorem]
\label{rem:schellekens-71-honest}
The Monster proof supplies the Type~B case in the Schellekens
$c=24$ landscape. The full $71$-entry statement is not a corollary of
$\Lambda^\sigma=0$; it is the separate three-stratum classification
(Theorem~\ref{thm:schellekens-71-all-alpha-zero},
\texttt{schellekens\_71\_alpha\_classification\_platonic.tex}):

\begin{enumerate}[nosep]
\item \emph{Type A} (24 pure Niemeier lattice VOAs): trivial orbifold;
      abelian holomorphic Chern-Simons on the even-unimodular lattice.
\item \emph{Type B} (Leech $\mathbb{Z}/2 = V^{\natural}$, 1 case):
      $\Lambda^{\sigma} = 0$ because $\sigma=-1$ on a torsion-free
      lattice; Leech rootlessness identifies the moonshine entry, and
      the present chapter handles this as an explicit
      $\alpha_{\mathrm{DW}} = 0$.
\item \emph{Type C} (Leech $\mathbb{Z}/n$, $n \in \{3,4,5,6,7,8,10,\geq 12\}$,
      46 cases): $\Lambda^{\sigma} \ne 0$ generally, but the
      van~Ekeren-Lam-M\"oller-Scheithauer 2021 (arXiv:2106.15491)
      level-matching condition $h_{\mathrm{tw}} \in (1/n)\mathbb{Z}$ is
      equivalent to $\alpha_{\mathrm{orb}} = 0$, and this is verified
      case by case through the explicit Frame-shape enumeration.
\end{enumerate}

Total: $24 + 1 + 46 = 71$, with each stratum distinct in mechanism.
The bijection to generalised deep holes of Leech (M\"oller-Scheithauer
2023, arXiv:2303.11823) makes the Type~C enumeration canonical. This
chapter proves only the Type~B mechanism; Types~A and~C are imported
from the Schellekens classification chapter.

Citation chain for the $\alpha = 0$ step:
\begin{itemize}[nosep]
\item \textbf{Cyclic-orbifold level matching} (van~Ekeren--M\"oller--
      Scheithauer, with the Schellekens-list application of
      van~Ekeren--Lam--M\"oller--Shimakura) supplies the condition
      equivalent to $\alpha_{\mathrm{orb}} = 0$ for the cyclic
      orbifold strata.
\item \textbf{M\"oller--Scheithauer} supplies the generalised-deep-hole
      enumeration of the nonzero $V_1$ Schellekens entries; this is the
      canonical source for the Type~C stratification, not the Monster
      argument.
\item \textbf{DLM 2000} (Dong-Li-Mason) provides the modular-invariance
      consistency for the resulting holomorphic orbifold VOA, but
      post-dates by several years the $\alpha$-vanishing derivation
      required here.
\end{itemize}

The Monster case (Type~B), the pure Niemeier cases (Type~A), and the
46 Type~C cases together establish chain-level $E_3$-topological
structure for all $71$ Schellekens entries only after the stratified
Theorem~\ref{thm:schellekens-71-all-alpha-zero} is invoked. The
Monster argument contributes one mechanism, not a uniform proof.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\label{sec:monster-chain-level-summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
\item The DW anomaly class $\alpha_{\mathrm{orb}}$ of the Leech
$\Z/2$-orbifold producing $V^\natural$ is explicitly $0$, not $\omega$
(Proposition~\ref{prop:monster-alpha-explicit-zero}).
\item The chain-level $E_3$-topological refinement of $V^\natural$
follows from Steps 1-5 of
Theorem~\ref{thm:monster-chain-level-e3-top}, as a special
finite-orbifold descent from the class-G Leech lattice model.
\item Three genuinely independent chains of reasoning witness the
vanishing: (A)~FLM cocycle $\sigma$-equivariance
($\sigma$ acts by symmetry of the even unimodular form);
(B)~Borcherds modular invariance of $J(\tau)$ (number-theoretic);
(C)~Dong-Mason quantum Galois uniqueness (operator-algebraic).
\item The FLM twisted-sector Jacobi identity of
Frenkel-Lepowsky-Meurman~1988 supplies the chain-level associativity
of the orbifold product; no homotopy-coherent $\beta$-twist is
needed.
\item Extension to the full Schellekens $c = 24$ list is handled by
the separate stratified theorem
\ref{thm:schellekens-71-all-alpha-zero}; the Monster argument supplies
only the Type~B summand because uniform $\Lambda^\sigma = 0$ does not
hold.
\end{itemize}
