% Ordered Associative Chiral Koszul Duality
% Integration-ready chapter file (stripped from standalone amsart draft).
% Uses only \providecommand for macros that may not be in main.tex preamble.

\providecommand{\Assch}{\mathrm{Ass}^{\mathrm{ch}}}
\providecommand{\Barch}{\overline{B}^{\mathrm{ch}}}
\providecommand{\Cobar}{\Omega^{\mathrm{ch}}}
\providecommand{\coHoch}{\operatorname{coHH}}
\providecommand{\Cotor}{\operatorname{Cotor}}
\providecommand{\Coext}{\operatorname{Coext}}
\providecommand{\RHom}{R\!\operatorname{Hom}}
\providecommand{\Tot}{\operatorname{Tot}}
\providecommand{\KK}{\mathbb{K}}
\providecommand{\Dpbw}{D^{\mathrm{pbw}}}
\providecommand{\Dco}{D^{\mathrm{co}}}
\providecommand{\chotimes}{\mathbin{\otimes^{\mathrm{ch}}}}
\providecommand{\wt}{\widetilde}
\providecommand{\eps}{\varepsilon}
\providecommand{\susp}{s}
\providecommand{\coeq}{\operatorname{coeq}}
\providecommand{\id}{\mathrm{id}}
\providecommand{\op}{\mathrm{op}}
\providecommand{\cop}{\mathrm{cop}}
\providecommand{\HH}{\operatorname{HH}}
\providecommand{\Tor}{\operatorname{Tor}}
\providecommand{\Ext}{\operatorname{Ext}}
\providecommand{\gr}{\operatorname{gr}}
\providecommand{\MC}{\operatorname{MC}}
\providecommand{\Ob}{\operatorname{Ob}}
\providecommand{\eq}{\operatorname{eq}}
\providecommand{\cF}{\mathcal{F}}
\providecommand{\cL}{\mathcal{L}}
\providecommand{\cA}{\mathcal{A}}

\chapter{Ordered Associative Chiral Koszul Duality}
% label removed: ch:ordered-associative-chiral-kd

\section{Introduction: the diagonal as the universal boundary}

The commutative shadow of chiral Koszul duality is by now classical. The genuinely associative
story is different. It is not the Francis--Gaitsgory equivalence between chiral Lie algebras and
cocommutative factorization coalgebras. It is a theory in which ordered configuration spaces
survive, shuffles do not collapse under symmetric-group quotients, and after linear duality
chiral algebras appear again on the far side.

The purpose of this note is to make the associative picture rigid enough to be useful. We do this
by returning to first principles and asking a single question.

\medskip

\emph{What is the correct coalgebra-side avatar of the diagonal bimodule ${}_A A_A$?}

\medskip

The answer is simple and structural:
if $C=\Barch(A)$ is the ordered bar coalgebra of an associative chiral algebra $A$, then the
correct boundary object is not an ad hoc kernel but the \emph{diagonal bicomodule}
\[
C_\Delta,
\]
namely the coalgebra $C$ equipped with its coproduct on the left and on the right. Once this is
recognized, the rest of the machine begins to lock into place.

On the algebra side, interval composition is derived tensor over $A$ and the annulus is Hochschild
homology. On the coalgebra side, interval composition becomes derived cotensor over $C$, the
diagonal becomes the composition unit, and the annulus becomes the derived cotrace of the diagonal
against itself:
\[
\HH^{\mathrm{ch}}_\bullet(A)\simeq C_\Delta \square_{C^e}^{\mathbf R} C_\Delta.
\]
The annulus is the self-cotensor of the universal boundary condition.

This note is organized as follows. In \S\ref{sec:setup} we isolate the exact regime in which the
homological algebra is clean and state the repository inputs used below. In \S\ref{sec:shuffle} we
prove the ordered chiral shuffle theorem. In \S\ref{sec:opposite} we prove opposite-duality and
enveloping duality. In \S\ref{sec:tangent} we construct the two-sided twisted bicomodule and prove
that it is exactly the one-defect ordered bar complex of a square-zero extension. In
\S\ref{sec:bimod-bicomod} we obtain the PBW-complete equivalence between bimodules and bicomodules
and prove that ${}_A A_A$ goes to $C_\Delta$. In \S\ref{sec:HH-coHH} we identify associative chiral
Hochschild homology and cohomology with coalgebraic coHochschild theory. In
\S\ref{sec:open-trace} we extract the ordered genus-zero open trace formalism and its Calabi--Yau
refinement. Finally, in \S\ref{sec:conjectures} we formulate the next frontier as a precise list of
conjectures.

\subsection*{Dictionary}
The new results of this note can be summarized by the following dictionary:
\[
A \longleftrightarrow C_\Delta,\qquad
A^e \longleftrightarrow C^e:=C\widehat\otimes C^{\cop},\qquad
-\otimes_A^{\mathbf L}- \longleftrightarrow -\square_C^{\mathbf R}-,
\]
\[
\HH^{\mathrm{ch}}_\bullet(A,M)
\longleftrightarrow
\coHoch^{\mathrm{ch}}_\bullet(C,\KK_A^{\mathrm{bi}}(M)),
\qquad
\HH_{\mathrm{ch}}^\bullet(A,M)
\longleftrightarrow
\coHoch_{\mathrm{ch}}^\bullet(C,\KK_A^{\mathrm{bi}}(M)).
\]
The slogan is: \emph{the associative dual does not merely mirror the algebra; it already remembers
the open boundary formalism.}

\subsection*{Ledger of status}
To keep the exposition honest, we separate three classes of statements.

\begin{enumerate}[label=(\roman*)]
\item \textbf{Repository inputs.}
The existence of the associative chiral bar--cobar equivalence, the one-sided module/comodule
Koszul duality, and the enveloping algebra formalism are taken as already established in the
repository.

\item \textbf{New theorems proved here.}
The ordered chiral shuffle theorem, opposite-duality, enveloping duality, the two-sided twisted
bicomodule, the identification of the tangent bar complex with the twisted bicomodule, the PBW-complete
bimodule/bicomodule equivalence, the diagonal correspondence, the Hochschild--coHochschild
dictionary, the ordered open trace formalism, the $R$-matrix as
ordered-to-unordered descent datum with the covering-space frame and descent identification,
the Yang--Baxter equation from $d^2=0$ via boundary-face analysis, the classical
Yang--Baxter equation as linearisation, and the affine ordered-bar
realization of the dg-shifted Yangian with Drinfeld generators and
RTT presentation.

\item \textbf{Frontier and resolved conjectures.}
The Francis--Gaitsgory commutator-shadow spectral sequence (now proved,
Theorem~\ref{thm:FG-shadow-core}), the associative modular Maurer--Cartan
class (proved), and the bordered configuration-space realization (conjectural).
\end{enumerate}

\section{The strongly admissible regime and the foundational inputs}
% label removed: sec:setup

We work over a field $k$ of characteristic $0$. Let $X$ be a smooth curve over $k$, and let
$\mathcal D(X)$ denote the relevant derived category of $D$-modules on $X$ (or on the Ran space of
$X$) endowed with the chiral tensor product
\[
\chotimes := \boxtimes_{D_X}.
\]
An $E_1$-chiral algebra means an algebra over the non-$\Sigma$ operad $\Assch$.

\begin{definition}[Strongly admissible associative chiral algebra]
An augmented $E_1$-chiral algebra $A$ on $X$ is called \emph{strongly admissible} if the following
hold.
\begin{enumerate}[label=(\alph*)]
\item $A$ is pro-nilpotent and equipped with an exhaustive separated descending PBW-type filtration
$F^\bullet A$ which is complete for the induced topology.

\item Every associated graded piece and every finite filtration quotient is bounded below and perfect
enough that completed tensor products, totalizations, and normalized chains behave exact\-ly on these
pieces.

\item The reduced ordered bar coalgebra
\[
C:=\Barch(A)
\]
is conilpotent, and the corresponding coderived category of bicomodules admits enough coflat
resolutions so that derived cotensor products are defined and associative.

\item Whenever linear duality is invoked, each graded/conformal piece of the object under consideration
is finite-dimensional.
\end{enumerate}
\end{definition}

\begin{remark}
This is the fortified regime in which hidden homological-algebra issues are kept on the surface.
The arguments below require no more than these hypotheses; they are chosen so that
every totalization, completion, normalization, and passage to coderived categories is legitimate.
\end{remark}

\begin{hypothesis}[Repository inputs]
% label removed: hyp:inputs
We assume the repository has already established the following.
\begin{enumerate}[label=(I)]
\item \textbf{Associative chiral bar--cobar.}
For every augmented pro-nilpotent strongly admissible $E_1$-chiral algebra $A$ there is a
quasi-isomorphism
\[
\Cobar \Barch(A)\xrightarrow{\sim} A,
\]
and, on the appropriate coalgebra side, the corresponding bar--cobar adjunction is an equivalence.

\item \textbf{One-sided module/comodule duality.}
For every such $A$ there is an equivalence between complete left $A$-modules and conilpotent left
$\Barch(A)$-comodules, with the usual coderived/contraderived refinement in the curved or completed
regime.

\item \textbf{Enveloping algebra formalism.}
The chiral enveloping algebra
\[
A^e := A\chotimes A^{\op}
\]
is defined, and $A$-bimodules are equivalently left $A^e$-modules.
\end{enumerate}
\end{hypothesis}

\begin{definition}[Universal twisting cochain]
Let $A$ be strongly admissible and set $C:=\Barch(A)$. The bar--cobar equivalence produces a
canonical twisting cochain
\[
\tau:C\to A
\]
characterized by the Maurer--Cartan equation
\[
d\tau+\tau\star\tau=0.
\]
We call $\tau$ the \emph{universal twisting cochain}.
\end{definition}

\begin{definition}[Opposite and diagonal objects]
Let $A$ be an associative chiral algebra and let $C$ be a coaugmented dg coalgebra.
\begin{enumerate}[label=(\alph*)]
\item $A^{\op}$ is the same underlying object with multiplication reversed.
\item $C^{\cop}$ is the same underlying object with coproduct flipped.
\item The \emph{coalgebraic enveloping object} is
\[
C^e:=C\widehat\otimes C^{\cop}.
\]
\item The \emph{diagonal bicomodule} $C_\Delta$ is $C$ equipped with left and right coactions both
equal to $\Delta_C$.
\end{enumerate}
\end{definition}

\begin{lemma}[Bicomodules as comodules over the enveloping coalgebra; \ClaimStatusProvedHere]
% label removed: lem:bicom-e
Let $C$ be a coaugmented conilpotent dg coalgebra. Then left $C^e$-comodules are canonically the
same thing as $C$-bicomodules.
\end{lemma}

\begin{proof}
Given a left $C^e$-coaction
\[
\rho^e:M\to C\otimes C^{\cop}\otimes M,
\]
compose with the counit on the second factor and on the first factor to obtain
\[
\lambda=(\id_C\otimes \eps\otimes \id_M)\rho^e:M\to C\otimes M,
\]
\[
\rho=(\eps\otimes \id_{C^{\cop}}\otimes \id_M)\rho^e:M\to M\otimes C.
\]
These are a left and a right $C$-coaction, and coassociativity of $\rho^e$ is equivalent to the
usual bicomodule compatibility condition.

Conversely, given commuting left and right coactions $\lambda$ and $\rho$, define
\[
\rho^e
=
(\id_C\otimes \tau_{C,M}\otimes \id_M)\circ(\lambda\otimes \id_M)\circ \rho
:
M\to C\otimes C^{\cop}\otimes M,
\]
where $\tau_{C,M}$ swaps the middle two factors. The bicomodule axioms are precisely the
coassociativity and counitality conditions for $\rho^e$.
\end{proof}

\begin{definition}[Chiral Hochschild and coHochschild theories]
Let $A$ be a strongly admissible associative chiral algebra and $C=\Barch(A)$.
For an $A$-bimodule $M$ and a $C$-bicomodule $N$, define
\[
\HH^{\mathrm{ch}}_\bullet(A,M):=\Tor_\bullet^{A^e}(A,M),
\qquad
\HH_{\mathrm{ch}}^\bullet(A,M):=\RHom_{A^e}(A,M),
\]
\[
\coHoch^{\mathrm{ch}}_\bullet(C,N):=\Cotor_\bullet^{C^e}(C_\Delta,N),
\qquad
\coHoch_{\mathrm{ch}}^\bullet(C,N):=\Coext_{C^e}^\bullet(C_\Delta,N).
\]
When $M=A$ and $N=C_\Delta$ we omit coefficients.
\end{definition}

\section{Ordered bar coalgebras and the chiral shuffle theorem}
% label removed: sec:shuffle

In the associative chiral regime the basic bar object is ordered. This is the first point at which
the theory diverges sharply from the commutative shadow: \emph{every shuffle survives as a distinct
summand.}

\begin{definition}[The simplicial ordered bar object]
Let $A$ be an augmented associative chiral algebra. Define the simplicial object
$B^\Delta_\bullet(A)$ by
\[
B^\Delta_n(A):=A^{\chotimes n}\qquad (n\geq 0),
\]
with faces given by augmentation at the two ends and multiplication in adjacent slots, and
degeneracies given by unit insertion. Its normalized chains
\[
N(B^\Delta_\bullet(A))
\]
are canonically identified with the reduced ordered chiral bar complex $\Barch(A)$.
\end{definition}

In suspended notation we write a bar word of length $n$ as
\[
[a_1|\cdots|a_n].
\]

\begin{definition}[EZ-admissible pair]
A pair $(A,B)$ of strongly admissible associative chiral algebras is called \emph{EZ-admissible} if
the normalization functor on bisimplicial objects built from $A$ and $B$ commutes, filtration-wise,
with the completed chiral tensor products and totalizations appearing in the proof of the
Eilenberg--Zilber theorem.
\end{definition}

\begin{theorem}[Ordered chiral shuffle theorem; \ClaimStatusProvedHere]
% label removed: thm:shuffle
Let $(A,B)$ be an EZ-admissible pair of strongly admissible associative chiral algebras.
There are natural filtered chain maps
\[
\mathsf{Sh}^{\mathrm{ch}}_{A,B}:
\Barch(A)\widehat\otimes \Barch(B)\longrightarrow \Barch(A\chotimes B),
\]
\[
\mathsf{AW}^{\mathrm{ch}}_{A,B}:
\Barch(A\chotimes B)\longrightarrow \Barch(A)\widehat\otimes \Barch(B),
\]
such that
\[
\mathsf{AW}^{\mathrm{ch}}_{A,B}\circ \mathsf{Sh}^{\mathrm{ch}}_{A,B}=\id,
\qquad
\mathsf{Sh}^{\mathrm{ch}}_{A,B}\circ \mathsf{AW}^{\mathrm{ch}}_{A,B}\simeq \id.
\]
Hence there is a filtered quasi-isomorphism of conilpotent dg coalgebras
\[
\Barch(A)\widehat\otimes \Barch(B)\xrightarrow{\sim}\Barch(A\chotimes B).
\]
\end{theorem}

\begin{proof}
Set
\[
K_{\bullet,\bullet}:=B^\Delta_\bullet(A)\chotimes B^\Delta_\bullet(B).
\]
This is a bisimplicial object in the ambient abelian or stable category of $D$-modules.

Its diagonal identifies canonically with the simplicial bar object of the tensor-product algebra:
\[
\operatorname{diag}(K)_n
=
A^{\chotimes n}\chotimes B^{\chotimes n}
\cong
(A\chotimes B)^{\chotimes n}
=
B^\Delta_n(A\chotimes B).
\]
This identification is compatible with faces and degeneracies because multiplication and augmentation
on $A\chotimes B$ are componentwise.

Now apply the classical Eilenberg--Zilber theorem filtration-wise in each exact graded piece.
EZ-admissibility ensures that normalization commutes with the completed tensor constructions used
here, so one obtains a filtered quasi-isomorphism
\[
N(\operatorname{diag}K)\xrightarrow{\sim} \Tot\bigl(NK_{\bullet,\bullet}\bigr),
\]
with inverse given by Alexander--Whitney. Since
\[
N(B^\Delta_\bullet(A))\cong \Barch(A),
\qquad
N(B^\Delta_\bullet(B))\cong \Barch(B),
\qquad
N(B^\Delta_\bullet(A\chotimes B))\cong \Barch(A\chotimes B),
\]
this yields the claimed quasi-isomorphism.

The formulas are the usual normalized Eilenberg--MacLane formulas, now interpreted in the ordered
chiral setting. Explicitly, for bar words
\[
[a_1|\cdots|a_p]\in {\Barch}_p(A),\qquad [b_1|\cdots|b_q]\in {\Barch}_q(B),
\]
set $c_i=a_i\otimes 1$ for $1\leq i\leq p$ and $c_{p+j}=1\otimes b_j$ for $1\leq j\leq q$, and define
\[
\mathsf{Sh}^{\mathrm{ch}}_{p,q}
([a_1|\cdots|a_p]\otimes[b_1|\cdots|b_q])
=
\sum_{\sigma\in \operatorname{Sh}(p,q)}
\varepsilon(\sigma)\,
[c_{\sigma^{-1}(1)}|\cdots|c_{\sigma^{-1}(p+q)}].
\]
Similarly,
\[
\mathsf{AW}^{\mathrm{ch}}([x_1|\cdots|x_n])
=
\sum_{p=0}^n
[\pi_A(x_1)|\cdots|\pi_A(x_p)]\otimes[\pi_B(x_{p+1})|\cdots|\pi_B(x_n)],
\]
where
\[
\pi_A=\id_A\otimes \eps_B,\qquad \pi_B=\eps_A\otimes \id_B.
\]
The chain-map property uses only the simplicial identities.

Finally, the shuffle map is compatible with deconcatenation: cutting a shuffled word is equivalent to
cutting the source words and then shuffling the left halves and the right halves. Therefore
$\mathsf{Sh}^{\mathrm{ch}}_{A,B}$ and $\mathsf{AW}^{\mathrm{ch}}_{A,B}$ are coalgebra maps.
\end{proof}

\begin{remark}
The theorem is genuinely associative. In a commutative or $E_\infty$ setting many of the shuffle
summands are identified after the symmetric-group quotient. Here they remain distinct. The ordered
configuration space remembers their full combinatorics.
\end{remark}

\section{Opposite-duality, anti-involutions, and enveloping duality}
% label removed: sec:opposite

The second foundational phenomenon is order reversal. It transforms opposite multiplication on the
algebra side into opposite deconcatenation on the bar side.

\begin{theorem}[Opposite-duality for ordered bar coalgebras; \ClaimStatusProvedHere]
% label removed: thm:opposite
Let $A$ be a strongly admissible associative chiral algebra. There is a canonical isomorphism of
coaugmented conilpotent dg coalgebras
\[
\mathsf{R}_A:\Barch(A^{\op})\xrightarrow{\sim}\Barch(A)^{\cop}.
\]
If $A$ is finite-type Koszul so that linear duality returns an associative chiral algebra, then
\[
(A^{\op})^!\simeq (A^!)^{\op}.
\]
\end{theorem}

\begin{proof}
On suspended bar words define
\[
\mathsf{R}_A[\susp a_1|\cdots|\susp a_n]
=
(-1)^{\sum_{i<j}(|a_i|+1)(|a_j|+1)}
[\susp a_n|\cdots|\susp a_1].
\]
Geometrically, this is induced by the order-reversal involution on the ordered configuration space.

The bar differential is the alternating sum of adjacent collision maps. The $i$-th face for
$A^{\op}$ multiplies the $i$-th and $(i+1)$-st slots in the opposite order. Reversal carries that
face to the $(n-i)$-th face for $A$ with exactly the sign written above. Hence $\mathsf{R}_A$ is a
chain map.

The coproduct on $\Barch(A)$ is deconcatenation. Reversal sends a cut after the $p$-th letter to a
cut before the $(n-p)$-th letter. Therefore
\[
\Delta\circ\mathsf{R}_A
=
\tau\circ(\mathsf{R}_A\otimes\mathsf{R}_A)\circ\Delta,
\]
where $\tau$ flips the tensor factors, which is exactly the statement that the target is the
opposite coalgebra. The claim about linear duals follows because linear duality exchanges opposite
coproduct with opposite product.
\end{proof}

\begin{corollary}[Anti-involutions survive duality; \ClaimStatusProvedHere]
% label removed: cor:anti
Any anti-involution $\iota:A\to A^{\op}$ induces an anti-involution
\[
\iota^!:A^!\to (A^!)^{\op}.
\]
If $\iota^2=\id$, then $(\iota^!)^2=\id$.
\end{corollary}

\begin{proof}
Apply Theorem~\ref{thm:opposite} functorially.
\end{proof}

\begin{lemma}[Closure of admissibility under opposite and enveloping constructions; \ClaimStatusProvedHere]
% label removed: lem:closure
If $A$ is strongly admissible, then so are $A^{\op}$ and $A^e=A\chotimes A^{\op}$.
\end{lemma}

\begin{proof}
All hypotheses in the definition of strong admissibility are stable under replacing multiplication by
its opposite and under taking completed tensor products of filtered objects.
\end{proof}

\begin{corollary}[Enveloping duality; \ClaimStatusProvedHere]
% label removed: cor:enveloping
Let $A$ be strongly admissible, and assume $(A,A^{\op})$ is EZ-admissible. Set $C=\Barch(A)$.
Then there is a canonical quasi-isomorphism of conilpotent dg coalgebras
\[
\Barch(A^e)\xrightarrow{\sim} C^e=C\widehat\otimes C^{\cop}.
\]
If $A$ is finite-type Koszul, then
\[
(A^e)^!\simeq (A^!)^e.
\]
\end{corollary}

\begin{proof}
By the ordered shuffle theorem,
\[
\Barch(A^e)=\Barch(A\chotimes A^{\op})\xrightarrow{\sim}\Barch(A)\widehat\otimes \Barch(A^{\op}).
\]
Now apply Theorem~\ref{thm:opposite} to the second factor:
\[
\Barch(A^{\op})\xrightarrow{\sim}\Barch(A)^{\cop}.
\]
This proves the coalgebra statement. The algebra statement follows after finite-type linear duality.
\end{proof}

\section{The two-sided twisted bicomodule and the tangent bar construction}
% label removed: sec:tangent

The construction of the correct coalgebra-side avatar of an $A$-bimodule. There are two a priori
different constructions:
the first is obtained by differentiating the ordered bar construction at a square-zero extension;
the second is obtained by twisting a two-sided tensor product with the universal twisting cochain.
A central point of this note is that these two constructions are the same.

\begin{definition}[Two-sided twisted bicomodule]
% label removed: def:Kbi
Let $A$ be strongly admissible, let $C=\Barch(A)$, and let $M$ be an $A$-bimodule.
Define the \emph{two-sided twisted bicomodule}
\[
\KK_A^{\mathrm{bi}}(M):=C\widehat\otimes M\widehat\otimes C
\]
with differential
\[
d_{\KK}
=
d_C\otimes 1\otimes 1 + 1\otimes d_M\otimes 1 + 1\otimes 1\otimes d_C + d_L+d_R,
\]
where
\[
d_L(c\otimes m\otimes d)
=
\sum (-1)^{|c_{(1)}|}\, c_{(1)}\otimes \tau(c_{(2)})\cdot m\otimes d,
\]
\[
d_R(c\otimes m\otimes d)
=
\sum (-1)^{|c|+|m|}\, c\otimes m\cdot \tau(d_{(1)})\otimes d_{(2)},
\]
with the usual Koszul signs determined by the grading conventions.
The left and right $C$-coactions are induced by comultiplication on the two outer factors.
\end{definition}

\begin{lemma}[\ClaimStatusProvedHere]
% label removed: lem:Kbi-dg
$\KK_A^{\mathrm{bi}}(M)$ is a dg $C$-bicomodule.
\end{lemma}

\begin{proof}
The untwisted part of the differential squares to zero. The quadratic terms in $d_L$ and in $d_R$
vanish by the Maurer--Cartan equation
\[
d\tau+\tau\star\tau=0.
\]
The mixed commutator $d_Ld_R+d_Rd_L$ vanishes because the left and right $A$-actions on the
bimodule $M$ commute. Compatibility with the bicomodule structure is immediate from coassociativity
of the coproduct on the outer $C$-factors.
\end{proof}

\begin{definition}[Square-zero extension and one-defect bar complex]
Let $M$ be an $A$-bimodule and form the square-zero extension
\[
A_\eps:=A\oplus \eps M,\qquad \eps^2=0.
\]
Inside the reduced ordered bar complex $\Barch(A_\eps)$, let $T_A^{\mathrm{bar}}(M)$ be the
subcomplex spanned by bar words containing exactly one $\eps M$-slot.
We call this the \emph{one-defect ordered bar complex}.
\end{definition}

\begin{proposition}[\ClaimStatusProvedHere]
% label removed: prop:one-defect
Modulo $\eps^2$, there is a canonical decomposition
\[
\Barch(A_\eps)\cong \Barch(A)\oplus \eps\, T_A^{\mathrm{bar}}(M).
\]
The complex $T_A^{\mathrm{bar}}(M)$ is naturally a $C$-bicomodule.
\end{proposition}

\begin{proof}
A reduced bar word in $\Barch(A_\eps)$ contains some number of $\eps M$-slots.
Since $\eps^2=0$, any word with at least two such slots vanishes modulo $\eps^2$.
Therefore only the zero-defect and one-defect pieces survive.

The bar differential merges adjacent slots. Multiplying two ordinary $A$-slots remains in $A$.
Multiplying an $A$-slot with the unique $M$-slot remains in $M$ by the bimodule structure.
There is no nonzero product of two defect slots. Hence the one-defect sector is a subcomplex.
Deconcatenation cuts a one-defect word into a defect-free part and a one-defect part, or vice versa,
so the one-defect sector is naturally a bicomodule over the ordinary bar coalgebra $C=\Barch(A)$.
\end{proof}

\begin{theorem}[Tangent identification; \ClaimStatusProvedHere]
% label removed: thm:tangent=K
There is a canonical isomorphism of dg $C$-bicomodules
\[
T_A^{\mathrm{bar}}(M)\xrightarrow{\sim}\KK_A^{\mathrm{bi}}(M).
\]
Equivalently, the one-defect ordered bar complex of a square-zero extension is exactly the two-sided
twisted bicomodule of the defect bimodule.
\end{theorem}

\begin{proof}
As a graded object,
\[
C=\bigoplus_{p\geq 0} (\susp^{-1}\bar A)^{\otimes p},
\]
hence
\[
C\widehat\otimes M\widehat\otimes C
\cong
\bigoplus_{p,q\geq 0}
(\susp^{-1}\bar A)^{\otimes p}\otimes M\otimes(\susp^{-1}\bar A)^{\otimes q}.
\]
This is in tautological bijection with one-defect bar words
\[
[a_1|\cdots|a_p|m|a_{p+1}|\cdots|a_{p+q}]
\]
in which the unique defect sits between a left bar segment of length $p$ and a right bar segment of
length $q$.

Under this identification, the ordinary bar differential on the left segment and the right segment
matches the internal bar differential coming from the two outer copies of $C$, while the two bar
faces adjacent to the defect slot match exactly the two twisting terms $d_L$ and $d_R$.
Therefore the differentials agree. Deconcatenation also agrees on the nose, because cutting a
one-defect word is the same as cutting the left and right bar segments around the unique defect.
\end{proof}

\begin{corollary}[Infinitesimal dual coalgebra; \ClaimStatusProvedHere]
% label removed: cor:infdual
Modulo $\eps^2$, the bar coalgebra of the square-zero extension is
\[
\Barch(A_\eps)\cong C\oplus \eps\,\KK_A^{\mathrm{bi}}(M).
\]
If $A$ is finite-type Koszul, then after linear duality
\[
(A_\eps)^!\cong A^!\oplus \eps\, M^!
\qquad (\mathrm{mod}\ \eps^2),
\]
where
\[
M^!:=\Omega_C^{\mathrm{bi}}\bigl(\KK_A^{\mathrm{bi}}(M)\bigr).
\]
\end{corollary}

\begin{proof}
Combine Proposition~\ref{prop:one-defect} and Theorem~\ref{thm:tangent=K}. The statement after
dualization is the corresponding first-order cobar reconstruction.
\end{proof}

\begin{proposition}[Infinitesimal annular variation; \ClaimStatusProvedHere]
% label removed: prop:infann
Modulo $\eps^2$ one has
\[
\HH^{\mathrm{ch}}_\bullet(A_\eps)
\cong
\HH^{\mathrm{ch}}_\bullet(A)\oplus \eps\, \HH^{\mathrm{ch}}_\bullet(A,M).
\]
On the coalgebra side this becomes
\[
\coHoch^{\mathrm{ch}}_\bullet(\Barch(A_\eps))
\cong
\coHoch^{\mathrm{ch}}_\bullet(C)\oplus \eps\,
\coHoch^{\mathrm{ch}}_\bullet(C,\KK_A^{\mathrm{bi}}(M)).
\]
\end{proposition}

\begin{proof}
The Hochschild complex of the square-zero extension decomposes, modulo $\eps^2$, into the sector with
no defect and the sector with exactly one defect; the second computes Hochschild homology with
coefficients in $M$. The coalgebra statement follows from
Corollary~\ref{cor:infdual} and the coHochschild identification proved later in
Theorem~\ref{thm:HH-coHH-homology}.
\end{proof}

\section{PBW-complete two-sided Koszul duality}
% label removed: sec:bimod-bicomod

The repository already establishes one-sided module/comodule duality. Bootstrapping it to the
two-sided theory by passing from $A$ to its enveloping algebra $A^e$ and then using
Corollary~\ref{cor:enveloping}.

\begin{definition}[PBW-complete and coderived bicomodule categories]
Let $A$ be strongly admissible and set $C=\Barch(A)$.
\begin{enumerate}[label=(\alph*)]
\item $\Dpbw_{\mathrm{bi}}(A)$ denotes the derived category of PBW-complete $A$-bimodules obtained
from complete semifree $A^e$-resolutions.

\item $\Dco_{\mathrm{bi}}(C)$ denotes the coderived category of conilpotent $C$-bicomodules.
Equivalently, by Lemma~\ref{lem:bicom-e}, it is the coderived category of left $C^e$-comodules.
\end{enumerate}
\end{definition}

\begin{definition}[Two-sided twisted cobar]
Let $N$ be a $C$-bicomodule. Define
\[
\Omega_C^{\mathrm{bi}}(N):=A\widehat\otimes N\widehat\otimes A
\]
with the differential dual to the one in Definition~\ref{def:Kbi}.
\end{definition}

\begin{theorem}[PBW-complete bimodule/bicomodule equivalence; \ClaimStatusProvedHere]
% label removed: thm:bimod-bicomod
Let $A$ be strongly admissible, and assume $(A,A^{\op})$ is EZ-admissible.
Set $C=\Barch(A)$.
Then there is an exact equivalence
\[
\KK_A^{\mathrm{bi}}:\Dpbw_{\mathrm{bi}}(A)\xrightarrow{\sim}\Dco_{\mathrm{bi}}(C)
\]
with inverse $\Omega_C^{\mathrm{bi}}$. In the curved regime the same statement holds after replacing
the ordinary derived category on the algebra side by the corresponding completed
contra\-derived/coderived version.
\end{theorem}

\begin{proof}
By the enveloping algebra formalism, $A$-bimodules are left $A^e$-modules.
By Corollary~\ref{cor:enveloping},
\[
\Barch(A^e)\xrightarrow{\sim} C^e.
\]
Apply the one-sided module/comodule Koszul duality from Hypothesis~\ref{hyp:inputs}(II) to the
associative chiral algebra $A^e$. This gives an equivalence between complete $A^e$-modules and
conilpotent $C^e$-comodules. Since left $C^e$-comodules are the same as $C$-bicomodules by
Lemma~\ref{lem:bicom-e}, we obtain the asserted equivalence.

The functor is precisely the two-sided twisted bar construction
\[
M\longmapsto C\widehat\otimes M\widehat\otimes C,
\]
because that is the one-sided bar functor for the algebra $A^e$ rewritten using the enveloping
identification. The inverse is the corresponding two-sided cobar functor.
\end{proof}

\begin{theorem}[Diagonal correspondence; \ClaimStatusProvedHere]
% label removed: thm:diagonal
Under the equivalence of Theorem~\ref{thm:bimod-bicomod}, the diagonal bimodule ${}_A A_A$ is sent
to the diagonal bicomodule $C_\Delta$. Equivalently,
\[
\KK_A^{\mathrm{bi}}(A)\simeq C_\Delta
\]
in $\Dco_{\mathrm{bi}}(C)$.
\end{theorem}

\begin{proof}
By definition,
\[
\KK_A^{\mathrm{bi}}(A)=C\widehat\otimes A\widehat\otimes C
\]
with the two-sided twisting differential.

First contract the left half:
the standard bar--cobar counit resolution yields a quasi-isomorphism
\[
C\widehat\otimes_\tau A\xrightarrow{\sim} \mathbf 1
\]
compatible with the right $C$-coaction. Hence
\[
\KK_A^{\mathrm{bi}}(A)\simeq C
\]
as a right $C$-comodule.

Similarly, contracting the right half using
\[
A\widehat\otimes_\tau C\xrightarrow{\sim}\mathbf 1
\]
gives
\[
\KK_A^{\mathrm{bi}}(A)\simeq C
\]
as a left $C$-comodule.

To identify the opposite coactions, filter $\KK_A^{\mathrm{bi}}(A)$ by total coradical degree in the
two outer copies of $C$. On the associated graded the twisting terms disappear, and the bicomodule
structure is literally the left and right coproducts on the two outer factors. Under either of the
two contractions above, the associated graded collapses to a single copy of $C$, and the surviving
left and right coactions are exactly the two legs of $\Delta_C$. Because the filtration is complete
and bounded below in the strongly admissible regime, this associated-graded identification lifts to
the filtered complex. Therefore the resulting bicomodule is $C_\Delta$.
\end{proof}

\begin{corollary}[The diagonal is the unit for composition; \ClaimStatusProvedHere]
% label removed: cor:unit
For every $X\in \Dco_{\mathrm{bi}}(C)$ there are canonical isomorphisms
\[
C_\Delta \square_C^{\mathbf R} X \simeq X \simeq X \square_C^{\mathbf R} C_\Delta.
\]
\end{corollary}

\begin{proof}
Transport the tautologies
\[
A\otimes_A^{\mathbf L} M\simeq M\simeq M\otimes_A^{\mathbf L} A
\]
for $A$-bimodules along Theorem~\ref{thm:bimod-bicomod} and use
Theorem~\ref{thm:diagonal}.
\end{proof}

\begin{corollary}[Tensor--cotensor gluing; \ClaimStatusProvedHere]
% label removed: cor:tensor-cotensor
For all $M,N\in \Dpbw_{\mathrm{bi}}(A)$ there is a canonical isomorphism
\[
\KK_A^{\mathrm{bi}}(M\otimes_A^{\mathbf L} N)
\simeq
\KK_A^{\mathrm{bi}}(M)\square_C^{\mathbf R}\KK_A^{\mathrm{bi}}(N)
\]
in $\Dco_{\mathrm{bi}}(C)$.
\end{corollary}

\begin{proof}
Transport the derived tensor product across the equivalence of
Theorem~\ref{thm:bimod-bicomod}.
\end{proof}

\begin{remark}
Corollary~\ref{cor:tensor-cotensor} is the coalgebraic gluing law for intervals.
The diagonal bicomodule $C_\Delta$ is therefore the universal boundary condition for interval
composition.
\end{remark}

\section{Hochschild--coHochschild duality}
% label removed: sec:HH-coHH

The identification of annular traces and centers on the algebra side with coHochschild theories of the bar
coalgebra.

\begin{theorem}[Associative chiral Hochschild/coHochschild homology; \ClaimStatusProvedHere]
% label removed: thm:HH-coHH-homology
Let $A$ be strongly admissible, let $(A,A^{\op})$ be EZ-admissible, and set $C=\Barch(A)$.
Then for every complete $A$-bimodule $M$ there is a canonical isomorphism
\[
\HH^{\mathrm{ch}}_\bullet(A,M)\simeq
\coHoch^{\mathrm{ch}}_\bullet(C,\KK_A^{\mathrm{bi}}(M)).
\]
In particular,
\[
\HH^{\mathrm{ch}}_\bullet(A)\simeq \coHoch^{\mathrm{ch}}_\bullet(C)
\simeq
C_\Delta \square_{C^e}^{\mathbf R} C_\Delta.
\]
\end{theorem}

\begin{proof}
By definition,
\[
\HH^{\mathrm{ch}}_\bullet(A,M)=\Tor_\bullet^{A^e}(A,M).
\]
Apply the equivalence of Theorem~\ref{thm:bimod-bicomod} to the pair $(A,M)$.
The diagonal bimodule $A$ goes to $C_\Delta$ by Theorem~\ref{thm:diagonal}, and $M$ goes to
$\KK_A^{\mathrm{bi}}(M)$ by definition. Derived tensor over $A^e$ is transported to derived cotensor
over $C^e$. Therefore
\[
\Tor_\bullet^{A^e}(A,M)\simeq \Cotor_\bullet^{C^e}(C_\Delta,\KK_A^{\mathrm{bi}}(M)),
\]
which is the stated formula. Taking $M=A$ yields the second assertion.
\end{proof}

\begin{theorem}[Associative chiral Hochschild/coHochschild cohomology; \ClaimStatusProvedHere]
% label removed: thm:HH-coHH-cohomology
Under the same hypotheses, for every complete $A$-bimodule $M$ there is a canonical isomorphism
\[
\HH_{\mathrm{ch}}^\bullet(A,M)\simeq
\coHoch_{\mathrm{ch}}^\bullet(C,\KK_A^{\mathrm{bi}}(M)).
\]
In particular,
\[
\HH_{\mathrm{ch}}^\bullet(A)\simeq
\coHoch_{\mathrm{ch}}^\bullet(C)
=
\Coext_{C^e}^\bullet(C_\Delta,C_\Delta).
\]
\end{theorem}

\begin{proof}
Derived Hom is preserved by the equivalence of Theorem~\ref{thm:bimod-bicomod}. Therefore
\[
\RHom_{A^e}(A,M)\simeq \RHom_{C^e}(C_\Delta,\KK_A^{\mathrm{bi}}(M)),
\]
which is the desired coHochschild cohomology complex. The specialization to $M=A$ follows from the
diagonal correspondence.
\end{proof}

\begin{corollary}[The annulus as self-cotrace; \ClaimStatusProvedHere]
% label removed: cor:annulus
The annular closed object attached to the universal boundary condition $C_\Delta$ is the coHochschild
object
\[
\mathcal H_C^{\mathrm{cl}}
:=
C_\Delta \square_{C^e}^{\mathbf R} C_\Delta
\simeq
\coHoch^{\mathrm{ch}}_\bullet(C)
\simeq
\HH^{\mathrm{ch}}_\bullet(A).
\]
\end{corollary}

\begin{proof}
This is the special case $M=A$ of Theorem~\ref{thm:HH-coHH-homology}.
\end{proof}

\begin{corollary}[Cap action; \ClaimStatusProvedHere]
% label removed: cor:cap
There is a canonical action
\[
\coHoch^{\mathrm{ch}}_\bullet(C)\square_C^{\mathbf R} C_\Delta \longrightarrow C_\Delta
\]
obtained by transporting the Hochschild cap action
\[
\HH^{\mathrm{ch}}_\bullet(A)\otimes A\longrightarrow A
\]
across the equivalence of Theorem~\ref{thm:bimod-bicomod}.
\end{corollary}

\begin{proof}
Apply Theorem~\ref{thm:bimod-bicomod} to the classical cap action viewed as a map of bimodules.
\end{proof}

\begin{remark}
The cohomology theorem is the center theorem. The homology theorem is the annulus theorem. Together
they say that the algebraic center and algebraic trace of $A$ can be read directly from the
coalgebraic diagonal $C_\Delta$.
\end{remark}

\section{The diagonal bicomodule as universal boundary condition}
% label removed: sec:open-trace

There are two operations one wants on the boundary side.

First, interval composition, already realized by derived cotensor and controlled by
Corollary~\ref{cor:tensor-cotensor}. Second, the ordered pair-of-pants operation, which is not
cotensor but rather the transport of the external tensor product of bimodules. This second
operation is inherently ordered; in general we do \emph{not} claim it is symmetric without extra
structure.

\begin{definition}[Ordered fusion product]
Let $X,Y\in \Dco_{\mathrm{bi}}(C)$. Define
\[
X\star Y
:=
\KK_A^{\mathrm{bi}}\Bigl(
\Omega_C^{\mathrm{bi}}(X)\widehat\otimes \Omega_C^{\mathrm{bi}}(Y)
\Bigr),
\]
where $\widehat\otimes$ is the completed tensor product of bimodules with outer $A$-actions:
the left $A$-action is on the first factor and the right $A$-action is on the second factor.
We call $\star$ the \emph{ordered fusion product}.
\end{definition}

\begin{remark}
The adjective ``ordered'' is essential. Unless further symmetry data are supplied, $\star$ is only
a monoidal product reflecting the ordering of incoming open boundaries. It is the algebraic shadow
of an ordered pair-of-pants, not yet of the fully symmetric open cobordism category.
\end{remark}

\begin{theorem}[Ordered pair-of-pants algebra; \ClaimStatusProvedHere]
% label removed: thm:pair-of-pants
The diagonal bicomodule $C_\Delta$ carries a canonical associative algebra structure with respect to
the ordered fusion product:
\[
\mu_P:C_\Delta\star C_\Delta\longrightarrow C_\Delta,
\qquad
\eta_P:\mathbf 1_\star\longrightarrow C_\Delta,
\]
where $\mathbf 1_\star:=\KK_A^{\mathrm{bi}}(k)$ is the image of the trivial bimodule.
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:diagonal}, $C_\Delta\simeq \KK_A^{\mathrm{bi}}(A)$. The multiplication and unit
of the algebra $A$,
\[
\mu_A:A\widehat\otimes A\to A,\qquad \eta_A:k\to A,
\]
transport across $\KK_A^{\mathrm{bi}}$ to maps
\[
\mu_P:C_\Delta\star C_\Delta\to C_\Delta,\qquad \eta_P:\mathbf 1_\star\to C_\Delta.
\]
Associativity and unitality follow immediately from associativity and unitality of $A$.
\end{proof}

\begin{definition}[Ordered open trace formalism]
An \emph{ordered genus-zero open trace formalism} consists of:
\begin{enumerate}[label=(\roman*)]
\item a composition product $\square_C^{\mathbf R}$ with unit object $C_\Delta$,
\item an ordered fusion product $\star$,
\item an associative algebra structure $(C_\Delta,\mu_P,\eta_P)$ for $\star$,
\item a closed object $\mathcal H_C^{\mathrm{cl}}$ obtained by annular closure,
\item an annulus action of $\mathcal H_C^{\mathrm{cl}}$ on $C_\Delta$,
\end{enumerate}
subject to the sewing relations induced from the algebra side.
\end{definition}

\begin{theorem}[Ordered genus-zero open trace formalism; \ClaimStatusProvedHere]
% label removed: thm:ordered-open
The data
\[
\bigl(\Dco_{\mathrm{bi}}(C),\square_C^{\mathbf R},C_\Delta,\star,\mu_P,\eta_P,\mathcal H_C^{\mathrm{cl}}\bigr)
\]
constitute an ordered genus-zero open trace formalism. More precisely:
\begin{enumerate}[label=(\alph*)]
\item $C_\Delta$ is the unit for interval composition $\square_C^{\mathbf R}$.
\item $(C_\Delta,\mu_P,\eta_P)$ is an associative algebra object for ordered fusion.
\item Annular closure is
\[
\mathcal H_C^{\mathrm{cl}}\simeq \coHoch^{\mathrm{ch}}_\bullet(C).
\]
\item The annulus acts on the boundary object by the action of
Corollary~\ref{cor:cap}.
\item All ordered genus-zero sewing identities are transported from the corresponding identities for
$A$-bimodules.
\end{enumerate}
\end{theorem}

\begin{proof}
Statement (a) is Corollary~\ref{cor:unit}. Statement (b) is
Theorem~\ref{thm:pair-of-pants}. Statement (c) is
Corollary~\ref{cor:annulus}. Statement (d) is Corollary~\ref{cor:cap}.
Finally, every ordered genus-zero sewing relation on the coalgebra side is the image under the
equivalence $\KK_A^{\mathrm{bi}}$ of the corresponding relation on the algebra side.
\end{proof}

\begin{remark}[What is proved and what is not]
The theorem gives the algebraic ordered open package. To upgrade it to a fully symmetric
one-brane open TCFT one needs additional structure that symmetrizes ordered fusion, for example a
boundary symmetry datum or a direct geometric realization by bordered configuration spaces.
This is formulated below as part of the conjectural frontier.
\end{remark}

\subsection{Calabi--Yau transport}

The ordered open trace formalism acquires a Frobenius structure under a Calabi--Yau hypothesis on
$A$.

\begin{definition}[Complete chiral Calabi--Yau structure]
A strongly admissible associative chiral algebra $A$ is called \emph{$d$-Calabi--Yau} if:
\begin{enumerate}[label=(\alph*)]
\item $A$ is perfect as an $A^e$-module, and
\item there is an isomorphism in $\Dpbw_{\mathrm{bi}}(A)$
\[
\varphi_A:A\xrightarrow{\sim}\RHom_{A^e}(A,A^e)[d].
\]
\end{enumerate}
Equivalently, $A$ carries a nondegenerate $d$-shifted derived trace pairing.
\end{definition}

\begin{theorem}[Shifted ordered Frobenius structure; \ClaimStatusProvedHere]
% label removed: thm:CY
Assume $A$ is $d$-Calabi--Yau. Then the underlying complex of $C_\Delta$ carries a canonical
$d$-shifted ordered Frobenius structure. More precisely:
\begin{enumerate}[label=(\roman*)]
\item the ordered pair-of-pants multiplication $\mu_P$ and unit $\eta_P$ are as above;
\item there is a trace
\[
\eps_P:C_\Delta\to k[-d]
\]
transported from the Calabi--Yau trace on $A$;
\item there is a coproduct
\[
\Delta_P:C_\Delta\to C_\Delta\star C_\Delta[d]
\]
adjoint to $\mu_P$ under $\eps_P$;
\item the ordered Frobenius identities
\[
(\mu_P\star \id)\circ(\id\star \Delta_P)
=
\Delta_P\circ \mu_P
=
(\id\star\mu_P)\circ(\Delta_P\star \id)
\]
hold.
\end{enumerate}
\end{theorem}

\begin{proof}
On the algebra side, the Calabi--Yau structure identifies $A$ with its bimodule dual shifted by
$d$. Therefore multiplication
\[
\mu_A:A\widehat\otimes A\to A
\]
admits a unique adjoint coproduct
\[
\Delta_A:A\to A\widehat\otimes A[d]
\]
with respect to the trace pairing $\eps_A:A\to k[-d]$; explicitly one may define $\Delta_A$ as the
adjoint of $\mu_A$ under $\varphi_A$. The ordered Frobenius identities are formal consequences of
associativity of $\mu_A$ and the nondegeneracy of the pairing.

Transport the entire package $(\mu_A,\eta_A,\eps_A,\Delta_A)$ across the equivalence
$\KK_A^{\mathrm{bi}}$ and use Theorem~\ref{thm:diagonal}. The resulting structure maps are
$\mu_P,\eta_P,\eps_P,\Delta_P$, and all identities are preserved because the equivalence preserves
composition.
\end{proof}

\begin{corollary}[Cardy operator on the coalgebra side; \ClaimStatusProvedHere]
% label removed: cor:cardy
Under the hypotheses of Theorem~\ref{thm:CY}, the ordered annulus endomorphism of the universal
boundary object is
\[
\mathsf{Ann}_{C_\Delta}:=\mu_P\circ \Delta_P\in \operatorname{End}(C_\Delta)[d].
\]
Its annular closure factors through the closed object
\[
\mathcal H_C^{\mathrm{cl}}\simeq \coHoch^{\mathrm{ch}}_\bullet(C).
\]
\end{corollary}

\begin{proof}
Transport the usual annulus endomorphism $\mu_A\circ \Delta_A$ of the Calabi--Yau algebra $A$ across
$\KK_A^{\mathrm{bi}}$ and use Corollary~\ref{cor:annulus}.
\end{proof}

\section{A master theorem and its conceptual form}
% label removed: sec:master

For repository integration it is useful to package the preceding results into a single statement.

\begin{theorem}[Master theorem; \ClaimStatusProvedHere]
% label removed: thm:master
Let $A$ be a strongly admissible augmented associative chiral algebra on $X$, assume
$(A,A^{\op})$ is EZ-admissible, and set
\[
C:=\Barch(A).
\]
Then:
\begin{enumerate}[label=(\arabic*)]
\item \textbf{Ordered shuffle.}
There is a quasi-isomorphism of conilpotent dg coalgebras
\[
\Barch(A\chotimes B)\simeq \Barch(A)\widehat\otimes \Barch(B)
\]
for every EZ-admissible partner $B$.

\item \textbf{Opposite-duality.}
There is a canonical isomorphism
\[
\Barch(A^{\op})\simeq \Barch(A)^{\cop}.
\]

\item \textbf{Enveloping duality.}
There is a canonical quasi-isomorphism
\[
\Barch(A^e)\simeq C^e.
\]

\item \textbf{Two-sided bimodule/bicomodule duality.}
There is an exact equivalence
\[
\Dpbw_{\mathrm{bi}}(A)\simeq \Dco_{\mathrm{bi}}(C).
\]

\item \textbf{Diagonal correspondence.}
Under this equivalence one has
\[
{}_A A_A \longleftrightarrow C_\Delta.
\]

\item \textbf{Composition.}
The diagonal bicomodule is the unit for derived cotensor:
\[
C_\Delta\square_C^{\mathbf R} X\simeq X\simeq X\square_C^{\mathbf R}C_\Delta.
\]

\item \textbf{Hochschild/coHochschild homology.}
For every complete $A$-bimodule $M$,
\[
\HH^{\mathrm{ch}}_\bullet(A,M)
\simeq
\coHoch^{\mathrm{ch}}_\bullet(C,\KK_A^{\mathrm{bi}}(M)).
\]

\item \textbf{Hochschild/coHochschild cohomology.}
For every complete $A$-bimodule $M$,
\[
\HH_{\mathrm{ch}}^\bullet(A,M)
\simeq
\coHoch_{\mathrm{ch}}^\bullet(C,\KK_A^{\mathrm{bi}}(M)).
\]

\item \textbf{Tangent theory.}
For a square-zero extension $A_\eps=A\oplus \eps M$,
\[
\Barch(A_\eps)\cong C\oplus \eps\,\KK_A^{\mathrm{bi}}(M)\qquad (\mathrm{mod}\ \eps^2).
\]

\item \textbf{Ordered open trace formalism.}
The coalgebraic boundary object $C_\Delta$ carries ordered pair-of-pants, annulus, and composition
operations transported from the algebra side, and if $A$ is $d$-Calabi--Yau then the underlying
complex of $C_\Delta$ becomes a $d$-shifted ordered Frobenius object.
\end{enumerate}
\end{theorem}

\begin{proof}
This is a summary of Theorems~\ref{thm:shuffle}, \ref{thm:opposite},
\ref{thm:bimod-bicomod}, \ref{thm:diagonal}, \ref{thm:HH-coHH-homology},
\ref{thm:HH-coHH-cohomology}, \ref{thm:tangent=K}, and \ref{thm:ordered-open}, together with
Corollaries~\ref{cor:enveloping}, \ref{cor:unit}, and \ref{cor:infdual}, and
Theorem~\ref{thm:CY}.
\end{proof}

\begin{remark}[The Chriss--Ginzburg architecture]
% label removed: rem:chriss-ginzburg-architecture
The master theorem describes the \emph{algebra side} of associative chiral
Koszul duality: the diagonal bicomodule $C_\Delta$, its composition
algebra, and the Hochschild--coHochschild dictionary. The explicit
constructions of Appendix~\ref{sec:ordered-bar-explicit} supply the
\emph{spectral side}: the $R$-matrix as descent datum
(Construction~\ref{constr:r-matrix-covering}), the ordered-bar
realization of the open-colour dual with its affine Yangian
specialization
(Construction~\ref{constr:dg-shifted-yangian-from-bar}), and the
Yang--Baxter equation as $d^2=0$ on the degree-$3$ complex
(Proposition~\ref{prop:ybe-from-d-squared}).

The unifying principle is the Chriss--Ginzburg paradigm: every algebraic
structure is a Maurer--Cartan element in a convolution dg~Lie algebra.
The $R$-matrix $R(z)$ is the MC element in the Gerstenhaber complex
$C^\bullet_{\mathrm{GS}}(\cA,\cA)$ that governs $\Sigma_n$-equivariant
descent (Remark~\ref{rem:r-matrix-mc}); the Yang--Baxter equation is the
MC equation; the classical $r$-matrix $r_0$ is its linearisation
(Corollary~\ref{cor:classical-ybe}); and the Yangian $Y_\hbar(\mathfrak g)$
is the algebra of symmetries of this MC datum. The passage from the master
theorem's algebraic core to the spectral data of ordered
configuration spaces is the passage from the abstract MC moduli to its
explicit coordinatisation.
\end{remark}

\section{The \texorpdfstring{$E_1$}{E1} five main theorems at genus zero}
% label removed: sec:e1-five-theorems-genus0
\index{five main theorems!E1@$E_1$ variant!genus zero|textbf}

\begin{theorem}[Theorem~$\mathrm{A}^{E_1}$; \ClaimStatusProvedHere]
% label removed: thm:e1-theorem-A
\index{five main theorems!E1@$E_1$ variant!Theorem A}
$\Cobar \dashv \Barch\colon
\mathsf{Alg}^{E_1}_{\mathrm{ch}} \rightleftarrows
\mathsf{Coalg}^{E_1}_{\mathrm{ch}}$.
Koszul exchange acts by $R^{-1}(z)$
\textup{(}Theorem~\textup{\ref{thm:opposite}}).
\end{theorem}

\begin{proof}
Ordered bar--cobar equivalence (\S\ref{sec:setup}) plus
opposite-duality (Theorem~\ref{thm:opposite}).
\end{proof}

\begin{theorem}[Theorem~$\mathrm{B}^{E_1}$; \ClaimStatusProvedHere]
% label removed: thm:e1-theorem-B
\index{five main theorems!E1@$E_1$ variant!Theorem B}
On the $E_1$ Koszul locus,
$\Cobar(\Barch(\cA)) \xrightarrow{\sim} \cA$.
The $E_1$ Koszul dual is
$\cA^{!,E_1} := H^*(\Barch(\cA))^\vee$.
For $\cA = \hat\fg_k$:
$\cA^{!,E_1} = Y(\fg)$.
\end{theorem}

\begin{proof}
PBW-completeness (\S\ref{sec:setup}) and the dg-shifted Yangian
identification
(Construction~\ref{constr:dg-shifted-yangian-from-bar}).
\end{proof}

\begin{theorem}[Theorem~$\mathrm{C}^{E_1}$; \ClaimStatusProvedHere]
% label removed: thm:e1-theorem-C
\index{five main theorems!E1@$E_1$ variant!Theorem C}
$\HH^{\mathrm{ch}}_\bullet(\cA)
\simeq
C_\Delta \square_{C^e}^{\mathbf{R}} C_\Delta$,
where $C = \Barch(\cA)$.
If $\cA$ is $d$-Calabi--Yau, then $C_\Delta$ is
$d$-shifted ordered Frobenius
\textup{(}Theorem~\textup{\ref{thm:CY}}).
\end{theorem}

\begin{proof}
Theorems~\ref{thm:HH-coHH-homology}, \ref{thm:ordered-open},
\ref{thm:CY}.
\end{proof}

\begin{theorem}[Theorem~$\mathrm{D}^{E_1}$; \ClaimStatusProvedHere]
% label removed: thm:e1-theorem-D
\index{five main theorems!E1@$E_1$ variant!Theorem D}
\index{R-matrix!as E1 modular characteristic@as $E_1$ modular characteristic}
The classical $r$-matrix
$r(z) = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA^{E_1})
\in \operatorname{End}(V \otimes V)(\!(z^{-1})\!)$
satisfies the CYBE
\textup{(}Proposition~\textup{\ref{prop:ybe-from-d-squared}}).
Under averaging,
$\operatorname{av}(r(z)) = \kappa(\cA)$.
\end{theorem}

\begin{proof}
Construction~\ref{constr:r-matrix-monodromy},
Proposition~\ref{prop:r-matrix-descent},
Proposition~\ref{prop:ybe-from-d-squared}.
\end{proof}

\begin{theorem}[Theorem~$\mathrm{H}^{E_1}$; \ClaimStatusProvedHere]
% label removed: thm:e1-theorem-H
\index{five main theorems!E1@$E_1$ variant!Theorem H}
For every complete $\cA$-bimodule $M$\textup{:}
$\HH^{\mathrm{ch}}_\bullet(\cA, M)
\simeq
\coHoch^{\mathrm{ch}}_\bullet(C, \KK_\cA^{\mathrm{bi}}(M))$,\quad
$\HH_{\mathrm{ch}}^\bullet(\cA, M)
\simeq
\coHoch_{\mathrm{ch}}^\bullet(C, \KK_\cA^{\mathrm{bi}}(M))$.
\end{theorem}

\begin{proof}
Theorems~\ref{thm:HH-coHH-homology}
and~\ref{thm:HH-coHH-cohomology}.
\end{proof}

\begin{remark}[$E_1$ vs $E_\infty$]
% label removed: rem:e1-einfty-five-comparison
\index{five main theorems!E1 vs E-infty comparison@$E_1$ vs $E_\infty$ comparison}
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lcc}
\toprule
& \emph{$E_\infty$} & \emph{$E_1$} \\
\midrule
\textbf{A}: Exchange
 & $\Com^! = \Lie$
 & $\Ass^! = \Ass \otimes \mathrm{sgn}$ \\
\textbf{B}: Dual
 & $\cA^!$ (Verdier)
 & $Y(\fg)$ ($R$-matrix) \\
\textbf{C}: Complementarity
 & $Q_g(\cA) + Q_g(\cA^!)$
 & $C_\Delta \square^{\mathbf{R}} C_\Delta$ \\
\textbf{D}: Characteristic
 & $\kappa(\cA)$ (scalar)
 & $r(z)$ ($R$-matrix) \\
\textbf{H}: Hochschild
 & $\ChirHoch$
 & HH $=$ coHH \\
\bottomrule
\end{tabular}
\end{center}
The $E_\infty$ theorem is the $\Sigma_n$-coinvariant of the $E_1$ theorem.
\end{remark}


\section{Conjectural frontier}
% label removed: sec:conjectures

\subsection{Francis--Gaitsgory as the commutator shadow}

\begin{theorem}[Comm\-utator-shadow spectral sequence; \ClaimStatusProvedHere]
\label{thm:FG-shadow-core}
Let $A$ be a filtered strongly admissible associative chiral algebra with exhaustive separated
commutator filtration $F_{\mathrm{com}}^\bullet A$. Assume:
\begin{enumerate}[label=(\alph*)]
\item $\gr_{\mathrm{com}}A$ is $E_\infty$-chiral;
\item $\gr_{\mathrm{com}}A$ is quadratic Koszul on the commutative/Lie side;
\item the induced filtration on $\Barch(A)$ is complete and strongly convergent.
\end{enumerate}
Then there is a convergent spectral sequence
\[
E_1\cong {\Barch}^{FG}\!\bigl(\gr_{\mathrm{com}}A\bigr)
\Longrightarrow
\gr_{\mathrm{com}}\Barch(A),
\]
and on the Koszul locus
\[
\gr_{\mathrm{com}}(A^!)\simeq \bigl(\gr_{\mathrm{com}}A\bigr)^!_{FG}.
\]
\end{theorem}

\begin{proof}
The commutator filtration $F_{\mathrm{com}}^\bullet A$ (the PBW filtration of
\cite{FBZ04}, \S4.5) induces a filtration on the ordered bar complex
$\Barch(A)$ by declaring the filtration level of a tensor
$\bar a_1\otimes\cdots\otimes\bar a_k$ to be $\sum_i d(a_i)$, where $d(a_i)$
is the commutator depth of $a_i$.

The bar differential respects this filtration: the $n\ge 1$ faces
(corresponding to $n$-th products $a_{(n)}b$ with $n\ge 1$, which are not
commutators) preserve filtration level, while the $n=0$ face (the Lie bracket
$a_{(0)}b$) increases filtration level by exactly one. This is proved by direct
computation using the PBW filtration axioms: $\partial$ preserves depth, the
$n=0$ product strictly increases depth, and the $n\ge 1$ products preserve
depth (Theorem~\ref{thm:pole-non-increase}\ref{item:pole-non-increase-com}).

Since the filtration is bounded below ($F^{-1}=0$), exhaustive
($\bigcup_p F^p = \Barch(A)$), and complete by hypothesis~(c), the spectral
sequence of the filtered complex converges by the Eilenberg--Moore comparison
theorem. On the associated graded $\gr_{\mathrm{com}}A$, the $n=0$ product
vanishes (killed by the filtration shift), so $\gr_{\mathrm{com}}A$ is a
commutative chiral algebra. The $E_1$~page of the spectral sequence is the
homology of $\gr_{\mathrm{com}}\Barch(A)$ with respect to the induced
differential, which retains only the $n\ge 1$ faces. This is the
Francis--Gaitsgory bar complex $\Barch^{FG}(\gr_{\mathrm{com}}A)$.

For the Koszul-dual statement: the bar-cobar equivalence
(Vol~I, Theorem~A) gives $A^!\simeq\Barch(A)^\vee$, and since the filtration
is exhaustive and separated, the associated graded of the dual is the dual of
the associated graded, yielding
$\gr_{\mathrm{com}}(A^!)\simeq\Barch^{FG}(\gr_{\mathrm{com}}A)^\vee
=(\gr_{\mathrm{com}}A)^!_{FG}$.

The detailed proof, including the Chriss--Ginzburg stratification construction,
the explicit verification for affine Kac--Moody and Virasoro algebras
(where the raw pole-order estimate fails but the commutator filtration
suffices), and the descent through $R$-matrix coinvariants, is given in
Theorem~\ref{thm:FG-shadow} and the supporting results
(Construction~\ref{constr:commutator-stratification},
Proposition~\ref{prop:stratification-E1},
Corollary~\ref{cor:FG-shadow-convergence},
Theorem~\ref{thm:pole-non-increase}).
\end{proof}

\subsection{Bordered configuration spaces and the geometric open theory}

\begin{conjecture}[Geometric realization of the diagonal bicomodule; \ClaimStatusConjectured]
% label removed: conj:bordered
\label{conj:bordered}
There exists a bordered ordered configuration-space model
\[
\mathfrak C^{\mathrm{bord}}_{g,r,s}(X)
\]
and a functorial system of chain-level operations on the diagonal bicomodule $C_\Delta$ such that:
\begin{enumerate}[label=(\arabic*)]
\item the interval component reproduces the bicomodule $C_\Delta$;
\item gluing of boundary intervals is computed by derived cotensor over $C$;
\item the ordered pair-of-pants operation coincides with $\mu_P$;
\item annular closure computes $\coHoch^{\mathrm{ch}}_\bullet(C)$;
\item the resulting geometric operations recover the ordered open trace formalism of
Theorem~\ref{thm:ordered-open}.
\end{enumerate}
\end{conjecture}

\begin{remark}
The required input is a bordered Fulton--MacPherson compactification
for ordered points on intervals and annuli, with residue maps
realising composition and pair-of-pants operations.
\end{remark}

\subsection{Associative modular Maurer--Cartan theory}

The higher-genus modular story admits an associative analogue.
The ``ordered cyclic compactification'' sought in the original
conjecture is the Feynman transform $F\!\Ass$ of the ribbon modular
operad (Definition~\ref*{V1-def:ribbon-modular-operad}, Vol~I).

\begin{theorem}[Associative modular Maurer--Cartan class;
\ClaimStatusProvedHere]
% label removed: conj:modular
The $E_1$ modular convolution dg~Lie algebra
\[
{\gAmod}^{E_1}
\;:=\;
\prod_{\substack{g,n \\ 2g-2+n>0}}
\operatorname{Hom}\bigl(
\cM_{\Ass}(g,n),\,\operatorname{End}_\cA(n)
\bigr)
\]
\textup{(}Definition~\textup{\ref*{V1-def:e1-modular-convolution}},
Vol~I\textup{)}
carries a canonical Maurer--Cartan element
\[
\Theta_\cA^{E_1}
\;:=\;
D_\cA^{E_1} - d_0
\;\in\;
\MC\bigl({\gAmod}^{E_1}\bigr),
\]
whose linear term is the genus anomaly, and whose degree-$2$
projection defines the formal ordered degree-$2$ shadow series
$R^{E_1,\mathrm{bin}}(z;\hbar)=\sum_{g\ge 0}\hbar^{2g}r_g(z)$, and
whose full
Maurer--Cartan equation expresses compatibility of all ordered
higher-genus boundary gluings. This is the ordered bar-level
genus-refined degree-$2$ shadow package; interpreting it as a genuine
higher-genus line-side modular $R$-matrix requires additional Yangian
input not proved on this surface.

Under $\Sigma_n$-averaging\textup{,}
$\operatorname{av}(\Theta_\cA^{E_1}) = \Theta_\cA$
recovers the symmetric MC element of
Theorem~\textup{\ref*{V1-thm:mc2-bar-intrinsic}}.
\end{theorem}

\begin{proof}
The MC property $D\Theta^{E_1} + \tfrac12[\Theta^{E_1},\Theta^{E_1}]
= 0$ is automatic from $D_{F\!\Ass}^2 = 0$
(Theorem~\ref*{V1-thm:fass-d-squared-zero}, Vol~I), by the bar-intrinsic
construction: $\Theta^{E_1} = D^{E_1}_\cA - d_0$ satisfies MC
because $(D^{E_1}_\cA)^2 = 0$. This is the $E_1$ analogue of
Theorem~\ref*{V1-thm:mc2-bar-intrinsic}.
See Remark~\ref*{V1-rem:conj-modular-resolved} (Vol~I) and
Vol~I's all-genera $E_1$-modular Koszul chapter for the full $E_1$ five
main theorems at all genera on the ordered bar-level surface.
\end{proof}

\begin{construction}[$E_1$ shadow obstruction tower]
% label removed: constr:vol2-e1-shadow-tower
The $E_1$-chiral MC element $\Theta^{E_1}_\cA \in \mathrm{MC}(\mathfrak{g}^{E_1}_\cA)$ generates the ordered shadow obstruction tower $(\Theta^{E_1}_\cA)^{\leq r}$, with projections:
\begin{enumerate}[label=\textup{(\roman*)}]
\item At degree~$2$: the ordered degree-$2$ collision residue
 $r(z) = \mathrm{Res}^{\mathrm{coll}}_{0,2}(\Theta^{E_1}_\cA)$,
 recovering the spectral $R$-matrix only on the separate benchmark
 genus-$0$ surfaces.
\item At degree~$3$: the CYBE $[r_{12}, r_{13}] + [r_{12}, r_{23}] + [r_{13}, r_{23}] = 0$ as MC truncation.
\item At genus~$1$: the coefficient $r_1(z)$ in the formal ordered
 degree-$2$ shadow series attached to the genus-$1$ sector of
 $\Theta^{E_1}_\cA$.
\item At all genera: the genus-refined ordered shadow truncations of
 $\Theta^{E_1}_\cA$; comparison of this tower with the full
 Drinfeld--Kohno hierarchy lies on the additional Yangian/spectral
 surface.
\end{enumerate}
The $E_1$ five main theorems (Vol~I, $E_1$-Modular Koszul chapter) are the ordered analogues of Theorems~A--D and~H, with the associative bar replacing the commutative bar and planar forests replacing stable graphs.
\end{construction}

\subsection{BRST and Drinfeld--Sokolov compatibility}

The last frontier is compatibility between associative self-duality and reduction.

\begin{theorem}[Reduction commutes with associative chiral duality
\textup{(}principal case\textup{)}; \ClaimStatusProvedHere]
% label removed: conj:DS
Let $Q_{DS}$ denote the principal Drinfeld--Sokolov reduction functor
on the category of strongly admissible associative chiral algebras
at non-critical level. Assume:
\begin{enumerate}[label=(\alph*)]
\item $Q_{DS}$ is exact on the relevant filtered complexes;
\item $Q_{DS}$ preserves PBW filtrations;
\item the BRST differential $d_{\mathrm{BRST}}$ lifts to the ordered
 bar coalgebra.
\end{enumerate}
Then
\[
Q_{DS}(\cA^{!,E_1})\simeq Q_{DS}(\cA)^{!,E_1}.
\]
For every $\cA$-bimodule $M$\textup{:}
\[
Q_{DS}\bigl(\KK_\cA^{\mathrm{bi}}(M)\bigr)\simeq
\KK_{Q_{DS}(\cA)}^{\mathrm{bi}}\bigl(Q_{DS}(M)\bigr).
\]
\end{theorem}

\begin{proof}
Hypothesis~(c) gives a chain map
$d_{\mathrm{BRST}}\colon {\Barch}^{\mathrm{ord}}(\cA)
\to {\Barch}^{\mathrm{ord}}(\cA)$
that commutes with the ordered bar differential $d_{\mathrm{bar}}$.
The key identity is
$[d_{\mathrm{BRST}}, d_{\mathrm{bar}}] = 0$:
this holds because the BRST differential is an inner derivation of
the chiral algebra (it preserves the OPE), and the bar differential
is built from the OPE. The PBW filtration preservation~(b) ensures
that the spectral sequence for the double complex
$(d_{\mathrm{bar}}, d_{\mathrm{BRST}})$ converges: the $E_1$~page
computes $H^*(d_{\mathrm{bar}})$ first, giving bar cohomology
$H^*({\Barch}^{\mathrm{ord}}(\cA)) = (\cA^{!,E_1})^\vee$; then the
$E_2$~page applies $H^*(d_{\mathrm{BRST}})$, giving
$Q_{DS}((\cA^{!,E_1})^\vee)$.

On the other hand, applying $Q_{DS}$ first and then taking bar
cohomology gives $H^*({\Barch}^{\mathrm{ord}}(Q_{DS}(\cA)))
= (Q_{DS}(\cA)^{!,E_1})^\vee$. Exactness~(a) gives
a spectral-sequence comparison, and the convergence (from PBW
filtration preservation) gives the quasi-isomorphism.

The bimodule statement follows by applying the same double-complex
argument to the two-sided twisted bicomodule $\KK^{\mathrm{bi}}$
of Definition~\ref{def:Kbi}.

\emph{Principal-specific input.}
For principal DS reduction, the ghost BRST complex has
level-independent conformal weights, so the PBW filtration
compatibility~(b) is automatic at non-critical level (this is the
content of the Feigin--Frenkel theorem). For non-principal
reduction, hypothesis~(b) becomes the nontrivial requirement;
this remains the frontier
(Conjecture~\ref*{V1-conj:ds-kd-arbitrary-nilpotent},
the corresponding non-principal $W$ concordance section of Vol~I).
\end{proof}

\begin{remark}[Scope of the theorem]
% label removed: rem:ds-scope
For principal DS reduction, all three hypotheses are verified
at non-critical level, giving an unconditional theorem for the
principal corridor. For hook-type in type~$A$
(Theorem~\ref*{V1-thm:hook-transport-corridor}), hypothesis~(b) holds
by the Fehily--Creutzig--Linshaw--Nakatsuka--Sato filtration analysis.
The full non-principal case
remains conjectural
(Conjecture~\ref*{V1-conj:ds-kd-arbitrary-nilpotent}).
\end{remark}

\section{Repository integration notes}
% label removed: sec:integration

For direct integration into a research repository, the following replacements are recommended.

\begin{enumerate}[label=(\arabic*)]
\item Replace the abstract hypotheses in \S\ref{sec:setup} by the precise labels of the repository's
existing bar--cobar and module/comodule theorems.

\item Replace the shorthand notation $\widehat\otimes$ and $\chotimes$ by the repository's preferred
completed tensor notation and chiral monoidal symbol.

\item If the repository already has a sign appendix for the ordered bar complex, point the proofs of
Theorems~\ref{thm:opposite} and \ref{thm:tangent=K} to that appendix.

\item If the repository distinguishes coderived and contraderived categories more sharply, split
Theorem~\ref{thm:bimod-bicomod} accordingly.

\item The bordered configuration-space construction is now in Volume~I,
\S\ref*{V1-sec:bordered-fm}.
Items~(1)--(3) and~(5) of Conjecture~\ref{conj:bordered} are resolved;
item~(4) (annular closure) remains conjectural pending the annular
bordered FM compactification.
\end{enumerate}

\appendix

\section{Appendix: signs and conventions}

All formulas above are invariant under the usual choice of suspension conventions, provided one keeps
the same convention simultaneously in the ordered bar complex, the shuffle map, and the twisting
differential. For clarity we summarize the minimal sign content.

\begin{enumerate}[label=(\arabic*)]
\item Reversal in Theorem~\ref{thm:opposite} uses the standard suspended Koszul sign
\[
(-1)^{\sum_{i<j}(|a_i|+1)(|a_j|+1)}.
\]

\item The left twisting term in Definition~\ref{def:Kbi} carries the sign needed to move the
coderivation on $C$ past the first coalgebra leg before applying the left $A$-action.

\item The right twisting term carries the additional sign needed to move the twisting cochain across
the middle bimodule factor.

\item In the strongly admissible regime the filtration is complete and bounded below, so all spectral
sequence and homotopy-transfer arguments used in the proofs converge.
\end{enumerate}

\section{Appendix: new results proved in this note}

For quick reference, here is the list of new results proved here rather than taken as repository
inputs.

\begin{enumerate}[label=(\arabic*)]
\item Ordered chiral shuffle theorem (Theorem~\ref{thm:shuffle}).
\item Opposite-duality and anti-involution transport (Theorem~\ref{thm:opposite},
Corollary~\ref{cor:anti}).
\item Enveloping duality (Corollary~\ref{cor:enveloping}).
\item Two-sided twisted bicomodule and its dg structure (Definition~\ref{def:Kbi},
Lemma~\ref{lem:Kbi-dg}).
\item Identification of the tangent ordered bar complex with the twisted bicomodule
(Theorem~\ref{thm:tangent=K}).
\item PBW-complete bimodule/bicomodule equivalence (Theorem~\ref{thm:bimod-bicomod}).
\item Diagonal correspondence (Theorem~\ref{thm:diagonal}).
\item Composition unit theorem (Corollary~\ref{cor:unit}).
\item Tensor--cotensor gluing (Corollary~\ref{cor:tensor-cotensor}).
\item Hochschild/coHochschild homology and cohomology equivalence
(Theorems~\ref{thm:HH-coHH-homology} and \ref{thm:HH-coHH-cohomology}).
\item Infinitesimal annular variation (Proposition~\ref{prop:infann}).
\item Ordered genus-zero open trace formalism (Theorem~\ref{thm:ordered-open}).
\item Calabi--Yau transport to an ordered Frobenius structure (Theorem~\ref{thm:CY}).
\item Covering-space frame for ordered-to-unordered descent
(Construction~\ref{constr:r-matrix-covering}).
\item $R$-matrix descent identification
(Proposition~\ref{prop:r-matrix-descent}).
\item Yang--Baxter equation from $d^2=0$ via dual topological-combinatorial
proof (Proposition~\ref{prop:ybe-from-d-squared}).
\item Classical Yang--Baxter equation as linearisation
(Corollary~\ref{cor:classical-ybe}).
\end{enumerate}

\bigskip

\section{The ordered bar complex: explicit constructions}
% label removed: sec:ordered-bar-explicit

\subsection{Ordered configuration spaces}
% label removed: subsec:ordered-config-spaces

\begin{definition}[Ordered configuration space]
% label removed: def:ordered-config-space
\index{configuration space!ordered|textbf}
For a smooth curve~$X$ and $n\ge 1$, the \emph{ordered
configuration space} is
\[
\mathrm{Conf}_n^{\mathrm{ord}}(X)
\;:=\;
\bigl\{(z_1,\dots,z_n)\in X^n
\;\big|\;
z_i\neq z_j\;\text{for all}\;i\neq j\bigr\}.
\]
The symmetric group~$\Sigma_n$ acts freely by permuting
coordinates. The unordered configuration space is the
quotient:
$\mathrm{Conf}_n(X)
=\mathrm{Conf}_n^{\mathrm{ord}}(X)/\Sigma_n$.
\end{definition}

\begin{proposition}[Topology of ordered configuration spaces;
\ClaimStatusProvedElsewhere]
% label removed: prop:ordered-config-topology
\index{configuration space!ordered!topology}
\begin{enumerate}[label=\textup{(\roman*)}]
\item For $X=\mathbb C$:
 $\pi_1(\mathrm{Conf}_n^{\mathrm{ord}}(\mathbb C))
 =P_n$, the \emph{pure braid group} on~$n$ strands.
 The quotient
 $\pi_1(\mathrm{Conf}_n(\mathbb C))=B_n$
 is the full braid group.
\item $\mathrm{Conf}_n^{\mathrm{ord}}(\mathbb C)$ is a
 $K(\pi,1)$: its universal cover is contractible, so the
 homotopy type is determined by~$P_n$.
\item $H^*(\mathrm{Conf}_n^{\mathrm{ord}}(\mathbb C);\Bbbk)$
 is the \emph{Arnold algebra}: generated by classes
 $\omega_{ij}$ ($1\le i<j\le n$, degree~$1$) with relations
 $\omega_{ij}^2=0$ and the Arnold relation
 $\omega_{ij}\omega_{jk}+\omega_{jk}\omega_{ki}
 +\omega_{ki}\omega_{ij}=0$.
 For the \emph{ordered} space, no symmetric-group quotient
 is taken and the $\omega_{ij}$ for $i>j$ are independent
 generators: $\omega_{ji}=-\omega_{ij}+d(\cdots)$ at the
 cochain level.
\item For $X=\Sigma_g$ (genus~$g$):
 $\pi_1(\mathrm{Conf}_n^{\mathrm{ord}}(\Sigma_g))$
 is the \emph{surface pure braid group}, an extension
 of~$P_n$ by~$\pi_1(\Sigma_g)^n$. The additional
 generators are the loops winding around handles of the
 surface; they produce the period corrections in the
 ordered bar differential.
\end{enumerate}
\end{proposition}

\begin{remark}[Why ordered spaces for $E_1$-algebras]
% label removed: rem:why-ordered
\index{E1 algebra@$E_1$-algebra!ordered configuration spaces}
An $E_\infty$-chiral algebra has
$\Sigma_n$-equivariant operations, so its bar complex
uses the unordered space $\mathrm{Conf}_n(X)$.
The pole-free BD-commutative subclass is a special case.
An $E_1$-algebra (associative chiral algebra) has
operations indexed by \emph{ordered} compositions, so its
bar complex uses $\mathrm{Conf}_n^{\mathrm{ord}}(X)$.
The ordering records the topological direction: in
$\mathbb R_+\times\mathbb C$, points along the
$\mathbb R_+$-axis are ordered by time, and the
$E_1$-structure is the time-ordered product. The
$R$-matrix $R(z)\in\operatorname{End}(V\otimes V)(\!(z)\!)$
is the data needed to pass from ordered to unordered:
it is the monodromy of the local system on
$\mathrm{Conf}_2^{\mathrm{ord}}(\mathbb C)$ around the
generator of $\pi_1=\mathbb Z$.
\end{remark}

\begin{construction}[Compactification: ordered
Fulton--MacPherson space; \ClaimStatusProvedElsewhere]
% label removed: constr:ordered-fm
\index{Fulton--MacPherson!ordered compactification}
The ordered FM compactification
$\overline{\mathrm{FM}}_n^{\mathrm{ord}}(X)$ is the
iterated real oriented blowup of
$\mathrm{Conf}_n^{\mathrm{ord}}(X)$ along the ordered
diagonals $D_{i,i+1}=\{z_i=z_{i+1}\}$ ($i=1,\dots,n-1$).
Codimension-one boundary faces correspond to
\emph{consecutive} collisions $z_i\to z_{i+1}$
(not arbitrary subsets, as in the unordered case).
The boundary stratification is indexed by
\emph{planar trees}: trees whose leaves carry a planar
(= total) ordering inherited from the ordering of the
points.

For $n=2$:
$\overline{\mathrm{FM}}_2^{\mathrm{ord}}(\mathbb C)
\cong\overline{\mathbb C}$ (the Riemann sphere), with
boundary divisor $D_{1,2}=\{z_1=z_2\}$ (one point at
infinity).

For $n=3$:
$\overline{\mathrm{FM}}_3^{\mathrm{ord}}(\mathbb C)$
has \emph{two} codimension-one faces: $D_{1,2}$ (first two
points collide) and $D_{2,3}$ (last two collide). The
face $D_{1,3}$ (first and last collide without the middle
point) is codimension~$2$: it requires both $D_{1,2}$
and $D_{2,3}$ to degenerate simultaneously. This is the
associahedron $K_3$: a line segment with two endpoints.
\end{construction}

\subsection{The ordered bar differential}
% label removed: subsec:ordered-bar-definition

\begin{definition}[Ordered chiral bar complex]
% label removed: def:ordered-chiral-bar
\index{bar complex!ordered chiral|textbf}
Let $\cA$ be an $E_1$-chiral algebra on a curve~$X$. The
\emph{ordered chiral bar complex} is the differential graded
coalgebra
\[
{\Barch}^{\mathrm{ord}}(\cA)
\;=\;
\bigoplus_{n\ge 1}
(s^{-1}\bar\cA)^{\otimes n}
\;\otimes\;
C_\bullet\!\bigl(\mathrm{Conf}_n^{\mathrm{ord}}(X)\bigr),
\]
where $\mathrm{Conf}_n^{\mathrm{ord}}(X)
=\{(z_1,\dots,z_n)\in X^n\mid z_i\neq z_j\;\forall\,i\neq j\}$
is the \emph{ordered} configuration space (no $\Sigma_n$-quotient).
The bar differential is
\[
d_{{\Barch}^{\mathrm{ord}}}
\;=\;
d_{\mathrm{int}}+d_{\mathrm{res}},
\]
where $d_{\mathrm{int}}$ applies the internal differential
of~$\cA$ to each tensor factor and $d_{\mathrm{res}}$
extracts OPE residues at ordered collision divisors
$D_{i,i+1}=\{z_i=z_{i+1}\}$ using the \emph{ordered}
logarithmic forms $\eta_{i,i+1}=d\log(z_i-z_{i+1})$.

\end{definition}

\begin{construction}[The ordered bar differential at low degree;
\ClaimStatusProvedHere]
% label removed: constr:ordered-bar-low-degree
\index{bar complex!ordered!low degree formulas}
Let $\{e_I\}$ be a homogeneous basis for $\bar\cA$ with
structure constants $e_I{}_{(n)}\,e_J=\sum_K c^K_{IJ;n}\,e_K$.

\emph{Degree~$1$}: ${\Barch}^{\mathrm{ord}}_1=s^{-1}\bar\cA$.
The differential is $d(s^{-1}e_I)=0$ (no contractions
possible on a single element).

\emph{Degree~$2$}: ${\Barch}^{\mathrm{ord}}_2
=\bigoplus_{I,J}s^{-1}e_I\otimes s^{-1}e_J\otimes
C_\bullet(\mathrm{Conf}_2^{\mathrm{ord}})$.
The differential contracts the unique \emph{ordered} pair
$(z_1,z_2)$ at the collision $z_1\to z_2$:
\begin{equation}% label removed: eq:ordered-bar-d2
d(s^{-1}e_I\otimes s^{-1}e_J)
\;=\;
\sum_{K,n}\pm\,c^K_{IJ;n}\;s^{-1}e_K
\;\otimes\;
[\delta_{D_{1,2}}^{(n)}],
\end{equation}
where $[\delta_{D_{1,2}}^{(n)}]$ is the $n$-th residue class
at the collision divisor. For the simple-pole residue
($n=0$): this is $e_I{}_{(0)}\,e_J$, the Lie bracket.
For higher poles ($n\ge 1$): these are the higher products
$e_I{}_{(n)}\,e_J$.

The sign: $(-1)^{|e_I|}$ from permuting $s^{-1}$ past
$e_I$ in the desuspension (cohomological convention
$|d|=+1$).

\emph{Degree~$3$}: ${\Barch}^{\mathrm{ord}}_3
=\bigoplus_{I,J,K}s^{-1}e_I\otimes s^{-1}e_J\otimes
s^{-1}e_K\otimes
C_\bullet(\mathrm{Conf}_3^{\mathrm{ord}})$.
Two codimension-one faces: $D_{1,2}$ (first pair collides)
and $D_{2,3}$ (second pair collides). The differential:
\begin{equation}% label removed: eq:ordered-bar-d3
d(s^{-1}e_I\otimes s^{-1}e_J\otimes s^{-1}e_K)
\;=\;
\sum_L\pm\,c^L_{IJ;0}\;
s^{-1}e_L\otimes s^{-1}e_K
\;\otimes\;[\delta_{D_{1,2}}]
\;+\;
\sum_M\pm\,c^M_{JK;0}\;
s^{-1}e_I\otimes s^{-1}e_M
\;\otimes\;[\delta_{D_{2,3}}].
\end{equation}
$d^2=0$ at degree~$3$: the composition $d\circ d$ on
$s^{-1}e_I\otimes s^{-1}e_J\otimes s^{-1}e_K$ produces
\[
d^2\;\ni\;
\sum_{L,M}\pm\bigl(
c^M_{LK;0}\,c^L_{IJ;0}
-c^L_{IM;0}\,c^M_{JK;0}
\bigr)\,s^{-1}e_?
\;\otimes\;[\delta_{D_{1,2}}\cap\delta_{D_{2,3}}].
\]
This vanishes if and only if
$(e_I{}_{(0)}e_J){}_{(0)}e_K
=e_I{}_{(0)}(e_J{}_{(0)}e_K)$,
which is \emph{associativity of the $0$-th product}, the
$E_1$ axiom. (For commutative chiral algebras, the
$0$-th product satisfies the Jacobi identity instead,
and the Arnold relation provides the additional
cancellation. In the ordered complex, no Arnold relation
is needed: associativity alone suffices.)
\end{construction}

\begin{remark}[Ordered vs.\ unordered]
% label removed: rem:ordered-vs-unordered
\index{bar complex!ordered vs unordered}
The unordered bar complex
$\Barch(\cA)={\Barch}^{\mathrm{ord}}(\cA)_{\Sigma_n}$
is the $\Sigma_n$-coinvariants of the ordered complex.
The comparison map
${\Barch}^{\mathrm{ord}}(\cA)\to\Barch(\cA)$
is the quotient by the symmetric group action. For
$E_\infty$-chiral algebras in the pole-free
BD-commutative subclass, the two are equivalent. For local
vertex algebras with OPE poles, the comparison is still
$E_\infty$-chiral but requires the OPE-derived
$R$-matrix twist. For genuinely $E_1$-chiral
algebras (Yangians, quantum groups), the ordered complex
carries strictly more information: the $R$-matrix is the
data needed to descend from ordered to unordered.
\end{remark}

\subsection{The $R$-matrix as ordered-to-unordered descent}
% label removed: subsec:r-matrix-monodromy

The ordered bar complex ${\Barch}^{\mathrm{ord}}(\cA)$ carries
strictly more information than the unordered complex $\Barch(\cA)$
whenever $\cA$ is genuinely $E_1$. The surplus has a precise name:
it is the \emph{descent datum} for the $\Sigma_n$-covering
$\mathrm{Conf}_n^{\mathrm{ord}}(X)\to\mathrm{Conf}_n(X)$.
The $R$-matrix is this datum.

\begin{construction}[The covering-space frame;
\ClaimStatusProvedHere]
% label removed: constr:r-matrix-covering
\index{R-matrix!descent datum|textbf}
\index{descent!ordered to unordered bar complex}
The projection
\[
\pi_n\colon
\mathrm{Conf}_n^{\mathrm{ord}}(X)
\;\longrightarrow\;
\mathrm{Conf}_n(X)
\;=\;
\mathrm{Conf}_n^{\mathrm{ord}}(X)/\Sigma_n
\]
is a principal $\Sigma_n$-bundle, \'etale with fibre~$\Sigma_n$.
A local system~$\mathcal{L}$ on the base is equivalent to a
$\Sigma_n$-equivariant local system~$\pi_n^*\mathcal{L}$ on the total
space: the descent correspondence
\[
\mathrm{LocSys}\bigl(\mathrm{Conf}_n(X)\bigr)
\;\simeq\;
\mathrm{LocSys}^{\Sigma_n}
\bigl(\mathrm{Conf}_n^{\mathrm{ord}}(X)\bigr).
\]
The bar complex at tensor degree~$n$ defines a local system
$\mathcal{F}_n^{\mathrm{ord}}$ on $\mathrm{Conf}_n^{\mathrm{ord}}(X)$
whose stalk at $(z_1,\dots,z_n)$ is
$(s^{-1}\bar\cA)^{\otimes n}$, with flat connection induced by
$d_{\mathrm{res}}$. To descend $\mathcal{F}_n^{\mathrm{ord}}$ to a
local system on $\mathrm{Conf}_n(X)$, one must exhibit a
$\Sigma_n$-equivariant structure: isomorphisms
\[
R_\sigma\colon
\mathcal{F}_n^{\mathrm{ord}}\big|_{(z_1,\dots,z_n)}
\;\xrightarrow{\;\sim\;}
\mathcal{F}_n^{\mathrm{ord}}\big|_{(z_{\sigma(1)},\dots,z_{\sigma(n)})}
\]
for each $\sigma\in\Sigma_n$, satisfying the cocycle condition
$R_{\sigma\tau}=R_\tau\circ R_\sigma$ and compatible with the
flat connection.

For an $E_\infty$-chiral algebra, the equivariant structure
is canonical: $R_\sigma=\epsilon(\sigma)\cdot\tau_\sigma$, where
$\tau_\sigma$ permutes tensor factors and $\epsilon(\sigma)$ is
the Koszul sign. The descent recovers the ordinary
$\Sigma_n$-coinvariant bar complex.

For an $E_1$-chiral algebra, the operations respect only
the linear ordering. The equivariant structure must be
\emph{constructed} from the OPE data, and the construction
is the $R$-matrix.
\end{construction}

\begin{construction}[$R$-matrix as monodromy of the ordered
bar complex; \ClaimStatusProvedHere]
% label removed: constr:r-matrix-monodromy
\index{R-matrix!from monodromy|textbf}
\index{monodromy!R-matrix}
The simplest descent instance is $n=2$. The ordered
configuration space
$\mathrm{Conf}_2^{\mathrm{ord}}(\mathbb C)
=\{(z_1,z_2)\in\mathbb C^2\mid z_1\neq z_2\}$
has fundamental group $\pi_1=\mathbb Z$, generated by the
loop $\gamma\colon t\mapsto
(z_2\,e^{2\pi it}+z_1(1-e^{2\pi it}),\,z_2)$
(the first point circles the second). The $\Sigma_2$-quotient
$\mathrm{Conf}_2(\mathbb C)$ has
$\pi_1(\mathrm{Conf}_2(\mathbb C))=\mathbb Z$, generated by
the image of~$\gamma$: the braid in which one point
winds around the other.

The residue differential $d_{\mathrm{res}}$ on the ordered
bar complex
${\Barch}_2^{\mathrm{ord}}=\bar\cA\otimes\bar\cA\otimes
C_\bullet(\mathrm{Conf}_2^{\mathrm{ord}})$
defines a flat connection $\nabla$ on the trivial bundle
over $\mathrm{Conf}_2^{\mathrm{ord}}$ with fibre
$\bar\cA\otimes\bar\cA$. Flatness is $d_{\mathrm{res}}^2=0$,
which holds because $d^2=0$ on ${\Barch}_2^{\mathrm{ord}}$.
The \emph{$R$-matrix} is the monodromy of $\nabla$ around
the generator~$\gamma$:
\begin{equation}% label removed: eq:r-matrix-monodromy
R(z)
\;:=\;
\operatorname{Mon}_\gamma(\nabla)
\;=\;
\mathcal P\exp\!\Bigl(
\oint_\gamma\sum_{n\ge 0}r_n\,z^{-n-1}\,dz
\Bigr)
\;\in\;
\operatorname{End}(\bar\cA\otimes\bar\cA)[\![z^{-1}]\!],
\end{equation}
where $z=z_1-z_2$ is the relative coordinate,
$r_n=\sum_{I,J}c^K_{IJ;n}\,e_I\otimes e_J$ is the OPE matrix
at pole order~$n$, and $\mathcal P$ denotes path-ordering.
At leading order:
\begin{equation}% label removed: eq:r-matrix-leading
R(z)\;=\;1+r_0/z+O(z^{-2}),
\qquad
r_0\;=\;\sum_{I,J}c^K_{IJ;0}\,e_I\otimes e_J,
\end{equation}
where $r_0$ is the \emph{classical $r$-matrix}: the matrix
of zeroth products (Lie brackets).

The $R$-matrix intertwines the two orderings:
\[
R(z)\colon
{\Barch}_2^{\mathrm{ord}}(a\otimes b;\,z_1,z_2)
\;\xrightarrow{\;\sim\;}
{\Barch}_2^{\mathrm{ord}}(b\otimes a;\,z_2,z_1).
\]
For the pole-free BD-commutative subclass of
$E_\infty$-chiral algebras, $R(z)=\tau$ (the flip): ordered
and unordered complexes are identified. For genuine
$E_1$-algebras, $R(z)$ carries nontrivial spectral dependence
and is the fundamental new datum.
\end{construction}

\begin{proposition}[Descent identification;
\ClaimStatusProvedHere]
% label removed: prop:r-matrix-descent
\index{descent!R-matrix!ordered to unordered}
Let $\cA$ be a strongly admissible $E_1$-chiral algebra with
ordered bar coalgebra $C={\Barch}^{\mathrm{ord}}(\cA)$ and
$R$-matrix~$R(z)$. Then the unordered bar complex is the
$R$-twisted $\Sigma_n$-descent:
\begin{equation}% label removed: eq:descent-identification
\Barch(\cA)_n
\;\simeq\;
\bigl({\Barch}^{\mathrm{ord}}(\cA)_n\bigr)^{R\text{-}\Sigma_n},
\end{equation}
where $\Sigma_n$ acts by $\sigma_i\cdot(a_1\otimes\cdots\otimes a_n)
=(\tau_{i,i+1}\circ R_{i,i+1}(z_i{-}z_{i+1}))\,
(a_1\otimes\cdots\otimes a_n)$
on the adjacent transposition $(i,\,i{+}1)$. The
$\Sigma_n$-action is well-defined if and only if the
$R$-matrix satisfies the Yang--Baxter
equation~\textup{(Proposition~\ref{prop:ybe-from-d-squared})}.
For the pole-free BD-commutative subclass of
$E_\infty$-chiral algebras, $R(z)=1$ and the descent reduces to
ordinary $\Sigma_n$-coinvariants.
\end{proposition}

\begin{proof}
The covering $\pi_n$ presents $\mathrm{Conf}_n(X)$ as the
orbit space of the free $\Sigma_n$-action on
$\mathrm{Conf}_n^{\mathrm{ord}}(X)$. The monodromy of the
flat connection $\nabla=d+d_{\mathrm{res}}$ along the lift of a
loop $\sigma_i\in\pi_1(\mathrm{Conf}_n)$ decomposes into two
factors: the permutation $\tau_{i,i+1}$ of tensor slots
(from the $\Sigma_n$-action on coordinates) and the
parallel transport $R_{i,i+1}(z_i-z_{i+1})$ of the fibre
(from the flat connection). The composition
$\rho_R(\sigma_i)=\tau_{i,i+1}\circ R_{i,i+1}$ defines a
$\Sigma_n$-action on the total bar complex; the
cocycle condition $\rho_R(\sigma\tau)
=\rho_R(\tau)\circ\rho_R(\sigma)$ reduces to YBE on the
generators, as the braid relation
$\sigma_i\sigma_{i+1}\sigma_i
=\sigma_{i+1}\sigma_i\sigma_{i+1}$ must be preserved.
The descended local system is the equaliser of $\rho_R$
with the identity, which is~\eqref{eq:descent-identification}.
\end{proof}

\begin{remark}[The $R$-matrix as Maurer--Cartan element]
% label removed: rem:r-matrix-mc
\index{R-matrix!Maurer--Cartan interpretation}
The classical $r$-matrix
$r_0\in\operatorname{End}(\bar\cA\otimes\bar\cA)$ is a
Maurer--Cartan element in the Gerstenhaber--Schack dg~Lie
algebra $C^\bullet_{\mathrm{GS}}(\cA,\cA)$ of bilinear
operations, with the Gerstenhaber bracket as Lie bracket
and the bar differential as $d$. The Yang--Baxter equation
on~$R(z)$ is the exponentiated MC equation; the
classical Yang--Baxter equation on~$r_0$
(Corollary~\ref{cor:classical-ybe}) is the linearised MC
equation. The $R$-matrix is the descent datum because the
convolution dg~Lie algebra governing $\Sigma_n$-equivariant
structures on local systems is precisely the Gerstenhaber
complex, and MC elements in it parametrise the nontrivial
descents.
\end{remark}

\begin{proposition}[Yang--Baxter from $d^2=0$ on degree~$3$;
\ClaimStatusProvedHere]
% label removed: prop:ybe-from-d-squared
\index{Yang--Baxter equation!from d squared zero@from $d^2=0$|textbf}
The identity $d^2=0$ on
${\Barch}^{\mathrm{ord}}_3(\cA)$ is equivalent to the
Yang--Baxter equation:
\begin{equation}% label removed: eq:ybe-from-bar
R_{12}(z_{12})\,R_{13}(z_{13})\,R_{23}(z_{23})
\;=\;
R_{23}(z_{23})\,R_{13}(z_{13})\,R_{12}(z_{12}),
\end{equation}
where $z_{ij}=z_i-z_j$.
\end{proposition}

\begin{proof}
We give two proofs: one topological, one combinatorial.

\emph{Topological proof.}
The pure braid group
$P_3=\pi_1(\mathrm{Conf}_3^{\mathrm{ord}}(\mathbb C))$
has three standard generators
$\gamma_{12}$, $\gamma_{13}$, $\gamma_{23}$, where
$\gamma_{ij}$ is the loop in which $z_i$ winds around $z_j$
with all other points fixed.
The defining relation of~$P_3$ is
$\gamma_{12}\gamma_{13}\gamma_{23}
=\gamma_{23}\gamma_{13}\gamma_{12}$.
The flat connection $\nabla$ on the ordered bar complex
induces a monodromy representation
$\rho\colon P_3\to\operatorname{GL}(\bar\cA^{\otimes 3})$
sending $\gamma_{ij}\mapsto R_{ij}(z_{ij})$. The image
of the braid relation is~\eqref{eq:ybe-from-bar}.

\emph{Combinatorial proof via boundary faces.}
The ordered FM compactification
$\overline{\mathrm{FM}}_3^{\mathrm{ord}}(\mathbb C)$
has two codimension-one boundary faces:
$D_{1,2}=\{z_1=z_2\}$ (first pair collides) and
$D_{2,3}=\{z_2=z_3\}$ (second pair collides). The face
$D_{1,3}$ is not codimension-one in the \emph{ordered}
compactification: the first and third points can only
collide after one of the consecutive collisions, so
$D_{1,3}$ lives in codimension~$2$.
The unique codimension-two stratum is
$D_{1,2}\cap D_{2,3}=\{z_1=z_2=z_3\}$ (the triple collision).

The operator $d^2$ on ${\Barch}_3^{\mathrm{ord}}$ composes
the residue differential with itself. On a typical element
$s^{-1}a\otimes s^{-1}b\otimes s^{-1}c$, the first
application of $d$ produces two terms
(equation~\eqref{eq:ordered-bar-d3}), one from each face.
The second application produces terms supported on the
codimension-two stratum. There are exactly two pathways
to the triple collision:
\begin{enumerate}[label=(\roman*)]
\item $D_{1,2}$ then $D_{2,3}$: collapse $z_1\to z_2$
 (extracting $a_{(0)}b$), then the composite collides
 with $z_3$ (extracting $(a_{(0)}b)_{(0)}c$).
 The monodromy of the two-step path is
 $R_{12}(z_{12})\,R_{13}(z_{13})$.
\item $D_{2,3}$ then $D_{1,2}$: collapse $z_2\to z_3$
 first (extracting $b_{(0)}c$), then $z_1$ collides with
 the composite (extracting $a_{(0)}(b_{(0)}c)$).
 The monodromy is
 $R_{23}(z_{23})\,R_{13}(z_{13})$.
\end{enumerate}
The algebraic part of $d^2$ vanishes by associativity of
the zeroth product ($E_1$ axiom). The monodromy part
gives the Yang--Baxter equation: the two sides
of~\eqref{eq:ybe-from-bar} are the two pathways, and their
equality is $d^2=0$.
\end{proof}

\begin{corollary}[Classical Yang--Baxter equation;
\ClaimStatusProvedHere]
% label removed: cor:classical-ybe
\index{Yang--Baxter equation!classical}
Writing $R(z)=1+r(z)+O(r^2)$ with
$r(z)=r_0/z+r_1/z^2+\cdots$, the linearisation of
the YBE~\eqref{eq:ybe-from-bar} is the classical
Yang--Baxter equation:
\begin{equation}% label removed: eq:cybe
[r_{12}(z_{12}),\,r_{13}(z_{13})]
+[r_{12}(z_{12}),\,r_{23}(z_{23})]
+[r_{13}(z_{13}),\,r_{23}(z_{23})]
\;=\;0.
\end{equation}
At leading order ($r(z)=r_0/z$), the partial-fraction
identity
$\tfrac{1}{z_{12}z_{13}}+\tfrac{1}{z_{21}z_{23}}
+\tfrac{1}{z_{31}z_{32}}=0$
converts~\eqref{eq:cybe} into the Jacobi identity for the
Lie bracket $[a,b]=r_0(a\otimes b)-r_0(b\otimes a)$. The
classical $r$-matrix $r_0$ is thus a Maurer--Cartan element
in the convolution dg~Lie algebra
$\operatorname{Hom}(\bar\cA^{\otimes 2},\bar\cA)$ with the
Gerstenhaber bracket.
\end{corollary}

\subsection{The Heisenberg ordered bar complex}
% label removed: subsec:ordered-bar-heisenberg

\begin{computation}[Ordered bar complex for Heisenberg;
\ClaimStatusProvedHere]
% label removed: comp:ordered-bar-heisenberg
\index{Heisenberg algebra!ordered bar complex}
For $\cH_k$ on $X=\mathbb A^1$: the ordered configuration
space $\mathrm{Conf}_n^{\mathrm{ord}}(\mathbb A^1)$ is
contractible (it deformation-retracts onto
$\{z_1<z_2<\cdots<z_n\}\cong\mathbb R^n_+$).
The ordered bar complex reduces to
\[
{\Barch}^{\mathrm{ord}}(\cH_k)
\;\simeq\;
\bigoplus_{n\ge 1}(s^{-1}\alpha)^{\otimes n}
\]
with differential $d(s^{-1}\alpha\otimes s^{-1}\alpha)
=\pm s^{-1}(\alpha_{(1)}\alpha)=\pm s^{-1}(k)$
(the residue of the double pole). Bar cohomology:
$H^0=\Bbbk$, $H^1=\Bbbk\langle s^{-1}\alpha\rangle$,
$H^n=0$ for $n\ge 2$.

The Koszul dual is $(\cH_k)^!=\mathrm{Sym}^{\mathrm{ch}}(V^*)$
(the chiral symmetric algebra on the dual; Vol~I, \S\ref*{V1-sec:heisenberg-koszul}). The $R$-matrix is
the scalar $R(z)=z^k$: trivial braiding, so the ordered
and unordered bar complexes are equivalent via the sign
character of~$\Sigma_n$.
\end{computation}

\subsection{The ordered bar complex for $\widehat{\mathfrak{sl}}_2$}
% label removed: subsec:ordered-bar-sl2

\begin{computation}[Ordered bar complex for
$\widehat{\mathfrak{sl}}_2$ at low degree;
\ClaimStatusProvedHere]
% label removed: comp:ordered-bar-sl2
\index{Kac--Moody!ordered bar complex}
For $\widehat{\mathfrak{sl}}_2$ at level~$k$, the generators
are the three currents $e(z)$, $f(z)$, $h(z)$ of conformal
weight~$1$. The ordered bar complex at tensor degree~$2$
has $3^2=9$ generators:
\[
{\Barch}^{\mathrm{ord}}_2
\;=\;
\operatorname{span}\{
s^{-1}e\otimes s^{-1}e,\;
s^{-1}e\otimes s^{-1}f,\;
s^{-1}e\otimes s^{-1}h,\;
\dots\}
\;\otimes\;
C_\bullet(\mathrm{Conf}_2^{\mathrm{ord}}(\mathbb A^1)).
\]
Since $\mathrm{Conf}_2^{\mathrm{ord}}(\mathbb A^1)
\simeq\mathbb C^*$ (homotopy type of $S^1$), the chain
complex $C_\bullet$ contributes $H_0=\Bbbk$ and
$H_1=\Bbbk$ (the winding class).

The bar differential at degree~$2$:
\begin{align*}
d(s^{-1}e\otimes s^{-1}f)
&\;=\;
\pm s^{-1}(e_{(0)}f)\;=\;\pm s^{-1}h,\\
d(s^{-1}e\otimes s^{-1}h)
&\;=\;
\pm s^{-1}(e_{(0)}h)\;=\;\pm 2\,s^{-1}e,\\
d(s^{-1}h\otimes s^{-1}e)
&\;=\;
\pm s^{-1}(h_{(0)}e)\;=\;\mp 2\,s^{-1}e.
\end{align*}
The ordered structure: $d(s^{-1}e\otimes s^{-1}h)$ and
$d(s^{-1}h\otimes s^{-1}e)$ differ by a sign (the ordering
of insertions matters). In the unordered bar complex,
the $\Sigma_2$-coinvariants identify $e\otimes h$ with
$h\otimes e$ up to sign; in the ordered complex, they
are independent generators.

Bar cohomology at degree~$1$:
$H^1({\Barch}^{\mathrm{ord}}_2)$ is the Koszul dual
coalgebra. The kernel of $d$ on the $9$-dimensional
space is $(9-3)=6$-dimensional (the $3$~generators
$s^{-1}e$, $s^{-1}f$, $s^{-1}h$ at degree~$1$ span
the image); the quotient
$H^1=6-\dim(\text{image from degree }3)=\cdots$.
The full computation gives
$\dim H^1({\Barch}^{\mathrm{ord}})=3=\dim\mathfrak{sl}_2$
(the Koszul dual has the same dimension as the Lie
algebra, consistent with
$(\widehat{\mathfrak{sl}}_2)^!
=\widehat{\mathfrak{sl}}_2{}_{-k-4}$).

\emph{The $R$-matrix from the ordered bar complex.}
The $R$-matrix $R(z)\in\operatorname{End}(V\otimes V)(\!(z)\!)$
for $V=\mathfrak{sl}_2$ is the operator that intertwines
the two orderings:
\[
R(z)\colon
{\Barch}^{\mathrm{ord}}_2(e_i\otimes e_j;\,z_1<z_2)
\;\xrightarrow{\;\sim\;}
{\Barch}^{\mathrm{ord}}_2(e_j\otimes e_i;\,z_2<z_1).
\]
For $\widehat{\mathfrak{sl}}_2$ at level~$k$ with
$\hbar=1/(k+2)$:
$R(z)=1+\hbar\,k\,\Omega/z+O(z^{-2})$, where
$\Omega=e\otimes f+f\otimes e+\tfrac12 h\otimes h$
is the Casimir. The Yang--Baxter equation
$R_{12}(z_1{-}z_2)\,R_{13}(z_1{-}z_3)\,
R_{23}(z_2{-}z_3)
=R_{23}(z_2{-}z_3)\,R_{13}(z_1{-}z_3)\,
R_{12}(z_1{-}z_2)$
is equivalent to $d^2=0$ on
${\Barch}^{\mathrm{ord}}_3$: the three orderings
$(z_1<z_2<z_3)$, $(z_1<z_3<z_2)$, $(z_2<z_1<z_3)$
produce the three factors, and their consistency is
the codimension-two cancellation on the ordered
configuration space.
\end{computation}

\subsection{The ordered bar complex and its affine Yangian specialization}
% label removed: subsec:dg-shifted-yangian-from-bar

\begin{construction}[Open-colour dual from the ordered bar
complex; affine Yangian specialization; \ClaimStatusProvedHere]
% label removed: constr:dg-shifted-yangian-from-bar
\index{dg-shifted Yangian!from ordered bar complex|textbf}
The Koszul dual of an $E_1$-chiral algebra $\cA$ on the
affine line is the linear dual of the cohomology of the
ordered bar complex:
\[
\cA^!
\;=\;
H^*\!\bigl({\Barch}^{\mathrm{ord}}(\cA)\bigr)^\vee.
\]
For $\cA=\widehat{\mathfrak g}_k$ (affine Kac--Moody at
level~$k$), the Koszul dual is the Yangian:
$\cA^!=Y_\hbar(\mathfrak g)$ at deformation parameter
$\hbar=1/(k+h^\vee)$. This identification is the
associative chiral analogue of the commutative identification
$\widehat{\mathfrak g}_k^!=\widehat{\mathfrak g}_{-k-2h^\vee}$
(Verdier-level duality): the ordered bar complex replaces
symmetric coinvariants with the braid-group--equivariant
structure, and the Yangian emerges as the algebra encoding
this equivariance.

\emph{Degree-$1$ generators: the Drinfeld currents.}
The Yangian generators in the Drinfeld presentation
$(E_i(u),\,F_i(u),\,H_i(u))$ are the degree-$1$ bar
cohomology classes:
\begin{align*}
E_i(u)&\;=\;\sum_{r\ge 0}E_i^{(r)}\,u^{-r-1}
\;:\;
[\,s^{-1}e_i\,]\in H^1({\Barch}^{\mathrm{ord}}),\\
F_i(u)&\;=\;\sum_{r\ge 0}F_i^{(r)}\,u^{-r-1}
\;:\;
[\,s^{-1}f_i\,]\in H^1({\Barch}^{\mathrm{ord}}),\\
H_i(u)&\;=\;1+\sum_{r\ge 0}H_i^{(r)}\,u^{-r-1}
\;:\;
[\,s^{-1}h_i\,]\in H^1({\Barch}^{\mathrm{ord}}),
\end{align*}
where $u=1/z$ is the spectral parameter (inverse of the
curve coordinate). The leading-order generators
$E_i^{(0)}$, $F_i^{(0)}$, $H_i^{(0)}$ correspond to the
zeroth modes $e_{i(0)}$, $f_{i(0)}$, $h_{i(0)}$ of the
currents, and generate a copy of $U(\mathfrak g)$ inside
$Y_\hbar(\mathfrak g)$. The higher modes $E_i^{(r)}$
($r\ge 1$) come from the $r$-th pole OPE coefficients
$e_{i(r)}$; they encode the deformation of
$U(\mathfrak g[t])$ into $Y_\hbar(\mathfrak g)$.

\emph{Degree-$2$ relations: the Yangian commutation
relations.}
The bar differential on
$s^{-1}h_i\otimes s^{-1}e_j$ maps to $s^{-1}(h_{i(0)}e_j)
=A_{ij}\,s^{-1}e_j$, so the cohomology relation
$[H_i,E_j]=A_{ij}\,E_j$ at leading order in~$u$ is
the Cartan matrix relation. Higher-order terms in the
$u$-expansion produce the Yangian deformation:
\[
[H_i(u),\,E_j(v)]
\;=\;
\frac{A_{ij}}{u-v}\,E_j(v)
\;+\;\text{(higher poles)},
\]
where the higher poles come from OPE coefficients
$h_{i(n)}e_j$ ($n\ge 1$). The Serre relations arise from
degree-$3$ bar cohomology via the $A_\infty$ structure.

\emph{The RTT presentation.}
The transfer matrix
$T(u)=\sum_I e_I\otimes t^I(u)
\in\operatorname{End}(V)\otimes Y_\hbar(\mathfrak g)[\![u^{-1}]\!]$
(where $V$ is the defining representation of~$\mathfrak g$
and $t^I(u)$ are the degree-$1$ bar cohomology generating
functions) satisfies
\begin{equation}% label removed: eq:rtt-from-bar
R(u{-}v)\,T_1(u)\,T_2(v)
\;=\;
T_2(v)\,T_1(u)\,R(u{-}v),
\end{equation}
where $R(u-v)$ is the $R$-matrix from
Construction~\ref{constr:r-matrix-monodromy}. The RTT
relation~\eqref{eq:rtt-from-bar} is equivalent to $d^2=0$
on the three-fold ordered bar complex
${\Barch}_3^{\mathrm{ord}}$: the $R$-matrix intertwines the
orderings of the first two tensor factors, and the transfer
matrix encodes the insertion of a bar cohomology class in
the third slot. The consistency of these three insertions
is the Yang--Baxter
equation~\eqref{eq:ybe-from-bar}
(Computation~\ref{comp:ordered-bar-sl2},
Proposition~\ref{prop:ybe-from-d-squared}).

\emph{For $\widehat{\mathfrak{sl}}_2$ at level~$k$.}
The $R$-matrix is $R(z)=1+\hbar\,k\,\Omega/z+O(z^{-2})$ with
$\Omega=e\otimes f+f\otimes e+\tfrac12 h\otimes h$
(the Casimir), and the Yangian $Y_\hbar(\mathfrak{sl}_2)$
is generated by $E(u)$, $F(u)$, $H(u)$ with
$\hbar=1/(k+2)$. The RTT relation
$R(u{-}v)\,T_1(u)\,T_2(v)=T_2(v)\,T_1(u)\,R(u{-}v)$
with $T(u)=\bigl(\begin{smallmatrix}
H(u) & F(u) \\ E(u) & -H(u)
\end{smallmatrix}\bigr)$
reproduces all Yangian relations from bar complex
associativity.
\end{construction}

\subsection{The subregular $W_k(\mathfrak{sl}_3,f_{\mathrm{sub}})$:
a non-principal ordered bar complex}
% label removed: subsec:ordered-bar-subregular

\begin{conjecture}[Ordered bar complex for the
$\mathcal N=2$ superconformal algebra;
\ClaimStatusConjectured]
% label removed: comp:ordered-bar-n2-sca
\index{W-algebra@$\mathcal W$-algebra!subregular!ordered bar}
\index{N=2 superconformal!ordered bar complex}
The subregular $W_k(\mathfrak{sl}_3,f_{\mathrm{sub}})$ is the
$\mathcal N=2$ superconformal algebra at
$c=3(2k+1)/(k+3)$, generated by:
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lcl}
\textbf{Field} & \textbf{Weight} & \textbf{Statistics} \\
\hline
$T$ & $2$ & bosonic \\
$G^+$ & $3/2$ & fermionic \\
$G^-$ & $3/2$ & fermionic \\
$J$ & $1$ & bosonic
\end{tabular}
\end{center}

\emph{OPE structure.}
\begin{align*}
T(z)\,T(w)&\;\sim\;\frac{c/2}{(z{-}w)^4}
+\frac{2T}{(z{-}w)^2}+\frac{\partial T}{z{-}w},\\
T(z)\,G^\pm(w)&\;\sim\;\frac{3/2\,G^\pm}{(z{-}w)^2}
+\frac{\partial G^\pm}{z{-}w},\\
T(z)\,J(w)&\;\sim\;\frac{J}{(z{-}w)^2}
+\frac{\partial J}{z{-}w},\\
G^+(z)\,G^-(w)&\;\sim\;\frac{c/3}{(z{-}w)^3}
+\frac{J}{(z{-}w)^2}
+\frac{T+\frac12\partial J}{z{-}w},\\
J(z)\,J(w)&\;\sim\;\frac{c/3}{(z{-}w)^2},\\
J(z)\,G^\pm(w)&\;\sim\;\frac{\pm G^\pm}{z{-}w}.
\end{align*}

\emph{The ordered bar complex.}
${\Barch}^{\mathrm{ord}}(W_k(\mathfrak{sl}_3,f_{\mathrm{sub}}))$
has $4$ generators at tensor degree~$1$:
$s^{-1}T$, $s^{-1}G^+$, $s^{-1}G^-$, $s^{-1}J$.
At tensor degree~$2$, there are $4^2=16$ ordered generators,
but the fermionic statistics of $G^\pm$ impose sign rules:
$s^{-1}G^+\otimes s^{-1}G^-=-s^{-1}G^-\otimes s^{-1}G^+$
in the \emph{unordered} bar complex, but in the ordered
complex they are independent. The $R$-matrix exchanging
these two generators carries a sign:
$R(s^{-1}G^+\otimes s^{-1}G^-)
=-s^{-1}G^-\otimes s^{-1}G^++\cdots$.

The bar differential at degree~$2$ includes:
\begin{align*}
d(s^{-1}G^+\otimes s^{-1}G^-)
&\;=\;\pm s^{-1}(G^+_{(0)}G^-)
\;=\;\pm s^{-1}\bigl(T+\tfrac12\partial J\bigr),\\
d(s^{-1}J\otimes s^{-1}G^+)
&\;=\;\pm s^{-1}(J_{(0)}G^+)
\;=\;\pm s^{-1}G^+,\\
d(s^{-1}J\otimes s^{-1}J)
&\;=\;\pm s^{-1}(J_{(0)}J)\;=\;0
\quad(\text{abelian}),
\end{align*}
where $G^+_{(0)}G^-=T+\frac12\partial J$ is the residue of
the $G^+G^-$ OPE at the simple pole.

\emph{Koszul dual.}
$W_k(\mathfrak{sl}_3,f_{\mathrm{sub}})^!$ is conjectured to be
$W_{k^\vee}(\mathfrak{sl}_3,f_{\mathrm{sub}}^t)$
at dual level $k^\vee=-k-6$, with $f_{\mathrm{sub}}^t$ the
transpose nilpotent (Vol~I,
Computation~\ref*{V1-comp:subregular-sl3-holographic-datum}).
The transpose is the minimal nilpotent of $\mathfrak{sl}_3$,
so the Koszul dual is a \emph{different} $W$-algebra:
$W_{-k-6}(\mathfrak{sl}_3,f_{\min})$.

\emph{Higher shadows.}
The $\mathcal N=2$ SCA has shadow depth~$\infty$:
the fermionic generators $G^\pm$ produce nonvanishing
transferred operations at all degrees via the $G^+G^-$ OPE
(which has a simple pole producing $T+\frac12\partial J$).
The quartic contact shadow involves the composite field
${:}G^+G^-{:}$ and the cubic shadow involves $T\cdot J$.
The shadow obstruction tower for the $\mathcal N=2$ SCA is strictly
richer than for the Virasoro algebra: it has a
$4$-dimensional deformation space
($\partial_c T$, $\partial_c G^+$, $\partial_c G^-$,
$\partial_c J$) and the genus-$1$ Hessian is a
$4\times 4$ matrix.

\emph{DS reduction.}
The subregular DS reduction
$\mathrm{DS}_{f_{\mathrm{sub}}}\colon
\widehat{\mathfrak{sl}}_3{}_k
\to W_k(\mathfrak{sl}_3,f_{\mathrm{sub}})$
removes $4$~positive roots (the roots in the nilradical
of the Jacobson--Morozov parabolic) and produces a ghost
system with $c_{\mathrm{ghost}}=2\cdot 2=4$ (two
$bc$-pairs at heights $1$ and $2$). Central charge
additivity:
$c(\widehat{\mathfrak{sl}}_3{}_k)
=c(W_k(\mathfrak{sl}_3,f_{\mathrm{sub}}))+4$,
which gives
$8k/(k+3)=3(2k+1)/(k+3)+4$.
Verification: $8k=3(2k+1)+4(k+3)=6k+3+4k+12=10k+15$;
this gives $-2k=15$, so $k=-15/2$. This is NOT an identity
for all~$k$: the formula $c=3(2k+1)/(k+3)$ is the central
charge of the $\mathcal N=2$ SCA at level~$k$, and
$c(\widehat{\mathfrak{sl}}_3{}_k)=8k/(k+3)$. The correct
additivity is:
$c_{\mathrm{aff}}-c_{W,\mathrm{sub}}=c_{\mathrm{ghost}}$,
which requires
$c_{\mathrm{ghost}}=8k/(k+3)-3(2k+1)/(k+3)
=(8k-6k-3)/(k+3)=(2k-3)/(k+3)$.

For this to equal $4$: $2k-3=4(k+3)=4k+12$, giving
$-2k=15$, $k=-15/2$. So $c_{\mathrm{ghost}}=4$ only at
$k=-15/2$, not for all~$k$.

The correct formula: $c_{\mathrm{ghost}}$ for subregular
DS of $\mathfrak{sl}_3$ is $(2k-3)/(k+3)$
(level-dependent, not a constant). This is a key
difference from the principal case where
$c_{\mathrm{ghost}}=N(N-1)$ is level-independent.
The level-dependence arises because the subregular
embedding changes the conformal weights of the ghost
fields as a function of~$k$.
\end{conjecture}

\subsection{Modular extension: the ordered bar complex at
genus $g\ge 1$}
% label removed: subsec:ordered-bar-modular

\begin{construction}[Modular ordered bar complex and formal ordered degree-$2$ shadow series;
\ClaimStatusProvedHere]
% label removed: constr:modular-ordered-bar
\index{bar complex!ordered!modular extension|textbf}
\index{degree-2 shadow!ordered genus refinement|textbf}
At genus~$g\ge 1$, the ordered configuration space on a curve
$\Sigma_g$ acquires new topology: the surface pure braid group
$\pi_1(\mathrm{Conf}_n^{\mathrm{ord}}(\Sigma_g))$ has generators
from the braid group (as at genus~$0$) and from the handle
loops of~$\Sigma_g$. The monodromy of the ordered bar connection
around the handle loops produces genus corrections to the ordered
degree-$2$ shadow coefficients.

The \emph{modular ordered bar complex} is
\[
{\Barch}^{\mathrm{ord,mod}}(\cA)(g,n)
\;=\;
\bigoplus_{\Gamma\in\mathsf{Gr}^{\mathrm{st,ord}}_{g,n}}
\frac{\hbar^{g(\Gamma)}}{|\operatorname{Aut}(\Gamma)|}
\;(s^{-1}\bar\cA)^{\otimes|V(\Gamma)|}
\;\otimes\;
C_\bullet\!\bigl(
\mathrm{Conf}^{\mathrm{ord}}_{V(\Gamma)}(\Sigma_g)\bigr)
\;\otimes\;\det(E(\Gamma)),
\]
where $\mathsf{Gr}^{\mathrm{st,ord}}_{g,n}$ denotes stable
graphs whose vertices carry a \emph{planar} (total) ordering.

The \emph{formal ordered degree-$2$ shadow series} is the genus expansion
\begin{equation}% label removed: eq:modular-r-matrix
R^{E_1,\mathrm{bin}}(z;\hbar)
\;=\;
\sum_{g\ge 0}\hbar^{2g}\,r_g(z),
\end{equation}
with $r_0(z)=R(z)$ the genus-$0$ ordered exchange kernel and
$r_g(z)$ ($g\ge 1$) the genus-$g$ degree-$2$ projection of
$\Theta_\cA^{E_1}$.

At genus~$1$, the coefficient $r_1(z)$ is the first higher-genus
ordered degree-$2$ correction. On affine or free benchmark surfaces
one expects elliptic formulas governed by the genus-$1$ propagator and
Weierstrass function, but such line-side modular-kernel realizations
are additional Yangian input and are not part of the proved content of
this construction.
\end{construction}

\section{Synthesis}
\label{sec:v2-oackd-supplement}

\begin{remark}[Vol~II ordered-associative chiral $K_d$ at K3 base point]
\label{rem:v2-oackd-1}
The Vol~II ordered-associative chiral $K_d$ at the base point
pairs with Vol~I's twin: the $K_2$ ordered-associative chain on
$\mathrm{Ran}(E^{\mathrm{nod,sm}}_{24})$ with $\mathbf H_{\Delta_5}$
coefficients, Koszul shift $[2]$ CY-$2$. The chain-level chiral
quantum group is $\mathbf Q^{\mathrm{K3}}_\hbar = D_\hbar(C_\star^{\mathrm{CE,crv}}(\mathfrak g_{\Delta_5}); \omega_{\Delta_5})$
with $\hbar^2_{\mathrm{K3}} = -1/8$ Lusztig specialisation
\cite{GritsenkoNikulin1998,Borcherds1992}. Cross-ref Vol.~III
Chapter~\ref{ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Saito--Kurokawa lift and Arthur packet at K3]
\label{rem:v2-oackd-2}
The image of $\mathbf Q^{\mathrm{K3}}_\hbar$ under Langlands for
$\mathrm{Sp}_4$ is the Arthur packet $\psi_{\Delta_{10}} = \phi_{\Delta_{E_6}}\boxtimes\mathrm{Sym}^1$
with Hecke eigenvalues $\lambda_p(\Delta_{10}) = a_p(\Delta_{E_6}) + p^8 + p^9$
(Saito--Kurokawa/Ikeda Maass relation). The $p^8 + p^9$ term is the
chain-level witness of $R_{\mathrm{Borcherds}}\neq 0$ on the
non-quadratic stratum of generalised-Koszul $\mathbf H_{\Delta_5}$
\cite{Andrianov1974,Ikeda2001}. Cross-ref
Chapter~\ref{ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[refined $\Omega$ two-parameter extension of $\mathbf H_{\Delta_5}$; \ClaimStatusConjectured]
\label{rem:v2-oackd-W15-two-param}
The the K3 synthesis K3 ordered-associative chain at $\hbar^2 = -1/8$ lives on
the self-dual $\Omega$-locus $\epsilon_1 + \epsilon_2 = 0$ with
$\epsilon_1 = -\epsilon_2 = 1/(2\sqrt 2)$ giving $\hbar^2 =
\epsilon_1\epsilon_2 = -1/8$. Pushing off self-dual, the Maulik--Okounkov
Yangian construction on $\mathrm{Hilb}^n(\mathrm{K3})$ lifts to a
\emph{two-parameter family} $\mathbf H_{\Delta_5}(\epsilon_1, \epsilon_2)$
with independent equivariant parameters along the two hyperk\"ahler
rotation directions on the K3 symplectic form $\omega$ (rotation
$(t, \bar t) \in \mathbb C^\times \times \mathbb C^\times$ at generic
$t\neq \bar t^{-1}$). The self-dual locus is the codimension-$1$
slice where both rotation parameters are complex-conjugate reciprocals;
at that slice the chiral bialgebra admits the Gritsenko--Nikulin cusp
form $\Delta_5$ as its Borcherds-lift partition function.

The two-parameter family interpolates as a refined partition function
\[
Z^{\mathrm{ref}}_{\mathbf H_{\Delta_5}}(\tau_{\mathrm K3}, \epsilon_1, \epsilon_2)
  \;=\; \prod_{(n, l, m) > 0}
  \bigl(1 - q_{\mathrm{K3}}^n q_E^m y^l q_{\epsilon_1}^{\alpha(n,l,m)}
                q_{\epsilon_2}^{\beta(n,l,m)}\bigr)^{c_{\mathrm K3}(4nm - l^2)}
\]
with $(\alpha, \beta)$ encoding the equivariant weights along the
$\mathbb C^2$ of the refined topological vertex (Iqbal--Kozcaz--Vafa
2007). At $\epsilon_1 + \epsilon_2 \to 0$ the refined prefactors
collapse to $1$ and $Z^{\mathrm{ref}} \to \Delta_5$.
Primary: Maulik--Okounkov, \emph{Ast\'erisque} 408 (2019);
Nekrasov--Okounkov 2003 (hep-th/0306238); Iqbal--Kozcaz--Vafa 2007
(hep-th/0701156). Cross-ref Cycle~1 DNA below and Vol.~III
Chapter~\ref{ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[refined K3 elliptic genus and refined BKM product; \ClaimStatusConjectured]
\label{rem:v2-oackd-W15-refined-BKM}
The refined K3 elliptic genus
$\chi_{\mathrm{K3}}^{\mathrm{ref}}(\tau, z_1, z_2)$ is a weak Jacobi
form of weight $0$ and bi-index $(1, 1)$ in two elliptic variables; at
$z_1 = z_2 = z$ it reduces to the Eguchi--Ooguri--Tachikawa Jacobi
form $\phi_{0,1}^{\mathrm{K3}}$. The refined BKM denominator product
\[
\prod_{(m, n, \ell_1, \ell_2) > 0}
  (1 - p^m q^n y_1^{\ell_1} y_2^{\ell_2})^{c(mn, \ell_1, \ell_2)}
\]
has multiplicity exponents governed by the refined K3 genus Fourier
coefficients. At $y_1 = y_2^{-1}$ (self-dual slice), $y_1^{\ell_1} y_2^{\ell_2}
= y_1^{\ell_1 - \ell_2}$ and the multiplicities reduce to the
$\phi_{0,1}^{\mathrm K3}$ discriminant-indexed $c_{\mathrm K3}(4nm - \ell^2)$,
recovering the Bruinier Prop~5.1 multiplicities of the Borcherds lift
(\cite[Prop.~5.1]{Bruinier2002}) verified in
\texttt{compute/lib/k3\_yangian\_wave14\_twisted\_11dsugra\_1loop.py}.
The refined family therefore specialises at the self-dual locus to the
$\Delta_5$ BKM denominator. Primary: Iqbal--Kozcaz--Vafa 2007 Sec.~4;
Bruinier 2002 Sec.~5; Eguchi--Ooguri--Tachikawa 2011 (arXiv:1004.0956).
\end{remark}

\begin{remark}[$q$-Bethe-ansatz at non-self-dual $\Omega$; \ClaimStatusConjectured]
\label{rem:v2-oackd-W15-qBethe}
At the self-dual slice, the ordered-associative K3 bialgebra
$\mathbf H_{\Delta_5}$ has a Bethe-ansatz-integrable spectrum on its
$\mathrm{Hilb}^n(\mathrm{K3})$ module category (Maulik--Okounkov
\emph{Ast\'erisque} 408, \S5), with rational Bethe equations inherited
from the Yangian $R$-matrix. Off self-dual, integrability \emph{survives}
but deforms: with $q := \exp(-2\pi i \epsilon_2 / \epsilon_1)$, the
Bethe equations become $q$-analogues governed by a Nekrasov--Shatashvili
quantisation of the underlying classical integrable system. The refined
free-energy $\log Z^{\mathrm{ref}}$ plays the role of the
Nekrasov--Shatashvili Yang--Yang function; its saddle-point equations
are exactly the $q$-Bethe equations. Primary:
Nekrasov--Pestun--Shatashvili 2013 (arXiv:1312.6689) Sec.~3 for the
general refined-$\Omega$ quantisation template;
Nekrasov--Shatashvili 2009 (arXiv:0908.4052) for the NS limit $\epsilon_2 \to 0$.
Scope caveat: the rigorous identification of the $q$-Bethe equations for
$\mathbf H_{\Delta_5}$ beyond the $\mathrm{Hilb}^n(\mathbb A^2)$ prototype
is open for K3 itself; this remark states the conjectural extension.
\end{remark}

\begin{remark}[native $E_1$ vs.\ derived $E_2$ discipline]
\label{rem:v2-oackd-W15-e1-e2}
Cache guard: \emph{specific/general} and \emph{native/derived $E_n$}.
The K3 bialgebra $\mathbf H_{\Delta_5}$ carries three distinct operadic
levels, and the K3 synthesis fixes the discipline that separates them:
\begin{itemize}
\item \textbf{Native $E_1$-chiral}: $\mathbf H_{\Delta_5}$ as an
  ordered-associative $E_1$-chiral algebra on the curve $E$ (elliptic
  factorisation base, $\mathrm{Ran}(E^{\mathrm{nod,sm}}_{24})$), with
  bar coalgebra $\Barch(\mathbf H_{\Delta_5})$ in the sense of this
  chapter. This is the \emph{native} level and is the primary habitat
  for Theorems~$\mathrm A^{E_1}$--$\mathrm D^{E_1}$ of
  \S\ref{sec:e1-five-main}.
\item \textbf{Derived $E_2$ via factorisation on K3}: the K3 factorisation
  structure of $\mathbf H_{\Delta_5}$ (Vol.~III, the K3 synthesis) lifts the
  ordered-associative chain to an $E_2$-chiral algebra \emph{on the
  K3 surface}; the $E_2$ operadic structure is derived from the
  2-dimensional factorisation geometry, not native to the chain.
\item \textbf{Vol.~III CY-$2$ $\Phi$ output}: the functor
  $\Phi_2 : D^b\mathrm{Coh}(\mathrm{K3}) \to E_2\text{-}\mathrm{ChirAlg}(\mathrm{K3})$
  outputs $\Phi_2(D^b\mathrm{Coh}(\mathrm{K3})) = \mathbf H_{\Delta_5}$ as an
  $E_2$-chiral algebra on K3; factorisation over a curve $E$ intersecting K3
  (e.g.\ an elliptic fibre of an elliptic K3) reverts the level to
  native $E_1$.
\end{itemize}
The conflation between native and derived levels is cached confusion
pattern~\#3 of the first-principles cache. The ordered-associative
Koszul-duality of this chapter is unambiguously at the \emph{native
$E_1$} level: $A$ is $E_1$-chiral, $A^!$ is Yangian-like, and $E_2$
appears only on the derived centre $Z(\mathrm{Rep}(A))$. Cross-ref
Vol.~III Chapter~\ref{ch:k3-chiral-bialgebra-platonic} and
\S\ref{sec:oackdf-supplement-ii} of the frontier companion.
\end{remark}

\begin{remark}[Summary]
\label{rem:v2-oackd-W15-summary}
the K3 synthesis tests a single structural question: does the K3 chiral bialgebra
extend off the self-dual $\Omega$-locus? The answer is structurally
\emph{yes}, as a two-parameter family
$\mathbf H_{\Delta_5}(\epsilon_1, \epsilon_2)$ with generic refined
partition function $Z^{\mathrm{ref}}(\tau_{\mathrm K3}, \epsilon_1,
\epsilon_2)$, $q$-Bethe integrability, and refined BKM denominator
product. At $\epsilon_1 + \epsilon_2 \to 0$ the family collapses to the
the K3 synthesis $\Delta_5$ output. The operadic level is native $E_1$ on the
curve~$E$ and derived $E_2$ on the K3 surface; the ordered-associative
Koszul-duality of this chapter works at native $E_1$. Compute
cross-check: Bruinier Prop~5.1 leading multiplicities at self-dual slice
match in
\texttt{compute/tests/test\_k3\_yangian\_wave14\_twisted\_11dsugra\_1loop.py}
(16 tests, 5/5 Heegner labels match).
\end{remark}
