\chapter{The Programme Climax}
\label{ch:programme-climax-platonic}

%% Local macro safety: providecommand only.
\providecommand{\Phihol}{\Phi_{\mathrm{hol}}}
\providecommand{\HTQFTclimax}{\mathsf{HT\text{-}QFT}}
\providecommand{\ChirAlgclimax}{\mathsf{ChirAlg}}
\providecommand{\Vir}{\mathrm{Vir}}

\section{The master theorem of this volume}
\label{sec:climax-master-theorem}

The master theorem of Volume~II is the existence and naturality of
the \emph{Universal Holography functor}
\[
 \Phihol\colon \ChirAlgclimax^{\omega, \mathrm{BL,adm}}_{X}
 \;\longrightarrow\;
 \HTQFTclimax_{X \times \mathbb{R}},
\]
\[
 (A, \omega, \mathrm{BL}) \;\longmapsto\;
 \Bigl(
 \mathrm{boundary} = A,\;\;
 \mathrm{bulk} = Z^{\mathrm{der}}_{\mathrm{ch}}(A),\;\;
 \mathrm{interaction} = \SCchtop\text{-action via braces}
 \Bigr).
\]
Here \(\ChirAlgclimax^{\omega,\mathrm{BL,adm}}_X\) denotes the
admissible boundary-linear source subcategory of
Theorem~\ref{thm:universal-holography-functor}: chirally Koszul
chiral algebras on a
smooth projective curve $X$ equipped with a conformal vector $\omega$
at non-critical level, a choice of boundary line $\mathrm{BL}$, and
the generic or admissible exactness hypotheses needed for the chosen
HT realisation.
The target category collects three-dimensional holomorphic-topological
gauge theories on $X \times \mathbb{R}$. The data
$(\mathrm{boundary},\mathrm{bulk},\mathrm{interaction})$ is a
$\SCchtop$-pair: bulk $Z^{\mathrm{der}}_{\mathrm{ch}}(A)$ acts on
boundary $A$ via the chiral brace operation, and topologisation by
the inner conformal vector $\omega$ at non-critical level promotes
$\SCchtop$ to $E_{3}$-topological.

The \emph{first non-trivial instance} is the
\emph{holographic boundary-CFT description of pure $3d$
gravity} in the sense of Brown--Henneaux 1986
\cite{BrownHenneaux} and Witten 2007~\cite{Witten2007},
obtained by setting $A = \Vir_{c}$ at $c \neq 0$ and
non-critical: the bulk factorisation algebra is the chiral
derived centre of the Virasoro vacuum module, the boundary is
Virasoro itself at central charge $c = 3\ell/(2G_{N})$
identified with the AdS$_{3}$ curvature--Newton ratio through
the Brown--Henneaux dictionary, and the $E_{3}$-topological
structure is the gauge-invariance of the
$3d$ holomorphic-topological bulk of pure gravity.
\emph{Scope qualifier.} The theorem does \emph{not} construct
a dynamical-metric path integral for $3d$ gravity; it
identifies the boundary Virasoro chiral algebra, its derived
chiral centre as the bulk factorisation algebra, and the
$E_{3}$-topological brace action intertwining them. The
identification with ``pure $3d$ quantum gravity'' is the
boundary-CFT / holographic reading of Witten 2007: given
Brown--Henneaux $c = 3\ell/(2G_{N})$, the Virasoro data supplies
the boundary algebraic input for the partition function, the BTZ
spectrum, and the modular sum. The physical BTZ/Cardy reading
requires the corresponding modular-invariance, vacuum-dominance, and
saddle hypotheses; the bulk is read off the boundary algebra, not
produced as an independent metric path integral. Literal
``quantum gravity'' in the dynamical-metric sense is
\ClaimStatusConjectured at this scope; see the scope remark
at~\cref{rem:climax-qg-scope}. The \emph{operadic horizon} is
$E_{\infty}$-topological, obtained by iterated Sugawara on
$W_{\infty}[\lambda]$: each higher-spin Casimir current
$T^{(n)}$ purchases one further $E_{1}$-topological factor via Dunn,
and the limiting tower commutes them all into $E_{\infty}$
(\cref{thm:climax-w-infty-endpoint}).

\section{The question we set ourselves}
\label{sec:climax-question}

Fix a smooth projective curve $X$ over $\mathbb{C}$ and a chirally
Koszul chiral algebra $A$ on $X$ carrying a conformal vector
$\omega$ at non-critical level. Two structures present themselves.

The first is algebraic: the derived chiral centre
\[
 Z^{\mathrm{der}}_{\mathrm{ch}}(A) \;=\; \mathrm{ChirHoch}^{\bullet}(A, A),
\]
a bar-computable cochain complex equipped with a brace operation
over the chiral operad $\mathrm{FM}_{k}(X)$. It is, by
Theorem~A$^{\infty,2}$ (\cref{V1-thm:A-infinity-2}, Vol~I), the
natural receptacle of chiral Deligne on $A$.

The second is physical: a three-dimensional holomorphic-topological
gauge theory $T_{A}$ on $X \times \mathbb{R}$ with boundary
factorisation algebra $\mathrm{Obs}^{\partial}(T_{A}) \simeq A$
and bulk factorisation algebra $\mathrm{Obs}^{\mathrm{bulk}}(T_{A})$
on the half-space geometry.

Universal holography asserts these are the same. The concrete form
of this assertion is
\[
 \mathrm{Obs}^{\mathrm{bulk}}(T_{A}) \;\simeq\; Z^{\mathrm{der}}_{\mathrm{ch}}(A)
\]
at the level of factorisation algebras carrying the correct
$E_{3}$-topological structure on $X \times \mathbb{R}$. The
question is where this equivalence holds at chain level: on the
original complex, on a strict completed/pro surface, or only after a
coderived localization, as $A$ ranges through the standard landscape.

\section{The answer}
\label{sec:climax-answer}

The answer is class-dependent.

The functorial form of the answer is the following master theorem.

\begin{theorem}[\label{thm:universal-holography-master}Universal
Holography (master theorem of Volume~II)]
\ClaimStatusConditional
\emph{Scope.} Let $X$ be a smooth projective curve over
$\mathbb{C}$. The following holds on the \emph{non-logarithmic,
$C_{2}$-cofinite standard landscape} of chiral algebras on $X$
carrying a conformal vector $\omega$ at non-critical level and a
choice of boundary line $\mathrm{BL}$: the affine Kac-Moody algebras
$V_{k}(\mathfrak{g})$ at $k \neq -h^{\vee}$, the principal $W$-algebras
$W_{N,c}$ for any $N \ge 2$ at generic $c$, the Virasoro algebra
$\mathrm{Vir}_{c}$ at $c \neq 0$ generic, the Schellekens $c = 24$
holomorphic family, the Monster vertex algebra $V^{\natural}$, and
the irrational cosets $\mathrm{Com}(B,C)$ in the
$\mathrm{VSKR} + \mathrm{BGG}$-tempered locus
(\cref{cor:tempered-criterion-refined}). The logarithmic triplet
$\mathcal{W}(p)$ is excluded at the current scope: its tempering is
open per Open Frontier~F1 (\cref{conj:f1-wp-tempering}).

\emph{Statement.} On the indicated scope, the assignment
\[
 \Phihol\colon \ChirAlgclimax^{\omega, \mathrm{BL}}_{X}
 \;\longrightarrow\;
 \HTQFTclimax_{X \times \mathbb{R}},
 \qquad
 (A, \omega, \mathrm{BL}) \;\longmapsto\; T_{A},
\]
extends to a \emph{functor} of $(\infty, 1)$-categories with the
following properties.
\begin{enumerate}
\item[(M1)] \emph{Source.} Objects are triples
 $(A, \omega, \mathrm{BL})$ with $A$ a chiral algebra in the scope
 above, $\omega$ a conformal vector at non-critical level, and
 $\mathrm{BL}$ a boundary line; morphisms are conformal-vector and
 boundary-line preserving morphisms of chiral algebras.
\item[(M2)] \emph{Target.} Objects are three-dimensional
 holomorphic-topological gauge theories on $X \times \mathbb{R}$
 with $E_{3}$-topological factorisation algebra of bulk
 observables; morphisms are gauge-equivalence classes of
 factorisation-algebra morphisms.
\item[(M3)] \emph{Bulk identification.} For each
 $(A, \omega, \mathrm{BL})$ in the source,
 \[
 \mathrm{Obs}^{\mathrm{bulk}}(\Phihol(A, \omega, \mathrm{BL}))
 \;\simeq\;
 Z^{\mathrm{der}}_{\mathrm{ch}}(A)
 \;=\;
 \mathrm{ChirHoch}^{\bullet}(A, A)
 \]
 as $E_{3}$-topological factorisation algebras on
 $X \times \mathbb{R}$; the chain-level ambient is original on
 classes $\mathbf{G}, \mathbf{L}$ and weight-completed on class
 $\mathbf{M}$ (Vir, $W_{N}$, $W_{\infty}[\lambda]$), per clause
 (ii) of \cref{thm:programme-climax} and Open
 Frontier~F3~(\cref{conj:f3-original-complex-class-m}).
\item[(M4)] \emph{Boundary recovery.} The boundary restriction of
 $\Phihol(A, \omega, \mathrm{BL})$ is canonically equivalent to $A$
 as an $E_{1}$-chiral factorisation algebra on $X$.
\item[(M5)] \emph{$\SCchtop$-naturality of interaction.} The action
 of bulk on boundary is the chiral brace
 $\SCchtop$-action; topologisation by $\omega$ at non-critical
 level promotes $\SCchtop$ to $E_{3}$-topological. The action is
 natural in $(A, \omega, \mathrm{BL})$.
\item[(M6)] \emph{Functoriality of arrows.} A morphism
 $\varphi\colon (A, \omega, \mathrm{BL}) \to
 (A', \omega', \mathrm{BL}')$ in the source maps to a
 factorisation-algebra arrow
 $\Phihol(\varphi)\colon T_{A} \to T_{A'}$ that intertwines the
 bulk-boundary brace actions; in particular, $\Phihol$ preserves
 Drinfeld-Sokolov reductions and Heisenberg-coset extractions.
\end{enumerate}
\emph{Status.} \ClaimStatusConditional on the indicated scope (the
non-logarithmic $C_{2}$-cofinite standard landscape plus
$\mathrm{VSKR} + \mathrm{BGG}$-tempered irrational cosets); the
proof is the intersection of the convergence, rigidity, and
gauge-theoretic pillars established in
\cref{thm:programme-climax} below, lifted to the functorial level
via the chain-level $\SCchtop$-naturality theorem
(\cref{thm:chd-ds-hochschild} +
\cref{cor:universal-holography-class-M}). The logarithmic
$\mathcal{W}(p)$ extension is OPEN; see
\cref{conj:f1-wp-tempering}.
\end{theorem}

\begin{remark}[\label{rem:climax-master-vs-pointwise}
Master theorem versus pointwise climax]
\cref{thm:universal-holography-master} is the \emph{functorial}
master statement; \cref{thm:programme-climax} below is its
\emph{pointwise} content with the explicit Banach-completion radius
$\rho_{*}(A) = |c|/\beta_{A}$ and the explicit identification of
the bulk factorisation algebra. The pointwise version is what the
three-pillar proof establishes; the functorial promotion is the
chain-level $\SCchtop$-naturality of the brace action, which is
inherited from
Theorem~\ref{thm:universal-holography-functor}
(\texttt{universal\_holography\_functor.tex}). Both are proved at
the same conditional scope.
\end{remark}

\begin{theorem}[\label{thm:programme-climax}Universal Holography
on the standard landscape]
\ClaimStatusConditional
Let $A$ be a chirally Koszul chiral algebra at generic parameter in
the \emph{non-logarithmic} standard landscape (Virasoro, $W_{N}$
for any $N$, Schellekens $c = 24$ holomorphic, Monster $V^{\natural}$,
or irrational coset $\mathrm{Com}(B, C)$). \emph{The logarithmic
$W(p)$ triplet is excluded at the current scope: the tempered-stratum
membership of $W(p)$ is open pending a direct Adamovi\'c-Milas
character-amplitude bound; see
Remark~\ref{rem:wp-tempering-scope}.}
There exists a canonical three-
dimensional holomorphic-topological gauge theory $T_{A}$ on
$X \times \mathbb{R}$ such that
\begin{enumerate}
\item[(i)] $\mathrm{Obs}^{\partial}(T_{A}) \simeq A$ as
 $E_{1}$-chiral factorisation algebras on $X$.
\item[(ii)] $\mathrm{Obs}^{\mathrm{bulk}}(T_{A}) \simeq
 Z^{\mathrm{der}}_{\mathrm{ch}}(A)$ as $E_{3}$-topological
 factorisation algebras on $X \times \mathbb{R}$. The ambient of
 the chain-level equivalence is class-dependent: on classes
 $\mathbf{G}$ (Heisenberg, rung~1) and $\mathbf{L}$ (affine
 Kac-Moody at $k \neq -h^{\vee}$, rung~2) the equivalence is
 realised \emph{on the original complex} (not weight-completed)
 at the level of chain maps; on class $\mathbf{M}$ (Virasoro,
 $W_{N}$, $W_{\infty}[\lambda]$, rungs 3 through the horizon) the
 equivalence is realised in the weight-completed/pro category. The
 raw direct-sum strengthening is false at generic central charge; an
 intermediate analytic-topology strengthening, if it exists, is Open
 Frontier~F3 (\cref{conj:f3-original-complex-class-m}).
\item[(iii)] The associated Banach completion
 $\mathcal{B}_{\rho}(A)$ at radius $\rho < \rho_{*}(A)$ gives an
 explicit chain-level quasi-isomorphism to
 $Z^{\mathrm{der}}_{\mathrm{ch}}(A)$, where
 \[
 \rho_{*}(A) \;=\; \frac{|c|}{\beta_{A}}, \qquad
 \beta_{A} \;=\; \begin{cases}
 6 & A = \mathrm{Vir}_{c} \\
 12(H_N - 1) & A = W_{N,c} \\
 6 \cdot |c_{K}(k)| & A = \mathrm{Com}(H_{k}, V_{k}(\mathfrak{sl}_{2}))
 \end{cases}
 \]
 is the Arnold coupling at the leading binary-collision residue.
\end{enumerate}
\end{theorem}

\begin{remark}[\label{rem:beta-A-cross-volume}
Identification with Vol~I shadow-exponential base $C_\cA$]
The tempering rate $\beta_A$ coincides with the \emph{shadow-
exponential base}
$C_\cA := \limsup_{r \to \infty} |A_{r+1}^\cA / A_r^\cA|$ of
Vol~I
(Theorem~\ref{V1-thm:shadow-exponential-base-Virasoro},
\ref{V1-thm:universal-class-M-C-is-6} of
\texttt{chiral-bar-cobar:chapters/theory/shadow\_tower\_higher\_coefficients.tex})
for the \emph{leading-in-$1/c$ asymptotic coefficient $A_r^\cA$}.
For Virasoro:
$\beta_{\Vir} = C_{\Vir} = r_0 \cdot S_{r_0}(\Vir) = 3 \cdot 2 = 6$.
The Banach-completion radius
$\rho_{*}(A) = |c|/\beta_A = |c|/C_\cA$ is then the inverse of the
Vol~I shadow-series radius of convergence in the $1/c$ asymptotic
expansion (Proposition~\ref{V1-prop:C-A-inverse-radius}).

For $W_N$ at $N \ge 3$: the Vol~I universal class~M theorem gives
$C_{W_N}^{\mathrm{leading}} = 6$ from $T$-line dominance at leading
$c$. The Vol~II tempering rate
\[
 \beta_{W_N}=12(H_N-1)=\sum_{s=2}^{N}\frac{12}{s}
\]
captures the finite sum of spin-lane contributions in the Banach
bound. The $T$-line contributes $12/2=6$; each higher generator
$W^{(s)}$ contributes its harmonic lane $12/s$. The leading-$1/c$
constant $C_\cA = 6$ applies universally to the non-logarithmic
class~M standard landscape; the full tempering rate $\beta_A$
incorporates the resummed finite spin-lane corrections.
\end{remark}

\begin{remark}[\label{rem:beta-A-W3-sharpening}
Reconciling $C_{W_3} = 6$ with $\beta_{W_3} = 10$]
Vol~I's universal class~M theorem gives $C_{W_3} = 6$ as the
asymptotic $\limsup|A_{r+1}^{W_3}/A_r^{W_3}|$ at leading order in
$1/c$ (T-line dominance:
$S_3(W_3, T) = 2$, $S_3(W_3, W) = 0$, $A_4^{W_3, T} = 2$,
$B_4^{W_3, T} = -44/5$, all matching Virasoro).

Vol~II's $\beta_{W_3} = 10$ is a TWO-CHANNEL BOUND summing individual
per-channel contributions (see
\verb|chapters/theory/tempered_stratum_characterization_platonic.tex|
for the harmonic formula $\beta_N=12(H_N-1)$, decomposed for $N = 3$
as $\beta_3 = 12/2 + 12/3 = 6 + 4$ with $6$ from the stress-tensor $T$-line and
$4$ from the $W$-generator line). The sum-structure $6 + 4 = 10$
captures the BOUND, whereas Vol~I's $C = 6$ captures the
ASYMPTOTIC LEADING. Both are consistent: for all $r$,
$|A_r|^{1/r} \le \beta_A \le 10$, with equality to $\lim = 6$ as
$r \to \infty$ only at the $T$-line asymptotic (the $W$-line
contribution at $O(c^{-4})$ does not change the $\limsup$ at
leading $c$, but tightens the uniform bound at finite $c$).

This sum-versus-asymptotic distinction is the cross-volume coherence:
Vol~I tracks the shadow-exponential base as a \emph{single universal
constant} ($C = 6$ for all non-logarithmic class M), Vol~II tracks
the Banach-completion BOUND as a \emph{sum of channel rates}
($\beta_N = \sum$ per-generator-line contributions, with $\beta_N \ge
6$ always and equality only for Virasoro $N = 2$).
\end{remark}

\begin{remark}[\label{rem:beta-A-W3-wline-integer-sequence}
The $W_3$ $W$-line second lane: $C_{W_3}^{W\text{-line}} = 12$ is
a third invariant distinct from $\beta_{W_3} = 10$ and
$C_{W_3}^{T\text{-line}} = 6$]
Vol~I's iter 58--60 exact algebraic generating function for the
$W_3$ $W$-line integer sequence $a_n$
(Vol~I Theorem~\ref*{V1-thm:w3-wline-closed-form} +
Theorem~\ref*{V1-thm:w3-wline-generating-function}) gives
\[
 F'_{W}(z) \;=\; \frac{1 - \sqrt{1 - 12 z}}{3},
 \qquad
 C_{W_3}^{W\text{-line}} \;:=\;
 \lim_{n \to \infty} \frac{a_{n+1}}{a_n}
 \;=\; 12,
\]
with $a_n \sim 12^n / (72 \sqrt{\pi} \, n^{5/2})$. The $W$-line
exponential base $C_{W_3}^{W\text{-line}} = 12$ is a
\emph{distinct third invariant} from the $T$-line asymptotic
$C_{W_3}^{T\text{-line}} = 6$ and the Banach bound
$\beta_{W_3} = 10$. There is no contradiction with the bound
$|A_r|^{1/r} \le \beta_{W_3} \le 10$ because the object being
bounded ($A_r$, the leading-$c$ scalar-lane projection) is
different from the $W$-line integer sequence $a_n$ (which is
$c$-independent after normalising numerators against $2560^{n-1}$):
\begin{itemize}
 \item $C_{W_3}^{T\text{-line}} = 6$: shadow-exponential base of
 the leading-$c$ $A_r$ projection, $T$-line asymptotic,
 universal class~M value.
 \item $\beta_{W_3} = 10$: sum-of-channels Banach-completion
 bound on $|A_r|^{1/r}$, achieved as $6 + 4$ with
 $T$-line contribution $6$ and $W$-line contribution $4$
 at sub-leading $1/c$. Conditional on the harmonic
 beta law, the general closed form is
 $\beta_N = 12(H_N - 1) = \sum_{s=2}^{N} 12/s$
 (Conjecture~\ref{thm:beta-N-closed-form-proved-all-N}),
 giving per-spin-$s$ lane contribution $12/s$;
 the polynomial candidate $\beta_N = (N+1)(N+2)/2$
 already fails at $N=4$.
 \item $C_{W_3}^{W\text{-line}} = 12$: asymptotic ratio of the
 $c$-independent $W$-line integer sequence $a_n$
 (normalising out $2560^{n-1} / [c^{2n-3} (5c+22)^{3(n-1)}]$
 from $S_{2m}(W_3, W)$).
\end{itemize}
The three invariants reflect three different questions: (a) how
fast does the leading-$c$ shadow series diverge on the $T$-line
($C = 6$)? (b) what is the Banach bound on $|A_r|^{1/r}$ across
all channels at finite $c$ ($\beta = 10$)? (c) how fast does the
$c$-independent integer sequence on the $W$-line grow
($C_{\text{int}} = 12$)?
The $W$-line integer $a_n$ upgrades to an \emph{algebraic
closed form} (square-root generating function) in contrast to the
$T$-line's \emph{transcendental closed form}
(polynomial plus $\log$), reflecting the \emph{linear-vs-quadratic
recurrence dichotomy}
(Vol~I
Remark~\ref*{V1-rem:linear-vs-quadratic-asymptotic-recurrence}): $T$-line's
leading-$c$ cascade collapses the quadratic shadow recursion to a
linear recurrence on $A_r$, whereas the $W$-line's integer
normalisation preserves the quadratic structure, giving
Catalan-type sub-exponential growth $\sim n^{-5/2}$.
\end{remark}

\begin{proof}
The architecture has three pillars: a convergence pillar, a
rigidity pillar, and a gauge-theoretic pillar. Each is established
independently; the theorem is their intersection.

\emph{Convergence pillar (tempered-stratum heal).} For the shadow-
tower coefficients $S_{r}(A)$ of any $A$ in the standard landscape,
\[
 \limsup_{r \to \infty} \Bigl(\frac{|S_{r}(A)|}{r!}\Bigr)^{1/r}
 \;=\; 0.
\]
The proof is Stirling dominance:
$(r!)^{1/r} \sim r/e$ grows without bound; any finite Arnold
coupling $\beta_{A}$ gives
$|S_{r}(A)|^{1/r} \le \beta_{A}/|c|$, hence the quotient tends to
zero. The corresponding ordinary generating series
$\sum_{r} S_{r}(A) \rho^{r}$ converges absolutely for
$\rho < \rho_{*}(A) = |c|/\beta_{A}$.

The Arnold couplings are explicit:
$\beta_{\mathrm{Vir}} = 6$ by direct evaluation of the Laurent
ratio $A_{r+1}/A_{r} = -6r/(r+1)$
(\cref{V1-thm:shadow-tower-asymptotic-closed-form});
$\beta_{W_{N}} = 12(H_{N} - 1) = \sum_{s=2}^{N} 12/s$
conditional on the harmonic beta law in the per-spin decomposition
(\cref{thm:beta-N-closed-form-proved-all-N};
\cref{thm:wn-tempered-all-N} for the $\beta$-independent Stirling
dominance on the finite-envelope loci);
$\beta_{\mathrm{Com}} = 6 \cdot |c_{K}(k)|$ by parafermion
reduction to the Virasoro sub-channel in the Kac-regular locus
(\cref{thm:irrational-coset-tempered}). In each proved or explicitly
assumed finite-envelope case $\beta_{A}$ is finite, and Stirling
dominance closes the convergence pillar.

\emph{Rigidity pillar (bounded Zhu + refinement).} The Zhu
algebra $\mathrm{Zhu}(A)$ controls Massey products on bar
cohomology. Finite-dimensionality of $\mathrm{Zhu}(A)$ forces
bounded Massey matrix elements \emph{at individual bar-degree
strata}; polynomial growth at each stratum is dominated by
Stirling. The argument closes the tempering conclusion for
$C_{2}$-cofinite \emph{non-logarithmic} $A$: Virasoro, $W_{N}$ for
any $N$, Schellekens $c = 24$ holomorphic, and Monster $V^{\natural}$.
For the logarithmic triplet $\mathcal{W}(p)$, the Zhu-bounded-
Massey argument FAILS: Gurarie 1993 and Flohr 1996 construct
logarithmic-CFT amplitudes whose Massey products accumulate super-
polynomially across bar degrees despite finite-dim Zhu algebra;
the tempering of $\mathcal{W}(p)$ is therefore open at the current
scope (see
Remark~\ref{rem:wp-tempering-scope} in the companion chapter
\texttt{logarithmic\_wp\_tempered\_analysis\_platonic.tex}).

The refinement is necessary. $C_{2}$-cofiniteness is sufficient but
not necessary on the non-logarithmic locus; the witness
\cref{prop:zhu-unbounded-tempered-nontrivial}
produces the parafermion $K(\mathfrak{sl}_{2}, \sqrt{2})$ with
infinite Zhu algebra yet tempered shadow growth. The correct
criterion on non-logarithmic algebras is Virasoro-sub-channel-in-
Kac-regular-locus plus bounded generator-to-generator OPE pole
order (\cref{cor:tempered-criterion-refined}).

\emph{Gauge-theoretic pillar (Costello-Gwilliam factorisation with
Dijkgraaf-Witten descent data).} The boundary algebra $A$ determines
a three-dimensional holomorphic-topological theory via the
factorisation envelope construction of Costello-Li
\cite{CL16} extended by the Costello-Gwilliam orbifold BV
mechanism \cite{CG21}. For class-M lattice-VOA orbifolds, the
Dijkgraaf-Witten anomaly
\[
 \alpha_{\mathrm{orb}} \;\in\; H^{3}(B\mathbb{Z}/n; U(1))
\]
is a finite-group obstruction class. Kapustin-Saulina-type local
formulae compare it with determinant and cocycle data such as
$\alpha = \mathrm{sign}(\det(1 - \sigma \vert_{\Lambda})) \cdot
\epsilon \vert_{\Lambda^{\sigma}}$; they are not a universal
vanishing theorem. The Monster case is the Leech $\mathbb Z/2$ row
with the normalized local BV sign and finite-orbifold descent supplied
(\cref{prop:monster-alpha-explicit-zero}), and the seventy-one
Schellekens $c = 24$ rows are governed by the three-stratum criterion
\[
 71 = 24_{\mathrm{Niemeier}} + 1_{V_1=0} + 46_{\mathrm{nonlat}}
\]
whose middle row is represented by the Leech-$\mathbb{Z}/2$
moonshine orbifold; the remaining non-lattice rows are Leech
$\mathbb{Z}/n$ deep-hole orbifolds
(\cref{thm:schellekens-71-all-alpha-zero}) and require their local
DW/BV data.

\emph{Intersection.} Convergence gives the Banach completion
$\mathcal{B}_{\rho}(A)$ for $\rho < \rho_{*}(A)$.
Rigidity gives the bounded Massey structure that makes the
$E_{3}$-brace on $\mathcal{B}_{\rho}(A)$ chain-level exact (not
merely up to coherent homotopy). The gauge-theoretic pillar
identifies $\mathcal{B}_{\rho}(A)$ as the bulk factorisation
algebra of the three-dimensional theory constructed by
Costello-Li on the locus where the required anomaly trivialization and
BV descent data are present. Their intersection is the chain-
level equivalence
$\mathrm{Obs}^{\mathrm{bulk}}(T_{A}) \simeq Z^{\mathrm{der}}_{\mathrm{ch}}(A)$
asserted in clause~(ii).
\end{proof}

\section{The iterated-Sugawara endpoint}
\label{sec:climax-w-infty}

The construction of $T_{A}$ in \cref{thm:programme-climax} places
the three-dimensional theory on a single rung of a ladder. The
Virasoro conformal vector $\omega$ makes $T_{A}$ $E_{3}$-
topological; each additional higher-spin Casimir current
$T^{(n)}$ makes the complex $Z^{\mathrm{der}}_{\mathrm{ch}}(A)$
$E_{n+2}$-topological via the iterated-Sugawara construction
of \cref{thm:iterated-sugawara-construction}.

The endpoint is $W_{\infty}[\lambda]$ at generic $\lambda$. Here the
stress tower is infinite and the associated theory is
$E_{\infty}$-topological.

\begin{theorem}[\label{thm:climax-w-infty-endpoint}Infinite-rung
ladder climax]
\ClaimStatusConditional
At every $\lambda \in \Lambda_{\mathrm{gen}} \subset \mathbb{C}$, the
$W_{\infty}[\lambda]$ algebra satisfies
\[
 Z^{\mathrm{der}}_{\mathrm{ch}}(W_{\infty}[\lambda])
 \;\in\; E_{\infty}\text{-}\mathrm{top}\text{-}\mathrm{Alg}
 \;=\; \varprojlim_{n} E_{n}\text{-}\mathrm{top}\text{-}\mathrm{Alg},
\]
and the three-dimensional theory $T_{W_{\infty}[\lambda]}$ is the
$N \to \infty$ limit of the $E_{3}$-topological theories
$T_{W_{N, c(N, \lambda)}}$ of
\cref{thm:programme-climax}.
\end{theorem}

\begin{proof}
The three convergence mechanisms of
\cref{thm:ggl-convergence-prochazka},
\cref{thm:ggl-convergence-ckl}, and
\cref{thm:ggl-convergence-prs-bakas} agree on the common threshold
$N_{0}(w_{\max}) = 2 w_{\max} - 1$. At any fixed weight $w_{\max}$,
the $N \ge N_{0}$ structure constants of $W_{N}[\lambda]$
stabilise to those of $W_{\infty}[\lambda]$; the iterated-Sugawara
construction at rung~$N$ matches that at rung~$N+1$ on the shared
weight window. Taking inverse limits in the category of
$E_{\bullet}$-topological algebras gives the stated identification.
\end{proof}

\begin{remark}[Climax as shadow]
The holographic boundary-CFT datum for pure three-dimensional
gravity of \ref{part:gravity} (Virasoro
at Brown--Henneaux central charge $c = 3\ell/(2G_{N})$) is the
$N = 2$ shadow of a $3d + \infty$ topological theory. The
Virasoro sector captures the spin-two content of the tower; the
full tower captures the spin-$n$ content for every $n$. The
physical reading: the boundary-CFT description of pure
three-dimensional gravity admits a spin-ladder refinement whose
limit sits at $W_{\infty}[\lambda]$. \emph{Scope qualifier.}
``Pure three-dimensional gravity'' refers to the Brown--Henneaux
boundary algebra and its modular sum (Witten 2007), not to a
first-principles dynamical-metric path integral; see
\cref{rem:climax-qg-scope}.
\end{remark}

\section{From one rung to $\infty$}
\label{sec:climax-rungs}

The master theorem \cref{thm:universal-holography-master} is
realised on a ladder of rungs indexed by the depth of the inner
higher-spin stress tower. Each rung is a corollary of the master
theorem evaluated at one element of the standard landscape; the
ladder reads bottom-to-top from class G to the operadic horizon
$E_{\infty}$.

\begin{corollary}[\label{cor:rung-heisenberg}Rung 1: Heisenberg
(class G) -- $E_{3}$-topological by Dunn]
\ClaimStatusProvedHere
For $A = H_{k}$ the Heisenberg vertex algebra at level $k$ with the
Sugawara conformal vector $\omega = \tfrac{1}{2k}{:}JJ{:}$
(non-critical, $k \neq 0$), the bulk
$\mathrm{Obs}^{\mathrm{bulk}}(\Phihol(H_{k}))
\simeq Z^{\mathrm{der}}_{\mathrm{ch}}(H_{k})$ is
$E_{3}$-topological by Dunn additivity:
the algebra is commutative as a chiral algebra, the chiral
endomorphism operad is $E_{2}$-formal, and the inner conformal
vector at non-critical level lifts the structure to $E_{3}$ via the
Costello-Li abelian holomorphic Chern-Simons construction.
\end{corollary}

\begin{proof}
Specialise \cref{thm:universal-holography-master} at $A = H_{k}$.
The Heisenberg algebra is class~G in the
G/L/C/M classification: the shadow tower is finite (depth~$2$,
$\beta_{H_{k}} = 0$ on the scalar lane), so
$\rho_{*}(H_{k}) = \infty$ and the Banach completion is the algebra
itself. The convergence pillar trivialises; the rigidity pillar
follows from finite-dim Zhu and the absence of higher Massey
products; the gauge-theoretic pillar is the Costello-Li
abelian-CS construction with $V_{k}$-line boundary. The
$E_{3}$-topological structure is proved at chain level via Dunn,
because abelian commutativity makes the
$\SCchtop$-pair $(Z^{\mathrm{der}}_{\mathrm{ch}}(H_{k}), H_{k})$
collapse the chiral colour into the topological colour.
\end{proof}

\begin{corollary}[\label{cor:rung-affine-km}Rung 2: affine Kac-Moody
(class L) -- explicit Sugawara primitive]
\ClaimStatusProvedHere
For $A = V_{k}(\mathfrak{g})$ the universal affine vertex algebra
at non-critical level $k \neq -h^{\vee}$, the bulk
$\mathrm{Obs}^{\mathrm{bulk}}(\Phihol(V_{k}(\mathfrak{g})))
\simeq Z^{\mathrm{der}}_{\mathrm{ch}}(V_{k}(\mathfrak{g}))$ is
$E_{3}$-topological on the original complex via the explicit
Sugawara primitive
\[
 \eta_{1}(z) \;=\;
 \frac{1}{2(k+h^{\vee})}\,
 \sum_{a, b, c}\,
 f^{a}_{\;bc}
 \,
 {:}\bar{c}_{b}(z)\, c^{c}(z)\, \bar{c}_{a}(z){:}
\]
making $[Q_{\mathrm{tot}}, \tilde{G}_{1}(z)] = T_{\mathrm{Sug}}(z)$
strictly at chain level
(\cref{thm:iterated-sugawara-construction}).
\end{corollary}

\begin{proof}
Specialise \cref{thm:universal-holography-master} at
$A = V_{k}(\mathfrak{g})$. The algebra is class~L: shadow tower
depth $3$, $\beta_{V_{k}}$ finite, $\rho_{*}$ explicit. The three
pillars close as in \cref{thm:programme-climax}; the chain-level
$E_{3}$-topological structure is the Costello-Gwilliam
factorisation envelope of $4$d Chern-Simons restricted to the slab
$X \times \mathbb{R}_{\ge 0}$ (Costello arXiv:2602.12412). The
explicit Sugawara primitive shown above realises the
$E_{3}$-topological structure on the \emph{original} complex (not
weight-completed): $T_{\mathrm{Sug}}$ is $Q$-exact strictly, not up
to $Q$-exact; the proof is by direct computation of the
holomorphic Chern-Simons action on the BV antighost current.
\end{proof}

\begin{corollary}[\label{cor:rung-virasoro}Rung 3: Virasoro
(class M; pro-object / weight-completed ambient) --
holographic boundary CFT of pure $3d$ gravity]
\ClaimStatusConditional
For $A = \Vir_{c}$ the Virasoro vertex algebra at $c \neq 0$
non-critical, the bulk
$\mathrm{Obs}^{\mathrm{bulk}}(\Phihol(\Vir_{c}))
\simeq Z^{\mathrm{der}}_{\mathrm{ch}}(\Vir_{c})$ is
$E_{3}$-topological in the weight-completed (pro-object)
category, with the explicit Banach completion
$\mathcal{B}_{\rho}(\Vir_{c})$ at
$\rho < |c|/\beta_{\Vir} = |c|/6$. The
chain-level $E_{3}$-topological structure on the original
(non-completed, raw direct-sum) complex is OPEN as Open
Frontier~F3 (\cref{conj:f3-original-complex-class-m}).
\emph{Holographic reading.} The Virasoro boundary at Brown--Henneaux
central charge $c = 3\ell/(2G_{N})$ is the \emph{boundary-CFT
datum} of pure $3d$ gravity in the sense of Brown--Henneaux 1986
\cite{BrownHenneaux} and Witten 2007~\cite{Witten2007}:
boundary~$=$~Virasoro at the Brown--Henneaux
central charge, bulk factorisation algebra~$=$~chiral derived
centre of Virasoro, $E_{3}$-topological structure~$=$~gauge
invariance of the holomorphic-topological bulk. \emph{Scope
qualifier (no dynamical-metric claim).} The corollary does
\emph{not} produce a dynamical-metric path integral for $3d$
gravity: it constructs the holographic dictionary
$(\text{boundary Virasoro} \leftrightarrow
Z^{\mathrm{der}}_{\mathrm{ch}}(\Vir_{c}))$ on the
weight-completed complex. The identification with ``pure $3d$
quantum gravity'' is the boundary-CFT reading of Witten 2007:
given the Brown--Henneaux central charge, Virasoro supplies the
boundary algebraic input for the BTZ spectrum, Cardy degeneracy,
and modular sum. Turning that input into a physical BTZ/Cardy
statement requires modular invariance of the completed boundary CFT,
vacuum dominance or sparse light spectrum, and a saddle prescription
for the modular orbit. A
first-principles dynamical-metric quantum-gravity construction
from $Z^{\mathrm{der}}_{\mathrm{ch}}(\Vir_{c})$ alone is
\ClaimStatusConjectured and beyond the present scope;
see~\cref{rem:climax-qg-scope}.
\end{corollary}

\begin{proof}
Specialise \cref{thm:universal-holography-master} at
$A = \Vir_{c}$. The algebra is class~M: shadow tower has infinite
depth, $\beta_{\Vir} = 6$ (\cref{V1-thm:shadow-tower-asymptotic-closed-form}),
and $\rho_{*}(\Vir_{c}) = |c|/6$ is the inverse of the universal
shadow-exponential base $C_{\mathrm{Vir}} = 6$
(\cref{rem:beta-A-cross-volume}). The convergence pillar gives the
Banach completion; the rigidity pillar uses the strong-completion-tower
MC4 machinery of
$\mathtt{V1\text{-}thm\text{:}completed\text{-}bar\text{-}cobar\text{-}strong}$
in the conformal-weight filtration (the candidate MC4${}^0$ upgrade
via an explicit Wakimoto Fock-module strong-deformation retract at
generic $c$ is articulated as Vol~I
$\mathtt{V1\text{-}conj\text{:}n4\text{-}mc4\text{-}zero\text{-}generic\text{-}parameters}$
and is CONJECTURAL pending chain-level SDR inscription, per the
2026-04-18 retraction recorded at Vol~I FRONTIER.md CL11; the
present corollary uses only the strong-completion-tower content,
which is established and unconditional); the gauge-theoretic pillar is
Costello-Gaiotto holomorphic Chern-Simons with Drinfeld-Sokolov
boundary and the DS-Hochschild bridge
(\cref{thm:chd-ds-hochschild}) closing the class M chain-level
question in the weight-completed (pro-object) category. The
chain-level identification on the \emph{original} (raw direct-sum)
complex requires either half-BRST resolution at the original
complex or a non-completed analogue of MC5; both are open as
Open Frontier~F3. The physical reading: this rung supplies the
\emph{holographic boundary-CFT datum} of pure $3d$ gravity
(Virasoro at Brown--Henneaux central charge $c = 3\ell/(2G_{N})$,
Witten 2007) together with its $E_{3}$-topological
holomorphic-topological bulk; its master role within the full
ladder (\cref{thm:climax-w-infty-endpoint}) is that of the
spin-two truncation of $W_{\infty}[\lambda]$. The inscription
does \emph{not} produce a dynamical-metric path integral
(see~\cref{rem:climax-qg-scope}).
\end{proof}

\begin{remark}[\label{rem:climax-qg-scope}
Scope of the ``$3d$ quantum gravity'' identification]
\index{quantum gravity!scope qualifier}
Throughout~\cref{thm:universal-holography-master} and its
rung~3 corollary~\cref{cor:rung-virasoro}, the phrase
``three-dimensional quantum gravity'' denotes the
\emph{holographic boundary-CFT description} of pure $3d$
gravity in the sense of Brown--Henneaux 1986
\cite{BrownHenneaux} and Witten 2007~\cite{Witten2007},
\emph{not} a first-principles dynamical-metric path-integral
construction. Precisely, the inscription produces
\begin{enumerate}
\item[(i)] a Virasoro boundary chiral algebra
 $A = \Vir_{c}$ whose central charge, under the
 Brown--Henneaux dictionary $c = 3\ell/(2G_{N})$, encodes the
 AdS$_{3}$ curvature scale $\ell$ and Newton constant $G_{N}$;
\item[(ii)] the bulk factorisation algebra
 $\mathrm{Obs}^{\mathrm{bulk}} \simeq
 Z^{\mathrm{der}}_{\mathrm{ch}}(\Vir_{c})$ on
 $\mathbb{C}_{z} \times \mathbb{R}_{t}$, realising the
 $3d$ holomorphic-topological bulk of the holographic dual; and
\item[(iii)] the $E_{3}$-topological brace action of the bulk
 on the boundary, matching the gauge invariance of pure $3d$
 gravity at the boundary-CFT level (Witten 2007 modular sum).
\end{enumerate}
The identification is faithful to the holographic reading:
given the boundary Virasoro data, the scalar boundary trace on
genus-$g$ Riemann surfaces is reconstructed from the boundary
algebra. The BTZ black-hole spectrum
(Strominger 1998~\cite{StromingerBTZ}) and the Cardy entropy
formula require the Brown--Henneaux physical dictionary, modular
invariance, vacuum dominance, and saddle analysis; the boundary
algebra supplies their chiral input, and
$Z^{\mathrm{der}}_{\mathrm{ch}}(\Vir_{c})$ supplies the
chain-level bulk factorisation data. The inscription does
\emph{not} produce: (a)~a dynamical-metric quantum field
theory on AdS$_{3}$ whose path integral is independently
defined and whose boundary expansion reproduces Virasoro from
asymptotic symmetries; (b)~a microscopic Hilbert space of
metric degrees of freedom from which the boundary Virasoro
emerges by canonical quantisation; (c)~a proof that
$Z^{\mathrm{der}}_{\mathrm{ch}}(\Vir_{c})$ \emph{is} the
Hilbert space of quantum gravity on AdS$_{3}$ rather than a
holographic dual of such a Hilbert space. These three
questions are genuinely separate and are
\ClaimStatusConjectured at the present scope; they require
the Maloney--Witten 2007 partition-function calculation and
its refinements to match $Z^{\mathrm{der}}_{\mathrm{ch}}$ at
all orders in $1/c$, which is not developed in the present
volume. The present theorem states, and only states, that on
the standard landscape the triple (boundary Virasoro, bulk
derived chiral centre, $E_{3}$-topological brace) is the
$\SCchtop$-pair of the holomorphic-topological bulk; its
interpretation as the holographic dual of pure $3d$ gravity is
via Brown--Henneaux and Witten 2007 and is at their scope.
\end{remark}

\begin{corollary}[\label{cor:rung-w-N}Rung $N$: principal $W_{N}$ --
$E_{N+1}$-topological]
\ClaimStatusProvedHere
For $A = W_{N, c}$ the principal $W_{N}$ vertex algebra at generic
$c$, the bulk
$\mathrm{Obs}^{\mathrm{bulk}}(\Phihol(W_{N, c}))
\simeq Z^{\mathrm{der}}_{\mathrm{ch}}(W_{N, c})$ is
$E_{N+1}$-topological via the iterated Sugawara construction:
each higher-spin Casimir $T^{(n)}$ for $n \in \{2, 3, \ldots, N\}$
is inner and admits a BRST primitive $G^{(n)}$, providing one
$E_{1}$-topological factor through Dunn additivity beyond the
chiral $E_{2}$ factor on $Z^{\mathrm{der}}_{\mathrm{ch}}$. The
chain-level identification is in the weight-completed category, in
parallel to Rung~3.
\end{corollary}

\begin{proof}
Specialise \cref{thm:universal-holography-master} at $A = W_{N,c}$.
The algebra is class~M with stress tower
$\{T^{(n)}\}_{2 \le n \le N}$ all inner and BRST-primitive (each
$T^{(n)} = [Q_{\mathrm{tot}}, G^{(n)}]$ on cohomology). The finite
principal $\cW_N$ tempering pillar needs only finiteness of
$\beta_{W_N}$; the harmonic closed form
$\beta_{W_N} = 12 (H_N - 1)$ is the conditional exact-radius law of
\cref{thm:beta-N-closed-form-proved-all-N}. The
$E_{N+1}$-topological promotion is by iterated Sugawara
(\cref{thm:e-infinity-topologization-ladder}): $E_{2}$-chiral
on $Z^{\mathrm{der}}_{\mathrm{ch}}$ tensored under Dunn with
$E_{1}$-topological for each spin
$T^{(n)}$, $n = 2, \ldots, N$, giving $E_{2 + (N-1)} = E_{N+1}$
on the bulk.
\end{proof}

\begin{corollary}[\label{cor:rung-w-infty}Rung $\infty$:
$W_{\infty}\lbrack\lambda\rbrack$ as an $E_{\infty}$-topological operadic horizon]
\ClaimStatusConditional
For $A = W_{\infty}[\lambda]$ at generic
$\lambda \in \Lambda_{\mathrm{gen}} \subset \mathbb{C}$, the bulk
$\mathrm{Obs}^{\mathrm{bulk}}(\Phihol(W_{\infty}[\lambda]))
\simeq Z^{\mathrm{der}}_{\mathrm{ch}}(W_{\infty}[\lambda])$ is
$E_{\infty}$-topological under finite-window stabilisation,
inverse-limit Dunn compatibility, weight-window strong convergence,
truncation-compatible antighost homotopies, and vanishing of the
weightwise obstruction classes
\[
 \delta_{w,r}\in
 \varprojlim\nolimits_N^{1}
 H^{-1}\!\left(\operatorname{End}^{(r)}
 \bigl(B^{\mathrm{ord}}(W_N[\lambda])^{\le w}\bigr)\right)
\]
of Theorem~\ref{thm:w-infty-e-infty-topologization-endpoint}:
\[
 Z^{\mathrm{der}}_{\mathrm{ch}}(W_{\infty}[\lambda])
 \;\in\; E_{\infty}\text{-}\mathrm{top}\text{-}\mathrm{Alg}
 \;=\; \varprojlim_{N} E_{N+1}\text{-}\mathrm{top}\text{-}\mathrm{Alg},
\]
the inverse limit of the $W_{N}$ rungs as $N \to \infty$ in the
pro-category where those hypotheses hold.
\end{corollary}

\begin{proof}
This is \cref{thm:climax-w-infty-endpoint}, recast as the
$N \to \infty$ rung of the master ladder
\cref{thm:universal-holography-master}. On every bar-weight window,
finite GGL stabilisation identifies the operations at all
$N\ge N_0(w)=2w-1$. The Dunn transition maps forget the highest
topological direction, the chosen antighost homotopies commute with
these transitions, and the vanishing of the classes $\delta_{w,r}$
removes the derived $\varprojlim^1$ obstruction to gluing the
arity-$r$ operations. The strong inverse limit is therefore an
$E_{\infty}^{\mathrm{top}}$-algebra structure on the derived chiral
centre.
\end{proof}

\begin{remark}[\label{rem:rungs-platonic-architecture}
The ladder as Platonic architecture]
The five rungs above form the Platonic operadic ladder of the
volume:
\begin{center}
\begin{tabular}{l|l|l|l}
Rung & Algebra & Class & Bulk operadic level \\
\hline
1 & $H_{k}$ Heisenberg & G & $E_{3}$-top (Dunn) \\
2 & $V_{k}(\mathfrak{g})$ affine KM, $k \neq -h^{\vee}$ & L & $E_{3}$-top (Sugawara) \\
3 & $\Vir_{c}$, $c \neq 0$ non-critical & M (pro-obj / weight-compl) & $E_{3}$-top (holographic BCFT of $3d$ gravity) \\
$N$ & $W_{N, c}$ principal & M (pro-obj / weight-compl) & $E_{N+1}$-top \\
$\infty$ & $W_{\infty}[\lambda]$ generic $\lambda$ & M (pro-obj / weight-compl) & $E_{\infty}$-top (horizon) \\
\end{tabular}
\end{center}
The horizon is reached not by adding new structure but by
commuting an infinite tower of Sugawara into a single
$E_{\infty}$-topological algebra. The boundary-CFT datum of pure
$3d$ gravity (Brown--Henneaux Virasoro at
$c = 3\ell/(2G_{N})$; see~\cref{rem:climax-qg-scope}) is the
spin-two truncation; the full theory at $W_{\infty}$ is the
Platonic endpoint of the volume.
\end{remark}

\section{Universal Trace Identity (Vol~I $\leftrightarrow$ Vol~III bridge)}
\label{sec:universal-trace-identity}

The Universal Holography functor $\Phihol$ admits a cross-volume
manifestation as a comparison between Vol~I's normalised BRST ghost
trace, Vol~II's Pentagon trace, and Vol~III's Borcherds weight. This
section states the comparison as an organising principle; per-family
verification is by direct computation on the K3-fibered Class A locus.

\emph{Vol~I ghost trace.} For a chirally Koszul chiral
algebra $A$ with BRST realisation, the universal Koszul conductor
takes the closed form
\[
 K(A) \;=\; - c_{\mathrm{ghost}}(\mathrm{BRST}(A)),
\]
collapsing the per-family $\kappa$ formulas of Vol~I (affine
Kac-Moody, Virasoro, $W_{N}$, lattice, betagamma, $bc$) to a single
ghost-trace functor on the BRST-gauged chiral category
(Vol~I~\texttt{kappa\_conductor.tex},
Chapter~\ref{V1-ch:kappa-conductor};
Vol~I~\texttt{climax\_theorem.tex},
Chapter~\ref{V1-ch:climax-theorem}). The K3 Mukai/conductor scalar
$K^{\kappa_{\mathrm{ch}}}=8$ belongs to this conductor line; it is
not the Borcherds weight of $\Delta_5$.

\emph{Vol~III Borcherds weight.} For a Calabi-Yau $3$-fold $X$
that is K3-fibered Class A (the eight diagonal symplectic orbifolds
$\mathrm{K3} \times E / (\mathbb{Z}/N\mathbb{Z})$ for
$N \in \{1, 2, 3, 4, 5, 6, 7, 8\}$ excluding orbifold-anomalous
strata; equivalently $N \in \{1, \ldots, 6\}$ in the
Gritsenko-Nikulin Borcherds-product window plus the STU model), the
Borcherds weight of the BKM superalgebra $G(X)$ admits the
universal closed form
\[
 \kappa_{\mathrm{BKM}}(X) \;=\; \frac{c_{N}(0)}{2},
\]
where $c_{N}(0)$ is the constant Fourier coefficient of the
twisted-elliptic-genus theta block at level $N$
(Volume~III's universal BKM weight proposition). For
\emph{Class B} CY$_{3}$ (the quintic, $\mathbb{C}^{3}$, the
conifold, local $\mathbb{P}^{2}$), $\kappa_{\mathrm{BKM}}$ is
undefined: the replacement invariant is
$\kappa_{\mathrm{BCOV}} = \chi(X)/24$ plus shadow depth.

\begin{conjecture}[\label{conj:universal-trace-identity-volii-bridge}
Universal Trace Identity: cross-volume bridge through $\Phihol$]
\ClaimStatusConjectured
\emph{Scope.} K3-fibered Class A CY$_{3}$ as above
($N \in \{1, \ldots, 6\}$); explicitly excluded for Class B
(quintic, $\mathbb{C}^{3}$, conifold, local $\mathbb{P}^{2}$).

\emph{Statement.} For every K3-fibered Class A CY$_{3}$ $X$ for
which the three trace functionals are defined, the normalised Vol~I
BRST ghost trace, the Vol~II Pentagon trace, and the Vol~III
Borcherds weight agree with the Borcherds constant term:
\[
 \mathrm{tr}_{\mathrm{ghost}}(Q_{\mathrm{BRST}}^2)
 \;=\;
 \mathrm{tr}_{\mathrm{Pentagon}}
 \;=\;
 \kappa_{\mathrm{BKM}}(\Phi_N)
 \;=\;
 \frac{c_N(0)}{2},
\]
where $\Phi_N$ is the Borcherds product attached to the $N$th
K3-fibered Class A row. The assertion is that $\Phihol$ identifies
the three trace functionals on the common K3-fibered shadow. It is
not an equality between the BKM weight and half of the
Mukai/conductor invariant; $K^{\kappa_{\mathrm{ch}}}=8$ is a
separate Heisenberg--Mukai datum.

\emph{Mechanism.}
\begin{enumerate}
\item[(a)] At $d = 2$, $\Phi(\mathrm{D}^{b}(\mathrm{Coh}(\mathrm{K3})))
 \simeq H_{\mathrm{Muk}}$, an $E_{2}$-Mukai-Heisenberg algebra
 whose bar Euler product is $\eta(q)^{24}$; the universal
 conductor by Vol~I gives an explicit lattice value
 $K^{\kappa_{\mathrm{ch}}}=8$, a Mukai/conductor invariant.
\item[(b)] At $d = 3$, twisting by an elliptic curve $E$
 (K\"unneth) gives $\Phi_{3}(\mathrm{K3} \times E)$ at native
 level $n = 1$. The scalar BPS partition function uses the
 unnormalised Igusa square
 $\Phi_{10}^{\mathrm{un}}=\Delta_5^2$, while the Borcherds
 denominator is $\Delta_5$ with
 $\mathrm{wt}(\Delta_5)=c_{\phi_{0,1}^{K3}}(0)/2=10/2=5$.
\item[(c)] The bridge is the explicit normalised-trace identity
 $\mathrm{tr}_{\mathrm{ghost}}=\mathrm{tr}_{\mathrm{Pentagon}}
 =\kappa_{\mathrm{BKM}}(\Phi_N)=c_N(0)/2$
 for each K3-fibered Class A CY$_{3}$ at $N \in \{1, \ldots, 6\}$;
 per-family verification through $N = 6$ is the content of
 Volume~III's universal BKM weight proposition.
\end{enumerate}

\emph{Evidence.} Per-family verified for K3-fibered Class A through
$N = 6$ (Vol~III). The programme-level conjecture is that the
normalised-trace agreement is too tight to be coincidence, but the unifying single
proof through $\Phi \circ \Phihol$ awaits a joint Vol~I + Vol~III
treatment. The companion Vol~III statement is the universal trace
identity conjecture in its
bar-cobar bridge chapter; this Vol~II bridge inscription is its
mirror through $\Phihol$.
\end{conjecture}

\begin{remark}[\label{rem:utis-class-b-exclusion}
Class B exclusion is essential]
The Universal Trace Identity does \emph{not} hold for Class B
CY$_{3}$. The proposed additive split of the BKM weight into a chiral
scalar plus $\chi(\mathcal{O}_{\mathrm{fiber}})$ is not a theorem.
The equality $5=2+3$ is only an $N=1$ K3 mnemonic; with the Vol~III
total-space chiral scalar it already fails at $N=1$, and the mnemonic
split fails at $N \ge 2$.
For Class B CY$_{3}$, $\kappa_{\mathrm{BKM}}$ is undefined; the
replacement invariants are $\kappa_{\mathrm{BCOV}} = \chi(X)/24$
(BCOV anomaly) and shadow depth, conditional on the CY-A
inf-categorical functor at $d = 3$. The mystery of \emph{why} the
identity holds without modification on K3-fibered Class A is the
remaining structural question.
\end{remark}

\begin{remark}[\label{rem:utis-mediator-kappa-ch}
The chiral scalar is not the Borcherds weight]
The chiral Hodge supertrace $\kappa_{\mathrm{ch}}(\Phi(X))$ is the
chiral-side scalar of the CY-to-chiral shadow. It is not the BKM
weight. At the K3$\times E$ witness the Heisenberg chiral scalar is
$\kappa_{\mathrm{ch}}^{\mathrm{Heis}}=3$, while the Borcherds weight
is $\kappa_{\mathrm{BKM}}(\mathfrak g_{\Delta_5})
=c_{\phi_{0,1}^{K3}}(0)/2=5$. The Mukai/conductor invariant
$K^{\kappa_{\mathrm{ch}}}=8$ is a third scalar on the
Mukai--Heisenberg line. The bridge through $\Phihol$ compares the
normalised trace functionals; it does not identify these invariants.
\end{remark}

\section{The three-volume architecture at climax}
\label{sec:climax-architecture}

\cref{thm:programme-climax} is the junction of three volumes. Each
volume supplies a pillar.

\textbf{Volume~I} supplies the algebraic engine: the properad-level
bar-cobar equivalence $\mathrm{Theorem~A}^{\infty,2}$
(\cref{V1-thm:A-infinity-2}), the four-tier Laurent stratification with
Fuchsian ODE characterisation
(\cref{V1-thm:all-tier-fuchsian-ode}), the arithmetic-duality
refinement locating Kummer-irregular primes by Laurent depth
(\cref{V1-thm:kummer-laurent-depth-controlled}), and the $E_{1}$/$E_{2}$
depth-distinction principle forcing motivic MZV freeness
(\cref{V1-thm:shadow-tower-depth-1-rationality}).

\textbf{Volume~II} supplies the physical interpretation: the
tempered-stratum heal identifying the standard landscape with the
domain of chain-level $E_{3}$-topological holography
(\cref{thm:tempered-stratum-contains-virasoro},
\cref{thm:wn-tempered-all-N},
\cref{conj:tempered-stratum-contains-wp}), the Schellekens-71
classification closing the anomaly vanishing
(\cref{thm:schellekens-71-all-alpha-zero}), the irrational-coset
extension refining the tempered criterion to
VSKR + BGG (\cref{cor:tempered-criterion-refined}), and the
iterated-Sugawara ladder culminating in $E_{\infty}$
(\cref{thm:climax-w-infty-endpoint}).

\textbf{Volume~III} supplies the categorical realisation: the
CY-to-chiral functor $\Phi$ with $E_{n}$-level dimension
dependence (\cref{thm:derived-framing-obstruction} via
infinity-categorical framing), the six-routes pentagon with
$\kappa_{\mathrm{ch}}$-stratification $\{3, 12, 24\}$
(\cref{V3-thm:cy-c-six-routes-generator-level-convergence}), the
super-Riccati shadow tower with $\max(m, n)$ complementarity
correction
(\cref{thm:super-shadow-self-duality}), and the $CY_{4}$
$p_{1}$-twisted double current algebra
(\cref{thm:cy4-p1-twisted-family}).

The three volumes meet at the same object. Vol~I describes it
algebraically ($Z^{\mathrm{der}}_{\mathrm{ch}}(A) =
\mathrm{ChirHoch}^{\bullet}(A, A)$ as a chain complex). Vol~II
describes it physically ($\mathrm{Obs}^{\mathrm{bulk}}(T_{A})$ as a
factorisation algebra of the three-dimensional holomorphic-
topological theory). Vol~III describes it categorically
($\Phi(C)$ for a cyclic $A_{\infty}$-category $C$ with
$H H^{-d}(C) \simeq k$). The three descriptions agree; they are the
same object read off from three pillars.

\section{The five honest open frontiers}
\label{sec:climax-open-frontiers}

The master theorem \cref{thm:universal-holography-master} is
proved at the scope stated; five honest open frontiers remain on
the non-degenerate locus, each documented as a named conjecture.
These frontiers are explicit research questions, not gaps in the
master statement; the climax is closed at its stated scope.

\begin{conjecture}[\label{conj:f1-wp-tempering}F1: logarithmic
$\mathcal{W}(p)$ triplet tempering]
\ClaimStatusConjectured
The logarithmic triplet vertex algebra $\mathcal{W}(p)$ at any
$p \ge 2$ is tempered: the shadow-tower coefficients $S_{r}(\mathcal{W}(p))$
satisfy $\limsup_{r \to \infty} (|S_{r}(\mathcal{W}(p))|/r!)^{1/r}
= 0$, so $\mathcal{W}(p)$ lies in the domain of
\cref{thm:universal-holography-master}.
\emph{Status.} Open. The Zhu-bounded-Massey proof chain used for
the non-logarithmic standard landscape FAILS for $\mathcal{W}(p)$:
Gurarie 1993 (arXiv:hep-th/9303160) and Flohr 1996
(arXiv:hep-th/9605151) construct logarithmic-CFT amplitudes whose
Massey products accumulate super-polynomially across bar degrees
despite finite-dimensional Zhu algebra. The remaining path is a
direct Adamovi\'c-Milas character-amplitude bound on the
$\phi_{0,1}$ generating series. The conjecture that the tempered
stratum contains $\cW(p)$ is recorded here as
\ClaimStatusConjectured.
\end{conjecture}

\begin{conjecture}[\label{conj:f2-periodic-cdg-non-simply-laced}F2:
periodic-CDG for admissible Kazhdan-Lusztig at non-simply-laced
type]
\ClaimStatusConjectured
For every non-simply-laced simple Lie algebra $\mathfrak{g}$
($B_{n}$, $C_{n}$, $D_{n}$ outside ADE-type folding,
$F_{4}$, $G_{2}$) at admissible level $k$, the periodic-CDG
filtration on $\mathrm{KL}_{k}^{\mathrm{adm}}$ is
Koszul-compatible. Equivalently, the chiral bar-cobar adjunction
$\Omega^{\mathrm{ch}} \dashv B^{\mathrm{ch}}$ descends
unconditionally to
$\mathrm{KL}_{k}^{\mathrm{adm}} \rightleftarrows
(\mathrm{KL}_{k^{!}}^{\mathrm{adm}})^{\mathrm{op}}$.
\emph{Status.} Open for non-simply-laced. The simply-laced sub-case
(in particular $\mathfrak{sl}_{2}$) is closed via the Kubota class
construction in the Volume~I admissible periodic-CDG chapter;
extension to non-simply-laced awaits Arkhipov-Gaitsgory twisted
Satake plus Brylinski-Deligne reciprocity. This is the
cross-volume bridge companion of the Volume~I periodic-CDG
conjecture.
\end{conjecture}

\begin{conjecture}[\label{conj:f3-original-complex-class-m}F3:
intermediate-topology chain-level $E_{3}$-topological for class M]
\ClaimStatusConjectured
For every class~M chiral algebra $A$ in the standard landscape
(Virasoro $\Vir_{c}$ at $c \neq 0$ non-critical; $W_{N}$ at generic
$c$; $W_{\infty}[\lambda]$ at generic $\lambda$), the
$E_{3}$-topological identification
$\mathrm{Obs}^{\mathrm{bulk}}(\Phihol(A))
\simeq Z^{\mathrm{der}}_{\mathrm{ch}}(A)$ is realised at chain
level in an explicitly topologized analytic model stricter than the
full weight completion. The discrete raw direct-sum bar complex is
excluded from this conjecture: at generic central charge the
raw-direct-sum statement is false.
\emph{Status.} Open. The topologisation tower
(\cref{thm:e-infinity-topologization-ladder}) gives chain-level
identifications on the original complex for classes G, L, C and
critical-level KM; class M is closed only in the weight-completed
category (Proposition~\ref*{prop:bv-bar-class-m-weight-completed}).
The remaining path is half-BRST resolution in an explicitly
topologized analytic model stricter than the full completion. The
direct-sum class-M chain-level statement is genuinely false on the
raw bar; the conjecture targets only such an intermediate
topologized layer.
\end{conjecture}

\begin{conjecture}[\label{conj:f4-super-complementarity-canonical}F4:
canonical pairing for super-complementarity
$\kappa + \kappa^{!} = \max(m, n)$]
\ClaimStatusConjectured
For super-Yangians $Y(\mathfrak{sl}(m | n))$, the
super-complementarity identity
$\kappa(Y(\mathfrak{sl}(m | n))) +
\kappa(Y(\mathfrak{sl}(n | m))^{!}) = \max(m, n)$
is canonicalised through a single bilinear pairing rather than the
two presently-coexisting pairings (super-trace pairing on the
$E_{1}$-bialgebra side and Berezinian pairing on the modular PVA
side).
\emph{Status.} Open. The identity is proved on the sub-Sugawara
line in both pairings independently; no programme-level
canonicalisation has been established. The remaining path is
Verdier-pairing inscription on the super-bar complex.
\end{conjecture}

\begin{conjecture}[\label{conj:f5-irregular-singular-genus-g}F5:
irregular-singular KZB regularity at $\overline{\mathcal{M}}_{g, n}$
boundaries for $g \ge 1$]
\ClaimStatusConjectured
The Jimbo-Miwa irregular-singular KZB framework gives
Stokes-sector composition from a compatible boundary formal type
(\cref{thm:irregular-singular-kzb-regularity}). That formal type
exists and is compatible with clutching at the boundary divisors of
$\overline{\mathcal{M}}_{g, n}$ for all $g \ge 1$.
\emph{Status.} Open. The chain-level smooth-locus statement is
closed by the Kohno-Felder KZB framework; boundary-stratum formal
type and regularity at $\overline{\mathcal{M}}_{g, n}$ for
$g \ge 1$ is the remaining frontier. The path is via the Mok25 logarithmic
Fulton-MacPherson compactification's snc structure plus
Gauss-Manin uncurving across boundary strata.
\end{conjecture}

\begin{remark}[\label{rem:five-frontiers-architecture}
The five frontiers are honest, not gaps]
None of F1-F5 is a gap in
\cref{thm:universal-holography-master}: each is a frontier
\emph{at the boundary} of the climax's domain of validity. F1 is
the logarithmic-versus-non-logarithmic boundary; F2 is the
simply-laced-versus-non-simply-laced boundary at the admissible
level; F3 is the original-complex-versus-weight-completed boundary
within class M; F4 is a canonicalisation question on the super
extension; F5 is a boundary-stratum question at the modular level.
The master theorem holds at its stated scope; the frontiers are
explicit research targets each with an identified path of attack.
\end{remark}

\section{The gravitational partition function from the bar trace}
\label{sec:climax-gravity-partition}

Fix $A = \Vir_{c}$ at non-critical central charge $c \neq 0$ and a
smooth projective curve $X$ of genus $g$ with $n$ marked points. The
classical $r$-matrix, trace-form level, and shadow obstruction tower
are the three scalar invariants of $A$ admitted by the programme:
\[
 r^{\Vir}(z) \;=\; \frac{c/2}{z^{3}} + \frac{2T}{z},
 \qquad
 \kappa(\Vir_{c}) \;=\; \frac{c}{2},
 \qquad
 F_{g} \;=\; \kappa \cdot \lambda_{g}^{\mathrm{FP}},
\]
with $\lambda_{g}^{\mathrm{FP}} = (2^{2g-1} - 1)|B_{2g}| / (2^{2g-1}
(2g)!)$ the Faber-Pandharipande closed form of the pointed Hodge
integral
$\int_{\overline{\cM}_{g,1}}\psi_1^{2g-2}\lambda_{g}$
\cite{FP00}. The question pinned down in this
section: what \emph{does} the universal holography functor $\Phihol$
produce as the partition function on $\overline{\cM}_{g, n}$, and
what of Maloney-Witten 2007 does it recover, reproduce, or inherit?

\begin{proposition}[\label{prop:f6-genus-three-lambda-residue}
F6 genus-three \(\lambda_g\)-residue witness]
\ClaimStatusProvedHere
The first scalar residue beyond the genus-two curved-Dunn base case is
\[
 \lambda_3^{\mathrm{FP}}
 =
 \int_{\overline{\cM}_{3,1}}\psi_1^4\lambda_3
 =
 [t^6]\frac{t/2}{\sin(t/2)}
 =
 \frac{31}{967680}.
\]
Consequently a uniform-weight chiral algebra with scalar
\(\kappa\) contributes
\[
 F_3=\kappa\,\lambda_3^{\mathrm{FP}}
 =
 \frac{31\,\kappa}{967680}
\]
to the F6 planted-forest scalar projection.
\end{proposition}

\begin{proof}
Faber--Pandharipande prove
\[
 1+\sum_{g\ge 1}
 \left(\int_{\overline{\cM}_{g,1}}\psi_1^{2g-2}\lambda_g\right)t^{2g}
 =
 \frac{t/2}{\sin(t/2)}
\]
\cite{FP00}. Equivalently
\[
 \lambda_g^{\mathrm{FP}}
 =
 \frac{2^{2g-1}-1}{2^{2g-1}}
 \frac{|B_{2g}|}{(2g)!}.
\]
At \(g=3\), \(B_6=1/42\), hence
\[
 \lambda_3^{\mathrm{FP}}
 =
 \frac{31}{32}\cdot\frac{1}{42}\cdot\frac{1}{720}
 =
 \frac{31}{967680}.
\]
The same rational number is checked independently by exact
power-series inversion and by the one-point
\(\lambda_g\)-multinomial specialization in
\texttt{compute/tests/test\_f6\_lambda\_g\_residue.py}.
\end{proof}

\begin{proposition}[\label{prop:f6-scalar-projection-no-multichannel-lift}
F6 scalar projection does not determine the socle lift]
\ClaimStatusProvedHere
Let \(N_{\mathbb Q}=\mathbb Q u\oplus\mathbb Q v\) be a two-channel
socle quotient and let
\(\pi:N_{\mathbb Q}\to\mathbb Q\) be the scalar projection
\(\pi(a u+b v)=a+b\). Then
\[
 \pi(\lambda_3^{\mathrm{FP}}u)
 =
 \pi(\lambda_3^{\mathrm{FP}}v)
 =
 \lambda_3^{\mathrm{FP}},
 \qquad
 \lambda_3^{\mathrm{FP}}u\neq \lambda_3^{\mathrm{FP}}v .
\]
Consequently the identity
\[
 F_3=\kappa\,\lambda_3^{\mathrm{FP}}
\]
fixes only the scalar projection of the F6 planted-forest class. A
multichannel socle lift requires an additional scalar-diagonal
hypothesis or a specified channel splitting
\(\mathbb Q\kappa\to N_{\mathbb Q}\).
\end{proposition}

\begin{proof}
The two displayed classes differ by
\(\lambda_3^{\mathrm{FP}}(u-v)\), a non-zero element of
\(\ker(\pi)\). Since their scalar projections agree, the scalar
residue cannot distinguish the two channel placements. The exact
two-channel calculation is recorded in
\texttt{compute/tests/test\_f6\_multichannel\_socle\_lift.py}.
\end{proof}

\begin{theorem}[\label{thm:gravity-climax-partition-function}
The holographic gravity partition function as an ordered bar trace]
\ClaimStatusConditional
\emph{Scope.} Let $A = \Vir_{c}$ at non-critical $c \neq 0$ and generic
in the Kac-discriminant complement. Fix $g \ge 0$ and $n \ge 0$, and a
stable point $[X; p_{1}, \ldots, p_{n}] \in \overline{\cM}_{g, n}$.

\emph{Statement.} The scalar trace comparison $(G2)=(G3)$ is proved on
the indicated scope. The comparison with the physical gravitational
quantity $(G1)$ holds under the following named physical comparison
package:
\begin{enumerate}[label=\textup{(H\arabic*)}]
\item \emph{Brown--Henneaux comparison.} A boundary comparison map
 \(\mathcal C_{\mathrm{BH}}\) identifies the vacuum Virasoro scalar
 \(q^{-c/24}\prod_{k\ge2}(1-q^k)^{-1}\) with the perturbative
 thermal-AdS$_3$ boundary character at
 \(c=3\ell/(2G_N)\).
\item \emph{Modular completion.} The completed boundary partition
 function is modular invariant under the required
 \(\mathrm{SL}_2(\Z)\)-action and contains the chosen Virasoro seed.
\item \emph{Vacuum dominance and saddle extraction.} The modular
 \(S\)-transform has a nondegenerate high-temperature saddle dominated
 by the vacuum sector, so the inverse Laplace saddle produces the
 Cardy/BTZ asymptotic.
\item \emph{Saddle labelling.} The physical saddle prescription sends
 the vacuum orbit to thermal AdS$_3$ and the heavy Virasoro sectors to
 the selected BTZ tower.
\end{enumerate}
Under \textup{(H1)--(H4)}, the following three scalars agree:
\begin{enumerate}
\item[(G1)] The image under \(\mathcal C_{\mathrm{BH}}\) of the
 Virasoro scalar trace, interpreted through \textup{(H2)--(H4)} as the
 saddle-dominated thermal AdS$_3$/BTZ boundary-CFT contribution in the
 sense of Witten 2007 \cite{Witten2007}.
\item[(G2)] The categorical trace of the ordered bar complex
 $B^{\mathrm{ord}}(\Vir_{c})$ against the $\kappa$-twisted Hodge
 bundle $\lambda_{g}$ on $\overline{\cM}_{g, n}$,
 \[
 \Tr_{B^{\mathrm{ord}}(\Vir_{c})}^{\mathrm{ch}}
 \bigl(q^{L_{0} - c/24}; \overline{\cM}_{g, n}\bigr)
 \;=\;
 \exp\!\Bigl(\sum_{g' = 0}^{g} F_{g'} \,\beta^{2 g' - 2}\Bigr)
 \cdot q^{-c/24}
 \cdot \prod_{k = 2}^{\infty} (1 - q^{k})^{-1},
 \]
 with $F_{g'} = \kappa(\Vir_{c}) \cdot \lambda_{g'}^{\mathrm{FP}}
 = (c/2) \lambda_{g'}^{\mathrm{FP}}$ and $\beta = 2\pi \im \tau$, the
 shadow-free-energy genus series of the convergence dichotomy
 (\cref{thm:convergence-dichotomy}).
\item[(G3)] The universal-holography bulk-observable trace
 $\Tr\bigl(\mathrm{Obs}^{\mathrm{bulk}}(\Phihol(\Vir_{c}))
 |_{\overline{\cM}_{g, n}}\bigr)$, the chain-level trace of the
 bulk factorisation algebra
 $Z^{\mathrm{der}}_{\mathrm{ch}}(\Vir_{c})$ on the family
 $\overline{\cM}_{g, n}$.
\end{enumerate}
Without \textup{(H1)--(H4)}, only the equality $(G2) = (G3)$ is proved;
it holds at chain level in the
weight-completed ambient of
\cref{thm:universal-holography-master}. For $g \ge 2$ the scalar
chain-level comparison passes through the genus-tower MC5-class-M
weight completion of the $\Vir_{c}$ derived centre.

\emph{The three scalars $(r(z), \kappa, F_{g})$ are the only
algebraic invariants of $\Vir_{c}$ used by this scalar partition
seed:}
$r^{\Vir}(z)$ determines the classical level of the boundary
$\SCchtop$-pair, $\kappa$ determines the perturbative genus-expansion
coefficients through the universal identity $F_{g} = \kappa \cdot
\lambda_{g}$, and the Hodge bundle $\lambda_{g}$ controls the
modular-weight dependence on the Deligne-Mumford boundary. The
additional physical data are precisely the comparison package
\textup{(H1)--(H4)}.
\end{theorem}

\begin{proof}
The equality $(G2) = (G3)$ is the chain-level trace reading of
\cref{thm:universal-holography-master}~(M3) evaluated on the
$\overline{\cM}_{g, n}$ family: both sides compute the same factorisation
homology of $Z^{\mathrm{der}}_{\mathrm{ch}}(\Vir_{c})$ against the
Hodge class, one via the $B^{\mathrm{ord}}$ definition and the other
via the $\mathrm{ChirHoch}^{\bullet}$ definition, and the two agree by
\cref{V1-thm:A-infinity-2} through bar-cobar duality. The equality
$F_{g'} = \kappa \cdot \lambda_{g'}$ is Vol~I Theorem~D
(\cref{V1-thm:obstruction-tower-universality}) with
$\lambda_{g'}^{\mathrm{FP}}$ the Faber-Pandharipande closed form.
Assumption \textup{(H1)} identifies the Virasoro scalar seed at
$c = 3\ell/(2G_N)$ with the perturbative thermal-AdS$_3$ boundary
character. Assumptions \textup{(H2)--(H4)} are exactly the analytic
steps that convert the seed into the saddle-dominated
BTZ/Cardy contribution: modular completion, vacuum dominance,
nondegenerate inverse-Laplace saddle, and the chosen saddle labelling.
Under those hypotheses \((G1)=\mathcal C_{\mathrm{BH}}(G2)\), while
\((G2)=(G3)\) was already proved chain-level.
\end{proof}

\begin{remark}[\label{rem:gravity-climax-maloney-witten-inheritance}
What Maloney-Witten 2007 is, and what
\cref{thm:gravity-climax-partition-function} does not promise]
\cref{thm:gravity-climax-partition-function} produces the scalar
perturbative seed that can be compared with a holographic partition
function only after the physical dictionary is imposed. Maloney-Witten 2007
\cite{MaloneyWitten2007} proposes a second object, the full
modular-invariant partition function obtained by summing over the
$\mathrm{SL}_{2}(\Z)$ orbit of the thermal saddle; this sum is
\emph{not} a trace on $B^{\mathrm{ord}}(\Vir_{c})$ in the
$\mathrm{SC}^{\mathrm{ch,top}}$ sense of the present volume, and is
the source of the negative-degeneracy pathology of Maloney-Witten
2007 (the integer-coefficient requirement fails at $c > 1$
without additional input). The programme does not produce the
Maloney-Witten sum from $Z^{\mathrm{der}}_{\mathrm{ch}}(\Vir_{c})$
alone. What it does produce is the chain-level scalar trace and its
explicit genus expansion. Interpreting that trace as an individual
thermal-AdS or BTZ saddle contribution, and assembling the
Maloney-Witten modular sum, requires a second datum beyond the
boundary chiral algebra: a prescription for the physical saddle set
and the ensemble over the modular orbit. The programme is
\emph{orthogonal} to that prescription; it supplies the perturbative
scalar factor and leaves the non-perturbative assembly unresolved. In
the three-volume architecture, the proposed assembly is controlled by
Vol~III's twisted-elliptic-genus Borcherds-product data, not by the
present universal-holography functor.
\end{remark}

\begin{corollary}[\label{cor:gravity-climax-shadow-convergence}
The perturbative scalar genus series is convergent; Page/Stokes
assembly is extra data]
\ClaimStatusProvedHere
The coefficients $F_{g} = (c/2) \lambda_{g}^{\mathrm{FP}}$ of the
gravitational genus expansion admit the Bernoulli asymptotic
$|F_{g + 1} / F_{g}| \to 1/(4\pi^{2})$. Hence the scalar series in
$\hbar^{2}$ has radius $4\pi^{2}$. Its ordinary Gevrey-$1$ Borel
transform is entire; no Page transition or BTZ Stokes jump follows
from this scalar tower alone. A Page/Stokes statement requires the
separate two-sector transseries and entropy-extraction hypotheses
recorded in~\cref{rem:stokes-is-page}.
\end{corollary}

\begin{proof}
The Bernoulli ratio follows from the Faber-Pandharipande formula and
the standard asymptotic $|B_{2 g + 2} / B_{2 g}| \to (2 g + 1)
(2 g + 2) / (2 \pi)^{2}$. The factorial in
$\lambda_{g}^{\mathrm{FP}}$ cancels this growth, leaving
$\lambda_{g+1}^{\mathrm{FP}}/\lambda_g^{\mathrm{FP}}\to 1/(4\pi^2)$.
Thus the scalar genus series is analytic in the variable $\hbar^2$
inside $|\hbar^2|<4\pi^2$. Dividing by $\Gamma(g)$ to form the
ordinary Borel transform only improves convergence, so the scalar
lane supplies no Borel-plane singularity. The Page interpretation is
therefore outside this corollary.
\end{proof}

\begin{remark}[\label{rem:gravity-climax-phi4-falsifies-hk-heuristic}
The $\mathrm{CY}_{4}$ $\Phi_{4}$-obstruction selects the abelian
stratum, not hyperk\"ahler]
A natural heuristic reads the $4d \to 3d$ gravity descent as
controlled by the Vol~III $\Phi_{4}$ functor, with hyperk\"ahler
$\mathrm{CY}_{4}$ as the obstruction-free locus. Vol~III's
Theorem~$\mathtt{V3\text{-}thm\text{:}phi\text{-}4\text{-}eff\text{-}p1\text{-}vanishing}$
together with Corollary~$\mathtt{V3\text{-}cor\text{:}phi\text{-}4\text{-}p1\text{-}vanishing\text{-}stratum}$
\textbf{falsify} this heuristic: the strict $\Sphere^{4}$-framing
$[p_{1}(T_{X})] = 0$ holds only on the abelian stratum
$X = \C^{4} / \Lambda$, and fails on every hyperk\"ahler
$\mathrm{CY}_{4}$ including $K3^{[2]}$ (where
$p_{1}(T_{K3^{[2]}}) = -2 c_{2}(T_{K3^{[2]}}) \neq 0$). The $4d \to 3d$
gravity descent obstructed by Pontryagin class is therefore a
\emph{distinct} phenomenon from the present $3d$ bulk holography; the
two obstruction classes do not coincide on the hyperk\"ahler locus.
The honest statement of the $\Phi_{4}$ link is the
$\Z$-shifted symplectic level $\ell(X, \alpha) =
\int_{X} p_{1}(T_{X}) \cup \alpha$ of Vol~III, which replaces the
naive strict-framing pointwise section with a $\mathbb{P}^{1}$-family
\emph{carrying} the $p_{1}$-twist. The gravity-climax reading of
Vol~III at CY-$4$ is therefore not a higher-dimensional uplift but a
parallel datum: the $p_{1}$-twisted $\mathbb{P}^{1}$-family is the
CY-$4$ companion of the $\SCchtop$-pair at CY-$3$.
\end{remark}

\begin{remark}[\label{rem:gravity-climax-conway-superselection}
The Conway sector $V^{f\natural}$ is a distinct superselection
sector, not a rung of the master ladder]
The rung~$3$ corollary
(\cref{cor:rung-virasoro}) specialises $\Phihol$ at $\Vir_{c}$, which
on the holomorphic-character side recovers the Monstrous Moonshine
modulus of Borcherds 1992~\cite{Borcherds1992} on
$\mathrm{II}_{1, 1}$ at $c = 24$. The Duncan 2007 Conway vertex
superalgebra $V^{f\natural}$ at $c = 12$ with
$\mathrm{Aut}(V^{f\natural}) = \mathrm{Co}_{0}$ is a
\emph{distinct} superselection sector, not a rung of the Virasoro
ladder: it sits at half the conductor ($\kappa(V^{f\natural}) = 6$,
Vol~III standalone),
carries an $N = 1$ small-superconformal structure incompatible with
the non-supersymmetric $\SCchtop$-pair at rung~$3$, and its Borcherds
lift uses the $\mathrm{II}_{1, 1} \oplus E_{8}$ input lattice rather
than $\mathrm{II}_{25, 1}$. The Conway sector is therefore a
\emph{parallel} gravity climax, not a dependent consequence of the
present theorem: the Vol~III K3-Yangian compute module
\texttt{conway\_leech\_k3.py} treats the construction as conjectural
pending the construction of $Y(\mathfrak{g}_{K3})$. Its independent
rung would sit at a separate $\SCchtop$-pair whose boundary is the
$c = 12$ Conway sVOA and whose bulk is
$Z^{\mathrm{der}}_{\mathrm{ch}}(V^{f\natural})$; the topologisation
ladder then produces a separate $E_{\infty}$-operadic horizon. The
programme records this as an honest independent frontier, not
subsumed by the Virasoro rung.
\end{remark}

\begin{remark}[\label{rem:gravity-climax-genus-g-through-F5}
High-genus partition function closure routes through F5]
The equality $(G2) = (G3)$ of
\cref{thm:gravity-climax-partition-function} extends to arbitrary
genus $g \ge 2$ in the weight-completed category unconditionally; its
upgrade to the \emph{original} bar complex on
$\overline{\cM}_{g, n}$ at arbitrary $g$ and with boundary-divisor
regularity coincides with Open Frontier~F5
(\cref{conj:f5-irregular-singular-genus-g}). The identification
$(G1) = (G2)$ at $g \ge 2$ is the holographic reading of
Witten~2007 in the Maloney-Witten 2007 regime and carries the
caveats of
\cref{rem:gravity-climax-maloney-witten-inheritance}. The
programme's closure of the high-genus perturbative scalar factor is
Corollary~\ref{cor:gravity-climax-shadow-convergence}: an analytic
scalar series in $\hbar^2$ with radius $4\pi^2$. What remains open is the
\emph{non-perturbative} assembly, which sits outside the master
theorem's scope.
\end{remark}

\section{What the climax does not say}
\label{sec:climax-limits}

\cref{thm:programme-climax} asserts the equivalence \emph{on the
standard landscape at generic parameter}. Three scope boundaries
deserve explicit acknowledgment.

First, the parameter locus is generic in the sense of the severe
Kac-discriminant complement. At measure-zero Kac collisions the
Banach completion degenerates; the chain-level equivalence holds
in the limit but not at the singular point itself.

Second, the critical level $k = -h^{\vee}$ for affine Kac-Moody is
excluded: Sugawara degenerates, the conformal vector ceases to be
inner, and the $E_{3}$ structure collapses to an $E_{2}$ structure
realising the Feigin-Frenkel centre. This is the single
exceptional stratum in the standard landscape; it carries its own
geometry (opers on the formal disk) rather than the
$E_{3}$-topological structure.

Third, the tempered criterion VSKR + BGG is strictly weaker than
$C_{2}$-cofiniteness. The non-tempered stratum, were it to exist,
would contain chiral algebras violating VSKR or exhibiting
unbounded generator-to-generator OPE pole order. No such algebra
has been constructed in the standard landscape; the conjectural
existence of one is an open problem whose resolution would require
either an explicit construction or a proof of universal
tempering.

\section{The inevitable consequences}
\label{sec:climax-consequences}

Once the climax theorem is established, a number of consequences
follow by pure reading.

The bulk-boundary pair $(Z^{\mathrm{der}}_{\mathrm{ch}}(A), A)$
satisfies a categorified Swiss-cheese structure
$\mathrm{SC}^{\mathrm{ch},\mathrm{top}}$ with the two colours
distinct. When $A$ carries a conformal vector at non-critical level,
topologisation collapses the chiral colour into the topological
colour, producing $E_{3}$-topological; this is
\cref{V1-thm:topologization-tower}. The ladder of
\cref{thm:iterated-sugawara-construction} refines the collapse by
one topological direction per inner stress tensor.

The shadow-tower coefficients $S_{r}(A)$ encode the bulk OPE at
weight~$r$. Their rationality in the parameter $c$ (Vol~I
\cref{V1-thm:virasoro-motivic-rationality-all-r}) reflects the
$E_{1}$-chiral structure of the boundary; their Kummer-irregular
prime content at specific Laurent depths
(\cref{V1-thm:kummer-laurent-depth-controlled}) reflects the
modularity of the bulk through the arithmetic-duality theorem
(Vol~I \cref{V1-thm:z-g-s-r-arithmetic-duality}) relating $S_{r}$ to
the Hurwitz-Bernoulli asymptotic on $\mathrm{Bun}_{SL_{2}}(\Sigma_{g})$.

The six routes to the BKM algebra $G(K3 \times E)$
(Vol~III \cref{V3-thm:cy-c-six-routes-generator-level-convergence})
do not converge to an isomorphic algebra; they assemble into a
pentagon with $\kappa_{\mathrm{ch}}$-stratification
$\{3, 12, 24\}$, with the Borcherds branch as source. The
universal object $G(K3 \times E)$ is the pentagon colimit. This
refines the naive universality principle into a categorical
one.

\begin{remark}[Epistemic closure]
The remaining open problems in the programme are parameter
questions and category extensions, not gaps in the climax: the
explicit closed form of $\beta_{N}$ for $N \ge 4$, the
uniform-duality conjecture extending Kummer absence to every
Bernoulli index, the CY-C generator-level intertwiner
construction with its four conditional hypotheses, and the
construction of an genuinely non-tempered chiral algebra (if it
exists). Each is a concrete problem with a concrete object of
study, not a structural obstruction.
\end{remark}

\begin{remark}[On the physical reading]
The climax theorem is the mathematical statement of a physical
principle: that three-dimensional holomorphic-topological gauge
theory is controlled by its boundary chiral algebra, with the
bulk factorisation algebra determined by the derived chiral
centre. The equivalence holds at chain level on the original
(raw direct-sum) complex for classes G, L; on class M (Virasoro,
$W_{N}$, $W_{\infty}[\lambda]$) it holds in the weight-completed
(pro-object) category. The raw direct-sum strengthening is false;
only an explicitly topologized intermediate strengthening remains
Open Frontier~F3 (\cref{conj:f3-original-complex-class-m}). The
physical prediction: every three-dimensional quantum theory with
a holomorphic-topological twist, a boundary vertex algebra, and
a conformal vector at non-critical level admits a canonical
derived-centre description at the level of its factorisation
observables. \emph{Scope qualifier for the Virasoro rung.} For
$A = \Vir_{c}$, the ``three-dimensional quantum gravity''
reading is the holographic boundary-CFT interpretation of
Brown--Henneaux 1986 and Witten 2007 (\cref{rem:climax-qg-scope}),
not a first-principles dynamical-metric path integral.
\end{remark}

\section{The programme as a whole}
\label{sec:programme-whole}

The modular Koszul duality programme rests on one principle: the
bar complex
\[
 B^{\mathrm{ord}}(A) \;=\; T^{c}(s^{-1} \bar{A})
\]
with its deconcatenation coproduct and chiral differential, is an
$E_{1}$-chiral coassociative coalgebra over the Koszul dual
operad $(\mathrm{ChirAss})^{!}$. It is the primitive object of the
programme; every other structure is either derived from it
($Z^{\mathrm{der}}_{\mathrm{ch}}(A)$, $A^{!}$,
$\mathrm{Obs}^{\mathrm{bulk}}(T_{A})$), or dual to it ($A^{i}$ via
Koszul cohomology, $A^{!}$ via Verdier duality).

The five theorems of the programme, A through D and H, are the
invariants extracted from $B^{\mathrm{ord}}(A)$ that survive
$\Sigma_{n}$-averaging. The climax theorem of this chapter is the
class-dependent existential closure: for every $A$ in the standard
landscape, the three descriptions of
$Z^{\mathrm{der}}_{\mathrm{ch}}(A)$ (algebraic, physical,
categorical) agree on the verified chain surface. For classes
$\mathbf G$ and $\mathbf L$ this is the original complex; for class
$\mathbf M$ it is the strict completed/pro surface or the coderived
localization, while the raw direct-sum original complex remains the
open frontier.

The programme reaches its Platonic form in this closure. No
remaining frontier is a gap in the climax; every remaining open
problem is a refinement of a parameter, a category extension, or a
conjectural construction whose precise mathematical content is
stated with full scope.
