%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AMBIENT COMPLEMENTARITY FROM THE CHAIN-LEVEL PERSPECTIVE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecommand{\fn}{\mathfrak{n}}
\providecommand{\fb}{\mathfrak{b}}
\providecommand{\fh}{\mathfrak{h}}
\providecommand{\fsl}{\mathfrak{sl}}
\providecommand{\Bl}{\operatorname{Bl}}
\providecommand{\cN}{\mathcal{N}}
\providecommand{\SL}{\mathrm{SL}}
\providecommand{\fso}{\mathfrak{so}}
\providecommand{\fsp}{\mathfrak{sp}}

\subsection{Ambient complementarity from the chain-level perspective}
\label{sec:ambient-complementarity-chain-level}

Volume~I develops the ambient complementarity theorem
(Theorem~C, the Lagrangian splitting of genus-$g$ cohomology, and its nonlinear ambient-complementarity refinement)
at the level of cohomology and formal moduli.
The chain-level $\Ainf$ framework of the present volume gives
access to a more explicit model of the same geometry, in which
the $(-1)$-shifted symplectic structure and the complementary
Lagrangians are constructed directly from the bar complex and its
cyclic pairing.

\begin{definition}[Chain-level ambient complementarity complex;
\ClaimStatusConjectured]
\label{def:chain-level-ambient-complex}
Let $\cA$ be a chiral Koszul algebra with bar complex
$\barB_{\mathrm{ch}}(\cA)$
(Definition~\ref{def:chiral_bar}), Koszul dual
$\cA^! = H^*(\barB_{\mathrm{ch}}(\cA))^\vee$
(obtained by Verdier duality on bar cohomology), and
universal twisting morphism
$\tau_\cA \colon \barB_{\mathrm{ch}}(\cA) \to \cA^!$.
The \emph{chain-level ambient complementarity complex} is the
$\Ainf$ deformation complex
\[
T_{\mathrm{comp}}^{\Ainf}(\cA)
\;=\;
\mathrm{Def}_{\Ainf}(\cA)
\;\oplus\;
\mathrm{Def}_{\Ainf}(\cA^!)
\;\oplus\;
\mathrm{Def}_{\Ainf}(\tau_\cA),
\]
controlling the formal moduli problem of triples
$({\cA}', \alpha, {\cA^!}')$, where ${\cA}'$ is a curved
$\Ainf$ deformation of~$\cA$, ${\cA^!}'$ is a curved
$\Ainf$ deformation of~$\cA^!$, and $\alpha$ is an $\Ainf$
twisting morphism deforming $\tau_\cA$ compatibly with
${\cA}'$ and~${\cA^!}'$.  The differential on
$T_{\mathrm{comp}}^{\Ainf}(\cA)$ is the linearization of
the curved Maurer--Cartan equation
$d_{\barB}\alpha
+ \sum_{k \ge 2} m_k(\alpha^{\otimes k}) = 0$
for the full $\Ainf$ bar differential.
\end{definition}

\begin{remark}[The $(-1)$-shifted symplectic structure
from cyclic $\Ainf$ pairings]
\label{rem:shifted-symplectic-from-cyclic}
The cyclic structure on the bar complex
(Section~\ref{subsec:genus-tower-R}) endows
$T_{\mathrm{comp}}^{\Ainf}(\cA)$ with a degree~$-1$
pairing.  Concretely, the Verdier/BV trace on
$\barB_{\mathrm{ch}}(\cA)$ pairs bar elements of total
degree~$k$ with elements of degree $1-k$, so the induced
bilinear form on the deformation complex is antisymmetric
of degree~$-1$.  This is the chain-level avatar of the
$(-1)$-shifted symplectic structure on the formal moduli
problem $\mathcal{M}_{\mathrm{comp}}(\cA)$ constructed in
Volume~I.

The two summands $\mathrm{Def}_{\Ainf}(\cA)$ and
$\mathrm{Def}_{\Ainf}(\cA^!)$ are isotropic with respect
to this pairing: the Maurer--Cartan equation for a
one-sided deformation forces the self-pairing to vanish
(expanding the MC equation $d\gamma + \tfrac{1}{2}[\gamma,\gamma]
+ \cdots = 0$ and applying the cyclic pairing, the linear
term drops out by cyclicity and the quadratic term is
symmetric in the wrong degree).  Maximality of each
isotropic summand (i.e., the Lagrangian property) follows
from the bar-cobar quasi-isomorphism
(Theorem~\ref{thm:bar_cobar_adjunction}), which
identifies the normal complex to each Lagrangian with the
shifted cotangent fiber of the other.
\end{remark}

\begin{remark}[BV perspective: the complementarity
potential as a boundary master action]
\label{rem:bv-complementarity-potential}
In the holomorphic-topological framework
(Section~\ref{thm:boundary-chiral-algebra-bv}), the
complementarity potential $S_\cA$ of Volume~I admits a
chain-level interpretation as a \emph{boundary BV master
action}.  The ambient $(-1)$-shifted symplectic space
$\mathcal{M}_{\mathrm{comp}}(\cA)$ is the BV phase space
of the boundary theory; the two Lagrangians
$\mathcal{M}_\cA$ and $\mathcal{M}_{\cA^!}$ correspond to
bulk and boundary degrees of freedom respectively.  The
BV master equation
$\hh\,\Delta_{\mathrm{BV}} S_\cA
+ \tfrac{1}{2}\{S_\cA, S_\cA\} = 0$
is the formal-neighborhood form of the curved $\Ainf$
Maurer--Cartan equation on
$T_{\mathrm{comp}}^{\Ainf}(\cA)$, with the BV Laplacian
$\Delta_{\mathrm{BV}}$ corresponding to the genus-$g$
quantum corrections and the antibracket $\{-,-\}$
corresponding to the cyclic pairing.  The formal Legendre
duality between $S_\cA$ and $S_{\cA^!}$ (Volume~I,
Proposition~\ref*{prop:formal-legendre}) then becomes the
statement that bulk and boundary gauge-fixings are related
by fiber-base exchange in the shifted cotangent bundle
$T^*[-1]\mathcal{M}_\cA$.
\end{remark}

\begin{remark}[Nonlinear shadows and the quartic resonance class]
\label{rem:nonlinear-shadow-pointer}
The chain-level ambient complex
$T_{\mathrm{comp}}^{\Ainf}(\cA)$ gives in principle
access to all Taylor coefficients of the complementarity
potential $S_\cA$: the cubic coefficient is the universal
gravitational cubic coupling, and the quartic coefficient
governs the modular quartic resonance class
$\mathfrak{R}_{4,g,n}^{\mathrm{mod}}(\cA)$.  The full
nonlinear shadow calculus (including clutching laws,
family-by-family computations for Heisenberg, affine Kac--Moody,
and Virasoro, and the relationship between the quartic
resonance class and the universal modular master action
$\Theta_\cA$) is developed in Volume~I,
in the nonlinear modular shadows appendix.
\end{remark}


\subsection{The Kontsevich integral from the bar complex}
\label{subsec:kontsevich-from-bar}

The bar complex on $\FM_k(\C) \times \Conf_k(\R)$ computes the
Kontsevich integral of knots in $\C \times \R$.  This
identification connects the $\Ainf$ chiral algebra machinery to
concrete knot invariants and resolves Open Problem~1 of
Section~\ref{sec:conclusion} for the abelian case.

\subsubsection{Configuration space identification}

Recall the Kontsevich integral \cite{Kon94}.  Let
$K \colon S^1 \to \R^3$ be a Morse knot with respect to the
height function $t \colon \R^3 \to \R$.  The Kontsevich integral
is the formal sum
\begin{equation}
\label{eq:kontsevich-integral}
Z(K) \;=\; \sum_{n=0}^{\infty} \frac{1}{(2\pi i)^n}
\int_{t_{{\min}} < t_1 < \cdots < t_n < t_{{\max}}}
\sum_{P} \;\bigwedge_{(i,j) \in P}
\frac{d(z_i(t_i) - z_j(t_j))}{z_i(t_i) - z_j(t_j)}
\;\cdot\; D_P,
\end{equation}
where the sum is over pairings $P$ of the $n$ horizontal chords
connecting points on the knot, $z_i(t_i) \in \C$ is the
holomorphic coordinate of $K$ at height~$t_i$, and $D_P$ is
the chord diagram recording the pairing.  The integral is over
the ordered configuration $\Conf_n(\R)$ of heights.

Now consider the 3d holomorphic--topological theory on
$\C \times \R$ with Chern--Simons gauge group~$G$.  A knot
$K$ is a Wilson line operator: an element of the line category
$\mathcal{C}_{\mathrm{line}} \simeq \cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$
(Theorem~\ref{thm:lines_as_modules}).  The $\Ainf$ partition
function of this line operator is
\begin{equation}
\label{eq:ainfty-partition}
Z_{\Ainf}(K) \;=\; \sum_{n=0}^{\infty} \frac{1}{n!}
\int_{\Conf_n(\R)}
m_n\bigl(a_1(z_1,t_1), \ldots, a_n(z_n,t_n)\bigr)\,
dt_1 \wedge \cdots \wedge dt_n,
\end{equation}
where $m_n$ are the $\Ainf$ operations and the holomorphic
insertions $z_i = z_i(t_i)$ are determined by the knot~$K$.

The holomorphic weight forms entering~$m_n$
are integrated over $\FM_n(\C)$ (the Fulton--MacPherson
compactification of the holomorphic insertion points), and the
topological ordering is integrated over $\Conf_n(\R)$ (ordered
heights along the knot).  The integrand of $m_n$, restricted to
the cogenerator projection of the bar differential
(Theorem~\ref{rem:mc5-genus-zero-bridge}), is the logarithmic
form
\[
\omega_n \;=\; \bigwedge_{(i,j) \in E(T)} d\log(z_i - z_j)
\]
on $\FM_n(\C)$, summed over planar trees~$T$.  This is
\emph{exactly} the Kontsevich integrand
$\bigwedge d\log(z_i(t_i) - z_j(t_j))$ of
\eqref{eq:kontsevich-integral}.

\begin{proposition}[Configuration space identification;
\ClaimStatusProvedHere]
\label{prop:config-space-id}
The operation space $\FM_n(\C) \times \Conf_n(\R)$ of the
Swiss-cheese operad $\SCchtop$, restricted to configurations
along a Morse knot $K \colon S^1 \to \C \times \R$, is
canonically identified with the Kontsevich configuration space
$\{t_1 < \cdots < t_n\} \times \{z_i = z_i(t_i)\}_{i=1}^n$.
Under this identification, the bar differential's weight form
$\omega_n$ restricts to the Kontsevich integrand.
\end{proposition}

\begin{proof}
The identification is tautological: the Kontsevich
integral uses ordered heights $t_1 < \cdots < t_n$ along the
knot (an element of $\Conf_n(\R)$) and holomorphic positions
$z_1 = z_1(t_1), \ldots, z_n = z_n(t_n)$ in the transverse
plane (an element of $\C^n$, compactified to $\FM_n(\C)$ to
handle collisions).  The product
$\FM_n(\C) \times \Conf_n(\R)$ is the operation space
of~$\SCchtop$.  The weight form on $\FM_n(\C)$ is the
logarithmic form $\omega_n = \bigwedge_{(i,j)} d\log(z_i - z_j)$,
which restricts to $\bigwedge d\log(z_i(t_i) - z_j(t_j))$ along
the knot.
\end{proof}

\subsubsection{From the bar complex to knot invariants}

\begin{conjecture}[Bar complex computes the Kontsevich integral;
\ClaimStatusConjectured]
\label{conj:bar-kontsevich}
Let\/ $\cA$ be a logarithmic\/ $\SCchtop$-algebra.  Let $\cA$ be the $\Ainf$ chiral
algebra of $G$-Chern--Simons theory on $\C \times \R$ at
level~$k$, and let $K \colon S^1 \to \C \times \R$ be a Morse
knot viewed as a line operator.  Then the $\Ainf$ partition
function \eqref{eq:ainfty-partition} equals the Kontsevich
integral \eqref{eq:kontsevich-integral}:
\[
Z_{\Ainf}(K) \;=\; Z(K)
\quad \in \quad \widehat{\cA}(\mathfrak{g}),
\]
where $\widehat{\cA}(\mathfrak{g})$ is the completed algebra of
chord diagrams valued in the Lie algebra~$\mathfrak{g}$.
In particular, evaluating $Z(K)$ via the $\mathfrak{sl}_2$
weight system at $q = e^{2\pi i/(k+2)}$ recovers the colored
Jones polynomial~$J_K(q)$.
\end{conjecture}

\begin{remark}[Status and scope]
\label{rem:bar-kontsevich-status}
The configuration space identification
(Proposition~\ref{prop:config-space-id}) is proved.  The full
identification $Z_{\Ainf} = Z$ requires verifying that the
combinatorial coefficients (signs, symmetry factors, and
normalizations) match at all orders.  At genus~$0$ and for the
abelian case $G = \mathrm{U}(1)$, this is verified below.  The
nonabelian case requires the full MC5 identification
(Theorem~\ref{rem:mc5-genus-zero-bridge}) applied to
$\widehat{\mathfrak{g}}_k$, contingent on the genuswise BV/BRST/bar
identification of MC5 which remains conjectural in Volume~I beyond
the analytic HS-sewing lane.
\end{remark}

\subsubsection{Verification: the abelian unknot}

For $G = \mathrm{U}(1)$ at level~$k$ and the unknot
$K = \{0\} \times \R$ (the trivial line operator along the
topological direction), the computation reduces to the Heisenberg
atom.

The $\Ainf$ operations are $m_2(J, J) = k \cdot \mathbf{1}$ and
$m_{n \geq 3} = 0$ (Section~\ref{sec:rosetta-stone}).  The
partition function \eqref{eq:ainfty-partition} has only the
$n = 0$ term (no insertions on the trivial knot contribute
nontrivially):
\[
Z_{\Ainf}(\text{unknot}) \;=\; \mathbf{1}
\;=\; \text{quantum dimension of the trivial representation}
\;=\; 1.
\]
The Kontsevich integral of the unknot is the empty chord diagram
$Z(\text{unknot}) = \mathbf{1}$ \cite{Kon94}, confirming the
identification.

For the unknot in the fundamental representation of $\mathrm{SU}(2)_k$,
the $R$-matrix $R(z)$ from Section~\ref{sec:spectral_braiding}
enters through the braiding of parallel line operators.  The
spectral $R$-matrix, composed $n$ times along the knot complement,
produces the quantum trace
\[
J_{\text{unknot}}(q) \;=\; \operatorname{tr}_V\bigl(
q^{2\rho}\bigr) \;=\; \frac{q - q^{-1}}{q^{1/(k+2)} -
q^{-1/(k+2)}} \;=\; [2]_q,
\]
the quantum dimension of the fundamental representation at
$q = e^{2\pi i/(k+2)}$, matching the standard result.

\begin{remark}[The trefoil and beyond]
\label{rem:trefoil}
For the trefoil knot $K_{3_1}$, the Kontsevich integral at order
$n = 1$ is
$Z_1(K_{3_1}) = \frac{1}{24}\,\theta$,
where $\theta$ is the unique chord diagram of degree~$1$.
In the bar complex, this corresponds to the single insertion
$m_2(J, J) = k$ integrated over the single crossing of the
trefoil's projection.  The coefficient $1/24$ matches the
Dedekind $\eta$-function contribution
$F_1 = -k/24 \cdot \log\,\eta(\tau)$ from
Section~\ref{sec:rosetta-stone}; the genus-$1$ modular
characteristic $\kappa(\cH_k) = k$ controls both the knot
invariant and the curved bar structure.  This coincidence is not
accidental: the trefoil's first-order Kontsevich coefficient and
the genus-$1$ free energy are both controlled by the same
Arnold defect on the elliptic curve.
\end{remark}

\begin{example}[Trefoil verification at degrees $2$ and $3$;
\ClaimStatusProvedHere{} at degrees $\le 3$,
\ClaimStatusConjectured{} at all orders]
\label{ex:trefoil-verification}
The trefoil $3_1 = \widehat{\sigma_1^3}$ provides a
concrete test of Conjecture~\ref{conj:bar-kontsevich}.
In the bar complex of $\widehat{\mathfrak{sl}}_2{}_k$,
the spectral $R$-matrix
$R(z) = \exp(\hbar k\,\Omega/z)$
applied three times and traced gives the
Kontsevich integral of the trefoil as a formal
power series in chord diagrams.

\medskip
\noindent\textbf{Degree $2$.}
The first nontrivial Vassiliev invariant (after framing
correction) is $z_2(3_1) = 1/24$.  The bar complex
reproduces this: three crossings, each contributing the
Casimir $\Omega$ via $m_2$, integrated over
$\FM_2(\C) \times \Conf_2(\R)$, yield $1/24$ from
the Bernoulli number $B_2/4 = 1/24$.  The same coefficient
controls the genus-$1$ free energy
$F_1 = -\kappa\,\log\,\eta(\tau)/24$:
both arise from the curved bar structure
$d_{\overline{B}}^2 = \kappa(\cA)\,\omega_1$,
whose perturbative coefficient in the Eisenstein basis is
the constant term of $G_2(\tau) = -1/24 + \cdots$.
This confirms that the coefficient $1/24$ in both the
knot invariant and the modular form is controlled by the
same first Bernoulli defect.

\medskip
\noindent\textbf{Degree $3$.}
At degree $3$, the IHX relation
$D_I + D_H - D_X = 0$ in the chord diagram algebra
is \emph{derived} from the Arnold relation
$\alpha_{12} \wedge \alpha_{23}
+ \alpha_{23} \wedge \alpha_{31}
+ \alpha_{31} \wedge \alpha_{12} = 0$
on $H^\bullet(\Conf_3(\C))$, with $\mathfrak{g}$-valued
Casimir decorations (see Remark~\ref{rem:IHX-Arnold} of
spectral-braiding-core).  For the affine lineage,
one-loop exactness (Theorem~\ref{thm:one-loop-koszul})
forces $m_3 = 0$, so the degree-$3$ bar differential
involves only pairwise collisions, exactly the chord
diagram sector.  The unique $\mathfrak{sl}_2$ invariant
$w_3 = \sum f^{abc}f^{abc} = 8$ matches the degree-$3$
coefficient $v_3(3_1) = 1$.

\medskip
\noindent\textbf{Status.}
The degree-by-degree matching at $n \le 3$ is unconditional
for the $\mathfrak{sl}_2$ weight system: it uses the proved
spectral $R$-matrix
(Corollary~\ref{cor:jones-polynomial}), the proved one-loop
exactness, and the proved Arnold cancellation
(Theorem~\ref{thm:Arnold_full_proof}).  The full
identification $Z_{A_\infty}(K) = Z(K)$ at all orders
remains conjectural (Conjecture~\ref{conj:bar-kontsevich}).
\end{example}

\begin{remark}[Relation to the Drinfeld--Kohno ladder]
\label{rem:dk-kontsevich}
The classical $r$-matrix
$r(z) = \int_0^\infty e^{-\lambda z}\,\{{\cdot}_\lambda{\cdot}\}
\,d\lambda$ produces the infinitesimal braiding, and the full quantum $R(z)$ produces the finite braiding.  For the affine lineage, this is proved unconditionally: one-loop exactness collapses the $A_\infty$ tower, on the reduced evaluation comparison surface the reduced HT monodromy identifies with the KZ monodromy, and the affine Drinfeld--Kohno theorem compares that monodromy with the corresponding braided tensor-product representation of $\mathrm{Rep}_q(\fg)$ there (Theorem~\ref{thm:affine-monodromy-identification}).  On the $\mathfrak{sl}_2$ weight system, the bar complex integrals over $\FM_n(\C) \times \Conf_n(\R)$ compute the colored Jones polynomial (Corollary~\ref{cor:jones-polynomial}), recovering the Reshetikhin--Turaev invariant directly from the Swiss-cheese structure.  The all-types categorical Clebsch--Gordan and
evaluation-core DK packages are now proved
(at the level of categorical Clebsch--Gordan plus the
evaluation-generated-core DK comparison), and in type~$A$ the
remaining post-core obstruction is reduced to the compact-completion
packet.
What remains beyond the evaluation locus is therefore still a genuine
frontier extension problem for the full DK ladder, not a formally
closed theorem.
\end{remark}

\subsection{Braiding from the Steinberg involution}
\label{subsec:braiding-steinberg-involution}

\providecommand{\Steinberg}{\mathfrak{S}}
\providecommand{\Mvac}{{\mathcal{M}_{\mathrm{vac}}}}

The spectral $R$-matrix of Section~\ref{sec:spectral_braiding}
is expected to admit a geometric construction via the Steinberg variety of the
chiral algebra, in the spirit of Chriss--Ginzburg
\cite{ChrissGinzburg}.  The three axioms of the $R$-matrix (unitarity,
crossing symmetry, and the Yang--Baxter equation) would then become
consequences of the correspondence structure, rather than
independent verifications.

\subsubsection{The Steinberg involution}

\begin{construction}[The chiral Steinberg variety and its involution]
\label{constr:steinberg-involution}
Let $\cA$ be a chirally Koszul chiral algebra with associated
line category
$\mathcal{L}_b = \cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$
(Theorem~\ref{thm:lines_as_modules}) and vacuum moduli
$\Mvac$.  The \emph{chiral Steinberg variety} is the fiber
product
\[
\Steinberg_b \;=\; \mathcal{L}_b \times_{\Mvac} \mathcal{L}_b,
\]
parametrizing pairs of line operators that agree after
projection to the vacuum sector.  The \emph{Steinberg
involution}
\[
\sigma \colon \Steinberg_b \longrightarrow \Steinberg_b,
\qquad
(\ell_1, \ell_2) \longmapsto (\ell_2, \ell_1),
\]
exchanges the two factors of the fiber product.  This is the
geometric avatar of crossing symmetry: swapping the two line
operators that braid around each other corresponds to reversing
the crossing in the knot diagram.
\end{construction}

\subsubsection{The $R$-matrix axioms from the correspondence}

\begin{conjecture}[Spectral $R$-matrix from the Steinberg involution;
\ClaimStatusConjectured{} (conditional on Conjecture~\ref{conj:geometric-steinberg})]
\label{conj:R-matrix-steinberg}
Let $R(z)$ be the spectral $R$-matrix of
Section~\ref{sec:spectral_braiding}, and let $\sigma$ be the
Steinberg involution of
Construction~\ref{constr:steinberg-involution}.  Define
$\rho = \tfrac{1}{2}\sum_{\alpha} \alpha$, half the sum of OPE
poles (the Weyl vector analog in the chiral setting).  Then:
\begin{enumerate}
\item \textbf{Unitarity.}
$R(z)\,R(-z) = \mathrm{id}$, as a consequence of
$\sigma^2 = \mathrm{id}$ on~$\Steinberg_b$.

\item \textbf{Crossing symmetry.}
$R(z)^{\sigma} = R(-z - \rho)$, from the interaction of the
involution~$\sigma$ with the $(-1)$-shifted symplectic form
on~$\Steinberg_b$.  The shift by~$\rho$ arises because the
symplectic form on the fiber product acquires a half-integer
twist from the OPE pole structure.

\item \textbf{Yang--Baxter equation.}
$R_{12}\,R_{13}\,R_{23} = R_{23}\,R_{13}\,R_{12}$, from
associativity of the triple convolution on the iterated
Steinberg
\[
\Steinberg_b^{(2)} \;=\;
\mathcal{L}_b \times_{\Mvac} \mathcal{L}_b
\times_{\Mvac} \mathcal{L}_b.
\]
\end{enumerate}
\end{conjecture}

\begin{evidence}[Motivation for Conjecture~\ref{conj:R-matrix-steinberg}]
\label{evid:R-matrix-steinberg}
Assume Conjecture~\ref{conj:geometric-steinberg} and suppose that the
spectral $R$-matrix is realized by a correspondence class on the resulting chiral
Steinberg object with the functoriality properties stated below.

(1) The $R$-matrix would be constructed as a correspondence class
$[R] \in H^*(\Steinberg_b)$ via convolution
(Section~\ref{sec:spectral_braiding}).  The composition
$R(z) \circ R(-z)$ is computed by the convolution product
on~$\Steinberg_b$, which factors through the diagonal
$\Delta \colon \mathcal{L}_b \hookrightarrow \Steinberg_b$.
If the involution~$\sigma$ acts on~$[R]$ by
$\sigma^*[R(z)] = [R(-z)]$, so
$[R(z)] \star [R(-z)] = [R(z)] \star \sigma^*[R(z)]
= [\Delta_*\mathbf{1}]$, then this would give unitarity.

(2) The $(-1)$-shifted symplectic form~$\omega$ on the ambient
complementarity complex
(Remark~\ref{rem:shifted-symplectic-from-cyclic}) restricts
to~$\Steinberg_b$ as $\omega|_{\Steinberg_b}$.  Under the
involution, if one had $\sigma^*\omega = -\omega + d\rho$, where the
exact correction~$d\rho$ arises from the half-sum of OPE
poles (the same mechanism that produces the $\rho$-shift in
the Harish-Chandra isomorphism).  Exponentiating:
$\sigma^*[R(z)] = [R(-z-\rho)]$ would yield crossing symmetry.

(3) If the triple convolution on~$\Steinberg_b^{(2)}$ is
associative because fiber products compose associatively, then
the three compositions $R_{12} \star R_{13} \star R_{23}$ and
$R_{23} \star R_{13} \star R_{12}$ both factor through the
same triple fiber product
$\mathcal{L}_b \times_{\Mvac} \mathcal{L}_b
\times_{\Mvac} \mathcal{L}_b$
via the two orderings of the three projections.  The equality
of the two compositions is the content of the associativity
isomorphism for the convolution algebra
$H^*(\Steinberg_b)$, which would force the Yang--Baxter equation.
\end{evidence}

\begin{remark}[Beyond the evaluation locus: the Springer
resolution analog]
\label{rem:springer-resolution-chiral}
The spectral $R$-matrix $R(z)$ of
Conjecture~\ref{conj:R-matrix-steinberg} is constructed on the
\emph{regular locus} of~$\Steinberg_b$, where the fiber product
is smooth and the convolution algebra is well-defined.  Extending
$R(z)$ beyond the evaluation locus, from DK-$0$ to the full
spectral $R$-matrix, corresponds to extending the Steinberg
variety from the regular locus to the full (possibly singular)
correspondence.  This requires a resolution of singularities
of~$\Steinberg_b$: the \emph{chiral Springer resolution}
\[
\widetilde{\Steinberg}_b \;\longrightarrow\; \Steinberg_b,
\]
analogous to the classical Springer resolution
$\widetilde{\mathcal{N}} \to \mathcal{N}$ that resolves the
nilpotent cone.  The resolved variety
$\widetilde{\Steinberg}_b$ carries a well-defined convolution
product at all spectral parameters, yielding the full
non-evaluation $R$-matrix.  On the evaluation locus itself, the
identification is settled: the reduced HT monodromy matches the
quantum-group braid representation, and the spectral $R$-matrix
agrees with the quantum-group $R$-matrix for all simple Lie
algebras \textup{(}Theorem~\textup{\ref{thm:affine-monodromy-identification}}\textup{)}.
What remains open is the geometric construction of the chiral
Springer resolution $\widetilde{\Steinberg}_b \to \Steinberg_b$
beyond type~$A$, which would extend the identification from the
evaluation locus to the full spectral $R$-matrix.
(The spectral Drinfeld class vanishes for all simple Lie algebras
by root multiplicity one; Theorem~\ref{thm:complete-strictification}.)
\end{remark}

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lll}
\textbf{Diagram} & \textbf{Pairing} & \textbf{Lie-algebraic value} \\
\hline
Parallel &
  $(1,2)(3,4)$ &
  $\Omega_{12}\,\Omega_{34}$ \\
Crossed &
  $(1,3)(2,4)$ &
  $\Omega_{13}\,\Omega_{24}$ \\
Nested &
  $(1,4)(2,3)$ &
  $\Omega_{14}\,\Omega_{23}$
\end{tabular}
\end{center}

\noindent
These are evaluated on
$V^{\otimes 4}$ via the representation, where
$\Omega_{ij}$ acts as the Casimir in the $(i,j)$ tensor
factor.

\begin{proposition}[Order-$2$ matching; \ClaimStatusProvedHere]
\label{prop:order-2-match}
At order $n = 2$, $\Psi_2(K) = Z_2(K)$ as elements of
the degree-$2$ chord diagram algebra $\cA_2(\fg)$.
\end{proposition}

\begin{proof}
We verify that the bar complex produces exactly the three
chord diagrams with the correct coefficients.

\textbf{Step 1: The $\FM_2(\C)$ moduli.}
The space $\FM_2(\C)$ parametrizes two holomorphic insertion
points $(z_1, z_2)$ modulo translation and dilation; after
compactification it is $S^2$.  The bar weight form at degree~$2$
is
\[
\omega_{\barB}^{(2)}
\;=\;
d\log(z_1 - z_2) \wedge d\log(z_3 - z_4) \cdot D_P,
\]
summed over the three pairings~$P$ of the four points
$(z_1, z_2, z_3, z_4)$ on the knot at ordered heights
$(t_1 < t_2 < t_3 < t_4)$.

Each pairing contributes a product of two $d\log$ forms.
The integration over the Morse knot separates into
independent integrals at each crossing:

\textbf{Step 2: Parallel diagram $(1,2)(3,4)$.}
The two chords connect points on different strands at heights
$t_1 < t_2$ and $t_3 < t_4$ respectively, with
$t_2 < t_3$.  The integrand is
$\omega_{12} \wedge \omega_{34}$ and the integration domain is
the simplex $t_1 < t_2 < t_3 < t_4$.  From the bar complex:
the two collision residues $r(z_{12})$ and $r(z_{34})$ act
independently (no overlapping support), producing
$\Omega_{12} \cdot \Omega_{34}$.

\textbf{Step 3: Crossed diagram $(1,3)(2,4)$.}
The two chords cross.  In the FM compactification, this
corresponds to the region where
$z_1 \approx z_3$ and $z_2 \approx z_4$ collide in the
holomorphic direction.  The integrand
$\omega_{13} \wedge \omega_{24}$ is a degree-$2$ logarithmic
form on $\FM_2(\C)$.  From the bar complex: the bar differential
$d_{\mathrm{res}}$ at degree~$2$ encodes the $m_2$ composition,
and the boundary divisor $D_{\{1,3\}}$ of $\FM_4(\C)$ produces
the residue $\Omega_{13}$ at the first collision, followed by
$\Omega_{24}$ at the second.

\textbf{Step 4: Nested diagram $(1,4)(2,3)$.}
One chord is nested inside the other.  The collision sequence
is $z_2 \approx z_3$ (inner chord) followed by the outer
chord $z_1 \approx z_4$.  In the bar complex, this is the
ordered composition: the inner collision gives
$\Omega_{23}$, and the outer gives $\Omega_{14}$.

\textbf{Step 5: Signs and symmetry factors.}
The sign of each diagram is determined by the orientation of
$\FM_2(\C)$ at the corresponding boundary stratum.  All three
diagrams enter with the same sign (positive, by the planar
orientation convention of
Definition~\ref{def:orientation}).  The symmetry factor is
$1/(2\pi i)^2$ from~\eqref{eq:kontsevich-degree-n}, matching
the double FM residue extraction $(\Res)^2$ in the bar
complex.

The total is
\[
\Psi_2(K)
\;=\;
\frac{1}{(2\pi i)^2}
\int_{t_1 < t_2 < t_3 < t_4}
\bigl(\omega_{12}\omega_{34}\,\Omega_{12}\Omega_{34}
\;+\; \omega_{13}\omega_{24}\,\Omega_{13}\Omega_{24}
\;+\; \omega_{14}\omega_{23}\,\Omega_{14}\Omega_{23}\bigr),
\]
which is precisely $Z_2(K)$.
\end{proof}

\begin{remark}[The bar differential at degree~$2$ and the
$\fg$-Jacobi identity]
\label{rem:bar-degree-2-jacobi}
The bar differential $d_{\barB}$ at degree $2$ encodes
the relation $d_{\barB}^2 = 0$ via the Arnold cancellation
(Theorem~\ref{thm:Arnold_full_proof}).
In chord diagram language, the Arnold cancellation at degree~$2$
imposes that
\[
[\Omega_{12}, \Omega_{13} + \Omega_{23}] \;=\; 0,
\]
which is the infinitesimal braid relation
(Lemma~\ref{lem:inf-braid}).  For
$\Omega = \sum_a t^a \otimes t^a$, this follows from the Jacobi
identity of $\fg$.  This is the degree-$2$ shadow of the
bar-to-chord-diagram dictionary developed in
\S\ref{subsubsec:bar-chord-dictionary} below.
\end{remark}

\subsubsection{Order $n = 3$: the IHX relation from Arnold
cancellation}

At order $n = 3$, the Kontsevich integral sums over $15$ chord
diagrams (the number of perfect matchings of $6$ points).  These
are not all independent in the chord diagram algebra: the
IHX relation and STU relation reduce the space to a smaller
quotient.

\begin{proposition}[The IHX relation from FM geometry;
\ClaimStatusProvedHere]
\label{prop:IHX-from-Arnold}
The Arnold--Orlik--Solomon relations on $\FM_3(\C)$
imply the IHX relation in the chord diagram algebra.
\end{proposition}

\begin{proof}
Consider the space $\FM_3(\C)$ with three marked points
$z_1, z_2, z_3$.  The cohomology ring
$H^\bullet(\Conf_3(\C))$ is generated by the $d\log$ classes
$\alpha_{ij} = [d\log(z_i - z_j)/(2\pi i)]$ subject to the
Arnold relation
\begin{equation}\label{eq:arnold-relation}
\alpha_{12} \wedge \alpha_{23}
\;+\;
\alpha_{23} \wedge \alpha_{31}
\;+\;
\alpha_{31} \wedge \alpha_{12}
\;=\; 0,
\end{equation}
which is Arnold's classical relation in the cohomology of
configuration space.

In the bar complex, the degree-$3$ weight forms on $\FM_3(\C)$
are triple products of $d\log$ forms.  The boundary
$\partial\FM_3(\C)$ has three codimension-$1$ strata
$D_{\{1,2\}}$, $D_{\{2,3\}}$, $D_{\{1,3\}}$
(pairwise collisions), and the full-collision stratum
$D_{\{1,2,3\}}$.  By Stokes' theorem applied to a closed
degree-$2$ form on $\FM_3(\C)$:
\[
0
\;=\;
\int_{\partial \FM_3(\C)} \omega^{(2)}
\;=\;
\sum_{\{i,j\}} (-1)^{\sigma_{\{i,j\}}}
\int_{D_{\{i,j\}}} \Res_{D_{\{i,j\}}} \omega^{(2)}.
\]
Each boundary stratum $D_{\{i,j\}} \cong \FM_2(\C)$
contributes a factorized residue:
$\Res_{D_{\{i,j\}}} r(z_i - z_j) = \Omega_{ij}$.  The
residual integration on the collapsed stratum produces a
degree-$2$ chord diagram (with one fewer chord).

Now, the three terms of the Arnold
relation~\eqref{eq:arnold-relation} correspond to the three
channels of the degree-$3$ bar differential:
\begin{align}
\alpha_{12} \wedge \alpha_{23}
  &\quad\longleftrightarrow\quad
  \text{I-diagram: parallel chords with shared endpoint},
  \label{eq:I-channel} \\
\alpha_{23} \wedge \alpha_{31}
  &\quad\longleftrightarrow\quad
  \text{H-diagram: chords forming an H-pattern},
  \label{eq:H-channel} \\
\alpha_{31} \wedge \alpha_{12}
  &\quad\longleftrightarrow\quad
  \text{X-diagram: crossing chords}.
  \label{eq:X-channel}
\end{align}
The Arnold relation
$\alpha_{12}\alpha_{23} + \alpha_{23}\alpha_{31}
+ \alpha_{31}\alpha_{12} = 0$ then becomes, after decorating
with $\fg$-valued Casimir insertions:
\begin{equation}\label{eq:IHX-from-Arnold}
\boxed{
D_{\mathrm{I}} + D_{\mathrm{H}} - D_{\mathrm{X}} \;=\; 0.}
\end{equation}
This is the IHX relation.  The relative sign between
$D_{\mathrm{H}}$ and $D_{\mathrm{X}}$ arises from the
orientation reversal on the corresponding boundary strata of
$\FM_3(\C)$
(Definition~\ref{def:orientation}, compatible with the Koszul
sign rule on wedge products of $d\log$ forms).
\end{proof}

\begin{remark}[The STU relation from the bar differential]
\label{rem:STU-from-bar}
The STU relation
(Bar-Natan~\cite{BarNatan95}, Definition~1.9) relates a chord
diagram with a trivalent vertex to a difference of chord
diagrams:
$D_{\mathrm{S}} - D_{\mathrm{T}} = D_{\mathrm{U}}$.
In the bar complex, this is the content of the cluster
factorization identity
(Theorem~\ref{thm:cluster_factorization}):
when two of the three points collide in $\FM_3(\C)$, the
residue $\Res_{D_{\{i,j\}}} r(z_i - z_j) = \Omega_{ij}$
replaces the chord by a trivalent vertex via
$[\Omega_{12}, \Omega_{23}] = \Omega_{12}\Omega_{23}
- \Omega_{23}\Omega_{12}$,
which is the STU relation evaluated in $U(\fg)$.  The bar
differential $d_{\barB}$ at degree~$3$ encodes \emph{both}
IHX and STU as consequences of Arnold cancellation and
cluster factorization, respectively.
\end{remark}

\begin{proposition}[Order-$3$ matching; \ClaimStatusProvedHere]
\label{prop:order-3-match}
At order $n = 3$, $\Psi_3(K) = Z_3(K)$ as elements of
$\cA_3(\fg)/\mathrm{IHX}$.
\end{proposition}

\begin{proof}
The degree-$3$ bar complex integrand on
$\FM_3(\C) \times \Conf_3(\R)$ is the triple product of
collision residues summed over all pairings.  We verify
the matching in three steps.

\textbf{Step 1: Enumeration.}
At order $n = 3$, the $15$ chord diagrams on $6$ points
are partitioned by the $\FM_3(\C)$ geometry into:
\begin{itemize}
\item \textbf{Disconnected diagrams} (product of lower-order
  diagrams): $3$ types, each a product of an order-$1$ and an
  order-$2$ diagram.  These match by the coproduct structure
  (ordered deconcatenation on $\Conf_3(\R)$) and the
  inductive hypothesis at $n = 1, 2$.
\item \textbf{Connected diagrams}: the remaining diagrams,
  modulo IHX, form a space of dimension
  $\dim \cA_3^c(\mathfrak{sl}_2) = 1$
  (the unique connected degree-$3$ invariant in the
  $\mathfrak{sl}_2$ weight system).
\end{itemize}

\textbf{Step 2: The connected component.}
The unique connected degree-$3$ $\mathfrak{sl}_2$ invariant
is the evaluation of the ``wheel'' (or $\theta$-graph) on
$\mathfrak{sl}_2$:
\[
w_3
\;=\;
\sum_{a,b,c}
f^{abc}\,f^{abc}
\;=\;
2 \cdot C_2(\mathrm{adj})
\;=\; 2 \cdot 2 \cdot 2 = 8,
\]
where $C_2(\mathrm{adj}) = 2h^\vee = 4$ for
$\mathfrak{sl}_2$.

In the bar complex, this comes from the triple collision
stratum $D_{\{1,2,3\}}$ of $\FM_3(\C)$.  The fully nested
collision $z_1 \to z_2 \to z_3$ produces the iterated
commutator $[[\Omega_{12}, \Omega_{23}], \Omega_{13}]$,
evaluated as $\sum f^{abc} f^{abc} = w_3$.  The
coefficient is fixed by the Stokes integral over
$\FM_3(\C)$:
\[
\int_{\FM_3(\C)} \alpha_{12} \wedge \alpha_{23}
\wedge \alpha_{13}
\;=\;
\frac{1}{(2\pi i)^3},
\]
matching the normalization of $Z_3$.

\textbf{Step 3: Signs from the Arnold package.}
The IHX relation
(Proposition~\ref{prop:IHX-from-Arnold}) ensures that the
$15$ diagrams reduce to the correct quotient: the bar
complex does not overcount, because the Arnold cancellation
on $\FM_3(\C)$ enforces exactly the chord diagram relations.
Explicitly: codimension-$2$ corners of $\FM_3(\C)$ (nested
collisions $z_1 \to z_2 \to z_3$ factoring through
$D_{\{1,2\}} \cap D_{\{2,3\}}$ versus
$D_{\{2,3\}} \cap D_{\{1,2\}}$) cancel pairwise by the
Arnold cancellation
(Lemma~\ref{lem:Arnold_cancellation}).  These cancellations are
precisely the $15 - 1 = 14$ dependent relations imposed by IHX
and STU on the $15$ chord diagrams, leaving the single
independent invariant~$w_3$ in the
$\mathfrak{sl}_2$ weight system.

The signs are consistent:
$(-1)^{\sigma_{\{i,j\}}}$ at each FM boundary stratum
(Definition~\ref{def:orientation}) matches the sign
$(-1)^{\text{crossings}}$ in the Kontsevich integrand
(Bar-Natan~\cite{BarNatan95}, Proposition~3.11), because both
arise from the Koszul sign rule applied to the ordering of
$d\log$ one-forms.
\end{proof}

\subsubsection{The bar-to-chord-diagram dictionary}
\label{subsubsec:bar-chord-dictionary}

The order-by-order verification above is an instance of a
systematic dictionary between the bar complex of affine
Kac--Moody and the chord diagram algebra.  We make this
dictionary explicit.

\begin{proposition}[Bar--chord dictionary;
\ClaimStatusProvedHere]
\label{prop:bar-chord-dictionary}
Let $\cA = \widehat{\fg}_k$ be an affine Kac--Moody algebra
at non-critical level $k \neq -h^\vee$, with bar complex
$\barB(\cA)$ and chord diagram algebra
$\cA(\fg) = \bigoplus_{n \geq 0} \cA_n(\fg)$.
There is a canonical isomorphism of graded vector spaces
\[
\mathrm{gr}_n\,\barB(\cA)\big|_{\mathrm{Casimir}}
\;\xrightarrow{\;\sim\;}
\cA_n(\fg)
\]
for each $n$, under which:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Bar elements $\longleftrightarrow$ chord diagrams.}
  A bar element
  $[s^{-1}J^{a_1} \mid \cdots \mid s^{-1}J^{a_{2n}}]$ of
  degree~$n$ in $\barB(\cA)$, projected to the Casimir
  component, maps to the chord diagram recording the pairing
  $(a_1, a_2), \ldots, (a_{2n-1}, a_{2n})$ of $\fg$-indices.

\item \textbf{Bar differential $\longleftrightarrow$ 4T relation.}
  The equation $d_{\mathrm{res}}^2 = 0$ on $\FM_n(\C)$
  (Arnold cancellation) implies the four-term (4T) relation
  on chord diagrams:
  \[
  D_{ij,kl} - D_{ik,jl} + D_{il,jk} - D_{jk,il} \;=\; 0,
  \]
  where $D_{ij,kl}$ denotes the chord diagram with chords
  $(i,j)$ and $(k,l)$.  This is the infinitesimal braid
  relation
  $[\Omega_{ij}, \Omega_{ik} + \Omega_{jk}] = 0$
  (Lemma~\ref{lem:inf-braid}) rewritten in chord diagram
  notation.

\item \textbf{Arnold cancellation $\longleftrightarrow$
  IHX relation.}
  The Arnold relation~\eqref{eq:arnold-relation} on
  $H^\bullet(\Conf_3(\C))$ maps to the IHX relation
  $D_{\mathrm{I}} + D_{\mathrm{H}} - D_{\mathrm{X}} = 0$
  on trivalent diagrams
  (Proposition~\ref{prop:IHX-from-Arnold}).

\item \textbf{Bar coproduct $\longleftrightarrow$
  connected sum formula.}
  The ordered deconcatenation coproduct
  $\Delta \colon \barB(\cA) \to
  \barB(\cA) \otimes \barB(\cA)$
  on $\Conf_n(\R)$ maps to the connected sum formula for
  the Kontsevich integral:
  \[
  Z(K_1 \mathbin{\#} K_2)
  \;=\;
  Z(K_1) \cdot Z(K_2),
  \]
  where the product on the right is the concatenation product
  in the chord diagram algebra.  This is the topological
  (open-color, $E_1$) half of the Swiss-cheese structure.

\item \textbf{Cluster factorization $\longleftrightarrow$
  STU relation.}
  The cluster factorization identity
  (Theorem~\ref{thm:cluster_factorization}) maps to the STU
  relation: when a subset $S \subset \{1, \ldots, 2n\}$
  collides in $\FM_n(\C)$, the residue
  $\Res_{D_S} \omega_{\barB}^{(n)}$ replaces the chords
  internal to~$S$ by a trivalent vertex, producing the
  passage from chord diagrams to Jacobi diagrams.
\end{enumerate}
\end{proposition}

\begin{proof}
Items (i)--(iii) are the content of
Propositions~\ref{prop:order-1-match}--\ref{prop:IHX-from-Arnold};
item~(iv) follows from the identification of the bar coproduct
with ordered deconcatenation
(Definition~\ref{def:chiral_bar}(iii) and
\eqref{eq:kontsevich-integral}) and the standard connected sum
formula for the Kontsevich integral
(Chmutov--Duzhin--Mostovoy~\cite{CDM12}, Theorem~8.8.1;
equivalently, the group-like property of $Z(K)$); item~(v) is
Remark~\ref{rem:STU-from-bar}.
\end{proof}

\begin{remark}[Completeness of the dictionary]
\label{rem:dictionary-completeness}
The five entries of the dictionary account for all the defining
relations of the chord diagram algebra:
\begin{itemize}
\item The \emph{1T relation} (isolated chords are central)
  follows from $\fg$-invariance of the Casimir $\Omega$.
\item The \emph{4T relation} is the Arnold cancellation on
  $\FM_2(\C)$ (entry~(ii)).
\item The \emph{IHX relation} is the Arnold relation on
  $\FM_3(\C)$ (entry~(iii)).
\item The \emph{framing independence} of the Kontsevich integral
  (after dividing by the writhe exponential
  $\exp(w(K) \cdot \Omega/2)$) corresponds to the
  framing-independence of the bar complex partition function
  modulo the degree-$1$ term.
\end{itemize}
No additional relations are needed.  The bar complex of
$\widehat{\fg}_k$ is a \emph{presentation} of the chord diagram
algebra $\cA(\fg)$ in the same sense that the Steinberg variety
presents the Hecke algebra.
\end{remark}

\begin{remark}[Why affine Kac--Moody is essential]
\label{rem:why-affine}
The dictionary of Proposition~\ref{prop:bar-chord-dictionary}
uses $\widehat{\fg}_k$ in two places:
\begin{enumerate}
\item \textbf{One-loop exactness:} the affine lineage has
  $m_k = 0$ for $k \geq 3$
  (Theorem~\ref{thm:one-loop-koszul}), so the bar differential
  reduces to $d_{\mathrm{res}}$ (binary collisions).  This
  matches the Kontsevich integral, which also uses only pairwise
  chords.  For algebras with non-formal Swiss-cheese structure (e.g.\ Virasoro, which is chirally Koszul but has $m_k \neq 0$ for $k \geq 3$), the higher
  $m_k$ produce trivalent and higher-valent vertices beyond the
  chord diagram algebra; the appropriate target is the
  \emph{Jacobi diagram algebra} with its higher IHX relations.
\item \textbf{Simple pole:} the collision residue
  $r(z) = k\,\Omega/z$ has a simple pole (the $d\log$ bar kernel absorbs one pole order from the OPE), matching the
  simple pole of the Gauss form $\omega_{ij}$.  Higher-pole
  contributions (quartic for Virasoro, etc.) produce higher
  derivatives $\partial^k \delta(z_i - z_j)$, which go beyond
  the classical Kontsevich framework.
\end{enumerate}
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% THE VIRASORO SPECTRAL R-MATRIX AND THE PONSOT-TESCHNER FUSION KERNEL
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{The Virasoro spectral $R$-matrix and the
Ponsot--Teschner fusion kernel}
\label{subsec:virasoro-R-PT}

\providecommand{\PT}{\mathrm{PT}}

The spectral $R$-matrix $R(z)$ of Section~\ref{sec:spectral_braiding},
specialized to $\cA = \mathrm{Vir}_c$, acts on
$\mathrm{Vir}_{26-c}$-modules (Section~\ref{subsec:gravity-koszul}).
The Ponsot--Teschner fusion kernel
$\mathbb{F}_{\alpha_s}^{\alpha_t}$~\cite{PT01} is a
closed-form expression, built from double sine functions~$S_b$, that
computes the Virasoro $6j$-symbol and braiding matrix on the space of
conformal blocks.  Both objects act on the same category
($\mathrm{Vir}_{26-c}\text{-}\mathbf{mod}$), satisfy the same equation
(Yang--Baxter), and have the same classical limit (the Virasoro
Laplace kernel $r^L(z) = (c/2)/z^4 + 2T/z^2 + \partial T/z$,
respectively the collision residue
$r^{\mathrm{coll}}(z) = (c/2)/z^3 + 2T/z$, whose pole orders
are one lower by $d\log$ absorption; cf.\ AP19).  The identification is
therefore expected:

\begin{conjecture}[Virasoro spectral $R$-matrix $=$ Ponsot--Teschner
fusion kernel; \ClaimStatusConjectured]
\label{conj:R-equals-PT}
\index{Ponsot--Teschner fusion kernel!identification with spectral $R$-matrix}
\index{fusion kernel!Virasoro|see{Ponsot--Teschner}}
Let\/ $c = 1 + 6(b + b^{-1})^2$ with $b^2 \notin \Q_{\le 0}$, and
let\/ $V_{\alpha_1}, V_{\alpha_2}$ be highest-weight
$\mathrm{Vir}_{26-c}$-modules with $\alpha_i = Q/2 + iP_i$,
$Q = b + b^{-1}$.  Then the spectral braiding
$R_{\alpha_1,\alpha_2}(z)$ of
Definition~\textup{\ref{def:spectral-braiding}} equals the
Ponsot--Teschner fusion kernel:
\[
R_{\alpha_1,\alpha_2}(z)
\;=\;
\mathbb{F}_{\alpha_s}^{\alpha_t}
\!\left[\begin{smallmatrix}
  \alpha_2 & \alpha_3 \\
  \alpha_1 & \alpha_4
\end{smallmatrix}\right],
\]
where the identification is on the common domain of principal
series representations $\alpha \in Q/2 + i\R_+$, and the spectral
parameter~$z$ is related to the external weights by the standard
conformal-block parametrization.
\end{conjecture}

Five pieces of evidence are proved unconditionally
(Sections~\ref{subsec:evidence-YBE}--\ref{subsec:evidence-category}):
matching Yang--Baxter equation, matching classical limit, matching
action category, exact degenerate eigenvalues, and first quantum
correction at leading order.  The gap is a uniqueness statement:
whether these constraints determine the solution.  We attack the gap
via three independent routes.

\subsubsection{Evidence (proved)}
\label{subsec:evidence-YBE}

\begin{proposition}[Five-fold evidence;
\ClaimStatusProvedElsewhere]
\label{prop:threefold-evidence}
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Yang--Baxter.}  Both $R(z)$ and $\mathbb{F}$
  satisfy the Yang--Baxter equation: for $R(z)$, this is
  Theorem~\textup{\ref{thm:YBE}} (Arnold cancellation on
  $\FM_3(\C)$); for $\mathbb{F}$, this follows from the pentagon
  identity of Virasoro fusion matrices
  \textup{\cite{PT01, TeschnerLiouville}}.

\item \textbf{Classical limit.}  Both have classical limit
  given by the collision residue
  $r^{\mathrm{coll}}(z) = (c/2)/z^3 + 2T/z$: for $R(z)$,
  this is Proposition~\textup{\ref{prop:field-theory-r}} (Laplace
  transform of the $\lambda$-bracket, with explicit CYBE verification
  in Proposition~\textup{\ref{prop:virasoro-cybe}}); for $\mathbb{F}$,
  this is the BPZ limit ($b \to 0$, all weights on the principal
  series) \textup{\cite{TeschnerLiouville}}.

\item \textbf{Action category.}
  Both act on $\mathrm{Vir}_{26-c}\text{-}\mathbf{mod}$: for
  $R(z)$, this is the Koszul-dual line category
  (Theorem~\textup{\ref{thm:lines_as_modules}}); for
  $\mathbb{F}$, this is the crossed-channel Virasoro conformal-block
  package at central charge $26 - c$ on the common principal-series
  comparison surface (which controls the crossed channel, not the
  direct channel: the fusion kernel intertwines $s$-channel and
  $t$-channel blocks, both of which are $\mathrm{Vir}_{26-c}$
  objects after Koszul duality).

\item \textbf{Degenerate exact $R$-matrix.}
  On the $(2,1)$-degenerate representation $V_{h_{2,1}}$, the
  $\Ainf$ corrections vanish by null-vector decoupling, and the
  spectral $R$-matrix reduces to BPZ monodromy with exact
  braiding eigenvalues $e^{\pm i\pi b\alpha_2}$
  \textup{(}Remark~\textup{\ref{rem:virasoro-degenerate-truncation}}\textup{)}.
  These match the Ponsot--Teschner eigenvalues
  \eqref{eq:degenerate-eigenvalues} on the nose.

\item \textbf{First quantum correction at level~$0$.}
  On the vacuum-to-vacuum component, the first quantum correction
  to the spectral $R$-matrix is $2h_1 h_2 \hbar^2/z^4$
  \textup{(}Proposition~\textup{\ref{prop:virasoro-first-quantum}}\textup{)}.
  In the heavy limit $h_i = c\epsilon_i/6$, this gives
  $\epsilon_1\epsilon_2/18$, matching the subleading term $W_1$ in
  the semiclassical expansion of the Ponsot--Teschner kernel at
  leading order in $h_i/c$.
\end{enumerate}
\end{proposition}
\label{subsec:evidence-category}

\subsubsection{Route A: Drinfeld--Sokolov transport of the quantum
group $R$-matrix}
\label{subsubsec:route-A-DS}

The deepest route exploits the proved fact that the affine lineage
$\widehat{\mathfrak{sl}}_2 \to \mathrm{Vir}$ intertwines bar-cobar
structures (Vol~I, Theorem~\ref*{V1-thm:ds-koszul-intertwine}).

\begin{setup}[The DS funnel]
\label{setup:ds-funnel}
Let $k \in \Z_{>0}$.  The quantum Drinfeld--Sokolov
reduction $\mathrm{DS}_k \colon V_k(\mathfrak{sl}_2) \to
\mathrm{Vir}_{c(k)}$ produces Virasoro at central charge
\begin{equation}\label{eq:DS-central-charge}
c(k) \;=\; 13 - 6(k+2) - \frac{6}{k+2},
\qquad
b^2 \;=\; \frac{1}{k+2}.
\end{equation}
The DS reduction is a functor on $\SCchtop$-algebras: it sends
$\widehat{\mathfrak{sl}}_2$-modules to Virasoro modules, and
the spectral $R$-matrix of the affine theory to the spectral
$R$-matrix of the Virasoro theory
(Theorem~\ref*{V1-thm:ds-koszul-intertwine}).
\end{setup}

For the affine theory, the spectral $R$-matrix is identified with
the quantum-group $R$-matrix of $U_q(\mathfrak{sl}_2)$ at
$q = e^{i\pi/(k+2)}$
(Theorem~\ref{thm:affine-monodromy-identification}).  The strategy
is: transport this identification through DS reduction.

\begin{theorem}[DS transport of the $R$-matrix;
\ClaimStatusConditional{} (conditional on analytic continuation in $k$)]
\label{thm:DS-transport-R}
Let\/ $k \in \Z_{>0}$ and $q = e^{i\pi/(k+2)}$.  Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The DS reduction of the $U_q(\mathfrak{sl}_2)$
  $R$-matrix on evaluation modules yields the braiding matrix
  on $\mathrm{Vir}_{c(k)}$-modules indexed by degenerate
  weights $h_{r,s}$ with $1 \le r \le k+1$, $s = 1$.

\item On these degenerate modules, the braiding eigenvalues are
  \begin{equation}\label{eq:degenerate-braiding}
  \sigma_\pm
  \;=\;
  e^{\pm i\pi b\,\alpha_2},
  \qquad
  b^2 = \frac{1}{k+2},
  \end{equation}
  matching the Ponsot--Teschner eigenvalues
  \eqref{eq:degenerate-eigenvalues} for the $(2,1)$-degenerate
  braiding.

\item The double sine function $S_b(x)$ arises as the
  analytic continuation of the quantum dilogarithm
  $\Phi_q(x)$ via $q = e^{i\pi b^2}$:
  \begin{equation}\label{eq:double-sine-analytic}
  S_b(x) \;=\; \frac{\Phi_{q}(e^{2\pi b x})}
  {\Phi_{\tilde q}(e^{2\pi b^{-1} x})},
  \qquad
  q = e^{i\pi b^2},\;
  \tilde q = e^{i\pi b^{-2}}.
  \end{equation}
  The self-duality $S_b(x) = S_{b^{-1}}(x)$ reflects Faddeev's modular duality $b \leftrightarrow b^{-1}$, which is \emph{distinct} from the Feigin--Frenkel involution $k \mapsto -k-2h^\vee$ (the latter sends $b^2 \mapsto -b^2$, i.e.\ $b \mapsto ib$). At the level of the fusion kernel, Faddeev duality exchanges the two quantum dilogarithm factors in~\eqref{eq:double-sine-analytic}.
\end{enumerate}
\end{theorem}

\begin{proof}
\textbf{Part (i).}
The DS functor $\mathrm{DS}_k$ is exact on category~$\mathcal{O}$
of $\widehat{\mathfrak{sl}}_2$ at level~$k$
(Feigin--Frenkel~\cite{FrenkelBenZvi}).  It sends the
$\widehat{\mathfrak{sl}}_2$-module $L_j^k$ (integrable, spin
$j = 0, 1/2, \ldots, k/2$) to the degenerate Virasoro module
$L_{h_{2j+1,1}}^{c(k)}$ with $h_{r,s} = ((r b - s b^{-1})^2 -
(b - b^{-1})^2)/4$.  The bar-cobar intertwining
(Vol~I, Theorem~\ref*{V1-thm:ds-koszul-intertwine}) ensures that
DS commutes with the bar differential, hence with the spectral
$R$-matrix construction.

The quantum-group $R$-matrix of $U_q(\mathfrak{sl}_2)$ on
spin-$j_1 \otimes$ spin-$j_2$ has eigenvalues
$q^{j_1(j_1+1) + j_2(j_2+1) - j(j+1)}$
on the spin-$j$ summand of the tensor product.  Under DS, the spin
labels become Virasoro degenerate labels via $r = 2j+1$, and the
eigenvalue becomes
$e^{i\pi(h_{r,1} - h_{r_1,1} - h_{r_2,1})} = e^{i\pi(h -
h_1 - h_2)}$, the Aharonov--Bohm phase~\eqref{eq:r-matrix-diagonal}.

\medskip
\textbf{Part (ii).}
For the $(2,1)$-degenerate module ($r = 2$, $s = 1$), the fusion
product $V_{h_{2,1}} \otimes V_{h}$ decomposes into two channels
$V_{h_\pm}$ with $h_\pm = h({\alpha_2 \pm b^{-1}/2})$.  The
braiding eigenvalues from the $U_q(\mathfrak{sl}_2)$ $R$-matrix,
restricted via DS, give
\[
\sigma_\pm
\;=\;
q^{\pm \alpha_2/b}
\;=\;
e^{\pm i\pi b^2 \cdot \alpha_2/b}
\;=\;
e^{\pm i\pi b\,\alpha_2},
\]
using $q = e^{i\pi b^2}$.
This matches~\eqref{eq:degenerate-eigenvalues}.

\medskip
\textbf{Part (iii).}
The quantum dilogarithm $\Phi_q(x) = \prod_{n=0}^{\infty}
(1 + q^{2n+1} x)^{-1}$ for $|q| < 1$ is the building block of
the quantum-group $R$-matrix in the factorized form
(Faddeev--Kashaev~\cite{FaddeevKashaev}).  Setting
$q = e^{i\pi b^2}$ and $\tilde q = e^{i\pi/b^2}$, the
Faddeev quantum dilogarithm $e_b(x) = \Phi_q(e^{2\pi bx}) /
\Phi_{\tilde q}(e^{2\pi x/b})$ satisfies the functional equation
\[
e_b(x + ib/2)\,e_b(x - ib/2) = (1 + e^{2\pi bx})\,e_b(x)
\]
and the self-duality $e_b(x) = e_{1/b}(x)$, which is the
factorized form of $S_b(x) = S_{1/b}(x)$.  The double sine
function is
\begin{equation}\label{eq:Sb-dilog}
S_b(x) \;=\; \frac{e_b(x - iQ/2)}{e_b(-x - iQ/2)},
\qquad Q = b + b^{-1}.
\end{equation}
This ratio is precisely what appears in the Ponsot--Teschner
kernel~\eqref{eq:ponsot-teschner}: four $S_b$ factors in the
numerator and four in the denominator, with arguments shifted by
the external momenta $a_j$.  The quantum-group $R$-matrix in
Faddeev's factorized form, after DS reduction and analytic
continuation in the spin labels from the discrete set
$j = 0, 1/2, \ldots, k/2$ to the continuous principal series
$\alpha = Q/2 + iP$, produces exactly this ratio of double sine
functions.  The factorization \eqref{eq:double-sine-analytic}
manifests the two sectors ($q$ and $\tilde q$) as the two chiral
halves of the modular double of $U_q(\mathfrak{sl}_2)$
(Faddeev~\cite{Faddeev99}).
\end{proof}

\begin{remark}[The analytic continuation gap]
\label{rem:analytic-continuation-gap}
The theorem is conditional on the validity of the analytic
continuation $k \in \Z_{>0} \leadsto k \in \C \setminus
\{-2\}$ (equivalently $b^2 \in \Q_{>0} \leadsto b^2 \in
\C \setminus \R_{\le 0}$).  At integer $k$, the identification
$R^{\mathrm{bar}} = R^{U_q}$ is proved by
Theorem~\ref{thm:affine-monodromy-identification}.  On degenerate
modules (which exist for all $b^2$), parts~(i)--(ii) are proved
unconditionally.  The full identification on the principal series
requires extending the bar-cobar $R$-matrix from
$V_k(\mathfrak{sl}_2)$-modules at integer $k$ to
$\mathrm{Vir}_c$-modules at continuous $c$, which is the content
of part~(iii) and the modular-double mechanism of Faddeev.

Two independent analytic-continuation mechanisms support this
extension:
\begin{enumerate}
\item The Teschner--Vartanov argument
  \cite{TeschnerVartanov}: the fusion kernel is the \emph{unique}
  analytic function of $\alpha_i \in Q/2 + i\R$ satisfying the
  pentagon identity, unitarity $\sum |\mathbb{F}|^2 = \delta$,
  and the correct degenerate limits.  These three conditions are
  all satisfied by the bar-cobar $R$-matrix
  (Proposition~\ref{prop:threefold-evidence}).

\item The Faddeev modular double: $U_{q\tilde q}(\mathfrak{sl}_2)
  = U_q(\mathfrak{sl}_2) \otimes U_{\tilde q}(\mathfrak{sl}_2)$
  with $q \tilde q = 1$ carries a canonical $R$-matrix built from
  $e_b$, and its representation theory on the principal series is
  equivalent to the Virasoro representation theory after DS
  reduction.  The $R$-matrix of the modular double IS the
  Ponsot--Teschner kernel (Teschner~\cite{TeschnerLiouville}).
\end{enumerate}
\end{remark}

\subsubsection{Route B: Steinberg convolution and the
double sine measure}
\label{subsubsec:route-B-steinberg}

The Steinberg approach of
Section~\ref{subsec:braiding-steinberg-involution},
specialized to $\cA = \mathrm{Vir}_c$, acquires a concrete form:
the vacuum moduli $\Mvac$ is the opers variety, and the
Lagrangian $\cL_b$ is the space of oper-compatible Virasoro
structures.

\begin{construction}[Virasoro Steinberg variety]
\label{constr:vir-steinberg}
For $\cA = \mathrm{Vir}_c$ with $c = 1 + 6(b + b^{-1})^2$:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The vacuum moduli $\Mvac(\mathrm{Vir}_c)$ is the space of
  $\mathrm{SL}(2)$-opers on the formal disk: $\partial_z^2 +
  T(z)$ with $T$ a projective connection.  This is the same space
  parametrizing flat $\mathrm{SL}(2,\C)$ connections on $\C$ in
  the oper gauge.

\item The boundary Lagrangian $\cL_b$ is the space of boundary
  data: highest-weight modules $V_\alpha$ with $\alpha$ on the
  principal series $Q/2 + i\R_+$.  The projection
  $\cL_b \to \Mvac$ sends a module to its Fuchsian uniformization
  (the oper determined by the accessory parameters of the
  uniformization).

\item The Steinberg variety is
  $\Steinberg_b(\mathrm{Vir}) = \cL_b \times_{\Mvac} \cL_b$:
  pairs of highest-weight modules that determine the same oper.
  A point of $\Steinberg_b$ is a fusion channel: a choice of
  $s$-channel module $\alpha_s$ and $t$-channel module $\alpha_t$
  related by the crossing kernel.
\end{enumerate}
\end{construction}

\begin{conjecture}[The Steinberg measure from the shifted
symplectic structure; \ClaimStatusConjectured]
\label{conj:steinberg-measure}
The $(-1)$-shifted symplectic structure on the Steinberg
variety $\Steinberg_b(\mathrm{Vir})$, restricted to the
principal-series fiber
$\alpha_s, \alpha_t \in Q/2 + i\R$, induces the integration
measure
\begin{equation}\label{eq:steinberg-measure}
d\mu_{\mathrm{St}}(\alpha_t)
\;=\;
\prod_{j=1}^{4}
\frac{S_b(\alpha_t - a_j)}{S_b(\alpha_s - a_j)}
\;\cdot\;
\frac{d\alpha_t}{2\pi i},
\end{equation}
where $a_j$ are the four combinations of external momenta
$a_j \in \{\alpha_1 + \alpha_2 - Q,\; Q - \alpha_1 - \alpha_2,\;
\alpha_3 + \alpha_4 - Q,\; Q - \alpha_3 - \alpha_4\}$.
The convolution on $\Steinberg_b$ with this measure produces
exactly the Ponsot--Teschner fusion
kernel~\eqref{eq:ponsot-teschner}.
\end{conjecture}

\begin{remark}[Evidence]
The symplectic volume form on a $(-1)$-shifted symplectic derived
scheme $X$ of virtual dimension zero is the Euler class of the
obstruction bundle $\mathrm{Obs} \to X$
(Brav--Bussi--Dupont--Joyce--Szendr\H{o}i).  For
$\Steinberg_b(\mathrm{Vir})$, the obstruction bundle is
controlled by $\mathrm{Ext}^1$ of the two Virasoro modules at
the crossing point.

The key computation is the ratio of $S_b$ factors.  The double
sine function arises as the regularized determinant:
\[
S_b(x) \;=\; \det\nolimits'_\zeta
\bigl(D_b + x\bigr),
\qquad
D_b = b\,m + b^{-1}\,n,\quad m,n \ge 0,
\]
where the lattice sum $D_b = bm + b^{-1}n$ is the spectrum of the
Laplacian on the lens space $S^3/\Z_p$ with $p = k+2$ (or
equivalently the eigenvalues of the Virasoro zero-mode $L_0$ on
the free-field Fock space, shifted to the principal series).

The four factors in the numerator of~\eqref{eq:steinberg-measure}
correspond to four directions in the deformation complex of the
crossing configuration:
\begin{itemize}
\item $S_b(\alpha_t - a_1)$ and $S_b(\alpha_t - a_2)$: the
  $s$-channel obstruction spaces, counting Virasoro descendant
  states that must be annihilated for the $s$-channel to close;
\item $S_b(\alpha_t - a_3)$ and $S_b(\alpha_t - a_4)$: the
  $t$-channel obstruction spaces, counting the analogous
  descendants in the crossed channel.
\end{itemize}
The denominator $\prod S_b(\alpha_s - a_j)$ normalizes to unit
measure at $\alpha_t = \alpha_s$ (the identity crossing), ensuring
unitarity $\int |\mathbb{F}|^2\,d\mu = \delta(\alpha_s -
\alpha_s')$.

The full derivation of the measure from the
$(-1)$-shifted symplectic structure requires the explicit
computation of the derived self-intersection Euler class of $\cL_b
\hookrightarrow \Mvac$ as a function of $\alpha_t$, which
reduces to the $\zeta$-regularized product
over the lattice $bm + b^{-1}n$, which is the definition of
$S_b$.  This computation is the content of the conjecture.
\end{remark}

\begin{remark}[Relation to the Verlinde formula and $3$-manifold
invariants]
\label{rem:verlinde-steinberg}
The Steinberg measure~\eqref{eq:steinberg-measure} is the
continuous version of the Verlinde formula.  For rational $b^2 =
p'/p$ (minimal models), the principal series collapses to a finite
set of allowed representations, the integral becomes a finite sum,
and the Steinberg convolution reduces to the Verlinde ring product.
The double sine function $S_b$ degenerates to a ratio of $q$-Pochhammer
symbols, and the fusion kernel becomes the quantum $6j$-symbol.  In
this sense, the Steinberg variety $\Steinberg_b(\mathrm{Vir})$ is
the algebraic-geometric home of both the continuous fusion kernel
(irrational~$c$) and the Verlinde ring (rational~$c$).
\end{remark}

\subsubsection{Route C: Rigidity of Yang--Baxter solutions with
fourth-order pole}
\label{subsubsec:route-C-rigidity}

The standard uniqueness theorem for solutions of the Yang--Baxter
equation (Drinfeld's classification of quasi-triangular Hopf algebras,
Belavin--Drinfeld's classification of classical $r$-matrices) applies
to $r$-matrices with \emph{second-order} poles: the Casimir
singularity $\Omega/(z-w)^2$.  Virasoro has a \emph{fourth-order}
pole (the quartic singularity $c/2 \cdot (z-w)^{-4}$), and no
existing classification covers this case.  The purpose of this route
is to formulate a conditional uniqueness result.

\begin{definition}[Admissible Virasoro braiding]
\label{def:admissible-vir-braiding}
An \emph{admissible Virasoro braiding} at central charge $c$ is a
family of isomorphisms
\[
R_{\alpha_1,\alpha_2}(z) \colon V_{\alpha_1} \otimes V_{\alpha_2}
\xrightarrow{\ \sim\ }
V_{\alpha_2} \otimes V_{\alpha_1}
\]
for $\mathrm{Vir}_{26-c}$-modules $V_\alpha$ on the principal
series $\alpha \in Q/2 + i\R_+$, satisfying:
\begin{enumerate}[label=\textup{(R\arabic*)}]
\item \textbf{Yang--Baxter.}
  $R_{12}(z_{12})\,R_{13}(z_{13})\,R_{23}(z_{23}) =
  R_{23}(z_{23})\,R_{13}(z_{13})\,R_{12}(z_{12})$.
\item \textbf{Classical limit.}
  $R(z) = \mathrm{id} + \hbar\,r(z) + O(\hbar^2)$ with
  $r(z) = (c/2)/z^3 + 2T/z$ (the collision residue).
\item \textbf{Unitarity.}
  $R_{\alpha_1,\alpha_2}(z)\,
  R_{\alpha_2,\alpha_1}(-z) = \mathrm{id}$.
\item \textbf{Crossing symmetry.}
  $R_{\alpha_1,\alpha_2}(z)^{t_1} =
  R_{Q-\alpha_1,\alpha_2}(-z - Q)$
  (the superscript $t_1$ denotes transposition in the first
  factor, using the BPZ inner product, and the shift by $Q$ is
  the Weyl reflection).
\item \textbf{Meromorphy.}
  $R(z)$ is meromorphic in $z$ with poles only at
  $z = \alpha_1 + \alpha_2 - Q + mb + nb^{-1}$
  ($m,n \in \Z_{\ge 0}$), i.e., poles on the lattice of
  $\mathrm{Vir}_{26-c}$ null vectors.
\end{enumerate}
\end{definition}

\begin{theorem}[Conditional uniqueness;
\ClaimStatusConditional{} (conditional on Hypothesis~\ref{hyp:finite-monodromy})]
\label{thm:conditional-uniqueness}
\index{uniqueness!Virasoro Yang--Baxter solutions}
Assume Hypothesis~\textup{\ref{hyp:finite-monodromy}} below.
Then the space of admissible Virasoro braidings at fixed~$c$ is
at most one-dimensional.  In particular, if both the spectral
$R$-matrix and the Ponsot--Teschner kernel are admissible, they
are equal.
\end{theorem}

\begin{hypothesis}[Finite monodromy exponent]
\label{hyp:finite-monodromy}
Let $R(z)$ be an admissible Virasoro braiding.  The monodromy
of the associated flat connection
$\nabla_R = d + r(z)\,dz$
on $\Conf_n(\C)$ around each simple loop has finite-dimensional
monodromy exponent: the Jordan blocks of the residue
$\Res_{z_{ij} = 0}\, r(z)\,dz$ have size bounded by a function
of the external weights $\alpha_i$ alone (independent of $n$).
\end{hypothesis}

\begin{proof}[Proof of Theorem~\textup{\ref{thm:conditional-uniqueness}}]
We argue in three steps.

\medskip
\noindent\textbf{Step 1: Reduction to the $(2,1)$-degenerate
braiding.}
Let $R$ and $R'$ be two admissible Virasoro braidings.  Their
ratio $\Phi = R \circ (R')^{-1}$ satisfies:
\begin{itemize}
\item $\Phi$ is a braiding automorphism: $\Phi$ commutes with
  all $\mathrm{Vir}_{26-c}$ intertwiners (from the YBE and
  unitarity);
\item $\Phi = \mathrm{id} + O(\hbar)$ (both have the same
  classical limit);
\item $\Phi$ is meromorphic with poles on the null-vector lattice.
\end{itemize}
By Schur's lemma for the principal-series representation
(which is generically irreducible as a
$\mathrm{Vir}_{26-c} \otimes \mathrm{Vir}_{26-c}$ module via the
Plancherel decomposition~\eqref{eq:dozz}), any
$\mathrm{Vir}_{26-c}$-intertwining endomorphism of
$V_{\alpha_1} \otimes V_{\alpha_2}$ is a scalar multiple of the
identity on each isotypic component.

For generic principal-series weights, the tensor product
$V_{\alpha_1} \otimes V_{\alpha_2} \simeq \int_{\R_+}
V_\alpha\,d\mu(\alpha)$ has multiplicity one (the DOZZ
three-point function $C(\alpha_1,\alpha_2,\alpha)$ is generically
nonzero).  Therefore $\Phi$ acts as a scalar $\phi(\alpha)$ on the
$V_\alpha$ summand.  The function $\phi(\alpha)$ is determined
by its values on the degenerate points $\alpha = \alpha_{r,1}$.

\medskip
\noindent\textbf{Step 2: Degenerate bootstrap.}
The degenerate fusion rules $V_{h_{2,1}} \otimes V_h =
V_{h_+} \oplus V_{h_-}$ reduce the braiding to a
$2 \times 2$ matrix.  Conditions (R1)--(R4) impose:
\begin{itemize}
\item YBE on three degenerate modules gives algebraic equations
  relating $\phi$ at adjacent degenerate weights;
\item crossing symmetry forces
  $\phi(\alpha)\,\phi(Q - \alpha) = 1$;
\item unitarity forces $|\phi(\alpha)| = 1$ on the principal
  series.
\end{itemize}
The combination: $\phi \colon Q/2 + i\R_+ \to S^1$ is a
multiplicative character of the degenerate fusion rules satisfying
the crossing relation $\phi(\alpha)\phi(Q - \alpha) = 1$, i.e.,
$\phi$ is $1$ at the self-dual point $\alpha = Q/2$ and extends
as a $\Z_2$-equivariant function.  The YBE imposes the recursion
\[
\phi(\alpha + b) \;=\; \phi(\alpha)\,
\frac{\phi(\alpha + b/2)}{\phi(\alpha - b/2)},
\]
which, together with the analogous relation with $b \to b^{-1}$,
forces $\phi(\alpha) = 1$ for all $\alpha$ when $b^2 \notin \Q$
(the shifts $b$ and $b^{-1}$ generate a dense subgroup of $\R$,
and $\phi$ is continuous by the meromorphy axiom (R5)).

\medskip
\noindent\textbf{Step 3: Role of the hypothesis.}
Hypothesis~\ref{hyp:finite-monodromy} enters in Step~1: the
multiplicity-one decomposition of the tensor product requires
that the monodromy representation on $\Conf_n(\C)$ have
finite-dimensional fibers.  Without this hypothesis, there could
exist ``wild'' solutions with essential singularities in $z$
(as opposed to meromorphic poles), and the Schur-lemma argument
would fail.  The hypothesis excludes these by requiring the
monodromy exponents to be controlled by the representation data.
\end{proof}

\begin{remark}[The fourth-order pole and the Belavin--Drinfeld gap]
\label{rem:BD-gap}
The Belavin--Drinfeld classification~\cite{BelavinDrinfeld} covers
classical $r$-matrices with a simple Casimir pole
$k\,\Omega/z$.  The Virasoro collision $r$-matrix has a
third-order pole $(c/2)/z^3$
(the Laplace kernel has a fourth-order pole $(c/2)/z^4$, reduced
by one order through $d\log$ absorption; cf.\ AP19).
This means the Virasoro collision $r$-matrix falls outside the
Belavin--Drinfeld framework.

The higher pole depth is not pathological; it is the defining
feature of the Virasoro algebra.  The Laplace kernel
$r^L(z) = (c/2)/z^4 + 2T/z^2 + \partial T/z$ has four
orders of singularity, in contrast to the affine case
$r^L(z) = k\,\Omega/z^2 + J/z$ which has two (AP126).
After $d\log$ absorption, the collision residues are
$r^{\mathrm{coll}}(z) = (c/2)/z^3 + 2T/z$ (Virasoro) and
$r^{\mathrm{coll}}(z) = k\,\Omega/z$ (affine).
The extra poles encode the higher-spin nature of the gravitational
field: the spin-$2$ stress tensor produces a Laplace kernel with
$z^{-4}$ leading singularity, while the spin-$1$ current produces
$z^{-2}$.

The conditional uniqueness theorem above handles this by using
representation-theoretic constraints (degenerate bootstrap, fusion
rules) instead of the Lie-algebraic classification.  This is
possible because the Virasoro algebra, while infinite-dimensional,
has rigid representation theory: the degenerate
fusion rules, combined with the Plancherel decomposition and
the $b \leftrightarrow b^{-1}$ symmetry, generate enough
constraints to pin down the braiding.
\end{remark}

\subsubsection{Synthesis: the identification as a conditional theorem}
\label{subsubsec:synthesis-PT}

Combining the three routes:

\begin{theorem}[Virasoro $R$-matrix identification;
\ClaimStatusConditional{} (conditional on one of the following)]
\label{thm:R-equals-PT-conditional}
\index{Ponsot--Teschner!conditional identification}
The spectral $R$-matrix $R(z)$ of
Definition~\textup{\ref{def:spectral-braiding}}, specialized to
$\cA = \mathrm{Vir}_c$, equals the Ponsot--Teschner fusion kernel
$\mathbb{F}$ on the principal series of
$\mathrm{Vir}_{26-c}$-modules, conditional on any one of the
following:
\begin{enumerate}[label=\textup{(\Alph*)}]
\item \textbf{DS analytic continuation}
  (Route~A): the bar-cobar $R$-matrix at integer level~$k$
  (proved to equal $R^{U_q(\mathfrak{sl}_2)}$ by
  Theorem~\textup{\ref{thm:affine-monodromy-identification}})
  extends continuously to all $b^2 \in \C \setminus \R_{\le 0}$
  through DS reduction, using the Faddeev modular double.

\item \textbf{Geometric Steinberg}
  (Route~B): Conjecture~\textup{\ref{conj:geometric-steinberg}}
  holds for $\mathrm{Vir}_c$, and the $(-1)$-shifted symplectic
  Euler class of $\Steinberg_b(\mathrm{Vir})$ equals the double
  sine measure~\eqref{eq:steinberg-measure}.

\item \textbf{Rigidity}
  (Route~C): Hypothesis~\textup{\ref{hyp:finite-monodromy}} holds,
  and the bar-cobar $R$-matrix is an admissible Virasoro braiding
  in the sense of
  Definition~\textup{\ref{def:admissible-vir-braiding}}.
\end{enumerate}
\end{theorem}

\begin{proof}
\textbf{(A)}: Theorem~\ref{thm:DS-transport-R} shows that the DS
reduction of the affine $R$-matrix matches the PT kernel on
degenerate modules.  The analytic continuation via the Faddeev
modular double extends this to the full principal series, where
the $R$-matrix of $U_{q\tilde q}(\mathfrak{sl}_2)$ is the PT
kernel by Teschner's theorem~\cite{TeschnerLiouville}.

\textbf{(B)}: By Conjecture~\ref{conj:R-matrix-steinberg}, the
Steinberg convolution would produce a braiding satisfying (R1)--(R3).
The measure~\eqref{eq:steinberg-measure} is the PT integrand by
construction.  Hence the Steinberg braiding equals $\mathbb{F}$.

\textbf{(C)}: Theorem~\ref{thm:conditional-uniqueness} shows the
space of admissible braidings is at most one-dimensional.  Both
$R(z)$ and $\mathbb{F}$ are admissible (the bar-cobar $R$-matrix
satisfies (R1) by Theorem~\ref{thm:YBE}, (R2) by
Proposition~\ref{prop:field-theory-r}, (R3) by skew-symmetry, and
(R5) by the meromorphy of the propagator; (R4) follows from the
BPZ reflection acting on the Koszul-dual modules).  Hence
$R = \mathbb{F}$.
\end{proof}

\begin{remark}[Strongest route: Route A is closest to unconditional]
\label{rem:strongest-route}
Of the three routes, Route~A requires the least new input: the
affine monodromy identification is proved
(Theorem~\ref{thm:affine-monodromy-identification}), DS reduction
commutes with bar-cobar (Vol~I), and the analytic continuation
from integer $k$ to continuous $b^2$ is the content of the
Faddeev--Teschner construction of the modular double, which is
established in the representation-theory
literature~\cite{Faddeev99, PT01, TeschnerLiouville}.  The
remaining logical gap is precisely the verification that the
bar-cobar $R$-matrix at non-integer $k$ is still given by the DS
reduction of the quantum-group $R$-matrix, i.e., that DS
reduction commutes with analytic continuation in the level.

For the degenerate modules, this is proved unconditionally
(Theorem~\ref{thm:DS-transport-R}(i)--(ii)): the exact braiding
eigenvalues $e^{\pm i\pi b\alpha_2}$ from the BPZ monodromy
(Remark~\ref{rem:virasoro-degenerate-truncation}) match the
Ponsot--Teschner eigenvalues on the nose.  The first quantum
correction at level~$0$
(Proposition~\ref{prop:virasoro-first-quantum}) provides a
further perturbative check: $2h_1 h_2\hbar^2/z^4$ matches the
subleading term $W_1$ of the PT semiclassical expansion at
leading order in $h_i/c$.  For the full
principal series, the gap reduces to a single analytic question:
does the Faddeev quantum dilogarithm $e_b(x)$ compute the
$\zeta$-regularized infinite product that arises from the
bar-cobar configuration-space integrals on
$\FM_n(\C) \times \Conf_n(\R)$ in the limit $n \to \infty$?
The affirmative answer would complete the identification.
\end{remark}

\begin{remark}[Physical content: graviton braiding from the
quartic pole]
\label{rem:graviton-braiding}
The identification $R^{\mathrm{bar}} = \mathbb{F}^{\PT}$ would
mean that the entire analytic structure of Virasoro fusion
(the double sine function, the modular $S$-matrix, the crossing
kernel, the Verlinde formula) emerges from the bar-cobar
adjunction of a single quartic-pole datum $\{T_\lambda T\} =
\partial T + 2T\lambda + (c/12)\lambda^3$.  The double sine
function $S_b$ is the graviton propagator in the spectral
representation; the fusion kernel is the graviton scattering
amplitude; and the pentagon identity is the Ward identity for
graviton 5-point functions.  The Steinberg variety
$\Steinberg_b(\mathrm{Vir})$ is the space of graviton crossings,
and its shifted symplectic structure is the BV phase space of the
crossing channel.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% THE CHIRAL SPRINGER RESOLUTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{The chiral Springer resolution}
\label{subsec:chiral-springer-resolution}
\index{Springer resolution!chiral|textbf}
\index{Steinberg!chiral Springer resolution|textbf}

The preceding remark identifies the central geometric frontier:
extending the spectral $R$-matrix from the evaluation locus (where
Theorem~\ref{thm:affine-monodromy-identification} settles the
identification) to the full spectral parameter requires a resolution
of singularities of the Steinberg object $\Steinberg_b$.  This
subsection develops the chiral Springer resolution in detail,
following the Chriss--Ginzburg paradigm
\cite{ChrissGinzburg}: the $K$-theory (or Borel--Moore homology) of
the classical Springer resolution $T^*(G/B) \to \cN$ produces the
Hecke algebra; the $K$-theory of the \emph{chiral} Springer resolution
$\widetilde{\Steinberg}_b \to \Steinberg_b$ should produce the Yangian
(the chiral Hecke algebra controlling the full
non-evaluation $R$-matrix).

\subsubsection{Review of the classical Springer resolution}
\label{sssec:classical-springer-review}

We recall the classical setup to fix notation and to make the analogy
precise.  Let~$G$ be a connected reductive group over~$\C$,
$B \subset G$ a Borel subgroup, $\cN \subset \fg$ the nilpotent
cone, and $\fn \subset \fb$ the nilradical of the Lie algebra of~$B$.

\begin{enumerate}[label=(\roman*),leftmargin=2em]
\item \textbf{The Springer resolution.}
  The cotangent bundle $\widetilde{\cN} := T^*(G/B)$ resolves the
  nilpotent cone via the Springer map
  $\mu \colon \widetilde{\cN} \to \cN$,
  $(gB, \xi) \mapsto \Ad_g(\xi)$,
  which is proper, birational, and an isomorphism over the regular
  nilpotent locus.

\item \textbf{Springer fibers.}
  For $x \in \cN$, the Springer fiber
  $\cB_x := \mu^{-1}(x) = \{gB \in G/B : x \in \Ad_g(\fn)\}$
  is a (generally singular) projective variety.  For $x$ regular
  nilpotent, $\cB_x$ is a single point; for $x$ subregular in type~$A_n$,
  $\cB_x$ is a chain of~$n-1$ copies of $\PP^1$; for $x = 0$,
  $\cB_x = G/B$.

\item \textbf{The Steinberg variety.}
  The classical Steinberg variety is
  $Z := \widetilde{\cN} \times_{\cN} \widetilde{\cN}
  = \{(gB, g'B, x) : x \in \Ad_g(\fn) \cap \Ad_{g'}(\fn)\}$.
  The convolution product on
  $H_*^{\mathrm{BM}}(Z) \cong H_W$
  recovers the Hecke algebra of the Weyl group (Chriss--Ginzburg
  \cite{ChrissGinzburg}, Kazhdan--Lusztig \cite{KL80}).

\item \textbf{$K$-theory and the Hecke algebra.}
  More precisely, $K_G(Z) \cong H_q(W)$,
  the Hecke algebra with~$q$ the equivariant parameter.  Modules for
  $K_G(Z)$ are $K_G(\widetilde{\cN})$-modules, i.e., equivariant
  coherent sheaves on the resolution.  The Springer correspondence
  assigns to each irreducible $W$-representation a pair (nilpotent
  orbit, local system).
\end{enumerate}

The three essential features are: (1)~the ambient space $\cN$ is
singular; (2)~the resolution $\widetilde{\cN} \to \cN$ is a
symplectic resolution (the cotangent bundle carries a canonical
symplectic form); (3)~the convolution algebra of the fiber product
$Z = \widetilde{\cN} \times_\cN \widetilde{\cN}$ is an algebra of
central importance (the Hecke algebra).  All three features have
chiral analogues.

\subsubsection{Singular locus of the chiral Steinberg object}
\label{sssec:singular-locus}

The chiral Steinberg object
$\Steinberg_b = \mathcal{L}_b \times_{\Mvac} \mathcal{L}_b$
(Construction~\ref{constr:steinberg-involution}) is smooth on the
evaluation locus, where bulk-boundary composition is well-defined
and the spectral $R$-matrix $R(z)$ of
Definition~\ref{def:spectral-braiding} is regular, but develops
singularities at non-evaluation spectral parameters.  The source
of these singularities is the collision of OPE poles in the
holomorphic direction, controlled by the bar differential $d_{\barB}$
on $\FM_k(\C)$.

\begin{conjecture}[Singular locus for the affine lineage;
\ClaimStatusConjectured]
\label{conj:singular-locus}
\index{Steinberg!singular locus}
Let $\cA = V_k(\fg)$ be an affine vertex algebra at non-critical
level $k \neq -h^\vee$, with boundary algebra
$\cA^!_{\mathrm{line}}$ the associated dg-shifted Yangian
\textup{(}Theorem~\textup{\ref{thm:yangian-recognition})}.
The singular locus of $\Steinberg_b$ is stratified by root type:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \textbf{Type $A_1$} ($\fg = \fsl_2$).
  The singular locus is the diagonal
  $\Delta \hookrightarrow \Steinberg_b$, where the two Lagrangian
  copies of $\mathcal{L}_b$ meet non-transversally.  Concretely,
  the $r$-matrix $r(z) = k\,\Omega/z$ (with Casimir $\Omega$) has a
  simple pole at $z = 0$, and the derived fiber product acquires a
  single singular stratum at the collision locus $z_{12} = 0$.
  The transverse slice to the diagonal is a conifold singularity
  $xy = z_{12}$ in the derived sense (the excess intersection bundle
  of $\mathcal{L}_b \cap \mathcal{L}_b$ along $\Delta$ has rank one).

\item \textbf{Type $A_2$} ($\fg = \fsl_3$).
  The singular locus has two strata: the diagonal $\Delta$ (where all
  spectral parameters collide) and an intermediate stratum
  corresponding to pairwise collision of simple-root OPE poles.
  The transverse slice at the deeper stratum involves
  a product of two conifold singularities, reflecting the two simple
  roots $\alpha_1, \alpha_2$ with $[\alpha_1, \alpha_2] \neq 0$.

\item \textbf{General type $A_n$} ($\fg = \fsl_{n+1}$).
  The singular stratification of $\Steinberg_b$ is indexed by
  subsets $S \subseteq \{\alpha_1, \ldots, \alpha_n\}$ of simple roots,
  with the stratum $\Sigma_S$ parametrizing configurations where the OPE
  poles corresponding to roots in $S$ collide.  The local transverse
  structure at $\Sigma_S$ is a product of conifold singularities,
  one for each root in~$S$.  This is the chiral analogue of the
  nilpotent orbit stratification $\cN = \bigsqcup_\lambda \cO_\lambda$.
\end{enumerate}
\end{conjecture}

\begin{remark}[Evidence]
The singular locus of the derived fiber product
$\Steinberg_b = \mathcal{L}_b \times_{\Mvac}^h \mathcal{L}_b$ is
controlled by the excess intersection complex.  By
Theorem~\ref{thm:bar-is-self-intersection}, the derived
self-intersection is modeled by the bar complex $\barB(\cA)$, and
the singular strata correspond to the loci where the bar differential
$d_{\barB}$ develops higher-order poles.

For type~$A_1$: the OPE of $V_k(\fsl_2)$ has the form
$J^a(z)\,J^b(w) \sim k\,\delta^{ab}/(z-w)^2 + f^{ab}{}_c J^c/(z-w)$,
and the bar kernel absorbs one pole, giving
$r(z) = k\,\Omega/z$.  The fiber product is transverse away from $z = 0$
(where $r(z)$ is regular) and acquires a conifold-type singularity at
$z = 0$ from the pole.  The transverse slice is the completion of the
$r$-matrix residue $\Omega$, which for $\fsl_2$ has rank one.

For type~$A_2$: each pair of adjacent simple roots contributes a
simple pole $r_{\alpha_i}(z) = \Omega_{\alpha_i}/z$, and
the two poles collide independently.  The root
$\alpha_1 + \alpha_2$ contributes a pole at the diagonal of the
two-particle configuration space, reflecting the non-commutativity
$[E_{\alpha_1}, E_{\alpha_2}] \neq 0$.  The stratification
mirrors the nilpotent orbit stratification: the zero orbit is
the full collision, the subregular orbits correspond to single-root
collisions, and the regular orbit is the smooth locus.
\end{remark}

\subsubsection{The resolution for type $A_1$}

\begin{construction}[Chiral Springer resolution for $\fsl_2$;
\ClaimStatusConjectured]
\label{constr:springer-sl2}
\index{Springer resolution!chiral!$\fsl_2$}
Let $\cA = V_k(\fsl_2)$ at level $k \neq -2$.  Define the
\emph{chiral Springer resolution} as the blowup of $\Steinberg_b$
along the singular diagonal $\Delta$:
\[
\pi \colon \widetilde{\Steinberg}_b
:= \Bl_\Delta(\Steinberg_b)
\;\longrightarrow\;
\Steinberg_b.
\]
This blowup is taken in the derived sense
\textup{(}cf.\ Khan \cite{Khan19}\textup{)}, respecting the
$(-1)$-shifted symplectic structure from
Theorem~\textup{\ref{thm:bar-is-self-intersection}(i)}.

The key geometric features:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \textbf{Exceptional fiber.}
  The exceptional divisor
  $E := \pi^{-1}(\Delta) \cong \PP(\mathcal{N}_{\Delta/\Steinberg_b})$
  is a $\PP^1$-bundle over $\Delta \cong \mathcal{L}_b$.  This is the
  chiral analogue of the Springer fiber $\cB_x \cong \PP^1$ for
  the subregular nilpotent orbit in type~$A_1$.

  The identification of the exceptional fiber with $\PP^1$ reflects
  the one-dimensionality of the excess intersection: for $\fsl_2$,
  the conormal bundle of $\mathcal{L}_b \hookrightarrow \Mvac$ has
  rank one in the holomorphic direction (from the single root $\alpha$),
  so $\mathcal{N}_{\Delta/\Steinberg_b}$ is a rank-$2$ bundle and its
  projectivization is indeed $\PP^1$.

\item \textbf{Smoothness.}
  The blowup $\widetilde{\Steinberg}_b$ is smooth: the excess conormal
  bundle is a vector bundle (not a coherent sheaf with torsion), because
  the singularity of $\Steinberg_b$ along $\Delta$ is of conifold type
  (transverse $A_1$ singularity $xy = z_{12}$), whose blowup is smooth.

\item \textbf{Symplectic structure.}
  The $(-1)$-shifted symplectic structure on $\Steinberg_b$
  pulls back to a $(-1)$-shifted symplectic structure on
  $\widetilde{\Steinberg}_b$.  Along the exceptional $\PP^1$,
  this restricts to the standard Fubini--Study form (shifted by $-1$
  to match the ambient degree), making
  $\widetilde{\Steinberg}_b \to \Steinberg_b$ a
  shifted symplectic resolution in the sense of the derived
  symplectic programme.
\end{enumerate}
\end{construction}

\begin{remark}[Comparison with the cotangent resolution]
\label{rem:cotangent-comparison}
In the classical setting, $T^*(G/B) \to \cN$ is simultaneously:
(a)~a resolution of singularities;
(b)~a symplectic resolution (the cotangent bundle carries a canonical
symplectic form);
(c)~a small resolution when~$G = \SL_2$ (the exceptional fiber has
codimension $\ge 2$ in the total space).

For the chiral Springer resolution in type~$A_1$:
(a)~holds by construction (the blowup resolves the conifold
singularity);
(b)~holds by the pullback of the $(-1)$-shifted symplectic form;
(c)~holds because the exceptional $\PP^1$ has dimension $1$ while
$\widetilde{\Steinberg}_b$ has formal dimension $3$ in the derived
sense (the bulk direction $\C \times \R$ contributes $3$, the
self-intersection drops by $2$, and the exceptional direction adds $1$).
Thus the chiral Springer resolution for $\fsl_2$ is a
shifted-symplectic small resolution.
\end{remark}

\subsubsection{Type $A$ in general: iterated blowup}
\label{sssec:type-A-general}

\begin{construction}[Chiral Springer resolution for type $A_n$;
\ClaimStatusConjectured]
\label{constr:springer-type-A}
\index{Springer resolution!chiral!type $A$}
For $\fg = \fsl_{n+1}$, the singular locus of $\Steinberg_b$ is
stratified by subsets $S \subseteq \{\alpha_1, \ldots, \alpha_n\}$
of simple roots (Conjecture~\ref{conj:singular-locus}(c)).
The chiral Springer resolution is constructed by an iterated blowup,
following the stratification from deepest to shallowest:
\[
\widetilde{\Steinberg}_b
= \Bl_{\Sigma_n} \circ \cdots \circ \Bl_{\Sigma_1}(\Steinberg_b),
\]
where $\Sigma_j$ denotes the union of strata of codimension $j$
\textup{(}corresponding to subsets $|S| = j$\textup{)}, blown up in
order of decreasing codimension.

For each stratum $\Sigma_S$ with $|S| = j$, the exceptional fiber of
the blowup is
$E_S \cong \prod_{\alpha_i \in S} \PP^1$,
a product of $j$ copies of $\PP^1$, one for each simple root whose
OPE pole contributes to the singularity.  At the deepest stratum
$\Sigma_{\{\alpha_1,\ldots,\alpha_n\}}$ \textup{(}the full diagonal,
where all poles collide\textup{)}, the exceptional fiber is
$(\PP^1)^n$, the product of $n$ copies of $\PP^1$ corresponding to
the $n$ simple roots.

\begin{enumerate}[label=\textup{(\alph*)}]
\item \textbf{Smoothness.}
  In type $A$, each root has multiplicity one
  (Theorem~\ref{thm:root-space-one-dim}) and the singularities at each
  stratum are products of conifold singularities.  Each individual
  conifold blowup is smooth, and the product structure ensures the
  iterated blowup is smooth.

\item \textbf{Springer fibers.}
  The Springer fiber of the chiral resolution at a point in stratum
  $\Sigma_S$ is $\prod_{\alpha_i \in S} \PP^1$.  For the deepest
  stratum (the full diagonal), this is the full flag variety
  analogue: a product of $n$ copies of $\PP^1$, carrying a natural
  action of the Weyl group $W = S_{n+1}$ by permutation of the
  factors.  This matches the classical Springer fiber of the zero
  nilpotent, which is $G/B$ with its $W$-action.

\item \textbf{Convolution.}
  The resolved Steinberg variety
  $\widetilde{Z} := \widetilde{\Steinberg}_b
  \times_{\widetilde{\cN}_{\mathrm{ch}}}
  \widetilde{\Steinberg}_b$
  carries a well-defined convolution product at all spectral
  parameters (the resolution removes the excess intersection that
  obstructs convolution on the singular locus).
\end{enumerate}
\end{construction}

\begin{remark}[Why type $A$ is clean]
\label{rem:type-A-clean}
In type $A$, every root has multiplicity one and the root system
is simply laced.  These two properties together force the singular
stratification of $\Steinberg_b$ to be a product of $A_1$
singularities: each simple root contributes independently.  The
iterated blowup therefore factors as a product of $A_1$ resolutions,
one per simple root.  This is the geometric expression of the fact
that the spectral Drinfeld obstruction vanishes for type $A$
(Theorem~\ref{thm:complete-strictification}): the strictification
is a product of $\fsl_2$ strictifications, each of which is trivially
resolved.

The cleanness of type $A$ is parallel to the classical fact that the
Springer resolution in type $A$ is \emph{semismall} and the
intersection cohomology of $\cN$ satisfies the decomposition theorem
with semisimple stalks.
\end{remark}

\subsubsection{Beyond type $A$: the non-simply-laced obstruction}
\label{sssec:beyond-type-A}

\begin{conjecture}[Obstructions beyond type $A$;
\ClaimStatusConjectured]
\label{conj:beyond-type-A}
\index{Springer resolution!chiral!non-simply-laced obstruction}
For non-simply-laced root systems ($B_n$, $C_n$, $F_4$, $G_2$),
the chiral Springer resolution requires genuinely new input beyond
the iterated conifold blowup of type~$A$.  The obstruction arises
from the interaction between long and short roots.
\begin{enumerate}[label=\textup{(\alph*)}]
\item \textbf{Type $B_2$} ($\fg = \fso_5$).
  The root system has roots $\pm\alpha_1, \pm\alpha_2,
  \pm(\alpha_1 \pm \alpha_2)$ with $\alpha_1$ short and $\alpha_2$
  long.  Although bar-kernel absorption ensures both roots contribute simple poles
  $r_{\alpha_i}(z) \sim \Omega_{\alpha_i}/z$ to the $r$-matrix, the
  \emph{residues} $\Omega_{\alpha_1}$ and $\Omega_{\alpha_2}$ have
  different norms under the invariant bilinear form (scaled by the
  root length ratio
  $|\alpha_{\mathrm{long}}|^2/|\alpha_{\mathrm{short}}|^2 = 2$).
  This asymmetry means the conifold singularities at the two root strata
  are not isomorphic: the transverse geometry at the long-root
  stratum has a quadratic scaling factor relative to the short-root
  stratum.  The blowup along the short-root stratum does not commute
  with the blowup along the long-root stratum, and the resolution
  requires a weighted blowup reflecting the root length ratio.

\item \textbf{Type $G_2$}.
  The root length ratio is $3$, and the six positive roots
  produce a singular locus with a non-normal-crossings stratification.
  The transverse slice at the deepest stratum involves a singularity
  of type $\tfrac{1}{3}(1,1)$, a cyclic quotient singularity that
  does not admit a crepant resolution.  This is the geometric shadow
  of the fact that the $G_2$ Yangian has irreducible higher-order
  structure not present in the simply-laced case.

\item \textbf{The general principle.}
  For a simple Lie algebra $\fg$, define the
  \emph{resolution complexity} $\nu(\fg)$ to be the number of
  distinct root lengths.  Then:
  \[
  \nu(\fg) = \begin{cases}
    1 & \fg \text{ simply laced } (A, D, E), \\
    2 & \fg \text{ non-simply-laced } (B_n, C_n, F_4, G_2).
  \end{cases}
  \]
  For $\nu(\fg) = 1$, the chiral Springer resolution is a product of
  $A_1$ resolutions (Construction~\ref{constr:springer-type-A}).
  For $\nu(\fg) = 2$, the resolution requires weighted blowups
  whose weights are determined by the root length ratio
  $|\alpha_{\mathrm{long}}|^2/|\alpha_{\mathrm{short}}|^2$
  (which equals $2$ for $B_n, C_n, F_4$ and $3$ for $G_2$),
  and the resulting space $\widetilde{\Steinberg}_b$ may fail to
  be smooth; the best one can hope for is a crepant partial
  resolution.
\end{enumerate}
\end{conjecture}

\begin{remark}[Evidence]
(a)\enspace For $B_2$: the $r$-matrix has the form
$r(z) = \Omega_{\mathrm{short}}/z + \Omega_{\mathrm{long}}/z$
at leading order (both roots contribute simple poles after the
bar kernel absorbs one order).  The Casimir residues satisfy
$\|\Omega_{\mathrm{long}}\|^2 = 2\|\Omega_{\mathrm{short}}\|^2$
under the invariant form.  The interaction between short and long
roots produces a collision channel at $z = 0$ whose transverse slice
is a weighted conifold $xy = z_{12}$ with non-isomorphic scaling in
the two root directions, preventing the blowup from factoring as a
product of $A_1$ resolutions.

(b)\enspace For $G_2$: the six positive roots $\alpha_1, \alpha_2,
\alpha_1 + \alpha_2, 2\alpha_1 + \alpha_2,
3\alpha_1 + \alpha_2, 3\alpha_1 + 2\alpha_2$ create a stratification
where the deepest collision involves the longest root
$3\alpha_1 + 2\alpha_2$.  The transverse slice involves the group
$\ZZ/3\ZZ$ (from the ratio
$|\alpha_{\mathrm{long}}|^2/|\alpha_{\mathrm{short}}|^2 = 3$),
giving a cyclic quotient singularity.  Crepant resolutions of
$\C^2/(\ZZ/3\ZZ)$ exist (the Hilbert--Chow resolution) but produce
exceptional curves of self-intersection $-3$, not $-2$, breaking
the ADE pattern.

(c)\enspace The resolution complexity $\nu(\fg)$ measures the number
of distinct orbit types in the Weyl group action on the root system.
When $\nu = 1$, all roots are equivalent under $W$ and the
singularity structure is uniform (each collision stratum is locally
a conifold).  When $\nu \ge 2$, the non-uniform root lengths create
singularities of different local types, and the resolution must
respect the relative geometry of these strata.
\end{remark}

\begin{remark}[Kac--Moody algebras and root multiplicities $> 1$]
\label{rem:kac-moody-root-mult}
\index{Springer resolution!chiral!Kac--Moody obstruction}
The true frontier beyond the scope of
Theorem~\ref{thm:complete-strictification} is not the non-simply-laced
finite case (where the chiral Springer resolution exists but requires
weighted blowups), but the \emph{Kac--Moody} case, where imaginary
roots have multiplicity $> 1$.  For a symmetrizable Kac--Moody
algebra $\fg$, an imaginary root $\delta$ has
$\dim \fg_\delta > 1$, and the multilinear Lie space at the
corresponding filtration degree is no longer one-dimensional.
The root-space one-dimensionality theorem
(Theorem~\ref{thm:root-space-one-dim}) fails, and with it the
mechanism that forces the spectral Drinfeld class to vanish.

Geometrically, root multiplicities $> 1$ manifest as singularities of
$\Steinberg_b$ that cannot be resolved by blowup: the excess
intersection bundle has rank $> 1$ in a single root direction, and the
projectivization of the conormal bundle yields exceptional fibers of
dimension $> 1$ in a single collision channel.  The resolution
$\widetilde{\Steinberg}_b$, if it exists, must handle these
higher-dimensional exceptional fibers, a problem analogous to the
Springer resolution for infinite-dimensional groups, where the geometry
of affine Grassmannians replaces flag varieties.

This is consistent with the algebraic picture: the Yangian of a
Kac--Moody algebra is expected to be a \emph{quantum toroidal algebra}
or \emph{quantum loop algebra} with genuinely new structure not present
in the finite-type Yangian, and the corresponding ``Springer fibers''
should be the geometric counterparts of these algebraic innovations.
\end{remark}

\subsubsection{The convolution algebra and the Yangian}
\label{sssec:convolution-yangian}

We now show that the convolution algebra of the resolved Steinberg
variety yields the Yangian, extending the proved correspondence
dictionary of Theorem~\ref{thm:steinberg-presentation}(iv) from the
evaluation locus to the full spectral parameter.

\begin{construction}[Convolution on $\widetilde{\Steinberg}_b$]
\label{constr:convolution-resolved}
\index{convolution!on resolved Steinberg}
Define the \emph{triple resolved Steinberg} as the derived fiber
product
\[
\widetilde{\Steinberg}_b^{(2)}
:= \widetilde{\Steinberg}_b
\times_{\widetilde{\mathcal{L}}_b}
\widetilde{\Steinberg}_b,
\]
where $\widetilde{\mathcal{L}}_b$ is the proper transform of
$\mathcal{L}_b$ in $\widetilde{\Steinberg}_b$.  The convolution
product on the resolved Steinberg is defined by the standard
pullback-pushforward recipe:
\[
\star \colon
H_*^{\mathrm{BM}}(\widetilde{\Steinberg}_b)
\otimes
H_*^{\mathrm{BM}}(\widetilde{\Steinberg}_b)
\xrightarrow{p_{12}^* \boxtimes p_{23}^*}
H_*^{\mathrm{BM}}(\widetilde{\Steinberg}_b^{(2)})
\xrightarrow{p_{13,*}}
H_*^{\mathrm{BM}}(\widetilde{\Steinberg}_b).
\]
\end{construction}

\begin{conjecture}[Associativity of the resolved convolution;
\ClaimStatusConjectured]
\label{conj:resolved-associativity}
\index{convolution!associativity}
The convolution product $\star$ on
$H_*^{\mathrm{BM}}(\widetilde{\Steinberg}_b)$ is associative.
\end{conjecture}

\begin{remark}[Proof strategy]
Associativity of convolution algebras in Borel--Moore homology is a
formal consequence of the associativity of fiber product composition,
provided that the pushforward maps $p_{13,*}$ are well-defined (i.e.,
the relevant maps are proper).  In the classical Steinberg setting,
properness follows from the properness of the Springer resolution
$\mu \colon \widetilde{\cN} \to \cN$.

For the chiral Steinberg resolution, properness of
$\pi \colon \widetilde{\Steinberg}_b \to \Steinberg_b$ holds by
construction (a blowup along a closed subvariety is always proper).
The key verification is that the iterated fiber product
\[
\widetilde{\Steinberg}_b^{(3)}
:= \widetilde{\Steinberg}_b
\times_{\widetilde{\mathcal{L}}_b}
\widetilde{\Steinberg}_b
\times_{\widetilde{\mathcal{L}}_b}
\widetilde{\Steinberg}_b
\]
admits a well-defined derived structure.  In the shifted-symplectic
setting, this is guaranteed by Pantev--To\"en--Vaqui\'e--Vezzosi
\cite{PTVV13}: the $(-1)$-shifted symplectic structure on
$\widetilde{\Steinberg}_b$ ensures that iterated Lagrangian
intersections are well-behaved.  The argument then proceeds
identically to the classical case: the two compositions
\[
([\alpha] \star [\beta]) \star [\gamma]
\quad\text{and}\quad
[\alpha] \star ([\beta] \star [\gamma])
\]
both factor through $p_{14,*}$ on
$\widetilde{\Steinberg}_b^{(3)}$, hence are equal.

The derivation of the Yang--Baxter equation from this associativity
follows the argument of Conjecture~\ref{conj:R-matrix-steinberg}(3),
now on the resolved space where the convolution is well-defined at
all spectral parameters.
\end{remark}

\begin{conjecture}[Yangian from the resolved Steinberg convolution]
\label{conj:yangian-springer}
\ClaimStatusConjectured
\index{Yangian!from Springer resolution}
Let $\fg$ be a simple Lie algebra and $\cA = V_k(\fg)$ at generic
level.  Then the convolution algebra of the chiral Springer resolution
contains the Yangian:
\[
Y(\fg) \;\hookrightarrow\;
H_*^{\mathrm{BM}}(\widetilde{\Steinberg}_b).
\]
More precisely:
\begin{enumerate}[label=\textup{(\roman*)}]
\item On the evaluation locus \textup{(}where $\Steinberg_b$ is
  smooth\textup{)}, the convolution algebra is
  $\cA^!_{\mathrm{line}}$-$\mathbf{mod}$, recovering the proved
  identification of
  Theorem~\textup{\ref{thm:steinberg-presentation}(iii)}.
\item On the full resolved space, the convolution algebra is the
  dg-shifted Yangian $Y_\hbar(\fg)$ of
  Theorem~\textup{\ref{thm:yangian-recognition}}, extended to all
  spectral parameters by the resolution.
\item The spectral $R$-matrix on the resolved space satisfies the
  full axioms \textup{(}unitarity, crossing, Yang--Baxter\textup{)}
  at all spectral parameters, not merely on the evaluation locus.
\end{enumerate}
\end{conjecture}

\begin{remark}[Evidence]
(i)~is proved unconditionally
(Theorem~\ref{thm:steinberg-presentation}).

(ii)~On the evaluation locus, the Yangian structure is already
established via the dg-shifted factorization bridge
(Theorem~\ref{thm:complete-strictification}).  The resolution
$\widetilde{\Steinberg}_b \to \Steinberg_b$ is an isomorphism
over the smooth (evaluation) locus, so the Yangian structure extends
tautologically.  The non-trivial content is the identification of the
convolution algebra over the \emph{exceptional} fibers.

For the exceptional fiber $E_\alpha \cong \PP^1$ at a simple root
$\alpha$, the Borel--Moore homology $H_*^{\mathrm{BM}}(\PP^1)$ is
two-dimensional (generated by the fundamental class $[\PP^1]$ in
degree~$2$ and the point class $[\mathrm{pt}]$ in degree~$0$).
The convolution with $[\PP^1]$ generates the Yangian's ``transfer
matrix'' operator, while $[\mathrm{pt}]$ generates the evaluation
map.  These are the algebraic generators of $Y(\fsl_2)$.
For general $\fg = \fsl_{n+1}$, the exceptional fibers
$E_{\alpha_i} \cong \PP^1$ for $i = 1, \ldots, n$ generate
the Yangian generators $\{e_i, f_i, h_i; e_i^{(1)}, f_i^{(1)},
h_i^{(1)}\}$, matching the Drinfeld presentation of $Y(\fsl_{n+1})$.

(iii)~follows from the associativity of the resolved convolution
(Conjecture~\ref{conj:resolved-associativity}), which guarantees the
Yang--Baxter equation at all spectral parameters, combined with the
Steinberg involution $\sigma$ which extends from $\Steinberg_b$ to
$\widetilde{\Steinberg}_b$ (the blowup of the diagonal is
$\sigma$-equivariant because $\sigma$ preserves the diagonal).
\end{remark}

\subsubsection{The extended correspondence dictionary}
\label{sssec:extended-dictionary}

The chiral Springer resolution extends the Steinberg--Hecke dictionary
of Theorem~\ref{thm:steinberg-presentation}(iv) to the full spectral
parameter:

\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Classical Springer} &
\textbf{Chiral Springer} &
\textbf{Object} \\
\midrule
$\cN$ (nilpotent cone) &
$\Steinberg_b^{\mathrm{sing}}$ (singular locus) &
Singular ambient \\
$\widetilde{\cN} = T^*(G/B) \to \cN$ &
$\widetilde{\Steinberg}_b \to \Steinberg_b$ &
Symplectic resolution \\
$\cB_x = \mu^{-1}(x)$ (Springer fiber) &
$E_S = \prod_{\alpha_i \in S} \PP^1$ &
Exceptional fiber \\
$H_*^{\mathrm{BM}}(Z) \cong H_W$ &
$H_*^{\mathrm{BM}}(\widetilde{\Steinberg}_b)
  \supseteq Y(\fg)$ &
Convolution algebra \\
$K_G(\widetilde{\cN}) \cong H_q(W)\text{-}\mathbf{mod}$ &
$K(\widetilde{\Steinberg}_b) \cong
  Y_\hbar(\fg)\text{-}\mathbf{mod}$ &
$K$-theory modules \\
IC purity (Decomposition Thm) &
Root multiplicity one
  (Thm~\ref{thm:root-space-one-dim}) &
Cleanness criterion \\
Springer correspondence &
Spectral $R$-matrix &
Representation theory \\
$W$-action on $H^*(\cB_x)$ &
$R(z)$-action on $H^*(E_S)$ &
Fiber action \\
\bottomrule
\end{tabular}
\end{center}

\begin{remark}[The Chriss--Ginzburg paradigm in the chiral world]
\label{rem:chriss-ginzburg-chiral}
The table above makes precise the analogy invoked throughout this
monograph: \emph{the bar complex presents the Swiss-cheese algebra, as
the Steinberg variety presents the Hecke algebra.}

The classical Chriss--Ginzburg theorem has two parts: the
\emph{algebraic} identification $H_*^{\mathrm{BM}}(Z) \cong H_W$
(which works on the singular Steinberg variety $Z$), and the
\emph{geometric} construction via the resolution $\widetilde{Z}$
(which produces the $q$-deformation $H_q(W)$).  Our story has the
same two-part structure:
\begin{enumerate}[label=(\roman*)]
\item The algebraic Steinberg presentation
  (Theorem~\ref{thm:steinberg-presentation}) works on the (possibly
  singular) $\Steinberg_b$ and recovers the $\SCchtop$-algebra
  structure; this is proved.
\item The chiral Springer resolution
  $\widetilde{\Steinberg}_b \to \Steinberg_b$ extends the convolution
  from the evaluation locus to all spectral parameters, producing the
  Yangian $Y(\fg)$ as the spectral deformation; this is the
  conjectural frontier developed above.
\end{enumerate}

The passage from (i)~to~(ii) is the passage from DK-$0$ (the
evaluation locus, where the $R$-matrix is the quantum-group
$R$-matrix) to the full spectral $R$-matrix (where the convolution
algebra is the Yangian).  The spectral Drinfeld strictification
(Theorem~\ref{thm:complete-strictification}) guarantees that this
passage is unobstructed for all simple Lie algebras, but the
\emph{geometric} construction of the resolution is the content of
Conjecture~\ref{conj:yangian-springer}.
\end{remark}

\begin{remark}[Status summary]
\label{rem:springer-status}
\begin{enumerate}[label=(\roman*)]
\item The algebraic Steinberg presentation
  (Theorem~\ref{thm:steinberg-presentation}): \textbf{proved}.
\item The singular locus analysis
  (Conjecture~\ref{conj:singular-locus}): \textbf{conjectured}.
  The evidence is the bar-complex model and the pole analysis from bar-kernel absorption.
\item The $\fsl_2$ chiral Springer resolution
  (Construction~\ref{constr:springer-sl2}): \textbf{conjectured}.
  The evidence is the conifold structure and the comparison with
  the classical $A_1$ Springer resolution.
\item The type $A$ iterated blowup
  (Construction~\ref{constr:springer-type-A}): \textbf{conjectured}.
  The cleanness relies on root multiplicity one
  (Theorem~\ref{thm:root-space-one-dim}, proved).
\item The non-simply-laced obstruction
  (Conjecture~\ref{conj:beyond-type-A}): \textbf{conjectured}.
  The weighted blowup mechanism is identified but not constructed.
\item The Yangian identification
  (Conjecture~\ref{conj:yangian-springer}): \textbf{conjectured}.
  On the evaluation locus, it reduces to the proved
  Theorem~\ref{thm:steinberg-presentation}(iii).
\item The Kac--Moody frontier
  (Remark~\ref{rem:kac-moody-root-mult}): \textbf{open}.
  Root multiplicities $> 1$ break the mechanism.
\end{enumerate}
\end{remark}

\section{Drinfeld double programme, part (b): antipode from orientation reversal}
\label{sec:drinfeld-double-antipode}

\subsection*{Reframing: uniqueness of the reconstructor up to natural transformation}

The unifying thesis of the Drinfeld double programme
(Remark~\ref{rem:drinfeld-programme-four-conditions}) is that
$U_\cA = \cA\bowtie\cA^!$ is the universal boundary-bulk
reconstructor: the boundary algebra $\cA$ determines the bulk
via $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$, and $U_\cA$ is the
chiral Hopf object that implements the reconstruction.  Part~(a)
of the programme constructs $U_\cA$; the present section
addresses the uniqueness clause of the thesis.  Hopf objects are
unique up to canonical involution, and the antipode $S_\cA$ is
the datum that witnesses this uniqueness.  Under the thesis, the
orientation-reversal construction of this section is the
statement that the reconstructor is determined by the boundary
algebra up to the canonical involution coming from Verdier
duality on $C$: two different assemblies of $U_\cA$ from the
same boundary data are related by $S_\cA$, and the antipode
axioms (a)--(d) of Conjecture~\ref{conj:drinfeld-double-antipode}
are the axioms that pin $S_\cA$ down up to inner conjugation.
Thus the material below is not an auxiliary construction; it is
the uniqueness condition that the reconstructor must satisfy.

The Drinfeld double programme (Remark~\ref{rem:drinfeld-double-programme}
in Chapter~\ref{chap:ordered-associative-chiral-kd}) assembles the Hopf
data of $U = \cA \bowtie \cA^!$ from four ingredients: the algebra
structure, the coproduct, the Hopf pairing, and the antipode.  The
present section isolates the antipode, identifies its geometric origin
as orientation reversal of the curve, and records the obstructions
that keep the construction conjectural beyond the pole-free locus.

The antipode of an ordinary Drinfeld double $D(H) = H \bowtie H^*$ is
an algebra anti-homomorphism $S \colon D(H) \to D(H)$ squaring to the
adjoint action by a distinguished group-like element $u \in D(H)$.
In the chiral
setting, the counterpart of $H \mapsto H^{\op}$ is the order-reversal
functor on the ordered bar complex, which is the content of
Theorem~\ref{thm:opposite}: the map
$\mathsf{R}_A \colon \Barch(A^{\op}) \xrightarrow{\sim} \Barch(A)^{\cop}$
geometrically realises the $z \mapsto -z$ involution on the ordered
configuration space $\Conf_n(\R)$ and, in the factorisation
presentation, the orientation-reversing involution
$\sigma \colon C \to \bar{C}$ on the underlying curve.  The
\emph{chiral Drinfeld antipode} is the extension of $\mathsf{R}_A$
from the ordered bar coalgebra to the (conjectural) Hopf object
$U_\cA = \cA \bowtie \cA^!$.

\subsection{The antipode from orientation reversal}
\label{subsec:antipode-orientation-reversal}

Let $C$ be a smooth complex curve, $\cA$ an $E_1$-chiral algebra on
$C$ in the sense of Chapter~\ref{chap:ordered-associative-chiral-kd},
and $\sigma \colon C \to \bar{C}$ the orientation-reversing
diffeomorphism (complex conjugation in a local analytic chart; on a
local coordinate patch $(U, z)$ it is the involution $z \mapsto -z$
combined with the antiholomorphic flip acting on sections).  Pullback
along $\sigma$ sends $D$-modules on $C$ to $D$-modules on $\bar{C}$,
and the universal property of Verdier duality on curves (see
\S\ref{subsec:orientation-verdier} below) identifies $\sigma^*$
with the Verdier functor $\mathbb{D}_{\Ran}$ on the factorisation
category of $\cA$.

\begin{definition}[Chiral Drinfeld antipode; \ClaimStatusConjectured]
\label{def:chiral-drinfeld-antipode}
Let $U_\cA = \cA \bowtie \cA^!$ denote the conjectural Hopf object
attached to the $E_1$-chiral Koszul pair $(\cA, \cA^!)$ of
Remark~\ref{rem:drinfeld-double-programme}.  The
\emph{chiral Drinfeld antipode} is the map
\[
S_{\cA} \colon U_\cA \longrightarrow U_\cA
\]
constructed in two stages.
\begin{enumerate}
\item \textbf{Bar-coalgebra stage.}  On the ordered bar coalgebra
$\Barch(\cA) = T^c(s^{-1}\bar\cA)$ (augmentation ideal, AP132),
$S_{\cA}$ restricts to the order-reversal isomorphism $\mathsf{R}_{\cA}$
of Theorem~\ref{thm:opposite}, followed by the Verdier intertwiner
$\mathbb{D}_{\Ran}(\Barch(\cA)) \simeq \Barch(\cA^!)$ of Volume~I,
Theorem~A.
\item \textbf{Double stage.}  On $U_\cA = \cA \bowtie \cA^!$,
$S_{\cA}$ exchanges the two tensorands via the canonical pairing
$\cA \otimes \cA^! \to \mathbf{k}$ coming from the twisting morphism
$\tau_\cA$, composed with the order-reversal of stage~(i) on each
factor.
\end{enumerate}
Concretely, on the Heisenberg boundary algebra $\cH_k$ with current
$J(z)$ and $\lambda$-bracket $\{J_\lambda J\} = k\,\lambda$, the
generator-level formula is
\begin{equation}
\label{eq:antipode-heisenberg}
S_{\cH_k}\bigl(J(z)\bigr) \;=\; -\,J(-z),
\end{equation}
extended to normally ordered products by the anti-homomorphism rule
$S(\NO{a\,b}) = \NO{S(b)\,S(a)}$ and to the coproduct side by the
cocommutative coalgebra structure of the free-field bar complex.
\end{definition}

\begin{remark}[Sanity check for the Heisenberg formula]
\label{rem:antipode-heisenberg-sanity}
Formula~\eqref{eq:antipode-heisenberg} is the generator-level
restriction of $\mathsf{R}_{\cH_k} \circ \mathbb{D}_{\Ran}$.  The
sign $-$ tracks the parity of the underlying bar word of length one
(the single desuspended generator $s^{-1}J$ sits in the bar grading
at which reversal acts by $(-1)^{(|J|+1)^2} = -1$ for a bosonic
field with $|J| = 0$), and the argument flip $z \mapsto -z$ tracks
the local-coordinate action of $\sigma$.  Squaring,
\[
S_{\cH_k}^{2}\bigl(J(z)\bigr)
\;=\; S_{\cH_k}\bigl(-J(-z)\bigr)
\;=\; -\bigl(-J(-(-z))\bigr)
\;=\; J(z),
\]
so $S_{\cH_k}^{2} = \id$ on generators.  The level $k$ enters the
bracket but not the antipode formula at arity one; the antipode
sees the level only through the order-reversal sign on longer bar
words, where $\{J_\lambda J\}$ feeds into the bar differential.
The squaring element for Heisenberg is $u = 1$.
\end{remark}

\begin{remark}[Compatibility with the $r$-matrix AP126 check]
\label{rem:antipode-r-matrix-check}
The classical $r$-matrix for an affine Kac--Moody boundary algebra
$\widehat{\mathfrak g}_k$ is $r(z) = k\,\Omega/z$ with the level $k$
surviving the $d\log$ absorption.  Under
Definition~\ref{def:chiral-drinfeld-antipode}, the antipode acts on
$r(z)$ by $r(z) \mapsto -r(-z) = k\,\Omega/z$, so the $r$-matrix is
$S$-invariant.  At $k = 0$ the $r$-matrix vanishes identically
(AP126/AP141), and the antipode collapses to the bosonic identity
on the trivial boundary algebra $\cH_0$, consistent with the
pole-free class $\mathbf{G}$ diagnostic of
Remark~\ref{rem:dimofte-k-matrix}.
\end{remark}

\subsection{The four antipode axioms}
\label{subsec:antipode-axioms}

The antipode of a Hopf algebra satisfies four axioms that together
determine it uniquely.  We list them for the conjectural chiral
Drinfeld double $U_\cA$ of Definition~\ref{def:chiral-drinfeld-antipode}
and record, for each axiom, the verification status on the
Heisenberg locus and the obstruction to extending the verification
beyond that locus.

\begin{conjecture}[Drinfeld double programme, part (b): antipode;
\ClaimStatusConjectured]
\label{conj:drinfeld-double-antipode}
Let $\cA$ be an $E_1$-chiral algebra of class $\mathbf{G}$, $\mathbf{L}$,
$\mathbf{C}$, or $\mathbf{M}$ in the sense of the shadow-depth
classification of Volume~I.  The chiral Drinfeld antipode $S_\cA$ of
Definition~\ref{def:chiral-drinfeld-antipode} satisfies the following
axioms on the conjectural Hopf object $U_\cA = \cA \bowtie \cA^!$.
\begin{enumerate}[label=\textup{(\alph*)}]
\item \textup{Algebra anti-homomorphism.}
$S_\cA(a \cdot b) = S_\cA(b) \cdot S_\cA(a)$ for all $a, b \in U_\cA$,
where the product is the bicrossed product on
$\cA \bowtie \cA^!$.
\item \textup{Unit preservation.} $S_\cA(1) = 1$.
\item \textup{Antipode axiom.}
$(\id \otimes S_\cA) \circ \Delta_\cA = \eta_\cA \circ \varepsilon_\cA$
and
$(S_\cA \otimes \id) \circ \Delta_\cA = \eta_\cA \circ \varepsilon_\cA$,
where $\Delta_\cA$ is the conjectural coproduct of part~(a) of the
Drinfeld double programme, $\eta_\cA$ is the unit of
$U_\cA$, and $\varepsilon_\cA$ is the counit.
\item \textup{Antipode squared by inner conjugation.}
$S_\cA^{\,2} = \mathrm{Ad}(u_\cA)$ for a squaring element
$u_\cA \in U_\cA$.  For class $\mathbf{G}$, $u_\cA = 1$ and
$S_\cA^{\,2} = \id$.  For higher classes, $u_\cA$ is a
non-trivial element determined by the higher $\Ainf$ operations
$m_k^{\cA}$, and its explicit form is currently unknown.
\end{enumerate}
\end{conjecture}

\begin{remark}[Verification status of the four axioms]
\label{rem:antipode-axiom-status}
\begin{enumerate}[label=\textup{(\alph*)}]
\item The anti-homomorphism axiom is the generator-level extension
of the opposite-duality theorem
(Theorem~\ref{thm:opposite}) from the bar coalgebra to the bicrossed
product.  At the bar level it is \textbf{proved}.  At the bicrossed
product level it is \textbf{conjectural} pending part~(a) of the
Drinfeld double programme.
\item Unit preservation holds trivially: both the bar reversal
$\mathsf{R}_\cA$ of Theorem~\ref{thm:opposite} and the Verdier
intertwiner fix the unit $1 \in \cA$.  \textbf{Proved} for the
ingredients; doubly conjectural pending part~(a).
\item The antipode axiom (c) requires the coproduct $\Delta_\cA$ of
part~(a) of the Drinfeld double programme and is therefore
\textbf{doubly conjectural}: conjectural by reference to a
conjectural coproduct.  On the Heisenberg locus, where the
coproduct is primitive, the axiom reduces to the identity
$J(z) + S(J(z)) = 0$, which is
formula~\eqref{eq:antipode-heisenberg}.  \textbf{Verified}
on class $\mathbf{G}$.
\item Antipode squared by inner conjugation is \textbf{verified} for class $\mathbf{G}$
($u_\cA = 1$, $S_\cA^{\,2} = \id$, computed in
Remark~\ref{rem:antipode-heisenberg-sanity}).  For classes
$\mathbf{L}$, $\mathbf{C}$, $\mathbf{M}$, the squaring element
$u_\cA$ has not been computed.  The expectation, motivated by the
parity of the higher $\Ainf$ operations $m_k$, is that
$u_\cA$ records the parity $(-1)^F$ of the ghost number filtration
on the bar complex.  This is part of the residual obstruction
discussed in \S\ref{subsec:antipode-obstructions}.
\end{enumerate}
\end{remark}

\subsection{Orientation reversal equals Verdier duality on curves}
\label{subsec:orientation-verdier}

The identification of the orientation-reversing pullback $\sigma^*$
with the Verdier functor $\mathbb{D}_{\Ran}$ on the factorisation
category of $\cA$ is a classical fact about $D$-modules on curves,
going back to the theory of holonomic duality.  We record the
precise statement and its consequence for the chiral Drinfeld
antipode.

\begin{proposition}[Orientation reversal as Verdier duality on curves;
\ClaimStatusProvedElsewhere]
\label{prop:orientation-verdier}
Let $C$ be a smooth complex curve with orientation $\omega$, and let
$\bar{C}$ denote the same underlying real-analytic manifold with
the opposite orientation $-\omega$ (equivalently, the conjugate
complex structure).  Let $\sigma \colon C \to \bar{C}$ be the
orientation-reversing diffeomorphism of underlying real manifolds.
Then pullback along $\sigma$ induces an equivalence
\[
\sigma^{*} \colon \Dmod(C) \xrightarrow{\sim} \Dmod(\bar{C})^{\op},
\]
which, under the natural identification of $\Dmod(\bar{C})^{\op}$
with the Verdier dual category $\Dmod(C)^{\vee}$, coincides with the
Verdier duality functor $\mathbb{D}_C$ up to a cohomological shift
by the complex dimension of $C$.
\end{proposition}

\begin{proof}
This is classical holonomic duality on curves; see
Beilinson--Bernstein \cite{BeilinsonBernstein} for the localisation
perspective, Borel et al.\ \cite{BorelDmodules} for the
$\cD$-module framing, and Drinfeld \cite{Drinfeld90} and
Drinfeld--Gaitsgory for the factorisation-category
formulation.  The statement is a one-dimensional specialisation of
the general fact that, for a smooth variety $X$, the Verdier dual is
obtained from the de Rham complex by dualising and shifting by
$\dim X$.  For $\dim_\C C = 1$, the shift is $[1]$, and the
orientation reversal exchanges the two halves of the de Rham
complex $\Omega^0_C \xrightarrow{d} \Omega^1_C$, swapping kernel
and cokernel and realising the Verdier duality functor as pullback
along the orientation-reversing involution.
\end{proof}

\begin{remark}[Consequence for the chiral Drinfeld antipode]
\label{rem:orientation-verdier-consequence}
Combining Proposition~\ref{prop:orientation-verdier} with the
Verdier intertwining theorem (Volume~I, Theorem~A), the chiral
Drinfeld antipode $S_\cA$ of
Definition~\ref{def:chiral-drinfeld-antipode} admits the following
factorisation-categorical presentation.  The bar coalgebra
$\Barch(\cA)$ is a factorisation coalgebra on
$\mathrm{Ran}(C)$; pullback along $\sigma$ sends it to
$\sigma^* \Barch(\cA)$, which Proposition~\ref{prop:orientation-verdier}
identifies with $\mathbb{D}_{\Ran}(\Barch(\cA))$; Volume~I's
Theorem~A identifies this Verdier dual with $\Barch(\cA^!)$; and
the order-reversal sign of Theorem~\ref{thm:opposite} recovers the
correct coopposite coalgebra structure.  The composite is the
generator-level antipode $S_\cA$ extended to the full bar complex.
\end{remark}

\subsection{Residual obstructions beyond class $\mathbf{G}$}
\label{subsec:antipode-obstructions}

The Heisenberg case of Definition~\ref{def:chiral-drinfeld-antipode}
is unambiguous because the bar complex is quadratic and the higher
$\Ainf$ operations $m_k$ vanish for $k \ge 3$.  Beyond class
$\mathbf{G}$, three obstructions block the extension of the
construction and the verification of Conjecture~\ref{conj:drinfeld-double-antipode}.

\begin{enumerate}
\item \textbf{Higher $\Ainf$ operations and the anti-homomorphism
axiom.}  For $\cA$ in class $\mathbf{L}$, $\mathbf{C}$, or
$\mathbf{M}$, the product on $U_\cA$ is $\Ainf$ and the axiom
$S(a \cdot b) = S(b) \cdot S(a)$ must be replaced by a homotopy
anti-homomorphism: the compatibility of $S$ with $m_k$ is governed
by a tower of coherent homotopies $\{S_k\}_{k \ge 2}$ whose
construction has not been carried out.
\item \textbf{Doubly conjectural antipode axiom.}  Axiom~(c) of
Conjecture~\ref{conj:drinfeld-double-antipode} depends on the
coproduct $\Delta_\cA$ of part~(a) of the Drinfeld double
programme.  Until $\Delta_\cA$ is constructed, the antipode axiom
cannot be checked beyond the primitive locus (class $\mathbf{G}$),
and any extension of $S_\cA$ beyond that locus is doubly
conjectural.
\item \textbf{Uncomputed squaring element for class $\mathbf{M}$.}
For Virasoro and the $\cW_N$ algebras, the squaring element
$u_\cA$ is expected to encode the parity of the higher $\Ainf$
operations and to be related to the ghost-number filtration on
the bar complex.  No explicit formula for $u_{\mathrm{Vir}_c}$
is known, and the candidate expressions that arise from
$(-1)^{F}$ for a fermionic ghost sector do not manifestly square
to the identity.  Until $u_{\mathrm{Vir}_c}$ is computed, the
antipode squared by inner conjugation axiom~(d) is conjectural for class $\mathbf{M}$.
\end{enumerate}

\begin{remark}[Relation to the Dimofte $K$-matrix]
\label{rem:antipode-dimofte-k-matrix}
The Dimofte $K$-matrix of Remark~\ref{rem:dimofte-k-matrix}
measures the deviation of the boundary coproduct from primitivity,
and the shadow-depth classification partitions the landscape by
the complexity of $K_\cA(z)$.  The antipode refines this picture:
the squaring element $u_\cA$ should be a functional of $K_\cA(z)$,
vanishing (equivalently, $u_\cA = 1$) when $K_\cA(z) = 1$
(class $\mathbf{G}$), polynomial when $K_\cA(z)$ is polynomial
(classes $\mathbf{L}$, $\mathbf{C}$), and having an infinite
expansion when $K_\cA(z)$ does (class $\mathbf{M}$).  A precise
formula $u_\cA = \Phi(K_\cA)$ would close the squared-antipode gap of
obstruction~(3) above and is the natural next step in part~(b) of
the Drinfeld double programme.
\end{remark}

\begin{remark}[Relation to Majid's double bosonisation]
\label{rem:antipode-majid}
In Majid's double bosonisation
\cite{Majid95}, reproduced in
Remark~\ref{rem:dimofte-double-bosonization}, the antipode of
$R(H) = H^{*\op} \bowtie_{R^{21}} \cB \bowtie_{R} H$ is
constructed from the antipode of the braided Hopf algebra $H$ and
the $R$-matrix $R$ of the ambient braided category.  At the
$E_1$-chiral level, the antipode of the conjectural Hopf object
$R(B^{\mathrm{ord}}(\cA))$ should therefore be the bar-level
antipode of this section, twisted by the meromorphic braiding
$r(z)$.  This twisting is again controlled by the squaring element,
closing the loop with obstruction~(3).  The proof that the twisted
antipode satisfies Majid's double-bosonisation axioms in the
meromorphic setting is part of the frontier of the spectral
braiding programme.
\end{remark}

\begin{remark}[Status summary of part (b)]
\label{rem:antipode-status}
\begin{enumerate}[label=(\roman*)]
\item Order reversal on the ordered bar coalgebra
(Theorem~\ref{thm:opposite}): \textbf{proved}.
\item Orientation reversal equals Verdier duality on curves
(Proposition~\ref{prop:orientation-verdier}): \textbf{proved
elsewhere} (classical holonomic duality).
\item Antipode definition at the generator level
(Definition~\ref{def:chiral-drinfeld-antipode},
formula~\eqref{eq:antipode-heisenberg}): \textbf{conjectural at
the double level, verified on class $\mathbf{G}$}.
\item Heisenberg antipode squared by inner conjugation
(Remark~\ref{rem:antipode-heisenberg-sanity}): \textbf{verified}.
\item Four antipode axioms
(Conjecture~\ref{conj:drinfeld-double-antipode}): axiom~(a)
proved at bar level, conjectural at double level; axiom~(b)
trivial; axiom~(c) doubly conjectural; axiom~(d) verified on
class $\mathbf{G}$, conjectural elsewhere.
\item Squaring element $u_\cA$ for classes
$\mathbf{L}, \mathbf{C}, \mathbf{M}$: \textbf{open}.
\item Homotopy anti-homomorphism tower for higher $\Ainf$ classes:
\textbf{open}.
\end{enumerate}
\end{remark}
