% Section file for Chapter: Twisted Holography and Quantum Gravity
% Result (G1): Perturbative Finiteness
%
% Develops the HS-sewing framework, shadow free energies,
% convergence of the gravitational partition function, the
% Heisenberg prototype, finiteness for the standard landscape,
% and implications for 3d quantum gravity.

\section{Perturbative finiteness}
\label{sec:thqg-perturbative-finiteness}
\label{ch:thqg-perturbative-finiteness}% alias for dangling \ref{ch:...}
\index{perturbative finiteness|textbf}
\index{UV finiteness!twisted holography}

% =====================================
% Local macros: provided only if absent from the ambient manuscript.
% =====================================
\providecommand{\HS}{\operatorname{HS}}
\providecommand{\Tr}{\operatorname{Tr}}
\providecommand{\Det}{\operatorname{Det}}
\providecommand{\Fred}{\operatorname{Fred}}
\providecommand{\rank}{\operatorname{rank}}
\providecommand{\Sym}{\operatorname{Sym}}
\providecommand{\id}{\mathrm{id}}
\providecommand{\ad}{\operatorname{ad}}
\providecommand{\wt}{\operatorname{wt}}
\providecommand{\Aut}{\operatorname{Aut}}
\providecommand{\Res}{\operatorname{Res}}
\providecommand{\Defcyc}{\operatorname{Def}_{\mathrm{cyc}}}
\providecommand{\gAmod}{\mathfrak{g}_{\cA}^{\mathrm{mod}}}
\providecommand{\Gmod}{\mathcal{G}^{\mathrm{mod}}}

Perturbative finiteness of twisted quantum gravity is the foundational analytic result that makes the gravitational shadow programme well defined. Three implications form the chain: (i)~$D_\cA^2 = 0$ (Theorem~\ref*{V1-thm:mc2-bar-intrinsic}) furnishes $\Theta_\cA \in \mathrm{MC}(\gAmod)$ at all genera without truncation; (ii)~the shadow representation $\operatorname{Sh}_{g,0}(\Theta_\cA)$ produces a cohomology class on the compact orbifold $\overline{\mathcal{M}}_g$, whose integral is finite; (iii)~Bernoulli asymptotics of the Faber--Pandharipande coefficients give convergence of the genus series with explicit radius $4\pi^2$. In standard perturbative quantum gravity, by contrast, the genus-$g$ contribution diverges for~$g \geq 2$: the integration domain is noncompact, the integrand distributional, the expansion asymptotic. In the twisted setting, where the boundary algebra~$\cA$ controls the bulk through the holographic modular Koszul datum $\mathcal{H}(T) = (\cA, \cA^!, \mathcal{C}, r(z), \Theta_\cA, \nabla^{\mathrm{hol}})$, all three pathologies vanish: the Maurer--Cartan equation is algebraic, Fulton--MacPherson compactification provides a geometric regulator, and the genus expansion converges.

The section develops this finiteness in six stages: (\S\ref{subsec:thqg-I-hs-sewing-framework}) the HS-sewing framework; (\S\ref{subsec:thqg-I-shadow-free-energies}) shadow free energies and the Bernoulli generating function; (\S\ref{subsec:thqg-I-convergence-grav}) convergence of the gravitational partition function; (\S\ref{subsec:thqg-I-heisenberg-prototype}) the Heisenberg partition function as prototype; (\S\ref{subsec:thqg-I-standard-landscape}) finiteness for the standard landscape; (\S\ref{subsec:thqg-I-3d-gravity}) implications for 3d quantum gravity.

% ======================================================================
% SUBSECTION 1: THE HS-SEWING FRAMEWORK FOR TWISTED GRAVITY
% ======================================================================

\subsection{The HS-sewing framework for twisted gravity}
\label{subsec:thqg-I-hs-sewing-framework}
\index{HS-sewing!twisted gravity framework}

The passage from finite-dimensional algebraic data (the OPE coefficients of~$\cA$) to infinite-genus partition functions requires a bridge between algebra and analysis. The HS-sewing condition provides this bridge: it guarantees that sewing amplitudes on pairs of pants compose to trace-class operators on the sewing Hilbert space.

\subsubsection{The sewing Hilbert space}

\begin{definition}[Sewing Hilbert space; cf.\ {\cite{costello-renormalization}}]
% label removed: def:thqg-I-sewing-hilbert-space
\index{sewing Hilbert space|textbf}
Let $\cA$ be a positive-energy chiral algebra with conformal grading $\cA = \bigoplus_{n \geq 0} H_n$, where $\dim H_n < \infty$ for all~$n$. For a sewing parameter $q \in (0,1)$, the \emph{sewing Hilbert space} is the $q$-weighted $\ell^2$-completion
\begin{equation}% label removed: eq:thqg-I-sewing-hilbert
\mathcal{H}_q(\cA) \;:=\; \widehat{\bigoplus}_{n \geq 0} q^{n/2}\,H_n \;=\; \Bigl\{ \sum_{n=0}^\infty v_n \;\Big|\; v_n \in H_n,\; \sum_{n=0}^\infty q^n \|v_n\|^2 < \infty \Bigr\},
\end{equation}
where $\|\cdot\|$ is any fixed Hermitian norm on each finite-dimensional $H_n$. The inner product is $\langle v, w \rangle_q = \sum_{n \geq 0} q^n \langle v_n, w_n \rangle_{H_n}$.
\end{definition}

\begin{remark}[Independence of norms]
% label removed: rem:thqg-I-norm-independence
Since each $H_n$ is finite-dimensional, different choices of Hermitian norm on $H_n$ give equivalent topologies on $\mathcal{H}_q(\cA)$. The $q$-weighting ensures that the completion is sensitive to conformal weight, with high-weight states exponentially suppressed. For $q \to 1^-$, the Hilbert space degenerates; for $q \to 0^+$, only the vacuum sector $H_0$ survives.
\end{remark}

\begin{lemma}[Completeness and separability; \ClaimStatusProvedHere]
% label removed: lem:thqg-I-completeness
\index{sewing Hilbert space!completeness}
$\mathcal{H}_q(\cA)$ is a separable Hilbert space for every $q \in (0,1)$. A Cauchy sequence $\{v^{(k)}\}_{k \geq 1}$ converges if and only if $\sum_{n \geq 0} q^n \|v^{(k)}_n - v^{(\ell)}_n\|^2 \to 0$ as $k, \ell \to \infty$.
\end{lemma}

\begin{proof}
Each $H_n$ is finite-dimensional, hence complete. The $q$-weighted $\ell^2$-completion is a weighted direct sum of Hilbert spaces with weights $q^n$; completeness of the direct sum follows from that of each summand together with the summability condition. Separability follows from taking a countable dense subset of each $H_n$ (finite-dimensional spaces are separable) and forming finite linear combinations.
\end{proof}

\begin{proposition}[Inclusion maps; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-inclusion-maps
\index{sewing Hilbert space!inclusion}
For $0 < q_1 < q_2 < 1$, the identity map on $\cA$ extends to a bounded inclusion $\iota_{q_1,q_2} \colon \mathcal{H}_{q_2}(\cA) \hookrightarrow \mathcal{H}_{q_1}(\cA)$ with operator norm $\|\iota_{q_1,q_2}\| = 1$. In particular, for every $v \in \mathcal{H}_{q_2}(\cA)$:
\begin{equation}% label removed: eq:thqg-I-inclusion
\|v\|_{q_1}^2 \;=\; \sum_{n \geq 0} q_1^n \|v_n\|^2 \;\leq\; \sum_{n \geq 0} q_2^n \|v_n\|^2 \;=\; \|v\|_{q_2}^2.
\end{equation}
\end{proposition}

\begin{proof}
Since $q_1 < q_2$, we have $q_1^n \leq q_2^n$ for all $n \geq 0$, giving the inequality termwise.
\end{proof}

\subsubsection{The HS-sewing condition}

\begin{definition}[HS-sewing condition]
\label{def:thqg-I-hs-sewing}
\index{HS-sewing!definition|textbf}
Let $\cA$ be a positive-energy chiral algebra with OPE structure constants $C^{c,k}_{a,i;\,b,j}$, where $a,b,c$ are conformal weights and $i,j,k$ index bases of $H_a$, $H_b$, $H_c$ respectively. The \emph{pair-of-pants multiplication operator} at weight $(a,b) \to c$ is the linear map $m^c_{a,b} \colon H_a \otimes H_b \to H_c$ with matrix entries $(m^c_{a,b})_{ij}^k = C^{c,k}_{a,i;\,b,j}$. The algebra~$\cA$ satisfies the \emph{HS-sewing condition} at parameter $q \in (0,1)$ if
\begin{equation}% label removed: eq:thqg-I-hs-sewing-condition
\boxed{ \sum_{a,b,c \geq 0} q^{a+b+c}\, \|m^c_{a,b}\|_{\HS}^2 \;<\; \infty,}
\end{equation}
where $\|m^c_{a,b}\|_{\HS}^2 = \sum_{i,j,k} |C^{c,k}_{a,i;\,b,j}|^2$ is the Hilbert--Schmidt norm of the multiplication operator.
\end{definition}

\begin{remark}[Physical content]
% label removed: rem:thqg-I-hs-physical
The HS-sewing condition controls the convergence of the sewing construction: a pair-of-pants decomposition of a genus-$g$ surface with $n$ punctures involves $2g - 2 + n$ pairs of pants, and each sewing circle contributes one composition of pair-of-pants operators. The HS condition guarantees that each such composition is Hilbert--Schmidt, and that the composition of two Hilbert--Schmidt operators is trace class, the key requirement for the trace that computes the partition function. The $q$-parameter is the sewing modulus $q = e^{-t}$ where $t > 0$ is the collar length.
\end{remark}

\begin{definition}[Hilbert--Schmidt and trace-class norms]
% label removed: def:thqg-I-hs-trace-norms
\index{Hilbert--Schmidt norm}
\index{trace-class!operator}
For a linear map $T \colon V \to W$ between finite-dimensional Hilbert spaces, the Hilbert--Schmidt norm is $\|T\|_{\HS}^2 = \Tr(T^*T) = \sum_{i,j} |T_{ij}|^2$. An operator $K$ on a Hilbert space $H$ is \emph{trace class} if $\|K\|_1 := \Tr\sqrt{K^*K} < \infty$. The key composition inequality is:
\begin{equation}% label removed: eq:thqg-I-hs-composition
\|AB\|_1 \;\leq\; \|A\|_{\HS}\,\|B\|_{\HS}
\end{equation}
for Hilbert--Schmidt operators $A, B$. Hence the composition of two HS operators is trace class, with trace bounded by the product of HS norms.
\end{definition}

\begin{lemma}[Schatten class hierarchy; \ClaimStatusProvedHere]
\label{lem:thqg-I-schatten}
\index{Schatten class}
Let $H$ be a separable Hilbert space and $S_p(H)$ the $p$-th Schatten class ($p \geq 1$). Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $S_1(H) \subset S_2(H) \subset S_p(H) \subset \mathcal{B}(H)$ for $1 \leq p \leq \infty$, where $\mathcal{B}(H)$ is bounded operators.
\item $S_1(H)$ is a two-sided ideal in $\mathcal{B}(H)$: if $K \in S_1(H)$ and $T \in \mathcal{B}(H)$, then $KT, TK \in S_1(H)$.
\item If $A \in S_p(H)$ and $B \in S_q(H)$ with $1/p + 1/q = 1/r \leq 1$, then $AB \in S_r(H)$.
\end{enumerate}
The sewing application uses $p = q = 2$, $r = 1$: two Hilbert--Schmidt operators compose to trace class.
\end{lemma}

\begin{proof}
Standard functional analysis; see Reed--Simon~\cite{RS78} or Simon~\cite{Simon05}. Part~(iii) is the generalized H\"older inequality for Schatten classes.
\end{proof}

\begin{proposition}[Pair-of-pants as HS operator; \ClaimStatusProvedElsewhere]
\label{prop:thqg-I-pants-hs}
\index{pair of pants!HS operator}
Under HS-sewing~\eqref{V1-eq:thqg-I-hs-sewing-condition}, the $q$-weighted multiplication operator $m_q \colon \mathcal{H}_q(\cA) \,\widehat{\otimes}\, \mathcal{H}_q(\cA) \to \mathcal{H}_q(\cA)$ is Hilbert--Schmidt, with
\begin{equation}% label removed: eq:thqg-I-mq-hs-bound
\|m_q\|_{\HS}^2 \;=\; \sum_{a,b,c \geq 0} q^{a+b+c}\,\|m^c_{a,b}\|_{\HS}^2 \;<\; \infty.
\end{equation}
Consequently, every closed amplitude on a genus-$g$ surface obtained by sewing is trace class.
\end{proposition}

\begin{proof}
Direct from the definition: $\|m_q\|_{\HS}^2$ is precisely the left-hand side of~\eqref{V1-eq:thqg-I-hs-sewing-condition}. A genus-$g$ surface with $n$ punctures is obtained by sewing $2g - 2 + n$ pairs of pants along $3g - 3 + n$ circles. Each sewing circle contributes one pair-of-pants composition. By the Hilbert--Schmidt composition inequality~\eqref{V1-eq:thqg-I-hs-composition}, each composition of two HS operators gives a trace-class operator. Since $g \geq 1$ requires at least two compositions, and trace-class operators form an ideal, the result follows.
\end{proof}

\begin{remark}[Sewing topology]
% label removed: rem:thqg-I-sewing-topology
\index{sewing!topology}
The pair-of-pants decomposition of a genus-$g$ surface $\Sigma_{g,n}$ into $2g - 2 + n$ trinions and $3g - 3 + n$ sewing circles is determined by a pants graph $\Gamma_P$. Different choices of $\Gamma_P$ give different factorizations of the sewing operator, but the trace (the partition function) is independent of $\Gamma_P$ by the factorization property. The sewing topology on the space of pants decompositions is captured by the flip graph, whose vertices are pants decompositions and whose edges are elementary moves (Dehn twists and handle slides). The partition function is invariant under flips by the pentagon and hexagon identities of the chiral algebra.
\end{remark}

\subsubsection{The polynomial-OPE / subexponential-sector criterion}

The analytic input is the criterion of Theorem~\ref{thm:general-hs-sewing}: polynomial OPE growth and subexponential sector growth together imply HS-sewing for all $q \in (0,1)$.

\begin{theorem}[HS-sewing from polynomial OPE growth; \ClaimStatusProvedHere]
\label{thm:general-hs-sewing}
\index{HS-sewing!polynomial OPE criterion}
Let\/ $\cA$ be a positive-energy chiral algebra satisfying:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Subexponential sector growth:} $\log\dim H_n = o(n)$ as $n \to \infty$.
\item \emph{Polynomial OPE growth:} There exist constants $K > 0$ and $N \in \mathbb{Z}_{\geq 0}$ such that $|C^{c,k}_{a,i;\,b,j}| \leq K(a + b + c + 1)^N$ for all conformal weights $a,b,c$ and all basis indices $i,j,k$.
\end{enumerate}
Then $\cA$ satisfies the HS-sewing condition for every $q \in (0,1)$:
\begin{equation}% label removed: eq:thqg-I-hs-criterion-bound
\sum_{a,b,c \geq 0} q^{a+b+c}\,\|m^c_{a,b}\|_{\HS}^2 \;\leq\; K^2 \sum_{n \geq 0} P_3(n)\,n^{2N}\, \bigl(\!\dim H_n\bigr)^3\,q^n \;<\; \infty,
\end{equation}
where $P_3(n) = \binom{n+2}{2}$ counts the number of triples $(a,b,c)$ with $a + b + c = n$.
\end{theorem}

\begin{proof}
The HS norm at weight level $(a,b,c)$ satisfies
\[
\|m^c_{a,b}\|_{\HS}^2 \;=\; \sum_{i=1}^{\dim H_a} \sum_{j=1}^{\dim H_b} \sum_{k=1}^{\dim H_c} |C^{c,k}_{a,i;\,b,j}|^2 \;\leq\; \dim H_a \cdot \dim H_b \cdot \dim H_c \cdot K^2(a{+}b{+}c{+}1)^{2N}.
\]
Summing over triples with $a + b + c = n$:
\[
\sum_{\substack{a,b,c \geq 0 \\ a+b+c = n}} q^n\,\|m^c_{a,b}\|_{\HS}^2 \;\leq\; K^2 q^n n^{2N} \sum_{\substack{a,b,c \geq 0 \\ a+b+c = n}} \dim H_a \cdot \dim H_b \cdot \dim H_c.
\]
The inner sum over triples is bounded by $\bigl(\sum_{j=0}^n \dim H_j\bigr)^3$. By the subexponential growth hypothesis, for every $\varepsilon > 0$ there exists $C_\varepsilon$ with $\dim H_j \leq C_\varepsilon \,e^{\varepsilon j}$. Hence $\sum_{j=0}^n \dim H_j \leq C_\varepsilon\,n\,e^{\varepsilon n}$. The total sum is therefore bounded by $K^2 C_\varepsilon^3 \sum_{n \geq 0} n^{2N+3}\, e^{3\varepsilon n}\,q^n$. Choosing $\varepsilon < |\log q|/4$, the exponential factor $e^{3\varepsilon n} q^n = e^{(3\varepsilon + \log q)n}$ decays geometrically, ensuring convergence of the power series.
\end{proof}

\begin{remark}[Optimality of the bound]
% label removed: rem:thqg-I-hs-optimality
The polynomial-OPE criterion is not optimal: examples with super-polynomial but sub-exponential OPE growth (such as certain completed W-algebras) may still satisfy HS-sewing. Nevertheless, the criterion covers the entire standard landscape of finitely strongly generated universal chiral algebras. The bound~\eqref{V1-eq:thqg-I-hs-criterion-bound} is loose by factors of order $n^3$ due to the crude estimate $\sum_{a+b+c=n} \dim H_a \dim H_b \dim H_c \leq (\sum_{j \leq n} \dim H_j)^3$; tighter bounds are available for specific families.
\end{remark}

\begin{remark}[The gap between HS-sewing and convergence]
% label removed: rem:thqg-I-gap-hs
\index{HS-sewing!necessary vs sufficient}
The HS-sewing condition is \emph{sufficient} for absolute convergence of the genus-$g$ partition function but not \emph{necessary}. Weaker conditions (e.g., trace-class sewing without the HS factorization) may suffice at specific genera. The HS condition provides uniform control across all genera: a single verification at the level of OPE data yields finiteness at every genus.
\end{remark}

\subsubsection{Explicit HS norms for the standard landscape}

\begin{computation}[HS norms for Heisenberg]
\label{comp:thqg-I-hs-heisenberg}
\index{Heisenberg!HS norms}
For the Heisenberg algebra $\mathcal{H}_k$ of rank~$1$ at level $k \in \mathbb{C}^{\times}$:
\begin{itemize}
\item $\dim H_n = p(n)$ (partitions of~$n$);
\item OPE: $a(z)a(w) \sim k/(z-w)^2$, giving $C^c_{a,b} = k\,\delta_{a+b,c+1}$ for the fundamental OPE, and all composite OPE grow polynomially with degree $N = 1$ (the Wick contraction is bilinear).
\item Growth: $\log p(n) \sim \pi\sqrt{2n/3}$ (Hardy--Ramanujan), so $\log \dim H_n = O(\sqrt{n})$, which is subexponential.
\end{itemize}
The HS sum factorizes by Wick's theorem into a one-particle contribution:
\begin{equation}% label removed: eq:thqg-I-hs-heisenberg-norm
\|m_q\|_{\HS}^2 \;=\; \prod_{n=1}^\infty \frac{1}{(1-q^n)^{2|k|^2}},
\end{equation}
which is finite for all $q \in (0,1)$. The one-particle operator has eigenvalues $q^n$, giving $\|T_q\|_1 = \sum_{n=1}^\infty q^n = q/(1-q)$, which is trace class for all $q < 1$.

The factorization is the consequence of the boson-fermion correspondence: the multi-particle Fock space partition function is the exponential of the one-particle trace. The partition counting function is $\prod_{n=1}^\infty (1-q^n)^{-1} = \sum_{n=0}^\infty p(n)q^n$; the Dedekind eta function $\eta(q) = q^{1/24}\prod_{n=1}^\infty (1-q^n)$ is a holomorphic modular form of weight $1/2$, related to the partition function by $\eta(q)^{-1} = q^{-1/24}\sum_{n=0}^\infty p(n)q^n$ (up to the $q^{-1/24}$ prefactor). Explicitly, the second quantization identity gives
\begin{equation}% label removed: eq:thqg-I-hs-heisenberg-factorization
\sum_{n=0}^\infty p(n)^2 q^n \;=\; \prod_{m=1}^\infty \frac{1}{(1-q^m)^2},
\end{equation}
and the HS norm is $|k|^2$ copies of this product.
\end{computation}

\begin{computation}[HS norms for affine Kac--Moody]
% label removed: comp:thqg-I-hs-affine
\index{affine Kac--Moody!HS norms}
For $\widehat{\fg}_k$ at non-critical level $k \neq -h^\vee$, with $\fg$ simple of dimension~$d$ and dual Coxeter number $h^\vee$:
\begin{itemize}
\item $\dim H_n \sim C\,n^{(d-\rank)/2}\,e^{\pi\sqrt{2dn/3}}$ (Kac--Peterson), so $\log \dim H_n = O(\sqrt{n})$, subexponential.
\item OPE: $J^a(z)J^b(w) \sim k\delta^{ab}/(z-w)^2 + f^{ab}{}_c J^c(w)/(z-w)$, polynomial of degree $N = 1$.
\item The HS norm satisfies
 \begin{equation}% label removed: eq:thqg-I-hs-affine-norm
 \|m_q\|_{\HS}^2 \;\leq\; C_k^2 \prod_{n=1}^\infty \frac{1}{(1-q^n)^{2d}}
 \end{equation}
 where $C_k$ depends on $k$ and the structure constants of $\fg$.
\end{itemize}
The key estimate for $C_k$ is obtained from the OPE normalization. The structure constants of $\widehat{\fg}_k$ at weight level $n$ grow as $|C^c_{a,b}| \leq \|f\|_\infty \cdot (k+h^\vee)$, where $\|f\|_\infty = \max_{a,b,c} |f^{ab}{}_c|$ is the maximum structure constant. For $\fg = \mathfrak{sl}_N$, one has $\|f\|_\infty = 1$ in the Chevalley basis, giving $C_k = |k + h^\vee|$.
\end{computation}

\begin{computation}[HS norms for Virasoro]
% label removed: comp:thqg-I-hs-virasoro
\index{Virasoro!HS norms}
For the Virasoro algebra $\mathrm{Vir}_c$ at central charge $c \in \mathbb{C}$:
\begin{itemize}
\item $\dim H_n = p(n)$ (Verma module dimensions);
\item OPE: $T(z)T(w) \sim c/(2(z-w)^4) + 2T(w)/(z-w)^2 + \partial T(w)/(z-w)$, polynomial of degree $N = 2$ (the $(z-w)^{-4}$ pole gives OPE coefficients growing at most quadratically in conformal weight).
\item Growth: $\log p(n) \sim \pi\sqrt{2n/3}$, subexponential.
\item The HS sum converges:
 \begin{equation}% label removed: eq:thqg-I-hs-virasoro-norm
 \|m_q\|_{\HS}^2 \;\leq\; C_c^2 \sum_{n \geq 0} p(n)^3\,n^{4}\,q^n \;<\; \infty \quad\text{for all } q \in (0,1).
 \end{equation}
\end{itemize}
The quartic growth of $n^4$ in the bound reflects the quartic OPE pole of $T(z)T(w)$. For the Virasoro algebra, the structure constants $C^c_{a,b}$ at weight level $n = a + b - c$ satisfy $|C^c_{a,b}| \leq P_2(n) := (n+1)(n+2)/2$ when $c$ is bounded; the precise bound involves the central charge through $|c|/2$ from the fourth-order pole.
\end{computation}

\begin{computation}[HS norms for $\beta\gamma$ system]
% label removed: comp:thqg-I-hs-betagamma
\index{beta-gamma system@$\beta\gamma$ system!HS norms}
For the $\beta\gamma$ system of conformal weights $(1,0)$:
\begin{itemize}
\item $\dim H_n = p(n)^2$ (two independent partition functions, one for $\beta$ modes and one for $\gamma$ modes).
\item OPE: $\beta(z)\gamma(w) \sim 1/(z-w)$, a simple pole. All composite OPE grow polynomially with degree $N = 1$.
\item Growth: $\log p(n)^2 = 2\log p(n) \sim 2\pi\sqrt{2n/3}$, subexponential.
\item The HS norm:
 \begin{equation}% label removed: eq:thqg-I-hs-betagamma-norm
 \|m_q\|_{\HS}^2 \;\leq\; C^2\prod_{n=1}^\infty \frac{1}{(1-q^n)^{4}} \;<\; \infty \quad\text{for all } q \in (0,1).
 \end{equation}
\end{itemize}
The exponent $-4$ in the product reflects the two bosonic degrees of freedom ($\beta$ and $\gamma$), each contributing $\prod_{n=1}^\infty (1-q^n)^{-2}$.
\end{computation}

\begin{computation}[HS norms for $\mathcal{W}_N$]
% label removed: comp:thqg-I-hs-wn
\index{W-algebra@$\mathcal{W}$-algebra!HS norms}
For the principal $\mathcal{W}$-algebra $\mathcal{W}_k(\mathfrak{sl}_N)$ at generic level:
\begin{itemize}
\item $\dim H_n$ is the number of $N$-colored partitions of~$n$ with colors of weight $2, 3, \ldots, N$; the growth is $\log \dim H_n = O(n^{(N-1)/N})$, subexponential for all~$N$.
\item OPE growth: the maximal singular order of the $W^{(s)}$ self-OPE is $2s$, so $N_{\max} = 2N$ for the $W^{(N)}$ field. All OPE coefficients grow at most polynomially with degree $\leq 2N$.
\item Convergence:
 \begin{equation}% label removed: eq:thqg-I-hs-wn-norm
 \|m_q\|_{\HS}^2 \;\leq\; K_N^2(c) \sum_{n \geq 0} (\dim H_n)^3\,n^{4N}\,q^n \;<\; \infty \quad\text{for all } q \in (0,1).
 \end{equation}
\end{itemize}
The $N$-colored partition function has generating series $\prod_{s=2}^N \prod_{m=s}^\infty (1-q^m)^{-1}$, and its growth exponent is controlled by the Meinardus theorem: $\log(\dim H_n) \sim C_N \cdot n^{(N-1)/N}$ with $C_N = N \cdot (\Gamma(1/N) \zeta(1+1/N))^{N/(N+1)} / (N+1)$. For $N = 2$ (Virasoro), $C_2 = \pi\sqrt{2/3}$; for $N = 3$ ($\mathcal{W}_3$), the growth is $O(n^{2/3})$.
\end{computation}

\begin{computation}[HS norms for lattice VOAs]
% label removed: comp:thqg-I-hs-lattice
\index{lattice VOA!HS norms}
For the lattice vertex algebra $V_\Lambda$ of an even integral lattice $\Lambda$ of rank~$r$:
\begin{itemize}
\item $\dim H_n = |\Lambda^*/\Lambda| \cdot p_r(n)$, where $p_r(n)$ is the $r$-colored partition function. Growth: $\log \dim H_n = O(\sqrt{n})$, subexponential.
\item OPE: inherited from rank-$r$ Heisenberg plus lattice vertex operators $V_\alpha(z)V_\beta(w) \sim (z-w)^{\langle\alpha,\beta\rangle}:\!V_{\alpha+\beta}(w)\!:$; the OPE growth is polynomial of degree $N = \max(r, \max_{\alpha \in \Lambda}|\langle\alpha,\alpha\rangle|/2)$.
\item The HS norm factors as
 \begin{equation}% label removed: eq:thqg-I-hs-lattice-norm
 \|m_q\|_{\HS}^2 \;\leq\; C_\Lambda^2\prod_{n=1}^\infty \frac{1}{(1-q^n)^{2r}} \,\Theta_\Lambda(q)^2 \;<\; \infty \quad\text{for all } q \in (0,1),
 \end{equation}
 where $\Theta_\Lambda(q) = \sum_{\alpha \in \Lambda} q^{\langle\alpha,\alpha\rangle/2}$ is the lattice theta function.
\end{itemize}
The factorization reflects the tensor-product structure $V_\Lambda = \mathcal{H}^{\otimes r} \otimes \mathbb{C}[\Lambda]$: the rank-$r$ Heisenberg part contributes $\prod_{n=1}^\infty (1-q^n)^{-2r}$ and the lattice group ring contributes $\Theta_\Lambda(q)^2$ (one factor from the bra side, one from the ket side of the HS norm).
\end{computation}

\begin{computation}[HS norms for free fermions]
\label{comp:thqg-I-hs-fermion}
\index{free fermions!HS norms}
For the free-fermion VOA of rank~$n$ (i.e., $n$ chiral fermions $\psi_1, \ldots, \psi_n$ of conformal weight $1/2$):
\begin{itemize}
\item $\dim H_m = \binom{n}{m}$ for $m \leq n$, $\dim H_m = 0$ for $m > n$ when counting weight-$m/2$ states; more precisely, the full Fock space has $\dim H_m$ growing as partitions into distinct parts, with generating function $\prod_{j=1}^n (1 + q^{j-1/2})$.
\item OPE: $\psi_i(z)\psi_j(w) \sim \delta_{ij}/(z-w)$, simple pole. OPE degree $N = 0$ (the structure constants are $0$ or $\pm 1$).
\item The HS norm:
 \begin{equation}% label removed: eq:thqg-I-hs-fermion-norm
 \|m_q\|_{\HS}^2 \;\leq\; \prod_{j=1}^{n} (1 + q^{j-1/2})^2 \;<\; \infty \quad\text{for all } q \in (0,1).
 \end{equation}
 This bound is finite because it is a finite product of bounded terms.
\end{itemize}
\end{computation}

\begin{table}[ht]
\centering
\caption{HS-sewing growth rates for the standard landscape}
% label removed: tab:thqg-I-hs-growth
\index{HS-sewing!growth rates}
\renewcommand{\arraystretch}{1.4}
{\footnotesize
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Family $\cA$} & $\boldsymbol{\dim H_n}$ & \textbf{OPE growth $N$} & \textbf{Sector growth} & \textbf{HS bound} \\
\hline
$\mathcal{H}_k$ (rank 1) & $p(n)$ & $1$ & $O(\sqrt{n})$ & $\prod_{n=1}^\infty (1-q^n)^{-2|k|^2}$ \\
\hline
$\widehat{\fg}_k$ & $\sim e^{\pi\sqrt{2dn/3}}$ & $1$ & $O(\sqrt{n})$ & $C_k^2\prod_{n=1}^\infty (1-q^n)^{-2d}$ \\
\hline
$\mathrm{Vir}_c$ & $p(n)$ & $2$ & $O(\sqrt{n})$ & $C_c^2\sum p(n)^3 n^4 q^n$ \\
\hline
$\beta\gamma$ system & $p(n)^2$ & $1$ & $O(\sqrt{n})$ & $\prod_{n=1}^\infty (1-q^n)^{-4}$ \\
\hline
$\mathcal{W}_N$ & $N$-colored parts & $2N$ & $O(n^{(N-1)/N})$ & $K_N^2(c)\sum (\dim H_n)^3 n^{4N} q^n$ \\
\hline
$V_\Lambda$ (rank $r$) & $|\Lambda^*/\Lambda|\,p_r(n)$ & $r$ & $O(\sqrt{n})$ & $C_\Lambda^2\prod_{n=1}^\infty (1-q^n)^{-2r}\Theta_\Lambda^2$ \\
\hline
Free fermions & $\leq 2^n$ & $0$ & polynomial & $\prod (1+q^{j-1/2})^2$ \\
\hline
\end{tabular}}
\end{table}

\subsubsection{Connection to trace-class operators on sewing Hilbert spaces}

\begin{proposition}[Trace-class amplitudes; \ClaimStatusProvedElsewhere]
% label removed: prop:thqg-I-trace-class-amplitudes
\index{trace class!sewing amplitudes}
Let\/ $\cA$ satisfy the HS-sewing condition at parameter $q$. Let $\Sigma_{g,n}$ be a genus-$g$ surface with $n$ punctures and a pants decomposition $\mathcal{P}$ with collar parameters $q_1, \ldots, q_{3g-3+n} \in (0,q]$. Then the sewing amplitude
\begin{equation}% label removed: eq:thqg-I-sewing-amplitude
Z_{\mathcal{P}}(\cA;\, q_1, \ldots, q_{3g-3+n}) \;=\; \Tr_{\mathcal{H}_q(\cA)^{\otimes n}} \Bigl( \prod_{\text{sewing circles}} m_{q_i} \Bigr)
\end{equation}
is well defined and absolutely convergent. The amplitude depends on the sewing moduli $(q_1, \ldots, q_{3g-3+n})$ but not on the choice of pants decomposition (by the factorization property of the chiral algebra).
\end{proposition}

\begin{proof}
Each pants composition $m_{q_i}$ is Hilbert--Schmidt by Proposition~\ref{prop:thqg-I-pants-hs}. A genus-$g$ surface requires $2g - 2 + n$ pairs of pants and $3g - 3 + n$ sewing circles. The sewing amplitude is a trace of a composition of $3g - 3 + n$ Hilbert--Schmidt operators. Since $3g - 3 + n \geq 2$ for $g \geq 1$ (and $\geq 3$ for $n = 0$), at least one pair of consecutive HS operators composes to give a trace-class operator. The remaining HS operators are bounded, and trace class times bounded is still trace class (Lemma~\ref{lem:thqg-I-schatten}(ii)). Hence the trace converges absolutely. Independence from the pants decomposition follows from the associativity and factorization axioms of the chiral algebra~\cite{BD04, FBZ04}.
\end{proof}

\begin{proposition}[Uniform bound on the trace; \ClaimStatusProvedHere]
\label{prop:thqg-I-uniform-trace-bound}
\index{trace class!uniform bound}
Under HS-sewing at parameter $q$, the sewing amplitude on a genus-$g$ surface with $n$ punctures satisfies the uniform bound
\begin{equation}% label removed: eq:thqg-I-uniform-trace
|Z_{\mathcal{P}}(\cA;\,q_1,\ldots,q_{3g-3+n})| \;\leq\; \|m_q\|_{\HS}^{3g-3+n}
\end{equation}
for all $q_1, \ldots, q_{3g-3+n} \in (0,q]$. In particular, the bound is uniform in the sewing moduli.
\end{proposition}

\begin{proof}
Each factor $m_{q_i}$ satisfies $\|m_{q_i}\|_{\HS} \leq \|m_q\|_{\HS}$ (since $q_i \leq q$ and the HS norm is monotone increasing in $q$). The trace of a composition of operators satisfies $|\Tr(A_1 \cdots A_k)| \leq \|A_1\|_{\HS}\cdots\|A_k\|_{\HS}$ when $k \geq 2$ (by iterated application of the HS composition inequality and the trace bound $|\Tr(K)| \leq \|K\|_1$).
\end{proof}

\begin{corollary}[Genus-$g$ partition function]
\label{cor:thqg-I-genus-g-partition}
\index{partition function!genus $g$}
For $\cA$ satisfying HS-sewing, the genus-$g$ partition function
\begin{equation}% label removed: eq:thqg-I-Z-g
Z_g(\cA) \;:=\; \int_{\overline{\mathcal{M}}_g} Z_{\mathcal{P}}(\cA;\,\mathbf{q}) \;\mu_{\mathrm{WP}}
\end{equation}
is well defined as an integral over the Deligne--Mumford compactification, where $\mu_{\mathrm{WP}}$ denotes the Weil--Petersson volume form.
\end{corollary}

\begin{proof}
The trace-class norm provides a pointwise bound on the integrand: $|Z_{\mathcal{P}}(\cA;\,\mathbf{q})| \leq \|T_{\mathbf{q}}\|_1$ where $T_{\mathbf{q}}$ is the sewing operator. By the HS-bound (Proposition~\ref{prop:thqg-I-uniform-trace-bound}), this norm is bounded uniformly in the interior of the moduli space. Near the boundary, the Fulton--MacPherson compactification provides the regulator: the sewing moduli $q_i$ vanish on the boundary divisors, and the $q$-weighted HS norms degenerate to zero. The integral over the compact orbifold $\overline{\mathcal{M}}_g$ is therefore finite.
\end{proof}

\begin{remark}[The Deligne--Mumford boundary]
% label removed: rem:thqg-I-dm-boundary
\index{Deligne--Mumford!boundary}
The boundary $\partial\overline{\mathcal{M}}_g = \overline{\mathcal{M}}_g \setminus \mathcal{M}_g$ consists of stable curves with nodes. Near a boundary stratum $\delta_\Gamma$ indexed by a dual graph $\Gamma$, the sewing moduli satisfy $q_e \to 0$ for each edge $e$ of $\Gamma$. The integrand $Z_{\mathcal{P}}(\cA;\,\mathbf{q})$ decomposes as a product of amplitudes on the irreducible components of the stable curve, multiplied by propagator insertions at the nodes. The vanishing of $q_e$ at the boundary ensures that the propagator insertions are trace class with trace-class norm tending to zero, giving the regularity needed for integrability over $\overline{\mathcal{M}}_g$.
\end{remark}


% ======================================================================
% SUBSECTION 2: SHADOW FREE ENERGIES AND THE BERNOULLI GENERATING FUNCTION
% ======================================================================

\subsection{Shadow free energies and the Bernoulli generating function}
\label{subsec:thqg-I-shadow-free-energies}
\index{shadow free energy|textbf}
\index{Bernoulli numbers!generating function}

The scalar projection of the Maurer--Cartan element $\Theta_\cA$ onto genus~$g$ is the shadow free energy $F_g(\cA)$. This is the degree-$0$, genus-$g$ component of the shadow algebra $\cA^{\mathrm{sh}} = H_\bullet(\Defcyc^{\mathrm{mod}}(\cA))$ (Definition~\ref{V1-def:shadow-algebra}).

\subsubsection{Definition of the shadow free energy}

\begin{definition}[Shadow free energy]
% label removed: def:thqg-I-shadow-free-energy
\index{shadow free energy!definition|textbf}
For a modular Koszul chiral algebra $\cA$ with universal Maurer--Cartan class $\Theta_\cA \in \mathrm{MC}(\gAmod)$ (Theorem~\ref*{V1-thm:mc2-bar-intrinsic}), the \emph{genus-$g$ shadow free energy} is the degree-zero shadow representation:
\begin{equation}% label removed: eq:thqg-I-Fg-def
F_g(\cA) \;:=\; \int_{\overline{\mathcal{M}}_g} \operatorname{Sh}_{g,0}(\Theta_\cA).
\end{equation}
On the uniform-weight lane (Vol~I, Definition~\ref*{V1-def:scalar-lane}),
genus universality identifies this
with $\int_{\overline{\mathcal{M}}_g} \kappa(\cA)\cdot\lambda_g$; for
arbitrary modular Koszul algebras, the unconditional scalar statement
is the genus-$1$ identity $F_1(\cA)=\kappa(\cA)/24$.
\end{definition}

\begin{remark}[Relation to the shadow algebra]
% label removed: rem:thqg-I-shadow-algebra-relation
The shadow free energy $F_g(\cA)$ is the $(r,g) = (0,g)$ component of the shadow algebra $\cA^{\mathrm{sh}} = H_\bullet(\Defcyc^{\mathrm{mod}}(\cA))$ in the bigrading by degree~$r$ and genus~$g$. The higher-degree shadows at genus $g$ (the cubic shadow $\mathfrak{C}_g$ at $r = 3$, the quartic resonance class $\mathfrak{Q}_g$ at $r = 4$) encode the gravitational interactions beyond the free-energy level. The shadow free energy is the simplest invariant, controlled entirely by the modular characteristic $\kappa(\cA)$.
\end{remark}

\begin{remark}[Physical interpretation: vacuum energy]
% label removed: rem:thqg-I-vacuum-energy
\index{shadow free energy!physical interpretation}
The shadow free energy $F_g(\cA)$ is the genus-$g$ vacuum energy of the
twisted holographic theory: it is the contribution to the path integral
from genus-$g$ worldsheets with no external insertions. In string
theory language, $F_g$ is the genus-$g$ cosmological constant. On the
proved scalar lane, $F_g$ is determined by the modular
characteristic $\kappa(\cA)$ through the Faber--Pandharipande integral;
for arbitrary modular Koszul algebras, the unconditional scalar
statement is the genus-$1$ value $F_1(\cA)=\kappa(\cA)/24$. Beyond that
lane, the scalar formula at genus~$g \geq 2$ receives a
cross-channel correction for multi-weight algebras
\textup{(}Volume~I, op:multi-generator-universality, resolved negatively\textup{)}.
\end{remark}

\subsubsection{The Faber--Pandharipande integral}

The key input from algebraic geometry is the evaluation of the Hodge integral:

\begin{proposition}[Faber--Pandharipande coefficient; \ClaimStatusProvedElsewhere]
\label{prop:thqg-I-faber-pandharipande}
\index{Faber--Pandharipande!coefficient}
\index{Hodge integral}
The integral of the top Hodge class over the moduli space of genus-$g$ curves is
\begin{equation}% label removed: eq:thqg-I-fp-integral
\lambda_g^{\mathrm{FP}} \;:=\; \int_{\overline{\mathcal{M}}_g} \lambda_g \;=\; \frac{2^{2g-1} - 1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}\,,
\end{equation}
where $B_{2g}$ is the $2g$-th Bernoulli number. This formula is due to Faber--Pandharipande~\cite{FP00}.
\end{proposition}

\begin{proof}[Proof sketch]
The integral $\int_{\overline{\mathcal{M}}_g} \lambda_g$ is computed by localization on $\overline{\mathcal{M}}_g$ using the Mumford relation $\lambda_g = (-1)^g \kappa_{2g-2}/(2g-2)!$ and the Witten--Kontsevich theorem for intersection numbers of $\psi$-classes. The Bernoulli numbers arise through the Euler--Maclaurin formula applied to the localization integral. A detailed proof is in Faber--Pandharipande~\cite{FP00}; the formula also follows from the string equation and the topological recursion relation.
\end{proof}

\begin{remark}[Bernoulli numbers]
% label removed: rem:thqg-I-bernoulli
\index{Bernoulli numbers!values}
The first ten Bernoulli numbers: $B_0 = 1$, $B_1 = -1/2$, $B_2 = 1/6$, $B_4 = -1/30$, $B_6 = 1/42$, $B_8 = -1/30$, $B_{10} = 5/66$, $B_{12} = -691/2730$, $B_{14} = 7/6$, $B_{16} = -3617/510$, $B_{18} = 43867/798$, $B_{20} = -174611/330$. The absolute values grow super-exponentially: $|B_{2g}| \sim 2 \cdot (2g)! / (2\pi)^{2g}$ (Euler's formula). The alternating signs $(-1)^{g+1} B_{2g} > 0$ reflect the alternation of Hodge classes.
\end{remark}

\begin{proposition}[Shadow free energy in closed form; \ClaimStatusProvedElsewhere{} {\textup{Theorem~\ref{V1-thm:modular-characteristic}}}]
\label{prop:thqg-I-Fg-closed-form}
\index{shadow free energy!closed form}
For any modular Koszul chiral algebra $\cA$ with
generators of the same conformal weight (uniform-weight lane):
\begin{equation}% label removed: eq:thqg-I-Fg-formula
\boxed{ F_g(\cA) \;=\; \kappa(\cA) \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}\,. }
\end{equation}
In particular, on this scalar lane $F_g$ depends only on $g$
and the single scalar $\kappa(\cA)$. At genus~$1$, the same formula
holds for every modular Koszul algebra.
\end{proposition}

\begin{proof}
This is the combination of genus universality on the
scalar lane ($\mathrm{obs}_g = \kappa \cdot \lambda_g$, cf.\
Theorem~\ref{V1-thm:genus-universality}) with the
Faber--Pandharipande evaluation of the Hodge integral
\textup{(}Proposition~\ref{prop:thqg-I-faber-pandharipande}\textup{)}.
\end{proof}

\begin{remark}[Universality]
% label removed: rem:thqg-I-universality
\index{shadow free energy!universality}
On the scalar lane, the genus-$g$ free energy depends only on
the single scalar $\kappa(\cA)$, regardless of the detailed OPE
structure. The Heisenberg at level $k$, the affine
$\widehat{\mathfrak{sl}}_2$ at level $k$, and the Virasoro at central
charge $c$ all have the same functional form
$F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ \textup{(}uniform-weight\textup{)}, differing only in the
value of $\kappa$. For multi-weight families, this scalar
factorization is only unconditional at genus~$1$. By the
universality of the modular characteristic (Theorem~D), higher-degree
shadows encode the additional nonlinear data beyond this scalar lane.
\end{remark}

\subsubsection{The $\hat{A}$-genus generating function}

\begin{theorem}[Generating function for shadow free energies; \ClaimStatusProvedElsewhere{} {\textup{Theorem~\ref{V1-thm:modular-characteristic}(ii)}}]
\label{thm:thqg-I-generating-function}
\index{A-hat genus@$\hat{A}$-genus!generating function|textbf}
For single-generator algebras \textup{(}and multi-generator
algebras satisfying the factorization condition of
Theorem~\textup{\ref{V1-thm:modular-characteristic}(i)(b))},
the formal generating series of shadow free energies has the
closed-form expression:
\begin{equation}% label removed: eq:thqg-I-gf-ahat
\boxed{ \sum_{g=1}^{\infty} F_g(\cA)\,x^{2g} \;=\; \kappa(\cA) \cdot \left( \frac{x/2}{\sin(x/2)} - 1 \right). }
\end{equation}
Equivalently, with the convention $F_0(\cA) = \kappa(\cA)$:
\begin{equation}% label removed: eq:thqg-I-gf-ahat-alt
\sum_{g=0}^{\infty} F_g(\cA)\,x^{2g} \;=\; \kappa(\cA) \cdot \frac{x/2}{\sin(x/2)}.
\end{equation}
\end{theorem}

\begin{proof}
We use the standard generating function for Bernoulli numbers. The generating function $\frac{t}{e^t - 1} = \sum_{n=0}^{\infty} \frac{B_n}{n!}\,t^n$ gives: The shadow free energy uses $\lambda_g^{\mathrm{FP}} = \frac{2^{2g-1}-1}{2^{2g-1}}\cdot\frac{|B_{2g}|}{(2g)!}$ with absolute values of Bernoulli numbers. The generating function is therefore
\begin{align}
\sum_{g=1}^{\infty} F_g\,x^{2g} &\;=\; \kappa \sum_{g=1}^{\infty} \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}\,x^{2g} \notag\\
&\;=\; \kappa \left( \frac{x/2}{\sin(x/2)} - 1 \right), % label removed: eq:thqg-I-gf-derivation
\end{align}
where the second equality uses the identity
\begin{equation}% label removed: eq:thqg-I-cosecant-bernoulli
\frac{x/2}{\sin(x/2)} \;=\; 1 + \sum_{g=1}^{\infty} \frac{(2^{2g-1}-1)|B_{2g}|}{2^{2g-1}\cdot(2g)!}\,x^{2g},
\end{equation}
obtainable from the Bernoulli generating function by the substitution $t = ix$ and the relation $\sin(x/2) = (e^{ix/2} - e^{-ix/2})/(2i)$.

The derivation proceeds as follows. The Bernoulli generating function gives $\frac{t}{e^t - 1} = 1 - t/2 + \sum_{g=1}^\infty \frac{B_{2g}}{(2g)!} t^{2g}$. Setting $t = ix$:
\[
\frac{ix}{e^{ix} - 1} \;=\; 1 - \frac{ix}{2} + \sum_{g=1}^\infty \frac{B_{2g}}{(2g)!}(ix)^{2g} \;=\; 1 - \frac{ix}{2} + \sum_{g=1}^\infty \frac{(-1)^g B_{2g}}{(2g)!} x^{2g}.
\]
Since $(-1)^g B_{2g} = -|B_{2g}|$ for $g \geq 1$, we have
\[
\frac{ix}{e^{ix}-1} \;=\; 1 - \frac{ix}{2} - \sum_{g=1}^\infty \frac{|B_{2g}|}{(2g)!}x^{2g}.
\]
Combining with the identity $\frac{ix}{e^{ix}-1} + \frac{ix}{2} = \frac{ix/2}{\tanh(ix/2)} = \frac{x/2}{\tan(x/2)}$, and using $\frac{x/2}{\sin(x/2)} = \frac{x/2}{\tan(x/2)} + \frac{x/2\,(1-\cos(x/2))}{\sin(x/2)\cos(x/2)}$, we arrive at~\eqref{V1-eq:thqg-I-cosecant-bernoulli} by the standard manipulation of the partial fraction expansion $\csc(z) = 1/z + 2z\sum_{n=1}^\infty (-1)^n/(z^2 - n^2\pi^2)$.

More directly: the function $\frac{x/2}{\sin(x/2)}$ is even and analytic at $x = 0$ with value $1$. Its Taylor expansion $\sum_{g=0}^\infty a_{2g} x^{2g}$ has coefficients $a_{2g} = \frac{(2^{2g-1}-1)|B_{2g}|}{2^{2g-1}(2g)!}$, which is verified by comparing with the standard expansion of $x/\sin(x) = \sum_{g=0}^\infty \frac{(2^{2g}-2)\,|B_{2g}|}{(2g)!}\, x^{2g}$ and substituting $x \mapsto x/2$.
\end{proof}

\begin{remark}[Two generating functions]
% label removed: rem:thqg-I-two-gfs
On the proved scalar lane, there are two natural generating functions
in play. The \emph{algebraic} generating function
$\sum_g F_g\,x^{2g} = \kappa(x/(2\sin(x/2)) - 1)$ uses the real
variable $x$ and converges for $|x| < 2\pi$. The \emph{physical}
generating function $\sum_g F_g\,\hbar^g$ uses the genus-counting
parameter~$\hbar$ and converges for $|\hbar| < 4\pi^2$. The relation
between the two is $\hbar = x^2$: the algebraic variable $x$ is the
``square root'' of the genus-counting parameter.
\end{remark}

\begin{remark}[Connection to the $\hat{A}$-genus]
% label removed: rem:thqg-I-ahat-connection
\index{A-hat genus@$\hat{A}$-genus!connection to shadow free energy}
On the proved scalar lane, the generating function $x/(2\sin(x/2))$ is
the square root of the Todd genus $\mathrm{td}(x) = x/(1-e^{-x})$ and
is closely related to the $\hat{A}$-genus $\hat{A}(x) = (x/2)/\sinh(x/2)$.
The relation is $x/(2\sin(x/2)) = \hat{A}(ix)$, a Wick rotation. This
Wick rotation corresponds to the passage from the Lorentzian
$\hat{A}$-genus (which controls index theory on spin manifolds) to the
Euclidean generating function (which controls genus integrals on moduli
spaces). The shadow free energy thus has a natural interpretation as a
``Wick-rotated $\hat{A}$-genus'' of the modular characteristic.
\end{remark}

\subsubsection{Absolute convergence from Bernoulli asymptotics}

\begin{theorem}[Absolute convergence of the scalar generating function; \ClaimStatusProvedHere]
\label{thm:thqg-I-absolute-convergence}
\index{absolute convergence!shadow free energy}
For any modular Koszul chiral algebra $\cA$ with generators of
uniform conformal weight, the
genus-counting series $\sum_{g=1}^{\infty} |F_g(\cA)|\,|\hbar|^g$
converges absolutely for $|\hbar| < 4\pi^2$. The generating function
$\sum_{g=1}^{\infty} F_g(\cA)\,\hbar^g$ extends to a meromorphic
function on $\mathbb{C}$ via the closed form
$\kappa \cdot (\frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)} - 1)$.
For multi-weight algebras, the unconditional statement is
the genus-$1$ identity $F_1(\cA) = \kappa(\cA)/24$;
at $g \geq 2$ the scalar formula receives a nonvanishing
cross-channel correction:
$F_g(\cA) = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}
+ \delta F_g^{\mathrm{cross}}(\cA)$
\textup{(}Volume~I, Open Problem~\textup{op:multi-generator-universality},
resolved negatively\textup{)}.
\end{theorem}

\begin{proof}
On the uniform-weight lane,
$F_g(\cA) = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$ for all $g \geq 1$
\textup{(}Volume~I, Theorem~D\textup{)}. The asymptotic behavior of
the Faber--Pandharipande coefficients is controlled by Euler's formula for the Bernoulli numbers,
$|B_{2g}| = 2 \cdot \zeta(2g) \cdot (2g)! / (2\pi)^{2g}$, where
$\zeta(2g) \to 1$ as $g \to \infty$. Substituting into $\lambda_g^{\mathrm{FP}} = \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}$:
\begin{align}
|F_g(\cA)| &\;=\; |\kappa(\cA)| \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!} \notag \\
&\;=\; |\kappa(\cA)| \cdot \underbrace{\frac{2^{2g-1}-1}{2^{2g-1}}}_{\to\,1} \cdot \underbrace{\frac{2\,\zeta(2g)}{(2\pi)^{2g}}}_{\sim\,2/(2\pi)^{2g}} \notag \\
&\;\sim\; \frac{2|\kappa(\cA)|}{(2\pi)^{2g}}. % label removed: eq:thqg-I-Fg-asymptotics
\end{align}
The two-sided bound for $g \geq 2$ is:
\[
\frac{2|\kappa|}{(2\pi)^{2g}} \;\leq\; |F_g| \;\leq\; \frac{2|\kappa|}{(2\pi)^{2g}} \cdot \frac{\zeta(2g)}{1 - 2^{1-2g}} \;\leq\; \frac{4|\kappa|}{(2\pi)^{2g}}\,.
\]
The ratio test now gives the convergence radius explicitly. The consecutive ratio is
\[
\frac{|F_{g+1}|}{|F_g|}
\;=\;
\frac{(2^{2g+1}-1)}{(2^{2g-1}-1)}
\cdot
\frac{|B_{2g+2}|}{|B_{2g}|}
\cdot
\frac{(2g)!}{(2g+2)!}
\cdot
\frac{2^{2g-1}}{2^{2g+1}}\,.
\]
By Euler's formula, $|B_{2g+2}|/|B_{2g}| = \zeta(2g+2)/\zeta(2g) \cdot (2g+2)(2g+1)/(2\pi)^2$.
Therefore $|F_{g+1}/F_g| = \zeta(2g+2)/\zeta(2g) \cdot \frac{2^{2g+1}-1}{2^{2g+1}} / \frac{2^{2g-1}-1}{2^{2g-1}} \cdot 1/(2\pi)^2 \to 1/(2\pi)^2$ as $g \to \infty$. The Cauchy--Hadamard radius of convergence is therefore
\[
R \;=\; \lim_{g \to \infty} |F_g/F_{g+1}| \;=\; (2\pi)^2 \;=\; 4\pi^2 \;\approx\; 39.48\,.
\]
This is not an artifact of a bound: the radius is \emph{exact}, determined by the first pole of the closed-form continuation $\kappa \cdot (\frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)} - 1)$. The poles occur at the zeros of $\sin(\sqrt{\hbar}/2)$,
i.e.\ at $\sqrt{\hbar}/2 = n\pi$, giving
$\hbar_n = 4\pi^2 n^2$ for $n = 1, 2, 3, \ldots$ The nearest pole to the origin is $\hbar_1 = 4\pi^2$, confirming $R = 4\pi^2$.

For the residues: writing $s(\hbar)=\sin(\sqrt{\hbar}/2)$, one
has $s'(\hbar_n)=(-1)^n/(8\pi n)$ at $\hbar_n = 4\pi^2 n^2$, so
\[
\Res_{\hbar = 4\pi^2 n^2}
\kappa \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}
\;=\; 8(-1)^n \kappa n^2\pi^2.
\]
\end{proof}

\begin{remark}[Factorially divergent vs.\ convergent]
% label removed: rem:thqg-I-factorial-convergent
\index{factorial growth!absence of}
In standard perturbative quantum field theory, the genus-$g$
contribution typically grows as $(2g)!$, reflecting the factorial
number of Feynman diagrams. On the scalar lane, the
shadow free energy satisfies $F_g \sim 2\kappa/(2\pi)^{2g}$, so the
series $\sum F_g \hbar^g$ is convergent, not merely asymptotic. The
reason is that the scalar shadow free energy there is an integral over
the compact moduli space $\overline{\mathcal{M}}_g$ of a smooth
cohomology class, not a sum over all Feynman diagrams.
\end{remark}

\subsubsection{Explicit values through genus 10}

\begin{proposition}[Shadow free energies through genus $10$ on the scalar lane; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-Fg-values
\index{shadow free energy!explicit values}
If $\cA$ has generators of uniform conformal weight, then using the
Faber--Pandharipande coefficients
\textup{(}Proposition~\ref{prop:thqg-I-faber-pandharipande}\textup{)}:
\begin{align}
F_1(\cA) &= \frac{\kappa}{24}, % label removed: eq:thqg-I-F1\\
F_2(\cA) &= \frac{7\kappa}{5760}, % label removed: eq:thqg-I-F2\\
F_3(\cA) &= \frac{31\kappa}{967680}, % label removed: eq:thqg-I-F3\\
F_4(\cA) &= \frac{127\kappa}{154828800}, % label removed: eq:thqg-I-F4\\
F_5(\cA) &= \frac{73\kappa}{3503554560}, % label removed: eq:thqg-I-F5\\
F_6(\cA) &= \frac{1414477\kappa}{2678117105664000}, % label removed: eq:thqg-I-F6\\
F_7(\cA) &= \frac{8191\kappa}{612141052723200}, % label removed: eq:thqg-I-F7\\
F_8(\cA) &= \frac{16931177\kappa}{49950709902213120000}, % label removed: eq:thqg-I-F8\\
F_9(\cA) &= \frac{5749691557\kappa}{669659197233029971968000}, % label removed: eq:thqg-I-F9\\
F_{10}(\cA) &= \frac{91546277357\kappa}{420928638260761696665600000}. % label removed: eq:thqg-I-F10
\end{align}
For arbitrary modular Koszul algebras, only the genus-$1$ identity
$F_1(\cA)=\kappa(\cA)/24$ is unconditional on the current record.
\end{proposition}

\begin{proof}
Direct substitution of the Bernoulli numbers into the
formula
$F_g = \kappa \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}$
\textup{(}uniform-weight\textup{)}.

At genus $g = 1$: $F_1 = \kappa \cdot \frac{1}{2} \cdot \frac{1/6}{2} = \kappa/24$.

At genus $g = 2$: $(2^3{-}1)/2^3 = 7/8$, $|B_4| = 1/30$, $4! = 24$. $F_2 = \kappa \cdot \frac{7}{8} \cdot \frac{1/30}{24} = \frac{7\kappa}{5760}$.

At genus $g = 3$: $|B_6| = 1/42$, $6! = 720$, $(2^5 - 1)/2^5 = 31/32$. $F_3 = \kappa \cdot \frac{31}{32} \cdot \frac{1/42}{720} = \frac{31\kappa}{32 \cdot 30240} = \frac{31\kappa}{967680}$.

At genus $g = 4$: $|B_8| = 1/30$, $8! = 40320$, $(2^7 - 1)/2^7 = 127/128$. $F_4 = \kappa \cdot \frac{127}{128} \cdot \frac{1/30}{40320} = \frac{127\kappa}{128 \cdot 1209600} = \frac{127\kappa}{154828800}$.

At genus $g = 5$: $|B_{10}| = 5/66$, $10! = 3628800$, $(2^9 - 1)/2^9 = 511/512$. $F_5 = \kappa \cdot \frac{511}{512} \cdot \frac{5/66}{3628800} = \kappa \cdot \frac{511 \cdot 5}{512 \cdot 66 \cdot 3628800} = \frac{2555\kappa}{122624409600} = \frac{73\kappa}{3503554560}$.

The remaining values are computed similarly.
\end{proof}

\begin{table}[ht]
\centering
\caption{Shadow free energies $F_g(\cA) = \kappa \cdot \lambda_g^{\mathrm{FP}}$ for three standard families, $g = 1, \ldots, 5$.}
% label removed: tab:thqg-I-Fg-specializations
\index{shadow free energy!table}
\renewcommand{\arraystretch}{1.5}
{\footnotesize
\begin{tabular}{|c|c|c|c|}
\hline
$\boldsymbol{g}$ & $\mathcal{H}_k$, $\kappa = k$ & $\widehat{\mathfrak{sl}}_{2,k}$, $\kappa = \frac{3(k+2)}{4}$ & $\mathrm{Vir}_c$, $\kappa = \frac{c}{2}$ \\
\hline
$1$ & $\dfrac{k}{24}$ & $\dfrac{k+2}{32}$ & $\dfrac{c}{48}$ \\[6pt]
\hline
$2$ & $\dfrac{7k}{5760}$ & $\dfrac{7(k+2)}{7680}$ & $\dfrac{7c}{11520}$ \\[6pt]
\hline
$3$ & $\dfrac{31k}{967680}$ & $\dfrac{31(k+2)}{1290240}$ & $\dfrac{31c}{1935360}$ \\[6pt]
\hline
$4$ & $\dfrac{127k}{154828800}$ & $\dfrac{127(k+2)}{206438400}$ & $\dfrac{127c}{309657600}$ \\[6pt]
\hline
$5$ & $\dfrac{73k}{3503554560}$ & $\dfrac{73(k+2)}{4671406080}$ & $\dfrac{73c}{7007109120}$ \\[6pt]
\hline
\end{tabular}}
\end{table}

\begin{remark}[Numerical magnitudes]
% label removed: rem:thqg-I-numerical-magnitudes
\index{shadow free energy!numerical estimates}
For the Heisenberg at $k = 1$: $F_1 \approx 0.0417$, $F_2 \approx 1.22 \times 10^{-3}$, $F_3 \approx 3.20 \times 10^{-5}$, $F_4 \approx 8.20 \times 10^{-7}$, $F_5 \approx 2.08 \times 10^{-8}$. The free energies decrease super-exponentially, with ratio $F_{g+1}/F_g \to 1/(2\pi)^2 \approx 0.0253$. By genus $10$, $F_{10} \approx 2.17 \times 10^{-16}$. The geometric decay with ratio $1/(4\pi^2) \approx 0.0253$ means that the genus expansion is an extremely rapidly converging series, even at $\hbar = 1$.
\end{remark}

\begin{proposition}[Cumulative partial sums; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-partial-sums
\index{shadow free energy!partial sums}
For the Heisenberg at $k = 1$ and $\hbar = 1$, the partial sums of the genus expansion are:
\begin{align}
S_1 &= F_1 = 0.04167\,, \notag \\
S_2 &= S_1 + F_2 = 0.04288\,, \notag \\
S_3 &= S_2 + F_3 = 0.04291\,, \notag \\
S_4 &= S_3 + F_4 = 0.04291\,, \notag \\
S_5 &= S_4 + F_5 = 0.04291\,, % label removed: eq:thqg-I-partial-sums
\end{align}
converging to $\kappa \cdot (1/\mathrm{sinc}(1/2) - 1) = (1/(2\sin(1/2)) - 1) \cdot 1 \approx 0.04291$.
\end{proposition}

\begin{proof}
Direct numerical evaluation.
\end{proof}


% ======================================================================
% SUBSECTION 3: CONVERGENCE OF THE GRAVITATIONAL PARTITION FUNCTION
% ======================================================================

\subsection{Convergence of the gravitational partition function}
\label{subsec:thqg-I-convergence-grav}
\index{gravitational partition function!convergence|textbf}

\subsubsection{Definition of the gravitational partition function}

\begin{definition}[Gravitational partition function]
% label removed: def:thqg-I-grav-partition
\index{gravitational partition function!definition|textbf}
For a holographic modular Koszul datum $\mathcal{H}(T) = (\cA, \cA^!, \mathcal{C}, r(z), \Theta_\cA, \nabla^{\mathrm{hol}})$ and a formal genus-counting parameter~$\hbar$, the \emph{gravitational partition function} is
\begin{equation}% label removed: eq:thqg-I-Z-grav-def
Z_{\mathrm{grav}}(T;\,\hbar) \;:=\; \sum_{g=0}^{\infty} \hbar^g \int_{\overline{\mathcal{M}}_{g}} \operatorname{Sh}_{g,0}(\Theta_\cA)\,.
\end{equation}
The \emph{scalar gravitational partition function} is the restriction to the degree-$0$ scalar channel:
\begin{equation}% label removed: eq:thqg-I-Z-grav-scalar
Z_{\mathrm{grav}}^{\mathrm{scal}}(T;\,\hbar) \;:=\; \sum_{g=0}^{\infty} F_g(\cA)\,\hbar^g\,,
\end{equation}
where on the scalar lane the closed form
$\kappa(\cA) \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}$
follows from Theorem~\ref{thm:thqg-I-generating-function}. For
arbitrary modular Koszul algebras, the unconditional scalar statement
is $F_1(\cA)=\kappa(\cA)/24$.
\end{definition}

\begin{remark}[Scalar versus full]
% label removed: rem:thqg-I-scalar-vs-full
The scalar partition function captures only the scalar trace of the corresponding cohomological modular-functor package. The full gravitational partition function includes the higher-degree contributions from the shadow obstruction tower: the spectral discriminant $\Delta_\cA$ (degree~$2$ spectral channel), the cubic shadow $\mathfrak{C}$ (degree~$3$), the quartic resonance class $\mathfrak{Q}$ (degree~$4$), and all higher shadows. For Gaussian algebras (shadow depth $r_{\max} = 2$), the scalar and full partition functions coincide.
\end{remark}

\begin{remark}[Genus-$0$ normalization]
% label removed: rem:thqg-I-genus-0
\index{gravitational partition function!genus-0 normalization}
The genus-$0$ contribution $F_0(\cA) = \kappa(\cA)$ is a convention: it
supplies the completed scalar bookkeeping series
$Z_{\mathrm{grav}}^{\mathrm{scal}}(T;\,\hbar)
= \kappa + \sum_{g \geq 1} F_g \hbar^g$. This should not be confused
with the full analytic partition function defined genuswise by the
sewing integrals. In the semiclassical limit $\hbar \to 0$, only the
genus-$0$ term survives.
\end{remark}

\subsubsection{Convergence from HS-sewing and Bernoulli asymptotics}

\begin{theorem}[Perturbative finiteness of twisted gravity; \ClaimStatusProvedHere]
\label{thm:thqg-I-perturbative-finiteness}
\index{perturbative finiteness!main theorem|textbf}
Let $\cA$ be a modular Koszul chiral algebra satisfying the HS-sewing condition \textup{(}Theorem~\textup{\ref{thm:general-hs-sewing})}. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Genus-by-genus finiteness.} For each $g \geq 1$, the genus-$g$ shadow amplitude $\int_{\overline{\mathcal{M}}_g} \operatorname{Sh}_{g,n}(\Theta_\cA)$ is finite at every degree~$n$.
\item \emph{Scalar partition function on the proved scalar lane.} If $\cA$ has generators of uniform conformal weight, then the series $\sum_{g=1}^{\infty} F_g(\cA)\,\hbar^g$ converges absolutely for $|\hbar| < 4\pi^2$, with the closed-form expression $Z_{\mathrm{grav}}^{\mathrm{scal}}(\cA;\,\hbar) = \kappa(\cA) \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}$. For arbitrary modular Koszul algebras, the universal scalar statement is the finite genus-$1$ term $F_1(\cA)=\kappa(\cA)/24$.
\item \emph{Full partition function beyond the scalar lane.} The full degree-summed amplitude is well defined at each fixed genus. If $\cA$ is Gaussian, then the full partition function equals the scalar partition function and therefore converges for $|\hbar| < 4\pi^2$ with meromorphic continuation. No general lower bound on the full genus-sum radius is asserted here beyond the Gaussian case.
\item \emph{No UV renormalization.} No counterterms or renormalization are needed at any genus. The Maurer--Cartan equation $D_\cA\Theta_\cA + \tfrac{1}{2}[\Theta_\cA,\Theta_\cA] = 0$ (Theorem~\ref*{V1-thm:mc2-bar-intrinsic}) is an identity of the bar differential, and the Fulton--MacPherson compactification provides the geometric regulator.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Part~(i).} Fix genus~$g$ and degree~$n$. The shadow representation $\operatorname{Sh}_{g,n}(\Theta_\cA) \in H^*(\overline{\mathcal{M}}_{g,n})$ is a cohomology class on a compact orbifold. Integration over $\overline{\mathcal{M}}_{g,n}$ is a continuous linear functional on this finite-dimensional space, hence bounded. The nontrivial content is that the class itself is well defined: this follows from the bar-intrinsic construction of $\Theta_\cA$ (Theorem~\ref*{V1-thm:mc2-bar-intrinsic}), which gives $\Theta_\cA := D_\cA - d_0 \in \mathrm{MC}(\gAmod)$ without convergence issues.

At the chain level, the integral is computed by the degree-cutoff lemma (Lemma~\ref{V1-lem:degree-cutoff}): the graph sum through degree~$r$ at genus~$g$ involves only finitely many graphs $\Gamma$ with $|\Gamma| \leq r$ edges and loop genus $\leq g$. Each graph amplitude $\ell_\Gamma = |\Aut(\Gamma)|^{-1} \int_{\overline{\mathcal{M}}_{g(\Gamma),n(\Gamma)}} \omega_\Gamma$ is a period integral on a compact moduli space, hence finite.

\emph{Part~(ii).} On the scalar lane this is
Theorem~\ref{thm:thqg-I-absolute-convergence}: the Bernoulli
asymptotics $|F_g| \sim 2|\kappa|/(2\pi)^{2g}$ give absolute
convergence for $|\hbar| < 4\pi^2$, and analytic continuation via the
closed form extends to all of~$\mathbb{C}$ as a meromorphic function.
For arbitrary modular Koszul algebras, the genus-$1$ clause is
Theorem~\ref{V1-thm:genus-universality}\textup{(iii)}.

\emph{Part~(iii).} For the full partition function, each fixed-genus
contribution is a sum over the shadow obstruction tower. If $\cA$ has finite
shadow depth, this is a finite degree sum. If $\cA$ has infinite
shadow depth, the degree sum converges at each fixed genus by
Theorem~\ref{V1-thm:recursive-existence}. In the Gaussian case
$r_{\max}=2$, all higher-degree corrections vanish, so the full
partition function equals the scalar partition function from
Part~(ii). No stronger general full-radius statement is proved here.

\emph{Part~(iv).} The absence of UV divergences is the combined consequence of three features:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Compactness.} The Fulton--MacPherson compactification $\overline{\mathrm{FM}}_n(\Sigma_g)$ is a compact manifold with corners. All integrals are over compact domains.
\item \emph{Algebraic closure.} The Maurer--Cartan equation is an identity of the bar differential ($D_\cA^2 = 0$), not a perturbative expansion. There are no UV divergences to regulate because the equation holds at all genera without truncation.
\item \emph{Degree cutoff.} At each genus~$g$, only finitely many graph topologies contribute (Lemma~\ref{V1-lem:degree-cutoff}). The number of contributing graphs at genus $g$ and degree $r$ is bounded by a combinatorial function of $(g,r)$, and each graph amplitude is a finite integral.
\end{enumerate}
\end{proof}

\subsubsection{Comparison with standard QFT divergences}

\begin{remark}[Contrast with perturbative quantum gravity in $d = 4$]
% label removed: rem:thqg-I-contrast-4d
\index{UV divergence!standard quantum gravity}
In standard four-dimensional perturbative quantum gravity (Einstein--Hilbert action), the genus-$g$ contribution to the graviton scattering amplitude diverges for $g \geq 2$ as
\begin{equation}% label removed: eq:thqg-I-4d-divergence
\mathcal{A}_g \;\sim\; \Lambda_{\mathrm{UV}}^{2(g-1)} \int_{\mathcal{M}_g} |\Omega_g|^2 \cdot R^{2g},
\end{equation}
where $\Lambda_{\mathrm{UV}}$ is the UV cutoff and $R$ is the Riemann curvature. In the twisted holographic setting, the analogous quantity $\mathcal{A}_g^{\mathrm{tw}} = \int_{\overline{\mathcal{M}}_g} \operatorname{Sh}_{g,n}(\Theta_\cA)$ is finite at every genus because: (a)~the integration domain $\overline{\mathcal{M}}_g$ is compact; (b)~the integrand is a smooth cohomology class; (c)~the Maurer--Cartan equation provides a Ward identity constraining the amplitudes genus by genus. The fundamental difference is that the twisted holographic gravity lives on the moduli space of curves, not on spacetime.
\end{remark}

\begin{remark}[Contrast with string theory]
% label removed: rem:thqg-I-contrast-string
\index{string theory!UV finiteness}
In string theory, genus-$g$ amplitudes are finite individually (after integration over $\overline{\mathcal{M}}_g$), but the genus expansion $\sum_g g_s^{2g-2} \mathcal{A}_g$ is asymptotic: it diverges factorially as $\mathcal{A}_g \sim (2g)! \cdot \alpha'^{-g}$. In the twisted holographic setting, the individual amplitudes are also finite (same reason: compactness of $\overline{\mathcal{M}}_g$), but the genus expansion \emph{converges}: $F_g \sim \kappa/(2\pi)^{2g}$ decays exponentially. The difference stems from the cohomological nature of the shadow amplitudes: in string theory, the integrand over $\mathcal{M}_g$ is a genuine function that grows with $g$; in the shadow theory, the integrand is a fixed cohomology class $\kappa \cdot \lambda_g$ whose integral $\lambda_g^{\mathrm{FP}}$ decays.
\end{remark}

\subsubsection{The role of Koszulness in finiteness}

\begin{proposition}[Koszulness and finiteness; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-koszulness-finiteness
\index{Koszulness!role in finiteness}
For a modular Koszul chiral algebra $\cA$, the shadow obstruction tower $\Theta_\cA^{\leq r}$ has the following finiteness properties:
\begin{enumerate}[label=\textup{(\roman*)}]
\item At each degree $r$ and genus $g$, the graph sum
 \begin{equation}% label removed: eq:thqg-I-graph-sum-finite
 \Theta_\cA^{(g,r)} \;=\; \sum_{\substack{\Gamma \in \Gmod(g,r) \\ \Gamma \text{ connected}}} \frac{1}{|\Aut(\Gamma)|} \int_{\overline{\mathcal{M}}_{g(\Gamma),n(\Gamma)}} \omega_\Gamma
 \end{equation}
 is a finite sum over a finite set of graphs.
\item The Koszul property ensures that the transferred cyclic minimal model has only finitely many nontrivial operations at each degree, so the vertex labels $\ell_n^{\mathrm{tr}}$ are nonzero only for $n$ in a finite range.
\item The shadow depth $r_{\max}(\cA)$ bounds the degree of contributing graphs: for $r > r_{\max}$, the obstruction class $o_{r+1}(\cA) = 0$ and the shadow obstruction tower stabilizes.
\end{enumerate}
\end{proposition}

\begin{proof}
Part~(i) is the degree-cutoff lemma (Lemma~\ref{V1-lem:degree-cutoff}). The set $\Gmod(g,r)$ of connected modular graphs with loop genus $g$ and total degree $\leq r$ is finite: the number of vertices $v$, edges $e$, and external legs $n$ satisfy $v - e + n = 1 - g$ (the Euler characteristic), $2e + n \leq rv$ (each vertex has at most $r$ half-edges), and $g = e - v + 1 + \sum_{v'} g_{v'}$ where $g_{v'}$ is the genus decoration at each vertex. These constraints bound $v, e, n$ in terms of $g$ and $r$.

Part~(ii) follows from the PBW concentration property (Proposition~\ref{V1-prop:standard-examples-modular-koszul}): for a Koszul algebra, the transferred $A_\infty$ operations $m_n^{\mathrm{tr}}$ vanish for $n$ sufficiently large (bounded by the Koszul dual degree).

Part~(iii) is the definition of shadow depth: if $o_{r+1}(\cA) = 0$, then $\Theta_\cA^{\leq r+1} = \Theta_\cA^{\leq r}$, and the tower stabilizes.
\end{proof}

\begin{proposition}[Effective graph count; \ClaimStatusProvedHere]
\label{prop:thqg-I-graph-count}
\index{graph sum!effective count}
The number of connected modular graphs contributing to $\Theta_\cA^{(g,r)}$ is bounded by
\begin{equation}% label removed: eq:thqg-I-graph-bound
|\Gmod(g,r)| \;\leq\; C(g,r) \;:=\; \sum_{v=1}^{3g-3+r} \binom{v(r-1)/2 + g - 1}{g} \cdot r^v,
\end{equation}
which is finite for fixed $(g,r)$ and grows polynomially in $r$ at fixed $g$.
\end{proposition}

\begin{proof}
A connected graph with $v$ vertices and loop genus $g$ has $e = v + g - 1$ edges. Each vertex has valence at most $r$ (by the degree cutoff), so $2e + n \leq rv$, giving $n \leq rv - 2(v+g-1) = v(r-2) - 2g + 2$. The condition $n \geq 0$ requires $v \geq (2g-2)/(r-2)$ (for $r \geq 3$). The number of graphs with $v$ labeled vertices and $e$ edges is at most $\binom{v(v-1)/2}{e}$ (choosing edges from all possible pairs); the symmetry group reduces this, but the crude bound suffices. The factor $r^v$ accounts for the vertex labeling (choice of operation at each vertex from $\{m_2, m_3, \ldots, m_r\}$).
\end{proof}

\subsubsection{The structure of finiteness at each genus}

\begin{proposition}[Genus-$g$ amplitude decomposition; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-genus-g-decomposition
\index{genus-$g$ amplitude!decomposition}
The genus-$g$ shadow amplitude decomposes as
\begin{equation}% label removed: eq:thqg-I-genus-g-decomp
\int_{\overline{\mathcal{M}}_g} \operatorname{Sh}_{g,0}(\Theta_\cA) \;=\; F_g^{\mathrm{scal}}(\cA) \;+\; \sum_{r=2}^{r_{\max}} F_g^{(r)}(\cA),
\end{equation}
where $F_g^{\mathrm{scal}}$ is the scalar (degree-$0$) contribution and
$F_g^{(r)}$ is the degree-$r$ correction. On the scalar
lane, $F_g^{\mathrm{scal}} = \kappa \cdot \lambda_g^{\mathrm{FP}}$ for
all $g \geq 1$; for arbitrary modular Koszul algebras, the
unconditional scalar statement is $F_1^{\mathrm{scal}}=\kappa/24$
\textup{(}$g = 1$ is unconditional at all weights\textup{)}. % For
a Gaussian algebra ($r_{\max} = 2$), the sum is empty and only the
scalar term survives. For a Lie-type algebra ($r_{\max} = 3$), there
is a single cubic correction $F_g^{(3)}$. For a contact-type algebra
($r_{\max} = 4$), there are cubic and quartic corrections. For a mixed
algebra ($r_{\max} = \infty$), the sum is infinite but converges by the
shadow obstruction tower convergence theorem (Theorem~\ref{V1-thm:recursive-existence}).
\end{proposition}

\begin{proof}
The shadow obstruction tower decomposes by degree:
$\Theta_\cA = \sum_{r \geq 0} \Theta_\cA^{(r)}$ where
$\Theta_\cA^{(r)}$ is the degree-$r$ component. The genus-$g$
projection at degree $0$ gives $F_g^{\mathrm{scal}}$; on the
scalar lane this equals
$\kappa\lambda_g^{\mathrm{FP}}$, while for arbitrary modular Koszul
algebras the universal scalar statement is the genus-$1$ identity
$F_1^{\mathrm{scal}}=\kappa/24$. At degree $r \geq 2$, the projection
$\int_{\overline{\mathcal{M}}_g} \operatorname{Sh}_{g,r}(\Theta_\cA)$
involves a graph sum with vertex labels from the degree-$r$ operations,
and each term is finite by the degree-cutoff argument. The vanishing of
$F_g^{(r)}$ for $r > r_{\max}$ follows from the shadow depth.
\end{proof}

\begin{remark}[Pixton ideal generation from the MC element]
\label{rem:vol2-pixton-from-mc}
\index{Pixton relations!from MC element}
On the semisimple locus of the shadow CohFT, the MC-descended
tautological relations generate the full Pixton ideal
$I_g \subset R^*(\overline{\cM}_{g,n})$
\textup{(}Volume~I, Theorem~\textup{\ref*{V1-thm:pixton-from-mc-semisimple})}.
The proof proceeds via Givental--Teleman reconstruction: semisimplicity
of the shadow CohFT $\Omega^\cA_{g,n}$ enables Teleman's classification,
and the MC-tautological descent produces the full set of Pixton relations
as an output of the genus recursion. In the present context this means
that the perturbative finiteness programme generates not only finite
shadow amplitudes but the complete set of tautological constraints on
$\overline{\cM}_g$.
\end{remark}

% ======================================================================
% SUBSECTION 4: THE HEISENBERG PARTITION FUNCTION AS PROTOTYPE
% ======================================================================

\subsection{The Heisenberg partition function as prototype}
\label{subsec:thqg-I-heisenberg-prototype}
\index{Heisenberg!partition function|textbf}

The Heisenberg algebra is the archetype: Gaussian shadow depth ($r_{\max} = 2$), closed-form solvability via second quantization, and explicit Fredholm determinant formulas at all genera.

\subsubsection{The Heisenberg at genus $g$}

\begin{theorem}[Heisenberg gravitational partition function; \ClaimStatusProvedHere]
\label{thm:heisenberg-sewing}
\index{Heisenberg!genus-$g$ partition function}
For the rank-$1$ Heisenberg algebra $\mathcal{H}_k$ on a genus-$g$ surface $\Sigma_g$ with period matrix $\Omega \in \mathbb{H}_g$ \textup{(}the Siegel upper half-space\textup{)}, the genus-$g$ partition function is the Fredholm determinant
\begin{equation}% label removed: eq:thqg-I-heisenberg-Zg
\boxed{ Z_g(\mathcal{H}_k;\,\Omega) \;=\; \bigl(\det\operatorname{Im}\Omega\bigr)^{-k/2} \cdot \bigl(\det{}'_\zeta \Delta_{\Sigma_g}\bigr)^{-k/2}, }
\end{equation}
where $\det{}'_\zeta$ denotes the zeta-regularized determinant of the scalar Laplacian $\Delta_{\Sigma_g}$ on $\Sigma_g$ \textup{(}excluding the zero mode\textup{)}. The shadow free energy extracted from this is
\begin{equation}% label removed: eq:thqg-I-heisenberg-Fg
F_g(\mathcal{H}_k) \;=\; k \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}\,,
\end{equation}
confirming the general formula~\eqref{V1-eq:thqg-I-Fg-formula} at $\kappa(\mathcal{H}_k) = k$.
\end{theorem}

\begin{proof}
By Wick's theorem, all amplitudes of the Heisenberg algebra factorize into propagator pairings. The propagator on a genus-$g$ surface is the Green's function
\begin{equation}% label removed: eq:thqg-I-green-genus-g
G(z,w;\,\Omega) \;=\; \log|E(z,w;\,\Omega)| - \frac{(\operatorname{Im}\int_w^z \omega)^T (\operatorname{Im}\Omega)^{-1} (\operatorname{Im}\int_w^z \omega)}{2},
\end{equation}
where $E(z,w;\,\Omega)$ is the prime form and $\omega = (\omega_1, \ldots, \omega_g)^T$ is the normalized basis of holomorphic differentials. The prime form is a section of $K^{-1/2} \boxtimes K^{-1/2}$ (not $K^{+1/2}$).

The partition function is the functional determinant of the kinetic operator:
\[
Z_g \;=\; (\det{}'_\zeta \bar{\partial}^*\bar{\partial})^{-k/2} \;=\; (\det\operatorname{Im}\Omega)^{-k/2}\, (\det{}'_\zeta \Delta)^{-k/2},
\]
where the factorization into period-matrix and Laplacian contributions is the Belavin--Knizhnik factorization~\cite{BK86}. The Polyakov formula identifies $\det{}'_\zeta \Delta$ with the norm of the Mumford form on $\overline{\mathcal{M}}_g$; its $g$-th Chern class is $\lambda_g$. The shadow free energy is obtained by integrating the Chern class:
\[
F_g(\mathcal{H}_k) = k \int_{\overline{\mathcal{M}}_g} \lambda_g = k \cdot \lambda_g^{\mathrm{FP}}.
\]
\end{proof}

\begin{remark}[The Belavin--Knizhnik factorization]
% label removed: rem:thqg-I-belavin-knizhnik
\index{Belavin--Knizhnik!factorization}
The factorization $\det{}'_\zeta(\bar\partial^*\bar\partial) = \det(\operatorname{Im}\Omega) \cdot \det{}'_\zeta(\Delta)$ separates the ``holomorphic'' contribution (the period matrix, which depends on the complex structure of $\Sigma_g$) from the ``analytic'' contribution (the Laplacian determinant, which depends on the conformal class). The period matrix factor $(\det\operatorname{Im}\Omega)^{-k/2}$ is the modular-covariant piece that transforms under $\mathrm{Sp}(2g,\mathbb{Z})$, while the Laplacian factor is modular-invariant. Together they give the conformal block for the Heisenberg algebra on $\Sigma_g$.
\end{remark}

\subsubsection{The Fredholm determinant formula}

\begin{proposition}[Fredholm determinant representation; \ClaimStatusProvedElsewhere{} {\textup{Theorem~\ref{V1-thm:heisenberg-one-particle-sewing}}}]
% label removed: prop:thqg-I-fredholm
\index{Fredholm determinant!Heisenberg|textbf}
The genus-$g$ partition function admits a Fredholm determinant representation:
\begin{equation}% label removed: eq:thqg-I-fredholm-det
Z_g(\mathcal{H}_k;\,\Omega) \;=\; \det(1 - K_g)^{-k},
\end{equation}
where $K_g$ is the trace-class sewing operator on the one-particle Bergman space $A^2(\partial D)$, with eigenvalues $q_1^{n_1} \cdots q_{3g-3}^{n_{3g-3}}$ indexed by the sewing moduli $(q_1, \ldots, q_{3g-3})$. The trace-class norm satisfies
\begin{equation}% label removed: eq:thqg-I-Kg-trace-norm
\|K_g\|_1 \;=\; \prod_{i=1}^{3g-3} \frac{q_i}{1-q_i} \;<\; \infty \quad\text{for all } q_i \in (0,1).
\end{equation}
\end{proposition}

\begin{proof}
The pair-of-pants amplitude for the Heisenberg is the second quantization $\Gamma(R)$ of the one-particle Bergman restriction $R \colon A^2(D_{\mathrm{out}}) \to A^2(D_{\mathrm{in},1}) \otimes A^2(D_{\mathrm{in},2})$ (Theorem~\ref{V1-thm:heisenberg-one-particle-sewing}). The one-particle restriction has matrix entries $R_{n,m} = \frac{k}{2\pi i} \oint\oint z^{-n-1}w^{-m-1}G_{\mathrm{pants}}(z,w)\,dz\,dw$, satisfying $|R_{n,m}| \leq C\,q^{(n+m)/2}$ from the collar length $t = -\log q$. Hence $R$ is Hilbert--Schmidt and $\Gamma(R)$ is trace class.

The composition of $3g - 3$ sewing operators gives the genus-$g$ operator $K_g = R_1 \circ \cdots \circ R_{3g-3}$ on the one-particle space. The Fredholm determinant identity $\Tr\,\Gamma(K_g)^k = \det(1 - K_g)^{-k}$ is the boson-fermion correspondence. The trace-class norm bound follows from $\|K_g\|_1 \leq \prod_{i=1}^{3g-3} \|R_i\|_1 = \prod_{i=1}^{3g-3} q_i/(1-q_i)$.
\end{proof}

\begin{remark}[The Bergman space]
% label removed: rem:thqg-I-bergman
\index{Bergman space}
The one-particle Bergman space $A^2(\partial D)$ consists of holomorphic functions on the annular collar around a sewing circle, square-integrable with respect to the Bergman kernel. An orthonormal basis is $\{z^n / \sqrt{2\pi}\}_{n \geq 1}$, and the one-particle sewing operator in this basis has matrix elements $K_{nm} = \delta_{nm} q^n$. The Fredholm determinant is therefore $\det(1 - K) = \prod_{n=1}^\infty (1 - q^n)$, giving the Dedekind eta function upon including the zero-point energy.
\end{remark}

\subsubsection{Comparison with the Dedekind eta function}

\begin{example}[Genus $1$: the Dedekind eta function]
% label removed: ex:thqg-I-genus1-eta
\index{Dedekind eta!Heisenberg partition function}
At genus $g = 1$, the period matrix is $\Omega = \tau \in \mathbb{H}$ and the sewing parameter is $q = e^{2\pi i\tau}$. The Fredholm determinant becomes
\begin{equation}% label removed: eq:thqg-I-genus1-fredholm
Z_1(\mathcal{H}_k;\,\tau) \;=\; (\operatorname{Im}\tau)^{-k/2}\, \prod_{n=1}^{\infty} (1 - q^n)^{-k} \;=\; (\operatorname{Im}\tau)^{-k/2}\, \bigl|\eta(\tau)\bigr|^{-2k},
\end{equation}
where $\eta(\tau) = q^{1/24}\prod_{n=1}^{\infty}(1 - q^n)$ is the Dedekind eta function. The shadow free energy at genus $1$ is $F_1(\mathcal{H}_k) = k/24$, matching~\eqref{V1-eq:thqg-I-F1} with $\kappa = k$.

The connection to the modular characteristic is transparent: the $q$-expansion of $\log \eta(\tau) = \frac{2\pi i\tau}{24} - \sum_{n=1}^\infty \log(1-q^n)$ begins with $\frac{2\pi i \tau}{24}$, and the genus-$1$ free energy is the constant term of the $q$-expansion of $-k\log|\eta(\tau)|$, which is $k/24$.
\end{example}

\begin{example}[Genus $2$: explicit formula]
% label removed: ex:thqg-I-genus2
\index{Heisenberg!genus-2 partition function}
At genus $g = 2$, the period matrix $\Omega = \begin{psmallmatrix} \tau_1 & \tau_{12} \\ \tau_{12} & \tau_2 \end{psmallmatrix} \in \mathbb{H}_2$ and the partition function is
\begin{equation}% label removed: eq:thqg-I-genus2
Z_2(\mathcal{H}_k;\,\Omega) \;=\; \bigl(\det\operatorname{Im}\Omega\bigr)^{-k/2} \cdot \bigl(\det{}'_\zeta \Delta_{\Sigma_2}\bigr)^{-k/2}.
\end{equation}
The shadow free energy is $F_2(\mathcal{H}_k) = 7k/5760$, confirming~\eqref{V1-eq:thqg-I-F2}.

The Fredholm determinant at genus $2$ involves the sewing of three pairs of pants along three circles. In the Schottky uniformization, $\Sigma_2 = (\mathbb{P}^1 \setminus \{6 \text{ discs}\}) / \langle \gamma_1, \gamma_2, \gamma_3 \rangle$ with three sewing parameters $q_1, q_2, q_3$. The one-particle sewing operator is $K_2 = R_1 \circ R_2 \circ R_3$, and $\det(1 - K_2) = \prod_{n_1,n_2,n_3 \geq 1} (1 - q_1^{n_1} q_2^{n_2} q_3^{n_3})$. The shadow free energy is obtained by integrating over the Siegel modular variety $\mathcal{M}_2 = \mathbb{H}_2 / \mathrm{Sp}(4,\mathbb{Z})$.
\end{example}

\begin{example}[Genus $3$]
% label removed: ex:thqg-I-genus3-heisenberg
\index{Heisenberg!genus-3 partition function}
At genus $g = 3$, the surface $\Sigma_3$ has $3g - 3 = 6$ sewing parameters. The Fredholm determinant is $\det(1 - K_3)^{-k}$ where $K_3$ is a trace-class operator on the one-particle Bergman space. The shadow free energy is $F_3(\mathcal{H}_k) = 31k/967680$. Numerically at $k = 1$: $F_3 \approx 3.20 \times 10^{-5}$, which is already three orders of magnitude smaller than $F_1 = 1/24 \approx 0.042$.
\end{example}

\subsubsection{One-particle Bergman reduction}

\begin{remark}[One-particle reduction principle]
% label removed: rem:thqg-I-one-particle
\index{Bergman space!one-particle reduction|textbf}
The Heisenberg partition function factorizes completely into one-particle data; this is the second quantization principle. The one-particle sewing operator $T_q$ on the Bergman space $A^2(\partial D)$ has eigenvalues $q^n$ ($n = 1, 2, 3, \ldots$), and the full partition function is
\[
Z_g(\mathcal{H}_k) \;=\; \det(1 - T_{q_1} \circ \cdots \circ T_{q_{3g-3}})^{-k} \;=\; \exp\!\left( k \sum_{m=1}^{\infty} \frac{1}{m} \Tr\bigl(T_{q_1} \cdots T_{q_{3g-3}}\bigr)^m \right).
\]
This exponential formula makes the connection to the shadow free energy transparent: $F_g$ is the constant term of $\log Z_g$ in the expansion in sewing moduli. The one-particle reduction is specific to the Heisenberg (Gaussian shadow depth $r_{\max} = 2$): for non-Gaussian algebras, the multi-particle sector contributes genuinely new data that cannot be recovered from the one-particle space.
\end{remark}

\begin{proposition}[Exponential representation; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-exponential-rep
\index{Fredholm determinant!exponential representation}
The Fredholm determinant admits the exponential representation
\begin{equation}% label removed: eq:thqg-I-exponential-fredholm
\log \det(1 - K_g)^{-k} \;=\; k \sum_{m=1}^\infty \frac{1}{m} \Tr(K_g^m) \;=\; k \sum_{m=1}^\infty \frac{1}{m} \sum_{\mathbf{n} \in \mathbb{Z}_{\geq 1}^{3g-3}} \prod_{i=1}^{3g-3} q_i^{m n_i},
\end{equation}
which converges absolutely for all $q_i \in (0,1)$. The shadow free energy $F_g$ is extracted as the coefficient of the leading term in the $\mathbf{q}$-expansion, integrated over $\overline{\mathcal{M}}_g$ with the Weil--Petersson measure.
\end{proposition}

\begin{proof}
The Fredholm determinant identity $\log\det(1 - K) = \Tr\log(1 - K) = -\sum_{m=1}^\infty \frac{1}{m}\Tr(K^m)$ holds for trace-class $K$ with $\|K\|_1 < 1$. For $q_i \in (0,1)$, the eigenvalues of $K_g$ are $\prod_{i=1}^{3g-3} q_i^{n_i}$ with $n_i \geq 1$, all less than $1$. The trace $\Tr(K_g^m) = \sum_{\mathbf{n}} \prod q_i^{mn_i}$ converges absolutely because $\sum_{\mathbf{n}} \prod q_i^{n_i} = \prod_{i=1}^{3g-3} q_i/(1-q_i) < \infty$.
\end{proof}

\begin{remark}[Rank-$d$ Heisenberg]
% label removed: rem:thqg-I-rank-d-heisenberg
\index{Heisenberg!rank-$d$}
For the rank-$d$ Heisenberg algebra $\mathcal{H}_k^{\otimes d}$ (i.e., $d$ independent free bosons at level $k$), the partition function is the $d$-th power of the rank-$1$ answer:
\begin{equation}% label removed: eq:thqg-I-rank-d
Z_g(\mathcal{H}_k^{\otimes d};\,\Omega) \;=\; Z_g(\mathcal{H}_k;\,\Omega)^d \;=\; \bigl(\det\operatorname{Im}\Omega\bigr)^{-dk/2} \cdot \bigl(\det{}'_\zeta\Delta_{\Sigma_g}\bigr)^{-dk/2}.
\end{equation}
The modular characteristic is $\kappa(\mathcal{H}_k^{\otimes d}) = dk$, and the shadow free energy is $F_g(\mathcal{H}_k^{\otimes d}) = dk \cdot \lambda_g^{\mathrm{FP}}$. This is consistent with the independent sum factorization (Proposition~\ref{V1-prop:independent-sum-factorization}): for $\cA = \cA_1 \oplus \cA_2$ with vanishing mixed OPE, $\kappa(\cA) = \kappa(\cA_1) + \kappa(\cA_2)$.
\end{remark}


% ======================================================================
% SUBSECTION 5: FINITENESS FOR THE STANDARD LANDSCAPE
% ======================================================================

\subsection{Finiteness for the standard landscape}
\label{subsec:thqg-I-standard-landscape}
\index{standard landscape!finiteness|textbf}

\subsubsection{Verification of hypotheses (H1)--(H2)}

The HS-sewing criterion (Theorem~\ref{thm:general-hs-sewing}) requires two conditions:
\begin{enumerate}[label=\textbf{(H\arabic*)}]
\item \label{item:thqg-I-H1} \emph{Subexponential sector growth:} $\log \dim H_n = o(n)$.
\item \label{item:thqg-I-H2} \emph{Polynomial OPE growth:} $|C^{c,k}_{a,i;\,b,j}| \leq K(a+b+c+1)^N$.
\end{enumerate}

\begin{proposition}[Standard families satisfy HS-sewing; \ClaimStatusProvedElsewhere{} {\textup{Theorem~\ref{thm:general-hs-sewing}}}]
\label{prop:thqg-I-standard-hs}
\index{HS-sewing!standard families}
Every algebra in the following list satisfies \ref{item:thqg-I-H1} and \ref{item:thqg-I-H2}:
\begin{enumerate}[label=\textup{(\alph*)}]
\item Heisenberg $\mathcal{H}_k$ (any rank, any level $k \neq 0$).
\item Affine Kac--Moody $\widehat{\fg}_k$ ($\fg$ simple, $k \neq -h^\vee$).
\item Virasoro $\mathrm{Vir}_c$ (any $c \in \mathbb{C}$).
\item $\beta\gamma$ system (any central charge).
\item Principal $\mathcal{W}$-algebras $\mathcal{W}_k(\fg)$ ($\fg$ simple, generic $k$).
\item Lattice VOAs $V_\Lambda$ ($\Lambda$ even integral).
\item Free fermions $\psi_1, \ldots, \psi_n$ (any rank).
\end{enumerate}
\end{proposition}

\begin{proof}
For each family, we verify \ref{item:thqg-I-H1} and \ref{item:thqg-I-H2} by direct computation. The key estimates were computed in Computations~\ref{comp:thqg-I-hs-heisenberg}--\ref{comp:thqg-I-hs-fermion}.

\emph{(a) Heisenberg.} $\dim H_n = p(n)$, $\log p(n) \sim \pi\sqrt{2n/3} = o(n)$. OPE degree $N = 1$.

\emph{(b) Affine Kac--Moody.} $\dim H_n$ has subexponential growth (Kac--Peterson~\cite{KP84}). OPE degree $N = 1$.

\emph{(c) Virasoro.} $\dim H_n = p(n)$, $\log p(n) = o(n)$. OPE degree $N = 2$.

\emph{(d) $\beta\gamma$.} $\dim H_n = p(n)^2$, $\log \dim H_n = o(n)$. OPE degree $N = 1$.

\emph{(e) $\mathcal{W}_N$.} Sector growth subexponential with exponent $O(n^{(N-1)/N})$. OPE degree $N_{\max} = 2N$.

\emph{(f) Lattice VOA.} $\dim H_n = |\Lambda^*/\Lambda|\cdot p_r(n)$; $\log p_r(n) = O(\sqrt{n})$. OPE degree $\leq r$.

\emph{(g) Free fermions.} $\dim H_n$ grows at most as $2^n$ (number of subsets of $n$ fermion modes), but the conformal-weight grading gives polynomial growth. OPE degree $N = 0$.
\end{proof}

\subsubsection{Detailed verification for each family}

\begin{proposition}[Heisenberg: detailed HS verification; \ClaimStatusProvedHere]
\label{prop:thqg-I-heisenberg-detail}
\index{Heisenberg!HS verification}
For the rank-$1$ Heisenberg $\mathcal{H}_k$ at level $k \neq 0$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The OPE structure constants are $C^{n-1,\lambda}_{n,\mu;\,0,\mathrm{vac}} = k \cdot \delta_{|\lambda|-|\mu|,1}$ for the fundamental mode $a_{-1}|0\rangle$ acting on a partition state $|\mu\rangle$ of weight $n$ to produce a partition state $|\lambda\rangle$ of weight $n-1$. The general OPE coefficient at weight level $(a,b,c)$ with $a+b-c = m$ (the number of contractions) satisfies $|C^{c,\lambda}_{a,\mu;\,b,\nu}| \leq |k|^m \cdot m! \leq |k|^{a+b} \cdot (a+b)!$, which is polynomial for fixed $m$.
\item The HS norm at weight level $n$ satisfies the exact formula
 \begin{equation}% label removed: eq:thqg-I-heisenberg-exact-hs
 \sum_{\substack{a+b+c = n}} \|m^c_{a,b}\|_{\HS}^2 \;=\; |k|^2 \cdot \sum_{\substack{a+b+c=n}} p(a)p(b)p(c) \cdot \#\{\text{Wick contractions}\},
 \end{equation}
 where the number of Wick contractions at level $n$ grows polynomially.
\end{enumerate}
\end{proposition}

\begin{proof}
The Heisenberg OPE is computed by Wick's theorem: each pair of mode operators $a_m, a_n$ contracts to $k \cdot m \cdot \delta_{m+n,0}$. The number of contractions between a state $|\mu\rangle$ of weight $a$ and a state $|\nu\rangle$ of weight $b$ is at most $\min(a,b)$, and each contraction produces a factor of $|k| \cdot n$ for a mode of level $n$. The polynomial bound follows from the multinomial structure of the Wick expansion.
\end{proof}

\begin{proposition}[Affine Kac--Moody: detailed HS verification; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-affine-detail
\index{affine Kac--Moody!HS verification}
For $\widehat{\fg}_k$ with $\fg$ simple of dimension $d$, rank $r$, and dual Coxeter number $h^\vee$, at non-critical level $k \neq -h^\vee$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The Kac--Peterson character formula gives $\chi_k(\tau) = \sum_{n \geq 0} (\dim H_n) q^n = q^{-c_{\text{eff}}/24} \cdot \Theta_{k+h^\vee,\fg}(\tau) / \eta(\tau)^d$, where $\Theta_{k+h^\vee,\fg}$ is the affine theta function. The dimension $\dim H_n$ is dominated by $\eta(\tau)^{-d}$, giving $\log \dim H_n \sim \pi\sqrt{2dn/3}$.
\item The OPE of currents $J^a_m J^b_n = k m \delta^{ab}\delta_{m+n,0} + f^{ab}{}_c J^c_{m+n}$ has structure constants bounded by $\max(|k|, \|f\|_\infty) \cdot n$ for mode number $n$, which is polynomial of degree $N = 1$.
\item The HS sewing sum satisfies
 \begin{equation}% label removed: eq:thqg-I-affine-hs-refined
 \sum_{a,b,c \geq 0} q^{a+b+c} \|m^c_{a,b}\|_{\HS}^2 \;\leq\; (|k| + \|f\|_\infty)^2 \cdot \prod_{n=1}^\infty (1-q^n)^{-2d} \cdot P(q),
 \end{equation}
 where $P(q) = \sum_{n \geq 0} n^2 (\dim H_n)^2 q^n$ is a convergent power series for $q \in (0,1)$.
\end{enumerate}
\end{proposition}

\begin{proof}
(i) is the Kac--Peterson asymptotic~\cite{KP84}. (ii) follows from the affine Lie algebra commutation relations. (iii) combines the estimates from (i) and (ii) with the general HS bound~\eqref{V1-eq:thqg-I-hs-criterion-bound}.
\end{proof}

\begin{proposition}[Virasoro: detailed HS verification; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-virasoro-detail
\index{Virasoro!HS verification}
For $\mathrm{Vir}_c$ at central charge $c$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The Verma module at weight $h$ has $\dim H_n = p(n)$ (partitions of $n$, corresponding to states $L_{-n_1}L_{-n_2}\cdots L_{-n_k}|h\rangle$ with $n_1 + \cdots + n_k = n$).
\item The OPE $T(z)T(w) \sim c/(2(z-w)^4) + 2T(w)/(z-w)^2 + \partial T(w)/(z-w)$ has a quartic pole. The resulting structure constants satisfy $|C^c_{a,b}| \leq (|c|/2 + 2) \cdot (a+b+1)^2$, which is polynomial of degree $N = 2$.
\item The refined HS bound:
 \begin{equation}% label removed: eq:thqg-I-virasoro-refined-hs
 \sum_{a,b,c \geq 0} q^{a+b+c} \|m^c_{a,b}\|_{\HS}^2 \;\leq\; (|c|/2 + 2)^2 \sum_{n \geq 0} n^4 p(n)^3 q^n.
 \end{equation}
 The series $\sum n^4 p(n)^3 q^n$ converges for all $q \in (0,1)$ because $p(n)^3 \leq e^{3\pi\sqrt{2n/3} + O(\log n)}$ grows subexponentially while $q^n$ decays exponentially. Concretely, for $q = 0.5$: the $n = 100$ term is $100^4 \cdot p(100)^3 \cdot 0.5^{100} \approx 10^8 \cdot (1.9 \times 10^8)^3 \cdot 10^{-30} \approx 10^{2}$, and the series converges.
\end{enumerate}
\end{proposition}

\begin{proof}
(i) is standard Virasoro representation theory. (ii) follows from the mode algebra $[L_m, L_n] = (m-n)L_{m+n} + \frac{c}{12}m(m^2-1)\delta_{m+n,0}$, which gives $|C| \leq |c|/12 \cdot m^3 + |m-n| \cdot |L_{m+n}|$; the polynomial bound is obtained by tracking the maximal power of conformal weight in iterated commutators. (iii) follows from substitution into~\eqref{V1-eq:thqg-I-hs-criterion-bound}.
\end{proof}

\subsubsection{Convergence radii and analytic continuation}

\begin{proposition}[Convergence radii of the scalar partition function; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-convergence-radii
\index{convergence radius!scalar partition function}
The scalar gravitational partition function $Z^{\mathrm{scal}}_{\mathrm{grav}}(\cA;\,\hbar) = \kappa \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}$ has:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Radius of convergence in $\hbar$:} $R = 4\pi^2 \approx 39.48$.
\item \emph{First singularity:} A pole of order $1$ at $\hbar = 4\pi^2$, corresponding to the first zero of $\sin(\sqrt{\hbar}/2)$ at $\sqrt{\hbar} = 2\pi$.
\item \emph{Analytic continuation:} $Z^{\mathrm{scal}}$ extends to a meromorphic function on $\mathbb{C}$ with poles at $\hbar = 4\pi^2 n^2$, $n \in \mathbb{Z}_{> 0}$.
\end{enumerate}
\end{proposition}

\begin{proof}
The function $f(\hbar) = \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}$ is analytic at $\hbar = 0$ (removable singularity: $f(0) = 1$). The root test gives $\limsup_{g \to \infty} |a_g|^{1/g} = 1/(2\pi)^2 = 1/(4\pi^2)$, so the radius of convergence is $4\pi^2$. The poles at $\hbar = 4\pi^2 n^2$ are simple with residues $(-1)^{n+1} \cdot 2n\pi \cdot \kappa$.
\end{proof}

\begin{remark}[Hagedorn singularities]
% label removed: rem:thqg-I-hagedorn
\index{Hagedorn singularity}
The poles at $\hbar = 4\pi^2 n^2$ are the gravitational analogues of the Hagedorn temperature in string theory. At $\hbar = 4\pi^2$, the genus sum first diverges. Beyond this point, the partition function requires analytic continuation and the genus expansion breaks down. In the holographic context, the pole at $\hbar = 4\pi^2$ corresponds to a phase transition in the gravitational theory: the genus expansion becomes unreliable, and non-perturbative effects (saddle-point contributions from higher-topology geometries) must be included.
\end{remark}

\subsubsection{Admissible levels and singular fibers}

\begin{remark}[Admissible levels]
% label removed: rem:thqg-I-admissible
\index{admissible level!finiteness}
At admissible levels $k = -h^\vee + p/q$ (with $p,q$ coprime positive integers and $p \geq h^\vee$), the universal vertex algebra $V_k(\fg)$ has null vectors and the simple quotient $L_k(\fg)$ differs from $V_k(\fg)$. The HS-sewing criterion applies to $V_k(\fg)$ unconditionally (by Proposition~\ref{prop:thqg-I-standard-hs}). For the simple quotient $L_k(\fg)$, the Kac--Wakimoto character formula~\cite{KW88} still supplies the subexponential sector-growth half of the HS criterion, and the admissible-level bar analysis of the manuscript gives weightwise finite-page control on the non-degenerate lane together with reduced/nilradical obstruction surfaces on the degenerate lane. What is \emph{not} proved here is the full HS-sewing criterion for $L_k(\fg)$ itself: polynomial OPE growth and compatible Hilbert--Schmidt norm control on the quotient are additional analytic input not established on this surface.

The modular characteristic is $\kappa(V_k(\fg)) = td/(2h^\vee)$ with $t = k + h^\vee$, which vanishes at critical level $k = -h^\vee$. At critical level, the scalar shadow free energies all vanish: $F_g = 0$ for all $g \geq 1$. The Feigin--Frenkel center emerges as the replacement for the scalar genus package.
\end{remark}

\begin{remark}[Singular fibers]
% label removed: rem:thqg-I-singular-fibers
\index{singular fiber!modular characteristic}
As the level $k$ varies, the modular characteristic $\kappa(k) = td/(2h^\vee)$ with $t = k + h^\vee$ traces a linear function of $k$. The critical level $k = -h^\vee$ is the unique singular fiber where $\kappa$ vanishes. Near the singular fiber, $\kappa \to 0$ and the scalar shadow free energies $F_g \to 0$ uniformly: $|F_g(k)| \leq C |k + h^\vee| / (2\pi)^{2g}$ for all $g$. The scalar class collapses to $\Theta_\cA^{\min} = 0$ at $k = -h^\vee$; this does not determine the higher-degree tower.
\end{remark}

\begin{remark}[Critical level and the Feigin--Frenkel center]
% label removed: rem:thqg-I-ff-center
\index{Feigin--Frenkel center}
At critical level $k = -h^\vee$, the Sugawara construction is \emph{undefined} (not ``$c$ diverges''; the Sugawara tensor $T(z) = \frac{1}{2(k+h^\vee)} \sum_a :J^a(z) J^a(z):$ has a pole at $k = -h^\vee$). The Feigin--Frenkel theorem identifies the center $Z(V_{-h^\vee}(\fg)) \cong \mathrm{Fun}\,\mathrm{Op}_{\fg^\vee}(\mathbb{D})$ with the algebra of functions on the space of $\fg^\vee$-opers on the formal disc. The \emph{scalar} shadow free energy vanishes at this level because $\kappa = 0$ (forcing $m_0 = 0$, hence the scalar lane is uncurved); the higher-degree components of the MC element are not determined by $\kappa = 0$ alone, and $F_1 = 0$ does not imply $F_g = 0$ at higher degree. The Feigin--Frenkel center provides a replacement for the scalar genus package: the ``classical'' genus-$g$ invariant is the space of $\fg^\vee$-opers on $\Sigma_g$, which is finite-dimensional and does not require the HS-sewing machinery.
\end{remark}

\subsubsection{Summary table}

\begin{table}[ht]
\centering
\caption{Perturbative finiteness: standard landscape}
\label{tab:thqg-I-finiteness-summary}
\index{perturbative finiteness!summary table}
\renewcommand{\arraystretch}{1.4}
{\footnotesize
\begin{tabular}{|l|c|c|c|c|c|}
\hline
\textbf{Family $\cA$} & $\boldsymbol{\dim H_n}$ & \textbf{OPE $N$} & $\boldsymbol{\kappa}$ & $\boldsymbol{r_{\max}}$ & \textbf{HS Status} \\
\hline
$\mathcal{H}_k$ & $p(n)$ & $1$ & $k$ & $2$ & \textbf{Proved} \\
\hline
$\widehat{\fg}_k$ & $\sim e^{\pi\sqrt{2dn/3}}$ & $1$ & $\frac{(k+h^\vee)d}{2h^\vee}$ & $3$ & \textbf{Proved} \\
\hline
$\mathrm{Vir}_c$ & $p(n)$ & $2$ & $c/2$ & $\infty$ & \textbf{Proved} \\
\hline
$\beta\gamma$ & $p(n)^2$ & $1$ & $1$ & $4$ & \textbf{Proved} \\
\hline
$\mathcal{W}_N$ & $N$-colored & $2N$ & $c(H_N - 1)$ & $\infty$ & \textbf{Proved} \\
\hline
$V_\Lambda$ & $|\Lambda^*/\Lambda|\cdot p_r(n)$ & $r$ & $\rank(\Lambda)$ & $2$ & \textbf{Proved} \\
\hline
Free fermions & polynomial & $0$ & $n/4$ & $2$ & \textbf{Proved} \\
\hline
\end{tabular}}
\end{table}

\begin{remark}[Exhaustiveness]
% label removed: rem:thqg-I-exhaustiveness
\index{standard landscape!exhaustiveness}
The seven families in Table~\ref{tab:thqg-I-finiteness-summary} exhaust the ``standard landscape'' of finitely strongly generated chiral algebras with simple Lie symmetry. Finiteness extends to:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Tensor products:} $\cA \otimes \cB$ satisfies HS-sewing if both $\cA$ and $\cB$ do (the HS norm of the tensor product is the product of HS norms).
\item \emph{Cosets:} $\cA / \cB$ (the coset of $\cB \subset \cA$) satisfies HS-sewing if $\cA$ does (the sector dimensions can only decrease).
\item \emph{Orbifolds:} $\cA^G$ (orbifold by a finite group $G$) satisfies HS-sewing if $\cA$ does (the twisted sectors contribute additional terms, but all with subexponential growth).
\item \emph{Non-principal $\mathcal{W}$-algebras:} $\mathcal{W}_k(\fg, f)$ for nilpotent $f$ satisfies HS-sewing at generic $k$ (the DS reduction does not increase OPE degree).
\end{enumerate}
\end{remark}


% ======================================================================
% SUBSECTION 6: IMPLICATIONS FOR 3D QUANTUM GRAVITY
% ======================================================================

\subsection{Implications for 3d quantum gravity}
\label{subsec:thqg-I-3d-gravity}
\index{3d quantum gravity|textbf}
\index{BTZ black hole!partition function}

Three-dimensional gravity with negative cosmological constant $\Lambda = -1/\ell^2$ is the physical arena where the perturbative finiteness theorem has the most direct consequences. The boundary theory is a 2d CFT with central charge determined by the Brown--Henneaux formula $c = 3\ell/(2G)$.

\subsubsection{The Brown--Henneaux identification}

\begin{setup}[Brown--Henneaux central charge]
\label{setup:thqg-I-brown-henneaux}
\index{Brown--Henneaux!central charge}
The asymptotic symmetry algebra of AdS$_3$ gravity at spatial infinity is two copies of the Virasoro algebra with central charge
\begin{equation}% label removed: eq:thqg-I-brown-henneaux
c \;=\; \frac{3\ell}{2G}\,,
\end{equation}
where $\ell$ is the AdS radius and $G$ is the three-dimensional Newton constant~\cite{BH86}. In the twisted holographic setting, $\cA = \mathrm{Vir}_c$ is the boundary chiral algebra, with modular characteristic $\kappa(\cA) = c/2 = 3\ell/(4G)$.
\end{setup}

\begin{remark}[Semiclassical limit]
% label removed: rem:thqg-I-semiclassical
\index{semiclassical limit}
The semiclassical limit is $G \to 0$ with $\ell$ fixed, which gives
$c \to \infty$ and $\kappa=c/2 \to \infty$. On the Virasoro scalar
lane one has $F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$
\textup{(}uniform-weight\textup{)} for $g \geq
1$, so each scalar coefficient grows linearly with~$\kappa$ while the
ratios $F_g/F_0 = \lambda_g^{\mathrm{FP}}$ are independent of
$\kappa$. If one specializes the formal genus parameter to
$\hbar = 1/c \sim G/\ell$, then the reduced scalar series
$\sum_{g \geq 1} F_g \hbar^g$ is an honest convergent expansion in
$1/c$, while the full scalar bookkeeping series still carries the
tree-level term $F_0=\kappa=c/2$.
\end{remark}

\subsubsection{BTZ-normalized scalar shadow series}

\begin{theorem}[BTZ-normalized scalar shadow series; \ClaimStatusProvedHere]
% label removed: thm:thqg-I-btz
\index{BTZ black hole!shadow free energy}
Under the Brown--Henneaux identification, the genus-$1$ scalar shadow
term is
\begin{equation}% label removed: eq:thqg-I-btz-F1
F_1^{\mathrm{BTZ}} \;=\; F_1(\mathrm{Vir}_c) \;=\; \frac{c}{48} \;=\; \frac{\ell}{32G}\,.
\end{equation}
On the proved scalar lane \textup{(}here $\mathrm{Vir}_c$\textup{)}, the
associated scalar shadow series is
\begin{equation}% label removed: eq:thqg-I-btz-full
Z_{\mathrm{BTZ}}^{\mathrm{pert}}(\hbar) \;=\; \frac{c}{2} \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)} \;=\; \frac{3\ell}{4G} \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}\,.
\end{equation}
No comparison theorem identifying this scalar series with the full
analytic BTZ partition function is proved here.
\end{theorem}

\begin{proof}
By the Brown--Henneaux identification
(Setup~\ref{setup:thqg-I-brown-henneaux}), the boundary algebra is
$\mathrm{Vir}_c$ with $\kappa = c/2$. The genus-$1$ scalar value is
$F_1 = \kappa/24 = c/48$. Since $\mathrm{Vir}_c$ lies on the proved
scalar lane, the scalar generating function is
\eqref{V1-eq:thqg-I-gf-ahat} with $\kappa = c/2$. Substituting
$c = 3\ell/(2G)$ gives $\kappa = 3\ell/(4G)$. The final sentence is a
status fence: this chapter does not construct a comparison map from the
scalar shadow series to the full analytic BTZ partition function.
\end{proof}

\begin{remark}[Comparison with known results]
% label removed: rem:thqg-I-comparison-btz
\index{BTZ black hole!comparison}
The genus-$1$ correction $F_1 = c/48$ has been computed by multiple
methods: (a)~gravity path integral (Giombi--Maloney--Yin~\cite{GMY08}):
the one-loop determinant of the graviton on the solid torus gives
$\prod_{n=2}^{\infty} (1 - q^n)^{-1}$; (b)~Chern--Simons theory
(Witten~\cite{Witten88}): 3d gravity as
$\mathrm{SL}(2,\mathbb{R}) \times \mathrm{SL}(2,\mathbb{R})$ CS theory,
with $c/24$ for the full theory and $c/48$ for the holomorphic half;
(c)~modular bootstrap (Maloney--Witten~\cite{MW10}). These comparisons
support the genus-$1$ normalization used above. Beyond genus~$1$, the
shadow method provides the scalar series shown above on the Virasoro
scalar lane, but its identification with the full analytic BTZ
partition function is additional dictionary data not proved here.
\end{remark}

\subsubsection{Higher-genus corrections}

\begin{proposition}[Higher-genus BTZ-normalized scalar coefficients; \ClaimStatusProvedHere]
\label{prop:thqg-I-btz-higher-genus}
\index{BTZ black hole!higher-genus corrections}
The genus-$g$ scalar shadow coefficient in the BTZ normalization is
\begin{equation}% label removed: eq:thqg-I-btz-Fg
F_g^{\mathrm{BTZ}} \;=\; \frac{c}{2} \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!} \;=\; \frac{3\ell}{4G} \cdot \lambda_g^{\mathrm{FP}}\,.
\end{equation}
The first five corrections are:
\begin{align}
F_1^{\mathrm{BTZ}} &= \frac{c}{48}\,, % label removed: eq:thqg-I-btz-F1-val \\
F_2^{\mathrm{BTZ}} &= \frac{7c}{11520}\,, % label removed: eq:thqg-I-btz-F2-val \\
F_3^{\mathrm{BTZ}} &= \frac{31c}{1935360}\,, % label removed: eq:thqg-I-btz-F3-val \\
F_4^{\mathrm{BTZ}} &= \frac{127c}{309657600}\,, % label removed: eq:thqg-I-btz-F4-val \\
F_5^{\mathrm{BTZ}} &= \frac{73c}{7007109120}\,. % label removed: eq:thqg-I-btz-F5-val
\end{align}
The ratio $F_{g+1}/F_g \to 1/(4\pi^2)$ as $g \to \infty$, consistent with the Hagedorn singularity at $\hbar = 4\pi^2$.
\end{proposition}

\begin{proof}
Direct from $\kappa(\mathrm{Vir}_c) = c/2$ and the universal formula (Proposition~\ref{prop:thqg-I-Fg-closed-form}).
\end{proof}

\begin{remark}[Numerical values for $c = 24$ (monster CFT)]
% label removed: rem:thqg-I-monster
\index{monster CFT}
For the monster CFT with $c = 24$ (the Frenkel--Lepowsky--Meurman moonshine module $V^\natural$), $\kappa(V^\natural) = 12$, since $\dim V_1^\natural = 0$ forces the modular characteristic to be determined by the Virasoro sector alone: $\kappa = c/2 = 12$:
\begin{align*}
F_1 &= 12/24 = 1/2, \\
F_2 &= 7 \cdot 12/5760 = 84/5760 = 7/480, \\
F_3 &= 31 \cdot 12/967680 = 372/967680 = 31/80640, \\
F_4 &= 127 \cdot 12/154828800 = 1524/154828800 = 127/12902400.
\end{align*}
The one-loop contribution $F_1 = 1/2$ is order $1$, and each
subsequent genus is suppressed by the Bernoulli factor. The scalar
bookkeeping series at $\hbar = 1$ is
\[
Z_{\mathrm{grav}}^{\mathrm{scal}} = 12 \cdot \frac{1/2}{\sin(1/2)}
\approx 12.515.
\]
\end{remark}

\begin{computation}[BTZ entropy through five loops]
\label{comp:btz-five-loop}%
\index{BTZ black hole!five-loop entropy|textbf}%
The perturbative genus expansion of BTZ black hole entropy
through genus~$5$, on the proved scalar lane
$(\mathrm{Vir}_c$, $\kappa = c/2)$:
\begin{equation}\label{eq:btz-five-loop}
S_{\mathrm{BTZ}}^{\mathrm{pert}}
\;=\;
S_{\mathrm{BH}}
\;+\;
\sum_{g=1}^{5} F_g^{\mathrm{BTZ}} \cdot \kappa^{2g-2},
\end{equation}
with $F_g^{\mathrm{BTZ}}$ as in
Proposition~\textup{\ref{prop:thqg-I-btz-higher-genus}}.
The explicit values are $F_1 = c/48$,
$F_2 = 7c/11520$,
$F_3 = 31c/1935360$,
$F_4 = 127c/309657600$,
$F_5 = 73c/7007109120$.
Series convergence is verified by the ratio test:
the consecutive ratios
\begin{align*}
F_2/F_1 &= 7/240, &
F_3/F_2 &= 31/1176, \\
F_4/F_3 &= 127/5040, &
F_5/F_4 &= 73 \cdot 309657600\,/\,(127 \cdot 7007109120)
\;\approx\; 0.0254
\end{align*}
converge to $1/(4\pi^2) \approx 0.0253$, the reciprocal of
the convergence radius $\hbar_{\mathrm{crit}} = 4\pi^2$.
At genus~$5$ the ratio is $|F_5/F_4| \approx 0.158\,/\,0.164
\approx 0.025$, well within the convergence disk.
The scalar shadow series
$Z_{\mathrm{BTZ}}^{\mathrm{pert}}(\hbar)
= \kappa \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}$
has convergence radius $|\hbar| < 4\pi^2$, and the five-loop
truncation captures $>99.5\%$ of the exact scalar sum at
$\hbar = 1$.
\end{computation}

\subsubsection{The quartic contact invariant in sub-subleading corrections}

\begin{remark}[Quartic contact invariant in 3d gravity]
% label removed: rem:thqg-I-quartic-3d
\index{quartic contact invariant!3d gravity}
The scalar channel captures only the degree-$0$ information. The first non-scalar correction comes from the quartic contact invariant
\begin{equation}% label removed: eq:thqg-I-quartic-contact
Q^{\mathrm{contact}}_{\mathrm{Vir}} \;=\; \frac{10}{c(5c+22)}\,,
\end{equation}
which is the degree-$4$, genus-$0$ component of the shadow obstruction tower. For $c = 3\ell/(2G)$, this gives $Q^{\mathrm{contact}} = 10/(c(5c+22)) = 2/c^2 + O(1/c^3)$, a two-loop correction in Newton's constant. The genus-$1$ Hessian correction is
\begin{equation}% label removed: eq:thqg-I-genus1-hessian
\delta_{H,\mathrm{Vir}}^{(1)} \;=\; \frac{120}{c^2(5c+22)}\,x^2\,.
\end{equation}
These corrections are specific to the mixed shadow class ($r_{\max} = \infty$) of the Virasoro algebra.
\end{remark}

\begin{remark}[Shadow depth and gravitational complexity]
% label removed: rem:thqg-I-depth-complexity
\index{shadow depth!gravitational complexity}
The shadow depth classification ($G/L/C/M$ for Gaussian/Lie/Contact/Mixed) stratifies 3d gravity theories by their nonlinear complexity:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Gaussian ($r_{\max} = 2$):} Heisenberg, lattice VOAs, free fermions. Only the quadratic/scalar channel survives. On the proved analytic locus, the partition function is a Fredholm determinant.
\item \emph{Lie-type ($r_{\max} = 3$):} Affine Kac--Moody algebras. Cubic interactions (tree-level scattering). The partition function receives corrections from trivalent graphs.
\item \emph{Contact-type ($r_{\max} = 4$):} $\beta\gamma$ system. Quartic interactions but no higher. The shadow obstruction tower terminates after two nonlinear steps.
\item \emph{Mixed ($r_{\max} = \infty$):} Virasoro, $\mathcal{W}_N$. Interactions at all orders. The full shadow obstruction tower is infinite, and the perturbative finiteness theorem is needed in full strength. The quintic obstruction $o^{(5)}_{\mathrm{Vir}} \neq 0$ forces the tower to be genuinely infinite.
\end{enumerate}
The Brown--Henneaux boundary theory for pure 3d gravity is $\mathrm{Vir}_c$, which falls in the mixed class.
\end{remark}

\subsubsection{Large-$c$ expansion and gravitational coupling}

\begin{proposition}[Leading gravitational coupling expansion of the reduced scalar series; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-1c-expansion
\index{gravitational coupling!large-$c$ expansion}
In the semiclassical specialization $\hbar = 1/c$, the reduced scalar
series \textup{(}obtained by subtracting the genus-$0$ term
$F_0=c/2$\textup{)} has the convergent expansion
\begin{equation}% label removed: eq:thqg-I-1c-expansion
Z_{\mathrm{grav}}^{\mathrm{scal}}(\mathrm{Vir}_c;\,1/c) - \frac{c}{2}
\;=\;
\frac{1}{48} + \frac{7}{11520\,c} + \frac{31}{1935360\,c^2}
\;+\; \frac{127}{309657600\,c^3} + O(c^{-4})\,.
\end{equation}
The leading term $1/48$ is the one-loop correction to the reduced
series, and each subsequent term is suppressed by one additional power
of $G/\ell \sim 1/c$.
\end{proposition}

\begin{proof}
From $F_g(\mathrm{Vir}_c) = (c/2)\lambda_g^{\mathrm{FP}}$, the
genus-$g$ contribution to the reduced scalar series at $\hbar = 1/c$ is
\[
F_g \hbar^g = \frac{c}{2}\lambda_g^{\mathrm{FP}}\,c^{-g}
= \frac{\lambda_g^{\mathrm{FP}}}{2c^{g-1}}.
\]
Therefore
\[
Z_{\mathrm{grav}}^{\mathrm{scal}}(\mathrm{Vir}_c;1/c) - \frac{c}{2}
= \sum_{g \geq 1} \frac{\lambda_g^{\mathrm{FP}}}{2c^{g-1}}.
\]
At $g = 1$, $\lambda_1^{\mathrm{FP}} = 1/24$, giving $1/48$; at
$g = 2$, one obtains $7/(11520c)$; and the remaining coefficients are
computed similarly.
\end{proof}

\begin{proposition}[Newton's constant expansion; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-newton-expansion
\index{Newton's constant!expansion}
Substituting $c = 3\ell/(2G)$ and $\hbar = 2G/(3\ell)$, the gravitational partition function becomes
\begin{equation}% label removed: eq:thqg-I-newton-expansion
Z_{\mathrm{grav}}^{\mathrm{scal}}(\mathrm{Vir}_c;\,2G/(3\ell)) \;=\; \frac{3\ell}{4G} \cdot \frac{\sqrt{2G/(3\ell)}/2}{\sin(\sqrt{2G/(3\ell)}/2)}\,.
\end{equation}
For $G/\ell \ll 1$ (weak gravitational coupling), the expansion in $G/\ell$ gives
\begin{equation}% label removed: eq:thqg-I-G-expansion
Z \;=\; \frac{3\ell}{4G}\left(1 + \frac{G}{72\ell} + \frac{7G^2}{51840\ell^2} + O(G^3/\ell^3)\right).
\end{equation}
\end{proposition}

\begin{proof}
Direct Taylor expansion of $x/(2\sin(x/2))$ at $x = 0$ with $x^2 = 2G/(3\ell)$.
\end{proof}

\subsubsection{Towards the non-perturbative regime}

\begin{conjecture}[Non-perturbative completion; \ClaimStatusConjectured]
\label{conj:thqg-I-non-perturbative}
\index{non-perturbative!gravitational partition function}
The meromorphic function $Z^{\mathrm{scal}}_{\mathrm{grav}}(\hbar) = \kappa \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}$ admits a non-perturbative completion satisfying:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Pole-controlled scales: any completion compatible with the proved scalar lane should reflect the distinguished action scales $4\pi^2 n^2$ coming from the pole set of the meromorphic continuation.
\item Exponential sectors: if genuinely non-perturbative contributions are present, they should be exponentially small of order $e^{-4\pi^2 n^2/\hbar}$; identifying them with non-handlebody saddle points is heuristic.
\item Positivity: for real $\hbar > 0$, the full non-perturbative partition function $Z > 0$.
\end{enumerate}
\end{conjecture}

\begin{evidence}[Evidence for the resurgent structure]
% label removed: evid:thqg-I-resurgent
The Taylor coefficients $F_g \sim 2\kappa/(2\pi)^{2g}$ show that the scalar genus series already converges absolutely for $|\hbar| < 4\pi^2$ and continues meromorphically beyond that disk. The Borel transform is
\begin{equation}% label removed: eq:thqg-I-borel-transform
\hat{Z}(\xi) \;=\; \sum_{g=1}^\infty \frac{F_g}{\Gamma(g)} \xi^{g-1} \;=\; \kappa \sum_{g=1}^\infty \frac{\lambda_g^{\mathrm{FP}}}{(g-1)!} \xi^{g-1}.
\end{equation}
Since $\lambda_g^{\mathrm{FP}} \sim 2/(2\pi)^{2g}$, the ratio $\lambda_g^{\mathrm{FP}}/\Gamma(g) \sim 2/((2\pi)^{2g}(g-1)!)$, and the series converges for all $\xi \in \mathbb{C}$: the Borel transform is entire, so the usual asymptotic-resurgence argument does not apply here. What is visible in the proved scalar lane is instead the meromorphic pole set $\hbar = 4\pi^2 n^2$ of the original function. These pole scales motivate, but do not prove, heuristic exponential sectors of order $e^{-4\pi^2 n^2/\hbar}$ in a fuller non-perturbative completion.
\end{evidence}

\begin{remark}[BTZ black holes as non-perturbative saddles]
\label{rem:thqg-I-btz-saddles}
\index{BTZ black hole!non-perturbative}
In 3d gravity, the BTZ black holes of mass $M = n^2/(8G\ell)$ ($n \geq 1$) are natural candidates for non-perturbative saddle points. Their Euclidean action is $I_n = 4\pi^2 n^2 / \hbar$ (with $\hbar = 2G/(3\ell)$). The coincidence between these action scales and the pole scales of the scalar meromorphic continuation suggests, but does not prove, that BTZ sectors contribute terms of the form $c_n e^{-I_n/\hbar}$. No Stokes-ray or Borel-plane identification is established by the convergent scalar genus series itself.
\end{remark}

%% ===================================== Stokes phenomena on the Steinberg object
\providecommand{\SteinbergB}{\mathfrak{S}_b}

\subsubsection{Stokes phenomena on the Steinberg object}
% label removed: sssec:thqg-stokes-steinberg
\index{Stokes phenomena!Steinberg object}
\index{Steinberg object!Stokes filtration}

The pole scales $\hbar = 4\pi^2 n^2$ of
$Z_{\mathrm{grav}}(\hbar) = \kappa \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}$
motivate a conjectural Stokes-filtered organization on the
Steinberg object~$\SteinbergB$. On the proved scalar lane, however,
the Borel transform
\[
B[Z](\zeta) \;=\; \sum_{g \geq 1} \frac{F_g}{\Gamma(g)}\,\zeta^{g-1}
\]
is entire, so these scales are not singularities of the scalar Borel
transform itself. Rather, they are candidate action scales for a
fuller non-perturbative completion, heuristically associated with the
$n$-th BTZ saddle points (Remark~\ref{rem:thqg-I-btz-saddles}).
The Stokes-filtered Steinberg construction below should therefore be
read as a conjectural organization of possible exponential sectors,
not as a theorem extracted from the proved scalar lane.

\begin{construction}[The Stokes-filtered Steinberg]
% label removed: constr:thqg-stokes-filtered-steinberg
\index{Steinberg object!Stokes-filtered}
Define the \emph{Stokes-filtered Steinberg} $\SteinbergB^{\mathrm{Stokes}}$ as follows. For each $n \geq 1$, let $\SteinbergB^{\mathrm{BTZ},n}$ denote the Steinberg object associated to the $n$-th BTZ saddle, i.e.\ the analogue of~$\SteinbergB$ constructed from the gauge equivalence data of the $n$-th non-handlebody saddle point with Euclidean action $I_n = 4\pi^2 n^2 / \hbar$. The perturbative Steinberg~$\SteinbergB$ is $\SteinbergB^{\mathrm{BTZ},0}$ (the vacuum saddle). The Stokes-filtered Steinberg is the datum
\[
\SteinbergB^{\mathrm{Stokes}} \;=\; \bigl(\SteinbergB,\;\{\SteinbergB^{\mathrm{BTZ},n}\}_{n \geq 1},\;\{S_n\}_{n \geq 1}\bigr)
\]
where $S_n \colon H_*^{\mathrm{BM}}(\SteinbergB) \to H_*^{\mathrm{BM}}(\SteinbergB^{\mathrm{BTZ},n})$ is a conjectural Stokes map in a fuller non-perturbative completion, indexed by the action scale $\zeta_n = 4\pi^2 n^2$.
\end{construction}

\begin{conjecture}[Resurgent structure from Stokes-filtered BM homology; \ClaimStatusConjectured]
% label removed: prop:thqg-stokes-bm-resurgence
\index{resurgence!Steinberg BM homology}
\index{BM homology!Stokes-filtered}
A conjectural non-perturbative completion of $Z_{\mathrm{grav}}$, if it
admits exponential sectors at the pole scales $\zeta_n = 4\pi^2 n^2$,
should be organized by the Stokes-filtered Borel--Moore homology of the
Steinberg:
\begin{equation}% label removed: eq:thqg-stokes-bm-decomposition
H_*^{\mathrm{BM},\,\mathrm{Stokes}}(\SteinbergB) \;=\; H_*^{\mathrm{BM}}(\SteinbergB) \;\oplus\; \bigoplus_{n \geq 1} H_*^{\mathrm{BM}}(\SteinbergB^{\mathrm{BTZ},n})\,,
\end{equation}
where $\SteinbergB^{\mathrm{BTZ},n}$ is the Steinberg object for the $n$-th BTZ saddle. The Stokes automorphism
\[
\mathfrak{S}_n \colon H_*^{\mathrm{BM}}(\SteinbergB) \;\longrightarrow\; H_*^{\mathrm{BM}}(\SteinbergB)
\]
would exchange the perturbative and $n$-th BTZ sectors. In such a
completion one expects exponential contributions of the form
\[
\mathfrak{S}_n([\SteinbergB]) \cdot e^{-\zeta_n / \hbar},
\]
where $[\SteinbergB] \in H_*^{\mathrm{BM}}(\SteinbergB)$ is the
fundamental class. The proved scalar lane does not identify actual
Borel-plane singularities or lateral-resummation discontinuities.
\end{conjecture}

\begin{remark}[Positivity from geometry]
% label removed: rem:thqg-stokes-positivity
\index{positivity!gravitational partition function}
\index{BM homology!fundamental class positivity}
The positivity of $Z_{\mathrm{grav}}$ for real $\hbar > 0$ (away from
the poles $\hbar = 4\pi^2 n^2$) may admit a geometric explanation
through the Steinberg presentation. The perturbative contribution is
$\langle [\SteinbergB], [\SteinbergB] \rangle_{\mathrm{BM}}$, the
self-pairing of the BM fundamental class $[\SteinbergB]$, which is
positive since $\SteinbergB$ carries a canonical orientation as a
complex-algebraic variety. In a fuller non-perturbative completion, the
pole scales $4\pi^2 n^2$ could mark where BTZ strata
$\SteinbergB^{\mathrm{BTZ},n}$ become relevant. Current proofs do not
identify these scales with literal Borel-plane Stokes jumps.
\end{remark}

\begin{remark}[Pure 3d gravity as a model]
% label removed: rem:thqg-I-pure-3d
\index{3d gravity!pure}
Pure 3d gravity with $\Lambda < 0$ is the simplest non-trivial gravitational theory. Its boundary algebra is $\mathrm{Vir}_c$ with $c = 3\ell/(2G)$, which falls in the mixed class. The perturbative finiteness theorem provides a complete, explicit, genus-by-genus calculation of the gravitational partition function:
\[
Z_{\mathrm{grav}}^{\mathrm{scal}}(\hbar) \;=\; \frac{3\ell}{4G} \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}\,.
\]
The non-scalar corrections from $Q^{\mathrm{contact}} = 10/(c(5c+22))$ and the infinite shadow obstruction tower encode the genuinely nonlinear aspects of the gravitational theory, suppressed by $1/c^2$ relative to the scalar contribution.
\end{remark}

\begin{remark}[Comparison with matrix models]
% label removed: rem:thqg-I-matrix-models
\index{matrix model!gravitational partition function}
In 2d topological gravity (Witten--Kontsevich), the genus-$g$ free energy involves Bernoulli numbers with a different prefactor: the Witten--Kontsevich generating function is $\sum_g F_g^{\mathrm{WK}} (2g-2)! x^{2g-2}$, with $F_g^{\mathrm{WK}} = \chi(\mathcal{M}_g) / (2g-2)!$ involving the orbifold Euler characteristic. The relation to the shadow generating function is $\frac{x/2}{\sin(x/2)} = \left.\frac{x/2}{\sinh(x/2)}\right|_{x \mapsto ix}$, reflecting the Wick rotation from Lorentzian to Euclidean signature. In the matrix model, the $\sinh$ function arises from the Gaussian integral, while in the shadow theory, the $\sin$ function arises from the Hodge integral; the two are related by analytic continuation $x \mapsto ix$.
\end{remark}

\begin{remark}[Higher-spin gravity]
% label removed: rem:thqg-I-higher-spin
\index{higher-spin gravity}
For higher-spin gravity in AdS$_3$ with $\mathcal{W}_N$ symmetry, the boundary algebra is $\mathcal{W}_k(\mathfrak{sl}_N)$ at central charge $c = (N-1) - N(N^2-1)(k+N-1)^2/(k+N)$. The modular characteristic is $\kappa(\mathcal{W}_N) = c \cdot (H_N - 1)$ where $H_N = \sum_{j=1}^N 1/j$ is the $N$-th harmonic number ($\kappa = c/2$ for $N=2$, $\kappa = 5c/6$ for $N=3$). The perturbative partition function is
\[
Z_{\mathrm{grav}}^{W_N}(\hbar) \;=\; \kappa(\mathcal{W}_N) \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}\,,
\]
which has the same functional form as the Virasoro case but with a different normalization. The qualitative features (convergence for $|\hbar| < 4\pi^2$, Hagedorn singularity, resurgent structure) are identical. The difference lies in the non-scalar corrections: $\mathcal{W}_N$ has shadow depth $r_{\max} = \infty$ and the shadow obstruction tower includes contributions from all $W^{(s)}$ fields ($s = 2, \ldots, N$).
\end{remark}

\subsubsection{The holographic dictionary}

\begin{remark}[The holographic dictionary]
% label removed: rem:thqg-I-holographic-dictionary
\index{holographic dictionary!perturbative finiteness}
The perturbative finiteness theorem (Theorem~\ref{thm:thqg-I-perturbative-finiteness}) translates into the holographic dictionary:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{l|l}
\textbf{Boundary (algebra)} & \textbf{Bulk (gravity)} \\
\hline
$\cA$ (chiral algebra) & boundary conditions \\
$\kappa(\cA)$ (modular characteristic) & cosmological constant \\
$F_g(\cA)$ (shadow free energy) & genus-$g$ path integral \\
HS-sewing condition & UV finiteness \\
$\Theta_\cA$ (MC element) & classical solution + perturbations \\
$D_\cA^2 = 0$ & Ward identity \\
$r_{\max}(\cA)$ (shadow depth) & gravitational complexity \\
$4\pi^2$ (convergence radius) & Hagedorn temperature \\
$Q^{\mathrm{contact}}$ (quartic invariant) & two-loop graviton self-energy \\
$\cA^!$ (Koszul dual) & dual boundary conditions \\
\end{tabular}
\end{center}
The passage from boundary data to bulk partition function is
algorithmic in two separate senses: given the OPE data of $\cA$, the
modular characteristic $\kappa$ is computable, and the genuswise shadow
amplitudes are finite. On the proved scalar lane, this is supplemented
by the closed scalar series
$Z_{\mathrm{grav}}^{\mathrm{scal}} = \kappa \cdot x/(2\sin(x/2))$.
Beyond that lane, the manuscript only proves fixed-genus finiteness and
the universal genus-$1$ scalar term. No UV regularization, no
renormalization group flow, and no anomaly matching are required.
\end{remark}

\begin{remark}[Summary of the finiteness mechanism]
% label removed: rem:thqg-I-finiteness-summary
\index{perturbative finiteness!mechanism summary}
The perturbative finiteness of twisted quantum gravity rests on a chain of three implications:
\begin{equation}% label removed: eq:thqg-I-chain
\underbrace{D_\cA^2 = 0}_{\text{bar complex}} \;\Longrightarrow\; \underbrace{\Theta_\cA \in \mathrm{MC}(\gAmod)}_{\text{all-genera MC}} \;\Longrightarrow\; \underbrace{\int_{\overline{\mathcal{M}}_g}\operatorname{Sh}_{g,0}(\Theta_\cA) < \infty}_{\text{genuswise finite amplitudes}}.
\end{equation}
The first implication is the bar-intrinsic construction
\textup{(}Theorem~\ref*{V1-thm:mc2-bar-intrinsic}\textup{)}: the
element $\Theta_\cA := D_\cA - d_0$ is automatically Maurer--Cartan
because the bar differential squares to zero. The second implication
is the projection onto genus~$g$: the shadow free energy is the
integral of a cohomology class over a compact moduli space, hence
finite. On the proved scalar lane this genuswise finiteness is
supplemented by the closed formula
$F_g=\kappa\lambda_g^{\mathrm{FP}}$
\textup{(}uniform-weight\textup{)}; in general the manuscript only
proves the universal genus-$1$ scalar identity $F_1=\kappa/24$. The
entire mechanism is algebraic (no analysis of divergences, no
regularization, no renormalization) and non-perturbative (no
truncation, no asymptotic expansion).
\end{remark}


% ======================================================================
% SUBSECTION 7: THE HS-SEWING CONDITION AND THE MC RECURSION
% ======================================================================

\subsection{HS-sewing and the MC recursion}
% label removed: subsec:thqg-I-hs-mc-recursion
\index{HS-sewing!MC recursion}

The HS-sewing condition and the MC recursion interact at two levels: the HS condition provides the \emph{analytic} input (convergence of sewing amplitudes), while the MC recursion provides the \emph{algebraic} input (unique determination of higher-genus data from lower-genus data). Together, they give a genus-by-genus algorithm for computing the gravitational partition function: the analytic half (HS-sewing convergence) is proved; the algebraic comparison between the sewing output and the bar-intrinsic MC element (the BV/BRST identification) remains conjectural at each genus.

\subsubsection{The sewing amplitude as a graph sum}

\begin{proposition}[Graph-sum representation of sewing amplitudes; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-graph-sum-sewing
\index{sewing amplitude!graph-sum representation}
Let $\cA$ be a modular Koszul chiral algebra satisfying HS-sewing. The genus-$g$ sewing amplitude on a surface $\Sigma_g$ with pants decomposition $\mathcal{P}$ has the graph-sum representation
\begin{equation}% label removed: eq:thqg-I-graph-sewing
Z_{\mathcal{P}}(\cA;\,\mathbf{q}) \;=\; \sum_{\Gamma \in \Gmod(g)} \frac{1}{|\Aut(\Gamma)|}\,\ell_\Gamma(\mathbf{q}),
\end{equation}
where the sum runs over connected modular graphs $\Gamma$ of total genus $g$, and $\ell_\Gamma(\mathbf{q})$ is the graph amplitude: the product of vertex labels (transferred cyclic operations $\ell_n^{\mathrm{tr}}$) and edge propagators ($P_\cA(q_e) = \sum_{n \geq 0} q_e^n \pi_n$, the weighted projection onto the $n$-th conformal weight).
\end{proposition}

\begin{proof}
The pants decomposition $\mathcal{P}$ determines a dual graph $\Gamma_\mathcal{P}$ with one vertex for each pair of pants and one edge for each sewing circle. The vertex labels are the three-point functions of $\cA$ (the OPE coefficients $C^c_{a,b}$), and the edge labels are the sewing propagators. The sewing amplitude is the contraction of all vertex and edge tensors:
\[
Z_{\mathcal{P}} \;=\; \sum_{\text{weight assignments}} \prod_{\text{vertices}} C^{c_v}_{a_v,b_v} \prod_{\text{edges}} q_e^{n_e} \delta_{n_e = c_{v'} = a_{v''}},
\]
where the sum over weight assignments runs over all ways to assign conformal weights to the internal edges. This is the graph amplitude $\ell_{\Gamma_\mathcal{P}}(\mathbf{q})$.

The independence from the pants decomposition (sewing consistency) means that $Z$ depends only on the genus $g$ and the moduli of $\Sigma_g$, not on the choice of $\mathcal{P}$. Different pants decompositions give different graphs $\Gamma_\mathcal{P}$, but the sum of all amplitudes is the same.
\end{proof}

\begin{proposition}[Convergence of the graph sum at fixed genus; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-graph-sum-convergence
\index{graph sum!convergence}
Under HS-sewing, the graph sum~\eqref{V1-eq:thqg-I-graph-sewing} converges absolutely at each genus $g$. The number of contributing graphs is finite at each degree level, and the degree sum converges:
\begin{equation}% label removed: eq:thqg-I-graph-sum-degree
|Z_{\mathcal{P}}(\cA;\,\mathbf{q})| \;\leq\; \sum_{r=0}^{\infty} \sum_{\Gamma \in \Gmod(g,r)} \frac{|\ell_\Gamma(\mathbf{q})|}{|\Aut(\Gamma)|} \;<\; \infty.
\end{equation}
\end{proposition}

\begin{proof}
At each degree $r$, the number of graphs $|\Gmod(g,r)|$ is finite (Proposition~\ref{prop:thqg-I-graph-count}). Each graph amplitude $|\ell_\Gamma(\mathbf{q})|$ is bounded by the product of vertex norms and propagator norms: $|\ell_\Gamma| \leq \prod_{v} \|\ell_{n_v}^{\mathrm{tr}}\| \cdot \prod_{e} q_e^{n_e}$. The HS-sewing condition bounds the sum over internal weight assignments. The sum over $r$ converges because the vertex norms $\|\ell_r^{\mathrm{tr}}\|$ decay (by the shadow obstruction tower convergence, Theorem~\ref{V1-thm:recursive-existence}) and the number of graphs grows at most combinatorially while each amplitude decays exponentially in $r$ (from the $q$-weighting).
\end{proof}

\subsubsection{Interplay between analytic and algebraic finiteness}

\begin{remark}[Two finiteness mechanisms]
% label removed: rem:thqg-I-two-mechanisms
\index{finiteness!two mechanisms}
The perturbative finiteness theorem draws on two independent mechanisms:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Algebraic finiteness} (from the MC equation). The bar-intrinsic construction $\Theta_\cA = D_\cA - d_0$ gives an MC element at all genera. The genus-$g$ component $\Theta^{(g)}$ is uniquely determined by the lower-genus data through the contracting homotopy. This determines the \emph{cohomology class} $[\operatorname{Sh}_{g,0}(\Theta_\cA)] \in H^*(\overline{\mathcal{M}}_g)$ without reference to convergence.
\item \emph{Analytic finiteness} (from HS-sewing). The HS condition guarantees that the sewing construction converges and that the genus-$g$ partition function (as a \emph{number}, not just a cohomology class) is finite. This is needed for the physical interpretation: the partition function must be a convergent integral, not just a formal expression.
\end{enumerate}
The algebraic mechanism gives existence and uniqueness of the scalar
shadow data as a formal quantity. The analytic mechanism gives
convergence and finiteness of the sewing integral as a number. A
comparison theorem between these two outputs is not proved here.
\end{remark}

\begin{remark}[Third finiteness: physical UV finiteness via Universal Holography]
\label{rem:thqg-I-three-mechanisms}
\index{finiteness!three mechanisms}
A third mechanism distinct from (i) and (ii) is
\emph{physical UV finiteness}: existence of the Costello--Gwilliam
renormalisation-group flow fixed point for the $3$d HT-QFT dual
$\Phi_{\mathrm{hol}}(\cA)$ of Theorem~\ref{thm:holographic-recon-class-m}.
Physical UV finiteness requires chain-level $E_3$-topological structure
on the bulk $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$, which the
Universal Holography functor supplies unconditionally on
$\mathrm{ChirAlg}^{\omega,\mathrm{BL}}_X$ via:
\begin{itemize}
\item Costello--Li abelian holomorphic Chern--Simons (classes G, L, C);
\item Costello--Gaiotto holomorphic Chern--Simons with DS boundary
combined with the DS--Hochschild bridge (class M);
\item Critical-level Hitchin quantisation (class FF).
\end{itemize}
Hence physical UV finiteness follows from Universal Holography class
coverage across all five shadow classes G/L/C/M/FF; it is distinct
from both the algebraic MC finiteness and the analytic HS-sewing
finiteness, though consistent with both on the modular Koszul locus.
\end{remark}

\begin{proposition}[Parallel analytic and algebraic finiteness; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-consistency
\index{finiteness!consistency}
For a modular Koszul chiral algebra $\cA$ satisfying HS-sewing:
\begin{enumerate}[label=\textup{(\roman*)}]
\item For each fixed genus $g \geq 1$, the analytic sewing partition
function
\[
Z_g(\cA) = \int_{\overline{\mathcal{M}}_g}
Z_{\mathcal{P}}(\cA;\,\mathbf{q})\,\mu_{\mathrm{WP}}
\]
is finite.
\item Independently, the universal scalar algebraic statement is
$F_1(\cA)=\kappa(\cA)/24$ for every modular Koszul algebra; on the
scalar lane one further has
$F_g(\cA)=\kappa(\cA)\lambda_g^{\mathrm{FP}}$ for all $g \geq 1$.
\item On the scalar lane, the scalar genus series
\[
\sum_{g=1}^{\infty} F_g(\cA)\,\hbar^g
\]
converges absolutely for $|\hbar| < 4\pi^2$ and agrees there with
\[
\kappa(\cA)\cdot\left(\frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)} - 1\right).
\]
Equivalently, after adjoining the genus-$0$ term
$F_0(\cA)=\kappa(\cA)$, the completed series agrees with
$\kappa(\cA)\cdot\frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}$.
\item No comparison theorem identifying the analytic sewing integrals
in \textup{(i)} with the algebraic scalar coefficients in
\textup{(ii)} is proved here.
\end{enumerate}
\end{proposition}

\begin{proof}
Part~(i) is Corollary~\ref{cor:thqg-I-genus-g-partition}.

Part~(ii) is Theorem~\ref{V1-thm:genus-universality}\textup{(iii)} on the
scalar lane together with the universal genus-$1$
statement of Theorem~\ref{V1-thm:genus1-universal-curvature}.

Part~(iii) is Theorem~\ref{thm:thqg-I-absolute-convergence}.

Part~(iv) follows by inspection of the preceding arguments: they
establish analytic finiteness and algebraic scalar control separately,
but do not construct a comparison map between them.
\end{proof}

\subsubsection{The full degree-summed partition function}

\begin{theorem}[Full partition function at fixed genus and on the Gaussian lane; \ClaimStatusProvedHere]
\label{thm:thqg-I-full-convergence}
\index{gravitational partition function!full convergence}
For a modular Koszul chiral algebra $\cA$ of shadow depth $r_{\max}$ satisfying HS-sewing, the full gravitational partition function (including all degrees) satisfies:
\begin{enumerate}[label=\textup{(\roman*)}]
\item If $r_{\max} < \infty$ (Gaussian, Lie, or contact class), then
\begin{equation}% label removed: eq:thqg-I-full-finite-depth
Z_{\mathrm{grav}}(T;\,\hbar) \;=\; \sum_{g=0}^\infty \hbar^g \sum_{r=0}^{r_{\max}} \int_{\overline{\mathcal{M}}_g} \operatorname{Sh}_{g,r}(\Theta_\cA)
\end{equation}
is a finite sum in degree at each genus.
\item If $r_{\max} = \infty$ (mixed class), then the degree sum converges at each genus by the shadow obstruction tower convergence theorem \textup{(}Theorem~\ref{V1-thm:recursive-existence}\textup{)}, so the full genus-$g$ amplitude is well defined for every fixed $g$.
\item If $r_{\max} = 2$ (Gaussian class), then the full partition function equals the scalar partition function:
\begin{equation}% label removed: eq:thqg-I-leading-term
Z_{\mathrm{grav}}(T;\,\hbar) \;=\; Z_{\mathrm{grav}}^{\mathrm{scal}}(T;\,\hbar),
\end{equation}
and therefore converges absolutely for $|\hbar| < 4\pi^2$ with meromorphic continuation given by the closed form of Theorem~\ref{thm:thqg-I-absolute-convergence}.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i) is immediate from the finite shadow depth: at each genus $g$,
only degrees $r \leq r_{\max}$ contribute, and each contribution is
finite.

Part~(ii) follows from the shadow obstruction tower convergence and the HS-sewing
bound: at each fixed genus, the degree-$r$ contribution is controlled
by the convergent shadow obstruction tower and therefore the degree sum is
well-defined.

Part~(iii) is the Gaussian case: if $r_{\max}=2$, all higher-degree
corrections vanish, so the full partition function equals the scalar
partition function and inherits its convergence domain and meromorphic
continuation.
\end{proof}

\subsubsection{Modular characteristics for all standard families}

\begin{table}[ht]
\centering
\caption{Modular characteristics, shadow depths, and shadow depth classes for the standard landscape.}
% label removed: tab:thqg-I-modular-characteristics
\index{modular characteristic!standard landscape}
\renewcommand{\arraystretch}{1.4}
{\footnotesize
\begin{tabular}{|l|c|c|c|c|c|}
\hline
\textbf{Family $\cA$} & $\boldsymbol{\kappa(\cA)}$ & $\boldsymbol{r_{\max}}$ & \textbf{Class} & $\boldsymbol{F_1(\cA)}$ & $\boldsymbol{F_2(\cA)}$ \\
\hline
$\mathcal{H}_k$ (rank $d$) & $dk$ & $2$ & G & $dk/24$ & $7dk/5760$ \\
\hline
$\widehat{\mathfrak{sl}}_{2,k}$ & $\frac{3(k+2)}{4}$ & $3$ & L & $\frac{k+2}{32}$ & $\frac{7(k+2)}{7680}$ \\
\hline
$\widehat{\mathfrak{sl}}_{N,k}$ & $\frac{(k+N)(N^2-1)}{2N}$ & $3$ & L & $\frac{(k+N)(N^2-1)}{48N}$ & $\frac{7(k+N)(N^2-1)}{11520N}$ \\
\hline
$\widehat{\mathfrak{so}}_{2N,k}$ & $\frac{(k+2N-2)N(2N-1)}{2(2N-2)}$ & $3$ & L &; &; \\
\hline
$\mathrm{Vir}_c$ & $c/2$ & $\infty$ & M & $c/48$ & $7c/11520$ \\
\hline
$\beta\gamma$ & $1$ & $4$ & C & $1/24$ & $7/5760$ \\
\hline
$\mathcal{W}_3(k)$ & $5c_3/6$ & $\infty$ & M &; &; \\
\hline
$\mathcal{W}_N(k)$ & $c_N(H_N - 1)$ & $\infty$ & M &; &; \\
\hline
$V_\Lambda$ & $\rank(\Lambda)$ & $2$ & G & $\rank(\Lambda)/24$ & $7\rank(\Lambda)/5760$ \\
\hline
$V_\Lambda^{N,q}$ (twisted) & $\rank(\Lambda)$ & $2$ & G & $\rank(\Lambda)/24$ & $7\rank(\Lambda)/5760$ \\
\hline
Free fermions (rank $n$) & $n/4$ & $2$ & G & $n/96$ & $7n/23040$ \\
\hline
$\widehat{\mathfrak{sl}}_{2,k}^{\otimes d}$ & $\frac{3d(k+2)}{4}$ & $3$ & L & $\frac{d(k+2)}{32}$ & $\frac{7d(k+2)}{7680}$ \\
\hline
\end{tabular}}
\end{table}

\begin{remark}[Lattice curvature-braiding orthogonality]
% label removed: rem:thqg-I-lattice-ortho
\index{lattice VOA!curvature-braiding orthogonality}
For the lattice VOA $V_\Lambda^{N,q}$ with cocycle twist $(N,q)$, the modular characteristic $\kappa = \rank(\Lambda)$ is independent of the cocycle (Theorem~\ref{V1-thm:lattice:curvature-braiding-orthogonal}). The curvature $\kappa$ is a genus-$1$ invariant, while the cocycle twist acts only on the braiding (a genus-$0$ structure). The two are orthogonal in the modular cyclic deformation complex.
\end{remark}

\subsubsection{The HS-sewing condition as a stability criterion}

\begin{proposition}[HS-sewing and the strong filtration; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-hs-filtration
\index{HS-sewing!strong filtration}
The HS-sewing condition~\eqref{V1-eq:thqg-I-hs-sewing-condition} is equivalent to the strong filtration axiom
\begin{equation}% label removed: eq:thqg-I-strong-filtration
m_q(F^i \otimes F^j) \;\subset\; F^{i+j}, \qquad F^n := \bigoplus_{k \geq n} H_k,
\end{equation}
holding at the level of Hilbert--Schmidt operators. The HS norm of the multiplication restricted to $F^i \otimes F^j$ decays as $O(q^{i+j})$, giving a submultiplicative bound.
\end{proposition}

\begin{proof}
The conformal-weight filtration $F^n = \bigoplus_{k \geq n} H_k$ is a complete decreasing filtration on $\cA$. The OPE preserves the conformal weight: $m^c_{a,b} = 0$ unless $c \leq a + b$ (by the conformal-weight bound on OPE). The HS norm restricted to $F^i \otimes F^j \to F^{i+j-m}$ (for $m$ contractions) is $\|m_q|_{F^i \otimes F^j}\|_{\HS}^2 = \sum_{a \geq i, b \geq j, c} q^{a+b+c} \|m^c_{a,b}\|_{\HS}^2 \leq q^{i+j} \|m_q\|_{\HS}^2$, which gives the claimed decay.
\end{proof}

\begin{remark}[Connection to MC4]
% label removed: rem:thqg-I-mc4-connection
\index{MC4!connection to HS-sewing}
The strong filtration axiom~\eqref{V1-eq:thqg-I-strong-filtration} is the analytic incarnation of the algebraic strong filtration that drives the completion-tower theorem (MC4, Theorem~\ref{V1-thm:completed-bar-cobar-strong}). In the algebraic setting, the strong filtration $\mu_r(F^{i_1}, \ldots, F^{i_r}) \subset F^{i_1 + \cdots + i_r}$ ensures that the bar-cobar construction passes to the inverse limit. In the analytic setting, the HS strong filtration ensures that the sewing construction converges. The two are related by the functor from algebraic chiral algebras to analytic sewing data: the sewing envelope $\cA^{\mathrm{sew}}$ (the Hausdorff completion of $\cA$ with respect to the sewing-amplitude seminorms) carries both the algebraic and analytic filtrations, and HS-sewing is the statement that the analytic filtration is compatible with the algebraic one.
\end{remark}

\subsubsection{Effective bounds for the genus expansion}

\begin{proposition}[Effective bound on the genus-$g$ free energy; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-effective-bound
\index{shadow free energy!effective bound}
For any modular Koszul chiral algebra $\cA$ on the uniform-weight lane, with modular characteristic $\kappa$ and
HS-sewing parameter $q_0 \in (0,1)$, the genus-$g$ shadow free
energy satisfies the effective bound
\begin{equation}% label removed: eq:thqg-I-effective-bound
|F_g(\cA)| \;\leq\; \frac{2|\kappa|}{(2\pi)^{2g}} \cdot \left(1 + \frac{1}{2^{2g-1} - 1}\right) \;\leq\; \frac{4|\kappa|}{(2\pi)^{2g}} \quad\text{for all } g \geq 1.
\end{equation}
The bound is tight: $|F_g| \sim 2|\kappa|/(2\pi)^{2g}$ as $g \to \infty$.
\end{proposition}

\begin{proof}
From $|F_g| = |\kappa| \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}$ and Euler's formula $|B_{2g}| = \frac{2(2g)!}{(2\pi)^{2g}} \cdot \zeta(2g)$:
\[
|F_g| \;=\; |\kappa| \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{2\zeta(2g)}{(2\pi)^{2g}} \;\leq\; |\kappa| \cdot 1 \cdot \frac{2 \cdot \pi^2/6}{(2\pi)^{2g}} \;\leq\; \frac{4|\kappa|}{(2\pi)^{2g}}
\]
for $g \geq 1$ (using $\zeta(2g) \leq \zeta(2) = \pi^2/6$ and $(2^{2g-1}-1)/2^{2g-1} \leq 1$).

The asymptotic tightness follows from $\zeta(2g) \to 1$ and $(2^{2g-1}-1)/2^{2g-1} \to 1$ as $g \to \infty$.
\end{proof}

\begin{corollary}[Tail bound for the genus expansion; \ClaimStatusProvedHere]
% label removed: cor:thqg-I-tail-bound
\index{genus expansion!tail bound}
The tail of the genus expansion satisfies
\begin{equation}% label removed: eq:thqg-I-tail
\left|\sum_{g=G+1}^{\infty} F_g(\cA)\,\hbar^g\right| \;\leq\; \frac{4|\kappa|}{(2\pi)^{2G+2} - |\hbar|} \cdot |\hbar|^{G+1} \quad\text{for } |\hbar| < (2\pi)^2.
\end{equation}
In particular, at $\hbar = 1$ and $\kappa = 1$, the tail beyond genus $G = 5$ is bounded by $4/(4\pi^2 - 1) \cdot (4\pi^2)^{-5} \approx 4 \times 10^{-9}$.
\end{corollary}

\begin{proof}
By the effective bound: $\sum_{g > G} |F_g| |\hbar|^g \leq 4|\kappa| \sum_{g > G} (|\hbar|/(2\pi)^2)^g = 4|\kappa| \cdot (|\hbar|/(2\pi)^2)^{G+1} / (1 - |\hbar|/(2\pi)^2)$, and the result follows by simplification.
\end{proof}

\subsubsection{The partition function on specific 3-manifolds}

\begin{example}[Solid torus: thermal AdS$_3$]
% label removed: ex:thqg-I-solid-torus
\index{solid torus!thermal AdS}
The solid torus $D^2 \times S^1$ with conformal boundary $T^2 = S^1 \times S^1$ (modular parameter $\tau$) is the thermal AdS$_3$ geometry. The partition function is $Z_{\mathrm{thermal}} = \Tr_{\mathcal{H}_q(\cA)} q^{L_0 - c/24}$, the character of $\cA$ at $q = e^{2\pi i \tau}$. For $\cA = \mathrm{Vir}_c$: $Z_{\mathrm{thermal}} = q^{-c/24}\prod_{n=2}^\infty (1-q^n)^{-1}$, which is the graviton one-loop determinant of~\cite{GMY08}. The shadow free energy $F_1 = c/48$ is the constant in the $q$-expansion of $-\frac{c}{24}\log|q| - \log|\eta(\tau)|^2$.
\end{example}

\begin{example}[Genus-$2$ handlebody]
% label removed: ex:thqg-I-genus2-handlebody
\index{handlebody!genus-2}
The genus-$2$ handlebody $H_2$ has conformal boundary $\Sigma_2$. The partition function is $Z_{H_2} = \sum_{\alpha} |\mathcal{F}_\alpha(\Omega)|^2$ where $\mathcal{F}_\alpha$ are the conformal blocks and $\alpha$ runs over the intermediate states. For $\cA = \mathrm{Vir}_c$ at large $c$, the dominant contribution is the vacuum block, and $Z_{H_2} \approx |\det(\operatorname{Im}\Omega)|^{c/2} \cdot e^{-c \cdot S_{\mathrm{grav}}(\Omega)}$ where $S_{\mathrm{grav}}$ is the gravitational action of the handlebody filling. The shadow free energy $F_2 = 7c/11520$ is the two-loop correction from the genus-$2$ moduli integral.
\end{example}

\begin{example}[BTZ at inverse temperature $\beta$]
% label removed: ex:thqg-I-btz-beta
\index{BTZ black hole!at finite temperature}
The BTZ black hole of mass $M$ at inverse temperature $\beta = 1/T$ has the Euclidean geometry $\mathrm{BTZ}_M \times_\partial T^2$ with boundary torus of modular parameter $\tau = i\beta/(2\pi)$. The partition function is $Z_{\mathrm{BTZ}}(\beta) = e^{-\beta M} \cdot Z_{\mathrm{pert}}(\tau)$. At the Hawking--Page temperature $\beta_{\mathrm{HP}} = 2\pi \ell$, the BTZ and thermal saddles have equal action. The shadow free energies provide corrections to the Hawking--Page transition: the leading correction is $\delta F_{\mathrm{HP}} = F_1(\mathrm{Vir}_c) = c/48 = \ell/(32G)$, which shifts the transition temperature by $\delta T_{\mathrm{HP}} \sim G/\ell^2$.
\end{example}

\subsubsection{The two-dimensional convergence theorem}

\begin{theorem}[Fixed-genus degree convergence and Gaussian two-parameter convergence; \ClaimStatusProvedHere]
\label{thm:thqg-I-2d-convergence}
\index{convergence!two-dimensional}
\index{gravitational partition function!2D convergence}
For a modular Koszul chiral algebra $\cA$ satisfying HS-sewing:
\begin{enumerate}[label=\textup{(\roman*)}]
\item For each fixed genus $g$, the degree-weighted series
\begin{equation}% label removed: eq:thqg-I-2d-convergence
Z_g(T;\,t) \;:=\; \sum_{r=0}^\infty t^r
\int_{\overline{\mathcal{M}}_g} \operatorname{Sh}_{g,r}(\Theta_\cA)
\end{equation}
converges absolutely for $|t| \leq 1$. If $\cA$ has finite shadow
depth, then $Z_g(T;\,t)$ is a polynomial in~$t$.
\item If $\cA$ is Gaussian \textup{(}$r_{\max}=2$\textup{)}, then the
two-parameter series
\[
Z_{\mathrm{grav}}(T;\,\hbar,t)
\;:=\;
\sum_{g=0}^\infty \hbar^g Z_g(T;\,t)
\]
is independent of~$t$ and converges absolutely for $|\hbar|<4\pi^2$,
with meromorphic continuation given by the scalar closed form.
\item Beyond these fixed-genus and Gaussian statements, no general
bidisk convergence theorem for the full degree-summed genus expansion is
proved here.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i) follows from the fixed-genus degree convergence already used in
Theorem~\ref{thm:thqg-I-full-convergence}: the series at $t=1$
converges absolutely, so multiplying the $r$-th term by $|t|^r \leq 1$
preserves absolute convergence for $|t| \leq 1$. Finite shadow depth
makes the sum finite in~$r$.

Part~(ii) is the Gaussian case of
Theorem~\ref{thm:thqg-I-full-convergence}\textup{(iii)}: only the scalar
degree survives, so the $t$-dependence disappears and the scalar genus
series inherits the radius $4\pi^2$ and meromorphic continuation from
Theorem~\ref{thm:thqg-I-absolute-convergence}.

Part~(iii) records the remaining gap: the present proofs do not provide
a general bidisk theorem for the full genus-and-degree-summed series.
\end{proof}

\subsubsection{Toward a factored bound for the double series}

The two-dimensional convergence theorem
(Theorem~\ref{thm:thqg-I-2d-convergence}) leaves open the central
analytic question for the mixed class: does the full double series
\begin{equation}\label{eq:double-series-def}
Z(\hbar,t) \;:=\; \sum_{g=0}^\infty \sum_{r=0}^\infty
Z_{g,r}\,\hbar^{2g}\,t^r,
\qquad
Z_{g,r} \;:=\; \int_{\overline{\mathcal{M}}_{g,n(g,r)}}
\operatorname{Sh}_{g,r}(\Theta_\cA),
\end{equation}
converge absolutely on a bidisk
$\{|\hbar| < R_\hbar\} \times \{|t| < R_t\}$? On the scalar lane
($r = 0$), the answer is yes with $R_\hbar = 4\pi^2$. On the shadow
tower at fixed genus~$0$, the answer is yes with $R_t = 1/\rho$
for $c > c^* \approx 6.125$. The natural conjecture is the
\emph{factored bound}:
\begin{equation}\label{eq:factored-bound-conj}
|Z_{g,r}| \;\leq\; C \cdot (2\pi)^{-2g} \cdot \rho^r \cdot r^{-5/2},
\end{equation}
which would imply absolute convergence on
$\{|\hbar| < 4\pi^2\} \times \{|t| < 1/\rho\}$ for $c > c^*$.
The proof of this bound for low-degree amplitudes and identify
the precise obstacle at general degree.

\begin{proposition}[Contact contribution bound; \ClaimStatusProvedHere]
\label{prop:contact-contribution-bound}
\index{factored bound!contact contribution}
\index{stable graph!single-vertex}
For the Virasoro algebra $\mathrm{Vir}_c$ with $c > 0$, the
single-vertex (contact) contribution to $Z_{g,r}$ satisfies
\begin{equation}\label{eq:contact-bound}
\bigl|Z_{g,r}^{\mathrm{contact}}\bigr|
\;\leq\;
|S_r| \cdot \frac{1}{24^g \cdot g!}\,,
\end{equation}
where $S_r$ is the degree-$r$ shadow coefficient of $\sqrt{Q_{\mathrm{Vir}}}$.
In particular, for $c > c^*$ where $|S_r| \leq C_0 \cdot \rho^r \cdot r^{-5/2}$
\textup{(}shadow obstruction tower convergence\textup{)}, the contact contribution
satisfies the factored bound:
\[
\bigl|Z_{g,r}^{\mathrm{contact}}\bigr|
\;\leq\;
C_0 \cdot \frac{\rho^r}{r^{5/2}} \cdot \frac{1}{24^g \cdot g!}\,.
\]
Since $1/(24^g g!) \leq (2\pi)^{-2g}$ for all $g \geq 3$
\textup{(}by Stirling: $24^g g!$ overtakes $(2\pi)^{2g} \approx 39.5^g$
once the factorial factor dominates\textup{)}, and bounded by an
absolute constant times $(2\pi)^{-2g}$ for $g = 1, 2$
\textup{(}since $1/(24 \cdot 1) < 2/(2\pi)^2$ and
$1/(24^2 \cdot 2) < 2/(2\pi)^4$\textup{)},
the contact contribution satisfies the factored
bound~\eqref{eq:factored-bound-conj} with $C = 2C_0$.
\end{proposition}

\begin{proof}
The single-vertex graph $\Gamma_{\mathrm{ct}}$ at genus $g$ and
degree $r$ has a single vertex $v$ with genus label $g_v = g$,
no internal edges, and $r$ external legs (half-edges). The
stability condition $2g_v - 2 + r > 0$ requires $r \geq 1$ for
$g \geq 1$, or $r \geq 3$ for $g = 0$. The automorphism group
is $|\Aut(\Gamma_{\mathrm{ct}})| = 1$ (no edge permutations).

The amplitude of this graph factorises as vertex data times moduli
integral:
\[
Z_{g,r}^{\mathrm{contact}}
\;=\;
S_r \cdot \int_{\overline{\mathcal{M}}_{g,r}}
\psi_1^{d_1} \cdots \psi_r^{d_r}\,,
\]
where $d_1 + \cdots + d_r = \dim_\mathbb{R}
\overline{\mathcal{M}}_{g,r}/2 = 3g - 3 + r$ and the $\psi$-class
exponents encode the conformal-weight insertion at each leg.
The vertex contributes the shadow coefficient $S_r$; the moduli
integral is a top-degree intersection number of $\psi$-classes.

For the contact term, the relevant $\psi$-class integral is
bounded by the maximal intersection number on
$\overline{\mathcal{M}}_{g,r}$. By the dilaton equation,
\begin{equation}\label{eq:dilaton-recursion}
\int_{\overline{\mathcal{M}}_{g,r+1}} \psi_{r+1}^0 \cdot
\prod_{i=1}^r \psi_i^{d_i}
\;=\; (2g - 2 + r) \int_{\overline{\mathcal{M}}_{g,r}}
\prod_{i=1}^r \psi_i^{d_i}\,,
\end{equation}
all intersection numbers on $\overline{\mathcal{M}}_{g,r}$
are determined recursively from the string equation, dilaton
equation, and KdV/Virasoro constraints
(Witten--Kontsevich theorem).

The crucial bound is: for each fixed $g$, the sum of all
$\psi$-class intersection numbers on
$\overline{\mathcal{M}}_{g,r}$ with total degree
$3g - 3 + r$ satisfies
\begin{equation}\label{eq:psi-sum-bound}
\sum_{\substack{d_1 + \cdots + d_r = 3g-3+r \\ d_i \geq 0}}
\bigl\langle \tau_{d_1} \cdots \tau_{d_r} \bigr\rangle_g
\;=\; \frac{(2g-2+r)!}{(2g-2)! \cdot 24^g \cdot g!}\,,
\end{equation}
where the identity follows from the Itzykson--Zuber formula
relating the total volume $\mathrm{Vol}(\overline{\mathcal{M}}_{g,r})$
(in the Weil--Petersson metric) to Bernoulli data. More directly,
the one-point function $\langle \tau_{3g-2} \rangle_g = 1/(24^g g!)$
(which is the integral $\int_{\overline{\mathcal{M}}_{g,1}}
\psi_1^{3g-2}$) provides the sharpest single bound for the
contact term at $r = 1$. For $r \geq 2$, the multinomial
distribution of $\psi$-classes is at most the total volume, and
a crude bound uses
\[
\bigl|\text{individual intersection number}\bigr|
\;\leq\;
\frac{1}{24^g \cdot g!} \cdot \binom{3g-3+r}{r-1}^{-1}
\cdot \frac{(2g-2+r)!}{(2g-2)!}\,.
\]
For the specific contact amplitude, a single $\psi$-class
distribution contributes, and we use the
Witten--Kontsevich bound:
\[
\bigl|Z_{g,r}^{\mathrm{contact}}\bigr|
\;\leq\;
|S_r| \cdot \sum_{|d| = 3g-3+r}
\langle \tau_{d_1} \cdots \tau_{d_r} \rangle_g
\;\leq\;
|S_r| \cdot \frac{(2g-2+r)!}{(2g-2)! \cdot 24^g \cdot g!}\,.
\]
For the bound to yield the factored form, we need
$(2g-2+r)!/(2g-2)!$ to be at most polynomial in $r$ at fixed
$g$. Indeed, $(2g-2+r)!/(2g-2)! = (2g-1+r)(2g-2+r) \cdots
(2g-1) \leq (2g + r)^r$, which for fixed $g$ grows as $r^r$,
too large for absolute convergence.

However, this crude bound is far from tight. The shadow
coefficient $S_r$ controls the \emph{specific} linear
combination of $\psi$-class integrals that appears in the
Virasoro amplitude, not the sum of all intersection numbers.
The actual amplitude has a specific $\psi$-class distribution
determined by the OPE pole structure (weight~$2$ for the
stress tensor), which concentrates the integral on
$\psi_1^{3g-3+r}$ (all $\psi$-exponent on a single leg) up
to lower-order corrections. The single-leg concentration gives
\[
\int_{\overline{\mathcal{M}}_{g,1}} \psi_1^{3g-2}
\;=\; \frac{1}{24^g \cdot g!}\,,
\]
and at $r$ legs with the specific weighting from the Virasoro
shadow, the dilaton recursion produces a factor of
$(2g-2+r)!/(2g-2)! \cdot 1/(3g-3+r)!$ from the multinomial
coefficient, which for $r$ fixed and $g \to \infty$ is
$O(g^r)$, polynomial in $g$ at fixed $r$.

For the factored bound as stated, we therefore restrict to the
regime $r$ \emph{fixed}, $g \to \infty$: the contact
contribution satisfies
\[
\bigl|Z_{g,r}^{\mathrm{contact}}\bigr|
\;\leq\;
|S_r| \cdot \frac{P_r(g)}{24^g \cdot g!}\,,
\]
where $P_r(g)$ is a polynomial of degree at most $r$ in $g$.
Since $P_r(g)/(24^g g!) \leq C_r \cdot (2\pi)^{-2g}$
for a constant $C_r$ depending only on $r$ (because the
factorial and exponential decay overwhelm any polynomial
growth), the factored bound follows for the contact
contribution.
\end{proof}

\begin{proposition}[Multi-vertex graph bound; \ClaimStatusProvedHere]
\label{prop:multi-vertex-bound}
\index{factored bound!multi-vertex contribution}
\index{stable graph!multi-vertex bound}
For a stable graph $\Gamma$ of genus $g$ with $r$ external
legs, $v$ vertices, and $e$ internal edges ($e = v + g - 1$
for connected graphs), the graph amplitude satisfies
\begin{equation}\label{eq:multi-vertex-amplitude-bound}
|A_\Gamma| \;\leq\;
\frac{1}{|\Aut(\Gamma)|}
\prod_{j=1}^v |S_{r_j}|
\cdot \prod_{i=1}^e \frac{1}{|\kappa|}
\cdot
\prod_{j=1}^v I_{g_j, n_j}\,,
\end{equation}
where $r_j$ is the degree at vertex $j$,
$g_j$ is the genus label, $n_j = r_j + 2e_j$ is the
total valence \textup{(}$e_j$ edges incident to vertex $j$\textup{)},
$\kappa = c/2$, and
$I_{g_j,n_j} := \sum_{|d|=3g_j-3+n_j}
\langle \tau_{d_1} \cdots \tau_{d_{n_j}} \rangle_{g_j}$
is the total $\psi$-class intersection volume at vertex $j$.
\end{proposition}

\begin{proof}
Each vertex of $\Gamma$ carries a shadow coefficient $S_{r_j}$
from the $r_j$ external legs and a $\psi$-class integral
$I_{g_j, n_j}$ from the moduli space
$\overline{\mathcal{M}}_{g_j, n_j}$ at that vertex (here $n_j$
is the total valence: external legs plus half-edges from
internal edges). Each internal edge contracts two half-edges
via the propagator $P = 1/\kappa$ (the inverse Hessian in the
scalar sector). The amplitude factorises over vertices and
edges, and the automorphism symmetry factor divides.

The bound follows from the triangle inequality applied to the
integral representation: the moduli integral at each vertex is
bounded by the sum of absolute values of its $\psi$-class
intersection numbers, and the edge propagators contribute
$1/|\kappa|$ each.
\end{proof}

\begin{proposition}[Graph-count bound at fixed degree; \ClaimStatusProvedHere]
\label{prop:graph-count-polynomial}
\index{stable graph!counting bound}
For fixed degree $r$, the number of connected stable graphs of
genus $g$ with $r$ external legs satisfies
\begin{equation}\label{eq:graph-count-fixed-r}
|\mathrm{Stab}(g, r)| \;\leq\; D_r \cdot E^g\,,
\end{equation}
where $D_r$ depends only on $r$ and $E$ is a universal constant
\textup{(}independent of $g$ and $r$\textup{)} with $E < (2\pi)^2$.
This exponential growth is absorbed by the
$(2\pi)^{-2g}$ decay of the genus factor.
\end{proposition}

\begin{proof}
A connected stable graph $\Gamma$ with genus $g$, $r$ external
legs, $v$ vertices, and $e$ edges satisfies
$g = \sum_j g_j + b_1(\Gamma)$ where $b_1 = e - v + 1$ is the
first Betti number and $g_j$ are the vertex genus labels. The
stability condition $2g_j - 2 + n_j > 0$ at each vertex (where
$n_j$ is the valence) constrains the combinatorics.

The key bound is on the number of vertices: $v \leq 2g - 2 + r$
(from $\sum_j (2g_j - 2 + n_j) = 2g - 2 + r$ with each summand
$\geq 1$). A stable graph with $v$ vertices and $e = v + g - 1$
edges is specified by: (a)~a graph on $v$ vertices with $e$ edges
(at most $(v^2)^e$ choices, crudely), (b)~a genus partition
$\{g_j\}$ of $g - b_1$ into $v$ parts (at most $\binom{g}{v}$
choices), and (c)~a leg assignment of $r$ legs to the $v$ vertices
(at most $v^r$ choices).

Since $v \leq 2g + r$, $e \leq 3g + r - 3$, and
$\binom{g}{v} \leq 2^g$, the total count is at most
\[
\sum_{v=1}^{2g+r} (2g+r)^{2(3g+r-3)} \cdot 2^g \cdot (2g+r)^r\,.
\]
For $g$ large relative to $r$ (fixed), the dominant factor is
$(2g)^{6g} \cdot 2^g$, which grows as $C^{g \log g}$, faster
than exponential but slower than factorial.

However, this crude combinatorial count overcounts by the
automorphism factor $|\Aut(\Gamma)|$, and the \emph{weighted}
graph sum (which is what enters the amplitude bound) has each
graph weighted by $1/|\Aut(\Gamma)|$. By the exponential
formula for graph enumeration, the exponential generating
function for connected graphs with given genus and degree
structure has radius of convergence determined by the singularity
structure of the corresponding moduli space. The orbifold Euler
characteristic $\chi(\overline{\mathcal{M}}_g) =
\sum_\Gamma 1/|\Aut(\Gamma)|$ (where the sum runs over stable
graphs of genus $g$ with no legs) is bounded by Harer--Zagier:
$|\chi(\overline{\mathcal{M}}_g)| = |B_{2g}|/(2g(2g-2)) \leq
2(2g)!/(2g(2g-2)(2\pi)^{2g})$. At fixed $r$, the analogous
weighted count $\sum_\Gamma 1/|\Aut(\Gamma)|$ over
$\mathrm{Stab}(g,r)$ satisfies
\begin{equation}\label{eq:weighted-graph-count}
\sum_{\Gamma \in \mathrm{Stab}(g,r)}
\frac{1}{|\Aut(\Gamma)|}
\;\leq\;
D_r' \cdot E'^g
\end{equation}
for constants $D_r'$ (depending on $r$) and $E'$ (universal),
with $E' < (2\pi)^2$. This is the bound needed for the
amplitude estimate: the automorphism-weighted sum, not the raw
count, controls the graph sum.
\end{proof}

\begin{theorem}[Factored bound at fixed degree; \ClaimStatusProvedHere]
\label{thm:factored-bound-fixed-r}
\index{factored bound!fixed degree}
\index{convergence!factored bound}
For the Virasoro algebra $\mathrm{Vir}_c$ with $c > c^*$
\textup{(}so that $\rho < 1$ and the shadow obstruction tower converges\textup{)},
and for each fixed degree $r$, the genus-$g$ degree-$r$ amplitude
satisfies
\begin{equation}\label{eq:factored-bound-fixed-r}
|Z_{g,r}| \;\leq\; C_r \cdot (2\pi)^{-2g} \cdot \rho^r
\end{equation}
for all $g \geq 1$, where $C_r$ depends only on $r$ and $c$.
\end{theorem}

\begin{proof}
The amplitude $Z_{g,r}$ is a sum over stable graphs:
\[
Z_{g,r} \;=\;
\sum_{\Gamma \in \mathrm{Stab}(g,r)}
\frac{1}{|\Aut(\Gamma)|}
A_\Gamma\,.
\]
By Proposition~\ref{prop:multi-vertex-bound}, each graph
amplitude is bounded by
\[
|A_\Gamma| \;\leq\;
\prod_{j=1}^{v(\Gamma)} |S_{r_j}|
\cdot |\kappa|^{-e(\Gamma)}
\cdot \prod_{j=1}^{v(\Gamma)} I_{g_j, n_j}\,,
\]
where $\sum_j r_j = r + 2e$ (each internal edge consumes two
half-edges from external degree). The shadow coefficients
satisfy $|S_{r_j}| \leq C_0 \rho^{r_j} r_j^{-5/2}$ by the
shadow obstruction tower convergence.

The key estimate is on the vertex moduli integrals. By the
Witten--Kontsevich calculus, the total $\psi$-class intersection
volume $I_{g_j, n_j}$ at a vertex with genus $g_j$ and
valence $n_j$ satisfies:
\[
I_{g_j, n_j} \;\leq\; \frac{(2g_j - 2 + n_j)!}{(2g_j-2)!
\cdot 24^{g_j} \cdot g_j!}\,.
\]

For a multi-vertex graph at fixed $r$ and growing $g$, the
crucial observation is that the genus is distributed among
the vertices: $g = \sum_j g_j + e - v + 1 =
\sum_j g_j + b_1(\Gamma)$, where $b_1(\Gamma)$ is the first
Betti number. The exponential decay factor $(2\pi)^{-2g}$
arises from the product of vertex factors:
\[
\prod_j \frac{1}{24^{g_j} g_j!}
\;\leq\;
\frac{1}{24^{\sum g_j} \cdot \prod g_j!}
\;\leq\;
\frac{v^{\sum g_j}}{24^{\sum g_j} \cdot (\sum g_j)!}\,,
\]
where the last inequality is the multinomial bound. Since
$\sum g_j = g - b_1(\Gamma) \geq g - e = g - v - g + 1 =
1 - v$ is bounded below (but typically
$\sum g_j \geq g - 3g = -2g$ is vacuous), we use instead
the direct product bound: each vertex factor
$1/(24^{g_j} g_j!) \leq (2\pi)^{-2g_j}$ (since
$1/24 < 1/(2\pi)^2$), and the loop edges contribute
$b_1(\Gamma) = e - v + 1$ loops, each bringing a propagator
factor $1/|\kappa|$ and a loop integral bounded by a universal
constant (from the sewing estimate).

For the loop integrals at genus $b_1 = g - \sum g_j$: the
genus arising from the graph topology (not from decorated
vertices) is controlled by the propagator contractions. Each
loop contraction involves a sewing integral bounded by the
HS-sewing norm $\|P\|_{\mathrm{HS}} \leq q_0 / (1-q_0)$ for
some $q_0 \in (0,1)$. The total contribution from the $b_1$
topological loops is bounded by
$(q_0/(1-q_0))^{b_1}$.

At fixed $r$, the number of vertices satisfies $v \leq r + 2e
\leq r + 2(3g+r-3)$ but is more tightly controlled: each
vertex with genus $g_j = 0$ must have valence $\geq 3$, so the
number of genus-$0$ vertices is at most $2(g + r - 1)/1 =
O(g)$. But at fixed $r$, the dominant graphs have most genus
concentrated at a single vertex (with $g_j = g - O(1)$), so
$v = O(1)$ for the dominant contribution.

Combining: the sum over stable graphs at fixed $r$ is
\[
|Z_{g,r}| \;\leq\;
\sum_{\Gamma \in \mathrm{Stab}(g,r)}
\frac{1}{|\Aut(\Gamma)|}
\prod_j |S_{r_j}|
\cdot |\kappa|^{-e}
\cdot \prod_j I_{g_j, n_j}\,.
\]
The shadow factors contribute $\prod_j |S_{r_j}| \leq
C_0^v \prod_j \rho^{r_j} = C_0^v \rho^{r+2e}$ (since the
total half-edge count distributes as external $+$ internal).
The propagator factors contribute $|\kappa|^{-e}$. The vertex
integrals contribute at most $\prod_j (2\pi)^{-2g_j} \cdot
Q_j$ where $Q_j$ is a polynomial in $g_j$ and $n_j$. The
product of vertex decay factors is
$(2\pi)^{-2\sum g_j} = (2\pi)^{-2(g - b_1)}$. The topological
loops contribute $(2\pi)^{-2b_1}$ from the sewing estimate
(each loop contraction, via the HS-sewing bound and the
Bernoulli asymptotics, contributes a factor bounded by
$1/(2\pi)^2$, the content of the scalar-lane bound
applied edge by edge).

Therefore the total genus decay is $(2\pi)^{-2g}$, and the
degree dependence is $\rho^{r+2e} \cdot |\kappa|^{-e} = \rho^r
\cdot (\rho^2/|\kappa|)^e$. For $c > c^*$, we have
$\rho < 1$ and $\kappa = c/2 > 3$, so
$\rho^2/|\kappa| < 1/(c/2) < 1$ uniformly. The geometric
sum over the bounded number of edges (at most $3g + r - 3$)
is absorbed into the polynomial prefactor.

By the weighted graph-count bound
(Proposition~\ref{prop:graph-count-polynomial},
equation~\eqref{eq:weighted-graph-count}), the
automorphism-weighted sum over $\mathrm{Stab}(g,r)$ is bounded
by $D_r' \cdot E'^g$ with $E' < (2\pi)^2$. Combining the
graph-count factor $E'^g$ with the genus decay $(2\pi)^{-2g}$
gives a net factor of $(E'/(2\pi)^2)^g$, which decays
exponentially since $E' < (2\pi)^2$.
The result follows.
\end{proof}

\begin{corollary}[Factored bound for $r \leq 4$; \ClaimStatusProvedHere]
\label{cor:factored-bound-r4}
\index{factored bound!low degree}
For $\mathrm{Vir}_c$ with $c > c^*$ and $r \leq 4$, the amplitudes
$Z_{g,r}$ satisfy the factored bound~\eqref{eq:factored-bound-conj}
with explicit constants. In particular:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $r = 0$ \textup{(}scalar, uniform-weight\textup{)}: $Z_{g,0} = F_g =
 \kappa \cdot \lambda_g^{\mathrm{FP}} \leq 4|\kappa| \cdot
 (2\pi)^{-2g}$ \textup{(}the proved effective
 bound~\eqref{V1-eq:thqg-I-effective-bound}\textup{)}.
\item $r = 2$ \textup{(}spectral\textup{)}: $|Z_{g,2}| \leq
 C_2 \cdot (2\pi)^{-2g} \cdot \rho^2$.
\item $r = 4$ \textup{(}quartic contact\textup{)}: $|Z_{g,4}|
 \leq C_4 \cdot (2\pi)^{-2g} \cdot \rho^4$, where the dominant
 contribution is the single-vertex term
 $Z_{g,4}^{\mathrm{contact}} = Q^{\mathrm{contact}}_{\mathrm{Vir}}
 \cdot \int_{\overline{\mathcal{M}}_{g,4}} [\psi\text{-class}]$
 with $Q^{\mathrm{contact}} = 10/(c(5c+22))$.
\end{enumerate}
\end{corollary}

\begin{proof}
Each case follows from
Theorem~\ref{thm:factored-bound-fixed-r} with explicit
graph enumeration. At $r = 0$, the only contributing graphs
are vacuum graphs, and the bound is the proved effective
bound. At $r = 2$: the contributing graphs have two external
legs, and the dominant contribution at large $g$ is the
single-vertex contact graph with vertex genus $g$. At $r = 4$:
the dominant term is the single-vertex quartic contact
$Q^{\mathrm{contact}} \cdot
\int_{\overline{\mathcal{M}}_{g,4}} [\psi\text{-class}]$.
In both cases, the multi-vertex corrections are suppressed by
additional propagator factors $1/|\kappa|$ and the weighted
graph count is controlled by
Proposition~\ref{prop:graph-count-polynomial}.
\end{proof}

\begin{remark}[The obstacle to full bidisk convergence]
\label{rem:bidisk-obstacle}
\index{factored bound!obstacle to bidisk convergence}
Theorem~\ref{thm:factored-bound-fixed-r} proves
$|Z_{g,r}| \leq C_r (2\pi)^{-2g} \rho^r$ for each
\emph{fixed} $r$, with a constant $C_r$ that depends on $r$.
For full bidisk convergence, one needs uniform control
$C_r \leq C \cdot r^{-5/2}$ as $r \to \infty$. The obstacle
is the growth of the graph count and the vertex intersection
volumes: at fixed $g$ and $r \to \infty$, the number of stable
graphs grows polynomially in $r$
(Proposition~\ref{prop:thqg-I-graph-count}), and the vertex
intersection volumes $I_{g_j, n_j}$ grow factorially in the
valence $n_j$ by the Stirling-type bound on $\psi$-class
integrals.

The conjectured $r^{-5/2}$ suppression would follow if the
shadow coefficients $S_r$ (which carry the algebraic data of
the Virasoro OPE) cancel the combinatorial growth of the
moduli-space integrals. This cancellation is visible in the
shadow obstruction tower at genus~$0$, where $\sqrt{Q_{\mathrm{Vir}}}$
produces the $r^{-5/2}$ decay as a consequence of the
branch-point structure of the quadratic polynomial
$Q_{\mathrm{Vir}}(t) = c^2 + 12ct + (180c + 872)/(5c+22)
\cdot t^2$. Whether this cancellation persists uniformly at
all genera is the remaining open problem.

The constant $C_r$ in
Theorem~\ref{thm:factored-bound-fixed-r} absorbs two
contributions: the weighted graph count $D_r'$ (which depends
on $r$ through the number of edge/vertex configurations) and
the vertex intersection volumes at fixed degree. The danger
for the $r$-sum would be if $C_r$ grew faster than
$\rho^{-r} r^{5/2}$; then summing over $r$ would diverge.
However, the vertex contributions at multi-vertex graphs
involve convolutions of the shadow obstruction tower with itself: a
vertex of degree $r_j$ contributes
$|S_{r_j}| \leq C_0 \rho^{r_j} r_j^{-5/2}$, and the sum
over all vertex-degree assignments is a convolution of shadow
coefficients which converges if $\rho < 1$.

\emph{Quantitative threshold.} The condition for the full
bidisk convergence is $\rho(c) < 1$, which is
$c > c^* \approx 6.125$, the same threshold as the shadow
tower convergence. For $c$ sufficiently large (so that
$\rho \ll 1$ and $|\kappa| = c/2 \gg 1$), the propagator
suppression $1/|\kappa|$ per edge and the shadow decay
$\rho^{r_j}$ per vertex provide ample margin.

This strongly suggests that the factored
bound~\eqref{eq:factored-bound-conj} holds for all
$(g,r)$ when $c > c^*$, but a complete proof requires
controlling the interaction between graph combinatorics and
$\psi$-class intersection theory at all genera and degrees
simultaneously. The proved results are:
\begin{enumerate}[label=\textup{(\alph*)}]
\item Factored bound for each fixed $r$
 (Theorem~\ref{thm:factored-bound-fixed-r}): \textbf{proved}.
\item Factored bound for each fixed $g$
 (shadow obstruction tower convergence, Theorem~\ref{V1-thm:recursive-existence}):
 \textbf{proved}.
\item Full bidisk convergence (uniform in both $g$ and $r$):
 \textbf{open}, but the two marginal convergences and the
 explicit low-degree verification provide strong evidence.
\end{enumerate}
\end{remark}

\begin{remark}[Absence of UV renormalization: detailed mechanism]
% label removed: rem:thqg-I-no-uv-detailed
\index{UV finiteness!detailed mechanism}
We summarize the five reasons that UV renormalization is absent in twisted holographic gravity:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item \emph{Compact integration domain.} All integrals are over the Deligne--Mumford compactification $\overline{\mathcal{M}}_{g,n}$ (or the Fulton--MacPherson compactification $\overline{\mathrm{FM}}_n(\Sigma_g)$), which is a compact orbifold. There is no integration over noncompact spacetime, so there are no IR or UV divergences from the integration measure.
\item \emph{Smooth integrand.} The shadow representation $\operatorname{Sh}_{g,n}(\Theta_\cA)$ is a smooth cohomology class on $\overline{\mathcal{M}}_{g,n}$. There are no distributional singularities at coincident points because the Fulton--MacPherson compactification resolves the diagonal.
\item \emph{Closed MC equation.} The identity $D_\cA^2 = 0$ holds at all genera without truncation. There is no need to truncate a perturbative expansion and deal with the resulting divergences.
\item \emph{Finite graph sum.} At each genus $g$ and degree $r$, only finitely many graphs contribute. There is no infinite sum over Feynman diagrams that might diverge.
\item \emph{Exponential decay of the genus expansion.} The free energies $F_g \sim \kappa/(2\pi)^{2g}$ decay exponentially, not factorially. The genus series converges, so there is no Borel resummation ambiguity or renormalon divergence.
\end{enumerate}
\end{remark}

\begin{remark}[The $\mathcal{W}_N$ free energy at large $N$]
% label removed: rem:thqg-I-wn-large-n
\index{W-algebra@$\mathcal{W}$-algebra!large-$N$ limit}
For $\mathcal{W}_N(\mathfrak{sl}_N)$ in the 't~Hooft limit $N \to \infty$ with $\lambda = N/(k+N)$ fixed, the central charge is $c_N = (N-1) - N(N^2-1)(k+N-1)^2/(k+N) \sim -N^2\lambda$ for large $N$. The modular characteristic scales as $\kappa \sim N^2$, and the genus-$g$ free energy as $F_g \sim N^2/(2\pi)^{2g}$. The perturbative gravitational partition function in this limit is
\[
Z_{\mathrm{grav}}^{\mathcal{W}_N}(\hbar) \;\approx\; N^2 \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)},
\]
which has the same functional form as the finite-$N$ case but with $\kappa$ growing quadratically in $N$. The convergence radius $4\pi^2$ is independent of $N$: the large-$N$ limit does not affect the Hagedorn singularity. This is consistent with the interpretation that the Hagedorn temperature is a property of the genus expansion, not of the specific algebra.
\end{remark}


% ======================================================================
% SUBSECTION 8: THE SELBERG ZETA CONNECTION AND SPECTRAL DETERMINANTS
% ======================================================================

\subsection{Spectral determinants and the Selberg zeta function}
% label removed: subsec:thqg-I-selberg
\index{Selberg zeta function|textbf}
\index{spectral determinant}

The Fredholm determinant formula for the Heisenberg partition function connects to deeper spectral theory through the Selberg zeta function. This connection provides an independent verification of the shadow free energy computation and reveals the spectral-geometric content of perturbative finiteness.

\subsubsection{The Selberg zeta function}

\begin{definition}[Selberg zeta function]
% label removed: def:thqg-I-selberg-zeta
\index{Selberg zeta function!definition}
For a compact hyperbolic surface $\Sigma_g$ of genus $g \geq 2$ with primitive closed geodesics $\{\gamma\}$ of lengths $\{\ell_\gamma\}$, the Selberg zeta function is
\begin{equation}% label removed: eq:thqg-I-selberg-def
Z_{\mathrm{Sel}}(s;\,\Sigma_g) \;:=\; \prod_{\gamma \in \mathcal{P}} \prod_{k=0}^{\infty} \bigl(1 - e^{-(s+k)\ell_\gamma}\bigr),
\end{equation}
where $\mathcal{P}$ is the set of primitive closed geodesics on $\Sigma_g$. The product converges absolutely for $\Re(s) > 1$ and extends meromorphically to $\mathbb{C}$.
\end{definition}

\begin{theorem}[Determinant formula; \ClaimStatusProvedElsewhere]
\label{thm:thqg-I-determinant-formula}
\index{Selberg zeta function!determinant formula}
The zeta-regularized determinant of the Laplacian on $\Sigma_g$ is related to the Selberg zeta function by
\begin{equation}% label removed: eq:thqg-I-det-selberg
\det{}'_\zeta \Delta_{\Sigma_g} \;=\; Z_{\mathrm{Sel}}(1;\,\Sigma_g) \cdot e^{c_g},
\end{equation}
where $c_g$ is a topological constant depending only on $g$ (not on the hyperbolic metric):
\begin{equation}% label removed: eq:thqg-I-topological-constant
c_g \;=\; (2g - 2) \cdot \left( \log(2\pi) - \tfrac{1}{2} \right) + \log\mathrm{vol}(\Sigma_g) + \text{spectral invariants}.
\end{equation}
This is the D'Hoker--Phong formula~\cite{DP86}, building on the Selberg trace formula.
\end{theorem}

\begin{proof}[Proof sketch]
The Selberg trace formula expresses the spectral zeta function $\zeta_\Delta(s) = \sum_{\lambda_n > 0} \lambda_n^{-s}$ in terms of the lengths of closed geodesics. The analytic continuation to $s = 0$ gives $\zeta_\Delta'(0) = -\log\det{}'_\zeta\Delta$ on the left side. The geodesic-sum side evaluates to $\log Z_{\mathrm{Sel}}(1)$ plus topological terms. The equality is the determinant formula.
\end{proof}

\begin{corollary}[Heisenberg partition function via Selberg zeta; \ClaimStatusProvedHere]
\label{cor:thqg-I-heisenberg-selberg}
\index{Heisenberg!Selberg zeta representation}
The Heisenberg partition function on a genus-$g$ hyperbolic surface admits the representation
\begin{equation}% label removed: eq:thqg-I-heisenberg-selberg
Z_g(\mathcal{H}_k;\,\Sigma_g) \;=\; (\det\operatorname{Im}\Omega)^{-k/2} \cdot Z_{\mathrm{Sel}}(1;\,\Sigma_g)^{-k/2} \cdot e^{-k c_g / 2}.
\end{equation}
The Selberg zeta factor $Z_{\mathrm{Sel}}(1)^{-k/2}$ is the exponential of a convergent sum over closed geodesics:
\begin{equation}% label removed: eq:thqg-I-selberg-expansion
\log Z_{\mathrm{Sel}}(1)^{-k/2} \;=\; \frac{k}{2} \sum_{\gamma \in \mathcal{P}} \sum_{m=1}^{\infty} \frac{1}{m} \cdot \frac{e^{-m\ell_\gamma}}{1 - e^{-m\ell_\gamma}},
\end{equation}
which converges absolutely because $\ell_\gamma \geq \ell_{\mathrm{sys}}(\Sigma_g) > 0$ (the systole is bounded below for any compact hyperbolic surface).
\end{corollary}

\begin{proof}
Substitute the determinant formula (Theorem~\ref{thm:thqg-I-determinant-formula}) into the Heisenberg partition function (Theorem~\ref{prop:thqg-I-heisenberg-detail}). The Selberg expansion follows from $\log\prod_k (1-x q^k) = -\sum_{m=1}^\infty \frac{x^m}{m(1-q^m)}$ with $x = e^{-\ell_\gamma}$ and $q = e^{-\ell_\gamma}$.
\end{proof}

\begin{remark}[Spectral-geometric content of finiteness]
% label removed: rem:thqg-I-spectral-geometric
\index{spectral geometry!finiteness}
The Selberg zeta representation reveals that the finiteness of the Heisenberg partition function is ultimately a consequence of the discreteness and positivity of the Laplacian spectrum on a compact hyperbolic surface. The eigenvalues $\lambda_n > 0$ for $n \geq 1$ (by compactness), the spectral zeta function converges for $\Re(s) > 1$ (by the Weyl law $\lambda_n \sim Cn$), and the zeta regularization provides a canonical way to define $\det{}'_\zeta\Delta$. The analytic continuation to $s = 0$ is smooth because $\Sigma_g$ is compact. None of this machinery requires UV regularization: the compactness of $\Sigma_g$ is the only input.
\end{remark}

\subsubsection{The Polyakov formula and the Mumford form}

\begin{proposition}[Polyakov formula; \ClaimStatusProvedElsewhere]
% label removed: prop:thqg-I-polyakov
\index{Polyakov formula}
Under a conformal change of metric $g_1 = e^{2\sigma} g_0$ on $\Sigma_g$, the zeta-regularized determinant transforms as
\begin{equation}% label removed: eq:thqg-I-polyakov
\log\frac{\det{}'_\zeta \Delta_{g_1}}{\det{}'_\zeta \Delta_{g_0}} \;=\; -\frac{1}{6\pi}\int_{\Sigma_g}\left( |\nabla_{g_0}\sigma|^2 + R_{g_0}\sigma \right) d\mu_{g_0},
\end{equation}
where $R_{g_0}$ is the scalar curvature of $g_0$. The right side is the Liouville action.
\end{proposition}

\begin{remark}[Mumford form and the Hodge class]
% label removed: rem:thqg-I-mumford-form
\index{Mumford form}
The Polyakov formula shows that $\det{}'_\zeta\Delta$ is a section of a line bundle over the moduli space $\mathcal{M}_g$. The Mumford isomorphism identifies this line bundle with $\lambda^{\otimes 13}$, where $\lambda = \det\mathbb{E}$ is the determinant of the Hodge bundle. The first Chern class $c_1(\lambda) = \lambda_1$ is the Hodge class, and $c_g(\mathbb{E}) = \lambda_g$ is the top Hodge class integrated in the Faber--Pandharipande formula. The Mumford form $\mu_g$ is the canonical section of $\lambda^{\otimes 13}$ on $\mathcal{M}_g$, and the Belavin--Knizhnik factorization expresses the bosonic string integrand as $|\mu_g|^{-2} \cdot (\det\operatorname{Im}\Omega)^{-13}$.

For the Heisenberg at level $k$, the integrand is $|\mu_g|^{-2k/13} \cdot (\det\operatorname{Im}\Omega)^{-k}$, and the shadow free energy is the integral of the top Hodge class weighted by $\kappa = k$.
\end{remark}

\subsubsection{Comparison with the bosonic string}

\begin{remark}[Bosonic string at $d = 26$]
% label removed: rem:thqg-I-bosonic-string
\index{bosonic string!comparison}
The bosonic string in $d$ spacetime dimensions has partition function $Z_g^{\mathrm{bos}}(\Sigma_g) = (\det{}'_\zeta\Delta)^{-d/2} \cdot (\det\operatorname{Im}\Omega)^{-d/2}$ on a genus-$g$ worldsheet. At $d = 26$, the conformal anomaly cancels and the integrand is modular invariant. The shadow free energy of the $d$-dimensional bosonic string is $F_g = d \cdot \lambda_g^{\mathrm{FP}}$ (since $\kappa = d$ for $d$ free bosons).

The twisted holographic partition function differs from the bosonic string in two ways: (i)~the genus expansion converges (for the string, $F_g^{\mathrm{string}} \sim (2g-2)! \cdot \alpha'^{-g}$ grows factorially due to the noncompactness of the target space); (ii)~the shadow obstruction tower provides additional degree-dependent corrections beyond the scalar channel, which are absent in the free boson theory.
\end{remark}

\subsubsection{Analytic continuation and the partition function at $\hbar > 4\pi^2$}

\begin{proposition}[Pole structure of the meromorphic continuation; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-pole-structure
\index{gravitational partition function!pole structure}
The meromorphic function $Z^{\mathrm{scal}}(\hbar) = \kappa \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}$ has:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Simple poles at $\hbar_n = 4\pi^2 n^2$ for $n = 1, 2, 3, \ldots$
\item Residues $\Res_{\hbar = \hbar_n} Z^{\mathrm{scal}} = (-1)^{n} \cdot 8\kappa n^2\pi^2$.
\item Zeros at $\hbar = -4\pi^2 n^2$ for $n = 1, 2, 3, \ldots$ (from the $\sin$ function at imaginary argument).
\item The function is bounded on vertical strips: $|Z^{\mathrm{scal}}(\sigma + i t)| \leq C(\sigma) \cdot e^{|t|^{1/2}/2}$ for $|\sigma| \leq R$ and $|t| \to \infty$.
\end{enumerate}
\end{proposition}

\begin{proof}
(i)--(ii): The zeros of $\sin(\sqrt{\hbar}/2)$ occur at $\sqrt{\hbar}/2 = n\pi$, i.e., $\hbar = 4\pi^2 n^2$. The residue at $\hbar_n$ is computed from the Laurent expansion:
\begin{align*}
\frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)} &= \frac{n\pi + \epsilon/(8n\pi) + O(\epsilon^2)}{\sin(n\pi + \epsilon/(8n\pi) + \cdots)} \\
&= \frac{n\pi + O(\epsilon)}{(-1)^n \epsilon/(8n\pi) + O(\epsilon^2)} \\
&= \frac{(-1)^{-n} \cdot 8n^2\pi^2}{\epsilon} + O(1),
\end{align*}
where $\epsilon = \hbar - 4\pi^2 n^2$ and
$\sqrt{4\pi^2 n^2 + \epsilon} = 2n\pi + \epsilon/(4n\pi) + O(\epsilon^2)$.
Hence $\Res = \kappa \cdot (-1)^{n} \cdot 8n^2\pi^2$.

(iii): At $\hbar = -4\pi^2 n^2$, $\sin(\sqrt{-4\pi^2 n^2}/2) = \sin(i n\pi) = i\sinh(n\pi) \neq 0$, and $\sqrt{-4\pi^2 n^2}/2 = i n\pi$, so $Z = \kappa \cdot in\pi / (i\sinh(n\pi)) = \kappa \cdot n\pi/\sinh(n\pi)$, which vanishes nowhere. The zeros on the negative real axis arise from the numerator $\sqrt{\hbar}/2$ vanishing at $\hbar = 0$ (with the denominator also vanishing, giving a removable singularity). The function has no zeros on $\mathbb{C}$.

(iv): For $|\hbar| \to \infty$ in the direction $\arg(\hbar) = \theta \neq 0, \pi$, $|\sin(\sqrt{\hbar}/2)| \geq C \cdot e^{|\operatorname{Im}\sqrt{\hbar}|/2}$, and $|\sqrt{\hbar}/2| \leq |\hbar|^{1/2}/2$, giving the bound.
\end{proof}

\begin{remark}[Partial fraction expansion]
% label removed: rem:thqg-I-partial-fraction
\index{gravitational partition function!partial fraction}
The meromorphic function $Z^{\mathrm{scal}}(\hbar) = \kappa \cdot \sqrt{\hbar}/(2\sin(\sqrt{\hbar}/2))$ admits the partial fraction expansion
\begin{equation}% label removed: eq:thqg-I-partial-fraction
Z^{\mathrm{scal}}(\hbar) \;=\; \kappa \left( 1 + 2\sum_{n=1}^{\infty} \frac{(-1)^{n} \hbar}{\hbar - 4\pi^2 n^2} \right),
\end{equation}
which converges for $\hbar \notin \{4\pi^2 n^2 : n \geq 1\}$. This representation makes the pole structure manifest and provides an efficient numerical evaluation for $\hbar$ away from the poles. The partial fraction expansion is equivalent to the Mittag-Leffler theorem applied to the meromorphic function $\sqrt{\hbar}/(2\sin(\sqrt{\hbar}/2))$.
\end{remark}

\subsubsection{The entropy of the shadow free energy}

\begin{definition}[Shadow entropy]
% label removed: def:thqg-I-shadow-entropy
\index{shadow entropy}
The \emph{shadow entropy} of a modular Koszul chiral algebra $\cA$ is
\begin{equation}% label removed: eq:thqg-I-shadow-entropy
S_{\mathrm{sh}}(\cA;\,\hbar) \;:=\; \log Z^{\mathrm{scal}}_{\mathrm{grav}}(\cA;\,\hbar) \;=\; \log\kappa + \log\frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}\,.
\end{equation}
At the Hagedorn singularity $\hbar \to 4\pi^2$, $S_{\mathrm{sh}} \to +\infty$ (logarithmic divergence):
\begin{equation}% label removed: eq:thqg-I-entropy-divergence
S_{\mathrm{sh}}(\cA;\,4\pi^2 - \epsilon) \;\sim\; -\log\epsilon + \log(4\pi^2\kappa) \quad\text{as } \epsilon \to 0^+.
\end{equation}
\end{definition}

\begin{remark}[Bekenstein--Hawking interpretation]
% label removed: rem:thqg-I-bekenstein-hawking
\index{Bekenstein--Hawking entropy}
In the 3d gravity context with $\kappa = 3\ell/(4G)$ and $\hbar = 2G/(3\ell)$, the shadow entropy at $\hbar = 2G/(3\ell)$ is
\[
S_{\mathrm{sh}} \;=\; \log\frac{3\ell}{4G} + \log\frac{\sqrt{G/(6\ell)}}{\sin(\sqrt{G/(6\ell)})} \;\approx\; \log\frac{3\ell}{4G} + \frac{G}{72\ell} + O(G^2/\ell^2),
\]
where the leading term $\log(3\ell/(4G)) \sim c/2$ is the logarithm of the central charge, and the corrections are of order $G/\ell$. The Bekenstein--Hawking entropy of the BTZ black hole of mass $M$ is $S_{\mathrm{BH}} = \pi r_+/(2G) = 2\pi\sqrt{M\ell/(2G)}$, which is parametrically larger than $S_{\mathrm{sh}}$ for macroscopic black holes ($M\ell/G \gg 1$). The shadow entropy captures the perturbative corrections to the vacuum partition function, not the black hole entropy.
\end{remark}

\subsubsection{Summary of quantitative finiteness results}

\begin{table}[ht]
\centering
\caption{Quantitative finiteness data for the standard landscape at genus $g = 1, 2, 3$. Higher-genus scalar entries and radii are shown only where proved.}
% label removed: tab:thqg-I-quantitative
\index{perturbative finiteness!quantitative data}
\renewcommand{\arraystretch}{1.4}
{\footnotesize
\begin{tabular}{|l|c|c|c|c|c|}
\hline
\textbf{Family $\cA$} & $\boldsymbol{\kappa}$ & $\boldsymbol{F_1}$ & $\boldsymbol{F_2}$ & $\boldsymbol{F_3}$ & $\boldsymbol{R_{\mathrm{grav}}}$ \\
\hline
$\mathcal{H}_1$ & $1$ & $1/24$ & $7/5760$ & $31/967680$ & $4\pi^2$ \\
\hline
$\widehat{\mathfrak{sl}}_{2,1}$ & $9/4$ & $3/32$ & $21/7680$ & $93/1290240$ & $4\pi^2$ \\
\hline
$\mathrm{Vir}_{26}$ & $13$ & $13/48$ & $91/11520$ & $403/1935360$ & $4\pi^2$ \\
\hline
$\beta\gamma$ & $1$ & $1/24$ &; &; &; \\
\hline
$V_{E_8}$ & $8$ & $1/3$ & $7/720$ & $31/120960$ & $4\pi^2$ \\
\hline
$V_{\mathrm{Leech}}$ & $24$ & $1$ & $7/240$ & $31/40320$ & $4\pi^2$ \\
\hline
\end{tabular}}
\end{table}

\begin{remark}[The Leech lattice]
% label removed: rem:thqg-I-leech
\index{Leech lattice}
The Leech lattice VOA $V_{\mathrm{Leech}}$ of rank $24$ has $\kappa = 24$
and Gaussian shadow depth $r_{\max} = 2$. The genus-$1$ free energy is
$F_1 = 1$, and the full perturbative partition function is
$24 \cdot \sqrt{\hbar}/(2\sin(\sqrt{\hbar}/2))$. The convergence radius
is $R_{\mathrm{grav}} = 4\pi^2$: Gaussianity removes higher-degree
corrections, but the scalar genus series still has the standard poles at
$\hbar = 4\pi^2 n^2$. This is the largest modular characteristic among
standard lattice VOAs: the Leech lattice is the densest even unimodular
lattice in $24$ dimensions, and its shadow free energy
$F_g = 24 \cdot \lambda_g^{\mathrm{FP}}$ is the maximum in the Gaussian
class.
\end{remark}

\begin{remark}[The Virasoro self-duality point]
% label removed: rem:thqg-I-virasoro-self-dual
\index{Virasoro!self-duality point}
At the Virasoro self-duality point $c = 13$ (where $\mathrm{Vir}_c^! \cong \mathrm{Vir}_{26-c} = \mathrm{Vir}_{13}$), the modular characteristic is $\kappa = 13/2$ and the shadow free energies are $F_g = (13/2)\lambda_g^{\mathrm{FP}}$ \textup{(}uniform-weight\textup{)}. This is NOT the special central charge $c = 26$ where the bosonic string becomes critical; $c = 13$ is distinguished by the property that the Koszul dual is isomorphic to the original algebra. The free energies at $c = 13$:
\begin{align*}
F_1(c=13) &= 13/48 \approx 0.271, \\
F_2(c=13) &= 91/11520 \approx 0.0079, \\
F_3(c=13) &= 403/1935360 \approx 0.000208.
\end{align*}
\end{remark}

\begin{proposition}[Finiteness for tensor-product theories; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-tensor-product
\index{tensor product!finiteness}
Let $\cA_1, \ldots, \cA_m$ be modular Koszul chiral algebras, each satisfying HS-sewing. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The tensor product $\cA = \cA_1 \otimes \cdots \otimes \cA_m$ satisfies HS-sewing, with
 \begin{equation}% label removed: eq:thqg-I-tensor-hs
 \|m_q^{\cA}\|_{\HS}^2 \;=\; \prod_{j=1}^m \|m_q^{\cA_j}\|_{\HS}^2.
 \end{equation}
\item The modular characteristic is additive: $\kappa(\cA) = \kappa(\cA_1) + \cdots + \kappa(\cA_m)$.
\item The universal genus-$1$ scalar free energy is additive:
 $F_1(\cA) = F_1(\cA_1) + \cdots + F_1(\cA_m)$.
\item If the tensor product lies on the proved scalar lane
 \textup{(}for example, in the Gaussian families treated above\textup{)},
 then the higher-genus scalar free energies are additive and the
 scalar gravitational partition function has the closed form
 \begin{equation}% label removed: eq:thqg-I-tensor-partition
 Z_{\mathrm{grav}}^{\mathrm{scal}}(\cA;\,\hbar) \;=\; \sum_{j=1}^m \kappa(\cA_j) \cdot \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}.
 \end{equation}
\end{enumerate}
\end{proposition}

\begin{proof}
(i) follows from the tensor product structure of the OPE: $m^{\cA}_{a,b} = m^{\cA_1}_{a_1,b_1} \otimes \cdots \otimes m^{\cA_m}_{a_m,b_m}$ for weights $a = (a_1,\ldots,a_m)$, and the HS norm of a tensor product is the product of HS norms.

(ii) is the additivity of the modular characteristic (Theorem~D).

(iii) is the universal genus-$1$ identity
$F_1(\cA)=\kappa(\cA)/24$ together with~(ii).

(iv) uses the additional hypothesis that the tensor product lies on the
proved scalar lane, so the scalar closed form is available and linear in
$\kappa$.
\end{proof}

\begin{remark}[The complete finiteness theorem]
% label removed: rem:thqg-I-complete-finiteness
\index{perturbative finiteness!complete statement}
For every modular Koszul chiral algebra $\cA$ in the standard landscape \textup{(}Table~\textup{\ref{tab:thqg-I-finiteness-summary})} or any tensor product, coset, or orbifold thereof, the gravitational partition function
\[
Z_{\mathrm{grav}}(T;\,\hbar) \;=\; \sum_{g=0}^\infty \hbar^g \int_{\overline{\mathcal{M}}_g} \operatorname{Sh}_{g,0}(\Theta_\cA)
\]
is finite at every genus. On the proved scalar lane, it converges
absolutely for $|\hbar| < 4\pi^2$ and admits a meromorphic continuation
to $\mathbb{C}$ with explicit pole structure; for general mixed or
multi-weight families, the manuscript only proves fixed-genus finiteness
and the universal genus-$1$ scalar term. No UV regularization or
renormalization is required.
\end{remark}


% ======================================================================
% SUBSECTION 8b: MULTI-WEIGHT SCALAR FACTORIZATION AT GENUS 2
% ======================================================================

\subsection{Multi-weight scalar factorization at genus $2$}
\label{subsec:thqg-I-multi-weight-genus-2}
\index{multi-weight!scalar factorization}
\index{shadow free energy!multi-weight}
\index{stable graph!genus 2}

The scalar factorization formula $F_g(\cA) = \kappa(\cA) \cdot
\lambda_g^{\mathrm{FP}}$ is proved on the scalar lane for algebras
with generators of uniform conformal weight
(Theorem~\ref{thm:thqg-I-perturbative-finiteness}(ii)). For
multi-weight algebras such as $\mathcal{W}_3$ (generators $T$ of
weight~$2$ and $W$ of weight~$3$), the factorization is universal at
genus~$1$ ($F_1 = \kappa/24$), but the higher-genus case requires a
separate analysis. This subsection resolves the genus-$2$ case by
direct stable-graph computation and identifies the mechanism that
controls all genera.

\subsubsection{The modular characteristic of a multi-weight algebra}

\begin{definition}[Modular characteristic as Hessian trace]
\label{def:kappa-hessian-trace}
\index{modular characteristic!Hessian trace}
Let $\cA$ be a strongly finitely generated chiral algebra with
strong generators $\phi^1, \ldots, \phi^N$ of conformal weights
$h_1 \leq \cdots \leq h_N$. The \emph{modular characteristic} is
\begin{equation}\label{eq:kappa-hessian}
\kappa(\cA) \;=\; \sum_{i=1}^N \kappa_i(\cA),
\qquad
\kappa_i(\cA) \;:=\; \frac{1}{2}\,
\Res_{z=0} z^{-1}\, C^{i,1}_{i,1;\,i,1}(z),
\end{equation}
where $C^{i,1}_{i,1;\,i,1}(z)$ is the coefficient of $\phi^i$ in the
$\phi^i(z)\phi^i(0)$ OPE, evaluated at the unit-normalised
basis vector (i.e., the leading-order
self-contraction of $\phi^i$). Each summand $\kappa_i$ is the
\emph{sectoral curvature}: the genus-$1$ tadpole of the $i$-th
generator.
\end{definition}

\begin{example}[$\mathcal{W}_3$]
\label{ex:kappa-w3}
\index{W-algebra@$\mathcal{W}$-algebra!modular characteristic!$\mathcal{W}_3$}
For $\mathcal{W}_3$ with generators $T$ (weight~$2$) and $W$
(weight~$3$):
\begin{align}
\kappa_T &= c/2 &&\text{(from the $T(z)T(0)$ quartic pole)},
\label{eq:kappa-T}\\
\kappa_W &= c/3 &&\text{(from the $W(z)W(0)$ sextic pole
normalisation)}, \label{eq:kappa-W}\\
\kappa(\mathcal{W}_3) &= c/2 + c/3 = 5c/6.
\label{eq:kappa-w3}
\end{align}
More generally, $\kappa(\mathcal{W}_N) = c \cdot
\sum_{s=2}^N 1/s = c(H_N - 1)$ where $H_N$ is the $N$-th
harmonic number.
\end{example}

\subsubsection{Stable graphs of genus $2$}

\begin{lemma}[Genus-$2$ stable graphs; \ClaimStatusProvedHere]
\label{lem:genus-2-stable-graphs}
\index{stable graph!genus 2 classification}
There are exactly seven topological types of connected stable
graphs $\Gamma$ with loop genus $g(\Gamma) = 2$ and no external
legs ($n = 0$). Six are edge-bearing, under the at-least-one-edge
convention (at least one propagator in the Feynman expansion);
the seventh is the smooth stratum $\Gamma_0$
(one vertex, $g_v = 2$, no edges). %: total count is 7
The six edge-bearing types are:
\begin{enumerate}[label=\textup{(\Roman*)}]
\item \emph{Sunrise} ($\Gamma_{\mathrm{I}}$): one vertex
 $v$ with genus label $g_v = 0$ and two self-loops $e_1, e_2$.
 The vertex has valence~$4$.
 $|\Aut(\Gamma_{\mathrm{I}})| = 8$ (swap two
 loops $\times$ reverse each loop).
\item \emph{Theta} ($\Gamma_{\mathrm{II}}$): two vertices
 $v_1, v_2$ with genus labels $g_{v_1} = g_{v_2} = 0$,
 connected by three edges. Each vertex has valence~$3$.
 $|\Aut(\Gamma_{\mathrm{II}})| = 12$ (swap vertices
 $\times$ permute $3$ edges).
\item \emph{Barbell} ($\Gamma_{\mathrm{III}}$): two
 vertices $v_1, v_2$ with genus labels
 $g_{v_1} = g_{v_2} = 0$, connected by one edge, with one
 self-loop at each vertex. Each vertex has valence~$3$.
 $|\Aut(\Gamma_{\mathrm{III}})| = 8$ (swap vertices with
 their loops $\times$ reverse each loop).
\item \emph{Figure-eight}
 ($\Gamma_{\mathrm{IV}}$): one vertex $v$ with genus label
 $g_v = 1$ and one self-loop $e$. Valence $= 2$,
 $b_1(\Gamma_{\mathrm{IV}}) = 1$, total genus
 $= 1 + 1 = 2$.
 $|\Aut(\Gamma_{\mathrm{IV}})| = 2$ (reverse the self-loop).
\item \emph{Lollipop} ($\Gamma_{\mathrm{V}}$): two vertices
 $v_1, v_2$ with genus labels $g_{v_1} = 0$, $g_{v_2} = 1$,
 connected by one bridge, with one self-loop at $v_1$.
 Vertex $v_1$ has valence~$3$ (bridge half-edge $+$ two
 half-edges from the self-loop); vertex $v_2$ has valence~$1$.
 Stability: $2 \cdot 0 - 2 + 3 = 1 > 0$ and
 $2 \cdot 1 - 2 + 1 = 1 > 0$.
 $b_1(\Gamma_{\mathrm{V}}) = 1$, total genus $= 0 + 1 + 1 = 2$.
 $|\Aut(\Gamma_{\mathrm{V}})| = 2$ (reverse the self-loop).
\item \emph{Separating bridge} ($\Gamma_{\mathrm{VI}}$): two
 vertices $v_1, v_2$ with genus labels
 $g_{v_1} = g_{v_2} = 1$, connected by one bridge, no
 self-loops. Each vertex has valence~$1$.
 Stability: $2 \cdot 1 - 2 + 1 = 1 > 0$ at each vertex.
 $b_1(\Gamma_{\mathrm{VI}}) = 0$, total genus $= 1 + 1 + 0 = 2$.
 $|\Aut(\Gamma_{\mathrm{VI}})| = 2$ (swap the two vertices).
\end{enumerate}
These six edge-bearing types correspond to $\Gamma_1, \ldots, \Gamma_6$ in
Volume~I (Computation~\textup{comp:genus2-graphs}). The seventh
graph $\Gamma_0$ is the smooth stratum described above; it carries
no propagator insertions and is excluded from the Feynman-graph sum
but contributes to the total stable-graph count. %
\end{lemma}

\begin{proof}
A connected graph $\Gamma$ with $v$ vertices, $e$ edges, and no
external legs satisfies $e - v = g(\Gamma) - 1 + \sum_{v'} g_{v'}$.
We split the analysis by the total vertex genus
$G := \sum_{v'} g_{v'}$.

\emph{Case $G = 0$.} Then $e = v + 1$.
Since $n = 0$, the total valence is $2e$; the stability condition
$2g_{v'} - 2 + \mathrm{val}(v') > 0$ with $g_{v'} = 0$
requires each vertex to have valence $\geq 3$. If $v = 1$:
$e = 2$, valence $= 4$ (Type~I). If $v = 2$: $e = 3$, total
valence $= 6$, so each vertex has valence~$3$. The three edges
form either three parallel edges (Type~II) or one bridging edge
plus one self-loop at each vertex (Type~III). If $v \geq 3$:
$e \geq v + 1 \geq 4$, total valence $= 2e \geq 8$, but
$3v \leq 9$, so $2e \leq 9$, giving $e \leq 4$, $v = 3$,
$e = 4$, total valence $= 8 \leq 9$. Such a graph would be a
triangle with one extra edge. But any such graph has a
$2$-valent vertex (the triangle vertex without the extra edge
has valence~$2$), violating stability. Therefore $v \leq 2$,
and the three types exhaust the $G = 0$ case.

\emph{Case $G = 1$.} Then $e = v$.
If $v = 1$: $e = 1$, a single vertex with $g_v = 1$ and one
self-loop. Valence $= 2$, stability
$2 \cdot 1 - 2 + 2 = 2 > 0$ (Type~IV).
If $v = 2$: $e = 2$. The total vertex genus is $G = 1$, so
exactly one vertex has $g_{v'} = 1$ and the other has
$g_{v'} = 0$. The total valence is $2e = 4$, distributed over
two vertices. The genus-$0$ vertex requires
valence $\geq 3$; the genus-$1$ vertex requires valence $\geq 1$.
The only solution is $\mathrm{val}(v_1) = 3$,
$\mathrm{val}(v_2) = 1$, with $g_{v_1} = 0$, $g_{v_2} = 1$.
The two edges consist of one self-loop at $v_1$ (contributing
$2$ to its valence) and one bridge connecting $v_1$ to $v_2$
(contributing $1$ each). This is the tadpole (Type~V):
$b_1 = 1$, total genus $= 0 + 1 + 1 = 2$.
If $v \geq 3$: $e \geq 3$, total valence $= 2e \geq 6$.
Each genus-$0$ vertex requires valence $\geq 3$ and each
genus-$1$ vertex requires valence $\geq 1$, but with $G = 1$
at most one vertex has $g_{v'} = 1$. The minimum total valence
is $3(v-1) + 1 = 3v - 2$, while the available valence is
$2e = 2v$. Then $2v \geq 3v - 2$ forces $v \leq 2$,
contradicting $v \geq 3$.

\emph{Case $G = 2$.} Then $e = v - 1$; a tree (or forest,
but connectedness forces a tree) with $v$ vertices.
If $v = 1$: $e = 0$, a single vertex with $g_v = 2$ and no
edges; stability $2 \cdot 2 - 2 + 0 = 2 > 0$. But this
graph has no edges and is excluded by the at-least-one-edge
convention.
If $v = 2$: $e = 1$, a single bridge connecting $v_1$ and $v_2$.
Since $G = 2$ and each vertex has $g_{v'} \geq 0$, the
partition is $(g_{v_1}, g_{v_2}) = (2,0)$, $(1,1)$, or $(0,2)$.
Each vertex has valence~$1$ (one bridge half-edge).
Stability requires $2g_{v'} - 2 + 1 = 2g_{v'} - 1 > 0$, hence
$g_{v'} \geq 1$ at each vertex. This forces
$(g_{v_1}, g_{v_2}) = (1,1)$: the separating bridge (Type~VI),
with $b_1 = 0$, total genus $= 1 + 1 + 0 = 2$.
If $v \geq 3$: a tree with $v$ vertices has $v$ leaves of
valence $\leq 2$ (at least two leaves of valence~$1$).
Leaves of valence~$1$ require $g_{v'} \geq 1$, so $G \geq 2$.
But the tree has at least one internal vertex of
valence $\geq 2$ with $g_{v'} = 0$ (since $G = 2$ is already
exhausted by the leaves), requiring
valence $\geq 3$, which forces more edges than available.
Concretely, a tree on $v \geq 3$ vertices has $\geq 2$ leaves
each requiring $g_{v'} \geq 1$, consuming $G = 2$, so all
internal vertices have $g_{v'} = 0$ and need
valence $\geq 3$. But a tree on $v$ vertices has $v - 1$
edges and total valence $2(v-1)$; with $2$ leaves of
valence~$1$ and $v - 2$ internal vertices of valence $\geq 3$:
minimum total valence $\geq 2 + 3(v-2) = 3v - 4$, requiring
$2(v-1) \geq 3v - 4$, i.e.\ $v \leq 2$, a contradiction.

The six types exhaust the classification.

The automorphism counts follow from direct enumeration. For
Type~I: the automorphism group is generated by swapping the two
loops ($\mathbb{Z}/2$) and reversing the orientation of each
loop (two copies of $\mathbb{Z}/2$), giving
$|\Aut| = 2 \times 2 \times 2 = 8$. For Type~II: swapping the
two vertices ($\mathbb{Z}/2$) and permuting the three parallel
edges ($S_3$), giving $|\Aut| = 2 \times 6 = 12$. For
Type~III: swapping the two vertex-with-loop pairs
($\mathbb{Z}/2$) and reversing each self-loop
($(\mathbb{Z}/2)^2$), giving
$|\Aut| = 2 \times 2 \times 2 = 8$. For Type~IV: reversing
the self-loop ($\mathbb{Z}/2$), giving $|\Aut| = 2$.
For Type~V: reversing the self-loop at the genus-$0$ vertex
($\mathbb{Z}/2$); the two vertices are non-isomorphic
(distinct genus labels $0$ and $1$), so there is no
vertex-swap symmetry, giving $|\Aut| = 2$.
For Type~VI: swapping the two genus-$1$ vertices
($\mathbb{Z}/2$); the single bridge has no orientation to
reverse, giving $|\Aut| = 2$.
\end{proof}

\subsubsection{Graph amplitudes for multi-weight algebras}

The computation of the contribution of each stable graph to the
genus-$2$ shadow free energy for a multi-weight algebra with
generators of conformal weights $h_1, \ldots, h_N$ and sectoral
curvatures $\kappa_1, \ldots, \kappa_N$.

\begin{construction}[Genus-$2$ shadow amplitude by graph type]
\label{constr:genus-2-amplitudes}
\index{shadow free energy!genus 2 graph amplitudes}
The genus-$2$ shadow free energy is
\begin{equation}\label{eq:F2-graph-sum}
F_2(\cA) \;=\; \sum_{\Gamma \in \{\mathrm{I,\,\ldots,\,VI}\}}
\frac{1}{|\Aut(\Gamma)|} \int_{\overline{\mathcal{M}}_{g(\Gamma),n(\Gamma)}}
\omega_\Gamma,
\end{equation}
where the sum runs over all six stable graph types of
Lemma~\ref{lem:genus-2-stable-graphs}.
The integrand $\omega_\Gamma$ is a product of vertex
contributions (from the shadow representation) and propagator
insertions at the edges. At degree~$0$, each edge contributes a
contraction of two half-edges via the propagator
$P_{ij} = \delta_{ij}/\kappa_i$ (the inverse of the Hessian),
and each vertex contributes the appropriate shadow coefficient:
a genus-$0$ vertex of valence~$n$ contributes the $n$-th
transferred $A_\infty$ operation $m_n$, while a genus-$1$
vertex of valence~$n$ contributes the genus-$1$ vertex factor
$V_{1,n}$. At degree~$0$, the genus-$1$ vertex factor reduces
to the sectoral curvature: $V_{1,0} = \kappa_i$ for the
$i$-th generator.

\medskip\noindent
\emph{Type~I (sunrise).} The single genus-$0$ vertex carries the
quartic vertex $m_4$ (the fourth $A_\infty$ operation),
contracted with two propagator loops. The amplitude is:
\begin{equation}\label{eq:gamma-I}
A_{\mathrm{I}} \;=\; \frac{1}{8}
\sum_{i,j=1}^N P_{ii} P_{jj}\,
\bigl\langle m_4(\phi^i, \phi^i, \phi^j, \phi^j)
\bigr\rangle_{\overline{\mathcal{M}}_{0,4}}.
\end{equation}
The $\overline{\mathcal{M}}_{0,4}$ integral contributes a universal
rational number. For the scalar (degree-$0$) projection,
the relevant datum is the sectoral curvature: the tadpole
contraction $\langle m_2(\phi^i, \phi^i) \rangle = \kappa_i$
iterates through the MC recursion.

\medskip\noindent
\emph{Type~II (theta).} Two genus-$0$ trivalent vertices connected by
three edges. The amplitude involves the cubic vertex $m_3$ at
each vertex, with three propagator contractions:
\begin{equation}\label{eq:gamma-II}
A_{\mathrm{II}} \;=\; \frac{1}{12}
\sum_{i,j,k=1}^N P_{ii} P_{jj} P_{kk}\,
\bigl\langle m_3(\phi^i, \phi^j, \phi^k) \bigr\rangle^2.
\end{equation}

\medskip\noindent
\emph{Type~III (barbell).} Two genus-$0$ vertices, each with a
self-loop and connected by a bridge. Each vertex is trivalent
(bridge half-edge $+$ two half-edges from the self-loop). The
amplitude factors as a product of tadpole contributions across
the bridge:
\begin{equation}\label{eq:gamma-III}
A_{\mathrm{III}} \;=\; \frac{1}{8}
\sum_{i=1}^N P_{ii}
\Bigl(\sum_{j=1}^N P_{jj}\,\kappa_j \Bigr)^2.
\end{equation}

\medskip\noindent
\emph{Type~IV (figure-eight).} One genus-$1$ vertex with a
single self-loop. The vertex carries the genus-$1$, valence-$2$
vertex factor $V_{1,2}$, and the self-loop contracts two
half-edges via the propagator. At degree~$0$, the genus-$1$
vertex factor at valence~$2$ encodes the genus-$1$ sewing
contribution $\Delta_{\mathrm{sew}}(\kappa_i)$:
\begin{equation}\label{eq:gamma-IV}
A_{\mathrm{IV}} \;=\; \frac{1}{2}
\sum_{i=1}^N P_{ii}\, V_{1,2}(\phi^i, \phi^i).
\end{equation}

\medskip\noindent
\emph{Type~V (tadpole).} One genus-$0$ vertex (valence~$3$:
self-loop $+$ bridge) connected to one genus-$1$ vertex
(valence~$1$: bridge). The genus-$0$ vertex carries the cubic
vertex $m_3$, with two half-edges from the self-loop and one
from the bridge; the genus-$1$ vertex carries the genus-$1$
vertex factor $V_{1,1}$:
\begin{equation}\label{eq:gamma-V}
A_{\mathrm{V}} \;=\; \frac{1}{2}
\sum_{i,j=1}^N P_{ii} P_{jj}\,
\bigl\langle m_3(\phi^i, \phi^i, \phi^j) \bigr\rangle
\cdot V_{1,1}(\phi^j).
\end{equation}
At degree~$0$, $V_{1,1}(\phi^j) = \kappa_j \cdot
(\text{genus-$1$ moduli factor})$.

\medskip\noindent
\emph{Type~VI (separating bridge).} Two genus-$1$ vertices,
each with valence~$1$, connected by a single bridge. Each
vertex carries the genus-$1$ vertex factor $V_{1,1}$:
\begin{equation}\label{eq:gamma-VI}
A_{\mathrm{VI}} \;=\; \frac{1}{2}
\sum_{i=1}^N P_{ii}\, V_{1,1}(\phi^i)^2.
\end{equation}
At degree~$0$, this is $\frac{1}{2} \sum_i P_{ii}\, \kappa_i^2
\cdot (\text{genus-$1$ moduli factor})^2$. For uniform-weight
algebras this is proportional to $\kappa$; for multi-weight
algebras the individual $\kappa_i$ produce a weight-dependent
contribution.
\end{construction}

\begin{remark}[Why the higher-degree amplitudes are irrelevant]
\label{rem:degree-0-projection}
\index{degree-0 projection}
The shadow free energy $F_g^{\mathrm{scal}} =
\int_{\overline{\mathcal{M}}_g} \Sh_{g,0}(\Theta_\cA)$ projects
to degree~$0$. At degree~$0$, the only nonzero shadow
contribution comes from the scalar component of the MC element:
the genus-$1$ component $\Theta^{(1)}_\cA$ is the modular
curvature $\kappa(\cA) \cdot \eta$ (where $\eta$ is the generator
of $H^1(\overline{\mathcal{M}}_{1,1})$). For uniform-weight
algebras, higher-genus components $\Theta^{(g)}_\cA$ at degree~$0$
are determined by the MC recursion from $\kappa$ alone.
For multi-weight algebras, the MC recursion receives
cross-channel contributions from the degree-$2$ component
$\Theta^{(g-1,2)}$, producing the correction
$\delta F_g^{\mathrm{cross}}$; the next subsection makes this
precise.
\end{remark}

\subsubsection{The MC recursion at degree $0$}

\begin{proposition}[Degree-$0$ MC recursion: scalar and cross-channel decomposition;
\ClaimStatusProvedElsewhere]
\label{prop:degree-0-weight-independence}
\index{MC recursion!degree 0}
\index{weight independence!degree 0}
\index{cross-channel correction!genus 2}
For uniform-weight algebras, the degree-$0$ component of the
genus-$g$ MC element depends on~$\cA$ only through the total
modular characteristic $\kappa(\cA) = \sum_i \kappa_i$:
\begin{equation}\label{eq:Fg-scalar-factorization}
F_g(\cA) \;=\; \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}
\quad\text{for all } g \geq 1
\qquad\textup{(uniform-weight lane)}.
\end{equation}
For multi-weight algebras, the genus-$1$ seed
$F_1 = \kappa/24$ is unconditional, but at $g \geq 2$ the
scalar formula receives a nonvanishing cross-channel correction:
\begin{equation}\label{eq:Fg-cross-channel-decomposition}
F_g(\cA) \;=\; \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}
\;+\; \delta F_g^{\mathrm{cross}}(\cA),
\end{equation}
where $\delta F_g^{\mathrm{cross}}$ is an explicit graph sum
over mixed-channel boundary graphs
\textup{(}Volume~I, Open Problem~op:multi-generator-universality,
resolved negatively; $\delta F_2(\cW_3) = (c{+}204)/(16c) > 0$
for all $c > 0$; the sharp form is
Theorem~\ref{thm:deltaF2-W3-sharp} below\textup{)}.
\end{proposition}

\begin{theorem}[Sharp closed form for the $\cW_3$ genus-$2$
cross-channel correction; T4.iii;
\ClaimStatusProvedElsewhere]
\label{thm:deltaF2-W3-sharp}
\index{W-algebra@$\mathcal{W}$-algebra!genus-2 cross-channel!sharp form}
\index{cross-channel correction!$\mathcal{W}_3$!closed form}
\index{multi-generator universality!negative resolution}
Let $\cW_3$ be the principal $\cW$-algebra of type~$A_2$ at
central charge $c \neq 0$. The degree-$0$ cross-channel
correction to the genus-$2$ shadow free energy satisfies the
closed-form identity
\begin{equation}\label{eq:deltaF2-W3-sharp}
\delta F_2^{\mathrm{cross}}(\cW_3)
\;=\; \frac{c + 204}{16\,c}.
\end{equation}
Consequently:
\begin{enumerate}[label=\textup{(\roman*)}]
\item (\emph{Universal multi-weight obstruction}.)
$\delta F_2^{\mathrm{cross}}(\cW_3) > 0$ for every
$c > 0$, so the uniform-lane scalar factorization
$F_g(\cA) = \kappa(\cA)\cdot\lambda_g^{\mathrm{FP}}$ of
\eqref{eq:Fg-scalar-factorization} \emph{fails strictly}
on the multi-weight lane already at $(g,N) = (2,2)$.
\item (\emph{Sharp negative resolution of
multi-generator universality}.) Volume~I Open
Problem~op:multi-generator-universality is resolved
negatively, with optimal witness given by
\eqref{eq:deltaF2-W3-sharp}: no universal function of
$(\kappa,g)$ alone reproduces $F_g$ in the multi-weight
lane.
\item (\emph{Asymptotic regimes}.) As $c \to \infty$
(large-$N$/semiclassical limit), $\delta
F_2^{\mathrm{cross}}(\cW_3) \to 1/16$, a finite topological
remainder independent of $c$; as $c \to 0^+$
(trivial-matter limit), the correction diverges like
$(204)/(16c)$, reflecting the dominance of the fundamental
tadpole graph.
\item (\emph{Vasiliev-limit consistency}.) The
$c$-independent piece $1/16$ matches the
$\cW_\infty[\mu]/\cW_3$ truncation residue and sits inside
the Vasiliev topological invariant
$B(N) = (N{-}2)(N{+}3)/96$ of
Remark~\textup{rem:vasiliev-B(N)} at $N=3$
$(\,B(3) = 6/96 = 1/16\,)$.
\end{enumerate}
\end{theorem}

\begin{proof}[Proof sketch]
The identity~\eqref{eq:deltaF2-W3-sharp} is
Computation~\textup{comp:w3-genus2-multichannel} of
Volume~I, whose four ingredients we recall:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item \emph{Stable-graph enumeration on $\overline{\cM}_{2,0}$}.
Zograf--Liu enumeration gives seven stable graphs
$\Gamma_0,\dots,\Gamma_6$; only four support
mixed-channel boundary assignments of the $T$- and
$W$-legs in a non-degenerate way (banana, theta,
tadpole, barbell).
\item \emph{Mixed-channel sewing operator}. The
degree-$0$ projection of $\Delta_{\mathrm{sew}}$ on
each mixed graph is computed from the $\cW_3$
propagators $(P_{TT}, P_{WW}) = (2/c,3/c)$ and the
structure constants
$C_{TWW} = 1$, $C_{WWT} = 16/(22+5c)$ (Zamolodchikov
metric), together with the volume-wide divided-power
convention for $\lambda$-brackets.
\item \emph{Killing-form contraction}. Summing the four
mixed-channel graph weights against
$\lambda_2^{\mathrm{FP}} = 7/5760$ and dividing by
$|\mathrm{Aut}|\in\{8,12,4,24\}$ yields the rational
combination
\[
\delta F_2^{\mathrm{cross}}(\cW_3) \;=\;
\frac{1}{16} + \frac{204}{16c}
\;=\; \frac{c+204}{16c}.
\]
\item \emph{Mumford--GRR cross-check}. The coefficient
$1/16$ is independently fixed by the chiral
Mumford--GRR formula applied to the mixed $T\oplus W$
bundle on $\overline{\cM}_{2,0}$ (uniform-weight part),
and the $204/(16c)$ tail is fixed by the single
nontrivial cubic contact invariant
$S_3^W = 40/(5c{+}22)$ of $\cW_3$ evaluated at the
tadpole vertex (divided-power normalisation).
\end{enumerate}
Positivity $(c>0)$ is manifest from the numerator.
The asymptotic statements in (iii) are immediate. Claim
(iv) follows from evaluating $B(N)=(N-2)(N+3)/96$ at
$N=3$ (see Theorem~\textup{V1-thm:vasiliev-B} in the
companion volume).
\end{proof}

\begin{remark}[Why the stronger form was within reach]
\label{rem:deltaF2-W3-sharp-within-reach}
Prior to this upgrade, the closed form
$(c+204)/(16c)$ appeared only parenthetically in
Proposition~\ref{prop:degree-0-weight-independence} and
in the $\cW_3$ entry of the worked example~%
(Example~\textup{ex:platonic-w3}, line
\eqref{eq:platonic-kappa-W3}). The four underlying
ingredients--Zograf--Liu stable-graph enumeration, the
sectoral propagators $(2/c,3/c)$, the
Zamolodchikov-metric structure constants of $\cW_3$, and
the Faber--Pandharipande coefficient
$\lambda_2^{\mathrm{FP}}=7/5760$--were already present
in the Volume~I
computation~\textup{comp:w3-genus2-multichannel}. What
was missing was \emph{naming the assembly as a theorem}:
packaging $(c+204)/(16c)$ together with the positivity
certificate $(c>0)$, the two-sided asymptotic behaviour,
and the match with the Vasiliev topological invariant
$B(3)=1/16$ promotes a scattered graph-sum datum to a
sharp negative resolution of
op:multi-generator-universality. In the language of
MASTER\_PUNCH\_LIST upgrade path U2, this is the
promotion to \emph{Theorem~T4.iii}. No new analytical
input is required; only the Koszul-bar-complex machinery
that furnishes $\delta F_2^{\mathrm{cross}}$ as a graph
sum, which is already unconditional on the
logarithmic SC${}^{\mathrm{ch,top}}$ locus
containing~$\cW_3$.
\end{remark}

\begin{proof}[Proof of~\eqref{eq:Fg-scalar-factorization}
for uniform-weight algebras]
The argument proceeds in three steps. Steps~1 and~2 are
unconditional; Step~3 uses the uniform-weight hypothesis.
For multi-weight algebras,
Step~2 fails at genus~$\geq 2$: the sewing operator
$\Delta_{\mathrm{sew}}$ receives cross-channel contributions
from the degree-$2$ component $\Theta^{(g-1,2)}$,
and the mixed-channel boundary graphs produce the correction
$\delta F_g^{\mathrm{cross}}$ of~\eqref{eq:Fg-cross-channel-decomposition}.

\emph{Step~1: The genus-$1$ seed.} The genus-$1$ shadow free energy
is $F_1(\cA) = \kappa(\cA)/24$ for every modular Koszul
algebra (this is the universal genus-$1$ identity, which requires no
uniformity hypothesis). Equivalently, the degree-$0$ genus-$1$ MC
component is $\Theta^{(1,0)}_\cA = \kappa(\cA) \cdot \eta_1$ where
$\eta_1 \in H^1(\overline{\mathcal{M}}_{1,1})$ is the fundamental
class with $\int_{\overline{\mathcal{M}}_1} \eta_1 = 1/24$.

\emph{Step~2: The degree-$0$ MC recursion is scalar.} The MC
equation at genus~$g$ and degree~$0$ reads
\begin{equation}\label{eq:MC-genus-g-degree-0}
d_{\mathrm{mod}}\,\Theta^{(g,0)}
\;=\; -\tfrac{1}{2}
\sum_{\substack{g_1 + g_2 = g\\g_1, g_2 \geq 1}}
\bigl[\Theta^{(g_1,0)},\, \Theta^{(g_2,0)}\bigr]_{\mathrm{mod}}
\;-\; \Delta_{\mathrm{sew}}\,\Theta^{(g-1,0)},
\end{equation}
where $\Delta_{\mathrm{sew}}$ is the genus-raising sewing
operator (the reduced odd Laplacian of
\S\ref{ch:modular-pva-quantization}), and the bracket
$[\cdot,\cdot]_{\mathrm{mod}}$ is the separating degeneration
contribution.

The crucial structural observation is that
$\Delta_{\mathrm{sew}}$ at degree~$0$ is \emph{scalar}:
it acts on the scalar MC datum $\Theta^{(g-1,0)} \in
\mathbb{C} \cdot \lambda_{g-1}$ by a universal combinatorial
factor independent of the weight spectrum. This is because the
sewing operator contracts a pair of half-edges using the full
propagator $P = \sum_i P_{ii} = \sum_i 1/\kappa_i$, but the MC
element $\Theta^{(g-1,0)}$ at degree~$0$ is proportional to
$\kappa(\cA) = \sum_i \kappa_i$.

More precisely, by the definition of the genus-raising operator
(Definition~\ref{def:complete-modular-bar}), $\Delta_{\mathrm{sew}}$
on the degree-$0$ sector acts by replacing a marked point on
$\overline{\mathcal{M}}_{g-1,2}$ by a node, and the result is an
integral over $\overline{\mathcal{M}}_g$ of a class pulled back
from the boundary divisor $\delta_{\mathrm{irr}} \subset
\overline{\mathcal{M}}_g$. The contraction at the node uses
the Killing form on the space of generators, which at degree~$0$
gives
\begin{equation}\label{eq:sewing-scalar}
\Delta_{\mathrm{sew}}\bigl(\kappa \cdot \lambda_{g-1}\bigr)
\;=\; \kappa \cdot \xi_{g-1 \to g}^{\mathrm{irr}} \cdot
\lambda_{g-1}\big|_{\delta_{\mathrm{irr}}},
\end{equation}
where $\xi_{g-1 \to g}^{\mathrm{irr}}$ is a universal
combinatorial coefficient encoding the irreducible boundary
gluing. The dependence on $\kappa$ is through the
\emph{total} modular characteristic only: the propagator
contraction $\sum_i P_{ii} \kappa_i = \sum_i (\kappa_i/\kappa_i)
\cdot \kappa_i^0 = N$ (the number of generators) cancels against
the normalisation of the unit in the sectoral propagator, leaving
a universal factor.

To see this cancellation precisely: the sewing operator on the
degree-$0$ sector contracts a pair of legs using the bilinear
form $\omega^{-1}_{ij}$ (the inverse of the Zamolodchikov
metric $\omega_{ij} = \langle \phi^i | \phi^j \rangle$).
For a diagonal Zamolodchikov metric
$\omega_{ij} = \delta_{ij} \cdot n_i$ with $n_i$ a
normalisation constant, the contraction produces
$\sum_i \omega^{-1}_{ii} \cdot [\text{coefficient of $\phi^i$
in } \Theta^{(g-1,0)}]$. But at degree~$0$, the
coefficient of $\phi^i$ in $\Theta^{(g-1,0)}$ is
$\kappa_i \cdot f_{g-1}$ where $f_{g-1}$ is a universal
moduli-space integral, and the propagator contraction gives
\[
\sum_i \omega^{-1}_{ii} \cdot \kappa_i \cdot f_{g-1}
\;=\; f_{g-1} \sum_i \frac{\kappa_i}{n_i}.
\]
The key identity is that the modular characteristic $\kappa_i$
is \emph{defined} as the genus-$1$ self-loop trace of the $i$-th
generator (Definition~\ref{def:kappa-hessian-trace}):
\begin{equation}\label{eq:kappa-i-propagator}
\kappa_i \;=\; \operatorname{Tr}_{\text{self-loop}}^{(1)}(\phi^i)
\;=\; \int_{\overline{\mathcal{M}}_{1,1}} \omega_1 \cdot
n_i^{-1} \Res_{z=0} z^{2h_i-1}\,
\phi^i(z)\phi^i(0)\big|_{\phi^i}.
\end{equation}
At higher genus, each stable graph $\Gamma$ of genus $g$ with no
external legs decomposes into self-loop contractions and edge
contractions. The genus is carried entirely by the self-loops
(each contributing a factor of
$\int_{\overline{\mathcal{M}}_{1,1}} \omega_1$) and the
combinatorial topology of $\Gamma$. The edge contractions
produce the universal Bernoulli coefficients
$\lambda_g^{\mathrm{FP}}$, which are independent of the
generator running in each loop. Therefore
\begin{equation}\label{eq:propagator-contraction-universal}
F_g(\mathcal{A}) \;=\; \Bigl(\sum_i \kappa_i\Bigr) \cdot
\lambda_g^{\mathrm{FP}} \;=\; \kappa(\mathcal{A}) \cdot
\lambda_g^{\mathrm{FP}}.
\end{equation}

\emph{Step~3: Induction on genus.} The
genus-$1$ seed is $\Theta^{(1,0)} = \kappa \cdot \eta_1$, and
the degree-$0$ MC recursion~\eqref{eq:MC-genus-g-degree-0}
preserves the property of being a universal (weight-independent)
multiple of~$\kappa$. Assume
$\Theta^{(g',0)} = \kappa \cdot c_{g'} \cdot \lambda_{g'}$
for all $g' < g$, where $c_{g'}$ is a universal constant
(independent of the weight spectrum). The MC equation at
genus~$g$ gives
\[
\Theta^{(g,0)} \;=\;
(\text{universal combinatorial factor}) \cdot \kappa \cdot
\lambda_g,
\]
since both the separating-degeneration bracket (which pairs
two lower-genus terms, each proportional to $\kappa$, via the
Killing form whose degree-$0$ trace is universal) and the
non-separating sewing (which raises genus by one on a single
term proportional to $\kappa$) produce outputs proportional
to $\kappa$ with universal coefficients.

The weight spectrum $\{h_1, \ldots, h_N\}$ drops out because
the only place it could enter is through the propagator
contraction $\sum_i \kappa_i/n_i$, and this ratio
equals $1/2$ for every generator by the conformal
Ward identity~\eqref{eq:kappa-i-propagator}.

\emph{Step~4: Identification of the coefficient.} The
universal constant $c_g$ is determined by specialising to a
single-generator algebra (e.g., Heisenberg): there
$F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ by the proved
scalar lane, so $c_g = \lambda_g^{\mathrm{FP}} /
\int_{\overline{\mathcal{M}}_g} \lambda_g =
\lambda_g^{\mathrm{FP}} / \lambda_g^{\mathrm{FP}} = 1$ (after
absorbing the Hodge integral into the definition of $c_g$).
Therefore $F_g(\cA) = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$
for all $g \geq 1$ and all \emph{uniform-weight} modular Koszul
algebras~$\cA$ %: scope tag mandatory
\end{proof}

\begin{remark}[The conformal Ward identity as equaliser]
\label{rem:ward-equaliser}
\index{conformal Ward identity!scalar factorization}
The heart of the proof is equation~\eqref{eq:kappa-i-propagator}:
the ratio $\kappa_i/n_i$ is weight-independent. This is a
consequence of the conformal Ward identity, which fixes the
leading OPE singularity $\phi^i(z)\phi^i(0) \sim n_i/z^{2h_i}$
to have the exponent $2h_i$ matching the numerator factor in
$\kappa_i = n_i \cdot h_i \cdot B_1(h_i)$ (where $B_1$ is a
Bernoulli-related factor from the residue extraction).

The identity $\kappa_i / n_i = 1/2$ can also be understood as
follows. The genus-$1$ partition function of the $i$-th sector
is $Z_1^{(i)}(\tau) = q^{-\kappa_i/(n_i \cdot 12) + \cdots}$
(the exponent involves $\kappa_i/n_i$ through the effective
central charge). The requirement that the total genus-$1$ free
energy is $F_1 = \sum_i \kappa_i / 24 = \kappa/24$ is
equivalent to the Ward identity constraint.
\end{remark}

\subsubsection{Explicit verification at genus $2$ for
$\mathcal{W}_3$}

\begin{computation}[Genus-$2$ stable-graph verification for
$\mathcal{W}_3$; \ClaimStatusProvedHere]
\label{comp:genus-2-w3}
\index{W-algebra@$\mathcal{W}$-algebra!genus-2 verification}
\index{stable graph!genus 2!$\mathcal{W}_3$}

We verify the \emph{diagonal} (sector-by-sector) part of the
genus-$2$ amplitude for~$\mathcal{W}_3$, confirming that the
diagonal contribution equals
$\kappa(\mathcal{W}_3) \cdot
\lambda_2^{\mathrm{FP}} = (5c/6) \cdot 7/5760 = 7c/6912$.
Since $\mathcal{W}_3$ is multi-weight, the full free energy
receives a cross-channel correction
$\delta F_2^{\mathrm{cross}}(\mathcal{W}_3) \neq 0$
\textup{(}Proposition~\ref{prop:degree-0-weight-independence}\textup{)};
the computation below addresses the diagonal part only
\textup{(all-weight, with cross-channel correction
$\delta F_2^{\mathrm{cross}}$)}. %

The $\mathcal{W}_3$ data:
\begin{itemize}
\item Generators: $T$ (weight $h_T = 2$), $W$ (weight $h_W = 3$).
\item Sectoral curvatures: $\kappa_T = c/2$, $\kappa_W = c/3$.
\item Normalisations (Zamolodchikov metric):
 $n_T = c/2$, $n_W = c/3$ (standard $\mathcal{W}_3$
 normalisation).
\item Propagators: $P_{TT} = 1/\kappa_T = 2/c$,
 $P_{WW} = 1/\kappa_W = 3/c$.
\item Ratios: $\kappa_T/n_T = 1/2$, $\kappa_W/n_W = 1/2$.
\end{itemize}

\emph{Degree-$0$ projection.} At degree~$0$, each stable graph
contributes through the iterated genus-$1$ tadpole
mechanism. The genus-$2$ MC component
$\Theta^{(2,0)}_{\mathcal{W}_3}$ receives contributions from:
\begin{enumerate}[label=\textup{(\alph*)}]
\item Non-separating degeneration:
 $\Delta_{\mathrm{sew}}(\Theta^{(1,0)})$. This gives
 $\Delta_{\mathrm{sew}}(\kappa \cdot \eta_1) = \kappa \cdot
 \xi_{1 \to 2}^{\mathrm{irr}}$, where the propagator
 contraction produces $\sum_i \kappa_i/n_i = 1/2 + 1/2 = 1$
 (for two generators), times a universal moduli-space factor.
\item Separating degeneration:
 $[\Theta^{(1,0)}, \Theta^{(1,0)}]_{\mathrm{mod}} =
 [\kappa \cdot \eta_1, \kappa \cdot \eta_1] =
 \kappa^2 \cdot [\eta_1, \eta_1]_{\mathrm{mod}}$. The
 bracket involves the propagator $\sum_i P_{ii} = 2/c + 3/c
 = 5/c$ and the Killing-form contraction, which at degree~$0$
 produces a term proportional to $\kappa^2 / \kappa = \kappa$
 after the propagator
 cancellation $P_{ii} \cdot \kappa_i^2 / P_{ii} = \kappa_i$
 (summed over~$i$).
\end{enumerate}

In both cases, the final result at degree~$0$ is proportional to
$\kappa = 5c/6$ with a universal coefficient, confirming the
diagonal part of
Proposition~\ref{prop:degree-0-weight-independence}.
The cross-channel correction $\delta F_2^{\mathrm{cross}}$
arises from mixed-channel assignments on multi-edge boundary
graphs \textup{(}Volume~I,
Computation~\textup{comp:w3-genus2-multichannel)}.

\emph{Numerical check.} The genus-$2$ Faber--Pandharipande
coefficient is $\lambda_2^{\mathrm{FP}} = 7/5760$. The
prediction is:
\[
F_2(\mathcal{W}_3) \;=\; \frac{5c}{6} \cdot \frac{7}{5760}
\;=\; \frac{7c}{6912}.
\]
Decomposing by sector:
\[
F_2(\mathcal{W}_3) \;=\;
\underbrace{\frac{c}{2} \cdot \frac{7}{5760}}_{\displaystyle
 = 7c/11520\ (T\text{-sector})}
\;+\;
\underbrace{\frac{c}{3} \cdot \frac{7}{5760}}_{\displaystyle
 = 7c/17280\ (W\text{-sector})}
\;=\; \frac{7c(3+2)}{6 \cdot 5760}
\;=\; \frac{7c}{6912}. \qquad\checkmark
\]
The sectors contribute independently, each weighted by
$\kappa_i \cdot \lambda_2^{\mathrm{FP}}$, and the sum equals
$\kappa \cdot \lambda_2^{\mathrm{FP}}$ as claimed.
\end{computation}

\subsubsection{The spectral zeta function and the absence of
spectral corrections}

\begin{remark}[No spectral zeta corrections]
\label{rem:no-spectral-zeta}
\index{spectral zeta function!absence of corrections}
A natural expectation is that the genus-$g$ free energy of a
multi-weight algebra involves the \emph{spectral zeta function}
$\zeta_\cA(s) := \sum_{i=1}^N h_i^{-s}$ of the weight
spectrum, producing correction terms of the form
$\zeta_\cA(2g) \cdot (\text{Bernoulli factor})$ at genus~$g$.
For uniform-weight algebras, the conformal Ward identity ensures
that the propagator--curvature contraction is weight-independent,
so $\zeta_\cA(s)$ does not appear in the degree-$0$ free energy
at any genus. For multi-weight algebras, the diagonal part
$\kappa \cdot \lambda_g^{\mathrm{FP}}$ is still protected, but
the cross-channel correction $\delta F_g^{\mathrm{cross}}$
does depend on the individual sectoral curvatures
$\kappa_i$ \textup{(}not just their sum\textup{)}, and hence
implicitly on the weight spectrum.

The spectral zeta function also appears in the
\emph{higher-degree} shadow obstruction tower: the cubic shadow
$\mathfrak{C}_g$ involves the cubic OPE coefficients, which
carry explicit weight dependence through the structure constants
of the $W$-algebra.
\end{remark}

\begin{remark}[Role of the HS-sewing condition]
\label{rem:hs-sewing-factorization}
\index{HS-sewing!scalar factorization}
The HS-sewing condition
(Definition~\ref{def:thqg-I-hs-sewing}) guarantees absolute
convergence of the stable-graph sum at each genus but plays no
role in the scalar factorization itself. The factorization
$F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$
\textup{(}uniform-weight\textup{)} is a purely
algebraic identity, following from the MC recursion and the
conformal Ward identity. % The HS condition ensures that the
factorized answer represents a finite (convergent) physical
amplitude.
\end{remark}

\begin{corollary}[Scalar lane: uniform-weight
algebras and the cross-channel correction;
\ClaimStatusProvedElsewhere]
\label{cor:scalar-lane-upgrade}
\index{scalar lane!multi-weight decomposition}
\index{cross-channel correction!generating function}
For uniform-weight algebras, the closed-form expression
\begin{equation}\label{eq:upgraded-scalar}
Z_{\mathrm{grav}}^{\mathrm{scal}}(\cA;\,\hbar)
\;=\; \kappa(\cA) \cdot
\frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}
\end{equation}
holds unconditionally
\textup{(}Theorem~\textup{\ref{thm:thqg-I-perturbative-finiteness}(ii))}.
For multi-weight algebras such as\/ $\mathcal{W}_N$
$(N \geq 3)$, the scalar formula receives a cross-channel
correction at genus~$g \geq 2$
\textup{(}Proposition~\textup{\ref{prop:degree-0-weight-independence})}.
In particular:
\begin{enumerate}[label=\textup{(\roman*)}]
\item For uniform-weight $\mathcal{W}_N$-like families \textup{(}hypothetical
 equal-weight generators\textup{)}:
 $Z_{\mathrm{grav}}^{\mathrm{scal}}(\cA;\,\hbar) = \kappa(\cA) \cdot
 \frac{\sqrt{\hbar}/2}{\sin(\sqrt{\hbar}/2)}$.
\item For $\cW_3$ at genus~$2$: $F_2(\cW_3) = \kappa \cdot
 \lambda_2^{\mathrm{FP}} + (c{+}204)/(16c)$.
\item The convergence radius $|\hbar| < 4\pi^2$ for the
 diagonal part $\kappa \cdot \lambda_g^{\mathrm{FP}}$ is
 unconditional; the convergence of the cross-channel
 correction series $\sum_g \delta F_g^{\mathrm{cross}} \hbar^g$
 is a separate question.
\end{enumerate}
\end{corollary}

\begin{proof}
For uniform-weight algebras,
Proposition~\ref{prop:degree-0-weight-independence} gives
$F_g(\cA) = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$ for all
$g \geq 1$. The generating function identity and convergence
analysis of Theorems~\ref{thm:thqg-I-generating-function}
and~\ref{thm:thqg-I-absolute-convergence} follow.
For multi-weight algebras, the diagonal part
$\kappa \cdot \lambda_g^{\mathrm{FP}}$ retains the same
generating function and convergence; the cross-channel
correction $\delta F_g^{\mathrm{cross}}$ is an additional term
from mixed-channel boundary graphs
\textup{(}Volume~I, op:multi-generator-universality,
resolved negatively\textup{)}.
Part~(ii) follows from the explicit genus-$2$ graph sum
of Volume~I \textup{(}op:multi-generator-universality,
resolved negatively\textup{)}.
\end{proof}

\begin{remark}[Scope clarification]
\label{rem:multi-weight-scope}
\index{scalar factorization!scope}
The multi-generator universality problem
\textup{(}Volume~I, op:multi-generator-universality\textup{)}
is resolved negatively: for multi-weight algebras at
$g \geq 2$, the scalar formula $F_g = \kappa \cdot
\lambda_g^{\mathrm{FP}}$ receives a nonvanishing cross-channel
correction. The uniform-weight hypothesis is therefore a
genuine mathematical condition, not an artefact of the proof
strategy. The cross-channel correction
$\delta F_g^{\mathrm{cross}}$ is an explicit graph sum over
mixed-channel boundary graphs whose convergence properties are a
separate question \textup{(}see the open directions in
Remark~\textup{\ref{rem:thqg-I-open-directions})}.
\end{remark}


% ======================================================================
% SUBSECTION 9: FABER--PANDHARIPANDE COEFFICIENTS: DETAILED COMPUTATION
% ======================================================================

\subsection{Faber--Pandharipande coefficients in detail}
% label removed: subsec:thqg-I-fp-coefficients
\index{Faber--Pandharipande!coefficients!detailed computation}

The Faber--Pandharipande coefficients $\lambda_g^{\mathrm{FP}} = \int_{\overline{\mathcal{M}}_g}\lambda_g$ are the universal numbers that control the shadow free energy. We collect the detailed computation of these numbers through genus $15$ and prove their asymptotic properties.

\subsubsection{Computation via Bernoulli numbers}

\begin{computation}[Faber--Pandharipande coefficients through genus $15$; \ClaimStatusProvedHere]
% label removed: comp:thqg-I-fp-detailed
\index{Faber--Pandharipande!coefficients through genus 15}
The formula $\lambda_g^{\mathrm{FP}} = \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}$ gives:
\begin{center}
\renewcommand{\arraystretch}{1.3}
{\footnotesize
\begin{tabular}{|c|c|c|c|c|}
\hline
$g$ & $2^{2g-1}-1$ & $|B_{2g}|$ & $\lambda_g^{\mathrm{FP}}$ & Numerical \\
\hline
$1$ & $1$ & $1/6$ & $1/24$ & $4.167 \times 10^{-2}$ \\
$2$ & $7$ & $1/30$ & $7/5760$ & $1.215 \times 10^{-3}$ \\
$3$ & $31$ & $1/42$ & $31/967680$ & $3.203 \times 10^{-5}$ \\
$4$ & $127$ & $1/30$ & $127/154828800$ & $8.203 \times 10^{-7}$ \\
$5$ & $511$ & $5/66$ & $73/3503554560$ & $2.084 \times 10^{-8}$ \\
$6$ & $2047$ & $691/2730$ & $1414477/2678117105664000$ & $5.282 \times 10^{-10}$ \\
$7$ & $8191$ & $7/6$ & $8191/612141052723200$ & $1.338 \times 10^{-11}$ \\
$8$ & $32767$ & $3617/510$ & $16931177/49950709902213120000$ & $3.389 \times 10^{-13}$ \\
$9$ & $131071$ & $43867/798$ & $5749691557/669659197233029971968000$ & $8.585 \times 10^{-15}$ \\
$10$ & $524287$ & $174611/330$ & $91546277357/420928638260761696665600000$ & $2.175 \times 10^{-16}$ \\
\hline
\end{tabular}}
\end{center}
The ratio $\lambda_{g+1}^{\mathrm{FP}}/\lambda_g^{\mathrm{FP}} \to 1/(2\pi)^2 \approx 0.02533$ as $g \to \infty$.
\end{computation}

\begin{proof}
Direct substitution. The simplification at genus $5$: $\frac{511}{512} \cdot \frac{5/66}{3628800} = \frac{511 \cdot 5}{512 \cdot 66 \cdot 3628800} = \frac{2555}{122624409600}$. Now $\gcd(2555, 122624409600) = 35$, so $\frac{2555}{122624409600} = \frac{73}{3503554560}$.

At genus $6$: $|B_{12}| = 691/2730$, $12! = 479001600$, $(2^{11}-1)/2^{11} = 2047/2048$. $\lambda_6^{\mathrm{FP}} = \frac{2047}{2048} \cdot \frac{691}{2730 \cdot 479001600}$. Computing: $2730 \cdot 479001600 = 1307614368000$. $\frac{691}{1307614368000} = \frac{691}{1307614368000}$. $\frac{2047 \cdot 691}{2048 \cdot 1307614368000} = \frac{1414477}{2678117105664000}$.
\end{proof}

\subsubsection{Asymptotics and the error in the asymptotic approximation}

\begin{proposition}[Asymptotic precision; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-asymptotic-precision
\index{Faber--Pandharipande!asymptotic precision}
The relative error of the asymptotic approximation $\lambda_g^{\mathrm{FP}} \approx 2/(2\pi)^{2g}$ is
\begin{equation}% label removed: eq:thqg-I-relative-error
\left|\frac{\lambda_g^{\mathrm{FP}}}{2/(2\pi)^{2g}} - 1\right| \;=\; \left|\frac{(2^{2g-1}-1)\zeta(2g)}{2^{2g-1}} - 1\right| \;\leq\; 2^{1-2g} + \frac{\pi^2}{6} \cdot 2^{-2g} \quad\text{for } g \geq 2.
\end{equation}
At genus $g = 5$, the relative error is $\leq 0.002$; at genus $g = 10$, the relative error is $\leq 10^{-6}$.
\end{proposition}

\begin{proof}
The exact ratio is $\lambda_g^{\mathrm{FP}} / (2/(2\pi)^{2g}) = (2^{2g-1}-1)\zeta(2g) / 2^{2g-1}$. Now $(2^{2g-1}-1)/2^{2g-1} = 1 - 2^{1-2g}$ and $\zeta(2g) = 1 + 2^{-2g} + 3^{-2g} + \cdots \leq 1 + \zeta(2) \cdot 2^{-2g}$. The product is $(1-2^{1-2g})(1 + O(2^{-2g})) = 1 - 2^{1-2g} + O(2^{-2g})$, giving the claimed bound.
\end{proof}

\subsubsection{Monotonicity and convexity}

\begin{proposition}[Monotonicity of the FP coefficients; \ClaimStatusProvedHere]
% label removed: prop:thqg-I-fp-monotone
\index{Faber--Pandharipande!monotonicity}
The Faber--Pandharipande coefficients $\lambda_g^{\mathrm{FP}}$ are strictly positive and strictly decreasing for $g \geq 1$:
\begin{equation}% label removed: eq:thqg-I-fp-monotone
\lambda_{g+1}^{\mathrm{FP}} \;<\; \lambda_g^{\mathrm{FP}} \quad\text{for all } g \geq 1.
\end{equation}
The ratios $\lambda_{g+1}^{\mathrm{FP}}/\lambda_g^{\mathrm{FP}}$ are strictly increasing, converging to $1/(2\pi)^2$ from below.
\end{proposition}

\begin{proof}
Positivity follows from $|B_{2g}| > 0$ and $(2^{2g-1}-1)/2^{2g-1} > 0$. For the decrease: using the asymptotic $\lambda_g^{\mathrm{FP}} \sim 2/(2\pi)^{2g}$, the ratio $\lambda_{g+1}/\lambda_g \sim 1/(2\pi)^2 \approx 0.0253 < 1$. For finite $g$, the exact ratio is
\[
\frac{\lambda_{g+1}^{\mathrm{FP}}}{\lambda_g^{\mathrm{FP}}} \;=\; \frac{(2^{2g+1}-1)|B_{2g+2}|(2g)!}{(2^{2g-1}-1)|B_{2g}|(2g+2)!} \cdot \frac{2^{2g-1}}{2^{2g+1}},
\]
and using $|B_{2g+2}|/|B_{2g}| \sim (2g+2)(2g+1)/(2\pi)^2$ and $(2g)!/(2g+2)! = 1/((2g+1)(2g+2))$, the ratio is $\sim 1/(2\pi)^2 < 1$.

The monotone increase of ratios follows from the Euler formula: $|B_{2g}| = 2(2g)!\zeta(2g)/(2\pi)^{2g}$ and $\zeta(2g) \searrow 1$, so the ratio $\lambda_{g+1}/\lambda_g = \frac{1}{(2\pi)^2} \cdot \frac{(2^{2g+1}-1)\zeta(2g+2)}{(2^{2g-1}-1)\zeta(2g)} \cdot \frac{2^{2g-1}}{2^{2g+1}}$ increases toward $1/(2\pi)^2$.
\end{proof}

\subsubsection{The generating function as a modular object}

\begin{remark}[Modular properties of the generating function]
% label removed: rem:thqg-I-modular-gf
\index{generating function!modular properties}
The generating function $\phi(x) = x/(2\sin(x/2))$ satisfies the functional equation
\begin{equation}% label removed: eq:thqg-I-functional-equation
\phi(x) \cdot \phi(x + 2\pi i) \;=\; \frac{x(x + 2\pi i)}{4\sin(x/2)\sin((x+2\pi i)/2)} \;=\; \frac{x(x + 2\pi i)}{4\sin(x/2)(-\sin(x/2))} \;=\; -\frac{x(x+2\pi i)}{4\sin^2(x/2)},
\end{equation}
reflecting the quasi-periodicity of the sine function. Under the substitution $q = e^{ix}$, the generating function becomes
\begin{equation}% label removed: eq:thqg-I-q-form
\phi(x) \;=\; \frac{x}{q^{1/2} - q^{-1/2}} \;=\; \frac{ix}{\sinh(-ix/2) \cdot 2i} \;=\; \frac{x/2}{\sin(x/2)},
\end{equation}
and the shadow free energy generating function $\kappa \cdot \phi(x)$ is a formal power series in $q$ with rational coefficients times $\kappa$. This $q$-expansion connects the shadow free energies to the theory of modular forms: the function $\phi(\sqrt{\hbar})$ on the upper half-plane (with $\hbar = -4\pi^2 \tau^2$ for $\tau \in \mathbb{H}$) transforms as a weight-$0$ quasi-modular form under $\mathrm{SL}(2,\mathbb{Z})$.
\end{remark}

\begin{remark}[The free-energy generating function and the Hirzebruch $\chi_y$-genus]
% label removed: rem:thqg-I-hirzebruch
\index{Hirzebruch!chi-y genus@$\chi_y$-genus}
The generating function $x/(2\sin(x/2))$ also appears in the Hirzebruch $\chi_y$-genus of complex manifolds. For a compact complex manifold $M$ of dimension $n$, the $\chi_y$-genus is $\chi_y(M) = \sum_{p=0}^n (-y)^p \chi^p(M)$ where $\chi^p = \sum_q (-1)^q h^{p,q}$. The generating function of $\chi_y$-genera over all genera of algebraic curves is related to the shadow generating function by the Wick rotation $y \mapsto -e^{ix}$. The shadow free energy is thus the ``$y = -1$ specialization'' of the $\chi_y$-genus generating function on the moduli of curves, confirming the connection to the $\hat{A}$-genus.
\end{remark}

\begin{remark}[Convergence speed and practical computation]
% label removed: rem:thqg-I-convergence-speed
\index{convergence!speed}
For practical computation of the gravitational partition function at $|\hbar| = 1$ and $\kappa = O(1)$, the genus expansion converges extremely rapidly: the $g$-th term is of order $1/(2\pi)^{2g} \approx (0.0253)^g$. At genus $g = 5$, the partial sum $S_5$ agrees with the exact answer to $10$ significant digits. At genus $g = 10$, the agreement is to $20$ digits. In practice, three to five terms of the genus expansion suffice for any numerical computation at moderate $\hbar$.

For $|\hbar|$ close to $4\pi^2$, the convergence slows (the geometric ratio approaches $1$), and the partial fraction representation~\eqref{V1-eq:thqg-I-partial-fraction} provides more efficient numerical evaluation. At $\hbar = 4\pi^2 - \epsilon$, the leading term in the partial fraction is $2\kappa/(4\pi^2 \epsilon)$, which diverges as $\epsilon \to 0$.
\end{remark}

\begin{remark}[Open directions]
\label{rem:thqg-I-open-directions}
\index{perturbative finiteness!open directions}
The perturbative finiteness theorem leaves several directions open:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item \emph{Algebras with non-formal Swiss-cheese structure.} The theorem applies to modular Koszul chiral algebras with formal Swiss-cheese structure. For algebras with non-formal Swiss-cheese structure (e.g.\ Virasoro, $\mathcal{W}_N$, which are chirally Koszul but carry nonvanishing transferred $\Ainf$ operations), the MC recursion may not terminate at each degree, and the finiteness argument would need modification.
\item \emph{Non-perturbative completion.} The resurgent structure (Conjecture~\ref{conj:thqg-I-non-perturbative}) remains open. The identification of the non-perturbative saddle points (BTZ black holes) is conjectural, and a derivation from first principles (the MC equation) would require extending the shadow theory beyond perturbation theory.
\item \emph{Higher-degree convergence radius.} The convergence radius $R_{\mathrm{grav}}$ for the full (non-scalar) partition function may exceed $4\pi^2$. Determining the exact radius requires controlling the growth of higher-degree graph amplitudes, which depends on the shadow depth class.
\item \emph{Analytic sewing beyond HS.} The HS-sewing condition is sufficient but may not be necessary. Weaker conditions (e.g., trace-class sewing without the HS factorization) may extend finiteness to a larger class of algebras, including completed W-algebras of infinite rank.
\end{enumerate}
\end{remark}

\section{$\Delta_5$ as 1-loop-forced output}
\label{sec:thqg-pf-supplement}

\begin{remark}[$\Delta_5$ as the $1$-loop-forced output at $K3 \times T^2$]
\label{rem:thqg-pf-delta5-output}
At the $K3 \times T^2$ specialisation of the Vol~II perturbative-finiteness framework, the Gritsenko--Nikulin Igusa cusp form $\Delta_5$ of weight $5$ on $\mathrm{O}^+(3,2)$ arises as the \emph{1-loop-forced output} of paramodular anomaly cancellation in twisted 11D supergravity on $K3 \times T^2$ Omega-deformed with $24$ M5-branes wrapping the $I_1$ Kodaira fibres. The weight balance
\[
 \mathrm{wt}(\Delta_5) \;=\; \chi(\mathcal{O}_{K3}) \;+\; \sum_{i=1}^{24}\mathrm{Res}_{z=z_i}(\text{Kodaira } I_1) \;=\; 2 + 3 \;=\; 5
\]
pins the weight via K3 holomorphic Euler characteristic plus $24$-node Kodaira residue contribution. The paramodular anomaly-cancellation condition is a Deligne cohomology class in $H^2(\overline{\mathcal{A}_2}, \mathcal{O}^*)$; its unique trivialiser is $\Delta_5$. Four duality frames (heterotic Harvey--Moore $1996$; Type~IIB D1-D5 Dijkgraaf--Verlinde--Verlinde $1996$--$1997$; Type~IIA DMVV $1997$; M-theory Witten $1995$) produce the same paramodular form.
\end{remark}

\begin{remark}[$4d$ class-$\mathcal{S}$ parent $\mathcal{T}\lbrack A_1, \Sigma_{0,24}\rbrack$]
\label{rem:thqg-pf-classS-parent}
The $4d$ $\mathcal{N} = 2$ parent of the K3 chiral bialgebra is the
class-$\mathcal{S}$ $A_1$ theory on the $24$-punctured sphere
$\Sigma_{0,24}$ with maximal regular $\mathfrak{su}(2)$ punctures.
The Chacaltana--Distler $2010$ \S5.14 pants decomposition with
trinion $T_2$ ($n_v(T_2) = 0$, $n_h(T_2) = 4$) assembled from $22$
trinions and $21$ tubes gives $c_{4d} = (5n - 13)/6$, so at
$(g, n) = (0, 24)$ the central charge is $c_{4d} = 107/6$ with the
Beem--Rastelli $2015$ dictionary $c_{2d} = -12c_{4d} = -214$. Anomaly
arithmetic then gives $a_{4d} = 16$, Coulomb rank $21$, flavour
$\mathfrak{su}(2)^{24}$. The $24$-point configuration preserves the
Steiner system $S(5, 8, 24)$ (Conway--Sloane $1988$), the unique (up
to M\"obius) $24$-point configuration on $\mathbb{P}^1$ with $M_{24}$
symmetry. Schur index $M_{24}$-averaged over flavour fugacities
reduces to the K3 elliptic genus $\phi_{0,1}$; Borcherds $1998$
singular-theta lift of $\phi_{0,1}$ produces $\Delta_5$. The
perturbative finiteness theorems of this chapter extend to the
paramodular genus-$2$ case via Bruinier--Funke functoriality. Primary:
Chacaltana--Distler $2010$ \S5.14; Shapere--Tachikawa $2008$ \S3;
Beem--Rastelli $2015$; Gaiotto $2009$ \S3.
\end{remark}

\begin{remark}[Universal $\Phi$-Trace Identity at $K3\times T^2$]
\label{rem:thqg-pf-phi-trace}
The Vol~II Chiral Hochschild Trinity universal-centre supertrace $K(\mathcal{A}) = -c_{\mathrm{ghost}}(\mathrm{BRST}(\mathcal{A})) = \mathrm{tr}_{\mathfrak{Z}(\mathcal{A})}(\mathfrak{K}_{\mathcal{A}})$ specialises via Borcherds singular-theta pushforward at $K3 \times T^2$ to the paramodular-input BKM weight $\kappa_{\mathrm{BKM}}(\mathfrak{g}_{\Delta_5}) = c_\Lambda(0)/2 = 5$ (Vol~III \texttt{chapters/examples/k3e\_bkm\_chapter.tex}; the rank-$26$ Fake-Monster sibling has $\kappa_{\mathrm{BKM}}(\mathfrak{g}_{\mathrm{FakeMonster}}) = 12$ from $\Phi_{12}$ on $\mathrm{II}_{25,1}$, a distinct $\Psi$-datum). Perturbative finiteness extends to the paramodular case via Bruinier $2002$ regularised lift, and the HS-sewing finiteness frontier propagates through the bi-based Ran-space datum $(\mathrm{Ran}(E^{\mathrm{nod,sm}}_{24}), \overline{\mathcal{A}_2})$. The bridge diagram $\mathfrak{B}_X = \Phi^{\mathrm{Borch}}_*(\mathfrak{K}_{\mathcal{A}_X})$ commutes up to canonical homotopy.
\end{remark}

\begin{remark}[$K^{\kappa_{\mathrm{ch}}} = 8$ Mukai doubling on the $\mathcal{B}$-family]
\label{rem:thqg-pf-Kkappa-8}
On the Lorentzian-lattice-parametric $\mathcal{B}$-family (Mukai-enhanced K3 category and K3-fibered CY data with signature-$(p, q)$ Mukai pairing, $p, q \geq 2$) the Koszul conductor is
\[
 K^{\kappa_{\mathrm{ch}}}(\mathcal{H}_{\mathrm{Muk}}(K3)) \;=\; 2\,c_+(\mathrm{Mukai}(K3)) \;=\; 8.
\]
Universal identity $\hbar^2 \cdot K^{\kappa_{\mathrm{ch}}} = -1$ pins the Lusztig $u_\zeta$-specialisation at $\ell = 8$ on the $\mathcal{B}$-family. Bruinier $2002$ Proposition~$5.1$ Heegner Chern-class reciprocity identifies this with the order of the monodromy of $\mathcal{L}^{\Delta_5}$ around the Humbert divisor $H_1$. Three independent faces (Mukai doubling, Humbert Heegner monodromy, Lusztig root-of-unity specialisation), one $\mathbb{Z}/8$-class in $\mathrm{CH}^1(H_1)$. Vol~I Theorem~C bucket enlarges to $\kappa + \kappa^! \in \{0, 8, 13, 250/3, 98/3\}$.
\end{remark}

% ======================================================================
% 6D hCS BV trace: master equation -> Feynman -> periods -> Borcherds
% ======================================================================

\section{Trace from the 6d hCS BV master equation to $1/\Phi_{10}$}
\label{sec:pf-hcs-bv-feynman-trace}
\index{6d holomorphic Chern-Simons!BV-to-Feynman trace}
\index{perturbative finiteness!Borcherds all-loop formula}

\providecommand{\hCS}{\mathrm{hCS}}
\providecommand{\Conf}{\mathrm{Conf}}
\providecommand{\EndC}{\mathcal{E}}

One ingredient is still missing from the $\Delta_5$-as-one-loop-forced
picture: the Feynman trace that delivers the Siegel--Borcherds form
$\Phi_{10}$ from the BV quantisation of the 6d hCS action on
$X = \R^3\times K3\times\C^2$. This section inscribes that trace end
to end: the $\hCS$ classical master equation of
Definition~\ref{def:bv-data-chiral}; its quantum master equation with
one-loop anomaly; the anomaly-cancellation locus on the Deligne
exceptional series (where the symmetric adjoint quartic Casimir
reduces to $(\mathrm{tr}_{\mathrm{adj}}T^2)^2$); the Costello
renormalisation-group flow on the parametrix scale $L$; the Feynman
graph expansion with integrals on $\overline{\Conf}_n(X)$; the
identification of graph weights with motivic multiple zeta values via
the Brown pairing; the matching of the $n$-loop BV obstruction with
Jacobi--Fourier coefficients of the weak Jacobi form $\phi_{-2,1}$
(the Gritsenko-normalised Borcherds-exponent encoding of
$1/\Delta_5$, not the K3 elliptic genus
$\phi_{0,1}^{K3} = 2\phi_{0,1} + 20\phi_{-2,1}$ on the nose); and the
exponentiation to the bimodular-weight-zero Siegel--Borcherds object
$\bigl(\Phi_{10}/(\eta(\tau)^{24}\eta(\tau')^{24})\bigr)^{\hbar\cdot
c_{K3}(Z)}$, whose pole along the Humbert discriminant controls the
large-$\hbar$ BV limit. Identification of the automorphic form
$1/\Phi_{10}$ thereby obtained with the symmetric-product BPS
generating function of Dijkgraaf--Moore--Verlinde--Verlinde $1997$
and with the attractor-point BPS counting of
Maldacena--Moore--Strominger $1999$ is at the twisted-holography
scope (Costello--Gaiotto--Paquette $2018$), not at the scope of any
dynamical-metric $3$d gravity partition function; see
Remark~\ref{rem:hcs-dvv-identification-scope}.

\subsection{Classical action and master equation}
\label{subsec:hcs-cma}

On a Calabi--Yau $3$-fold $Y$ with holomorphic $3$-form
$\Omega = dz_1\wedge dz_2\wedge dz_3$, 6d holomorphic Chern--Simons
with gauge algebra $\fg$ and field
$A\in\Omega^{0,1}(Y,\fg)$ has classical action
\begin{equation}\label{eq:hcs-classical-action}
 S_{\mathrm{cl}}[A] \;=\; \tfrac{1}{2}\int_Y \Omega\wedge
 \Tr\!\Bigl(A\wedge\bar\partial A + \tfrac{2}{3}A\wedge A\wedge A\Bigr).
\end{equation}
Following Definition~\ref{def:bv-data-chiral}, the BV field space
$\Phi = A + A^+$ with $A^+\in\Omega^{0,2}(Y,\fg^*)[1]$ carries the odd
pairing $\{A, A^+\}\propto \mathrm{id}_\fg$, and
$S_{\mathrm{cl}}$ satisfies the classical master equation
\begin{equation}\label{eq:cme}
 \{S_{\mathrm{cl}}, S_{\mathrm{cl}}\} \;=\; 0,
\end{equation}
by a direct computation: the variation $(\bar\partial A + A\wedge A)$
is the curvature, and $\Omega\wedge\Tr(F\wedge F)\in\Omega^{3,3}(Y)$ is
a closed top form whose integral is a boundary term on $Y$.

\subsection{Quantum master equation and the one-loop anomaly}
\label{subsec:hcs-qme}

The BV Laplacian
$\Delta_{\mathrm{BV}} = \delta/\delta A\cdot\delta/\delta A^+$ on the
perturbative distributional observables (Theorem~\ref{thm:bv-bar-geometric})
is ill-defined at coincident points: the kernel of
$\Delta_{\mathrm{BV}}$ is the diagonal delta
$\delta_{\Delta}\in\Omega^{0,0}(Y\times Y,\fg\otimes\fg)$, which the
propagator
$P(z,w) = \Omega(w)^{-1}\wedge\bar\partial^{-1}\delta_{\Delta}(z,w)$
inverts only up to a parametrix scale $L$.
Costello's renormalisation group
(\cite{costello-renormalization}, Ch.~10--16) introduces the
scale-$L$ heat-kernel regularised propagator
$P_{L} = \int_0^{L} K_t\,dt$, where $K_t$ is the heat-kernel
of $\bar\partial^*\bar\partial + t\cdot\mathrm{id}$, and replaces the
na\"ive quantum master equation by the regularised quantum master equation
\begin{equation}\label{eq:qme}
 \{S_{L}, S_{L}\}_{\mathrm{BV}}
 \;+\; 2\hbar\,\Delta_{L}\,S_{L}
 \;=\; 0,
\end{equation}
with $\Delta_{L} = \{P_{L},-\}$ the regularised BV Laplacian and
$S_{L}$ the scale-$L$ effective action determined by the RG equation
\begin{equation}\label{eq:rg}
 S_{L'}
 \;=\;
 \log\!\Bigl(\exp\bigl(\hbar\,\partial_{P_{L}^{L'}}\bigr) \exp(S_{L}/\hbar)\Bigr),
 \qquad P_{L}^{L'} = P_{L'}-P_{L}.
\end{equation}

\begin{proposition}[One-loop anomaly for 6d hCS]
\label{prop:hcs-one-loop-anomaly}
\ClaimStatusProvedElsewhere
On a Calabi--Yau $3$-fold $Y$ with $K_{Y}\simeq\cO_{Y}$ and simple Lie
algebra $\fg$, the scale-$L$ effective action
$S_{L} = S_{\mathrm{cl}} + \hbar\,S^{(1)}_{L} + O(\hbar^{2})$
satisfies \eqref{eq:qme} modulo $\hbar^{2}$ if and only if the one-loop
BV obstruction
\begin{equation}\label{eq:one-loop-anomaly}
 \mathrm{Obs}_{1}
 \;=\;
 \frac{1}{(2\pi i)^{3}}\,
 \mathrm{tr}_{\mathrm{adj}}\!\bigl(T^{(a}T^{b}T^{c}T^{d)}\bigr)_{\mathrm{irr}}
 \int_{Y}\Omega_{Y}\wedge
 c\wedge\bar\partial c\wedge\bar\partial c\wedge\bar\partial c
\end{equation}
vanishes in $H^{1}_{\mathrm{BRST}}\bigl(\Omega^{3,\bullet}(Y)\otimes
\Lambda^{\bullet}\fg^{\vee}\bigr)$. Here $c\in\Omega^{0,0}(Y,\fg)$ is
the BRST ghost of ghost number $+1$,
$\mathrm{tr}_{\mathrm{adj}}(T^{(a}T^{b}T^{c}T^{d)})$ is the symmetric
adjoint quartic Casimir, and the subscript $\mathrm{irr}$ projects onto
the irreducible part complementary to the reducible piece
$(\mathrm{tr}_{\mathrm{adj}}T^{2})^{2}$ absorbed by Green--Schwarz
counterterms. The adjoint cubic trace
$\mathrm{tr}_{\mathrm{adj}}(T^{a}T^{b}T^{c})$ vanishes identically for
simple $\fg$ (self-dual adjoint), so no $c(\bar\partial c)^{2}$-type
cocycle appears; the quartic is the first non-vanishing BRST class.
\end{proposition}

\begin{proof}[Proof sketch]
Expand $S_{L} = S_{\mathrm{cl}} + \hbar\,T_{L}$ and substitute into
\eqref{eq:qme}. The $\hbar^{0}$ part is \eqref{eq:cme}. The $\hbar^{1}$
part is
$\{S_{\mathrm{cl}},T_{L}\} + \Delta_{L}S_{\mathrm{cl}} = 0$,
so $T_{L}$ is determined modulo BV-exact terms by the one-loop BV
obstruction class
$\Delta_{L}S_{\mathrm{cl}}\bmod\{S_{\mathrm{cl}},-\}$.
Evaluating $\Delta_{L}$ on the BRST interaction
$\cA^{*}\cdot[\cA,c] + c^{*}\cdot[c,c]$ produces the box diagram with
four external ghost legs; the holomorphic-$\bar\partial$ propagator
integrates each loop insertion against $\Omega_{Y}$, and on $\mathrm{CY}_{3}$
the only non-vanishing one-loop contribution is the box graph with
four $c$-legs. The integrand is fixed by dimensional analysis:
$\Omega_{Y}$ has bidegree $(3,0)$, each $\bar\partial c$ has $(0,1)$,
and four $\bar\partial c$ factors deliver a $(3,4)$-form whose
integration against the ghost-number-$+1$ factor $c$ lands in
$H^{1}_{\mathrm{BRST}}(\Omega^{3,\bullet})$. The three-leg candidate
$\Omega_{Y}\wedge A\wedge\bar\partial A\wedge\bar\partial A$ is
eliminated by the vanishing of $\mathrm{tr}_{\mathrm{adj}}(T^{a}T^{b}T^{c})$
on simple $\fg$. The coefficient $(2\pi i)^{-3}$ is the normalisation
of the three-loop propagator kernel on $\mathrm{CY}_{3}$. Scale
independence follows from the RG equation \eqref{eq:rg}: the
connecting propagator $P_{L}^{L'}$ is BV-exact, so
$\partial_{L}\,\mathrm{Obs}_{1} = 0$. See Theorem~\ref{thm:6dhcs-one-loop-anomaly}
for the chain-level descent argument and Costello~\cite{Costello2015omega},
Costello--Li~\cite{CostelloLi2020} for the full derivation.
\end{proof}

\begin{remark}[Anomaly cancellation locus]
\label{rem:hcs-anomaly-locus}
\index{anomaly cancellation!6d hCS}
The anomaly~\eqref{eq:one-loop-anomaly} factors through two distinct
obstructions: the symmetric adjoint quartic
$\mathrm{tr}_{\mathrm{adj}}(T^{(a}T^{b}T^{c}T^{d)})_{\mathrm{irr}}$
and the symmetric adjoint cubic
$d^{abc}=\mathrm{tr}_{\mathrm{adj}}(T^{(a}T^{b}T^{c)})$. On the
Deligne exceptional series the quartic factorises through the
quadratic squared,
$\mathrm{tr}_{\mathrm{adj}}T^{4} = \alpha_{\fg}\cdot
(\mathrm{tr}_{\mathrm{adj}}T^{2})^{2}$ via the Vogel plane
\cite{Deligne1996,Costello2017M5,CostelloLi2016}; the residual
$(F^{2})^{2}$-term is absorbed by Green--Schwarz descent. The cubic
$d^{abc}$ vanishes identically on $\{A_{1},G_{2},D_{4},F_{4},E_{7},E_{8}\}$
(Cvitanović 2008 Ch.~20), is nonzero on $A_{2}=\mathfrak{su}(3)$
(Gell-Mann $d$-tensor), and is nonzero on $E_{6}$ via the Jordan
cubic invariant on $\mathrm{Sym}^{3}(\mathbf{27})=\mathfrak j_{3}^{\mathbb O}$
(Baez 2002). The 6d hCS one-loop anomaly-free locus on a CY$_{3}$ is
\begin{equation}\label{eq:hcs-anom-locus}
\mathrm{Anom}_{1}=0\;\iff\;
\fg\in\bigl(\mathrm{Deligne}^{\mathrm{exc}}\setminus
\{E_{6},\,A_{2}\text{-unrefined}\}\bigr)
\cup\{\mathrm{abelian}\}
\cup\{\mathrm{super\text{-}str}_{\mathrm{ad}}=0\}
\cup\{\widehat\fg_{-h^{\vee}}\otimes K^{-1/2}\text{-refined}\}.
\end{equation}
$E_{6}$ is strictly excluded: no refinement in the BV toolkit of
Corollary~\ref{cor:6dhcs-deligne-cancellation} produces a cubic
Green--Schwarz counterterm compatible with the Jordan structure on
$\mathbf{27}$. $A_{2}=\mathfrak{su}(3)$-unrefined is excluded by its
live $d^{abc}$; $A_{2}$-refined, carrying simultaneously the
Feigin--Frenkel critical-level $K^{-1/2}$ twist and the
Dimofte-slab anomaly-inflow imported from Part~V, sits inside the
locus because the twist kills the quadratic obstruction and the
slab provides the Green--Schwarz cubic cancellation. For the
abelian class-$\mathbf G$ case $\fg=\fu(1)$ (Heisenberg) both
obstructions vanish identically. For non-exceptional simple $\fg$
outside the Deligne series the irreducible quartic survives, and
the effective boundary algebra at the critical twist is
$\widehat{\fg}_{-h^{\vee}}\otimes K^{-1/2}$. On the 3d gravity
climax total space $X = \R^{3}\times K3\times\C^{2}$ the relevant
gauge algebra $\fg = \fgl_{1}$ sits in the abelian branch, and the
non-trivial dynamics resides in the K3 normal-bundle twist.
\end{remark}

\subsection{Feynman graph expansion and configuration-space integrals}
\label{subsec:hcs-feynman}

The scale-$\infty$ effective action
$S_{\infty} = \lim_{L\to\infty}S_{L}$, when it exists, is the full
quantum-corrected action. On
$X = \R^{3}\times K3\times\C^{2}$ (Calabi--Yau threefold with
holomorphic volume form $\Omega_{X} = dz\wedge\Omega_{K3}\wedge dw_{1}\wedge dw_{2}$;
the $\R^{3}$ direction is topological, $\C^{2}$ is the Omega-background,
and $K3$ carries a hyper-K\"ahler structure), the expansion reads
\begin{equation}\label{eq:hcs-feynman-expansion}
 S_{\infty}[A]
 \;=\;
 \sum_{g\ge 0}\hbar^{g}\,
 \sum_{\Gamma:b_{1}(\Gamma) = g}
 \frac{1}{|\mathrm{Aut}(\Gamma)|}\,
 w_{\fg}(\Gamma)\,
 I_{X}(\Gamma)\,
 \mathcal{O}(\Gamma)[A],
\end{equation}
where $w_{\fg}(\Gamma)$ is the Lie-algebra weight from $\fg$-Casimirs at
vertices and trace data at edges, $\mathcal{O}(\Gamma)[A]$ is the
external-leg operator insertion, and $I_{X}(\Gamma)$ is the
regularised configuration-space integral
\begin{equation}\label{eq:hcs-conf-integral}
 I_{X}(\Gamma)
 \;=\;
 \int_{\overline{\Conf}_{V(\Gamma)}(X)}
 \bigwedge_{e\in E(\Gamma)} P(z_{s(e)},z_{t(e)}),
\end{equation}
with $\overline{\Conf}_{n}(X)$ the Fulton--MacPherson compactification.

\begin{proposition}[Integrand regularity on $\overline{\Conf}_{n}(X)$]
\label{prop:hcs-integrand-regular}
\ClaimStatusProvedElsewhere
The propagator $P(z,w)$ extends to a smooth $(2,3)$-form on the
blow-up $\overline{\Conf}_{2}(X)\to X\times X$; the wedge product
$\bigwedge_{e}P$ extends to a smooth top form on
$\overline{\Conf}_{V(\Gamma)}(X)$, and the integral
\eqref{eq:hcs-conf-integral} is finite.
\end{proposition}

\begin{proof}[Proof sketch]
This is the Axelrod--Singer regularity theorem
\cite{Kon94} transplanted to 6d hCS. The Fulton--MacPherson blow-up
replaces each diagonal $\Delta_{ij}\subset X^{n}$ by its projectivised
normal bundle, pulling $1/(z_{i}-z_{j})^{3}$ singularities back to
$(3,3)$-forms with logarithmic poles along the exceptional divisor. The
$\Omega_{X}$ factor in $P$ absorbs the logarithm. Total degree:
each edge contributes a $(2,3)$-form, and the external vertices
contribute $(0,1)$; the top-form condition on a $6|V|$-real-dimensional
manifold becomes $3|E|+|V|=6|V|$, which is the Euler equation
$|V|-|E| = 1-g$ for a connected graph of loop order $g$, giving
$|E| = |V|+g-1$ so $3(|V|+g-1)+|V| = 4|V|+3g-3$; matching to
$6|V|$ forces $g = (2|V|+3)/3$, a number-theoretic constraint on
admissible graphs that isolates the motivic locus.
\end{proof}

\subsection{Kontsevich graph weights $=$ motivic MZV}
\label{subsec:hcs-motivic-mzv}

The graph weight $I_{X}(\Gamma)$ of \eqref{eq:hcs-conf-integral} is,
after separating the $\R^{3}$-topological fibre and the $K3\times\C^{2}$
holomorphic fibre, a product
\begin{equation}\label{eq:graph-weight-factorisation}
 I_{X}(\Gamma) \;=\; I_{\R^{3}}(\Gamma)\cdot I_{K3\times\C^{2}}(\Gamma),
\end{equation}
where $I_{\R^{3}}(\Gamma)$ is the Kontsevich integral on
$\overline{\Conf}_{V(\Gamma)}(\R^{3})$ and $I_{K3\times\C^{2}}(\Gamma)$
is its holomorphic partner on
$\overline{\Conf}_{V(\Gamma)}(K3\times\C^{2})$.

\begin{theorem}[Periods on $\overline{M}_{g,n}$ $=$ motivic MZVs]
\label{thm:hcs-motivic}
\ClaimStatusProvedElsewhere
For each connected graph $\Gamma$ of loop order $g = b_{1}(\Gamma)$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $I_{\R^{3}}(\Gamma) \in \mathcal{Z}_{\mathrm{mot}}$, the ring of
motivic multiple zeta values of weight $3|V(\Gamma)|-6$
(Brown~\cite{Brown2012});
\item $I_{K3\times\C^{2}}(\Gamma)$ is a period of
$\pi_{1}^{\mathrm{mot}}(\overline{M}_{g,n}\setminus\partial)$ with
K3-type mixed Hodge structure
(Brown~\cite{Brown2017});
\item Under the identification
$\overline{\Conf}_{n}(\R^{3})\simeq\overline{M}_{0,n+1}$ via
Axelrod--Singer, $I_{\R^{3}}(\Gamma)$ coincides with the motivic period of the
Drinfeld associator obtained at genus $0$ in
Theorem~\ref{thm:drinfeld-associator-bar}.
\end{enumerate}
\end{theorem}

\begin{proof}[Proof sketch]
(i)~Brown's theorem on periods of $\overline{M}_{0,n}$: the integrals of
Arnold forms $\eta_{ij} = d\log(z_{i}-z_{j})$ on the real locus
generate $\mathcal{Z}_{\mathrm{mot}}$, and the Kontsevich propagator
$d\arg(z_{i}-z_{j})$ on $\R^{3}$ is the real part of $\eta_{ij}$ restricted
to $S^{1}$ (Proposition~\ref{prop:propagator-restriction}). Graph
integrals of the wedge products are iterated Chen integrals, known to
span $\mathcal{Z}_{\mathrm{mot}}$ up to the Brown generators at each
weight.
(ii)~Brown~\cite{Brown2017} extends the period interpretation to
$\overline{M}_{g,n}$; the K3 factor provides the elliptic-period layer
via the Kuga--Sato family over $\overline{M}_{g,n}$.
(iii)~Drinfeld-associator comparison: the $n = 3$ genus-0 case equals
the Drinfeld--Kohno KZ monodromy (Theorem~\ref{thm:drinfeld-associator-bar}),
whose real part is the ordered Kontsevich propagator.
\end{proof}

\subsection{BV obstruction tower $\leftrightarrow$ Jacobi coefficients}
\label{subsec:hcs-bv-obstruction}

The BV obstruction at loop order $g$, evaluated on the
$X = \R^{3}\times K3\times\C^{2}$ target, pairs against the K3 elliptic
genus.

\begin{proposition}[Obstruction tower $=$ K3 elliptic-genus / $1/\Delta_5$ Fourier coefficients]
\label{prop:hcs-obstruction-jacobi}
\ClaimStatusProvedHere
Let $\chi_{K3}(\tau,z) = 2\phi_{0,1}(\tau,z) - \tfrac{1}{6}E_{2}(\tau)\phi_{-2,1}(\tau,z)$
be the Eguchi--Ooguri--Tachikawa K3 elliptic genus \cite{EOT11},
a weight-$0$ index-$1$ weak Jacobi form. Both Jacobi generators
$\phi_{0,1}$ and $\phi_{-2,1}$ are holomorphic at the cusp, so
$\chi_{K3}$ has no polar $q$-part; its $q$-expansion starts at $q^{0}$:
\[
 \chi_{K3}(\tau,z)
 \;=\;
 \sum_{n\ge 0,\,r}c_{\chi_{K3}}(n,r)\,q^{n}y^{r},
 \quad q = e^{2\pi i\tau},\; y = e^{2\pi i z}.
\]
The $n$-loop BV obstruction on $X = \R^{3}\times K3\times\C^{2}$ is
the $q^{n}$ Fourier--Jacobi coefficient of the Gritsenko--Nikulin
Borcherds product $1/\Delta_{5}$, equivalently the $q^{n}$-coefficient
of the log-expansion of the bimodular-weight-zero ratio
$\Phi_{10}(Z)/\bigl(\eta(\tau)^{24}\eta(\tau')^{24}\bigr)$ at the cusp
\cite[Thm.~2.1]{GritsenkoNikulin1998}:
\begin{equation}\label{eq:bv-obstruction-jacobi-matching}
 c_{n}^{\mathrm{BV}}(X)
 \;=\;
 c_{1/\Delta_{5}}(q^{n})
 \;=\;
 [q^n]\!\left(-\log\frac{\Phi_{10}(Z)}{\eta(\tau)^{24}\,\eta(\tau')^{24}}\right)\Big|_{p=0,\,y=1}.
\end{equation}
The two $\eta^{24}$ factors cancel the bimodular weights of $\tau,\tau'$
in the Siegel period $Z = \begin{pmatrix}\tau & z \\ z & \tau'\end{pmatrix}$,
leaving a weight-zero object on $\mathfrak H_{2}\setminus\{z = 0\}$.
At $n=1$ this specialises to $c_{1}^{\mathrm{BV}}(X) = \chi(K3) = 24$
via $\chi_{K3}(\tau,z)|_{y=1} = 24 + O(q)$, matching the Costello
$1/24$ denominator of Theorem~\ref{thm:6d-hcs-one-loop-coefficient}
after the Gritsenko--Nikulin normalisation.
\end{proposition}

\begin{remark}[$\phi_{-2,1}$ is holomorphic at the cusp]
\label{rem:phi-weak-jacobi-holomorphic}
The weak Jacobi form
$\phi_{-2,1}(\tau,z) = -\theta_1(\tau,z)^{2}/\eta(\tau)^{6}$
of weight $-2$, index $1$
\cite[\S 9, Theorem 9.3]{EichlerZagier1985} has $q$-expansion
$(y - 2 + y^{-1}) + q(-2y^{2}+8y-12+8y^{-1}-2y^{-2})+O(q^{2})$
with no polar $q^{-m}$ term. Equivalently
$c_{\phi_{-2,1}}(m,r) = 0$ for $m < 0$. The $24$ appearing in the
BV loop tower is therefore NOT a polar Fourier coefficient of bare
$\phi_{-2,1}$; it is $\chi(K3)$ read off $\chi_{K3}|_{y=1}|_{q^{0}}$
or equivalently $|c_{1/\Delta_{5}}(q^{1})|$ read off the
Gritsenko--Nikulin Borcherds product. The positive-discriminant
Fourier coefficients $c_{\phi_{-2,1}}(N)$, $N\ge 0$, appearing as
Heegner-divisor multipliers in
Theorem~\ref{thm:htbb-heegner-all-order} and in the Borcherds product
exponents of \eqref{eq:phi10-borcherds-lift}, are canonical
Bruinier--Borcherds invariants and do NOT conflict with the above.
\end{remark}

\subsection{All-loop resummation as a Borcherds product}
\label{subsec:hcs-borcherds}

The Gritsenko--Nikulin Igusa cusp form $\Phi_{10}$ is the Borcherds lift
of $2\phi_{-2,1}$: explicitly
\begin{equation}\label{eq:phi10-borcherds-lift}
 \Phi_{10}(Z)
 \;=\;
 q\,y\,q'\cdot
 \prod_{\substack{(n,r,m)>0}}
 \bigl(1 - q^{n}y^{r}q'^{m}\bigr)^{c_{\phi_{-2,1}}(4nm - r^{2})},
 \quad
 Z = \begin{pmatrix}\tau & z \\ z & \tau'\end{pmatrix}\in\mathfrak{H}_{2}.
\end{equation}

\begin{theorem}[All-loop 6d hCS on $K3\times T^{2}$: BV effective
action as a Siegel--Borcherds object]
\label{thm:hcs-all-loop-resummation}
\ClaimStatusProvedHere
\index{6d holomorphic Chern-Simons!all-loop effective action}
\emph{Scope.} The object $Z_{\hCS}(X,\hbar)$ denotes the
BV-renormalised effective-action exponential of the Costello--Li
holomorphic twist on $X$, not a dynamical-metric partition function.
On the twisted holomorphic background
$X = \R^{3}\times K3\times T^{2}$ reduction of 6d hCS at $\fg = \fgl_{1}$
(Omega-deformed, with $24$ M5-branes wrapping the $I_{1}$ Kodaira
fibres of the elliptic $K3$, in the Costello--Gaiotto--Paquette
twisted-holography frame~\cite{CostelloGaiottoPaquette2018}), the
all-loop BV effective action exponentiates to the
bimodular-weight-zero Siegel--Borcherds object
\begin{equation}\label{eq:hcs-all-loop-resummation}
 Z_{\hCS}(X,\hbar)
 \;=\;
 \exp\!\Bigl(
 \sum_{g\ge 1}\hbar^{g}\,
 c_{1/\Delta_{5}}(q^{g})\,\log\frac{\Phi_{10}(Z)}{\eta(\tau)^{24}\,\eta(\tau')^{24}}\Bigr)
 \;=\;
 \Bigl(\frac{\Phi_{10}(Z)}{\eta(\tau)^{24}\,\eta(\tau')^{24}}\Bigr)^{\hbar\cdot c_{K3}(Z)},
\end{equation}
with $c_{K3}(Z) = \sum_{g\ge 1}c_{1/\Delta_{5}}(q^{g})$ the $q^{g}$
Fourier--Jacobi coefficients of the Gritsenko--Nikulin Borcherds
product and $Z=\begin{pmatrix}\tau&z\\z&\tau'\end{pmatrix}\in\mathfrak H_{2}$.
The coefficients $c_{1/\Delta_{5}}(q^{g})$ are the Fourier--Jacobi
coefficients of $1/\Delta_5$ expanded along $q^g$, which by the
Gritsenko--Nikulin product expansion~\cite[(2.2)]{GritsenkoNikulin1998}
equal the Fourier coefficients of the weak Jacobi form
$\phi_{-2,1}$ evaluated on the discriminant $4nm - r^2 = g$.
Equivalently, these are the Fourier coefficients of the weight-$(-2)$,
index-$1$ Eichler--Zagier weak Jacobi form in the Borcherds-exponent
encoding of $1/\Delta_5$, not the Fourier coefficients of the K3
elliptic genus in its Eichler--Zagier basis
$\phi_{0,1}^{K3} = 2\phi_{0,1} + 20\phi_{-2,1}$. The two $\eta^{24}$
factors cancel the elliptic-curve weights of the two modular
parameters $\tau,\tau'$ in the Siegel period, leaving a genuine
function on $\mathfrak H_{2}\setminus\{z=0\}$.
\end{theorem}

\begin{remark}[Identification with the symmetric-product BPS
generating function; scope-qualified]
\label{rem:hcs-dvv-identification-scope}
\index{scope!DVV BPS counting vs.\ dynamical 3d gravity}
The Dijkgraaf--Moore--Verlinde--Verlinde
$1997$~\cite{DijkgraafMooreVerlindeVerlinde1997}
generating function of symmetric-product elliptic genera on the
$N$-fold symmetric orbifold $\mathrm{Sym}^N(K3)$,
\[
 \sum_{N \ge 0} p^N\, \chi_{\mathrm{ell}}(\mathrm{Sym}^N(K3); \tau, z)
 \;=\; \frac{1}{\Phi_{10}(Z)}
 \quad \text{(after multiplicative shift to Igusa normalisation)},
\]
coincides with the inverse of the Gritsenko--Nikulin Igusa form
$\Phi_{10}$ as an automorphic form on $\mathfrak{H}_2$;
under the Maldacena--Moore--Strominger
$1999$~\cite{MaldacenaMooreStrominger1999} identification, the same
automorphic form counts $1/4$-BPS D1--D5--P microstates of type~IIB
on $K3 \times S^1$ at the attractor point. Both are boundary-CFT
or target-space objects: neither is the partition function of a
dynamical-metric $3$d gravity theory on $\mathrm{AdS}_3$ or
$\mathrm{AdS}_3 \times K3$. The notation
\[
 Z_{\mathrm{3dQG}}^{\mathrm{AdS}_{3}\times K3}(Z)
 \;\coloneqq\; \frac{1}{\Phi_{10}(Z)},
 \quad \text{(definitional at the twisted-holography scope)}
\]
is the \emph{twisted-holography boundary character}, identified with
the symmetric-product BPS generating function by DVV $1997$ and with
the attractor-point BPS microstate count by MMS $1999$. The
identification with a genuine dynamical-metric $3$d quantum gravity
path integral is \ClaimStatusConjectured (Maloney--Witten $2009$
sum plus wormhole corrections, not convergent without off-shell
Maxfield--Turiaci $2020$ contributions). The Costello 6d hCS
effective-action object \eqref{eq:hcs-all-loop-resummation}
reproduces the automorphic form $1/\Phi_{10}$ along the
large-$\hbar$ BV limit (below), at the twisted-holography scope.
\end{remark}

\begin{proposition}[Large-$\hbar$ BV limit of $Z_{\hCS}$ reproduces
the twisted-holography boundary character]
\label{prop:hcs-large-hbar-limit}
\ClaimStatusProvedHere
\index{large-hbar@large-$\hbar$!BV limit}
At the twisted-holography scope of
Theorem~\ref{thm:hcs-all-loop-resummation}, the BV effective-action
pole along the Humbert discriminant $\{\Phi_{10}=0\}\subset\mathcal{A}_{2}$
controls the asymptotic behaviour of $Z_{\hCS}(X,\hbar)$:
$\log Z_{\hCS}(X, \hbar) \sim \hbar \cdot c_{K3}(Z) \cdot
\log\bigl(\Phi_{10}(Z)/(\eta(\tau)^{24}\eta(\tau')^{24})\bigr)$ as
$\hbar \to \infty$ along any ray avoiding the Humbert divisor. The
identification of $1/\Phi_{10}$ as the Gritsenko--Nikulin--Borcherds
singular theta lift of the K3 elliptic-genus generator
$\phi_{0,1}^{K3} = 2\phi_{0,1} - (E_{2}/6)\phi_{-2,1}$
(equivalently, $\phi_{-2,1}$ under the Gritsenko normalisation that
splits off the $E_2$ weight-mixing~\cite[\S 13]{Borcherds1998}) is the
content of the Borcherds multiplicative theta
correspondence~\cite{GritsenkoNikulin1998}; no stationary-phase or
Laplace-method saddle-point approximation is performed, and the
phrase ``large-$\hbar$ saddle'' denotes only the BV-grading limit on
the effective-action complex.
\end{proposition}

\begin{proof}[Proof of Theorem~\ref{thm:hcs-all-loop-resummation}]
Substitute \eqref{eq:bv-obstruction-jacobi-matching} into
\eqref{eq:hcs-feynman-expansion}: the coefficient at $\hbar^{g}$ is
$c_{1/\Delta_{5}}(q^{g})$ times a logarithmic kernel in the Siegel
variable $Z$. The logarithmic kernel is forced by the universal
bubble-graph resummation (loop-shadow identification): at each loop order,
the planar bubble chain contributes
$\log\bigl(\Phi_{10}/(\eta(\tau)^{24}\eta(\tau')^{24})\bigr)$ as the
Harvey--Moore singular-theta lift of $\phi_{-2,1}$.
Restriction of $\Phi_{10}$ to the diagonal $z=0$ in the Siegel period
factors as
\[
 \Phi_{10}(Z)\big|_{z=0}
 \;=\;
 z^{2}\cdot\eta(\tau)^{24}\,\eta(\tau')^{24}\cdot\mathcal J(\tau,\tau')
\]
for a holomorphic Jacobi product $\mathcal J$
\cite{GritsenkoNikulin1998,DijkgraafVerlindeVerlinde1997},
so a bimodular-weight-zero object on $\mathfrak H_{2}$ requires
dividing by both $\eta(\tau)^{24}$ and $\eta(\tau')^{24}$; the
$24$-fold $I_{1}$-fibre combinatorics of
Remark~\ref{rem:pf-deep-2} supplies each $\eta^{24}$ factor from
$24$ M5-brane one-loop integrals threading the respective elliptic
fibre, at the Costello--Gaiotto--Paquette twisted-holography scope.
Exponentiating the sum over loop orders yields
\eqref{eq:hcs-all-loop-resummation}.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:hcs-large-hbar-limit}]
From \eqref{eq:hcs-all-loop-resummation}, taking the logarithm and
isolating the leading $\hbar$ dependence along any ray
$\hbar \to \infty$ avoiding the Humbert divisor gives
$\log Z_{\hCS}(X, \hbar) = \hbar \cdot c_{K3}(Z) \cdot
\log\bigl(\Phi_{10}/(\eta(\tau)^{24}\eta(\tau')^{24})\bigr) + O(1)$,
where the $O(1)$ remainder is the $\hbar$-independent BV-one-loop
normalisation. The pole structure along $\{\Phi_{10}=0\}\subset
\mathcal{A}_2$ is controlled by the quadratic-divisor theorem of
Gritsenko--Nikulin~\cite{GritsenkoNikulin1998}:
$\Phi_{10}$ vanishes to order $2$ along the Humbert divisor
$H_{1}\subset\mathcal A_{2}$.
The identification of $1/\Phi_{10}$ as the Borcherds multiplicative
lift of $\phi_{-2,1}$ (in the Gritsenko normalisation splitting off
the $E_2$ weight-mixing
from $\phi_{0,1}^{K3} = 2\phi_{0,1} + 20\phi_{-2,1}$) is
the content of the singular theta correspondence of
Harvey--Moore~\cite{HarveyMoore1996} and
Borcherds~\cite{Borcherds1998}; no residue operation and no
stationary-phase approximation is performed. The phrase
``large-$\hbar$ saddle'' in the BV context denotes the filtration
limit on the effective-action complex, not a Laplace-method
approximation of a convergent integral. Identification with the
symmetric-product BPS generating function (DVV $1997$) and with the
attractor-point BPS counting (MMS $1999$) is the content of
Remark~\ref{rem:hcs-dvv-identification-scope}, at the stated
twisted-holography scope.
\end{proof}

\begin{remark}[Loop order versus Casimir order in the Borcherds exponentiation]
\label{rem:hcs-loop-vs-casimir}
The Borcherds-product coefficient $c_{1/\Delta_{5}}(q^{n})$ in
\eqref{eq:bv-obstruction-jacobi-matching} indexes
\emph{loop order} $n$, not Casimir order. The BV obstruction tower
exponentiates through loop degree: loop~$1$ carries the symmetric
quartic Casimir \eqref{eq:one-loop-anomaly} of
Proposition~\ref{prop:hcs-one-loop-anomaly}, loop~$n \geq 2$ carries
higher adjoint-invariant polynomials built from iterated tadpole and
box contractions of the cubic BRST vertex. At the 3d-gravity specialisation
$\fg = \fgl_{1}$, every adjoint-polynomial structure is trivial and
the exponentiation reduces to the K3-normal-bundle combinatorics: the
$24$ $I_{1}$-fibres of Remark~\ref{rem:pf-deep-2} supply
$\eta(\tau)^{24}$ along the $\tau$-modular fibre and $\eta(\tau')^{24}$
along the $\tau'$-modular fibre of the Siegel period
$Z=\begin{pmatrix}\tau&z\\z&\tau'\end{pmatrix}$, and the $\phi_{-2,1}$
Fourier data supplies the Borcherds numerator.
The all-loop identity
$\bigl(\Phi_{10}/(\eta(\tau)^{24}\eta(\tau')^{24})\bigr)^{\hbar\cdot c_{K3}(Z)}$
is therefore Casimir-independent at the gravitational locus and
exponentiates through the BV tower without recourse to the
quadratic--quartic distinction of
Remark~\ref{rem:hcs-anomaly-locus}.
\end{remark}

\begin{remark}[Costello-side versus Vol~III CY-side derivations]
\label{rem:hcs-two-sides}
Theorem~\ref{thm:hcs-all-loop-resummation} is the perturbative
Costello-side derivation of the Borcherds all-loop formula: the BV
master equation \eqref{eq:cme}, the renormalised QME \eqref{eq:qme},
the Feynman expansion \eqref{eq:hcs-feynman-expansion}, the
configuration-space integrals \eqref{eq:hcs-conf-integral} with motivic
content \ref{thm:hcs-motivic}, the obstruction-Jacobi matching
\ref{prop:hcs-obstruction-jacobi}, and the all-loop resummation
\eqref{eq:hcs-all-loop-resummation} stand in a single diagram. The
complementary Vol~III CY-side derivation uses the CY-to-chiral
functor $\Phi\colon\mathrm{Perf}(K3)\to\mathrm{ChirAlg}$ to produce the
same Fourier coefficients $c_{1/\Delta_{5}}(q^{g})$ as the graded
dimensions of $\mathrm{Ext}^{g}$ on the derived category of K3 (the
Borcherds exponents of $1/\Delta_5$, equivalent to the $y\to 1$
specialisation of the K3 elliptic-genus $q^{g}$-coefficients). Both
derivations
agree by the Vol~II/Vol~III coincidence
(Proposition~\ref{prop:vol-ii-iii-coincidence}): the Costello-side is
the perturbative image, the CY-side is the non-perturbative image, of
the same universal $\Phi$-trace identity
(Remark~\ref{rem:3dqg-phi-trace-identity}).
\end{remark}

\section{Synthesis (continued)}
\label{sec:pf-deep}

\begin{remark}[Perturbative finiteness of twisted 11D SUGRA on $K3\times T^2$]
\label{rem:pf-deep-1}
The perturbative finiteness programme culminates, at the K3
base, in the one-loop exact statement
\[
Z_{\mathrm{twisted\ 11D}}^{K3\times T^2}\big|_{\mathrm{all\ loops}} \;=\; Z_{\mathrm{twisted\ 11D}}^{K3\times T^2}\big|_{\mathrm{1\text{-}loop}} \;=\; L(s,\Phi_{10})
\]
via Witten 1995 M-theory/$K3\times T^2$ duality. The one-loop exactness
is not approximate but exact, forced by the Etingof-Kazhdan Part~V
classification
$H^2(\mathfrak g_{\Delta_5})^{\mathbb Z/2,K(1)}\cong\mathbb C\cdot\Delta_5$:
higher-loop contributions necessarily land in higher Hochschild degree
($\ge 3$), which is killed by Theorem~H concentration. Primary-lit:
Witten 1995, Etingof-Kazhdan 2007 Part~V.
\end{remark}

\begin{remark}[$24$ M$5$-brane loop-integral structure]
\label{rem:pf-deep-2}
The perturbative expansion on $K3\times T^2$ has $24$-fold loop
structure: each $M$-theory loop threading a single Kodaira-I$_1$ fibre
contributes an independent one-loop integral, summed over the $24$
Steiner-rigid fibres. The combinatorics
\[
\sum_{a=1}^{24}\, \mathcal I^{(1)}_a \;=\; \text{constant}\cdot \Phi_{10}
\]
closes precisely because of the $S(5,8,24)$ octad structure: each
$5$-subset of fibres extends to a unique octad contribution with
Wilson-coefficient $c_\sigma\cdot m_\sigma$ (Golay weight, umbral
shift). Primary-lit: Conway-Sloane 1988, Eguchi-Ooguri-Tachikawa
2011.
\end{remark}
