% Status and semantic-level disputes are settled by the concordance (concordance.tex).
% This file is the master chapter for the twisted holography / quantum gravity
% programme.  It assumes the theorem environments and typography of main.tex.

\chapter{Twisted Holography and Quantum Gravity}
% label removed: chap:twisted-holography-quantum-gravity
\index{twisted holography|textbf}
\index{quantum gravity!modular Koszul approach|textbf}
\index{holographic modular Koszul datum!quantum gravity programme|textbf}

% ----------------------------------------------------------------------
% Local macros: provided only if absent from the ambient manuscript.
% ----------------------------------------------------------------------
\providecommand{\Bbbk}{\mathbb{k}}
\providecommand{\HS}{\operatorname{HS}}
\providecommand{\wt}{\operatorname{wt}}
\providecommand{\CE}{\operatorname{CE}}
\providecommand{\End}{\operatorname{End}}
\providecommand{\Hom}{\operatorname{Hom}}
\providecommand{\Sym}{\operatorname{Sym}}
\providecommand{\id}{\mathrm{id}}
\providecommand{\Tr}{\operatorname{Tr}}
\providecommand{\Det}{\operatorname{Det}}
\providecommand{\Aut}{\operatorname{Aut}}
\providecommand{\Fred}{\operatorname{Fred}}
\providecommand{\Spec}{\operatorname{Spec}}
\providecommand{\Res}{\operatorname{Res}}
\providecommand{\rank}{\operatorname{rank}}
\providecommand{\ad}{\operatorname{ad}}
\providecommand{\Ainf}{\mathsf{A}_{\infty}}
\providecommand{\Linf}{L_\infty}
\providecommand{\PV}{\operatorname{PV}}
\providecommand{\RHom}{\operatorname{RHom}}
\providecommand{\BBar}{\operatorname{Bar}}
\providecommand{\Cobar}{\operatorname{\Omega}}
\providecommand{\barB}{\overline{B}}
\providecommand{\Diff}{\operatorname{Diff}}
\providecommand{\tr}{\operatorname{tr}}
\providecommand{\Zder}{\operatorname{Z}_{\mathrm{der}}}
\providecommand{\Abulk}{A_{\mathrm{bulk}}}
\providecommand{\Bbound}{B_{\partial}}
\providecommand{\sn}{\mathrm{SN}}
\providecommand{\hSym}{\widehat{\Sym}}
\providecommand{\lines}{\mathsf{Lines}}
\providecommand{\ModEnv}{\operatorname{ModEnv}}
\providecommand{\ohat}{\widehat{\otimes}}
\providecommand{\Mbar}{\overline{\mathcal M}}
\providecommand{\Perf}{\operatorname{Perf}}
\providecommand{\dCrit}{\operatorname{dCrit}}
\providecommand{\gr}{\operatorname{gr}}
\providecommand{\coker}{\operatorname{coker}}
\providecommand{\Spf}{\operatorname{Spf}}

% ======================================================================
%
%  SECTION 1: THE HOLOGRAPHIC MODULAR KOSZUL DATUM
%
% ======================================================================

\section{The holographic modular Koszul datum}
% label removed: sec:thqg-holographic-datum

\subsection{Standing hypotheses}
% label removed: subsec:thqg-standing

\begin{definition}[Standing hypotheses]
% label removed: def:thqg-standing-hypotheses
A \emph{gravitational input} is a quadruple $(\cA, X, \langle\cdot,\cdot\rangle, k)$ where:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\cA$ is a chiral algebra on a smooth projective curve $X$, chirally Koszul
  in the sense of Theorem~\ref*{V1-thm:koszul-equivalences-meta} (any of the twelve
  equivalent characterizations);
\item $\cA$ is cyclically admissible
  (Definition~\ref{def:cyclically-admissible}): conformal grading, exhaustive
  filtration, bounded poles, invariant pairing $\langle\cdot,\cdot\rangle$;
\item the HS-sewing criterion holds: polynomial OPE growth and
  subexponential sector growth (Theorem~\ref{thm:general-hs-sewing});
\item the level $k$ avoids the critical value (for $\widehat{\mathfrak{g}}$:
  $k \ne -h^\vee$; for universal $\mathcal{W}$-algebras: generic level).
\end{enumerate}
All results below assume these hypotheses unless explicitly relaxed.
% label removed: fwk:thqg-standing-hypotheses%
\end{definition}

\begin{remark}[Scope of the hypotheses]
% label removed: rem:thqg-scope
The four conditions are satisfied by:
\begin{itemize}
\item all affine Kac--Moody algebras $V_k(\mathfrak{g})$ at non-critical level;
\item all principal $\mathcal{W}$-algebras $\mathcal{W}_k(\mathfrak{g}, f_{\mathrm{prin}})$ at generic $k$;
\item all free-field algebras (Heisenberg, $\beta\gamma$, $bc$, lattice);
\item the Virasoro algebra at all central charges $c$;
\item hook-type $\mathcal{W}$-algebras in type~$A$ (Fehily, Creutzig--Linshaw--Nakatsuka--Sato).
\end{itemize}
The critical exclusion in~(iv) removes the locus where the Sugawara construction is undefined.
The HS-sewing criterion in~(iii) is automatic for the standard landscape
(Volume~I, Theorem~\ref{thm:general-hs-sewing}).
\end{remark}


\subsection{The Swiss-cheese convolution algebra}
% label removed: subsec:thqg-swiss-cheese-conv

Fix a gravitational input $(\cA, X, \langle\cdot,\cdot\rangle, k)$.
The holomorphic-topological geometry on $\C \times \R_{\ge 0}$ produces
a Swiss-cheese operad $\mathsf{SC}^{\mathrm{ch,top}}$
(Chapter~\ref{chap:ht-bulk-boundary-line}).
Its Koszul dual cooperad $(\mathsf{SC}^{\mathrm{ch,top}})^{!}$
determines a convolution dg Lie algebra.

\begin{definition}[Swiss-cheese convolution algebra]
% label removed: def:thqg-swiss-cheese-conv
\index{Swiss-cheese convolution algebra}
The \emph{Swiss-cheese convolution algebra} of $\cA$ is
\begin{equation}% label removed: eq:thqg-gSC
\mathfrak{g}^{\mathrm{SC}}_\cA
\;:=\;
\Convstr\bigl(
(\mathsf{SC}^{\mathrm{ch,top}})^{!},\;
\End_\cA
\bigr),
\end{equation}
the strict convolution dg Lie algebra of the Koszul dual cooperad
evaluated in the endomorphism operad of $\cA$.  Its differential is
the convolution differential $D_\cA$; its bracket is the
operadic composition bracket.
\end{definition}

\begin{proposition}[Factorization of the Swiss-cheese algebra;
\ClaimStatusProvedHere]
% label removed: prop:thqg-gSC-factorization
The Swiss-cheese convolution algebra decomposes as a direct product
\begin{equation}% label removed: eq:thqg-gSC-factorization
\mathfrak{g}^{\mathrm{SC}}_\cA
\;\cong\;
\gAmod \;\times\; \mathfrak{g}^{\R}_\cA,
\end{equation}
where:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\gAmod = \Convstr(\mathcal{C}^!_{\mathrm{ch}},
  \mathcal{P}^{\mathrm{ch}})$ is the modular convolution dg Lie
  algebra (Definition~\ref*{V1-def:modular-convolution-dg-lie}),
  controlling the chiral ($\C$) direction;
\item $\mathfrak{g}^{\R}_\cA$ is the topological ($\R$) convolution
  algebra, controlling the $E_1$-coalgebra structure along the
  topological direction.
\end{enumerate}
The two factors commute: $[\gAmod, \mathfrak{g}^{\R}_\cA] = 0$.
\end{proposition}

\begin{proof}
The Swiss-cheese operad factors as a semidirect product of the
chiral operad (governing disk operations in $\C$) and the
associative operad (governing interval operations along $\R$).
The Koszul dual cooperad inherits the same factorization, and the
convolution functor preserves products.
\end{proof}


\subsection{The six components}
% label removed: subsec:thqg-six-components

\begin{definition}[Holographic modular Koszul datum]
% label removed: def:thqg-holographic-datum
\index{holographic modular Koszul datum|textbf}
Given a gravitational input $(\cA, X, \langle\cdot,\cdot\rangle, k)$, the
\emph{holographic modular Koszul datum} is the sextuple
\begin{equation}% label removed: eq:thqg-holographic-datum
\mathcal{H}(\cA) \;=\; \bigl(\cA,\;\cA^!,\;\mathcal{C},\;r(z),\;
\Theta_\cA,\;\nabla^{\mathrm{hol}}\bigr),
\end{equation}
whose six components are defined as follows.
\end{definition}

\begin{enumerate}[label=\textbf{Component (\alph*):}, leftmargin=4.5em, itemsep=1.5ex]

\item \textbf{The boundary chiral algebra $\cA$.}
% label removed: item:thqg-component-a
This is the input datum: a chirally Koszul, cyclically admissible
chiral algebra on $X$.  In the holographic context, $\cA$ is the
algebra of boundary local operators for a 3d holomorphic-topological
theory on $\C \times \R_{\ge 0}$.  Its OPE data are the initial
conditions for the entire holographic system.

\item \textbf{The Koszul dual algebra $\cA^!$.}
% label removed: item:thqg-component-b
\index{Koszul dual!holographic}
The Koszul dual is
\begin{equation}% label removed: eq:thqg-koszul-dual
\cA^! \;:=\; \bigl(H^\bullet(B(\cA))\bigr)^\vee,
\end{equation}
the linear dual of the bar cohomology.  The bar complex $B(\cA)$ is
the cofree coalgebra on the desuspended generators of $\cA$, with
differential encoding the OPE.  The Verdier duality converts the
coalgebra structure on $H^\bullet(B(\cA))$ into an algebra structure
on $\cA^!$.

The Koszul dual is \emph{not} the cobar construction: $\Omega(B(\cA))
\simeq \cA$ is bar-cobar inversion (Theorem~B), while $\cA^!$ is
obtained by the composite $B \to H^\bullet \to (-)^\vee$.

\begin{center}
\renewcommand{\arraystretch}{1.2}
\small
\begin{tabular}{lll}
\textbf{Family} & $\cA$ & $\cA^!$ \\
\hline
Heisenberg & $\mathcal{H}$ & Free boson (not self-dual) \\
Affine $\widehat{\mathfrak{g}}_k$ & $V_k(\mathfrak{g})$
  & $V_{-k-2h^\vee}(\mathfrak{g})$ \\
Virasoro & $\mathrm{Vir}_c$ & $\mathrm{Vir}_{26-c}$ \\
$\beta\gamma$ & $\beta\gamma$ & $bc$ \\
Lattice $V_\Lambda$ & $V_\Lambda$ & $V_{\Lambda^*}$
\end{tabular}
\end{center}

\item \textbf{The line-operator category $\mathcal{C}$.}
% label removed: item:thqg-component-c
\index{line-operator category!holographic}
The category of line operators along $\R$ is the module category of
the Koszul dual:
\begin{equation}% label removed: eq:thqg-line-category
\mathcal{C} \;\simeq\; \cA^!\text{-}\mathsf{mod}.
\end{equation}
This is a dg category with compact generator given by $\cA^!$ itself.
The identification follows from the line-operator theorem
(Theorem~\ref{thm:lines_as_modules}): the $E_1$-coalgebra structure
along $\R$ produces a monoidal category whose modules are precisely
line operators, and the perturbative construction of Dimofte--Niu--Py
identifies this monoidal category with $\cA^!$-modules.

\item \textbf{The collision residue $r(z)$.}
% label removed: item:thqg-component-d
\index{collision residue|textbf}
\index{classical Yang--Baxter equation!from collision residue}
The collision residue is the genus-$0$, arity-$2$ projection of the
universal MC element:
\begin{equation}% label removed: eq:thqg-collision-residue
r(z) \;:=\; \Res^{\mathrm{coll}}_{0,2}(\Theta_\cA)
\;\in\;
\cA^! \ohat \cA^!\bigl[\!\bigl[z^{-1}, z\bigr]\!\bigr].
\end{equation}
The notation $\Res^{\mathrm{coll}}_{0,2}$ denotes the residue of the
MC element at the codimension-$1$ boundary stratum of $\overline{C}_2(X)$
where the two points collide.  The spectral parameter $z$ is the
relative coordinate of the two insertions.

The collision residue satisfies the classical Yang--Baxter equation:
\begin{equation}% label removed: eq:thqg-cybe
[r_{12}(z_1-z_2),\, r_{13}(z_1-z_3)]
+ [r_{12}(z_1-z_2),\, r_{23}(z_2-z_3)]
+ [r_{13}(z_1-z_3),\, r_{23}(z_2-z_3)]
= 0.
\end{equation}
This is the genus-$0$, arity-$3$ MC equation, evaluated on the
codimension-$2$ boundary of $\overline{C}_3(X)$.  The three terms
correspond to the three boundary strata where pairs of points
collide, and the vanishing is the Arnold relation.

\item \textbf{The universal MC element $\Theta_\cA$.}
% label removed: item:thqg-component-e
\index{Maurer--Cartan element!universal|textbf}
The bar-intrinsic MC element
(Volume~I, Theorem~\ref*{V1-thm:mc2-bar-intrinsic}) is
\begin{equation}% label removed: eq:thqg-theta
\Theta_\cA \;:=\; D_\cA - d_0
\;\in\;
\MC\bigl(\gAmod\bigr),
\end{equation}
where $D_\cA$ is the full bar differential and $d_0$ is the linear
part.  The MC equation
\begin{equation}% label removed: eq:thqg-mc-equation
D_\cA \Theta_\cA + \tfrac{1}{2}[\Theta_\cA, \Theta_\cA] = 0
\end{equation}
holds because $D_\cA^2 = 0$
(Volume~I, Theorem~\ref{thm:convolution-d-squared-zero}).

The element $\Theta_\cA$ decomposes by genus and arity:
\begin{equation}% label removed: eq:thqg-theta-decomposition
\Theta_\cA
= \sum_{g \ge 0} \sum_{r \ge 2} \hbar^g\, \Theta_\cA^{(g,r)},
\end{equation}
where $\Theta_\cA^{(g,r)}$ is the component with loop genus $g$
and arity $r$ (number of inputs in the graph sum).  The finite-order
truncations $\Theta_\cA^{\le r} := \sum_{s=2}^{r}\sum_g
\hbar^g\,\Theta_\cA^{(g,s)}$ are the shadow obstruction tower.

\item \textbf{The shadow connection $\nabla^{\mathrm{hol}}$.}
% label removed: item:thqg-component-f
\index{shadow connection|textbf}
\index{modular shadow connection}
The modular shadow connection is
\begin{equation}% label removed: eq:thqg-shadow-connection
\nabla^{\mathrm{hol}}_{g,n}
\;:=\; d - \operatorname{Sh}_{g,n}(\Theta_\cA),
\end{equation}
where $\operatorname{Sh}_{g,n}$ is the shadow projection
(Volume~I, Corollary~\ref*{V1-cor:shadow-extraction}) that evaluates
$\Theta_\cA$ on the genus-$g$, $n$-pointed stratum of the
modular operad.  The shadow connection is a connection on the
moduli space $\Mbar_{g,n}$ valued in the cyclic deformation
complex $\Defcyc^{\mathrm{mod}}(\cA)$.

\end{enumerate}


\subsection{Projection theorem}
% label removed: subsec:thqg-projection

\begin{theorem}[All components are projections of $\Theta_\cA$;
\ClaimStatusProvedHere]
% label removed: thm:thqg-projection
\index{holographic modular Koszul datum!projection theorem}
Every component of the holographic modular Koszul datum
$\mathcal{H}(\cA) = (\cA, \cA^!, \mathcal{C}, r(z),
\Theta_\cA, \nabla^{\mathrm{hol}})$ is determined by $\Theta_\cA$:
\begin{center}
\renewcommand{\arraystretch}{1.4}
\small
\begin{tabular}{lll}
\textbf{Component} & \textbf{Projection} & \textbf{Formula} \\
\hline
$\cA$ & Input & $\cA$ is the input \\[2pt]
$\cA^!$ & $H^\bullet(D_\cA) = H^\bullet(d_0 + \Theta_\cA)$
  & Bar cohomology + Verdier dual \\[2pt]
$\mathcal{C}$ & $\cA^!\text{-}\mathsf{mod}$
  & Module category of $\cA^!$ \\[2pt]
$r(z)$ & $\Res^{\mathrm{coll}}_{0,2}(\Theta_\cA)$
  & Genus-$0$, arity-$2$ boundary residue \\[2pt]
$\Theta_\cA$ & Identity & The MC element itself \\[2pt]
$\nabla^{\mathrm{hol}}_{g,n}$
  & $d - \operatorname{Sh}_{g,n}(\Theta_\cA)$
  & Shadow projection to $(g,n)$
\end{tabular}
\end{center}
The components $\cA^!$, $\mathcal{C}$, $r(z)$, and
$\nabla^{\mathrm{hol}}$ are all functorial in $\cA$ through
$\Theta_\cA$.
\end{theorem}

\begin{proof}
The bar differential is $D_\cA = d_0 + \Theta_\cA$, so:
\begin{enumerate}[label=(\roman*)]
\item $\cA^! = (H^\bullet(B(\cA)))^\vee = (H^\bullet(D_\cA))^\vee$
  is determined by the differential, hence by $\Theta_\cA$.
\item $\mathcal{C} \simeq \cA^!\text{-}\mathsf{mod}$ depends only
  on $\cA^!$.
\item $r(z) = \Res^{\mathrm{coll}}_{0,2}(\Theta_\cA)$ is
  the boundary residue of $\Theta_\cA$ at the collision
  stratum of $\overline{C}_2(X)$, a direct projection.
\item $\nabla^{\mathrm{hol}}_{g,n} = d - \operatorname{Sh}_{g,n}(\Theta_\cA)$
  is the shadow projection, a direct projection.
\end{enumerate}
Functoriality: a quasi-isomorphism $\cA \xrightarrow{\sim} \cA'$ of
chirally Koszul algebras induces a gauge equivalence
$\Theta_\cA \sim \Theta_{\cA'}$ in $\MC(\gAmod)$
(Volume~I, Theorem~\ref{thm:shadow-homotopy-invariance}),
and all projections are gauge-equivariant.
\end{proof}


\subsection{Flatness of the shadow connection}
% label removed: subsec:thqg-flatness

\begin{theorem}[Flatness; \ClaimStatusProvedHere]
% label removed: thm:thqg-flatness
\index{shadow connection!flatness}
The shadow connection $\nabla^{\mathrm{hol}}_{g,n}$ is flat:
\begin{equation}% label removed: eq:thqg-flatness
(\nabla^{\mathrm{hol}}_{g,n})^2 = 0.
\end{equation}
\end{theorem}

\begin{proof}
Expanding:
\begin{align}
(\nabla^{\mathrm{hol}}_{g,n})^2
&= (d - \operatorname{Sh}_{g,n}(\Theta_\cA))^2 \notag \\
&= - d\,\operatorname{Sh}_{g,n}(\Theta_\cA)
   - \operatorname{Sh}_{g,n}(\Theta_\cA)\,d
   + \operatorname{Sh}_{g,n}(\Theta_\cA)^2.
   % label removed: eq:thqg-flatness-expand
\end{align}
The shadow projection $\operatorname{Sh}_{g,n}$ is a Lie algebra
homomorphism on the $(g,n)$-stratum, so:
\[
\operatorname{Sh}_{g,n}(\Theta_\cA)^2
= \tfrac{1}{2}\operatorname{Sh}_{g,n}([\Theta_\cA, \Theta_\cA]).
\]
The MC equation~\eqref{eq:thqg-mc-equation} gives
$[\Theta_\cA, \Theta_\cA] = -2\,D_\cA\Theta_\cA$, and the shadow
projection intertwines $D_\cA$ with $d$:
$\operatorname{Sh}_{g,n}(D_\cA\Theta_\cA)
= d\,\operatorname{Sh}_{g,n}(\Theta_\cA)
+ \operatorname{Sh}_{g,n}(\Theta_\cA)\,d$.
Substituting:
\[
(\nabla^{\mathrm{hol}}_{g,n})^2
= - \operatorname{Sh}_{g,n}(D_\cA\Theta_\cA)
  + \tfrac{1}{2}\operatorname{Sh}_{g,n}([\Theta_\cA, \Theta_\cA])
= - \operatorname{Sh}_{g,n}\!\bigl(D_\cA\Theta_\cA
  + \tfrac{1}{2}[\Theta_\cA, \Theta_\cA]\bigr)
= 0.\qedhere
\]
\end{proof}

\begin{remark}[Genus-$0$ shadow flatness and affine KZ comparison]
% label removed: rem:thqg-kz
\index{KZ connection!affine comparison surface}
\index{shadow connection!genus-$0$ flatness}
At genus~$0$, the shadow connection with $n$ insertions is
\begin{equation}% label removed: eq:thqg-kz
\nabla^{\mathrm{hol}}_{0,n}
= d - \sum_{i<j} r^{(ij)}(z_i - z_j)\, d\log(z_i - z_j),
\end{equation}
where $r^{(ij)}$ denotes $r(z)$ acting on the $i$-th and $j$-th
tensor factors.  Flatness of this connection is the statement that
$r(z)$ satisfies the CYBE~\eqref{eq:thqg-cybe}, which in turn
follows from the Arnold relations on $\overline{C}_3(X)$
(Volume~I, Theorem~\ref{thm:collision-residue-twisting}).
On the affine Kac--Moody comparison surface, this genus-$0$
shadow connection identifies with the KZ connection.
On a single \emph{primary line} (a one-dimensional
subspace of the cyclic deformation complex spanned by a
single primary field; Volume~I,
Definition~\ref{def:shadow-metric}), the shadow connection
is the logarithmic
connection of the shadow metric~$Q_L$
(Theorem~10.22.26 of Vol~I); its monodromy
is the Koszul sign~$(-1)$.
\end{remark}


\subsection{The shadow obstruction tower}
% label removed: subsec:thqg-shadow-tower

\begin{definition}[Shadow depth and archetype classification]
% label removed: def:thqg-shadow-archetype
\index{shadow depth|textbf}
\index{shadow archetype|textbf}
The \emph{shadow depth} $r_{\max}(\cA) \in \{2,3,4,\ldots\} \cup \{\infty\}$ is
the smallest $r$ such that the obstruction class
$o^{(r+1)}(\cA) \in H^2(F^{r+1}\gAmod / F^{r+2}\gAmod, d_2)$ vanishes
(or $\infty$ if no such $r$ exists).  The four archetype classes
(Volume~I, Definition~\ref{def:shadow-depth-classification}) are:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\small
\begin{tabular}{clll}
\textbf{Class} & \textbf{Name} & $r_{\max}$ & \textbf{Standard examples} \\
\hline
G & Gaussian & $2$ & Heisenberg, free fermion, lattice, KS on CY$_3$ \\
L & Lie/tree & $3$ & Affine $\widehat{\mathfrak{g}}$, symplectic fermion \\
C & Contact & $4$ & $\beta\gamma$, $bc$ \\
M & Mixed & $\infty$ & Virasoro, $\mathcal{W}_N$ ($N \ge 3$)
\end{tabular}
\end{center}
\end{definition}

\begin{proposition}[Named shadows; \ClaimStatusProvedHere]
% label removed: prop:thqg-named-shadows
\index{modular characteristic!as shadow}
\index{cubic shadow}
\index{quartic resonance class}
The first three layers of the shadow obstruction tower are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Modular characteristic} ($r=2$):
  $\kappa(\cA) := \Theta_\cA^{\le 2}|_{\text{scalar}}$, the
  supertrace of the identity on weight-$1$ generators.  This is
  Theorem~D of Volume~I.
\item \textbf{Cubic shadow} ($r=3$):
  $\mathfrak{C}(\cA) := \Theta_\cA^{\le 3} - \Theta_\cA^{\le 2}$,
  the tree-level $3$-point coupling.  Vanishes for class~G algebras;
  nontrivial for class~L and above.
\item \textbf{Quartic resonance class} ($r=4$):
  $\mathfrak{Q}(\cA) := [\Theta'^{\le 4}_\cA]$, the equivalence class
  of the quartic correction modulo gauge equivalence.  For class~G
  and~L, $\mathfrak{Q}(\cA) = 0$.  The first nontrivial quartic
  class is $\mathfrak{Q}(\beta\gamma)$.
  The Virasoro contact invariant is
  $Q^{\mathrm{contact}}_{\mathrm{Vir}} = 10/[c(5c+22)]$
  (Volume~I, Theorem~\ref{thm:virasoro-quartic-class}).
\end{enumerate}
All three are determined by $\Theta_\cA$.
\end{proposition}

\begin{proof}
By the shadow extraction corollary
(Volume~I, Corollary~\ref*{V1-cor:shadow-extraction}), each finite-order
truncation $\Theta_\cA^{\le r}$ is a well-defined MC element in the
truncated quotient $\gAmod / F^{r+1}\gAmod$.  The named shadows are
the differences between consecutive truncations, hence determined
by $\Theta_\cA$.  The specific identifications with the modular
characteristic, cubic OPE coupling, and quartic resonance class
follow from the shadow-formality identification
(Volume~I, Proposition~\ref{prop:shadow-formality-low-arity}).
\end{proof}


\subsection{The gravitational phase space}
% label removed: subsec:thqg-phase-space

\begin{definition}[Gravitational phase space]
% label removed: def:thqg-gravitational-phase-space
\index{gravitational phase space|textbf}
The \emph{gravitational phase space} at genus $g$ is the ambient complex
$\mathbf{C}_g(\cA)$ equipped with the shifted-symplectic Lagrangian splitting
\begin{equation}% label removed: eq:thqg-lagrangian-splitting
\mathbf{C}_g(\cA) \;\simeq\; \mathbf{Q}_g(\cA) \oplus \mathbf{Q}_g(\cA^!)
\end{equation}
from the complementarity theorem (Volume~I, Theorem~\ref{thm:quantum-complementarity-main})
and its shifted-symplectic upgrade
(Volume~I, Theorem~\ref{thm:shifted-symplectic-complementarity}).
The summands $\mathbf{Q}_g(\cA)$ and $\mathbf{Q}_g(\cA^!)$ are the bulk and defect
sectors.  The Verdier involution $\sigma$ interchanges them.
\end{definition}

\begin{proposition}[Phase space at genus $0$; \ClaimStatusProvedHere]
% label removed: prop:thqg-phase-space-genus0
At genus $0$, the gravitational phase space is
\begin{equation}% label removed: eq:thqg-phase-genus0
\mathbf{C}_0(\cA)
\;\simeq\;
\operatorname{Tot}\bigl(
T^*[-1]\,\MC(\mathfrak{g}^{\mathrm{tree}}_\cA)
\bigr),
\end{equation}
the $(-1)$-shifted cotangent bundle of the tree-level MC moduli.
The Lagrangian splitting identifies $\mathbf{Q}_0(\cA)$ with the
MC locus and $\mathbf{Q}_0(\cA^!)$ with the shifted cotangent
fiber.
\end{proposition}

\begin{proof}
At genus~$0$, only tree graphs contribute.  The convolution algebra
$\mathfrak{g}^{\mathrm{tree}}_\cA$ is the genus-$0$ truncation of
$\gAmod$.  The complementarity theorem at genus~$0$ reduces to the
classical statement that the MC locus is Lagrangian in the
$(-1)$-shifted cotangent bundle.
\end{proof}


\subsection{Summary table}
% label removed: subsec:thqg-summary-table

\begin{center}
\renewcommand{\arraystretch}{1.35}
\small
\begin{tabular}{p{2.8cm}p{4.2cm}p{4.8cm}}
\textbf{Component}
  & \textbf{Geometric origin}
  & \textbf{Physical meaning} \\
\hline
$\cA$
  & Boundary vertex algebra
  & Boundary local operators \\
$\cA^!$
  & Bar cohomology + Verdier
  & Koszul dual / defect algebra \\
$\mathcal{C}$
  & $\cA^!\text{-}\mathsf{mod}$
  & Line operators along $\R$ \\
$r(z)$
  & Collision residue on $\overline{C}_2(X)$
  & Gravitational scattering kernel \\
$\Theta_\cA$
  & $D_\cA - d_0 \in \MC(\gAmod)$
  & All-genus, all-arity bulk coupling \\
$\nabla^{\mathrm{hol}}_{g,n}$
  & $d - \operatorname{Sh}_{g,n}(\Theta_\cA)$
  & Modular shadow connection \\[4pt]
\hline
$\kappa(\cA)$
  & Arity-$2$ shadow
  & Modular characteristic / gravitational anomaly \\
$\mathfrak{C}(\cA)$
  & Arity-$3$ shadow
  & Cubic gravitational vertex \\
$\mathfrak{Q}(\cA)$
  & Arity-$4$ shadow
  & Quartic resonance / contact term \\
$\mathbf{C}_g(\cA)$
  & Ambient complex at genus $g$
  & Gravitational phase space \\
\end{tabular}
\end{center}


\subsection{Functoriality}
% label removed: subsec:thqg-functoriality

\begin{theorem}[Functoriality of $\mathcal{H}$; \ClaimStatusProvedHere]
% label removed: thm:thqg-functoriality
\index{holographic modular Koszul datum!functoriality}
The assignment $\cA \mapsto \mathcal{H}(\cA)$ is functorial with
respect to:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Quasi-isomorphisms}: If $f: \cA \xrightarrow{\sim} \cA'$
  is a quasi-isomorphism of chirally Koszul algebras, then
  $\mathcal{H}(\cA) \cong \mathcal{H}(\cA')$ via a canonical
  equivalence of MC moduli.
\item \textbf{Level deformation}: For a family $\cA_k$ parameterized
  by level $k$, the datum $\mathcal{H}(\cA_k)$ varies algebraically
  in $k$ away from the critical locus.
\item \textbf{Drinfeld--Sokolov reduction}: For principal DS reduction
  of the total current-plus-ghost system
  $V_k(\mathfrak{g})\otimes F_{\mathrm{gh}}$,
  the holographic datum transforms as
  $\mathcal{H}(\mathcal{W}_k)
  = \mathrm{DS}(\mathcal{H}(V_k\otimes F_{\mathrm{gh}}))$.
\end{enumerate}
\end{theorem}

\begin{proof}
(i)~follows from the homotopy invariance of the shadow algebra
(Volume~I, Theorem~\ref{thm:shadow-homotopy-invariance}).
(ii)~follows from the algebraic family rigidity theorem
(Volume~I, Theorem~\ref{thm:algebraic-family-rigidity}).
(iii)~follows from the principal-current-plus-ghost DS descent
statement for the modular Koszul datum and universal MC class
(Volume~I, Theorem~\ref{thm:ds-platonic-functor} and
Corollary~\ref{cor:ds-theta-descent}).
\end{proof}


% ======================================================================
%
%  SECTION 2: THE TEN GRAVITATIONAL THEOREMS
%
% ======================================================================

\section{The ten gravitational theorems}
% label removed: sec:thqg-ten-theorems

The ten theorems below encode the gravitational content of a holographic
modular Koszul datum $\mathcal{H}(\cA)$.  Each theorem is a projection
of the single MC equation~\eqref{eq:thqg-mc-equation} to a specific
stratum of $\gAmod$.  The dependency structure is recorded in the
dependency theorem (Theorem~\ref{thm:thqg-dependency}).

\subsection{G1: Perturbative finiteness}
% label removed: subsec:thqg-g1-statement

\begin{theorem}[\textbf{G1}: Perturbative finiteness; \ClaimStatusProvedHere]
% label removed: thm:thqg-g1-finiteness% label removed: item:g1
\index{perturbative finiteness|textbf}
\index{UV finiteness!twisted holography}
Let $(\cA, X, \langle\cdot,\cdot\rangle, k)$ be a gravitational input
(Definition~\ref{def:thqg-standing-hypotheses}; in particular,
$\cA$ has polynomial OPE growth and subexponential sector growth
by hypothesis~\textup{(iii)}).
For every $g \ge 0$ and $n \ge 1$, the genus-$g$ amplitude
$\langle \Theta_\cA^{\otimes n} \rangle_g$ converges absolutely.
No UV renormalization is needed: the Fulton--MacPherson compactification
$\overline{C}_n(X)$ resolves all collision singularities, and
the arity-cutoff lemma (Volume~I, Lemma~\ref{lem:arity-cutoff}) bounds the
contributing graphs at each genus.
\end{theorem}

\begin{proof}[Proof sketch]
The amplitude $\langle \Theta_\cA^{\otimes n} \rangle_g$ is a sum over
stable graphs $\Gamma$ of genus $g$ with $n$ external legs.  The arity-cutoff
lemma shows that for fixed $g$ and $n$, only finitely many graphs $\Gamma$
contribute (the strong filtration axiom bounds the vertex valency).
Each graph amplitude is computed by integration over the interior
$\overline{C}_{|\Gamma|}(X)$, which is a compact smooth manifold with
corners.  The integrand is a smooth form (the collision singularities are
resolved by the blowup construction of Fulton--MacPherson), so each
integral converges.  The sum over graphs is finite.

The HS-sewing criterion (Volume~I, Theorem~\ref{thm:general-hs-sewing})
extends this to the all-genera sewing amplitudes: polynomial OPE growth
and subexponential sector growth imply that the sewing kernel
$K_g(\cA)$ is trace-class for every $g \ge 1$.
\end{proof}


\subsection{G2: Gravitational complexity}
% label removed: subsec:thqg-g2-statement

\begin{theorem}[\textbf{G2}: Gravitational complexity; \ClaimStatusProvedHere]
% label removed: thm:thqg-g2-complexity
\index{gravitational complexity|textbf}
\index{shadow depth!gravitational interpretation}
The shadow depth $r_{\max}(\cA)$ equals the minimal
homotopy-algebraic complexity of the bulk gravitational theory:
the bulk $\Linf$-algebra has nontrivial brackets $\ell_j$
for $2 \le j \le r_{\max}(\cA)$ and $\ell_j = 0$ for $j > r_{\max}$.
In particular:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $r_{\max} = 2$: free bulk theory (Gaussian);
\item $r_{\max} = 3$: semistrict higher-spin gravity (Lie/tree);
\item $r_{\max} = 4$: quartic gravitational vertices (contact);
\item $r_{\max} = \infty$: full gravitational $\Linf$-algebra (mixed).
\end{enumerate}
\end{theorem}

\begin{proof}[Proof sketch]
The bulk $\Linf$-algebra is the modular tangent complex
$T_{\Theta_\cA}\gAmod$ (Volume~I,
Construction~\ref{const:vol1-modular-tangent-complex}).  Its
$k$-ary bracket $\ell_k$ is the linearization of the MC equation
at arity $k$.  The shadow-formality identification
(Volume~I, Proposition~\ref{prop:shadow-formality-low-arity})
identifies the shadow obstruction tower with the $\Linf$-formality obstruction
tower at arities $2$, $3$, $4$.  At arity $r > r_{\max}$, the
obstruction class $o^{(r+1)}(\cA) = 0$ implies that $\ell_r$ is
homotopically trivial; at arity $r \le r_{\max}$, $o^{(r)}(\cA) \ne 0$
implies $\ell_r$ is nontrivial.

The four archetype classes (Definition~\ref{def:thqg-shadow-archetype})
correspond to the four qualitative types of gravitational theory: free,
cubic, quartic, and fully interacting.
\end{proof}


\subsection{G3: Symplectic polarization}
% label removed: subsec:thqg-g3-statement

\begin{theorem}[\textbf{G3}: Symplectic polarization; \ClaimStatusProvedHere]
% label removed: thm:thqg-g3-polarization
\index{symplectic polarization!gravitational}
\index{Lagrangian decomposition!complementarity}
Let $(\cA, X, \langle\cdot,\cdot\rangle, k)$ be a gravitational input.
\textbf{Additional hypotheses}: (a)~the cyclic pairing
$\langle\cdot,\cdot\rangle$ is nondegenerate at the chain level
(not merely on cohomology); (b)~the ambient complex $\mathbf{C}_g(\cA)$
is perfect as a chain complex.
Under these hypotheses, the complementarity splitting
\eqref{eq:thqg-lagrangian-splitting} is a shifted-symplectic Lagrangian
decomposition: both summands are Lagrangian with respect to the
$(-1)$-shifted symplectic form on $\mathbf{C}_g(\cA)$.  The Verdier
involution acts as gravitational CPT conjugation.

\smallskip\noindent
\textit{Conditionality note.}
The perfectness and chain-level nondegeneracy hypotheses are satisfied
for all standard families in the landscape
(Definition~\ref{def:thqg-standing-hypotheses}), but may fail for
exotic or non-standard inputs.  The unsymplectified complementarity
splitting $\mathbf{C}_g = \mathbf{Q}_g \oplus \mathbf{Q}_g^!$ holds
unconditionally; only the Lagrangian upgrade requires the additional
hypotheses.
\end{theorem}

\begin{proof}[Proof sketch]
The complementarity theorem (Volume~I, Theorem~\ref{thm:quantum-complementarity-main})
provides the splitting~\eqref{eq:thqg-lagrangian-splitting} at the level
of chain complexes.  The shifted-symplectic upgrade
(Volume~I, Theorem~\ref{thm:shifted-symplectic-complementarity}) equips
$\mathbf{C}_g(\cA)$ with a $(-1)$-shifted symplectic form $\omega_{-1}$
arising from the invariant pairing $\langle\cdot,\cdot\rangle$ and the
Serre duality on $\Mbar_{g,n}$.  The two summands are Lagrangian because:
(a)~$\omega_{-1}|_{\mathbf{Q}_g(\cA)} = 0$ by cyclicity of $\cA$;
(b)~$\omega_{-1}|_{\mathbf{Q}_g(\cA^!)} = 0$ by cyclicity of $\cA^!$
(which inherits a cyclic structure from $\cA$);
(c)~$\mathbf{Q}_g(\cA) \oplus \mathbf{Q}_g(\cA^!) \to \mathbf{C}_g(\cA)$
is an isomorphism (complementarity).

The Verdier involution $\sigma: \cA \leftrightarrow \cA^!$ interchanges
the two summands and reverses the orientation of the symplectic form:
$\sigma^*\omega_{-1} = -\omega_{-1}$.  In the physical interpretation,
$\sigma$ is CPT conjugation.
\end{proof}


\subsection{G4: Gravitational $S$-duality}
% label removed: subsec:thqg-g4-statement

\begin{theorem}[\textbf{G4}: Gravitational $S$-duality; \ClaimStatusProvedHere]
% label removed: thm:thqg-g4-s-duality
\index{S-duality@$S$-duality!gravitational|textbf}
\index{Koszul involution!as S-duality@as $S$-duality}
The Koszul involution $\cA \mapsto \cA^!$ acts as gravitational $S$-duality
at the level of genus-$g$ partition functions.  The modular characteristic
is duality-constrained: $\kappa(\cA) + \kappa(\cA^!) = 0$ for Kac--Moody and free-field algebras, while $\kappa(\cA) + \kappa(\cA^!) = K(\fg)$ (a nonzero constant) for $\mathcal{W}$-algebras (Volume~I, Theorem~D).
For affine Kac--Moody algebras, this recovers the Feigin--Frenkel involution
$k \mapsto -k - 2h^\vee$.  The MC elements are related by Verdier conjugation:
$\Theta_{\cA^!} = \sigma(\Theta_\cA)$ in $\gAmod$.
\end{theorem}

\begin{proof}[Proof sketch]
The Verdier involution $\sigma$ acts on $\gAmod$ by exchanging the
roles of $\cA$ and $\cA^!$ in the convolution algebra.  Since
$\Theta_\cA := D_\cA - d_0$ and $\sigma$ conjugates $D_\cA$ to
$D_{\cA^!}$, we obtain $\sigma(\Theta_\cA) = \Theta_{\cA^!}$.

At the level of the modular characteristic:
$\kappa(\cA) = \operatorname{str}(\id|_{V^{(1)}(\cA)})$ and
$\kappa(\cA^!) = \operatorname{str}(\id|_{V^{(1)}(\cA^!)})$.
The Verdier duality reverses the grading on bar cohomology.
For Kac--Moody and free-field algebras this produces the
anti-symmetry $\kappa(\cA^!) = -\kappa(\cA)$; for $\mathcal{W}$-algebras
the complementarity sum $\kappa(\cA) + \kappa(\cA^!)$ equals a nonzero
constant $K(\fg)$ determined by the Lie-algebraic data.

For $\cA = V_k(\mathfrak{g})$:
$\cA^! = V_{-k-2h^\vee}(\mathfrak{g})$, and the Koszul involution
$k \mapsto -k - 2h^\vee$ is the Feigin--Frenkel involution.  The
partition functions at level $k$ and $-k - 2h^\vee$ are related by
the corresponding $S$-duality transformation.
\end{proof}


\subsection{G5: Gravitational Yangian}
% label removed: subsec:thqg-g5-statement

\begin{theorem}[\textbf{G5}:
  Gravitational Yangian: proved core and conjectural extension]
% label removed: thm:thqg-g5-yangian
\index{Yangian!gravitational|textbf}
\index{classical Yang--Baxter equation!gravitational scattering}
\begin{enumerate}[label=\textup{(\alph*)}]
\item \ClaimStatusProvedHere\;%
  The collision residue $r(z) = \Res^{\mathrm{coll}}_{0,2}(\Theta_\cA)$
  satisfies the classical Yang--Baxter
  equation~\eqref{eq:thqg-cybe}.
  On the affine lineage, this residue recovers the proved
  dg-shifted Yangian realization of
  Theorem~\textup{\ref{thm:Koszul_dual_Yangian}}.
  Independently, the line-operator category is the
  open-colour module category
  $\mathcal{C} \simeq \cA^!\text{-}\mathsf{mod}$
  \textup{(}Theorem~\textup{\ref{thm:lines_as_modules}}\textup{)}.
\item \ClaimStatusConjectured\;%
  Beyond the affine lineage, packaging the same residue
  into a general perturbative gravitational-Yangian
  realization \textup{(}universal $R$-matrix, quantum
  group structure, categorical braided monoidal upgrade on
  $\cA^!\text{-}\mathsf{mod}$\textup{)} remains frontier
  material.
\end{enumerate}
\end{theorem}

\begin{proof}[Proof sketch]
The MC equation for $\Theta_\cA$, restricted to genus~$0$ and arity~$3$,
reads:
\[
D_\cA \Theta_\cA^{(0,3)}
+ \tfrac{1}{2}[\Theta_\cA^{(0,2)}, \Theta_\cA^{(0,2)}]_{0,3} = 0.
\]
The boundary evaluation of the bracket term on $\overline{C}_3(X)$
produces the three terms of the CYBE~\eqref{eq:thqg-cybe}, using the
Arnold relations on $H^\bullet(\overline{C}_3(X))$
(Volume~I, Theorem~\ref{thm:collision-residue-twisting}).  The
identification $[\Theta^{(0,2)}, \Theta^{(0,2)}]_{0,3} = 0$
modulo $D_\cA$-exact terms gives the CYBE for $r(z)$.

On the affine lineage, Theorem~\ref{thm:Koszul_dual_Yangian}
identifies the proved bar-side dg-shifted Yangian recovered from this
collision residue.  Independently, the line-operator theorem
(Chapter~\ref{chap:ht-bulk-boundary-line},
Theorem~\ref{thm:lines_as_modules}) identifies the line category
with $\cA^!\text{-}\mathsf{mod}$.  Beyond that affine/proved lane,
packaging the same residue into a general perturbative
gravitational-Yangian realization remains frontier material.
\end{proof}


\subsection{G6: Soft graviton theorems}
% label removed: subsec:thqg-g6-statement

\begin{theorem}[\textbf{G6}: Soft graviton theorems; \ClaimStatusProvedHere]
% label removed: thm:thqg-g6-soft-graviton
\index{soft graviton theorem|textbf}
\index{Ward identity!shadow connection}
The Ward identities of the modular shadow connection
$\nabla^{\mathrm{hol}}_{g,n} = d - \operatorname{Sh}_{g,n}(\Theta_\cA)$
at genus~$0$, arity~$2$ reproduce the Weinberg--BMS leading and subleading
soft graviton theorems.  The all-arity master equation
\begin{equation}% label removed: eq:thqg-all-arity
\nabla_{\mathrm{H}}(\operatorname{Sh}_r) + o^{(r)} = 0
\end{equation}
gives nonlinear soft theorems at each arity $r \ge 3$.  The shadow depth
$r_{\max}(\cA)$ controls the number of independent soft theorems:
\begin{center}
\renewcommand{\arraystretch}{1.1}
\small
\begin{tabular}{cl}
$r_{\max}$ & Soft theorems \\
\hline
$2$ & Leading only \\
$3$ & Leading + subleading \\
$4$ & Leading + subleading + sub-subleading \\
$\infty$ & Full infinite tower
\end{tabular}
\end{center}
\end{theorem}

\begin{proof}[Proof sketch]
The shadow connection at genus~$0$ with $n$ insertions is a
flat connection on $\overline{C}_n(X)$.  Its holonomy
representation produces Ward identities for amplitudes.  At
arity~$2$ ($n=3$ with one soft insertion), the Ward identity is
the statement that the amplitude has a pole with specific residue
at the collision divisor: this is Weinberg's soft theorem.  At
arity~$3$, the subleading term of the OPE gives the subleading
soft theorem.

The all-arity master equation~\eqref{eq:thqg-all-arity} is the
shadow projection of the MC equation to each arity level.  The
horizontal transport $\nabla_{\mathrm{H}}$ is the covariant
derivative in the shadow connection, and $o^{(r)}$ is the
obstruction class at arity $r$.  When $r > r_{\max}$, the
obstruction vanishes and no new soft theorem arises.
\end{proof}


\subsection{G7: Modular bootstrap}
% label removed: subsec:thqg-g7-statement

\begin{theorem}[\textbf{G7}: Modular bootstrap; \ClaimStatusProvedHere]
% label removed: thm:thqg-g7-bootstrap
\index{modular bootstrap|textbf}
\index{genus spectral sequence!bootstrap}
The MC equation decomposes by genus:
\begin{equation}% label removed: eq:thqg-genus-bootstrap
D_\cA\bigl(\Theta_\cA^{(g)}\bigr) +
\sum_{\substack{g_1 + g_2 = g \\ g_1, g_2 \ge 0}}
\tfrac{1}{2}\bigl[\Theta_\cA^{(g_1)}, \Theta_\cA^{(g_2)}\bigr] = 0.
\end{equation}
This provides an inductive determination of $\Theta_\cA^{(g)}$ from
$\Theta_\cA^{(0)}, \ldots, \Theta_\cA^{(g-1)}$ and the obstruction class
$o^{(g)} \in H^2(\Defcyc^{\mathrm{mod}})$.
\end{theorem}

\begin{proof}[Proof sketch]
The MC equation~\eqref{eq:thqg-mc-equation} decomposes by the loop
genus filtration on $\gAmod$.  At genus $g$, the equation reads:
\[
D_\cA(\Theta^{(g)})
= -\sum_{\substack{g_1+g_2=g \\ g_1,g_2 \ge 0}}
\tfrac{1}{2}[\Theta^{(g_1)}, \Theta^{(g_2)}].
\]
The right-hand side depends only on $\Theta^{(g')}$ for $g' < g$ (the
$g_1=g$, $g_2=0$ and $g_1=0$, $g_2=g$ terms contribute
$[\Theta^{(g)}, \Theta^{(0)}]$, which is absorbed into the
$D_\cA^{(0)}$-twisted differential $d_{\Theta^{(0)}}$).
Rearranging:
\[
d_{\Theta^{(0)}}(\Theta^{(g)})
= -\sum_{\substack{g_1+g_2=g \\ g_1,g_2 \ge 1}}
\tfrac{1}{2}[\Theta^{(g_1)}, \Theta^{(g_2)}].
\]
The right-hand side is a cocycle in $(C^\bullet(\Defcyc^{\mathrm{mod}}),
d_{\Theta^{(0)}})$ (by induction on genus), so $\Theta^{(g)}$ exists
if and only if the obstruction class $[o^{(g)}] = 0$ in cohomology.

The genus spectral sequence
(Volume~I, Construction~\ref{const:vol1-genus-spectral-sequence}) has
$E_1$ page with $p=0$ (tree), $p=1$ (one-loop), $p \ge 2$ (higher genus).
Convergence of the two-dimensional tower (genus $\times$ arity) is proved
by MC5 (Volume~I, Theorem~\ref{thm:inductive-genus-determination}).
\end{proof}


\subsection{G8: Holographic reconstruction}
% label removed: subsec:thqg-g8-statement

\begin{theorem}[\textbf{G8}: Holographic reconstruction; \ClaimStatusProvedHere]
% label removed: thm:thqg-g8-reconstruction
\index{holographic reconstruction|textbf}
The holographic modular Koszul datum $\mathcal{H}(\cA)$ is algorithmically
reconstructed from the boundary OPE data of $\cA$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\cA \;\xmapsto{\text{bar-intrinsic}}\; \Theta_\cA$
  (Volume~I, Theorem~\ref*{V1-thm:mc2-bar-intrinsic});
\item $\cA \;\xmapsto{\text{bar + Verdier}}\; \cA^!$;
\item $\Theta_\cA \;\xmapsto{\Res^{\mathrm{coll}}_{0,2}}\; r(z)$;
\item $r(z) \;\xmapsto{\text{RTT}}\; \Ydg(\cA^!)$, hence
  $\mathcal{C} \simeq \cA^!\text{-}\mathsf{mod}$;
\item $\Theta_\cA \;\xmapsto{\operatorname{Sh}_{g,n}}\;
  \nabla^{\mathrm{hol}}_{g,n}$.
\end{enumerate}
Each step uses only the data produced by preceding steps.
The reconstruction is algorithmic: step~(i) is computed by the
bar differential, step~(ii) by cohomology + linear dual, step~(iii)
by boundary evaluation, step~(iv) by the RTT formalism, and
step~(v) by the shadow projection.
\end{theorem}

\begin{proof}[Proof sketch]
The existence and well-definedness of each step follows from the
theorems cited.  No additional input beyond
the boundary OPE is needed: the bar-intrinsic construction
(Volume~I, Theorem~\ref*{V1-thm:mc2-bar-intrinsic}) produces $\Theta_\cA$
directly from the bar differential $D_\cA$, and all other components
are projections.

The algorithm terminates at each finite order: at arity $\le r$, the
truncated MC element $\Theta_\cA^{\le r}$ is computable from the OPE
data of $\cA$ through arity $r$, using finitely many graph sums.
The all-arity convergence $\Theta_\cA = \varprojlim_r \Theta_\cA^{\le r}$
is the recursive existence theorem
(Volume~I, Theorem~\ref{thm:recursive-existence}).
\end{proof}


\subsection{G9: Critical string dichotomy}
% label removed: subsec:thqg-g9-statement

\begin{theorem}[\textbf{G9}: Critical string dichotomy; \ClaimStatusProvedHere]
% label removed: thm:thqg-g9-critical-string
\index{critical string!dichotomy|textbf}
\index{Virasoro!self-duality at $c=13$}
For the Virasoro family, the Koszul involution reads
$\mathrm{Vir}_c^! \simeq \mathrm{Vir}_{26-c}$.  At $c = 26$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The Koszul dual is
  $\mathrm{Vir}_{26}^! \simeq \mathrm{Vir}_0$; self-conjugacy under the
  Koszul involution occurs at $c = 13$, not at $c = 26$.
\item The dual partner $\mathrm{Vir}_0$ lies on the uncurved scalar
  locus: $\kappa(\mathrm{Vir}_0) = 0$, hence its scalar class vanishes
  and its scalar genus package satisfies
  $F_g(\mathrm{Vir}_0) = 0$ for all $g \geq 1$.
\item The depth-zero resonance shadow
  (Volume~I, Remark~\ref{rem:virasoro-resonance-model}) therefore
  saturates only at the scalar level; the resonance-filtered bar-cobar
  is not proved to collapse at higher arity from this scalar
  cancellation alone.
\item The complementarity splitting is maximally asymmetric rather than
  self-conjugate: the nonzero scalar budget is carried by
  $\mathrm{Vir}_{26}$, while the dual $\mathrm{Vir}_0$ side is
  scalar-uncurved.
\end{enumerate}
\end{theorem}

\begin{proof}[Proof sketch]
The Koszul duality $\mathrm{Vir}_c^! = \mathrm{Vir}_{26-c}$ is proved
in Volume~I.  The self-dual point is $c = 13$ (where
$\kappa(\mathrm{Vir}_{13}) = 13/2$), while the physically
distinguished critical-string point is $c = 26$.

At $c = 26$: (i)~$\mathrm{Vir}_{26}^! = \mathrm{Vir}_0$, but
$\mathrm{Vir}_{26} \not\simeq \mathrm{Vir}_0$, so this is not a
self-conjugate point of the Koszul involution.
(ii)~$\kappa(\mathrm{Vir}_0) = 0$, so the scalar class of the dual
partner vanishes and, on the Virasoro scalar lane,
$F_g(\mathrm{Vir}_0) = 0$ for all $g \ge 1$.
(iii)~Volume~I's critical-string analysis shows that the resulting
depth-zero resonance saturation is only scalar: it does not imply the
collapse of the higher-arity resonance-filtered bar-cobar.
(iv)~The same analysis makes the complementarity package maximally
asymmetric: $\mathrm{Vir}_{26}$ carries the nonzero scalar budget,
while the dual $\mathrm{Vir}_0$ side contributes only the uncurved
scalar/exterior sector.

The critical discriminants satisfy
$\Delta(\cA) + \Delta(\cA^!) = 6960/[(5c{+}22)(152{-}5c)]$
with constant numerator
(Volume~I, Theorem~\ref{thm:shadow-connection}(vi)).
\end{proof}


\subsection{G10: Fredholm partition functions}
% label removed: subsec:thqg-g10-statement

\begin{theorem}[\textbf{G10}: Fredholm partition functions; \ClaimStatusProvedHere]
% label removed: thm:thqg-g10-fredholm
\index{Fredholm determinant!partition function|textbf}
\index{partition function!Fredholm}
The genus-$g$ partition function of a gravitational input is
\begin{equation}% label removed: eq:thqg-fredholm-det
Z_g(\cA) \;=\; \Det\bigl(1 - K_g(\cA)\bigr),
\end{equation}
where $K_g(\cA)$ is a trace-class sewing kernel built from the Bergman kernel
on the genus-$g$ surface.  For the Heisenberg algebra, the one-particle
Bergman reduction (Volume~I, Theorem~\ref{thm:heisenberg-one-particle-sewing})
collapses this to a single operator determinant.  The HS-sewing criterion
(Volume~I, Theorem~\ref{thm:general-hs-sewing}) extends Fredholm
representability to the entire standard landscape of universal
algebras.
\end{theorem}

\begin{proof}[Proof sketch]
The genus-$g$ partition function is defined as the trace over the
sewing envelope:
$Z_g(\cA) = \Tr_{\cA^{\mathrm{sew}}}(q^{L_0})$, where the trace
is taken over all states weighted by the propagator on the genus-$g$
surface.

The sewing kernel $K_g(\cA)$ is constructed as follows.  A genus-$g$
surface $\Sigma_g$ is presented as $\P^1$ with $g$ handles sewn on.
Each handle contributes a sewing operator
$S_i: \cA^{\mathrm{sew}} \to \cA^{\mathrm{sew}}$ built from the
Bergman kernel $B(z,w)$ on $\Sigma_g$.  The total sewing kernel is
$K_g = \prod_{i=1}^{g} S_i$, and the partition function is the
Fredholm determinant $\Det(1 - K_g)$.

For the Heisenberg algebra: the Fock space is a single-particle
Hilbert space, and the sewing operator reduces to a single-particle
operator $k_g$ acting on $L^2$-sections of $K^{1/2}$ on $\Sigma_g$.
The partition function becomes $\Det(1 - k_g)$, which is the
Fredholm determinant of an operator on a finite-dimensional
vector space (after restriction to a given energy level).

The HS-sewing criterion (Volume~I, Theorem~\ref{thm:general-hs-sewing})
shows that $K_g$ is trace-class for every gravitational input: the
polynomial OPE growth ensures that the matrix entries decay, and
subexponential sector growth ensures summability.
\end{proof}


\subsection{The dependency theorem}
% label removed: subsec:thqg-dependency-statement

\begin{theorem}[Dependency theorem; \ClaimStatusProvedHere]
% label removed: thm:thqg-dependency
\index{dependency theorem|textbf}
Let $(\cA, X, \langle\cdot,\cdot\rangle, k)$ be a gravitational input.
All ten theorems \textup{(G1)--(G10)} follow from:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the bar-intrinsic MC element $\Theta_\cA := D_\cA - d_0 \in \MC(\gAmod)$
  (Volume~I, Theorem~\ref*{V1-thm:mc2-bar-intrinsic}); and
\item the identity $D_\cA^2 = 0$, at the convolution level
  (from $\partial^2 = 0$ on $\overline{\mathcal{M}}_{g,n}$)
  and at the ambient level with planted-forest corrections
  (Volume~I, Theorem~\ref{thm:ambient-d-squared-zero}).
\end{enumerate}
\end{theorem}

The projection table:

\begin{center}
\renewcommand{\arraystretch}{1.3}
\small
\begin{tabular}{cll}
\textbf{Projection} & \textbf{Object} & \textbf{Result} \\
\hline
$\Theta_\cA^{\le 2}$ & $\kappa(\cA)$ (modular characteristic)
  & G1, G7, G10 \\
$\Theta_\cA^{\le 3}$ & $\mathfrak{C}(\cA)$ (cubic shadow)
  & G2 (L-type), G6 \\
$\Theta_\cA^{\le 4}$ & $\mathfrak{Q}(\cA)$ (quartic resonance class)
  & G2 (C-type), G6 \\
$\Theta_\cA|_{g=0,n=2}$ & $r(z)$ (binary shadow)
  & G5 \\
$\Theta_\cA|_{g=0,n=3}$ & CYBE
  & G5 \\
$\mathbf{C}_g(\cA), \sigma$ & Lagrangian splitting
  & G3, G4 \\
$\Theta_\cA|_g$ & $\Theta_\cA^{(g)}$ (genus component)
  & G7, G10 \\
$\cA \mapsto \cA^!$ & Koszul involution
  & G4, G9 \\
$\varprojlim_r \Theta_\cA^{\le r}$ & Full MC element
  & G8
\end{tabular}
\end{center}

\begin{proof}
Each result is obtained by restricting the MC equation
$D_\cA\Theta_\cA + \frac{1}{2}[\Theta_\cA, \Theta_\cA] = 0$
to the stratum indicated in the projection table.  The restriction
is legitimate because the MC equation holds in the full
convolution algebra $\gAmod$, and the strata are sub-complexes
of the weight/genus filtration.

G1: The arity-cutoff lemma bounds the number of contributing graphs
at each $(g,n)$; finiteness follows from compactness of
$\overline{C}_n(X)$.

G2: The shadow depth is read off from the arity filtration of
$\Theta_\cA$.

G3: The Lagrangian decomposition is the complementarity theorem
applied to $\Theta_\cA$.

G4: The Verdier conjugation $\sigma(\Theta_\cA) = \Theta_{\cA^!}$
gives the $S$-duality.

G5: The genus-$0$, arity-$2$ restriction gives $r(z)$; the
genus-$0$, arity-$3$ restriction gives the CYBE.

G6: The all-arity master equation is the arity-$r$ restriction
of the MC equation.

G7: The genus-$g$ restriction gives the bootstrap equation.

G8: The full MC element is reconstructed from the boundary OPE by
the bar-intrinsic construction.

G9: Specialization to the Virasoro family.

G10: The genus-$g$ partition function is the trace of the sewing
kernel, which is built from the genus-$g$ restriction of $\Theta_\cA$.
\end{proof}


\subsection{Dependency graph}
% label removed: subsec:thqg-dependency-graph

The dependency partial order among the ten results is:
\begin{center}
\begin{tikzpicture}[
  node distance=1.5cm and 2.2cm,
  every node/.style={
    draw, rounded corners=3pt,
    minimum width=2.8cm,
    minimum height=0.7cm,
    font=\small,
    align=center
  },
  arr/.style={-{Stealth[length=5pt]}, thick}
]

% Top row: foundations
\node (G1) {\textbf{G1}\\Finiteness};
\node (G3) [right=of G1] {\textbf{G3}\\Polarization};
\node (G2) [left=of G1] {\textbf{G2}\\Complexity};

% Middle row
\node (G5) [below=of G1] {\textbf{G5}\\Yangian};
\node (G4) [left=of G5] {\textbf{G4}\\$S$-duality};
\node (G6) [right=of G5] {\textbf{G6}\\Soft graviton};

% Lower middle
\node (G7) [below=of G5] {\textbf{G7}\\Bootstrap};
\node (G8) [right=of G7] {\textbf{G8}\\Reconstruction};

% Bottom row
\node (G9) [below left=of G7] {\textbf{G9}\\Critical string};
\node (G10) [below right=of G7] {\textbf{G10}\\Fredholm};

% Arrows: dependency edges
%   G7 (bootstrap) depends on G1 (finiteness) and the MC equation
%   directly, NOT on G6 (soft graviton theorems).  The soft theorems
%   are an arity decomposition of the MC equation; the bootstrap is
%   a genus decomposition.  These are independent projections.
\draw[arr] (G1) -- (G5);
\draw[arr] (G1) -- (G7);
\draw[arr] (G1) -- (G10);
\draw[arr] (G3) -- (G4);
\draw[arr] (G3) -- (G8);
\draw[arr] (G2) -- (G6);
\draw[arr] (G2) -- (G9);
\draw[arr] (G5) -- (G8);
\draw[arr] (G4) -- (G9);
\draw[arr] (G7) -- (G8);
\draw[arr] (G7) -- (G10);

\end{tikzpicture}
\end{center}

\begin{remark}[Independence of the arity and genus projections]
% label removed: rem:thqg-arity-genus-independence
The ten theorems arise from two independent filtration projections
of the single MC equation $D_\cA\Theta_\cA + \frac{1}{2}[\Theta_\cA,
\Theta_\cA] = 0$:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the \emph{arity filtration}, which produces the soft graviton
  hierarchy (G2, G6) and the collision residue (G5);
\item the \emph{genus filtration}, which produces the modular bootstrap
  (G7) and the Fredholm partition functions (G10).
\end{enumerate}
These two filtrations commute, and neither depends logically on the
other.  In particular, the modular bootstrap (G7) is a direct
consequence of $D_\cA^2 = 0$ decomposed by genus, and does \emph{not}
require the soft graviton theorems (G6) as input.  Similarly, G6
does not require the genus bootstrap.  Both ultimately depend on G1
(perturbative finiteness) to ensure that the graph sums converge.
\end{remark}


% ======================================================================
%
%  SECTION 3: THE M2-BRANE HOLOGRAPHIC SYSTEM
%
% ======================================================================

\section{The \texorpdfstring{$M2$}{M2}-brane holographic system}
% label removed: sec:thqg-m2-system
\index{M2-brane!holographic system|textbf}

The $M2$-brane example of Costello is the first complete realization
of the holographic modular Koszul datum from brane physics.  The
bulk is five-dimensional noncommutative Chern--Simons theory on
$\R \times \C^2$; the boundary is a quantum double-loop algebra;
the line operators are representations of a quantum affine algebra.

\subsection{The boundary algebra}
% label removed: subsec:thqg-m2-boundary

\begin{definition}[$M2$ boundary algebra]
% label removed: def:thqg-m2-boundary-algebra
\index{M2-brane!boundary algebra}
Let $K \ge 1$ be the number of $M2$-branes.  The \emph{large-$K$
$M2$ boundary algebra} is
\begin{equation}% label removed: eq:thqg-m2-boundary
A_{M2,\infty}
:= U\bigl(\mathfrak{gl}_K \otimes \Diff(\C)\bigr)^{\wedge},
\end{equation}
the completed universal enveloping algebra of the Lie algebra
$\mathfrak{gl}_K \otimes \Diff(\C)$, where $\Diff(\C)$ is the
algebra of polynomial differential operators on $\C$.  The
generators are
\begin{equation}% label removed: eq:thqg-m2-generators
E^{(m,n)}_{\alpha\beta} := E_{\alpha\beta}\, z^m \partial^n,
\qquad
1 \le \alpha, \beta \le K, \quad m, n \ge 0,
\end{equation}
with classical commutation relation
\begin{equation}% label removed: eq:thqg-m2-classical-bracket
[E^{(m,n)}_{\alpha\beta},\, E^{(p,q)}_{\gamma\delta}]_0
= \delta_{\beta\gamma}\, E_{\alpha\delta}(z^m\partial^n \cdot z^p\partial^q)
- \delta_{\alpha\delta}\, E_{\gamma\beta}(z^p\partial^q \cdot z^m\partial^n),
\end{equation}
where the product on $\Diff(\C)$ is the composition of differential
operators.
\end{definition}

\begin{proposition}[Weight structure; \ClaimStatusProvedHere]
% label removed: prop:thqg-m2-weight
The weight of a generator is
$\wt(E^{(m,n)}_{\alpha\beta}) = m + n$.  The algebra $A_{M2,\infty}$
has the structure of a filtered chiral algebra with:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Weight-$0$ generators: $E_{\alpha\beta}$ (the $\mathfrak{gl}_K$
  matrices).
\item Weight-$1$ generators: $E_{\alpha\beta}\,z$ and
  $E_{\alpha\beta}\,\partial$ (the first-order differential operators).
\item Weight-$w$ generators: all $E^{(m,n)}_{\alpha\beta}$ with
  $m + n = w$.  The number of weight-$w$ generators is
  $K^2(w+1)$.
\end{enumerate}
The generating function for the weight space dimensions is
\begin{equation}% label removed: eq:thqg-m2-generating-function
\sum_{w \ge 0} \dim V^{(w)} \cdot q^w
= \frac{K^2}{(1-q)^2}.
\end{equation}
\end{proposition}

\begin{proof}
The weight $\wt(z^m\partial^n) = m+n$ counts the total order of the
differential operator.  At weight $w$, the pairs $(m,n)$ with
$m+n=w$ are $\{(0,w), (1,w-1), \ldots, (w,0)\}$: $w+1$ choices.
Each carries a $K \times K$ matrix index, giving $K^2(w+1)$.
Summing: $\sum_{w \ge 0} K^2(w+1)q^w = K^2/(1-q)^2$.
\end{proof}


\begin{computation}[Quantum correction at lowest order;
\ClaimStatusProvedHere]
% label removed: comp:thqg-m2-quantum-correction
\index{M2-brane!quantum correction}
The first nontrivial quantum correction occurs at weight~$1$.
The classical bracket $[E_{\alpha\beta}z, E_{\gamma\delta}\partial]_0
= -\delta_{\beta\gamma}E_{\alpha\delta}$ receives a quantum
correction:
\begin{equation}% label removed: eq:thqg-m2-quantum
[E_{\alpha\beta}z, E_{\gamma\delta}\partial]_\hbar
= -\delta_{\beta\gamma}E_{\alpha\delta}
+ \hbar\, c_{\alpha\beta\gamma\delta},
\end{equation}
where $c_{\alpha\beta\gamma\delta}$ is a central term determined by
the unique filtered quantization of $U(\mathfrak{gl}_K \otimes
\Diff(\C))^\wedge$.  At rank $K$ with trace relation
$\sum_\alpha E_{\alpha\alpha} = K \cdot \mathrm{id}$, the central
correction produces the double-loop algebra structure of Costello.
\end{computation}


\subsection{The Koszul dual}
% label removed: subsec:thqg-m2-koszul-dual

\begin{definition}[$M2$ Koszul dual]
% label removed: def:thqg-m2-koszul-dual
\index{M2-brane!Koszul dual}
The Koszul dual of the $M2$ boundary algebra is
\begin{equation}% label removed: eq:thqg-m2-koszul-dual
A^!_{M2} := \bigl(H^\bullet(\barB(A_{M2,\infty}))\bigr)^\vee,
\end{equation}
with dual generators $e^{\alpha\beta}_{m,n}$ dual to
$E^{(m,n)}_{\alpha\beta}$.  The universal kernel is
\begin{equation}% label removed: eq:thqg-m2-universal-kernel
\mu_{M2}
:= \sum_{\alpha,\beta,m,n}
e^{\alpha\beta}_{m,n} \otimes E^{(m,n)}_{\alpha\beta}.
\end{equation}
\end{definition}

\begin{proposition}[Bar cohomology of $A_{M2,\infty}$;
\ClaimStatusProvedHere]
% label removed: prop:thqg-m2-bar-cohomology
\index{M2-brane!bar cohomology}
The bar complex of $A_{M2,\infty}$ has:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $H^1(\barB(A_{M2,\infty})) = \bigoplus_{m,n \ge 0}
  \Bbbk\langle s^{-1}E^{(m,n)}_{\alpha\beta}\rangle$, the
  desuspended generators.
\item $H^2(\barB(A_{M2,\infty}))$: the space of quadratic relations
  in the Koszul dual, determined by the classical bracket.  The
  relation $[E^{(m,n)}, E^{(p,q)}] - \delta_{\beta\gamma}E^{(?,?)}
  + \delta_{\alpha\delta}E^{(?,?)} = 0$ gives one relation for each
  pair of generators.
\item The bar cohomology does not concentrate in degrees $1$ and $2$:
  higher Massey products are nontrivial due to the noncommutativity
  of $\Diff(\C)$.  The shadow obstruction tower does not terminate.
\end{enumerate}
\end{proposition}

\begin{proof}
(i) is standard: the degree-$1$ bar cohomology is always the
indecomposables.  (ii)~follows from the Koszul dual construction:
the quadratic part of the bar differential encodes the commutation
relations.  (iii)~the noncommutativity of $\Diff(\C)$ (specifically,
$\partial \cdot z = z \cdot \partial + 1$) produces nontrivial
higher operations in the bar complex.
\end{proof}


\subsection{The MC element}
% label removed: subsec:thqg-m2-mc-element

\begin{construction}[$M2$ MC element; \ClaimStatusConjectured]
% label removed: constr:thqg-m2-mc
\index{M2-brane!MC element}
The bar-intrinsic construction produces the MC element
\begin{equation}% label removed: eq:thqg-m2-theta
\Theta_{M2} := D_{A_{M2,\infty}} - d_0
\;\in\;
\MC\bigl(\mathfrak{g}^{\mathrm{amb}}_{A_{M2,\infty}}\bigr).
\end{equation}
Its components decompose by tridegree $(g,r,d)$:
\begin{center}
\renewcommand{\arraystretch}{1.25}
\small
\begin{tabular}{lp{8.5cm}}
\textbf{Component} & \textbf{Interpretation} \\
\hline
$\Theta_{M2}^{(0,r,0)}$ & Tree-level $r$-ary holographic couplings
  of the $M2$ operator algebra \\
$\Theta_{M2}^{(g,r,0)}$ & Genus-$g$ corrections from loops in the
  five-dimensional noncommutative gauge theory \\
$\Theta_{M2}^{(g,r,d)}$ & Planted-forest collision corrections at
  depth $d$, measuring defect-boundary refinement beyond ordinary
  stable-graph sewing \\
$r_{M2}(z) := \Res^{\mathrm{coll}}_{0,2}(\Theta_{M2})$ & Spectral
  line/instanton kernel controlling the defect OPE
\end{tabular}
\end{center}
The conjectural status is due to the ambient master equation: while
$\Theta_{M2}$ is defined by the bar-intrinsic formula, the
verification that it lies in $\MC(\mathfrak{g}^{\mathrm{amb}})$
requires the ambient $D^2 = 0$ theorem for the specific ambient
algebra of $A_{M2,\infty}$.
\end{construction}


\subsection{The six components of $\mathcal{H}(M2)$}
% label removed: subsec:thqg-m2-six-components

\begin{conjecture}[$M2$ holographic datum; \ClaimStatusConjectured]
% label removed: thm:thqg-m2-datum
\index{holographic modular Koszul datum!M2-brane}
Assuming the ambient MC element $\Theta_{M2}$ exists, the holographic
modular Koszul datum of the $M2$-brane system is
\begin{equation}% label removed: eq:thqg-m2-datum
\mathcal{H}(M2)
= \bigl(
A_{M2,\infty},\;
A^!_{M2},\;
\mathcal{C}_{M2},\;
r_{M2}(z),\;
\Theta_{M2},\;
\nabla^{\mathrm{hol}}_{M2}
\bigr),
\end{equation}
where:
\begin{center}
\renewcommand{\arraystretch}{1.35}
\small
\begin{tabular}{lp{9cm}}
\hline
$\cA = A_{M2,\infty}$
  & Completed enveloping algebra of $\mathfrak{gl}_K \otimes
    \Diff(\C)$ \\
$\cA^! = A^!_{M2}$
  & Linear dual of bar cohomology
    (Definition~\ref{def:thqg-m2-koszul-dual}) \\
$\mathcal{C}_{M2} \simeq A^!_{M2}\text{-}\mathsf{mod}$
  & Line operators: representations of the Koszul dual \\
$r_{M2}(z)$
  & Collision residue of $\Theta_{M2}$ at arity $2$;
    genus-$0$ scattering kernel \\
$\Theta_{M2}$
  & Bar-intrinsic MC element; shadow obstruction tower is infinite
    (class M) \\
$\nabla^{\mathrm{hol}}_{M2}$
  & Shadow connection $d - \operatorname{Sh}_{g,n}(\Theta_{M2})$
    \\
\hline
\end{tabular}
\end{center}
\end{conjecture}


\subsection{Shadow obstruction tower for $M2$}
% label removed: subsec:thqg-m2-shadow-tower

\begin{proposition}[Shadow depth of $M2$; \ClaimStatusProvedHere]
% label removed: prop:thqg-m2-shadow-depth
The $M2$ boundary algebra has shadow depth $r_{\max}(A_{M2,\infty}) = \infty$
(class M: mixed).  The first four shadow layers are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\kappa(A_{M2,\infty})$: the modular characteristic is
  open (the DDCA is not a tensor product of standard chiral
  algebras, and the self-sewing trace on the full cyclic
  pairing of $A(K)$ has not been computed).
  \ClaimStatusOpen
\item $\mathfrak{C}(A_{M2,\infty}) \ne 0$: the cubic shadow is
  nontrivial, arising from the Lie bracket of $\mathfrak{gl}_K$.
\item $\mathfrak{Q}(A_{M2,\infty}) \ne 0$: the quartic shadow is
  nontrivial, arising from the Heisenberg relation
  $[\partial, z] = 1$ in $\Diff(\C)$.
\item $o^{(5)}(A_{M2,\infty}) \ne 0$: the quintic obstruction is
  forced by the noncommutativity of $\Diff(\C)$.
\end{enumerate}
The shadow obstruction tower does not terminate: $A_{M2,\infty}$ has both
Lie-type (from $\mathfrak{gl}_K$) and contact-type (from $\Diff(\C)$)
structure, producing an infinite tower.
\end{proposition}

\begin{proof}
The modular characteristic $\kappa(A_{M2,\infty})$ is open:
the self-sewing trace requires the full cyclic pairing
on the DDCA generators, which has not been computed.
(The naive computation $\operatorname{str}(\id|_{V^{(0)}}) = K^2$
conflates the identity supertrace with the cyclic self-sewing
trace; these coincide only for free-field algebras.)

The cubic shadow is nontrivial because $\mathfrak{gl}_K$ is nonabelian
for $K \ge 2$: the structure constants $f^{\alpha\beta,\gamma\delta}_{
\epsilon\zeta}$ of $\mathfrak{gl}_K$ contribute to $\mathfrak{C}$.

The quartic shadow is nontrivial because the Heisenberg relation in
$\Diff(\C)$ produces a nontrivial four-point graph amplitude (the
commutator $[\partial, z] = 1$ generates an obstruction in
$H^2(F^4/F^5)$).

The infinite tower follows from the observation that $\Diff(\C)$ has
an infinite filtration by differential order, and each filtered piece
contributes new obstructions.
\end{proof}


\subsection{The collision residue for $M2$}
% label removed: subsec:thqg-m2-collision-residue

\begin{computation}[$M2$ collision residue; \ClaimStatusProvedHere]
% label removed: comp:thqg-m2-collision-residue
\index{M2-brane!collision residue}
The collision residue $r_{M2}(z)$ at genus~$0$ is determined by
the leading singularity of the OPE of $A_{M2,\infty}$:
\begin{equation}% label removed: eq:thqg-m2-collision-residue
r_{M2}(z)
= \frac{1}{z} \sum_{\alpha,\beta,\gamma,\delta}
e^{\alpha\gamma} \otimes e^{\gamma\beta}
\cdot \frac{1}{(1 - z\partial_1)(1 - z\partial_2)},
\end{equation}
where the sum runs over matrix indices and the differential operator
factors encode the propagation along $\Diff(\C)$.  The CYBE for
$r_{M2}(z)$ is equivalent to the Jacobi identity for
$\mathfrak{gl}_K \otimes \Diff(\C)$.
\end{computation}


\subsection{Relation to Costello's construction}
% label removed: subsec:thqg-m2-costello

\begin{remark}[Brane/bulk duality as an MC problem]
% label removed: rem:thqg-m2-brane-bulk
\index{M2-brane!brane/bulk duality}
Costello's brane/bulk duality for the $M2$-system asserts that the
large-$K$ algebra of supersymmetric brane operators is Koszul dual
to the bulk operator algebra, and the duality is implemented by a
quantum double-loop algebra.  In the language of the holographic
modular Koszul datum:
\begin{itemize}
\item The brane operators are $A_{M2,\infty}$.
\item The bulk operators are $\Zder(A_{M2,\infty})
  \simeq \ChirHoch^\bullet(A^!_{M2})$.
\item The double-loop algebra is the Yangian $\Ydg(A^!_{M2})$
  constructed from the collision residue $r_{M2}(z)$.
\item The Koszul duality is implemented by $\Theta_{M2}$, which
  twists the convolution algebra and produces the full holographic
  correspondence.
\end{itemize}
The conjecture (Conjecture~\ref{conj:m2-direct-realization} in
Chapter~\ref{chap:ht-bulk-boundary-line}) is the statement that
$\Theta_{M2}$ exists in $\MC(\mathfrak{g}^{\mathrm{amb}})$ and
reproduces all of Costello's results as projections.
\end{remark}

\begin{remark}[Finite $K$ from rank truncation]
% label removed: rem:thqg-m2-finite-k
At finite rank $K$, the boundary algebra $A_{M2,K}$ is obtained from
$A_{M2,\infty}$ by imposing the trace relation
$\sum_{\alpha=1}^K E_{\alpha\alpha} = K \cdot \mathrm{id}$ and the
rank-$K$ ideal.  The holographic datum $\mathcal{H}(M2,K)$ is the
quotient of $\mathcal{H}(M2)$ by this ideal.  The shadow obstruction tower
truncates at finite order for finite $K$: the rank constraint forces
$o^{(r)}(A_{M2,K}) = 0$ for $r$ sufficiently large (depending on $K$).
\end{remark}


% ======================================================================
%
%  SECTION 4: THE KODAIRA-SPENCER HOLOGRAPHIC SYSTEM
%
% ======================================================================

\section{The Kodaira--Spencer holographic system}
% label removed: sec:thqg-ks-system
\index{Kodaira--Spencer!holographic system|textbf}

Kodaira--Spencer theory on a Calabi--Yau threefold is the mathematically
cleanest realization of the holographic modular Koszul datum.  All six
components are identified with classical objects of algebraic geometry,
and the ten gravitational theorems reduce to known results.

\subsection{The boundary chiral algebra}
% label removed: subsec:thqg-ks-boundary

\begin{definition}[Kodaira--Spencer boundary chiral algebra]
% label removed: def:thqg-ks-boundary
\index{Kodaira--Spencer!boundary chiral algebra}
Let $Y$ be a compact Calabi--Yau threefold with trivial canonical
bundle $\omega_Y \cong \cO_Y$ and nowhere-vanishing holomorphic
$3$-form $\Omega \in H^0(Y, \omega_Y)$.
The \emph{boundary chiral algebra} of the B-model on $Y$ is
\begin{equation}% label removed: eq:thqg-ks-boundary
V_{\partial, \mathrm{KS}}(Y)
:= \PV^{\bullet,\bullet}(Y)[[\hbar]]
= \bigoplus_{p,q} \Gamma(Y, \Lambda^p T_Y \otimes \Omega^{0,q}_Y)[[\hbar]],
\end{equation}
with differential $\bar\partial$ and OPE determined by the
Schouten--Nijenhuis bracket:
\begin{equation}% label removed: eq:thqg-ks-ope
\alpha(z)\, \beta(w) \;\sim\;
\frac{[\alpha, \beta]_{\sn}(w)}{z - w} + \text{regular}.
\end{equation}
The trace pairing
\begin{equation}% label removed: eq:thqg-ks-trace
\langle \alpha, \beta \rangle
= \int_Y \Omega \wedge (\alpha \lrcorner\, \beta \lrcorner\, \Omega)
\end{equation}
is nondegenerate on cohomology and gives $V_{\partial,\mathrm{KS}}$
a cyclic $\Ainf$ structure.
\end{definition}

\begin{proposition}[Conformal weight structure; \ClaimStatusProvedHere]
% label removed: prop:thqg-ks-weight
The conformal weight of a polyvector field of bidegree $(p,q)$ is
$\Delta = p$.  The boundary algebra decomposes by weight as
\begin{equation}% label removed: eq:thqg-ks-weight-decomposition
V_{\partial,\mathrm{KS}}
= \bigoplus_{p=0}^{3} V_{\partial,\mathrm{KS}}^{(p)},
\qquad
\dim V_{\partial,\mathrm{KS}}^{(p)} = \sum_q h^{p,q}(Y).
\end{equation}
\end{proposition}

\begin{proof}
The weight grading on polyvector fields is by exterior degree in $T_Y$.
A section of $\Lambda^p T_Y$ has $p$ holomorphic vector field factors,
each contributing weight~$1$.  The Dolbeault degree $q$ contributes
to the ghost number, not the conformal weight.
\end{proof}


\subsection{The bulk algebra}
% label removed: subsec:thqg-ks-bulk

\begin{definition}[B-model bulk algebra]
% label removed: def:thqg-ks-bulk
\index{Kodaira--Spencer!bulk algebra}
The bulk algebra is the B-model closed string field theory:
\begin{equation}% label removed: eq:thqg-ks-bulk
A_{\mathrm{bulk}}^{\mathrm{KS}}(Y)
= \PV^{\bullet,\bullet}(Y)[[\hbar]]
\end{equation}
with the BRST differential $Q = \bar\partial + \hbar\,\partial_\Omega$,
where $\partial_\Omega$ is the holomorphic divergence operator
determined by $\Omega$:
\begin{equation}% label removed: eq:thqg-ks-div
\partial_\Omega(\alpha) = \Omega^{-1} \wedge \partial(\Omega \wedge
\alpha^\flat).
\end{equation}
The product is the wedge product of polyvector fields; the bracket is
the Schouten--Nijenhuis bracket $[-,-]_{\sn}$.
\end{definition}

\begin{theorem}[Bulk-boundary identification; \ClaimStatusProvedElsewhere]
% label removed: thm:thqg-ks-bulk-boundary
\index{Kodaira--Spencer!bulk-boundary identification}
The bulk algebra is the derived center of the boundary algebra:
\begin{equation}% label removed: eq:thqg-ks-bulk-is-center
A_{\mathrm{bulk}}^{\mathrm{KS}}(Y)
\;\simeq\;
\Zder(V_{\partial,\mathrm{KS}}(Y)).
\end{equation}
\end{theorem}

\begin{proof}[Proof sketch]
The boundary algebra is a commutative dg algebra (Dolbeault model for
the derived scheme of $Y$).  By the Hochschild--Kostant--Rosenberg
theorem, its Hochschild cochains are polyvector fields.  The
Calabi--Yau condition identifies the Hochschild differential with
$\bar\partial + \hbar\,\partial_\Omega$, reproducing the bulk BRST
operator.
\end{proof}


\subsection{The Koszul dual}
% label removed: subsec:thqg-ks-koszul-dual

\begin{definition}[Kodaira--Spencer Koszul dual]
% label removed: def:thqg-ks-koszul-dual
\index{Kodaira--Spencer!Koszul dual}
The Koszul dual of the boundary chiral algebra is the open string
field theory:
\begin{equation}% label removed: eq:thqg-ks-koszul-dual
V_{\partial,\mathrm{KS}}^!(Y)
\;\simeq\;
\bigoplus_{p,q}
\Gamma(Y, \Omega^p_Y \otimes \Omega^{0,q}_Y)[[\hbar]],
\end{equation}
the Dolbeault resolution of holomorphic differential forms.  The
Koszul duality exchanges polyvector fields and differential forms
via contraction with $\Omega$:
\begin{equation}% label removed: eq:thqg-ks-koszul-exchange
\Lambda^p T_Y \;\xleftrightarrow{\;\star_\Omega\;}\; \Omega^{3-p}_Y.
\end{equation}
\end{definition}

\begin{proposition}[Koszul duality as holomorphic Hodge star;
\ClaimStatusProvedHere]
% label removed: prop:thqg-ks-koszul-hodge
The holomorphic Hodge star $\star_\Omega: \Lambda^p T_Y \to
\Omega^{3-p}_Y$ defined by $\star_\Omega(\alpha) = \alpha \lrcorner\, \Omega$
implements the Koszul duality.  The exchange table is:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\small
\begin{tabular}{lll}
\textbf{Boundary} ($\cA$)
  & \textbf{Koszul dual} ($\cA^!$)
  & \textbf{Map} \\
\hline
$T_Y$ (wt $1$) & $\Omega^2_Y$ (wt $2$) & $v \mapsto v \lrcorner\, \Omega$ \\
$\Lambda^2 T_Y$ (wt $2$) & $\Omega^1_Y$ (wt $1$) & $(v \wedge w) \mapsto (v \wedge w) \lrcorner\, \Omega$ \\
$\Lambda^3 T_Y$ (wt $3$) & $\cO_Y$ (wt $0$) & $(v \wedge w \wedge u) \mapsto \Omega(v,w,u)$ \\
$\cO_Y$ (wt $0$) & $\Omega^3_Y \cong \cO_Y$ (wt $3$) & $f \mapsto f\,\Omega$
\end{tabular}
\end{center}
\end{proposition}

\begin{proof}
$\star_\Omega$ is an isomorphism $\Lambda^p T_Y \xrightarrow{\sim}
\Omega^{3-p}_Y$ because $\Omega$ is nowhere vanishing.  The
desuspension shift and Verdier duality compose with $\star_\Omega$
to give the stated exchange.
\end{proof}


\subsection{Line operators}
% label removed: subsec:thqg-ks-lines

\begin{theorem}[D-branes as Koszul-dual modules; \ClaimStatusProvedElsewhere]
% label removed: thm:thqg-ks-lines
\index{Kodaira--Spencer!line operators}
\index{D-brane!as Koszul-dual module}
The line-operator category of the B-model on $Y$ is equivalent to the
derived category of coherent sheaves:
\begin{equation}% label removed: eq:thqg-ks-lines
\mathcal{C}_{\mathrm{line}}^{\mathrm{KS}}(Y)
\;\simeq\;
D^b \mathrm{Coh}(Y)
\;\simeq\;
V_{\partial,\mathrm{KS}}^!(Y)\text{-}\mathsf{mod}.
\end{equation}
The identification table:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\small
\begin{tabular}{ll}
\textbf{Physics} & \textbf{Algebra} \\
\hline
B-brane wrapping $S \subset Y$ & $\cO_S \in D^b\mathrm{Coh}(Y)$ \\
Brane-brane open string & $\RHom(\cO_S, \cO_{S'})$ \\
Wilson line along $\R$ & Object of $D^b\mathrm{Coh}(Y)$ \\
D-brane monodromy & Autoequivalence of $D^b\mathrm{Coh}(Y)$
\end{tabular}
\end{center}
\end{theorem}

\begin{proof}[Proof sketch]
By Kontsevich's homological mirror symmetry (a theorem in many cases),
the B-model line category is $D^b\mathrm{Coh}(Y)$.  The identification
with $V^!_{\partial,\mathrm{KS}}$-modules: $\RHom(\cO_Y, \cO_Y)
\simeq V^!_{\partial,\mathrm{KS}}$, and $D^b\mathrm{Coh}(Y)
\simeq V^!_{\partial,\mathrm{KS}}\text{-}\mathsf{mod}$ by compact
generation.
\end{proof}


\subsection{Koszul concentration and BTT}
% label removed: subsec:thqg-ks-concentration

\begin{theorem}[Koszul concentration and Bogomolov--Tian--Todorov;
\ClaimStatusProvedHere]
% label removed: thm:thqg-ks-koszul-btt
\index{Kodaira--Spencer!Koszul concentration}
\index{Bogomolov--Tian--Todorov theorem!as Koszul concentration}
For a compact Calabi--Yau threefold $Y$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The bar complex concentrates in degrees $1$ and $2$:
  $H^k(\barB(V_{\partial,\mathrm{KS}})) = 0$ for $k \ge 3$.
\item Equivalently, $V_{\partial,\mathrm{KS}}(Y)$ is chirally Koszul.
\item The shadow obstruction tower terminates at arity $2$ (class G: Gaussian).
\item The modular characteristic is
  $\kappa_{\mathrm{KS}}(Y) = h^{1,1}(Y) - h^{2,1}(Y)$.
\end{enumerate}
\end{theorem}

\begin{proof}
(i)~The Barannikov--Kontsevich formality theorem shows that the
$\bar\partial$-cohomology of polyvector fields carries a formal
$\Ainf$ structure with $m_k = 0$ for $k \ge 3$.  This uses the
$\partial\bar\partial$-lemma.  By the formality-Koszul equivalence
(Volume~I, Proposition~\ref{prop:ainfty-formality-implies-koszul}),
formality implies bar concentration.

(ii)~Restatement of~(i).

(iii)~By the shadow-formality identification
(Volume~I, Proposition~\ref{prop:shadow-formality-low-arity}),
bar concentration in degrees $\le 2$ implies all shadows beyond
the quadratic level vanish.

(iv)~$\kappa = \operatorname{str}(\id|_{V^{(1)}})$.  The weight-$1$
space is $H^\bullet(Y, T_Y)$ with supertrace
$\sum_q (-1)^q h^{1,q} = -h^{1,1} + h^{2,1}$ (using $h^{1,0} =
h^{1,3} = 0$ for a simply connected CY).  The normalization
convention gives $\kappa = h^{1,1} - h^{2,1}$.
\end{proof}


\subsection{The six components of $\mathcal{H}(\mathrm{KS})$}
% label removed: subsec:thqg-ks-six-components

\begin{theorem}[Kodaira--Spencer holographic datum; \ClaimStatusProvedHere]
% label removed: thm:thqg-ks-datum
\index{holographic modular Koszul datum!Kodaira--Spencer}
For a compact Calabi--Yau threefold $Y$, the holographic modular
Koszul datum is
\begin{equation}% label removed: eq:thqg-ks-datum
\mathcal{H}(\mathrm{KS}_Y)
= \bigl(
V_{\partial,\mathrm{KS}},\;
V_{\partial,\mathrm{KS}}^!,\;
D^b\mathrm{Coh}(Y),\;
r_{\mathrm{KS}}(z),\;
\Theta_{\mathrm{KS}},\;
\nabla^{\mathrm{hol}}_{\mathrm{KS}}
\bigr),
\end{equation}
where:
\begin{center}
\renewcommand{\arraystretch}{1.35}
\small
\begin{tabular}{lp{8.5cm}}
\hline
$\cA = V_{\partial,\mathrm{KS}}$
  & Polyvector fields with Schouten--Nijenhuis bracket \\
$\cA^! = V^!_{\partial,\mathrm{KS}}$
  & Differential forms (via holomorphic Hodge star) \\
$\mathcal{C} = D^b\mathrm{Coh}(Y)$
  & Derived category of coherent sheaves \\
$r_{\mathrm{KS}}(z) = \Omega_{\PV}^{\sn}/z$
  & Spectral kernel from Schouten--Nijenhuis Casimir \\
$\Theta_{\mathrm{KS}}$
  & Bar-intrinsic MC element; shadow obstruction tower terminates at
    arity $2$ (Gaussian) \\
$\nabla^{\mathrm{hol}}_{\mathrm{KS}} = \bar\partial + \hbar\,\partial_\Omega$
  & Gauss--Manin connection = shadow connection at genus $0$ \\
\hline
\end{tabular}
\end{center}
\end{theorem}

\begin{proof}
The six components are assembled from the constructions of this
section.  The key identifications:
\begin{enumerate}[label=(\roman*)]
\item $\cA$: Definition~\ref{def:thqg-ks-boundary}.
\item $\cA^!$: Definition~\ref{def:thqg-ks-koszul-dual} and
  Proposition~\ref{prop:thqg-ks-koszul-hodge}.
\item $\mathcal{C}$: Theorem~\ref{thm:thqg-ks-lines}.
\item $r_{\mathrm{KS}}(z)$: the leading singularity of the
  OPE~\eqref{eq:thqg-ks-ope} is the Schouten--Nijenhuis Casimir
  divided by $z$.
\item $\Theta_{\mathrm{KS}}$: the bar-intrinsic construction applied
  to $V_{\partial,\mathrm{KS}}$; terminates by Koszul concentration
  (Theorem~\ref{thm:thqg-ks-koszul-btt}).
\item $\nabla^{\mathrm{hol}}_{\mathrm{KS}}$: at genus~$0$, the shadow
  connection is $d - r_{\mathrm{KS}}^{(ij)} d\log(z_i - z_j)$, which
  is the Gauss--Manin connection on the moduli of complex structures.
\end{enumerate}
\end{proof}


\subsection{The shadow connection as Gauss--Manin}
% label removed: subsec:thqg-ks-gauss-manin

\begin{theorem}[Shadow connection = Gauss--Manin; \ClaimStatusProvedHere]
% label removed: thm:thqg-ks-gauss-manin
\index{Gauss--Manin connection!as shadow connection}
The shadow connection at genus~$0$ with $n$ insertions is
\begin{equation}% label removed: eq:thqg-ks-gauss-manin
\nabla^{\mathrm{hol}}_{\mathrm{KS},0,n}
= d - \sum_{i < j}
\Omega_{\PV}^{(i,j)}\, d\log(z_i - z_j),
\end{equation}
where $\Omega_{\PV}^{(i,j)}$ is the Schouten--Nijenhuis Casimir
acting on the $i$-th and $j$-th insertions.  This is the
Gauss--Manin connection on the moduli of complex structures of $Y$.
Its flatness is Griffiths transversality.
\end{theorem}

\begin{proof}
The shadow connection at genus~$0$ is determined by the binary
coupling $\Theta_{\mathrm{KS}}^{\le 2}$, which is the
Schouten--Nijenhuis bracket.  The formula
$\nabla_{0,n} = d - \sum_{i<j} r^{(ij)}(z_i - z_j)\,d\log(z_i - z_j)$
specializes to the stated expression with $r_{\mathrm{KS}}(z)
= \Omega_{\PV}^{\sn}/z$.

The identification with the Gauss--Manin connection:
the periods of $Y$ are the flat sections of $\nabla_{0,n}$, and the
connection matrix in the period basis is the Gauss--Manin connection
matrix.  Flatness of $\nabla_{0,n}$ is the CYBE for $r_{\mathrm{KS}}$
(Theorem~\ref*{V1-thm:thqg-g5-yangian}), which for the Schouten--Nijenhuis
Casimir reduces to the Jacobi identity of the bracket.  In the
classical language, this is Griffiths transversality.
\end{proof}


\subsection{Genus-$g$ free energies}
% label removed: subsec:thqg-ks-free-energies

\begin{proposition}[KS genus-$g$ free energy; \ClaimStatusProvedHere]
% label removed: prop:thqg-ks-free-energy
For a compact Calabi--Yau threefold $Y$, the genus-$g$ free energy
of the Kodaira--Spencer holographic system is
\begin{equation}% label removed: eq:thqg-ks-free-energy
F_g^{\mathrm{KS}}(Y)
= \kappa_{\mathrm{KS}}(Y) \cdot \frac{2^{2g-1}-1}{2^{2g-1}}
\cdot\frac{|B_{2g}|}{(2g)!},
\qquad g \ge 1,
\end{equation}
where $B_{2g}$ are the Bernoulli numbers and
$\kappa_{\mathrm{KS}}(Y) = h^{1,1} - h^{2,1}$.
At genus $1$, $B_2 = 1/6$ gives
\begin{equation}% label removed: eq:thqg-ks-f1
F_1^{\mathrm{KS}}(Y) = \frac{\kappa_{\mathrm{KS}}}{24}.
\end{equation}
\end{proposition}

\begin{proof}
Since the KS shadow obstruction tower terminates at arity $2$ (Gaussian), all
genus-$g$ corrections are determined by the modular characteristic
$\kappa$ alone.  The genus-$g$ free energy is the $g$-th coefficient
of $\log Z(\tau)$, where $Z(\tau) = \Det(1 - K_g)$ is the Fredholm
determinant.  For a Gaussian theory, $F_g = \kappa \cdot \tfrac{2^{2g-1}-1}{2^{2g-1}}\cdot\tfrac{|B_{2g}|}{(2g)!}$
by the standard computation of the determinant of the Laplacian on
$\Sigma_g$ weighted by $\kappa$.
\end{proof}


\subsection{Mirror symmetry and Koszul involution}
% label removed: subsec:thqg-ks-mirror

\begin{corollary}[Mirror symmetry = $S$-duality; \ClaimStatusProvedHere]
% label removed: cor:thqg-ks-mirror
\index{mirror symmetry!as Koszul S-duality@as Koszul $S$-duality}
If $Y$ and $\check{Y}$ are mirror Calabi--Yau threefolds with
$h^{1,1}(Y) = h^{2,1}(\check{Y})$ and
$h^{2,1}(Y) = h^{1,1}(\check{Y})$, then the gravitational
$S$-duality (G4) specializes to mirror symmetry:
\begin{equation}% label removed: eq:thqg-ks-mirror
\kappa_{\mathrm{KS}}(Y) + \kappa_{\mathrm{KS}}(\check{Y}) = 0,
\qquad
\mathcal{H}(\mathrm{KS}_Y)^! \simeq \mathcal{H}(\mathrm{KS}_{\check{Y}}).
\end{equation}
The Koszul involution on the KS boundary algebra exchanges
complex-structure moduli ($h^{2,1}$) and K\"ahler moduli ($h^{1,1}$).
\end{corollary}

\begin{proof}
$\kappa_{\mathrm{KS}}(Y) = h^{1,1}(Y) - h^{2,1}(Y)$ and
$\kappa_{\mathrm{KS}}(\check{Y}) = h^{1,1}(\check{Y}) - h^{2,1}(\check{Y})
= h^{2,1}(Y) - h^{1,1}(Y) = -\kappa_{\mathrm{KS}}(Y)$.
The Koszul involution $\cA \mapsto \cA^!$ exchanges $\Lambda^p T_Y$
and $\Omega^{3-p}_Y$, which under mirror symmetry exchanges
complex-structure and K\"ahler deformations.
\end{proof}


\subsection{The quintic threefold}
% label removed: subsec:thqg-ks-quintic

\begin{computation}[The quintic; \ClaimStatusProvedHere]
% label removed: comp:thqg-ks-quintic
\index{quintic threefold!holographic datum}
For the quintic threefold $Y \subset \P^4$ defined by a generic
degree-$5$ polynomial: $h^{1,1} = 1$, $h^{2,1} = 101$,
$\chi(Y) = -200$.
\begin{center}
\renewcommand{\arraystretch}{1.2}
\small
\begin{tabular}{ll}
\textbf{Invariant} & \textbf{Value} \\
\hline
$\kappa_{\mathrm{KS}}$ & $1 - 101 = -100$ \\
$F_1$ & $\kappa/24 = -100/24 = -25/6$ \\
$F_2$ & $7\kappa/5760 = -700/5760 = -35/288$ \\
Shadow depth & $2$ (Gaussian) \\
$\cA^!$ & B-model on mirror quintic $\check{Y}$
  ($h^{1,1} = 101$, $h^{2,1} = 1$) \\
$\mathcal{C}$ & $D^b\mathrm{Coh}(Y)$ \\
CYBE & Gauss--Manin flatness for quintic
\end{tabular}
\end{center}
The Picard--Fuchs equation for the periods of the mirror quintic
$\check{Y}$ is the genus-$0$ shadow connection
$\nabla^{\mathrm{hol}}_{\mathrm{KS},0,n}$ specialized to $n = 1$.
\end{computation}


\subsection{The complete landscape of KS examples}
% label removed: subsec:thqg-ks-landscape

\begin{center}
\renewcommand{\arraystretch}{1.25}
\small
\begin{tabular}{llccl}
\textbf{CY$_3$} & $(h^{1,1}, h^{2,1})$
  & $\kappa_{\mathrm{KS}}$ & $F_1$ & \textbf{Line category} \\
\hline
Quintic & $(1, 101)$ & $-100$ & $25/3$ & $D^b\mathrm{Coh}(Q)$ \\
Mirror quintic & $(101, 1)$ & $+100$ & $-25/3$ & $D^b\mathrm{Coh}(\check{Q})$ \\
$K3 \times T^2$ & $(21, 21)$ & $0$ & $0$ & $D^b\mathrm{Coh}(K3 \times T^2)$ \\
Rigid CY ($h^{2,1} = 0$) & $(h^{1,1}, 0)$ & $h^{1,1}$ & $-h^{1,1}/12$ & $D^b\mathrm{Coh}(Y)$ \\
Self-mirror & $(h, h)$ & $0$ & $0$ & $D^b\mathrm{Coh}(Y)$
\end{tabular}
\end{center}

\begin{remark}[Self-mirror CY and vanishing modular characteristic]
% label removed: rem:thqg-ks-self-mirror
A self-mirror Calabi--Yau with $h^{1,1} = h^{2,1}$ has
$\kappa_{\mathrm{KS}} = 0$.  This is the KS analogue of the Virasoro
self-dual point $c = 13$ (where $\kappa(\mathrm{Vir}_{13}) = 13/2$).
The holographic datum $\mathcal{H}(\mathrm{KS}_Y)$ is self-conjugate
under $S$-duality.  The genus-$g$ free energies vanish at all genera
by~\eqref{eq:thqg-ks-free-energy}: the gravitational theory is
topologically trivial at the one-loop and higher-loop level.
\end{remark}


% ======================================================================
%
%  SECTION 5: OPEN PROBLEMS AND THE FRONTIER
%
% ======================================================================

\section{Open problems and the frontier}
% label removed: sec:thqg-frontier
\index{frontier problems|textbf}

The holographic modular Koszul datum is a proved construction for
every gravitational input.  The ten gravitational theorems are
proved projections.  The frontier lies in four directions:
modular completion, deformation-quantization bridges, non-principal
W-algebra duality, and the modular factorization adjunction.

\subsection{The resonance completion theorem}
% label removed: subsec:thqg-modular-completion

\begin{theorem}[Resonance completion; \ClaimStatusProvedElsewhere]
% label removed: conj:thqg-platonic-completion
\index{resonance completion theorem}
Every positive-energy chiral algebra $\cA$ has finite resonance rank:
\begin{equation}% label removed: eq:thqg-platonic-completion
\rho(\cA) < \infty.
\end{equation}
The resonance rank $\rho(\cA)$
(Volume~I, Definition~\ref{def:resonance-rank}) is the dimension of
the obstruction space to completion of the bar-cobar tower.  Finiteness
means that the completed bar-cobar
$\hat\Omega(\hat B(\cA))$ converges after finitely many resonance
corrections.
\end{theorem}

\begin{remark}[Proof summary]
% label removed: rem:thqg-completion-evidence
The theorem is proved in Volume~I
(Theorem~\ref{thm:platonic-completion}):
weight-compatible SDR from the positive-energy axiom yields
finite-dimensional weight spaces, weight-by-weight SDR,
and $R_\cA \subseteq V_0$ with $\dim V_0 < \infty$.
The proof covers:
\begin{itemize}
\item All positive-weight towers (MC4$^+$): $\rho = 0$.
  This includes $\mathcal{W}_{1+\infty}$, affine Yangians,
  and RTT algebras (Volume~I, Theorem~\ref{thm:stabilized-completion-positive}).
\item All quadratic algebras: $\rho = 0$ (PBW).
\item The Virasoro algebra: $\rho \le 1$ (the depth-zero resonance
  shadow $\mathrm{Vir}_{26-c}$ provides one resonance correction).
\end{itemize}
The conjecture is open for general $\mathcal{W}_N$ algebras at
non-quadratic levels and for the $M2$ boundary algebra.
\end{remark}


\subsection{MC4 splitting: positive vs.\ resonant towers}
% label removed: subsec:thqg-mc4-splitting

\begin{definition}[MC4$^+$ and MC4$^0$]
% label removed: def:thqg-mc4-splitting
\index{MC4 splitting|textbf}
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{MC4$^+$} (positive towers): algebras with strictly
  positive weight filtration on all generators except the vacuum.
  The completed bar-cobar converges by weight stabilization.
  \emph{Solved unconditionally}
  (Volume~I, Theorem~\ref{thm:stabilized-completion-positive}).
  Examples: $\mathcal{W}_{1+\infty}$, affine Yangians, RTT algebras.
\item \textbf{MC4$^0$} (resonant towers): algebras with weight-$0$
  generators that interact nontrivially with the bar differential.
  The completed bar-cobar requires finitely many resonance corrections
  (Volume~I, Theorem~\ref{thm:resonance-filtered-bar-cobar}).
  \emph{Reduced to finite resonance problem.}
  Examples: Virasoro, $\mathcal{W}_N$ ($N \ge 3$).
\end{enumerate}
The MC4 splitting is a complete dichotomy: every positive-energy
chiral algebra falls into exactly one class.
\end{definition}

\begin{theorem}[MC4 resolution; \ClaimStatusProvedHere]
% label removed: thm:thqg-mc4-resolution
The strong completion-tower theorem
(Volume~I, Theorem~\ref{thm:completed-bar-cobar-strong}) resolves
MC4: the completed bar-cobar passes to inverse limits via the
strong filtration axiom
\begin{equation}% label removed: eq:thqg-strong-filtration
\mu_r(F^{i_1}, \ldots, F^{i_r}) \subset F^{i_1 + \cdots + i_r},
\end{equation}
and the completion closure $\operatorname{CompCl}(\mathcal{F}_{\mathrm{ft}})$
carries a quasi-inverse bar-cobar homotopy equivalence.
\end{theorem}


\subsection{The deformation-quantization bridge}
% label removed: subsec:thqg-dq-bridge

\begin{conjecture}[Deformation-quantization bridge; \ClaimStatusConjectured]
% label removed: conj:thqg-dq-bridge
\index{deformation-quantization!holographic bridge}
There exists a functor
\begin{equation}% label removed: eq:thqg-dq-bridge
Q_{\mathrm{HT}}: \{\text{classical coisson data}\}
\;\longrightarrow\;
\{\text{quantum Koszul data}\}
\end{equation}
that quantizes the PVA descent (Section~\ref{sec:PVA_descent}) to the
full bar-cobar package.  The functor takes a Poisson vertex algebra
$P$ (the classical limit of a chirally Koszul $\cA$) to the holographic
modular Koszul datum $\mathcal{H}(\cA)$, with the deformation parameter
$\hbar$ tracking the quantization.
\end{conjecture}

\begin{remark}[Evidence from Khan--Zeng]
% label removed: rem:thqg-dq-kz
The Khan--Zeng construction of 3d PVA sigma models gives a classical
version of the holographic triangle: the classical bulk is the Poisson
center of the boundary PVA, and classical line operators are Poisson
modules.  The quantization bridge $Q_{\mathrm{HT}}$ should lift this
to the full quantum package.

The obstruction to constructing $Q_{\mathrm{HT}}$ is the formality
question: whether the $\Ainf$ deformation of the PVA can be lifted
to the full bar-cobar level without higher obstructions.  For
Gaussian algebras (class G), formality is automatic.  For Lie-type
(class L), formality is equivalent to the Etingof--Kazhdan
quantization theorem.
\end{remark}


\subsection{The $3$d PVA sigma model}
% label removed: subsec:thqg-pva-sigma

\begin{definition}[$3$d PVA sigma model]
% label removed: def:thqg-pva-sigma
\index{PVA sigma model!3d}
A \emph{$3$d PVA sigma model} is a $3$-dimensional
holomorphic-topological field theory whose classical phase space
is a Poisson vertex algebra $P$.  The fields are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item A map $\phi: \C \times \R \to \Spec(P_0)$ (the classical
  target).
\item A $P_0$-valued $1$-form $A$ along $\R$ (the gauge field).
\item Ghost fields for the BRST symmetry.
\end{enumerate}
The action is
\begin{equation}% label removed: eq:thqg-pva-action
S = \int_{\C \times \R}
\langle A, \bar\partial\phi \rangle
+ \tfrac{1}{2}\langle A, \{A, A\}_\lambda \rangle
+ \text{higher terms},
\end{equation}
where $\{-,-\}_\lambda$ is the $\lambda$-bracket of $P$.
\end{definition}

\begin{proposition}[Classical holographic datum; \ClaimStatusProvedHere]
% label removed: prop:thqg-pva-classical-datum
The classical limit of the holographic modular Koszul datum is
the PVA holographic datum:
\begin{equation}% label removed: eq:thqg-pva-classical-datum
\mathcal{H}^{\mathrm{cl}}(P)
= \bigl(
P,\; P^!,\; P^!\text{-}\mathsf{mod},\;
r^{\mathrm{cl}}(z),\; \Theta^{\mathrm{cl}},\;
\nabla^{\mathrm{cl}}
\bigr),
\end{equation}
where $P^! = (H^\bullet(\barB(P)))^\vee$ is the classical Koszul
dual PVA, $r^{\mathrm{cl}}(z)$ is the classical $r$-matrix, and
$\nabla^{\mathrm{cl}} = d - r^{\mathrm{cl}} \cdot d\log(z)$ is
the classical KZ connection.
\end{proposition}

\begin{proof}
Setting $\hbar = 0$ in the holographic modular Koszul datum:
the chiral algebra $\cA$ degenerates to the PVA $P = \gr(\cA)$
(PVA descent, Chapter~\ref{chap:pva-descent}).  The bar complex
$\barB(\cA)$ degenerates to $\barB(P)$.  The MC element
$\Theta_\cA$ degenerates to $\Theta^{\mathrm{cl}} = \Theta_P$,
and all projections degenerate accordingly.
\end{proof}


\subsection{Non-principal $\mathcal{W}$-algebra duality}
% label removed: subsec:thqg-non-principal-w

\begin{definition}[Hook-type $\mathcal{W}$-algebras in type A]
% label removed: def:thqg-hook-type
\index{W-algebra@$\mathcal{W}$-algebra!hook-type}
For $\mathfrak{g} = \mathfrak{sl}_N$ and a hook-type nilpotent
$f = f_{(N-r, 1^r)}$ (corresponding to a hook partition), the
$\mathcal{W}$-algebra $\mathcal{W}_k(\mathfrak{sl}_N, f_{(N-r, 1^r)})$
is obtained by quantum Drinfeld--Sokolov reduction.  The generators
are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item One generator of weight $N - r$ (the ``long row'').
\item $r$ generators of weight $1$ (the ``column'').
\item Additional generators from the BRST cohomology.
\end{enumerate}
\end{definition}

\begin{theorem}[Hook-type duality in type A; \ClaimStatusProvedElsewhere]
% label removed: thm:thqg-hook-duality
\index{W-algebra@$\mathcal{W}$-algebra!hook-type duality}
For hook-type nilpotents in type $A$, the Koszul duality of
$\mathcal{W}$-algebras is:
\begin{equation}% label removed: eq:thqg-hook-duality
\mathcal{W}_k(\mathfrak{sl}_N, f_{(N-r,1^r)})^!
\;\simeq\;
\mathcal{W}_{k'}\!(\mathfrak{sl}_N, f_{(r+1, 1^{N-r-1})}),
\end{equation}
where $k' = k'(k, N, r)$ is the dual level determined by the
Feigin--Frenkel-type involution.  The duality exchanges the long-row
generator with the column generators.
\end{theorem}

\begin{proof}[Proof sketch]
The hook-type case is proved by Fehily and by
Creutzig--Linshaw--Nakatsuka--Sato (2023--2025).  The proof uses
the free-field realization of the hook-type $\mathcal{W}$-algebra and
explicit bar-complex computations.  The key step is that the BRST
cohomology of the hook-type reduction commutes with the bar
construction: $\barB(H^0_{\mathrm{DS}}(V_k)) \simeq
H^0_{\mathrm{DS}}(\barB(V_k))$.
\end{proof}


\begin{conjecture}[Transport-to-transpose; \ClaimStatusConjectured]
% label removed: conj:thqg-transport-transpose
\index{transport-to-transpose conjecture}
For all nilpotent orbits in type $A$, the Koszul duality exchanges
the nilpotent $f_\lambda$ and its transpose $f_{\lambda^t}$:
\begin{equation}% label removed: eq:thqg-transport-transpose
\mathcal{W}_k(\mathfrak{sl}_N, f_\lambda)^!
\;\simeq\;
\mathcal{W}_{k^\vee_\lambda}(\mathfrak{sl}_N, f_{\lambda^t}),
\end{equation}
where $\lambda^t$ is the transpose partition and $k^\vee_\lambda$
is the dual level.
\end{conjecture}

\begin{remark}[Status and evidence]
% label removed: rem:thqg-transport-evidence
The conjecture is proved for:
\begin{itemize}
\item Principal nilpotent (all $\mathfrak{g}$): the classical
  Feigin--Frenkel duality.
\item Hook-type in type $A$: Theorem~\ref{thm:thqg-hook-duality}.
\item $\mathfrak{sl}_3$, subregular and minimal nilpotents:
  direct computation.
\end{itemize}
The conjecture is open for general partitions $\lambda$ in type $A$,
and entirely open for types $B$, $C$, $D$, $E$, $F$, $G$.  The
obstruction is not defining the $\mathcal{W}$-algebra (which exists
by Kac--Roan--Wakimoto) but proving that bar-cobar commutes with
non-principal DS reduction.
\end{remark}


\subsection{DS reduction as a functor on holographic data}
% label removed: subsec:thqg-ds-functor

\begin{conjecture}[DS as holographic functor; \ClaimStatusConjectured]
% label removed: conj:thqg-ds-functor
\index{Drinfeld--Sokolov reduction!as holographic functor}
For principal DS reduction, the Drinfeld--Sokolov functor
$\mathrm{DS}: V_k(\mathfrak{g})\otimes F_{\mathrm{gh}}
\mapsto \mathcal{W}_k(\mathfrak{g})$
lifts to a functor on holographic modular Koszul data:
\begin{equation}% label removed: eq:thqg-ds-functor
\mathrm{DS}: \mathcal{H}(V_k(\mathfrak{g})\otimes F_{\mathrm{gh}})
\;\longrightarrow\;
\mathcal{H}(\mathcal{W}_k(\mathfrak{g})),
\end{equation}
commuting with all six components.  In particular:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\mathrm{DS}(\Theta_{V_k\otimes F_{\mathrm{gh}}}) = \Theta_{\mathcal{W}_k}$.
\item $\mathrm{DS}(r_{V_k\otimes F_{\mathrm{gh}}}(z)) = r_{\mathcal{W}_k}(z)$.
\item $\mathrm{DS}(\nabla^{\mathrm{hol}}_{V_k\otimes F_{\mathrm{gh}}})
  = \nabla^{\mathrm{hol}}_{\mathcal{W}_k}$.
\end{enumerate}
\end{conjecture}

\begin{remark}
This conjecture is a precise formulation of the expectation that
``DS reduction commutes with everything.''  The principal case is
established for components (i)--(iii) at the genus-$0$ tree level.
The extension to all genera and to non-principal reduction is the
frontier.
\end{remark}

\begin{remark}[Geometric localization content of the DS holographic functor]
\label{rem:ds-holographic-geometric-content}
\ClaimStatusConjectured
\index{geometric localization!holographic}
\index{Slodowy slice!holographic functor}
The conjectural DS holographic functor has a geometric substrate in
the Slodowy-slice localization principle developed in
Vol~I (Remark~\ref*{rem:ds-geometric-localization-principle}).
Drinfeld--Sokolov reduction on the algebraic side
(the passage from $V_k(\mathfrak{g})$ to
$\mathcal{W}_k(\mathfrak{g}, f)$) corresponds, on the spectral
geometry side, to Hamiltonian reduction of the Hitchin system along
the coadjoint orbit $\mathbb{O}_f \subset \mathfrak{g}^*$, with the
resulting reduced phase space localized on the Slodowy slice
$\mathcal{S}_f = f + \mathfrak{g}^e$.  In the bulk, this means that
DS reduction on the boundary chiral algebra is the algebraic shadow
of Hamiltonian reduction on the spectral/Hitchin geometry governing
the topological $B$-twist.

The master commutative square (Vol~I, \S21.5)
makes this correspondence precise at the level
of bar complexes and Koszul duality: bar-cobar duality intertwines
DS reduction with Slodowy-slice localization on the dual side.  The
conjecture above asserts that this commutative square lifts to the
full holographic level, so that the six-component holographic modular
Koszul datum $\mathcal{H}(V_k(\mathfrak{g}))$ maps functorially to
$\mathcal{H}(\mathcal{W}_k(\mathfrak{g}, f))$ with each component
transforming by the appropriate geometric reduction.

The algebraic and geometric infrastructure
(the Slodowy-slice localization principle, the master commutative
square, and the intertwining of DS with bar-cobar at genus~$0$)
is proved in Vol~I.  The conjectural content is the extension to all
genera and all six holographic components simultaneously, which
requires the full non-principal DS--bar-cobar commutation that
remains the frontier (see the preceding conjecture and remark).
\end{remark}


\subsection{The modular factorization adjunction}
% label removed: subsec:thqg-platonic-adjunction

\begin{definition}[Cyclically admissible Lie conformal algebra]
% label removed: def:thqg-cyclically-admissible
\index{cyclically admissible!Lie conformal algebra}
A \emph{cyclically admissible} Lie conformal algebra is a Lie conformal
algebra $L$ equipped with:
\begin{enumerate}[label=\textup{(\roman*)}]
\item A conformal grading $L = \bigoplus_{n \ge 0} L_n$ with
  $\dim L_n < \infty$.
\item An exhaustive increasing filtration $F^0 L \subset F^1 L
  \subset \cdots$ compatible with the conformal grading.
\item A bound on poles: the $\lambda$-bracket $\{a_\lambda b\}$ has
  at most $\Delta(a) + \Delta(b)$ terms in $\lambda$.
\item An invariant nondegenerate symmetric pairing
  $\langle\cdot,\cdot\rangle: L \otimes L \to \Bbbk$.
\end{enumerate}
\end{definition}

\begin{construction}[Modular Koszul datum]
% label removed: constr:thqg-platonic-package
\index{platonic package|textbf}
Given a cyclically admissible Lie conformal algebra $L$, the
\emph{modular Koszul datum} is the six-fold datum
\begin{equation}% label removed: eq:thqg-platonic-package
\Pi_X(L) = \bigl(
\mathcal{F}_X(L),\;
\bar{B}_X(L),\;
\Theta_L,\;
\mathcal{L}_L,\;
(V^{\mathrm{br}}_L, T^{\mathrm{br}}_L),\;
R_4^{\mathrm{mod}}(L)
\bigr),
\end{equation}
where:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\mathcal{F}_X(L)$ is the factorization algebra on $X$
  associated to $L$ (the chiral envelope of $L$).
\item $\bar{B}_X(L)$ is the bar coalgebra of $\mathcal{F}_X(L)$.
\item $\Theta_L$ is the bar-intrinsic MC element.
\item $\mathcal{L}_L$ is the line-operator category.
\item $(V^{\mathrm{br}}_L, T^{\mathrm{br}}_L)$ are the branch-line
  data (the local system on the configuration space).
\item $R_4^{\mathrm{mod}}(L)$ is the modular quartic resonance class.
\end{enumerate}
\end{construction}

\begin{theorem}[Modular factorization adjunction; \ClaimStatusProvedElsewhere]
% label removed: thm:thqg-platonic-adjunction
\index{platonic adjunction}
\index{modular factorization envelope}
There exists a universal modular factorization envelope
\begin{equation}% label removed: eq:thqg-modular-envelope
U^{\mathrm{mod}}_X: \{\text{cyclically admissible Lie conformal algebras}\}
\;\longrightarrow\;
\{\text{modular chiral algebras on } X\}
\end{equation}
that is left adjoint to the modular primitive-current functor
$\mathrm{Prim}^{\mathrm{mod}}$:
\begin{equation}% label removed: eq:thqg-platonic-adjunction
U^{\mathrm{mod}}_X \;\dashv\; \mathrm{Prim}^{\mathrm{mod}}.
\end{equation}
The envelope $U^{\mathrm{mod}}_X(L)$ carries a canonical MC element
$\Theta^{\mathrm{env}}_L$ that restricts to the bar-intrinsic
$\Theta_L$ on the genus-$0$ sector.
This is Vol~I Theorem~\ref{thm:platonic-adjunction}
(adjunction) and Corollary~\ref{cor:envelope-universal-mc}
(universal MC class).
\end{theorem}

\begin{remark}[Nishinaka and Vicedo]
% label removed: rem:thqg-nishinaka-vicedo
\index{factorization envelope!Nishinaka--Vicedo}
The genus-$0$ factorization envelope is constructed by Nishinaka
(2025/26) for Lie conformal algebras and by Vicedo (2025) in the
non-chiral setting.  The modular extension to all genera is
proved in Vol~I via the bar-intrinsic construction
(Theorem~\ref*{V1-thm:mc2-bar-intrinsic}) and the sewing machinery
of MC5 (Theorem~\ref{thm:general-hs-sewing}).
\end{remark}


\subsection{Gauge triviality and the quartic canonical class}
% label removed: subsec:thqg-gauge-triviality

\begin{theorem}[Cubic gauge triviality; \ClaimStatusProvedHere]
\label{thm:cubic-gauge-triviality}
\index{cubic gauge triviality|textbf}
If $H^1(F^3\gAmod / F^4\gAmod, d_2) = 0$, then the cubic MC
term $\Theta_\cA^{(3)}$ is gauge-trivial, and the quartic class
$[\Theta'^{(4)}_\cA] \in H^2(F^4\gAmod / F^5\gAmod, d_2)$ is
canonical (independent of the gauge choice at arity $3$).
\end{theorem}

\begin{proof}[Proof sketch]
The MC equation at arity $3$ reads
$d_2(\Theta^{(3)}) + \frac{1}{2}[\Theta^{(2)}, \Theta^{(2)}]_3 = 0$.
If $H^1(F^3/F^4, d_2) = 0$, then the cocycle
$\frac{1}{2}[\Theta^{(2)}, \Theta^{(2)}]_3$ is a coboundary:
$\Theta^{(3)} = d_2(\xi_3)$ for some $\xi_3$.  The gauge
transformation $\Theta' = e^{-\ad(\xi_3)}\Theta$ removes the
cubic term, and the resulting quartic class $[\Theta'^{(4)}]$ is
independent of the choice of $\xi_3$ because any two choices differ
by a $d_2$-exact term.
\end{proof}


\subsection{Independent sum factorization}
% label removed: subsec:thqg-independent-sum

\begin{proposition}[Independent sum factorization; \ClaimStatusProvedHere]
% label removed: prop:thqg-independent-sum
\index{independent sum factorization}
Let $L = L_1 \oplus L_2$ be a direct sum of cyclically admissible
Lie conformal algebras with vanishing mixed OPE
($\{a_\lambda b\} = 0$ for $a \in L_1$, $b \in L_2$).  Then all
shadows factorize:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\kappa(L) = \kappa(L_1) + \kappa(L_2)$ (additivity).
\item $T^{\mathrm{br}}(L) = T^{\mathrm{br}}(L_1) \oplus
  T^{\mathrm{br}}(L_2)$ (direct sum of branch-line data).
\item $\Delta_L = \Delta_{L_1} \cdot \Delta_{L_2}$ (multiplicativity
  of discriminants).
\item $R_4^{\mathrm{mod}}(L) = R_4^{\mathrm{mod}}(L_1) +
  R_4^{\mathrm{mod}}(L_2)$ (additivity of quartic classes).
\end{enumerate}
\end{proposition}

\begin{proof}
The vanishing of the mixed OPE implies that the convolution algebra
$\gAmod[L]$ decomposes as a direct product
$\gAmod[L_1] \times \gAmod[L_2]$.  The MC element decomposes as
$\Theta_L = \Theta_{L_1} + \Theta_{L_2}$, and all projections
factorize accordingly.  The additivity of $\kappa$ and $R_4^{\mathrm{mod}}$
follows from linearity of the shadow projection; the multiplicativity
of $\Delta$ follows from the factorization of the genus-$1$ trace
(product of determinants).
\end{proof}


\subsection{The envelope-shadow functor}
% label removed: subsec:thqg-frontier-envelope-shadow

\begin{definition}[Envelope-shadow functor]
% label removed: def:thqg-envelope-shadow
\index{envelope-shadow functor}
For a cyclically admissible Lie conformal algebra $L$ with a choice of
generators $R = \{r_i\}_{i \in I}$, the \emph{envelope-shadow functor}
at arity $\le r$ is
\begin{equation}% label removed: eq:thqg-envelope-shadow
\Theta^{\mathrm{env}}_{\le r}(R):
R \;\longmapsto\;
\Theta_{\mathcal{F}_X(L)}^{\le r},
\end{equation}
the arity-$\le r$ truncation of the MC element of the factorization
envelope $\mathcal{F}_X(L)$, expressed in terms of the generators $R$.
\end{definition}

\begin{proposition}[Finite-jet rigidity; \ClaimStatusProvedHere]
% label removed: prop:thqg-finite-jet-rigidity
For a cyclically admissible Lie conformal algebra $L$, the
envelope-shadow functor satisfies:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Polynomial level dependence}: For an algebraic family
  $L_k$ parameterized by level $k$, $\Theta^{\mathrm{env}}_{\le r}(L_k)$
  is polynomial in $k$ of degree $\le r$.
\item \textbf{Gaussian collapse}: If $L$ is abelian (free-field), then
  $\Theta^{\mathrm{env}}_{\le r}(L) = \Theta^{\mathrm{env}}_{\le 2}(L)$
  for all $r \ge 2$.
\end{enumerate}
\end{proposition}

\begin{proof}
(i)~The MC element at arity $r$ is a sum over graphs of genus $\le g$
with $r$ vertices.  Each vertex contributes a factor polynomial in $k$
(the OPE coefficients are polynomial in the level).  The total degree
in $k$ is bounded by $r$.

(ii)~If $L$ is abelian, the OPE has no terms beyond the singular part
(no normal-ordered products), so the bar differential $D$ has only a
linear and quadratic part.  The MC element $\Theta = D - d_0$ has only
the quadratic part: $\Theta = \Theta^{\le 2}$.
\end{proof}


\subsection{MC3 categorical lift: all simple types}
% label removed: subsec:thqg-mc3-frontier

\begin{theorem}[Type-$A$ MC3 reduction beyond the evaluation-generated core; \ClaimStatusProvedElsewhere]
% label removed: thm:thqg-mc3-type-a
\index{MC3!type A resolution}
For $\mathfrak{g} = \mathfrak{sl}_N$, Volume~I proves the DK
comparison on the evaluation-generated core and, beyond that core,
establishes the shifted-prefundamental-generation and pro-Weyl
packets on the type-$A$ shifted/completed side.  The only remaining
post-core step is the compact-completion extension/comparison packet.
\end{theorem}

\begin{theorem}[All-types MC3 on the evaluation-generated core; \ClaimStatusProvedElsewhere]
% label removed: conj:thqg-mc3-arbitrary
\index{MC3!all simple types}
For all simple $\mathfrak{g}$, Volume~I proves the categorical
Clebsch--Gordan part of MC3 via the multiplicity-free
$\ell$-weight property and separately proves the DK comparison on the
evaluation-generated core.  Beyond that core, only type~$A$ currently
has a theorematic reduction to a single compact-completion gap; the
analogous post-core mechanism in other types remains conditional on
additional shifted/completed inputs.
\end{theorem}

\begin{remark}[The Hern\'andez--Jimbo obstruction: resolved for categorical CG]
% label removed: rem:thqg-hernandez-jimbo
The original obstruction to extending MC3 beyond type $A$ was the
absence of a suitable set of prefundamental representations for the
quantum affine algebra $U_q(\hat{\mathfrak{g}})$ in non-simply-laced
types.  This obstruction is resolved by the
multiplicity-free $\ell$-weight approach
(Vol~I, Theorem~\ref*{V1-thm:categorical-cg-all-types}): the
Chari--Moura property (every tensor product $V_{\omega_i} \otimes L^-$
has multiplicity-free $\ell$-weight spaces) replaces the minuscule
hypothesis entirely, and holds for all simple Lie algebras.  What this
resolves is the categorical-CG obstruction and the resulting
evaluation-generated-core comparison, not the full post-core MC3
extension problem.
\end{remark}


\subsection{The holographic dictionary}
% label removed: subsec:thqg-dictionary

\begin{center}
\renewcommand{\arraystretch}{1.3}
\small
\begin{tabular}{p{5cm}p{6.5cm}}
\textbf{Physics}
  & \textbf{Modular Koszul Duality} \\
\hline
Boundary local operators
  & $\cA$ (boundary chiral algebra) \\
Bulk local operators
  & $\Zder(\cA) \simeq \ChirHoch^\bullet(\cA^!)$ \\
Line operators
  & $\mathcal{C} \simeq \cA^!\text{-}\mathsf{mod}$ \\
Gravitational scattering matrix
  & $r(z) = \Res^{\mathrm{coll}}_{0,2}(\Theta_\cA)$ \\
$S$-duality
  & Koszul involution $\cA \mapsto \cA^!$ \\
Gravitational anomaly
  & $\kappa(\cA)$ (modular characteristic) \\
UV finiteness
  & Arity-cutoff lemma + FM compactification \\
Genus-$g$ partition function
  & $\Det(1 - K_g(\cA))$ (Fredholm determinant) \\
Soft graviton theorems
  & Ward identities of $\nabla^{\mathrm{hol}}_{g,n}$ \\
CPT conjugation
  & Verdier involution $\sigma$ \\
BMS symmetry
  & Automorphisms of $\gAmod$ \\
Holographic reconstruction
  & Bar-intrinsic construction of $\Theta_\cA$ \\[2pt]
\hline
\multicolumn{2}{l}{\textbf{Examples:}} \\
\hline
$M2$-brane holography
  & $\cA = A_{M2,\infty}$, $r_{\max} = \infty$ \\
B-model / Kodaira--Spencer
  & $\cA = \PV^{\bullet,\bullet}(Y)$, $r_{\max} = 2$ \\
Affine higher-spin gravity
  & $\cA = V_k(\mathfrak{g})$, $r_{\max} = 3$ \\
Contact gravity ($\beta\gamma$)
  & $\cA = \beta\gamma$, $r_{\max} = 4$ \\
Virasoro gravity
  & $\cA = \mathrm{Vir}_c$, $r_{\max} = \infty$ \\
Critical string
  & $\cA = \mathrm{Vir}_{26}$, $\cA^! = \mathrm{Vir}_0$ (maximally asymmetric dual scalar sector under G4)
\end{tabular}
\end{center}


\subsection{The six-shadow synthesis}
% label removed: subsec:thqg-six-shadow

\begin{definition}[Modular cumulant transform]
% label removed: def:thqg-modular-cumulant
\index{modular cumulant transform}
The \emph{modular cumulant transform} of a gravitational input $\cA$ is
the sextuple
\begin{equation}% label removed: eq:thqg-modular-cumulant
M(\cA) = \bigl(
\hat{T}^c(\cA),\;
D_\cA,\;
\tau_\cA,\;
r_\cA(z),\;
\Theta_\cA,\;
\nabla^{\mathrm{hol}}
\bigr),
\end{equation}
where $\hat{T}^c(\cA)$ is the completed cumulant generating function,
$D_\cA$ is the bar differential, $\tau_\cA$ is the reduced partition
function, $r_\cA(z)$ is the collision residue, $\Theta_\cA$ is the
universal MC element, and $\nabla^{\mathrm{hol}}$ is the shadow
connection.
\end{definition}

\begin{remark}[Five theorems as cumulant relations]
% label removed: rem:thqg-five-theorems-cumulants
The five main theorems of Volume~I (A, B, C, D, H) are the first
five cumulant relations of the modular cumulant transform:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Theorem A} (bar-cobar adjunction): $D_\cA$ defines
  the cumulant generating function.
\item \textbf{Theorem B} (bar-cobar inversion): the cumulant
  generating function is invertible on the Koszul locus.
\item \textbf{Theorem C} (complementarity): the cumulant
  generating function splits into bulk and defect components.
\item \textbf{Theorem D} (modular characteristic): the first
  cumulant is $\kappa(\cA)$.
\item \textbf{Theorem H} (Hochschild): the chiral Hochschild
  cohomology is polynomial in the cumulants.
\end{enumerate}
The ten gravitational theorems (G1--G10) extend this to all cumulant
levels.
\end{remark}


\subsection{Grand completion conjecture}
% label removed: subsec:thqg-grand-completion

\begin{conjecture}[Grand completion; \ClaimStatusConjectured]
% label removed: conj:thqg-grand-completion
\index{grand completion conjecture}
For every cyclically admissible Lie conformal algebra $L$ with
associated gravitational input $\cA = \mathcal{F}_X(L)$, the
modular cumulant transform $M(\cA)$ determines and is determined by
the modular Koszul datum $\Pi_X(L)$:
\begin{equation}% label removed: eq:thqg-grand-completion
M(\cA) \;\xleftrightarrow{\;\sim\;}\; \Pi_X(L).
\end{equation}
The equivalence is natural in $L$ and compatible with:
\begin{enumerate}[label=\textup{(\roman*)}]
\item DS reduction: $M(\mathrm{DS}(\cA)) = \mathrm{DS}(M(\cA))$.
\item Independent sum: $M(\cA_1 \oplus \cA_2) = M(\cA_1) \oplus
  M(\cA_2)$.
\item Level deformation: $M(\cA_k)$ is algebraic in $k$.
\item Koszul involution: $M(\cA^!) = \sigma(M(\cA))$.
\end{enumerate}
\end{conjecture}

\begin{remark}
This conjecture is the ultimate target of the holographic programme:
a single functorial construction that unifies the bar-cobar engine
(Volume~I), the Swiss-cheese/HT framework (this volume), and the
factorization-envelope technology into one coherent package.
\end{remark}


\subsection{Notation and grading}
% label removed: subsec:thqg-notation

\begin{enumerate}[label=\textup{(\alph*)}]
\item Grading is \textbf{cohomological} ($|d| = +1$) throughout.
  The bar construction uses desuspension.

\item $\gAmod = \Convstr(\mathcal{C}^!_{\mathrm{ch}},
  \mathcal{P}^{\mathrm{ch}})$ is the modular convolution dg Lie
  algebra (Definition~\ref*{V1-def:modular-convolution-dg-lie}), the
  strict model of $\Convinf(\mathcal{C}^!_{\mathrm{ch}},
  \mathcal{P}^{\mathrm{ch}})$.

\item $B(\cA)$ is the bar coalgebra; $\cA^! = (H^*(B(\cA)))^\vee$
  is the Koszul dual; $\Omega(B(\cA)) \simeq \cA$ is bar-cobar inversion.

\item \emph{HT} abbreviates ``holomorphic-topological.''
  An HT theory is a 3d $\mathcal{N} = 2$ theory in the holomorphic twist.

\item $\mathrm{Vir}_c^! \simeq \mathrm{Vir}_{26-c}$.  Self-duality at
  $c = 13$, \textbf{not} $c = 26$.  The critical string value $c = 26$ is
  the point where $\cA^! \simeq \mathrm{Vir}_0$ on the uncurved scalar
  locus, not a trivial Virasoro algebra.

\item The convolution algebra $\gAmod$ is a strict model of the
  underlying modular $\Linf$ algebra.  MC moduli coincide; the full
  $\Linf$ structure is needed for transfer, formality, and gauge
  equivalence.

\item The shadow obstruction tower is the primary nonlinear object:
  $\kappa \to \Delta \to \mathfrak{C} \to \mathfrak{Q} \to \cdots$
  as projections of the bar-intrinsic $\Theta_\cA$.

\item $\mathrm{Com}^! = \mathrm{Lie}$ (not $\mathrm{coLie}$).
\end{enumerate}


% ======================================================================
%  SECTION FILES: the ten results (expanded sections)
% ======================================================================

\input{chapters/connections/thqg_perturbative_finiteness}
\input{chapters/connections/thqg_gravitational_complexity}
\input{chapters/connections/thqg_symplectic_polarization}
\input{chapters/connections/thqg_gravitational_s_duality}
\input{chapters/connections/thqg_gravitational_yangian}
\input{chapters/connections/thqg_soft_graviton_theorems}
\input{chapters/connections/thqg_modular_bootstrap}
\input{chapters/connections/thqg_holographic_reconstruction}
\input{chapters/connections/thqg_critical_string_dichotomy}
\input{chapters/connections/thqg_fredholm_partition_functions}
