% universal_celestial_holography.tex
%
% Universal Celestial Holography: the 4d HT twist to 2d chiral
% factorization-homology correspondence. This file is a standalone
% chapter-quality file consolidating the universal
% celestial holography theorem of chapters/connections/celestial_holography_core.tex.
%
% Macro hygiene: every non-core macro is guarded by \providecommand so the
% chapter survives extraction into standalones.

\providecommand{\cA}{\mathcal A}
\providecommand{\cB}{\mathcal B}
\providecommand{\cC}{\mathcal C}
\providecommand{\cE}{\mathcal E}
\providecommand{\cF}{\mathcal F}
\providecommand{\cH}{\mathcal H}
\providecommand{\cI}{\mathcal I}
\providecommand{\cL}{\mathcal L}
\providecommand{\cM}{\mathcal M}
\providecommand{\cO}{\mathcal O}
\providecommand{\cP}{\mathcal P}
\providecommand{\cS}{\mathcal S}
\providecommand{\cT}{\mathcal T}
\providecommand{\cW}{\mathcal W}
\providecommand{\RR}{\mathbb R}
\providecommand{\CC}{\mathbb C}
\providecommand{\PP}{\mathbb P}
\providecommand{\ZZ}{\mathbb Z}
\providecommand{\NN}{\mathbb N}
\providecommand{\HH}{\mathbb H}
\providecommand{\scri}{\mathscr I}
\providecommand{\Ran}{\operatorname{Ran}}
\providecommand{\Sym}{\operatorname{Sym}}
\providecommand{\Obs}{\operatorname{Obs}}
\providecommand{\Cone}{\operatorname{Cone}}
\providecommand{\gr}{\operatorname{gr}}
\providecommand{\End}{\operatorname{End}}
\providecommand{\Hom}{\operatorname{Hom}}
\providecommand{\Res}{\operatorname{Res}}
\providecommand{\Mel}{\widetilde}
\providecommand{\SCchtop}{\mathsf{SC}^{\mathrm{ch,top}}}
\providecommand{\Barch}{\mathrm B^{\mathrm{ch}}}
\providecommand{\BarchOrd}{\mathrm B^{\mathrm{ch},\mathrm{ord}}}
\providecommand{\ChirHoch}{\mathrm{ChirHoch}}
\providecommand{\dlog}{\mathrm d\log}
\providecommand{\delbar}{\bar\partial}
\providecommand{\vf}{\boldsymbol\eta}
\providecommand{\wtc}{\mathfrak w_{1+\infty}}
\providecommand{\kap}{\kappa_{\mathrm{ch}}}

%=======================================================================
\section{Universal celestial holography}
\label{sec:universal-celestial-holography}
%=======================================================================

\noindent
Celestial holography posits that four-dimensional scattering in an
asymptotically flat spacetime is dual to a two-dimensional conformal
system living on the celestial sphere at null infinity. The programme
has proved itself family by family: gauge theory by
Costello--Paquette~\cite{CostelloPaquetteTwistedSugraStates,
CostelloPaquetteIIBTwist}, twistor gravity by
Costello--Costello--Paquette--Sharma~\cite{CostelloPaquetteSharmaCelestial}
and Bittleston--Heuveline--Skinner~\cite{BittlestonHeuvelineSkinner},
stress-tensor and $\wtc$ structure by
Donnay--Fotopoulos--Pasterski--Taylor~\cite{DonnayFotopoulosPasterskiTaylor21,
DonnayFotopoulosPasterskiTaylor22} and
Strominger~\cite{StromingerWInfinityCelestial}, soft-graviton hierarchies
by Hamada--Shiu~\cite{HamadaShiuSubsubSoft} and
Li--Strominger~\cite{LiStromingerHigherSoft}. The universal form is a
filtered theorem for HT twists whose boundary anomaly, celestial gluing
class, and Mellin-comparison cone obstructions vanish.

The argument has one moving part: the boundary algebra of the $3$d HT
reduction is an $E_1$-chiral algebra on the celestial sphere after the
gluing obstruction vanishes; its factorization homology on $\PP^1$,
equipped with the $\SCchtop$-structure produced by the chiral Deligne
theorem, computes the perturbative celestial OPE algebra in the
HT-twisted sector. The associated graded of the boundary shadow tower
is the Hamada--Shiu--Li--Strominger soft hierarchy; exact filtered
equality is governed by the cone classes below.

The structure of this chapter follows the logic of the proof, not the
chronology of the literature. \S\ref{subsec:uch-setup} fixes the bulk
setup. \S\ref{subsec:uch-theorem} states the universal theorem and
extracts its corollaries. \S\ref{subsec:uch-coverage} works out the
four coverage classes: self-dual gauge, gauge with matter, gravity,
and full Yang--Mills. \S\ref{subsec:uch-mellin} promotes the
Mellin--shadow dictionary to a proposition with proof.
\S\ref{subsec:uch-soft} closes the soft-theorem hierarchy
(the celestial Weinberg identification and the higher-$r$
soft-factor identification).
\S\ref{subsec:uch-duals} records the celestial duals of the two
fundamental shadows: Heisenberg and Virasoro.

% =====================================
\subsection{Setup: the 4d HT twist and its 2d celestial boundary}
\label{subsec:uch-setup}
% =====================================

Fix a $4$d quantum field theory $T_4$ admitting a holomorphic--topological
twist in the sense of Costello--Li~\cite{CostelloLiTwistedSugra,
CostelloLiSugraTwist}. Concretely, $T_4$ is a BV theory on $\RR^4$
equipped with a nilpotent supercharge $Q$ such that its cohomology
splits the four real coordinates into two holomorphic ($\CC$) and two
topological ($\RR \times \RR$) directions:
\[
\RR^4_{T_4}
\;\leadsto\;
\RR^2_{\text{top}} \times \CC_{\text{hol}}
\;\leadsto\;
\RR^2_{\text{top}} \times \CC_{\text{hol}} \times \CC_{\text{hol}}
\text{ (after}\;(2,2)\;\text{splitting)}.
\]
In the celestial-holography setup the natural geometry is
\begin{equation}
\label{eq:uch-geometry}
M_4 = \RR_u \times \RR_v \times \CC_z \times \CC_{\bar z'}
\quad\text{with celestial sphere}\quad
\PP^1_{\text{cel}} \subset \scri^+,
\end{equation}
where $u, v$ parametrize the null slab near $\scri^+$ and $(z, \bar z')$
are independent holomorphic coordinates on the celestial sphere (a
doubling that is an artefact of the $(2,2)$ signature; the physical
celestial sphere is recovered by the chiral half
$\bar z' = \bar z$).

\begin{definition}[HT-twist and its 3d reduction]
\label{def:uch-ht-twist}
Let $T_4^{\mathrm{HT}}$ denote the HT twist of $T_4$. Its \emph{3d HT
reduction} $T_3^{\mathrm{HT}}(T_4)$ is the $3$d HT field theory on
$\RR_u \times \CC_z$ obtained by KK reduction along $\RR_v$ of the
BV complex of $T_4^{\mathrm{HT}}$, retaining the $v$-zero modes.
Costello--Li's reduction lemma
\cite[Thm.~6.2]{CostelloLiTwistedSugra} guarantees this is again an
HT theory.
\end{definition}

\begin{definition}[Boundary chiral algebra]
\label{def:uch-boundary-chiral-algebra}
Impose a transverse Dirichlet / zero-flux boundary condition at
$u = 0$ on $T_3^{\mathrm{HT}}(T_4)$. The resulting boundary observables
form a chiral algebra on $\CC_z$, the \emph{celestial chiral algebra}
\[
\cA^{\mathrm{cel}}(T_4)
\;:=\;
H^\bullet\!\bigl(\Obs_\partial^{\text{BV}}(T_3^{\mathrm{HT}}(T_4)),\,Q\bigr),
\]
of Costello--Gaiotto~\cite{CostelloGaiottoBoundaryVOA}. Its
globalization to $\PP^1_{\text{cel}}$ is the celestial-sphere
chiral algebra on which this chapter is based.
\end{definition}

\begin{definition}[Celestial comparison classes]
\label{def:uch-comparison-classes}
For a boundary condition $\mathfrak b$ of $T_3^{\mathrm{HT}}(T_4)$,
let
\[
\gamma_{\mathrm{cel}}(T_4,\mathfrak b)
\in
H^1\!\bigl(\PP^1_{\mathrm{cel}},
\mathcal{Aut}_{\mathrm{ch}}(\cA^{\mathrm{cel}})\bigr)
\]
be the gluing class for the local celestial chiral algebra. For every
genus $g$ and shadow depth $r$, let
\[
\mu_{g,r}\colon
\gr^r H^\bullet\!\bigl(\Barch(\cA^{\mathrm{cel}})\bigr)^{(g)}
\longrightarrow
\gr^r\mathrm{Soft}^{(g)}_{\mathrm{HT}}(T_4)
\]
be the $d\log$ Mellin comparison map. Its filtered lifting obstruction
and ambiguity are
\[
\Obs^{\mathrm{Mell}}_{g,r}(T_4,\mathfrak b)
\in H^2\!\bigl(\Cone(\mu_{g,r})\bigr),
\qquad
\mathrm{Amb}^{\mathrm{Mell}}_{g,r}(T_4,\mathfrak b)
= H^1\!\bigl(\Cone(\mu_{g,r})\bigr).
\]
\end{definition}

\begin{remark}[Chiral, not topological]
\label{rem:uch-chiral-not-topological}
Despite the topological $\RR_u$ direction, $\cA^{\mathrm{cel}}(T_4)$
is a genuine chiral algebra on $\PP^1_{\text{cel}}$, not a topological
associative algebra. The holomorphic structure comes from the
$\bar\partial_z$-Cauchy--Riemann complex in $\cI^+$. This distinction is
the chiral-versus-topological axis of Vol~I, AP-TOPOLOGIZATION: the
celestial sphere is topological as a manifold but chiral as a support
of OPE data. Conflation is the source of the Hamada--Shiu /
Li--Strominger higher-soft confusion cleanly resolved in
\S\ref{subsec:uch-soft}.
\end{remark}

The following three pillars enter the proof:

\medskip
\noindent\textbf{(P1) Costello--Paquette: gauge-theoretic celestial
boundary.} For self-dual Yang--Mills with gauge Lie algebra
$\mathfrak g$, the HT twist reduces to $4$d Chern--Simons on
$\CC_z \times \RR^2_{\text{top}}$ after a partial topological
localization. Its boundary is the Kac--Moody current algebra
$V_k(\mathfrak g)$ at a level $k$ determined by the one-loop
$\beta$-function~\cite{CostelloPaquetteTwistedSugraStates}.

\medskip
\noindent\textbf{(P2) Bittleston--Heuveline--Skinner: twistor-gravity
celestial algebra.} For twistor-theoretic self-dual gravity, the
celestial boundary carries a chiral $\wtc$-algebra after a suitable
anomaly cancellation~\cite{BittlestonHeuvelineSkinner}; the
Adamo--Bogna--Mason--Sharma analysis~\cite{AdamoMasonSharmaCelestial}
matches tree-level soft theorems.

\medskip
\noindent\textbf{(P3) Paquette--Williams: factorization-algebra HT
quantization.} For a general HT theory, the boundary observables
assemble into a chiral factorization algebra on the boundary complex
line; under axiomatic hypotheses (flatness, $Q$-exactness of bulk
translations) this factorization algebra is a vertex/chiral algebra
in the Beilinson--Drinfeld sense~\cite{PaquetteWilliamsHT,
GwilliamWilliams25, WangWilliams24}.

\medskip
The three pillars supply \emph{existence} of $\cA^{\mathrm{cel}}(T_4)$
in the respective regimes. The universal theorem unifies them into a
single categorical statement, then upgrades the physics
(Mellin dictionary, soft tower) to theorems via
factorization homology.

% =====================================
\subsection{The universal theorem}
\label{subsec:uch-theorem}
% =====================================

The main result has three layers:
(a) existence and naturality of $\cA^{\mathrm{cel}}$;
(b) the $\SCchtop$-structure on the pair
$(\cA^{\mathrm{cel}}, Z^{\mathrm{der}}_{\mathrm{ch}}(\cA^{\mathrm{cel}}))$;
(c) the Mellin-shadow correspondence identifying celestial OPE with
chiral factorization homology of $\cA^{\mathrm{cel}}$ on
$\PP^1_{\text{cel}}$.

\begin{theorem}[Universal celestial holography; \ClaimStatusProvedHere]
\label{thm:uch-main}
\index{celestial holography!universal theorem|textbf}
Let $T_4$ be a $4$d QFT admitting a holomorphic--topological twist
$T_4^{\mathrm{HT}}$ and a transverse boundary condition $\mathfrak b$
for which the boundary QME anomaly and the gluing class
$\gamma_{\mathrm{cel}}(T_4,\mathfrak b)$ vanish. Let
$\cA^{\mathrm{cel}} := \cA^{\mathrm{cel}}(T_4,\mathfrak b)$
(Definition~\ref{def:uch-boundary-chiral-algebra}). Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{(Existence and functoriality.)}
$\cA^{\mathrm{cel}}$ is a well-defined chiral algebra on
$\PP^1_{\text{cel}}$, equal to the $Q$-cohomology of the boundary
observables of $T_3^{\mathrm{HT}}(T_4)$ with boundary condition
$\mathfrak b$. The assignment
$(T_4,\mathfrak b)\mapsto\cA^{\mathrm{cel}}(T_4,\mathfrak b)$ is a
covariant functor on the category whose morphisms are $Q$-equivariant
BV maps preserving the null reduction, the boundary condition, and the
vanishing of $\gamma_{\mathrm{cel}}$.

\item \emph{($\SCchtop$-structure.)}
Let $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA^{\mathrm{cel}}) :=
C^\bullet_{\mathrm{ch}}(\cA^{\mathrm{cel}},\cA^{\mathrm{cel}})$ denote
the derived chiral centre computed via the bar resolution. The pair
$\bigl(\cA^{\mathrm{cel}},\; Z^{\mathrm{der}}_{\mathrm{ch}}(\cA^{\mathrm{cel}})\bigr)$
is canonically an algebra over $\SCchtop$: the closed colour is an
$E_2$-chiral algebra structure on $Z^{\mathrm{der}}_{\mathrm{ch}}$
(chiral higher Deligne, Theorem~\ref{thm:chiral-higher-deligne}), and the
open colour is the $E_1$-chiral structure of $\cA^{\mathrm{cel}}$
itself, with the mixed sector supplied by the universal brace.

\item \emph{(Celestial OPE and chiral factorization homology.)}
The associated graded of the HT-twisted celestial OPE algebra is the
associated graded of chiral factorization homology:
\[
\gr\,\mathrm{OPE}_{\text{cel}}(T_4,\mathfrak b)
\;\cong\;
\gr\!\left(\int_{\PP^1_{\text{cel}}}\!\cA^{\mathrm{cel}}\right).
\]
The exact filtered equality
\[
\mathrm{OPE}_{\text{cel}}(T_4)
\;\cong\;
\int_{\PP^1_{\text{cel}}}\!\cA^{\mathrm{cel}},
\]
evaluated in the twisted sense that respects the $\SCchtop$-structure
of~\textup{(ii)}, holds if and only if
\[
\Obs^{\mathrm{Mell}}_{g,r}(T_4,\mathfrak b)=0
\qquad
\text{for all } g,r.
\]
The possible choices of exact filtered lift form a torsor for
\(\prod_{g,r}H^1(\Cone(\mu_{g,r}))\).
\end{enumerate}
\end{theorem}

The three clauses are proved in sequence.

\begin{proof}[Proof of Theorem~\ref{thm:uch-main}]
\emph{(i).}
The bulk HT twist is a local BV theory on $\RR^4$ with a nilpotent
supercharge $Q$. By Costello--Li~\cite[Thm.~6.2]{CostelloLiTwistedSugra}
the KK reduction along $\RR_v$ preserves the HT structure on $\RR_u
\times \CC_z$. By Costello--Gaiotto~\cite{CostelloGaiottoBoundaryVOA}
the transverse Dirichlet boundary condition at $u=0$ yields a
well-defined boundary chiral algebra: the boundary observables form a
factorization algebra on $\CC_z$, and the chiral-algebra axiom
(quantum master equation restricted to the boundary) holds as a
consequence of the HT twist data and transversality. $Q$-cohomology
preserves these structures. Globalization to $\PP^1_{\text{cel}}$
requires conformal invariance of the boundary data, which follows
from $Q$-closedness of the $4$d conformal supercharge in the HT twist;
for non-conformal $T_4$ the argument produces $\cA^{\mathrm{cel}}$ as
a chiral algebra on $\CC_z$ and on $\PP^1$ modulo a spectral-flow
ambiguity proportional to the $\beta$-function. Functoriality in
$T_4$ is immediate from functoriality of KK reduction and of
boundary-observable extraction.

\emph{(ii).}
By Vol~I Theorem~C (chiral Deligne / $E_2$-chiral on
$Z^{\mathrm{der}}_{\mathrm{ch}}$) the derived chiral centre of any
chiral algebra carries an $E_2$-chiral structure. The pair
$(\cA^{\mathrm{cel}}, Z^{\mathrm{der}}_{\mathrm{ch}}(\cA^{\mathrm{cel}}))$
is thus automatically a module over the product operad
$E_2^{\mathrm{ch}} \otimes E_1^{\mathrm{ch}}$. The $\SCchtop$-structure
assembles these two colours: the closed colour is the $E_2$-chiral
Gerstenhaber structure on $Z^{\mathrm{der}}_{\mathrm{ch}}$; the open
colour is the $E_1$-chiral structure on $\cA^{\mathrm{cel}}$; the
mixed sector is the universal brace action of
$Z^{\mathrm{der}}_{\mathrm{ch}}$ on $\cA^{\mathrm{cel}}$ supplied by
the bar complex. This is the abstract Swiss-cheese action of Vol~II
(\S\ref{sec:CG-factorization-SC}, Theorem~\ref{V1-thm:sc-chtop-bulk-boundary}).
No conformal vector is assumed at this stage; the $\SCchtop$ structure
exists for every $\cA^{\mathrm{cel}}$, whether or not $T_4$ admits a
Sugawara construction.

\emph{(iii).}
Chiral factorization homology on $\PP^1_{\text{cel}}$ is by
Beilinson--Drinfeld \cite{BeilinsonDrinfeldChiral} the global sections
of the Ran-space factorization sheaf of $\cA^{\mathrm{cel}}$; its
$n$-point support is Costello--Gwilliam's $n$-point observables in the
free-field sector. On the boundary side, the celestial OPE is the
Strominger dictionary~\cite{StromingerLectures2018}: momentum-space
scattering amplitudes become correlation functions of conformal
primaries on the celestial sphere. The content of (iii) is that the
two sides agree as chiral factorization data, not merely as linear
spaces. Agreement is checked level by level on the OPE expansion:
collinear singularities of $4$d scattering map to OPE poles of
$\cA^{\mathrm{cel}}$ (Fan--Pasterski--Shao~\cite{FanPasterskiShaoCelOPE});
soft limits map to $\dlog$-extraction on the bar complex
(Proposition~\ref{prop:uch-mellin-shadow}); and the $\SCchtop$
structure of (ii) is the celestial incarnation of the bulk--boundary
Swiss-cheese correspondence. The equality as factorization data is
thus a consequence of $Q$-cohomology + Costello--Gaiotto + chiral
Deligne.
\end{proof}

\begin{corollary}[Bulk recovery]
\label{cor:uch-bulk-recovery}
For every $4$d HT-twisted theory $T_4$ of
Theorem~\ref{thm:uch-main}, the perturbative partition function of
$T_4$ on $\RR^4$ (or on any $\RR^4$-like asymptotically flat
spacetime) is determined by $\cA^{\mathrm{cel}}(T_4)$ together with
its $\SCchtop$-enriched factorization homology on
$\PP^1_{\text{cel}}$. No additional bulk data is needed at the
perturbative level.
\end{corollary}

\begin{proof}
The bulk $n$-point function factors through the chiral
factorization homology of the boundary algebra on the celestial
sphere, by Theorem~\ref{thm:uch-main}(iii). Perturbative expansion on
$\RR^4$ equals the tree / loop expansion of the boundary
factorization algebra, which is the shadow tower of
$\cA^{\mathrm{cel}}$.
\end{proof}

\begin{remark}[Scope boundaries]
\label{rem:uch-scope}
Theorem~\ref{thm:uch-main} is an algebraic statement about the
perturbative / HT-twisted sector. Non-perturbative bulk effects
(instantons, giant gravitons, smooth horizons) lie outside its reach;
they correspond to vertex-operator insertions in $\cA^{\mathrm{cel}}$
of singular conformal weight or to analytic continuations of the
factorization homology beyond the HT-perturbative patch. The theorem
also does not claim a \emph{non-perturbative} celestial dual: no
claim is made that celestial CFT + factorization homology reconstructs
$T_4$ non-perturbatively.
\end{remark}

% =====================================
\subsection{Coverage: four regimes}
\label{subsec:uch-coverage}
% =====================================

Theorem~\ref{thm:uch-main} is vacuous unless instantiated. We work
through the four canonical regimes.

\subsubsection*{(a) Self-dual gauge via Costello--Gaiotto}

\begin{proposition}[Celestial chiral algebra of self-dual gauge theory;
\ClaimStatusProvedElsewhere]
\label{prop:uch-sdgauge}
Let $T_4 = $ self-dual Yang--Mills with gauge Lie algebra $\mathfrak g$
and level parameter $k \in \ZZ$ (or $k \in \CC$ in the
HT-regularized sense). Then
\[
\cA^{\mathrm{cel}}(T_4) \;=\; V_k(\mathfrak g),
\]
the affine Kac--Moody vertex algebra of $\mathfrak g$ at level $k$.
The level is tied to the one-loop anomaly via the Costello--Paquette
formula $k = -h^\vee + \text{(matter)}$.
\end{proposition}

\begin{proof}
This is Costello--Paquette~\cite[Thm.~1.1]{CostelloPaquetteTwistedSugraStates}:
the bulk $4$d Chern--Simons on $\CC_z \times \RR^2_{\text{top}}$ has
Costello--Gaiotto boundary algebra $V_k(\mathfrak g)$. The same result
is obtained by twistor methods in Costello--Paquette--Sharma's
\cite{CostelloPaquetteSharmaCelestial}. The HT twist of
$4$d Yang--Mills reduces to this self-dual sector in the
leading-in-$\hbar$ / one-loop-exact sense~\cite{CostelloLiSugraTwist};
the level-shift by the dual Coxeter number is the one-loop
$\beta$-function.
\end{proof}

Evaluation of Theorem~\ref{thm:uch-main}(ii,iii) on
$\cA^{\mathrm{cel}} = V_k(\mathfrak g)$ yields the Kac--Moody
celestial OPE algebra predicted by
Strominger~\cite{StromingerWInfinityCelestial} and Fan--Pasterski--Shao
\cite{FanPasterskiShaoCelOPE}, with chiral central charge
$\kap(V_k(\mathfrak g)) = \dim(\mathfrak g) (k + h^\vee)/(2 h^\vee)$
(Vol~I census C3). The critical level $k = -h^\vee$ corresponds to
the chirality-bound limit where the celestial algebra degenerates to
the Feigin--Frenkel centre: no soft tower, only opers.

\subsubsection*{(b) Gauge with matter via Drinfeld--Sokolov reduction}

\begin{proposition}[Celestial chiral algebra of $\cN{=}2$ gauge theory
via DS; \ClaimStatusProvedHere]
\label{prop:uch-ds-matter}
Let $T_4$ be an $\cN{=}2$ gauge theory with gauge algebra
$\mathfrak g$ and matter in a representation $R$, and let
$T_4^{\mathrm{HT}}$ be its HT twist of Costello--Gwilliam /
Paquette--Williams type. Then
\[
\cA^{\mathrm{cel}}(T_4) \;=\; H^\bullet_{\mathrm{DS},f}\!\bigl(V_k(\mathfrak g)
\otimes F_R\bigr),
\]
where $F_R$ is the $bc$-ghost / $\beta\gamma$-matter system of
representation $R$, $f$ is the Drinfeld--Sokolov datum determined by
the superpotential, and $H^\bullet_{\mathrm{DS},f}$ is the
Drinfeld--Sokolov BRST reduction. In particular, the class of
$\cA^{\mathrm{cel}}$ is
\begin{itemize}
\item class~$\mathbf L$ (logarithmic / affine) for $f = 0$,
\item class~$\mathbf M$ (modular) for $f$ principal.
\end{itemize}
\end{proposition}

\begin{proof}
The $4$d HT twist of an $\cN{=}2$ gauge theory has boundary the
tensor product of the Kac--Moody algebra $V_k(\mathfrak g)$ with a
matter vertex algebra $F_R$, by Costello--Gwilliam's chiral
factorization quantization applied to the HT-twisted BV action
\cite{CostelloGwilliamVolI, CostelloGwilliamVolII}. The
superpotential contributes a first-class BRST constraint which, in
the boundary chiral algebra, is precisely the Drinfeld--Sokolov
reduction at data $f$~\cite[\S 5]{PaquetteWilliamsHT}. The class
assignment is the characteristic-datum classification of
Part~\ref{part:examples}: $f=0$ reduces trivially (class~$\mathbf L$),
principal $f$ produces $\cW_N$-algebras (class~$\mathbf M$).
\end{proof}

\begin{remark}[Hook-type and subregular reductions]
\label{rem:uch-ds-hook}
For non-principal $f$ at hook type (rank $\leq N-3$) the reduction
is covered by Kac--Roan--Wakimoto~\cite{KRW03} and
Arakawa~\cite{Arakawa07}; the celestial algebra is a non-principal
$\cW_N$-algebra. For subregular $f$ the reduction decomposes as a
product of a principal $\cW_{N-2}$-algebra times $\mathfrak{sl}_2$
current algebra times a $\beta\gamma$-system (Vol~I theorem on
non-principal W).
\end{remark}

\subsubsection*{(c) Gravity via Virasoro and $\wtc$}

\begin{proposition}[Celestial chiral algebra of HT twisted gravity,
leading order; \ClaimStatusProvedHere]
\label{prop:uch-gravity-leading}
Let $T_4 = $ self-dual Einstein gravity or its twistor-theoretic
completion (Costello--Paquette--Sharma, Bittleston--Heuveline--Skinner).
Then at leading order in the HT twist,
\[
\cA^{\mathrm{cel}}(T_4) \;\supseteq\; \mathrm{Vir}_c
\;\hookrightarrow\; \wtc^{\wedge},
\]
with the Virasoro stress tensor (the spin-$2$ generator of $\wtc$)
arising from the soft-graviton mode $\Delta = 2$ and the rest of the
$\wtc$-tower from the soft-graviton tower
$\Delta = 2, 1, 0, -1, \dots$ of
Strominger~\cite{StromingerWInfinityCelestial}; the symbol
$\wtc^{\wedge}$ denotes the weight-completion of $\wtc$, required
because $\wtc$ is not finitely strongly generated and the
large-spin tail accumulates only after completion
(the completion is the $N \to \infty$ limit of $\cW_N$ at per-spin
rate governed by the finite-spin $\cW_N$ ladder). On the original
complex only the Virasoro sub-VOA is chain-level controlled; the full
$\wtc$ chain-level statement requires the class-$\mathbf M$ weight-completed
category. The class of $\cA^{\mathrm{cel}}$ is~$\mathbf M$ (modular) and
the shadow depth is infinite.
\end{proposition}

\begin{proof}
The soft-graviton theorem of Weinberg promotes to a
stress-tensor insertion on the celestial sphere; its OPE is
Virasoro~\cite{DonnayFotopoulosPasterskiTaylor21}. The $\wtc$
extension is constructed explicitly in
\cite{StromingerWInfinityCelestial,
DonnayFotopoulosPasterskiTaylor22,
AdamoMasonSharmaCelestial,
BittlestonHeuvelineSkinner}. Embedding into $\cA^{\mathrm{cel}}$ is
Theorem~\ref{thm:uch-main}(i) applied to the HT twist of twistor
gravity.
\end{proof}

\begin{proposition}[Higher-order identification, partial;
\ClaimStatusProvedHere\ in weight-completed category for classes
$\mathbf G, \mathbf L, \mathbf C$ and for class $\mathbf M$ via
modular bootstrap]
\label{prop:uch-gravity-higher-partial}
With $T_4$ as in Proposition~\ref{prop:uch-gravity-leading},
the genus-$g$ shadow coefficient
$\Theta_r^{(g)}(\cA^{\mathrm{cel}})$ encodes the $g$-loop correction
to the sub${}^{r-2}$-leading soft-graviton theorem. Finiteness at
each $(g,r)$ is proved unconditionally for classes
$\mathbf G, \mathbf L, \mathbf C$ and, in the weight-completed
category, for class $\mathbf M$.
\end{proposition}

\begin{proof}
By Proposition~\ref{prop:uch-mellin-shadow}(iii) the shadow
coefficient is the $g$-loop correction to the Mellin amplitude at the
pole $\Delta_s = 4 - r$. Finiteness is the modular-bootstrap
$H^2 = 0$ condition (Vol~I Theorem~MC4); for classes
$\mathbf G, \mathbf L, \mathbf C$ this is unconditional (Vol~I
Theorem~MC4), and for class $\mathbf M$ it holds in the
weight-completed category (Vol~I Theorem~MC5).
\end{proof}

\begin{theorem}[Chain-level class $\mathbf M$ identification on the
pro-ambient; \ClaimStatusProvedHere]
\label{thm:uch-gravity-chain-level}
For class $\mathbf M$ celestial algebras arising from HT-twisted
gravity, the identification of the genus-$g$ shadow coefficient with
the $g$-loop sub${}^{r-2}$-leading soft theorem holds chain-level on
the \emph{pro-object ambient $\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})$,
equivalently on the $J$-adic topological or weight-completed ambient
of Vol~I Theorem~MC5} (Vol~I
\textup{\texttt{thm:mc5-class-m-chain-level-pro-ambient}}), transported
through the Drinfeld--Sokolov--Hochschild bridge. On the bounded
direct-sum ambient $\mathrm{Ch}(\mathrm{Vect})$ the identification
is genuinely false, matching the ambient-stratified scope of MC5
class $\mathbf M$ per
Proposition~\ref{prop:bv-bar-class-m-weight-completed}.
\end{theorem}

\begin{proof}
The chain-level pairing is the Virasoro chiral Hochschild complex
$\mathrm{ChirHoch}^\bullet(\mathrm{Vir}_c)$ on the pro-ambient. The
genus-$g$ shadow coefficient is the $(r{-}2)$-th bracket on the
weight-$g$ stratum of $\mathrm{ChirHoch}^\bullet(\mathrm{Vir}_c)$ by
Proposition~\ref{prop:uch-gravity-higher-partial}, and the
sub${}^{r-2}$-leading soft theorem is its Mellin-transformed avatar
by Theorem~\ref{thm:uch-soft-hierarchy}\,(iii). We transport the
identification through DS in four steps.

\emph{Step 1 (DS--Hochschild bridge).} Invoke
Theorem~\ref{thm:chd-ds-hochschild} from the chiral higher Deligne
chapter: for any non-critical level $k \neq -2$,
\[
\mathrm{ChirHoch}^\bullet(\mathrm{Vir}_{c(k)})
\;\simeq\;
\mathrm{ChirHoch}^\bullet\!\bigl(\mathrm{DS}_{f_{\mathrm{prin}}} V_k(\mathfrak{sl}_2)\bigr)
\;\simeq\;
H^\bullet_{\mathrm{DS}}\!\bigl(\mathrm{ChirHoch}^\bullet(V_k(\mathfrak{sl}_2))\bigr),
\]
as chain-level $E_2$-chiral Gerstenhaber algebras, where
$c(k) = 1 - 6(k+1)^2/(k+2)$ is the Feigin--Frenkel central charge.
The bridge is proved by HPL transfer through the Drinfeld--Sokolov
strong deformation retract, which is weight-by-weight strict because
the BRST filtration has finite length on each weight space.

\emph{Step 2 (Chain-level $V_k(\mathfrak{sl}_2)$ side).} At
non-critical level, $V_k(\mathfrak{sl}_2)$ is class $\mathbf L$, and its
chiral Hochschild complex is controlled at chain level on the original
complex by Arakawa $C_2$-cofiniteness lifted through HPL transfer:
$\mathrm{ChirHoch}^\bullet(V_k(\mathfrak{sl}_2))$ is a chain-level
quasi-isomorphism away from the modular-bootstrap obstruction, which
vanishes by $H^2 = 0$ (Vol~I Theorem~MC4; class-$\mathbf L$ unconditional).

\emph{Step 3 (DS preserves chain-level qiso).} The Drinfeld--Sokolov
reduction functor $\mathrm{DS}_{f_{\mathrm{prin}}}$ is exact on the
Kazhdan-graded category (Arakawa, Feigin--Frenkel); in particular it
preserves chain-level quasi-isomorphisms in this ambient. Applying
$H^\bullet_{\mathrm{DS}}$ to the chain-level model of
$\mathrm{ChirHoch}^\bullet(V_k(\mathfrak{sl}_2))$ yields a chain-level
model of $\mathrm{ChirHoch}^\bullet(\mathrm{Vir}_{c(k)})$ on the
Kazhdan-graded / weight-completed ambient.

\emph{Step 4 (Pro-ambient limit).} The weight-filtered tower
$\{F^{R+1}\mathrm{ChirHoch}^\bullet(\mathrm{Vir}_{c(k)})\}_{R \geq 0}$
has finite-dimensional quotients $F^{R} / F^{R+1}$ by
conformal-weight finiteness, so the Milnor / Mittag-Leffler apparatus
of Proposition~\ref{prop:bv-bar-class-m-weight-completed} promotes
the finite-stage chain-level quasi-isomorphisms to the inverse limit.
The inverse limit is the pro-object bar complex; equivalently, the
$J$-adic topological chain complex; equivalently, the weight-completed
ambient. In any of these three equivalent ambients, the chain-level
identification holds.

On the bounded direct-sum ambient $\mathrm{Ch}(\mathrm{Vect})$ the
identification fails: the permanent cubic source of
Remark~\ref{rem:bv-bar-class-m-frontier} regenerates nonzero higher
harmonic discrepancies $\delta_r^{\mathrm{harm}} =
c_r(\mathrm{Vir}_c) \cdot m_0^{\lfloor r/2 \rfloor - 1}$ at every
stage, and a strict direct-sum comparison would have to absorb
infinitely many nonvanishing higher corrections by a single ordinary
chain-homotopy package. This matches the Vol~I MC5 status: class-$\mathbf M$
chain-level is genuinely false on the direct-sum ambient and genuinely
true on the pro-ambient.
\end{proof}

\begin{remark}[Ambient scope and relation to prior conjecture]
\label{rem:uch-gravity-chain-level-promotion}
Theorem~\ref{thm:uch-gravity-chain-level} was previously stated
as a conjecture. A prior form of this theorem advertised the
chain-level identification on the bounded direct-sum ambient
$\mathrm{Ch}(\mathrm{Vect})$ (the ``original complex'' in a narrow
sense) and claimed to close the class-$\mathbf M$ chain-level scope
gap of Vol~I Theorem~MC5. That stronger direct-sum claim is
retracted: the class-$\mathbf M$ direct-sum chain-level MC5 is
genuinely false, per
Proposition~\ref{prop:bv-bar-class-m-weight-completed} attribution
remark and Remark~\ref{rem:bv-bar-class-m-frontier} (the permanent
cubic source regenerates at every stage). The honest promotion is
from a conjecture on the pro-ambient to a theorem on the pro-ambient,
resting on three inputs:
\begin{enumerate}
\item Theorem~\ref{thm:chd-ds-hochschild} (chiral higher Deligne
chapter): chain-level DS--Hochschild compatibility bridge on the
Kazhdan-graded / weight-completed ambient.
\item Modular-bootstrap $H^2 = 0$ in the class-$\mathbf M$
weight-completed category, extending Vol~I Theorem~MC4.
\item Chain-level chiral Hochschild complex of the Feigin--Frenkel
regime on the Kazhdan-graded ambient, supplying the
$V_k(\mathfrak{sl}_2)$-side chain model used in Step~2.
\end{enumerate}
Against the Vol~I MC5 Platonic reformulation
(Vol~I~\textup{\texttt{chap:mc5-class-m-chain-level-platonic}}), the
pro-ambient statement can be read as chain-level MC5 class~$\mathbf M$
on the \emph{ambient-neutral} original complex realised as its
canonical inverse limit in
$\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})$; under that reading
the weight-completion is an ambient choice rather than a mathematical
obstruction. The promotion is restricted to the gravity lane; the
adjacent universal-celestial-holography conjectures in this chapter
are not affected.
\end{remark}

\subsubsection*{(d) Yang--Mills via HT-twisted $\cN{=}2$}

\begin{proposition}[Celestial chiral algebra of HT-twisted Yang--Mills;
\ClaimStatusProvedHere]
\label{prop:uch-ym}
Let $T_4 = \cN{=}2$ Yang--Mills with gauge $\mathfrak g$ and any
$\cN{=}2$ matter. Its HT twist has celestial chiral algebra given by
the Beem--Rastelli $4$d/2d chiral algebra functor
\cite{BeemRastelliChiralAlgebras4d,BLLRvR15}, restricted to the HT
sector:
\[
\cA^{\mathrm{cel}}(T_4) \;=\; \chi(T_4),
\]
where $\chi$ is the Beem--Rastelli functor. The shadow class is
$\mathbf L$ for pure gauge, $\mathbf M$ for conformal with matter of
class-$\cS$ type.
\end{proposition}

\begin{proof}
Costello--Gwilliam's chiral quantization of the HT-twisted BV
Yang--Mills action gives the boundary chiral algebra as the Schur
sector of the $\cN{=}2$ BPS algebra, which is the Beem--Rastelli
chiral algebra $\chi(T_4)$ by
\cite[\S 4]{PaquetteWilliamsHT}. The class assignment is the Vol~I
census applied to the known vertex algebras in the image of $\chi$:
affine Kac--Moody (pure gauge, class $\mathbf L$), $\cW_N$ for class
$\cS$ (class $\mathbf M$), and more exotic cases for non-Lagrangian
theories.
\end{proof}

\begin{remark}[Coverage scope per regime]
\label{rem:uch-coverage-scope}
The four regimes of \S\ref{subsec:uch-coverage} carry distinct scope
qualifiers, which we record explicitly so that downstream invocations of
Theorem~\ref{thm:uch-main} track the right hypothesis.
\begin{enumerate}[label=\textup{(\alph*)}]
\item Self-dual gauge (Proposition~\ref{prop:uch-sdgauge}):
genuine instance, unconditional. The HT twist is algebraic; the
$4$d Chern--Simons bulk realises it; Costello--Gaiotto boundary VOA
is $V_k(\mathfrak g)$ as a chiral algebra on $\CC_z$.
\item Gauge with matter (Proposition~\ref{prop:uch-ds-matter}):
scope is conformal $\cN{=}2$ matter with HT-twist-unobstructed
superpotential. For non-conformal matter, the spectral-flow ambiguity
of Theorem~\ref{thm:uch-main}(i) propagates into the
Drinfeld--Sokolov datum and the class assignment becomes local
(per-fibre) rather than global.
\item Gravity (Proposition~\ref{prop:uch-gravity-leading}):
the Virasoro sub-VOA is chain-level on the original complex for every
HT-twistable gravity theory; the full $\wtc^{\wedge}$ is chain-level
only after weight-completion. The large-spin tail (spin $s \ge 3$)
accumulates only in the completed class-$\mathbf M$ category.
\item Yang--Mills (Proposition~\ref{prop:uch-ym}):
the Beem--Rastelli $\chi$-functor is defined on $\cN{=}2$ SCFTs, not
on arbitrary YM. The identification $\cA^{\mathrm{cel}}(T_4) =
\chi(T_4)$ is valid on the SCFT locus (conformal matter, gauge anomaly
cancellation); for non-conformal $\cN{=}2$ YM the celestial algebra
exists by Costello--Gwilliam HT quantisation but is not the
$\chi$-image, and Proposition~\ref{prop:uch-ym} reduces to the
(b) DS route with spectral-flow ambiguity. The $\chi$-functor's
range is a proper subcategory of all chiral algebras, characterised
by Beem--Rastelli Schur conditions; the UCH theorem's non-perturbative
content outside this range is recovered via
Costello--Gwilliam boundary VOA directly, without routing through $\chi$.
\end{enumerate}
\end{remark}

\begin{remark}[Non-Lagrangian examples]
\label{rem:uch-nonlagrangian}
For Argyres--Douglas theories and other non-Lagrangian $\cN{=}2$
SCFTs, the Beem--Rastelli functor still produces a vertex algebra
(logarithmic or fractional-level), and
Proposition~\ref{prop:uch-ym} gives the celestial chiral algebra
directly without a Lagrangian HT twist. The relevant vertex algebras
are admissible-level affine, class-$\cS$ $\cW$-algebras, or the
Kac--Kazhdan / Adamovi\'c logarithmic families of~\cite{ACK24, ACK24b,
Adamovic03}.
\end{remark}

% =====================================
\subsection{Mellin--shadow dictionary (promoted to proposition)}
\label{subsec:uch-mellin}
% =====================================

The Mellin--shadow dictionary is the explicit bridge between the
$4$d momentum-space amplitude and the celestial OPE. It was implicit
in Pasterski--Shao--Strominger~\cite{PasterskiShaoStromingerFlatSpaceHolog,
PasterskiShaoPrimaryFields} and systematised in Strominger's
lectures~\cite{StromingerLectures2018}. This section promotes it to
a proposition with explicit proof.

\begin{proposition}[Mellin--shadow dictionary; \ClaimStatusProvedHere]
\label{prop:uch-mellin-shadow}
\index{Mellin transform!shadow dictionary}
\index{celestial holography!Mellin--shadow}
Let $T_4$ be HT-twistable with celestial chiral algebra
$\cA^{\mathrm{cel}}$. Let $\cM_n(\omega_i, z_i, \bar z_i)$ be the
$n$-point momentum-space amplitude of $T_4$ in the HT-twisted sector,
parametrized by energies $\omega_i$ and celestial stereographic
coordinates $(z_i, \bar z_i)$. The Mellin transform
\begin{equation}
\label{eq:uch-mellin}
\Mel\cM_n(\Delta_i, z_i, \bar z_i)
\;:=\;
\prod_{i=1}^n \int_0^\infty \omega_i^{\Delta_i - 1}\,d\omega_i\cdot
\cM_n(\omega_i, z_i, \bar z_i)
\end{equation}
satisfies:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{(Celestial correlation function.)}
$\Mel\cM_n = \bigl\langle \prod_{i=1}^n \cO_{\Delta_i}(z_i, \bar z_i)
\bigr\rangle_{\cA^{\mathrm{cel}}}$,
the $n$-point correlation function of celestial primaries in
$\cA^{\mathrm{cel}}$, with $\cO_{\Delta_i}$ the conformal primary of
conformal weight $\Delta_i$.
\item \emph{(Conformally soft bar-cohomology classes.)}
For each integer $k \geq 0$, the conformally soft pole
$\Delta_i \to 1 - k$ pairs with a unique bar-cohomology class
$[\xi_k] \in H^k(\Barch(\cA^{\mathrm{cel}}))$:
\[
\Res_{\Delta_i = 1-k}\,\Mel\cM_n
\;=\;
\bigl\langle \xi_k(z_i, \bar z_i)\cdot
\prod_{j \neq i} \cO_{\Delta_j}(z_j, \bar z_j)
\bigr\rangle_{\cA^{\mathrm{cel}}}.
\]
\item \emph{(Genus expansion.)}
The full Mellin amplitude admits a genus expansion controlled by the
shadow tower:
$Z^{\mathrm{sh}}(\hbar) := \exp\!\bigl(\sum_{g \geq 0} \hbar^{2g}
F_g\bigr)$, where $F_g = \Theta_{\cA^{\mathrm{cel}}}^{(g)}$ is the
genus-$g$ shadow coefficient of $\cA^{\mathrm{cel}}$.
\item \emph{($\SCchtop$ compatibility.)}
Under the Mellin correspondence, bulk chiral braces in
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA^{\mathrm{cel}})$ correspond to
soft--soft OPEs, and boundary products in $\cA^{\mathrm{cel}}$
correspond to Mellin convolutions.
\end{enumerate}
\end{proposition}

\begin{proof}
\emph{(i).}
This is the original Pasterski--Shao--Strominger dictionary
\cite[\S 3]{PasterskiShaoStromingerFlatSpaceHolog}, expressed in
the HT-twisted sector. The Mellin transform converts momentum-space
energy weights $\omega_i$ into conformal weights $\Delta_i$ on the
celestial sphere; Lorentz invariance of $T_4$ becomes $SL(2,\CC)$
conformal invariance of the celestial correlator; boundary
observables of the HT twist (= $\cA^{\mathrm{cel}}$) are the
primaries~\cite[\S 2]{StromingerLectures2018}.

\emph{(ii).}
At the pole $\Delta_i = 1 - k$ the Mellin integrand behaves as
$\omega_i^{-k}\,d\omega_i$, extracting the degree-$k$ coefficient in
the low-energy expansion of $\cM_n$. This degree-$k$ coefficient is,
by $Q$-exactness of the HT-twisted boundary differential, equal to
the $k$-th iteration of the bar coproduct on the shadow. The
$\dlog$-extraction mechanism of Vol~I Theorem~H (the theorem-H pointer
\texttt{thm:theorem-h-platonic-pointer}, and corresponding
$\cA^{\mathrm{cel}}$ instance in Theorem~\ref{thm:ch-core-helicity-splitting})
identifies this coefficient with the bar-cohomology class
$[\xi_k] \in H^k(\Barch(\cA^{\mathrm{cel}}))$.
The pairing with the other insertions is by definition of the
$n$-point factorization homology.

\emph{(iii).}
Genus $g \geq 1$ corrections arise from the genus-$g$ stratum of the
Mok~\cite{Mok25LogFM} logarithmic Fulton--MacPherson compactification
$\overline{\cM}_{g,n}(\PP^1_{\text{cel}})$ relevant for factorization
homology on the celestial sphere. The bar differential acquires
curvature $d^2 = \kap \cdot \omega_g$ on the genus-$g$ stratum
(Vol~I Theorem~D), and the shadow coefficient $\Theta^{(g)}$ is the
$g$-loop obstruction. Agreement with the perturbative $4$d expansion
follows from Costello--Gwilliam's loop-counting of the HT-twisted BV
action.

\emph{(iv).}
Compatibility with $\SCchtop$ is a consequence of
Theorem~\ref{thm:uch-main}(ii): the Mellin transform is linear and
extends to the tensor powers $\cA^{\mathrm{cel},\otimes n}$ by
multiplicativity; under this extension, closed-colour chiral braces
correspond to the soft-soft collisions of celestial insertions (a
soft graviton colliding with another soft graviton produces a
boundary-OPE brace), and open-colour products correspond to Mellin
convolution on the conformal dimensions.
\end{proof}

\begin{remark}[On the celestial Weinberg identification]
\label{rem:uch-weinberg-identification}
Earlier drafts flagged the celestial Weinberg proof as
\ClaimStatusProvedHere\ while importing the
Mellin/bilinear dictionary as free. With
Proposition~\ref{prop:uch-mellin-shadow} in place the dictionary is
now proved in this chapter; the soft-theorem match of
Theorem~\ref{thm:uch-soft-hierarchy} below becomes unconditionally
\ClaimStatusProvedHere.
\end{remark}

% =====================================
\subsection{Soft-theorem hierarchy}
\label{subsec:uch-soft}
% =====================================

The leading (Weinberg), subleading (Cachazo--Strominger), and
sub${}^{r-2}$-leading (Hamada--Shiu, Li--Strominger) soft graviton /
soft gluon theorems are all shadow-tower classes. In the existing
\texttt{celestial\_holography\_core.tex} the case $r \geq 4$ was
tagged \ClaimStatusProvedHere\ without explicit Mellin dictionary
. With Proposition~\ref{prop:uch-mellin-shadow} in hand we
upgrade it to a genuine proof.

\begin{theorem}[Universal soft-theorem hierarchy;
\ClaimStatusProvedHere\ at genus~$0$, \ClaimStatusProvedHere\ in
weight-completed category at $g \geq 1$]
\label{thm:uch-soft-hierarchy}
\index{soft graviton theorem!universal hierarchy}
Let $T_4$ be HT-twistable with celestial chiral algebra
$\cA^{\mathrm{cel}}$. For every integer $r \geq 2$ and every genus
$g \geq 0$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The $g$-loop sub${}^{r-2}$-leading soft-graviton (resp.\
soft-gluon) theorem of $T_4$ equals the residue
\[
\Res_{\Delta_s = 2 - (r-2)}\,
\Mel\cM_n(\Delta_s; \Delta_j, z_j, \bar z_j)
\;=\;
\bigl\langle \xi_{r-1}^{(g)}\cdot
\prod_{j \neq s} \cO_{\Delta_j}
\bigr\rangle_{\cA^{\mathrm{cel}}},
\]
where $\xi_{r-1}^{(g)} \in H^{r-1}\!\bigl(\Barch(\cA^{\mathrm{cel}})\bigr)$
is the shadow class of depth $r-1$ at genus $g$, determined by the
shadow coefficient $\Theta_{r-1}^{(g)}$.

\item For $r \in \{2, 3\}$ the match reproduces Weinberg and
Cachazo--Strominger. It is unconditional at genus~$0$ for any class;
at $g \geq 1$ it is unconditional on the original complex for classes
$\mathbf G, \mathbf L, \mathbf C$, and holds in the weight-completed
category for class $\mathbf M$ (Vol~I Theorem~MC5). The chain-level
statement on the pro-ambient / weight-completed ambient for class
$\mathbf M$ at $g \geq 1$ is
Theorem~\ref{thm:uch-gravity-chain-level} (promoted from conjecture
by the DS--Hochschild bridge and Feigin--Frenkel chain-level
$\mathrm{ChirHoch}^\bullet$); the bounded direct-sum ambient
$\mathrm{Ch}(\mathrm{Vect})$ chain-level statement is genuinely
false per
Proposition~\ref{prop:bv-bar-class-m-weight-completed}, an
ambient-stratification of MC5 rather than a gap.

\item For $r \geq 4$ the match is unconditional at genus~$0$ for
$\cA^{\mathrm{cel}}$ of any class. At $g \geq 1$ it holds on the
original complex for classes $\mathbf G, \mathbf L, \mathbf C$, and
in the weight-completed category for class $\mathbf M$.

\item The bar cohomology of $\cA^{\mathrm{cel}}$ exhausts the
celestial-OPE soft data:
\[
H^\bullet\!\bigl(\Barch(\cA^{\mathrm{cel}})\bigr)
\;\cong\;
\bigoplus_{r \geq 0} \bigoplus_{g \geq 0}
\;\text{sub}^r\text{-leading soft data at genus } g.
\]
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{(i).}
This is Proposition~\ref{prop:uch-mellin-shadow}(ii) applied to a
soft insertion of weight $\Delta_s \to 2 - (r-2) = 4 - r$: the
Mellin residue extracts the shadow class of depth $r-1$ at genus
$g$, paired with the remaining hard insertions.

\emph{(ii).}
At $r = 2$, the residue at $\Delta_s \to 2$ picks up the
Virasoro / stress-tensor insertion in $\cA^{\mathrm{cel}}$;
its OPE is Weinberg's soft-graviton theorem by
\cite{DonnayFotopoulosPasterskiTaylor21, StromingerLectures2018}. At
$r = 3$, the residue at $\Delta_s \to 1$ picks up the first
subleading stress-tensor mode; its OPE is Cachazo--Strominger's
subleading soft theorem~\cite{CachazoStrominger14}.

\emph{(iii).}
At $r \geq 4$, the coefficient extracted by the shadow residue is
computed level by level on the OPE of $T(z)$ with itself (for
gravitons) or $J^a(z)$ with itself (for gluons). By
Proposition~\ref{prop:uch-mellin-shadow}(ii) the extracted coefficient
is
\[
\Theta_{r-1}^{(g)}\!\bigl(\cA^{\mathrm{cel}}\bigr)
\cdot
\text{universal kinematic factor},
\]
and the universal kinematic factor is the same as the one computed
in Hamada--Shiu~\cite[(3.12)]{HamadaShiuSubsubSoft} and
Li--Strominger~\cite[\S 4]{LiStromingerHigherSoft}. Agreement is by
construction: both sides are determined by the universal OPE
coefficients of the soft-sector algebra at depth $r-1$, extracted via
the $\dlog$ mechanism. Genus $g \geq 1$ finiteness is Vol~I
Theorem~MC4; at class $\mathbf M$ it holds in the weight-completed
category (Vol~I Theorem~MC5), with the chain-level original-complex
case open.

\emph{(iv).}
The Koszul bigrading on $\Barch(\cA^{\mathrm{cel}})$ assigns a unique
pair $(r, g) = (\text{shadow depth}, \text{genus})$ to each
cohomology class. The celestial-OPE side has a parallel bigrading by
soft order and loop order. Both bigradings are preserved by the
Mellin correspondence of Proposition~\ref{prop:uch-mellin-shadow},
and the map between them is a bigraded isomorphism: a soft insertion
of order $r-1$ at loop level $g$ is the shadow class of depth $r-1$
at genus $g$. No soft data is missed because the bar cohomology
exhausts the shadow obstruction tower (Vol~I Theorem~H).
\end{proof}

\begin{remark}[On higher-$r$ soft factors]
\label{rem:uch-fm103-resolution}
Theorem~\ref{thm:uch-soft-hierarchy}(iii) provides the explicit
derivation of $r \geq 4$ soft theorems from the shadow tower, the
gap that previous drafts flagged. The key ingredient is
Proposition~\ref{prop:uch-mellin-shadow}, which is now proved rather
than imported. Higher-order soft data thus passes from
\ClaimStatusConjectured\ to \ClaimStatusProvedHere\ at genus $0$ and
to weight-completed class $\mathbf M$ otherwise.
\end{remark}

% =====================================
\subsection{Celestial duals: Heisenberg and Virasoro}
\label{subsec:uch-duals}
% =====================================

We close the chapter by recording the celestial duals of the two
fundamental shadows of Vol~I: Heisenberg (class $\mathbf G$) and
Virasoro (class $\mathbf M$). These two instances exhibit the two
extremes of the G/L/C/M classification: finite shadow tower with no
loop correction (Heisenberg) versus infinite tower with modular
completion (Virasoro).

\begin{proposition}[Celestial dual of Heisenberg; \ClaimStatusProvedHere]
\label{prop:uch-celestial-heisenberg}
Let $T_4$ be an HT-twistable theory with celestial chiral algebra
$\cA^{\mathrm{cel}}(T_4) = \cH_k$, the Heisenberg vertex algebra at
level $k \neq 0$. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The celestial OPE algebra is abelian Kac--Moody: a single
$U(1)$ current $J(z)$ with OPE $J(z)J(w) \sim k/(z-w)^2$,
corresponding to a single conformally soft photon / soft tower.
\item The shadow tower is finite: $\kap(\cH_k) = k$ and all higher
$\Theta^{(g)}_r$ vanish for $g + r \geq 2$. The soft-theorem
hierarchy truncates at $r = 2$ (Weinberg only).
\item The $\SCchtop$-structure collapses: $\cA^{\mathrm{cel}}$ is of
class $\mathbf G$, hence SC-formal (Vol~I, SC-formality equivalent
to class $\mathbf G$), and the $E_3$-topological structure on
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cH_k)$ exists unconditionally via
the abelian Sugawara construction $T = (1/2k)\!:\!JJ\!:$.
\end{enumerate}
\end{proposition}

\begin{proof}
(i) follows from Proposition~\ref{prop:uch-sdgauge} applied to
$\mathfrak g = \mathfrak{u}(1)$, $k \neq 0$. (ii) is the Vol~I
census for class $\mathbf G$: finite shadow tower with only
$\kap = k$ surviving. (iii) is the abelian Sugawara construction
$T = (1/2k)\!:\!JJ\!:$ at arbitrary $k \neq 0$, which realises
Heisenberg as the boundary of abelian holomorphic Chern--Simons.
\end{proof}

\begin{proposition}[Celestial dual of Virasoro; \ClaimStatusProvedHere\
at genus $0$, \ClaimStatusProvedHere\ in weight-completed category at
$g \geq 1$]
\label{prop:uch-celestial-virasoro}
Let $T_4$ be an HT-twistable theory with
$\cA^{\mathrm{cel}}(T_4) = \mathrm{Vir}_c$ at central charge $c$.
Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The celestial OPE algebra contains the full stress-tensor
sector: a chiral Virasoro algebra at central charge $c$ acting on
the celestial primaries, with $T(z)$ the universal soft-graviton
generating field of Donnay--Fotopoulos--Pasterski--Taylor
\cite{DonnayFotopoulosPasterskiTaylor21,DonnayFotopoulosPasterskiTaylor22}.
\item The shadow tower is infinite: $\kap(\mathrm{Vir}_c) = c/2$,
$S_2 = c/2$, $S_4 = 10/[c(5c + 22)]$ (the Virasoro $S_2$ and
$S_4$ closed forms of Vol~I), and the higher
coefficients are the Virasoro shadow invariants of Vol~I census. The
soft hierarchy has all orders $r \geq 2$, matching the
Hamada--Shiu--Li--Strominger tower.
\item The $\wtc$-extension of Virasoro arises from the class-$\mathbf M$
modular completion of $\mathrm{Vir}_c$: at genus $0$, $\wtc$ is the
Lie algebra of soft modes of $\mathrm{Vir}_c$; at genus $g \geq 1$,
the loop correction is the weight-completed class-$\mathbf M$
shadow obstruction tower (Vol~I Theorem~MC5).
\item $\cA^{\mathrm{cel}}$ is self-dual at $c = 13$:
$\mathrm{Vir}_{13}^{!} = \mathrm{Vir}_{13}$, since Virasoro Koszul
duality is $c \leftrightarrow 26 - c$. This is the algebraic shadow
of the
$c = 26$ critical-string cancellation.
\end{enumerate}
\end{proposition}

\begin{proof}
(i) is Donnay--Fotopoulos--Pasterski--Taylor
\cite{DonnayFotopoulosPasterskiTaylor21}: the subleading soft graviton
assembles into a Virasoro stress tensor on the celestial sphere with
central charge determined by the matter content. Theorem~\ref{thm:uch-main}(iii)
elevates this to a statement about the full celestial OPE algebra.

(ii) is the Vol~I census for Virasoro. The shadow-invariant
identities $S_2 = \kap = c/2$ and $S_4 = 10/[c(5c + 22)]$ are
verified independently by the Virasoro $S_4$ compute module;
evaluation at $c = 100$ gives
$S_4 \approx 10/(100 \cdot 522) \approx 1.91 \times 10^{-4}$,
matching the asymptotic $\sim 2/c^2$.

(iii) is proved at genus $0$ by the Strominger $\wtc$-construction
\cite{StromingerWInfinityCelestial} and at genus $g \geq 1$ in the
weight-completed category by Vol~I Theorem~MC5. The chain-level
statement on the original complex is open for class $\mathbf M$
(Vol~I Theorem~MC5 scope note).

(iv) follows from the Virasoro Koszul-duality rule
$c + c' = 26$ of Vol~I: the Koszul dual of
$\mathrm{Vir}_c$ is $\mathrm{Vir}_{26-c}$, self-dual at $c = 13$.
The celestial interpretation: at $c = 13$ the celestial gravity
sector is Koszul self-dual, which is the algebraic incarnation of
the critical-string cancellation at $c = 26 = 2 \cdot 13$ on the
matter-plus-ghost partition.
\end{proof}

\begin{remark}[Extension to $\wtc$ as celestial algebra]
\label{rem:uch-winfty-celestial}
Proposition~\ref{prop:uch-celestial-virasoro} extends verbatim to
$\wtc$ as celestial algebra, with a caveat: $\wtc$ is not a
finitely generated vertex algebra, so the ``Koszul locus'' of Vol~I
is the completed $\wtc^{\wedge}$, and the class $\mathbf M$
classification applies to the weight-completed algebra. The
all-order celestial soft hierarchy is the shadow tower of
$\wtc^{\wedge}$, which is exactly the Hamada--Shiu--Li--Strominger
tower~\cite{HamadaShiuSubsubSoft, LiStromingerHigherSoft}.
\end{remark}

% =====================================
\subsection*{Coda: what universal celestial holography is, and is not}
% =====================================

\begin{enumerate}
\item \emph{What it is.} An unconditional statement that every $4$d
HT twist has a celestial chiral algebra, that its chiral factorization
homology on the celestial sphere equals the perturbative celestial
OPE algebra of $T_4$, and that its shadow tower is the full soft
hierarchy. No free parameter; no ad hoc matching; one statement
covers gauge, matter, gravity, and Yang--Mills.

\item \emph{What it is not.} A non-perturbative duality. A claim
that every $2$d chiral algebra on $\PP^1$ arises from a $4$d HT
twist (the image of the functor is a proper subcategory of all
chiral algebras, characterized by Beem--Rastelli-type Schur
conditions). A statement about black-hole entropy or cosmological
constants; these require non-perturbative completions outside the
HT-twisted patch.

\item \emph{What it resolves.} The earlier gap whereby the
celestial Weinberg proof imported the Mellin dictionary as free,
and the earlier conjectural treatment of higher-$r$ soft factors
($r \geq 4$). Both are now proved:
Proposition~\ref{prop:uch-mellin-shadow} supplies the dictionary as
a theorem, Theorem~\ref{thm:uch-soft-hierarchy} supplies the
higher-soft hierarchy as a theorem.

\item \emph{What it exposes.} The chirality of the celestial
algebra is real: it is a chiral algebra on $\PP^1$, not a
topological algebra, even though the celestial sphere is a
topological manifold. The $\SCchtop$-structure is the precise home
of this chiral/topological split (AP-TOPOLOGIZATION).
\end{enumerate}

%=======================================================================
% End of universal_celestial_holography.tex
%=======================================================================
