% !TEX root = ../../main.tex
% ============================================================================
% Platonic W_infty E_infty-topological endpoint.
%
% Endpoint scope: the W_infty endpoint of the E_infty-topologization
% ladder is conditional on inverse-limit compatibility, all-spin
% homotopy, weight-window strong convergence, and obstruction-vanishing
% hypotheses. The rational-lambda
% truncation locus is treated separately by a companion theorem
% identifying the countable union of truncation hypersurfaces.
%
% Chapter structure:
% Section 1. Generic-lambda locus and the universal W_infty[lambda].
% Section 2. GGL convergence mechanism I: quasi-finite representation
% of lambda-Yangian via Prochazka triangular truncation.
% Section 3. GGL convergence mechanism II: Creutzig-Kanade-Linshaw
% parafermion framework + Heisenberg coset.
% Section 4. GGL convergence mechanism III: Pope-Romans-Shen classical
% w_infty wedge algebra + quantum deformation.
% Section 5. Uniform-in-spin convergence threshold N_0(w_max) = 2w_max-1.
% Section 6. The W_infty E_infty-topologization endpoint theorem.
% Section 7. Rational-lambda scope: truncation locus + companion theorem.
% Section 8. Local 6d hCS defect algebra (Costello-Gaiotto 2015).
% ============================================================================

\section{The \texorpdfstring{$\cW_\infty$}{W-infinity} \texorpdfstring{$\Einfty$}{E-infinity}-topological endpoint}
\label{sec:w-infty-e-infty-endpoint}

The $\Einfty$-topologization ladder of
Theorem~\ref{thm:e-infinity-topologization-ladder}
delivers $\Etopo{N+1}$ on $Z^{\mathrm{der}}_{\mathrm{ch}}(\cW_N)$ at every
finite spin $N$. Theorem~\ref{thm:e-infinity-specialisation-Winfty}
asserts the conditional $N \to \infty$ limit: the universal two-parameter algebra
$\cW_\infty[\lambda]$ of
Linshaw\,\cite{Linshaw-Winfty-universal} carries an
$\Einfty$-topological structure on its derived chiral centre once the
inverse-limit and convergence hypotheses are supplied.
Theorem~\ref{thm:w-infty-e-infty-topological-convergence} then provides
three coupled hypotheses -- Gaberdiel--Gopakumar OPE stabilisation,
$\infty$-categorical Dunn compatibility, and weight-window strong
convergence -- together with obstruction-vanishing for the homotopy
gluing. Their simultaneous verification at generic $c$ upgrades the
endpoint to a chain-level statement.

The generic endpoint has four independent hypotheses: finite-window GGL
stabilisation of universal structure constants, inverse-limit
compatibility of the iterated Dunn tower, a weight-window bound, and
vanishing of the resulting \(\lim^1\) obstruction classes. The
finite-window tests and the Prochazka / Eberhardt--Prochazka tables
supply evidence for the first hypothesis only. The endpoint theorem below is
conditional on the simultaneous all-spin form of these hypotheses. The
rational-$\lambda$ truncation locus is treated separately by an explicit
companion theorem.

\subsection{The generic-\texorpdfstring{$\lambda$}{lambda} locus}
\label{subsec:generic-lambda-locus}

The universal two-parameter $\cW_\infty[\lambda]$ of
Linshaw\,\cite{Linshaw-Winfty-universal} is a $\Z$-graded vertex algebra
with strong generators $\{T, W_3, W_4, \ldots\}$ of conformal weights
$\{2, 3, 4, \ldots\}$, one per integer spin $n \ge 2$, with OPE
structure constants that are polynomials in the central charge $c$
and the parameter $\lambda$. The \emph{truncation locus}
\begin{equation}\label{eq:truncation-locus}
\Lambda_{\mathrm{trunc}} \;=\;
\Bigl\{ (c, \lambda) \;:\; \cW_\infty[\lambda]\text{ truncates to some }
\cW_N[\lambda] \text{ at finite spin } N \Bigr\}
\end{equation}
is the countable union of the triality orbits of $\lambda \in
\{0, 1/2, 1, \infty, N, (N-1)/N, N/(N-1), \ldots : N \in \Z_{\ge 2}\}$,
together with the minimal-model loci of each $\cW_N$-truncation.
Concretely $\Lambda_{\mathrm{trunc}}$ is the union of countably many
irreducible hypersurfaces in $(c, \lambda)$-space
\textup{(}Prochazka--Rapcak~\cite{ProchazkaRapcak18}, Gaberdiel--Gopakumar--Li--Peng~\cite{%
GaberdielGopakumarLiPeng-Winfty}, Linshaw~\cite{Linshaw-Winfty-universal}
\textup{)}.

\begin{definition}[Generic-$\lambda$ locus]
\label{def:generic-lambda-locus}
\index{generic lambda locus@generic $\lambda$ locus|textbf}
\index{Winfty parameter space!generic locus}
The \emph{generic-$\lambda$ locus} $\Lambda_{\mathrm{gen}}$ is the
complement in $(c, \lambda)$-space of $\Lambda_{\mathrm{trunc}}$.
Equivalently, $(c, \lambda) \in \Lambda_{\mathrm{gen}}$ if and only if
every strong generator $W_n$ of $\cW_\infty[\lambda]$ of spin $n \ge 2$
is non-null and algebraically independent from $\{T, W_3, \ldots,
W_{n-1}\}$.
\end{definition}

\begin{remark}[Generic-$\lambda$ is open dense]
\label{rem:generic-lambda-open-dense}
$\Lambda_{\mathrm{gen}}$ is open dense in the $(c, \lambda)$-parameter
space of $\cW_\infty[\lambda]$. Its complement is the countable union
of $\cW_N$-truncation hypersurfaces plus finitely many minimal-model
lines. Every point of $\Lambda_{\mathrm{gen}}$ carries the full infinite
tower of strong generators.
\end{remark}

\subsection{GGL convergence mechanism I: Prochazka triangular truncation}
\label{subsec:ggl-mechanism-i-prochazka}

The first finite-window stabilisation theorem for GGL convergence at
generic $\lambda$ passes through Prochazka's triangular control of the universal
$\cW_\infty[\lambda]$ structure constants.

\begin{theorem}[Finite-window GGL stabilisation via Prochazka triangular
control; \ClaimStatusConditional]
\label{thm:ggl-convergence-prochazka}
\index{GGL convergence!Prochazka triangular truncation|textbf}
\index{Prochazka truncation!GGL convergence}
Let $(c, \lambda) \in \Lambda_{\mathrm{gen}}$ and fix a finite window
\[
M \;\ge\; \max(n_1,n_2,n_3,k).
\]
Assume the Prochazka--Rapcak triangular presentation is available on
this window with no null relation among the generators of spin
\(\le M\), and assume the projection to the finite truncation
\(\cW_N[\lambda]\) preserves the chosen normalisation for every
\(N\ge M\). Write the finite spin filtration on this window as
\begin{equation}\label{eq:prochazka-filtration}
F^{\le 2}\cW_\infty[\lambda]\subset
F^{\le 3}\cW_\infty[\lambda]\subset\cdots\subset
F^{\le M}\cW_\infty[\lambda].
\end{equation}
Then the OPE structure constant
\begin{equation}\label{eq:structure-constant-f}
f^{n_1 n_2}_{n_3,k}(c, \lambda)
\;=\;
\operatorname{Res}_{z \to w}\, (z-w)^{k-1}\,
\bigl[ W_{n_1}(z) W_{n_2}(w)\bigr]_{W_{n_3}}
\end{equation}
is computed inside the spin-\(\le M\) triangular window and stabilises
at truncation depth \(N\ge M\). Thus, under the stated finite-window
presentation and normalisation hypotheses, the specialisation of
\(f^{n_1 n_2}_{n_3,k}\) to \(\cW_N[\lambda]\) agrees with its
\(\cW_\infty[\lambda]\) value for all
\(N \ge \max(n_1,n_2,n_3,k)\).
\end{theorem}

\begin{proof}
The proof is the finite-window implication. In the assumed triangular
presentation, all normally ordered monomials contributing to the
coefficient of \(W_{n_3}\) in
\(W_{n_1}(z)W_{n_2}(w)\) have spin at most
\(\max(n_1,n_2,n_3,k)\). Choosing
\(M\) above that maximum therefore confines the computation of
\eqref{eq:structure-constant-f} to the spin-\(\le M\) presentation.
For \(N\ge M\), the projection to \(\cW_N[\lambda]\) preserves this
finite presentation and its normalisation by hypothesis, so the same
finite computation gives the same structure constant. The generic
\(\lambda\) assumption prevents a null relation inside the chosen
window from lowering the spin depth. No assertion about convergence of
the whole all-spin tower is used in this finite-window argument.
\end{proof}

\begin{remark}[Triangular truncation as three-commuting-Heisenbergs]
\label{rem:prochazka-three-heisenbergs}
The Prochazka realisation of $\cW_\infty[\lambda]$ as three commuting
Heisenberg currents $\alpha_1, \alpha_2, \alpha_3$ with specific
inner-product matrix $h_{ij}(\lambda)$ is the vertex-algebraic analogue
of the classical $u(\infty)$ wedge-algebra realisation. The three
Heisenbergs reflect the $\mathrm{S}_3$-triality of
$\cW_\infty[\lambda]$ under $\lambda \leftrightarrow
(1/(1-\lambda), 1-1/\lambda)$
\textup{(}Gaberdiel--Gopakumar~\cite{GaberdielGopakumar2011-Winfty}
\textup{)}; the triality exchanges the three Heisenberg roles, leaving
the structure constants invariant.
\end{remark}

\subsection{GGL convergence mechanism II: Creutzig--Kanade--Linshaw
parafermion framework}
\label{subsec:ggl-mechanism-ii-ckl}

The second finite-window stabilisation theorem uses the
Creutzig--Kanade--Linshaw
(CKL) coset framework as an independent route to the same bounded
structure constants.

\begin{theorem}[Finite-window GGL stabilisation via CKL parafermions;
\ClaimStatusConditional]
\label{thm:ggl-convergence-ckl}
\index{GGL convergence!Creutzig-Kanade-Linshaw|textbf}
\index{Creutzig-Kanade-Linshaw parafermion framework}
At $(c, \lambda) \in \Lambda_{\mathrm{gen}}$, fix a finite window
\(M\ge \max(n_1,n_2,n_3,k)\). Assume the CKL Heisenberg-coset
presentation of the relevant \(\cW_\infty[\lambda]\) fields is
compatible with finite-rank restriction through rank \(M\), and assume
the Pieri-rule truncation introduces no null relation in that window.
Then the OPE structure constants \(f^{n_1 n_2}_{n_3,k}(c,\lambda)\)
computed by the CKL route stabilise at truncation depth
\(N\ge M\).
\end{theorem}

\begin{proof}
Under the stated CKL hypotheses, the correlator contributing to
\(f^{n_1 n_2}_{n_3,k}\) is a finite sum of parafermion exchange
channels with rank bounded by \(M\). The finite-rank restriction to
\(\mathfrak{sl}_N\), \(N\ge M\), preserves those channels by the
assumed Pieri-rule compatibility. The Heisenberg coset is part of the
chosen presentation and is assumed to commute with this finite-rank
restriction on the window, so the same finite calculation computes the
\(\cW_N[\lambda]\) and \(\cW_\infty[\lambda]\) constants. The generic
\(\lambda\) hypothesis excludes accidental null-vector collapse in the
window. This proves the finite-window stabilisation theorem; it does not
assert unconditional all-spin convergence.
\end{proof}

\begin{remark}[CKL versus Prochazka disjointness]
\label{rem:ckl-vs-prochazka-disjoint}
Theorems~\ref{thm:ggl-convergence-prochazka} and
\ref{thm:ggl-convergence-ckl} provide genuinely disjoint
finite-window routes to the GGL stabilisation theorem. The Prochazka route uses three
commuting Heisenbergs +
Miura realisation + spin-filtration. The CKL route uses
$\mathfrak{sl}_\infty$-parafermions + Heisenberg coset + Pieri rule at
infinite rank. Neither route invokes the other. The two agree on the
polynomiality of $f^{n_1 n_2}_{n_3,k}$ in $(c, \lambda)$ and on the
truncation threshold $N \ge \max(n_1, n_2, n_3, k)$, which by the
formulation of Theorem~\ref{thm:w-infty-e-infty-topological-convergence}
is the exact finite-window stabilisation needed for the weight-window
condition~\textup{(c)}.
\end{remark}

\subsection{GGL convergence mechanism III: Pope--Romans--Shen
classical wedge algebra}
\label{subsec:ggl-mechanism-iii-prs}

The third finite-window stabilisation theorem starts from the classical
Pope--Romans--Shen (PRS) wedge algebra and then asks for compatibility
of the Bakas quantum deformation with the same bounded spin window.

\begin{theorem}[Finite-window GGL stabilisation via PRS wedge algebra + Bakas
quantisation; \ClaimStatusConditional]
\label{thm:ggl-convergence-prs-bakas}
\index{GGL convergence!Pope-Romans-Shen + Bakas|textbf}
\index{Pope-Romans-Shen wedge algebra}
\index{Bakas quantum deformation}
Let $w_\infty$ be the classical Pope--Romans--Shen wedge algebra of
higher-spin area-preserving diffeomorphisms of the cylinder
$\cylinder = \R \times S^1$, constructed in
\cite{PopeRomansShen-winfty-wedge}. Its Bakas quantum deformation
$W_\infty = \mathrm{Quant}_\hbar(w_\infty)$
\cite{Bakas-Winfty,BergshoeffPopeShen-Winfty-quantum} with
$\hbar$-expansion parameter identified with the inverse central charge
$\hbar = 1/c$ gives the wedge specialisation of the
$\cW_\infty$ family. Fix a finite window
\(M\ge\max(n_1,n_2,n_3,k)\). Assume the PRS
\(\mathrm{SU}(\infty)\)-to-\(\mathrm{SU}(N+1)\) wedge truncation
preserves all classical constants in this window for \(N\ge M\), and
assume the Bakas quantum deformation is windowwise compatible with the
same truncation order by order in \(\hbar\). Then the corresponding
quantum structure constants stabilise at depth \(N\ge M\).
\end{theorem}

\begin{proof}
The classical PRS wedge calculation of a fixed constant
\(g^{n_1 n_2}_{n_3,k}\) only uses modes inside the chosen spin window.
By the windowwise truncation hypothesis, the classical
\(\mathrm{SU}(\infty)\) and \(\mathrm{SU}(N+1)\) computations therefore
agree for \(N\ge M\). The Bakas deformation replaces the Poisson bracket
by its Moyal deformation. The assumed order-by-order compatibility says
that each \(\hbar^p\)-coefficient of the quantum constant is obtained
from the same finite classical window, so it stabilises at the same
depth. If the \(\hbar\)-series is summed at \(\hbar=1/c\), this gives the
finite-window quantum stabilisation. Extension from the wedge
specialisation to the full two-parameter family is an additional
normalisation-identification hypothesis, not a consequence of the PRS
calculation alone.
\end{proof}

\begin{remark}[Three mechanisms, three mathematical ingredients]
\label{rem:three-mechanisms-three-ingredients}
The three finite-window routes to the GGL stabilisation theorem use three genuinely
disjoint mathematical ingredients:
\begin{itemize}
\item \textbf{Prochazka triangular truncation} (Miura realisation +
 three Heisenberg currents + spin filtration).
\item \textbf{CKL parafermion framework}
 ($\mathfrak{sl}_\infty$-parafermions + Heisenberg coset + Pieri
 rule at infinite rank).
\item \textbf{PRS wedge algebra + Bakas quantisation} (symplectic
 geometry of $\mathrm{SU}(\infty)$ + Moyal deformation at
 $\hbar = 1/c$).
\end{itemize}
No route invokes the algebraic ingredients of another. Agreement on
the finite-window stabilisation threshold
$N \ge \max(n_1, n_2, n_3, k)$ confirms the threshold is structural
within the checked window, not an unconditional proof of all-spin
convergence.
\end{remark}

\subsection{Uniform-in-spin convergence threshold}
\label{subsec:uniform-in-spin-threshold}

The weight-window condition has an explicit uniform-in-spin bound
compatible with the two-slot OPE terms in the ordered bar differential.

\begin{proposition}[Uniform threshold $N_0(w_{\max}) = 2w_{\max} - 1$;
\ClaimStatusProvedHere]
\label{prop:uniform-threshold-2wmax-minus-1}
\index{weight-window threshold!uniform|textbf}
\index{convergence threshold!uniform in spin}
For every bar-weight window $[w_{\min}, w_{\max}]$ and every point
$(c, \lambda) \in \Lambda_{\mathrm{gen}}$, assume finite-window GGL
stabilisation holds for all OPE constants with
\(n_i,k\le 2w_{\max}-1\). Then the finite-$N$ truncation
$\cW_N[\lambda]$ of $\cW_\infty[\lambda]$ induces an isomorphism on
the weight-window subspaces for all $N \ge 2 w_{\max} - 1$. In
particular the bar-weight-$w$ component of the ordered bar complex
$B^{\mathrm{ord}}(\cW_\infty[\lambda])$ is computed in the truncation
$\cW_{2w - 1}[\lambda]$ for every $w \le w_{\max}$.
\end{proposition}

\begin{proof}
A bar-weight-$w$ element of $B^{\mathrm{ord}}(A)$ is a sum over
$k$-tuples $(a_1, \ldots, a_k)$ of strong generators with total
conformal weight $\le w$. In particular every slot entering the
bar differential has spin at most $w$. The differential contracts two
slots at a time. For vertex algebra fields of spins $p$ and $q$, every
non-vacuum singular OPE term entering the ordered bar differential has
output spin and pole order bounded by $p+q-1$: the $r$-th product has
weight $p+q-r-1$, and the vacuum term is killed by the augmentation of
the reduced ordered bar complex. Therefore, for all two-slot
contractions in the window,
\[
n_1\le w,\qquad n_2\le w,\qquad n_3\le 2w-1,\qquad k\le 2w-1 .
\]
By the finite-window stabilisation theorem
Theorem~\ref{thm:ggl-convergence-prochazka}, or by either independent
finite-window route in
Theorems~\ref{thm:ggl-convergence-ckl} and
\ref{thm:ggl-convergence-prs-bakas}, the corresponding structure
constants $f^{n_1n_2}_{n_3,k}$ stabilise whenever
$N\ge\max(n_1,n_2,n_3,k)$, hence whenever $N\ge2w-1$.

Uniformity in $\lambda$: the bound $N_0(w_{\max}) = 2w_{\max} - 1$ is
independent of $\lambda \in \Lambda_{\mathrm{gen}}$ because the
Prochazka filtration is constructed over the full parameter space and
only depends on the spin grading, not on the specific values of
structure constants.
\end{proof}

\begin{remark}[The $N_0 = w_{\max} - 1$ heuristic]
\label{rem:n0-refinement-2wmax}
The rough threshold $N_0 = w_{\max} - 1$ is the weight-one-at-a-time
heuristic: a weight-$w$ element only sees generators of spin at most
$w$ before the bar differential is applied. The refined bound
$N_0 = 2 w_{\max} - 1$ accounts
explicitly for two-slot OPE interactions in the bar differential,
which are the actual consumers of truncation depth. It is the uniform
bound used by the endpoint proof.
\end{remark}

\subsection{The \texorpdfstring{$\cW_\infty$}{W-infinity}
\texorpdfstring{$\Einfty$}{E-infinity}-topologization endpoint}
\label{subsec:w-infty-endpoint-theorem}

The finite-window GGL stabilisation theorems, the uniform threshold, and the
weightwise inverse-limit obstruction theory determine the endpoint
theorem.

\begin{theorem}[$\cW_\infty$ $\Einfty$-topologization endpoint;
\ClaimStatusConditional]
\label{thm:w-infty-e-infty-topologization-endpoint}
\index{Wbar infinity algebra@$\cW_\infty$-algebra!E\_infty-topologization endpoint|textbf}
\index{E-infinity-topologization!inverse-limit endpoint|textbf}
\index{endpoint theorem!W-infinity}
Let $(c, \lambda) \in \Lambda_{\mathrm{gen}}$. Assume the all-spin
family of finite-window GGL stabilisation hypotheses, inverse-limit Dunn
compatibility, weight-window strong convergence,
truncation-compatible antighost homotopies, and vanishing of the
obstruction classes
\[
 \delta_{w,r}\in
 \varprojlim\nolimits_N^{1}
 H^{-1}\!\left(\operatorname{End}^{(r)}
 \bigl(B^{\mathrm{ord}}(\cW_N[\lambda])^{\le w}\bigr)\right)
\]
recorded in
Theorems~\textup{\ref{thm:e-infinity-weightwise-inverse-limit}} and
\textup{\ref{thm:w-infty-e-infty-topological-convergence}}.
Then
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cW_\infty[\lambda])$ carries a
chain-level $\Einfty$-topological algebra structure, obtained as the
strong inverse limit of the $\mathrm{E}_{N+1}^{\mathrm{top}}$-structures on
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cW_N[\lambda])$ along the triangular
filtration~\eqref{eq:prochazka-filtration}. The limit is strong in
the sense of
Theorem~\textup{\ref{thm:w-infty-e-infty-topological-convergence}}(c,d):
every bar-weight window $[w_{\min}, w_{\max}]$ is computed in the
finite truncation $\cW_{N_0(w_{\max})}[\lambda]$ with
$N_0(w_{\max}) = 2 w_{\max} - 1$.

The resulting structure is the inverse-limit endpoint of the
$\Einfty$-topologization ladder of
Theorem~\textup{\ref{thm:e-infinity-topologization-ladder}}: it is
commutative up to all higher coherences at generic $\lambda$.
\end{theorem}

\begin{proof}
The proof assembles the finite-rung constructions with the stated
inverse-limit hypotheses.

\textbf{(i) Finite-$N$ rungs.}
Theorem~\ref{thm:e-infinity-specialisation-WN} supplies for each
finite $N \ge 2$ an $\mathrm{E}_{N+1}^{\mathrm{top}}$-structure on
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cW_N[\lambda])$ via the iterated
Sugawara identities at spins $2, 3, \ldots, N$.

\textbf{(ii) All-spin antighost compatibility.}
Theorem~\ref{thm:casimir-antighost-commutativity} supplies, for each
finite \(N\), the screened Koszul homotopies making the finite
antighost systems \(\{G^{(2)},\ldots,G^{(N)}\}\) pairwise
BRST-commuting, together with the higher coherence homotopies needed by
the finite Dunn assembly. Eventual constancy of these homotopies on
bounded \(\cW_\infty[\lambda]\) weight windows is one of the stated
inverse-limit hypotheses, not a consequence of the finite theorem.

\textbf{(iii) Finite-window GGL stabilisation.}
Theorems~\ref{thm:ggl-convergence-prochazka},
\ref{thm:ggl-convergence-ckl}, and
\ref{thm:ggl-convergence-prs-bakas} give conditional and independent
finite-window routes for the OPE structure constants
$f^{n_1 n_2}_{n_3, k}(c, \lambda)$ to stabilise at truncation depth
$N \ge \max(n_1, n_2, n_3, k)$. The endpoint assumes their compatible
all-spin extension.

\textbf{(iv) Uniform weight-window threshold.}
Proposition~\ref{prop:uniform-threshold-2wmax-minus-1} lifts the
structure-constant stabilisation to a weight-window stabilisation of
the ordered bar complex: bar-weight-$w$ data is computed in
$\cW_{2w - 1}[\lambda]$.

\textbf{(v) $\infty$-operadic limit.}
Theorem~\ref{thm:e-infinity-weightwise-inverse-limit}, applied with
the hypotheses recorded in
Theorem~\ref{thm:w-infty-e-infty-topological-convergence}, identifies
the weight-window-stable inverse limit of the finite-$N$
$\mathrm{E}_{N+1}^{\mathrm{top}}$-structures with the operadic target
$\Einfty = \lim_N \mathrm{E}_{N+1}^{\mathrm{top}}$ in
$\mathrm{Op}_\infty^{\otimes}$ (Lurie HA~\cite{HA} Notation 5.1.1.5).
The vanishing of the classes \(\delta_{w,r}\) is what lifts the finite
homotopies and higher coherences to the completed chain-level object.

Combining (i)--(v) at $(c, \lambda) \in \Lambda_{\mathrm{gen}}$:
each bar-weight window of $B^{\mathrm{ord}}(\cW_\infty[\lambda])$ is
computed in the finite truncation $\cW_{N_0(w_{\max})}[\lambda]$, and
the $\mathrm{E}_{N_0 + 1}^{\mathrm{top}}$-structure of the truncation
is transported along the filtration morphisms to produce a strong
chain-level $\Einfty$-algebra structure on
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cW_\infty[\lambda])$.
\end{proof}

\begin{remark}[Endpoint versus finite rungs]
\label{rem:endpoint-versus-finite-rungs}
Theorem~\ref{thm:w-infty-e-infty-topologization-endpoint} is the
inverse-limit form of the finite-rung ladder. It is conditional on
the all-spin finite-window GGL hypotheses, inverse-limit Dunn compatibility,
weight-window strong convergence, and obstruction-vanishing hypotheses
recorded in
Theorem~\ref{thm:w-infty-e-infty-topological-convergence}.
The executable checks in Section~\ref{subsec:w-infty-endpoint-tests}
verify the finite threshold arithmetic and decorator consistency; they
do not compute all-spin structure constants or prove the endpoint.
\end{remark}

\subsection{Rational-\texorpdfstring{$\lambda$}{lambda} scope: truncation
locus companion theorem}
\label{subsec:rational-lambda-scope}

At truncation-locus points $(c, \lambda) \in \Lambda_{\mathrm{trunc}}$,
$\cW_\infty[\lambda]$ reduces to a finite-spin algebra $\cW_N[\lambda]$.
The $\Einfty$-topologization endpoint does not apply (the infinite
stress tower collapses to depth $N$); what survives is the
$\mathrm{E}_{N+1}^{\mathrm{top}}$-rung itself.

\begin{theorem}[Truncation-locus companion; \ClaimStatusProvedHere]
\label{thm:truncation-locus-companion}
\index{Winfty truncation locus!companion theorem|textbf}
\index{rational lambda!E\_infty endpoint scope}
For $(c, \lambda) \in \Lambda_{\mathrm{trunc}}$ with
$\cW_\infty[\lambda] \cong \cW_N[\lambda]$ at depth $N =
N(c, \lambda) \in \Z_{\ge 2}$, the derived chiral centre
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cW_\infty[\lambda])$ carries an
$\mathrm{E}_{N+1}^{\mathrm{top}}$-structure (not $\Einfty$) as the
endpoint of the ladder; the structure is the
$\mathrm{E}_{N+1}^{\mathrm{top}}$-datum of
Theorem~\textup{\ref{thm:e-infinity-specialisation-WN}} applied to
the finite-$N$ algebra.
\end{theorem}

\begin{proof}
Truncation $\cW_\infty[\lambda] \cong \cW_N[\lambda]$ at $(c, \lambda)
\in \Lambda_{\mathrm{trunc}}$ means the universal algebra reduces to a
finite-generator algebra of depth $N$. The higher-spin stress tower
collapses at depth $N$: $T^{(n)}$ for $n > N$ is a null-vector or a
composite of lower-spin fields, hence supplies no new independent
antighost $G^{(n)}$. Theorem~\ref{thm:e-infinity-topologization-ladder}
at depth $N$ produces an $\mathrm{E}_{N+1}^{\mathrm{top}}$-structure,
which is the terminal rung of the ladder for the truncated family.

No $\Einfty$-ladder convergence is needed at truncation points: the
ladder stabilises already at finite depth, and the statement coincides
with the finite-$N$ theorem (without any passage to inverse limit).
\end{proof}

\begin{remark}[Completeness of scope]
\label{rem:complete-scope}
The universal $\cW_\infty[\lambda]$ parameter space decomposes as
$\Lambda_{\mathrm{gen}} \sqcup \Lambda_{\mathrm{trunc}}$:
\begin{itemize}
\item On $\Lambda_{\mathrm{gen}}$:
 Theorem~\ref{thm:w-infty-e-infty-topologization-endpoint} delivers
 $\Einfty$-top under the inverse-limit hypotheses.
\item On $\Lambda_{\mathrm{trunc}}$:
 Theorem~\ref{thm:truncation-locus-companion} delivers
 $\mathrm{E}_{N+1}^{\mathrm{top}}$ with finite $N$.
\end{itemize}
The $\Einfty$-topologization endpoint theorem holds under those
hypotheses at generic $\lambda$; at rational truncation points the
ladder itself stabilises at finite height. Thus the alternatives are a
conditional inverse-limit problem on the generic locus and a finite
rung on the truncation locus.
\end{remark}

\subsection{Local 6d hCS defect algebra on
\texorpdfstring{$\mathrm{CY}_3$}{CY3} (Costello--Gaiotto 2015)}
\label{subsec:cross-volume-6d-hcs}

The universal $\cW_\infty[\lambda]$-algebra arises independently on
the hCS side: it is the boundary algebra of $6$d holomorphic
Chern--Simons on a Calabi--Yau threefold $Y$ in the presence of a
codimension-$2$ defect along a curve $C \subset Y$
\textup{(}Costello--Gaiotto~\cite{costello-gaiotto-6d-hCS}\textup{)}.

\begin{proposition}[Local $6$d hCS endpoint and compact Hall obstruction;
\ClaimStatusConditional]
\label{prop:vol-ii-iii-coincidence}
\index{6d holomorphic Chern-Simons!Winfty E-infinity endpoint|textbf}
\index{6d holomorphic Chern-Simons!CY3 defect}
\index{Costello-Gaiotto 2015!Winfty}
At $(c, \lambda) \in \Lambda_{\mathrm{gen}}$, the chain-level
$\Einfty$-topological structure on
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cW_\infty[\lambda])$ of
Theorem~\ref{thm:w-infty-e-infty-topologization-endpoint} matches the
local Costello--Gaiotto defect algebra of $6$d holomorphic
Chern--Simons on a Calabi--Yau threefold $Y$ with a codimension-$2$
defect supported on a curve $C \subset Y$, after removing the
Heisenberg factor and identifying the Costello--Gaiotto parameter
$\Psi$ with the triality parameter $\lambda$.

This is a local boundary comparison. It does not construct a compact
critical CoHA, a completed Hall--Drinfeld double, or a
Hall-to-Borcherds comparison for compact $K3\times E$. A finite Rees
hCS--Hall map has target only a finite oriented Rees Hall complex:
\[
 \mathsf{Obs}_{6d\,\mathrm{hCS}}^{\le N,\le r}
 \xrightarrow{\;\Theta^{\mathrm{Rees},N,r,L,m}\;}
 \mathsf{Hall}_{\mathrm{crit}}^{\mathrm{Rees},\mathrm{or},\le N,\le L}.
\]
Passing from this finite map to a compact critical CoHA requires
compatible inverse limits, vanishing-cycle realisation, orientations,
Thom--Sebastiani transport, proper pushforward, lci pullback,
equivariance, Tate twists, and completions. Passing from the realised
positive half to a Hall--Drinfeld double additionally requires a
negative half, Cartan, Hall coproduct, non-degenerate Hall pairing,
Borcherds--Serre kernel comparison, centre computation, and a common
pro-Borcherds topology.
\end{proposition}

\begin{proof}
Costello--Gaiotto~\cite{costello-gaiotto-6d-hCS} show that $6$d hCS on
$Y$ with defect on $C$ has boundary algebra
$\cW_{1+\infty}^{\Psi = -\sigma_2}$, the universal $\cW_{1+\infty}$
algebra with Heisenberg coupling $\Psi$ determined by the second
Chern class of the normal bundle $N_{C/Y}$ as
$\sigma_2 = c_1(N_{C/Y})^2$. Removing the Heisenberg subalgebra via
the coset reduction yields $\cW_\infty[\lambda]$ with $\lambda$
determined by $\Psi$; the map $\Psi \mapsto \lambda$ is the standard
triality-covariant parametrisation of Gaberdiel--Gopakumar~\cite{%
GaberdielGopakumar2011-Winfty}.

The $6$d hCS defect algebra is factorisation-theoretic in the
Costello--Gwilliam sense: locally on the formal neighbourhood of the
defect, the transverse topological directions and the holomorphic
directions assemble by Dunn additivity. After the Heisenberg coset the
boundary algebra is the same universal $\cW_\infty[\lambda]$ family
used in the endpoint theorem. The inverse-limit construction in
Theorem~\ref{thm:w-infty-e-infty-topologization-endpoint} therefore
acts on the same local vertex algebra once the generic-$\lambda$ and
all-spin finite-window, Dunn-compatibility, and obstruction-vanishing
hypotheses are imposed.

The compact Hall assertions are different constructions. A finite Rees
map records bounded hCS observables as finite Rees Hall classes; it has
not supplied Borel--Moore homology with vanishing cycles, the compact
orientation datum, the completed coproduct, the negative half, or the
Hall pairing. Hence the local $6$d hCS/$\cW_\infty$ comparison proves
the boundary endpoint and constructs no compact CoHA or Hall--Drinfeld
double. The displayed obstruction chain is forced by the missing data:
each dashed passage requires extra structure absent from a finite Rees
layer.
\end{proof}

\begin{remark}[Three typed constructions]
\label{rem:three-way-consistency}
At $(c, \lambda) \in \Lambda_{\mathrm{gen}}$, three constructions meet
on the same local $\cW_\infty[\lambda]$ boundary algebra:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the iterated-Sugawara ladder inverse limit
 \textup{(}Theorem~\ref{thm:w-infty-e-infty-topologization-endpoint}\textup{)};
\item the three-mechanism GGL structure-constant stabilisation
 \textup{(}Theorems~\ref{thm:ggl-convergence-prochazka},
 \ref{thm:ggl-convergence-ckl},
 \ref{thm:ggl-convergence-prs-bakas}\textup{)};
\item the local Costello--Gaiotto $6$d hCS defect algebra on
 $\mathrm{CY}_3$
 \textup{(}Proposition~\ref{prop:vol-ii-iii-coincidence}\textup{)}.
\end{enumerate}
The compact $K3\times E$ Hall problem starts after these local
identifications: the positive half must be realised as a compact
critical CoHA, doubled, oriented, completed, and compared with the
Borcherds denominator before any Hall--Drinfeld conclusion follows.
\end{remark}

\subsection{Finite-window executable checks}
\label{subsec:w-infty-endpoint-tests}

The executable finite-window check
\texttt{compute/tests/test\_winfty\_finite\_window.py} verifies the
two-slot arithmetic behind
Proposition~\ref{prop:uniform-threshold-2wmax-minus-1}: a
bar-weight-\(w\) ordered-bar differential can require spin cutoff
\(2w-1\). In particular the spin-\(\le4\) truncation gives the finite
\(\mathrm{E}_5^{\mathrm{top}}\) rung but does not meet the
bar-weight-\(4\) threshold, which is spin \(7\).

The file \texttt{compute/tests/test\_w\_infty\_endpoint.py} records
decorator-level consistency for the conditional theorem surfaces. It
does not compute all-spin \(\cW_\infty\) structure constants, does not
compare new Prochazka / CKL / PRS-Bakas tables, and does not prove
obstruction vanishing. Its role is to keep the declared finite-window
hypotheses, operadic data, and conditional endpoint hypotheses separated.

\providecommand{\wtc}{\mathfrak{w}_{1+\infty}}

\subsection{Celestial specialisation: Strominger's \texorpdfstring{$w_{1+\infty}$}{w1+infty}
as the classical endpoint}
\label{subsec:celestial-specialisation-strominger}

The inverse-limit endpoint of
Theorem~\ref{thm:w-infty-e-infty-topologization-endpoint} specialises
to the celestial chiral algebra of 4d self-dual gravity along
\(\hbar\)-adically controlled generic paths. Strominger's
$w_{1+\infty}$ \cite{StromingerWInfinityCelestial} is the
Pope--Romans--Shen wedge algebra of area-preserving diffeomorphisms of
the cylinder, extended by a Heisenberg current; the universal
$\cW_{1+\infty}[\lambda]$ at generic $\lambda$ and finite $c$ Bakas-quantises
this classical structure with $\hbar = 1/c$, so the $\hbar\to 0$ limit
recovers the Poisson vertex algebra underlying Strominger's soft
graviton OPE.

\begin{theorem}[Celestial $w_{1+\infty}$ as the classical endpoint of
the $\Einfty$-topologization ladder; \ClaimStatusConditional]
\label{thm:celestial-winfty-classical-endpoint}
\index{celestial!w_{1+infty}|textbf}
\index{Strominger!w_{1+infty} endpoint}
\index{celestial holography!endpoint theorem}
Let $\wtc := \mathfrak{w}_{1+\infty}$ denote Strominger's celestial
chiral algebra, presented as the Poisson vertex algebra with strong
generators $\{H, W^{(2)}, W^{(3)}, W^{(4)}, \dots\}$ of conformal weights
$\{1, 2, 3, 4, \dots\}$ and classical $\lambda$-brackets
\begin{equation}\label{eq:celestial-winfty-lambda-brackets}
\{W^{(p)}{}_\lambda W^{(q)}\}_{\mathrm{cl}}
\;=\;
\bigl((p-1)\partial + (p+q-2)\lambda\bigr) W^{(p+q-2)},
\qquad
\{H{}_\lambda W^{(q)}\}_{\mathrm{cl}} \;=\; 0
\quad (q \ge 2),
\end{equation}
with $H$ the Heisenberg current carrying the ``$1+$'' soft-photon
sector.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(Classical-limit identification.)} There is a canonical
isomorphism of Poisson vertex algebras
\[
\wtc
\;\;\cong\;\;
\lim_{\hbar \to 0}\,\cW_{1+\infty}[\lambda=0]_{c = \hbar^{-1}},
\]
where $\cW_{1+\infty}[\lambda]$ is Prochazka--Rapcak's universal
two-parameter family \cite{ProchazkaRapcak18} and the limit is the
classical $c \to \infty$ rescaling in which all quantum OPE corrections
vanish. The mode identification $W^{(p)}_m = w^p_m$ with
$[w^p_m, w^q_n] = (m(q-1) - n(p-1))\, w^{p+q-2}_{m+n}$ matches
Strominger's commutator~\cite[eq.~(1)]{StromingerWInfinityCelestial}.

\item \textup{($\Einfty$-topological structure.)} Fix a generic path
\((c_t,\lambda_t)\in\Lambda_{\mathrm{gen}}\) with
\(\hbar_t=c_t^{-1}\to0\) and \(\lambda_t\to0\). Assume:
\[
\begin{gathered}
\text{the endpoint hypotheses of
Theorem~\ref{thm:w-infty-e-infty-topologization-endpoint} hold for
each \(t\),}\\
\text{the finite-window antighosts and Dunn coherences form
\(\hbar\)-adic Mittag--Leffler systems,}\\
\delta^{\hbar}_{w,r}\in
\varprojlim\nolimits_N^{1}
H^{-1}\!\left(\operatorname{End}^{(r)}
\bigl(B^{\mathrm{ord}}(\cW_N[\lambda_t])^{\le w}\bigr)
\widehat{\otimes}\C[[\hbar]]\right)
\text{ vanishes for all \(w,r\),}\\
\text{and the chosen path is triality-compatible with the
\(\lambda=0\) classical normalisation.}
\end{gathered}
\]
Then the classical derived chiral centre
\(Z^{\mathrm{der}}_{\mathrm{ch}}(\wtc)\) inherits an
\(\Einfty\)-topological algebra structure by \(\hbar\to0\)
specialisation. The antighosts \(G^{(n)}\) specialise to Poisson
antighosts \(G^{(n)}_{\mathrm{cl}}\), and the finite-window threshold
\(N_0(w_{\max})=2w_{\max}-1\) remains the same.

\item \textup{($\SCchtop$-realisation.)} The $\Einfty$-topological
datum of (ii) is the boundary component of an
$\SCchtop$ bulk--boundary datum whose bulk is the holomorphic--topological
3d slab reduction of 4d self-dual gravity, equivalently (after the
Costello--Paquette--Sharma twistor twist \cite{CostelloPaquetteSharmaCelestial})
holomorphic Chern--Simons theory on twistor space $\mathbb{PT}$ with
gauge algebra $\mathfrak{ham}(\C^2) = \mathrm{Lie}(w_\infty)$, compactified
on the twistor line $\CP^1 \subset \mathbb{PT}$ identified with the
celestial sphere.
\end{enumerate}
\end{theorem}

\begin{proof}
\textbf{(i) Classical-limit identification.}
Bakas quantisation (Theorem~\ref{thm:ggl-convergence-prs-bakas}) identifies
$\cW_\infty[\mu]$ at $\mu = \lambda$ with the Moyal deformation of the
PRS wedge algebra $w_\infty$ at $\hbar$-parameter tied to the central
charge via $\hbar^2 = (c(5c+22))^{-1}$ (Bergshoeff--Pope--Shen
\cite{BergshoeffPopeShen-Winfty-quantum} Theorem 3.2). The ``$1+$''
Heisenberg extension to $\cW_{1+\infty}[\lambda]$ appears as the
triality-covariant coset factor: Prochazka--Rapcak~\cite{ProchazkaRapcak18}
Theorem 4.3 realise $\cW_{1+\infty}[\lambda] = \cW_\infty[\lambda]
\otimes \mathrm{Heis}$, with $\lambda = 0$ the triality-fixed point at
which the Moyal deformation degenerates to Poisson bracket on $\C^2$.
Taking $\hbar\to 0$ (equivalently $c\to\infty$ with generators rescaled
$W^{(p)} \mapsto c^{(p-2)/2} W^{(p)}$) sends the Moyal bracket to the
Poisson bracket on $T^*S^1$, which by
PRS~\cite{PopeRomansShen-winfty-wedge} is exactly the area-preserving
diffeomorphism algebra of the cylinder generating
$\mathfrak{w}_{1+\infty}$. The mode commutator match
$[w^p_m, w^q_n] = (m(q-1) - n(p-1))\,w^{p+q-2}_{m+n}$ is the Fourier
decomposition of~\eqref{eq:celestial-winfty-lambda-brackets}: writing
$W^{(p)}(z) = \sum_m w^p_m z^{-m-p}$ and extracting the Laurent mode
of the $\lambda$-bracket recovers Strominger's commutator verbatim
\cite[eq.~(1)]{StromingerWInfinityCelestial}.

\textbf{(ii) $\Einfty$-topological structure.}
For each finite \(t\), the endpoint theorem supplies a chain-level
\(\Einfty\)-topological structure on
\(\Zder(\cW_\infty[\lambda_t])\) under its hypotheses. On a fixed
bar-weight window \(w\), the finite-rung construction is already
computed in spin cutoff \(N_0(w)=2w-1\). The assumed
\(\hbar\)-adic Mittag--Leffler condition therefore gives a completed
inverse system of the finite operations, translations, antighost
homotopies, and Dunn coherences. The obstruction group is precisely
\[
\varprojlim\nolimits_N^{1}
H^{-1}\!\left(\operatorname{End}^{(r)}
\bigl(B^{\mathrm{ord}}(\cW_N[\lambda_t])^{\le w}\bigr)
\widehat{\otimes}\C[[\hbar]]\right).
\]
Vanishing of \(\delta^\hbar_{w,r}\) lifts the finite coherences through
the completed tower. Specialising \(\hbar\) to \(0\) sends the quantum
OPE brackets to the Poisson brackets of \(\wtc\), sends
\(G^{(n)}\) to \(G^{(n)}_{\mathrm{cl}}\), and preserves the finite
Dunn coherences because they have already been lifted in the completed
system. Thus
\(Z^{\mathrm{der}}_{\mathrm{ch}}(\wtc)\) carries the asserted
chain-level \(\Einfty\)-topological structure.

\textbf{(iii) $\SCchtop$-realisation.}
The 3d holomorphic--topological slab reduction of 4d self-dual gravity
on $\R^4 = \C \times \R^2$ with the HT twist adapted to the fibration
$\R^4 \to \R^2$ produces a 3d bulk theory on $\C \times \R$ whose
boundary on $\C \times \{0\}$ carries the celestial chiral algebra
\cite{CostelloPaquetteSharmaCelestial,
BittlestonHeuvelineSkinner}. Costello--Paquette--Sharma identify the
4d self-dual sector with holomorphic Chern--Simons on twistor space
$\mathbb{PT} = \cO(1)\oplus\cO(1) \to \CP^1$ with gauge algebra
$\mathfrak{ham}(\C^2)$ of Hamiltonian vector fields on the symplectic
fibre; compactifying hCS along the fibre directions delivers the
boundary chiral algebra $\wtc$ on the twistor base $\CP^1$,
identified with the celestial sphere. The resulting bulk--boundary pair
$(\text{3d HT gravity}, \wtc)$ is governed by the two-coloured
Swiss-cheese operad $\SCchtop$: the bulk operations are the
$E_3^{\mathrm{top}}$ operations of the HT 3-manifold, the boundary
operations are the \(E_\infty^{\mathrm{top}}\) operations of
part~(ii), and the mixed operations are the bulk-to-boundary maps of
Costello--Gwilliam factorisation on $\C \times \R_{\ge 0}$. This is
the $\SCchtop$-algebra structure of the foundational
Swiss-cheese-chiral-topological framework (chapter
\texttt{factorization\_swiss\_cheese.tex}) applied to the present
bulk--boundary pair under the hypotheses of part~(ii).
\end{proof}

\begin{remark}[Soft-theorem OPE as the chiral OPE]
\label{rem:soft-theorem-chiral-ope}
The celestial OPE of positive-helicity soft gravitons
\cite[eq.~(11)]{StromingerWInfinityCelestial},
\begin{equation}\label{eq:soft-graviton-ope}
\lim_{\Delta_1 \to 2}\lim_{\Delta_2 \to 2}
\mathcal{O}^+_{\Delta_1}(z_1, \bar z_1)\,\mathcal{O}^+_{\Delta_2}(z_2, \bar z_2)
\;\sim\;
\sum_{k \ge 0} \frac{B_k(z_1, z_2)}{(z_1 - z_2)^{1-k}},
\end{equation}
with $B_k$ the subleading soft coefficients of
Cachazo--Strominger~\cite{CachazoStrominger14} and
Cachazo--He--Yuan \cite[and the celestial sub-subleading literature via]{CachazoStrominger14}, coincides with the classical
$\lambda$-bracket~\eqref{eq:celestial-winfty-lambda-brackets} of
$W^{(2)}$ with $W^{(2)}$ after the Mellin transform. The soft tower
$\{B_k\}_{k \ge 0}$ is the Laurent expansion of
$\{W^{(p)}_\lambda W^{(q)}\}_{\mathrm{cl}}$ at $p = q = 2$, with
$k$-th soft order tied to pole order $k+1$ by the dictionary of
Theorem~\ref{thm:gravity-infinite-soft-tower}(i). The
$k = 0$ (Weinberg) and $k = 1$ (Cachazo--Strominger) entries are the
binary OPE; entries $k \ge 2$ require the ternary $m_3$ operation and
thus probe the $\Ainf$-structure on $\wtc$ beyond leading Virasoro. The
Strominger tower is therefore equivalent to the $\Ainf$-tower of
Theorem~\ref{thm:gravity-infinite-soft-tower} under
Theorem~\ref{thm:celestial-winfty-classical-endpoint}(i).
\end{remark}

\begin{remark}[$\mathrm{CoHA}(\C^3)=Y^+$, not $\cW_{1+\infty}$]
\label{rem:cross-vol-coha-winfty}
For the toric $\C^3$ critical model,
$\mathrm{CoHA}(\C^3) = Y^+$ is the positive half of the affine Yangian
of $\mathfrak{gl}_1$, \emph{not} $\cW_{1+\infty}$ itself.
Schiffmann--Vasserot~\cite{SchiffmannVasserot13} identify the
Hall/shuffle positive half; Maulik--Okounkov stable envelopes and the
completed Yangian action supply the double/centre and Fock
representation. The typed chain is
\[
 \mathrm{CoHA}(\C^3)=Y^+(\widehat{\mathfrak{gl}}_1)
 \hookrightarrow D_\hbar^\wedge(Y^+)
 \xrightarrow{\;\mathrm{Fock}_\lambda\;}
 \End(\cW_{1+\infty,\lambda}\text{-}\mathrm{vac}).
\]
Under Theorem~\ref{thm:celestial-winfty-classical-endpoint}(i), the
classical limit of $Y^+$ is the positive-mode Poisson subalgebra of
$\wtc$ generated by $\{w^p_m:m\ge0\}$. The negative modes, the Cartan
current, and the state-field correspondence enter only after the
double/centre and Fock evaluation. The ``six routes to
$G(K3 \times E)$'' are six distinct constructions; the twistor-gravity
route factors through $\wtc$, while the compact Hall--Borcherds routes
require the compact critical CoHA and double data isolated in
Proposition~\ref{prop:vol-ii-iii-coincidence}.
\end{remark}

\begin{remark}[Igusa square and scalar normalisations]
\label{rem:igusa-square-normalisations}
The $K3\times E$ Borcherds lane uses a square-root normalisation
which is not a $W_{1+\infty}$ or CoHA statement. The monic
Gritsenko--Nikulin denominator is
\[
 D_5=64^{-1}\Delta_5,
\]
where $\Delta_5$ is the weight-$5$ Igusa form with multiplier
$\nu_{\Delta_5}$. Its scalar square is
\[
 \Phi_{10}^{\mathrm{un}}=\Delta_5^2,
\]
a weight-$10$ scalar Siegel modular form in the DVV/DMVV
normalisation. In Oberdieck--Pandharipande normalisation the monic
scalar is
\[
 \Phi_{10}^{\mathrm{OP}}=D_5^2=4096^{-1}\Delta_5^2,
 \qquad
 Z_{\mathrm{OP/DT}}^{K3\times E}
 =-(\Phi_{10}^{\mathrm{OP}})^{-1}
 =-4096\,\Delta_5^{-2}.
\]
The normalisation is fixed by the exact coefficient computation
\texttt{igusa-cusp-form/compute/verify\_square\_root.py}: coefficients
are expanded after the leading monomial of $64^{-1}\Delta_5$, with
$[qrs]\,(64^{-1}\Delta_5)/(qrs)^{1/2}=93$ and
$29-93=-64$, the $q\,r$ coefficient of $\phi_{0,1}$.
Thus $D_5$, $\Delta_5$, $\Phi_{10}^{\mathrm{OP}}$, and
$\Phi_{10}^{\mathrm{un}}$ record respectively the monic denominator,
the character-valued square root, the OP scalar square, and the
unnormalised DVV/DMVV scalar square. None of these normalisations
constructs the compact Hall orientation, the Hall bracket, or the
Hall--Drinfeld double.
\end{remark}

\begin{remark}[Scope of the ``$1+$'' and pure self-dual gravity]
\label{rem:scope-of-one-plus}
For pure 4d self-dual Einstein gravity (no matter coupling), the
celestial chiral algebra is $w_\infty$ (spin-$2$ onwards), not the
``$1+$''-extended $w_{1+\infty}$: the Heisenberg current $H$ of
weight~$1$ requires a $U(1)$ soft-photon sector. Coupling self-dual
gravity to a $U(1)$ gauge field (self-dual Maxwell) introduces $H$ as
the soft-photon current \cite{DonnayFotopoulosPasterskiTaylor21};
coupling to a K3 sigma model introduces $24$ Heisenberg currents via
$H^2(K3, \Z) \cong \Z^{22}$ extended by the pair of instanton winding
numbers, whence the extension to $\mathfrak{w}_{1+\infty}^{\oplus 24}$
of the celestial--moonshine bridge
(Theorem~\ref{thm:celestial-moonshine-bridge}). The statement (i)
admits the same proof after restricting to $\cW_\infty[\lambda=0]$
in place of $\cW_{1+\infty}[\lambda=0]$; (ii) and (iii) are unchanged.
\end{remark}

\begin{remark}[Three independent comparisons]
\label{rem:celestial-winfty-iv-triangle}
Three disjoint verifications of
Theorem~\ref{thm:celestial-winfty-classical-endpoint}(i) agree on the
classical-limit identification:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The \emph{wedge-algebra route} (PRS + Bakas, this chapter
Theorem~\ref{thm:ggl-convergence-prs-bakas}): Moyal deformation of
$w_\infty$ recovers $\cW_\infty[\mu=1/2]$; triality-orbit extension
to $\lambda = 0$ gives $\cW_{1+\infty}[\lambda=0]$; $\hbar \to 0$
returns $\wtc$.
\item The \emph{twistor route} (Costello--Paquette--Sharma + Bittleston--Heuveline--Skinner):
twistor-space holomorphic Chern--Simons with gauge algebra
$\mathfrak{ham}(\C^2)$ has boundary chiral algebra
isomorphic to $\wtc$ by direct BV computation, and matches
$\cW_{1+\infty}[\lambda=0]$ at the quantum level by Bittleston--Heuveline--Skinner
anomaly cancellation.
\item The \emph{soft-theorem route} (Strominger+Himwich--Pate--Singh):
the commutator algebra of soft graviton modes $w^p_m$ at every
$(p,m)$ is computed from the $4$d scattering amplitudes and agrees
with~\eqref{eq:celestial-winfty-lambda-brackets} at the Poisson level.
\end{enumerate}
The three routes use disjoint mathematical ingredients (symplectic
geometry of $\mathrm{SU}(\infty)$, BV-cohomology on twistor space,
Mellin-transformed 4d amplitudes) and agree on the classical-limit
identification.
\end{remark}

\subsection{Endpoint scope}
\label{subsec:headline-inscription}

At generic $\lambda \in \Lambda_{\mathrm{gen}}$, the
$\cW_\infty$ endpoint is the exact inverse-limit theorem obtained
from Prochazka triangular truncation, Creutzig--Kanade--Linshaw
parafermion compatibility, Pope--Romans--Shen wedge algebra with Bakas
quantisation, weight-window strong convergence, and vanishing of the
\(\lim^1\) obstruction classes \(\delta_{w,r}\). At rational-$\lambda$ truncation points
$\Lambda_{\mathrm{trunc}}$, the ladder stabilises at finite depth $N
= N(c, \lambda)$ with terminal rung
$\mathrm{E}_{N+1}^{\mathrm{top}}$. The finite-window executable checks
verify the threshold arithmetic \(N_0(w)=2w-1\) and keep the generic
endpoint hypotheses separated from the finite-rung theorem.

Theorem~\ref{thm:w-infty-e-infty-topologization-endpoint} is the
topological-gravity endpoint of Part~\ref{part:gravity}: 3d quantum
gravity with Virasoro boundary is the \(N=2\) shadow of a
3d$+\infty$-topological theory on the
$\cW_\infty[\lambda]$ boundary.

% =====================================
% Bibliographic notes: expected new .bib entries
% Linshaw-Winfty-universal - Linshaw, arXiv:1710.02275
% ProchazkaRapcak18 - Prochazka-Rapcak, arXiv:1711.06888
% GaberdielGopakumar2011-Winfty - Gaberdiel-Gopakumar, arXiv:1207.6697
% GaberdielGopakumarLiPeng-Winfty - Gaberdiel-Gopakumar-Li-Peng, arXiv:1501.07236
% Prochazka-Winfty-lambda - Prochazka, arXiv:1711.06888 (lambda parametrisation)
% CKL-parafermion - Creutzig-Kanade-Linshaw, arXiv:1802.09836
% PopeRomansShen-winfty-wedge - Pope-Romans-Shen, Phys.Lett. B236 (1990) 173
% Bakas-Winfty - Bakas, Phys.Lett. B228 (1989) 57
% BergshoeffPopeShen-Winfty-quantum - Bergshoeff-Pope-Shen, Phys.Lett. B229 (1989) 223
% BergshoeffPopeShen-Winfty-deformations - Bergshoeff-Pope-Shen, Nucl.Phys. B363 (1991) 163
% costello-gaiotto-6d-hCS - Costello-Gaiotto, arXiv:1509.05099 (6d hCS)
% =====================================
