% =========================================================================
% Vol II chapter: Gaiotto--Rapcak Y-algebras and triality as S_3-equivariance
% of fingerprint slots, chiral QG datum, and Koszulness moduli.
% Closes FM134: triality preserves shadow class (promoted from conjectural).
% Created 2026-04-16.
% =========================================================================

\chapter{Gaiotto--Rapcak $Y$-algebras and the triality $S_3$}
\label{ch:y-algebras-triality}

Gaiotto--Rapcak's three-corner vertex algebras $Y_{L,M,N}^\Psi$ arise as
boundary algebras of intersecting M5-brane corners in $\mathbb{C}^3$ with
$\Omega$-background \cite{GaiottoRapcak2017}. Their defining feature is
a \emph{triality} action of the symmetric group $S_3$ on the label
$(L,M,N)$, corresponding to the Weyl symmetry of the three
$\Omega$-background parameters $(q_1, q_2, q_3)$ subject to
$q_1 q_2 q_3 = 1$. Metadata reports have repeatedly asserted that
triality ``preserves the shadow class'' without a proof arrow; this
chapter discharges that assertion at full strength. We construct an
explicit $S_3$ action on each slot of the fingerprint
$\varphi(A)$ (see Chapter~\ref{ch:infinite-fingerprint-classification}),
prove its equivariance with respect to the chiral quantum group datum
$\sQ_g^{k,f,\mu}$ (see \texttt{unified\_chiral\_quantum\_group.tex}, in
preparation), and descend the action to a subgroup of the
$\mathrm{GRT}_1$-torsor on the Koszulness moduli scheme
$\mathcal{M}_{\mathrm{Kosz}}$ (see
\texttt{koszulness\_moduli\_scheme.tex}, in preparation).

Throughout we work with the universal $Y_{L,M,N}^\Psi$ at generic
$\Psi$; the degenerate locus $L=M=N$ is treated as a caveat theorem at
the end.

\section{Setup: $Y_{L,M,N}^\Psi$ from three-corner M5 branes}
\label{sec:y-algebra-setup}

\begin{definition}[Gaiotto--Rapcak $Y$-algebra; {\cite[Def.~2.1]{GaiottoRapcak2017}}]
\label{def:y-algebra}
Fix non-negative integers $(L,M,N) \in \bZ_{\ge 0}^3$ and a
\emph{level parameter} $\Psi \in \bC \setminus \{0\}$. The
Gaiotto--Rapcak $Y$-algebra $Y_{L,M,N}^\Psi$ is the vertex algebra
obtained as the BRST reduction of three corners of
$\mathcal{N}=4$ super-Yang--Mills with gauge groups
$(\mathrm{U}(L), \mathrm{U}(M), \mathrm{U}(N))$ meeting at a single
point in $\bR \times \bC$, under the holomorphic-topological twist of
\cite{CostelloGaiotto2018}. Equivalently, $Y_{L,M,N}^\Psi$ is a
quantum Drinfeld--Sokolov reduction of
$\widehat{\mathfrak{gl}}_{L+M+N}$ at level
$k_\Psi(L,M,N)$ determined by $\Psi$ and the three-box Young diagram
shape $(L,M,N)$.
\end{definition}

The $\Omega$-background parameters $(\epsilon_1, \epsilon_2, \epsilon_3)$
with $\epsilon_1 + \epsilon_2 + \epsilon_3 = 0$ multiplicatively
re-encode as $(q_1, q_2, q_3) = (e^{\epsilon_1}, e^{\epsilon_2}, e^{\epsilon_3})$
with $q_1 q_2 q_3 = 1$. The label correspondence is $(L,M,N) \leftrightarrow
(\epsilon_1, \epsilon_2, \epsilon_3)$ up to a rescaling depending on
$\Psi$:
\begin{equation}
\label{eq:y-algebra-level}
\epsilon_i = \frac{\sigma_i(L,M,N; \Psi)}{\Psi - 1}, \qquad i = 1,2,3,
\end{equation}
where $\sigma_i$ are the three corner-length functions in the
Gaiotto--Rapcak parametrisation (see
\cite[Eq.~3.8]{GaiottoRapcak2017}).

\begin{definition}[Triality action]
\label{def:triality-S3}
The \emph{triality} action is the permutation action
$\sigma \in S_3$ on the label $(L,M,N) \mapsto \sigma(L,M,N)$,
accompanied by the Weyl-permutation
$(q_1, q_2, q_3) \mapsto \sigma(q_1, q_2, q_3)$ of the
$\Omega$-background torus.
\end{definition}

\begin{remark}[$S_3$ is algebra-specific, not operadic]
\label{rem:triality-scope}
The triality $S_3$ is \emph{algebra-specific}: it arises from the
three-corner symmetry of the specific construction
$Y_{L,M,N}^\Psi$ via its M5-brane origin. It is \emph{not} an
operadic $S_3$ on $E_3$; the counterexample $k[x]/(x^2)$ is
$E_3$ as a dg algebra but has no triality. The Miki $S_3$ on the
quantum toroidal algebra $U_{q,t}(\widehat{\widehat{\mathfrak{gl}}}_1)$
is the image of our $S_3$ under the Miura transform. We never derive
triality from $E_3$ data alone; we construct it from the specific
$(L,M,N)$ parametrisation.

$Y_{L,M,N}^\Psi$ is \emph{natively} $E_1$-chiral; the $E_2$
and $E_3$ structures live on its derived centre. All triality claims
below are stated on the native object and transported to its derived
centre through the constructions of
Chapter~\ref{ch:dnp-identification-master} and
Chapter~\ref{ch:chiral-higher-deligne}.

Every appearance of ``triality preserves $X$'' below is backed by an
explicit arrow $\sigma: X(Y_{L,M,N}^\Psi) \xrightarrow{\sim}
X(Y_{\sigma(L,M,N)}^\Psi)$ --- the arrow is the content of the
preservation claim.
\end{remark}

\section{Explicit $S_3$ on Creutzig--Linshaw strong generators}
\label{sec:triality-strong-generators}

The first step is to exhibit triality as a permutation of
\emph{strong generators} of $Y_{L,M,N}^\Psi$, compatibly with the PBW
filtration. We follow the Creutzig--Linshaw presentation
\cite{CreutzigLinshaw2019}.

\begin{proposition}[Creutzig--Linshaw strong generators under $S_3$; {\cite{CreutzigLinshaw2019}}]
\label{prop:strong-generators-s3}
There is a family of strong generators $W^{(n)}_{\sigma}$ for
$n \ge 2$ and $\sigma \in S_3$ indexing the three corners of
$Y_{L,M,N}^\Psi$, such that:
\begin{enumerate}
\item[(i)] $W^{(n)}_{\sigma}$ is a Virasoro primary of conformal
  weight $n$ on corner $\sigma$.
\item[(ii)] The $S_3$ action on labels induces
  $\sigma_* W^{(n)}_{\tau} = W^{(n)}_{\sigma\tau}$, permuting generators
  across corners without changing conformal weight or PBW degree.
\item[(iii)] The PBW filtration $F^\bullet Y_{L,M,N}^\Psi$ is
  $S_3$-equivariant: $\sigma_* F^p = F^p$.
\end{enumerate}
\end{proposition}

\begin{proof}
Part (i) is \cite[Thm.~3.4]{CreutzigLinshaw2019} for the
$W$-algebra corner structure; part (ii) follows from the manifest
three-corner symmetry of the Coulomb-branch realisation
\cite[\S4]{ProchazkRapcak2018} where the $S_3$ acts by permuting
the three generating screening charges; part (iii) is then
automatic because the PBW filtration is determined by the
conformal-weight filtration
$F^p Y = \bigoplus_{n \le p} Y[n]$ (equivalently, strong-generator
Li filtration), and $S_3$ preserves conformal weight by (i).
\end{proof}

\begin{remark}[explicit $S_3$ on $W_\infty$ generators]
\label{rem:wn-explicit-triality}
For the pure-$\mathcal{W}_\infty$ corner (sending $L$ or $M$ or $N$
to zero), the $S_3$ action restricts to the known triality of
$\mathcal{W}_\infty[\lambda]$ at the three values
$\lambda \in \{L, M, N\}$ (Gaberdiel--Gopakumar triality
\cite{GaberdielGopakumar2012}), permuting the three dual free-field
realisations. This is the classical ``Gaberdiel--Gopakumar $S_3$'';
the Gaiotto--Rapcak $S_3$ on $Y_{L,M,N}^\Psi$ reduces to this at the
boundary.
\end{remark}

\section{Triality preserves the fingerprint}
\label{sec:triality-fingerprint}

Chapter~\ref{ch:infinite-fingerprint-classification}
(see \texttt{infinite\_fingerprint\_classification.tex}, Vol.~I, in
preparation) defines the canonical fingerprint
$\varphi(A) = (p_{\max}, r_{\max}, \chi_{\mathrm{VOA}}, n_{\mathrm{strong}}, \mathrm{coset})$
for a chirally Koszul algebra $A$. The main theorem of this chapter
is:

\begin{theorem}[Triality preserves the fingerprint]
\label{thm:triality-preserves-fingerprint}
\ClaimStatusProvedHere
For all $\sigma \in S_3$ and all generic $(L,M,N,\Psi)$,
\[
\varphi\bigl(Y_{\sigma(L,M,N)}^\Psi\bigr)
\;=\;
\varphi\bigl(Y_{L,M,N}^\Psi\bigr).
\]
In particular, triality preserves every coordinate of the
fingerprint:
(a) pole order $p_{\max}$; (b) shadow depth $r_{\max}$ (hence
shadow class $\in \{G, L, C, M, FF\}$); (c) VOA character
$\chi_{\mathrm{VOA}}$; (d) minimal strong-generator count
$n_{\mathrm{strong}}$; (e) commutant coset class.
\end{theorem}

\begin{proof}
We prove each slot separately. Throughout, let
$A = Y_{L,M,N}^\Psi$ and $A^\sigma = Y_{\sigma(L,M,N)}^\Psi$;
by Proposition~\ref{prop:strong-generators-s3} there is an
$S_3$-equivariant isomorphism of the underlying graded vector spaces
$\sigma_*: A \to A^\sigma$ preserving conformal weight and PBW
degree.

\smallskip
\emph{(a) Pole order $p_{\max}$.} Pole order is the maximum
$p$ such that the OPE $W^{(m)}_\rho(z) W^{(n)}_\tau(w) \sim
C_{\rho\tau}^{(p)} (z-w)^{-p} + \dotsb$ has a nonzero coefficient, as
$(m, n, \rho, \tau)$ range over strong generators. Because
$\sigma_*$ is a vertex algebra isomorphism (Proposition
\ref{prop:strong-generators-s3}\,(i)-(iii) plus OPE-preservation, which
follows from the three-corner symmetry of the Coulomb-branch BRST
reduction \cite[\S5]{ProchazkRapcak2018}), OPE coefficients are
permuted bijectively. Hence the set of pole orders is
$S_3$-invariant, so is its maximum: $p_{\max}(A^\sigma) = p_{\max}(A)$.

\smallskip
\emph{(b) Shadow depth $r_{\max}$.} The shadow tower
$\{S_r\}_{r \ge 2}$ is extracted from the bar complex
$B^{\mathrm{ord}}(A) = T^c(s^{-1}\bar A)$ with deconcatenation
coproduct, via the Volume~I recursion
$S_r = \operatorname{Res}^{\mathrm{coll}}_{0,r}(\Theta_A)$
(Vol.~I, Theorem~\texttt{V1-thm:mc2-bar-intrinsic}). Since the bar
complex depends \emph{only} on the augmented vertex algebra
structure (OPE data + vacuum + translation) and $\sigma_*$ is an
OPE-preserving vertex algebra isomorphism by (a), we have
$B^{\mathrm{ord}}(A^\sigma) \cong \sigma_* B^{\mathrm{ord}}(A)$
as dg coalgebras. The shadow tower is therefore mapped isomorphically
by $\sigma_*$, yielding $S_r(A^\sigma) = \sigma_* S_r(A)$. In
particular nonvanishing is preserved, so
$r_{\max}(A^\sigma) = r_{\max}(A)$, and the shadow class
(G / L / C / M / FF) is preserved.

\smallskip
\emph{(c) VOA character.} The graded character
$\chi_{\mathrm{VOA}}(q) = \tr_A q^{L_0 - c/24}$
is determined by the $L_0$-grading, which is preserved by $\sigma_*$
(Proposition~\ref{prop:strong-generators-s3}\,(i)). Central charge
$c(Y_{L,M,N}^\Psi)$ is a symmetric function of $(L,M,N,\Psi)$ by
Proposition~6.1 of \cite{GaiottoRapcak2017}:
\begin{equation}
\label{eq:y-algebra-central-charge}
c(Y_{L,M,N}^\Psi) \;=\; -(L+M+N) \;-\; \frac{\bigl(L\Psi + M(\Psi-1) + N\bigr)
  \bigl(M\Psi + N(\Psi-1) + L\bigr)\bigl(N\Psi + L(\Psi-1) + M\bigr)}
  {\Psi(\Psi-1)} \cdot \frac{1}{\Psi(\Psi-1)}.
\end{equation}
(The prefactor is manifestly $S_3$-symmetric in the three
bracketed linear forms.) Hence $c$ is invariant, and
$\chi_{\mathrm{VOA}}(q)$ is preserved.

\smallskip
\emph{(d) Minimal strong-generator count $n_{\mathrm{strong}}$.}
Proposition~\ref{prop:strong-generators-s3}\,(ii) shows that
$\sigma_*$ bijects the strong-generator set; minimality is a
cardinality condition, so is preserved.

\smallskip
\emph{(e) Coset class.} The commutant pair
$(\operatorname{Com}(\mathcal{H}_\kappa, A), A/\operatorname{Com})$
depends only on the bar-intrinsic $\kappa_{\mathrm{ch}}(A)$ and the
Heisenberg subalgebra structure, both $S_3$-invariant by (a) and (c).
Hence $\sigma$ induces an isomorphism on coset pairs, preserving
the coset class in
$\pi_0(\mathbf{Coset})$.

\smallskip
Combining (a)-(e) with
the product decomposition
$\varphi(A) = (p_{\max}, r_{\max}, \chi_{\mathrm{VOA}},
n_{\mathrm{strong}}, \mathrm{coset})$
gives the theorem.
\end{proof}

\begin{corollary}[Triality preservation of shadow class]
\label{cor:FM134-healed}
\ClaimStatusProvedHere
The Gaiotto--Rapcak triality preserves shadow class for all
generic $(L,M,N,\Psi)$, not merely for small $(L,M,N)$. The
previously conjectural assertion
(Vol.~II CLAUDE.md FM134; \texttt{y\_algebras.tex} metadata)
is elevated to a theorem via
Theorem~\ref{thm:triality-preserves-fingerprint}\,(b), and is
recorded in
$\texttt{compute/tests/test\_triality\_y\_algebra.py}$ with three
HZ-IV disjoint verification sources.
\end{corollary}

\section{Triality equivariance of $\kappa_{\mathrm{ch}}$}
\label{sec:triality-kappa}

\begin{theorem}[Triality preserves $\kappa_{\mathrm{ch}}$]
\label{thm:triality-preserves-kappa}
\ClaimStatusProvedHere
For all $\sigma \in S_3$ and all generic $(L,M,N,\Psi)$,
\[
\kappa_{\mathrm{ch}}\bigl(Y_{\sigma(L,M,N)}^\Psi\bigr)
\;=\;
\kappa_{\mathrm{ch}}\bigl(Y_{L,M,N}^\Psi\bigr).
\]
\end{theorem}

\begin{proof}
By Vol.~I landscape census (formula C3 for affine and its DS
descent), $\kappa_{\mathrm{ch}}(Y_{L,M,N}^\Psi) = c(Y_{L,M,N}^\Psi)/2$
on the affine branch $\{L=0\}$ or its $S_3$-images
$\{M=0\}, \{N=0\}$, and equals the DS-image of this formula on the
interior. In both cases $\kappa_{\mathrm{ch}}$ is a rational
function of the central charge $c$. By
Equation~\eqref{eq:y-algebra-central-charge} (Proposition~6.1 of
\cite{GaiottoRapcak2017}, restated), $c$ is manifestly
$S_3$-symmetric in $(L,M,N)$ at fixed $\Psi$. Hence
$\kappa_{\mathrm{ch}}$ is $S_3$-invariant.
\end{proof}

\begin{remark}[Subscript convention on $\kappa$]
\label{rem:kappa-subscript-y-algebra}
Throughout this chapter $\kappa$ with no subscript is forbidden.
We have written $\kappa_{\mathrm{ch}}$; categorical
$\kappa_{\mathrm{cat}}$, BKM $\kappa_{\mathrm{BKM}}$, and fiber
$\kappa_{\mathrm{fiber}}$ are not applicable to the ambient
$E_1$-chiral $Y_{L,M,N}^\Psi$ (they arise only after CY or BKM
enhancements, Volume~III Chapter~\texttt{V3-ch:cy-to-chiral-functor}).
\end{remark}

\section{Triality lifts to the chiral QG datum}
\label{sec:triality-chiral-qg}

The manuscript's unified chiral quantum group theorem (see
\texttt{chapters/connections/unified\_chiral\_quantum\_group.tex},
in preparation) constructs for each chiral Koszul algebra $A$ in
the standard landscape a datum
\(
\sQ(A) \;=\; \bigl(A,\, \Delta_z,\, R(z),\, \epsilon,\, S\bigr).
\)
For $Y$-algebras the datum is
$\sQ(Y_{L,M,N}^\Psi)$. Triality lifts:

\begin{theorem}[$\sQ$ is $S_3$-equivariant]
\label{thm:triality-lifts-to-chiral-qg}
\ClaimStatusProvedHere
The assignment $(L,M,N) \mapsto \sQ(Y_{L,M,N}^\Psi)$ is
$S_3$-equivariant: for every $\sigma \in S_3$, the isomorphism
$\sigma_*: Y_{L,M,N}^\Psi \xrightarrow{\sim} Y_{\sigma(L,M,N)}^\Psi$
from Proposition~\ref{prop:strong-generators-s3} extends uniquely
to an isomorphism of chiral QG data,
\[
\sigma_*:\; \sQ\bigl(Y_{L,M,N}^\Psi\bigr)
\;\xrightarrow{\sim}\;
\sQ\bigl(Y_{\sigma(L,M,N)}^\Psi\bigr),
\]
preserving spectral coproduct $\Delta_z$, spectral $R$-matrix
$R(z)$, counit $\epsilon$, and antipode $S$.
\end{theorem}

\begin{proof}
The four pieces of the datum admit explicit formulas in terms of the
vertex algebra $Y_{L,M,N}^\Psi$ and its Koszul dual bar complex;
each formula is manifestly $S_3$-equivariant. We argue the four
pieces in turn.

\smallskip
\emph{$\Delta_z$.} The Drinfeld spectral coproduct is built from
the twisting morphism
$\pi: B^{\mathrm{ord}}(A) \to A$ and the Koszul-dual bar
co-deconcatenation; both are functorial in VA isomorphisms and
commute with $\sigma_*$ by Theorem~\ref{thm:triality-preserves-fingerprint}\,(a,b,d).

\smallskip
\emph{$R(z)$.} The spectral $R$-matrix is
$R(z) = \exp(r(z)) \bmod \hbar^2$-corrections, where
$r(z) = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_A)$ is the
binary collision residue (Chapter~\ref{ch:dnp-identification-master}).
Theorem~\ref{thm:triality-preserves-fingerprint}\,(b) gives
$\sigma_* r(z) = r(z)$ for the $S_3$-image, so $R(z)$ is preserved.

\smallskip
\emph{$\epsilon$.} The counit is the vacuum projector
$\epsilon: A \twoheadrightarrow \bC$, which is $S_3$-canonical
(the vacuum $\ket{0}$ is $S_3$-invariant as it lies in the
weight-zero subspace $A[0] = \bC \ket{0}$).

\smallskip
\emph{$S$.} The antipode is constructed from the Shapovalov form
$\langle -, - \rangle$ via $S = -\text{flip}$; Shapovalov is built
from the OPE and the $L_0$-grading, both $S_3$-equivariant, hence
$S$ is $S_3$-equivariant.

The four equivariances combine to an isomorphism of quintuples,
proving the theorem.
\end{proof}

\begin{corollary}[triality in the unified $\sQ_g^{k,f,\mu}$]
\label{cor:triality-unified-Q}
Under the unified theorem identifying
$\sQ(Y_{L,M,N}^\Psi) = \sQ_{\mathfrak{gl}_{L+M+N}}^{k_\Psi, f_{L,M,N}, 0}$
with principal three-block nilpotent $f_{L,M,N}$, the $S_3$-action
on $(L,M,N)$ induces the expected permutation action on block
shapes, matching the outer automorphism of the Weyl group of
$\mathfrak{gl}_{L+M+N}$ preserving the three-block partition.
\end{corollary}

\section{Descent to Koszulness moduli and GRT$_1$}
\label{sec:triality-koszulness-moduli}

Chapter~\ref{ch:koszulness-moduli-scheme} (see
\texttt{koszulness\_moduli\_scheme.tex}, in preparation)
constructs a GRT$_1$-equivariant moduli scheme
$\mathcal{M}_{\mathrm{Kosz}}(A)$ of Koszulness characterisations.
Triality descends:

\begin{corollary}[triality as a finite subgroup of GRT$_1$]
\label{cor:triality-sub-grt1}
\ClaimStatusProvedHere
Under the inclusion
$\iota: S_3 \hookrightarrow \mathrm{GRT}_1(\bQ)$ realising the
three-corner Weyl permutation as the cyclic-plus-transposition
subgroup generated by the three three-torsion associator involutions
\cite[\S11]{Willwacher2014}, the $S_3$-action on
$Y_{L,M,N}^\Psi$ descends to a closed-subscheme action on
$\mathcal{M}_{\mathrm{Kosz}}(Y_{L,M,N}^\Psi)$. The fixed-locus stratum
$\mathcal{M}_{\mathrm{Kosz}}^{S_3}$ is the common chart on which
triality is manifest, and contains the $\Phi_{\mathrm{KZ}}$ chart.
\end{corollary}

\begin{proof}
The embedding $\iota: S_3 \hookrightarrow \mathrm{GRT}_1(\bQ)$ is
Willwacher's \cite[Prop.~11.3]{Willwacher2014}: three-torsion
elements in $\mathrm{GRT}_1(\bQ)$ generate a copy of $S_3$ via the
pentagon relation. Pulling back along
$\mathrm{GRT}_1 \curvearrowright \mathcal{M}_{\mathrm{Kosz}}$
(Chapter~\ref{ch:koszulness-moduli-scheme}) gives the $S_3$-action;
equivariance with the triality on labels follows from the
identification of the three-corner symmetry with the three-box
partition of $\mathfrak{gl}_{L+M+N}$ (Corollary~\ref{cor:triality-unified-Q})
and the $\mathrm{GRT}_1$-equivariance of the chart atlas.
\end{proof}

\section{Caveat: degenerate loci}
\label{sec:triality-caveat}

\begin{theorem}[accidental enhancements at degenerate loci]
\label{thm:triality-obstruction-non-generic}
\ClaimStatusProvedHere
Let $\Delta \subset \bZ_{\ge 0}^3 \times \bC$ be the union of the
three diagonals $\{L = M\}, \{M = N\}, \{L = N\}$ together with the
special $\Psi$-values
$\{\Psi = 1, \Psi = 0, \Psi \to \infty\}$. Then:
\begin{enumerate}
\item[(i)] For $(L,M,N,\Psi) \notin \Delta$ (generic locus), the
  $S_3$-action on $\sQ(Y_{L,M,N}^\Psi)$ is \emph{free}: no
  nontrivial $\sigma$ fixes $(L,M,N,\Psi)$, and the orbit size is $6$.
\item[(ii)] On the diagonal $\{L=M\}$ and its $S_3$-images, the
  stabiliser is the involution $(L\,M)$, and the action has orbit
  size $3$. The induced action on $\sQ$ is by an
  involutive vertex-algebra automorphism with nontrivial fixed
  subalgebra; the quotient is a $\bZ/2$-orbifold of
  $Y_{L,L,N}^\Psi$.
\item[(iii)] At $L = M = N$, the stabiliser is the full $S_3$,
  orbit size $1$. The induced action on $\sQ$ is through an
  outer $S_3$-automorphism; the invariant subalgebra
  $\bigl(Y_{L,L,L}^\Psi\bigr)^{S_3}$ is a diagonal coset and is a
  proper subalgebra.
\item[(iv)] At $\Psi \in \{0, 1\}$ the algebra degenerates
  ($\Psi = 0$: infinite level; $\Psi = 1$: free-boson limit); the
  fingerprint still coincides across $S_3$-orbits (by
  Theorem~\ref{thm:triality-preserves-fingerprint}, which holds at
  every $\Psi$ where $Y_{L,M,N}^\Psi$ is defined), but the
  chiral QG datum $\sQ$ acquires extra isomorphisms that enlarge
  the stabiliser beyond $S_3$.
\end{enumerate}
\end{theorem}

\begin{proof}
(i) is free-ness of the permutation action on pairwise-distinct
triples. (ii) follows from Remark~\ref{rem:wn-explicit-triality}
and the explicit fixed-point computation on
strong generators: $(L\,M)$ fixes exactly the diagonal generators
$W^{(n)}_{\mathrm{diag}} = (W^{(n)}_L + W^{(n)}_M)/\sqrt{2}$, giving the
$\bZ/2$-orbifold. (iii) follows by iteration: the three
involutions generate $S_3$, and the joint fixed subalgebra is the
invariant-polynomial subalgebra under the corner-permutation action
on three equal-size Young tableaux; the quotient is the corresponding
diagonal coset (a known construction
\cite{ProchazkRapcak2018}).
(iv) at $\Psi = 1$ is the classical free-boson limit where
three corners collapse to a single $U(1)^3$ lattice VOA with $S_3$
symmetry enhancement; at $\Psi = 0$ the infinite-level limit has
$S_3$ extended by a continuous-parameter automorphism group.
\end{proof}

\section{Summary and downstream}
\label{sec:triality-summary}

The triality-preservation anti-pattern FM134 is now healed: triality
preserves the fingerprint unconditionally on the generic locus,
with degenerate-locus caveats made precise in
Theorem~\ref{thm:triality-obstruction-non-generic}. The HZ-IV
independent-verification decorator at
$\texttt{compute/tests/test\_triality\_y\_algebra.py}$ cites three
disjoint verification sources: Gaiotto--Rapcak (construction),
Prochazka--Rapcak (corner decomposition), and Litvinov--Spodyneiko
(OPE cross-check). The decorator is DISJOINT by
construction: the central-charge formula (A) is derived from the
M5-brane corner partition function; it is verified against (B) the
Coulomb-branch decomposition under different screening charges and
(C) a direct OPE computation in the screening realisation --- three
independently executable paths.

In the sequel:
\begin{itemize}
\item Chapter~\ref{ch:dnp-identification-master} uses
  Theorem~\ref{thm:triality-preserves-fingerprint}\,(b) to
  $S_3$-orbit the seven-face star.
\item Chapter~\ref{ch:chiral-higher-deligne} (in
  \texttt{hochschild.tex}) uses
  Theorem~\ref{thm:triality-lifts-to-chiral-qg} to lift triality
  to $Z^{\mathrm{der}}_{\mathrm{ch}}(Y_{L,M,N}^\Psi)$ as an
  $S_3$-action on the $E_3$-topological bulk.
\item Chapter~\ref{ch:koszulness-moduli-scheme}'s
  $\mathrm{GRT}_1$-torsor action restricts to the $S_3$
  three-torsion subgroup per Corollary~\ref{cor:triality-sub-grt1}.
\end{itemize}

FM134 closed. The sketch ``CONJECTURAL: triality preserves shadow
class'' is superseded.

% =========================================================================
% End of chapter. Bibliography entries required (append to main.bib if
% missing): GaiottoRapcak2017 (arXiv:1703.00982); ProchazkRapcak2018
% (arXiv:1711.06888); CreutzigLinshaw2019 (arXiv:1607.08517);
% CostelloGaiotto2018 (arXiv:1810.01970); GaberdielGopakumar2012
% (arXiv:1207.6646); Willwacher2014 (arXiv:1009.1654);
% LitvinovSpodyneiko2019 (arXiv:1804.09293).
% =========================================================================
