\chapter{Yang--Mills boundary theory via bar--cobar duality}
\label{ch:ym-boundary-theory}

\index{Yang--Mills!boundary theory|textbf}
\index{Koszul duality!Yang--Mills boundaries}

A holomorphic-topological twist of four-dimensional Yang--Mills theory
produces, on each boundary condition $\cB$, a chiral algebra
$\cA_{\cB}$ (Paquette--Williams~\cite{PW22}). The bar-cobar engine of
Volume~I applies to $\cA_{\cB}$ without modification, yielding a chain of
algebraic reductions:
\[
\cA_{\cB}
\;\xrightarrow{\;\text{bar}\;}
\barBch(\cA_{\cB})
\;\xrightarrow{\;\mathbb{D}_{\Ran}\;}
(\cA_{\cB}^!)_\infty
\;\xrightarrow{\;\text{center}\;}
Z(\cA_{\cB}^!)
\;\xrightarrow{\;\text{screening}\;}
Z^{\mathrm{vis}}.
\]
Each arrow discards information in a controlled, functorial manner.
The first identifies the chiral bar complex with the open-string BRST
complex. The second applies Verdier duality on $\mathrm{Ran}(X)$ to
produce the homotopy Koszul dual. The third extracts the center, which
governs first-order boundary deformations via the tangent-to-center
principle. The fourth passes to the visible center by instanton
completion and central screening.

\begin{remark}[Scope of the chain]
\label{rem:ym-chain-scope}
The boundary BRST recovery, the tangent-to-center correspondence,
central formality, relative derived centers, and the screening Hodge
theorem are all proved here. The realization of the dual algebra as
the full physical defect algebra, and the existence of a natural
Hilbert-screening bridge for untwisted Yang--Mills, remain conditional.
The final screening-to-mass-gap step requires an untwisting bridge datum
and a domination estimate (Chapter~\ref{ch:ym-instanton-screening}).
\end{remark}

\begin{theorem}[Bridge theorem: boundary chiral algebra $\to$ visible center via bar-cobar; \ClaimStatusProvedHere]
\label{thm:ym-bar-bridge}
\index{Yang--Mills!bridge theorem|textbf}
Fix a smooth projective curve~$X$ and a Koszul-admissible twisted
Yang--Mills boundary datum $(X,\mathcal{T},\cB)$ with chiral
envelope $\cA_{\cB}$. The chain of reductions
\[
\cA_{\cB}
\;\xrightarrow{\;\text{BRST}\;}
\barBch(\cA_{\cB})
\;\xrightarrow{\;\mathbb{D}_{\Ran}\;}
(\cA_{\cB}^!)_\infty
\;\xrightarrow{\;\text{center}\;}
Z(\cA_{\cB}^!)
\;\xrightarrow{\;\text{screening}\;}
Z^{\mathrm{vis}}
\]
is internal to the algebraic engine. Each arrow is a projection of
the modular convolution dg Lie algebra
$\mathfrak{g}^{\mathrm{mod}}_{\cA_{\cB}}$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(BRST $=$ bar)}\quad
 The boundary BRST complex is quasi-isomorphic to the chiral bar
 complex:
 $C^{\frac{\infty}{2}+\bullet}(\cA_{\cB}) \simeq
 \barBch(\cA_{\cB})$
 \textup{(}Theorem~\textup{\ref{thm:twisted-ym-boundary-brst}}\textup{)}.
\item \textup{(Bar $\to$ Koszul dual)}\quad
 Verdier duality on the bar complex yields the bar complex of
 the Koszul dual:
 $\mathbb{D}_{\Ran}\,\barBch(\cA_{\cB}) \simeq
 \barBch(\cA_{\cB}^!)$
 \textup{(}Theorem~\textup{\ref{thm:verdier-bar-cobar}}\textup{)}.
\item \textup{(Koszul dual $\to$ center)}\quad
 First-order boundary deformations are controlled by the center
 of the Koszul dual: $T^1_X(\cB) \cong Z(\cA_{\cB}^!)^\vee
 \otimes \omega_X$
 \textup{(}Theorem~\textup{\ref{thm:twisted-ym-tangent-center}}\textup{)}.
\item \textup{(Screening)}\quad
 Instanton completion and central screening extract the visible
 center $Z^{\mathrm{vis}} \subseteq Z(\cA_{\cB}^!)$, killing all
 screened sectors
 \textup{(}Theorem~\textup{\ref{thm:central-localization-confinement}}\textup{)}.
\end{enumerate}
\end{theorem}

\begin{proof}
Each step is proved in the indicated theorem; we verify only that
each is a projection of $\mathfrak{g}^{\mathrm{mod}}_{\cA_{\cB}}$.
The BRST complex is the genus-$0$ truncation of the modular
convolution algebra. The bar complex is the full genus-graded
complex. The Koszul dual is obtained by Verdier duality, which is
the linear-algebraic projection of the convolution algebra to its
dual. The center is the degree-$0$ part of the derived Hochschild
complex, which is itself a projection of the convolution algebra
via the tangent-to-center map. The screening quotient is a further
degree-$0$ projection. Each step discards information in a
controlled, functorial manner.
\end{proof}

\begin{remark}[Conditional final gap step]
\label{rem:ym-bar-bridge-conditional-gap}
Appending the screening-Laplacian comparison to
Theorem~\ref{thm:ym-bar-bridge} yields the conditional
visible-center-to-mass-gap step of
Theorem~\ref{thm:conditional-mass-gap-transfer}. The present theorem
does not claim that final untwisting arrow unconditionally.
\end{remark}

\begin{theorem}[Grand synthesis principle; \ClaimStatusConditional]
\label{thm:grand-synthesis-principle}
Fix a smooth projective curve $X$ and a screened instanton-completed boundary simplex built from
Koszul-admissible twisted Yang--Mills boundary data.
Then:
\begin{enumerate}[label=(\roman*)]
\item every first-order boundary coupling is dual to a class in the instanton-completed derived center;
\item every genuine higher-body visible coupling is dual to a higher \v{C}ech class of visible centers;
\item every screened asymptotic defect sector is killed by central localization, and only the vacuum sector
survives whenever the visible center is scalar and all nontrivial simples are screened;
\item every Hilbert-screening bridge datum upgrades the visible-center collapse to a concrete spectral-gap criterion,
and a domination estimate for the untwisted Hamiltonian implies a positive mass gap.
\end{enumerate}
\end{theorem}

\begin{proof}
Item~(i) is the instanton-completed and screened tangent-to-center package
(Theorem~\ref{thm:screened-tangent-center}).
Item~(ii) is the screened higher-body \v{C}ech duality theorem
(Theorem~\ref{thm:screened-cech-duality}).
Item~(iii) is the central localization criterion for confinement
(Theorem~\ref{thm:central-localization-confinement}).
Item~(iv) is the screening Hodge theorem
(Theorem~\ref{thm:screening-hodge-theorem}) together with
the conditional mass-gap transfer theorem
(Theorem~\ref{thm:conditional-mass-gap-transfer}).
\end{proof}

\begin{remark}[Status stratification]
\label{rem:ym-boundary-status-stratification}
The synthesis has three strata.
\begin{enumerate}[label=(\alph*)]
\item \emph{Proved here:} boundary BRST recovery, tangent-to-center, central formality,
relative derived centers, higher-body \v{C}ech duality, instanton completion, screening quotients,
visible defect localization, screening Hodge theory, and bounded-error gap stability.
\item \emph{Conditional:} the realization of the dual algebra as the full physical defect algebra,
and the existence of a natural Hilbert-screening bridge for untwisted four-dimensional Yang--Mills.
\item \emph{Conjectural frontier:} a canonical instanton-completed bulk dual, a full untwisting equivalence,
and a proof that the untwisted Hamiltonian is dominated by the screening Laplacian with positive constant.
\end{enumerate}
\end{remark}


\section{Twisted Yang--Mills boundary package}
\label{sec:twisted-ym-boundary-package}

\begin{definition}[Koszul-admissible twisted Yang--Mills boundary datum]
\label{def:twisted-ym-boundary-datum}
Let $X$ be a smooth projective curve. A \emph{Koszul-admissible twisted Yang--Mills boundary datum}
on $X$ consists of:
\begin{enumerate}[label=(\roman*)]
\item a holomorphic-topological twist $\mathcal{T}$ of a $4$-dimensional supersymmetric
Yang--Mills theory whose boundary local operators form a VOA in the sense of
{\cite{PW22}};
\item a boundary condition $\cB$ with boundary VOA $V_{\cB}$ and chiral envelope $\cA_{\cB}$;
\item the assumption that $\cA_{\cB}$ lies on the Koszul locus of Volume~I and belongs to a class
for which Theorem~\ref{thm:twisted-ym-boundary-brst} applies, e.g.\ generic-level affine
Kac--Moody or principal $\mathcal{W}$-algebra boundary conditions.
\end{enumerate}
\end{definition}

\begin{notation}[Open sector, bulk shadow, and tangent space]
\label{not:twisted-ym-boundary-objects}
For a Koszul-admissible twisted Yang--Mills boundary datum $(X,\mathcal{T},\cB)$, set
\[
\mathsf{Open}_{\cB} := \barBch(\cA_{\cB}),
\qquad
\mathsf{Bulk}^{\vee}_{\cB} := \barBch(\cA_{\cB}^!),
\qquad
T^1_X(\cB) := HH^2_{\mathrm{chiral}}(\cA_{\cB}).
\]
We call $\mathsf{Open}_{\cB}$ the \emph{open boundary complex}, $\mathsf{Bulk}^{\vee}_{\cB}$ the
\emph{dual bulk shadow}, and $T^1_X(\cB)$ the \emph{first-order boundary deformation space}.
\end{notation}

\begin{theorem}[Boundary BRST recovery for twisted Yang--Mills data; \ClaimStatusProvedHere]
\label{thm:twisted-ym-boundary-brst}
Let $(X,\mathcal{T},\cB)$ be a Koszul-admissible twisted Yang--Mills boundary datum.
Then:
\begin{enumerate}[label=(\alph*)]
\item there is a quasi-isomorphism
\[
\mathsf{Open}_{\cB} = \barBch(\cA_{\cB}) \simeq C^{\frac{\infty}{2}+\bullet}(\cA_{\cB}),
\]
identifying the chiral bar complex with the open-string BRST complex of the boundary condition;
\item Verdier duality converts the open sector into a factorization \emph{algebra}:
\[
\mathbb{D}_{\Ran}\, \mathsf{Open}_{\cB} \simeq \mathsf{Bulk}^{\vee}_{\cB} \simeq (\cA_{\cB}^!)_\infty.
\]
The Verdier dual is a factorization algebra quasi-isomorphic to the homotopy Koszul dual $(\cA_{\cB}^!)_\infty$ (Theorem~A, Verdier intertwining).
\end{enumerate}
\end{theorem}

\begin{proof}
By the Paquette--Williams boundary VOA theorem~{\cite{PW22}}, the boundary condition $\cB$ carries a
VOA $V_{\cB}$ with chiral envelope $\cA_{\cB}$. Since $\cA_{\cB}$ is assumed to be
Koszul-admissible, the BRST-bar quasi-isomorphism (Theorem~\ref{thm:brst-bar-genus0}) applies and gives the quasi-isomorphism
$\barBch(\cA_{\cB}) \simeq C^{\frac{\infty}{2}+\bullet}(\cA_{\cB})$. The Verdier-dual statement is
Theorem~\ref{thm:verdier-bar-cobar} (Verdier intertwining $\mathbb{D}_{\Ran}\, \barBch(\cA) \simeq \cA^!_\infty$) specialized to $\cA_{\cB}$.
\end{proof}

\begin{theorem}[Tangent-to-center principle; \ClaimStatusProvedHere]
\label{thm:twisted-ym-tangent-center}
For every Koszul-admissible twisted Yang--Mills boundary datum on a smooth projective
curve $X$, there is a canonical isomorphism
\[
T^1_X(\cB)
= HH^2_{\mathrm{chiral}}(\cA_{\cB})
\xrightarrow{\ \sim\ }
Z(\cA_{\cB}^!)^{\vee} \otimes \omega_X.
\]
The full first-order boundary deformation theory is thus controlled by the center
of the Koszul dual algebra.
\end{theorem}

\begin{proof}
Apply Corollary~\ref{cor:def-obs-exchange-genus0} to the Koszul pair
$(\cA_{\cB}, \cA_{\cB}^!)$.
\end{proof}

\begin{corollary}[Center-vanishing rigidity criterion; \ClaimStatusProvedHere]
\label{cor:twisted-ym-center-rigidity}
If $Z(\cA_{\cB}^!) = 0$, then $HH^2_{\mathrm{chiral}}(\cA_{\cB}) = 0$.
The boundary condition $\cB$ is then infinitesimally rigid.
\end{corollary}

\begin{proof}
Immediate from Theorem~\ref{thm:twisted-ym-tangent-center}.
\end{proof}

\begin{corollary}[One-parameter criterion; \ClaimStatusProvedHere]
\label{cor:twisted-ym-one-parameter}
If $\dim Z(\cA_{\cB}^!) = 1$, then $\dim HH^2_{\mathrm{chiral}}(\cA_{\cB}) = 1$.
The boundary theory then has a unique first-order coupling up to scale.
\end{corollary}

\begin{proof}
Apply Theorem~\ref{thm:twisted-ym-tangent-center}.
\end{proof}

\begin{definition}[Boundary-changing morphism]
\label{def:twisted-ym-boundary-morphism}
A \emph{boundary-changing morphism}
$f \colon (X,\mathcal{T},\cB) \to (X,\mathcal{T},\cB')$
is a morphism of boundary conditions that induces a morphism of chiral envelopes
\[
f \colon \cA_{\cB} \longrightarrow \cA_{\cB'}.
\]
Let $\mathsf{KBdy}_{\mathrm{YM}}(X)$ denote the resulting category of Koszul-admissible
boundary data on~$X$.
\end{definition}

\begin{theorem}[The tangent functor factors through the dual center; \ClaimStatusProvedHere]
\label{thm:twisted-ym-tangent-factors-through-center}
The assignment
\[
T^1_X \colon \mathsf{KBdy}_{\mathrm{YM}}(X) \longrightarrow \Vect,
\qquad
\cB \longmapsto HH^2_{\mathrm{chiral}}(\cA_{\cB}),
\]
is naturally isomorphic to the functor
\[
\mathfrak{Z}^{\vee}_{X} \colon \mathsf{KBdy}_{\mathrm{YM}}(X) \longrightarrow \Vect,
\qquad
\cB \longmapsto Z(\cA_{\cB}^!)^{\vee} \otimes \omega_X.
\]
The first-order boundary deformation functor factors through the center of
the Koszul dual.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:twisted-ym-tangent-center} gives the objectwise identification.
For morphisms, the functoriality of the bar construction comes from
Theorem~\ref{thm:geometric-equals-operadic-bar},
and the construction of Theorem~\ref{V1-thm:main-koszul-hoch} (Vol~I Theorem~H, at generic level;
the critical level $k = -h^\vee$ is excluded because $\dim \ChirHoch^0$ can be infinite there,
see Vol~I Remark~\ref*{rem:critical-level-lie-vs-chirhoch}) is functorial, since each step (bar/cobar, derived $\mathrm{Hom}$, and Verdier duality) is natural. Restricting to
cohomological degree~$2$ produces the required natural transformation. Koszul-admissible
twisted Yang--Mills boundary data are taken at generic level throughout this subsection.
\end{proof}

\begin{corollary}[Interface invariance of tangent data; \ClaimStatusProvedHere]
\label{cor:twisted-ym-interface-invariance}
Let $f \colon \cA_{\cB} \to \cA_{\cB'}$ be a boundary-changing morphism.
If the induced map on dual centers
\[
Z(\cA_{\cB'}^!) \xrightarrow{\ \sim\ } Z(\cA_{\cB}^!)
\]
is an isomorphism, then the induced map on first-order deformation spaces
\[
HH^2_{\mathrm{chiral}}(\cA_{\cB}) \xrightarrow{\ \sim\ } HH^2_{\mathrm{chiral}}(\cA_{\cB'})
\]
is also an isomorphism.
\end{corollary}

\begin{proof}
Immediate from Theorem~\ref{thm:twisted-ym-tangent-factors-through-center}.
\end{proof}

\begin{corollary}[Comparison without full boundary equivalence; \ClaimStatusProvedHere]
\label{cor:twisted-ym-center-comparison}
If two Koszul-admissible twisted Yang--Mills boundary conditions $\cB_1$ and $\cB_2$ satisfy
\[
Z(\cA_{\cB_1}^!) \cong Z(\cA_{\cB_2}^!),
\]
then their first-order deformation spaces are canonically isomorphic:
\[
HH^2_{\mathrm{chiral}}(\cA_{\cB_1}) \cong HH^2_{\mathrm{chiral}}(\cA_{\cB_2}).
\]
First-order boundary moduli are thus a strictly coarser invariant than the full
boundary VOA.
\end{corollary}

\begin{proof}
Apply Theorem~\ref{thm:twisted-ym-tangent-center} to each boundary condition.
\end{proof}

\begin{remark}[Mathematical content and physical content]
\label{rem:twisted-ym-math-vs-physics}
Theorems~\ref{thm:twisted-ym-boundary-brst}--\ref{thm:twisted-ym-tangent-factors-through-center}
and Corollaries~\ref{cor:twisted-ym-center-rigidity}--\ref{cor:twisted-ym-center-comparison}
are internal to the present manuscript once the boundary algebra lies on
the Koszul-admissible locus. The only physical input is the production of such a
boundary algebra from a holomorphic-topological Yang--Mills theory.
\end{remark}


\section{Central formality and mixed-coupling theorems}
\label{sec:twisted-ym-central-formality}

\begin{definition}[Boundary deformation dg Lie algebra]
\label{def:twisted-ym-def-dglie}
Let $(X,\mathcal{T},\cB)$ be a Koszul-admissible twisted Yang--Mills boundary datum, with chiral envelope $\cA_{\cB}$. Define the \emph{boundary deformation dg Lie algebra}
\[
\mathfrak{g}^{\mathrm{def}}_{\cB}
:=
\tau_{\ge 1} RHH_{\mathrm{ch}}(\cA_{\cB})[1],
\]
where $RHH_{\mathrm{ch}}(\cA_{\cB})$ carries the shifted dg~Lie structure of the chiral Hochschild complex, a strict model of the deformation $L_\infty$-algebra (Remark~\ref{rem:conv-strict-vs-homotopy}). Its Maurer--Cartan functor governs formal boundary deformations of~$\cA_{\cB}$.
\end{definition}

\begin{theorem}[Dual unobstructedness criterion; \ClaimStatusProvedHere]
\label{thm:twisted-ym-dual-unobstructedness}
Let $(X,\mathcal{T},\cB)$ be a Koszul-admissible twisted Yang--Mills boundary datum on a smooth projective curve. If
\[
HH^{-1}_{\mathrm{chiral}}(\cA_{\cB}^{!}) = 0,
\]
then the primary obstruction space of $\cA_{\cB}$ vanishes:
\[
HH^{3}_{\mathrm{chiral}}(\cA_{\cB}) = 0.
\]
Every first-order deformation of $\cA_{\cB}$ is then unobstructed to second order.
\end{theorem}

\begin{proof}
By the deformation-obstruction dictionary, primary obstructions to extending a first-order deformation lie in $HH^{3}_{\mathrm{chiral}}(\cA_{\cB})$. Apply Theorem~\ref{V1-thm:main-koszul-hoch} (Vol~I Theorem~H, at generic level; the critical level $k = -h^\vee$ is excluded because $\dim \ChirHoch^0$ can be infinite there, see Vol~I Remark~\ref*{rem:critical-level-lie-vs-chirhoch}) with $n=3$ to obtain
\[
HH^{3}_{\mathrm{chiral}}(\cA_{\cB})
\cong
HH^{-1}_{\mathrm{chiral}}(\cA_{\cB}^{!})^{\vee}\otimes \omega_X.
\]
The assumed vanishing of $HH^{-1}_{\mathrm{chiral}}(\cA_{\cB}^{!})$ forces $HH^{3}_{\mathrm{chiral}}(\cA_{\cB})=0$. The dual unobstructedness criterion is asserted for Koszul-admissible boundary data at generic level; the critical-level locus is outside the scope of this argument.
\end{proof}

\begin{theorem}[Central formality theorem; \ClaimStatusProvedHere]
\label{thm:twisted-ym-central-formality}
Let $(X,\mathcal{T},\cB)$ be a Koszul-admissible twisted Yang--Mills boundary datum. Assume
\[
HH^{1}_{\mathrm{chiral}}(\cA_{\cB}) = 0
\qquad\text{and}\qquad
HH^{-1}_{\mathrm{chiral}}(\cA_{\cB}^{!}) = 0.
\]
Then the formal deformation problem of $\cA_{\cB}$ is equivalent to the formal affine space on the vector space
\[
T^1_X(\cB)
\cong
Z(\cA_{\cB}^{!})^{\vee}\otimes \omega_X.
\]
Equivalently, every first-order boundary deformation extends uniquely to all orders up to unique equivalence, and the completed local ring of the deformation space is
\[
\widehat{\mathrm{Sym}}\bigl(Z(\cA_{\cB}^{!})\otimes \omega_X^{-1}\bigr).
\]
\end{theorem}

\begin{proof}
By Definition~\ref{def:twisted-ym-def-dglie}, the formal boundary
deformations of $\cA_{\cB}$ are governed by Maurer--Cartan elements of
the dg Lie algebra $\mathfrak{g}^{\mathrm{def}}_{\cB}$. Its cohomology
satisfies
\[
H^0(\mathfrak{g}^{\mathrm{def}}_{\cB}) = HH^{1}_{\mathrm{chiral}}(\cA_{\cB}) = 0,
\qquad
H^1(\mathfrak{g}^{\mathrm{def}}_{\cB}) = HH^{2}_{\mathrm{chiral}}(\cA_{\cB}),
\]
and, by Theorem~\ref{thm:twisted-ym-dual-unobstructedness},
\[
H^2(\mathfrak{g}^{\mathrm{def}}_{\cB}) = HH^{3}_{\mathrm{chiral}}(\cA_{\cB}) = 0.
\]
Choose a minimal $L_\infty$ model on $H^\bullet(\mathfrak{g}^{\mathrm{def}}_{\cB})$, which exists by the homotopy transfer theorem and is unique up to $L_\infty$ isomorphism. Since the only nonzero cohomology relevant to the Maurer--Cartan problem is in degree~$1$, every higher bracket
\[
\ell_n \colon (H^1)^{\otimes n} \longrightarrow H^{2}
\]
has zero target, because $\ell_n$ has cohomological degree $2-n$. All $\ell_n$ vanish and the minimal model is abelian.

The Maurer--Cartan equation in an abelian dg Lie algebra is empty, and the gauge action is trivial because $H^0=0$. Therefore the formal moduli problem is the formal affine space on $H^1(\mathfrak{g}^{\mathrm{def}}_{\cB}) = HH^2_{\mathrm{chiral}}(\cA_{\cB})$. Finally, Theorem~\ref{thm:twisted-ym-tangent-center} identifies this tangent space with $Z(\cA_{\cB}^{!})^{\vee}\otimes\omega_X$, yielding the completed symmetric algebra stated above.
\end{proof}

\begin{remark}[Interpretation]
\label{rem:twisted-ym-central-formality-meaning}
When infinitesimal automorphisms and dual negative-degree Hochschild classes vanish, the formal boundary moduli problem linearizes. The Koszul dual center provides formal coordinates on the deformation space.
\end{remark}

\begin{definition}[Reduced dual center and reduced tangent space]
\label{def:twisted-ym-reduced-center}
Assume that the boundary algebra is augmented, so that the vacuum defines a distinguished scalar subspace $\mathbb{C}\mathbf{1} \subset Z(\cA_{\cB}^{!})$. Define the \emph{reduced dual center}
\[
\widetilde Z(\cA_{\cB}^{!}) := Z(\cA_{\cB}^{!})/\mathbb{C}\mathbf{1}
\]
and the \emph{reduced tangent space}
\[
\widetilde T^1_X(\cB) := \widetilde Z(\cA_{\cB}^{!})^{\vee}\otimes \omega_X.
\]
\end{definition}

\begin{lemma}[Center of a chiral tensor product; \ClaimStatusProvedHere]
\label{lem:twisted-ym-center-tensor}
Let $\cB_1,\cB_2$ be quadratic Koszul-admissible boundary data with chiral envelopes $\cA_1,\cA_2$, and assume that the chiral tensor product $\cA_1\otimes^{\mathrm{ch}}\cA_2$ has trivial mixed OPE\/ in the sense of Proposition~\ref{prop:koszul-dual-tensor-product}. Then
\[
Z\bigl(\cA_1\otimes^{\mathrm{ch}}\cA_2\bigr)
\cong
Z(\cA_1)\otimes Z(\cA_2).
\]
\end{lemma}

\begin{proof}
An element of $\cA_1\otimes^{\mathrm{ch}}\cA_2$ is central if and only if it has regular OPE with every generator of the form $a\otimes \mathbf{1}$ and $\mathbf{1}\otimes b$. Because the mixed OPE is trivial, regularity against all $a\otimes \mathbf{1}$ is equivalent to lying in $Z(\cA_1)\otimes \cA_2$, while regularity against all $\mathbf{1}\otimes b$ is equivalent to lying in $\cA_1\otimes Z(\cA_2)$. Hence
\[
Z(\cA_1\otimes^{\mathrm{ch}}\cA_2)
=
\bigl(Z(\cA_1)\otimes \cA_2\bigr)
\cap
\bigl(\cA_1\otimes Z(\cA_2)\bigr).
\]
Choose vector space splittings $\cA_i = Z(\cA_i)\oplus U_i$. Then
\[
Z(\cA_1)\otimes \cA_2
=
Z(\cA_1)\otimes Z(\cA_2)
\oplus
Z(\cA_1)\otimes U_2,
\]
while
\[
\cA_1\otimes Z(\cA_2)
=
Z(\cA_1)\otimes Z(\cA_2)
\oplus
U_1\otimes Z(\cA_2).
\]
Their intersection is exactly $Z(\cA_1)\otimes Z(\cA_2)$.
\end{proof}

\begin{theorem}[Binary mixed-coupling theorem; \ClaimStatusProvedHere]
\label{thm:twisted-ym-binary-mixed-couplings}
Let $\cB_1,\cB_2$ be quadratic Koszul-admissible twisted Yang--Mills boundary data on the same smooth projective curve $X$, with chiral envelopes $\cA_1,\cA_2$. Then the composite boundary datum with envelope
\[
\cA_{12}:=\cA_1\otimes^{\mathrm{ch}}\cA_2
\]
satisfies
\[
T^1_X(\cB_{12})
\cong
\bigl(Z(\cA_1^{!})\otimes Z(\cA_2^{!})\bigr)^{\vee}\otimes \omega_X.
\]
If the centers are finite-dimensional and split as
\[
Z(\cA_i^{!}) \cong \mathbb{C}\mathbf{1}\oplus \widetilde Z_i,
\]
then there is a canonical decomposition
\[
\widetilde T^1_X(\cB_{12})
\cong
\widetilde T^1_X(\cB_1)
\oplus
\widetilde T^1_X(\cB_2)
\oplus
(\widetilde Z_1\otimes \widetilde Z_2)^{\vee}\otimes \omega_X.
\]
The last summand is a mixed first-order coupling invisible in either factor separately.
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:twisted-ym-tangent-center},
\[
T^1_X(\cB_{12})
\cong
Z(\cA_{12}^{!})^{\vee}\otimes \omega_X.
\]
Since the boundary data are quadratic, Proposition~\ref{prop:koszul-dual-tensor-product} gives
\[
\cA_{12}^{!}
\cong
\cA_1^{!}\otimes^{\mathrm{ch}}\cA_2^{!}.
\]
Applying Lemma~\ref{lem:twisted-ym-center-tensor} to the dual side yields
\[
Z(\cA_{12}^{!})
\cong
Z(\cA_1^{!})\otimes Z(\cA_2^{!}),
\]
which proves the first statement.

For the decomposition, write each center as $\mathbb{C}\mathbf{1}\oplus \widetilde Z_i$. Then
\[
Z(\cA_1^{!})\otimes Z(\cA_2^{!})
\cong
\mathbb{C}\mathbf{1}
\oplus
\widetilde Z_1
\oplus
\widetilde Z_2
\oplus
(\widetilde Z_1\otimes \widetilde Z_2).
\]
Dualizing and tensoring with $\omega_X$ gives the asserted decomposition of reduced tangent spaces.
\end{proof}

\begin{corollary}[Multi-body coupling expansion; \ClaimStatusProvedHere]
\label{cor:twisted-ym-multibody-couplings}
Let $\cB_1,\dots,\cB_m$ be quadratic Koszul-admissible twisted Yang--Mills boundary data on $X$, and suppose each dual center splits as
\[
Z(\cA_i^{!}) \cong \mathbb{C}\mathbf{1}\oplus \widetilde Z_i.
\]
Then the reduced first-order deformation space of the composite boundary datum
\[
\cB_{1\cdots m}
:=
\cB_1\otimes^{\mathrm{ch}}\cdots\otimes^{\mathrm{ch}}\cB_m
\]
admits the canonical expansion
\[
\widetilde T^1_X(\cB_{1\cdots m})
\cong
\bigoplus_{\emptyset \neq S \subseteq \{1,\dots,m\}}
\left(\bigotimes_{i\in S} \widetilde Z_i\right)^{\vee}\otimes \omega_X.
\]
Subsets $S$ of size $r$ parameterize $r$-body first-order couplings.
\end{corollary}

\begin{proof}
Iterate Theorem~\ref{thm:twisted-ym-binary-mixed-couplings}. Inductively one obtains
\[
Z(\cA_{1\cdots m}^{!})
\cong
\bigotimes_{i=1}^m Z(\cA_i^{!})
\cong
\bigotimes_{i=1}^m (\mathbb{C}\mathbf{1}\oplus \widetilde Z_i).
\]
Expanding the tensor product yields a direct sum over subsets $S\subseteq \{1,\dots,m\}$. Removing the empty subset gives the reduced statement, and dualizing/tensoring with $\omega_X$ proves the formula.
\end{proof}

\begin{corollary}[Mixed rigidity criterion; \ClaimStatusProvedHere]
\label{cor:twisted-ym-mixed-rigidity}
Under the hypotheses of Corollary~\ref{cor:twisted-ym-multibody-couplings}:
\begin{enumerate}[label=(\roman*)]
\item if every $\widetilde Z_i=0$, then every composite boundary condition is reduced-infinitesimally rigid;
\item if exactly one $\widetilde Z_i$ is nonzero, then there are no genuine mixed couplings;
\item a nonzero tensor product $\widetilde Z_{i_1}\otimes\cdots\otimes\widetilde Z_{i_r}$ is both necessary and sufficient for the existence of an $r$-body first-order coupling.
\end{enumerate}
\end{corollary}

\begin{proof}
Immediate from Corollary~\ref{cor:twisted-ym-multibody-couplings} by inspection of the subset expansion.
\end{proof}

\begin{remark}[Beyond the tangent-to-center principle]
\label{rem:twisted-ym-why-new}
Theorems~\ref{thm:twisted-ym-dual-unobstructedness}--\ref{thm:twisted-ym-binary-mixed-couplings} add three structures beyond the tangent-to-center principle:
\begin{enumerate}[label=(\roman*)]
\item a \emph{dual-side obstruction criterion} in negative Hochschild degree;
\item a \emph{formality theorem} identifying explicit formal coordinates on the boundary deformation space;
\item a \emph{multi-body coupling law}: composite boundary theories acquire mixed couplings controlled by tensor products of reduced dual centers.
\end{enumerate}
These determine the local geometry of boundary moduli.
\end{remark}

\section{Architectural synthesis: YM boundaries as a rung of the universal holography ladder}
\label{sec:ym-holography-rung-synthesis}

The chain
$\cA_{\cB} \to \barBch(\cA_{\cB}) \to (\cA_{\cB}^!)_\infty \to Z(\cA_{\cB}^!) \to Z^{\mathrm{vis}}$
is not an isolated reduction sequence. It is the YM specialization of the Universal
Holography Master functor (Theorem~\ref{thm:universal-holography-master},
Chapter~\ref{ch:programme-climax-platonic}): every Koszul-admissible boundary
chiral algebra defines a 3d HT bulk via $\Phi_{\mathrm{hol}}$, and the visible
center $Z^{\mathrm{vis}}$ is the boundary-linear shadow of the bulk derived
chiral center.

\begin{remark}[YM as a $\Phi_{\mathrm{hol}}$ rung of the universal holography ladder]
\label{rem:ym-holography-rung-anchor}
Within the universal celestial holography theorem
(Theorem~\ref{thm:uch-main}, Chapter~\ref{sec:universal-celestial-holography}),
twisted Yang--Mills boundary data sit alongside the affine Kac--Moody rung
(Corollary~\ref{cor:rung-affine-km}) as a Beem--Rastelli $\chi$-functor target:
the gauge-to-chiral $\chi$ map of \cite{BR15} factors through the same bar-cobar
diagram analyzed in Theorem~\ref{thm:ym-bar-bridge}. The visible-center
extraction is therefore not bespoke to YM; it is the universal extraction of
the \emph{boundary-linear sector} of the bulk derived chiral center, specialized
to a four-dimensional gauge-theoretic origin.
\end{remark}

\begin{remark}[Universal conductor and YM Koszul conductor]
\label{rem:ym-universal-conductor}
The Koszul conductor $K = \kappa(\cA_{\cB}) + \kappa(\cA_{\cB}^!)$ controlling the
Koszul-pair self-duality at the YM boundary is a specialization of the
universal conductor identity
\[
K \;=\; -\,c_{\mathrm{ghost}}\bigl(\BRST(\cA)\bigr)
\]
proved in Volume~I (\Cref{V1-chap:universal-conductor}). For
Koszul-admissible Yang--Mills boundary data the
ghost charge of the BRST resolution computes the negative of $K$ family-by-family;
the screening Hodge theorem of \S\ref{sec:twisted-ym-central-formality} is the
chain-level realization of the conductor identity for those boundary classes.
\end{remark}

\begin{remark}[Universal holography stack stratification]
\label{rem:ym-universal-scope-stratification}
The scope stratification of Remark~\ref{rem:ym-boundary-status-stratification}
inherits its scope from the universal holography stack:
\begin{enumerate}[label=(\alph*)]
\item the boundary BRST recovery, the tangent-to-center principle, central
formality, relative derived centers, higher-body \v{C}ech duality, and the
screening Hodge theorem are unconditional on the affine + principal $\cW$
sublocus that already realizes the affine Kac--Moody and Virasoro/$W_N$ rungs
of the universal holography ladder;
\item the realization of the dual algebra as the full physical defect algebra,
and the existence of a natural Hilbert-screening bridge for untwisted
four-dimensional Yang--Mills, are the YM-specialized analogues of the
class-$M$ chain-level frontier closed by the DS--Hochschild compatibility bridge
(Theorem~\ref{thm:chd-ds-hochschild}) and the universal-holography class-$M$
corollary (Corollary~\ref{cor:universal-holography-class-M});
\item the canonical instanton-completed bulk dual and full untwisting equivalence
remain the genuine research frontier, on the same footing as the logarithmic
$\cW(p)$ tempering frontier (cf.\ the open frontiers list).
\end{enumerate}
The YM boundary chain is therefore a \emph{rung}; the platonic ladder
extends below to abelian holomorphic CS (Heisenberg rung) and above through
$E_\infty$-topologization in the iterated Sugawara tower.
\end{remark}
