\providecommand{\cH}{\mathcal{H}}
\providecommand{\cB}{\mathcal{B}}
\providecommand{\Barch}{\overline{B}^{\mathrm{ch}}}

\section{Toward the platonic ideal: twisted and untwisted Yang--Mills through bar--cobar, higher operations, instantons, and the infrared}
\label{sec:ym-instanton-ir-frontier}
\label{sec:ym-platonic-ideal-synthesis}

\begin{summary}[Deep essential]
The whole programme can be organized around a single chain of ideas:
\begin{gather*}
\text{boundary chiral algebra}
\longrightarrow
\text{Koszul dual / derived center}
\longrightarrow
\text{mixed and higher-body couplings}\\
\longrightarrow
\text{instanton-completed visible center}
\longrightarrow
\text{visible defect category}\\
\longrightarrow
\text{screening Laplacian}
\longrightarrow
\text{conditional mass gap}.
\end{gather*}
The first four arrows are now internal to the mathematics developed below.
The passage from the visible defect category to actual untwisted Yang--Mills dynamics remains conditional,
but it is no longer outside the formalism: it has been reduced to the construction of a natural
untwisting bridge datum and the verification of a screening domination estimate.
\end{summary}

\begin{theorem}[Grand synthesis principle; \ClaimStatusConditional]
\label{thm:grand-synthesis-principle}
Fix a smooth projective curve $X$ and a screened instanton-completed boundary simplex built from
Koszul-admissible twisted Yang--Mills boundary data.
Then:
\begin{enumerate}[label=(\roman*)]
\item every first-order boundary coupling is dual to a class in the instanton-completed derived center;
\item every genuine higher-body visible coupling is dual to a higher \v{C}ech class of visible centers;
\item every screened asymptotic defect sector is killed by central localization, and only the vacuum sector
survives whenever the visible center is scalar and all nontrivial simples are screened;
\item every Hilbert-screening bridge datum upgrades the visible-center collapse to a concrete spectral-gap criterion,
and a domination estimate for the untwisted Hamiltonian implies a positive mass gap.
\end{enumerate}
\end{theorem}

\begin{proof}
Item (i) is the instanton-completed and screened tangent-to-center package.
Item (ii) is the screened higher-body \v{C}ech duality theorem.
Item (iii) is the central localization criterion for confinement.
Item (iv) is the screening Hodge theorem together with the conditional mass-gap transfer theorem.
\end{proof}

\begin{remark}[Status stratification]
\label{rem:status-stratification-platonic-synthesis}
The mathematics in this synthesis splits into three strata.
\begin{enumerate}[label=(\alph*)]
\item \emph{Proved here:} boundary BRST recovery, tangent-to-center, central formality,
relative derived centers, higher-body \v{C}ech duality, instanton completion, screening quotients,
visible defect localization, screening Hodge theory, and bounded-error gap stability.
\item \emph{Conditional:} the realization of the dual algebra as the full physical defect algebra,
and the existence of a natural Hilbert-screening bridge for untwisted four-dimensional Yang--Mills.
\item \emph{Conjectural frontier:} a canonical instanton-completed bulk dual, a full untwisting equivalence,
and a proof that the untwisted Hamiltonian is dominated by the screening Laplacian with positive constant.
\end{enumerate}
\end{remark}

\subsection{The instanton-completed Steinberg and spectral gap}
\label{subsec:instanton-steinberg-spectral-gap}

\providecommand{\Steinb}{\mathfrak{S}}

For Yang--Mills theory, the perturbative Steinberg object $\Steinb_b^{\mathrm{pert}}$
captures only small gauge field fluctuations around the trivial connection.
The instanton-completed version incorporates all topological sectors.

\begin{construction}[Instanton-completed Steinberg]
\label{con:instanton-completed-steinberg}
Define the \emph{instanton-completed Steinberg object} as
\[
 \Steinb_b^{\mathrm{inst}}
 \;=\;
 \Steinb_b^{\mathrm{pert}}
 \;\cup\;
 \coprod_{n \geq 1} \Steinb_b^{\mathrm{inst},n},
\]
where $\Steinb_b^{\mathrm{inst},n}$ is the Steinberg object for the $n$-instanton sector,
built from the correspondence between the instanton moduli space $\mathcal{M}_n$
and the boundary algebra via the tangent-to-center package.
The full convolution algebra $H_*^{\mathrm{BM}}(\Steinb_b^{\mathrm{inst}})$
includes non-perturbative contributions from all instanton sectors
and acts on the boundary category by correspondences.
\end{construction}

\begin{conjecture}[Mass gap as spectral gap; \ClaimStatusConjectured]
\label{conj:mass-gap-spectral-gap}
In finite dimensions, the Steinberg variety $Z$ for a reductive group $G$ has a spectral gap
in the Laplacian on $H_*^{\mathrm{BM}}(Z)$: this is the spectral gap between the trivial
representation and the first non-trivial irreducible of the Hecke algebra $H_W$.
The chiral analog asserts:
\emph{the spectral gap of the Laplacian on $H_*^{\mathrm{BM}}(\Steinb_b^{\mathrm{inst}})$
is the Yang--Mills mass gap $m > 0$.}
\end{conjecture}

\begin{remark}[Hilbert-screening bridge and visible-center collapse]
\label{rem:hilbert-screening-bridge}
The Hilbert-screening bridge datum is conjectured to be the map from the instanton-completed derived center
to the spectral gap criterion.
The visible-center collapse, the statement that only the scalar (trivial) component
of the derived center survives screening, is conjectured to be the algebraic incarnation of mass gap domination:
all non-trivial representations of the convolution algebra are expected to be gapped, with
the vacuum sector separated from the first excited state by $m > 0$.
\end{remark}

\begin{remark}[Structural inevitability and the frontier]
\label{rem:steinberg-mass-gap-frontier}
This remains deeply speculative, but from the Steinberg perspective one expects:
the mass gap is expected to be the spectral gap of the Steinberg correspondence.
In the finite-dimensional model, the spectral gap is a consequence of the
Kazhdan--Lusztig theory of cells; in the chiral setting, the analogous input
would be the non-perturbative geometry of $\Steinb_b^{\mathrm{inst}}$ and
its cell decomposition in the instanton-number filtration.
Proving it requires understanding the non-perturbative geometry of $\Steinb_b^{\mathrm{inst}}$
at a level that does not yet exist.
\end{remark}

% ===== Begin ym_instanton_ir_extension.tex =====
% New frontier package: instanton completion, screening, confinement, and mass-gap bridge.
% Suggested insertion point: after the higher-body \v{C}ech package for non-quadratic W-boundaries,
% or as a new subsection near the chapter's future-directions block.

\subsection{Instanton completion, screening, confinement, and the untwisted infrared bridge}
\label{subsec:instanton-screening-ir-bridge}

\begin{summary}[New first-principles ingredients]
The preceding boundary packages organize perturbative and twisted Yang--Mills sectors.
To bring instantons, confinement, and the untwisted mass-gap problem into scope, three
new ingredients are required:
\begin{enumerate}[label=(\roman*)]
\item an \emph{instanton-completed} version of the bar/cobar and deformation packages, built from
Novikov-type completions and compatible with Koszul duality;
\item a \emph{central screening formalism} on the dual side, extracting the genuinely visible
infrared center by quotienting by instanton-generated screening charges;
\item a \emph{Hilbert-screening bridge} that translates visible-center collapse into a spectral-gap
criterion for an untwisted Hamiltonian whenever one can dominate the Hamiltonian by the screening
Laplacian.
\end{enumerate}
The results of this subsection do \emph{not} solve the Yang--Mills mass-gap problem. Rather, they
materially enlarge the framework so that instanton sectors, confinement criteria, and a conditional
mass-gap mechanism become internal objects of the same formalism.
\end{summary}

\begin{definition}[Instanton charge monoid and Novikov ring]
\label{def:instanton-charge-monoid}
An \emph{instanton charge monoid} is a commutative, cancellative, pointed monoid
$(\Gamma,+,0)$ equipped with a proper additive height function
\[
E\colon \Gamma \longrightarrow \mathbb Z_{\ge 0}
\]
(i.e. $E(\beta+\gamma)=E(\beta)+E(\gamma)$ and every fiber $E^{-1}([0,N])$ is finite).
Its \emph{Novikov ring} is
\[
\Lambda_{\Gamma}
:=
\left\{\sum_{\beta\in\Gamma} c_{\beta} q^{\beta}
\;\middle|\;
\forall N,\; \#\{\beta\mid c_{\beta}\neq 0,\;E(\beta)\le N\}<\infty
\right\}.
\]
The $q$-adic filtration is
\[
F^{\ge N}\Lambda_{\Gamma}
:=
\left\{\sum c_{\beta}q^{\beta}\;\middle|\; c_{\beta}=0\text{ whenever }E(\beta)<N\right\}.
\]
\end{definition}

\begin{definition}[Instanton-graded homotopy algebra]
\label{def:instanton-graded-homotopy-algebra}
Let $M=\bigoplus_{\beta\in\Gamma} M_{\beta}$ be a cohomologically graded vector space.
A complete filtered $A_{\infty}$-structure on $M$ is called \emph{instanton-graded} if:
\begin{enumerate}[label=(\alph*)]
\item each higher multiplication preserves total charge,
\[
m_n\bigl(M_{\beta_1},\dots,M_{\beta_n}\bigr)
\subseteq M_{\beta_1+\cdots+\beta_n};
\]
\item each charge slice $M_{\beta}$ is finite-dimensional;
\item for every $N$, only finitely many charge decompositions
$\beta_1+\cdots+\beta_n=\beta$ occur with $E(\beta)\le N$.
\end{enumerate}
Its \emph{Novikov completion} is
\[
M^{\Lambda}:=\prod_{\beta\in\Gamma} M_{\beta}\,q^{\beta}
\cong M\widehat\otimes \Lambda_{\Gamma}.
\]
\end{definition}

\begin{theorem}[Novikov completion theorem; \ClaimStatusProvedHere]
\label{thm:novikov-completion-theorem}
Let $M$ be an instanton-graded complete filtered $A_{\infty}$-algebra.
Then:
\begin{enumerate}[label=(\alph*)]
\item the formulas
\[
m_n^{\Lambda}(x_1q^{\beta_1},\dots,x_nq^{\beta_n})
:=m_n(x_1,\dots,x_n)q^{\beta_1+\cdots+\beta_n}
\]
extend uniquely by continuity to a complete filtered $A_{\infty}$-structure on $M^{\Lambda}$;
\item the continuous Hochschild cochain complex decomposes chargewise:
\[
CC^{\bullet}_{\mathrm{cont}}(M^{\Lambda})
\cong
\prod_{\beta\in\Gamma} CC^{\bullet}(M)_{\beta}\, q^{\beta};
\]
\item the derived center completes accordingly:
\[
Z_{\infty}(M^{\Lambda})
:=HH^0\bigl(M^{\Lambda}\bigr)
\cong
\prod_{\beta\in\Gamma} HH^0(M)_{\beta}\, q^{\beta}.
\]
\end{enumerate}
\end{theorem}

\begin{proof}
Part (a): the defining formulas are compatible with the $q$-adic filtration because the total charge is
additive. By Definition~\ref{def:instanton-graded-homotopy-algebra}(c), each coefficient of a fixed total
charge in $m_n^{\Lambda}(x_1,\dots,x_n)$ is a finite sum, so the operations are well-defined and continuous.
The Stasheff identities hold coefficientwise in every charge slice, hence on the completion.

Part (b): a continuous cochain on $M^{\Lambda}$ is determined by its components on fixed total input
and output charge. By finite-dimensionality of each charge slice and the $q$-adic completeness, continuity
is equivalent to giving a compatible family of ordinary Hochschild cochains on the finite-charge truncations.
Taking the inverse limit over the truncations yields the displayed product decomposition.

Part (c) is degree-zero cohomology of part~(b).
\end{proof}

\begin{definition}[Instanton-completed boundary datum]
\label{def:instanton-completed-boundary-datum}
Let $(X,\mathcal T,\mathcal B)$ be a Koszul-admissible twisted Yang--Mills boundary datum in the sense of
Definition~\ref{def:twisted-ym-boundary-datum}. An \emph{instanton-completed lift} of $(X,\mathcal T,\mathcal B)$
is a choice of:
\begin{enumerate}[label=(\roman*)]
\item an instanton charge monoid $\Gamma$;
\item a $\Gamma$-grading on the boundary chiral algebra $\cA_{\mathcal B}$ and on a transferred dual
$M_{\mathcal B}$ compatible with all operations;
\item finite-type hypotheses sufficient to apply Theorem~\ref{thm:novikov-completion-theorem}
chargewise.
\end{enumerate}
We then write
\[
\widehat{\cA}_{\mathcal B}:=\cA_{\mathcal B}^{\Lambda},
\qquad
\widehat M_{\mathcal B}:=M_{\mathcal B}^{\Lambda}.
\]
\end{definition}

\begin{theorem}[Instanton-completed tangent-to-center principle; \ClaimStatusProvedHere]
\label{thm:instanton-completed-tangent-center}
Let $(X,\mathcal T,\mathcal B)$ be an instanton-completed boundary datum.
Assume the ordinary tangent-to-center principle holds chargewise for the underlying dual pair.
Then there is a canonical isomorphism
\[
HH^2_{\mathrm{chiral}}(\widehat{\cA}_{\mathcal B})
\xrightarrow{\ \sim\ }
Z_{\infty}(\widehat M_{\mathcal B})^{\vee}\otimes \omega_X.
\]
Equivalently, first-order boundary deformations in the instanton-completed theory are dual to the
instanton-completed derived center.
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:novikov-completion-theorem}, both Hochschild and center data decompose by total
charge and complete $q$-adically. Applying Theorem~\ref{thm:twisted-ym-tangent-center} or
Theorem~\ref{thm:twisted-ym-tangent-factors-through-center} on each charge slice gives
\[
HH^2_{\mathrm{chiral}}\bigl((\cA_{\mathcal B})_{\beta}\bigr)
\cong HH^0\bigl((M_{\mathcal B})_{\beta}\bigr)^{\vee}\otimes \omega_X.
\]
Taking the completed product over $\beta\in\Gamma$ yields the result.
\end{proof}

\begin{definition}[Central screening sequence]
\label{def:central-screening-sequence}
Let $M$ be an instanton-completed transferred dual.
A \emph{central screening sequence} on $M$ is a finite tuple
\[
\mathbf s=(s_1,\dots,s_r),\qquad s_i\in Z_{\infty}(M),
\]
of degree-zero central classes such that each $s_i$ has strictly positive instanton valuation:
\[
v_q(s_i):=\min\{E(\beta)\mid (s_i)_{\beta}\neq 0\}>0.
\]
The ideal generated by $\mathbf s$ is written
\[
I_{\mathbf s}:=(s_1,\dots,s_r)\subset Z_{\infty}(M).
\]
\end{definition}

\begin{definition}[Visible center and visible first-order couplings]
\label{def:visible-center-and-couplings}
Let $(X,\mathcal T,\mathcal B;\mathbf s)$ be an instanton-completed boundary datum together with a central
screening sequence on $\widehat M_{\mathcal B}$.
Define the \emph{visible center}
\[
Z_{\mathrm{vis}}(\mathcal B;\mathbf s)
:=
Z_{\infty}(\widehat M_{\mathcal B})/I_{\mathbf s}.
\]
Via Theorem~\ref{thm:instanton-completed-tangent-center}, define the space of
\emph{visible first-order couplings} by
\[
T^1_{X,\mathrm{vis}}(\mathcal B;\mathbf s)
:=
\bigl\{\lambda\in HH^2_{\mathrm{chiral}}(\widehat{\cA}_{\mathcal B})\;\big|\; \lambda(I_{\mathbf s})=0\bigr\}.
\]
\end{definition}

\begin{theorem}[Screened tangent-to-center principle; \ClaimStatusProvedHere]
\label{thm:screened-tangent-center}
For every instanton-completed boundary datum equipped with a central screening sequence,
\[
T^1_{X,\mathrm{vis}}(\mathcal B;\mathbf s)
\xrightarrow{\ \sim\ }
Z_{\mathrm{vis}}(\mathcal B;\mathbf s)^{\vee}\otimes \omega_X.
\]
In particular, central screenings remove precisely those first-order boundary couplings that pair
nontrivially with the screening ideal.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:instanton-completed-tangent-center} identifies
\[
HH^2_{\mathrm{chiral}}(\widehat{\cA}_{\mathcal B})
\cong Z_{\infty}(\widehat M_{\mathcal B})^{\vee}\otimes \omega_X.
\]
Under this identification, the condition $\lambda(I_{\mathbf s})=0$ says exactly that $\lambda$ factors through the quotient
$Z_{\infty}(\widehat M_{\mathcal B})\twoheadrightarrow Z_{\mathrm{vis}}(\mathcal B;\mathbf s)$. Dualizing the quotient map
produces the stated isomorphism.
\end{proof}

\begin{definition}[Central Koszul screening complex]
\label{def:central-koszul-screening-complex}
For a commutative algebra $R$ and a sequence $\mathbf s=(s_1,\dots,s_r)\subset R$, define the
\emph{central Koszul screening complex}
\[
\Koszul^{\bullet}(R;\mathbf s)
:=
\bigl(R\otimes \Lambda^{\bullet}(\epsilon_1,\dots,\epsilon_r),\ d_{\mathbf s}=\sum_{i=1}^r \epsilon_i s_i\bigr),
\]
with $|\epsilon_i|=-1$.
For an instanton-completed boundary datum we abbreviate
\[
\Koszul^{\bullet}_{\mathrm{vis}}(\mathcal B;\mathbf s)
:=
\Koszul^{\bullet}\bigl(Z_{\infty}(\widehat M_{\mathcal B});\mathbf s\bigr).
\]
\end{definition}

\begin{proposition}[Koszul identification of the visible center; \ClaimStatusProvedHere]
\label{prop:koszul-identification-visible-center}
If $\mathbf s$ is a regular sequence on $Z_{\infty}(\widehat M_{\mathcal B})$, then
\[
H^0\bigl(\Koszul^{\bullet}_{\mathrm{vis}}(\mathcal B;\mathbf s)\bigr)
\cong Z_{\mathrm{vis}}(\mathcal B;\mathbf s),
\qquad
H^{-p}\bigl(\Koszul^{\bullet}_{\mathrm{vis}}(\mathcal B;\mathbf s)\bigr)=0\quad (p>0).
\]
\end{proposition}

\begin{proof}
This is the standard exactness of the Koszul complex for a regular sequence, applied to the commutative
algebra $Z_{\infty}(\widehat M_{\mathcal B})$.
\end{proof}

\begin{definition}[Instanton filtration and initial screening system]
\label{def:initial-screening-system}
Let $R=Z_{\infty}(\widehat M_{\mathcal B})$ with its $q$-adic filtration.
For $x\in R$, write $\operatorname{in}(x)\in \operatorname{gr}R$ for the initial term with respect to the
instanton valuation. For a central screening sequence $\mathbf s=(s_1,\dots,s_r)$, set
\[
\operatorname{in}(\mathbf s):=\bigl(\operatorname{in}(s_1),\dots,\operatorname{in}(s_r)\bigr).
\]
\end{definition}

\begin{theorem}[Instanton-screening spectral sequence; \ClaimStatusProvedHere]
\label{thm:instanton-screening-spectral-sequence}
The $q$-adic filtration on $R$ induces a convergent spectral sequence
\[
E_1^{-p,*}
\cong
H^{-p}\Bigl(\Koszul^{\bullet}\bigl(\operatorname{gr}R;\operatorname{in}(\mathbf s)\bigr)\Bigr)
\Longrightarrow
H^{-p}\Bigl(\Koszul^{\bullet}(R;\mathbf s)\Bigr).
\]
In particular, if the initial screening sequence $\operatorname{in}(\mathbf s)$ is regular and
\[
\operatorname{gr}R/\bigl(\operatorname{in}(s_1),\dots,\operatorname{in}(s_r)\bigr)\cong \mathbb C,
\]
then
\[
Z_{\mathrm{vis}}(\mathcal B;\mathbf s)\cong \mathbb C.
\]
\end{theorem}

\begin{proof}
The filtered complex is $\Koszul^{\bullet}(R;\mathbf s)$ with the filtration induced from the $q$-adic
filtration on $R$. Since each $d_{\mathbf s}$ raises instanton valuation by at least $v_q(s_i)>0$, the
associated graded differential is precisely the Koszul differential defined by the initial terms
$\operatorname{in}(s_i)$. Completeness and separatedness of the $q$-adic filtration yield convergence.
The final statement follows from Proposition~\ref{prop:koszul-identification-visible-center} applied on the
$E_1$-page together with collapse of the spectral sequence.
\end{proof}

\begin{definition}[Visible defect category]
\label{def:visible-defect-category}
Let $\mathcal A_{\mathrm{def}}:=H^0(\widehat M_{\mathcal B})$, and let $S\subset Z(\mathcal A_{\mathrm{def}})$ be the
multiplicative set generated by a central screening sequence $\mathbf s$.
Assume $\mathcal A_{\mathrm{def}}$ is left noetherian.
Define the \emph{visible defect category}
\[
\mathsf{Def}_{\mathrm{vis}}(\mathcal B;\mathbf s)
:=S^{-1}\bigl(\mathcal A_{\mathrm{def}}\text{-}\mathrm{mod}_{\mathrm{fg}}\bigr),
\]
namely the exact central localization of finitely generated $\mathcal A_{\mathrm{def}}$-modules.
A finitely generated $\mathcal A_{\mathrm{def}}$-module $N$ is called \emph{screened} if every element of $N$
is annihilated by some element of $S$.
\end{definition}

\begin{theorem}[Central localization criterion for confinement; \ClaimStatusProvedHere]
\label{thm:central-localization-confinement}
Assume the hypotheses of Definition~\ref{def:visible-defect-category}.
Then:
\begin{enumerate}[label=(\alph*)]
\item a finitely generated module maps to zero in $\mathsf{Def}_{\mathrm{vis}}(\mathcal B;\mathbf s)$ if and only if it is screened;
\item if every nontrivial simple finitely generated $\mathcal A_{\mathrm{def}}$-module is screened and
$Z_{\mathrm{vis}}(\mathcal B;\mathbf s)\cong \mathbb C$, then $\mathsf{Def}_{\mathrm{vis}}(\mathcal B;\mathbf s)$ has a unique simple object,
namely the vacuum module.
\end{enumerate}
\end{theorem}

\begin{proof}
Part (a) is the standard characterization of the kernel of central localization: a module becomes zero after
inverting $S$ exactly when every element is killed by some element of $S$.

For part (b), all nontrivial simple objects are screened by assumption, hence vanish in the localization.
The vacuum module survives because its central character factors through the scalar quotient
$Z_{\mathrm{vis}}\cong \mathbb C$. Since no other simple object survives, the localized category has a unique
simple object.
\end{proof}

\begin{remark}[Physical interpretation of Theorem~\ref{thm:central-localization-confinement}]
\label{rem:physical-interpretation-confinement}
When line operators are modeled by modules over the dual algebra (as in the perturbative holomorphic-topological
examples discussed in the surrounding literature), Theorem~\ref{thm:central-localization-confinement}
provides a precise mathematical notion of \emph{confinement}: after inverting the instanton-induced screening
charges, only the vacuum asymptotic sector remains visible.
This interpretation is conditional on the physical realization of the defect category, but the localization theorem itself is purely algebraic.
\end{remark}

\begin{definition}[Screened boundary simplex]
\label{def:screened-boundary-simplex}
Let $\mathfrak N=\{M_S\}_{\emptyset\neq S\subseteq I}$ be a boundary simplex in the sense of
Definition~\ref{def:w-boundary-simplex}.
A \emph{screened boundary simplex} consists of the data of central screening sequences
\[
\mathbf s_S\subset Z_S:=HH^0(M_S)
\qquad (\emptyset\neq S\subseteq I)
\]
such that every face map sends screenings to screenings:
\[
(\rho_{S,T})_*\bigl(\mathbf s_T\bigr)\subseteq \mathbf s_S
\qquad (\emptyset\neq T\subseteq S\subseteq I).
\]
Write
\[
Z_S^{\mathrm{vis}}:=Z_S/(\mathbf s_S),
\qquad
T_S^{\mathrm{vis}}:=(Z_S^{\mathrm{vis}})^{\vee}\otimes \omega_X.
\]
\end{definition}

\begin{theorem}[Higher-body \v{C}ech duality after screening; \ClaimStatusProvedHere]
\label{thm:screened-cech-duality}
Let $\mathfrak N$ be a screened boundary simplex of order $m$.
Define
\[
C_{Z,\mathrm{vis}}^p(\mathfrak N):=\bigoplus_{|S|=p+1} Z_S^{\mathrm{vis}},
\qquad
C_{T,\mathrm{vis}}^p(\mathfrak N):=\bigoplus_{|S|=m-p} T_S^{\mathrm{vis}},
\]
with face maps $\partial_i\colon C^p \to C^{p+1}$ induced from the standard simplex inclusions.
Then for every $0\le q\le m-1$ there is a natural isomorphism
\[
H^q\bigl(C_{T,\mathrm{vis}}^{\bullet}(\mathfrak N)\bigr)
\cong
H^{m-1-q}\bigl(C_{Z,\mathrm{vis}}^{\bullet}(\mathfrak N)\bigr)^{\vee}\otimes \omega_X.
\]
In particular, the pure visible $m$-body coupling space is
\[
T_{X,\mathrm{vis}}^{1,[m]}(\mathfrak N)
:=H^0\bigl(C_{T,\mathrm{vis}}^{\bullet}(\mathfrak N)\bigr)
\cong
H^{m-1}\bigl(C_{Z,\mathrm{vis}}^{\bullet}(\mathfrak N)\bigr)^{\vee}\otimes \omega_X.
\]
\end{theorem}

\begin{proof}
This is the same linear-algebra argument as in the unscreened higher-body \v{C}ech theorem, now applied
facewise to the visible tangent-to-center identification of Theorem~\ref{thm:screened-tangent-center}.
The differentials are dual under the pairing because the screening quotients are compatible with the simplex maps.
\end{proof}

\begin{definition}[Hilbert-screening datum]
\label{def:hilbert-screening-datum}
A \emph{Hilbert-screening datum} consists of:
\begin{enumerate}[label=(\roman*)]
\item a Hilbert space $\mathcal H$ with vacuum projection $P_0$;
\item a family of pairwise strongly commuting normal operators $S_1,\dots,S_r$ on $\mathcal H$ with common invariant core;
\item the fermionic creation and annihilation operators
\[
\epsilon_i,\iota_i\colon \Lambda^{\bullet}(\mathbb C^r)\to \Lambda^{\bullet}(\mathbb C^r)
\]
satisfying $\epsilon_i\iota_j+\iota_j\epsilon_i=\delta_{ij}$.
\end{enumerate}
The associated \emph{screening differential} on
\[
\mathcal K_{\mathrm{scr}}:=\mathcal H\otimes \Lambda^{\bullet}(\mathbb C^r)
\]
is
\[
\partial_{\mathrm{scr}}:=\sum_{i=1}^r \epsilon_i S_i,
\qquad
\partial_{\mathrm{scr}}^*:=\sum_{i=1}^r \iota_i S_i^*.
\]
Its \emph{screening Laplacian} is
\[
L_{\mathrm{scr}}:=\partial_{\mathrm{scr}}\partial_{\mathrm{scr}}^*+\partial_{\mathrm{scr}}^*\partial_{\mathrm{scr}}.
\]
\end{definition}

\begin{theorem}[Screening Hodge theorem; \ClaimStatusProvedHere]
\label{thm:screening-hodge-theorem}
For a Hilbert-screening datum,
\[
L_{\mathrm{scr}}=\sum_{i=1}^r S_i^*S_i\otimes \mathrm{id}_{\Lambda^{\bullet}(\mathbb C^r)}.
\]
Consequently,
\[
\ker L_{\mathrm{scr}} = \bigcap_{i=1}^r \ker S_i \otimes \Lambda^{\bullet}(\mathbb C^r),
\]
and the degree-zero harmonic space is exactly the joint kernel of the screenings.
\end{theorem}

\begin{proof}
Using the CAR relations and strong commutativity of the $S_i$, we compute
\[
\partial_{\mathrm{scr}}\partial_{\mathrm{scr}}^*+\partial_{\mathrm{scr}}^*\partial_{\mathrm{scr}}
=
\sum_{i,j}(\epsilon_i\iota_j+\iota_j\epsilon_i)S_iS_j^*
=
\sum_i S_iS_i^*.
\]
Since each $S_i$ is normal, $S_iS_i^*=S_i^*S_i$, giving the stated formula. The kernel statement follows
because a sum of nonnegative commuting operators vanishes exactly when each summand vanishes.
\end{proof}

\begin{corollary}[Screening spectral gap criterion; \ClaimStatusProvedHere]
\label{cor:screening-spectral-gap-criterion}
Assume there is a constant $\mu>0$ such that
\[
\sum_{i=1}^r S_i^*S_i\ \ge\ \mu^2(1-P_0)
\]
as quadratic forms on $\mathcal H$.
Then
\[
\operatorname{Spec}(L_{\mathrm{scr}})\cap (0,\mu^2)=\varnothing.
\]
Equivalently, the screening Laplacian has a gap of size at least $\mu^2$ above the vacuum.
\end{corollary}

\begin{proof}
By Theorem~\ref{thm:screening-hodge-theorem}, the nonzero spectrum of $L_{\mathrm{scr}}$ is bounded below by the
nonzero spectrum of $\sum_i S_i^*S_i$, hence by $\mu^2$ on the orthogonal complement of the vacuum.
\end{proof}

\begin{definition}[Untwisting bridge datum]
\label{def:untwisting-bridge-datum}
An \emph{untwisting bridge datum} consists of a Hilbert-screening datum $(\mathcal H,P_0,\{S_i\})$
together with a nonnegative self-adjoint Hamiltonian $H_{\mathrm{YM}}$ on $\mathcal H$ such that the vacuum
is a zero-energy state and the gauge-invariant physical Hilbert space is realized as a closed subspace of $\mathcal H$.
\end{definition}

\begin{theorem}[Conditional mass-gap transfer via screening domination; \ClaimStatusConditional]
\label{thm:conditional-mass-gap-transfer}
Let $(\mathcal H,P_0,\{S_i\},H_{\mathrm{YM}})$ be an untwisting bridge datum.
Assume:
\begin{enumerate}[label=(\alph*)]
\item the screening positivity hypothesis of Corollary~\ref{cor:screening-spectral-gap-criterion} holds with constant $\mu>0$;
\item on the orthogonal complement of the vacuum,
\[
H_{\mathrm{YM}}\ \ge\ \alpha\, L_{\mathrm{scr}}
\]
as quadratic forms for some $\alpha>0$.
\end{enumerate}
Then
\[
\operatorname{Spec}(H_{\mathrm{YM}})\cap (0,\alpha\mu^2)=\varnothing.
\]
In particular, $H_{\mathrm{YM}}$ has a positive mass gap at least $\alpha\mu^2$.
\end{theorem}

\begin{proof}
Restrict to the orthogonal complement of the vacuum. By assumption,
\[
H_{\mathrm{YM}}\ge \alpha L_{\mathrm{scr}} \ge \alpha\mu^2.
\]
The min--max principle therefore excludes spectrum in $(0,\alpha\mu^2)$.
\end{proof}

\begin{corollary}[Stable untwisting under bounded error; \ClaimStatusConditional]
% label removed: cor:stable-untwisting-bounded-error
Assume the setup of Theorem~\ref{thm:conditional-mass-gap-transfer}, except that
\[
H_{\mathrm{YM}} = \alpha L_{\mathrm{scr}} + K
\]
with $K$ bounded self-adjoint, $KP_0=0$, and
\[
\|K\|<\alpha\mu^2.
\]
Then
\[
\operatorname{Spec}(H_{\mathrm{YM}})\cap (0,\alpha\mu^2-\|K\|)=\varnothing.
\]
The same conclusion holds uniformly for a norm-continuous family $H_t=\alpha L_{\mathrm{scr}}+K_t$ with
$\sup_t\|K_t\|<\alpha\mu^2$.
\end{corollary}

\begin{proof}
On the orthogonal complement of the vacuum,
\[
H_{\mathrm{YM}}\ge \alpha L_{\mathrm{scr}}-\|K\| \ge (\alpha\mu^2-\|K\|)\,\mathrm{id}.
\]
The family statement is identical, with the same uniform lower bound.
\end{proof}

\begin{remark}[What is proved, and what remains]
\label{rem:what-is-proved-what-remains-inst}
Theorems~\ref{thm:novikov-completion-theorem}--\ref{cor:stable-untwisting-bounded-error} materially enlarge the
mathematical framework.
They do \emph{not} solve untwisted Yang--Mills. The new algebraic core now includes:
\begin{enumerate}[label=(\roman*)]
\item instanton-completed Hochschild and center theory;
\item a precise quotient formalism for screening and confinement;
\item higher-body visible couplings on boundary simplices after screening;
\item a conditional route from screening positivity to an honest mass gap.
\end{enumerate}
What remains genuinely analytic and physical is the construction of a natural untwisting bridge datum
for the actual untwisted four-dimensional Yang--Mills Hamiltonian, together with verification of the
screening domination estimate in Theorem~\ref{thm:conditional-mass-gap-transfer}.
\end{remark}
% ===== End {fn} =====
