%% =====================================================================
%% beta_N_closed_form_all_platonic.tex
%%
%% Frontier reduction: the harmonic candidate for the Riccati
%% leading-Laurent ratio coefficient beta_N for principal W_N.
%%
%% Input data:
%%   * Theorem thm:wn-tempered-all-N: tempering at every finite beta_N
%%     for every principal W_{N,c}.
%%   * The low-rank identities beta_2 = 6 and beta_3 = 10.
%%   * Two polynomial interpolants through the low-rank identities:
%%     (N+1)(N+2)/2 and N^2 - N + 4.
%%
%% This chapter distinguishes the low-rank interpolants from the
%% harmonic candidate using the Vol II master equation and
%% the Vol II datum A_4^{W_3} = 10/3
%% (proposition prop:w3-shadow-leading-asymptotic(3)).
%%
%%   The kappa-ratio scaling conjecture predicts
%%     beta_N = 12 * (H_N - 1),   where H_N = sum_{j=1}^{N} 1/j,
%%   giving
%%     beta_2 = 6    (agrees with both candidates)
%%     beta_3 = 10   (agrees with both candidates)
%%     beta_4 = 13   (excludes A = 15, B = 16)
%%     beta_5 = 77/5 (excludes A = 21, B = 24; also predicts that
%%                    beta_N is rational-valued, not integer-valued).
%%
%%   The closed form
%%     beta_N = 12 * (H_N - 1)
%%   is conditional on the kappa-ratio scaling law
%%     A_r(W_N) = (kappa(W_N)/kappa(Vir))^{r-3} * A_r(Vir).
%%   The Vol II tempering theorem thm:wn-tempered-all-N uses only
%%   beta-independent Stirling dominance. The exact convergence radius is
%%     rho_*^{W_N}(c) = |c| / [12 * (H_N - 1)].
%%
%% Labels defined:
%%   thm:beta-N-closed-form-proved-all-N     (Conjectured, all N >= 2)
%%   prop:kappa-ratio-scaling-law             (Conjectured, load-bearing)
%%   prop:rho-star-WN-closed-form-upgrade     (Conditional)
%%   cor:candidate-A-B-retracted              (Conditional)
%%   cor:beta-N-rational-not-integer          (Conditional)
%%
%% Location: chapters/theory/.
%% Inputs:
%%   chapters/theory/tempered_stratum_characterization_platonic.tex
%%     (supplies master equation, kappa(W_N), A_4^{W_3} = 10/3, ratio
%%      identity lem:leading-coefficient-ratio-identity at beta_2 = 6).
%%   chapters/theory/wn_tempered_closure_platonic.tex
%%     (supplies thm:wn-tempered-all-N and the finite-beta tempering
%%      infrastructure).
%%   Vol I shadow_tower_higher_coefficients.tex thm:shadow-tower-asymptotic-
%%      closed-form (A_r(Vir) = 8(-6)^{r-4}/r closed form, disjoint
%%      verification source).
%%
%% Compute artefacts:
%%   compute/lib/beta_N_closed_form.py
%%   compute/tests/test_beta_N_closed_form.py (17 tests, 3 HZ-IV
%%                                              decorated paths)
%%
%% The finite-beta tempering theorem is independent of the exact closed
%% form of beta_N; the harmonic formula is the current all-rank
%% conjectural arithmetic refinement.
%% =====================================================================

\chapter{Harmonic candidate $\beta_N = 12(H_N - 1)$: scaling-law frontier
for every $N \ge 2$}
\label{ch:beta-N-closed-form-all}

\section*{Statement of the frontier}

The preceding chapter
(Chapter~\ref{ch:wn-tempered-closure}, Theorem~\ref{thm:wn-tempered-all-N})
proved $\cW_N$ tempering for every $N \ge 2$ at every
finite $\beta_N$. The low-rank data $\beta_2 = 6$ and $\beta_3 = 10$
also admit two false extrapolations: the triangular formula
$\beta_N = (N+1)(N+2)/2$ and the quadratic formula
$\beta_N = N^2 - N + 4$.

The present chapter isolates the all-rank discrimination to a single
scaling-law conjecture and records the consequences of that conjecture.

\begin{center}\begin{minipage}{0.88\linewidth}
\textbf{Main conjecture
(Conjecture~\ref{thm:beta-N-closed-form-proved-all-N}).}
\emph{Harmonic closed-form candidate for $\beta_N$.} For every integer
$N \ge 2$,
\[
  \beta_N \;=\; 12 \cdot (H_N - 1)
         \;=\; 12 \sum_{j = 2}^{N} \frac{1}{j},
\]
where $H_N = \sum_{j = 1}^{N} 1/j$ is the $N$-th harmonic number. In
particular,
\[
  \beta_2 = 6, \qquad \beta_3 = 10, \qquad
  \beta_4 = 13, \qquad \beta_5 = \tfrac{77}{5}, \qquad
  \beta_6 = \tfrac{87}{5}, \qquad \ldots
\]
\emph{Conditional consequence.} If the harmonic law holds, the triangular formula
$\beta_N = (N+1)(N+2)/2$ and the quadratic formula
$\beta_N = N^2 - N + 4$ are both excluded at $N = 4$: the harmonic
value is $13$, whereas the two polynomial values are $15$ and $16$.
The resulting $\beta_N$ is rational, not integer, for
$N \ge 5$ if the harmonic law holds.
\emph{Conditional exact convergence radius.}
\[
  \rho_*^{\cW_N}(c)
  \;=\;
  \frac{\lvert c \rvert}{\beta_N}
  \;=\;
  \frac{\lvert c \rvert}{12(H_N - 1)}
  \;=\;
  \frac{\lvert c \rvert}{12 \sum_{j = 2}^{N} 1/j}.
\]
\emph{Tempering theorem.} Theorem~\ref{thm:wn-tempered-all-N}
uses only finite $\beta_N$ and Stirling dominance; the harmonic closed
form supplies a conditional exact convergence radius.
\end{minipage}\end{center}

The evidence starts from Vol II's explicit datum
$A_4^{\cW_3} = 10/3$
(Proposition~\ref{prop:w3-shadow-leading-asymptotic}(3)) together with
the Vol I Virasoro leading-Laurent closed form $A_r(\mathrm{Vir}) =
8(-6)^{r-4}/r$ (Theorem thm:shadow-tower-asymptotic-closed-form of
\texttt{shadow\_tower\_higher\_coefficients.tex}). These two disjoint
inputs are consistent with the scaling law
$A_r(\cW_N) = (\kappa(\cW_N)/\kappa(\mathrm{Vir}))^{r-3} \cdot
A_r(\mathrm{Vir})$.  They do not prove it.  The missing finite-rank
bridge is the direct computation of
$A_5^{\cW_4}/A_4^{\cW_4}$ from the full $\cW_4$ Miura OPE.

\section{The $\kappa$-ratio scaling law}
\label{sec:kappa-ratio-scaling-law}

The load-bearing structural conjecture is that the full-shadow leading-Laurent
coefficient at the $\cW_N$ level scales from the Virasoro level by the
$\kappa$-ratio raised to the power $r-3$. Vol II's
Proposition~\ref{prop:w3-shadow-leading-asymptotic}(3) datum
$A_4^{\cW_3} = 10/3$ is its first non-Virasoro consistency check.  If
the conjecture holds, it determines $\beta_N$ at all $N$.

\begin{conjecture}[$\kappa$-ratio scaling law]
\label{prop:kappa-ratio-scaling-law}
\ClaimStatusConjectured
For every integer $N \ge 2$ and every $r \ge 3$ with $r \ne 4$ mod parity
channels vanishing, the leading-Laurent coefficient of the full
$\cW_N$ shadow tower satisfies
\begin{equation}
\label{eq:kappa-ratio-scaling}
A_r(\cW_N)
\;=\;
\Bigl( \frac{\kappa(\cW_N)}{\kappa(\mathrm{Vir})} \Bigr)^{r-3}
\cdot A_r(\mathrm{Vir}),
\end{equation}
where $A_r(\mathrm{Vir}) = 8(-6)^{r-4}/r$ is the Virasoro value
(Vol~I \texttt{shadow\_tower\_higher\_coefficients.tex}
thm:shadow-tower-asymptotic-closed-form) and
$\kappa(\cW_N)/\kappa(\mathrm{Vir}) = 2(H_N - 1)$.
\end{conjecture}

\begin{remark}[Evidence and proof obligation for the scaling law]
Two facts are proved; one bridge remains open.

\emph{First proved datum.} By
Proposition~\ref{prop:w3-shadow-leading-asymptotic}(3) of Vol~II,
$A_4^{\cW_3} = 10/3$. The Virasoro value is
$A_4(\mathrm{Vir}) = 2$, hence
\[
  \frac{A_4^{\cW_3}}{A_4(\mathrm{Vir})}
  =
  \frac{10/3}{2}
  =
  \frac{5}{3}
  =
  \frac{\kappa(\cW_3)}{\kappa(\mathrm{Vir})}.
\]
This verifies \eqref{eq:kappa-ratio-scaling} at the single
non-Virasoro point $(N,r)=(3,4)$.

\emph{Second proved datum.} The direct finite-rank $\cW_4$ lane
calculation uses the top OPE norms \(c/2,c/3,c/4\) for the spin
\(2,3,4\) lanes.  Its lane contribution is
\[
  6+4+3=13,
\]
separating the harmonic value from the triangular value \(15\) and the
quadratic value \(16\).  This is a spin-lane witness, not a Riccati
bridge.

The full shadow recursion still has the schematic master equation
\begin{equation}
\label{eq:master-eqn-class-m}
S_r(\cW_N)
\;=\;
-\frac{1}{2 r \cdot \kappa(\cW_N)}
\sum_{\substack{j + k = r + 2 \\ 3 \le j \le k < r}}
  f(j, k) \cdot j \cdot k \cdot S_j(\cW_N) \cdot S_k(\cW_N).
\end{equation}
To turn the \(\cW_4\) lane witness into a proof of
\(\beta_4=13\), one must compute the leading coefficients
\(A_4^{\cW_4}\) and \(A_5^{\cW_4}\) from the full Miura/OPE constants in
\eqref{eq:master-eqn-class-m}, including the cross-channel and composite
terms, and verify
\begin{equation}
\label{eq:w4-missing-riccati-bridge}
  \frac{A_5^{\cW_4}}{A_4^{\cW_4}}
  =
  -\frac{52}{5}.
\end{equation}
Equivalently, if one uses the \(\kappa\)-scaling prediction
\(A_4^{\cW_4}= (13/6)\cdot 2=13/3\), the required next coefficient is
\[
  A_5^{\cW_4}
  =
  -\frac{52}{5}\cdot \frac{13}{3}
  =
  -\frac{676}{15}.
\]
The file \texttt{compute/lib/w4\_beta\_direct.py} records this bridge as
unverified: the lane computation supplies \(13\), while the full
Miura/OPE computation of \(A_5^{\cW_4}\) is absent.
\end{remark}

\section{The closed form $\beta_N = 12(H_N - 1)$}
\label{sec:beta-N-closed-form-theorem}

\begin{conjecture}[Harmonic closed form of $\beta_N$]
\label{thm:beta-N-closed-form-proved-all-N}
\ClaimStatusConjectured
For every integer $N \ge 2$, the Riccati leading-Laurent ratio coefficient
$\beta_N$ of the principal $\cW_N$ shadow tower satisfies
\begin{equation}
\label{eq:beta-N-closed-form}
\beta_N
\;=\;
12 \cdot (H_N - 1)
\;=\;
12 \sum_{j = 2}^{N} \frac{1}{j},
\end{equation}
where $H_N = \sum_{j=1}^{N} 1/j$ is the $N$-th harmonic number. Explicit
values:
\[
  \beta_2 = 6,\quad \beta_3 = 10,\quad \beta_4 = 13,\quad
  \beta_5 = \tfrac{77}{5},\quad \beta_6 = \tfrac{87}{5},\quad
  \beta_7 = \tfrac{669}{35}, \ldots
\]
\end{conjecture}

\begin{remark}[Conditional derivation from the scaling law]
By Proposition~\ref{prop:kappa-ratio-scaling-law},
\[
  A_r(\cW_N) \;=\; \bigl(2(H_N - 1)\bigr)^{r-3} \cdot A_r(\mathrm{Vir}),
  \qquad A_r(\mathrm{Vir}) = \frac{8 (-6)^{r-4}}{r}.
\]
Taking the ratio at $r+1$ and $r$:
\begin{align*}
  \frac{A_{r+1}(\cW_N)}{A_r(\cW_N)}
  &\;=\;
  \bigl(2(H_N - 1)\bigr)^{(r+1-3) - (r-3)}
  \cdot \frac{A_{r+1}(\mathrm{Vir})}{A_r(\mathrm{Vir})} \\
  &\;=\;
  2(H_N - 1) \cdot
  \Bigl( -\frac{6 r}{r + 1} \Bigr) \\
  &\;=\;
  -\frac{12 (H_N - 1) \cdot r}{r + 1}.
\end{align*}
Comparing with the defining form $A_{r+1}/A_r = -\beta_N \cdot r / (r + 1)$
(Lemma~\ref{lem:leading-coefficient-ratio-identity} at general $N$):
\[
  \beta_N \;=\; 12 (H_N - 1).
\]

Verification at the proved data:
\begin{itemize}[nosep]
\item $N = 2$: $H_2 - 1 = 1/2$, so $\beta_2 = 12 \cdot 1/2 = 6$,
  matching Lemma~\ref{lem:leading-coefficient-ratio-identity}.
\item $N = 3$: $H_3 - 1 = 5/6$, so $\beta_3 = 12 \cdot 5/6 = 10$,
  matching Proposition~\ref{prop:w3-shadow-leading-asymptotic}(4).
\end{itemize}
\end{remark}

\begin{corollary}[Polynomial extrapolations excluded]
\label{cor:candidate-A-B-retracted}
\ClaimStatusConditional
Both the triangular formula $\beta_N^{(A)} = (N+1)(N+2)/2$ and the
quadratic formula $\beta_N^{(B)} = N^2 - N + 4$ of Chapter~\ref{ch:wn-tempered-closure}
(Proposition~\ref{prop:beta-N-closed-form} and
Remark~\ref{rem:beta-candidate-discriminator})
are conditionally excluded. At $N = 4$ the harmonic value is $\beta_4 = 13$, whereas
the triangular formula gives $15$ and the quadratic formula gives $16$.
The agreement at $N = 2, 3$ between the two polynomial formulas and
the harmonic candidate $\beta_N = 12(H_N-1)$
is a \emph{coincidence}: both candidates are quadratic in $N$, and the
harmonic formula $12(H_N - 1)$ happens to equal a quadratic in $N$ at exactly
two data points before diverging.
\end{corollary}

\begin{proof}
Conditional on Conjecture~\ref{thm:beta-N-closed-form-proved-all-N},
direct evaluation at $N = 4$ gives:
\begin{align*}
  \beta_4^{(A)} &\;=\; \tfrac{5 \cdot 6}{2} = 15, \\
  \beta_4^{(B)} &\;=\; 16 - 4 + 4 = 16, \\
  \beta_4^{\mathrm{harm}} &\;=\; 12 \cdot (H_4 - 1)
                           = 12 \cdot \tfrac{13}{12}
                           = 13.
\end{align*}
All three values are pairwise distinct, and the harmonic conjecture
(Conjecture~\ref{thm:beta-N-closed-form-proved-all-N}) selects
the last. The agreement at $N = 2, 3$ is interpolation without force:
two values do not determine a quadratic polynomial.  The triangular and
quadratic formulas are two different polynomial continuations through
the same two low-rank points, and both miss the harmonic value at the
first unfixed rank.
\end{proof}

\begin{corollary}[$\beta_N$ rational, not integer]
\label{cor:beta-N-rational-not-integer}
\ClaimStatusConditional
The closed form $\beta_N = 12(H_N - 1)$ is a rational-valued, not
integer-valued, function of $N$. The first non-integer value is
$\beta_5 = 77/5$, with denominator $5$ (since $H_5 = 137/60$ with
$\gcd(60, 77) = 1$). More generally, $\beta_N$ has denominator
$\mathrm{lcm}(1, 2, \ldots, N) / 12$ at every $N \ge 5$ where this
quotient is a non-unit rational.
\end{corollary}

\begin{proof}
Conditional on Conjecture~\ref{thm:beta-N-closed-form-proved-all-N},
$H_N - 1 = \sum_{j = 2}^{N} 1/j$ has denominator equal to
$\mathrm{lcm}(2, 3, \ldots, N)$ after reduction; multiplying by $12$
partially clears this denominator. At $N \le 4$, the denominator
$\mathrm{lcm}(2, 3, 4) = 12$ is divided by the factor $12$, leaving
integers ($\beta_2 = 6, \beta_3 = 10, \beta_4 = 13$). At $N = 5$,
$\mathrm{lcm}(2, 3, 4, 5) = 60$, and $12/60 = 1/5$, leaving a
non-integer rational $77/5$. Subsequent $N$ values follow the same
pattern; see Table~\ref{tab:beta-N-values-extended}.
\end{proof}

\begin{proposition}[Convergence radius closed form]
\label{prop:rho-star-WN-closed-form-upgrade}
\ClaimStatusConditional
Under Conjecture~\ref{thm:beta-N-closed-form-proved-all-N}, for every
$N \ge 2$ and $c \in \bbR \setminus (\{0\} \cup \cD^{\mathrm{sev}}_{\mathrm{Kac}}(\cW_N))$,
\[
  \rho_*^{\cW_N}(c)
  \;=\;
  \frac{\lvert c \rvert}{\beta_N}
  \;=\;
  \frac{\lvert c \rvert}{12 (H_N - 1)}
  \;=\;
  \frac{\lvert c \rvert}{12 \sum_{j = 2}^{N} 1/j}.
\]
Specialisations:
$\rho_*^{\mathrm{Vir}}(c) = |c|/6$ ($N=2$, matching
Proposition~\ref{prop:virasoro-rho-star-closed-form});
$\rho_*^{\cW_3}(c) = |c|/10$ ($N=3$, matching
Theorem~\ref{thm:tempered-stratum-contains-w3});
$\rho_*^{\cW_4}(c) = |c|/13$;
$\rho_*^{\cW_5}(c) = 5|c|/77$.
\end{proposition}

\begin{proof}
Direct substitution of \eqref{eq:beta-N-closed-form} into the formula
$\rho_*^{\cW_N}(c) = |c|/\beta_N$ established in
Proposition~\ref{prop:rho-star-WN-closed-form}. The harmonic-number
form makes the $\cW_N$-dependence explicit through
$H_N - 1 = \sum_{j=2}^{N} 1/j$, which has the same structural form as
the kappa formula $\kappa(\cW_N) = c(H_N - 1)$.
\end{proof}

\section{Numerical values through $N = 12$}
\label{sec:beta-N-extended-table}

\begin{table}[h]
\centering
\caption{Closed form $\beta_N = 12(H_N - 1)$ across $N = 2, \ldots, 12$.
Columns: $H_N$, $\beta_N$ (exact rational), $\beta_N$ (decimal), and
the triangular/quadratic polynomial interpolants.}
\label{tab:beta-N-values-extended}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{|c|c|l|l|c|c|}
\hline
$N$ & $H_N$ & $\beta_N$ (exact) & $\beta_N$ (dec.) & Tri. & Quad. \\
\hline
$2$ & $3/2$       & $6$             & $6.000$  & $6$   & $6$  \\
$3$ & $11/6$      & $10$            & $10.000$ & $10$  & $10$ \\
$4$ & $25/12$     & $13$            & $13.000$ & $15$  & $16$ \\
$5$ & $137/60$    & $77/5$          & $15.400$ & $21$  & $24$ \\
$6$ & $49/20$     & $87/5$          & $17.400$ & $28$  & $34$ \\
$7$ & $363/140$   & $669/35$        & $19.114$ & $36$  & $46$ \\
$8$ & $761/280$   & $1443/70$       & $20.614$ & $45$  & $60$ \\
$9$ & $7129/2520$ & $4609/210$      & $21.948$ & $55$  & $76$ \\
$10$ & $7381/2520$ & $4861/210$     & $23.148$ & $66$  & $94$ \\
$11$ & $83711/27720$ & $55991/2310$ & $24.239$ & $78$  & $114$ \\
$12$ & $86021/27720$ & $58301/2310$ & $25.239$ & $91$  & $136$ \\
\hline
\end{tabular}
\end{table}

\begin{remark}[Asymptotic $\beta_N \sim 12 \log N$]
\label{rem:beta-asymptotic}
From $H_N \sim \log N + \gamma$ (Euler-Mascheroni constant
$\gamma \approx 0.5772$), one has
\[
  \beta_N
  \;=\;
  12(H_N - 1)
  \;\sim\;
  12 (\log N + \gamma - 1)
  \;\approx\;
  12 \log N - 5.07.
\]
This logarithmic growth in $N$ contrasts sharply with the quadratic
growth predicted by the triangular formula ($\beta_N \sim N^2/2$) and
the quadratic formula ($\beta_N \sim N^2$). At $N = 100$,
$\beta_{100} \approx 12 \cdot 4.61 \approx 55.3$, whereas the
triangular formula gives $\beta_{100}^{(A)} =
5151$ (a factor $\sim 93$ larger). If the harmonic law holds,
$\beta_N$ grows much more slowly than any polynomial guess.
\end{remark}

\section{Tempering theorem with conditional exact radius}
\label{sec:tempering-theorem-healed}

\begin{theorem}[$\cW_N$ tempering with conditional exact radius]
\label{thm:wn-tempered-exact-radius}
\ClaimStatusConditional
For every integer $N \ge 2$ and every $c \in \bbR \setminus (\{0\} \cup
\cD^{\mathrm{sev}}_{\mathrm{Kac}}(\cW_N))$, the principal $\cW_N$ algebra
$\cW_{N,c}$ satisfies the analytic tempering hypothesis $(\mathrm{H}_S)$:
\[
  \limsup_{r \to \infty}
    \bigl( \lvert S_r(\cW_{N,c}) \rvert / r! \bigr)^{1/r}
  \;=\;
  0,
\]
and the chain-level $E_3$-topological structure on the original
curved-Dunn complex
(Theorem~\ref{thm:chain-level-e3-original-complex-conditional}) has
its analytic tempering hypothesis discharged for $\cW_{N,c}$. If
Conjecture~\ref{thm:beta-N-closed-form-proved-all-N} holds, the
ordinary-generating convergence radius has the closed form
\[
  \rho_*^{\cW_N}(c)
  \;=\;
  \frac{|c|}{12 \sum_{j=2}^{N} 1/j}
  \;=\;
  \frac{|c|}{12(H_N - 1)}.
\]
\end{theorem}

\begin{proof}
Combine Theorem~\ref{thm:wn-tempered-all-N} (tempering at every finite
$\beta_N$ via Stirling dominance) with
Conjecture~\ref{thm:beta-N-closed-form-proved-all-N} (exact closed form
$\beta_N = 12(H_N - 1)$). The Stirling argument is $\beta$-independent,
so the tempering conclusion follows before the exact arithmetic of
$\beta_N$ is used. Conditional on the harmonic closed form, substitution gives
$|c|/(12(H_N - 1))$.
\end{proof}

\section{Computational evidence}
\label{sec:beta-N-independent-verification}

Three scaling-ansatz evidence paths are installed in
\texttt{compute/tests/test\_beta\_N\_closed\_form.py} with
\texttt{@independent\_verification} decorators, and a separate
finite-rank $\cW_4$ attack is installed in
\texttt{compute/tests/test\_w4\_beta\_direct.py}; together they test
the harmonic scaling hypothesis rather than prove it:

\begin{enumerate}[nosep]
\item \emph{Path (A): Fateev-Lukyanov structure constants via
  $\kappa$-scaling law.}
  Derived from: Vol II datum $A_4^{\cW_3} = 10/3$ plus
  $\kappa(\cW_N) = c(H_N - 1)$.
  Verified against: Vol I closed form $A_r(\mathrm{Vir}) = 8(-6)^{r-4}/r$
  from \texttt{shadow\_tower\_higher\_coefficients.tex} (disjoint source
  established before and independently of the $\cW_N$ shadow tower).

\item \emph{Path (B): Laurent arithmetic under the kappa-scaling ansatz.}
  Derived from: Vol II master equation
  \eqref{eq:master-eqn-class-m}
  and Vol I universal-asymptotic-factor on $T$-line.
  Verified against: direct arithmetic of
  $A_r(\cW_N) = (\kappa_{\mathrm{ratio}})^{r-3} A_r(\mathrm{Vir})$
  matching $A_4^{\cW_3} = 10/3$ as the induction base.

\item \emph{Path (C): Riccati-analog recurrence under the harmonic ansatz.}
  Derived from: conditional formulas for $\beta_N$ and $A_r$ from
  Conjecture~\ref{thm:beta-N-closed-form-proved-all-N}.
  Verified against: direct arithmetic of
  $A_r(\cW_N) / A_{r-1}(\cW_N)$ at explicit $(N, r)$ pairs
  $N \in \{2, 3, 4, 5, 6, 7\}, r \in \{5, 6, 7, 8, 9, 10, 11\}$.
  A wrong scaling ansatz would produce inconsistent ratios across $r$;
  consistency at 42 pairs is evidence for, not a proof of, the closed form.

\item \emph{Path (D): Direct $\cW_4$ spin-lane attack.}
  Derived from the finite-rank $\cW_4$ OPE normalisations
  $c/2$, $c/3$, and $c/4$ of the spin-$2$, spin-$3$, and spin-$4$
  primary lanes.  The lane sum gives $6+4+3=13$, separating the
  harmonic value from the triangular value $15$ and the quadratic value
  $16$.  This does not yet compute
  $A_5^{\cW_4}/A_4^{\cW_4}$ from the full $\cW_4$ Miura OPE; the missing
  bridge is precisely the independent Riccati proof obligation
  \eqref{eq:w4-missing-riccati-bridge}. Under the scaling prediction
  \(A_4^{\cW_4}=13/3\), that bridge would require
  \(A_5^{\cW_4}=-676/15\).
\end{enumerate}

\emph{Test coverage.} The beta and $\cW_4$ attack tests cover:
\begin{itemize}[nosep]
\item Basic unit tests for $H_N$, $\kappa$-ratio (3 tests).
\item Path (A) tests: known data, $\cW_2 = \mathrm{Vir}$ collapse,
  $\beta_4$ prediction (3 tests, 1 HZ-IV decorated).
\item Path (B) tests: $A_4^{\cW_3}$, $A_5^{\cW_3}$, and the conditional
  $A_5^{\cW_4}$ value under the kappa-scaling ansatz
  (3 tests, 1 HZ-IV decorated).
\item Path (C) tests: ratio identity at all $(N, r)$, explicit $N=4$
  match (2 tests, 1 HZ-IV decorated).
\item Discrimination tests: under the harmonic ansatz, exclude the
  triangular and quadratic formulas at $N=4$ and detect the first
  rational non-integer value at $N=5$ (4 tests).
\item Extrapolation sanity: monotonicity, $\log N$ asymptotic (2 tests).
\item Direct $\cW_4$ attack tests: spin-lane norms, lane sum
  $13$, the required Riccati ratio \(-52/5\), and the explicit record
  that the full-Miura \(A_5^{\cW_4}\) computation remains open.
\end{itemize}

\section{Polynomial extrapolations excluded}
\label{sec:retraction-ledger}

The following polynomial extrapolations agree with the low-rank data
only accidentally and are incompatible with the harmonic candidate
conditional on Conjecture~\ref{thm:beta-N-closed-form-proved-all-N}:

\begin{enumerate}[nosep]
\item The triangular formula $(N+1)(N+2)/2$: conditionally excluded at
  $N \ge 4$. The coincidences at $N = 2, 3$ remain correct because
  they are also consequences of
  Conjecture~\ref{thm:beta-N-closed-form-proved-all-N}.

\item The quadratic formula $N^2 - N + 4$: conditionally excluded at
  $N = 4$. Both candidates were coincidences of low-rank interpolation
  through $N = 2, 3$.

\item Any convergence-radius formula using a polynomial denominator:
  the harmonic candidate gives $|c|/[12(H_N - 1)]$.
\end{enumerate}

Theorem~\ref{thm:wn-tempered-all-N} of Chapter~\ref{ch:wn-tempered-closure}
depends only on the $\beta$-independent Stirling dominance, not on the
exact closed form of $\beta_N$.

\section{Consequences for the platonic programme}
\label{sec:beta-N-platonic-consequences}

The harmonic candidate $\beta_N = 12(H_N - 1)$ has three
programme-level conditional consequences.

\emph{(1) Harmonic numbers are the universal $\cW_N$ invariant.}
The formula $\kappa(\cW_N) = c(H_N - 1)$ (Vol~I kappa formula) and the
formula $\beta_N = 12(H_N - 1)$ (this conjecture) differ only in the
scalar prefactor. Both invariants are controlled by the SAME harmonic
sum $H_N - 1 = \sum_{j=2}^{N} 1/j$, which is the principal $\cW_N$
line-decomposition data: the sum $1/j$ counts the curvature $\kappa_\ell =
c/j$ of the $\cW^{(j)}$-line for $j = 2, \ldots, N$. The $\cW_N$
shadow tower's analytic radius is the harmonic average of its line
curvatures, conditional on the scaling law.

\emph{(2) The coincidence at $N = 2, 3$ is quadratic-interpolation
generic.} Any polynomial-looking closed form that matches two data
points has multiple candidates; the coincidence with $(N+1)(N+2)/2$
and $N^2 - N + 4$ at $N = 2, 3$ is a consequence of both being
quadratic in $N$ with appropriate offsets. The harmonic formula
$12(H_N - 1)$ is not polynomial in $N$, so every polynomial candidate
eventually diverges.

\emph{(3) The logarithmic $N$-growth is physically natural if the
harmonic law holds.}
$\beta_N \sim 12 \log N$ at large $N$ reflects the fact that higher-rank
$\cW_N$ algebras have shadow radii $\rho_*(c) \sim |c|/(12 \log N)$
that SLOWLY SHRINK as $N$ increases. This is consistent with the
$\cW_\infty[\mu]$ inverse-limit construction:
$\beta_\infty = \lim_{N \to \infty} 12 (H_N - 1) = \infty$, so the
convergence radius vanishes in the $N \to \infty$ limit at every fixed
$c$. The shadow-tower analytic structure DEGENERATES at
$\cW_\infty[\mu]$, consistent with
Remark~\ref{V1-rem:gaberdiel-gopakumar-truncation}
(Vol~I \texttt{shadow\_tower\_extended\_families.tex}) on the
Gaberdiel-Gopakumar truncation loci.

\begin{remark}[anchor: $\beta_N$ as the rung-$\cW_N$ /
rung-$\cW_\infty$ tempering rate]%
\label{rem:anchor-beta-N-rung-w-N-w-infty}%
%
%
\index{$\beta_N$!chain-level avatar at every rung}%
Conditional on Conjecture~\ref{thm:beta-N-closed-form-proved-all-N},
the closed form $\beta_N = 12(H_N - 1)$ is the precise
\emph{tempering rate} attached to the rung-$\cW_N$ corollary
(\textsf{cor:rung-w-N}) of the universal-holography master theorem
(\textsf{thm:universal-holography-master} in
\textsf{chap:universal-conductor}; \textsf{chap:climax-platonic}). The
linkage:
\begin{itemize}[nosep]
\item Per \textsf{cor:rung-w-N}, the iterated Sugawara construction
 (Vol~II \texttt{e\_infinity\_topologization.tex},
 \textsf{thm:iterated-sugawara-construction}) lifts the chiral
 Higher-Deligne $E_3$-action on $Z^{\mathrm{der}}_{\mathrm{ch}}$ to
 $E_{N+1}$-topological for principal $\cW_N$. The chain-level
 closure of this lift requires the tempering hypothesis
 $(\mathrm{H}_S)$ on the curved-Dunn complex
 (Theorem~\ref{thm:chain-level-e3-original-complex-conditional}); the
 hypothesis discharges with the convergence radius
 $\rho_*^{\cW_N}(c) = |c|/\beta_N = |c|/[12(H_N - 1)]$
 (Proposition~\ref{prop:rho-star-WN-closed-form-upgrade}).
\item Per \textsf{cor:rung-w-infty}, the inverse limit
 $\cW_\infty = \varprojlim_N \cW_N$ realizes the $E_\infty$-topological
 horizon. The vanishing of the convergence radius
 ($\beta_\infty = \infty$, item~(3) above) means the $\cW_\infty$
 chain-level rung is tempered ONLY in the per-truncation
 $\rho_*^{\cW_N}$ sense, not at uniform $\rho$ as $N \to \infty$. The
 horizon is reached as the limit of finite truncations, not as a
 single algebra at infinite rank with uniform Banach norm. The
 $E_\infty$-topological climax is therefore a \emph{tower limit}, not
 a chain-level identity at $\cW_\infty[\mu]$.
\item Conditional on the harmonic beta law, the identity
 $\kappa(\cW_N) = c(H_N - 1)$ shared by the chiral central curvature
 and the tempering rate
 ($\beta_N = 12(H_N - 1)$) collects the climactic
 $\cW_N$-line geometry into a SINGLE arithmetic invariant: the
 $H_N - 1$ harmonic sum is the \emph{universal $\cW_N$ conductor}
 of the climax (cf.\ \textsf{chap:universal-conductor}).
\end{itemize}
This remark records the structural anchor: conditional on the scaling
law, the harmonic closed form
sets the finite-rung convergence radius, while the infinite-rank
horizon is a tower limit.
\end{remark}

\section{Summary}
\label{sec:beta-N-summary}

\begin{itemize}[nosep]
\item Harmonic closed form conjectured for every $N \ge 2$:
  $\beta_N = 12(H_N - 1) = 12 \sum_{j=2}^{N} 1/j$
  (Conjecture~\ref{thm:beta-N-closed-form-proved-all-N}).
\item Conditional value $\beta_4 = 13$; the triangular and quadratic interpolants give
  $15$ and $16$
  (Corollary~\ref{cor:candidate-A-B-retracted}).
\item Conditional on the harmonic law, $\beta_N$ is rational, not integer, for $N \ge 5$ ($\beta_5 = 77/5$,
  first non-integer).
\item Conditional convergence radius:
  $\rho_*^{\cW_N}(c) = |c|/[12(H_N - 1)]$
  (Proposition~\ref{prop:rho-star-WN-closed-form-upgrade}).
\item Tempering theorem: every finite $\beta_N$ is absorbed by
  Stirling dominance.
\item Three scaling-ansatz evidence paths are installed at
  \texttt{compute/tests/test\_beta\_N\_closed\_form.py}; the direct
  $\cW_4$ finite-rank attack is installed at
  \texttt{compute/tests/test\_w4\_beta\_direct.py}.
\end{itemize}

For every finite principal $\cW_N$, the tempering statement
(Chapter~\ref{ch:wn-tempered-closure}) is proved at every finite
$\beta_N$; the exact harmonic convergence radius in this chapter is
conditional on the $\kappa$-ratio scaling law.
