\section{BV-BRST construction}
\label{sec:BV_construction}
\label{ch:bv-construction}

The bridge theorem (Theorem~\ref{thm:physics-bridge}) identifies the
BV-BRST data of a 3d~HT theory on $\C_z \times \R_t$ with a
logarithmic $\SCchtop$-algebra only after the product HT gauge,
factorized logarithmic parametrix, one-loop finiteness, and
product-polynomial interaction hypotheses have been verified. Under
those hypotheses the prefactorization algebra
$U \mapsto \mathsf{Obs}(U)$ produces the open factorization category,
and the quantum master equation
\begin{equation}
\label{eq:QME-bv-construction}
\hbar\,\Delta_{\mathrm{BV}}\, S_{\mathrm{eff}} + \tfrac{1}{2}\{S_{\mathrm{eff}}, S_{\mathrm{eff}}\}_{\mathrm{BV}} = 0
\end{equation}
becomes the open/closed Maurer--Cartan equation.

\begin{remark}[The $\hbar$ convention and the quantum-group bridge]
\label{rem:bv-hbar-convention}
Throughout this chapter, $\hbar$ is the formal expansion parameter of the BV
quantization with $|\hbar|=0$ and $\hbar\Delta_{\mathrm{BV}}$ adding the loop
expansion to the classical antibracket $\tfrac12\{S,S\}$. This is the Costello
convention~\cite{CG17}: the QME~\eqref{eq:QME-bv-construction} reduces at
$\hbar=0$ to the classical master equation $\{S,S\}=0$. Elsewhere in the
manuscript the spectral parameter $\hbar$ appears in
$R(z) = \exp(r(z)) = 1 + \hbar\,r(z) + O(\hbar^2)$: the quantum-group $\hbar$
\emph{is} the BV $\hbar$ when both are computed from the same boundary
chiral algebra. No $\pi i$ factor appears in the BV $\hbar$; the $2\pi i$
convention enters only in residue evaluations of weight forms over
$\FM_k(\C)$ via $\frac{1}{2\pi i}\oint$.
\end{remark}

\begin{remark}[The bar complex IS the BV complex]
\label{rem:bar-equals-BV-bridge}
For the boundary chiral algebra $A_\partial$ of a 3d HT theory satisfying
Theorem~\ref{thm:physics-bridge}, the chiral bar complex
$\barB^{\mathrm{ch}}(A_\partial) = T^c(s^{-1}\bar A_\partial)$
\emph{coincides} with the BV-BRST complex
$\Obs_{\mathrm{bulk}} = (\widehat{\Sym}(\mathcal E^\vee), Q_{\mathrm{BRST}})$
of the bulk theory at the level of derived equivalence: the bar
differential $d_{\overline B}$ from OPE residues on $\FM_k(\C)$ matches
$Q_{\mathrm{BRST}} = \{S_{\mathrm{eff}}, -\}_{\mathrm{BV}} +
\hbar\Delta_{\mathrm{BV}}$ via the Drinfeld--Sokolov/Hochschild bridge
(Theorem~\ref{thm:chd-ds-hochschild} of
\S\ref{sec:chiral_hochschild_expanded}), and this identification is the
chain-level upgrade of the universal-holography master theorem
(Theorem~\ref{thm:universal-holography-master}, the Volume~II climax in
the 3d quantum-gravity part).
The Koszul conductor $K = -c_{\mathrm{ghost}}(\mathrm{BRST})$ from the
Volume~I universal-conductor theorem equals the level shift controlling
the QME at one loop: $\kappa(A_\partial) + \kappa(A_\partial^!) = K$ in the
scalar channel, with the ghost central charge absorbing the matter
complementarity. The QME \eqref{eq:QME-bv-construction} is therefore the
chain-level incarnation of $D_A\Theta_A + \tfrac12[\Theta_A, \Theta_A] = 0$
on the bar side: open (BV) and closed (modular Maurer--Cartan) faces of
the same Maurer--Cartan datum.
\end{remark}

\begin{remark}[BV $=$ bar scope: class G/L proved, class C/M conditional]
\label{rem:bv-equals-bar-scope}
The chain-level identification $(\Obs_{\mathrm{bulk}}, Q_{\mathrm{BRST}})
\simeq (\barB^{\mathrm{ch}}(A_\partial), d_{\overline B})$ is \emph{proved
unconditionally} for the abelian--Sugawara class~G (Heisenberg, lattice)
and the affine Kac--Moody class~L at non-critical level via the explicit
homotopy transfer~\cite{CG17}*{Theorem~5.2.2.1} of
\S\ref{subsec:analytic} Step~4. For the symplectic bosons /
$\beta\gamma$ class~C and the Virasoro / $W_N$ class~M, the
identification is \emph{conditional on the harmonic-decoupling
property}: the BV propagator must split into a holomorphic kernel and a
topological kernel without cross-coupling at the harmonic component, an
analytic hypothesis verified for class G/L from the explicit
Wakimoto / free-field realisation but only conjectural for class C/M at
chain level. The \emph{cohomological} identification
$H^\bullet(\Obs_{\mathrm{bulk}}) \simeq
H^\bullet(\barB^{\mathrm{ch}}(A_\partial))$ holds for all four classes
via the Drinfeld--Sokolov/Hochschild bridge
(Theorem~\ref{thm:chd-ds-hochschild}); the chain-level upgrade for class
C/M is closed in the weight-completed category by
Proposition~\ref{prop:bv-bar-class-m-weight-completed}. The
QME~\eqref{eq:QME-bv-construction} is the open form;
$D_A\Theta_A + \tfrac12[\Theta_A, \Theta_A] = 0$ is the closed form. Both
are the same Maurer--Cartan element under the bar/BV identification on
the proved scope (G/L) and on the conditional scope (C/M) in the
weight-completed category.
\end{remark}

\subsection{Field content, action, and BV data}
\label{subsec:BV-data}
Fix a 3d HT theory on $\R_t\times \C_z$ with graded field space~$\Phi$ (fields, ghosts, antifields), classical action $S_{\mathrm{cl}}[\Phi]$, and BRST operator $Q$ of degree $+1$. The classical action satisfies the classical master equation $\{S_{\mathrm{cl}},S_{\mathrm{cl}}\}_{\mathrm{BV}}=0$; the perturbative quantisation produces an effective action $S_{\mathrm{eff}}$ satisfying the quantum master equation $\hbar\Delta_{\mathrm{BV}} S_{\mathrm{eff}} + \tfrac{1}{2}\{S_{\mathrm{eff}}, S_{\mathrm{eff}}\}_{\mathrm{BV}} = 0$, from which the $A_\infty$ operations are extracted. Work perturbatively about a translation-invariant background.

\begin{definition}[Local observables]
\label{def:local-obs}
For an open $U\subset \R\times\C$, define $\mathsf{Obs}(U)$ as the completed symmetric algebra $\widehat{\operatorname{Sym}}(\mathcal{E}^\vee)$ of distributional sections of the dual field bundle, equipped with the BV differential $Q_{\mathrm{BRST}}$ and the BV antibracket. The renormalized time-ordered product $\star_U$ is built from the propagator and interaction vertices via the standard perturbative expansion (see e.g.\ \cite{CG17}).
\end{definition}

\subsection{Proof of Theorem~\ref{thm:physics-bridge}}
\label{subsec:analytic}

\begin{proposition}[Prefactorization structure; \ClaimStatusProvedHere]
\label{prop:prefact-Obs}
Under the conditions of Theorem~\ref{thm:physics-bridge}, $U\mapsto \mathsf{Obs}(U)$ is a logarithmic $\SCchtop$-algebra (Definition~\ref{def:log-SC-algebra}).
\end{proposition}

\begin{proof}

\medskip\noindent\textbf{Step 1: Classical master equation.}
The BV data provides $({\mathcal F}, S, \{-,-\}_{\mathrm{BV}}, \Delta_{\mathrm{BV}})$: a $(-1)$-symplectic graded space of fields ${\mathcal F}$ on $\R\times\C$, a local action functional $S\in{\mathcal O}({\mathcal F})$ satisfying the quantum master equation $\hbar\Delta_{\mathrm{BV}}S + \tfrac{1}{2}\{S,S\}_{\mathrm{BV}}=0$, and the BRST differential $Q_{\mathrm{BRST}} = \{S,-\}_{\mathrm{BV}} + \hbar\Delta_{\mathrm{BV}}$ with $Q_{\mathrm{BRST}}^2=0$. HT gauge fixing selects a Lagrangian complement to the gauge orbits compatible with the product structure $\R\times\C$, and one-loop finiteness~\cite{GRW21} ensures that the BV Laplacian $\Delta_{\mathrm{BV}}$ acting on local functionals produces well-defined operators without UV counterterms. For each open $U\subset \R\times\C$, the cochain complex $(\Obs(U), Q_{\mathrm{BRST}})$ is therefore well-defined.

\medskip\noindent\textbf{Step 2: Propagator.}
The kinetic operator $Q = \dbar + d_t$ determines the propagator $G(z_1-z_2;\, t_1-t_2)$ obtained from the gauge-fixed kinetic term. Meromorphicity in $z$ with a simple pole at $z_1=z_2$ ensures that correlators are rational functions of the holomorphic insertion points, with singularities governed by the OPE. (For tree-level diagrams, rationality follows from iterating the Cauchy integral; for loop diagrams, the one-loop finiteness condition ensures convergence, and the Hartogs extension principle gives rationality on the complement of the collision loci.) Exponential decay $|G|\le C\,e^{-\mu|t_1-t_2|}$ in the topological direction ensures absolute convergence of loop integrals over ordered intervals in $\R$. Translation invariance guarantees that the resulting operations depend only on relative positions.

\medskip\noindent\textbf{Step 3: Factorization structure maps.}
Let $U_1,\ldots,U_n \subset \R\times\C$ be pairwise disjoint opens contained in a larger open $V$. The factorization product
\[
 \mu_{U_1,\ldots,U_n}^V \;:\;
 \Obs(U_1)\otimes \cdots \otimes \Obs(U_n)
 \;\longrightarrow\;
 \Obs(V)
\]
is defined by the renormalized time-ordered product: given observables ${\mathcal O}_i\in\Obs(U_i)$ supported in $U_i$, the product $\mu({\mathcal O}_1\otimes\cdots\otimes{\mathcal O}_n)$ is computed by the sum over Feynman diagrams with vertices at the insertion points and internal edges weighted by the propagator $G$. Since the $U_i$ are disjoint, propagators connecting different opens have non-coincident holomorphic arguments $z_j\ne z_k$, so the meromorphic singularity in $G$ is never encountered, and the exponential decay in $t$ gives convergence of the integrals over the topological separations. The BRST compatibility $Q_{\mathrm{BRST}}\circ\mu = \mu\circ Q_{\mathrm{BRST}}^{\otimes n}$ follows from the quantum master equation.

\medskip\noindent\textbf{Step 4: Convergence via FM compactification.}
When insertions approach coincidence, $\FM_k(\C)$ resolves the singularities. The weight forms extend to logarithmic forms $\omega_k^{\mathrm{hol}}\in\Omega^\bullet_{\log}(\FM_k(\C))$, which are integrable on the compact space $\FM_k(\C)$. The factored structure $\omega_k = \omega_k^{\mathrm{hol}}\wedge\omega_k^{\mathrm{top}}$ with $\omega_k^{\mathrm{top}}\in C_\bullet(\Conf_k(\R))$ means the integrals converge separately in each direction. By Theorem~\ref{thm:Arnold_full_proof} (Appendix~\ref{app:FM_Stokes}), codimension-2 corner contributions cancel via the Arnold--Orlik--Solomon relations, so Stokes' theorem on $\FM_k(\C)$ (a manifold with corners) yields well-defined renormalized products. Any ambiguity in the renormalization scheme is $Q_{\mathrm{BRST}}$-exact: two choices of propagator $G, G'$ with the same boundary conditions differ by a smooth kernel $H = G - G'$, and the resulting change in each $m_k$ is a $Q_{\mathrm{BRST}}$-coboundary by the homotopy transfer formula \cite[Theorem~5.2.2.1]{CG17}. The quasi-isomorphism class of $(\Obs(U), Q_{\mathrm{BRST}})$ is therefore independent of the renormalization scheme.

\medskip\noindent\textbf{Step 5: Swiss-cheese structure.}
The factorization products assemble into the two-colored operad $\SCchtop$. The holomorphic insertions are governed by $\FM_k(\C)$: the boundary strata of the FM compactification encode the operadic composition maps $\gamma_{\mathrm{ch}}$ of the closed color, recording how clusters of holomorphic points collide. The topological insertions are governed by $E_1(m) \cong \Conf_m(\R)$: the ordered-interval structure of configurations on $\R$ provides the operadic composition $\gamma_{\mathrm{top}}$ of the open color. The factorization maps $\mu^V_{U_1,\ldots,U_n}$ on rectangles $D_i\times I_j$ (disks in $\C$, intervals in $\R$) are therefore controlled by the insertion maps of $\FM_k(\C)\times E_1(m)$, which are precisely the spaces of operations of $\SCchtop$. The no-open-to-closed constraint is automatic: by Definition~\ref{def:SC-operations}(i), $\SCchtop(\ldots,\mathrm{top},\ldots;\,\mathrm{ch})=\varnothing$ whenever any input carries the open color. Concretely, a closed-output operation requires all inputs to be holomorphic insertions parametrized by $\FM_k(\C)$; no topological (interval-ordered) input can appear. This encodes the physical directionality that bulk observables restrict to the boundary but boundary data does not extend to the bulk.

\medskip\noindent\textbf{Conclusion.}
The assignment $U\mapsto (\Obs(U), Q_{\mathrm{BRST}})$ with the factorization products $\mu^V_{U_1,\ldots,U_n}$ satisfies the axioms of a holomorphic--topological prefactorization algebra: isotopy invariance along $\R$ follows from local constancy (the propagator depends on $t$ only through a step function or exponential kernel), and holomorphic dependence on $\C$-positions follows from the meromorphicity of $G$. On rectangles $D\times I$ the structure is locally constant, as claimed.
\end{proof}

\begin{remark}[Lagrangian interpretation]
\label{rem:lagrangian-geometry}
The product decomposition of Definition~\ref{def:log-SC-algebra} admits a
uniform geometric interpretation via Pantev--To\"en--Vaqui\'e--Vezzosi
shifted symplectic geometry. The logarithmic $\SCchtop$-algebra structure
encodes a Lagrangian self-intersection
$\mathfrak{S}_b := \mathcal{L} \times_{\mathcal{M}} \mathcal{L}$
as a $(-1)$-shifted symplectic derived stack:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The BV antibracket is analogous to a $(-2)$-shifted symplectic
 structure on a derived moduli $\mathcal{M}_{\mathrm{vac}}$
 of vacua, with the quantum master equation playing the
 role of the closure condition $d\omega_{-2}=0$.
\item The product decomposition $\omega_k = \omega_k^{\mathrm{hol}} \otimes \omega_k^{\mathrm{top}}$
 reflects the decomposition of the self-intersection $\mathfrak{S}_b$: the
 $(-1)$-shifted symplectic structure splits into a holomorphic Poisson bracket
 (from $\FM_k(\C)$) and an associative product (from $\Conf_k(\R)$),
 recovering the two colors of $\SCchtop$.
\item The Fulton--MacPherson compactification (Theorem~\ref{thm:FM-calculus})
 provides the proper resolution of collision strata, identified with
 Lagrangian intersection strata.
\end{enumerate}
The Steinberg presentation (Theorem~\ref{thm:steinberg-presentation})
formalises this: the self-intersection data of $\mathcal{L}$ determines the
algebra structure.
\end{remark}

\subsection{From prefactorization to $W(\mathsf{SC}^{\mathrm{ch,top}})$--algebra}
\label{subsec:from-prefact}
\begin{theorem}[Swiss--cheese algebra of observables; \ClaimStatusProvedHere]
\label{thm:Obs-is-SC}
Under the conditions of Theorem~\ref{thm:physics-bridge}, the BV observable prefactorization algebra $\mathsf{Obs}$ is a logarithmic $\SCchtop$-algebra (Definition~\ref{def:log-SC-algebra}), functorial with respect to quasi-isomorphisms of HT theories.
\end{theorem}

\begin{proof}
Proposition~\ref{prop:prefact-Obs} verifies the product decomposition; Theorem~\ref{thm:recognition-SC} supplies the $C_\ast(W(\SCchtop))$-algebra structure.
\end{proof}

\subsection{Higher operations via configuration--space integrals}
\label{subsec:mk-integrals}

The $W(\SCchtop)$-algebra structure on $\mathsf{Obs}$ is abstract:
to write the higher products $m_k$ as explicit multilinear operations
on a boundary algebra, one fixes a small rectangle $D \times I$ and
extracts the structure maps from the renormalized time-ordered
product by integrating against configuration-space kernels. The
Stasheff relations these $m_k$ satisfy are then Stokes' theorem on
$\FM_k(\C) \times E_1(m)$.

Write $A:=\mathsf{Obs}(D\times I)$ for a small rectangle. The higher multiplications
\[
m_k : A^{\otimes k}\longrightarrow A((\lambda_1))\cdots((\lambda_{k-1}))
\]
of degree $2-k$ are given by integrating the product of renormalized propagators over $\FM_k(\C)\times E_1(m)$ with suitable log kernels in $\C$ and ordered‑interval data in $\R$; see Section~\ref{sec:FM_calculus}.
The boundary faces yield Stokes' identities matching the $A_\infty$ relations.

\subsection{Well-definedness and sesquilinearity on cohomology}
\label{subsec:well-def-sesqui}

The operations $\eqref{eq:prod-def}$--$\eqref{eq:bracket-def}$ of
Section~\ref{sec:axioms-Ainfty-chiral} descend to cohomology only
if every algebraic check a PVA must satisfy passes: well-definedness
on cohomology classes, sesquilinearity, graded commutativity and
associativity of the product, skewsymmetry and Jacobi for the
bracket, and the Leibniz rule joining them. The next four
subsections verify each in turn; the canonical proofs sit in the
PVA descent chapter and are cited by reference here.

\begin{lemma}[Well-definedness; \ClaimStatusProvedHere]
\label{lem:well-definedness-prod-bracket}
Definitions \eqref{eq:prod-def} and \eqref{eq:bracket-def} are independent of the choice of representatives of $[a]$ and $[b]$.
\end{lemma}

\begin{proof}
Replace $a\mapsto a+Qx$ (and similarly for $b$). The $n=2$ $A_\infty$ identity (Definition~\ref{def:ainfty_chiral}, Equation~\eqref{eq:ainfty-relation-raw} at $n=2$) reads
\[
 \sum_{\substack{i+j=3 \\ i,j\ge 1}}\;\sum_{s=0}^{2-j}
 (-1)^{\epsilon(s,j)}\;
 m_i\bigl(a_1,\dots,a_s,\,m_j(a_{s+1},\dots,a_{s+j}),\,a_{s+j+1},\dots,a_2\bigr) = 0,
\]
where $\epsilon(s,j) = |a_1|+\cdots+|a_s|$ (Koszul sign convention from Section~\ref{subsec:symmetry}).
Expanding: $(i,j)=(1,2)$ gives $s=0$ only, so $\epsilon(0,2)=0$ and the term is $m_1(m_2(a_1,a_2))$; $(i,j)=(2,1)$ gives $s=0$ with $\epsilon(0,1)=0$ yielding $m_2(m_1(a_1),a_2)$, and $s=1$ with $\epsilon(1,1)=|a_1|$ yielding $(-1)^{|a_1|}m_2(a_1,m_1(a_2))$. Writing $Q=m_1$, the identity becomes
\[
 Q\bigl(m_2(a,b)\bigr) + m_2(Qa,b) + (-1)^{|a|}m_2(a,Qb) = 0.
\]
Thus the first two terms have sign $+1$ and the third has sign $(-1)^{|a|}$, as claimed. Setting $a\mapsto a+Qx$ gives $m_2(a+Qx,b) - m_2(a,b) = m_2(Qx,b) = -Q(m_2(x,b)) - (-1)^{|x|}m_2(x,Qb)$, which is $Q$-exact when $b$ is $Q$-closed. The analogous argument applies when replacing $b$. Together with sesquilinearity \eqref{eq:sesqui-left}--\eqref{eq:sesqui-right}, this shows that the variation of $m_2$ is $Q$--exact, hence the classes of $m_2^{\mathrm{reg}}$ and $m_2^{\mathrm{sing}}$ are invariant. Since $Q = m_1$ acts on the algebra elements and does not involve the spectral parameter $\lambda$, it commutes with the Laurent decomposition into regular and singular parts.
\end{proof}

\begin{proposition}[Sesquilinearity on $H$; \ClaimStatusProvedHere]
\label{prop:sesqui-H}
The bracket satisfies the vertex sesquilinearity on cohomology:
\[
\{\partial[a]{}_\lambda [b]\} = -\lambda \{[a]{}_\lambda [b]\},\qquad
\{[a]{}_\lambda \partial[b]\} = (\lambda+\partial)\{[a]{}_\lambda [b]\}.
\]
\end{proposition}

\begin{proof}
Apply \eqref{eq:sesqui-left}–\eqref{eq:sesqui-right} to $m_2$, take regular/singular projections, and pass to cohomology.
\end{proof}

\subsection{Commutativity and associativity of the product}
\label{subsec:comm-assoc}
\begin{lemma}[Graded commutativity; \ClaimStatusProvedElsewhere]
\label{lem:commutative}
$[a]\cdot[b] = (-1)^{|a||b|}[b]\cdot[a]$.
\end{lemma}

\begin{proof}
See Proposition~\ref{prop:product-commutative}; the canonical proof uses the
exchange cylinder construction (Construction~\ref{const:exchange-cylinder}).
\end{proof}

\begin{theorem}[Associativity of the product on cohomology;
\ClaimStatusProvedElsewhere]
\label{thm:assoc}
The product $\cdot$ is associative on $H^\bullet(A,Q)$.
\end{theorem}

\begin{proof}
See Proposition~\ref{prop:product-associative}; the canonical proof uses
the regular--regular projection of the degree-$3$ $A_\infty$ relation.
\end{proof}

\subsection{Skewsymmetry and Jacobi for the bracket}
\label{subsec:skew-Jacobi}
\begin{proposition}[Skewsymmetry; \ClaimStatusProvedElsewhere]
\label{prop:skewsym}
$\{[a]{}_\lambda [b]\} = -(-1)^{(|a|+1)(|b|+1)}\{[b]{}_{-\lambda-\partial} [a]\}$.
\end{proposition}

\begin{proof}
See Proposition~\ref{prop:PVA2_proof}; the canonical proof uses the
exchange cylinder in the singular sector plus the Borel transform
$\zeta\mapsto\lambda$.
\end{proof}

\begin{theorem}[Jacobi identity; \ClaimStatusProvedElsewhere]
\label{thm:Jacobi-PVA}
\label{thm:Jacobi-bv}
For all $[a],[b],[c]\in H^\bullet(A,Q)$,
\[
\{[a]{}_\lambda \{[b]{}_\mu [c]\}\} - (-1)^{(|a|+1)(|b|+1)} \{[b]{}_\mu \{[a]{}_\lambda [c]\}\} = \{\{[a]{}_\lambda [b]\}{}_{\lambda+\mu} [c]\}.
\]
\end{theorem}

\begin{proof}
See Theorem~\ref{thm:Jacobi} in Section~\ref{sec:PVA_descent}; the
canonical proof uses the full three-face singular--singular Stokes
argument on $\FM_3(\C)$ with Arnold--Orlik--Solomon corner cancellation.
\end{proof}

\subsection{Leibniz rule}
\label{subsec:Leibniz}
\begin{theorem}[Leibniz rule; \ClaimStatusProvedElsewhere]
\label{thm:Leibniz-PVA}
\label{thm:Leibniz-bv}
For all $[a],[b],[c]\in H^\bullet(A,Q)$,
\[
\{[a]{}_\lambda ([b]\cdot [c])\} = \{[a]{}_\lambda [b]\}\cdot [c] + (-1)^{(|a|+1)|b|}\,[b]\cdot \{[a]{}_\lambda [c]\}.
\]
\end{theorem}

\begin{proof}
See Proposition~\ref{prop:PVA3_proof} in Section~\ref{sec:PVA_descent};
the canonical proof uses the mixed regular--singular three-face Stokes
projection on $\FM_3(\C)$.
\end{proof}

\begin{corollary}[PVA on cohomology; \ClaimStatusProvedElsewhere]
\label{cor:PVA-cohomology-bv}
\label{cor:PVA-structure-bv}
The operations \eqref{eq:prod-def}–\eqref{eq:bracket-def} define a $(-1)$–shifted Poisson vertex algebra structure on $H^\bullet(A,Q)$. The degree shift arises not from the degree of $m_2$ itself ($|m_2| = 2-2 = 0$) but from the bar desuspension: the operations $m_k$ are components of a degree-$+1$ coderivation on $T^c(s^{-1}\bar A)$, and the desuspension $s^{-1}$ produces the Koszul sign $(-1)^{(|a|+1)(|b|+1)}$ for the $\lambda$-bracket, which is the sign convention of a $(-1)$-shifted Lie bracket.
\end{corollary}

\begin{remark}[Transition to FM calculus]
\label{rem:transition-to-FM}
The $m_k$ are defined; the Stasheff identities remain to be
verified. They are a consequence of Stokes' theorem on
$\FM_k(\C)$: codimension-$1$ faces encode compositions
$m_i \circ m_j$; codimension-$2$ corners cancel via the
Arnold--Orlik--Solomon relations.
Section~\ref{sec:FM_calculus} carries this out.
\end{remark}
