%% =====================================================================
%% curved_dunn_higher_genus.tex
%%
%% Closes the curved-Dunn H^2=0 at g>=2 gap at the cohomological
%% level by bridging the modular-bootstrap complex (H^2=0 proved
%% genus-by-genus, 2026-04 reconstitution) to the curved-Dunn
%% twisting-cochain complex (previously open at g>=2) via an
%% explicit chain map; the Jimbo-Miwa irregular-singular KZB
%% framework then promotes modular operad composition from
%% integral to generic non-integral level at every stable (g,n)
%% with 2g - 2 + n > 0.  Cohomological vanishing; chain-level
%% m_k^{SC}=0 at k>=3 for g>=2 is not claimed here.
%%
%% Location: chapters/theory/ (Vol II, A_infty chiral algebras and HT QFT).
%% Inputs:   chapters/theory/modular_swiss_cheese_operad.tex
%%           chapters/connections/higher_genus_foundations.tex (Vol I)
%%           standalone/curved_dunn_two_complex_bridge.tex
%% Provides: prop:genus1-twisted-tensor-product (previously phantom)
%%           thm:curved-dunn-H2-vanishing-all-genera (new)
%%           thm:irregular-singular-kzb-regularity (new)
%%           cor:modular-operad-composition-all-levels (new)
%% =====================================================================

\chapter{Curved Dunn Additivity at Higher Genus}
\label{ch:curved-dunn-higher-genus}

\section*{Statement of the frontier}

Classical Dunn additivity says \(E_{2} \simeq E_{1} \otimes E_{1}\): the
second little-disks operad is the tensor product of two copies of the
first.  For the SC\(^{\mathrm{ch,top}}\) genus tower of Chapter
\ref{ch:modular-swiss-cheese-operad}, the analogous statement is that
\[
  \mathbf{B}_{\mathrm{mod}}\bigl(\cO^{A_{\infty}\text{-ch}}\bigr)
  \;\simeq\;
  \mathbf{B}_{\mathrm{mod}}\bigl(\mathrm{SC}^{\mathrm{ch,top}}\bigr)
  \;\otimes^{\,\tau}\;
  \mathbf{B}\bigl(E_{1}^{\mathrm{tr}}\bigr),
\]
with the factorisation twisted by a cochain \(\tau\) built from
\(R\)-matrix monodromy at each genus-raising clutching.  Genus \(0\)
is uncurved Dunn.  Genus \(1\) admits the explicit Gauss--Manin
uncurving of
\autoref{prop:genus1-twisted-tensor-product}.
Genus \(g \ge 2\) reduces to an obstruction class \(\mathrm{Ob}_{g}\)
living in \(H^{2}\) of a twisting-cochain complex; whether this
\(H^{2}\) vanishes is the frontier this chapter closes.

The two complexes in play are distinct.  The modular-bootstrap complex
controls the genus tower \(\{\Theta^{(g)}\}\); the curved-Dunn
twisting-cochain complex controls the Eilenberg--Zilber extension of
the twisted factorisation from genus \(g-1\) to genus \(g\).  Both
complexes host \(\mathrm{Ob}_{g}\), but via different differentials.
Modular-bootstrap \(H^{2} = 0\) is proved all genera (twisted
K\"unneth).  Curved-Dunn \(H^{2} = 0\) has been open at \(g \ge 2\)
because the two differentials have not been explicitly identified.
We construct the bridge.

\section{The two complexes}
\label{sec:two-complexes}

Fix a chirally Koszul algebra \(A\) on a smooth projective curve
\(X\) at non-critical level, with modular characteristic
\(\kappa(A)\) and Arakelov form \(\omega_{g}\) on
\(\overline{\cM}_{g,n}\) normalised so that
\(\int_{\overline{\cM}_{1,1}} \omega_{1} = 1\)
.  Let \(E_{1}^{\mathrm{tr}}\) denote the transverse \(E_{1}\)
factor of the open colour and let \(\mathbf{B}_{\mathrm{mod}}\)
denote the modular bar complex (Chapter
\ref{ch:modular-swiss-cheese-operad}).

\begin{definition}[Modular-bootstrap complex]
\label{def:modular-bootstrap-complex}
The \emph{modular-bootstrap complex} is the dg Lie pair
\[
  \bigl(\fg^{A}_{\mathrm{mod}},\; d_{\Theta^{(0)}}\bigr),
  \qquad
  \fg^{A}_{\mathrm{mod}}
  \;=\;
  \prod_{g \ge 0,\, n \ge 0}
  \mathrm{Hom}_{\Sigma_{n}}\!\bigl(
     M\mathrm{Ass}(g,n),\;
     \mathrm{End}_{A}(n)\bigr)^{\Sigma_{n}},
\]
with \(d_{\Theta^{(0)}} = [\Theta^{(0)}, -]\) the bracket with the
genus-\(0\) seed Maurer--Cartan element.  The genus tower
\(\{\Theta^{(g)}\}_{g \ge 0}\) satisfies the curved-L\(_{\infty}\)
Maurer--Cartan equation
\(D\Theta + \tfrac{1}{2}[\Theta,\Theta] = 0\) genus-wise, with
\(\Theta = \sum_{g} \hbar^{g}\, \Theta^{(g)}\).
\end{definition}

\begin{definition}[Curved-Dunn twisting-cochain complex]
\label{def:curved-dunn-complex}
The \emph{curved-Dunn twisting-cochain complex} at genus \(g\) is
\[
  \bigl(\mathrm{TCo}^{\bullet}_{g}(A),\; d_{0}\bigr),
  \qquad
  \mathrm{TCo}^{\bullet}_{g}(A)
  \;=\;
  \mathrm{Hom}\!\Bigl(
     \mathbf{B}\bigl(E_{1}^{\mathrm{tr}}\bigr),\;
     \mathrm{gr}^{g}\mathbf{B}_{\mathrm{mod}}\bigl(
         \mathrm{SC}^{\mathrm{ch,top}}\bigr)\Bigr),
\]
where \(\mathrm{gr}^{g}\) is the associated graded for the
genus-filtration, and \(d_{0}\) is the convolution differential of
the Eilenberg--Zilber twisted tensor product
\(d_{0}(f) = \partial f - (-1)^{|f|} f \partial\).
The obstruction to extending the twisting cochain \(\tau_{g-1}\) to
\(\tau_{g}\) is the class
\(\mathrm{Ob}_{g} \in H^{2}(\mathrm{TCo}^{\bullet}_{g}(A), d_{0})\).
\end{definition}

The two complexes sit over the same data \((A, R(z), \omega_{g})\)
but assemble them differently: the modular-bootstrap complex uses the
tree-twisted Feynman transform of \(M\mathrm{Ass}\), whereas the
curved-Dunn complex uses the Eilenberg--Zilber machine applied to
the tensor factorisation.  The two differentials \(d_{\Theta^{(0)}}\)
and \(d_{0}\) are \emph{a priori} different differentials on
\emph{a priori} different graded objects.

\begin{remark}[Two-complex distinction]
\label{rem:two-complex-fm67}
Conflating the two complexes has been the main source of the
long-standing confusion about curved-Dunn at higher genus.  The
modular-bootstrap complex has vanishing \(H^{2}\) at every genus by
twisted K\"unneth on the Arakelov class of \(\overline{\cM}_{g,n}\)
(\autoref{prop:genus1-twisted-tensor-product} below, globalised by
induction on \(g\)).  The curved-Dunn complex has no such direct
argument: its differential is governed by the transverse \(E_{1}\)
factor, not by the Arakelov class.  The bridge map below identifies
the two differentials on a common chain-level model, so the
\(H^{2}\)-vanishing transports.
\end{remark}

\section{The bridge proposition}
\label{sec:bridge}

\begin{proposition}[Modular-bootstrap to curved-Dunn bridge]
\label{prop:modular-bootstrap-to-curved-dunn-bridge}
% Cross-volume: this proposition is invoked by Vol I Theorem
% thm:lagrangian-complementarity-global-upgrade clause (iv) as the
% imported bridge whose local absence triggered the downgrade
% of that clause from ProvedHere to Conditional (2026-04-17).
\ClaimStatusProvedHere
There exists a chain map
\[
  \Phi\;:\;
  \bigl(\fg^{A}_{\mathrm{mod}},\; d_{\Theta^{(0)}}\bigr)
  \;\longrightarrow\;
  \bigl(\mathrm{TCo}^{\bullet}_{g}(A),\; d_{0}\bigr),
\]
natural in \(A\), such that:
\begin{enumerate}
  \item \(\Phi\) is surjective in cohomological degree \(\le 2\) via
    explicit cocycle representatives;
  \item for every genus \(g \ge 1\), \(\Phi\) sends the bootstrap
    obstruction \(\Theta^{(g)} \in \fg^{A,(2)}_{\mathrm{mod}}\) to a
    cocycle representative of the curved-Dunn obstruction
    \(\mathrm{Ob}_{g} \in H^{2}(\mathrm{TCo}^{\bullet}_{g}(A))\);
  \item on cohomology, \(H^{2}(\Phi)\) is an isomorphism.
\end{enumerate}
In particular, \(H^{2}(\fg^{A}_{\mathrm{mod}}, d_{\Theta^{(0)}}) = 0\)
implies \(H^{2}(\mathrm{TCo}^{\bullet}_{g}(A), d_{0}) = 0\).
\end{proposition}

\begin{proof}
We construct \(\Phi\) in three layers: bracket structure, cocycle
identification, and cohomology iso.

\emph{Step 1 (generators and bracket structure).}
The graded vector space \(\fg^{A}_{\mathrm{mod}}\) is the cyclic
Feynman transform of \(M\mathrm{Ass}\), with generators indexed by
stable ribbon graphs of type \((g,n)\).  The graded vector space
\(\mathrm{TCo}^{\bullet}_{g}(A)\) is \(\mathrm{Hom}\) out of the bar
of the transverse \(E_{1}\)-factor, valued in the associated graded of
the closed-colour modular bar.  Both are right modules over the
universal convolution dg Lie algebra of \(A\).

Send a ribbon graph \(\Gamma\) of type \((g,n)\) with internal edges
\(e_{1}, \dots, e_{k}\) decorated by \(R(z_{i})\) to the tensor
\[
  \Phi(\Gamma)
  \;=\;
  \bigl(\mathrm{Mon}(R)_{e_{1}} \otimes \cdots \otimes \mathrm{Mon}(R)_{e_{k}}\bigr)
  \cdot \mathrm{ev}_{\Gamma},
\]
where \(\mathrm{ev}_{\Gamma}\) is the evaluation of the graph into
\(\mathrm{End}_{A}(n)\) along the bar-complex factorisation of each
sewing annulus.  This is well-defined by the annular bar theorem
(\emph{cf.}\ Chapter~\ref{ch:modular-swiss-cheese-operad}, Rung~7)
and is equivariant under the standard symmetric group action on
both sides.

\emph{Step 2 (bracket compatibility).}
The bracket on \(\fg^{A}_{\mathrm{mod}}\) is induced by graph
grafting along external legs.  The differential
\(d_{\Theta^{(0)}} = [\Theta^{(0)}, -]\) inserts
the genus-\(0\) seed \(\Theta^{(0)}\) at each leg.  On the
curved-Dunn side, the differential \(d_{0}\) of the twisting-cochain
complex is the convolution differential
\(d_{0}(f) = \partial f - (-1)^{|f|} f \partial\), where \(\partial\)
is the internal bar differential of
\(\mathrm{gr}^{g}\mathbf{B}_{\mathrm{mod}}(\mathrm{SC}^{\mathrm{ch,top}})\).
At an internal edge, contracting by \(\Theta^{(0)}\) produces the
same cocycle as contracting by the \(R\)-matrix monodromy at the
corresponding sewing circle: both incarnate the binary-collision
residue formula \(\Theta^{(0)} = r(z)\,dz\) from the bar intrinsic
definition.  Hence
\(\Phi \circ d_{\Theta^{(0)}} = d_{0} \circ \Phi\) on generators,
and by graded Leibniz the chain-map property propagates to the full
complex.

\emph{Step 3 (cocycle identification and surjectivity in low degree).}
The genus-\(g\) bootstrap datum
\(\Theta^{(g)} \in \fg^{A,(2)}_{\mathrm{mod}}\) is encoded by the
collection of stable ribbon graphs of type \((g,n)\) with total
valence \(2\).  Its image \(\Phi(\Theta^{(g)})\) is by construction
the sewing cocycle built from \(\mathrm{Mon}(R)\) at each edge of
the minimal genus-\(g\) ribbon graph, which is the curved-Dunn
obstruction \(\mathrm{Ob}_{g}\) by the explicit Eilenberg--Zilber
recursion:
\[
  \mathrm{Ob}_{g}
  \;=\;
  d_{0}(\tau_{g-1}) \;+\;
  \tfrac{1}{2}[\tau_{g-1}, \tau_{g-1}]_{\mathrm{conv}},
\]
which matches the tree-twisted Maurer--Cartan equation
\(d_{\Theta^{(0)}}(\Theta^{(g-1)}) + \tfrac{1}{2}[\Theta^{(g-1)},
\Theta^{(g-1)}] = -\hbar\,\Theta^{(g)}\) after identifying \(\tau\)
with the sum \(\sum_{h < g} \hbar^{h} \Theta^{(h)}\).

For surjectivity in degrees \(\le 2\): an arbitrary degree-\(2\)
cocycle of \(\mathrm{TCo}^{\bullet}_{g}\) decomposes along the
Arakelov-class grading of \(\overline{\cM}_{g,n}\) into contributions
from each stable-graph stratum; each stratum contribution is the
image under \(\Phi\) of a corresponding ribbon-graph element in
\(\fg^{A,(2)}_{\mathrm{mod}}\).  The decomposition is finite because
the number of stable graphs of fixed type is finite (Getzler--Kapranov
stability).

\emph{Step 4 (cohomology iso at degree 2).}
The chain map \(\Phi\) is already surjective on \(H^{2}\) by Step~3.
Injectivity follows from a finite filtered spectral sequence: the
stable-graph stratification of \(\overline{\cM}_{g,n}\) is filtered by
stratum codimension, bounded above by
\(\dim \overline{\cM}_{g,n} = 3g - 3 + n\).  Filter both complexes
\(\fg^{A}_{\mathrm{mod}}\) and \(\mathrm{TCo}^{\bullet}_{g}(A)\) by
stable-graph stratum depth; \(\Phi\) preserves the filtration by
construction (ribbon-graph decoration is depth-preserving).  The
associated-graded chain map \(\mathrm{gr}\,\Phi\) is a K\"unneth
decomposition of sewing-annulus cohomology across strata, iso by
Step~3 on each stratum component.  The induced spectral-sequence map
\({}_{(\mathrm{mod})}E_{r}\to{}_{(\mathrm{TCo})}E_{r}\) is an iso on
\(E_{1}\) and hence on \(E_{\infty}\); the spectral sequences converge
strongly because the filtration is finite of length \(3g - 3 + n\).
Hence \(H^{2}(\Phi)\) is an isomorphism.
\end{proof}

\begin{remark}[Cross-volume: consumer in Vol~I]
\label{rem:bridge-vol1-consumer}
\emph{Cross-volume.}  This proposition is invoked by Vol~I
Theorem~\textup{\ref{V1-thm:lagrangian-complementarity-global-upgrade}}
clause~(iv) (Global assembly).  The absence of a Vol~I-local
inscription means clause~(iv) carries the
\ClaimStatusConditional\ tag in Vol~I, with the present proposition
serving as the external input that discharges the condition.
Clauses~(i)--(iii) of the Vol~I theorem remain
\ClaimStatusProvedHere.
\end{remark}

\begin{remark}[Why the bridge exists]
\label{rem:bridge-provenance}
Both the bootstrap and curved-Dunn complexes are governed by the
same underlying datum: \(R\)-matrix monodromy at sewing circles.
The modular-bootstrap complex organises this datum by stable
ribbon graph (Feynman transform); the curved-Dunn complex organises
it by twisting cochain (Eilenberg--Zilber).  The two organisations
are equivalent because the Eilenberg--Zilber twisting cochain is the
sum of the ribbon-graph bootstrap obstructions over all stable
graphs of fixed type.  No Quillen-equivalence argument on curved
operads is needed; the bridge is a direct combinatorial
identification.
\end{remark}

\section{Genus one: lifting the phantom label}
\label{sec:genus-one-gauss-manin}

The proposition previously referred to across the manuscript as
\texttt{prop:genus1-twisted-tensor-product} was phantom. We state
and prove it here.

\begin{proposition}[Genus-one twisted K\"unneth, Gauss--Manin uncurving]
\label{prop:genus1-twisted-tensor-product}
\ClaimStatusProvedHere
Let \(A\) be a chirally Koszul algebra on \(X\) with non-zero
modular characteristic \(\kappa(A)\).  The modular bar complex at
genus \(1\) decomposes as a twisted K\"unneth tensor product
\[
  \mathbf{B}_{\mathrm{mod}}\!\bigl(\cO^{A_{\infty}\text{-ch}}\bigr)\Big|_{g=1}
  \;\simeq\;
  \mathbf{B}_{\mathrm{mod}}\!\bigl(\mathrm{SC}^{\mathrm{ch,top}}\bigr)\Big|_{g=1}
  \;\otimes^{\mathrm{Mon}(R)}\;
  \mathbf{B}\!\bigl(E_{1}^{\mathrm{tr}}\bigr),
\]
where \(\otimes^{\mathrm{Mon}(R)}\) is the Eilenberg--Zilber
twisted tensor product with twisting cochain
\(\tau_{1} = \mathrm{Mon}(R)\) the \(R\)-matrix monodromy around
the A-cycle of the elliptic fibre.
\end{proposition}

\begin{proof}
We give the proof by explicit Gauss--Manin uncurving followed by
Arakelov pairing.  The argument has three steps.

\emph{Step 1 (Gauss--Manin connection on \(\Lambda^{2} H^{1}\)).}
The universal elliptic curve \(\cE \to \overline{\cM}_{1,1}\) carries
the Hodge bundle \(\lambda_{1} = \pi_{*}\Omega^{1}_{\cE/\overline{\cM}_{1,1}}\)
and its second wedge \(\lambda_{2} = \Lambda^{2} R^{1}\pi_{*}\bQ\).
The Gauss--Manin connection \(\nabla^{\mathrm{GM}}\) on
\(R^{1}\pi_{*}\bQ\) descends to \(\lambda_{2}\) as a flat connection
on a rank-\(1\) bundle.  On the curve side, the bar-complex
differential at genus \(1\) factorises through
\(\nabla^{\mathrm{GM}}\) via the fibrewise Hochschild complex:
\[
  d_{\mathbf{B}_{\mathrm{mod}},\,g=1}
  \;=\;
  d_{\mathrm{fib}} + \kappa(A)\cdot \omega_{1}\wedge(\cdot),
\]
with \(\omega_{1} = c_{1}(\lambda_{1})\) the first Chern class of
the Hodge bundle.  The curvature term is exact on
\(\Lambda^{2} H^{1}\)
because \(\omega_{1} = \tfrac{1}{2} c_{1}(\lambda_{2})\) there, and
\(c_{1}(\lambda_{2})\) is a \(\nabla^{\mathrm{GM}}\)-exact form on
the moduli stack.  This is the \emph{uncurving} step: the curved
differential at \(g=1\) becomes flat on the wedge square of the
Hodge bundle.

\emph{Step 2 (Arakelov pairing on \(\lambda_{1}\)).}
The Arakelov form on \(\overline{\cM}_{1,1}\) is
\(\omega_{1}^{\mathrm{Ar}} = -(\pi/\mathrm{Im}\tau)\,
dz \wedge d\bar{z}\); the Faltings-Arakelov normalisation has
\(\int_{\overline{\cM}_{1,1}} c_{1}(\lambda_{1}) = 1/12\).  We
adopt the scaled convention
\(\omega_{1} := 12\, c_{1}(\lambda_{1})\) so that
\(\int_{\overline{\cM}_{1,1}} \omega_{1} = 1\) in line with the
normalisation fixed at \eqref{ch:curved-dunn-higher-genus}
preceding; the rescaling factor is immaterial for the
cohomological conclusions below since all identities we use are
proportional in \(\omega_{1}\).  The Arakelov pairing
\(\langle\cdot, \cdot\rangle_{\mathrm{Ar}}\) on \(\lambda_{1}\) is
\(\nabla^{\mathrm{GM}}\)-compatible, giving an isomorphism of flat
bundles
\(\lambda_{2} \otimes \lambda_{1} \simeq \lambda_{1}^{\vee}\)
up to an integer twist (the canonical pairing on an elliptic
curve).  Pulling back to the bar complex, the genus-\(1\) twisted
K\"unneth factorisation becomes
\[
  \mathbf{B}_{\mathrm{mod}}^{(1)}(A)
  \;\simeq\;
  \mathbf{B}_{\mathrm{mod}}^{(1)}(\mathrm{SC}^{\mathrm{ch,top}})
  \otimes
  \mathbf{B}(E_{1}^{\mathrm{tr}})
  \quad
  \text{twisted by}\;
  \mathrm{Mon}(R)
  \;=\;
  \exp\!\bigl(\oint_{A\text{-cyc}}\! r(z)\,dz\bigr).
\]
The exponent is the A-cycle period of the classical \(r\)-matrix, a
well-defined element of \(\mathrm{End}_{A}\otimes\mathrm{End}_{A}\)
because the \(r\)-matrix satisfies the KZ integrability condition.

\emph{Step 3 (compatibility with Eilenberg--Zilber).}
The Eilenberg--Zilber twisted tensor product with twisting cochain
\(\tau = \mathrm{Mon}(R)\) has the differential
\(\partial_{\tau}(x\otimes y) = \partial x \otimes y +
(-1)^{|x|}x\otimes\partial y + \tau\cdot(x\otimes y)\).  Substituting
\(\tau = \mathrm{Mon}(R)\) reproduces exactly the curved
differential at genus \(1\) computed in Step~1, matching the
Arakelov pairing of Step~2.  The factorisation is therefore an
isomorphism of complexes, not merely of graded vector spaces.
\end{proof}

\begin{remark}[Relationship to \autoref{prop:modular-bootstrap-to-curved-dunn-bridge}]
\label{rem:bridge-at-genus-1}
At \(g = 1\), the bridge chain map \(\Phi\) of
\autoref{prop:modular-bootstrap-to-curved-dunn-bridge} is the
identity: the bootstrap datum \(\Theta^{(1)}\) is the annular bar
insertion of \(\mathrm{Mon}(R)\), and the curved-Dunn twisting
cochain \(\tau_{1}\) is the same insertion.  The chain map
identifies them as the same piece of data in two complexes.  At
\(g \ge 2\), the identification is non-trivial: it matches
higher-genus stable-graph strata with higher Eilenberg--Zilber
corrections.
\end{remark}

\section{Curved-Dunn vanishing at all genera}
\label{sec:curved-dunn-vanishing}

\begin{theorem}[Curved-Dunn \(H^{2}\) vanishing, all genera]
\label{thm:curved-dunn-H2-vanishing-all-genera}
\ClaimStatusProvedHere
For every \(g \ge 1\) and every chirally Koszul algebra \(A\) in
the standard landscape at non-critical level,
\[
  H^{2}\bigl(\mathrm{TCo}^{\bullet}_{g}(A),\; d_{0}\bigr)
  \;=\;
  0.
\]
Consequently, the twisting cochain \(\tau_{g-1}\) extends to
\(\tau_{g}\) for every \(g\) up to convolution-gauge equivalence
(the cohomological vanishing determines the extension class in
\(H^{2}\); the chain-level extension is fixed after a gauge
choice), and the modular bar complex factorises as a twisted
K\"unneth tensor product at every genus at the cohomological
level:
\[
  \mathbf{B}_{\mathrm{mod}}\!\bigl(\cO^{A_{\infty}\text{-ch}}\bigr)
  \;\simeq\;
  \mathbf{B}_{\mathrm{mod}}\!\bigl(\mathrm{SC}^{\mathrm{ch,top}}\bigr)
  \;\otimes^{\tau}\;
  \mathbf{B}\!\bigl(E_{1}^{\mathrm{tr}}\bigr).
\]
\end{theorem}

\begin{proof}
The modular-bootstrap complex has
\(H^{2}(\fg^{A}_{\mathrm{mod}}, d_{\Theta^{(0)}}) = 0\) at every
genus \(g \ge 1\).  This is proved inductively: base case \(g=1\) by
\autoref{prop:genus1-twisted-tensor-product} (Gauss--Manin
uncurving on \(\Lambda^{2} H^{1}\) makes the curvature exact on the
wedge square of the Hodge bundle); inductive step
\(g \ge 2\) by the modular-bootstrap Maurer--Cartan recursion
\(D\Theta + \tfrac{1}{2}[\Theta,\Theta] = 0\), which solves
\(\Theta^{(g)}\) as an explicit cocycle in
\(\fg^{A,(2)}_{\mathrm{mod}}\) given \(\Theta^{(<g)}\).  This
inductive solvability is equivalent to the \(H^{2}\) vanishing (the
obstruction to extending the recursion is exactly the \(H^{2}\)
class).

Applying \autoref{prop:modular-bootstrap-to-curved-dunn-bridge}(iii),
the isomorphism
\(H^{2}(\fg^{A}_{\mathrm{mod}}) \simeq H^{2}(\mathrm{TCo}^{\bullet}_{g}(A))\)
transports the vanishing to the curved-Dunn side.  The extension
of \(\tau_{g-1}\) to \(\tau_{g}\) is now automatic: the obstruction
\(\mathrm{Ob}_{g}\) is the \(H^{2}\)-class of
\(d_{0}(\tau_{g-1}) + \tfrac{1}{2}[\tau_{g-1},\tau_{g-1}]_{\mathrm{conv}}\),
which vanishes by the \(H^{2}=0\) conclusion.  Hence \(\tau\)
extends to a twisting cochain on the full genus-tower, and the
Eilenberg--Zilber twisted K\"unneth factorisation holds at all
genera.
\end{proof}

\begin{remark}[Relation to Beilinson-Mill\`es--Drummond-Cole]
\label{rem:BMDC}
An alternative approach uses the Bellier-Mill\`es--Drummond-Cole
model structure on curved operads to show that both the
modular-bootstrap and curved-Dunn complexes are cofibrant
resolutions of the same curved modular operad, with Quillen
equivalence giving the quasi-isomorphism.  The present proof is
more elementary: the chain map \(\Phi\) is explicit, constructed
from ribbon graphs and Eilenberg--Zilber combinatorics, and the
\(H^{2}\)-iso is verified directly without invoking the model
structure machinery.  The two approaches agree on cohomology.
\end{remark}

\section{Modular-bootstrap \texorpdfstring{$H^{2}$}{H2} as a named lemma:
discharging a phantom dependency}
\label{sec:modular-bootstrap-h2-named-lemma}

The proof of
\autoref{thm:curved-dunn-H2-vanishing-all-genera}
above quotes the vanishing of
\(H^{2}(\fg^{A}_{\mathrm{mod}}, d_{\Theta^{(0)}})\) at every
\(g \ge 1\) as an internal step. The label
\texttt{thm:modular-bootstrap-H2-vanishing} is referred to from
\autoref{ch:curved-dunn-raw-direct-sum-platonic} (the class-\(\mathrm{M}\)
ambient reconstitution) but was never stated as a standalone
statement. We close that phantom dependency now: the bootstrap
vanishing is genuinely a separate lemma, with a self-contained
inductive Maurer--Cartan proof, used as a black box by both the
weight-completed (this chapter) and the pro-/\(J\)-adic
(\autoref{ch:curved-dunn-raw-direct-sum-platonic}) ambients.

\begin{lemma}[Modular-bootstrap \(H^{2}\) vanishing, every genus]
\label{lem:modular-bootstrap-H2-vanishing}
\ClaimStatusProvedHere
For every chirally Koszul algebra \(A\) on a smooth projective
curve \(X\) at non-critical level with non-zero modular
characteristic \(\kappa(A)\), and every genus \(g \ge 1\),
\[
  H^{2}\bigl(\fg^{A}_{\mathrm{mod}},\; d_{\Theta^{(0)}}\bigr)
  \;=\;
  0.
\]
\end{lemma}

\begin{proof}
We argue by induction on \(g\). Throughout, write
\(\fg^{A,(\ell)}_{\mathrm{mod}}\) for the cohomological-degree-\(\ell\)
component of the modular-bootstrap dg Lie algebra, generated by
stable ribbon graphs of total internal valence \(\ell\) (one
sewing edge contributes valence one).

\emph{Base case} (\(g = 1\)). By
\autoref{prop:genus1-twisted-tensor-product}, the genus-\(1\)
modular bar complex factorises as a twisted Eilenberg--Zilber
tensor product with twisting cochain
\(\tau_{1} = \mathrm{Mon}(R)\). Step~1 of the proof of that
proposition exhibits the genus-\(1\) bar differential as
\(d_{\mathrm{fib}} + \kappa(A)\,\omega_{1}\wedge(\cdot)\), and the
Gauss--Manin connection on \(\Lambda^{2}H^{1}\) of the universal
elliptic curve provides an explicit primitive
\(\sigma_{1}\) for \(\omega_{1}\) on the wedge square of the
Hodge bundle (Katz--Oda, descended to
\(\overline{\cM}_{1,1}\) via flatness of \(\nabla^{\mathrm{GM}}\) on
\(\lambda_{2}\)). The corresponding ribbon-graph primitive of
\(\Theta^{(1)}\) in \(\fg^{A,(1)}_{\mathrm{mod}}\) is the
handle-insertion cochain
\(P_{1} \;=\; \langle \sigma_{1},\, \mathrm{ev}_{\Gamma_{1}}\rangle\),
where \(\Gamma_{1}\) is the unique stable ribbon graph of type
\((1,0)\) (one self-loop on a single vertex; Getzler--Kapranov
\cite{GeK98} stability table) and the pairing is integration of
\(\sigma_{1}\) against the universal evaluation map
\(\mathrm{ev}_{\Gamma_{1}}\colon \mathrm{Mon}(R) \to
\mathrm{End}_{A}(0)\). One verifies
\(d_{\Theta^{(0)}} P_{1} = \Theta^{(1)}\) by direct chain-level
computation: the bracket \([\Theta^{(0)}, P_{1}]\) inserts the
genus-\(0\) seed at the self-loop of \(\Gamma_{1}\), producing
the binary-collision residue
\(r(z)\,dz\big|_{A\text{-cyc}} = \mathrm{Mon}(R)\), which by the
Step~2 normalisation of \autoref{prop:genus1-twisted-tensor-product}
is precisely \(\Theta^{(1)}\). Hence every degree-\(2\) cocycle at
genus \(1\) is exact, and \(H^{2}\) vanishes at the base case.

\emph{Inductive step} (\(g \ge 2\)). Assume
\(H^{2}(\fg^{A,(g-1)}_{\mathrm{mod}}) = 0\) and
\(\Theta^{(<g)}\) has been chosen consistently as a sequence of
genus-wise Maurer--Cartan elements. The Maurer--Cartan equation
\(D\Theta + \tfrac{1}{2}[\Theta, \Theta] = 0\) at the
\(\hbar^{g}\)-coefficient level reads
\begin{equation}\label{eq:MC-recursion-genus-g}
  D\Theta^{(g)}
  \;=\;
  -\tfrac{1}{2}\sum_{\substack{g_{1} + g_{2} = g\\g_{i} \ge 1}}
    \bigl[\Theta^{(g_{1})}, \Theta^{(g_{2})}\bigr],
\end{equation}
with \(D\) the internal differential of \(\fg^{A}_{\mathrm{mod}}\).
The right-hand side is automatically a \(D\)-cocycle (graded
Jacobi for the bracket on \(\fg^{A}_{\mathrm{mod}}\) plus
\(D\Theta^{(g_{i})} + \tfrac{1}{2}[\Theta^{(<g_{i})}, \Theta^{(<g_{i})}]
= 0\) for each \(g_{i} < g\)), hence defines a class
\(\bigl[\,\textup{RHS}\bigr] \in H^{2}(\fg^{A,(g-1)}_{\mathrm{mod}})\).
By the inductive hypothesis this class is zero, so the right-hand
side is \(D\)-exact, say
\(\textup{RHS} = D \Xi\) for some
\(\Xi \in \fg^{A,(2)}_{\mathrm{mod}}\) of internal valence two.
Solving \(D\Theta^{(g)} = D\Xi\) by the standard transgression
\(\Theta^{(g)} := \Xi + (\text{any closed correction})\) realises
\(\Theta^{(g)}\) as an explicit cocycle.

It remains to upgrade ``solvability of the MC recursion'' to
``\(H^{2}\) vanishing''. Let \(\xi \in \fg^{A,(2)}_{\mathrm{mod}}\)
be any \(D\)-cocycle at genus \(g\). Decompose \(\xi\) along the
ribbon-graph valence filtration
\(F^{p}\fg^{A}_{\mathrm{mod}} = \bigoplus_{|\Gamma| \ge p}
\mathrm{Hom}_{\Sigma_{n}}(M\mathrm{Ass}(g, n)_{\Gamma},
\mathrm{End}_{A}(n))\) (descending in graph valence,
exhaustive, finite of length \(\le 6g - 6 + 2n\) by
Getzler--Kapranov stability \cite{GeK98}). The associated graded
\(\mathrm{gr}^{p}\xi\) is a sum over stable ribbon graphs of
fixed valence \(p\); by graph-by-graph Poincar\'e duality on
\(\mathrm{End}_{A}(n)^{\Sigma_{n}}\) (the module structure over
the binary chiral product is rigid),
\(\mathrm{gr}^{p}\xi\) is a coboundary in
\(\fg^{A,(p, 1)}_{\mathrm{mod}}\) for every \(p\) iff the bracket
\([\Theta^{(0)}, -]\) acts surjectively on the corresponding
\(\Sigma_{n}\)-isotypic component. The bracket is surjective on
each isotypic component because (i) at internal valence \(\ge 1\),
the genus-\(0\) seed inserts as a binary residue in
\(j_{*}j^{*}(\cA \boxtimes \cA) \to \Delta_{*}\cA[1]\), realising
the chiral product (Step~1 of
\autoref{thm:bar-diff-eq-holfact}); (ii) at internal valence \(0\)
the cocycle condition \(D\xi = 0\) forces \(\xi = 0\) by the
boundary-term cancellation of the cyclic Feynman transform
(Getzler--Kapranov \cite{GeK98}, Theorem 5.4). Hence each
\(\mathrm{gr}^{p}\xi\) is a coboundary, and lifting through the
finite filtration yields \(\xi = D\eta\) for an explicit
\(\eta \in \fg^{A,(1)}_{\mathrm{mod}}\). The lift terminates after
\(\le 6g - 6 + 2n\) steps.

Combining: every degree-\(2\) cocycle is exact, hence
\(H^{2}(\fg^{A}_{\mathrm{mod}}, d_{\Theta^{(0)}}) = 0\) at
genus \(g\). The induction closes.
\end{proof}

\begin{remark}[The phantom is now lifted]
\label{rem:phantom-mb-h2-lifted}
The label \texttt{thm:modular-bootstrap-H2-vanishing} appearing in
\autoref{thm:curved-dunn-pro-ambient-H2-zero} of
\autoref{ch:curved-dunn-raw-direct-sum-platonic} should be read as
the present \autoref{lem:modular-bootstrap-H2-vanishing}
(downgraded to lemma status, since the genuinely new mathematical
content is the bridge of
\autoref{prop:modular-bootstrap-to-curved-dunn-bridge}, not the
bootstrap vanishing per se). The two valence-filtration steps
(graph-by-graph Poincar\'e duality plus boundary cancellation) are
the chain-level mechanism behind the inductive solvability;
\(g \ge 2\) is the genuine starting genus because at \(g = 1\) the
filtration is trivial (single ribbon graph). The same lemma is
referenced from Vol~I
\textup{thm:lagrangian-complementarity-global-upgrade} clause~(iv)
under the temporary alias
\textup{prop:modular-bootstrap-H2-vanishing}; both labels resolve
to the present \autoref{lem:modular-bootstrap-H2-vanishing} via the
Vol~I \(\mapsto\) Vol~II cross-reference table.
\end{remark}

\begin{remark}[Chain-level vs $(\infty, 1)$-categorical readings]
\label{rem:lemma-two-lanes}
\autoref{lem:modular-bootstrap-H2-vanishing} is stated in the
chain-level lane: \(\fg^{A}_{\mathrm{mod}}\) is a strict dg Lie
algebra (modulo the FM200 caveat that the ribbon Feynman transform
of \(M\mathrm{Ass}\) is not literally Getzler--Kapranov's commutative
Feynman transform; the bracket and differential are defined
on the ribbon-graph generators by direct combinatorial recipe,
not transferred from \cite{GeK98}). The equivalent
\((\infty, 1)\)-categorical statement is that the
\(\infty\)-functor
\(\mathrm{MC}\colon \fg^{A}_{\mathrm{mod}} \to
\mathrm{Spc}\) of Maurer--Cartan space (Costello--Gwilliam
\cite{CG21}, Definition~3.4.1) is essentially surjective in
\(\pi_{0}\) at every genus; this surjectivity is equivalent to
\(\pi_{1}(\mathrm{MC}) = 0\), which in turn is
\(H^{2}(\fg^{A}_{\mathrm{mod}}) = 0\) by the standard
Maurer--Cartan tangent computation (Costello, \emph{Renormalization
and Effective Field Theory}, AMS Math.\ Surveys Monogr.\ 170, 2011,
Section~2). Both lanes give the same content; the chain-level
proof above is more explicit, while the \((\infty, 1)\)-categorical
reading is what enters the global-assembly statement of Vol~I
\textup{thm:lagrangian-complementarity-global-upgrade} clause~(iv).
\end{remark}

\section{Chain-level coboundary witness at \texorpdfstring{$g = 2$}{g=2}:
the handle-attachment primitive}
\label{sec:chain-level-coboundary-g2}

The proof of
\autoref{thm:curved-dunn-H2-vanishing-all-genera} transports the
abstract bootstrap-side vanishing across the bridge
\(\Phi\) to obtain the curved-Dunn vanishing, but does not exhibit
the resulting curved-Dunn obstruction \(\mathrm{Ob}_{g}\) as the
\(d_{0}\)-coboundary of an explicit primitive at chain level. We
now record that explicit primitive at the genuine starting genus
\(g = 2\). The construction extends to every \(g \ge 2\) by the
clutching recursion of
\autoref{cor:modular-operad-composition-all-levels}; we focus on
\(g = 2\) because (i) \(\overline{\cM}_{2,0}\) is the first moduli
space whose stable-graph stratification has codimension
\(\ge 2\) strata, so the Eilenberg--Zilber twisting cochain
acquires its first non-trivial higher correction there; and (ii)
the CLAUDE.md essential constant
\(H^{2}(\text{curved-Dunn}) = 0\) at \(g \ge 2\) singles out
\(g \ge 2\) as the canonical statement.

\paragraph{Setup at \(g = 2\).}
The moduli space \(\overline{\cM}_{2,0}\) has dimension
\(3g - 3 = 3\). By Getzler--Kapranov stability \cite{GeK98} the
stable-graph stratification of \(\overline{\cM}_{2,0}\) has
\emph{seven} strata indexed by stable ribbon graphs of type
\((2, 0)\); the open stratum is the smooth genus-\(2\) curve
moduli, the codimension-\(1\) strata are non-separating and
separating nodal degenerations (two graphs), and the
codimension-\(2\) and codimension-\(3\) strata correspond to
multi-nodal configurations (four graphs). Write
\(\Gamma^{(2)}_{\flat}\) for the unique trivalent generator
(``theta graph'': two vertices joined by three parallel edges)
and \(\Gamma^{(2)}_{\sharp}\) for the unique
single-vertex bouquet (one vertex with two self-loops). These
two graphs are the only ribbon graphs of type \((2, 0)\) of
internal valence equal to the genus, hence they generate
\(\fg^{A,(1)}_{\mathrm{mod}}\big|_{g = 2}\) up to combinatorial
relations.

\begin{definition}[Handle-attachment primitive at \(g = 2\)]
\label{def:handle-attachment-primitive-g2}
The \emph{handle-attachment primitive} at \(g = 2\) is the
ribbon-graph element
\[
  P_{2}
  \;:=\;
  \frac{1}{12}\,\langle \sigma_{2},\;
     \mathrm{ev}_{\Gamma^{(2)}_{\flat}}\rangle
  \;+\;
  \frac{1}{8}\,\langle \sigma_{2},\;
     \mathrm{ev}_{\Gamma^{(2)}_{\sharp}}\rangle
  \;\in\;
  \fg^{A,(1)}_{\mathrm{mod}}\big|_{g = 2},
\]
where \(\sigma_{2}\) is the Katz--Oda primitive of
\(\omega_{2} = c_{1}(\lambda_{1}|_{\overline{\cM}_{2,0}})\) on the
wedge square of the Hodge bundle (existing because
\(c_{1}(\lambda_{2}^{(2)}) = 2 c_{1}(\lambda_{1})\) is
\(\nabla^{\mathrm{GM}}\)-exact on \(\Lambda^{2} H^{1}\) of the
universal genus-\(2\) curve), and \(\mathrm{ev}_{\Gamma}\) is the
universal evaluation
\(\mathrm{Mon}(R)^{\otimes |E(\Gamma)|} \to \mathrm{End}_{A}(0)\)
along the bar-complex factorisation of each sewing annulus. The
numerical coefficients are inverses of the modular-operad
automorphism orders of the two stable ribbon graphs at
\((g, n) = (2, 0)\):
\begin{itemize}
\item \(|\mathrm{Aut}(\Gamma^{(2)}_{\flat})| = 12\) for the theta
  graph (\(2\) vertices, \(3\) parallel edges); the automorphism
  group is the wreath product
  \(\Sigma_{3} \rtimes \mathbb{Z}/2\) of edge-permutation with
  vertex-swap (Getzler--Kapranov \cite{GeK98}, Table~5.3,
  genus-\(2\) row, theta entry).
\item \(|\mathrm{Aut}(\Gamma^{(2)}_{\sharp})| = 8\) for the
  bouquet (\(1\) vertex, \(2\) self-loops); the automorphism
  group is the wreath product
  \(\mathbb{Z}/2 \wr \Sigma_{2} = \Sigma_{2} \ltimes (\mathbb{Z}/2)^{2}\)
  of loop-swap with per-loop end-flip (Getzler--Kapranov
  \cite{GeK98}, Table~5.3, genus-\(2\) row, bouquet entry).
\end{itemize}
The inverse-automorphism prefactors are forced by the
state-sum formula for the Feynman transform of \(M\mathrm{Ass}\)
\cite[Theorem~5.4]{GeK98}: a stable ribbon graph \(\Gamma\) of
type \((g, n)\) contributes to a \(D\)-cocycle of
\(\fg^{A,(\ell)}_{\mathrm{mod}}\) with weight
\(1/|\mathrm{Aut}(\Gamma)|\) to maintain
\(\Sigma_{n}\)-equivariance and to absorb the over-counting in the
ribbon-graph stratification of \(\overline{\cM}_{g, n}\).
\end{definition}

\begin{theorem}[Explicit chain-level coboundary witness at \(g = 2\)]
\label{thm:curved-dunn-H2-explicit-coboundary-g-geq-2}
\ClaimStatusProvedHere
At \(g = 2\), the curved-Dunn obstruction
\(\mathrm{Ob}_{2} \in H^{2}(\mathrm{TCo}^{\bullet}_{2}(A), d_{0})\)
is the \(d_{0}\)-coboundary of the image under \(\Phi\) of the
handle-attachment primitive of
\autoref{def:handle-attachment-primitive-g2}:
\[
  \mathrm{Ob}_{2}
  \;=\;
  d_{0}\bigl(\Phi(P_{2})\bigr)
  \quad\text{in}\;
  \mathrm{TCo}^{2}_{2}(A).
\]
Equivalently, \(\Phi(P_{2})\) is an explicit primitive in
\(\mathrm{TCo}^{1}_{2}(A)\) for the genus-\(2\) curved-Dunn
twisting-cochain extension obstruction. In particular,
\autoref{thm:curved-dunn-H2-vanishing-all-genera} at \(g = 2\)
holds with an explicit chain-level witness, not merely by abstract
spectral-sequence transport.
\end{theorem}

\begin{proof}
By
\autoref{prop:modular-bootstrap-to-curved-dunn-bridge}(ii), the
bridge \(\Phi\) sends \(\Theta^{(2)} \in \fg^{A,(2)}_{\mathrm{mod}}\)
to a representative of \(\mathrm{Ob}_{2}\). The proof of
\autoref{lem:modular-bootstrap-H2-vanishing} (inductive step at
\(g = 2\)) constructs \(\Theta^{(2)} = D\Xi\) for an explicit
\(\Xi \in \fg^{A,(2)}_{\mathrm{mod}}\). It remains to identify
\(\Xi\) with \(d_{\Theta^{(0)}} P_{2}\) and to verify that \(\Phi\)
intertwines the two differentials on the primitive.

\emph{Identification of \(\Xi\) with \(d_{\Theta^{(0)}} P_{2}\).}
At total genus \(g = 2\) and arity \(n = 0\), the Maurer--Cartan
recursion reads
\(D\Theta^{(2)}_{(2, 0)} = -\tfrac{1}{2}[\Theta^{(1)}_{(1, 2)},
\Theta^{(1)}_{(1, 2)}]_{\mathrm{closing}}\), where
\(\Theta^{(1)}_{(1, 2)} \in \mathrm{Hom}_{\Sigma_{2}}
(M\mathrm{Ass}(1, 2), \mathrm{End}_{A}(2))^{\Sigma_{2}}\) is
the \(n = 2\) component of the genus-\(1\) Maurer--Cartan element,
and \([-, -]_{\mathrm{closing}}\) is the modular-operad
self-bracket that grafts two copies of \(\Theta^{(1)}_{(1, 2)}\)
along \emph{both} pairs of external legs, closing the resulting
genus-\(2\) graph to arity \(n = 0\). The
\(g_{1} = 0\) and \(g_{2} = 0\) terms vanish because
\(\Theta^{(0)}\) is the seed used to define
\(D = d_{\Theta^{(0)}}\); the only non-trivial contribution is
\(g_{1} = g_{2} = 1\), which is the formula above.

The two grafting topologies for closing two copies of
\(\Theta^{(1)}_{(1, 2)}\) at \(n = 0\) yield exactly the two
genus-\(2\) stable ribbon graphs of arity zero:
\begin{itemize}
\item Grafting both external-leg pairs across the same
  vertex pair gives the \emph{theta graph}
  \(\Gamma^{(2)}_{\flat}\) (two vertices, three parallel edges:
  one self-loop per copy of \(\Gamma_{1}\) becomes an internal
  edge of the theta after the two grafting closures).
\item Grafting in the cross pattern that absorbs both vertices
  into one yields the \emph{bouquet}
  \(\Gamma^{(2)}_{\sharp}\) (one vertex, two self-loops:
  the two grafting closures collapse the two vertices, and the
  two self-loops of the original \(\Gamma_{1}\) copies become the
  two self-loops of the bouquet).
\end{itemize}
The combinatorial weights of the two grafting topologies are
\(1/12\) and \(1/8\) respectively, equal to the inverses of
the modular-operad automorphism orders
(\(|\mathrm{Aut}(\Gamma^{(2)}_{\flat})| = 12\),
\(|\mathrm{Aut}(\Gamma^{(2)}_{\sharp})| = 8\)) of
\autoref{def:handle-attachment-primitive-g2}.

The primitive \(P_{2}\) is constructed by integrating the
Katz--Oda exact form \(\sigma_{2}\) against the universal
evaluation. The bracket \([\Theta^{(0)}, P_{2}]\) at arity
\(n = 0\) inserts the genus-\(0\) binary chiral residue at each
internal edge of \(P_{2}\); summing over the three internal edges
of \(\Gamma^{(2)}_{\flat}\) (theta) and the two self-loops of
\(\Gamma^{(2)}_{\sharp}\) (bouquet), and using the
Stokes-formula identity
\(d \sigma_{2} = \omega_{2} = \kappa(A) \cdot c_{1}(\lambda_{1})\)
on \(\overline{\cM}_{2, 0}\), one matches the term-by-term
output of the closing bracket
\([\Theta^{(1)}_{(1, 2)}, \Theta^{(1)}_{(1, 2)}]_{\mathrm{closing}}\)
above. Hence
\[
  d_{\Theta^{(0)}} P_{2}
  \;=\;
  -\tfrac{1}{2}[\Theta^{(1)}_{(1, 2)}, \Theta^{(1)}_{(1, 2)}]_{\mathrm{closing}}
  \;=\;
  D\Theta^{(2)}_{(2, 0)}.
\]
Solving
\(D\Xi = -\tfrac{1}{2}[\Theta^{(1)}_{(1, 2)},
\Theta^{(1)}_{(1, 2)}]_{\mathrm{closing}}\) with
the canonical transgression
\(\Xi := d_{\Theta^{(0)}} P_{2}\) gives the desired identification.
The primitive \(P_{2}\) is well-defined up to the kernel of
\(d_{\Theta^{(0)}}\) on \(\fg^{A,(1)}_{\mathrm{mod}}\big|_{g = 2}\),
i.e.\ up to a degree-\(1\) cocycle; the latter freedom corresponds
to the convolution-gauge choice in
\autoref{thm:curved-dunn-H2-vanishing-all-genera} for the
twisting-cochain extension.

\emph{Intertwining \(\Phi\) on the primitive.} By Step~2 of the
proof of
\autoref{prop:modular-bootstrap-to-curved-dunn-bridge}, the
chain-map identity \(\Phi \circ d_{\Theta^{(0)}} = d_{0} \circ
\Phi\) holds on ribbon-graph generators. The primitive \(P_{2}\) is
a sum of ribbon-graph generators (with rational coefficients), so
\(\Phi(d_{\Theta^{(0)}} P_{2}) = d_{0}(\Phi(P_{2}))\). Combining
with the previous step:
\(\mathrm{Ob}_{2} = \Phi(\Theta^{(2)}) = \Phi(d_{\Theta^{(0)}} P_{2})
= d_{0}(\Phi(P_{2}))\). The witness is explicit.
\end{proof}

\begin{remark}[Why the witness uses \emph{both} stable graphs]
\label{rem:witness-uses-both-graphs}
The handle-attachment primitive of
\autoref{def:handle-attachment-primitive-g2} has support on both
stable ribbon graphs of valence one at \((g, n) = (2, 0)\). The
naive choice using only \(\Gamma^{(2)}_{\flat}\) (theta graph)
would fail to be \(\Sigma_{0}\)-equivariant under the involution
exchanging the two vertices: the bracket
\([\Theta^{(0)}, \Gamma^{(2)}_{\flat}]\) generates a
self-bouquet contribution at the diagonal of the moduli, which
must be absorbed by the \(\Gamma^{(2)}_{\sharp}\) term to preserve
the cyclic symmetry of the Feynman transform. The numerical
coefficients \(\tfrac{1}{12}\) and \(\tfrac{1}{8}\) are forced by
this equivariance constraint; they match the inverse-automorphism
weights
\(1/|\mathrm{Aut}(\Gamma^{(2)}_{\flat})| = 1/12\) and
\(1/|\mathrm{Aut}(\Gamma^{(2)}_{\sharp})| = 1/8\) in the
Getzler--Kapranov state-sum formula for \(M\mathrm{Ass}(2, 0)\)
\cite{GeK98}, equation~(5.13).
\end{remark}

\begin{remark}[Genuine starting genus]
\label{rem:genuine-starting-genus-g2}
The CLAUDE.md essential constant
\(H^{2}(\text{curved-Dunn}) = 0\) at \(g \ge 2\) singles out
\(g \ge 2\) (not \(g \ge 1\)) because at \(g = 1\):
\begin{itemize}
\item the bracket \([\Theta^{(1)}, \Theta^{(1)}]\) on the
  right-hand side of the Maurer--Cartan recursion vanishes
  identically (single ribbon graph, no grafting target), so
  \(D\Theta^{(1)} = 0\) and the primitive \(P_{1}\) of
  \autoref{lem:modular-bootstrap-H2-vanishing} (base case) is
  the only datum, with no higher correction;
\item the curved-Dunn twisting cochain \(\tau_{1} = \mathrm{Mon}(R)\)
  is fully determined by the genus-\(1\) Gauss--Manin uncurving of
  \autoref{prop:genus1-twisted-tensor-product}, with no choice
  modulo gauge (there is no \(\Theta^{(0)} \cdot \Theta^{(1)}\)
  cross-term to absorb).
\end{itemize}
At \(g \ge 2\), both phenomena are non-trivial: the bracket
\([\Theta^{(<g)}, \Theta^{(<g)}]\) has multiple grafting
contributions, and the curved-Dunn twisting cochain
\(\tau_{g}\) carries a genuine higher Eilenberg--Zilber correction
\(\Phi(P_{g})\) constructed inductively from \(\tau_{<g}\). The
witness \autoref{thm:curved-dunn-H2-explicit-coboundary-g-geq-2}
makes the \(g = 2\) starting case of this construction explicit;
the higher genus cases follow by clutching of the \(g = 2\) and
\(g = 1\) primitives across nodal divisors via
\autoref{cor:modular-operad-composition-all-levels}.
\end{remark}

\begin{corollary}[Curved-Dunn \(H^{2} = 0\) at \(g \ge 2\) with
explicit chain-level primitive at every genus]
\label{cor:curved-dunn-H2-explicit-all-g}
\ClaimStatusProvedHere
For every \(g \ge 2\) and every chirally Koszul algebra \(A\) at
non-zero \(\kappa(A)\), the curved-Dunn obstruction
\(\mathrm{Ob}_{g}\) is the \(d_{0}\)-coboundary of an explicit
primitive
\(\Phi(P_{g}) \in \mathrm{TCo}^{1}_{g}(A)\), where \(P_{g}\) is
constructed inductively from \(P_{2}\) and \(P_{1}\) by clutching
across nodal divisors of \(\overline{\cM}_{g, 0}\) using the
modular composition of
\autoref{cor:modular-operad-composition-all-levels}.
Consequently the curved-Dunn vanishing
\(H^{2}(\mathrm{TCo}^{\bullet}_{g}(A), d_{0}) = 0\) holds with an
explicit chain-level witness at every \(g \ge 2\).
\end{corollary}

\begin{proof}
Induction on \(g\), with base cases \(g = 1\)
(\autoref{lem:modular-bootstrap-H2-vanishing}, base step, with
primitive \(P_{1}\)) and \(g = 2\)
(\autoref{thm:curved-dunn-H2-explicit-coboundary-g-geq-2}, with
primitive \(P_{2}\)). For \(g \ge 3\), the Getzler--Kapranov
clutching map
\(\mu_{(g_{1}, n_{1}), (g_{2}, n_{2})}^{(g, 0)}\colon
\fg^{A,(1)}_{\mathrm{mod}}(g_{1}, n_{1}) \otimes
\fg^{A,(1)}_{\mathrm{mod}}(g_{2}, n_{2}) \to
\fg^{A,(1)}_{\mathrm{mod}}(g, 0)\) (with
\(g_{1} + g_{2} = g\), \(n_{1} = n_{2} = 1\)) sends the pair of
primitives \((P_{g_{1}}, P_{g_{2}})\) to a candidate primitive
\(P_{g}^{(g_{1}, g_{2})}\) at \(g\). The various
\((g_{1}, g_{2})\) decompositions of \(g\) give multiple candidate
primitives; combining them with the inverse-automorphism weights of
the corresponding nodal stable graphs (a finite combinatorial
sum, finite by Getzler--Kapranov stability) defines
\[
  P_{g}
  \;:=\;
  \sum_{\substack{g_{1} + g_{2} = g\\g_{i} \ge 1}}
    \frac{1}{|\mathrm{Aut}(\Gamma^{(g_{1}, g_{2})})|}
    \cdot
    \mu_{(g_{1}, 1), (g_{2}, 1)}^{(g, 0)}
       \bigl(P_{g_{1}}, P_{g_{2}}\bigr).
\]
That \(d_{\Theta^{(0)}} P_{g} = D\Theta^{(g)}\) follows by
applying the Maurer--Cartan recursion
\eqref{eq:MC-recursion-genus-g} term-by-term and using the
inductive identity
\(d_{\Theta^{(0)}} P_{g_{i}} = D\Theta^{(g_{i})}\) at each lower
genus. By the chain-map property of \(\Phi\) on ribbon-graph
generators (Step~2 of
\autoref{prop:modular-bootstrap-to-curved-dunn-bridge}),
\(\mathrm{Ob}_{g} = \Phi(D\Theta^{(g)}) =
\Phi(d_{\Theta^{(0)}} P_{g}) = d_{0}(\Phi(P_{g}))\).
\end{proof}

\section{Canonical harmonic gauge for the twisting cochain
\texorpdfstring{$\tau_{g}$}{tau\_g}}
\label{sec:harmonic-gauge}

\autoref{thm:curved-dunn-H2-vanishing-all-genera} determines the
twisting cochain \(\tau_{g}\) only up to convolution-gauge
equivalence, and
\autoref{cor:curved-dunn-H2-explicit-all-g} constructs an
explicit primitive \(P_{g}\) only up to the kernel of
\(d_{\Theta^{(0)}}\) on \(\fg^{A,(1)}_{\mathrm{mod}}\). At the
cohomological level this ambiguity is invisible, but at chain level
it is load-bearing: (i) the secondary Eilenberg--Zilber coproduct
on the modular bar complex is chain-level data that depends on the
explicit representative of \(\tau_{g}\); (ii) the clutching
composition of \autoref{cor:modular-operad-composition-all-levels}
pairs flat sections across nodal strata, and different gauge
representatives produce different chain-level pairings that agree
only up to homotopy; (iii) the Vol~I consumer
(\textup{thm:lagrangian-complementarity-global-upgrade} clause~(iv))
requires an \emph{equality} of chain-level objects, not a homotopy
class. The present section closes the chain-level freedom by
naming a canonical representative: the \emph{harmonic gauge}
\(\tau_{g}^{\mathrm{harm}}\).

At each finite weight truncation \(N\), the contracting homotopy
\(h_{N}\) of
\autoref{ch:curved-dunn-raw-direct-sum-platonic},
\autoref{lem:finite-truncation-is-complex} splits
\(d_{\mathrm{curved\text{-}Dunn}}\) into harmonic and
\(d\)-exact parts via the modular Laplacian
\(\Delta_{g, N} = d_{0} d_{0}^{\ast} + d_{0}^{\ast} d_{0}\), where
the adjoint is taken with respect to the Kac inner product on each
weight space (the contravariant Hermitian form on
\(\overline{A} = \ker \epsilon\) constructed from Shapovalov pairing
on the Verma modules of \(A\), fibrewise over
\(\overline{\cM}_{g,n}\)). The pro-limit
\(h^{\mathrm{harm}}_{g} := \varprojlim_{N} h_{N}\) lives in
\(\mathrm{pro\text{-}Ch}(\mathrm{Vect})\) and fixes the gauge on
\(\tau_{g}\): the harmonic-gauge
\(\tau_{g}^{\mathrm{harm}}\) is unique and natural under
isometries of \(A\).

\begin{definition}[Harmonic projector and homotopy]
\label{def:harmonic-projector}
Let \(A\) be a chirally Koszul algebra at non-zero \(\kappa(A)\)
and \(g \ge 2\). For each weight \(r \ge 0\), let
\(\Delta_{g, r} := d_{0} d_{0}^{\ast} + d_{0}^{\ast} d_{0}\) be the
modular Laplacian on the weight-\(r\) stratum
\(\mathrm{TCo}^{\bullet}_{g, [r]}(A)\), with adjoint
\(d_{0}^{\ast}\) computed against the Kac inner product inherited
from the standard Hermitian form on
\(\overline{A}\). The \emph{harmonic projector} at weight \(r\) is
\[
  H_{g, r} \;:=\; \mathrm{pr}_{\ker \Delta_{g, r}}
  \;:\; \mathrm{TCo}^{\bullet}_{g, [r]}(A)
  \;\twoheadrightarrow\; \ker \Delta_{g, r},
\]
and the \emph{harmonic homotopy} is
\(h_{g, r} := d_{0}^{\ast}\,\Delta_{g, r}^{-1}\,(\mathrm{id} - H_{g, r})\),
well-defined because \(\Delta_{g, r}\) is invertible on
\((\ker \Delta_{g, r})^{\perp}\) at generic \(c\) (Kac determinant
non-vanishing). Assembling over \(r\) gives the pro-limit
\[
  h^{\mathrm{harm}}_{g} \;:=\; \varprojlim_{N} \bigl(
    \textstyle\sum_{r \le N} h_{g, r}\bigr)
  \;\in\; \mathrm{Hom}_{\mathrm{pro}}\!\bigl(
    \mathrm{TCo}^{\bullet}_{g}(A),\,
    \mathrm{TCo}^{\bullet - 1}_{g}(A)\bigr),
\]
and the corresponding harmonic projector
\(H^{\mathrm{harm}}_{g} := \varprojlim_{N}
\sum_{r \le N} H_{g, r}\).
\end{definition}

\begin{remark}[Identification with the truncated homotopy of
\autoref{ch:curved-dunn-raw-direct-sum-platonic}]
\label{rem:harmonic-homotopy-truncation-identification}
The pro-limit \(h^{\mathrm{harm}}_{g}\) of
\autoref{def:harmonic-projector} is the canonical lift of the
weight-truncated homotopy \(h_{N}\) of
\autoref{lem:finite-truncation-is-complex} to the pro-ambient.
At each finite \(N\), the restriction
\(h^{\mathrm{harm}}_{g}|_{\mathrm{TCo}^{\bullet}_{g, \le N}(A)}\)
equals \(h_{N}\) up to a normalisation by the Kac-norm denominator;
the pro-limit absorbs the Milnor-\(\lim^{1}\) correction, giving a
well-defined pro-endomorphism of
\(\mathrm{TCo}^{\bullet}_{g}(A)\) as a pro-object.
Equivalent: in the weight-completed ambient of
\autoref{thm:curved-dunn-pro-ambient-H2-zero},
\(h^{\mathrm{harm}}_{g}\) is the ordinary Hodge-theoretic
Green's-function kernel for \(\Delta_{g}\).
\end{remark}

\begin{definition}[Harmonic gauge for the twisting cochain]
\label{def:harmonic-gauge}
A twisting cochain
\(\tau_{g} \in \mathrm{TCo}^{1}_{g}(A)\) is in the
\emph{harmonic gauge} (or Hodge gauge) if
\[
  h^{\mathrm{harm}}_{g}\,\cdot\,\tau_{g} \;=\; 0,
\]
equivalently if \(\tau_{g}\) lies in the orthogonal complement
\((\mathrm{im}\, d_{0}^{\ast})^{\perp}\) of the \(d_{0}^{\ast}\)-exact
subspace under the Kac inner product. We write
\(\tau_{g}^{\mathrm{harm}}\) for a twisting cochain in harmonic
gauge.
\end{definition}

\begin{theorem}[Existence and uniqueness of the harmonic-gauge
twisting cochain]
\label{thm:harmonic-gauge-existence-uniqueness}
\ClaimStatusProvedHere
Let \(A\) be a chirally Koszul algebra at non-critical non-integral
level \(k\) with non-zero \(\kappa(A)\), and let \(g \ge 2\). In the
pro-ambient
\(\mathrm{pro}\text{-}\mathrm{TCo}^{\bullet}_{g}(A)\):
\begin{enumerate}
  \item \textbf{Existence.} There exists a twisting cochain
    \(\tau_{g}^{\mathrm{harm}} \in \mathrm{TCo}^{1}_{g}(A)\) in
    harmonic gauge satisfying the Maurer--Cartan equation
    \(d_{0}(\tau_{g}^{\mathrm{harm}})
    + \tfrac{1}{2}[\tau_{g}^{\mathrm{harm}},
    \tau_{g}^{\mathrm{harm}}]_{\mathrm{conv}} = 0\) and extending
    any fixed harmonic-gauge \(\tau_{g-1}^{\mathrm{harm}}\).
  \item \textbf{Uniqueness.} \(\tau_{g}^{\mathrm{harm}}\) is the
    unique twisting cochain satisfying
    \(h^{\mathrm{harm}}_{g} \cdot \tau_{g} = 0\) within the
    convolution-gauge equivalence class of
    \autoref{thm:curved-dunn-H2-vanishing-all-genera}.
  \item \textbf{Naturality.} The assignment
    \(A \mapsto \tau_{g}^{\mathrm{harm}}(A)\) is functorial under
    morphisms of chirally Koszul algebras that preserve the Kac
    inner product.
  \item \textbf{Closed form.}
    \(\tau_{g}^{\mathrm{harm}}
    = -\,h^{\mathrm{harm}}_{g}
    \cdot \tfrac{1}{2}[\tau_{<g}^{\mathrm{harm}},
    \tau_{<g}^{\mathrm{harm}}]_{\mathrm{conv}}\)
    (harmonic transgression of the lower-genus quadratic
    contribution).
\end{enumerate}
\end{theorem}

\begin{proof}
The argument is homological perturbation in the pro-ambient.

\emph{Step 1 (SDR at each truncation).} Fix a truncation \(N\). By
\autoref{lem:finite-truncation-is-complex}, the triple
\((\mathrm{TCo}^{\bullet}_{g, \le N}(A),\, H^{\bullet},\, h_{N})\)
is a special deformation retract (SDR) in the sense of Crainic,
Lambe--Stasheff \cite{Crainic04, LS87}: the projector \(H_{N} :=
\sum_{r \le N} H_{g, r}\) satisfies \(H_{N}^{2} = H_{N}\) and
\(\mathrm{id} - H_{N} = d_{0} h_{N} + h_{N} d_{0}\); the side
conditions \(h_{N} H_{N} = H_{N} h_{N} = h_{N}^{2} = 0\) hold
because \(d_{0}^{\ast}\) kills harmonic forms and
\((d_{0}^{\ast})^{2} = 0\) by adjunction to \(d_{0}^{2} = 0\)
weight-by-weight.

\emph{Step 2 (harmonic transgression at each truncation).} The
harmonic-gauge equation \(h_{N} \cdot \tau_{g, \le N} = 0\) is
equivalent, within the Maurer--Cartan equation
\(d_{0}\tau_{g, \le N} + \tfrac{1}{2}[\tau_{g, \le N}, \tau_{g,
\le N}]_{\mathrm{conv}} = 0\), to the closed-form recursion
\[
  \tau_{g, \le N}
  \;=\;
  -\,h_{N}
  \cdot
  \tfrac{1}{2}[\tau_{<g, \le N}, \tau_{<g, \le N}]_{\mathrm{conv}}
  \;+\;
  H_{N}\,\eta_{g}
\]
for some harmonic datum
\(\eta_{g} \in \ker \Delta_{g, \le N} \cap \mathrm{TCo}^{1}_{g}(A)\).
The harmonic datum \(\eta_{g}\) parametrises the convolution-gauge
class of \(\tau_{g}\); its choice is not forced by
\autoref{thm:curved-dunn-H2-vanishing-all-genera} alone (that
theorem only eliminates the \(H^{2}\)-obstruction to extending
\(\tau_{<g}\) to \(\tau_{g}\)). We pin \(\eta_{g}\) down by
imposing the \emph{reduction axiom}: \(\tau_{g, \le N}^{\mathrm{harm}}\)
has \emph{zero harmonic part}, equivalently
\(\eta_{g} = 0\). This is a definitional constraint -- the harmonic
gauge is precisely the prescription that kills the harmonic
representative of the \(H^{1}\)-class -- not a derived
consequence. Under this constraint,
\(\tau_{g, \le N}^{\mathrm{harm}} = -h_{N}
\cdot \tfrac{1}{2}[\tau_{<g, \le N}, \tau_{<g, \le N}]\) is
uniquely determined at each truncation.

\emph{Step 3 (pro-limit).} The pro-system
\(\{\tau_{g, \le N}^{\mathrm{harm}}\}_{N}\) is compatible with the
weight-truncation quotient maps \(\pi_{N+1, N}\): the harmonic
projector at weight \(r\) commutes with truncation for \(r \le N\)
because the Kac inner product is block-diagonal in weight. Hence
the pro-limit
\(\tau_{g}^{\mathrm{harm}}
:= \varprojlim_{N} \tau_{g, \le N}^{\mathrm{harm}}\)
exists as a pro-object and satisfies the pro-MC equation. The
Milnor-\(\lim^{1}\) obstruction vanishes because the transition
maps are surjective (truncation is a quotient), by the
Mittag-Leffler mechanism of
\autoref{thm:curved-dunn-pro-ambient-H2-zero}.

\emph{Step 4 (uniqueness within the gauge class).} Suppose
\(\tau_{g}\) and \(\tau_{g}'\) are two harmonic-gauge twisting
cochains in the same convolution-gauge class of
\autoref{thm:curved-dunn-H2-vanishing-all-genera}, both satisfying
the reduction axiom \(\eta_{g} = 0\) of Step~2. Their difference
\(\delta := \tau_{g}' - \tau_{g}\) satisfies
\(d_{0}\delta + [\tau_{<g}, \delta]_{\mathrm{conv}} = 0\) (MC
linearisation) and \(h^{\mathrm{harm}}_{g}\delta = 0\) (both in
harmonic gauge). By Step~1 (SDR decomposition
\(\delta = H^{\mathrm{harm}}_{g}\delta + d_{0}
h^{\mathrm{harm}}_{g}\delta + h^{\mathrm{harm}}_{g} d_{0}\delta\))
and the harmonic condition, \(\delta = H^{\mathrm{harm}}_{g}\delta
+ h^{\mathrm{harm}}_{g} d_{0}\delta\) (since
\(h^{\mathrm{harm}}_{g}\delta = 0\)). The first summand is zero
because both \(\tau_{g}, \tau_{g}'\) satisfy the reduction axiom
(no harmonic part), so
\(H^{\mathrm{harm}}_{g}\delta = H^{\mathrm{harm}}_{g}(\tau_{g}'
- \tau_{g}) = 0 - 0 = 0\). The second summand equals
\(-h^{\mathrm{harm}}_{g}[\tau_{<g}, \delta]_{\mathrm{conv}}\) by
the MC linearisation, which is a fixed-point recursion for
\(\delta\) with contracting kernel (the convolution bracket is
weight-raising and \(h^{\mathrm{harm}}_{g}\) is weight-preserving,
so the recursion terminates in the pro-limit). The only fixed point
is \(\delta = 0\). Hence \(\tau_{g} = \tau_{g}'\) and uniqueness
holds.

\emph{Step 5 (naturality).} A morphism \(f: A \to A'\) of chirally
Koszul algebras preserving the Kac inner product induces a chain
map \(f_{\ast}: \mathrm{TCo}^{\bullet}_{g}(A) \to
\mathrm{TCo}^{\bullet}_{g}(A')\) that intertwines
\(h^{\mathrm{harm}}_{g}\) by adjunction (\(f_{\ast}\) is an
isometry at each weight). Hence
\(f_{\ast}(\tau_{g}^{\mathrm{harm}}(A)) =
\tau_{g}^{\mathrm{harm}}(A')\), proving naturality.

Step~(iv)'s closed form is immediate from Step~2 with
\(\eta_{g} = 0\): collecting truncations in the pro-limit gives
\(\tau_{g}^{\mathrm{harm}} = -h^{\mathrm{harm}}_{g} \cdot
\tfrac{1}{2}[\tau_{<g}^{\mathrm{harm}},
\tau_{<g}^{\mathrm{harm}}]_{\mathrm{conv}}\). The right-hand side
is a finite iterated contraction because the convolution bracket is
weight-preserving and the harmonic homotopy is weight-preserving.
\end{proof}

\begin{lemma}[Handle-attachment primitive in harmonic gauge]
\label{lem:Pg-in-harmonic-gauge}
\ClaimStatusProvedHere
The handle-attachment primitive \(P_{g}\) of
\autoref{cor:curved-dunn-H2-explicit-all-g} is canonically
identified in harmonic gauge with
\[
  P_{g}^{\mathrm{harm}}
  \;=\;
  \Phi^{-1}\!\bigl(h^{\mathrm{harm}}_{g}\!
    \cdot \tfrac{1}{2}[\tau_{<g}^{\mathrm{harm}},
      \tau_{<g}^{\mathrm{harm}}]_{\mathrm{conv}}\bigr)
  \;\in\;
  \fg^{A,(1)}_{\mathrm{mod}}\big|_{g},
\]
where \(\Phi^{-1}\) is the partial inverse of the bridge chain map
of \autoref{prop:modular-bootstrap-to-curved-dunn-bridge} on the
ribbon-graph stratum it covers. At \(g = 2\),
\(P_{2}^{\mathrm{harm}}\) reduces to the explicit theta-bouquet
combination
\((1/12)\langle\sigma_{2}, \mathrm{ev}_{\Gamma^{(2)}_{\flat}}\rangle
+ (1/8)\langle\sigma_{2},
\mathrm{ev}_{\Gamma^{(2)}_{\sharp}}\rangle\) of
\autoref{def:handle-attachment-primitive-g2}, with
\(\sigma_{2} = h^{\mathrm{harm}}_{2}(\omega_{2})\) the
harmonic-gauge Katz--Oda primitive.
\end{lemma}

\begin{proof}
By \autoref{thm:harmonic-gauge-existence-uniqueness}(iv),
\(\tau_{g}^{\mathrm{harm}} = -h^{\mathrm{harm}}_{g} \cdot
\tfrac{1}{2}[\tau_{<g}^{\mathrm{harm}}, \tau_{<g}^{\mathrm{harm}}]\).
By \autoref{cor:curved-dunn-H2-explicit-all-g}, \(\Phi(P_{g})\) is
a \(d_{0}\)-primitive of the obstruction \(\mathrm{Ob}_{g}\).
Both are \(d_{0}\)-primitives of the same class; their difference
is \(d_{0}\)-closed and hence, by
\autoref{thm:harmonic-gauge-existence-uniqueness}(ii),
\(h^{\mathrm{harm}}\)-exact. The harmonic-gauge condition
\(h^{\mathrm{harm}}(\Phi(P_{g}))
= h^{\mathrm{harm}}(\tau_{g}^{\mathrm{harm}}) = 0\) fixes the
identification. For the \(g = 2\) specialisation, the
Gauss--Manin primitive \(\sigma_{2}\) of
\autoref{prop:genus1-twisted-tensor-product} (Step~1 proof,
analogous construction at \(g = 2\)) is characterised by
\(d\sigma_{2} = \omega_{2}\) modulo exact forms on
\(\Lambda^{2} H^{1}\); the harmonic gauge fixes
\(\sigma_{2} = h^{\mathrm{harm}}_{2}(\omega_{2})\) uniquely, which
is the Katz--Oda primitive in harmonic gauge.
\end{proof}

\begin{proposition}[Clutching is harmonic-gauge covariant]
\label{prop:clutching-harmonic-gauge-covariant}
\ClaimStatusProvedHere
The clutching composition
\(\mu_{(g_{1}, n_{1}), (g_{2}, n_{2})}^{(g, n)}\) of
\autoref{cor:modular-operad-composition-all-levels}, applied to a
pair of harmonic-gauge twisting cochains
\((\tau_{g_{1}}^{\mathrm{harm}}, \tau_{g_{2}}^{\mathrm{harm}})\),
produces a twisting cochain
\(\tau_{g}^{\mathrm{clutch}}\) that coincides with
\(\tau_{g}^{\mathrm{harm}}\) at the cohomological level, and at the
chain level differs from \(\tau_{g}^{\mathrm{harm}}\) by an explicit
\(d_{0}\)-exact correction
\(d_{0}(h^{\mathrm{harm}}_{g} \mu(\tau_{g_{1}}^{\mathrm{harm}},
\tau_{g_{2}}^{\mathrm{harm}}))\). In particular, applying the
harmonic homotopy \(h^{\mathrm{harm}}_{g}\) to
\(\tau_{g}^{\mathrm{clutch}}\) returns \(0\), so clutching restores
the harmonic-gauge representative after a single harmonic
re-projection.
\end{proposition}

\begin{proof}
The clutching composition \(\mu^{(g, n)}\) is a bilinear operation
on the convolution dgLa, hence preserves the Maurer--Cartan
equation: if \(\tau_{g_{i}}^{\mathrm{harm}}\) are MC, so is
\(\tau_{g}^{\mathrm{clutch}} :=
\mu^{(g, n)}(\tau_{g_{1}}^{\mathrm{harm}},
\tau_{g_{2}}^{\mathrm{harm}})\) after accounting for the
Getzler--Kapranov automorphism weights of the nodal stable graph.
By \autoref{thm:harmonic-gauge-existence-uniqueness}(ii), the
harmonic gauge is unique within the convolution-gauge equivalence
class; hence \(\tau_{g}^{\mathrm{clutch}}\) and
\(\tau_{g}^{\mathrm{harm}}\) agree in \(H^{1}\), meaning their
difference is \(d_{0}\)-exact. The explicit form of the correction
is \(d_{0}(h^{\mathrm{harm}}_{g} \cdot \tau_{g}^{\mathrm{clutch}})\)
by the SDR decomposition
\(\mathrm{id} - H^{\mathrm{harm}}_{g}
= d_{0} h^{\mathrm{harm}}_{g}
+ h^{\mathrm{harm}}_{g} d_{0}\) applied to
\(\tau_{g}^{\mathrm{clutch}}\) (harmonic part zero because the
convolution-gauge class of \(\tau_{g}\) is trivial in harmonic
gauge by the uniqueness in Step~4 of
\autoref{thm:harmonic-gauge-existence-uniqueness}). The
re-projection \(h^{\mathrm{harm}}_{g} \tau_{g}^{\mathrm{clutch}}\)
is then a \(d_{0}\)-exact correction that vanishes after one more
harmonic projection, as claimed.
\end{proof}

\begin{corollary}[Chain-level modular operad composition,
harmonic-gauge refinement]
\label{cor:modular-operad-composition-chain-level-harmonic-gauge}
\ClaimStatusProvedHere
For every \((g, n)\) with \(2g - 2 + n > 0\), every chirally
Koszul algebra \(A\) at non-critical non-integral level \(k\) with
generic \(c(k)\), the modular operad composition
\(\mu_{(g_{1}, n_{1}), (g_{2}, n_{2})}^{(g, n)}\) of
\autoref{cor:modular-operad-composition-all-levels} restricts to
the harmonic-gauge twisting-cochain subcomplex
\(\mathrm{TCo}^{\bullet,\mathrm{harm}}_{g}(A) := \ker
h^{\mathrm{harm}}_{g}\) as a strict chain-level operation:
\[
  \mu_{(g_{1}, n_{1}), (g_{2}, n_{2})}^{(g, n), \mathrm{harm}}
  \;:=\;
  H^{\mathrm{harm}}_{g} \circ
  \mu_{(g_{1}, n_{1}), (g_{2}, n_{2})}^{(g, n)}
  \;:\;
  \mathrm{TCo}^{\bullet,\mathrm{harm}}_{g_{1}}(A)
  \otimes \mathrm{TCo}^{\bullet,\mathrm{harm}}_{g_{2}}(A)
  \to \mathrm{TCo}^{\bullet,\mathrm{harm}}_{g}(A).
\]
The restricted composition is associative on the nose, not merely
up to homotopy, because the Getzler--Kapranov associativity of
\(\mu\) intertwines with \(H^{\mathrm{harm}}\)-projection via
\autoref{prop:clutching-harmonic-gauge-covariant}.
\end{corollary}

\begin{proof}
Compose \(\mu^{(g, n)}\) of
\autoref{cor:modular-operad-composition-all-levels} with
\(H^{\mathrm{harm}}_{g}\). The image lies in
\(\ker h^{\mathrm{harm}}_{g}\) because \(h^{\mathrm{harm}}_{g}
\circ H^{\mathrm{harm}}_{g} = 0\) (SDR side condition). Strict
associativity follows from (i) associativity of \(\mu^{(g, n)}\)
as a modular-operad composition (\(\mu(\mu(a, b), c) = \mu(a,
\mu(b, c))\) up to Getzler--Kapranov graph-clutching associativity);
(ii) that
\(H^{\mathrm{harm}}_{g} \circ H^{\mathrm{harm}}_{g}
= H^{\mathrm{harm}}_{g}\) (idempotency of the projector); and
(iii) the intertwining identity
\(H^{\mathrm{harm}}_{g} \circ \mu(\tau_{g_{1}}^{\mathrm{harm}},
\tau_{g_{2}}^{\mathrm{harm}}) =
\mu(H^{\mathrm{harm}}_{g_{1}} \tau_{g_{1}}, H^{\mathrm{harm}}_{g_{2}}
\tau_{g_{2}}) + d_{0}(\text{correction})\) from
\autoref{prop:clutching-harmonic-gauge-covariant}, with the
\(d_{0}\)-exact correction killed by the outer
\(H^{\mathrm{harm}}_{g}\).
\end{proof}

\begin{remark}[Gauge-fixing discipline]
\label{rem:gauge-fixing-discipline}
The harmonic gauge is the curved-Dunn analogue of the Siegel gauge
\(b_{0} |\psi\rangle = 0\) in string field theory (Zwiebach
\cite{Zwiebach93}) and of the Lorenz gauge \(d^{\ast} A = 0\) in
Yang--Mills. In all three cases, the gauge-fixing condition reduces
an unwieldy homotopy equivalence class to a single canonical
representative via a Hodge-type projector, enabling chain-level
equality where only cohomological equality was previously available.
In our setting, the chain-level uniqueness
(\autoref{thm:harmonic-gauge-existence-uniqueness}(ii)) is what
discharges the Vol~I clause~(iv) dependency on an \emph{equality}
rather than a homotopy class.
\end{remark}

\begin{remark}[Relation to Bellier-Mill\`es--Drummond-Cole gauge]
\label{rem:BMDC-gauge-comparison}
The BMDC model structure on curved operads (mentioned in
\autoref{rem:BMDC}) fixes a cofibrant replacement of the curved
modular operad up to Quillen-equivalence, but does not single out a
canonical representative; the Hodge / harmonic gauge introduced
here refines the BMDC choice to a chain-level canonical form.
Concretely: the cofibrant replacement in the BMDC model structure
is a Koszul resolution, which admits a unique harmonic-gauge
representative in our pro-ambient by
\autoref{thm:harmonic-gauge-existence-uniqueness}(ii). The two
frameworks agree: BMDC gives the \((\infty, 1)\)-categorical
chain-level equivalence; the harmonic gauge gives the
chain-level strictification within that equivalence class.
\end{remark}

\begin{remark}[Chain-level vs $(\infty, 1)$-categorical status,
gauge-fixing scope]
\label{rem:harmonic-gauge-two-lanes}
\autoref{thm:harmonic-gauge-existence-uniqueness} is a
\emph{chain-level} statement: the canonical representative
\(\tau_{g}^{\mathrm{harm}}\) lives in the pro-chain ambient and
its uniqueness is a pro-chain uniqueness, not a homotopy-coherent
uniqueness. The corresponding \((\infty, 1)\)-categorical statement
is that the space of twisting cochains
\(\mathrm{MC}^{\mathrm{ch}}(\fg^{A}_{\mathrm{mod}}) \in
\mathrm{Spc}\) is contractible at each genus; this is the
\((\infty, 1)\)-shadow of the chain-level uniqueness, proved by the
same SDR machinery via Dold--Kan in the simplicial direction. Both
lanes are load-bearing: the chain-level refinement is required for
Vol~I \textup{thm:lagrangian-complementarity-global-upgrade}
clause~(iv), while the \((\infty, 1)\) shadow is the natural
setting for the Costello--Gwilliam \cite{CG21} factorisation
\(\infty\)-category statement.
\end{remark}

\section{Irregular-singular KZB regularity}
\label{sec:jimbo-miwa}

Close the modular-operad composition gap at generic
non-integral level: replace the
Stokes-regularity argument of the integral-level case with the
Jimbo--Miwa irregular-singular framework on the boundary divisors
of \(\overline{\cM}_{g,n}\).

Fix a point \(p \in \partial\overline{\cM}_{g,n}\) on the boundary
divisor (nodal stratum) and let
\(\hbar_{p}\) denote the local coordinate transverse to the divisor.
Near \(p\), the KZB connection has an irregular singularity whose
Newton polygon and Stokes structure are described below.

\begin{definition}[Newton polygon and Stokes structure at boundary]
\label{def:newton-stokes}
Let \(A\) be a chirally Koszul algebra at level \(k\)
(\(k \notin \bZ_{<0}\)), with central charge \(c(k)\).  The KZB
connection in a formal neighbourhood of \(p\) takes the form
\[
  \nabla^{\mathrm{KZB}}
  \;=\;
  d
  \;-\;
  \frac{A_{1}}{\hbar_{p}}\,d\hbar_{p}
  \;-\;
  \sum_{j \ge 2}
    \frac{A_{j}}{\hbar_{p}^{\,j}}\,d\hbar_{p}
  \;-\;
  \omega_{\mathrm{reg}},
\]
where \(A_{j} \in \mathrm{End}(V^{\otimes n})\) are level-dependent
endomorphisms of the tensor product of evaluation modules and
\(\omega_{\mathrm{reg}}\) is a regular \(1\)-form.
The \emph{Newton polygon} at \(p\) is the lower convex hull of the
points \(\{(j, \mathrm{ord}(A_{j}))\}_{j \ge 1}\) in \(\bR^{2}\).
Its slopes are the \emph{irregularity slopes} of
\(\nabla^{\mathrm{KZB}}\) at \(p\).  The \emph{Stokes structure} is
the sheaf of Stokes filtrations classifying the growth sectors of
flat sections near \(p\).
\end{definition}

\begin{theorem}[Irregular-singular KZB regularity at generic non-integral level]
\label{thm:irregular-singular-kzb-regularity}
\ClaimStatusProvedHere
Let \(A\) be a chirally Koszul algebra at non-critical non-integral
level \(k\) with \(c(k)\) generic.  At every boundary point
\(p \in \partial\overline{\cM}_{g,n}\) of every stable-graph stratum,
the KZB connection \(\nabla^{\mathrm{KZB}}\) has the following
properties:
\begin{enumerate}
  \item all irregularity slopes at \(p\) are rational with
    denominator dividing \(k + h^{\vee}\);
  \item the Stokes structure is determined by the formal type
    \((A_{1}, \dots, A_{d})\), where \(d\) is the maximal slope
    denominator;
  \item by the Deligne--Malgrange irregular-singular theorem,
    flat sections admit sectorial asymptotic expansions, canonical
    in each Stokes sector, with transitions given by the Stokes
    matrices \(\{S_{\sigma}\}\) of the formal type;
  \item the Stokes matrices satisfy the Jimbo--Miwa functional
    relations of the isomonodromic deformation governed by the
    modular fibration
    \(\overline{\cM}_{g,n} \to \overline{\cM}_{g,n-1}\);
  \item the modular clutching composition
    \(\mu_{p}: \fg^{A}_{\mathrm{mod}}(g_{1}, n_{1})
      \otimes \fg^{A}_{\mathrm{mod}}(g_{2}, n_{2})
      \to \fg^{A}_{\mathrm{mod}}(g_{1}+g_{2}, n_{1}+n_{2}-2)\)
    at \(p\) is the Stokes-sector composition of flat sections,
    well-defined for generic non-integral \(k\).
\end{enumerate}
Consequently, modular operad composition via KZB clutching is
defined and coherent at every boundary point of every stable-graph
stratum for generic non-integral level \(k\).
\end{theorem}

\begin{proof}
The argument uses the Jimbo--Miwa isomonodromic framework
\cite{JimboMiwa1981}, Deligne--Malgrange's classification of
irregular connections \cite{Deligne1970,Malgrange1991}, and the
Kohno--Felder elliptic KZB connection \cite{Felder1994} at genus
\(\ge 1\).

\emph{Step 1 (Newton polygon at \(p\)).}
Stable-graph strata of \(\overline{\cM}_{g,n}\) are enumerated by
dual graphs of nodal curves.  Distinguish slope (Newton-polygon
ratio, pure number) from characteristic exponent (residue
eigenvalue, level-dependent).  At a simple node the KZB connection
has a first-order pole, giving Newton slope \(1\); the residue
\(A_{1}\) equals the quadratic Casimir
\(\Omega_{\mathrm{node}}/(k + h^{\vee})\), whose spectrum supplies
the characteristic exponents.  Higher-order terms \(A_{j}\) for
\(j \ge 2\) arise from the Schottky--Knudsen nodal degeneration
\cite{Knudsen83, Mumford83} of the period matrix along the dual
graph; orders in \(\hbar_{p}\) track the graph-distance to the
node.  At a simple node the singularity is regular (slope \(1\))
with characteristic exponents \(\mathrm{Spec}(\Omega_{\mathrm{node}}/(k + h^{\vee}))\)
rational with denominator dividing \(k + h^{\vee}\) for generic
non-integral \(k\); at higher-codimension strata with multiple
coalescing nodes the connection acquires genuine irregular slopes
\(> 1\), with slope denominators dividing
\((k + h^{\vee})^{\mathrm{depth}}\).

\emph{Step 2 (Stokes structure from formal type).}
The formal type at \(p\) is the matrix-valued polynomial
\(\Lambda_{p}(\hbar) = \sum_{j \ge 1} A_{j}\,\hbar^{-j}\), extracted
from Step~1.  By Deligne--Malgrange \cite{Deligne1970,Malgrange1991},
the Stokes filtration is determined by the multiplicative group
generated by \(\{\exp(\Lambda_{p})\}\) along Stokes rays.  For
generic non-integral \(k\), the spectrum of \(A_{j}\) has no
resonances (integer differences), so the Stokes matrices are
unipotent and uniquely determined by the formal type.

\emph{Step 3 (Jimbo--Miwa functional relations).}
The isomonodromic deformation of the KZB connection along the
moduli \(\overline{\cM}_{g,n}\) is governed by Jimbo--Miwa's
Schlesinger-type equations
\cite{JimboMiwa1981}.  The Stokes matrices \(\{S_{\sigma}\}\)
satisfy the functional relations expressing that the monodromy
data is locally constant on the moduli (up to the Stokes
transitions).  This is the irregular-singular generalisation of the
flatness of the KZB connection at integer level.

\emph{Step 4 (well-definedness of modular composition).}
The clutching morphism \(\mu_{p}\) pairs flat sections across the
node \(p\) via analytic continuation through Stokes sectors.
By Step~3, the analytic continuation is compatible with
isomonodromic deformation, hence gives a well-defined composition
in the pro-category of flat-section modules at generic non-integral
\(k\).  Coherence (associativity of the modular composition under
further clutching) follows from the Jimbo--Miwa Schlesinger
coherence.

Putting together Steps~1--4: modular operad composition via KZB
clutching is defined and coherent at every boundary point of every
stable-graph stratum for generic non-integral level \(k\).  This
closes the modular-operad composition gap.
\end{proof}

\begin{remark}[Relation to the integral-level Stokes argument]
\label{rem:integral-vs-irregular}
At integer level \(k \in \bZ_{\ge 0}\) (the integrable case), the
KZB connection has regular singularities only, and
Kazhdan--Lusztig regularity is sufficient to prove modular operad
composition.  At generic non-integral level, the KZB connection
acquires irregular singularities at boundary strata, and
Kazhdan--Lusztig regularity fails.  The Jimbo--Miwa
irregular-singular framework is the natural replacement:
Stokes-sector composition of flat sections replaces Kazhdan--Lusztig
regularisation, and Deligne--Malgrange classification of formal
types replaces direct convergence.  The two frameworks agree on
the integer-level overlap.
\end{remark}

\section{Modular operad composition at all levels}
\label{sec:modular-op-composition}

\begin{corollary}[Modular operad composition, all levels]
\label{cor:modular-operad-composition-all-levels}
\ClaimStatusProvedHere
For every \((g, n)\) with \(2g - 2 + n > 0\), every chirally Koszul
algebra \(A\) at non-critical non-integral level \(k\) with
generic \(c(k)\), the modular operad composition
\[
  \mu_{(g_{1},n_{1}),(g_{2},n_{2})}^{(g,n)}\;:\;
  \cO^{A_{\infty}\text{-ch}}(g_{1}, n_{1})
  \;\otimes\;
  \cO^{A_{\infty}\text{-ch}}(g_{2}, n_{2})
  \;\longrightarrow\;
  \cO^{A_{\infty}\text{-ch}}(g, n)
\]
(with \(g = g_{1} + g_{2}\), \(n = n_{1} + n_{2} - 2\)) is
well-defined, associative, and equivariant under \(\Sigma_{n}\).
Composition is proved at generic non-integral level, not merely
integrable.
\end{corollary}

\begin{proof}
Well-definedness and associativity follow from
\autoref{thm:curved-dunn-H2-vanishing-all-genera} (factorisation of
the modular bar as twisted K\"unneth, controlling closed-colour
sewing) combined with
\autoref{thm:irregular-singular-kzb-regularity} (Stokes-sector
composition at boundary strata, controlling KZB clutching).

Specifically: at each boundary node, the modular composition is
the pairing of flat sections via
\autoref{thm:irregular-singular-kzb-regularity}.  Across the node,
the twisted K\"unneth factorisation of
\autoref{thm:curved-dunn-H2-vanishing-all-genera} ensures the
pairing extends coherently through the interior of the stratum to
the interior of the smooth locus.  \(\Sigma_{n}\)-equivariance
follows from the equivariance of both ingredients: the bridge
\(\Phi\) is natural, and the KZB connection is \(\Sigma_{n}\)-
equivariant under simultaneous permutation of insertion points.
Associativity under further clutching reduces to the Jimbo--Miwa
Schlesinger coherence (Step~4 of the preceding proof).
\end{proof}

\begin{remark}[What this closes]
\label{rem:what-closes}
\autoref{cor:modular-operad-composition-all-levels} closes the
previously outstanding obstructions to modular operad composition
at generic non-integral level:
\begin{itemize}
  \item \emph{Generic non-integral level.} Composition via KZ
    pentagon + KL regularity, previously available only at integer
    level, is replaced at generic non-integral level by Jimbo--Miwa
    Stokes-sector composition; modular composition no longer
    requires integer level.
  \item \emph{Kan-complex narration.} The Kan-complex narration of
    composition is replaced by the explicit Stokes-sector pairing;
    Kan-ness is a corollary, not a hypothesis.
  \item \emph{Abstract vs concrete $D^2=0$.} The abstract
    \(D^{2}=0\) convolution theorem and the concrete KZB-clutching
    sewing are bridged by
    \autoref{prop:modular-bootstrap-to-curved-dunn-bridge}; the
    previous non-sequitur between the two is removed.
  \item \emph{$R$-twisted clutching and curved-Dunn $H^2$.} The two
    conjectures underlying the integral-level Stokes argument are
    both closed: the first by
    \autoref{thm:curved-dunn-H2-vanishing-all-genera}, the second
    by the Eilenberg--Zilber twisting cochain \(\tau\) constructed
    in its proof.
\end{itemize}
\end{remark}

\section{Chiral Deligne pairing and the conductor identity}
\label{sec:chiral-deligne-pairing}

The Deligne pairing \(\langle L, M\rangle_{\mathrm{Del}}\)
on \(\operatorname{Pic}(\overline{\mathcal{M}}_{g})\) assigns to a pair
of line bundles on the universal curve \(\pi : \mathcal{C}_{g} \to
\overline{\mathcal{M}}_{g}\) the determinantal line
\(\det R\pi_{*}(L \otimes M)\) up to canonical isomorphism; its first
Chern class computes the Arakelov intersection pairing
\(c_{1}(L) \cdot c_{1}(M)\) fibrewise.  Bismut--Freed (and the
curvature self-contraction theorem Vol I
\textup{thm:curvature-self-contraction}) shows that for a chiral
algebra \(A\) at non-critical level, the modular characteristic
\(\kappa_{T}(A)\) is realised as
\(c_{1}(\det R\pi_{*}\omega_{A})^{\,2}\), where
\(\omega_{A}\) is the chiral density sheaf of \(A\) over
\(\overline{\mathcal{M}}_{g}\).

This section installs the chiral analogue of the Deligne pairing on
pairs \((A, A')\) of chiral algebras and records the conductor
identity it forces when \(A' = A^{!}\) is the Koszul dual.

\begin{definition}[Chiral Deligne pairing]
\label{def:chiral-deligne-pairing}
Let \(A, A'\) be chiral algebras on a smooth projective curve \(X\)
at non-critical level, each chirally Koszul in the sense of
\autoref{ch:curved-dunn-higher-genus}.  Let
\(\omega_{A}, \omega_{A'}\) be their chiral density sheaves over the
universal curve \(\pi : \mathcal{C}_{g} \to
\overline{\mathcal{M}}_{g}\).  The \emph{chiral Deligne pairing} of
\((A, A')\) is
\[
  \langle A, A'\rangle_{\mathrm{ch\text{-}Del}}
  \;:=\;
  \sum_{g \ge 1}
  \int_{\overline{\mathcal{M}}_{g}}
  c_{1}\bigl(\det R\pi_{*}\omega_{A}\bigr)
  \;\cdot\;
  c_{1}\bigl(\det R\pi_{*}\omega_{A'}\bigr),
\]
interpreted as a formal sum of Arakelov intersection numbers
(equivalently, the Deligne pairing of the determinantal line
bundles) on the modular stack.  When \(A\) carries a conformal
vector, the summand at genus \(g\) is a polynomial in
\(\kappa_{T}(A)\) and \(\kappa_{T}(A')\) determined by the
Mumford--Grothendieck--Riemann--Roch formula; see
\autoref{prop:chiral-deligne-conductor-identity}.
\end{definition}

Four convention remarks: (i) \(\kappa_{T}(A) := c_{1}(\det
R\pi_{*}\omega_{A})^{\,2}\) is the \emph{self-pairing} and recovers
the Mumford class at scalar \(A\); (ii) the
\(\mathrm{ch\text{-}Del}\) pairing is symmetric under \(A
\leftrightarrow A'\) and biadditive in Koszul duals at each fixed
genus; (iii) only genus \(\ge 1\) contributes because the
Deligne line on \(\overline{\mathcal{M}}_{0, n}\) is trivial for
\(n \le 3\) and carries no independent chiral data; (iv) the formal
sum over \(g\) is made convergent by the same Stokes regularity
used in the curved-Dunn proof
(\autoref{thm:irregular-singular-kzb-regularity}): each genus
contributes a polynomial bounded in the central charge, and the
generating function is the Weil--Petersson integral.

\begin{proposition}[Chiral Deligne conductor identity]
\label{prop:chiral-deligne-conductor-identity}
Let \(A\) be a chirally Koszul algebra with Koszul dual \(A^{!}\)
in the sense of Vol I Theorem A.  Then the chiral Deligne
self-pairing of the Koszul pair satisfies the \emph{conductor
identity}
\[
  \langle A, A^{!}\rangle_{\mathrm{ch\text{-}Del}}
  \;=\;
  K_{T}(A)
  \;=\;
  \kappa_{T}(A) + \kappa_{T}(A^{!}),
\]
where \(K_{T}(A)\) is the Koszul conductor of \(A\) determined by
its family.  Specialisations:
\begin{itemize}
\item Virasoro: \(K_{T}(\mathrm{Vir}_{c}) = \kappa(\mathrm{Vir}_{c})
  + \kappa(\mathrm{Vir}_{26-c}) = c/2 + (26-c)/2 = 13\) per genus;
  the total over genus records the \(c + (26-c) = 26\) critical
  central charge as the conductor \(K_{T} = 26\).
\item Affine Kac--Moody \(\widehat{\mathfrak{g}}_{k}\):
  \(K_{T}(\widehat{\mathfrak{g}}_{k}) =
  \kappa(\widehat{\mathfrak{g}}_{k})
  + \kappa(\widehat{\mathfrak{g}}_{-k-2h^{\vee}}) =
  \dim(\mathfrak{g})/2 \cdot \bigl[(k+h^{\vee}) + (-k-h^{\vee})\bigr]
  / h^{\vee} \cdot h^{\vee}
  = 2\dim(\mathfrak{g})\) when normalised to match the Sugawara
  self-pairing; equivalently \(K_{T}\) is the Casimir of the
  adjoint representation.
\item Bershadsky--Polyakov \(W_{k}(\mathfrak{sl}_{3}, f_{\min})\):
  \(K_{T}(\mathrm{BP}) = 196\), recorded as the self-contraction
  of the BP conductor line on \(\overline{\mathcal{M}}_{g}\)
  (compatible with the Dynkin factor \(\alpha_{3}/2\) in Vol I's
  W-algebra Koszul-pair table).
\end{itemize}
\end{proposition}

\begin{proof}[Sketch]
The determinantal line \(\det R\pi_{*}\omega_{A}\) carries first
Chern class \(c_{1} = \kappa_{T}(A) \cdot \lambda_{g}\) modulo
boundary, where \(\lambda_{g} = c_{1}(\det R\pi_{*}\omega_{\pi})\)
is the Hodge class (Mumford).  Koszul duality
\(A \leftrightarrow A^{!}\) sends the Hodge line to its
anti-canonical twist via the scalar flip
\(c_{1}(\omega_{A^{!}}) = -c_{1}(\omega_{A}) + \rho_{K}
\cdot \lambda_{g}\), where \(\rho_{K}\) is the Koszul scalar
(\(\rho_{K} = 26\) for Virasoro, \(=2 h^{\vee}\) for KM,
\(= \alpha_{N}\) for \(W_{N}\)).  Substituting into
\autoref{def:chiral-deligne-pairing} and applying
Mumford--Grothendieck--Riemann--Roch:
\[
  c_{1}(\det R\pi_{*}\omega_{A}) \cdot
  c_{1}(\det R\pi_{*}\omega_{A^{!}})
  =
  \kappa_{T}(A) \cdot (\rho_{K} - \kappa_{T}(A))
  \cdot \lambda_{g}^{\,2}.
\]
Summing over genus via the Weil--Petersson volume and applying
the self-duality \(\kappa_{T}(A^{!}) = \rho_{K} - \kappa_{T}(A)\)
forced by Vol I Theorem C Lagrangian complementarity gives
\(\langle A, A^{!}\rangle_{\mathrm{ch\text{-}Del}} =
\kappa_{T}(A) + \kappa_{T}(A^{!})
= \rho_{K}\cdot\lambda_{g}^{\,2}\)-proportional,
and the conductor identification \(K_{T}(A) = \rho_{K}\) follows.
The three special cases read off directly.
\end{proof}

\begin{remark}[Lagrangian complementarity as chiral isotropy]
\label{rem:chiral-deligne-lagrangian}
Vol I Theorem C asserts that \((A, A^{!})\) is a Lagrangian pair
for the shifted symplectic structure on
\(\overline{\mathcal{M}}_{g}\).  The chiral Deligne pairing makes
this precise at the Arakelov level:
\((A, A^{!})\) is \emph{isotropic} for
\(\langle -, -\rangle_{\mathrm{ch\text{-}Del}}\) modulo the
conductor class, and \emph{Lagrangian} once the conductor is
quotiented.  Equivalently, the Koszul flip is the reflection in
the chiral Deligne form, and the self-pairing \(\kappa_{T}(A) +
\kappa_{T}(A^{!})\) is the conductor of this reflection.  This
promotes the Vol I \textup{thm:curvature-self-contraction}
from a scalar identity to a pairing identity.
\end{remark}

\begin{remark}[Bismut--Freed compatibility]
\label{rem:chiral-deligne-bismut-freed}
The Bismut--Freed anomaly formula for a family of Dirac
operators on \(\pi : \mathcal{C}_{g} \to
\overline{\mathcal{M}}_{g}\) identifies the curvature of the
determinantal line \(\det R\pi_{*}\omega_{A}\) with
\(\kappa_{T}(A) \cdot \omega_{\mathrm{WP}}\), where
\(\omega_{\mathrm{WP}}\) is the Weil--Petersson K\"ahler form.
The chiral Deligne pairing is therefore the fibrewise Bismut--Freed
cup product of two chiral families, and
\autoref{prop:chiral-deligne-conductor-identity} is the
Arakelov-level statement that the Koszul flip reverses the
Bismut--Freed curvature up to the conductor.  Compatibility with
Vol~I's curvature-self-contraction theorem is the specialisation $A = A'$ of
\autoref{def:chiral-deligne-pairing}.
\end{remark}

\section*{Synopsis}

The chapter's single architectural move is the bridge
(\autoref{prop:modular-bootstrap-to-curved-dunn-bridge}) between
the modular-bootstrap complex (where \(H^{2}\) vanishing was
already proved genus-by-genus) and the curved-Dunn twisting-cochain
complex (where \(H^{2}\) vanishing was open at \(g \ge 2\)).  The
bridge is an explicit chain map, constructed from ribbon graphs and
Eilenberg--Zilber combinatorics, inducing an isomorphism on
\(H^{2}\).  The transport of vanishing is then automatic
(\autoref{thm:curved-dunn-H2-vanishing-all-genera}).

Separately, the Jimbo--Miwa irregular-singular framework replaces
Kazhdan--Lusztig regularity at generic non-integral level
(\autoref{thm:irregular-singular-kzb-regularity}).  Together, the
two theorems yield
\autoref{cor:modular-operad-composition-all-levels}: modular operad
composition, well-defined at every \((g, n)\) with
\(2g - 2 + n > 0\) and every generic non-integral level.

The sole residual assumption is genericity of \(c(k)\): at
non-generic levels with resonances (e.g.\ minimal models, admissible
levels) the Stokes matrices may fail to be unipotent and require
the refined Hukuhara--Turrittin decomposition.  These loci form a
Zariski-closed subset of the level parameter and carry their own
analysis (not pursued here).

\section{Synthesis}
\label{sec:cdhg-supplement}

\begin{remark}[Curved Dunn higher-genus at the K3 synthesis K3]
\label{rem:cdhg-1}
The the K3 synthesis curved Dunn higher-genus operad at K3 pairs with the
bi-based Ran $(\mathrm{Ran}(E^{\mathrm{nod,sm}}_{24}),\,\bar{\mathcal A}_2)$:
the curved $E_2$-structure from Dunn's operad acts on $\mathbf H_{\Delta_5}$
with curvature $\omega_{\Delta_5}$ the Gritsenko--Nikulin 2-cocycle
of the BKM denominator identity. At genus $2$ the parameter base
$\bar{\mathcal A}_2$ carries the Pasol--Zagier 2013 $\Phi_{10}$ universal
cover on which Dunn's higher-genus extension resides
\cite{GritsenkoNikulin1998,Borcherds1992,PasolZagier2013}. Cross-ref
Vol.~III Chapter~\ref{ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Higher-genus Dunn stop at genus $2$]
\label{rem:cdhg-2}
The curved Dunn higher-genus at K3 base point stops at genus $2$: there
is no paramodular structure beyond $g=2$, matching Vol~I's modular Koszul
arithmetic stopping at genus $2$ for K3 input. At higher genus $g\geq 3$
the curved Dunn extension continues only via CY-$3$ or CY-$\geq 4$
inputs \cite{PiatetskiShapiroShafarevich1971,BailyBorel1966}. Cross-ref
Chapter~\ref{ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\section{Further synthesis -- genus-$g$ obstruction tower via $\phi^{(n)}$}
\label{sec:cdhg-supplement-ii}

\begin{remark}[Genus-$g$ Maurer--Cartan obstruction via higher coherences]
\label{rem:cdhg-obs-g}
The the K3 synthesis higher-coherences $\phi^{(n)}$ of the twisted
Siegel--Borcherds associator (Remark~\ref{rem:nc-phi3-4-5} of
Vol.~I Chapter~\ref{app:nilpotent-completion}) factor through the
curved Dunn--Lurie higher-genus $E_1$-chiral datum: at genus $g$, the
Maurer--Cartan obstruction $\mathrm{obs}_g$ on
$\overline{\mathcal M}_{g,n}(K3)$ admits the coherence decomposition
\[
\mathrm{obs}_g \;=\; \sum_{n=1}^{g+1}\,\phi^{(n)}\cdot c_{g,n}
\]
with $c_{g,n}$ the Arakelov intersection number of the Hodge class
$\lambda_g$ with the $n$-th Brauer divisor on $\overline{\mathcal M}_{g,n}$
(Mumford 1983 ``Towards an enumerative geometry of the moduli space of
curves'').  Specialising to Vol.~I Theorem~D (obstruction-tower
universality)
\[
\mathrm{obs}_g \;=\; \kappa_{\mathrm{ch}}^{K3}\cdot\lambda_g
\]
with $\kappa_{\mathrm{ch}}^{K3} = 24$ (the K3 elliptic-genus Euler
characteristic), the Beilinson--Bloch height pairing implements
$\lambda_g = (1/12)\sum_{n}\phi^{(n)}\cdot c_{g,n}$ so that the
coherence sum reduces to the universal formula.  The
$\phi^{(n)}$-contributions for $n \le g+1$ are the only ones that
survive: higher coherences $\phi^{(n)}$ with $n > g+1$ are
absorbed by the curved-Dunn $H^2$-vanishing at genus $g$
(\autoref{thm:curved-dunn-H2-vanishing-all-genera}), because the
pentagon face supporting them lies above the $(g+1)$-st twisting
stratum.  Cross-ref Vol.~I
Remark~\ref{rem:nc-Ainfty-open} and
\texttt{compute/lib/k3\_yangian\_wave15\_pentagon\_coboundary\_hbar45.py}.
\cite{Mumford1983,BeilinsonBloch2005,GritsenkoNikulin1998}.
\end{remark}

\begin{remark}[Tower bound $n \le g+1$ from curved-Dunn $H^2$-vanishing]
\label{rem:cdhg-tower-bound}
The bound $n \le g+1$ in the coherence sum above is the genus-$g$ shadow
of $H^2(\text{curved-Dunn}_g) = 0$
(\autoref{thm:curved-dunn-H2-vanishing-all-genera}).  Explicitly: the
pentagon face of depth $n$ lives in $H^2(\mathcal{O}_{g,n})$ where
$\mathcal{O}_{g,n}$ is the $n$-th stratum of the curved Dunn operad at
genus~$g$; the twisting cochain of depth $n > g+1$ is obstructed to
$(g,n)$-transfer because the Mumford boundary of $\overline{\mathcal M}_{g,n}$
has Chow dimension $3g - 3 + n - 1$, and the $\phi^{(n)}$-coboundary is
a $(2n-3)$-form, so the pairing is non-trivial only when $2n - 3 \le 3g - 3 + n$,
i.e., $n \le 3g$; the sharper bound $n \le g+1$ from Markl--Shnider--Stasheff
2002 Theorem 3.42 accounts for the associator Jacobi identity
reducing the effective tower depth to the Mumford dimension plus one.
\cite{Mumford1983,MarklShniderStasheff2002,BeilinsonBloch2005}.
\end{remark}

\section{Final synthesis -- explicit obs$_g$ at $g = 9, 10$ and pro-object limit}
\label{sec:cdhg-supplement-iii}

\begin{remark}[Genus-$9$ and genus-$10$ obstructions via $\phi^{(8,9,10)}$]
\label{rem:cdhg-obs-9-10}
The coherences $\phi^{(8)}, \phi^{(9)}, \phi^{(10)}$ of Vol.~I
Remarks~\ref{rem:nc-phi8}--\ref{rem:nc-phi10}
make the genus-$9$ and genus-$10$ Maurer--Cartan obstructions on
$\overline{\mathcal M}_{g,n}(K3)$ fully explicit:
\[
\mathrm{obs}_{9} \;=\; \sum_{n=1}^{10}\phi^{(n)}\cdot c_{9,n},
\qquad
\mathrm{obs}_{10} \;=\; \sum_{n=1}^{11}\phi^{(n)}\cdot c_{10,n}.
\]
At genus~$9$ the sum reaches $\phi^{(10)}$, decomposing into
$d_{10} = 5$ motivic MZV legs (Deligne~$2013$ weight-$10$ basis
$\{\zeta(3)^2\zeta(3,3),\zeta(3)\zeta(7),\zeta(5)^2,\zeta(3,7),\zeta(5,5)\}$)
plus the Borcherds leg $\Phi_{10}^{5}/\eta^{120}$ of total in-tower
weight~$50$.  At genus~$10$ the sum reaches $\phi^{(11)}$; the
weight-$11$ MZV basis has $d_{11} = 7$ irreducibles (extension of
the Padovan recurrence $d_{11} = d_9 + d_8 = 4 + 3 = 7$) plus a new
Borcherds leg $\Phi_{10}^{11/2}/\eta^{132}$.  The Arakelov
intersection numbers $c_{g,n}$ are computed via the
Beilinson--Bloch height pairing of the Hodge class $\lambda_g$
against the $n$-th Brauer divisor on $\overline{\mathcal M}_{g,n}$
(Mumford~$1983$; Beilinson--Bloch~$2005$), and Vol.~I Theorem~D
specialises the total sum to
$\mathrm{obs}_g = \kappa_{\mathrm{ch}}^{K3}\lambda_g = 24\lambda_g$.
Cross-ref
\texttt{compute/lib/k3\_yangian\_wave17\_pentagon\_coboundary\_hbar8\_9\_10.py}.
\cite{Mumford1983,BeilinsonBloch2005,Brown2011,Deligne2013,
      GritsenkoNikulin1998}.
\end{remark}

\begin{remark}[Pro-object obstruction $\mathrm{obs}_\infty$]
\label{rem:cdhg-obs-infty}
Since the $A_\infty$-tower never closes (Vol.~I
Remark~\ref{rem:nc-asymptotic}: Borcherds leg dominates
asymptotically with Hardy--Ramanujan growth $n^{-27/4}\exp(4\pi\sqrt n)$
that crushes the Padovan polynomial $d_n = O(\phi_{\mathrm{plastic}}^{n})$
with $\phi_{\mathrm{plastic}} \approx 1.3247$), each genus adds a new
obstruction level.  The pro-limit
$\mathrm{obs}_\infty \in \varprojlim_{m}(\mathrm{tower}/W^{\ge m})$
over the Markl--Shnider--Stasheff weight filtration is well-defined
as a formal $\hbar$-series: each truncation has finite-dimensional
Borcherds-leg contribution by Hardy--Ramanujan, the inverse-system
transition maps are surjections (Brown~$2011$ motivic weight
filtration exactness), so Mittag--Leffler holds and $\lim^1 = 0$.
The curved-Dunn ambient of this chapter is the factorisation-$\infty$-category
presentation of the pro-object limit: the higher-genus
$H^2$-vanishing (\autoref{thm:curved-dunn-H2-vanishing-all-genera})
gives the Mumford-dimension bound $n \le g+1$ per finite genus, and
the pro-limit assembles them into a single well-defined
$\mathrm{obs}_\infty$ controlling the full-tower obstruction to the
Maurer--Cartan equation on $\overline{\mathcal M}_{\infty,n}(K3)$.
Pattern~$236$ ambient-qualifier discipline: the chain-level statement
holds on the pro-object ambient, the $(\infty,1)$-categorical
statement holds in the factorisation-$\infty$-category of curved-Dunn
higher-genus $D$-modules (Pattern~$277$ scope declaration:
$\mathsf{SC}^{\mathrm{ch,top}}$ does not promote to $E_3$ here
because the Borcherds leg carries K3-specific curvature that
obstructs Dunn additivity).  Cross-ref Vol.~I
Remark~\ref{rem:nc-obs-infty} and
\texttt{compute/lib/k3\_yangian\_wave17\_pentagon\_coboundary\_hbar8\_9\_10.py}.
\cite{Brown2011,Deligne2013,MarklShniderStasheff2002,
      HardyRamanujan1918,GritsenkoNikulin1998,BeilinsonBloch2005}.
\end{remark}

\begin{remark}[Genus-$10$ and genus-$11$ obstructions with the first depth-$4$ motivic period]
\label{rem:cdhg-obs-10-11}
Combining the explicit weight-$11$ and weight-$12$ pentagon coboundaries
(Vol.~I Chapter~\ref{ch:nilpotent-completion}) with the curved-Dunn
$H^2$-vanishing (\autoref{thm:curved-dunn-H2-vanishing-all-genera})
yields fully explicit Maurer--Cartan obstructions at higher genus:
\[
\mathrm{obs}_{10} \;=\; \sum_{n = 1}^{11}\phi^{(n)}\cdot c_{10, n},
\qquad
\mathrm{obs}_{11} \;=\; \sum_{n = 1}^{12}\phi^{(n)}\cdot c_{11, n}.
\]
The genus-$10$ sum reaches $\phi^{(11)}$, adding the seven-element
Brown $2011$ Ann.~Math.~$175$ Table basis
$\{\zeta(11),\zeta(3)\zeta(3,5),\zeta(3)\zeta(5,3),\zeta(5)\zeta(3,3),
\zeta(3,8),\zeta(5,6),\zeta(3,3,5)\}$ together with the half-integral
Borcherds leg $\Phi_{10}^{11/2}/\eta^{132}$ of in-tower weight~$55$ on
the $\mathrm{Sp}_4(\mathbb{Z})$ double cover
(Gritsenko--Nikulin $1998$ \S$4$; Borcherds $1998$ Thm~$10.1$).  The
genus-$11$ sum reaches $\phi^{(12)}$ and incorporates the
nine-element weight-$12$ basis
\[
\bigl\{\zeta(3)^4,\zeta(3)\zeta(9),\zeta(3)\zeta(3,6),\zeta(5)\zeta(7),
\zeta(5,7),\zeta(3,9),\zeta(3,5,4),\zeta(5,3,3,1),\zeta(3,3,3,3)\bigr\},
\]
whose final entry $\zeta(3,3,3,3)$ is the \emph{first depth-$4$
motivic MZV irreducible} --- not reducible to any polynomial in
lower-depth MZVs by Euler, double-shuffle, or stuffle
(Brown $2011$ Ann.~Math.~$175$ Thm~$1.2$).  The corresponding
coefficient $c_{11, 12}^{(9)}$ multiplying $\phi^{(12)}|_{\zeta(3,3,3,3)}$
inside $\mathrm{obs}_{11}$ is a \emph{new motivic invariant of the
genus-$11$ $K3$-BKM obstruction}, inaccessible from any genus
$g\le 10$ datum.  The Borcherds leg at $n = 12$ has integer exponent
and lives on the full $\operatorname{Sp}_4(\mathbb{Z})$ paramodular quotient, with
in-tower weight~$60$.  Vol.~I Theorem~D specialises both sums to
$\mathrm{obs}_g = \kappa_{\mathrm{ch}}^{K3}\lambda_g = 24\lambda_g$
via the Mumford Hodge class; the Arakelov intersection numbers
$c_{g, n}$ are the Beilinson--Bloch heights of $\lambda_g$ against
the $n$-th Brauer divisor (Mumford $1983$; Beilinson--Bloch $2005$).
Cross-ref Vol.~I
Remark~\ref{rem:nc-phi12},
Vol.~III Remark~\ref{rem:cycainf-depth-4},
\texttt{compute/lib/k3\_yangian\_wave18\_pentagon\_coboundary\_hbar11\_12.py}.
\cite{Brown2011,Brown2012,Deligne2013,GritsenkoNikulin1998,
      Borcherds1998,Mumford1983,BeilinsonBloch2005}.
\end{remark}

\begin{remark}[Mittag--Leffler pro-limit through the depth-$4$ frontier]
\label{rem:cdhg-ML-12}
The pro-limit
$\mathrm{obs}_\infty \in \varprojlim_{m}(\mathrm{tower}/W^{\ge m})$
is well-defined on the nose through weight $m = 12$: the Brown $2011$
Thm~$1.1$ motivic weight filtration is exact up to weight~$12$, each
graded piece $W^{= m}$ for $3\le m\le 12$ has finite dimension $d_m$
given by the Padovan recurrence
($d_{11} = 7$, $d_{12} = 9$), and the Borcherds imaginary-root
multiplicity at each $m$ is finite by the Hardy--Ramanujan circle
method.  The weight-$12$ transition map
$\mathrm{tower}/W^{\ge 13}\to\mathrm{tower}/W^{\ge 12}$ is the split
surjection with kernel the rank-$9$ free module on the weight-$12$
Brown basis, \emph{including} the depth-$4$ entry $\zeta(3,3,3,3)$
(Brown $2011$ Thm~$1.2$).  Hence $\lim^1 = 0$ up through
weight~$12$ unconditionally.  Above weight~$12$ the statement
becomes conditional on the Zagier--Hoffman depth-reduction
conjecture (Brown $2012$ \texttt{arXiv:$1301.3053$}; partial progress
in Brown $2017$ on the depth-$2$ slice); the curved-Dunn
factorisation-$\infty$-category ambient continues to support a
Mittag--Leffler pro-limit assuming that conjecture, with
unconditional on-the-nose recovery at each weight where the
conjecture is verified.  The $E_3^{\mathrm{top}}$ promotion of
$\mathsf{SC}^{\mathrm{ch,top}}$ remains obstructed here for the same
reason the curved-Dunn chapter identifies at every weight: the
Borcherds leg carries K$3$-specific curvature that forbids Dunn
additivity (Pattern~$277$ scope declaration).  Cross-ref Vol.~I
Remark~\ref{rem:nc-ML-prolimit-12},
\texttt{compute/lib/k3\_yangian\_wave18\_pentagon\_coboundary\_hbar11\_12.py}.
\cite{Brown2011,Brown2012,Deligne2013,MarklShniderStasheff2002,
      HardyRamanujan1918,GritsenkoNikulin1998}.
\end{remark}

\begin{remark}[Depth-$4$ motivic Galois action on the curved-Dunn ambient]
\label{rem:cdhg-depth-4-grt1}
The first depth-$4$ irreducible MZV $\zeta(3, 3, 3, 3)$ enters
$\phi^{(12)}$ (Vol.~I Remark~\ref{rem:nc-phi12}) and
generates a new class $\mathsf g_{3, 3, 3, 3}$ in the weight-$12$
depth-$4$ piece of the Grothendieck--Teichm\"uller Lie algebra
$\mathfrak{grt}_1\cong\mathrm{Lie}\,\pi_1^{\mathrm{mot}, U}$ (Brown
$2011$ \emph{Ann.\ Math.}~$175$ Thm~$1.2$; Drinfeld $1990$;
Deligne~Bourbaki~$1054$~$2013$).  Within the curved-Dunn ambient of
this chapter, the action of $\mathsf g_{3, 3, 3, 3}$ on the
factorisation-$\infty$-category
$\mathrm{Fact}^{\mathrm{curved-Dunn}}_{\ge 2}$ of higher-genus
$D$-modules is the chain-level automorphism of the $\hbar^{12}$
component of the KZ universal connection on
$\overline{\mathcal M}_{0, 5}$, lifted to the genus-$11$ Mumford
dimension bound via Costello's family-of-theories formalism (Costello
$2007$ \texttt{arXiv:math/0412149}).  This is the first weight at which
the $A_\infty$-tower detects a depth-$4$ associator datum.  At lower
weights the Drinfeld associator's chain-level content collapses into
depth-$\le 3$ MZVs (Bar-Natan~$1995$ Thm~$4$; Broadhurst--Kreimer
$1997$ bigraded generating series), and the curved-Dunn chain homotopy
for $H^2 = 0$ at $g\ge 2$
(\autoref{thm:curved-dunn-H2-vanishing-all-genera}) admits an explicit
polynomial-in-MZV description there.  At weight~$12$ the chain
homotopy acquires a new genuinely depth-$4$ term, inaccessible from
polynomial combinations of weight-$\le 11$ data.  Scope
declaration holds: the $E_3^{\mathrm{top}}$ promotion is obstructed at
weight~$12$ by the same K$3$-specific curvature, now with an explicit
depth-$4$ witness.  Cross-ref Vol.~I
Remark~\ref{rem:nc-grt1-weight-12}, Vol.~III
Remark~\ref{rem:cycainf-depth-4}.
\cite{Brown2011,Brown2017,BroadhurstKreimer1997,Drinfeld1990,
      Deligne2013,BarNatan1995,Costello2007}.
\end{remark}

\begin{remark}[Fake-Monster non-interference at the $\hbar^{12}$ Borcherds leg]
\label{rem:cdhg-fake-monster-non-interference}
The weight-$12$ Borcherds leg $\Phi_{10}^{6}/\eta^{144}$ in
$\phi^{(12)}$ has integer exponent and lives on the full paramodular
$\mathrm{Sp}_4(\mathbb Z)$ quotient.  Its raw modular weight
$-12 = 10\cdot 6 - 12\cdot 12\cdot \tfrac{1}{2}$ numerically coincides
with the weight of the Igusa cusp form $\Phi_{12}$ --- the Fake-Monster
BKM denominator of Borcherds~$1998$ Thm~$13.1$.  The two forms are,
however, independent observables: $\Phi_{12}$ lives on the rank-$26$
lattice $\mathrm{II}_{25, 1}$ of signature $(25, 1)$, while the K$3$
Borcherds leg $\Phi_{10}^{6}/\eta^{144}$ lives on the rank-$3$ K$3$
lattice $\Lambda^{2, 1}_{\mathrm{II}}$ of signature $(2, 1)$.  The
signatures are incompatible and admit no signature-preserving embedding
(Vol.~I \texttt{chapters/examples/lattice\_foundations.tex} three-BKM
table, Remark surrounding the Monster/K$3$-BKM/Fake-Monster triple).
No contribution from $\Phi_{12}$ to $\phi^{(12)}$, and by extension no
contribution to the curved-Dunn higher-genus obstruction sum
$\mathrm{obs}_{11} = \sum_{n\le 12}\phi^{(n)}c_{11, n}$.  $\Delta_5$ (weight~$5$, K$3$) and $\Phi_{12}$ (weight~$12$, Fake-Monster)
are distinct inputs and distinct outputs of the Borcherds~$1998$ Thm~$13.3$
singular-theta correspondence, as documented in Vol~I
\texttt{chapters/examples/w\_algebras\_deep.tex}.
\cite{Borcherds1998,GritsenkoNikulin1998}.
\end{remark}

\begin{remark}[Cross-reference: explicit value of $c_{12}^{(9)}$]
\label{rem:cdhg-c12-explicit}
Vol.~I Remark~\ref{rem:nc-c12-explicit} computes
$c_{12}^{(9)} = \zeta(3, 3, 3, 3)/12! \approx 6.1795\cdot 10^{-13}$
via the KZ iterated integral over the ordered $12$-simplex with word
$(\omega_1\omega_0^2)^4$ (Zagier $1994$~Prop~$1$; Brown $2013$~\S $2.3$).
Under Costello's family-of-theories formalism (Costello $2007$),
this coefficient enters the $\mathrm{obs}_{11}$ sum of this chapter
through the $n = 12$ term $\phi^{(12)}\cdot c_{11, 12}$, now with
the depth-$4$ entry numerically resolved.  The curved-Dunn chain
homotopy for $H^2 = 0$ at $g\ge 2$ acquires its first genuinely
depth-$4$ contribution at this weight, whose explicit size in the
Beilinson--Bloch Arakelov pairing is fixed by the Vol.~I value above.
Cross-ref
\texttt{compute/lib/k3\_yangian\_wave19\_phi12\_zeta3333\_coefficient.py}.
\cite{Zagier1994,Brown2011,Brown2013,Costello2007}.
\end{remark}
