\section{From $W(\mathsf{SC}^{\mathrm{ch,top}})$ to axioms and back}
\label{ch:theory-equivalence}

The operadic definition of a boundary chart is canonical but
opaque for computation: an action of $C_\ast(W(\SCchtop))$ is a
collection of chain maps from cellular chains of Fulton--MacPherson
cells, parametrised by the entire Boardman--Vogt resolution, and
the resulting structure is not directly recognisable as the kind
of $\lambda$-bracket data a working vertex algebraist writes down.
A coordinate presentation in terms of multilinear operations
$\{m_k\}$ with sesquilinearity and Stasheff identities is
computable, but it is not obvious that every such presentation
arises from an operad action, nor that two presentations related
by a change of chart give the same underlying algebraic object.
The deficiency is a bridge: does the axiomatic presentation
capture the operad, or does it sit strictly inside it?

Theorem~\ref{thm:rectification} supplies the bridge. Every tame
collection $\{m_k\}$ satisfying the axioms of
Definition~\ref{def:ainfty_chiral} arises uniquely, up to
contractible choice, from a $C_\ast(W(\SCchtop))$-algebra
structure on the same underlying complex. The axioms are
neither stronger nor weaker than the operad: they are a
coordinate expression of it.

\subsection{From the operad to explicit $m_k$}
\label{subsec:operad-to-mk-equiv}

Let $(A_{\mathsf{ch}}, A_{\mathsf{top}})$ be a $C_\ast(W(\SCchtop))$-algebra with
underlying complex $A$ and translation operator $\partial$.
For each $k \ge 1$, choose a fundamental chain
$[\FM_k(\C)] \in C_\ast(\FM_k(\C))$ and record the $E_1$ ordering.
Define
\[
 m_k(a_1,\ldots,a_k)
 := \bigl\langle \rho\bigl([\FM_k(\C)] \times [E_1(\text{ord})]\bigr),\,
 a_1 \otimes \cdots \otimes a_k \bigr\rangle
 \;\in\; A((\lambda_1))\cdots((\lambda_{k-1})),
\]
where $\rho$ is the operad action and the $\lambda$-dependence
is the generating function of the logarithmic forms on $\FM_k(\C)$.
Sesquilinearity~\eqref{eq:sesqui-left}--\eqref{eq:sesqui-right}
holds because $\FM_k(\C)$ is defined modulo translations (so the
$\C$-action generates $\partial$ and yields $\lambda$-multiplications),
and the spectral substitution law in~\eqref{eq:ainfty-relation-raw}
is the image of the boundary face identification in $\partial\FM_k(\C)$
where a consecutive block collapses to an effective parameter.

\subsection{From axioms to the operad: rectification}
\label{subsec:rectification-equiv}

The converse, from a tame $A_\infty$ chiral algebra back to an
operadic structure, is Theorem~\ref{thm:rectification}
(proved in Section~\ref{sec:axioms-Ainfty-chiral}):
every tame $\{m_k\}$ determines a $C_\ast(W(\SCchtop))$-algebra
structure, unique up to contractible choice.

The proof proceeds in four steps:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Assemble an $E_1$ dg coassociative coalgebra $\mathcal{C}_A = T^c(s^{-1}\bar A)$
 from the $A_\infty$ data; the $A_\infty$ identities ensure $d_{\mathcal{C}}^2 = 0$.
\item Apply the cobar functor $\Omega(\mathcal{C}_A)$ to produce a strict
 $\SCchtop$-algebra $\widetilde A$.
\item Construct a quasi-isomorphism $\varepsilon\colon \widetilde A \xrightarrow{\;\sim\;} A$
 (the augmentation map) by evaluating on fundamental chains; tameness
 ensures the map lands in the correct spectral-parameter completed space.
\item Invoke homotopy-Koszulity of $\SCchtop$
 (Theorem~\ref{thm:homotopy-Koszul}) to conclude the structure is
 unique up to a contractible space of choices: the Quillen equivalence
 (Theorem~\ref{thm:bar-cobar-adjunction}) implies any two lifts
 are connected by a contractible space of quasi-isomorphisms.
\end{enumerate}

The uniqueness up to contractible choice (step~(iv)) is the content of homotopy-Koszulity:
without it, distinct lifts could produce genuinely inequivalent operad
algebra structures on the same underlying data.

\subsection{Compatibility with the PVA structure on cohomology}
\label{subsec:compat-PVA-equiv}

On cohomology $H^\bullet(A, Q)$, the $C_\ast(W(\SCchtop))$-algebra
structure descends to a Poisson vertex algebra. The mechanism is the
holomorphic filtration: the associated graded of $C_\ast(W(\SCchtop))$
with respect to pole order is the free product $\cP^{\mathrm{ch}} * E_1$,
so the $E_1$ page of the associated spectral sequence carries
commutative-associative (regular) and Lie (singular) products
independently.

Concretely: the binary operation $m_2$ decomposes as
$m_2 = m_2^{\mathrm{reg}} + m_2^{\mathrm{sing}}$ (regular and singular
parts in $\lambda$). On cohomology, $m_2^{\mathrm{reg}}$ descends
to a graded-commutative product (the normally-ordered product) and
$m_2^{\mathrm{sing}}$ descends to the $\lambda$-bracket
(Definition~\ref{def:lambda-bracket}). The $A_\infty$ relation at
$n = 2$ with $m_0 = 0$, restricted to regular and singular parts
separately, recovers the Leibniz rule for the $\lambda$-bracket
over the commutative product: the PVA axioms of
Theorem~\ref{thm:cohomology_PVA}.

The higher operations $m_{k \geq 3}$, restricted to cohomology,
contribute only if they have a component in $\ker(Q)^{\otimes k}$
that maps to a non-$Q$-exact element. On the Koszul locus
(Volume~I, Theorem~H), the chiral Hochschild complex
$\mathrm{C}^\bullet_{\mathrm{ch}}(A, A)$ is concentrated in degrees
$\{0, 1, 2\}$, and the higher $m_{k \geq 3}$ are $Q$-exact:
the PVA on cohomology sees only the binary data.

\subsection{$E_3$ algebraic versus $E_3$-topological}
\label{subsec:e3-algebraic-vs-topological}

The rectification theorem produces an $\SCchtop$-algebra structure
on the pair $(A_{\mathsf{ch}}, A_{\mathsf{top}})$, not an $E_3$
structure. The identification $\SCchtop \rightsquigarrow E_3$ is a
separate theorem with two distinct facets.

\emph{$E_3$-algebraic.} The chiral Higher Deligne theorem
(Theorem~\ref{thm:chd-deligne-tamarkin}) endows
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(A) =
H^*(\mathrm{C}^\bullet_{\mathrm{ch}}(A, A), \delta)$ with an
$E_3$-algebra structure via the heptagon edges
(3)$\leftrightarrow$(4) of Chapter~\ref{ch:sc-chtop-heptagon}. This
requires the $\Einf$-chiral input: the symmetric bar $B^\Sigma(A)$
exists as an $E_2$-coalgebra, and the higher Deligne conjecture
adds one more $E_1$. For the present $\Eone$-chiral input
(Yangian-type), only the ordered bar $B^{\mathrm{ord}}(A)$ exists;
the HDC route gives only $E_2$, not $E_3$.

\emph{$E_3$-topological.} Topologization via Sugawara
$T(z) = [Q_{\mathrm{tot}}, G(z)]$ (conformal vector at non-critical
level) makes $\C$-translations $Q$-exact, and Dunn additivity
applied to the topologized single-coloured operad
$E_2^{\mathrm{hol}} \otimes E_1^{\mathrm{top}} \simeq
E_3^{\mathrm{top}}$ gives an $E_3$-topological structure on the
derived center. This is proved chain-level for affine $V_k(\fg)$ at
non-critical level (Theorem~\ref{thm:E3-topological-km}); for class M
it holds chain-level in the weight-completed category via the
iterated Sugawara ladder
(Theorem~\ref{thm:e-infinity-topologization-ladder});
the general chiral-algebra-with-conformal-vector case is
conjectural (Conjecture~\ref{conj:E3-topological-general}).

The two faces are conjecturally identified as families over
$\hbar \cdot H^3(\mathfrak{g})[[\hbar]]$; the identification is
cohomological for affine $V_k(\fg)$ at non-critical level, and
chain-level may fail in class M. The present rectification theorem
produces $\SCchtop$ structure unconditionally and is agnostic to
the topologization step: any conclusion about $E_3$ on the derived
center carries the topologization hypothesis.

\subsection{Equivalence anchors in the universal-holography theorem}
\label{subsec:equivalence-holography-anchors}

\begin{remark}[Operad/axiom equivalence in the universal-holography master]
\label{rem:equivalence-holography-anchor}%
\index{universal holography!equivalence anchor}%
The rectification theorem above is the technical bridge between
the operadic input to the universal-holography master
(Theorem~\ref{thm:universal-holography-master}) and the
family-by-family axiomatic verifications that realise the rung
corollaries (Corollaries~\ref{cor:rung-heisenberg},
\ref{cor:rung-affine-km}, \ref{cor:rung-virasoro},
\ref{cor:rung-w-N}, \ref{cor:rung-w-infty}). Each rung corollary
takes a specific algebra $\cA$, exhibits its $A_\infty$ chiral
structure $\{m_k\}$ via Definition~\ref{def:ainfty_chiral}
(equivalently, by the present rectification, an
$\SCchtop$-algebra structure), then routes through topologization
(when a conformal vector exists at non-critical level) into the
master theorem's bulk-identification clause. The Volume~I
Koszul-reflection theorem and the universal-conductor formula
anchor on the present operad/axiom equivalence: the bar
differential $d_{\barB}$ assembled from the $m_k$ is
$\KZ^*(\nabla_{\mathrm{Arnold}})$ on the closed-colour side, and
the BRST ghost charge of the boundary topologization is the
negative of $\kappa(\cA)$ on the open-colour side.
\end{remark}
