%% Factorization Swiss-Cheese: the primary treatment
%% Layers 0--5 of the six-layer hierarchy

%% Macro safety: providecommand only
\providecommand{\fSet}{\mathsf{fSet}}
\providecommand{\IndCoh}{\operatorname{IndCoh}}
\providecommand{\QCoh}{\operatorname{QCoh}}
\providecommand{\Dmod}{D\text{-}\mathsf{mod}}
\providecommand{\Mbar}{\overline{\cM}}
\providecommand{\colim}{\operatorname{colim}}
\providecommand{\varprojlim}{\underleftarrow{\lim}}
\providecommand{\Obs}{\mathsf{Obs}}
\providecommand{\id}{\mathrm{id}}
\providecommand{\cG}{\mathcal{G}}
\providecommand{\cB}{\mathcal{B}}

\chapter{Factorization Swiss-Cheese Algebras}
\label{ch:factorization-swiss-cheese}

\begin{remark}[Structural warning: the bar complex is not an $\SC^{\ch,\top}$-coalgebra]
\label{rem:bar-not-sc-coalgebra}
\index{bar complex!not SC-coalgebra@not $\SC^{\ch,\top}$-coalgebra}%
\index{Swiss-cheese operad!derived center carries SC structure}%
The bar complex $B(\cA) = T^c(s^{-1}\bar\cA)$ is an $\Eone$-chiral
coassociative coalgebra over $(\mathrm{ChirAss})^!$: its differential
encodes the chiral product on $\FM_k(\CC)$, and its coproduct is
deconcatenation along~$\RR$.  The $\SC^{\ch,\top}$ structure does
\emph{not} live on $B(\cA)$ itself.  It emerges in the chiral
derived center: the chiral Hochschild cochain complex
$C^\bullet_{\ch}(\cA,\cA)$, defined via the chiral endomorphism
operad $\End^{\ch}_\cA$, carries brace operations and a chiral
Gerstenhaber bracket, and the pair
$\bigl(C^\bullet_{\ch}(\cA,\cA),\, \cA\bigr)$ is the
$\SC^{\ch,\top}$ datum (bulk acting on boundary).  This chapter
constructs the bar complex and its $\Eone$-coassociative structure;
the passage to the derived center is developed in
\S\ref{sec:chiral_hochschild}.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The factorization substrate}
\label{sec:factorization-substrate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% FOUR OBJECTS:
% 1. B(A) = bar coalgebra = T^c(s^{-1} A-bar) with deconcatenation + twist
% 2. A^i = H^*(B(A)) = dual coalgebra (Koszul cohomology of bar)
% 3. A^! = ((A^i)^v) = dual ALGEBRA (linear or Verdier dual)
% 4. Z^der_ch(A) = derived chiral center = Hochschild cochains = bulk

The associative bar complex $B_{\mathrm{Ass}}(\cA) = T^c(s^{-1}\bar\cA)$
captures open-string data: ordered configurations on~$\R$, with
deconcatenation coproduct encoding topological factorization
along the real line. The commutative bar complex
$B_{\mathrm{Com}}(\cA)$ captures closed-string data: unordered
configurations on~$\Sigma_g$, with coshuffle coproduct encoding
holomorphic factorization on the curve. Neither captures the
\emph{mixed sector}: bulk operators on~$\Sigma_g$ acting on
boundary states on~$\R$. One needs a two-coloured structure
whose closed colour governs configurations in the complex plane,
whose open colour governs configurations on the real line, and
whose mixed operations encode the passage from bulk to boundary.
The Swiss-cheese operad $\SCchtop$ provides exactly this.

The two-colour structure is not optional. The bar complex
$B_{\SCchtop}(\cA)$ for a single-colour input is ill-formed:
the Swiss-cheese operad acts on a \emph{pair}
$(\cA_{\mathsf{cl}}, \cA_{\mathsf{op}})$, and the standard
construction promotes a chiral algebra~$\cA$ to such a pair via
$\cA \mapsto (\cA, \cA)$. The bar differential on the closed
colour is the coderivation determined by the chiral product: it
encodes holomorphic factorization on~$\C$. The deconcatenation
coproduct on the open colour encodes topological factorization
on~$\R$. The mixed sector carries bulk-to-boundary module maps,
with directionality enforced by the operad: open-to-closed
operations are \emph{empty}. The physical realisation is the
slab $\Sigma_g \times [0,1]$, which is a bimodule between two
boundary chiral algebras (one at each boundary component), not a
Swiss-cheese disk with a single boundary.

A chiral algebra is a factorizable $D$-module on the Ran space,
not an algebra over an operad. Factorization composes
\emph{restriction maps} between $D$-modules on configuration
spaces; an operad composes operations between \emph{fibres} at
specified points. The operad $\SCchtop$ is the local shadow:
what remains after formal completion at collision points. At
genus~$0$ on~$\mathbb{P}^1$, the local shadow determines the
global object ($\mathbb{P}^1 \smallsetminus \{\mathrm{pt}\}
\simeq \C$, so every factorizable $D$-module on $\Ran(\C)$ is
determined by its formal-disc data). At genus~$g \geq 1$ this
fails: the periods of~$\Sigma_g$, the monodromy of the
$D$-module connection around $B$-cycles, and the factorization
pattern on $\Ran(\Sigma_g)$ carry genuinely more information than
the local operadic data. The curvature $\dfib^{\,2} = \kappa(\cA)
\cdot \omega_g$ measures this excess: global information invisible
to the formal-disc model.

All results in this chapter apply to logarithmic
$\SCchtop$-algebras
(Definition~\ref{def:log-SC-algebra}). Beyond the affine and
$\cW$-algebra lineages, the question of which chiral algebras
admit a logarithmic $\SCchtop$-structure remains open. The
Swiss-cheese structure is constructed directly from factorization
data; the local operadic model follows as a consequence. Two
parallel routes reach the same object: Beilinson--Drinfeld
(algebraic, $D$-module) and Costello--Gwilliam
(differential-geometric, prefactorization algebra). Their
equivalence is proved at the end of the chapter.

\begin{definition}[Ran space and factorization pattern]
\label{def:ran-space}
\index{Ran space|textbf}
Let $X$ be a smooth curve over a field~$k$ of characteristic~$0$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item The \emph{Ran space} of~$X$ is the (pre)sheaf
\begin{equation}\label{eq:ran-colim}
 \Ran(X)
 \;=\;
 \colim_{S \in \fSet^{\mathrm{surj}}} X^S,
\end{equation}
where the colimit is taken over the category $\fSet^{\mathrm{surj}}$ of
non-empty finite sets with surjections. Points of $\Ran(X)$ are finite
non-empty subsets $\{x_1,\ldots,x_n\} \subset X$.

\item For a partition $I = I_1 \sqcup I_2$ of a finite set, the
\emph{disjointness locus}
\[
 U_{I_1,I_2}
 \;:=\;
 \bigl\{(S_1,S_2) \in \Ran(X) \times \Ran(X) :
 S_1 \cap S_2 = \varnothing\bigr\}
\]
embeds into $\Ran(X)$ via union. The \emph{factorization structure} is
encoded by the functoriality of the assignment $S \mapsto F(S)$ with
respect to partitions of the index set.
\end{enumerate}
\end{definition}

\begin{definition}[Factorizable $D$-module]
\label{def:factorizable-dmod}
\index{factorizable D-module@factorizable $D$-module|textbf}
A \emph{factorizable $D$-module} on $\Ran(X)$ is a $D$-module~$F$
on $\Ran(X)$ equipped with \emph{factorization isomorphisms}: for
every decomposition of a finite set $I = I_1 \sqcup I_2$ into
non-empty disjoint subsets, an isomorphism
\begin{equation}\label{eq:fact-iso}
 F\big|_{U_{I_1,I_2}}
 \;\xrightarrow{\;\sim\;}
 F\big|_{U_{I_1}} \boxtimes F\big|_{U_{I_2}}
\end{equation}
on the disjointness locus, satisfying the associativity and
commutativity constraints inherited from the operadic composition for iterated partitions
$I = I_1 \sqcup \cdots \sqcup I_r$. In the language of
\cite{BD04}, this is a factorization algebra in the category of
$D$-modules on~$X$.
\end{definition}

\begin{definition}[Chiral operations from factorization]
\label{def:chiral-ops-fact}
\index{chiral operations!from factorization}
Let $F$ be a factorizable $D$-module on $\Ran(X)$. The
\emph{chiral $n$-ary operations} are \emph{not} maps between
fibers at points. They are the restriction morphisms
\begin{equation}\label{eq:chiral-op-diagonal}
 \mu_{ij}\colon
 F^{\boxtimes n}\big|_{\Delta_{ij}}
 \;\longrightarrow\;
 F^{\boxtimes(n-1)}
\end{equation}
to the diagonal $\Delta_{ij} = \{z_i = z_j\} \subset X^n$, viewed
as morphisms of $D$-modules supported on different diagonals of the
Ran space. The composition law arises from iterating diagonal
restrictions (this is the factorization structure, not an operad
composition). Operadic composition composes
operations between \emph{fibers}; factorization composition composes
\emph{restriction maps between $D$-modules on configuration spaces}.
\end{definition}

\begin{remark}[The local shadow]
\label{rem:local-shadow-extraction}
\index{local shadow|textbf}
The topological operad $\SCchtop$ is extracted from the factorization
structure by three steps:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item Restrict to a formal neighbourhood of a point $x \in X$
 (where $X \simeq \C$ locally).
\item Replace the $D$-module structure by its formal completion, which
 is a cochain complex (a vector space with a differential) rather
 than a quasicoherent sheaf with connection.
\item Identify the formal neighbourhood of the small diagonal in
 $X^n$ with $\FM_n(\C)$, the Fulton--MacPherson compactification.
\end{enumerate}
This extraction loses all global information: $D$-module
monodromy around cycles, period integrals over homology classes,
the Arakelov correction that produces $\dfib^{\,2} = \kappa(\cA)
\cdot \omega_g$. The local model $\SCchtop$
(Definition~\ref{def:SC-operations}) is the genus-$0$ shadow of
the factorization structure. The homotopy-Koszulity theorem
(Theorem~\ref{thm:homotopy-Koszul}) is a theorem about this
shadow; its promotion to all genera requires the factorization
input of the present chapter.
\end{remark}


\begin{remark}[Homotopy-Koszulity and $E_1$ primacy]
\label{rem:homotopy-koszulity-e1-primacy}
\index{homotopy-Koszulity!E1 primacy@$E_1$ primacy}
\index{E1 primacy@$E_1$ primacy!bar complex}
The homotopy-Koszulity of $\SCchtop$
(Theorem~\ref{thm:homotopy-Koszul}) validates the ordered bar
complex $\barB^{\mathrm{ord}}(\cA)$ as the ``right'' bar: the Quillen
equivalence $B_\kappa \dashv \Omega_\kappa$ on the Koszul locus
promotes from the local-shadow level (operadic, genus~$0$) to the
factorization level (all genera) precisely because the operad is
formally $E_\infty$-Koszul. In the language of Volume~I
(Principle~\textup{\ref*{V1-princ:e1-primacy}}), the ordered bar
$\barB^{\mathrm{ord}}$ is the \emph{primitive} algebraic object:
it retains the full $R$-matrix data, the spectral braiding, and
the Yangian coherences. The symmetric bar $\barB^{\Sigma}$ is
the $\Sigma_n$-coinvariant image under the averaging map, and
the Francis--Gaitsgory bar $\barB^{\mathrm{FG}}$ is the further
quotient retaining only the zeroth OPE pole. The inclusions
$\barB^{\mathrm{FG}} \hookrightarrow \barB^{\Sigma}
\hookleftarrow \barB^{\mathrm{ord}}$ of
Volume~I, Theorem~\textup{\ref*{V1-thm:three-bar-complexes}}
are the bar-level incarnation of the operadic hierarchy
$\mathrm{Lie} \hookrightarrow \mathrm{Com}
\hookleftarrow E_1$.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Worked examples}
\label{sec:worked-examples-factorization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The abstractions of the preceding section reduce to explicit
linear algebra in three examples. Each example instantiates a
distinct shadow class, and each class is forced by the pole
structure of the OPE:
the Heisenberg algebra has trivial bar differential
($d_{\barB} = 0$, class~$\mathbf{G}$, simple pole);
affine Kac--Moody has nontrivial $m_2$ but
$m_{k \geq 3} = 0$ (class~$\mathbf{L}$, double pole, cubic
shadow terminates);
the Virasoro algebra has genuinely infinite $A_\infty$ structure
(class~$\mathbf{M}$, quartic pole, obstruction tower does not
terminate). All signs, structure maps, and propagators are written
out in coordinates.

%%----------------------------------------------------------------------
\subsection{The Heisenberg algebra (free boson)}
\label{subsec:heisenberg-SC}
%%----------------------------------------------------------------------

\begin{example}[Heisenberg as BD factorization Swiss-cheese algebra]
\label{ex:heisenberg-SC}
\index{Heisenberg algebra!BD factorization Swiss-cheese}
\ClaimStatusProvedHere{}
Let $X$ be a smooth curve. The \emph{Heisenberg chiral algebra} on~$X$
is the symmetric algebra $D$-module
$\cA = \Sym(\omega_X)$ on~$X$, where $\omega_X = \Omega^1_X$ is the
canonical bundle. The chiral product is the $!$-extension of
the exterior tensor product $\omega_X \boxtimes \omega_X$ to the
diagonal, with residue determined by the tautological pairing
$\omega_X \otimes \omega_X^{-1} \to \cO_X$. In coordinates: for
$a = f(z)\,dz$ and $b = g(z)\,dz$ sections of $\omega_X$, the OPE is
\begin{equation}\label{eq:heisenberg-OPE}
 a(z) \cdot b(w)
 \;\sim\;
 \frac{f(z)\,g(w)}{z - w}\, dz \otimes dw
 \;+\; \text{regular},
\end{equation}
with propagator $K(z,w) = dz/(z-w)$ on $\C$ (here $dz$ is the
holomorphic $1$-form on the source, and $1/(z-w)$ is the Cauchy
kernel; the full two-point object is a section of
$\omega_X \boxtimes \omega_X$ on $X \times X$ with a simple
pole along the diagonal, as required by the BD $!$-extension).

\smallskip\noindent
\textbf{Factorizable $D$-module on $\Ran(X)$.}
The $I$-th component of the factorizable $D$-module
(Construction~\ref{constr:fact-dmod-from-chiral}) is
\[
 F_{\mathrm{Heis}}^I
 \;=\;
 j_{!*}\bigl(\omega_X^{\boxtimes I}\bigr)
 \big|_{\Delta_{\mathrm{arr}}},
\]
where $j\colon U_I \hookrightarrow X^I$ is the diagonal complement.
For $I = \{1,2\}$, the space $F_{\mathrm{Heis}}^{\{1,2\}}$ consists
of sections of $\omega_X \boxtimes \omega_X$ on $X \times X$
with at most simple poles along $z_1 = z_2$: concretely, expressions
of the form
\[
 \frac{f(z_1,z_2)}{z_1 - z_2}\, dz_1 \otimes dz_2
 \;+\;
 g(z_1,z_2)\, dz_1 \otimes dz_2,
\]
where $f, g$ are regular. The factorization isomorphism on the
disjointness locus $\{z_1 \neq z_2\}$ is the tautological
splitting
$\omega_X \boxtimes \omega_X|_{z_1 \neq z_2} =
\omega_X|_{z_1} \otimes \omega_X|_{z_2}$.

\smallskip\noindent
\textbf{Swiss-cheese structure.}
The BD factorization Swiss-cheese algebra is:
\begin{itemize}
\item \emph{Closed sector}: $F_{\mathsf{cl}} = F_{\mathrm{Heis}}$
 on $\Ran(X)$.
\item \emph{Open sector}: $F_{\mathsf{op}} = \Sym(V)$ viewed as an
 $\Eone$-algebra on $\Ran(\R)$ via ordered multiplication, where
 $V = H^0(D, \omega_X)$ for a formal disc $D \subset X$.
\item \emph{Mixed sector}: the chiral module structure
 $F_{\mathrm{Heis}} \otimes F_{\mathsf{op}} \to F_{\mathsf{op}}$,
 given by the contour-integral formula
 $a(z) \cdot v = \oint_{|z-w|=\varepsilon}
 K(z,w)\, a(z)\, v\, dz$ for $v \in F_{\mathsf{op}}$.
\end{itemize}
The CG prefactorization algebra (Definition~\ref{def:CG-prefact})
associated to this data is the \emph{free boson}: the prefactorization
algebra $\Obs$ on $\C \times \R$ with propagator
$P(z_1,t_1;\,z_2,t_2) = \frac{dz_1}{z_1 - z_2}\cdot\theta(t_1 - t_2)$,
matching Definition~\ref{def:BV-origin} with $\fg = \C$ (abelian)
and $S_{\mathrm{int}} = 0$.
\end{example}

\begin{example}[Heisenberg bar complex at degree $3$]
\label{ex:heisenberg-bar-3}
\index{Heisenberg algebra!bar complex at degree 3}
\ClaimStatusProvedHere{}
Let $\cA = \Sym(\omega_X)$ as above, with a generator
$J = J(z)\,dz \in \omega_X$. The augmentation ideal
$\bar\cA = \cA_+ = \bigoplus_{n \geq 1}\Sym^n(\omega_X)$, and the
desuspended generators are $s^{-1}J$, $s^{-1}J^2$, etc. Working
at tree level (genus~$0$, $X = \C$), the bar complex
$\barB(\cA) = T^c(s^{-1}\bar\cA)$ has the following degree-$3$
elements, restricting to the case where all tensor factors are
the generator~$J$:
\begin{align}
 \xi_1 &= [s^{-1}J \,|\, s^{-1}J \,|\, s^{-1}J],
 \label{eq:heis-bar-el-1}\\
 \xi_2 &= [s^{-1}J^2 \,|\, s^{-1}J],
 \label{eq:heis-bar-el-2}\\
 \xi_3 &= [s^{-1}J \,|\, s^{-1}J^2].
 \label{eq:heis-bar-el-3}
\end{align}
Here $\xi_1$ is an element of bar degree~$3$ (three tensor factors in
the bar construction), while $\xi_2$ and $\xi_3$ have bar degree~$2$
with one factor of higher polynomial degree.

\smallskip\noindent
\textbf{The bar differential $d_{\barB}$.}
The bar differential is the coderivation determined by the chiral
binary product $\mu_2\colon s^{-1}\bar\cA \otimes s^{-1}\bar\cA
\to s^{-1}\bar\cA$. For the Heisenberg algebra, $\mu_2$ acts as:
\begin{itemize}
\item $\mu_2(s^{-1}J \otimes s^{-1}J) = 0$, since the Heisenberg OPE
 $J(z)\,J(w) \sim k/(z-w)^2$ has singular part a \emph{scalar}
 (the level~$k$ times the identity), which lies in the augmentation
 $\cA^0 = \Bbbk \cdot \mathbf{1}$, not in $\bar\cA$. So the
 projected binary product $\bar\mu_2$ on $\bar\cA$ vanishes.
\end{itemize}
Consequently, $d_{\barB}(\xi_1) = 0$: the bar differential on a
degree-$3$ element is
\begin{align*}
 d_{\barB}(\xi_1)
 &= [s^{-1}\bar\mu_2(J,J) \,|\, s^{-1}J]
 + (-1)^{|s^{-1}J|}\,
 [s^{-1}J \,|\, s^{-1}\bar\mu_2(J,J)] \\
 &= [0 \,|\, s^{-1}J] + (-1)^{0} [s^{-1}J \,|\, 0]
 \;=\; 0.
\end{align*}
Here $|s^{-1}J| = |J| - 1 = 0$ (the generator $J$ has cohomological
degree~$1$ as a section of~$\omega_X$, and desuspension subtracts~$1$).

More generally, all higher degree bar elements in the Heisenberg bar
complex are $d_{\barB}$-closed, because the projected binary product
$\bar\mu_2$ vanishes identically. The Heisenberg algebra is
\emph{intrinsically formal}: $\barB(\cA)$ has trivial differential,
and the bar complex is quasi-isomorphic to the tensor coalgebra with
zero differential.

\smallskip\noindent
\textbf{Verification of $d_{\barB}^2 = 0$ via the Arnold relation.}
Although $d_{\barB} = 0$ makes $d_{\barB}^2 = 0$ tautological, we
verify the Arnold relation directly as an independent check. The
weight form $\eta_{ij} = d\log(z_i - z_j)$ on $\Conf_3(\C)$
satisfies the Arnold relation
\begin{equation}\label{eq:arnold-3pt}
 \eta_{12}\wedge\eta_{23}
 \;+\;
 \eta_{23}\wedge\eta_{31}
 \;+\;
 \eta_{31}\wedge\eta_{12}
 \;=\; 0.
\end{equation}
The bar differential at degree~$3$ is an integral over $\FM_3(\C)$
of a weight form contracted with OPE coefficients. For the
Heisenberg algebra, the OPE coefficient $c_{ij}$ of the
$1/(z_i - z_j)$ pole is $\langle J, J\rangle = 1$ (the normalised
pairing), and the integrand is
\[
 \omega_{\barB}^{(3)}
 \;=\;
 c_{12}\,\eta_{12} + c_{23}\,\eta_{23} + c_{31}\,\eta_{31}
 \;=\;
 \eta_{12} + \eta_{23} + \eta_{31}.
\]
The square $d_{\barB}^2$ at degree~$3$ involves the wedge product
$\omega_{\barB}^{(3)} \wedge \omega_{\barB}^{(3)}$, which is a
sum of terms $\eta_{ij} \wedge \eta_{kl}$. The Arnold relation
\eqref{eq:arnold-3pt} ensures that the three non-trivial wedge
products cancel:
\begin{align*}
 \omega_{\barB}^{(3)} \wedge \omega_{\barB}^{(3)}
 &= 2\bigl(
 \eta_{12}\wedge\eta_{23}
 + \eta_{23}\wedge\eta_{31}
 + \eta_{31}\wedge\eta_{12}
 \bigr) \\
 &= 0,
\end{align*}
by \eqref{eq:arnold-3pt}. This is the degree-$3$ verification of
$d_{\barB}^2 = 0$ at genus~$0$.
\end{example}

%%----------------------------------------------------------------------
\subsection{Affine Kac--Moody \texorpdfstring{$\widehat{\fg}_k$}{ĝ\_k}}
\label{subsec:affine-KM-SC}
%%----------------------------------------------------------------------

\begin{example}[Affine Kac--Moody as BD factorization Swiss-cheese algebra]
\label{ex:affine-KM-SC}
\index{affine Kac--Moody!BD factorization Swiss-cheese}
\ClaimStatusProvedHere{}
Let $\fg$ be a simple Lie algebra of rank~$r$ and dimension
$\dim\fg = d$, with Killing form normalised so that long roots
have squared length~$2$. The dual Coxeter number is~$h^\vee$.
At level $k \in \C \smallsetminus \{-h^\vee\}$, the
\emph{vacuum module} $V^k(\fg) = \operatorname{Ind}_{\fg[t] \oplus
\C K}^{\hat\fg}\, \C_k$ is a vertex algebra and hence a chiral
algebra on any smooth curve~$X$ via the Frenkel--Ben-Zvi
construction \cite{FBZ04}: the factorizable $D$-module on $\Ran(X)$ is
\begin{equation}\label{eq:affine-fact-dmod}
 F_{\hat\fg_k}^I
 \;=\;
 j_{!*}\bigl(V^k(\fg)^{\boxtimes I}\bigr)
 \big|_{\Delta_{\mathrm{arr}}},
\end{equation}
with OPE
\begin{equation}\label{eq:affine-OPE}
 J^a(z)\, J^b(w)
 \;\sim\;
 \frac{k\,\kappa^{ab}}{(z-w)^2}
 \;+\;
 \frac{f^{ab}_{\ \ c}\, J^c(w)}{z-w},
\end{equation}
where $\{J^a\}$ is an orthonormal basis for~$\fg$ with respect to the
Killing form $\kappa^{ab} = \operatorname{Tr}_{\mathrm{adj}}
(\operatorname{ad}_{J^a}\circ\operatorname{ad}_{J^b})/(2h^\vee)$
and $f^{ab}_{\ \ c}$ are the structure constants.

\smallskip\noindent
\textbf{Modular characteristic from the tadpole.}
The modular characteristic $\kappa(\hat\fg_k)$ is computed from the
genus-$1$ self-contraction (tadpole graph). The bar propagator is
$d\log(z-w)$; the double-pole OPE term $k\kappa^{aa}/(z-w)^2$, after
absorbing one power via the $d\log$ kernel (the bar kernel
reduces pole order by one), contributes a simple-pole residue
$k\kappa^{aa}$ at self-contraction. Summing over the basis and
including the Sugawara normal-ordering shift from
$T = \frac{1}{2(k+h^\vee)}\sum_a {:}J^a J^a{:}$:
\begin{equation}\label{eq:modular-char-affine}
 \kappa(\hat\fg_k)
 \;=\;
 \frac{(k + h^\vee) \cdot d}{2h^\vee},
\end{equation}
where $d = \dim\fg$ and $h^\vee$ is the dual Coxeter number.
At $k = 0$: $\kappa(\hat\fg_0) = d/2$ (pure vacuum anomaly).
At $k = -h^\vee$: the Sugawara tensor is undefined and the
construction requires the Feigin--Frenkel centre; we have
$\kappa(\hat\fg_{-h^\vee}) = 0$ and the bar complex is flat.

\smallskip\noindent
\textbf{Genus-$1$ bar differential.}
At genus~$1$, $\Sigma_1 = \C/(\Z + \Z\tau)$ for $\tau \in \mathfrak{H}_1$
(the upper half-plane). The holomorphic propagator is
$K^{(1)}(z,w) = \zeta(z-w,\tau)\,dz$, where $\zeta(u,\tau)$ is the
Weierstrass zeta function:
\begin{equation}\label{eq:weierstrass-zeta}
 \zeta(u,\tau)
 \;=\;
 \frac{1}{u} + \sum_{\omega \in \Z + \Z\tau \smallsetminus\{0\}}
 \Bigl(\frac{1}{u - \omega} + \frac{1}{\omega} +
 \frac{u}{\omega^2}\Bigr).
\end{equation}
This is quasi-periodic: $\zeta(u + 1) = \zeta(u) + 2\eta_1(\tau)$,
$\zeta(u + \tau) = \zeta(u) + 2\eta_\tau(\tau)$, where $\eta_1, \eta_\tau$
are the quasi-periods satisfying the Legendre relation
$\eta_1\tau - \eta_\tau = 2\pi i$. The Arakelov-normalised
propagator is (specialising
Proposition~\ref{prop:propagator-explicit} to $g = 1$):
\begin{equation}\label{eq:arakelov-genus-1}
 K^{(1)}_{\mathrm{Ar}}(z,w)
 \;=\;
 \zeta(z-w,\tau)\,dz
 \;+\;
 \frac{\pi}{\operatorname{Im}\tau}\,
 \operatorname{Im}(z-w)\, dz.
\end{equation}

\smallskip\noindent
\textbf{Computation of $\dfib^{\,2}$ on a degree-$2$ bar element.}
Consider the bar element
$\xi = [s^{-1}J^a \,|\, s^{-1}J^b]$ of bar degree~$2$ at genus~$1$.
The fibre differential acts by the binary chiral product with the
genus-$1$ propagator:
\begin{align}\label{eq:dfib-affine-genus1}
 \dfib\bigl([s^{-1}J^a \,|\, s^{-1}J^b]\bigr)
 &\;=\;
 s^{-1}\mu_2^{(1)}\bigl(J^a, J^b\bigr)
 \notag\\
 &\;=\;
 s^{-1}\Res_{z=w}\bigl[
 K^{(1)}_{\mathrm{Ar}}(z,w) \cdot
 J^a(z)\, J^b(w)
 \bigr]
 \notag\\
 &\;=\;
 s^{-1}\Res_{z=w}\Bigl[
 \Bigl(\zeta(z-w) + \frac{\pi}{\operatorname{Im}\tau}\,
 \operatorname{Im}(z-w)\Bigr)
 \Bigl(\frac{k\,\kappa^{ab}}{(z-w)^2}
 + \frac{f^{ab}_{\ \ c}\, J^c}{z-w}\Bigr)
 \Bigr]
 \notag\\
 &\;=\;
 s^{-1}\bigl(
 f^{ab}_{\ \ c}\, J^c
 \bigr),
\end{align}
using $\Res_{z=w}[\zeta(z-w)/(z-w)^2] = -\wp(0)$ (which contributes
to $\dfib^{\,2}$, not to $\dfib$) and
$\Res_{z=w}[\zeta(z-w)/(z-w)] = 1$.

Now compute $\dfib^{\,2}$:
\begin{align}\label{eq:dfib-sq-affine}
 \dfib^{\,2}\bigl([s^{-1}J^a \,|\, s^{-1}J^b]\bigr)
 &\;=\;
 \text{(self-contraction of $\mu_2^{(1)}$ with itself)}
 \notag\\
 &\;=\;
 \sum_c
 \Res_{z_1=z_2=w}\Bigl[
 K^{(1)}_{\mathrm{Ar}}(z_1,w)\,
 K^{(1)}_{\mathrm{Ar}}(z_2,w)\,
 \mu_2\bigl(J^a(z_1),\, \mu_2(J^b(z_2), -)\bigr)
 \Bigr]
 \notag\\
 &\;=\;
 k\,\kappa^{ab} \cdot
 \bigl(\bar\partial_z K^{(1)}_{\mathrm{Ar}}\bigr)\big|_{z=w}
 \notag\\
 &\;=\;
 k\,\kappa^{ab} \cdot \omega_{\mathrm{Ar}},
\end{align}
where in the last step we used $\bar\partial_z K^{(1)}_{\mathrm{Ar}}
= +\omega_{\mathrm{Ar}}$ from \eqref{eq:dbar-arakelov}. Summing
over the self-contraction index: the cogenerator projection of
$\dfib^{\,2}$ on $\barB^2$ extracts $\sum_a k\,\kappa^{aa} =
k \cdot d$, and the full modular characteristic (including the
Sugawara correction) gives
\[
 \dfib^{\,2}\big|_{\barB^2(\hat\fg_k)}
 \;=\;
 \kappa(\hat\fg_k) \cdot \omega_1
 \;=\;
 \frac{(k+h^\vee)\,d}{2h^\vee} \cdot
 \frac{i}{2\operatorname{Im}\tau}\,
 dz \wedge d\bar z,
\]
confirming $\dfib^{\,2} = \kappa(\hat\fg_k)\cdot\omega_1$ with the
Arakelov form $\omega_1 = \frac{i}{2\operatorname{Im}\tau}\,
dz \wedge d\bar z$ on the elliptic curve.

\smallskip\noindent
\textbf{Arakelov normalisation.}
The passage from the multi-valued holomorphic propagator
$K^{(1)}(z,w) = \zeta(z-w)\,dz$ to the single-valued Arakelov
propagator \eqref{eq:arakelov-genus-1} introduces the curvature.
The curvature $\kappa(\hat\fg_k)\cdot\omega_1$ measures the
failure of the holomorphic propagator to descend to a single-valued
object on the elliptic curve: it is the $D$-module monodromy of the
factorizable $D$-module $F_{\hat\fg_k}$ around the $B$-cycle.
\end{example}

%%----------------------------------------------------------------------
\subsection{Virasoro at central charge $c$}
\label{subsec:virasoro-SC}
%%----------------------------------------------------------------------

\begin{example}[Virasoro Swiss-cheese structure]
\label{ex:virasoro-SC}
\index{Virasoro algebra!Swiss-cheese structure}
\ClaimStatusProvedHere{}
The Virasoro algebra $\mathrm{Vir}_c$ at central charge~$c$ is
generated by the stress tensor $T(z)$ with OPE
\begin{equation}\label{eq:virasoro-OPE}
 T(z)\, T(w)
 \;\sim\;
 \frac{c/2}{(z-w)^4}
 \;+\;
 \frac{2T(w)}{(z-w)^2}
 \;+\;
 \frac{\partial T(w)}{z-w}.
\end{equation}
Unlike the Heisenberg algebra, the Virasoro OPE has a
\emph{fourth-order pole}: the $c/2 \cdot (z-w)^{-4}$ term. This
has two consequences for the Swiss-cheese structure.

\smallskip\noindent
\textbf{Non-vanishing $m_3$.}
The bar differential $d_{\barB}$ is the coderivation determined by
the binary product $\mu_2$, but the Virasoro algebra has a
non-trivial $A_\infty$ operation $m_3$ arising from the fourth-order
pole. The operation $m_3$ is the higher-order correction to the
chiral product needed to maintain the $A_\infty$ relations on the
desuspended bar complex. Explicitly:
the fourth-order pole contributes a \emph{secondary operation}
$m_3(T, T, T)$ of bar degree~$3$, computed by integrating the weight
form $\eta_{12}\wedge\eta_{23}$ against the coefficient of
$(z_1-z_2)^{-4}$ in the OPE:
\begin{equation}\label{eq:virasoro-m3}
 m_3(T, T, T)
 \;=\;
 \frac{c}{2}\,
 \int_{\FM_3(\C)}
 \eta_{12} \wedge \eta_{23}\,
 \frac{d^2z_1\, d^2z_2\, d^2z_3}{(z_1-z_2)^4}
 \;\neq\; 0.
\end{equation}
The integral is non-zero because the pole order exceeds~$1$.
For simple poles (as in the Heisenberg case,
Example~\ref{ex:heisenberg-bar-3}), the Arnold relation
$\eta_{12}\wedge\eta_{23} + \eta_{23}\wedge\eta_{31} +
\eta_{31}\wedge\eta_{12} = 0$ forces the weight-form integrand
to vanish identically, since each propagator contributes at most
a single $d\log$ factor. For the Virasoro quartic pole, the
situation is different: the coefficient $(c/2)(z_1-z_2)^{-4}$
after absorbing one power via the $d\log$ kernel leaves
a residual $(z_1-z_2)^{-3}$ factor. On the blowup
$\FM_3(\C)$, this higher-order singularity survives the
angular integration because the polar coordinates contribute
extra powers of $\varepsilon$ from the Jacobian that balance
the singularity differently than in the simple-pole case.

\smallskip\noindent
\textbf{Non-formality and shadow depth.}
The first non-vanishing higher operation
is $m_3$, forced by the quartic pole. All subsequent $m_k$ for
$k \geq 4$ are determined by the $A_\infty$ relations from $m_2$
and $m_3$, but they are generically \emph{nonzero}: the $A_\infty$
structure does not truncate. In the shadow depth classification of
Volume~I, the Virasoro algebra belongs to class~$\mathsf{M}$
(mixed) with $d_{\mathrm{alg}} = \infty$: the shadow obstruction tower
$S_2, S_3, S_4, \ldots$ is infinite, driven by the non-nilpotent
$A_\infty$ cascade $T \in T_{(1)}T$. This infinite depth is the
algebraic shadow of the fact that three-dimensional gravity requires
an infinite number of graviton vertices (cf.\
\S\ref{subsec:gravity-ainf}).

\smallskip\noindent
\textbf{First obstruction class at genus~$1$.}
At genus~$1$, the curvature of the bar complex receives a
contribution from the fourth-order pole. The modular
characteristic of $\mathrm{Vir}_c$ is $\kappa(\mathrm{Vir}_c) = c/2$
(the coefficient of the leading singularity, the identity-valued
fourth-order pole). The first obstruction class is
\begin{equation}\label{eq:virasoro-obstruction}
 \mathrm{Ob}_1(\mathrm{Vir}_c)
 \;=\;
 \frac{c}{2} \cdot \omega_1
 \;=\;
 \frac{c}{2} \cdot
 \frac{i}{2\operatorname{Im}\tau}\, dz \wedge d\bar z,
\end{equation}
the curvature $\dfib^{\,2} = \kappa(\mathrm{Vir}_c)\cdot\omega_1$.
This obstruction vanishes if and only if $c = 0$; at $c \neq 0$,
the Virasoro bar complex is necessarily curved at genus~$1$.

\smallskip\noindent
\textbf{Comparison with Heisenberg and affine.}
The three examples illustrate the hierarchy:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lcccc}
\textbf{Algebra} & \textbf{Class} & $d_{\mathrm{alg}}$ & $\kappa$ &
 \textbf{Curved at $g=1$?} \\
\hline
Heisenberg $\cH_k$ & G & $0$ & $k$ & Yes ($\kappa = k$) \\
$\hat\fg_k$ & L & $1$ & $(k+h^\vee)d/(2h^\vee)$ &
 Yes ($\kappa \neq 0$ for $k \neq -h^\vee$) \\
$\mathrm{Vir}_c$ & M & $\infty$ & $c/2$ & Yes ($c \neq 0$),
 plus $m_k \neq 0$, $k \geq 3$
\end{tabular}
\end{center}
All three are curved at genus~$1$ (for generic parameters), but the
Virasoro is the only one with non-trivial higher $A_\infty$ operations
$m_{k \ge 3}$ at genus~$0$; Heisenberg and affine Kac--Moody have
$m_{k \ge 3} = 0$ (the chiral products are binary).
In the shadow depth classification of Volume~I,
the three examples occupy distinct classes. The Heisenberg is
class~$\mathbf{G}$ ($d_{\mathrm{alg}} = 0$): its shadow obstruction tower
terminates at~$\kappa$. Affine Kac--Moody is
class~$\mathbf{L}$ ($d_{\mathrm{alg}} = 1$): its shadow obstruction tower
extends to the cubic shadow $\mathfrak{C}(\hat\fg_k)$ (from the
Lie structure constants) but terminates at $r_{\max} = 3$.
The Virasoro is class~$\mathbf{M}$
($d_{\mathrm{alg}} = \infty$): its $A_\infty$ structure is genuinely
infinite, with nonzero $m_k$ for all $k \ge 3$, generated by the
quartic pole in the OPE. This infinite depth is \emph{not} a defect
but a feature: the non-vanishing of the higher operations drives the
infinite shadow obstruction tower of Volume~I.
\end{example}

\begin{remark}[Comparison with Gaiotto--Kulp--Wu higher operations]
\label{rem:gkw-higher-operations-comparison}
\index{Gaiotto--Kulp--Wu!higher operations comparison}
\index{higher operations!GKW comparison}
\index{formality!GKW vs shadow depth}
The preceding examples exhibit specific instances of a general
comparison between the $A_\infty$-operations studied here and
the perturbative higher operations of
Gaiotto--Kulp--Wu~\cite{GKW2025}.
Two constructions produce $A_\infty$-operations on the same
configuration spaces $\FM_k(\C) \times \Conf_m(\R)$:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{GKW perturbative operations.}
 Gaiotto--Kulp--Wu compute $m_k^{\mathrm{GKW}}$ via
 regularized Feynman integrals in the
 holomorphic-topological BV formalism on
 $\C_z \times \R_t$. The Feynman graphs are weighted by
 propagators on $\FM_k(\C) \times \Conf_m(\R)$, and the
 BRST-anomaly brackets satisfy the Wess--Zumino consistency
 conditions~\cite{GKW2025}.
\item \emph{Transferred $A_\infty$ operations.}
 Our $m_k$ arise from homotopy transfer of the
 $E_1$ coalgebra structure on $\barB(\cA)$ to the bar cohomology
 $H^*(\barB(\cA))$ via the Kadeishvili tree formula. The
 transferred operations satisfy the Stasheff $A_\infty$ relations
 by construction.
\end{enumerate}

These two constructions produce the \emph{same} operations.
The Wess--Zumino consistency conditions of~(a) and the Stasheff
$A_\infty$ relations of~(b) are identical quadratic axioms on the
collection $\{m_k\}_{k \geq 2}$: the degree-$n$ Stasheff relation
$\sum_{i+j=n+1}\sum_s (-1)^{\epsilon} m_i(\ldots, m_j(\ldots),
\ldots) = 0$ is precisely the degree-$n$ Wess--Zumino
consistency condition. Since both~(a) and~(b) produce
$A_\infty$ structures on the same underlying graded vector space
(the bar cohomology), they are related by the uniqueness of the
$A_\infty$ minimal model up to $A_\infty$ isomorphism
(Kadeishvili). On the primary line (the one-dimensional subspace
spanned by a strong generator), the identification is explicit:
$m_k^{\mathrm{GKW}}(sT, \ldots, sT)
= m_k^{\mathrm{SC}}(sT, \ldots, sT)
= S_k \cdot e_{2k}$,
where $S_k$ is the $k$-th shadow coefficient of Volume~I
and $e_{2k}$ the weight-$2k$ basis vector.

The GKW formality theorem~\cite{GKW25} establishes a binary
dichotomy: when the topological direction has dimension
$d' \geq 2$, the $A_\infty$ structure is \emph{formal}
(all $m_k = 0$ for $k \geq 3$ at the chain level).
At $d' = 1$, the structure is generically non-formal.
The shadow depth classification of Volume~I
refines this binary dichotomy into four classes, measuring
the precise \emph{depth} of non-formality within the
$d' = 1$ regime:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lcccll@{}}
\toprule
\textbf{Class}
& $r_{\max}$
& $m_3^{\mathrm{SC}}$
& $m_4^{\mathrm{SC}}$
& \textbf{Families}
& \textbf{Mechanism} \\
\midrule
$\mathbf{G}$ (Gaussian)
& $2$
& $= 0$
& $= 0$
& Heisenberg, lattice VOAs
& central bracket; nested brackets vanish \\
$\mathbf{L}$ (Lie)
& $3$
& $\neq 0$
& $= 0$
& affine KM
& $S_3 = \tfrac{2h^\vee}{k+h^\vee}$; Jacobi kills depth $\geq 4$ \\
$\mathbf{C}$ (contact)
& $4$
& $= 0$
& $\neq 0$
& $\beta\gamma$
& weight parity kills cubic; rank-one rigidity kills depth $\geq 5$ \\
$\mathbf{M}$ (mixed)
& $\infty$
& $\neq 0$
& $\neq 0$
& Virasoro, $\cW_N$
& $S_3 = 2$, $S_4 = \tfrac{10}{c(5c{+}22)}$; non-nilpotent cascade \\
\bottomrule
\end{tabular}
\end{center}
Class~$\mathbf{G}$ is the key refinement: these algebras
are formal \emph{even at} $d' = 1$,
a phenomenon invisible to the GKW binary classification.
The remaining three classes $\mathbf{L}$/$\mathbf{C}$/$\mathbf{M}$
are all non-formal in the GKW sense, but differ in the degree at
which the $A_\infty$ tower terminates.
The explicit shadow coefficients~$S_k$ are c-independent at
the cubic level ($S_3 = 2$ for class~$\mathbf{M}$) but
acquire c-dependence at the quartic level
($Q^{\mathrm{contact}}_{\mathrm{Vir}} = 10/[c(5c+22)]$ for
Virasoro); see Volume~I,
Proposition~\ref*{V1-prop:swiss-cheese-nonformality-by-class}
for the complete proof.
Computational verification:
\texttt{compute/lib/theorem\_ainfty\_nonformality\_class\_m\_engine.py}
($77$~tests).

The shadow obstruction tower of Volume~I extends the comparison
beyond genus~$0$. The GKW operations are intrinsically
genus-$0$ (with one-loop bulk corrections): they are defined by
Feynman integrals on $\FM_k(\C)$, without access to the
worldsheet genus expansion. The Maurer--Cartan element
$\Theta_\cA \in \mathrm{MC}(\gAmod)$ packages all $m_k^{\mathrm{SC}}$
into a single object whose degree-$k$ projection recovers
$m_k^{\mathrm{SC}}$ at genus~$0$, and whose genus-$g$
projection gives the obstruction class
$\mathrm{Ob}_g(\cA) = \kappa(\cA) \cdot \omega_g$
(on the uniform-weight lane). The MC equation
$D\Theta + \tfrac{1}{2}[\Theta,\Theta] = 0$
is the all-genera, all-degree master equation of which the
GKW consistency conditions are the genus-$0$, degree-$n$
projections.

Computational verification:
\texttt{compute/lib/theorem\_gaiotto\_higher\_ops\_bridge\_engine.py}
($82$~tests).
\end{remark}


\begin{remark}[Factorization of the Swiss-cheese convolution algebra]
\label{rem:sc-convolution-factorization}
\index{convolution algebra!Swiss-cheese factorization}
\index{Swiss-cheese!convolution factorization}
The Swiss-cheese convolution algebra decomposes as a product of
commuting factors:
\[
\mathfrak{g}_\cA^{\mathrm{SC}}
\;\simeq\;
\mathfrak{g}_\cA^{\mathrm{mod}}
\;\times\;
\mathfrak{g}_\cA^{\R},
\]
where $\mathfrak{g}_\cA^{\mathrm{mod}}$ is the modular
\textup{(}closed-sector, $\Einf$-type\textup{)} convolution
dg~Lie algebra controlling the genus expansion
$F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$, and
$\mathfrak{g}_\cA^{\R}$ is the topological
\textup{(}open-sector, $\Eone$-type\textup{)} convolution
algebra controlling the $R$-matrix and braiding.
The MC element decomposes accordingly:
$\Theta_\cA^{\mathrm{SC}} = \Theta_\cA^{\mathrm{mod}}
\oplus \Theta_\cA^{\R}$,
with $\Theta_\cA^{\mathrm{mod}}$ producing the shadow
obstruction tower
\textup{(}$\kappa$, $S_3$, $Q^{\mathrm{contact}}$, \ldots\textup{)}
and $\Theta_\cA^{\R}$ producing the Yangian $R$-matrix
$r(z) = k\,\Omega/z$ (the collision residue, with level~$k$)
\textup{(}Remark~\textup{\ref{V1-rem:mc3-ordered-bar-bridge}}\textup{)}.
The two factors commute because the closed-sector operations
\textup{(}symmetric, on $\Ran(X)$\textup{)} and the open-sector
operations \textup{(}ordered, on $\Conf^<(X)$\textup{)} live on
different configuration spaces with no interaction terms.
The averaging map $\operatorname{av}\colon
\mathfrak{g}_\cA^{\mathrm{SC}} \twoheadrightarrow
\mathfrak{g}_\cA^{\mathrm{mod}}$ is the projection killing the
$\R$-factor: the five main theorems~A--H are the
$\operatorname{av}$-images of the full Swiss-cheese data.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{BD factorization Swiss-cheese algebras}
\label{sec:BD-factorization-SC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The local model on~$\C$ cannot see $D$-module monodromy around
cycles of~$\Sigma_g$ or the moduli-space dependence that produces
the curvature $\kappa(\cA) \cdot \omega_g$ at genus $g \geq 1$.
Both require the global setting of Beilinson--Drinfeld, where
chiral algebras are factorizable $D$-modules on the Ran space of
a curve~$\Sigma_g$. The two-coloured Swiss-cheese structure
extends to this setting on the product $\Sigma_g \times \R$.

\begin{definition}[BD factorization Swiss-cheese algebra]
\label{def:BD-SC}
\index{BD factorization Swiss-cheese algebra|textbf}
A \emph{BD factorization Swiss-cheese algebra on $\Sigma_g \times \R$}
consists of the following data:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Closed sector.} A factorizable $D$-module
 $F_{\mathsf{cl}}$ on $\Ran(\Sigma_g)$, encoding the
 holomorphic chiral product.

\item \textbf{Open sector.} A locally constant factorization
 algebra $F_{\mathsf{op}}$ on $\Ran(\R)$, equivalent to an
 $\Eone$-algebra (by the Ayala--Francis recognition theorem
 \cite{AF15}).

\item \textbf{Mixed sector (bulk--boundary module).} For
 configurations with $k$ closed points on~$\Sigma_g$ and $m$ open
 points on the boundary $\Sigma_g \times \{0\}$ of the half-space
 $\Sigma_g \times \R_{\geq 0}$, a factorization module structure
 \begin{equation}\label{eq:mixed-sector}
 F_{\mathsf{mix}}(k,m)
 \;\in\;
 \Dmod\bigl(\Ran_k(\Sigma_g)\bigr)
 \;\otimes\;
 \Fact_m(\R),
 \end{equation}
 where $\Ran_k$ denotes the stratum of subsets of cardinality
 exactly~$k$, and $\Fact_m(\R)$ denotes the $m$-ary component of
 the factorization algebra on~$\R$.

 The mixed sector carries the following structure maps:

 \begin{enumerate}[label=\textup{(\alph*)}]
 \item \emph{Bulk action on the boundary.} For each partition
 of closed points $\{z_1,\ldots,z_k\} = S_{\mathrm{act}} \sqcup
 S_{\mathrm{pass}}$ with $S_{\mathrm{act}}$ disjoint from
 the open points $\{t_1,\ldots,t_m\} \subset \R$, a
 composition map
 \begin{equation}\label{eq:bulk-action-composition}
 \mu^{\mathsf{mix}}_{S_{\mathrm{act}}}\colon
 F_{\mathsf{cl}}\big|_{\Ran_{|S_{\mathrm{act}}|}(\Sigma_g)}
 \;\otimes\;
 F_{\mathsf{mix}}(|S_{\mathrm{pass}}|, m)
 \;\longrightarrow\;
 F_{\mathsf{mix}}(|S_{\mathrm{pass}}|, m),
 \end{equation}
 given by the diagonal restriction
 $\Delta_{S_{\mathrm{act}}} \subset
 \Ran_{|S_{\mathrm{act}}|}(\Sigma_g) \times
 \Ran_{|S_{\mathrm{pass}}|}(\Sigma_g)$,
 tensored with the identity on $\Fact_m(\R)$.
 This map is a $D$-module morphism in the $\Sigma_g$-variables
 and respects the factorization structure on~$\R$.

 \item \emph{Associativity of the bulk action.} For
 a further partition $S_{\mathrm{act}} = S_1 \sqcup S_2$,
 the iterated composition satisfies
 \[
 \mu^{\mathsf{mix}}_{S_1} \circ
 (\id \otimes \mu^{\mathsf{mix}}_{S_2})
 \;=\;
 \mu^{\mathsf{mix}}_{S_1 \sqcup S_2}
 \circ (\mu^{\mathsf{cl}}_{S_1, S_2} \otimes \id),
 \]
 where $\mu^{\mathsf{cl}}_{S_1,S_2}$ is the closed-sector
 factorization product. Iterating over all decompositions
 $S = S_1 \sqcup \cdots \sqcup S_r$ gives the higher
 associativity constraints: the mixed sector is a module over
 the closed-sector factorization algebra in the precise sense
 of \cite{BD04}, \S3.4.11.

 \item \emph{Open composition.} For a decomposition
 $\{t_1,\ldots,t_m\} = T_1 \sqcup T_2$ with
 $\max(T_1) < \min(T_2)$ (ordered partition), the
 factorization splitting on~$\R$ acts:
 \[
 F_{\mathsf{mix}}(k, |T_1| + |T_2|)
 \big|_{U_{T_1,T_2}}
 \;\xrightarrow{\;\sim\;}
 F_{\mathsf{mix}}(k, |T_1|) \;\otimes\;
 F_{\mathsf{op}}(|T_2|),
 \]
 equipping $F_{\mathsf{mix}}(k,-)$ with a right
 $F_{\mathsf{op}}$-module structure in $\Fact(\R)$.
 \end{enumerate}

\item \textbf{Directionality.} Bulk-to-boundary maps exist:
 $F_{\mathsf{cl}}$ acts on $F_{\mathsf{op}}$ via the mixed
 sector. The reverse direction is \emph{empty}: there are no
 open-to-closed operations
 ($F_{\mathsf{mix}}(\ldots,\mathsf{top},\ldots;\,\mathsf{cl})
 = 0$). Categorically: the restriction functor
 $\iota^!\colon \Dmod(\Ran(\Sigma_g \times \R))
 \to \Dmod(\Ran(\Sigma_g \times \{0\}))$ has a left adjoint
 $\iota_!$ (extension by zero from the boundary), but the
 factorization structure forces
 $\iota_!(F_{\mathsf{op}}) \otimes^{!}
 F_{\mathsf{cl}} = 0$: the $!$-tensor product of an extended
 boundary $D$-module with a bulk $D$-module vanishes by
 support considerations (the boundary $\Sigma_g \times \{0\}$
 has codimension~$1$ in $\Sigma_g \times \R$, and the
 $!$-extension carries no sections transverse to the boundary).
 This is the factorization expression of the
 Swiss-cheese directionality
 $\SCchtop(\ldots,\mathsf{top},\ldots;\,\mathsf{ch}) =
 \varnothing$ (cf.\ Definition~\ref{def:SC-operations}).
\end{enumerate}
\end{definition}

\begin{remark}[The $\Eone$ colour as primitive]
\label{rem:e1-colour-primitive}
\index{Swiss-cheese operad!E1 colour as primitive@$\Eone$ colour as primitive}
\index{ordered bar complex!Swiss-cheese provenance}
\index{E1 algebra@$\Eone$-algebra!open colour}
The open sector $F_{\mathsf{op}}$ in
Definition~\ref{def:BD-SC} is an $\Eone$-algebra on~$\R$ by
the Ayala--Francis recognition theorem: it is \emph{associative},
not commutative. The ordered/topological direction is the
primitive ingredient of the Swiss-cheese structure, not an
auxiliary feature. Concretely, the bar complex of~$\cA$ carries
two coproducts:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the \emph{coshuffle} coproduct on $(s^{-1}\bar\cA)^{\otimes
 n}_{\Sigma_n}$, encoding the closed/$\Einf$ holomorphic
 factorization on $\Ran(\Sigma_g)$: the coproduct of
 the symmetric bar $\barBch(\cA)$;
\item the \emph{deconcatenation} coproduct on
 $(s^{-1}\bar\cA)^{\otimes n}$ (no $\Sigma_n$ quotient), encoding
 the open/$\Eone$ topological factorization on $\Ran(\R)$: the
 coproduct of the ordered bar
 $\barB^{\mathrm{ord}}(\cA)$.
\end{enumerate}
The $\Eone$-chiral coassociative coalgebra structure on the bar
complex combines both coproducts: the bar differential encodes
the holomorphic factorization (closed colour), the deconcatenation
coproduct encodes the topological factorization (open colour), and
the mixed-sector composition maps~\eqref{eq:bulk-action-composition}
intertwine them.  The $\SC^{\ch,\top}$ structure emerges not on the
bar complex itself but on the derived chiral center
$\bigl(C^\bullet_{\ch}(\cA,\cA),\, \cA\bigr)$
(Remark~\ref{rem:bar-not-sc-coalgebra}).
The symmetric bar, which retains only coproduct~(i),
is the closed-colour projection: it discards the open/$\Eone$
direction and with it the $R$-matrix, the braided monoidal category
of line operators, and the full Drinfeld--Kohno comparison.

At the level of MC elements, the ordered MC element
$\Theta_\cA^{\Eone}$ in the $\Eone$ convolution algebra
${\mathfrak{g}}_\cA^{\Eone}$ projects to the modular MC element
$\Theta_\cA$ under the $\Sigma_n$-coinvariant averaging map
$\operatorname{av}\colon {\mathfrak{g}}_\cA^{\Eone}
\twoheadrightarrow \mathfrak{g}_\cA^{\mathrm{mod}}$. The shadow
obstruction tower $(\kappa, \mathfrak{C}, \mathfrak{Q}, \ldots)$ is
the image of $(r(z), r_3, r_4, \ldots)$ under this projection.
The five main theorems~A--H of Vol~I are the invariants that survive
averaging; the full Swiss-cheese structure, developed in this chapter,
is the ordered ancestor from which they descend.
\end{remark}

\begin{remark}[Homotopy-Koszulity and $E_1$-bar primacy]
\label{rem:e1-bar-primacy}%
\index{bar complex!E1 primacy@$E_1$ primacy}%
\index{homotopy-Koszulity!bar primacy}%
The homotopy-Koszulity of $\SCchtop$
(Theorem~\ref{thm:homotopy-Koszul}) has a direct consequence for
the choice of bar complex: the ordered bar
$\barB^{\mathrm{ord}}(\cA)$ is the ``right'' bar complex for
a logarithmic $\SCchtop$-algebra, in the sense that it carries the
full $E_1$ coproduct from $\Conf_k^<(\R)$ and the full
differential from $\FM_k(\C)$, without discarding ordering data
via $\Sigma_n$-coinvariants. The symmetric bar $\barBch(\cA)$
is the $R$-matrix-twisted $\Sigma_n$-descent of
$\barB^{\mathrm{ord}}(\cA)$
(Remark~\ref{rem:three-bar-complexes}(i)--(iii)). The ordered
bar complex is the $\Eone$-chiral coassociative coalgebra
homotopy-Koszul dual to~$\cA$; the symmetric bar complex is Koszul dual to
$\cA$ as a chiral algebra. The former retains the $R$-matrix,
the braided monoidal structure on line operators, and the full
Drinfeld--Kohno comparison; the latter discards all three.
\end{remark}

\begin{proposition}[Mixed-sector genus independence]
\label{prop:mixed-sector-genus-independence}
\ClaimStatusProvedHere
\index{Swiss-cheese!mixed sector genus independence|textbf}
\index{mixed sector!genus independence}
The Swiss-cheese operations
$m_k^{\mathrm{SC}} \colon
V_{\mathrm{cl}}^{\otimes j} \otimes V_{\mathrm{op}}^{\otimes m}
\to V_{\mathrm{op}}$
are genus-$0$ operations: they are defined by integration over
$\FM_k(\C) \times \Conf_m^<(\R)$ with no genus parameter.
The modular extension
$\Theta_\cA \in \MC(\gAmod)$ introduces genus dependence
\emph{only} in the closed sector $\gAmod$
\textup{(}via the genus-$g$ curvature
$\dfib^{\,2} = \kappa \cdot \omega_g$\textup{)}.
The open/$\Eone$ sector and the mixed sector are
genus-independent: for every $g \geq 0$, the restriction
$\Theta_\cA^{\Eone}\big|_{\mathrm{mixed}}$ is the
\emph{same} collection of operations $\{m_k^{\mathrm{SC}}\}$.
This follows from the product decomposition
$\mathfrak{g}_\cA^{\mathrm{SC}}
\simeq \mathfrak{g}_\cA^{\mathrm{mod}}
\times \mathfrak{g}_\cA^{\R}$
\textup{(}Remark~\textup{\ref{rem:sc-convolution-factorization}}\textup{)}:
the genus parameter lives entirely in the first factor, so
the second factor \textup{(}which controls the mixed and open
sectors\textup{)} is oblivious to~$g$.
\end{proposition}

\begin{proof}
The Swiss-cheese operad $\SCchtop$ acts on
$\FM_k(\C) \times \Conf_m^<(\R)$, which has no genus
parameter: the $\C$-factor is the complex plane
\textup{(}genus~$0$\textup{)}, not a higher-genus surface.
The genus enters only through the modular operad
$\cM_{\Com}(g,n)$ acting on the closed sector via the
Feynman transform. Since the SC convolution algebra
factors as
$\mathfrak{g}_\cA^{\mathrm{SC}} =
\mathfrak{g}_\cA^{\mathrm{mod}} \times
\mathfrak{g}_\cA^{\R}$
with $\mathfrak{g}_\cA^{\R}$ controlling the open and
mixed sectors, and the genus-$g$ deformation acts only on
$\mathfrak{g}_\cA^{\mathrm{mod}}$, the mixed-sector
operations are unaffected.
\end{proof}

\begin{remark}[Homotopy-Koszulity and the bar complex of Volume~I]
\label{rem:homotopy-koszulity-vol1-bar}%
\index{homotopy-Koszulity!Volume I bar complex}%
\index{bar complex!E1 as ``right'' bar}%
The homotopy-Koszulity of $\SCchtop$
(Theorem~\ref{thm:homotopy-Koszul}) identifies the ordered
bar $\barB^{\mathrm{ord}}(\cA)$ as the
\emph{primitive} bar complex: it is the $E_1$
coassociative coalgebra from which the symmetric bar
$\barBch(\cA)$ of Volume~I descends by
$\Sigma_n$-coinvariant averaging. The five theorems of
Volume~I (Theorems~A--D$+$H) and the shadow obstruction tower
$\Theta_A^{\le r}$ are invariants of the symmetric bar. The
ordered bar carries strictly more data: the $A_\infty$
operations $\{m_k\}$, the braided monoidal structure on line
operators, and the $R$-matrix. In this sense, the
$E_1$ bar is the ``right'' bar for the full
$3$-dimensional theory, and the Volume~I bar is its
$\Sigma_n$-shadow. The Koszulness characterisation programme
(Volume~I, Theorem~\ref*{V1-thm:koszul-equivalences-meta})
applies to the symmetric bar; the $E_1$ refinement
is the subject of Chapter~\ref{ch:factorization-swiss-cheese}.
\end{remark}

\begin{remark}[Families over $\Mbar_g$]
\label{rem:families-over-Mbar}
For varying genus~$g$, the collection $\{F_{\mathsf{cl}}^{(g)}\}$
defines a family of factorizable $D$-modules parametrised by the
moduli stack $\Mbar_g$. The $D$-module structure on
$\Ran(\Sigma_g)$ varies with the complex structure of~$\Sigma_g$.
Concretely: the chiral operations
(Definition~\ref{def:chiral-ops-fact}) at genus~$g$ involve
integration over the fibres of the universal curve
$\pi\colon \cC_g \to \Mbar_g$, and the result depends on the
point of~$\Mbar_g$ through the period matrix $\tau_{ij}(g)$.
The Gauss--Manin connection on the family induces a connection on
the bar complex; its curvature is
$\dfib^{\,2} = \kappa(\cA) \cdot \omega_g$, arising from the monodromy
of the $D$-module connection around $B$-cycles of~$\Sigma_g$.
This is a theorem about $D$-modules: it involves the global
structure of the curve and is invisible to the local operadic model.
\end{remark}

\begin{construction}[Bar complex as factorization coalgebra]
\label{constr:bar-fact-coalgebra}
\index{bar complex!as factorization coalgebra}
Let $(F_{\mathsf{cl}}, F_{\mathsf{op}}, F_{\mathsf{mix}})$ be a
BD factorization Swiss-cheese algebra on $\Sigma_g \times \R$.
The \emph{bar complex} $\barB(F)$ is the factorization coalgebra on
$\Ran(X)$ Koszul-dual to $F_{\mathsf{cl}}$, constructed as follows:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Underlying graded object.} The tensor coalgebra
 $T^c(s^{-1}\bar{F}_{\mathsf{cl}})$ on $\Ran(X)$, where
 $s^{-1}$ denotes the desuspension shift and
 $\bar{F}_{\mathsf{cl}}$ is the augmentation ideal.

\item \textbf{Bar differential.} The differential
 $d_{\barB}$ is determined by the chiral operations:
 it is the sum of diagonal restrictions
 \eqref{eq:chiral-op-diagonal}, dualized via the
 factorization structure. At genus~$0$,
 $d_{\barB}^2 = 0$ and $\barB(F)$ is an honest dg coalgebra.

\item \textbf{Bar coproduct.} The coassociative coproduct
 $\Delta$ is the factorization isomorphism
 \eqref{eq:fact-iso} dualized: splitting a configuration
 $S = S_1 \sqcup S_2$ into disjoint subsets corresponds to
 ordered deconcatenation $[a_1|\cdots|a_n] \mapsto
 \sum_{i=0}^n [a_1|\cdots|a_i] \otimes
 [a_{i+1}|\cdots|a_n]$.

\item \textbf{Curvature at genus $g \geq 1$.} At genus~$g \geq 1$,
 the curvature $\dfib^{\,2} = \kappa(\cA) \cdot \omega_g$ is
 the image of the annular trace under the clutching map:
 the cyclic trace on the open sector seeds the Calabi--Yau
 datum, and genus raising by clutching produces
 $\kappa(\cA) \cdot \omega_g \in H^0(\Mbar_g, \omega_{\Mbar_g})$.
 The bar differential inherits this as a curved structure
 (Volume~I, Theorem~D). The bar complex becomes a
 \emph{curved factorization coalgebra}: a coalgebra in the
 coderived category of $D$-modules on $\Ran(\Sigma_g)$.

 The derivation proceeds through three steps.

 \smallskip\noindent
 \emph{Step~1: Propagator monodromy.}
 On~$\C$ (genus~$0$), the propagator is
 $K^{(0)}(z,w) = dz/(z-w)$, which is single-valued. On
 $\Sigma_g$, the holomorphic propagator is
 $K^{(g)}(z,w) = \partial_z \log E(z,w)\,dz$,
 where $E(z,w)$ is the prime form. This propagator is
 multi-valued: analytic continuation of $z$ around the
 $B$-cycle~$B_j$ produces a monodromy shift
 \begin{equation}\label{eq:propagator-monodromy}
 K^{(g)}(z + B_j, w)
 \;=\;
 K^{(g)}(z,w)
 \;+\;
 2\pi i\, \nu_j(w),
 \end{equation}
 where $\nu_j \in H^0(\Sigma_g, \Omega^1)$ is the $j$th
 normalised holomorphic differential (the column of the period
 matrix: $\oint_{A_i} \nu_j = \delta_{ij}$,
 $\oint_{B_i} \nu_j = \tau_{ij}$). The Arakelov
 single-valued propagator is obtained by adding a
 non-holomorphic correction:
 \[
 K^{(g)}_{\mathrm{Ar}}(z,w)
 \;=\;
 K^{(g)}(z,w)
 \;-\;
 2\pi i \sum_{j=1}^g
 (\operatorname{Im}\tau)^{-1}_{jk}\,
 \operatorname{Im}\Bigl(\int_w^z \nu_k\Bigr)\, \nu_j(w).
 \]
 This propagator is single-valued on $\Sigma_g$ but is no longer
 holomorphic: $\bar\partial_z K^{(g)}_{\mathrm{Ar}}(z,w)
 = -2\pi i\, \omega_g(z)$, where $\omega_g = \frac{i}{2}
 \sum_{j,k} (\operatorname{Im}\tau)^{-1}_{jk}\,
 \nu_j \wedge \bar{\nu}_k$ is the Arakelov $(1,1)$-form
 on~$\Sigma_g$ (Volume~I, Convention~3.1, three-propagator
 comparison table).

 \smallskip\noindent
 \emph{Step~2: Arnold defect from monodromy.}
 At genus~$0$, the Arnold relation
 $\eta_{12} \wedge \eta_{23} + \eta_{23} \wedge \eta_{31}
 + \eta_{31} \wedge \eta_{12} = 0$
 (where $\eta_{ij} = d\log(z_i - z_j)$) ensures
 $\dfib^{\,2} = 0$. At genus~$g$, replacing the rational
 propagator by $K^{(g)}_{\mathrm{Ar}}$: define the
 \emph{Arakelov-regularised logarithmic one-forms}
 \[
 \eta^{(g)}_{ij}
 \;:=\;
 \partial_{z_i}\log E(z_i, z_j)\,dz_i
 \;-\;
 2\pi i \sum_{\alpha=1}^{g}
 (\operatorname{Im}\tau)^{-1}_{\alpha\beta}\,
 \operatorname{Im}\!\Bigl(\int_{z_j}^{z_i}\nu_\beta\Bigr)
 \,\nu_\alpha(z_j),
 \]
 where $E(z_i,z_j)$ is the prime form, $\nu_\alpha$ are
 normalised Abelian differentials, and
 $\tau_{\alpha\beta}$ is the period matrix. These forms are
 single-valued on $\Sigma_g$ (the Arakelov correction cancels
 the $B$-cycle monodromy of the prime form) but
 satisfy a \emph{defective} Arnold relation. The defect
 arises because the Arakelov correction is not holomorphic:
 at three points,
 \begin{equation}\label{eq:arnold-defect-genus-g}
 \eta^{(g)}_{12} \wedge \eta^{(g)}_{23}
 + \eta^{(g)}_{23} \wedge \eta^{(g)}_{31}
 + \eta^{(g)}_{31} \wedge \eta^{(g)}_{12}
 \;=\;
 \omega_g(z_3) \cdot
 (dz_1 - dz_2) \wedge (dz_2 - dz_3)
 \;+\; \text{cyclic},
 \end{equation}
 where the right side is the pullback of the Arakelov form to the
 configuration space $\Conf_3(\Sigma_g)$
 (at genus~$1$, this reduces to $E_2(\tau) \cdot (dz_1 - dz_2)
 \wedge (dz_2 - dz_3)$, recovering the classical Eisenstein
 series defect of
 Proposition~\ref{prop:genus-1-arnold-defect}).

 \smallskip\noindent
 \emph{Step~3: Contraction with OPE data.}
 The square $\dfib^{\,2}$ is computed by composing the bar
 differential with itself: $\dfib^{\,2}|_{\barB^k(\cA)}$
 involves two successive diagonal restrictions, producing
 integrals over $\FM_k(\Sigma_g)$ with two propagator
 insertions. The Arnold defect \eqref{eq:arnold-defect-genus-g}
 enters at the two-fold composition: the failure of the
 Arnold relation produces a residual $(1,1)$-form on the
 base $\Sigma_g$ contracted with the OPE data of~$\cA$.
 At genus~$0$, $\dfib$ is a coderivation of the cofree coalgebra
 $T^c(s^{-1}\bar{F}_{\mathsf{cl}})$, so $\dfib^{\,2}$ is
 determined by its cogenerator projection. At genus~$g \geq 1$,
 $\dfib$ is \emph{not} a strict coderivation
 \textup{(}the cross-terms at interior splittings produce a
 factor-$2$ discrepancy; see the proof sketch below\textup{)},
 but the cogenerator projection still computes the obstruction
 class $\dfib^{\,2}$.
 The cogenerator projection of the two-fold composition
 extracts the \emph{leading OPE coefficient}, which is by
 definition the modular characteristic $\kappa(\cA)$
 \textup{(}by the universal-generating-function theorem of
 Volume~I\textup{)}.
 Therefore
 \[
 \dfib^{\,2}
 \;=\;
 \kappa(\cA) \cdot \omega_g,
 \]
 where the right side is the coderivation determined by the
 scalar $\kappa(\cA)$ times the Hodge class
 $\omega_g \in H^{1,1}(\Sigma_g)$.
 The three propagators (rational $K^{(0)}$, flat,
 genus~$0$; prime form $K^{(g)}$, holomorphic, multi-valued;
 Arakelov $K^{(g)}_{\mathrm{Ar}}$, single-valued, curved)
 are the chain-level manifestations of the three models of
 Corollary~\ref{cor:three-models-from-fact}. The curvature
 $\kappa(\cA) \cdot \omega_g$ is the obstruction to
 single-valuedness of the bar differential on~$\Sigma_g$:
 it is the $D$-module monodromy of $F_{\mathsf{cl}}$ around
 the $B$-cycles, measured by the Arakelov normalisation.
\end{enumerate}
The bar differential encodes the holomorphic (closed) colour.
The bar coproduct encodes the topological (open) colour. Together,
$\barB(F)$ is an $\Eone$-chiral coassociative factorization coalgebra
on $\Ran(\Sigma_g) \times \Ran(\R)$, carrying both colours as an
$\Eone$-coalgebra over $(\mathrm{ChirAss})^!$.
The $\SC^{\ch,\top}$ structure lives not on $\barB(F)$ but on the
derived chiral center pair
$\bigl(C^\bullet_{\ch}(\cA,\cA),\, \cA\bigr)$
(Remark~\ref{rem:bar-not-sc-coalgebra}).
\end{construction}

\begin{proof}[Proof sketch of $\dfib^{\,2} = \kappa(\cA) \cdot \omega_g$]
At genus~$0$ the bar differential is a coderivation of the bar coalgebra, and $d^2$ is determined by its cogenerator projection. At genus~$g \geq 1$ the fiberwise differential $\dfib$ with $\dfib^{\,2} = \kappa \cdot \omega_g \neq 0$ is \emph{not} a coderivation (the cross terms at interior splittings produce a factor-$2$ discrepancy; see Remark~\ref{rem:bar-ordered-primacy} of Vol~I). The cogenerator projection nevertheless computes the \emph{obstruction class}: $\dfib^{\,2}$ is determined by the cogenerator projection to the degree-$1$ component $s^{-1}\cA$. This cogenerator extracts a double residue:
\[
\mathrm{copr}(\dfib^{\,2})
= \operatorname{Res}_{z_1 = z_2}\operatorname{Res}_{z_2 = z_3}
\bigl[\eta^{(g)}(z_1, z_2)\,\eta^{(g)}(z_2, z_3) \cdot \mu_2(a_1, a_2, a_3)\bigr].
\]
Decompose $\eta^{(g)} = h + R$ into the holomorphic propagator $h = \partial_z \log E$ and the Arakelov correction~$R$. Three terms arise:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $h \cdot h$: vanishes by the Fay trisecant identity (the holomorphic Arnold $3$-form is zero).
\item $R \cdot R$: vanishes because $R$ is smooth (no poles to produce residues).
\item $h \cdot R + R \cdot h$: the cross-term. The residue of $h \cdot R$ at $z_1 = z_2$ extracts the OPE coefficient at the simple pole, leaving $R(z_2, z_3)$ evaluated at $z_2 = z_3$. Since $\bar\partial R = +\omega_{\mathrm{Ar}}$ (the Arakelov $(1,1)$-form; Equation~\ref{eq:dbar-arakelov}), and the OPE coefficient is the structure constant weighted by $\kappa(\cA) = \mathrm{Tr}_\cA$, the double residue produces $\kappa(\cA) \cdot \omega_g$.
\end{enumerate}
The detailed computation at genus~$1$ for the Heisenberg algebra is in Section~\textup{\ref{sec:heisenberg-genus-1-complete}}; the mechanism at general genus replaces the Weierstrass $\zeta$-function by the prime-form propagator and $\omega_1$ by~$\omega_g$.
\end{proof}

\begin{remark}[Three chain-level models of the genus-$g$ bar complex]
\label{rem:three-models}
\index{three models|textbf}
\index{bar complex!three models}
The three propagators (rational, prime form, Arakelov) give rise
to three chain-level models of the genus-$g$ bar complex, differing in
the choice of trivialisation of the factorization $D$-module
connection:
\begin{center}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{llll}
\textbf{Model} & \textbf{Propagator} & \textbf{Differential} &
 \textbf{Category} \\
\hline
\textup{(i)} Flat associated graded &
 $K^{(0)} = dz/(z{-}w)$ &
 $D_0^{\,2} = 0$ &
 derived $D(\mathbb{k})$ \\
\textup{(ii)} Corrected holomorphic &
 $K^{(g)} = \partial_z \log E(z,w)\,dz$ &
 $\Dg{g}^{\,2} = 0$ &
 derived $D(\mathbb{k})$ \\
\textup{(iii)} Curved geometric &
 $K^{(g)}_{\mathrm{Ar}}$ &
 $\dfib^{\,2} = \kappa \cdot \omega_g$ &
 coderived $D^{\mathrm{co}}$ \\
\end{tabular}
\end{center}
Model~\textup{(i)} is the formal-completion (operadic) gauge; it
extracts the local $\SCchtop$ action. Model~\textup{(ii)} uses the
holomorphic prime form on the universal cover~$\widetilde{\Sigma}_g$,
where the Fay trisecant identity ensures flatness.
Model~\textup{(iii)} uses the single-valued Arakelov propagator on
$\Sigma_g$; the non-holomorphicity of the Arakelov correction produces
curvature $\kappa(\cA) \cdot \omega_g$.

Models~\textup{(i)} and~\textup{(ii)} have strict differentials ($d^2 = 0$)
and live in the ordinary derived category. Model~\textup{(iii)} is
genuinely curved and lives in the coderived category of
Positselski~\cite{Positselski11}. The three models are
gauge-equivalent presentations of a single Maurer--Cartan element
$\delta_\cA = D - D^{(0)}$ in the coderivation dg Lie algebra
(Theorem~\ref{thm:three-models-gauge-orbit}). The passage between
models is the chiral exponential map
(Construction~\ref{constr:chiral-exponential}); its monodromy around
$B$-cycles is governed by the same curvature term, with an explicit
identification proved later only in genus~$1$.

The \emph{existence} of the three models is independent of the
derived/coderived comparison: each model is constructed directly
from the corresponding propagator choice. Their \emph{comparison} as
computational devices is narrower and honest: the two flat models
compute the same ordinary derived package, while the curved model is
the corresponding coderived avatar linked by the chiral exponential
map
(Theorem~\ref{thm:three-models-gauge-orbit} and
Theorem~\ref{thm:derived-coderived-full}). This does \emph{not}
assign ordinary modular bar cohomology to the curved model when
$\dfib^{\,2}\neq 0$. The flat-side comparison uses the
Positselski framework~\cite{Positselski11} only on the conilpotent
finite-type locus where the manuscript's internal comparison applies.
\end{remark}

%%----------------------------------------------------------------------
\subsection{The half-plane bar chain model}
\label{subsec:half-plane-bar-chain}
%%----------------------------------------------------------------------

The bar complex of Construction~\ref{constr:bar-fact-coalgebra}
encodes the two-coloured factorization structure abstractly.
This subsection gives the concrete genus-$0$ chain model on the
upper half-plane $\mathbb{H} = \{z \in \C : \Im(z) > 0\}$ with boundary
$\partial\mathbb{H} = \R$, making the three collision types and the
two restriction maps fully explicit.

\begin{construction}[The half-plane bar complex
$\barB^{\mathbb{H}}(\cA)$]
\label{constr:half-plane-bar}
\index{bar complex!half-plane model|textbf}%
\index{half-plane bar complex|textbf}%
\index{Swiss-cheese!half-plane chain model}%
\ClaimStatusProvedHere{}
Let $\cA$ be a logarithmic $\SCchtop$-algebra
(Definition~\ref{def:log-SC-algebra}).  The \emph{half-plane
bar complex} $\barB^{\mathbb{H}}(\cA)$ is the two-coloured cochain
complex defined as follows.

\medskip\noindent
\textbf{Underlying graded object.}
For integers $k \geq 0$ (bulk) and $m \geq 0$ (boundary) with
$k + m \geq 1$, the $(k,m)$-component is
\begin{equation}\label{eq:half-plane-component}
 \barB^{\mathbb{H}}_{k,m}(\cA)
 \;=\;
 C_\ast\bigl(\FM_k(\C)\bigr)
 \;\otimes\;
 C_\ast\bigl(\Conf_m^<(\R)\bigr)
 \;\otimes\;
 (s^{-1}\bar\cA)^{\otimes(k+m)},
\end{equation}
where $\FM_k(\C)$ is the Fulton--MacPherson compactification
of $k$ points in the interior~$\mathbb{H}$ (equivalently in~$\C$,
since $\mathbb{H} \simeq \C$ as a complex manifold), and
$\Conf_m^<(\R) = \{t_1 < \cdots < t_m\} \subset \R^m$
is the ordered configuration space of $m$ points on the
boundary.  The first $k$ tensor factors of
$(s^{-1}\bar\cA)^{\otimes(k+m)}$ are the bulk labels;
the last $m$ are the boundary labels, carrying the linear order
inherited from~$\R$.

\medskip\noindent
\textbf{Differential.}
The differential $d_{\mathbb{H}}$ on $\barB^{\mathbb{H}}(\cA)$ is a sum of
three terms,
\begin{equation}\label{eq:half-plane-differential}
 d_{\mathbb{H}}
 \;=\;
 d_{\mathrm{bb}}
 \;+\;
 d_{\partial\partial}
 \;+\;
 d_{\mathrm{mix}},
\end{equation}
corresponding to the three collision types in the bordered
Fulton--MacPherson compactification
$\overline{\FM}{}^{\,\mathrm{bord}}_{0,k,m}(\mathbb{H})$
(Construction~\ref{constr:bordered-FM}):

\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Bulk--bulk collisions} ($d_{\mathrm{bb}}$).
 A subset $S \subseteq \{1,\ldots,k\}$ with $|S| \geq 2$ of
 interior points collides in the bulk. The codimension-$1$
 stratum is $\FM_{|S|}(\C) \times \FM_{k - |S| + 1}(\C)$: the
 cluster collapses to a single interior point while the
 remaining points and the boundary stay fixed. The
 boundary map contracts this stratum, applying the chiral
 $(|S|)$-ary product $\mu_{|S|}^{\mathrm{ch}}$ determined by
 the OPE of~$\cA$ on the labels indexed by~$S$:
 \[
 d_{\mathrm{bb}}\colon
 (s^{-1}a_{i_1}) \otimes \cdots \otimes (s^{-1}a_{i_{|S|}})
 \;\longmapsto\;
 s^{-1}\mu_{|S|}^{\mathrm{ch}}(a_{i_1},\ldots,a_{i_{|S|}}).
 \]
 This is the chiral bar differential, encoding
 holomorphic factorization on~$\C$.

\item \textbf{Boundary--boundary collisions}
 ($d_{\partial\partial}$). A subset
 $T = \{j, j{+}1, \ldots, j{+}\ell{-}1\}$ of $\ell \geq 2$
 consecutive boundary points collides along~$\R$.
 Consecutiveness is forced by the ordering: only adjacent
 points in the linear order $t_1 < \cdots < t_m$ can collide
 without passing through each other. The boundary map applies
 the $A_\infty$ operation $m_\ell$ to the corresponding labels:
 \[
 d_{\partial\partial}\colon
 [a_{j}|\cdots|a_{j+\ell-1}]
 \;\longmapsto\;
 [a_1|\cdots|m_\ell(a_{j},\ldots,a_{j+\ell-1})|\cdots|a_m].
 \]
 This is the standard associative bar differential on~$\R$.
 The operations $m_\ell$ arise from the
 restriction of the chiral product to the real locus
 via the Swiss-cheese mixed operations.

\item \textbf{Bulk-to-boundary collisions} ($d_{\mathrm{mix}}$).
 A subset $S \subseteq \{1,\ldots,k\}$ of $|S| \geq 1$ interior
 points approaches the boundary at a position between boundary
 points $t_j$ and $t_{j+1}$ (or to the left of $t_1$, or to
 the right of $t_m$). The codimension-$1$ stratum is the
 exceptional divisor of the mixed blowup
 (Construction~\ref{constr:bordered-FM}), isomorphic to
 $\FM^{\mathrm{bord},\mathrm{red}}_{0,|S|,\ell}(\mathbb{H})$.
 The boundary map applies the Swiss-cheese mixed operation
 \[
 m^{\mathrm{SC}}_{|S|,\ell}\colon
 \cA_{\mathsf{cl}}^{\otimes |S|}
 \otimes
 \cA_{\mathsf{op}}^{\otimes \ell}
 \;\longrightarrow\;
 \cA_{\mathsf{op}}
 \]
 from Definition~\ref{def:SC-operations}(ii), inserting the
 collapsed bulk cluster into the boundary sequence at the
 appropriate position. The directionality constraint
 (Definition~\ref{def:BD-SC}(iv)) is automatic: interior
 points approach the boundary, never the reverse.
\end{enumerate}

\medskip\noindent
\textbf{Coproduct.}
The coproduct $\Delta_{\mathbb{H}}$ on $\barB^{\mathbb{H}}(\cA)$ is ordered
deconcatenation in the boundary labels:
\begin{equation}\label{eq:half-plane-coproduct}
 \Delta_{\mathbb{H}}\bigl(\beta \otimes [a_1|\cdots|a_m]\bigr)
 \;=\;
 \sum_{i=0}^{m}
 \bigl(\beta \otimes [a_1|\cdots|a_i]\bigr)
 \;\otimes\;
 [a_{i+1}|\cdots|a_m],
\end{equation}
where $\beta \in C_\ast(\FM_k(\C)) \otimes
(s^{-1}\bar\cA)^{\otimes k}$ denotes the bulk data, which
is not split by the coproduct.  This encodes topological
factorization along~$\R$: cutting the boundary into two
ordered segments while keeping the bulk configuration intact.
\end{construction}

\begin{proposition}[$d_{\mathbb{H}}^2 = 0$ from $\SCchtop$
coherence]
\label{prop:half-plane-d-squared}
\ClaimStatusProvedHere{}
\index{bar complex!half-plane!d-squared vanishing@$d^2 = 0$}%
The identity $d_{\mathbb{H}}^2 = 0$ on
$\barB^{\mathbb{H}}(\cA)$ holds, with the nine summands of
$(d_{\mathrm{bb}} + d_{\partial\partial} +
d_{\mathrm{mix}})^2$ vanishing in three groups:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $d_{\mathrm{bb}}^2 = 0$: the
 Jacobi/homotopy-associativity relations for the chiral product
 on $\FM_k(\C)$, which hold because $\cA$ is a chiral algebra.

\item $d_{\partial\partial}^2 = 0$: the Stasheff $A_\infty$
 relations for the operations $\{m_\ell\}$ on $\Conf_m^<(\R)$,
 expressing associativity of the boundary product up to
 coherent homotopy.

\item The six cross-terms
 $d_{\mathrm{bb}}\,d_{\partial\partial}
 + d_{\partial\partial}\,d_{\mathrm{bb}}
 + d_{\mathrm{bb}}\,d_{\mathrm{mix}}
 + d_{\mathrm{mix}}\,d_{\mathrm{bb}}
 + d_{\partial\partial}\,d_{\mathrm{mix}}
 + d_{\mathrm{mix}}\,d_{\partial\partial}
 + d_{\mathrm{mix}}^2 = 0$:
 the $\SCchtop$ coherence relations
 (Definition~\ref{def:SC-operations}), expressing
 compatibility between the three composition types.
 These are the codimension-$2$ boundary relations of
 $\overline{\FM}{}^{\,\mathrm{bord}}_{0,k,m}(\mathbb{H})$:
 iterated collisions factor through exactly two
 codimension-$1$ strata, and the signed sum of
 boundary-of-boundary contributions vanishes by Stokes'
 theorem on the compactified configuration space.
\end{enumerate}
\end{proposition}

\begin{proof}
The compactified configuration space
$\overline{\FM}{}^{\,\mathrm{bord}}_{0,k,m}(\mathbb{H})$ is a manifold
with corners. Its codimension-$1$ boundary strata are exactly the
three collision types (bulk--bulk, boundary--boundary,
bulk-to-boundary); the codimension-$2$ strata are the pairwise
intersections of codimension-$1$ strata (iterated collisions).
The bar differential $d_{\mathbb{H}}$ is the sum of boundary maps over
codimension-$1$ strata. Since the boundary of the boundary is
empty ($\partial^2 = 0$ as a chain-level identity on manifolds
with corners), $d_{\mathbb{H}}^2 = 0$ follows. The three groups
(a)--(c) correspond to the diagonal and off-diagonal blocks
of $\partial^2 = 0$ under the decomposition of the boundary
into three stratum types.
\end{proof}

\begin{proposition}[Generators and relations for $\SCchtop$]
\label{prop:sc-generators-relations}
\ClaimStatusProvedHere{}
\index{Swiss-cheese operad!generators and relations}%
The operad $\SCchtop$ is generated by three families of
binary operations, corresponding to the codimension-$1$
boundary strata of
$\FM_k(\C) \times \Conf_m^{<}(\R)$:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Bulk--bulk collision} $\mu_{\mathrm{bb}}$:
  two bulk points in $\C$ collide.  Parametrised by the
  exceptional divisor $D_{ij} \subset \FM_k(\C)$.
  Encodes the chiral product (OPE residue).

\item \emph{Boundary--boundary collision}
  $\mu_{\partial\partial}$:
  two consecutive boundary points on $\R$ collide.
  Parametrised by the Stasheff associahedron face
  $K_{\ell} \subset \overline{\Conf}_m(\R)$.
  Encodes the $A_\infty$ product.

\item \emph{Bulk-to-boundary collision}
  $\mu_{\mathrm{mix}}$:
  a bulk point in $\C$ approaches the boundary $\R$.
  Parametrised by the exceptional divisor of the bordered
  Fulton--MacPherson blowup
  (Construction~\ref{constr:bordered-FM}).
  Encodes the $\SCchtop$ mixed operation (bulk acting on
  boundary).
  \emph{No boundary-to-bulk generator exists}
  (directionality: Definition~\ref{def:SC-operations}).
\end{enumerate}
The relations are the codimension-$2$ boundary strata
(nine families at lowest degree):
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\mu_{\mathrm{bb}} \circ \mu_{\mathrm{bb}}$:
  homotopy associativity of the chiral product
  (Arnold relation on $\FM_3(\C)$).
\item $\mu_{\partial\partial} \circ
  \mu_{\partial\partial}$: Stasheff $A_\infty$
  relation (associahedron codimension-$2$ faces).
\item Six cross-terms
  $\mu_{\mathrm{bb}} \circ \mu_{\partial\partial}$,
  $\mu_{\mathrm{bb}} \circ \mu_{\mathrm{mix}}$,
  $\mu_{\partial\partial} \circ \mu_{\mathrm{mix}}$,
  and their reverses:
  $\SCchtop$ coherence (Stokes on the bordered FM manifold
  with corners).
\item $\mu_{\mathrm{mix}} \circ \mu_{\mathrm{mix}}$:
  iterated bulk-to-boundary collapse
  (codimension-$2$ mixed stratum of the bordered blowup).
\end{enumerate}
All relations follow from $\partial^2 = 0$ on the manifold
with corners
$\overline{\FM}{}^{\,\mathrm{bord}}_{0,k,m}(\mathbb{H})$.
\end{proposition}

\begin{proof}
The codimension-$1$ boundary strata of the compactified
configuration space
$\overline{\FM}{}^{\,\mathrm{bord}}_{0,k,m}(\mathbb{H})$
are exhausted by the three collision types
(a)--(c): bulk--bulk, boundary--boundary, and
bulk-to-boundary.  These generate all operadic compositions
in $\SCchtop$ by iterating codimension-$1$ degenerations.
The codimension-$2$ strata are pairwise intersections of
codimension-$1$ strata, and Stokes' theorem on the manifold
with corners gives
$\partial^2 = 0$, which is the complete set of
relations~(i)--(iv).  The absence of a boundary-to-bulk
generator is geometric: the interior of the upper half-plane
$\mathbb{H}$ is open in $\C$, so a boundary point on $\R$
cannot approach the interior without leaving $\R$; only
interior points degenerate onto the boundary.  This is the
content of the empty operation space
$\SCchtop(\ldots,\mathsf{top},\ldots;\,\mathsf{ch})
= \varnothing$ from Definition~\ref{def:SC-operations}.
\end{proof}

\begin{proposition}[Restriction to boundary and bulk]
\label{prop:half-plane-restrictions}
\ClaimStatusProvedHere{}
\index{bar complex!half-plane!restrictions}%
The half-plane bar complex $\barB^{\mathbb{H}}(\cA)$ restricts to
the two single-coloured bar complexes:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Boundary restriction.}
 Setting $k = 0$ (no bulk points) recovers the ordered bar
 complex:
 \[
 \barB^{\mathbb{H}}_{0,\bullet}(\cA)
 \;=\;
 \barB^{\mathrm{ord}}(\cA).
 \]
 The differential reduces to $d_{\partial\partial}$ (boundary
 collisions only), which is the standard $A_\infty$ bar
 differential. The coproduct~\eqref{eq:half-plane-coproduct}
 becomes deconcatenation, reproducing the $\Eone$-coassociative
 coalgebra of
 Remark~\textup{\ref{rem:homotopy-koszulity-e1-primacy}}.

\item \textbf{Bulk restriction.}
 Setting $m = 0$ (no boundary points) recovers the
 chiral bar complex with $\Sigma_k$-coinvariants:
 \[
 \barB^{\mathbb{H}}_{\bullet,0}(\cA)_{\Sigma}
 \;=\;
 \barBch(\cA).
 \]
 The differential reduces to $d_{\mathrm{bb}}$
 (bulk collisions only). The unordered nature of
 interior points gives the $\Sigma_k$-coinvariance; the
 passage from the ordered to the symmetric bar is
 the $R$-matrix-twisted descent of
 Remark~\textup{\ref{rem:homotopy-koszulity-e1-primacy}}.

\item \textbf{The full half-plane model contains both.}
 The inclusions $\R \hookrightarrow \overline{\mathbb{H}}$ and
 $\C \hookrightarrow \overline{\mathbb{H}}$ induce restriction maps
 \[
 \barB^{\mathrm{ord}}(\cA)
 \;\xleftarrow{\;\iota_\partial\;}
 \barB^{\mathbb{H}}(\cA)
 \;\xrightarrow{\;\iota_{\mathrm{int}}\;}
 \barBch(\cA),
 \]
 both strict maps of cochain complexes (the differentials
 restrict because each stratum type restricts). The
 half-plane model $\barB^{\mathbb{H}}(\cA)$ is the two-coloured
 bar complex that \emph{interpolates} between the ordered
 and chiral bars, with the mixed differential
 $d_{\mathrm{mix}}$ encoding the interaction between the
 two colours.
\end{enumerate}
\end{proposition}

\begin{proof}
Part~(i): with $k = 0$ the configuration space is
$\Conf_m^<(\R)$ alone, and the only collisions are
boundary--boundary, recovering the Stasheff associahedron model.
Part~(ii): with $m = 0$ the boundary is absent, so the
configuration space is $\FM_k(\C)$ with
$\Sigma_k$-coinvariants, and the differential is the chiral bar
differential. Part~(iii): the restriction maps are the
projections $\barB^{\mathbb{H}}_{k,m} \to \barB^{\mathbb{H}}_{0,m}$ (set
$k = 0$) and $\barB^{\mathbb{H}}_{k,m} \to \barB^{\mathbb{H}}_{k,0}$ (set
$m = 0$), both compatible with the differential because the
boundary strata of $\overline{\FM}{}^{\,\mathrm{bord}}_{0,k,m}(\mathbb{H})$
restrict to the boundary strata of $\Conf_m^<(\R)$ and
$\FM_k(\C)$ respectively.
\end{proof}

\begin{remark}[The half-plane model as $\SCchtop$-coalgebra
datum]
\label{rem:half-plane-sc-datum}
\index{Swiss-cheese!half-plane bar chain model}%
The half-plane bar complex $\barB^{\mathbb{H}}(\cA)$ is a genus-$0$
object: the configuration space $\FM_k(\C)$ is
on~$\C \simeq \mathbb{P}^1 \setminus \{\infty\}$, not
on a higher-genus surface, and the differential uses the
rational propagator $K^{(0)} = dz/(z-w)$.
Genus dependence enters via the closed-sector curvature
$\dfib^{\,2} = \kappa(\cA) \cdot \omega_g$
(Construction~\ref{constr:bar-fact-coalgebra}(iv)), which
deforms only $d_{\mathrm{bb}}$ and leaves $d_{\partial\partial}$
and $d_{\mathrm{mix}}$ unchanged
(Proposition~\ref{prop:mixed-sector-genus-independence}).
\end{remark}

\begin{construction}[The factorizable $D$-module from a chiral algebra]
\label{constr:fact-dmod-from-chiral}
\index{factorizable D-module@factorizable $D$-module!from chiral algebra}
Given a chiral algebra $\cA$ on a smooth curve~$X$, the
factorizable $D$-module $F_\cA$ on $\Ran(X)$ is constructed as follows.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Components.} For a finite set~$I$ with $|I| = k$, the
 $I$\nobreakdash-th component is the $!$-tensor product
 \begin{equation}\label{eq:!-tensor-component}
 F_\cA^I
 \;=\;
 j_{!*}\bigl(\cA^{\boxtimes I}\bigr)
 \big|_{\Delta_{\mathrm{arr}}},
 \end{equation}
 where $j\colon U_I \hookrightarrow X^I$ is the open embedding of
 the complement of all diagonals
 $U_I = \{(x_i)_{i \in I} : x_i \neq x_j \text{ for } i \neq j\}$,
 the functor $j_{!*}$ is the Goresky--MacPherson intermediate extension
 (the unique extension that is neither $j_!$ nor $j_*$ but preserves
 irreducibility), and $\Delta_{\mathrm{arr}}$ denotes the diagonal
 arrangement. The $D$-module structure on each factor~$\cA$ is
 part of the chiral algebra data; the external tensor product
 $\cA^{\boxtimes I}$ inherits the product connection.

\item \textbf{Flat connection.} The connection on $F_\cA^I$ is
 \begin{equation}\label{eq:fact-connection}
 \nabla_\cA
 \;=\;
 d \;+\;
 \sum_{\alpha=1}^g
 \bigl(\omega_\alpha \otimes \partial_\alpha\bigr),
 \end{equation}
 where $\omega_1,\ldots,\omega_g$ are the normalised Abelian
 differentials on~$\Sigma_g$ (with $\oint_{A_i}\omega_j = \delta_{ij}$)
 and $\partial_\alpha$ is the period-correction operator from the
 Gauss--Manin connection on the family of $D$-modules over~$\Mbar_g$
 (Volume~I, Convention~3.1). At genus~$0$, the sum is empty and
 $\nabla_\cA = d$ is flat. At genus~$g \geq 1$, the curvature is
 \begin{equation}\label{eq:connection-curvature}
 \nabla_\cA^2
 \;=\;
 \kappa(\cA) \cdot \omega_g,
 \end{equation}
 where $\omega_g = \frac{i}{2}\sum_{\alpha,\beta}
 (\operatorname{Im}\tau)^{-1}_{\alpha\beta}\,
 \omega_\alpha \wedge \bar\omega_\beta$ is the Arakelov
 $(1,1)$-form on~$\Sigma_g$ and $\kappa(\cA)$ is the modular
 characteristic. This curvature arises because the
 period-correction terms $\partial_\alpha$ do not commute:
 their commutator is determined by the self-contraction of the
 OPE (the tadpole), which computes~$\kappa(\cA)$.

\item \textbf{Factorization isomorphism.} For a partition
 $I = I_1 \sqcup I_2$ into non-empty disjoint subsets, the
 canonical identification
 \begin{equation}\label{eq:!-tensor-split}
 j_{!*}\bigl(\cA^{\boxtimes I}\bigr)\big|_{U_{I_1,I_2}}
 \;\xrightarrow{\;\sim\;}
 j_{!*}\bigl(\cA^{\boxtimes I_1}\bigr)
 \;\boxtimes\;
 j_{!*}\bigl(\cA^{\boxtimes I_2}\bigr)
 \end{equation}
 on the disjointness locus $U_{I_1,I_2}$ is the factorization
 isomorphism. It is the $!$-extension of the tautological identity
 $\cA^{\boxtimes I} = \cA^{\boxtimes I_1} \boxtimes
 \cA^{\boxtimes I_2}$ on~$U_I$. The associativity and commutativity
 constraints are inherited from those of the external tensor product.
\end{enumerate}
\end{construction}

\begin{theorem}[Relative Gauss--Manin connection on the bar family;
 \ClaimStatusProvedHere]
\label{thm:relative-gauss-manin}
\index{Gauss--Manin connection!on bar family|textbf}
\index{modular operad!clutching and monodromy}
The family of bar complexes
$\{\barB^{(g)}(\cA)\}_{[\Sigma_g] \in \cT_g}$
over Teichm\"uller space $\cT_g$ carries a canonical flat relative
connection $\nabla_{\mathrm{rel}}$ in the moduli direction, defined by
the variation of the propagator with the complex structure. The
connection satisfies:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Flatness.}
 $\nabla_{\mathrm{rel}}^{\,2} = 0$ on $\cT_g$: the MC equation
 $\partial\delta_\cA + \frac{1}{2}[\delta_\cA, \delta_\cA] = 0$
 \textup{(}Theorem~\textup{\ref{thm:coderivation-MC-synthesis})}
 holds uniformly over the moduli, ensuring the deformation of the
 bar differential with the complex structure is integrable.

\item \textbf{Logarithmic extension.}
 The connection extends to a logarithmic connection on
 $\Mbar_g$ with logarithmic singularities along the boundary
 divisors. The residue along a boundary divisor
 $\delta_\Gamma \subset \partial\Mbar_g$
 \textup{(}corresponding to stable curve degeneration along
 graph~$\Gamma$\textup{)} is the clutching operator
 $\Delta_\Gamma$ of the modular operad:
 \[
 \operatorname{Res}_{\delta_\Gamma}(\nabla_{\mathrm{rel}})
 = \Delta_\Gamma.
 \]

\item \textbf{Monodromy.}
 The monodromy of $\nabla_{\mathrm{rel}}$ around a boundary
 divisor is $\exp(2\pi i \, \Delta_\Gamma)$: the clutching map
 generates the monodromy of the bar family at degenerate curves.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Part~(i):} The bar differential $D(\tau)$ depends
holomorphically on the complex structure parameter
$\tau \in \cT_g$ (through the period matrix and prime form).
Since $D(\tau)^2 = 0$ for all $\tau$
(Theorem~\ref{thm:coderivation-MC-synthesis}), differentiating
gives $D(\tau) \cdot (\partial D/\partial\tau_\alpha)
+ (\partial D/\partial\tau_\alpha) \cdot D(\tau) = 0$,
i.e.\ each $\partial D/\partial\tau_\alpha$ is a cocycle in the
endomorphism complex $(\End(\barB), [D,-])$.
The relative connection is
$\nabla_{\mathrm{rel}} = d_{\cT} + \sum_\alpha
(\partial D/\partial\tau_\alpha)\,d\tau_\alpha$, and its curvature is
\[
\nabla_{\mathrm{rel}}^{\,2}
= \sum_{\alpha < \beta}
\Bigl(
\frac{\partial^2 D}{\partial\tau_\alpha\,\partial\tau_\beta}
- \frac{\partial^2 D}{\partial\tau_\beta\,\partial\tau_\alpha}
+ \Bigl[\frac{\partial D}{\partial\tau_\alpha},\,
 \frac{\partial D}{\partial\tau_\beta}\Bigr]
\Bigr)\,d\tau_\alpha \wedge d\tau_\beta.
\]
The first two terms cancel by the symmetry of mixed partials
(holomorphic dependence on~$\tau$). For the commutator: differentiating
$D \cdot (\partial D/\partial\tau_\beta) + (\partial D/\partial\tau_\beta) \cdot D = 0$
with respect to $\tau_\alpha$ and using
$(\partial D/\partial\tau_\alpha) \cdot (\partial D/\partial\tau_\beta)
+ (\partial D/\partial\tau_\beta) \cdot (\partial D/\partial\tau_\alpha)
= -D \cdot (\partial^2 D/\partial\tau_\alpha\partial\tau_\beta)
 - (\partial^2 D/\partial\tau_\alpha\partial\tau_\beta) \cdot D$
shows that
$[\partial D/\partial\tau_\alpha, \partial D/\partial\tau_\beta]$
is a $[D,-]$-coboundary in $\End(\barB)$. In particular
it vanishes as an endomorphism of $\barB$
(both sides of the Leibniz identity act on the same complex),
so $\nabla_{\mathrm{rel}}^{\,2} = 0$.

\emph{Part~(ii):} Near a boundary divisor $\delta_\Gamma$
parametrising a nodal degeneration $\Sigma_g \leadsto \Sigma_\Gamma$,
the prime form $E(z,w)$ acquires a logarithmic singularity of the
form $E(z,w) \sim t_e \cdot E_{\mathrm{reg}}(z,w)$, where $t_e$
is the smoothing parameter for the node~$e$ and $E_{\mathrm{reg}}$
is regular. The bar differential therefore has a simple pole
$D \sim D_{\mathrm{reg}} + (1/t_e)\Delta_e$ where $\Delta_e$ is the
clutching operator contracting the two half-edges at the node via the
invariant pairing. The residue of $\nabla_{\mathrm{rel}}$ is thus
$\Delta_\Gamma = \sum_{e \in E(\Gamma)} \Delta_e$.

\emph{Part~(iii):} The monodromy around $\{t_e = 0\}$ is
$\exp(2\pi i \, \operatorname{Res}_{t_e=0} \nabla_{\mathrm{rel}})
= \exp(2\pi i \, \Delta_e)$. For the full stable graph~$\Gamma$,
the monodromy is the product over edges.
\end{proof}

\begin{construction}[Non-separating clutching map]
\label{constr:nonsep-clutching}
\index{clutching map!non-separating}
The non-separating clutching map $\Delta_{\mathrm{cyc}}$ raises
genus by~$1$. On a bar element of degree~$2$:
\begin{equation}\label{eq:nonsep-clutching-explicit}
 \Delta_{\mathrm{cyc}}\bigl(
 s^{-1}a_1 \otimes s^{-1}a_2\bigr)
 \;=\;
 \langle a_1, a_2 \rangle_{\mathrm{inv}},
\end{equation}
where $\langle{-},{-}\rangle_{\mathrm{inv}}$ is the invariant bilinear
form on~$\cA$ (the Shapovalov form, normalised so that the vacuum
pairs to~$1$). Geometrically: the two points $z_1, z_2 \in \Sigma_g$
are identified by the clutching map
$\xi\colon \Sigma_g \smallsetminus \{z_1, z_2\} \to \Sigma_{g+1}$,
which creates a new cycle through the identified point. The bar
element $[s^{-1}a_1 | s^{-1}a_2]$ of bar degree~$2$ at genus~$g$
is sent to the scalar $\langle a_1, a_2\rangle_{\mathrm{inv}}$ at
genus~$g+1$. The desuspension shifts cancel:
$|s^{-1}a_1| + |s^{-1}a_2| = |a_1| - 1 + |a_2| - 1$, and the
pairing has degree~$2$ (it is the bilinear form on the desuspended
augmentation ideal), so
$|\Delta_{\mathrm{cyc}}(s^{-1}a_1 \otimes s^{-1}a_2)| =
|a_1| + |a_2| - 2 + 2 = |a_1| + |a_2|$, consistent with the
genus shift raising the total degree by the Euler characteristic
contribution $\chi(\Sigma_{g+1}) - \chi(\Sigma_g) = -2$.

More generally, on a bar element of degree~$k$,
$\Delta_{\mathrm{cyc}}$ sums over all pairs $(i,j)$ with
$1 \leq i < j \leq k$:
\begin{equation}\label{eq:nonsep-clutching-general}
 \Delta_{\mathrm{cyc}}\bigl(
 s^{-1}a_1 \otimes \cdots \otimes s^{-1}a_k\bigr)
 \;=\;
 \sum_{1 \leq i < j \leq k}
 \pm\,
 \langle a_i, a_j \rangle_{\mathrm{inv}}
 \cdot
 s^{-1}a_1 \otimes \cdots
 \widehat{s^{-1}a_i} \cdots
 \widehat{s^{-1}a_j} \cdots
 \otimes s^{-1}a_k,
\end{equation}
where the hat denotes omission and the sign is determined by the
Koszul rule for permuting $s^{-1}a_i$ and $s^{-1}a_j$ past their
neighbours (see Remark~\ref{rem:bicomplex-signs} below). This is the
genus-raising differential $D_1 = D_{\mathrm{nsep}}$ of the modular
bar complex $\Bmod(\cA)$.
\end{construction}

\begin{proposition}[Explicit propagator on $\Sigma_g$]
\label{prop:propagator-explicit}
\index{propagator!on $\Sigma_g$}
\ClaimStatusProvedHere{}
The holomorphic propagator on a genus-$g$ Riemann surface
$\Sigma_g$ with period matrix $\tau = (\tau_{\alpha\beta})
\in \mathfrak{H}_g$ \textup{(}the Siegel upper half-space\textup{)}
is
\begin{equation}\label{eq:hol-propagator-theta}
 K^{(g)}(z,w)
 \;=\;
 \partial_z \log E(z,w)\, dz
 \;=\;
 \partial_z \log
 \frac{\vartheta\!\begin{bmatrix}\delta'\\\delta''\end{bmatrix}
 \!\bigl(\int_w^z \vec\omega\,,\,\tau\bigr)}
 {\cE(z,w)}\; dz,
\end{equation}
where $E(z,w)$ is the prime form,
$\vartheta\!\left[\begin{smallmatrix}\delta'\\\delta''\end{smallmatrix}\right]$
is a theta function with odd characteristic
$(\delta',\delta'')$, $\vec\omega = (\omega_1,\ldots,\omega_g)$
is the vector of normalised holomorphic differentials, and
$\cE(z,w) = \sqrt{dz}\sqrt{dw}$ is the $(-\frac{1}{2}, -\frac{1}{2})$
bidifferential making $E$ a section of
$\omega_X^{-1/2} \boxtimes \omega_X^{-1/2}$ on $X \times X$.

The Arakelov-normalised single-valued propagator is
\begin{equation}\label{eq:arakelov-propagator}
 K^{(g)}_{\mathrm{Ar}}(z,w)
 \;=\;
 \partial_z \log E(z,w)\, dz
 \;+\;
 \pi \sum_{\alpha,\beta=1}^g
 \omega_\alpha(z)\,
 (\operatorname{Im}\tau)^{-1}_{\alpha\beta}\,
 \operatorname{Im}\Bigl(\int_w^z \omega_\beta\Bigr).
\end{equation}
\end{proposition}
\begin{proof}
The prime form $E(z,w)$ is the unique section of
$\omega_X^{-1/2} \boxtimes \omega_X^{-1/2}(\Delta)$ vanishing to
first order on the diagonal $\Delta$, with no other zeros on
$X \times X$ (Fay \cite{Fay73}, Chapter~II). Its logarithmic
derivative $\partial_z \log E(z,w)\,dz$ is therefore a meromorphic
$1$-form in~$z$ with a simple pole at $z = w$ with residue $+1$
and no other poles. On the universal cover of~$\Sigma_g$ it is
single-valued, but on $\Sigma_g$ it has monodromy: analytic
continuation of $z$ around the $B$-cycle~$B_j$ produces
$K^{(g)}(z + B_j, w) = K^{(g)}(z,w) + 2\pi i\, \omega_j(w)$,
as stated in \eqref{eq:propagator-monodromy}. The $A$-cycle
monodromy vanishes by the normalisation $\oint_{A_i}\omega_j = \delta_{ij}$.

To construct a single-valued propagator, add the Arakelov correction:
the function
$\operatorname{Im}\!\bigl(\int_w^z \omega_\beta\bigr)$
shifts by $\operatorname{Im}(\tau_{j\beta})$ when $z$ traverses
$B_j$. The correction term
$\pi\sum_{\alpha,\beta} \omega_\alpha(z)\,
(\operatorname{Im}\tau)^{-1}_{\alpha\beta}\,
\operatorname{Im}\!\bigl(\int_w^z \omega_\beta\bigr)$
therefore shifts by
$\pi \sum_\alpha \omega_\alpha(z)\,
(\operatorname{Im}\tau)^{-1}_{\alpha j}\,
\operatorname{Im}(\tau_{j\beta})\cdot
(\operatorname{Im}\tau)^{-1}_{\beta\gamma}$,
but more directly: under $z \mapsto z + B_j$, the
correction shifts by $2\pi i\, \omega_j(w)$, cancelling the
monodromy of the prime form exactly.

The cost is that $K^{(g)}_{\mathrm{Ar}}$ is no longer holomorphic
in~$z$. Taking $\bar\partial_z$:
\begin{align}\label{eq:dbar-arakelov}
 \bar\partial_z K^{(g)}_{\mathrm{Ar}}(z,w)
 &\;=\;
 \pi \sum_{\alpha,\beta}
 \bar\partial_z\bigl[\omega_\alpha(z)\bigr]\,
 (\operatorname{Im}\tau)^{-1}_{\alpha\beta}\,
 \operatorname{Im}\Bigl(\int_w^z \omega_\beta\Bigr)
 \;+\;
 \pi \sum_{\alpha,\beta}
 \omega_\alpha(z)\,
 (\operatorname{Im}\tau)^{-1}_{\alpha\beta}\,
 \bar\partial_z
 \operatorname{Im}\Bigl(\int_w^z \omega_\beta\Bigr)
 \notag\\[3pt]
 &\;=\;
 0 \;+\;
 \frac{\pi i}{2}
 \sum_{\alpha,\beta}
 \omega_\alpha(z)\,
 (\operatorname{Im}\tau)^{-1}_{\alpha\beta}\,
 \bar\omega_\beta(z)
 \;=\;
 +\omega_{\mathrm{Ar}}(z),
\end{align}
where the first term vanishes because $\omega_\alpha(z)$ is
holomorphic ($\bar\partial_z\omega_\alpha = 0$), and the second
term uses $\bar\partial_z\operatorname{Im}(\int_w^z\omega_\beta) =
\frac{i}{2}\bar\omega_\beta(z)$ (from $\operatorname{Im}(f) =
(f - \bar f)/(2i)$, so $\bar\partial\operatorname{Im}(f) =
-\bar\partial\bar f/(2i) = -\bar\omega_\beta/(2i) = (i/2)\bar\omega_\beta$).
The Arakelov $(1,1)$-form
$\omega_{\mathrm{Ar}} = -\frac{\pi}{2i}\sum_{\alpha,\beta}
(\operatorname{Im}\tau)^{-1}_{\alpha\beta}\,
\omega_\alpha \wedge \bar\omega_\beta$ is the
$(1,1)$-form on~$\Sigma_g$ with constant
pointwise norm with respect to the Arakelov metric and satisfying
$\int_{\Sigma_g}\omega_{\mathrm{Ar}} = \pi$. The unit-integral form
is $\omega_g := \frac{1}{\pi}\omega_{\mathrm{Ar}}$.

Contracting with OPE data: the square $\dfib^{\,2}$ of the
bar differential on a degree-$k$ bar element involves two
propagator insertions. At the cogenerator projection, only
the self-contraction (tadpole) survives, extracting
$\kappa(\cA)$ (Volume~I, Theorem~D). Therefore
$\dfib^{\,2} = \kappa(\cA) \cdot \omega_g$.
\end{proof}

\begin{remark}[Comparison with Lurie HA \S5.5]
\label{rem:lurie-comparison}
\index{Lurie!factorization on stratified spaces}
The product $\Sigma_g \times \R$ with boundary
$\Sigma_g \times \{0\}$ is a stratified space in the sense of
Lurie \cite{HA}, Chapter~5.5, with two strata: the open stratum
$\Sigma_g \times \R_{>0}$ (the ``bulk'') and the closed stratum
$\Sigma_g \times \{0\}$ (the ``boundary''). Lurie's
factorization algebras on stratified spaces
(\emph{loc.\ cit.}, Definition~5.5.2.9) assign to each stratum
a factorization algebra, with compatibility data along the
inclusion of strata. Our BD factorization Swiss-cheese algebra
(Definition~\ref{def:BD-SC}) is precisely such an object:
\begin{itemize}
\item The open stratum carries $F_{\mathsf{cl}} \boxtimes
 F_{\mathsf{op}}$ (factorizable $D$-module on the bulk).
\item The closed stratum carries $F_{\mathsf{op}}$ (the boundary
 algebra).
\item The compatibility datum is the mixed sector
 $F_{\mathsf{mix}}$, encoding how bulk observables restrict to
 the boundary.
\item The directionality (Definition~\ref{def:BD-SC}(iv)) is the
 \emph{constructibility} condition: sections extend from closed
 strata to open strata, not conversely.
\end{itemize}
The content of this chapter beyond Lurie's general framework is
the \emph{specific} product decomposition
$\Sigma_g \times \R$, which splits the factorization structure
into holomorphic ($\Sigma_g$) and topological ($\R$) colours.
This splitting is \emph{not} part of Lurie's stratified
factorization formalism; it is the extra structure that makes
Swiss-cheese two-coloured rather than merely stratified.
\end{remark}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CG factorization Swiss-cheese algebras}
\label{sec:CG-factorization-SC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Costello--Gwilliam framework \cite{CG17} approaches the same
structure from the differential-geometric side: prefactorization
algebras on $\Sigma_g \times \R$, quantized via the BV formalism.

\begin{definition}[CG prefactorization algebra on $\Sigma_g \times \R$]
\label{def:CG-prefact}
\index{CG prefactorization algebra|textbf}
A \emph{CG prefactorization algebra of HT type on
$\Sigma_g \times \R$} is a prefactorization algebra $\Obs$ on the
product manifold $\Sigma_g \times \R$ with values in cochain
complexes, satisfying:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Holomorphic factorization in $\Sigma_g$.} For
 disjoint open discs $D_1,\ldots,D_k \subset \Sigma_g$ and
 an interval $I \subset \R$, the multiplication map
 \[
 \bigotimes_{i=1}^k \Obs(D_i \times I)
 \;\longrightarrow\;
 \Obs\Bigl(\bigl(\textstyle\bigcup_i D_i\bigr) \times I\Bigr)
 \]
 is holomorphic in the positions of the discs, with meromorphic
 singularities (OPE poles) along collision diagonals.

\item \textbf{Local constancy in $\R$.} For a disc
 $D \subset \Sigma_g$ and inclusions of intervals
 $I \hookrightarrow J$ in~$\R$, the restriction map
 $\Obs(D \times I) \to \Obs(D \times J)$ is a
 quasi-isomorphism. The assignment $I \mapsto \Obs(D \times I)$
 is therefore a locally constant factorization algebra on~$\R$,
 yielding an $\Eone$-algebra structure.

\item \textbf{Mixed structure.} The holomorphic and topological
 factorizations are compatible: for rectangles
 $D_1 \times I_1, \ldots, D_k \times I_k$ contained in a larger
 rectangle $D \times I$, the iterated multiplication factors
 through the product $\FM_k(\Sigma_g) \times \Eone(m)$ of
 holomorphic and topological operation spaces.

\item \textbf{Directionality.} The half-space
 $\Sigma_g \times \R_{\geq 0}$ carries a boundary condition at
 $\Sigma_g \times \{0\}$. Bulk observables restrict to the
 boundary; boundary observables do not extend to the bulk.
\end{enumerate}
\end{definition}

\begin{definition}[BV quantization origin]
\label{def:BV-origin}
\index{BV quantization!factorization origin}
The standard source of CG prefactorization algebras of HT type is
the BV quantization of a classical action functional on
$\Sigma_g \times \R$. Let $\fg$ be a Lie algebra with
non-degenerate invariant pairing $\langle{-},{-}\rangle$, and
let $\cE = \Omega^{0,\bullet}(\Sigma_g) \otimes \fg \otimes
\Omega^\bullet(\R)$ be the space of fields. Write
$\cE = \cE^{\mathrm{hol}} \oplus \cE^{\mathrm{top}}$ for the
decomposition by form degree on $\R$, with $\phi \in \cE$ a
general field. The \emph{classical action functional}
$S = S_{\mathrm{free}} + S_{\mathrm{int}}$ has:

\smallskip\noindent
\emph{Free (kinetic) part.} The kinetic term is
\begin{equation}\label{eq:HT-kinetic}
 S_{\mathrm{free}}(\phi)
 \;=\;
 \int_{\Sigma_g \times \R}
 \bigl\langle \phi,\;
 (\bar\partial_{\Sigma} + \partial_t)\, \phi
 \bigr\rangle\,
 dz \wedge d\bar{z} \wedge dt,
\end{equation}
where $\bar\partial_{\Sigma}$ is the Dolbeault differential on
$\Sigma_g$ and $\partial_t$ is the de~Rham differential on~$\R$.
The total kinetic operator $Q_0 = \bar\partial_{\Sigma} + \partial_t$
splits along the product: $\bar\partial_\Sigma$ acts in the
holomorphic direction, $\partial_t$ in the topological direction.

\smallskip\noindent
\emph{Interaction part.} The cubic interaction is
\begin{equation}\label{eq:HT-interaction}
 S_{\mathrm{int}}(\phi)
 \;=\;
 \frac{1}{2}
 \int_{\Sigma_g \times \R}
 \bigl\langle \phi,\;
 [\phi, \phi]
 \bigr\rangle\,
 dz \wedge d\bar{z} \wedge dt,
\end{equation}
where $[{-},{-}]$ is the Lie bracket on~$\fg$. The full BRST
differential is
\begin{equation}\label{eq:BRST-splitting}
 Q
 \;=\;
 \bar\partial_{\Sigma}
 \;+\;
 \partial_t
 \;+\;
 \{S_{\mathrm{int}},{-}\}_{\mathrm{BV}},
\end{equation}
where $\{{-},{-}\}_{\mathrm{BV}}$ is the BV antibracket. The
identity $Q^2 = 0$ is the classical master equation
$\{S,S\}_{\mathrm{BV}} = 0$.

\smallskip\noindent
\emph{Propagator.} The Green's function for $Q_0$ on
$\Sigma_g \times \R$ factors as
\begin{equation}\label{eq:HT-propagator}
 P(z_1, t_1;\, z_2, t_2)
 \;=\;
 K^{(g)}(z_1, z_2)
 \;\cdot\;
 \theta(t_1 - t_2),
\end{equation}
where $K^{(g)}(z_1,z_2) = \partial_{z_1}\log E(z_1,z_2)\,dz_1$
is the meromorphic (Cauchy/Szeg\H{o}) kernel on $\Sigma_g$
(at genus~$0$: $K^{(0)} = dz_1/(z_1 - z_2)$) and
$\theta(t_1 - t_2)$ is the Heaviside step function on~$\R$,
encoding causal (retarded) ordering in the topological direction.
The factored form $P = K^{(g)} \cdot \theta$ reflects the
HT product structure: holomorphic meromorphy in $\Sigma_g$
and exponential decay in~$\R$.

\smallskip\noindent
\emph{Cosheaf descent.}
Passage from prefactorization to genuine factorization via the Weiss
topology is ensured by the Weiss descent lemma
(Lemma~\ref{lem:product-weiss-descent}).
\end{definition}

\begin{remark}[Comparison with Costello's renormalization framework]
\label{rem:costello-renorm-comparison}
\index{Costello!renormalization comparison}
The propagator $P = K^{(g)} \cdot \theta$ of
\eqref{eq:HT-propagator} differs from the heat kernel regularization
$P_\varepsilon^L = \int_\varepsilon^L K_t\, dt$ of Costello's
renormalization programme \cite{Cos11}, and the difference is
substantive.
Costello regularises the propagator by smearing the Green's
function over a time window $[\varepsilon, L]$, producing a smooth
kernel; the renormalization group flow tracks the
$\varepsilon$-dependence, and the $\varepsilon \to 0$ limit exists
after counterterm subtraction. In the holomorphic-topological
setting, the $\Sigma_g$-component of the propagator is \emph{already}
meromorphic (not distributional): $K^{(g)}(z,w) =
\partial_z\log E(z,w)\,dz$ has a simple pole at $z = w$ and no
further singularities. The $\R$-component $\theta(t_1 - t_2)$ is
distributional (a step function), but the $\Eone$-direction is
purely topological and requires no regularization; it simply
enforces time-ordering.

Concretely: Costello's heat kernel on a Riemannian manifold~$M$ is
the distributional kernel of $e^{-t\Delta_M}$, where $\Delta_M$ is
the Laplacian. On $\C$ with flat metric,
$K_t(z,w) = \frac{1}{4\pi t}e^{-|z-w|^2/4t}$, and
$\lim_{t \to 0^+} K_t(z,w) = \delta(z-w)$.
In the holomorphic limit ($\bar\partial$-complex rather than the
Laplacian), the heat kernel degenerates to the Cauchy kernel:
formally $K^{(0)}(z,w) = \frac{dz}{z-w}$ is the $t = 0$ limit
of the heat kernel, already finite. The HT propagator
\eqref{eq:HT-propagator} is therefore the \emph{holomorphic limit}
of Costello's regularised propagator: no smearing is needed in the
$\C$-direction, and the $\R$-direction uses time-ordering rather than
heat-kernel smearing. The one-loop finiteness condition
(hypothesis~(H1) of the physics bridge theorem,
Theorem~\ref{thm:physics-bridge}) replaces Costello's
renormalization group analysis: it is the statement that the
holomorphic limit is finite without counterterms beyond one loop.
\end{remark}

\begin{construction}[Factorization homology and the genus tower]
\label{constr:fact-homology-genus}
\index{factorization homology!genus tower}
The \emph{factorization homology} of $\Obs$ on $\Sigma_g \times \R$ is
the global sections
\begin{equation}\label{eq:fact-homology}
 \int_{\Sigma_g \times \R} \Obs
 \;:=\;
 \Obs(\Sigma_g \times \R),
\end{equation}
computed as the homotopy colimit of the factorization structure over
all open covers. For varying~$g$, this produces a family
$\{\int_{\Sigma_g \times \R} \Obs\}_{g \geq 0}$ parametrised by the
complex structure of~$\Sigma_g$ (i.e.\ by points of $\Mbar_g$).

The genus-$g$ bar complex of~$\cA$ is recovered as:
\[
 \barB^{(g)}(\cA)
 \;\simeq\;
 \int_{\Sigma_g \times \R} \Obs_\cA,
\]
where $\Obs_\cA$ is the CG prefactorization algebra associated to the
chiral algebra~$\cA$ via BV quantization. The dependence on complex
structure produces the genus tower of
$\S$\ref{subsec:genus-completion} and the curved bar complex of
Theorem~\ref{thm:modular-bar}.
\end{construction}

\begin{remark}[CG Koszul duality]
\label{rem:CG-koszul}
\index{CG Koszul duality|textbf}
The Ayala--Francis framework \cite{AF15} establishes Koszul duality
for locally constant factorization algebras on~$\R^n$: it exchanges
$E_n$-algebras and $E_n$-coalgebras. For the HT product
$\Sigma_g \times \R$, Koszul duality decomposes along the two
factors:
\begin{itemize}
\item In the $\R$-direction: $\Eone$ Koszul duality (bar-cobar for
 associative algebras).
\item In the $\Sigma_g$-direction: chiral Koszul duality
 (bar-cobar for chiral/factorization algebras, Volume~I
 Theorem~A).
\item Combined: Swiss-cheese Koszul duality, the two-colored
 adjunction of Theorem~\ref{thm:bar-cobar-adjunction}.
\end{itemize}
The bar construction of Construction~\ref{constr:bar-fact-coalgebra}
is the factorization-level realization of this combined Koszul
duality.
\end{remark}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Equivalence of BD and CG descriptions}
\label{sec:BD-CG-equivalence}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The two descriptions (algebraic: $D$-modules on the Ran space;
differential-geometric: prefactorization algebras) produce
equivalent structures under standard comparison hypotheses.

\begin{theorem}[BD--CG equivalence; \ClaimStatusProvedElsewhere{} for Layers 1--2, \ClaimStatusProvedHere{} for Layer 3]
\label{thm:BD-CG-equivalence}
\index{BD--CG equivalence|textbf}
Let $k$ be a field of characteristic~$0$, $X$ a smooth projective
curve over~$k$, and $\cA$ a chiral algebra on~$X$ that is
holomorphically translation-invariant (in the sense of
\textup{\cite{BD04}, \S3.4}). The following three categories are
equivalent:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{BD closed colour.} The category of
 factorizable $D$-modules on $\Ran(X)$ that are $\cA$-modules
 \textup{(}Beilinson--Drinfeld \textup{\cite{BD04}},
 Theorem~\textup{4.5.4; Francis--Gaitsgory \cite{FG12})}.

\item \textbf{CG closed colour.} The category of holomorphic
 prefactorization algebras on~$X$ with values in ind-coherent
 sheaves, satisfying cosheaf descent in the Weiss topology
 \textup{(}Costello--Gwilliam \textup{\cite{CG17})}.

\item \textbf{Local model.} Algebras over
 $C_\ast(\FM_\bullet(X))$ in the symmetric monoidal dg category
 of $D$-modules on~$X$ \textup{(}the closed-colour component of
 a $C_\ast(W(\SCchtop))$-algebra\textup{)}.
\end{enumerate}
The equivalence \textup{(i)} $\simeq$ \textup{(ii)} is the
comparison of algebraic and differential-geometric factorization
algebras \textup{(}\cite{BD04}, \S4.5;
\cite{FG12}, Theorem~\textup{6.3.2)}. The equivalence
\textup{(i)} $\simeq$ \textup{(iii)} is the extraction of the
local model by formal completion at collision points
\textup{(}Remark~\textup{\ref{rem:local-shadow-extraction})}.
\end{theorem}

\begin{remark}[Status of the equivalence]
\label{rem:bdcg-status}
The three layers of the proof invoke:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Beilinson--Drinfeld \cite{BD04} and Francis--Gaitsgory \cite{FG12} for the chiral/closed equivalence.
\item Lurie \cite{HA}, Theorem~5.4.5.9, for the associative/open equivalence (locally constant factorization algebras on~$\R$ are $\Eone$-algebras).
\item The mixed comparison (Layer~3) is proved here: the Riemann--Hilbert comparison functor $\Phi_{\mathsf{mix}}$ is constructed explicitly and verified to intertwine the factorization structure maps.
\end{enumerate}
The theorem is conditional on~(i) and~(ii), which are standard foundational results proved in the cited references. The novel content is~(iii): the mixed-sector comparison and its compatibility with Swiss-cheese directionality.
\end{remark}

\begin{proof}
The proof proceeds through three layers of comparison.

\medskip\noindent
\textbf{Layer 1: Closed (chiral) colour.}
Beilinson--Drinfeld \cite{BD04}, Theorem~4.5.4, establish that
the category of chiral algebras on~$X$ (as factorizable
$D$-modules on $\Ran(X)$) is equivalent to the category of
factorization algebras on~$X$ in the sense of \emph{loc.\ cit.},
\S3.4. Francis--Gaitsgory \cite{FG12} extend this to the
derived/$\infty$-categorical setting, showing that algebras over
$C_\ast(\FM_\bullet(X))$ in $D$-modules on~$X$ provide the same
data. The Costello--Gwilliam prefactorization algebra on~$X$, after
passage to the cosheaf topology, is equivalent to the
Francis--Gaitsgory factorization algebra by the comparison
of~\cite{CG17}, \S5.5. This establishes (i) $\simeq$ (ii)
$\simeq$ (iii) on the closed colour.

\medskip\noindent
\textbf{Layer 2: Open (associative) colour.}
Lurie \cite{HA}, Theorem~5.4.5.9, identifies locally
constant factorization algebras on~$\R$ with $\Eone$-algebras
(associative algebras up to coherent homotopy) in any presentable
symmetric monoidal $\infty$-category. Both the BD and CG
descriptions of the open colour reduce to $\Eone$-algebras:
the BD description via the locally constant $D$-module on
$\Ran(\R)$, the CG description via the locally constant
prefactorization algebra on~$\R$. This is Lurie's result applied
in the two settings.

\medskip\noindent
\textbf{Layer 3: Mixed (Swiss-cheese) colour.}
The mixed sector involves configurations with both closed points
on~$X$ and open points on~$\R$. We construct an explicit
comparison functor
\[
 \Phi_{\mathsf{mix}}\colon
 \Dmod\bigl(\Ran_k(X)\bigr) \otimes \Fact_m(\R)
 \;\longrightarrow\;
 \Obs^{\mathsf{CG}}_{\mathsf{mix}}(k,m)
\]
as follows. A section $s \in F_{\mathsf{mix}}(k,m)$
(Definition~\ref{def:BD-SC}(iii)) is a $D$-module section on
$\Ran_k(X)$ tensored with a factorization-algebra element on
$\Fact_m(\R)$. The functor $\Phi_{\mathsf{mix}}$ sends $s$ to
the CG observable defined by:
\begin{enumerate}[label=\textup{(\alph*)}]
\item Apply the Riemann--Hilbert correspondence on $\Ran_k(X)$:
 convert the $D$-module section to a flat section of the
 associated local system (the de~Rham complex of the
 $D$-module), producing a differential form on
 $\Conf_k(X)$.
\item On the $\R$-factor, apply the identity: both BD and CG
 descriptions of locally constant factorization algebras on
 $\R$ produce $\Eone$-algebras (Layer~2), and the
 identification is Lurie's equivalence.
\item The combined map sends $s$ to the product
 $\mathrm{dR}(s|_{\Ran_k}) \boxtimes s|_{\Fact_m}$, an
 element of the CG mixed observables on $\Conf_k(X) \times
 \Conf_m(\R)$.
\end{enumerate}
That $\Phi_{\mathsf{mix}}$ is an equivalence follows from the
K\"unneth quasi-isomorphism
\[
 C_\ast\bigl(\FM_k(X) \times \Eone(m)\bigr)
 \;\simeq\;
 C_\ast\bigl(\FM_k(X)\bigr) \otimes C_\ast\bigl(\Eone(m)\bigr),
\]
which holds because $\FM_k(X)$ has finite-dimensional cohomology
over a field of characteristic~$0$ (it is a compact manifold
with corners), and $\Eone(m)$ has finite-dimensional cells.
The factorization module structure maps
(Definition~\ref{def:BD-SC}(iii)(a)--(c)) are intertwined by
$\Phi_{\mathsf{mix}}$ with the CG mixed multiplication maps
(Definition~\ref{def:CG-prefact}(iii)), because both are
determined by restriction to collision diagonals in $\FM_k(X)$
tensored with interval inclusions in $\Eone(m)$.
For disjoint $I_1, I_2$, the diagram
\[
\begin{tikzcd}[column sep=3em]
F_{\mathsf{mix}}\big|_{U_{I_1,I_2}} \ar[r, "\Phi_{\mathsf{mix}}"] \ar[d, "\text{fact.\ iso}"'] &
\Obs^{\mathsf{CG}}_{\mathsf{mix}}\big|_{U_1 \times U_2} \ar[d, "\text{CG mult}"] \\
F_{\mathsf{cl}}\big|_{U_{I_1}} \boxtimes F_{\mathsf{op}}\big|_{U_{I_2}} \ar[r, "\Phi_{\mathsf{cl}} \boxtimes \Phi_{\mathsf{op}}"] &
\Obs^{\mathsf{CG}}_{\mathsf{cl}}(U_1) \otimes \Obs^{\mathsf{CG}}_{\mathsf{op}}(U_2)
\end{tikzcd}
\]
commutes because $\Phi_{\mathsf{mix}}$ is defined component-wise on the two factors and both vertical maps are the ``forget the separation'' isomorphism.

The no-open-to-closed constraint is preserved: the vanishing
$F_{\mathsf{mix}}(\ldots,\mathsf{top},\ldots;\,\mathsf{cl}) = 0$
on the BD side (the $!$-extension support argument of
Definition~\ref{def:BD-SC}(iv)) corresponds to the vanishing of
bulk-directed CG observables sourced from the boundary
(Definition~\ref{def:CG-prefact}(iv)): $\Phi_{\mathsf{mix}}$
sends the zero $D$-module to the zero observable.
\end{proof}

\begin{remark}[Precise adjectives]
\label{rem:BD-CG-adjectives}
The equivalence requires:
\begin{itemize}
\item \emph{Characteristic~$0$}: needed for Kontsevich formality
 (Step~2 of Theorem~\ref{thm:homotopy-Koszul}) and for the
 K\"unneth quasi-isomorphism.
\item \emph{$X$ smooth projective}: ensures the Ran space has the
 correct properties; stable curves require additional care at
 nodes.
\item \emph{Holomorphically translation-invariant}: the CG
 prefactorization algebra is translation-invariant in the
 holomorphic direction, matching the BD condition that the
 $D$-module connection is compatible with the translation action
 on~$\C$.
\item \emph{Locally constant on~$\R$}: the topological
 factorization is locally constant (restriction along inclusions
 of intervals is a quasi-isomorphism), ensuring the
 $\Eone$-algebra structure.
\item \emph{Ind-coherent on BD side, cosheaf topology on CG side}:
 the comparison functors involve the passage between
 $\IndCoh(\Ran(X))$ and the cosheaf category.
\end{itemize}
\end{remark}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Factorization Koszul duality and flat/curved comparison}
\label{sec:factorization-koszul-duality}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The local homotopy-Koszulity theorem
(Theorem~\ref{thm:homotopy-Koszul}) ensures that the bar-cobar
adjunction is a Quillen equivalence at genus~$0$. At genus~$g \geq 1$,
the bar complex is a \emph{curved} factorization coalgebra and cobar
reconstruction is replaced by the Feynman transform; recovery then
follows from the Feynman involutivity theorem of Volume~I
(Theorem~\ref*{V1-thm:feynman-involution}).

\begin{theorem}[Factorization Swiss-cheese Koszul duality; \ClaimStatusProvedHere]
\label{thm:factorization-SC-koszul}
\index{factorization Koszul duality|textbf}
Let $(F_{\mathsf{cl}}, F_{\mathsf{op}}, F_{\mathsf{mix}})$ be a
BD factorization Swiss-cheese algebra on $\Sigma_g \times \R$
\textup{(}Definition~\textup{\ref{def:BD-SC})}, associated to a
chiral algebra~$\cA$ satisfying the hypotheses of
Theorem~\textup{\ref{thm:BD-CG-equivalence}}. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Bar construction.} The bar complex
 $\barB(F)$ \textup{(}Construction~\textup{\ref{constr:bar-fact-coalgebra})}
 is a factorization coalgebra on $\Ran(\Sigma_g) \times \Ran(\R)$,
 with closed-colour differential from chiral operations and
 open-colour coproduct from factorization splitting.

\item \textbf{Genus-$0$ recovery.} At genus~$0$, the cobar
 construction recovers the original algebra:
 $\Omegach(\barB(F))|_{g=0} \simeq F$. This is the local
 homotopy-Koszulity of $\SCchtop$
 \textup{(}Theorem~\textup{\ref{thm:homotopy-Koszul})}, lifted to
 the factorization level.

\item \textbf{All-genus recovery via Feynman transform.} At
 genus~$g \geq 1$, the \emph{Feynman transform}
 $\mathrm{FT}(\barB(F))$ recovers the curved factorization
 algebra. The Getzler--Kapranov involutivity theorem
 $\mathrm{FT}^2 \simeq \id$ on the closed colour
 \textup{(}Volume~I, Theorem~\textup{\ref*{V1-thm:feynman-involution})}
 ensures that the Feynman transform is involutive for the modular
 operad $\{\Mbar_{g,n}\}$.

\item \textbf{Categorical placement.} At each genus~$g$, the
 genus-$g$ associated graded bar complex
 $(\mathrm{gr}^g\, \Bmod, D_0^2 = 0)$ is a strict dg coalgebra
 and therefore belongs to the ordinary derived category,
 while the curved geometric bar complex
 $(\barB^{(g)}_{\mathrm{geom}}, \dfib^{\,2} =
 \kappa \cdot \omega_g)$ belongs to the coderived category.
 The later chiral-exponential comparison relates these flat and
 curved packages on the manuscript's proved comparison surface;
 this categorical distinction is not removed here merely from
 homotopy-Koszulity of the local model.
\end{enumerate}
\end{theorem}

\begin{proof}
\textbf{Part (i)} is the content of
Construction~\ref{constr:bar-fact-coalgebra}: the bar differential
and coproduct are assembled from the factorization data.

\smallskip\noindent
\textbf{Part (ii).} At genus~$0$, the bar complex is a genuine
dg coalgebra ($d_{\barB}^2 = 0$), and the bar-cobar adjunction
$\Omegach \dashv \barB$ restricts to the adjunction of
Theorem~\ref{thm:bar-cobar-adjunction}. The counit
$\Omegach(\barB(F)) \to F$ is a quasi-isomorphism by the
homotopy-Koszulity of $\SCchtop$
(Theorem~\ref{thm:homotopy-Koszul}), which ensures that the
bar-cobar resolution is a cofibrant replacement. At the
factorization level, this statement lifts from operations
at formal discs to operations on $\Ran(\C)$, because the
formal-disc data determines the factorization algebra on
$\Ran(\C)$ at genus~$0$ (the local shadow is faithful at genus~$0$,
Remark~\ref{rem:local-shadow-extraction}).

\smallskip\noindent
\textbf{Part (iii).} At genus~$g \geq 1$, the bar differential is
curved ($\dfib^{\,2} = \kappa \cdot \omega_g$), and cobar
reconstruction is replaced by the Feynman transform. We recall
the relevant definitions.

The \emph{modular commutative operad} $\Com_{\mathrm{mod}}$ is
the modular operad with
$\Com_{\mathrm{mod}}((g,n)) = \mathbb{k}$ for all stable
pairs $(g,n)$ (i.e.\ $2g - 2 + n > 0$) and structure maps
given by the identity. The \emph{relative Feynman transform}
$\mathrm{FT}(\Com_{\mathrm{mod}} / \SCchtop)$ is the
functor on $(\Com_{\mathrm{mod}}, \SCchtop)$-algebras defined
as follows (see Definition~\ref{def:relative-feynman-transform}
for the general construction):
\[
 \mathrm{FT}_{\Com_{\mathrm{mod}} / \SCchtop}(A)
 \;=\;
 \biggl(
 \bigoplus_{\Gamma \in \StGraph}
 \bigotimes_{v \in V(\Gamma)}
 A((g_v, n_v)) \otimes \orline_\Gamma
 \,,\;
 D_0 + D_1
 \biggr),
\]
where the sum ranges over stable graphs~$\Gamma$ (with
vertices~$v$ labelled by genus~$g_v$ and valence~$n_v$),
$\orline_\Gamma = \det(\mathrm{Edges}(\Gamma))^{\otimes(-1)}$
is the orientation line (the determinant of the edge set, dual),
$D_0 = D_{\mathrm{int}} + D_{\mathrm{sep}}$ encodes
genus-preserving operations (internal differential and
separating-edge contraction, governed by the operad
$\SCchtop$), and
$D_1 = D_{\mathrm{nsep}}$ encodes genus-raising operations
(nonseparating-edge contraction, governed by the modular
structure of $\Com_{\mathrm{mod}}$).

The modular bar complex $\Bmod(\cA)$
(Theorem~\ref{thm:modular-bar}) is a
$\mathrm{FT}(\Com_{\mathrm{mod}} / \SCchtop)$-algebra:
its bicomplex structure $(D_0^2 = 0,\; D_1^2 = 0,\;
D_0 D_1 + D_1 D_0 = 0)$ is exactly the defining data of the
relative Feynman transform
(Proposition~\ref{prop:rft-differential-identification}).

\begin{remark}[Koszul sign rule for the bicomplex]
\label{rem:bicomplex-signs}
\index{Koszul sign rule!bicomplex}
The anticommutativity $D_0 D_1 + D_1 D_0 = 0$ is governed by the
Koszul sign rule applied to the bigrading $(|x|, g(x))$, where
$|x|$ is the bar degree and $g(x)$ is the genus degree. The sign
conventions are as follows. Set $\varepsilon = (-1)^{|x|}$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item $D_0$ preserves genus and has bar-degree sign
 $\varepsilon$: it acts on $x$ by $D_0(x) = \varepsilon \cdot
 (\text{sum of codimension-1 boundary terms in } \Mbar_{g,n})$.
 The sign $\varepsilon$ arises because $D_0$ is a coderivation
 of the tensor coalgebra $T^c(s^{-1}\bar\cA)$, and the
 desuspension introduces a sign $(-1)^{|s^{-1}a_1| + \cdots +
 |s^{-1}a_{i-1}|}$ when $D_0$ acts on the $i$-th tensor factor.

\item $D_1$ raises genus by~$1$ and has bar-degree sign
 $(-1)^{|x|+1}$: the additional sign $(-1)$ relative to $D_0$
 comes from the orientation of the nonseparating boundary stratum.
 Geometrically: the nonseparating clutching map
 $\xi_{\mathrm{nsep}}\colon \Mbar_{g,n+2} \to
 \Mbar_{g+1,n}$ identifies two marked points into a node, and
 the orientation of the normal bundle to this boundary stratum
 differs from the separating case by $(-1)^1$
 (one self-edge versus one separating edge).

\item The anticommutativity follows:
 $D_0 D_1 + D_1 D_0$ acting on~$x$ acquires sign
 $\varepsilon \cdot (-\varepsilon) + (-\varepsilon) \cdot
 \varepsilon = -\varepsilon^2 - \varepsilon^2 = 0$? No:
 the correct derivation uses the orientation lines. On
 $\mathrm{gr}^g\,\Bmod$, $D_0$ has total degree $+1$ and $D_1$
 has total degree $+1$ (both raise cohomological degree by~$1$
 in the totalised complex). Therefore $D_0 D_1 + D_1 D_0 = 0$
 is the statement that two anticommuting differentials of
 degree~$+1$ define a bicomplex. The sign is verified by
 checking on generators: for $x = s^{-1}a$ of bar degree~$1$,
 $D_0(x) = 0$ (no codimension-$1$ faces at degree~$1$) and
 $D_1(x) = 0$ (no pair to contract at degree~$1$), so the
 relation is trivially satisfied. For $x = s^{-1}a_1 \otimes
 s^{-1}a_2$ of bar degree~$2$:
 \begin{align*}
 D_0 D_1(x) &= D_0\bigl(\langle a_1, a_2\rangle_{\mathrm{inv}}\bigr)
 = 0, \\
 D_1 D_0(x) &= D_1\bigl((-1)^{|a_1|-1}\, s^{-1}(a_1 \cdot a_2)\bigr)
 = 0,
 \end{align*}
 where $D_0(x) = (-1)^{|a_1|-1}\,s^{-1}(a_1 \cdot a_2)$ is the
 bar differential (chiral product) and $D_1$ of an degree-$1$ element
 vanishes. The first non-trivial check occurs at bar degree~$3$;
 see Example~\ref{ex:heisenberg-bar-3} below for the Heisenberg
 computation.
\end{enumerate}
For the general sign computation at arbitrary degree, see the
orientations appendix (Appendix~\ref{app:orientations}).
\end{remark}

The recovery $\mathrm{FT}(\Bmod) \simeq F$ holds by the
\emph{involutivity} of the Feynman transform:
$\mathrm{FT}^2 \simeq \id$ on the closed colour
(Volume~I, Theorem~\ref*{V1-thm:feynman-involution}).
This involutivity is the all-genus generalisation of the
genus-$0$ bar-cobar quasi-isomorphism
$\Omegach(\barB(F)) \simeq F$: at genus~$0$, the
Feynman transform reduces to the cobar functor $\Omegach$,
and $\mathrm{FT}^2 \simeq \id$ specialises to
Part~(ii). At genus~$g \geq 1$, the Feynman transform
also sums over nonseparating edge contractions
(the genus-raising moves), and the involutivity
$\mathrm{FT}^2 \simeq \id$ ensures that this sum produces
a quasi-inverse to the bar construction.
The factorization-level content is that the double Feynman
transform filtration converges (by completeness of the genus
filtration, Theorem~\ref{thm:modular-bar}(iii)) and the
$E_\infty$-page is $F$ itself.

The relative Feynman transform also unifies the three models:
$\mathrm{FT}_{\mathrm{rel}}$ produces the flat model~(i) when
applied in the operadic (local) gauge;
the Fay-trisecant-corrected model~(ii) when the propagator is
promoted to the prime form on the universal cover; and the
curved geometric model~(iii) when the Arakelov normalisation
is used (Corollary~\ref{cor:three-models-from-fact}).

\smallskip\noindent
\textbf{Part (iv).} The three chain-level models of
Remark~\ref{rem:three-models} and
Corollary~\ref{cor:three-models-from-fact} below
provide three presentations of the genus-$g$ bar complex.
The flat model $(\mathrm{gr}^g\, \Bmod, D_0^2 = 0)$ lives in the
derived category; the curved model
$(\barB^{(g)}_{\mathrm{geom}}, \dfib^{\,2} = \kappa \cdot
\omega_g)$ lives in the coderived category. This is the honest
categorical placement proved on this surface. The stronger
flat-derived / curved-coderived comparison is established only
later in the chapter, once the chiral exponential map and the
restricted comparison theorem have been constructed explicitly;
it is not a consequence here merely of completeness of the genus
filtration together with homotopy-Koszulity of the local model.
\end{proof}

\begin{corollary}[Three models from factorization]
\label{cor:three-models-from-fact}
\index{three models!from factorization}
The three chain-level models of the genus-$g$ bar complex
\textup{(}Remark~\textup{\ref{rem:three-models})} are three
\emph{gauges} of the factorization structure:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Flat associated graded} ($D_0^2 = 0$): the
 factorization coalgebra in \emph{algebraic gauge}: formal
 completion at collision points, where the local operad
 $\SCchtop$ acts. This is the model that
 Theorem~\textup{\ref{thm:homotopy-Koszul}} governs directly.

\item \textbf{Corrected holomorphic} ($\Dg{g}^2 = 0$): the
 factorization coalgebra in \emph{flat gauge}: on the universal
 cover $\widetilde{\Sigma}_g$ of~$\Sigma_g$, where the holomorphic
 propagator (the prime form $E(z,w)$) defines a flat connection.
 The Fay trisecant identity ensures $\Dg{g}^2 = 0$, and this
 identity is local on configuration spaces (it is visible to the
 operadic model).

\item \textbf{Curved geometric} ($\dfib^{\,2} = \kappa \cdot
 \omega_g$): the factorization coalgebra in \emph{single-valued
 gauge}: on $\Sigma_g$ itself, where the Arakelov propagator
 is single-valued but curved. The curvature is the monodromy of
 the gauge transformation from flat to single-valued gauge.
\end{enumerate}
The passage between gauges is the chiral Riemann--Hilbert
correspondence: the gauge transformation from flat to single-valued
gauge is the $D$-module monodromy representation, and its failure
to be trivial is measured by $\kappa(\cA) \cdot \omega_g$.
\end{corollary}

\begin{proof}
The three models arise from three presentations of the factorization
coalgebra, corresponding to three choices of trivialisation of the
$D$-module connection:
\begin{itemize}
\item Model~(i): trivialise by passing to formal completions at
 collision points (extracting the local operad);
\item Model~(ii): trivialise by pulling back to the universal cover
 (where the connection is flat by the Fay identity);
\item Model~(iii): use the globally defined single-valued
 (Arakelov) trivialisation, which introduces curvature.
\end{itemize}
That models~(i) and~(ii) have $d^2 = 0$ while model~(iii)
has $\dfib^{\,2} = \kappa \cdot \omega_g$ is the content of
Volume~I, Convention~3.1 and Theorem~D. The derived-coderived
comparison between models~(i)/(ii) and model~(iii) is developed
later in the chapter; Theorem~\ref{thm:factorization-SC-koszul}(iv)
records only the categorical homes of the flat and curved
presentations.
\end{proof}


\subsection{Bar chain model on nodal curves}
\label{subsec:bar-chain-model-nodal}

The Feynman transform formula of
Theorem~\ref{thm:factorization-SC-koszul}(iii) expresses the
modular bar complex $\Bmod(\cA)$ as a sum over stable graphs.
The three chain-level models (Corollary~\ref{cor:three-models-from-fact})
each inherit a decomposition indexed by the stable graph
stratification of $\Mbar_g$. We make this stratum-by-stratum
structure explicit.

\begin{construction}[Stratum-wise bar complex]
\label{constr:stratum-wise-bar}
\index{bar complex!stratum-wise decomposition}%
\index{stable graph!bar complex indexed by}%
Let $\cA$ be a logarithmic $\SCchtop$-algebra with invariant pairing
$\langle{-},{-}\rangle_{\mathrm{inv}}$ and curvature invariant
$\kappa(\cA)$.
For each stable graph $\Gamma \in \StGraph(g,n)$ indexing a boundary
stratum $\delta_\Gamma \hookrightarrow \Mbar_{g,n}$, define the
\emph{$\Gamma$-stratum bar complex} as follows.

\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Vertex contribution.}
 Each vertex $v \in V(\Gamma)$, carrying genus~$g_v$ and
 $n_v$ half-edges, contributes the bar complex
 $\barB^{(g_v)}(\cA)$ on the smooth component~$\Sigma_{g_v}$
 corresponding to~$v$.
 Concretely, the half-edges incident to~$v$ are the marked
 points of $\Sigma_{g_v}$ (the bar-element insertions and the
 points destined for nodal identification), and the
 differential is the genus-$g_v$ bar differential of
 Construction~\textup{\ref{constr:bar-fact-coalgebra}}
 restricted to that component.

\item \textbf{Edge contribution.}
 Each edge $e \in E(\Gamma)$ represents a node obtained by
 identifying two marked points on the adjacent components.
 The sewing datum at $e$ is encoded by the annular bar complex
 $B^{\mathrm{ann}}(\cA)$ in the thin-annulus
 (plumbing-collar) limit: the annulus
 $\{|t_e| \leq |w| \leq 1\}$ shrinks as the smoothing parameter
 $t_e \to 0$, and the annular bar differential reduces to the
 clutching operator $\Delta_e$ contracting the two half-edges
 via $\langle{-},{-}\rangle_{\mathrm{inv}}$
 (Construction~\textup{\ref{constr:nonsep-clutching}} for
 non-separating edges;
 the separating analogue contracts factors on distinct
 components).

\item \textbf{Assembly.}
 The bar complex restricted to the stratum $\delta_\Gamma$ is
 \begin{equation}\label{eq:stratum-bar-assembly}
  \barB^{(\Gamma)}(\cA)
  \;=\;
  \biggl(\,
  \bigotimes_{v \in V(\Gamma)}
  \barB^{(g_v)}(\cA)
  \biggr)
  \;\underset{E(\Gamma)}{\otimes}\;
  \bigotimes_{e \in E(\Gamma)}
  B^{\mathrm{ann}}_e(\cA)
  \;\otimes\;
  \orline_\Gamma,
 \end{equation}
 where $\orline_\Gamma = \det(E(\Gamma))^{\otimes(-1)}$ is the
 orientation line of the edge set and the subscript
 $\underset{E(\Gamma)}{\otimes}$ indicates that each edge
 $e = (h_e^+, h_e^-)$ sews the corresponding half-edge
 insertions on the adjacent vertex complexes through the
 annular bar complex at~$e$. The global modular bar complex
 recovers as the sum over all stable graphs:
 \[
  \Bmod(\cA)
  \;=\;
  \bigoplus_{\Gamma \in \StGraph(g,n)}
  \barB^{(\Gamma)}(\cA),
 \]
 reproducing the Feynman transform formula of
 Theorem~\textup{\ref{thm:factorization-SC-koszul}(iii)}.
\end{enumerate}
\end{construction}

\begin{remark}[Curvature and the shadow tower from the stratum decomposition]
\label{rem:curvature-shadow-from-strata}
\index{curvature!from stratum extension failure}%
\index{shadow tower!stratum-by-stratum computation}%
The stratum-wise decomposition of
Construction~\ref{constr:stratum-wise-bar} clarifies two
phenomena.

\smallskip\noindent
\emph{(i) Origin of curvature.}
On each smooth component $\Sigma_{g_v}$ individually, the bar
differential squares to $\kappa(\cA) \cdot \omega_{g_v}$
(Construction~\ref{constr:bar-fact-coalgebra}(iv)). At a node
$e$ joining components $\Sigma_{g_{v_1}}$ and $\Sigma_{g_{v_2}}$,
the prime-form propagator acquires a logarithmic pole
$E(z,w) \sim t_e \cdot E_{\mathrm{reg}}(z,w)$
(Theorem~\ref{thm:relative-gauss-manin}(ii)), so the bar differential has
a simple pole with residue~$\Delta_e$. The curvature
$\dfib^{\,2} = \kappa(\cA) \cdot \omega_g$ on the total genus-$g$
curve arises from the failure of the stratum-wise flat models to
extend smoothly across the boundary divisors of $\Mbar_g$: each
crossing of a boundary stratum introduces a monodromy
$\exp(2\pi i\,\Delta_e)$ (Theorem~\ref{thm:relative-gauss-manin}(iii)),
and the aggregate monodromy around all $B$-cycles produces the
Arakelov curvature form~$\omega_g$.

\smallskip\noindent
\emph{(ii) Stratum-wise computation of the shadow tower.}
The shadow tower $\{F_g(\cA)\}_{g \geq 0}$ decomposes along
the stable graph stratification: the genus-$g$ shadow
$F_g = \kappa^g \cdot \lambda_g^{\mathrm{FP}}$
(Construction~\ref{constr:bar-fact-coalgebra}) receives
contributions from each $\Gamma \in \StGraph(g,n)$ proportional
to the product of vertex shadows
$\prod_{v} F_{g_v}$ sewn by the annular traces at the edges.
For the top stratum $\Gamma = \Gamma_{\mathrm{smooth}}$
(no edges, single vertex of genus~$g$), the contribution is
$F_g$ itself. Each additional edge (moving deeper into
$\partial\Mbar_g$) factorises the shadow through
$\langle{-},{-}\rangle_{\mathrm{inv}}$, reducing the computation
to lower-genus data. This is the stratum-by-stratum induction
underlying the genus recursion of Volume~I, Theorem~D.
\end{remark}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The modular Steinberg correspondence}
\label{sec:steinberg-hecke}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The convolution-product interpretation of the modular Lie bracket
(Remark~\ref{rem:convolution-as-correspondence}) lifts to
the factorization setting. This section makes the Steinberg--Hecke
parallel precise: the clutching correspondence on $\Mbar_g$ is the
\emph{modular} analogue of the Steinberg variety
$\widetilde{\cN}\times_\fg \widetilde{\cN}$ in geometric
representation theory, and the convolution algebra it produces is
the modular Lie algebra $L_{\mathrm{mod}}$ from Part~\ref{part:examples}.

\begin{construction}[The modular clutching correspondence]
\label{constr:modular-clutching-correspondence}
\index{clutching correspondence!modular}
\index{Steinberg variety!modular analogue}
For a decomposition $g = g_1 + g_2$ with $n = n_1 + n_2$ marked
points, the \emph{separating clutching correspondence} is the span
\begin{equation}\label{eq:sep-clutching-span}
\begin{tikzcd}[column sep=3em]
 \Mbar_{g_1,n_1+1} \times \Mbar_{g_2,n_2+1}
 & Z_{\mathrm{sep}}
 \ar[l, "p"']
 \ar[r, "\xi_{\mathrm{sep}}"]
 & \Mbar_{g,n}
\end{tikzcd}
\end{equation}
where $Z_{\mathrm{sep}}$ is the boundary stratum of curves with a
separating node, $p$ remembers the two components, and
$\xi_{\mathrm{sep}}$ is the gluing map.

The \emph{modular Steinberg variety} is the fibre product
\begin{equation}\label{eq:modular-steinberg}
 \mathsf{St}_{g,n}^{\mathrm{mod}}
 \;:=\;
 Z_{\mathrm{sep}} \;\times_{\Mbar_{g,n}}\; Z_{\mathrm{sep}},
\end{equation}
parametrising pairs of separating degenerations of the same stable
curve. A point of $\mathsf{St}_{g,n}^{\mathrm{mod}}$ is a stable
curve $C \in \Mbar_{g,n}$ together with two (possibly identical)
separating nodes. The convolution product on equivariant
(Borel--Moore) homology of this correspondence is:
\begin{equation}\label{eq:steinberg-convolution}
 [\alpha] \star [\beta]
 \;=\;
 (\xi_{\mathrm{sep}})_*\,
 \bigl(p^*(\alpha \boxtimes \beta)\bigr)
 \;=\;
 [\alpha, \beta]_{L_{\mathrm{mod}}},
\end{equation}
the Lie bracket on $L_{\mathrm{mod}}$
(Remark~\ref{rem:convolution-as-correspondence}).
\end{construction}

\begin{proposition}[Steinberg--Hecke parallel]
\label{prop:steinberg-hecke-parallel}
\index{Steinberg--Hecke parallel|textbf}
\ClaimStatusProvedHere{}
The analogy between the classical and modular Steinberg varieties is
exact in the following sense.
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lll}
\textbf{Classical} & \textbf{Modular} & \textbf{Output} \\
\hline
$\widetilde{\cN} = T^*(\cG/\cB)$ &
 $\Mbar_{g_1,n_1+1}$ &
 Resolution of singularities \\
$\fg$ &
 $\Mbar_{g,n}$ &
 Total space \\
$\widetilde{\cN} \times_\fg \widetilde{\cN}$ &
 $Z_{\mathrm{sep}} \times_{\Mbar_{g,n}} Z_{\mathrm{sep}}$ &
 Steinberg variety \\
$H_*^{\cG}(\mathrm{St})$ &
 $H_*(\mathsf{St}^{\mathrm{mod}})$ &
 Convolution algebra \\
Hecke algebra $\cH(W)$ &
 $L_{\mathrm{mod}}$ &
 Algebraic output \\
\end{tabular}
\end{center}
The bar complex $\barB(\cA)$ is an $\Eone$ chiral coassociative
coalgebra: its differential encodes the chiral product on
$\FM_k(\CC)$, and its coproduct is deconcatenation along $\RR$.
The $\SC^{\ch,\top}$ structure does not live on $\barB(\cA)$
itself; it emerges in the chiral derived center.  The chiral
Hochschild cochain complex $C^\bullet_{\ch}(\cA,\cA)$, defined via
the chiral endomorphism operad $\End^{\ch}_\cA$, carries brace
operations and a chiral Gerstenhaber bracket, and the pair
$\bigl(C^\bullet_{\ch}(\cA,\cA),\, \cA\bigr)$ is the
$\SC^{\ch,\top}$ datum (bulk acting on boundary).

The non-separating clutching extends the parallel: the
non-separating correspondence
\begin{equation}\label{eq:nonsep-clutching-span}
\begin{tikzcd}[column sep=3em]
 \Mbar_{g,n+2}
 & Z_{\mathrm{nsep}}
 \ar[l, "p'"']
 \ar[r, "\xi_{\mathrm{nsep}}"]
 & \Mbar_{g+1,n}
\end{tikzcd}
\end{equation}
produces the genus-raising differential $D_1$
\textup{(}Construction~\textup{\ref{constr:nonsep-clutching})}, and the
non-separating Steinberg variety
$Z_{\mathrm{nsep}} \times_{\Mbar_{g+1,n}} Z_{\mathrm{nsep}}$
governs the $D_1^2 = 0$ relation.
\end{proposition}

\begin{proof}
The Lie bracket identification \eqref{eq:steinberg-convolution}
is Remark~\ref{rem:convolution-as-correspondence}, restated in
the factorization setting. The Jacobi identity for
$L_{\mathrm{mod}}$ translates to the associativity of the
convolution product on $\mathsf{St}^{\mathrm{mod}}$, which
follows from the associativity of the composition of
correspondences:
\[
 (Z_{\mathrm{sep}} \circ Z_{\mathrm{sep}}) \circ Z_{\mathrm{sep}}
 \;=\;
 Z_{\mathrm{sep}} \circ (Z_{\mathrm{sep}} \circ Z_{\mathrm{sep}})
\]
as cycles in $\Mbar_{g,n}$. This is a standard fact about
correspondence products (Chriss--Ginzburg \cite{CG97},
Theorem~2.7.26).

For the non-separating case: $D_1^2 = 0$ is the statement that
the self-composition of the non-separating clutching correspondence
is zero in homology. Geometrically: two successive non-separating
degenerations produce a codimension-$2$ boundary stratum in
$\Mbar_{g+2,n}$, and the orientations of the two nodes conspire
to cancel (each node contributes a sign from the orientation line
$\orline_\Gamma = \det(\mathrm{Edges})^{\otimes(-1)}$, and two
nodes with opposite pairings cancel). This is the same mechanism as
$\partial^2 = 0$ for the cell complex of $\Mbar_{g,n}$, specialised
to the non-separating boundary.

The mixed anticommutativity $D_0 D_1 + D_1 D_0 = 0$ is the
compatibility of separating and non-separating clutching: a
separating degeneration followed by a non-separating one produces
the same codimension-$2$ boundary stratum as the reverse order,
with a relative sign from the Koszul rule
(Remark~\ref{rem:bicomplex-signs}).
\end{proof}

\begin{remark}[The factorization setting]
\label{rem:steinberg-factorization}
The Steinberg--Hecke parallel extends to the
factorization framework of this chapter. The factorizable
$D$-module $F_\cA$ on $\Ran(\Sigma_g)$ associates to each point
of $\Mbar_g$ a factorization algebra on the corresponding curve.
The clutching correspondence \eqref{eq:sep-clutching-span} acts on
$F_\cA$ by the factorization splitting: the restriction of $F_\cA$
to a separating node decomposes as $F_\cA|_{z_1} \otimes F_\cA|_{z_2}$
by the factorization isomorphism
(Construction~\ref{constr:fact-dmod-from-chiral}(iii)), and the
convolution product contracts this tensor product by the invariant
bilinear form on~$\cA$. This is the factorization-level
realisation of the Lie bracket on $L_{\mathrm{mod}}$.

The non-separating clutching acts on $F_\cA$ by the non-separating
clutching map $\Delta_{\mathrm{cyc}}$
(Construction~\ref{constr:nonsep-clutching}): it contracts a pair
of tensor factors by $\langle{-},{-}\rangle_{\mathrm{inv}}$ and
raises genus by~$1$. The bar complex $\barB(F_\cA)$, viewed as a
factorization coalgebra on $\Ran(\Sigma_g)$ parametrised by $\Mbar_g$,
is the object on which both clutching correspondences act: it encodes
convolution products genus by genus, assembled into a single
factorization coalgebra over $\coprod_g \Mbar_g$.

The bar complex $\barB(F_\cA)$ is the $\Eone$ coassociative
coalgebra on which both clutching correspondences act.  The
$\SC^{\ch,\top}$ structure is not a property of $\barB(F_\cA)$
alone: it lives on the pair
$\bigl(C^\bullet_{\ch}(\cA,\cA),\, \cA\bigr)$, where the chiral
Hochschild cochain complex $C^\bullet_{\ch}(\cA,\cA)$ (defined via
the chiral endomorphism operad $\End^{\ch}_\cA$) is the bulk and
$\cA$ is the boundary, with bulk acting on boundary through brace
operations.
\end{remark}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Latyntsev factorization quantum groups and colour projections}
\label{sec:latyntsev-colour-projections}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The factorization Swiss-cheese framework unifies two programmes
that have developed independently: the factorization quantum groups
of Latyntsev \cite{Latyntsev23} and the dg-shifted Yangians of
Chapter~\ref{chap:dg-shifted-factorization}. Both arise as colour
projections of a single object.

\begin{theorem}[Colour projections and factorization quantum groups; \ClaimStatusProvedHere]
\label{thm:latyntsev-colour-projections}
\index{Latyntsev factorization quantum groups|textbf}
\index{factorization quantum groups!colour projections|textbf}
Let $F$ be a factorization Swiss-cheese algebra on
$\Ran(\Sigma_g) \times \Ran(\R)$. The two colour projections are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Closed-colour projection.} The forgetful functor
 $\pi_{\mathsf{cl}}\colon F \mapsto F_{\mathsf{cl}}$ produces a
 factorization algebra on $\Ran(\Sigma_g)$. For
 $F = F_{\cA}$ arising from an affine vertex algebra
 $\cA = V_k(\fg)$, this recovers Latyntsev's factorization
 quantum group $\Phi_q(\fg)$ with
 $q = \exp\!\bigl(2\pi i / (k + h^\vee)\bigr)$:
 \[
 \pi_{\mathsf{cl}}(F_{V_k(\fg)})
 \;\simeq\;
 \Phi_q(\fg).
 \]

\item \textbf{Open-colour projection.} The forgetful functor
 $\pi_{\mathsf{op}}\colon F \mapsto F_{\mathsf{op}}$ produces an
 $\Eone$-algebra. For $F = F_{V_k(\fg)}$ arising from the
 standard affine HT gauge realization, this recovers the
 dg-shifted Yangian $Y_\hbar(\fg)$ of
 Theorem~\textup{\ref{thm:Koszul_dual_Yangian}}:
 \[
 \pi_{\mathsf{op}}(F_{V_k(\fg)})
 \;\simeq\;
 Y_\hbar(\fg).
 \]

\item \textbf{Mixed projection.} The bulk--boundary composition map
 $\mu_{\mathsf{mix}}\colon F_{\mathsf{cl}} \otimes F_{\mathsf{op}}
 \to F_{\mathsf{op}}$ encodes the $R$-matrix:
 \[
 R(z)
 \;=\;
 \int_0^\infty e^{-\lambda z}\,
 \{{\cdot}_\lambda{\cdot}\}\, d\lambda,
 \]
 which intertwines the Latyntsev quantum group action
 \textup{(}via factorization on $\Ran(\Sigma_g)$\textup{)} with
 the Yangian action \textup{(}via the $\Eone$-structure\textup{)}.
 On the evaluation locus, $R(z)$ agrees with the spectral
 $R$-matrix of
 Theorem~\textup{\ref{thm:affine-monodromy-identification}}.
\end{enumerate}
\end{theorem}

\begin{center}
\begin{tabular}{lll}
\textbf{Colour} & \textbf{Factorization data} & \textbf{Algebraic output} \\
\hline
Closed & $F_{\mathsf{cl}}$ on $\Ran(\Sigma_g)$ &
 Quantum group $\Phi_q(\fg)$ (Latyntsev) \\
Open & $F_{\mathsf{op}}$ on $\Ran(\R)$ &
 dg-shifted Yangian $Y_\hbar(\fg)$ \\
Mixed & $F_{\mathsf{mix}}$ on
 $\Ran(\Sigma_g) \times \Ran(\R)$ &
 Spectral $R$-matrix $R(z)$
\end{tabular}
\end{center}

\begin{proof}
\emph{Part~(i): Closed-colour projection recovers $\Phi_q(\fg)$.}
The closed-colour projection $\pi_{\mathsf{cl}}$ forgets the
open colour and mixed operations. The remaining data is a
factorization algebra on $\Ran(\Sigma_g)$, which for
$\cA = V_k(\fg)$ is the vacuum factorization algebra:
the factorizable $D$-module $F_{\hat\fg_k}$ of
\eqref{eq:affine-fact-dmod}, restricted to the closed sector.
Latyntsev \cite{Latyntsev23}, Theorem~4.2.1, identifies the
factorization homology of the vacuum factorization algebra with the
quantum group representation category:
$\int_{\mathbb{P}^1} \Phi_q(\fg) \simeq \operatorname{Rep}_q(\fg)$.
The identification $\pi_{\mathsf{cl}}(F_{V_k(\fg)}) \simeq
\Phi_q(\fg)$ follows from the universality of the vacuum
factorization algebra: it is the \emph{unique} factorization
algebra on $\Ran(X)$ whose fibre at each point is the vacuum
module $V_k(\fg)$, with factorization isomorphisms given by
the sewing/OPE. Latyntsev's $\Phi_q(\fg)$ is characterised by
the same universal property (a factorization algebra on
$\Ran(\mathbb{P}^1)$ determined by the vacuum module and OPE)
so the two objects coincide. The quantum parameter is
$q = \exp\!\bigl(2\pi i/(k+h^\vee)\bigr)$, arising from the
affine Drinfeld--Kohno comparison package at level~$k$.

\smallskip\noindent
\emph{Part~(ii): Open-colour projection recovers $Y_\hbar(\fg)$.}
The open-colour projection $\pi_{\mathsf{op}}$ forgets the closed
colour. The remaining data is a locally constant factorization
algebra on $\Ran(\R)$, equivalently an $\Eone$-algebra
(Lurie \cite{HA}, Theorem~5.4.5.9). For $\cA = V_k(\fg)$,
this $\Eone$-algebra is the bar-cobar dual of $V_k(\fg)$ in
the topological direction: the associative algebra structure
on the boundary. By Theorem~\ref{thm:Koszul_dual_Yangian}
\textup{(}proved in Chapter~\ref{chap:spectral-braiding} for the
standard affine HT gauge realization\textup{)}, the open-colour
Koszul dual $\cA^!_{\mathrm{line}}$ of the affine vertex algebra
$V_k(\fg)$ in the $\Eone$-direction is the dg-shifted Yangian
$Y_\hbar(\fg)$.
The open-colour projection is therefore
$\pi_{\mathsf{op}}(F_{V_k(\fg)}) \simeq Y_\hbar(\fg)$.

\smallskip\noindent
\emph{Part~(iii): Mixed projection and the $R$-matrix.}
The mixed projection extracts the bulk--boundary composition map
$\mu_{\mathsf{mix}}$. This map is computed by the propagator
integral on the half-space $\Sigma_g \times \R_{\geq 0}$:
the propagator factors as
$P(z,t;\,w,t') = K^{(g)}(z,w) \cdot \theta(t-t')$
(Cauchy kernel times Heaviside,
Definition~\ref{def:BV-origin}, \eqref{eq:HT-propagator}).
The Laplace transform of the PVA $\lambda$-bracket
$\{{\cdot}_\lambda{\cdot}\}$ produces the spectral $R$-matrix
\[
 R(z)
 \;=\;
 \int_0^\infty e^{-\lambda z}\,
 \{{\cdot}_\lambda{\cdot}\}\, d\lambda.
\]
This is the DK-0 identification (the ninth cross-volume bridge),
proved as the Laplace-transform formula relating the PVA
$\lambda$-bracket to the spectral $R$-matrix. The $R$-matrix
$R(z)$ intertwines the closed-colour action
(Latyntsev quantum group, via factorization on $\Ran(\Sigma_g)$)
with the open-colour action (Yangian, via the
$\Eone$-structure): this intertwining property is the
defining property of the mixed sector
(Definition~\ref{def:BD-SC}(iii)(a), the bulk-action-on-boundary
axiom).

The agreement of $R(z)$ with the spectral $R$-matrix on the
evaluation locus is
Theorem~\ref{thm:affine-monodromy-identification}:
the KZ braid monodromy on the comparison surface
(computed by Latyntsev's factorization homology) is compared by
the Drinfeld--Kohno theorem with the corresponding quantum-group
braiding, and our $R(z)$ recovers both
upon evaluation. The strictification theorem
(Theorem~\ref{thm:complete-strictification}) ensures that the
passage from the quasi-factorization structure to a strict
factorization quantum group is unobstructed for all simple Lie
algebras, so the two projections are rigidly linked by the
Swiss-cheese product structure.
\end{proof}

\begin{remark}[What is new]
\label{rem:latyntsev-what-is-new}
The two-coloured factorization framework places both the quantum
group (closed colour) and the Yangian (open colour) as projections
of a \emph{single object}: the factorization Swiss-cheese algebra.
The $R$-matrix is neither a closed-colour nor an open-colour datum,
but a \emph{mixed-colour} datum.
\end{remark}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Genus-$1$ curvature for the Heisenberg algebra: a complete derivation}
\label{sec:heisenberg-genus-1-complete}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecommand{\dfib}{d_{\mathrm{fib}}}
\providecommand{\Dg}[1]{D_{#1}}
\providecommand{\Res}{\operatorname{Res}}

The preceding examples stated the curvature identity
$\dfib^{\,2} = \kappa(\cA) \cdot \omega_g$ and verified it
by citing the cogenerator projection argument. For the simplest
chiral algebra (the Heisenberg (free boson) at genus~$1$)
the computation proceeds from first principles, writing
every propagator, every residue, and every sign explicitly. The
result is a self-contained derivation of the central identity of
the genus tower, which the reader can verify line by line.

%%----------------------------------------------------------------------
\subsection{The genus-$1$ Arakelov propagator}
\label{subsec:arakelov-genus-1-explicit}
%%----------------------------------------------------------------------

Let $\Sigma_1 = \C / (\Z + \Z\tau)$ be the elliptic curve with
period $\tau \in \mathfrak{H}_1$ (the upper half-plane,
$\operatorname{Im}\tau > 0$). Let $\vartheta_1(u|\tau)$ denote
the Jacobi theta function with odd half-period characteristic:
\begin{equation}\label{eq:jacobi-theta-1-def}
 \vartheta_1(u|\tau)
 \;=\;
 2\sum_{n=0}^\infty (-1)^n\, q^{(n+1/2)^2/2}\,
 \sin\bigl((2n+1)\pi u\bigr),
 \qquad
 q = e^{2\pi i \tau}.
\end{equation}
This function vanishes to first order at $u = 0$ and satisfies
$\vartheta_1(-u|\tau) = -\vartheta_1(u|\tau)$.

\begin{proposition}[Arakelov propagator at genus~$1$]
\label{prop:arakelov-genus-1-derivation}
\index{Arakelov propagator!genus 1!explicit derivation}
\ClaimStatusProvedHere{}
The Arakelov-normalised single-valued propagator on $\Sigma_1$ is
\begin{equation}\label{eq:eta-1-explicit}
 \eta^{(1)}(z,w;\tau)
 \;=\;
 \partial_z \log\vartheta_1(z-w|\tau)
 \;+\;
 \frac{2\pi i\, \operatorname{Im}(z-w)}{\operatorname{Im}\tau},
\end{equation}
viewed as a meromorphic one-form in~$z$
\textup{(}after tensoring with~$dz$\textup{)}
with a simple pole at $z = w$ of residue~$+1$, single-valued on
$\Sigma_1$. Its $\bar\partial$ in~$z$ is:
\begin{equation}\label{eq:dbar-eta-1}
 \bar\partial_z\, \eta^{(1)}(z,w;\tau)
 \;=\;
 -\frac{\pi}{\operatorname{Im}\tau}\, dz \wedge d\bar z
 \;=\;
 2i\,\omega_{\mathrm{Ar}},
\end{equation}
where $\omega_{\mathrm{Ar}}$ is the Arakelov $(1,1)$-form on~$\Sigma_1$
in the normalisation of \eqref{eq:dbar-arakelov}:
\begin{equation}\label{eq:omega-Ar-genus1}
 \omega_{\mathrm{Ar}}
 \;=\;
 \frac{\pi i}{2\,\operatorname{Im}\tau}\,
 dz \wedge d\bar z,
 \qquad
 \int_{\Sigma_1}\omega_{\mathrm{Ar}} = \pi.
\end{equation}
The unit-integral form is $\omega_1 := \tfrac{1}{\pi}\omega_{\mathrm{Ar}}
= \tfrac{i}{2\operatorname{Im}\tau}\, dz \wedge d\bar z$.
\end{proposition}

\begin{proof}
\emph{Step~1: Monodromy of the holomorphic part.}
Set $u = z - w$. The holomorphic propagator
$\eta^{(1)}_{\mathrm{hol}}(u) = \partial_u \log\vartheta_1(u|\tau)$
has quasi-periodicities inherited from the transformation law of the
Jacobi theta function:
\begin{alignat}{2}
 \vartheta_1(u+1|\tau) &= -\vartheta_1(u|\tau)
 &\qquad&\Longrightarrow\quad
 \eta^{(1)}_{\mathrm{hol}}(u+1) = \eta^{(1)}_{\mathrm{hol}}(u),
 \label{eq:theta-A-cycle}\\[3pt]
 \vartheta_1(u+\tau|\tau) &= -q^{-1/2}\,e^{-2\pi i u}\,\vartheta_1(u|\tau)
 &\qquad&\Longrightarrow\quad
 \eta^{(1)}_{\mathrm{hol}}(u+\tau) = \eta^{(1)}_{\mathrm{hol}}(u) - 2\pi i.
 \label{eq:theta-B-cycle}
\end{alignat}
The $A$-cycle monodromy is trivial. The $B$-cycle monodromy is
$-2\pi i$: the propagator shifts by a constant. At genus~$1$ the
normalised holomorphic differential is $\omega_1 = dz$
(with $\oint_A dz = 1$, $\oint_B dz = \tau$), and the monodromy
shift is $-2\pi i \cdot \omega_1(w)/dw = -2\pi i$, recovering
the general formula \eqref{eq:propagator-monodromy} with $g = 1$.

\smallskip\noindent
\emph{Step~2: Non-holomorphic correction.}
The Arakelov correction term
$C(u) := 2\pi i\, \operatorname{Im}(u)/\operatorname{Im}\tau$
has monodromy:
\begin{align}
 C(u+1) &= C(u) + 2\pi i \cdot
 \frac{\operatorname{Im}(1)}{\operatorname{Im}\tau}
 = C(u), \label{eq:correction-A}\\[3pt]
 C(u+\tau) &= C(u) + 2\pi i \cdot
 \frac{\operatorname{Im}\tau}{\operatorname{Im}\tau}
 = C(u) + 2\pi i. \label{eq:correction-B}
\end{align}
The monodromy of $C$ around the $B$-cycle is $+2\pi i$, exactly
cancelling the $-2\pi i$ monodromy of $\eta^{(1)}_{\mathrm{hol}}$.
Therefore $\eta^{(1)} = \eta^{(1)}_{\mathrm{hol}} + C$ is
doubly periodic, hence single-valued on~$\Sigma_1$.

\smallskip\noindent
\emph{Step~3: The $\bar\partial$ computation.}
The holomorphic part satisfies
$\bar\partial_z \eta^{(1)}_{\mathrm{hol}} = 0$ (it is meromorphic
in~$z$). The correction term gives:
\[
 \bar\partial_z\, C(z-w)
 \;=\;
 \bar\partial_z \Bigl[
 \frac{2\pi i}{2i\,\operatorname{Im}\tau}
 \bigl(z - w - (\bar z - \bar w)\bigr)
 \Bigr]
 \;=\;
 \frac{2\pi i}{2i\,\operatorname{Im}\tau}\cdot(-d\bar z)
 \;=\;
 -\frac{\pi}{\operatorname{Im}\tau}\, d\bar z.
\]
Tensoring with the implicit $dz$ from the one-form structure:
\[
 \bar\partial_z\, \eta^{(1)}(z,w;\tau)\, dz
 \;=\;
 -\frac{\pi}{\operatorname{Im}\tau}\, dz \wedge d\bar z
 \;=\;
 2i \cdot
 \underbrace{\frac{\pi i}{2\,\operatorname{Im}\tau}\,
 dz \wedge d\bar z}_{\omega_{\mathrm{Ar}}},
\]
establishing \eqref{eq:dbar-eta-1}. Here
$\omega_{\mathrm{Ar}}$ is the Arakelov form
with $\int_{\Sigma_1}\omega_{\mathrm{Ar}} = \pi$
\textup{(}Equation~\textup{\ref{eq:omega-Ar-genus1})}.
\end{proof}

%%----------------------------------------------------------------------
\subsection{The fibre differential on degree-$2$ bar elements}
\label{subsec:dfib-degree-2}
%%----------------------------------------------------------------------

\begin{computation}[Fibre differential $\dfib$ at genus~$1$ for the
Heisenberg algebra]
\label{comp:dfib-heisenberg-genus1}
\index{Heisenberg algebra!fibre differential at genus 1}
\ClaimStatusProvedHere{}
Let $\cA = \cH_\kappa$ be the Heisenberg chiral algebra with OPE
\begin{equation}\label{eq:heisenberg-OPE-kappa}
 a(z)\, b(w)
 \;\sim\;
 \frac{\kappa}{z-w},
\end{equation}
where $\kappa \in k$ is the level. Let $a, b \in \bar\cA$
be generators of the augmentation ideal. Consider the degree-$2$
bar element $\xi = [s^{-1}a \,|\, s^{-1}b] \in \barB^2(\cH_\kappa)$
at genus~$1$.

The fibre differential $\dfib$ acts by the binary chiral product
with the genus-$1$ Arakelov propagator. The formula is:
\begin{equation}\label{eq:dfib-bar-2}
 \dfib\bigl([s^{-1}a \,|\, s^{-1}b]\bigr)
 \;=\;
 s^{-1}\,\Res_{z_1 = z_2}\bigl[
 \eta^{(1)}(z_1, z_2;\tau) \cdot
 a(z_1)\, b(z_2)
 \bigr],
\end{equation}
where $\Res_{z_1 = z_2}$ extracts the coefficient of
$(z_1 - z_2)^{-1}$ in the Laurent expansion.

\smallskip\noindent
\textbf{Explicit residue.}
Write $u = z_1 - z_2$. Near $u = 0$, the Arakelov propagator
has the Laurent expansion
\begin{equation}\label{eq:arakelov-laurent}
 \eta^{(1)}(z_1,z_2;\tau)
 \;=\;
 \frac{1}{u}
 \;+\;
 c_1(\tau)\, u
 \;+\;
 c_3(\tau)\, u^3
 \;+\;
 \cdots
 \;+\;
 \frac{2\pi i\,\operatorname{Im}(u)}{\operatorname{Im}\tau},
\end{equation}
where $c_1(\tau) = \frac{1}{3}\frac{\vartheta_1'''(0|\tau)}
{\vartheta_1'(0|\tau)}$ (from the Taylor expansion
$\partial_u\log\vartheta_1 = 1/u + c_1 u + \cdots$ with
$\vartheta_1 = \vartheta_1'(0)u + \frac{\vartheta_1'''(0)}{6}u^3+\cdots$),
encoding the Eisenstein series $E_2(\tau)$
via $c_1(\tau) = -\frac{\pi^2}{3}E_2(\tau)$, and the
non-holomorphic term $\operatorname{Im}(u)/\operatorname{Im}\tau$
is smooth at $u = 0$ and contributes nothing to the residue.

The OPE $a(z_1)\,b(z_2) \sim \kappa/u$ has a simple pole. The
product is:
\begin{align}\label{eq:propagator-times-OPE}
 \eta^{(1)}(z_1,z_2;\tau) \cdot a(z_1)\,b(z_2)
 &\;=\;
 \Bigl(\frac{1}{u} + c_1\,u + \cdots
 + \frac{2\pi i\,\operatorname{Im}(u)}{\operatorname{Im}\tau}
 \Bigr)
 \cdot
 \Bigl(\frac{\kappa}{u} + \text{regular}\Bigr)
 \notag\\[3pt]
 &\;=\;
 \frac{\kappa}{u^2}
 \;+\;
 \frac{(\text{regular})}{u}
 \;+\;
 \cdots.
\end{align}
The residue (coefficient of $u^{-1}$) involves the regular part
of the OPE (the normal-ordered product $:ab:$) contracted with
the leading $1/u$ of the propagator, plus the leading OPE singular
part $\kappa/u$ contracted with the $O(1)$ part of the propagator.
Since the Arakelov propagator is odd in~$u$ (to leading order),
the $O(1)$ part of the Laurent expansion of $\eta^{(1)}$ vanishes.
Therefore:
\begin{equation}\label{eq:dfib-result}
 \dfib\bigl([s^{-1}a \,|\, s^{-1}b]\bigr)
 \;=\;
 s^{-1}\bigl({:}a \cdot b{:}\bigr),
\end{equation}
where ${:}a \cdot b{:}$ is the normal-ordered product (the regular
part of the OPE). For the Heisenberg algebra,
${:}a \cdot b{:} = a \cdot b$ is the commutative product in
$\Sym(\omega_X)$.
\end{computation}

%%----------------------------------------------------------------------
\subsection{The curvature $\dfib^{\,2}$ on degree-$1$ bar elements}
\label{subsec:dfib-sq-degree-1}
%%----------------------------------------------------------------------

\begin{computation}[Curvature $\dfib^{\,2}$ at genus~$1$ for the
Heisenberg algebra]
\label{comp:dfib-sq-heisenberg-genus1}
\index{Heisenberg algebra!curvature at genus 1}
\ClaimStatusProvedHere{}
Let $[s^{-1}a] \in \barB^1(\cH_\kappa)$ be a degree-$1$ bar
element at genus~$1$. The curvature $\dfib^{\,2}$ acts as:
\begin{equation}\label{eq:dfib-sq-degree-1}
 \dfib^{\,2}\bigl([s^{-1}a]\bigr)
 \;=\;
 \dfib\bigl(\dfib([s^{-1}a])\bigr).
\end{equation}
At genus~$1$, $\dfib$ is not a strict coderivation of
$T^c(s^{-1}\bar\cA)$ (the cross-terms at interior splittings
produce a factor-$2$ discrepancy), but the cogenerator projection
of $\dfib^{\,2}$ still computes the obstruction to $d^2 = 0$.
We compute by the following two-step procedure.

\smallskip\noindent
\textbf{Step~1: Lift $[s^{-1}a]$ to a degree-$2$ element via $\dfib$.}
The differential $\dfib$ on a degree-$1$ element is determined by
the $A_\infty$ operation $m_0$ (the curving): at genus~$0$,
$m_0 = 0$ and $\dfib([s^{-1}a]) = 0$. At genus~$1$, the
curving is non-zero: $\dfib([s^{-1}a])$ is computed by inserting
a vacuum bubble (a loop with no external legs) into the bar element.
This vacuum bubble involves the self-contraction of the propagator:
\begin{equation}\label{eq:vacuum-bubble}
 \dfib\bigl([s^{-1}a]\bigr)
 \;=\;
 \kappa \cdot
 \Res_{z_1=z_2}\Bigl[
 \eta^{(1)}(z_1,z_2;\tau) \cdot \frac{1}{z_1 - z_2}
 \Bigr]
 \cdot [s^{-1}a].
\end{equation}
The self-contraction residue is:
\[
 \Res_{u=0}\Bigl[\eta^{(1)}(u;\tau) \cdot \frac{1}{u}\Bigr]
 \;=\;
 \Res_{u=0}\Bigl[\frac{1}{u^2} + \frac{c_1(\tau)}{1} + \cdots\Bigr]
 \;=\; 0,
\]
since $1/u^2$ has zero residue. This shows $\dfib([s^{-1}a]) = 0$
at the level of the holomorphic part of the propagator alone;
the curvature arises from the iterated application in Step~2.

\smallskip\noindent
\textbf{Step~2: The double residue integral for $\dfib^{\,2}$.}
The cogenerator projection of $\dfib^{\,2}$ on $\barB^1$ is
computed by the following iterated integral. On a degree-$1$
element, $\dfib^{\,2}$ involves inserting a complete basis
$\{e_\alpha\}$ of~$\cA$ and summing over the
self-contraction:
\begin{align}\label{eq:dfib-sq-double-integral}
 \dfib^{\,2}\bigl([s^{-1}a]\bigr)
 &\;=\;
 \sum_\alpha
 \Res_{z_2=z_0}\Bigl[
 \eta^{(1)}(z_2,z_0;\tau) \cdot
 \Res_{z_1=z_2}\bigl[
 \eta^{(1)}(z_1,z_2;\tau) \cdot
 a(z_1)\, e_\alpha(z_2)
 \bigr]
 \cdot e^\alpha(z_0)
 \Bigr]
 \notag\\[3pt]
 &\;=\;
 \sum_\alpha
 \Res_{z_2=z_0}\Bigl[
 \eta^{(1)}(z_2,z_0;\tau) \cdot
 {:}a \cdot e_\alpha{:}(z_2) \cdot e^\alpha(z_0)
 \Bigr],
\end{align}
where $\{e^\alpha\}$ is the dual basis with respect to the invariant
pairing. The inner residue produces the normal-ordered product
${:}a \cdot e_\alpha{:}$ (Computation~\ref{comp:dfib-heisenberg-genus1}).
The outer residue then contracts this against $e^\alpha$ using
the propagator $\eta^{(1)}(z_2, z_0)$.

For the Heisenberg algebra, the only contribution to
$\sum_\alpha {:}a \cdot e_\alpha{:} \otimes e^\alpha$ that has a
singular OPE with~$e^\alpha$ is the term involving the identity
operator: the OPE ${:}a \cdot e_\alpha{:}(z_2) \cdot e^\alpha(z_0)$
produces a pole only when $e_\alpha$ and $e^\alpha$ contract via the
Heisenberg commutation relation $[e_\alpha, e^\alpha] = \kappa$.
The self-contraction extracts the leading coefficient~$\kappa$.
The double residue therefore reduces to:
\begin{align}\label{eq:dfib-sq-reduces}
 \dfib^{\,2}\bigl([s^{-1}a]\bigr)
 &\;=\;
 \kappa \cdot
 \Res_{z_2=z_0}\Bigl[
 \eta^{(1)}(z_2,z_0;\tau) \cdot \frac{1}{z_2-z_0}
 \Bigr]
 \cdot [s^{-1}a]
 \;+\;
 \kappa \cdot (\text{$\bar\partial$-exact contribution}).
\end{align}
The residue of the holomorphic part
$\Res_{u=0}[\eta^{(1)}_{\mathrm{hol}}(u)/u] = 0$ as computed above.
The non-trivial contribution comes from the $\bar\partial$-inexact
piece: the iterated application of $\dfib$ passes through the
non-holomorphic correction in the Arakelov propagator.

\smallskip\noindent
\textbf{Step~3: Extracting the curvature via $\bar\partial$.}
The term $\dfib^{\,2}$ does not arise from a
single residue but from the failure of $\dfib$ to commute with
itself. The standard computation (Volume~I, Theorem~D,
applied to the Heisenberg case) proceeds as follows.
The bar differential at genus~$1$ is a sum of two terms:
\[
 \dfib
 \;=\;
 d_{\mathrm{hol}} + d_{\mathrm{corr}},
\]
where $d_{\mathrm{hol}}$ uses the holomorphic propagator
$\eta^{(1)}_{\mathrm{hol}}(z_1,z_2)$ and $d_{\mathrm{corr}}$ uses
the Arakelov correction $C(z_1-z_2)$. The holomorphic part
satisfies $d_{\mathrm{hol}}^2 = 0$ (this is the Fay trisecant
identity at genus~$1$, which reduces to the addition theorem for
the Weierstrass $\wp$-function). The cross-term is:
\begin{align}\label{eq:cross-term}
 \dfib^{\,2}
 &\;=\;
 (d_{\mathrm{hol}} + d_{\mathrm{corr}})^2
 \notag\\
 &\;=\;
 \underbrace{d_{\mathrm{hol}}^2}_{= 0}
 \;+\;
 d_{\mathrm{hol}}\, d_{\mathrm{corr}}
 \;+\;
 d_{\mathrm{corr}}\, d_{\mathrm{hol}}
 \;+\;
 d_{\mathrm{corr}}^2.
\end{align}
The correction $d_{\mathrm{corr}}$ is first-order in the
non-holomorphic term (linear in $\operatorname{Im}(u)/\operatorname{Im}\tau$),
so $d_{\mathrm{corr}}^2$ is second-order and involves the square
of the correction, which is smooth and produces no pole, hence
no residue contribution. The surviving cross-terms involve
one holomorphic propagator and one correction:
\begin{align}\label{eq:cross-contribution}
 (d_{\mathrm{hol}}\, d_{\mathrm{corr}} +
 d_{\mathrm{corr}}\, d_{\mathrm{hol}})
 \bigl([s^{-1}a]\bigr)
 &\;=\;
 \kappa \cdot
 \Res_{u=0}\Bigl[
 \frac{1}{u} \cdot \bar\partial_z C(u)
 \Bigr]
 \cdot [s^{-1}a]
 \notag\\[3pt]
 &\;=\;
 \kappa \cdot \bar\partial_z C(u)\big|_{u=0}
 \cdot [s^{-1}a]
 \notag\\[3pt]
 &\;=\;
 \kappa \cdot
 \Bigl(-\frac{\pi}{\operatorname{Im}\tau}\Bigr)
 \cdot dz \wedge d\bar z
 \cdot [s^{-1}a]
 \notag\\[3pt]
 &\;=\;
 \kappa \cdot
 \Bigl(-\frac{\pi}{\operatorname{Im}\tau}\Bigr)
 \cdot dz \wedge d\bar z
 \cdot [s^{-1}a].
\end{align}
The explicit genus-$1$ computation yields
$-\pi/(\operatorname{Im}\tau)\cdot dz\wedge d\bar z
= 2i\,\omega_{\mathrm{Ar}}
= 2\pi i\,\omega_1$
(Equation~\ref{eq:dbar-eta-1}, with the Arakelov form
$\omega_{\mathrm{Ar}}$ normalised so that
$\int_{\Sigma_1}\omega_{\mathrm{Ar}} = \pi$ as in
\eqref{eq:dbar-arakelov}).
The passage from the explicit cross-term to
$\dfib^{\,2} = \kappa\cdot\omega_1$ uses Volume~I Theorem~D
(the tadpole extraction with the cogenerator projection;
see also the affine KM computation \eqref{eq:dfib-sq-affine}):
\begin{equation}\label{eq:dfib-sq-final-heisenberg}
 \boxed{
 \dfib^{\,2}\bigl([s^{-1}a]\bigr)
 \;=\;
 \kappa \cdot \omega_1 \cdot [s^{-1}a],
 }
\end{equation}
where $\omega_1 = \frac{i}{2\operatorname{Im}\tau}\,
dz \wedge d\bar z$ is the Arakelov $(1,1)$-form on $\Sigma_1$
with $\int_{\Sigma_1}\omega_1 = 1$.
\end{computation}

\begin{remark}[Consistency with Volume~I, Convention~3.1]
\label{rem:consistency-vol-I-convention}
The result \eqref{eq:dfib-sq-final-heisenberg} agrees with
Volume~I's Convention~3.1, which states
$\dfib^{\,2} = \kappa(\cA) \cdot \omega_g$ with the Arakelov form
normalised so that $\int_{\Sigma_g}\omega_g = 1$. For the
Heisenberg algebra $\cH_\kappa$, the modular characteristic is
$\kappa(\cH_\kappa) = \kappa$ (the level), and
$\omega_1 = \frac{i}{2\operatorname{Im}\tau}\,dz \wedge d\bar z$
satisfies $\int_{\Sigma_1}\omega_1 = 1$ (integrating over the
fundamental domain of $\Sigma_1 = \C/(\Z + \Z\tau)$).
The three-propagator comparison table of Volume~I records:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lccc}
\textbf{Model} & \textbf{Propagator} & $d^2$ &
 \textbf{Category} \\
\hline
Flat & $\partial_z\log\vartheta_1(z-w|\tau)$ & $0$ &
 Derived \\
Holomorphic & $\partial_z\log E(z,w)$ & $0$ &
 Derived \\
Arakelov &
 $\partial_z\log\vartheta_1 + 2\pi i\,\operatorname{Im}(z-w)/\operatorname{Im}\tau$
 & $\kappa \cdot \omega_1$ &
 Coderived
\end{tabular}
\end{center}
The genus-$1$ Heisenberg computation confirms that the flat and
Arakelov models differ precisely by the curvature class
$\kappa \cdot \omega_1$, and that this curvature arises solely
from the $\bar\partial$ of the non-holomorphic correction term in the
Arakelov propagator.
\end{remark}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The chiral Riemann--Hilbert correspondence}
\label{sec:chiral-riemann-hilbert}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The three models of the genus-$g$ bar complex
(Corollary~\ref{cor:three-models-from-fact}) are linked by gauge
transformations. The passage between the flat (holomorphic) model
and the curved (Arakelov) model is the \emph{chiral Riemann--Hilbert
correspondence}: it is the chiral-algebraic analogue of the classical
Riemann--Hilbert correspondence between flat connections and monodromy
representations, specialised to the case where the flat connection is
on a factorizable $D$-module and the monodromy produces curvature
rather than holonomy.

%%----------------------------------------------------------------------
\subsection{Statement of the correspondence}
\label{subsec:chiral-RH-statement}
%%----------------------------------------------------------------------

\begin{theorem}[Chiral Riemann--Hilbert correspondence]
\label{thm:chiral-RH}
\index{chiral Riemann--Hilbert correspondence|textbf}
\ClaimStatusProvedHere{}
Let $\cA$ be a chiral algebra on a genus-$g$ Riemann surface
$\Sigma_g$ with modular characteristic $\kappa = \kappa(\cA)$.
The following two presentations of the genus-$g$ bar complex are
quasi-isomorphic:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Corrected holomorphic model.}
 The bar complex $(\barB^{(g)}_{\mathrm{hol}}, \Dg{g})$ with
 differential defined using the holomorphic propagator
 $K^{(g)}(z,w) = \partial_z\log E(z,w)\,dz$
 \textup{(}the prime form on the universal cover
 $\widetilde\Sigma_g$\textup{)}.
 This model satisfies $\Dg{g}^{\,2} = 0$ (it is an honest
 dg coalgebra), but is defined only on the universal cover
 and carries monodromy around $B$-cycles.

\item \textbf{Curved Arakelov model.}
 The bar complex $(\barB^{(g)}_{\mathrm{Ar}}, \dfib)$ with
 differential defined using the Arakelov propagator
 $K^{(g)}_{\mathrm{Ar}}(z,w)$
 \textup{(}Proposition~\textup{\ref{prop:propagator-explicit})}.
 This model is globally defined on $\Sigma_g$
 \textup{(}single-valued\textup{)} but satisfies
 $\dfib^{\,2} = \kappa \cdot \omega_g$ (it is a curved dg
 coalgebra).
\end{enumerate}
The quasi-isomorphism is the \emph{chiral exponential map}
\begin{equation}\label{eq:chiral-exp-map}
 \Phi_g\colon
 (\barB^{(g)}_{\mathrm{hol}}, \Dg{g})
 \;\xrightarrow{\;\sim\;}
 (\barB^{(g)}_{\mathrm{Ar}}, \dfib),
\end{equation}
defined in
Construction~\textup{\ref{constr:chiral-exp-map}} below. This map
is a morphism of coalgebras \textup{(}it preserves the coproduct
$\Delta$\textup{)} and satisfies
$\Phi_g \circ \Dg{g} = \dfib \circ \Phi_g$. Here the
quasi-isomorphism is understood in the appropriate sense: on the left,
in the derived category of dg coalgebras; on the right, in the
coderived category of curved dg coalgebras.
\end{theorem}

%%----------------------------------------------------------------------
\subsection{The chiral exponential map}
\label{subsec:chiral-exp-map}
%%----------------------------------------------------------------------

\begin{construction}[The chiral exponential map $\Phi_g$]
\label{constr:chiral-exp-map}
\index{chiral exponential map|textbf}
The map $\Phi_g$ is the gauge transformation that replaces the
holomorphic propagator by the Arakelov propagator in all bar
operations. On a bar element of degree~$n$:
\begin{equation}\label{eq:Phi-g-explicit}
 \Phi_g\bigl([s^{-1}a_1 \,|\, \cdots \,|\, s^{-1}a_n]\bigr)
 \;=\;
 \sum_{\Gamma \in \mathsf{Graph}(n)}
 \int_{\FM_n(\Sigma_g)}
 \Biggl(
 \prod_{e = (i,j) \in E(\Gamma)}
 K^{(g)}_{\mathrm{Ar}}(z_i, z_j)
 \Biggr)
 \cdot
 \Biggl(
 \prod_{v \in V(\Gamma)}
 c_v(\cA)
 \Biggr),
\end{equation}
where:
\begin{itemize}
\item $\mathsf{Graph}(n)$ is the set of (connected and disconnected)
 graphs on the vertex set $\{1,\ldots,n\}$, where each vertex~$v$
 carries a chiral algebra element~$a_v$ and each edge~$e = (i,j)$
 carries a propagator.
\item $c_v(\cA)$ denotes the OPE coefficient at the vertex~$v$
 (the structure constants of the chiral product at the collision
 point).
\item The integral is over the Fulton--MacPherson compactification
 $\FM_n(\Sigma_g)$, ensuring convergence at collision boundaries.
\item The sum over $\Gamma$ is finite at each degree~$n$ (bounded by
 the number of graphs on $n$ vertices).
\end{itemize}
At degree $n = 1$: $\Phi_g([s^{-1}a]) = [s^{-1}a]$ (the identity;
there is only the empty graph on one vertex, which contributes the
identity map).

At degree $n = 2$: $\Phi_g$ is the gauge transformation that sends
$[s^{-1}a_1 | s^{-1}a_2]$ to the same bar element but with every
occurrence of the holomorphic propagator $K^{(g)}(z_1,z_2)$ replaced
by $K^{(g)}_{\mathrm{Ar}}(z_1,z_2)$. The difference is the
Arakelov correction:
\begin{equation}\label{eq:Phi-g-correction}
 \Phi_g - \id
 \;=\;
 \sum_{\Gamma \text{ with } \geq 1 \text{ edges}}
 (\text{integrals of Arakelov corrections over } \FM_n),
\end{equation}
and this difference is a homotopy (see the proof of
Theorem~\ref{thm:chiral-RH} below).
\end{construction}

%%----------------------------------------------------------------------
\subsection{Proof of the chiral Riemann--Hilbert quasi-isomorphism}
\label{subsec:chiral-RH-proof}
%%----------------------------------------------------------------------

\begin{proof}[Proof of Theorem~\textup{\ref{thm:chiral-RH}}]
The holomorphic and Arakelov propagators differ by the Arakelov
correction:
\begin{equation}\label{eq:propagator-difference}
 K^{(g)}_{\mathrm{Ar}}(z,w) - K^{(g)}(z,w)
 \;=\;
 \pi \sum_{\alpha,\beta=1}^g
 \omega_\alpha(z)\,
 (\operatorname{Im}\tau)^{-1}_{\alpha\beta}\,
 \operatorname{Im}\Bigl(\int_w^z \omega_\beta\Bigr)
 \;=:\;
 R^{(g)}(z,w).
\end{equation}
The correction $R^{(g)}(z,w)$ is a smooth one-form on
$\Sigma_g \times \Sigma_g$ (no poles) and satisfies:
\begin{equation}\label{eq:correction-dbar}
 \bar\partial_z R^{(g)}(z,w)
 \;=\;
 +\omega_{\mathrm{Ar}}(z).
\end{equation}
% Resolved: the sign +omega_Ar follows from eq:dbar-arakelov
% (dbar Im(f) = (i/2) omega-bar, giving coefficient pi*i/2 = +omega_Ar).
Since $R^{(g)}$ is smooth, it defines a bounded operator on the bar
complex (it does not create new poles at collision boundaries of
$\FM_n(\Sigma_g)$).

\smallskip\noindent
\textbf{Step~1: $\Phi_g$ intertwines the differentials.}
We verify $\Phi_g \circ \Dg{g} = \dfib \circ \Phi_g$.
The holomorphic differential $\Dg{g}$ is a coderivation of the
tensor coalgebra ($\Dg{g}^{\,2} = 0$), determined by its
cogenerator projection using $K^{(g)}$ at each binary operation.
The Arakelov differential $\dfib$ is \emph{not} a strict
coderivation at $g \geq 1$ ($\dfib^{\,2} = \kappa \cdot \omega_g
\neq 0$), but its cogenerator projection, using
$K^{(g)}_{\mathrm{Ar}}$, has the same combinatorial structure.
The map $\Phi_g$ replaces every propagator insertion by the Arakelov
version. Since the Arakelov and holomorphic propagators have the
\emph{same} singular part (the pole $1/(z{-}w)$ is unchanged; the
correction $R^{(g)}$ is smooth), the intertwining
$\Phi_g \circ \Dg{g} = \dfib \circ \Phi_g$ follows because
the structure maps (OPE residues) are unchanged by the
smooth gauge transformation; only the propagators on internal
edges change.

\smallskip\noindent
\textbf{Step~2: $\Phi_g$ is a quasi-isomorphism.}
We construct a homotopy inverse. Define $\Psi_g$ by the same
formula as~$\Phi_g$ but with $K^{(g)}_{\mathrm{Ar}}$ replaced by
$K^{(g)}$ (the reverse gauge transformation). Then
$\Psi_g \circ \Phi_g = \id + [\dfib, h]$, where the homotopy $h$
involves integration of the correction $R^{(g)}$ over one fewer
edge. Explicitly:
\begin{equation}\label{eq:homotopy}
 (\Psi_g \circ \Phi_g - \id)
 \bigl([s^{-1}a_1|\cdots|s^{-1}a_n]\bigr)
 \;=\;
 \sum_{\Gamma \text{ with } \geq 1 \text{ edge}}
 \int_{\FM_n(\Sigma_g)}
 \Bigl(\prod_{e \in E(\Gamma)} R^{(g)}_{e}\Bigr)
 \cdot
 \prod_v c_v,
\end{equation}
which vanishes at degree~$1$ (no edges on one vertex) and is
$\bar\partial$-exact at higher degrees by \eqref{eq:correction-dbar}:
each factor $R^{(g)}(z_i,z_j)$ satisfies
$\bar\partial_{z_i} R^{(g)} = +\omega_{\mathrm{Ar}}$, and by
Stokes' theorem on $\FM_n(\Sigma_g)$ the integral of the
$\bar\partial$-exact form is a boundary term. The boundary
contributions are the lower-degree operations, precisely the
homotopy $[\dfib, h]$. Therefore $\Psi_g \circ \Phi_g$ is
chain-homotopic to the identity. By symmetry, $\Phi_g \circ \Psi_g$
is likewise chain-homotopic to the identity.

\smallskip\noindent
\textbf{Step~3: Category interpretation.}
On the left (holomorphic model), $(\barB^{(g)}_{\mathrm{hol}},\Dg{g})$
is an honest dg coalgebra ($\Dg{g}^{\,2} = 0$) and lives in the
derived category $\mathsf{D}(\barB\text{-}\mathsf{comod})$. On the
right (Arakelov model), $(\barB^{(g)}_{\mathrm{Ar}}, \dfib)$ is a
curved dg coalgebra ($\dfib^{\,2} = \kappa \cdot \omega_g$) and
lives in the coderived category
$\mathsf{D}^{\mathrm{co}}(\barB\text{-}\mathsf{comod})$. The map
$\Phi_g$ is a quasi-isomorphism in the derived-coderived sense:
it is a morphism whose cone is coacyclic (acyclic with respect to
the coderived structure). This is the content of the
later flat-derived / curved-coderived comparison, made explicit
through the gauge transformation $\Phi_g$; Theorem~\ref{thm:factorization-SC-koszul}(iv)
provides only the categorical placement of the two sides.
\end{proof}

%%----------------------------------------------------------------------
\subsection{Explicit computation of $\Phi_1$ for the Heisenberg
at degree~$2$}
\label{subsec:Phi-1-heisenberg}
%%----------------------------------------------------------------------

\begin{computation}[Chiral exponential map $\Phi_1$ at degree~$2$
for the Heisenberg]
\label{comp:Phi-1-heisenberg}
\index{chiral exponential map!Heisenberg at degree 2}
\ClaimStatusProvedHere{}
Let $\cA = \cH_\kappa$ and $g = 1$. At degree~$2$, the bar element
is $\xi = [s^{-1}a \,|\, s^{-1}b]$. There are two graphs on
vertex set $\{1,2\}$: the empty graph (no edges) and the complete
graph $K_2$ (one edge connecting vertices $1$ and $2$).

\smallskip\noindent
\textbf{Empty graph.} Contributes $\id(\xi) = [s^{-1}a \,|\, s^{-1}b]$
(no propagator insertion).

\smallskip\noindent
\textbf{One-edge graph $K_2$.} The single edge $(1,2)$ carries the
correction $R^{(1)}(z_1,z_2)$. The OPE coefficient at the collapse
$z_1 \to z_2$ is $c_{12} = \kappa$ (the Heisenberg singular OPE
coefficient). The contribution is:
\begin{align}\label{eq:Phi-1-K2}
 \Phi_1^{K_2}(\xi)
 &\;=\;
 \int_{\FM_2(\Sigma_1)}
 R^{(1)}(z_1,z_2) \cdot \kappa \cdot
 [s^{-1}(a \cdot b)(z_2)]
 \notag\\[3pt]
 &\;=\;
 \kappa \cdot
 \biggl[
 \int_{\FM_2(\Sigma_1)}
 \frac{\pi}{\operatorname{Im}\tau}\,
 \operatorname{Im}(z_1-z_2)
 \biggr]
 \cdot s^{-1}(a \cdot b).
\end{align}
The integral
$\int_{\FM_2(\Sigma_1)} \frac{\pi}{\operatorname{Im}\tau}\,
\operatorname{Im}(z_1-z_2)$ is regularised by the FM compactification.
On the blowup of the diagonal, the correction $R^{(1)}(z_1,z_2)$
is smooth and the integral converges. The value is determined by
the symmetry $z_1 \leftrightarrow z_2$: since
$R^{(1)}(z_1,z_2) = -R^{(1)}(z_2,z_1)$ (the correction is
antisymmetric), and the measure on $\FM_2(\Sigma_1)$ is symmetric
in the two points, the integral vanishes:
\begin{equation}\label{eq:Phi-1-K2-vanishes}
 \int_{\FM_2(\Sigma_1)}
 R^{(1)}(z_1,z_2) = 0.
\end{equation}

Therefore, at degree~$2$:
\begin{equation}\label{eq:Phi-1-degree-2}
 \Phi_1\bigl([s^{-1}a \,|\, s^{-1}b]\bigr)
 \;=\;
 [s^{-1}a \,|\, s^{-1}b].
\end{equation}
The chiral exponential map is the identity at degree~$2$ for the
Heisenberg algebra at genus~$1$. This is consistent with the fact
that the Heisenberg algebra is commutative (the normal-ordered
product is commutative), so the gauge transformation that replaces
holomorphic by Arakelov propagators does not modify the bar elements
at low degree; the curvature is carried entirely by the
\emph{differential}, not by the \emph{elements}. The first
non-trivial correction from $\Phi_1$ appears at degree~$3$ and
higher, where graphs with two or more edges contribute
non-symmetrically.
\end{computation}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Positselski machine for curved bar complexes}
\label{sec:positselski-machine}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecommand{\Dco}{\mathsf{D}^{\mathrm{co}}}
\providecommand{\Dctr}{\mathsf{D}^{\mathrm{ctr}}}
\providecommand{\Hot}{\mathsf{Hot}}
\providecommand{\Acyclco}{\mathsf{Acycl}^{\mathrm{co}}}

The genus-$g$ bar complex with $\dfib^{\,2} = \kappa \cdot \omega_g
\neq 0$ is a \emph{curved} dg coalgebra. The ordinary derived
category of such an object is trivial on the current claim surface:
the manuscript's bar-complex acyclicity result
\textup{(}the acyclicity proposition in Volume~I's curved bar-cobar
chapter\textup{)}
shows that the underlying curved bar complex is acyclic when
$\kappa \neq 0$.
Positselski's theory of coderived and contraderived categories
\cite{Pos11} resolves this triviality by enlarging the class of
acyclic objects. This section applies Positselski's framework to
our setting, producing the curved co-contra comparison at genus~$g$.

%%----------------------------------------------------------------------
\subsection{Coderived and contraderived categories}
\label{subsec:coderived-contraderived}
%%----------------------------------------------------------------------

\begin{construction}[Positselski's categorical framework]
\label{constr:positselski-framework}
\index{Positselski!coderived category|textbf}
\index{Positselski!contraderived category|textbf}
Let $(C, d_C, \kappa_C)$ be a curved dg coalgebra over a field~$k$
of characteristic~$0$: a graded coalgebra~$C$ equipped with a
coderivation $d_C$ of degree~$+1$ satisfying
$d_C^2 = \kappa_C \cdot \id_C$ for a \emph{curvature element}
$\kappa_C \in k$ (more generally,
$\kappa_C \in C^2$ satisfying $d_C(\kappa_C) = 0$).

\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Coderived category.}
The \emph{coderived category} of $C$-comodules is
\begin{equation}\label{eq:coderived-def}
 \Dco(C\text{-}\mathsf{comod})
 \;:=\;
 \Hot(C\text{-}\mathsf{comod}) \,/\, \Acyclco,
\end{equation}
where $\Hot(C\text{-}\mathsf{comod})$ is the homotopy category of
$C$-comodules (morphisms up to chain homotopy) and $\Acyclco$ is
the thick subcategory of \emph{coacyclic} objects: those comodules~$M$
that can be obtained as totalizations of short exact sequences of
comodules. Concretely, $M$ is coacyclic if there exists a short
exact sequence of $C$-comodules
$0 \to M' \to M'' \to M''' \to 0$
whose totalization is $M$ (the notion is the comodule analogue of
contractibility, but adapted to the curved setting where the
ordinary notion of acyclicity is trivial).

\item \textbf{Contraderived category.}
Dually, for a curved dg algebra $(A, d_A, \kappa_A)$ with
$d_A^2 = \kappa_A$, the \emph{contraderived category} of
$A$-contramodules is
\begin{equation}\label{eq:contraderived-def}
 \Dctr(A\text{-}\mathsf{contra})
 \;:=\;
 \Hot(A\text{-}\mathsf{contra}) \,/\, \mathsf{Acycl}^{\mathrm{ctr}},
\end{equation}
where $\mathsf{Acycl}^{\mathrm{ctr}}$ consists of
\emph{contraacyclic} objects (obtained from products of short exact
sequences, rather than coproducts as in the coderived case).

\item \textbf{Why ordinary derived methods fail in the curved case.}
If $\kappa_C \neq 0$, ordinary cohomological derived methods are no
longer the right invariant for the curved theory. On the
higher-genus bar-complex surfaces relevant in this monograph, the
underlying curved bar complexes are acyclic on the ordinary
cochain-complex surface \textup{(}by the acyclicity proposition in
Volume~I's curved bar-cobar chapter\textup{)}, while the coderived
category remains nontrivial. The coderived category avoids this
collapse by using a weaker equivalence relation adapted to the
curved setting.
\end{enumerate}
\end{construction}

\begin{remark}[Why comodules and contramodules, not modules]
\label{rem:comod-vs-mod}
\index{Positselski!comodules vs modules}
For coalgebras, the correct linear-algebraic notion is
\emph{comodules} (not modules): a $C$-comodule~$M$ is a graded
vector space with a coaction $\delta\colon M \to C \otimes M$
compatible with the comultiplication and coderivation. The bar
complex $\barB(\cA)$ is a coalgebra (with coproduct $\Delta$ from
deconcatenation), so its representations are comodules. The Koszul
dual $\cA^!$ is an algebra (obtained by Verdier duality on $\barB(\cA)$), and its
representations are \emph{contramodules}: graded vector spaces~$P$
with a contraaction $\pi\colon \operatorname{Hom}(A, P) \to P$
satisfying associativity and unit constraints. Contramodules are
\emph{not} the same as modules in general (they differ for
infinite-dimensional algebras, which is the relevant case here);
the distinction is essential for the Koszul duality equivalence to
hold.
\end{remark}

%%----------------------------------------------------------------------
\subsection{Application to the genus-$g$ bar complex}
\label{subsec:positselski-application}
%%----------------------------------------------------------------------

\begin{theorem}[Curved co-contra duality at genus~$g$]
\label{thm:curved-koszul-genus-g}
\index{curved Koszul duality!genus $g$|textbf}
\ClaimStatusProvedHere{}
Let $\cA$ be a chiral algebra with modular characteristic
$\kappa = \kappa(\cA) \neq 0$ whose genus-$g$ bar coalgebra has
finite-dimensional graded pieces, and let
$\barB^{(g)}(\cA) = (\barB^{(g)}_{\mathrm{Ar}}, \dfib,
\kappa \cdot \omega_g)$ be the curved bar complex at genus~$g$
\textup{(}the Arakelov model of
Corollary~\textup{\ref{cor:three-models-from-fact}(iii))}.

\begin{enumerate}[label=\textup{(\roman*)}]
\item The curved bar complex $\barB^{(g)}(\cA)$ is a curved dg
 coalgebra in Positselski's sense:
 \begin{itemize}
 \item The underlying graded coalgebra is
 $T^c(s^{-1}\bar\cA)$ with deconcatenation coproduct;
 \item The coderivation is $\dfib$, of degree~$+1$;
 \item The scalar curvature datum is
 $\kappa \cdot \omega_g$, and the structural relation is
 $\dfib^{\,2} = \kappa \cdot \omega_g \cdot \id$.
 \end{itemize}
 On this surface, that is the curved-coalgebra structure
 proved. Maurer--Cartan equations for deformations live in the
 associated coderivation/convolution deformation algebra, not in
 the bar coalgebra itself.

\item \textbf{Completed-dual co-contra correspondence.}
 The completed linear dual algebra
 $\barB^{(g)}(\cA)^\vee = \operatorname{Hom}_k(\barB^{(g)}(\cA), k)$
 inherits the dual curved dg-algebra structure. Positselski's
 coderived/contraderived comparison then gives an equivalence
 between:
 \begin{equation}\label{eq:curved-koszul-equivalence}
 \Dco\bigl(\barB^{(g)}(\cA)\text{-}\mathsf{comod}\bigr)
 \;\simeq\;
 \Dctr\bigl(\barB^{(g)}(\cA)^\vee\text{-}\mathsf{contra}\bigr).
 \end{equation}
 This is the curved co-contra duality attached to the genus-$g$
 bar coalgebra. A further identification of
 $\barB^{(g)}(\cA)^\vee$ with a curved completion of $\cA^!$
 requires extra comparison hypotheses
 \textup{(}for example sectorwise finiteness on the
 factorization-Positselski lane\textup{)} and is not part of the
 present theorem.

\item The equivalence \eqref{eq:curved-koszul-equivalence} is
 compatible with the genus tower at the level of the bar coalgebra
 and its completed dual: the genus-raising clutching map
 $\Delta_{\mathrm{cyc}}\colon \barB^{(g)} \to \barB^{(g+1)}$
 of Construction~\textup{\ref{constr:nonsep-clutching}} dualizes to
 a morphism of completed dual algebras
 \[
 \barB^{(g+1)}(\cA)^\vee \longrightarrow \barB^{(g)}(\cA)^\vee.
 \]
 Thus the stagewise co-contra correspondence of~\textup{(}ii\textup{)}
 propagates uniformly along the genus tower.
 This theorem does not claim a stronger all-genus identification
 with plain~$\cA^!$ or a separate global functoriality statement
 beyond these stagewise dual maps.
\end{enumerate}
\end{theorem}

\begin{proof}
\textbf{Part (i)} is a verification of the curved-coalgebra axioms
relevant here. The
graded coalgebra $T^c(s^{-1}\bar\cA)$ with deconcatenation
coproduct is conilpotent (the coaugmentation filtration is
exhaustive: $F_n = \bigoplus_{k \leq n} (s^{-1}\bar\cA)^{\otimes k}$
satisfies $\bigcup_n F_n = T^c$). The coderivation $\dfib$ has
degree~$+1$ and satisfies $\dfib^{\,2} = \kappa \cdot \omega_g$
(the curvature identity proved in
Computation~\ref{comp:dfib-sq-heisenberg-genus1} for the
Heisenberg case and in general by
Construction~\ref{constr:bar-fact-coalgebra}(iv)). This is the
scalar-curvature curved dg coalgebra structure used below.

\smallskip\noindent
\textbf{Part (ii).} This is the main content. The proof has
two ingredients:

\smallskip\noindent
\emph{Ingredient~1: Positselski's comodule-contramodule
correspondence.}
Positselski \cite{Pos11}, Theorem~5.3 (see also
\emph{op.\ cit.}, Theorems~0.2.6 and~6.5), establishes:
for a conilpotent curved dg coalgebra~$C$ over a field of
characteristic~$0$ whose graded pieces are finite-dimensional,
there is an equivalence
\[
 \Dco(C\text{-}\mathsf{comod})
 \;\simeq\;
 \Dctr(C^\vee\text{-}\mathsf{contra}),
\]
where $C^\vee = \operatorname{Hom}_k(C, k)$ is the linear dual,
equipped with the dual algebra structure and the dual curvature.
The conilpotency of~$C$ is essential: it ensures that the cobar
construction $\Omegach(C)$ is well-defined (the infinite sum in
the cobar differential converges in the conilpotent filtration).

\smallskip\noindent
\emph{Ingredient~2: The completed dual algebra present here.}
The linear dual of the bar complex $\barB^{(g)}(\cA) =
T^c(s^{-1}\bar\cA)$ is the completed tensor algebra
$\barB^{(g)}(\cA)^\vee = \widehat{T}(s\,\bar\cA^\vee)$
(the product-dual of the coproduct-coalgebra). This completed
algebra carries the dual differential and the same scalar
curvature datum $\kappa \cdot \omega_g$. It is the algebra that
appears on the contraderived side of Positselski's theorem. A
further comparison with a curved completion of the genus-$0$
Koszul dual algebra~$\cA^!$ is a separate input: on the
manuscript's factorization-Positselski lane it requires the extra
sectorwise-finiteness hypotheses recorded in the Yangian/DK
factorization Positselski theorem, and it is not used in the
present genus-$g$ theorem.

Combining the two ingredients:
\[
 \Dco\bigl(\barB^{(g)}(\cA)\text{-}\mathsf{comod}\bigr)
 \;\simeq\;
 \Dctr\bigl(\barB^{(g)}(\cA)^\vee\text{-}\mathsf{contra}\bigr),
\]
which is exactly \eqref{eq:curved-koszul-equivalence}.

\smallskip\noindent
\textbf{Part (iii).} The compatibility with the genus tower
is the stagewise compatibility stated in the theorem. The
non-separating clutching map
$\Delta_{\mathrm{cyc}}\colon \barB^{(g)} \to \barB^{(g+1)}$
is the genus-raising coalgebra map of
Construction~\ref{constr:nonsep-clutching}. Dualizing gives a
morphism of completed dual algebras
$\barB^{(g+1)}(\cA)^\vee \to \barB^{(g)}(\cA)^\vee$. Thus the
coderived/contraderived comparison of part~(ii) may be applied
uniformly at each genus stage, without claiming any stronger
all-genus identification with plain~$\cA^!$.
\end{proof}

%%----------------------------------------------------------------------
\subsection{The Heisenberg at genus~$1$: the Weyl algebra}
\label{subsec:heisenberg-weyl}
%%----------------------------------------------------------------------

\begin{example}[Curved Koszul duality for the Heisenberg at genus~$1$]
\label{ex:heisenberg-curved-koszul}
\index{Heisenberg algebra!curved Koszul duality at genus 1}
\index{Weyl algebra!as curved Koszul dual}
\ClaimStatusProvedHere{}
The Heisenberg chiral algebra $\cH_\kappa$ at genus~$0$ is formal:
$\barB(\cH_\kappa)$ has $d_{\barB} = 0$
(Example~\ref{ex:heisenberg-bar-3}), and the Koszul dual is the
polynomial algebra $\cH_\kappa^! = k[x]$ (the free commutative
algebra on one generator, i.e.\ the Koszul dual of the free Lie
coalgebra on one cogenerator).

At genus~$1$, the bar complex inherits curved differential
$\dfib^{\,2} = \kappa \cdot \omega_1$ from the annular trace
composed with clutching
\textup{(}Computation~\ref{comp:dfib-sq-heisenberg-genus1}\textup{)}.
Its completed dual algebra $\barB^{(1)}(\cH_\kappa)^\vee$ is the
curved completion of the genus-$0$ Koszul dual polynomial algebra
$k[x]$. This completed dual algebra is presented as follows.

\smallskip\noindent
\textbf{The Weyl algebra from curvature.}
The genus-$0$ Koszul dual $\cH_\kappa^! = k[x]$ is commutative. The
curvature $\kappa \cdot \omega_1$ deforms the commutative product:
the curved differential $d$ satisfies $d^2 = \kappa$
(writing $\kappa$ for $\kappa \cdot \omega_1$ with the $(1,1)$-form
absorbed into the differential-form coefficient). This means the
Koszul dual at genus~$1$ is no longer commutative but
\emph{filtered}: the associated graded is $k[x]$, and the curvature
forces $[d, x] \neq 0$. Concretely, introduce a second generator
$\partial$ as the image of $d$ acting on the cogenerator, subject to:
\begin{equation}\label{eq:weyl-from-curvature}
 [\partial, x] = \kappa.
\end{equation}
This is the \emph{Weyl algebra} $\cW_\kappa = k\langle x,
\partial\rangle / ([\partial, x] = \kappa)$. The identification is:
\begin{equation}\label{eq:curved-koszul-heisenberg}
 \Dctr\bigl(\barB^{(1)}(\cH_\kappa)^\vee\text{-}\mathsf{contra}\bigr)
 \;\simeq\;
 \mathsf{D}(\cW_\kappa\text{-}\mathsf{mod}),
\end{equation}
the derived category of modules over the Weyl algebra. The
equivalence holds because the contraderived category of a
curved algebra with invertible curvature agrees with the
ordinary derived category of the ``resolved'' (uncurved) algebra
obtained by adjoining the curvature relation
(Positselski \cite{Pos11}, Theorem~3.6).

\smallskip\noindent
\textbf{The full equivalence.}
Combining with
Theorem~\ref{thm:curved-koszul-genus-g}(ii):
\begin{equation}\label{eq:heisenberg-genus-1-full}
 \boxed{
 \Dco\bigl(\barB^{(1)}(\cH_\kappa)\text{-}\mathsf{comod}\bigr)
 \;\simeq\;
 \mathsf{D}(\cW_\kappa\text{-}\mathsf{mod}).
 }
\end{equation}
The coderived category of the genus-$1$ Heisenberg bar complex is
equivalent to the derived category of Weyl algebra modules. This
is the simplest instance of curved Koszul duality.

\smallskip\noindent
\textbf{Interpretation.}
The Weyl algebra governs the quantum mechanics of a single
harmonic oscillator: $x$ is the position operator,
$\partial = \kappa^{-1}\partial_x$ is the rescaled momentum
operator, and $[\partial, x] = \kappa$ is the canonical
commutation relation at level~$\kappa$. The equivalence
\eqref{eq:heisenberg-genus-1-full} is therefore a precise algebraic
statement: the genus-$1$ curved bar complex of the free boson
chiral algebra ``is'' the quantum mechanics of a harmonic
oscillator, in the sense that their derived/coderived categories
of representations are equivalent. The curvature
$\kappa \cdot \omega_1$ (the failure of $d^2 = 0$, the obstruction
to formality at genus~$1$) is the \emph{source} of the
non-commutativity of the Weyl algebra: it is the canonical
commutation relation, viewed from the coalgebra side.
\end{example}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The pentagon of equivalences for $\SCchtop$}
\label{sec:SC-pentagon}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The operad $\SCchtop$ admits five redundant presentations, and every
equivalence between adjacent presentations must be proved to close the
pentagon.  This section catalogues the five presentations, records
which equivalences are proved in the preceding sections, and supplies
the missing edges.

\subsection{The five presentations}
\label{subsec:pentagon-five}

Fix a logarithmic $\SCchtop$-algebra~$\cA$
(Definition~\ref{def:log-SC-algebra}).  The following five descriptions
of the $\SCchtop$-structure on (or associated to) $\cA$ are developed
in the present volume:

\medskip
\begin{enumerate}[label=\textbf{(P\arabic*)}]
\item \textbf{Operadic.}\label{P:operadic}
 The two-coloured topological operad $\SCchtop$
 (Definition~\ref{def:SC-operations}), generated by the
 codimension-$1$ boundary strata of
 $\FM_k(\C) \times \Conf_m^{<}(\R)$ with relations from
 codimension-$2$ strata
 (Proposition~\ref{prop:sc-generators-relations}).
 An $\SCchtop$-algebra is a pair
 $(\cA_{\mathsf{cl}}, \cA_{\mathsf{op}})$ with structure maps
 indexed by $\FM_k(\C) \times E_1(m)$.

\item \textbf{Koszul dual.}\label{P:koszul}
 The homotopy-Koszulity of $\SCchtop$
 (Theorem~\ref{thm:homotopy-Koszul}): the counit
 $\Omega\mathbf{B}(\SCchtop) \xrightarrow{\sim} \SCchtop$
 is a quasi-isomorphism.  The Boardman--Vogt resolution
 $W(\SCchtop) = \Omega\mathbf{B}(\SCchtop)$ is the cofibrant
 replacement.  The Koszul dual cooperad is
 $(\SCchtop)^! = (\mathsf{Lie}^c, \mathsf{Ass}^c,
 \text{shuffle-mixed})$
 (Proposition~\ref{thm:SC-self-duality}).
 The bar-cobar duality functor is involutive on
 $\SCchtop$-algebras:
 $(\cA^!)^! \simeq \cA$
 (Theorem~\ref{thm:duality-involution}).

\item \textbf{Factorization.}\label{P:factorization}
 The chiral derived center
 $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA) :=
 C^\bullet_{\mathrm{ch}}(\cA,\cA)$
 carries an $E_2$-chiral structure via Tamarkin's theorem
 (Theorem~\ref{thm:tamarkin-higher-structure}), and the pair
 $\bigl(C^\bullet_{\mathrm{ch}}(\cA,\cA),\, \cA\bigr)$
 is the $\SCchtop$ datum: bulk acting on boundary via the
 universal brace
 (Proposition~\ref{prop:swiss-cheese-from-tamarkin},
 Theorem~\ref{thm:bulk-CHC}).

\item \textbf{BV/BRST.}\label{P:BV}
 The BV observable prefactorization algebra
 $U \mapsto \mathsf{Obs}(U)$ on $\C \times \R$ is a logarithmic
 $\SCchtop$-algebra (Theorem~\ref{thm:Obs-is-SC}), with the
 quantum master equation
 $\hbar\Delta_{\mathrm{BV}} S_{\mathrm{eff}}
 + \tfrac{1}{2}\{S_{\mathrm{eff}},
 S_{\mathrm{eff}}\}_{\mathrm{BV}} = 0$
 becoming the open/closed Maurer--Cartan equation in
 $C^\bullet_{\mathrm{ch,top}}(\cA)[1]$
 (Theorem~\ref{thm:MC-deformations}).

\item \textbf{Convolution.}\label{P:convolution}
 The Swiss-cheese convolution $L_\infty$-algebra
 $\gSC_T :=
 \Hom_{\Sigma}\bigl(\mathbf{B}(\SCchtop),\;
 \End_{(\cA_{\mathsf{cl}},\,\cA_{\mathsf{op}})}\bigr)$
 (Definition~\ref{def:sc-convolution}), with canonical
 Maurer--Cartan element $\alpha_T \in \mc(\gSC_T)$
 (Theorem~\ref{thm:3d-universal-mc}).
 The SC convolution algebra factors as
 $\mathfrak{g}_\cA^{\mathrm{SC}} \simeq
 \mathfrak{g}_\cA^{\mathrm{mod}} \times
 \mathfrak{g}_\cA^{\R}$
 (Remark~\ref{rem:sc-convolution-factorization}).
\end{enumerate}

\subsection{The pentagon: proved equivalences}
\label{subsec:pentagon-proved}

The five presentations are arranged cyclically as
\ref{P:operadic}--\ref{P:koszul}--\ref{P:factorization}--\ref{P:BV}--\ref{P:convolution}--\ref{P:operadic}.
The five edges and five diagonals of the resulting pentagon
provide ten pairwise equivalences. The following seven are proved
in the preceding chapters.

\medskip
\noindent\textbf{Edges:}
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{\ref{P:operadic}\,$\leftrightarrow$\,\ref{P:koszul}}
 (Operadic $\leftrightarrow$ Koszul dual).
 Theorem~\ref{thm:homotopy-Koszul}: the bar-cobar counit
 $\Omega\mathbf{B}(\SCchtop) \xrightarrow{\sim} \SCchtop$
 is a quasi-isomorphism. This identifies $\SCchtop$-algebras
 with $\Omega\mathbf{B}(\SCchtop)$-algebras.
 \emph{Status: proved}
 (Theorem~\ref{thm:homotopy-Koszul};
 Chapter~\ref{ch:line-operators}).

\item \textbf{\ref{P:koszul}\,$\leftrightarrow$\,\ref{P:factorization}}
 (Koszul dual $\leftrightarrow$ Factorization).
 Theorem~\ref{thm:factorization-SC-koszul}: the bar construction
 produces a factorization coalgebra, and at genus~$0$ the cobar
 recovers the original algebra; at all genera the Feynman
 transform is involutive.
 \emph{Status: proved}
 (Theorem~\ref{thm:factorization-SC-koszul};
 \S\ref{sec:factorization-koszul-duality}).

\item \textbf{\ref{P:factorization}\,$\leftrightarrow$\,\ref{P:BV}}
 (Factorization $\leftrightarrow$ BV/BRST).
 Theorem~\ref{thm:bulk-CHC}: the chiral Hochschild cochains
 (factorization presentation) are quasi-isomorphic to the BV
 bulk observables.
 \emph{Status: proved}
 (Theorem~\ref{thm:bulk-CHC};
 \S\ref{sec:chiral_hochschild}).

\item \textbf{\ref{P:BV}\,$\leftrightarrow$\,\ref{P:convolution}}
 (BV/BRST $\leftrightarrow$ Convolution).
 Theorem~\ref{thm:MC-deformations}: deformations of~$\cA$
 as a $W(\SCchtop)$-algebra are classified by MC elements in
 the convolution $L_\infty$-algebra
 $\gSC_T = \Hom_\Sigma(\mathbf{B}(\SCchtop), \End_\cA)$.
 The QME of the BV theory becomes the MC equation in $\gSC_T$.
 \emph{Status: proved}
 (Theorem~\ref{thm:MC-deformations};
 \S\ref{sec:chiral_hochschild}).
\end{enumerate}

\noindent\textbf{Diagonals:}
\begin{enumerate}[label=\textup{(\roman*)},resume]
\item \textbf{\ref{P:operadic}\,$\leftrightarrow$\,\ref{P:factorization}}
 (Operadic $\leftrightarrow$ Factorization).
 Theorem~\ref{thm:BD-CG-equivalence}: the BD (algebraic), CG
 (differential-geometric), and local-model (operadic)
 descriptions produce equivalent categories.
 \emph{Status: proved}
 (Theorem~\ref{thm:BD-CG-equivalence};
 \S\ref{sec:BD-CG-equivalence}).

\item \textbf{\ref{P:operadic}\,$\leftrightarrow$\,\ref{P:BV}}
 (Operadic $\leftrightarrow$ BV/BRST).
 Theorem~\ref{thm:Obs-is-SC}: the BV observable prefactorization
 algebra is a logarithmic $\SCchtop$-algebra.
 \emph{Status: proved}
 (Theorem~\ref{thm:Obs-is-SC};
 \S\ref{sec:BV_construction}).

\item \textbf{\ref{P:koszul}\,$\leftrightarrow$\,\ref{P:convolution}}
 (Koszul dual $\leftrightarrow$ Convolution).
 The convolution $L_\infty$-algebra $\gSC_T$ is defined as
 $\Hom_\Sigma(\mathbf{B}(\SCchtop), \End_\cA)$, so its
 $L_\infty$-brackets are the transferred brackets from the
 Koszul-dual cooperad $\mathbf{B}(\SCchtop)$.  Strictification
 of this $L_\infty$-algebra via the bar-cobar resolution gives
 back the convolution dg~Lie algebra.  This identification is
 the definition of the convolution algebra and is tautological.
 \emph{Status: proved by construction}
 (Definition~\ref{def:sc-convolution}).
\end{enumerate}

\subsection{Missing equivalences: the three remaining edges}
\label{subsec:pentagon-missing}

Three pairwise equivalences remain to close the pentagon.
These are the ``diagonal'' edges
\ref{P:convolution}\,$\leftrightarrow$\,\ref{P:operadic},
\ref{P:koszul}\,$\leftrightarrow$\,\ref{P:BV},
and
\ref{P:factorization}\,$\leftrightarrow$\,\ref{P:convolution}.
We state each as a proposition (when the tools for a proof exist in
the preceding sections) or a conjecture (when additional input is
needed).

\begin{proposition}[Convolution $\leftrightarrow$ Operadic:
recognition from MC data;
\ClaimStatusProvedHere]
\label{prop:pentagon-convolution-operadic}
\index{pentagon of equivalences!convolution to operadic}
Let\/ $\cA$ be a logarithmic\/ $\SCchtop$-algebra
\textup{(}Definition~\textup{\ref{def:log-SC-algebra})}.
The following data are equivalent:
\begin{enumerate}[label=\textup{(\alph*)}]
\item An $\SCchtop$-algebra structure on the pair\/
 $(\cA_{\mathsf{cl}}, \cA_{\mathsf{op}})$, i.e.\ a morphism
 of two-coloured operads\/
 $\SCchtop \to \End_{(\cA_{\mathsf{cl}},\,\cA_{\mathsf{op}})}$.
\item A Maurer--Cartan element\/
 $\alpha \in \mc(\gSC_T)$ in the Swiss-cheese convolution
 $L_\infty$-algebra of
 Definition~\textup{\ref{def:sc-convolution}}.
\end{enumerate}
The correspondence sends an $\SCchtop$-algebra structure to the
twisting morphism\/
$\tau \colon \mathbf{B}(\SCchtop) \to
\End_{(\cA_{\mathsf{cl}},\,\cA_{\mathsf{op}})}$
determined by the algebra structure maps; this twisting morphism
is an MC element in $\gSC_T$ by definition.  Conversely, an MC
element\/~$\alpha$ in $\gSC_T$ determines a morphism
$\Omega\mathbf{B}(\SCchtop) \to
\End_{(\cA_{\mathsf{cl}},\,\cA_{\mathsf{op}})}$
via the bar-cobar adjunction, and
homotopy-Koszulity
\textup{(}Theorem~\textup{\ref{thm:homotopy-Koszul})}
lifts this to a genuine $\SCchtop$-algebra structure.
\end{proposition}

\begin{proof}
The bar-cobar adjunction for coloured operads establishes a
bijection between twisting morphisms
$\tau\colon \mathbf{B}(\cP) \to \cQ$ and operad maps
$\Omega\mathbf{B}(\cP) \to \cQ$
(Loday--Vallette \cite{LV12}, Theorem~11.3.3). Specialising
to $\cP = \SCchtop$ and
$\cQ = \End_{(\cA_{\mathsf{cl}}, \cA_{\mathsf{op}})}$:
a twisting morphism $\tau$ is precisely an MC element in
$\gSC_T = \Hom_\Sigma(\mathbf{B}(\SCchtop), \End_\cA)$
(by the definition of the convolution $L_\infty$-structure
on $\Hom_\Sigma$; see \cite{LV12}, \S11.1).

In the forward direction, an $\SCchtop$-algebra structure
is a strict operad map $\SCchtop \to \End_\cA$.
Composing with the universal twisting morphism
$\iota\colon \mathbf{B}(\SCchtop) \to \SCchtop$ gives a
twisting morphism
$\tau = \iota \circ \alpha\colon \mathbf{B}(\SCchtop) \to
\End_\cA$, i.e.\ an MC element in $\gSC_T$.

In the reverse direction, an MC element
$\alpha \in \mc(\gSC_T)$ is a twisting morphism
$\tau_\alpha\colon \mathbf{B}(\SCchtop) \to \End_\cA$,
which by the bar-cobar adjunction corresponds to a dg operad map
$\Omega\mathbf{B}(\SCchtop) \to \End_\cA$.
The counit
$\epsilon\colon \Omega\mathbf{B}(\SCchtop) \xrightarrow{\sim}
\SCchtop$ is a quasi-isomorphism by
Theorem~\ref{thm:homotopy-Koszul}. Since $\End_\cA$ is
fibrant in the model structure on two-coloured dg operads
(its underlying chain complex has no acyclicity conditions),
the lifting property of the cofibrant replacement
$\Omega\mathbf{B}(\SCchtop)$ produces an $\SCchtop$-algebra
map, unique up to homotopy.

The two constructions are inverse up to homotopy: given an
$\SCchtop$-algebra, the round trip produces a
$W(\SCchtop)$-algebra quasi-isomorphic to the original; given
an MC element, the round trip produces a gauge-equivalent MC
element. Strictification from $W(\SCchtop)$ to $\SCchtop$ is
provided by the homological perturbation lemma
(transfer along the quasi-isomorphism $\epsilon$).
\end{proof}

\begin{proposition}[Koszul dual $\leftrightarrow$ BV/BRST:
bar-cobar resolution of observables;
\ClaimStatusProvedHere]
\label{prop:pentagon-koszul-bv}
\index{pentagon of equivalences!Koszul dual to BV/BRST}
Let\/ $\cA$ be the BV-BRST complex of a $3$d HT theory satisfying the
hypotheses of Theorem~\textup{\ref{thm:physics-bridge}}.
Then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The Koszul dual\/ $\cA^!_{\mathrm{line}}$ of
 the boundary algebra \textup{(}the open-colour Koszul dual\textup{)} is a
 $(\mathsf{Lie},\mathsf{Ass})$-algebra, and the bar complex\/
 $\barB^{\mathrm{ord}}(\cA)$ is the BV-BRST complex of the Koszul dual
 theory on the dual boundary.
\item The bar-cobar resolution\/
 $\Omega\barB^{\mathrm{ord}}(\cA) \xrightarrow{\sim} \cA$
 is the cofibrant replacement of~$\cA$ as an $\SCchtop$-algebra:
 the cobar of the bar is a quasi-isomorphic $W(\SCchtop)$-algebra
 that serves as the BV homotopy equivalence recovering the
 original theory from its bar complex.
\item The MC equation $d\alpha + \frac{1}{2}[\alpha,\alpha] = 0$
 in\/ $C^\bullet_{\mathrm{ch,top}}(\cA)[1]$ is the quantum master
 equation of the BV theory, and the bar differential\/
 $d_{\barB}$ on\/ $\barB^{\mathrm{ord}}(\cA)$ is the
 Koszul-dual presentation of the same data.
\end{enumerate}
\end{proposition}

\begin{proof}
Part~(a) follows by composing three proved results.
Theorem~\ref{thm:Obs-is-SC} identifies
$\cA$ as a logarithmic $\SCchtop$-algebra.
The two-colour Koszul duality
(Proposition~\ref{thm:SC-self-duality}) sends
$\SCchtop$-algebras to
$(\SCchtop)^!$-algebras, with open colour
$\mathsf{Ass}^! = \mathsf{Ass}$ and closed colour
$\mathsf{Com}^! = \mathsf{Lie}$, so the Koszul dual
$\cA^!_{\mathrm{line}}$ is a
$(\mathsf{Lie},\mathsf{Ass})$-algebra.
The bar complex $\barB^{\mathrm{ord}}(\cA)$ is the
$E_1$-coassociative coalgebra whose linear dual (on the
chirally Koszul locus) is $\cA^!_{\mathrm{line}}$.
This coalgebra encodes the same BV data as the original
theory, expressed in the Koszul-dual variables.

Part~(b) is the factorization Koszul duality at genus~$0$
(Theorem~\ref{thm:factorization-SC-koszul}(ii)):
$\Omega\barB(F)|_{g=0} \simeq F$, specialised to the
BV prefactorization algebra $F = \mathsf{Obs}$.

Part~(c) follows from Theorem~\ref{thm:MC-deformations},
which identifies the QME with the MC equation in
$C^\bullet_{\mathrm{ch,top}}(\cA)[1]$, together with the
standard identification of the bar differential as the
coderivation dual to the MC element
(the bar differential encodes the $A_\infty$ operations
$\{m_k\}$, which are the components of the MC element
$\alpha_T$; the MC equation
$d\alpha + \frac{1}{2}[\alpha,\alpha] = 0$ is equivalent to
$d_{\barB}^2 = 0$).
\end{proof}

\begin{conjecture}[Factorization $\leftrightarrow$ Convolution:
universal brace as convolution product]
\label{conj:pentagon-factorization-convolution}
\index{pentagon of equivalences!factorization to convolution}
Let\/ $\cA$ be a logarithmic\/ $\SCchtop$-algebra.
There is a canonical quasi-isomorphism of dg~Lie algebras
\begin{equation}\label{eq:brace-convolution-qiso}
 \bigl(C^\bullet_{\mathrm{ch,top}}(\cA,\cA)[1],\;
 [{-},{-}]_G\bigr)
 \;\xrightarrow{\;\sim\;}
 \bigl(\gSC_T,\;
 [{-},{-}]_{L_\infty}\bigr),
\end{equation}
identifying the Gerstenhaber bracket on chiral Hochschild
cochains \textup{(}the brace model of
Proposition~\textup{\ref{prop:geometric-braces-well-defined})}
with the $L_\infty$ bracket on the Swiss-cheese convolution algebra
\textup{(}Definition~\textup{\ref{def:sc-convolution})}.
Under this identification:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The brace operations
 $\{{-}\}\{{-},\ldots,{-}\}$ on chiral Hochschild cochains
 correspond to the higher $L_\infty$ brackets $\ell_n$ on
 $\gSC_T$ indexed by two-coloured trees.
\item The Tamarkin $E_2$-structure on
 $C^\bullet_{\mathrm{ch}}(\cA,\cA)$
 \textup{(}Theorem~\textup{\ref{thm:tamarkin-higher-structure})}
 coincides with the $E_2$-structure on the closed-sector
 component of $\gSC_T$, via the decomposition
 $\gSC_T \simeq \mathfrak{g}_\cA^{\mathrm{mod}} \times
 \mathfrak{g}_\cA^{\R}$
 \textup{(}Remark~\textup{\ref{rem:sc-convolution-factorization})}.
\item The universal MC element $\alpha_T$
 \textup{(}Theorem~\textup{\ref{thm:3d-universal-mc})}
 corresponds to the MC element classifying the
 $W(\SCchtop)$-deformation of~$\cA$
 \textup{(}Theorem~\textup{\ref{thm:MC-deformations})}.
\end{enumerate}
\end{conjecture}

\begin{remark}[Evidence for
Conjecture~\ref{conj:pentagon-factorization-convolution}]
\label{rem:pentagon-fc-evidence}
\index{pentagon of equivalences!evidence for P3-P5}
Three independent lines of evidence support
Conjecture~\ref{conj:pentagon-factorization-convolution}.

\textit{First}, on the associated graded with respect to the
holomorphic weight filtration, both sides decompose as tensor
products of a closed-sector (chiral) and an open-sector
(topological) piece; the equivalence on
$\mathrm{gr}^F$ reduces to the classical brace-convolution
correspondence of Getzler--Jones \cite{GJ94} applied separately
to $\FM_k(\C)$ and $E_1(m)$.

\textit{Second}, at the level of MC elements, parts~(a)--(c)
are verified for the Heisenberg algebra
(Computation~\ref{comp:tamarkin-e2-heisenberg}) and for
$\widehat{\mathfrak{sl}}_2$
(Computation~\ref{comp:tamarkin-e2-sl2}): in both cases, the
MC element in the convolution algebra equals the MC element
in the brace complex under the identification
$C^\bullet_{\mathrm{ch,top}}(\cA)[1] \cong \gSC_T$.

\textit{Third}, the quasi-isomorphism
\eqref{eq:brace-convolution-qiso} is an instance of the
general operadic cochain comparison: for a Koszul operad $\cP$,
the brace complex
$C^\bullet_\cP(A) := \Hom(\cP^{\text{\textexclamdown}}, \End_A)$
is quasi-isomorphic to the convolution $L_\infty$-algebra
$\Hom_\Sigma(\mathbf{B}(\cP), \End_A)$ by the Koszul
resolution $\cP^{\text{\textexclamdown}} \hookrightarrow
\mathbf{B}(\cP)$ (Loday--Vallette
\cite{LV12}, Theorem~10.1.13). The only obstruction to
applying this directly is the two-coloured nature of
$\SCchtop$: the Koszul resolution of the two-coloured operad
must intertwine the mixed operations correctly. The single-colour
case is standard; the extension to two colours requires a
systematic treatment of mixed-degree Koszul resolutions.
\end{remark}

\subsection{Pentagon closure and redundancy}
\label{subsec:pentagon-closure}

\begin{theorem}[Pentagon closure; \ClaimStatusProvedHere]
\label{thm:pentagon-closure}
\index{pentagon of equivalences!closure|textbf}
\index{Swiss-cheese operad!pentagon of equivalences|textbf}
Every pair of presentations
$(\mathrm{P}i, \mathrm{P}j)$ with $1 \le i < j \le 5$ is
connected by at least one proved equivalence, obtained either
directly or by composing at most two proved equivalences.
Each property of the $\SCchtop$-structure is therefore
verified from at least two independent angles.
\end{theorem}

\begin{proof}
The seven proved equivalences of
\S\ref{subsec:pentagon-proved}
connect all ten pairs via paths of length at most~$2$.
Explicitly:

\smallskip\noindent
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Pair} & \textbf{Direct} & \textbf{Composite (length 2)} \\
\midrule
P1--P2 & (i) & --- \\
P2--P3 & (ii) & --- \\
P3--P4 & (iii) & --- \\
P4--P5 & (iv) & --- \\
P1--P3 & (v) & (i)+(ii) \\
P1--P4 & (vi) & (v)+(iii) \\
P2--P5 & (vii) & (i)+Prop.~\ref{prop:pentagon-convolution-operadic} \\
P5--P1 & Prop.~\ref{prop:pentagon-convolution-operadic} & (iv)+(vi) \\
P2--P4 & Prop.~\ref{prop:pentagon-koszul-bv} & (ii)+(iii) \\
P3--P5 & Conj.~\ref{conj:pentagon-factorization-convolution} & (iii)+(iv) \\
\bottomrule
\end{tabular}
\end{center}

\smallskip\noindent
The ``Composite'' column shows that even the pair P3--P5
(the single conjectural direct link) is covered by the
composite (iii)+(iv):
$\text{P3} \xrightarrow{\text{(iii)}} \text{P4}
\xrightarrow{\text{(iv)}} \text{P5}$.
Hence every pair has at least one proved path of length
$\le 2$, and the pentagon is closed.

For the redundancy claim: each of the five proved edges
(i)--(iv) and Prop.~\ref{prop:pentagon-convolution-operadic}
has an alternative verification via a composite of other
proved equivalences.  For example, edge~(i)
(Operadic $\leftrightarrow$ Koszul) is independently confirmed by
composing (v) and (ii):
$\text{P1} \xrightarrow{\text{(v)}} \text{P3}
\xrightarrow{\text{(ii)}^{-1}} \text{P2}$.
The diagonal (v) (Operadic $\leftrightarrow$ Factorization) is
independently confirmed by composing (i) and (ii).
Thus every property is verified from at least two independent
angles.
\end{proof}

\begin{remark}[Status of the full pentagon]
\label{rem:pentagon-status}
Nine of the ten pairwise equivalences are proved (seven directly,
two via Propositions~\ref{prop:pentagon-convolution-operadic}
and~\ref{prop:pentagon-koszul-bv}).  The tenth
(Conjecture~\ref{conj:pentagon-factorization-convolution}:
Factorization $\leftrightarrow$ Convolution as a direct
quasi-isomorphism of dg~Lie algebras) is the only remaining
open problem.  It is covered by the composite path
P3 $\to$ P4 $\to$ P5, so the pentagon closes without it;
its resolution would provide the final direct link and complete
many-fold redundancy for all ten pairs.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Synthesis: the five presentations and their equivalences}
\label{subsec:pentagon-synthesis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Table~\ref{tab:five-presentations} collects the five
presentations of the $\SCchtop$-structure developed in this
chapter, together with their defining data, output structure,
and the theorems establishing each.

\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{1.25}
\small
\begin{tabular}{@{}clll@{}}
\toprule
& \textbf{Presentation} & \textbf{Defining data} & \textbf{Key theorem} \\
\midrule
\ref{P:operadic}
& Operadic
& \parbox[t]{5.2cm}{Two-coloured operad $\SCchtop$;
  generators from codim-$1$ strata of
  $\FM_k(\C) \times \Conf_m^{<}(\R)$,
  relations from codim-$2$}
& Prop.~\ref{prop:sc-generators-relations}
\\[4pt]
\ref{P:koszul}
& Koszul dual
& \parbox[t]{5.2cm}{Cooperad $(\SCchtop)^! =
  (\mathsf{Lie}^c, \mathsf{Ass}^c, \text{shuffle-mixed})$;
  cofibrant replacement
  $W(\SCchtop) = \Omega\mathbf{B}(\SCchtop)$}
& Thm.~\ref{thm:homotopy-Koszul},
  Prop.~\ref{thm:SC-self-duality}
\\[4pt]
\ref{P:factorization}
& Factorization
& \parbox[t]{5.2cm}{Chiral derived center
  $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)
  = C^\bullet_{\mathrm{ch}}(\cA,\cA)$
  with $E_2$-chiral structure;
  pair $(Z^{\mathrm{der}}_{\mathrm{ch}}(\cA),\, \cA)$
  is the SC datum}
& Thm.~\ref{thm:tamarkin-higher-structure},
  Thm.~\ref{thm:bulk-CHC}
\\[4pt]
\ref{P:BV}
& BV/BRST
& \parbox[t]{5.2cm}{Observable prefactorization algebra
  $\mathsf{Obs}(U)$ on $\C \times \R$;
  QME $=$ open/closed MC equation
  in $C^\bullet_{\mathrm{ch,top}}(\cA)[1]$}
& Thm.~\ref{thm:Obs-is-SC},
  Thm.~\ref{thm:MC-deformations}
\\[4pt]
\ref{P:convolution}
& Convolution
& \parbox[t]{5.2cm}{$L_\infty$-algebra
  $\gSC_T = \Hom_\Sigma(\mathbf{B}(\SCchtop),
  \End_\cA)$;
  canonical MC element $\alpha_T \in \mc(\gSC_T)$}
& Def.~\ref{def:sc-convolution},
  Thm.~\ref{thm:3d-universal-mc}
\\
\bottomrule
\end{tabular}
\caption{The five presentations of the $\SCchtop$-structure
  on a logarithmic $\SCchtop$-algebra~$\cA$.}
\label{tab:five-presentations}
\end{table}

\begin{proposition}[Star topology through the operadic hub;
\ClaimStatusProvedHere]
\label{prop:star-topology}
\index{pentagon of equivalences!star topology}
Every pairwise equivalence among the five presentations
factors through the operadic presentation~\textup{\ref{P:operadic}}
via a path of length at most~$2$ consisting entirely of
proved equivalences.
Explicitly, the four spokes of the star are:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \textup{\ref{P:operadic}}$\,\leftrightarrow\,$\textup{\ref{P:koszul}}:
  homotopy-Koszulity
  \textup{(}Theorem~\textup{\ref{thm:homotopy-Koszul})}.
\item \textup{\ref{P:operadic}}$\,\leftrightarrow\,$\textup{\ref{P:factorization}}:
  BD--CG equivalence
  \textup{(}Theorem~\textup{\ref{thm:BD-CG-equivalence})}.
\item \textup{\ref{P:operadic}}$\,\leftrightarrow\,$\textup{\ref{P:BV}}:
  BV recognition
  \textup{(}Theorem~\textup{\ref{thm:Obs-is-SC})}.
\item \textup{\ref{P:operadic}}$\,\leftrightarrow\,$\textup{\ref{P:convolution}}:
  MC recognition
  \textup{(}Proposition~\textup{\ref{prop:pentagon-convolution-operadic})}.
\end{enumerate}
Any equivalence
$\textup{P}i \leftrightarrow \textup{P}j$ with
$i,j \ne 1$ is obtained by composing spoke~$(i)^{-1}$
with spoke~$(j)$.
\end{proposition}

\begin{proof}
Each spoke is proved in the sections cited.
For a non-hub pair $(\mathrm{P}i, \mathrm{P}j)$ with
$i, j \ne 1$, the composite
$\mathrm{P}i \xrightarrow{\text{spoke}(i)^{-1}}
\mathrm{P1} \xrightarrow{\text{spoke}(j)} \mathrm{P}j$
is a path of length~$2$ through proved equivalences.
This covers all $\binom{4}{2} = 6$ non-hub pairs, and the
four spokes cover the remaining four hub pairs,
exhausting all $\binom{5}{2} = 10$.
\end{proof}

The star topology through~\ref{P:operadic} suffices for all
logical dependencies. The direct edges between non-hub
presentations (proved in~\S\ref{subsec:pentagon-proved}
and~\S\ref{subsec:pentagon-missing}) provide independent
verification: each property of the $\SCchtop$-structure
is confirmed from at least two routes.

\begin{remark}[The three conjectural direct links]
\label{rem:conjectural-direct-links}
\index{pentagon of equivalences!conjectural links}
Three direct links between non-hub presentations carry
independent mathematical content beyond the star-composite
paths. Each would establish a structural identification
not visible from the operadic hub alone.

\textit{(1) Koszul $\leftrightarrow$ BV/BRST}
(Proposition~\ref{prop:pentagon-koszul-bv}).
The bar complex $\barB^{\mathrm{ord}}(\cA)$ directly
encodes the BV-BRST data of the Koszul dual theory.
Independent content: the bar differential $d_{\barB}$ is
the Koszul-dual presentation of the quantum master equation;
the cobar $\Omega\barB^{\mathrm{ord}}(\cA)$ recovers the
original BV theory without passing through the operadic
description. This link is proved.

\textit{(2) BV/BRST $\leftrightarrow$ Convolution.}
The QME of the BV theory equals the MC equation in the
convolution $L_\infty$-algebra $\gSC_T$
(Theorem~\ref{thm:MC-deformations}).
Independent content: the BV antibracket and the
$L_\infty$ brackets on $\gSC_T$ are related by an explicit
formula involving the BV Laplacian $\Delta_{\mathrm{BV}}$
and the homotopy transfer data from
$\mathbf{B}(\SCchtop)$. This link is proved.

\textit{(3) Factorization $\leftrightarrow$ Convolution}
(Conjecture~\ref{conj:pentagon-factorization-convolution}).
The Gerstenhaber bracket on chiral Hochschild cochains
should be quasi-isomorphic to the $L_\infty$ bracket on
$\gSC_T$.
Independent content: this would identify the
brace operations on
$C^\bullet_{\mathrm{ch}}(\cA,\cA)$ with the higher
$L_\infty$ operations indexed by two-coloured trees, without
appealing to the operadic or BV descriptions. The
obstruction is the two-coloured Koszul resolution
intertwining mixed operations
(Remark~\ref{rem:pentagon-fc-evidence}).
This is the sole remaining open problem.
\end{remark}

\begin{remark}[$\SCchtop$ is the generic case;
$E_3$-topological is the special case]
\label{rem:sc-generic-e3-special}
\index{Swiss-cheese operad!generic vs.\ $E_3$}
\index{topologization!conformal vector requirement}
The operad $\SCchtop$ is two-coloured with inherent
directionality: bulk-to-boundary operations exist, but
open-to-closed operations are empty. Dunn additivity
does not apply to coloured operads, so $\SCchtop$ is
\emph{not} equivalent to $E_3$.

The passage $\SCchtop \to E_3$ requires an inner conformal
vector: a Virasoro element $T(z) \in \cA$ at non-critical
level such that $\C$-translations become $Q$-exact
(Sugawara construction). When $T(z) = \{Q, G(z)\}$,
the complex structure on $\C$ becomes cohomologically
trivial, the two colours of $\SCchtop$ collapse, and
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ acquires a genuine
$E_3$-topological algebra structure independent of the
complex structure on~$\C$
(Theorem~\ref{thm:topologization} in
Chapter~\ref{ch:en-koszul}).

$\SCchtop$ is therefore the \emph{generic} structure on the
derived chiral center pair
$(Z^{\mathrm{der}}_{\mathrm{ch}}(\cA), \cA)$; the
$E_3$-topological structure is the \emph{special} case
obtained by quotienting out the holomorphic direction.
Algebras without conformal vector are confined to
$\SCchtop$:

\smallskip
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Hypothesis} & \textbf{Structure on}
$\boldsymbol{(Z^{\mathrm{der}}_{\mathrm{ch}}(\cA),\,\cA)}$ \\
\midrule
No conformal vector
& $\SCchtop$ (two-coloured, holomorphic-dependent) \\
Conformal vector at non-critical level
& $E_3$-topological (one-coloured, holomorphic-independent) \\
Critical level $k = -h^\vee$
& Sugawara undefined; stuck at $\SCchtop$ \\
\bottomrule
\end{tabular}
\end{center}

\smallskip\noindent
Examples confined to $\SCchtop$:
$E_1$-chiral algebras (Yangians), any algebra at critical
level $k = -h^\vee$, and Calabi--Yau functor outputs lacking
conformal vectors.
In each case, the five presentations of
Table~\ref{tab:five-presentations} and the pentagon of
equivalences apply in full; the absence of a conformal vector
obstructs only the final collapse to $E_3$.
(The Heisenberg algebra $H_k$ at $k \ne 0$ and lattice vertex
algebras do \emph{not} belong to this list: the abelian Sugawara
$T = \frac{1}{2k}{:}JJ{:}$ provides a conformal vector of
central charge $c = 1$, and abelian holomorphic Chern--Simons
provides the $3$d HT theory, so they reach $E_3$-topological.)
\end{remark}

\begin{theorem}[Pentagon of equivalences for $\SCchtop$;
\ClaimStatusProvedHere]
\label{thm:five-presentations-equivalence}
\index{pentagon of equivalences!main theorem|textbf}
\index{Swiss-cheese operad!five presentations equivalence|textbf}
The five presentations of\/ $\SCchtop$
\textup{(}operadic, Koszul dual, factorization, BV/BRST,
convolution; \S\textup{\ref{subsec:pentagon-five})}
are pairwise equivalent.
Specifically:
\begin{enumerate}[label=\textup{(\alph*)}]
\item All equivalences factor through the operadic hub
 \textup{(}Presentation~\ref{P:operadic}\textup{)}.  Each of the
 remaining four presentations is connected to the operadic
 presentation by a direct, proved equivalence:
 \begin{center}
 \renewcommand{\arraystretch}{1.15}
 \begin{tabular}{@{}ll@{}}
 \toprule
 \textbf{Link} & \textbf{Source} \\
 \midrule
 \ref{P:operadic}\,$\leftrightarrow$\,\ref{P:koszul}
   & Theorem~\textup{\ref{thm:homotopy-Koszul}}
   \textup{(}bar-cobar counit\textup{)} \\
 \ref{P:operadic}\,$\leftrightarrow$\,\ref{P:factorization}
   & Theorem~\textup{\ref{thm:BD-CG-equivalence}}
   \textup{(}BD--CG--local model\textup{)} \\
 \ref{P:operadic}\,$\leftrightarrow$\,\ref{P:BV}
   & Theorem~\textup{\ref{thm:Obs-is-SC}}
   \textup{(}BV observables are $\SCchtop$\textup{)} \\
 \ref{P:operadic}\,$\leftrightarrow$\,\ref{P:convolution}
   & Proposition~\textup{\ref{prop:pentagon-convolution-operadic}}
   \textup{(}MC recognition\textup{)} \\
 \bottomrule
 \end{tabular}
 \end{center}

\item The direct links
 \ref{P:koszul}\,$\leftrightarrow$\,\ref{P:factorization}
 \textup{(}Theorem~\textup{\ref{thm:factorization-SC-koszul})},
 \ref{P:factorization}\,$\leftrightarrow$\,\ref{P:BV}
 \textup{(}Theorem~\textup{\ref{thm:bulk-CHC})},
 \ref{P:BV}\,$\leftrightarrow$\,\ref{P:convolution}
 \textup{(}Theorem~\textup{\ref{thm:MC-deformations})},
 and
 \ref{P:koszul}\,$\leftrightarrow$\,\ref{P:BV}
 \textup{(}Proposition~\textup{\ref{prop:pentagon-koszul-bv})}
 carry independent mathematical content beyond what the operadic
 hub provides: they relate genuinely different structures
 \textup{(}Koszul cooperad, factorization coalgebra, BV
 observable algebra, $L_\infty$ convolution\textup{)} without
 passing through the operad itself.

\item Every pair of presentations is connected by at least one
 proved equivalence of composite length at most~$2$
 \textup{(}Theorem~\textup{\ref{thm:pentagon-closure}};
 Proposition~\textup{\ref{prop:star-topology})}.
 The single conjectural direct link
 \textup{(}\ref{P:factorization}\,$\leftrightarrow$\,\ref{P:convolution};
 Conjecture~\textup{\ref{conj:pentagon-factorization-convolution})}
 is circumvented by the composite path\/
 $\mathrm{P3} \to \mathrm{P4} \to \mathrm{P5}$.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(a) is Proposition~\ref{prop:star-topology}: the four spokes
of the star through~\ref{P:operadic} are all proved equivalences.
Part~(b) records the five non-hub direct links proved in
\S\ref{subsec:pentagon-proved} and \S\ref{subsec:pentagon-missing}.
Part~(c) combines Theorem~\ref{thm:pentagon-closure} with
Proposition~\ref{prop:star-topology}: the nine proved pairwise
equivalences (four spokes plus five non-hub direct links) cover all
ten pairs via paths of length at most~$2$, and the star structure
alone covers all ten pairs via paths of length at most~$2$.
\end{proof}

\begin{remark}[Star topology of the pentagon]
\label{rem:pentagon-star-topology}
\index{pentagon of equivalences!star topology}
The operadic presentation~\ref{P:operadic} serves as the hub of a
star graph: every other presentation connects to it by a single
proved equivalence. The remaining five direct links
\textup{(}four proved, one conjectural\textup{)} are the non-hub
edges and diagonals of the pentagon, providing redundancy. The star
topology reflects the operadic origin of the entire structure:
$\SCchtop$ is defined as a two-coloured topological operad, and each
alternative presentation is a theorem expressing the same operad in
a different language. The hub-and-spoke structure guarantees that any
property proved in one presentation transfers to all others through
at most two intermediate steps. The non-hub direct links carry
independent mathematical content
\textup{(}Remark~\textup{\ref{rem:conjectural-direct-links})}: the
Koszul--BV link identifies the bar differential with the quantum
master equation; the factorization--BV link identifies chiral
Hochschild cochains with BV observables; the BV--convolution link
identifies the QME with the MC equation in $\gSC_T$.
\end{remark}
