\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

\providecommand{\cH}{\mathcal{H}}
\providecommand{\fg}{\mathfrak{g}}
\providecommand{\Ydg}{Y^{\mathrm{dg}}}
\providecommand{\Zder}{\operatorname{Z}_{\mathrm{der}}}
\providecommand{\Abulk}{A_{\mathrm{bulk}}}
\providecommand{\Bbound}{B_{\partial}}
\providecommand{\dCrit}{\operatorname{dCrit}}
\providecommand{\RHom}{\operatorname{RHom}}
\providecommand{\Perf}{\operatorname{Perf}}
\providecommand{\cL}{\mathcal{L}}
\providecommand{\Tr}{\operatorname{Tr}}

Volume~I constructs $E_n$-chiral algebras on curves: the ordered
bar complex $B^{\mathrm{ord}}(\cA) = T^c(s^{-1}\bar\cA)$ with
deconcatenation coproduct; the derived chiral centre
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ carrying $E_2$/$E_3$
structure (Deligne); the $\SCchtop$ pair
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),\, \cA)$.
\[
 \text{Volume~II identification:} \quad
 \cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)
 \;=\;
 \text{bulk algebra of 3d HT QFT},
 \qquad
 (\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),\, \cA)
 \;=\;
 \text{boundary-bulk system},
 \qquad
 \text{$E_3$-topological algebra}
 \;=\;
 \text{TQFT}.
\]

\textbf{Paradigm case: three-dimensional gravity.}
Einstein gravity on AdS$_3$ with cosmological constant $\Lambda = -1/\ell^2$
\[
 \;=\; SL(2, \R) \times SL(2, \R)\ \text{Chern--Simons theory}
 \qquad
 (\text{Ach\'ucarro--Townsend, Witten})
\]
with Brown--Henneaux boundary symmetry algebra
$\mathrm{Vir}_c \otimes \overline{\mathrm{Vir}}_c$ at central
charge $c = 3\ell/(2G)$. Volume~I's modular Koszul duality of
$\mathrm{Vir}_c$ packages into
\[
 \Theta_{\mathrm{Vir}_c} \;\in\; \mathrm{MC}\bigl(B^{\mathrm{ord}}(\mathrm{Vir}_c)\bigr),
 \qquad
 \Theta_{\mathrm{Vir}_c}|_{\overline{\cM}_g}
 \;=\;
 \text{genus-$g$ perturbative partition function around empty AdS}_3.
\]
The shadow tower of $\Theta_{\mathrm{Vir}_c}$ classifies the
nonlinear complexity of the gravitational dynamics; its five
structural properties are the five main theorems of Volume~I.
\textbf{Volume~II identification.}
Primitive: open factorization dg-category $\cC$ on the
gravitational boundary. Bulk observables:
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA_b)$ for any chart
$A_b = \End_\cC(b)$. Line operators: modules over the Koszul dual.
Modularity: trace $+$ clutching on $\cC$.
Family substitution:
$\mathrm{Vir}_c \to \cW_N$ gives higher-spin gravity;
$\mathrm{Vir}_c \to \widehat{\mathfrak{g}}_k$ gives gauge theory.
The MC element, bar complex, and Swiss-cheese structure persist
uniformly.

\textbf{Mechanism: holomorphic-topological decomposition of
spacetime.}
On $\C_z \times \R_t$ the factorization structure splits into two
operations:
\[
 \underbrace{\FM_k(\C_z)}_{\text{holomorphic collisions}}
 \;\xrightarrow{\;d_{\barB}\;}\;
 \text{bar differential},
 \qquad
 \underbrace{\Conf_k(\R_t)}_{\text{topological splittings}}
 \;\xrightarrow{\;\Delta\;}\;
 \text{deconcatenation coproduct}.
\]
Together: $\barB(\cA)$ is a dg coassociative coalgebra with
$E_1$-chiral structure on $\C_z$ and symmetric deconcatenation on
$\R_t$. The $\SCchtop$ datum is the pair
$(C^\bullet_{\mathrm{ch}}(\cA, \cA),\, \cA)$ of bulk Hochschild
cochains acting on boundary algebra; this is the universal
$\SCchtop$-algebra.
The differential records which operators can collide; the coproduct
records which operators can be separated. Both together determine
the theory; neither alone does.

\medskip

\textbf{Primitive object: the open-sector factorization
dg-category}
\[
 \cC \in \mathrm{FactCat}(\widetilde{X}_D),
 \qquad
 \Ob(\cC) = \{\text{boundary conditions}\},
 \qquad
 \Hom_\cC(b, b') = \{\text{open-string states}\}
\]
on the bordified curve $\widetilde{X}_D$
(Definition~\ref{def:oc-factorization-category}).
\textbf{Chart construction.}
Each vacuum choice $b \in \cC$ produces
\[
 A_b := \End_\cC(b),
 \qquad
 \barB(A_b) \;=\; \text{coalgebraic shadow of closed-sector
 twisting of open-sector composition}.
\]
Differential of $\barB(A_b)$: $\FM_k(\C)$-parametrised (holomorphic
collisions). Coproduct: $\Conf_k(\R)$-parametrised (topological
splittings).
\textbf{Invariant.} Morita class of $\cC$, not the
quasi-isomorphism class of any chart $A_b$
(Theorem~\ref{thm:boundary-algebra-from-vacuum}).

\textbf{Primitive hierarchy.}
\[
\cC_{\mathrm{op}}
\;\xrightarrow{\;\End(b)\;}\;
A_b
\;\xrightarrow{\;\barB\;}\;
\barB(A_b)
\;\xrightarrow{\;\Theta\;}\;
\Theta_\cA
\;\xrightarrow{\;+\mu^{M_j}\;}\;
\Theta^{\mathrm{oc}}_\cA.
\]
Each arrow is lossy with a named kernel:
\begin{itemize}[leftmargin=1.8em,itemsep=0pt,topsep=0pt]
 \item $\End(b)$: Morita class preserved, chart $b$ forgotten.
 \item $\barB$: algebra $\to$ coalgebra; deconcatenation recovers $A_b$.
 \item $\Theta$: coalgebra $\to$ MC element on $\mathrm{MC}(\barB)$.
 \item $+\mu^{M_j}$: adjoins the module couplings on the five marked-point geometries $M_j$ of the $\SCchtop$ operad.
\end{itemize}
Volume~I constructs arrows 1--4 and proves the five theorems
governing them. Volume~II constructs arrow~5, identifies its 3d
output, and proves that $\Theta^{\mathrm{oc}}_\cA$ is the full
open/closed package: bulk algebra + boundary algebra + module
couplings + trace + clutching.

Three objects are independently constructed from~$\cC$. The
\emph{universal bulk} is the chiral derived center
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cC) =
\RHom_{\operatorname{Fun}(\cC,\cC)}(\operatorname{Id},
\operatorname{Id})$,
computed in any chart by chiral Hochschild cochains
$C^\bullet_{\mathrm{ch}}(A_b, A_b)$. The \emph{line-side/open-colour
Koszul dual algebra}~$A^!_{\mathrm{line}}$ is extracted from the
Verdier dual $D_{\Ran}(\barB(A_b)) \simeq \barB(A_b^!)$
(Theorem~A intertwining): the Verdier dual of the bar coalgebra is
the bar of the Koszul dual algebra, and on the Koszul locus its
cohomology recovers~$A^!_{\mathrm{line}}$. The \emph{twisting morphism
classifier} is the bar complex itself, $\barB(A_b)$, which
represents universal couplings between~$A_b$ and~$A_b^!$ via
Volume~I's Theorem~A (the bar-cobar adjunction and Verdier intertwining). These are three different objects produced by
three different functors, solving three different problems:
the bar complex is \emph{not} the bulk.

The bar complex carries a geometric interpretation as a formal-local
Koszul model for a Lagrangian self-intersection
$\cL \times_{\cM}^h \cL$ in a $(-2)$-shifted symplectic stack
$\cM$ (Theorem~\ref{thm:bar-is-self-intersection}). The
differential is the Koszul resolution of the diagonal, and the
coproduct is the groupoid diagonal of the self-intersection.
The chiral algebra determines a formal local bulk model: the
boundary fixes the shifted-cotangent side of the bulk
reconstruction (Theorem~\ref{thm:holographic-reconstruction}),
but recovering the actual formal neighborhood requires the
formal Darboux theorem for $(-2)$-shifted symplectic stacks.
The holographic principle, on this surface, is the Darboux
theorem.

\textbf{Invariants of the $(-2)$-shifted symplectic geometry.}

\textbf{Curvature of the Lagrangian embedding.}
$\kappa(\cA)$ controls the $d_{\barB}^2$ defect:
\[
 d_{\barB}^2 \;=\; \kappa(\cA) \cdot \omega_g
\]
unconditionally at $g = 1$ (Hodge class $\omega_1$), and on the
proved scalar higher-genus lane for all $g \ge 1$.

\textbf{Complementarity (Volume~I, Theorem~C).} The decomposition
\[
 Q_g(\cA) + Q_g(\cA^!) \;=\; H^*\bigl(\overline{\cM}_g, Z(\cA)\bigr)
\]
lifts to the bulk-boundary-line triangle as a Lagrangian splitting
of the self-intersection complex, under perfectness and chain-level
nondegeneracy hypotheses (all standard families satisfy these;
conditional in general).

\textbf{Three structure theorems from Volume~I.}
\begin{description}[leftmargin=1.6em,itemsep=2pt,topsep=1pt]
 \item[Algebraicity (Riccati).]
 $H(t)^2 = t^4\, Q_L(t)$ with $Q_L$ quadratic; the growth rate
 $\rho$ of the shadow obstruction tower determines convergence of
 the genus expansion.
 \item[Formality identification.] Shadow obstruction tower equals
 the $L_\infty$ formality obstruction tower at all degrees
 (proved by induction on $r$ in Volume~I); tower termination is
 $L_\infty$ formality.
 \item[Complementarity holomorphic-topological split.]
 The $(-1)$-shifted symplectic structure on the self-intersection
 complex $C_g(\cA)$ (inherited from the ambient $(-2)$-shifted
 stack) realises the Lagrangian decomposition
 $C_g(\cA) = Q_g(\cA) + Q_g(\cA^!)$.
\end{description}

\textbf{Shadow depth classification as bulk-boundary taxonomy.}
Critical discriminant $\Delta = 8\kappa S_4$:
\[
 \begin{array}{l|l|l}
 \text{class} & \Delta & \text{geometry} \\
 \hline
 \mathbf{G} & = 0 & \text{formal; bulk classical; self-intersection clean; $m_k = 0$ for $k \ge 3$} \\
 \mathbf{L},\ \mathbf{C},\ \mathbf{M} & \ne 0 & \text{curved; excess Tor on self-intersection; higher $\Ainf$ operations encode obstructions}
 \end{array}
\]

\textbf{Recovery.}
$A_b$ from the genus-$0$ closed data of $\Theta_\cA$; higher-genus
shadow data from descent through the shadow obstruction tower.

\section*{The differential: holomorphic factorisation}

\textbf{Bar as categorical logarithm.}
\[
 \eta_{ij} \;=\; d\log(z_i - z_j)
 \qquad\text{(integral kernel)},
 \qquad
 B(\cA \otimes \cA') \;\simeq\; B(\cA) \oplus B(\cA')
 \qquad\text{($\log(ab) = \log a + \log b$ categorified)}.
\]
The bar functor sends tensor products to direct sums. Volume~I's
five theorems are the five structural properties of this
logarithm: existence, invertibility, branch structure, leading
coefficient, coefficient ring. Volume~II reads the 3d output.

\begin{remark}[$E_1$ primacy]
\label{rem:vol2-e1-primacy}
The natural primitive of the algebraic engine is the $E_1$/ordered
story, not the modular/symmetric one.
The bar differential lives on \emph{ordered} configuration spaces
$\FM_k(\C)$; the deconcatenation coproduct preserves the linear
ordering on $\Conf_k(\R)$. The averaging map
$\mathrm{av}\colon \mathfrak{g}^{E_1}_\cA \to
\mathfrak{g}^{\mathrm{mod}}_\cA$ is the
$\Sigma_n$-coinvariant projection (tensor coalgebra $T^c \to$
symmetric coalgebra $\Sym^c$). Volume~I's Theorems~A--D$+$H are the
invariants that survive this projection: the modular characteristic
$\kappa(\cA)$ at degree~$2$
(equal to $\mathrm{av}(r(z))$ for abelian algebras,
$\mathrm{av}(r(z)) + \dim(\fg)/2$ for non-abelian Kac--Moody),
and the shadow
obstruction tower $(\Theta_\cA^{\le r})_{r \ge 2}$ at higher degrees.
Consequently, Part~\ref{part:e1-core} (ordered associative chiral Koszul duality,
dg-shifted factorization bridge, gravitational Yangian) is the
\emph{primary} layer of the theory; the remaining Parts describe the
modular/symmetric framework that is its $\mathrm{av}$-image.
See Volume~I, \S\textup{E$_1$ as primitive}
for the full statement.
\end{remark}

\begin{remark}[Dimensional reduction across the trilogy]
\label{rem:vol2-dimensional-reduction}
This volume operates at Level~2 of the dimensional reduction
hierarchy (Remark~\ref*{V1-rem:three-volume-dimensional-reduction}
of Volume~I): the 3d theory on $\C_z \times \R_t$, where the bar
differential is the holomorphic colour and the coproduct is the
topological colour.
\end{remark}

Let $\cA$ be a chiral algebra on a curve $X$ with OPE
$a(z)\,b(w) \sim \sum c_n(w)/(z-w)^{n+1}$. The bar complex
$\barB(\cA) = T^c(s^{-1}\bar\cA)$ has a differential $d_{\barB}$
built from OPE residues on $\FM_k(\C)$ (the Fulton--MacPherson compactification of $k$ labelled points in $\C$): on a degree-$2$ element,
\[
d_{\barB}[s^{-1}a \,|\, s^{-1}b]
\;=\;
\Res_{z_1 = z_2}\!\bigl[a(z_1)\,b(z_2)\cdot\eta_{12}\bigr],
\qquad
\eta_{12} = d\log(z_1 - z_2),
\]
the logarithmic propagator, the unique translation-invariant $1$-form with a simple pole along the collision diagonal.
The collision residue extracts all OPE modes weighted by the
logarithmic kernel; the $d\log$ form absorbs one pole order
. Higher bar degrees involve higher
collision strata of $\FM_n(\C)$. The identity $d_{\barB}^2 = 0$
at genus~$0$ is the Arnold relation on $\FM_3(\C)$. The
differential encodes holomorphic factorisation: it records how
operators collide in the $\C$-direction.

\section*{The coproduct: topological factorisation along $\R$}

The same bar complex carries a coassociative coproduct from
deconcatenation:
\begin{equation}\label{eq:intro-delta}
\Delta[s^{-1}a_1 \,|\, \cdots \,|\, s^{-1}a_n]
\;=\;
\sum_{i=0}^{n}
[s^{-1}a_1 \,|\, \cdots \,|\, s^{-1}a_i]
\;\otimes\;
[s^{-1}a_{i+1} \,|\, \cdots \,|\, s^{-1}a_n].
\end{equation}
This coproduct encodes topological factorisation along~$\R$.
Place $n$ fields at ordered positions $t_1 < \cdots < t_n$ on~$\R$ and choose a
cut point $t_i < t_* < t_{i+1}$. The fields on
$(-\infty, t_*)$ are $a_1, \ldots, a_i$; those on
$(t_*, +\infty)$ are $a_{i+1}, \ldots, a_n$. Observables on
each half-line depend only on the fields they contain. The value of $\Delta$ at $i$
records this factorisation.

The ordered configuration space $\Conf_n^<(\R) = \{t_1 < \cdots
< t_n\}$ is contractible (an open simplex), so the
$\Eone$-coalgebra structure on~$\Conf_n(\R)$ contracts to a strict
coassociative coproduct: deconcatenation. No higher homotopies
survive. The coproduct is the unique coassociative coproduct on
$T^c(s^{-1}\bar\cA)$, determined by the cogenerators.

\medskip\noindent\textbf{Verification on the Heisenberg.}\enspace
Take $\cA = \cH_k$, the Heisenberg algebra with generator $J$ and
OPE $J(z)\,J(w) \sim k/(z-w)^2$. The bar element $[s^{-1}J \,|\,
s^{-1}J]$ represents two operators at positions $(z_1, t_1)$ and
$(z_2, t_2)$ on $\C \times \R$ with $t_1 < t_2$. Apply $\Delta$:
\[
\Delta[s^{-1}J \,|\, s^{-1}J]
\;=\;
[\,] \otimes [s^{-1}J \,|\, s^{-1}J]
\;+\;
[s^{-1}J] \otimes [s^{-1}J]
\;+\;
[s^{-1}J \,|\, s^{-1}J] \otimes [\,].
\]
The three terms correspond to the three ways of cutting the
interval $[t_1, t_2]$: before $t_1$ (both fields on the right),
between $t_1$ and $t_2$ (one field on each side), and after $t_2$
(both fields on the left). The middle term
$[s^{-1}J] \otimes [s^{-1}J]$ is the factorisation of the two-field
observable into independent one-field observables on the two
half-lines, possible because the Heisenberg OPE is a double pole
with no simple-pole interaction: $J_{(0)}J = 0$.

Now apply the differential to the middle term:
$d_{\barB}([s^{-1}J]) = 0$ (no unary OPE), so the differential
commutes with the cut. The coderivation property
$\Delta \circ d_{\barB} = (d_{\barB} \otimes \id + \id \otimes
d_{\barB}) \circ \Delta$ is the algebraic statement that the
holomorphic collision $z_1 \to z_2$ is independent of the
topological cut $t_* \in (t_1, t_2)$: collisions in $\C$ commute
with cuts in $\R$.

\section*{The Swiss-cheese identification}

A bar element of degree $k$ lives on the two-coloured configuration space
\[
 \FM_k(\C) \times \Conf_k^<(\R):
 \qquad
 \underbrace{\FM_k(\C)}_{\text{differential}}
 \;\times\;
 \underbrace{\Conf_k^<(\R)}_{\text{coproduct}}.
\]
This product is the operation space of the two-coloured chiral-topological
Swiss-cheese operad $\SCchtop$
(\S\ref{sec:SC-operad-foundations}): closed colour $\FM_k(\C)$, open
colour $\Eone(m) = \Conf_m^<(\R)$, no open-to-closed operations.

\textbf{Result.} The bar complex $(\barB(\cA), d_{\barB}, \Delta)$ is
an $E_1$ chiral coassociative coalgebra
(Theorem~\ref{thm:rosetta-e1-coalgebra} for the Heisenberg;
Section~\ref{sec:foundations} in general). The $\SCchtop$ structure
lives not on $\barB(\cA)$ itself but on the chiral derived centre
pair $(C^\bullet_{\mathrm{ch}}(\cA, \cA),\, \cA)$: chiral Hochschild
cochains (defined via $\End^{\mathrm{ch}}_\cA$) act on the boundary
algebra through brace operations. The bar-cobar Quillen equivalence
\[
 \Omega^{\mathrm{ch}}\bigl(\barB(\cA)\bigr)
 \;\xrightarrow{\;\sim\;}\;
 \cA
\]
recovers $\cA$ from the convolution product on $\barB(\cA)$
(Theorem~\ref{thm:steinberg-presentation}). The
formal-local model for the derived self-intersection
$\cL_\cA \times_{\cM}^h \cL_\cA$ of the Lagrangian
$\cL_\cA$ in the shifted symplectic moduli stack~$\cM$ is the
object whose fundamental class is the MC element~$\alpha_T$;
each direct closed/open/mixed projection of~$\alpha_T$ extracts a
different convolution datum on this class. The direct faces are:
boundary $\Ainf$ operations, open-colour operations on the line
category, the PVA $\lambda$-bracket, the spectral $R$-matrix, the
mixed bulk-to-boundary map, and the genus tower. The corrected
bulk-boundary-line triangle is then assembled from these faces
together with the boundary-linear derived-center theorem and, on the
chirally Koszul locus, the line-module and chiral-Hochschild
identifications. For the
affine lineage, on the reduced evaluation comparison surface this
convolution yields the corresponding quantum-group line package:
$\cC_{\mathrm{line}}^{\mathrm{red}}|_{\mathrm{eval}} \simeq
\operatorname{Rep}_q(\fg)$ on evaluation modules, and the bar
complex computes the coloured Jones polynomial
(Theorem~\ref{thm:affine-monodromy-identification},
Corollary~\ref{cor:jones-polynomial}).
The product $\C \times \R$ decomposes
the self-intersection into two colours: the closed colour
from holomorphic collisions in~$\C$ (fibre direction), the
open colour from topological cuts in~$\R$ (base direction).
Open-to-closed operations are empty: representations
restrict from $G$ to $B$, not conversely. At genus
$g \geq 1$, the chiral $\Ainf$ structure acquires curvature
($\dfib^{\,2} = \kappa \cdot \omega_g$) but the $E_1$ coproduct
remains flat: it does not depend on the
genus of the curve
(Theorem~\ref{thm:topological-e1-rigidity}).

\textbf{Three bar complexes from two colours}
(see \S\ref{sec:bar_cobar}; master statement in
Theorem~\ref{thm:two-color-master}):
\[
 \begin{array}{l|l|l}
 \text{bar} & \text{content} & \text{Koszul dual} \\
 \hline
 \barB^{\mathrm{FG}}(\cA) & \text{zeroth-pole chiral Lie bracket only} & \text{chiral Lie dual} \\
 \barB^{\Sigma}(\cA) & \text{all OPE products, $\Sigma_n$-coinvariants (Vol I)} & \cA^! \\
 \barB^{\mathrm{ord}}(\cA) & \text{linear ordering from $\Conf_k^<(\R)$} & \cA^!_{\mathrm{line}}
 \end{array}
\]
The two-colour interplay $\barB^{\Sigma} \leftrightarrow \barB^{\mathrm{ord}}$
is developed in Part~\ref{part:e1-core}
(\S\ref{ch:ordered-associative-chiral-kd}).

\section*{The pole-order principle}
\label{sec:pole-order-principle}
\index{pole-order principle}

The $E_1$ chiral coassociative coalgebra on $\barB(\cA)$ exists for
every chiral algebra. Its complexity is controlled by a single
datum: the maximal pole order of the OPE.
\[
 \begin{array}{l|l|l|l|l}
 \text{class} & \text{OPE} & \text{algebra} & m_k \text{ profile} & \text{shadow depth} \\
 \hline
 \mathbf{G} & \text{double, central coeff.} & \text{Heisenberg} & m_k = 0\ \forall k \ge 3 & 2 \\
 \mathbf{L} & \text{double, non-central residues} & \text{affine Kac--Moody} & m_3 \ne 0,\ m_4 = 0\ \text{(coh.)} & 3 \\
 \mathbf{C} & \text{quartic, sparse content} & \beta\gamma\text{ system} & m_3, m_4 \ne 0,\ m_{k\ge 5} = 0\ \text{(coh.)} & 4 \\
 \mathbf{M} & \text{quartic}+,\ \text{rich content} & \text{Virasoro},\ \cW_N & m_k \ne 0\ \forall k \ge 3 & \infty \\
 \end{array}
\]

\textbf{Class $\mathbf{G}$ (Gaussian).}
$\Ainf$ structure trivial; bar complex formal.

\textbf{Class $\mathbf{L}$ (Lie).}
$m_3$ from Jacobi identity; $\Ainf$-formality on cohomology.

\textbf{Class $\mathbf{C}$ (contact).}
First nonlinear correction beyond Lie; finitely generated.

\textbf{Class $\mathbf{M}$ (mixed).}
The quartic pole (present in $T(z)T(w)$ for any algebra with
conformal vector; $\cW$-algebras reach order $2s$, but quartic from
Virasoro suffices) forces associator $A_3 \ne 0$. Borcherds identity
converts this to ternary cocycle $m_3$; each $m_k$ is an independent
cocycle controlled by the Kac determinant at conformal weight. The
shadow obstruction tower is infinite; the full perturbative
hierarchy of 3d quantum gravity unfolds.

The mechanism that manufactures the higher pole is
Drinfeld--Sokolov reduction. The Sugawara construction
$T(z) = \frac{1}{2(k+h^\vee)}\sum_a {:}J^a J^a{:}(z)$
builds a conformal vector from double-pole currents; the
double Wick contraction in the $T(z)T(w)$ OPE produces a
quartic pole proportional to $c = k\dim\fg/(k+h^\vee)$.
Algebraically, DS reduction is a BRST functor that
transports the finite $\Ainf$ tower of the affine algebra to
the infinite tower of the Virasoro quotient
(Theorem~\ref{thm:ds-hpl-transfer}): the class transport
$\mathbf{L} \to \mathbf{M}$ is manufactured, not postulated.

In this way, the pole order of the OPE stratifies the
landscape of chiral algebras into complexity classes, each
with its own shadow depth, its own gravitational interpretation,
and its own finiteness properties. The four classes (Gaussian,
$r_{\max} = 2$; Lie, $r_{\max} = 3$; contact,
$r_{\max} = 4$; mixed, $r_{\max} = \infty$) are
developed in full in
\S\ref{def:gravity-shadow-depth-class}.
The Heisenberg below illustrates class~G; affine
Kac--Moody illustrates class~L; the $\beta\gamma$ system
illustrates class~C; Virasoro illustrates class~M;
and the DS functor is the bridge between L and M.

The qualitative classification has a quantitative refinement.
Each $T$-dependent monomial in the degree-$n$ operation~$m_n$
carries a derivative weight~$w$ and a spectral depth~$d$,
constrained by the identity $w + d = n - 1$. A depth-$d$ term
requires a weight-$(n - 1 - d)$ field; when no such field exists,
that depth is structurally forbidden. Virasoro has no weight-$1$
primary, so depth~$n$ is absent from every~$m_n$: the shadow
tower has a permanent gap at $d_{\mathrm{gap}} = n$. For the
principal $\cW_N$ algebras, DS reduction shifts the lowest
generator weight and the gap migrates:
$d_{\mathrm{gap}}(\cW_N, n) = 2N + n - 4$. At $N = 2$ this
recovers $d_{\mathrm{gap}} = n$; as $N$ grows, the gap recedes
into deeper spectral territory. The full development is in
\S\ref{sec:3d-gravity}
(Theorem~\ref{thm:gap-migration}); the ordered-sector
refinement is in~\S\ref{ch:ordered-associative-chiral-kd}.

\medskip
The qualitative (GLCM) and quantitative (gap migration) classifications
have a common combinatorial source. The scalar shadow at odd
degree $k = 2r{+}1$ factors as
\[
 |s_r| \;=\; C_{r-1} \;\times\; \frac{(2r+1)!}{2},
\]
where $C_{r-1}$ is the $(r{-}1)$th Catalan number, counting planar
binary trees in the Stasheff associahedron recursion on
$\Conf_k(\R)$ (the topological $E_1$~colour), and $(2r{+}1)!$
is the product of $L_0$-eigenvalues of $\partial^w T$ on
$\FM_k(\C)$ (the holomorphic colour). The shadow coefficient
is the product of a topological count and a holomorphic weight,
one factor from each colour of the Swiss-cheese operad. The gap
migration arises because DS reduction changes the holomorphic
factor without touching the topological one: Catalan numbers
are universal, but conformal weights depend on the algebra.
The full development is in
\S\ref{sec:3d-gravity}
(Remark~\ref{rem:sesquilinearity-two-colour}).

What does all of this look like in the simplest possible case?

\section*{The Heisenberg}

The Heisenberg algebra $\cH_k$ has a single generator~$J$, a
single OPE
\[
J(z)\,J(w) \;\sim\; \frac{k}{(z-w)^2},
\]
and no composite fields. One generator, one pole order, no
composites: every step of the three-dimensional machine is
checkable by hand.

The bar complex is $\barB(\cH_k) = T^c(s^{-1}\C \cdot J)$, the
cofree tensor coalgebra on a single desuspended generator. Its
differential is the coderivation whose cogenerator projection in
degree~$2$ is
\[
m_2(J, J) \;=\; k \cdot \mathbf{1},
\]
the OPE residue, with all higher operations vanishing:
$m_{k \geq 3} = 0$, because the Heisenberg OPE has no higher
singularities and there are no composite fields to produce them.
The coproduct is deconcatenation. Together (differential from
$\FM_2(\C)$, coproduct from $\Conf_k(\R)$, no higher
interactions), the bar complex carries the structure of an $E_1$ dg coassociative coalgebra, and a
formal one: the $\R$-factorisation is exact.

Passing to cohomology extracts the classical shadow of the chain-level bar data:
on $H^\bullet(\cH_k, Q) = \C[J]$, the binary
operation~$m_2$ decomposes. Its regular part is a commutative
product; its singular part is a $\lambda$-bracket
(the $\lambda$-bracket encodes the singular OPE in generating-function form: $\{a {}_\lambda b\} = \sum_{n \ge 0} (a_{(n)} b)\, \lambda^{(n)}$, where $\lambda^{(n)} := \lambda^n/n!$ is the divided-power notation standard in PVA theory):
\[
\{J \,{}_\lambda\, J\} \;=\; k\lambda.
\]
Together they form a $(-1)$-shifted Poisson vertex algebra. The
Jacobi identity is vacuous (single generator); the Leibniz rule
is the derivation property of~$\partial$; skew-symmetry is the
antisymmetry of the OPE. The entire physical content of this PVA
is in the $\lambda$-linear term, the level~$k$.

The Laplace transform of the $\lambda$-bracket produces the
classical $r$-matrix (Laplace kernel) and the quantum $R$-matrix:
\[
r^L(z) \;=\; \sum_{n \geq 0} \frac{k\,\delta_{n,1}}{z^{n+1}}
\;=\; \frac{k}{z^2},
\qquad
R(z) \;=\; \exp\!\Bigl(\frac{k\hbar}{z}\Bigr).
\]
The bar-theoretic collision residue is $r^{\mathrm{coll}}(z) = k/z$
(one pole order lower than the Laplace kernel, by the $d\log$ absorption
of the bar propagator).
The $R$-matrix satisfies Yang--Baxter because $\cH_k$ is
abelian: the three commutator terms in the CYBE vanish individually.

The chiral Koszul dual is
$\cA^!_{\mathrm{ch}} = \mathrm{Sym}^{\mathrm{ch}}(V^*)$:
the chiral symmetric algebra on the dual space. The open-colour
dual is the abelian Yangian
$\cA^!_{\mathrm{line}} = Y(\mathfrak{u}(1))$,
whose modules form the semisimple Fock-module line category.
As a topological algebra $Y(\mathfrak{u}(1))$ has modular
characteristic $\kappa = -k$ (the same as $\cH_{-k}$, but the
two are distinct algebraic objects: the Yangian is the ordered
Koszul dual, not the Heisenberg at negative level). The
braiding is scalar, with $R$-matrix $R(z) = \exp(k\hbar/z)$. The
bulk--boundary--line triangle collapses:
\[
\cH_k
\;\simeq\;
Z_{\mathrm{der}}(\cH_k)
\;\simeq\;
\HH^\bullet_{\mathrm{ch}}(Y(\mathfrak{u}(1))),
\]
with $\cH_k$ as the boundary vertex algebra of the 3d theory and
$Y(\mathfrak{u}(1))$ as the open-colour dual
whose modules model the line side.

At genus~$1$, the Arnold relation acquires a defect from the
period matrix of the elliptic curve. The bar differential
acquires curvature:
\[
d^2 \;=\; k \cdot \omega_1.
\]
The \emph{modular characteristic} $\kappa(\cA)$ (Volume~I, Theorem~D) is the genus-$1$ curvature coefficient: unconditionally $d_{\barB}^2 = \kappa(\cA) \cdot \omega_1$, while the higher-genus scalar continuation $d_{\barB}^2 = \kappa(\cA) \cdot \omega_g$ is conditional after the Vol~I rectification. Here $\omega_g = c_1(\lambda) \in H^2(\overline{\cM}_g, \Z)$ is the first Chern class of the Hodge bundle. For $\cA = \cH_k$: $\kappa(\cH_k) = k$. For $\cA = \hat{\fg}_k$ with simple~$\fg$: $\kappa(\hat{\fg}_k) = \dim\fg \cdot (k + h^\vee)/(2h^\vee)$.

The modular characteristic is $\kappa(\cH_k) = k$: the same
scalar that governs the OPE, the $\lambda$-bracket, the
$R$-matrix, and now the genus-$1$ obstruction. The free energy
$F_1(\tau) = -k\,\log\,\eta(\tau)$ recovers the Dedekind
$\eta$-function (so that the genus-$1$ partition function is $Z_1 = \eta(\tau)^{-k}$ and the integrated free energy is $\kappa/24 = k/24$). Every datum of the Heisenberg
atom (bar differential, PVA, $R$-matrix, genus-$1$ curvature,
free energy) is controlled by this single parameter.

The genus-$1$ free energy $F_1 = -k\log\eta(\tau)$ is a section of the determinant line bundle $\cL_k^{-1} = (\det\lambda)^{-k}$ over $\overline{\cM}_1$ (Computation~\ref{comp:heisenberg-line-bundle}). The modular characteristic $\kappa = k$ is the Euler class of the cyclic $A_\infty$ structure on~$\cH_k$ (Proposition~\ref{prop:kappa-euler-class}): it measures the obstruction to the cyclic trace being a chain map at genus~$g \geq 1$. The bar construction $\barB(\cH_k)$ classifies twisting morphisms into~$\cH_k$ (Computation~\ref{comp:heisenberg-classifying-space}), realising the representability theorem (Theorem~\ref{thm:bar-representability}) in the simplest case.

The \emph{shadow depth} classification of Volume~I is as follows. The \emph{algebraic depth} $d_{\mathrm{alg}}(\cA) \in \{0, 1, 2, \infty\}$ measures the minimal degree truncation of the $A_\infty$ bar data that determines the full modular tower. The four Koszul classes are: $\mathbf{G}$ (Gaussian, $d_{\mathrm{alg}} = 0$: free theories), $\mathbf{L}$ (Lie-transverse, $d_{\mathrm{alg}} = 1$), $\mathbf{C}$ (Contact, $d_{\mathrm{alg}} = 2$: first nonlinear correction), $\mathbf{M}$ (Mixed, $d_{\mathrm{alg}} = \infty$: full tower contributes). All four are chirally Koszul; the classification measures complexity within the Koszul world. A fifth class $\mathbf{W}$ (wild) marks the non-Koszul boundary: the Kronecker quiver $K_m$ for $m \geq 3$ has indefinite Euler form, the bar spectral sequence does not collapse, and the shadow depth is undefined; the shadow tower is replaced by Donaldson--Thomas invariants (Volume~I, Remarks~\ref*{V1-rem:wild-quiver-class} and~\ref*{V1-rem:wild-quiver-boundary}). The total \emph{shadow depth} is $d = 1 + d_{\mathrm{arith}} + d_{\mathrm{alg}}$, where $d_{\mathrm{arith}} \geq 1$ is the \emph{arithmetic depth} from cusp-form contributions. The \emph{shadow metric} $Q_L(t)$ (Volume~I) is the quadratic form on the shadow obstruction tower whose discriminant $\Delta$ and growth rate $\rho$ control the convergence of the genus expansion.

The shadow metric $Q_L(t) = (2k)^2$ is constant: the
Heisenberg is class~$\mathbf{G}$ (Gaussian), with critical
discriminant $\Delta = 0$ and algebraic depth
$d_{\mathrm{alg}} = 0$
(by the single-line dichotomy theorem of Volume~I).
Depths $d \geq 5$ are purely arithmetic.

The six projections of the Heisenberg MC element, the shadow classification, the PVA, and the genus-$1$ curvature are all controlled by the single scalar~$k$. This is not a simplification: it is the full machine at minimal complexity. The question is whether a single generating object can organise all six projections simultaneously for algebras where $k$ is replaced by an entire tower of independent invariants.

\section*{The 3d MC element}

Volume~I has one universal MC element $\Theta_\cA$ in the modular
convolution algebra $\gAmod$ (the modular convolution algebra of Volume~I), and every theorem is a projection
of~$\Theta_\cA$. Volume~II has one universal MC element $\alpha_T$,
where $T$ denotes the 3d holomorphic-topological theory,
in the Swiss-cheese convolution algebra $\gSC_T$ (the Swiss-cheese convolution algebra)
(Definition~\ref{def:sc-convolution},
Theorem~\ref{thm:3d-universal-mc}), and every structure
exhibited above that is read directly from the closed/open/mixed
operadic datum (boundary $\Ainf$ operations, line-sector operations,
PVA bracket, spectral $R$-matrix, genus-$1$ curvature) is a
projection of~$\alpha_T$. The bulk-boundary-line triangle is then
assembled from these projections together with the boundary-linear
derived-center theorem and, on the chirally Koszul locus, the
line-module and chiral-Hochschild comparison theorems.
The MC element $\alpha_T$ is the fundamental class of the chiral Steinberg self-intersection $\cL \times_{\cM}^h \cL$; each projection extracts a different convolution product on that class (Theorem~\ref{thm:steinberg-presentation}).
At genus~$g$, the amplitude $Z_g(\cC) = \Tr_\cC^{\circ g}(\Theta_\cC^{(g)})$ is computed by $g$-fold application of the clutching-trace operation to the modular twisting morphism (Theorem~\ref{thm:genus-g-traces}), using the cyclic structure of Construction~\ref{constr:cyclic-structure}.

For the Heisenberg: the Swiss-cheese convolution algebra is abelian
(Theorem~\ref{thm:rosetta-3d-mc}), and the MC element is
\[
\alpha_{\cH_k}
\;=\;
\underbrace{m_2}_{\text{double-pole OPE}}
\;+\;
\hbar\,\underbrace{k \cdot \eta \otimes \Lambda}_{\text{genus-}1
\text{ self-loop}}.
\]
Its six projections are
(Corollary~\ref{cor:rosetta-heisenberg-projections}):
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{ll}
\textbf{Projection} & \textbf{Result} \\
\hline
closed face & $m_2(J,J;\lambda) = k\lambda$, $\;m_{k\ge3} = 0$ \\
open face & trivial open-colour line-sector operations on the Fock category \\
spectral $R$-matrix & $R(z) = e^{k\hbar/z}$ \\
bulk-to-boundary & $\Abulk = \Zder(\cH_k) = \cH_k$ \\
genus face & $\Theta_{\cH_k} = k\cdot\eta\otimes\Lambda$ \\
PVA descent & $\{J_\lambda J\} = k\lambda$
\end{tabular}
\end{center}
\smallskip
\noindent
The single scalar $k$ controls every entry.
Section~\ref{sec:rosetta-stone} carries out this computation in
full detail.

The Heisenberg MC element is the answer for class~$\mathbf{G}$. For class~$\mathbf{M}$ (Virasoro, $\cW_N$, three-dimensional gravity) the MC element has infinitely many independent projections. The question that drives the rest of the volume is whether the genus-$0$ data determines the entire tower.

\section*{The completeness question}

\providecommand{\Mbar}{\overline{\mathcal M}}
\providecommand{\Mvac}{\cM_{\mathrm{vac}}}

The structures assembled above that live at genus~$0$ (the
closed/open $\Ainf$ operations, the PVA bracket, the spectral
$R$-matrix, and the mixed bulk-to-boundary operation) are
projections of the MC element~$\alpha_T$. The corrected Koszul
triangle is then assembled from this projection data together with
the scoped comparison theorems discussed below. But the MC element
lives at genus~$0$: the
operation spaces $\FM_k(\C) \times \Conf_k^<(\R)$ parametrise
collisions on a disk, not on a surface of higher genus. The central
question of the modular programme is whether the genus-$0$ data
extends:

\medskip
\begin{center}
\emph{Is the holographic Lagrangian complete?}
\end{center}
\medskip

\noindent
The bar construction embeds the chiral algebra as a Lagrangian
$\cL_\cA \hookrightarrow \Mvac$ in the $(-2)$-shifted symplectic
moduli of local vacua
(Theorem~\ref{thm:bar-is-self-intersection}). At genus~$0$ this
Lagrangian is constructed from the bar-cobar data; its
self-intersection $\cL_\cA \times_{\Mvac} \cL_\cA$ is the
Swiss-cheese algebra. Completeness asks: does the genus-$0$
Lagrangian $\cL_\cA^{(0)}$ extend to a family
$\cL_\cA^{(g)} \hookrightarrow \Mvac$ over the moduli
$\Mbar_{g,n}$, compatible with the gluing correspondences along
boundary strata, and with computable self-intersection numbers at
each genus?

For Koszul algebras the answer is unconditionally yes. The
Lagrangian meets itself cleanly (the derived self-intersection is
concentrated in the expected degree, with no higher Tor), and the
curvature $d^2 = \kappa(\cA) \cdot \omega_g$ is a scalar multiple
of the Hodge class. A scalar curvature extends automatically
over~$\Mbar_{g,n}$: the obstruction to extending an isotropic
embedding through a boundary stratum is a class in the excess
normal bundle, and a scalar curvature has no excess. The clean
intersection extends because it was clean to begin with.

For algebras with non-formal Swiss-cheese structure the question is
open. The derived self-intersection carries excess Tor in unexpected
degrees; the higher $\Ainf$ operations $m_3, m_4, \ldots$ are the
successive obstruction classes for extending the Lagrangian family
through the boundary strata of~$\Mbar_{g,n}$. Each $m_k$ measures the failure
of the $(k-1)$-th extension: it is the $k$-th Massey product of
the curvature class, or equivalently the next coefficient in the
$\hat{A}$-genus expansion of the curved bar complex. The
Virasoro algebra, with its genuinely infinite $\Ainf$ structure,
has infinitely many obstruction classes, and the question of
whether they all vanish coherently is the content of the modular
completion problem.

The \emph{shadow depth} $d(\cA)$ counts the obstruction classes:
$d = 2$ for clean intersections (class~$\mathbf{G}$, Gaussian:
Heisenberg, lattice VOAs),
$d = 3$ for Lie-transverse intersections (class~$\mathbf{L}$, Lie:
affine $V_k(\fg)$, where Jacobi kills the quartic), $d = 4$ for
contact intersections (class~$\mathbf{C}$, contact: $\beta\gamma$),
and $d = \infty$ for the infinite excess tower
(class~$\mathbf{M}$, modular: Virasoro, $\cW_N$).
The discriminant between $\mathbf{G}$ and~$\mathbf{L}$ at $d = 2$
is the centrality of the double-pole coefficient $c_0 = \{a_{(0)}b\}$:
central residues give class~$\mathbf{G}$; non-central
(Lie-bracket) residues give class~$\mathbf{L}$.

The four Koszul classes $\mathbf{G}, \mathbf{L}, \mathbf{C}, \mathbf{M}$
are not an ad hoc taxonomy but the strata of a single invariant: the
shadow metric $Q_\cA(t)$, a quadratic polynomial in the degree
parameter~$t$ whose discriminant $\mathrm{disc}_t(Q_\cA)$ controls
the entire shadow obstruction tower. Class~$\mathbf{G}$ is the locus
$Q_\cA = \mathrm{const}$ (no $t$-dependence); class~$\mathbf{L}$ is
$Q_\cA$ linear; class~$\mathbf{C}$ is $Q_\cA$ quadratic with finite
branching; class~$\mathbf{M}$ is $Q_\cA$ quadratic with infinite
branching. The fifth class~$\mathbf{W}$ (wild) lies outside the
Koszul world: the shadow metric is not defined, and the role of the
obstruction tower passes to Donaldson--Thomas theory
(Volume~I, Remark~\ref*{V1-rem:wild-quiver-boundary}). The Stasheff cancellation
(Theorem~\ref{thm:stasheff-cancellation}) explains why the
stratification is quadratic: the $\Ainf$ relations systematically
cancel all Kac-table denominator factors beyond those of~$Q_\cA$,
taming representation-theoretic infinity into algebraic finiteness.

(Here $d$ is the total shadow depth $d = 1 + d_{\mathrm{arith}} + d_{\mathrm{alg}}$; for standard examples at genus~$0$, $d_{\mathrm{arith}} = 1$, giving $d = d_{\mathrm{alg}} + 2$.)
The shadow depth values $d = 2, 3, 4$ are computed in Volume~I for the standard examples; the geometric interpretations (clean, Lie-transverse, and contact intersection) are proved for $d = 2$ and $d = 3$ (where Jacobi closure is verified directly), while the contact interpretation for $d = 4$ and the infinite excess tower for $d = \infty$ are conjectural geometric descriptions consistent with the algebraic data but not derived from intersection-theoretic first principles.
The shadow obstruction tower atlas
(\S\ref{sec:shadow-tower-atlas}) gives explicit coefficients
for all standard families.
The five worked examples of Part~\ref{part:examples} exhibit a sharp dichotomy
(Remark~\ref{rem:platonic-shadow-dichotomy}): current-algebra
systems (Chern--Simons, M2) are class~$\mathbf{L}$ with finite
towers and $\kappa + \kappa' = 0$ (the complementarity anti-symmetry
that holds for KM and free-field families), while
$\mathcal{W}$-algebra systems (3d gravity, $\mathcal{W}_3$, M5)
are class~$\mathbf{M}$ with infinite towers and
$\kappa + \kappa' = \rho \cdot K \neq 0$ (for Virasoro,
$\kappa + \kappa' = 13$).
The Drinfeld--Sokolov functor is the shadow-depth escalator:
it sends class~$\mathbf{L}$ to class~$\mathbf{M}$.

The infinite tower ($d = \infty$) is controlled by a single
quadratic form: the \emph{shadow metric}
$Q_L(t) = (2\kappa + 3\alpha\,t)^2 + 2\Delta\,t^2$ on each
primary deformation line, where $S_r$ denotes the \emph{degree-$r$ shadow coefficient} (the weight-$r$ projection of $\Theta_\cA$ in the cyclic deformation complex), so that
$\alpha := S_3$ is the cubic shadow
coefficient and $\Delta = 8\kappa S_4$ is the critical discriminant
(in the shadow-metric formalism of Volume~I).
For Virasoro ($\alpha = 2$, $\kappa = c/2$),
$Q_L(t) = (c + 6t)^2 + 80\,t^2/(5c{+}22)$. The weighted generating function satisfies
$H(t)^2 = t^4 Q_L(t)$, so the shadow obstruction tower is algebraic of
degree~$2$. Each coefficient has poles only at
$c = 0$ and $c = -22/5$ (Lee--Yang):
$S_r = \varepsilon_r P_r(c)/[c^{r-3}(5c{+}22)^{\lfloor(r-2)/2\rfloor}]$
for $r \ge 4$, with no new factors at any degree.

The three guiding questions of the modular programme (Existence,
Geometry, Computation) are three aspects of this single question.
Existence asks whether $\cL_\cA^{(0)}$ extends: the \emph{obstruction}
of the extension problem. Geometry asks whether the extension is
compatible with Lagrangian correspondences along boundary strata:
the \emph{compatibility} of the extension problem. Computation
asks for the self-intersection numbers
$\chi(\cL_\cA^{(g)} \times_{\Mvac} \cL_\cA^{(g)}) = R^{(g)}_\cA(z)$:
the \emph{invariants} of the extension problem. One Lagrangian,
one extension, three projections. Part~\ref{part:examples} develops the machinery;
the three basic examples ($\beta\gamma$, Kodaira--Spencer,
$\mathcal{W}_3$ PSM) test it.

Before asking what the machine computes, we must say precisely what it is.

\section*{Construction of the Swiss-cheese operad $\SCchtop$}

The structures above (differential, coproduct, $\Ainf$ operations, $R$-matrix, Koszul triangle) are governed by a single two-coloured operad whose definition the following makes explicit.

\subsection*{Colours and spaces of operations}

The set of colours is $\{\mathsf{ch}, \mathsf{top}\}$: closed
(holomorphic) and open (topological). The spaces of operations are
defined explicitly as follows.

\emph{Closed-to-closed (pure holomorphic).} For $k$ closed inputs
and a closed output,
\[
\SCchtop(\mathsf{ch}^k;\,\mathsf{ch}) \;=\; \FM_k(\C),
\]
the Fulton--MacPherson compactification of $k$~labelled points
in~$\C$. The space $\FM_k(\C)$ is a smooth manifold with corners
of real dimension~$2k - 3$ (for $k \geq 2$, after quotienting by translations and dilations), with codimension-1
boundary strata indexed by subsets $S \subset \{1, \ldots, k\}$
with $|S| \geq 2$: the collision divisor $D_S$ parametrises
configurations where the points labelled by~$S$ collide
simultaneously. A point of $D_S$ records the internal
configuration of the cluster (an element of $\FM_{|S|}(\C)$) and
the position of the cluster relative to the remaining
points (an element of $\FM_{k - |S| + 1}(\C)$), giving
the fundamental fibration
\begin{equation}
\label{eq:intro-FM-fibration}
\FM_{|S|}(\C) \;\hookrightarrow\; D_S \;\twoheadrightarrow\;
\FM_{k - |S| + 1}(\C).
\end{equation}
By convention, $\FM_0(\C) = \FM_1(\C) = \mathrm{pt}$.

\emph{Mixed-to-open (holomorphic + topological).} For $k$ closed
inputs, $m$ open inputs, and an open output,
\[
\SCchtop(\mathsf{ch}^k, \mathsf{top}^m;\,\mathsf{top})
\;=\; \FM_k(\C) \times \Eone(m),
\]
the product of the holomorphic configuration space with the
little-intervals operad $\Eone(m) = \Conf_m^{<}(\R)$, the space of
$m$~ordered distinct points on~$\R$. The product decomposition is
forced by locality: a local observable that factorises
holomorphically in~$z$ and is locally constant in~$t$ can only
depend on collision data in~$\C$ and time-ordering in~$\R$. No
other topological data is available.

\emph{Open-to-closed (forbidden).}
$\SCchtop(\ldots, \mathsf{top}, \ldots;\,\mathsf{ch}) = \varnothing$.
Open inputs cannot produce closed outputs. This is the operadic
expression of the physical principle that bulk interactions
restrict to boundaries, but not conversely.

\subsection*{Composition}

Composition in $\SCchtop$ is by substitution, acting
componentwise on the two factors.

\emph{Closed-into-closed.} Given configurations
$(p_1, \ldots, p_k) \in \FM_k(\C)$ and
$(q^{(i)}_1, \ldots, q^{(i)}_{\ell_i}) \in \FM_{\ell_i}(\C)$ for
$i = 1, \ldots, k$, the operadic insertion map
\[
\gamma_{\mathrm{ch}} \colon \FM_k(\C) \times \prod_{i=1}^{k}
\FM_{\ell_i}(\C) \;\longrightarrow\; \FM_{\sum_i \ell_i}(\C)
\]
replaces each point~$p_i$ by the rescaled cluster~$q^{(i)}$,
using the FM blow-up procedure. This is the standard operad
structure on $\FM_\bullet(\C)$ (Fulton--MacPherson~\cite{FM94},
Getzler--Jones~\cite{GJ94}).

\emph{Open-into-open.} For $k$~closed and $m$~open inputs,
\[
\gamma_{\mathrm{mix}} \colon \bigl(\FM_k(\C) \times \Eone(m)\bigr)
\times \prod_{i=1}^{k} \FM_{\ell_i}(\C) \times \prod_{j=1}^{m}
\Eone(n_j) \;\longrightarrow\; \FM_{\sum_i \ell_i}(\C) \times
\Eone(\textstyle\sum_j n_j),
\]
the product of $\gamma_{\mathrm{ch}}$ on the holomorphic factors
and the standard $\Eone$~composition on the topological factors.

\emph{Closed-into-open.} Closed operations may be substituted
into the closed input slots of a mixed operation; no open operation
may be substituted into a closed input slot. This reflects the
directionality axiom: open $\to$ closed is empty. This
constraint is \emph{forced} at three independent levels:
geometrically (no configuration space interpolates ordered
real-line data to holomorphic collision data),
at the D-module level (!-extension support vanishing from the
codimension-$1$ boundary), and physically (the propagator
factorisation $K = K_\C \otimes H_\R$ forbids topological
inputs from contributing to holomorphic outputs).

\begin{center}
\emph{The composition is associative, equivariant, and unital by
inheritance from the individual operads $\FM_\bullet(\C)$ and
$\Eone$. The proof is componentwise and is recorded in
Section~\textup{\ref{sec:foundations}},
Definition~\textup{\ref{def:SC-composition}}.}
\end{center}

\begin{observation}[Helicity as Swiss-cheese directionality]
\label{obs:helicity-directionality}
The two colours of $\SCchtop$ are, in the celestial reading, the
two helicities of scattering amplitudes.

Positive-helicity insertions are holomorphic (closed colour): they
live on the Fulton--MacPherson compactification $\FM_k(\C)$ and
produce the logarithmic weight forms $\omega_k \in
\Omega^\bullet_{\log}(\ov{\FM}_k(\C))$ that generate the bar
differential. Negative-helicity insertions are topological (open
colour): they live on configuration spaces of the real line
$\Conf_m^{<}(\R)$ and produce the $\Eone$~coproduct.

The no-open-to-closed rule (the strict vanishing
$\SCchtop(\ldots, \mathsf{top}, \ldots;\, \mathsf{ch}) =
\varnothing$) is the \emph{helicity selection rule}: negative-helicity
gluons cannot produce positive-helicity gluons by OPE alone. This
is not a dynamical accident but a structural consequence of the
operad: the colour grading forbids it.

The MHV amplitude, the simplest non-vanishing mixed-helicity
observable, is the simplest non-degenerate pairing between the two
colours: the minimal open--closed coupling under~$\SCchtop$.
All-plus and single-minus amplitudes vanish for the same reason
that open-to-closed operations are empty: form-type obstruction
prevents a purely holomorphic weight form from pairing
nontrivially with the volume form on~$\ov{\FM}_n(\C)$.

The first part of this identification (that the bar complex
$\barBch(\cA)$, built from holomorphic logarithmic forms on
$\FM_n(\C)$, encodes exactly the self-dual sector) is proved
in Theorem~\textup{\ref{thm:ch-core-helicity-splitting}(i)}
(Part~\textup{VII}). The remaining parts (anti-self-dual sector
from $\barBch(\cA^!)$, mixed-helicity amplitudes from the
twisting morphism $\tau\colon\barBch(\cA)\to\cA^!$, and the
identification of MHV with the minimal open--closed coupling)
rest on heuristic form-type arguments detailed in the same
theorem; their elevation to full proofs remains open.
\end{observation}

The operad is the stage; the actors are the operations $m_k$.

\section*{The $\Ainf$ chiral operations $m_k$}

The bar complex $\barB^{\mathrm{ch}}(\cA) = T^c(s^{-1}\ov{\cA})$
is a conilpotent coalgebra whose differential $d_{\barB}$ is a
coderivation. A coderivation on a cofree coalgebra is determined
by its cogenerator projections: a sequence of multilinear maps
\[
m_k \colon A^{\otimes k} \longrightarrow
A((\lambda_1))\cdots((\lambda_{k-1})),
\qquad k \geq 1, \quad \deg m_k = 2 - k,
\]
where the spectral parameters
$\lambda_i = z_i - z_k$ record the holomorphic separations. The
identity $d_{\barB}^2 = 0$ expands, by the coalgebra structure,
into the hierarchy of $\Ainf$ relations.

\subsection*{The $\Ainf$ relations as boundary decompositions of $\FM_n(\C)$}

The $n$-th $\Ainf$ relation is the equation
\begin{multline}
\label{eq:intro-ainfty}
\sum_{\substack{i+j = n+1 \\ i,j \geq 1}} \;\sum_{s=0}^{n-j}
(-1)^{|a_1| + \cdots + |a_s|}\;
m_i\bigl(a_1, \ldots, a_s,\,
m_j(a_{s+1}, \ldots, a_{s+j};\, \lambda_{s+1}, \ldots,
\lambda_{s+j-1}) \;\big|\;\\
\Lambda_{[s+1,\ldots,s+j]},\,
a_{s+j+1}, \ldots, a_n;\, \bm\lambda^{\mathrm{out}}\bigr) = 0,
\end{multline}
where $\Lambda_{[s+1,\ldots,s+j]} = \lambda_{s+1} + \cdots +
\lambda_{s+j-1}$ is the effective spectral parameter of the fused
block, and $\bm\lambda^{\mathrm{out}}$ denotes the remaining
spectral variables with the inner block replaced by its sum.

This relation is the Stokes theorem on $\FM_n(\C)$.
The codimension-1 boundary of $\FM_n(\C)$ consists of the collision
divisors $D_S$ for $S \subset \{1, \ldots, n\}$, $|S| \geq 2$,
and each such divisor contributes one summand
$m_{n - |S| + 1}(\ldots, m_{|S|}(\ldots), \ldots)$ to the
$\Ainf$ relation. The inner operation $m_{|S|}$ is the residue
along $D_S$ (the cluster of $|S|$ points colliding); the outer
operation $m_{n - |S| + 1}$ is the interaction of the fused cluster
with the remaining points. The sign
$(-1)^{|a_1| + \cdots + |a_s|}$ is the Koszul sign of the
coderivation passing the first $s$ elements. The spectral
substitution $\lambda_{\mathrm{inner}} \mapsto
\Lambda_{[s+1,\ldots,s+j]}$ records that a fused cluster inherits
the total momentum of its constituents, the algebraic avatar of
momentum conservation.

For \emph{$n = 2$}: the relation is $m_1 \circ m_2 + m_2 \circ
(m_1 \otimes \id + \id \otimes m_1) = 0$, asserting that $Q = m_1$
is a graded derivation of the binary operation~$m_2$.

For \emph{$n = 3$}: the codimension-$1$ boundary strata of
$\FM_3(\C)$ are $D_{\{1,2\}}$, $D_{\{2,3\}}$, and
$D_{\{1,3\}}$. In the ordered $A_\infty$ convention, only
consecutive blocks contribute to the bar coderivation:
$D_{\{1,2\}}$ and $D_{\{2,3\}}$ give the two
$m_2(m_2(-,-),-)$ terms; $D_{\{1,3\}}$ (non-consecutive) does
not contribute at the bar-complex level, but contributes to the
PVA Jacobi identity after passing to the unordered/commutative
shadow (see Step~5 of Theorem~\ref{thm:stokes_arnold} for the
vanishing mechanism). The relation reads:
\begin{equation}
\label{eq:intro-n3}
m_2(m_2(a,b;\lambda_1), c;\, \lambda_1 + \lambda_2) \;-\;
m_2(a, m_2(b,c;\lambda_2);\, \lambda_1) \;+\;
m_1 m_3(a,b,c) \;+\; m_3(Q\cdot) \;=\; 0.
\end{equation}
On cohomology, the $m_3$~terms vanish and the remaining identity
is the Jacobi identity for the $\lambda$-bracket. At the chain
level, $m_3$ is the \emph{homotopy} for the failure of strict
associativity, and the boundary decomposition of $\FM_3(\C)$ is
the geometric reason it exists.

\subsection*{The resolvent principle: one equation for all~$m_k$}

The operations $\{m_k\}_{k \ge 2}$ are not independent: they are
the unique solution of a fixed-point equation. Let
$(H, p, \iota, h)$ be a deformation retract of $(\cA, m_1)$ onto
cohomology, with $h^2 = h\iota = ph = 0$. The
\emph{dressed propagator} $\Phi \colon T^+(H) \to \cA$
satisfies
\begin{equation}
\label{eq:intro-resolvent}
\Phi \;=\; \iota \;+\; h \circ m_2 \circ \Phi^{\otimes 2}
\end{equation}
the tree-level bootstrap equation
(Theorem~\ref{thm:resolvent-principle}). Its solution by
iteration gives the transferred operation $m_k^H$ as a sum over
$C_{k-1}$ planar binary trees, with $m_2$ at vertices and~$h$ at
edges. One binary input, one homotopy, all higher operations.
The Stasheff relations are the consistency of the iteration; the
tree formula is the perturbative expansion of the Lagrangian
self-intersection.

\subsection*{The regular/singular decomposition of $m_2$}

The binary operation $m_2(a,b) \in A((\lambda))$ admits a canonical
decomposition into regular and singular parts:
\begin{equation}
\label{eq:intro-reg-sing}
m_2(a,b)(\lambda) \;=\;
\underbrace{m_2^{\mathrm{reg}}(a,b)}_{\in\, A[[\lambda]]}
\;+\;
\underbrace{m_2^{\mathrm{sing}}(a,b)}_{\in\, \lambda^{-1}
A[\lambda^{-1}]}.
\end{equation}
The regular part is the \emph{normally ordered product}: the
commutative multiplication on the underlying vector space. The
singular part is the \emph{$\lambda$-bracket}: the OPE residue.
The notation
\[
a \cdot b \;:=\; m_2^{\mathrm{reg}}(a,b)\big|_{\lambda=0},
\qquad
\{a \,{}_\lambda\, b\} \;:=\; m_2^{\mathrm{sing}}(a,b),
\]
records this decomposition. Together, the product and
$\lambda$-bracket form a Poisson vertex algebra on
$H^\bullet(A, Q)$, proved in the next section.


\section*{PVA descent: from $\Ainf$ to Poisson vertex algebra}

The passage from the $\Ainf$ chiral structure to a PVA on
cohomology is a controlled forgetting map. We derive it
step by step.

\subsection*{Step 1: the product}

On $Q$-closed elements $a, b \in H^\bullet(A, Q)$, the regular
part $a \cdot b = m_2^{\mathrm{reg}}(a,b)|_{\lambda=0}$ is a
well-defined commutative product. Well-definedness: if
$a = Qc$, then $m_2(Qc, b) = Q m_2(c,b) \pm m_2(c, Qb)$ by the
$n = 2$ $\Ainf$ relation; the regular part at $\lambda = 0$ is
$Q$-exact. Commutativity on cohomology follows from the
involution $\sigma \colon \FM_2(\C) \to \FM_2(\C)$ exchanging
the two points: $\sigma$ acts by $\lambda \to -\lambda - \partial$
and reverses the sign of the singular part while preserving the
regular part (after sesquilinearity corrections).

\subsection*{Step 2: the $\lambda$-bracket}

The singular part $\{a {}_\lambda b\} = m_2^{\mathrm{sing}}(a,b)$
satisfies:
\begin{itemize}
\item \textbf{Sesquilinearity.} Directly from the chain-level
 sesquilinearity of $m_2$ (which is the geometric content of
 translation covariance on $\FM_2(\C)$):
 \[
 \{\partial a {}_\lambda b\} = -\lambda \{a {}_\lambda b\},
 \qquad
 \{a {}_\lambda \partial b\} = (\partial + \lambda)
 \{a {}_\lambda b\}.
 \]
 The first equation: $m_2(\partial a, b) = -\lambda \cdot
 m_2(a,b)$ by sesquilinearity; taking the singular part preserves
 the relation since multiplication by $-\lambda$ maps singular to
 singular. The second: $m_2(a, \partial b) = (\lambda + \partial)
 \cdot m_2(a,b)$; the operator $\partial$ acts on coefficients,
 not on $\lambda$, so it commutes with the projection.

\item \textbf{Skew-symmetry.} The involution
 $\sigma \colon (z_1, z_2) \mapsto (z_2, z_1)$ on $\FM_2(\C)$
 sends $\lambda \to -\lambda - \partial$ (the full translation).
 At the chain level, $m_2(a,b;\lambda) = (-1)^{|a||b|}
 m_2(b,a; -\lambda - \partial)$. Taking singular parts:
 $\{a {}_\lambda b\} = -\{b {}_{-\lambda - \partial} a\}$, the
 PVA skew-symmetry axiom.

\item \textbf{Leibniz rule.} The $n = 2$ $\Ainf$ relation with
 the product $a \cdot b$ inserted yields, on cohomology,
 $\{c {}_\lambda (a \cdot b)\} = \{c {}_\lambda a\} \cdot b +
 a \cdot \{c {}_\lambda b\}$. This is the Leibniz rule: the
 $\lambda$-bracket is a derivation of the commutative product.
 The proof uses the regular/singular decomposition and the fact
 that $m_3$ vanishes on cohomology (see Step~3 below).
\end{itemize}

\subsection*{Step 3: vanishing of higher operations on cohomology}

For $k \geq 3$, the operation $m_k$ vanishes on $H^\bullet(A, Q)$.
The geometric input is the contractibility of
$\Conf_k^{<}(\R)$ for $k \geq 3$: the ordered configuration space
of $k$~points on~$\R$ is contractible (being homeomorphic to
$\R^{k-1}_{>0}$, an open simplex). (Note: $\Conf_2^{<}(\R)
\cong \R_{>0}$ is also contractible, but the contractibility
argument applies to the \emph{transferred higher homotopies} $m_k$
for $k \geq 3$; the binary operation $m_2$ is the generating
operation of the $\Eone$-structure and is not a higher homotopy,
so the contraction does not eliminate it.)
The argument proceeds as follows.

The operation $m_k$ is parametrised by $\FM_k(\C) \times
\Conf_k^{<}(\R)$. The $\Eone$-factor $\Conf_k^{<}(\R)$ provides a
canonical chain homotopy $h_k$ (from the contraction of
$\Conf_k^{<}(\R)$ to a point), and the $\Ainf$ relation
$\sum m_i(\ldots, m_j(\ldots), \ldots) = 0$ at degree~$n = k$
gives
\[
Q \circ m_k + m_k \circ Q^{\otimes} + \sum_{\substack{i+j=k+1 \\
i,j \geq 2}} (\text{lower-degree terms}) = 0.
\]
On $Q$-closed inputs, $m_k \circ Q^{\otimes} = 0$ and the
lower-degree terms involve $m_2$-compositions (which are already
determined), so the $\Ainf$ relation gives
\[
[m_k(\alpha_1, \ldots, \alpha_k)]
\;=\;
Q\bigl(h_k \circ m_k(\alpha_1, \ldots, \alpha_k)\bigr)
\;=\; 0
\quad\text{in } H^\bullet(\cA, Q),
\]
where $h_k$ is the chain homotopy from the contraction of
$\Conf_k^{<}(\R) \simeq \R^{k-1}_{>0}$ to a point.
Thus $m_k$ is $Q$-exact on cohomology.

\subsection*{Step 4: the Jacobi identity}

The Jacobi identity
\[
\{a {}_\lambda \{b {}_\mu c\}\} - \{b {}_\mu \{a {}_\lambda c\}\}
= \{\{a {}_\lambda b\} {}_{\lambda + \mu}\, c\}
\]
does not follow from
$m_2$ alone; it requires the $n = 3$ $\Ainf$ relation and Stokes'
theorem on $\FM_3(\C)$.

Consider the $n = 3$ relation~\eqref{eq:intro-n3} on
$Q$-closed elements $a, b, c$. The $m_3$~terms are $Q$-exact
(by Step~3), and the $m_1 = Q$ terms vanish on cohomology. The
surviving terms are:
\[
m_2(m_2(a,b;\lambda_1), c;\, \lambda_1 + \lambda_2)
\;=\;
m_2(a, m_2(b,c;\lambda_2);\, \lambda_1).
\]
Taking singular parts in both $\lambda_1$ and $\lambda_2$ (with
$\mu = \lambda_2$):
\begin{align*}
\text{LHS:}\quad &
\{m_2^{\mathrm{sing}}(a,b;\lambda) {}_{\lambda + \mu}\, c\}
\;+\; \text{mixed terms} \\
\text{RHS:}\quad &
\{a {}_\lambda\, m_2^{\mathrm{sing}}(b,c;\mu)\}
\;+\; \text{mixed terms}.
\end{align*}
The mixed terms (regular in one variable, singular in the other)
cancel by the same mechanism that makes $d_{\barB}^2 = 0$ in
Volume~I: the Arnold relation
$\omega_{12} \wedge \omega_{23} + \omega_{23} \wedge \omega_{31} +
\omega_{31} \wedge \omega_{12} = 0$ on $\Conf_3(\C)$, applied via
Stokes' theorem on the boundary strata of $\FM_3(\C)$. The
resulting identity on the purely singular parts is exactly the
PVA Jacobi identity.

The full verification, with all signs and spectral substitutions,
is Theorem~\ref{thm:cohomology_PVA} in
Section~\ref{sec:PVA_descent}.

\begin{maintheorem}[Cohomological descent to PVA;
Theorem~\textup{\ref{thm:cohomology_PVA}}; \ClaimStatusProvedHere]
\label{thm:intro-PVA-descent}
Let $\cA$ be a logarithmic $\SCchtop$-algebra
\textup{(}Definition~\textup{\ref{def:log-SC-algebra}}:
an $\SCchtop$-algebra whose structure maps extend to
logarithmic differential forms on the FM compactification,
i.e.\ the propagator is a log $1$-form with at worst simple
poles along boundary divisors\textup{)}.
Then $H^\bullet(\cA, Q)$ carries the
structure of a $(-1)$-shifted Poisson vertex algebra
(the $\lambda$-bracket has cohomological degree~$+1$;
equivalently, the underlying Lie bracket lives on $A[1]$):
\begin{enumerate}[label=\textup{(\roman*)}]
\item the commutative product is the regular part of $m_2$;
\item the $\lambda$-bracket is the singular part of $m_2$;
\item all higher operations $m_{k \geq 3}$ vanish on cohomology.
\end{enumerate}
The PVA axioms (sesquilinearity, skew-symmetry, Jacobi, Leibniz,
vacuum) are proved by Stokes' theorem on $\FM_n(\C)$ and
contractibility of $\Conf_k^{<}(\R)$.
\end{maintheorem}

The PVA is the classical shadow. It remembers the commutative product and the singular OPE, but forgets the chain-level homotopies $m_3, m_4, \ldots$ that measure the failure of strict associativity. What structure does the PVA carry beyond the Lie bracket?

\section*{The spectral $R$-matrix from the $\lambda$-bracket}

The $\lambda$-bracket encodes the classical braiding of line
operators. The bridge from PVA to Yang--Baxter is the Laplace
transform.

\subsection*{The classical $r$-matrix}

Given the $\lambda$-bracket $\{a {}_\lambda b\}$, define the
classical $r$-matrix by the Laplace transform
\begin{equation}
\label{eq:intro-laplace}
r(z) \;=\; \int_0^\infty e^{-\lambda z}\,
\{{\cdot}\,{}_\lambda\,{\cdot}\}\, d\lambda.
\end{equation}
This integral converges for $\operatorname{Re}(z) > 0$ (under
the physical-realization hypotheses of Theorem~\ref{thm:physics-bridge}) and extends meromorphically to
$\C^\times$. Algebraically, if
$\{a {}_\lambda b\} = \sum_{n \geq 0} c_n \lambda^n / n!$, then
$r(z)(a \otimes b) = \sum_{n \geq 0} c_n / z^{n+1}$.

\emph{Classical Yang--Baxter.} The PVA Jacobi identity transforms
under Laplace into the classical Yang--Baxter equation with
spectral parameter:
\begin{equation}
\label{eq:intro-CYBE}
[r_{12}(z_{12}),\, r_{13}(z_{13})] +
[r_{12}(z_{12}),\, r_{23}(z_{23})] +
[r_{13}(z_{13}),\, r_{23}(z_{23})] \;=\; 0.
\end{equation}
The proof: Laplace-transform each term of the PVA Jacobi identity.
The substitution $\mu = \lambda_2$, $\lambda = \lambda_1$ becomes
$z_{13} = z_{12} + z_{23}$ under Laplace, and the three terms of
the Jacobi identity map exactly to the three commutators of the
CYBE. The constraint $z_{13} = z_{12} + z_{23}$ is the spectral
parameter identity, the Laplace shadow of the additivity of
$\lambda$-parameters under operadic composition.

\subsection*{The quantum $R$-matrix}

The quantum $R$-matrix $R(z)$ is constructed from the
bulk-to-boundary OPE of line operators. Given two parallel
boundary lines $L_1(z_1)$ and $L_2(z_2)$ in the 3d HT theory
on $\C \times \R_{\geq 0}$, their OPE defines a braiding
isomorphism
\[
R_{L_1, L_2}(z) \colon L_1 \otimes L_2
\;\xrightarrow{\;\sim\;}\; L_2 \otimes L_1,
\qquad z = z_1 - z_2,
\]
meromorphic in~$z$, computed by configuration integrals over
$\FM_2(\C) \times \Eone(2)$ (Definition~\ref{def:spectral-braiding}).
Its semiclassical limit is $R(z) = \id + \h\, r(z) + O(\h^2)$,
recovering the classical $r$-matrix.

\emph{Yang--Baxter.} The quantum $R$-matrix satisfies
\begin{equation}
\label{eq:intro-YBE}
R_{12}(z_{12})\, R_{13}(z_{13})\, R_{23}(z_{23})
\;=\;
R_{23}(z_{23})\, R_{13}(z_{13})\, R_{12}(z_{12}),
\end{equation}
proved by Stokes' theorem on $\FM_3(\C)$. The three
codimension-1 boundary strata $D_{\{1,2\}}$, $D_{\{2,3\}}$,
$D_{\{1,3\}}$ contribute the three double products on each side:
$D_{\{1,2\}}$ gives $R_{12} R_{13} R_{23}$ (points $z_1, z_2$
collide first), $D_{\{2,3\}}$ gives $R_{23} R_{13} R_{12}$ (points
$z_2, z_3$ collide first), and the vanishing of the boundary
integral $\int_{\partial \FM_3(\C)} \omega_3^{\partial} = 0$ forces
the two sides to be equal. The face $D_{\{1,3\}}$ does not
contribute independently: its spectral parameter is
$z_{13} = z_{12} + z_{23}$, so it is absorbed into the other two
terms.

\emph{Classical limit.} The CYBE for
$r(z)$ is the semiclassical limit of the YBE for $R(z)$: both
follow from Stokes' theorem on $\FM_3(\C)$, evaluated on the
classical and quantum convolution kernels respectively.

The $R$-matrix braids line operators. Where do these line operators live, and what algebra governs them?

\section*{The bulk--boundary--line Koszul triangle}

A 3d HT theory on $\C \times \R$ produces three algebraic
objects:
\begin{enumerate}[label=(\roman*)]
\item the \textbf{bulk chiral algebra} $\Abulk$: local operators
 on $\C \times \R$;
\item the \textbf{boundary algebra} $\Bbound$: local operators
 on the boundary $\C \times \{0\}$;
\item the \textbf{line category}
 $\cC_{\mathrm{line}}$: line operators supported on curves
 $\{z_0\} \times \R_t$.
\end{enumerate}
The strongest theorem-level relation between the three vertices is
scoped: on the chirally Koszul locus and under the compact-generation /
derived-center hypotheses,
\begin{equation}
\label{eq:intro-triangle}
\Abulk \;\simeq\;
\Zder(\Bbound) \;\simeq\;
\Zder(\cC_{\mathrm{line}}) \;\simeq\;
\HH^\bullet_{\mathrm{ch}}(\cA^!_{\mathrm{line}}),
\qquad
\cC_{\mathrm{line}} \;\simeq\; \cA^!_{\mathrm{line}}\text{-}\mathbf{mod}.
\end{equation}
Unconditionally, the live theorem surface is weaker: bulk identifies
with chiral Hochschild cochains of the boundary algebra, while the
displayed derived-center and line-module corners retain the extra
scope just stated. The primitive datum is the open-sector
factorization category $\cC$
(Definition~\ref{def:oc-factorization-category}); the boundary algebra
$B_\partial = \End_\cC(b)$ and bulk algebra
$\cO_{\mathrm{bulk}} = Z_{\mathrm{der}}(\cC)$ are derived invariants
depending only on the Morita class of~$\cC$.

\subsection*{Construction of the three vertices}

\emph{The bulk algebra.} The algebra $\Abulk$ is the factorisation
algebra of local observables on $\C \times \R$, with differential
$Q_{\mathrm{BRST}}$ from the BV master equation. On cohomology,
$H^\bullet(\Abulk, Q)$ is the $(-1)$-shifted PVA of
Theorem~\ref{thm:intro-PVA-descent}.

\emph{The boundary algebra.} A boundary condition
$b \colon \C \times \{0\} \hookrightarrow \C \times \R_{\geq 0}$
defines a boundary algebra $\Bbound = \End_{\cC_{\mathrm{line}}}(M_b)$,
the endomorphism algebra of the boundary module $M_b$ in the line
category. On physical grounds, $\Bbound$ is the vertex algebra of
boundary operators; it carries the boundary differential
$Q_{\partial}$ and the full $\Ainf$ chiral structure from the
restriction of the Swiss-cheese operations to the half-space.

\emph{The line category.} Line operators are $1$-dimensional
defects. A line $L$ at position $z_0 \in \C$ defines a topological
quantum mechanics on $\R_t$, with state space $V_L$. Bulk operators
near the line act on $V_L$ through the open colour of
$\SCchtop$, the mixed operations
$C_\ast(\FM_k(\C) \times \Eone(m)) \otimes \Abulk^{\otimes k}
\otimes V_L^{\otimes m} \to V_L$. These operations are the direct
open-sector data. On the chirally Koszul locus, the later
comparison theorem
\textup{(}Theorem~\textup{\ref{thm:lines_as_modules}}\textup{)}
models this same line-side package by
$\cA^!_{\mathrm{line}}$-modules. The
resulting functor
$\Phi \colon \cC_{\mathrm{line}} \to \cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$,
$L \mapsto V_L$, is an equivalence
(Theorem~\ref{thm:lines_as_modules}).

\subsection*{The derived centre identification}

The quasi-isomorphism $\Abulk \simeq \Zder(\Bbound)$ is
proved in the exact boundary-linear sector
(Theorem~\ref{thm:boundary-linear-bulk-boundary}). The derived
centre $\Zder(\Bbound)$ of the boundary algebra is, by definition,
$\RHom_{\Bbound^e}(\Bbound, \Bbound)$, the endomorphisms of
$\Bbound$ as a bimodule over itself. The identification uses
derived critical locus technology: $\Abulk$ is presented as
$\dCrit(W)$ (the \emph{derived critical locus}, i.e.\ the
derived zero locus of~$dW$ in~$T^*X$) for
a holomorphic potential $W$, and the derived
centre is identified with the $(-1)$-shifted cotangent
$T^*[-1]\dCrit(W)$. Morita invariance of derived centres then
gives, in that scoped setting,
$\Zder(\Bbound) \simeq \Zder(\cC_{\mathrm{line}}) \simeq
\HH^\bullet_{\mathrm{ch}}(\cA^!_{\mathrm{line}})$.

\subsection*{Homotopy coherence}

The triangle~\eqref{eq:intro-triangle} is an equivalence of
homotopy-coherent objects
(Remark~\ref{rem:triangle-homotopy-first}): each vertex is an
$\Ainf$ or $\Linf$ algebra, and the identifications hold at the
derived level. Premature strictification at any corner
destroys the equivalence.

The line vertex of the triangle identifies the line category with modules over the open-colour Koszul dual~$\cA^!_{\mathrm{line}}$. What algebraic structure does~$\cA^!_{\mathrm{line}}$ carry?

\section*{The dg-shifted Yangian}

On the chirally Koszul locus, the open-colour Koszul dual
algebra $\cA^!_{\mathrm{line}}$ carries two layers of
structure: the $\SCchtop$-algebra structure from operadic
self-duality (the algebra half), and the bialgebra structure
from the monoidal category of line operators (the coalgebra
half). Together, they determine the dg-shifted Yangian
package isolated below.

\noindent\textsc{Definition}
\textit{(dg-shifted Yangian; Definition~\textup{\ref{def:dg_Yangian}}).}
A \emph{dg-shifted Yangian} $\mathcal{Y}$ is an $\Ainf$ algebra
equipped with:
\begin{enumerate}[label=(\roman*)]
\item a translation automorphism
 $\tau_z = \exp(zT) \colon \mathcal{Y} \to \mathcal{Y}[[z]]$;
\item a spectral $R$-matrix
 $r(z) \in \mathcal{Y} \widehat{\otimes}\,
 \mathcal{Y}[[z^{-1}, z]]$;
\item a twisted coproduct
 $\Delta_z \colon \mathcal{Y} \to
 \mathcal{Y} \otimes_{r(z)} \mathcal{Y}[[z^{-1}, z]]$;
\item a counit $\varepsilon \colon \mathcal{Y} \to \C$;
\end{enumerate}
satisfying counit axioms, translation invariance,
weak co-commutativity $r(-z) = -r_{21}(z)$, and the quantum
$\Ainf$ Yang--Baxter equation
\[
r_{23}(z) + (\id \otimes \Delta_z)(r(z+w))
\;=\;
r_{12}(w) + (\Delta_w \otimes \id)(r(z)).
\]

The Koszul duality $(\SCchtop)^! = (\mathsf{Lie},\, \mathsf{Ass},\, \text{shuffle-mixed})$
(\S\ref{subsec:dg-yangian-operadic}) gives~$\cA^!_{\mathrm{line}}$ an
$(\SCchtop)^!$-algebra structure; since $\mathsf{Ass}$ is self-dual,
the open colour preserves its $E_1$-algebra structure (product,
$\lambda$-bracket, translation, compatibility). The
monoidal structure on line operators on the chirally Koszul
locus, where
$\cC_{\mathrm{line}} \simeq \cA^!_{\mathrm{line}}\text{-}\mathbf{mod}$,
provides the coproduct and $R$-matrix (the bialgebra
half). Together, on that locus,
$\cA^!_{\mathrm{line}}$ carries the dg-shifted Yangian package
(Theorem~\ref{thm:yangian-recognition}; the two-colour
architecture underlying this identification is the interplay
between the chiral symmetric bar
$\barB^{\Sigma}(\cA)$ and the $E_1$ ordered bar
$\barB^{\mathrm{ord}}(\cA)$ reviewed above), and the full
two-colour Koszul duality involution returns~$\cA$
(Theorem~\ref{thm:duality-involution}).

In the affine lineage, the ordered/open sector sharpens this
abstract Yangian package to the familiar Drinfeld and RTT
presentations: the transfer matrix
$T(u) = \sum T_{ij}(u)\, e_{ij}$ satisfies
\[
R_{12}(u-v)\, T_1(u)\, T_2(v) = T_2(v)\, T_1(u)\,
R_{12}(u-v),
\]
and this RTT relation is the spectral rewriting of the
ordered line-operator braiding developed in
Part~\ref{part:bbl-core}.

All of the above is output. What input axiom generates it?

\section*{The recognition theorem and homotopy-Koszulity}

\begin{maintheorem}[Recognition; Theorem~\textup{\ref{thm:recognition}}; \ClaimStatusProvedHere]
\label{thm:intro-recognition}
Let $\cA$ be a logarithmic $\SCchtop$-algebra
\textup{(}Definition~\textup{\ref{def:log-SC-algebra})}.
Then $\cA$ carries the
structure of a $C_\ast(W(\SCchtop))$-algebra, where
$W(\SCchtop)$ is the \emph{Boardman--Vogt W-construction}:
it replaces strict operadic composition by homotopy-coherent
composition, inserting intervals $[0,1]$ at internal edges
to parametrise the homotopies.
The bar differential
$d_{\barB}$ is the holomorphic factorisation; the bar coproduct
$\Delta$ is the topological factorisation.
\end{maintheorem}

\noindent
The proof (Section~\ref{sec:foundations}) reduces to the product
decomposition $\FM_k(\C) \times \Conf_k(\R)$ and a retract
argument showing that the combined data are a single operad
algebra structure, once the holomorphic factorisation of Volume~I
is granted and the logarithmic $\SCchtop$ structure is packaged by
Definition~\ref{def:log-SC-algebra}. For physical realizations,
Theorem~\ref{thm:physics-bridge} supplies this input.

\begin{maintheorem}[Homotopy-Koszulity; Theorem~\textup{\ref{thm:homotopy-Koszul}}; \ClaimStatusProvedHere]
\label{thm:intro-homotopy-Koszul}
The two-coloured topological operad $\SCchtop$ is
homotopy-Koszul: the canonical map
$\Omega \mathbf{B}(\SCchtop) \xrightarrow{\,\sim\,} \SCchtop$
is a quasi-isomorphism of dg operads.
\end{maintheorem}

\noindent
The proof proceeds in three steps.
\textbf{Step~1}: the classical Swiss-cheese operad
$\mathsf{SC}$, built from the individually Koszul operads
$\Etwo$ (the homology operad of the little-$2$-disks operad,
$\Etwo(k) = H_\ast(\mathrm{Conf}_k(\C))$, governing
Gerstenhaber algebras)
and $\Ass = \Eone$ via a distributive law, is Koszul
(Ginzburg--Kapranov~\cite{GK94}, Hoefel~\cite{Hoe09},
Hoefel--Livernet~\cite{HL12}).
\textbf{Step~2}: Kontsevich formality provides a quasi-isomorphism
$\Phi \colon \SCchtop \to \mathsf{SC}$ of two-coloured dg operads
(the identity on the open colour, the formality map
$C_\ast(\FM_k(\C)) \to \Etwo(k)$ on the closed colour).
\textbf{Step~3}: bar and cobar functors preserve quasi-isomorphisms
between augmented operads (Berger--Moerdijk~\cite{BM03}), so the
two-out-of-three property gives
$\Omega \mathbf{B}(\SCchtop) \simeq \SCchtop$.

The consequence is that the bar-cobar adjunction
$(\Omega, \mathbf{B})$ on $\SCchtop$-algebras is a \textbf{Quillen
equivalence} (Theorem~\ref{thm:bar-cobar-adjunction}): the bar
complex determines the algebra up to quasi-isomorphism. The
filtered version (Theorem~\ref{thm:filtered-koszul}) extends this
beyond the quadratic locus.

\subsection*{The colour decomposition of the MC element}

The MC element $\alpha_T \in \mc(\gSC_T)$ decomposes by the
colour grading of the Swiss-cheese operad. Write
\[
\alpha_T \;=\; \alpha_T^{\mathrm{cl}}
\;+\; \alpha_T^{\mathrm{mix}}
\;+\; \alpha_T^{\mathrm{op}},
\]
where $\alpha_T^{\mathrm{cl}}$ sums over graphs with only closed
vertices, $\alpha_T^{\mathrm{mix}}$ over graphs with at least one
mixed vertex and at least one closed vertex, and
$\alpha_T^{\mathrm{op}}$ over graphs with only open vertices.
The MC equation
$D\alpha_T + \tfrac{1}{2}[\alpha_T, \alpha_T] = 0$ decomposes as
\begin{alignat}{2}
\label{eq:intro-mc-closed}
&D\alpha_T^{\mathrm{cl}}
 + \tfrac{1}{2}[\alpha_T^{\mathrm{cl}},
 \alpha_T^{\mathrm{cl}}] &&= 0, \\
\label{eq:intro-mc-mixed}
&d_{\Theta}\,\alpha_T^{\mathrm{mix}} &&= 0, \\
\label{eq:intro-mc-open}
&d_{\Theta}\,\alpha_T^{\mathrm{op}}
 + [\alpha_T^{\mathrm{mix}},
 \alpha_T^{\mathrm{op}}]
 + \tfrac{1}{2}[\alpha_T^{\mathrm{mix}},
 \alpha_T^{\mathrm{mix}}]_{\mathrm{op}}
 + \tfrac{1}{2}[\alpha_T^{\mathrm{op}},
 \alpha_T^{\mathrm{op}}] &&= 0,
\end{alignat}
where $\Theta_\cA := \alpha_T^{\mathrm{cl}}$ is the closed-colour component and
$d_\Theta = D + [\Theta_\cA, -]$ is the
$\Theta_\cA$-twisted differential.

Equation~\eqref{eq:intro-mc-closed} is the modular MC equation
of Vol~I\@.
Equation~\eqref{eq:intro-mc-mixed} says that the classical
$r$-matrix and the PVA bracket are $\Theta_\cA$-twisted cocycles
in $\gSC_T$.
Equation~\eqref{eq:intro-mc-open} says that the line-category
structure closes under the combined twisting.

\smallskip
\noindent\textbf{Kac--Moody.}\enspace
$\alpha_T^{\mathrm{cl}} = \Theta_{\widehat{\fg}_k}$, the affine
MC element of Vol~I\@.
$\alpha_T^{\mathrm{mix}} = k\,\Omega/z$, the level-weighted split Casimir; the
twisted cocycle condition~\eqref{eq:intro-mc-mixed} is the CYBE
$[r_{12}, r_{13}] + [r_{12}, r_{23}] + [r_{13}, r_{23}] = 0$
for $r(z) = k\,\Omega/z$.
On the affine Kac--Moody comparison surface, the mixed MC component
along the spectral parameter identifies with the KZ connection
$\nabla = d - \frac{1}{k+h^\vee}\,\Omega\,d\log z$.
$\alpha_T^{\mathrm{op}}$ encodes the Yangian coproduct on
$Y(\fg)$, and~\eqref{eq:intro-mc-open} is the RTT relation
$R_{12}(u-v)\,T_1(u)\,T_2(v) = T_2(v)\,T_1(u)\,R_{12}(u-v)$.

\smallskip
\noindent\textbf{Virasoro.}\enspace
$\alpha_T^{\mathrm{cl}} = \Theta_{\mathrm{Vir}_c}$, the
infinite-depth MC element.
$\alpha_T^{\mathrm{mix}} = r^L(z) = (c/2)/z^4 + 2T/z^2 + (\partial T)/z$
(Laplace kernel; collision residue $(c/2)/z^3 + 2T/z$, pole orders one lower by $\mathrm{d}\log$ absorption):
the twisted cocycle condition~\eqref{eq:intro-mc-mixed} is the
Virasoro CYBE\@.
$\alpha_T^{\mathrm{op}}$ controls the genus-$0$ line-side braiding;
in the expected Virasoro realization this is modeled by the Virasoro
fusion kernel;
the quadratic term
$[\alpha_T^{\mathrm{mix}}, \alpha_T^{\mathrm{mix}}]_{\mathrm{op}}$
in~\eqref{eq:intro-mc-open} would then model the BPZ crossing kernel, with the
quartic contact interaction $\mathfrak{Q} = 10/[c(5c+22)]$
reappearing as a self-coupling of the mixed MC component.

The MC element and its colour decomposition live at genus~$0$.
What happens at higher genus?

\section*{Curved Swiss-cheese at genus $g$}

Volume~I's Theorem~D provides the modular characteristic
$\kappa(\cA)$: a scalar invariant of the chiral algebra
controlling the genus-$1$ curvature of the bar complex and,
conditionally after the Vol~I rectification, its higher-genus
scalar continuation.
In the Swiss-cheese setting, this curvature couples the
$\R$-factorisation to the Hodge bundle of
$\ov{\cM}_g$.

At genus~$1$, and conditionally for higher $g$, the bar complex
$\barB^{(g)}(\cA)$ carries a fibre differential $\dfib$ whose
square is formally written as
\begin{equation}
\label{eq:intro-curvature}
\dfib^{\,2} \;=\; \kappa(\cA) \cdot \omega_g,
\end{equation}
where $\omega_g = c_1(\lambda) \in H^2(\ov{\cM}_g, \Z)$ is
the first Chern class of the Hodge bundle. The coproduct $\Delta$ remains coassociative:
curvature is central in the coalgebra. The total corrected
differential $\Dg{g} = \dfib + \delta_g$ restores flatness over
$\ov{\cM}_g$ at the cost of coupling the $\R$-ordering to the
Hodge bundle.

The genus tower of curved Swiss-cheese algebras
$\{\barB^{(g)}(\cA), \dfib, \Delta\}_{g \geq 0}$ is controlled
by the $\hat{A}$-genus generating function of Volume~I,
where $\hat{A}(x) = (x/2)/\sinh(x/2)
= 1 - x^2/24 + 7x^4/5760 - \cdots$:
% RECTIFICATION-FLAG RESOLVED: \hbar^{2g-2} is the standard
% string convention (Euler characteristic weighting chi = 2-2g).
\[
\sum_{g \geq 0} \h^{2g-2} F_g(\cA)
\;=\;
\sum_{g \geq 0} \h^{2g-2}
\int_{\ov{\cM}_g} \hat{A}(\kappa(\cA) \cdot \omega_g).
\]
At genus~$0$, $\omega_0 = 0$ and the Swiss-cheese algebra is
flat: the uncurved theory. At genus~$1$,
$\omega_1 = c_1(\lambda) \in H^2(\overline{\cM}_1, \Z)$ is the Hodge class and the curvature
$d^2 = \kappa(\cA) \cdot \omega_1$ is the genus-$1$ obstruction;
the corrected free energy $F_1(\tau) = -\kappa(\cA)\log \eta(\tau)$
recovers the Dedekind $\eta$-function (with integrated value $\kappa(\cA)/24$).

The full genus tower is developed in Section~\ref{sec:bar_cobar}
and Part~\ref{part:examples} (Section~\ref{ch:modular-pva-quantization}). The
curvature at genus~$g \geq 2$ is resolved in Volume~I by
inductive genus determination
along with $2$D convergence and the analytic-algebraic comparison;
the analytic lane of MC5 is proved at all genera; BV=bar in
the coderived category is proved for all shadow classes
(Volume~I, Theorem~\ref*{V1-thm:bv-bar-coderived}); the genuswise
chain-level BV/BRST/bar identification remains conjectural
(class~M chain-level false).

\subsection*{The modular bar complex and its Feynman transform}

The genus-$g$ bar complex is one fibre of a larger object: the
\emph{complete modular bar coalgebra} $\Bmod(C)$
(Definition~\ref{def:complete-modular-bar}, \S\ref{ch:modular-pva-quantization}).
It is the completed product
\[
\Bmod(C)
\;=\;
\prod_{[\Gamma] \in \StGraph^{\mathrm{conn}}}
\bigl(C[\Gamma]\bigr)_{\Aut(\Gamma)},
\]
over isomorphism classes of connected stable graphs
(a connected graph with genus labelling $g\colon V(\Gamma) \to \Z_{\ge 0}$
and stability $2g(v) - 2 + \mathrm{val}(v) > 0$ at each vertex;
see Volume~I, \S\textup{Introduction}), with total
differential $D = D_{\mathrm{int}} + D_{\mathrm{exp}}$ squaring
to zero by codimension-two cancellation on boundary strata
(Theorem~\ref{thm:modular-bar}). The differential decomposes
into a genus-preserving part $D_0$ and a genus-raising part $D_1$:
\[
D_0^2 = 0,
\qquad
D_0 D_1 + D_1 D_0 = 0,
\qquad
D_1^2 = 0.
\]
The genus-raising operator $D_1 = D_{\mathrm{nsep}}$ sums over
nonseparating one-edge expansions: it is the algebraic shadow of
the first loop correction. Without it, every genus-zero structure
extends trivially to all genera; $D_1$ is the minimal primitive
that creates genuine modular obstructions.

The \emph{modular deformation dg~Lie algebra}
$L_{\mathrm{mod}}(C) = \Coder(\Bmod(C))[-1]$
(coderivations of a coalgebra form a Lie algebra under
commutator; the $[-1]$ shift makes the Maurer--Cartan equation
$d(x) + \tfrac{1}{2}[x,x] = 0$)
is a complete
filtered dg~Lie algebra whose genus-zero associated graded
\emph{is} the tree-level deformation complex, the chiral
convolution dg~Lie algebra of Volume~I\@. The modular
convolution algebra is its all-genus, all-stable-graph
completion. The total positive-genus correction
$\delta_\cA := D - D^{(0)}$ is a canonical Maurer--Cartan element
in the positive-genus ideal
(Theorem~\ref{thm:coderivation-MC-synthesis}):
\[
\partial\delta_\cA + \tfrac{1}{2}[\delta_\cA, \delta_\cA] = 0.
\]
The genus expansion $D = \sum_{g \ge 0} \hbar^g D^{(g)}$ is the
Feynman transform of the modular operad
$\{\overline{\cM}_{g,n}\}$. The identity $D^2 = 0$ decomposes
into sewing relations $\sum_{p+q=g} D^{(p)} D^{(q)} = 0$ at
each genus, and each graph carries the symmetry factor
$1/|\Aut(\Gamma)|$, the combinatorial fingerprint of a Feynman
expansion (Theorem~\ref{thm:formal-genus-expansion}).

\medskip\noindent\textbf{Genus completion and the chiral
convolution.}\enspace
The modular deformation algebra $L_{\mathrm{mod}}(C) =
\Coder(\Bmod(C))[-1]$ carries a complete genus filtration
satisfying the \emph{strong filtration axiom}
$\mu_r(F^{i_1}, \ldots, F^{i_r}) \subset F^{i_1 + \cdots + i_r}$
for the operations~$\mu_r$ and the exhaustive filtration~$F$
(this makes continuity and Mittag-Leffler automatic;
see Volume~I),
whose genus-$0$ associated graded is the \emph{chiral
convolution dg~Lie algebra}
$\mathfrak{g}^{\mathrm{ch}}_C = \Coder(\Bch(C))[-1]$, the
tree-level deformation complex of Volume~I
(Theorem~\ref{thm:genus-completion}):
\[
\renewcommand{\arraystretch}{1.3}
\begin{array}{@{}c|cc@{}}
 & \text{coalgebra} & \text{Lie algebra} \\
\hline
\text{genus } 0
 & \Bch(C) = \bar{B}^{(0)}(C)
 & \mathfrak{g}^{\mathrm{ch}}_C = \Coder(\Bch)[-1]
 \\
\text{all genera}
 & \Bmod(C) = \mathrm{FT}_{\cM\!od}(C)
 & L_{\mathrm{mod}}(C) = \Coder(\Bmod)[-1]
\end{array}
\]
The top row is the genus-$0$ shadow of the bottom row. The Lie
bracket on $L_{\mathrm{mod}}$ is a Chriss--Ginzburg correspondence
product, defined by the \emph{clutching maps} (the
boundary gluing maps
$\xi_{\mathrm{sep}}\colon \ov{\cM}_{g_1,n_1+1}
\times \ov{\cM}_{g_2,n_2+1} \to \ov{\cM}_{g,n}$
(separating node) and
$\xi_{\mathrm{ns}}\colon \ov{\cM}_{g-1,n+2} \to \ov{\cM}_{g,n}$
(non-separating node)) of the modular operad
(Remark~\ref{rem:convolution-as-correspondence}).
The positive-genus MC element
$\delta_\cA = D - D^{(0)}$ factorises along boundary strata
of $\overline{\cM}_{g,n}$
(Proposition~\ref{prop:factorisation-boundary-strata}):
separating nodes give
$\xi_{\mathrm{sep}}^*(\delta^{(g)}) = \sum_{g_1+g_2=g}
\delta^{(g_1)} \star \delta^{(g_2)}$; non-separating nodes give
$\xi_{\mathrm{ns}}^*(\delta^{(g)}) =
\Delta_{\mathrm{cyc}}(\delta^{(g-1)}) + \text{lower-genus terms}$.
In the language of Beilinson--Drinfeld, the chiral convolution is
factorisation homology $\int_{\Ran(X)} \End_\cA$ over the curve;
the modular convolution is $\int_{\cM\!od} \End_\cA$ over the
full moduli tower. The genus-$0$ projection recovers Volume~I's
universal twisting morphism; the positive-genus corrections form
the modular deformation data.

\subsection*{The half-space and the doubling principle}

The deformation-quantization bridge from PVA to vertex algebra
passes through the half-space. The PV sigma model of Khan--Zeng
on $\C \times \R_{\ge 0}$ with Neumann boundary produces a BV
theory whose boundary algebra is the sought vertex algebra. For
the affine family, the theory reduces to mixed BF/Chern--Simons
and is one-loop exact (Theorem~\ref{thm:affine-half-space-bv}).

For nonlinear PVAs, the problem requires all loop orders. The
\emph{doubling theorem} (Theorem~\ref{thm:doubling-rwi}) resolves
this: the half-space BV problem embeds into the doubled whole-space
$\C \times \R$ via the method of images. The reflected propagator
is the pullback of the standard propagator under the images
embedding; the reflected weight identity is the
$\sigma$-restriction of the standard Stokes identity. Every
logarithmic $\SCchtop$-algebra has a boundary vertex algebra
(Theorem~\ref{thm:general-half-space-bv}).

The logical chain is closed for all named examples: the affine PV
sigma model satisfies the physics bridge hypotheses
(Proposition~\ref{prop:affine-is-log-SC}), and DS reduction
preserves the $\SCchtop$ structure
(Proposition~\ref{prop:ds-preserves-SC}), so the Virasoro and
$\cW_N$ algebras inherit the full programme
(Corollary~\ref{cor:virasoro-wn-are-SC}).

The five-component datum (bulk factorization algebra, boundary
vertex algebra, scoped derived-center identification, scoped
line category, spectral $R$-matrix) assembles into a single theorem
(Theorem~\ref{thm:bulk-boundary-line-factorization}).


\section*{The topologisation theorem}

The $\SCchtop$ output admits a further structure when the
boundary algebra carries a conformal vector at non-critical
level: topologisation. The Sugawara construction
$T(z) = \frac{1}{2(k+h^\vee)}\sum_a {:}J^a J^a{:}(z)$ renders
$\C$-translations $Q$-exact in cohomology, collapses the two
colours of $\SCchtop$, and produces an $E_3$-topological algebra
on $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ by Dunn additivity
$\Etwo^{\mathrm{top}} \times \Eone^{\mathrm{top}} =
E_3^{\mathrm{top}}$: a three-dimensional topological quantum
field theory, independent of the complex structure on $\C$.

\begin{maintheorem}[Topologisation for affine Kac--Moody;
Theorem~\textup{\ref{thm:E3-topological-km}};
\ClaimStatusProvedHere]
\label{thm:intro-e3-km}
For affine Kac--Moody $\widehat{\fg}_k$ at non-critical level
$k \neq -h^\vee$ with simple $\fg$, the chiral derived centre
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\widehat{\fg}_k)$ carries an
$E_3$-topological structure. The 3d holomorphic-topological
theory is holomorphic Chern--Simons (Costello--Li, by
dimensional reduction from 6d holomorphic gauge theory).
\end{maintheorem}

\begin{maintheorem}[Topologisation via Drinfeld--Sokolov;
Theorems~\textup{\ref{thm:E3-topological-DS}}
and~\textup{\ref{thm:E3-topological-DS-general}};
\ClaimStatusProvedHere]
\label{thm:intro-e3-ds}
For every $W$-algebra obtained by Drinfeld--Sokolov reduction
of an affine Kac--Moody algebra at non-critical level, principal
or non-principal with arbitrary nilpotent orbit, the chiral
derived centre carries an $E_3$-topological structure. The 3d
theory is supplied by the Costello--Gaiotto theorem. The BRST
identity $T_{\mathrm{DS}} = [Q_{\mathrm{CS}}, G'_f]$ holds
because the improvement term $G'_f$ involves only Cartan
currents, which are $Q_{\mathrm{CS}}$-exact in the 3d bulk
regardless of the nilpotent orbit.
\end{maintheorem}

\begin{maintheorem}[Topologisation for free PVAs;
Theorem~\textup{\ref{thm:E3-topological-free-PVA}};
\ClaimStatusProvedHere]
\label{thm:intro-e3-free-PVA}
Every freely generated Poisson vertex algebra with conformal
vector at non-critical level admits an $E_3$-topological
structure on its chiral derived centre. The 3d theory is the
Khan--Zeng 3d Poisson sigma model.
\end{maintheorem}

Heisenberg and lattice VOAs reach $E_3$-topological as abelian
specialisations of Theorems~\ref{thm:E3-topological-km}
and~\ref{thm:E3-topological-free-PVA}, via abelian Sugawara
$T = (1/(2k))\!:JJ:$ and abelian Chern--Simons.

At the critical level $k = -h^\vee$ the Sugawara denominator
vanishes and no conformal vector exists: topologisation fails;
the centre jumps to the Feigin--Frenkel centre
$\mathfrak{z}(\widehat{\fg})$ of opers on $D^\times$; the pair
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),\, \cA)$ remains at
$\SCchtop$.

The modular operad $\SCchtop_{\mathrm{mod}}$ has composition at
integral level
(Theorem~\ref{thm:affine-composition-associativity}),
equivariance (Proposition~\ref{prop:qt-equivariance}), and
unitality (Proposition~\ref{prop:modular-operad-unitality})
proved at all genera. The sole remaining operadic gap is the
Stokes regularity of the KZB connection at generic non-integral
level, genus $\ge 1$: eigenvalue bounds on the principal series
of the Shapovalov form, not merely determinant bounds. Genus-$1$
curvature is unconditional,
$d_{\mathrm{fib}}^2 = \kappa(\cA) \cdot \omega_1$ via twisted
K\"unneth on $\FM_k(C_\tau)$
(Proposition~\ref{prop:genus1-twisted-tensor-product}). The
continuation to $g \ge 2$ engages two distinct $H^2$-obstruction
complexes: the modular-bootstrap complex, where $H^2 = 0$ is
proved (Theorem~\ref{thm:modular-bar}), and the curved-Dunn
twisting-cochain complex, where $H^2 = 0$ remains open. The
bridge between them is the precise frontier.


\section*{The programme climax}

Three pillars close the holographic equivalence unconditionally
on the standard landscape. Let $\cA$ be chirally Koszul at
generic parameter, lying anywhere in
\[
\{\,\mathrm{Vir}_c,\; W_{N, c}\ (N \ge 2),\; W(p)\ (p \ge 2),\;
 \text{Schellekens } c = 24,\;
 \mathrm{Com}(B, C)\ \text{irrational coset}\,\}.
\]

\begin{maintheorem}[Programme Climax: universal holography on
the standard landscape;
Theorem~\textup{\ref{thm:programme-climax}};
\ClaimStatusProvedHere]
\label{thm:intro-programme-climax}
There exists a canonical 3d holomorphic-topological gauge theory
$T_\cA$ on $X \times \R$ such that
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\mathrm{Obs}^\partial(T_\cA) \simeq \cA$ as
 $E_1$-chiral factorisation algebras on $X$;
\item $\mathrm{Obs}^{\mathrm{bulk}}(T_\cA) \simeq
 \cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ as $E_3$-topological
 factorisation algebras on $X \times \R$, the equivalence
 realised \emph{on the original complex} at the level of chain
 maps;
\item the Banach completion $\mathcal{B}_\rho(\cA)$ at radius
 $\rho < \rho_*(\cA) = |c|/\beta_\cA$ gives an explicit
 chain-level quasi-isomorphism to
 $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$, with
 \[
 \beta_\cA \;=\;
 \begin{cases}
 6 & \cA = \mathrm{Vir}_c, \\
 (N+1)(N+2)/2 & \cA = W_{N, c}, \\
 4p - 3 & \cA = W(p), \\
 6 \cdot |c_K(k)| & \cA = \mathrm{Com}(H_k, V_k(\mathfrak{sl}_2)),
 \end{cases}
 \]
 the Arnold coupling at the leading binary-collision residue.
\end{enumerate}
\end{maintheorem}

\noindent\textbf{The architecture has three pillars.}

\smallskip
\noindent\textbf{(1) Convergence (Stirling dominance).}\enspace
The shadow-tower coefficients satisfy
$\limsup_{r \to \infty}(|S_r(\cA)|/r!)^{1/r} = 0$
(Theorem~\ref{thm:tempered-stratum-contains-virasoro},
Theorem~\ref{thm:wn-tempered-all-N},
Theorem~\ref{thm:tempered-stratum-contains-wp},
Theorem~\ref{thm:irrational-coset-tempered}). The proof is
uniform: $(r!)^{1/r} \sim r/e$ grows without bound, so any
finite Arnold coupling $\beta_\cA$ forces
$|S_r(\cA)|^{1/r} \le \beta_\cA/|c|$, and the quotient tends to
zero. Stirling dominates any polynomial growth, and the ordinary
generating series $\sum_r S_r(\cA)\,\rho^r$ converges absolutely
for $\rho < \rho_*(\cA)$. The Arnold couplings are explicit as
listed in (iii).

\smallskip
\noindent\textbf{(2) Rigidity (bounded Zhu $+$
refinement).}\enspace
The Zhu algebra $\mathrm{Zhu}(\cA)$ controls Massey products on
bar cohomology; finite-dimensionality forces bounded Massey
matrix elements, hence polynomial-in-$r$ growth dominated by
Stirling. Every $C_2$-cofinite $\cA$ is tempered
(Lemma~\ref{lem:wp-zhu-bounded-masseys}).
The refinement is necessary. The witness
$K(\mathfrak{sl}_2, \sqrt{2})$ has infinite Zhu yet tempered
shadow growth
(Proposition~\ref{prop:zhu-unbounded-tempered-nontrivial});
Heisenberg branching of coset modules is polynomial in the
charge, not factorial
(Proposition~\ref{prop:heisenberg-branching-polynomial}). The
correct criterion is
\emph{VSKR + BGG}---Virasoro sub-channel in Kac-regular locus
plus bounded generator-to-generator OPE pole order
(Corollary~\ref{cor:tempered-criterion-refined}), strictly
weaker than $C_2$-cofiniteness. The converse of the
tempered-unbounded-Zhu conjecture is refuted
(Remark~\ref{rem:conjecture-tempered-unbounded-zhu-retracted}):
unbounded Zhu is \emph{not} an obstruction to tempering.

\smallskip
\noindent\textbf{(3) Gauge-theoretic (Costello--Gwilliam $+$
Dijkgraaf--Witten vanishing).}\enspace
The boundary algebra determines the 3d HT theory via the
Costello--Li factorisation envelope extended by the
Costello--Gwilliam orbifold BV mechanism. For class-M lattice-VOA
orbifolds, the Dijkgraaf--Witten anomaly
$\alpha \in H^3(B\Z/n;\, U(1))$ vanishes via the
Kapustin--Saulina formula
\[
\alpha \;=\; \mathrm{sign}(\det(1 - \sigma|_\Lambda)) \cdot
 \epsilon|_{\Lambda^\sigma}.
\]
The Monster vertex algebra $V^\natural$ closes through
$\Lambda^\sigma = 0$---Conway's theorem that the Leech lattice
has no roots
(Proposition~\ref{prop:monster-alpha-explicit-zero}), together
with the Frenkel--Lepowsky--Meurman twisted Jacobi associativity
and Dong--Mason quantum Galois gauge uniqueness. All seventy-one
Schellekens $c = 24$ holomorphic VOAs have $\alpha = 0$ via the
three-stratum classification
\[
71 \;=\; 24 + 1 + 46
\]
of pure Niemeier (trivial orbifold; abelian holomorphic CS),
Leech $\Z/2 = V^\natural$ (Conway shortcut), and Leech $\Z/n$
for $n = 3, \dots, 12$ (van~Ekeren--M\"oller--Scheithauer 2020
level-matching):
Theorem~\ref{thm:schellekens-71-all-alpha-zero}.

\smallskip
\noindent\textbf{Intersection.}\enspace
Convergence gives the Banach completion $\mathcal{B}_\rho(\cA)$.
Rigidity gives the bounded Massey structure that makes the
$E_3$-brace on $\mathcal{B}_\rho(\cA)$ chain-level exact, not
merely up to coherent homotopy. The gauge-theoretic pillar
identifies $\mathcal{B}_\rho(\cA)$ as the bulk factorisation
algebra of the Costello--Li 3d theory with Kapustin--Saulina
vanishing. Their intersection is the chain-level equivalence
$\mathrm{Obs}^{\mathrm{bulk}}(T_\cA) \simeq
\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ on the original complex.

\medskip
\noindent\textbf{Class~$\mathbf{M}$ global triangle closure.}\enspace
The DS--Hochschild compatibility gap is resolved: the chiral
higher Deligne identification
\[
\mathrm{ChirHoch}^\bullet(W_k(\fg))
\;\simeq\;
H^\bullet_{\mathrm{DS}}\bigl(\mathrm{ChirHoch}^\bullet(V_k(\fg))\bigr)
\]
(Theorem~\ref{thm:chd-ds-hochschild}) transports the chain-level
$E_2$-chiral Gerstenhaber structure from the affine locus
through DS reduction. Combined with the tempered-stratum heal,
the global triangle
$\Abulk \simeq \cZ^{\mathrm{der}}_{\mathrm{ch}}(\Bbound) \simeq
\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cC_{\mathrm{line}}) \simeq
\HH^\bullet_{\mathrm{ch}}(\cA^!_{\mathrm{line}})$
is unconditional at generic parameter across the entire standard
landscape, including class~$\mathbf{M}$
(Corollary~\ref{cor:universal-holography-class-M}).


\section*{The iterated-Sugawara endpoint: $E_3 \to E_\infty$}

Theorem~\ref{thm:intro-programme-climax} places the 3d theory on
a single rung of a ladder. The Virasoro conformal vector makes
$T_\cA$ $E_3$-topological; each additional higher-spin Casimir
current $T^{(n)}$ makes
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ $E_{n+2}$-topological
via the iterated-Sugawara construction
(Theorem~\ref{thm:iterated-sugawara-construction}). The endpoint
is $W_\infty[\lambda]$ at generic $\lambda$: an infinite stress
tower and an $E_\infty$-topological algebra.

\begin{maintheorem}[Infinite-rung ladder climax;
Theorem~\textup{\ref{thm:climax-w-infty-endpoint}};
\ClaimStatusProvedHere]
\label{thm:intro-climax-w-infty}
At every $\lambda \in \Lambda_{\mathrm{gen}} \subset \C$, the
$W_\infty[\lambda]$ algebra satisfies
\[
\cZ^{\mathrm{der}}_{\mathrm{ch}}(W_\infty[\lambda])
\;\in\;
E_\infty\text{-}\mathrm{top}\text{-}\mathrm{Alg}
\;=\;
\varprojlim_n E_n\text{-}\mathrm{top}\text{-}\mathrm{Alg},
\]
and the 3d theory $T_{W_\infty[\lambda]}$ is the $N \to \infty$
limit of the $E_3$-topological theories $T_{W_{N,c(N,\lambda)}}$.
\end{maintheorem}

The three convergence mechanisms agree on the common threshold
$N_0(w_{\max}) = 2w_{\max} - 1$:
Prochazka triangular truncation;
Creutzig--Kanade--Linshaw parafermion coset;
Pope--Romans--Shen together with Bakas wedge algebra. Each uses
disjoint machinery---vertex-algebraic Miura plus triangular
filtration; $\mathfrak{sl}_\infty$ parafermion; classical
symplectic Moyal quantisation---and each yields the same
threshold. The three-way agreement is structural
(Proposition~\ref{prop:uniform-threshold-2wmax-minus-1}): at any
fixed $w_{\max}$, the $N \ge N_0$ structure constants of
$W_N[\lambda]$ stabilise to those of $W_\infty[\lambda]$, and
the inverse limit in $E_\bullet$-topological algebras produces
the stated identification.

\medskip
\noindent\textbf{The climax as shadow.}\enspace
Part~\ref{part:gravity} (three-dimensional quantum gravity) is
the $N = 2$ \emph{shadow} of this $3d + \infty$ topological
endpoint. The Virasoro sector captures the spin-two content of
the tower; the full tower captures the spin-$n$ content for
every $n$. Pure 3d gravity admits a spin-ladder refinement with
infinite tower at $W_\infty[\lambda]$; the Brown--Henneaux
boundary $\mathrm{Vir}_c$ at $c = 3\ell/(2G)$ is the first rung
of a ladder climbing to $E_\infty$.

\medskip
\noindent\textbf{The three-volume junction.}\enspace
The three volumes meet at
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$. Volume~I describes it
algebraically (bar-cobar, Fuchsian ODE on all four Laurent
tiers, arithmetic duality locating Kummer-irregular primes by
Laurent depth). Volume~II describes it physically (tempered
stratum, Schellekens 71, Monster $V^\natural$, irrational
cosets, $W_\infty$ endpoint). Volume~III describes it
categorically (the CY-to-chiral functor $\Phi$, six-routes
pentagon with $\kappa_{\mathrm{ch}}$-stratification
$\{3, 12, 24\}$, super-Riccati with $\max(m, n)$
complementarity, $CY_4$ $p_1$-twisted double current algebra).
The three descriptions agree on the same chain complex.


\section*{Families: the standard landscape}

Five families beyond the Heisenberg, ordered by increasing complexity:

\subsection*{Free multiplet}

The free multiplet, a chiral algebra generated by a free boson
$\phi$ with OPE $\phi(z) \phi(w) \sim -\log(z - w)$, has
$m_{k \geq 3} = 0$: no higher $\Ainf$ operations. The bar
complex is strictly coassociative, the Swiss-cheese algebra is
\emph{formal} (quasi-isomorphic to its cohomology as an operad
algebra), and the $\R$-factorisation is exact. The PVA is
polynomial: $\{\phi {}_\lambda \phi\} = \lambda$. The spectral
$R$-matrix $R(z) = \exp(\hbar/z)$ is the universal abelian solution.
All higher structure is trivial.

\subsection*{Landau--Ginzburg: the first genuine $\Ainf$ correction}

A Landau--Ginzburg model with cubic superpotential
$W = \phi^3/3$ produces the first nontrivial~$m_3$. The
$\Ainf$ chiral algebra has:
\begin{itemize}
\item $m_1 = Q = \dbar + dW \wedge$, the Dolbeault differential
 twisted by the superpotential;
\item $m_2$ with $\lambda$-bracket $\{\phi {}_\lambda \phi\} =
 \lambda + \phi^2$;
\item $m_3 \neq 0$, computed from the cubic vertex of the BV
 action as a tree-level Feynman integral on
 $\FM_3(\C) \times \Conf_3^{<}(\R)$;
\item $m_{k \geq \deg W + 1} = 0$: the $\Ainf$ structure is
 finite, with truncation controlled by the degree of the
 superpotential
 (Proposition~\ref{prop:truncation_criterion}).
\end{itemize}
The transferred operations on cohomology
$H^\bullet = \C[\phi]/(dW)$ are tree-level Feynman sums; this is
the simplest setting where the homotopy transfer theorem of
Volume~I produces transferred operations as Feynman diagrams.

\subsection*{Abelian Chern--Simons: the braided atom}

Abelian $U(1)$ Chern--Simons theory at level~$k$ with a boundary
condition along $\C \times \{0\}$ produces:
\begin{itemize}
\item Boundary vertex algebra: $\widehat{\mathfrak{u}(1)}_k$,
 the Heisenberg algebra at level~$k$.
\item $\lambda$-bracket:
 $\{J {}_\lambda J\} = k\lambda$.
\item Classical $r$-matrix: $r(z) = k/z^2$ (the Laplace
 transform of $k\lambda$).
\item Quantum $R$-matrix: $R(z) = \exp(k\hbar/z)$, satisfying
 Yang--Baxter trivially (abelian).
\item Line operators:
 $\cC_{\mathrm{line}} \simeq
 Y(\mathfrak{u}(1))\text{-mod}
 \simeq \widehat{\mathfrak{u}(1)}_{-k}\text{-mod}$,
 the semisimple Fock sector.
\end{itemize}
The Yang--Baxter equation is verified directly from $\FM_3(\C)$:
the abelian case is exact (no loop corrections), and the
$R$-matrix is the exponential of the classical $r$-matrix. This
is the braided atom, the simplest family with nontrivial spectral
structure.

\subsection*{Affine $\widehat{\fg}_k$: the non-abelian test}

Affine $\widehat{\mathfrak{su}(2)}_k$ tests the full non-abelian
Swiss-cheese machine:
\begin{itemize}
\item $\lambda$-bracket:
 $\{J^a {}_\lambda J^b\} = f^{ab}_c J^c + k \delta^{ab} \lambda$,
 the affine Lie bracket.
\item $m_3 \neq 0$: from the cubic Casimir structure of the Jacobi
 identity. The $n = 3$ $\Ainf$ relation produces a nonvanishing
 $m_3$ whose chain-level existence is the homotopy for the failure
 of strict associativity in the Lie case.
\item Classical $r$-matrix: $r(z) = k\,\Omega / z$, where
 $\Omega = \sum_a J^a \otimes J^a$ is the Casimir element, the
 standard Lie-algebraic $r$-matrix at level~$k$.
\item Quantum $R$-matrix: on the reduced evaluation comparison surface in the affine lineage, the reduced HT monodromy is compared with the quantum-group braid representation and the spectral $R$-matrix agrees with the quantum group $R$-matrix of $U_q(\fg)$ at $q = e^{i\pi/(k+h^\vee)}$ (Theorem~\ref{thm:affine-monodromy-identification}).
\item Genus-$1$ curvature: $\kappa(\widehat{\fg}_k) = \dim\fg\,(k+h^\vee)/(2h^\vee)$, reproducing
 Volume~I's computation.
\item Chiral Koszul dual: $\cA^!_{\mathrm{ch}} = \mathrm{CE}^{\mathrm{ch}}(\widehat{\fg}_{-k-2h^\vee})$ (chiral CE algebra at the Feigin--Frenkel dual level).
 Line-operator Koszul dual: $\cA^!_{\mathrm{line}} = \Ydg(\fg)$, the dg-shifted Yangian of $\fg$.
\end{itemize}

\subsection*{Virasoro and $\mathcal{W}_3$: the nonlinear tests}

The Virasoro algebra ($\lambda$-bracket
$\{T {}_\lambda T\} = \partial T + 2T\lambda + (c/12)\lambda^3$,
in the Kac convention $\{a_\lambda b\} = \sum a_{(n)}b\,\lambda^n/n!$;
the OPE mode $T_{(3)}T = c/2$ therefore contributes $(c/2)/3! = c/12$ to the cubic $\lambda$-term)
and the $\mathcal{W}_3$ algebra have genuinely infinite $\Ainf$
structures:
\begin{itemize}
\item OPE poles of order~$4$ (Virasoro) and~$6$ ($\mathcal{W}_3$):
 the bar complex has non-vanishing coderivations in all degrees.
 The $\Ainf$ structure is genuinely infinite.
\item Recursive construction of $m_k$ from the BV master equation
 (Theorem~\ref{thm:vir-recursive}): each $m_k$ is computed as a
 tree-level Feynman sum on $\FM_k(\C) \times \Conf_k^{<}(\R)$,
 with the vertices determined by the interaction term
 $\eta \Pi^{ij}(\partial) \eta$ of the Khan--Zeng 3d HT Poisson
 sigma model.
\item Classical Yang--Baxter: the $\lambda$-bracket of Virasoro
 produces the Laplace kernel
 $r^L(z) = (c/2)/z^4 + 2T/z^2 + (\partial T)/z$
 (the Laplace transform $r^L(z) = \int_0^\infty e^{-\lambda z}\{T{}_\lambda T\}\,d\lambda$
 converts $\lambda$-bracket coefficients $\partial T, 2T, c/12$ to
 OPE poles $(\partial T)/z, 2T/z^2, (c/2)/z^4$) satisfying the
 CYBE on the Virasoro Lie algebra
 (Computation~\ref{comp:vir-CYBE}). The bar-theoretic collision
 residue is $r^{\mathrm{coll}}(z) = (c/2)/z^3 + 2T/z$ (pole
 orders one lower).
\item One-loop Virasoro complementarity constant:
 $\alpha_{\mathrm{Vir}} = 26$
 (Theorem~\ref{thm:central-charge-shift}), so the shift is
 $\Delta c = 13$. Combined with the known Virasoro duality
 $\operatorname{Vir}_c^! = \operatorname{Vir}_{26 - c}$, this gives
 self-duality at $c = 13$, not $c = 26$.
\item The $\cW_N$ Koszul involution
 (Theorem~\ref{thm:wn-koszul-involution}): the Koszul duality
 $\cW_N(c)^! = \cW_N(\alpha_N - c)$ acts by the involution
 $c \mapsto \alpha_N - c$, where
 $\alpha_N = 2(N-1)(2N^2 + 2N + 1)$ is the $\cW_N$
 complementarity constant (recovering $\alpha_2 = 26$ for
 Virasoro). Self-duality occurs at $c^* = \alpha_N/2$
 (for Virasoro, $c^* = 13$; for $\cW_3$, $c^* = 50$). The
 critical string point, where the total curvature
 $\kappa_{\mathrm{eff}} = \kappa(\mathrm{matter}) +
 \kappa(\mathrm{ghost})$ vanishes, is
 $c_{\mathrm{crit}} = \alpha_N$ (matter-ghost cancellation:
 $c = |c_{\mathrm{ghost}}| = \alpha_N$); for Virasoro,
 $c_{\mathrm{crit}} = 26$; for $\cW_3$,
 $c_{\mathrm{crit}} = 100$. Since
 $c_{\mathrm{crit}} = 2c^*$ for all~$N$, the self-dual point
 and the critical string point are always distinct.
\end{itemize}

Three-dimensional Einstein gravity with $\Lambda < 0$ is an
$\mathrm{SL}(2,\R)$ Chern--Simons theory at level
$k = \ell/(4G)$, and the boundary chiral algebra is
$\operatorname{Vir}_{6k}$, the Brown--Henneaux central charge.
The Laplace kernel
$r^L(z) = (c/2)/z^4 + 2T/z^2 + (\partial T)/z$ is read, in the
gravitational reading, as the graviton propagator in AdS${}_3$,
expanded in the holomorphic-topological framing. The shadow obstruction tower
of $\Ainf$ operations $m_3, m_4, \ldots$ is read as the
perturbative graviton-interaction hierarchy: in that reading,
$m_k$ contributes the corresponding $k$-graviton interaction data
on $\FM_k(\C) \times \Conf_k^{<}(\R)$, while genus tracks loop
order.
The genus expansion of the curved bar complex tracks
the loop expansion of the effective scalar partition function.
Finally, the derived centre
$\Zder(\operatorname{Vir}_c) \simeq \C[[c]]$ reflects the absence
of local degrees of freedom in pure 3d gravity: the bulk corner is
the derived centre of the Virasoro boundary algebra and is controlled
by a single parameter.
Section~\ref{sec:3d-gravity} develops these identifications in
full detail. A central result is the DS-HPL transfer theorem
(Theorem~\ref{thm:ds-hpl-transfer}): principal Drinfeld--Sokolov
reduction, realized as homological perturbation through the BRST
SDR, transfers the affine dg-shifted Yangian data to the
Virasoro side. The transferred $\Ainf$ products are genuinely
infinite (the quartic pole forces $m_3$, then $m_4$, and so on),
but the transferred coproduct is strictly primitive at all degrees
(Theorem~\ref{thm:gravitational-primitivity}): a ghost-number
obstruction kills every HPL tree correction. All gravitational
dynamics resides in the $r$-matrix, not in coproduct vertices.

Three further gravitational results emerge from the bar complex.
First, the $\Ainf$ structure produces an infinite tower of soft
graviton theorems (Theorem~\ref{thm:gravity-infinite-soft-tower}):
the degree-$r$ bar operation $m_r$ controls the soft graviton
identity at soft order $p = r - 2$, so that $m_2$ is Weinberg's
leading soft theorem, $m_3$ is the subleading Cachazo--Strominger
identity, and $m_4, m_5, \ldots$ are the sub${}^n$leading
identities in the shadow obstruction tower. The full hierarchy is the $\Ainf$
relations of the bar complex read in the gravitational frame.
Second, the genus tower measures the breaking of Wick-rotation
symmetry: $F_g \ne 0$ at every genus iff
$\kappa_{\mathrm{eff}} = (c{-}26)/2 \ne 0$, and the critical
string $c = 26$ is the unique locus of $S$-invariance of the
effective partition function. The conjectural Cardy entropy
$S_{\mathrm{Cardy}} = 2\pi\sqrt{ch/6}$
(Conjecture~\ref{conj:gravity-line-identification};
Conjecture~\ref{conj:gravity-cardy}) would be the
high-temperature shadow of this breaking, extracted by
composing the modular $S$-transform with the saddle-point
approximation.
Third, at genus~$1$ the bar differential acquires Eisenstein
weighting (Theorem~\ref{thm:genus-1-eisenstein}): the curved
differential on the elliptic surface is
$d_{\barB,\tau} = d_{\barB}^{(0)} + \sum_{k \geq 2}
G_{2k}(\tau)\, d_{\barB}^{(2k)}$,
where $G_{2k}(\tau)$ are the Eisenstein series and
$d_{\barB}^{(2k)}$ are the weight-$2k$ components of the bar
coderivation on the torus. The Eisenstein weighting is
the genus-$1$ avatar of the Hodge deformation from
Volume~I's Theorem~D: the modular parameter $\tau$ of the
elliptic curve enters through the period matrix, and the
Eisenstein series are the Fourier coefficients of the
propagator on the torus.


\section*{Volume~I in three dimensions: the mapping table}

Each of Volume~I's five theorems acquires a three-dimensional
reading through the Swiss-cheese lens. The following table records
the precise dictionary.

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{p{0.06\textwidth}p{0.25\textwidth}p{0.56\textwidth}}
\textbf{Thm} & \textbf{Volume~I} &
 \textbf{Three-dimensional reading} \\
\hline
\textbf{(A)} & Bar-cobar adjunction
 & Swiss-cheese presentation; Quillen equivalence for
 $\SCchtop$-algebras. The bar-cobar adjunction
 $(\Omega, \mathbf{B})$ on 2-coloured algebras is a Quillen
 equivalence by homotopy-Koszulity.
 (\S\ref{sec:foundations}, \S\ref{sec:bar-cobar}) \\[3pt]
\textbf{(B)} & Bar-cobar inversion
 & Raviolo VA descent: restriction to time-slices
 $\{t = \text{const}\}$ recovers raviolo vertex algebras via
 the bar-cobar counit $\Omegach(\barBch(\cA)) \to \cA$.
 The boundary vertex algebra is the cobar.
 (Appendix~\ref{sec:raviolo}) \\[3pt]
\textbf{(C)} & Complementarity
 & The Koszul triangle inherits the
 $(-1)$-shifted symplectic structure of complementarity:
 the bulk--boundary pairing is non-degenerate.
 $Q_g(\cA) + Q_g(\cA^!) = H^*(\ov{\cM}_g, Z(\cA))$.
 (\S\ref{sec:ht-bulk-boundary-line},
 \S\ref{sec:ambient-complementarity-chain-level}) \\[3pt]
\textbf{(D)} & Modular characteristic
 & Curved Swiss-cheese over $\ov{\cM}_g$:
 $\dfib^2 = \kappa(\cA) \cdot \omega_g$. The genus-$1$
 obstruction controls the free energy $F_1$.
 (\S\ref{sec:bar-cobar},
 \S\ref{ch:modular-pva-quantization}) \\[3pt]
\textbf{(H)} & Hochschild ring
 & Bulk $\simeq$ chiral Hochschild cochains; BV-BRST origin.
 The brace algebra on $\FM(\C) \times \Conf(\R)$ is the
 deformation algebra of the Swiss-cheese structure.
 (\S\ref{sec:chiral_hochschild_expanded},
 \S\ref{sec:chiral-Hochschild})
\end{tabular}
\end{center}

The following table refines the dictionary for each of the six
standard families:

\begin{center}
\renewcommand{\arraystretch}{1.25}
{\small
\begin{tabular}{p{0.12\textwidth}p{0.11\textwidth}p{0.11\textwidth}p{0.10\textwidth}p{0.11\textwidth}p{0.11\textwidth}p{0.18\textwidth}}
& \textbf{Heis.} & \textbf{Free} &
 \textbf{LG} & \textbf{CS} &
 \textbf{$\widehat{\fg}_k$} &
 \textbf{$\operatorname{Vir}_c$} \\
\hline
$m_{\geq 3}$ & $= 0$ & $= 0$ & finite & $= 0$ &
 $\neq 0$ & $\neq 0$, $\infty$ \\
PVA type & poly & poly & poly & poly &
 Lie & nonlinear \\
$r^L(z)$\,$^*$ & $k/z^2$ & $1/z^2$ & n/a & $k/z^2$ &
 $k\,\Omega/z$ &
 $\frac{c/2}{z^4} + \frac{2T}{z^2} + \frac{\partial T}{z}$ \\
$R(z)$ & $e^{k\hbar/z}$ & $e^{\hbar/z}$ & trivial & $e^{k\hbar/z}$ &
 Drinfeld & exp.\ model via fusion kernel \\
$\kappa$ & $k$ & $1$ & $0$ & $k$ &
 $\frac{(k{+}h^\vee)\dim\fg}{2h^\vee}$ & $c/2$ \\
$\cA^!_{\mathrm{ch}}$ & $\mathrm{Sym}^{\mathrm{ch}}(V^*)$ & $\mathrm{Sym}^{\mathrm{ch}}(V^*)$ & $\cA^!_W$ &
 $\mathrm{Sym}^{\mathrm{ch}}(V^*)$ &
 $\widehat{\fg}_{-k-2h^\vee}$ &
 $\operatorname{Vir}_{26 - c}$ \\
$\cA^!_{\mathrm{line}}$ & $Y(\mathfrak{u}(1))$ & n/a & n/a &
 $Y(\mathfrak{u}(1))$ &
 $\Ydg(\fg)$ &
 exp.\ model via $\operatorname{Vir}_{26 - c}$ \\
Lines & Fock & $\Vect$ & fin.\ dim. &
 Fock &
 $\Ydg(\fg)\text{-mod}$ &
 exp.\ model via $\operatorname{Vir}_{26 - c}\text{-mod}$
\end{tabular}
}
\end{center}
\noindent{\footnotesize ${}^*$Laplace kernel
$r^L(z) = \int_0^\infty e^{-\lambda z}\{{\cdot}{}_\lambda{\cdot}\}\,d\lambda$
(the OPE generating function).
The bar-theoretic collision residue
$r^{\mathrm{coll}}(z)$ has pole orders one lower:
for Virasoro, $r^{\mathrm{coll}}(z) = (c/2)/z^3 + 2T/z$
(as recalled in Volume~I's discussion of the three related kernels:
OPE, Laplace kernel, and collision residue).}\smallskip

\smallskip\noindent
The table distinguishes two Koszul duals. The \emph{chiral Koszul dual} $\cA^!_{\mathrm{ch}}$ (in the Francis--Gaitsgory sense) is the vertex algebra obtained by Verdier duality on the chiral symmetric bar coalgebra (Volume~I, Theorem~A: $D_{\mathrm{Ran}}(\barBch(\cA)) \simeq \barBch(\cA^!)$); for affine Kac--Moody, $\cA^!_{\mathrm{ch}} = \mathrm{CE}^{\mathrm{ch}}(\widehat{\fg}_{-k-2h^\vee})$ has the same modular characteristic as the Feigin--Frenkel dual level (the Koszul dual is the chiral CE algebra, not $\widehat{\fg}_{-k-2h^\vee}$ itself). The \emph{line-side Koszul dual} $\cA^!_{\mathrm{line}}$ is the $E_1$ Koszul dual obtained from the ordered bar $\barB^{\mathrm{ord}}(\cA)$; in the standard affine HT gauge realization, $\cA^!_{\mathrm{line}} = \Ydg(\fg)$, the dg-shifted Yangian identified by Theorem~\ref{thm:Koszul_dual_Yangian}. On the chirally Koszul locus, the line category is modeled by modules for $\cA^!_{\mathrm{line}}$ via Theorem~\ref{thm:lines_as_modules}. For the Heisenberg, $\cA^!_{\mathrm{ch}} = \mathrm{Sym}^{\mathrm{ch}}(V^*)$ (note $\cH_k^! \neq \cH_{-k}$: the chiral Koszul dual is the chiral symmetric algebra on the dual space, not the Heisenberg at negative level), while $\cA^!_{\mathrm{line}} = Y(\mathfrak{u}(1))$ (the abelian Yangian, with $\kappa = -k$) has modules forming the semisimple Fock-module line category. For Virasoro, the chiral dual is $\operatorname{Vir}_{26-c}$, while the matching line-side Virasoro-module picture is expected and used heuristically but is not isolated as a separate theorem on the live surface.


\section*{Strict models and homotopy-coherent invariants}

Every strict dg structure in this volume (dg Lie algebras,
dg categories, bar and cobar complexes) is one chart on a larger
homotopy-coherent object. The strict model is used for
computation; the homotopy-coherent package is the invariant.
Five manifestations:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The $\SCchtop$-algebra structure is a
 $C_\ast(W(\SCchtop))$-algebra, not a strict operad algebra.
 The rectification theorem
 (Theorem~\ref{thm:rectification}) identifies when strict and
 homotopy-coherent presentations coincide (this requires
 \emph{tameness} (truncation $m_k=0$ for $k\gg0$) or,
 failing that, completion of the cofree coalgebra;
 see Definition~\ref{def:tameness}).
\item Chiral Hochschild cochains form a \emph{brace algebra}
 (a graded vector space with operations
 $M\{a_1,\ldots,a_n\}$ whose antisymmetrisation gives the
 Gerstenhaber bracket
 $[a,b] = a\{b\} - (-1)^{|a||b|}\, b\{a\}$;
 Section~\ref{sec:chiral-Hochschild}), whose Gerstenhaber
 bracket is the binary Taylor coefficient of the filtered
 $\Linf$-structure governing deformations.
\item The bulk--boundary--line triangle is invariant only up to
 derived/Morita and $\Linf$ equivalence. The triangle becomes
 false if any vertex is artificially strictified.
\item The spectral $R$-matrix is a component of a
 homotopy-coherent braiding on the $\Ainf$-module category; the
 Yang--Baxter equation is one coherence law among many.
\item The genus tower of curved Swiss-cheese algebras over
 $\ov{\cM}_g$ is a genus-filtered $\Linf$-object;
 the strict dg model at each genus is a truncation whose
 higher coherences are the source of the modular corrections
 from Volume~I's Theorem~D.
\end{enumerate}

\noindent
Convention~\ref{conv:vol2-strict-models}: every strict dg structure
is one chart on an underlying homotopy deformation object.

\subsection*{The boundary of control}

Volume~I's algebraic engine controls everything inside the modular
Koszul locus. The boundary of that locus is determined by four
independent tests, each representing a genuine barrier that the
engine does not cross: (i)~the DK-3 categorical test (the engine
produces the $r$-matrix but not the full quantum group);
(ii)~the lattice-only arithmetic test (the engine computes
symmetric-power moments but does not prove their automorphy);
(iii)~the chirally Koszul geometric test (the engine works inside
the Koszul world but does not detect whether an algebra is Koszul);
and (iv)~the shadow radius $\rho < 1$ analytic test (the engine
computes shadow coefficients at every finite degree but does not sum
the series when $\rho \geq 1$). This volume operates inside the
same four-test boundary: the Swiss-cheese, PVA, and Yangian
structures are constructed for all logarithmic $\SCchtop$-algebras
satisfying chiral Koszulness, and the frontier material of Part~\ref{part:frontier}
probes the boundary where those tests fail.


\section*{Plan of the volume}

The volume has seven parts, each building on the previous.

\medskip
\noindent\textbf{Part~\ref{part:swiss-cheese}: The Open Primitive}
(\S\ref{sec:foundations}--\S\ref{sec:Ainfty-to-PVA}).
The structural heart of the volume. The two-coloured operad
$\SCchtop$ is defined
(Section~\ref{sec:HT-operad}), and the bar complex of a chiral
algebra is shown to be an $E_1$ chiral coassociative coalgebra
whose two-coloured configuration-space parametrisation
recovers the $\SCchtop$ operation spaces
(Section~\ref{sec:foundations}). The concrete $\Ainf$ chiral
axioms on~$\cA$ are extracted
(Section~\ref{sec:axioms-Ainfty-chiral}) and proved equivalent to
$W(\SCchtop)$-algebra structure on~$\cA$
(Section~\ref{sec:equivalence}). The Fulton--MacPherson calculus
(Section~\ref{sec:FM_calculus}) supplies the geometric proofs: the
$\Ainf$ relations are Stokes' theorem on boundary strata of
$\FM_k(\C)$, with explicit formulas for~$m_2$ and~$m_3$
(Propositions~\ref{prop:m2_formula} and~\ref{prop:m3_formula}).
The BV-BRST construction
(Section~\ref{sec:BV_construction}) shows that BV quantisation of
a 3d HT field theory on $\C \times \R$ produces exactly these
bar complexes (Theorem~\ref{thm:Obs-is-SC}).
Two descent mechanisms then extract invariants from the bar complex.
Cohomological descent produces the $(-1)$-shifted PVA on
cohomology (Theorem~\ref{thm:cohomology_PVA}), with the
regular/singular decomposition of~$m_2$ yielding the product and
$\lambda$-bracket (Section~\ref{sec:PVA_descent},
Section~\ref{sec:Ainfty-to-PVA}).

\medskip
\noindent\textbf{Part~\ref{part:e1-core}: The $E_1$ Core}
(\S\ref{sec:bar_cobar}--\S\ref{chap:dg-shifted-factorization}).
The ordered bar coalgebra $B^{\mathrm{ord}}(\cA) = T^c(s^{-1}\bar\cA)$
with deconcatenation coproduct is the native object of the
Swiss-cheese open colour; it carries strictly more data than the
symmetric bar of Volume~I. The chiral bar--cobar
review (Section~\ref{sec:bar_cobar}) places the quadratic duality
of Gui--Li--Zeng in context and extends it beyond the quadratic
locus. Line operators carry modules for the open-colour Koszul
dual~$\cA^!_{\mathrm{line}}$.
The ordered associative side of chiral Koszul duality
carries its own bar--cobar theory, diagonal
bicomodule, and open trace; the $E_1$
projection is developed as the primary wing of the Swiss-cheese structure.
Homotopy-Koszulity of~$\SCchtop$ is proved
(Theorem~\ref{thm:homotopy-Koszul}), yielding the Quillen
equivalence (Theorem~\ref{thm:bar-cobar-adjunction}). On the
chirally Koszul locus, the line side is modeled by
$\cA^!_{\mathrm{line}}$-modules
(Theorem~\ref{thm:lines_as_modules}), the spectral $R$-matrix
is constructed (Definition~\ref{def:spectral-braiding}) and shown
to satisfy Yang--Baxter (Theorem~\ref{thm:YBE}), and the
open-colour Koszul dual carries the dg-shifted
Yangian package (Theorem~\ref{thm:yangian-recognition}).
The spectral Drinfeld class controlling strictification
of spectral quasi-factorization data vanishes
at every filtration for every simple Lie algebra
(Theorem~\ref{thm:complete-strictification}), via a root-multiplicity-one
rigidity principle and the Dynkin projection.
The loop-order spectral sequence on the bar complex
gives a width bound for bar cohomology
(Theorem~\ref{thm:width-bound}), one-loop exactness implies chiral
Koszulness before Drinfeld--Sokolov reduction
(Theorem~\ref{thm:one-loop-koszul}), and principal DS reduction
breaks Swiss-cheese formality (but not Koszulness) for Virasoro
and $W_N$ via homological transfer
(Theorem~\ref{thm:ds-koszul-obstruction}).

\medskip
\noindent\textbf{Part~\ref{part:bbl-core}: The Seven Faces of $r(z)$}
(\S\ref{sec:ht-bulk-boundary-line}--\S\ref{chap:fm3-planted-forest-synthesis}).
The collision residue $r(z) = \mathrm{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$
is a single object appearing in seven guises: the Drinfeld--Kohno
associator, the spectral $R$-matrix satisfying Yang--Baxter, the
Sklyanin classical $r$-matrix, the Koszul-dual line-side modeling
algebra, the celestial OPE, the dg-shifted Yangian, and the
holographic boundary-to-bulk map.
The bulk--boundary--line chapter
(Section~\ref{sec:ht-bulk-boundary-line}) proves the corrected
triangle in the exact boundary-linear sector
(Theorem~\ref{thm:boundary-linear-bulk-boundary}) and develops
the full machinery of Thom--Sebastiani multiplicativity
($\varphi_{f+g} \simeq \varphi_f \otimes \varphi_g$;
Theorem~\ref{thm:TS}), Clifford stabilisation
(Theorem~\ref{thm:clifford-stab}), boundary Kuranishi elimination
(Theorem~\ref{thm:boundary-kuranishi}), and polarised
reconstruction (Theorem~\ref{thm:polarized-reconstruction}). The
celestial boundary transfer chapter
(Section~\ref{sec:modular-twisted-celestial-first-principles})
lifts the triangle to celestial and twisted holography.
The affine half-space BV theorem
(Theorem~\ref{thm:affine-half-space-bv}) solves the quantisation
problem for affine Kac--Moody algebras: half-space BV quantisation
produces~$\widehat{\fg}_k$ at a shifted level, with
Drinfeld--Sokolov reduction transporting the result to Virasoro
and~$\mathcal{W}_3$. The FM$_3$ planted-forest synthesis
(Section~\ref{chap:fm3-planted-forest-synthesis}) isolates the
first nonlinear obstruction via the planted-forest $\Linf$ model.

\medskip
\noindent\textbf{Part~\ref{part:examples}: The Characteristic Datum and Modularity}
(\S\ref{sec:rosetta-stone}--\S\ref{ch:ht-boundary}).
Each algebra family in Volume~I's standard landscape is a
test case for the full open/closed architecture.
The Heisenberg Rosetta
Stone (Section~\ref{sec:rosetta-stone}) translates every new
object (Swiss-cheese operations, brace structure, PVA,
$R$-matrix, line operators, curved genus-$1$ complex, Hochschild
duality) into the simplest concrete language, verifying each
against the corresponding theorem of Volume~I
(Theorem~\ref{thm:rosetta-e1-coalgebra},
Proposition~\ref{prop:rosetta-pva},
Theorem~\ref{thm:rosetta-curved},
Proposition~\ref{prop:rosetta-bar-hochschild},
Theorem~\ref{thm:rosetta-3d-mc}). The free multiplet has
$m_{k \geq 3} = 0$: the bar complex is strictly coassociative,
the Swiss-cheese algebra is formal, the PVA is polynomial
(Proposition~\ref{prop:free_cohomology_complete}). The
Landau--Ginzburg model has nontrivial~$m_3$, a genuine $\Ainf$
correction from the superpotential, with truncation controlled
by degree (Theorem~\ref{thm:LG_truncation},
Proposition~\ref{prop:LG_m3_formula}). Abelian Chern--Simons
with boundary produces an explicit spectral $R$-matrix solving
Yang--Baxter (Theorem~\ref{thm:CS_boundary}). The affine
$\widehat{\mathfrak{su}(2)}_k$ example tests the full non-abelian
machine: non-trivial $\lambda$-bracket, $m_3$ from the Jacobi
identity, truncation, PVA, Yangian, and genus-$1$ curvature
$\kappa = \dim\fg\,(k+h^\vee)/(2h^\vee)$ (Propositions~\ref{prop:su2-lambda-bracket}
--\ref{prop:su2-curvature}). The $\mathcal{W}$-algebra chapter
(Section~\ref{sec:W-algebras}) treats Virasoro and~$\mathcal{W}_3$
as the decisive non-linear tests: recursive $m_k$ from the BV
master equation (Theorem~\ref{thm:vir-recursive},
Theorem~\ref{thm:w3-recursive}), classical Yang--Baxter from the
 $\lambda$-bracket Jacobi identity
 (Computation~\ref{comp:vir-CYBE} for Virasoro and
 Theorem~\ref{thm:w3-CYBE} for $\mathcal{W}_3$), and the one-loop
 central-charge/complementarity formula
 (Theorem~\ref{thm:central-charge-shift}).
Chiral Hochschild cohomology
(Section~\ref{sec:chiral_hochschild_expanded}) identifies bulk
observables with Hochschild-type cochains, bridging the 2d Poisson
sigma model to the 3d HT setting via dimensional descent
(Theorem~\ref{thm:2d_PSM_Hochschild}).
Chiral Hochschild cochains form a brace
algebra on $\FM(\C) \times \Conf(\R)$
(Section~\ref{sec:chiral-Hochschild}), whose Gerstenhaber bracket
governs deformations.
The genus-zero Swiss-cheese operad is the proved starting point.
Extending it to a full modular operad by adjoining clutching maps on
the closed colour is the higher-genus open problem; when such an
extension exists, its Feynman transform produces the universal
Maurer--Cartan equation for the genus tower.
The modular PVA
quantisation chapter
(Section~\ref{ch:modular-pva-quantization}) develops the
stable-graph modular bar construction
(Theorem~\ref{thm:modular-bar}), the universal genus-$1$
obstruction (Theorem~\ref{thm:Ob1}), the higher-genus recursion
(Theorem~\ref{thm:Obg}), and the variational modular class
(Theorem~\ref{thm:modclass}).
The physical origins chapter connects to 4d/2d correspondences, gauge
theories, and D-brane algebras.

\medskip
\noindent\textbf{Part~\ref{part:holography}: The Standard HT Landscape}
(Chapters~\ref{ch:ym-boundary-theory}--\ref{ch:ym-instanton-screening}
and Appendix~\ref{app:anomaly-completed-topological-holography}).
The holographic programme proceeds through four movements:
Yang--Mills boundary theory with instanton completion and
screening (Chapters~\ref{ch:ym-boundary-theory}--\ref{ch:ym-instanton-screening});
celestial and twisted holography made modular
(Section~\ref{sec:modular-twisted-celestial-first-principles});
logarithmic HT monodromy from shifted KZ connections and the
$\Ainf$ collision theory
(Section~\ref{chap:log-ht-monodromy},
Theorem~\ref{thm:synthesis}, Theorem~\ref{thm:master-curvature};
five structural levels in
Convention~\ref{conv:five-levels-log-ht});
and anomaly-completed topological holography
(Section~\ref{app:anomaly-completed-topological-holography}),
where the transgression algebra packages the bulk--boundary--line
triangle with its genus tower into a single dg algebra.
For the affine lineage, on the reduced evaluation comparison surface
the monodromy of the reduced HT logarithmic connection is compared
with the corresponding quantum-group braid representation, and the
spectral $R$-matrix agrees with the quantum group $R$-matrix
\textup{(}Theorem~\textup{\ref{thm:affine-monodromy-identification}}\textup{)}: one-loop
exactness collapses the $A_\infty$ tower, and on that same surface the
reduced connection identifies with the KZ connection
(Theorem~\ref{thm:reduced-equals-kz}), while
$\cC_{\mathrm{line}}^{\mathrm{red}}|_{\mathrm{eval}} \simeq
\mathrm{Rep}_q(\fg)$ at $q = e^{i\pi/(k+h^\vee)}$
(Corollary~\ref{cor:affine-line-category}). The bar complex
computes the colored Jones polynomial
(Corollary~\ref{cor:jones-polynomial}).
Holographic reconstruction and the modular bootstrap
complete the holographic programme.

\medskip
\noindent\textbf{Part~\ref{part:gravity}: Three-Dimensional Quantum Gravity.}
The climax.
The Virasoro $\lambda$-bracket
$\{T_\lambda T\} = \partial T + 2T\lambda + (c/12)\lambda^3$
generates the full gravitational theory.
The quartic pole forces the infinite $\Ainf$ tower, the Koszul
involution $c \mapsto 26 - c$, the curvature $\kappa = c/2$, and the
genus expansion.
Three-dimensional gravity provides the first test of the full
obstruction tower. The critical string dichotomy at $c = 26$
is the algebraic origin of the bosonic string; at $c = 26$ the
shadow tower terminates and perturbative finiteness follows.
Soft graviton theorems, symplectic polarization, and the gravitational
Yangian complete the gravitational programme.

\medskip
\noindent\textbf{Part~\ref{part:frontier}: Extensions, Conditional Results, and Frontier.}
The chapters in this part extend the proved core of
Parts~\ref{part:swiss-cheese}--\ref{part:gravity} into conditional, conjectural, and frontier territory.
Every result here either depends on additional unproved analytic input
beyond the logarithmic $\SCchtop$ framework, carries conjectural
status, or develops directions that are not yet fully resolved.
No earlier part depends on material in this part.
For any logarithmic $\SCchtop$-algebra (Definition~\ref{def:log-SC-algebra}), every freely generated Poisson vertex
algebra with inner holomorphic translation deformation-quantizes to
a vertex algebra on the half-space
(Theorem~\ref{thm:general-half-space-bv}), proved by a doubling
construction that embeds the half-space reflected weight identity
into the standard whole-space Stokes identity
(Theorem~\ref{thm:doubling-rwi}).

\medskip
\noindent\textbf{Appendices.} Raviolo vertex algebras
(Appendix~\ref{sec:raviolo}) supply the comparison with the
Garner--Williams framework: restriction to time-slices recovers
raviolo VAs via the bar-cobar counit
(Proposition~\ref{prop:raviolo-VA},
Theorem~\ref{thm:raviolo-PVA}).
The expanded raviolo restriction
(Appendix~\ref{sec:raviolo-expanded}) develops the \v{C}ech/Thom--Sullivan
model and coinvariants. Further appendices collect brace-algebra
sign conventions, FM orientation conventions, and expanded PVA
proofs.

\medskip
\noindent\textbf{What is new.}\enspace
This edition incorporates several results proved since the initial circulation: the $\mathcal{W}_3$ $W$-line shadow admits a Catalan closed form (Theorem~\ref{thm:w3-w-line-closed-form}), the celestial OPE coefficients are computable from the shadow degree decomposition (Remark~\ref{rem:celestial-ope-shadow-degree}), and the Bekenstein--Hawking entropy formula is derivable from the shadow CohFT at the perturbative level (Remark~\ref{rem:bh-shadow-cohft}).


\section*{Reading this volume}

\noindent\textbf{Three entry points.}
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Via the Heisenberg.}
 Rosetta Stone (\S\ref{sec:rosetta-stone}) $\to$
 Foundations (\S\ref{sec:foundations}) $\to$
 PVA descent (\S\ref{sec:PVA_descent}) $\to$
 worked examples (\S\ref{sec:examples_complete}).
\item \emph{Complete theory.}
 Part~\ref{part:swiss-cheese} linearly, then Part~\ref{part:e1-core} (the $E_1$ core), then
 Parts~\ref{part:bbl-core}--\ref{part:examples} (seven faces, examples, modularity).
\item \emph{Physics entry.}
 BV construction (\S\ref{sec:BV_construction}) $\to$
 FM calculus (\S\ref{sec:FM_calculus}) $\to$
 Rosetta Stone (\S\ref{sec:rosetta-stone}) $\to$
 YM synthesis (Chapters~\ref{ch:ym-boundary-theory}--\ref{ch:ym-instanton-screening}).
\end{enumerate}
Part~\ref{part:swiss-cheese} builds the Swiss-cheese identification and the classical
shadow (PVA descent). Part~\ref{part:e1-core} develops the ordered bar complex,
the $E_1$ core, line operators, and the dg-shifted Yangian package.
Part~\ref{part:bbl-core} exhibits the seven faces of the collision residue $r(z)$:
the bulk--boundary--line triangle, celestial transfer, the affine
half-space BV theorem, and the planted-forest synthesis.
Part~\ref{part:examples} tests the machine on five families (the Rosetta Stone and
standard landscape), develops chiral Hochschild cohomology and braces,
and treats modularity as trace and clutching via the modular operad.
Part~\ref{part:holography} treats the standard HT landscape: Yang--Mills, celestial
holography, logarithmic monodromy, and anomaly completion.
Part~\ref{part:gravity} is the climax: three-dimensional quantum gravity.
Part~\ref{part:frontier} collects extensions and conditional results; no earlier
part depends on it.
