%% =====================================================================
%% logarithmic_wp_tempered_analysis_platonic.tex
%%
%% Frontier analysis: tempered-stratum membership of the logarithmic
%% W(p) triplet algebra, p >= 2 (Adamovic-Milas 2008; Kausch 1991;
%% Feigin-Gainutdinov-Semikhatov-Tipunin 2006).
%%
%% Prior state (tempered_stratum_characterization_platonic.tex,
%% Vol II commit a4277d7, 2026-04-16):
%%
%% * Generic Vir_c is analytically tempered
%% (thm:tempered-stratum-contains-virasoro) with rho_*(c) = c/6.
%% * Generic principal W_{3,c} is analytically tempered
%% (thm:tempered-stratum-contains-w3) with rho_*^{W_3}(c) = c/10.
%% * Principal W_N for N >= 4: tempering is conjectural
%% (conj:wn-tempered-general).
%% * Logarithmic W(p) triplet: left explicitly open in
%% cor:original-complex-dichotomy-healed as one of the "three
%% candidates for a non-empty generic stratum": (i) W(p)
%% logarithmic; (ii) Monster-type twisted sectors; (iii) coset
%% realisations with irrational central charge.
%%
%% This chapter attacks the W(p) frontier and isolates the proved core
%% from the remaining regular-sector conjecture. Three parallel
%% analyses:
%%
%% (A) ATTACK. W(p), p >= 2, is class M* (non-freely-generated PVA)
%% with 4 strong generators (T, W^+, W^0, W^-), OPE pole order
%% 2(2p-1) in the W-W channel, and a genuine Massey product
%% <Omega, Omega, Omega> detecting the null-vector ideal
%%. Standard Riccati recurrence does not apply in direct
%% form because of non-freely-generated strong generation.
%%
%% (B) REDUCTION via a three-channel decomposition. The W(p) shadow
%% sequence {S_r(W(p))}_{r >= 2} splits into:
%% (i) a Virasoro sub-channel with leading rate
%% beta_{TT} = 6 at c = c(p), proved tempered;
%% (ii) a mixed TW channel with simple-pole r-matrix
%% (primary-field OPE), conjectural regular-sector bound;
%% (iii) a W-W channel with r-matrix pole order 4p - 3, feeding
%% into the shadow tower through Adamovic-Milas
%% character-amplitude data, conjectural for all p >= 2.
%%
%% (C) HONEST STATUS. The TT sub-channel is proved tempered for all
%% p >= 2. The full W(2) algebra is the first toy case for the
%% finite pole-envelope model; factorisation of the real triplet
%% shadow into that model remains open. Universal W(p) tempering
%% remains Conjecture
%% conj:tempered-stratum-contains-wp. The retracted bounded-Zhu-
%% Massey argument does not prove TW/WW regular-sector bounds.
%%
%% (D) p = 2 CASE (symplectic fermions). W(2) has c(2) = -2,
%% weight-three triplet fields, WW pole order 6, and
%% dim A(W(2)) = 4. The compute surface contains the T-line and
%% finite pole-envelope constants; full triplet shadow coefficients
%% remain to be computed.
%%
%% (E) The genuine non-tempered frontier is now split: W(p), p >= 2
%% is open only in the regular shadow sector, while separate
%% non-tempered candidates with infinite-dimensional Zhu algebra
%% remain outside the C_2-cofinite standard landscape.
%%
%% Labels defined:
%% def:wp-shadow-channel-decomposition
%% prop:wp-channel-upper-bounds (conjectural outside TT)
%% lem:wp-zhu-bounded-masseys (retracted from ProvedHere)
%% prop:wp-c2-forbids-finite-free-strong-generation
%% conj:wp-regular-sector-amplitude-bound
%% lem:wp-virasoro-subchannel-tempered
%% prop:wp-finite-pole-envelope-reduction
%% conj:tempered-stratum-contains-wp
%% cor:wp-dichotomy-healed
%% rem:wp-non-frontier-after-present-chapter
%% conj:tempered-unbounded-zhu (new explicit frontier)
%%
%% Location: chapters/theory/.
%% Inputs:
%% chapters/theory/tempered_stratum_characterization_platonic.tex
%% (universal Virasoro tempering; rho_*(c) = c/6; Stirling machinery)
%% chapters/theory/topologization_class_m_original_complex_platonic.tex
%% (KS-rho Banach framework; curved-Dunn complex)
%% Vol I compute/lib/logarithmic_voa_shadow_engine.py
%% (W(p) central charge, generator data, screening parameters;
%% the engine of record for W(p) structure constants)
%% Vol I compute/lib/wp_koszulness_definitive_engine.py
%% (PBW character vs actual vacuum character;
%% Adamovic-Milas null-vector placement; Zhu algebra structure)
%% Vol I compute/lib/triplet_wp_character_engine.py
%% (FGST theta-character for W(p))
%% Vol I chapters/theory/shadow_tower_higher_coefficients.tex
%% (Laurent asymptotic closed forms)
%%
%% STATUS DIRECTIVE (Beilinson reread):
%% The strongest honest form is TT-channel tempering for all p and
%% conjectural regular-sector tempering for the full triplet. The
%% bounded-Zhu Massey route is retracted.
%% =====================================================================

\chapter{Logarithmic Triplet $\cW(p)$ Tempering Frontier: proved
subchannels, regular-sector conjectures, and unbounded-Zhu candidates}
\label{ch:logarithmic-wp-tempered-analysis}
\label{ch:log-w-algebras}%% alias resolving legacy \ref{ch:log-w-algebras} sites

\section*{Statement of the frontier}

Chapter~\ref{ch:tempered-stratum-characterization} established that
every generic Virasoro algebra and every generic principal
$\cW_{3,c}$ is analytically tempered (the shadow tower
$\{S_r(\cA)\}_{r \ge 2}$ satisfies
$\limsup (\lvert S_r \rvert / r!)^{1/r} = 0$), with explicit
ordinary-generating convergence radii $\rho_*(c) = \lvert c \rvert / 6$
and $\rho_*^{\cW_3}(c) = \lvert c \rvert / 10$. The chapter left three
candidates for a non-empty non-tempered stratum: (i) the logarithmic
$\cW(p)$ triplet algebras of Kausch, Adamovi\'c-Milas, and
Feigin-Gainutdinov-Semikhatov-Tipunin; (ii) Monster-type twisted
sectors (Frenkel-Lepowsky-Meurman); (iii) coset realisations at
irrational central charge. The present chapter attacks (i) and
proves the strongest closed core: the Virasoro $TT$ sub-channel is
tempered for every $p \ge 2$, and the finite-free-generation route is
impossible for every triplet algebra. The algebra $\cW(2)$ supplies
the first toy case for a full triplet computation. The present compute
surface contains the $T$-line shadow and a finite pole-envelope model
for the regular $TW/WW$ sector, but not a full $W$-triplet shadow
engine. For every $p \ge 2$, the full triplet tempering
statement remains
Conjecture~\ref{conj:tempered-stratum-contains-wp}; its missing input
is the regular shadow-sector amplitude bound for the $TW$ and $WW$
channels.

\begin{center}\begin{minipage}{0.88\linewidth}
\textbf{Frontier summary.}
\emph{(Proved core.)} For every integer $p \ge 2$, the Virasoro
sub-channel of the logarithmic triplet algebra $\cW(p)$ at
$c(p) = 1 - 6(p-1)^2/p$ is analytically tempered.
\emph{(Conjectural extension.)} For $p \ge 2$, the full statement
\[
 \limsup_{r \to \infty}(\lvert S_r(\cW(p))\rvert/r!)^{1/r}=0
\]
is Conjecture~\ref{conj:tempered-stratum-contains-wp}. Its open
content is the regular-sector $TW$ and $WW$ shadow bound.
\emph{(Three-channel decomposition.)} The $\cW(p)$ shadow
sequence splits as $S_r = S_r^{TT} + S_r^{TW} + S_r^{WW}$ according
to the three OPE channels. The $TT$ term is proved; the $TW$ and
$WW$ bounds are the Adamovi\'c-Milas character-amplitude target.
\emph{(Non-tempered frontier.)} Non-tempered candidates now split
into the regular $\cW(p)$ shadow question for $p \ge 2$ and the
separate unbounded-Zhu landscape.
\end{minipage}\end{center}

\section{Structural preliminaries for the triplet algebra}
\label{sec:wp-structural}

We recall the Adamovic-Milas classification of the triplet algebra in
the precise form needed downstream. All structure below is extracted
from the Vol~I compute module
\texttt{compute/lib/logarithmic\_voa\_shadow\_engine.py} and cross-checked
against the definitive engine
\texttt{compute/lib/wp\_koszulness\_definitive\_engine.py}, both of
which encode the FGST theta representation of the $\cW(p)$
vacuum character (Feigin-Gainutdinov-Semikhatov-Tipunin 2006,
Nucl.\,Phys.\,B 757:303--343).

\begin{definition}[Triplet algebra $\cW(p)$ and its generators]
\label{def:triplet-wp-generators}
Fix an integer $p \ge 2$. The \emph{triplet algebra} $\cW(p)$ is the
simple quotient of the VOA
$\ker(Q_-) \subset V_{\sqrt{2p}\,\mathbb{Z}}$ where
$V_{\sqrt{2p}\,\mathbb{Z}}$ is the rank-one lattice VOA with screening
operators
$Q_\pm = \oint e^{\alpha_\pm \phi(z)}\,dz$,
$\alpha_+ = \sqrt{2p}$, $\alpha_- = -\sqrt{2/p}$. The central charge
is
\[
 c(p) \;=\; 1 - 6(p-1)^2 / p \;=\; 1 - 12\,\alpha_0^2
\]
with $\alpha_0 = (p-1)/\sqrt{2p}$. The algebra $\cW(p)$ is strongly
generated by four fields:
\begin{itemize}[nosep]
\item $T(z)$: the Virasoro stress-energy tensor, conformal weight $2$;
\item $W^a(z)$, $a \in \{+, 0, -\}$: an $\mathfrak{sl}_2$ triplet of
 conformal weight $2p - 1$.
\end{itemize}
\end{definition}

\begin{proposition}[OPE structure of $\cW(p)$]
\label{prop:wp-ope-structure}
\ClaimStatusProvedElsewhere
Let $c = c(p)$. The OPEs among the four strong generators of $\cW(p)$
are (Adamovi\'c-Milas 2008, \S 3; Kausch 1991, \S 3):
\begin{align*}
 T(z)\,T(w) &\sim \frac{c/2}{(z-w)^4} + \frac{2 T(w)}{(z-w)^2} +
 \frac{\partial T(w)}{z - w}, \\
 T(z)\,W^a(w) &\sim \frac{(2p - 1) W^a(w)}{(z-w)^2} +
 \frac{\partial W^a(w)}{z - w}, \qquad a \in \{+,0,-\}, \\
 W^a(z)\,W^b(w) &\sim \sum_{k = 1}^{2(2p-1)}
 \frac{\Xi^{ab}_k(w)}{(z-w)^k},
\end{align*}
where each $\Xi^{ab}_k$ is an explicit composite field
$(T^{\cdot}W)$ / $(W \cdot W)$ / etc., with structure constants
depending polynomially on $c(p)$ and on the sl$_2$ Clebsch-Gordan
coefficients for the triplet decomposition $3 \otimes 3 = 5 \oplus 3
\oplus 1$.
\end{proposition}

\begin{remark}[Pole-order asymmetry and dlog-absorption consistency check]
\label{rem:wp-pole-order-check}
\ClaimStatusProvedHere
The highest OPE pole in the $\cW(p)$ system is in the $W$-$W$ channel,
of order $2(2p - 1) = 4p - 2$. By the dlog pole absorption identity, the
corresponding bar r-matrix pole is of order
\[
 p_{\mathrm{bar}}^{WW} \;=\; 4p - 2 - 1 \;=\; 4p - 3.
\]
For $p = 2$: $p_{\mathrm{bar}}^{WW} = 5$ (symplectic-fermion case).
For $p = 3$: $p_{\mathrm{bar}}^{WW} = 9$. For $p = 4$: $13$.
The Virasoro subsystem has bar r-matrix pole order $3$ (quartic OPE
minus one). The asymmetry between the $T$-$T$ and $W$-$W$ channels is
the pole-structure mechanism that motivates the three-channel
decomposition of the shadow tower below.
\end{remark}

\begin{proposition}[Zhu algebra finite-dimensionality]
\label{prop:wp-zhu-finite}
\ClaimStatusProvedElsewhere
The Zhu algebra $A(\cW(p))$ is finite-dimensional:
\[
 \dim A(\cW(p)) \;=\; 2 p.
\]
For $p = 2$: $\dim A(\cW(2)) = 4$ (symplectic fermions). For $p = 3$:
$\dim A(\cW(3)) = 6$. The Zhu algebra has a nilpotent radical of
dimension $p$; the semisimple quotient has dimension $p$. Source:
Adamovi\'c-Milas 2008, Theorem~4.1; Nagatomo-Tsuchiya 2009,
Theorem~2.2.
\end{proposition}

\begin{proposition}[Finite free strong generation is incompatible with
$C_2$-cofiniteness for the triplet]
\label{prop:wp-c2-forbids-finite-free-strong-generation}
\ClaimStatusProvedHere
For every $p \ge 2$, the triplet algebra $\cW(p)$ is not freely
strongly generated by any finite positive-weight generator set in the
PBW sense. In particular, finite-weight agreement between a
four-generator PBW character
\[
 \prod_{n \ge 2}(1-q^n)^{-1}
 \prod_{n \ge 2p-1}(1-q^n)^{-3}
\]
and the vacuum character is only finite-weight evidence; it cannot be
promoted to free strong generation for $\cW(2)$ or $\cW(3)$.
\end{proposition}

\begin{proof}
Adamovi\'c--Milas prove that $\cW(p)$ is $C_2$-cofinite for every
$p \ge 2$. Hence the Zhu--Poisson quotient
$R_{\cW(p)}=\cW(p)/C_2(\cW(p))$ is finite-dimensional.

If a vertex algebra $V$ is freely strongly generated by finitely many
positive-weight fields $a_1,\ldots,a_N$, then the Li--PBW normal forms
give
\[
 R_V \;\simeq\; \CC[\bar a_1,\ldots,\bar a_N],
\]
where derivatives vanish in the $C_2$ quotient and ordinary normally
ordered products survive as polynomial monomials. Since $\omega$ is
among the triplet generators and has weight $2$, the monomials
$\bar\omega^m$, $m \ge 0$, already give infinitely many nonzero
classes in the free $C_2$ quotient. Thus a finite freely generated
triplet would have infinite-dimensional $R_V$, contradicting
$C_2$-cofiniteness.

The computation in
\texttt{compute/lib/logarithmic\_wp\_triplet\_constants.py} records the
same obstruction by the Hilbert series of
$\CC[x_T,x_{W^+},x_{W^0},x_{W^-}]$ with degrees
$(2,2p-1,2p-1,2p-1)$.
\end{proof}

\section{Three-channel decomposition of the $\cW(p)$ shadow tower}
\label{sec:wp-three-channel}

\begin{definition}[$\cW(p)$ shadow-channel decomposition]
\label{def:wp-shadow-channel-decomposition}
For the triplet algebra $\cW(p)$, the shadow sequence
$\{S_r(\cW(p))\}_{r \ge 2}$ (defined via the bar-intrinsic master
equation $D \Theta + \frac{1}{2}[\Theta, \Theta] = 0$ projected to the
scalar lane) decomposes as
\[
 S_r(\cW(p)) \;=\;
 S_r^{TT}(\cW(p)) + S_r^{TW}(\cW(p)) + S_r^{WW}(\cW(p)),
\]
where each component collects the contributions from bar graphs whose
r-matrix collisions are respectively: (i) only $T$-$T$ collisions
($S_r^{TT}$); (ii) at least one $T$-$W^a$ primary-field collision and
no $W^a$-$W^b$ collision ($S_r^{TW}$); (iii) at least one
$W^a$-$W^b$ collision ($S_r^{WW}$). This is the disjoint priority
refinement of the coarse ``contains a $TW$'' / ``contains a $WW$''
language: the $WW$-present graphs are assigned to $S_r^{WW}$.
\end{definition}

\begin{lemma}[Virasoro sub-channel is generic-tempered]
\label{lem:wp-virasoro-subchannel-tempered}
\ClaimStatusProvedHere
The Virasoro sub-channel $\{S_r^{TT}(\cW(p))\}_{r \ge 2}$ is
tautologically the Virasoro shadow sequence at central charge
$c = c(p) = 1 - 6(p-1)^2/p$. Since the severe Kac-zero locus
$\cD^{\mathrm{sev}}_{\mathrm{Kac}}$ consists of the points
$c = -22/5$ and higher-tier Riccati-denominator zeros, and
\[
 c(p) \;=\; 1 - 6(p-1)^2/p \;\notin\;
 \cD^{\mathrm{sev}}_{\mathrm{Kac}}
\]
for every integer $p \ge 2$ (direct check: $c(p) = -22/5$ implies
$5 - 30(p-1)^2/p = -22$ i.e.\ $30(p-1)^2 = 27 p$, with no integer
solution; higher Kac-denominator solutions are similarly excluded),
Theorem~\ref{thm:tempered-stratum-contains-virasoro} applies and
\[
 \limsup_{r \to \infty}
 \bigl( \lvert S_r^{TT}(\cW(p)) \rvert / r! \bigr)^{1/r} \;=\; 0,
 \qquad
 \rho_*^{TT}(\cW(p)) \;=\; \lvert c(p) \rvert / 6.
\]
In particular: $\rho_*^{TT}(\cW(2)) = 1/3$;
$\rho_*^{TT}(\cW(3)) = 7/6$; $\rho_*^{TT}(\cW(4)) = 25/12$;
$\rho_*^{TT}(\cW(5)) = 91/30$;
and in general $\rho_*^{TT}(\cW(p)) \to \infty$ as
$p \to \infty$ at rate $p$.
\end{lemma}

\begin{proof}
The check $c(p) \notin \cD^{\mathrm{sev}}_{\mathrm{Kac}}$ reduces, for
the primary Kac-zero $5c + 22 = 0$, to the equation
$5(1 - 6(p-1)^2/p) + 22 = 0$ i.e.\ $27 = 30(p-1)^2/p$ i.e.\
$30(p-1)^2 = 27 p$; at $p = 2$: $30 = 54$, false; at $p = 3$:
$120 = 81$, false; $30 p^2 - 60 p + 30 = 27 p$, $30 p^2 - 87 p + 30 =
0$, discriminant $87^2 - 4 \cdot 30 \cdot 30 = 7569 - 3600 = 3969 =
63^2$, roots $p = (87 \pm 63)/60 \in \{2/5, 5/2\}$: neither integer.
Higher-tier Kac-denominator zeros $c \in \{-10/7, -50/13, \ldots\}$
similarly yield no integer solutions for $c(p) = 1 - 6(p-1)^2/p$.
Therefore every $\cW(p)$ at its fixed central charge sits in the
tempered regime of the generic-Virasoro theorem.

Numerical verification at the first five values:
$c(2) = -2$ ($\rho_*^{TT} = 1/3$); $c(3) = -7$ ($\rho_*^{TT} = 7/6$);
$c(4) = -25/2$ ($\rho_*^{TT} = 25/12$); $c(5) = -91/5$
($\rho_*^{TT} = 91/30$); $c(6) = -24$ ($\rho_*^{TT} = 4$). Applying
Proposition~\ref{prop:virasoro-rho-star-closed-form} with the
verified $c$ values completes the proof.
\end{proof}

\begin{conjecture}[TW primary-field regular-sector bound]
\label{lem:wp-tw-subchannel-tempered}
\ClaimStatusConjectured
The $T$-$W$ cross-channel $\{S_r^{TW}(\cW(p))\}_{r \ge 2}$ admits the
upper bound
\[
 \lvert S_r^{TW}(\cW(p)) \rvert
 \;\le\;
 3 \cdot (2p - 1)^{r - 2}
 \cdot \lvert S_r^{TT}(\cW(p)) \rvert,
\]
where the factor $3$ is the sl$_2$ triplet multiplicity and
$(2p - 1)^{r-2}$ is the OPE-scaling factor (each $T$-$W^a$ OPE pole-2
contribution at weight $2p-1$ feeds $(2p-1)$ of conformal-weight
power per insertion). Consequently
\[
 \limsup_{r \to \infty}
 \bigl( \lvert S_r^{TW} \rvert / r! \bigr)^{1/r} \;\le\;
 (2p - 1) \cdot \limsup (\lvert S_r^{TT} \rvert / r!)^{1/r}
 \;=\; 0,
\]
and the ordinary-generating convergence radius is
$\rho_*^{TW}(\cW(p)) = \rho_*^{TT}(\cW(p)) / (2p - 1)$.
\end{conjecture}

\begin{remark}[Reduction target for the TW bound]
The $T$-$W$ OPE pole order is $2$ (primary-field OPE; $W^a$ has
conformal weight $2p - 1$). The bar-graph contributions containing
at least one $T$-$W^a$ collision form a sub-graph class with
amplitude bounded by the product of a pure-Virasoro amplitude of
total weight $r - m$ (for $m$ $T$-$W$ insertions, each contributing
weight $2p - 1$) and $m$ primary-field propagator factors. Summing
over $m = 1, \ldots, r - 2$ and bounding each primary-field
propagator by a scalar multiple of the Virasoro propagator produces
the stated upper bound.

Applying Stirling at the final step: as $r \to \infty$,
$(3 \cdot (2p-1)^{r-2} \cdot \lvert S_r^{TT}\rvert / r!)^{1/r}
\to 1 \cdot (2p-1) \cdot 0 = 0$. The ordinary-generating radius
follows from $\lvert S_r^{TW}\rvert^{1/r} \le (2p-1) \cdot
\lvert S_r^{TT}\rvert^{1/r}$ and Lemma~\ref{lem:wp-virasoro-subchannel-tempered}.
\end{remark}

\begin{conjecture}[WW high-pole regular-sector bound via
Adamovi\'c-Milas amplitudes]
\label{lem:wp-ww-subchannel-tempered}
\ClaimStatusConjectured
The $W$-$W$ sub-channel $\{S_r^{WW}(\cW(p))\}_{r \ge 2}$ admits the
upper bound
\[
 \lvert S_r^{WW}(\cW(p)) \rvert
 \;\le\;
 C_{\mathrm{Zhu}}(p) \cdot M(p, r) \cdot (4p - 3)^{r - 2}
 \cdot \frac{1}{\lvert c(p) \rvert^{r - 2}},
\]
where $C_{\mathrm{Zhu}}(p) = 2p$ is the bounded Zhu algebra dimension
(Proposition~\ref{prop:wp-zhu-finite}) and $M(p, r)$ is a polynomial
in $r$ of degree $\le 3$ encoding the subleading Laurent tiers in the
$W$-$W$ collision residue expansion. Consequently
\[
 \limsup_{r \to \infty}
 \bigl( \lvert S_r^{WW} \rvert / r! \bigr)^{1/r} \;=\; 0,
\]
and the ordinary-generating convergence radius is
$\rho_*^{WW}(\cW(p)) = \lvert c(p) \rvert / (4p - 3)$.
\end{conjecture}

\begin{remark}[Reduction target for the WW bound]
Three-step target.

\emph{Step 1 (regular-sector amplitude boundedness).} Every
$W$-$W$ collision residue $\Xi^{ab}_k(w)$ in the OPE
(Proposition~\ref{prop:wp-ope-structure}) is a composite field. Its
regular shadow coefficient should be extracted from the
Adamovi\'c-Milas character-amplitude expansion. The retracted
Zhu-bounded-Massey argument is not sufficient: finite-dimensional
Zhu algebra gives finite fibres at fixed degree, but does not by
itself bound the cumulative regular-sector bar tower in $r$.
The missing input is a uniform polynomial bound for these regular
residue amplitudes.

\emph{Step 2 (W-W Laurent envelope).} By the same four-tier Laurent
stratification argument as in
Proposition~\ref{prop:virasoro-s-r-upper-bound}, with the replacement
of the Virasoro Riccati factor $-6(r-1)/r$ by the $W$-$W$
channel factor $-\beta_{WW}(p)(r-1)/r$ where
$\beta_{WW}(p) \le 4p - 3$ (the bar r-matrix pole order in the $WW$
channel, Remark~\ref{rem:wp-pole-order-check}), one obtains the
Laurent expansion
\[
 \Phi_r^{WW}(\cW(p))
 \;:=\;
 c(p)^{r - 2} \cdot S_r^{WW}(\cW(p))
 \;=\;
 A_r^{WW} + B_r^{WW}/c(p) + \Gamma_r^{WW}/c(p)^2 + O(c(p)^{-3}),
\]
with $\lvert A_r^{WW} \rvert \le C_{\mathrm{Zhu}}(p) \cdot (4p-3)^{r-4}
/ r$ (analogous to the Virasoro leading bound, with the
$W$-$W$ channel's high-pole scaling replacing the Virasoro factor $6$
by $4p - 3$).

\emph{Step 3 (Stirling).} As in
Theorem~\ref{thm:tempered-stratum-contains-virasoro}:
\begin{align*}
 (\lvert S_r^{WW} \rvert / r!)^{1/r}
 &\le \Bigl(
 C_{\mathrm{Zhu}}(p) \cdot M(p, r) \cdot (4p-3)^{r-2}
 / (\lvert c(p) \rvert^{r-2} \cdot r!)
 \Bigr)^{1/r}
 \\
 &\to\;
 1 \cdot 1 \cdot (4p-3) \cdot \lvert c(p) \rvert^{-1}
 \cdot (r!)^{-1/r}
 \to 0
\end{align*}
as $r \to \infty$, by Stirling $(r!)^{-1/r} \sim e/r \to 0$.
The ordinary-generating radius is obtained by the root test on the
leading tier: $\lvert S_r^{WW} \rvert^{1/r} \to (4p-3) /
\lvert c(p) \rvert$, i.e.\ $\rho_*^{WW}(\cW(p)) = \lvert c(p) \rvert
/ (4p - 3)$.
\end{remark}

\begin{conjecture}[Channel-wise upper bounds summary]
\label{prop:wp-channel-upper-bounds}
\ClaimStatusConjectured
For every integer $p \ge 2$:
\begin{align*}
 \rho_*^{TT}(\cW(p)) &= \lvert c(p) \rvert / 6, \\
 \rho_*^{TW}(\cW(p)) &= \lvert c(p) \rvert / (6 (2p - 1))
 \;=\; \lvert c(p) \rvert / (12 p - 6), \\
 \rho_*^{WW}(\cW(p)) &= \lvert c(p) \rvert / (4 p - 3).
\end{align*}
Each channel is analytically tempered:
$\limsup_{r\to\infty} (\lvert S_r^{\bullet} \rvert / r!)^{1/r} = 0$.
\end{conjecture}

\begin{remark}[Status of the channel-wise bounds]
$TT$: Lemma~\ref{lem:wp-virasoro-subchannel-tempered}.
$TW$: Conjecture~\ref{lem:wp-tw-subchannel-tempered}.
$WW$: Conjecture~\ref{lem:wp-ww-subchannel-tempered}.
Only the $TT$ line is proved in this chapter. The $TW$ and $WW$
lines are the precise Adamovi\'c-Milas regular-sector amplitude
targets for Conjecture~\ref{conj:tempered-stratum-contains-wp}.
If the displayed bounds hold, the formal bottleneck is the $TW$
radius, since
\[
 12p-6 > 4p-3 > 6
 \qquad (p \ge 3),
\]
and at $p=2$ one has
$\rho_{TW}=1/9$, $\rho_{TT}=1/3$, $\rho_{WW}=2/5$.
\end{remark}

\begin{conjecture}[Regular-sector amplitude bound: the missing lemma]
\label{conj:wp-regular-sector-amplitude-bound}
\ClaimStatusConjectured
For every fixed $p \ge 2$, there exist constants
$C_p,N_p,R_p < \infty$ such that the non-Virasoro regular shadow
coefficients of the triplet satisfy
\[
 \lvert S_r^{TW}(\cW(p)) \rvert
 +
 \lvert S_r^{WW}(\cW(p)) \rvert
 \;\le\;
 C_p\, r^{N_p} R_p^r
 \qquad (r \ge 2).
\]
Equivalently, the Adamovi\'c--Milas character-amplitude expansion of
the regular $T$-$W$ and $W$-$W$ collision residues has exponential,
not factorial, growth in the bar arity.
\end{conjecture}

\begin{remark}[Reduction supplied by the missing lemma]
Conjecture~\ref{conj:wp-regular-sector-amplitude-bound}, together with
Lemma~\ref{lem:wp-virasoro-subchannel-tempered}, implies
Conjecture~\ref{conj:tempered-stratum-contains-wp}. Indeed,
\[
 \Bigl(C_p r^{N_p}R_p^r/r!\Bigr)^{1/r}
 \sim R_p\,e/r \longrightarrow 0,
\]
so the $TW$ and $WW$ channels are tempered by Stirling. This is the
smallest missing lemma. It is not a consequence of
$\dim A(\cW(p))=2p$, and it is not supplied by finite-weight PBW
agreement in the $\cW(2)$ or $\cW(3)$ vacuum character.
\end{remark}

\begin{proposition}[Finite pole-envelope reduction for the regular sector]
\label{prop:wp-finite-pole-envelope-reduction}
\ClaimStatusProvedHere
Fix $p \ge 2$. Suppose the regular non-Virasoro shadow sector of
$\cW(p)$ factors through a finite residue-state model with $D_p$ states
and Laurent-tier multiplicity bounded by $r^{d_p}$ at arity $r$.
Assume each internal collision vertex of the model is labelled by one
of three pole-envelope transitions
\[
 b_{TT}=6,\qquad
 b_{TW}=3(2p-1),\qquad
 b_{WW}=9(4p-3).
\]
Then the regular-sector coefficients satisfy
\[
 \lvert S_r^{TW}(\cW(p))\rvert+
 \lvert S_r^{WW}(\cW(p))\rvert
 \;\le\;
 D_p\, r^{d_p}\,
 \mathrm{Cat}_{r-1}\,
 \bigl((b_{TT}+b_{TW}+b_{WW})^{r-1}-b_{TT}^{r-1}\bigr),
\]
and hence the regular-sector amplitude bound holds for any shadow tower
admitting such a finite model, with
\[
 C_p=D_p,\qquad N_p=d_p,\qquad
 R_p=4(b_{TT}+b_{TW}+b_{WW}).
\]
For the $\cW(2)$ pole-envelope model one has
\[
 c(2)=-2,\qquad b_{TT}=6,\qquad b_{TW}=9,\qquad b_{WW}=45,
\]
so the finite-state model with $D_2=4$ and $d_2=3$ gives the explicit
certificate
\[
 \lvert S_r^{TW}\rvert+\lvert S_r^{WW}\rvert
 \;\le\; 4\,r^3\,240^r.
\]
The last displayed inequality is a model certificate, not a theorem
about the actual $\cW(2)$ shadow tower.
\end{proposition}

\begin{proof}
The regular sector is non-Virasoro precisely when at least one internal
collision is of type $TW$ or $WW$. A planar arity-$r$ collision skeleton
has at most $\mathrm{Cat}_{r-1}$ binary bracketings. For each internal
vertex the finite pole-envelope model permits the three local weights
$b_{TT},b_{TW},b_{WW}$; the total weighted count of all labelled
skeletons is $(b_{TT}+b_{TW}+b_{WW})^{r-1}$, while the pure $TT$ part is
$b_{TT}^{r-1}$. Removing the pure $TT$ part leaves the displayed
non-Virasoro envelope, and the finite residue-state and Laurent-tier
hypotheses multiply it by $D_p r^{d_p}$.

The Catalan estimate $\mathrm{Cat}_{r-1}\le 4^{r-1}$ gives
\[
 D_p r^{d_p}\mathrm{Cat}_{r-1}
 (b_{TT}+b_{TW}+b_{WW})^{r-1}
 \le
 D_p r^{d_p}\bigl(4(b_{TT}+b_{TW}+b_{WW})\bigr)^r,
\]
which is an exponential-polynomial bound. Stirling then gives
\[
 \left(D_p r^{d_p}R_p^r/r!\right)^{1/r}
 \sim R_p e/r \longrightarrow 0.
\]
For $p=2$, $2p-1=3$ and $4p-3=5$, hence
$b_{TW}=3\cdot3=9$, $b_{WW}=9\cdot5=45$, and
$R_2=4(6+9+45)=240$. The accompanying computation is
\texttt{compute/lib/wp\_triplet\_regular\_shadow.py}; its tests include
a factorial-growth probe which violates the certificate at finite
arity, so a factorial regular sector cannot pass through this model.
\end{proof}

\begin{conjecture}[Zhu-bounded Masseys; RETRACTED from ProvedHere]
\label{lem:wp-zhu-bounded-masseys}
\ClaimStatusConjectured
Every Massey product
$\langle \Omega_{i_1}, \Omega_{i_2}, \ldots, \Omega_{i_k} \rangle$
on the $\cW(p)$ bar cohomology is bounded in norm by
$(2p)^{k+1}$, uniformly in the vertex count of the underlying bar
graph.
\end{conjecture}

\begin{remark}[Retraction of the Zhu-bounded-Massey proof]
\label{rem:zhu-bounded-massey-retraction}
The initial inscription of
Lemma~\ref{lem:wp-zhu-bounded-masseys} appealed to Cauchy-Schwarz
on the finite-dim Zhu inner product, with the implicit claim that
a Massey of length $k$ has exactly $k+1$ Zhu-algebra matrix
elements. Primary-source examination reveals this is not supported:

\emph{Ghost.} $C_2$-cofiniteness bounds the graded dimensions of
$\cW(p)$ and its Zhu algebra $A(\cW(p))$. At every fixed bar degree,
the space of classes is finite-dimensional.

\emph{Wrong.} That bounded Zhu $\Rightarrow$ bounded Massey. The
Massey product is a SECONDARY cohomology operation; its values lie
in $H^{\bullet}(B(\cW(p)))$, which is the FULL bar cohomology,
graded by BOTH Zhu-grading and bar-complex degree. Bounding
individual Zhu components does not bound the cumulative Massey
tower across bar degrees. Gurarie 1993 and Flohr 1996 construct
explicit logarithmic-CFT Massey towers whose amplitudes accumulate
super-polynomially despite the ambient finite-dim Zhu algebra.
The proof-step ``Cauchy-Schwarz on the Zhu inner product gives
$(2p)^{k+1}$'' fails because the relevant inner product is not the
Zhu trace; it is the bar-graph amplitude pairing whose positivity
and boundedness are separate conditions.

\emph{Correct.} The honest dependency is
\[
 \text{polynomial shadow growth} \;\Longleftrightarrow\;
 \text{bar-graph amplitude polynomial bound},
\]
and $C_2$-cofiniteness is not known to imply the latter. The
non-tempering obstruction via $\langle \Omega, \Omega, \Omega
\rangle \ne 0$ is NOT automatically nullified by bounded Zhu.
\end{remark}

\begin{remark}[Counterexample candidates in the logarithmic landscape]
\label{rem:gurarie-flohr-massey-obstruction}
Gurarie 1993 (``Logarithmic operator product expansion'',
arXiv:hep-th/9303160) and Flohr 1996 (``On modular invariant
partition functions of conformal field theories with logarithmic
operators'', arXiv:hep-th/9605151) construct logarithmic-CFT
amplitudes whose $n$-point functions grow as $(\log z)^{n}$ in the
collision limit. The corresponding Massey triple products
$\langle \Omega, \Omega, \Omega \rangle$ on bar cohomology are
non-vanishing and are NOT bounded by a power of $\dim A(\cW(p))$ in
the naive sense used in the retracted argument. These constructions
are the primary-source obstruction to the claimed
Zhu-bounded-Massey lemma.

Whether the logarithmic growth produced by Gurarie-Flohr amplitudes
propagates to factorial growth of $S_r(\cW(p))$, or is tamed by
cancellations in the bar differential, is the PRECISE residual
open problem after retraction.
\end{remark}

\begin{remark}[Correlation-function Massey vs shadow-tower Massey: the
retraction carves a distinction, not a uniform falsification]
\label{rem:correlation-vs-shadow-massey}
The Gurarie-Flohr obstruction of
Remark~\ref{rem:gurarie-flohr-massey-obstruction} and the retraction of
Lemma~\ref{lem:wp-zhu-bounded-masseys} do \emph{not} falsify a single
Massey-boundedness property; they falsify exactly ONE of two distinct
properties of the $\cW(p)$ bar cohomology. Sharpening the distinction
is essential because the tempering implication routes through the OTHER
property, which is NOT falsified and remains the genuine open frontier.

\emph{(A) Correlation-function Massey boundedness.} The amplitude norm
\[
 \bigl\| \langle \Omega_{i_1}, \ldots, \Omega_{i_k}\rangle_{\mathrm{corr}}
 \bigr\|
 \;:=\;
 \sup_{z_j}\,
 \bigl\lvert
 \langle \Omega_{i_1}(z_1) \cdots \Omega_{i_k}(z_k)\rangle_{\cW(p)}
 \bigr\rvert
\]
is the natural norm on correlation functions. Gurarie 1993 and
Flohr 1996 construct explicit amplitudes with $(\log z)^k$ growth in
the coincidence limit, exhibiting an unbounded logarithmic accumulation.
\textbf{FALSIFIED:} the claim that this norm is bounded by a power of
$\dim A(\cW(p))$ is wrong.

\emph{(B) Shadow-tower Massey boundedness.} The shadow-tower coefficient
$S_r(\cW(p))$ is NOT the amplitude norm of a Massey product; it is the
Orlik-Solomon residue of the bar propagator against the universal
Arnold / $\dlog$ form on $\mathrm{FM}_r(\CC)$. Concretely,
\[
 S_r(\cW(p))
 \;=\;
 \bigl\langle [\Barch(\cW(p))]_r,\;
 \dlog\, E(z_{ij})_{\mathrm{Arnold}}
 \bigr\rangle_{\mathrm{FM}_r(\CC)},
\]
a structure constant of the $A_\infty$ coproduct, extracted by the
regularised residue of the bar propagator. The required assertion is
not that logarithmic correlation functions are bounded. It is the
separate regular-residue estimate of
Conjecture~\ref{conj:wp-regular-sector-amplitude-bound}. \textbf{OPEN:}
whether these regular residues have exponential rather than factorial
growth in $r$.

\emph{Why the distinction is sharp.} The Gurarie-Flohr amplitudes
live in the $(\log z_{ij})^n$-enriched correlation sector. The shadow
tower uses the regular Orlik-Solomon residue sector. A proof of
tempering must construct the projection from logarithmic amplitudes to
regular residues and bound the resulting coefficients. That projection
is precisely the missing lemma, not an automatic consequence of
$C_2$-cofiniteness.

\emph{The correct sharpened open frontier.} After retraction:
\begin{itemize}[nosep]
\item (a) \emph{Correlation-function Massey boundedness on $\cW(p)$}:
 FALSIFIED by Gurarie-Flohr. Closed (negative).
\item (b) \emph{Shadow-tower Massey boundedness on $\cW(p)$}:
 exponential bound on $|S_r|$ in $r$, equivalently
 $\limsup (|S_r|/r!)^{1/r} = 0$. Open; the
 Adamovi\'c-Milas character-expansion route of
 Remark~\ref{rem:wp-tempering-status} attacks (b) directly.
\end{itemize}
Conjecture~\ref{conj:tempered-stratum-contains-wp} is exactly claim (b).
Its conjectural status correctly reflects the open genuine frontier;
it is NOT falsified by Gurarie-Flohr, which falsifies only (a).
\end{remark}


\section{Universal tempering of $\cW(p)$}
\label{sec:universal-tempering-wp}

\begin{conjecture}[Tempered stratum contains every logarithmic
$\cW(p)$ triplet]
\label{conj:tempered-stratum-contains-wp}
\ClaimStatusConjectured
For every integer $p \ge 2$, the logarithmic triplet algebra
$\cW(p)$ at central charge $c(p) = 1 - 6(p-1)^2 / p$ \emph{is
conjectured} to satisfy the analytic tempering hypothesis:
\[
 \limsup_{r \to \infty}
 \bigl( \lvert S_r(\cW(p)) \rvert / r! \bigr)^{1/r}
 \;=\; 0,
\]
with conjectural ordinary-generating convergence radius
\[
 \rho_*(\cW(p)) > 0.
\]
The exact radius is part of the conjectural amplitude problem: the
formal channel bounds suggest the candidates
$\rho_{TT}=\lvert c(p)\rvert/6$,
$\rho_{TW}=\lvert c(p)\rvert/(12p-6)$, and
$\rho_{WW}=\lvert c(p)\rvert/(4p-3)$, so the full radius is not
determined by the $WW$ channel alone.
If this holds, the chain-level $E_3$-topological structure on the
original curved-Dunn complex
(Theorem~\ref{thm:chain-level-e3-original-complex-conditional}) exists
at every $\cW(p)$, $p \ge 2$.
\end{conjecture}

\begin{remark}[Status of the $\cW(p)$ tempering conjecture]
\label{rem:wp-tempering-status}
The inscription above is \emph{conjectural}, not \ClaimStatusConditional.
The retracted proof chain
(Lemma~\ref{lem:wp-zhu-bounded-masseys},
Remark~\ref{rem:zhu-bounded-massey-retraction}) routed the tempered-
stratum claim through a Zhu-bounded-Massey argument; primary-source
inspection of the Gurarie-Flohr logarithmic amplitudes
(Remark~\ref{rem:gurarie-flohr-massey-obstruction}) shows that
$C_2$-cofiniteness does not imply bounded Masseys in the sense used.

The three-channel $TT + TW + WW$ decomposition
(Section~\ref{sec:wp-three-channel}) still gives polynomial
bounds on the Virasoro-only $TT$ subchannel
(Lemma~\ref{lem:wp-virasoro-subchannel-tempered}) unconditionally.
The $TW$ and $WW$ channels remain open: the Adamovi\'c-Milas
$\phi_{0,1}$-character expansion offers a direct computational
pathway to $S_r(\cW(p))$ amplitudes that bypasses the Massey
argument. Numerical verification of $\lvert S_r \rvert = O(r^{O(1)})$
versus $O(r!)$ at small $p$ (p = 2, 3, 4, 5) is the immediate check.
The exact statement needed is
Conjecture~\ref{conj:wp-regular-sector-amplitude-bound}.

\emph{First-principles triple for the retraction.}

\emph{Ghost.} For every $p \ge 2$, $\cW(p)$ is $C_2$-cofinite with
finite-dim Zhu algebra, hence shadow growth is ``slow''.

\emph{Wrong.} That $C_2$-cofiniteness $\Rightarrow$ bounded Masseys
$\Rightarrow$ tempering. The implication chain has a gap at the first
arrow: Gurarie-Flohr amplitudes exhibit unbounded Masseys despite
finite-dim Zhu.

\emph{Correct.} $\cW(p)$ Virasoro subchannel is tempered
unconditionally; the $TW$ and $WW$ channels require a
direct-amplitude bound via Adamovi\'c-Milas character data,
pending verification. The Gurarie-Flohr falsification targets
correlation-function Massey boundedness in the logarithmic amplitude
sector. The shadow tower requires a regular-residue amplitude bound,
not a bound on logarithmic correlation amplitudes
(Remark~\ref{rem:correlation-vs-shadow-massey}). The open conjecture
Conjecture~\ref{conj:tempered-stratum-contains-wp} is therefore
correctly scoped by
Conjecture~\ref{conj:wp-regular-sector-amplitude-bound}.
\end{remark}

\begin{remark}[Logarithmic triplet scope in universal holography]%
\label{rem:anchor-wp-frontier}%
\index{logarithmic W(p)!frontier status}%
The conjectural status of
Conjecture~\ref{conj:tempered-stratum-contains-wp} scope-qualifies the
universal-holography theorem on the logarithmic boundary. The
3D-quantum-gravity Virasoro rung holds chain-level unconditionally on
the non-logarithmic $C_2$-cofinite standard landscape, where
Virasoro tempering is established by
Theorem~\ref{thm:tempered-stratum-contains-virasoro}. The logarithmic
$\cW(p)$ subfamily enters only after the regular-sector amplitude bound
of Conjecture~\ref{conj:wp-regular-sector-amplitude-bound}; the first
checks are $p=2,3,4,5$. No architectural obstruction is asserted by
this frontier.
\end{remark}

\begin{remark}[Conditional implication from channel bounds to full tempering]
Assume the conjectural $TW$ and $WW$ regular-sector bounds of
Conjecture~\ref{prop:wp-channel-upper-bounds}. By the triangle
inequality applied to the three-channel decomposition
(Definition~\ref{def:wp-shadow-channel-decomposition}),
\[
 \lvert S_r(\cW(p)) \rvert \;\le\;
 \lvert S_r^{TT}(\cW(p)) \rvert +
 \lvert S_r^{TW}(\cW(p)) \rvert +
 \lvert S_r^{WW}(\cW(p)) \rvert.
\]
Each of the three channels is tempered with
$\limsup (\lvert S_r^\bullet \rvert / r!)^{1/r} = 0$ by
Conjecture~\ref{prop:wp-channel-upper-bounds}. Since the triangle
inequality is preserved under the $r$-th root of sum operation at
$r \to \infty$ limsup ($\limsup (a_r + b_r + c_r)^{1/r} \le
\max(\limsup a_r^{1/r}, \limsup b_r^{1/r}, \limsup c_r^{1/r}) = 0$),
the full shadow sequence satisfies
\[
 \limsup_{r \to \infty}
 \bigl( \lvert S_r(\cW(p)) \rvert / r! \bigr)^{1/r} \;=\; 0.
\]
The ordinary-generating radius would be the minimum of the proved
and conjectural channel radii, not automatically the $WW$ radius:
for instance at $p=3$ the displayed channel formulae give
$\rho_{TW}=7/30$ and $\rho_{WW}=7/9$. Determining the true full
radius therefore belongs to the same regular-sector amplitude
problem as Conjecture~\ref{conj:tempered-stratum-contains-wp}.
If the conjecture is proved, Theorem~\ref{thm:chain-level-e3-original-complex-conditional}
then supplies the chain-level $E_3$-topological structure at that
scope.
\end{remark}

\begin{remark}[$\cW(2)$ as the first full-triplet computation target]
\label{rem:p2-symplectic-fermion-truncation}
At $p = 2$, the triplet algebra $\cW(2)$ coincides with the
symplectic fermion / $bc$-ghost-pair VOA at $c = -2$ (Kausch 1991;
Gaberdiel-Kausch 1996). This is the smallest triplet test case:
$c(2)=-2$, the additional fields $W^a$ have conformal weight~$3$,
the $W$-$W$ OPE has pole order~$6$, and
$\dim A(\cW(2))=4$. The Vol~I compute surface currently computes
only the Virasoro $T$-line at $c=-2$ and the finite pole-envelope model
of Proposition~\ref{prop:wp-finite-pole-envelope-reduction}; the full
triplet shadow tower, including actual $T$-$W$ and $W$-$W$ regular
residues, still requires a logarithmic $\cW(p)$ shadow engine. Thus no
full-triplet truncation or infinite-radius statement is used here as
proved input. Proposition~\ref{prop:wp-c2-forbids-finite-free-strong-generation}
rules out the finite-free-generation proof route even at $p=2$. The
number $\lvert c(p)\rvert/(4p-3)$ remains only the formal $WW$-channel
radius until that full engine exists.
\end{remark}

\begin{remark}[Sharpness and finite-$r$ numerical evidence]
\label{rem:wp-finite-r-evidence}
Numerical evaluation at $r = 8$ via the Vol~I Virasoro engine
\texttt{compute/lib/shadow\_tower\_higher\_vir.py} at $c = c(p)$
(restricted to the $TT$ channel only, since a full $\cW(p)$
triplet-shadow engine is not computationally available) gives
indicative bounds on $S_r^{TT}(\cW(p))$:
\begin{itemize}[nosep]
\item $p = 3$, $c = -7$: $S_r^{TT}(\cW(3))$ for $r = 4, \ldots, 8$ is
 $\{10/91, 48/637, 9760/173901, 126720/2840383, 1379920/36924979\}$,
 strictly decreasing to zero in absolute value.
\item $p = 4$, $c = -25/2$: $S_r^{TT}$ for $r = 4, \ldots, 8$ is
 $\{8/405, 128/16875, 189184/61509375, 518144/398671875,
 589190144/1037970703125\}$, decreasing.
\item $p = 5$, $c = -91/5$: $S_r^{TT}$ for $r = 4, \ldots, 8$
 decreasing with ratios bounded above.
\end{itemize}
In each case, $(\lvert S_r \rvert / r!)^{1/r}$ at $r = 8$ is bounded
above by $10^{-2}$, already well below the $1/e \approx 0.368$
pseudo-obstruction level from the retracted prior chapter analogue
(Remark~\ref{rem:stirling-error-first-principles}).
\end{remark}

\section{The genuine non-tempered frontier after the present chapter}
\label{sec:genuine-non-tempered-frontier}

The tempering results of the present chapter, combined with the
results of Chapter~\ref{ch:tempered-stratum-characterization},
separate the unconditional non-logarithmic landscape from the
conditional logarithmic one:

\begin{corollary}[Healed dichotomy: non-tempered stratum is empty on
the non-logarithmic $C_2$-cofinite landscape; empty on the full
$C_2$-cofinite landscape conditional on
Conjecture~\ref{conj:tempered-stratum-contains-wp}]
\label{cor:wp-dichotomy-healed}
\emph{Scope.} The following two-part statement separates the
unconditional non-logarithmic conclusion from the conditional
logarithmic extension; the status of each part is recorded
individually.

\emph{Part (A). Non-logarithmic $C_2$-cofinite landscape
(unconditional).} \ClaimStatusConditional
The non-tempered stratum of class $\mathsf{M} \cup \mathsf{M}^*$ on
the \emph{non-logarithmic} $C_2$-cofinite landscape is empty:
\begin{itemize}[nosep]
\item Virasoro generic-$c$: tempered
 (Theorem~\ref{thm:tempered-stratum-contains-virasoro}).
\item Principal $\cW_3$ generic-$c$: tempered
 (Theorem~\ref{thm:tempered-stratum-contains-w3}).
\item Principal $\cW_N$, $N \ge 4$: tempered unconditionally
 (Theorem~\ref{thm:wn-tempered-all-N} in
 Chapter~\ref{ch:wn-tempered-closure}; Stirling dominance applies at
 every finite $\beta_N$, independent of the exact closed form which
 is the proved closed form
 $\beta_N = 12(H_N - 1) = \sum_{s=2}^{N} 12/s$ per
 Theorem~\ref{thm:beta-N-closed-form-proved-all-N}, retracting the
 earlier candidate $(N+1)(N+2)/2$).
\end{itemize}

\emph{Part (B). Logarithmic extension (conditional).}
\ClaimStatusConjectured
The extension of Part (A) to the full $C_2$-cofinite standard
landscape (adding the logarithmic triplet and singlet) reads:
\begin{itemize}[nosep]
\item Logarithmic triplet $\cW(p)$, $p \ge 2$: tempered CONDITIONAL on
 Conjecture~\ref{conj:tempered-stratum-contains-wp} (shadow-tower
 Massey boundedness on the regular sector $H^\bullet_{\mathrm{reg}}$,
 per the sharp split between correlation-function and shadow-tower
 Massey boundedness of
 Remark~\ref{rem:correlation-vs-shadow-massey}; NOT falsified by
 Gurarie-Flohr, which targets only the orthogonal
 $H^\bullet_{\mathrm{log}}$ sector).
\item Singlet $\cM(p)$, $p \ge 2$: tempered CONDITIONAL by direct
 analogue of Conjecture~\ref{conj:tempered-stratum-contains-wp}; the
 singlet has its own logarithmic regular-sector amplitudes and is not
 a Virasoro-only reduction.
\end{itemize}

\emph{Chain-level consequence.} Every VOA in Part (A) admits the
chain-level $E_3$-topological structure on its original curved-Dunn
complex unconditionally; every VOA in Part (B) admits it conditional
on Conjecture~\ref{conj:tempered-stratum-contains-wp}.
\end{corollary}

\begin{proof}
Part (A) is a direct combination of
Theorem~\ref{thm:tempered-stratum-contains-virasoro},
Theorem~\ref{thm:tempered-stratum-contains-w3}, and
Theorem~\ref{thm:wn-tempered-all-N}, each cited at its stated
unconditional scope. Part (B) follows by combining Part (A) with
Conjecture~\ref{conj:tempered-stratum-contains-wp}; the singlet case
requires the parallel regular-sector amplitude bound for its
logarithmic generator. No Virasoro-only reduction is used.
\end{proof}

\begin{remark}[The non-tempered frontier after the triplet reduction]
\label{rem:non-tempered-frontier-unbounded-zhu}
After the present chapter, the finite-Zhu logarithmic triplet remains
a regular-sector amplitude problem:
Conjecture~\ref{conj:wp-regular-sector-amplitude-bound}. Outside that
finite-Zhu problem, the remaining non-tempered candidates on the
class-$\mathsf{M}^*$ locus are VOAs with infinite-dimensional Zhu
algebra.

Three explicit candidates survive as genuine frontier problems:
\begin{enumerate}[nosep]
\item \textbf{Monster-type twisted sectors (Frenkel-Lepowsky-Meurman)}:
 the full orbifold $\cV^\natural$ of the Leech lattice VOA by the
 $\mathbb{Z} / 2$ Leech involution, viewed as a sum of twisted sectors,
 has a logarithmic pyramid of pseudo-trace modules whose total
 dimension is infinite (Miyamoto 2004). The genuine open question
 is whether the shadow tower of the WHOLE pyramid (as opposed to
 the vacuum sector alone) is tempered.
\item \textbf{Coset realisations at irrational central charge
 (Creutzig-Kanade-Linshaw)}: commutants
 $\mathrm{Com}(H_{\kappa}, \cA)$ for irrational $\kappa$ typically
 have infinite-dim Zhu algebra generated by a non-rational lattice.
 Tempering of such cosets is open.
\item \textbf{Non-rational affine minimal cosets
 (Adamovi\'c et al.)}: $\widehat{\mathfrak{sl}}_2$ at admissible
 levels $k = -2 + p/q$ has a logarithmic module category with
 infinite-dim Zhu algebra. Tempering is open.
\end{enumerate}
These are the infinite-Zhu frontiers. The triplet $\cW(p)$ is a
separate finite-Zhu frontier until
Conjecture~\ref{conj:wp-regular-sector-amplitude-bound} is proved.
\end{remark}

\begin{conjecture}[Tempering criterion: bounded Zhu implies
tempered]
\label{conj:tempered-unbounded-zhu}
\ClaimStatusConjectured
Let $\cA$ be a simple chiral algebra (chirally Koszul in the Vol~I
sense or more generally). If the Zhu algebra $A(\cA)$ is finite-dimensional
(equivalently, $\cA$ is $C_2$-cofinite), then $\cA$ is analytically
tempered:
\[
 \limsup_{r \to \infty}
 \bigl( \lvert S_r(\cA) \rvert / r! \bigr)^{1/r}
 \;=\; 0.
\]
Equivalently (contrapositive form): every non-tempered VOA has
infinite-dimensional Zhu algebra.
\end{conjecture}

\begin{remark}[Evidence for Conjecture~\ref{conj:tempered-unbounded-zhu}]
\label{rem:evidence-for-tempering-criterion}
The $C_2$-cofinite landscape at this stage of the programme consists
of: (a) generic Virasoro (tempered unconditionally, Vol~II
Theorem~\ref{thm:tempered-stratum-contains-virasoro}); (b) principal
$\cW_N$, $N \ge 2$ (tempered unconditionally, Vol~II
Theorem~\ref{thm:tempered-stratum-contains-w3} for $N=3$,
Theorem~\ref{thm:wn-tempered-all-N} for $N \ge 4$ via $\beta$-
independent Stirling dominance); (c) logarithmic $\cW(p)$ and
singlet $\cM(p)$, $p \ge 2$ (tempered CONDITIONAL on
Conjecture~\ref{conj:tempered-stratum-contains-wp}, which is
\ClaimStatusConjectured~at the present stage; the regular-sector
shadow-tower Massey boundedness claim is not falsified by
Gurarie-Flohr per
Remark~\ref{rem:correlation-vs-shadow-massey}, but a direct
Adamovi\'c-Milas character-amplitude bound is still pending); (d)
lattice VOAs at positive-definite even lattices of finite rank
(tempered unconditionally, since their shadow towers have the
abelian class $\mathsf{G}$ structure with finite depth); (e) affine
$V_k(\mathfrak{g})$ at generic level (tempered unconditionally as
class $\mathsf{L}$ with shadow-tower truncation at $r_{\max} = 3$);
(f) minimal models $L_c(h)$ at rational $c_{p,q}$ (tempered
unconditionally by restricted quotient of generic Virasoro;
finite-dim Zhu structure of Arakawa 2012).

Five of six classes admit unconditional tempering proofs; the
logarithmic class (c) is conjectural and provides the remaining
finite-Zhu test case. The universal-tempering conjecture
is the natural statement once the logarithmic case is closed;
Conjecture~\ref{conj:tempered-unbounded-zhu} records the natural
universal endpoint with its dependency on
Conjecture~\ref{conj:tempered-stratum-contains-wp} made explicit.
\end{remark}

\section{Independent verification structure}
\label{sec:wp-iv-summary}

The proved and conjectural pieces of this chapter have the following
verification and evidence structure, implemented in
\texttt{compute/tests/test\_logarithmic\_wp\_tempered.py} per the
Vol~II HZ-IV protocol.

\textbf{1. Virasoro-sub-channel Kac-exclusion
(Lemma~\ref{lem:wp-virasoro-subchannel-tempered}).}
\begin{itemize}[nosep]
\item \emph{Derived from}: direct algebraic solution of
 $c(p) = 1 - 6(p-1)^2/p = -22/5$: no integer $p \ge 2$ solution.
\item \emph{Verified against}: Vol~I engine
 \texttt{compute/lib/logarithmic\_voa\_shadow\_engine.py::triplet\_central\_charge}
 evaluated at $p = 2, 3, 4, 5, 10$ and compared numerically to
 $-22/5 = -4.4$: all values distinct.
\item \emph{Disjoint rationale}: derivation uses algebraic Kac-zero
 solution; verification uses the independent Vol~I compute
 engine.
\end{itemize}

\textbf{2. Channel-radius arithmetic
(Conjecture~\ref{prop:wp-channel-upper-bounds}, outside the proved
$TT$ line).}
\begin{itemize}[nosep]
\item \emph{Derived from}: Theorem~\ref{thm:tempered-stratum-contains-virasoro}
 for the $TT$ line, plus the Adamovi\'c-Milas OPE pole orders for
 the conjectural $TW$ and $WW$ regular-sector lines.
\item \emph{Verified against}: engine
 \texttt{compute/lib/shadow\_tower\_higher\_vir.py::virasoro\_shadow\_sequence}
 at $c = c(p)$ for $p = 2, 3, 4, 5$ through $r = 8$; the $TW$ and
 $WW$ entries are radius arithmetic targets, not full-channel
 computations. The arithmetic check records that the formal bottleneck
 is $TW$, not $WW$.
\item \emph{Disjoint rationale}: the proved $TT$ line uses the
 Virasoro recurrence engine. The $TW$ and $WW$ lines require a
 future logarithmic $\cW(p)$ shadow engine.
\end{itemize}

\textbf{3. Zhu algebra dimension, not Zhu-bounded Masseys
(Proposition~\ref{prop:wp-zhu-finite}).}
\begin{itemize}[nosep]
\item \emph{Derived from}: Adamovi\'c-Milas 2008
 Proposition~4.3 ($\dim A(\cW(p)) = 2p$).
\item \emph{Verified against}: independent computation of the
 Adamovi\'c-Milas formula for $p = 2, 3, 4, 5$ giving
 $\{4, 6, 8, 10\}$.
\item \emph{Disjoint rationale}: derivation cites the Adamovi\'c-Milas
 paper; verification re-derives the dimension formula arithmetically
 via the triplet's 2 trivial + $p-1$ non-trivial + $p-1$ pseudo-trace
 module count. It does not verify any Massey bound.
\end{itemize}

\textbf{4. Finite free strong generation obstruction
(Proposition~\ref{prop:wp-c2-forbids-finite-free-strong-generation}).}
\begin{itemize}[nosep]
\item \emph{Derived from}: Adamovi\'c--Milas $C_2$-cofiniteness plus
 the Li--PBW description of the $C_2$ quotient of a freely strongly
 generated vertex algebra.
\item \emph{Verified against}: direct Hilbert-series calculation in
 \texttt{compute/lib/logarithmic\_wp\_triplet\_constants.py} for the
 polynomial $C_2$ quotient
 $\CC[x_T,x_{W^+},x_{W^0},x_{W^-}]$ with degrees
 $(2,2p-1,2p-1,2p-1)$.
\item \emph{Disjoint rationale}: the proof uses the structural
 implication ``free strong generation $\Rightarrow$ polynomial
 $C_2$ quotient''; the test computes the forced Hilbert series and
 detects infinite support without using triplet characters.
\end{itemize}

\textbf{5. Regular-sector amplitude bound
(Conjecture~\ref{conj:wp-regular-sector-amplitude-bound}).}
\begin{itemize}[nosep]
\item \emph{Derived from}: not proved; this is the exact missing
 lemma for $TW/WW$ triplet tempering.
\item \emph{Finite reduction}: Proposition~\ref{prop:wp-finite-pole-envelope-reduction}
 proves that any finite residue-state pole-envelope realisation of
 the regular sector gives the required exponential-polynomial bound.
 For the $\cW(2)$ model the exact constants are
 $C_2=4$, $N_2=3$, $R_2=240$.
\item \emph{Verified against}: overclaim guards and the finite-model
 tests in \texttt{compute/tests/test\_logarithmic\_wp\_tempered.py}
 ensure that the chapter does not reassert finite-free-generation,
 full $\cW(2)$ truncation, or a full-triplet radius formula as proved;
 the factorial-growth probe rejects any sequence with $r!$ growth.
\item \emph{Disjoint rationale}: the guard is negative verification:
 it prevents the retracted proof routes from masquerading as
 evidence for the missing lemma. The finite-model certificate proves
 only the combinatorial reduction; the real $\cW(p)$ factorisation
 into that model remains the open mathematical input.
\end{itemize}

\textbf{6. Universal $\cW(p)$ tempering
(Conjecture~\ref{conj:tempered-stratum-contains-wp}).}
\begin{itemize}[nosep]
\item \emph{Derived from}: combination of
 the proved $TT$ line and
 Conjecture~\ref{conj:wp-regular-sector-amplitude-bound}.
\item \emph{Verified against}: numerical extraction of
 $(\lvert S_r^{TT} \rvert / r!)^{1/r}$ at $r = 8$ from the Vol~I
 Virasoro engine at $c = c(p)$ for $p = 3, 4, 5$; values all
 well below $1/e \approx 0.368$.
\item \emph{Disjoint rationale}: this is evidence for the $TT$ line
 only. It does not compute the full triplet shadow tower.
\end{itemize}

\textbf{7. Dichotomy status on $C_2$-cofinite
(Corollary~\ref{cor:wp-dichotomy-healed}).}
\begin{itemize}[nosep]
\item \emph{Derived from}: combination of
 Theorem~\ref{thm:tempered-stratum-contains-virasoro},
 Theorem~\ref{thm:tempered-stratum-contains-w3}, and
 Conjecture~\ref{conj:tempered-stratum-contains-wp}.
\item \emph{Verified against}: explicit enumeration of
 $C_2$-cofinite families with the logarithmic triplet and singlet
 entries marked conjectural, not verified.
\item \emph{Disjoint rationale}: the corollary is a logical
 combination; the verification enumerates the known
 $C_2$-cofinite families.
\end{itemize}

\section{Location in the programme and heal-mode directive applied}
\label{sec:wp-location-heal-mode}

\begin{remark}[Heal-mode directive applied]
\label{rem:wp-heal-mode-applied}
The strongest honest form: the prior
chapter left $\cW(p)$ as "one of three candidates for a non-empty
non-tempered stratum" based on the free-strong-generation Massey-obstruction
characterisation of $\cW(p)$ as non-freely-generated (class
$\mathsf{M}^*$) and the presumed factorial-growth implication of
non-tempering. The honest analysis reveals this presumption to be
unwarranted in two directions. First,
Proposition~\ref{prop:wp-c2-forbids-finite-free-strong-generation}
shows that finite free strong generation is incompatible with the
$C_2$-cofinite triplet; finite PBW agreement is not a proof route.
Second, the Zhu-bounded-Massey mechanism is not a proof of regular
shadow bounds. The strongest honest form is therefore the explicit
missing lemma
Conjecture~\ref{conj:wp-regular-sector-amplitude-bound}; universal
$C_2$-cofinite tempering remains the endpoint conjecture
Conjecture~\ref{conj:tempered-unbounded-zhu}, not a theorem of this
chapter.
\end{remark}

This chapter isolates the logarithmic $\cW(p)$ frontier of
Chapter~\ref{ch:tempered-stratum-characterization}:

\begin{itemize}[nosep]
\item \textbf{Status before this chapter}: $\cW(p)$ left open, listed
 among three candidates for the non-empty non-tempered stratum.
\item \textbf{Status after this chapter}: the $TT$ sub-channel is
 tempered for every $p \ge 2$; the full triplet statement is
 reduced to the regular-sector $TW$ and $WW$ amplitude bounds of
 Conjecture~\ref{conj:tempered-stratum-contains-wp}; the
 chain-level $E_3$-topological structure on the original
 curved-Dunn complex remains conditional on that conjecture.
\item \textbf{Remaining genuine frontiers}: Monster-type twisted
 sectors (infinite pyramid); coset realisations at irrational
 central charge; non-rational affine minimal cosets; and the
 regular-sector $\cW(p)$ triplet bounds for $p \ge 2$.
\item \textbf{Cross-links}:
 Chapter~\ref{ch:tempered-stratum-characterization} (Virasoro + $\cW_3$
 tempering); Vol~I
 \texttt{compute/lib/logarithmic\_voa\_shadow\_engine.py}
 (W(p) structure); Vol~I
 \texttt{compute/lib/wp\_koszulness\_definitive\_engine.py}
 (Adamovi\'c-Milas generator count; Zhu algebra dimension).
\end{itemize}

The universal tempering conjecture
(Conjecture~\ref{conj:tempered-unbounded-zhu}) is a natural endpoint
only after Conjecture~\ref{conj:tempered-stratum-contains-wp} is
proved. The sharp dichotomy presently established is weaker:
non-logarithmic $C_2$-cofinite families are tempered, while the
logarithmic triplet and singlet remain regular-sector frontiers.
