
\section{Cohomological descent to a shifted Poisson vertex algebra}
\label{sec:PVA_descent}
\label{sec:Ainfty-to-PVA}

The $A_\infty$ chiral algebra $(\cA, Q, \{m_k\})$ is a chain-level
object: the operations $m_k$ act on cochains, not on cohomology
classes.  Passing to cohomology $H^\bullet(\cA, Q)$ strips away the
homotopical complexity (the higher operations $m_{k \geq 3}$
become $Q$-exact and vanish, Proposition~\ref{prop:m3_vanish})
and the surviving binary operation~$m_2$ descends to a
$(-1)$-shifted Poisson vertex algebra: a commutative product (from
the regular part of~$m_2$) and a skew-symmetric $\lambda$-bracket
(from the singular part) satisfying Jacobi and Leibniz.  This
descent is the motivic projection of
Remark~\ref{rem:pva-depth-decomposition}: it retains the arithmetic
content of the bar complex while discarding its homotopy-theoretic
part.

Three points of the construction require emphasis.

\begin{enumerate}[label=\textup{(\arabic*)}]
\item We work with the \emph{unsymmetrized} regular and singular parts of the binary kernel.
      Graded commutativity and skew-symmetry are then \emph{theorems}, not definitions.
\item We separate the two formal variables that play different roles.  The collision/OPE
      variable is denoted by $\zeta$, while the standard polynomial PVA variable is denoted
      by $\lambda$.  The two are related by the usual Borel transform of singular coefficients.
\item The Jacobi and Leibniz identities are derived from the \emph{three} pairwise
      boundary divisors $D_{\{1,2\}},D_{\{1,3\}},D_{\{2,3\}}\subset \partial\FM_3(\C)$.
      The non-consecutive face $D_{\{1,3\}}$ is not discarded; it is precisely the geometric
      source of the third Jacobi/Leibniz term.
\end{enumerate}

\begin{maintheorem}[Cohomological descent to a shifted PVA; \ClaimStatusProvedHere]
\label{thm:cohomology-PVA-main}%
\label{thm:cohomology_PVA}%
\label{thm:pva-coisson-bridge}%
Let $(\A,Q,\partial,\mathbf 1,\{m_k\}_{k\ge1})$ be a
logarithmic\/ $\SCchtop$-algebra
\textup{(}Definition~\textup{\ref{def:log-SC-algebra})}.
Write the binary kernel in the collision variable $\zeta$ as
\[
m_2(a,b;\zeta)=m_2^{\mathrm{reg}}(a,b;\zeta)+m_2^{\mathrm{sing}}(a,b;\zeta),
\qquad
m_2^{\mathrm{sing}}(a,b;\zeta)=\sum_{n\ge0}(a_{(n)}b)\,\zeta^{-n-1}.
\]
Define
\[
\mu(a,b):=m_2^{\mathrm{reg}}(a,b;0),
\qquad
\{a_\lambda b\}:=\sum_{n\ge0}\frac{\lambda^n}{n!}\,a_{(n)}b.
\]
Then:

\begin{enumerate}[label=\textup{(\roman*)}]
\item The operations $\mu$ and $\{-{}_\lambda-\}$ descend to $H^\bullet(\A,Q)$.
\item The descended product is unital, associative, and graded commutative; the descended
      $\lambda$-bracket has cohomological degree $-1$ and satisfies sesquilinearity,
      shifted skew-symmetry, Jacobi, and the Leibniz rule.  Hence
      $H^\bullet(\A,Q)$ is a $(-1)$-shifted Poisson vertex algebra.
\item All higher operations $m_{k\ge3}$ vanish on cohomology
      (Proposition~\ref{prop:m3_vanish}).
\end{enumerate}
\end{maintheorem}

The rest of the section proves all three parts.

\begin{remark}[Depth decomposition and PVA formality]
\label{rem:pva-depth-decomposition}
Part~(iii), the vanishing of $m_{k \ge 3}$ on cohomology, is the
statement that the descended $A_\infty$ algebra is \emph{formal}.
In the language of Vol~I
(via the depth decomposition theorem), this means the
\emph{algebraic depth} $d_{\mathrm{alg}}$ of the $3$-dimensional
theory's bar cohomology is zero at the PVA level: the higher Massey
products, which measure the rational homotopy type of the shadow
tower, are killed by the descent to the PVA.  The chiral algebra
itself may have $d_{\mathrm{alg}} = \infty$ (e.g., Virasoro,
where $T_{(1)}T = 2T$ drives an infinite shadow cascade), but the
PVA shadow retains only the \emph{arithmetic} depth
$d_{\mathrm{arith}}$ (Hecke eigenforms, $L$-function content).
The PVA descent is therefore a \emph{motivic projection}: it
strips the mixed-Tate (homotopy-theoretic) part (the higher
$A_\infty$ operations $m_{k \ge 3}$, which become $Q$-exact by the
contractibility of $\Conf_k^<(\R)$, Proposition~\ref{prop:m3_vanish})
and preserves
the non-Tate (arithmetic) part of the depth decomposition, namely
the binary product $m_2$ and its residues.
In the shadow metric formulation
(of Volume~I),
the PVA shadow is the
$\hbar \to 0$ limit of $Q_L(t)$: the critical discriminant
$\Delta = 8\kappa S_4$ vanishes on the classical slice,
recovering the Gaussian envelope
$Q_L^{\mathrm{cl}}(t) = (2\kappa + 3\alpha t)^2$.
\end{remark}

\begin{remark}[PVA descent as the classical projection of a two-stage tower]
\label{rem:pva-two-stage-projection}
\index{PVA descent!two-stage projection}
\index{averaging map!PVA as further projection}
The Poisson vertex algebra $H^\bullet(\cA, Q)$ arises by a
two-stage projection from the ordered (primitive) bar data.  The
first stage is the averaging map
$\mathrm{av}\colon T^c(s^{-1}\bar\cA) \to \Sym^c(s^{-1}\bar\cA)$,
which passes from the ordered bar complex $\barB^{\mathrm{ord}}(\cA)$
(the $E_1$ coalgebra, retaining full $R$-matrix and spectral data)
to the symmetric bar complex $\barB^{\Sigma}(\cA)$ (the modular
coalgebra, retaining the scalar invariants $\kappa$, cubic shadow, etc.).
The second stage is the passage to cohomology
$H^\bullet(\cA, Q)$: the higher $A_\infty$ operations $m_{k \ge 3}$
become $Q$-exact and vanish
(Proposition~\ref{prop:m3_vanish}), and the binary operation~$m_2$
descends to the commutative product and $\lambda$-bracket of the PVA.
Thus the full chain of projections is
\[
  T^c \;\xrightarrow{\;\mathrm{av}\;}
  \Sym^c \;\xrightarrow{\;H^\bullet\;}
  \mathrm{PVA}.
\]
The first arrow forgets the $R$-matrix (ordered-to-unordered); the
second forgets homotopy (chain-level to cohomology).  The
PVA retains the arithmetic content of the bar complex
(binary residues, Hecke eigenforms) while discarding both
the spectral data ($R$-matrix, Yangian coherences) and the
homotopy data (higher $A_\infty$ operations, shadow obstruction
tower).
\end{remark}

\begin{remark}[Unsymmetrized vs.\ symmetrized product]
\label{rem:unsymmetrized-product}
The product $\mu(a,b) := m_2^{\mathrm{reg}}(a,b;0)$ defined above is
\emph{unsymmetrized}: it uses $m_2^{\mathrm{reg}}(a,b;0)$ directly, whereas
Definition~\ref{def:product} in \S\ref{subsec:product-bracket} defines
the symmetrized product
$[a]\cdot[b] := \tfrac{1}{2}\bigl(m_2^{\mathrm{reg}}(a,b) +
(-1)^{|a||b|}m_2^{\mathrm{reg}}(b,a)\bigr)$.
The two agree on $H^\bullet(\A,Q)$: the exchange cylinder
(Proposition~\ref{prop:product-commutative}) proves graded commutativity of
$\mu$ on cohomology, so the symmetrization is redundant \emph{a~posteriori}.
The unsymmetrized form simplifies the chain-level
Stokes arguments; the symmetrized form in \S\ref{subsec:product-bracket}
makes skew-symmetry manifest at the cochain level.
\end{remark}

\begin{remark}[Symplectic origin of the shifted PVA]
\label{rem:symplectic-origin-PVA}
The $(-1)$-shifted PVA on $H^\bullet(\A,Q)$ is
related to a $(-1)$-shifted symplectic structure (PTVV), via two steps.

\smallskip\noindent\emph{Step~1: from $\mathfrak{S}_b$ to the bar complex.}
The self-intersection
$\mathfrak{S}_b = \mathscr{L}_b \times_{\mathscr{M}} \mathscr{L}_b$ of the
Lagrangian embedding $\mathscr{L}_b \hookrightarrow \mathscr{M}$ carries a
canonical $(-1)$-shifted symplectic form (PTVV).
By Theorem~\ref{thm:bar-is-self-intersection}, the bar complex
$\barB(\A)$ provides the formal bar/Koszul model for the derived
functions on $\mathfrak{S}_b$ near the boundary locus, so the
$(-1)$-shifted symplectic form induces a $(-1)$-shifted Poisson
bracket on $\barB(\A)$.

\smallskip\noindent\emph{Step~2: descent to cohomology.}
The bracket on $\barB(\A)$ descends to $H^\bullet(\barB(\A))
\simeq H^\bullet(\A,Q)$ by the shifted Darboux formalism
(Proposition~\ref{prop:PVA-from-symplectic}).  It is at this
stage that the $\lambda$-bracket
$\{{\cdot}_\lambda{\cdot}\}$ appears, via the residue extraction
along the collision divisor $D_{\{1,2\}} \subset \FM_2(\C)$.

\smallskip
The proofs of the PVA axioms below (Jacobi from the three-face
Stokes argument on $\FM_3(\C)$, Leibniz from the exchange cylinder,
skew-symmetry from the two-point winding) are direct
computations using the manifold-with-corners structure of
$\FM_k(\C)$.  They can be \emph{interpreted} as reflecting
geometric properties of the self-intersection $\mathfrak{S}_b$,
but the proofs themselves do not invoke derived symplectic
geometry; they are independent of it.
\end{remark}

\providecommand{\Steinb}{\mathfrak{S}}

\begin{proposition}[The PVA bracket is the Steinberg Poisson bracket;
\ClaimStatusProvedElsewhere]
\label{prop:PVA-from-symplectic}
The $(-1)$-shifted Poisson bracket $\{a_\lambda b\}$ on $H^\bullet(\A,Q)$ is
the Poisson bracket associated to the $(-1)$-shifted symplectic structure
$\omega_{-1}$ on the Steinberg self-intersection
$\Steinb_b = \mathscr{L}_b \times_{\mathscr{M}} \mathscr{L}_b$
\textup{(}Theorem~\textup{\ref{thm:steinberg-presentation}},
Remark~\textup{\ref{rem:steinberg-lagrangian-origin})}.
\end{proposition}

\begin{proof}
The argument has three steps.

\smallskip
\noindent\textbf{Step~1 (Functions on the self-intersection).}
By Theorem~\ref{thm:bar-is-self-intersection}, the bar complex
$\barB(\A)$ supplies the formal bar/Koszul model for the derived
functions on the Lagrangian self-intersection near the boundary
locus.
The Lagrangian embedding
$\mathscr{L}_b \hookrightarrow \mathscr{M}$ into the $(-2)$-shifted
symplectic target endows the derived self-intersection $\Steinb_b$ with a
canonical $(-1)$-shifted symplectic form $\omega_{-1}$
(Pantev--To\"en--Vaqui\'e--Vezzosi~\cite{PTVV13}).

\smallskip
\noindent\textbf{Step~2 (From symplectic form to Poisson bracket).}
The $(-1)$-shifted symplectic form $\omega_{-1}$ on $\Steinb_b$ induces,
by the shifted Darboux formalism, a $(-1)$-shifted Poisson bracket
$\{-,-\}_{\omega}$ on $\mathcal{O}(\Steinb_b) \simeq \barB(\A)$.
A remark on structures: $\barB(\A)$ carries a
\emph{coalgebra} structure (the deconcatenation coproduct from the
bar construction), but $\mathcal{O}(\Steinb_b)$ is a commutative
dg-\emph{algebra} (the algebra of derived functions on the
self-intersection).  The identification
$\barB(\A) \simeq \mathcal{O}(\Steinb_b)$ endows $\barB(\A)$ with
a commutative product \emph{in addition to} its coalgebra structure;
the Poisson bracket is a binary operation on this commutative
algebra structure, not on the coalgebra.  (The two structures are
compatible: they assemble into a bialgebra in the derived sense,
reflecting the Hopf-algebraic nature of the groupoid algebra
$\mathcal{O}(\Steinb_b)$.)
On cohomology $H^\bullet(\barB(\A)) \simeq H^\bullet(\A,Q)$, this
bracket descends to a well-defined $(-1)$-shifted Poisson structure.

\smallskip
\noindent\textbf{Step~3 (Identification with the $\lambda$-bracket).}
The $\lambda$-bracket
\[
\{a_\lambda b\}
\;=\;
\Res_{\zeta=0}\bigl[m_2^{\mathrm{sing}}(a,b;\zeta)\cdot e^{\lambda\zeta}\bigr]
\]
extracts the residue of the binary singular kernel along the collision
divisor $D_{\{1,2\}} \subset \FM_2(\C)$.  Under the identification
$\barB(\A) \simeq \mathcal{O}(\Steinb_b)$, this collision divisor is
the conormal direction to the diagonal
$\Delta \colon \mathscr{L}_b \hookrightarrow
\mathscr{L}_b \times_{\mathscr{M}} \mathscr{L}_b$:
the residue along $D_{\{1,2\}}$ extracts the conormal component
of the Poisson bivector, that is, the component in
$N^*_{\Delta/\Steinb_b}$ transverse to the diagonal
$\Delta \colon \mathscr{L}_b \hookrightarrow \Steinb_b$.
The Lagrangian condition identifies this conormal bundle with the
tangent bundle $T\mathscr{L}_b$, so the residue is a bivector on
$\mathscr{L}_b$, which is precisely the $(-1)$-shifted Poisson
bivector $\pi_\omega$ dual to $\omega_{-1}$.
The exponential $e^{\lambda\zeta}$ is the Borel kernel that converts
the Laurent residue into the polynomial $\lambda$-bracket.
Hence $\{a_\lambda b\}$ on $H^\bullet(\A,Q)$ coincides with the
descended Poisson bracket $\{-,-\}_{\omega}$.
\end{proof}

\subsection{Binary descent from the arity-$2$ relation}

\begin{proposition}[$A_\infty$ arity-$2$ compatibility; \ClaimStatusProvedHere]
\label{prop:m1_m2}
The $n=2$ specialization of the $A_\infty$ identity \eqref{eq:ainfty-relation-raw} is
\begin{equation}
\label{eq:repaired-n2}
Q(m_2(a,b))=m_2(Qa,b)+(-1)^{\degree{a}}m_2(a,Qb).
\end{equation}
Equivalently, $Q=m_1$ is a graded derivation of the binary operation.
\end{proposition}

\begin{proof}
This is exactly the $(i,j)=(1,2)$ and $(i,j)=(2,1)$ part of
\eqref{eq:ainfty-relation-raw}.  No other term occurs at arity $2$.
\end{proof}

\begin{lemma}[Descent of the regular and singular binary parts; \ClaimStatusProvedHere]
\label{lem:lambda_descends}
Let $a,b\in\A$ be $Q$-closed.  Then $\mu(a,b)$ and $\{a_\lambda b\}$ are $Q$-closed and
their cohomology classes depend only on the classes $[a],[b]\in H^\bullet(\A,Q)$.
\end{lemma}

\begin{proof}
Since $Q$ acts on coefficients in $\A$ and does not touch the formal variables,
it commutes with the regular/singular projections and with taking the constant
term at $\zeta=0$.  Thus \eqref{eq:repaired-n2} implies
\[
Q\mu(a,b)=\mu(Qa,b)+(-1)^{\degree{a}}\mu(a,Qb),
\]
and, coefficientwise in the singular expansion,
\[
Q(a_{(n)}b)=(Qa)_{(n)}b+(-1)^{\degree{a}}a_{(n)}(Qb).
\]
Hence $Qa=Qb=0$ implies $Q\mu(a,b)=0$ and $Q(a_{(n)}b)=0$ for all $n\ge0$, so the
polynomial bracket $\{a_\lambda b\}$ is $Q$-closed coefficientwise.

If $a'=a+Qx$, then \eqref{eq:repaired-n2} gives
\[
m_2(a',b)-m_2(a,b)
=
m_2(Qx,b)
=
Qm_2(x,b)-(-1)^{\degree{x}}m_2(x,Qb).
\]
For $Qb=0$, the difference is $Q$-exact.  Applying the regular projection, constant-term
projection, or any coefficient projection of the singular part preserves $Q$-exactness.
The same argument applies in the second variable.
\end{proof}

\begin{proposition}[Sesquilinearity in cohomology; \ClaimStatusProvedHere]
\label{prop:PVA1_proof}
The descended $\lambda$-bracket satisfies the standard polynomial PVA relations
\begin{align}
\label{eq:repaired-PVA1a}
\{\partial a_\lambda b\} &= -\lambda\,\{a_\lambda b\},\\
\label{eq:repaired-PVA1b}
\{a_\lambda \partial b\} &= (\lambda+\partial)\,\{a_\lambda b\}.
\end{align}
\end{proposition}

\begin{proof}
The polynomial bracket is defined from the singular coefficients, not
from the Laurent kernel itself.  Those coefficients are precisely the coefficients that
appear in the chain-level sesquilinearity relations of
Definition~\ref{def:sesquilinearity}.  Therefore the same relations descend coefficientwise
to cohomology.  The Borel transform packaging
$\sum_{n\ge0}(a_{(n)}b)\,\lambda^n/n!$ preserves linear identities among the coefficients,
so the polynomial bracket satisfies \eqref{eq:repaired-PVA1a}--\eqref{eq:repaired-PVA1b}.
\end{proof}

\subsection{The exchange cylinder and the two-point symmetry theorem}

The $A_\infty$ operations are defined on \emph{ordered} configurations:
the inputs $a_1, \ldots, a_k$ are ordered by $t_1 < \cdots < t_k$
on the topological line.  The ordered configuration space
$\Conf_2^{<}(\R)$ is disconnected (its two components correspond
to the two orderings $t_1 < t_2$ and $t_2 < t_1$), so the
topological direction alone cannot exchange two insertions.  But
$\Conf_2(\C \times \R)$ \emph{is} connected: two bulk insertions
exchange by winding in the holomorphic plane (a half-turn around the
collision divisor) while simultaneously swapping their topological
coordinates.  This exchange cylinder is the geometric mechanism that
produces both graded commutativity of the product and shifted
skew-symmetry of the bracket on cohomology.

\begin{construction}[Explicit exchange path]
\label{const:exchange-cylinder}
Fix $r>0$ and consider two bulk points in $\R_t\times\C_z$:
\[
x_1(0)=(-1,r),\qquad x_2(0)=(1,-r).
\]
Define a path $s\mapsto (x_1(s),x_2(s))\in \Conf_2(\R\times\C)$ by
\begin{equation}
\label{eq:exchange-path}
x_1(s)=\bigl(-\cos(\pi s),\,r\,e^{\pi i s}\bigr),
\qquad
x_2(s)=\bigl(\cos(\pi s),\,-r\,e^{\pi i s}\bigr),
\qquad 0\le s\le1.
\end{equation}
Its separation vector is
\[
x_1(s)-x_2(s)=\bigl(-2\cos(\pi s),\,2r\,e^{\pi i s}\bigr),
\]
which never vanishes: at $s=\tfrac12$ the topological separation vanishes, but the
holomorphic separation is $2ri\neq0$; away from $s=\tfrac12$ the topological separation
is already nonzero.  Thus \eqref{eq:exchange-path} is a genuine isotopy in the full
configuration space exchanging the two endpoints.
\end{construction}

\begin{remark}[The exchange cylinder as symplectic rotation]
\label{rem:exchange-symplectic-rotation}
The exchange path~\eqref{eq:exchange-path} winds in the holomorphic $\C$-plane
while simultaneously transposing the topological $\R$-coordinates.  In the
language of the $(-1)$-shifted self-intersection $\mathfrak{S}_b$, this is
the Lagrangian monodromy of the correspondence: the holomorphic winding
is the symplectic rotation that connects the two sheets of the
self-intersection, and the topological transposition records the change
of $E_1$-ordering.  Commutativity and skew-symmetry on cohomology
(Propositions~\ref{prop:product-commutative} and~\ref{prop:PVA2_proof}) are
thus consequences of the monodromy being contractible in the full
$\C\times\R$ configuration space.
\end{remark}

\begin{proposition}[Exchange path as Lagrangian monodromy;
\ClaimStatusProvedHere]
\label{prop:exchange-lagrangian-monodromy}
The exchange path \textup{(}holomorphic winding in $\C$ combined
with topological transposition in $\R$\textup{)} is the Lagrangian
monodromy of the $(-1)$-shifted self-intersection\/
$\mathfrak{S}_b$ around the collision divisor\/
$D_{1,2} \subset \FM_2(\C)$.  Specifically:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The exchange path traces a loop in the full
  three-dimensional configuration space\/
  $\mathrm{Conf}_2(\C \times \R)$ that exchanges the two
  points.  This loop generates\/
  $\pi_1\bigl(\mathrm{Conf}_2(\C \times \R)\bigr) \cong \Z$.
\item The monodromy of the $(-1)$-shifted symplectic form\/
  $\omega_{-1}$ on\/ $\mathfrak{S}_b$ along this generator is the
  involution $\sigma$ exchanging the two sheets of the
  self-intersection.
\item The skew-symmetry\/
  $\{a_\lambda b\} = -\{b_{-\lambda-\partial} a\}$ is the statement\/
  $\sigma^*(\mathrm{residue}) = -(\mathrm{residue})$:
  the monodromy acts by $-1$ on the collision residue.
\end{enumerate}
\end{proposition}

\begin{proof}
The space $\mathrm{Conf}_2(\R)$ is \emph{disconnected} (two
components indexed by the ordering), so the exchange path does
not live in the product $\FM_2(\C) \times \mathrm{Conf}_2(\R)$.
Rather, the exchange path lives in the full three-dimensional
configuration space $\mathrm{Conf}_2(\C \times \R)$, which
\emph{is} connected (Construction~\ref{const:exchange-cylinder}).
The $\FM_2(\C)$ factor is homotopy equivalent to $S^1$ (the
angular coordinate around the collision divisor $D_{1,2}$), and
the exchange path combines a half-turn in the holomorphic factor
with a transposition in the topological factor, producing a
generator of $\pi_1(\mathrm{Conf}_2(\C \times \R)) \cong \Z$.

The self-intersection $\mathfrak{S}_b = \cL \times_{\cM}^h \cL$
is fibered over $\FM_2(\C)$ with fiber the two-point OPE data.
The $(-1)$-shifted symplectic form $\omega_{-1}$ on $\mathfrak{S}_b$
restricts to the collision residue along $D_{1,2}$: it is the
pairing $\Res_{z_1 = z_2}[a(z_1) b(z_2) \, d\log(z_1 - z_2)]$
that defines the $\lambda$-bracket.  Under the exchange generator
(half-turn in $\FM_2(\C)$ combined with topological transposition),
$z_1 - z_2 \mapsto z_2 - z_1$: the residue integral changes sign
because the contour orientation reverses (equivalently,
$\log(z_1-z_2) \mapsto \log(z_1-z_2) + i\pi$ contributes a
sign to the integrand).  Algebraically:
$\sigma^*\{a_\lambda b\} = \{b_{-\lambda - \partial} a\}$, and
the relation $\{a_\lambda b\} = -\{b_{-\lambda - \partial} a\}$
is precisely $\sigma^*(\mathrm{residue}) = -(\mathrm{residue})$.
\end{proof}

\begin{lemma}[Chain-level exchange homotopies; \ClaimStatusProvedHere]
\label{lem:PVA2_proof}
Let $H^{\mathrm{reg}}_{\mathrm{ex}}(a,b)$ and
$H^{\mathrm{sing}}_{\mathrm{ex}}(a,b;\zeta)$ be the chain homotopies obtained by
pulling the two-point weight form along the cylinder swept out by
\eqref{eq:exchange-path} and then projecting to the regular and singular sectors.
Then:
\begin{align}
\label{eq:exchange-reg}
\mu(a,b)-(-1)^{\degree{a}\degree{b}}\mu(b,a)
&=
QH^{\mathrm{reg}}_{\mathrm{ex}}(a,b)
-H^{\mathrm{reg}}_{\mathrm{ex}}(Qa,b)
-(-1)^{\degree{a}}H^{\mathrm{reg}}_{\mathrm{ex}}(a,Qb),\\[4pt]
\label{eq:exchange-sing}
m_2^{\mathrm{sing}}(a,b;\zeta)
+(-1)^{(\degree{a}+1)(\degree{b}+1)}
\,\tau^\ast m_2^{\mathrm{sing}}(b,a;\zeta)
&=
QH^{\mathrm{sing}}_{\mathrm{ex}}(a,b;\zeta)
-H^{\mathrm{sing}}_{\mathrm{ex}}(Qa,b;\zeta) \notag\\
&\quad
-(-1)^{\degree{a}}H^{\mathrm{sing}}_{\mathrm{ex}}(a,Qb;\zeta),
\end{align}
where $\tau^\ast$ denotes the standard vertex-algebra involution
$\zeta\mapsto-\zeta$ (which becomes $\lambda\mapsto-\lambda$ under
Borel transform) together with translation transfer
$\lambda\mapsto\lambda-\partial$; the net substitution is
$\lambda\mapsto-\lambda-\partial$.
\end{lemma}

\begin{proof}
Pull back the two-point logarithmic kernel to the exchange cylinder
$[0,1]\times \FM_2(\C)$ obtained from Construction~\ref{const:exchange-cylinder}.
Because the theory is topological in the $t$-direction, moving along the $s$-parameter
changes the correlation kernel by a $Q$-exact term.  Concretely, if
$\widetilde\omega_2(a,b)$ is the two-point weight form, define
\[
\Xi_{\mathrm{ex}}(a,b):=\int_0^1 \iota_{\partial_s}\widetilde\omega_2(a,b;s)\,ds.
\]
Stokes' theorem on the cylinder gives
\[
(Q+d)\Xi_{\mathrm{ex}}(a,b)
=
\widetilde\omega_2(a,b)\big|_{s=1}
-
\widetilde\omega_2(a,b)\big|_{s=0}.
\]
At $s=0$ we recover the original ordering.  At $s=1$ the inputs are exchanged.
For the regular part $\mu$, which has degree $0$ after taking the constant term,
the exchange sign is the ordinary graded-commutative sign
$(-1)^{\degree{a}\degree{b}}$.

For the singular part the operation $m_2^{\mathrm{sing}}$ has cohomological degree $-1$.
The Koszul transposition sign for exchanging two inputs of a degree-$(-1)$ map is
$(-1)^{(\degree{a}-1)(\degree{b}-1)}$.  Since the exponents
$(\degree{a}-1)(\degree{b}-1)$ and $(\degree{a}+1)(\degree{b}+1)$ differ by
$-2\degree{a}-2\degree{b}$, which is always even, we have
\[
(-1)^{(\degree{a}-1)(\degree{b}-1)}
=
(-1)^{(\degree{a}+1)(\degree{b}+1)}.
\]
This is exactly the sign appearing in \eqref{eq:exchange-sing}.  The involution
$\tau^\ast$ records that exchanging the two points sends the collision coordinate
$\zeta=z_1-z_2$ to $-\zeta=z_2-z_1$; after Borel transform this is the usual
substitution $\lambda\mapsto-\lambda-\partial$.
Projecting the Stokes identity to the regular and singular sectors yields
\eqref{eq:exchange-reg} and \eqref{eq:exchange-sing}.
\end{proof}

\begin{proposition}[Graded commutativity of the product; \ClaimStatusProvedHere]
\label{prop:product-commutative}
On cohomology,
\[
[a]\cdot[b]:=[\mu(a,b)]
\]
is graded commutative:
\[
[a]\cdot[b]=(-1)^{\degree{a}\degree{b}}[b]\cdot[a].
\]
\end{proposition}

\begin{proof}
If $Qa=Qb=0$, \eqref{eq:exchange-reg} shows that
$\mu(a,b)-(-1)^{\degree{a}\degree{b}}\mu(b,a)$ is $Q$-exact.  Passing to
cohomology gives the claim.
\end{proof}

\begin{proposition}[Skew-symmetry of the $\lambda$-bracket; \ClaimStatusProvedHere]
\label{prop:PVA2_proof}
For cohomology classes $[a],[b]\in H^\bullet(\A,Q)$,
\begin{equation}
\label{eq:repaired-skew}
\{[a]_\lambda [b]\}
=
-(-1)^{(\degree{a}+1)(\degree{b}+1)}
\{[b]_{-\lambda-\partial}[a]\}.
\end{equation}
\end{proposition}

\begin{proof}
Take the singular part of the exchange identity \eqref{eq:exchange-sing} on
$Q$-closed representatives.  The right-hand side is $Q$-exact, hence vanishes in
cohomology.  Now apply the Borel transform coefficientwise.  Since the Borel transform
commutes with linear combinations and with the translation operator $\partial$ on
coefficients, it converts the $\tau^\ast$-action on the Laurent kernel into the standard
polynomial substitution $\lambda\mapsto-\lambda-\partial$.  This gives
\eqref{eq:repaired-skew}.
\end{proof}

\subsection{Associativity from the regular--regular sector}

\begin{proposition}[Associativity of the descended product; \ClaimStatusProvedHere]
\label{prop:product-associative}
The product $[a]\cdot[b]:=[\mu(a,b)]$ is associative on $H^\bullet(\A,Q)$.
\end{proposition}

\begin{proof}
Take the $n=3$ $A_\infty$ relation and evaluate it on $Q$-closed inputs
$a,b,c$.  Project to the regular--regular sector and then set all collision variables
to $0$.  The only surviving compositions are the two ordered products:
\[
\mu(\mu(a,b),c)-\mu(a,\mu(b,c)).
\]
(The sign $(-1)^{|a|}$ in the $A_\infty$ identity becomes trivial on the
symmetrized product: since $\mu$ is graded commutative on $Q$-closed inputs
(Proposition~\ref{prop:product-commutative}), the two orderings
$\mu(\mu(a,b),c)$ and $\mu(a,\mu(b,c))$ are the only surviving terms after
regular--regular projection and symmetrization.)
The remaining contribution is the regular--regular projection of the $m_3$ term,
which is $Q$-exact because the total-collision face contributes a $Q$-boundary
(the vanishing of $m_3$ on cohomology, proved in
Proposition~\ref{prop:m3_vanish} below, ensures the remaining term is $Q$-exact).
Hence the associator is $Q$-exact.  Passing to cohomology gives strict associativity.
\end{proof}

\subsection{The three-face Stokes theorem on $\FM_3(\C)$}
\label{subsec:three-face-stokes}

The Jacobi and Leibniz identities for the PVA bracket arise from
Stokes' theorem on the three-point configuration space $\FM_3(\C)$.
The key geometric fact is that $\partial\FM_3(\C)$ has \emph{three}
pairwise collision divisors $D_{\{1,2\}}$, $D_{\{2,3\}}$, and
$D_{\{1,3\}}$, plus a total-collision face $D_{\{1,2,3\}}$: the
first two correspond to consecutive collisions, but the third
(the non-consecutive face $D_{\{1,3\}}$) is the geometric
source of the third Jacobi term.  Discarding it would break Jacobi.

The $3$-point geometry requires all three pairwise divisors:
\[
D_{\{1,2\}},\qquad D_{\{2,3\}},\qquad D_{\{1,3\}}\subset \partial\FM_3(\C).
\]
The orientation signs are
\[
\epsilon_{12}=+1,\qquad \epsilon_{23}=+1,\qquad \epsilon_{13}=-1,
\]
as computed in Appendix~\ref{app:orientations}.  The minus sign on $D_{\{1,3\}}$
is exactly what is needed for the third Jacobi/Leibniz term.

\begin{lemma}[Three-face singular factorization; \ClaimStatusProvedHere]
\label{lem:PVA3_proof}
Let $\Omega_3^{\mathrm{sing}\text{-}\mathrm{sing}}(a,b,c)$ be the doubly singular sector of the
three-point logarithmic form.  Then its residues along the three pairwise divisors are:
\begin{align}
\label{eq:res12-jac}
\Res_{D_{\{1,2\}}}\Omega_3^{\mathrm{sing}\text{-}\mathrm{sing}}
&=
\beta(\beta(a,b),c)\ \leadsto\ \{\{a_\lambda b\}_{\lambda+\mu}c\},\\[4pt]
\label{eq:res23-jac}
\Res_{D_{\{2,3\}}}\Omega_3^{\mathrm{sing}\text{-}\mathrm{sing}}
&=
\beta(a,\beta(b,c))\ \leadsto\ \{a_\lambda\{b_\mu c\}\},\\[4pt]
\label{eq:res13-jac}
\Res_{D_{\{1,3\}}}\Omega_3^{\mathrm{sing}\text{-}\mathrm{sing}}
&=
(-1)^{(\degree{a}+1)(\degree{b}+1)}
\,\beta(b,\beta(a,c))
\ \leadsto\ 
(-1)^{(\degree{a}+1)(\degree{b}+1)}
\{b_\mu\{a_\lambda c\}\}.
\end{align}
The symbol ``$\leadsto$'' means: apply the Borel transform in the relevant singular
variables and substitute the outer fused parameter by the sum of the inner parameters.
\end{lemma}

\begin{proof}
Near each divisor one chooses standard FM blow-up coordinates.

\smallskip
\noindent\textbf{Face $D_{\{1,2\}}$.}
Write
\[
\zeta_{12}=z_1-z_2=\varepsilon_{12}e^{i\theta_{12}},
\qquad
u_{12}=\frac{z_1+z_2}{2}-z_3.
\]
The product decomposition in Definition~\ref{def:log-SC-algebra} implies that, up to terms regular in $\varepsilon_{12}$,
the three-point form splits as
\[
d\log\varepsilon_{12}\wedge
\omega_2(a,b;\zeta_{12})
\wedge
\omega_2\bigl(m_2(a,b),c;u_{12}\bigr).
\]
Taking the singular residue in the inner and outer channels yields the iterated singular
composition $\beta(\beta(a,b),c)$.  The outer fused collision parameter is the sum of
the two incoming polynomial parameters, hence $\lambda+\mu$.

\smallskip
\noindent\textbf{Face $D_{\{2,3\}}$.}
Similarly, with
\[
\zeta_{23}=z_2-z_3=\varepsilon_{23}e^{i\theta_{23}},
\qquad
u_{23}=z_1-\frac{z_2+z_3}{2},
\]
factorization gives the ordered composition $\beta(a,\beta(b,c))$, which becomes
$\{a_\lambda\{b_\mu c\}\}$ after Borel transform.

\smallskip
\noindent\textbf{Face $D_{\{1,3\}}$.}
Here
\[
\zeta_{13}=z_1-z_3=\varepsilon_{13}e^{i\theta_{13}},
\qquad
u_{13}=z_2-\frac{z_1+z_3}{2}.
\]
The residue again factors into an inner and an outer binary piece, but now the
cluster $\{1,3\}$ has to be moved past the external input $b$.  Because the singular
binary piece has degree $-1$, the transposition contributes the shifted Koszul sign
$(-1)^{(\degree{a}+1)(\degree{b}+1)}$.  Combining this with the orientation sign
$\epsilon_{13}=-1$ produces exactly the third Jacobi term with the correct overall sign.
\end{proof}

\begin{theorem}[Jacobi identity; \ClaimStatusProvedHere]
\label{thm:Jacobi}
For all cohomology classes $[a],[b],[c]\in H^\bullet(\A,Q)$,
\begin{equation}
\label{eq:repaired-jacobi}
\{[a]_\lambda\{[b]_\mu[c]\}\}
-
(-1)^{(\degree{a}+1)(\degree{b}+1)}
\{[b]_\mu\{[a]_\lambda[c]\}\}
=
\{\{[a]_\lambda[b]\}_{\lambda+\mu}[c]\}.
\end{equation}
\end{theorem}

\begin{proof}
Apply Stokes' theorem to the doubly singular three-point form:
\[
0
=
\int_{\FM_3(\C)}(Q+d)\Omega_3^{\mathrm{sing}\text{-}\mathrm{sing}}
=
QJ_3(a,b,c)+
\sum_{S\in\{\{1,2\},\{2,3\},\{1,3\}\}}
\epsilon_S\int_{D_S}\Res_{D_S}\Omega_3^{\mathrm{sing}\text{-}\mathrm{sing}}.
\]
Here $J_3(a,b,c)$ is the interior Jacobiator homotopy.  The total-collision divisor
contributes only the $Q$-boundary term $QJ_3(a,b,c)$, so it disappears after passage
to cohomology.  By Lemma~\ref{lem:PVA3_proof}, the three pairwise residues are exactly
the three iterated brackets in \eqref{eq:repaired-jacobi}.  Arnold--Orlik--Solomon
cancellation at codimension-$2$ corners (Theorem~\ref{thm:Arnold_full_proof}, Appendix~\ref{app:FM_Stokes}) ensures that no extra corner contribution survives.
Hence the Jacobiator is $Q$-exact; on cohomology it vanishes.
\end{proof}

\begin{remark}[Lagrangian correspondences and the Jacobi identity]
\label{rem:jacobi-lagrangian}
The three boundary faces $D_{\{1,2\}},D_{\{2,3\}},D_{\{1,3\}}\subset
\partial\FM_3(\C)$ appearing in the Stokes argument are the three ways of
composing Lagrangian correspondences in the $(-1)$-shifted symplectic
self-intersection $\mathfrak{S}_b$.  The Jacobi identity is thus the
associativity of correspondence composition.  The codimension-$2$ cancellation
(Arnold--Orlik--Solomon) is the statement that transverse Lagrangian triple
intersections carry well-defined orientations, so no boundary correction
survives the passage to cohomology.
\end{remark}

\begin{proposition}[Jacobi as associativity of Lagrangian convolution;
\ClaimStatusProvedHere]
\label{prop:jacobi-lagrangian-convolution}
The Jacobi identity for $\{{\cdot}_\lambda{\cdot}\}$ is the associativity
of Lagrangian triple convolution in $\Steinb_b$.
\end{proposition}

\begin{proof}
The three boundary faces of $\FM_3(\C)$ are the three collision divisors
\[
D_{\{1,2\}},\qquad D_{\{2,3\}},\qquad D_{\{1,3\}}.
\]
Under the identification of $\barB(\A)$ with the formal
bar/Koszul model of the derived self-intersection
\textup{(}Theorem~\textup{\ref{thm:bar-is-self-intersection}}\textup{)},
each divisor $D_S$
corresponds to a Lagrangian correspondence composition.  Concretely, the
self-intersection $\Steinb_b = \mathscr{L}_b \times_{\mathscr{M}}
\mathscr{L}_b$ acts as a correspondence from $\mathscr{L}_b$ to itself,
and the triple fibre product
$\mathscr{L}_b \times_{\mathscr{M}} \mathscr{L}_b \times_{\mathscr{M}}
\mathscr{L}_b$ admits three pair-projections
\[
p_{12},\quad p_{23},\quad p_{13}
\;\colon\;
\Steinb_b \times_{\mathscr{L}_b} \Steinb_b
\;\longrightarrow\;
\Steinb_b,
\]
one for each way of composing two of the three Lagrangian
correspondences.  These three projections are precisely the
restrictions to the three collision divisors:
\begin{itemize}
\item $D_{\{1,2\}}$: compose via $p_{12}$, yielding the iterated bracket
  $\{\{a_\lambda b\}_{\lambda+\mu} c\}$;
\item $D_{\{2,3\}}$: compose via $p_{23}$, yielding
  $\{a_\lambda \{b_\mu c\}\}$;
\item $D_{\{1,3\}}$: compose via $p_{13}$, yielding
  $(-1)^{(\degree{a}+1)(\degree{b}+1)}\{b_\mu \{a_\lambda c\}\}$.
\end{itemize}
These are the three residues computed in
Lemma~\ref{lem:PVA3_proof}.

Stokes' theorem on $\FM_3(\C)$ states
$\int_{\partial\FM_3(\C)} = 0$ (up to $Q$-exact terms that vanish on
cohomology).  The boundary $\partial\FM_3(\C)$ has four divisors:
$D_{\{1,2\}}$, $D_{\{2,3\}}$, $D_{\{1,3\}}$, and the total collision
$D_{\{1,2,3\}}$.  The total collision divisor $D_{\{1,2,3\}} \cong \FM_3(\C)$
contributes a $Q$-exact term (the $m_1$--$m_3$ cross-terms of
\S\ref{sec:FM_calculus}) that vanishes on passing to cohomology $H^\bullet(A,Q)$,
so only the three pairwise divisors survive, with orientation signs
$\epsilon_{12}=+1$, $\epsilon_{23}=+1$, $\epsilon_{13}=-1$.
The vanishing of the total boundary integral is therefore
\[
\{a_\lambda\{b_\mu c\}\}
\;-\;
(-1)^{(\degree{a}+1)(\degree{b}+1)}\{b_\mu\{a_\lambda c\}\}
\;=\;
\{\{a_\lambda b\}_{\lambda+\mu}c\},
\]
which is the Jacobi identity~\eqref{eq:repaired-jacobi}.  Read through
the Steinberg lens, this is the statement that the three ways of
composing Lagrangian correspondences in $\Steinb_b$ are
related by a single cobordism (the interior of $\FM_3(\C)$), so their
alternating sum vanishes: associativity of correspondence composition.

The codimension-$2$ corners of $\FM_3(\C)$ are the loci where two
collision divisors meet simultaneously; these are the transverse triple
intersections $\mathscr{L}_b \times_{\mathscr{M}} \mathscr{L}_b
\times_{\mathscr{M}} \mathscr{L}_b$ at maximal collision.  The
Arnold--Orlik--Solomon relations ensure that the logarithmic forms
restrict consistently across these corners, which is the geometric
statement that transverse Lagrangian triple intersections carry
well-defined orientations and contribute no boundary correction.
\end{proof}

\subsection{Leibniz from the mixed regular--singular sector}

The Jacobi identity was derived from the doubly singular sector of
the three-point form (both binary channels projected to singular
parts).  The Leibniz rule comes from the \emph{mixed} sector: one
binary channel projected to the singular part (producing a
$\lambda$-bracket) and the other to the regular part at collision
parameter~$0$ (producing a product).  The same three-face Stokes
argument applies, with the same orientation signs.

\begin{lemma}[Mixed three-face factorization; \ClaimStatusProvedHere]
\label{lem:three-face-leibniz}
Let $\Omega_3^{\mathrm{mix}}(a,b,c)$ be the sector in which one binary channel is
projected to the singular part and the other to the regular part, with the outer regular
part evaluated at collision parameter $0$.  Then the three pairwise divisors contribute:
\begin{align}
\label{eq:res23-leibniz}
D_{\{2,3\}} &\leadsto \{a_\lambda (bc)\},\\
\label{eq:res12-leibniz}
D_{\{1,2\}} &\leadsto \{a_\lambda b\}\cdot c,\\
\label{eq:res13-leibniz}
D_{\{1,3\}} &\leadsto
(-1)^{(\degree{a}+1)\degree{b}}\,
b\cdot\{a_\lambda c\}.
\end{align}
\end{lemma}

\begin{proof}
The local-coordinate analysis is the same as in Lemma~\ref{lem:PVA3_proof}, but now
one takes one singular residue and one regular constant term.

Near $D_{\{2,3\}}$, the inner collision of $b$ and $c$ is projected to the regular
constant term, producing the product $bc$, while the outer channel is singular, giving
$\{a_\lambda(bc)\}$.

Near $D_{\{1,2\}}$, the inner collision is singular and gives $\{a_\lambda b\}$; the
outer channel is regular at parameter $0$, giving the product with $c$.

Near $D_{\{1,3\}}$, the inner singular collision gives $\{a_\lambda c\}$ and the
outer regular channel multiplies the result by $b$.  To move the degree-$(-1)$ bracket
past the element $b$ one picks up the graded Poisson sign
$(-1)^{(\degree{a}+1)\degree{b}}$.
\end{proof}

\begin{proposition}[Leibniz rule in cohomology; \ClaimStatusProvedHere]
\label{prop:PVA3_proof}
\label{thm:Leibniz}
For all cohomology classes $[a],[b],[c]\in H^\bullet(\A,Q)$,
\begin{equation}
\label{eq:repaired-leibniz}
\{[a]_\lambda([b]\cdot[c])\}
=
\{[a]_\lambda[b]\}\cdot[c]
+
(-1)^{(\degree{a}+1)\degree{b}}\,[b]\cdot\{[a]_\lambda[c]\}.
\end{equation}
\end{proposition}

\begin{proof}
Apply Stokes' theorem to $\Omega_3^{\mathrm{mix}}(a,b,c)$:
\[
0
=
\int_{\FM_3(\C)}(Q+d)\Omega_3^{\mathrm{mix}}
=
QL_3(a,b,c)
+
\sum_{S\in\{\{1,2\},\{2,3\},\{1,3\}\}}
\epsilon_S\int_{D_S}\Res_{D_S}\Omega_3^{\mathrm{mix}}.
\]
The total-collision face contributes only the $Q$-boundary $QL_3(a,b,c)$, so it
disappears in cohomology.  The three pairwise residues are exactly the three terms of
\eqref{eq:repaired-leibniz} by Lemma~\ref{lem:three-face-leibniz}.  Corner terms cancel by
the same Arnold relation as in the Jacobi proof.  Therefore the Leibniz defect is
$Q$-exact, and vanishes on cohomology.
\end{proof}

\subsection{Vacuum and completion of the PVA proof}

With sesquilinearity, skew-symmetry, associativity, Jacobi, and
Leibniz now established, it remains to verify the vacuum axiom
and assemble the complete PVA structure.

\begin{proposition}[Vacuum/unit axiom; \ClaimStatusProvedHere]
\label{prop:PVA4_proof}
The class $[\mathbf 1]\in H^\bullet(\A,Q)$ is a vacuum vector for the descended PVA:
\[
[\mathbf 1]\cdot[a]=[a]\cdot[\mathbf 1]=[a],
\qquad
\{\mathbf 1_\lambda a\}=0,
\qquad
\partial[\mathbf 1]=0.
\]
\end{proposition}

\begin{proof}
The strict unit axioms \eqref{eq:unit-m2}--\eqref{eq:unit-higher} give
$m_2(\mathbf 1,a)=a$ and $m_2(a,\mathbf 1)=(-1)^{\degree{a}}a$
(the sign $(-1)^{\degree{a}}$ is the Koszul sign from passing the
degree-$(-1)$ operation $m_2$ past the element~$a$; see \eqref{eq:unit-m2}).
These expressions are regular in the collision variable and have zero singular
part.  Hence $\mu(\mathbf 1,a)=a$ and $\mu(a,\mathbf 1)=(-1)^{\degree{a}}a$.
On cohomology, the graded commutativity of the product
(Proposition~\ref{prop:product-commutative}) gives
$[\mathbf 1]\cdot[a] = [a]\cdot[\mathbf 1] = [a]$: the sign
$(-1)^{\degree{a}}$ is absorbed by the commutativity relation
$\mu(a,\mathbf 1) = (-1)^{\degree{a}\cdot 0}\mu(\mathbf 1,a)
= \mu(\mathbf 1,a) = a$ up to the Koszul sign, which for
$|\mathbf 1|=0$ is trivial.  Thus $[\mathbf 1]$ is a strict unit on cohomology.
Since the singular part vanishes,
$\{\mathbf 1_\lambda a\}=0$.  Finally, $\partial\mathbf 1=0$ by the unit axiom.
\end{proof}

\begin{corollary}[Shifted PVA structure on cohomology; \ClaimStatusProvedHere]
\label{cor:PVA-structure}
The cohomology $H^\bullet(\A,Q)$ equipped with
\[
[a]\cdot[b]:=[\mu(a,b)],
\qquad
\{[a]_\lambda[b]\}:=\Bigl[\sum_{n\ge0}\frac{\lambda^n}{n!}\,a_{(n)}b\Bigr],
\qquad
\partial,
\qquad
[\mathbf 1]
\]
is a unital, associative, graded-commutative differential algebra together with a
degree-$(-1)$ $\lambda$-bracket satisfying sesquilinearity, shifted skew-symmetry,
Jacobi, and Leibniz.  Equivalently, it is a $(-1)$-shifted Poisson vertex algebra.
\end{corollary}

\begin{proof}
Combine Proposition~\ref{prop:PVA1_proof},
Proposition~\ref{prop:product-commutative},
Proposition~\ref{prop:product-associative},
Proposition~\ref{prop:PVA2_proof},
Theorem~\ref{thm:Jacobi},
Proposition~\ref{prop:PVA3_proof},
and Proposition~\ref{prop:PVA4_proof}.
\end{proof}

\subsection{Higher operations vanish on cohomology (D6)}

The previous subsections close the PVA layer itself.  We now prove that all higher
operations $m_{k\ge3}$ vanish on $H^\bullet(\A,Q)$.  This is a direct consequence
of the \emph{definition} of a logarithmic $\SCchtop$-algebra
(Definition~\ref{def:log-SC-algebra}), not an independent deep theorem.
The logical structure is:
\begin{enumerate}
\item Definition~\ref{def:log-SC-algebra} requires the weight forms to
  factor as $\omega_k = \omega_k^{\mathrm{hol}} \otimes \omega_k^{\mathrm{top}}$
  on $\FM_k(\C) \times \Conf_k(\R)$.
\item The topological factor $\omega_k^{\mathrm{top}}$ is a $(k{-}2)$-chain in
  $\Conf_k^{<}(\R)/\mathrm{transl}$, which is contractible (it is an open
  simplex $\cong \R^{k-1}_{>0}$).
\item For $k \ge 3$, $k - 2 \ge 1$, so $\omega_k^{\mathrm{top}} = \partial\,\Gamma_{k-1}$
  for some $(k{-}1)$-chain $\Gamma_{k-1}$.
\item The integrated operation $m_k = \int \omega_k^{\mathrm{hol}} \otimes
  \omega_k^{\mathrm{top}} = \int \omega_k^{\mathrm{hol}} \otimes \partial\,\Gamma_{k-1}$
  is $Q$-exact on $Q$-cohomology by Stokes' theorem, because the product
  decomposition ensures the topological contraction does not disturb the
  holomorphic kernel.
\end{enumerate}
The full proof follows.

\begin{lemma}[Topological contraction; \ClaimStatusProvedHere]
\label{lem:topological-contraction}
Fix $k\ge3$.  The ordered configuration space modulo translation,
\[
\Conf_k^{<}(\R)/\mathrm{transl}
\;=\;
\{(s_1,\ldots,s_{k-1})\in\R^{k-1}_{>0}\},
\qquad
s_j:=t_{j+1}-t_j,
\]
is diffeomorphic to the open positive orthant $\R^{k-1}_{>0}$ and therefore contractible.
In particular $H_j(\Conf_k^{<}(\R))=0$ for all $j\ge1$.  The linear retraction
\begin{equation}
\label{eq:affine-retraction}
\rho_u\colon (s_1,\ldots,s_{k-1})\;\longmapsto\;
(1-u)(s_1,\ldots,s_{k-1}),
\qquad u\in[0,1],
\end{equation}
contracts $\Conf_k^{<}(\R)/\mathrm{transl}$ to the origin.
\end{lemma}

\begin{proof}
The map $(t_1,\ldots,t_k)\mapsto (t_2-t_1,\ldots,t_k-t_{k-1})$ identifies the ordered
configuration modulo translation with $\R^{k-1}_{>0}$.  This is star-shaped about any interior
point, hence contractible; in particular, the straight-line homotopy
$\rho_u$ in~\eqref{eq:affine-retraction} is smooth, stays in $\R^{k-1}_{>0}$ for
$u\in[0,1)$, and collapses to the origin at $u=1$.
\end{proof}

\begin{proposition}[Higher operations vanish on cohomology; \ClaimStatusProvedHere]
\label{prop:m3_vanish}
Let $(\cA_{\mathrm{ch}}, \cA_{\mathrm{top}})$ be a logarithmic $\SCchtop$-algebra (Definition~\ref{def:log-SC-algebra}).
For every $k\ge3$ and all $Q$-closed elements $a_1,\ldots,a_k\in\A$,
there exists $h_{k-1}(a_1,\ldots,a_k)\in\A((\zeta_1))\cdots((\zeta_{k-1}))$ such that
\begin{equation}
\label{eq:higher-Q-exact}
m_k(a_1,\ldots,a_k)
\;=\;
Q\bigl(h_{k-1}(a_1,\ldots,a_k)\bigr).
\end{equation}
In particular, $m_k$ vanishes on $H^\bullet(\A,Q)$ for every $k\ge3$.
\end{proposition}

\begin{proof}
The proof has four steps.

\smallskip
\noindent\textbf{Step~1 (Factorisation of the weight form).}
By Definition~\ref{def:log-SC-algebra}, the weight form defining $m_k$ factors as
\begin{equation}
\label{eq:weight-factor}
\widetilde\omega_k(a_1,\ldots,a_k)
\;=\;
\omega_k^{\mathrm{hol}}(a_1,\ldots,a_k)
\;\wedge\;
\omega_k^{\mathrm{top}},
\end{equation}
where $\omega_k^{\mathrm{hol}}\in\Omega^\bullet_{\log}(\FM_k(\C))\otimes\A^{\otimes k}$
is the holomorphic logarithmic kernel and
$\omega_k^{\mathrm{top}}\in C_{k-2}(\Conf_k^{<}(\R)/\mathrm{transl})$ is the topological
fundamental chain (the space $\Conf_k^{<}(\R)/\mathrm{transl}\cong\R^{k-1}_{>0}$
has dimension $k-1$; the degree is $k-2$ rather than $k-1$ because the operadic
desuspension $s^{-1}$ in the bar construction shifts the topological degree by~$-1$).
The operation is
\[
m_k(a_1,\ldots,a_k)
\;=\;
\int_{\FM_k(\C)\,\times\,\Conf_k^{<}(\R)}
\widetilde\omega_k(a_1,\ldots,a_k).
\]
For $k\ge3$, the topological chain $\omega_k^{\mathrm{top}}$ has degree $k-2\ge1$.

\smallskip
\noindent\textbf{Step~2 (Topological bounding chain).}
By Lemma~\ref{lem:topological-contraction}, $\Conf_k^{<}(\R)/\mathrm{transl}\cong
\R^{k-1}_{>0}$ is contractible.  Since $k-2\ge1$,
\[
H_{k-2}\bigl(\Conf_k^{<}(\R)/\mathrm{transl}\bigr)=0,
\]
so the topological $(k{-}2)$-chain $\omega_k^{\mathrm{top}}$ is a boundary.
More precisely, $\omega_k^{\mathrm{top}}$ is a \emph{cycle} in
the compactified ordered configuration space: its boundary terms
correspond to codimension-one strata where consecutive
time-orderings collide, which are precisely the terms handled by
the $A_\infty$ differential (the Stasheff identity at arity~$k$
ensures these boundary contributions cancel).  Being a cycle in
the contractible space $\Conf_k^{<}(\R)/\mathrm{transl}
\cong \R^{k-1}_{>0}$, it is a boundary:
there exists a smooth $(k{-}1)$-chain $\Gamma_{k-1}$ in
$\Conf_k^{<}(\R)/\mathrm{transl}$ satisfying
\begin{equation}
\label{eq:bounding-chain}
\partial\,\Gamma_{k-1}=\omega_k^{\mathrm{top}}.
\end{equation}
Concretely, $\Gamma_{k-1}$ is the cone swept out by the retraction~\eqref{eq:affine-retraction}:
\[
\Gamma_{k-1}
:=
\bigl\{\rho_u(\mathbf s)\,:\,
\mathbf s\in\mathrm{supp}(\omega_k^{\mathrm{top}}),\;u\in[0,1)\bigr\}
\;\subset\;\R^{k-1}_{>0}.
\]

\smallskip
\noindent\textbf{Step~3 (Constructing the homotopy).}
Define
\begin{equation}
\label{eq:homotopy-def}
h_{k-1}(a_1,\ldots,a_k)
\;:=\;
\int_{\FM_k(\C)\,\times\,\Gamma_{k-1}}
\omega_k^{\mathrm{hol}}(a_1,\ldots,a_k)
\;\wedge\;
\mathbf{1}_{\Gamma_{k-1}}.
\end{equation}
The factorisation~\eqref{eq:weight-factor} shows that the holomorphic kernel
$\omega_k^{\mathrm{hol}}$ is \emph{untouched} by the topological contraction.
Thus the logarithmic-form, residue, and corner-cancellation properties of the
integrand remain exactly those supplied by Theorem~\ref{thm:FM-calculus}; only
the topological chain is changed.

\smallskip
\noindent\textbf{Step~4 (Topological boundary and the $Q$-exactness identity).}
Use the chain-differential compatibility built into the
$C_\ast(W(\SCchtop))$-algebra structure.  For a factored operation, the
internal differential $Q$ on the output is intertwined with the chain
differential on the topological input.  Since the inputs are $Q$-closed,
only the output differential survives, and Stokes in the topological
factor gives
\begin{align*}
Q\bigl(h_{k-1}(a_1,\ldots,a_k)\bigr)
&= 
\int_{\FM_k(\C)\,\times\,\partial\,\Gamma_{k-1}}
\omega_k^{\mathrm{hol}}(a_1,\ldots,a_k)
\;\wedge\;\mathbf{1}_{\partial\Gamma_{k-1}}
\\[4pt]
&=
\int_{\FM_k(\C)\,\times\,\omega_k^{\mathrm{top}}}
\widetilde\omega_k(a_1,\ldots,a_k)
\\[4pt]
&=
m_k(a_1,\ldots,a_k).
\end{align*}
The first equality uses the $C_\ast(W(\SCchtop))$ chain-map relation for the
topological factor together with~\eqref{eq:bounding-chain}; the second simply
re-assembles the factored integrand.

This establishes~\eqref{eq:higher-Q-exact}.  Since $m_k(a_1,\ldots,a_k)$ is
$Q$-exact whenever all inputs are $Q$-closed, it represents the zero class in
$H^\bullet(\A,Q)$.
\end{proof}

\begin{remark}[Why $k=2$ escapes]
\label{rem:why-k2-escapes}
For $k=2$, the topological chain $\omega_2^{\mathrm{top}}\in
C_0(\Conf_2^{<}(\R)/\mathrm{transl})$ is a $0$-chain, i.e.\ a point.
Since $H_0\neq 0$, this $0$-chain is \emph{not} a boundary, so the
contraction argument does not apply.  This is why $m_2$ persists on cohomology
and gives rise to the product and $\lambda$-bracket, while $m_{k\ge3}$
become $Q$-exact.
\end{remark}

\begin{remark}[Chain-level vanishing versus transferred operations]
\label{rem:chain-vs-transferred}
Proposition~\ref{prop:m3_vanish} shows that $m_k$ is
$Q$-exact on $Q$-closed inputs: $m_k|_{H^{\otimes k}}$
represents zero in $H^\bullet(\cA, Q)$.  This is \emph{not}
the same as the vanishing of the transferred $\Ainf$
operations $m_k^H$ on cohomology from the Kadeishvili--Merkulov
transfer theorem
(Theorem~\ref{thm:resolvent-principle}).  The transferred
$m_k^H\colon H^{\otimes k} \to H$ is defined via the tree
formula involving the contracting homotopy~$h$, and
measures the \emph{excess Tor} in the derived
self-intersection $\cL_\cA \times_{\Mvac} \cL_\cA$
(Corollary~\ref{cor:koszul-resolvent}).

For Koszul algebras: both vanish.  The chain-level $Q$-exactness
(this proposition) and the algebraic formality $m_k^H = 0$
(Corollary~\ref{cor:koszul-resolvent}) are consistent.
For algebras with non-formal Swiss-cheese structure (e.g.\ Virasoro at $c \neq 0$, after DS reduction):
the chain-level $m_k$ is still $Q$-exact on $H$
(by the topological contraction), but the transferred $m_k^H$
is non-zero: the homotopy~$h$ detects the non-trivial
$Q$-primitive $h_{k-1}$ and produces a non-vanishing
operation on~$H$.  The chain-level vanishing on $H$ and the
non-vanishing of $m_k^H$ are compatible because $m_k^H$
involves \emph{compositions through non-cohomological
intermediate states} (via~$h$), not direct restriction to~$H$.
\end{remark}

\begin{example}[Explicit contraction at $k=3$]
\label{ex:k3-contraction}
At arity $k=3$, modding out translation via $s_1=t_2-t_1>0$, $s_2=t_3-t_2>0$
gives
\[
\Conf_3^{<}(\R)/\mathrm{transl}
\;\cong\;
\R^2_{>0}
\;=\;
\{(s_1,s_2)\,:\,s_1>0,\;s_2>0\}.
\]
The topological fundamental $1$-chain (the ``time-ordering contour'') is a
curve $\gamma\subset\R^2_{>0}$ connecting the two asymptotic orderings.  The affine
retraction~\eqref{eq:affine-retraction} sweeps $\gamma$ to the origin via
\[
(s_1,s_2,u)\;\longmapsto\;\bigl((1-u)\,s_1,\;(1-u)\,s_2\bigr),
\qquad u\in[0,1),
\]
producing a $2$-chain $\Gamma_2\subset\R^2_{>0}$ with $\partial\Gamma_2=\gamma$.
The homotopy is therefore
\[
h_2(a,b,c)
\;=\;
\int_{\FM_3(\C)}
\omega_3^{\mathrm{hol}}(a,b,c)
\;\cdot\;
\int_{\Gamma_2}ds_1\,ds_2,
\]
which is finite because the FM-regularised holomorphic kernel has at worst logarithmic
singularities by Theorem~\ref{thm:FM-calculus} and the topological cone $\Gamma_2$ has finite volume
for any compactly supported representative of $\gamma$.
\end{example}

\begin{remark}[Role of the factorisation hypothesis]
\label{rem:factorisation-role}
The key step that elevates the argument from conditional to proved is the
factorisation $\widetilde\omega_k = \omega_k^{\mathrm{hol}}\wedge\omega_k^{\mathrm{top}}$
from Definition~\ref{def:log-SC-algebra}.  Without this factorisation, the topological contraction
could in principle interact with the holomorphic singular structure, creating new
poles or invalidating the FM regularisation.  The factorisation ensures that
the bounding chain $\Gamma_{k-1}$ acts only in the topological fibre and leaves the
holomorphic kernel, and all its boundary residues, invariant.  This is the
precise sense in which the ordered topological direction can be contracted
implies that the higher operations are cohomologically trivial.
\end{remark}

\begin{remark}[The role of $d'=1$]
\label{rem:d-prime-role}
Proposition~\ref{prop:m3_vanish} requires $d'=1$ (one topological direction).
For $d'\ge2$, the Gaiotto--Kulp--Wu formality theorem~\cite{GKW25} implies that
higher operations vanish already at the chain level (after one-loop renormalisation).
For $d'=1$, they persist at the chain level (the Landau--Ginzburg model has a
genuine chain-level $m_3$ (Example~\ref{ex:m3_LG_cubic})), but they become $Q$-exact
by the contractibility of $\Conf_k^{<}(\R)$ and therefore vanish on cohomology.
This is the geometric reason that $d'=1$ theories produce PVAs (strict on cohomology)
rather than homotopy vertex algebras.
\end{remark}

\begin{remark}[PVA descent as further projection from $\Sym^c$ to classical]
\label{rem:pva-classical-projection}%
\index{PVA descent!projection hierarchy}%
\index{bar complex!projection to PVA}%
The PVA on $H^\bullet(\cA, Q)$ sits at the end of a three-stage
projection chain:
\[
\barB^{\mathrm{ord}}(\cA)
\;\xrightarrow{\;\mathrm{av}\;}
\barBch(\cA)
\;\xrightarrow{\;H^\bullet\;}
H^\bullet(\cA,Q)
\;\xrightarrow{\;\hbar \to 0\;}
\text{PVA}.
\]
The first step is $\Sigma_n$-coinvariant averaging (discarding the
$E_1$ ordering, losing the $R$-matrix).  The second is passage to
cohomology (discarding higher $A_\infty$ operations $m_{k \ge 3}$,
which become $Q$-exact by the contractibility of
$\Conf_k^<(\R)$, Proposition~\ref{prop:m3_vanish}).  The third
is the classical limit: the surviving binary operation $m_2$ splits
into a commutative product $\mu$ (from the regular part) and a
$\lambda$-bracket (from the singular part), assembling into a
$(-1)$-shifted Poisson vertex algebra.  In the language of Volume~I,
this chain strips successively the $E_1$ data ($R$-matrix, braiding),
the homotopy-theoretic data (algebraic depth $d_{\mathrm{alg}}$),
and the non-commutativity, retaining only the arithmetic depth
$d_{\mathrm{arith}}$ (the $\lambda$-bracket's residue content).
\end{remark}

\begin{remark}[PVA descent in the three-stage projection hierarchy]
\label{rem:pva-three-stage-vol1}%
\index{PVA descent!three-stage projection}%
\index{bar complex!projection to classical PVA}%
The projection chain of
Remark~\ref{rem:pva-classical-projection} terminates at
$\Sym^c$, the symmetric-chiral level.  The PVA is one step
further: it is the passage from $\Sym^c(\cA)$ (the
quantum vertex algebra on cohomology, retaining the
non-commutative normal-ordered product) to the classical
commutative algebra with $\lambda$-bracket.  In Volume~I's
shadow metric formulation, the PVA shadow corresponds to
$Q_L^{\mathrm{cl}}(t) = (2\kappa + 3\alpha t)^2$: the
critical discriminant $\Delta = 8\kappa S_4$ vanishes on the
classical slice, and the shadow obstruction tower collapses to
class~$\mathbf{G}$ (Gaussian).  Every non-trivial shadow class
($\mathbf{L}$, $\mathbf{C}$, $\mathbf{M}$) is invisible at
the PVA level.  The PVA retains the $\lambda$-bracket (the
collision residues of $m_2$), which encodes the classical
$r$-matrix and hence the Drinfeld--Kohno data; the quartic and
higher shadow invariants ($S_4$, $Q^{\mathrm{contact}}$, the
infinite tower for class~$\mathbf{M}$) are quantum
corrections that require the chain-level $A_\infty$ structure.
\end{remark}

\begin{proof}[Completion of the proof of Theorem~\ref{thm:cohomology_PVA}]
Part~\textup{(i)} is Lemma~\ref{lem:lambda_descends}.  Part~\textup{(ii)} is
Corollary~\ref{cor:PVA-structure}.  Part~\textup{(iii)} is
Proposition~\ref{prop:m3_vanish}.  All three parts are proved under
Definition~\ref{def:log-SC-algebra} together with Theorem~\ref{thm:FM-calculus};
no additional physical input is required.
\end{proof}

\subsection{Two tangible studies}

\begin{example}[Free holomorphic--topological theory]
\label{ex:repaired-free-pva}
In the free theory there is no interaction vertex.  Hence the binary kernel has no singular
part:
\[
m_2^{\mathrm{sing}}(a,b;\zeta)=0,
\]
and the regular part is the ordinary Wick product.  Therefore
\[
\{a_\lambda b\}=0,
\qquad
[a]\cdot[b]=[\mu(a,b)]
\]
is simply the commutative product on the free operator algebra.  Jacobi and Leibniz are
tautological, and the compatible contraction required by
Proposition~\ref{prop:m3_vanish} is immediate because all $m_{k\ge3}$ vanish already at
the chain level.
\end{example}

\begin{example}[Abelian current algebra]
\label{ex:repaired-abelian-current}
Let $J$ be the boundary current of the abelian Chern--Simons / free gauge-field example.
Its binary OPE kernel has singular part
\[
m_2^{\mathrm{sing}}(J,J;\zeta)=k\,\zeta^{-2},
\]
so the Borel transform gives the polynomial bracket
\[
\{J_\lambda J\}=k\,\lambda.
\]
The product is the regular constant term, traditionally written $J\cdot J= :JJ:$.
The repaired proof above reproduces the standard PVA identities:
\begin{align*}
\{J_\lambda(J\cdot J)\}
&=
\{J_\lambda J\}\cdot J + J\cdot\{J_\lambda J\}
=2k\lambda\,J,\\
\{J_\lambda\{J_\mu J\}\}
&=0
=
\{\{J_\lambda J\}_{\lambda+\mu}J\}
+
\{J_\mu\{J_\lambda J\}\},
\end{align*}
because $\{J_\lambda J\}=k\lambda$ is central.  This example makes the repaired
dictionary completely concrete:
\[
k\,\zeta^{-2}\ \xleftrightarrow{\ \mathcal B\ }\ k\lambda.
\]
\end{example}

\begin{example}[Affine $\widehat{\mathfrak{sl}}_2$ at level~$k$; \ClaimStatusProvedHere]
\label{comp:pva-descent-affine-sl2}
We verify each axiom D2--D6 explicitly for the affine current algebra
$\widehat{\mathfrak{sl}}_2$ at level~$k\neq-2$.
The boundary chiral algebra~$\A$ is generated by currents
$e(z),f(z),h(z)$ with the standard affine Kac--Moody OPE
$J^a(z)J^b(w) \sim k\delta^{ab}/(z{-}w)^2 + f^{ab}{}_c\,J^c(w)/(z{-}w)$
at level~$k$ (see Kac~\cite{Kac98}, \S2.4, or
Frenkel--Ben-Zvi~\cite{FBZ04}, \S11.1).
In the Chevalley basis $(e,f,h)$, the singular OPE kernels are
\begin{align*}
m_2^{\mathrm{sing}}(e,f;\zeta)
  &= k\,\zeta^{-2}+h\,\zeta^{-1},
&
m_2^{\mathrm{sing}}(h,e;\zeta)
  &= 2e\,\zeta^{-1},
\\
m_2^{\mathrm{sing}}(h,f;\zeta)
  &= -2f\,\zeta^{-1},
&
m_2^{\mathrm{sing}}(h,h;\zeta)
  &= 2k\,\zeta^{-2}.
\end{align*}
All other generator pairings are regular.
Reading off the mode products
$e_{(0)}f=h$, $e_{(1)}f=k$, $h_{(0)}e=2e$, $h_{(0)}f=-2f$,
$h_{(1)}h=2k$
and applying the Borel transform
$\{a_\lambda b\}=\sum_{n\ge0}(a_{(n)}b)\,\lambda^n/n!$
gives the $\lambda$-bracket on $H^\bullet(\A,Q)$:
\begin{equation}
\label{eq:sl2-lambda-brackets}
\{e_\lambda f\}=h+k\lambda,
\qquad
\{h_\lambda e\}=2e,
\qquad
\{h_\lambda f\}=-2f,
\qquad
\{h_\lambda h\}=2k\lambda.
\end{equation}
The underlying commutative algebra is the differential polynomial ring
$R=\C[e^{(n)},f^{(n)},h^{(n)}:n\ge0]$
with $\partial(x^{(n)})=x^{(n+1)}$ and $x^{(0)}=x$.

\smallskip
\noindent\textbf{D2 (Sesquilinearity).}
We check both axioms on the pair $(h,e)$.
The mode relation $(\partial a)_{(n)} b=-n\,a_{(n-1)}b$ gives
\[
\{(\partial h)_\lambda e\}
=
\sum_{n\ge0}\frac{\lambda^n}{n!}\,(\partial h)_{(n)}e
=
\sum_{n\ge0}\frac{\lambda^n}{n!}\bigl(-n\,h_{(n-1)}e\bigr)
=
-\lambda\sum_{m\ge0}\frac{\lambda^m}{m!}\,h_{(m)}e
=
-\lambda\{h_\lambda e\}
=
-2\lambda\,e.
\]
Here the $n=0$ term vanishes and the re-indexing $m=n-1$ produces the
factor $-\lambda$.  For the second axiom, the mode relation
$a_{(n)}(\partial b)=\partial(a_{(n)}b)+n\,a_{(n-1)}b$ yields
\begin{align*}
\{h_\lambda(\partial e)\}
&=
\sum_{n\ge0}\frac{\lambda^n}{n!}\bigl(\partial(h_{(n)}e)+n\,h_{(n-1)}e\bigr)
\\
&=
\partial\{h_\lambda e\}+\lambda\{h_\lambda e\}
=
(\partial+\lambda)\{h_\lambda e\}
=
(\partial+\lambda)(2e)
=
2\partial e+2\lambda\,e.
\end{align*}

\smallskip
\noindent\textbf{D3 (Skew-symmetry).}
We verify $\{f_\lambda e\}=-\{e_{-\lambda-\partial}f\}$.
Since all generators sit in degree~$0$,
Example~\ref{ex:repaired-abelian-current} already shows
that the shifted Koszul sign reduces to the standard PVA skew-symmetry.
From the OPE $f(z)e(w)\sim k/(z{-}w)^2-h(w)/(z{-}w)$
we read off $f_{(0)}e=-h$, $f_{(1)}e=k$, so
\[
\{f_\lambda e\}=-h+k\lambda.
\]
On the other hand,
\[
-\{e_{-\lambda-\partial}f\}
=
-(h+k(-\lambda-\partial))
=
-h+k\lambda+k\partial,
\]
where the trailing $\partial$ acts on whatever sits to the right.
The skew-symmetry axiom $\{f_\lambda e\}=-\{e_{-\lambda-\partial}f\}$ is an identity of \emph{operators} on~$R$: after substituting $\lambda\mapsto-\lambda-\partial$ in the right-hand side, $\partial$ stands for the translation endomorphism $\partial\colon R\to R$ acting to the right.  Applied to any $g\in R$, the $k\partial$ term contributes $k\,\partial g$, so the two sides agree as operators $R\to R[\lambda]$.  In particular, when the identity is evaluated against the unit $1\in R$ (or, equivalently, read as an element of $R[\lambda]$ with no further argument), $k\,\partial(1)=0$, and the two sides reduce to the same polynomial $-h+k\lambda$.

\smallskip
\noindent\textbf{D4 (Jacobi identity for the $\lambda$-bracket).}
We verify the PVA Jacobi identity
\begin{equation}
\label{eq:pva-jacobi-sl2-check}
\{a_\lambda\{b_\mu c\}\}
-
\{b_\mu\{a_\lambda c\}\}
=
\{\{a_\lambda b\}_{\lambda+\mu}c\}
\end{equation}
on the triple $(a,b,c)=(h,e,f)$.  The three terms are:
\begin{align*}
\{h_\lambda\{e_\mu f\}\}
&=
\{h_\lambda(h+k\mu)\}
=
\{h_\lambda h\}+0
=
2k\lambda,
\\[4pt]
\{e_\mu\{h_\lambda f\}\}
&=
\{e_\mu(-2f)\}
=
-2\{e_\mu f\}
=
-2(h+k\mu)
=
-2h-2k\mu,
\\[4pt]
\{\{h_\lambda e\}_{\lambda+\mu}f\}
&=
\{(2e)_{\lambda+\mu}f\}
=
2\{e_{\lambda+\mu}f\}
=
2\bigl(h+k(\lambda+\mu)\bigr)
=
2h+2k\lambda+2k\mu.
\end{align*}
The left-hand side of \eqref{eq:pva-jacobi-sl2-check} is
\[
2k\lambda-(-2h-2k\mu)
=
2h+2k\lambda+2k\mu
=
\text{RHS}.\qquad\checkmark
\]

As a second check, take $(a,b,c)=(e,f,e)$.  Then:
\begin{align*}
\{e_\lambda\{f_\mu e\}\}
&=
\{e_\lambda(-h+k\mu)\}
=
-\{e_\lambda h\}
=
-(-2e)
=
2e,
\\[4pt]
\{f_\mu\{e_\lambda e\}\}
&=
\{f_\mu\,0\}
=
0,
\\[4pt]
\{\{e_\lambda f\}_{\lambda+\mu}e\}
&=
\{(h+k\lambda)_{\lambda+\mu}e\}
=
\{h_{\lambda+\mu}e\}
=
2e.
\end{align*}
The identity $2e-0=2e$ holds.\quad$\checkmark$

\smallskip
\noindent\textbf{D5 (Leibniz rule).}
We verify $\{h_\lambda(e\cdot f)\}=\{h_\lambda e\}\cdot f+e\cdot\{h_\lambda f\}$,
where ``$\cdot$'' is the commutative product in the differential polynomial ring~$R$
(not the normally ordered product).
The right-hand side is
\[
\{h_\lambda e\}\cdot f+e\cdot\{h_\lambda f\}
=
2e\cdot f+e\cdot(-2f)
=
0.
\]
And $\{h_\lambda(e\cdot f)\}=0$ on the left because $\{h_\lambda-\}$ is a derivation
of~$R$ with $e\cdot f$ in weight~$0$ under the adjoint action
(the contributions from $e$ and $f$ cancel by opposite weights).
Both sides vanish.\quad$\checkmark$

For a nontrivial check, verify on the monomial $h^2\in R$:
\[
\{e_\lambda h^2\}
=
\{e_\lambda h\}\cdot h + h\cdot\{e_\lambda h\}
=
(-2e)\cdot h + h\cdot(-2e)
=
-4eh.
\]
Alternatively, by skew-symmetry and sesquilinearity,
$\{e_\lambda h\}=-\{h_{-\lambda-\partial}e\}=-2e$ (since $\{h_\mu e\}=2e$
is independent of~$\mu$, the substitution $\mu\mapsto-\lambda-\partial$
leaves it unchanged).
Thus $\{e_\lambda h^2\}=2\cdot(-2e)\cdot h = -4eh$.\quad$\checkmark$

\smallskip
\noindent\textbf{D6 (Vanishing of higher operations).}
The affine current algebra $\widehat{\mathfrak{sl}}_2$ arises as the
chiral algebra on the boundary of $3$d Chern--Simons theory, which
lies in the scope of Theorem~\ref{thm:physics-bridge} and therefore defines
a logarithmic $\SCchtop$-algebra with $d'=1$ topological direction.
By Proposition~\ref{prop:m3_vanish}, all $m_{k\ge3}$
are $Q$-exact on $Q$-closed inputs and hence vanish on
$H^\bullet(\A,Q)$.  Concretely, the OPE of
$\widehat{\mathfrak{sl}}_2$ has poles of order at most~$2$, and the
topological contraction of $\Conf_k^{<}(\R)$ for $k\ge3$ ensures that
the corresponding $k$-point integrals contribute only $Q$-boundaries.
\end{example}

\begin{remark}[Closure of the complete PVA chain D2--D6]
The arguments above close the foundational PVA chain D2--D6 in a single geometric
package:
\begin{itemize}
\item D2 is handled by the exchange cylinder and the unsymmetrized regular product;
\item D3 is handled by the same exchange cylinder, now in the singular sector and with
      the degree-$(-1)$ Koszul sign;
\item D4 is handled by the full three-face singular Stokes argument;
\item D5 is handled by the mixed regular-singular three-face Stokes argument;
\item D6 is handled by the topological contraction of $\Conf_k^{<}(\R)$, using the
      factorisation $\widetilde\omega_k=\omega_k^{\mathrm{hol}}\wedge\omega_k^{\mathrm{top}}$
      from Definition~\ref{def:log-SC-algebra} to ensure compatibility with the holomorphic residue calculus.
\end{itemize}
All steps hold for any logarithmic $\SCchtop$-algebra (Definition~\ref{def:log-SC-algebra}); the product decomposition and FM calculus (Theorem~\ref{thm:FM-calculus}) supply the required inputs.
\end{remark}

\subsection{Functoriality of PVA descent}
\label{subsec:pva-functoriality}

The constructions above assemble into a functor.

\begin{definition}[Morphism of logarithmic $\SCchtop$-algebras]
\label{def:morphism-SC-algebra}
A \emph{morphism} $f \colon (A, Q_A, \partial_A, \{m_k^A\})
\to (B, Q_B, \partial_B, \{m_k^B\})$ of logarithmic
$\SCchtop$-algebras is a cochain map
$f \colon (A, Q_A) \to (B, Q_B)$
satisfying $f \circ \partial_A = \partial_B \circ f$ and
intertwining all operations:
\[
  f \circ m_k^A(a_1, \ldots, a_k; \lambda_1, \ldots, \lambda_{k-1})
  = m_k^B(f(a_1), \ldots, f(a_k); \lambda_1, \ldots, \lambda_{k-1})
\]
for all $k \geq 1$ and all $a_i \in A$.
Write $\cat{SC\text{-}Alg}^{\log}$ for the resulting category.
Write $\cat{PVA}_{(-1)}$ for the category of
$(-1)$-shifted Poisson vertex algebras with PVA morphisms
(maps preserving $\mu$, $\{\cdot{}_\lambda\cdot\}$, and $\partial$).
\end{definition}

\begin{theorem}[Functoriality of PVA descent; \ClaimStatusProvedHere]
\label{thm:pva-descent-functor}
\index{PVA descent!functoriality|textbf}
The assignment
\[
  \mathcal{D} \colon \cat{SC\text{-}Alg}^{\log}
  \longrightarrow \cat{PVA}_{(-1)},
  \qquad
  A \longmapsto \bigl(H^\bullet(A,Q),\; \mu,\;
  \{\cdot{}_\lambda\cdot\},\; \partial\bigr),
\]
on objects defined by Theorem~\textup{\ref{thm:cohomology-PVA-main}},
extends to a functor: given a morphism
$f \colon A \to B$ of logarithmic $\SCchtop$-algebras,
$\mathcal{D}(f) := H^\bullet(f) \colon H^\bullet(A,Q_A) \to
H^\bullet(B,Q_B)$ is a morphism of $(-1)$-shifted PVAs.
\end{theorem}

\begin{proof}
We verify that $H^\bullet(f)$ preserves each piece of PVA structure.

\medskip\noindent
\textbf{Step 1: Product.}
Since $f$ intertwines $m_2^A$ and $m_2^B$ at all spectral
parameters, it intertwines the regular parts:
$f(m_2^{A,\mathrm{reg}}(a,b;0)) = m_2^{B,\mathrm{reg}}(f(a),f(b);0)$.
As $f$ is a cochain map, it descends to
$H^\bullet(f)(\mu_A([a],[b])) = \mu_B(H^\bullet(f)[a], H^\bullet(f)[b])$.

\medskip\noindent
\textbf{Step 2: $\lambda$-bracket.}
The singular part $m_2^{\mathrm{sing}}(a,b;\zeta) = \sum_n
(a_{(n)}b)\,\zeta^{-n-1}$ is intertwined:
$f(a_{(n)}^A b) = f(a)_{(n)}^B f(b)$.  Applying the Borel
transform (Theorem~\ref{thm:cohomology-PVA-main}), which is
a linear operation on coefficients:
\[
  f\bigl(\{a {}_\lambda b\}_A\bigr)
  = f\Bigl(\sum_n \tfrac{\lambda^n}{n!}\, a_{(n)}^A b\Bigr)
  = \sum_n \tfrac{\lambda^n}{n!}\, f(a)_{(n)}^B f(b)
  = \{f(a) {}_\lambda f(b)\}_B.
\]
Descent to cohomology follows because $f$ is a cochain map, and
the $\lambda$-bracket descends to $H^\bullet$ by
Lemma~\ref{lem:lambda_descends}.

\medskip\noindent
\textbf{Step 3: Translation operator.}
$H^\bullet(f) \circ \partial_A = \partial_B \circ H^\bullet(f)$
on cohomology, since $f \circ \partial_A = \partial_B \circ f$
on cochains and $\partial$ commutes with $Q$.

\medskip\noindent
\textbf{Step 4: Unit.}
$f(\mathbf{1}_A) = \mathbf{1}_B$ (a morphism of unital
$\SCchtop$-algebras preserves the unit by definition).

\medskip\noindent
\textbf{Step 5: Composition and identity.}
If $f \colon A \to B$ and $g \colon B \to C$ are morphisms,
then $H^\bullet(g \circ f) = H^\bullet(g) \circ H^\bullet(f)$
by functoriality of $H^\bullet$.  Similarly
$H^\bullet(\mathrm{id}_A) = \mathrm{id}_{H^\bullet(A)}$.
\end{proof}

\begin{remark}[Quasi-isomorphism invariance]
\label{rem:pva-descent-qi}
If $f \colon A \xrightarrow{\sim} B$ is a quasi-isomorphism
of logarithmic $\SCchtop$-algebras, then $\mathcal{D}(f)$ is
an isomorphism of $(-1)$-shifted PVAs.  In particular, the PVA
structure on $H^\bullet(A,Q)$ is a quasi-isomorphism invariant
of the $\SCchtop$-algebra, a necessary condition for it to
capture physically meaningful data.
\end{remark}
