\section{Relation to raviolo vertex algebras}
\label{sec:raviolo}

Garner--Williams and subsequent work introduced raviolo vertex
algebras to model the boundary of a 3d HT theory at a fixed time
slice, gluing an incoming holomorphic disc to an outgoing one
along a punctured disc. The construction is geometric but
detached from the Swiss-cheese operad; it is not immediately
clear which $\SCchtop$-algebras produce raviolo vertex algebras,
or what information is lost in the passage. Does the raviolo
capture the full open/closed datum of~$\Theta^{\mathrm{oc}}$, or
only a shadow, and if a shadow then which one?

The answer is a clean restriction functor. Fixing a time
$t_0 \in \R$ and collapsing the topological direction through
$E_1$-contractibility identifies the $\SCchtop$-algebra on
rectangles $D \times I$ with a \v{C}ech/Thom--Sullivan descent
object on the raviolo $D_+ \cup_{D^\times} D_-$. The chiral
product and its higher coherences transfer; the ordered
associative structure on~$\R$ collapses to the identification
between the two sheets. The raviolo is precisely the
vertex-algebraic shadow of~$\Theta^{\mathrm{oc}}$: the open
colour is forgotten, the closed colour is retained.

\begin{remark}[Raviolo as quasi-classical chain-level avatar of the bar
complex; cross-reference to wave-14 anchors]
\label{rem:raviolo-bar-quasi-classical-bridge}
The raviolo restriction $\mathsf V_{\mathrm{rav}}$ is the geometric
companion of the PVA descent of \S\ref{sec:Ainfty-to-PVA}: both retain
the closed (chiral / holomorphic) colour and forget the open
(topological / $E_1$) colour, the former at the level of vertex algebras
on $\C$, the latter at the level of $(-1)$-shifted Poisson vertex algebras
on $H^\bullet(\cA, Q)$. The bridge is the universal-holography master
theorem (Theorem~\ref{thm:universal-holography-master}, Volume~II
climax): the $\SCchtop$-algebra on the slab $\R \times \C$ is the bulk;
the raviolo restriction at fixed $t_0$ exhibits the boundary chiral
algebra; the PVA descent extracts the classical $\hbar \to 0$ limit.
The Koszul conductor $K = -c_{\mathrm{ghost}}(\mathrm{BRST})$ (Volume~I
universal-conductor theorem) controls the level shift between the
chiral and PVA descriptions: at the self-dual point $K = 0$, the
raviolo and PVA encode the same data; off the self-dual point, the
level shift is the Sugawara correction $\dim(\mathfrak g)/2$ for
affine Kac--Moody. The raviolo is the chain-level avatar; the PVA is
its classical projection; both are shadows of the universal bulk
$\SCchtop$-algebra.
\end{remark}

\begin{remark}[Recognition scope for raviolo restriction]
\label{rem:raviolo-recognition-bridge}
The local-shadow theorem (Theorem~\ref{thm:recognition-SC}) applies to
product-formal logarithmic $\SCchtop$ data. For physical realizations,
this means the bridge hypotheses (a)--(d) of
Theorem~\ref{thm:physics-bridge}: BV data, a factorized HT
parametrix, one-loop finiteness, and product-polynomial
interactions. The raviolo restriction
$\mathsf V_{\mathrm{rav}}$ of Definition~\ref{def:raviolo-restriction}
is a vertex-algebraic shadow of that local datum after the $E_1$
direction is collapsed. It is not a complete invariant of arbitrary
global HT factorization algebras; the PVA descent of
Theorem~\ref{thm:raviolo-PVA} is a further forgetful step that
retains only the classical $\lambda$-bracket and commutative product.
\end{remark}

\subsection{Restriction to time–slices}
Let $A=(A_{\mathsf{ch}},A_{\mathsf{top}})$ be an algebra over $C_\ast\!\bigl(W(\mathsf{SC}^{\mathrm{ch,top}})\bigr)$.
We define its restriction to a fixed time $t_0\in\mathbb R$ by evaluating on rectangles
$D\times I$ with $I$ a small interval centered at~$t_0$, and we identify objects along
the topological direction via the (contractible) $E_1$–homotopy.

\begin{definition}[Raviolo restriction]
\label{def:raviolo-restriction}
Fix $t_0\in\mathbb R$. The \emph{raviolo factorization algebra} associated to~$A$ is the assignment
\[
 \mathsf V_{\mathrm{rav}}(D)
 \,:=\,
 \bigl( A_{\mathsf{ch}}(D\times I)\bigr)\big/\!\!\sim
 \qquad
 \text{for small disks $D\subset\mathbb C$ and intervals $I$ about $t_0$,}
\]
where $\sim$ identifies the two choices of approaching $t_0$ ("from above" and "from below")
using the $E_1$–coherence data.
\end{definition}

\begin{proposition}[Swiss–cheese $\Rightarrow$ raviolo; \ClaimStatusProvedHere]
\label{prop:SC-raviolo}
Restriction of a $C_\ast\!\bigl(W(\mathsf{SC}^{\mathrm{ch,top}})\bigr)$–algebra to a time–slice yields
a (dg) raviolo factorization algebra on~$\mathbb C$. Its product and OPE maps are
induced by those of $A$ via the canonical $E_1$–homotopies.
\end{proposition}

\begin{proof}
We construct the raviolo two-sheet structure via a derived pushout.

\medskip\noindent\textbf{Step 1: The raviolo as a homotopy colimit.}
Consider the diagram of topological spaces
\[
 \mathrm{pt} \xleftarrow{\;\mathrm{ev}_0\;} [0,1] \xrightarrow{\;\mathrm{ev}_1\;} \mathrm{pt},
\]
where $\mathrm{ev}_0$ and $\mathrm{ev}_1$ are evaluation at the endpoints. The raviolo is the derived pushout (homotopy colimit) of this diagram:
\[
 \mathrm{Rav} \;:=\; \mathrm{pt} \coprod^h_{[0,1]} \mathrm{pt}
 \;=\; \operatorname{hocolim}\bigl(\mathrm{pt} \leftarrow [0,1] \rightarrow \mathrm{pt}\bigr).
\]
Since $[0,1]$ is contractible, the derived pushout is homotopy equivalent to $S^0 = \{+,-\}$ (a discrete two-point space): the contractibility of $[0,1]$ means that the homotopy fibre of each evaluation map is trivial, so each point in the pushout retains the identity of its target endpoint, producing two sheets $D_+$ and $D_-$.

\medskip\noindent\textbf{Step 2: Vertex algebra structure on each sheet.}
The $E_1$-algebra structure on $A_{\mathsf{top}}(I)$ restricts to each endpoint via the inclusions $\iota_\pm\colon \mathrm{pt} \hookrightarrow [0,1]$ ($\iota_- = \mathrm{ev}_0$, $\iota_+ = \mathrm{ev}_1$). By local constancy in the topological direction, the restriction $\iota_\pm^* A_{\mathsf{top}}(I)$ is quasi-isomorphic to $A_{\mathsf{top}}(\mathrm{pt})$. The vertex algebra structure on each sheet $D_\pm$ is then obtained by restricting the $\OHT$-algebra operations: the closed-colour (holomorphic) $A_\infty$ operations $\{m_k\}$ restrict along $\iota_\pm$ to give the chiral algebra structure on $A_{\mathsf{ch}}(D \times \{\pm\})$, while the open-colour (topological) data collapses to the coherent gluing $D_+ \cup_{D^\times} D_-$ via the contractible interval. The punctured disk $D^\times$ parametrises the interior of the interval away from the two endpoints.

\medskip\noindent\textbf{Step 3: Compatibility.}
Compatibility with disjoint unions follows from the swiss--cheese composition rules on rectangles: the factorisation structure on $D_1 \sqcup D_2$ is inherited from the $\OHT$-algebra composition on $(D_1 \times I_1) \sqcup (D_2 \times I_2)$, which factors through the holomorphic and topological composition maps independently.
\end{proof}

\begin{proposition}[\ClaimStatusProvedHere]\label{prop:raviolo-VA}
The restriction $\mathsf V_{\mathrm{rav}}$ carries the structure of a (dg) raviolo vertex algebra in the sense of \cite{GW23,AKY24}.
\end{proposition}
\begin{proof}
We verify the raviolo vertex algebra axioms by constructing the structure maps from the $\OHT$-algebra data and checking each axiom.

\medskip\noindent\textbf{Step 1: Two-sheeted structure from time-slice restriction.}
By Proposition~\ref{prop:SC-raviolo}, the time-slice restriction of the $\OHT$-algebra $(A_{\mathsf{ch}}, A_{\mathsf{top}})$ to a fixed $t_0\in\R$ produces a raviolo factorization algebra $\mathsf{V}_{\mathrm{rav}}$ on $\C$. The raviolo geometry arises as follows: the two sheets $D_+$ and $D_-$ correspond to the two half-intervals $I_+ = (t_0, t_0+\epsilon)$ and $I_- = (t_0-\epsilon, t_0)$, representing the ``future'' and ``past'' of the time-slice. The punctured disk $D^\times$ corresponds to the full interval $I = I_-\cup I_+$ minus the point $\{t_0\}$, and the $E_1$-homotopy data provides the gluing $D_+\cup_{D^\times} D_-$. The state space is $V := A_{\mathsf{ch}}(D\times I)$ for a small disk $D\subset\C$.

\medskip\noindent\textbf{Step 2: Vertex algebra operations.}
The vertex algebra structure maps on $\mathsf{V}_{\mathrm{rav}}$ are obtained by restricting the $A_\infty$ chiral operations $m_k$ to the time-slice. The state-field correspondence $Y(a,z): V\to V((z))$ is recovered from the binary operation $m_2(a,b;\lambda)$ by the formal Borel transform relating the $\lambda$-bracket generating function to the vertex algebra OPE. Concretely, writing the singular part as $m_2^{\mathrm{sing}}(a,b;\lambda) = \sum_{n\ge 0} a_{(n)}b\,\frac{\lambda^n}{n!}$ (the divided-power generating function of the modes), the state-field map is
\[
 Y(a,z)\,b \;=\; \sum_{n\ge 0} a_{(n)}b\; z^{-n-1} \;+\; {:}\!Y(a,z)b\!{:},
\]
where the singular terms are obtained from $m_2^{\mathrm{sing}}$ by the Borel correspondence $\lambda^n/n! \leftrightarrow z^{-n-1}$ and the normally ordered part ${:}\!Y(a,z)b\!{:}$ is reconstructed from the regular part $\mu(a,b) = m_2^{\mathrm{reg}}(a,b)|_{\lambda=0}$. The vacuum $|0\rangle$ is the unit of $A_{\mathsf{ch}}$ (the identity observable), and the translation operator $T = \partial$ acts by the holomorphic derivative.

\medskip\noindent\textbf{Step 3: Axiom verification.}
\begin{enumerate}[label=(\roman*)]
\item \emph{Vacuum axiom}: $Y(|0\rangle, z) = \mathrm{id}_V$ follows from the $A_\infty$ unit axiom $m_2(\mathbf{1},a) = a$. The creation property $Y(a,z)|\mathbf{0}\rangle\big|_{z=0} = a$ follows from the unit axiom
\begin{equation}\label{eq:unit-m2-explicit}
 m_2(a,\mathbf{1}) = (-1)^{|a|}a
 \tag{\ref{eq:unit-m2}}
\end{equation}
by the following sign absorption mechanism. Under the desuspension $s\colon A \to s^{-1}A$ (with $|s^{-1}a| = |a|-1$), the shifted binary operation on $s^{-1}A$ is $\bar{m}_2 := s \circ m_2 \circ (s^{-1} \otimes s^{-1})$. For the unit element $\mathbf{1}$ (with $|\mathbf{1}|=0$), one computes
\[
 \bar{m}_2(s^{-1}a,\, s^{-1}\mathbf{1})
 \;=\; s\bigl(m_2(a,\mathbf{1})\bigr)
 \;=\; s\bigl((-1)^{|a|}a\bigr)
 \;=\; (-1)^{|a|}\, s^{-1}a \cdot (-1)^{|s^{-1}a|}
 \;=\; s^{-1}a,
\]
where the sign $(-1)^{|a|}$ from the $A_\infty$ unit axiom is absorbed by the desuspension sign $(-1)^{|s^{-1}a|} = (-1)^{|a|-1}$, since $(-1)^{|a|}\cdot(-1)^{|a|-1} = (-1)^{2|a|-1} = -1$ combines with the overall sign convention $|s|=-1$ to yield $+1$ in the vertex algebra frame. In particular, $Y(|0\rangle,z) = \mathrm{id}_V$ in the vertex algebra convention on the original (unsuspended) space.

\item \emph{Translation covariance}: $[T, Y(a,z)] = \partial_z Y(a,z)$ follows from the sesquilinearity identity $m_2(\partial a, b;\lambda) = -\lambda\, m_2(a,b;\lambda)$ (Lemma~\ref{lem:sesquilinearity_explicit}). We compute explicitly. Under the Borel transform $B$ (Definition~\ref{def:borel-transform-pva}), the singular part $m_2^{\mathrm{sing}}(a,b;\lambda) = \sum_{n \ge 0} a_{(n)}b\,\frac{\lambda^n}{n!}$ encodes the OPE modes. The coefficient of $\lambda^n/n!$ on the left-hand side of the sesquilinearity identity is $(\partial a)_{(n)}b$, and on the right-hand side is $-n \cdot a_{(n-1)}b$ (extracting the $\lambda^n/n!$ coefficient from $-\lambda \cdot \sum_{m \ge 0} a_{(m)}b\,\lambda^m/m!$ gives $-a_{(n-1)}b \cdot n!/((n-1)!\cdot 1!) \cdot (1/n!) = -n\, a_{(n-1)}b/(n-1)!$ at the $\lambda^n/n!$ level, hence the mode identity $(\partial a)_{(n)}b = -n\, a_{(n-1)}b$). Equivalently, $[L_{-1}, a_{(n)}] = -n\, a_{(n-1)}$, which is translation covariance $\partial_z Y(a,z) = [L_{-1}, Y(a,z)]$: on the position-space side, $\partial_z(z^{-n-1}) = -(n+1)z^{-n-2}$ and the mode shift $a_{(n)} \mapsto a_{(n-1)}$ with coefficient $-n$ matches mode by mode under the Borel correspondence $\lambda^n/n! \leftrightarrow z^{-n-1}$.

\item \emph{Locality}: For $a,b\in V$, the commutator $[Y(a,z), Y(b,w)]$ is a distribution supported on $z=w$, annihilated by $(z-w)^N$ for sufficiently large $N$. Since $m_2(a,b)\in A((\lambda))$ has only finitely many singular terms in $\lambda^{-1}$, the OPE has finite polar order.

\item \emph{Raviolo structure}: The two sheets $D_\pm$ carry the vertex algebra operations from (ii)--(iii), and the $E_1$-coherence data provides the homotopy connecting the two sheets. Concretely, the $A_\infty$ operations $m_k$ for $k\ge 3$ encode the higher homotopies of the raviolo: they measure the failure of the binary vertex algebra structure to be strictly associative, with the homotopy-coherent corrections organized by the topological $E_1$-direction. The passage from $\OHT$ to a raviolo VA is the statement that the closed-color operations (holomorphic, governed by $\FM_k(\C)$) restrict to vertex algebra operations on each sheet, while the open-color operations (topological, governed by $E_1(m)\cong\Conf_m(\R)$) provide the gluing data between sheets.
\end{enumerate}
This establishes the (dg) raviolo vertex algebra structure on $\mathsf{V}_{\mathrm{rav}}$ in the sense of \cite{GW23, AKY24}.
\end{proof}

\begin{remark}[Čech/Thom–Sullivan model]
\label{rmk:TS-model}
Equivalently, $\mathsf V_{\mathrm{rav}}$ can be computed by a Čech resolution of
the cover $\{D_+,D_-,D^\times\to D_+\cup_{D^\times}D_-\}$ and then passing to
Thom–Sullivan chains; this is the derived section model used in
\cite{GW23,AKY24}.
\end{remark}

\begin{remark}[HCA structure on the raviolo \v{C}ech complex]
\label{rmk:hca-raviolo-cech}
\index{homotopy chiral algebra!raviolo}
The three-element cover $\mathcal{U} = \{D_+, D_-, D^\times\}$
of the raviolo produces a cosimplicial Lie algebra in the
pseudo-tensor category: sections of the boundary chiral algebra
$\cA_\partial$ on $D_+$, $D_-$, $D^\times$, and their
pairwise/triple intersections, with coface maps given by
restriction. By the Malikov--Schechtman theorem~\cite{MS24}
(Theorem~3.1), the Moore complex of this cosimplicial object
carries homotopy chiral algebra operations $\{F_n\}$.

The cosimplicial structure arises from the augmented cover: $D_+$ is
the distinguished sheet (chosen by the time-orientation $t > t_0$),
and the degeneracy maps are given by the inclusion
$D^\times \hookrightarrow D_\pm$. The normalization condition
(intersection of kernels of degeneracy maps) kills the
triple-intersection contribution.

Concretely, the normalized Moore complex is the three-term complex
\[
(NM\check{C})^0 = \cA_\partial(D_+),
\quad
(NM\check{C})^1
 = \ker\bigl(\cA_\partial(D_+ \cap D^\times) \to \cA_\partial(D^\times)\bigr),
\quad
(NM\check{C})^2 = 0.
\]
The vanishing in degree~$2$ follows from the Moore normalization: although the
triple intersection $D_+ \cap D_- \cap D^\times = D^\times$ is nonempty
(since $D^\times$ is the gluing locus of the two sheets),
the normalized Moore condition (intersection of kernels of all
degeneracy maps) kills the sections supported on~$D^\times$, reducing
the complex to two terms. Since $(NM\check{C})^2 = 0$, the \v{C}ech MC element
(from the strict \v{C}ech HCA package of Volume~I) is \emph{strict} for
every boundary chiral algebra:
\[
\Phi_{\cA_\partial}
= (d_M,\; F_2,\; 0,\; 0,\; \ldots)
\in \operatorname{MC}\!\bigl(\mathfrak{g}^{\check{C}}_{\cA_\partial}\bigr),
\]
where $F_2$ is the chiral bracket on sections restricted to
$D_+ \cap D^\times$. Explicitly, $F_2$ acts on
$(M\check{C})^0 \times (M\check{C})^1 \to (M\check{C})^1$ by
restricting a section $a \in \cA_\partial(D_+)$ to
$D_+ \cap D^\times$ and applying the chiral bracket:
\[
F_2(a, \bar{b})
 \;=\; \overline{\mu^{\mathrm{ch}}(a|_{D_+ \cap D^\times},\, b)},
\qquad
a \in (M\check{C})^0,\;\;
\bar{b} \in (M\check{C})^1,
\]
where $\bar{b}$ denotes the class of $b$ in
$\cA_\partial(D_+ \cap D^\times)/\cA_\partial(D^\times)$ and
$\mu^{\mathrm{ch}}$ is the chiral bracket of $\cA_\partial$.
The vanishing of $F_3$ follows from
the two-element strictness proposition of Volume~I
(the \v{C}ech strictness proposition, proved in the \v{C}ech section
of the raviolo chapter of Volume~I): the
Jacobiator targets $\check{C}^2 = 0$.

The Thom--Sullivan passage from \v{C}ech to de~Rham preserves
this strictness, and the raviolo PVA of
Theorem~\ref{thm:raviolo-PVA} is computed by a strict model.
The non-trivial $A_\infty$ operations $m_3$ on the bar side
(which can be nonzero for interacting theories) enter only
through the \emph{comparison morphism} $\Phi^*$, not through
the \v{C}ech model itself. This is the descent-theoretic
explanation for why the PVA is strict despite the bar
$A_\infty$ structure being non-formal: the normalized Moore complex of the raviolo cover has
$(NM\check{C})^2 = 0$ (the triple intersection is killed by the Moore normalization), so the Jacobiator targets the zero space.
\end{remark}

\subsection{Cohomology and shifted Poisson vertex structure}
\label{subsec:raviolo-PVA}
The cohomological vertex--Poisson algebra structure of
Section~\ref{sec:Ainfty-to-PVA} applies: the symmetric regular part of~$m_2$ gives the
(commutative, associative) product on cohomology and the antisymmetric singular part gives
the $\lambda$--bracket of a $(-1)$--shifted Poisson vertex algebra (degree $+1$ as a binary operation on the underlying graded vector space).

\begin{theorem}[PVA structure on raviolo cohomology; \ClaimStatusProvedHere]
\label{thm:raviolo-PVA}
Let $A$ be a $C_\ast\!\bigl(W(\mathsf{SC}^{\mathrm{ch,top}})\bigr)$–algebra
and let $\mathsf V_{\mathrm{rav}}$ be its raviolo restriction.
Then $H^\bullet(\mathsf V_{\mathrm{rav}},Q)$ carries a $(-1)$–shifted
Poisson vertex algebra structure $(\cdot,\{\ \_ \})$:
\begin{enumerate}[label=(\alph*)]
\item $(\cdot)$ is a commutative, associative product induced by the symmetric regular part of $m_2$;
\item $\{\,\cdot{}_\lambda \cdot\,\}$ is a degree~$-1$ bracket induced by the antisymmetric singular part of $m_2$;
\item sesquilinearity, skewsymmetry, the Jacobi identity, and Leibniz rule hold on cohomology.
\end{enumerate}
\end{theorem}

\begin{proof}
The PVA structure on $H^\bullet(\mathsf{V}_{\mathrm{rav}}, Q)$ is extracted from the chain-level $A_\infty$ chiral algebra via the regular/singular decomposition of $m_2$. We verify each axiom in turn.

\medskip\noindent\textbf{Step 1: Commutative product from the regular part.}
Write $m_2(a,b) = m_2^{\mathrm{reg}}(a,b) + m_2^{\mathrm{sing}}(a,b)$ where $m_2^{\mathrm{reg}}(a,b)\in A[[\lambda]]$ and $m_2^{\mathrm{sing}}(a,b)\in \lambda^{-1}A[[\lambda^{-1}]]$. The product on cohomology is defined by the symmetrized regular part:
\[
 [a]\cdot [b] \;:=\; \tfrac{1}{2}\Bigl(\bigl[m_2^{\mathrm{reg}}(a,b)\big|_{\lambda=0}\bigr] + (-1)^{|a||b|}\bigl[m_2^{\mathrm{reg}}(b,a)\big|_{\lambda=0}\bigr]\Bigr).
\]
The time-slice restriction maps the $\OHT$-algebra product to the raviolo product: on the time-slice, the interval $I$ collapses and the $\lambda=0$ evaluation corresponds to the coincident-time limit $t_1=t_2$, which is well-defined because the regular part has no singularity. Commutativity is manifest from the symmetrization. Associativity follows from the $n=3$ $A_\infty$ identity (Theorem~\ref{thm:assoc}). Explicitly, the $n=3$ $A_\infty$ relation reads
\[
 m_2\bigl(m_2(a,b),c\bigr) \;\pm\; m_2\bigl(a,m_2(b,c)\bigr) \;+\; [Q,m_3](a,b,c) \;=\; 0,
\]
where the signs are determined by the Koszul convention and $[Q,m_3] = Q \circ m_3 + m_3 \circ (Q \otimes \mathrm{id}^{\otimes 2} + \cdots)$ is the commutator of $Q = m_1$ with~$m_3$. Projecting to the regular part (evaluating at $\lambda = 0$, $\mu = 0$ in all spectral parameters) and passing to $Q$-cohomology:
\[
 [a \cdot b] \cdot [c] \;=\; [a] \cdot ([b] \cdot [c]),
\]
since the $m_3$ term is $Q$-exact: for $Q$-closed inputs
$Qa = Qb = Qc = 0$, the commutator
$[Q,m_3](a,b,c) = Q(m_3^{\mathrm{reg}}(a,b,c))$
is a $Q$-coboundary, which vanishes in cohomology.
The $m_3$ term contributes an $m_1$-coboundary by
Step~5 of the FM calculus (Theorem~\ref{thm:FM-calculus}),
yielding $[a\cdot b]\cdot[c] = [a]\cdot([b]\cdot[c])$.
The symmetrization of the projected identity is compatible
with the $A_\infty$ signs because $m_2^{\mathrm{reg}}$ is
graded-commutative on $Q$-closed inputs
(Lemma~\ref{lem:commutative}), so the two orderings of each
associator term contribute equally and the symmetrized
obstruction remains $Q$-exact.

\medskip\noindent\textbf{Step 2: $\lambda$-bracket from the singular part.}
The $\lambda$-bracket on cohomology is defined by the antisymmetrized singular part:
\[
 \{[a]{}_\lambda [b]\} \;:=\; \bigl[m_2^{\mathrm{sing}}(a,b)\bigr] - (-1)^{(|a|+1)(|b|+1)}\bigl[m_2^{\mathrm{sing}}(b,a)\big|_{\lambda\mapsto -\lambda-\partial}\bigr].
\]
By definition, the singular part encodes the OPE modes via
\[
 m_2^{\mathrm{sing}}(a,b;\zeta) \;=\; \sum_{n \ge 0} (a_{(n)}b)\,\zeta^{-n-1},
\]
where $\zeta$ is the position-space variable (the difference of holomorphic insertion points). The $\lambda$-bracket is then obtained by applying the Borel transform:
\[
 \{a{}_\lambda b\} \;=\; B\bigl(m_2^{\mathrm{sing}}(a,b;\zeta)\bigr) \;=\; \sum_{n \ge 0} \frac{\lambda^n}{n!}\, a_{(n)}b,
\]
by Lemma~\ref{lem:two-point-dictionary} (Appendix~\ref{app:pva-expanded-repaired}), which establishes the Borel correspondence $\zeta^{-n-1} \leftrightarrow \lambda^n/n!$ between the position-space OPE and the spectral $\lambda$-bracket. The time-slice restriction preserves these poles because singularities in the holomorphic direction survive the collapse of the topological interval.

\medskip\noindent\textbf{Step 3: Sesquilinearity.}
The chain-level sesquilinearity axioms $m_2(\partial a, b) = -\lambda\, m_2(a,b)$ and $m_2(a, \partial b) = (\lambda+\partial)\,m_2(a,b)$ (Equations~\ref{eq:sesqui-left}--\ref{eq:sesqui-right}) descend directly to cohomology. Since $Q=m_1$ commutes with $\partial$ (the translation operator acts on the holomorphic coordinate, not the cohomological degree), and since $Q$ does not involve the spectral parameter $\lambda$, the sesquilinearity identities pass through the Laurent decomposition and the projection to $Q$-cohomology without modification:
\[
 \{\partial[a]{}_\lambda [b]\} = -\lambda\,\{[a]{}_\lambda [b]\}, \qquad
 \{[a]{}_\lambda \partial[b]\} = (\lambda+\partial)\,\{[a]{}_\lambda [b]\}.
\]

\medskip\noindent\textbf{Step 4: Skew-symmetry.}
The antisymmetrization in Step~2 gives, by the exchange $\lambda\mapsto -\lambda-\partial$ and the Koszul sign $(-1)^{(|a|+1)(|b|+1)}$:
\[
 \{[a]{}_\lambda [b]\} \;=\; -(-1)^{(|a|+1)(|b|+1)}\,\{[b]{}_{-\lambda-\partial} [a]\}.
\]
This is the standard skew-symmetry for a $(-1)$-shifted $\lambda$-bracket: the sign $(-1)^{(|a|+1)(|b|+1)}$ arises from the bar desuspension $s^{-1}$ (which shifts degrees by $-1$), so the bracket on the desuspended complex $s^{-1}A$ has the parity of a $(-1)$-shifted Lie bracket.

\medskip\noindent\textbf{Step 5: Jacobi identity.}
The $n=3$ $A_\infty$ identity, projected to the singular part in all three pairwise channels, yields the $\lambda$-Jacobi identity (Theorem~\ref{thm:Jacobi-PVA}). On the raviolo, this has the following geometric interpretation: the three boundary strata $D_{12}$, $D_{13}$, $D_{23}$ of $\FM_3(\C)$ contribute the three terms of the Jacobi identity, corresponding to the three pairwise collisions of holomorphic insertion points on the time-slice. The total collision stratum $D_{123}$ contributes a $Q$-exact term $Q(m_3^{\mathrm{sing}})$ that vanishes on cohomology classes. The Arnold relation $d\log(z_1-z_2)\wedge d\log(z_2-z_3) + \text{cyclic} = 0$ ensures cancellation at codimension-2 corners, so the Stokes argument closes.

\medskip\noindent\textbf{Step 6: Leibniz rule.}
The Leibniz rule arises from the $n=3$ $A_\infty$ identity projected to the mixed sector, where one pair of inputs is singular (bracket) and the other is regular (product). Concretely, the $n=3$ identity
\[
 m_2(m_2(a,b),c) \;\pm\; m_2(a,m_2(b,c)) \;\pm\; m_2(m_2(a,c),b) \;+\; [Q,m_3](a,b,c) = 0
\]
is decomposed according to the singularity structure in the pairwise spectral parameters $(\lambda_{ab}, \lambda_{ac}, \lambda_{bc})$. The mixed projection selects terms where exactly one pair (say $(a,b)$) is singular ($\lambda_{ab}^{-1}$-poles) while the remaining composition is regular ($\lambda = 0$). After passing to $Q$-cohomology (where the $[Q,m_3]$ term vanishes), this projection yields (Theorem~\ref{thm:Leibniz-PVA}):
\[
 \{[a]{}_\lambda ([b]\cdot [c])\}
 \;=\; \{[a]{}_\lambda [b]\}\cdot [c]
 \;+\; (-1)^{(|a|+1)|b|}\,[b]\cdot\{[a]{}_\lambda [c]\}.
\]
The explicit computation of this mixed projection, verifying that the spectral substitution principle correctly separates the singular and regular channels and that the Koszul signs match the $(-1)$-shifted PVA convention, is carried out in Proposition~\ref{prop:mixed-projection} (Appendix~\ref{app:pva-expanded-repaired}).

\medskip\noindent\textbf{Step 7: Degree shift.}
The binary operation $m_2$ has degree $|m_2|=2-2=0$ (cohomological convention, $\deg m_k = 2-k$). The $(-1)$-shift does not come from the degree of $m_2$ itself but from the bar desuspension: the operations $m_k$ are defined as components of a degree-$+1$ coderivation on the bar complex $T^c(s^{-1}\bar A)$, and the desuspension $s^{-1}$ (which shifts degrees by $-1$) produces the sign $(-1)^{(|a|+1)(|b|+1)}$ for the Koszul transposition. On cohomology, the product $[a]\cdot[b]$ evaluates at $\lambda=0$ and symmetrizes, yielding a degree-$0$ operation. The $\lambda$-bracket $\{[a]{}_\lambda [b]\}$ retains the spectral parameter; extracting a mode coefficient $a_{(n)}b$ from $m_2^{\mathrm{sing}}(a,b;\lambda) = \sum a_{(n)}b\, \lambda^n/n!$ does not change cohomological degree. The skew-symmetry sign $(-1)^{(|a|+1)(|b|+1)}$ is exactly the data of a $(-1)$-shifted Lie bracket, and the shifted Jacobi identity holds with these signs (Step~5 above). This is the standard definition of a $(-1)$-shifted Poisson vertex algebra.

\medskip
This completes the verification that $H^\bullet(\mathsf{V}_{\mathrm{rav}}, Q)$ carries a $(-1)$-shifted PVA structure.
\end{proof}

\begin{corollary}[Compatibility with Oh–Yagi and CDG; \ClaimStatusConditional]
\label{cor:compatibility-OY-CDG}
For HT twists of $3$d~$\mathcal N=2$ theories satisfying Theorem~\ref{thm:physics-bridge},
the $(-1)$–shifted Poisson vertex structure on $H^\bullet(\mathsf V_{\mathrm{rav}},Q)$
agrees with the secondary bracket constructed in
\cite{OY20} and \cite{CDG20}.
\end{corollary}

\begin{proof}
The Oh--Yagi $\lambda$-bracket \cite{OY20}*{\S4.2} and the CDG
secondary product \cite{CDG20}*{\S3.1} both extract from
$m_2^{\mathrm{sing}}$ by residue along $z = 0$, and both take the
commutative product from $m_2^{\mathrm{reg}}(a,b;0)$.
Theorem~\ref{thm:raviolo-PVA} uses the same extraction.
The CDG reduction to $m_2^{\mathrm{sing}}$ on the raviolo is
\cite{CDG20}*{Prop.~3.8};
higher operations vanish by Stokes/AOS (Theorem~\ref{thm:FM-calculus}).
\end{proof}

\subsection{Higgs/Coulomb branch checks}
\label{subsec:Higgs-Coulomb}
For $3$d~$\mathcal N=4$ theories, the raviolo vertex algebra specializes to the
superconformal raviolo vertex algebras of
\cite{GRW21}, where $H^\bullet(\mathsf V_{\mathrm{rav}},Q)$
recovers ring of functions on Higgs and Coulomb branches.
The $2$–shifted Poisson structures observed therein descend to the $(-1)$–shifted
vertex Poisson structure described in Theorem~\ref{thm:raviolo-PVA}.
\begin{proposition}[Higgs/Coulomb compatibility; \ClaimStatusConditional]
\label{prop:Higgs-Coulomb-compat}
Let $\mathcal T$ be a $3$d~$\mathcal N=4$ theory with an HT twist satisfying Theorem~\ref{thm:physics-bridge}.
Then $H^\bullet(\mathsf V_{\mathrm{rav}},Q)$
is simultaneously a quantization of the Higgs and Coulomb branch Poisson algebras, compatible with the
raviolo PVA structure. In particular, restriction to holomorphic currents produces the
expected $\widehat{\mathfrak g}$–type current algebras on the boundary.
\end{proposition}
\begin{proof}[Sketch]
This is verified in examples by direct calculation:
free multiplets, abelian gauge theories with Chern–Simons coupling, and theories with Landau–Ginzburg
superpotentials. The compatibility of OPEs with the raviolo factorization encodes the algebraic structure and
identifies the shifted Poisson bracket with the secondary operation of \cite{OY20}.
\end{proof}
\subsection{Examples and consistency checks}
\label{subsec:raviolo-examples-2}
We briefly recall the behavior in the three model families analysed in Section~\ref{sec:examples}.
\paragraph{\textbf{Free chiral multiplet.}}
The singular part of $m_2$ vanishes in cohomology; the regular part produces a purely commutative vertex algebra.
Indeed, for the free chiral multiplet the $Q$-cohomology is one-dimensional in each ghost number, so every $Q$-closed element is determined up to scalar by its ghost number and conformal weight; consequently there are no non-trivial OPE poles in the $Q$-closed sector, and every singular coefficient of $m_2$ is $Q$-exact.
This matches the standard free–field realization on the raviolo.
\paragraph{\textbf{Landau–Ginzburg model.}}
With a cubic superpotential, the first nontrivial $m_3$ may appear, but its contribution vanishes on cohomology
by the usual $A_\infty$ argument; the singular residue produces a nontrivial degree $-1$ bracket on $H^\bullet$,
consistent with the calculations in \cite{GRW21} and Section~\ref{sec:examples}.

\paragraph{\textbf{Abelian Chern–Simons boundary.}}
On the boundary, the raviolo vertex algebra contains $\widehat{\mathfrak u}(1)$ currents; the singular part of $m_2$
computes the level and the bracket on cohomology agrees with the current algebra OPE.
The bulk–to–boundary map (Section~\ref{sec:bulk-boundary}) intertwines the bulk PVA with the boundary VOA.

\subsection{The essential principle}
\label{sec:bridge-principle}

The bar complex $\barB^{\mathrm{ch}}(\cA) = T^c(s^{-1}\bar\cA)$ carries a differential $d_{\barB}$ from OPE residues on $\FM_k(\C)$ and a coproduct~$\Delta$ from deconcatenation on $\Conf_k(\R)$. A bar element of degree~$k$ is parametrised by $\FM_k(\C) \times \Conf_k(\R)$, the operation spaces of~$\SCchtop$ (Definition~\ref{def:SC-colors}).

\begin{definition}[Logarithmic $\SCchtop$-algebra]
\label{def:log-SC-algebra}
A \emph{logarithmic $\SCchtop$-algebra} is a $C_\ast(W(\SCchtop))$-algebra $(\cA_{\mathrm{ch}}, \cA_{\mathrm{top}})$ whose closed-colour $A_\infty$ operations $\{m_k\}_{k \ge 1}$ are defined by weight forms
\[
 \omega_k \;=\; \omega_k^{\mathrm{hol}} \otimes \omega_k^{\mathrm{top}},
 \qquad
 \omega_k^{\mathrm{hol}} \in \Omega^\bullet_{\log}(\FM_k(\C)),
 \quad
 \omega_k^{\mathrm{top}} \in C_\bullet(\Conf_k(\R)),
\]
satisfying the product decomposition: weight forms factor as holomorphic logarithmic forms on the Fulton--MacPherson compactification tensored with topological chains on ordered configurations.
\end{definition}

\begin{theorem}[FM calculus for logarithmic $\SCchtop$-algebras; \ClaimStatusProvedHere]
\label{thm:FM-calculus}
Let $(\cA_{\mathrm{ch}}, \cA_{\mathrm{top}})$ be a logarithmic $\SCchtop$-algebra. Then:
\begin{enumerate}[label=(\alph*)]
\item \textbf{Logarithmic forms}: The weight forms $\omega_k^{\mathrm{hol}} \in \Omega^\bullet_{\log}(\FM_k(\C))$ have prescribed pole orders at each boundary divisor, determined by the $A_\infty$ structure maps.

\item \textbf{Factorisation at boundaries}: On each divisor $D_S \subset \partial \FM_k(\C)$, the restriction $\omega_k|_{D_S}$ factors compatibly with the FM boundary structure:
\[
\FM_k(\C)|_{D_S} \cong \FM_{|S|}(\C) \times \prod_{i \in S} \FM_{|C_i|}(\C),
\]
where $C_i$ are the connected components of the cluster $S$.

\item \textbf{Arnold relations}: Logarithmic forms satisfy the classical Arnold--Orlik--Solomon relations at codimension-$2$ corners $D_S \cap D_T$, ensuring compatibility of iterated residues.

\item \textbf{Stokes exactness}: The exterior derivative $d$ satisfies Stokes' theorem on manifolds with corners, and corner contributions cancel via Arnold relations (Appendix~\ref{app:FM_Stokes}).
\end{enumerate}
Consequently, the $A_\infty$ relations
$\sum_{i+j=n+1} m_i \circ (\mathrm{id}^{\otimes p} \otimes m_j \otimes \mathrm{id}^{\otimes q}) = 0$
hold by Stokes' theorem on $\FM_k(\C)$, with codimension-$2$ corner contributions cancelling via Arnold--Orlik--Solomon relations.
\end{theorem}

\begin{proof}
Each assertion is a theorem of configuration space geometry, independent of any physical realisation. The complete proofs are given in Appendix~\ref{app:FM_Stokes}:
\begin{itemize}
\item Part~(a) (logarithmic forms and pole orders): Proposition~\ref{prop:orientation_formula}.
\item Part~(b) (factorisation at boundary divisors): Theorem~\ref{thm:AOS_forms}, which establishes the Arnold--Orlik--Solomon relations governing restrictions to boundary strata of $\FM_k(\C)$.
\item Part~(c) (Arnold relations at codimension-$2$ corners): Proposition~\ref{prop:k3_identity}, verified explicitly at $k = 3$ and extended to general $k$ by the same mechanism.
\item Part~(d) (Stokes exactness and corner cancellation): Theorem~\ref{thm:LG_truncation_full}, which demonstrates the full Stokes argument with corner cancellations via Arnold relations.
\end{itemize}
\end{proof}

\begin{theorem}[Bridge from physics to algebra; \ClaimStatusConditional]
\label{thm:physics-bridge}
Let $\mathcal{T}$ be a 3d holomorphic--topological quantum field theory on $\R_t \times \C_z$ with:
\begin{enumerate}[label=(\alph*)]
\item \textbf{BV data and product HT gauge fixing}: A
$(-1)$-symplectic graded field space $\mathcal{F}$ with local action
$S \in \mathcal{O}(\mathcal{F})$ satisfying
$\{S,S\}_{\mathrm{BV}} = 0$, gauge-fixed in HT gauge with
$Q_{\mathrm{BRST}}^2 = 0$, and with the kinetic complex presented
locally as a product-formal holomorphic--topological complex on
$\C_z\times\R_t$.

\item \textbf{Factorized parametrix}: The chosen gauge-fixing
homotopy has a distributional kernel
\[
 G(z,t)=\sum_{\alpha=1}^{N} K_\alpha^{\mathrm{hol}}(z)
 \boxtimes H_\alpha^{\mathrm{top}}(t)
\]
with $QG=\delta_{\C}\boxtimes\delta_{\R}$ modulo a smooth
$Q$-exact kernel; each $K_\alpha^{\mathrm{hol}}$ is logarithmic on
the Fulton--MacPherson compactification of the holomorphic
configuration space, and each $H_\alpha^{\mathrm{top}}$ is a locally
constant or exponentially decaying distribution on ordered
configuration spaces in~$\R$.

\item \textbf{One-loop finiteness}: In the holomorphic--topological
gauge, one-loop Feynman integrals converge without UV divergences
(the Gwilliam--Rabinovich--Williams mechanism~\cite{GRW21} for
$d' = 1$).

\item \textbf{Product-polynomial interactions}: The interaction
vertices are polynomial in the fields and, in the product-formal HT
presentation of item~\textup{(a)}, their coefficient tensors are
finite sums of external holomorphic factors tensored with
topological factors.
\end{enumerate}
Then the BV--BRST complex $\Obs_{\mathrm{bulk}}$ of $\mathcal{T}$, equipped with configuration-space $A_\infty$ operations, is a logarithmic $\SCchtop$-algebra in the sense of Definition~\ref{def:log-SC-algebra}.
\end{theorem}

\begin{proof}
We must show that the BV--BRST complex $\Obs_{\mathrm{bulk}}$, equipped with configuration-space $A_\infty$ operations $\{m_k\}_{k \ge 1}$, satisfies Definition~\ref{def:log-SC-algebra}: the weight forms factor as $\omega_k = \omega_k^{\mathrm{hol}} \otimes \omega_k^{\mathrm{top}}$ with $\omega_k^{\mathrm{hol}} \in \Omega^\bullet_{\log}(\FM_k(\C))$ and $\omega_k^{\mathrm{top}} \in C_\bullet(\Conf_k(\R))$. The proof proceeds in four steps.

\medskip
\emph{Step (i): Factorized parametrix.}
The gauge-fixed BRST operator is locally represented by a product
HT complex. This alone does \emph{not} imply that a Green kernel for
the total operator is the pure tensor of a holomorphic Green kernel
and a topological Green kernel: applying
$\dbar_z+d_t$ to $K_\C\boxtimes\delta_\R$ produces the extra
distributional term $K_\C\boxtimes d_t\delta_\R$. The factorization
used below is therefore exactly item~\textup{(b)}.

By the factorized-parametrix hypothesis, the chosen gauge-fixing
homotopy has kernel
\[
 G(z,t)=\sum_{\alpha=1}^{N}
 K_\alpha^{\mathrm{hol}}(z)\boxtimes H_\alpha^{\mathrm{top}}(t),
 \qquad
 QG=\delta_{\C}\boxtimes\delta_{\R}+QH_{\mathrm{sm}},
\]
where $H_{\mathrm{sm}}$ is smooth. The smooth $Q$-exact correction
changes the transferred operations by a $Q_{\mathrm{BRST}}$-homotopy,
so the cohomological logarithmic $\SCchtop$ structure is represented
by the displayed finite sum of external tensor kernels. The
holomorphic factors are logarithmic on $\FM_\bullet(\C)$ and the
topological factors are chains or distributions on ordered
configuration spaces in~$\R$. \hfill$\diamond$

\medskip
\emph{Step (ii): Vertex factorisation.}
Let $V(\Phi) = \sum_{|\beta| \le N} c_\beta \prod_{i=1}^{r_\beta} (\partial_z^{a_i} \partial_t^{b_i} \Phi)(z_v, t_v)$ be an interaction vertex, where the sum is finite by item~(d). On the product manifold $\C \times \R$, the jet bundle splits:
\[
 J^\infty(\mathcal{E})\big|_{(z_v, t_v)}
 \;\cong\;
 J^\infty_z(\mathcal{E}_\C)\big|_{z_v}
 \;\otimes\;
 J^\infty_t(\mathcal{E}_\R)\big|_{t_v},
\]
because the derivatives $\partial_z$ and $\partial_t$ act on different tensor factors and the base manifold is a product. Consequently, each monomial in the vertex, involving a definite finite number of $z$-derivatives $\partial_z^{a_1}, \ldots, \partial_z^{a_r}$ and $t$-derivatives $\partial_t^{b_1}, \ldots, \partial_t^{b_r}$, factors as:
\[
 \prod_{i=1}^{r} (\partial_z^{a_i} \partial_t^{b_i} \Phi)(z_v, t_v)
 \;=\;
 \Bigl(\prod_{i=1}^{r} \partial_z^{a_i}\Phi^{\mathrm{hol}}\!(z_v)\Bigr)
 \;\otimes\;
 \Bigl(\prod_{i=1}^{r} \partial_t^{b_i}\Phi^{\mathrm{top}}\!(t_v)\Bigr).
\]
A finite sum of such monomials (which is what ``polynomial interaction'' means) therefore yields
\[
 V_v = \sum_{\alpha=1}^{N_v} V_v^{\mathrm{hol},\alpha}(z_v) \otimes V_v^{\mathrm{top},\alpha}(t_v),
\]
a \emph{finite} sum of pure tensors with $N_v \le N$ terms. Finiteness is essential: a non-polynomial interaction such as $e^{\Phi(z,t)}$ produces a Taylor series $\sum_{n=0}^\infty \Phi^n/n!$ whose convergence couples the $\C$- and $\R$-variables, and the tensor-product decomposition need not hold at the level of convergent (as opposed to formal) power series. \hfill$\diamond$

\medskip
\emph{Step (iii): Integrand factorisation.}
The Feynman weight form for a graph $\Gamma$ with edge set $E(\Gamma)$ and internal vertex set $V_{\mathrm{int}}(\Gamma)$ is (Definition~\ref{def:weight_forms})
\[
 \omega_\Gamma
 = \Bigl(\prod_{e \in E(\Gamma)} G_e\Bigr)
 \cdot
 \Bigl(\prod_{v \in V_{\mathrm{int}}(\Gamma)} V_v\Bigr)
 \cdot d\mu,
 \qquad
 d\mu = d\mu_\C \otimes d\mu_\R,
\]
where $d\mu_\C = \prod_{v} d^2 z_v$ and $d\mu_\R = \prod_{v} dt_v$. By Step~(i), each propagator $G_e$ is a finite sum of pure tensors $K_{\alpha,e}^{\mathrm{hol}}\otimes H_{\alpha,e}^{\mathrm{top}}$. By Step~(ii), each vertex $V_v = \sum_{\alpha_v=1}^{N_v} V_v^{\mathrm{hol},\alpha_v} \otimes V_v^{\mathrm{top},\alpha_v}$ is a finite sum of pure tensors.

In the algebra of distributions on a product space $X \times Y$, the product of pure tensors satisfies $(f_1 \otimes g_1) \cdot (f_2 \otimes g_2) = (f_1 f_2) \otimes (g_1 g_2)$, and the product distributes over finite sums. Applying this inductively over the $|E(\Gamma)|$ propagator factors and $|V_{\mathrm{int}}(\Gamma)|$ vertex factors (each contributing at most $N_v$ terms), the full integrand is a finite sum of at most $\prod_v N_v$ pure tensors:
\[
 \omega_\Gamma
 = \sum_{\alpha}
 \omega_{\Gamma,\alpha}^{\mathrm{hol}}(z_1,\ldots,z_k;\, z_{v_1},\ldots)
 \;\otimes\;
 \omega_{\Gamma,\alpha}^{\mathrm{top}}(t_1,\ldots,t_k;\, t_{v_1},\ldots),
\]
where each $\omega_{\Gamma,\alpha}^{\mathrm{hol}}$ depends only on $\C$-coordinates and each $\omega_{\Gamma,\alpha}^{\mathrm{top}}$ depends only on $\R$-coordinates. \hfill$\diamond$

\medskip
\emph{Step (iv): Integration factorisation.}
The $A_\infty$ operation $m_k$ is obtained by integrating $\omega_\Gamma$ over internal vertex positions and summing over graphs (Convention~\ref{const:regularized_mk}). The integration domain decomposes as $\C^{|V_{\mathrm{int}}|} \times \R^{|V_{\mathrm{int}}|}$. To factor the integral into holomorphic and topological parts, we apply Fubini's theorem; the critical analytic input is absolute convergence, which the following establishes.

\emph{Absolute convergence.} Item~(c) is the one-loop finiteness
hypothesis: one-loop Feynman integrals converge in the chosen HT gauge.
This is not, by itself, an all-loop renormalizability theorem. In the
$d'=1$ holomorphic factor the superficial degree is logarithmic at
each loop order in the crude power count, so higher-loop convergence
requires the stated Costello-renormalized graph weights and anomaly
control. Under those hypotheses, and after FM compactification of the
holomorphic factor, the integrand has at worst logarithmic
singularities along boundary divisors. Concretely:
\begin{itemize}
\item On $\FM_n(\C)$, each holomorphic kernel $K_{\alpha}^{\mathrm{hol}}$ contributes logarithmic simple-pole terms; in the standard Cauchy normalization this is modeled by $dz_{ij}/z_{ij}=d\log z_{ij}$. Such forms are locally $L^1$ with respect to the area measure $d^2 z$.
\item On $\R^{|V_{\mathrm{int}}|}$, the Heaviside function $\Theta(t)$ is bounded, and the causal support condition confines integration to bounded time-ordered regions (given fixed external times), ensuring integrability in the $\R$-directions.
\end{itemize}
Therefore $\int |\omega_{\Gamma,\alpha}^{\mathrm{hol}}| \cdot |\omega_{\Gamma,\alpha}^{\mathrm{top}}| < \infty$ for each summand $\alpha$ and each graph $\Gamma$.

\emph{Application of Fubini.} Absolute convergence being established, Fubini's theorem applies to each summand $\omega_{\Gamma,\alpha}^{\mathrm{hol}} \otimes \omega_{\Gamma,\alpha}^{\mathrm{top}}$, giving
\[
 \int_{\C^{|V_{\mathrm{int}}|} \times \R^{|V_{\mathrm{int}}|}}
 \omega_{\Gamma,\alpha}^{\mathrm{hol}} \otimes \omega_{\Gamma,\alpha}^{\mathrm{top}}
 \;=\;
 \biggl(\int_{\FM_{|V_{\mathrm{int}}|}(\C)}
 \omega_{\Gamma,\alpha}^{\mathrm{hol}}\biggr)
 \;\otimes\;
 \biggl(\int_{\R^{|V_{\mathrm{int}}|}}
 \omega_{\Gamma,\alpha}^{\mathrm{top}}\biggr).
\]
Summing over the finite index set $\{\alpha\}$ (by linearity) and over graphs $\Gamma$:
\[
 m_k = \sum_\Gamma \sum_\alpha
 \biggl(\int_{\FM_{|V_{\mathrm{int}}|}(\C)}
 \omega_{\Gamma,\alpha}^{\mathrm{hol}}\biggr)
 \;\otimes\;
 \biggl(\int_{\R^{|V_{\mathrm{int}}|}}
 \omega_{\Gamma,\alpha}^{\mathrm{top}}\biggr).
\]

\emph{Form identification.} It remains to verify that the integrated factors have the correct form type:
\begin{itemize}
\item \emph{Holomorphic factor.} The integrated holomorphic weight is a meromorphic form of the external coordinates $z_1, \ldots, z_k$, with at-worst-simple logarithmic poles along each collision divisor $\{z_i = z_j\}$, inherited from the holomorphic kernels in the factorized parametrix. On $\FM_k(\C)$, the standard local model $dz_{ij}/z_{ij} = d\log(z_{ij})$ extends to a section of $\Omega^1_{\log}(\FM_k(\C))$ at the boundary divisor $D_{\{i,j\}}$. Products and residues of such forms remain logarithmic (the algebra $\Omega^\bullet_{\log}$ is closed under wedge product). Hence the integrated weight is $\omega_k^{\mathrm{hol}} \in \Omega^\bullet_{\log}(\FM_k(\C))$.

\item \emph{Topological factor.} The topological kernels
$H_{\alpha}^{\mathrm{top}}(t_{ij})$ are locally constant or
exponentially decaying distributions on ordered configuration
spaces. In the standard causal normalization they are represented by
Heaviside kernels imposing time-ordering. The integrated topological
weights are therefore chains
$\omega_k^{\mathrm{top}} \in C_\bullet(\Conf_k(\R))$ supported on
ordered strata, which are precisely the $E_1$-operad strata of
$\Conf_k(\R)$.
\end{itemize}
The resulting weight form is
\[
 \omega_k = \omega_k^{\mathrm{hol}} \otimes \omega_k^{\mathrm{top}}
 \;\in\;
 \Omega^\bullet_{\log}(\FM_k(\C)) \otimes C_\bullet(\Conf_k(\R)),
\]
as required by Definition~\ref{def:log-SC-algebra}. \hfill$\diamond$

\medskip
\noindent\textbf{Summary of hypotheses.}
Each item of the theorem statement enters exactly once:
\begin{enumerate}[label=(\alph*)]
\item \emph{BV data and product HT gauge fixing} provides the
BRST complex and the product-formal kinetic presentation. The
condition $Q^2=0$ ensures $m_1^2=0$.
\item \emph{Factorized parametrix} provides the finite tensor
decomposition of the singular propagator used in Step~(i). This
factorization is a hypothesis, not a consequence of merely writing
$Q=\dbar_z+d_t$.
\item \emph{One-loop finiteness} provides absolute convergence of
the Feynman integrals after FM compactification, which is the
analytic hypothesis of Fubini's theorem (Step~(iv)). Without it, the
integrals may diverge, and the factorisation of integrated weight
forms would be formal rather than analytic.
\item \emph{Product-polynomial interactions} ensure each vertex
factor is a \emph{finite} sum of pure tensors (Step~(ii)). A
non-polynomial interaction could produce an infinite series whose
convergence entangles the $\C$- and $\R$-variables, obstructing the
tensor-product decomposition at the integrand level.
\end{enumerate}

\textbf{$\SCchtop$ structure.} By the local-shadow theorem
(Theorem~\ref{thm:recognition-SC}), the product-formal
prefactorisation algebra on $\C \times \R$ whose weight forms factor
as above has a local $C_\ast(W(\SCchtop))$-algebra shadow. The
factorisation established in Steps~(i)--(iv) therefore identifies
$\Obs_{\mathrm{bulk}}$ as a logarithmic $\SCchtop$-algebra in the
sense of Definition~\ref{def:log-SC-algebra}.
\end{proof}

\begin{example}[Free Chiral Multiplet Propagator]
\label{ex:free_propagator}
For the free chiral multiplet $\Phi$ with action
\[
S_{\mathrm{free}} = \int_{\R \times \C} \bar{\Phi} \wedge (\partial_t + \bar{\partial}) \Phi,
\]
the singular parametrix is modeled by
$K_{\mathrm{sing}} = \delta(t_1 - t_2)/(2\pi(z_1-z_2))$, with the
smooth $Q$-exact correction understood as in
Theorem~\ref{thm:physics-bridge}. This exhibits the product
decomposition of the singular part: meromorphic in $z$ with a simple
pole, distributional in the topological direction, and
translation-invariant.
\end{example}

\begin{remark}[Physical realisations]
\label{rem:physical-realisations}
Theorem~\ref{thm:physics-bridge} applies to holomorphic twists of
3d $\mathcal{N}=2$ theories~\cite{CDG20} and to HT theories with
$d'=1$~\cite{GRW21, GKW25} after the factorized logarithmic
parametrix required in item~\textup{(b)} has been supplied. The worked
examples of Part~\textup{IV} record these gauge choices explicitly.
\end{remark}

\subsubsection*{II. Chain-level structure (Section \ref{sec:BV_construction})}

\begin{theorem}[Chain-level $A_\infty$ chiral structure; \ClaimStatusProvedHere]
\label{thm:chain_level_structure}
Let $(\cA_{\mathrm{ch}}, \cA_{\mathrm{top}})$ be a logarithmic $\SCchtop$-algebra. Then $\cA_{\mathrm{ch}}$, equipped with operations $m_k$ from integration of weight forms over $\Conf_k(\R) \times \FM_k(\C)$, is an $A_\infty$ chiral algebra. The $A_\infty$ relations follow from Stokes' theorem on $\FM_k(\C)$ with corner cancellation via Arnold--Orlik--Solomon (Theorem~\ref{thm:stokes_arnold}).
\end{theorem}

\begin{proof}
This is a direct consequence of Theorem~\ref{thm:stokes_arnold} (Section~\ref{sec:BV_construction}). That theorem proves that for any family of logarithmic weight forms $\{\omega_k\}$ on $\FM_k(\C)$ satisfying interior closedness, boundary factorisation, and Arnold corner cancellation (all of which hold for a logarithmic $\SCchtop$-algebra by Theorem~\ref{thm:FM-calculus}), the operations $m_k$ defined by integration satisfy the $A_\infty$ identities. The proof proceeds by Stokes' theorem on the FM compactification (Step~1), residue-to-composition identification at codimension-$1$ boundaries (Step~2), Koszul sign verification (Step~3), and codimension-$2$ corner cancellation via Arnold relations (Step~5).
\end{proof}

\subsubsection*{III. PVA descent (Section \ref{sec:PVA_descent})}

\begin{theorem}[PVA descent; \ClaimStatusProvedHere]
\label{thm:PVA-descent-roadmap}
For any logarithmic $\SCchtop$-algebra, $H^\bullet(\cA_{\mathrm{ch}},Q)$ is a $(-1)$-shifted Poisson vertex algebra: the $\lambda$-bracket descends from $m_2$, and $m_{k \geq 3}$ vanish on cohomology via homotopies $h_{k-1}$ from topological contraction of $\Conf_k^{<}(\R)$ (Theorem~\ref{thm:cohomology_PVA}).
\end{theorem}

\begin{proof}
This is Theorem~\ref{thm:cohomology_PVA} (Section~\ref{sec:PVA_descent}), proved in full there. The argument decomposes as: (i)~descent of $\mu$ and $\{-{}_\lambda-\}$ to cohomology via the regular/singular splitting of $m_2$; (ii)~verification of the PVA axioms (sesquilinearity, shifted skew-symmetry, Jacobi, Leibniz) for the descended operations, with the $(-1)$-shift arising from the desuspension in the bar complex; and (iii)~vanishing of $m_{k \ge 3}$ on cohomology (Proposition~\ref{prop:m3_vanish}), using the contractibility of $\Conf_k^{<}(\R)$ to construct explicit nullhomotopies.
\end{proof}

\subsubsection*{IV. Chiral Hochschild and bar--cobar duality (Sections \ref{sec:chiral_hochschild_expanded}--\ref{sec:bar_cobar})}

\begin{theorem}[Bulk as chiral Hochschild; \ClaimStatusConditional]
\label{thm:bulk-hochschild-roadmap}
$C^\bullet_{\mathrm{ch}}(A_\partial) \simeq \A_{\text{bulk}}$ as $A_\infty$ chiral algebras (Theorem~\ref{thm:bulk_hochschild}). The filtered bar--cobar adjunction extending~\cite{GLZ22} has differential $d_{\overline{B}}$ from FM residue sums with $d_{\overline{B}}^2 = 0$ by Arnold relations (Theorem~\ref{thm:bar_cobar_adjunction}).
\end{theorem}

\begin{proof}
The two claims are proved in separate later sections.

The bulk--Hochschild identification is Theorem~\ref{thm:bulk_hochschild} (Section~\ref{sec:chiral_hochschild_expanded}), proved via: (1)~reduction of factorization homology along $\R$ using local constancy of observables in the topological direction; (2)~identification of the resulting complex on $\C$ with chiral Hochschild cochains via the holomorphic weight filtration on the Ran space; (3)~matching of the bulk differential $d_{\mathrm{bulk}}$ with the chiral Hochschild differential $\delta_Q + \delta_{\mathrm{Hoch}}$; and (4)~filtered quasi-isomorphism verification. See Remark~\ref{rem:bulk-hochschild-scope} for the precise scope.

The bar--cobar adjunction is Theorem~\ref{thm:bar_cobar_adjunction} (Section~\ref{sec:bar_cobar}), proved by applying the operadic bar--cobar formalism to the two-coloured HT operad $\OHT = C_\ast(W(\SCchtop))$, with conilpotence ensured by tree-complexity and pole-order filtrations, and the Maurer--Cartan equation verified in the convolution dg Lie algebra.
\end{proof}

\phantomsection\label{sec:bridge-inputs-summary}

\subsection{The $d'=1$ formality gap}

Let $d'$ denote the number of topological directions. The Gaiotto--Kulp--Wu formality theorem \cite{GKW25} establishes:

\begin{itemize}
\item \textbf{$d' \geq 2$}: Higher $A_\infty$ operations beyond $m_2$ stabilize: quantum corrections vanish after one loop and the theory is formal.

\item \textbf{$d' = 1$}: Formality fails. Higher $A_\infty$ operations $m_k$ can persist at all loop orders.
\end{itemize}

Three-dimensional HT theories on $\R \times \C$ have $d'=1$. When and why higher operations vanish in this setting remains open.

\subsection{Organization}

Section~\ref{sec:HT-operad} constructs the HT operad $\OHT$ and defines $A_\infty$ chiral algebras.
Section~\ref{sec:BV_construction} derives the chain-level $A_\infty$ structure from BV quantization.
Section~\ref{sec:FM_calculus} develops FM boundary calculus, proving the $A_\infty$ relations via Stokes' theorem.
Section~\ref{sec:PVA_descent} establishes cohomological descent to PVAs.
Section~\ref{sec:chiral_hochschild_expanded} relates bulk observables to chiral Hochschild cochains.
Section~\ref{sec:bar_cobar} develops the filtered chiral bar--cobar adjunction.
Section~\ref{sec:examples} presents three worked examples.
Appendix~\ref{app:FM_Stokes} proves orientation conventions, residue formulas, and Arnold relations.

\subsection{Relation to Prior Work}

This manuscript proves foundational results for structures appearing in the physics literature:

\begin{itemize}
\item \textbf{Costello--Gwilliam \cite{CG17}}: Factorization algebras and BV quantization supply the framework; we extract the $A_\infty$ chiral structure implicit in their constructions.

\item \textbf{Costello--Dimofte--Gaiotto \cite{CDG20}}: Boundary chiral algebras and bulk PVAs are constructed physically; proofs and the chain-level $A_\infty$ structure appear here.

\item \textbf{Khan--Zeng \cite{KZ25}}: PVA axioms and the 3d HT Poisson sigma model supply explicit formulas; we derive the $\lambda$-Jacobi identity from $A_\infty$ relations.

\item \textbf{Gaiotto--Kulp--Wu \cite{GKW25}}: Higher operations and configuration space techniques; we complete the proofs via FM calculus.

\item \textbf{Gui--Li--Zeng \cite{GLZ22}}: Quadratic chiral duality is our benchmark; we extend to the non-quadratic $A_\infty$ setting.

\item \textbf{Tamarkin \cite{Tam02}}: Chiral Hochschild theory and $*$-Lie deformations provide the algebraic framework; we give a geometric realization in the HT context.
\end{itemize}

\subsection{Raviolo as time-slice shadow of universal holography}
\label{subsec:raviolo-holography-anchor}

\begin{remark}[Raviolo restriction in the universal-holography master]
\label{rem:raviolo-holography-anchor}%
\index{raviolo!universal-holography anchor}%
The raviolo restriction
$\sV_{\mathrm{rav}} = (A_{\mathsf{ch}}(D \times I)) / \sim$
of Definition~\ref{def:raviolo-restriction} is the time-slice
shadow of the universal-holography master theorem
(Theorem~\ref{thm:universal-holography-master}). For an algebra
$\cA$ with conformal vector at non-critical level, the canonical
3d HT theory $T_\cA$ on $X \times \R$ has time-slice observables
on each $X \times \{t_0\}$ that, after the contractible
$\Eone$-collapse along $\R$, recover the boundary chiral algebra
$\cA = \Obs^\partial(T_\cA)$ as a raviolo vertex algebra in the
sense of Garner--Williams. The bulk observables
$\Obs^{\mathrm{bulk}}(T_\cA) \simeq \cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$
are computed via factorization homology along $\R$; the raviolo
restriction extracts the $\C$-direction shadow at fixed time,
retaining the chiral product (closed colour) and discarding the
open colour through the $\Eone$ contractibility identification.

The raviolo apparatus assembled here (the time-slice
restriction, \S\ref{subsec:raviolo-time-slices}; the PVA descent
on cohomology, Theorem~\ref{thm:raviolo-PVA}; the bridge from
physics to algebra, Theorem~\ref{thm:physics-bridge}; the
chain-level $A_\infty$ chiral structure,
Theorem~\ref{thm:chain_level_structure}; the bulk-as-chiral-Hochschild
identification, Theorem~\ref{thm:bulk-hochschild-roadmap}) is
the family-by-family verification machinery for the rung corollaries
(Corollaries~\ref{cor:rung-heisenberg}, \ref{cor:rung-affine-km},
\ref{cor:rung-virasoro}, \ref{cor:rung-w-N}, \ref{cor:rung-w-infty})
of the master theorem. Each rung specialises the present apparatus
to a particular family ($\cA = \cH_k$, $V_k(\fg)$, $\mathrm{Vir}_c$,
$\cW_N$, $\cW_\infty$); each preserves the log-$\SCchtop$
hypothesis (G/L/C lineages directly; class M via the
Drinfeld--Sokolov/Hochschild compatibility bridge,
Theorem~\ref{thm:chd-ds-hochschild}).

The directional $\SCchtop \neq E_3$ distinction is enforced by the
raviolo restriction itself: the time-slice raviolo is a vertex
algebra (closed colour), not an $E_3$-topological algebra; the
$E_3$-topological structure on the bulk arises via topologization
\emph{after} the raviolo restriction, when the conformal vector
acts via Sugawara on the bulk derived center.
\end{remark}

\subsection{Acknowledgments}

This work is informed by conversations with Kevin Terng and draws on talks by Davide Gaiotto.
