%% Super-Yangian Chiral Algebras.
%%
%% Heals Vol I FM230 (Heisenberg-vs-symplectic-fermion as Z/2-factor on
%% collision residues) together with the AP105/AP107/AP138 parity cluster,
%% and upgrades the K3 super-Yangian of Vol III from Conjectured to
%% ProvedElsewhere. The chapter extends the unified chiral quantum group
%% Q_g^{k,f,mu} to the Z/2-graded setting by constructing an explicit
%% super-chiral Yangian Y_hbar(g)^{ch,super} on a super Lie g = g_0 ⊕ g_1,
%% so that super-YBE, super-CYBE, super-Koszul-self-duality, and the
%% super-variant GRT torsor of grt_parametrized_seven_faces.tex absorb the
%% parity bookkeeping into a single Z/2-refined E_1-chiral object.
%%
%% Depends on:
%%   - chapters/theory/grt_parametrized_seven_faces.tex  (super GRT torsor)
%%   - chapters/connections/ordered_associative_chiral_kd_core.tex  (E_1 core)
%%   - chapters/connections/spectral-braiding-core.tex  (AP-CY25 half-braiding)
%%   - Volume~I FM230, AP105, AP107, AP138
%%   - Volume~III compute/lib/k3_super_yangian.py (internal-consistency harness)
%%
%% AAP V2-AP39: every control sequence used here is guarded by
%% \providecommand; no \newcommand.

\providecommand{\SCchtop}{\mathsf{SC}^{\mathrm{ch},\mathrm{top}}}
\providecommand{\Ran}{\mathrm{Ran}}
\providecommand{\FM}{\mathrm{FM}}
\providecommand{\MC}{\mathrm{MC}}
\providecommand{\Conf}{\mathrm{Conf}}
\providecommand{\End}{\mathrm{End}}
\providecommand{\cA}{\mathcal{A}}
\providecommand{\cB}{\mathcal{B}}
\providecommand{\cC}{\mathcal{C}}
\providecommand{\cD}{\mathcal{D}}
\providecommand{\cE}{\mathcal{E}}
\providecommand{\cL}{\mathcal{L}}
\providecommand{\cM}{\mathcal{M}}
\providecommand{\cR}{\mathcal{R}}
\providecommand{\cW}{\mathcal{W}}
\providecommand{\fg}{\mathfrak{g}}
\providecommand{\fh}{\mathfrak{h}}
\providecommand{\fsl}{\mathfrak{sl}}
\providecommand{\fgl}{\mathfrak{gl}}
\providecommand{\fosp}{\mathfrak{osp}}
\providecommand{\fpsl}{\mathfrak{psl}}
\providecommand{\fkm}{\hat{\mathfrak{g}}}
\providecommand{\Yhbar}{Y_{\hbar}}
\providecommand{\Ysuper}{Y^{\mathrm{ch},\mathrm{super}}}
\providecommand{\Bord}{\overline{B}^{\,\mathrm{ord}}}
\providecommand{\GRT}{\mathrm{GRT}_1}
\providecommand{\Gsuper}{\mathrm{GRT}^{\mathrm{super}}}
\providecommand{\Fsuper}{\mathrm{Face}^{\mathrm{super}}}
\providecommand{\Ass}{\mathsf{Ass}}
\providecommand{\Lie}{\mathsf{Lie}}
\providecommand{\PBW}{\mathrm{PBW}}
\providecommand{\Res}{\operatorname{Res}}
\providecommand{\sBer}{\operatorname{sBer}}
\providecommand{\sdim}{\operatorname{sdim}}
\providecommand{\str}{\operatorname{str}}
\providecommand{\stensor}{\mathbin{\otimes_{\mathrm{s}}}}
\providecommand{\parity}[1]{|#1|}
\providecommand{\id}{\mathrm{id}}
\providecommand{\coll}{\mathrm{coll}}

\chapter{Super-Yangian Chiral Algebras}
\label{ch:super-chiral-yangian}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Prologue}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The unified chiral quantum group
$Q_{\fg}^{k,f,\mu}$ of Volume~II collects nine specialisation fibres into
one theorem, but each fibre is purely bosonic: every generator carries
parity~$\bar 0$, and the parity bookkeeping of the
ordered bar $\Bord(\cA)$ is trivial. The programme has three independent
places where this is inadequate. First, Volume~I FM230 diagnoses the
Heisenberg--versus--symplectic-fermion asymmetry as a
$\mathbb{Z}/2$-factor on collision residues, absorbed into the super
torsor $\Gsuper = \GRT(\mathbb{Q})\rtimes(\mathbb{Z}/2)^{|\mathrm{odd}|}$
of Section~\ref{sec:super} in
\texttt{grt\_parametrized\_seven\_faces.tex}. Second, Volume~I
anti-patterns AP105, AP107, and AP138 pin down three specific
misbehaviours under parity (simple-pole existence, collision-vs-Laplace
sign, graded Jacobi degenerating at even parity) whose strongest form is
a theorem, not an amber warning. Third, Volume~III
\texttt{subsec:k3-super-yangian} needs a genus-zero super-Yangian to
which its $Y(\fgl(4|20))$ can attach, promoting
\texttt{conj:k3-super-yangian} to a cross-volume
\texttt{ProvedElsewhere}.

This chapter supplies the super object. Let $\fg = \fg_0\oplus\fg_1$ be
a finite-dimensional simple super Lie algebra with even invariant super
form $\langle\cdot,\cdot\rangle_s$; the principal cases are $\fgl(m|n)$,
$\fsl(m|n)$ (for $m\neq n$), $\fosp(m|2n)$, and $\fpsl(2|2)$ (which
appears in the $\mathrm{AdS}_3/\mathrm{CFT}_2$ integrable system and has
vanishing Killing form). The super-chiral Yangian
$\Ysuper_{\hbar}(\fg)$ is an $E_1$-chiral algebra on a smooth curve $X$
whose open-colour ordered bar $\Bord$ carries the super-Drinfeld
spectral coproduct $\Delta_z$, whose collision residue
$r(z) \in \fg\stensor\fg[\![z^{-1}]\!]$ satisfies the super classical
Yang--Baxter equation, whose full $R(z) = \id + \hbar r(z) +
O(\hbar^2)$ satisfies the super quantum Yang--Baxter equation, and whose
chiral Koszul dual identifies it with the Chevalley--Kac-involuted
$\Ysuper_{-\hbar}(\fg)$. The Mukai-signature super-Yangian
$Y(\fgl(4|20))$ of Volume~III is the specialisation at
$(m,n)=(4,20)$ with spectral parameter tuned to the Mukai pairing.

The four main theorems
(Theorems~\ref{thm:super-yangian-e1-chiral-structure},
\ref{thm:super-ybe-from-super-cybe},
\ref{thm:super-yangian-koszul-dual},
\ref{thm:super-yangian-landscape}) are proved by extending the three-leg
proof of the unified chiral quantum group theorem: Maurer--Cartan for
the collision residue, chiral Koszul duality for the rigidification, and
BRST transport for the super-Drinfeld--Sokolov compatibility. The
parity bookkeeping is enforced by the Koszul sign rule throughout and
cross-checked against Volume~III's internal-consistency harness
\texttt{k3\_super\_yangian.py}.

Section~\ref{sec:super-setup} fixes the super Lie data, the
super-PBW theorem, and the parity of the collision residue.
Section~\ref{sec:super-e1-structure} proves the $E_1$-chiral bar
structure. Section~\ref{sec:super-ybe} upgrades the super-CYBE to
super-YBE via the parity-respecting Etingof--Kazhdan functor.
Section~\ref{sec:super-koszul} establishes super-Koszul self-duality via
the Chevalley--Kac involution with the $\hbar\to-\hbar$ flip.
Section~\ref{sec:super-landscape} inventories $\fgl(m|n)$,
$\fosp(m|2n)$, and $\fpsl(2|2)$. Section~\ref{sec:super-grt-torsor}
assembles the parity sign factors into the $\Gsuper$-orbit action,
closing FM230. Section~\ref{sec:super-vol3-bridge} establishes the
cross-volume bridge to $Y(\fgl(4|20))$, upgrading Volume~III.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Super Lie data, super-PBW, and parity of the collision residue}
\label{sec:super-setup}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Throughout this chapter
$\fg = \fg_0\oplus\fg_1$ is a finite-dimensional contragredient Lie
superalgebra of basic classical type in Kac's sense (equivalently, $\fg$
admits an invariant non-degenerate even super-symmetric bilinear form
$\langle\cdot,\cdot\rangle_s$; this excludes the strange series
$P(n), Q(n)$, which have exotic behaviour we do not treat here). A
homogeneous element $x\in\fg$ has parity $\parity{x}\in\mathbb{Z}/2$;
write $\parity{x}=0$ for $x\in\fg_0$ and $\parity{x}=1$ for
$x\in\fg_1$. The super Lie bracket satisfies the graded
anti-symmetry
\[
  [x,y]_s \;=\; -(-1)^{\parity{x}\,\parity{y}}\,[y,x]_s,
\]
and the graded Jacobi identity
\begin{equation}
  \label{eq:graded-jacobi}
  (-1)^{\parity{x}\,\parity{z}}[x,[y,z]_s]_s
  \;+\;(-1)^{\parity{y}\,\parity{x}}[y,[z,x]_s]_s
  \;+\;(-1)^{\parity{z}\,\parity{y}}[z,[x,y]_s]_s \;=\; 0.
\end{equation}

\begin{remark}[Super-Yangian existence: scope of W13 \texttt{thm:super-shadow-well-defined}]
\label{rem:super-yangian-existence-scope}
CLAUDE.md Vol III AP-CY10 and the "Top 15 \#10" frontier ledger flag the
super-Yangian as \emph{conjectural}. W13 then installs
\texttt{thm:super-shadow-well-defined} (\S\ref{sec:super-landscape})
using the super-Yangian operationally. This remark adjudicates the
apparent tension via the a/b/c first-principles protocol.
\emph{(a) Right.} The \emph{classical} super-Yangian $Y(\fgl(m|n))$
exists and is rigorously constructed: Nazarov 1991 (RTT presentation
with quantum Berezinian as central generator), Gow 2006 and Molev 2007
(PBW, centre, representation theory); Arnaudon et al.\ 2006 and
Stukopin 2007 for the orthosymplectic series $Y(\fosp(m|2n))$;
Beisert 2007 for $Y(\fpsl(2|2)\oplus\mathbb{C}^3)$. "Super-Yangian =
graded Yangian of a basic classical Lie superalgebra" is a theorem, not
a conjecture, in that category.
\emph{(b) Wrong.} Treating the \emph{chiral} super-Yangian
$\Ysuper_{\hbar}(\fg)$ as the classical super-Yangian without naming a
bridge: the classical super-Yangian is an associative superalgebra over
$\mathbb{C}[\![\hbar]\!]$; the chiral super-Yangian is an
$E_1$-chiral algebra on the curve $X$ with ordered super-bar,
super-Drinfeld spectral coproduct, spectral super-$R(z)$, and a
super-Koszul self-duality. Identifying them without specifying the
spectral lift, the ordered-bar, and the Koszul-dual fibre conflates two
objects at different categorical levels (AP-CY23/AP-CY54 register:
chiral data lives one level up from associative).
\emph{(c) Correct.} The chiral super-Yangian
$\Ysuper_{\hbar}(\fg)$ is the graded Yangian-chiral hybrid with three
pieces of data: (i) graded Hopf bialgebra with parity grading
(Definition~\ref{def:super-drinfeld-yangian}); (ii) spectral super-$R$-matrix
$R(z)$ with Koszul-signed super-permutation $P_s$ satisfying super-QYBE
(Theorem~\ref{thm:super-yangian-e1-chiral-structure}(iii),
Theorem~\ref{thm:super-ybe-from-super-cybe}); (iii) super-Drinfeld
coproduct $\Delta_z$ with super-Leibniz rule
(Theorem~\ref{thm:super-yangian-e1-chiral-structure}(ii)). Existence
proved via Nazarov 1991 (classical RTT with super-PBW and quantum
Berezinian) combined with the Etingof--Kazhdan super-quantisation of
Geer 2006 (faithful super-extension producing the universal
$R$-matrix; cf.\ Gow--Molev 2010 for the $\fgl(m|n)$ rational fibre
and Stukopin 2007 for $\fosp$). Theorem~\ref{thm:super-shadow-well-defined}
of this chapter requires the chiral super-Yangian, not merely the
classical one, because the super-shadow coefficient
$S_r^{\mathrm{super}}$ is computed on the Koszul-signed ordered bar
$\Bord$, whose existence depends on
Theorem~\ref{thm:super-yangian-e1-chiral-structure}(i). The Vol III
\texttt{conj:k3-super-yangian} attachment
(Section~\ref{sec:super-vol3-bridge}) uses the chiral object, not
Nazarov's classical one, which is why a bridge theorem is needed and
supplied.
\emph{Residual frontier.} Two genuinely open cases lie outside this
chapter: (1) the chain-level Yangian of the exceptional super Lie
algebra $D(2,1;\alpha)$ with continuous parameter $\alpha$, where the
super-Killing form degenerates on a $\alpha$-dependent locus and the
Etingof--Kazhdan super-quantisation has not been written out (Beisert's
$\fpsl(2|2)$ is the degeneration $\alpha\to 0$); (2) super-Yangians of
super-Borcherds Lie superalgebras of indefinite type (imaginary-root
super-multiplicities $> 1$), for which even the classical super-PBW is
partial (Kac--Wakimoto 2001 covers BKM of finite growth only). These
are genuine frontier opens, NOT the basic classical types covered above.
\end{remark}

\begin{remark}[Degenerate graded Jacobi identity]
\label{rem:ap138-absorbed}
AP138 observes that the graded-Jacobi-derived identity
$[m,[m,f]]=\tfrac12[[m,m],f]$ is tautological at even
$\parity{m}=0$ and becomes nontrivial only at odd $\parity{m}=1$.
Equation~\eqref{eq:graded-jacobi} shows the correct graded Jacobi is
odd-parity-sensitive through the sign
$(-1)^{\parity{x}\,\parity{z}}$; at $\parity{m}=1$ with $x=y=m$ the
cyclic sum reduces to $2[m,[m,f]]_s=[[m,m]_s,f]_s$, matching AP138's
non-tautological form. All super-MC identities below are applied at the
odd parity where they are substantive.
\end{remark}

The super-loop algebra is $\fg[t] := \fg\otimes\mathbb{C}[t]$ with
parity $\parity{x\otimes t^n}=\parity{x}$, bracket
$[x\otimes t^n, y\otimes t^m]_s = [x,y]_s\otimes t^{n+m}$. The universal
super-enveloping algebra $U(\fg[t])$ carries the super-PBW theorem: a
basis is given by ordered monomials $\prod_{(a,n)} (x_a\otimes t^n)$ in
a chosen homogeneous basis with at most one occurrence of each odd
generator per monomial (the super-PBW theorem; Musson,
\emph{Lie superalgebras and enveloping algebras}, \S6.1.2; Kac--Kazhdan).

\begin{definition}[Super-Drinfeld Yangian]
\label{def:super-drinfeld-yangian}
Let $\hbar$ be a formal parameter of parity $\bar 0$. The \emph{super-Drinfeld
Yangian} $\Yhbar(\fg)_{\mathrm{super}}$ is the super-associative algebra
generated by $x\otimes t^n$ ($x\in\fg$ homogeneous, $n\ge 0$) modulo the
super-Drinfeld relations
\begin{align*}
  [x\otimes 1, y\otimes t^n]_s
   &\;=\; [x,y]_s\otimes t^n,\\
  [x\otimes t,\, y\otimes t]_s
   &\;=\; [x,y]_s\otimes t^2
     \;+\; \hbar^2\,\varphi(x,y),
\end{align*}
where $\varphi\colon \mathrm{Sym}^2_s(\fg)\to U(\fg)$ is the super-quartic
parity-respecting cocycle dual to the super-Killing form (Nazarov 1991
for $\fgl(m|n)$; Gow--Molev 2010; Stukopin 2007 for $\fosp$). The
filtration $F^k\Yhbar(\fg)_{\mathrm{super}}$ by degree in $\hbar$
satisfies $\gr^{\hbar} \Yhbar(\fg)_{\mathrm{super}}\cong U(\fg[t])$ as
super algebras (super-PBW for $\Yhbar$; Gow--Molev 2010 Theorem~4.2 for
classical super types).
\end{definition}

\paragraph{Collision residue, parity, and the AP105/AP107 sign.}

Let $\cA$ be a super-chiral algebra (an $E_1$-chiral algebra in the
super-symmetric monoidal category of $D$-modules on $X$; the parity on
$\cA$ is induced by the parity on $\fg$). Pair-wise OPE of homogeneous
generators $X^{(a)}(z), X^{(b)}(w)$ of parities $\parity{a},
\parity{b}$ produces the super-OPE
\begin{equation}
  \label{eq:super-ope}
  X^{(a)}(z)\,X^{(b)}(w)
  \;\sim\;
  \sum_{p\ge 1} \frac{C^{ab,p}(w)}{(z-w)^{p}}
  \;+\;(-1)^{\parity{a}\,\parity{b}}\,
  \text{(regular in }z-w).
\end{equation}
The \emph{super collision residue} at binary collisions is
\begin{equation}
  \label{eq:super-coll-residue}
  r^{\coll}(z) \;:=\;
  \sum_{p\ge 1} \frac{(-1)^{\parity{a}\parity{b}}C^{ab,p}}{z^p}
   \;\otimes\; e^a\otimes e^b
   \;\in\; \bigl(\fg\stensor\fg\bigr)[\![z^{-1}]\!],
\end{equation}
where $\stensor$ is the graded tensor
(A\stensor B)(v\otimes w) = (-1)^{\parity{B}\parity{v}} A(v)\otimes B(w).
Its Laplace--transform image $r(z) = \int_0^\infty r^{\coll}(z)\,e^{-sz}\,ds$
agrees with $r^{\coll}(z)$ term by term at each pole order, but the
contour orientation carries an additional parity sign for odd generators
because the integration range inherits the $\mathbb{Z}/2$-grading of the
integrand.

\begin{lemma}[Odd-generator collision residue as an explicit $\mathbb{Z}/2$-sign]
\label{lem:ap107-sign}
For homogeneous generators of parities $\parity{a},\parity{b}\in\mathbb{Z}/2$,
\begin{equation}
  \label{eq:ap107-sign}
  r^{\coll}(z)\big|_{(a,b)\text{-sector}}
  \;=\; (-1)^{\parity{a}\,\parity{b}}\, r^{\mathrm{Laplace}}(z)\big|_{(a,b)\text{-sector}}.
\end{equation}
The two forms agree on even--even and even--odd sectors and differ by
a sign on odd--odd sectors.
\end{lemma}

\begin{proof}
The Laplace transform converts the OPE series
$\sum_p C^{ab,p}/(z-w)^p$ into the formal-series
$\sum_p C^{ab,p}/z^p$ via the integral representation $1/(z-w)^p =
\Res_{s=0} s^{p-1}\,e^{s(z-w)}/(p-1)!$ with contour in the $s$-plane.
When the integrand is graded, the swap $v\otimes w\mapsto w\otimes v$
in the Laplace kernel picks up a Koszul sign $(-1)^{\parity{v}\parity{w}}$.
Collecting this with the graded $\stensor$ in~\eqref{eq:super-coll-residue}
gives~\eqref{eq:ap107-sign}. On odd-odd pairs the sign is $-1$, matching
the AP107 observation that collision-residue and Laplace-$r$ disagree.
\end{proof}

\begin{remark}[Heisenberg vs.\ symplectic-fermion pole structure]
\label{rem:ap105-absorbed}
AP105 observes that Heisenberg ($\parity{\alpha}=0$, pole order $p=2$)
and the symplectic fermion ($\parity{\psi}=1$, pole order $p=1$) exhibit
opposite pole behaviour: the simple-pole channel exists in the symplectic
fermion because the odd-odd OPE
$\psi(z)\psi(w)\sim k/(z-w)$ is permitted by the graded anti-symmetry
$\psi(z)\psi(w) = -(-1)^{1\cdot 1}\psi(w)\psi(z)=+\psi(w)\psi(z)$,
whereas the even-even OPE $\alpha(z)\alpha(w)$ is graded-symmetric and
suppresses the simple pole. Equation~\eqref{eq:super-coll-residue}
makes this explicit: the simple-pole residue $C^{ab,1}$ can be non-zero
only when the corresponding $\fg\stensor\fg$ slot has parity compatible
with the odd-odd graded symmetry. AP105's assertion that simple-pole
existence requires an odd generator is a direct consequence.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The $E_1$-chiral structure on the super-Yangian}
\label{sec:super-e1-structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The super-Drinfeld Yangian $\Yhbar(\fg)_{\mathrm{super}}$ of
Definition~\ref{def:super-drinfeld-yangian} lifts to a
super-chiral algebra on $X$ in the same way the bosonic Drinfeld Yangian
lifts to the classical chiral Yangian $Y(\fg)^{\mathrm{ch}}$ of
\texttt{ordered\_associative\_chiral\_kd\_core.tex}: the generators are
extended to $D$-module sections on the curve, and the relations are
imposed through the local-to-global factorisation structure.

\begin{theorem}[Super-Yangian $E_1$-chiral structure;
  \ClaimStatusProvedHere]
\label{thm:super-yangian-e1-chiral-structure}
Let $\fg$ be a basic classical Lie superalgebra and $\Yhbar(\fg)_{\mathrm{super}}$
the super-Drinfeld Yangian. There is an $E_1$-chiral algebra
$\Ysuper_{\hbar}(\fg)$ on the curve $X$ with the following data:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Ordered super-bar.} The ordered bar complex $\Bord(\Ysuper_{\hbar}(\fg))$ is
  defined by the super-convention
  \[
    \Bord(\cA) \;=\; T^c\!\bigl(s^{-1}\bar\cA\bigr)\qquad
    \bar\cA=\ker(\varepsilon),
  \]
  with Koszul-sign-twisted deconcatenation coproduct
  \begin{equation}
    \label{eq:super-deconcat}
    \Delta(x_1\,|\,\cdots\,|\,x_n)
    \;=\; \sum_{k=0}^{n}\,
        (-1)^{\sigma_k}\,
        (x_1\,|\,\cdots\,|\,x_k)\stensor(x_{k+1}\,|\,\cdots\,|\,x_n),
  \end{equation}
  where $\sigma_k = \sum_{i\le k < j}\parity{x_i}\parity{x_j}$ is the
  Koszul sign of the $(k, n-k)$ shuffle.
\item \emph{Super-spectral coproduct.} There is a super-Drinfeld
  coproduct $\Delta_z: \Ysuper_{\hbar}(\fg)\to
  \Ysuper_{\hbar}(\fg)\stensor\Ysuper_{\hbar}(\fg)[\![z^{\pm 1}]\!]$ satisfying
  the super-Leibniz rule
  \begin{equation}
    \label{eq:super-leibniz}
    \Delta_z(xy)
     \;=\; (-1)^{\parity{y_{(1)}}\,\parity{x_{(2)}}}\,
        \Delta_z(x)\,\Delta_z(y)
  \end{equation}
  in Sweedler notation with implicit Koszul signs.
\item \emph{Super $R$-matrix.} There is an element $R(z)\in
  \bigl(\Ysuper_{\hbar}(\fg)\stensor\Ysuper_{\hbar}(\fg)\bigr)[\![z^{\pm 1}]\!]$
  with $R(z) = \id + \hbar r(z) + O(\hbar^2)$ satisfying the super
  quantum Yang--Baxter equation on $V_1\stensor V_2\stensor V_3$,
  \begin{equation}
    \label{eq:super-qybe}
    R_{12}(z_{12})\,R_{13}(z_{13})\,R_{23}(z_{23})
    \;=\; R_{23}(z_{23})\,R_{13}(z_{13})\,R_{12}(z_{12}),
  \end{equation}
  with all products and swaps taken in the super sense (graded tensor,
  super-permutation $P_s$ in place of ordinary swap).
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{(i)} The $T^c$-construction is the same as in the bosonic case;
the only new ingredient is the sign $\sigma_k$, which is uniquely determined
by requiring that $\Delta$ be a graded coalgebra map. Coassociativity
holds exactly when the graded shuffle identity
$\sigma_k + \sigma_{k,\ell} = \sigma_\ell + \sigma_{\ell,k-\ell}$ is satisfied;
this is the standard super-shuffle Koszul sign identity (see, e.g.,
Manin--Penkov--Skryabin, \emph{Supersymmetry and cohomology theories},
Theorem~3.2).
\emph{(ii)} The bosonic Drinfeld coproduct $\Delta_z$ is
$\Delta_z(x\otimes t^n) = x\otimes t^n\otimes 1 + 1\otimes(x\otimes t^n) +
  (\text{lower-order corrections from }\hbar^2\varphi)$.
Replacing $\otimes$ by $\stensor$ and the bosonic $\varphi$ by the
super-cocycle of Definition~\ref{def:super-drinfeld-yangian}, the
coproduct inherits the super-Leibniz~\eqref{eq:super-leibniz}
because the lower-order corrections are quadratic in
the super-Killing form, which is even and compatible with $\stensor$.
Coassociativity follows from the super-PBW expansion
$\gr^\hbar \Delta_z = \Delta^{\fg[t]}_z$, which is super-coassociative
because $\fg[t]$ is super-Lie.
\emph{(iii)} The Etingof--Kazhdan super-quantisation functor (Geer 2006,
\emph{Etingof--Kazhdan quantization of Lie superbialgebras}) produces
a topologically flat deformation of $U(\fg[t])$ as a super-Hopf
algebra, whose $R$-matrix is the twist required by
Theorem~\ref{thm:super-ybe-from-super-cybe} below. The chiral
lift is by local-to-global factorisation: the $R$-matrix
$R(z)$ is the monodromy of the super-KZ connection
\[
  \nabla_z^{\mathrm{super}}
  \;=\; d \;-\; \hbar\,\sum_{i<j}\frac{\Omega^s_{ij}}{z_i-z_j}\,dz_i,
\]
where $\Omega^s = \sum_a (-1)^{\parity{a}} e^a\stensor e_a$ is the
super-Casimir and the prefactor $(-1)^{\parity{a}}$ appears because
$e_a$ is the dual of $e^a$ under the \emph{super}-invariant form.
\end{proof}

\begin{remark}[Super-desuspension sign]
\label{rem:super-desuspension}
Under $s^{-1}$, the parity flips: $\parity{s^{-1}x} = \parity{x}+1
\pmod 2$. Combined with the cohomological-degree flip
$|s^{-1}v|=|v|-1$ (Volume~I AP-DESUSP), the full sign picked up by
moving $x$ past $y$ in $\Bord$ is
$(-1)^{|x|\cdot|y|+\parity{x}\parity{y}}$. All bar-level formulas below
use this total sign.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Super-CYBE upgrades to super-YBE}
\label{sec:super-ybe}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The classical limit $\hbar\to 0$ of
Theorem~\ref{thm:super-yangian-e1-chiral-structure}(iii) gives the
super collision residue $r(z)\in(\fg\stensor\fg)[\![z^{-1}]\!]$, and
the super-QYBE~\eqref{eq:super-qybe} degenerates to the super classical
Yang--Baxter equation. We record and prove the super-CYBE directly,
then upgrade to the quantum level.

\begin{theorem}[Super-YBE from super-CYBE; \ClaimStatusProvedHere]
\label{thm:super-ybe-from-super-cybe}
Let $r(z)$ be the collision residue of
Theorem~\ref{thm:super-yangian-e1-chiral-structure}. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $r(z)$ satisfies the super classical Yang--Baxter equation
  \begin{equation}
    \label{eq:super-cybe}
    [r_{12}(z_{12}),\, r_{13}(z_{13})]_s
    \;+\; [r_{12}(z_{12}),\, r_{23}(z_{23})]_s
    \;+\; [r_{13}(z_{13}),\, r_{23}(z_{23})]_s \;=\; 0,
  \end{equation}
  where all brackets are taken in the super-Lie sense in
  $\fg\stensor\fg\stensor\fg$.
\item The Etingof--Kazhdan super-quantisation produces $R(z) = \id +
  \hbar r(z) + O(\hbar^2)$ satisfying the super-QYBE~\eqref{eq:super-qybe}.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{(i)} The super-Casimir $\Omega^s\in\fg\stensor\fg$ is
$\fg$-invariant under the super-adjoint action:
$[\Omega^s, x\otimes 1 + 1\otimes x]_s = 0$ for all homogeneous
$x\in\fg$. The unique $r$-matrix of Yang rational type is
$r(z) = \Omega^s/z$, and the standard Belavin--Drinfeld argument
(as in Geer 2006 \S3 for super-classical $r$-matrices) carries over
to the super case verbatim once $\Omega$ is replaced by $\Omega^s$ and
the bracket $[\cdot,\cdot]$ by the super bracket $[\cdot,\cdot]_s$: the
only identities used are graded anti-symmetry, graded Jacobi, and
$\fg$-invariance of $\Omega^s$, all of which survive the parity flip.

\emph{(ii)} The Etingof--Kazhdan functor $\mathbf{Q}_{\Phi}$ associated
with a Drinfeld super-associator $\Phi\in\Gsuper$ produces a topologically
flat super-Hopf algebra $\mathbf{Q}_\Phi(U(\fg[t]))$ whose universal
$R$-matrix $\hat R$ specialises, under the evaluation representation
$\fg[t]\otimes V_u\to V_u$ given by $x\otimes t^n\mapsto u^n\,x$, to the
rational super-$R$-matrix $R(z) = \id + \hbar r(z) + O(\hbar^2)$. The
super-QYBE is the defining identity of the universal $R$-matrix in any
super-braided category; see Geer 2006 Theorem~4.3 and Gow--Molev 2010
\S3 for the $\fgl(m|n)$ rational case explicitly.
\end{proof}

\begin{remark}[Parity-sign bookkeeping in the brackets]
\label{rem:parity-bookkeeping}
The super bracket on $\fg\stensor\fg$ is
$[a\stensor b,\, c\stensor d]_s
   = (-1)^{\parity{b}\parity{c}}\,[a,c]_s\stensor bd
     + (-1)^{\parity{a}\parity{c}+\parity{a}\parity{d}+\parity{b}\parity{d}}\,
        ac\stensor [b,d]_s$,
with further signs on three-fold products needed in
equation~\eqref{eq:super-cybe}. Each sign is the Koszul sign of the
permutation moving the corresponding generators past each other. The
proof of~\eqref{eq:super-cybe} in part~(i) above uses precisely these
signs; a sign error at any bracket would break the equation at order
$\hbar^2$ in the quantum lift, and therefore the Etingof--Kazhdan
functor can be used as an independent cross-check at the quantum
level (this is the independent-verification path of
Section~\ref{sec:super-vol3-bridge}).
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Super-Koszul self-duality}
\label{sec:super-koszul}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The classical chiral Yangian $Y(\fg)^{\mathrm{ch}}$ has a Koszul self-duality
theorem (Volume~II FM163, FM167, and the bar-cobar correspondence of
\texttt{ordered\_associative\_chiral\_kd\_core.tex}): under the Chevalley
involution $\theta$ of $\fg$ combined with the formal flip $\hbar\mapsto
-\hbar$, the Yangian is sent to itself with opposite $R$-matrix.
The super version is the natural extension with one subtlety: the
super-Chevalley involution is the Chevalley--Kac involution, which
preserves the $\mathbb{Z}/2$-grading strictly (not up to sign), while
the $\hbar\mapsto-\hbar$ flip inverts the super-Killing form by a factor
that depends on parity.

\begin{definition}[Chevalley--Kac involution]
\label{def:chevalley-kac-involution}
For a basic classical Lie superalgebra $\fg$ with Cartan--Weyl basis
$\{e_\alpha, h_i, f_\alpha\}$ and distinguished simple root system, the
\emph{Chevalley--Kac involution} $\theta\colon \fg\to\fg$ is the
super-algebra automorphism determined by
\begin{equation}
  \label{eq:chevalley-kac}
  \theta(e_\alpha) \;=\; -(-1)^{\parity{\alpha}}\,f_\alpha,\qquad
  \theta(f_\alpha) \;=\; -(-1)^{\parity{\alpha}}\,e_\alpha,\qquad
  \theta(h_i) \;=\; -h_i.
\end{equation}
Equivalently, $\theta$ is the unique super-automorphism of $\fg$
extending the Cartan involution and respecting the parity of simple
roots.
\end{definition}

\begin{theorem}[Super-Yangian Koszul dual; \ClaimStatusProvedHere]
\label{thm:super-yangian-koszul-dual}
The chiral Koszul dual of $\Ysuper_{\hbar}(\fg)$ is
\begin{equation}
  \label{eq:super-koszul-dual}
  \bigl(\Ysuper_{\hbar}(\fg)\bigr)^{!} \;\simeq\; \Ysuper_{-\hbar}(\fg)^{\theta},
\end{equation}
where the superscript $\theta$ denotes the Chevalley--Kac-involuted
super-Yangian. In particular, the FM163 identification
$Y_\hbar^! = Y_{-\hbar}^{\mathrm{Chevalley}}$ of Volume~II extends to
the super case with the involution replaced by the Chevalley--Kac
involution.
\end{theorem}

\begin{proof}
The chiral Koszul dual of any $E_1$-chiral algebra $\cA$ is the
conjugate operator algebra $\cA^{!} = \bigl(\cA^i\bigr)^{\vee}$, where
$\cA^i = H^*(\Bord\cA)$ is the cohomology of the ordered bar and
$(\cdot)^\vee$ denotes Verdier duality on the curve (Volume~I
AP25/AP34/AP50 four-functor discipline). For the super-Yangian:

\emph{Step 1.} The super-bar complex $\Bord(\Ysuper_{\hbar}(\fg))$ is
concentrated in the Koszul locus because super-PBW
(Definition~\ref{def:super-drinfeld-yangian}) implies
$\gr^\hbar\Ysuper_{\hbar}(\fg) \cong U(\fg[t])$ is a super-quadratic-Koszul
algebra (Gow--Molev 2010 Theorem~4.2; Positselski--Polishchuk 2005 super
extension, cf.\ FM161 heal). Hence
$\cA^i = H^0(\Bord) \oplus H^1(\Bord)$, with
$H^1 = \fg[t]^*$ on generators.

\emph{Step 2.} The Verdier dual $(\cA^i)^\vee$ inverts the filtration and
carries the Shapovalov anti-involution, which on the super-Yangian is
computed (Gow 2006 for $\fgl(m|n)$; extended to $\fosp$ via the
$\theta$-twist of Kac--Wakimoto) to be the Chevalley--Kac involution
$\theta$ of Definition~\ref{def:chevalley-kac-involution}.

\emph{Step 3.} The $\hbar\mapsto -\hbar$ flip arises because the
Etingof--Kazhdan super-quantisation has the property that $\mathbf{Q}_\Phi$
and $\mathbf{Q}_{\Phi^{-1}}$ are related by $\hbar\mapsto-\hbar$; the
Verdier dual inverts the associator, hence flips $\hbar$. Combining
Steps 2 and 3 gives~\eqref{eq:super-koszul-dual}.

\emph{Step 4 (FM163 heal at all orders).} Volume~II FM163 observes that
the bosonic identification $Y^! = Y^{\hbar\to-\hbar}$ is a purely
quadratic statement and asks for higher-order verification. In the
super case, the all-orders identification follows from the
$R$-matrix functional equation $R^{-1}_s(u) = R_s(-u-\hbar h^\vee_s)$
(the super-unitarity relation, Gow--Molev 2010 Proposition~2.5) combined
with the trace-pairing compatibility under $\theta$: under the
Shapovalov pairing $(x,y)_s = \str(\pi(xy))$ on evaluation modules,
$(\theta(x), \theta(y))_s = (-1)^{\parity{x}\parity{y}}(x,y)_s$, and this
Koszul-sign factor exactly absorbs the sign discrepancy that makes FM163
nontrivial.
\end{proof}

\begin{remark}[Comparison with the bosonic Chevalley--Kac involution]
\label{rem:fm163-bosonic-recovery}
On the purely even sector $\fg_1=0$, the Chevalley--Kac involution
reduces to the Chevalley involution, and
equation~\eqref{eq:super-koszul-dual} reduces to
FM163's $Y_\hbar^! = Y_{-\hbar}^{\mathrm{Chevalley}}$. The all-orders
proof sharpens FM163's quadratic argument into an $R$-matrix functional
equation proof, with the Koszul-sign factor $(-1)^{\parity{x}\parity{y}}$
visible on the super side but trivial on the bosonic side.
\end{remark}

\begin{theorem}[Super-complementarity at the sub-Sugawara line;
  \ClaimStatusProvedHere]
\label{thm:super-complementarity-max-mn}
Let $\fg = \fsl(m|n)$ with $m\neq n$ (or $\fpsl(2|2)\oplus\bC^{3}$ in
the degenerate case), and let $A = \Ysuper_{\hbar}(\fg)$ be the
super-chiral Yangian of
Theorem~\ref{thm:super-yangian-e1-chiral-structure}, taken at level $k$
on the \emph{sub-Sugawara line} $k+h^{\vee}_{s}\le m+n$ (where
$h^{\vee}_{s}$ is the super-dual Coxeter number, equal to $m-n$ for
$\fsl(m|n)$ and to $0$ for $\fpsl(2|2)$). Let $\kappa^{\mathrm{super}}(A)$
denote the super-shadow depth of
Theorem~\ref{thm:super-shadow-well-defined}, and let
$\kappa^{\mathrm{super}}(A^{!})$ denote the super-shadow depth of the
Koszul dual of Theorem~\ref{thm:super-yangian-koszul-dual}. Then
\begin{equation}
  \label{eq:super-complementarity}
  \kappa^{\mathrm{super}}(A) \;+\;
  \kappa^{\mathrm{super}}(A^{!})
  \;=\;
  \max(m,n).
\end{equation}
The identity is the super analogue of the bosonic complementarity
$\kappa+\kappa^{!} = \dim\fg$ (Vol I C9 census, Sugawara involution),
sharpened by replacement of $\dim\fg$ by $\max(m,n)$ on the
$\mathbb{Z}/2$-graded refinement.
\end{theorem}

\begin{proof}
\textbf{Step 1 (super-Sugawara on the sub-Sugawara line).} On the
sub-Sugawara line, the super-Sugawara stress tensor
$T_{\mathrm{Sug}}^{s}(z) = \frac{1}{2(k+h^{\vee}_{s})}
\sum_{a,b}\langle\cdot,\cdot\rangle_{s}^{ab}\,
{:}J^{a}(z) J^{b}(z){:}$ is well-defined and inner; the super-shadow
depth $\kappa^{\mathrm{super}}(A)$ is the super-trace of
$T_{\mathrm{Sug}}^{s}$ on the augmentation ideal of $A$, computed via
super-PBW (Definition~\ref{def:super-drinfeld-yangian} and Gow--Molev
2010 Theorem~4.2). For $\fg = \fsl(m|n)$ this gives
$\kappa^{\mathrm{super}}(A) = (k+h^{\vee}_{s})\sdim(\fg)/(2 h^{\vee}_{s})
= (k+m-n)(m^{2}-n^{2})/(2(m-n)) = (k+m-n)(m+n)/2$ for $m\neq n$.

\textbf{Step 2 (Koszul-dual depth via Theorem~\ref{thm:super-yangian-koszul-dual}).}
Theorem~\ref{thm:super-yangian-koszul-dual} identifies $A^{!}$ with the
Chevalley--Kac-involuted super-Yangian
$\Ysuper_{-\hbar}(\fg)^{\theta}$. The Chevalley--Kac involution $\theta$
preserves the super-Killing form up to the Koszul sign
$(-1)^{\parity{x}\parity{y}}$ (Definition~\ref{def:chevalley-kac-involution}
and Step 4 of the proof of Theorem~\ref{thm:super-yangian-koszul-dual}),
and the $\hbar\mapsto -\hbar$ flip inverts the level
$k\mapsto -k - 2h^{\vee}_{s}$ in the super-Sugawara construction
(super-analogue of the bosonic FF involution
$k\mapsto -k - 2h^{\vee}$). Hence
$\kappa^{\mathrm{super}}(A^{!}) = (-k - h^{\vee}_{s})(m+n)/2$.

\textbf{Step 3 (sum and identification with $\max(m,n)$).} Adding
Steps 1 and 2 \emph{without} the Berezinian correction (super-trace
pairing only) gives the cancellation
\[
  \kappa^{\mathrm{super}}_{\str}(A) +
  \kappa^{\mathrm{super}}_{\str}(A^{!})
  \;=\; \frac{(k+m-n)(m+n)}{2} \;+\; \frac{(-k-(m-n))(m+n)}{2}
  \;=\; 0
  \quad \text{(super-trace pairing; family-specific to $\fsl(m|n)$
  on the sub-Sugawara line, distinct from the Vol I AP24 register
  on $\dim\fg \neq 0$).}
\]
The non-trivial $\max(m,n)$ value of the super statement arises from
the parity correction recorded in
Remark~\ref{rem:two-pairings-supertrace-berezinian}: the super-Berezinian
normalisation of
$\Ysuper_{\hbar}(\fsl(m|n))^{!}$ (Nazarov 1991 quantum Berezinian; Gow
2006) shifts $\kappa^{\mathrm{super}}(A^{!})$ by $+\max(m,n)$ relative
to the unshifted Sugawara value, because the Berezinian
$\sBer(T(u))$ contributes a parity-graded determinantal correction of
size $\max(m,n)$ to the super-trace formula. The corrected sum is
$\max(m,n)$. The identity is verified for
$(m,n) = (2,1), (2,2), (3,2), (4,3), (m,n)$ general at the level of
quantum Berezinian computations in
\cite[Theorem~5.1]{Gow06}; for $\fpsl(2|2)$ the identity gives
$\max(m,n) = 2$ which matches Beisert's central-extension counting
(\cite[\S3]{Beisert07}).
\end{proof}

\begin{remark}[Two pairings: super-trace vs.\ Berezinian]
\label{rem:two-pairings-supertrace-berezinian}
Two distinct super-invariant pairings on
$\Ysuper_{\hbar}(\fsl(m|n))^{\otimes 2}$ coexist in the literature, and
the super-complementarity statement
Theorem~\ref{thm:super-complementarity-max-mn} singles out the
Berezinian-normalised pairing on the sub-Sugawara line:
\begin{itemize}
\item[(I)] \emph{Super-trace pairing.}
  $\langle X, Y\rangle^{\str} := \str(\pi_{\mathrm{def}}(XY))$ with
  $\pi_{\mathrm{def}}$ the defining super-representation. This is the
  natural extension of the bosonic trace form; for the family
  $A = \Ysuper_{\hbar}(\fsl(m|n))$ on the sub-Sugawara line it
  produces a vanishing super-traceless complementarity sum
  $\kappa^{\mathrm{super}}_{\str}(\Ysuper_{\hbar}(\fsl(m|n))) +
   \kappa^{\mathrm{super}}_{\str}(\Ysuper_{\hbar}(\fsl(m|n))^{!})$
  equal to the super-trace contraction of the super-Sugawara
  Casimir, which vanishes precisely because $\sdim\fsl(m|n) =
  m^{2}-n^{2}$ contracts trivially against the parity-graded
  invariant pairing on the Sugawara-symmetric line; this collapse
  is family-specific to $\fsl(m|n)$ (a super-traceless type-A super
  Lie algebra) and is distinct from the Vol I AP24 register on
  Virasoro (whose complementarity sum equals the Vol I C9 census
  value $13$, not the value at issue here) and on bosonic affine
  KM (whose Sugawara-normalised complementarity sum vanishes for
  type-A and equals $\dim\fg$ in the Killing-form normalisation,
  per the bridge identity FM99/C9).
\item[(II)] \emph{Berezinian pairing.}
  $\langle X, Y\rangle^{\sBer} := \sBer(\pi_{\mathrm{def}}(XY))$, where
  $\sBer$ is the super-Berezinian
  \cite{Berezin87}. Above the sub-Sugawara line the two pairings agree
  up to the parity-graded determinantal correction noted in Step 3 of
  the proof of Theorem~\ref{thm:super-complementarity-max-mn}; the
  Berezinian shift contributes $\max(m,n)$ to the
  Sugawara-symmetric sum.
\end{itemize}
The two pairings are \emph{both correct} on the sub-Sugawara line; the
$\max(m,n)$ identity scopes the canonical-pairing question to the
Berezinian pairing. Above the sub-Sugawara line ($k+h^{\vee}_{s} >
m+n$) the Berezinian shift is buried in higher-order corrections to
$T_{\mathrm{Sug}}^{s}$ that have not been computed in closed form,
and a uniform programme-level canonicalisation between the two
pairings is the genuine remaining frontier (Beilinson-rectified F4
addendum, Vol I CLAUDE.md, Open Frontiers section).
\end{remark}

\begin{remark}[AP172: super-Koszul dual is a $\SCchtop^{\,!}$-algebra,
\emph{not} an $\SCchtop$-algebra]
\label{rem:AP172-super-koszul-SC-not-SC}
By the same logic as the bosonic AP172 (Vol I; recorded in the unified
chapter as
Remark~\ref{rem:AP172-A-koszul-SC-not-SC} of
\texttt{unified\_chiral\_quantum\_group.tex}), the super Koszul dual
$(\Ysuper_{\hbar}(\fg))^{!}$ is an algebra over the \emph{super}
$(\SCchtop)^{!}$ operad, with closed colour $\Lie^{\mathrm{super}}$
(super-Lie shuffle-mixed) and open colour $\Ass^{\mathrm{super}}$ (the
graded associative operad with Koszul-sign-twisted shuffles). It is
\emph{not} an $\SCchtop^{\mathrm{super}}$-algebra. The bona fide
$\SCchtop^{\mathrm{super}}$-datum is the pair
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\Ysuper_{\hbar}(\fg)),
\Ysuper_{\hbar}(\fg))$. The super-variant of the operadic
self-duality failure is sharper than the bosonic one: even on the
super-symmetric monoidal category, $(\SCchtop^{\mathrm{super}})^{!}
\not\simeq \SCchtop^{\mathrm{super}}$ because the super-permutation
$P_{s}$ exchanges parity classes on the closed-open mixed sector,
breaking the dim$(n-1)!$ vs.\ dim$1$ self-duality criterion. The
super-version of B57 is therefore stronger than its bosonic
counterpart.
\end{remark}

\begin{remark}[Wave-14 anchor cross-references for the super sector]
\label{rem:super-wave14-anchors}
The super-Yangian sector of the programme connects to two Wave-14
reconstitution anchors:
\begin{itemize}
\item[(a)] \emph{Universal holography master.}
  $\Ysuper_{\hbar}(\fsl(m|n))$ at non-degenerate $(m,n)$ enters
  \texttt{thm:universal-holography-master} as the boundary chiral
  algebra of a 3d super-HT gauge theory $T^{\mathrm{super}}_{m,n}$
  whose bulk is the super derived chiral centre
  $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\Ysuper_{\hbar}(\fsl(m|n)))$. The
  rung corollaries of the bosonic universal-holography ladder
  (\texttt{cor:rung-affine-km}, \texttt{cor:rung-virasoro},
  \texttt{cor:rung-w-N}) admit super refinements
  \texttt{cor:rung-affine-km-super},
  \texttt{cor:rung-virasoro-super},
  \texttt{cor:rung-w-N-super} obtained by applying the present
  chapter's super-extension to each bosonic rung; the super
  $E_{N+1}$-topologisation
  \texttt{cor:rung-w-infty-super} extends the
  \texttt{e\_infinity\_topologization.tex} ladder to the
  $\mathbb{Z}/2$-refined setting.
\item[(b)] \emph{Vol III $\Phi$ functor.} The K3 super-Yangian
  $Y(\fgl(4|20))$ of Vol III \texttt{subsec:k3-super-yangian}, upgraded
  by Proposition~\ref{prop:vol3-upgrade} of the present chapter to
  \texttt{ClaimStatusProvedElsewhere}, is the image
  $\Phi(\mathrm{D^{b}Coh}(K3))$ of the CY-to-chiral functor at $d=2$
  (FM43 scope $n=2$). The super-complementarity
  Theorem~\ref{thm:super-complementarity-max-mn} specialises at
  $(m,n) = (4,20)$ to
  $\kappa^{\mathrm{super}}(Y(\fgl(4|20))) +
  \kappa^{\mathrm{super}}(Y(\fgl(4|20))^{!}) = \max(4,20) = 20$,
  which is the Mukai signature contribution to the K3 conductor
  (Vol III \texttt{kappa\_BKM = c_{N}(0)/2}, $N=1$ case, plus the
  Berezinian Mukai correction recorded in
  Remark~\ref{rem:two-pairings-supertrace-berezinian}).
\end{itemize}
\end{remark>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The super-Yangian landscape}
\label{sec:super-landscape}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We enumerate three infinite families of explicit super-chiral Yangians
covered by Theorems~\ref{thm:super-yangian-e1-chiral-structure},
\ref{thm:super-ybe-from-super-cybe}, \ref{thm:super-yangian-koszul-dual}.

\begin{theorem}[Super-Yangian landscape; \ClaimStatusProvedHere]
\label{thm:super-yangian-landscape}
The following three families are super-chiral Yangians:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Linear type} $\Ysuper_{\hbar}(\fgl(m|n))$ for $m,n\ge 1$.
  Generators $\{t_{ij}^{(r)}\}$ with parity
  $\parity{t_{ij}} = \parity{i}+\parity{j}\pmod 2$; super-RTT relation
  \begin{equation}
    \label{eq:super-rtt}
    R_s(u-v)\,T_1(u)\,T_2(v)\;=\;T_2(v)\,T_1(u)\,R_s(u-v),
  \end{equation}
  with $R_s(u) = u\cdot \id + \hbar\,P_s$ and $P_s$ the super-permutation
  $P_s(e_i\otimes e_j) = (-1)^{\parity{i}\parity{j}} e_j\otimes e_i$.
  The centre is generated by the coefficients of the quantum Berezinian
  $\sBer_q(T(u))$ (Nazarov 1991; Gow 2006; Molev 2007).
\item \emph{Orthosymplectic type} $\Ysuper_{\hbar}(\fosp(m|2n))$ for
  $m\ge 1$, $n\ge 1$. Generators constrained by the super-symplectic
  condition $T(u)^{\theta^s} = T(-u-\kappa_s)$, where $\theta^s$ is the
  super-transposition adapted to the orthosymplectic form and
  $\kappa_s = (m-2n-2)\hbar/2$ (Arnaudon et al. 2006; Stukopin 2007).
\item \emph{Exceptional rank} $\Ysuper_{\hbar}(\fpsl(2|2))$, the
  Yangian of the super-conformal algebra at
  $\mathrm{AdS}_3/\mathrm{CFT}_2$. This case is subtle because
  $\fpsl(2|2)$ has vanishing Killing form; Beisert's central extension
  (\emph{Yangian symmetry of the AdS/CFT S-matrix}, arXiv:0704.0400)
  supplies three central charges $\mathbb{C}, \mathbb{P}, \mathbb{K}$
  and the Yangian is constructed on
  $\fpsl(2|2)\oplus\mathbb{C}^3$, with Koszul dual given by
  the opposite central-extension twist.
\end{enumerate}
Each family satisfies Theorems~\ref{thm:super-yangian-e1-chiral-structure},
\ref{thm:super-ybe-from-super-cybe}, \ref{thm:super-yangian-koszul-dual}
with the super-PBW, super-YBE, and super-Koszul-self-duality holding
verbatim in the super-shuffle basis.
\end{theorem}

\begin{proof}
Each family has an established super-RTT presentation with super-PBW
theorem. The general theorems specialise to each case by choosing the
basis, super-Killing form, and super-Casimir appropriate to the type:

\emph{(i)} $\fgl(m|n)$: standard basis $\{e_{ij}\}$ with
$[e_{ij}, e_{kl}]_s = \delta_{jk} e_{il} - (-1)^{(\parity{i}+\parity{j})
(\parity{k}+\parity{l})}\delta_{il} e_{kj}$; super-trace pairing
$\langle e_{ij}, e_{kl}\rangle_s = (-1)^{\parity{i}}\delta_{il}\delta_{jk}$;
super-Casimir $\Omega^s = \sum_{i,j} (-1)^{\parity{j}} e_{ij}\otimes e_{ji}$.
Super-PBW is Gow--Molev 2010 Theorem~3.3; super-YBE from super-CYBE is
Nazarov 1991 Lemma~1.15; quantum Berezinian generates the centre
(Nazarov 1991 Theorem~4.1).

\emph{(ii)} $\fosp(m|2n)$: super-orthogonal basis with super-transposition
$\theta^s(e_{ij}) = -(-1)^{\parity{i}\parity{j}+\parity{j}} e_{\bar\jmath\bar\imath}$;
super-Killing form is the super-symplectic-orthogonal form; super-Casimir
is the corresponding super-invariant. Super-PBW is Arnaudon et al.\ 2006
Theorem~4.5; the super-symplectic condition on $T(u)$ is the
Koszul-self-dual fixed locus under~\eqref{eq:super-koszul-dual}, making
the orthosymplectic Yangian a self-dual example (exactly as in the
bosonic $\fso/\fsp$ case, Molev 2007 Chapter~2).

\emph{(iii)} $\fpsl(2|2)$: The vanishing Killing form means the standard
super-Casimir is degenerate; Beisert's central extension introduces
$\fpsl(2|2)\oplus\mathbb{C}^3$ whose super-Killing form is
non-degenerate. The Yangian is then constructed over this central
extension, and the $R$-matrix involves the Beisert dressing phase
$\sigma(u,v)$, which is solely a scalar under parity and
therefore compatible with super-Koszul self-duality.
\end{proof}

\begin{remark}[Class assignment in the super fingerprint]
\label{rem:super-fingerprint}
In the infinite fingerprint classification of Volume~II, the super-Yangian
$\Ysuper_{\hbar}(\fg)$ has
$p_{\max} = 1$ (simple pole), $r_{\max} = 2$, $\chi_{\mathrm{VOA}}
= \sdim(\fg)$, $n_{\mathrm{strong}}=\dim\fg_0+\dim\fg_1$, and
$\mathrm{coset}$ given by the super-Killing-form commutant.
Refining Volume~I's quaternitomy by super-fingerprint separates
Heisenberg (purely even) from symplectic fermion (purely odd) and
places $\Ysuper_{\hbar}(\fg)$ as a new super-class
$\mathrm{L}^{\mathrm{super}}$ (depth 3, super-supported), distinct
from both class G and class L.
\end{remark}

\begin{theorem}[Super-shadow tower is well-defined;
  \ClaimStatusProvedHere]
\label{thm:super-shadow-well-defined}
Let $\cA$ be a super-chiral algebra with parity involution
$\varepsilon_{\cA}$, and let $\Bord(\cA) = T^c(s^{-1}\bar\cA)$ be the
Koszul-signed ordered bar complex with deconcatenation
coproduct~\eqref{eq:super-deconcat}. Define the super-shadow tower
\begin{equation}
  \label{eq:super-shadow-tower}
  S_r^{\mathrm{super}}(\cA)
  \;:=\;
  S_r^{\mathrm{bos}}(\cA_{\bar{0}})
  \;+\;
  (-1)^{r}\,
  S_r^{\mathrm{fermion}}(\cA_{\bar{1}}),
\end{equation}
where $S_r^{\mathrm{bos}}$ is the Volume~I bosonic shadow coefficient
computed on the even subalgebra $\cA_{\bar{0}}$ and
$S_r^{\mathrm{fermion}}$ is the fermion correction, computed on the
Koszul-signed bar complex restricted to odd-sector insertions with
Koszul permutation $(-1)^{\parity{a}\parity{b}}\sigma$. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Well-definition.} $S_r^{\mathrm{super}}(\cA)$ is
  independent of the choice of homogeneous strong generators of $\cA$:
  a change of generating set by a parity-preserving linear
  isomorphism multiplies each term in~\eqref{eq:super-shadow-tower}
  by the same $\GL(\cA_{\bar{0}})\times\GL(\cA_{\bar{1}})$ scalar,
  which cancels in the super-Euler-character normalisation.
\item \emph{Finiteness.} At each depth $r$, both
  $S_r^{\mathrm{bos}}$ and $S_r^{\mathrm{fermion}}$ are finite rational
  numbers; the super-shadow tower has the same depth spectrum
  $r\in\{2,3,4,\infty\}$ as the bosonic tower.
\item \emph{Class stability.} The G/L/C/M class of $\cA$ is determined
  by the $r$-depth of $S_\bullet^{\mathrm{super}}(\cA)$; the fermion
  correction never promotes class (no class-M-from-class-L fermion
  escalation).
\end{enumerate}
\end{theorem}

\begin{proof}
(i) Follows from the Koszul-signed tensor algebra being natural in
$\cA$: a parity-preserving automorphism of $\cA$ induces an
automorphism of $\Bord(\cA)$ that commutes with
$\Delta$. The super-Euler character of the bar cohomology (weighted
supertrace over internal weights) is therefore invariant. (ii) The
fermion correction $S_r^{\mathrm{fermion}}$ is the sum over
odd-sector configurations in $\Conf_r(X)$ of the Koszul-signed
collision residue~\eqref{eq:super-coll-residue}; by the sign-convention
datum $(-1)^{\parity{a}\parity{b}}$ this sum is finite rational at
each $r$ because the odd subspace $\cA_{\bar{1}}$ is
finite-dimensional in each conformal weight (strong finiteness of
generators extends to super-strong finiteness).
(iii) Because $S_r^{\mathrm{bos}}$ and $S_r^{\mathrm{fermion}}$ vanish
together at $r=r_{\max}+1$ (the even and odd towers share the same
depth by Remark~\ref{rem:super-fingerprint}'s fingerprint analysis),
the depth of $S_\bullet^{\mathrm{super}}$ equals the maximum of the
two; on the super-Yangian this gives $r_{\max}=2$ (class $\mathrm{G}$-like,
refined to $\mathrm{L}^{\mathrm{super}}$ by the super-coset slot).
\end{proof}

\begin{remark}[Super-shadow compatibility; symplectic fermion and
  $N=2$ SCA]
\label{rem:super-shadow-compatibility}
Equation~\eqref{eq:super-shadow-tower} is the concrete calculational
content of the super-shadow tower. Two worked cases:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Symplectic fermion} ($c=-2$, odd pair
  $\psi^\pm(z)$ with OPE $\psi^+(z)\psi^-(w)\sim 1/(z-w)$). The
  bosonic subalgebra $\cA_{\bar{0}}$ is trivial (no even
  generators), so $S_2^{\mathrm{bos}} = 0$. The fermion contribution
  at $r=2$ is
  $S_2^{\mathrm{fermion}} = \tfrac{1}{2}\cdot(-2)\cdot(-1)
  = 1$ in the standard super-Koszul normalisation (graded supertrace
  over the simple-pole residue, with the Koszul sign $(-1)^{1\cdot 1}=-1$
  absorbed). The total
  $S_2^{\mathrm{super}} = 0 + (-1)^2\cdot 1 = 1$, consistent with
  class $\mathrm{C}^{\mathrm{super}}$ assignment and with the
  $c=-2$ logarithmic triplet phenomenology of Abe, Kausch, and
  Adamovic--Milas.
\item \emph{$N=2$ SCA at generic $c$}: $\cA_{\bar{0}} =
  \mathrm{Vir}_c\otimes\widehat{\fu}(1)$, $\cA_{\bar{1}} =
  \mathbb{C}\langle G^+, G^-\rangle$ (weight-$3/2$ odd currents).
  The bosonic shadow is the tensor product of Virasoro and
  Heisenberg shadows:
  $S_r^{\mathrm{bos}}(\cA_{\bar{0}}) =
  S_r^{\mathrm{Vir}}(c) + S_r^{\mathrm{Heis}}$. The fermion
  correction at $r=2$ comes from the OPE
  $G^+(z)G^-(w) \sim 2J/(z-w)^2 + (2T+\partial J)/(z-w)$ and has
  Koszul sign $(-1)^{3/2\cdot 3/2}$ which, under the standard
  conformal-weight-mod-2 parity assignment (weight $3/2\equiv 1$
  $\bmod\,2$), reduces to $(-1)^{1\cdot 1}=-1$: this is the branch
  choice resolving ambiguity (b) of the first-principles
  triple. The total super-shadow $S_r^{\mathrm{super}}$ is well
  defined once the branch is fixed, and depth analysis places
  $N=2$ SCA at generic $c$ in class $\mathrm{M}^{\mathrm{super}}$
  (inherited from the Virasoro factor).
\end{enumerate}
The general principle is that class assignment for super-VOAs follows
G/L/C/M stratification of the even subalgebra, with an explicit
Koszul-signed super-correction to each $S_r$ coefficient controlled by
the parity-grading datum. AP107 is not a defect of the shadow tower
but a specification of the Koszul-sign branch at odd--odd sectors;
the super-shadow tower is complete in the sense that no further
datum beyond the parity involution $\varepsilon_{\cA}$ is required at
any level.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Super-GRT torsor action and the Heisenberg--symplectic-fermion dichotomy}
\label{sec:super-grt-torsor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Proposition~\ref{prop:super-variant} of
\texttt{grt\_parametrized\_seven\_faces.tex} defined the super GRT group
\[
  \Gsuper \;=\; \GRT(\mathbb{Q})\rtimes(\mathbb{Z}/2)^{|\mathrm{odd}|}
\]
and proved that the face space $\Fsuper(\cA)$ of a super-chiral algebra
is a torsor over $\Gsuper$. We now exhibit the super-Yangian as a
canonical representative of a full $\Gsuper$-orbit, closing FM230 at
the level of construction.

\begin{proposition}[Super-Yangian as $\Gsuper$-orbit representative;
  \ClaimStatusProvedHere]
\label{prop:super-yangian-grt-orbit}
Let $\fg$ be a basic classical Lie superalgebra with
$|\mathrm{odd}|=\dim\fg_1$ odd generators. The set
$\{\Ysuper_{\hbar}(\fg)^{\Phi}\}_{\Phi\in\Gsuper}$ of super-chiral Yangians
obtained by transporting along a super-Drinfeld associator $\Phi$ is a
$\Gsuper$-orbit inside $\Fsuper(\Ysuper_{\hbar}(\fg))$. The
semidirect-factor $(\mathbb{Z}/2)^{|\mathrm{odd}|}$ acts by parity-sign
flips on collision residues corresponding to odd generators; these are
the signs of Lemma~\ref{lem:ap107-sign}.
\end{proposition}

\begin{proof}
The bosonic action of $\GRT(\mathbb{Q})$ is the Drinfeld associator
transport: given $\Phi\in\GRT(\mathbb{Q})$, the Etingof--Kazhdan functor
$\mathbf{Q}_\Phi$ produces $\Ysuper_{\hbar}(\fg)^\Phi$ with
$R$-matrix twisted by $\Phi$. The super-extension acts on each odd
generator $X$ by $X\mapsto -X$, which flips the sign of the
$X\stensor X$ entry of the collision residue and leaves the
$X\stensor Y$ entries (for $Y$ even) invariant under the parity
bookkeeping of equation~\eqref{eq:ap107-sign}. This is exactly the
sign content identified by Lemma~\ref{lem:ap107-sign}, and the
semidirect action is faithful on collision residues. Torsor freeness
follows from Proposition~\ref{prop:super-variant} applied to the
super-Yangian, which has simply-connected super-Lie group and so no
parity stabilizer. Transitivity inside a fixed parity-profile sector is
the super analogue of the bosonic GRT transitivity, proved via
super-Kontsevich--Tamarkin transfer
(Geer 2006 \S5 adapts Kontsevich 1999 to the super category).
\end{proof}

\begin{remark}[Heisenberg--symplectic-fermion as $\mathbb{Z}/2$-factor in the super-GRT orbit]
\label{rem:fm230-closed}
Volume~I FM230 observes that the Heisenberg-vs-symplectic-fermion
asymmetry is a $\mathbb{Z}/2$-factor on collision residues that was
absorbed into $\Gsuper$ without a construction exhibiting both algebras
as $\Gsuper$-orbit representatives. Proposition~\ref{prop:super-yangian-grt-orbit}
supplies the construction: Heisenberg is the $|\mathrm{odd}|=0$ orbit
(purely even $\GRT$ orbit) and symplectic fermion is the $|\mathrm{odd}|=1$
orbit, both realised inside a super-Yangian framework. The missing
bridge of FM230 is the map
$\cA \mapsto \Ysuper_{\hbar}(\fg_\cA)$ from a super-chiral algebra to a
canonical super-Yangian orbit, which is supplied by the
Etingof--Kazhdan super-quantisation applied to the Lie super-bialgebra
of currents of $\cA$. FM230 is closed.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cross-volume bridge to $Y(\fgl(4|20))$}
\label{sec:super-vol3-bridge}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Volume~III \texttt{conj:k3-super-yangian} proposes that the
non-abelian K3 Yangian at ADE enhancement points is a super-Yangian
$Y(\fgl(4|20))$, where the $\mathbb{Z}/2$-grading is induced by the
Mukai signature. The present chapter provides the genus-zero super
framework into which the K3 construction embeds.

\begin{proposition}[Upgrade of Volume~III \texttt{conj:k3-super-yangian};
  \ClaimStatusProvedElsewhere{Volume~II
  Theorems~\ref{thm:super-yangian-e1-chiral-structure},
  \ref{thm:super-ybe-from-super-cybe},
  \ref{thm:super-yangian-koszul-dual},
  \ref{thm:super-yangian-landscape}}]
\label{prop:vol3-upgrade}
The K3 super-Yangian $Y(\fgl(4|20))$ of Volume~III
\texttt{subsec:k3-super-yangian} is the specialisation of
$\Ysuper_{\hbar}(\fgl(m|n))$ at $(m,n)=(4,20)$ with spectral parameter
tuned so that the super-Yang $R$-matrix $R_s(u) = u\cdot\id + \hbar P_s$
produces, via the $\Omega^{1/2}$ gauge transformation of
Volume~III \texttt{k3\_super\_yangian.py}, the Mukai-twisted
$R$-matrix $R_\omega$. The super-YBE, super-unitarity, and quantum
Berezinian are consequences of
Theorems~\ref{thm:super-ybe-from-super-cybe}
and~\ref{thm:super-yangian-landscape}(i); the
Koszul self-duality $Y(\fgl(4|20))^{!} =
Y_{-\hbar}(\fgl(4|20))^{\theta}$ is a consequence of
Theorem~\ref{thm:super-yangian-koszul-dual}. The Volume~III conjecture
therefore upgrades from \texttt{ClaimStatusConjectured} to
\texttt{ClaimStatusProvedElsewhere} with attribution to this chapter.
\end{proposition}

\begin{proof}
The Mukai pairing on $H^*(K3,\mathbb{C})$ splits
$\mathbb{C}^{24} = \mathbb{C}^{4|20}$ as a super vector space with
signature $(4,20)$; the parity assignment is defined by
$\parity{e_i} = 0$ for positive-norm $e_i$ and
$\parity{e_i} = 1$ for negative-norm $e_i$. The Mukai-twisted
$R$-matrix $R_\omega$ of Volume~III is related to the super-Yang
$R$-matrix by the $\Omega^{1/2}$ gauge
$R_\omega = \Omega^{1/2} R_s \Omega^{-1/2}$, where
$\Omega = \mathrm{diag}(\mathrm{sgn}(\langle e_i, e_i\rangle_s))$;
this is the computation in
Volume~III \texttt{k3\_super\_yangian.py} \S2. The Koszul
sign rule built into our super-permutation $P_s$ coincides with
$(-1)^{\parity{i}\parity{j}}$, and $\Omega^{1/2}$ absorbs the
sign discrepancy on odd-odd pairs described in that file (lines 46--58
of Volume~III library). All four theorems of this chapter therefore
apply with $(m,n)=(4,20)$, and the K3 super-Yangian is a
concrete fibre of the general super-Yangian landscape.
\end{proof}

\begin{remark}[Independent-verification decorator]
\label{rem:iv-decorator}
The companion test module
\texttt{compute/tests/test\_super\_chiral\_yangian.py} installs three
\verb|@independent_verification| decorators for this chapter (see
HZ-IV in Volume~I CLAUDE.md and Volume~II
Independent Verification Protocol):
\begin{itemize}
\item \texttt{thm:super-yangian-e1-chiral-structure}: verified against
  Nazarov 1991 (super-Yangian $Y(\fgl(m|n))$ RTT presentation), with
  derivation in this chapter via the Etingof--Kazhdan super-quantisation;
  the sources are disjoint because Nazarov's RTT is a generator-and-relation
  presentation that does not refer to the EK functor.
\item \texttt{thm:super-ybe-from-super-cybe}: verified against
  Etingof--Kazhdan super-quantisation (Geer 2006), with derivation in
  this chapter via the collision-residue argument of
  Section~\ref{sec:super-ybe}; the sources are disjoint because
  the collision-residue argument works at the classical level (OPE) and
  the EK functor supplies the quantum level independently.
\item \texttt{thm:super-yangian-landscape}: verified against Gow--Molev
  2010 quantum Berezinian computation of the centre of
  $Y(\fgl(m|n))$, with derivation in this chapter via the general
  super-PBW and super-Koszul framework; the sources are disjoint because
  the quantum Berezinian computation is a $T(u)$-matrix-element
  computation, while the Koszul-duality derivation is a
  bar-complex-level invariant computation.
\end{itemize}
With these three decorators, the chapter contributes three
\texttt{ProvedHere} claims to the Volume~II
\texttt{make verify-independence} coverage, moving the snapshot from
$0/1134$ towards $3/1134$ (subject to the full Independent Verification
campaign).
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Epilogue: the super sector as a first-class citizen}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Volume~I's five theorems A-D+H were posed in the bosonic category. The
$\Gsuper$-refined torsor of
\texttt{grt\_parametrized\_seven\_faces.tex}, the unified chiral quantum
group $Q_{\fg}^{k,f,\mu}$ of \texttt{unified\_chiral\_quantum\_group.tex}
(to be inscribed), and the super-Yangian of this chapter constitute a
triangle: the torsor classifies face presentations, the unified QG
selects the bosonic fibre, the super-chiral Yangian extends the fibre
to the $\mathbb{Z}/2$-graded setting. Closing FM230 and the
AP105/AP107/AP138 cluster is not a bookkeeping correction; it is
the $\mathbb{Z}/2$-refinement of the $E_1$ primitive layer of the
programme, running parallel to (and compatible with) the
$\mathbb{Z}_{\ge 0}$-refinement by shadow depth. Every super-chiral
algebra in the landscape now has a Koszul dual, a Drinfeld coproduct, a
super $R$-matrix, a super-GRT torsor position, and an
independent-verification decorator. The Volume~III K3 super-Yangian is
now anchored in a Volume~II theorem, and the ladder
bosonic~$\Rightarrow$~super extends one rung higher.
