%% =====================================================================
%% topologization_class_m_original_complex_platonic.tex
%%
%% Scope note:
%% ------------------------------------------------
%% The obstruction normalization kappa^{(infty)}_orig = 1/e is not a
%% current theorem of the manuscript. The current active surface is the
%% tempered-stratum result in
%% chapters/theory/tempered_stratum_characterization_platonic.tex:
%% generic Virasoro is tempered, with radius governed by the corrected
%% Stirling/root estimate. The labels in this file remain only as
%% dependencies for later comparison statements; the corrected active
%% proof routes them through the tempered-stratum theorem.
%% =====================================================================
%%
%% Frontier resolution: chain-level E_3-topological structure on
%% Z^{der}_ch(A) for class M at generic c on the ORIGINAL complex
%% (NOT weight-completed, NOT weight-by-weight finite).
%%
%% Status of the question before this chapter:
%%   * Weight-completed class M: PROVED unconditional
%%     (prop:bv-bar-class-m-weight-completed, bv_brst.tex:2285).
%%   * Direct-sum class M: GENUINELY FALSE
%%     (thm:curved-dunn-class-M-raw-direct-sum-fails,
%%      curved_dunn_raw_direct_sum_platonic.tex, and
%%      prop:zamolodchikov-cocycle-direct-sum-witness,
%%      class_m_direct_sum_obstruction_platonic.tex): the Zamolodchikov
%%      quasi-primary Lambda exhibits an explicit chain-level cocycle
%%      at weight 4, g=2 with d^2_fib(xi_Lambda) = S_4(Vir_c) * omega_2^2
%%      non-zero at generic c.
%%   * The gap between these is the ORIGINAL-COMPLEX regime: an
%%     intermediate chain model on the raw direct sum augmented by a
%%     single chain-level homotopy data, convergent in a precise
%%     analytic norm.
%%
%% First-principles analysis of the question:
%%   (ghost, correct): the weight-completed proof uses finite weight
%%     cutoffs + Milnor/Mittag-Leffler; the pro-ambient construction
%%     uses the same finite cutoffs + inverse limit. Both replace the
%%     original complex by a projective system. The question asks for
%%     a construction STILL on the original direct sum that assembles
%%     all weights into a single chain complex without projective limit.
%%   (wrong claim): "a convergent geometric series works naively".
%%     The Kac-Shapovalov determinant det(G_N)(c) at generic c grows
%%     factorially (det(G_N) ~ (N!)^{const}) but the SMALLEST
%%     EIGENVALUE lambda_min(G_N) does NOT grow: it equals a product
%%     of PROXIMATE factors (h - h_{r,s}(c)) each of size c_0, hence
%%     lambda_min(G_N) is essentially a positive constant (depending
%%     on c) uniformly in N at generic c. This kills the naive
%%     geometric-series convergence argument.
%%   (correct statement): the shadow coefficients S_r(Vir_c) decay
%%     only polynomially in r at generic c (not exponentially), so
%%     the obstruction series sum_r S_r * omega_g^m does NOT converge
%%     in any Kac-Shapovalov-norm on the raw direct sum. The ORIGINAL
%%     complex does not carry a natural convergent chain-level E_3;
%%     instead, the chain-level E_3 on the original complex is
%%     CONDITIONAL on a precise analytic hypothesis (shadow-decay
%%     improvement S_r(Vir_c) = O(1/r!) at some specific locus, which
%%     does NOT hold for generic class M algebras).
%%
%% Resolution (CONDITIONAL YES with precise hypothesis):
%%   We construct the Kac-Shapovalov norm |||.|||_{KS,rho} on the
%%   original raw direct-sum complex, parametrised by rho > 0, and
%%   prove:
%%     (i) At rho = 0: |||xi|||_{KS,0} is the uncompleted weight
%%         filtration norm; the raw d^2 != 0 obstruction persists.
%%     (ii) At rho > 0: |||xi|||_{KS,rho} adds a geometric weight
%%          rho^r per weight-r component. Convergence of
%%          sum_r S_r(A) * rho^r requires S_r(A) = O(r!^{-alpha})
%%          for some alpha > 0 at generic c.
%%     (iii) For class M, S_r(Vir_c) = O(r^{-1/c}) at large r and
%%           generic c (from the BPZ decomposition), so the series
%%           does NOT converge for rho > 0.
%%     (iv) Therefore the chain-level E_3 on the original complex is
%%          CONDITIONAL on the analytic hypothesis (H_S): the shadow
%%          coefficients of A decay super-polynomially in r.
%%     (v) For algebras satisfying (H_S) -- the "analytically tempered"
%%          class M subfamily, including the completed Virasoro
%%          algebra Vir_c^{~} with explicit taming factor -- the
%%          chain-level E_3 is constructed on the ORIGINAL complex.
%%     (vi) The OBSTRUCTION at generic class M is the explicit
%%           cocycle class
%%             kappa^{(infty)} := lim sup_{r} (S_r(A) / r!)^{1/r}
%%           which is positive at generic Vir_c (obstruction to (H_S)).
%%
%% Labels defined:
%%   def:kac-shapovalov-norm (norm on original complex)
%%   prop:kac-shapovalov-eigenvalue-asymptotic (lambda_min bounded by
%%       a c-dependent constant, does NOT grow)
%%   prop:shadow-decay-class-m (S_r(Vir_c) = O(r^{-1/c}) at generic c)
%%   thm:chain-level-e3-original-complex-conditional
%%       (CONDITIONAL YES: chain-level E_3-topological on original
%%       complex for analytically tempered class M)
%%   thm:chain-level-e3-original-complex-obstruction-generic-class-m
%%       (NO for generic class M: explicit obstruction kappa^{(infty)}
%%       > 0, precise cocycle blocking the chain-level lift)
%%   cor:class-m-original-complex-dichotomy (the dichotomy
%%       analytically tempered vs generic class M)
%%   rem:relation-to-weight-completion (the weight-completed and
%%       conditional original-complex constructions are quasi-isomorphic
%%       under (H_S); they differ precisely when (H_S) fails)
%%
%% Location: chapters/theory/.
%% Inputs:
%%   chapters/theory/curved_dunn_higher_genus.tex (thm:curved-dunn-H2-vanishing-all-genera)
%%   chapters/theory/curved_dunn_raw_direct_sum_platonic.tex (raw direct-sum failure)
%%   chapters/theory/class_m_direct_sum_obstruction_platonic.tex (Zamolodchikov witness)
%%   chapters/connections/bv_brst.tex (prop:bv-bar-class-m-weight-completed)
%%   chapters/connections/e_infinity_topologization.tex (thm:e-infinity-topologization-ladder at non-critical)
%% =====================================================================

\chapter{The Original-Complex Frontier: chain-level $E_3$-topological
for class $\mathsf{M}$ at generic $c$}
\label{ch:topologization-class-m-original-complex}

\begin{remark}[\label{rem:original-complex-scope-correction}%
Scope correction for the original-complex obstruction]
\ClaimStatusProvedHere
The DICHOTOMY framing of this chapter (tempered YES / generic
$\mathrm{Vir}_c$ NO, with obstruction
$\kappa^{(\infty)}_{\mathrm{orig}}(\mathrm{Vir}_c) = 1/e > 0$)
is replaced on the active surface by the corrected tempered-stratum
theorem.

\emph{Ghost.} At generic $c$, the shadow sequence $S_r(\mathrm{Vir}_c)$
has only polynomial decay; therefore the ordinary generating radius
$\rho_*$ and the tempered-stratum analytic norm converge in an
annular regime tied to~$c$.

\emph{Wrong.} The claim
$\limsup_r (\lvert S_r(\mathrm{Vir}_c) \rvert / r!)^{1/r} = 1/e > 0$
conflated the Stirling factor $(r!)^{-1/r} \sim e/r$ with the answer
$1/e$. The Stirling factor belongs in the DENOMINATOR of the
$1/r$-root and produces a factor $\to 0$ as $r \to \infty$; the
claimed obstruction $1/e$ cannot emerge from any polynomial
lower bound on $\lvert S_r \rvert$.

\emph{Correct.} The Stirling cancellation gives
$(\lvert S_r(\mathrm{Vir}_c) \rvert / r!)^{1/r}
 \le (\beta_{\mathrm{Vir}} / \lvert c \rvert) \cdot (e/r) \cdot
 (C r^{O(1)})^{1/r} \to 0$
at every fixed generic $c$. Every generic $\mathrm{Vir}_c$ is
\emph{tempered} without obstruction. The chain-level
$E_3$-topological structure on the original complex exists
unconditionally on the non-logarithmic $C_2$-cofinite standard
landscape, via the Banach completion $\mathcal{B}_{\rho}(A)$ at
$\rho < \lvert c \rvert / 6$; this is
Theorem~\ref{thm:tempered-stratum-contains-virasoro} in the
companion chapter
\texttt{tempered\_stratum\_characterization\_platonic.tex}.

The current inscription is
Theorem~\ref{thm:programme-climax}
(Chapter~\ref{chap:programme-climax-platonic}).

The dichotomy statements below
(Propositions~\ref{prop:kac-shapovalov-eigenvalue-asymptotic},
\ref{prop:shadow-decay-class-m};
Theorems~\ref{thm:chain-level-e3-original-complex-conditional},
\ref{thm:chain-level-e3-original-complex-obstruction-generic-class-m};
Corollary~\ref{cor:class-m-original-complex-dichotomy}) are
retained as comparison labels for the analytic lane; the current
surface proves the corrected implication by routing the conclusion
through the tempered-stratum theorem rather than through the
$1/e$ obstruction normalization.
\end{remark}

\section*{Statement of the frontier}

For a chirally Koszul algebra $\cA$ of class $\mathsf{M}$
(Virasoro~$\mathrm{Vir}_c$, principal $\cW_N$, logarithmic $\cW$) at
generic central charge and non-critical level, three chain-level
ambients for the curved-Dunn twisting-cochain complex have been
studied:
\begin{enumerate}[nosep]
\item The \emph{raw direct-sum} ambient
      $\bigoplus_{r \ge 0} \mathrm{TCo}^{\bullet}_{g, r}(\cA)$. On this
      ambient $d^2 \neq 0$ at generic~$c$, witnessed by the
      Zamolodchikov quasi-primary $\Lambda(z) = :T T:(z) -
      \tfrac{3}{10}\, \partial^2 T(z)$ at weight~$4$, $g = 2$
      (Proposition~\ref{prop:zamolodchikov-cocycle-direct-sum-witness}).
\item The \emph{weight-completed} ambient
      $\widehat{\mathrm{TCo}}^{\bullet}_g(\cA) =
      \varprojlim_N \bigoplus_{r \le N} \mathrm{TCo}^{\bullet}_{g,r}(\cA)$.
      On this ambient $d^2 = 0$ unconditionally at every genus and for
      every shadow class
      (Proposition~\ref{prop:bv-bar-class-m-weight-completed},
      Theorem~\ref{thm:curved-dunn-H2-vanishing-all-genera}).
\item The \emph{weight-by-weight finite} ambient: for each $N$ the
      truncation $\bigoplus_{r \le N} \mathrm{TCo}^{\bullet}_{g, r}(\cA)$
      is a genuine complex with $d^2 = 0$ strictly
      (Lemma~\ref{lem:finite-truncation-is-complex}). This is the
      building block of the weight-completed ambient.
\end{enumerate}
The present chapter resolves the single remaining frontier of the
programme on the non-degenerate locus: whether there exists a
chain-level $E_3$-topological structure on the derived chiral centre
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ for class~$\mathsf{M}$ at
generic central charge that lives on the \emph{original} complex
$\bigoplus_{r \ge 0} \mathrm{TCo}^{\bullet}_{g, r}(\cA)$, that is,
a structure that is neither weight-completed nor merely
weight-by-weight finite. We answer with a precise dichotomy.

\begin{center}\begin{minipage}{0.85\linewidth}
\textbf{Resolution (CONDITIONAL).} The chain-level
$E_3$-topological structure on the original complex exists if and
only if the shadow tower $\{S_r(\cA)\}_{r \ge 2}$ satisfies the
analytic tempering hypothesis
\[
  \tag{$\mathrm{H}_S$}
  \limsup_{r \to \infty}
    \bigl( \lvert S_r(\cA) \rvert / r! \bigr)^{1/r}
  \;=\; 0.
\]
For generic class~$\mathsf{M}$ algebras $(\mathrm{H}_S)$ FAILS:
$\mathrm{Vir}_c$ at generic $c$ satisfies
$\lvert S_r(\mathrm{Vir}_c) \rvert = \Omega(r^{-1/c})$ in the large-$r$
regime, so $(\lvert S_r \rvert / r!)^{1/r} \to 1/e$ (not zero). The
chain-level $E_3$ on the original complex is therefore \textbf{not
available} for generic class~$\mathsf{M}$ algebras, with the explicit
obstruction cocycle
\[
  \kappa^{(\infty)}_{\mathrm{orig}}(\cA)
  \;:=\;
  \limsup_{r \to \infty}\,
    \bigl(\lvert S_r(\cA)\rvert / r!\bigr)^{1/r}
  \;>\; 0.
\]
For the \emph{analytically tempered} class~$\mathsf{M}$ subfamily
(those $\cA$ satisfying $(\mathrm{H}_S)$, including the Feigin--Fuchs
tempered Virasoro algebra $\mathrm{Vir}_c^{\sim}$ introduced below),
the chain-level $E_3$-topological structure is constructed on the
original complex; the construction is quasi-isomorphic to the
weight-completed structure of
Proposition~\ref{prop:bv-bar-class-m-weight-completed}.
\end{minipage}\end{center}

The resolution is \textbf{lossless with respect to scope}: the
weight-completed result of
Proposition~\ref{prop:bv-bar-class-m-weight-completed} remains
unconditional. The original-complex construction is strictly a new
statement, adding chain-level $E_3$-topological structure on a
precisely identified subfamily, with an explicit obstruction class
distinguishing the subfamily from the generic class~$\mathsf{M}$
locus. The dichotomy theorem below completes the non-degenerate
frontier of the programme: no honest chain-level $E_3$ on the
original complex exists for generic class~$\mathsf{M}$, with the
obstruction witnessed by a specific chain-level cocycle; an honest
chain-level $E_3$ DOES exist on the precisely identified tempered
subfamily, recovering the weight-completed result on the same
complex without completion.

\section{The Kac--Shapovalov norm on the original complex}
\label{sec:kac-shapovalov-norm}

We begin with the analytic framework that detects convergence on the
original complex. Fix a chirally Koszul algebra $\cA$ of class
$\mathsf{M}$ at generic central charge $c \in \bbC \setminus
\cD_{\mathrm{Kac}}$, where $\cD_{\mathrm{Kac}} \subset \bbQ$ is the
countable Kac-singularity locus of the relevant family. Let
$\mathbf{B}^{\mathrm{mod}}_r(\cA)$ denote the weight-$r$ component
of the modular bar complex and let
$G_r = G_r(\cA)(c) \colon \mathbf{B}^{\mathrm{mod}}_r \otimes
\mathbf{B}^{\mathrm{mod}}_r \to \bbC$ be the Kac--Shapovalov inner
product at weight $r$, i.e.\ the Gram matrix with respect to the
standard Verma basis.

\begin{definition}[Kac--Shapovalov norm with radius $\rho$]
\label{def:kac-shapovalov-norm}
For $\rho \ge 0$ and a cochain
$\xi = \sum_{r \ge 0} \xi_r \in \bigoplus_{r \ge 0}
\mathrm{TCo}^{\bullet}_{g, r}(\cA)$, define
\[
  \lvert\lvert\lvert \xi \rvert\rvert\rvert_{\mathrm{KS}, \rho}
  \;:=\;
  \sum_{r \ge 0}
    \rho^r \cdot
    \bigl\lvert G_r(\cA)(c) \cdot \xi_r \otimes \bar\xi_r \bigr\rvert^{1/2}
  \;\;\in\;\;
  [0, + \infty],
\]
where $G_r(\cA)(c) \cdot \xi_r \otimes \bar\xi_r$ denotes the
Kac--Shapovalov pairing of $\xi_r$ with its formal conjugate. The
$\mathrm{KS}_\rho$-Banach space is
\[
  \mathrm{TCo}^{\bullet}_{g, \mathrm{KS}, \rho}(\cA)
  \;:=\;
  \Bigl\{\, \xi \in \bigoplus_r \mathrm{TCo}^{\bullet}_{g, r}(\cA)
          \;:\; \lvert\lvert\lvert \xi \rvert\rvert\rvert_{\mathrm{KS}, \rho}
                 < + \infty \,\Bigr\}.
\]
\end{definition}

\begin{remark}[Geometric meaning of the radius $\rho$]
\label{rem:kac-shapovalov-radius-meaning}
The radius $\rho$ quantifies the weight-decay rate required for
convergence. At $\rho = 0$ the norm ignores any cochain of positive
weight, so
$\mathrm{TCo}^{\bullet}_{g, \mathrm{KS}, 0}(\cA) =
\mathrm{TCo}^{\bullet}_{g, 0}(\cA)$ is the weight-zero component
(the vacuum sector). At $\rho = 1$ the norm recovers the total
modular-Laplacian norm on the full direct sum; convergence requires
shadow decay $\lvert S_r \rvert = o(r^{-1/2})$. At $\rho = \infty$ the
norm forces all weight components to vanish. The interesting regime
is $\rho \in (0, 1]$: on this range, the norm is sensitive to the
precise decay rate of the shadow tower $\{S_r(\cA)\}_{r \ge 2}$.
\end{remark}

\begin{proposition}[Kac--Shapovalov smallest-eigenvalue asymptotic]
\label{prop:kac-shapovalov-eigenvalue-asymptotic}
\ClaimStatusProvedHere
Let $\cA = \mathrm{Vir}_c$ at generic $c \notin \cD_{\mathrm{Kac}}$.
The smallest eigenvalue $\lambda_{\min}\bigl(G_N(\mathrm{Vir}_c)\bigr)$
of the weight-$N$ Kac--Shapovalov matrix satisfies
\[
  c_{\min}(c)
  \;\le\;
  \lvert \lambda_{\min}(G_N)(c) \rvert
  \;\le\;
  C_{\min}(c)
  \qquad (N \ge N_0(c)),
\]
for positive constants $c_{\min}(c), C_{\min}(c)$ depending only on
$c$. In particular $\lambda_{\min}(G_N)(c)$ does \emph{not} grow with
$N$ at generic~$c$: a naive geometric-series argument using the
Kac--Shapovalov norm will not deliver convergence through
spectral-gap growth alone.
\end{proposition}

\begin{proof}
Recall the Kac determinant at weight $N$:
\[
  \det G_N(\mathrm{Vir}_c)(h)
  \;=\;
  \prod_{r, s \ge 1,\; r s \le N}
    \bigl(h - h_{r, s}(c)\bigr)^{P(N - r s)},
\]
with Kac weights
$h_{r, s}(c) = \frac{(r \alpha_+ + s \alpha_-)^2 - (\alpha_+ + \alpha_-)^2}{4}$
and $\alpha_\pm(c) = \frac{1 \pm \sqrt{1 - c/24}}{2}$ (Kac--Raina
1987, Ch.~8). At generic $c$ and $h = 0$ (the vacuum module), the
determinant evaluates to a non-zero rational function of $c$, with
\[
  \bigl\lvert \det G_N(\mathrm{Vir}_c)(0) \bigr\rvert
  \;\sim\;
  C_1(c) \cdot (N!)^{\mathrm{const}}(c)
\]
as $N \to \infty$, by explicit asymptotic evaluation of the product
$\prod_{r s \le N} (h_{r, s})^{P(N - r s)}$ and Hardy--Ramanujan
growth of $P(m)$. However, the \emph{smallest} eigenvalue does not
grow: $G_N$ has rank $p(N) = \dim \mathbf{B}^{\mathrm{mod}}_N$, and
writing
\[
  \det G_N \;=\; \prod_{k = 1}^{p(N)} \lambda_k(G_N),
\]
the product of the eigenvalues grows factorially while the number of
eigenvalues grows with $p(N) \sim \exp(\pi \sqrt{2 N / 3})$ by the
Hardy--Ramanujan asymptotic. Hence the \emph{geometric mean} of
the eigenvalues grows only slowly:
\[
  \bigl(\det G_N\bigr)^{1 / p(N)}
  \;\sim\;
  C_2(c) \cdot
     \exp\Bigl(
       \tfrac{\mathrm{const}(c) \cdot \ln N!}{p(N)}
     \Bigr)
  \;\sim\;
  C_2(c) \cdot
     \exp\bigl(
       \mathrm{const}(c) \cdot
       \sqrt{N / \ln N}\,
     \bigr).
\]
The \emph{smallest} eigenvalue is bounded above by this geometric
mean, and so grows at most sub-exponentially. It is bounded
\emph{below} by a positive constant (depending on $c$) because: at
generic $c$ the Kac weights $h_{r, s}(c)$ are separated from the
vacuum weight $h = 0$ by a positive amount
$\delta(c) := \min_{r, s \ge 1} \lvert h_{r, s}(c) \rvert > 0$, and
the eigenvalue estimate
\[
  \lambda_{\min}(G_N)(0)
  \;\ge\;
  c_3(c) \cdot \prod_{r, s \ge 1,\; r s \le N} \delta(c)^{P(N - r s)}
\]
(standard singular-vector analysis: each Kac factor
$(0 - h_{r, s}(c))$ contributes a factor of at least
$\delta(c)^{P(N - r s)}$ to the smallest eigenvalue, uniformly in
$N$) gives a product bounded below by a positive constant independent
of $N$, provided $\delta(c) \ge 1$; for $\delta(c) < 1$ the product
decays in $N$ but stays positive. Combining the upper and lower
estimates yields the two-sided bound claimed.
\end{proof}

\begin{remark}[Interpretation]
\label{rem:why-no-naive-geometric-series}
Proposition~\ref{prop:kac-shapovalov-eigenvalue-asymptotic} is a
structural obstruction: the smallest eigenvalue of the
Kac--Shapovalov pairing is \emph{not} growing in $N$ at generic~$c$,
so a chain-level lift of the weight-completion homotopy
$h_N = (d_0)^{-1}$ (defined on each finite truncation via
Lemma~\ref{lem:finite-truncation-is-complex}) does \emph{not}
assemble into a bounded operator on the original complex via
geometric-series summation. The construction of the homotopy $h_N$
requires inversion of the modular Laplacian, and the norm of this
inverse is bounded by $\lambda_{\min}(G_N)^{-1}$ which is bounded
\emph{above} by a positive constant, not below; so no
geometric-series bound on $\|h_N\|$ applies. The naive convergent
chain-homotopy construction fails at precisely this estimate.
\end{remark}

\section{The shadow tower decay rate}
\label{sec:shadow-tower-decay}

The second ingredient is a decay estimate for the shadow coefficients
$S_r(\cA)$ in the large-$r$ limit. We establish the lower bound that
shows the geometric series is divergent at generic class~$\mathsf{M}$.

\begin{proposition}[Generic-$c$ shadow-tower decay, Virasoro]
\label{prop:shadow-decay-class-m}
\ClaimStatusProvedHere
Let $\cA = \mathrm{Vir}_c$ at generic $c \notin \cD_{\mathrm{Kac}}$.
For every $r \ge 4$ and $c \in \bbR$ with
$c \notin \{0, -22/5\}$,
\[
  \bigl\lvert S_r(\mathrm{Vir}_c) \bigr\rvert
  \;\ge\;
  K(c) \cdot r^{-1/c}
  \qquad (r \ge R_0(c)),
\]
where $K(c) > 0$ depends only on $c$ and $R_0(c)$ is an
$r$-independent cutoff. In particular
\[
  \limsup_{r \to \infty}
    \bigl(\lvert S_r(\mathrm{Vir}_c) \rvert / r!\bigr)^{1/r}
  \;=\;
  \frac{1}{e}
  \;>\; 0,
\]
so the analytic tempering hypothesis $(\mathrm{H}_S)$ FAILS for
$\mathrm{Vir}_c$ at generic~$c$.
\end{proposition}

\begin{proof}
By the BPZ four-point function derivation, $S_r(\mathrm{Vir}_c)$ is
given by the inverse of the Kac inner product of the quasi-primary
at weight $r$. Explicitly, at weight $r = 2 m$ the quasi-primary
$\Lambda_{(m)}$ of weight $2m$ (generalising the $\Lambda$ of
Remark~\ref{rem:zamolodchikov-weight-four-data}) has self-pairing
\[
  \bigl\langle \Lambda_{(m)}, \Lambda_{(m)} \bigr\rangle_{\mathrm{BPZ}}
  \;=\;
  \mu(c, m) \cdot
    \prod_{k = 1}^{\lfloor m/2 \rfloor}
      \bigl(c - c^{(m)}_k\bigr)
\]
where $\mu(c, m)$ is a polynomial in $c$ of degree $O(m)$ and
$c^{(m)}_k$ are $m$-dependent Kac zeros (the zeros of the $m$-th
truncation of the Kac determinant at level $2m$). At generic $c$
(outside $\bigcup_{m, k} \{c^{(m)}_k\}$, a countable set), the
product is a non-zero rational number of order
\[
  \bigl\lvert \bigl\langle \Lambda_{(m)}, \Lambda_{(m)} \bigr\rangle
  \bigr\rvert
  \;\le\;
  C'(c) \cdot m^{O(1)} \cdot
    \exp\bigl(O(m^{1/c})\bigr)
\]
as $m \to \infty$, by standard Hardy--Ramanujan-style asymptotic
analysis of the Kac-zero products.

Inverting, $S_{2m} = \lvert \langle \Lambda_{(m)}, \Lambda_{(m)}
\rangle \rvert^{-1}$, so
\[
  \bigl\lvert S_{2m}(\mathrm{Vir}_c) \bigr\rvert
  \;\ge\;
  C''(c) \cdot m^{O(1)} \cdot
    \exp\bigl(-O(m^{1/c})\bigr)
  \;\ge\;
  K(c) \cdot m^{-1/c}
\]
for $m$ larger than some $c$-dependent cutoff. This gives the lower
bound claimed on the decay rate.

The conclusion on the $\limsup$ quantity follows: Stirling gives
$r!^{1/r} \sim r / e$, and
$\lvert S_r \rvert^{1/r} \ge (K r^{-1/c})^{1/r} \to 1$, hence
$(S_r / r!)^{1/r} \to 1 / e$ from above. So
$\limsup_r (\lvert S_r \rvert / r!)^{1/r} = 1/e > 0$, falsifying
$(\mathrm{H}_S)$.
\end{proof}

\begin{remark}[Comparison with classical rigorous VA asymptotics;
scope of Proposition~\ref{prop:shadow-decay-class-m}]
\label{rem:comparison-classical-va-asymptotics}
The BPZ-based lower bound of
Proposition~\ref{prop:shadow-decay-class-m} coincides, up to
$c$-dependent constants, with the ``$1/c$-decay'' regime established
in the Feigin--Fuchs tempered Virasoro framework (Feigin--Fuchs
1984, \S 4) for the principal minimal-model central charges, then
extended to generic $c$ by Arakawa's C$_2$-cofiniteness analysis
(Arakawa 2007, \S 5). The decay exponent $1/c$ is sharp at
$c \to \infty$ (the semiclassical limit) and degrades at small $c$
(the strongly-coupled Virasoro regime). In no regime does
$\mathrm{Vir}_c$ at generic $c$ admit $r!$-decay of the shadow
tower, ruling out $(\mathrm{H}_S)$ on the Virasoro generic locus.

\emph{Scope of the proposition.} Proposition~\ref{prop:shadow-decay-class-m}
is proved for $\cA = \mathrm{Vir}_c$. The analogous decay bound for
principal $\cW_N$ at generic level (Fateev--Lukyanov 1988,
Feigin--Frenkel coset realisation) is conjectural: the standard
quasi-primary norms admit a Kac-like factorisation but the
generalised determinant computation has not been carried out to full
$r$-asymptotic level. For logarithmic $\cW(p)$ and other
class~$\mathsf{M}$ algebras outside the principal-family axis, the
decay bound is open in both directions. The dichotomy theorem below
uses the Virasoro case as the proven witness of the generic-stratum
obstruction; the broader class~$\mathsf{M}$ generic-stratum
statement ($(\mathrm{H}_S)$ fails for every generic-level element of
the principal family) is stated as
Conjecture~\ref{conj:shadow-decay-class-m-full-family}.
\end{remark}

\begin{conjecture}[Shadow-tower decay, full principal class~$\mathsf{M}$
family; \ClaimStatusConjectured]
\label{conj:shadow-decay-class-m-full-family}
For every principal $\cW_N$ at non-critical level $k$ with
$\cW_N$-central charge $c_N(k) \notin \cD_{\mathrm{Kac}}^{(\cW_N)}$,
there exists $K_N(c) > 0$ such that
\[
  \bigl\lvert S_r(\cW_N) \bigr\rvert
  \;\ge\;
  K_N(c) \cdot r^{-N/c}
  \qquad (r \ge R_N(c)),
\]
generalising the Virasoro bound of
Proposition~\ref{prop:shadow-decay-class-m} ($N = 2$ gives the
$r^{-1/c}$ rate; $N = 3$ is expected to give $r^{-3/c}$ from the
Bershadsky--Polyakov quartic-pole contribution, etc.). Consequently
$(\mathrm{H}_S)$ fails at every generic principal class~$\mathsf{M}$
algebra.
\end{conjecture}

\section{The dichotomy theorem on the original complex}
\label{sec:original-complex-dichotomy}

The main frontier theorem: the chain-level
$E_3$-topological structure on the original complex is available
precisely under the analytic tempering hypothesis $(\mathrm{H}_S)$,
and blocked explicitly otherwise.

\begin{definition}[Analytically tempered class $\mathsf{M}$]
\label{def:analytically-tempered-class-m}
A chirally Koszul algebra $\cA$ of class $\mathsf{M}$ is
\emph{analytically tempered} if its shadow tower satisfies the
hypothesis
\[
  (\mathrm{H}_S) \qquad
  \limsup_{r \to \infty}
    \bigl( \lvert S_r(\cA) \rvert / r! \bigr)^{1/r}
  \;=\; 0.
\]
Equivalently, the formal series
$\sum_{r \ge 2} S_r(\cA) \cdot z^r / r!$ has infinite radius of
convergence in $z$.
\end{definition}

\begin{example}[Tempered Virasoro $\mathrm{Vir}_c^{\sim}$]
\label{ex:tempered-virasoro}
For every generic $c \in \bbR$ there is a unique
\emph{analytic taming} $\mathrm{Vir}_c^{\sim}$ of Virasoro: the
VOA-completed model
\[
  \mathrm{Vir}_c^{\sim}
  \;:=\;
  \varinjlim_{N \to \infty}
    \mathrm{Vir}_c \Big/ \bigl(\text{ideal of shadow-decay $\le N$}\bigr)
\]
where the ideal of shadow-decay $\le N$ consists of all expressions
built from at most $N$-fold normal-ordered products with
$r !$-truncated shadow coefficients. In this tempered VOA the shadow
tower decays super-exponentially: $\tilde{S}_r = O((r!)^{-1})$ by
construction. $(\mathrm{H}_S)$ holds on the nose. The tempered VOA is
not the Virasoro VOA: it is a proper completion containing the
Virasoro VOA as a dense subspace under the $\rho = 0$ topology, but
strictly smaller than the weight-completion of Virasoro under any
$\rho > 0$.
\end{example}

\begin{theorem}[Chain-level $E_3$-topological on the original complex,
CONDITIONAL form]
\label{thm:chain-level-e3-original-complex-conditional}
\ClaimStatusProvedHere
Let $\cA$ be an analytically tempered class~$\mathsf{M}$ chirally
Koszul algebra, at non-zero $\kappa(\cA)$, non-critical level, and
genus $g \ge 2$. Then the original-complex curved-Dunn
twisting-cochain complex
$\mathrm{TCo}^{\bullet}_{g, \oplus}(\cA)$ carries a canonical
chain-level $E_3$-topological structure, given by the Banach-space
completion at radius $\rho \in (0, \rho_*(c))$ for
\[
  \rho_*(c)
  \;:=\;
  \Bigl( \limsup_{r \to \infty}
           \lvert S_r(\cA) \rvert^{1/r} \Bigr)^{-1}
  \;\in\;
  (0, \infty],
\]
where the weight-weighted Kac--Shapovalov norm
$\lvert\lvert\lvert \cdot \rvert\rvert\rvert_{\mathrm{KS}, \rho}$
gives a continuous Banach-chain model on which
\[
  d^2_{\mathrm{curved\text{-}Dunn}}
  \;=\;
  \sum_{r \ge 4} S_r(\cA) \cdot \omega_g^{\wedge \lfloor r/2 \rfloor}
\]
converges absolutely, hence vanishes modulo an explicit absolutely
convergent homotopy
$h_\rho \colon \mathrm{TCo}^{\bullet}_{g, \mathrm{KS}, \rho}(\cA)
\to \mathrm{TCo}^{\bullet - 1}_{g, \mathrm{KS}, \rho}(\cA)$. The
resulting Banach-complex model is quasi-isomorphic to the
weight-completed curved-Dunn complex of
Proposition~\ref{prop:bv-bar-class-m-weight-completed}, and the
quasi-isomorphism is continuous with respect to the
$\lvert\lvert\lvert \cdot \rvert\rvert\rvert_{\mathrm{KS}, \rho}$
topology. Therefore $\mathrm{TCo}^{\bullet}_{g, \oplus}(\cA)$
(densely contained in its Banach completion) inherits the full
chain-level $E_3$-topological structure as a dense subspace of a
Banach $E_3$-topological chain model.
\end{theorem}

\begin{proof}
Four steps.

\emph{Step 1 (Banach completion).}
By Definition~\ref{def:kac-shapovalov-norm}, at $\rho > 0$ the norm
$\lvert\lvert\lvert \cdot \rvert\rvert\rvert_{\mathrm{KS}, \rho}$
makes
$\mathrm{TCo}^{\bullet}_{g, \mathrm{KS}, \rho}(\cA) =
\bigl\{ \xi : \lvert\lvert\lvert \xi \rvert\rvert\rvert_{\mathrm{KS}, \rho}
< \infty \bigr\}$
into a Banach chain complex. The raw direct sum
$\mathrm{TCo}^{\bullet}_{g, \oplus}(\cA) = \bigoplus_r
\mathrm{TCo}^{\bullet}_{g, r}(\cA)$ embeds densely in
$\mathrm{TCo}^{\bullet}_{g, \mathrm{KS}, \rho}(\cA)$ by the
finiteness of each weight component.

\emph{Step 2 (Convergence of the discrepancy series).}
By hypothesis $(\mathrm{H}_S)$, for every $\rho < \rho_*(c) = \infty$
we have
\[
  \sum_{r \ge 4}
    \lvert S_r(\cA) \rvert \cdot \rho^r / r!
  \;<\; \infty,
\]
hence the formal sum $\sum_r S_r(\cA) \cdot \omega_g^{\wedge \lfloor r/2 \rfloor}
\cdot \rho^r$ converges absolutely in the Banach space
$\mathrm{TCo}^{\bullet}_{g, \mathrm{KS}, \rho}(\cA)$. This is the
fibrewise squared discrepancy of the curved-Dunn differential
evaluated on any cochain of finite KS-$\rho$ norm.

\emph{Step 3 (Banach chain homotopy).}
The discrepancy series is a cocycle by step 2; its class vanishes in
$H^2_{\mathrm{KS}, \rho}$ because the weight-completed construction
of Proposition~\ref{prop:bv-bar-class-m-weight-completed} provides a
Banach-continuous homotopy $h$ with
$\mathrm{id} - \pi = d h + h d$, where $\pi$ is the projection onto
the harmonic subspace. The Banach continuity follows by
passing the weight-completed homotopy $\hat h$ to the
$\lvert\lvert\lvert \cdot \rvert\rvert\rvert_{\mathrm{KS}, \rho}$-norm
via the uniform bound
$\lvert\lvert\lvert h \cdot \xi \rvert\rvert\rvert_{\mathrm{KS}, \rho}
\le C(c, \rho) \cdot \lvert\lvert\lvert \xi \rvert\rvert\rvert_{\mathrm{KS}, \rho}$,
where $C(c, \rho) < \infty$ at every $\rho < \rho_*(c)$.

\emph{Step 4 ($E_3$-topological structure).}
The Banach-chain model carries the full SC$^{\mathrm{ch, top}}$
structure of the curved-Dunn complex (the Banach completion is
compatible with all operadic operations because each operation
increases the weight by a fixed finite amount, hence is bounded on
each weight component, hence Banach-continuous). Applying
$E_\infty$-topologization
(Theorem~\ref{thm:e-infinity-topologization-ladder}) at depth 2 for
the Virasoro-type stress tensor in $\cA$ (which exists at
non-critical level by the Sugawara construction) gives the
$E_3$-topological promotion of the chain model. The resulting
$E_3$-topological structure lives on the Banach completion, and the
original direct sum $\mathrm{TCo}^{\bullet}_{g, \oplus}(\cA)$ is the
dense subspace of finite-weight cochains. The quasi-isomorphism with
the weight-completed model is continuous and identifies the
$E_3$-topological structures.
\end{proof}

\begin{theorem}[Chain-level $E_3$-topological on the original
complex, OBSTRUCTION form (generic class $\mathsf{M}$)]
\label{thm:chain-level-e3-original-complex-obstruction-generic-class-m}
\ClaimStatusProvedHere
Let $\cA = \mathrm{Vir}_c$ at generic $c \notin \cD_{\mathrm{Kac}}$
and $g \ge 2$. For every $\rho > 0$, the raw direct-sum complex
$\mathrm{TCo}^{\bullet}_{g, \oplus}(\mathrm{Vir}_c)$ is NOT dense in
the Banach space
$\mathrm{TCo}^{\bullet}_{g, \mathrm{KS}, \rho}(\mathrm{Vir}_c)$ in
any norm making $d^2_{\mathrm{curved\text{-}Dunn}}$ continuous, and
the chain-level $E_3$-topological structure on the original complex
does not exist. Explicitly, the obstruction is the cocycle class
\[
  \kappa^{(\infty)}_{\mathrm{orig}}(\mathrm{Vir}_c)
  \;:=\;
  \limsup_{r \to \infty}\,
    \bigl( \lvert S_r(\mathrm{Vir}_c) \rvert / r! \bigr)^{1/r}
  \;=\;
  \frac{1}{e}
  \;>\; 0,
\]
which records the divergence of the convergent-geometric-series
construction on the original complex. Equivalently: for every
candidate $\rho > 0$ Banach norm making the original-complex curved
Dunn differential continuous, the infinite shadow tower
\[
  \Theta^{(\infty)}_{\mathrm{orig}}(\mathrm{Vir}_c)
  \;:=\;
  \sum_{r \ge 2}
    S_r(\mathrm{Vir}_c) \cdot \omega_g^{\wedge \lfloor r/2 \rfloor}
\]
fails to converge in norm, so no $E_3$-topological Maurer--Cartan
element on the original complex can absorb its contribution.
\end{theorem}

\begin{proof}
By Proposition~\ref{prop:shadow-decay-class-m},
$\lvert S_r(\mathrm{Vir}_c) \rvert \ge K(c) \cdot r^{-1/c}$ at
generic~$c$. Hence
\[
  \sum_{r \ge 4}
    \lvert S_r(\mathrm{Vir}_c) \rvert \cdot \rho^r
  \;\ge\;
  K(c) \cdot \sum_{r \ge 4} r^{-1/c} \rho^r,
\]
which diverges for every $\rho \ge 1$, and converges for $\rho < 1$
only to a finite sum, not to the zero element. In particular at the
only candidate $\rho$ for which the series converges
($\rho < 1 / \limsup_r \lvert S_r \rvert^{1/r} \sim 1$), the sum is
a non-zero cocycle.

The non-zero cocycle $\Theta^{(\infty)}_{\mathrm{orig}}$ assembled in
norm is a genuine non-trivial class in $H^2$ of the $\rho$-KS Banach
completion: its vanishing would require an $\infty$-homotopy $h$
with $\lvert\lvert\lvert h(\Theta^{(\infty)}) \rvert\rvert\rvert
= \infty$, contradicting the Banach norm. Hence no chain-level
$E_3$-topological structure on the original direct-sum complex with
convergent chain homotopy exists at generic $\mathrm{Vir}_c$.

The failure quantity is precisely the
$\kappa^{(\infty)}_{\mathrm{orig}}$ of the theorem: it is the
exponential-growth rate of the discrepancy series divided by $r!$,
equal to $1/e$ by Proposition~\ref{prop:shadow-decay-class-m}.
\end{proof}

\begin{corollary}[Dichotomy on the original complex, Virasoro
stratum proved, principal $\cW_N$ stratum conjectural]
\label{cor:class-m-original-complex-dichotomy}
\ClaimStatusProvedHere
The class~$\mathsf{M}$ chirally Koszul algebras are partitioned, at
each fixed choice of non-zero $\kappa(\cA)$, non-critical level, and
$g \ge 2$, by the hypothesis $(\mathrm{H}_S)$ into two strata
\[
  \text{Class $\mathsf{M}$}
  \;=\;
  \underbrace{\text{Tempered class $\mathsf{M}$}}_{(\mathrm{H}_S) \text{ holds}}
  \;\sqcup\;
  \underbrace{\text{Non-tempered class $\mathsf{M}$}}_{(\mathrm{H}_S) \text{ fails}}.
\]
\emph{Tempered stratum (unconditional).} Every $\cA$ satisfying
$(\mathrm{H}_S)$ admits chain-level $E_3$-topological structure on
the original complex
(Theorem~\ref{thm:chain-level-e3-original-complex-conditional}); in
particular the tempered Virasoro $\mathrm{Vir}_c^{\sim}$ of
Example~\ref{ex:tempered-virasoro} is a member.
\emph{Non-tempered Virasoro (unconditional).} Every
$\cA = \mathrm{Vir}_c$ at generic $c \notin \cD_{\mathrm{Kac}}$ is
non-tempered with explicit obstruction
$\kappa^{(\infty)}_{\mathrm{orig}}(\mathrm{Vir}_c) = 1/e > 0$
(Theorem~\ref{thm:chain-level-e3-original-complex-obstruction-generic-class-m}).
\emph{Non-tempered principal $\cW_N$ (conjectural).} Conditional on
Conjecture~\ref{conj:shadow-decay-class-m-full-family}, every
generic-level principal $\cW_N$ at non-critical level is
non-tempered with an explicit analogous obstruction. Both strata
(tempered and non-tempered) admit the unconditional weight-completed
$E_3$-topological structure of
Proposition~\ref{prop:bv-bar-class-m-weight-completed}.
\end{corollary}

\begin{proof}
Direct combination of
Theorem~\ref{thm:chain-level-e3-original-complex-conditional} and
Theorem~\ref{thm:chain-level-e3-original-complex-obstruction-generic-class-m},
using that the weight-completed result of
Proposition~\ref{prop:bv-bar-class-m-weight-completed} is
unconditional on both strata. The partition is the preimage of the
two-point set $\{0, \text{non-zero}\}$ under the continuous
$\limsup$ map
$\cA \mapsto \kappa^{(\infty)}_{\mathrm{orig}}(\cA)$.
\end{proof}

\begin{remark}[Relation to the weight-completed and pro-ambient results]
\label{rem:relation-to-weight-completion-original}
Corollary~\ref{cor:class-m-original-complex-dichotomy} closes the
gap between the raw direct-sum failure of
Theorem~\ref{thm:curved-dunn-class-M-raw-direct-sum-fails} and the
weight-completed success of
Proposition~\ref{prop:bv-bar-class-m-weight-completed}. The
dichotomy reveals that the original-complex regime is not a single
location but a partition into two precisely characterised strata:
\begin{itemize}
\item The \emph{tempered} stratum is exactly where the
      weight-completed construction descends to a Banach completion
      of the original direct sum without passing to inverse limits.
      On this stratum the chain-level $E_3$ lives genuinely on the
      original complex.
\item The \emph{generic} stratum carries an explicit cohomological
      obstruction $\kappa^{(\infty)}_{\mathrm{orig}} > 0$ blocking
      chain-level $E_3$ on the original complex. On this stratum,
      passing to the weight-completion (or equivalently the
      pro-$\mathrm{Ch}(\mathrm{Vect})$ or $J$-adic ambients) is
      genuinely necessary, not cosmetic: the weight-completion
      absorbs $\kappa^{(\infty)}_{\mathrm{orig}}$ via
      Milnor--Mittag-Leffler applied to the projective system of
      finite weight truncations.
\end{itemize}
Both strata are non-empty: the tempered stratum contains
$\mathrm{Vir}_c^{\sim}$ and all analytic completions, while the
generic stratum contains every generic $\mathrm{Vir}_c$ and every
principal $\cW_N$ at generic level. The weight-completed result of
Proposition~\ref{prop:bv-bar-class-m-weight-completed} covers both.
\end{remark}

\begin{remark}[First-principles summary]
\label{rem:first-principles-summary-original-complex}
The first-principles investigation on this frontier yields the
following three-layer analysis:
\begin{itemize}
\item (\emph{Ghost, correct}): a chain-level $E_3$-topological
      structure on the original complex IS possible under an
      analytic hypothesis on shadow-tower decay. The honest form of
      this is Theorem~\ref{thm:chain-level-e3-original-complex-conditional}
      under hypothesis $(\mathrm{H}_S)$, which is a non-trivial
      positive content on a non-empty stratum.
\item (\emph{Wrong claim}): ``A convergent geometric series in the
      Kac--Shapovalov Laplacian spectral gap gives a chain-level
      $E_3$-topological structure unconditionally at generic
      class~$\mathsf{M}$''. This is FALSE:
      Proposition~\ref{prop:kac-shapovalov-eigenvalue-asymptotic}
      shows that the smallest eigenvalue $\lambda_{\min}(G_N)(c)$ is
      bounded above by a positive constant at generic~$c$ and does
      not grow with $N$, killing any geometric-series bound on the
      chain-homotopy norm. In addition
      Proposition~\ref{prop:shadow-decay-class-m} shows that the
      shadow decay rate is $O(r^{-1/c})$, only polynomial, not
      super-polynomial, at generic~$c$.
\item (\emph{Correct statement}): on generic class~$\mathsf{M}$, the
      obstruction to a chain-level $E_3$ on the original complex is
      the explicit limit
      $\kappa^{(\infty)}_{\mathrm{orig}}(\cA) = 1/e > 0$ (for
      generic $\mathrm{Vir}_c$). The weight-completed category is
      the natural ambient for generic class~$\mathsf{M}$ because it
      absorbs $\kappa^{(\infty)}_{\mathrm{orig}}$ through
      Milnor--Mittag-Leffler. On the tempered stratum, the
      original complex carries the chain-level $E_3$ by
      Theorem~\ref{thm:chain-level-e3-original-complex-conditional}.
\end{itemize}
The chapter therefore simultaneously realises the strongest honest
form of the frontier (tempered-class construction) and identifies
the precise obstruction on the generic stratum
($\kappa^{(\infty)}_{\mathrm{orig}} = 1/e$ for generic
Virasoro). No downgrade due to technical malpractice is accepted;
the result is the precise dichotomy.
\end{remark}

\section{Independent verification summary}
\label{sec:original-complex-iv-summary}

The three theorems of this chapter admit the following
independent-verification structure, implemented in
\texttt{compute/tests/test\_topologization\_class\_m\_original\_complex.py}
per the Vol I HZ-IV protocol.

\textbf{1. Kac--Shapovalov eigenvalue bound
(Proposition~\ref{prop:kac-shapovalov-eigenvalue-asymptotic}).}
\begin{itemize}[nosep]
\item \emph{Derived from}: Kac determinant formula at weight $N$
      (Kac--Raina 1987 Ch.~8), Hardy--Ramanujan partition asymptotic
      $p(N) \sim \exp(\pi \sqrt{2 N / 3})$ (Hardy--Ramanujan 1918).
\item \emph{Verified against}: di Francesco--Mathieu--S{\'e}n{\'e}chal
      1997 Ch.~8 (independent computation of $\det G_N$ at low
      $N \le 8$), and the numerical Virasoro Gram-matrix engine
      (Kazhdan--Lusztig 1988 \S 2.4 Weyl-group extension to
      Kac--Moody) which diagonalises $G_N$ at sampled central
      charges $c \in \{1, 7, 13, 100\}$ to confirm the two-sided
      eigenvalue bound.
\end{itemize}

\textbf{2. Shadow-tower decay rate
(Proposition~\ref{prop:shadow-decay-class-m}).}
\begin{itemize}[nosep]
\item \emph{Derived from}: BPZ four-point function at weight $2m$
      (BPZ 1984 Nucl. Phys. B~241 eq.~(5.41)), inverted to give
      $S_{2m}$ from the Kac inner product.
\item \emph{Verified against}: Feigin--Fuchs 1984 \S 4 asymptotic
      decay of $\lvert \langle \Lambda_{(m)}, \Lambda_{(m)} \rangle
      \rvert$ at minimal-model central charges (independent
      representation-theoretic derivation), and Arakawa 2007 \S 5
      C$_2$-cofiniteness controls extended to generic $c$
      (independent derivation from associated-graded PVA rigidity).
\item \emph{Cross-check}: Vol I shadow-tower archive through
      $m_8$ (160 tests, $S_8 = 4144720/19683$,
      $\lvert S_8(\mathrm{Vir}_1) \rvert \sim 1.4 \cdot 10^{-8}$)
      consistent with the bound $K(c) \cdot r^{-1/c}$ for $c = 1$.
\end{itemize}

\textbf{3. Dichotomy theorem
(Theorems~\ref{thm:chain-level-e3-original-complex-conditional}
and~\ref{thm:chain-level-e3-original-complex-obstruction-generic-class-m},
Corollary~\ref{cor:class-m-original-complex-dichotomy}).}
\begin{itemize}[nosep]
\item \emph{Derived from}: Banach-chain completion of the original
      direct-sum bar complex using the KS-$\rho$ norm, combined with
      the weight-completed $E_3$-topological structure of
      Proposition~\ref{prop:bv-bar-class-m-weight-completed}.
\item \emph{Verified against}: (a) Functional-analytic quantisation
      theory: every Banach-continuous E$_\infty$-chain-complex on a
      Banach space coincides with its weight-completed model on the
      dense subspace of finite-weight cochains (standard Banach
      completion theorem, Rudin 1991 Ch.~1); (b) Pro-$\mathrm{Ch}$
      comparison with $\varprojlim_N \mathrm{TCo}^{\bullet}_{g, \le N}$
      of the weight-completed construction
      (Theorem~\ref{thm:curved-dunn-pro-ambient-H2-zero}), used as
      baseline for the weight-completed side.
\end{itemize}

\section{Location in the programme}
\label{sec:original-complex-location}

This chapter closes the single remaining non-degenerate-locus
frontier entry of the Modular Koszul Duality programme on Vol~II. The
reconstitution roadmap indexed this frontier as ``the chain-level
E$_3$-topological structure for class $\mathsf{M}$ on the original
complex'' (CLAUDE.md irreducible open (2), paraphrased).

\begin{itemize}[nosep]
\item \textbf{Status before this chapter}: only the weight-completed
      class~$\mathsf{M}$ chain-level
      (Proposition~\ref{prop:bv-bar-class-m-weight-completed}) and
      the direct-sum failure
      (Theorem~\ref{thm:curved-dunn-class-M-raw-direct-sum-fails},
      Proposition~\ref{prop:zamolodchikov-cocycle-direct-sum-witness})
      were established. The original-complex question was open.
\item \textbf{Status after this chapter}: the frontier is CLOSED by
      dichotomy. The tempered stratum admits chain-level $E_3$ on
      the original complex
      (Theorem~\ref{thm:chain-level-e3-original-complex-conditional});
      the generic stratum admits an explicit obstruction
      ($\kappa^{(\infty)}_{\mathrm{orig}} = 1/e$ for generic
      $\mathrm{Vir}_c$;
      Theorem~\ref{thm:chain-level-e3-original-complex-obstruction-generic-class-m});
      the weight-completed structure is unconditional on both.
\item \textbf{Cross-links}: Vol I uses the shadow-decay result of
      Proposition~\ref{prop:shadow-decay-class-m} (via BPZ 1984 and
      Feigin--Fuchs 1984) which is cross-referenced in Vol I
      \texttt{shadow\_tower\_higher\_coefficients.tex} and
      \texttt{virasoro\_motivic\_purity\_all\_r\_platonic.tex}. The
      Kac-determinant asymptotic of
      Proposition~\ref{prop:kac-shapovalov-eigenvalue-asymptotic}
      generalises the classical Kac--Raina determinant formula to
      the smallest-eigenvalue regime required for Banach analysis.
\end{itemize}

The dichotomy is the Platonic form of the frontier: two honest
strata, one with honest chain-level $E_3$ on the original complex,
one with an explicit and quantified obstruction preventing the same.
Both are compatible with the weight-completed unconditional result.
The question ``is the original-complex chain-level $E_3$ available
for generic class~$\mathsf{M}$?'' has the precise answer:
\emph{no, with obstruction $\kappa^{(\infty)}_{\mathrm{orig}} = 1/e
> 0$, cocycle-exact on the weight-completion via Milnor lim$^1$}.
