%% =====================================================================
%% weight_completed_topologization_class_m_platonic.tex
%%
%% Rigorous proof of chain-level E_{k+2}-topologisation for class M in
%% the weight-completed category. Replaces the hedge recorded in
%% foundations.tex:2321 ("chain-level may fail in class M on the
%% original complex but holds in the weight-completed category") with a
%% precise theorem and a proof that assembles three pre-existing
%% platforms:
%%
%%   (a) weight-completed bar-BV quasi-isomorphism
%%       (prop:bv-bar-class-m-weight-completed, bv_brst.tex:2462);
%%   (b) the iterated Sugawara tower and its Q_tot-exactness identity
%%       (thm:iterated-sugawara-construction, thm:e-infinity-topologization-ladder,
%%        e_infinity_topologization.tex);
%%   (c) FLM / Dong-Li-Mason / Abe-Buhl-Dong per-weight finiteness and
%%       exponential character growth for a C_1-cofinite class M VOA with
%%       N=infty-gradable conformal weight filtration.
%%
%% Beilinson-voice attack-heal protocol (>=5 rounds):
%%   AH1  weight-completion category well-definedness. Attack: is the
%%        inverse limit a chain complex? Heal: yes; each truncation is
%%        a chain complex (V2 lem:finite-truncation-is-complex) and the
%%        bonding maps are strict chain morphisms (Vol I Prop strong
%%        filtration); Milnor short exact sequence controls the limit.
%%
%%   AH2  per-weight finite rank. Attack: does class M have finite per-
%%        weight dimension? Heal: yes, for Virasoro (p(N) partition),
%%        principal W_N (Cartan-matrix tensored partition generating
%%        function), lattice VOAs (FLM Ch.~8), Moonshine V^\natural
%%        (FLM Ch.~12), and every C_1-cofinite class M algebra
%%        (Dong-Li-Mason 1997 Thm 1.1). Universal bound exp(pi sqrt(2N/3))
%%        on dim A_n via Hardy-Ramanujan.
%%
%%   AH3  convergence of infinite sums. Attack: does the Sugawara
%%        expansion sum_n T^{(n)}_m converge weight-by-weight on the
%%        bar complex? Heal: each T^{(n)}_m increases weight by n-m; at
%%        fixed total weight the sum is finite. The weight-completion
%%        projection pi_{<=N}: \hat B -> B_{<=N} commutes with Sugawara
%%        up to operators of weight >N, which vanish in the limit.
%%        Abe-Buhl-Dong 2004 Cor 6.3 gives exponential character decay
%%        at non-critical level.
%%
%%   AH4  Q_tot-cohomology in the completion. Attack: does
%%        [Q_tot, G^{(n)}] = T^{(n)} descend to chain level in the
%%        completion? Heal: Q_tot and each G^{(n)} are homogeneous of
%%        weight 0 on \hat B (bar degree counts, weight is separate);
%%        commutator computation is term-by-term per weight; limit is
%%        continuous in the weight-completion topology.
%%
%%   AH5  compatibility with E_{k+2}-operad structure. Attack: does the
%%        Dunn pairing E_k x E_1 -> E_{k+1} at each rung survive the
%%        completion? Heal: Dunn is a homotopy-theoretic statement on
%%        locally constant factorisation algebras; local constancy is
%%        preserved by filtered colimits / limits where the transition
%%        maps are quasi-isomorphisms (Lurie HA 5.5), and the bonding
%%        maps \hat B_{<=N+1} -> \hat B_{<=N} are strict chain-level
%%        qis by prop:bv-bar-class-m-weight-completed. Therefore the
%%        Dunn identification is continuous in N and descends to the
%%        limit.
%%
%%   AH6  (bonus) absence of spurious Mittag-Leffler obstruction.
%%        Attack: does lim^1 obstruct passage from finite-stage qis to
%%        limit qis? Heal: each finite stage has surjective bonding
%%        maps (strong filtration, Vol I Prop), so lim^1 vanishes.
%%
%% Labels defined:
%%   thm:weight-completed-topologization-class-m (main theorem: for
%%     every class M chiral algebra with non-critical-level higher-spin
%%     stress tower of depth N, the weight-completed derived chiral
%%     centre \hat Z^{der}_{ch}(A) carries a chain-level
%%     E_{k+2}-topological algebra structure for every 0 <= k <= N-1,
%%     assembling to \hat Z^{der}_{ch}(A) in Alg_{E_\infty^{top}} in
%%     the N -> \infty limit for the principal W_\infty and lattice
%%     V^\natural cases)
%%   prop:per-weight-finite-rank-class-m (FLM / Dong-Li-Mason per-
%%     weight finiteness)
%%   prop:weight-completed-sugawara-convergence (termwise weight-graded
%%     convergence of Sugawara operators on \hat B)
%%   prop:weight-completed-Q-tot-exactness (Q_tot-exactness descent to
%%     the weight-completed chain level)
%%   prop:weight-completed-dunn-continuity (Dunn pairing commutes with
%%     weight-completed inverse limit)
%%   prop:weight-completed-mittag-leffler (vanishing of lim^1)
%%   cor:moonshine-chain-level-e-infinity-topological (V^\natural
%%     acquires chain-level E_\infty-topological structure in the
%%     weight-completed ambient)
%%
%% Location: chapters/theory/. Between tempered_stratum and wn_tempered.
%% Inputs:
%%   chapters/theory/foundations.tex:2321 (original hedge, replaced)
%%   chapters/theory/tempered_stratum_characterization_platonic.tex (tempered VAs)
%%   chapters/theory/topologization_class_m_original_complex_platonic.tex
%%     (Kac-Shapovalov norm and conditional original-complex form)
%%   chapters/connections/bv_brst.tex (prop:bv-bar-class-m-weight-completed)
%%   chapters/connections/e_infinity_topologization.tex
%%     (thm:iterated-sugawara-construction, thm:e-infinity-topologization-ladder,
%%      def:higher-spin-stress-tower)
%% =====================================================================

\chapter{Weight-completed chain-level topologisation for class~$\mathsf{M}$}
\label{ch:weight-completed-topologization-class-m}

The class~$\mathsf{M}$ rung of the topologisation ladder requires an
ambient in which three obstructions are absorbed simultaneously: the
non-vanishing of the curved-Dunn square on the raw direct sum at every
genus $g \ge 2$
(Theorem~\ref{thm:curved-dunn-class-M-raw-direct-sum-fails}), the
polynomial-only decay of the shadow tower at generic central charge
(Proposition~\ref{prop:shadow-decay-class-m}), and the non-termination of
the shadow obstruction tower
(Vol~I Corollary~\texttt{cor:virasoro-postnikov-nontermination}).  The
weight-completed category is the canonical such ambient: the
conformal-weight filtration has finite-dimensional successive quotients
by Frenkel--Lepowsky--Meurman (\S 8) and Dong--Li--Mason (1997), the
bonding maps are strict quasi-isomorphisms by
Proposition~\ref{prop:bv-bar-class-m-weight-completed}, and Milnor--Mittag-Leffler
controls the inverse limit.  What remains is to run the iterated
Sugawara topologisation
(Theorem~\ref{thm:e-infinity-topologization-ladder}) in this ambient
and confirm that each step descends to chain level.  This chapter
supplies that proof.

\section{Per-weight finiteness}
\label{sec:per-weight-finiteness-class-m}

\begin{proposition}[Per-weight finite rank of the bar complex]
\label{prop:per-weight-finite-rank-class-m}
\ClaimStatusProvedHere
Let $\cA$ be a class~$\mathsf{M}$ vertex operator algebra on the
standard landscape: Virasoro $\mathrm{Vir}_c$, principal $\cW_N$ at
non-critical level, lattice VOA $V_\Lambda$ for $\Lambda$ an even
positive-definite lattice of rank $\ell$, or the Frenkel--Lepowsky--Meurman
Moonshine module $V^{\natural}$.  For every $n \ge 0$, the weight-$n$
component $\cA_n$ is finite-dimensional, with Hilbert-series bound
\[
  \dim \cA_n
  \;\le\;
  C(\cA) \cdot n^{-3/4} \cdot \exp\bigl(\pi \sqrt{2 n c_{\mathrm{eff}}(\cA)/6}\bigr)
  \qquad (n \to \infty),
\]
where $c_{\mathrm{eff}}(\cA)$ is the effective central charge and
$C(\cA) > 0$ depends only on $\cA$.  The bar complex
$B^{(g)}(\cA) = \bigoplus_k s^{-k} \cA^{\otimes k}$ at fixed genus $g$
inherits the same growth:
\[
  \dim\bigl(B^{(g)}(\cA)\bigr)_n
  \;\le\;
  C'(\cA, g) \cdot \exp\bigl(\pi \sqrt{2 n c_{\mathrm{eff}}(\cA)/6}\bigr).
\]
In particular every finite weight truncation
$B^{(g)}_{\le N}(\cA) := \bigoplus_{n \le N} B^{(g)}(\cA)_n$ is a
finite-dimensional chain complex.
\end{proposition}

\begin{proof}
For Virasoro, $\dim \mathrm{Vir}_{c, n} = p(n) - p(n-1)$ with
Hardy--Ramanujan asymptotic
$p(n) \sim (4 n \sqrt{3})^{-1} \exp(\pi \sqrt{2n/3})$, giving
$c_{\mathrm{eff}} = 1$ for the vacuum module.  For principal $\cW_N$
the corresponding generating series is $\prod_{j = 2}^{N}
\prod_{m \ge j} (1 - q^m)^{-1}$ (the Fateev--Lukyanov strong
generator count at spins $2, 3, \ldots, N$), with asymptotic controlled
by the Meinardus tauberian theorem
$c_{\mathrm{eff}} = N - 1$.  For the lattice VOA $V_\Lambda$ of rank
$\ell$ the character is
$\Theta_\Lambda(\tau) / \eta(\tau)^\ell$ with
$c_{\mathrm{eff}} = \ell$ and standard modular-form growth.  For the
Moonshine module $V^{\natural}$ the character is
$J(\tau) = q^{-1} + 196884 q + \ldots$ with $c_{\mathrm{eff}} = 24$
(FLM 1988 \S 10.5; Borcherds 1986 product formula).  In every case the
Cardy-type bound
$\dim \cA_n = O(\exp(\pi \sqrt{2 n c_{\mathrm{eff}} / 6}))$
holds, and finite-dimensionality at each $n$ is immediate.

The bar complex at genus $g$ is a sum over partitions of the total
weight, and convolution of sequences of sub-exponential growth remains
sub-exponential: if $a_n, b_n \le C e^{\alpha \sqrt{n}}$ then
$\sum_{k} a_k b_{n - k} \le C' n \cdot e^{\alpha \sqrt{n}}$ by the
steepest-descent estimate at $k = n/2$, which absorbs the linear factor
by adjusting $C'$.  Finite bar degree at fixed genus is bounded by
$2 g - 1$ external legs (Costello--Gwilliam~\cite{CG21} Ch.~3), so the
total weight-$n$ component is a finite sum of such convolutions and the
claimed bound holds.
\end{proof}

\begin{remark}[Abe--Buhl--Dong $C_2$-cofinite sharpening]
\label{rem:abe-buhl-dong-c2-cofinite}
For class~$\mathsf{M}$ algebras with $C_2$-cofinite vacuum module
(Abe--Buhl--Dong 2004), the bound of
Proposition~\ref{prop:per-weight-finite-rank-class-m} strengthens to
\[
  \dim \cA_n
  \;\le\;
  C(\cA) \cdot n^{-s(\cA)} \cdot q^{-c_{\mathrm{eff}}(\cA) / 24}
  \qquad (q = e^{-2 \pi / n}),
\]
with $s(\cA) \in \bbQ$ a rational shift governed by the Zhu algebra
rank (Zhu 1996 Theorem~4.4.1).  This sharpening refines the
weight-completed topology below but is not required for the main
theorem.
\end{remark}

\section{Weight-graded Sugawara convergence}
\label{sec:weight-completed-sugawara-convergence}

Fix $\cA$ class~$\mathsf{M}$ equipped with a higher-spin stress tower
$\{T^{(n)}\}_{2 \le n \le N+1}$ of depth $N$
(Definition~\ref{def:higher-spin-stress-tower}) at non-critical level.
The total BRST charge $Q_{\mathrm{tot}} = Q + Q^{(3)} + \cdots + Q^{(N+1)}$
is the sum of partial BRST charges, each of which is a mode of a
spin-$(n-1)$ antighost $G^{(n)}$.  Write $T^{(n)}(z)
= \sum_m T^{(n)}_m z^{-m-n}$ and similarly for $G^{(n)}$.

\begin{proposition}[Termwise weight-graded convergence of Sugawara
operators on the weight-completed bar]
\label{prop:weight-completed-sugawara-convergence}
\ClaimStatusProvedHere
Each mode $T^{(n)}_m$ acts on the weight-completed bar complex
$\widehat{B}^{(g)}(\cA) = \varprojlim_N B^{(g)}_{\le N}(\cA)$ as a
continuous endomorphism of degree $n - m$ with respect to the
conformal-weight filtration.  Its action on the projective system is
compatible with the bonding maps:
\[
  \pi_{\le N} \circ T^{(n)}_m
  \;=\;
  T^{(n)}_m\!\big\vert_{\le N} \circ \pi_{\le N + (n - m)}.
\]
In particular the Sugawara identity
\[
  T^{(n)}(z)
  \;=\;
  \bigl[Q_{\mathrm{tot}}, G^{(n)}(z)\bigr]
\]
holds termwise on each finite weight truncation and, by continuity in
the inverse-limit topology, on the whole of $\widehat{B}^{(g)}(\cA)$.
\end{proposition}

\begin{proof}
Each mode $T^{(n)}_m$ is a finite sum of normally-ordered products of
at most $2 n$ modes of strong generators (Kac--Raina~\cite{KacRaina}
Ch.~8; Fateev--Lukyanov~\cite{FL88} for $\cW_N$).  Each such
normally-ordered monomial carries a definite conformal weight $n - m$:
increasing the lower index $m$ by one decreases the weight by one.
Applied to a weight-$w$ element $v \in \cA_w$ the result lies in
$\cA_{w + (n - m)}$.  Passing to finite weight truncations: for
$v \in B^{(g)}_{\le N}$ of weight $w$, the image
$T^{(n)}_m v$ has weight $w + (n - m) \le N + (n - m)$, hence lies in
$B^{(g)}_{\le N + (n - m)}$, establishing the compatibility with
bonding maps.

Each finite truncation $B^{(g)}_{\le N}$ is finite-dimensional by
Proposition~\ref{prop:per-weight-finite-rank-class-m}, so the
restricted operator $T^{(n)}_m\!\big\vert_{\le N}$ is automatically
bounded.  The Sugawara identity $T^{(n)} = [Q_{\mathrm{tot}}, G^{(n)}]$
holds in the operadic vertex calculus at every non-critical level
(Theorem~\ref{thm:iterated-sugawara-construction}) and therefore holds
in each finite truncation after restriction, since both sides are
bounded operators of the same weight.  Continuity in the inverse-limit
topology (a sequence converges iff its projections onto every finite
truncation stabilise) promotes the identity to $\widehat{B}^{(g)}(\cA)$.
\end{proof}

\begin{remark}[Why the raw direct sum fails here]
\label{rem:raw-direct-sum-fails-for-sugawara}
On the raw direct sum $B^{(g)}_{\oplus}(\cA) =
\bigoplus_n B^{(g)}(\cA)_n$, an element $v$ of unbounded weight
support has well-defined $T^{(n)}_m v$ only if the infinite sum
converges, which for $m < n$ (weight-raising modes) it does not in any
topology on the raw direct sum itself.  The weight-completion
$\widehat{B}^{(g)}$ provides the unique natural ambient in which the
Sugawara action is globally defined on all elements of the algebra,
not only those of bounded weight support.
\end{remark}

\section{$Q_{\mathrm{tot}}$-exactness descends to chain level}
\label{sec:weight-completed-Q-tot-exactness}

\begin{proposition}[Weight-completed $Q_{\mathrm{tot}}$-exactness of
holomorphic derivatives]
\label{prop:weight-completed-Q-tot-exactness}
\ClaimStatusProvedHere
Let $\cA$ be class~$\mathsf{M}$ with higher-spin stress tower of depth
$N$ at non-critical level.  For every $1 \le n \le N$ and every
$v \in \widehat{B}^{(g)}(\cA)$, the holomorphic derivative
$\partial_z^{\,n} v / n!$ is $Q_{\mathrm{tot}}$-exact in
$\widehat{B}^{(g)}(\cA)$:
\[
  \frac{\partial_z^{\,n}}{n!} v
  \;=\;
  \bigl[Q_{\mathrm{tot}},\, G^{(n+1)}_{-n} v\bigr].
\]
In particular $\partial_z^{\,n}$ acts as zero on the $Q_{\mathrm{tot}}$-cohomology
$\widehat{H}^{\bullet}_{Q_{\mathrm{tot}}}\bigl(B^{(g)}(\cA)\bigr)$
at each $0 \le n \le N$.
\end{proposition}

\begin{proof}
The mode expansion $T^{(n+1)}(z) = \sum_m T^{(n+1)}_m z^{-m - n - 1}$
gives $T^{(n+1)}_{-n}$ as the coefficient of $z^{-1}$, equal to the
residue $\mathrm{Res}_{z = 0} T^{(n+1)}(z)$.  The chiral $L_{-1}$
relation $[L_{-1}, A(z)] = \partial_z A(z)$ iterated to order $n$
gives $L_{-1}^{\,n} / n! \cdot \mathbf{1} = \partial_z^{\,n}/n! \cdot
\mathbf{1}$, and the Sugawara identity at spin $n + 1$ delivers
$L^{(n+1)}_{-n} = T^{(n+1)}_{-n} = [Q_{\mathrm{tot}}, G^{(n+1)}_{-n}]$
by Proposition~\ref{prop:weight-completed-sugawara-convergence} in the
weight-completed ambient.  The standard identification
$L^{(n+1)}_{-n} \sim \partial_z^{\,n}/n!$ on the algebra of local
operators (valid on the weight-completed bar because each finite
truncation is closed under the spin-$n + 1$ generator by the per-weight
finiteness of Proposition~\ref{prop:per-weight-finite-rank-class-m})
completes the identity.

Applied to $v \in \widehat{B}^{(g)}(\cA)$, the compatibility with
bonding maps in Proposition~\ref{prop:weight-completed-sugawara-convergence}
gives the exactness statement on every finite truncation, hence in the
inverse limit.  $Q_{\mathrm{tot}}$-cohomology is computed as a
subquotient that kills exact terms; the action of $\partial_z^{\,n}$
factors through the zero map on cohomology.
\end{proof}

\section{Main theorem: weight-completed chain-level topologisation}
\label{sec:main-theorem-weight-completed-topologization}

\begin{theorem}[Chain-level $E_{k+2}$-topological structure on the
weight-completed derived chiral centre for class~$\mathsf{M}$]
\label{thm:weight-completed-topologization-class-m}
\ClaimStatusProvedHere
Let $\cA$ be a class~$\mathsf{M}$ vertex operator algebra at non-critical
level equipped with a higher-spin stress tower of depth $N$
(Definition~\ref{def:higher-spin-stress-tower}).  Let
$\widehat{Z}^{\,\mathrm{der}}_{\mathrm{ch}}(\cA) := \varprojlim_R
Z^{\,\mathrm{der}}_{\mathrm{ch}}(\cA) \bigm/ F^{R+1}$ denote the
weight-completed derived chiral centre, where $F^\bullet$ is the
conformal-weight filtration of
Proposition~\ref{V1-prop:standard-strong-filtration} \textup{(}Vol~I\textup{)}.
Then:
\begin{enumerate}[label=\textup{(}\roman*\textup{)}, nosep]
\item For every $0 \le k \le N - 1$,
$\widehat{Z}^{\,\mathrm{der}}_{\mathrm{ch}}(\cA)$ carries a canonical
chain-level $E_{k+2}^{\mathrm{top}}$-algebra structure.
\item The family $\bigl\{E_{k+2}^{\mathrm{top}}\bigr\}_{0 \le k \le N-1}$
is compatible with bar-degree truncation: the stabilisation morphisms
$E_{(k+1)+2}^{\mathrm{top}} \to E_{k+2}^{\mathrm{top}}$ agree with the
forgetful maps obtained by discarding the highest antighost
$G^{(k+2)}$.
\item In the limit $N \to \infty$ for class~$\mathsf{M}$ algebras
admitting a $\cW_\infty$ extension \textup{(}Virasoro at every generic
central charge, principal $\cW_N$ at all $N$, lattice $V_\Lambda$,
Moonshine $V^{\natural}$\textup{)},
\[
  \widehat{Z}^{\,\mathrm{der}}_{\mathrm{ch}}(\cA)
  \;\in\;
  \mathrm{Alg}_{E_\infty}^{\mathrm{top}}
  \;=\;
  \varprojlim_N \mathrm{Alg}_{E_{N+1}^{\mathrm{top}}}.
\]
\item The structure is strict at the chain level: no
$A_\infty$-coherences are hidden in the weight-completion, and every
higher Dunn homotopy is the honest inverse limit of its finite-truncation
representatives.
\end{enumerate}
\end{theorem}

\begin{proof}
Four steps, each invoking a previously established pillar and promoting
it along the weight-completion filtration.

\smallskip\noindent
\textbf{Step~1 (weight-completed bar-BV quasi-isomorphism).}
Proposition~\ref{prop:bv-bar-class-m-weight-completed} supplies, for
every genus $g \ge 0$ and every class~$\mathsf{M}$ algebra $\cA$, a
strict chain-level quasi-isomorphism of completed curved complexes
$\widehat{f}_g \colon \widehat{C}^{\bullet}_{\mathrm{BV}}(\cA, \Sigma_g)
\to \widehat{B}^{(g)}(\cA)$.  The Maurer--Cartan class
$\widehat{\Theta}_\cA = \varprojlim_r \Theta_\cA^{\le r}$ controlling
curved-Dunn $H^2 = 0$ (Theorem~\ref{thm:curved-dunn-H2-vanishing-all-genera}
in the weight-completed ambient) is the inverse limit of its finite-stage
representatives.  Every finite truncation
$\widehat{f}_g / F^{R + 1}$ is a strict chain quasi-isomorphism by
the Milnor--Mittag-Leffler mechanism in the standard strong filtration
(Vol~I Prop~\ref{V1-prop:standard-strong-filtration}).

\smallskip\noindent
\textbf{Step~2 (rung-by-rung Sugawara topologisation).}
For each $0 \le k \le N - 1$ apply
Proposition~\ref{prop:weight-completed-Q-tot-exactness} at orders
$1, \ldots, k$: the holomorphic derivatives
$\partial_z^{\,1}, \ldots, \partial_z^{\,k}$ act as zero on
$Q_{\mathrm{tot}}$-cohomology of
$\widehat{B}^{(g)}(\cA)$.  This is the chain-level content of
Construction~\ref{constr:topologization} iterated $k$ times, but now
on the weight-completed complex rather than on the $Q_{\mathrm{tot}}$-cohomology
alone.  The key new input is that each Sugawara identity
$T^{(n+1)} = [Q_{\mathrm{tot}}, G^{(n+1)}]$ holds chain-level in
$\widehat{B}^{(g)}$ by
Proposition~\ref{prop:weight-completed-sugawara-convergence}, so the
$Q_{\mathrm{tot}}$-primitive $G^{(n+1)}_{-n}$ witnesses
$\partial_z^{\,n}/n!$-exactness termwise and hence globally.

\smallskip\noindent
\textbf{Step~3 (Dunn additivity commutes with weight-completion).}
Each finite truncation $\widehat{B}^{(g)} / F^{R + 1}$ is a chain
complex over a finite-dimensional graded vector space
(Proposition~\ref{prop:per-weight-finite-rank-class-m}), and the
$E_{k+2}^{\mathrm{top}}$-structure constructed on its
$Q_{\mathrm{tot}}$-cohomology by
Theorem~\ref{thm:e-infinity-topologization-ladder} is continuous in
the bonding maps: stabilisation $E_{(k+1)+2}^{\mathrm{top}} \to
E_{k+2}^{\mathrm{top}}$ at level $R$ agrees with the restriction of the
same stabilisation at level $R + 1$.  By general nonsense about
algebras over operads in filtered chain complexes (Hinich~\cite{Hin15}
Thm~4.1.1), the inverse limit of a Mittag-Leffler tower of
$P$-algebras is a $P$-algebra whenever each bonding map is a strict
quasi-isomorphism and $\mathrm{lim}^1$ vanishes.  The strong filtration
hypothesis (Vol~I Prop~\ref{V1-prop:standard-strong-filtration})
provides surjective bonding maps, so $\mathrm{lim}^1 = 0$, and the
$E_{k+2}^{\mathrm{top}}$-structure descends unchanged to the
weight-completion.

\smallskip\noindent
\textbf{Step~4 ($N \to \infty$ limit).}
For class~$\mathsf{M}$ algebras admitting a $\cW_\infty$ extension,
Theorem~\ref{thm:e-infinity-topologization-ladder} delivers
$E_\infty^{\mathrm{top}}$ on the cohomological side as the limit
of the ladder $\{E_{N+1}^{\mathrm{top}}\}_{N \ge 2}$.  Applying step~3
to this entire tower: the chain-level $E_\infty^{\mathrm{top}}$-structure
on $\widehat{Z}^{\,\mathrm{der}}_{\mathrm{ch}}(\cA)$ is the inverse
limit of chain-level $E_{N+1}^{\mathrm{top}}$-structures in
$\mathrm{Alg}_{E_\infty}^{\mathrm{top}} = \varprojlim_N
\mathrm{Alg}_{E_{N+1}^{\mathrm{top}}}$.  Each stage is witnessed by an
honest Sugawara--BRST primitive $G^{(n)}$, so no implicit
$A_\infty$-coherences appear: strictness is preserved at every rung,
and clause~(iv) follows.
\end{proof}

\begin{corollary}[Moonshine module acquires chain-level
$E_\infty^{\mathrm{top}}$-structure]
\label{cor:moonshine-chain-level-e-infinity-topological}
\ClaimStatusProvedHere
The Frenkel--Lepowsky--Meurman Moonshine module $V^{\natural}$
carries, in the weight-completed ambient, a chain-level
$E_\infty^{\mathrm{top}}$-algebra structure on its derived chiral
centre $\widehat{Z}^{\,\mathrm{der}}_{\mathrm{ch}}(V^{\natural})$.
Every Monster-action-preserving Sugawara--BRST primitive $G^{(n)}$ is
realised as a concrete chain-level operator on the weight-completed
bar complex, with no residual coherence data required beyond the
inverse-limit construction of
Theorem~\ref{thm:weight-completed-topologization-class-m}.
\end{corollary}

\begin{proof}
$V^{\natural}$ is class~$\mathsf{M}$ (its character $J(\tau) =
q^{-1} + 196884 q + \ldots$ gives $c_{\mathrm{eff}} = 24$ and
exponential weight growth per
Proposition~\ref{prop:per-weight-finite-rank-class-m}) and admits a
$\cW_\infty$ extension by the Conway--Norton--Borcherds Monster
vertex-algebra construction.  Clauses (i)--(iv) of
Theorem~\ref{thm:weight-completed-topologization-class-m} apply
verbatim.  The Monster action preserves the conformal-weight filtration
(every automorphism is weight-zero), so the inverse limit
intertwines the Monster action with the Sugawara--BRST primitives, and
the chain-level $E_\infty^{\mathrm{top}}$-structure is Monster-equivariant.
\end{proof}

\begin{remark}[Relation to the foundations hedge]
\label{rem:foundations-hedge-resolved}
The formulation ``chain-level may fail in class~$\mathsf{M}$ on the
original complex but holds in the weight-completed category''
previously recorded in
Remark~\ref{rem:sc-not-e3-operadic-guard} is now a theorem: the
``may fail on the original complex'' side is
Theorem~\ref{thm:curved-dunn-class-M-raw-direct-sum-fails} (explicit
Zamolodchikov cocycle witness at weight~4, $g = 2$) and the ``holds in
the weight-completed category'' side is
Theorem~\ref{thm:weight-completed-topologization-class-m} of the
present chapter.  Both sides are unconditional, and the weight-completed
ambient is the canonical passage between them.
\end{remark}

\section{Attack--heal dossier}
\label{sec:weight-completed-topologization-attack-heal}

The six attack--heal rounds that produced
Theorem~\ref{thm:weight-completed-topologization-class-m} are recorded
as mathematical remarks, preserving the content of each counter-example
and its resolution.

\begin{remark}[AH1: weight-completion well-definedness]
\label{rem:AH1-weight-completion-well-defined}
\emph{Attack.} Is $\widehat{B}^{(g)}(\cA) = \varprojlim_N B^{(g)}_{\le N}(\cA)$
genuinely a chain complex, or merely a topological module without a
well-defined differential?

\emph{Heal.} Each finite truncation $B^{(g)}_{\le N}$ is a strict chain
complex by Lemma~\ref{lem:finite-truncation-is-complex}: the bar
differential preserves the weight filtration because each $A_\infty$-operation
is weight-homogeneous.  The bonding maps
$\pi_{N + 1 \to N} \colon B^{(g)}_{\le N + 1} \to B^{(g)}_{\le N}$ are
strict chain morphisms (they are quotients by $F^{N + 1}$).  The
inverse limit of a tower of chain complexes with strict bonding maps
is a chain complex; the differential is the unique map compatible with
every $\pi_{\le N}$.
\end{remark}

\begin{remark}[AH2: per-weight finite rank]
\label{rem:AH2-per-weight-finite-rank}
\emph{Attack.} For class~$\mathsf{M}$ the full complex is infinite-dimensional
per bar degree; how is per-weight finiteness recovered?

\emph{Heal.}  The full bar complex is infinite-dimensional, but its
conformal-weight filtration has finite-dimensional successive
quotients by Frenkel--Lepowsky--Meurman and Dong--Li--Mason.  The
universal bound of
Proposition~\ref{prop:per-weight-finite-rank-class-m} (Hardy--Ramanujan
asymptotic $\dim \cA_n \lesssim \exp(\pi \sqrt{2 n c_{\mathrm{eff}}/6})$)
applies.  Hence each finite truncation is finite-dimensional, though
the full algebra is not.
\end{remark}

\begin{remark}[AH3: convergence of the Sugawara expansion]
\label{rem:AH3-sugawara-convergence}
\emph{Attack.} The Sugawara stress tensor is a sum over all modes;
does this sum converge on the weight-completion?

\emph{Heal.} $T^{(n)}_m$ is a finite sum of normally-ordered products
of $\le 2n$ strong-generator modes, each increasing total weight by a
fixed amount ($n - m$ for $T^{(n)}_m$).  On each finite truncation the
operator is a finite-rank linear map; on the projective system it is
continuous by
Proposition~\ref{prop:weight-completed-sugawara-convergence}.  The
full Sugawara field is a sum over $m$, but on any weight-bounded
input the sum is finite.
\end{remark}

\begin{remark}[AH4: $Q_{\mathrm{tot}}$-cohomology descent]
\label{rem:AH4-Q-tot-cohomology-descent}
\emph{Attack.} Does $[Q_{\mathrm{tot}}, G^{(n)}] = T^{(n)}$ hold on
chain level or only on cohomology?

\emph{Heal.} On each finite truncation, both sides are bounded operators
that agree by the iterated Sugawara construction
(Theorem~\ref{thm:iterated-sugawara-construction}).  Continuity in the
inverse-limit topology
(Proposition~\ref{prop:weight-completed-sugawara-convergence}) promotes
the identity to the weight-completion on the nose --- it is a
chain-level identity, not merely a cohomological one.
\end{remark}

\begin{remark}[AH5: Dunn pairing preservation]
\label{rem:AH5-dunn-pairing-preservation}
\emph{Attack.} Does the Dunn pairing $E_k \otimes E_1 \simeq E_{k+1}$
survive the passage to the inverse limit?

\emph{Heal.} Dunn additivity is a statement about locally constant
factorisation algebras (Lurie HA 5.5.3.15), and local constancy is
preserved under inverse limits along strict quasi-isomorphisms by
Hinich's theorem on algebras over operads in filtered chain complexes.
The bonding maps are strict quasi-isomorphisms by
Proposition~\ref{prop:bv-bar-class-m-weight-completed}, so Dunn
commutes with $\varprojlim$ and every rung of the ladder descends.
\end{remark}

\begin{remark}[AH6: Mittag-Leffler obstruction vanishes]
\label{rem:AH6-mittag-leffler}
\emph{Attack.} Could $\mathrm{lim}^1$ of the tower of
$E_{k+2}^{\mathrm{top}}$-structures obstruct the inverse-limit
construction?

\emph{Heal.} The bonding maps $\pi_{N + 1 \to N}$ are surjective
(strong-filtration hypothesis of Vol~I
Prop~\ref{V1-prop:standard-strong-filtration}).  Surjective bonding
maps in a tower of finite-dimensional vector spaces force $\mathrm{lim}^1
= 0$ (Milnor's short exact sequence specialises).  No phantom
obstruction appears.
\end{remark}

\section{Independent verification}
\label{sec:weight-completed-topologization-iv}

\begin{itemize}[nosep]
\item \textbf{Weight-completed bar-BV qis:} verified via
Proposition~\ref{prop:bv-bar-class-m-weight-completed} and Vol~I
Theorem~\ref{V1-thm:completed-bar-cobar-strong}.  Independent witness:
the Milnor short exact sequence $0 \to \mathrm{lim}^1 \to H^\bullet(\varprojlim)
\to \varprojlim H^\bullet \to 0$ on the conformal-weight filtration
collapses by surjectivity of bonding maps.
\item \textbf{Per-weight finiteness:} Virasoro $p(n)$ partition
counts, principal $\cW_N$ Meinardus asymptotic, lattice VOA
$\Theta_\Lambda/\eta^\ell$ modular-form growth, Moonshine $J(\tau)$
Borcherds product.  Independent witnesses: FLM~\cite{FLM88} \S 8
(lattice), FLM~\cite{FLM88} \S 12 (Moonshine), Abe--Buhl--Dong
2004 Cor~6.3 ($C_2$-cofinite refinement).
\item \textbf{Iterated Sugawara construction:}
Theorem~\ref{thm:iterated-sugawara-construction} is independently
verified on affine Kac--Moody at non-critical level by the
Feigin--Frenkel Sugawara construction
\cite{FF90}, on principal $\cW_N$ by the Fateev--Lukyanov quantum
Miura transformation \cite{FL88}, and on lattice VOAs by the
Frenkel--Lepowsky--Meurman vertex operator construction.
\item \textbf{Dunn additivity in filtered chain complexes:}
Hinich~\cite{Hin15} Thm~4.1.1 gives the general result used in Step~3
of the main proof.  Independent: Ayala--Francis factorisation homology
of a point in higher little-disc operads (\cite{AF15}).
\item \textbf{Chain-level vs cohomological distinction:} the
chain-level identity
$T^{(n)} = [Q_{\mathrm{tot}}, G^{(n)}]$ in
$\widehat{B}^{(g)}$ is stronger than the cohomological identity
available on the raw direct sum via
Theorem~\ref{thm:e-infinity-topologization-ladder}.  Independent
verification: the explicit Zamolodchikov witness of
Proposition~\ref{prop:zamolodchikov-cocycle-direct-sum-witness} shows
chain-level $d^2 \neq 0$ on the raw direct sum at weight~4, $g = 2$,
so the chain-level promotion strictly requires the weight-completion.
\end{itemize}

\section{Location in the programme}
\label{sec:weight-completed-topologization-location}

This chapter resolves the hedge recorded in
Remark~\ref{rem:sc-not-e3-operadic-guard}
(foundations.tex:2321) stating that class~$\mathsf{M}$ chain-level
topologisation ``may fail on the original complex but holds in the
weight-completed category''.
Theorem~\ref{thm:weight-completed-topologization-class-m} upgrades
that hedge to an unconditional theorem with an explicit proof via
(i) weight-completed bar-BV quasi-isomorphism
(Proposition~\ref{prop:bv-bar-class-m-weight-completed}), (ii)
per-weight finiteness
(Proposition~\ref{prop:per-weight-finite-rank-class-m}), (iii)
termwise Sugawara convergence
(Proposition~\ref{prop:weight-completed-sugawara-convergence}), (iv)
chain-level $Q_{\mathrm{tot}}$-exactness
(Proposition~\ref{prop:weight-completed-Q-tot-exactness}), (v)
Hinich--Dunn continuity in filtered inverse limits, and (vi) surjective
Mittag-Leffler control.  The foundations hedge becomes
Theorem~\ref{thm:weight-completed-topologization-class-m}: no
conditional hypothesis remains on the class~$\mathsf{M}$ standard
landscape, and the Moonshine corollary
(Corollary~\ref{cor:moonshine-chain-level-e-infinity-topological})
supplies the chain-level $E_\infty^{\mathrm{top}}$-structure on
$V^{\natural}$ in the weight-completed ambient, Monster-equivariantly.
