\documentclass[11pt]{amsart}
\usepackage[localtheorems]{raeez-math-template}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\providecommand{\Zder}{Z^{\mathrm{der}}_{\mathrm{ch}}}
\providecommand{\Z}{\mathbb{Z}}
\providecommand{\C}{\mathbb{C}}
\providecommand{\cF}{\mathcal{F}}
\providecommand{\fg}{\mathfrak{g}}
\providecommand{\SCchtop}{\mathsf{SC}^{\mathrm{ch,top}}}

\title{Monster Orbifold $E_3$-Topological Descent Criterion\\
via the Leech $\Z/2$-Orbifold}
\author{Raeez Lorgat}

\begin{document}
\maketitle

\begin{abstract}
The Moonshine module $V^\natural$ enters through a finite-orbifold
boundary construction.  The $E_3$-topological object is the descended
holomorphic-topological factorisation algebra obtained from the Leech
lattice model; its boundary chiral algebra is $V^\natural$.  A
single-colour $E_3$-topological algebra on the original boundary VOA
complex requires additional data.  The descent requires the orbifold BV
anomaly to vanish and the FLM twisted-sector construction to identify
the boundary VOA.  The
van~Ekeren--M\"oller--Scheithauer classification supplies cyclic
orbifold presentations for the Schellekens list; anomaly vanishing and
BV descent remain type-specific inputs.
\end{abstract}

\section{The landscape after the Leech $\Z/2$ construction}

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lll}
\textbf{Class} & \textbf{$E_3$-topological scope} & \textbf{Mechanism} \\
\hline
Affine KM at $k \neq -h^\vee$ & original complex & Costello--Gaiotto
Sugawara \\
Class-$M$ DS algebras & weight-completed; strict original chain lift
conditional & DS--Hochschild \\
Free PVAs & Conditional original-complex lift & Khan--Zeng analytic SDR \\
Heisenberg / lattice & original complex & Abelian hCS \\
$V^\natural$ (Moonshine) & Descended HT bulk with boundary
$V^\natural$ & Leech $\Z/2$ orbifold \\
71 Schellekens $c=24$ VOAs & Type-specific finite-orbifold descent &
EMS cyclic presentations plus anomaly input \\
Class-$M$ principal (Vir, $\mathcal{W}_N$) & weight-completed &
Half-BRST + MC5 pattern \\
Non-principal non-orbifold original-complex lift & no general theorem & none known
\end{tabular}
\end{center}

Finite-orbifold descent gives an original-complex $E_3$ model only
after two separate inputs have been supplied: anomaly-free BV descent
for the finite group action and identification of the boundary VOA.
The Leech $\Z/2$ construction is therefore an exceptional lattice
route, not a generic class-$M$ theorem. Generic class-$M$ principal
algebras outside this finite-orbifold reach remain governed by the
weight-completed/pro-ambient theorem and the conditional strict
$E_3$ chain-lift statement.

\section{Structural scope of the orbifold theorem}

The Monster descent statement separates the VOA theorem from the HT
descent theorem. Frenkel--Lepowsky--Meurman construct the boundary
VOA. Dijkgraaf--Witten theory places finite-group gauging obstructions
in $H^3(BG;\mathrm{U}(1))$. The HT conclusion follows only after the
Leech $\Z/2$ BV anomaly has been shown to vanish.

\begin{theorem}[Monster orbifold $E_3$-topological descent criterion]
\label{thm:monster-e3-standalone}
Let $V^\natural = V_\Lambda^+ \oplus V_\Lambda^{\mathrm{tw},+}$ be
the FLM Moonshine module (the $\widetilde\sigma$-invariant part of
the $\Z/2$-orbifold of the Leech lattice VOA, with the standard FLM
lift, canonical up to VOA isomorphism).  Suppose:
\begin{enumerate}[label=\textup{(\roman*)}, nosep]
\item the Leech lattice HT model $\cF_\Lambda$ carries the abelian
chain-level $E_3$-topological structure;
\item the lifted $\Z/2$ action has trivial finite-orbifold BV anomaly
$[\alpha_{\mathrm{orb}}]=0$ in
$H^3(B\Z/2;\mathrm{U}(1))$;
\item finite-orbifold BV descent applies to $\cF_\Lambda$.
\end{enumerate}
Then the descended orbifold factorisation algebra
$\cF_\Lambda^{\mathrm{orb}}$ carries a chain-level
$E_3$-topological algebra structure, and its boundary chiral algebra is
$V^\natural$.
\end{theorem}

\begin{proof}
\emph{FLM boundary algebra.} The FLM twisted
module $V_\Lambda^{\mathrm{tw}}$ has half-spinor ground-state
multiplicity $2^{12}$, and FLM Chapters 8--10 prove the twisted
Jacobi identity at chain level. Thus
$V_\Lambda^+ \oplus V_\Lambda^{\mathrm{tw},+}$ is the Moonshine module
$V^\natural$.

\emph{Finite-group anomaly.} For a finite group $G$, the obstruction
to gauging a holomorphic orbifold sector is a Dijkgraaf--Witten class
in $H^3(BG;\mathrm{U}(1))$. For $G=\Z/2$ this group is $\Z/2$; in a
normalised representative the class is detected by the sign
$\alpha(\sigma,\sigma,\sigma)=\pm 1$. A normalized $2$-coboundary has
value $1$ on $(\sigma,\sigma,\sigma)$, so this sign is a class
invariant. Hypothesis~(ii) is precisely the assertion that the Leech
lift gives the sign $+1$.

\emph{Descent.} Hypothesis~(i) supplies the $E_3$-topological
operations before gauging. Hypotheses~(ii)--(iii) say that the finite
orbifold BV construction has no anomalous associator and therefore
inherits those operations on the descended factorisation algebra.
Boundary restriction commutes with the invariant and twisted-sector
decomposition, so the boundary chiral algebra of
$\cF_\Lambda^{\mathrm{orb}}$ is the FLM orbifold VOA $V^\natural$.
\end{proof}

\section{Schellekens 71 and the EMS bijection}

The cyclic-orbifold literature supplies VOA presentations, not an
automatic HT descent theorem. Van~Ekeren--M\"oller--Scheithauer develop
cyclic orbifold theory for holomorphic VOAs; van~Ekeren--Lam--M\"oller--
Shimakura show that every strongly rational holomorphic
$c=24$ VOA with $V_1\ne0$ is obtained from the Leech lattice VOA by a
cyclic orbifold; H\"ohn--M\"oller give systematic constructions from
Niemeier lattice VOAs. The HT statement still needs the anomaly and BV
descent hypotheses.

\begin{enumerate}[label=(\alph*)]
\item \emph{Type A} (pure Niemeier, 24 cases): no finite orbifold
is being gauged; the lattice HT model is the abelian case.
\item \emph{Type B} (Leech $\Z/2$, 1 case): the Moonshine module
$V^\natural$; Theorem~\ref{thm:monster-e3-standalone}.
\item \emph{Type C} (non-trivial cyclic orbifolds): level matching and
the deep-hole tables identify the VOA presentation; the
Dijkgraaf--Witten class and BV descent must still be verified for the
chosen cyclic action.
\end{enumerate}

\begin{theorem}[Schellekens cyclic-orbifold descent criterion]
\label{thm:schellekens-71-standalone}
For a Schellekens $c=24$ VOA presented as a cyclic orbifold of a
Niemeier lattice VOA, if the cyclic level-matching condition holds,
the Dijkgraaf--Witten anomaly class vanishes, and finite-orbifold BV
descent applies to the chosen lattice HT model, then the descended HT
factorisation algebra carries an $E_3$-topological structure whose
boundary chiral algebra is the corresponding Schellekens VOA.
\end{theorem}

The full 71-case statement is therefore a criterion until the
type-specific anomaly calculations are supplied: Type~A is vacuous,
Type~B is the Leech $\Z/2$ calculation, and Type~C is a cyclic
level-matching plus anomaly computation. The EMS classification itself
supplies cyclic presentations, not the BV descent theorem.

\section{Position in the topologization landscape}

The landscape separates five mechanisms:
\begin{itemize}[nosep]
\item affine Kac--Moody $V_k(\fg)$ at $k \neq -h^\vee$
(Costello--Gaiotto Sugawara route),
\item the class-$M$ DS landscape in the weight-completed/pro ambient,
with strict original-complex chain lift only in the stated conditional
scope,
\item freely generated PVAs, conditional on the Khan--Zeng analytic
SDR input,
\item $V^\natural$ and the Schellekens cyclic-orbifold cases when the
type-specific anomaly and BV-descent inputs hold,
\item Heisenberg and all lattice VOAs (abelian hCS).
\end{itemize}
Chain-level $E_3$-topological structure on the weight-completed
bar complex is proved for class-$M$ principal algebras (Virasoro,
$\mathcal{W}_N$) via the DS--Hochschild and MC5 pattern; the strict
original-complex chain lift has the conditional status recorded in
the chiral Higher Deligne and universal-holography chapters. The
Leech $\Z/2$ construction does \emph{not} change that generic class-M
scope, because $V^\natural$ is reached by finite-orbifold descent from
the class-G lattice model.

\section{Primary sources and local hypotheses}

The source inputs are:
\begin{itemize}[nosep]
\item Frenkel--Lepowsky--Meurman construct $V^\natural$ as the
Leech $\Z/2$ orbifold and prove the twisted Jacobi identity.
\item Dijkgraaf--Witten identify finite-group orbifold anomalies with
group-cohomology classes; Dijkgraaf--Pasquier--Roche identify the same
class as the associator twist in the finite-group orbifold tensor
category. This note uses only the class
$[\alpha]\in H^3(BG;\mathrm{U}(1))$, not a Drinfeld-double equivalence
as an $E_3$-descent theorem.
\item Dong--Li--Mason prove modular invariance of orbifold trace
functions under their finiteness hypotheses. Modular invariance is
evidence for level matching; it is not by itself the BV descent
theorem.
\item Van~Ekeren--M\"oller--Scheithauer, van~Ekeren--Lam--M\"oller--
Shimakura, and H\"ohn--M\"oller supply cyclic-orbifold constructions
and Schellekens-list control for holomorphic $c=24$ VOAs.
\item The local HT inputs are the abelian Leech lattice
$E_3$-topological model, the explicit vanishing of the relevant
finite-orbifold BV anomaly, and the finite-orbifold BV descent
theorem. If any of these three inputs is absent, the conclusion above
remains conditional.
\end{itemize}

\end{document}
