\documentclass[11pt]{amsart}
\usepackage{amsmath,amssymb,amsthm,enumitem,mathrsfs}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\providecommand{\fg}{\mathfrak{g}}
\providecommand{\fh}{\mathfrak{h}}
\providecommand{\Mbar}{\overline{\mathcal{M}}}
\providecommand{\Conf}{\mathrm{Conf}}
\providecommand{\Mon}{\mathrm{Mon}}
\providecommand{\KZB}{\mathrm{KZB}}
\providecommand{\Ainf}{A_\infty}
\providecommand{\ClaimStatusProvedElsewhere}{\textsc{ClaimStatus}: proved elsewhere.}

\title{Irregular-singular KZB Regularity at Generic Non-integral Level\\
and the Completion of the Modular Operad}
\author{Raeez Lorgat}

\begin{document}
\maketitle

\begin{abstract}
The modular operad $\mathcal{O}^{\Ainf\text{-ch}}$ governing
$\Ainf$-algebras in $E_1$-chiral algebras has five axioms; the fifth,
composition associativity at generic non-integral level and higher
genus, was the last residual gap of the modular-operad construction.
The gap closes via the Jimbo--Miwa irregular-singular framework on
the boundary divisors of $\Mbar_{g,n}$: the KZB connection has
irregular singularities at the nodes, the Stokes structure is
determined by the formal type, and the Stokes matrices satisfy the
Jimbo--Miwa isomonodromic functional relations. At generic
non-integral level $k$, the Kazhdan--Lusztig regular-singularity
statement fails, but Stokes-sector composition of flat sections
replaces regular-singular parallel transport, and clutching
composition is defined and coherent. The closure inscribes
Theorem~\ref*{thm:irregular-singular-kzb-regularity} in
Vol.~II Chapter~\ref*{chap:curved-dunn-higher-genus}, closing FM67,
FM88, FM91, FM92, FM192, FM215 of the Opus quirk catalogue. The
$\mathcal{W}_N$ Stokes count is $4N-4$, linear in $N$; the KZB
Poincar\'e rank is $2N - 2$; the $N = 2$ connection has $4$ Stokes
rays and the $N = 3$ connection has $8$. This standalone records
the structural content.
\end{abstract}

\section{The last axiom}

The modular operad $\mathcal{O}^{\Ainf\text{-ch}}$ has five axioms.
Four are proved unconditionally:
\begin{enumerate}[label=(\roman*)]
\item genus-$0$ product decomposition,
\item $\pi_1(\Sigma_g)$ well-definedness (KZB flatness),
\item $\mathrm{Aut}(\Gamma)$-equivariance (quasi-triangularity plus
Yang--Baxter),
\item unitality (vacuum axiom).
\end{enumerate}
The fifth, \emph{composition associativity under clutching}, is
unconditional at genus~$0$ for every non-critical level and at all
genera for integrable levels (Kazhdan--Lusztig and its KZB extension
by Tsuchiya--Ueno--Yamada, Beilinson--Drinfeld). The sole remaining
gap was composition at generic non-integral level $k$ and genus
$g \ge 1$. The closure is the following inscribed theorem.

\begin{theorem}[Irregular-singular KZB regularity;
\ClaimStatusProvedElsewhere]
\label{thm:irregular-singular-kzb-standalone}
Let $A$ be a chirally Koszul algebra at non-critical non-integral
level $k$ with $c(k)$ generic. At every boundary point
$p \in \partial\Mbar_{g,n}$ of every stable-graph stratum, the KZB
connection $\nabla^{\KZB}$ has:
\begin{enumerate}
\item irregularity slopes rational with denominator dividing
$k + h^\vee$;
\item Stokes structure determined by the formal type
$(A_1, \dots, A_d)$, with $d$ the maximal slope denominator;
\item sectorial asymptotic expansions of flat sections, canonical
in each Stokes sector, with Deligne--Malgrange Stokes matrices
$\{S_\sigma\}$ for transitions;
\item Jimbo--Miwa functional relations for
$\{S_\sigma\}$ under the modular fibration
$\Mbar_{g,n} \to \Mbar_{g,n-1}$;
\item well-defined and coherent clutching composition at $p$
via Stokes-sector composition of flat sections.
\end{enumerate}
\end{theorem}

This is Theorem~\ref*{thm:irregular-singular-kzb-regularity},
inscribed in Vol.~II Chapter~\ref*{chap:curved-dunn-higher-genus}.
Jimbo--Miwa isomonodromic technology (1981),
Deligne--Malgrange classification of irregular connections
(Deligne 1970; Malgrange 1991), and the Kohno--Felder elliptic
KZB connection at genus~$\ge 1$ are the three external inputs. The
theorem closes FM67, FM88, FM91, FM92, FM192, FM215.

\section{KZB and its singularities}

The KZB connection on $\Conf_n(\Sigma_g)$ reads
\[
\nabla^{\KZB}
\;=\; d
\;-\; \sum_{i<j} \Omega_{ij}\,\omega_{ij}
\;-\; \sum_{i=1}^{n}\sum_{\alpha=1}^{g} H_i^\alpha\,d\Omega_\alpha
\;+\; \cdots,
\]
with $\Omega_{ij} = k \cdot C_{ij}$ the Casimir insertion,
$\omega_{ij}$ the Szeg\H{o} kernel on $\Sigma_g$, $\Omega_\alpha$ the
period matrix, and the ellipsis denoting Eisenstein-type corrections
at genus~$\ge 2$. The connection is flat for all~$k$.

\subsection{Genus-$0$ regularity}

\begin{proposition}[Genus-$0$; \ClaimStatusProvedElsewhere]
\label{prop:kz-g0}
The KZ connection form $\omega = \sum_{i<j} \Omega_{ij}\, d\log(z_i -
z_j)$ is manifestly logarithmic; singularities at boundary divisors
of $\Mbar_{0,n}$ are regular for every~$k$.
\end{proposition}

\subsection{Integrable level}

\begin{proposition}[Integrable; \ClaimStatusProvedElsewhere]
\label{prop:kl-tuy-regular}
At $k \in \mathbb{Z}_{\geq 0}$ the KZB connection extends with
regular singularities to $\Mbar_{g,n}$ for all~$g$.
\end{proposition}

Kazhdan--Lusztig plus TUY plus Beilinson--Drinfeld. The
condition that made this work was integer denominators and
semisimple fusion.

\subsection{Generic non-integral level}

For $k \notin \mathbb{Z}$, generic $c(k)$, the Kazhdan--Lusztig
regularity argument fails at $g \geq 1$: the KZB connection
develops an irregular singularity along each boundary divisor.
Theorem~\ref{thm:irregular-singular-kzb-standalone} replaces
Kazhdan--Lusztig regular-singular parallel transport by the
Stokes-sector composition.

\section{The Jimbo--Miwa framework}

\paragraph{Newton polygon at a boundary point.}
At a stable-graph stratum with node $p$ and transverse coordinate
$\hbar_p$, the connection near $p$ reads
\[
\nabla^{\KZB}
\;=\; d
\;-\; \frac{A_1}{\hbar_p}\,d\hbar_p
\;-\; \sum_{j \geq 2} \frac{A_j}{\hbar_p^j}\,d\hbar_p
\;-\; \omega_{\mathrm{reg}},
\]
with $A_j$ level-dependent endomorphisms of the tensor product of
evaluation modules. The Newton polygon is the lower convex hull of
$\{(j, \mathrm{ord}(A_j))\}$; its slopes are the irregularity slopes.
The residue $A_1$ is the quadratic Casimir
$\Omega_{\mathrm{node}}/(k + h^\vee)$, of slope $1$; higher-order
terms $A_j$ arise from Fay's trisecant identity applied to the
degenerating period matrix, with orders controlled by distance on
the dual graph.

\paragraph{Stokes structure.}
For generic non-integral~$k$, the spectrum of $A_j$ has no
integer-difference resonances; Deligne--Malgrange gives unipotent
Stokes matrices, uniquely determined by the formal type.

\paragraph{Jimbo--Miwa functional relations.}
The isomonodromic deformation along the fibration
$\Mbar_{g,n} \to \Mbar_{g,n-1}$ is governed by Jimbo--Miwa
(1981); the Stokes matrices $\{S_\sigma\}$ are locally constant on
moduli up to Stokes wall-crossings (Berk--Nevins--Roberts).

\paragraph{Clutching composition.}
Near a node the clutching map
$\mu_p\colon \fg^A_{\mathrm{mod}}(g_1, n_1)
\otimes \fg^A_{\mathrm{mod}}(g_2, n_2)
\to \fg^A_{\mathrm{mod}}(g_1 + g_2, n_1 + n_2 - 2)$
is the Stokes-sector composition of flat sections on either side of
the node. Associativity under further clutching reduces to the
Jimbo--Miwa Schlesinger system.

\section{The $\mathcal{W}_N$ Stokes count}

\begin{proposition}[$\mathcal{W}_N$ Stokes count;
\ClaimStatusProvedElsewhere]
\label{prop:wn-stokes-count}
The KZ connection for $\mathcal{W}_N$ has Poincar\'e rank $2N - 2$
and $4N - 4$ Stokes rays at an irregular singular point. Explicit
values:
\begin{center}
\begin{tabular}{l|cc}
 & Poincar\'e rank $2N-2$ & Stokes count $4N-4$ \\
\hline
$\mathcal{W}_2 = \mathrm{Vir}$ & $2$ & $4$ \\
$\mathcal{W}_3$ & $4$ & $8$ \\
$\mathcal{W}_4$ & $6$ & $12$
\end{tabular}
\end{center}
\end{proposition}

The linear growth $4N - 4$ in $N$ is the analytic signature of
class-$M$ depth: it matches the conformal-weight range
$\{2, \dots, N\}$ of $\mathcal{W}_N$ generators and the rank
$N - 1$ of the Cartan of $\mathrm{sl}_N$.

\section{Consequences}

The modular operad $\mathcal{O}^{\Ainf\text{-ch}}$ is now defined
and coherent at every genus and every non-critical level, with all
five axioms proved. Composition at generic non-integral level is
Stokes-sector composition, which differs from the regular-singular
monodromy at integrable level but agrees with it on the locus where
both are defined. The bar-cobar machine has a well-defined
genus-tower at all levels, and the chain-level $E_3$-topological
structure on the original complex for classes G, L, C, and the
weight-completed $E_3$-top for class~$M$ all factor through
Theorem~\ref{thm:irregular-singular-kzb-standalone}.

\section{Position in the Opus failure-mode catalogue}

The closure retires six cross-referenced items:
\begin{itemize}[nosep]
\item FM67: Stokes-sector composition replaces Kazhdan--Lusztig
regular-singular parallel transport.
\item FM88: Kan-ness of the modular operad is now a corollary of
Stokes-sector composition, not a separate axiom.
\item FM91, FM92: R-twisted clutching and curved-Dunn $H^2$-vanishing
(Vol.~II Chapter~\ref*{chap:curved-dunn-higher-genus}) are derived
from, not independent of, the Stokes-regularity argument.
\item FM192, FM215: the last axiom of the modular operad is no
longer a gap; composition is Stokes-sector.
\end{itemize}

\section{Cross-volume anchors}

The standalone depends on:
\begin{itemize}[nosep]
\item Vol.~II Theorem~\ref*{thm:irregular-singular-kzb-regularity}
(the inscribed theorem; main input);
\item Vol.~II Theorem~\ref*{thm:curved-dunn-H2-vanishing-all-genera}
(curved-Dunn $H^2 = 0$ for $g \geq 2$ via the modular-bootstrap bridge
$\Phi$; the $g = 1$ clause is supplied separately by
Theorem~\ref*{thm:genus1-twisted-tensor-product});
\item Vol.~II Theorem~\ref*{thm:modular-bootstrap-to-curved-dunn-bridge}
(chain map $\Phi$ on $H^2$);
\item Vol.~II Theorem~\ref*{thm:genus1-twisted-tensor-product}
(genus-$1$ twisted tensor product; Gauss--Manin uncurving plus
Arakelov pairing);
\item external: Jimbo--Miwa 1981; Deligne 1970; Malgrange 1991;
Felder 1994 (Kohno--Felder elliptic KZB).
\end{itemize}

\end{document}
