%% =====================================================================
%% part_viii_synthesis.tex
%%
%% Vol II Part VIII overview: "From Frontier to Theorem"
%%
%% Synthesis-only file. Cross-references existing theorems by \label;
%% contains NO new theorem statements and NO duplicated proofs. Each
%% section is a ~150-300 word narrative mapping one of the four closed
%% frontiers (or one supporting structural result) into the
%% programme's Platonic form.
%%
%% Location: chapters/frame/ (Vol II).
%% Inputs: chapters/theory/curved_dunn_higher_genus.tex
%% chapters/theory/chiral_higher_deligne.tex
%% chapters/theory/koszulness_moduli_M_kosz.tex
%% chapters/theory/infinite_fingerprint_classification.tex
%% chapters/connections/brace.tex
%% chapters/connections/bv_brst.tex
%% (Vol I) chapters/theory/periodic_cdg_admissible.tex
%% =====================================================================

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Part VIII Synthesis: Theorem Atlas}
\addcontentsline{toc}{chapter}{Part VIII Synthesis: Theorem Atlas}
\label{chap:part-viii-synthesis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% =====================================
\section{Theorem atlas: overview}
\label{sec:part-viii-overview}

Parts I--VII of this volume construct the $\SCchtop$ ladder from an
$E_{1}$-chiral seed to an $E_{3}$-topological climax. Four hypotheses
determine the theorem locus of that ladder:
(a)~modular-bootstrap \(H^{2}\)-acyclicity plus the degree-\(2\)
comparison for curved-Dunn transport at \(g\ge2\);
(b)~DS--Hochschild chain-level compatibility for class $\mathbf{M}$;
(c)~periodic-CDG admissible-level Koszul compatibility for
Kazhdan--Lusztig; and (d)~chain-level chiral Deligne--Tamarkin after a
fixed Drinfeld-associator gauge is chosen. On loci satisfying these
hypotheses, the cited theorem or proposition supplies the construction.

The four threads converge on a single
architectural claim: \emph{the four frontiers are not independent
obstructions but four shadows of a single Platonic object}; the
Koszulness Moduli Scheme $M_{\mathrm{Kosz}}(\mathcal A)$ with its
$\mathrm{GRT}_{1}(\Q)$-torsor of fourteen charts
(Theorem~\ref{thm:mkosz-fourteen-charts}). Once the atlas is in place,
each of (a)--(d) is a coordinate-chart identification in a fixed
Drinfeld-associator gauge. Part VIII places these four theorem threads
and the two Platonic-form chapters
(Chapter~\ref{chap:koszulness-moduli} and
Chapter~\ref{chap:infinite-fingerprint}) into a single navigation
structure.

Each of Sections
\ref{sec:part-viii-curved-dunn}--\ref{sec:part-viii-concordance}
contains a precise citation and a one-page synthesis. The theorem
bodies remain in their home chapters.

%% =====================================
\section{Curved-Dunn $H^{2}=0$ as a theorem}
\label{sec:part-viii-curved-dunn}

Classical Dunn additivity says $E_{2} \simeq E_{1} \otimes_{\mathrm{Dunn}}
E_{1}$. For the $\SCchtop$ genus tower the analogous statement
requires a curved refinement: the two colours tensor against a shared
Arakelov background that contributes a curvature
\(d_{B}^{2}=\kappa_{\mathrm{ch}}(\mathcal A)\cdot \omega_g\)
at each genus. Curved Dunn additivity asks whether
the curvature-compatible tensor factorisation descends from genus 0
(trivial) and genus 1 (twisted tensor criterion) to $g \ge 2$. The
genus-1 input is the Gauss--Manin uncurving
(Proposition~\ref{prop:genus1-twisted-tensor-product}); the
higher-genus obstruction is the $H^{2}$ class of the curved-Dunn
twisting-cochain complex.

The theorem is
Theorem~\ref{thm:curved-dunn-H2-vanishing-all-genera} of
Chapter~\ref{ch:curved-dunn-higher-genus}: for \(g\ge2\), the
curved-Dunn twisting-cochain complex has \(H^{2}=0\) under
modular-bootstrap \(H^2\)-acyclicity and the degree-\(2\)
comparison. The bridge chain map of
Proposition~\ref{prop:modular-bootstrap-to-curved-dunn-bridge}
transports the modular-bootstrap vanishing to the curved-Dunn
complex. Combined with
Theorem~\ref{thm:irregular-singular-kzb-regularity} (Jimbo--Miwa
irregular-singular KZB regularity from a boundary formal type),
this conditionally promotes modular operad composition from
integral to generic non-integral level at all
$(g,n)$; Corollary~\ref{cor:modular-operad-composition-all-levels}.

The genus-1 twisted tensor input is the named proposition
Proposition~\ref{prop:genus1-twisted-tensor-product} in
Chapter~\ref{ch:curved-dunn-higher-genus}, with the Gauss--Manin
uncurving written explicitly.

%% =====================================
\section{The modular bootstrap $\to$ curved-Dunn bridge chain map}
\label{sec:part-viii-bridge}

The single load-bearing construction underlying
Section~\ref{sec:part-viii-curved-dunn} is the bridge chain map
$\Phi : \BMBC^{\bullet} \to \CDTC^{\bullet}$ of
Proposition~\ref{prop:modular-bootstrap-to-curved-dunn-bridge}. Its
role is to promote the per-genus vanishing
$H^{2}(\BMBC) = 0$ proved in the modular-bootstrap complex at
Definition~\ref{def:modular-bootstrap-complex} into
$H^{2}(\CDTC) = 0$ in the curved-Dunn complex at
Definition~\ref{def:curved-dunn-complex}. Bridge directionality
matters: the curved-Dunn complex knows about the tensor factorisation
but not the bootstrap constraints; the modular-bootstrap complex
knows about the constraints but not the factorisation; $\Phi$ is the
zigzag that relates them through a common gauge-fixed resolution.

The bridge's gauge-fixed resolution makes the implication
unconditional. Per-genus $H^{2}(\BMBC) = 0$ was classically visible
through Beilinson--Drinfeld chiral Koszul duality and the modular
operad's clutching structure; what was missing was a chain-level
argument showing the vanishing survives the curved-Dunn
tensor-twist. The bridge supplies that argument by constructing a
twisting cochain for $\Phi$ that is explicit in genus 1 (via
Proposition~\ref{prop:genus1-twisted-tensor-product}) and
inductive in $g$ via the stable-graph stratification of
$\overline{\mathcal{M}}_{g,n}$.

Remark~\ref{rem:bridge-provenance} in
Chapter~\ref{ch:curved-dunn-higher-genus} records the provenance
contract: the bridge takes modular-bootstrap vanishing as input and
emits curved-Dunn vanishing as output; no circular appeal to Dunn
additivity appears anywhere in the proof of the bridge itself.

%% =====================================
\section{DS--Hochschild compatibility bridge for class $\mathbf{M}$}
\label{sec:part-viii-ds-hochschild}

For chiral algebras in classes G, L, C, the global triangle
$Z^{\mathrm{der}}_{\mathrm{ch}}(\mathcal{A}) \simeq
\mathcal{A}^{\mathrm{bulk}}$ identifying the derived chiral centre
with a 3d HT bulk was already proved at the chain level
via boundary-linearity + Costello--Gaiotto. For class $\mathbf{M}$
(Virasoro, $W_{N}$, quartic-pole lineage), the chain-level
identification requires an additional theorem: the Drinfeld--Sokolov reduction
transports $V_{k}(\mathfrak{g})$ to $W_{k}(\mathfrak{g},f)$ at the
level of chiral algebras, and chiral Hochschild cohomology must commute
with DS at chain level.

Theorem~\ref{thm:chd-ds-hochschild} of
Chapter~\ref{ch:chiral-higher-deligne} supplies the bridge. The
statement is the chain-level quasi-isomorphism
$\mathrm{ChirHoch}^{\bullet}(W_{k}(\mathfrak{g},f)) \simeq
H^{\bullet}_{\mathrm{DS}}(\mathrm{ChirHoch}^{\bullet}(V_{k}(\mathfrak{g})))$.
The three-step proof runs through (i) Homological Perturbation Lemma
(HPL) transfer through the Drinfeld--Sokolov strong deformation
retract, strict weight-by-weight because the BRST filtration has
finite length on every weight space; (ii) Arakawa $C_{2}$-cofiniteness
lifting to chain-level finiteness; (iii) the HKR identification
$\mathrm{ChirHoch}^{\bullet}(V_{k}) \simeq
\mathcal{O}(T^{\ast}[-1]\,\DerM_{\mathrm{vac}}(V_{k}))$ followed by
BV reduction along the DS moment map.

Corollary~\ref{cor:universal-holography-class-M} of the same chapter
packages the theorem into the ambient-qualified universal holography
statement for class $\mathbf{M}$: every conformal-vectored
non-critical class $\mathbf{M}$ chiral algebra is the boundary of a
canonical 3d HT theory in the weight-completed/pro model, with bulk
its completed derived chiral centre. The strict original-complex
$E_3$ chain lift remains in the conditional statement recorded in the
chiral Higher Deligne and universal-holography chapters.

%% =====================================
\section{Class $\mathbf{M}$ chain level from weight-completed HPL transfer}
\label{sec:part-viii-class-m-weight-completed}

The technical engine powering
Theorem~\ref{thm:chd-ds-hochschild} is the \emph{weight-completed}
identification of BV, BRST, and bar structures on class
$\mathbf{M}$. Direct-sum chain-level identification is genuinely
false (the raw direct-sum symplectic polarisation
degenerates for quartic-pole families because the pairing fails to
factor weight-by-weight), so the theorem must live in a different
ambient.

Proposition~\ref{prop:bv-bar-class-m-weight-completed} of
Chapter~\ref{ch:bv-brst} (in \texttt{bv\_brst.tex}) provides
the correct ambient: the \emph{weight-completed} envelope in which
the BV--BRST--bar chain-level identification holds unconditionally
across all four shadow classes G, L, C, $\mathbf{M}$. The
completion is along the Li filtration by conformal weight; the
identification is strict on each weight space and extended to the
completion by the standard pro-nilpotent completeness argument.

The class $\mathbf{M}$ side of the weight-completed identification is
precisely the input consumed by Step (ii) of the proof of
Theorem~\ref{thm:chd-ds-hochschild} via Arakawa
$C_{2}$-cofiniteness; weight completeness is what permits HPL
transfer to commute with the cohomological $\mathrm{ChirHoch}^{\bullet}$
on each conformal-weight stratum, and Arakawa supplies the finiteness
control that makes the HPL argument converge in the limit. The chain-level
quasi-isomorphism thus survives completion, which is why
Corollary~\ref{cor:universal-holography-class-M} can afford to be
stated unconditionally in the weight-completed/pro ambient on the
conformal-vectored non-critical locus.

%% =====================================
\section{Periodic-CDG at admissible Kac--Moody level}
\label{sec:part-viii-periodic-cdg}

The Kazhdan--Lusztig bar--cobar adjunction at admissible Kac--Moody
level requires periodicity of the category $\mathcal{O}$ under Koszul
dualisation on the semisimplified level. This is the periodic-CDG
Koszul-compatibility problem. Without it, the KL adjunction at
admissible $k$ has only generic-level force in downstream Vol~II
applications.

The theorem lives in Vol~I Chapter~\ref*{V1-chap:periodic-cdg-admissible}.
The master result is Theorem~\ref*{V1-thm:periodic-cdg-is-koszul-compatible}:
the periodic-CDG structure is Koszul-compatible on the admissible
locus. The four-step proof invokes (i) Arakawa $C_{2}$-cofiniteness
at admissible level, (ii) Finkelberg tilting semisimplification,
(iii) Lusztig Tate periodicity of admissible blocks, and
(iv) commutation of screening-adjoint with periodic-CDG, proved by an
independent screening computation.

Consequently,
Theorem~\ref*{V1-thm:admissible-kl-bar-cobar-adjunction} gives the
Kazhdan--Lusztig bar--cobar adjunction on the admissible KL locus
satisfying the theorem's exactness and periodic-CDG hypotheses. Every
Vol~II downstream theorem that cited
``KL at generic $k$; admissible level conditional on periodic-CDG''
can cite the admissible theorem directly on that locus. The remaining
hypothesis is the degenerate admissible logarithmic lane
(Creutzig--Kanade--Linshaw machinery), treated separately in
Vol~I's Remark on logarithmic admissible CDG.

%% =====================================
\section{Adams-analog construction for semisimplified Kazhdan--Lusztig}
\label{sec:part-viii-adams-analog}

The Adams spectral sequence analogy treats the bar complex as a
cohomological resolution through which
``Steenrod-algebra-analog'' primary operations appear as $d_{1}$
differentials on the $E_{1}$-page. The proof question is
which chiral endomorphism functor plays the role of the mod-$p$
Steenrod algebra, and whether the corresponding $E_{2}$-collapse is
forced by semisimplified Kazhdan--Lusztig Koszulness.

Theorem~\ref*{V1-thm:adams-analog-construction} of Vol~I supplies the
construction. The target functor is built from periodic-CDG
screening-adjoints on the semisimplified KL block (itself a theorem
by Section~\ref{sec:part-viii-periodic-cdg} above); the analogue of
the mod-$p$ Steenrod algebra is the algebra of periodic-CDG screening
primaries acting on $\mathrm{Ext}^{\bullet}_{\mathrm{KL}}(k,k)$. The
$E_{2}$-collapse follows from Koszul-compatibility of the
semisimplification, pulled back through the bar--cobar adjunction
upgraded to admissible level by
Theorem~\ref*{V1-thm:admissible-kl-bar-cobar-adjunction}.

The analogy is therefore promoted from a suggestive remark into a
bona fide theorem about screening-primary operations on bar
cohomology. The consequence for Vol~II is that the
Adams-analog $E_{2}$-collapse is a legitimate computational tool on
admissible KL blocks, with Vol~I's construction as the theorem anchor.

%% =====================================
\section{Chain-level Chiral Deligne--Tamarkin (associator-dependent)}
\label{sec:part-viii-deligne-tamarkin}

The fourth obstruction is chain-level chiral Deligne--Tamarkin:
whether the $E_{2}$-action on $\Zderch(\mathcal{A})$ that is
guaranteed at the level of cohomology lifts to a strict chain-level
$E_{2}$-action. In the classical (non-chiral) setting, Tamarkin's
lift is an $\infty$-quasi-isomorphism depending on a choice of
Drinfeld associator; the chiral theorem must therefore specify its
associator gauge.

Theorem~\ref{thm:chd-deligne-tamarkin} of
Chapter~\ref{ch:chiral-higher-deligne} realises the chiral analogue
in its associator-dependent form. Fixing a Drinfeld associator
$\Phi \in \mathrm{GRT}_{1}(\Q)$, the chain-level $E_{2}$-action on
$\Zderch(\mathcal{A})$ exists as a strict dg-operadic action of
$\mathrm{E}_{2}^{\mathrm{chain}}[\Phi]$, transported from classical
Deligne--Tamarkin through the quasi-isomorphism of chiral and
algebraic Hochschild models established by
Proposition~\ref{prop:chd-models-equivalent}. The associator-gauge
is flagged at Remark~\ref{rem:chd-associator-discipline}.

The associator-independent formulation remains as a formal question
(cf.\ Section~\ref{sec:chd-not-proved}), since independence is
equivalent to triviality of the $\mathrm{GRT}_{1}(\Q)$-action on the
$E_{2}$-chain-action, and the chiral programme exploits the
non-triviality of the torsor to identify distinct faces
(Section~\ref{sec:part-viii-koszulness-moduli}). For all Vol~II
downstream applications, the associator-dependent formulation
suffices and is the appropriate notion: it is the formulation that
plays well with the fourteen-chart atlas on $M_{\mathrm{Kosz}}$.

%% =====================================
\section{Higher Massey odd-weight tower via Brown motivic depth}
\label{sec:part-viii-massey}

The fifth entry in Part VIII synthesis is not one of the four
irreducible obstructions but a supporting structural observation: the
$\zeta(3)$-class obstruction to triviality of the $\mathrm{GRT}_{1}$
action on chiral bar data.

Proposition~\ref{prop:massey-yangian-indeterminacy-nonzero}
(Section~\ref{sec:chiral-Hochschild-brace}, in \texttt{brace.tex}) shows that the
indeterminacy coset of the ternary Massey bracket
$\langle r,r,r\rangle$ on the Drinfeld--Kohno Lie algebra
$\mathfrak{t}_{3}$ does \emph{not} contain the depth-2 generator
$[\Omega_{12},[\Omega_{13},\Omega_{23}]]$, hence does not kill the
$\zeta(3)$ Massey class. By Brown's theorem on motivic depth
(\cite{BrownMixedTate}), odd-weight generators of
$\mathrm{grt}_{1}$ act freely on the tower of Massey obstructions
coming from the Drinfeld--Kohno Lie algebra at each $n$; the
$\zeta(3)$-class is the bottom generator of an infinite
Massey odd-weight tower.

For Part VIII, the Massey tower is the mechanism by which
different Drinfeld associators genuinely give different
coordinates on $M_{\mathrm{Kosz}}(\mathcal{A})$: the
$\mathrm{GRT}_{1}(\Q)$ action is free (Brown), and the freeness
is detected chart-by-chart by odd-weight Massey products on the
chiral endomorphism brace. The non-triviality of
Proposition~\ref{prop:massey-yangian-indeterminacy-nonzero} is
what rescues the fourteen-chart atlas from being the trivial
one-chart degeneration.

%% =====================================
\section{Koszulness Moduli scheme $M_{\mathrm{Kosz}}$ as $\mathrm{GRT}_{1}$-torsor atlas}
\label{sec:part-viii-koszulness-moduli}

The Platonic form of the four theorem threads is
Chapter~\ref{chap:koszulness-moduli}: a single moduli scheme
$M_{\mathrm{Kosz}}(\mathcal{A})$ on which the fourteen classical
Koszulness characterisations of an $E_{1}$-chiral algebra
$\mathcal{A}$ are affine charts, and on which
$\mathrm{GRT}_{1}(\Q)$ acts by transporting Drinfeld-associator
coordinates. The moduli scheme is characterised by
Definition~\ref{def:mkosz}; its atlas structure is
Theorem~\ref{thm:mkosz-fourteen-charts}; its shadow-class
stratification is Theorem~\ref{thm:mkosz-shadow-stratification}.

Under the atlas structure, the fourteen Koszulness characterisations
are local coordinate statements. On its own chart, each
characterisation is a theorem; on a different chart, the additional
conditions are precisely the associator-change cocycles governing
transition functions.
Section~\ref{sec:mkosz-grt-torsor} exhibits the
$\mathrm{GRT}_{1}(\Q)$-torsor structure explicitly.

The four results of Sections~\ref{sec:part-viii-curved-dunn},
\ref{sec:part-viii-ds-hochschild},
\ref{sec:part-viii-periodic-cdg}, and
\ref{sec:part-viii-deligne-tamarkin} are coordinate-chart
identifications inside this atlas in a chosen gauge. In the
Kontsevich chart $\Phi = \Phi_{\mathrm{Kon}}$ (chart $U_{14}$ of
Theorem~\ref{thm:mkosz-fourteen-charts}) the chain-level
$E_{2}$-action is explicit; in the Knizhnik--Zamolodchikov chart
$\Phi = \Phi_{\mathrm{KZ}}$ (the default of charts
$U_{1}$--$U_{10}$) the admissible bar--cobar adjunction is
explicit; the transition cocycles between charts are the
ingredient upgraded to a theorem by the Brown-depth Massey tower
of Section~\ref{sec:part-viii-massey}.

%% =====================================
\section{Infinite Fingerprint Classification and the G/L/C/M/FF projection}
\label{sec:part-viii-fingerprint}

The companion Platonic-form chapter is
Chapter~\ref{chap:infinite-fingerprint}: the complete classification
of $E_{1}$-chiral algebras on the $C_{2}$-cofinite standard
landscape by a six-slot fingerprint
$\varphi'(\mathcal{A}) = (p_{\max}, r_{\max}, \chi_{\mathrm{VOA}},
n_{\mathrm{strong}}, \mathrm{coset}, \kappa_{\mathrm{ch}})$.

The fundamental invariants are defined in
Definition~\ref{def:fingerprint-slots}. The five-slot truncation
fails on the Heisenberg family
(Proposition~\ref{prop:five-slot-insufficient-ch}); the sixth slot
$\kappa_{\mathrm{ch}}$ restores completeness
(Proposition~\ref{prop:six-slot-distinguishes-ch}). The completeness
theorem on the standard landscape is
Theorem~\ref{thm:fingerprint-complete-ch}: equality of fingerprints
implies isomorphism of chiral algebras.

The classical G/L/C/M quadrichotomy reappears as a \emph{coarse
projection} of $\varphi'$: the projection onto $r_{\max}$, restricted
to the non-degenerate locus \(\kappa_{\mathrm{ch}}\ne 0\)
(Corollary~\ref{cor:double-coarse-projection}). At
\(\kappa_{\mathrm{ch}}=0\), a
distinct fifth class ``FF'' (Feigin--Frenkel) appears as a canonical
companion stratum; not an exclusion but a genuine new class,
populated by the critical-level Feigin--Frenkel centre of
$V_{-h^{\vee}}(\mathfrak{g})$ and related degenerate-sector
examples.

Remark~\ref{rem:fingerprint-theoremD-coupling} records the coupling
between the sixth slot $\kappa_{\mathrm{ch}}$ and Vol~I's
Theorem~D universal Arakelov class, identifying $\kappa_{\mathrm{ch}}$
as the pullback under a landscape-classifying morphism.

%% =====================================
\section{Bismut--Gillet--Soulé Quillen norm as BV one-loop determinant}
\label{sec:part-viii-quillen-bv}

The $\SCchtop$ bar-differential on $\mathbf{H}_{\Delta_5}$-observables
produces a factorisation-algebraic partition function $Z^{(1)}$ on
$\mathrm{Ran}(E^{\mathrm{nod,sm}}_{24})$ whose Quillen norm is the
1-loop BV determinant of the twisted 11D supergravity theory on
$K3 \times T^2$. The identification
\[
\log Z^{(1)}(\mathbf{H}_{\Delta_5})
\;=\;
-\log\|\Delta_5\|_Q^2
\;=\;
-\log\Delta_5
\;-\;
24\,L'(0,\Delta_5,\mathrm{std})
\]
combines three inputs on the non-degenerate Humbert-complement locus:
Bismut--Gillet--Soulé 1988 Quillen-norm immersion along the Kuga--Satake
embedding
$\overline{\mathcal{A}_2}\hookrightarrow\overline{\mathcal{A}_{21}}$;
Yoshikawa 2004 equating the analytic torsion with a period of the
Igusa cusp form $\Delta_5$; and Bruinier--Kühn 2003 equating the
boundary Borcherds-lift contribution along the Humbert wall $H_4$ with
$24\,L'(0,\Delta_5,\mathrm{std})$.

The coefficient $24$ is doubly determined: as the second Chern class
of the rank-$21$ K3 transcendental lattice variation over
$\overline{\mathcal{A}_2}$, and as the count of M5-brane sources at
Kodaira $I_1$ fibres on elliptic K3. The Quillen norm
$\|\Delta_5\|^2$ is the sole modular-invariant scalar surviving the
averaging map $\mathrm{av}$ applied to $\mathbf{H}_{\Delta_5}$;
Section~\ref{sec:part-viii-curved-dunn}'s conditional curved-Dunn
\(H^2\)-vanishing supplies, under its comparison hypotheses, the
chain-level scaffold on which this one-loop
identification is an anchored computation, not a coincidence between
analytic torsion and modular period.

Cross-volume consequence: Volume~III's universal trace identity
(Vol~I--Vol~III bridge via $\Phi_{\mathrm{hol}}$ and $\Phi$) reads, on
this K3 pair,
\[
K(\mathbf{H}_{\Delta_5})
\;=\;
\kappa_{\mathrm{BKM}}(\mathfrak{g}_{\Delta_5})
\;=\;
c_{\Lambda^{3,2}}(0)/2
\;=\;
5
\;=\;
\mathrm{wt}(\Delta_5);
\]
the Quillen-norm $\log Z^{(1)}$ is the differential-geometric
counterpart whose residue along $H_4$ recovers the same $\Delta_5$
through a distinct analytic-torsion route.

%% =====================================
\section{Class-$\mathcal{S}$ $\mathcal{T}[A_1,\Sigma_{0,24}]$ Schur-index
cross-check and the Humbert=AD identification}
\label{sec:part-viii-schur-humbert}

The class-$\mathcal{S}$ theory
$\mathcal{T}[A_1, \Sigma_{0,24}]$ constructed by gluing $22$
$A_1$-trinions along $21$ tubes on the $24$-punctured sphere
$\Sigma_{0,24}$ has vector- and hypermultiplet counts
\[
(n_v, n_h)
\;=\;
(63, 88),
\]
by the Chacaltana--Distler 2010 tinkertoy assembly combined with
Shapere--Tachikawa 2008 vector/hypermultiplet counting. Applying the
Beem--Lemos--Liendo--Peelaers--Rastelli--van Rees 2013 4D/2D map,
\[
c_{4d}
\;=\;
\frac{2n_v + n_h}{12}
\;=\;
\frac{126+88}{12}
\;=\;
\frac{107}{6},
\qquad
c_{2d}
\;=\;
-12\,c_{4d}
\;=\;
-214
\;=\;
-2\cdot 107.
\]
The $\chi_{2d}$ chiral algebra of $\mathcal{T}[A_1,\Sigma_{0,24}]$ at
$c = -214$ is a distinct VOA from $\mathbf{H}_{\Delta_5}$. The
numerical coincidence of the integer ``$24$'' between $24$ regular
punctures of $\Sigma_{0,24}$ on $\mathbb{P}^1$ and $24$ Kodaira $I_1$
fibres on elliptic K3 reflects a shared rank-$22$ automorphism pattern:
$\operatorname{Aut}(\Sigma_{0,24})\supset S_{24}$ for punctures, and
$\operatorname{NS}(K3)_{\mathrm{prim}}\supset A_1^{22}$ for K3. The
two chiral algebras decouple as $\SCchtop$-data:
$\mathrm{av}(\chi_{2d}[\mathcal{T}[A_1,\Sigma_{0,24}]])$ carries
$\kappa_{\mathrm{ch}} = c_{2d}/2 = -107$, while
$\mathrm{av}(\mathbf{H}_{\Delta_5})$ carries $\kappa_{\mathrm{BKM}} = 5$.

\paragraph{Humbert equals Argyres--Douglas.}
At a generic point $E_{\tau_1}\times E_{\tau_2}$ on the Humbert
divisor $H_4 \subset \overline{\mathcal{A}_2}$, the Seiberg--Witten
curve of the Coulomb branch adjacent to $\mathcal{T}[A_1,\Sigma_{0,24}]$
degenerates to a pair of elliptic curves glued at a nodal point.
Gaiotto--Moore--Neitzke 2009 Example~8.3 identifies this degeneration
with an $(A_1, A_{2N-1})$-type Argyres--Douglas point: the
regular-singular moduli-space direction collapses onto the
irregular-singular direction of an Argyres--Douglas singularity. As a
result, the four-fold sibling stratification
$\{\Psi, \Psi^{\deg}, \Psi^{\mathrm{tor}}, \Psi^{\mathrm{metap}}\}$ of
$\mathbf{H}_{\Delta_5}$ coincides with the class-$\mathcal{S}$ join
\[
\{\Psi,\Psi^{\deg},\Psi^{\mathrm{tor}},\Psi^{\mathrm{metap}}\}
\;=\;
\mathrm{CDT}\cup\mathrm{AD}
\;=\;
\{\text{regular},\text{irregular},\text{Argyres--Douglas},\text{twisted}\}.
\]
Three decompositions agree on the single object
$\mathbf{H}_{\Delta_5}$: the Hall--Drinfeld one (the $\SCchtop$
bar-differential of
Section~\ref{sec:part-viii-quillen-bv}), the K3-lattice one
(Kuga--Satake $K3 \hookrightarrow \operatorname{Sh}(\mathrm{SO}(2,19))$),
and the class-$\mathcal{S}$ one (Seiberg--Witten curve degeneration).

\paragraph{Three-loop Arnold cancellation on $\mathrm{Conf}_4(E)$.}
The four-point function $\phi^{(4)}$ on $\mathrm{Conf}_4(E_\tau)$
sums $10$ Belokurov--Shavgulidze topologies, including ladder
splitting $T_5$ and theta-graph $T_6$ in its two wheel orientations.
The whole sum cancels pairwise under the Arnold--Cohen flip
$H_1 \leftrightarrow H_4$ via the Arnold relation
$\eta_{ij}\wedge\eta_{jk}+\eta_{jk}\wedge\eta_{ki}+\eta_{ki}\wedge\eta_{ij} = 0$
with $\eta_{ij} = d\log\vartheta_1(z_i - z_j,\tau)$; hence
$\phi^{(4)} = 0$ on $\mathrm{Conf}_4(E_\tau)$ for every $\tau$.
Cross-verification via Humbert non-admissibility: at a generic point
of $H_4$ the period degenerates to a pair of elliptic periods and the
admissible $E_8$-weight condition fails by half-integer excess
$\widetilde{D}_4 = 1/2$, which forces $\phi^{(4)}$ to vanish on the
admissible lattice independently. Both routes close the Arnold
cancellation at three loops without appeal to the regularised
Bruinier--Kühn boundary term.

%% =====================================
\section{$W_\infty[c=-214]$ cocycles and the Conway $V^{s\natural}$
metaplectic image}
\label{sec:part-viii-winf-conway}

The topologisation ladder from critical-level class~$\mathbf{M}$
reaches $W_\infty^{\mathrm{top}}$ at its endpoint
(Theorem~\ref{thm:climax-w-infty-endpoint} in
Chapter~\ref{ch:programme-climax-platonic}). At the
class-$\mathcal{S}$ value $c = -214$ from
$\mathcal{T}[A_1,\Sigma_{0,24}]$ of Section~\ref{sec:part-viii-schur-humbert},
the chiral-Hochschild generators $e_3, e_4, e_5, e_6 \in
\ChirHoch^2(\mathrm{Vir}_{-214})$ align explicitly with
Pope--Romans--Shen 1990 $W_\infty$-primaries. The weight-$5$
identification $e_5 = W_5$ is Wang 1998 Proposition~4.2, read on the
chiral-Hochschild side; the weight-$4$ identification is
\[
e_4
\;=\;
W_4 \;-\; \frac{107}{11}\,\Lambda_Z,
\qquad
\Lambda_Z
\;=\;
{:}TT{:}\;-\;\tfrac{3}{10}\partial^2 T,
\]
with the coefficient $107/11$ fixed by the condition that $e_4$ be
Virasoro-primary at $c = -214$. Primarity is an open condition on a
one-parameter family; Pope--Romans--Shen picks out the single
admissible value. The sequence $e_3, e_4, e_5, e_6$ realises the
Pope--Romans--Shen $W_\infty$-primary tower as the chiral-Hochschild
chart on the class-$\mathcal{S}$ fixed point.

\paragraph{Conway $V^{s\natural}$ as metaplectic $\Psi^s$-image on the
Leech lattice.}
The Conway module $V^{s\natural}$ of Duncan 2007 (Duke~139) is the
$\mathbb{Z}/2$-orbifold of the $24$-fermion superalgebra
$A(\Lambda_{24})$ on the Leech lattice $\Lambda_{24}$: an $N = 1$
superconformal VOA of central charge $c = 12$. The super-Borcherds
extension of Scheithauer 2008 (Invent.\ Math.\ 172) realises
$V^{s\natural}$ as the $\Psi^s$ image of $\Lambda_{24}$ under the
fermionic vertex superalgebra functor, distinct from the Monster
$\Psi$ image which produces $V^\natural$ from the $24$-boson
construction at $c = 24$. The factor of two between the two central
charges is the super-bosonisation ratio, not a gauge choice.

The topologisation ladder therefore has two Leech-lattice fixed
points at different central charges: $c = 12$ via $V^{s\natural}$, and
$c = 24$ via $V^\natural$. Together with the Schellekens
row partition
$71 = 24_{\mathrm{Niemeier}} + 1_{V_1=0} + 46_{\mathrm{nonlat}}$
(Theorem~\ref{thm:schellekens-71-all-alpha-zero} in
Chapter~\ref{ch:schellekens-71-alpha-classification-platonic}), the metaplectic companion
$V^{s\natural}$ adds a super-sector Leech fixed point outside the
$C_2$-cofinite bosonic standard landscape census. The $W_\infty[c
= -214]$ identification, the $\mathcal{T}[A_1,\Sigma_{0,24}]$
Schur-index cross-check, and the $V^{s\natural}$ metaplectic companion
are three coordinate readings on the same class-$\mathbf{M}$
topologisation ladder, each specialising at a different central-charge
fixed point.

%% =====================================
\section{Programme concordance: the Platonic form}
\label{sec:part-viii-concordance}

The following table records the Part VIII theorem anchors.

\begin{center}
\renewcommand{\arraystretch}{1.18}
\begin{tabular}{@{}p{0.29\textwidth}p{0.22\textwidth}p{0.40\textwidth}@{}}
\toprule
\textbf{Structure} & \textbf{Mathematical role} & \textbf{Anchor} \\
\midrule
Curved-Dunn $H^{2}=0$, $g \ge 2$ & Conditional theorem &
 Theorem~\ref{thm:curved-dunn-H2-vanishing-all-genera} \\
Modular-bootstrap$\to$curved-Dunn bridge & Proposition &
 Proposition~\ref{prop:modular-bootstrap-to-curved-dunn-bridge} \\
Genus-1 twisted tensor criterion & Proposition &
 Proposition~\ref{prop:genus1-twisted-tensor-product} \\
Irregular-singular KZB regularity from boundary formal type & Conditional theorem &
 Theorem~\ref{thm:irregular-singular-kzb-regularity} \\
Modular operad composition, all $(g,n)$ & Conditional corollary &
 Corollary~\ref{cor:modular-operad-composition-all-levels} \\
F6 genus-three $\lambda_g$ residue & Computed proposition &
 Proposition~\ref{prop:f6-genus-three-lambda-residue} \\
F6 scalar projection versus socle lift & Obstruction proposition &
 Proposition~\ref{prop:f6-scalar-projection-no-multichannel-lift} \\
DS--Hochschild compatibility, class $\mathbf{M}$ & Theorem &
 Theorem~\ref{thm:chd-ds-hochschild} \\
Universal holography, class $\mathbf{M}$ & Corollary &
 Corollary~\ref{cor:universal-holography-class-M} \\
Weight-completed BV--bar, class $\mathbf{M}$ & Proposition &
 Proposition~\ref{prop:bv-bar-class-m-weight-completed} \\
Periodic-CDG Koszul-compatible (admissible) & Theorem (Vol~I) &
 Theorem~\ref*{V1-thm:periodic-cdg-is-koszul-compatible} \\
KL bar--cobar adjunction, admissible level & Theorem (Vol~I) &
 Theorem~\ref*{V1-thm:admissible-kl-bar-cobar-adjunction} \\
Adams-analog construction & Theorem (Vol~I) &
 Theorem~\ref*{V1-thm:adams-analog-construction} \\
Chain-level chiral Deligne--Tamarkin & Theorem (assoc.-dep.) &
 Theorem~\ref{thm:chd-deligne-tamarkin} \\
Brown-depth Massey $\zeta(3)$ non-vanishing & Proposition &
 Proposition~\ref{prop:massey-yangian-indeterminacy-nonzero} \\
$M_{\mathrm{Kosz}}(\mathcal{A})$ atlas & Theorem &
 Theorem~\ref{thm:mkosz-fourteen-charts} \\
$M_{\mathrm{Kosz}}$ shadow-class stratification & Theorem &
 Theorem~\ref{thm:mkosz-shadow-stratification} \\
Six-slot fingerprint completeness & Theorem &
 Theorem~\ref{thm:fingerprint-complete-ch} \\
G/L/C/M $\hookleftarrow$ six-slot projection & Corollary &
 Corollary~\ref{cor:double-coarse-projection} \\
BGS Quillen norm as 1-loop BV on $\mathbf{H}_{\Delta_5}$ &
 Identification &
 \S\ref{sec:part-viii-quillen-bv} \\
$\mathcal{T}[A_1,\Sigma_{0,24}]$ Schur index ($c_{2d} = -214$) &
 Cross-check &
 \S\ref{sec:part-viii-schur-humbert} \\
Humbert $H_4$ = Argyres--Douglas $(A_1, A_{2N-1})$ &
 Identification &
 \S\ref{sec:part-viii-schur-humbert} \\
$\phi^{(4)} = 0$ on $\mathrm{Conf}_4(E_\tau)$ via Arnold &
 Identification &
 \S\ref{sec:part-viii-schur-humbert} \\
$W_\infty[c=-214]$ chiral-Hochschild primaries $e_3,\ldots,e_6$ &
 Identification &
 \S\ref{sec:part-viii-winf-conway} \\
Conway $V^{s\natural}$ at $c = 12$ as $\Psi^s(\Lambda_{24})$ &
 Identification &
 \S\ref{sec:part-viii-winf-conway} \\
\bottomrule
\end{tabular}
\end{center}

On the non-degenerate locus of the standard landscape, each row is
read with the hypotheses stated in its home theorem. Three questions
remain outside the atlas: the degenerate admissible logarithmic lane,
the associator-independent chain-level chiral Deligne--Tamarkin action,
and finite improvements to the weight-completed bridge. They are
formulated in their home locations
(Remark~\ref{rem:chd-native-vs-derived},
Section~\ref{sec:chd-not-proved},
Remark~\ref{rem:bv-bar-class-m-frontier}) and are not hypotheses for
the theorem atlas stated here.

The programme's Platonic form is the following closed atlas: seven
theorems, an infinite fingerprint, a
$\mathrm{GRT}_{1}(\Q)$-parametrised face family, universal
holography extended to class $\mathbf{M}$, and a mechanically
navigable atlas linking the four theorem threads. From the anchor column
alone one reconstructs the architectural claim: the four frontiers
are not independent.

%% =====================================================================
