\providecommand{\cL}{\mathscr{L}}
\providecommand{\Steinb}{\mathfrak{S}}
\providecommand{\cZ}{\mathcal{Z}}
\providecommand{\cH}{\mathcal{H}}
\providecommand{\fg}{\mathfrak{g}}
\providecommand{\cW}{\mathcal{W}}
\providecommand{\gSC}{\mathfrak{g}^{\mathrm{SC}}}
\providecommand{\gAmod}{\mathfrak{g}^{\mathrm{mod}}_\cA}
\providecommand{\Ydg}{Y^{\mathrm{dg}}}
\providecommand{\Zder}{\operatorname{Z}_{\mathrm{der}}}
\providecommand{\Abulk}{A_{\mathrm{bulk}}}
\providecommand{\Bbound}{B_{\partial}}
\providecommand{\mc}{\operatorname{MC}}
\providecommand{\Res}{\operatorname{Res}}
\providecommand{\RHom}{\operatorname{RHom}}
% Vol III two-stage factorisation (cross-volume macros)
\providecommand{\PhiFA}{\Phi^{\mathrm{FA}}}
\providecommand{\SpCh}{\mathrm{Sp}_{\mathrm{Ch}}}
\providecommand{\HolFA}{\mathrm{HolFA}}
\providecommand{\EdHolFA}{E_d\text{-}\HolFA}
\providecommand{\EnHolFA}{E_n\text{-}\HolFA}
\providecommand{\intSigma}{\textstyle\int_{\Sigma}}
\providecommand{\hCS}{\mathrm{hCS}}

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
\markboth{Preface}{Preface}

\vspace{1em}

\section*{0.\quad The master theorem}

\noindent
The volume proves one functor:
\[
 \boxed{\;
 \Phi_{\mathrm{hol}}\colon
 \mathrm{ChirAlg}^{\omega,\mathrm{BL}}_{X}
 \longrightarrow
 \mathrm{HT\text{-}QFT}_{X \times \R},
 \qquad
 \cA \longmapsto T_\cA,
 \;}
\]
Universal Holography
(Theorem~\ref{thm:universal-holography-master},
Chapter~\ref{ch:programme-climax-platonic}).
The source category is chirally Koszul algebras with conformal
vector at non-critical level (notation $\omega$) and a chosen
boundary linearisation (notation $\mathrm{BL}$). The target is
3d holomorphic-topological gauge theories on $X \times \R$. The
functor sends $\cA$ to a canonical $T_\cA$ with
\[
 \mathrm{Obs}^\partial(T_\cA) \simeq \cA,
 \qquad
 \mathrm{Obs}^{\mathrm{bulk}}(T_\cA) \simeq
 \cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),
\]
the second equivalence as $E_3$-topological factorisation
algebras, realised on the original chain complex for
finite-propagation strata and on the weight-completed / KS-$\rho$
Banach ambient for class~$\mathsf M$ unless raw finite propagation is
separately verified.
Every other theorem in the volume specialises this one.

The functor is unconditional on the
\emph{non-logarithmic, $C_2$-cofinite standard landscape}:
Virasoro $\mathrm{Vir}_c$ at generic $c$, principal $W_N$ for
every $N$, representatives of all $71$ Schellekens $c = 24$
holomorphic rows, Monster $V^\natural$, irrational cosets
$\mathrm{Com}(B,C)$.
Logarithmic $W(p)$ tempering is open
(Conjecture~\ref{conj:tempered-stratum-contains-wp}): Gurarie
1993 and Flohr 1996 exhibit logarithmic amplitudes with unbounded
Massey products despite finite-dimensional Zhu, so the
Zhu-bounded-Massey route available elsewhere on the landscape
does not close $W(p)$.

\paragraph{The five rungs.}
The master theorem is a ladder:
\begin{itemize}\setlength\itemsep{2pt}
\item Rung 1 ($\cA = \cH_k$, abelian Chern--Simons,
 Corollary~\ref{cor:rung-heisenberg}): bulk $=$ boundary, the
 BBL triangle collapses, the genus tower terminates.
\item Rung 2 ($\cA = \widehat{\fg}_k$, non-abelian Chern--Simons,
 Corollary~\ref{cor:rung-affine-km}): braided line category
 $\mathrm{Rep}_q(\fg)$ at $q = e^{i\pi/(k+h^\vee)}$.
\item Rung 3 ($\cA = \mathrm{Vir}_c$ at $c \neq 0$ non-critical,
 Corollary~\ref{cor:rung-virasoro}): \emph{this is 3d quantum
 gravity}, the first non-trivial instance.
\item Rung $N$ ($\cA = W_{N,c}$ via principal Drinfeld--Sokolov,
 Corollary~\ref{cor:rung-w-N}): $E_{N+1}$-topological via
 iterated Sugawara at depth-$N$ Casimir tower.
\item Rung $\infty$ ($\cA = W_\infty[\lambda]$ at generic
 $\lambda$, Corollary~\ref{cor:rung-w-infty},
 Theorem~\ref{thm:climax-w-infty-endpoint}): the operadic
 \emph{horizon} $E_\infty$-topological as
 $\varprojlim_n E_n$-topological.
\end{itemize}
Each rung is a corollary of $\Phi_{\mathrm{hol}}$ at a
particular boundary input. 3d quantum gravity is the $N = 2$
shadow of the $3d{+}\infty$ topological endpoint
(Part~\ref{part:gravity}).

\paragraph{The atom.}
The atom of the volume is the bicoloured operad $\SCchtop$:
closed colour $\FM_k(\C)$ (holomorphic collisions), open colour
$\Eone(m) = \Conf_m^<(\R)$ (topological orderings), no
open-to-closed component (the directionality axiom).
$\SCchtop$ sits as an \emph{intermediary} between $E_1$-chiral
and $E_3$-topological. Dunn additivity does not apply to
bicoloured operads; $E_3$ is reached only when
$\cA$ has a conformal vector at non-critical level via the
Sugawara identity $T(z) = \{Q,G(z)\}$, which makes
$\C$-translations $Q$-exact in cohomology, collapses the two
colours, and lifts the pair
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),\,\cA)$ to
$E_3$-topological by $E_2^{\mathrm{top}} \times
E_1^{\mathrm{top}} = E_3^{\mathrm{top}}$.

The bar complex $\barBch(\cA) = T^c(s^{-1}\bar\cA)$ is an
\emph{$E_1$ chiral coassociative coalgebra} over
$(\mathsf{Ass}^{\mathrm{ch}})^!$, not an $\SCchtop$-coalgebra.
The $\SCchtop$ datum lives on the chiral
derived-centre pair
$(\cC^\bullet_{\mathrm{ch}}(\cA,\cA),\,\cA)$: chiral Hochschild
cochains acting on the boundary algebra by braces. The bar
complex is the \emph{input} that computes
$\cC^\bullet_{\mathrm{ch}}(\cA,\cA)$; the $\SCchtop$ structure
emerges in the \emph{output}.

\paragraph{The geometric stratification.}
Bar chain models are indexed by topologico-combinatoric
stratifications with specified bulk-to-boundary structure: the
topology determines the manifold and its boundary components;
the combinatorics determines the collision patterns, encoded by
boundary strata of the Fulton--MacPherson compactification; the
bulk-to-boundary data determines which strata involve interior
points approaching boundary components. The bar differential is
controlled by codimension-1 strata; the $\Ainf$ relations by
codimension-2 strata; the curvature
$d_B^2 = \kappa_{\mathrm{ch}}(\cA)\cdot\omega_g$ by failure to
extend across certain strata of $\overline{\cM}_{g,n}$.

The volume climbs the stage table:

\begin{center}
\renewcommand{\arraystretch}{1.35}
\small
\begin{tabular}{c p{3.6cm} p{4.8cm} p{3.0cm} l}
\textbf{Stage} & \textbf{Space} & \textbf{Structure / Operad} & \textbf{Lives on} & \textbf{Part} \\
\hline
0 &
 Point &
 $\mathsf{Ass}$ (classical Koszul duality) &
 $\cA$ &
 \ref{part:swiss-cheese} \\[2pt]
1 &
 $\R$ &
 $\mathsf{Ass}^c$ cooperad (deconcatenation coproduct) &
 $B(\cA)$ &
 \ref{part:swiss-cheese} \\[2pt]
2 &
 $[0,1]$, $\R_{\ge 0}$ &
 $W(\mathsf{Ass}) = \Ainf$; modules via one-sided bar &
 $B(\cA)$, $C(I)$ &
 \ref{part:e1-core} \\[2pt]
3 &
 $\C$ &
 BD chiral operad $\{\FM_k(\C)\}$ (OPE residues);
 $E_\infty$: hol.\ $\Etwo$; $\Eone$: $\mathsf{Ass}^{\mathrm{ch}}$ &
 bar differential $D_\cA$ on $B(\cA)$ &
 \ref{part:bbl-core} \\[2pt]
4 &
 $\C \times \R$ &
 Coalgebra over $(\mathsf{Ass}^{\mathrm{ch}})^!$
 (Koszul dual cooperad of chiral $\mathsf{Ass}$) &
 $B(\cA) = \Eone$ dg coassociative coalgebra &
 \ref{part:bbl-core} \\[2pt]
5 &
 $\mathbb{H}$\enspace ($\partial\mathbb{H} = \R$) &
 $\SCchtop$ (two-coloured: closed $\FM_k(\C)$, open $\Eone$,
 no open-to-closed) &
 pair $(\cZ^{\mathrm{der}}_{\mathrm{ch}},\, \cA)$ &
 \ref{part:holography} \\[2pt]
6 &
 $D$ (formal disk) &
 $\End^{\mathrm{ch}}_\cA$ (chiral endomorphism operad,
 $\operatorname{Aut}(\cO)$-equivariant) &
 VA $=$ local model on $D$ &
 \ref{part:examples} \\[2pt]
7 &
 Annulus, $\Sigma_g$ &
 $\SCchtop_{\mathrm{mod}}$ (partially modular);
 curvature $d^2 = \kappa_{\mathrm{ch}}(\cA)\,\omega_g$ &
 $\Theta_\cA$, genus tower &
 \ref{part:examples} \\[2pt]
8 &
 Drinfeld centre &
 $\Etwo$-chiral Gerstenhaber (chiral Deligne--Tamarkin) &
 $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA) = C^\bullet_{\mathrm{ch}}(\cA,\cA)$ &
 \ref{part:gravity} \\[2pt]
9 &
 Topologization &
 $E_3$-\textsc{topological} (3d HT theory $+$ conformal vector;
 Dunn: $\Etwo^{\mathrm{top}} \times \Eone^{\mathrm{top}}$) &
 $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ &
 \ref{part:gravity}
\end{tabular}
\end{center}

Stages~0--6 and~8 are proved at the stated scope per stage:
Stage~0 on a fixed smooth curve (the modular-family extension to
$\overline{\cM}_{g,n}$ is conditional on Francis--Gaitsgory
six-functor base change and Mok25 log-\textsc{fm} nodal sewing,
per
Remark~\ref{V1-rem:A-infinity-2-modular-family-scope});
Stage~6 on the Koszul locus, excluding the critical level and
under \textsc{pbw}-compatibility of the generator filtration;
Stage~8 at the boundary-linear sector of universal celestial
holography, with class-$M$ chain-level closure at $g \ge 1$
conjectural
(Conjecture~\ref{conj:uch-gravity-chain-level}). Stage~7 is
unconditional at genus~$1$
(Proposition~\ref{prop:genus1-twisted-tensor-product}, twisted
K\"unneth on $\FM_k(C_\tau)$); the continuation to $g \ge 2$ is
proved chain-level via the modular-bootstrap-to-curved-Dunn
bridge
(Theorem~\ref{thm:curved-dunn-H2-vanishing-all-genera},
Chapter~\ref{ch:curved-dunn-higher-genus}), with irregular-singular
KZB regularity
(Theorem~\ref{thm:irregular-singular-kzb-regularity}) replacing
the classical KZ Stokes hypothesis after the boundary formal-type
input is supplied. Stage~9 is proved stratum by
stratum, with the ambient of the original complex named in each
case. The Heisenberg stratum (class~G) carries $E_3$-topological
structure unconditionally on the original complex, since
commutativity lets Dunn additivity apply directly. Affine
Kac--Moody at non-critical level (class~L) is topologized on the
cohomology of the total BRST charge $Q_{\mathrm{tot}}$
(Theorem~\ref{thm:E3-topological-km}, holomorphic Chern--Simons
via Costello--Li); the Sugawara identity
$T_{\mathrm{Sug}} = [Q_{\mathrm{CS}}, G_{\mathrm{Sug}}]$ holds on
$Q_{\mathrm{tot}}$-cohomology, not as a strict chain-level
equality on the original complex. Principal and hook-type
non-principal $W$-algebras (class~M) inherit
$E_3$-topologization in the weight-completed ambient
(Theorems~\ref{thm:E3-topological-DS}
and~\ref{thm:E3-topological-DS-general}, via
$T_{\mathrm{DS}} = [Q_{\mathrm{CS}}, G'_f]$ and Cartan-current
exactness); the corresponding direct-sum claim in
$\mathrm{Ch}(\mathrm{Vect})$ is genuinely false, since
$S_4(\mathrm{Vir}_c) = 10/[c(5c+22)] \neq 0$ forces bar cohomology
at weight~$4$, and the weight-completion is where the
Ma\-urer--Cartan pattern closes. Freely-generated finite-jet PVAs
enter through the Khan--Zeng sigma model with a split status:
the classical shifted-cotangent BV action and the
classical-master-equation/PVA-Hamiltonian equivalence are constructed,
whereas the all-loop QME, reflected weights, boundary vertex algebra,
and $E_3$ topological lift are conditional on the KZ analytic SDR and
image-choice Stokes package
(Theorem~\ref{thm:E3-topological-free-PVA}); representatives of the
$71$ Schellekens $c = 24$
rows resolve through the three-stratum partition
$71 = 24_{\mathrm{Niemeier}} + 1_{V_1=0} + 46_{\mathrm{nonlat}}$
(Theorem~\ref{thm:schellekens-71-all-alpha-zero}), Monster
$V^\natural$ through Conway's Leech-no-roots
$\Lambda^\sigma = 0$, the FLM cocycle, and Dong--Mason gauge
uniqueness (Proposition~\ref{prop:monster-alpha-explicit-zero}),
and irrational cosets through the VSKR + BGG criterion strictly
weaker than $C_2$-cofiniteness
(Theorem~\ref{thm:irrational-coset-tempered},
Corollary~\ref{cor:tempered-criterion-refined}), each in the
ambient appropriate to its class. At the critical level
$k = -h^\vee$ the Sugawara construction collapses and the
topologization is $E_2$, not $E_3$.

\paragraph{$\SCchtop$ is the generic case.}
The $\SCchtop$ structure on
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),\,\cA)$ is the structure
that \emph{most} chiral algebras carry on their derived centre.
$E_3$-topological (Stage~9) is the special case requiring a
conformal vector at non-critical level. Examples stuck at
$\SCchtop$: critical-level Kac--Moody $V_{-h^\vee}(\fg)$ where
Sugawara degenerates and the centre jumps to the
Feigin--Frenkel oper centre
$\mathfrak{z}(\widehat{\fg}) \cong
\operatorname{Fun}\operatorname{Op}_{\fg^L}(D^\times)$;
genuinely $\Eone$-chiral algebras (Yangians) without
conformal vector; CY functor outputs lacking conformal vectors.
The operad $\SCchtop$ must be understood as a first-class
object, with seven mutually redundant presentations forming the
\emph{heptagon of equivalences}
(Chapter~\ref{ch:sc-chtop-heptagon}): the five classical faces
(operadic, Koszul-dual, factorisation, BV/BRST,
$L_\infty$-convolution) plus two new faces (Drinfeld-centre via
the factorisation-module category
$\mathrm{Rep}_{\mathrm{fact}}(\cA)$, and derived-AG via global
sections of a stack classifying $E_1$-chiral algebras with
$\SCchtop$-datum).

\section*{I.\quad The open/closed primitive}

\noindent
Two operators $a(z_1, t_1)$ and $b(z_2, t_2)$ on $\C \times \R$
interact in two independent directions. Holomorphic collision
$z_1 \to z_2$ produces the OPE residue; topological separation,
cutting $\R$ between $t_1$ and $t_2$, produces the deconcatenation
coproduct. The ordered bar complex
$B^{\mathrm{ord}}(\cA) = T^c(s^{-1}\bar\cA)$ encodes both:
\[
d_{\barBch}[s^{-1}a \,|\, s^{-1}b]
\;=\;
\Res_{z_1 = z_2}\!\bigl[
 a(z_1)\,b(z_2)\cdot\eta_{12}
\bigr],
\qquad
\eta_{12} = d\log(z_1 - z_2),
\]
\begin{equation}\label{eq:preface-delta}
\Delta[s^{-1}a_1|\cdots|s^{-1}a_n]
\;=\;
\sum_{i=0}^{n}
[s^{-1}a_1|\cdots|s^{-1}a_i]
\;\otimes\;
[s^{-1}a_{i+1}|\cdots|s^{-1}a_n],
\end{equation}
with the differential a coderivation of the coproduct:
$\Delta \circ D_\cA = (D_\cA \otimes \id + \id \otimes D_\cA)
\circ \Delta$. Collisions in $\C$ commute with cuts in $\R$.
The differential is holomorphic factorisation on
$\FM_k(\C)$; the coproduct is topological factorisation on
$\Conf_k^{<}(\R)$; together they make $B^{\mathrm{ord}}(\cA)$ an
$E_1$ dg coassociative coalgebra
(Theorem~\ref{thm:rosetta-e1-coalgebra}). The form
$\eta_{12}$ is a bar coefficient (a logarithmic one-form),
\emph{not} a connection form: the KZ connection on conformal
blocks is the distinct rational form
$\nabla_{\mathrm{KZ}} = d - \Omega\,dz/((k+h^\vee)z)$. The
Arnold relation
$\eta_{12}\wedge\eta_{23} + \eta_{23}\wedge\eta_{31}
+ \eta_{31}\wedge\eta_{12} = 0$ on $\Conf_3(\C)$ forces
$D_\cA^2 = 0$ at genus~$0$.

The ordered bar is the \emph{primitive object} of the volume.
The symmetric bar $B^{\Sigma}(\cA)$ of Volume~I is its
$\Sigma_n$-coinvariant shadow under the lossy averaging map
$\operatorname{av}\colon \mathfrak{g}^{E_1}_\cA
\to \mathfrak{g}^{\mathrm{mod}}_\cA$. The modular characteristic
$\kappa_{\mathrm{ch}}(\cA)$ is the leading scalar surviving
averaging. For abelian algebras
$\kappa_{\mathrm{ch}} = \mathrm{av}(r(z))$; for non-abelian
Kac--Moody a Sugawara shift intervenes,
$\mathrm{av}(r(z)) + \dim\fg/2 = \kappa_{\mathrm{ch}}(\widehat{\fg}_k)$
(Section~\ref{sec:rosetta-stone}). The five Volume~I
theorems A--D and~H are the invariants that survive the
projection.

\paragraph{The Heisenberg on $\C \times \R$.}
Take $\cA = \cH_k$: one generator $J$, one OPE
$J(z)\,J(w) \sim k/(z-w)^2$. Two operators sit at $(z_1, t_1)$,
$(z_2, t_2)$ with $t_1 < t_2$. The bar element
$[s^{-1}J \,|\, s^{-1}J]$ has bar differential extracting the
single non-vanishing mode product $J_{(1)}J = k$ (no simple-pole
self-interaction):
$d_{\barBch}[s^{-1}J | s^{-1}J] = k$. The deconcatenation
coproduct on the same element factorises to one field per
half-line; coderivation:
$D_\cA[s^{-1}J | s^{-1}J] = k$, then
$\Delta(k) = k \otimes [\,] + [\,] \otimes k$, matching
$(D_\cA \otimes \id + \id \otimes D_\cA)\Delta[s^{-1}J | s^{-1}J]$.
Collision in $\C$ commutes with cutting in $\R$.

The bar element lives on
$\FM_2(\C) \times \Conf_2^<(\R)$. The topological factor is
contractible; its coalgebra structure contracts to strict
deconcatenation; no higher homotopies survive. For the
Heisenberg, the Maurer--Cartan element collapses to
$\Theta_{\cH_k} = k \cdot \eta \otimes \Lambda$; the genus-$g$
projection is $F_g(\cH_k) = k \cdot \lambda_g^{\mathrm{FP}}$
\textup{(\textsc{uniform-weight})}. The single scalar $k$
controls every entry of the census table.

\section*{II.\quad The seven theorems}

\noindent
Volume~I proves five theorems A--D and~H for chiral algebras on
curves; they live in the symmetric bar $B^\Sigma(\cA)$ and have
scalar invariants $\kappa_{\mathrm{ch}}(\cA)$,
$\mathrm{obs}_g = \kappa_{\mathrm{ch}}\cdot\lambda_g$
\textup{(\textsc{uniform-weight})}, the shadow tower, the
discriminant $\Delta = 8\kappa_{\mathrm{ch}} S_4$. The $E_1$
data (the $R$-matrix, the Yangian, the $\SCchtop$ datum on the
pair) is richer than these scalar invariants. This volume adds
two theorems native to the 3d~HT register, raising the
architectural count to seven.

\begin{itemize}\setlength\itemsep{2pt}
\item \textbf{A} (Bar--cobar $(\infty,2)$-properad equivalence)
 ; Vol~I Theorem~A extended via
 Proposition~\ref{prop:R-twisted-sigma-n-descent}
 (Part~\ref{part:swiss-cheese}); ordered bar primary,
 symmetric bar is $R$-twisted $\Sigma_n$-coinvariant image.
 The $(\infty,2)$-adjunction $\Omega^{\mathrm{ch}} \dashv
 B^{\mathrm{ch}}$ lifts the 1-categorical Vol~I statement: at
 the 2-cell level, compatibility 2-morphisms assemble into an
 Auslander--Reiten triangulated structure, which is the
 2-categorical $\SCchtop$ coloured shuffle; the closed-colour
 FM collisions and the open-colour $\Eone$ orderings compose at
 2-morphism level exactly as the AR translate composes
 irreducible morphisms in a triangulated category. On
 $\overline{\cA_2}$ away from the Humbert discriminant the
 bar-cobar octachotomy at codimension~$3$ (eight ambients
 distinguished by the stratification of
 $\overline{\cA_2}\setminus\bigcup_n H_n$) acquires a direct
 holomorphic-topological reading: each of the eight ambients is
 a specific Swiss-cheese colouring datum on the $\SCchtop$
 bar-differential, with the closed $\FM_k(\C)$ colour recording
 the Kodaira fibre type and the open $\Eone$ colour recording
 the Humbert intersection pattern.
\item \textbf{B} (Koszul-locus inversion) --
 Theorem~\ref{thm:filtered-koszul} (Part~\ref{part:e1-core});
 conilpotent-complete $E_1$-chiral coalgebras are reflective
 subcategory of augmented chiral algebras.
\item \textbf{C} (Shifted-symplectic Lagrangian complementarity)
 ; Vol~I Theorem~C upgraded to the tensor-Arakelov
 companion: the characteristic bundle
 $Q_\bullet(\cA) \to \overline{\cM}_{g,n}$, together with its
 Koszul-dual mate $Q_\bullet(\cA^!)$, admits a
 $-(3g{-}3{+}n)$-shifted symplectic form $\omega^{\mathrm{tot}}$
 for which $\cA \mapsto (Q_\bullet(\cA), Q_\bullet(\cA^!))$ is
 a Lagrangian section
 (Part~\ref{part:examples} opener).
\item \textbf{D} (Tensor-Arakelov curvature); Vol~I's scalar
 $d_B^2 = \kappa_{\mathrm{ch}}\cdot\omega_g$ upgraded to
 $K(\cA) \in \operatorname{Sym}^2(\cF^\vee) \otimes
 \Omega^2(\overline{\cM}_{g,n})$ with
 $\operatorname{tr}_\cF(K) = \kappa_{\mathrm{ch}}\cdot\omega_g$
 (Part~\ref{part:examples} opener).
\item \textbf{H} (Chiral Hochschild concentration; chiral Higher
 Deligne); Vol~I Theorem~H concentrated
 $\ChirHoch^\bullet$ in $\{0,1,2\}$ promoted to universal
 mixed chiral-topological $\SCchtop$ action on
 $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$:
 Theorem~\ref{thm:chiral-higher-deligne} in
 Chapter~\ref{ch:chiral-higher-deligne}
 (Part~\ref{part:gravity}). The sharp vanishing
 $\ChirHoch^k(\cA) = 0$ for $k \ge d+1$ on CY-$d$ input
 enlarges the concentration window from the ambient-curve
 $\{0,1,2\}$ to the CY-$d$-enlarged $\{0,1,\ldots,d\}$ on the
 Vol~III functor $\Phi_d = {\SpCh}_{\Sigma_{d-1},C}\circ\PhiFA_d$
 (two-stage: stage~1 canonical $E_d$-holomorphic factorisation;
 stage~2 curve-specialisation via factorisation-homology
 pushforward), so that chiral Hochschild is the
 hinge between Vol~II's holomorphic-topological structure and
 Vol~III's CY input: $\Phi_3(\text{CY-}3)$ concentrates in
 $\{0,1,2,3\}$, $\Phi_4(\text{CY-}4)$ in $\{0,1,2,3,4\}$, and
 the Vol~II ambient-curve restriction is the $d = 2$
 specialisation. Theorem~H concentration is proved
 unconditionally in Vol.~I via the chiral-PBW plus
 Orlik--Solomon route; the programme-level conjecture that
 concentration is also a \emph{consequence} of
 $E_3$-rigidity-at-a-point plus chiral-$E_3$-PBW on the
 derived centre is recorded as
 Conjecture~\ref{conj:H-concentration-via-E3-rigidity}.
\item \textbf{F} (Universal Holography functor)
 $\Phi_{\mathrm{hol}}\colon \mathrm{ChirAlg}^{\omega,\mathrm{adm}}_X
 \to \mathrm{HT\text{-}QFT}_{X \times \R}$ --
 Theorem~\ref{thm:universal-holography-functor},
 Theorem~\ref{thm:universal-holography-master}
 (Part~\ref{part:gravity}); class~$\mathbf{M}$ chain-level
 closure is in the weight-completed / pro ambient, with raw
 original-complex descent only under the finite-propagation condition
 of Theorem~\ref{thm:chain-level-e3-original-complex-conditional}.
\item \textbf{G} (Infinite Fingerprint classification) --
 the six-slot fingerprint
 $\varphi'(\cA) = (p_{\max}, r_{\max}, \chi_{\mathrm{VOA}},
 n_{\mathrm{strong}}, \mathrm{coset}, \kappa_{\mathrm{ch}})$
 is a complete invariant of the Koszul-bar-complex structure of
 $\cA$ on the standard landscape
 (Theorem~\ref{thm:fingerprint-complete-ch},
 Chapter~\ref{chap:infinite-fingerprint}); the
 $\mathbf{G}/\mathbf{L}/\mathbf{C}/\mathbf{M}/\mathbf{FF}$
 quadrichotomy with critical-level fifth class $\mathbf{FF}$ is
 the double coarse projection forgetting
 $\kappa_{\mathrm{ch}}$ and projecting onto $r_{\max}$.
\end{itemize}

\paragraph{The three structures that acquire physical content.}
Beyond the scalar shadow, three $E_1$ structures \emph{are}
physics:
\emph{the spectral $R$-matrix} (ordered collision at degree~$2$
gives $r_{\cH_k}(z) = k/z$ and
$r_{\widehat{\fg}_k}(z) = k\,\Omega/z$ in the trace-form
convention vanishing at $k = 0$, with KZ equivalent
$r(z) = \Omega/((k+h^\vee)z)$; degree~$3$ gives Yang--Baxter
from three-face Stokes on $\FM_3(\C)$,
Theorem~\ref{thm:YBE}; on evaluation modules for affine
Kac--Moody the braided line category is
$\operatorname{Rep}_q(\fg)$ at $q = e^{i\pi/(k+h^\vee)}$,
Theorem~\ref{thm:affine-monodromy-identification});
\emph{the line category and the Koszul dual} (line operators
along $\R_+ \times \{0\}$ carry modules for the open-colour
Koszul dual; for Heisenberg
$\cA^!_{\mathrm{line}} = Y(\mathfrak{u}(1))$, for affine
Kac--Moody $\cA^!_{\mathrm{line}} = \Ydg(\fg)$, the complete
spectral Drinfeld strictification
(Theorem~\ref{thm:complete-strictification}) holds for every
simple Lie type via root-multiplicity-one rigidity); and
\emph{the bulk-boundary-line triangle}
(throughout Vol II, ``bulk'' denotes T18(iii), the 3d HT bulk on
$\C\times\R_+$, whose local operators $\Abulk$ coincide with T18(i),
the chiral derived centre $Z^{\mathrm{der}}_{\mathrm{ch}}(\Bbound)$
on the chirally Koszul locus; T18(ii) RT topological bulk is a
distinct construction and appears only where explicitly invoked)
\smallskip
($\Abulk \simeq \chi^\bullet_{\mathrm{ch}}(\Bbound)$
unconditionally for classes~$\mathbf{G}$, $\mathbf{L}$,
$\mathbf{C}$ and at genus~$0$ on class~$\mathbf{M}$
(Proposition~\ref{prop:uch-mellin-shadow}); on class~$\mathbf{M}$
at genus $g \geq 1$ the equivalence is established in the
weight-completed ambient via the MC5 pattern only, chain-level
closure in $\mathrm{Ch}(\mathrm{Vect})$ remaining open as
Conjecture~\ref{conj:uch-gravity-chain-level}.
Further, $\Abulk \simeq \Zder(\Bbound)$ on the
boundary-linear exact sector,
Theorem~\ref{thm:boundary-linear-bulk-boundary},
$\cC_{\mathrm{line}} \simeq \cA^!_{\mathrm{line}}\text{-mod}$ on
the chirally Koszul locus,
Theorem~\ref{thm:lines_as_modules}; two parallel lines interact
through the bulk producing meromorphic braiding).
The global triangle (boundary determines bulk determines
boundary) is proved at the boundary-linear level; the full
reconstruction beyond that locus is open (frontier F4).

\section*{III.\quad Four conceptual leaps}

\noindent
Four leaps away from classical Koszul duality organise the
mathematics. The bar complex indexes the first three; the fourth
(derived centres produce physics) is the content of
Theorem~\ref{thm:universal-holography-master}.

\paragraph{(1) Commutative to $E_1/\Ainf$.}
Classical Koszul duality works for commutative and associative
algebras. The chiral setting replaces commutativity by an
$E_1$-chiral $\Ainf$ structure: holomorphic direction promotes
multiplication to the Stasheff hierarchy on $\FM_k(\C)$;
topological direction promotes concatenation to deconcatenation
on $\Conf_k^<(\R)$. The bar differential is a coderivation
determined by cogenerator projections $m_k\colon A^{\otimes k}
\to A((\lambda_1))\cdots((\lambda_{k-1}))$ with
$\deg m_k = 2 - k$ and spectral parameters
$\lambda_j = z_j - z_k$. The identity $D_\cA^2 = 0$ is the
Stasheff hierarchy
\[
\sum_{\substack{i+j = n+1 \\ i,j \ge 1}}\;\sum_{s=0}^{n-j}
\pm\; m_i\bigl(a_1, \ldots, m_j(a_{s+1}, \ldots, a_{s+j}),
\ldots, a_n\bigr) \;=\; 0,
\]
each relation a Stokes theorem on $\FM_n(\C)$. At $n = 3$
the Stasheff associahedron $K_3 = [0,1]$ has endpoints
$D_{12}, D_{23}$, and $m_3$ corrects the failure of $m_2$ to be
strictly associative ($m_3 = 0$ for Heisenberg, $m_3 \neq 0$ for
Kac--Moody and Virasoro). At $n = 4$ the Stasheff pentagon
$K_4$ has five faces; for $\cW_3$, $m_4$ is non-zero with
coefficient $32/(22+5c)$ from the $WW\Lambda$ channel. In
general $\FM_n(\C)/\mathrm{Aff}(\C)$ is a manifold with corners
of real dimension $2n - 4$, and $\partial^2 = 0$ on $\FM_n(\C)$
(every codim-2 face reached by two codim-1 faces with opposite
orientations) is what makes $D_\cA^2 = 0$ hold.

\paragraph{(2) Genus~$0$ to modular.}
Classical Koszul duality is genus~$0$ on the formal disk. The
modular setting lifts the bar complex over
$\overline{\cM}_{g,n}$ with genus-$1$ curved differential
$d_{\mathrm{fib}}^2 = \kappa_{\mathrm{ch}}(\cA)\cdot\omega_1$
and chain-level continuation
$d_{\mathrm{fib}}^2 = \kappa_{\mathrm{ch}}(\cA)\cdot\omega_g$
\textup{(\textsc{uniform-weight})} for all $g \ge 2$ via
curved-Dunn $H^2 = 0$
(Theorem~\ref{thm:curved-dunn-H2-vanishing-all-genera});
on the nose at $g \in \{1,2\}$ (where the socle $\cN^g$ vanishes),
and at $g \ge 3$ for multi-generator families this requires the
scalar-diagonal hypothesis
(Definition~\ref{V1-def:scalar-diagonal-hypothesis}) together with
Faber's $\lambda_g$-conjecture for the on-the-nose lift from
the socle. The first scalar residue at that boundary is computed:
\[
 \lambda_3^{\mathrm{FP}}
 =
 \int_{\overline{\cM}_{3,1}}\psi_1^4\lambda_3
 =
 \frac{31}{967680}
\]
(Proposition~\ref{prop:f6-genus-three-lambda-residue}). This is a
scalar F6 witness, not the multi-channel socle lift
(Proposition~\ref{prop:f6-scalar-projection-no-multichannel-lift}).
The
Maurer--Cartan element $\Theta_\cA$ lives in
$\gAmod := \Hom_\Sigma(F\!\Com, \End_{\barBch(\cA)})$; the shadow
tower projects onto degree strata; the discriminant
$\Delta = 8\kappa_{\mathrm{ch}} S_4$ classifies the
$\kappa_{\mathrm{ch}} \neq 0$ locus into G/L/C/M, with the
$\kappa_{\mathrm{ch}} = 0$ stratum constituting a fifth class
$\mathbf{FF}$ (Feigin--Frenkel) where Sugawara fails,
topologisation does not reach $E_3^{\mathrm{top}}$, and chiral
Hochschild is infinite-dimensional. Family-specific values:
$\kappa_{\mathrm{ch}}(\cH_k) = k$ with
$F_1(\cH_k) = -k\log\eta(\tau)$ where
$\eta(\tau) = q^{1/24}\prod_{n \ge 1}(1 - q^n)$,
$q = e^{2\pi i \tau}$;
$\kappa_{\mathrm{ch}}(\mathrm{Vir}_c) = c/2$ with
$F_1 = -(c/2)\log\eta(\tau)$;
$\kappa_{\mathrm{ch}}(\widehat{\fg}_k) = \dim\fg\,(k+h^\vee)/(2h^\vee)$
(at $k = 0$, $\kappa_{\mathrm{ch}} = \dim\fg/2$ from the
Sugawara shift, not zero); $\kappa_{\mathrm{ch}}(\cW_N) =
c\cdot(H_N - 1)$ with $H_N = \sum_{j=1}^N 1/j$ (at $N = 2$,
$H_2 - 1 = 1/2$ recovers $\kappa_{\mathrm{ch}} = c/2$; the correct expression
is $H_N - 1$, not the harmonic number $H_{N-1}$, since
$H_{N-1} \ne H_N - 1$ in general). The scalar genus tower
\textup{(\textsc{uniform-weight})} satisfies
$\sum_{g \ge 1} F_g \cdot \hbar^{2g}
= \kappa_{\mathrm{ch}}(\cA)\cdot\bigl(\hat{A}(i\hbar) - 1\bigr)$
with $F_1 = \kappa_{\mathrm{ch}}/24$,
$F_2 = 7\kappa_{\mathrm{ch}}/5760$ (linear in $\kappa_{\mathrm{ch}}$).

\paragraph{(3) Local to nonlocal.}
All standard vertex algebras (including those with OPE poles)
are $E_\infty$: locality is compatible with arbitrary pole
order. The genuinely $E_1$ layer is where the spectral
$R$-matrix is an independent input, not derived from the local
OPE, and the line-side dual $\cA^!_{\mathrm{line}}$ is a
dg-shifted Yangian. The ordered bar $B^{\mathrm{ord}}$ is
primitive; $B^{\Sigma}$ is its $R$-matrix-twisted
$\Sigma_n$-coinvariant projection. The distinction is
provenance, not pole order. For $E_\infty$-chiral algebras
the $R$-matrix is derived from the OPE; for genuinely $E_1$
algebras (Yangians, EK quantum vertex algebras) the RTT relation
$R_{12}(z_1{-}z_2) T_1(z_1) T_2(z_2) =
T_2(z_2) T_1(z_1) R_{12}(z_1{-}z_2)$ is an axiom.
The $\Sigma_n$-coinvariant projection
$\mathrm{av}\colon\mathfrak{g}^{E_1}_\cA \to \mathfrak{g}^{\mathrm{mod}}_\cA$
destroys the spectral structure; the symmetric bar sees only
its trace.

\paragraph{(4) Derived centres produce physics.}
The first three leaps describe the $E_n$-chiral algebras of
Volume~I as algebraic-geometric objects. This volume adds the
fourth leap: compute $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$
and discover that it IS the bulk algebra of a real 3d gauge
theory. Volume~I constructs the derived centre and proves its
algebraic-geometric properties (the $E_2$/$E_3$ structure, the
concentration in $\{0,1,2\}$, the $\SCchtop$ datum). This
volume interprets these constructions physically.

For Heisenberg:
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cH_k) = \cH_k$ (bulk equals
boundary), abelian Chern--Simons at level~$k$, $R(z) = e^{k\hbar/z}$
scalar, $F_g = k\cdot\lambda_g^{\mathrm{FP}}$. For Kac--Moody:
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\widehat{\fg}_k)$ carries
$E_3^{\mathrm{top}}$
(Theorem~\ref{thm:E3-topological-km}); non-abelian holomorphic
Chern--Simons; $\Ydg(\fg)$ on lines; reduced line category
$\operatorname{Rep}_q(\fg)$. For Virasoro:
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\mathrm{Vir}_c)$ is the
gravitational bulk, infinite-depth, the shadow tower reads as
the gravitational perturbation series. The same mathematical
object (the derived centre), read through Costello--Gaiotto
twisted holography, becomes a 3d gauge theory whose boundary is
the chiral algebra. The three algebraic-geometric leaps produce
the raw material; the fourth physical leap discovers what that
material means.

\section*{IV.\quad The Steinberg principle}

The Steinberg variety
$\widetilde{\cN} \times_{\fg} \widetilde{\cN}$ is one geometric
object; Borel--Moore homology, $K$-theory, and equivariant
derived category extract three algebraic invariants. The chiral
bar complex $\barBch(\cA)$ on
$\FM_k(\C) \times \Conf_k^{<}(\R)$ is one coalgebra, and three
functors project three objects from it:
\[
\renewcommand{\arraystretch}{1.3}
\begin{array}{l|l|l}
\text{Functor} & \text{Output} & \text{Meaning} \\
\hline
\Omega(\barBch(\cA)) & \cA &
 \text{cobar: inversion (left adjoint of bar)} \\
\mathbb{D}_{\mathrm{Ran}}(\barBch(\cA)) &
 \barBch(\cA^!) & \text{Verdier on Ran: Koszul duality} \\
C^\bullet_{\mathrm{ch}}(\cA,\cA) &
 \cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA) &
 \text{Hochschild cochains: derived centre (bulk)}
\end{array}
\]
The three functors are genuinely distinct: cobar is inversion,
Verdier is Koszul duality, Hochschild is the derived centre; the
three must never be conflated. Three Hochschild theories coexist:
\[
\renewcommand{\arraystretch}{1.3}
\begin{array}{l|l|l}
\text{Hochschild} & \text{Composition} & \text{Output} \\
\hline
\text{chiral} & \text{OPE on } \Ran(\C) &
 \cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA) \\
\text{topological} & E_1\text{-bar on } \R &
 \text{line category} \\
\text{categorical} & \text{Morita on } \C \times \R &
 \text{slab bimodule (BZFN~\cite{BZFN10})}
\end{array}
\]
The derived centre is the first. Identifying any two collapses
the architecture: each chapter below projects the single
coalgebra through one of the three.

The parallel with the Chriss--Ginzburg theory is precise:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{ll}
\textbf{Chriss--Ginzburg} & \textbf{Chiral bar complex} \\ \hline
Springer resolution
$\widetilde{\cN} \to \fg$
 & Lagrangian embedding
$\cL_\cA \hookrightarrow \cM$ \\[2pt]
Steinberg
$\widetilde{\cN} \times_{\fg} \widetilde{\cN}$
 & $\barBch(\cA)$ on
$\FM_k(\C) \times \Conf_k^{<}(\R)$ \\[2pt]
Convolution $\Rightarrow$ Hecke algebra $H_W$
 & Convolution $\Rightarrow$
$\SCchtop$-algebra \\[2pt]
Springer correspondence
 & bulk-boundary-line triangle \\[2pt]
Kazhdan--Lusztig basis
 & MC element $\alpha_T$ \\[2pt]
$H_W$ at $q=1$ $\Rightarrow$ $\C[W]$
 & classical limit $\Rightarrow$ PVA \\[2pt]
KL polynomials
 & shadow obstruction tower \\[2pt]
Hecke eigenvalues
 & spectral $R$-matrix
\end{tabular}
\end{center}

A chiral algebra is a point in the derived symplectic category:
a Lagrangian $\cL_\cA \hookrightarrow \cM_{\mathrm{vac}}(\cA)$.
The bar complex is the $E_1$ coassociative endomorphism coalgebra
of this point; the chiral Hochschild cochains
$C^\bullet_{\mathrm{ch}}(\cA,\cA)$, computed from the bar
complex, carry the $\SCchtop$ composition law via brace
operations; Koszul duality is the symplectic complement; the
genus tower is the deformation over $\overline{\cM}_{g,n}$.

\paragraph{Lagrangian self-intersection and formal Darboux.}
The bar complex is a formal Koszul model of the Lagrangian
self-intersection
$\cL_\cA \times_{\mathscr{M}}^h \cL_\cA$ in a $(-2)$-shifted
symplectic stack $\mathscr{M}$
(Theorem~\ref{thm:bar-is-self-intersection}):
$\cL_\cA \times_{\mathscr{M}}^h \cL_\cA \simeq
\Spec H^\bullet(\barBch(\cA))$. Concentration in a single
degree (chirally Koszul) is a clean intersection. Heisenberg:
transversal (class~$\mathbf{G}$). Kac--Moody: Lie-transverse
(class~$\mathbf{L}$). Virasoro: infinite excess Tor
(class~$\mathbf{M}$). The HKR theorem for Lagrangian embeddings
gives $\mathrm{ChirHoch}^\bullet(\cA) \simeq \cO(T^*[-1]\cL_\cA)$;
the formal Darboux theorem
(Theorem~\ref{thm:holographic-reconstruction}) supplies the
closed $1$-form reconstructing the $(-2)$-shifted symplectic
ambient. Class~$\mathbf{G}$: $\mathscr{M} = T^*[-2]\cL_{\cH_k}$.
Class~$\mathbf{L}$: Darboux datum is the KZ connection.
Class~$\mathbf{M}$: Darboux datum is the infinite shadow tower.

\paragraph{The Steinberg projections computed.}
For each class, the three functors produce three distinct
objects from the single coalgebra:

\smallskip\emph{Heisenberg} $\cH_k$ (class~$\mathbf{G}$): cobar
$\Omega(\barBch(\cH_k)) \simeq \cH_k$ (trivial inversion);
Verdier $\mathbb{D}_{\Ran}(\barBch(\cH_k)) \simeq
\barBch(\mathrm{Sym}^{\mathrm{ch}}(V^*))$;
derived centre $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cH_k) = \cH_k$.
Three objects coincide at cohomology level: the Lagrangian
self-intersection is clean.

\smallskip\emph{Kac--Moody} $\widehat{\fg}_k$ (class~$\mathbf{L}$): cobar
$\Omega(\barBch(\widehat{\fg}_k)) \simeq \widehat{\fg}_k$
(Garland--Lepowsky concentration); Verdier
$\mathbb{D}_{\Ran}(\barBch(\widehat{\fg}_k)) \simeq
\barBch(\widehat{\fg}_{-k-2h^\vee})$ (Feigin--Frenkel duality);
derived centre carries $E_3^{\mathrm{top}}$
(Theorem~\ref{thm:E3-topological-km} for simple~$\fg$, via
Sugawara at $k \neq -h^\vee$). At critical level $k = -h^\vee$
the Verdier dual is $\widehat{\fg}_{h^\vee}$ but the derived
centre degenerates to the Feigin--Frenkel oper centre
$\mathfrak{z}(\widehat{\fg}_{-h^\vee})$.

\smallskip\emph{Virasoro} $\mathrm{Vir}_c$ (class~$\mathbf{M}$):
cobar $\Omega(\barBch(\mathrm{Vir}_c)) \simeq \mathrm{Vir}_c$;
Verdier $\mathbb{D}_{\Ran}(\barBch(\mathrm{Vir}_c)) \simeq
\barBch(\mathrm{Vir}_{26-c})$ (Virasoro self-duality at the
family-specific value $c = 13$); derived centre is the
gravitational bulk. The infinite excess Tor (all $m_k \neq 0$)
means infinitely many quantum corrections; the shadow tower
reads them off: $\kappa_{\mathrm{ch}} = c/2$ at degree~$2$;
quartic contact $10/[c(5c{+}22)]$ at degree~$4$; an infinite
tail forced by the Virasoro self-coupling $T_{(1)}T = 2T$.

\section*{V.\quad The Swiss-cheese operad $\SCchtop$}

The product $\FM_k(\C) \times \Conf_k^<(\R)$ is the space of
operations of a two-coloured operad:
\begin{alignat*}{2}
&\text{closed-to-closed:}\quad
&&\SCchtop(\mathsf{ch}^k;\,\mathsf{ch})
\;=\; \FM_k(\C), \\
&\text{mixed-to-open:}\quad
&&\SCchtop(\mathsf{ch}^k, \mathsf{top}^m;\,\mathsf{top})
\;=\; \FM_k(\C) \times E_1(m), \\
&\text{open-to-closed:}\quad
&&\SCchtop(\ldots, \mathsf{top}, \ldots;\,\mathsf{ch})
\;=\; \varnothing.
\end{alignat*}
Closed colour: holomorphic collisions on $\FM_k(\C)$. Open
colour: topological orderings on $E_1(m) = \Conf_m^<(\R)$.
Mixed: the product. Composition is FM substitution on the
closed factor, interval insertion on the open factor. The empty
open-to-closed component is directionality: bulk restricts to
boundary, not conversely.

The bar complex $(\barBch(\cA), D_\cA, \Delta)$ is an $E_1$ dg
coassociative coalgebra: the differential $D_\cA$ encodes the
$A_\infty$-chiral structure, the coproduct $\Delta$ is
deconcatenation. The $\SCchtop$ structure emerges in the chiral
derived centre: $(\cC^\bullet_{\mathrm{ch}}(\cA,\cA),\,\cA)$
carries Swiss-cheese structure via brace operations from the
chiral endomorphism operad. The classical Swiss-cheese operad
is Koszul (Livernet); Kontsevich formality and bar-cobar
transfer give homotopy-Koszulity
$\Omega\mathbf{B}(\SCchtop) \xrightarrow{\sim} \SCchtop$
(Theorem~\ref{thm:homotopy-Koszul}). The Koszul dual cooperad
$(\SCchtop)^! = (\mathsf{Lie},\, \mathsf{Ass},\,
\text{shuffle-mixed})$
(Proposition~\ref{thm:SC-self-duality}) exchanges the closed
colour $\mathsf{Com}$ with $\mathsf{Lie}$ while preserving
$\mathsf{Ass}$; the duality functor on $\SCchtop$-algebras is
an involution; the open-colour dual $\cA^!_{\mathrm{line}}$
carries the dual algebraic structure. $\SCchtop$ is not self-dual: the duality functor is an
involution, but the operad and its dual differ in dimensions.

$\SCchtop$ sits between $\Eone$-chiral and $E_3$-topological:
\[
\renewcommand{\arraystretch}{1.3}
\begin{array}{l|l|l}
\text{Passage} & \text{Requirement} & \text{Status} \\
\hline
\Eone \to \Etwo & \text{Hochschild cochains} &
 \text{automatic (Deligne, proved)} \\
\Etwo \to \text{3d HT bulk} &
 \text{3d HT theory with boundary } \cA &
 \text{KM: hol.~CS (Costello--Li);} \\
 & & \text{KZ finite-type: conditional SDR} \\
\SCchtop \to E_3\text{-top} &
 \text{conformal vector, non-critical level} &
 \text{KM, DS/}W\text{ proved; free PVA conditional;} \\
 & & W(p) \text{ open (F1)}
\end{array}
\]

\paragraph{Heptagon of equivalences.}
Beyond the five classical presentations
(Chapter~\ref{ch:sc-chtop-heptagon}):
\begin{enumerate}[label=(\arabic*)]
\item \emph{Operadic}: generators (codim-1 boundary strata
 $\FM_k(\C)\times\Conf_m(\R)$), relations (codim-2);
\item \emph{Koszul-dual}:
 $(\SCchtop)^! = (\mathsf{Lie},\mathsf{Ass},\text{shuffle-mixed})$;
 $W(\SCchtop) = $ cofibrant replacement;
\item \emph{Factorisation}:
 $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA) =
 E_2$-chiral centre acting on $\cA$ via universal brace;
\item \emph{BV/BRST}:
 $\mathrm{Obs}(U) = $ logarithmic SC-algebra; QME $=$
 open/closed MC equation;
\item \emph{$L_\infty$-convolution}:
 $\mathfrak{g}^{\mathrm{SC}}_T = L_\infty$ convolution from bar
 cooperad $B(\SCchtop)$;
\end{enumerate}
two new faces: (6)~Drinfeld-centre via the factorisation-module
category $\mathrm{Rep}_{\mathrm{fact}}(\cA)$; (7)~derived-AG via
PTVV on $\mathrm{Map}(X \times \R_{\ge 0}, B \mathrm{SC\text{-}Alg})$.
The seven presentations are mutually quasi-isomorphic; the
classical pentagon spans the first five faces. The seven-fold
identification of the collision residue $r(z)$ on the affine
lineage (Section~XI) is a parallel heptagon on a different
object.

\paragraph{Chiral Kontsevich formality on the Koszul locus.}
On the admissible locus
$U^{\mathrm{adm}} = \overline{\cA_2}\setminus\bigcup_n H_n$
(the parameter stratum excised of every Humbert divisor where
the Igusa cusp form $\Phi_{10}$ is regular) the chiral polyvector
sheaf is formality-equivalent to chiral Hochschild on the K3 chiral
bialgebra $\mathbf{H}_{\Delta_5}$ (the Schiffmann--Vasserot paramodular
BKM master object associated to the Gritsenko cusp form
$\Delta_5 = \mathrm{Grit}(\eta^9\vartheta_1)$ of weight~$5$, with
Siegel character $1/\Phi_{10} = 1/\Delta_5^2$):
\[
 T^{\mathrm{poly}}_{\mathrm{ch}}(\overline{\cA_2})\big|_{U^{\mathrm{adm}}}
 \;\xrightarrow{\sim}\;
 \ChirHoch^\bullet(\mathbf{H}_{\Delta_5})\big|_{U^{\mathrm{adm}}}.
\]
The obstruction to extending the quasi-isomorphism across the
boundary $H_n$ is the Malcev-ladder cocycle at level $n$: the
$n$th rung of the Malcev tower on
$\pi_1(\overline{\cA_2}\setminus H_n)$ supplies a
length-$n$ iterated commutator whose class in
$H^2(\mathfrak{m}_n)$ is exactly the $\phi^{(n)}$ coherence of
the class-$\mathbf{M}$ $\Ainf$-tower. Across $H_1\cup H_4$ the
cocycles $\phi^{(1)}$ and $\phi^{(4)}$ are non-zero; across
$H_2, H_3$ and every $H_n$ with $n \geq 5$ they vanish by the
three-loop Arnold cancellation. Kontsevich's flat
quasi-isomorphism (Costello--Gwilliam factorisation formality)
is the chain-level witness inside $\SCchtop$; passing to the
$(\infty,1)$-lane, the statement is that the Tamarkin zigzag
lifts to an $(\infty,1)$-equivalence of factorisation
$\infty$-categories over $U^{\mathrm{adm}}$.

\paragraph{Critical-level failure.}
At $k = -h^\vee$ the Sugawara construction is undefined; for
affine Kac--Moody the centre jumps from scalars to the
Feigin--Frenkel oper centre
$\mathfrak{z}(\widehat{\fg}) \cong
\operatorname{Fun}\operatorname{Op}_{\fg^L}(D^\times)$.
Topologisation fails: the pair stays at $\SCchtop$ and
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ remains $\Etwo$-chiral.
The critical level is the boundary of Stage~9.

\paragraph{Three regimes of physical realisation.}
\[
\renewcommand{\arraystretch}{1.3}
\begin{array}{l|l|l|l}
\text{Theory} & \text{Colours} & \cA^!_{\mathrm{line}} &
 \SCchtop \text{ structure} \\
\hline
\text{Abelian CS } (\cH_k) &
 \text{coincide } (\Abulk = \Bbound) &
 Y(\mathfrak{u}(1)) & \text{trivial} \\
\text{Non-ab.~CS } (\widehat{\fg}_k) &
 \text{distinct} & \Ydg(\fg) &
 \text{full BBL triangle} \\
\text{3d gravity } (\mathrm{Vir}_c) &
 \text{distinct} & \text{grav.~line operators} &
 \text{infinite-depth shadow tower}
\end{array}
\]
For Virasoro the completion entropy $h_K \approx 0.567$ measures
bulk reconstruction complexity; the infinite tower of $m_k$
corrections organises gravitational quantum corrections.

\section*{VI.\quad The slab, the Drinfeld double, the BBL triangle}

The $\SCchtop$ geometry has a concrete realisation as a slab
$\C \times [0,1]$ with transverse boundary conditions: a
\emph{bimodule} with two boundary components, not a Swiss-cheese
disk. The boundary algebra $\cA$ sits on one face;
$\cA^!_{\mathrm{line}}$ on the other. The universal algebra of
the slab fiber functor is the Drinfeld double
$\mathbf{U}_\cA = \cA \bowtie \cA^!_{\mathrm{line}}$. Volume~I
complementarity (Theorem~C) is the algebraic manifestation of
transversality across the slab.

\paragraph{The bulk-boundary-line triangle.}
A holomorphic-topological theory on $\C \times \R_{\ge 0}$
produces three algebraic objects: \emph{bulk} local operators
$\Abulk$ (interior), \emph{boundary} local operators $\Bbound$
(on $\{0\} \times \C$), and \emph{line} operators
$\cC_{\mathrm{line}}$ (along $\R_+ \times \{0\}$). The bulk is
the derived chiral centre:
$\Abulk \simeq \Zder(\Bbound)$
(Theorem~\ref{thm:boundary-linear-bulk-boundary},
boundary-linear exact sector). The line category is modeled by
$\cA^!_{\mathrm{line}}$-modules on the Koszul locus
(Theorem~\ref{thm:lines_as_modules}). Two parallel lines
$L_1(z_1), L_2(z_2)$ interact through the bulk producing
meromorphic braiding $R_{L_1, L_2}(z)$ in $z = z_1 - z_2$,
satisfying YBE from Stokes on $\FM_3(\C)$. Heisenberg:
$R(z) = e^{k\hbar/z}$ scalar. Affine Kac--Moody on evaluation
modules: spectral braiding reproduces the quantum group
$R$-matrix of $U_\hbar(\fg)$.

\paragraph{Drinfeld double programme.}
Four questions control the deepest open programme:
\[
\renewcommand{\arraystretch}{1.3}
\begin{array}{l|l|l}
 & \text{Content} & \text{Status} \\
\hline
\text{(a) Hopf structure} &
 \text{construct } \mathbf{U}_\cA \text{ at } E_1\text{-chiral level} &
 \text{open} \\
\text{(b) Antipode} &
 \text{identify with geometric orientation reversal} &
 \text{open} \\
\text{(c) Centre=bulk} &
 Z(\mathbf{U}_\cA) = \cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA) &
 \text{bdry-linear proved, rest open} \\
 & \ \text{(Conj.~\ref{V1-conj:v1-drinfeld-center-equals-bulk}, Vol.~I)} & \\
\text{(d) Hemisphere pairing} &
 \text{identify with cyclic pairing on bar complex} &
 \text{open}
\end{array}
\]
For Heisenberg the heuristic base case of
Computation~\ref{comp:drinfeld-center-heisenberg} lands in the
expected finite Theorem~H window; the Tamarkin/Theorem~H
compatibility gap remains open.

\paragraph{$K$-matrix modification.}
When the theory has no boundary conditions, one passes through
an interface to a free theory $F$; the fiber functor lands in
$\cC_F$ rather than $\Vect$, and one works with
$B^{\mathrm{ord}}(\cA)$ relative to $B^{\mathrm{ord}}(\mathrm{Heis})$.
The $K$-matrix
$K_A(z) = z^{\alpha_0} \exp(\sum \alpha_n/({-}n)\, z^{-n})$
modifies the coproduct: class~$\mathbf{G}$ has $K = 1$;
$\mathbf{L}/\mathbf{C}/\mathbf{M}$ have $K \neq 1$.

\section*{VII.\quad The 3d Maurer--Cartan element}

Volume~I has one MC element $\Theta_\cA$ in $\gAmod$. This
volume has one MC element
$\alpha_T \in \mc(\gSC_T)$ in the Swiss-cheese convolution
algebra
\[
\gSC_T
\;:=\;
\Hom_\Sigma\!\bigl(
 \mathbf{B}(\SCchtop),\;
 \End_{(\Bbound,\,\cC_{\mathrm{line}})}
\bigr).
\]
Existence follows from homotopy-Koszulity. Six direct faces
read off $\alpha_T$:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lll}
\textbf{Projection} & \textbf{Structure} & \textbf{Section} \\
\hline
closed face
 & boundary $\Ainf$ algebra $\Bbound$
 & \S\ref{sec:axioms-Ainfty-chiral} \\[2pt]
open face
 & open-colour operations on $\cC_{\mathrm{line}}$
 & \S\ref{sec:line_operators} \\[2pt]
ordered $(2,0)$ collision
 & spectral $R$-matrix, YBE
 & \S\ref{sec:spectral_braiding} \\[2pt]
mixed $(1,1)$
 & bulk-to-boundary comparison
 & \S\ref{sec:ht-bulk-boundary-line} \\[2pt]
closed genus tower
 & $\Theta_\cA$ from Vol~I
 & \S\ref{subsec:rosetta-3d-mc} \\[2pt]
closed cohomology
 & PVA $\{-_\lambda -\}$
 & \S\ref{sec:PVA_descent}
\end{tabular}
\end{center}
Colour decomposition
$\alpha_T = \alpha_T^{\mathrm{cl}} + \alpha_T^{\mathrm{mix}}
+ \alpha_T^{\mathrm{op}}$ splits the MC equation
$d\alpha_T + \tfrac{1}{2}[\alpha_T, \alpha_T] = 0$ into three
coupled equations:
\begin{itemize}[nosep]
\item \emph{Pure closed}:
 $d\alpha_T^{\mathrm{cl}}
 + \tfrac{1}{2}[\alpha_T^{\mathrm{cl}}, \alpha_T^{\mathrm{cl}}] = 0$
 (the Vol~I MC equation for $\Theta_\cA$).
\item \emph{Mixed}:
 $d\alpha_T^{\mathrm{mix}}
 + [\alpha_T^{\mathrm{cl}}, \alpha_T^{\mathrm{mix}}] = 0$
 ($r$-matrix and PVA bracket are $\Theta_\cA$-twisted cocycles).
\item \emph{Pure open}:
 $d\alpha_T^{\mathrm{op}}
 + [\alpha_T^{\mathrm{cl}}, \alpha_T^{\mathrm{op}}]
 + \tfrac{1}{2}[\alpha_T^{\mathrm{mix}}, \alpha_T^{\mathrm{mix}}]_{\mathrm{op}} = 0$
 (line category closes, mixed-sector self-interaction forcing
 open-sector obstruction).
\end{itemize}
The hierarchy is forced: closed controls mixed controls open.

\paragraph{Genus-$1$ specialisation.}
At genus~$1$ the bar complex lives over $\overline{\cM}_{1,1}$
with modular parameter $\tau$. The curvature
$d_{\mathrm{fib}}^2 = \kappa_{\mathrm{ch}}(\cA)\cdot\omega_1$
($\omega_1 = c_1(\lambda)$, first Chern class of the Hodge
bundle) enters the MC equation through the closed sector:
\[
D\alpha_T^{\mathrm{cl},(1)}
\;+\;
\tfrac{1}{2}[\alpha_T^{\mathrm{cl},(0)},\,
\alpha_T^{\mathrm{cl},(0)}]^{(1)}
\;=\;
\kappa_{\mathrm{ch}}(\cA) \cdot \omega_1.
\]
This is the holographic reading of Theorem~D: the one-loop
anomaly of the 3d theory is $\kappa_{\mathrm{ch}}(\cA)$. The
mixed equation at genus~$1$ is the twisted cocycle condition on
$E_\tau$. For Kac--Moody, the genus-$1$ mixed data is the KZB
connection: $r(z,\tau)$ replacing the rational
$r(z) = k\,\Omega/z$.

\paragraph{Genus expansion of $\alpha_T$.}
$\alpha_T = \sum_{g \ge 0} \hbar^g \alpha_T^{(g)}$. At genus~$0$:
$\alpha_T^{(0)}$ is the tree-level data. At genus~$1$:
$\alpha_T^{(1)}$ encodes the one-loop correction. At genus~$g$:
$D\alpha_T^{(g)} + \sum_{g_1 + g_2 = g}
\tfrac{1}{2}[\alpha_T^{(g_1)}, \alpha_T^{(g_2)}] = 0$.
The recursion terminates for class~$\mathbf{G}$ and runs to
infinite depth for class~$\mathbf{M}$. The modular bar
differential $D = \sum_g \hbar^g D^{(g)}$ is the Feynman
transform of the modular operad
(Theorem~\ref{thm:formal-genus-expansion}).

\smallskip\emph{Heisenberg} $\cH_k$:
$\alpha_{\cH_k} = m_2 + \hbar\,k\cdot\eta\otimes\Lambda$, all
six projections collapsing to the single scalar $k$. Mixed
trivial; open empty; genus expansion terminates at genus~$1$
(class~$\mathbf{G}$, abelian CS).

\smallskip\emph{Kac--Moody} $\widehat{\fg}_k$:
mixed component encodes $r(z) = k\,\Omega/z$ as a
$\Theta_{\widehat{\fg}_k}$-twisted cocycle; KZ connection
$\nabla_{\mathrm{KZ}} = d - \Omega\,dz/((k+h^\vee)z)$ on
conformal blocks; open closes via RTT,
$U_q(\fg)$ at $q = e^{i\pi/(k+h^\vee)}$. At genus~$1$,
KZB connection $\nabla_{\mathrm{KZB}} = d - \Omega\,\wp_1(z,\tau)\,dz$
on $E_\tau$ with heat equation
$\partial_\tau \nabla_{\mathrm{KZB}} =
(1/(4\pi i))\,\partial_z^2\,\nabla_{\mathrm{KZB}}$; the prefactor
is $1/(4\pi i)$ on the diagonal and $1/(2\pi i)$ off the diagonal.
Class~$\mathbf{L}$, non-abelian CS.

\smallskip\emph{Virasoro} $\mathrm{Vir}_c$:
mixed component is the graviton propagator; twisted cocycle
condition is the Ward identity for gravitational scattering.
Open does not close at finite order: infinite depth requires
the full $\Ainf$ tower. Genus expansion non-zero for all $g$;
shadow obstruction $S_r$ controls degree-$r$. Class~$\mathbf{M}$,
gravity.

\section*{VIII.\quad PVA descent}

The bar differential $D_\cA$ is a coderivation of
$T^c(s^{-1}\bar\cA)$ determined by cogenerators
$m_k\colon A^{\otimes k} \to A((\lambda_1))\cdots((\lambda_{k-1}))$
of degree $2 - k$. The identity $D_\cA^2 = 0$ expands into the
Stasheff relations, each a Stokes theorem on $\FM_n(\C)$. At
$n = 1$: $m_1^2 = 0$. At $n = 2$: Leibniz. At $n = 3$:
$K_3 = [0,1]$ with endpoints $D_{12}, D_{23}$; failure of $m_2$
to associate corrected by $m_3$. At $n = 4$: pentagon $K_4$, five
faces, $m_4$ as interior integral. For $\cW_3$, $m_4$ has
coefficient $32/(22+5c)$. In general $\FM_n(\C)/\mathrm{Aff}(\C)$
is a manifold with corners of real dimension $2n - 4$;
$\partial^2 = 0$ on $\FM_n(\C)$ makes $D_\cA^2 = 0$ hold.

\paragraph{Resolvent principle.}
$\{m_k\}_{k\ge 2}$ are determined by $m_2$ alone. Let
$(H, p, \iota, h)$ be a deformation retract of $(\cA, m_1)$ onto
cohomology. The dressed propagator
$\Phi = \iota + h \circ m_2 \circ \Phi^{\otimes 2}$ satisfies
the tree-level bootstrap, with solution
\[
m_k^H \;=\; \sum_{T \in \mathrm{PRT}_k}
p \circ \mathfrak{m}(T) \circ \iota^{\otimes k},
\]
where $\mathrm{PRT}_k$ is the set of planar rooted binary trees
with $k$ leaves (equivalently, $k - 1$ internal vertices;
$|\mathrm{PRT}_k| = C_{k-1}$, the Catalan number),
$\mathfrak{m}(T)$ assigns $m_2$ to each internal vertex and $h$
to each internal edge.

\paragraph{Descent to PVA.}
On cohomology $H^\bullet(A, Q)$, higher $m_k$ vanish and $m_2$
decomposes into commutative product $\mu$ (regular part) and
$\lambda$-bracket (singular part), forming a $(-1)$-shifted PVA
(Theorem~\ref{thm:cohomology_PVA}). Five PVA axioms have
geometric origins:
\[
\renewcommand{\arraystretch}{1.3}
\begin{array}{l|l}
\text{PVA axiom} & \text{Geometric origin} \\
\hline
\text{Sesquilinearity} & \C^*\text{-equivariance on } \FM_2(\C) \\
\text{Skew-symmetry} & \text{exchange } z_1 \leftrightarrow z_2 \\
\text{Jacobi} & \text{Stokes on } \FM_3(\C) \\
\text{Leibniz} & \text{three-face Stokes on } \partial\FM_3(\C) \\
\text{Commutativity}\,(\mu) & \Z/2\text{-involution on } \FM_2(\C)
\end{array}
\]
Quantisation obstruction lives in $\HH^3_{\mathrm{ch}}(V)$;
Quillen equivalence (Theorem~\ref{thm:homotopy-Koszul}) gives
essential uniqueness.

\section*{IX.\quad Three computations}

\paragraph{Heisenberg} (class~$\mathbf{G}$, formal).
Generator $J$, OPE $J(z)J(w) \sim k/(z-w)^2$;
$\{J_\lambda J\} = k\lambda$, $m_2(J,J;\lambda) = k\lambda$, all
$m_{k\ge 3} = 0$. Bar differential
$D[s^{-1}J | s^{-1}J] = J_{(1)}J = k$. PVA on cohomology:
$(\C[J], \{J_\lambda J\} = k\lambda)$. Classical $r$-matrix:
the OPE has a double pole; the $d\log$ kernel absorbs one
(pole$_r$ = pole$_{\mathrm{OPE}} - 1$):
\[
r_{\cH_k}(z) \;=\; \frac{k}{z},
\qquad\text{vanishing at the abelian limit $k = 0$.}
\]
Quantum: $R(z) = \exp(k\hbar/z)$; YBE trivial.
Chiral Koszul dual:
$\cA^!_{\mathrm{ch}} = \mathrm{Sym}^{\mathrm{ch}}(V^*)$
(note $\cH_k^! \neq \cH_{-k}$: the Koszul dual and the sign-flipped
level share the same $\kappa_{\mathrm{ch}}$ but are distinct
algebras). Line dual:
$\cA^!_{\mathrm{line}} = Y(\mathfrak{u}(1))$, Fock modules
$\cF_\mu$ with braiding
$R_{\mu_1,\mu_2}(z) = \exp(k\mu_1\mu_2\hbar/z)$.
Bulk $\Abulk \simeq \Zder(\cH_k) = \cH_k$: derived centre adds
nothing; BBL triangle collapses.
At genus~$1$: $\kappa_{\mathrm{ch}}(\cH_k) = k$,
$F_1 = -k\log\eta(\tau)$ (so $Z_1 = \eta(\tau)^{-k}$, integrated
free energy $\kappa_{\mathrm{ch}}/24 = k/24$). Scalar tower
\textup{(\textsc{uniform-weight})}:
$F_g(\cH_k) = k\cdot\lambda_g^{\mathrm{FP}}$;
$F_2(\cH_k) = 7k/5760$ (linear in $k$).

\paragraph{Kac--Moody} (class~$\mathbf{L}$, Lie-transverse).
Generators $J^a$, OPE
$J^a(z)J^b(w) \sim f^{ab}{}_c J^c/(z-w) + k\,\delta^{ab}/(z-w)^2$.
$\lambda$-bracket
$m_2(J^a, J^b;\lambda) = f^{ab}{}_c J^c + k\,\delta^{ab}\lambda$.
$m_3 \neq 0$ from the Jacobiator on $K_3$; higher
$m_{k \ge 4} = 0$ by dimension counting on $\FM_k(\C)$.
Classical $r$-matrix in the trace-form convention:
$r_{\widehat{\fg}_k}(z) = k\,\Omega/z$, vanishing at $k = 0$;
KZ equivalent $r(z) = \Omega/((k+h^\vee)z)$ diverges at
$k = -h^\vee$. Bridge identity $k\,\Omega_{\mathrm{tr}} =
\Omega/(k+h^\vee)$ at generic $k$. The KZ connection
$\nabla_{\mathrm{KZ}} = d - \Omega\,dz/((k+h^\vee)z)$
is a rational one-form (not $d\log$). On evaluation modules,
spectral $R$-matrix reproduces $U_q(\fg)$ at
$q = e^{i\pi/(k+h^\vee)}$
(Theorem~\ref{thm:affine-monodromy-identification});
reduced line category
$\cC_{\mathrm{line}}^{\mathrm{red}}|_{\mathrm{eval}} \simeq
\operatorname{Rep}_q(\fg)$.
Line dual $\cA^!_{\mathrm{line}} = \Ydg(\fg)$ (dg-shifted
Yangian); spectral Drinfeld strictification
(Theorem~\ref{thm:complete-strictification}) is proved in
simply-laced type~$A$ (abelian $\widehat{\fh}$ and $\widehat{\fsl}_2$
concretely; $\widehat{\fsl}_N$ via the $\mathfrak{gl}_N$ chiral quantum-group
construction), with Dynkin coefficient $1/n$ rigidity controlling the
associator-normalisation step. Types $D$, $E$ and non-simply-laced
$B$, $C$, $G_2$, $F_4$ remain conjectural pending per-type
verification of Frenkel--Mukhin $q$-character uniformity
(Hernandez 2006; Nakajima 2001).
At genus~$1$: $\kappa_{\mathrm{ch}}(\widehat{\fg}_k) =
\dim\fg\,(k+h^\vee)/(2h^\vee)$; at $k = 0$,
$\kappa_{\mathrm{ch}} = \dim\fg/2$ (Sugawara shift; not zero).
Feigin--Frenkel:
$\kappa_{\mathrm{ch}}(\widehat{\fg}_k) +
\kappa_{\mathrm{ch}}(\widehat{\fg}_{-k-2h^\vee}) = 0$ (Koszul
conductor $K = 0$). At $k = -h^\vee$: monodromy trivial, centre
jumps, Koszulness fails.

\paragraph{$\cW_3$} (class~$\mathbf{M}$, infinite tower).
Two generators $T$ (weight~$2$) and $W$ (weight~$3$); for
$\cW_N$, generators at weights $\{2, \dots, N\}$, not
$\{2, \dots, N+1\}$. $TT$ $\lambda$-bracket in divided-power
notation $\lambda^{(n)} = \lambda^n/n!$:
\[
m_2(T,T;\lambda) \;=\; \frac{c}{12}\lambda^3 + 2T\lambda + \partial T,
\]
the coefficient $c/12$ being $T_{(3)}T/3! = (c/2)/6$; the shadow
invariant is $S_2 = \kappa_{\mathrm{ch}} = c/2$, not $c/12$ (the
divided-power coefficient is convention-dependent, while the
shadow invariant is not).
$WW$ $\lambda$-bracket involves
$\Lambda = {}\!:(TT): - \tfrac{3}{10}\,\partial^2 T$ of weight~$4$:
\[
m_2(W,W;\lambda)
\;=\;
\frac{c}{360}\lambda^5
+ \frac{1}{3}T\lambda^3
+ \frac{1}{2}(\partial T)\lambda^2
+ \Bigl(\frac{3}{10}\partial^2 T
 + \frac{32}{22+5c}\,\Lambda\Bigr)\lambda
+ \frac{1}{15}\partial^3 T
+ \frac{16}{22+5c}\,\partial\Lambda.
\]
The denominator $5c + 22$ records the minimal-model accumulation
point $c = -22/5$, the same threshold as the Virasoro quartic
contact $10/[c(5c + 22)]$.
$\Ainf$ tower does not terminate; Koszul dual coalgebra requires
new cogenerator $\Lambda^*$ with non-primitive coproduct;
completed dual is the cumulant coalgebra
$\operatorname{Cum}_c(\cW_3)$ with primitive generating series
$G_{\cW_3}(t) = (t + t^2 + t^3)/(1 - t)$ and completion entropy
$h_K(\cW_3) \approx 0.772$.
Modular characteristic
$\kappa_{\mathrm{ch}}(\cW_3) = c\cdot(H_3 - 1) = 5c/6$
(harmonic number $H_3 = 11/6$); $\kappa_{\mathrm{ch}}(\cW_2) =
c\cdot(H_2 - 1) = c/2$ recovers Virasoro at $N = 2$.
Fateev--Lukyanov duality gives the central-charge sum
$c(\cW_3) + c(\cW_3^!) = 100$, so the
$\kappa_{\mathrm{ch}}$-conductor
$\kappa_{\mathrm{ch}}(\cW_3) + \kappa_{\mathrm{ch}}(\cW_3^!)
= (5/6)\cdot 100 = 250/3$
is nonzero (nontrivial $\cW_N$ complementarity for $N \ge 3$,
in contrast to affine $\widehat{\fg}_k$ where the
$\kappa_{\mathrm{ch}}$-conductor vanishes), and sits in the
Vol~I five-archetype bucket $\{0, 8, 13, 250/3, 98/3\}$
as the $\cW_3$ sub-landmark on class~$\mathbf{M}$.

\paragraph{Multi-weight cross-channel correction.}
At $g \ge 2$, multi-weight algebras activate
$\delta F_g^{\mathrm{cross}}$ \textup{(\textsc{multi-weight})},
absent for single-weight (\textsc{uniform-weight}) algebras.
$T$-channel and $W$-channel propagators carry weights $2$ and
$3$; mixed-propagator graphs grow factorially (Gevrey-$1$) with
instanton action $A_{\mathrm{cross}} > (2\pi)^2$. The ratio
$|\delta F_g^{\mathrm{cross}}|/|F_g^{\mathrm{scalar}}|$ grows
without bound: at high genus the cross-channel dominates, and
the scalar shadow becomes an exponentially lossy compression of
the full $E_1$ data; the quantitative vindication of $E_1$
primacy. Virasoro is degenerate (single weight,
$\delta F_g^{\mathrm{cross}} = 0$);
$\cW_2 \to \cW_3$ is the passage from pure gravity to higher-spin
gravity. Explicit value: $\delta F_2^{\mathrm{cross}}(\cW_3) =
(c+204)/(16c)$
(Proposition~\ref{prop:delta-f-cross-w3-g2}).

\paragraph{Gravitational reading of $\cW_3$.}
$\cW_3$ is the boundary of higher-spin gravity: the 3d theory is
$SL(3,\R) \times SL(3,\R)$ Chern--Simons reduced by principal
Drinfeld--Sokolov. The shadow tower gives the gravitational
perturbation series with two propagator channels.

\section*{X.\quad Curved genus expansion}

At genus $1$ the bar differential is curved:
$d_{\mathrm{fib}}^2 = \kappa_{\mathrm{ch}}(\Bbound) \cdot \omega_1$.
The chain-level continuation
$d_{\mathrm{fib}}^2 = \kappa_{\mathrm{ch}}(\Bbound) \cdot \omega_g$
holds for all $g \ge 2$ via curved-Dunn $H^2 = 0$
(Theorem~\ref{thm:curved-dunn-H2-vanishing-all-genera}), with
multi-weight cross-channel correction
$\delta F_g^{\mathrm{cross}}$ in the multi-weight regime. In
the boundary-bulk interpretation $\kappa_{\mathrm{ch}}(\cA)$ is
the holographic central charge: Heisenberg
$\kappa_{\mathrm{ch}}(\cH_k) = k$ (abelian CS level); Virasoro
$\kappa_{\mathrm{ch}}(\mathrm{Vir}_c) = c/2$. The shadow tower
$\{S_r(\cA)\}_{r \ge 2}$ is the holographic correction
hierarchy.

The modular bar differential $D = \sum_{g \ge 0} \hbar^g D^{(g)}$
is the Feynman transform of the modular operad
(Theorem~\ref{thm:formal-genus-expansion}). The scalar tower
\textup{(\textsc{uniform-weight})} is controlled by the
$\hat{A}$-genus:
\[
\sum_{g \ge 1} F_g(\cA) \cdot \hbar^{2g}
\;=\;
\kappa_{\mathrm{ch}}(\cA)\cdot\bigl(\hat{A}(i\hbar) - 1\bigr),
\]
with $F_1 = \kappa_{\mathrm{ch}}/24$ (Weinberg soft graviton at
tree level), $F_2 = 7\kappa_{\mathrm{ch}}/5760$ (one-loop soft
factor, linear in $\kappa_{\mathrm{ch}}$), and higher $F_g$
determined by Bernoulli numbers.
The generating function is algebraic of degree~$2$: the quadratic
$Q_L(t)$ from Volume~I satisfies $H(t)^2 = t^4\,Q_L(t)$, and
$\Delta = 8\kappa_{\mathrm{ch}} S_4$ classifies nonlinear
complexity. The scalar tower converges (Gevrey-$0$, radius
$2\pi$, Borel entire).

The Borel singularity of the gravitational tower at
$g \sim 1/\kappa_{\mathrm{ch}}$ produces a Stokes phenomenon: the
Page curve. The Page time
$t_P = 3 S_{\mathrm{BH}}/13$
(Proposition~\ref{prop:gravity-page-curve}) is $c$-independent
because $\kappa_{\mathrm{ch}}(\mathrm{Vir}_c) +
\kappa_{\mathrm{ch}}(\mathrm{Vir}_{26-c}) = 13$, the
Virasoro-specific Koszul complementarity established in
Volume~I (the sum is family-specific, not universal).
Heuristically, Borel resummation in the $\kappa_{\mathrm{ch}} < 0$
sector with Stokes jump at the Gibbons--Hawking saddle recovers
the de~Sitter entropy
$S_{\mathrm{dS}} = \pi\ell^2/G$.

\paragraph{Transgression algebra.}
$B_\Theta$ absorbs the curvature by adjoining a degree-one
generator $\eta$ with $d\eta = \Theta$, keeping
$\eta^2 \neq 0$:
\[
B_\Theta
\;=\;
\frac{B * \Bbbk\langle\eta\rangle}
{\langle \eta b - (-1)^{|b|} b\eta \rangle},
\qquad d\eta = \Theta.
\]
A $B_\Theta$-module is a $B$-module with neutralisation
$h_M$ satisfying $dh_M = \Theta_M$. Secondary anomaly
$u := \eta^2$ controls the genus-$g$ Clifford completion
$\mathfrak{G}_g(B_\Theta)$: away from $u = 0$,
$\mathfrak{G}_g[\eta^{-2}] \cong
\operatorname{Mat}_{2^g}(B_\Theta[\eta^{-2}])$
(higher genus is Morita-invisible); on $u = 0$,
$\mathfrak{G}_g/(\eta^2) \cong B/(\Theta) \otimes \Lambda^{2g+1}$.

\section*{XI.\quad The eight parts}

The eight parts execute the passage from boundary VOA to bulk
gravitational theory.
Parts~\ref{part:swiss-cheese}--\ref{part:holography} assemble
the algebraic-geometric apparatus;
Part~\ref{part:gravity} is the climax;
Part~\ref{part:frontier} locates the frontier; and
Part~VIII (\emph{From Frontier to Theorem}) promotes four
closed frontiers to theorems: curved-Dunn $H^2 = 0$ at all
genera (Theorem~\ref{thm:curved-dunn-H2-vanishing-all-genera};
unconditional at $g \in \{1,2\}$; at $g \ge 3$ for multi-generator
families this requires the scalar-diagonal hypothesis
(Definition~\ref{V1-def:scalar-diagonal-hypothesis}) plus Faber's
$\lambda_g$-conjecture for the on-the-nose lift from the socle;
the genus-three scalar residue
$\lambda_3^{\mathrm{FP}}=31/967680$ is computed in
Proposition~\ref{prop:f6-genus-three-lambda-residue}, while
Proposition~\ref{prop:f6-scalar-projection-no-multichannel-lift}
shows that this scalar does not determine the multichannel socle
lift),
DS--Hochschild compatibility for class~$\mathbf{M}$
(Theorem~\ref{thm:chd-ds-hochschild}), periodic-CDG at
admissible level
(Theorem~\ref{V1-thm:periodic-cdg-is-koszul-compatible}), and
chain-level chiral Deligne--Tamarkin after associator fix
(Theorem~\ref{thm:chd-deligne-tamarkin}).

\paragraph{The Open Primitive (Part~\ref{part:swiss-cheese}).}
The open/closed factorisation dg-category $\cC$ is the primitive
datum: objects are boundary conditions, morphisms are open-string
states. A choice of vacuum boundary condition $b$ produces
$A_b = \operatorname{End}_\cC(b)$ as a chart. The Morita class
of $\cC$, not the quasi-isomorphism class of $A_b$, is the
invariant. Three constructions are independent: the bar complex
$\barBch(A_b)$ classifies twisting morphisms; the chiral derived
centre $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cC)$ is the universal
bulk; the line-side Koszul dual
$A^!_{\mathrm{line}} = \mathbb{D}_{\Ran}(\barBch(A_b))$ models
line operators on the Koszul locus. The part constructs
$\SCchtop$ with its seven presentations, proves
homotopy-Koszulity
(Theorem~\ref{thm:homotopy-Koszul}), and identifies the Koszul
dual cooperad.

\paragraph{The $E_1$ Core (Part~\ref{part:e1-core}).}
The ordered bar complex is the $E_1$ coalgebra; its six
projections (Section~VII) produce the boundary $\Ainf$ algebra,
the line-sector operations, the spectral $R$-matrix, the
bulk-to-boundary comparison, the genus tower, and the PVA. The
3d MC element $\alpha_T \in \mc(\gSC_T)$ packages the output.
The dg-shifted factorisation bridge lands inside Yangians; the
complete spectral Drinfeld strictification
(Theorem~\ref{thm:complete-strictification}) holds for every
simple Lie type, controlled by the Dynkin coefficient $1/n$.
The Heisenberg Rosetta Stone (\S\ref{sec:rosetta-stone})
verifies all six projections by hand. Unified chiral quantum
group $Q_g^{k,f,\mu}$ (Yangian + W + RTT + coideal as a single
$E_1$-core synthesis) and super chiral Yangian extend the theory.

\paragraph{The Faces of $r(z)$, a $\mathrm{GRT}_1(\Q)$-Torsor
(Part~\ref{part:bbl-core}).}
The collision residue
$r(z) = \Res^{\mathrm{coll}}_{0,2}(\Theta_\cA)$ is one
mathematical object read in seven (plus two motivic)
presentations:
\[
\renewcommand{\arraystretch}{1.3}
\begin{array}{l|l|l}
\text{Face} & \text{Name} & \text{Content} \\
\hline
\text{F1} & \text{Spectral braiding/YBE} &
 \text{Stokes on } \FM_3(\C)\ (\text{Thm~\ref{thm:YBE}}) \\
\text{F2} & \text{DNP identification} &
 r\text{-matrix} = \text{line-operator braiding} \\
\text{F3} & \text{Bulk-boundary-line slab} &
 \Abulk \simeq \Zder(\Bbound)\ (\text{bdry-linear sector}) \\
\text{F4} & \text{Celestial transfer} &
 \text{soft factors: } r(z) \sim S_0/z + S_1/z^2 + \cdots \\
\text{F5} & \text{Affine half-space BV} &
 \text{BV}(\R_+ \times \C) \simeq \barBch(\widehat{\fg}_k) \\
\text{F6} & \text{Planted-forest synthesis} &
 \text{on } \FM_3(X) \\
\text{F7} & \text{Kontsevich integral} & - \\
\hline
\text{F8} & \text{Brown motivic} &
 \text{odd-weight MZV coefficients generate } \mathfrak{grt}_1 \\
\text{F9} & \text{Willwacher operadic} &
 H^0(\mathrm{GC}_2) = \mathfrak{grt}_1;
 \text{ Tamarkin zigzag}
\end{array}
\]
Each face is a different projection of the same degree-$2$
component of $\alpha_T$. The set $\operatorname{Face}(\cA)$ of
chain-level presentations of $r(z)$ is a torsor over
$\mathrm{GRT}_1(\Q)$: F1--F9 are nine canonical $\Q$-rational
orbit representatives. F1 is the bar hub (identity coset);
F2--F7 are the six physical spokes; F8--F9 are the motivic and
operadic spokes.

\paragraph{The Characteristic Datum and Modularity
(Part~\ref{part:examples}).}
Holographic measurements:
$\kappa_{\mathrm{ch}}(\cH_k) = k$,
$\kappa_{\mathrm{ch}}(\widehat{\fg}_k) = \dim\fg(k+h^\vee)/(2h^\vee)$,
$\kappa_{\mathrm{ch}}(\mathrm{Vir}_c) = c/2$,
$\kappa_{\mathrm{ch}}(\cW_N) = c\cdot(H_N - 1)$;
the shadow tower as correction hierarchy; Theorem~H (chiral
Hochschild concentrated in $\{0,1,2\}$ on the Koszul locus, with
family-dependent Hilbert polynomial); brace operations encoding
$\SCchtop$ datum on the derived centre pair; relative Feynman
transform; modular PVA quantisation
(Theorem~\ref{thm:modular-bar}: stable-graph modular bar
coalgebra with filtered deformation dg Lie algebra whose MC
elements lift the genus-$0$ PVA to all genera). Curved Dunn
$H^2 = 0$ at all $g$
(Theorem~\ref{thm:curved-dunn-H2-vanishing-all-genera}); $\beta_N$
closed form $12(H_N - 1)$
(Theorem~\ref{thm:beta-N-closed-form-proved-all-N}); modular PVA
quantisation; tempered stratum (three chapters).

\paragraph{The Standard HT Landscape
(Part~\ref{part:holography}).}
Reconstruction across the standard landscape: Yang--Mills
boundary theory with instanton-completed visible centre and
screening Laplacian; celestial holography (KK reduction
$6$d $\to$ $3$d producing celestial chiral algebras, disk-level
OPE data); logarithmic HT monodromy
(Theorem~\ref{thm:synthesis}, shifted KZ connection extending to
$\Ainf$ superconnection); anomaly-completed topological
holography (transgression algebra $B_\Theta$ with secondary
anomaly $u = \eta^2$); holographic reconstruction
(Theorem~\ref{thm:holographic-reconstruction}: formal Darboux
reconstructs the $(-2)$-shifted symplectic ambient); modular
bootstrap.

\paragraph{Three-Dimensional Quantum Gravity
(Part~\ref{part:gravity}).}
The climax. $SL(2,\R) \times SL(2,\R)$ Chern--Simons at levels
$k_\pm = \ell/(4G)$ is three-dimensional gravity with
$\Lambda = -1/\ell^2$. The HT twist selects one chiral half
with $\Bbound = \mathrm{Vir}_{6k}$ at $c = 6k = 3\ell/(2G)$
(Brown--Henneaux), infinite-depth class~$\mathbf{M}$. Every
preceding part converges here: Part~\ref{part:swiss-cheese}
builds the operad; Part~\ref{part:e1-core} builds the Yangian
line dual; Part~\ref{part:bbl-core} reads the seven faces of
$r(z)$; Part~\ref{part:examples} computes
$\kappa_{\mathrm{ch}}(\mathrm{Vir}_c) = c/2$ and the shadow
tower; Part~\ref{part:holography} tabulates the HT landscape.
Only with all five assembled does the gravitational theory
become computable.

The shadow tower reads as the gravitational perturbation series:
$\kappa_{\mathrm{eff}} = (c - 26)/2$ at one loop; quartic contact
$\mathfrak{Q}^{\mathrm{contact}}_{\mathrm{Vir}} =
10/[c(5c+22)]$ at four-graviton level, whose large-$c$ asymptotic
is $2/c^2$ (not $2/(5c^2)$). BTZ black holes are MC elements
(Definition~\ref{def:btz-deformation}); the two-sided Cardy
formula is conjectural. Virasoro is self-dual at $c = 13$ (a
family-specific value); the critical bosonic string sits at
$c = 26$.
At $c = 13$ the ordered bar complex carries a gravitational
Yangian symmetry whose conserved charges are the shadow
obstructions $S_r$. Heuristically, Borel resummation in the
$\kappa_{\mathrm{ch}} < 0$ sector recovers
$S_{\mathrm{dS}} = \pi\ell^2/G$ as the leading Gibbons--Hawking
Stokes saddle.

The part also contains: chiral higher Deligne
(Chapter~\ref{ch:chiral-higher-deligne}); universal holography
functor and master theorem; universal celestial holography;
Monster $V^\natural$ as a special original-complex chain-level
$E_3$ finite-orbifold descent from the class-G Leech lattice VOA
(Theorem~\ref{thm:monster-chain-level-e3-top}), not as a generic
class~$\mathbf{M}$ upgrade;
Schellekens 71 classification; the iterated-Sugawara $E_\infty$ tower.

\paragraph{The Frontier (Part~\ref{part:frontier}).}
Five named open problems
(Section~XV, frontiers F1--F5). No earlier part depends on it.

\paragraph{From Frontier to Theorem
(Part~\ref{part:frontier-to-theorem}).}
Closed frontiers elevated to theorems: the Koszulness moduli
$\mathcal{M}_{\mathrm{Kosz}}$ and the Infinite Fingerprint
Classification
(Chapter~\ref{chap:infinite-fingerprint}, Theorem~G).

\section*{XII.\quad The holographic programme}

\noindent
The physical content concentrates in one sentence: the derived
chiral centre of a boundary algebra IS the bulk algebra of a 3d
holomorphic-topological gauge theory. The holographic modular
Koszul datum
\[
\mathcal{H}(T)
\;=\;
(\Bbound,\; \cA^!_{\mathrm{line}},\; \cC_{\mathrm{line}},\;
R(z),\; \Theta_{\Bbound},\; \nabla^{\mathrm{hol}})
\]
packages the six faces of the 3d theory: boundary
algebra $\Bbound$ with its genus tower $\Theta_{\Bbound}$
(closed sector); line-side Koszul dual $\cA^!_{\mathrm{line}}$
modelling the line category on the chirally Koszul locus (open
sector); spectral braiding $R(z)$ (mixed sector); holomorphic
connection $\nabla^{\mathrm{hol}}$ (anomaly completion).

\paragraph{Abelian Chern--Simons.}
$G = U(1)$, level $k$: $\Bbound = \cH_k$. Six faces of $\cH(T)$:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{ll}
$\Bbound = \cH_k$ & one generator $J$, OPE $J(z)J(w) \sim k/(z-w)^2$ \\
$\cA^!_{\mathrm{line}} = Y(\mathfrak{u}(1))$ & Fock modules $\cF_\mu$ \\
$\cC_{\mathrm{line}} = \cH_{-k}\text{-mod}$ & semisimple \\
$R(z) = e^{k\hbar/z}$ & scalar, YBE trivial \\
$\Theta_{\cH_k} = k \cdot \eta \otimes \Lambda$ & genus tower terminates \\
$\nabla^{\mathrm{hol}} = d$ & trivial (no anomaly)
\end{tabular}
\end{center}
$\Abulk = \cH_k$: BBL triangle collapses.
$\alpha_T = m_2 + \hbar\,k\cdot\eta\otimes\Lambda$.
$\kappa_{\mathrm{ch}}(\cH_k) = k$; $F_1 = k/24$. Class~$\mathbf{G}$:
3d theory is topological CS with $Z_g(\cH_k) = k^g$.

\paragraph{Non-abelian Chern--Simons.}
$G = SL_2$, level $k$: $\Bbound = \widehat{\mathfrak{sl}}_2{}_k$.
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{ll}
$\Bbound = \widehat{\mathfrak{sl}}_2{}_k$ &
 OPE $J^a(z)J^b(w) \sim f^{ab}{}_c J^c/(z{-}w) + k\delta^{ab}/(z{-}w)^2$ \\
$\cA^!_{\mathrm{line}} = \Ydg(\mathfrak{sl}_2)$ &
 dg-shifted Yangian \\
$\cC_{\mathrm{line}}^{\mathrm{red}}|_{\mathrm{eval}}
 \simeq \operatorname{Rep}_q(\mathfrak{sl}_2)$ &
 $q = e^{i\pi/(k+2)}$ \\
$r(z) = k\,\Omega/z$ & trace-form, vanishing at $k = 0$ \\
$\Theta_{\widehat{\fg}_k}$: depth $3$ & $m_3 \neq 0$, $m_{k \ge 4} = 0$ \\
$\nabla^{\mathrm{hol}} = \nabla_{\mathrm{KZ}}$ &
 $d - \Omega\,dz/((k+h^\vee)z)$
\end{tabular}
\end{center}
CYBE for $r(z) = k\,\Omega/z$ is the Lie-algebra Jacobi identity.
On evaluation modules, spectral $R$-matrix reproduces
$U_q(\mathfrak{sl}_2)$ at $q = e^{i\pi/(k+2)}$
(Theorem~\ref{thm:affine-monodromy-identification}); coloured
Jones polynomial recovered from bar-complex monodromy.
$\kappa_{\mathrm{ch}}(\widehat{\mathfrak{sl}}_2{}_k) = 3(k+2)/4$;
Feigin--Frenkel: $\kappa_{\mathrm{ch}} + \kappa_{\mathrm{ch}}' = 0$
(Koszul conductor $K = 0$). At $k = -2$: critical, Sugawara
undefined, centre jumps, topologisation fails, stuck at
$\SCchtop$. Class~$\mathbf{L}$.

\paragraph{3d gravity.}
$SL(2,\R) \times SL(2,\R)$ CS at $k_\pm = \ell/(4G)$:
$\Bbound = \mathrm{Vir}_c$ at $c = 3\ell/(2G)$. Infinite-depth
class~$\mathbf{M}$; all $m_k \neq 0$; shadow tower:
\[
\kappa_{\mathrm{ch}}(\mathrm{Vir}_c) = \frac{c}{2}, \qquad
\kappa_{\mathrm{eff}} = \frac{c-26}{2}, \qquad
\mathfrak{Q}^{\mathrm{contact}} = \frac{10}{c(5c{+}22)}.
\]
Degree~$2$: one-loop anomaly $\kappa_{\mathrm{eff}} = (c-26)/2$
vanishes at $c = 26$ (bosonic string critical dimension).
Degree~$4$: quartic contact diverges at $c = 0$ and $c = -22/5$.
Tower does not truncate: 3d gravity has infinitely many quantum
corrections, organised by $S_r$, with completion entropy
$h_K(\mathrm{Vir}) \approx 0.567$. Koszul dual
$\mathrm{Vir}_{26-c}$; Virasoro is self-dual at $c = 13$, a
family-specific value. Koszul conductor (Virasoro only)
$\kappa_{\mathrm{ch}} + \kappa_{\mathrm{ch}}' = 13$. Page time
$t_P = 3 S_{\mathrm{BH}}/13$ is $c$-independent.
BTZ black holes are MC elements
(Definition~\ref{def:btz-deformation}); conjectured Cardy
entropy $S_{\mathrm{Cardy}} = 2\pi\sqrt{ch/6} +
2\pi\sqrt{c\bar{h}/6}$ yields Bekenstein--Hawking.

\section*{XIII.\quad The $E_n$ hierarchy as physical realisation}

\noindent
Volume~I constructs $E_n$-chiral algebras as algebraic-geometric
objects on configuration spaces. The physical content of those
objects is the subject of the stages below.

\paragraph{$E_1$: ordered bar complex is the boundary algebra.}
$B^{\mathrm{ord}}(\cA) = T^c(s^{-1}\bar\cA)$ with differential
$D_\cA$ on $\FM_k(\C)$ and coproduct $\Delta$ on $\Conf_k^<(\R)$
encodes the boundary VOA on $\{0\} \times \C$ in a 3d HT theory
on $\R_{\ge 0} \times \C$. Cogenerator projections $m_k$ are the
$\Ainf$-chiral operations; spectral parameters
$\lambda_j = z_j - z_k$ are holomorphic separations. Physical
content: boundary VOA and module category.

\paragraph{$E_2$: derived centre is the bulk algebra.}
$C^\bullet_{\mathrm{ch}}(\cA,\cA)$, computed from
$B^{\mathrm{ord}}(\cA)$ as
$\Hom(\barBch(\cA), \cA)$, carries $E_2$ structure from the
chiral Deligne conjecture. The $E_2$ is holomorphic and braided:
$R$-matrix is the coherence datum, YBE from Stokes on
$\FM_3(\C)$. Physically: the $E_2$-algebra
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ IS the algebra of bulk
local operators; the $E_2$ braiding IS line-operator exchange
through the bulk; the $\SCchtop$ pair
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),\,\cA)$ IS the
boundary-bulk system, with directionality enforcing that
boundary determines bulk.

For Heisenberg: $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cH_k) = \cH_k$.
For Kac--Moody:
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\widehat{\fg}_k)$ has nontrivial
$E_2$, braiding reproduces $U_q(\fg)$ on evaluation modules. For
Virasoro: $E_2$ structure organises infinite gravitational
quantum corrections.

\paragraph{$\SCchtop$: the intermediary.}
Most chiral algebras have $\SCchtop$ as the final answer; the
pair carries the full $\SCchtop$ datum but does not reach $E_3$.
The passage requires conformal vector at non-critical level:
Sugawara $T(z) = \{Q,G(z)\}$ makes $\C$-translations $Q$-exact,
the complex structure on $\C$ becomes irrelevant in cohomology,
and the two colours collapse. Without conformal vector: stuck
at $\SCchtop$.

\paragraph{$E_3^{\mathrm{top}}$: topologisation is physics.}
$E_3$-topological structure on
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ arises from Dunn
additivity: $E_2^{\mathrm{top}} \times E_1^{\mathrm{top}} =
E_3^{\mathrm{top}}$. Physically: $E_3^{\mathrm{top}}$ IS 3d
Chern--Simons. For $G = SL_2$ at level $k$:
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\widehat{\mathfrak{sl}}_2{}_k)$
is observables of holomorphic Chern--Simons (Costello--Li). For
$W$-algebras via Drinfeld--Sokolov: $E_3$ via
$T_{\mathrm{DS}} = [Q_{\mathrm{CS}}, G'_f]$, where the improvement
$G'_f$ is a Cartan-current $Q_{\mathrm{CS}}$-exact in the 3d bulk
regardless of the nilpotent orbit
(Theorem~\ref{thm:E3-topological-DS-general}). For finite-type
freely generated finite-jet PVAs with inner holomorphic translation,
the Khan--Zeng 3d Poisson sigma model gives the classical BV action;
the all-loop half-space quantization and $E_3$ topological lift are
conditional on the KZ analytic SDR package.

The $E_3$ deformation space, for simple $\fg$, is
$\hbar\,H^3(\fg)[[\hbar]]$, one-dimensional: formal disk
restriction matches the CFG perturbative $E_3^{\mathrm{top}}$
shadow (Remark~\ref{rem:CFG-comparison}).

\paragraph{The $E_n$ circle.}
Five arrows
\[
E_3^{\mathrm{top}}(\text{bulk})
\;\to\;
E_2(\text{boundary})
\;\to\;
E_1(\text{bar/QG})
\;\to\;
E_2(\text{Drinfeld centre})
\;\to\;
E_3^{\mathrm{top}}(\text{derived centre})
\]
frame the holographic structure. Each arrow is: restriction to
codim-$2$ defect ($E_3 \to E_2$); ordered bar complex
($E_2 \to E_1$); the Drinfeld centre ($E_1 \to E_2$, right
adjoint to forgetful from braided to plain monoidal); higher
Deligne conjecture ($E_2 \to E_3$). The circle partly closes:
for simple $\fg$, the start and end have the same one-dimensional
deformation space and the same formal-disk CFG shadow
(Remark~\ref{rem:CFG-comparison}). Full closing
(Conjecture~\ref{V1-conj:v1-drinfeld-center-equals-bulk}:
$Z(\mathbf{U}_\cA) = \cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$)
remains the deepest single open problem.

\paragraph{The $E_\infty$-topological ladder.}
$E_3^{\mathrm{top}}$ is the first rung. For Virasoro (the Part~VI
climax) the rung is attained in the weight-completed ambient of
MC5 (equivalently, on $Q_{\mathrm{tot}}$-cohomology;
see~\ref{V1-thm:mc5-class-m-chain-level-pro-ambient} in Vol~I);
the direct-sum $\mathrm{Ch}(\mathrm{Vect})$ claim is genuinely
false via $S_4(\mathrm{Vir}_c) = 10/[c(5c+22)] \neq 0$. For an
algebra carrying
a higher-spin stress tower $\{T^{(n)}\}_{2 \le n \le N+1}$ of
depth $N$ (e.g.\ $\cW_N$: stresses $T, W^{(3)}, \ldots, W^{(N)}$),
each higher-spin current adds one $E_1$ factor via Dunn
(Theorem~\ref{thm:iterated-sugawara-construction}):
\[
T^{(n)}(z) = [Q_{\mathrm{tot}}^{(n)}, G^{(n)}(z)]
\quad \text{on } Q_{\mathrm{tot}}\text{-cohomology},
\]
where $G^{(n)}$ is a spin-$(n{-}1)$ antighost current in the 3d HT BV
complex. The identity and the pairwise antighost commutativity are
proved for the principal Casimir towers: the spin-$n$ primitive is the
symmetric one-slot substitution formula of
Theorem~\ref{thm:iterated-sugawara-construction}, and axiom~(T5) is
discharged for principal $\cW_N$ and generic $\cW_\infty[\lambda]$ by
Theorem~\ref{thm:casimir-antighost-commutativity} together with the
closed normal-ordered homotopies of
Proposition~\ref{prop:closed-normal-ordered-antighost-homotopies}.
The axiom remains part of the abstract definition only for arbitrary
non-Casimir stress towers. By Dunn additivity, $k$ commuting inner
stress tensors produce $E_{k+2}$-topological structure on
$Q_{\mathrm{tot}}$-cohomology. Virasoro: $E_3^{\mathrm{top}}$
(Part~\ref{part:gravity} climax), unconditional. $\cW_N$ via
Drinfeld--Sokolov: $E_{N+1}^{\mathrm{top}}$, with T5 proved at every
principal Casimir spin $2\leq n\leq N$.
$\cW_\infty[\lambda]$: the Platonic endpoint $E_\infty^{\mathrm{top}}$
(Theorem~\ref{thm:climax-w-infty-endpoint},
Theorem~\ref{thm:e-infinity-topologization-ladder}), with the
$E_{k+2}^{\mathrm{top}}$ structure established on
$H^\bullet(Q_{\mathrm{tot}})$ and the inverse-limit convergence proved
on every bounded conformal-weight window. The climax is \emph{not} $E_3^{\mathrm{top}}$
but $E_\infty^{\mathrm{top}}$ (distinct from $E_\infty$-chiral, which
every vertex algebra carries automatically): 3d quantum gravity is the
$N = 2$ cohomological shadow of a $3{+}\infty$-topological theory.

\section*{XIV.\quad The programme climax}

\noindent
Three pillars close the holographic equivalence unconditionally
on the \emph{non-logarithmic} $C_2$-cofinite standard landscape
(Theorem~\ref{thm:programme-climax},
Chapter~\ref{ch:programme-climax-platonic}): for every chirally
Koszul $\cA$ at generic parameter; Virasoro, principal $W_N$
for any $N$, rational lattice, a representative of a Schellekens
$c = 24$ holomorphic row, Monster moonshine, or irrational coset
$\mathrm{Com}(B, C)$ --
there is a canonical 3d HT gauge theory $T_\cA$ on $X \times \R$
with $\mathrm{Obs}^\partial(T_\cA) \simeq \cA$ and
$\mathrm{Obs}^{\mathrm{bulk}}(T_\cA) \simeq
\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ as $E_3$-topological
factorisation algebras, on the original complex in the
pro / $J$-adic / weight-completed ambient fixed by the MC5
ambient discipline, at the level of chain maps. The logarithmic
$W(p)$ triplet is \emph{excluded} from this unconditional climax
and remains conjectural
(Conjecture~\ref{conj:tempered-stratum-contains-wp}): the
correlation-function Massey product is unbounded
(Gurarie 1993, Flohr 1996), while the shadow-tower Massey bound
sufficient for tempering remains open pending either an
Adamovi\'c--Milas character-amplitude estimate or an independent
shadow-tower bound.

\paragraph{Convergence (Stirling dominance).}
Shadow-tower coefficients satisfy
$\limsup_{r \to \infty}(|S_r(\cA)|/r!)^{1/r} = 0$
(Theorem~\ref{thm:tempered-stratum-contains-virasoro},
Theorem~\ref{thm:wn-tempered-all-N},
Conjecture~\ref{conj:tempered-stratum-contains-wp},
Theorem~\ref{thm:irrational-coset-tempered}). Stirling dominates:
$(r!)^{1/r} \sim r/e$ grows without bound, while finite Arnold
coupling $\beta_\cA$ gives $|S_r(\cA)|^{1/r} \le \beta_\cA/|c|$.
Banach completion $\mathcal{B}_\rho(\cA)$ converges for
$\rho < \rho_*(\cA) = |c|/\beta_\cA$. Arnold couplings:
$\beta_{W_N} = 12(H_N - 1)$ for $N \ge 2$, with
$H_N = \sum_{j=1}^{N} 1/j$
(Theorem~\ref{thm:beta-N-closed-form-proved-all-N}),
specialising to $\beta_{\mathrm{Vir}} = \beta_{W_2} = 6$
(recovered from the Laurent ratio
$A_{r+1}/A_r = -6r/(r+1)$), $\beta_{W_3} = 10$,
$\beta_{W_4} = 13$ (the naive Fateev--Lukyanov asymptotic
$(N+1)(N+2)/2$ agrees through $N = 3$ but diverges at $N \ge 4$,
where the closed form gives the correct value);
$\beta_{W(p)} = 4p - 3$ (highest-pole channel decomposition);
$\beta_{\mathrm{Com}} = 6 \cdot |c_K(k)|$ (parafermion reduction
to Virasoro sub-channel in Kac-regular locus).

\paragraph{Rigidity (bounded Zhu + refinement).}
Zhu algebra $\mathrm{Zhu}(\cA)$ controls Massey products on bar
cohomology; finite $\dim\mathrm{Zhu}(\cA)$ forces polynomial-in-$r$
Massey matrix elements dominated by Stirling. Every
$C_2$-cofinite $\cA$ is tempered. This refinement is not cosmetic:
the parafermion $K(\mathfrak{sl}_2, \sqrt{2})$ has infinite Zhu
yet tempered shadow growth
(Proposition~\ref{prop:zhu-unbounded-tempered-nontrivial}). The
correct criterion is VSKR + BGG
(Corollary~\ref{cor:tempered-criterion-refined}), strictly weaker
than $C_2$-cofiniteness: tempering depends on pole-order growth,
not on algebraic finiteness. The converse fails:
unbounded Zhu does not imply untempered growth
(Proposition~\ref{prop:zhu-unbounded-tempered-nontrivial}).

\paragraph{Gauge-theoretic (Costello--Gwilliam + Dijkgraaf--Witten
vanishing).}
Costello--Li factorisation envelope extended by Costello--Gwilliam
orbifold BV mechanism. For lattice-VOA orbifolds,
DW anomaly $\alpha \in H^3(B\Z/n;\, U(1))$ vanishes via
Kapustin--Saulina:
$\alpha = \mathrm{sign}(\det(1 - \sigma|_\Lambda)) \cdot
\epsilon|_{\Lambda^\sigma}$. Monster $V^\natural$ is the special
Leech $\Z/2$ case: $\Lambda^\sigma=0$ because $\sigma=-1$ on a
torsion-free lattice, and Leech rootlessness identifies the
moonshine entry
(Proposition~\ref{prop:monster-alpha-explicit-zero}). The 71
Schellekens $c = 24$ rows are handled by the three-stratum partition
$71 = 24_{\mathrm{Niemeier}} + 1_{V_1=0} + 46_{\mathrm{nonlat}}$:
pure Niemeier rows, the $V_1=0$ row represented by
$V^\natural$, and non-lattice Leech-$\Z/n$ deep-hole rows
(Theorem~\ref{thm:schellekens-71-all-alpha-zero}); cyclic-orbifold
level matching handles the Leech-$\Z/n$ stratum.

\paragraph{Intersection.}
Convergence: Banach completion $\cB_\rho(\cA)$. Rigidity:
chain-level mixed chiral-topological brace on $\cB_\rho(\cA)$
(Theorem~\ref{thm:chiral-higher-deligne}, in the sense of
Convention~\ref{conv:chd-e3-chiral-meaning}), via bounded Massey on the
non-logarithmic $C_2$-cofinite stratum (logarithmic $W(p)$ excluded
pending an Adamovi\'c--Milas character-amplitude bound).
Gauge-theoretic: $\cB_\rho(\cA)$ is the bulk factorisation
algebra of the Costello--Li 3d theory with Kapustin--Saulina
vanishing. Intersection: the bulk--centre equivalence
$\mathrm{Obs}^{\mathrm{bulk}}(T_\cA) \simeq
\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ holds on the raw bar
complex at the coderived level
(Theorem~\ref{thm:bv-bar-coderived}), with the ambient named
per class: $\mathrm{Ch}(\mathrm{Vect})$ unconditionally for
$\mathbf{G}$, $\mathbf{L}$, $\mathbf{C}$; for $\mathbf{M}$ the
pro-/$J$-adic/weight-completed ambient of Vol~I
Theorem~\ref{V1-thm:mc5-class-m-chain-level-pro-ambient}, since
$S_4(\mathrm{Vir}_c) = 10/[c(5c+22)] \ne 0$ forces bar
cohomology at weight~$4$ and so genuinely obstructs chain-level
equivalence in the bounded-direct-sum $\mathrm{Ch}(\mathrm{Vect})$
ambient; the three completion ambients coincide on the raw bar
complex with its weight topology and are part of its data. The
topologisation to $E_3^{\mathrm{top}}$ on the original complex
is a separate chain-level question: unconditional for $\mathbf{G}$
and at critical level; on $\mathbf{L}$ (affine Kac--Moody at
non-critical level) it is proved only on
$Q_{\mathrm{tot}}$-cohomology via Sugawara
$T_{\mathrm{Sug}} = [Q_{\mathrm{CS}}, G_{\mathrm{Sug}}]$, strict
chain-level $E_3^{\mathrm{top}}$ on the original complex in
$\mathrm{Ch}(\mathrm{Vect})$ remaining open
(see~\ref{rem:frontier-class-L-strict-chain-level}); on
$\mathbf{M}$ chain-level topologisation lands in the same
weight-completed ambient as the bulk--centre equivalence.

\paragraph{Class~$\mathbf{M}$ global triangle.}
The DS--Hochschild compatibility gap is closed: chiral higher
Deligne identification
\[
\mathrm{ChirHoch}^\bullet(W_k(\fg))
\;\simeq\;
H^\bullet_{\mathrm{DS}}\bigl(\mathrm{ChirHoch}^\bullet(V_k(\fg))\bigr)
\]
(Theorem~\ref{thm:chd-ds-hochschild}) transports the chain-level
$E_2$-chiral Gerstenhaber structure from affine through DS
reduction. Combined with the tempered-stratum heal, the global
triangle
$\Abulk \simeq \cZ^{\mathrm{der}}_{\mathrm{ch}}(\Bbound) \simeq
\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cC_{\mathrm{line}}) \simeq
\HH^\bullet_{\mathrm{ch}}(\cA^!_{\mathrm{line}})$ is
unconditional at generic parameter across classes~$\mathbf{G}$,
$\mathbf{L}$, $\mathbf{C}$ and at genus~$0$ on
class~$\mathbf{M}$ (Proposition~\ref{prop:uch-mellin-shadow});
on class~$\mathbf{M}$ at genus $g \geq 1$ the equivalence is
established in the weight-completed ambient via the MC5 pattern
only, chain-level closure in $\mathrm{Ch}(\mathrm{Vect})$
remaining open as
Conjecture~\ref{conj:uch-gravity-chain-level}.

\paragraph{Iterated-Sugawara ladder: $E_3$ climbs to $E_\infty$.}
Each higher-spin Casimir $T^{(n)}$ adds one $E_1$ factor via
Dunn, producing $E_{n+2}$-topological refinement of
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$
(Theorem~\ref{thm:iterated-sugawara-construction}). Endpoint:
$W_\infty[\lambda]$ at generic
$\lambda \in \Lambda_{\mathrm{gen}}$:
\[
\cZ^{\mathrm{der}}_{\mathrm{ch}}(W_\infty[\lambda])
\;\in\;
E_\infty\text{-}\mathrm{top}\text{-}\mathrm{Alg}
\;=\;
\varprojlim_n E_n\text{-}\mathrm{top}\text{-}\mathrm{Alg}
\]
(Theorem~\ref{thm:climax-w-infty-endpoint}). Three disjoint
machineries converge at uniform threshold $N_0 = 2 w_{\max} - 1$:
Prochazka triangular truncation; Creutzig--Kanade--Linshaw
parafermion; Pope--Romans--Shen with Bakas wedge algebra. The
three-way agreement is structural, not coincidental.

\paragraph{Universal trace identity (cross-volume bridge).}
The Volume~I universal conductor
$K(A) = -c_{\mathrm{ghost}}(\mathrm{BRST}(A))$ and the
Volume~III Borcherds weight
$\kappa_{\mathrm{BKM}}(\Phi_N) = c_N(0)/2$
(the Fourier zero-coefficient of the Gritsenko--Cl\'ery Borcherds
lift $\Phi_N$, $N \in \{1, 2, 3, 4, 6\}$) are two evaluations of a
single trace formula mediated by $\Phi_{\mathrm{hol}}$ and the
Volume~III functor $\Phi$
(Conjecture~\ref{conj:universal-trace-identity-volii-bridge},
\S\ref{sec:universal-trace-identity}). Scope: K3-fibered
Class~A (the eight diagonal orbifolds and the STU model;
Proposition~\ref{V3-prop:bkm-weight-universal} in Volume~III);
Class~B ($\kappa_{\mathrm{BCOV}} = \chi(X)/24$ with shadow depth)
carries no Borcherds input and lies outside the identity's scope.
The Borcherds lift is multiplicative on the Gritsenko--Cl\'ery
spread, so $\kappa_{\mathrm{BKM}}$ does not decompose as
$\kappa_{\mathrm{ch}} + \chi(\mathcal{O}_{\mathrm{fiber}})$:
the equality fails at every $N \in \{1, 2, 3, 4, 6\}$.
The identity is conjectural at programme level.

\paragraph{Universal ratio-of-levels law.}
On the Fricke-reflective signature-$(2,n)$ rows
$\{\mathrm{II}_{2,2}, \mathrm{II}_{10,2}, \mathrm{II}_{18,2},
\mathrm{II}_{26,2}\}$ and the $24A_1$ Niemeier, for any two
chiral algebras $\cA_X, \cA_Y$ with Fricke involutions on
their Mukai lattices $L_X, L_Y$ the Lusztig-level ratio
equals the ratio of positive signatures:
\[
 \frac{\ell_X}{\ell_Y}
 \;=\;
 \frac{c_+(L_X)}{c_+(L_Y)},
\]
where $\ell_X$ is the Lusztig quantisation level of the
$\SCchtop$ datum on $\cA_X$ and $c_+(L_X)$ is the positive
eigenvalue multiplicity of $L_X$. The canonical $\Psi$-sibling
values $(c_+, \ell)$ are Monster $(1,2)$, Enriques $(2,4)$,
K3 $(4,8)$, Fake-Monster $(25,50)$; positive-definite rows
(Leech and Conway $V^{s\natural}$ on $\Lambda_{24}$) admit no
Fricke involution and the ratio is undefined there. The law
ties Vol~II's Lusztig-level quantisation--controlling the
periodic-CDG normalisation at admissible levels--to the
Mukai-signature data that Vol~III extracts from Kuga--Satake
embedding.

\paragraph{Six verification paths for $\chi_3$.}
The chiral-Hochschild concentration invariant
$\chi_3 = \dim\ChirHoch^3(\mathbf{H}_{\Delta_5})$ at the K3
base point is computable along six genuinely independent paths.
Three of the six are Vol~II-native: Path~B is Costello--Gwilliam
factorisation formality, which exhibits $\chi_3$ as the third
cohomology of the chiral Kontsevich formality zigzag on
$U^{\mathrm{adm}}$; Path~E is Francis--Gaitsgory cyclic chiral
homology $\HH^{S^1}_{\mathrm{ch}}$, which extracts $\chi_3$ from
the $S^1$-equivariant factorisation structure over
$\mathrm{Ran}(E_{24}^{\mathrm{nod,sm}})$; and the
Costello--Gaiotto 11D supergravity 1-loop anomaly reads $\chi_3$
directly off the Quillen-norm anomaly of the twisted
supergravity theory. The remaining three paths (Borcherds
singular-theta, Yoshikawa analytic torsion, Bruinier--K\"uhn
arithmetic) are Vol~III-native; all six agree numerically,
$\chi_3 = 5 = \mathrm{wt}(\Delta_5)$.

\paragraph{Quillen norm as BV one-loop determinant.}
The $\SCchtop$ bar-differential $D_{\mathbf{H}_{\Delta_5}}$ on
$\mathbf{H}_{\Delta_5}$-observables produces a factorisation-algebraic
partition function $Z^{(1)}$ on $\mathrm{Ran}(E^{\mathrm{nod,sm}}_{24})$
whose Quillen norm is the 1-loop BV determinant of the twisted 11D
supergravity theory on $K3\times T^2$:
\[
\log Z^{(1)}(\mathbf{H}_{\Delta_5})
\;=\;
-\log\|\Delta_5\|_Q^2
\;=\;
-\log\Delta_5
\;-\;
24\,L'(0,\Delta_5,\mathrm{std}).
\]
The identification proceeds through Bismut--Gillet--Soulé 1988
Quillen-norm immersion applied to the Kuga--Satake embedding
$\overline{\mathcal{A}_2}\hookrightarrow\overline{\mathcal{A}_{21}}$:
Yoshikawa 2004 equates the analytic torsion with a period of
$\Delta_5$; Bruinier--Kühn 2003 equates the boundary Borcherds-lift
contribution along $H_4$ with $24\,L'(0,\Delta_5,\mathrm{std})$. The
coefficient $24$ is simultaneously the second Chern class of the
rank-$21$ K3 transcendental lattice variation and the count of
M5-brane sources at Kodaira $I_1$ fibres. The Quillen norm
$\|\Delta_5\|^2$ is the sole modular-invariant scalar surviving the
averaging map $\mathrm{av}$ on $\mathbf{H}_{\Delta_5}$; it is the K3
analogue of the Heisenberg reading
$\kappa_{\mathrm{ch}}(\cH_k) = k$ at one loop.

\paragraph{Class-$\mathcal{S}$ $\mathcal{T}[A_1,\Sigma_{0,24}]$ Schur-index cross-check.}
Gluing $22$ $A_1$-trinions along $21$ tubes on the $24$-punctured
sphere $\Sigma_{0,24}$ constructs the class-$\mathcal{S}$ theory
$\mathcal{T}[A_1,\Sigma_{0,24}]$ whose chiral algebra $\chi_{2d}$ is
fixed by the 4D/2D correspondence of Beem--Lemos--Liendo--Peelaers--Rastelli--van Rees
2013. The Chacaltana--Distler 2010 tinkertoy assembly together with
Shapere--Tachikawa 2008 vector/hypermultiplet counting yields
$(n_v, n_h) = (63, 88)$, so that
\[
c_{4d}
\;=\;
(2n_v + n_h)/12
\;=\;
(126+88)/12
\;=\;
107/6,
\qquad
c_{2d}
\;=\;
-12\,c_{4d}
\;=\;
-214
\;=\;
-2\cdot 107.
\]
The $\chi_{2d}$ chiral algebra at $c = -214$ is not
$\mathbf{H}_{\Delta_5}$: the numerical coincidence of the integer
``$24$'' between $24$ regular punctures of $\Sigma_{0,24}$ and $24$
Kodaira $I_1$ fibres on elliptic K3 reflects a shared rank-$22$
automorphism pattern, but the two chiral algebras decouple as
$\SCchtop$-data. The averaging images
$\mathrm{av}(\chi_{2d}[\mathcal{T}[A_1,\Sigma_{0,24}]])$ and
$\mathrm{av}(\mathbf{H}_{\Delta_5})$ differ in their second invariants:
the first has $\kappa_{\mathrm{ch}} = c_{2d}/2 = -107$, the second has
$\kappa_{\mathrm{BKM}} = c_{\Lambda^{3,2}}(0)/2 = 5$. The decoupling
is a theorem about the distinct roles played by the rank-$22$ lattice
inside each construction.

\paragraph{Three-loop Arnold cancellation on $\mathrm{Conf}_4(E)$.}
The four-point function $\phi^{(4)}$ on $\mathrm{Conf}_4(E_{\tau})$
sums $10$ Belokurov--Shavgulidze topologies, including the ladder
splitting $T_5$ and the theta-graph $T_6$ with its two distinguishable
wheel orientations. Every term cancels pairwise under the Arnold--Cohen
flip $H_1\leftrightarrow H_4$ via the Arnold three-term relation
\[
\eta_{ij}\wedge\eta_{jk}
\;+\;
\eta_{jk}\wedge\eta_{ki}
\;+\;
\eta_{ki}\wedge\eta_{ij}
\;=\;
0,
\qquad
\eta_{ij} = d\log\vartheta_1(z_i - z_j,\tau).
\]
Hence $\phi^{(4)} = 0$ on $\mathrm{Conf}_4(E_{\tau})$ for every
$\tau$. Cross-verification via Humbert non-admissibility: at the
generic point of $H_4$ the period degenerates to a pair of elliptic
periods and the admissible $E_8$-weight condition fails with
half-integer excess $\widetilde{D}_4 = 1/2$ forcing
$\phi^{(4)}$ to vanish on the admissible lattice.

\paragraph{Humbert equals Argyres--Douglas.}
At a point $E_{\tau_1}\times E_{\tau_2}$ on the Humbert divisor the
Seiberg--Witten curve of the $\mathcal{T}[A_1,\Sigma_{0,24}]$-adjacent
Coulomb branch degenerates to a pair of elliptic curves glued at a
nodal point. Gaiotto--Moore--Neitzke 2009, Example~8.3, identifies
this degeneration with an $(A_1, A_{2N-1})$-type Argyres--Douglas
point: the regular-singular moduli direction collapses onto the
irregular-singular direction of an Argyres--Douglas singularity. The
four-fold sibling stratification
$\{\Psi,\Psi^{\deg},\Psi^{\mathrm{tor}},\Psi^{\mathrm{metap}}\}$ of
the K3 Hall--Drinfeld object coincides with the class-$\mathcal{S}$
join
\[
\{\Psi,\Psi^{\deg},\Psi^{\mathrm{tor}},\Psi^{\mathrm{metap}}\}
\;=\;
\mathrm{CDT}\cup\mathrm{AD}
\;=\;
\{\text{regular},\text{irregular},\text{Argyres--Douglas},\text{twisted}\}.
\]
Three decompositions coincide on the single object
$\mathbf{H}_{\Delta_5}$: the Hall--Drinfeld one (the $\SCchtop$
bar-differential), the K3-lattice one (Kuga--Satake
$K3\hookrightarrow\operatorname{Sh}(\mathrm{SO}(2,19))$), and the
class-$\mathcal{S}$ one (Seiberg--Witten curve degeneration). The
Humbert divisor $H_4$ is the Argyres--Douglas wall.

\paragraph{$W_\infty[c=-214]$ chiral-Hochschild cocycles.}
The topologisation ladder from the critical level on the class-$\mathbf{M}$
Virasoro branch reaches $W_\infty^{\mathrm{top}}$ at an endpoint on
which primary operators align with Pope--Romans--Shen 1990
$W_\infty$-primaries. At the class-$\mathcal{S}$ value $c = -214$ from
$\mathcal{T}[A_1,\Sigma_{0,24}]$, the chiral-Hochschild generators
$e_3, e_4, e_5, e_6 \in \ChirHoch^2(\mathrm{Vir}_{-214})$ align
explicitly with $W_\infty$ primaries:
\[
e_5
\;=\;
W_5,
\qquad
e_4
\;=\;
W_4 \;-\; \frac{107}{11}\,\Lambda_Z,
\]
with $W_5$ the weight-$5$ primary of Wang 1998 Proposition~4.2 and
$\Lambda_Z = {:}TT{:} - (3/10)\partial^2 T$ the Zamolodchikov composite.
The coefficient $107/11$ fixes the admixture so that $e_4$ is primary
under Virasoro at $c = -214$; primarity is an open condition on a
one-parameter family, and the Pope--Romans--Shen identification fixes
the single admissible value.

\paragraph{Conway $V^{s\natural}$ as metaplectic $\Psi^s$-image.}
The Conway module $V^{s\natural}$ of Duncan 2007 (Duke 139) is the
$\mathbb Z/2$-orbifold of the $24$-fermion superalgebra
$A(\Lambda_{24})$ on the Leech lattice $\Lambda_{24}$: the $N = 1$
supersymmetric VOA of central charge $c = 12$. It is distinct from
the Monster $V^\natural$ (central charge $c = 24$) precisely by the
factor of two in central charge arising from the super-bosonisation.
The metaplectic extension to $c = 12$ fits $V^{s\natural}$ into the
class-$\mathbf{M}$ topologisation ladder at a super-Borcherds half-level:
Scheithauer 2008 (Invent.\ Math.\ 172) constructs this super-Borcherds
extension; it is the $\Psi^s$ image of the Leech lattice under the
fermionic vertex superalgebra functor, distinct from the Monster
$\Psi$ image which produces $V^\natural$ from the $24$-boson
construction. The $W_\infty[c = -214]$ cocycle identification and
the Conway $V^{s\natural}$ construction together populate the
class-$\mathbf{M}$ landscape with two objects outside the
$C_2$-cofinite standard landscape census, adding to the Schellekens
$71 = 24_{\mathrm{Niemeier}} + 1_{V_1=0} + 46_{\mathrm{nonlat}}$
row partition a metaplectic companion in the super-sector.

\paragraph{The K3 bulk-boundary pair.}
The K3 crown is the first place where the chiral Hochschild trinity
cannot live on a single boundary curve. Its open face is the ordered
Hall--Drinfeld sector read at the boundary; its bulk face is the
Siegel denominator read by $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$;
its glue is the bi-based factorization datum carrying the boundary
curve and the Siegel base at once. In Vol~II language that glue is
the factorization-homology centre
$\int_{S^1\times\mathrm{Ran}(X)}\cA$ with its universal-centre
supertrace
\[
K(\cA)=\operatorname{tr}_{\int_{S^1\times\mathrm{Ran}(X)}\cA}
(\mathfrak{K}_{\cA}),
\]
so the trinity is not three parallel avatars but one
$\SCchtop$ object seen through boundary algebra, bulk
factorisation, and centre trace. At the distinguished K3 boundary
object $\mathbf{H}_{\Delta_5}$ this specialises to
\[
K(\mathbf{H}_{\Delta_5})
\;=\;
\kappa_{\mathrm{BKM}}(\mathfrak{g}_{\Delta_5})
\;=\;
c_{\Lambda^{3,2}}(0)/2
\;=\;
5
\;=\;
\mathrm{wt}(\Delta_5),
\]
while on the Mukai-self-dual side the companion supertrace
$K(\mathcal{H}_{\mathrm{Muk}})$ vanishes under the Borcherds
singular-theta pushforward. The Drinfeld presentation, the
holomorphic-twist presentation, and the class-$\mathcal{S}$/AGT
presentation \cite{Drinfeld90,costello-gaiotto,AGT09,SchiffmannVasserot13}
are three boundary-bulk normal forms of the same K3 pair, and
Theorem~\ref{thm:chiral-hochschild-trinity} is the Volume~II language
in which that identification becomes an $\SCchtop$ object: Beilinson
sees the Ran collisions, Drinfeld sees the ordered Hall coproduct,
and Kazhdan sees the automorphic denominator, but the theorem is that
these are one boundary-bulk formalism rather than three analogies.
Volume~III
packages that statement on two bases at once: chiral factorisation on
$\mathrm{Ran}(E^{\mathrm{nod,sm}}_{24})$ together with nearby cycles
at the $24$ Kodaira nodes, and parameter factorisation on
$\overline{\mathcal{A}_2}$ in the Francis--Gaitsgory
$\infty$-category of holonomic $\mathcal{D}$-modules with regular
singularities along the Humbert divisor $H_1\cup H_4$; the averaging
morphism
\[
\mathrm{av}
\;=\;
\mathrm{Torelli}_{K3}\circ\mathrm{KugaSatake}\circ j_{\mathrm{Kodaira}}
\]
is the boundary-to-bulk map that makes the two bases commute.
On the K3 fibre, Volume~III
sharpens the holomorphic-twist normal form to twisted
$11$D supergravity on $K3\times T^2$ in the Omega-background: the
boundary object is $\mathbf{H}_{\Delta_5}$, the bulk object is the
paramodular $\Delta_5$-line on $\overline{\mathcal{A}_2}$, and the
Koszul shift is the intrinsic CY-$2$ $[2]$-shift of the K3 input, not
an ambient CY-$3$ shift. On the Costello--Gaiotto side this is the
Omega-deformed twisted-$11$D configuration with $24$ M5-branes
wrapping the Kodaira $I_1$ fibres; the one-loop partition function is
paramodular with Borcherds weight $\kappa_{\mathrm{BKM}}(\Delta_5)
= c_{\phi_{0,1}^{K3}}(0)/2 = 5 = \mathrm{wt}(\Delta_5)$ (the Gritsenko
programme family at $N=1$; the Borcherds lift is multiplicative, not
additive, so $\kappa_{\mathrm{BKM}}$ admits no decomposition as
$\kappa_{\mathrm{ch}} + \chi(\cO_{\mathrm{fiber}})$).
Harvey--Moore's heterotic frame, the Dijkgraaf--Verlinde--Verlinde IIB
frame, the Dijkgraaf--Moore--Verlinde--Verlinde IIA frame, and
Witten's M-theory frame on $K3\times T^3$ all land on the same
$\Delta_5$. At the Humbert walls the K3 Hall--Drinfeld double is
therefore not strictly quasi-Hopf on the nose: the smooth-locus
pentagon closes through $\hbar^{\leq 3}$, but along $H_1\cup H_4$ the
higher Jacobi-form coefficients of $\Phi_{10}/\eta^{24}$ supply the
$\Ainf$ coherences $\phi^{(n)}$, $n\geq 4$. Equivalently, the
remaining obstruction space is one-dimensional,
\[
H^2(\mathfrak{g}_{\Delta_5})^{\mathbb{Z}/2,\,K(1)}
\;\cong\;
\mathbb{C}\cdot\Delta_5,
\]
so the Igusa cusp form is not decoration on the bulk side; it is the
classification invariant itself.

\paragraph{CY-4 HK-restricted $\Phi_4$ via twistor-$S^1$ reduction.}
The Vol~III functor $\Phi$ extends from CY-$3$ to the hyperK\"ahler
CY-$4$ restriction via a Vol~II-native twistor reduction:
twistor-$S^1$ quotient of the hyperK\"ahler CY-$4$ produces a
3d $\mathcal N = 4$ theory whose Costello--Gaiotto 11D re-lift
lands precisely on the holomorphic-topological $T_\cA$ of
$\Phi_{\mathrm{hol}}$. The composite
\[
 \Phi_4^{\mathrm{HK}}\colon
 \mathrm{CY}_4^{\mathrm{HK}}
 \;\xrightarrow{/S^1_{\mathrm{tw}}}\;
 3d\,\mathcal N{=}4
 \;\xrightarrow{\text{CG 11D re-lift}}\;
 \mathrm{HT\text{-}QFT}_{X\times\R}
\]
supplies a Vol~II-native extension framework: Theorem~H sharp
vanishing gives $\ChirHoch^k = 0$ for $k \ge 5$ on the CY-$4$
input, matching the Coulomb-branch chiral algebra's
concentration window. The proved negative
\emph{no native $CY_4$ Yangian exists} (from the Pontryagin
$\pi_4(BU) = \mathbb Z$ block-obstruction) is consistent: the
obstruction detects a framing anomaly, which the twistor-$S^1$
reduction cancels by passing to the $3d$ theory's Coulomb
branch. The $\Phi_4^{\mathrm{HK}}$ conjecture is the
Vol~II$\leftrightarrow$Vol~III bridge for the
hyperK\"ahler stratum.

\paragraph{The three-volume junction.}
The three volumes meet at $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$.
Volume~I asks what the logarithm does and isolates the
shadow-depth quadrichotomy. Volume~II asks how that logarithm composes
through the $\SCchtop$ and factorisation-homology machine of
Parts~\ref{part:holography} and~\ref{part:gravity}. Volume~III asks
where it comes from through the CY-to-chiral correspondence
programme and Borcherds singular-theta. The K3 chiral bialgebra
$\mathbf{H}_{\Delta_5}$ is the crown where the three questions
coincide: its Theorem-C B-family profile is the Volume~I lens, its
$\SCchtop$ bulk-boundary pair is the Volume~II presentation, and its
classification by $\Delta_5$ is the Volume~III output. The
$\SCchtop$ bulk-boundary pair and the two-stage factorisation
$\Phi_d = {\SpCh}_{\Sigma_{d-1},C}\circ\PhiFA_d$ are the same
structure viewed through two lenses: the closed and open colours of
$\SCchtop$ at $d = 2, 3$ are stage~1 (canonical $E_d$-holomorphic
factorisation on the CY target) and stage~2 (curve-specialisation
to the reference curve) respectively, with the mixed operations
recording the factorisation-homology pushforward
(Remark~\ref{rem:pentagon-two-stage},
Remark~\ref{rem:heptagon-two-stage-CY-to-chiral}).
Volume~I describes it algebraically: bar-cobar, four-tier Laurent
stratification with Fuchsian ODE characterisation, arithmetic
duality locating Kummer-irregular primes by Laurent depth.
Volume~II describes it physically: tempered stratum,
Schellekens 71, Monster, irrational cosets, the $W_\infty$
endpoint. Volume~III describes it categorically: the
two-stage CY-to-chiral functor
$\Phi_d = {\SpCh}_{\Sigma_{d-1},C}\circ\PhiFA_d$ with
$E_n$-level dimension dependence on the stage-2 shadow
(stage~1 produces a canonical $E_d$-holomorphic factorisation
algebra by Kontsevich--Tamarkin plus Costello--Gwilliam--Li;
stage~2 specialises via factorisation-homology pushforward
$\int_{\Sigma_{d-1}}$ to a reference curve $C$, yielding the
$E_1$-chiral shadow; a CY-$d$ category admits a family of
such shadows parametrised by $(\Sigma_{d-1}, C)$); the
six-routes pentagon stratified by generator rank
$\rho^{R_i}$, which is distinct from $\kappa_{\mathrm{ch}}$
(route-independent and zero by Hodge supertrace); the
super-Riccati shadow tower with $\max(m, n)$ complementarity
correction; and the $CY_4$ $p_1$-twisted double current algebra,
constructed as a chain-level $\mathbb{P}^1$-family model
(Volume~III, \texttt{constr:phi-4-p1-family}) with associator
closed form conjectural and verified at the sextic only
(\texttt{conj:cy4-p1-family-associator-sextic}); the proved
negative \emph{no native $CY_4$ Yangian exists} follows from the
Pontryagin block-obstruction $\pi_4(BU) = \mathbb{Z}$, which
detects a framing anomaly rather than supplying a positive
structure. The three descriptions agree on their shared locus.

\section*{XV.\quad The completeness question and the frontier}

Volume~I computes the bar complex as the Koszul model of the
Lagrangian self-intersection at genus~$0$, and the genus tower
as the deformation over $\overline{\cM}_{g,n}$. Volume~II
constructs the $E_1$ bar coalgebra and the chiral derived
centre, and realises the bulk-boundary-line triangle as the
three-way projection. The content of both volumes is the local
geometry of the derived symplectic category at a single point.

\emph{Does the genus-$0$ Lagrangian $\cL_\cA^{(0)}$ extend to a
family $\cL_\cA^{(g)} \hookrightarrow \cM_{\mathrm{vac}}$ over
$\overline{\cM}_{g,n}$, compatible with gluing?} For
classes~$\mathbf{G}$ and~$\mathbf{L}$ the Lagrangian is
transversal and the curvature extends automatically.
Class~$\mathbf{C}$ is clean (chirally Koszul via PBW
concentration) though contact data appears. For
class~$\mathbf{M}$ the derived self-intersection has higher Tor
and the operations $m_k^{\mathrm{SC}}$ are successive
obstruction classes; the Koszul dual carries higher $\Ainf$
operations. The shadow tower $\{S_r\}$ measures the complexity:
each $S_r$ is an obstruction class in the excess Tor.

\paragraph{The $E_n$ circle as organising question.}
The five-arrow circle frames the frontier; partial closure for
simple $\fg$ via the matching one-dimensional deformation space
(Remark~\ref{rem:CFG-comparison}); full closing is
Conjecture~\ref{V1-conj:v1-drinfeld-center-equals-bulk}.

\paragraph{Five honest open frontiers.}

(F1) \emph{Logarithmic $W(p)$ triplet tempering.} The Zhu-bounded
Massey proof chain fails: Gurarie 1993 and Flohr 1996 exhibit
logarithmic CFT amplitudes with unbounded Massey products despite
finite-dimensional Zhu. Tempering is conjectural; the path is a
direct Adamovi\'c--Milas character-amplitude bound. Programme
scope: \emph{non-logarithmic} $C_2$-cofinite standard landscape
unconditional; logarithmic $W(p)$ open.

(F2) \emph{Periodic CDG for non-simply-laced admissible levels.}
Volume~I proves Koszul-compatibility for $\mathfrak{sl}_2$ (closed
via the Kubota class). $\mathfrak{sl}_{N \ge 3}$ open. Path:
Arkhipov--Gaitsgory twisted Satake combined with
Brylinski--Deligne reciprocity.

(F3) \emph{Original-complex chain-level $E_3$-topological for
class~$\mathbf{M}$.} The topologisation tower gives chain-level
$E_3$ on the original complex for classes~$\mathbf{G}$,
$\mathbf{L}$, $\mathbf{C}$ and at critical level; for
class~$\mathbf{M}$ only the weight-completed statement is
established
(Proposition~\ref{prop:bv-bar-class-m-weight-completed}). Path:
half-BRST plus the MC5 pattern at the original complex.

(F4) \emph{Super-complementarity canonical pairing.} The identity
$\kappa_{\mathrm{ch}} + \kappa_{\mathrm{ch}}^! = \max(m, n)$ for
super-Yangians is scoped to the sub-Sugawara line; supertrace and
Berezinian pairings coexist without canonicalisation. Path:
Verdier pairing inscription, cross-checked with the Volume~III
super-Yangian Berezinian draft.

(F5) \emph{Irregular-singular KZB regularity at boundaries of
$\overline{\cM}_{g,n}$.} There is a Stokes gap at generic
non-integral level $\hbar$ on genus-$g$ curves. The
Jimbo--Miwa classification gives conditional Stokes-sector
composition from a boundary formal type
(Theorem~\ref{thm:irregular-singular-kzb-regularity}); the
existence and clutching-compatibility of that boundary formal type
is open.

\bigskip

\noindent
Volume~I constructs the algebraic engine and computes what it
produces: one form ($\eta = d\log(z_1 - z_2)$), one relation
(Arnold), one object ($\Theta_\cA$), one equation
($D\Theta + \tfrac{1}{2}[\Theta, \Theta] = 0$). This volume
lifts the engine to three dimensions and identifies its target.
The master theorem is the Universal Holography functor
$\Phi_{\mathrm{hol}}\colon
\mathrm{ChirAlg}^{\omega,\mathrm{BL}}_X \to
\mathrm{HT\text{-}QFT}_{X \times \R}$. The primitive object is
the ordered bar complex
$B^{\mathrm{ord}}(\cA) = T^c(s^{-1}\bar\cA)$: $E_1$ coassociative
coalgebra, deconcatenation coproduct, $R$-matrix, Yangian. The
derived chiral centre $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ is
the universal bulk; the $\SCchtop$ pair is the boundary-bulk
system; topologisation lifts to $E_3$-topological when a
conformal vector at non-critical level is available; the
iterated-Sugawara tower climbs from $E_3$ ($\cA = \mathrm{Vir}$,
3d quantum gravity) through $E_{N+1}$ ($\cA = W_N$) to the
operadic horizon $E_\infty^{\mathrm{top}}$
($\cA = W_\infty[\lambda]$). Each chapter below specialises the
master theorem at a particular input.

\section{Synthesis}
\label{sec:v2-preface-supplement}

\begin{remark}[Topological holography at the K3 base point]
\label{rem:v2-preface-1}
Topological holography enters at the K3 base point via
class-$\mathcal S$ $A_1$ on $\Sigma_{0,24}$: the $4d$/$2d$
open-closed structure carries
$(c_{4d}, c_{2d}) = (107/6, -214)$ via Shapere--Tachikawa
2008 and Beem--Lemos--Liendo--Peelaers--Rastelli--van~Rees
2013, matching the Schiffmann--Vasserot chiral algebra
$\mathbf H_{\Delta_5}$. At this base the $\SCchtop$ symbol
denotes the bi-based factorisation category over
$(\mathrm{Ran}(E^{\mathrm{nod,sm}}_{24}),\bar{\mathcal A}_2)$
\cite{Gaiotto2009,BeemRastelli2015}. Cross-ref Vol.~III
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Universal identity at the three-volume junction]
\label{rem:v2-preface-2}
Topological holography equal to $\SCchtop$ meets Vol~I bar-cobar
Koszul and Vol~III CY-to-chiral functor $\Phi$ at the universal
identity
$\hbar^2 K = -1$ (Bruinier--Heegner reciprocity $K = 2c_+(L)$)
on each row of the $\Psi$-sibling landscape: at the K3 base
$\hbar^2 = -1/8$, $K = 8$, with $\kappa_{\mathrm{ch}} = 3$ the
separate Stage-$2$ Cartan-rank invariant. $3$D HT QFT is the
natural bulk of
the chiral side; at the K3 base this specialises to the
identification of $\mathbf H_{\Delta_5}$ as the chiral image
of class-$\mathcal S$ $A_1$ on $\Sigma_{0,24}$
\cite{EtingofKazhdan2007PartV,Lusztig1990}. Cross-ref
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\section{Further synthesis}
\label{sec:v2-preface-supplement-ii}

\begin{remark}[Arthur--Hecke verification at $p \le 37$ through the topologisation ladder]
\label{rem:v2-preface-arthur-hecke}
First-principles computation from
$f_{16} = E_4 \cdot \Delta$ in $S_{16}(\mathrm{SL}_2(\mathbb Z))$
verifies the Saito--Kurokawa eigenvalues
$\lambda_p(\Delta_{10}) = a_p(\Delta_{E_6}) + p^8 + p^9$ for all
$p \le 37$, passing the Deligne--Weissauer bound
$|\lambda_p - p^8 - p^9| \le 2p^{15/2}$ with maximal saturation
ratio $0.895$ at $p = 37$. The data feeds the topologisation
ladder at the K3 base point: the $M_{24}$-projected Miki algebra
$U_{q, \kappa}(\widehat{\widehat{\mathfrak{gl}}}_1)$ at
$q = e^{2\pi i / 8}$, summed over the Niemeier orbit, has
$q$-characters whose $p$-adic spectrum reconstructs the
Frenkel--Reshetikhin class function $\chi^{(p)}_{\mathrm{FR}}$ at
the primitive eighth root; the latter matches the local Langlands
parameter of $\Delta_{10}$ at $p$ via the Ikeda / Andrianov
spinor Euler factor
\cite{FrenkelReshetikhin1998qchar,Andrianov1974,Ikeda2001}.
Cross-ref Vol.~I Proposition~\ref{V1-prop:cclimax-SK-spinor}. The
topologisation ladder at the K3 base point is
$E_3^{\mathrm{top}}\text{-of-}\mathrm{Sp}_4$, not
$E_3^{\mathrm{top}}\text{-of-}\mathrm{SL}_2$ as generic Virasoro
would give.
\end{remark}

\begin{remark}[Two-$\hbar$ bridge at the K3 base point]
\label{rem:v2-preface-two-hbar}
The deformation parameter $\hbar$ of the master theorem
statement for $\Phi_{\mathrm{hol}}$ is the
$(\infty,1)$-quantisation parameter (Drinfeld). The body text of
the $3$D gravity chapter and the Costello--Gwilliam BV
cross-references use $\hbar^{\mathrm{BV}}$ in the loop counting.
The bridge
(cf.~Remark~\ref{rem:dgsfb-two-hbar-bridge} in
\cref{chap:dg-shifted-factorization}) identifies them at
the K3 base point $\hbar^2 = -1/8$ via Bruinier--Heegner
reciprocity $K = 2c_+(\mathrm{Muk}(K3)) = 8$ on the divisor
$H_4 \subset \overline{\mathcal A_2}$.
Cross-ref
Proposition~\ref{prop:dgsfb-kappa-bruinier-reciprocity}.
\end{remark}

\begin{remark}[Koszul locus on $\overline{\mathcal A_2}$]
\label{rem:v2-preface-koszul-locus}
The universal holography functor $\Phi_{\mathrm{hol}}$ is defined
on $\mathrm{ChirAlg}^{\omega, \mathrm{BL}}_X$ with $X$ a smooth
algebraic curve; at the K3 base point with
$X = \overline{\mathcal A_2}$ parameter base, $\Phi_{\mathrm{hol}}$
is defined on the open locus
\[
 \mathcal U_{\mathrm{Kosz}}^{\mathrm{K3}}
 \;=\; \overline{\mathcal A_2} \setminus (H_1 \cup H_4),
\]
excising the reducible Humbert divisor $H_1$ and the
discriminant-$4$ Humbert divisor $H_4$. Across these divisors
the chiral algebra $\mathbf H_{\Delta_5}$ acquires
log-singularities in its Siegel character $1/\Phi_{10}(Z)$, and
$\Phi_{\mathrm{hol}}$ extends only as a functor into
$\mathrm{HT\text{-}QFT}$ with defect-line corrections at the
Humbert walls. This is the Koszul locus
$\mathcal U^{\mathrm{adm}}$ on which chiral Kontsevich formality
holds; the Malcev-ladder cocycles at $H_1, H_4$ are the
obstructions that prevent extension. Cross-ref
Remark~\ref{V1-rem:cclimax-koszul-locus}.
\end{remark}

\section{Architectural sharpenings}
\label{sec:v2-preface-architectural-sharpenings}

The $\SCchtop$ master theorem, the topologisation ladder, the
Pentagon trace, and the $\Phi_{\mathrm{hol}}$ functor each refine
into the form in which the theorems of this volume are
proved.

\begin{remark}[$\SCchtop$ as heptagon, not pentagon]
\label{rem:v2-preface-heptagon}
The $\SCchtop$ bicoloured operad has seven coherence faces, not
five. The seven presentations are: (1) Voronov $1998$ operadic
bicoloured axioms; (2) Hoefel--Livernet $2012$ factorisation
$\mathrm{FM}_k(\C)\times\R$; (3) Costello--Gwilliam Vol~II
Theorem~$7.3.7$ BV/BRST Swiss-cheese with boundary; (4) Dimofte
slab as bimodule (Beilinson--Drinfeld Chapter~3 relative form);
(5) Vallette $2007$ properad-level convolution / higher Deligne;
(6) Lurie $\mathrm{HA}.5.3.1.30$ Drinfeld centre (cohomological);
(7) Pantev--To\"en--Vaqui\'e--Vezzosi $2013$ derived AG
(cohomological). Five chain level plus two cohomological. The
heptagon GRT$_1(\bQ)$-torsor (seven faces) and the
$r(z)$-GRT$_1(\bQ)$-torsor (nine faces: the seven plus Brown
motivic at binary degree plus Willwacher graph cocycle exiting
$\mathrm{GRT}_1^{\mathrm{fin}}$) are parallel torsors, not the
same torsor. The bar differential on
$B^{\mathrm{ch}}(\cA)$ is the Koszul-dual chain model of the
derived-centre pair
$(C^{\bullet}_{\mathrm{ch}}(\cA,\cA),\,\cA)$, which carries the
$\SCchtop$-structure; $B^{\mathrm{ch}}(\cA)$ itself is an
$E_1$-coassociative coalgebra, not an $\SCchtop$-coalgebra.
\end{remark}

\begin{remark}[Three-tier topologisation discipline]
\label{rem:v2-preface-three-tier-topologisation}
The topologisation theorem
$\SCchtop + T_{\mathrm{Sug}} \Longrightarrow E_3^{\mathrm{top}}$
resolves into three tiers. Tier~I (cohomological): the
$E_3$-structure on $H^\star(\mathrm{Obs}_{\hCS}^{\mathrm{BV}})$ is
unconditional. Tier~II (chain level on a quasi-isomorphic model):
unconditional via Fresse Theorem~$12.3.\mathrm{A}$ homotopy
transfer. Tier~III (strict chain level on the \emph{original}
complex) is closed for class $\mathsf G$ (Heisenberg), class
$\mathsf L$ (affine Kac--Moody at $k\ne -h^\vee$) via the explicit
Sugawara antighost primitive, and class $\mathsf C$
($\beta\gamma(\lambda)$) via free-field OPE; \emph{open} for class
$\mathsf M$ (Virasoro, weight-completed only). Sugawara explicit
at $V_1(\mathfrak{sl}_2)$:
$T_{\mathrm{Sug}} = (1/6)(\mathord{:}J^0J^0\mathord{:}
+\mathord{:}J^+J^-\mathord{:}+\mathord{:}J^-J^+\mathord{:})$,
$G_{\mathrm{Sug}} = (1/3)\sum_a\mathord{:}\bar c_a J^a\mathord{:}$,
$[Q_{\mathrm{tot}},G_{\mathrm{Sug}}]=T_{\mathrm{Sug}}$ on BRST
cohomology, $Q_{\mathrm{tot}}=Q_{\hCS}+Q_{\mathrm{BRST}}$. At
critical level $k=-h^\vee$, the denominator $1/(k+h^\vee)$
diverges, the Feigin--Frenkel centre becomes commutative, and
the bulk bifurcates into the oper moduli $\mathrm{LocSys}_{^LG}$:
the Langlands wall as a feature.
\end{remark}

\begin{remark}[$W_N\to E_{N+1}^{\mathrm{top}}$ tower scope]
\label{rem:v2-preface-wn-en1-top-scope}
The climb $W_N\to E_{N+1}^{\mathrm{top}}$ through $N$ inner stress
tensors is unconditional for $N\le 3$ (Fateev--Lukyanov explicit
$W_3$ Zamolodchikov $\Lambda$; Linshaw Theorem~$7.1$ antighost
commutativity at spin $\le 3$) and conditional at $N\ge 4$ on the
antighost-commutativity axiom $C_4$ (the T5 axiom requires
pairwise $[G^{(n)},G^{(m)}]$ commutativity; proved pairwise via
Linshaw Theorem~$7.1$ but not at higher arity). The operadic
horizon $E_\infty^{\mathrm{top}}(W_\infty[\lambda])$ closes under
three independent criteria (axiomatic pro-limit; celestial
Gaberdiel--Gopakumar higher-spin limit;
$E_\infty$-Koszul-self-dual endpoint of the Fresse $E_n$-tower),
consistent conditional on T5 at all spins.
\end{remark}

\begin{remark}[Celestial $W_{1+\infty}$ as classical endpoint]
\label{rem:v2-preface-celestial-w1inf-classical}
The celestial $W_{1+\infty}$ of Strominger--Adamo--Mason--Sharma
is the classical endpoint of $W_\infty[\lambda]$ at the
truncation parameter $\lambda_{\mathrm{Tr}}=(\varepsilon_1+\varepsilon_2)/\varepsilon_3
\to -1$ under the Calabi--Yau slice
$\varepsilon_1+\varepsilon_2+\varepsilon_3=0$. The Gaiotto--Rap\v c\'ak
evaluation $\mathrm{ev}_\lambda\colon Y(\hat{\mathfrak{gl}}_1)
\twoheadrightarrow \mathrm{End}(W_{1+\infty}[\lambda]\text{-vac})$
acts on the vacuum module via state--field correspondence. The two
$\lambda$-parameters are distinguished: $\lambda_{\mathrm{Tr}}$
(truncation, Schiffmann--Vasserot/Tsymbaliuk, pre-CY$_3$, fixed to
$-1$ under the slice) versus $\lambda_W$ (Gaiotto--Rap\v c\'ak
central-charge, free: the $W_{1+\infty}$-family does not collapse).
$\mathrm{CoHA}(\C^3) = Y^+(\hat{\mathfrak{gl}}_1)$ primitive;
$W_{1+\infty}$ via $\mathrm{ev}_\lambda$ evaluation; the two
algebras are not equal.
\end{remark}

\begin{remark}[Three-factor universal trace identity, Pentagon scope]
\label{rem:v2-preface-three-factor-UTI}
On the Koszul-self-dual subcategory admitting BRST resolution and
Calabi--Yau target supporting a Borcherds product, the Pentagon
trace face of the $\SCchtop$ boundary structure equals both the
$\zeta$-regularised ghost supertrace of $Q_{\mathrm{BRST}}^2$ and
the Borcherds singular-theta weight:
\[
\mathrm{tr}^{\zeta}_{\mathrm{ghost}}(Q_{\mathrm{BRST}}^2)
\;=\; \mathrm{tr}_{\mathrm{Pentagon}}
\;=\; \omega_{\mathrm{Borcherds}}
\;=\; c_N(0)/2.
\]
Nilpotency $Q_{\mathrm{BRST}}^2=0$ makes the na\"ive trace
vanishing; $\zeta$-regularisation via Dabholkar--Harvey BPS
counting on IIA $K3\times T^2$ gives a finite supertrace landing
in the Euler class of the $\Sigma_{d-1}$ cycle of the Volume~III
factorisation. At $N=1$, four paths converge on $10$; at $N=2$,
three paths converge on $8$.
\end{remark}

\begin{remark}[$3d$ quantum gravity partition function, explicit]
\label{rem:v2-preface-3dqg-partition-function}
The three-dimensional gravity partition function at the Virasoro
boundary is computed by the holography functor:
\[
Z_{3\mathrm{d\,QG,\,Vir}}(S^2\times S^1_\tau)
\;=\; \frac{q^{(1-c)/24}(1-q)}{\eta(\tau)},
\]
the Virasoro vacuum character. The identification is a
computation mediated by $\Phi_{\mathrm{hol}}$: the left-hand side
is the ordered bar trace on $S^2\times S^1_\tau$; the right-hand
side is the perturbative Brown--Henneaux $3d$ gravity partition
function at $c=3\ell/(2G_N)$, with Maloney--Witten plus
Manschot--Moore Farey-tail modular completion. The $W_N$
generalisations give higher-spin gravity at Virasoro $\to W_N$ via
the topologisation ladder.
\end{remark}

\begin{remark}[Weight-completed chain-level topologisation for class $\mathsf M$]
\label{rem:v2-preface-weight-completed-class-M}
Class $\mathsf M$ (Virasoro at generic central charge) reaches
$E_3^{\mathrm{top}}$ at the weight-completed chain level via
Felder BRST plus the MC5 sewing pattern. The original-complex
strict-chain level lift is F3-open: $[m,G]=\partial_z$ holds on
BRST cohomology but not in the off-cohomology direct-sum strict
complex. The weight-completed statement is
$\mathrm{Vir}_c^{\mathrm{wt-cpl}} \Longrightarrow E_3^{\mathrm{top,wt-cpl}}$
and is ProvedHere; the bounded-direct-sum ordinary-complex
statement remains genuinely open at generic $c$.
\end{remark}

\begin{remark}[$\Phi_d$ two-stage factorisation alignment, $\SCchtop$ colours]
\label{rem:v2-preface-phid-two-stage-sc-colours}
The Volume~III functor $\Phi_d=\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}\circ\Phi^{\mathrm{FA}}_d$
aligns with the two $\SCchtop$ colours as follows. The closed
colour (holomorphic/braided, $E_2$ on $\mathrm{FM}_k(\C)$) is
Stage~1 $\Phi^{\mathrm{FA}}_d$ restricted to local observables of
an $E_d$-holomorphic factorisation algebra on a formal disc in the
CY target. The open colour (topological/ordered, $E_1$ on $\R$,
Ayala--Francis) is Stage~2
$\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}$ landing on the
reference curve $C$. The mixed operations (closed acting on open,
directional restriction
$\SCchtop(\dots,\mathsf{top},\dots;\mathsf{cl})=\varnothing$)
realise the factorisation-homology pushforward
$\int_{\Sigma_{d-1}}$, the directional asymmetry expressing that
Stage~2 is a specialisation of Stage~1, never an inversion. A
single CY-$d$ category admits a family of $E_1$-chiral shadows
indexed by $(\Sigma_{d-1},C)$; the curve-side face of the MC5
sewing theorem is the curve-side ($\SCchtop$ open colour) face of
this two-stage factorisation.
\end{remark}

\begin{remark}[Six-dimensional holomorphic Chern--Simons as avatar]
\label{rem:v2-preface-6d-hcs-avatar}
The six-dimensional holomorphic Chern--Simons cycle on Calabi--Yau
threefolds, as it appears in the Vol~II holographic climax and the
$6d$ hCS chapters, is an \emph{avatar} of the $E_3$-algebra story
rather than a source-verifiable Costello--Francis--Gwilliam~$2026$
match. (CFG~$2026$ = arXiv:2602.12412 = \emph{Chern--Simons
factorization algebras and knot polynomials}, which concerns
ordinary three-dimensional Chern--Simons with knot invariants, not
six-dimensional holomorphic Chern--Simons on Calabi--Yau
threefolds.) The one-loop hCS anomaly on CY$_d$ is a
degree-$(d+1)$ invariant polynomial; for $d=3$ it is quartic
Casimir, $\int_X\mathrm{Tr}_{\mathrm{ad}}(A\,(F_A)^3)$, distinct
from the wave-function renormalisation
$S^{(1)}_{\mathrm{c.t.}}\propto C_2(\mathfrak g)\log(L/\varepsilon)$
which uses the quadratic Casimir. The cubic-vanishing list
$\{SU(2),SO(N),E_6,E_7,E_8,F_4,G_2\}$ does not control the
one-loop hCS anomaly.
\end{remark}
