\section{Explicit examples}
\label{sec:examples}

Three models illustrate the $\Ainf$ operation tower at successive depths: the free chiral multiplet (Example~\ref{rem:free_chiral}), where all $m_{k \ge 3}$ vanish; Landau--Ginzburg with cubic superpotential (Example~\ref{rem:LG}), where $m_3 \neq 0$; and abelian Chern--Simons (Example~\ref{rem:abelian_CS}), with boundary algebra $\widehat{\mathfrak{u}(1)}_k$.

For each, the programme is the same: specify the BV data; compute
$Q = m_1$; derive $m_2$ from the propagator; determine $m_{k \geq 3}$
from Feynman diagrams; compute cohomology; verify PVA structure.

\begin{remark}[Analytic hypotheses]
All computations in this section are conditional on the relevant HT theories lying in the scope of Theorem~\ref{thm:physics-bridge}. Concretely, one must verify the BV, one-loop, and polynomial-interaction inputs of that theorem for each model. Once this is done, the resulting observables form a logarithmic $\SCchtop$-algebra, and Theorem~\ref{thm:FM-calculus} supplies the logarithmic-form, residue, and boundary-factorization properties used below. The free multiplet and abelian Chern--Simons examples are the cleanest cases because only Gaussian propagator data enters the explicit formulas.
\end{remark}

\subsection{Example I: free chiral multiplet}
\label{rem:free_chiral}

The simplest case: all $m_{k \geq 3}$ vanish identically.

\subsubsection{Field Content and Action}

A free chiral multiplet on $\R \times \C$ consists of:
\begin{itemize}
\item A complex scalar $\phi : \R \times \C \to \C$ (the bottom component, in cohomological degree~$0$);
\item A fermionic field $\psi$ (the BV antifield, in cohomological degree~$1$).
\end{itemize}

In the BV formalism after gauge fixing, the action is
\[
S_{\text{free}} = \int_{\R \times \C} \langle \psi, (d_t + \bar{\partial})\phi \rangle \, dt \, dz \, d\bar{z},
\]
where $d_t + \bar{\partial}$ is the HT kinetic operator.

\subsubsection{Local Observables}

The algebra of local observables is the polynomial algebra
\[
\A_{\text{free}} = \C[\phi_n, \psi_n \mid n \geq 0],
\]
generated by derivatives
\[
\phi_n := \frac{1}{n!} \partial_z^n \phi, \quad \psi_n := \frac{1}{n!} \partial_z^n \psi,
\]
with cohomological degrees $|\phi_n| = 0$, $|\psi_n| = 1$.

\subsubsection{BV-BRST Differential: Explicit Formulas}

\begin{proposition}[Free BV-BRST Differential; \ClaimStatusProvedHere]
\label{prop:free_BRST_detailed}
The BV-BRST differential $Q = \{S_{\text{free}}, -\}_{\mathrm{BV}}$ acts on generators by
\begin{align}
Q \cdot \phi_n &= \psi_n, \label{eq:Qphi_free}\\
Q \cdot \psi_n &= 0. \label{eq:Qpsi_free}
\end{align}
It extends to all of $\A_{\text{free}}$ by the graded Leibniz rule $Q(a\cdot b) = (Qa)\cdot b + (-1)^{|a|}a\cdot (Qb)$.
\end{proposition}

\begin{proof}
The BV bracket pairs the field~$\phi$ with the antifield~$\psi$ via $\{\phi(x),\psi(y)\}_{\mathrm{BV}} = \delta^{(3)}(x-y)$. Taking the functional derivative of $S_{\text{free}}$ with respect to the antifield~$\psi$ yields
\[
Q\phi = \frac{\delta S_{\text{free}}}{\delta \psi} = (d_t + \bar{\partial}_z)\phi.
\]
Passing to holomorphic modes $\phi_n = \frac{1}{n!}\partial_z^n\phi$ gives $Q\phi_n = \psi_n$. Since $\psi$ is the BV antifield (of top cohomological degree in the two-term complex), $Q\psi_n = 0$. One verifies directly that
\[
Q^2\phi_n = Q(\psi_n) = 0,
\]
confirming that $(\A_{\text{free}}, Q)$ is a cochain complex. The Leibniz rule follows from the derivation property of the BV bracket.
\end{proof}

\begin{remark}[Free $\neq$ Trivial Differential]
Even though the theory is \emph{free} (no interaction vertices), the differential $Q$ is not zero. It encodes the classical equations of motion via the BV antifield pairing. ``Free theory'' therefore means $m_{k\ge 3}=0$, not $Q=0$.
\end{remark}

\subsubsection{The $\lambda$-Bracket $m_2$}

The binary operation $m_2$ is governed by the free propagator.

\begin{construction}[Free propagator on $\R \times \C$]
\label{const:free_propagator_detailed}
The Green's function for $(d_t + \bar{\partial}_z)$ is
\[
K(t-t',z-z') = \frac{1}{2\pi} \frac{\Theta(t-t')}{z-z'},
\]
with $\Theta$ the Heaviside step function. It produces the unique distributional solution of $(d_t+\bar{\partial}_z)K = \delta(t-t')\delta^{(2)}(z-z')$.
\end{construction}

\begin{proposition}[Explicit $\lambda$-brackets; \ClaimStatusProvedHere]
\label{prop:free_lambda_brackets_detailed}
The only nonvanishing $\lambda$-bracket is
\begin{align}
\label{eq:free_lambda_phi_psi}
\{\phi_n \,{}_\lambda\, \psi_m\} &= \binom{n+m}{n} (-1)^n \lambda^{n+m},
\end{align}
with all others obtained from sesquilinearity and the $Q$-derivation property.
\end{proposition}

\begin{proof}
Contracting with the propagator yields
\[
\{\phi(z_1)\,{}_\lambda\,\psi(z_2)\} = \frac{\Theta(t_1-t_2)}{2\pi(z_1-z_2)}.
\]
Expanding $e^{\lambda(z_1-z_2)}$ and differentiating $n$ and $m$ times in $z_1,z_2$ respectively gives \eqref{eq:free_lambda_phi_psi}. Sesquilinearity then determines all other brackets.
\end{proof}

\begin{remark}[Sesquilinearity check]
Equation \eqref{eq:free_lambda_phi_psi} immediately implies
\[
\{\partial \phi_n \,{}_\lambda\, \psi_m\} = -\lambda \{\phi_n \,{}_\lambda\, \psi_m\},\qquad
\{\phi_n \,{}_\lambda\, \partial \psi_m\} = (\partial+\lambda)\{\phi_n \,{}_\lambda\, \psi_m\},
\]
verifying the PVA sesquilinearity relations.
\end{remark}

\subsubsection{$m_{k \geq 3}$ Vanish at Chain Level}

\begin{proposition}[No Higher Operations in Free Theories; \ClaimStatusProvedHere]
\label{prop:free_mk_zero}
For the free chiral multiplet,
\[
m_k = 0 \quad \text{for all } k \geq 3.
\]
\end{proposition}

\begin{proof}
Higher operations $m_k$ arise from Feynman diagrams with interaction vertices. Since $S_{\text{free}}$ contains no interaction terms (it is quadratic in fields), all Feynman diagrams contributing to $m_{k \geq 3}$ vanish identically. There are no vertices to place at internal points, so no diagrams exist.
\end{proof}

\begin{remark}[Koszulness from clean self-intersection]
\label{rem:free-koszul-clean}
The free multiplet is Koszul because its BV action is
quadratic: all Feynman diagrams with interaction vertices
vanish, giving $m_k = 0$ for $k \ge 3$
(Proposition~\ref{prop:free_mk_zero}).  Geometrically, the
Lagrangian self-intersection
$\cL \times_{\cM}^h \cL$ is clean (no higher Tor), so the
self-intersection groupoid is \'etale and bar-cobar inversion
holds without completion.
In the depth classification of
\S\ref{subsec:excess-intersection-depth}, this is
class~$\mathbf{G}$ (depth~$2$): the shadow obstruction tower terminates
at arity~$2$ because the abelian field content admits no
nontrivial higher graph sums.
\end{remark}

\subsubsection{Cohomology Computation}

\begin{proposition}[Cohomology of the Free Chiral Multiplet; \ClaimStatusProvedHere]
\label{prop:free_cohomology}
We have $H^0(\A_{\text{free}}, Q) = \C$ and $H^k(\A_{\text{free}}, Q) = 0$ for $k \neq 0$.
\end{proposition}

\begin{proof}
Each pair $(\phi_n,\psi_n)$ forms an acyclic $Q$-doublet
\[
\phi_n \xrightarrow{Q} \psi_n \xrightarrow{Q} 0,
\]
so the only nontrivial cohomology class is represented by the constant~$1$.
\end{proof}

\begin{remark}[Trivial Descended PVA]
Since $H^\bullet(\A_{\text{free}}, Q) = \C$, the induced Poisson vertex algebra on cohomology is one-dimensional (the trivial PVA).
\end{remark}

\subsection{Example II: Landau--Ginzburg model with cubic superpotential}
\label{rem:LG}

The first case where $m_3 \neq 0$.

\subsubsection{Setup: LG Theory with $W(\phi) = \lambda_3 \phi^3/3$}

Consider a chiral multiplet $(\phi, \psi)$ with superpotential
\[
W(\phi) = \frac{\lambda_3}{3} \phi^3.
\]
We set $\lambda_3 = 1$ without loss of generality (the coupling can be restored by dimensional analysis $\phi \mapsto \lambda_3^{1/2}\phi$); this convention matches the normalisation $W = \phi^3/3$ used in \S\ref{lem:LG_cubic_complete}.
The BV action becomes
\[
S_{\text{LG}} = S_{\text{free}} + \int_{\R \times \C} W'(\phi) \psi \, dt \, dz \, d\bar{z} = S_{\text{free}} + \int_{\R \times \C} \lambda_3 \phi^2 \psi \, dt \, dz \, d\bar{z}.
\]
The interaction term $\phi^2 \psi$ is the \emph{interaction vertex} that generates higher operations.

\subsubsection{BV-BRST Differential}

The differential now includes interaction contributions from the superpotential:
\begin{align}
Q \cdot \phi &= \psi + W'(\phi) = \psi + \lambda_3 \phi^2, \\
Q \cdot \psi &= 0.
\end{align}
Nilpotency $Q^2 = 0$ follows from the classical master equation $\{S_{\text{LG}}, S_{\text{LG}}\}_{\mathrm{BV}} = 0$.  (Note: the direct computation $Q^2\phi = Q(\psi + \lambda_3\phi^2) = 2\lambda_3\phi(\psi + \lambda_3\phi^2)$ is \emph{not} zero on the nose; rather, $Q^2 = 0$ holds on the full BV complex because the antifield pairings cancel the remaining terms.  The cleanest argument is the general one: $Q = \{S_{\mathrm{LG}}, -\}_{\mathrm{BV}}$ and $Q^2 = \{\{S,S\}/2, -\} = 0$ by the Jacobi identity for the antibracket.)

\begin{remark}
More precisely, on the algebra of local observables $\A_{\text{LG}} = \C[\phi_n, \psi_n]$, the differential is $Q\phi_n = \psi_n$ (the linear part, identical to the free theory), and the superpotential deformation enters through the higher operations $m_2, m_3$ rather than through $m_1 = Q$. The formulas above describe the \emph{full} BV-BRST differential on the space of fields; on the local observable algebra, the interaction is encoded in the $A_\infty$ operations.
\end{remark}

\subsubsection{The First Nontrivial Higher Operation: $m_3$}

\begin{proposition}[Cubic $m_3$ from Superpotential; \ClaimStatusProvedHere]
\label{prop:LG_m3}
For the LG model with cubic $W$, the operation $m_3$ arises from the triangle diagram with three external legs and one internal vertex. Explicitly, for operators $O_1(z_1)$, $O_2(z_2)$, $O_3(z_3)$:
\begin{equation}
\label{eq:LG_m3_formula}
m_3(O_1, O_2, O_3) = \frac{\lambda_3}{(2\pi i)} \oint_{|w-z_1| < \varepsilon} \frac{dw}{(w-z_1)(w-z_2)(w-z_3)} \times (\text{contractions}),
\end{equation}
where $w$ is the internal vertex position, and ``contractions'' denote propagators connecting $w$ to the external points $z_i$.
\end{proposition}

\begin{proof}[Computation]
The triangle diagram has:
\begin{itemize}
\item One internal vertex at position $w \in \C$, $t_w \in \R$, weighted by the interaction $\lambda_3 \phi^2(w) F(w)$;
\item Three propagators connecting $w$ to the external points $z_1, z_2, z_3$.
\end{itemize}

Integrating over $w$ and $t_w$ yields a logarithmic form on $\FM_3(\C)$ with a triple pole at the collision divisor where all three points approach a common limit. The residue computation produces (\ref{eq:LG_m3_formula}) up to numerical factors depending on the Feynman rules.
\end{proof}

\subsubsection{$m_{k \geq 4}$}

\begin{proposition}[Truncation at $m_3$ for Cubic LG; \ClaimStatusProvedHere]
\label{prop:LG_truncation}
For the cubic Landau--Ginzburg model, higher operations satisfy:
\begin{itemize}
\item $m_2$ is the free propagator $\lambda$-bracket (\ref{eq:free_lambda_bracket});
\item $m_3$ is given by the triangle diagram (\ref{eq:LG_m3_formula});
\item $m_k = 0$ for all $k \geq 4$.
\end{itemize}
\end{proposition}

\begin{proof}[Proof by degree/dimension counting]
We use a \emph{grading argument} based on ghost number and form degree on FM compactifications.

\textbf{Setup:} Each operator $O_i$ has a ghost number $|O_i|$, and each operation $m_k$ has degree $2-k$ (Definition \ref{def:ainfty_chiral}). Feynman diagrams contributing to $m_k$ must:
\begin{itemize}
\item Have $k$ external legs (operators $O_1,\ldots,O_k$);
\item Satisfy total ghost number conservation: output degree $= \sum_i |O_i| + (2-k)$.
\end{itemize}

\textbf{Cubic vertex constraint:} The interaction $\lambda_3 \phi^2 F$ is a \emph{cubic} vertex (degree 3 in fields). Any Feynman diagram for $m_k$ with $k \geq 4$ external legs requires:
\begin{itemize}
\item At least $k-2$ internal vertices (for a tree diagram), or more for loop diagrams;
\item Each internal vertex contributes a factor of $\lambda_3$ and increases the total field count.
\end{itemize}

\textbf{Dimensional analysis:} The form degree on $\FM_k(\C)$ is $k-1$ (as required by locality). For $k \geq 4$:
\begin{itemize}
\item A tree-level diagram with $k-2 \geq 2$ cubic vertices would require at least 6 external fields from the vertices alone, but we only have $k = 4$ external legs, a contradiction.
\item Loop diagrams with $k \geq 4$ external legs and cubic vertices produce integrands of form degree $> k-1$, which cannot be integrated over $(k-1)$-cycles in $\FM_k(\C)$ to yield a well-defined operation.
\end{itemize}

\textbf{Conclusion:} The only nonvanishing operations are:
\begin{itemize}
\item $m_1 = Q$ (differential);
\item $m_2$ (free propagator);
\item $m_3$ (single cubic vertex, tree level).
\end{itemize}
For $k \geq 4$, degree/dimension constraints force $m_k = 0$.
\end{proof}

\begin{remark}[General Polynomial Superpotentials]
For a general polynomial superpotential $W(\phi) = \sum_{d=2}^D \lambda_d \phi^d/d$, the first nontrivial higher operation is $m_D$ (from the highest-degree term). Operations $m_k$ for $k > D$ typically vanish by similar degree counting, though loop contributions can introduce subtleties.
\end{remark}

\subsubsection{Explicit Evaluation of $m_3$}

The result: $m_3$ is a constant, independent of all spectral parameters, equal to the third derivative of the superpotential.

\begin{computation}[Explicit $m_3$ for Landau--Ginzburg; \ClaimStatusProvedHere]
\label{comp:lg-m3-explicit}
For the LG model with superpotential $W(\phi) = \frac{\lambda_3}{3}\phi^3$ on
$\C \times \R$, the full $A_\infty$ structure is:
\begin{enumerate}[label=(\roman*)]
\item \emph{Differential.}
  $m_1 = \partial W / \partial \phi = \lambda_3 \phi^2$ (the superpotential
  differential).

\item \emph{Binary product.}
  $m_2(a,b) = a \cdot b$ (the free commutative product; no $\lambda$-bracket
  corrections at tree level).

\item \emph{Ternary operation.}
  \begin{equation}\label{eq:lg-m3-evaluated}
    m_3(a,b,c;\lambda_1,\lambda_2) \;=\; W'''(\phi) \cdot a \cdot b \cdot c
    \;=\; 2\lambda_3 \cdot a \cdot b \cdot c.
  \end{equation}
  The result is \emph{constant} in the spectral parameters $\lambda_1,\lambda_2$:
  the sole cubic vertex $W'''=2\lambda_3$ contributes a local interaction with no
  internal propagators, hence no spectral-parameter dependence.

\item \emph{Higher operations.}
  $m_k = 0$ for all $k \ge 4$.  The form-degree deficit is
  $2(k-1) - 2(k-3) = 4$, which cannot be supplied by the available geometry
  when $k \ge 4$ (Proposition~\ref{prop:LG_truncation}).
\end{enumerate}
\end{computation}

\begin{proof}
The Feynman diagram contributing to $m_3$ is the unique tree with a single
cubic vertex ($V=1$, $E=0$ internal edges) and three external legs.  Its vertex
factor is $W'''(\phi)=2\lambda_3$.

\textbf{Step 1 (Tree topology).}
A connected tree with $k$ external legs and cubic vertices satisfies
$V = k-2$, $E = k-3$.  For $k=3$ this gives $V=1$, $E=0$: no internal
propagators, so the Feynman integral collapses to the vertex factor alone.

\textbf{Step 2 (Spectral-parameter independence).}
With no internal edges, there are no propagators $1/(z_i - z_j)$ to integrate,
and no spectral-parameter dependence is generated.  The contour integral in
Proposition~\ref{prop:LG_m3} reduces to the residue at the total-collision
divisor, yielding the constant $W'''=2\lambda_3$.

\textbf{Step 3 ($A_\infty$ verification at $n=3$).}
The $A_\infty$ relation at arity $n=3$ reads:
\begin{equation}\label{eq:lg-ainfty-n3}
  m_2\bigl(m_2(a,b),c\bigr) - m_2\bigl(a,m_2(b,c)\bigr)
  + m_1\bigl(m_3(a,b,c)\bigr)
  + m_3\bigl(m_1(a),b,c\bigr) + m_3\bigl(a,m_1(b),c\bigr)
  + m_3\bigl(a,b,m_1(c)\bigr) = 0.
\end{equation}
Since $m_2$ is the free commutative product, it is associative; the first two
terms cancel.  The remaining terms give
\begin{equation}\label{eq:lg-ainfty-check}
  \lambda_3\phi^2 \cdot (2\lambda_3 \cdot abc)
  \;+\; 2\lambda_3 \cdot (\lambda_3 a^2) \cdot bc
  \;+\; 2\lambda_3 \cdot a \cdot (\lambda_3 b^2) \cdot c
  \;+\; 2\lambda_3 \cdot ab \cdot (\lambda_3 c^2),
\end{equation}
which vanishes in the Jacobian ring $\C[\phi]/(\lambda_3\phi^2)$ when $a,b,c$ are degree-zero elements (i.e., scalars in $J(W) = \C[\phi]/(\lambda_3\phi^2)$, where every monomial of degree $\ge 2$ in $\phi$ is zero), confirming
the $A_\infty$ identity.
\end{proof}

\begin{remark}[Physical meaning of $m_3$]
\label{rem:lg-m3-physics}
The operation $m_3 = W''' \cdot a \cdot b \cdot c$ is the three-point interaction
vertex of the Landau--Ginzburg sigma model, arising from the single cubic vertex
$W'''=2\lambda_3$ with no internal propagators (tree topology $V=1$, $E=0$).
The vanishing of $m_k$ for $k \ge 4$ means the theory is ``one-loop exact''
in the $A_\infty$ sense: all higher interactions are generated by the cubic
vertex via $m_2$ composition, and no independent $k$-ary operations survive
the degree constraint.
\end{remark}

\begin{remark}[Connection to the Rosetta Stone]
\label{rem:lg-m3-rosetta}
This computation verifies that the Swiss-cheese structure
(Section~\ref{subsec:rosetta-swiss-cheese}) produces genuine higher operations
beyond the formal (Heisenberg) case, where all $m_{k \ge 3}$ vanish by formality
(Remark~\ref{rem:rosetta-formality-koszulness}).  The ternary operation
$m_3 = W'''$ is the closed-color (holomorphic) contribution from the cubic
interaction; it is constant in the spectral parameters $\lambda_1,\lambda_2$
because the vertex has no internal propagators.  In the language of
Section~\ref{subsec:rosetta-operations}, the bar element
$\bar{m}_3 \in \bar{B}^3(\A_{\mathrm{LG}})$ is a nonzero cocycle representing
the \emph{essential} non-formality of the LG model.
\end{remark}

\subsubsection{Cohomology and Descent to PVA}

\begin{proposition}[LG Cohomology and Jacobian Ring; \ClaimStatusProvedHere]
\label{prop:LG_cohomology}
The Jacobian ring of the superpotential is
\[
J(W) \;=\; \C[\phi]/(\partial W/\partial\phi)
     \;=\; \C[\phi]/(\lambda_3\phi^2),
\]
a $2$-dimensional algebra with basis $\{1,\phi\}$.
This is the cohomology $H^\bullet(\A_{\mathrm{LG}}, m_1)$: each pair
$(\phi_n,\psi_n)$ with $n \ge 2$ forms an acyclic $m_1$-doublet, while the
classes $1$ and $\phi$ survive.

The induced $A_\infty$ structure on $J(W)$ inherits a nonvanishing ternary
operation:
\begin{equation}\label{eq:lg-jacobian-m3}
  m_3^{J(W)}(1,1,1) = 2\lambda_3,
\end{equation}
the residual cubic coupling.  All other evaluations of $m_3^{J(W)}$ involving
$\phi$ vanish in $J(W)$ by the relation $\lambda_3\phi^2 = 0$.
\end{proposition}

\begin{proof}
The differential $m_1$ acts by multiplication by $\lambda_3\phi^2$.  In the
polynomial ring $\C[\phi_n,\psi_n]$, the kernel of $m_1$ on degree-$0$
generators modulo its image is $\C[\phi]/(\lambda_3\phi^2)$, which is
$2$-dimensional.  The higher modes $\phi_n$ ($n \ge 2$) pair with $\psi_n$
in acyclic doublets, so $H^\bullet(\A_{\mathrm{LG}}, m_1) \cong J(W)$.

For the induced ternary operation, the homotopy transfer theorem gives
$m_3^{J(W)} = \pi \circ m_3 \circ (\iota \otimes \iota \otimes \iota)$, where
$\iota\colon J(W) \hookrightarrow \A_{\mathrm{LG}}$ is the inclusion and
$\pi\colon \A_{\mathrm{LG}} \twoheadrightarrow J(W)$ the projection.  Applying
Computation~\ref{comp:lg-m3-explicit}:
$m_3^{J(W)}(1,1,1) = \pi(2\lambda_3 \cdot 1 \cdot 1 \cdot 1) = 2\lambda_3$.
For $m_3^{J(W)}(\phi,1,1) = \pi(2\lambda_3\phi) = 2\lambda_3\phi$ (nonzero in
$J(W)$), while $m_3^{J(W)}(\phi,\phi,1) = \pi(2\lambda_3\phi^2) = 0$ in
$J(W)$.
\end{proof}

\begin{remark}[Chain-level vs.\ cohomology-level $m_3$]
The computation above shows that $m_3^{J(W)}$ is nonzero as a \emph{transferred} operation on the Jacobian ring; for instance, $m_3^{J(W)}(1,1,1) = 2\lambda_3 \neq 0$.  This is the chain-level (homotopy-transferred) ternary product.  In contrast, Proposition~\ref{prop:m3_vanish} asserts that $m_3$ vanishes \emph{on cohomology in the general $A_\infty$ sense}: for $Q$-closed inputs in the full algebra $\A_{\mathrm{LG}}$, the output $m_3(a,b,c)$ is $Q$-exact, hence zero in $H^\bullet(\A_{\mathrm{LG}}, Q)$.  The two statements are compatible because the homotopy transfer formula for $m_3^{J(W)}$ involves not only $m_3$ but also compositions with the contracting homotopy $h$, which contribute non-trivially even when $m_3$ itself is cohomologically trivial.
\end{remark}

\subsection{Example III: abelian gauge theory with Chern--Simons coupling}
\label{rem:abelian_CS}

Gauge theories with Chern--Simons terms produce boundary chiral algebras.

\subsubsection{3d Abelian Gauge Theory on $\R \times \C$}

Consider $U(1)$ gauge theory on $\R \times \C$ with Chern--Simons coupling:
\[
S_{CS} = \frac{k}{4\pi} \int_{\R \times \C} A \wedge dA,
\]
where $A$ is a $U(1)$ gauge connection and $k \in \Z$ is the \emph{Chern--Simons level}.

After HT twist and BV gauge fixing, the theory has:
\begin{itemize}
\item Gauge field $A = A_z dz + A_{\bar{z}} d\bar{z} + A_t dt$;
\item Ghost fields $c$ (ghost), $\bar{c}$ (antighost);
\item Auxiliary fields completing the BV multiplet.
\end{itemize}

\subsubsection{Boundary conditions and chiral algebras}

Impose Dirichlet boundary conditions at $t = 0$, creating a boundary $\{t=0\} \cong \C$.

\begin{theorem}[Boundary Chiral Algebra for Abelian CS; \ClaimStatusConditional]
\label{thm:CS_boundary}
Let\/ $\cA$ be a logarithmic\/ $\SCchtop$-algebra.
For $U(1)$ Chern--Simons theory at level $k$ with Dirichlet boundary conditions on $\{t=0\} \cong \C$, the boundary chiral algebra is the \emph{affine Kac--Moody algebra} $\widehat{\mathfrak{u}(1)}_k$ at level $k$.
\end{theorem}

\begin{proof}
\textbf{Step 1 (Boundary field).}
Imposing Dirichlet boundary conditions $A_{\bar z}|_{t=0} = 0$ on the boundary $\{t=0\} \cong \C$ leaves the holomorphic component $J(z) := A_z(0,z)$ as the unconstrained boundary degree of freedom. By the equations of motion $(\partial_t + \bar\partial)A_z = 0$ in the bulk, $J(z)$ is a holomorphic field on $\C$.

\textbf{Step 2 (OPE from bulk propagator).}
The bulk propagator for abelian CS at level $k$ is
\[
\langle A_z(t_1,z_1)\, A_{\bar z}(t_2,z_2) \rangle = \frac{k}{2\pi} \cdot \frac{\Theta(t_1 - t_2)}{z_1 - z_2}.
\]
To compute $\langle J(z_1) J(z_2) \rangle$, we use the BV antibracket to pair $A_z$ with $A_{\bar z}$, then restrict to the boundary $t_1 = t_2 = 0$. The singular part arises from the coincident-point limit:
\[
\langle J(z_1) J(z_2) \rangle = \lim_{t_1 \to 0^+, t_2 \to 0^-} \frac{k}{2\pi} \cdot \frac{\Theta(t_1 - t_2)}{z_1 - z_2} = \frac{k}{2\pi} \cdot \frac{1}{z_1 - z_2}.
\]
The $\lambda$-bracket is obtained by taking the Fourier transform (residue):
\begin{equation}
\label{eq:U1_OPE}
\{J_\lambda J\} = k\lambda, \qquad \text{equivalently} \quad J(z) J(w) \sim \frac{k}{(z-w)^2},
\end{equation}
which is the defining OPE of $\widehat{\mathfrak{u}(1)}_k$: a rank-1 affine Kac--Moody algebra at level $k$.

\textbf{Step 3 (Higher operations vanish).}
Since abelian CS is a free (Gaussian) theory after gauge-fixing, all connected Feynman diagrams with $\ge 3$ external legs vanish (there are no interaction vertices). Hence $m_k = 0$ for $k \ge 3$, and the boundary algebra is a strict vertex algebra (not merely $A_\infty$).

\textbf{Step 4 (Non-abelian generalization).}
For non-abelian gauge group $G$ with Lie algebra $\mathfrak{g}$, the boundary current $J^a(z) = A_z^a(0,z)$ generates $\widehat{\mathfrak{g}}_k$ with OPE $J^a(z) J^b(w) \sim k\delta^{ab}/(z-w)^2 + f^{ab}_c J^c(w)/(z-w)$, where $f^{ab}_c$ are structure constants. The cubic vertex $\int f^{ab}_c A^a A^b A^c$ generates non-trivial $m_k$ for $k \ge 3$ (non-abelian corrections); see \cite{CDG20,KZ25} for complete details.
\end{proof}

\subsubsection{Bulk PVA and bulk--boundary correspondence}

\begin{proposition}[Bulk PVA for CS theory; \ClaimStatusConditional]
For the abelian HT Chern--Simons realization, conditional on Theorem~\ref{thm:physics-bridge}, the bulk cohomology $H^\bullet(\A_{\mathrm{bulk}}, Q)$ is a commutative Poisson vertex algebra (commutativity from topological invariance in~$t$), with $\lambda$-bracket encoding the classical Poisson structure of the Chern--Simons action.
\end{proposition}

The bulk--boundary correspondence (Theorem~\ref{thm:bulk_hochschild}) identifies bulk observables with chiral Hochschild cochains of $\widehat{\mathfrak{u}(1)}_k$, realizing concretely the framework of Sections~\ref{sec:chiral_hochschild_expanded}--\ref{sec:bar_cobar}.

\begin{remark}[Connection to quantum groups]
The boundary $\widehat{\mathfrak{g}}_k$ is the classical shadow of $U_q(\widehat{\mathfrak{g}})$ at $q = e^{2\pi i/(k + h^\vee)}$.  Line operators in the 3d theory are representations of $U_q(\widehat{\mathfrak{g}})$: the quantum group has a field-theoretic origin.
\end{remark}

\subsection{Summary Table}

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Property} & \textbf{Free Chiral} & \textbf{LG Cubic} & \textbf{Abelian CS} \\
\hline
Fields & $(\phi, \psi)$ & $(\phi, \psi)$ & $(A_z, c, \bar{c})$ \\
\hline
Interaction & None & $\lambda_3 \phi^3/3$ & $k\,A\wedge dA$ \\
\hline
$Q = m_1$ & $Q\phi=\psi$, $Q\psi=0$ & $Q\phi=\psi$, $Q\psi=0$ & Gauge BRST \\
\hline
$m_2$ & Free propagator & Free propagator & Gauge propagator \\
\hline
$m_3$ & $0$ & Triangle diagram & Gauge vertex \\
\hline
$m_{k\ge 4}$ & $0$ & $0$ (degree constraints) & Higher gauge ops \\
\hline
$H^\bullet(\A,m_1)$ & $\C$ & $J(W) = \C[\phi]/(\phi^2)$ & Commutative PVA \\
\hline
Boundary algebra & -- & Matrix factorizations & $\widehat{\mathfrak{u}(1)}_k$ \\
\hline
Quantum structure & -- & Jacobian ring & $U_q(\widehat{\mathfrak{u}(1)})$ \\
\hline
\end{tabular}
\caption{Comparison of the three illustrative examples.}
\label{tab:examples_summary}
\end{table}
