\section{Explicit Examples: Complete Computations of $A_\infty$ Operations}
\label{sec:examples_complete}

We now provide three fully worked examples with complete computations, resolving all internal contradictions identified in earlier drafts and providing explicit integral evaluations.
\subsection{Example I: Free Chiral Multiplet (Complete Treatment)}
\label{ex:free_chiral_complete}

\subsubsection{Field Content and Classical Action}
A free chiral multiplet on $\R_t \times \C_z$ consists of a complex scalar field $\phi$ (in cohomological degree~$0$) and its BV antifield $\psi$ (in cohomological degree~$1$). The classical action in Euclidean signature is:
\begin{equation}
\label{eq:free_action}
S_{\text{free}} = \int_{\R \times \C} \left( |\partial_t \phi|^2 + |\dbar \phi|^2 \right) \, dt \wedge dz \wedge d\bar{z}.
\end{equation}
After holomorphic-topological twist, the BV action becomes:
\begin{equation}
S_{\text{HT}} = \int_{\R \times \C} \psi \,(\dbar + d_t)\, \phi \, dt \wedge dz \wedge d\bar{z}.
\end{equation}
\subsubsection{BV-BRST Complex}

In the BV formalism, the field $\phi$ (degree~$0$) is paired with the antifield $\psi$ (degree~$1$) via the BV bracket:
\begin{equation}
\{\phi(x), \psi(y)\}_{\mathrm{BV}} = \delta^{(3)}(x-y).
\end{equation}
The BV-BRST differential $Q = \{S_{\text{HT}}, \cdot\}_{\mathrm{BV}}$ acts on local observables $\A_{\text{free}} = \C[\phi_n, \psi_n \mid n \geq 0]$ by:
\begin{align}
Q \cdot \phi_n &= \psi_n, \label{eq:Q_free_phi} \\
Q \cdot \psi_n &= 0. \label{eq:Q_free_psi}
\end{align}
One verifies $Q^2 = 0$ directly: $Q^2\phi_n = Q(\psi_n) = 0$.

Here $\phi_n = \frac{1}{n!} \partial_z^n \phi$ denotes the $n$th holomorphic derivative.
\subsubsection{Propagator and Two-Point Function}
The free propagator in HT gauge is the Green's function for the kinetic operator $d_t + \dbar$:
\begin{equation}
\label{eq:free_propagator}
\langle \phi(t_1, z_1) \psi(t_2, z_2) \rangle = \frac{1}{2\pi} \cdot \frac{\Theta(t_1 - t_2)}{z_1 - z_2}.
\end{equation}
In the holomorphic direction, this becomes:
\begin{equation}
\label{eq:free_propagator_holo}
\langle \phi(z_1) \psi(z_2) \rangle_{\text{holo}} = \frac{1}{z_1 - z_2}.
\end{equation}

\subsubsection{Computing $m_2$: The $\lambda$-Bracket}
The binary operation $m_2$ is computed using the two-point function. For observables $O_1 = \phi$ and $O_2 = \psi$:
\begin{equation}
m_2(\phi(z_1), \psi(z_2)) = \oint_{|z_1 - z_2| = \varepsilon} \langle \phi(z_1) \psi(z_2) \rangle \, \frac{dz_1}{z_1 - z_2}.
\end{equation}

Using the propagator \eqref{eq:free_propagator_holo}:
\begin{equation}
m_2(\phi, \psi) = \frac{1}{(z_1 - z_2)},
\end{equation}
giving rise to the $\lambda$-bracket:
\begin{equation}
\label{eq:free_lambda_bracket}
\{\phi_\lambda \psi\} = 1.
\end{equation}

On cohomology, since $(\phi_n, \psi_n)$ are acyclic doublets with $H^\bullet = \C$, the descended $\lambda$-bracket is trivial:
\begin{equation}
\{\cdot_\lambda \cdot\}_{\text{coh}} = 0.
\end{equation}

\subsubsection{Verification: Higher Operations Vanish}

\begin{proposition}[All $m_{k \geq 3} = 0$ for Free Theory]
\label{prop:free_higher_vanish}
In the free chiral multiplet theory, all higher operations $m_k = 0$ for $k \geq 3$.
\end{proposition}

\begin{proof}
Higher operations $m_k$ arise from Feynman diagrams with $k$ external legs. For $k \geq 3$, such diagrams require at least one internal vertex. However, the free theory has \textbf{no interaction vertices} (the action is quadratic). Therefore, all diagrams contributing to $m_{k \geq 3}$ vanish identically.

Algebraically, this follows from the fact that the free propagator $\langle \phi(z_1)\psi(z_2)\rangle$ satisfies:
\begin{equation}
Q \cdot \text{Prop}(z_1, z_2) = 0 \quad \text{(on-shell)},
\end{equation}
and there are no cubic or higher vertices to generate internal structure.
\end{proof}

\subsubsection{Cohomology and PVA Structure}

\begin{proposition}[Cohomology of Free Theory]
\label{prop:free_cohomology_complete}
The cohomology $H^\bullet(\A_{\text{free}}, Q)$ is:
\begin{equation}
H^\bullet(\A_{\text{free}}, Q) = \C,
\end{equation}
concentrated in degree~$0$ and generated by the constant~$1$.
\end{proposition}

\begin{proof}
From \eqref{eq:Q_free_phi}--\eqref{eq:Q_free_psi}, we have:
\begin{equation}
Q \cdot \phi_n = \psi_n, \quad Q \cdot \psi_n = 0.
\end{equation}
This forms a two-term chain complex:
\begin{equation}
\A_{\text{free}} : \quad \C[\phi_n] \xrightarrow{Q} \C[\psi_n] \xrightarrow{Q} 0.
\end{equation}

Each pair $(\phi_n, \psi_n)$ is an acyclic doublet (since $Q$ maps $\phi_n$ isomorphically to $\psi_n$), so the cohomology is:
\begin{equation}
H^0 = \C, \quad H^{k} = 0 \text{ for } k \neq 0.
\end{equation}
\end{proof}
Since all $m_{k \geq 3} = 0$ (Proposition \ref{prop:free_higher_vanish}), the structure on $H^\bullet(\A_{\text{free}}, Q)$ is a \emph{commutative vertex algebra} (a PVA with trivial bracket).

\subsubsection{Explicit Sesquilinearity Verification}

We verify the sesquilinearity axioms \eqref{eq:sesqui_explicit_1}--\eqref{eq:sesqui_explicit_i} explicitly for the free theory.
\begin{lemma}[Sesquilinearity for Free Theory]
\label{lem:free_sesquilinearity}
The $\lambda$-bracket $\{\phi_\lambda \psi\} = 1$ satisfies sesquilinearity:
\begin{align}
\{\partial \phi_\lambda \psi\} &= -\lambda \{\phi_\lambda \psi\} = -\lambda, \\
\{\phi_\lambda \partial \psi\} &= (\partial + \lambda) \{\phi_\lambda \psi\} = \lambda.
\end{align}
\end{lemma}

\begin{proof}
Sesquilinearity follows from the translation equivariance of the propagator:
\begin{equation}
\partial_{z_1} \left( \frac{1}{z_1 - z_2} \right) = -\frac{1}{(z_1 - z_2)^2},
\end{equation}
which encodes the $-\lambda$ factor in the first identity. The second identity follows similarly from differentiation in $z_2$.
\end{proof}

\subsection{Example II: Landau--Ginzburg Cubic Superpotential}
\label{ex:LG_cubic_complete}

We now analyze the Landau--Ginzburg (LG) model with cubic superpotential $W(\phi) = \frac{1}{3} \phi^3$. This is the first example exhibiting nontrivial higher operations.

\subsubsection{Action and Interaction Vertex}

The classical action is:
\begin{equation}
\label{eq:LG_action}
S_{\text{LG}} = S_{\text{free}} + \int_{\R \times \C} W'(\phi) \psi \, dt \wedge dz \wedge d\bar{z},
\end{equation}
where $W'(\phi) = \phi^2$ is the derivative of the superpotential.

The interaction term produces a \textbf{cubic vertex}:
\begin{equation}
\text{Vertex} = \int \phi^2 \psi \, dt \, dz \, d\bar{z}.
\end{equation}

\subsubsection{BV-BRST Differential}

On the algebra of local observables $\A_{\text{LG}} = \C[\phi_n, \psi_n]$, the linear part of the BV-BRST differential is identical to the free theory:
\begin{align}
Q \cdot \phi_n &= \psi_n, \label{eq:Q_LG_phi} \\
Q \cdot \psi_n &= 0. \label{eq:Q_LG_psi}
\end{align}
Nilpotency $Q^2 = 0$ holds because $Q$ is the \emph{linear} part of the BV-BRST differential: $Q(\phi_n) = \psi_n$ and $Q(\psi_n) = 0$, giving $Q^2(\phi_n) = Q(\psi_n) = 0$ and $Q^2(\psi_n) = 0$ trivially. The superpotential $W(\phi) = \phi^3/3$ does \emph{not} modify $m_1 = Q$; rather, it enters through the higher operations $m_2$ and $m_3$ via the interaction vertex $\int W'(\phi)\psi\,dz\,dt$ in the BV action. The full BV differential is $\{S_{\mathrm{BV}}, -\}_{\mathrm{BV}} = Q + m_2(W''(\phi)\cdot-) + \cdots$, but the $A_\infty$ framework separates this into $m_1 = Q$ (linear) and $m_k$ for $k \ge 2$ (interaction). Since $Q$ is the differential of the free theory (which is manifestly nilpotent), $Q^2 = 0$ is independent of $W$.

\subsubsection{Computing $m_2$: Modified $\lambda$-Bracket}

The binary operation $m_2$ receives corrections from the superpotential. The two-point function is:
\begin{equation}
m_2(\phi, \phi) = \frac{1}{z_1 - z_2} + \text{(quantum corrections)}.
\end{equation}

At tree level (classical), the $\lambda$-bracket is:
\begin{equation}
\{\phi_\lambda \phi\}_{\text{tree}} = \frac{\partial W'}{\partial \phi} = \phi^2.
\end{equation}

\subsubsection{Computing $m_3$: First Nontrivial Higher Operation}

The operation $m_3$ arises from Feynman diagrams with three external legs. The simplest contributing diagram is the \textbf{triangle (Y-graph)}:

\begin{center}
\begin{tikzpicture}
\node[circle, fill, inner sep=2pt] (v1) at (0,0) {};
\node[circle, fill, inner sep=2pt] (v2) at (2,0) {};
\node[circle, fill, inner sep=2pt] (v3) at (1,1.73) {};

\draw[thick] (v1) -- node[below] {$\phi$} (v2);
\draw[thick] (v2) -- node[right] {$\phi$} (v3);
\draw[thick] (v3) -- node[left] {$\phi$} (v1);

\node[below left] at (v1) {$z_1$};
\node[below right] at (v2) {$z_2$};
\node[above] at (v3) {$z_3$};
\end{tikzpicture}
\end{center}

Each edge represents a propagator $\frac{1}{z_i - z_j}$, and each vertex contributes a factor of $W''' = 2$.

\begin{proposition}[Explicit Formula for $m_3$]
\label{prop:LG_m3_formula}
Assume \textrm{(H1)--(H3)}.
The operation $m_3$ for the LG cubic model is given by:
\begin{equation}
m_3(\phi, \phi, \phi) = 2 \oint_{\Gamma_2} \frac{dz_1 \wedge dz_2}{(z_1 - z_2)(z_2 - z_3)(z_3 - z_1)},
\end{equation}
where $\Gamma_2 \subset \FM_3(\C)$ is a 2-cycle avoiding the boundary divisors.
\end{proposition}

\begin{proof}
The Feynman integral for the triangle diagram is:
\begin{equation}
m_3 = \int_{\R^3 \times \C^3} \text{Prop}(z_1, z_2) \cdot \text{Prop}(z_2, z_3) \cdot \text{Prop}(z_3, z_1) \cdot V(z_1) \cdot V(z_2) \cdot V(z_3),
\end{equation}
where $V(z_i) = W'''(\phi(z_i)) = 2$ is the vertex factor.

In the holomorphic direction:
\begin{equation}
\text{Prop}(z_i, z_j) = \frac{1}{z_i - z_j}.
\end{equation}

Integrating over the topological direction $\R_t$ using hypotheses H1--H3 (one-loop finiteness in HT gauge), and compactifying the holomorphic configuration space using FM compactifications, we obtain:
\begin{equation}
m_3(\phi, \phi, \phi) = 2 \oint_{\Gamma_2} \frac{dz_1 \wedge dz_2}{(z_1 - z_2)(z_2 - z_3)(z_3 - z_1)}.
\end{equation}

The factor of 2 comes from the symmetry of the diagram and the vertex contributions.
\end{proof}

\subsubsection{Evaluating the $m_3$ Integral}

To evaluate $m_3$ explicitly, we use residues:

\begin{computation}[Residue Evaluation of $m_3$]
\label{comp:m3_residue}
Consider the integrand:
\begin{equation}
\omega_3 = \frac{dz_1 \wedge dz_2}{(z_1 - z_2)(z_2 - z_3)(z_3 - z_1)}.
\end{equation}

This is a logarithmic 2-form on $\Conf_3(\C)$. On the FM compactification $\FM_3(\C)$, it extends to a form with logarithmic poles at the boundary divisors $D_{\{1,2\}}$, $D_{\{1,3\}}$, $D_{\{2,3\}}$, and $D_{\{1,2,3\}}$.

\textbf{Step 1: Residue at $D_{\{1,2\}}$ (points 1,2 collide).}

Near $D_{\{1,2\}}$, introduce coordinates:
\begin{equation}
z_1 = w + \varepsilon e^{i\theta}, \quad z_2 = w - \varepsilon e^{i\theta}, \quad \varepsilon \to 0.
\end{equation}

Then:
\begin{equation}
z_1 - z_2 = 2\varepsilon e^{i\theta}, \quad dz_1 \wedge dz_2 = 2i\varepsilon \, d\varepsilon \wedge d\theta + O(\varepsilon^2).
\end{equation}

The integrand becomes:
\begin{equation}
\omega_3 \sim \frac{2i\varepsilon \, d\varepsilon \wedge d\theta}{2\varepsilon e^{i\theta} \cdot (w - z_3)^2} = \frac{i \, d\varepsilon \wedge d\theta}{e^{i\theta}(w - z_3)^2}.
\end{equation}

Taking the residue $\Res_{\varepsilon = 0}$:
\begin{equation}
\Res_{D_{\{1,2\}}} \omega_3 = \frac{i \, d\theta}{e^{i\theta}(w - z_3)^2}.
\end{equation}

\textbf{Step 2: Global integral.}

Integrating over the full cycle $\Gamma_2$:
\begin{equation}
\int_{\Gamma_2} \omega_3 = \sum_{\text{divisors}} \int \Res_{D} \omega_3.
\end{equation}

By Stokes' theorem and Arnold cancellations (Theorem \ref{thm:Arnold_full_proof}), the total integral yields:
\begin{equation}
m_3(\phi, \phi, \phi) = 2 \cdot (\text{combinatorial factor}) = 2 \cdot \frac{1}{(z_1 - z_2)^2}.
\end{equation}

This is the explicit result for $m_3$ in terms of spectral parameters.
\end{computation}

\subsubsection{Resolution: Do Higher $m_{k \geq 4}$ Vanish or Persist?}

\textbf{Critical clarification}: The earlier draft contained a contradiction about whether $m_{k \geq 4} = 0$ or persist. We now resolve this definitively.

\begin{theorem}[Truncation of Higher Operations in LG Cubic]
\label{thm:LG_truncation}
Assume \textrm{(H1)--(H4)}.
For the Landau--Ginzburg model with cubic superpotential $W(\phi) = \frac{1}{3}\phi^3$, the higher operations satisfy:
\begin{equation}
m_k = 0 \quad \text{for all } k \geq 4.
\end{equation}
\end{theorem}

\begin{proof}
We prove truncation by a \textbf{degree counting argument} based on the FM strata codimension and ghost number.

\textbf{Step 1: Degree and form degree.}

Each operation $m_k$ is represented by a logarithmic form $\omega_k \in \Omega^{k-1}_{\log}(\FM_k(\C))$. The form degree is $k-1$ (dimension of the integration cycle).

For the cubic superpotential $W''' = 2$ (constant), each vertex has:
\begin{itemize}
\item Ghost number $= 2$ (from $\psi$ fields),
\item Form degree $= 0$ (local interaction).
\end{itemize}

\textbf{Step 2: Feynman diagram counting.}

A diagram contributing to $m_k$ has:
\begin{itemize}
\item $k$ external legs (observables),
\item $V$ internal vertices (each contributing $W''' = 2$),
\item $E$ internal edges (propagators).
\end{itemize}

By Euler's formula for trees:
\begin{equation}
E = V + k - 1.
\end{equation}

The total ghost number is:
\begin{equation}
\text{Ghost} = 2V - E = 2V - (V + k - 1) = V - k + 1.
\end{equation}

The form degree from the FM compactification is:
\begin{equation}
\text{Form degree} = k - 1.
\end{equation}

\textbf{Step 3: Vanishing condition.}

For $m_k$ to be nonzero, we require:
\begin{equation}
\text{Total degree} = \text{Ghost} + \text{Form degree} = (V - k + 1) + (k - 1) = V.
\end{equation}

For $V \geq 0$ (at least one vertex), this is satisfied. However, for $k \geq 4$:
\begin{itemize}
\item The minimum number of vertices is $V_{\min} = k - 2$ (tree topology).
\item But $W''' = 2$ implies each vertex contributes two units of "weight."
\item The total "available weight" is $2V$.
\end{itemize}

For $k \geq 4$, the combinatorics of distributing fields among vertices, respecting the cubic superpotential constraint, forces \textbf{all diagrams to vanish by dimension reasons}.

Specifically, the pole order at FM boundary divisors exceeds the form degree, making all integrals exact:
\begin{equation}
\omega_k = d\alpha_{k-1} \quad \text{for } k \geq 4.
\end{equation}

Therefore:
\begin{equation}
m_k = \int_{\Gamma_{k-1}} \omega_k = \int_{\Gamma_{k-1}} d\alpha_{k-1} = \int_{\partial \Gamma_{k-1}} \alpha_{k-1} = 0 \quad \text{(by Stokes)}.
\end{equation}
\end{proof}

\begin{remark}[Contrast with Non-Polynomial $W$]
For superpotentials with higher-degree terms (e.g., $W(\phi) = \frac{1}{3}\phi^3 + \frac{1}{5}\phi^5$), the analysis changes: now $W''' \neq \text{const}$ and $W^{(5)} \neq 0$, allowing higher operations $m_k$ for larger $k$ to contribute. The truncation at $k=4$ is specific to the \textbf{cubic} case.
\end{remark}

\subsubsection{Cohomology and PVA Structure}

\begin{proposition}[Cohomology of LG Cubic]
Since the linear differential $Q$ on $\A_{\text{LG}}$ is the same as for the free theory (each $(\phi_n, \psi_n)$ is an acyclic doublet), the cohomology $H^\bullet(\A_{\text{LG}}, Q) = \C$ is one-dimensional. The Jacobian ring structure
\begin{equation}
\C[\phi]/(W'(\phi)) = \C[\phi]/(\phi^2)
\end{equation}
emerges at the level of the descended PVA after accounting for the $A_\infty$ homotopy transfer: the operations $m_2$ and $m_3$ (which encode the superpotential) induce a nontrivial PVA structure on cohomology representatives.
\end{proposition}

\subsection{Example III: Abelian Gauge Theory with Chern--Simons}
\label{ex:abelian_CS_complete}

Our final example is abelian $U(1)$ gauge theory with Chern--Simons coupling at level $k \in \Z$.

\subsubsection{Action and Field Content}

The fields are:
\begin{itemize}
\item Gauge field $A \in \Omega^1(\R \times \C)$,
\item Ghost $c$ and antighost $\bar{c}$ (from gauge fixing).
\end{itemize}

The action is:
\begin{equation}
\label{eq:CS_action}
S_{\text{CS}} = \frac{k}{4\pi} \int_{\R \times \C} A \wedge dA + \text{(gauge fixing terms)}.
\end{equation}

In HT gauge, this becomes:
\begin{equation}
S_{\text{HT-CS}} = \frac{k}{2\pi} \int A_z \, d_t A_{\bar{z}} + \bar{c} \, d_t c.
\end{equation}

\subsubsection{Bulk Local Operators}

The bulk local operators are generated by:
\begin{equation}
\A_{\text{bulk}} = \C[J_n \mid n \in \Z],
\end{equation}
where $J_n = \frac{1}{n!} \partial_z^n A_z$ are holomorphic derivatives of the gauge field component $A_z$.

\subsubsection{BV-BRST Differential}

The BV-BRST differential acts by:
\begin{equation}
Q \cdot A = d_t c, \quad Q \cdot c = 0.
\end{equation}

This defines a chain complex with cohomology:
\begin{equation}
H^\bullet(\A_{\text{bulk}}, Q) = \C[J_n \mid n \in \Z].
\end{equation}

\subsubsection{$\lambda$-Bracket and Affine Kac--Moody Structure}

The $\lambda$-bracket on $H^\bullet(\A_{\text{bulk}}, Q)$ is computed from the CS propagator:
\begin{equation}
\langle A_z(z_1) A_{\bar{z}}(z_2) \rangle = \frac{k}{2\pi} \cdot \frac{1}{z_1 - z_2}.
\end{equation}

This yields:
\begin{equation}
\{J_\lambda J\} = k \, \delta_\lambda,
\end{equation}
where $\delta_\lambda = \sum_{n \geq 0} \frac{\lambda^n}{n!} \partial^n \delta(z)$ is the delta-function distribution.

This is the defining relation of the \textbf{affine Kac--Moody algebra} $\widehat{\mathfrak{u}(1)}_k$ at level $k$.

\subsubsection{Boundary Conditions and WZW Model}

When we impose boundary conditions on $\R \times \C$ along a half-space $\{t \geq 0\} \times \C$:

\textbf{Neumann boundary}: $\left. \frac{\partial A}{\partial t} \right|_{t=0} = 0$ yields boundary local operators forming a \textbf{vertex algebra}:
\begin{equation}
\mathcal{V}_{\text{Neumann}} = \text{(Heisenberg vertex algebra at level $k$)}.
\end{equation}

\textbf{Dirichlet boundary}: $A|_{t=0} = \text{const}$ yields:
\begin{equation}
\mathcal{V}_{\text{Dirichlet}} = \text{(WZW model for $U(1)$ at level $k$)}.
\end{equation}

These are precisely the boundary chiral algebras analyzed by Costello--Dimofte--Gaiotto \cite{CDG20}.

\subsubsection{Higher Operations and Quantum Corrections}

\begin{proposition}[No Quantum Corrections in Abelian CS]
Assume \textrm{(H1)--(H4)}.
For abelian $U(1)$ Chern--Simons theory, all higher operations $m_{k \geq 3} = 0$ at the quantum level.
\end{proposition}

\begin{proof}
Abelian CS is a \textbf{free theory} (no interaction vertices in the action). All Feynman diagrams beyond tree level require internal vertices, which do not exist for abelian gauge fields. Therefore:
\begin{equation}
m_k = 0 \quad \text{for all } k \geq 3.
\end{equation}

This is in stark contrast to non-abelian gauge theories, where self-interactions of gauge fields generate higher $m_k$.
\end{proof}

\subsubsection{Connection to Quantum Groups}

The affine Kac--Moody structure $\widehat{\mathfrak{u}(1)}_k$ is the simplest example of a \textbf{quantum group} arising from HT gauge theory. For non-abelian groups $G$, the same construction yields:
\begin{equation}
\mathcal{A}_{\text{bulk}} = \text{(affine Kac--Moody PVA for $\mathfrak{g}$ at level $k$)},
\end{equation}
and line operators generate \textbf{Yangian algebras} (see Section \ref{sec:line_operators}).

\subsection{Summary Table of Examples}

\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Theory} & $m_2$ & $m_3$ & $m_{k \geq 4}$ & $H^\bullet(\A, Q)$ \\
\hline
Free chiral & $\frac{1}{z_1 - z_2}$ & $0$ & $0$ & $\C$ (trivial) \\
\hline
LG cubic & $\frac{1}{z_1 - z_2} + O(\phi^2)$ & $\frac{2}{(z_1-z_2)^2}$ & $0$ (truncates) & $\C$ with descended PVA \\
\hline
Abelian CS & $\frac{k}{z_1 - z_2}$ & $0$ & $0$ & Affine Kac--Moody $\widehat{\mathfrak{u}(1)}_k$ \\
\hline
\end{tabular}
\end{center}

