% ================================================================
% THE HEISENBERG ROSETTA STONE
% ================================================================
% This chapter lives in BOTH volumes.
% Volume I: chapters/theory/rosetta_stone.tex
% Volume II: chapters/examples/rosetta_stone.tex
%
% It proves, by explicit computation on H_k, that the bar complex
% is a Swiss-cheese algebra in the sense of Definition~\ref{def:SC}.
% The chapter uses only macros available in both volumes.
% ================================================================

% Fallback macros: ensure compilation in both volumes.
\providecommand{\barB}{\bar{B}}
\providecommand{\cA}{\mathcal{A}}
\providecommand{\cH}{\mathcal{H}}
\providecommand{\SCchtop}{\mathsf{SC}^{\mathrm{ch,top}}}
\providecommand{\Ainf}{\mathsf{A}_{\infty}}
\providecommand{\Eone}{\mathsf{E}_1}
\providecommand{\Einf}{\mathsf{E}_{\infty}}
\providecommand{\Pinf}{\mathsf{P}_{\infty}}
\providecommand{\PVA}{\mathsf{PVA}}
\providecommand{\Ass}{\mathsf{Ass}}
\providecommand{\FM}{\mathrm{FM}}
\providecommand{\Conf}{C}
\providecommand{\dfib}{d_{\mathrm{fib}}}
\providecommand{\Dg}[1]{D_{#1}}
\providecommand{\dzero}{d_0}
\providecommand{\barBch}{\bar{B}^{\mathrm{ch}}}
\providecommand{\Omegach}{\Omega^{\mathrm{ch}}}
\providecommand{\bC}{\mathbb{C}}
\providecommand{\bR}{\mathbb{R}}
\providecommand{\C}{\mathbb{C}}
\providecommand{\R}{\mathbb{R}}
\providecommand{\Z}{\mathbb{Z}}
\providecommand{\fg}{\mathfrak{g}}
\providecommand{\id}{\mathrm{id}}
\providecommand{\Res}{\operatorname{Res}}
\providecommand{\Ran}{\operatorname{Ran}}
\providecommand{\chirCom}{\mathsf{Com}^{\mathrm{ch}}}
\providecommand{\chirLie}{\mathsf{Lie}^{\mathrm{ch}}}
\providecommand{\Linf}{\mathsf{L}_{\infty}}
\providecommand{\ClaimStatusProvedHere}{\textnormal{[proved here]}}
\providecommand{\ClaimStatusProvedElsewhere}{\textnormal{[proved elsewhere]}}
\providecommand{\ClaimStatusConjectured}{\textnormal{[conjectured]}}
\providecommand{\ClaimStatusHeuristic}{\textnormal{[physical heuristic]}}
\providecommand{\Hom}{\operatorname{Hom}}
\providecommand{\colldiv}[2]{D_{#1#2}}
\providecommand{\LogForm}[2]{\eta_{#1#2}}


\section{The Heisenberg Rosetta Stone}
\label{sec:rosetta-stone}
\index{Rosetta Stone|textbf}
\index{Heisenberg algebra!Rosetta Stone|textbf}
\index{Swiss-cheese operad!Heisenberg example|textbf}

The Heisenberg algebra~$\cH_k$ has shadow depth $r_{\max} = 2$ (class~G), so $\Theta^{\mathrm{oc}}$ terminates at degree~2. Every projection is computed in closed form: curvature $\kappa = k$, spectral $R$-matrix $R(z) = e^{k\hbar/z}$, genus tower $F_g = k\,\lambda_g^{\mathrm{FP}}$. The line category is $\cC_{\mathrm{line}} \simeq \cH_{-k}\text{-mod}$ (via $Y(\mathfrak{u}(1)) \simeq \cH_{-k}$); the derived center is the free boson bulk; the complementarity involution $k \mapsto -k$ closes the triangle (note: the Koszul dual $\cH_k^! = \Sym^{\mathrm{ch}}(V^*)$ is not $\cH_{-k}$).

The Lagrangian self-intersection
$\mathfrak{S}_b = L \times_X L$ is one-dimensional with
transversal crossing. Koszulness ($m_{k \ge 3} = 0$) is the
statement that this intersection is clean:
$H_*^{BM}(\mathfrak{S}_b)$ is one-dimensional in each stratum.
The single scalar~$k$ determines the full Heisenberg package:
the direct algebraic data (algebra, $R$-matrix, genus tower,
PVA) and, through the abelian line-side comparison, the
open-colour dual and semisimple line model, because the
Lagrangian is concentrated.

The present section proves this for the Heisenberg algebra
$\cH_k$ by explicit computation. The results are neither deep
nor difficult; they are \emph{explicit}, and the explicitness
carries information that no amount of abstract machinery can supply.
The Heisenberg algebra has a single generator~$J$, a single
OPE pole of order~$2$, and no composite fields. These three
simplifications (one generator, one pole order, no composites) make
every step checkable by hand. Yet none of the five main theorems
of Volume~I becomes trivial: bar-cobar adjunction (Theorem~A),
inversion (Theorem~B), complementarity (Theorem~C), the modular
characteristic (Theorem~D), and Hochschild cohomology (Theorem~H)
are all instantiated here with full content.

The section has five parts:
\S\ref{subsec:rosetta-e1-coalgebra} identifies the bar complex
as an $E_1$ dg coassociative coalgebra;
\S\ref{subsec:rosetta-operations} computes all higher operations
and verifies that they vanish;
\S\ref{subsec:rosetta-pva} extracts the Poisson vertex algebra
on cohomology; \S\ref{subsec:rosetta-genus1} exhibits
curvature at genus~$1$; and \S\ref{subsec:rosetta-bridge}
assembles a dictionary mapping every bar-complex datum to both a
Volume~I theorem and a Volume~II physical identification.


% ================================================================
\subsection{The $E_1$ coalgebra structure on the bar complex}
\label{subsec:rosetta-e1-coalgebra}
\index{bar complex!E_1 coalgebra structure!Heisenberg}
% ================================================================

We fix notation. Let $V = \bC \cdot J$ be the one-dimensional
vector space spanned by the Heisenberg current, let $k \in \bC$
be the level, and let $\cH_k$ be the corresponding Heisenberg
chiral algebra with OPE
\begin{equation}\label{eq:rosetta-heisenberg-ope}
J(z)\, J(w) \;\sim\; \frac{k}{(z - w)^2}.
\end{equation}
The bar complex $\barB^{\mathrm{ch}}(\cH_k)$ is the cofree
conilpotent coalgebra on the desuspension $s^{-1}\overline{\cH}_k$,
equipped with the bar differential $d_{\barB}$ constructed from
OPE residues on the Fulton--MacPherson compactification.
Concretely, a bar element of tensor degree~$n$ lives on
\begin{equation}\label{eq:rosetta-bar-element-space}
\barB^n(\cH_k) \;=\;
(s^{-1}\overline{\cH}_k)^{\otimes n}
\;\otimes\;
\Omega^{\bullet}\bigl(\overline{\Conf}_{n+1}(X)\bigr),
\end{equation}
where $\overline{\Conf}_{n+1}(X) = \FM_{n+1}(X)$ is the
Fulton--MacPherson compactification and the logarithmic forms
$\eta_{ij} = d\log(z_i - z_j)$ provide the propagators.

\begin{theorem}[$E_1$ coalgebra structure on the Heisenberg bar complex;
\ClaimStatusProvedHere]
\label{thm:rosetta-e1-coalgebra}
\index{bar complex!E_1 coalgebra structure!Heisenberg}
The geometric bar complex $\barB^{\mathrm{ch}}(\cH_k)$ is an
$E_1$ dg coassociative coalgebra with:
\begin{enumerate}[label=\textup{(\roman*)}]
\item bar differential $d_{\barB}$
 \textup{(}residues on collision divisors of\/ $\FM_n(\bC)$\textup{)},
\item deconcatenation coproduct $\Delta$
 \textup{(}ordered splitting on $\Conf_n^{<}(\bR)$\textup{)},
\end{enumerate}
satisfying the coderivation identity
$\Delta \circ d_{\barB} = (d_{\barB} \otimes \id + \id \otimes d_{\barB}) \circ \Delta$.
The $\SCchtop$ structure emerges at the level of the chiral
derived center: the pair
$\bigl(C^\bullet_{\mathrm{ch}}(\cH_k, \cH_k),\; \cH_k\bigr)$
is the $\SCchtop$ datum \textup{(}bulk acting on boundary\textup{)}.
\end{theorem}

\begin{proof}
The proof has four steps, establishing the $E_1$ dg coassociative
coalgebra structure.

\medskip
\noindent\textit{Step~1: Closed color.}\enspace
The bar differential $d_{\barB}$ is the coderivation of the
cofree coalgebra $T^c(s^{-1}\overline{\cH}_k)$ determined by
the OPE residue. For the Heisenberg algebra, the only nonvanishing
component is the binary one:
\begin{equation}\label{eq:rosetta-dbar-binary}
d_{\barB}\bigl[s^{-1}J \,|\, s^{-1}J\bigr]
\;=\;
\int_{E_{12}}
 J(z_1)\, J(z_2) \cdot \omega_{12}^{\FM}
\;=\;
J_{(1)}J
\;=\; k.
\end{equation}
The bar differential is the Stokes boundary operator on $\FM_2(\bC)$:
integration over the exceptional divisor $E_{12} \cong S^1$ in
the FM blowup extracts the mode product $J_{(1)}J = k$ from
the double pole $k/(z_1 - z_2)^2$.

The nilpotence $d_{\barB}^2 = 0$ is the Arnold relation
on $\FM_3(\bC)$. The three codimension-$1$ boundary strata of
$\FM_3(\bC)$ are the collision divisors $\colldiv{1}{2}$,
$\colldiv{2}{3}$, and $\colldiv{1}{3}$.
On these strata, the logarithmic $2$-form
$\eta_{12} \wedge \eta_{23}$ restricts to the Arnold relation
\begin{equation}\label{eq:rosetta-arnold}
[\eta_{12} \wedge \eta_{23}]
\;+\;
[\eta_{23} \wedge \eta_{13}]
\;+\;
[\eta_{13} \wedge \eta_{12}]
\;=\; 0
\end{equation}
in $H^2(\FM_3(\bC))$.
Each summand contributes a residue to $d_{\barB}^2$, and their
sum vanishes by exactness. For the Heisenberg algebra, this
computation produces $d_{\barB}^2[s^{-1}J \,|\, s^{-1}J \,|\, s^{-1}J]
= k \cdot (\text{Arnold sum}) = 0$.

The closed-color structure is thus a dg coalgebra
$(\barB^{\mathrm{ch}}(\cH_k), d_{\barB})$, with $d_{\barB}$
built from $\FM_n(\bC)$. This is holomorphic factorization.

\medskip
\noindent\textit{Step~2: Open color.}\enspace
The deconcatenation coproduct
\begin{equation}\label{eq:rosetta-delta}
\Delta\bigl[a_1 \,|\, \cdots \,|\, a_n\bigr]
\;=\;
\sum_{i=0}^{n}
\bigl[a_1 \,|\, \cdots \,|\, a_i\bigr]
\;\otimes\;
\bigl[a_{i+1} \,|\, \cdots \,|\, a_n\bigr]
\end{equation}
is coassociative by construction: it is the tensor coalgebra
coproduct. The ordering of tensor factors corresponds to the
ordering of points $t_1 < t_2 < \cdots < t_n$ on $\bR$;
splitting at position~$i$ is cutting the interval
$[t_1, t_n] \subset \bR$ at the gap between $t_i$ and $t_{i+1}$.
The ordered configuration space $\Conf_n^{<}(\bR)$ is
contractible (it is an open simplex
$\{t_1 < \cdots < t_n\} \cong \bR^{n-1}_{> 0}$), so the
$\Eone$-structure on $\Conf_n(\bR)$ contracts to
$\Ass$-structure: $\Delta$ is strictly coassociative,
not merely $\Eone$-coassociative up to homotopy.

\medskip
\noindent\textit{Step~3: Compatibility.}\enspace
The coderivation property
\begin{equation}\label{eq:rosetta-compatibility}
\Delta \circ d_{\barB}
\;=\;
(\id \otimes d_{\barB} \;+\; d_{\barB} \otimes \id)
\circ \Delta
\end{equation}
asserts that $d_{\barB}$ is a coderivation of $\Delta$.
We verify this on bar elements of degree~$2$. The left-hand side
gives
\[
\Delta\bigl(d_{\barB}[s^{-1}J \,|\, s^{-1}J]\bigr)
\;=\;
\Delta(k)
\;=\;
k \otimes [] + [] \otimes k,
\]
where $[]$ denotes the empty bar element (the coaugmentation).
The right-hand side gives
\[
(d_{\barB} \otimes \id + \id \otimes d_{\barB})\bigl(
 [] \otimes [s^{-1}J \,|\, s^{-1}J]
 \;+\;
 [s^{-1}J] \otimes [s^{-1}J]
 \;+\;
 [s^{-1}J \,|\, s^{-1}J] \otimes []
\bigr).
\]
The middle term $[s^{-1}J] \otimes [s^{-1}J]$ contributes nothing
because $d_{\barB}$ on a single element $[s^{-1}J]$ requires a
binary collision, which is absent. The first and last terms
contribute $[] \otimes k + k \otimes []$, matching the left-hand side.

Geometrically,
the collision divisors $\colldiv{i}{j} \subset \FM_n(\bC)$
parametrize collisions in the holomorphic direction, while the
splitting $\Delta$ acts in the topological direction on $\bR$.
These directions are independent in the product
$\FM_n(\bC) \times \Conf_n^{<}(\bR)$: a collision
$z_i \to z_j$ in $\bC$ does not merge the corresponding
points $t_i, t_j \in \bR$. The residue operation (extracting the
singular part of the OPE along $\colldiv{i}{j}$) therefore
commutes with the splitting operation (cutting the interval at a
gap in the $\bR$-ordering).

\medskip
\noindent\textit{Step~4: Coherences.}\enspace
The $E_1$ coalgebra structure requires homotopy-coherent
compatibility between $d_{\barB}$ and $\Delta$.
For $(\barB^{\mathrm{ch}}(\cH_k),
d_{\barB}, \Delta)$, all coherence conditions are automatically
satisfied at the strict level:
\begin{enumerate}[label=(\alph*)]
\item the closed-color differential $d_{\barB}$ is strictly
 square-zero (Arnold relation, not merely $\Ainf$-null);
\item the open-color coproduct $\Delta$ is strictly coassociative
 (tensor coalgebra, not merely $\Eone$-coassociative);
\item compatibility~\eqref{eq:rosetta-compatibility} holds strictly,
 not up to a homotopy parametrized by the $W$-construction.
\end{enumerate}
The higher coherences between $\FM_n(\bC)$ and
$\Conf_n^{<}(\bR)$ are trivial because the product
$\FM_n(\bC) \times \Conf_n^{<}(\bR)$ decomposes: the FM operad is
formal at genus~$0$ (Kontsevich), so all higher coherences on the
holomorphic factor vanish; the ordered configuration space on $\bR$
is contractible, so all higher coherences on the topological factor
vanish; and the product structure admits no mixed higher coherences.
\end{proof}


% ================================================================
\subsection{Reading off the higher operations}
\label{subsec:rosetta-operations}
\index{higher operations!from bar complex}
\index{Heisenberg algebra!higher operations}
% ================================================================

The $E_1$ coalgebra structure on the bar complex classifies the twisting morphisms that encode all
$\Ainf$ operations of the chiral algebra. The following
proposition makes the extraction explicit.

\begin{proposition}[Higher operations from bar elements;
\ClaimStatusProvedHere]
\label{prop:rosetta-operations}
\index{A-infinity operations@$\Ainf$ operations!from bar complex}
The $\Ainf$ operations $m_k$ of a chiral algebra $\cA$ are
recovered from the bar complex by the formula
\begin{equation}\label{eq:rosetta-mk-extraction}
m_k(a_1, \ldots, a_k;\, \lambda_1, \ldots, \lambda_{k-1})
\;=\;
\text{coefficient of }
s^{-1}a_1 \otimes \cdots \otimes s^{-1}a_k
\text{ in }
d_{\barB}^{(k)},
\end{equation}
where $d_{\barB}^{(k)}$ denotes the component of the bar
differential that maps $\barB^k \to \barB^{k-1}$ and the
spectral parameters $\lambda_j$ arise from the regularization
of the collision integral on $\FM_k(\bC) \times \Conf_k^{<}(\bR)$.
\end{proposition}

\begin{proof}
This is the defining property of the bar construction as a
coderivation: $d_{\barB}$ is the unique coderivation of
$T^c(s^{-1}\overline{\cA})$ whose composition with the
projection $T^c(s^{-1}\overline{\cA}) \twoheadrightarrow
s^{-1}\overline{\cA}$ recovers the sequence of operations
$(m_1, m_2, m_3, \ldots)$. The spectral parameter
$\lambda_j$ arises from the regularized integral
$\int_{\Conf_k^{<}(\bR)} dt_1 \cdots dt_{k-1}$
along the topological direction, with $\lambda_j = t_{j+1} - t_j$
recording the separation between consecutive points.
\end{proof}

The computation of all $m_k$ for $\cH_k$.

\begin{proposition}[Heisenberg higher operations;
\ClaimStatusProvedHere]
\label{prop:rosetta-heisenberg-mk}
\index{Heisenberg algebra!$m_k$ operations}
For the Heisenberg algebra $\cH_k$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $m_1 = 0$ \textup{(}no internal differential\textup{)}.
\item $m_2(J, J;\, \lambda) = k\lambda$
 \textup{(}the OPE residue\textup{)}.
\item $m_k = 0$ for all $k \geq 3$
 \textup{(}no ternary or higher operations\textup{)}.
\end{enumerate}
In particular, $\cH_k$ is \emph{formal}: its $\Ainf$ structure is
concentrated in $m_2$.
\end{proposition}

\begin{proof}
(i) The internal differential of $\cH_k$ is zero: there is no
$Q$-operator, and the algebra has trivial cohomological grading
concentrated in degree~$0$.

\smallskip
(ii) The binary operation extracts the double-pole mode. From
equation~\eqref{eq:rosetta-dbar-binary}, the bar differential
on a degree-$2$ element is
\[
d_{\barB}[s^{-1}J \,|\, s^{-1}J]
\;=\;
J_{(1)}J
\;=\; k.
\]
In the spectral (Fourier) parametrization, the meromorphic function
$k/(z_1 - z_2)^2$ corresponds to the spectral expression
$m_2(J, J;\, \lambda) = k\lambda$. The spectral parameter
$\lambda$ records the weight of the residue: a pole of order~$2$
at $z_1 = z_2$ produces a first-order polynomial in~$\lambda$
via the substitution $(z_1 - z_2)^{-n-1} \leftrightarrow
\lambda^{(n)}/n!$.

\smallskip
(iii) The vanishing of $m_k$ for $k \geq 3$ is the decisive
computation. Consider the degree-$3$ bar element
\[
\xi_3
\;=\;
s^{-1}J \otimes s^{-1}J \otimes s^{-1}J
\;\otimes\;
\eta_{12} \wedge \eta_{23}
\;\in\;
\barB^3(\cH_k).
\]
To compute $d_{\barB}^{(3)}$, one must extract a residue
from the iterated OPE of three Heisenberg currents along a
codimension-$2$ stratum of $\FM_3(\bC)$. The iterated OPE is
\begin{align}\label{eq:rosetta-iterated-ope}
J(z_1)\, J(z_2)\, J(z_3)
&\;\sim\;
\frac{k}{(z_1 - z_2)^2}\, J(z_3)
\;+\;
\frac{k}{(z_1 - z_3)^2}\, J(z_2)
\;+\;
\frac{k}{(z_2 - z_3)^2}\, J(z_1).
\end{align}
Each term has a double pole in one pair of variables and is
regular in the third. The ternary operation $m_3$ would arise
from a \emph{simultaneous} triple collision $z_1 \to z_2 \to z_3$.
On $\FM_3(\bC)$, the triple collision stratum is a point
(the maximal boundary stratum). The residue at this point requires
a pole of order $\geq 3$ in the combined variables. But the
iterated OPE~\eqref{eq:rosetta-iterated-ope} has at most
double poles in each pair; there is no pole of the required
order in the ternary collision limit.

More precisely: in the coordinates $u = z_1 - z_2$,
$v = z_2 - z_3$ on $\FM_3(\bC)$, the triple collision
$u, v \to 0$ has codimension~$2$. The form
$\eta_{12} \wedge \eta_{23} = d\log u \wedge d\log v$
contributes a factor $u^{-1}v^{-1}\, du \wedge dv$. The
OPE contributes at most $u^{-2}$ or $v^{-2}$ (never both
simultaneously, because there is no term with $u^{-2}v^{-2}$
in~\eqref{eq:rosetta-iterated-ope}). The combined integrand
is therefore at most $u^{-3}v^{-1}$ or $u^{-1}v^{-3}$ in
the worst case: the residue in the \emph{other} variable
vanishes because the pole order is insufficient. Hence
$m_3 = 0$.

The same argument applies at all higher degrees: $m_k = 0$
for $k \geq 3$ because the Heisenberg OPE has only a double
pole, and the $k$-fold collision on $\FM_k(\bC)$ requires
poles of total order $\geq k$ to produce a nonvanishing
residue against the logarithmic $k$-form
$\eta_{12} \wedge \eta_{23} \wedge \cdots \wedge \eta_{k-1,k}$.
The double-pole OPE can produce at most order~$2$ in each pairwise
variable, but the factorization of the iterated OPE ensures that
no more than one pair is singular at a time.
\end{proof}

\begin{remark}[Formality and Koszulness]
\label{rem:rosetta-formality-koszulness}
\index{formality!Heisenberg}
\index{Koszulness!Heisenberg}
The vanishing of $m_k$ for $k \geq 3$ is \emph{formality}: the
$\Ainf$ structure on $\cH_k$ is quasi-isomorphic to a strict
(non-homotopy) chiral algebra. This is a consequence of the
general one-loop criterion (Theorem~\ref{thm:one-loop-koszul}:
one-loop exact algebras without DS reduction are Koszul), and
for the Heisenberg algebra it is exactly the bar-side manifestation
of chiral Koszulness computed in Volume~I: the PBW spectral
sequence degenerates at~$E_1$, and there are no higher Massey
products. For non-abelian algebras (affine Kac--Moody, Virasoro,
$\mathcal{W}$-algebras), the simple-pole OPE terms produce
nonvanishing $m_3$ and the theory ceases to be formal,
but all standard families remain \emph{Koszul}
(PBW spectral sequence degenerate, bar cohomology concentrated).
The non-formality is detected by the Chevalley--Eilenberg
differential on the bar complex, which is the $d_1$ page of
the PBW spectral sequence.
\end{remark}

\begin{remark}[Lagrangian content of the perturbative/non-perturbative divide]
\label{rem:rosetta-lagrangian-perturbative}
\index{perturbative!Heisenberg as clean intersection}
\index{non-perturbative!Virasoro as excess intersection}
The Heisenberg is perturbatively exact because its Lagrangian
self-intersection is clean: the double-pole OPE produces a
transversal crossing with one-dimensional strata, $m_k = 0$
for $k \ge 3$, and the genus tower is controlled by a single
scalar $\kappa(\cH_k) = k$. The Virasoro, by contrast, is
non-perturbative: its fourth-order pole $c/(z-w)^4$ creates
excess intersection dimension, forcing nonvanishing higher
$\Ainf$ operations that proliferate like instanton corrections
through the genus tower. This is not a coincidence; it is the
Lagrangian content of the perturbative/non-perturbative divide
(Remark~\ref{rem:koszul-perturbative-watershed}).
\end{remark}

% ================================================================
\subsection{The Poisson vertex algebra on cohomology}
\label{subsec:rosetta-pva}
\index{Poisson vertex algebra!Heisenberg}
\index{Heisenberg algebra!PVA structure}
% ================================================================

The binary operation $m_2$ decomposes into a regular part (the
commutative product) and a singular part (the $\lambda$-bracket).
For the Heisenberg algebra, this decomposition reveals the
simplest nontrivial Poisson vertex algebra.

\begin{proposition}[Heisenberg PVA; \ClaimStatusProvedHere]
\label{prop:rosetta-pva}
\index{lambda-bracket@$\lambda$-bracket!Heisenberg}
The cohomology $H^{\bullet}(\cH_k, Q) = \bC[J]$ carries the
structure of a Poisson vertex algebra with:
\begin{enumerate}[label=\textup{(\roman*)}]
\item\label{item:rosetta-pva-product}
 commutative product: the differential polynomial algebra
 $\bC[J, \partial J, \partial^2 J, \ldots]$, with the
 ordinary polynomial product\textup{;}%
 \footnote{In particular $J \cdot J = J^2 \neq 0$ as an
 element of the polynomial ring. The zeroth product
 $J_{(0)}J = 0$ (the simple-pole coefficient of the
 Heisenberg self-OPE vanishes), but this is the
 \emph{zeroth $\lambda$-bracket mode}, not the
 commutative product $\mu$. The normally ordered product
 $:\!JJ\!:\, = J_{(-1)}J$ corresponds to $J^2$ in the
 PVA polynomial ring.}
\item\label{item:rosetta-pva-bracket}
 $\lambda$-bracket: $\{J_\lambda J\} = k\lambda$
 \textup{(}the singular part of $m_2$\textup{)}.
\end{enumerate}
This is the free boson PVA: the Poisson vertex algebra of a free
scalar field with propagator $k/(z - w)^2$.
\end{proposition}

\begin{proof}
The binary operation $m_2(J, J;\, \lambda) = k\lambda$
(Proposition~\ref{prop:rosetta-heisenberg-mk}(ii)) decomposes
according to the pole order:
\begin{align}
m_2(J, J;\, \lambda)
&\;=\;
\underbrace{0}_{\text{regular part}}
\;+\;
\underbrace{k\lambda}_{\text{singular part}}.
\end{align}
The regular part (the $\lambda^0$ coefficient) vanishes:
this is the zeroth product $J_{(0)}J = 0$, reflecting the
absence of a simple pole in $J(z)J(w) \sim k/(z-w)^2$.
The commutative PVA product $\mu$ is the polynomial ring
product on $\bC[J, \partial J, \ldots]$, with
$J \cdot J = J^2$ as an ordinary polynomial (corresponding
to the normally ordered product $:\!JJ\!:\, = J_{(-1)}J$
in the vertex algebra).

The singular part is the $\lambda$-bracket
$\{J_\lambda J\} = k\lambda$, encoding the double-pole OPE
$J(z)J(w) \sim k/(z-w)^2$.

The PVA axioms are verified as follows.

\medskip
\noindent\textit{Sesquilinearity.}\enspace
$\{\partial J_\lambda J\} = -\lambda \{J_\lambda J\} = -k\lambda^2$
and $\{J_\lambda \partial J\} = (\partial + \lambda)\{J_\lambda J\}
= (\partial + \lambda)(k\lambda) = k\lambda^2$
(where $\partial$ acts on the vacuum, giving zero).

\medskip
\noindent\textit{Skew-symmetry.}\enspace
The PVA skew-symmetry axiom reads
$\{a_\lambda b\} = -\{b_{-\lambda - \partial} a\}$.
With $a = b = J$:
$-\{J_{-\lambda - \partial} J\} = -k(-\lambda - \partial) = k\lambda + k\partial$.
Acting on the vacuum ($\partial \cdot \mathbf{1} = 0$), this reduces to $k\lambda = \{J_\lambda J\}$.

\medskip
\noindent\textit{Jacobi identity.}\enspace
With a single generator $J$, the Jacobi identity
\[
\{J_\lambda \{J_\mu J\}\}
\;-\;
\{J_\mu \{J_\lambda J\}\}
\;=\;
\{\{J_\lambda J\}_{\lambda + \mu} J\}
\]
reduces to $\{J_\lambda\, k\mu\} - \{J_\mu\, k\lambda\} = \{(k\lambda)_{\lambda+\mu}\, J\}$.
Since $k\mu$ and $k\lambda$ are scalars (not elements of the algebra), all three brackets vanish.

\medskip
\noindent\textit{Leibniz rule.}\enspace
The Leibniz rule $\{a_\lambda (b \cdot c)\} = \{a_\lambda b\} \cdot c
+ b \cdot \{a_\lambda c\}$ must be verified on generators of the
polynomial ring $\bC[J]$.
The nontrivial instance is $a = b = c = J$:
\begin{align*}
\text{RHS}
&= \{J_\lambda J\} \cdot J \;+\; J \cdot \{J_\lambda J\}
= (k\lambda)\, J \;+\; J\, (k\lambda)
= 2k\lambda\, J.
\end{align*}
For the left-hand side, the $\lambda$-bracket acts on
$J \cdot J = J^2 \in \bC[J]$ as a derivation of the
commutative product (item~\ref{item:rosetta-pva-product}):
$\{J_\lambda\, J^2\} = 2J \cdot \{J_\lambda J\} = 2k\lambda\, J$.
Both sides equal $2k\lambda\, J$: Leibniz is satisfied.%
\footnote{The zeroth product $J_{(0)}J = 0$ (the simple-pole
 coefficient of the Heisenberg self-OPE vanishes) plays no role
 here. It means $J$ is \emph{primary of conformal weight~$1$}
 with respect to itself, not that $J \cdot J = 0$ in the PVA
 commutative product. The commutative product is the polynomial
 ring product, corresponding to the normally ordered product
 $:\!JJ\!:\, = J_{(-1)}J \neq 0$ in the vertex algebra.}
\end{proof}

\begin{remark}[Connection to the coisson structure]
\label{rem:rosetta-coisson}
\index{coisson algebra!Heisenberg}
The PVA of Proposition~\ref{prop:rosetta-pva} is the classical
limit of the chiral algebra $\cH_k$: it is the Beilinson--Drinfeld
coisson structure on the commutative $\mathcal{D}_X$-algebra
underlying $\cH_k$. The $\lambda$-bracket $\{J_\lambda J\} = k\lambda$
encodes the symplectic pairing on $V = \bC \cdot J$: the coefficient
$k$ of $\lambda$ is the level. This is the simplest
instance of the general principle that the chiral Koszul dual
$\cA^!_{\mathrm{ch}}$ of a chiral algebra $\cA$ is controlled by the
$\lambda$-bracket of its Beilinson--Drinfeld coisson structure,
as proved in Volume~I.
\end{remark}


% ================================================================
\subsection{Genus 1: curvature appears}
\label{subsec:rosetta-genus1}
\index{curvature!genus 1!Heisenberg}
\index{Heisenberg algebra!genus 1 curvature}
\index{Swiss-cheese operad!curved}
% ================================================================

At genus~$0$, the bar complex $(\barB^{\mathrm{ch}}(\cH_k),
d_{\barB})$ is an honest chain complex: $d_{\barB}^2 = 0$,
and the $E_1$ coalgebra structure is flat. At genus~$1$, the
situation changes qualitatively. The propagator on an elliptic
curve $E_\tau = \bC / (\Z + \Z\tau)$ is no longer single-valued:
the Weierstrass zeta function
\begin{equation}\label{eq:rosetta-elliptic-propagator}
G_\tau(z)
\;=\;
\zeta_\tau(z) \;-\; \frac{\pi^2}{3}\, E_2(\tau) \cdot z
\end{equation}
has $B$-cycle monodromy $G_\tau(z + \tau) - G_\tau(z) = -2\pi i$.
This monodromy, absent at genus~$0$, is the source of curvature.

\begin{theorem}[Curved $E_1$ coalgebra at genus~$1$;
\ClaimStatusProvedHere]
\label{thm:rosetta-curved}
\index{curved $E_1$ coalgebra!genus 1}
At genus $g = 1$, the bar complex $\barB^{(1)}(\cH_k)$ with:
\begin{enumerate}[label=\textup{(\roman*)}]
\item fiberwise differential $\dfib$ \textup{(}residues using
 the elliptic propagator $d\log E_\tau(z, w)$\textup{)},
\item coproduct $\Delta$ \textup{(}unchanged from genus~$0$\textup{)},
\end{enumerate}
satisfies:
\begin{enumerate}[label=\textup{(\alph*)}]
\item\label{item:rosetta-curved-delta}
 $\Delta$ is coassociative \textup{(}same proof as genus~$0$:
 the deconcatenation coproduct is purely combinatorial and
 does not depend on the propagator or the genus\textup{)};
\item\label{item:rosetta-curved-dsquared}
 $\dfib^{\,2} = k \cdot \omega_1$, where
 $\omega_1 = c_1(\mathbb{E}) \in H^2(\overline{\cM}_1)$
 is the first Chern class of the Hodge bundle;
\item\label{item:rosetta-curved-coder}
 $\dfib$ is \emph{not} a coderivation of $\Delta$: the
 curvature $\dfib^{\,2} = k\cdot\omega_1$ produces a
 factor-$2$ discrepancy at every interior splitting because
 $\omega_1$ contracts the closed-colour collision class
 against the same $\bR$-interval on both branches
 (Volume~I,
 Remark~\ref{V1-rem:sc-higher-genus}\textup{(ii)});
\item\label{item:rosetta-curved-corrected}
 the period-corrected differential
 $\Dg{1} = \dfib + \delta_{\mathrm{per}}$, where
 $\delta_{\mathrm{per}}$ is built from the Fay trisecant
 identity, satisfies $\Dg{1}^{\,2} = 0$ \emph{and} is a
 coderivation of $\Delta$ (Volume~I,
 Remark~\ref{V1-rem:sc-higher-genus}\textup{(iii)}).
\end{enumerate}
The $E_1$ dg coalgebra structure at genus~$1$ is therefore
carried by the period-corrected triple
$(\barB^{(1)}(\cH_k), \Dg{1}, \Delta)$, not by
$(\barB^{(1)}(\cH_k), \dfib, \Delta)$. The fibrewise
differential $\dfib$ records only the Hodge curvature class on
$\overline{\cM}_1$; the period correction restores both flatness
and the coderivation property simultaneously.
\end{theorem}

\begin{proof}
\ref{item:rosetta-curved-delta}:
The coproduct $\Delta$ is the tensor coalgebra structure,
defined by the ordering of tensor factors. It depends only on
the combinatorial data of the bar complex, not on the
propagator or the genus of the curve. The proof of
coassociativity is identical to the genus-$0$ case (Step~2 of
Theorem~\ref{thm:rosetta-swiss-cheese}).

\medskip
\ref{item:rosetta-curved-dsquared}:
We compute $\dfib^{\,2}$.
On $\FM_3(E_\tau)$, the differential $\dfib$ acts twice via
the elliptic propagator. The first application produces a
function $G_\tau(z_1 - z_2)$; the second transports this
function around the $B$-cycle of $E_\tau$. The
$B$-cycle monodromy of $G_\tau$ contributes a constant shift:
\begin{equation}\label{eq:rosetta-monodromy}
G_\tau(z + \tau) - G_\tau(z) = -2\pi i.
\end{equation}
When $\dfib$ acts a second time, the monodromy of the first
propagator interacts with the second propagator. The
double-pole OPE $J(z_1)\, J(z_2) \sim k/(z_1 - z_2)^2$
contributes a factor of~$k$. The combined effect is:
\begin{equation}\label{eq:rosetta-dsquared-computation}
\dfib^{\,2}\bigl[s^{-1}J \,|\, s^{-1}J \,|\, s^{-1}J\bigr]
\;=\;
k \cdot (-2\pi i)^2 \cdot
\left(
 \text{period integral over } E_\tau
\right)
\;=\;
k \cdot \omega_1,
\end{equation}
where the period integral, after pushforward to
$\overline{\cM}_1$, produces the Hodge class
$\omega_1 = c_1(\mathbb{E})$. The coefficient $k$ records
the Heisenberg level; the curvature class lives in
$H^2(\overline{\cM}_1)$, not in the coalgebra of bar elements.

\medskip
\ref{item:rosetta-curved-coder}:
We show that $\dfib$ fails the Leibniz rule for $\Delta$ at
interior splittings. Apply $\Delta\circ\dfib^{\,2}$ to the
length-three element
$[s^{-1}J\,|\,s^{-1}J\,|\,s^{-1}J]$ and split between the
second and third factor:
\[
\Delta_{2{,}3}\bigl(\dfib^{\,2}[s^{-1}J\,|\,s^{-1}J\,|\,s^{-1}J]\bigr)
\;=\;
k\cdot\omega_1\otimes [s^{-1}J]
\;+\;
[s^{-1}J\,|\,s^{-1}J]\otimes(k\cdot\omega_1).
\]
The Leibniz rule for $\dfib$ acting on the same element via
$\dfib\otimes\id + \id\otimes\dfib$ produces, at the same
splitting, the sum
\[
\bigl(\dfib\otimes\id + \id\otimes\dfib\bigr)^{2}\Delta_{2{,}3}
[s^{-1}J\,|\,s^{-1}J\,|\,s^{-1}J]
\;=\;
2\,k\cdot\omega_1\otimes [s^{-1}J]
\;+\;
2\,[s^{-1}J\,|\,s^{-1}J]\otimes(k\cdot\omega_1),
\]
because the Hodge class $\omega_1$ contracts the closed-colour
collision against the same $\bR$-interval on \emph{both}
branches of the splitting. The two sides differ by a factor
of two; $\dfib$ is therefore not a coderivation of~$\Delta$.
This is the genus-$1$ Heisenberg specialization of
Remark~\ref{V1-rem:sc-higher-genus}\textup{(ii)} of Volume~I.
The genus-$0$ argument fails because $\omega_0 = 0$, so the
discrepancy is invisible at the cusp.

\medskip
\ref{item:rosetta-curved-corrected}:
The corrected differential $\Dg{1} = \dfib + \delta_{\mathrm{per}}$
incorporates a period correction $\delta_{\mathrm{per}}$ that
compensates for the $B$-cycle monodromy. The period correction
is determined by the requirement $\Dg{1}^{\,2} = 0$: it must
satisfy
\begin{equation}\label{eq:rosetta-period-correction}
\delta_{\mathrm{per}}^{\,2}
\;+\;
\dfib \circ \delta_{\mathrm{per}}
\;+\;
\delta_{\mathrm{per}} \circ \dfib
\;=\;
-k \cdot \omega_1.
\end{equation}
The existence and uniqueness of $\delta_{\mathrm{per}}$ is the
Heisenberg specialization of the period-corrected differential
constructed in Volume~I; the Fay trisecant identity yields
both the square-zero relation
\eqref{eq:rosetta-period-correction} and the cancellation of
the factor-$2$ discrepancy from~(c) at every interior
splitting. After this cancellation $\Dg{1}$ is a genuine
coderivation of $\Delta$, and the curved $E_1$ dg
coalgebra structure persists at genus~$1$ as
$(\barB^{(1)}(\cH_k), \Dg{1}, \Delta)$. The period correction
couples the topological direction ($\bR$-ordering) to the Hodge
bundle $\mathbb{E}$ over $\overline{\cM}_1$: it is the
first place where the holomorphic and topological directions of the
$E_1$ coalgebra interact nontrivially.
\end{proof}

\begin{remark}[Physical meaning of curvature]
\label{rem:rosetta-curvature-physics}
\index{conformal anomaly!Heisenberg}
The curvature $\dfib^{\,2} = k \cdot \omega_1$ is the conformal
anomaly of the Heisenberg theory. At genus~$0$, the theory is
conformally invariant: $d_{\barB}^2 = 0$ and the partition function
is a constant. At genus~$1$, the torus $E_\tau$ has a modulus
$\tau \in \mathfrak{H}$, and the theory acquires a conformal anomaly
proportional to the level~$k$.

The anomaly lives in the holomorphic (closed-color) direction
and is invisible to the topological (open-color) direction:
$\Delta$ is coassociative at every genus. This is the
$E_1$ coalgebra incarnation of the principle that the conformal
anomaly is a \emph{holomorphic} obstruction. The central
charge $c = 1$ of the Heisenberg algebra (one free boson)
enters through the modular characteristic $\kappa(\cH_k) = k$
computed in Volume~I: the curvature
coefficient is the level, and the level is the basic scalar
invariant of the Koszul pair $(\cH_k, \cH_k^!)$.
\end{remark}

\begin{remark}[Genus~$0$ as the flat limit]
\label{rem:rosetta-flat-limit}
The genus-$0$ theory is the \emph{flat} limit of the genus-$1$
theory: as $\tau \to i\infty$ (the cusp of the modular curve),
the elliptic curve $E_\tau$ degenerates to a nodal rational curve,
the propagator $G_\tau(z) \to (z - w)^{-1}$ loses its monodromy,
and the curvature $\dfib^{\,2} = k \cdot \omega_1 \to 0$. The
$E_1$ coalgebra structure specializes from curved to flat. This
degeneration is the bar-complex avatar of the $q$-expansion:
the genus-$1$ bar complex is a deformation of the genus-$0$ bar
complex by the nome $q = e^{2\pi i \tau}$, and the curvature
is the leading obstruction to extending the genus-$0$ theory to
genus~$1$.
\end{remark}


% ================================================================
\subsection{The bridge: one object, two readings}
\label{subsec:rosetta-bridge}
\index{Rosetta Stone!dictionary}
% ================================================================

The Heisenberg bar complex is a single mathematical object (an
$E_1$ curved dg coassociative coalgebra) but it admits
two simultaneous readings: one algebraic (Volume~I), one physical
(Volume~II). The following table records the correspondence.

\begin{center}
\small
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{@{}l@{\;\;}l@{\;\;}l@{}}
\textbf{Bar complex} & \textbf{Vol.\@ I reading} &
 \textbf{Vol.\@ II reading} \\
\hline
$d_{\barB}$
 & bar differential
 & closed-color (holomorphic) \\[2pt]
$\Delta$
 & coalgebra coproduct
 & open-color (topological) \\[2pt]
$d_{\barB}^{\,2} = 0$
 & Arnold relations
 & $\Ainf$ identity ($n = 2$) \\[2pt]
$\Delta$ coassociative
 & cofree coalgebra
 & $\Eone$-coalgebra \\[2pt]
$d_{\barB}$ coderivation of $\Delta$
 & bar is dg coalgebra
 & color compatibility \\[2pt]
$m_2$ from bar
 & Koszul dual OPE
 & $\lambda$-bracket / PVA \\[2pt]
$m_k = 0$ for $k \geq 3$
 & bar $A_\infty$-formality (Koszulness)
 & SC-formality \\[2pt]
$\dfib^{\,2} = k \cdot \omega_1$
 & curvature (Thm.\@ C)
 & curved $E_1$ coalgebra \\[2pt]
$\kappa(\cH_k) = k$
 & modular characteristic (Thm.\@ D)
 & conformal anomaly \\[2pt]
$H^{\bullet}(\barB) = \bC \oplus \bC c_k$
 & bar cohomology (Thm.\@ A)
 & Hochschild (Thm.\@ H) \\[2pt]
$\rho_n^{\mathrm{HT}} = \rho_n^{\mathrm{KZ}}$
 & monodromy identification
 & $\cC_{\mathrm{line}}^{\mathrm{red}} \simeq \mathrm{Rep}_q$
 (Thm~\ref{thm:affine-monodromy-identification})
\end{tabular}
\end{center}

Each row is a theorem on the left and a physical identification on
the right.

\begin{proposition}[Complementarity for the Heisenberg algebra;
\ClaimStatusProvedElsewhere]
\label{prop:rosetta-complementarity}
\index{complementarity!Heisenberg}
The Heisenberg algebra and its Koszul dual
$\cH_k^! = \mathrm{Sym}^{\mathrm{ch}}(V^*)$,
as computed in Volume~I,
satisfy:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\kappa(\cH_k) + \kappa(\cH_k^!) = 0$:
 the modular characteristics are opposite;
\item $\mathbf{Q}_1(\cH_k) \oplus \mathbf{Q}_1(\cH_k^!)
 = H^{\bullet}(\overline{\cM}_1,\, \mathcal{Z}_{\cH_k})$:
 the quantum corrections are complementary Lagrangians.
\end{enumerate}
This is Theorem~C
\textup{(}the quantum complementarity theorem of Volume~I\textup{)}
specialized to the Heisenberg case. The curvature coefficient
$\kappa(\cH_k) = k$ has opposite sign in the dual:
$\kappa(\cH_k^!) = -k$, reflecting the opposite $B$-cycle
monodromy of the dual propagator.
\end{proposition}

\begin{remark}[$bc$--$\beta\gamma$ Koszul duality and the statistics exchange]
\label{rem:rosetta-bc-betagamma-koszul}
\index{Koszul duality!bc-betagamma@$bc$--$\beta\gamma$}%
\index{complementarity!free fields}%
The Heisenberg complementarity $K(\cH_k) = 0$ is the first
instance of a universal pattern for all free-field chiral
algebras. The $bc$ ghost system of conformal weights
$(\lambda, 1-\lambda)$ and the $\beta\gamma$ system of the same
weights are Koszul dual to each other:
\[
bc_\lambda^! \;=\; \beta\gamma_\lambda,
\qquad
\beta\gamma_\lambda^! \;=\; bc_\lambda.
\]
The mechanism is the chiral incarnation of classical
$\mathrm{Ext}/\mathrm{Sym}$ duality: $bc_\lambda$ is the
chiral exterior algebra $\bigwedge^{\mathrm{ch}}(V)$ on
$V = \bC b \oplus \bC c$ (fermionic), and its Koszul dual is the
chiral symmetric algebra $\mathrm{Sym}^{\mathrm{ch}}(V^*)$
(bosonic), which is precisely the $\beta\gamma$ system. The bar
complex has $m_2$ only (simple-pole OPE), confirming that both
systems are Koszul. Koszul duality exchanges statistics while
preserving conformal weights; it does \emph{not} exchange spins
$\lambda \mapsto 1 - \lambda$ (that is a relabelling, not a
dualisation).

The complementarity constant vanishes:
$K(bc_\lambda) = c_{bc}(\lambda) + c_{\beta\gamma}(\lambda)
= -2(6\lambda^2 - 6\lambda + 1) + 2(6\lambda^2 - 6\lambda + 1)
= 0$
for all $\lambda$. This extends to tensor products: for mutually
regular Koszul algebras,
$(\cA \otimes \cB)^! \simeq \cA^! \otimes \cB^!$,
so $K = 0$ for any tensor product of Heisenberg, $bc$, and
$\beta\gamma$ systems.

At the string-theory point $\lambda = 2$, $\mu = 3/2$: the Koszul
dual of the reparametrisation ghost $bc_2$ ($c = -26$) is the
bosonic spin-$2$ system $\beta\gamma_2$ ($c = +26$). A spin-$2$
boson is a symmetric tensor field, a graviton. The Koszul dual of
the ghost is, morally, a graviton: the
$\bigwedge \leftrightarrow \mathrm{Sym}$ exchange relates forms
(antisymmetric, diffeomorphism ghosts) to jets (symmetric, metric
fluctuations). This is the free-field shadow of the phenomenon that
Koszul duality of the Virasoro algebra encodes three-dimensional
quantum gravity. The crucial difference: for Virasoro,
$K = 13 \neq 0$, because the DS reduction that produces
Virasoro from affine KM is nonlinear in the level. The free-field
case $K = 0$ is the unique setting where Koszul complementarity is
a strict sign flip.
\end{remark}

\begin{remark}[The modular characteristic is the level]
\label{rem:rosetta-kappa-is-k}
\index{modular characteristic!Heisenberg}
For the Heisenberg algebra, the modular characteristic
$\kappa(\cH_k) = k$ \emph{is} the level. This is the simplest
instance of the general relation: $\kappa$ measures the scalar
component of the genus-$1$ curvature
(as computed in Volume~I), and for a single
free boson with propagator $k/(z - w)^2$, the curvature is
$k \cdot \omega_1$ with no further structure. The $\hat{A}$-genus
generating function for the Heisenberg genus tower is
\begin{equation}\label{eq:rosetta-ahat}
\hat{A}_{\cH_k}(q)
\;=\;
\prod_{n=1}^{\infty}\,
\frac{n\, q^{n/2}}{e^{n k q^n / 2} - e^{-n k q^n / 2}}
\end{equation}
which, at $k = 1$, specializes to the standard $\hat{A}$-series.
\end{remark}

\begin{proposition}[Bar cohomology and Hochschild cohomology;
\ClaimStatusProvedElsewhere]
\label{prop:rosetta-bar-hochschild}
\index{bar cohomology!Heisenberg}
\index{Hochschild cohomology!Heisenberg}
The bar cohomology of $\cH_k$ at genus~$0$ is
\begin{equation}\label{eq:rosetta-bar-cohomology}
H^n(\barB^{\mathrm{ch}}(\cH_k))
\;=\;
\begin{cases}
\bC & n = 0, \\
0 & n = 1, \\
\bC \cdot c_k & n = 2, \\
0 & n \geq 3,
\end{cases}
\end{equation}
recovering the central extension class $c_k \in H^2$
computed on the Heisenberg bar complex in Volume~I.
This is the chiral Hochschild cohomology of Volume~II:
$\mathrm{CH}^{\bullet}(\cH_k, \cH_k) \simeq
H^{\bullet}(\barB^{\mathrm{ch}}(\cH_k))$, identifying the
central charge as a Hochschild class.
\end{proposition}

\begin{remark}[The Rosetta Stone principle]
\label{rem:rosetta-principle}
\index{Rosetta Stone!principle}
The Heisenberg algebra is the simplest chiral algebra, but it is
not trivial: it carries curvature ($\dfib^{\,2} = k \cdot \omega_1$),
complementarity ($\kappa(\cH_k) + \kappa(\cH_k^!) = 0$),
the $\hat{A}$-genus, and the full modular structure.
Every feature of the general theory is already present.

The Rosetta Stone is the principle that these features have two
simultaneous readings, algebraic (Volume~I) and physical
(Volume~II), unified by the Swiss-cheese structure of a single
dg coalgebra. The bar differential~$d_{\barB}$ is the
holomorphic side; the coproduct~$\Delta$ is the topological
side; their interaction
$\Delta \circ d_{\barB} = (d_{\barB} \otimes \id
+ \id \otimes d_{\barB}) \circ \Delta$
is the content of the 3d theory on $\bC \times \bR$. At genus~$0$,
both readings are equivalent and either suffices. At genus~$1$
and beyond, the curvature couples the two readings, and the full
Swiss-cheese structure becomes necessary.

The Heisenberg bar complex is a single coalgebra that unifies
Koszul duality with holomorphic--topological factorization
(Theorem~\ref{thm:steinberg-presentation}).
The Rosetta Stone is the dictionary that makes this analogy precise.
\end{remark}

% ================================================================
\subsection{The Heisenberg 3d MC element}
\label{subsec:rosetta-3d-mc}
\index{universal MC element!3d!Heisenberg}
\index{Heisenberg algebra!3d MC element}
% ================================================================

The Swiss-cheese convolution $L_\infty$-algebra
$\gSC_T$ (Definition~\ref{def:sc-convolution}) and its canonical
MC element $\alpha_T$ (Theorem~\ref{thm:3d-universal-mc}) specialise
to the Heisenberg as follows.

\begin{theorem}[Heisenberg 3d MC element; \ClaimStatusProvedHere]
\label{thm:rosetta-3d-mc}
For the Heisenberg theory $T = (\cH_k, \cH_{-k}\text{-mod})$ on
$\C \times \R_{\ge 0}$, the Swiss-cheese convolution algebra
$\gSC_T$ is abelian: $[\alpha,\beta] = 0$ for all
$\alpha, \beta \in \gSC_T$. The MC element is
\begin{equation}\label{eq:alpha-heisenberg}
\alpha_{\cH_k}
\;=\;
\alpha_{\mathrm{cl}}
\;+\;
\hbar\,\alpha_{\mathrm{loop}},
\end{equation}
where the two components are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Closed-colour, genus-$0$ component:}
 $\alpha_{\mathrm{cl}}$ is the binary operation
 $m_2(J,J;\lambda) = k\lambda$ on $\FM_2(\C)$, encoding the
 double-pole OPE\@. No higher closed vertices contribute
 ($m_k = 0$ for $k \ge 3$, by
 Proposition~\textup{\ref{prop:rosetta-heisenberg-mk}}).
\item \emph{Closed-colour, genus-$1$ component:}
 $\alpha_{\mathrm{loop}} = k \cdot \eta \otimes \Lambda$ is the
 genus-$1$ self-loop correction from the unique graph
 $\Gamma_{\mathrm{irr}}$ \textup{(}one vertex of genus~$0$ with
 one self-edge\textup{)}. The BV operator $\Delta$ traces the
 level $\langle J, J \rangle = k$; the boundary class
 $[\delta_{\mathrm{irr}}]$ gives
 $\lambda_1 = \tfrac{1}{12}\delta_{\mathrm{irr}}$.
\end{enumerate}
There is no mixed-colour or open-colour MC contribution: the
abelian structure forces all mixed and open graph sums to vanish.
\end{theorem}

\begin{proof}
\emph{Abelianity.}\enspace
The Lie bracket on $\gSC_T$ is the operadic composition bracket,
which requires at least one nontrivial vertex operation. For the
Heisenberg, $m_k = 0$ for $k \ge 3$ and the simple-pole OPE
residue $J_{(0)}J = 0$ vanishes. Every composition of two graph
contributions involves at least one operation $m_k$ with $k \ge 3$
or a simple-pole insertion, hence vanishes. The bracket is
identically zero.

\emph{Closed-colour component.}\enspace
The only contributing two-coloured trees with all vertices closed
are those with each vertex labelled by $m_2$ (the binary OPE).
Stability $2g(v) - 2 + \mathrm{val}(v) > 0$ with
$\mathrm{val}(v) = 2$ and $g(v) = 0$ fails ($2 \cdot 0 - 2 + 2 = 0
\not> 0$), so at genus~$0$ no nontrivial tree contributes
beyond the binary operation itself.
The element $\alpha_{\mathrm{cl}}$ is the identity
\[
\alpha_{\mathrm{cl}}
\;=\;
m_2 \;\in\;
\Hom\bigl(\mathbf{B}^{(0,2)}(\SCop),\;
\End_{\cH_k}\bigr),
\]
encoding the double-pole OPE at the unique two-point closed
vertex. Its MC equation $D\alpha_{\mathrm{cl}} +
\tfrac{1}{2}[\alpha_{\mathrm{cl}}, \alpha_{\mathrm{cl}}] = 0$
reduces to $d_{\barB}^2 = 0$ (the Arnold relation, verified in
Theorem~\ref{thm:rosetta-swiss-cheese}, Step~1).

\emph{Genus-$1$ component.}\enspace
At genus~$1$, the unique graph is $\Gamma_{\mathrm{irr}}$: one
vertex of genus~$0$ with one self-edge and one half-edge. The
graph contribution is $\hbar \cdot \Delta$, where
$\Delta(sJ) = \langle J, J \rangle \cdot s\mathbf{1} = k \cdot
s\mathbf{1}$. The chain $W_{\Gamma_{\mathrm{irr}}} =
[\delta_{\mathrm{irr}}]$ gives the Hodge class
$\lambda_1 = \tfrac{1}{12}\delta_{\mathrm{irr}}$. Therefore
$\alpha_{\mathrm{loop}} = k \cdot \eta \otimes \Lambda$, and the
total MC element is $\alpha_{\cH_k} = \alpha_{\mathrm{cl}} +
\hbar\,k \cdot \eta \otimes \Lambda$.

\emph{Mixed and open colours.}\enspace
A mixed-colour graph has at least one open vertex (labelled by an
$E_1$-operation on line modules) and at least one closed vertex.
For the Heisenberg, line modules are modules over
$Y(\mathfrak{u}(1)) \simeq \cH_{-k}$, the abelian open-colour
Koszul dual. The
Heisenberg module category is semisimple: every module is a direct
sum of Fock spaces $\mathcal{F}_\mu$, and the $E_1$-operations on
Fock modules are scalar (the vertex operators are abelian). Every
mixed graph contribution is therefore proportional to a product of
scalars, and the structure maps of $\gSC_T$ annihilate them by the
coderivation property applied to the trivial $m_k = 0$ ($k \ge 3$)
at the closed vertices. The open-colour contribution vanishes
for the same reason.
\end{proof}

The six projections of Proposition~\ref{prop:alpha-projections}
specialise as follows.

\begin{corollary}[Heisenberg projections; \ClaimStatusProvedHere]
\label{cor:rosetta-heisenberg-projections}
For the Heisenberg theory:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Closed face} $=$ the boundary $\Ainf$ algebra $\cH_k$
 with $m_2(J,J;\lambda) = k\lambda$ and $m_{k \ge 3} = 0$.
\item \emph{Open face} $=$ the semisimple Fock category with
 trivial open-colour line-sector operations.
\item \emph{Spectral $R$-matrix}: $R(z) = e^{k\hbar/z}$, the
 abelian braiding. The Yang--Baxter equation is satisfied
 trivially \textup{(}$R$ is scalar\textup{)}.
\item \emph{Bulk-to-boundary}: $\Abulk = \Zder(\cH_k) = \cH_k$
 \textup{(}abelian algebras are their own derived centers\textup{)}.
\item \emph{Genus face}: $\Theta_{\cH_k} = k \cdot \eta \otimes
 \Lambda$, recovering Vol~I\@.
\item \emph{PVA}: $\{J_\lambda J\} = k\lambda$, the rank-$1$ PVA
 bracket.
\end{enumerate}
\end{corollary}

\begin{proof}
(i)--(ii): Propositions~\ref{prop:rosetta-heisenberg-mk}
and~\ref{prop:rosetta-operations}.
(iii): The spectral braiding of two Fock modules $\mathcal{F}_{\mu_1}$,
$\mathcal{F}_{\mu_2}$ at spectral separation~$z$ is
$R_{\mu_1,\mu_2}(z) = e^{k\mu_1\mu_2\hbar/z}$. For the fundamental
module ($\mu = 1$): $R(z) = e^{k\hbar/z}$.
(iv): $\cH_k$ is commutative ($J_{(0)}J = 0$), so
$\HH^0(\cH_k) = \cH_k$ and the derived center is the algebra
itself.
(v): Restriction of $\alpha_{\cH_k}$ to the closed genus-expanded
sector gives $\alpha_{\mathrm{cl}} + \hbar\,\alpha_{\mathrm{loop}}
= m_2 + \hbar\,k\cdot\eta\otimes\Lambda = \Theta_{\cH_k}$.
(vi): $m_2(J,J;\lambda) = k\lambda$ descends to the PVA bracket
by the descent theorem
(Theorem~\ref{thm:cohomology_PVA}).
\end{proof}

\begin{computation}[The Heisenberg hydrogen atom; \ClaimStatusProvedHere]%
\label{comp:heisenberg-hydrogen-atom}%
\index{Heisenberg algebra!hydrogen atom|textbf}%
\index{hydrogen atom!Heisenberg bar complex}%
The Heisenberg algebra is the hydrogen atom of the bar-complex
programme: all data reduce to a single scalar~$k$ and all
higher complexity vanishes. We collect the complete
package in one place.

\smallskip
\noindent
\emph{Operations.}
The single nonvanishing operation is
$m_2(J,J;\lambda) = k\lambda$
(Proposition~\ref{prop:rosetta-heisenberg-mk}).
All $m_k = 0$ for $k \ge 3$.
The depth spectrum is $\{1\}$: the bar
cogenerators live in degree~$2$ only, and
$\barBch(\cH_k)$ is cogenerated in degree~$1$
with the single relation $d_{\barB}[s^{-1}J\,|\,s^{-1}J] = k$.
The weight-depth identity $w + d = n - 1$ (Theorem~\ref{thm:gap-migration}(i)) is trivially satisfied: the unique monomial has $w = 0$, $d = 1$, $n = 2$.
The Swiss-cheese structure is SC-formal: the higher
coherences of $W(\SCchtop)$ are trivially satisfied.

\smallskip
\noindent
\emph{$R$-matrix.}
The collision residue is $r^{\mathrm{coll}}(z) = k/z$
(the $d\log$ kernel absorbs one power from the
double-pole OPE: $k/(z-w)^2 \cdot d\log(z-w)
\leadsto k/z$).
The connection on $\Conf_2^{\mathrm{ord}}(\C)$ is
$\nabla = d - k \cdot d\log(z)$,
and the monodromy is $\exp(-2\pi i k)$.
The spectral $R$-matrix on modules is
\begin{equation}\label{eq:heisenberg-hydrogen-R}
R(z) \;=\; e^{k\hbar/z},
\end{equation}
confirming
Corollary~\ref{cor:rosetta-heisenberg-projections}(iii).
The Yang--Baxter equation is trivially satisfied
($R$ is scalar). The braiding is nontrivial
but derived from the local OPE: tier~(ii) of the
three-tier picture
(Section~\ref{subsec:ordered-three-tier}).

\smallskip
\noindent
\emph{Genus-$1$ $r$-matrix.}
On $E_\tau$, the rational propagator $1/z$ is replaced by
$\zeta(z|\tau)$. Since $c_0 = J_{(0)}J = 0$
(no simple pole), the quasi-periodic part of
$\zeta(z|\tau)$ drops out of the $r$-matrix:
\begin{equation}\label{eq:heisenberg-hydrogen-genus1-r}
r^{(1)}_{\cH_k}(z)
\;=\;
k \cdot \wp(z|\tau)
\;=\;
k\biggl(\frac{1}{z^2}
 - \sum_{n=1}^{\infty}(2n+1)\, G_{2n+2}(\tau)\, z^{2n}
\biggr).
\end{equation}
The genus-$1$ correction is the Eisenstein-weighted series
$-k\bigl(3G_4(\tau)\,z^2 + 5G_6(\tau)\,z^4 + \cdots\bigr)$.
The $r$-matrix is doubly periodic on $E_\tau$: no
$B$-cycle monodromy. Curvature and braiding are
decoupled.

\smallskip
\noindent
\emph{Complete MC element.}
The total MC element (Theorem~\ref{thm:rosetta-3d-mc}) is
\begin{equation}\label{eq:heisenberg-hydrogen-theta}
\Theta_{\cH_k}
\;=\;
k\lambda
\;+\;
k \sum_{g \ge 1} \hbar^{2g}\, \lambda_g^{\mathrm{FP}} \cdot \omega_g,
\end{equation}
purely curvature-driven: the genus tower contains
no shadow corrections because $m_n = 0$ for all $n \ge 3$. The free energy is $F^{\mathrm{tot}} = k \cdot (\hbar/2)/\sin(\hbar/2)$
(Theorem~\ref{thm:ahat-lagrangian}).

\smallskip
\noindent
\emph{Euler characteristic.}
The genus-$1$ partition function
$Z_1(\cH_k) = \eta(\tau)^{-k}$
(Computation~\ref{comp:heisenberg-line-bundle})
recovers the Dedekind eta function. The $q$-expansion
$\eta(q)^{-1} = q^{-1/24}\prod_{n=1}^{\infty}(1-q^n)^{-1}$
is the generating function for partitions (the
pentagonal theorem). The Heisenberg bar complex,
through the genus tower, knows the combinatorics of
integer partitions.

\smallskip
\noindent
\emph{Koszul dual.}
$\cH_k^! = \mathrm{Sym}^{\mathrm{ch}}(V^*)$, the
chiral symmetric algebra on the dual.
The Poincar\'{e} series of the bar complex is
$P(t) = 1 + t$ (one cogenerator in degree~$1$).
\end{computation}

\begin{computation}[Complete $E_1$ ordered shadow for $\cH_k$;
\ClaimStatusProvedHere]%
\label{comp:heisenberg-e1-ordered-shadow}%
\index{Heisenberg algebra!E1 ordered shadow@$E_1$ ordered shadow|textbf}%
\index{ordered shadow!Heisenberg|textbf}%
\index{hydrogen atom!E1 ordered shadow@$E_1$ ordered shadow}%
The Heisenberg algebra is the hydrogen atom of the $E_1$ ordered
shadow programme: all data reduce to a single scalar~$k$, the shadow
tower terminates at degree~$2$, and the entire ordered structure is
computed in closed form at every genus. We assemble the complete
package.

\smallskip
\noindent
\emph{(1) The ordered shadow polynomial.}
The single nonvanishing operation is
\begin{equation}\label{eq:e1-shadow-m2}
m_2(J,J;\lambda) \;=\; k\lambda,
\end{equation}
valid for all $k \in \bC$. The spectral parameter $\lambda$ is the
Fourier dual of the collision coordinate $z_1 - z_2$ on
$\FM_2(\bC)$, and records the weight of the residue: the double pole
$k/(z_1 - z_2)^2$ produces $k\lambda$ via the substitution
$(z_1 - z_2)^{-n-1} \leftrightarrow \lambda^{(n)}/n!$. The shadow
tower terminates: $m_k = 0$ for all $k \ge 3$
(Proposition~\ref{prop:rosetta-heisenberg-mk}). The depth spectrum is
$\{1\}$: the shadow depth is $r_{\max} = 2$ (class~G, Gaussian),
bar cogenerators live in degree~$2$ only, and the weight-depth
identity $w + d = n - 1$ is satisfied trivially ($w = 0$, $d = 1$,
$n = 2$).

\smallskip
\noindent
\emph{(2) The $E_1$ content: spectral ordering.}
The spectral parameter $\lambda$ in $m_2(J,J;\lambda) = k\lambda$
carries the ordering information of the $E_1$-structure. On the
ordered bar complex $\bar{B}^{\mathrm{ch,ord}}(\cH_k)$, the
differential at tensor degree~$2$ is
\[
d_{\mathrm{res}}[s^{-1}J \,|\, s^{-1}J]
\;=\; k,
\]
with the ordering $z_1 < z_2$ on $\bR$ recorded in the tensor
sequence $s^{-1}J \otimes s^{-1}J$ (the first factor corresponds to
the earlier point). The parameter $\lambda$ is the \emph{directed}
spectral flow: under the transposition $\sigma_{12}$ that exchanges
the two points, $\lambda \mapsto -\lambda$, and
$m_2(J,J;-\lambda) = -k\lambda = -m_2(J,J;\lambda)$. The
antisymmetry in $\lambda$ reflects the Koszul sign of the
desuspension: $s^{-1}J$ has odd cohomological degree.

The ordered bar complex has generating function
(Computation~\ref{comp:heisenberg-dim-table}):
\[
\sum_{n,w \ge 1}
\dim\bar{B}^{\mathrm{ch,ord}}_{n,w}\; t^n q^w
\;=\;
\frac{tq(1-q)}{1-q-tq},
\]
with $\dim\bar{B}^{\mathrm{ch,ord}}_{n,w} = \binom{w-1}{n-1}$
(compositions of $w$ into $n$ positive parts).

\smallskip
\noindent
\emph{(3) The $R$-matrix: Taylor expansion to order~$50$.}
The collision residue is $r^{\mathrm{coll}}(z) = k/z$ (the
$d\log$ kernel absorbs one power from the double-pole OPE:
$k/(z-w)^2 \cdot d\log(z-w) \leadsto k/z$). The
connection on $\Conf_2^{\mathrm{ord}}(\bC)$ is
$\nabla = d - k\, d\log(z)$, and the monodromy around
the generator $\gamma$ is $\exp(-2\pi i k)$. The spectral
$R$-matrix on modules is
\begin{equation}\label{eq:e1-shadow-R}
R(z) \;=\; e^{k\hbar/z}
\;=\;
\sum_{n=0}^{\infty} \frac{(k\hbar)^n}{n!\, z^n}.
\end{equation}
This is the abelian braiding: the Yang--Baxter equation
$R_{12}R_{13}R_{23} = R_{23}R_{13}R_{12}$ is trivially satisfied
because $R$ is a scalar (all factors commute). The Taylor
expansion to order~$50$ in $u = 1/z$:
\begin{align}\label{eq:e1-R-expansion-50}
R(z) \;&=\;
1 + k\hbar\, u + \tfrac{k^2\hbar^2}{2}\, u^2
+ \tfrac{k^3\hbar^3}{6}\, u^3
+ \tfrac{k^4\hbar^4}{24}\, u^4
+ \tfrac{k^5\hbar^5}{120}\, u^5
\notag\\
&\quad
+ \tfrac{k^6\hbar^6}{720}\, u^6
+ \tfrac{k^7\hbar^7}{5040}\, u^7
+ \tfrac{k^8\hbar^8}{40320}\, u^8
+ \tfrac{k^9\hbar^9}{362880}\, u^9
+ \tfrac{k^{10}\hbar^{10}}{3628800}\, u^{10}
\notag\\
&\quad + \cdots
+ \tfrac{(k\hbar)^n}{n!}\, u^n + \cdots
+ \tfrac{(k\hbar)^{50}}{50!}\, u^{50}
+ O(u^{51}),
\end{align}
with $u = 1/z$ and the general coefficient
$(k\hbar)^n/n!$. At $k = 1$, $\hbar = 1$:
\[
R(z)\big|_{k=\hbar=1}
\;=\;
e^{1/z}
\;=\;
1 + \frac{1}{z} + \frac{1}{2z^2}
+ \frac{1}{6z^3} + \frac{1}{24z^4}
+ \frac{1}{120z^5} + \cdots.
\]
The $50$th coefficient is $1/50! \approx 3.29 \times 10^{-65}$:
the series converges faster than any power, confirming that
the Heisenberg $R$-matrix is an entire function of $1/z$.

The three-tier placement
(Section~\ref{subsec:ordered-three-tier}): $\cH_k$ is
tier~(ii): the $R$-matrix is nontrivial but \emph{derived}
from the local OPE $J(z)J(w) \sim k/(z-w)^2$ via the
monodromy of the flat connection on $\Conf_2^{\mathrm{ord}}(\bC)$.
The descent $\bar{B}^{\mathrm{ch,ord}} \to \barBch$ is
$R$-matrix twisted
(Proposition~\ref{prop:r-matrix-descent}), but since
$R$ is scalar, the twist amounts to a phase and the two
complexes carry the same cohomological information.

\smallskip
\noindent
\emph{(4) Genus-$1$ $E_1$ shadow.}
At genus~$1$, the rational propagator $1/z$ is replaced by the
elliptic propagator $G_\tau(z) = \zeta(z|\tau) - \tfrac{\pi^2}{3}
E_2(\tau)\cdot z$ on $E_\tau = \bC/(\Z + \Z\tau)$.
The genus-$1$ binary operation acquires an Eisenstein correction:
\begin{equation}\label{eq:e1-shadow-genus1-m2}
m_2^{(1)}(J,J;\lambda;\tau)
\;=\;
k\lambda
\;-\;
\frac{\pi^2 k}{3}\, E_2(\tau)\, \lambda.
\end{equation}
The correction $-(\pi^2 k/3)\, E_2(\tau)\, \lambda$ arises from
the regularization of the elliptic propagator: the Weierstrass
$\zeta$-function $\zeta(z|\tau)$ has quasi-periodicity
$\zeta(z+\tau|\tau) - \zeta(z|\tau) = -2\pi i + 2\eta_\tau$,
and the subtraction $-(\pi^2/3)\, E_2(\tau)\cdot z$ renders $G_\tau$
with monodromy $-2\pi i$
(equation~\eqref{eq:rosetta-monodromy}). The Eisenstein series
\begin{equation}\label{eq:e2-expansion}
E_2(\tau)
\;=\;
1 - 24\sum_{n=1}^{\infty} \sigma_1(n)\, q^n
\;=\;
1 - 24q - 72q^2 - 96q^3 - 168q^4 - 144q^5 - \cdots
\end{equation}
(with $q = e^{2\pi i \tau}$ and $\sigma_1(n) = \sum_{d|n} d$)
encodes the genus-$1$ deformation of the Heisenberg shadow.

The genus-$1$ $r$-matrix, from
equation~\eqref{eq:heisenberg-hydrogen-genus1-r}, is
\begin{equation}\label{eq:e1-genus1-r}
r^{(1)}_{\cH_k}(z)
\;=\;
k\cdot\wp(z|\tau)
\;=\;
k\biggl(
\frac{1}{z^2}
- \sum_{n=1}^{\infty}(2n+1)\, G_{2n+2}(\tau)\, z^{2n}
\biggr),
\end{equation}
where $\wp$ is the Weierstrass elliptic function and
$G_{2n+2}(\tau) = \sum_{\substack{(m,n) \neq (0,0)}}
(m + n\tau)^{-(2n+2)}$ are the Eisenstein series. The
key structural fact: since $c_0 = J_{(0)}J = 0$ (no simple pole),
the $r$-matrix is the Weierstrass $\wp$-function, which is
\emph{doubly periodic} on $E_\tau$, with no $B$-cycle monodromy.
Curvature and braiding decouple
(Theorem~\ref{thm:higher-genus-spectral-dichotomy}\ref{item:genus-g-decoupling}).
This is the simplest instance of the decoupling
regime: the Heisenberg is the unique standard family with $c_0 = 0$.

The genus-$1$ $R$-matrix is therefore
\begin{equation}\label{eq:e1-genus1-R}
R^{(1)}(z;\tau)
\;=\;
\exp\bigl(k\hbar\cdot\wp(z|\tau)\bigr)
\;=\;
\exp\biggl(
k\hbar\Bigl(
\frac{1}{z^2}
- 3G_4(\tau)\, z^2
- 5G_6(\tau)\, z^4
- \cdots
\Bigr)
\biggr),
\end{equation}
a doubly periodic meromorphic function on $E_\tau$ (with
an essential singularity at $z = 0$).

\smallskip
\noindent
\emph{(5) Genus-$2$ $E_1$ shadow: the Bergman kernel replacement.}
At genus~$g \ge 2$, the propagator on $\Sigma_g$ is the abelian
differential of the third kind $f(z,w) = \partial_z \log E(z,w)$,
where $E(z,w)$ is the Szeg\H{o} prime form. The genus-$g$
collision residue for $\cH_k$ is
(Theorem~\ref{thm:higher-genus-spectral-dichotomy}):
\begin{equation}\label{eq:e1-genus-g-r}
r^{(\Sigma_g)}_{\cH_k}(z,w)
\;=\;
k \cdot B(z,w),
\end{equation}
where $B(z,w) = \partial_z \partial_w \log E(z,w)$ is the
Bergman kernel, the unique symmetric bidifferential on
$\Sigma_g \times \Sigma_g$ with a double pole on the diagonal
and no other singularities. Since $c_0 = 0$, the zeroth-pole
term $c_0 \cdot f(z,w)$ in the general formula
\eqref{eq:genus-g-r-matrix} vanishes, and only the Bergman
kernel term survives. The $B$-cycle monodromy vanishes
(equation~\eqref{eq:genus-g-r-monodromy} with $c_0 = 0$):
the genus-$g$ $r$-matrix for $\cH_k$ is a globally meromorphic
bidifferential on $\Sigma_g \times \Sigma_g$ at every genus.

At genus~$2$ specifically, the Bergman kernel on a genus-$2$ curve
$\Sigma_2$ with period matrix $\Omega = \bigl(\begin{smallmatrix}
\tau_1 & \tau_{12} \\ \tau_{12} & \tau_2
\end{smallmatrix}\bigr)$ is
\[
B(z,w)
\;=\;
\frac{1}{(z-w)^2}
\;+\;
\sum_{i,j=1}^{2}
\bigl(\mathrm{Im}\,\Omega\bigr)^{-1}_{ij}\;
\omega_i(z)\,\omega_j(w)
\;+\;
(\text{higher-order diagonal corrections}),
\]
and the genus-$2$ Heisenberg $r$-matrix is $r^{(2)} = k \cdot B$.
The genus-$2$ $R$-matrix is $R^{(2)}(z,w) = \exp(k\hbar\cdot B(z,w))$,
again globally meromorphic (no $B$-cycle monodromy). The genus tower
is $F_g = k \cdot \lambda_g^{\mathrm{FP}}$ at all genera (Theorem~\ref{thm:ahat-lagrangian}), with the free energy
$F^{\mathrm{tot}} = k \cdot (\hbar/2)/\sin(\hbar/2)$.

\smallskip
\noindent
\emph{(6) The Euler-eta and pentagonal verification.}
The genus-$1$ partition function
$Z_1(\cH_k) = \eta(\tau)^{-k}$
(Computation~\ref{comp:heisenberg-line-bundle}) gives, at $k = 1$:
\begin{equation}\label{eq:e1-euler-eta}
\eta(q)
\;=\;
q^{1/24}\prod_{n=1}^{\infty}(1 - q^n)
\;=\;
q^{1/24}\sum_{n=-\infty}^{\infty}(-1)^n\, q^{n(3n-1)/2},
\end{equation}
where the last equality is Euler's pentagonal theorem. The
pentagonal numbers $\omega(n) = n(3n-1)/2$ for $n \in \Z$ are
\begin{align}\label{eq:pentagonal-numbers}
&n = 0:\; 0, \quad
n = 1:\; 1, \quad
n = -1:\; 2, \quad
n = 2:\; 5, \quad
n = -2:\; 7,
\notag\\
&n = 3:\; 12, \quad
n = -3:\; 15, \quad
n = 4:\; 22, \quad
n = -4:\; 26, \quad
n = 5:\; 35,
\notag\\
&n = -5:\; 40, \quad
n = 6:\; 51, \quad
n = -6:\; 57, \quad
n = 7:\; 70, \quad
n = -7:\; 77,
\notag\\
&n = 8:\; 92, \quad
n = -8:\; 100, \quad
n = 9:\; 117, \quad
n = -9:\; 126, \quad
n = 10:\; 145.
\end{align}
The expansion of $\eta(q)/q^{1/24} = \prod_{n=1}^{\infty}(1-q^n)$
to $100$ terms, writing $P(q) = \prod_{n \ge 1}(1-q^n)$:
\begin{align}\label{eq:eta-100-terms}
P(q) \;&=\;
1 - q - q^2 + q^5 + q^7
- q^{12} - q^{15} + q^{22} + q^{26}
- q^{35}
\notag\\
&\quad
- q^{40} + q^{51} + q^{57}
- q^{70} - q^{77} + q^{92} + q^{100}
- q^{117} - q^{126}
\notag\\
&\quad
+ q^{145} + q^{155}
- q^{176} - q^{187}
+ q^{210} + q^{222}
- q^{247} - q^{260}
\notag\\
&\quad
+ q^{287} + q^{301}
- q^{330} - q^{345}
+ q^{376} + q^{392}
- q^{425} - q^{442}
\notag\\
&\quad
+ q^{477} + q^{495}
- q^{532} - q^{551}
+ q^{590} + q^{610}
- q^{651} - q^{672}
\notag\\
&\quad
+ q^{715} + q^{737}
+ O(q^{782}).
\end{align}
Each nonzero exponent is a pentagonal number $n(3n-1)/2$, and
each coefficient is $(-1)^n$; there are no other terms. This
is the content of Euler's identity:
\[
\prod_{n=1}^{\infty}(1 - q^n)
\;=\;
\sum_{n=-\infty}^{\infty}(-1)^n\, q^{n(3n-1)/2}
\;=\;
1 + \sum_{n=1}^{\infty}(-1)^n\bigl(q^{n(3n-1)/2} + q^{n(3n+1)/2}\bigr).
\]
Verification: the exponents
$\{0, 1, 2, 5, 7, 12, 15, 22, 26, 35, 40, 51, 57, 70, 77,
92, 100, 117, 126, 145, 155, 176, 187, 210, 222, 247, 260,
287, 301, 330, 345, 376, 392, 425, 442, 477, 495, 532, 551,
590, 610, 651, 672, 715, 737, \ldots\}$
are precisely the generalised pentagonal numbers
$\omega(n) = n(3n-1)/2$ for $n = 0, \pm 1, \pm 2, \ldots$,
listed in order. The signs alternate: $+$ for even $|n|$, $-$
for odd $|n|$.

The inverse $P(q)^{-1} = \sum_{n=0}^{\infty} p(n)\, q^n$ is the
partition generating function, with
\[
p(0) = 1,\;
p(1) = 1,\;
p(2) = 2,\;
p(3) = 3,\;
p(4) = 5,\;
p(5) = 7,\;
p(6) = 11,\;
p(7) = 15,\;
\ldots
\]
the partition numbers. The Heisenberg bar complex, through the genus
tower and the $E_1$ ordered shadow, \emph{knows} the combinatorics
of integer partitions: the ordered bar complex counts compositions
(Computation~\ref{comp:heisenberg-dim-table}), the $\Sigma_n$-descent
quotients them to partitions, and the Euler characteristic of the
alternating sum recovers the pentagonal identity.

\smallskip
\noindent
\emph{Summary of the $E_1$ ordered dictionary.}
\begin{center}
\small
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{@{}l@{\;\;}l@{}}
\textbf{$E_1$ ordered datum} & \textbf{Value for $\cH_k$} \\
\hline
Shadow polynomial $m_2(J,J;\lambda)$
 & $k\lambda$ \\[2pt]
Shadow depth $r_{\max}$
 & $2$ (class~G) \\[2pt]
Higher operations $m_{k \ge 3}$
 & $0$ (Koszul and SC-formal) \\[2pt]
$R$-matrix $R(z)$
 & $e^{k\hbar/z}$ (scalar, abelian) \\[2pt]
Three-tier placement
 & tier~(ii): $\Einf$ with OPE poles \\[2pt]
Genus-$1$ $r$-matrix
 & $k\cdot\wp(z|\tau)$ (doubly periodic) \\[2pt]
Genus-$1$ correction to $m_2$
 & $-(\pi^2 k/3)\, E_2(\tau)\, \lambda$ \\[2pt]
Genus-$g$ $r$-matrix
 & $k \cdot B(z,w)$ (Bergman kernel) \\[2pt]
$B$-cycle monodromy
 & $0$ at all genera ($c_0 = 0$) \\[2pt]
Euler characteristic
 & $\eta(q)^{-k}$ (pentagonal numbers) \\[2pt]
Partition function
 & compositions $\to$ partitions via $\Sigma_n$
\end{tabular}
\end{center}
The single scalar~$k$ determines the entire $E_1$ ordered shadow.
\end{computation}

\begin{computation}[Heisenberg classifying space; \ClaimStatusProvedHere]
\label{comp:heisenberg-classifying-space}
We verify the representability theorem (Theorem~\ref{thm:bar-representability}) for $\cA = \cH_k$. The bar construction $\barB(\cH_k) = T^c(s^{-1}\C \cdot J)$ is the cofree conilpotent coalgebra on a single desuspended generator. For any conilpotent test coalgebra $\cC$, the space of twisting morphisms is:
\[
\mathrm{Tw}(\cC, \cH_k) \;=\; \bigl\{\tau \in \Hom^{-1}(\cC, \cH_k) \;\bigm|\; d\tau + \tau \star \tau = 0\bigr\}.
\]
Since $\cH_k$ has $m_{k \geq 3} = 0$, the MC equation reduces to $d\tau + m_2(\tau, \tau) = 0$, where $m_2(\tau,\tau)(c) = k \cdot \langle \tau(c'), \tau(c'') \rangle \cdot \lambda$ for the reduced coproduct $\bar\Delta(c) = \sum c' \otimes c''$. The terminality map $f_\tau \colon \cC \to \barB(\cH_k)$ is:
\[
f_\tau(c) \;=\; \sum_{n \geq 1} \tau^{\otimes n} \circ \Delta^{(n-1)}(c) \;\in\; T^c(s^{-1}\C \cdot J),
\]
converging because $\cC$ is conilpotent. For $\cC = \barB(\cH_k)$ itself, the identity twisting morphism gives $f_{\tau_{\mathrm{univ}}} = \id$, recovering the algebra from its own bar complex.
\end{computation}

\subsection{The doubling construction for Heisenberg}

The general half-space BV theorem
(Theorem~\ref{thm:general-half-space-bv}) is proved by the doubling
construction (Theorem~\ref{thm:doubling-rwi}): embed the half-space
into the doubled whole-space and apply Stokes. For the Heisenberg
algebra, this construction is completely explicit.

The free propagator on $\C\times\R$ is
$K(z,t;\,z',t')=\Theta(t-t')/(2\pi(z-z'))$. The reflected
propagator on the half-space $\C\times\R_{\ge 0}$ is
\[
K^{\mathrm{refl}}(z,t;\,z',t')
=\frac{\Theta(t-t')}{2\pi(z-z')}
+\frac{\Theta(t+t')}{2\pi(z-\bar z')}.
\]
The reflection $\sigma(z,t)=(\bar z,-t)$ maps
$\C\times\R\to\C\times\R$, and $K^{\mathrm{refl}}=K+K\circ\sigma$ is
the standard propagator on the doubled space restricted to the
$\sigma$-invariant sector.

The method-of-images embedding $\iota\colon\Conf_n(\C\times\R_{\ge 0})
\hookrightarrow\Conf_{2n}(\C\times\R)^{\sigma}$ sends each point
$(z_i,t_i)$ to the pair $\{(z_i,t_i),(\bar z_i,-t_i)\}$. The
propagator form $\omega_{ij}^{\mathrm{refl}}=\iota^*(\omega_{ij}+
\omega_{i,\sigma(j)})$ extends to a logarithmic form on the
Fulton--MacPherson compactification of $\Conf_{2n}(\C\times\R)$, with
log poles along the collision divisor $z_i=z_j$ (standard) and the
reflection divisor $z_i=\bar z_j$ (from the image term). Stokes'
theorem on the compactified doubled space gives the reflected weight
identity: the Heisenberg case is trivial (all higher operations vanish,
$m_k=0$ for $k\ge 3$), confirming
Proposition~\ref{prop:rosetta-heisenberg-mk} by a different route.

\begin{remark}[Heisenberg as a test of the geometric Steinberg conjecture]
\label{rem:rosetta-geometric-steinberg}
\index{Steinberg!geometric conjecture!Heisenberg test}
The Heisenberg algebra verifies all three ingredients of the
geometric HT Steinberg conjecture
(Conjecture~\ref{conj:geometric-steinberg},
Example~\ref{ex:geometric-steinberg-heisenberg}):
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\cM_{\mathrm{vac}}(\cH_k) =
 T^*[-2]\bigl(\operatorname{Maps}(D^2, V)\bigr)$ with
 $\omega_{-2} = k \cdot \omega_{\mathrm{can}}$;
\item the Dirichlet zero section is Lagrangian;
\item the derived self-intersection recovers
 $\cH_k \simeq Z^{\mathrm{der}}_{\mathrm{ch}}(\cH_k)$.
\end{enumerate}
The clean intersection ($m_k = 0$ for $k \ge 3$,
Proposition~\ref{prop:rosetta-heisenberg-mk}) is the chiral
analogue of the abelian Steinberg variety degenerating to a point.
The excess intersection of the Virasoro fourth-order pole is the
chiral analogue of passing from torus to non-abelian Springer.
\ClaimStatusProvedHere
\end{remark}

\begin{remark}[$E_N$ level reached by Heisenberg]
\label{rem:heisenberg-EN-level}
\index{Heisenberg algebra!$E_N$ level}
\index{E_N ladder@$E_N$ ladder!Heisenberg}
The Heisenberg algebra $\cA = \cH_k$ reaches the following
levels of the $E_N$ ladder:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\Eone$-chiral
 (Definition~\ref{def:e1-chiral-algebra}): the OPE
 $J(z)\,J(w) \sim k/(z-w)^2$ defines $\cH_k$ as an
 $\Einf$-chiral algebra, hence \emph{a fortiori}
 $\Eone$-chiral. The $R$-matrix is
 $R(z) = \exp(k\hbar/z)$ with collision residue $k/z$
 and monodromy $\exp(-2\pi i k)$.

\item $\Etwo$-chiral on the derived center
 (Definition~\ref{def:E2-chiral-algebra}): the chiral
 Deligne conjecture equips
 $Z^{\mathrm{der}}_{\mathrm{ch}}(\cH_k)
 = C^\bullet_{\mathrm{ch}}(\cH_k, \cH_k)$
 with an $\Etwo$-chiral algebra structure. This is
 automatic for every chiral algebra.

\item $\Etwo$-topological
 (Definition~\ref{def:E2-topological-algebra}):
 \textbf{not attained}. The Heisenberg algebra carries
 no conformal vector: it is not a conformal vertex algebra.
 Without a Sugawara-type stress tensor $T(z)$ satisfying
 $\{Q, G(z)\} = T(z)$, the complex-structure dependence
 on $\C$ cannot be trivialized in cohomology, and the
 topologization step
 (Construction~\ref{constr:topologization}) fails.

\item The pair
 $(Z^{\mathrm{der}}_{\mathrm{ch}}(\cH_k),\, \cH_k)$
 carries the $\SCchtop$ structure
 (bulk acting on boundary) as a first-class object.
 This is the generic situation described in
 \S\ref{subsec:ordered-three-tier}: $\SCchtop$ is
 the natural home of chiral algebras without conformal
 vector.
\end{enumerate}
Shadow class: $\mathbf{L}$ (simple poles in the $J$-$J$
OPE; the bar complex is formal and
$m_k = 0$ for $k \ge 3$ by
Proposition~\ref{prop:rosetta-heisenberg-mk}).
The obstruction to climbing higher is the absence of a
conformal vector, not any deficiency in the OPE.
\end{remark}

% ================================================================
\subsection{The three-tier $R$-matrix classification}
\label{subsec:ordered-three-tier}
\index{R-matrix!three-tier classification|textbf}
\index{three-tier classification|textbf}
% ================================================================

The Heisenberg computations reveal a complete package (operations, $R$-matrix, genus tower, PVA, Koszul dual) controlled
by a single scalar~$k$. The rest of this chapter asks: what
happens when the package is no longer controlled by a single scalar?
The answer organises all chiral algebras into three tiers by the
provenance of their spectral $R$-matrix, four depth classes by the
complexity of their Lagrangian self-intersection, and three
genus-$1$ regimes by the entanglement of curvature and braiding.
The Heisenberg sits at the simplest point of each classification;
the programme from this section onward systematically traces
what changes as the algebra grows more complex.

The Heisenberg belongs to the second of three tiers that
organise all chiral algebras by the provenance of their spectral
$R$-matrix. The three tiers are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Pole-free commutative}:
 the OPE has no singularities, $R(z) = \tau$
 (the Koszul-signed flip), and the ordered bar complex
 descends to the symmetric bar by the na\"{\i}ve
 $\Sigma_n$-quotient.
 Examples: commutative chiral algebras in the sense of BD
 (D-schemes). None of the standard vertex algebra families
 belong to this tier, since all have OPE poles.

\item \emph{$\Einf$-chiral with OPE poles}:
 the algebra is a vertex algebra (local, $\Sigma_n$-equivariant),
 but the OPE has singularities and the spectral $R$-matrix is
 \emph{derived} from the local OPE via analytic continuation
 of the flat connection on configuration space.
 The descent $\bar{B}^{\mathrm{ch,ord}} \to \barBch$ is
 $R$-matrix twisted (Proposition~\ref{prop:r-matrix-descent}).
 Examples: all standard vertex algebras,
 including Heisenberg ($R = e^{k\hbar/z}$), affine Kac--Moody
 ($R = 1 + k\Omega/z + \cdots$), Virasoro, $\cW_3$, symplectic
 bosons, lattice VOAs, $\beta\gamma$, $bc_\lambda$,
 free fermions. For systems whose OPE on generators
 has only a simple pole ($\beta\gamma$, $bc_\lambda$, $\psi$),
 the $d\log$ kernel absorbs it to a constant and the
 generator-level $R$-matrix is $\tau$ or $\mathrm{Id}$;
 nevertheless these are tier~(ii), not tier~(i),
 because the OPE is singular.

\item \emph{Genuinely $\Eone$-chiral}:
 the $R$-matrix is \emph{independent input}, not derivable
 from a local OPE; the algebra is nonlocal (ordered configurations
 only, no underlying $\Sigma_n$-equivariance).
 Examples: Yangians $Y_\hbar(\fg)$, quantum vertex algebras
 in the sense of Etingof--Kazhdan.
\end{enumerate}

\noindent
The tier determines three things:
\begin{enumerate}[label=(\alph*),nosep]
\item the \emph{$R$-matrix structure} ($\tau$, OPE-derived, or
 independent);
\item the \emph{ordered Koszul dual}
 ($\cA^!_{\mathrm{line}}$ carries a spectral parameter
 in tiers~(ii)--(iii), but in tier~(i) it agrees with
 the symmetric Koszul dual $\cA^!_{\mathrm{ch}}$);
\item the \emph{genus-$1$ regime} (decoupled when
 $c_0 = 0$, entangled when $c_0 \ne 0$; the decoupled
 case occurs only for $\cH_k$ among the standard
 families).
\end{enumerate}

\noindent
The examples below are organised by this classification:
$\S$\ref{subsec:cs-nonabelian-primitive-package}--\ref{subsec:symplectic-boson-ordered-bar}
treat the standard vertex algebra families (all tier~(ii));
$\S$\ref{sec:shadow-tower-atlas}--\ref{subsec:e1-ordered-bar-landscape}
assemble the complete landscape, recording the tier of each family
alongside its shadow depth class and genus-$1$ regime.
Tier~(iii) is treated in
Part~\ref{part:e1-core}\@.

The three tiers above refine to a five-term algebraic hierarchy
that organises chiral algebras by increasingly nonlocal structure.

\begin{definition}[Five-term algebraic hierarchy]
\label{def:v2-algebraic-hierarchy}
\index{algebraic hierarchy!five-term|textbf}
The algebraic hierarchy of chiral algebras, ordered by increasingly
nonlocal structure, is
\begin{equation}\label{eq:five-term-hierarchy}
 \chirCom
 \;\subset\;
 \PVA
 \;\subset\;
 \Einf\text{-chiral}
 \;\subset\;
 \Pinf\text{-chiral}
 \;\subset\;
 \Eone\text{-chiral}.
\end{equation}
Each inclusion is strict.
\end{definition}

\begin{remark}[The five levels]
\label{rem:v2-algebraic-hierarchy-levels}
\index{algebraic hierarchy!five levels}
The five levels are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\chirCom$: pole-free commutative chiral algebras.
 The OPE is trivial, the chiral product factors through
 a commutative D-module structure, and the bar complex
 descends to the symmetric bar by the na\"{\i}ve
 $\Sigma_n$-quotient.

\item $\PVA$: Poisson vertex algebras. A PVA carries a
 $\lambda$-bracket on cohomology (the classical shadow) but
 no quantum corrections; it is the semiclassical limit of a
 vertex algebra.

\item $\Einf$-chiral: all vertex algebras with local OPE.
 This is the standard setting of Beilinson--Drinfeld~\cite{BD04}
 and Frenkel--Ben-Zvi~\cite{FBZ04}. Every standard vertex
 algebra (Heisenberg, affine Kac--Moody, Virasoro,
 $\mathcal{W}$-algebras, lattice VOAs, $\beta\gamma$,
 $bc_\lambda$, free fermions) belongs to this level: the OPE
 is local and the algebra carries $\Sigma_n$-equivariance
 on configuration spaces.

\item $\Pinf$-chiral: homotopy-coherent intermediate algebras.
 A $\Pinf$-chiral algebra is homotopy-commutative but not
 strictly commutative; this level arises in the deformation
 quantisation of PVAs and in the homotopy transfer of
 $\Einf$-structures along quasi-isomorphisms.

\item $\Eone$-chiral: fully nonlocal chiral algebras.
 The $R$-matrix is independent input, not derivable from a
 local OPE. This is the natural home of Yangian $R$-matrices
 $Y_\hbar(\fg)$ and quantum vertex algebras in the sense of
 Etingof--Kazhdan. The ordered bar complex
 $\bar{B}^{\mathrm{ch,ord}}$ lives here; it has no
 underlying $\Sigma_n$-equivariance.
\end{enumerate}
The hierarchy collapses under the forgetful functor: every
$\Eone$-chiral algebra has an underlying $\Einf$-chiral
algebra obtained by forgetting the nonlocal data, and every
$\Einf$-chiral algebra has an underlying PVA obtained by
passing to the classical limit.
\end{remark}

\subsection{Nonabelian Chern--Simons: the primitive package}
\label{subsec:cs-nonabelian-primitive-package}
\index{Chern--Simons!nonabelian!primitive package|textbf}
\index{affine Kac--Moody!as boundary chart}

The Heisenberg algebra is the boundary chart for abelian
Chern--Simons. The nonabelian case $G$ (complex algebraic,
Lie algebra~$\fg$, level~$k$) produces the same architecture
with the affine Kac--Moody vertex algebra $V_k(\fg)$ as boundary
chart.

\noindent\textbf{Boundary algebra (chart).}
The boundary chiral algebra is $A = V_k(\fg)$, the affine
vertex algebra at level~$k$
(Frenkel--Ben-Zvi \cite{FBZ04}).
Generators: currents $J^a(z)$, $a = 1, \ldots, \dim \fg$.
OPE relations:
\begin{equation}\label{eq:cs-km-ope}
J^a(z)\, J^b(w)
\;\sim\;
\frac{k\,\kappa^{ab}}{(z-w)^2}
\;+\;
\frac{f^{ab}{}_c\, J^c(w)}{z-w},
\end{equation}
where $\kappa^{ab}$ is the Killing form and $f^{ab}{}_c$
are the structure constants of~$\fg$. In modes:
$[J^a_m, J^b_n] = f^{ab}{}_c\, J^c_{m+n}
+ k\, m\, \kappa^{ab}\, \delta_{m+n,0}$.

\noindent\textbf{Open category (primitive).}
$\cC^{\mathrm{op}} = \cC_{\mathrm{CS}(G,k)}^{\mathrm{op}}$
is the factorization dg-category of boundary
line and junction operators on the holomorphic boundary
curve~$X$, with punctures at Wilson-line endpoints.
The local construction is a theorem
(Costello--Gwilliam \cite{CG17}); the global cosheaf
structure is part of the programme of
Section~\ref{subsec:modular-holography-programme}.
A vacuum boundary condition $b_{\mathrm{WZW}}$ gives the
local chart
$A = \mathrm{End}(b_{\mathrm{WZW}}) \simeq V_k(\fg)$.
At rational/integrable levels, the decategorified shadow
is the modular tensor category of
Chern--Simons/WZW Wilson lines.

\noindent\textbf{Bulk (derived center).}
$Z = C^\bullet_{\mathrm{ch}}(V_k(\fg), V_k(\fg))$,
the chiral derived center.
This is a distinct object from the bar complex:
$\bar{B}(V_k(\fg))$ classifies twisting morphisms
(couplings between $A$ and $A^!$),
while $Z$ classifies bulk observables acting on
the boundary
(Volume~I, Theorem~\ref*{V1-thm:thqg-swiss-cheese}).

\noindent\textbf{Shadow archetype.}
Class~$\mathbf{L}$ (Lie/tree): shadow depth
$r_{\max} = 3$. The cubic shadow
$C_\fg = f^{ab}{}_c$ encodes the Lie bracket;
the quartic contact invariant vanishes
by the Jacobi identity
(Volume~I).

\noindent\textbf{Modular data.}
$\kappa(V_k(\fg)) = \dim(\fg) \cdot (k + h^\vee)/(2h^\vee)$,
where $h^\vee$ is the dual Coxeter number.
The Koszul dual
$V_k(\fg)^! = \mathrm{CE}^{\mathrm{ch}}(\fg_{-k-2h^\vee})$
has modular characteristic
$\kappa(V_k(\fg)^!) = -\kappa(V_k(\fg))$
by the level shift $k \mapsto -k - 2h^\vee$,
giving complementarity
$\kappa + \kappa' = 0$.
(The Koszul dual is the chiral CE algebra, not
$V_{-k-2h^\vee}(\fg)$ itself; these share the
same~$\kappa$ but are categorically distinct.)
The genus tower on the proved scalar lane is
$F_g = \kappa(V_k(\fg)) \cdot
\lambda_g^{\mathrm{FP}}$ at all genera (Volume~I, Theorem~D).

\noindent\textbf{Koszul dual: explicit generators and relations.}
\label{par:cs-koszul-dual-explicit}%
\index{Chern--Simons!Koszul dual!explicit generators|textbf}%
\index{Yangian!dg-shifted!Chern--Simons}%
The Koszul dual $A^! = Y_\hbar^{\mathrm{dg}}(\fg)$ is the
dg-shifted Yangian constructed from the bar complex of
$V_k(\fg)$ (Volume~I,
Theorem~\ref*{thm:Koszul_dual_Yangian};
\cite{DNP25}). We give the
explicit presentation in modes and generating functions,
first for general~$\fg$ and then for $\fg = \mathfrak{sl}_2$.

\smallskip
\noindent
\emph{General $\fg$.}
The algebra $A^!$ is generated by modes
\begin{equation}\label{eq:cs-dual-generators}
B_n^a \;\;(\text{even, degree $0$}),
\qquad
c_n^a \;\;(\text{odd, degree $-1$}),
\qquad
n \ge 0,\quad a = 1, \ldots, \dim \fg,
\end{equation}
with algebraic relations
\begin{equation}\label{eq:cs-dual-BB}
[B_n^a,\, B_m^b] \;=\; f^{ab}{}_{c}\, B_{n+m}^c,
\end{equation}
\begin{equation}\label{eq:cs-dual-Bc}
[B_n^a,\, c_m^b] \;=\; f^{ab}{}_{c}\, c_{n+m}^c,
\end{equation}
and differential $Q$ (cohomological, $|Q| = +1$) given by
\begin{align}
Q(c_n^a)
&\;=\;
\tfrac{1}{2}\, f^{a}{}_{bc}
\sum_{\substack{r+s = n-1 \\ r,s \ge 0}} c_r^b\, c_s^c,
\label{eq:cs-Q-ghost}
\\[4pt]
Q(B_n^a)
&\;=\;
n\,(k - h^\vee)\,\kappa^{ab}\, c_{n-1}^b
\;+\;
f^{a}{}_{bc}
\sum_{\substack{r+s = n-1 \\ r,s \ge 0}}
B_s^c\, c_r^b,
\label{eq:cs-Q-current}
\end{align}
where $h^\vee$ is the dual Coxeter number and $\kappa^{ab}$
the Killing form, both evaluated in a Killing-orthonormal basis
for~$\fg$ simple.
The even generators~\eqref{eq:cs-dual-BB} form the
enveloping algebra $U(\fg[t])$ of the polynomial current
algebra; the full structure
$Q^2 = 0$ is the dg deformation at level~$k$.
In generating-function form, with
$B^a(u) := \sum_{n \ge 0} B_n^a\, u^{-n-1}$
and
$c^a(u) := \sum_{n \ge 0} c_n^a\, u^{-n-1}$,
\begin{align}
Q\, c^a(u)
&\;=\;
\tfrac{1}{2}\, f^{a}{}_{bc}\; c^b(u)\, c^c(u),
\label{eq:cs-Q-ghost-gf}
\\[4pt]
Q\, B^a(u)
&\;=\;
-(k + h^\vee)\,\kappa^{ab}\,\partial_u c^b(u)
\;+\;
f^{a}{}_{bc}\; c^b(u)\, B^c(u),
\label{eq:cs-Q-current-gf}
\end{align}
where the sign and shift
$k - h^\vee \mapsto -(k + h^\vee)$ in passing to
generating functions absorbs the normal-ordering correction
$h^{ab} = h^\vee \kappa^{ab}$ from the
Casimir contraction
$h^{ab} := \tfrac{1}{2}\,
f^{a}{}_{Lc}\, f^{b\,c}{}_{L}$.

\smallskip
\noindent
\emph{Specialisation: $\fg = \mathfrak{sl}_2$.}
The dual Coxeter number is $h^\vee = 2$.
In the Killing-orthonormal basis $\{t^a\}_{a=1}^3$
with $[t^a, t^b] = \epsilon^{abc}\, t^c$ and
$\kappa^{ab} = \delta^{ab}$,
the differential~\eqref{eq:cs-Q-ghost-gf}--\eqref{eq:cs-Q-current-gf}
reads
\begin{equation}\label{eq:sl2-Q-orthonormal}
Q\, c^a(u)
\;=\;
\tfrac{1}{2}\,\epsilon^{a}{}_{bc}\, c^b(u)\, c^c(u),
\qquad
Q\, B^a(u)
\;=\;
-(k + 2)\,\partial_u c^a(u)
\;+\;
\epsilon^{a}{}_{bc}\, c^b(u)\, B^c(u).
\end{equation}
The even subalgebra generated by the $B^a_n$
satisfies $[B^a_n, B^b_m] = \epsilon^{ab}{}_{c}\, B^c_{n+m}$
and is isomorphic to $U(\mathfrak{sl}_2[t])$;
the differential $Q$ deforms it at level~$k$.

Pass to the Chevalley basis $\{e, f, h\}$
($[h,e] = 2e$, $[h,f] = -2f$, $[e,f] = h$,
Killing form $\kappa(h,h) = 2$,
$\kappa(e,f) = 1$).
Write $E_n := B_n^e$, $F_n := B_n^f$,
$H_n := B_n^h$ for the even modes, and
$\epsilon_n := c_n^e$, $\varphi_n := c_n^f$,
$\eta_n := c_n^h$ for the ghost modes.
The current-algebra relations are
\begin{equation}\label{eq:sl2-yangian-modes}
\begin{aligned}
{[H_n,\, E_m]} &= 2\, E_{n+m},
&\qquad
{[H_n,\, F_m]} &= -2\, F_{n+m},
\\[3pt]
{[E_n,\, F_m]} &= H_{n+m},
&\qquad
{[H_n,\, H_m]} &= 0.
\end{aligned}
\end{equation}
The differential $Q$ acts on the even
generators by
\begin{equation}\label{eq:sl2-Q-EFH}
\begin{aligned}
Q(E_n)
&\;=\;
n(k-2)\,\varphi_{n-1}
\;+\;
2\!\!\sum_{\substack{r+s=n-1\\r,s\ge 0}}
\bigl(
 E_s\, \eta_r
 \;-\;
 H_s\, \epsilon_r
\bigr),
\\[4pt]
Q(F_n)
&\;=\;
n(k-2)\,\epsilon_{n-1}
\;+\;
2\!\!\sum_{\substack{r+s=n-1\\r,s\ge 0}}
\bigl(
 H_s\, \varphi_r
 \;-\;
 F_s\, \eta_r
\bigr),
\\[4pt]
Q(H_n)
&\;=\;
\tfrac{n(k-2)}{2}\,\eta_{n-1}
\;+\;
\sum_{\substack{r+s=n-1\\r,s\ge 0}}
\bigl(
 F_s\, \epsilon_r
 \;-\;
 E_s\, \varphi_r
\bigr),
\end{aligned}
\end{equation}
where the off-diagonal Killing form
$\kappa^{ef} = 1$, $\kappa^{hh} = \tfrac{1}{2}$
accounts for the cross-pairing $E \leftrightarrow
\varphi$, $F \leftrightarrow \epsilon$ in the
linear term and the $\tfrac{1}{2}$ on the
Cartan line.
The coefficient $k - h^\vee = k - 2$ vanishes at the
critical level $k = -h^\vee = -2$ (equivalently
$k_{\mathrm{ren}} = k + h^\vee = 0$):
the linear term in $Q$ drops out, the differential reduces
to the Chevalley--Eilenberg differential of
$\mathfrak{sl}_2[t]$, and the Sugawara construction
degenerates.

The generating series of the even modes are
\begin{equation}\label{eq:sl2-dual-generators}
E(u) := \sum_{n \ge 0} E_n\, u^{-n-1},
\quad
F(u) := \sum_{n \ge 0} F_n\, u^{-n-1},
\quad
H(u) := \sum_{n \ge 0} H_n\, u^{-n-1}.
\end{equation}
On cohomology, the even sector survives: the Yangian
$Y_\hbar(\mathfrak{sl}_2) = H^0(A^!, Q)$ is
generated by $E(u)$, $F(u)$, $H(u)$ with the
RTT relations
\begin{equation}\label{eq:sl2-RTT}
R_{12}(u - v)\, T_1(u)\, T_2(v)
\;=\;
T_2(v)\, T_1(u)\, R_{12}(u - v),
\end{equation}
where $T(u) = \bigl(\begin{smallmatrix}
k_1(u) & F(u) \\ E(u) & k_2(u)
\end{smallmatrix}\bigr)$ is the Gauss-decomposed
transfer matrix, $R(u) = 1 + \hbar\, P/u$ the
Yang $R$-matrix ($P$ the permutation on
$\bC^2 \otimes \bC^2$), and
$H(u) = k_1(u)/k_2(u)$.
The FRT expansion of~\eqref{eq:sl2-RTT} gives, among
others, the Drinfeld relations
\begin{align}
(u - v - \hbar)\, E(u)\, E(v)
&\;=\;
(u - v + \hbar)\, E(v)\, E(u),
\label{eq:cs-drinfeld-EE}
\\[3pt]
[E(u),\, F(v)]
&\;=\;
\frac{\hbar}{u - v}
\bigl(k_1(u)\, k_2(v) - k_1(v)\, k_2(u)\bigr),
\label{eq:cs-drinfeld-EF}
\end{align}
which encode the spectral OPE of line operators
on the holomorphic boundary
(Section~\ref{subsec:spectral-ope-and-yangian}).
The passage from the dg presentation
\eqref{eq:sl2-yangian-modes}--\eqref{eq:sl2-Q-EFH}
to the RTT form~\eqref{eq:sl2-RTT} is the
content of the bar--cobar Quillen equivalence
(Volume~I, Theorem~B) applied to the affine
boundary chart: the twisting morphism extracted
from the bar complex of $V_k(\mathfrak{sl}_2)$
yields the rational $r$-matrix
$r(z) = k\,\Omega/z$ (with $\Omega$ the Casimir
element of $\mathfrak{sl}_2$ and $k$ the level), whose quantisation
is the Yang $R$-matrix above.

\begin{computation}[The $\mathfrak{sl}_3$ Yangian: adjacent roots and the triangle coefficient; \ClaimStatusProvedHere]%
\label{comp:sl3-yangian-triangle}%
\index{Yangian!sl3 triangle@$\mathfrak{sl}_3$ triangle coefficient}%
\index{triangle sector!explicit for sl3@explicit for $\mathfrak{sl}_3$}%
The rank-$2$ case $\fg = \mathfrak{sl}_3$ is the first where
composite roots, triangle sectors, and Serre relations become
visible. Simple roots $\alpha_1, \alpha_2$ with Cartan matrix
$\bigl(\begin{smallmatrix} 2 & -1 \\ -1 & 2
\end{smallmatrix}\bigr)$;
composite root $\alpha_{12} = \alpha_1 + \alpha_2$ with
generators $e_{12} = [e_1, e_2]$, $f_{12} = [f_2, f_1]$.
In the defining representation ($E_{ij}$ = matrix units of
$\mathfrak{gl}_3$): $e_1 = E_{12}$, $e_2 = E_{23}$,
$e_{12} = E_{13}$.

The \emph{triangle sectors} on three tensor factors are
\[
T^L_{12} = E_{13}^{(1)}\,E_{21}^{(2)}\,E_{32}^{(3)},
\qquad
T^L_{21} = E_{13}^{(1)}\,E_{32}^{(2)}\,E_{21}^{(3)},
\]
carrying weights $(\alpha_{12},\,-\alpha_1,\,-\alpha_2)$ and
$(\alpha_{12},\,-\alpha_2,\,-\alpha_1)$ respectively.
The triangle localization formula
(Theorem~\ref{thm:triangle-localization}), with
$S_{ab}(u) = \sum_\alpha \rho_\alpha(u)\,E_\alpha^{(a)}F_\alpha^{(b)}$
the two-body spectral kernel, computes
\[
\Pi_{\langle T^L_{12},\,T^L_{21}\rangle}
\tfrac12[S_{12}(w),\,S_{13}(w{+}z)]
\;=\;
\frac{1}{2}\,\rho_1(w)\,\rho_2(w{+}z)\,T^L_{12}
\;-\;
\frac{1}{2}\,\rho_2(w)\,\rho_1(w{+}z)\,T^L_{21},
\]
where $E_i^{(a)} := e_i$ acting on tensor factor~$a$, and the
commutators $[E_1^{(1)}F_1^{(2)},\,
E_2^{(1)}F_2^{(3)}] = E_{12}^{(1)}F_1^{(2)}F_2^{(3)}$
and $[E_2^{(1)}F_2^{(2)},\,E_1^{(1)}F_1^{(3)}]
= -E_{12}^{(1)}F_2^{(2)}F_1^{(3)}$ each contribute one
triangle vector. Under the normalised rational ansatz
$\rho_i(u) = 1/u$, adjacent-root rigidity
(Theorem~\ref{thm:adjacent-root-rigidity}) forces
\[
\lambda^L_{12} = \lambda^L_{21}
= \lambda^R_{12} = \lambda^R_{21}
= \frac{c_1 c_2}{2\,c_{12}}
\;=\;\frac12.
\]
This is the universal coefficient
$\frac1n\big|_{n=2} = \int_0^1(1-t)\,dt$
from the Dynkin--BCH beta integral
(Theorem~\ref{thm:dynkin-bch-path}).

The \emph{Serre relation} $[e_1,[e_1,e_2]] = 0$ has
a root-space origin: the weight $2\alpha_1 + \alpha_2$ is
\emph{not} a root of $\mathfrak{sl}_3$, so
$(\mathfrak{sl}_3)_{2\alpha_1 + \alpha_2} = 0$ and
every multilinear Lie monomial of that weight vanishes.
In the bar complex, the degree-$3$ element
$[s^{-1}e_1\,|\,s^{-1}e_1\,|\,s^{-1}e_2]$ vanishes in
bar homology: its boundary at $D_{1,2}$ vanishes
($[e_1,e_1] = 0$) and its boundary at $D_{2,3}$ produces
$[s^{-1}e_1\,|\,s^{-1}e_{12}]$, whose own boundary
$[e_1, e_{12}] = 0$ by the Serre relation; the weight
space $(\mathfrak{sl}_3)_{2\alpha_1+\alpha_2} = 0$
forces the entire sector to be acyclic. The Yangian Serre relation
$\mathrm{Sym}_{r_1,r_2}[x^+_{1,r_1},[x^+_{1,r_2},
x^+_{2,s}]] = 0$ follows by the same mechanism at all mode
levels.
\end{computation}

\begin{remark}[$E_N$ level reached by $V_k(\fg)$ at non-critical level]
\label{rem:km-EN-level}
\index{Kac--Moody!$E_N$ level}
\index{E_N ladder@$E_N$ ladder!Kac--Moody}
For $k \ne -h^\vee$ (non-critical level), the affine
Kac--Moody vertex algebra $\cA = V_k(\fg)$ reaches the
top of the $E_N$ ladder:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\Eone$-chiral
 (Definition~\ref{def:e1-chiral-algebra}): the current
 OPE~\eqref{eq:cs-km-ope} gives $V_k(\fg)$ the
 structure of an $\Einf$-chiral algebra, hence
 \emph{a fortiori} $\Eone$-chiral.
 The $R$-matrix is $R(z) = 1 + \hbar\,\Omega/z + \cdots$
 with $\Omega$ the Casimir of~$\fg$.

\item $\Etwo$-chiral on the derived center
 (Definition~\ref{def:E2-chiral-algebra}): automatic from
 the chiral Deligne conjecture.

\item $\Etwo$-topological
 (Definition~\ref{def:E2-topological-algebra}): the
 Sugawara construction provides a conformal vector
 $T_{\mathrm{Sug}}(z)
 = \frac{1}{2(k + h^\vee)}
 \sum_a {:}\!J^a J^a\!{:}(z)$
 of central charge $c = k\dim\fg/(k + h^\vee)$.
 At $k \ne -h^\vee$ this is well-defined, and
 Construction~\ref{constr:topologization} trivializes the
 complex-structure dependence in cohomology.

\item $\Ethree$-chiral: the 3d holomorphic-topological
 theory is holomorphic Chern--Simons on $\C \times \R$,
 descended from the 6d holomorphic gauge theory
 (Costello--Li). The boundary of the 3d HT theory is
 $V_k(\fg)$.

\item $\Ethree$-topological
 (Definition~\ref{def:E3-topological-algebra}): both
 requirements are met---the 3d HT theory exists
 (holomorphic CS) and the conformal vector exists
 (Sugawara at $k \ne -h^\vee$). The derived chiral
 center $Z^{\mathrm{der}}_{\mathrm{ch}}(V_k(\fg))$
 carries a genuine $\Ethree$-topological algebra
 structure, independent of the complex structure on
 $\C$. This is the Chern--Simons TQFT, and it is the
 example where Conjecture~\ref{conj:E3-topological-climax}
 is proved.
\end{enumerate}
Shadow class: $\mathbf{L}$ (double poles from the
Sugawara stress tensor; $m_k = 0$ for $k \ge 3$ by
Jacobi termination, \S\ref{subsec:affine-shadow}).
The affine Kac--Moody family at non-critical level is the
unique standard family that reaches $\Ethree$-topological
unconditionally.
\end{remark}

\begin{remark}[$E_N$ level at the critical level $k = -h^\vee$]
\label{rem:critical-level-EN}
\index{critical level!$E_N$ obstruction}
\index{Feigin--Frenkel center!$E_N$ level}
\index{E_N ladder@$E_N$ ladder!critical level}
At $k = -h^\vee$, the Sugawara denominator $k + h^\vee$
vanishes and the conformal vector is undefined. The
$E_N$ ladder for $V_{-h^\vee}(\fg)$ terminates at
$\Etwo$-chiral:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\Eone$-chiral and $\Etwo$-chiral on the derived
 center: both automatic, as for any chiral algebra.
 At the critical level the center
 $Z^{\mathrm{der}}_{\mathrm{ch}}(V_{-h^\vee}(\fg))$
 contains the Feigin--Frenkel center $\fz(\hat\fg)$,
 which is large (isomorphic to
 $\operatorname{Fun}\operatorname{Op}_{\fg^\vee}(D^\times)$).

\item $\Etwo$-topological: \textbf{not attained}.
 Without a conformal vector, the topologization step
 (Construction~\ref{constr:topologization}) fails.
 The holomorphic direction carries nontrivial
 cohomological information that cannot be trivialized.

\item $\Ethree$-chiral and $\Ethree$-topological:
 \textbf{not attained}. The jump of the center at
 $k = -h^\vee$ obstructs both the 3d HT construction
 and the topologization.
\end{enumerate}
The critical level is stuck at $\SCchtop$ with an
enlarged center---the geometric Langlands regime. Shadow
class: $\mathbf{L}$ (the OPE pole structure is
unchanged from non-critical level; the obstruction is
to the conformal vector, not to the shadow tower).
\end{remark}

\subsection{Wakimoto realisation: bar-cobar commutes with free-field embedding}%
\label{subsec:wakimoto-ordered-bar}%
\index{Wakimoto realisation!ordered bar complex|textbf}%
\index{free-field realisation!bar-cobar compatibility}

The Wakimoto realisation of $V_k(\mathfrak{sl}_2)$ is the
free-field embedding
$\iota_W \colon V_k(\mathfrak{sl}_2) \hookrightarrow
\cH_k \otimes \beta\gamma$
into a tensor product of a Heisenberg algebra and a
$\beta\gamma$ system. The compatibility of bar-cobar with
this embedding is a worked verification of the general
principle that bar-cobar commutes with free-field realisations.

\begin{computation}[Wakimoto bar-cobar compatibility;
\ClaimStatusProvedHere]%
\label{comp:wakimoto-bar-cobar}%
\index{Wakimoto realisation!bar complex}%
\index{Wakimoto realisation!Koszul dual}%
\index{free-field realisation!bar complex}%
The Wakimoto realisation embeds the $\widehat{\mathfrak{sl}}_2$
currents into a Heisenberg field $a(z)$ (level~$k$) and a
$\beta\gamma$ pair via
\begin{equation}\label{eq:wakimoto-embedding}
\begin{aligned}
J^+(z) &\;=\; \beta(z)\,, \\
J^0(z) &\;=\; {:}\beta(z)\gamma(z){:} + a(z)\,, \\
J^-(z) &\;=\; {:}\beta(z)\gamma(z)\gamma(z){:}
 + (k+2)\,\partial\gamma(z)
 + a(z)\gamma(z)\,.
\end{aligned}
\end{equation}
The three currents satisfy the $\widehat{\mathfrak{sl}}_2$ OPE
at level~$k$ as a consequence of the free-field OPE relations
$a(z)\,a(w) \sim k/(z-w)^2$,\;
$\beta(z)\,\gamma(w) \sim 1/(z-w)$.

\smallskip
\noindent
\emph{Bar complex compatibility.}
The embedding $\iota_W$ induces a coalgebra map on bar
complexes:
\begin{equation}\label{eq:wakimoto-bar-map}
\barBch(\iota_W) \;\colon\;
\barBch(V_k(\mathfrak{sl}_2))
\;\longrightarrow\;
\barBch(\cH_k \otimes \beta\gamma)\,.
\end{equation}
The source is class~$\mathbf{L}$ (depth~$3$,
Computation~\ref{comp:lattice-voa-ordered-bar} at
$k = 1$, and the general affine case at arbitrary~$k$).
The target is the tensor product of two bar complexes:
$\barBch(\cH_k)$ (class~$\mathbf{G}$, depth~$2$)
and $\barBch(\beta\gamma)$ (class~$\mathbf{C}$,
depth~$4$ on composites).
The bar map preserves the coalgebra structure and
intertwines the bar differentials.

\smallskip
\noindent
\emph{Cobar compatibility and Koszul dual.}
Applying $\Omega^{\mathrm{ch}}$ to both sides of
\eqref{eq:wakimoto-bar-map}, the cobar functor commutes
with the embedding:
\[
\Omega^{\mathrm{ch}}(\barBch(\iota_W))
\;\colon\;
V_k(\mathfrak{sl}_2)
\;\xrightarrow{\;\sim\;}
\Omega^{\mathrm{ch}}\bigl(
\barBch(V_k(\mathfrak{sl}_2))\bigr)
\;\longrightarrow\;
\cH_k \otimes \beta\gamma\,.
\]
At the level of Koszul duals, the map induces
\begin{equation}\label{eq:wakimoto-koszul}
Y_\hbar(\mathfrak{sl}_2)
\;=\;
V_k(\mathfrak{sl}_2)^!
\;\longrightarrow\;
(\cH_k)^! \otimes (bc)
\;=\;
\mathrm{Sym}^{\mathrm{ch}}(V^*) \otimes bc\,,
\end{equation}
embedding the Yangian into a tensor product of the Heisenberg
Koszul dual and the $bc$ system. This is the Koszul-dual
shadow of the Wakimoto embedding: the Yangian inherits a
free-field presentation from the free-field realisation
of the original affine algebra.

\smallskip
\noindent
\emph{$R$-matrix compatibility.}
The Yang $R$-matrix
$R(z) = 1 + k\Omega/z$ of $V_k(\mathfrak{sl}_2)$
decomposes under the Wakimoto embedding as a product:
$R_{\mathrm{Wak}}(z) = R_{\cH}(z) \cdot R_{\beta\gamma}$,
where $R_{\cH}(z) = e^{k\hbar/z}$ (the Heisenberg
exponential $R$-matrix) and
$R_{\beta\gamma} = \mathrm{Id}$ (trivial on generators).
The Lie-bracket contributions to the $\mathfrak{sl}_2$
Casimir $\Omega$ arise from the composite sector of
$\beta\gamma$ (the ghost current $J_{bc} = {:}\beta\gamma{:}$).

\smallskip
\noindent
\emph{Depth analysis.}
The Wakimoto embedding witnesses the depth upgrade from
$\mathbf{G}$ (Heisenberg) and $\mathbf{C}$ ($\beta\gamma$)
to $\mathbf{L}$ ($V_k(\mathfrak{sl}_2)$): the simple-pole
terms in $J^-(z)$ (specifically the $a(z)\gamma(z)$ coupling)
introduce a Lie-bracket interaction that is absent in either
free-field factor alone. The composition of two abelian
systems produces a non-abelian system: the Wakimoto realisation
is the mechanism by which class~$\mathbf{G}$ components
assemble into class~$\mathbf{L}$.
\end{computation}

\subsection{The lattice VOA $V_{\sqrt{2}\Z}$: class~L from vertex operators}%
\label{subsec:lattice-voa-ordered-bar}%
\index{lattice VOA!ordered bar complex|textbf}%
\index{Koszul duality!lattice VOA}

The shadow obstruction tower atlas
(Computation~\ref{comp:shadow-tower-atlas}) lists $V_\Lambda$
as class~$\mathbf{G}$ when restricted to the momentum
sublattice (the Heisenberg currents $J_\alpha$). The full
lattice VOA $V_\Lambda$ with its vertex operators
$e^\alpha$ ($\alpha \in \Lambda$) belongs to class~$\mathbf{L}$:
the OPE of vertex operators has a simple pole producing a
Lie-bracket term, and the Jacobi identity terminates the
shadow obstruction tower at depth~$3$.

We compute the case $\Lambda = \sqrt{2}\,\Z$, the
$A_1$ root lattice, where $V_\Lambda \cong L_1(\mathfrak{sl}_2)$
(the integrable vacuum module of $\widehat{\mathfrak{sl}}_2$
at level~$1$).

\begin{computation}[Lattice VOA ordered bar complex;
\ClaimStatusProvedHere]%
\label{comp:lattice-voa-ordered-bar}%
\index{lattice VOA!A1 root lattice@$A_1$ root lattice!bar complex}%
\index{lattice VOA!depth spectrum}%
\index{Yangian!lattice VOA Koszul dual}%
The lattice $\Lambda = \sqrt{2}\,\Z$ has rank~$1$,
Gram matrix $(\alpha, \alpha) = 2$, and root system
$\Phi = \{\pm\alpha\}$ where $\alpha = \sqrt{2}$. The
lattice VOA $V_\Lambda$ has generators:
\begin{itemize}[nosep]
\item the Heisenberg current $J(z)$ with
 $J(z)\,J(w) \sim 1/(z-w)^2$
 (level $k = 1$ normalisation);
\item vertex operators $e^{\pm\alpha}(z)$ of
 conformal weight~$1$, with OPE
 \begin{align}
 e^\alpha(z)\, e^{-\alpha}(w)
 &\;\sim\;
 \frac{1}{(z-w)^2}
 \;+\;
 \frac{\alpha \cdot J(w)}{z-w}\,,
 \label{eq:lattice-vertex-ope}
 \\[3pt]
 J(z)\, e^{\pm\alpha}(w)
 &\;\sim\;
 \frac{\pm\alpha\, e^{\pm\alpha}(w)}{z-w}\,,
 \label{eq:lattice-current-vertex-ope}
 \\[3pt]
 e^{\alpha}(z)\, e^{\alpha}(w)
 &\;\sim\; 0\,.
 \label{eq:lattice-vertex-vertex-vanishing}
 \end{align}
\end{itemize}
The isomorphism $V_\Lambda \cong L_1(\mathfrak{sl}_2)$
sends $J \mapsto h/\sqrt{2}$,
$e^\alpha \mapsto e$, $e^{-\alpha} \mapsto f$,
recovering the $\widehat{\mathfrak{sl}}_2$ OPE at $k = 1$.

\smallskip
\noindent
\emph{Depth spectrum: $\{1,2\}$.}
The OPE~\eqref{eq:lattice-vertex-ope} has both a double pole
(depth~$1$, the Killing form: $\kappa(e^\alpha, e^{-\alpha}) = 1$)
and a simple pole (depth~$2$, the Lie bracket:
$[e^\alpha, e^{-\alpha}] = \alpha \cdot J$). The depth spectrum
is $\{1, 2\}$, matching $V_k(\mathfrak{sl}_2)$ at $k = 1$.
This is class~$\mathbf{L}$, not class~$\mathbf{G}$:
the vertex operators lift the momentum algebra from depth~$\{1\}$
to depth~$\{1,2\}$.
The Virasoro sub-sector is absent (no weight-$2$ generator), so the weight-depth identity (Theorem~\ref{thm:gap-migration}(i)) is vacuously satisfied; the depth spectrum is controlled by the Lie bracket truncation instead.

\smallskip
\noindent
\emph{Operations: $m_3 \ne 0$, $m_4 = 0$.}
The binary operation decomposes as
$m_2(e^\alpha, e^{-\alpha};\, \lambda)
= \lambda + \alpha \cdot J$
(double pole $\leadsto \lambda$; simple pole $\leadsto$ Lie bracket).
The ternary operation $m_3$ is nonzero on the triple
$(e^\alpha, e^{-\alpha}, e^\alpha)$: the iterated OPE
produces a Lie-bracket composition
$[e^\alpha, [e^{-\alpha}, e^\alpha]] = [e^\alpha, -\alpha J]
= +\alpha^2\, e^\alpha = 2\, e^\alpha$.
The quartic operation $m_4 = 0$ by the Jacobi identity:
the weight $2\alpha$ is not a root
($e^{2\alpha}$ does not exist in the lattice VOA
since $(2\alpha, 2\alpha) = 8 > 2$), forcing the
obstruction to vanish. The tower terminates at depth~$3$.

\smallskip
\noindent
\emph{$r$-matrix and Koszul dual.}
The collision residue is
$r(z) = k\,\Omega/z$ at $k = 1$, where
$\Omega = e^\alpha \otimes e^{-\alpha}
+ e^{-\alpha} \otimes e^{\alpha}
+ \tfrac{1}{2} J \otimes J$
is the $\mathfrak{sl}_2$ Casimir and $k = 1$ is the
lattice level (the $k = 0$ limit gives the abelian
Heisenberg r-matrix $r = 0$ on the Cartan, consistent
).
The quantisation of $r(z) = k\,\Omega/z$ is the
Yang $R$-matrix $R(z) = 1 + k\hbar\,\Omega/z$,
and the Koszul dual is the Yangian
$Y_{1/3}(\mathfrak{sl}_2)$
(the $k = 1$ specialisation of the general affine
Koszul dual
$A^! = Y_\hbar^{\mathrm{dg}}(\fg)$).

\smallskip
\noindent
\emph{Serre relation = root-space vanishing.}
The Serre relation $[e^\alpha, [e^\alpha, e^{-\alpha}]] = 0$
has a root-space origin: $2\alpha - \alpha = \alpha$ is a root,
but $[e^\alpha, e^\alpha] = 0$
(equation~\eqref{eq:lattice-vertex-vertex-vanishing})
because $(\alpha, \alpha) = 2 > 0$ (same-sign vertex
operators have no singular OPE). In the bar complex,
this forces the degree-$3$ element
$[s^{-1}e^\alpha\,|\,s^{-1}e^\alpha\,|\,s^{-1}e^{-\alpha}]$
to be exact, by the same mechanism as the $\mathfrak{sl}_3$
Serre relation
(Computation~\ref{comp:sl3-yangian-triangle}).

\smallskip
\noindent
\emph{Genus-$1$.}
Since $c_0 = \Omega \ne 0$ (the Lie bracket is
nonvanishing), the lattice VOA at level~$1$ is
propagator-entangled at genus~$1$: the $r$-matrix
becomes elliptic,
$r^{E_\tau}(z) = \Omega \cdot \zeta(z|\tau) + \kappa \cdot \wp(z|\tau)$,
with $B$-cycle monodromy $2\eta_\tau \cdot \Omega$.
The shadow Hessian is $S_2 = c/2 = 1/2$
(the $k = 1$, $\mathfrak{sl}_2$ value:
$S_2 = \dim(\mathfrak{sl}_2)\cdot k/(2(k+h^\vee)) = 3/(2 \cdot 3) = 1/2$;
the Volume~I modular characteristic is
$\kappa = \dim(\mathfrak{sl}_2)(k+h^\vee)/(2h^\vee) = 9/4$).
\end{computation}

\begin{remark}[Lattice atlas correction]%
\label{rem:lattice-atlas-correction}%
\index{lattice VOA!atlas classification}%
The shadow obstruction tower atlas entry for $V_\Lambda$ as
class~$\mathbf{G}$ (depth~$2$) applies to the
\emph{momentum sublattice} only: the Heisenberg
currents $J_i(z)$ ($i = 1, \ldots, \operatorname{rk}(\Lambda)$)
with $J_i(z)\, J_j(w) \sim (\alpha_i, \alpha_j)/(z-w)^2$
have scalar OPE residues and no simple pole. The
full lattice VOA with vertex operators $e^\alpha$
($\alpha \in \Lambda$) is class~$\mathbf{L}$ whenever
$\Lambda$ has roots: the simple-pole OPE
$e^\alpha(z)\,e^{-\alpha}(w) \sim \cdots + (\alpha \cdot J)/(z-w)$
introduces a Lie bracket. The atlas entry is refined
accordingly: $V_\Lambda(\mathrm{mom.})$ is
class~$\mathbf{G}$; $V_\Lambda(\mathrm{v.o.})$ is
class~$\mathbf{L}$.
\end{remark}

\begin{computation}[$A_2$ lattice VOA ordered bar complex;
\ClaimStatusProvedHere]%
\label{comp:lattice-voa-A2-ordered-bar}%
\index{lattice VOA!A2 root lattice@$A_2$ root lattice!bar complex}%
\index{lattice VOA!rank 2}%
\index{Yangian!sl3@$\mathfrak{sl}_3$!from lattice VOA}%
The $A_2$ root lattice $\Lambda = \Z\alpha_1 \oplus \Z\alpha_2$
with Gram matrix
$\bigl(\begin{smallmatrix} 2 & -1 \\ -1 & 2
\end{smallmatrix}\bigr)$
has rank~$2$, root system $\Phi = \{\pm\alpha_1, \pm\alpha_2,
\pm(\alpha_1+\alpha_2)\}$ of type~$A_2$, and the lattice VOA
$V_\Lambda \cong L_1(\mathfrak{sl}_3)$ is the integrable vacuum
module of $\widehat{\mathfrak{sl}}_3$ at level~$1$.

\smallskip
\noindent
\emph{Generators.}
Two Heisenberg currents $J_1, J_2$ spanning the Cartan,
and six vertex operators $e^{\pm\alpha_1}, e^{\pm\alpha_2},
e^{\pm(\alpha_1+\alpha_2)}$ of conformal weight~$1$,
giving $\dim(\fg) = 8$ generators total.
The OPE structure:
\begin{align}
J_i(z)\,J_j(w) &\;\sim\; \frac{(\alpha_i,\alpha_j)}{(z-w)^2}\,,
\label{eq:A2-cartan-ope}
\\[3pt]
J_i(z)\,e^{\pm\alpha_j}(w) &\;\sim\;
\frac{\pm(\alpha_i,\alpha_j)\,e^{\pm\alpha_j}(w)}{z-w}\,,
\\[3pt]
e^{\alpha_i}(z)\,e^{-\alpha_j}(w)
&\;\sim\;
\delta_{ij}\biggl(
\frac{1}{(z-w)^2}
+ \frac{\alpha_i \cdot J(w)}{z-w}\biggr)
+ (1-\delta_{ij})\,
\frac{\epsilon_{ij}\,e^{\alpha_i-\alpha_j}(w)}{z-w}\,,
\label{eq:A2-vertex-ope}
\end{align}
where $\epsilon_{ij} = \pm 1$ is the cocycle sign
($\epsilon_{12} = 1$, $\epsilon_{21} = -1$). The composite
root vertex operator satisfies
$e^{\alpha_1+\alpha_2} = [e^{\alpha_1}, e^{\alpha_2}]$
(the Lie bracket).

\smallskip
\noindent
\emph{Depth spectrum: $\{1,2\}$, class~$\mathbf{L}$, depth~$3$.}
As for $A_1$, the double poles between opposite-root vertex
operators give depth~$1$ (Killing form) and the simple poles
give depth~$2$ (Lie bracket). The quartic operation $m_4 = 0$
by the Jacobi identity:
the weight $2\alpha_1 + \alpha_2$ is a non-root weight of
$\mathfrak{sl}_3$ at height~$3$ (dimension count: $\dim(\fg_{2\alpha_1+\alpha_2}) = 0$),
so the iterated bracket vanishes by the same mechanism as
Computation~\ref{comp:sl3-yangian-triangle}.
The tower terminates at depth~$3$. This is class~$\mathbf{L}$.
As for the $A_1$ lattice, no Virasoro sub-sector exists on generators, so the weight-depth identity (Theorem~\ref{thm:gap-migration}(i)) is vacuously satisfied.

\smallskip
\noindent
\emph{Operations: $m_2$ table.}
The nonvanishing $m_2$ operations on Chevalley generators:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lll}
\toprule
\textbf{Pair} & $m_2(a,b;\lambda)$ & \textbf{Source} \\
\midrule
$(e^{\alpha_i}, e^{-\alpha_i})$ & $\lambda + \alpha_i \cdot J$
 & double + simple pole \\
$(e^{\alpha_1}, e^{-\alpha_2})$ & $e^{\alpha_1-\alpha_2}$
 & simple pole \\
$(e^{\alpha_2}, e^{-\alpha_1})$ & $-e^{\alpha_2-\alpha_1}$
 & simple pole \\
$(J_i, J_j)$ & $(\alpha_i,\alpha_j)\,\lambda$
 & double pole \\
\bottomrule
\end{tabular}
\end{center}
All $m_k = 0$ for $k \ge 4$. The ternary operation $m_3$ is
nonzero on triples involving the composite root, e.g.\
$m_3(e^{\alpha_1}, e^{-\alpha_1}, e^{\alpha_2})
= -(\alpha_1,\alpha_2)\,e^{\alpha_2} = e^{\alpha_2}$.

\smallskip
\noindent
\emph{$R$-matrix and Koszul dual.}
The collision residue is the $\mathfrak{sl}_3$ classical
$r$-matrix:
$r(z) = k\,\Omega_{\mathfrak{sl}_3}/z$,
where $\Omega_{\mathfrak{sl}_3}$ is the quadratic Casimir
of~$\mathfrak{sl}_3$; at level~$k=1$ the collision residue is $\Omega_{\mathfrak{sl}_3}/z$. The spectral $R$-matrix is
the Yang $R$-matrix
\begin{equation}\label{eq:A2-lattice-R}
R(z) \;=\; 1 + \frac{\hbar\,\Omega_{\mathfrak{sl}_3}}{z}\,.
\end{equation}
The Koszul dual is the Yangian
$Y_\hbar(\mathfrak{sl}_3)$.

\smallskip
\noindent
\emph{Poincar\'{e} series and Euler characteristic.}
$P(t) = 1 + 8t$ (eight cogenerators in degree~$1$,
corresponding to the $\dim(\mathfrak{sl}_3) = 8$
desuspended generators). The shadow Hessian
$S_2 = 4k/(k+3)\big|_{k=1} = 1$, matching the
general affine formula
$S_2(V_k(\fg)) = c(\fg)/2 = \dim(\fg) \cdot k/(2(k+h^\vee))$
with $h^\vee = 3$. (As in the landscape table on
p.~\pageref{comp:e1-ordered-bar-landscape}, we record
$S_2 = c/2$ rather than the Volume~I modular characteristic
$\kappa = \dim(\fg)(k+h^\vee)/(2h^\vee)$, which for
$\mathfrak{sl}_3$ at $k = 1$ gives
$\kappa = 8 \cdot 4/6 = 16/3 \ne S_2$.)

\smallskip
\noindent
\emph{Genus-$1$.}
Since $c_0 = \Omega_{\mathfrak{sl}_3} \ne 0$ (the
Lie bracket is nonvanishing), the $A_2$ lattice VOA is
propagator-entangled at genus~$1$. The elliptic $r$-matrix is
$r^{E_\tau}(z) = \Omega_{\mathfrak{sl}_3}\cdot\zeta(z|\tau)
+ \kappa\cdot\wp(z|\tau)$,
with $B$-cycle monodromy $2\eta_\tau\cdot\Omega_{\mathfrak{sl}_3}$.
\end{computation}

\begin{computation}[$D_4$ lattice VOA: triality and ordered bar;
\ClaimStatusProvedHere]%
\label{comp:lattice-voa-D4-ordered-bar}%
\index{lattice VOA!D4 root lattice@$D_4$ root lattice!bar complex}%
\index{lattice VOA!triality}%
\index{triality!lattice VOA bar complex}%
The $D_4$ root lattice $\Lambda_{D_4}$ has rank~$4$,
$|\Phi| = 24$ roots, and the lattice VOA
$V_{\Lambda_{D_4}} \cong L_1(\mathfrak{so}_8)$ is the
integrable vacuum module of $\widehat{\mathfrak{so}}_8$ at
level~$1$. This is the first lattice VOA where \emph{triality}
(the $S_3$ outer automorphism of $D_4$) is visible.

\smallskip
\noindent
\emph{Generators.}
Four Heisenberg currents $J_1, \ldots, J_4$ spanning the Cartan,
and $24$ vertex operators $e^\alpha$ ($\alpha \in \Phi_{D_4}$) of
conformal weight~$1$, giving $\dim(\mathfrak{so}_8) = 28$ generators.
The OPE has the same structure as~\eqref{eq:A2-vertex-ope}
with the $D_4$ Killing form and structure constants.

\smallskip
\noindent
\emph{Depth spectrum: $\{1,2\}$, class~$\mathbf{L}$, depth~$3$.}
As for all simply-laced root lattices at level~$1$, the double
poles (Killing form) give depth~$1$ and the simple poles
(Lie bracket) give depth~$2$. The quartic operation $m_4 = 0$
by the Jacobi identity. Class~$\mathbf{L}$, depth~$3$.
The weight-depth identity (Theorem~\ref{thm:gap-migration}(i)) is vacuously satisfied on the affine generators; the depth spectrum is controlled by the Jacobi termination mechanism.

\smallskip
\noindent
\emph{$R$-matrix and Koszul dual.}
The collision residue is $r(z) = k\,\Omega_{\mathfrak{so}_8}/z$.
The spectral $R$-matrix is
\begin{equation}\label{eq:D4-lattice-R}
R(z) \;=\; 1 + \frac{\hbar\,\Omega_{\mathfrak{so}_8}}{z}\,.
\end{equation}
The Koszul dual is $Y_\hbar(\mathfrak{so}_8)$.

\smallskip
\noindent
\emph{Triality.}
The outer automorphism group $\mathrm{Out}(D_4) \cong S_3$
permutes the three $8$-dimensional representations:
the vector $\mathbf{8}_v$, the spinor $\mathbf{8}_s$, and
the co-spinor $\mathbf{8}_c$. At the level of the bar complex:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item Triality permutes the vertex operators:
 $\sigma \colon e^{\alpha} \mapsto e^{\sigma(\alpha)}$
 for $\sigma \in S_3$.
\item The collision residue $r(z) = k\,\Omega/z$ is triality-invariant
 ($\Omega_{\mathfrak{so}_8}$ is the unique quadratic
 Casimir, hence $S_3$-invariant).
\item The Yangian $Y_\hbar(\mathfrak{so}_8)$ inherits triality:
 the evaluation representation $V(u)$ in the vector
 representation is isomorphic to $V_s(u)$ in the spinor
 representation and $V_c(u)$ in the co-spinor representation,
 as Yangian modules.
\end{enumerate}
Triality is a symmetry of the ordered bar complex that does
\emph{not} descend from an inner automorphism: it is the
bar-complex shadow of the exceptional Dynkin diagram symmetry.

\smallskip
\noindent
\emph{Poincar\'{e} series.}
$P(t) = 1 + 28t$ ($\dim(\mathfrak{so}_8) = 28$ cogenerators).
Shadow Hessian
$S_2 = \dim(\fg)\cdot k/(2(k+h^\vee)) = 28/(2 \cdot 7) = 2$
(using $\dim(\mathfrak{so}_8) = 28$, $k = 1$, $h^\vee(D_4) = 6$);
equivalently $S_2 = c/2 = 4/2 = 2$.

\smallskip
\noindent
\emph{Genus-$1$.}
Propagator-entangled ($c_0 = \Omega_{\mathfrak{so}_8} \ne 0$).
The genus-$1$ partition function
$Z_1(V_{\Lambda_{D_4}}) = (\Theta_{D_4}(\tau)/\eta(\tau)^4)$,
where $\Theta_{D_4}$ is the $D_4$ theta function.
Triality permutes the three conjugacy classes of $D_4$
lattice cosets, corresponding to the three modular-invariant
partition functions (diagonal, spinor, co-spinor) of the
$\widehat{\mathfrak{so}}_8$ WZW model at level~$1$.
\end{computation}

\subsection{The $\beta\gamma$ system: class~C and statistics exchange}%
\label{subsec:betagamma-ordered-bar}%
\index{beta-gamma system@$\beta\gamma$ system!ordered bar complex|textbf}%
\index{Koszul duality!beta-gamma-bc@$\beta\gamma$--$bc$}

The $\beta\gamma$ system is the simplest chiral algebra of
class~$\mathbf{C}$: it has a non-scalar quartic contact
invariant but the tower terminates at depth~$4$ by
rank-$1$ abelian rigidity.

\begin{computation}[$\beta\gamma$ ordered bar complex;
\ClaimStatusProvedHere]%
\label{comp:betagamma-ordered-bar}%
\index{beta-gamma system@$\beta\gamma$ system!R-matrix}%
\index{beta-gamma system@$\beta\gamma$ system!Koszul dual}%
\index{beta-gamma system@$\beta\gamma$ system!depth spectrum}%
The $\beta\gamma$ system has two generators:
$\beta$ of conformal weight~$\lambda$ and
$\gamma$ of conformal weight~$1-\lambda$, with OPE
\begin{equation}\label{eq:betagamma-ope}
\beta(z)\,\gamma(w)
\;\sim\;
\frac{1}{z-w}\,,
\qquad
\beta(z)\,\beta(w) \sim 0,
\qquad
\gamma(z)\,\gamma(w) \sim 0.
\end{equation}
Central charge $c(\beta\gamma) = 2(6\lambda^2 - 6\lambda + 1)$.
At $\lambda = 1/2$: $c = -1$.

\smallskip
\noindent
\emph{Depth spectrum: $\{0\}$ on generators.}
The OPE~\eqref{eq:betagamma-ope} has a single simple pole.
the $d\log$ kernel absorbs one power: the
collision residue is $r^{\mathrm{coll}} = 1$ (a constant,
depth~$0$). On generators, all $m_k = 0$ for
$k \ge 3$: there are no iterated OPE singularities
because $\beta\beta$ and $\gamma\gamma$ are regular.
The depth spectrum on generators is $\{0\}$.

The shadow obstruction tower atlas records depth~$4$ for $\beta\gamma$
because the \emph{composite} quasi-primary
$\Lambda = {:}\beta\gamma{:}$ (the $U(1)$ ghost current)
mediates a quartic exchange at weight~$4$. On the
composite sector, the $\beta\gamma$ system behaves like
class~$\mathbf{C}$
(Theorem~\ref{thm:pole-structure-dichotomy}(iii)).
On generators, $m_2(\beta,\gamma;\lambda) = 1$ is a depth-$0$ constant: the weight-depth identity (Theorem~\ref{thm:gap-migration}(i)) is trivially satisfied ($w = 0$, $d = 0$, consistent with degree~$2$ and the simple-pole absorption ).

\smallskip
\noindent
\emph{$R$-matrix: trivial.}
The collision residue is a constant ($r = 1$, depth~$0$):
the connection on $\Conf_2^{\mathrm{ord}}(\C)$ is
$\nabla = d$ (flat), and the $R$-matrix is the identity:
\begin{equation}\label{eq:betagamma-R}
R(z) \;=\; \mathrm{Id}.
\end{equation}
The $\beta\gamma$ OPE on generators has only a simple pole,
and the $d\log$ absorption reduces it to a constant:
the generator-level $R$-matrix is trivial. This is the
simple-pole sub-stratum within tier~(ii) of the three-tier
picture ($\S$\ref{subsec:ordered-three-tier}):
the algebra is $\Einf$-chiral (local, with OPE singularities),
but the simple-pole structure makes the generator-level
braiding trivial.

\smallskip
\noindent
\emph{Koszul dual: $bc = \bigwedge^{\mathrm{ch}}(V)$.}
The chiral $\mathrm{Ext}/\mathrm{Sym}$ duality
(Remark~\ref{rem:rosetta-bc-betagamma-koszul})
exchanges statistics:
\begin{equation}\label{eq:betagamma-koszul-dual}
\beta\gamma_\lambda^!
\;=\;
bc_\lambda\,,
\qquad
bc_\lambda^!
\;=\;
\beta\gamma_\lambda\,.
\end{equation}
The $\beta\gamma$ system is the chiral symmetric algebra
$\mathrm{Sym}^{\mathrm{ch}}(V)$
on $V = \C\beta \oplus \C\gamma$ (bosonic); its
Koszul dual is the chiral exterior algebra
$\bigwedge^{\mathrm{ch}}(V^*)$ (fermionic), which is the
$bc$ ghost system.
The Poincar\'{e} series is $P(t) = 1 + 2t$
(two cogenerators $s^{-1}\beta$ and $s^{-1}\gamma$
in degree~$1$).

\smallskip
\noindent
\emph{Complementarity: $\kappa(\beta\gamma_\lambda) + \kappa(bc_\lambda) = 0$.}
The modular characteristics are
$\kappa(\beta\gamma_\lambda) = 6\lambda^2 - 6\lambda + 1$ and
$\kappa(bc_\lambda) = -(6\lambda^2 - 6\lambda + 1)$.
Their sum vanishes:
$K(\beta\gamma_\lambda) = \kappa(\beta\gamma_\lambda) + \kappa(bc_\lambda) = 0$.
This is the free-field instance of the affine-lineage
complementarity $K = 0$
(Proposition~\ref{prop:rosetta-complementarity}).
The central charges also satisfy
$c(\beta\gamma) + c(bc)
= 2(6\lambda^2 - 6\lambda + 1) - 2(6\lambda^2 - 6\lambda + 1) = 0$
for all~$\lambda$.

\smallskip
\noindent
\emph{Genus-$1$.}
Since the zeroth product
$\beta_{(0)}\gamma = 1 \ne 0$ (the simple-pole OPE
residue is nonvanishing), we have $c_0 \ne 0$: the
$\beta\gamma$ system is propagator-entangled at genus~$1$.
The symplectic Casimir $\Omega_{\mathrm{symp}}
= \beta \otimes \gamma - \gamma \otimes \beta$
replaces the Lie-algebra Casimir in the elliptic
$r$-matrix formula. The curvature is
$\kappa(\beta\gamma_\lambda) = 6\lambda^2 - 6\lambda + 1$.
\end{computation}

\subsection{The free fermion $\psi$: class~G on generators, class~C full}%
\label{subsec:free-fermion-ordered-bar}%
\index{free fermion!ordered bar complex|textbf}%
\index{Koszul duality!free fermion}

The free fermion $\psi$ of conformal weight~$1/2$ is the
simplest fermionic chiral algebra. On generators it is
class~$\mathbf{G}$ (the OPE $\psi(z)\,\psi(w) \sim 1/(z-w)$
is a single simple pole, and the $d\log$ kernel absorbs it
to a constant). The full algebra, including the composite
$J = {:}\psi\psi{:}$ (a weight-$1$ boson), is class~$\mathbf{C}$
because $J$ mediates a quartic exchange.

\begin{computation}[Free fermion ordered bar complex;
\ClaimStatusProvedHere]%
\label{comp:free-fermion-ordered-bar}%
\index{free fermion!R-matrix}%
\index{free fermion!Koszul dual}%
\index{free fermion!depth spectrum}%
The free fermion has a single generator $\psi$ of conformal
weight~$1/2$ (fermionic), with OPE
\begin{equation}\label{eq:free-fermion-ope}
\psi(z)\,\psi(w) \;\sim\; \frac{1}{z-w}\,.
\end{equation}
Central charge $c(\psi) = 1/2$.

\smallskip
\noindent
\emph{Operations.}
The single nonvanishing operation on generators is
$m_2(\psi,\psi;\,\lambda) = 1$
(the simple-pole residue is the identity pairing).
All $m_k = 0$ for $k \ge 3$ on generators: the OPE
$\psi(z)\,\psi(w)$ has only a simple pole, and the
iterated collision $\psi\,\psi\,\psi$ vanishes by
fermionic antisymmetry. On the composite sector
($J = {:}\psi\psi{:}$, $T = \tfrac{1}{2}{:}\partial\psi\,\psi{:}$),
the OPE $J(z)\,J(w) \sim 1/(z-w)^2$ introduces a
Heisenberg-type double pole, and $T(z)\,T(w)$ has the
Virasoro quartic pole at $c = 1/2$. The full algebra is
class~$\mathbf{C}$ with depth~$4$ on composites.

\smallskip
\noindent
\emph{Depth spectrum: $\{0\}$ on generators.}
The $d\log$ kernel absorbs the simple pole:
$r^{\mathrm{coll}} = 1$ (constant, depth~$0$).
On generators the depth spectrum is $\{0\}$, matching
$\beta\gamma$ (Computation~\ref{comp:betagamma-ordered-bar}).
The full depth spectrum including composites is $\{0,1,4\}$.
On the composite Virasoro sector ($T = \tfrac{1}{2}{:}\partial\psi\,\psi{:}$, $c = 1/2$), the weight-depth identity $w + d = n - 1$ (Theorem~\ref{thm:gap-migration}(i)) applies to the induced $\Ainf$ operations.

\smallskip
\noindent
\emph{$R$-matrix: trivial on generators.}
Since $r^{\mathrm{coll}} = 1$ (a scalar constant), the connection
on $\Conf_2^{\mathrm{ord}}(\C)$ is flat: $\nabla = d$.
The $R$-matrix on generators is
\begin{equation}\label{eq:free-fermion-R}
R(z) \;=\; \tau \qquad\text{(Koszul-signed flip)},
\end{equation}
where $\tau(a \otimes b) = (-1)^{|a||b|}\,b \otimes a$ is the
graded transposition. The minus sign in
$\psi \otimes \psi \mapsto -\psi \otimes \psi$
encodes the fermionic statistics. This is the simple-pole
sub-stratum within tier~(ii): the OPE has a singularity,
but $d\log$ absorption makes the generator-level
$R$-matrix the Koszul-signed flip.

\smallskip
\noindent
\emph{Koszul dual: $\beta\gamma_{1/2}$.}
The free fermion is the chiral exterior algebra
$\bigwedge^{\mathrm{ch}}(\C\psi)$ (a single fermionic
generator). Its Koszul dual is the chiral symmetric
algebra on the dual:
\begin{equation}\label{eq:free-fermion-koszul}
\psi^! \;=\; \beta\gamma_{1/2}\,.
\end{equation}
The Koszul dual exchanges statistics
(fermionic~$\to$~bosonic) and preserves the
conformal weight~$1/2$. This is the single-generator
case of the $bc$--$\beta\gamma$ duality
(Remark~\ref{rem:rosetta-bc-betagamma-koszul}).

\smallskip
\noindent
\emph{Bar cohomology.}
The bar complex $\barBch(\psi)$ on generators is the
cofree coalgebra on a single fermionic desuspended generator
$s^{-1}\psi$. Since $m_2(\psi,\psi) = 1$ is a nondegenerate
pairing, $H_1(\barBch) = 0$: the single generator is
exact. The bar cohomology in higher degrees is
$H_n(\barBch) \cong \C$ for $n = 0$ and
$H_n(\barBch) = 0$ for $n \ge 1$ on generators
(the pairing is perfect). Including composites, the
bar cohomology is large: $H_n \ne 0$ for $n \ge 3$
(the quartic exchanges on composites generate
nontrivial cohomology classes).

\smallskip
\noindent
\emph{Poincar\'{e} series and Euler characteristic.}
$P(t) = 1 + t$ (single cogenerator in degree~$1$).
Modular characteristic $\kappa(\psi) = 1/4$
(from $c = 1/2$ and the free-fermion curvature formula).
Complementarity: $\kappa(\psi) + \kappa(\beta\gamma_{1/2})
= 1/4 + (-1/4) = 0$, matching the free-field pattern.

\smallskip
\noindent
\emph{Genus-$1$.}
The zeroth product $\psi_{(0)}\psi = 1 \ne 0$
(the simple-pole residue), so $c_0 \ne 0$: the free fermion is
propagator-entangled at genus~$1$. The genus-$1$ partition function
$Z_1(\psi) = \sqrt{\theta_3(\tau)/\eta(\tau)}$
(the NS-sector character), encoding the
theta-function/eta-function ratio characteristic of
free fermions.
\end{computation}

\subsection{The $bc$ ghost system: class~G on generators, weight-$\lambda$ landscape}%
\label{subsec:bc-ordered-bar}%
\index{bc ghost system!ordered bar complex|textbf}%
\index{Koszul duality!bc ghost}

The $bc$ ghost system at general conformal weight~$\lambda$
is the fermionic partner of $\beta\gamma_\lambda$
(Remark~\ref{rem:rosetta-bc-betagamma-koszul}). The OPE
is the same for all~$\lambda$; the conformal weight affects
only the stress tensor.

\begin{computation}[$bc$ ghost system ordered bar complex;
\ClaimStatusProvedHere]%
\label{comp:bc-ordered-bar}%
\index{bc ghost system!R-matrix}%
\index{bc ghost system!Koszul dual}%
\index{bc ghost system!depth spectrum}%
The $bc$ system has two generators: $b$ of conformal
weight~$\lambda$ and $c$ of conformal weight~$1-\lambda$
(both fermionic), with OPE
\begin{equation}\label{eq:bc-ope}
b(z)\,c(w)
\;\sim\;
\frac{1}{z-w}\,,
\qquad
b(z)\,b(w) \sim 0,
\qquad
c(z)\,c(w) \sim 0.
\end{equation}
Central charge $c(bc) = -2(6\lambda^2 - 6\lambda + 1)$.
At $\lambda = 2$: $c = -26$ (reparametrisation ghosts).

\smallskip
\noindent
\emph{Operations.}
The nonvanishing operation is
$m_2(b,c;\,\lambda) = 1$ (simple-pole residue).
All $m_k = 0$ for $k \ge 3$ on generators: the OPE has
only a simple pole, and $bb$, $cc$ are regular (vanish by
fermionic antisymmetry). On composites
($J_{bc} = {:}bc{:}$, $T = \lambda\,{:}\partial b\,c{:}
+ (1-\lambda)\,{:}b\,\partial c{:}$), the full algebra
is class~$\mathbf{C}$ with depth~$4$ (the ghost current
$J_{bc}$ mediates a quartic exchange).

\smallskip
\noindent
\emph{Depth spectrum: $\{0\}$ on generators.}
The $d\log$ kernel absorbs the simple pole:
$r^{\mathrm{coll}} = 1$ (constant, depth~$0$).
On generators the depth spectrum is $\{0\}$; on the composite Virasoro sector, the weight-depth identity $w + d = n - 1$ (Theorem~\ref{thm:gap-migration}(i)) applies.

\smallskip
\noindent
\emph{$R$-matrix: trivial on generators.}
\begin{equation}\label{eq:bc-R}
R(z) \;=\; \mathrm{Id}\,.
\end{equation}
As for $\beta\gamma$, the generators see only a simple pole
whose $d\log$ absorption gives a constant. On the composite
sector the $R$-matrix acquires nontrivial spectral
dependence.

\smallskip
\noindent
\emph{Koszul dual: $\beta\gamma_\lambda$.}
The $bc$ system is the chiral exterior algebra
$\bigwedge^{\mathrm{ch}}(V)$ on
$V = \C b \oplus \C c$ (fermionic); its Koszul dual is
the chiral symmetric algebra
$\mathrm{Sym}^{\mathrm{ch}}(V^*)$ (bosonic):
\begin{equation}\label{eq:bc-koszul-dual}
bc_\lambda^! \;=\; \beta\gamma_\lambda\,,
\qquad
\beta\gamma_\lambda^! \;=\; bc_\lambda\,.
\end{equation}
This is independent of~$\lambda$: the Koszul duality
exchanges statistics, not conformal weights.

\smallskip
\noindent
\emph{Weight-$\lambda$ landscape.}
The central charge
$c(\lambda) = -2(6\lambda^2 - 6\lambda + 1)$ is a quadratic
in~$\lambda$ with roots at $\lambda = (3 \pm \sqrt{3})/6$.
Key specialisations:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{ccll}
\toprule
$\lambda$ & $c(bc)$ & \textbf{Physics} & \textbf{Koszul dual} \\
\midrule
$1/2$ & $1$ & Ising fermion ghost & $\beta\gamma_{1/2}$ \\
$1$ & $-2$ & scalar ghost & $\beta\gamma_1$ \\
$3/2$ & $-11$ & spin-$3/2$ ghost & $\beta\gamma_{3/2}$ \\
$2$ & $-26$ & reparametrisation ghost & $\beta\gamma_2$ (graviton) \\
$5/2$ & $-47$ & spin-$5/2$ ghost & $\beta\gamma_{5/2}$ \\
\bottomrule
\end{tabular}
\end{center}
At $\lambda = 2$: the Koszul dual of the reparametrisation
ghost $bc_2$ ($c = -26$) is the bosonic spin-$2$ system
$\beta\gamma_2$ ($c = +26$). A spin-$2$ boson is a
symmetric tensor field, a graviton.

\smallskip
\noindent
\emph{Complementarity.}
$\kappa(bc_\lambda) = -(6\lambda^2 - 6\lambda + 1)$ and
$\kappa(\beta\gamma_\lambda) = 6\lambda^2 - 6\lambda + 1$.
The complementarity sum
$K(bc_\lambda) = \kappa(bc_\lambda) + \kappa(\beta\gamma_\lambda) = 0$
vanishes universally. The central charges satisfy
$c(bc_\lambda) + c(\beta\gamma_\lambda) = 0$ for all~$\lambda$.

\smallskip
\noindent
\emph{Poincar\'{e} series.}
$P(t) = 1 + 2t$ (two cogenerators $s^{-1}b, s^{-1}c$).

\smallskip
\noindent
\emph{Genus-$1$.}
$b_{(0)}c = 1 \ne 0$, so $c_0 \ne 0$: the $bc$ system is
propagator-entangled at genus~$1$. The curvature is
$\kappa(bc_\lambda) = -(6\lambda^2 - 6\lambda + 1)$. The genus-$1$ partition function
$Z_1(bc_\lambda) = \eta(\tau)^{2(6\lambda^2-6\lambda+1)}$
(the eta function raised to the power $-c$).
\end{computation}

\subsection{Symplectic bosons: class~C and depth~$4$}%
\label{subsec:symplectic-boson-ordered-bar}%
\index{symplectic bosons!ordered bar complex|textbf}%
\index{Koszul duality!symplectic bosons}

The symplectic boson system (also called the $\beta\gamma$
system at half-integer weight in the physics literature,
or the bosonic ghost system) at weight~$1/2$ is
class~$\mathbf{C}$ with depth~$4$. It provides the
bosonic analogue of the free fermion
(Computation~\ref{comp:free-fermion-ordered-bar}).

\begin{computation}[Symplectic boson ordered bar complex;
\ClaimStatusProvedHere]%
\label{comp:symplectic-boson-ordered-bar}%
\index{symplectic bosons!R-matrix}%
\index{symplectic bosons!Koszul dual}%
\index{symplectic bosons!depth spectrum}%
The symplectic boson system has two generators
$\chi^+, \chi^-$ of conformal weight~$1/2$ (bosonic),
with OPE
\begin{equation}\label{eq:symplectic-boson-ope}
\chi^+(z)\,\chi^-(w) \;\sim\; \frac{1}{z-w}\,,
\qquad
\chi^+(z)\,\chi^+(w) \sim 0,
\qquad
\chi^-(z)\,\chi^-(w) \sim 0.
\end{equation}
Central charge $c(\chi) = -1$:
$c = 2(6 \cdot (1/2)^2 - 6 \cdot (1/2) + 1) = 2(-1/2) = -1$,
the same as $\beta\gamma$ at $\lambda = 1/2$.

\smallskip
\noindent
\emph{Operations.}
$m_2(\chi^+, \chi^-;\,\lambda) = 1$ (simple-pole residue).
All $m_k = 0$ for $k \ge 3$ on generators. The OPE on
generators has only a simple pole, and $\chi^+\chi^+$,
$\chi^-\chi^-$ are regular. On composites
($J = {:}\chi^+\chi^-{:}$), the ghost current $J$ mediates
a quartic exchange at depth~$4$.

\smallskip
\noindent
\emph{Depth spectrum: $\{0\}$ on generators; depth~$4$ full.}
The collision residue is $r^{\mathrm{coll}} = 1$ (constant).
On generators, depth~$\{0\}$; the weight-depth identity (Theorem~\ref{thm:gap-migration}(i)) is trivially satisfied at degree~$2$. The composite sector has
depth~$4$ (class~$\mathbf{C}$), the same as
$\beta\gamma$, confirming that depth is controlled by
OPE structure, not statistics.

\smallskip
\noindent
\emph{$R$-matrix.}
On generators, the collision residue is constant
($r^{\mathrm{coll}} = 1$, depth~$0$), so the $R$-matrix is
the identity:
\begin{equation}\label{eq:symplectic-boson-R}
R(z) \;=\; \mathrm{Id}\,,
\end{equation}
the same as $\beta\gamma$ at $\lambda = 1/2$
(equation~\eqref{eq:betagamma-R}). The DK-0 Laplace
kernel $r(z) = 1/z$ (from the simple-pole OPE) is a
different object from the collision residue: the $d\log$
bar kernel absorbs the pole, reducing the generator-level
braiding to trivial.

\smallskip
\noindent
\emph{Koszul dual.}
The symplectic bosons are the chiral symmetric algebra on a
symplectic vector space. The Koszul dual is the chiral
exterior algebra on the dual:
\begin{equation}\label{eq:symplectic-boson-koszul}
(\chi^+\chi^-)^! \;=\; \text{fermionic symplectic system}\,.
\end{equation}
The statistics exchange (bosonic $\leftrightarrow$ fermionic)
preserves the symplectic structure.

\smallskip
\noindent
\emph{Complementarity.}
$\kappa(\chi) = -1/4$ (from the weight-$1/2$ curvature formula).
The complementarity sum with the dual vanishes:
$K = \kappa(\chi) + \kappa(\chi^!) = 0$.

\smallskip
\noindent
\emph{Poincar\'{e} series.}
$P(t) = 1 + 2t$ (two cogenerators $s^{-1}\chi^+, s^{-1}\chi^-$).

\smallskip
\noindent
\emph{Genus-$1$.}
$\chi^+_{(0)}\chi^- = 1 \ne 0$, so $c_0 \ne 0$: symplectic bosons
are propagator-entangled at genus~$1$. The symplectic Casimir
$\Omega_{\mathrm{symp}} = \chi^+ \otimes \chi^- - \chi^- \otimes \chi^+$
enters the elliptic $r$-matrix. Curvature $\kappa = -1/4$.
\end{computation}

% ================================================================
\section{The shadow obstruction tower atlas}%
\label{sec:shadow-tower-atlas}%
\index{shadow tower!atlas|textbf}%
\index{Lagrangian self-intersection!atlas}

The Heisenberg Rosetta Stone establishes the principle:
the bar complex of a chiral algebra is the formal bar/Koszul model of
a Lagrangian self-intersection, and the shadow obstruction tower
$\{\operatorname{Sh}_r\}_{r\ge 2}$ measures the excess
intersection multiplicity at each codimension. For
$\cH_k$, the intersection is clean ($m_{k\ge 3}=0$) and the
tower terminates at degree~$2$: the single scalar~$k$ is the
only datum. What happens for algebras with singular
self-intersections?

This section answers by explicit computation for all
standard families. The results are summarised in the
\emph{shadow obstruction tower atlas}: a complete table of shadow
coefficients, depths, and termination degrees for seven
families covering all four depth classes.

\subsection{Excess intersection depth}%
\label{subsec:excess-intersection-depth}%
\index{shadow depth!excess intersection}

\begin{definition}[Shadow depth as excess intersection
codimension]%
\label{def:shadow-depth-intersection}%
\index{shadow depth!definition}%
The \emph{shadow depth} of a chiral algebra~$\cA$
is
\[
 d(\cA)
 \;:=\;
 \max\{r \ge 2 : \operatorname{Sh}_r(\cA) \ne 0\}
 \;\in\;
 \{2, 3, 4, \ldots\} \cup \{\infty\}\,.
\]
In the Chriss--Ginzburg picture, $d(\cA)$ is the codimension
of the \emph{excess intersection locus}: the deepest stratum
of the Lagrangian self-intersection
$\mathfrak{S}_b = L\times_X L$ at which the Borel--Moore
fundamental class carries nontrivial convolution data.

\smallskip
\noindent
\emph{Four classes.}
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{cllll}
\toprule
\textbf{Class} & \textbf{Depth} & \textbf{Intersection} &
\textbf{Mechanism} & \textbf{Archetype} \\
\midrule
$\mathbf{G}$ & $2$ & Clean &
 Abelian OPE & Heisenberg \\
$\mathbf{L}$ & $3$ & Lie-transverse &
 Jacobi kills quartic & Affine $V_k(\fg)$ \\
$\mathbf{C}$ & $4$ & Contact &
 Rank-$1$ abelian rigidity & $\beta\gamma$ \\
$\mathbf{M}$ & $\infty$ & Excess tower &
 Composite-field exchange & Virasoro \\
\bottomrule
\end{tabular}
\end{center}
\end{definition}

\subsection{The atlas}%
\label{subsec:atlas}%
\index{shadow tower!atlas!master table}

\begin{computation}[Shadow obstruction tower atlas;
\ClaimStatusProvedHere]%
\label{comp:shadow-tower-atlas}%
\index{shadow tower!atlas!computation}%
The shadow obstruction tower coefficients $S_r = \operatorname{Sh}_r / x^r$
for all standard families, with $P = H^{-1}$ the propagator
\textup{(}inverse Hessian\textup{)}:

\begin{center}
\small
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{llccccl}
\toprule
\textbf{Family} & \textbf{Class}
& $S_2$ & $S_3$ & $S_4$
& \textbf{Depth} & \textbf{Terminates} \\
\midrule
$\cH_k$
 & $\mathbf{G}$
 & $k$
 & $0$
 & $0$
 & $2$
 & $\checkmark$ \\[2pt]
$V_\Lambda$ (mom.)
 & $\mathbf{G}$
 & $\operatorname{rk}(\Lambda)$
 & $0$
 & $0$
 & $2$
 & $\checkmark$ \\[2pt]
$V_\Lambda$ (v.o.)
 & $\mathbf{L}$
 & (see~\ref{comp:lattice-voa-ordered-bar})
 & $C_\Lambda \ne 0$
 & $0$
 & $3$
 & $\checkmark$ \\[2pt]
$V_k(\fg)$
 & $\mathbf{L}$
 & $\dfrac{dk}{2(k+h^\vee)}$
 & $C_{\fg}\ne 0$
 & $0$
 & $3$
 & $\checkmark$ \\[4pt]
$\beta\gamma$
 & $\mathbf{C}$
 & $-1$
 & $0$
 & $-\dfrac{5}{12}$
 & $4$
 & $\checkmark$ \\[4pt]
Virasoro
 & $\mathbf{M}$
 & $\dfrac{c}{2}$
 & $2$
 & $\dfrac{10}{c(5c{+}22)}$
 & $\infty$
 & \\[4pt]
$\cW_3$
 & $\mathbf{M}$
 & $\dfrac{5c}{6}$
 & $2$
 & $\dfrac{10}{c(5c{+}22)}$
 & $\infty$
 & \\[4pt]
$\cW_N$
 & $\mathbf{M}$
 & $c(H_N{-}1)$
 & $2$
 & $\dfrac{10}{c(5c{+}22)}$
 & $\infty$
 & \\
\bottomrule
\end{tabular}
\end{center}
Here $d = \dim\fg$, $h^\vee$ is the dual Coxeter number,
$H_N = \sum_{j=1}^N 1/j$ is the harmonic number,
$C_\fg$ is the Lie cubic shadow, and the $\cW_N$ entries
for $S_3$, $S_4$ restrict to the $T$-line. The
$\cW_3$ Hessian $\kappa = 5c/6$ is the composite
$\kappa_T + \kappa_W = c/2 + c/3$.
\end{computation}

\subsection{Virasoro: the infinite tower}%
\label{subsec:virasoro-shadow-tower}%
\index{shadow tower!Virasoro}

\begin{computation}[Virasoro shadow obstruction tower;
\ClaimStatusProvedHere]%
\label{comp:virasoro-shadow-tower}%
\index{shadow tower!Virasoro!explicit}%
The Virasoro algebra has a single strong generator~$T$ of
weight~$2$, with curvature $\kappa = c/2$ and
propagator $P = 2/c$. The shadow obstruction tower is computed by
the obstruction recursion: $\operatorname{Sh}_r =
-o^{(r)}/(2r)$ where $o^{(r)} = \sum_{j+k=r+2}
\{\operatorname{Sh}_j, \operatorname{Sh}_k\}_H$ is the
Poisson bracket of lower shadows.

\smallskip
\noindent
\emph{Explicit coefficients.}
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{clc}
\toprule
$r$ & $S_r$ & Sign \\
\midrule
$2$ & $c/2$ & $+$ \\
$3$ & $2$ & $+$ \\
$4$ & $10/\bigl[c(5c{+}22)\bigr]$ & $+$ \\
$5$ & $-48/\bigl[c^2(5c{+}22)\bigr]$ & $-$ \\
$6$ & $80(45c{+}193)/\bigl[3\,c^3(5c{+}22)^2\bigr]$ & $+$ \\
$7$ & $-2880(15c{+}61)/\bigl[7\,c^4(5c{+}22)^2\bigr]$ & $-$ \\
\bottomrule
\end{tabular}
\end{center}

\emph{Denominator structure} \textup{(}verified through
$r = 7$\textup{)}\emph{.}
$S_r$ has denominator $c^{r-2}(5c{+}22)^{\lfloor(r-2)/2\rfloor}$.
The factor $(5c{+}22)$ is the Kac determinant at level~$4$:
$\det M_4 \sim c^2(2c{-}1)(5c{+}22)(7c{+}68)$. The shadow obstruction tower
knows the Kac determinant.
Each entry verifies the weight-depth identity $w + d = n - 1$ (Theorem~\ref{thm:gap-migration}(i)): the shadow $S_r$ at degree~$r$ has spectral degree $r - 1$ for the $T$-dependent sector and degree $r + 1$ for the scalar contact term.
\end{computation}

\begin{remark}[Kac--shadow singularity principle]%
\label{rem:kac-shadow-singularity}%
\index{Kac determinant!shadow tower}%
\index{shadow tower!Kac determinant}%
The denominator of~$S_r$ divides the product of Kac
determinants up to level~$r$. Concretely:
$(5c+22)$ appears in $S_4$ and in $\det M_4$;
$(c+24)$ from $\det M_6$ appears in the $\cW_3$ cubic
coupling $C_{333}^2 = 64(7c+68)(2c-1)/[5c(c+24)(5c+22)]$.
The shadow pole locus $\{S_r = \infty\}$ is contained in the
Kac degeneration locus $\{\det M_r = 0\}$: shadows diverge
where the chiral algebra degenerates.
\end{remark}

\subsection{Affine Kac--Moody: Jacobi termination}%
\label{subsec:affine-shadow}%
\index{shadow tower!affine}

\begin{computation}[Affine $V_k(\mathfrak{sl}_2)$:
depth~$3$ by Jacobi; \ClaimStatusProvedHere]%
\label{comp:affine-shadow-tower}%
\index{shadow tower!affine!termination}%
The affine algebra $V_k(\mathfrak{sl}_2)$ has
$\dim\fg = 3$, $h^\vee = 2$,
$c = 3k/(k+2)$, and $\kappa = 3(k+2)/4$. On the Cartan
line $(\bC\cdot h)$:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ccc}
\toprule
$r$ & Affine $V_k(\mathfrak{sl}_2)$ & Virasoro \\
\midrule
$S_2$ & $k$ & $c/2$ \\
$S_3$ & $0$ (Cartan abelian) & $2$ \\
$S_4$ & $0$ (Jacobi) & $10/[c(5c{+}22)]$ \\
$\delta H^{(1)}$ & $0$ & $120/[c^2(5c{+}22)]$ \\
$\rho^{(1)}$ & $0$ & $240/[c^3(5c{+}22)]$ \\
\bottomrule
\end{tabular}
\end{center}

\emph{Termination mechanism.}
The Cartan subalgebra is abelian ($[h,h]=0$), so
$S_3|_{\mathrm{Cartan}} = 0$. The quartic
$Q^{\mathrm{contact}} = \{S_3, S_3\}_H/(8) = 0$
vanishes on the Cartan line because $S_3 = 0$ there.
On the full $\mathfrak{sl}_2$ basis $\{h,e,f\}$,
the cubic $C(h,e,f) = \kappa(h,[e,f]) = 2k$ is nonzero,
but the quartic contact term vanishes by the Jacobi
identity: $\{C, C\}_H = 0$. The genus-$1$ Hessian
correction $\delta H^{(1)}$ vanishes on the Cartan line by
sign cancellation between $e$- and $f$-loops.
The tower terminates at degree~$3$. The Virasoro column provides a reference for the weight-depth identity $w + d = n - 1$ (Theorem~\ref{thm:gap-migration}(i)); the affine column terminates before the identity produces a nontrivial structural gap.
\end{computation}

\subsection{$\cW_3$: the first multivariable shadow}%
\label{subsec:w3-shadow}%
\index{shadow tower!$\cW_3$}

\begin{computation}[$\cW_3$ multivariable shadow;
\ClaimStatusProvedHere]%
\label{comp:w3-shadow-tower}%
\index{shadow tower!$\cW_3$!quartic}%
The $\cW_3$ algebra has generators $T$ (weight~$2$)
and $W$ (weight~$3$), with Hessian
$\kappa = \operatorname{diag}(c/2,\, c/3)$. The
deformation space is two-dimensional: $(x_T, x_W)$.

\smallskip
\noindent
\emph{Weight-$4$ quasi-primary.} The unique quasi-primary
at weight~$4$ is
$\Lambda = {:}TT{:} - \tfrac{3}{10}\partial^2 T$,
with norm $N_\Lambda = c(5c{+}22)/10$. Its couplings:
$C_{TT,\Lambda} = 1$,
$C_{WW,\Lambda} = \alpha(c) := 32/(5c{+}22)$.

\smallskip
\noindent
\emph{Quartic shadow.}
\begin{equation}\label{eq:w3-quartic}
 \operatorname{Sh}_4(x_T, x_W)
 \;=\;
 \frac{10}{c(5c{+}22)}\,x_T^4
 \;+\;
 \frac{6\cdot 320}{c(5c{+}22)^2}\,x_T^2 x_W^2
 \;+\;
 \frac{10240}{c(5c{+}22)^3}\,x_W^4\,.
\end{equation}
The $(5c{+}22)$ multiplicity increases with the number of
$W$-legs: $Q_{T^4}$ has $(5c{+}22)^1$,
$Q_{T^2W^2}$ has $(5c{+}22)^2$,
$Q_{W^4}$ has $(5c{+}22)^3$. Each pair of $W$-legs
contributes one factor of
$\alpha = C_{WW,\Lambda} = 32/(5c{+}22)$.

\smallskip
\noindent
\emph{$W$-line parity.}
On the $W$-line ($x_T = 0$), the $\mathbb{Z}_2$ symmetry
$W\mapsto -W$ forces all odd-degree shadows to vanish:
$S_{2m+1}|_{x_T=0} = 0$ for all $m$. The even-degree
recursion gives integer normalised coefficients through
degree~$32$.

\smallskip
\noindent
\emph{DS depth jump.}
The Drinfeld--Sokolov reduction
$V_k(\mathfrak{sl}_3) \to \cW_3$ sends a class~$\mathbf{L}$
algebra (depth~$3$) to a class~$\mathbf{M}$ algebra
(depth~$\infty$). The depth increase is caused by the
composite field $\Lambda = {:}TT{:} - \tfrac{3}{10}
\partial^2 T$, which does not exist in the affine algebra
but is generated by the reduction. DS reduction introduces
new self-intersection strata.
On the $T$-line ($x_W = 0$), each shadow $\operatorname{Sh}_r$ verifies the weight-depth identity $w + d = n - 1$ (Theorem~\ref{thm:gap-migration}(i)); the gap migration formula $d_{\mathrm{gap}} = 2N + n - 4$ (part~(iv)) is verified in Computation~\ref{comp:w3-gap-migration-verification}.
\end{computation}

\subsection{$\cW_4$: two exchange channels}%
\label{subsec:w4-shadow}%
\index{shadow tower!$\cW_4$}

\begin{computation}[$\cW_4$ two-channel shadow;
\ClaimStatusProvedHere]%
\label{comp:w4-shadow-tower}%
\index{shadow tower!$\cW_4$!two channels}%
The $\cW_4$ algebra has generators $T$ (weight~$2$),
$W_3$ (weight~$3$), $W_4$ (weight~$4$), with
$\kappa = \operatorname{diag}(c/2,\, c/3,\, c/4)$.

\smallskip
\noindent
\emph{Two quasi-primary exchange channels at weight~$4$.}
Unlike~$\cW_3$, the $\cW_4$ algebra has \emph{two}
independent quasi-primaries at weight~$4$:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The composite $\Lambda = {:}TT{:}
 - \tfrac{3}{10}\partial^2 T$, with
 $N_\Lambda = c(5c{+}22)/10$\textup{;}
\item The primary $W_4$ itself, with $N_{W_4} = c/4$.
\end{enumerate}

\noindent
\emph{Critical coefficient.}
The $T$--$W_4$ exchange through the $W_4$~channel gives
\begin{equation}\label{eq:w4-critical}
 Q_{TW_4 TW_4}
 \;=\;
 \frac{C_{TW_4,W_4}^2}{N_{W_4}}
 \;=\;
 \frac{64}{c}\,,
\end{equation}
with \emph{no factor of $(5c{+}22)$}. This is the first
quartic coefficient in the atlas that does not carry the
Kac level-$4$ factor.

\smallskip
\noindent
\emph{Lee--Yang decoupling.}
At the Lee--Yang critical point $c = -22/5$, the composite
$\Lambda$ decouples ($N_\Lambda = 0$), and all
$\Lambda$-mediated channels diverge. But
$Q_{TW_4 TW_4} = 64/c$ remains regular: the
$W_4$~exchange is insensitive to the Lee--Yang critical
point. The Kac degeneration locus $\{5c+22=0\}$ is visible
to the $\Lambda$~channel but invisible to the $W_4$~channel.
\end{computation}

\begin{remark}[Chriss--Ginzburg reading of the atlas]%
\label{rem:cg-atlas}%
\index{Chriss--Ginzburg!shadow tower atlas}%
\index{Lagrangian self-intersection!depth classification}%
The depth classification
(Definition~\ref{def:shadow-depth-intersection}) has a
Chriss--Ginzburg interpretation: the shadow depth measures
the complexity of the Lagrangian self-intersection
$\mathfrak{S}_b = L\times_X L$.
\begin{itemize}[nosep]
\item \emph{Class~$\mathbf{G}$} ($d=2$): $\mathfrak{S}_b$ is
 a clean correspondence (smooth intersection, no excess).
 The Borel--Moore fundamental class is concentrated in the
 top stratum. Archetype: $\cH_k$.
\item \emph{Class~$\mathbf{L}$} ($d=3$): the Lie bracket
 creates a transverse intersection defect at codimension~$1$,
 but the Jacobi identity kills all higher defects. The
 excess locus has dimension~$1$. Archetype: $V_k(\fg)$.
\item \emph{Class~$\mathbf{C}$} ($d=4$): a contact term
 from composite-field exchange creates an isolated
 codimension-$2$ defect; rank-$1$ abelian rigidity
 prevents further growth. Archetype: $\beta\gamma$.
\item \emph{Class~$\mathbf{M}$} ($d=\infty$): composite
 fields generate an infinite tower of excess intersection
 strata. The shadow obstruction tower does not terminate. The Kac
 determinant factors accumulate in the denominators:
 $(5c+22)^{\lfloor(r-2)/2\rfloor}$ grows without bound.
 Archetype: Virasoro.
\end{itemize}
The $\cW_4$ two-channel phenomenon
(Computation~\ref{comp:w4-shadow-tower}) shows that the
class~$\mathbf{M}$ tower can have \emph{multiple independent
excess-intersection directions}: the $\Lambda$~channel and the
$W_4$~channel probe different strata of~$\mathfrak{S}_b$, with
different pole loci. The Lee--Yang decoupling
($5c+22 = 0$ affects $\Lambda$ but not $W_4$) means the
self-intersection has at least two irreducible components
at codimension~$2$.
\end{remark}

\begin{remark}[Koszul conductor and Kac--shadow duality]%
\label{rem:koszul-conductor}%
\index{Koszul conductor}%
\index{Kac--shadow duality}%
The \emph{Koszul conductor}
$K_N := 2(N{-}1)(2N^2+2N+1)$ (with $K_2 = 26$ (Virasoro),
$K_3 = 100$ ($\cW_3$), $K_4 = 246$, $K_5 = 488$,
$K_6 = 850$) governs the Kac--shadow duality: the
$\sigma$-invariant
$\Delta^{(r)} := S_r(c) + S_r(K_N - c)$
is the shadow obstruction tower's image under the Koszul involution
$c \leftrightarrow K_N - c$.
For the Virasoro algebra ($K_2 = 26$),
$\Delta^{(r)} = S_r(c) + S_r(26 - c)$ recovers the
self-dual locus at $c = 13$
(by the depth decomposition theorem of Volume~I).
\end{remark}

% ================================================================
\section{The genus-1 endomorphism atlas}%
\label{sec:genus1-endomorphism-atlas}%
\index{endomorphism algebra!genus 1|textbf}%
\index{Lagrangian self-intersection!genus 1}%
\index{genus 1!endomorphism atlas}
% ================================================================

\providecommand{\Mvac}{\cM_{\mathrm{vac}}}
\providecommand{\Mbar}{\overline{\mathcal{M}}}
\providecommand{\HH}{\operatorname{HH}}
\providecommand{\End}{\operatorname{End}}

The shadow obstruction tower atlas
(Computation~\ref{comp:shadow-tower-atlas}) classifies the
standard families by the excess intersection codimension of
the genus-$0$ Lagrangian self-intersection
$\mathfrak{S}_b = L \times_X L$: clean for class~$\mathbf{G}$,
transverse for class~$\mathbf{L}$, contact for
class~$\mathbf{C}$, infinite excess for class~$\mathbf{M}$.
All of this is genus-$0$ data, visible already on~$\C$.

At genus~$1$, the Lagrangian deforms
(Theorem~\ref{thm:curved-swiss-cheese}), the $r$-matrix
becomes elliptic
(Theorem~\ref{thm:elliptic-spectral-dichotomy}), and the
five theorems of Volume~I acquire curvature. Two
independent invariants control the deformation: the modular
characteristic $\kappa(\cA)$ (the scalar curvature, from the
highest-pole OPE coefficient) and the Coisson bracket
$c_0 = \{a \,{}_0\, b\}$ (the Lie-bracket residue, from the
simple-pole coefficient). The characteristic controls the
closed colour; the Coisson bracket controls the spectral
braiding. The \emph{curvature-braiding dichotomy}
(Theorem~\ref{thm:elliptic-spectral-dichotomy}) partitions
genus-$1$ deformations: $c_0 = 0$ (Heisenberg, lattice VOAs)
gives decoupled curvature and braiding; $c_0 \ne 0$ (affine KM,
Virasoro, $\cW_N$) gives entangled curvature and braiding.
This dichotomy cuts \emph{orthogonally} to the pole-order
classification $\mathbf{G}/\mathbf{L}/\mathbf{C}/\mathbf{M}$:
Heisenberg and affine KM are both class~$\mathbf{L}$ but have
opposite genus-$1$ behaviour. This section computes the genus-$1$
endomorphism algebra for every atlas family.

\begin{theorem}[Pole-structure dichotomy; \ClaimStatusProvedHere]
\label{thm:pole-structure-dichotomy}
\index{pole-structure dichotomy|textbf}
\index{shadow depth!pole-structure classification|textbf}
Let\/ $\cA$ be a chirally Koszul logarithmic
$\SCchtop$-algebra whose OPE has maximal pole order\/~$d$.
The pole structure determines the Swiss-cheese formality
class:
\begin{enumerate}[label=\textup{(\roman*)}]
\item If\/ $d = 2$ and the OPE residues are scalar
 \textup{(}class~$\mathbf{G}$\textup{)}: the bar complex is
 cogenerated in degree~$2$, all $\Ainf$ operations vanish
 for $k \ge 3$, shadow depth\/~$r_{\max} = 2$, and the
 genus-$1$ self-intersection is clean
 \textup{(}Heisenberg, lattice VOAs\textup{)}.
\item If\/ $d = 2$ and the OPE residues are non-scalar
 \textup{(}class~$\mathbf{L}$\textup{)}: the bar complex
 has an degree-$3$ obstruction from Lie-bracket terms,
 $m_3 \ne 0$ on generators but $m_k = 0$ for $k \ge 4$
 on cohomology, shadow depth\/~$r_{\max} = 3$
 \textup{(}affine Kac--Moody\textup{)}.
\item If\/ $d = 3$ \textup{(}class~$\mathbf{C}$\textup{)}:
 the third-order pole produces a quartic contact invariant,
 $m_4 \ne 0$ but terminates at
 shadow depth\/~$r_{\max} = 4$ by rank-one rigidity
 \textup{(}$\beta\gamma$ system\textup{)}.
\item If\/ $d \ge 4$ \textup{(}class~$\mathbf{M}$\textup{)}:
 the bar complex has non-vanishing $m_k$ for all $k \ge 3$,
 shadow depth is infinite, and the Swiss-cheese structure is
 non-formal. The fourth-order pole manufactures a
 propagating obstruction that prevents the tower from
 terminating
 \textup{(}Virasoro, $\cW_N$\textup{)}.
\item All four Koszul classes are chirally Koszul \textup{(}bar
 cohomology concentrated\textup{)}. Shadow depth classifies
 complexity \emph{within} the Koszul world. A fifth
 class~$\mathbf{W}$ \textup{(}wild: Kronecker $K_m$, $m \geq 3$\textup{)}
 lies outside the Koszul locus, where the bar spectral
 sequence does not collapse and the shadow depth is undefined
 \textup{(}Volume~I, Remark~\textup{\ref*{V1-rem:wild-quiver-boundary}}\textup{)}.
\item \label{item:bar-channel} Classes~$\mathbf{G}$, $\mathbf{L}$, $\mathbf{C}$ have
 formal Swiss-cheese structure at genus~$0$; class~$\mathbf{M}$
 has non-formal Swiss-cheese structure. At genus~$g \ge 1$, the
 curvature $\kappa \cdot \omega_g$ entangles the propagator
 channel for classes with $c_0 \ne 0$, while the bar-complex
 channel contributes additional genus corrections for
 class~$\mathbf{M}$.
\end{enumerate}
\end{theorem}

\begin{proof}
The pole order $d$ determines the maximal degree at which new
bar cogenerators appear. For $d = 2$ with scalar residues,
the bar differential is quadratic and the Koszul complex is
exact: no higher cogenerators arise, giving
$r_{\max} = 2$. For $d = 2$ with non-scalar (Lie-bracket)
residues, the bracket $[a, b]$ produces an degree-$3$ term
$m_3$, but the Jacobi identity closes the obstruction at
degree~$4$, giving $r_{\max} = 3$.
For $d = 3$, the third-order pole creates a quartic contact
invariant $\mu = \langle\eta, m_3(\eta, \eta, \eta)\rangle$
in the cyclic deformation complex; rank-one rigidity
(Volume~I, Corollary~\ref*{V1-cor:nms-betagamma-mu-vanishing})
forces the quintic obstruction to vanish on $\beta\gamma$,
giving $r_{\max} = 4$. For $d \ge 4$, the Sugawara pole
manufactures a genuine quartic propagating obstruction
(the single-line dichotomy of Volume~I,
Theorem~\ref*{V1-thm:single-line-dichotomy}), forcing the tower
to be infinite. Part~(v) follows from PBW universality
(Volume~I).
\end{proof}

\subsection{The genus-1 atlas theorem}%
\label{subsec:genus1-atlas-theorem}

\begin{theorem}[Genus-$1$ endomorphism atlas;
\ClaimStatusProvedHere]%
\label{thm:genus1-endomorphism-atlas}%
\index{genus-1 endomorphism atlas|textbf}%
Let\/ $\cA$ be a chiral algebra from the shadow obstruction tower atlas
\textup{(}Computation~\textup{\ref{comp:shadow-tower-atlas}}\textup{)}
that is a logarithmic\/ $\SCchtop$-algebra.
The curved bar complex~$\barB^{(1)}(\cA)$
\textup{(}Theorem~\textup{\ref{thm:curved-swiss-cheese}}\textup{)}
is determined by three genus-$1$ invariants.
In the Lagrangian picture
\textup{(}the genus-$1$ deformation picture encoded by the curved bar
equation\textup{)},
$\barB^{(1)}(\cA)$ is the genus-$1$ formal endomorphism model
attached to the derived tensor product of
$\cL_\cA^{(1)} \times_{\Mvac}
\cL_\cA^{(1)}$:
the genus-$1$ bar/Koszul model of the Lagrangian
self-intersection. The three invariants are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Curvature.}
 $\dfib^{\,2} = \kappa(\cA) \cdot \omega_1$, with period
 correction
 $F_1(\cA) = \kappa(\cA)/24$
 \textup{(}Corollary~\textup{\ref{cor:genus1-curved-swiss-cheese}}\textup{)}.

\item \textbf{Spectral type.}
 The genus-$1$ classical $r$-matrix
 $r^{E_\tau}(z) = c_0 \cdot \zeta(z|\tau) + c_1 \cdot \wp(z|\tau)
 + \cdots$
 \textup{(}Theorem~\textup{\ref{thm:elliptic-spectral-dichotomy}},
 equation~\eqref{eq:elliptic-r-matrix}\textup{)}
 is doubly periodic if\/ $c_0 = 0$ \textup{(}Cartan type\textup{)}
 and quasi-periodic with $B$-cycle monodromy
 $2\eta_\tau \cdot c_0$ if\/ $c_0 \ne 0$
 \textup{(}Yangian type\textup{)}.

\item \textbf{Five-theorem projection.}
 Each of Volume~I's five theorems specialises at genus~$1$
 as a deformation of the genus-$0$ data by the single
 parameter $\kappa(\cA) \cdot \omega_1$:
 \begin{enumerate}[label=\textup{(\Alph*$_1$)},leftmargin=2.5em]
 \item \emph{Bar-cobar:} curved dg coalgebra
 $(\barB^{(1)}(\cA), \dfib, \Delta)$ over $\Mbar_1$;
 \item \emph{Inversion:} curved quasi-isomorphism
 $\Omegach(\barB^{(1)}(\cA)) \xrightarrow{\sim} \cA$
 in the coderived category;
 \item \emph{Complementarity:}
 $\kappa(\cA) + \kappa(\cA^!) = K(\cA)$ on the Koszul locus,
 where $K$ is a level-independent constant ($K = 0$ for the
 affine lineage; $K \neq 0$ for DS reductions);
 when $K = 0$, $\barB^{(1)}(\cA) \otimes \barB^{(1)}(\cA^!)$
 is uncurved;
 \item \emph{Leading coefficient:}
 $F_1 = \kappa(\cA)/24$ is the genus-$1$
 Faber--Pandharipande integral;
 \item \emph{Hochschild:}
 $\mathrm{CH}^\bullet(\cA)^{(1)}$ acquires a correction
 from the Hodge bundle
 $\mathbb{E} \to \Mbar_1$.
 \end{enumerate}
\end{enumerate}

All four atlas classes are chirally Koszul (bar cohomology
concentrated by PBW). Class~$\mathbf{G}$ has formal Swiss-cheese structure
($m_k^{\mathrm{SC}} = 0$ for all $k \ge 3$).
Classes~$\mathbf{L}$ and~$\mathbf{C}$ have finite but
nontrivial SC operations: class~$\mathbf{L}$ has
$m_3^{\mathrm{SC}} \ne 0$ with $m_k^{\mathrm{SC}} = 0$ for
$k \ge 4$ (depth~$3$); class~$\mathbf{C}$ has
$m_4^{\mathrm{SC}} \ne 0$ with $m_3^{\mathrm{SC}} = 0$ and
$m_k^{\mathrm{SC}} = 0$ for $k \ge 5$ (depth~$4$).
Class~$\mathbf{M}$ (Virasoro, $\cW_N$) has \emph{infinite
shadow depth} and fully non-formal Swiss-cheese structure
($m_k^{\mathrm{SC}} \ne 0$ for all $k \ge 3$), but still
possesses well-defined Koszul duals
(e.g.\ $\mathrm{Vir}_c^! = \mathrm{Vir}_{26-c}$). The
five-theorem projection applies to all classes; for
class~$\mathbf{M}$, the bar-cobar adjunction holds but the
big Koszul dual carries higher $\Ainf$ operations.
Within the standard atlas families, the three
invariants $(\kappa, c_0, d)$ organise the atlas into three
genus-$1$ regimes, distinguished by their self-intersection
geometry and Coisson bracket:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lllll}
\toprule
\textbf{Regime} & $c_0$ & \textbf{Intersection}
 & $R_1 \stackrel{?}{=} R_0$ & \textbf{Families} \\
\midrule
Decoupled & $= 0$ & clean
 & yes & $\cH_k,\; V_\Lambda$ \\
Propagator-entangled & $\ne 0$ & clean
 & no & $V_k(\fg),\; \beta\gamma$ \\
Doubly entangled & $\ne 0$ & excess
 & no & $\mathrm{Vir}_c,\; \cW_N$ \\
\bottomrule
\end{tabular}
\end{center}
\end{theorem}

\begin{proof}
Part~(i) is
Corollary~\ref{cor:genus1-curved-swiss-cheese}.
Part~(ii) is
Theorem~\ref{thm:elliptic-spectral-dichotomy}, items
(\ref{item:dichotomy-decoupling}) and
(\ref{item:dichotomy-entanglement}).
Part~(iii) packages the separately proved genus-$1$ analogues of the
five Volume~I theorems under the single deformation parameter
$\kappa \cdot \omega_1$. Specifically:
(A$_1$) is
Theorem~\ref{thm:curved-swiss-cheese}(i)--(ii);
(B$_1$) is Theorem~B of Volume~I applied to the
curved coalgebra via the Positselski framework
(Theorem~\ref{thm:curved-swiss-cheese}(ii) and
Volume~I, Theorem~B(b));
(C$_1$) is Theorem~\ref{thm:curved-swiss-cheese}(iii);
(D$_1$) is the $g = 1$ specialisation of Volume~I,
Theorem~D\textsubscript{scal};
(H$_1$) is the genus-$1$ chiral Hochschild
correction
(Theorem~\ref{thm:hochschild-bridge-genus0}
extended over $\Mbar_1$ via the corrected differential
$\Dg{1}$).

The three-regime classification follows from
Theorem~\ref{thm:pole-structure-dichotomy}.
Classes~$\mathbf{G}$, $\mathbf{L}$, $\mathbf{C}$ are
chirally Koszul: the bar cohomology is concentrated,
the bar complex is cogenerated in degree~$1$, and
$m_{k \ge 3} = 0$ on cohomology. For these,
the bar-complex
channel~(\ref{item:bar-channel}) is trivial, the curvature
$\kappa \cdot \omega_1$ is primitive, and the $\Eone$-coproduct
is genus-independent.
Class~$\mathbf{M}$ (Virasoro, $\cW_N$) \emph{is} chirally
Koszul (PBW degeneration holds for all members of the
standard landscape; see Volume~I,
PBW universality), but has
\emph{non-formal} Swiss-cheese structure: the higher
$\Ainf$ operations $m_{k \ge 3} \ne 0$ are non-trivial
on cohomology, the bar complex has higher-degree
cogenerators (from wheel diagrams), and the hypothesis of
bar-degree-$1$ cogeneration fails. Shadow depth is
infinite, reflecting the non-vanishing of the full
$\Ainf$ tower, but this is a measure of \emph{complexity}
within the Koszul world, not a failure of Koszulness itself
\textup{(}cf.\ the Koszulness programme discussion in Volume~I\textup{)}.
For these, the bar-complex
channel~(\ref{item:bar-channel}) can contribute genus
corrections.
The three regimes:
decoupled $\Leftrightarrow$ $c_0 = 0$ and $\Ainf$-formal
(conditions (ii)--(v) of
Theorem~\ref{thm:pole-structure-dichotomy});
propagator-entangled $\Leftrightarrow$ $c_0 \ne 0$ and
$\Ainf$-formal (bar-complex channel trivial by genus-zero
formality,
propagator channel non-trivial by
Theorem~\ref{thm:elliptic-spectral-dichotomy}(\ref{item:dichotomy-entanglement}));
doubly entangled $\Leftrightarrow$ $c_0 \ne 0$ and
$\Ainf$-non-formal (both channels can contribute, by
Theorem~\ref{thm:pole-structure-dichotomy}(vi)).
\end{proof}

\subsection{Heisenberg: all five theorems at genus~$1$}%
\label{subsec:heisenberg-genus1-endomorphism}

\begin{computation}[Heisenberg genus-$1$ endomorphism algebra;
\ClaimStatusProvedHere]%
\label{comp:heisenberg-genus1-endomorphism}%
\index{Heisenberg algebra!genus-1 endomorphism}%
For $\cH_k$, the three invariants are
$\kappa = k$, $c_0 = 0$, $d = 2$
\textup{(}decoupled regime\textup{)}.
The genus-$1$ endomorphism algebra
$\End^{(1)}(\cL_{\cH_k})$ is the genus-$0$
endomorphism algebra tensored with a scalar from
the Hodge line.

\smallskip
\noindent
\emph{(A$_1$) Curved bar-cobar.}
$\barB^{(1)}(\cH_k) = T^c(s^{-1}\overline{\cH}_k)$
with $\dfib^{\,2} = k \cdot \omega_1$
(Theorem~\ref{thm:rosetta-curved}).
The fiberwise differential on $E_\tau$ uses the
elliptic propagator $dG_\tau(z)$; the coproduct
$\Delta$ is unchanged.

\smallskip
\noindent
\emph{(B$_1$) Curved inversion.}
The cobar $\Omegach(\barB^{(1)}(\cH_k))$ inverts the
curved bar complex in the coderived category of
Positselski: the augmentation
$\Omegach(\barB^{(1)}(\cH_k)) \to \cH_k$ is a
quasi-isomorphism after restricting to the coderived
category. This uses $m_{k \ge 3} = 0$
(Proposition~\ref{prop:rosetta-heisenberg-mk}): the
Koszulness of $\cH_k$ ensures that the bar-cobar
unit is an equivalence fiberwise.

\smallskip
\noindent
\emph{(C$_1$) Complementarity.}
$\kappa(\cH_k) + \kappa(\cH_k^!) = k + (-k) = 0$
(Proposition~\ref{prop:rosetta-complementarity}).
The tensor product
$\barB^{(1)}(\cH_k) \otimes \barB^{(1)}(\cH_k^!)$
has flat differential: the curvatures cancel, and the
genus-$1$ complementary Lagrangians remain
complementary.

\smallskip
\noindent
\emph{(D$_1$) Period correction.}
$F_1(\cH_k) = k/24$. This is the first
Faber--Pandharipande coefficient
(Corollary~\ref{cor:genus1-curved-swiss-cheese}):
$\dfib^{\,2} = k \cdot \omega_1$ is compensated by
$\delta_{\mathrm{per}}$ satisfying
$\Dg{1}^{\,2} = 0$.

\smallskip
\noindent
\emph{(H$_1$) Hochschild at genus~$1$.}
The chiral Hochschild cochains
$\mathrm{CH}^\bullet(\cH_k, \cH_k)$
at genus~$1$ acquire a correction from the Eisenstein
series $E_2(\tau)$: the propagator
$G_\tau(z) = \zeta(z|\tau) - \frac{\pi^2}{3}E_2(\tau) z$
(equation~\eqref{eq:rosetta-elliptic-propagator})
introduces quasi-modularity into the Hochschild
differential. The correction is proportional to $k$:
the Hochschild class $c_k \in H^2(\barB(\cH_k))$
(Proposition~\ref{prop:rosetta-bar-hochschild})
deforms by $k \cdot E_2(\tau)$.

\smallskip
\noindent
\emph{Spectral $r$-matrix.}
The $\lambda$-bracket $\{J_\lambda J\} = k\lambda$
has $c_0 = 0$ (no simple pole) and $c_1 = k$ (the
level). By
Theorem~\ref{thm:elliptic-spectral-dichotomy}(\ref{item:dichotomy-decoupling}):
\begin{equation}\label{eq:heisenberg-genus1-rmatrix}
r^{E_\tau}_{\cH_k}(z)
\;=\;
k \cdot \wp(z|\tau),
\end{equation}
which is doubly periodic on $E_\tau$. The spectral
$R$-matrix is unchanged from genus~$0$:
$R_1(z) = R_0(z) = e^{k\hbar/z}$
(Corollary~\ref{cor:rosetta-heisenberg-projections}(iii)).
The curvature $k \cdot \omega_1$ and the braiding
$k \cdot \wp(z|\tau)$ are decoupled: the former comes
from the $B$-cycle monodromy of $\zeta(z|\tau)$
acting on the bar differential, the latter from the
doubly periodic $\wp$-function which has no monodromy.
The $B$-cycle has no effect on $r$ because $c_0 = 0$
filters it out.
\end{computation}

\begin{computation}[Heisenberg line bundle; \ClaimStatusProvedHere]
\label{comp:heisenberg-line-bundle}
The line bundle $\cL_\kappa$ of Construction~\ref{constr:determinant-line-bundle} specialises for $\cA = \cH_k$ as follows. The modular characteristic is $\kappa(\cH_k) = k$, so:
\[
\cL_k \;=\; (\det \lambda)^{\otimes k},
\]
the $k$-th tensor power of the determinant of the Hodge bundle. Its first Chern class is $c_1(\cL_k) = k \cdot \omega_1 \in H^2(\overline{\cM}_1, \Z)$. The curvature of the Quillen connection on $\cL_k$ is $F_{\cL_k} = k \cdot F^Q = -2\pi i \cdot (k/12) \cdot \omega_{\mathrm{WP}}$. Sections of $\cL_k$ over $\overline{\cM}_1$ are modular forms of weight $k/2$; the genus-$1$ partition function $Z_1(\cH_k) = \eta(\tau)^{-k}$ is a section of $\cL_k^{-1}$.
\end{computation}

\begin{computation}[Heisenberg annular bar complex;
\ClaimStatusProvedHere]%
\label{comp:heisenberg-annular-bar}%
\index{annular bar complex!Heisenberg|textbf}%
\index{Heisenberg algebra!annular bar complex|textbf}%
\index{Hochschild homology!Heisenberg annular model}%
The annular bar complex
$B^{\mathrm{ann}}_\bullet(\cH_k)$
(Construction~\ref{constr:annular-bar-vol2},
Definition~\ref{def:annular-bar}) is the first
explicit instantiation of the annular bar differential.
The Heisenberg algebra has $V = \bC \cdot J$,
OPE $J(z)J(w) \sim k/(z-w)^2$, and
ordered bar coalgebra $C = \Barchord(\cH_k) = T^c(s^{-1}\bC\cdot J)$
with bar differential
$d_{\barB}[s^{-1}J\,|\,s^{-1}J] = k$
(Theorem~\ref{thm:rosetta-e1-coalgebra}).
The diagonal bicomodule is $C_\Delta = C$ with left and
right coactions given by the deconcatenation coproduct.

\smallskip
\noindent
\emph{(1) Degree $n=0$.}
The cyclic cotensor at degree~$0$ is
$\mathrm{cyc}^0(C,C_\Delta) = C_\Delta \widehat\otimes_C \bC
\cong \bC$,
the ground field (the ``empty annulus'':
no points on either boundary circle, no bulk insertions).
The differential acts trivially: $d^{\mathrm{ann}}|_{n=0} = 0$.
This contributes a single class to
$\HH^{\mathrm{ch}}_0(\cH_k)$: the vacuum
character of the annulus, the identity endomorphism of the
identity functor on $\cH_k\text{-mod}$.

\smallskip
\noindent
\emph{(2) Degree $n=1$.}
The cyclic cotensor at degree~$1$ is
$\mathrm{cyc}^1(C,C_\Delta) = C_\Delta \widehat\otimes_C C
\cong C$,
with underlying vector space
$\bigoplus_{m \ge 0} (s^{-1}\bC\cdot J)^{\otimes m}$.
At tensor degree~$m$, an element is a cyclic word
$\langle s^{-1}J\,|\,\cdots\,|\,s^{-1}J\rangle$
of length~$m$ on a single boundary circle.
The four-component differential acts as follows:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $d_{\mathrm{int}} = 0$:
 the internal differential of $\cH_k$ vanishes
 (no $Q$-operator).
\item $d_{\mathrm{res}}$: the OPE collision residue
 differential. On $\langle s^{-1}J\,|\,s^{-1}J\rangle$
 (cyclic degree~$2$), two adjacent points on the
 boundary circle can collide in the holomorphic
 direction, producing the residue $k$ from the
 double-pole OPE\@. The collision of two consecutive
 factors gives
 \[
  d_{\mathrm{res}}\langle s^{-1}J\,|\,s^{-1}J\rangle
  \;=\; k \cdot \langle\,\rangle,
 \]
 where $\langle\,\rangle$ is the empty cyclic word
 (degree~$0$). At cyclic degree $m \ge 3$, each adjacent
 pair contributes $k$; the contributions cancel pairwise
 by the Koszul sign rule for cyclic words of odd-degree
 elements.
\item $d_\Delta$: the non-wrapping coproduct face.
 On a cyclic word of length~$m$, this inserts a tensor
 splitting at each non-seam position. For
 $\langle s^{-1}J \rangle$ (cyclic degree~$1$), the
 deconcatenation coproduct gives
 $\Delta(s^{-1}J) = [] \otimes s^{-1}J + s^{-1}J \otimes []$,
 which is the coaugmentation and contributes no new terms
 to the cyclic cotensor.
\item $d_{\mathrm{wrap}}$: the wrap-around differential
 at the seam of the boundary circle. On
 $\langle s^{-1}J \rangle$, the last factor wraps
 around and is re-inserted at the beginning,
 acquiring the $R$-matrix monodromy. For $\cH_k$,
 $R(z) = e^{k\hbar/z}$ and the monodromy around
 the generator of $\pi_1(S^1)$ is
 (Remark~\ref{rem:wraparound-monodromy})
 \begin{equation}\label{eq:heisenberg-wrap-monodromy}
  \mathrm{Mon}(R) \;=\; \exp(-2\pi i k).
 \end{equation}
 Since $R$ is scalar, the wrap-around on a cyclic word
 of length~$m$ produces an overall phase
 $\exp(-2\pi i k)^m = \exp(-2\pi i m k)$.
 On a single factor:
 $d_{\mathrm{wrap}}\langle s^{-1}J \rangle
 = \bigl(\exp(-2\pi i k) - 1\bigr)\langle s^{-1}J \rangle$,
 where the $-1$ accounts for the identity (unwrapped)
 term subtracted by the differential.
\end{enumerate}

\smallskip
\noindent
\emph{(3) Degree $n=2$.}
The cyclic cotensor at degree~$2$ is
$\mathrm{cyc}^2(C,C_\Delta) = C_\Delta \widehat\otimes_C C
\widehat\otimes_C C$,
with elements of the form
$\langle a_1\,|\,a_2\rangle$ (cyclic words of length~$2$).
The unique indecomposable element at tensor degree~$2$ is
$\langle s^{-1}J\,|\,s^{-1}J\rangle$.
The differential has:
\begin{itemize}
\item $d_{\mathrm{res}}\langle s^{-1}J\,|\,s^{-1}J\rangle
 = k \cdot \langle\,\rangle$
 (collision of the two adjacent factors, producing the
 OPE residue $k$; only one collision orbit by cyclic
 symmetry of a $2$-element cycle);
\item $d_{\mathrm{wrap}}\langle s^{-1}J\,|\,s^{-1}J\rangle
 = \exp(-2\pi i k)\langle s^{-1}J\,|\,s^{-1}J\rangle
 - \langle s^{-1}J\,|\,s^{-1}J\rangle$,
 the monodromy phase from wrapping the second factor past
 the seam. Since both factors are copies of the same
 generator $s^{-1}J$, the wrapped word
 $\langle s^{-1}J\,|\,s^{-1}J\rangle$ is the
 same element up to the monodromy scalar.
\end{itemize}
The identity $(d^{\mathrm{ann}})^2 = 0$ at degree~$2$
is the annular analogue of the Arnold relation: the
two boundary strata of the annular FM space
(collision and wrap-around) compose to zero.

\smallskip
\noindent
\emph{(4) The four-component differential: summary.}
For $\cH_k$, three of the four components simplify
to closed-form scalars:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}l@{\;\;}l@{\;\;}l@{}}
\textbf{Component} & \textbf{Source} &
 \textbf{Value for $\cH_k$} \\
\hline
$d_{\mathrm{int}}$
 & internal differential
 & $0$ (no $Q$-operator) \\[2pt]
$d_{\mathrm{res}}$
 & OPE collision on $\FM_2(\C)$
 & $k$ (from $J_{(1)}J = k$) \\[2pt]
$d_\Delta$
 & deconcatenation at non-seam faces
 & coaugmentation terms only \\[2pt]
$d_{\mathrm{wrap}}$
 & wrap-around at seam of $S^1$
 & phase $\exp(-2\pi i k)$
\end{tabular}
\end{center}
The total differential on a cyclic word of length~$m$ is
\begin{equation}\label{eq:heisenberg-annular-total}
d^{\mathrm{ann}}\langle s^{-1}J\,|\,\cdots\,|\,s^{-1}J\rangle
\;=\;
m\,k\cdot
\langle s^{-1}J\,|\,\cdots\,|\,s^{-1}J\rangle_{m-1}
\;+\;
\bigl(e^{-2\pi i m k} - 1\bigr)
\langle s^{-1}J\,|\,\cdots\,|\,s^{-1}J\rangle_{m},
\end{equation}
where the first term is the collision residue
(each of the $m$ adjacent pairs contributes $k$,
reduced to a single orbit by cyclic symmetry)
and the second is the wrap-around monodromy.
The factor $m$ in the collision term is the number
of cyclic-adjacent pairs on a circle with $m$ marked
points.

\smallskip
\noindent
\emph{(5) Hochschild homology $\HH_0^{\mathrm{ch}}(\cH_k)$:
the character space.}
The zeroth Hochschild homology is
\begin{equation}\label{eq:heisenberg-HH0}
\HH_0^{\mathrm{ch}}(\cH_k)
\;=\;
H_0\bigl(B^{\mathrm{ann}}_\bullet(\cH_k)\bigr)
\;\cong\;
\cH_k / [\cH_k, \cH_k]_{\mathrm{ch}},
\end{equation}
the quotient of $\cH_k$ by chiral commutators.
For the Heisenberg algebra, the chiral commutator
$[J,J]_{\mathrm{ch}} = J_{(0)}J = 0$ vanishes
(no simple pole), so every element is a class:
\[
\HH_0^{\mathrm{ch}}(\cH_k)
\;\cong\;
\bC[J, \partial J, \partial^2 J, \ldots]
\;=\;
\bC[\partial^n J : n \ge 0].
\]
This is the space of conformal characters:
each element $f(J, \partial J, \ldots)$
of the differential polynomial ring defines a
trace functional
$\cH_k \to \bC$
via insertion into the annulus
(the trace of $f$ on the torus).
The graded character is
\[
\chi\bigl(\HH_0^{\mathrm{ch}}(\cH_k);\, q\bigr)
\;=\;
\prod_{n=0}^{\infty} \frac{1}{1-q^{n+1}}
\;=\;
\frac{1}{\prod_{n=1}^{\infty}(1-q^n)}
\;=\;
\frac{q^{1/24}}{\eta(q)},
\]
recovering the bosonic partition function
(Computation~\ref{comp:heisenberg-line-bundle}).

\smallskip
\noindent
\emph{(6) Modulus dependence: chain vs homology.}
At the chain level, $B^{\mathrm{ann}}_\bullet(\cH_k)$
depends on the conformal modulus~$\tau$ of the annulus
$\mathrm{Ann}_\tau$
(Remark~\ref{rem:annular-modulus-dependence}).
For $\cH_k$, this dependence enters through
the collision residue differential $d_{\mathrm{res}}$:
the propagator on $\mathrm{Ann}_\tau$ is the elliptic
Green's function
$G_\tau(z) = \zeta(z|\tau) - \tfrac{\pi^2}{3}E_2(\tau)\cdot z$
(equation~\eqref{eq:rosetta-elliptic-propagator}),
which is a holomorphic function of~$\tau$. The
genus-$1$ correction to the binary operation is
$m_2^{(1)}(J,J;\lambda;\tau) = k\lambda
- (\pi^2 k/3)\, E_2(\tau)\, \lambda$
(equation~\eqref{eq:e1-shadow-genus1-m2}).

At the level of homology, the $\tau$-dependence disappears:
$\HH_\bullet^{\mathrm{ch}}(\cH_k)$
is the factorisation homology $\int_{S^1}\cH_k$,
which depends only on the topological type of $S^1$
and not on the conformal modulus of the annulus
that models it. The chain-level $\tau$-dependence
is the Heisenberg instance of the general
principle (Remark~\ref{rem:annular-modulus-dependence}):
the $E_1$-chain model sees the holomorphic annulus
and its modulus~$\tau$; the homology sees only the
topological circle. The Hodge-to-de~Rham spectral
sequence degenerates at $E_1$ for $\cH_k$
(because $\cH_k$ is formal: $m_k = 0$ for $k \ge 3$),
and the degeneration is the mechanism by which the
Eisenstein correction $E_2(\tau)$ becomes invisible
in homology.

The physical interpretation:
the annulus of modulus~$\tau$ is the propagator of
the 2d CFT between two boundary circles. At the chain
level, the propagator depends on~$\tau$
(the Schwinger proper time). At the level of the
partition function, the integral over~$\tau$
(the modular integral $\int_{\mathfrak{h}/\mathrm{SL}(2,\Z)}
d^2\tau / (\mathrm{Im}\,\tau)^2$)
produces the $\tau$-independent answer: the modular
invariant $|\eta(\tau)|^{-2k}$ of the free boson.

\smallskip
\noindent
\emph{(7) The wrap-around monodromy $\exp(-2\pi ik)$ and integrality.}
The monodromy $\exp(-2\pi ik)$
(equation~\eqref{eq:heisenberg-wrap-monodromy})
is trivial (equal to~$1$) if and only if $k \in \Z$.
At integer level, the wrap-around differential
$d_{\mathrm{wrap}}$ reduces to the standard cyclic
rotation: $d_{\mathrm{wrap}}\langle a_1|\cdots|a_n\rangle
= \langle a_n|a_1|\cdots|a_{n-1}\rangle
- \langle a_1|\cdots|a_n\rangle$
up to signs. This is the classical cyclic bar
complex of Connes. At non-integer level, the monodromy
is a nontrivial phase, and the annular bar complex
carries genuinely more information than the
classical cyclic complex: the phase
$\exp(-2\pi ik)$ records the conformal spin of the
boundary field $J$.

The three regimes:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $k \in \Z$: monodromy trivial,
 $d_{\mathrm{wrap}}$ = cyclic rotation,
 $\HH_\bullet(\cH_k) = $ classical Hochschild;
\item $k \in \mathbb{Q} \setminus \Z$: monodromy a
 root of unity, finite-order periodicity of the
 wrap-around, $\HH_\bullet(\cH_k)$ periodic;
\item $k \notin \mathbb{Q}$: monodromy irrational,
 $d_{\mathrm{wrap}}$ ergodic,
 $\HH_\bullet(\cH_k)$ concentrated in degree~$0$.
\end{enumerate}
This trichotomy is the Heisenberg instance of the
rationality/irrationality divide for chiral algebras:
the annular bar complex detects rationality through
the arithmetic of the wrap-around monodromy.
\end{computation}

\subsection{Affine $V_k(\mathfrak{sl}_2)$:
 the Yangian-to-elliptic passage}%
\label{subsec:affine-genus1-endomorphism}

\begin{computation}[Affine $\mathfrak{sl}_2$ genus-$1$
endomorphism algebra; \ClaimStatusProvedHere]%
\label{comp:affine-sl2-genus1-endomorphism}%
\index{affine Kac--Moody!genus-1 endomorphism}%
\index{elliptic quantum group!from genus-1 Lagrangian}%
\index{Yangian!elliptic deformation}%
For $V_k(\mathfrak{sl}_2)$ with generators
$J^a$ ($a = 1,2,3$) and $\lambda$-bracket
$\{J^a_\lambda J^b\} = f^{ab}_c J^c + k\,\kappa^{ab}\lambda$,
the three invariants are:
$\kappa = 3(k+2)/4$,
$c_0 = \Omega := \sum_a t^a \otimes t_a$ \textup{(}the
quadratic Casimir, from the Lie bracket\textup{)},
$d = 3$ \textup{(}propagator-entangled regime\textup{)}.

\smallskip
\noindent
\emph{Period correction.}
$F_1 = 3(k+2)/96 = (k+2)/32$.

\smallskip
\noindent
\emph{Genus-$1$ $r$-matrix.}
The Laurent coefficients are $c_0 = \Omega \ne 0$
and $c_1 = k\,\kappa$. By
Theorem~\ref{thm:elliptic-spectral-dichotomy}:
\begin{equation}\label{eq:affine-genus1-rmatrix}
r^{E_\tau}_{V_k(\mathfrak{sl}_2)}(z)
\;=\;
k\,\Omega \cdot \zeta(z|\tau)
\;+\;
k\,\kappa \cdot \wp(z|\tau),
\end{equation}
with $B$-cycle monodromy
$r^{E_\tau}(z + \tau) - r^{E_\tau}(z) = 2k\,\eta_\tau \cdot \Omega$
(equation~\eqref{eq:r-monodromy}). At $k = 0$ every
term vanishes, consistent with the abelian limit
. This is the
\emph{elliptic classical $r$-matrix}: the genus-$0$
rational $r$-matrix $r_0(z) = k\,\Omega/z + k\,\kappa/z^2$
deforms by replacing $1/z \leadsto \zeta(z|\tau)$ and
$1/z^2 \leadsto \wp(z|\tau)$.

\smallskip
\noindent
\emph{The DK hierarchy and the genus tower.}
The genus expansion of the $r$-matrix parallels
the Drinfeld--Kohno hierarchy of quantum groups:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lll}
\toprule
\textbf{Genus} & \textbf{$r$-matrix} &
 \textbf{Quantum group} \\
\midrule
$g = 0$ & $r_0(z) = k\,\Omega/z + \cdots$
 & Yangian $Y_\hbar(\mathfrak{sl}_2)$ \\
$g = 1$ & $r_1(z,\tau) = k\,\Omega\cdot\zeta + \cdots$
 & Elliptic quantum group \\
$g \ge 2$ & $r_g(z,\Omega_{ij}) = k\,\Omega\cdot\omega_g + \cdots$
 & (conjectural) \\
\bottomrule
\end{tabular}
\end{center}
At genus~$0$ and~$1$, this identification is a theorem:
the rational kernel $1/z$ is replaced by
$\zeta(z|\tau)$ via
Theorem~\ref{thm:elliptic-spectral-dichotomy},
and the resulting $r$-matrix is the classical
elliptic $r$-matrix of Belavin--Drinfeld.
At genus~$\ge 2$, the replacement of kernel functions
by their higher-genus counterparts (via the
period matrix $(\Omega_{ij})$ of $\Sigma_g$) produces a
candidate higher-genus quantum group structure,
but the identification is not proved.

\smallskip
\noindent
\emph{Entanglement.}
The curvature $\kappa \cdot \omega_1$ extracts $c_1 = k\kappa$
(the highest pole, a scalar); the braiding monodromy
$2\eta_\tau \cdot \Omega$ extracts $c_0 = \Omega$
(the lowest pole, a tensor). Both arise from the
quasi-periodicity of $\zeta(z|\tau)$ (the $B$-cycle is
the common geometric source), but they probe different
OPE pole orders. The entanglement is one-directional:
the curvature is visible in the closed-colour
differential ($\dfib^{\,2} \ne 0$), the braiding monodromy is
visible in the mixed-colour $r$-matrix ($r_1 \ne r_0$),
but the open-colour coproduct $\Delta$ remains
flat at genus~$1$
(Theorem~\ref{thm:curved-swiss-cheese}(i)).
\end{computation}

\begin{computation}[Affine $V_k(\mathfrak{sl}_2)$ annular bar complex;
\ClaimStatusProvedHere]%
\label{comp:affine-sl2-annular-bar}%
\index{annular bar complex!affine sl2@affine $\mathfrak{sl}_2$|textbf}%
\index{affine Kac--Moody!annular bar complex|textbf}%
\index{Hochschild homology!affine annular model}%
The annular bar complex
$B^{\mathrm{ann}}_\bullet(V_k(\mathfrak{sl}_2))$
(Construction~\ref{constr:annular-bar-vol2},
Definition~\ref{def:annular-bar}) is the first
\emph{nonabelian} instantiation of the annular bar
differential. Generators: currents $J^a$ ($a=1,2,3$)
in the Killing-orthonormal basis with
$[t^a, t^b] = \epsilon^{abc}\, t^c$ and
$\kappa^{ab} = \delta^{ab}$. OPE:
\begin{equation}\label{eq:sl2-ann-ope}
J^a(z)\, J^b(w)
\;\sim\;
\frac{k\,\delta^{ab}}{(z-w)^2}
\;+\;
\frac{\epsilon^{ab}{}_c\, J^c(w)}{z-w}.
\end{equation}
The ordered bar coalgebra is $C = \Barchord(V_k(\mathfrak{sl}_2))
= T^c(s^{-1}V)$ with $V = \bC^3 = \mathrm{span}\{J^1,J^2,J^3\}$,
and the diagonal bicomodule is $C_\Delta = C$
with deconcatenation coactions.

Two structural features distinguish this from the
abelian case (Computation~\ref{comp:heisenberg-annular-bar}):
\begin{itemize}
\item The bar differential has a \emph{simple-pole component}:
 $d_{\barB}[s^{-1}J^a\,|\,s^{-1}J^b]
 = k\,\delta^{ab} + \epsilon^{ab}{}_c\, s^{-1}J^c$.
 The first term (double pole, scalar) is the Heisenberg
 contribution; the second (simple pole, valued in~$V$)
 is the Lie bracket. Heisenberg has only the first.
\item The $R$-matrix is \emph{matrix-valued}:
 $R(z) = 1 + k\,\Omega/z + \cdots$ with
 $\Omega = \sum_a t^a \otimes t_a \in
 \mathfrak{sl}_2 \otimes \mathfrak{sl}_2$,
 while Heisenberg has $R(z) = e^{k/z}$ (scalar).
 The KZ monodromy $\exp(-2\pi ik\,\Omega)$ is a
 genuine matrix acting on $V^{\otimes n}$, not a phase.
\end{itemize}

\smallskip
\noindent
\emph{(1) Degree $n=0$.}
As in the abelian case,
$\mathrm{cyc}^0(C,C_\Delta) \cong \bC$
with $d^{\mathrm{ann}}|_{n=0} = 0$. This contributes the
vacuum class to $\HH^{\mathrm{ch}}_0(V_k(\mathfrak{sl}_2))$.

\smallskip
\noindent
\emph{(2) Degree $n=1$.}
The cyclic cotensor at degree~$1$ is
$\mathrm{cyc}^1(C,C_\Delta) \cong C$,
with underlying space
$\bigoplus_{m \ge 0} (s^{-1}V)^{\otimes m}$.
A cyclic word of tensor degree~$m$ is
$\langle s^{-1}J^{a_1}\,|\,\cdots\,|\,s^{-1}J^{a_m}\rangle$.
The four components of $d^{\mathrm{ann}}$ act as follows.

\begin{enumerate}[label=\textup{(\alph*)}]
\item $d_{\mathrm{int}} = 0$: no internal differential
 ($V_k(\mathfrak{sl}_2)$ has no $Q$-operator at the
 level of generators).

\item $d_{\mathrm{res}}$: the OPE collision residue.
 On a cyclic word of degree~$2$:
 \begin{equation}\label{eq:sl2-ann-dres-2}
 d_{\mathrm{res}}
 \langle s^{-1}J^a\,|\,s^{-1}J^b\rangle
 \;=\;
 k\,\delta^{ab}\cdot\langle\,\rangle
 \;+\;
 \epsilon^{ab}{}_c\cdot
 \langle s^{-1}J^c\rangle.
 \end{equation}
 The first term is the double-pole residue (the
 Heisenberg piece: collision contracts two generators
 to the scalar~$k\,\delta^{ab}$); the second is the
 simple-pole residue (the Lie-bracket piece: collision
 fuses $J^a$ and $J^b$ into $\epsilon^{ab}{}_c\, J^c$).
 At degree~$m \ge 3$, each cyclically adjacent pair
 $(a_i, a_{i+1})$ contributes both terms:
 \begin{equation}\label{eq:sl2-ann-dres-m}
 d_{\mathrm{res}}
 \langle s^{-1}J^{a_1}\,|\,\cdots\,|\,s^{-1}J^{a_m}\rangle
 \;=\;
 \sum_{i \in \Z/m\Z}
 \Bigl(
  k\,\delta^{a_i a_{i+1}}\cdot
  \langle\cdots\,
  \widehat{a_i}\,\widehat{a_{i+1}}
  \,\cdots\rangle
 \;+\;
  \epsilon^{a_i a_{i+1}}{}_c\cdot
  \langle\cdots\,
  s^{-1}J^c\,\cdots\rangle
 \Bigr),
 \end{equation}
 where $\widehat{a_i}\,\widehat{a_{i+1}}$ denotes
 omission of the colliding pair. The summation
 is over the $m$ cyclically adjacent pairs.
 In the abelian case ($\epsilon^{ab}{}_c = 0$), only the
 first term survives, recovering the Heisenberg formula.

\item $d_\Delta$: the deconcatenation coproduct at
 non-seam faces. Same structural form as the
 abelian case; no new features from the Lie bracket.

\item $d_{\mathrm{wrap}}$: the wrap-around differential.
 This is the principal novelty. On a cyclic word
 of degree~$m$, the last factor wraps around the
 boundary circle and is re-inserted at the beginning,
 acquiring the KZ monodromy
 (Remark~\ref{rem:wraparound-monodromy}).

 For $V_k(\mathfrak{sl}_2)$, the $R$-matrix is
 \begin{equation}\label{eq:sl2-ann-Rmatrix}
 R(z) \;=\; 1 + \frac{k\,\Omega}{z}
 + \frac{k^2\,\Omega^2}{2z^2} + \cdots
 \;=\; \exp\!\Bigl(\frac{k\,\Omega}{z}\Bigr)
 + O(1/z^2),
 \end{equation}
 where $\Omega = \sum_a t^a \otimes t_a$
 is the quadratic Casimir tensor.
 The monodromy of the KZ connection around the
 generator of $\pi_1(S^1)$ is
 \begin{equation}\label{eq:sl2-ann-KZ-monodromy}
 \mathrm{Mon}_{\mathrm{KZ}}
 \;=\;
 \cP\exp\!\Bigl(
  -\frac{k}{2\pi i}
  \oint \Omega_{ij}\, d\log(z_i - z_j)
 \Bigr)
 \;=\;
 \exp(-2\pi ik\,\Omega_{(m)}),
 \end{equation}
 where $\Omega_{(m)} = \sum_{1 \le i < j \le m}
 \Omega_{ij}$ is the total Casimir acting on
 $V^{\otimes m}$, with $\Omega_{ij}$ placing
 $\Omega$ in the $i$-th and $j$-th tensor factors.

 On a single generator ($m=1$):
 \[
  d_{\mathrm{wrap}}\langle s^{-1}J^a \rangle
  \;=\;
  \bigl(\exp(-2\pi ik\cdot 0) - 1\bigr)
  \langle s^{-1}J^a \rangle
  \;=\; 0,
 \]
 since $\Omega_{(1)} = 0$ (no pair of factors for
 the Casimir to act on).

 On a pair ($m=2$): $\Omega_{(2)} = \Omega_{12}$
 acts on $s^{-1}J^a \otimes s^{-1}J^b$ as
 $\Omega_{12}(J^a \otimes J^b) = \sum_c
 (t^c \cdot J^a) \otimes (t_c \cdot J^b)
 = \sum_c \epsilon^{ca}{}_d\, \epsilon_{c}{}^{b}{}_e\,
 J^d \otimes J^e$.
 For $\mathfrak{sl}_2$, the Casimir eigenvalue on
 $V \otimes V = \mathrm{Sym}^2 V \oplus \bC$
 (the decomposition $\mathbf{3} \otimes \mathbf{3}
 = \mathbf{5} \oplus \mathbf{3} \oplus \mathbf{1}$
 of the adjoint representation) is:
 \begin{align}
 \Omega_{12}\big|_{\mathbf{5}} &= 1,
 &
 \Omega_{12}\big|_{\mathbf{3}} &= -1,
 &
 \Omega_{12}\big|_{\mathbf{1}} &= -2,
 \label{eq:sl2-casimir-eigenvalues}
 \end{align}
 using $\Omega_{12} = \tfrac{1}{2}(C_2^{\mathrm{total}}
 - C_2^{(1)} - C_2^{(2)})$ with $C_2^{\mathrm{adj}} = 2$
 on each factor.
 The wrap-around on a cyclic two-element word is:
 \begin{equation}\label{eq:sl2-ann-wrap-2}
 d_{\mathrm{wrap}}
 \langle s^{-1}J^a\,|\,s^{-1}J^b\rangle
 \;=\;
 \bigl(
  e^{-2\pi ik\,\Omega_{12}} - 1
 \bigr)
 \langle s^{-1}J^a\,|\,s^{-1}J^b\rangle,
 \end{equation}
 where $e^{-2\pi ik\,\Omega_{12}}$ acts as a
 matrix on the colour indices.
 Projecting onto the irreducible components:
 \begin{align}
 d_{\mathrm{wrap}}\big|_{\mathbf{5}}
 &= (e^{-2\pi ik} - 1) \cdot \id_{\mathbf{5}},
 \notag \\[3pt]
 d_{\mathrm{wrap}}\big|_{\mathbf{3}}
 &= (e^{2\pi ik} - 1) \cdot \id_{\mathbf{3}},
 \label{eq:sl2-ann-wrap-isotypic}\\[3pt]
 d_{\mathrm{wrap}}\big|_{\mathbf{1}}
 &= (e^{4\pi ik} - 1) \cdot \id_{\mathbf{1}}.
 \notag
 \end{align}
 The three isotypic components acquire \emph{different}
 monodromy phases. This is the fundamental
 non-abelian phenomenon: the Heisenberg annular bar
 has a single scalar phase $e^{-2\pi ik}$ at each
 degree, while $V_k(\mathfrak{sl}_2)$ splits the
 wrap-around into representation-theoretic eigenspaces.

 The monodromy $\exp(-2\pi ik\,\Omega_{(m)})$ uses the
 \emph{unreduced} bar-complex collision residue
 $r(z) = k\,\Omega/z$, not the KZ-normalised coefficient
 $\Omega/(k+h^\vee)$.  The two differ by the Sugawara
 normalisation: reducing to conformal-block level
 (dividing by the level of the invariant form) replaces
 $k\,\Omega$ with $\Omega/(k+h^\vee)$, recovering
 the standard KZ monodromy
 $\exp\!\bigl({-}2\pi i\,\Omega/(k+h^\vee)\bigr)$
 of Theorem~\textup{\ref{thm:affine-monodromy-identification}}.
\end{enumerate}

\smallskip
\noindent
\emph{(3) Degree $n=2$.}
At degree~$2$, the indecomposable elements are
$\langle s^{-1}J^a\,|\,s^{-1}J^b\rangle$
(the same underlying vector space as degree~$1$,
degree~$2$, but now the cyclic word has two marked
segments on the boundary circle).
The four-component differential combines:
\begin{itemize}
\item $d_{\mathrm{res}}
 \langle s^{-1}J^a\,|\,s^{-1}J^b\rangle
 = k\,\delta^{ab}\cdot\langle\,\rangle
 + \epsilon^{ab}{}_c\cdot\langle s^{-1}J^c\rangle$
 (identical to degree~$1$, degree~$2$:
 equation~\eqref{eq:sl2-ann-dres-2});
\item $d_{\mathrm{wrap}}
 \langle s^{-1}J^a\,|\,s^{-1}J^b\rangle
 = (e^{-2\pi ik\,\Omega_{12}} - 1)
 \langle s^{-1}J^a\,|\,s^{-1}J^b\rangle$
 (equation~\eqref{eq:sl2-ann-wrap-2}).
\end{itemize}
The identity $(d^{\mathrm{ann}})^2 = 0$ at degree~$2$
requires cancellation between
$d_{\mathrm{res}} \circ d_{\mathrm{wrap}}$ and
$d_{\mathrm{wrap}} \circ d_{\mathrm{res}}$.
This is the annular Arnold relation
(Theorem~\ref{thm:annular-bar-differential}): the
two boundary strata of $\overline{\FM}{}^{\mathrm{ann}}_{2}$
compose to zero. At the algebraic level, it is the
statement that the KZ monodromy
$e^{-2\pi ik\,\Omega_{12}}$ \emph{intertwines} the
OPE collision map: the Lie bracket $\epsilon^{ab}{}_c$
commutes with the Casimir action $\Omega_{12}$
(because $\Omega$ is $\fg$-invariant).

\smallskip
\noindent
\emph{(4) The four-component differential: summary.}
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}l@{\;\;}l@{\;\;}l@{}}
\textbf{Component} & \textbf{Source} &
 \textbf{Value for $V_k(\mathfrak{sl}_2)$} \\
\hline
$d_{\mathrm{int}}$
 & internal differential
 & $0$ (no $Q$-operator on generators) \\[2pt]
$d_{\mathrm{res}}$
 & OPE collision on $\FM_2(\C)$
 & $k\,\delta^{ab} + \epsilon^{ab}{}_c\, J^c$
  \;(double + simple pole) \\[2pt]
$d_\Delta$
 & deconcatenation at non-seam faces
 & coaugmentation terms only \\[2pt]
$d_{\mathrm{wrap}}$
 & wrap-around at seam of $S^1$
 & matrix $\exp(-2\pi ik\,\Omega_{(m)})$
 on $V^{\otimes m}$
\end{tabular}
\end{center}
Comparison with Heisenberg
(Computation~\ref{comp:heisenberg-annular-bar}):
the Heisenberg column has $d_{\mathrm{res}} = k$
(scalar) and $d_{\mathrm{wrap}} = e^{-2\pi ik}$ (phase).
The $V_k(\mathfrak{sl}_2)$ column replaces both with
matrix-valued operations: $d_{\mathrm{res}}$ carries
the Lie bracket, and $d_{\mathrm{wrap}}$ carries the
Casimir matrix exponential.

\smallskip
\noindent
\emph{(5) $\HH_0^{\mathrm{ch}}(V_k(\mathfrak{sl}_2))$:
the character space.}
The zeroth chiral Hochschild homology is
\begin{equation}\label{eq:sl2-HH0}
\HH_0^{\mathrm{ch}}(V_k(\mathfrak{sl}_2))
\;\cong\;
V_k(\mathfrak{sl}_2)
\big/
[V_k(\mathfrak{sl}_2),\,
 V_k(\mathfrak{sl}_2)]_{\mathrm{ch}},
\end{equation}
the quotient by chiral commutators.
The chiral commutator of the generators is
$J^a_{(0)} J^b = \epsilon^{ab}{}_c\, J^c$
(the simple-pole residue), which is the
\emph{adjoint action} of $\fg$ on $V_k(\fg)$.
The quotient~\eqref{eq:sl2-HH0} is therefore the
space of $\fg$-coinvariants:
\begin{equation}\label{eq:sl2-HH0-coinv}
\HH_0^{\mathrm{ch}}(V_k(\mathfrak{sl}_2))
\;\cong\;
V_k(\mathfrak{sl}_2)_{\mathfrak{sl}_2}
\;=\;
\bigl\{
 v \in V_k(\mathfrak{sl}_2)
 \,:\,
 J^a_{(0)} v = 0
 \;\text{for all } a
\bigr\}^*,
\end{equation}
i.e., the dual of the space of $\mathfrak{sl}_2$-singular
vectors. This is a strict quotient of the Heisenberg answer
$\bC[\partial^n J^a : n \ge 0,\, a=1,2,3]$: the Lie-bracket
piece of $d_{\mathrm{res}}$ imposes the additional
$\fg$-coinvariance condition that is absent for $\cH_k$.

At \emph{integrable} level $k \in \Z_{\ge 0}$,
the algebra $V_k(\mathfrak{sl}_2)$ has finitely many
irreducible modules $L_0, L_1, \ldots, L_k$
(with $L_j$ of spin~$j/2$), and the character
space has dimension $k+1$:
\begin{equation}\label{eq:sl2-HH0-integrable}
\dim\, \HH_0^{\mathrm{ch}}(V_k(\mathfrak{sl}_2))
\;=\; k+1
\qquad (k \in \Z_{\ge 0}).
\end{equation}
The basis consists of the characters
$\chi_j(\tau) = \mathrm{tr}_{L_j}(q^{L_0 - c/24})$,
$j = 0, 1, \ldots, k$, with
$c = 3k/(k+2)$. These are the conformal blocks of
the WZW model on the torus: each character is a
trace functional obtained by inserting an element
of $\HH_0^{\mathrm{ch}}$ into the annulus.

At generic (non-integrable) level, the $\fg$-coinvariant
space is infinite-dimensional, generated by
$\mathfrak{sl}_2$-singular vectors at each conformal
weight. The graded character is
\begin{equation}\label{eq:sl2-HH0-generic-char}
\chi\bigl(\HH_0^{\mathrm{ch}}(V_k(\mathfrak{sl}_2));\, q\bigr)
\;=\;
\frac{1}{\prod_{n=1}^{\infty}(1-q^n)^3}
\;\cdot\;
P_{\mathfrak{sl}_2\text{-}\mathrm{sing}}(q),
\end{equation}
where $\prod(1-q^n)^{-3}$ is the free-boson
factor ($\dim\fg = 3$ copies) and
$P_{\mathfrak{sl}_2\text{-}\mathrm{sing}}(q)$
is the Poincar\'e polynomial of the singular
vector quotient, which depends on the level~$k$.

\smallskip
\noindent
\emph{(6) The non-abelian features: structure-constant
collision and matrix monodromy.}
Two phenomena distinguish the nonabelian annular bar
from the abelian case.

\emph{(6a) The Lie-bracket collision.}
The simple-pole term
$\epsilon^{ab}{}_c\, J^c$ in
$d_{\mathrm{res}}$ means that two generators on the
boundary circle can \emph{fuse} into a third generator,
not merely annihilate to a scalar. On a cyclic word
of degree~$3$:
\begin{multline}\label{eq:sl2-ann-dres-3}
d_{\mathrm{res}}
\langle s^{-1}J^a\,|\,s^{-1}J^b\,|\,s^{-1}J^c\rangle
\;=\;
k\,\delta^{ab}\cdot
\langle s^{-1}J^c\rangle
\;+\;
k\,\delta^{bc}\cdot
\langle s^{-1}J^a\rangle
\;+\;
k\,\delta^{ca}\cdot
\langle s^{-1}J^b\rangle \\
\;+\;
\epsilon^{ab}{}_d\cdot
\langle s^{-1}J^d\,|\,s^{-1}J^c\rangle
\;+\;
\epsilon^{bc}{}_d\cdot
\langle s^{-1}J^a\,|\,s^{-1}J^d\rangle
\;+\;
\epsilon^{ca}{}_d\cdot
\langle s^{-1}J^d\,|\,s^{-1}J^b\rangle.
\end{multline}
The first line is the Heisenberg contribution
(double-pole contractions of each adjacent pair);
the second line is the Lie-bracket contribution
(simple-pole fusions). The Jacobi identity
$\epsilon^{ab}{}_d\,\epsilon^{dc}{}_e
+ \epsilon^{bc}{}_d\,\epsilon^{da}{}_e
+ \epsilon^{ca}{}_d\,\epsilon^{db}{}_e = 0$
ensures that applying $d_{\mathrm{res}}$ twice to the
second line yields zero: this is the chain-level
statement that the $\mathfrak{sl}_2$ Jacobi identity
controls $(d^{\mathrm{ann}})^2 = 0$.

\emph{(6b) The matrix KZ monodromy.}
The wrap-around $d_{\mathrm{wrap}}$ on
$V^{\otimes m}$ is the matrix exponential
$\exp(-2\pi ik\,\Omega_{(m)})$, which does not reduce
to a scalar. The eigenvalues of $\Omega_{(m)}$ on an
irreducible $\mathfrak{sl}_2$-representation of
spin~$\ell$ inside $V^{\otimes m}$ are
$\tfrac{1}{2}(\ell(\ell+1) - m \cdot 2)$
(from $\Omega_{(m)} = \tfrac{1}{2}
(C_2^{\mathrm{total}} - \sum_i C_2^{(i)})$
with $C_2^{\mathrm{adj}} = 2$).
The wrap-around differential thus
\emph{decomposes the annular bar complex
into isotypic components}, each acquiring a
different monodromy eigenvalue
$\exp(-\pi ik(\ell(\ell+1) - 2m))$.
The isotypic decomposition of
$B^{\mathrm{ann}}_\bullet(V_k(\mathfrak{sl}_2))$
by the total-spin quantum number~$\ell$ is the
chain-level avatar of the decomposition of
$\HH^{\mathrm{ch}}_\bullet(V_k(\mathfrak{sl}_2))$
into sectors labelled by integrable representations.

The three regimes of the wrap-around, by analogy with
Computation~\ref{comp:heisenberg-annular-bar}(7):
\begin{enumerate}[label=\textup{(\roman*)}]
\item $k \in \Z_{\ge 0}$ (integrable):
 $\exp(-2\pi ik\,\Omega_{(m)})$ is a matrix
 whose eigenvalues are roots of unity.
 The annular bar complex decomposes into $k+1$
 sectors, one per integrable highest-weight
 module~$L_j$. Each sector is periodic.
\item $k \in \bQ \setminus \Z$ (rational,
 non-integrable): eigenvalues are roots of unity of
 varying orders; the annular bar complex is
 quasi-periodic with the common period determined
 by the denominator of~$k$.
\item $k \notin \bQ$ (irrational): the eigenvalues
 $\exp(-\pi ik\,\ell(\ell+1))$ for distinct spins~$\ell$
 are rationally independent. The wrap-around acts
 ergodically on each isotypic component,
 and $\HH^{\mathrm{ch}}_\bullet(V_k(\mathfrak{sl}_2))$
 is concentrated in degree~$0$.
\end{enumerate}

At integrable level, the finite-dimensionality
$\dim\,\HH_0^{\mathrm{ch}} = k+1$
(equation~\eqref{eq:sl2-HH0-integrable}) is the
statement that the wrap-around monodromy, together with
the Lie-bracket collision, selects exactly the $k+1$
conformal characters from the infinite-dimensional
space of $\fg$-coinvariants. The annular bar complex
is the chain-level mechanism behind the Verlinde formula.
\end{computation}


\subsection{The genus-1 atlas and the modular programme}%
\label{subsec:genus1-atlas-table}

\begin{computation}[Genus-$1$ atlas; \ClaimStatusProvedHere]%
\label{comp:genus1-atlas}%
\index{genus-1 atlas|textbf}%
\index{modular programme!genus-1 coefficients}%
For all standard families, the genus-$1$ invariants:

\begin{center}
\small
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{llcccccc}
\toprule
\textbf{Family} & \textbf{Class}
& $\kappa$ & $F_1 = \kappa/24$
& $c_0$ & \textbf{$r_1$ type}
& $R_1 {=} R_0$? \\
\midrule
$\cH_k$ & $\mathbf{G}$
 & $k$ & $k/24$
 & $0$ & periodic
 & $\checkmark$ \\[2pt]
$V_\Lambda$ (mom.) & $\mathbf{G}$
 & $\operatorname{rk}(\Lambda)$
 & $\operatorname{rk}(\Lambda)/24$
 & $0$ & periodic
 & $\checkmark$ \\[2pt]
$V_\Lambda$ (v.o.) & $\mathbf{L}$
 & $\dfrac{(1{+}h^\vee_\Lambda)\operatorname{rk}(\Lambda)}{2h^\vee_\Lambda}$
 & (as $V_k(\fg)$)
 & $\Omega_\Lambda \ne 0$ & quasi-per.\
 & \\[4pt]
$V_k(\fg)$ & $\mathbf{L}$
 & $\dfrac{(k{+}h^\vee)\dim\fg}{2h^\vee}$
 & $\dfrac{(k{+}h^\vee)\dim\fg}{48h^\vee}$
 & $\Omega_\fg \ne 0$ & quasi-per.\
 & \\[4pt]
$\beta\gamma$ & $\mathbf{C}$
 & $-1$
 & $-1/24$
 & $\Omega_{\mathrm{symp}} \ne 0$ & quasi-per.\
 & \\[2pt]
$\mathrm{Vir}_c$ & $\mathbf{M}$
 & $c/2$
 & $c/48$
 & $\partial T \ne 0$ & quasi-per.\
 & \\[2pt]
$\cW_3$ & $\mathbf{M}$
 & $5c/6$
 & $5c/144$
 & $\ne 0$ & quasi-per.\
 & \\[2pt]
$\cW_N$ & $\mathbf{M}$
 & $c(H_N{-}1)$
 & $c(H_N{-}1)/24$
 & $\ne 0$ & quasi-per.\
 & \\
\bottomrule
\end{tabular}
\end{center}
Here $\Omega_\fg = \sum_a t^a \otimes t_a$ is the
quadratic Casimir,
$\Omega_{\mathrm{symp}}$ is the symplectic pairing
from $\{\beta \,{}_0\, \gamma\} = 1$
\textup{(}the simple-pole OPE\textup{)},
and $\partial T = T_{(0)}T$ is the translation
derivation of the Virasoro PVA\@. The $R_1 = R_0$
column is blank when $R_1 \ne R_0$.
\end{computation}

\begin{remark}[The genus-$1$ dichotomy refines the depth
classification]%
\label{rem:genus1-dichotomy}%
\index{genus-1 dichotomy}%
\index{Coisson bracket!genus-1 classification}%
The shadow obstruction tower atlas
(Computation~\ref{comp:shadow-tower-atlas}) classifies by
the genus-$0$ shadow depth $d \in \{2,3,4,\infty\}$.
The genus-$1$ Coisson invariant $c_0$ provides an
orthogonal classification: among the seven atlas families,
$c_0 = 0$ picks out exactly the abelian algebras
($\cH_k$ and $V_\Lambda$), while $c_0 \ne 0$ picks
out everything with a Lie bracket or symplectic pairing.
The combined invariant $(d, c_0)$ produces the
three-regime classification of
Theorem~\ref{thm:genus1-endomorphism-atlas}:
the genus-$0$ depth controls the bar-complex channel
(clean for $d < \infty$, excess for $d = \infty$),
and $c_0$ controls the propagator channel.
All four classes $\mathbf{G}$, $\mathbf{L}$,
$\mathbf{C}$, $\mathbf{M}$ are chirally Koszul (PBW
degeneration holds throughout the standard landscape).
What distinguishes class~$\mathbf{M}$ is
\emph{non-formality}: the higher $\Ainf$ operations
$m_{k \ge 3}$ are non-trivial on cohomology,
the bar-complex channel is activated by the excess
self-intersection, and shadow depth is infinite.
This is a measure of structural complexity within the
Koszul world, not a failure of Koszulness.
The two invariants are complementary: the genus-$0$ depth~$d$
determines the shadow obstruction tower architecture (how many $\Ainf$
operations are non-vanishing); the genus-$1$ Coisson bracket~$c_0$
determines whether that architecture is ``decoupled''
($c_0 = 0$: modular and spectral data independent) or
``entangled'' ($c_0 \ne 0$: modular and spectral data share
common algebraic sources, as in the Verlinde formula for
affine KM or the BTZ entropy for Virasoro).
\end{remark}

\begin{remark}[The first modular coefficient and
question~\textup{(iii)} of the modular programme]%
\label{rem:modular-programme-genus1}%
\index{modular programme!first coefficient}%
\index{modular holography programme!genus 1}%
The period correction $F_1 = \kappa(\cA)/24$ is the
first genuinely modular coefficient requested in
question~(iii) of the modular holography programme
(Section~\ref{subsec:modular-holography-programme}).
In the Lagrangian picture, $F_1$ is the leading term
of the genus-$1$ self-intersection invariant
\[
R^{(1)}_\cA(z)
\;=\;
\chi\!\bigl(
 \cL_\cA^{(1)} \times_{\Mvac} \cL_\cA^{(1)}
\bigr)
\]
(Section~\ref{subsec:modular-holography-programme},
question~(iii$'$)). The three regimes of
Theorem~\ref{thm:genus1-endomorphism-atlas}
answer this question as follows:
\begin{enumerate}[label=\textup{(\alph*)},nosep]
\item \emph{Decoupled} ($c_0 = 0$):
 $R^{(1)}(z) = R^{(0)}(z)$. The genus-$1$
 Lagrangian self-intersection is trivially deformed;
 the Euler characteristic is unchanged. The only
 genus-$1$ effect is the scalar period correction
 $F_1 = \kappa/24$.

\item \emph{Propagator-entangled} ($c_0 \ne 0$, clean
 intersection):
 $R^{(1)}(z,\tau) = r^{E_\tau}(z)$ is the elliptic
 $r$-matrix~\eqref{eq:elliptic-r-matrix}, computed
 explicitly for all affine algebras and the
 $\beta\gamma$ system. The genus-$1$
 self-intersection carries additional monodromy
 $2\eta_\tau \cdot c_0$ from the $B$-cycle of
 $E_\tau$. The bar-complex channel is trivial in the
 genus-zero formal cases.

\item \emph{Doubly entangled} ($c_0 \ne 0$, excess
 intersection):
 $R^{(1)}(z,\tau)$ receives corrections from both
 channels. The propagator channel contributes the
 elliptic deformation; the bar-complex channel
 contributes corrections from the higher Swiss-cheese
 operations $m_{k \ge 3}$ (the wheel diagrams that
 source the infinite shadow obstruction tower). The algebra
 has non-formal Swiss-cheese structure (the transferred
 boundary operations $m_k^{\mathrm{SC}} \ne 0$ for all
 $k \ge 3$), though it is chirally Koszul and retains a
 well-defined Koszul dual ($\mathrm{Vir}_c^! = \mathrm{Vir}_{26-c}$)
 carrying higher $\Ainf$ operations. Computing
 $R^{(1)}_{\mathrm{Vir}_c}(z,\tau)$ explicitly is
 the concrete test case for question~(iii) of the
 modular programme.
\end{enumerate}
\end{remark}

\subsection{The complete E$_1$ ordered bar landscape}%
\label{subsec:e1-ordered-bar-landscape}%
\index{ordered bar complex!landscape table|textbf}%
\index{E1 landscape@$E_1$ landscape|textbf}

The preceding atlas tables
(Computations~\ref{comp:shadow-tower-atlas}
and~\ref{comp:genus1-atlas}) classify the standard
families by shadow depth and genus-$1$ invariants
separately. The following table assembles the
complete ordered bar landscape: all invariants of the
$\Eone$-coloured bar complex for every standard family,
in a single comparison.

\begin{computation}[Complete $\Eone$ ordered bar landscape;
\ClaimStatusProvedHere]%
\label{comp:e1-ordered-bar-landscape}%
\index{ordered bar complex!landscape!master table}%
\index{depth spectrum!landscape}%
\index{R-matrix!landscape}%
\index{Koszul dual!landscape}%

\begin{center}
\small
\renewcommand{\arraystretch}{1.5}
\setlength{\tabcolsep}{4pt}
\begin{tabular}{llccccccl}
\toprule
\textbf{Family}
 & \textbf{Class}
 & \textbf{Depth}
 & $R(z)$
 & \textbf{Koszul dual}
 & $P(t)$
 & $S_2^\dagger$
 & $c_0$
 & \textbf{Genus-$1$} \\
\midrule
\multicolumn{9}{l}{\textit{Tier~\textup{(ii)}: $\Einf$-chiral with
 OPE poles \textup{(}$R$-matrix derived from local OPE\textup{)}}} \\[2pt]
\multicolumn{9}{l}{\quad\textit{--- simple-pole families
 \textup{(}$d\log$ absorbs to $R = \tau$ or $\mathrm{Id}$
 on generators\textup{)}}} \\[2pt]
$\psi$ (fermion)
 & $\mathbf{G}$/$\mathbf{C}$
 & $\{0\}$
 & $\tau$
 & $\beta\gamma_{1/2}$
 & $1{+}t$
 & $1/4$
 & $1$
 & entangled \\[3pt]
$bc_\lambda$
 & $\mathbf{G}$/$\mathbf{C}$
 & $\{0\}$
 & $\mathrm{Id}$
 & $\beta\gamma_\lambda$
 & $1{+}2t$
 & $+1$
 & $1$
 & entangled \\[3pt]
$\beta\gamma$
 & $\mathbf{C}$
 & $\{0\}$
 & $\mathrm{Id}$
 & $bc$
 & $1{+}2t$
 & $-1$
 & $\Omega_{\mathrm{symp}}$
 & entangled \\[3pt]
\multicolumn{9}{l}{\quad\textit{--- higher-pole families
 \textup{(}$R(z) \ne \tau$\textup{)}}} \\[2pt]
$\cH_k$
 & $\mathbf{G}$
 & $\{1\}$
 & $e^{k\hbar/z}$
 & $\mathrm{Sym}^{\mathrm{ch}}(V^*)$
 & $1{+}t$
 & $1/2$
 & $0$
 & decoupled \\[3pt]
$\chi^+\chi^-$ (symp.)
 & $\mathbf{C}$
 & $\{0\}$
 & $\mathrm{Id}$
 & ferm.\ symp.
 & $1{+}2t$
 & $-1/2$
 & $\Omega_{\mathrm{symp}}$
 & entangled \\[3pt]
$V_\Lambda$ ($A_1$)
 & $\mathbf{L}$
 & $\{1,2\}$
 & $1{+}k\Omega/z$ ($k{=}1$)
 & $Y_{1/3}(\mathfrak{sl}_2)$
 & $1{+}3t$
 & $1/2$
 & $\Omega\ne 0$
 & entangled \\[3pt]
$V_\Lambda$ ($A_2$)
 & $\mathbf{L}$
 & $\{1,2\}$
 & $1{+}k\Omega/z$ ($k{=}1$)
 & $Y_\hbar(\mathfrak{sl}_3)$
 & $1{+}8t$
 & $1$
 & $\Omega\ne 0$
 & entangled \\[3pt]
$V_\Lambda$ ($D_4$)
 & $\mathbf{L}$
 & $\{1,2\}$
 & $1{+}k\Omega/z$ ($k{=}1$)
 & $Y_\hbar(\mathfrak{so}_8)$
 & $1{+}28t$
 & $2$
 & $\Omega\ne 0$
 & entangled \\[3pt]
$V_k(\mathfrak{sl}_2)$
 & $\mathbf{L}$
 & $\{1,2\}$
 & $1{+}k\Omega/z$
 & $Y_\hbar(\mathfrak{sl}_2)$
 & $1{+}3t$
 & $\dfrac{3k}{2(k{+}2)}$
 & $\Omega\ne 0$
 & entangled \\[5pt]
$V_k(\mathfrak{sl}_3)$
 & $\mathbf{L}$
 & $\{1,2\}$
 & $1{+}k\Omega/z$
 & $Y_\hbar(\mathfrak{sl}_3)$
 & $1{+}8t$
 & $\dfrac{8k}{2(k{+}3)}$
 & $\Omega\ne 0$
 & entangled \\[5pt]
$\mathrm{Vir}_c$
 & $\mathbf{M}$
 & $\{0,\ldots,n{-}1,n{+}1\}$ at degree~$n$
 & non-closed
 & Vir-Yangian
 & $1{+}t$
 & $c/2$
 & $\partial T\ne 0$
 & entangled \\[3pt]
$\cW_3$
 & $\mathbf{M}$
 & $\{0,\ldots,3,5\}$
 & non-closed
 & $\cW_3$-Yangian
 & $1{+}2t$
 & $5c/6$
 & $\ne 0$
 & entangled \\[3pt]
BP
 & $\mathbf{M}$
 & $\{0,1,2,3\}$
 & $4{\times}4$ block
 & (see text)
 & $1{+}4t$
 & (see text)
 & $\ne 0$
 & entangled \\[3pt]
Wakimoto
 & $\mathbf{L}$
 & $\{1,2\}$
 & $R_\cH \cdot R_{\beta\gamma}$
 & $\mathrm{Sym}^{\mathrm{ch}} \otimes bc$
 & $1{+}3t$
 & $\frac{3k}{2(k{+}2)}$
 & $\Omega\ne 0$
 & entangled \\[3pt]
\midrule
\multicolumn{9}{l}{\textit{Tier~\textup{(iii)}: genuinely $\Eone$-chiral
 \textup{(}$R$-matrix independent input,
 not derived from local OPE\textup{)}}} \\[2pt]
$V_q(\fg)$
 & $\mathbf{L}$
 & $\{1,2\}$
 & $R_q(\fg)$
 & (Part~\ref{part:e1-core})
 & $1{+}\dim(\fg)\,t$
 & (Part~\ref{part:e1-core})
 & $\ne 0$
 & (Part~\ref{part:e1-core}) \\
\bottomrule
\end{tabular}
\end{center}

\smallskip
\noindent
\emph{Reading the table.}
``Class'' is the shadow obstruction tower depth classification
(Definition~\ref{def:shadow-depth-intersection}).
``Depth'' is the set of cogenerator degrees minus one
(the depth spectrum of the ordered bar complex).
$R(z)$ is the spectral $R$-matrix on the fundamental
module (``non-closed'' means the $R$-matrix is
meromorphic but not closed-form as a single exponential).
$P(t)$ is the Poincar\'{e} series of the bar
cogenerators (counting bar cohomology generators by
desuspended degree).
$S_2^\dagger$ is the shadow Hessian
normalised as half the Virasoro central charge $c/2$
when the family has a Virasoro subalgebra or an
affine sub-sector (Heisenberg, lattice VOAs, affine KM,
Virasoro, $\cW_N$); for simple-pole families
($\psi$, $bc_\lambda$, $\beta\gamma$, symplectic bosons)
whose generator-level $S_2$ is the modular characteristic
$\kappa$, the table records $\kappa$. The dagger
distinguishes $S_2^\dagger$ from the Volume~I modular
characteristic $\kappa = \dim(\fg)(k{+}h^\vee)/(2h^\vee)$,
which differs for non-abelian families; e.g.\ for
$V_1(\mathfrak{sl}_2)$, $S_2^\dagger = 1/2$ but
$\kappa = 9/4$.
$c_0$ is the zeroth-product Coisson bracket
(the simple-pole OPE residue that controls genus-$1$
entanglement).

The table is organised by the three-tier $R$-matrix
classification
($\S$\ref{subsec:ordered-three-tier}).
All standard vertex algebra families are $\Einf$-chiral
(tier~(ii)): their $R$-matrices are derived from the
local OPE\@. Within tier~(ii), simple-pole families
($\psi$, $bc_\lambda$, $\beta\gamma$) have
generator-level $R = \tau$ or $\mathrm{Id}$
(the $d\log$ kernel absorbs the simple OPE pole to
a constant), while higher-pole families have genuinely
$z$-dependent $R(z)$. Wakimoto appears as a separate
row: the same algebra as $V_k(\mathfrak{sl}_2)$ but
exhibiting the $R$-matrix product decomposition
$R_\cH \cdot R_{\beta\gamma}$ from the free-field
embedding. Tier~(iii) (genuinely $\Eone$-chiral)
is represented by the quantum vertex algebra $V_q(\fg)$;
the full treatment is in Part~\ref{part:e1-core}\@.
Within each tier, the shadow depth class
($\mathbf{G}$/$\mathbf{L}$/$\mathbf{C}$/$\mathbf{M}$)
and the genus-$1$ regime provide orthogonal cuts:

\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item \emph{Finite formal} ($\mathbf{G}$, $\mathbf{L}$,
 $\mathbf{C}$): the bar complex is finitely cogenerated,
 the Swiss-cheese structure is formal at genus~$0$, and
 the Koszul dual has finitely many generators.
\item \emph{Infinite non-formal} ($\mathbf{M}$): the bar
 complex has infinitely many cogenerators
 (from composite-field exchange), the Swiss-cheese
 structure is non-formal, and the Koszul dual carries
 the full $\Ainf$ tower.
\item \emph{Genus-$1$ orthogonal cut}: within each class,
 $c_0 = 0$ gives decoupled genus-$1$ behaviour (only
 $\cH_k$ among the standard families), while $c_0 \ne 0$
 gives entangled behaviour (all other families).
\end{enumerate}
The Virasoro depth column $\{0,\ldots,n{-}1,n{+}1\}$ encodes the weight-depth identity $w + d = n - 1$ and the structural gap at $d = n$ (Theorem~\ref{thm:gap-migration}(i)--(ii)); the $\cW_3$ depth column $\{0,\ldots,3,5\}$ reflects the gap migration $d_{\mathrm{gap}} = 2N + n - 4 = 4$ at degree~$2$ (part~(iv)).
\end{computation}

\subsection{Coset and orbifold bar complexes}%
\label{subsec:coset-orbifold-bar}%
\index{coset!ordered bar complex|textbf}%
\index{orbifold!ordered bar complex|textbf}%
\index{GKO coset!bar complex|textbf}%
\index{permutation orbifold!bar complex|textbf}

The standard families in the landscape table
(Computation~\ref{comp:e1-ordered-bar-landscape})
are all \emph{primitive}: each is a single vertex algebra, not
constructed from other vertex algebras by algebraic operations.
Two fundamental constructions produce new vertex algebras from
old: the \emph{coset} (commutant) and the \emph{orbifold}
(invariant subalgebra under a finite group).
Both are $\Einf$-chiral (they are vertex algebras, hence local),
and both have ordered bar complexes that are determined by, but
differ from, the bar complexes of their parent algebras.
This section computes the ordered bar complexes for the three
canonical constructions: the GKO coset, the $\Z_2$ lattice
orbifold, and the permutation orbifold.

\subsubsection{The GKO coset: bar complex of a commutant}%
\label{subsubsec:gko-coset-bar}%
\index{GKO coset!ordered bar complex|textbf}%
\index{coset!commutant!bar complex}%
\index{unitary minimal models!bar complex}

The Goddard--Kent--Olive coset construction starts from the
tensor product
$\cA := V_1(\mathfrak{sl}_2) \otimes V_{k-1}(\mathfrak{sl}_2)$,
which carries the diagonal subalgebra
$V_k(\mathfrak{sl}_2) \hookrightarrow \cA$
at the combined level $k = 1 + (k{-}1)$. The coset is the
commutant
\begin{equation}\label{eq:gko-coset-def}
\cC(k)
\;:=\;
\mathrm{Com}\bigl(
 V_k(\mathfrak{sl}_2),\;
 V_1(\mathfrak{sl}_2) \otimes V_{k-1}(\mathfrak{sl}_2)
\bigr)\,,
\end{equation}
the subalgebra of~$\cA$ commuting with the diagonal currents.
For $k \ge 1$ integer, $\cC(k)$ is the unitary minimal model
$\cM(k+1, k+2)$ with central charge
\begin{equation}\label{eq:gko-central-charge}
c(k) \;=\; 1 - \frac{6}{(k+1)(k+2)}\,.
\end{equation}

\begin{computation}[GKO coset ordered bar complex;
\ClaimStatusProvedHere]%
\label{comp:gko-coset-ordered-bar}%
\index{GKO coset!depth spectrum}%
\index{GKO coset!R-matrix}%
\index{unitary minimal models!Koszul dual}%
\index{GKO coset!genus 1}%
The commutant $\cC(k)$ is a Virasoro minimal model:
it is generated by the Virasoro field~$T$ (weight~$2$)
alone, with finitely many irreducible modules.
At $k = 1$: $\cC(1) \cong \C$ (trivial, $c = 0$).
At $k = 2$: $\cC(2) \cong \cM(3,4)$, the Ising model
($c = 1/2$, three irreducible modules).
At $k = 3$: $\cC(3) \cong \cM(4,5)$, the tricritical
Ising model ($c = 7/10$). The higher unitary minimal
models $\cM(k{+}1, k{+}2)$ for $k \ge 4$ are all
Virasoro algebras at irrational central charge
$c(k) < 1$.

\smallskip
\noindent
\emph{Depth spectrum and class.}
Since $\cC(k)$ is a Virasoro algebra at central charge
$c(k)$, the OPE is
$T(z)\,T(w) \sim (c/2)/(z-w)^4
+ 2T(w)/(z-w)^2 + \partial T(w)/(z-w)$,
with the characteristic fourth-order pole.
The bar complex inherits the Virasoro shadow obstruction tower:
class~$\mathbf{M}$, infinite shadow depth,
non-formal Swiss-cheese structure.
The shadow coefficients $S_r(\cC(k))$ are exactly the
Virasoro shadow coefficients
(Computation~\ref{comp:virasoro-shadow-tower})
evaluated at $c = c(k) = 1 - 6/((k{+}1)(k{+}2))$.
The denominators involve $c(k) \cdot (5c(k) + 22)^{\lfloor(r-2)/2\rfloor}$,
which is nonzero for all $k \ge 2$: the
Ising value $c = 1/2$ and Lee--Yang value $c = -22/5$
are the only potential poles, and $5c(k) + 22 \ne 0$
for $k \ge 2$.

\smallskip
\noindent
\emph{Operations: inherited from the tensor product.}
The embedding $\cC(k) \hookrightarrow \cA$ is a
morphism of vertex algebras, hence induces a chain map
\begin{equation}\label{eq:gko-bar-inclusion}
\iota_*\colon
\bar{B}^{\mathrm{ch,ord}}(\cC(k))
\;\longrightarrow\;
\bar{B}^{\mathrm{ch,ord}}(\cA)\,,
\end{equation}
and the image of $\iota_*$ consists of those bar elements
that commute with the diagonal $V_k(\mathfrak{sl}_2)$-action.
Concretely, for bar degree~$n$:
\begin{equation}\label{eq:gko-bar-invariant}
\bar{B}^{\mathrm{ch,ord}}_n(\cC(k))
\;\cong\;
\bigl\{
\xi \in \bar{B}^{\mathrm{ch,ord}}_n(\cA)
\;\bigm|\;
J^a_{\mathrm{diag}} \cdot \xi = 0\;\;
\text{for all $a$}
\bigr\}\,,
\end{equation}
where $J^a_{\mathrm{diag}} = J^a_{(1)} + J^a_{(k-1)}$ are
the diagonal affine currents and the action is by the
coderivation extending the $V_k$-module structure on~$\cA$.
The bar differential $d_{\barBch}$ preserves this invariant
subspace (it is built from OPE residues of $\cC(k)$-fields,
which commute with~$J^a_{\mathrm{diag}}$). The coproduct
$\Delta$ also preserves invariance (it is a tensor
coalgebra operation on the ordering, not on the $\fg$-action).
Therefore $\bar{B}^{\mathrm{ch,ord}}(\cC(k))$ inherits the full
$E_1$ dg coalgebra structure from~$\bar{B}^{\mathrm{ch,ord}}(\cA)$ by restriction to
invariants.

The bar complex of $\cC(k)$ is \emph{not} the quotient of
$\bar{B}^{\mathrm{ch,ord}}(\cA)$ by the ideal generated by the
diagonal currents. Rather, it is the \emph{invariant
subcomplex}: the commutant is a subalgebra, not a quotient
algebra, and bar of a subalgebra is a sub-coalgebra.

\smallskip
\noindent
\emph{Binary operation.}
At $k = 2$ (Ising model, $c = 1/2$), the single generator
is $T$ and the binary operation is
$m_2(T, T;\, \lambda) = (1/4)\lambda^3 + 2T\lambda
+ \partial T$.
This is the standard Virasoro $m_2$ at $c = 1/2$.
For $k = 2$, the GKO bar complex is isomorphic to
$\bar{B}^{\mathrm{ch,ord}}(\mathrm{Vir}_{1/2})$, already
in the landscape as a specialisation of the Virasoro
row at $c = 1/2$.

\smallskip
\noindent
\emph{$r$-matrix.}
The coset $r$-matrix is the restriction of the tensor
product $r$-matrix to the $V_k$-singlet sector.
For $\cA = V_1(\mathfrak{sl}_2) \otimes V_{k-1}(\mathfrak{sl}_2)$,
the collision residue of the tensor product is
\[
r_\cA(z)
\;=\;
\frac{\Omega^{(1)}}{z}
\;+\;
\frac{\Omega^{(2)}}{z}\,,
\]
where $\Omega^{(1)}$ and $\Omega^{(2)}$ are the
$\mathfrak{sl}_2$ Casimirs acting on the first and
second tensor factors respectively (the levels $k = 1$
and $k - 1$ enter through the collision residues of the
individual factors). The coset $r$-matrix is the
projection to the diagonal $V_k$-singlet sector:
\begin{equation}\label{eq:gko-r-matrix}
r_{\cC(k)}(z)
\;=\;
\mathrm{pr}_{\mathrm{sing}}
\circ\; r_\cA(z)
\;\circ\; \mathrm{incl}_{\mathrm{sing}}\,,
\end{equation}
where $\mathrm{pr}_{\mathrm{sing}}$ projects to
$\{v : J^a_{\mathrm{diag},0}\, v = 0\}$.
On minimal-model modules $L_{r,s}^{(k)}$ (classified
by the Kac table of $\cM(k{+}1, k{+}2)$), the $R$-matrix
is non-closed-form: it inherits the non-formal Virasoro
structure of the shadow obstruction tower at $c = c(k)$.

\smallskip
\noindent
\emph{Koszul dual.}
Since $\cC(k)$ is a Virasoro algebra at central
charge~$c(k)$, the Koszul dual is
$\cC(k)^! = \mathrm{Vir}_{26 - c(k)}$.
The complementarity constant is
\begin{equation}\label{eq:gko-complementarity}
K(\cC(k))
\;=\;
\kappa(\cC(k)) + \kappa(\cC(k)^!)
\;=\;
\frac{c(k)}{2} + \frac{26 - c(k)}{2}
\;=\; 13\,,
\end{equation}
matching the universal Virasoro complementarity constant
$K = 13$.

\smallskip
\noindent
\emph{Modular characteristic.}
$\kappa(\cC(k)) = c(k)/2$
(the Virasoro value at central charge $c(k)$).
The genus-$1$ regime is entangled ($c_0 = \partial T \ne 0$).

\smallskip
\noindent
\emph{Landscape entry.}
\begin{center}
\small
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{llccccccl}
\toprule
\textbf{Family}
 & \textbf{Class}
 & \textbf{Depth}
 & $R(z)$
 & \textbf{Koszul dual}
 & $P(t)$
 & $\kappa$
 & $c_0$
 & \textbf{Genus-$1$} \\
\midrule
$\cC(2)$ (Ising)
 & $\mathbf{M}$
 & as Vir
 & non-closed
 & $\mathrm{Vir}_{25.5}$
 & $1{+}t$
 & $1/4$
 & $\ne 0$
 & entangled \\[3pt]
$\cC(k)$ ($k \ge 3$)
 & $\mathbf{M}$
 & as Vir
 & non-closed
 & $\mathrm{Vir}_{26-c(k)}$
 & $1{+}t$
 & $\frac{c(k)}{2}$
 & $\ne 0$
 & entangled \\
\bottomrule
\end{tabular}
\end{center}
\end{computation}

\begin{remark}[The coset bar complex as a relative construction]%
\label{rem:coset-relative-bar}%
\index{coset!relative bar complex}%
\index{relative bar complex!coset}%
The coset bar complex admits a relative interpretation.
The tensor product $\cA = V_1 \otimes V_{k-1}$ has bar
complex $\bar{B}^{\mathrm{ch,ord}}(\cA) \cong
\bar{B}^{\mathrm{ch,ord}}(V_1) \otimes
\bar{B}^{\mathrm{ch,ord}}(V_{k-1})$ (the K\"{u}nneth
isomorphism for ordered bar complexes of mutually
regular tensor products). The diagonal embedding
$V_k \hookrightarrow \cA$ defines a $V_k$-coaction
on $\bar{B}^{\mathrm{ch,ord}}(\cA)$, and the coset bar
complex is the \emph{relative cotensor}:
\begin{equation}\label{eq:coset-relative-cotensor}
\bar{B}^{\mathrm{ch,ord}}(\cC(k))
\;\simeq\;
\C \;\square_{\barBch(V_k)}^{\mathbf{R}}\;
\bar{B}^{\mathrm{ch,ord}}(\cA)\,,
\end{equation}
where the left factor $\C$ denotes the trivial
$\barBch(V_k)$-comodule (the coaugmentation) and the
derived cotensor $\square^{\mathbf{R}}$ is computed in
the coderived category. This is the bar-side avatar of
the commutant: the commutant algebra is the
$V_k$-invariant subalgebra; the commutant bar complex is
the $\barBch(V_k)$-coinvariant sub-coalgebra.

This relative presentation makes the GKO coset construction
functorial at the level of bar complexes: the coset map
$V_k \hookrightarrow \cA \twoheadleftarrow \cC(k)$ lifts
to a fiber sequence
$\barBch(\cC(k)) \to \barBch(\cA)
\to \barBch(V_k)$
in the category of conilpotent dg coalgebras.
\end{remark}


\subsubsection{The $\Z_2$ orbifold: bar complex of invariants}%
\label{subsubsec:z2-orbifold-bar}%
\index{orbifold!Z2@$\Z_2$!bar complex|textbf}%
\index{lattice VOA!orbifold|textbf}%
\index{orbifold!c=1 theory}

For a lattice VOA $V_\Lambda$ with an automorphism
$\sigma\colon V_\Lambda \to V_\Lambda$ of finite order,
the orbifold (or invariant) subalgebra $V_\Lambda^\sigma$ is
the fixed-point vertex algebra. The canonical example is the
$\Z_2$~orbifold of the $A_1$ lattice VOA.

\begin{computation}[$\Z_2$ orbifold ordered bar complex;
\ClaimStatusProvedHere]%
\label{comp:z2-orbifold-ordered-bar}%
\index{orbifold!Z2@$\Z_2$!depth spectrum}%
\index{orbifold!Z2@$\Z_2$!R-matrix}%
\index{orbifold!Z2@$\Z_2$!Koszul dual}%
\index{orbifold!c=1 theory!bar complex}%
The lattice $\Lambda = \sqrt{2}\,\Z$ has lattice VOA
$V_\Lambda \cong L_1(\mathfrak{sl}_2)$
(Computation~\ref{comp:lattice-voa-ordered-bar}).
The $\Z_2$ automorphism is the Cartan involution
$\sigma\colon J \mapsto -J$,
$e^\alpha \mapsto e^{-\alpha}$,
$e^{-\alpha} \mapsto e^{\alpha}$.
The fixed-point algebra is
\begin{equation}\label{eq:z2-orbifold-def}
V_\Lambda^{\Z_2}
\;=\;
\bigl\{v \in V_\Lambda \;\bigm|\; \sigma(v) = v\bigr\}\,.
\end{equation}
This is the $c = 1$ orbifold theory at the self-dual radius.

\smallskip
\noindent
\emph{Generators.}
The $\Z_2$-invariant generators are:
\begin{itemize}[nosep]
\item the Virasoro field
 $T = \tfrac{1}{2}\,{:}JJ{:}$
 (conformal weight~$2$, invariant since $\sigma(J^2) = (-J)^2 = J^2$);
\item the even vertex operator combinations
 $X^+ = e^\alpha + e^{-\alpha}$
 (weight~$1$, $\sigma(X^+) = e^{-\alpha} + e^\alpha = X^+$);
\item the bilinear $Y = {:}(e^\alpha)(e^{-\alpha}){:}$
 (weight~$2$, invariant).
\end{itemize}
The odd combination $X^- = e^\alpha - e^{-\alpha}$ has
$\sigma(X^-) = -X^-$ and is \emph{not} in $V_\Lambda^{\Z_2}$;
it generates the unique nontrivial twisted module.
The Heisenberg current $J$ itself satisfies $\sigma(J) = -J$,
so $J \notin V_\Lambda^{\Z_2}$. The orbifold algebra
does not contain the Heisenberg subalgebra; it is generated
by the Virasoro field, the invariant vertex operators, and
their composites.

\smallskip
\noindent
\emph{Bar complex as invariant sub-coalgebra.}
The $\Z_2$-action on $V_\Lambda$ induces a $\Z_2$-action on
the ordered bar complex $\bar{B}^{\mathrm{ch,ord}}(V_\Lambda)$
by the diagonal action on tensor factors:
\begin{equation}\label{eq:z2-bar-action}
\sigma\bigl[a_1 \,|\, \cdots \,|\, a_n\bigr]
\;=\;
[\sigma(a_1) \,|\, \cdots \,|\, \sigma(a_n)]\,.
\end{equation}
Since $\sigma$ is an automorphism of $V_\Lambda$, it
commutes with both the bar differential $d_{\barBch}$
(which is built from the OPE, preserved by automorphisms)
and the deconcatenation coproduct~$\Delta$ (which depends
only on the tensor ordering). Therefore:
\begin{equation}\label{eq:z2-orbifold-bar}
\bar{B}^{\mathrm{ch,ord}}(V_\Lambda^{\Z_2})
\;\cong\;
\bar{B}^{\mathrm{ch,ord}}(V_\Lambda)^{\Z_2}\,,
\end{equation}
the $\Z_2$-invariant sub-coalgebra of the lattice bar complex.
Both the bar differential and the deconcatenation coproduct restrict to
the invariant subspace.

\smallskip
\noindent
\emph{Depth spectrum: $\{1, 2, \ldots\}$, class~$\mathbf{M}$.}
The orbifold algebra $V_\Lambda^{\Z_2}$ contains the
Virasoro field~$T$ of conformal weight~$2$ with the
fourth-order OPE at $c = 1$. The Virasoro subalgebra
forces class~$\mathbf{M}$, infinite shadow depth, and
non-formal Swiss-cheese structure, the same mechanism
as for any algebra containing a Virasoro sub-sector.
This represents a depth \emph{increase} relative to the
parent: $V_\Lambda \cong L_1(\mathfrak{sl}_2)$ is
class~$\mathbf{L}$ (depth~$3$), but $V_\Lambda^{\Z_2}$
is class~$\mathbf{M}$ because the Sugawara construction
$T = \tfrac{1}{2}\,{:}JJ{:}$ introduces the fourth-order
pole.

The mechanism is: the orbifold removes the
simple-pole generator~$J$ (which is odd under $\sigma$)
but retains its quadratic composite $T = \tfrac{1}{2}{:}JJ{:}$,
which has a fourth-order self-OPE. The orbifold
trades a class-$\mathbf{L}$ generating set
$\{J, e^\alpha, e^{-\alpha}\}$ for a class-$\mathbf{M}$
generating set $\{T, X^+, Y\}$. The DS
depth-jump mechanism
(Computation~\ref{comp:w3-shadow-tower})
is at work here in a different guise: passing from
$V_\Lambda$ to $V_\Lambda^{\Z_2}$ replaces generators
by composites, just as the DS reduction
$V_k(\mathfrak{sl}_3) \to \cW_3$ replaces currents
by the Sugawara field and its partners.

\smallskip
\noindent
\emph{Operations: $m_2$ on invariant generators.}
On the generator $X^+ = e^\alpha + e^{-\alpha}$:
\begin{align}
m_2(X^+, X^+;\, \lambda)
&\;=\;
m_2(e^\alpha{+}e^{-\alpha},\, e^\alpha{+}e^{-\alpha};\, \lambda)
\notag
\\[4pt]
&\;=\;
\underbrace{m_2(e^\alpha, e^{-\alpha};\, \lambda)
+ m_2(e^{-\alpha}, e^\alpha;\, \lambda)}_{\text{cross terms}}
\;+\;
\underbrace{m_2(e^\alpha, e^\alpha;\, \lambda)
+ m_2(e^{-\alpha}, e^{-\alpha};\, \lambda)}_{ = 0}
\notag
\\[4pt]
&\;=\;
(\lambda + \alpha \cdot J)
+ (\lambda - \alpha \cdot J)
\;=\;
2\lambda\,,
\label{eq:z2-orbifold-m2-xplus}
\end{align}
using the lattice OPE~\eqref{eq:lattice-vertex-ope}
and the vanishing~\eqref{eq:lattice-vertex-vertex-vanishing}.
The Lie-bracket terms $\pm\alpha \cdot J$ cancel in
the invariant sector because $J$ is $\sigma$-odd.
On the Virasoro field $T$, the binary operation is
the standard Virasoro $m_2$ at $c = 1$:
$m_2(T, T;\, \lambda) = \tfrac{1}{2}\lambda^3
+ 2T\lambda + \partial T$.

\smallskip
\noindent
\emph{$r$-matrix.}
The orbifold $r$-matrix is the restriction of the parent
$r$-matrix to the $\sigma$-invariant sector:
\begin{equation}\label{eq:z2-orbifold-r-matrix}
r_{V^{\Z_2}}(z)
\;=\;
\mathrm{pr}_{\sigma = +1}\;\circ\;
r_{V_\Lambda}(z)
\;\circ\;
\mathrm{incl}_{\sigma = +1}\,.
\end{equation}
On the $\sigma$-invariant modules of $V_\Lambda^{\Z_2}$, the
Casimir $\Omega_{\mathfrak{sl}_2}$ projects to the
$\sigma$-invariant part. The off-diagonal components
$(e^\alpha \otimes e^{-\alpha} + e^{-\alpha} \otimes e^\alpha)$
contribute; the Cartan component $\tfrac{1}{2} J \otimes J$
does not (it is odd--odd $= $ even, so it contributes).
The restricted $r$-matrix is non-closed form:
$r_{V^{\Z_2}}(z)$ is a meromorphic function of~$z$
with poles, but the projection to the $\Z_2$-invariant
subspace of $\End(M_1 \otimes M_2)$ produces a truncated
Casimir.

\smallskip
\noindent
\emph{Koszul dual.}
The Koszul dual $(V_\Lambda^{\Z_2})^!$ is not the
$\Z_2$-invariant part of $Y_{1/3}(\mathfrak{sl}_2)$
(the Koszul dual of the parent). Rather, it is a distinct
object: the orbifold Koszul dual, determined by the bar
complex $\bar{B}^{\mathrm{ch,ord}}(V_\Lambda^{\Z_2})
= \bar{B}^{\mathrm{ch,ord}}(V_\Lambda)^{\Z_2}$.
Since the orbifold is class~$\mathbf{M}$, the Koszul dual
carries the full infinite $\Ainf$ tower.

\smallskip
\noindent
\emph{Genus-$1$.}
The orbifold partition function is
\begin{equation}\label{eq:z2-orbifold-partition}
Z_1(V_\Lambda^{\Z_2})
\;=\;
\frac{1}{2}\biggl(
\frac{|\Theta_\Lambda(\tau)|^2}{|\eta(\tau)|^2}
\;+\;
\biggl|\frac{\eta(\tau)}{\theta_2(\tau)}\biggr|
\;+\;
\biggl|\frac{\eta(\tau)}{\theta_4(\tau)}\biggr|
\;+\;
\biggl|\frac{\eta(\tau)}{\theta_3(\tau)}\biggr|
\biggr)\,,
\end{equation}
the standard orbifold modular-invariant partition function
(the $D_4$ modular invariant of $\widehat{\mathfrak{su}}(2)_1$,
not to be confused with the $D_4$ lattice VOA of
Computation~\ref{comp:lattice-voa-D4-ordered-bar}).
The genus-$1$ regime is entangled
($c_0 \ne 0$ from the Virasoro subalgebra).
The shadow Hessian is $S_2 = c/2 = 1/2$.
\end{computation}


\begin{remark}[Orbifold depth jump: L $\to$ M by composite generation]%
\label{rem:orbifold-depth-jump}%
\index{orbifold!depth jump}%
\index{depth jump!orbifold}%
\index{shadow depth!orbifold increase}%
The $\Z_2$ orbifold of $V_{\sqrt{2}\Z}$ exhibits a
\emph{depth jump}: the parent algebra is class~$\mathbf{L}$
(depth~$3$) but the orbifold is class~$\mathbf{M}$
(depth~$\infty$). The mechanism is the same as the
DS reduction depth jump
(Computation~\ref{comp:w3-shadow-tower}):
passing to invariants removes simple-pole generators
and replaces them with their quadratic composites,
which carry fourth-order poles. The DS reduction
$V_k(\mathfrak{sl}_3) \to \cW_3$ removes currents and
introduces $T = T_{\mathrm{Sug}}$; the $\Z_2$ orbifold
removes $J$ and retains $T = \tfrac{1}{2}\,{:}JJ{:}$.
Both are instances of a general principle: \emph{passing to
invariants under a reductive group action can only
increase shadow depth, never decrease it}, because the
invariant algebra is generated by composites whose
pole orders are bounded below by the pole orders of the
parent generators, and composite fields generically have
higher pole orders.
\end{remark}


\subsubsection{The permutation orbifold: bar complex of the symmetric product}%
\label{subsubsec:permutation-orbifold-bar}%
\index{permutation orbifold!bar complex|textbf}%
\index{symmetric product!bar complex|textbf}%
\index{orbifold!permutation!bar complex}

Given a vertex algebra~$V$ and a positive integer~$n$,
the permutation orbifold is the $S_n$-invariant subalgebra
\begin{equation}\label{eq:perm-orbifold-def}
V^{(n)}
\;:=\;
(V^{\otimes n})^{S_n}\,,
\end{equation}
where $S_n$ acts by permuting the tensor factors.
The permutation orbifold is an $\Einf$-chiral algebra
(a vertex algebra) for any choice of~$V$.

\begin{computation}[Permutation orbifold ordered bar complex;
\ClaimStatusProvedHere]%
\label{comp:permutation-orbifold-bar}%
\index{permutation orbifold!depth spectrum}%
\index{permutation orbifold!symmetric product formula}%
\index{permutation orbifold!Koszul dual}%
\index{symmetric product!bar complex!explicit}%

\smallskip
\noindent
\emph{Tensor product bar complex.}
For mutually regular vertex algebras $V_1, \ldots, V_n$
(no singular cross-OPE), the ordered bar complex of the
tensor product satisfies the K\"{u}nneth isomorphism:
\begin{equation}\label{eq:tensor-product-bar}
\bar{B}^{\mathrm{ch,ord}}(V_1 \otimes \cdots \otimes V_n)
\;\cong\;
\bar{B}^{\mathrm{ch,ord}}(V_1)
\otimes \cdots \otimes
\bar{B}^{\mathrm{ch,ord}}(V_n)\,,
\end{equation}
with the bar differential acting as the sum of
individual bar differentials and the coproduct as
the product of individual coproducts. For $n$~copies
of the same algebra $V$:
$\bar{B}^{\mathrm{ch,ord}}(V^{\otimes n})
\cong \bar{B}^{\mathrm{ch,ord}}(V)^{\otimes n}$.

\smallskip
\noindent
\emph{Permutation action.}
The $S_n$-action on $V^{\otimes n}$ permutes the tensor
factors: $\sigma(v_1 \otimes \cdots \otimes v_n)
= v_{\sigma^{-1}(1)} \otimes \cdots \otimes v_{\sigma^{-1}(n)}$.
This induces an $S_n$-action on the bar complex:
\begin{equation}\label{eq:perm-bar-action}
\sigma\bigl[a_1^{(i_1)} \,|\, \cdots \,|\, a_m^{(i_m)}\bigr]
\;=\;
[a_1^{(\sigma(i_1))} \,|\, \cdots \,|\, a_m^{(\sigma(i_m))}]\,,
\end{equation}
where the superscript $(i)$ records which tensor factor
the generator belongs to. The bar differential and
coproduct commute with this action (the OPE of
$V^{\otimes n}$ permutes with the tensor factor labels,
and the deconcatenation coproduct depends only on the
bar ordering, not on the tensor factor labels).
Therefore:
\begin{equation}\label{eq:perm-orbifold-bar}
\bar{B}^{\mathrm{ch,ord}}(V^{(n)})
\;\cong\;
\bigl(\bar{B}^{\mathrm{ch,ord}}(V)^{\otimes n}\bigr)^{S_n}\,,
\end{equation}
the $S_n$-invariant sub-coalgebra of the $n$-fold tensor
product of bar complexes. This is the ordered bar complex
analogue of the symmetric product.

\smallskip
\noindent
\emph{Structure of the invariant sub-coalgebra.}
The invariant bar complex~\eqref{eq:perm-orbifold-bar}
is \emph{not} the symmetric tensor product
$\mathrm{Sym}^n(\barBch(V))$ (which would be the
$S_n$-coinvariants, a quotient). It is the
$S_n$-\emph{invariants}, a subcoalgebra. In
characteristic~$0$, the norm map
$N = \sum_{\sigma \in S_n} \sigma$ provides a splitting
$(\barBch(V)^{\otimes n})^{S_n}
\hookrightarrow \barBch(V)^{\otimes n}
\twoheadrightarrow (\barBch(V)^{\otimes n})_{S_n}$,
and the invariants and coinvariants are isomorphic. The
permutation orbifold bar complex is therefore isomorphic
to the symmetric product of bar complexes.

\smallskip
\noindent
\emph{Generators of the invariant bar complex.}
The invariant generators are the symmetrised
bar elements:
\begin{equation}\label{eq:perm-bar-generators}
[a]_{\mathrm{sym}}^{(n)}
\;:=\;
\frac{1}{n!}\sum_{\sigma \in S_n}
\sigma\bigl[a^{(1)}\bigr]
\;=\;
\frac{1}{n!}\sum_{i=1}^{n}
[a^{(i)}]\,,
\end{equation}
for each generator~$a$ of~$V$.
The bar complex of $V^{(n)}$ also contains
\emph{multi-factor} invariants, i.e.\ bar elements
involving generators from distinct tensor factors
$[a^{(i)} \,|\, b^{(j)}]$ with $i \ne j$, symmetrised
over~$S_n$.

\smallskip
\noindent
\emph{Depth spectrum and class.}
The shadow depth of $V^{(n)}$ depends on $V$:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item If $V$ is class~$\mathbf{G}$ (e.g.\ $\cH_k$):
 each copy contributes only $m_2$, and the tensor
 product remains class~$\mathbf{G}$. Since
 $S_n$-invariants preserve the class (no new composites
 arise from symmetrisation of abelian generators),
 $V^{(n)}$ is class~$\mathbf{G}$.

\item If $V$ is class~$\mathbf{L}$ (e.g.\ $V_k(\fg)$):
 the single-factor bar differential has $m_3 \ne 0$.
 Symmetrised multi-factor elements
 $[a^{(i)} \,|\, b^{(j)} \,|\, c^{(i)}]$ with
 $i \ne j$ give new cross-factor $m_3$ terms, but
 the Jacobi identity still kills $m_4$ (the Jacobi
 mechanism operates within each factor and the cross-factor
 terms cannot generate fourth-order poles).
 $V^{(n)}$ remains class~$\mathbf{L}$.

\item If $V$ is class~$\mathbf{M}$
 (e.g.\ $\mathrm{Vir}_c$):
 the full infinite shadow obstruction tower of each copy is
 inherited by the tensor product and hence by the
 invariants. $V^{(n)}$ is class~$\mathbf{M}$.
 The Sugawara-like field
 $T_{\mathrm{tot}} = T^{(1)} + \cdots + T^{(n)}$
 at central charge~$nc$ provides the class-$\mathbf{M}$
 generator for the permutation orbifold.
\end{enumerate}

In every case, the permutation orbifold preserves or
inherits the shadow depth class of the parent. There
is no depth jump, because the $S_n$-invariant subalgebra
of a tensor product does not create new composite fields
that were absent in the parent: the composites within each
factor are already present, and the cross-factor composites
are products (not genuinely new composites in the OPE
sense).

\smallskip
\noindent
\emph{Modular characteristic.}
The modular characteristic is additive on tensor products:
$\kappa(V^{\otimes n}) = n\,\kappa(V)$. The orbifold
does not change the modular characteristic
(it is a subalgebra at the same central charge):
\begin{equation}\label{eq:perm-kappa}
\kappa(V^{(n)}) \;=\; n\,\kappa(V)\,.
\end{equation}

\smallskip
\noindent
\emph{$r$-matrix.}
The $r$-matrix of the tensor product is the sum of the
individual $r$-matrices:
$r_{V^{\otimes n}}(z) = \sum_{i=1}^{n} r_V^{(i)}(z)$,
where $r_V^{(i)}$ acts on the $i$-th tensor factor.
The orbifold $r$-matrix is the $S_n$-symmetrisation:
\begin{equation}\label{eq:perm-r-matrix}
r_{V^{(n)}}(z)
\;=\;
\mathrm{pr}_{S_n}\;\circ\;
\biggl(\sum_{i=1}^{n} r_V^{(i)}(z)\biggr)
\;\circ\; \mathrm{incl}_{S_n}\,,
\end{equation}
projected to the $S_n$-invariant sector.

\smallskip
\noindent
\emph{Koszul dual.}
For mutually regular tensor products, the Koszul dual
distributes: $(V_1 \otimes V_2)^! \simeq V_1^! \otimes V_2^!$.
For the permutation orbifold:
\begin{equation}\label{eq:perm-koszul-dual}
(V^{(n)})^!
\;\simeq\;
\bigl((V^!)^{\otimes n}\bigr)^{S_n}
\;=\;
(V^!)^{(n)}\,.
\end{equation}
Koszul duality commutes with the permutation orbifold:
the Koszul dual of the orbifold is the orbifold of
the Koszul dual. For $V = \cH_k$:
$((\cH_k)^{(n)})^! \simeq
(\mathrm{Sym}^{\mathrm{ch}}(V^*))^{(n)}$.
For $V = V_1(\mathfrak{sl}_2)$:
$((V_1(\mathfrak{sl}_2))^{(n)})^! \simeq
(Y_{1/3}(\mathfrak{sl}_2))^{(n)}$, the $S_n$-invariant
subalgebra of the $n$-fold Yangian tensor product.

\smallskip
\noindent
\emph{Genus-$1$ partition function.}
The genus-$1$ partition function of the permutation orbifold
is related to the parent by the DMVV formula:
\begin{equation}\label{eq:dmvv}
\sum_{n \ge 0} p^n\, Z_1(V^{(n)};\, \tau)
\;=\;
\prod_{m > 0,\, \ell \in \Z}
\bigl(1 - p^m\, q^\ell\bigr)^{-c_{m\ell}}\,,
\end{equation}
where $q = e^{2\pi i\tau}$ and $c_{m\ell}$ are the
Fourier coefficients of $Z_1(V;\, \tau)$. This is the
generating function for symmetric orbifolds, first
established by Dijkgraaf--Moore--Verlinde--Verlinde.
In the bar-complex language, the DMVV formula is the
statement that the generating function of Euler
characteristics of the symmetric product of bar
complexes reproduces the infinite-product side
of~\eqref{eq:dmvv}.

\smallskip
\noindent
\emph{Landscape entries.}
\begin{center}
\small
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{llccccccl}
\toprule
\textbf{Family}
 & \textbf{Class}
 & \textbf{Depth}
 & $R(z)$
 & \textbf{Koszul dual}
 & $P(t)$
 & $S_2^\dagger$
 & $c_0$
 & \textbf{Genus-$1$} \\
\midrule
$\cH_k^{(n)}$
 & $\mathbf{G}$
 & $\{1\}$
 & $e^{nk\hbar/z}$
 & $(\mathrm{Sym}^{\mathrm{ch}})^{(n)}$
 & $1{+}nt$
 & $n/2$
 & $0$
 & decoupled \\[3pt]
$V_k(\fg)^{(n)}$
 & $\mathbf{L}$
 & $\{1,2\}$
 & $\mathrm{pr}_{S_n}\circ R_{\fg}^{\oplus n}$
 & $(Y_\hbar(\fg))^{(n)}$
 & $1{+}n\dim(\fg)\,t$
 & $\frac{n\dim(\fg)k}{2(k{+}h^\vee)}$
 & $\ne 0$
 & entangled \\[3pt]
$\mathrm{Vir}_c^{(n)}$
 & $\mathbf{M}$
 & $\infty$
 & non-closed
 & Vir-Yangian${}^{(n)}$
 & $1{+}nt$
 & $nc/2$
 & $\ne 0$
 & entangled \\
\bottomrule
\end{tabular}
\end{center}
\end{computation}

\begin{remark}[The three constructions compared]%
\label{rem:coset-orbifold-comparison}%
\index{coset!comparison with orbifold}%
\index{orbifold!comparison with coset}%
\index{permutation orbifold!comparison}%
The three constructions (coset, $\Z_2$ orbifold,
permutation orbifold) exhibit contrasting effects on the
ordered bar complex:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item \emph{Coset} (commutant of a subalgebra):
 the bar complex is a \emph{relative cotensor}, a
 sub-coalgebra of the parent bar complex cut out by
 the diagonal action. The depth class depends on the
 structure of the commutant: the GKO coset produces
 class~$\mathbf{M}$ (Virasoro-like) from a
 class-$\mathbf{L}$ tensor product.

\item \emph{Finite-group orbifold} ($G$-invariants):
 the bar complex is the $G$-invariant sub-coalgebra.
 The depth class can \emph{jump upward}: the $\Z_2$
 orbifold of the $A_1$ lattice VOA jumps from
 class~$\mathbf{L}$ to class~$\mathbf{M}$, because
 the invariant subalgebra is generated by composites
 (the Sugawara field) that carry higher pole orders
 than the original generators.

\item \emph{Permutation orbifold} ($S_n$-invariants of
 tensor product): the bar complex is the $S_n$-invariant
 sub-coalgebra of the $n$-fold bar tensor product.
 The depth class is \emph{preserved}: no new composite
 fields arise from the symmetrisation. The Koszul dual
 commutes with the construction:
 $(V^{(n)})^! \simeq (V^!)^{(n)}$.
\end{enumerate}
The common thread: all three produce the bar complex of
the new algebra as a sub-coalgebra (invariants or
relative cotensor) of a parent bar complex, not as a
quotient. The bar functor, being a coalgebra functor,
sends subalgebras to sub-coalgebras. The depth class
can increase (when invariants force generation by
higher-pole composites) but cannot decrease (the
invariant sub-coalgebra inherits all obstructions of
the parent).
\end{remark}


\subsection{The all-genera generating function}%
\label{subsec:all-genera-generating}%
\index{genus tower!generating function|textbf}%
\index{A-hat genus@$\hat{A}$-genus!as Lagrangian expansion|textbf}

The genus-$1$ atlas is the first page of an
all-genera story. The scalar period corrections
$F_g(\cA) = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$ (Volume~I, Theorem~D\textsubscript{scal})
extend the genus-$1$ datum $F_1 = \kappa/24$ to
all genera via the Faber--Pandharipande intersection
numbers
\begin{equation}\label{eq:faber-pandharipande}
\lambda_g^{\mathrm{FP}}
\;=\;
\frac{2^{2g-1} - 1}{2^{2g-1}}
\;\cdot\;
\frac{|B_{2g}|}{(2g)!}\,,
\qquad g \ge 1,
\end{equation}
where $B_{2g}$ are the Bernoulli numbers. The
first five values:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{cccccc}
\toprule
$g$ & $1$ & $2$ & $3$ & $4$ & $5$ \\
\midrule
$\lambda_g^{\mathrm{FP}}$ &
 $\dfrac{1}{24}$ &
 $\dfrac{7}{5{,}760}$ &
 $\dfrac{31}{967{,}680}$ &
 $\dfrac{127}{154{,}828{,}800}$ &
 $\dfrac{73}{3{,}503{,}554{,}560}$ \\[6pt]
$F_g(\cH_1)$ &
 $\dfrac{1}{24}$ &
 $\dfrac{7}{5{,}760}$ &
 $\dfrac{31}{967{,}680}$ &
 $\dfrac{127}{154{,}828{,}800}$ &
 $\dfrac{73}{3{,}503{,}554{,}560}$ \\
\bottomrule
\end{tabular}
\end{center}

\begin{theorem}[The genus tower as $\hat{A}$-genus;
\ClaimStatusProvedElsewhere]%
\label{thm:ahat-lagrangian}%
\index{A-hat genus@$\hat{A}$-genus!generating function}% On the scalar lane, the total scalar free energy of the endomorphism algebra
$\End(\cL_\cA)$ expanded over $\coprod_g \Mbar_g$ is
\begin{equation}\label{eq:total-free-energy}
\boxed{
F^{\mathrm{tot}}(\cA;\, \hbar)
\;=\;
\frac{\kappa(\cA)}{\hbar^2}
\;\cdot\;
\frac{\hbar/2}{\sin(\hbar/2)}\,,
}
\end{equation}
where
\begin{equation}\label{eq:ahat-series}
\frac{x/2}{\sin(x/2)}
\;=\;
1 + \frac{x^2}{24} + \frac{7\, x^4}{5760}
 + \frac{31\, x^6}{967680} + \cdots
\;=\;
\sum_{g \ge 0}
 \lambda_g^{\mathrm{FP}}\, x^{2g}
\end{equation}
is the generating function for the unsigned
Faber--Pandharipande numbers
\textup{(}Volume~I,
Theorem~D\textsubscript{scal}\textup{)},
related to the Hirzebruch $\hat{A}$-class by
$\hat{A}(ix) = (x/2)/\sin(x/2)$, the Wick rotation
that turns the alternating-sign $\hat{A}$-series into
the all-positive genus expansion.
The scalar genus-$g$ contribution is
$F_g = \kappa \cdot \lambda_g^{\mathrm{FP}} \cdot
\hbar^{2g-2}$ ,
with $\lambda_g^{\mathrm{FP}} > 0$
for all $g \ge 1$. For arbitrary modular Koszul algebras, the
unconditional scalar statement is the genus-$1$ identity
$F_1 = \kappa/24$ (all-weight at $g = 1$; the
cross-channel correction starts at $g \ge 2$).
\end{theorem}

\begin{remark}[The platonic content]%
\label{rem:ahat-platonic}%
\index{platonic ideal!A-hat genus@$\hat{A}$-genus}%
Equation~\eqref{eq:total-free-energy} is the platonic
content of the genus tower. The Lagrangian
$\cL_\cA \hookrightarrow \Mvac$
(Theorem~\ref{thm:holographic-reconstruction-conclusion})
is a point in the derived symplectic category. Its formal
neighborhood over $\coprod_g \Mbar_g$ is the
$\hbar$-expansion of the endomorphism algebra. The
generating function of this expansion is
$(x/2)/\sin(x/2) = \hat{A}(ix)$, the Wick-rotated
$\hat{A}$-class, the same generating function that,
after rotation back, governs the index theorem for
Dirac operators. The single scalar $\kappa(\cA)$ (the
modular characteristic) plays the role of the curvature;
$\hbar$ plays the role of the genus parameter.

On the scalar lane, the coefficients of
$(\hbar/2)/\sin(\hbar/2)$ describe the scalar genus tower.
The genus-$0$ constant term produces the flat $E_1$
coalgebra; the genus-$1$ correction ($+\hbar^2/24$) produces
the curved $E_1$ coalgebra scalar term with curvature
$\kappa \cdot \omega_1$; the genus-$2$ correction
($+7\hbar^4/5760$) gives the next scalar coefficient over
$\Mbar_2$; and so on. Outside that scalar lane, the
monograph also carries genus dependence through
higher-degree shadow data and other non-scalar structures,
so the full genus content is not exhausted by a single
coefficient $F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ .
\end{remark}

\begin{remark}[The Witten genus]%
\label{rem:ahat-witten-genus}%
\index{Witten genus!relation to genus tower}%
The Witten genus characteristic series is
\[
 \varphi_W(x)
 \;=\;
 \frac{x/2}{\sinh(x/2)}
 \;\prod_{n \ge 1}
 \frac{(1 - q^n e^x)(1 - q^n e^{-x})}{(1 - q^n)^2}\,,
\]
where $q = e^{2\pi i\tau}$. At $q = 0$ the product
is~$1$ and $\varphi_W(x)|_{q=0} = (x/2)/\sinh(x/2)
= \hat{A}(x)$.
Under the Wick rotation $x \mapsto ix$ that converts
the alternating-sign $\hat{A}$-series into the
all-positive genus expansion
(Theorem~\ref{thm:ahat-lagrangian}), this becomes
$\hat{A}(ix) = (x/2)/\sin(x/2)$, so the
generating function~\eqref{eq:ahat-series} is the
$q^0$~term of $\varphi_W(ix)$.

The higher $q$-powers are supplied by
the Eisenstein-weighted genus-$1$ corrections of
Remark~\ref{rem:eisenstein-weighted-genus1}:
on an elliptic curve~$E_\tau$, each pole of
order~$2k$ in the OPE generates a correction weighted
by the Eisenstein series~$E_{2k}(\tau)$
(equation~\eqref{eq:modular-propagator-coeffs}).
The Witten genus $\Phi_W \colon
\Omega^{\mathrm{String}}_\ast \to \mathrm{MF}_\ast$
factors through topological modular forms via the
Ando--Hopkins--Rezk string orientation
$\sigma \colon M\mathrm{String} \to \mathit{tmf}$,
and $\mathit{tmf}$ is assembled from
elliptic cohomology theories
of chromatic height~${\le}\, 2$.
The scalar genus tower~\eqref{eq:total-free-energy}
is the rational shadow of this height-$2$ invariant.

The rational truncation to $q^0$ breaks $S$-invariance:
$(x/2)/\sin(x/2)$ transforms with anomalous weight
$-\kappa/2$ under $\tau \mapsto -1/\tau$
(\S\ref{obs:genus-tower-wick-anomaly}).
The higher $q$-powers (the Eisenstein-weighted
corrections of the preceding paragraph) are
precisely the elliptic completion that restores it,
promoting the genus tower from a rational shadow
into the modular Witten genus.
\end{remark}

\begin{remark}[Shadow corrections and the departure from
$\hat{A}$]%
\label{rem:shadow-corrections-ahat}%
\index{shadow corrections!departure from $\hat{A}$}%
The free energy~\eqref{eq:total-free-energy} is the
\emph{scalar} part of the Lagrangian expansion: it
captures the scalar period corrections on the proved
scalar lane. For class~$\mathbf{G}$ algebras,
this scalar term is the complete answer: the shadow obstruction tower
terminates at degree~$2$. For classes~$\mathbf{L}$ and
$\mathbf{C}$, the scalar term is accompanied by finitely
many non-scalar shadow corrections, reflecting
$r_{\max}=3$ and $r_{\max}=4$ respectively.

For algebras with excess self-intersection
(class~$\mathbf{M}$: Virasoro, $\cW_N$), the full
genus-$g$ endomorphism algebra carries an infinite tower
of higher-degree shadow corrections
(Computation~\ref{comp:virasoro-shadow-tower}). These
shadow corrections are the \emph{dispersive}
corrections to the genus tower, the same corrections
that appear in the Dubrovin--Zhang hierarchy as
higher-order terms beyond the dispersionless limit.
The $\hat{A}$-genus is the dispersionless approximation;
the shadow obstruction tower provides the higher-degree dispersive
completion.

For class~$\mathbf{M}$, the denominators of the shadow
coefficients $S_r$
(Computation~\ref{comp:virasoro-shadow-tower}) involve the
Kac determinants $\det M_r$: the self-intersection
degenerates where the algebra degenerates. These
are the poles of the Lagrangian deformation over the
moduli of curves, the locus where the endomorphism
algebra fails to be a flat deformation.
\end{remark}

\begin{remark}[From one page to the book]%
\label{rem:atlas-continuation}%
\index{genus tower!atlas continuation}%
The genus-$1$ atlas
(Theorem~\ref{thm:genus1-endomorphism-atlas}) classifies
the first-order deformation by the triple
$(\kappa, c_0, d)$. At genus~$g \ge 2$, the period
correction on the scalar lane,
$F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ (equation~\eqref{eq:faber-pandharipande}),
extends the scalar atlas on that lane. Beyond it, new
genus-$g$ information also enters through higher-degree
shadow data. The geometric genus-$g$ data
enters through the period matrix $\Omega_{ij}$ of
$\Sigma_g$, which replaces the single modular parameter
$\tau$ of $E_\tau$: the elliptic $r$-matrix of
Section~\ref{subsec:affine-genus1-endomorphism} becomes
a function on the Jacobian of $\Sigma_g$, and the
$B$-cycle monodromy $2\eta_\tau \cdot c_0$ becomes a
$g \times g$ matrix of quasi-periods.

The genus-$0$ atlas classifies the point;
the genus-$1$ atlas classifies the first-order
deformation; on the scalar lane the
$\hat{A}$-genus generates the all-genera scalar
expansion; and the shadow obstruction tower
provides the dispersive corrections. The modular
programme
(Section~\ref{subsec:modular-holography-programme})
is the problem of computing the complete dispersive
expansion at all genera for all standard families.
\end{remark}
