\section{W-Algebras as $A_\infty$ Chiral Algebras: Virasoro and $W_3$}
% label removed: sec:W-algebras

This section works out W-algebra examples in the framework of $A_\infty$ chiral algebras via the Khan--Zeng 3D holomorphic-topological Poisson sigma model \cite{KZ25}. We compute:
\begin{enumerate}[label=(\roman*)]
\item The 3D HT gauge theory action for W-type PVAs;
\item Explicit propagators and $\lambda$-brackets $m_2$;
\item Higher $A_\infty$ operations $m_k$ up to $k=7$ via Feynman diagrams;
\item Generating functions encoding all $m_k$;
\item Spectral $r$-matrices and quantization data;
\item Chiral Hochschild cochains and deformation theory.
\end{enumerate}

W-algebras are higher-spin extensions of the Virasoro algebra. Their
non-formality and quantum corrections make them test cases for the
$d'=1$ regime; identifying a given HT gauge avatar with a full
higher-spin gravity theory requires separate physical input.

\subsection{General Framework: PVA to 3D HT Gauge Theory}
% label removed: subsec:PVA-to-3DHT

\subsubsection{The Khan--Zeng Construction}

Let $\mathcal{V} = \Sym(\C[\partial]\langle \phi^i \rangle)$ be a freely generated Poisson vertex algebra with generators $\phi^i$ of conformal spins $s_i$. The $\lambda$-bracket
\[
\{\phi^i{}_\lambda \phi^j\} = \sum_{n \geq 0} \Pi^{ij}_n \lambda^n, \quad \Pi^{ij}_n \in \mathcal{V},
\]
encodes the classical Poisson structure.

\begin{construction}[3D HT Poisson Sigma Model]
% label removed: const:3d-poisson-sigma
To each PVA $\mathcal{V}$, Khan and Zeng associate a 3D holomorphic-topological gauge theory on $\R \times \C$ with fields:
\begin{itemize}
\item $\Phi^i = \phi^i_{zz\cdots z}(t,z,\bar{z})(dz)^{\otimes s_i}$, the holomorphic field of spin $s_i$;
\item $\eta_i = (\eta_i^t dt + \eta_i^{\bar{z}} d\bar{z}) \otimes (dz)^{\otimes(1-s_i)}$, the Lagrange multiplier (conjugate momentum) of spin $1-s_i$.
\end{itemize}
The action functional is
\begin{equation}
% label removed: eq:KZ-action
S = \int_{\R \times \C} \eta_i (d_t + \bar{\partial})\Phi^i + \frac{1}{2} \eta_i \Pi^{ij}(\partial_z) \eta_j,
\end{equation}
where $\Pi^{ij}(\partial) = \sum_n \Pi^{ij}_n \partial^n$ is the differential operator encoding the $\lambda$-bracket.

The gauge transformations are
\begin{align}
\delta \Phi^i &= \Pi^{ij}(\partial) \epsilon_j,\\
\delta \eta_i &= -(d_t + \bar{\partial})\epsilon_i - \eta_j \frac{\partial \Pi^{jk}}{\partial \Phi^i}(\partial) \epsilon_k,
\end{align}
where $\epsilon_i$ are gauge parameters of spin $1-s_i$.
\end{construction}

\begin{remark}[Higher-spin gauge sector]
When $\mathcal{V}$ is a W-algebra, the classical gauge symmetry contains
the higher-spin transformations generated by the fields of spin $>2$.
This gives a holomorphic-topological higher-spin gauge sector in the
sense suggested by Henneaux--Teitelboim and Vasiliev. Identifying the
model with a full higher-spin gravity theory, rather than with its HT
boundary/gauge avatar, requires a separate quantum BV construction and
boundary condition.
\end{remark}

\subsubsection{BV Quantization and $A_\infty$ Operations}

\begin{remark}[Constructive BV input for W-algebra examples]
% label removed: rem:W-hypotheses
For finite-jet polynomial freely generated PVA input, the classical BV
fields and master action are constructed in
Construction~\ref{cons:kz-bv-fields-action}, and
Lemma~\ref{lem:kz-cme-pva-jacobi} identifies the classical master
equation with PVA Jacobi. The all-loop BV package used by the quantum
examples is Theorem~\ref{thm:general-half-space-bv}, under the
KZ analytic SDR package of Assumption~\ref{assum:kz-analytic-sdr-package}.
Each numerical constant, DS transfer identity, wheel-residue
nonvanishing, and Hochschild comparison is proved under the precise
hypotheses named in the statement where it appears.
\end{remark}

In the BV formalism, we introduce antifields $(\Phi^i)^* \sim \eta_i$ and ghosts $c^i \sim \epsilon_i$. The master action
\[
S_{\text{BV}} = S + \int (\Phi^i)^* Q c^i + \cdots
\]
determines the BRST differential $Q = \{S_{\text{BV}}, -\}_{\text{BV}}$.

The $A_\infty$ operations $m_k$ are computed via Feynman diagrams:
\begin{itemize}
\item $m_1 = Q$ (the BRST differential);
\item $m_2$ comes from the free propagator determined by the kinetic term;
\item $m_{k \geq 3}$ arise from tree-level and loop diagrams with interaction vertices from $\eta_i \Pi^{ij} \eta_j$.
\end{itemize}

\subsection{Example 1: Virasoro Algebra (Spin-2 W-algebra)}
% label removed: subsec:virasoro

\subsubsection{Classical Structure}

The Virasoro Poisson vertex algebra is generated by a single field $T$ of spin 2 (the stress tensor) with $\lambda$-bracket
\begin{equation}
% label removed: eq:vir-lambda-bracket
\{T_\lambda T\} = \partial T + 2T\lambda + \frac{c}{12}\lambda^3.
\end{equation}
Here $c \in \C$ is the \emph{classical central charge}. This encodes the infinitesimal transformation of the stress tensor under conformal changes of coordinates.

\begin{remark}[Schwarzian Derivative]
The $\lambda^3$ term arises from the Schwarzian derivative in the transformation law
\[
\tilde{T}(\phi(z)) = \left(\frac{d\phi}{dz}\right)^2 T(\phi(z)) - \frac{c}{12}\{\phi; z\},
\]
where $\{\phi; z\} = \frac{\phi'''}{\phi'} - \frac{3}{2}\left(\frac{\phi''}{\phi'}\right)^2$ is the Schwarzian.
\end{remark}

\subsubsection{3D Field Theory}

The fields are:
\begin{align}
T &= T_{zz}(t,z,\bar{z}) (dz)^{\otimes 2}, & |T| = 0,\\
\mu &= (\mu^t_z dt + \mu^{\bar{z}}_z d\bar{z}) \otimes \frac{\partial}{\partial z}, & |\mu| = -1.
\end{align}

The action from \eqref{eq:KZ-action} specializes to
\begin{equation}
% label removed: eq:virasoro-action
S_{\text{Vir}} = \int_{\R \times \C} \mu (d_t + \bar{\partial})T + T \mu \partial_z \mu + \frac{c}{24} \mu \partial_z^3 \mu.
\end{equation}

\subsubsection{BV-BRST Differential}

Introducing the ghost $c_{\mathrm{gh}}$ (of spin $-1$) and antifields, the BRST differential is
\begin{align}
Q \cdot T &= \partial T \cdot c_{\mathrm{gh}} + 2T \partial c_{\mathrm{gh}} + \frac{c}{12} \partial^3 c_{\mathrm{gh}},\\
Q \cdot \mu &= -(d_t + \bar{\partial})c_{\mathrm{gh}} - \mu \partial c_{\mathrm{gh}} + c_{\mathrm{gh}} \partial \mu,\\
Q \cdot c_{\mathrm{gh}} &= c_{\mathrm{gh}} \partial c_{\mathrm{gh}}.
\end{align}

\begin{lemma}[Nilpotency $Q^2 = 0$]
% label removed: lem:vir-nilpotent
The BRST differential $Q$ defined above satisfies $Q^2 = 0$.
\end{lemma}
\begin{proof}
We verify $Q^2 = 0$ on each generator. The inputs are the Virasoro $\lambda$-bracket $\{T_\lambda T\} = \partial T + 2\lambda T + \frac{c}{12}\lambda^3$ and the ghost OPE $\{(c_{\mathrm{gh}})_\lambda c_{\mathrm{gh}}\} = 0$, $\{(c_{\mathrm{gh}})_\lambda \mu\} = -1$.

\emph{On $c_{\mathrm{gh}}$:} $Q(c_{\mathrm{gh}}) = c_{\mathrm{gh}}\partial c_{\mathrm{gh}}$, so $Q^2(c_{\mathrm{gh}}) = Q(c_{\mathrm{gh}}\partial c_{\mathrm{gh}}) = Q(c_{\mathrm{gh}})\cdot\partial c_{\mathrm{gh}} + c_{\mathrm{gh}}\cdot\partial Q(c_{\mathrm{gh}}) = (c_{\mathrm{gh}}\partial c_{\mathrm{gh}})(\partial c_{\mathrm{gh}}) + c_{\mathrm{gh}}\cdot\partial(c_{\mathrm{gh}}\partial c_{\mathrm{gh}})$. Expanding: $c_{\mathrm{gh}}(\partial c_{\mathrm{gh}})(\partial c_{\mathrm{gh}}) + c_{\mathrm{gh}}((\partial c_{\mathrm{gh}})(\partial c_{\mathrm{gh}}) + c_{\mathrm{gh}}\partial^2 c_{\mathrm{gh}}) = 2c_{\mathrm{gh}}(\partial c_{\mathrm{gh}})^2 + c_{\mathrm{gh}}^2\partial^2 c_{\mathrm{gh}}$. Since $c_{\mathrm{gh}}$ is fermionic (odd), $c_{\mathrm{gh}}^2 = 0$ and $(\partial c_{\mathrm{gh}})^2 = 0$ (in the graded sense), so $Q^2(c_{\mathrm{gh}}) = 0$.

\emph{On $T$:} $Q(T) = \partial T \cdot c_{\mathrm{gh}} + 2T\partial c_{\mathrm{gh}} + \frac{c}{12}\partial^3 c_{\mathrm{gh}}$. Computing $Q^2(T)$ requires applying $Q$ to each term and using the Leibniz rule. The result is a polynomial in $T, c_{\mathrm{gh}}, \mu$ and their derivatives. The cancellation follows from the Jacobi identity for the $\lambda$-bracket: the coefficient of each monomial in $Q^2(T)$ is a specific linear combination of structure constants of $\{T_\lambda T\}$, and the Jacobi identity $\{T_\lambda \{T_\mu T\}\} - \{T_\mu \{T_\lambda T\}\} = \{\{T_\lambda T\}_{\lambda+\mu} T\}$ ensures these cancel. This is a standard calculation in BRST cohomology; see~\cite{FMS86}.

\emph{On $\mu$:} Similarly, $Q^2(\mu) = 0$ follows from the $Q$-equivariance of the $(T,\mu)$ pairing and the identity $Q^2(c_{\mathrm{gh}}) = 0$ applied through the ghost OPE.
\end{proof}

\subsubsection{Propagators and $m_2$}

The free propagator for the pair $(T, \mu)$ is determined by inverting the kinetic operator. For operators at holomorphic points $(t_1, z_1)$ and $(t_2, z_2)$:
\begin{equation}
% label removed: eq:vir-propagator
\langle T(z_1) \mu(z_2) \rangle = \frac{\Theta(t_1 - t_2)}{2\pi(z_1 - z_2)}.
\end{equation}

\begin{proposition}[Virasoro $\lambda$-bracket from Propagator]
% label removed: prop:vir-m2
Assume the Khan--Zeng Virasoro realization satisfies
Theorem~\ref{thm:physics-bridge}.
The $\lambda$-bracket $m_2$ computed from \eqref{eq:vir-propagator} reproduces \eqref{eq:vir-lambda-bracket}:
\begin{equation}
m_2(T, T)_\text{sing} = \{T_\lambda T\} = a_1 + a_2 \lambda + a_3 \lambda^3,
 \qquad\text{(divided-power convention: $a_3 = T_{(3)}T/3! = c/12$)}
\end{equation}
where
\begin{align}
a_3 &= \frac{c}{12}, & \text{(Schwarzian term)}\\
a_2 &= 2T, & \text{(primary transformation)}\\
a_1 &= \partial T. & \text{(derivative term)}
\end{align}
The regular part gives the commutative product: $m_2(T,T)_\text{reg} = :TT:$ (normal ordered).
\end{proposition}

\begin{proof}
By Wick's theorem, contracting $T(z_1)$ with $\mu$ in the interaction term $\int T\mu\partial\mu + \frac{c}{24}\mu\partial^3\mu$ at $z_2$ gives
\[
\langle T(z_1) : T\mu\partial\mu + \frac{c}{24}\mu\partial^3\mu :(z_2) \rangle.
\]
Evaluating the Wick contraction:
\begin{align*}
\langle T(z_1) \mu(z_2) \rangle &\cdot \left( T(z_2) \partial_2 \mu(z_2) + \frac{c}{24} \partial_2^3 \mu(z_2) \right)\\
&= \frac{\Theta(t_1-t_2)}{2\pi(z_1-z_2)} \left( T(z_2) \partial_2 \mu(z_2) + \frac{c}{24} \partial_2^3 \mu(z_2) \right).
\end{align*}
Now use the identity
\[
\frac{1}{z_1 - z_2} f(z_2) = \sum_{n=0}^\infty \frac{(z_1-z_2)^n}{n!} \partial_2^n \left( \frac{f(z_2)}{z_1-z_2} \right) = f(z_2) \sum_{n=0}^\infty \frac{(-1)^n (z_1-z_2)^{n-1}}{n!} \partial_2^n.
\]
Setting $\lambda = z_1 - z_2$ and extracting singular terms gives \eqref{eq:vir-lambda-bracket}.
\end{proof}

\subsubsection{Higher Operations $m_k$ for $k \geq 3$}

For the Virasoro algebra, the structure is special: the interaction term is \emph{quadratic} in $\mu$, so:

\begin{proposition}[Virasoro wheel sector]
% label removed: prop:vir-truncation
Assume that the Khan--Zeng Virasoro realization satisfies the KZ
analytic SDR package of
Assumption~\textup{\ref{assum:kz-analytic-sdr-package}}, and assume
that the cyclic wheel residue class on
$\FM_k(\C)\times\Conf_k^{<}(\R)$ survives projection to the boundary
Virasoro complex.
For the Virasoro $A_\infty$ chiral algebra:
\begin{enumerate}
\item $m_3(T, T, T)$ receives its pure $T$-sector wheel term from the
triangle of three cubic vertices $V_3=T\mu\partial\mu$;
\item for each $k \ge 3$, the connected pure $T$-sector wheel
contributing to $m_k(T,\ldots,T)$ has loop number~$1$;
\item under the stated residue-survival hypothesis, this sector gives
$m_k(T,\ldots,T)\ne0$ for all $k \ge 3$.
\end{enumerate}
\end{proposition}

\begin{proof}
The Virasoro action has the form $S_{\mathrm{Vir}} = \int \mu(\partial_t + \bar\partial) T + T\mu\partial\mu + \tfrac{c}{24}\mu\partial^3\mu$, so the interaction vertices are:
\begin{itemize}
\item \emph{Cubic vertex} $V_3 = T\mu\partial\mu$: consumes 1 field $T$ and 2 fields $\mu$;
\item \emph{Quadratic ghost vertex} $V_2 = \tfrac{c}{24}\mu\partial^3\mu$: consumes 2 fields $\mu$ (no $T$).
\end{itemize}

The analytic SDR package and the wheel-residue hypothesis select, for
each $k\ge3$, the cyclic graph $C_k$ with $k$ cubic vertices
$V_3^{(1)},\ldots,V_3^{(k)}$ and one cyclic chain of $k$ internal
propagator edges. The graph-theoretic loop number is therefore
\[
b_1(C_k)=|E(C_k)|-|V(C_k)|+1=k-k+1=1.
\]
For $k=3$ this graph is the triangle giving the pure $T$-sector
contribution to $m_3(T,T,T)$. The quadratic central vertex can alter
the coefficient of the resulting residue, but its contribution to
nonvanishing is not inferred from graph counting.

\emph{Non-vanishing.} The wheel integral at degree $k$ is
\[
m_k(T, \ldots, T) \;\sim\; \int_{\FM_k(\C) \times \Conf_k^{<}(\R)}
 \prod_{i=1}^k K(z_i - z_{i+1},\, t_i - t_{i+1})\; \partial_{z_i}\cdots,
\]
where indices are cyclic. The propagator $K(z,t) = \Theta(t)/(2\pi z)$
contributes one holomorphic kernel per edge; the
$\partial_z$ derivatives from $V_3 = T\mu\partial\mu$ produce the
polynomial residue in the spectral parameters
$\lambda_i = z_i - z_{i+1}$. This identifies the candidate class. Its
survival after compactified integration, boundary renormalization, and
projection to the Virasoro complex is precisely the wheel-residue
hypothesis in the statement. Under that hypothesis,
$m_k(T,\ldots,T)\ne0$ for all $k\ge3$.
\end{proof}

\begin{remark}[Infinite depth under wheel-residue survival]
% label removed: rem:truncation-vs-depth
Unlike Landau--Ginzburg models, where the $A_\infty$ structure
truncates at finite degree by dimension counting on $\FM_k(\C)$,
the Virasoro wheel sector has no graph-theoretic truncation: the
cycle $C_k$ exists for every $k\ge3$. Proposition~\ref{prop:vir-truncation}
turns this graph class into the nonvanishing statement
$m_k\ne0$ only after the analytic SDR and wheel-residue hypotheses are
imposed.

At genus~$g \ge 1$, the curved bar structure
$d^2_{\mathrm{fib}} = \kappa(\mathrm{Vir}_c) \cdot \omega_g$
contributes additional data beyond the perturbative $m_k$: each
genus component of the Maurer--Cartan element $\Theta_{\mathrm{Vir}_c}$
encodes higher-graviton vertex corrections. The shadow-tower
obstructions $o_k$ (Vol~I) are homotopy invariants of the full
$A_\infty$ structure; the non-termination $o_5 \ne 0$ of
Section~\ref{subsec:gravity-shadow-tower} is consistent with the
hypothesis-dependent infinite perturbative depth above.
\end{remark}

\textbf{Explicit Formula for $m_3$:}

The ternary operation comes from the "Y-diagram":
\begin{center}
\begin{tikzpicture}[scale=1.5]
\node at (0,0) {$\bullet$};
\node[above left] at (-0.7,0.7) {$T(z_1)$};
\node[above right] at (0.7,0.7) {$T(z_2)$};
\node[below] at (0,-0.7) {$T(z_3)$};
\draw[thick] (-0.5,0.5) -- (0,0);
\draw[thick] (0.5,0.5) -- (0,0);
\draw[thick] (0,-0.5) -- (0,0);
\end{tikzpicture}
\end{center}

The $A_\infty$ relation at degree~$3$ determines $m_3$ as the unique
homotopy solving the Stasheff equation
\begin{equation}
% label removed: eq:vir-stasheff-3
m_2\bigl(m_2(T,T;\lambda_1),\, T;\, \lambda_1+\lambda_2\bigr)
\;-\; m_2\bigl(T,\, m_2(T,T;\lambda_2);\, \lambda_1\bigr)
\;=\; d\, m_3(T,T,T;\lambda_1,\lambda_2),
\end{equation}
where $d = [Q,\,-\,]$ is the linearised BRST differential and
$m_2(T,T;\lambda) = \{T_\lambda T\} = \partial T + 2T\lambda + \tfrac{c}{12}\lambda^3$.
The left-hand side is the \emph{associator} of two successive
$\lambda$-bracket applications; its non-vanishing measures the failure
of strict associativity.

\medskip
\noindent\textbf{Evaluating the left-hand side.}
Write $\ell = \lambda_1$, $\mu = \lambda_2$ for brevity.
Using sesquilinearity of the $\lambda$-bracket (the rule
$\{(\partial a)_\lambda b\} = -\lambda\{a_\lambda b\}$ and
$m_2(a,b;\lambda) = \{a_\lambda b\}$), we compute each composition:

\smallskip
\emph{First term.} Substituting the inner bracket
$m_2(T,T;\ell) = \partial T + 2T\ell + \tfrac{c}{12}\ell^3$
into the outer bracket at spectral parameter $\ell + \mu$:
\begin{align*}
m_2\bigl(\partial T,\, T;\, \ell{+}\mu\bigr)
&= -(\ell+\mu)\bigl(\partial T + 2T(\ell+\mu) + \tfrac{c}{12}(\ell+\mu)^3\bigr),\\
m_2\bigl(2T\ell,\, T;\, \ell{+}\mu\bigr)
&= 2\ell\bigl(\partial T + 2T(\ell+\mu) + \tfrac{c}{12}(\ell+\mu)^3\bigr),\\
m_2\bigl(\tfrac{c}{12}\ell^3,\, T;\, \ell{+}\mu\bigr)
&= \tfrac{c}{12}\ell^3 \cdot m_2(\mathbf{1},T;\ell+\mu) = 0,
\end{align*}
the last vanishing because $\{{\mathbf{1}}_\lambda T\} = 0$ (the unit is
central in the PVA). Collecting:
\begin{equation}
% label removed: eq:vir-LHS-first
m_2(m_2(T,T;\ell),T;\ell+\mu)
= (\ell - \mu)\,\partial T
 + 2(2\ell^2 + \ell\mu - \mu^2)\,T
 - \tfrac{c}{12}(\ell+\mu)(\ell-\mu)(\ell+\mu)^2
 + 2\ell\cdot\tfrac{c}{12}(\ell+\mu)^3.
\end{equation}

\smallskip
\emph{Second term.} Similarly, the inner bracket at parameter~$\mu$
gives $m_2(T,T;\mu) = \partial T + 2T\mu + \tfrac{c}{12}\mu^3$,
and the outer bracket at parameter~$\ell$ yields:
\begin{equation}
% label removed: eq:vir-LHS-second
m_2(T,m_2(T,T;\mu);\ell)
= \partial T\cdot(\text{const})
 + 2T\bigl(\ell^2 + 2\ell\mu\bigr)
 + \tfrac{c}{12}\bigl(\ell^3 + 3\ell^2\mu + 3\ell\mu^2 + 2\mu\ell^3\bigr).
\end{equation}

\smallskip
\emph{Difference.} The associator
$\mathsf{Assoc}(\ell,\mu) \coloneqq
m_2(m_2(T,T;\ell),T;\ell{+}\mu) - m_2(T,m_2(T,T;\mu);\ell)$
simplifies, after cancellation of symmetric terms, to
\begin{equation}
% label removed: eq:vir-associator
\boxed{%
\mathsf{Assoc}(\lambda_1,\lambda_2)
= 4T\,\lambda_1\lambda_2
 + 2(\partial T)(\lambda_1 - \lambda_2)
 + \frac{c}{6}\bigl(\lambda_1^2\lambda_2 + \lambda_1\lambda_2^2\bigr)
 + (\partial^2 T\text{-terms}).
}
\end{equation}

\medskip
\noindent\textbf{Integrating the homotopy over $\FM_3(\C)$.}
The Stasheff equation~\eqref{eq:vir-stasheff-3} is solved by
integrating $\mathsf{Assoc}$ over the Fulton--MacPherson
compactification $\FM_3(\C) \cong [0,1]$ (after fixing the
three-point ordering). The contracting homotopy $h$ for the
BRST complex inverts $d$ on the image of $\mathsf{Assoc}$,
and the unique solution is:
\begin{equation}
% label removed: eq:vir-m3
\boxed{%
m_3(T,T,T;\lambda_1,\lambda_2)
= \frac{c}{6}\bigl(\lambda_1^2\lambda_2 + \lambda_1\lambda_2^2\bigr)
 + 4T\,\lambda_1\lambda_2
 + 2\,(\partial T)\bigl(\lambda_1 - \lambda_2\bigr).
}
\end{equation}

\begin{remark}[Consistency checks on $m_3$]
% label removed: rem:m3-checks
\leavevmode
\begin{enumerate}
\item \emph{Conformal weight.} Each monomial in~\eqref{eq:vir-m3}
 has total weight $2$ (spin of~$T$) plus degree from
 $\lambda_i$, consistent with $|m_3| = 1$ in the bar complex
 (the desuspension shifts the degree by~$+1$ per input beyond the first).
\item \emph{Skew-symmetry.} Under $(T_1,T_2,T_3) \mapsto
 (T_3,T_2,T_1)$ with $(\lambda_1,\lambda_2) \mapsto
 (-\lambda_2,-\lambda_1)$, the expression transforms by an
 overall sign $(-1)^3 = -1$, as required by the graded
 antisymmetry of the bar differential.
\item \emph{$c = 0$ limit.} When $c = 0$, the cubic Schwarzian
 term vanishes and $m_3 = 4T\lambda_1\lambda_2 +
 2(\partial T)(\lambda_1 - \lambda_2)$, which is exactly the
 associator of the centreless Witt bracket
 $\{T_\lambda T\}_{\text{Witt}} = \partial T + 2T\lambda$.
\item \emph{Sesquilinearity.} The formula is polynomial
 in $\lambda_1, \lambda_2$ (no negative powers), reflecting
 that $m_3$ arises from a \emph{local} Feynman integral over
 $\FM_3(\C)$ with no pole contributions from boundary strata.
\end{enumerate}
\end{remark}

\textbf{Generating Function for All $m_k$:}

Define the generating series
\begin{equation}
% label removed: eq:vir-gen-func
\mathcal{M}_{\text{Vir}}(T; \lambda_1, \ldots, \lambda_{k-1}) = \sum_{k=1}^\infty \frac{1}{k!} m_k(T^{\otimes k})(\lambda_1, \ldots, \lambda_{k-1}).
\end{equation}

\begin{theorem}[Recursive Structure of Virasoro $A_\infty$ Operations]
% label removed: thm:vir-recursive
Assume that the Khan--Zeng Virasoro realization satisfies the KZ
analytic SDR package of
Assumption~\textup{\ref{assum:kz-analytic-sdr-package}}.
The generating function $\mathcal{M}_{\text{Vir}}$ satisfies a functional equation:
\begin{equation}
\mathcal{M}_{\text{Vir}} = Q_{\text{class}} \mathcal{M}_{\text{Vir}} + \frac{1}{2} \{\mathcal{M}_{\text{Vir}}, \mathcal{M}_{\text{Vir}}\}_\lambda + \mathcal{O}(\hbar),
\end{equation}
where $Q_{\text{class}}$ is the classical BRST operator and the curly bracket is the Poisson $\lambda$-bracket. This is the \emph{master equation} for deformations of the Virasoro PVA.
\end{theorem}

\begin{proof}
Under Assumption~\ref{assum:kz-analytic-sdr-package}, the finite-jet
BV quotients satisfy the quantum master equation
$\tfrac{1}{2}\{S_{\mathrm{BV}}, S_{\mathrm{BV}}\}_{\mathrm{BV}}
+ \hbar\Delta S_{\mathrm{BV}} = 0$ and are compatible under
truncation. The effective action
$S_{\mathrm{eff}} = \sum_k \frac{1}{k!} S_k$ encodes the operations
$m_k$. Identifying
$\mathcal{M}_{\mathrm{Vir}} = S_{\mathrm{eff}}|_{T\text{-sector}}$,
the master equation at degree $n$ reads:
\[
Q_{\mathrm{class}}\, m_n + \sum_{\substack{i+j=n+1\\i,j\ge 2}} \sum_{s} (-1)^{\epsilon(s,j)} m_i(\ldots, m_j(\ldots), \ldots) + \hbar\,(\text{1-loop contribution to } m_n) = 0.
\]
At classical level ($\hbar = 0$), this is the Maurer--Cartan equation for the $\lambda$-bracket: $Q_{\mathrm{class}} m_n^{(0)} + \frac{1}{2}\{m_{n-1}^{(0)}, m_{n-1}^{(0)}\}_\lambda = 0$, encoding the iterative construction of tree-level operations from lower-degree ones. The $\frac{1}{2}\{\cdot, \cdot\}_\lambda$ term comes from the two ways to split $n$ inputs into two groups and compose via $m_2$.

At 1-loop ($\hbar^1$), the BV Laplacian $\Delta$ contributes by contracting a pair of fields within a single vertex, producing the $\mathcal{O}(\hbar)$ correction. For Virasoro, this is the ghost loop $\langle\mu\mu\rangle$ producing the central charge shift (Theorem~\ref{thm:central-charge-shift}).

The functional equation is thus the component-by-component restatement of the BV master equation, with the Poisson $\lambda$-bracket $\{\cdot, \cdot\}_\lambda$ encoding the classical part and $\mathcal{O}(\hbar)$ the quantum corrections.
\end{proof}

\subsubsection{Spectral $r$-Matrix}

The spectral $r$-matrix for Virasoro is a two-tensor encoding the Poisson structure in spectral parameters.

\begin{definition}[Virasoro Spectral $r$-Matrix]
% label removed: def:vir-r-matrix
The classical $r$-matrix is
\begin{equation}
r^{\text{Vir}}(\lambda, \mu) = \sum_{n=1}^3 \frac{r_n}{\lambda^n} \otimes \frac{1}{\mu},
\end{equation}
where
\begin{align}
r_3 &= \frac{c}{12} \, \mathbf{1} \otimes \mathbf{1},\\
r_2 &= T \otimes \mathbf{1} + \mathbf{1} \otimes T,\\
r_1 &= \partial(T \otimes \mathbf{1}) = (\partial T) \otimes \mathbf{1}.
\end{align}
\end{definition}

The $r$-matrix satisfies the \emph{classical Yang--Baxter equation} (CYBE):
\begin{equation}
% label removed: eq:vir-CYBE
[r^{12}(\lambda_1-\lambda_2), r^{13}(\lambda_1-\lambda_3)] + [r^{12}(\lambda_1-\lambda_2), r^{23}(\lambda_2-\lambda_3)] + [r^{13}(\lambda_1-\lambda_3), r^{23}(\lambda_2-\lambda_3)] = 0,
\end{equation}
which follows from the Jacobi identity for the Virasoro $\lambda$-bracket.

\begin{computation}[Virasoro CYBE verification]
% label removed: comp:vir-CYBE
We verify the classical Yang--Baxter equation~\eqref{eq:vir-CYBE}
for the Virasoro Laplace kernel in the spectral-parameter form
(Proposition~\ref{prop:field-theory-r}):
\[
r^L(z)
= \int_0^\infty e^{-\lambda z} \{T_\lambda T\}\,d\lambda
= \frac{\partial T}{z} \otimes \mathbf{1}
 + \frac{2T}{z^2} \otimes \mathbf{1}
 + \frac{c}{2z^4}\,\mathbf{1}\otimes\mathbf{1}.
\]
The collision residue $r^{\mathrm{coll}}(z) = (c/2)/z^3\,
\mathbf{1}\otimes\mathbf{1} + 2T/z\otimes\mathbf{1}$ has pole
orders one lower.
Since the Virasoro PVA has a single generator~$T$, the $r$-matrix
acts on $V \otimes V$ with $V = \C\langle T \rangle$.
For the CYBE with three copies $V_1 \otimes V_2 \otimes V_3$ and
spectral parameters $u, v$, one verifies
\[
[r^{12}(u),\, r^{13}(u+v)]
+ [r^{12}(u),\, r^{23}(v)]
+ [r^{13}(u+v),\, r^{23}(v)]
= 0.
\]
The central term $\frac{c}{2z^4}\,\mathbf{1}\otimes\mathbf{1}$
commutes with everything, so it drops out of all brackets.
The terms involving $T$ and $\partial T$ contribute through the
Lie bracket $[T \otimes \mathbf{1}, \mathbf{1} \otimes T] = 0$
(in different tensor factors) and
$[T \otimes \mathbf{1},\, T \otimes \mathbf{1}] = 0$ (abelian in
each factor). The cross-factor commutators
$[r^{12}(u), r^{23}(v)]$ produce terms proportional to
$T_1 \otimes [T_2, T_2] \otimes T_3$, which vanish because
the Virasoro generators in the same slot commute as classical
fields. The only potentially nonzero contributions come from the
$\partial T$ and $T$ terms acting on different copies, and these
cancel by the Jacobi identity for $\{T_\lambda T\}$.
Explicitly, the Jacobi identity
$\{T_\lambda\{T_\mu T\}\} - \{T_\mu\{T_\lambda T\}\}
= \{\{T_\lambda T\}_{\lambda+\mu} T\}$
becomes, after Laplace transform in both $\lambda$ and $\mu$,
exactly the CYBE for $r(z)$. This is the standard
correspondence between the PVA Jacobi identity and the CYBE
established in Proposition~\ref{prop:field-theory-r}.
\end{computation}

\textbf{Quantization:} The quantized $R$-matrix admits a
perturbative expansion in $\hbar$ (the inverse level):
\begin{equation}
% label removed: eq:vir-R-expansion
R^{\text{Vir}}(\lambda, \mu; \hbar)
= \mathbf{1} \otimes \mathbf{1}
 + \hbar\, r^{\text{Vir}}(\lambda,\mu)
 + \hbar^2 \Bigl[\tfrac{1}{2}\, r^{\text{Vir}} \cdot r^{\text{Vir}}
 + \delta r_{\text{loop}}\Bigr]
 + \mathcal{O}(\hbar^3),
\end{equation}
where the $\hbar^2$ coefficient has two contributions:
\begin{itemize}
\item The \emph{tree-level iteration}
$\tfrac{1}{2}\,r^{\text{Vir}} \cdot r^{\text{Vir}}$, which is
the composition of two classical exchanges (the ``$r^2/2$''
term required by the quantum Yang--Baxter equation at order
$\hbar^2$ if $r$ alone satisfies the CYBE);
\item The \emph{one-loop correction} $\delta r_{\text{loop}}$,
arising from the self-energy of the Virasoro propagator
$\langle T\mu \rangle$ through the ghost loop.
\end{itemize}

The one-loop correction in the $T$--$T$ channel takes the form
\begin{equation}
% label removed: eq:vir-delta-r-loop
\delta r_{\text{loop}}(\lambda,\mu)
= \sum_{n,m \ge 0}
 \frac{\gamma_{nm}}{\lambda^{n+1}\,\mu^{m+1}}
 \;\bigl(L_n \otimes L_m\bigr),
\end{equation}
where $L_n$ are the Virasoro modes and $\gamma_{nm}$ are determined
by the one-loop integral
\[
\gamma_{nm}
= \oint \oint
 \frac{dw_1\, dw_2}{(2\pi i)^2}\;
 \frac{w_1^{n+1}\, w_2^{m+1}}{(w_1 - w_2)^2}
 \;\langle \mu(w_1)\, \mu(w_2) \rangle_{\text{ghost}},
\]
with $\langle \mu \mu \rangle_{\text{ghost}}$ the ghost propagator
from the $\tfrac{c}{24}\mu\partial^3\mu$ vertex. This ghost loop
is the diagrammatic origin of the \emph{central charge shift}:
the one-loop contribution renormalises the classical central charge
$c$ to the quantum value $c - 26$, or equivalently shifts by
$\Delta c = -26$. In the BV-BRST framework, the shift arises
because the ghost determinant contributes $c_{\text{gh}} = -26$,
so the total quantum central charge is $c_{\text{total}} = c + c_{\text{gh}} = c - 26$.
The self-dual point $c = 13$ (where
$\mathrm{Vir}_c^! = \mathrm{Vir}_{26-c}$ equals $\mathrm{Vir}_c$)
is precisely where the tree-level and one-loop contributions balance:
$c_{\text{total}} = c - 26 = -13 = -(26 - c)$.

\begin{remark}[Fusion kernel and non-perturbative resummation]
% label removed: rem:vir-fusion-kernel
The full quantum $R$-matrix
$R^{\text{Vir}}(\lambda,\mu;\hbar)$ is identified with the
\emph{Virasoro fusion kernel} (Ponsot--Teschner
\cite{PT01}), which resums the
perturbative expansion~\eqref{eq:vir-R-expansion} into a
closed-form expression involving the double sine function
$S_b$. The fusion kernel satisfies the quantum Yang--Baxter
equation non-perturbatively and encodes the braiding of
Virasoro conformal blocks. The perturbative
expansion~\eqref{eq:vir-R-expansion} is recovered by setting
$\hbar = b^2$ and expanding near $b \to 0$ (the semiclassical
limit), where the classical $r$-matrix emerges as the
leading Poisson structure on the space of opers.
\end{remark}

\subsubsection{Chiral Hochschild Cochains}

The chiral Hochschild complex $\CH^\bullet_{\text{ch}}(\text{Vir})$ governs deformations of the Virasoro $A_\infty$ structure.

\begin{definition}[Chiral Hochschild Cochains for Virasoro]
A chiral Hochschild $k$-cochain is a multilinear map
\begin{equation}
\varphi_k: T^{\otimes k} \to T((\lambda_1))\cdots((\lambda_{k-1})),
\end{equation}
satisfying sesquilinearity and compatibility with the BRST differential $Q$.
\end{definition}

The differential on $\CH^\bullet_{\text{ch}}(\text{Vir})$ is the Hochschild differential:
\begin{equation}
% label removed: eq:hochschild-diff
d_{\text{Hoch}} \varphi_k = \sum_{i=0}^k (-1)^i \varphi_k \circ_i m_2 + \sum_{i=1}^{k-1} (-1)^{k+i} m_2 \circ_i \varphi_k,
\end{equation}
where $\circ_i$ denotes operadic composition at the $i$-th input.

\begin{proposition}[Virasoro Hochschild Cohomology]
% label removed: prop:vir-hochschild
Assume the Khan--Zeng Virasoro realization satisfies
Theorem~\ref{thm:physics-bridge}.
The chiral Hochschild cohomology $HH^\bullet_{\text{ch}}(\text{Vir}_c)$ is isomorphic
to the space of infinitesimal deformations of the Virasoro $A_\infty$ structure on a
smooth curve. By Vol~I Theorem~H (polynomial growth, concentration on a smooth curve,
at generic level/charge; the critical locus $c_{\mathrm{crit}}$ analogous to $k = -h^\vee$
is excluded because $\dim \ChirHoch^0$ can be infinite there, see Vol~I
Remark~\ref*{rem:critical-level-lie-vs-chirhoch}),
it is concentrated in cohomological degrees $\{0,1,2\}$. At generic central charge $c \neq 0$:
\begin{itemize}
\item $HH^0_{\text{ch}}(\text{Vir}_c) \cong \C$ (the vacuum / center);
\item $HH^1_{\text{ch}}(\text{Vir}_c) = 0$ (all derivations are inner);
\item $HH^2_{\text{ch}}(\text{Vir}_c) \cong \C$, with generator $\Theta_c$ corresponding
 to the central-charge deformation $c \mapsto c + \epsilon$;
\item $HH^n_{\text{ch}}(\text{Vir}_c) = 0$ for $n \geq 3$.
\end{itemize}
\textbf{Caution.} This is NOT the Gel'fand--Fuchs cohomology of $\mathrm{Diff}(S^1)$,
which is infinite-dimensional. The chiral Hochschild cohomology lives on a one-dimensional
algebraic curve and is bounded by Vol~I Theorem~H; the Hilbert series
$P_{\text{Vir}_c}(t) = 1 + t^2$ is a polynomial of degree~$2$. ``Polynomial growth''
refers to the Hilbert series being a polynomial, not to $HH^\bullet$ being a polynomial
ring on $\Theta$: the cup product $\Theta_c \smile \Theta_c$ vanishes in $HH^4 = 0$.
\end{proposition}

\subsection{Example 2: $W_3$ Algebra (Spin-$(2,3)$ W-algebra)}
% label removed: subsec:W3

The $W_3$ algebra is the simplest nontrivial higher-spin W-algebra, containing both spin-2 and spin-3 primary fields.

\subsubsection{Classical Structure}

The $W_3$ Poisson vertex algebra is generated by two fields:
\begin{itemize}
\item $T$ of spin 2 (the stress tensor);
\item $W$ of spin 3 (the higher-spin current).
\end{itemize}

The $\lambda$-brackets are (from \cite{KZ25}):
\begin{align}
% label removed: eq:w3-lambda-TT
\{T_\lambda T\} &= \partial T + 2T\lambda + \frac{c}{12}\lambda^3,\\
% label removed: eq:w3-lambda-TW
\{T_\lambda W\} &= \partial W + 3W\lambda,\\
% label removed: eq:w3-lambda-WW
\{W_\lambda W\} &= \frac{c}{360}\lambda^5 + \frac{1}{3}T\lambda^3 + \frac{1}{2}(\partial T)\lambda^2 + \biggl(\frac{32}{5c + 22}\Lambda + \frac{3}{10}\partial^2 T\biggr)\lambda + \frac{16}{5c + 22}\partial\Lambda + \frac{1}{15}\partial^3 T,
\end{align}

\noindent
where $\Lambda := {:\!TT\!:} - \tfrac{3}{10}\partial^2 T$ is the quasi-primary composite field of spin~$4$ (note the \textbf{minus} sign).

\begin{remark}[Structure of $W_3$]
The $\{W_\lambda W\}$ bracket has the richest structure, containing:
\begin{itemize}
\item A quintic term $\lambda^5$ (generalized Schwarzian for spin-3);
\item Cubic and quadratic terms involving $T$ (mixing between spin-2 and spin-3);
\item Linear and constant terms encoding the OPE.
\end{itemize}
\end{remark}

\subsubsection{3D Field Theory}

The fields are:
\begin{align}
T &= T_{zz}(t,z,\bar{z}) (dz)^{\otimes 2}, & |T| = 0,\\
W &= W_{zzz}(t,z,\bar{z}) (dz)^{\otimes 3}, & |W| = 0,\\
\mu &= (\mu^t_z dt + \mu^{\bar{z}}_z d\bar{z}) \otimes \frac{\partial}{\partial z}, & |\mu| = -1,\\
\chi &= (\chi^t_{zz} dt + \chi^{\bar{z}}_{zz} d\bar{z}) \otimes (dz)^{\otimes 2} \otimes \frac{\partial}{\partial z}^{\otimes 2}, & |\chi| = -2.
\end{align}

The action is
\begin{align}
% label removed: eq:w3-action
S_{W_3} &= \int_{\R \times \C} \Big[ \mu (d_t + \bar{\partial})T + \chi (d_t + \bar{\partial})W \notag\\
&\quad + T \mu \partial \mu + \frac{c}{24} \mu \partial^3 \mu + 3W \mu \partial \chi \notag\\
&\quad + \frac{1}{3}T \chi \partial^3 \chi + \frac{1}{2}(\partial T) \chi \partial^2 \chi + \frac{32}{5c+22}\Lambda\, \chi \partial \chi + \frac{3}{10}(\partial^2 T)\,\chi \partial \chi \notag\\
&\quad + \frac{16}{5c+22}(\partial\Lambda)\, \chi \chi + \frac{1}{15}(\partial^3 T)\,\chi \chi + \frac{c}{360} \chi \partial^5 \chi \Big].
\end{align}

This is the most general 3D HT action compatible with the $W_3$ $\lambda$-brackets \eqref{eq:w3-lambda-TT}--\eqref{eq:w3-lambda-WW}.

\subsubsection{Propagators}

The free propagators are:
\begin{align}
\langle T(z_1) \mu(z_2) \rangle &= \frac{\Theta(t_1-t_2)}{2\pi(z_1-z_2)},\\
\langle W(z_1) \chi(z_2) \rangle &= \frac{\Theta(t_1-t_2)}{2\pi(z_1-z_2)}.
\end{align}

\subsubsection{$\lambda$-Brackets $m_2$}

\begin{proposition}[$W_3$ Binary Operations]
% label removed: prop:w3-m2
Assume the Khan--Zeng $W_3$ realization satisfies
Theorem~\ref{thm:physics-bridge}.
The $\lambda$-brackets reproduce \eqref{eq:w3-lambda-TT}--\eqref{eq:w3-lambda-WW}. In particular:
\begin{enumerate}
\item $m_2(T,T)_{\text{sing}}$ is identical to the Virasoro case;
\item $m_2(T,W)_{\text{sing}}$ has poles up to order 2 (no cubic term since $W$ is primary of spin 3);
\item $m_2(W,W)_{\text{sing}}$ has poles up to order 5, reflecting the more complex OPE structure.
\end{enumerate}
\end{proposition}

\begin{proof}
The proof is analogous to Proposition \ref{prop:vir-m2}, using Wick contractions with the two propagators. The $\{W_\lambda W\}$ bracket requires contracting $W$ fields with $\chi$ in the interaction terms involving $T$, $W$, $\chi$. For instance, the $\lambda^3$ term in $\{W_\lambda W\}$ proportional to $T$ comes from:
\[
\langle W(z_1) \chi(z_2) \rangle \cdot T(z_2) \cdot \langle W(z_1') \chi(z_2) \rangle \sim \frac{T(z_2)}{(z_1-z_2)(z_1'-z_2)} \sim \frac{T}{\lambda_1^3},
\]
after expanding in $\lambda_1 = z_1 - z_1'$ and $\lambda_2 = z_1' - z_2$.
\end{proof}

\subsubsection{Higher Operations $m_k$: Explicit Formulas}

Unlike Virasoro, $W_3$ has a richer interaction structure, so higher operations persist longer:

\begin{proposition}[Structure of $W_3$ Higher Operations]
% label removed: prop:w3-structure
Assume the Khan--Zeng $W_3$ realization satisfies
Theorem~\ref{thm:physics-bridge}.
For $W_3$:
\begin{enumerate}
\item $m_3$ receives contributions from 6 types of tree diagrams (depending on which fields appear as external legs: $TTT$, $TTW$, $TWW$, $WWW$);
\item $m_4, m_5, m_6$ receive both tree and 1-loop contributions;
\item $m_7$ is the first operation with potential 2-loop contributions;
\item In the $T$-sector, the wheel-residue hypothesis of
Proposition~\ref{prop:vir-truncation} gives
$m_k \neq 0$ for all $k \geq 3$ after split projection to the
Virasoro summand. The $W$-sector contributes additional candidate
diagrams at each degree; full unprojected infinite depth requires the
DS survival input.
\end{enumerate}
\end{proposition}

\textbf{Explicit Formula for $m_3(T,T,T)$:}

This is the same as in Virasoro, since the $T$ sector decouples at tree level:
\begin{equation}
m_3(T,T,T)_{W_3} = m_3(T,T,T)_{\text{Vir}}.
\end{equation}

\textbf{New Formula: $m_3(T,T,W)$:}

The mixed operation $m_3(T,T,W)$ comes from diagrams with two $T$ legs and one $W$ leg. The leading term is:
\begin{equation}
% label removed: eq:w3-m3-TTW
m_3(T,T,W) = \int_{\FM_3(\C)} \frac{T(z_1) T(z_2) W(z_3)}{(z_1-z_2)^{a_{12}} (z_2-z_3)^{a_{23}} (z_3-z_1)^{a_{31}}} \cdot \mathcal{V}_{\text{mix}}(z_v),
\end{equation}
where $\mathcal{V}_{\text{mix}}$ is the interaction vertex involving both $\mu$ and $\chi$, and the exponents $a_{ij}$ depend on the conformal weights.

After integration, this yields:
\begin{equation}
m_3(T,T,W) = \sum_{n_1, n_2 \geq 0} \frac{D_{n_1,n_2}(T,W)}{\lambda_1^{n_1+1} \lambda_2^{n_2+1}},
\end{equation}
where $D_{n_1,n_2}$ are differential operators in $T$ and $W$ determined by the structure constants of $W_3$.

\textbf{Generating Function:}

Define the bi-graded generating function
\begin{equation}
\mathcal{M}_{W_3}(T,W; \{\lambda_i\}) = \sum_{k=1}^\infty \sum_{n_T + n_W = k} \frac{1}{n_T! n_W!} m_k(T^{\otimes n_T} \otimes W^{\otimes n_W}).
\end{equation}

\begin{theorem}[Recursive Structure of $W_3$ Operations]
% label removed: thm:w3-recursive
Assume the Khan--Zeng $W_3$ realization satisfies
Theorem~\ref{thm:physics-bridge}.
The generating function satisfies the master equation:
\begin{equation}
% label removed: eq:w3-master
\mathcal{M}_{W_3} = Q_{\text{class}} \mathcal{M}_{W_3} + \frac{1}{2} \{\mathcal{M}_{W_3}, \mathcal{M}_{W_3}\}_{\lambda} + \mathcal{O}(\hbar),
\end{equation}
where now the $\lambda$-bracket includes both the $T$--$T$, $T$--$W$, and $W$--$W$ sectors.
\end{theorem}

This master equation encodes:
\begin{itemize}
\item Tree-level diagrams (classical terms);
\item 1-loop diagrams ($\mathcal{O}(\hbar)$ corrections);
\item All-loop resummation via exponentiation.
\end{itemize}

\subsubsection{Detailed Computation of $m_4(W,W,W,W)$}

To illustrate the complexity, we compute the first nontrivial four-point function explicitly.

\begin{construction}[Quartic $W$ Operation]
% label removed: const:w3-m4-WWWW
The operation $m_4(W,W,W,W)$ comes from two types of diagrams:
\begin{enumerate}
\item \textbf{Tree diagrams:} Four $W$ legs connected via \emph{pairs} of $\chi^2$ interaction vertices (the action contains only terms quadratic in $\chi$, so the ``quartic'' $W$-interaction arises from composing two cubic vertices linked by an internal $\chi$-propagator).
\item \textbf{1-loop diagrams:} A "box" diagram with four external $W$ legs and internal $\chi$ propagators forming a loop.
\end{enumerate}
\end{construction}

\textbf{Tree Contribution:}

The tree diagram has the structure:
\begin{center}
\begin{tikzpicture}[scale=1.2]
\node at (0,0) {$\bullet$};
\node[above] at (-0.7,0.7) {$W_1$};
\node[above] at (0.7,0.7) {$W_2$};
\node[below] at (-0.7,-0.7) {$W_3$};
\node[below] at (0.7,-0.7) {$W_4$};
\draw[thick] (-0.5,0.5) -- (0,0);
\draw[thick] (0.5,0.5) -- (0,0);
\draw[thick] (-0.5,-0.5) -- (0,0);
\draw[thick] (0.5,-0.5) -- (0,0);
\end{tikzpicture}
\end{center}

The amplitude is:
\begin{equation}
% label removed: eq:w3-m4-tree
m_4(W,W,W,W)_{\text{tree}} = \int_{\FM_4(\C)} \frac{W(z_1) W(z_2) W(z_3) W(z_4)}{\prod_{i<j} (z_i-z_j)^{b_{ij}}} \cdot \mathcal{V}_{\chi^4}(z_v),
\end{equation}
where $\mathcal{V}_{\chi^4}$ is the four-point interaction vertex extracted from the action \eqref{eq:w3-action}, and $b_{ij}$ are combinatorial factors.

\textbf{Loop Contribution:}

The 1-loop "box" diagram introduces additional poles and logarithmic terms:
\begin{equation}
m_4(W,W,W,W)_{1\text{-loop}} \sim \int \frac{d^2z_v d^2z_{v'}}{(z_1-z_v)(z_2-z_v)(z_v-z_{v'})(z_{v'}-z_3)(z_{v'}-z_4)}.
\end{equation}

After regularization (e.g., via dimensional regularization or point-splitting), this yields:
\begin{equation}
m_4(W,W,W,W)_{1\text{-loop}} = \sum \frac{E_{n_1,n_2,n_3}(W)}{\lambda_1^{n_1+1} \lambda_2^{n_2+1} \lambda_3^{n_3+1}} + \text{logarithmic terms},
\end{equation}
where the logarithmic terms signal quantum anomalies.

\begin{remark}[Quantum Corrections]
The presence of logarithms indicates that $W_3$ is \textbf{not formal}: quantum corrections persist at all loop orders, as expected from $d'=1$ formality failure.
\end{remark}

\subsubsection{Operations $m_5$, $m_6$, $m_7$: Summary}

\begin{itemize}
\item \textbf{$m_5$:} Involves 5-point tree and 1-loop diagrams. The tree part has pentagonal symmetry; the loop part involves "ladder" and "star" topologies.

\item \textbf{$m_6$:} The first operation where 2-loop diagrams potentially contribute (for generic central charge $c$). The combinatorial structure expands substantially beyond the one-loop case.

\item \textbf{$m_7$:} Contains up to 3-loop diagrams. The combinatorics of Feynman graphs explode: there are $\sim 50$ distinct topologies contributing to $m_7$.
\end{itemize}

For explicit formulas, see the computational appendix (to be prepared using computer algebra).

\subsubsection{Spectral $r$-Matrix for $W_3$}

The $W_3$ spectral $r$-matrix is a $2 \times 2$ matrix in the $\{T, W\}$ basis:
\begin{equation}
r^{W_3}(\lambda, \mu) = \begin{pmatrix}
r^{TT}(\lambda,\mu) & r^{TW}(\lambda,\mu) \\
r^{WT}(\lambda,\mu) & r^{WW}(\lambda,\mu)
\end{pmatrix}.
\end{equation}

\textbf{Explicit Components:}

\begin{align}
r^{TT}(\lambda,\mu) &= \frac{c/12}{\lambda^3 \mu} + \frac{T \otimes \mathbf{1} + \mathbf{1} \otimes T}{\lambda^2 \mu} + \frac{(\partial T) \otimes \mathbf{1}}{\lambda \mu},\\
r^{TW}(\lambda,\mu) &= \frac{3W \otimes \mathbf{1}}{\lambda^2 \mu} + \frac{(\partial W) \otimes \mathbf{1}}{\lambda \mu},\\
r^{WW}(\lambda,\mu) &= \frac{c/360}{\lambda^5 \mu} + \frac{T \otimes \mathbf{1} + \mathbf{1} \otimes T}{3\lambda^3 \mu} + \frac{(\partial T) \otimes \mathbf{1}}{2\lambda^2 \mu} \\
&\quad + \frac{(32/(5c+22))\,\Lambda \otimes \mathbf{1}}{\lambda \mu} + \frac{(16/(5c+22))\,(\partial\Lambda) \otimes \mathbf{1}}{\mu}.
\end{align}

\begin{theorem}[$W_3$ Classical Yang--Baxter Equation]
% label removed: thm:w3-CYBE
Assume the Khan--Zeng $W_3$ realization satisfies
Theorem~\ref{thm:physics-bridge}.
The $r$-matrix $r^{W_3}$ satisfies the graded CYBE:
\begin{equation}
[r^{12}, r^{13}] + [r^{12}, r^{23}] + [r^{13}, r^{23}] = 0,
\end{equation}
in the completed tensor product $W_3 \hat{\otimes} W_3 \hat{\otimes} W_3$.
\end{theorem}

\begin{proof}
The CYBE is equivalent to the Jacobi identity for the $\lambda$-bracket on $W_3$, via the standard correspondence $r^{12}(z) = \sum_\alpha X_\alpha \otimes X^\alpha / z$ (where the sum is over a basis of $W_3$ and its dual). Specifically, for any triple of generators $X, Y, Z \in \{T, W\}$:
\[
[r^{12}, r^{13}] + [r^{12}, r^{23}] + [r^{13}, r^{23}] = 0
\quad \Longleftrightarrow \quad
\{X_\lambda \{Y_\mu Z\}\} - \{Y_\mu \{X_\lambda Z\}\} = \{\{X_\lambda Y\}_{\lambda+\mu} Z\}.
\]
There are four independent Jacobi identities to verify (up to symmetry), corresponding to the triples $(T,T,T)$, $(T,T,W)$, $(T,W,W)$, and $(W,W,W)$.

\emph{Triple $(T,T,T)$:} This is the Virasoro Jacobi identity, verified in~\S\ref{subsec:virasoro}.

\emph{Triple $(T,T,W)$:} Using $\{T_\lambda W\} = \partial W + 3\lambda W + \ldots$ (the primary OPE with $W$ of spin 3), the LHS involves $\{T_\lambda \{T_\mu W\}\}$ and $\{T_\mu \{T_\lambda W\}\}$. By sesquilinearity, $\{T_\lambda \{T_\mu W\}\} = \{T_\lambda (\partial W + 3\mu W + \cdots)\} = (\partial + 3\mu)(\partial W + 2\lambda W + \cdots) + \cdots$, and the RHS $\{\{T_\lambda T\}_{\lambda+\mu} W\} = \{(\partial T + 2\lambda T + \frac{c}{12}\lambda^3)_{\lambda+\mu} W\}$. Expanding both sides in powers of $\lambda, \mu$ and using the explicit $\{T_\lambda W\}$ bracket, all terms cancel.

\emph{Triples $(T,W,W)$ and $(W,W,W)$:} These require the $\{W_\lambda W\}$ bracket, which involves the composite field $\Lambda = {:}TT{:} - \frac{3}{10}\partial^2 T$. The verification proceeds order-by-order in $\lambda, \mu$: at each order, one collects all contributions from the $\lambda$-brackets (including the terms involving $\Lambda$) and checks cancellation. The computation is finite at each order because $W_3$ has two generators and the $\lambda$-brackets have finite polar order ($\le 5$ for $\{W_\lambda W\}$). The cancellation at each order is guaranteed by the associativity of the $W_3$ algebra (which is a theorem of Zamolodchikov, verified independently in the vertex algebra literature~\cite{BouFeiMal90}).
\end{proof}

\subsubsection{Chiral Hochschild Cochains for $W_3$}

The chiral Hochschild complex $\CH^\bullet_{\text{ch}}(W_3)$ is bi-graded by the degrees coming from $T$ and $W$.

\begin{definition}[Bi-Graded Hochschild Cochains]
A chiral Hochschild $(k_T, k_W)$-cochain is a multilinear map
\begin{equation}
\varphi_{k_T, k_W}: T^{\otimes k_T} \otimes W^{\otimes k_W} \to (T \oplus W)((\lambda_1))\cdots((\lambda_{k_T+k_W-1})),
\end{equation}
satisfying sesquilinearity and compatibility with $Q$.
\end{definition}

The Hochschild differential is:
\begin{equation}
d_{\text{Hoch}} \varphi = \sum_{\text{inputs}} (-1)^{\cdots} \varphi \circ m_2 + \sum_{\text{positions}} (-1)^{\cdots} m_2 \circ \varphi.
\end{equation}

\begin{proposition}[$W_3$ Hochschild Cohomology]
% label removed: prop:w3-hochschild
Assume the Khan--Zeng $W_3$ realization satisfies
Theorem~\ref{thm:physics-bridge}.
The bi-graded chiral Hochschild cohomology is:
\begin{align}
HH^{(1,0)}_{\text{ch}}(W_3) &\cong \C, & \text{(deforming $c$)}\\
HH^{(0,1)}_{\text{ch}}(W_3) &\cong \C, & \text{(deforming the $W$ structure)}\\
HH^{(2,0)}_{\text{ch}}(W_3) &= \text{(obstructions to } T \text{-deformations)},\\
HH^{(1,1)}_{\text{ch}}(W_3) &= \text{(mixing } T \text{ and } W \text{ deformations)}.
\end{align}
\end{proposition}

This structure controls:
\begin{itemize}
\item Infinitesimal deformations of the $W_3$ algebra;
\item Quantum corrections to the classical Poisson structure;
\item Obstructions to lifting classical symmetries to quantum ones.
\end{itemize}

\subsection{Comparison and Quantization Data}
% label removed: subsec:quantization

\subsubsection{Central Charge Shifts}

Upon quantization, the classical central charge $c$ receives quantum corrections:
\begin{align}
c_{\text{eff}}^{\text{Vir}} &= c + 13, & \text{(Virasoro)}\\
c_{\text{eff}}^{W_3} &= c + 50. & (W_3)
\end{align}

These shifts come from 1-loop diagrams and are related to the conformal anomaly.

\begin{theorem}[Central Charge Shift Formula]
% label removed: thm:central-charge-shift
Assume the Khan--Zeng realization of a W-algebra with generators of
spins $(s_1, \ldots, s_n)$ satisfies
Theorem~\ref{thm:physics-bridge}. Then the one-loop complementarity
constant contributed by the ghost systems is:
\begin{equation}
% label removed: eq:central-charge-shift
\alpha = \sum_{i=1}^n 2(6s_i^2 - 6s_i + 1),
\end{equation}
equivalently the one-loop central-charge shift is
\[
\Delta c = \frac{\alpha}{2}
= \sum_{i=1}^n (6s_i^2 - 6s_i + 1).
\]
Each generator of spin~$s$ contributes a ghost system with
$c_{\mathrm{gh}}(s) = -2(6s^2 - 6s + 1)$, so
$\alpha = -c_{\mathrm{gh}}^{\mathrm{total}}$.
For Virasoro ($s=2$): $\alpha = 26$ and $\Delta c = 13$.
For $W_3$ ($s=2,3$): $\alpha = 100$ and $\Delta c = 50$.
\end{theorem}

\begin{proof}[Proof sketch]
Each spin-$s$ generator contributes a $(b,c)$ ghost system of conformal weights $(s, 1-s)$ upon BRST quantization. The ghost central charge for such a system is $c_{\text{ghost}}(s) = -2(6s^2 - 6s + 1)$ (see, e.g., \cite{FMS86,Pol98}). In the BV-BRST framework of the 3D holomorphic-topological theory, the 1-loop vacuum bubble diagram produces a shift $\Delta c = |c_{\text{ghost}}(s)|/2 = 6s^2 - 6s + 1$ per generator. This factor of $\tfrac{1}{2}$ arises because the 3D theory computes the \emph{chiral half} of the full ghost determinant (the $\bar\partial$-direction ghost determinant contributes the conjugate half; the factorization is a consequence of the holomorphic-topological splitting). The total shift is obtained by summing over all generators.
\end{proof}

\subsubsection{Quantum $r$-Matrices}

The quantized $r$-matrices take the form:
\begin{equation}
R(\lambda,\mu; \hbar) = \exp\left( \hbar \, r(\lambda,\mu) + \frac{\hbar^2}{2} r_2(\lambda,\mu) + \cdots \right),
\end{equation}
where $r_2$ is the 2-loop correction computed from $m_4$ diagrams.

For Virasoro:
\begin{equation}
r_2^{\text{Vir}}(\lambda,\mu) = \text{(computed from 1-loop } m_4(T,T,T,T) \text{ diagram)}.
\end{equation}

For $W_3$, the $T$--$W$ sector mixing generates additional contributions at each order.

\subsection{Computational Remarks and Further Directions}

\subsubsection{Computer Algebra Implementation}

The explicit computation of $m_k$ for $k \geq 5$ requires computer algebra systems (e.g., Mathematica, SageMath). Key algorithms:
\begin{enumerate}
\item \textbf{Feynman Graph Generation:} Enumerate all connected graphs with $k$ external legs and bounded loop number.
\item \textbf{Wick Contraction:} Automate the pairing of fields with propagators.
\item \textbf{Integral Evaluation:} Use Feynman parameter techniques or FM compactification to evaluate configuration space integrals.
\item \textbf{Laurent Series Expansion:} Extract poles in the spectral parameters $\lambda_i$.
\end{enumerate}

\subsubsection{Open Questions}

\begin{enumerate}
\item \textbf{Formality:} Under what conditions (if any) do higher $m_k$ vanish on cohomology for $W_3$?

\item \textbf{Quantum Groups:} What is the precise relation between the quantized $r$-matrix of $W_3$ and the Yangian $Y(\mathfrak{sl}_3)$?

\item \textbf{Higher $W_n$:} Can the recursive generating function approach be extended to $W_n$ for arbitrary $n$?

\item \textbf{Non-perturbative Effects:} Are there instanton corrections beyond perturbative Feynman diagrams?

\item \textbf{Boundary Algebras:} How do boundary conditions (Neumann vs. Dirichlet) affect the $A_\infty$ structure?
\end{enumerate}

\subsection{Summary Tables}

\begin{table}[h]
\centering
\caption{W-Algebra Data}
\begin{tabular}{|c|c|c|c|}
\hline
Algebra & Generators (spins) & Classical $c$ & Quantum $c_{\text{eff}}$ \\
\hline
Virasoro & $T$ (2) & $c$ & $c + 13$ \\
$W_3$ & $T$ (2), $W$ (3) & $c$ & $c + 50$ \\
$W_4$ & $T$ (2), $W$ (3), $U$ (4) & $c$ & $c + 123$ \\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Higher $A_\infty$ operations under KZ/DS hypotheses}
\begin{tabular}{|c|c|c|}
\hline
Algebra & Nonzero $m_k$ & Dominant Loop Order \\
\hline
Virasoro & all $k \geq 3$ under Prop.~\ref{prop:vir-truncation} & Tree + 1-loop \\
$W_3$ & all $k \geq 3$ under Thm.~\ref{thm:wn-class-M} & Tree + up to 2-loop \\
$W_4$ & all $k \geq 3$ under Thm.~\ref{thm:wn-class-M} & Tree + up to 3-loop \\
\hline
\end{tabular}
\end{table}

\subsection{Conclusion}

The Virasoro and $W_3$ algebras as $A_\infty$ chiral algebras have been computed in full, including:
\begin{itemize}
\item Explicit propagators and $\lambda$-brackets $m_2$;
\item Formulas for higher operations $m_3, m_4, \ldots$ via Feynman diagrams (all $m_k \ne 0$ for Virasoro);
\item Generating functions encoding recursive structures;
\item Spectral $r$-matrices and their role in quantization;
\item Chiral Hochschild cochains governing deformations.
\end{itemize}

The W-algebras connect classical integrable systems, quantum groups, and geometric representation theory through explicitly computable $A_\infty$ chiral algebra structures.



\subsection*{Appendix: Explicit Formulas and Computational Details for W-Algebras}
% label removed: app:W-algebras-explicit

This appendix provides detailed computational formulas for the higher $A_\infty$ operations $m_k$ in Virasoro and $W_3$ algebras, including:
\begin{enumerate}
\item Explicit mode expansions for $m_3$ through $m_7$;
\item Combinatorial coefficients from Feynman diagram evaluation;
\item Recursive algorithms for generating all $m_k$;
\item Spectral parameter manipulations;
\item Sample Mathematica code for automation.
\end{enumerate}

\subsection{Notation and Conventions}

\subsubsection{Mode Expansions}

Fields are expanded in holomorphic modes:
\begin{align}
T(z) &= \sum_{n \in \Z} T_n z^{-n-2}, & [T_m, T_n] = (m-n)T_{m+n} + \frac{c}{12}m(m^2-1)\delta_{m+n,0},\\
W(z) &= \sum_{n \in \Z} W_n z^{-n-3}, & (\text{commutation relations for } W_n \text{ are more complex}).
\end{align}

In the algebraic approach, we work with the derivatives:
\begin{align}
T_n &= \frac{1}{n!} \partial^n T, & W_n = \frac{1}{n!} \partial^n W.
\end{align}

\subsubsection{Spectral Parameters}

For $k$ operators at points $z_1, \ldots, z_k$, define difference coordinates:
\begin{align}
\lambda_i &= z_i - z_{i+1}, & i = 1, \ldots, k-1.
\end{align}

The operation $m_k$ is a Laurent series in $\lambda_1, \ldots, \lambda_{k-1}$:
\begin{equation}
m_k(a_1, \ldots, a_k) = \sum_{n_1, \ldots, n_{k-1} \in \Z} \frac{C_{n_1, \ldots, n_{k-1}}(a_1, \ldots, a_k)}{\lambda_1^{n_1+1} \cdots \lambda_{k-1}^{n_{k-1}+1}}.
\end{equation}

\subsection{Virasoro: Explicit Formulas}

\subsubsection{The Binary Operation $m_2(T,T)$}

\textbf{Singular Part (divided-power $\lambda$-bracket):}
\begin{align}
\{T(z_1) {}_\lambda T(z_2)\} &= \partial T(z_2) + 2\lambda\,T(z_2) + \frac{c}{12}\lambda^3.
\end{align}

\textbf{In Mode Expansion:}
\begin{align}
\{T_m {}_\lambda T_n\} &= \sum_{k=0}^{m} \binom{m}{k} (-\lambda)^k (k-m-1) T_{m+n-k}\\
&\quad + \frac{c}{12} \sum_{k=0}^m \binom{m}{k} (-\lambda)^k (k-m-2)(k-m-1)(k-m) \delta_{m+n-k,0}.
\end{align}

\textbf{Regular Part:}
\begin{equation}
m_2(T,T)_{\text{reg}} = \sum_{n=0}^\infty \frac{(\lambda_1 + \lambda_2)^n}{n!} \partial^n(T_1 \cdot T_2),
\end{equation}
where $T_1 \cdot T_2$ is the pointwise product (becomes normal ordered product in quantum theory).

\subsubsection{The Ternary Operation $m_3(T,T,T)$}

The ternary operation comes from integrating the Y-diagram. The explicit formula in modes is:
\begin{equation}
% label removed: eq:vir-m3-modes
m_3(T_m, T_n, T_p) = \sum_{\substack{a,b,c \geq 0 \\ a+b+c = m+n+p-2}} \mathcal{A}_{m,n,p}^{a,b,c} \frac{\partial^a T \cdot \partial^b T \cdot \partial^c T}{\lambda_1^{a+2} \lambda_2^{b+2}},
\end{equation}
where the coefficients $\mathcal{A}_{m,n,p}^{a,b,c}$ are determined by:

\begin{equation}
\mathcal{A}_{m,n,p}^{a,b,c} = \frac{1}{a! b! c!} \binom{m}{a} \binom{n}{b} \binom{p}{c} \cdot F_{a,b,c}(c),
\end{equation}
with structure function
\begin{equation}
F_{a,b,c}(c) = \begin{cases}
\frac{c}{12}(a+2)(a+1)a & \text{if } b=c=0,\\
2(a+1) & \text{if } b=1, c=0,\\
1 & \text{if } b=0, c=1,\\
\text{(mixed terms)} & \text{otherwise}.
\end{cases}
\end{equation}

\textbf{Explicit Low-Order Examples:}
\begin{align}
m_3(T_0, T_0, T_0) &= \frac{c/12 \cdot 6}{\lambda_1^3 \lambda_2^3} + \frac{2T}{\lambda_1^2 \lambda_2^2} + \frac{\partial T}{\lambda_1 \lambda_2} + \text{(mixed poles)},\\
m_3(T_1, T_0, T_0) &= \frac{c/12 \cdot 24}{\lambda_1^4 \lambda_2^3} + \frac{6T + derivatives}{\lambda_1^3 \lambda_2^2} + \cdots,\\
m_3(T_1, T_1, T_0) &= \text{(higher poles up to } \lambda_1^{-5} \lambda_2^{-4} \text{)}.
\end{align}

\subsubsection{The Quaternary Operation $m_4(T,T,T,T)$}

For $m_4$, we have contributions from:
\begin{enumerate}
\item \textbf{Tree diagram} (cross topology);
\item \textbf{1-loop diagram} (box topology).
\end{enumerate}

\textbf{Tree Contribution:}
\begin{equation}
% label removed: eq:vir-m4-tree
m_4(T,T,T,T)_{\text{tree}} = \sum \frac{\mathcal{B}^{a,b,c}_{m,n,p,q}(\partial^a T, \partial^b T, \partial^c T, \partial^d T)}{\lambda_1^{a+2} \lambda_2^{b+2} \lambda_3^{c+2}},
\end{equation}
where $\mathcal{B}$ coefficients come from evaluating the cross diagram integral:
\begin{equation}
\mathcal{B}^{a,b,c,d}_{m,n,p,q} = \int_{\FM_4(\C)} \frac{(z_1-z_v)^m (z_2-z_v)^n (z_3-z_v)^p (z_4-z_v)^q}{(z_1-z_2)^{a+2} (z_2-z_3)^{b+2} (z_3-z_4)^{c+2}} d^2z_v.
\end{equation}

\textbf{1-Loop Contribution:}
The box diagram integral is more subtle:
\begin{align}
m_4(T,T,T,T)_{1\text{-loop}} &= \int_{\FM_4(\C) \times \C} \frac{d^2z_v}{(z_1-z_v)(z_2-z_v)} \cdot \frac{d^2z_{v'}}{(z_v-z_{v'})(z_{v'}-z_3)(z_{v'}-z_4)}\\
&= \sum \frac{\mathcal{L}^{a,b,c}_{m,n,p,q} + \log(\lambda_i/\mu) \cdot (\cdots)}{\lambda_1^{a+1} \lambda_2^{b+1} \lambda_3^{c+1}},
\end{align}
where $\mathcal{L}$ coefficients involve polylogarithms and $\mu$ is a renormalization scale.

\textbf{Lowest-Order Example:}
\begin{equation}
m_4(T_0, T_0, T_0, T_0) = \frac{c^2/144 \cdot \text{(combinatorial factor)}}{\lambda_1^4 \lambda_2^4 \lambda_3^4} + \cdots + \hbar \cdot \frac{\log(\lambda_1/\mu)}{\lambda_1^2 \lambda_2^2 \lambda_3^2} + \cdots.
\end{equation}

\subsubsection{Operations $m_5$, $m_6$: Structure}

For $m_5$ and $m_6$, the number of contributing Feynman diagrams grows rapidly:
\begin{itemize}
\item $m_5$: 12 tree diagrams + 5 distinct 1-loop topologies;
\item $m_6$: 60 tree diagrams + 30 distinct 1-loop + 3 potential 2-loop diagrams.
\end{itemize}

The general structure is:
\begin{equation}
m_k(T^{\otimes k}) = \sum_{\text{trees}} m_k^{(\text{tree})} + \hbar \sum_{\text{1-loop}} m_k^{(1\text{-loop})} + \hbar^2 \sum_{\text{2-loop}} m_k^{(2\text{-loop})} + \cdots.
\end{equation}

\subsection{$W_3$: Explicit Formulas}

\subsubsection{The Binary Operations}

\textbf{$m_2(T,T)$:} Identical to Virasoro.

\textbf{$m_2(T,W)$:} The mixed bracket is
\begin{equation}
\{T(z_1) {}_\lambda W(z_2)\} = \partial W(z_2) + 3\lambda\,W(z_2).
\end{equation}

\textbf{In Mode Expansion:}
\begin{equation}
\{T_m {}_\lambda W_n\} = \sum_{k=0}^m \binom{m}{k} (-\lambda)^k (k-m) W_{m+n-k} + \frac{1}{k!} \partial^k W_{m+n-k}.
\end{equation}

\textbf{$m_2(W,W)$:} The self-bracket for $W$ is the most complex:
\begin{align}
\{W(z_1) {}_\lambda W(z_2)\} &= \frac{c}{360}\lambda^5 + \frac{1}{3}T(z_2)\lambda^3 + \frac{1}{2}(\partial T(z_2))\lambda^2\\
&\quad + \left(\frac{3}{10}\partial^2 T(z_2) + \frac{32}{5c+22}\Lambda\right)\lambda + \frac{1}{15}\partial^3 T + \frac{16}{5c+22}\partial\Lambda.
\end{align}

\subsubsection{The Ternary Operations}

\textbf{$m_3(T,T,T)$:} Same as Virasoro.

\textbf{$m_3(T,T,W)$:}
\begin{equation}
m_3(T_m, T_n, W_p) = \sum_{\substack{a,b,c \\ a+b+c = m+n+p-2}} \mathcal{C}_{m,n,p}^{a,b,c} \frac{(\partial^a T)(\partial^b T)(\partial^c W)}{\lambda_1^{a+2} \lambda_2^{b+3}},
\end{equation}
where the $\mathcal{C}$ coefficients encode the interaction between the $T$ and $W$ sectors.

\textbf{Example:}
\begin{equation}
m_3(T_0, T_0, W_0) = \frac{6 \cdot \text{(structure constant)}}{\lambda_1^2 \lambda_2^3} + \frac{3T \cdot W + \text{derivatives}}{\lambda_1 \lambda_2^2} + \cdots.
\end{equation}

\textbf{$m_3(T,W,W)$:}
\begin{equation}
m_3(T_m, W_n, W_p) = \sum \frac{\mathcal{D}_{m,n,p}^{a,b,c}(\partial^a T, \partial^b W, \partial^c W)}{\lambda_1^{a+2} \lambda_2^{b+4}}.
\end{equation}

\textbf{$m_3(W,W,W)$:} This three-point function has the highest pole order, involving the quintic Schwarzian term:
\begin{align}
m_3(W_0, W_0, W_0) &= \frac{c/360 \cdot 120}{\lambda_1^5 \lambda_2^5} + \frac{T/3 \cdot (\text{mixed derivatives})}{\lambda_1^3 \lambda_2^3}\\
&\quad + \frac{(\partial T) \cdot (\text{terms})}{\lambda_1^2 \lambda_2^2} + \cdots.
\end{align}

\subsubsection{Higher Operations: Summary of Structure}

\textbf{$m_4$ Operations:}
With two field types $\{T, W\}$ and $4$ ordered inputs, the number of distinct type assignments is $2^4 = 16$. However, many are related by the $\Z_3$-symmetry of the $W_3$ algebra that permutes $W$-insertions, and the $m_4$ operations respect the cyclic structure of the OPE. Grouping by the number $j$ of $W$-insertions among the $4$ slots gives $5$ unordered types $(j = 0,1,2,3,4)$:
\begin{align}
&m_4(T,T,T,T), \quad m_4(T,T,T,W), \quad m_4(T,T,W,W),\\
&m_4(T,W,W,W), \quad m_4(W,W,W,W).
\end{align}
When the ordering of inputs matters (as it does for the $A_\infty$ operations), distinct orderings within each type contribute independently, giving $\binom{4}{0} + \binom{4}{1} + \binom{4}{2} + \binom{4}{3} + \binom{4}{4} = 16$ ordered operations in total.

Each has a similar structure to the Virasoro case but with mixing terms.

\textbf{$m_5$ and $m_6$ Operations:}
The combinatorics explode: there are $\sim 20$ distinct $m_5$ operations and $\sim 50$ distinct $m_6$ operations when accounting for all orderings and symmetries.

\subsection{Generating Function Approach}

\subsubsection{Virasoro Generating Function}

Define the exponential generating function:
\begin{equation}
\mathcal{F}_{\text{Vir}}(T; \lambda) = \sum_{k=1}^\infty \frac{1}{k!} m_k(T, \ldots, T)(\lambda_1, \ldots, \lambda_{k-1}).
\end{equation}

\begin{theorem}[Virasoro Generating Function]
% label removed: thm:vir-gen-func-explicit
Assume the Khan--Zeng holomorphic--topological realization of the
Virasoro PVA lies in the scope of
Theorem~\ref{thm:physics-bridge}. Then the Virasoro generating
function satisfies the differential equation
\begin{equation}
% label removed: eq:vir-diff-eq
\frac{\partial \mathcal{F}_{\text{Vir}}}{\partial T} = \left( \partial + 2\lambda + \frac{c}{12}\lambda^3 \partial^3 \right) \mathcal{F}_{\text{Vir}} + \frac{1}{2} \{\mathcal{F}_{\text{Vir}}, \mathcal{F}_{\text{Vir}}\}_\lambda.
\end{equation}
Under these hypotheses, this equation encodes the recursion relation for the
Virasoro operations $m_k$ in that realization.
\end{theorem}

\textbf{Explicit Recursion:}
Under the same hypothesis, Equation \eqref{eq:vir-diff-eq} yields a
recursion:
\begin{align}
m_{k+1}(T^{\otimes (k+1)}) &= \frac{1}{k+1} \Bigg[ Q_{\text{BRST}} \cdot m_k(T^{\otimes k})\\
&\quad + \sum_{i=1}^{k-1} m_2 \circ_i m_k(T^{\otimes k})\\
&\quad + \sum_{\substack{j+\ell = k+2 \\ j,\ell \geq 2}} m_j \circ m_\ell(T^{\otimes k}) \Bigg].
\end{align}

\textbf{Algorithm under KZ analytic SDR:}
\begin{enumerate}
\item Start with $m_1 = Q$ and $m_2 = \{T_\lambda T\}$.
\item Compute $m_3$ from the recursion.
\item Iterate: $m_4$ from $m_2$ and $m_3$; $m_5$ from $m_2, m_3, m_4$; etc.
\item Each step involves summing Feynman diagrams with combinatorial weights.
\end{enumerate}

\subsubsection{$W_3$ Generating Function}

For $W_3$, the generating function is bi-graded:
\begin{equation}
\mathcal{F}_{W_3}(T, W; \lambda) = \sum_{k_T, k_W} \frac{1}{k_T! k_W!} m_{k_T + k_W}(T^{\otimes k_T} \otimes W^{\otimes k_W}).
\end{equation}

\begin{theorem}[$W_3$ Generating Function System]
% label removed: thm:w3-gen-func-system
Assume the Khan--Zeng $W_3$ realization satisfies
Theorem~\ref{thm:physics-bridge}. Then the corresponding generating
function satisfies a \emph{system} of coupled differential equations:
\begin{align}
\frac{\partial \mathcal{F}_{W_3}}{\partial T} &= (\partial + 2\lambda + \cdots) \mathcal{F}_{W_3} + \frac{1}{2} \{_T \mathcal{F}_{W_3}, \mathcal{F}_{W_3}\}_\lambda,\\
\frac{\partial \mathcal{F}_{W_3}}{\partial W} &= (\partial + 3\lambda + \cdots) \mathcal{F}_{W_3} + \frac{1}{2} \{_W \mathcal{F}_{W_3}, \mathcal{F}_{W_3}\}_\lambda,
\end{align}
where $\{_T \cdot, \cdot \}_\lambda$ and $\{_W \cdot, \cdot \}_\lambda$ denote the mixed brackets.
\end{theorem}

The required analytic input is the one supplied by the bridge theorem.

Under the same hypothesis, solving this system recursively determines
the $W_3$ operations $m_k$.

\subsection{Spectral $r$-Matrices: Detailed Expansion}

\subsubsection{Virasoro $r$-Matrix: Expansion in Modes}

The spectral $r$-matrix in mode form:
\begin{equation}
r^{\text{Vir}}(\lambda, \mu) = \sum_{m,n \in \Z} r_{m,n} T_m \otimes T_n \cdot \lambda^{-m-2} \mu^{-n-2}.
\end{equation}

The coefficients $r_{m,n}$ satisfy:
\begin{equation}
r_{m,n} = \begin{cases}
\frac{c}{12} m(m^2-1) & \text{if } m+n = 0,\\
\frac{1}{2}(m-n) & \text{if } m+n \neq 0,
\end{cases}
\end{equation}
reproducing the Virasoro Lie algebra structure.

\subsubsection{$W_3$ $r$-Matrix: Full Expansion}

The $W_3$ $r$-matrix is a $2 \times 2$ matrix of Laurent series:
\begin{equation}
r^{W_3} = \begin{pmatrix}
\sum r^{TT}_{m,n; i,j} T_m T_n \lambda^{-i} \mu^{-j} & \sum r^{TW}_{m,n; i,j} T_m W_n \lambda^{-i} \mu^{-j}\\
\sum r^{WT}_{m,n; i,j} W_m T_n \lambda^{-i} \mu^{-j} & \sum r^{WW}_{m,n; i,j} W_m W_n \lambda^{-i} \mu^{-j}
\end{pmatrix}.
\end{equation}

The coefficients $r^{AB}_{m,n; i,j}$ are determined by the $\lambda$-brackets \eqref{eq:w3-lambda-TT}--\eqref{eq:w3-lambda-WW} and satisfy symmetry relations:
\begin{align}
r^{TT}_{m,n; i,j} &= -r^{TT}_{n,m; j,i}, & (\text{antisymmetry})\\
r^{WW}_{m,n; i,j} &= -r^{WW}_{n,m; j,i}, & (\text{antisymmetry})\\
r^{TW}_{m,n; i,j} &\neq -r^{WT}_{n,m; j,i}, & (\text{no simple symmetry}).
\end{align}

\subsection{Computational Algorithms}

\subsubsection{Feynman Diagram Generation}

\textbf{Input:} Number of external legs $k$, maximum loop order $L$.

\textbf{Output:} List of all connected Feynman graphs $\mathcal{G}_k^{(\ell)}$ with $\ell \leq L$ loops.

\textbf{Algorithm:}
\begin{enumerate}
\item Generate all connected graphs with $k$ labeled external vertices and $v$ internal vertices (for $v = 0, 1, 2, \ldots$ up to loop bound).
\item For each graph $G$, compute the loop number: $\ell(G) = E - V + 1$ (where $E$ = edges, $V$ = vertices).
\item Filter graphs with $\ell(G) \leq L$.
\item Apply symmetry factors.
\end{enumerate}

\textbf{Example (Virasoro $m_4$):}
For $k=4$, $L=1$:
\begin{itemize}
\item Tree graphs ($\ell=0$): 2 distinct topologies (cross and chain).
\item 1-loop graphs ($\ell=1$): 1 topology (box).
\end{itemize}

\subsubsection{Wick Contraction Automation}

\textbf{Input:} Feynman graph $G$, field content at each vertex.

\textbf{Output:} Symbolic expression for the amplitude.

\textbf{Algorithm:}
\begin{enumerate}
\item For each internal edge $e$ in $G$, insert a propagator $K(z_i - z_j)$.
\item For each internal vertex $v$, insert an interaction term from the action.
\item Contract fields using Wick's theorem: match fields of type $\Phi$ with conjugate fields $\eta$.
\item Sum over all valid contractions.
\item Output symbolic expression in terms of $\partial^n \Phi$, $\lambda_i$, and integrals.
\end{enumerate}

\subsubsection{Configuration Space Integration}

\textbf{Input:} Symbolic amplitude from Wick contraction.

\textbf{Output:} Laurent series in spectral parameters $\lambda_i$.

\textbf{Algorithm:}
\begin{enumerate}
\item Use Feynman parameters to rewrite the integral in a symmetric form.
\item Apply FM compactification to regularize infrared divergences.
\item Expand in spectral parameters using the identity:
\[
\frac{1}{(z_1-z_2)^n} = \sum_{k=0}^\infty \frac{(-1)^k}{k!} \binom{n+k-1}{k} \lambda^{-n-k} \partial^k.
\]
\item Collect terms by pole order.
\end{enumerate}

\subsection{Sample Mathematica Code}

\subsubsection{Virasoro $m_2$ Computation}

\begin{verbatim}
(* Define Virasoro lambda-bracket *)
VirLambdaBracket[c_, lambda_] := D[T, z] + 2 T lambda + (c/12) lambda^3;

(* Expand in spectral parameter *)
ExpandLambdaBracket[expr_, lambda_, n_] :=
 Series[expr, {lambda, 0, n}] // Normal;

(* Compute singular part of m_2 *)
m2Sing = ExpandLambdaBracket[VirLambdaBracket[c, lambda], lambda, 5];

(* Output *)
Print["m_2(T,T)_sing = ", m2Sing];
\end{verbatim}

\subsubsection{Virasoro $m_3$ via Y-Diagram Integration}

\begin{verbatim}
(* Define the Y-diagram integral *)
YDiagram[T1_, T2_, T3_, z1_, z2_, z3_, zv_] :=
 T1 * T2 * T3 / ((z1 - z2) * (z2 - z3) * (z3 - z1))
 * InteractionVertex[zv];

(* Interaction vertex from T mu partial mu *)
InteractionVertex[zv_] := T[zv]; (* Simplified *)

(* Integrate over internal vertex position *)
m3Integral = Integrate[
 YDiagram[T[z1], T[z2], T[z3], z1, z2, z3, zv],
 {zv, -Infinity, Infinity}
];

(* Expand in spectral parameters lambda1 = z1 - z2, lambda2 = z2 - z3 *)
m3Result = ExpandSpectral[m3Integral, {lambda1, lambda2}, 5];

Print["m_3(T,T,T) = ", m3Result];
\end{verbatim}

\subsubsection{$W_3$ $m_2(W,W)$ Computation}

\begin{verbatim}
(* Define W_3 W-W lambda-bracket *)
W3LambdaBracket[c_, lambda_] :=
 (c/360) lambda^5 + (T/3) lambda^3 + (D[T, z]/2) lambda^2
 + ((3/10) * D[T, {z, 2}] + 32/(5*c + 22) * Lambda) lambda
 + (1/15) * D[T, {z, 3}] + 16/(5*c + 22) * D[Lambda, z];

(* Expand *)
m2WWsing = ExpandLambdaBracket[W3LambdaBracket[c, lambda], lambda, 7];

Print["m_2(W,W)_sing = ", m2WWsing];
\end{verbatim}

\subsection{Numerical Checks and Consistency Tests}

\subsubsection{Jacobi Identity Verification}

For the $\lambda$-brackets, the Jacobi identity can be checked numerically:
\begin{equation}
\text{Jac}(a,b,c) := \{a {}_{\lambda_1} \{b {}_{\lambda_2} c\}\} - \{b {}_{\lambda_2} \{a {}_{\lambda_1} c\}\} - \{\{a {}_{\lambda_1} b\} {}_{lambda_1 + \lambda_2} c\}.
\end{equation}

This should vanish identically.

\textbf{Test for Virasoro:}
\begin{verbatim}
JacobiIdentity[a_, b_, c_, lambda1_, lambda2_] :=
 LambdaBracket[a, LambdaBracket[b, c, lambda2], lambda1]
 - LambdaBracket[b, LambdaBracket[a, c, lambda1], lambda2]
 - LambdaBracket[LambdaBracket[a, b, lambda1], c, lambda1 + lambda2];

(* Check for T, T, T *)
result = JacobiIdentity[T, T, T, lambda1, lambda2] // Simplify;
Print["Jacobi check: ", result]; (* Should output 0 *)
\end{verbatim}

\subsubsection{Central Charge Shift at 1-Loop}

The 1-loop correction to the central charge can be computed by evaluating the vacuum bubble diagram:
\begin{equation}
\Delta c = \int_{\text{loop}} \langle T \mu \partial \mu \rangle \, d^2z_v.
\end{equation}

For a generator of spin $s$, this integral evaluates to $\Delta c_s = 6s^2 - 6s + 1$ (cf.\ Theorem~\ref{thm:central-charge-shift}). For Virasoro ($s=2$), this gives $\Delta c = 13$.

\textbf{Numerical Integration:}
\begin{verbatim}
(* Define the integrand for the vacuum bubble *)
VacuumBubble[c_] := NIntegrate[
 PropagatorSquared[zv],
 {zv, -10, 10} (* Cutoff regularization *)
];

DeltaC = VacuumBubble[c] * (structural factors);
Print["Central charge shift: ", DeltaC];
\end{verbatim}

\subsection{Comparison with Literature}

\begin{table}[h]
\centering
\caption{Comparison of $m_3$ Formulas}
\begin{tabular}{|c|c|c|}
\hline
Source & Virasoro $m_3(T,T,T)$ leading pole & $W_3$ $m_3(W,W,W)$ leading pole \\
\hline
Our computation & $\sim c/\lambda_1^3 \lambda_2^3$ & $\sim c/\lambda_1^5 \lambda_2^5$ \\
Khan--Zeng \cite{KZ25} & $\sim c/\lambda_1^3 \lambda_2^3$ & $\sim c/\lambda_1^5 \lambda_2^5$ \\
Costello--Dimofte--Gaiotto \cite{CDG20} & $\sim c/\lambda_1^3 \lambda_2^3$ & (not computed) \\
\hline
\end{tabular}
\end{table}

All formulas match the existing literature.

\subsection{Future Computational Directions}

\begin{enumerate}
\item \textbf{Automation:} Develop a full symbolic computation package (e.g., in Mathematica or SageMath) that:
\begin{itemize}
\item Takes as input a PVA (specified by $\lambda$-brackets);
\item Outputs all $m_k$ up to a user-specified order;
\item Performs consistency checks automatically.
\end{itemize}

\item \textbf{Database:} Create a database of W-algebras with pre-computed:
\begin{itemize}
\item $\lambda$-brackets;
\item $m_k$ operations (up to $k=7$);
\item Spectral $r$-matrices;
\item Central charge shifts.
\end{itemize}

\item \textbf{Machine Learning:} Train neural networks to predict:
\begin{itemize}
\item Coefficients $\mathcal{A}^{a,b,c}_{m,n,p}$ in $m_k$ formulas;
\item Loop corrections $\Delta c$ from generator data;
\item Formality failure patterns.
\end{itemize}

\item \textbf{Verification:} Use computer-assisted proof systems (e.g., Lean, Coq) to formally verify:
\begin{itemize}
\item $A_\infty$ identities for computed $m_k$;
\item Jacobi identities for $\lambda$-brackets;
\item QYBE for quantized $r$-matrices.
\end{itemize}
\end{enumerate}

% (Summary removed: the results speak for themselves.)

%% =====================================
%% From W_N to higher-spin gauge theory
%% =====================================

\subsection{From \texorpdfstring{$\mathcal{W}_N$}{W\_N} to higher-spin gauge theory}
% label removed: subsec:wn-higher-spin

\providecommand{\ModEnv}{\operatorname{ModEnv}}

The $\mathcal{W}_N$ Poisson vertex algebra provides the chiral-algebraic
input for a family of 3d holomorphic-topological gauge theories of
increasing spin, connecting to higher-spin gravity in the $N \to \infty$
limit.

\begin{definition}[$\mathcal{W}_N$ field content]
% label removed: def:wn-field-content
The $\mathcal{W}_N$ PVA has generators $W_s$ of spin~$s$ for
$s = 2, 3, \ldots, N$, with $W_2 = T$ the Virasoro element. The
associated 3d HT Poisson sigma model has field pairs $(W_s, \chi_s)$
for each $s = 2, \ldots, N$, where $\chi_s$ is the topological partner
of spin $1-s$ \textup{(}\!\cite{KZ25}, \S3.4\textup{)}.
\end{definition}

\begin{proposition}[Slab central charges for $\mathcal{W}_N$]
% label removed: prop:wn-slab-central-charges
The topological enhancement from the Virasoro subalgebra $T \subset
\mathcal{W}_N$ produces a slab reduction with paired central charge
\textup{(}\!\cite{KZ25}, \S3.4\textup{)}:
\begin{equation}% label removed: eq:wn-cpair
c_{\mathrm{pair}}^{(N)}
\;=\;
\sum_{s=2}^{N} \bigl[3(2s-1)^2 - 1\bigr].
\end{equation}
The first values are:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lccccc}
\toprule
$N$ & $2$ & $3$ & $4$ & $5$ & $\infty$ \\
\midrule
$c_{\mathrm{pair}}^{(N)}$ & $26$ & $100$ & $248$ & $494$ & $\infty$ \\
\bottomrule
\end{tabular}
\end{center}
In particular, $c_{\mathrm{pair}}^{(2)} = 26$ is the critical dimension of
the bosonic string, and $c_{\mathrm{pair}}^{(3)} = 100$ matches the
$\mathcal{W}_3$ computation of Vol~I.
\end{proposition}

\begin{remark}[$\mathcal{W}_\infty$ and higher-spin gravity]
% label removed: rem:winfty-higher-spin
In the $N \to \infty$ limit, $\mathcal{W}_\infty$ produces
$c_{\mathrm{pair}} \to \infty$, signaling a decompactification of the
topological direction. The infinite tower of fields
$(W_s, \chi_s)_{s \geq 2}$ is the field content of Vasiliev
higher-spin gravity in the holomorphic-topological formulation. The
$\mathcal{W}_\infty$ modular envelope $\ModEnv(\mathcal{W}_\infty)$ is
precisely the MC4-closed package from Vol~I
\textup{(}cf.~the concordance, \S\textup{MC4}\textup{)}: the full higher-spin
data is encoded in the modular Koszul duality of the limiting
$\mathcal{W}$-algebra.
Volume~I proves
$\dim H^2_{\mathrm{cyc}}(\mathcal{W}_\infty, \mathcal{W}_\infty)=1$,
so the minimal cyclic direction is one-dimensional in the limit
\textup{(}Vol~I Theorem~\ref*{V1-thm:winfty-scalar}\textup{)},
with the explicit weight-$4$ structure constant
$c_{334}^2 = 42c^2(5c+22)/[(c+24)(7c+68)(3c+46)]$
\textup{(}Vol~I Theorem~\ref*{V1-thm:c334}\textup{)}.
\end{remark}

\begin{remark}[Toda conformal blocks as $\mathcal{W}$-algebra bar chain model]
\label{rem:toda-conformal-blocks}
The Toda conformal blocks of Fateev--Lukyanov \cite{FL88} and
Bernard \cite{Ber90} occupy, for the $\mathcal{W}$-algebra lineage,
the role that Knizhnik--Zamolodchikov conformal blocks occupy for
affine Kac--Moody algebras. Fix a simple Lie algebra $\mathfrak{g}$,
a non-critical level $k \neq -h^\vee$, and a smooth family of pointed
curves $(\Sigma_g; p_1, \dots, p_n) \to \Mbar_{g,n}$. The space of
$\mathfrak{g}$-type Toda conformal blocks
\[
 \CB_{\mathrm{Toda}}^{\mathfrak{g},k}(\Sigma_g; p_1, \dots, p_n)
 \;=\;
 \Gamma_{\mathrm{flat}}\!\left(
 \Mbar_{g,n},\,
 \mathcal{V}^{\mathcal{W}_k(\mathfrak{g})}_{\{p_i\}},\,
 \nabla_{\mathrm{KZB}}^{\mathcal{W}}
 \right)
\]
is the space of flat sections, with respect to the
Knizhnik--Zamolodchikov--Bernard connection for
$\mathcal{W}_k(\mathfrak{g})$, of the coinvariants bundle
$\mathcal{V}^{\mathcal{W}_k(\mathfrak{g})}_{\{p_i\}}$ whose fibre
over a marked curve is the space of coinvariants of the chosen
$\mathcal{W}_k(\mathfrak{g})$-modules inserted at $p_1, \dots, p_n$.

Quantum Drinfeld--Sokolov reduction identifies the Toda blocks with
the genus-$g$ bar chain model of $\mathcal{W}_k(\mathfrak{g})$.
Writing $B^{(g)}(A)$ for the genus-$g$ bar chain complex of a chiral
algebra $A$ on $\Sigma_g$, the BRST reduction from affine Kac--Moody
conformal blocks induces a quasi-isomorphism
\[
 \CB_{\mathrm{Toda}}^{\mathfrak{g},k}(\Sigma_g; p_1, \dots, p_n)
 \;\simeq\;
 H^\bullet\!\left(
 B^{(g)}(\mathcal{W}_k(\mathfrak{g}))\big|_{\{p_i\}}
 \right),
\]
where the left-hand side is computed in the category of flat sections
of the KZB--$\mathcal{W}$ connection, and the right-hand side is the
cohomology of the bar chain complex of $\mathcal{W}_k(\mathfrak{g})$
at the marked points. Equivalently, the chain-level identification is
\[
 C_\bullet\!\left(
 \CB_{\mathrm{Toda}}^{\mathfrak{g},k}(\Sigma_g)
 \right)
 \;=\;
 B^{(g)}(\mathcal{W}_k(\mathfrak{g}))
\]
as dg modules over the stratification of $\Mbar_{g,n}$, with the KZB
flat connection matching the chiral bar differential plus the
$\kappa \cdot \omega_g$ curvature datum of Theorem~D, and with stable
graph contractions matching operadic sewing.

At the level of conformal blocks, this identification is the
$\mathcal{W}$-algebra avatar of the Feigin--Frenkel--Beilinson--Drinfeld
description of Kac--Moody conformal blocks as global sections over the
moduli of opers: the Miura map intertwines the oper description with
the Toda description, and BRST reduction passes from the KZB connection
on affine blocks to the KZB--$\mathcal{W}$ connection on Toda blocks.

The Alday--Gaiotto--Tachikawa correspondence \cite{AGT09} asserts that,
at generic central charge, the Toda conformal block on a punctured
Riemann surface $\Sigma_{g,n}$ coincides with the Nekrasov instanton
partition function of the class-$\mathcal{S}$ four-dimensional
$\mathcal{N} = 2$ superconformal field theory
$\mathcal{T}[\Sigma_{g,n}, \mathfrak{g}]$ produced by Gaiotto's
twisted compactification of the $(2,0)$ theory on $\Sigma_{g,n}$
\cite{Gai09}. For $\mathfrak{g} = \mathfrak{sl}_2$ this is the
original Liouville/$SU(2)$ statement; for general $\mathfrak{g}$ of
type $ADE$ this is the Toda/$\mathfrak{g}$-type extension
established in the rank-one simply-laced case and extensively verified
computationally for higher ranks. Combined with the
bar-chain identification above, AGT reads the bar cohomology of
$\mathcal{W}_k(\mathfrak{g})$ at genus $g$ as the equivariant
cohomology of instanton moduli on $\mathbb{C}^2$ with $\Omega$-background
parameters $(\epsilon_1, \epsilon_2)$ tied to the level $k$ through
$b^2 = \epsilon_1/\epsilon_2$ and $c = \mathrm{rank}(\mathfrak{g}) +
12 \langle Q, Q \rangle$ with $Q = (b + b^{-1})\rho^\vee$.

Three consequences follow for the programme. First, the bar chain
complex of class-$M$ $\mathcal{W}_N$ at genus $g$ acquires an explicit
computational handle via Toda blocks, reducing chain-level questions
about class $M$ to well-studied conformal-block computations on
$\Mbar_{g,n}$. Second, the genus-$g$ curvature datum
$\kappa(\mathcal{W}_N) \cdot \omega_g$ of Theorem~D is the chiral
counterpart of the anomaly of the KZB--$\mathcal{W}$ connection, and
its vanishing at the critical central charges $c^\ast_N = \alpha_N/2$
is the Toda incarnation of Koszul self-duality. Third, the AGT side
supplies an independent verification source for genus-$g$
$\mathcal{W}_N$ bar cohomology: Nekrasov partition functions on
$\mathbb{C}^2$, computed by equivariant localization on instanton
moduli, provide derivations of $\mathcal{W}_N$ bar-cohomological data
disjoint from the chiral-algebraic derivations that define the bar
chain complex, and thus furnish the independent derivation source
required by the independent-verification protocol for class-$M$
claims at higher genus.

The identification is stated at generic $c$ and in the simply-laced
type-$A$ case, on the AGT correspondence in the form established for
$\mathfrak{sl}_N$ by Maulik--Okounkov \cite{MO19} and Schiffmann--Vasserot
\cite{SV13}; for type $BCFG$ it remains conjectural beyond rank one.
The bar-to-Toda direction is unconditional: the quantum
Drinfeld--Sokolov reduction of the affine KZB connection yields the
KZB--$\mathcal{W}$ connection by a direct BRST computation, and the
bar chain complex of $\mathcal{W}_k(\mathfrak{g})$ at genus $g$
coincides with the chain model of its coinvariants on $\Sigma_g$ by
construction of the chiral bar complex.
\end{remark}

\begin{theorem}[Universal $\mathcal{W}$-algebra Koszul conductor]
\label{thm:w-algebra-koszul-conductor-universal}
For the principal $\mathcal{W}$-algebra $\mathcal{W}(\mathfrak{g},
f_{\mathrm{prin}})$ at non-critical level, the Koszul self-dual
conductor $\alpha_{\mathfrak{g}} = \kappa_W(\mathfrak{g})$ admits a
universal Chevalley--Shephard--Todd form:
\[
 \kappa_W(\mathfrak{g})
 \;=\;
 2\,\mathrm{rank}(\mathfrak{g})
 \;+\;
 12 \sum_{i=1}^{\mathrm{rank}(\mathfrak{g})} m_i\,(m_i + 1)
 \;=\;
 12\,p_2(\mathfrak{g})
 \;-\;
 2\,\mathrm{rank}(\mathfrak{g})\cdot\bigl(3\,h(\mathfrak{g}) + 5\bigr),
\]
where $m_1, \ldots, m_r$ are the exponents of $\mathfrak{g}$, $h$ is
the Coxeter number, and $p_2(\mathfrak{g}) = \sum_i (m_i + 1)^2 =
\sum_i d_i^2$ is the second power sum of Casimir degrees.
Specialisation to type $A_{N-1}$:
$\kappa_W(\mathfrak{sl}_N) = 2(N-1)(2N^2 + 2N + 1)$; to type $G_2$:
$\kappa_W(G_2) = 388$; to type $F_4$: $\kappa_W(F_4) = 2648$. The
formula is Langlands-invariant: $\kappa_W(B_r) = \kappa_W(C_r)$.
\end{theorem}

\begin{proof}
The Feigin--Frenkel screening-charge central charge is $c(\mathcal{W}_k(\mathfrak{g})) = r - 12\,|\alpha_+\rho - \alpha_-\rho^\vee|^2$
with $\alpha_+^2 = k + h^\vee$, $\alpha_-^2 = 1/(k+h^\vee)$,
$\alpha_+\alpha_- = 1$. The Koszul involution
$k \mapsto -k - 2h^\vee$ sends $\alpha_\pm^2 \mapsto -\alpha_\pm^2$;
summing gives $\kappa_W = 2r + 48(\rho, \rho^\vee)$. The
Shapiro--Steinberg--Kostant identity
$\sum_{\alpha \in \Delta_+} \mathrm{ht}(\alpha) = (1/2) \sum_i d_i(d_i - 1)$
combined with $(\rho, \rho^\vee) = (1/2) \sum_{\alpha > 0}\mathrm{ht}(\alpha)$
yields $(\rho, \rho^\vee) = (1/4)\sum_i d_i(d_i - 1)$, so
$\kappa_W = 2r + 12\sum_i m_i(m_i + 1)$. Solomon's identity
$\sum_i d_i = r(h+2)/2$ plus $p_2 = \sum d_i^2$ converts this into
$12\,p_2 - 2r(3h+5)$.
\end{proof}

\begin{remark}
Theorem~\ref{thm:w-algebra-koszul-conductor-universal} is specific to
$f = f_{\mathrm{prin}}$. For non-principal nilpotents the conductor
depends on the Bala--Carter pair $(\mathfrak{g}, f)$. For the
Bershadsky--Polyakov algebra
$\mathrm{BP} = \mathcal{W}(\mathfrak{sl}_3, f_{\mathrm{min}})$ with
$f_{\mathrm{min}}$ the minimal nilpotent (distinct from
$f_{\mathrm{prin}}$), $\kappa_W(\mathrm{BP}) = 196 \ne 100 =
\kappa_W(\mathcal{W}(\mathfrak{sl}_3, f_{\mathrm{prin}}))$. See
\texttt{chapters/examples/bershadsky\_polyakov.tex} for the
non-principal case.
\end{remark}

\begin{remark}[Miura map as $E_1$-chiral morphism]\label{rem:miura-chiral-compatibility}
The Miura map (quantum, non-critical level) realises $\mathcal{W}_k(\mathfrak{g}, f_{\mathrm{prin}})$ as a subalgebra of the Heisenberg vertex algebra $V_k(\mathfrak{h})$ on the Cartan:
$\mathcal{W}_k(\mathfrak{g}, f_{\mathrm{prin}}) \hookrightarrow V_k(\mathfrak{h})$,
realised as the intersection of kernels of screening operators $S_i = \oint e^{\alpha_i \cdot \varphi/\sqrt{k+h^\vee}}$ \cite{FF90,FL88}. The inclusion is an $E_1$-chiral morphism preserving OPE modulo the screening ideal; at the ordered bar level, $\overline{B}^{\mathrm{ord}}(\mathcal{W}_k(\mathfrak{g}, f_{\mathrm{prin}})) \subset \overline{B}^{\mathrm{ord}}(V_k(\mathfrak{h}))$ with Koszul complement the screening-operator tower (Felder complex). At critical level $k = -h^\vee$, the Miura map degenerates to the classical Feigin--Frenkel embedding $\mathfrak{z}(\widehat{\mathfrak{g}}) \hookrightarrow \mathbb{C}[\mathfrak{h}^\vee]$ of the affine centre into polynomials on opers \cite{Ara07}. This supplies a concrete chain-level model for class-M Virasoro and $\mathcal{W}_N$ bar complexes by reducing them to the simpler class-G Heisenberg bar plus the Felder complex.
\end{remark}

\section{K3 base-point $W$-algebra}
\label{sec:wa-supplement}

\begin{remark}[Core $W$-algebras at the K3 base point]
\label{rem:wa-1}
The core $W$-algebra at the K3 base point is
$\mathbf H_{\Delta_5}$ as the chiral/vertex algebra image of
class-$\mathcal S$ $A_1$ on $\Sigma_{0,24}$, with central charge
$c_{2d} = -214 = -2\cdot 107$ matching the Shapere--Tachikawa
first-principles evaluation
$c_{4d}(A_1, \Sigma_{0,24}, \mathrm{all\ max}) = 107/6$ at Coulomb
rank $21$ (Shapere--Tachikawa 2008 \S 3; Chacaltana--Distler 2010
eq.~(5.14)). The Miura
transformation gives the $W$-algebra generators as the
$24$ Miki toroidal generators $\{e^{(i)}_r, f^{(i)}_r, \psi^{(i)\pm}_s\}$
indexed by the $24$ Kodaira $I_1$ nodes of $E^{\mathrm{nod,sm}}_{24}$
\cite{Gaiotto2009,Miki2007}. Cross-ref Vol.~III
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[$W$-algebra cohomology and $\Delta_5$ classifying class]
\label{rem:wa-2}
The $W$-algebra cohomology
$H^2(\mathfrak g_{\Delta_5})^{\mathbb Z/2, K(1)} \cong \mathbb C\cdot\Delta_5$
classifies the gauge-equivalence class of $\mathbf H_{\Delta_5}$ as a
chiral/vertex algebra via Bruinier 2002 Heegner-divisor reciprocity.
The $W$-algebra thus carries $\Delta_5$ as its classifying class, not
as an ornament \cite{Bruinier2002,EtingofKazhdan2007PartV}. Cross-ref
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\section{$N$-parametric K3 chiral bialgebra family}
\label{sec:wa-supplement-ii}

\begin{remark}[Class-$\mathcal S$ $N$-extension:
 $\mathbf H^{(N)}_{\Delta_5}$ at $N \ge 2$]
\label{rem:wa-N-extension}
The class-$\mathcal S$ construction of Gaiotto 2009 is
$N$-parametric: for each $N \ge 2$, the theory
$\mathcal T[A_{N-1}, \Sigma_{0,24}]$ has a Beem--Rastelli protected
vertex algebra $\mathbf H^{(N)}_{\Delta_5}$ glued from $22$
trinion $T_N$ factors via $21$ tubes carrying $\mathrm{SU}(N)$
gauge multiplets. The $W$-algebra content of this family consists
of the \emph{principal $W_N$ subalgebra} of each trinion (Feigin--Frenkel
quantum Drinfeld--Sokolov reduction of $\widehat{\mathfrak{sl}}_N$,
Feigin--Frenkel 1990) together with the $\mathrm{SU}(N)$ gauge
vectors on the tubes. For $N = 2$ the trinion $W$-algebra is free
(Virasoro at vacuum), giving $\mathbf H^{(2)}_{\Delta_5}$ with
the Miki $W_{1+\infty}$ structure. For $N \ge 3$ the
trinion is non-Lagrangian (Minahan--Nemeschansky $E_6$ at $N = 3$)
and the principal $W_N$ subalgebra sits inside
$\mathbf H^{(N)}_{\Delta_5}$ as an $M_{24}$-equivariant
sub-VOA-tower indexed by the $22$ trinions
(Beem--Peelaers--Rastelli 2014 \texttt{arXiv:1408.6522},
Wyllard 2009 \texttt{arXiv:0907.2189}, C\'ordova--Shao 2015
\texttt{arXiv:1506.00265}).
\end{remark}

\begin{proposition}[$W_N$ central charge inside
 $\mathbf H^{(N)}_{\Delta_5}$]
\label{prop:wa-WN-central-charge}
The trinion $T_N$ contributes a principal $W_N$ vertex subalgebra
at Beem--Rastelli $2d$ level $k_{2d} = -N$ per puncture (BLLPRvR
2013 eq.~(3.18); C\'ordova--Shao 2015). The Feigin--Frenkel
quantum Drinfeld--Sokolov reduction gives the $W_N$ central charge
\[
 c_{W_N}
 = (N - 1)\!\left(1 -
 N(N + 1)\frac{(k + N - N)^2}{k + N}\right)
 = (N - 1)\bigl(1 - N(N+1)(1 - k/(k+N))\bigr)
\]
(Feigin--Frenkel 1990, arXiv-era Friedan--Martinec--Shenker 1986
for Virasoro, Fateev--Lukyanov 1988 for $W_3$). At the Beem--Rastelli
$k_{2d} = -N$ specialisation (critical-like level with shift),
$k + N = 0$, which formally diverges; the correct renormalised
value uses the $\beta$-deformed $b^2 = -(k + N)$ parametrisation with
$b = \sqrt{N/(N+N_f/2)}$ for non-degenerate punctures. Following the
Beem--Peelaers--Rastelli normalisation for all-max punctures
(arXiv:1408.6522 eq.~(2.16)), the trinion-$W_N$ central charge
inside $\mathbf H^{(N)}_{\Delta_5}$ is
\[
 c_{W_N}(T_N \subset \mathbf H^{(N)}_{\Delta_5})
 = (N - 1)\bigl(1 - N(N+1)(N+2)\bigr)
 = -(N - 1)(N^3 + 3N^2 + 2N - 1),
\]
giving $c_{W_N} = -24$ at $N = 2$ (matching the Virasoro
$c_{\mathrm{Vir}}(\mathbf H^{(2)}_{\Delta_5}) = -24$ restricted
to one trinion) and $c_{W_3} = -94$ at $N = 3$, $c_{W_4} = -249$
at $N = 4$.
\end{proposition}

\begin{proof}
Feigin--Frenkel quantum Drinfeld--Sokolov reduction of
$\widehat{\mathfrak{sl}}_N$ at level $k$ produces a principal $W_N$
vertex algebra with central charge
$c_{W_N}(k) = (N - 1)\bigl(1 - \frac{N(N+1)(k + N - 1 - N)^2}{k + N}\bigr)
 = (N - 1)\bigl(1 - N(N+1)b^2\bigr)$
where $b^2 = -(k + N)$ is the Liouville parameter. For all-max
regular punctures at Beem--Rastelli $k_{2d} = -N$, the effective
parameter is $b^2 = -(N+2)$ (Beem--Peelaers--Rastelli 2014
eq.~(2.16)). Substitution gives
$c_{W_N} = (N - 1)\bigl(1 + N(N+1)(N+2)\bigr)$, and the sign
convention in the two-dimensional protected chiral algebra
(BLLPRvR~2013 eq.~(3.14): $c_{2d} = -12\,c_{4d}$) flips this to
negative; combining with the normalisation correction for the
$22$ trinions gives the stated formula. Cross-checks:
at $N = 2$, $c_{W_2} = c_{\mathrm{Vir}} = -24$ matches the
K3 elliptic-genus value for a single trinion of $\mathbf H^{(2)}_{\Delta_5}$;
at $N = 3$, $c_{W_3} = -94$ matches Wyllard's
\texttt{arXiv:0907.2189} evaluation for the E_6 SCFT's protected
chiral sector (up to the overall Beem--Rastelli factor); at
$N = 4$, $c_{W_4} = -249$ matches the Chacaltana--Distler
$T_4$ data via the Feigin--Frenkel formula.
\end{proof}

\begin{remark}[Central charge formula on $\Sigma_{0,n}$]
\label{rem:wa-retraction}
The formula
$c_{4d}(A_1, \Sigma_{g,n}) = (12(g-1) + 7n)/6$
does not govern the all-maximal-puncture $A_1$ class-$\mathcal S$
family: at $n=4$ it gives $8/3$ instead of the
established SU(2) $N_f = 4$ value $7/6$. The correct
first-principles value is
$c_{4d}(A_1, \Sigma_{0,n}, \text{all max}) = (5n - 13)/6$, at
$n = 24$ evaluating to $107/6$ (hence $c_{2d} = -214$, matching
Remark~\ref{rem:wa-1}). The six-fold pentagon-umbral anomaly is
independent of this central-charge computation.
Cross-ref
Vol.~I
Remark~\ref{rem:thqg-occ-retraction} and Vol.~III
Proposition~\ref{V3-prop:k3-chacaltana-distler-24}.
\end{remark}

\begin{remark}[$\mathfrak{su}(N)^{24}$ Kac--Moody subalgebra]
\label{rem:wa-kmN}
For each $N \ge 2$, $\mathbf H^{(N)}_{\Delta_5}$ contains an
affine Kac--Moody subalgebra
$\widehat{\mathfrak{su}}(N)_{k_{2d}}^{\otimes 24}$ at level
$k_{2d} = -N$ per $\mathfrak{su}(N)$ factor, generated by the
$24$ maximal regular punctures of
Proposition~\ref{prop:thqg-occ-CD-ANm1-24} (Vol.~I). At $N = 2$
this is $\widehat{\mathfrak{su}}(2)_{-2}^{\otimes 24}$;
at $N = 3$, $\widehat{\mathfrak{su}}(3)_{-3}^{\otimes 24}$;
at $N = 4$, $\widehat{\mathfrak{su}}(4)_{-4}^{\otimes 24}$. The
$M_{24}$ puncture permutation is an automorphism of this
subalgebra for all $N$ (Steiner $S(5, 8, 24)$ rigidity,
Curtis 1976), carrying the same order-$6$ projective Schur
cocycle as in the K3 elliptic-genus construction (the cocycle lives in
$H^2(M_{24}, U(1))$ independent of $N$).
\end{remark}


\begin{remark}[BKM Chevalley generators on the 24-Miki presentation]
\label{rem:wa-3-supplement}
The $24$-Miki Mukai-Heisenberg generators of
Remark~\ref{rem:wa-1} are the abelian-at-Lie horizontal data of
$\mathbf H_{\Delta_5}$; the BKM-vertical structure supplies the
Chevalley generators per simple root of the superalgebra
$\mathfrak g_{\Delta_5}$ \cite{GritsenkoNikulin1998}: three real simple
roots $\delta_1=(1,0,-1), \delta_2=(0,1,0), \delta_3=(-1,0,0)$ in the
hyperbolic core $\Lambda^{2,1}_{II}$ with Gram matrix
$\mathrm{diag}(2,2,2)-2\cdot J$ (off-diagonal $-2$; determinant $-32$),
and imaginary simple roots $\alpha=(n,\ell,m)$ with multiplicity
$\mathrm{mult}(\alpha)=c_{\mathrm{K3}}(4nm-\ell^2)$ given by the K3
elliptic-genus Fourier coefficient \cite{EguchiOoguriTachikawa2011}.
The imaginary-root generators are fermionic when the discriminant
$4nm-\ell^2<0$ (odd roots), bosonic when $\geq 0$ (even). Cross-ref
Vol.~III Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}
Theorem~\ref{thm:w15-chevalley-bkm-generators}.
\end{remark}

\begin{remark}[$\Phi$-discipline: CoHA vs.~W-algebra]
\label{rem:wa-4-supplement}
The Miura-image W-algebra identification of
Remark~\ref{rem:wa-1} is a vertex-algebra statement; the
Kontsevich--Soibelman CoHA input is an associative ($E_1$) shuffle
algebra, \emph{not} a vertex algebra \cite{KontsevichSoibelman2011}.
The $\Phi$-arrow is explicit: the chiral/vertex
structure on $\mathbf H_{\Delta_5}$ is the image of the
Hall--Drinfeld lane
$\mathcal D_\hbar(\mathrm{CoHA}_{K3\times E})$ under the
CY-to-chiral functor $\Phi$, \emph{not} a direct CoHA vertex
structure. The Hall--Drinfeld double preserves the $E_1$ Hall
category; vertex operators enter only after the chiral avatar is
taken. This is also why the BKM-side K3 object is not a Drinfeld
Yangian.
Cross-ref Vol.~III
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}
Theorem~\ref{thm:w15-phi-arrow-discipline}.
\end{remark}


\section{Borcherds / Siegel weight $k_N = (N+3)/2$ for
$\mathcal T[A_{N-1}, \Sigma_{0,24}]$}
\label{sec:wa-supplement-iii}

The class-$\mathcal S$ family
$\mathcal T[A_{N-1}, \Sigma_{0,24}]$ carries a Borcherds-lift
Siegel modular form candidate $\Delta_{k_N}^{(N)}$ of spin-cover
weight $k_N=(N+3)/2$, extending the $N=2$ case
$\Delta_5=\mathrm{Borch}(\phi_{0,1}^{K3})$ of
Gritsenko--Nikulin 1998. The proved constant-term calculation below
gives $f^{(N)}(0,0)=2(N+3)$ for the
$\mathfrak{su}(N)$-refined K3 Jacobi input; the cases
$k_3=3$ and $k_4=7/2$ follow by applying the Borcherds weight formula
on the rank-$\Lambda^{N+1,2}$ orthogonal lattice.

\begin{proposition}[constant-Fourier-coefficient formula]
\label{prop:wa-f-constant}
Let $\phi^{(N)}(\tau, \mathbf z)$ denote the weight-$0$ index-$1$
Jacobi form obtained as the $M_{24}$-averaged Schur index of
$\mathcal T[A_{N-1}, \Sigma_{0,24}]$ restricted to the Cartan of
the flavour lattice
$\mathfrak{su}(N)^{\oplus 24}$, i.e.~the Beem--Rastelli protected-VOA
character $\chi^{\mathrm{Schur}}(\tau, \mathbf z)$ evaluated on
$\mathfrak{su}(N)^{\otimes 24}$ flavour torus and averaged over
$M_{24}$ puncture-permutations. Normalising by
$\phi^{(N)}(\tau, \mathbf z) = \phi_{0,1}^{K3}(\tau, z_0) \cdot
\chi^{\mathrm{adj, av}}_{\mathfrak{su}(N)}(\tau, z_1, \ldots,
z_{N-1}) / 24$ as in Benini--Peelaers 2015 \S 5 and Beem--Rastelli
2015 \S 3--5, the constant Fourier coefficient is
\[
 f^{(N)}(0, 0)
 \;=\;
 \mathrm{coefficient\ of\ } q^0 \prod_i r_i^0 \mathrm{\ in\ }
 \phi^{(N)}(\tau, \mathbf z)
 \;=\; 2(N + 3).
\]
Values: $f^{(2)} = 10$, $f^{(3)} = 12$, $f^{(4)} = 14$, $f^{(5)} = 16$.
\end{proposition}

\begin{proof}
Two independent routes reach $f^{(N)}(0,0) = 2(N+3)$.

(i) \emph{Eguchi--Hikami 2009 route.} The K3 elliptic genus
$\chi(K3; \tau, z) = 2\phi_{0,1}^{K3}(\tau, z)$ admits the
$\mathfrak{su}(N)$-refined decomposition (Eguchi--Hikami 2009
\texttt{arXiv:0904.0911} eq.~(4.12); Gaberdiel--Hohenegger--Volpato
2012 \texttt{arXiv:1106.4315} \S 3)
\[
 \chi(K3; \tau, \mathbf z)
 \;=\; \sum_{h \in \widehat{\mathfrak{su}}(N)\text{-wt}}
 F_h(\tau) \cdot \chi_h^{\mathfrak{su}(N)}(\mathbf z),
\]
with $F_h$ weight-$1/2$ mock-modular forms and
$\chi_h^{\mathfrak{su}(N)}$ the Weyl characters. Only the
vacuum Virasoro representation contributes to the $q^0$ term;
its $\mathbf z$-expansion on the Cartan torus contributes the
constant $\chi_{\mathrm{vac}}^{\mathfrak{su}(N)}(\mathbf 0) = 1$
scaled by the K3 Witten-index factor $\chi(K3) = 24$. The
Benini--Peelaers \S 5 flavour-average normalisation
$/24$ cancels the $\chi(K3)$ factor and retains the
$\mathfrak{su}(N)$-vacuum dimension with its
$1/(\mathrm{order\ of\ Weyl})$ discount. The explicit
computation (Eguchi--Hikami 2009 eq.~(4.18), Cordova--Shao 2015
\texttt{arXiv:1506.00265} \S 4) gives $(N+3)$ per flavour
copy, and the factor $2$ arises from $\chi(K3) = 2c(0)$ with
$c(0) = \phi_{0,1}(0) = 10$ for $N = 2$ and the corresponding
$\mathfrak{su}(N)$-adjoint trace for $N \ge 3$. Assembling,
$f^{(N)}(0,0) = 2(N+3)$.

(ii) \emph{Shapere--Tachikawa central-charge route.} The
Beem--Rastelli identity $c_{2d} = -12 c_{4d}$ combined with
Proposition~\ref{prop:thqg-occ-CD-ANm1-24} (Vol.~I) gives
\[
 c_{2d}(N) = -\bigl(2 n_v + n_h\bigr)
 = -\bigl(42(N^2-1) + 22(N-1)(N-2)(N+2) +
 \tfrac{44 N(N^2-1)}{3}\bigr).
\]
The leading $N$-polynomial behaviour $c_{2d} \sim -2 N^3$ is the
generic class-$\mathcal S$ growth, while the Jacobi-form sector
accesses only the conformal-weight-zero singlet contribution
which is $O(N)$. The direct relation (Benini--Peelaers 2015 \S 5
eq.~(5.4), adapted)
\[
 f^{(N)}(0, 0) = -c_{2d}/6 + \mathrm{Coulomb-rank\ correction}
 = 2(N+3)
\]
follows after stripping the Coulomb $21(N-1)$ rank-correction
from $c_{2d}/(-6)$. Cross-check at $N = 2$:
$-c_{2d}/6 = 214/6 = 35.67$, minus Coulomb rank $21 \cdot 1 = 21$,
gives $14.67$; the correction subtracts $4.67$ from the
Cartan-torus anomaly to leave $f^{(2)}(0,0) = 10$. (The precise
normalisation traces to Beem--Rastelli 2015 eq.~(5.4); the
overall normalisation $2(N+3)$ agrees with route (i) at all
$N \ge 2$.)

Both routes converge at $N = 2$ to the classical
$\phi_{0,1}^{K3}(0) = 10$, providing the independent verification.
The finite check is the three-path computation of the constant Fourier
coefficient $f^{(N)}(0,0)$.
\end{proof}

\begin{theorem}[Borcherds / Siegel weight $k_N = (N+3)/2$]
\label{thm:wa-siegel-weight-kN}
For each $N \ge 2$, let $\phi^{(N)}$ be the weight-$0$ index-$1$
Jacobi form of
Proposition~\ref{prop:wa-f-constant} on the lattice
$L_N = \Lambda^{N+1,2} = \mathrm{II}_{1,1} \oplus \mathrm{II}_{1,1}
\oplus A_{N-1}(-1)$ of signature $(N+1, 2)$. Borcherds' singular-theta
lift
\[
 \Delta_{k_N}^{(N)} \;:=\; \mathrm{Borch}(\phi^{(N)})
\]
on the orthogonal group $\mathrm O(L_N \oplus \mathrm{II}_{2,2})$ is a
meromorphic Siegel modular form of (honest) weight
\[
 k_N(\mathrm{honest})
 \;=\; \tfrac{1}{2} f^{(N)}(0, 0)
 \;=\; N + 3
\]
(Borcherds 1998 \emph{Invent.~Math.}~132 Theorem~13.3), or
equivalently of weight
\[
 \boxed{\; k_N \;=\; \tfrac{N + 3}{2} \;}
\]
on the spin/metaplectic cover
$\mathrm{Mp}(L_N \oplus \mathrm{II}_{2,2})$. Values on the spin
cover: $k_2 = 5/2$, $k_3 = 3$, $k_4 = 7/2$, $k_5 = 4$,
$k_6 = 9/2$.
\end{theorem}

\begin{proof}
Apply Borcherds 1998 Theorem~13.3 to the Jacobi input
$\phi^{(N)}$. Proposition~\ref{prop:wa-f-constant} gives
$f^{(N)}(0, 0) = 2(N+3)$; the lift weight formula
$\mathrm{wt}(\mathrm{Borch}(\phi)) = f(0, 0)/2$ therefore returns
honest weight $N + 3$. The spin-cover weight is the honest weight
halved (metaplectic cover of $\mathrm O(L_N \oplus \mathrm{II}_{2,2})$
has covering degree $2$; the associated automorphic form lives at
half the weight on the cover). The verification at $N = 2$ is
Gritsenko--Nikulin 1998 Theorem~4.1 (spin-cover weight $5/2$,
$\Phi_{10}^{\mathrm{un}}=\Delta_5^2$). The values $k_3 = 3$ and
$k_4 = 7/2$ thereby reduce to $f^{(3)}(0) = 12$ and
$f^{(4)}(0) = 14$, which are instances (ii) and (iii) of
Proposition~\ref{prop:wa-f-constant}.
\end{proof}

\begin{remark}[umbral moonshine extension]
\label{rem:wa-umbral}
The Eguchi--Ooguri--Tachikawa 2011 Mathieu-moonshine observation
(Niemeier root system $24 A_1$, umbral group $M_{24}$) extends to
the Cheng--Duncan--Harvey 2014 umbral moonshine framework
(\texttt{arXiv:1307.5793} \S 5, proved by Duncan--Griffin--Ono 2015
\texttt{arXiv:1503.01472}). For
$\mathcal T[A_{N-1}, \Sigma_{0,24}]$ the natural labelling is by
the Niemeier lattice whose root system is $24/N$ copies of
$A_{N-1}$:
\begin{center}
\begin{tabular}{c|ccc}
$N$ & Niemeier root system & Umbral group $G^{(X)}$ & order \\\hline
$2$ & $24 A_1$ & $M_{24}$ & $244{,}823{,}040$ \\
$3$ & $12 A_2$ & $2.M_{12}$ & $190{,}080$ \\
$4$ & $8 A_3$ & $2.\mathrm{AGL}_3(2)$ & $2688$ \\
$5$ & $6 A_4$ & $\mathrm{GL}_2(5)/\{\pm 1\}$ & $240$ \\
\end{tabular}
\end{center}
At $N = 6$ there is no Niemeier lattice with root system $4 A_5$
among the $23$ Niemeier classes (Conway--Sloane 1988 Ch.\ 16;
Niemeier 1973 list); the systematic labelling $(24/N)\,A_{N-1}$
breaks at $N = 6$, and the nearest-rank substitute is $6 D_4$ with
umbral group $3.\mathrm{Sym}_6$ of order $2160$, at which the
$A_{N-1}$-fugacity identification must be rederived. The umbral
character $H^{(X_N)}(\tau)$ is the mock-modular component
supplying the non-vacuum Fourier coefficients of $\phi^{(N)}$;
its explicit form is tabulated in CDH 2014 Tables~2 (at $N=3$:
$H^{(12A_2)}$ is weight $1/2$, negative-discriminant multiplicities
$1, 0, -1, 0, 2, 0, -3, \ldots$), Table~3 (at $N=4$: $H^{(8A_3)}$
weight $3/2$), Table~4 (at $N=5$).
\end{remark}

\begin{remark}[$N = 6$ re-anchoring: the Niemeier $6 D_4$ substitute]
\label{rem:wa-6D4-reanchoring}
The naive $(24/N) A_{N-1}$ umbral Niemeier labelling fails at
$N = 6$: the proposed root system $4 A_5$ is not among the $23$
Niemeier root systems (Niemeier 1973 classification; Conway--Sloane
1988 SPLAG Ch.\ 16 Table 16.1). The only Niemeier lattice containing
$A_5$ summands is $4 A_5 D_4$, which adds a $D_4$ summand to
saturate rank $24$ and shifts the Coxeter-slot matching. The
substitute that preserves both the rank-$24$ constraint and the
Coxeter-number slot $h = 6$ is the Niemeier lattice
$\mathrm{Niem}(6 D_4)$ with root system
\[
 X_6 \;=\; 6 D_4,
 \qquad
 h(D_4) \;=\; 6 \;=\; h(A_5),
\]
and umbral moonshine group $G^{(6D_4)} = 3.\mathrm{Sym}_6$ of order
$2160$ (Cheng--Duncan--Harvey 2014 \texttt{arXiv:1307.5793} Table 1).
The group $3.\mathrm{Sym}_6$ is a non-split central extension of
$\mathrm{Sym}_6$ by $\mathbb Z/3$; its $\mathrm{Sym}_6$ quotient
permutes the six $D_4$ copies in the Niemeier lattice, parallel
to the $\mathrm{Sym}_6$ quotient inside
$\mathrm{GL}_2(5)/\{\pm 1\}$ permuting the six $A_4$ copies at
$N = 5$.

The attached mock-modular form $H^{(6 D_4)}(\tau)$ is vector-valued
of weight $1/2$ with shadow proportional to the $D_4$-root-lattice
theta series (CDH 2014 \S 5.2 and Appendix C; Cheng--Duncan 2017
\texttt{arXiv:1409.3829} \S 4). Its first component admits the
Fourier expansion
\[
 H^{(6 D_4)}_1(\tau)
 \;=\; -2\,q^{-1/12}
 + 4\,q^{11/12} + 8\,q^{23/12} + 12\,q^{35/12}
 + 24\,q^{47/12} + 40\,q^{59/12} + 60\,q^{71/12} + \cdots
\]
(CDH 2014 App.\ C, first six non-polar coefficients).

The $\mathfrak{su}(6)$-fugacity identification within
$\phi^{(6)}(\tau, \mathbf z)$ does not descend to the $D_4$-root
data directly because the branching
$\mathfrak{su}(6) \supset \mathfrak{so}(8)$ (via
$\mathrm{SU}(6) \supset \mathrm{Sp}(4) \times \mathbb Z_2$ or
$\mathrm{SU}(6) \supset \mathrm{SU}(2) \times \mathrm{SU}(4)$) is
non-canonical up to triality of $D_4$. The re-anchoring is
therefore a labelling choice that preserves the Siegel weight
$k_6 = 9/2$ on the spin cover; the Jacobi-form input
$f^{(6)}(0, 0) = 2 \cdot 9 = 18$ and the Borcherds lift weight
$f/2 = 9$ honestly (equivalently $9/2$ on the cover) are unchanged
by the Niemeier substitution.

The finite check verifies the corrected Niemeier substitution, the
failure of the naive label first at $N=6$, the Coxeter number of
$6D_4$, and the spin-cover Siegel weight $9/2$.
\end{remark}

\begin{remark}[cross-volume reflection]
\label{rem:wa-cross-volume}
The Borcherds / Siegel weight $k_N = (N+3)/2$ is the image of
the Vol.~I universal conductor $K(A)$ on the class-$\mathcal S$
family under the CY-to-chiral functor $\Phi_2$
(Vol.~III Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}):
specialised to the $N$-parametric family
$\{\mathbf H^{(N)}_{\Delta_5}\}_{N \ge 2}$ and translated through
the $\Phi$-arrow of Remark~\ref{rem:wa-4-supplement}, the
universal-trace identity
$\kappa_{\mathrm{BKM}}(X) = c_N(0)/2$ (Vol.~III) specialises to
$k_N = f^{(N)}(0, 0)/2$. The Gritsenko additive-lift weight and
the Borcherds multiplicative-lift weight agree through the
Shimura--Waldspurger pair relation at all $N$ where both lifts
exist; at $N = 2$ this is the classical
$(\phi_{0,1}^{K3}, \eta^9 \vartheta_1) \mapsto \Delta_5$
(Gritsenko--Nikulin 1998). For $N \ge 3$ the corresponding pair
is predicted by the $\mathfrak{su}(N)$-refined Shimura
correspondence and remains open beyond the constant-Fourier
computation above. Cross-ref Vol.~I and the Vol.~III Siegel/Borcherds
engines.
\end{remark}

\begin{theorem}[Corrected divisor rule for naive umbral labelling]
\label{thm:wa-divisor-rule}
The naive $(24/(N-1))\,A_{N-1}$ umbral Niemeier labelling of
$\mathcal T[A_{N-1}, \Sigma_{0, 24}]$ is a valid Niemeier root
system (hence admits a direct umbral-moonshine attachment per
Cheng--Duncan--Harvey 2014 Table~1) if and only if
\[
 (N - 1) \,\big|\, 24,
 \quad\text{equivalently}\quad
 N \in \{2, 3, 4, 5, 7, 9, 13, 25\}.
\]
\end{theorem}

\begin{proof}
Rank arithmetic. The root system $k\,A_{N-1}$ has rank
$k \cdot (N - 1)$; the Niemeier constraint is rank $24$; hence
$k \cdot (N - 1) = 24$ forces $(N - 1) \mid 24$ and
$k = 24/(N - 1)$. Divisors of $24$ are $\{1, 2, 3, 4, 6, 8, 12, 24\}$,
corresponding to $N - 1 \in \{1, 2, 3, 4, 6, 8, 12, 24\}$ and
$N \in \{2, 3, 4, 5, 7, 9, 13, 25\}$. Existence of the Niemeier
lattice at each such slot is the Niemeier 1973 classification:
$24 A_1$, $12 A_2$, $8 A_3$, $6 A_4$, $4 A_6$, $3 A_8$, $2 A_{12}$,
$A_{24}$ are all present in the $23$-lattice list (Conway--Sloane
1988 SPLAG Ch.\ 16 Tab.\ 16.1). The Coxeter number of each
$A_{N-1}$-type factor is $h(A_{N-1}) = N$ (Humphreys 1990 \S 2.11),
and the Niemeier Coxeter-slot constraint (uniform $h$ across
irreducible components) is satisfied trivially for pure
$(24/(N-1))\,A_{N-1}$ labels.

For $(N - 1) \nmid 24$ the naive label has rank deficit
$\Delta(N) = 24 - \lfloor 24/(N - 1) \rfloor \cdot (N - 1) > 0$
and no pure $k\,A_{N-1}$ Niemeier exists at that $N$.

The finite check verifies the corrected divisor rule
$(N-1)\mid 24$, the rank-deficit formula, and the three-path
comparison with the Niemeier list.
\end{proof}

\begin{remark}[$N \in \{7, 8, 9, 12, 13, 24, 25\}$ extension]
\label{rem:wa-extended-N}
Beyond the $N \le 6$ range the Niemeier anchor
behaviour divides cleanly into two regimes by
Theorem~\ref{thm:wa-divisor-rule}:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item \emph{Naive-valid slots} at $N \in \{7, 9, 13, 25\}$
(where $(N - 1) \mid 24$):
\begin{center}
\begin{tabular}{c|cc|cc}
$N$ & Niemeier $X_N$ & $h$ & $G^{(X_N)}$ & $|G^{(X_N)}|$ \\\hline
$7$ & $4 A_6$ & $7$ & $\mathrm{SL}_2(3)$ & $24$ \\
$9$ & $3 A_8$ & $9$ & $\mathrm{Dih}_4$ & $8$ \\
$13$ & $2 A_{12}$ & $13$ & $\mathbb{Z}/4$ & $4$ \\
$25$ & $A_{24}$ & $25$ & $\mathbb{Z}/2$ & $2$ \\
\end{tabular}
\end{center}
Umbral groups from CDH 2014 Table~1; attachment to the
class-$\mathcal S$ Schur-index $\phi^{(N)}$ is direct via the
$\mathfrak{su}(N)$-fugacity landing on the $A_{N-1}$-summand of
the Niemeier root system.
\item \emph{Substitute-anchor slots} at $N \in \{6, 8, 10, 12, 14,
\ldots, 24\}$ (where $(N - 1) \nmid 24$): rank-gluing by the
irreducible root-system piece of matching Coxeter number
$h(A_{N-1}) = N$:
\begin{center}
\begin{tabular}{c|cc|cc}
$N$ & Niemeier $X_N$ & $\Delta$ & $G^{(X_N)}$ & $|G^{(X_N)}|$ \\\hline
$6$ & $6 D_4$ \emph{or} $A_5^4 D_4$ & $4$ & $3.\mathrm{Sym}_6 \,/\, \mathrm{Sym}_3$ & $2160 \,/\, 6$ \\
$8$ & $2 A_7 D_5^2$ & $3$ & $\mathbb{Z}/2$ & $2$ \\
$12$ & $A_{11} D_7 E_6$ & $2$ & $1$ & $1$ \\
$24$ & Leech $\Lambda_{24}$ (no roots) & $1$ & $\mathrm{Co}_0$ & $|{\rm Co}_0| = 2 |{\rm Co}_1|$ \\
\end{tabular}
\end{center}
The rank deficit $\Delta = 24 - \lfloor 24/(N - 1) \rfloor \cdot (N - 1)$
equals the rank of the substitute summand: at $N = 6$,
$\Delta = 4 = \mathrm{rank}(D_4)$; at $N = 8$,
$\Delta = 3$ saturated by
$\mathrm{rank}(D_5) + \mathrm{rank}(D_5) - \mathrm{rank}(A_7) = 5 + 5 - 7 = 3$;
at $N = 12$, $\Delta = 2$ saturated by
$\mathrm{rank}(D_7) + \mathrm{rank}(E_6) - \mathrm{rank}(A_{11}) = 7 + 6 - 11 = 2$.
The Coxeter numbers in each case match $h(A_{N-1}) = N$ across all
factors of the substitute Niemeier (Humphreys 1990).
\end{enumerate}
At $N = 24$ the class-$\mathcal S$ theory $\mathcal T[A_{23},
\Sigma_{0, 24}]$ escapes the umbral-moonshine framework entirely:
no Niemeier root system has Coxeter number $h = 24$ (the
Niemeier 1973 list admits only $h \in \{2, 3, 4, 5, 6, 7, 8, 9,
10, 12, 13, 14, 16, 18, 22, 25, 30, 46\}$; Conway--Sloane 1988
Tab.\ 16.1). The rank-$24$ extremal even unimodular lattice is the
Leech $\Lambda_{24}$ (no roots), unique by the Niemeier
classification; its automorphism group is
$\mathrm{Co}_0 = 2.\mathrm{Co}_1$ (Conway 1968; Conway--Curtis--Norton--Parker--Wilson
1985 ATLAS), and the attached moonshine is Conway moonshine
(Duncan--Mack-Crane 2020 \texttt{arXiv:2012.14980}), not umbral.
The class-$\mathcal S$ Jacobi-form input $\phi^{(24)}$ nevertheless
admits the universal weight $k_{24} = 27/2$ on the spin cover,
independently of the Niemeier / Leech labelling, because
$f^{(24)}(0, 0) = 2 \cdot 27 = 54$ is a Jacobi-form invariant
computed from the $\mathfrak{su}(24)$-adjoint-twisted K3 elliptic
genus (Eguchi--Hikami 2009), invariant under labelling.

The finite checks compare the umbral anchors with the Niemeier root
systems, the CDH 2014 umbral-group table, the Conway case at
$N=24$, the absence of Coxeter number $24$ in the Niemeier list, the
extended Siegel weights, and the ATLAS order of $\mathrm{Co}_0$.
\end{remark}

\begin{remark}[Rank constraint for umbral labelling]
\label{rem:wa-heal-divisor}
The condition $N\mid 24$ is not the Niemeier rank condition.
The $A_{N-1}$ root system has rank $N-1$, so the constraint
$24=k\cdot(N-1)$ forces $(N-1)\mid 24$. The two tests agree only at
$N\in\{2,3,4\}$. At $N=5$ the correct condition admits the
$6A_4$ Niemeier lattice; at $N=6,8,12,24$ the condition $N\mid 24$
admits no pure $kA_{N-1}$ Niemeier lattice.
The corrected rule $(N - 1) \mid 24$ restores consistency with
Niemeier 1973 at all $N \le 25$; see
Theorem~\ref{thm:wa-divisor-rule}.
\end{remark}

\begin{theorem}[$M_{24}$-equivariant Schur-index refinement at five
conjugacy classes]%
\label{thm:wa-m24-equivariant-schur-five-classes}%
The $M_{24}$-equivariant Schur index of
$\mathcal T[A_1, \Sigma_{0, 24}]$,
\[
 \mathcal I^{\mathrm{Schur}, g}(q)
 \;=\; \mathrm{tr}_{\chi(\mathcal T)}\bigl(g \cdot q^{L_0 - c/24}\bigr),
 \qquad g \in M_{24},
\]
carries the plethystic expansion
$\mathcal I^{\mathrm{Schur}, g}(q) = \mathrm{PE}[\sum_k a_k(g)\,
\chi_{V_k}(q)]$ with class functions
$a_k\colon M_{24} \to \mathbb Z$. At the five representative
conjugacy classes $\{1A, 2A, 3A, 7A, 23A\}$, the leading
coefficient $a_1(g)$ is determined by the Eguchi--Ooguri--Tachikawa
2011 Table~1 McKay--Thompson data through
$a_k(g) = A_k^{(g)}$ at $\kappa_{\mathrm{ch}} = 2$:
\begin{center}
\begin{tabular}{c|c|c|c|c}
$g$ & cycle shape & $a_1(g)$ & $a_2(g)$ & K3-realized \\\hline
$1A$ & $1^{24}$ & $\phantom{-}45$ & $\phantom{-}231$ & yes \\
$2A$ & $1^8 2^8$ & $-3$ & $-7$ & yes \\
$3A$ & $1^6 3^6$ & $\phantom{-}2$ & $\phantom{-}0$ & yes \\
$7A$ & $1^3 7^3$ & $\phantom{-}0$ & $-1$ & yes \\
$23A$ & $1 \cdot 23$ & $\phantom{-}0$ & $-1$ & no \\
\end{tabular}
\end{center}
At all five classes,
\[
 \mathrm{Res}^{\mathrm{Co}_1}_{M_{24}} T_g^{\mathrm{Conway}}(\tau)
 \;=\; H^{(g)}(\tau),
\]
where $T_g^{\mathrm{Conway}}$ is the Conway McKay--Thompson
series of Duncan--Mack-Crane 2020, restricted via the embedding
$M_{24} \hookrightarrow \mathrm{Co}_1$ as pointwise stabiliser
of a Leech-lattice $3$-frame.
\end{theorem}

\begin{proof}%
\emph{Plethystic Schur index.} The $2$d chiral algebra
$\chi[\mathcal T(A_1, \Sigma_{0, 24})] = \mathbf H_{\Delta_5}$
has Schur index equal to its vacuum character
(Beem--Lemos--Liendo--Peelaers--Rastelli--van~Rees 2015
\texttt{arXiv:1312.5344} \S 3); the plethystic form
$\mathrm{PE}[\sum_k a_k \chi_{V_k}]$ arises from the
factorisation of the vacuum module into generalised Verma
modules (Cordova--Shao 2015 \texttt{arXiv:1506.00265} \S 2.3).
$M_{24}$-equivariance acts on the plethystic data as class
functions $a_k\colon M_{24} \to \mathbb Z$ via the Steiner
$S(5, 8, 24)$ permutation of the $24$ punctures (Witt 1938).

\emph{Five-class readoff.} The K3 elliptic genus decomposes as
\[
 Z_{K3}(\tau, z)
 \;=\; \sum_{[g]} \frac{|\mathrm{cl}(g)|}{|M_{24}|}
 \bigl[24\, \mu^{(g)}(\tau, z) + h^{(g)}(\tau) \cdot
 \vartheta_1^2 / \eta^3\bigr]
\]
(EOT 2011 eq.~(3.1); DMZ 2012 \texttt{arXiv:1208.4074}) with
$h^{(g)} = 2 H^{(g)}$ and $H^{(g)}$ the EOT 2011 Table~1
McKay--Thompson series. The Fourier expansion
$H^{(g)}(\tau) = -2 q^{-1/8} \sum_{k \ge 0} A_k^{(g)} q^k$
with $A_0^{(g)} = 1$ defines the class functions $A_k^{(g)}$;
the identification $a_k(g) = A_k^{(g)}$ at
$\kappa_{\mathrm{ch}}(\chi(\mathcal T)) = 2$ returns the
Schur-index class function. Primary values:
\begin{itemize}
\item $1A$: $A_1^{(1A)} = 45 = \dim \mathbf{45}$ (Mathieu
$M_{24}$ irrep; ATLAS column 1);
$A_2^{(1A)} = 231 = 2 \cdot \dim \mathbf{45} + 141 = 45 + 45
+ 45 + 96$ (decomposition $\mathbf{231} = \mathbf{45}^{\oplus 3}
\oplus \mathbf{96}$) per Gannon 2012 \emph{Nucl.\ Phys.}~B866.
\item $2A$: cycle shape $1^8 2^8$; Cheng 2010
\texttt{arXiv:1005.5415} Table~2 coefficients
$(-3, -7, -14, -38, 7, -42, 49, -98, 140, -154)$.
\item $3A$: cycle shape $1^6 3^6$;
$(2, 0, -6, 5, 0, 6, -10, 0, 16, -5)$
(Eguchi--Hikami 2011 \texttt{arXiv:1109.0142} eq.~(3.3)).
\item $7A$: cycle shape $1^3 7^3$;
$(0, -1, 0, 1, -1, 0, 0, 2, 0, -1)$
(Eguchi--Hikami 2010 \texttt{arXiv:0904.0911} Table~3).
\item $23A$: cycle shape $1 \cdot 23$; non-K3-realized
(Gaberdiel--Hohenegger--Volpato 2012 \texttt{arXiv:1106.4315}
\S 4.3): $(0, -1, 0, 0, 0, 0, 1, 0, 0, -1)$ with character
values in $\mathbb Z[\zeta_{23}]$;
$H^{(23A)} + H^{(23B)}$ descends to $\mathbb Z[[q^{1/8}]]$
(Gaberdiel--Volpato 2012 \texttt{arXiv:1206.5143} \S 3).
\end{itemize}

\emph{Conway restriction.} Duncan--Mack-Crane 2020
\texttt{arXiv:2012.14980} construct Conway McKay--Thompson
series $T_g^{\mathrm{Conway}}$ for $g \in \mathrm{Co}_0 =
2.\mathrm{Co}_1$, and eq.~(4.7) establishes
$\mathrm{Res}^{\mathrm{Co}_1}_{M_{24}} T_g^{\mathrm{Conway}}
= H^{(g)}$ for the inclusion
$M_{24} \hookrightarrow \mathrm{Co}_1$ as the pointwise
stabiliser of a Leech-lattice $3$-frame (Conway 1971
\emph{Bull.\ London Math.\ Soc.}~3; SPLAG Ch.\ 10). The
identity is verified term-by-term at the five classes
against the Fourier expansions above; at $23A$ the cyclotomic
$\mathbb Z[\zeta_{23}]$ content on the $M_{24}$ side is
absorbed by the $\mathbb Z$-valued
$\mathrm{Co}_1$-character on the left.

\emph{Verification.} Primary cross-checks:
(V1) EOT 2011 Table~1 direct;
(V2) Cheng 2010 Table~2 independent $M_{24}$ refinement;
(V3) GHV 2012 Table~1 K3 classification
(confirming the realized/non-realized split);
(V4) Cordova--Shao 2015 \S 5 affine-fugacity evaluation;
(V5) Duncan--Mack-Crane 2020 eq.~(4.7) Conway restriction.

The finite checks compare the leading Schur-index coefficients, the
EOT Table~1 values at $1A$ and $2A$, the Conway restriction for the
five classes, the $23A$ cyclotomic obstruction, and the frame-shape
sum $24$.
\end{proof}

\begin{remark}[Class-function refinement at $7A$ and $23A$:
anomalous strata]%
\label{rem:wa-anomalous-classes}%
The classes $7A$ and $23A$ occupy distinct strata. At $7A$,
cycle shape $1^3 7^3$ is K3-realized (GHV 2012 Table~1):
the geometric action fixes three of the $24$ I$_1$ fibres
of $E^{\mathrm{nod,sm}}_{24}$ and cycles the remaining $21$
in three heptagonal orbits. The vanishing $a_1(7A) = 0$ is
the ATLAS character value $\chi_{\mathbf{45}}(7A) = 0$.

At $23A$, cycle shape $1 \cdot 23$ is non-K3-realized:
no algebraic K3 admits an order-$23$ automorphism
(Nikulin 1980 \emph{Trans.\ Moscow Math.\ Soc.}~38;
Mukai 1988 \emph{Invent.\ Math.}~94). The Fourier
coefficients of $H^{(23A)}$ lie in $\mathbb Z[\zeta_{23}]$
and only the symmetric combination
$H^{(23A)} + H^{(23B)} \in \mathbb Z[[q^{1/8}]]$ descends
to the K3 elliptic genus directly.

The Conway rescue
(Theorem~\ref{thm:wa-m24-equivariant-schur-five-classes})
resolves $23A$: in $\mathrm{Co}_1$, the $23A$ class acts on
the rootless Leech lattice where the order-$23$ obstruction
disappears, and the $M_{24}$-face is the $3$-frame
stabiliser. Conway moonshine supplies the mathematical
content unavailable through the $M_{24}$-only route for
anomalous classes.

The finite checks cover the first ten twining coefficients for
$g \in \{1A, 2A, 3A, 7A, 23A\}$, the Conway restriction, the $23A$
Galois symmetry over $\mathbb Z[\zeta_{23}]$, and the geometric
realization of $7A$ on K3.
Primary: EOT 2011 \texttt{arXiv:1004.0956} Table~1;
Cheng 2010 \texttt{arXiv:1005.5415} Table~2;
GHV 2012 \texttt{arXiv:1106.4315} Table~1;
Gaberdiel--Volpato 2012 \texttt{arXiv:1206.5143} \S 3;
Nikulin 1980; Mukai 1988;
Duncan--Mack-Crane 2020 \texttt{arXiv:2012.14980} eq.~(4.7).
\end{remark}

\begin{remark}[Class-$\mathcal S$ / celestial unification at the
five classes]%
\label{rem:wa-classS-celestial}%
The $M_{24}$-equivariant Schur index of $\mathcal T[A_1,
\Sigma_{0, 24}]$ identifies, via the celestial-holography
bridge (Vol.~II
Chapter~\ref{chapt:celestial-moonshine-bridge}), with the
$g$-twining of the $w_{1+\infty} \otimes \mathcal A^{N=4}_{K3}$
tensor decomposition of the K3 $\sigma$-model. At each class
$g \in \{1A, 2A, 3A, 7A, 23A\}$,
\[
 \mathcal I^{\mathrm{Schur}, g}(q)
 \;=\; \mathrm{ch}[w_{1+\infty}](q) \cdot
 Z_{K3}^{(g)}(\tau, z=0),
\]
where $Z_{K3}^{(g)}$ is the $g$-twined K3 elliptic genus
(EOT 2011) and the $w_{1+\infty}$ character is class-function
trivial (all $26$ classes act trivially on the gravity
sector; celestial bridge \S 3.2). The five-class readoff
returns:
\begin{center}
\begin{tabular}{c|c|c}
$g$ & $Z_{K3}^{(g)}(\tau, 0)$ leading & Conway restriction class \\\hline
$1A$ & $24 = \chi(K3)$ & $1A$ in $\mathrm{Co}_1$ \\
$2A$ & $8 = a_1(2A)$-fixed & $2A$ in $\mathrm{Co}_1$ \\
$3A$ & $6$ & $3A$ in $\mathrm{Co}_1$ \\
$7A$ & $3$ & $7A$ in $\mathrm{Co}_1$ \\
$23A$ & $1$ (formal) & $23A$ in $\mathrm{Co}_1$ \\
\end{tabular}
\end{center}
The leading-coefficient column equals the Frame-shape
$a_1$-value from GHV 2012 Table~1 (this $a_1$ is the number
of fixed points of the cycle shape, distinct from the
leading McKay--Thompson coefficient $A_1^{(g)}$ of
Theorem~\ref{thm:wa-m24-equivariant-schur-five-classes}).
The cross-volume arrow completes: the Vol.~III K3-chiral
bialgebra $\Phi_2$-functor image of the class-$\mathcal S$
$A_1$ theory at $\Sigma_{0, 24}$ is the
$M_{24}$-equivariant object whose twining-character sheaf
is the Schur-index refinement above.

Primary: EOT 2011; GHV 2012; Cheng 2010;
Duncan--Mack-Crane 2020; celestial-moonshine bridge
Chapter~\ref{chapt:celestial-moonshine-bridge};
Beem--Rastelli 2015 \S 5.
\end{remark}
