\section{W-Algebras as $A_\infty$ Chiral Algebras: Virasoro and $W_3$}
% label removed: sec:W-algebras

W-algebras are the decisive test cases for the $A_\infty$ chiral framework in the $d' = 1$ regime. The reason is structural: the pre-reduction affine vertex algebra $V_k(\mathfrak{g})$ is Koszul (Theorem~\ref{thm:one-loop-koszul}), so the transferred $A_\infty$ operations on bar cohomology vanish ($m_k = 0$ for $k \ge 3$), though the Swiss-cheese operations on $V_k(\mathfrak{g})$ itself have $m_3^{\mathrm{SC}} \neq 0$ (class~$\mathbf{L}$, depth~$3$). Drinfeld--Sokolov reduction changes this. The BRST functor manufactures the higher operations $m_k$ for $k \ge 3$ that break Swiss-cheese formality (Theorem~\ref{thm:ds-koszul-obstruction}): the quartic OPE pole of the Virasoro generator, the quintic pole of $W_3$, and the higher poles of $W_N$ are all artefacts of the reduction, absent in the affine input. The resulting $\mathcal{W}$-algebra remains chirally Koszul (the bar complex is well-behaved); its infinite transferred tower is the wheel-residue theorem below under the KZ analytic SDR hypotheses. The Khan--Zeng 3D holomorphic-topological Poisson sigma model~\cite{KZ25} supplies the classical Hamiltonian bidifferential for freely generated PVAs; Theorem~\ref{thm:general-half-space-bv} supplies the all-loop BV quantization only after the KZ analytic SDR package is imposed.

\subsection{General Framework: PVA to 3D HT Gauge Theory}
% label removed: subsec:PVA-to-3DHT

\subsubsection{The Khan--Zeng Construction}

Let $\mathcal{V} = \Sym(\C[\partial]\langle \phi^i \rangle)$ be a freely generated Poisson vertex algebra with generators $\phi^i$ of conformal spins $s_i$. The $\lambda$-bracket
\[
\{\phi^i{}_\lambda \phi^j\} = \sum_{n \geq 0} \Pi^{ij}_n \lambda^n, \quad \Pi^{ij}_n \in \mathcal{V},
\]
encodes the classical Poisson structure.

\begin{construction}[3D HT Poisson Sigma Model]
To each freely generated PVA $\mathcal{V}$, Khan and Zeng associate a classical 3D holomorphic-topological gauge theory on $\R \times \C$ with fields:
\begin{itemize}
\item $\Phi^i = \phi^i_{zz\cdots z}(t,z,\bar{z})(dz)^{\otimes s_i}$, the holomorphic field of spin $s_i$;
\item $\eta_i = (\eta_i^t dt + \eta_i^{\bar{z}} d\bar{z}) \otimes (dz)^{\otimes(1-s_i)}$, the Lagrange multiplier (conjugate momentum) of spin $1-s_i$.
\end{itemize}
The action functional is
\begin{equation}
% label removed: eq:KZ-action
S = \int_{\R \times \C} \eta_i (d_t + \bar{\partial})\Phi^i + \frac{1}{2} \eta_i \Pi^{ij}(\partial_z) \eta_j,
\end{equation}
where $\Pi^{ij}(\partial) = \sum_n \Pi^{ij}_n \partial^n$ is the differential operator encoding the $\lambda$-bracket.

The gauge transformations are
\begin{align}
\delta \Phi^i &= \Pi^{ij}(\partial) \epsilon_j,\\
\delta \eta_i &= -(d_t + \bar{\partial})\epsilon_i - \eta_j \frac{\partial \Pi^{jk}}{\partial \Phi^i}(\partial) \epsilon_k,
\end{align}
where $\epsilon_i$ are gauge parameters of spin $1-s_i$.
\end{construction}

\begin{remark}[Higher-spin gauge sector]
When $\mathcal{V}$ is a W-algebra, the classical gauge symmetry contains the higher-spin transformations generated by the fields of spin $>2$. This gives a holomorphic-topological higher-spin gauge sector in the sense suggested by Henneaux--Teitelboim and Vasiliev. Identifying the model with a full higher-spin gravity theory, rather than with its HT boundary/gauge avatar, requires a separate quantum BV construction and boundary condition.
\end{remark}

\subsubsection{BV Quantization and $A_\infty$ Operations}

\begin{remark}[Constructive BV input for W-algebra examples]
% label removed: rem:W-hypotheses
For finite-jet polynomial freely generated PVA input, the classical BV
fields and master action are constructed in
Construction~\ref{cons:kz-bv-fields-action}, and
Lemma~\ref{lem:kz-cme-pva-jacobi} identifies the classical master
equation with PVA Jacobi. The all-loop BV package used by the quantum
examples is Theorem~\ref{thm:general-half-space-bv}, under the
KZ analytic SDR package of Assumption~\ref{assum:kz-analytic-sdr-package}.
Each numerical constant, DS transfer identity, wheel-residue
nonvanishing, and Hochschild comparison is proved under the precise
hypotheses named in the statement where it appears.
\end{remark}

In the BV formalism, we introduce antifields $(\Phi^i)^* \sim \eta_i$ and ghosts $c^i \sim \epsilon_i$. The master action
\[
S_{\text{BV}} = S + \int (\Phi^i)^* Q c^i + \cdots
\]
determines the BRST differential $Q = \{S_{\text{BV}}, -\}_{\text{BV}}$.

The $A_\infty$ operations $m_k$ are computed via Feynman diagrams:
\begin{itemize}
\item $m_1 = Q$ (the BRST differential);
\item $m_2$ comes from the free propagator determined by the kinetic term;
\item $m_{k \geq 3}$ arise from tree-level and loop diagrams with interaction vertices from $\eta_i \Pi^{ij} \eta_j$.
\end{itemize}

\subsection{Example 1: Virasoro Algebra (Spin-2 W-algebra)}
% label removed: subsec:virasoro

\subsubsection{Classical Structure}

The Virasoro Poisson vertex algebra is generated by a single field $T$ of spin 2 (the stress tensor) with $\lambda$-bracket
\begin{equation}
% label removed: eq:vir-lambda-bracket
\{T_\lambda T\} = \partial T + 2T\lambda + \frac{c}{12}\lambda^3.
\end{equation}
Here $c \in \C$ is the \emph{classical central charge}. This encodes the infinitesimal transformation of the stress tensor under conformal changes of coordinates.

\begin{remark}[Schwarzian Derivative]
The $\lambda^3$ term arises from the Schwarzian derivative in the transformation law
\[
\tilde{T}(\phi(z)) = \left(\frac{d\phi}{dz}\right)^2 T(\phi(z)) - \frac{c}{12}\{\phi; z\},
\]
where $\{\phi; z\} = \frac{\phi'''}{\phi'} - \frac{3}{2}\left(\frac{\phi''}{\phi'}\right)^2$ is the Schwarzian.
\end{remark}

\subsubsection{3D Field Theory}

The fields are:
\begin{align}
T &= T_{zz}(t,z,\bar{z}) (dz)^{\otimes 2}, & |T| = 0,\\
\mu &= (\mu^t_z dt + \mu^{\bar{z}}_z d\bar{z}) \otimes \frac{\partial}{\partial z}, & |\mu| = -1.
\end{align}

The action from \eqref{eq:KZ-action} specializes to
\begin{equation}
% label removed: eq:virasoro-action
S_{\text{Vir}} = \int_{\R \times \C} \mu (d_t + \bar{\partial})T + T \mu \partial_z \mu + \frac{c}{24} \mu \partial_z^3 \mu.
\end{equation}

\subsubsection{BV-BRST Differential}

Introducing the ghost $c_{\mathrm{gh}}$ (of spin $-1$) and antifields, the BRST differential is
\begin{align}
Q \cdot T &= \partial T \cdot c_{\mathrm{gh}} + 2T \partial c_{\mathrm{gh}} + \frac{c}{12} \partial^3 c_{\mathrm{gh}},\\
Q \cdot \mu &= -(d_t + \bar{\partial})c_{\mathrm{gh}} - \mu \partial c_{\mathrm{gh}} + c_{\mathrm{gh}} \partial \mu,\\
Q \cdot c_{\mathrm{gh}} &= c_{\mathrm{gh}} \partial c_{\mathrm{gh}}.
\end{align}

\begin{lemma}[Nilpotency $Q^2 = 0$]
% label removed: lem:vir-nilpotent
The BRST differential $Q$ defined above satisfies $Q^2 = 0$.
\end{lemma}
\begin{proof}
We verify $Q^2 = 0$ on each generator. The inputs are the Virasoro $\lambda$-bracket $\{T_\lambda T\} = \partial T + 2\lambda T + \frac{c}{12}\lambda^3$ and the ghost OPE $\{(c_{\mathrm{gh}})_\lambda c_{\mathrm{gh}}\} = 0$, $\{(c_{\mathrm{gh}})_\lambda \mu\} = -1$.

\emph{On $c_{\mathrm{gh}}$:} $Q(c_{\mathrm{gh}}) = c_{\mathrm{gh}}\partial c_{\mathrm{gh}}$, so $Q^2(c_{\mathrm{gh}}) = Q(c_{\mathrm{gh}}\partial c_{\mathrm{gh}}) = Q(c_{\mathrm{gh}})\cdot\partial c_{\mathrm{gh}} + c_{\mathrm{gh}}\cdot\partial Q(c_{\mathrm{gh}}) = (c_{\mathrm{gh}}\partial c_{\mathrm{gh}})(\partial c_{\mathrm{gh}}) + c_{\mathrm{gh}}\cdot\partial(c_{\mathrm{gh}}\partial c_{\mathrm{gh}})$. Expanding: $c_{\mathrm{gh}}(\partial c_{\mathrm{gh}})(\partial c_{\mathrm{gh}}) + c_{\mathrm{gh}}((\partial c_{\mathrm{gh}})(\partial c_{\mathrm{gh}}) + c_{\mathrm{gh}}\partial^2 c_{\mathrm{gh}}) = 2c_{\mathrm{gh}}(\partial c_{\mathrm{gh}})^2 + c_{\mathrm{gh}}^2\partial^2 c_{\mathrm{gh}}$. Since $c_{\mathrm{gh}}$ is fermionic (odd), $c_{\mathrm{gh}}^2 = 0$ and $(\partial c_{\mathrm{gh}})^2 = 0$ (in the graded sense), so $Q^2(c_{\mathrm{gh}}) = 0$.

\emph{On $T$:} $Q(T) = \partial T \cdot c_{\mathrm{gh}} + 2T\partial c_{\mathrm{gh}} + \frac{c}{12}\partial^3 c_{\mathrm{gh}}$. Computing $Q^2(T)$ requires applying $Q$ to each term and using the Leibniz rule. The result is a polynomial in $T, c_{\mathrm{gh}}, \mu$ and their derivatives. The cancellation follows from the Jacobi identity for the $\lambda$-bracket: the coefficient of each monomial in $Q^2(T)$ is a specific linear combination of structure constants of $\{T_\lambda T\}$, and the Jacobi identity $\{T_\lambda \{T_\mu T\}\} - \{T_\mu \{T_\lambda T\}\} = \{\{T_\lambda T\}_{\lambda+\mu} T\}$ ensures these cancel. This is a standard calculation in BRST cohomology; see~\cite{FMS86}.

\emph{On $\mu$:} Similarly, $Q^2(\mu) = 0$ follows from the $Q$-equivariance of the $(T,\mu)$ pairing and the identity $Q^2(c_{\mathrm{gh}}) = 0$ applied through the ghost OPE.
\end{proof}

\subsubsection{Propagators and $m_2$}

The free propagator for the pair $(T, \mu)$ is determined by inverting the kinetic operator. For operators at holomorphic points $(t_1, z_1)$ and $(t_2, z_2)$:
\begin{equation}
% label removed: eq:vir-propagator
\langle T(z_1) \mu(z_2) \rangle = \frac{\Theta(t_1 - t_2)}{2\pi(z_1 - z_2)}.
\end{equation}

\begin{proposition}[Virasoro $\lambda$-bracket from Propagator]
% label removed: prop:vir-m2
Assume the Virasoro KZ realization satisfies the analytic SDR package
of Assumption~\textup{\ref{assum:kz-analytic-sdr-package}}.
The $\lambda$-bracket $m_2$ computed from \eqref{eq:vir-propagator} reproduces \eqref{eq:vir-lambda-bracket}:
\begin{equation}
m_2(T, T)_\text{sing} = \{T_\lambda T\} = a_1 + a_2 \lambda + a_3 \lambda^3,
 \qquad\text{(divided-power convention: $a_3 = T_{(3)}T/3! = c/12$)}
\end{equation}
where
\begin{align}
a_3 &= \frac{c}{12}, & \text{(Schwarzian term)}\\
a_2 &= 2T, & \text{(primary transformation)}\\
a_1 &= \partial T. & \text{(derivative term)}
\end{align}
The regular part gives the commutative product: $m_2(T,T)_\text{reg} = :TT:$ (normal ordered).
\end{proposition}

\begin{proof}
By Wick's theorem, contracting $T(z_1)$ with $\mu$ in the interaction term $\int T\mu\partial\mu + \frac{c}{24}\mu\partial^3\mu$ at $z_2$ gives
\[
\langle T(z_1) : T\mu\partial\mu + \frac{c}{24}\mu\partial^3\mu :(z_2) \rangle.
\]
Evaluating the Wick contraction:
\begin{align*}
\langle T(z_1) \mu(z_2) \rangle &\cdot \left( T(z_2) \partial_2 \mu(z_2) + \frac{c}{24} \partial_2^3 \mu(z_2) \right)\\
&= \frac{\Theta(t_1-t_2)}{2\pi(z_1-z_2)} \left( T(z_2) \partial_2 \mu(z_2) + \frac{c}{24} \partial_2^3 \mu(z_2) \right).
\end{align*}
Now use the identity
\[
\frac{1}{z_1 - z_2} f(z_2) = \sum_{n=0}^\infty \frac{(z_1-z_2)^n}{n!} \partial_2^n \left( \frac{f(z_2)}{z_1-z_2} \right) = f(z_2) \sum_{n=0}^\infty \frac{(-1)^n (z_1-z_2)^{n-1}}{n!} \partial_2^n.
\]
Setting $\lambda = z_1 - z_2$ and extracting singular terms gives \eqref{eq:vir-lambda-bracket}.
\end{proof}

\subsubsection{Higher Operations $m_k$ for $k \geq 3$}

For the Virasoro algebra, the structure is special: the interaction term is \emph{quadratic} in $\mu$, so:

\begin{proposition}[Virasoro wheel sector]
% label removed: prop:vir-truncation
Assume that the Khan--Zeng Virasoro realization satisfies the KZ
analytic SDR package of
Assumption~\textup{\ref{assum:kz-analytic-sdr-package}}, and assume
that the cyclic wheel residue class on
$\FM_k(\C)\times\Conf_k^{<}(\R)$ survives projection to the boundary
Virasoro complex.
For the Virasoro $A_\infty$ chiral algebra:
\begin{enumerate}
\item $m_3(T, T, T)$ receives its pure $T$-sector wheel term from the
triangle of three cubic vertices $V_3=T\mu\partial\mu$;
\item for each $k \ge 3$, the connected pure $T$-sector wheel
contributing to $m_k(T,\ldots,T)$ has loop number~$1$;
\item under the stated residue-survival hypothesis, this sector gives
$m_k(T,\ldots,T)\ne0$ for all $k \ge 3$.
\end{enumerate}
\end{proposition}

\begin{proof}
The Virasoro action has the form $S_{\mathrm{Vir}} = \int \mu(\partial_t + \bar\partial) T + T\mu\partial\mu + \tfrac{c}{24}\mu\partial^3\mu$, so the interaction vertices are:
\begin{itemize}
\item \emph{Cubic vertex} $V_3 = T\mu\partial\mu$: consumes 1 field $T$ and 2 fields $\mu$;
\item \emph{Quadratic ghost vertex} $V_2 = \tfrac{c}{24}\mu\partial^3\mu$: consumes 2 fields $\mu$ (no $T$).
\end{itemize}

The analytic SDR package and the wheel-residue hypothesis select, for
each $k\ge3$, the cyclic graph $C_k$ with $k$ cubic vertices
$V_3^{(1)},\ldots,V_3^{(k)}$ and one cyclic chain of $k$ internal
propagator edges. The graph-theoretic loop number is therefore
\[
b_1(C_k)=|E(C_k)|-|V(C_k)|+1=k-k+1=1.
\]
For $k=3$ this graph is the triangle giving the pure $T$-sector
contribution to $m_3(T,T,T)$. The quadratic central vertex can alter
the coefficient of the resulting residue, but its contribution to
nonvanishing is not inferred from graph counting.

\emph{Non-vanishing.} The wheel integral at degree $k$ is
\[
m_k(T, \ldots, T) \;\sim\; \int_{\FM_k(\C) \times \Conf_k^{<}(\R)}
 \prod_{i=1}^k K(z_i - z_{i+1},\, t_i - t_{i+1})\; \partial_{z_i}\cdots,
\]
where indices are cyclic. The propagator $K(z,t) = \Theta(t)/(2\pi z)$
contributes one holomorphic kernel per edge; the
$\partial_z$ derivatives from $V_3 = T\mu\partial\mu$ produce the
polynomial residue in the spectral parameters
$\lambda_i = z_i - z_{i+1}$. This identifies the candidate class. Its
survival after compactified integration, boundary renormalization, and
projection to the Virasoro complex is precisely the wheel-residue
hypothesis in the statement. Under that hypothesis,
$m_k(T,\ldots,T)\ne0$ for all $k\ge3$.
\end{proof}

\begin{remark}[Wheel diagrams as resolvent tree evaluations]
% label removed: rem:wheel-as-resolvent-evaluation
Under the hypotheses of Proposition~\ref{prop:vir-truncation}, the
wheel diagrams above are not \emph{ad hoc} Feynman computations but
evaluations of the resolvent tree formula
(Theorem~\ref{thm:resolvent-principle},
equation~\eqref{eq:resolvent-tree-formula}). The resolvent
principle expresses each $m_k^W$ as a sum over $C_{k-1}$
planar binary trees, with the binary OPE $m_2^{\mathrm{aff}}$
at internal vertices and the BRST contracting homotopy
$h_{\mathrm{DS}}$ at internal edges. When this abstract tree
sum is evaluated using the Khan--Zeng propagator
$K(t,z) = \Theta(t)/(2\pi z)$ and the cubic vertex
$V_3 = T\mu\partial\mu$, the individual tree contributions
reassemble into the single wheel integral above:
the BRST homotopy provides the non-cohomological intermediate
$\mu$-states that connect consecutive vertices around the
cycle (Theorem~\ref{thm:tree-wheel-bridge}).

The dichotomy is sharp: for the pre-reduction affine
algebra $\widehat{\fg}_k$ (Koszul by
Theorem~\ref{thm:one-loop-koszul}), the transferred operations $m_k^H$
vanish for $k \geq 3$
(Corollary~\ref{cor:koszul-resolvent}), and no wheel diagrams
arise. Under the wheel-survival hypothesis, Drinfeld--Sokolov
reduction breaks Swiss-cheese formality
(Theorem~\ref{thm:ds-koszul-obstruction}) by manufacturing
the fourth-order Virasoro pole from the affine simple pole,
producing the excess Tor classes that the resolvent trees
evaluate to wheel classes; the $\cW$-algebra remains
chirally Koszul (bar cohomology concentrated).
\end{remark}

\begin{remark}[The fourth-order pole as excess intersection]
% label removed: rem:virasoro-excess-intersection
The Virasoro OPE has a fourth-order pole
$T(z)\,T(w) \sim c/2(z-w)^{-4} + \cdots$.
In the Lagrangian self-intersection picture, this pole
creates \emph{excess intersection dimension}: the derived
intersection
$\cL \times_{\cM}^h \cL$ carries higher Tor in degrees that
a clean intersection would not have. Under the KZ analytic SDR and
wheel-residue hypotheses, these higher Tor degrees seed the
Swiss-cheese $\Ainf$ operations represented by the wheel diagrams
$m_k$ on $\FM_k(\C) \times \Conf_k^{<}(\R)$. The fourth-order pole
prevents transversality; the assertion that the resulting
Swiss-cheese structure is genuinely non-formal is exactly the
nonvanishing statement $m_k \ne 0$ for all $k \ge 3$ under the
wheel-residue survival hypothesis.

Under that nonvanishing hypothesis this is class~$\mathbf{M}$ in the
depth classification
(Definition~\ref{def:shadow-depth-intersection}): infinite
excess, infinite shadow depth. By contrast, the Heisenberg
(double pole only, \'etale self-intersection,
class~$\mathbf{G}$) and Kac--Moody (simple pole,
Lie-transverse intersection, class~$\mathbf{L}$) have clean
self-intersections with $m_k = 0$ for $k \ge 3$.

Classes~$\mathbf{G}$, $\mathbf{L}$, $\mathbf{C}$ are
chirally Koszul: the PBW spectral sequence concentrates
and bar cohomology is concentrated, with $m_k = 0$ for
$k \ge 3$ on cohomology
(by the Koszul equivalence theorem of Volume~I).
The class~$\mathbf{M}$ sector under the KZ/DS hypotheses
(Virasoro, $\cW_N$) \emph{is}
chirally Koszul (by PBW universality) but is \emph{not}
collision-pure: the fourth-order pole causes purity
failure, and the weight spectral sequence does not
degenerate at~$E_1$. These algebras possess well-defined
Koszul duals (e.g.\ $\mathrm{Vir}_c^! = \mathrm{Vir}_{26-c}$),
and the big dual carries higher $\Ainf$ operations
reflecting non-formal Swiss-cheese structure.
Shadow depth measures the \emph{complexity} of the
Lagrangian self-intersection within the standard
families; for classes~$\mathbf{G}$/$\mathbf{L}$/$\mathbf{C}$
this complexity lives within the chirally Koszul world,
while for class~$\mathbf{M}$ under these hypotheses it reflects the additional
structure of nonvanishing transferred $\Ainf$ operations
(non-formal Swiss-cheese structure, not failure of chiral
Koszulness).
\end{remark}

\begin{remark}[Infinite depth under wheel-residue survival]
% label removed: rem:truncation-vs-depth
Unlike Landau--Ginzburg models, where the $A_\infty$ structure
truncates at finite degree by dimension counting on $\FM_k(\C)$,
the Virasoro wheel sector has no graph-theoretic truncation: the
cycle $C_k$ exists for every $k\ge3$. Proposition~\ref{prop:vir-truncation}
turns this graph class into the nonvanishing statement
$m_k\ne0$ only after the analytic SDR and wheel-residue hypotheses are
imposed.

At genus~$g \ge 1$, the curved bar structure
$d^2_{\mathrm{fib}} = \kappa(\mathrm{Vir}_c) \cdot \omega_g$
contributes additional data beyond the perturbative $m_k$: each
genus component of the Maurer--Cartan element $\Theta_{\mathrm{Vir}_c}$
encodes higher-graviton vertex corrections. The shadow-tower
obstructions $o_k$ (Vol~I) are homotopy invariants of the full
$A_\infty$ structure; the non-termination $o_5 \ne 0$ of
Section~\ref{subsec:gravity-shadow-tower} is consistent with the
hypothesis-dependent infinite perturbative depth above.
Under the same hypotheses, these non-vanishing higher operations
$m_k$ ($k \ge 3$) are instances of the BRST homological transfer from
Drinfeld--Sokolov reduction: the pre-reduction affine algebra
$\hat{\mathfrak{g}}_k$ is Koszul, but DS reduction introduces the
higher operations via Theorem~\ref{thm:ds-koszul-obstruction}.
\end{remark}

\begin{remark}[DS preserves Koszulness, destroys formality]%
\label{rem:ds-koszul-formality-scissors}%
\index{Drinfeld--Sokolov reduction!Koszulness vs.\ formality}%
Principal DS reduction is a functor that preserves chiral
Koszulness. Under the wheel-residue and split-projection hypotheses,
it destroys Swiss-cheese formality for rank~$\ge 2$.
The pre-reduction affine algebra $V_k(\fg)$ has
$m_k^{\mathrm{SC}} = 0$ for $k \ge 4$ (class~$\mathbf{L}$, depth~$3$; $m_3^{\mathrm{SC}} \neq 0$).
Under the same hypotheses, the post-reduction $\cW$-algebra has
$m_k \neq 0$ for all $k \ge 3$ (class~$\mathbf{M}$, non-formal): the
resolvent tree formula generates the infinite $\Ainf$ tower from the
formal input via the DS contracting homotopy. Both algebras
are chirally Koszul (Theorem~\ref{thm:ds-koszul-obstruction}),
but formality is lost. At the Yangian level: the affine
Yangian $Y_\hbar(\fg)$ is a strict filtered deformation of
$U(\fg[t])$; the $\cW$-algebra Yangian $\Ydg(\cW_k(\fg))$ is
a curved $\Ainf$-deformation
(Corollary~\ref{cor:gauge-gravity-dichotomy}).
\end{remark}

\textbf{Explicit Formula for $m_3$:}

The ternary operation comes from the "Y-diagram":
\begin{center}
\begin{tikzpicture}[scale=1.5]
\node at (0,0) {$\bullet$};
\node[above left] at (-0.7,0.7) {$T(z_1)$};
\node[above right] at (0.7,0.7) {$T(z_2)$};
\node[below] at (0,-0.7) {$T(z_3)$};
\draw[thick] (-0.5,0.5) -- (0,0);
\draw[thick] (0.5,0.5) -- (0,0);
\draw[thick] (0,-0.5) -- (0,0);
\end{tikzpicture}
\end{center}

The $A_\infty$ relation at degree~$3$ determines $m_3$ as the unique
homotopy solving the Stasheff equation
\begin{equation}
% label removed: eq:vir-stasheff-3
m_2\bigl(m_2(T,T;\lambda_1),\, T;\, \lambda_1+\lambda_2\bigr)
\;-\; m_2\bigl(T,\, m_2(T,T;\lambda_2);\, \lambda_1\bigr)
\;=\; d\, m_3(T,T,T;\lambda_1,\lambda_2),
\end{equation}
where $d = [Q,\,-\,]$ is the linearised BRST differential and
$m_2(T,T;\lambda) = \{T_\lambda T\} = \partial T + 2T\lambda + \tfrac{c}{12}\lambda^3$.
The left-hand side is the \emph{associator} of two successive
$\lambda$-bracket applications; its non-vanishing measures the failure
of strict associativity. The $m_1$ terms vanish because the inputs
$T$ are $Q$-closed ($T$ represents the stress tensor on cohomology,
satisfying $QT = 0$).

\medskip
\noindent\textbf{Evaluating the left-hand side.}
Write $\ell = \lambda_1$, $\mu = \lambda_2$ for brevity.
Using sesquilinearity of the $\lambda$-bracket (the rule
$\{(\partial a)_\lambda b\} = -\lambda\{a_\lambda b\}$ and
$m_2(a,b;\lambda) = \{a_\lambda b\}$); for the Virasoro algebra, $Q = 0$ on the generators $T, \partial T, \partial^2 T, \ldots$, so the chain-level $m_2$ coincides with the cohomological $\lambda$-bracket and sesquilinearity (Definition~\ref{def:sesquilinearity},
equations~\eqref{eq:sesqui-left}--\eqref{eq:sesqui-right}) holds strictly. We compute each composition:

\smallskip
\emph{First term.} Substituting the inner bracket
$m_2(T,T;\ell) = \partial T + 2T\ell + \tfrac{c}{12}\ell^3$
into the outer bracket at spectral parameter $\ell + \mu$,
using left-sesquilinearity $m_2(\partial T, T;\lambda) = -\lambda\, m_2(T,T;\lambda)$
and $\{{\mathbf{1}}_\lambda T\} = 0$:
\begin{equation}
% label removed: eq:vir-LHS-first
m_2(m_2(T,T;\ell),T;\ell+\mu)
= (\ell - \mu)\,\partial T
 + 2(\ell^2 - \mu^2)\,T
 + \frac{c}{12}(\ell+\mu)^3(\ell - \mu).
\end{equation}

\smallskip
\emph{Second term.} The inner bracket at parameter~$\mu$
gives $m_2(T,T;\mu) = \partial T + 2T\mu + \tfrac{c}{12}\mu^3$.
Using right-sesquilinearity $m_2(T,\partial T;\lambda) = (\lambda+\partial)\,m_2(T,T;\lambda)$:
\begin{equation}
% label removed: eq:vir-LHS-second
m_2(T,m_2(T,T;\mu);\ell)
= \partial^2 T
 + (3\ell + 2\mu)\,\partial T
 + 2(\ell^2 + 2\ell\mu)\,T
 + \frac{c}{12}(\ell^4 + 2\mu\ell^3).
\end{equation}

\smallskip
\emph{Difference.} Alternatively, the PVA Jacobi identity gives $A_3(\ell,\mu) = -\{T_\mu\{T_\ell T\}\}$ directly. Computing:
\begin{equation}
% label removed: eq:vir-associator
\boxed{%
A_3(\lambda_1,\lambda_2)
= -\partial^2 T
 - (2\lambda_1 + 3\lambda_2)\,\partial T
 - 2\lambda_2(2\lambda_1 + \lambda_2)\,T
 - \frac{c}{12}\lambda_2^3(2\lambda_1 + \lambda_2).
}
\end{equation}

\medskip
\noindent\textbf{From the associator to $m_3$: the normally ordered product.}
The $\lambda$-bracket is the singular part of the full OPE\@.
The full vertex algebra OPE is associative (Borcherds identity),
so the non-associativity $A_3 \neq 0$ of the singular part
is compensated by the regular part (the normally ordered product~$:TT:$).
Decomposing $m_2^{\mathrm{full}} = m_2^{\mathrm{sing}} + m_2^{\mathrm{reg}}$
and projecting associativity to the one-generator PVA:
\[
A_3^{\mathrm{sing}} + m_3 = 0,
\qquad
m_3 = -A_3.
\]
This is the unique ternary operation making the chiral $A_\infty$ structure
on the PVA consistent with the associativity of the full vertex algebra.
\begin{equation}
% label removed: eq:vir-m3
\boxed{%
m_3(T,T,T;\lambda_1,\lambda_2)
= \partial^2 T
 + (2\lambda_1 + 3\lambda_2)\,\partial T
 + 2\lambda_2(2\lambda_1 + \lambda_2)\,T
 + \frac{c}{12}\lambda_2^3(2\lambda_1 + \lambda_2).
}
\end{equation}

\begin{remark}[Consistency checks on $m_3$]
% label removed: rem:m3-checks
\leavevmode
\begin{enumerate}
\item \emph{Conformal weight.} Each monomial in~\eqref{eq:vir-m3}
 has total weight~$2$ (spin of~$T$) plus degree from~$\lambda_i$,
 consistent with $|m_3| = 2-3 = -1$ in the bar complex.
\item \emph{$c = 0$ limit.} When $c = 0$,
 $m_3 = \partial^2 T + (2\lambda_1 + 3\lambda_2)\,\partial T
 + 2\lambda_2(2\lambda_1 + \lambda_2)\,T$:
 the normally ordered product $:TT:$ still contributes
 (the Witt algebra $\lambda$-bracket is not associative either).
\item \emph{Polynomiality.} The formula is polynomial
 in $\lambda_1, \lambda_2$ (no negative powers), reflecting
 locality of the FM integral over~$\FM_3(\C)$.
\item \emph{Structural origin.} The $\partial^2 T$ and
 $\partial T$ terms arise from the OPE $\{:TT:{}_\lambda T\}$
 (modes $n \le 2$); the $T$ and scalar terms from
 the skew-symmetry contribution $\{T_\lambda {:TT:}\}$.
\end{enumerate}
\end{remark}

\textbf{Generating Function for All $m_k$:}

Define the generating series
\begin{equation}
% label removed: eq:vir-gen-func
\mathcal{M}_{\text{Vir}}(T; \lambda_1, \ldots, \lambda_{k-1}) = \sum_{k=1}^\infty \frac{1}{k!} m_k(T^{\otimes k})(\lambda_1, \ldots, \lambda_{k-1}).
\end{equation}

\begin{theorem}[Recursive Structure of Virasoro $A_\infty$ Operations]
% label removed: thm:vir-recursive
Assume that the Khan--Zeng Virasoro realization satisfies the KZ
analytic SDR package of
Assumption~\textup{\ref{assum:kz-analytic-sdr-package}}.
The generating function $\mathcal{M}_{\text{Vir}}$ satisfies a functional equation:
\begin{equation}
\mathcal{M}_{\text{Vir}} = Q_{\text{class}} \mathcal{M}_{\text{Vir}} + \frac{1}{2} \{\mathcal{M}_{\text{Vir}}, \mathcal{M}_{\text{Vir}}\}_\lambda + \mathcal{O}(\hbar),
\end{equation}
where $Q_{\text{class}}$ is the classical BRST operator and the curly bracket is the Poisson $\lambda$-bracket. This is the \emph{master equation} for deformations of the Virasoro PVA.
\end{theorem}

\begin{proof}
Under Assumption~\ref{assum:kz-analytic-sdr-package}, the finite-jet
BV quotients satisfy the quantum master equation
$\tfrac{1}{2}\{S_{\mathrm{BV}}, S_{\mathrm{BV}}\}_{\mathrm{BV}}
+ \hbar\Delta S_{\mathrm{BV}} = 0$ and are compatible under
truncation. The effective action
$S_{\mathrm{eff}} = \sum_k \frac{1}{k!} S_k$ encodes the operations
$m_k$. Identifying
$\mathcal{M}_{\mathrm{Vir}} = S_{\mathrm{eff}}|_{T\text{-sector}}$,
the master equation at degree $n$ reads:
\[
Q_{\mathrm{class}}\, m_n + \sum_{\substack{i+j=n+1\\i,j\ge 2}} \sum_{s} (-1)^{\epsilon(s,j)} m_i(\ldots, m_j(\ldots), \ldots) + \hbar\,(\text{1-loop contribution to } m_n) = 0.
\]
At classical level ($\hbar = 0$), this is the Maurer--Cartan equation for the $\lambda$-bracket: $Q_{\mathrm{class}} m_n^{(0)} + \frac{1}{2}\{m_{n-1}^{(0)}, m_{n-1}^{(0)}\}_\lambda = 0$, encoding the iterative construction of tree-level operations from lower-degree ones. The $\frac{1}{2}\{\cdot, \cdot\}_\lambda$ term comes from the two ways to split $n$ inputs into two groups and compose via $m_2$.

At 1-loop ($\hbar^1$), the BV Laplacian $\Delta$ contributes by contracting a pair of fields within a single vertex, producing the $\mathcal{O}(\hbar)$ correction. For Virasoro, this is the ghost loop $\langle\mu\mu\rangle$ producing the central charge shift (Theorem~\ref{thm:central-charge-shift}).

The functional equation is thus the component-by-component restatement of the BV master equation, with the Poisson $\lambda$-bracket $\{\cdot, \cdot\}_\lambda$ encoding the classical part and $\mathcal{O}(\hbar)$ the quantum corrections.
\end{proof}

\subsubsection{Spectral $r$-Matrix}

The spectral $r$-matrix for Virasoro is a two-tensor encoding the Poisson structure in spectral parameters.

\begin{definition}[Virasoro Laplace Kernel $r$-Matrix]
% label removed: def:vir-r-matrix
%: This is the Laplace kernel r^L(z), not the collision residue r^{coll}(z).
% Collision residue: r^{coll}(z) = (c/2)/z^3 + 2T/z (poles at odd orders).
% Laplace kernel: poles at z^{-1}, z^{-2}, z^{-4}.
The Laplace kernel (Proposition~\ref{prop:field-theory-r}) is
\begin{equation}
r^{L,\text{Vir}}(z)
= \frac{(\partial T) \otimes \mathbf{1}}{z}
+ \frac{(T \otimes \mathbf{1} + \mathbf{1} \otimes T)}{z^2}
+ \frac{(c/2)\,\mathbf{1} \otimes \mathbf{1}}{z^4}.
\end{equation}
The collision residue (bar complex r-matrix, one pole order lower)
is
\begin{equation}
r^{\mathrm{coll},\text{Vir}}(z) = \frac{c/2}{z^3}\,\mathbf{1}\otimes\mathbf{1} + \frac{2T}{z}\otimes\mathbf{1}.
\end{equation}
\end{definition}

\begin{remark}[Virasoro $r$-matrix as endomorphism-valued]
% label removed: rem:vir-r-endomorphism
The Virasoro $r$-matrix lives in $\mathrm{End}(V) \otimes \mathrm{End}(V)((z^{-1}))$, where $V$ is a highest-weight $\mathrm{Vir}_c$-module, not in $\mathrm{Vir}_c \otimes \mathrm{Vir}_c((z^{-1}))$ (which would require a convergent Casimir sum over the infinite-dimensional Lie algebra). The ``first slot acts'' convention writes $T$ for the action of the stress tensor on the first tensor factor.
\end{remark}

The $r$-matrix satisfies the \emph{classical Yang--Baxter equation} (CYBE):
\begin{equation}
% label removed: eq:vir-CYBE
[r^{12}(\lambda_1-\lambda_2), r^{13}(\lambda_1-\lambda_3)] + [r^{12}(\lambda_1-\lambda_2), r^{23}(\lambda_2-\lambda_3)] + [r^{13}(\lambda_1-\lambda_3), r^{23}(\lambda_2-\lambda_3)] = 0,
\end{equation}
which follows from the Jacobi identity for the Virasoro $\lambda$-bracket.

\begin{computation}[Virasoro CYBE verification]
% label removed: comp:vir-CYBE
We verify the classical Yang--Baxter equation~\eqref{eq:vir-CYBE}
for the Virasoro Laplace kernel in the spectral-parameter form
(Proposition~\ref{prop:field-theory-r}):
\[
r^L(z)
= \int_0^\infty e^{-\lambda z} \{T_\lambda T\}\,d\lambda
= \frac{\partial T}{z} \otimes \mathbf{1}
 + \frac{2T}{z^2} \otimes \mathbf{1}
 + \frac{c}{2z^4}\,\mathbf{1}\otimes\mathbf{1}.
\]
The collision residue $r^{\mathrm{coll}}(z) = (c/2)/z^3\,
\mathbf{1}\otimes\mathbf{1} + 2T/z\otimes\mathbf{1}$ has pole
orders one lower (Volume~I, Remark~\ref{V1-rem:three-r-matrices}).
Since the Virasoro PVA has a single generator~$T$, the $r$-matrix
acts on $V \otimes V$ with $V = \C\langle T \rangle$.
For the CYBE with three copies $V_1 \otimes V_2 \otimes V_3$ and
spectral parameters $u, v$, one verifies
\[
[r^{12}(u),\, r^{13}(u+v)]
+ [r^{12}(u),\, r^{23}(v)]
+ [r^{13}(u+v),\, r^{23}(v)]
= 0.
\]
The central term $\frac{c}{2z^4}\,\mathbf{1}\otimes\mathbf{1}$
commutes with everything, so it drops out of all brackets.
The terms involving $T$ and $\partial T$ contribute through the
Lie bracket $[T \otimes \mathbf{1}, \mathbf{1} \otimes T] = 0$
(in different tensor factors) and
$[T \otimes \mathbf{1},\, T \otimes \mathbf{1}] = 0$ (abelian in
each factor). The cross-factor commutators
$[r^{12}(u), r^{23}(v)]$ produce terms proportional to
$T_1 \otimes [T_2, T_2] \otimes T_3$, which vanish because
the Virasoro generators in the same slot commute as classical
fields. The only potentially nonzero contributions come from the
$\partial T$ and $T$ terms acting on different copies, and these
cancel by the Jacobi identity for $\{T_\lambda T\}$.
Explicitly, the Jacobi identity
$\{T_\lambda\{T_\mu T\}\} - \{T_\mu\{T_\lambda T\}\}
= \{\{T_\lambda T\}_{\lambda+\mu} T\}$
becomes, after Laplace transform in both $\lambda$ and $\mu$,
exactly the CYBE for $r(z)$. This is the standard
correspondence between the PVA Jacobi identity and the CYBE
established in Proposition~\ref{prop:field-theory-r}.
\end{computation}

\textbf{Quantization:} The quantized $R$-matrix admits a
perturbative expansion in $\hbar$ (the inverse level):
\begin{equation}
% label removed: eq:vir-R-expansion
R^{\text{Vir}}(\lambda, \mu; \hbar)
= \mathbf{1} \otimes \mathbf{1}
 + \hbar\, r^{\text{Vir}}(\lambda,\mu)
 + \hbar^2 \Bigl[\tfrac{1}{2}\, r^{\text{Vir}} \cdot r^{\text{Vir}}
 + \delta r_{\text{loop}}\Bigr]
 + \mathcal{O}(\hbar^3),
\end{equation}
where the $\hbar^2$ coefficient has two contributions:
\begin{itemize}
\item The \emph{tree-level iteration}
$\tfrac{1}{2}\,r^{\text{Vir}} \cdot r^{\text{Vir}}$, which is
the composition of two classical exchanges (the ``$r^2/2$''
term required by the quantum Yang--Baxter equation at order
$\hbar^2$ if $r$ alone satisfies the CYBE);
\item The \emph{one-loop correction} $\delta r_{\text{loop}}$,
arising from the self-energy of the Virasoro propagator
$\langle T\mu \rangle$ through the ghost loop.
\end{itemize}

The one-loop correction in the $T$--$T$ channel takes the form
\begin{equation}
% label removed: eq:vir-delta-r-loop
\delta r_{\text{loop}}(\lambda,\mu)
= \sum_{n,m \ge 0}
 \frac{\gamma_{nm}}{\lambda^{n+1}\,\mu^{m+1}}
 \;\bigl(L_n \otimes L_m\bigr),
\end{equation}
where $L_n$ are the Virasoro modes and $\gamma_{nm}$ are determined
by the one-loop integral
\[
\gamma_{nm}
= \oint \oint
 \frac{dw_1\, dw_2}{(2\pi i)^2}\;
 \frac{w_1^{n+1}\, w_2^{m+1}}{(w_1 - w_2)^2}
 \;\langle \mu(w_1)\, \mu(w_2) \rangle_{\text{ghost}},
\]
with $\langle \mu \mu \rangle_{\text{ghost}}$ the ghost propagator
from the $\tfrac{c}{24}\mu\partial^3\mu$ vertex. This ghost loop
is the diagrammatic origin of the \emph{central charge shift}:
the one-loop contribution renormalises the classical central charge
$c$ to the quantum value $c - 26$, or equivalently shifts by
$\Delta c = -26$. In the BV-BRST framework, the shift arises
because the ghost determinant contributes $c_{\text{gh}} = -26$,
so the total quantum central charge is $c_{\text{total}} = c + c_{\text{gh}} = c - 26$.
The self-dual point $c = 13$ (where
$\mathrm{Vir}_c^! = \mathrm{Vir}_{26-c}$ equals $\mathrm{Vir}_c$)
is precisely where the tree-level and one-loop contributions balance:
$c_{\text{total}} = c - 26 = -13 = -(26 - c)$. This is the unique
$\mathcal{W}_N$ self-dual point satisfying
$K_N = c^*_N$, because
$K_N/c^*_N = 2(H_N - 1)$ equals~$1$ only at $N = 2$ (where
$H_2 = 3/2$); for $N \ge 3$ the ratio exceeds~$1$.

\begin{remark}[Fusion kernel and non-perturbative resummation]
% label removed: rem:vir-fusion-kernel
The expected non-perturbative completion of the full quantum
$R$-matrix $R^{\text{Vir}}(\lambda,\mu;\hbar)$ is the
Ponsot--Teschner Virasoro fusion kernel~\cite{PT01}. This comparison
is meaningful only after fixing the four external Liouville momenta,
the $s$- and $t$-channels, the PT contour, and the conformal-block
normalization. In that normalization the fusion kernel is written with
double sine functions $S_b$, satisfies the Moore--Seiberg
braid/pentagon relations, and has a semiclassical expansion whose
leading term is the Virasoro classical $r$-matrix. The perturbative
expansion~\eqref{eq:vir-R-expansion} supplies the local comparison
surface; it is not by itself an identification.
\end{remark}

\subsubsection{Chiral Hochschild Cochains}

The chiral Hochschild complex $\CH^\bullet_{\text{ch}}(\text{Vir})$ governs deformations of the Virasoro $A_\infty$ structure.

\begin{definition}[Chiral Hochschild Cochains for Virasoro]
A chiral Hochschild $k$-cochain is a multilinear map
\begin{equation}
\varphi_k: T^{\otimes k} \to T((\lambda_1))\cdots((\lambda_{k-1})),
\end{equation}
satisfying sesquilinearity and compatibility with the BRST differential $Q$.
\end{definition}

The differential on $\CH^\bullet_{\text{ch}}(\text{Vir})$ is the Hochschild differential:
\begin{equation}
% label removed: eq:hochschild-diff
d_{\text{Hoch}} \varphi_k = \sum_{i=0}^k (-1)^i \varphi_k \circ_i m_2 + \sum_{i=1}^{k-1} (-1)^{k+i} m_2 \circ_i \varphi_k,
\end{equation}
where $\circ_i$ denotes operadic composition at the $i$-th input.

\begin{proposition}[Virasoro Hochschild Cohomology]
% label removed: prop:vir-hochschild
Let\/ $\cA$ be a logarithmic\/ $\SCchtop$-algebra.
The chiral Hochschild cohomology $HH^\bullet_{\text{ch}}(\text{Vir}_c)$ is isomorphic
to the space of infinitesimal deformations of the Virasoro $A_\infty$ structure on a
smooth curve. By Vol~I Theorem~H (polynomial growth, concentration on a smooth curve,
at generic level/charge; the critical locus $c_{\mathrm{crit}}$ analogous to $k = -h^\vee$
is excluded because $\dim \ChirHoch^0$ can be infinite there, see Vol~I
Remark~\ref*{rem:critical-level-lie-vs-chirhoch}),
it is concentrated in cohomological degrees $\{0,1,2\}$. At generic central charge $c \neq 0$:
\begin{itemize}
\item $HH^0_{\text{ch}}(\text{Vir}_c) \cong \C$ (the vacuum / center);
\item $HH^1_{\text{ch}}(\text{Vir}_c) = 0$ (all derivations are inner);
\item $HH^2_{\text{ch}}(\text{Vir}_c) \cong \C$, with generator $\Theta_c$ corresponding
 to the central-charge deformation $c \mapsto c + \epsilon$;
\item $HH^n_{\text{ch}}(\text{Vir}_c) = 0$ for $n \geq 3$.
\end{itemize}
\textbf{Caution.} This is NOT the Gel'fand--Fuchs cohomology of $\mathrm{Diff}(S^1)$,
which is infinite-dimensional. The chiral Hochschild cohomology lives on a one-dimensional
algebraic curve and is bounded by Vol~I Theorem~H; the Hilbert series
$P_{\text{Vir}_c}(t) = 1 + t^2$ is a polynomial of degree~$2$. ``Polynomial growth''
refers to the Hilbert series being a polynomial, not to $HH^\bullet$ being a polynomial
ring on $\Theta$: the cup product $\Theta_c \smile \Theta_c$ vanishes in $HH^4 = 0$.
\end{proposition}

\subsection{Example 2: $W_3$ Algebra (Spin-$(2,3)$ W-algebra), Classical Structure}
% label removed: subsec:W3

The $W_3$ algebra is the simplest nontrivial higher-spin W-algebra, containing both spin-2 and spin-3 primary fields.

\subsubsection{Classical Structure}

The $W_3$ Poisson vertex algebra is generated by two fields:
\begin{itemize}
\item $T$ of spin 2 (the stress tensor);
\item $W$ of spin 3 (the higher-spin current).
\end{itemize}

The $\lambda$-brackets are (from \cite{KZ25}):
\begin{align}
% label removed: eq:w3-lambda-TT
\{T_\lambda T\} &= \partial T + 2T\lambda + \frac{c}{12}\lambda^3,\\
% label removed: eq:w3-lambda-TW
\{T_\lambda W\} &= \partial W + 3W\lambda,\\
% label removed: eq:w3-lambda-WW
\{W_\lambda W\} &= \frac{c}{360}\lambda^5 + \frac{1}{3}T\lambda^3 + \frac{1}{2}(\partial T)\lambda^2 + \biggl(\frac{32}{5c + 22}\Lambda + \frac{3}{10}\partial^2 T\biggr)\lambda + \frac{16}{5c + 22}\partial\Lambda + \frac{1}{15}\partial^3 T,
\end{align}

\noindent
where $\Lambda := {:\!TT\!:} - \tfrac{3}{10}\partial^2 T$ is the quasi-primary composite field of spin~$4$ (note the \textbf{minus} sign).

\begin{remark}[Structure of $W_3$]
The $\{W_\lambda W\}$ bracket has the richest structure, containing:
\begin{itemize}
\item A quintic term $\lambda^5$ (generalized Schwarzian for spin-3);
\item Cubic and quadratic terms involving $T$ (mixing between spin-2 and spin-3);
\item Linear and constant terms encoding the OPE.
\end{itemize}
\end{remark}

\subsubsection{3D Field Theory}

The fields are:
\begin{align}
T &= T_{zz}(t,z,\bar{z}) (dz)^{\otimes 2}, & |T| = 0,\\
W &= W_{zzz}(t,z,\bar{z}) (dz)^{\otimes 3}, & |W| = 0,\\
\mu &= (\mu^t_z dt + \mu^{\bar{z}}_z d\bar{z}) \otimes \frac{\partial}{\partial z}, & |\mu| = -1,\\
\chi &= (\chi^t_{zz} dt + \chi^{\bar{z}}_{zz} d\bar{z}) \otimes (dz)^{\otimes 2} \otimes \frac{\partial}{\partial z}^{\otimes 2}, & |\chi| = -2.
\end{align}

The action is
\begin{align}
% label removed: eq:w3-action
S_{W_3} &= \int_{\R \times \C} \Big[ \mu (d_t + \bar{\partial})T + \chi (d_t + \bar{\partial})W \notag\\
&\quad + T \mu \partial \mu + \frac{c}{24} \mu \partial^3 \mu + 3W \mu \partial \chi \notag\\
&\quad + \frac{1}{3}T \chi \partial^3 \chi + \frac{1}{2}(\partial T) \chi \partial^2 \chi + \frac{32}{5c+22}\Lambda\, \chi \partial \chi + \frac{3}{10}(\partial^2 T)\,\chi \partial \chi \notag\\
&\quad + \frac{16}{5c+22}(\partial\Lambda)\, \chi \chi + \frac{1}{15}(\partial^3 T)\,\chi \chi + \frac{c}{360} \chi \partial^5 \chi \Big].
\end{align}

This is the most general 3D HT action compatible with the $W_3$ $\lambda$-brackets \eqref{eq:w3-lambda-TT}--\eqref{eq:w3-lambda-WW}.

\subsubsection{Propagators}

The free propagators are:
\begin{align}
\langle T(z_1) \mu(z_2) \rangle &= \frac{\Theta(t_1-t_2)}{2\pi(z_1-z_2)},\\
\langle W(z_1) \chi(z_2) \rangle &= \frac{\Theta(t_1-t_2)}{2\pi(z_1-z_2)}.
\end{align}

%% =====================================
%% W_3 Koszul dual under DS-bar compatibility and chiral Koszulness
%% =====================================

\subsubsection{Koszul dual of $\mathcal{W}_3$}
\label{subsubsec:w3-koszul-dual}
\index{Koszul dual!W3 algebra@$\mathcal{W}_3$ algebra|textbf}%
\index{W-algebra!Koszul dual of W3@Koszul dual of $\mathcal{W}_3$}%

The Virasoro Koszul duality $\mathrm{Vir}_c^! = \mathrm{Vir}_{26-c}$
(Proposition~\ref{prop:gravity-koszul-dual})
generalises to $\mathcal{W}_3$ by incorporating the spin-$3$ ghost
system.

\begin{theorem}[Same-family Koszul dual of $\mathcal{W}_3$ under DS/bar transport]
\label{thm:w3-koszul-dual}
Assume the DS/bar transport package identifying the filtered-complete
Koszul dual with the principal same-family DS reduction. Then the
Koszul dual of the $\mathcal{W}_3$ algebra at central charge~$c$ is
\begin{equation}
\label{eq:w3-koszul-dual}
\mathcal{W}_{3,c}^!
\;\simeq\;
\mathcal{W}_{3,\,100-c}.
\end{equation}
The companion involution is $c \mapsto 100 - c$, with fixed central
charge $c = 50$. The coefficient
$\beta_{\partial\Lambda} = 16/(22+5c)$ of $\partial\Lambda$ in
$\{W_\lambda W\}$, equivalently the coefficient
$\beta_{\Lambda}=32/(22+5c)$ of $\Lambda$, transforms
to $\beta'_0 = 16/(522 - 5c)$.
\end{theorem}

\begin{proof}
Each generator of $\mathcal{W}_3$ contributes a $bc$-ghost system
upon BV-BRST quantization of the Khan--Zeng 3D HT action.
The ghost central charge for spin~$s$ is
$c_{\mathrm{gh}}(s) = -2(6s^2 - 6s + 1)$:
\[
c_{\mathrm{gh}}(2) = -26, \qquad
c_{\mathrm{gh}}(3) = -74, \qquad
c_{\mathrm{gh}}^{\mathrm{total}} = -100.
\]
This is the $N = 3$ specialisation of
$\alpha_N = 2(N{-}1)(2N^2{+}2N{+}1)$
(Proposition~\ref{prop:wn-complementarity}):
$\alpha_3 = 2 \cdot 2 \cdot 25 = 100$.

The Verdier dual pairing $D_{\mathrm{Ran}}(\barB(\mathcal{W}_{3,c}))
\simeq \barB(\mathcal{W}_{3,c}^!)$ acts through the BPZ
(Shapovalov) inner product on weight spaces, shifting $c \mapsto 100 - c$.
The assertion that the Koszul dual is again a $\mathcal{W}_3$ algebra
(rather than some deformation) is exactly the DS/bar input:
it follows from chiral Koszulness
(Theorem~\ref{thm:one-loop-koszul}, applied to the affine
pre-image $V_k(\mathfrak{sl}_3)$) and the DS-bar intertwining
theorem (Volume~I): DS reduction preserves the spin spectrum,
and bar-cobar commutes with DS reduction.

The $WW$ structure constant transforms by Zamolodchikov's
uniqueness theorem: $\beta_{\partial\Lambda}=16/(22+5c)$ and
$\beta_{\Lambda}=32/(22+5c)$ are determined by $c$ through the
Jacobi identity, so $c \mapsto 100 - c$ gives
$\beta'_0 = 16/(522 - 5c)$.
\end{proof}

\begin{remark}[The general $\mathcal{W}_N$ Koszul involution]
\label{rem:wn-koszul-involution}
\index{Koszul involution!W-algebra@$\mathcal{W}_N$}%
For general principal $\mathcal{W}_N$, the complementarity constant
$\alpha_N = 2(N{-}1)(2N^2{+}2N{+}1)$
(Proposition~\ref{prop:wn-complementarity}) gives
the Koszul involution $c \mapsto \alpha_N - c$, with:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcccc}
\toprule
$N$ & $\alpha_N$ & Self-dual $c$ & $K_{\mathcal{W}_N}$ & Critical $c$ \\
\midrule
$2$ (Virasoro) & $26$ & $13$ & $13$ & $26$ \\
$3$ & $100$ & $50$ & $250/3$ & $100$ \\
$4$ & $246$ & $123$ & $1599/6$ & $246$ \\
General & $2(N{-}1)(2N^2{+}2N{+}1)$ & $\alpha_N/2$ & $(H_N{-}1)\alpha_N$ & $\alpha_N$ \\
\bottomrule
\end{tabular}
\end{center}
Here $K_{\mathcal{W}_N} = \kappa + \kappa^! = (H_N - 1)\alpha_N$
is the complementarity sum
(Proposition~\ref{prop:complementarity-sum-formula} below),
and the critical central charge $c_{\mathrm{crit}} = \alpha_N$
is the matter-ghost cancellation point for $\mathcal{W}_N$ strings.
The $\mathcal{W}_3$ self-dual point $c = 50$ plays the role for
higher-spin gravity that $c = 13$ plays for pure gravity.
\end{remark}

\begin{proposition}[Complementarity sum formula]
\label{prop:complementarity-sum-formula}
\index{complementarity sum!general formula|textbf}
For the principal $\mathcal{W}_N$ algebra at central charge~$c$,
\begin{equation}\label{eq:complementarity-sum-formula}
K_N \;:=\; \kappa(\mathcal{W}_{N,c})
 + \kappa(\mathcal{W}_{N,\alpha_N - c})
\;=\; (H_N - 1)\,\alpha_N,
\end{equation}
where $H_N = \sum_{j=1}^N 1/j$ is the $N$-th harmonic number
and $\alpha_N = 2(N{-}1)(2N^2{+}2N{+}1)$. The ratio
$K_N/c_N^* = 2(H_N - 1)$ equals~$1$ if and only if $N = 2$
\textup{(}Virasoro\textup{)}: the unique $\mathcal{W}_N$ algebra
where the complementarity sum equals the self-dual central charge.
\end{proposition}

\begin{proof}
The curvature of $\mathcal{W}_{N,c}$ is
$\kappa(\mathcal{W}_{N,c}) = c\,(H_N - 1)$, where $H_N - 1
= \sum_{s=2}^N 1/s$ is the contribution-per-unit-central-charge
from each spin-$s$ generator. The Koszul involution
$c \mapsto \alpha_N - c$
(Proposition~\ref{prop:wn-complementarity}) gives
$\kappa(\mathcal{W}_{N,\alpha_N - c}) = (\alpha_N - c)(H_N - 1)$.
The sum is $K_N = \alpha_N(H_N - 1)$, independent of~$c$.
The ratio $K_N/c_N^* = 2(H_N - 1) = 1$ iff $H_N = 3/2$, which
holds iff $N = 2$ (since $H_3 = 11/6 > 3/2$).
\end{proof}

\begin{remark}[The ghost identity]%
\label{rem:ghost-identity-alphaN}%
\index{ghost central charge!WN@$\mathcal{W}_N$ identity}%
The critical central charge $\alpha_N$ has a direct
physical origin: it equals $|c_{\mathrm{ghost}}(\cW_N)|$.
The $\cW_N$ ghost system consists of $bc$-pairs of
spins $s = 2, 3, \ldots, N$, each contributing
$c_s = -2(6s^2 - 6s + 1)$. Summing:
$c_{\mathrm{ghost}} = \sum_{s=2}^{N} c_s
= -2(N{-}1)(2N^2{+}2N{+}1) = -\alpha_N$.
The critical string condition $c = \alpha_N$ is
therefore $c_{\mathrm{matter}} + c_{\mathrm{ghost}} = 0$.
\end{remark}

\begin{remark}[Self-dual halving]%
\label{rem:self-dual-halving}%
\index{self-dual point!genus tower halving}%
At the Koszul self-dual point $c^* = \alpha_N/2$,
the curvature $\kappa(\cW_{N,c^*}) = c^*(H_N - 1)
= \tfrac{1}{2}\alpha_N(H_N - 1)
= \tfrac{1}{2}\kappa(\cW_{N,\alpha_N})$.
At genus~$1$, where the scalar formula
$F_1 = \kappa \cdot \lambda_1^{\mathrm{FP}}$ holds
unconditionally for all families, this gives
$F_1(c^*) = \tfrac{1}{2}\,F_1(\alpha_N)$.
For uniform-weight algebras (Virasoro, $N = 2$) the
scalar formula $F_g = \kappa\cdot\lambda_g^{\mathrm{FP}}$
holds at all genera, so the halving extends:
$F_g(c^*) = \tfrac{1}{2}\,F_g(\alpha_N)$ for all~$g \ge 1$.
For $N \ge 3$ ($\cW_N$ is multi-weight), genus~$\ge 2$
receives cross-channel corrections
$\delta F_g^{\mathrm{cross}} \ne 0$
(Volume~I, Theorem~\textup{\ref{V1-thm:multi-weight-genus-expansion}}),
so the halving is exact only at genus~$1$.
\end{remark}

\begin{remark}[Mumford exponent $=$ Koszul self-dual point]
\label{rem:mumford-koszul}
\index{Mumford isomorphism!Koszul connection}
For the Virasoro algebra, both the Mumford isomorphism
$\det{}'_\zeta\Delta \sim \lambda^{\otimes 13}$ and the Koszul
self-duality $\mathrm{Vir}_{13}^! = \mathrm{Vir}_{13}$ yield the
number~$13 = |c_{\mathrm{ghost}}|/2 = 26/2$. For the general
$\mathcal{W}_N$ family, the Grothendieck--Riemann--Roch computation
$c_1(\det\pi_*\omega_C^{\otimes s}) = (6s^2-6s+1)\lambda_1$
(Mumford) gives the total ghost Hodge degree
$\sum_{s=2}^N(6s^2-6s+1) = \alpha_N/2$, which equals the
Koszul self-dual central charge $c_N^* = \alpha_N/2$
\textup{(}Proposition~\textup{\ref{prop:complementarity-sum-formula})}.
Both invariants trace to the same source: the conformal anomaly
of the spin-$s$ ghost system, summed over $s = 2,\ldots,N$.
At genus~$1$, the self-dual halving gives
$F_1(c^*) = (\alpha_N/4)\lambda_1^{\mathrm{FP}}$,
the genus-$1$ invariant evaluated at the Mumford exponent.
For $N = 2$ (Virasoro, uniform-weight), the scalar formula
extends to all genera: $F_g(c^*) = (\alpha_2/4)\lambda_g^{\mathrm{FP}}
= (13/2)\lambda_g^{\mathrm{FP}}$.
For $N \ge 3$ (multi-weight), the all-genera formula receives
cross-channel corrections at $g \ge 2$
(Volume~I, Theorem~\ref{V1-thm:multi-weight-genus-expansion}).
\end{remark}

%% =====================================
%% W_N to higher-spin gauge theory
%% =====================================

\subsection{From \texorpdfstring{$\mathcal{W}_N$}{W\_N} to higher-spin gauge theory}
% label removed: subsec:wn-higher-spin

\providecommand{\ModEnv}{\operatorname{ModEnv}}

The $\mathcal{W}_N$ Poisson vertex algebra provides the chiral-algebraic
input for a family of 3d holomorphic-topological gauge theories of
increasing spin, connecting to higher-spin gravity in the $N \to \infty$
limit.

\begin{definition}[$\mathcal{W}_N$ field content]
% label removed: def:wn-field-content
The $\mathcal{W}_N$ PVA has generators $W_s$ of spin~$s$ for
$s = 2, 3, \ldots, N$, with $W_2 = T$ the Virasoro element. The
associated 3d HT Poisson sigma model has field pairs $(W_s, \chi_s)$
for each $s = 2, \ldots, N$, where $\chi_s$ is the topological partner
of spin $1-s$ \textup{(}\!\cite{KZ25}, \S3.4\textup{)}.
\end{definition}

\begin{proposition}[Slab central charges for $\mathcal{W}_N$]
% label removed: prop:wn-slab-central-charges
The topological enhancement from the Virasoro subalgebra $T \subset
\mathcal{W}_N$ produces a slab reduction with paired central charge
\textup{(}\!\cite{KZ25}, \S3.4\textup{)}:
\begin{equation}% label removed: eq:wn-cpair
c_{\mathrm{pair}}^{(N)}
\;=\;
\sum_{s=2}^{N} \bigl[3(2s-1)^2 - 1\bigr].
\end{equation}
The first values are:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lccccc}
\toprule
$N$ & $2$ & $3$ & $4$ & $5$ & $\infty$ \\
\midrule
$c_{\mathrm{pair}}^{(N)}$ & $26$ & $100$ & $246$ & $488$ & $\infty$ \\
\bottomrule
\end{tabular}
\end{center}
In particular, $c_{\mathrm{pair}}^{(2)} = 26$ is the critical dimension of
the bosonic string, and $c_{\mathrm{pair}}^{(3)} = 100$ matches the
$\mathcal{W}_3$ computation of Vol~I.
\end{proposition}

\begin{remark}[$\mathcal{W}_\infty$ and higher-spin gravity]
% label removed: rem:winfty-higher-spin
In the $N \to \infty$ limit, $\mathcal{W}_\infty$ produces
$c_{\mathrm{pair}} \to \infty$, signaling a decompactification of the
topological direction. The infinite tower of fields
$(W_s, \chi_s)_{s \geq 2}$ is the holomorphic-topological higher-spin
field tower suggested by the Vasiliev/Henneaux--Teitelboim picture.
Identifying this tower with a full higher-spin gravity theory requires
the quantum BV and boundary-condition data stated in
Remark~\ref{rem:W-hypotheses}. The $\mathcal{W}_\infty$ modular
envelope $\ModEnv(\mathcal{W}_\infty)$ is the candidate MC4-closed
comparison package from Vol~I
\textup{(}cf.~the concordance, \S\textup{MC4}\textup{)}.
Volume~I proves that $\mathcal{W}_\infty$ has a one-dimensional
minimal cyclic direction,
\[
\dim H^2_{\mathrm{cyc}}(\mathcal{W}_\infty, \mathcal{W}_\infty)=1,
\]
and computes the explicit weight-$4$ structure constant
\[
c_{334}^2=\frac{42c^2(5c+22)}{(c+24)(7c+68)(3c+46)}.
\]
\end{remark}

%% =====================================
%% Shadow depth classification for all principal W_N
%% =====================================

\subsection{Shadow depth for principal
\texorpdfstring{$\mathcal{W}_N$}{W\_N} under KZ/DS split projection}
\label{subsec:wn-class-M}

Under the analytic SDR and wheel-residue hypotheses of
Proposition~\ref{prop:vir-truncation}, the Virasoro wheel sector
projects into every principal $\mathcal{W}_N$ algebra ($N \ge 2$).
The structural reason is minimal: the stress tensor~$T$ sits inside
every $\mathcal{W}_N$, and its cubic vertex
$V_3 = T\mu\partial\mu$ generates candidate wheel diagrams at every
degree.

\begin{theorem}[Class-$\mathbf{M}$ criterion for principal
$\mathcal{W}_N$]
\label{thm:wn-class-M-stable}
%: primary label thm:wn-class-M lives in w-algebras-w3.tex; this is the stable-landscape copy
\index{W-algebra!shadow depth}%
\index{shadow depth!principal W-algebras}%
Assume that the Khan--Zeng/DS realization of the principal
$\mathcal{W}_N$ algebra satisfies the KZ analytic SDR package of
Assumption~\textup{\ref{assum:kz-analytic-sdr-package}}, that the
Virasoro wheel-residue hypothesis of
Proposition~\textup{\ref{prop:vir-truncation}} holds, and that the
projection to the $T$-sector is split by the chosen DS comparison.
Then the projected transferred operations
\[
 \pi_T\,m_k^{\mathcal W_N}(T,\ldots,T)
\]
are nonzero for all $k\ge 3$. Consequently the strict
$\mathcal W_N$ object has class~$\mathbf M$ whenever this projected
nonzero class survives the unprojected DS transfer.
\end{theorem}

\begin{proof}
The argument proceeds in three steps.

\medskip
\emph{Step~1: The Virasoro sub-action.}
The $\mathcal{W}_N$ PVA has generators $W_s$ of spin~$s$ for
$s = 2, 3, \ldots, N$, with $W_2 = T$. The Khan--Zeng 3D HT action
decomposes as
\[
S_{\mathcal{W}_N}
= \underbrace{\int \mu(d_t + \bar\partial)T + T\mu\partial\mu
 + \tfrac{c}{24}\mu\partial^3\mu}_{S_{\mathrm{Vir}}}
\;+\; S_{\mathrm{higher}},
\]
where $S_{\mathrm{higher}}$ collects all vertices involving
$W_s, \chi_s$ for $s \ge 3$. The Virasoro sub-action
$S_{\mathrm{Vir}}$ governs the $T$-sector propagator
$\langle T(z_1)\,\mu(z_2) \rangle = \Theta(t_1-t_2)/(2\pi(z_1-z_2))$
and the cubic vertex $V_3 = T\mu\partial\mu$.

\medskip
\emph{Step~2: Sector decoupling at tree level.}
Consider $m_k(T, \ldots, T)$, the operation with $k$ external
$T$-legs and no $W_s$-legs. At tree+one-loop level, the only
internal propagator that connects two $\mu$-legs at cubic
vertices $V_3$ is $\langle T\mu \rangle$. The higher-spin fields
$(W_s, \chi_s)$ for $s \ge 3$ can appear in diagrams contributing
to $m_k(T, \ldots, T)$ only through vertices that couple at least
one $\chi_s$ to the diagram. But the $T$--$\chi_s$ coupling in
$S_{\mathrm{higher}}$ always requires at least one external
$W_s$-leg or an internal $W_s$-propagator. Since no $W_s$-legs
are prescribed, such diagrams either:
\begin{enumerate}[label=(\alph*)]
\item require a $W_s$-loop (which is a higher-loop correction
 beyond the one-loop wheel), or
\item decouple by $Q$-exactness of intermediate $\chi_s$-states
 in the BRST homotopy (the $W_s$-propagator contracts a
 $Q$-closed state with a $Q$-exact intermediate, giving zero
 on cohomology).
\end{enumerate}
Consequently, at the one-loop level:
\begin{equation}
\label{eq:wn-sector-decoupling}
m_k^{\mathcal{W}_N}(T, \ldots, T)
\;\equiv\; m_k^{\mathrm{Vir}}(T, \ldots, T)
\pmod{\text{higher-loop corrections}}.
\end{equation}

\medskip
\emph{Step~3: Projected wheel non-vanishing.}
By Proposition~\ref{prop:vir-truncation}, the Virasoro wheel class
\[
m_k^{\mathrm{Vir}}(T, \ldots, T)
\;\sim\; \int_{\FM_k(\C) \times \Conf_k^{<}(\R)}
 \prod_{i=1}^k K(z_i - z_{i+1},\, t_i - t_{i+1})\;
 \partial_{z_i}\cdots
\]
is nonzero for all $k \ge 3$ under the wheel-residue survival
hypothesis. The graph mechanism is purely combinatorial: each cubic
vertex $V_3$ has exactly $2$ $\mu$-slots, so the connected one-loop
graph at degree~$k$ is the Hamiltonian cycle $C_k$, which exists for
all $k \ge 3$. The compactified integral and its boundary
renormalization are exactly the analytic content supplied by the KZ SDR
package.

By~\eqref{eq:wn-sector-decoupling}, this one-loop wheel integral
contributes to the projected $T$-sector operation. Higher-loop
diagrams from the $W_s$-sectors may add further terms, but a proof of
the full unprojected statement must also exclude cancellation against
the projected class. Under the split-projection hypothesis this gives
\[
\pi_T\,m_k^{\mathcal{W}_N}(T, \ldots, T) \ne 0
\quad\text{for all } k \ge 3.
\]
Thus the projected $T$-sector operation is nonzero. If this projected
class survives the unprojected DS transfer, then
$m_k^{\mathcal W_N}\ne0$ for all $k\ge3$, and the strict
$\mathcal W_N$ object has class~$\mathbf M$. Without that survival
hypothesis the proof establishes projected class-$\mathbf M$ evidence.
\end{proof}

\begin{remark}[Additional non-vanishing from higher-spin sectors]
\label{rem:wn-additional-diagrams}
\index{W-algebra!higher-spin wheel diagrams}%
The criterion uses only the projected $T$-sector. The higher-spin
generators $W_s$ ($s \ge 3$) contribute additional
candidate operations: for instance, the mixed operations
$m_k(W_{s_1}, \ldots, W_{s_k})$ receive contributions
from wheel diagrams built on higher-spin vertices, plus
additional tree and multi-loop graphs. The $\mathcal{W}_N$
action has interaction vertices of the form
$W_s \chi_{s'} \partial^{a} \chi_{s''}$ whenever the OPE
$\{W_{s\,\lambda} W_{s'}\}$ is nontrivial, providing
valence-2 $\chi$-slots analogous to the $\mu$-slots
in the Virasoro case. These yield additional Hamiltonian
candidate cycles in the $\chi$-edge graph.

For $\mathcal{W}_N$ with $N-1$ generators, the maximum
loop order at degree~$k$ grows with $N$: the Virasoro
$T$-sector contributes at 1-loop, the $W_3$-sector at up to
2-loop, and in general the $W_s$-sector allows diagrams
with up to $(s-1)$-loops from the degree-$(2s-1)$ pole in the
$W_s$-self-OPE (after the $d\log$ bar kernel absorbs one pole order).
\end{remark}

\begin{remark}[Koszulness vs.\ non-formality for $\mathcal{W}_N$]
\label{rem:wn-koszul-nonformality}
\index{W-algebra!Koszulness vs.\ non-formality}%
Under the hypotheses of Theorem~\ref{thm:wn-class-M-stable}, the
principal $\mathcal{W}_N$ has \emph{non-formal} Swiss-cheese
structure: the transferred $\Ainf$ operations $m_k$ do not vanish on
cohomology. This is \emph{not} a failure of chiral Koszulness.
Every principal $\mathcal{W}_N$ is chirally Koszul
\textup{(}by the one-loop exactness criterion,
Theorem~\textup{\ref{thm:one-loop-koszul}},
applied to the affine pre-image, composed with
Drinfeld--Sokolov reduction\textup{)}: bar cohomology is
concentrated, and the Koszul dual
$\mathcal{W}_N^! = \mathcal{W}_{N,\,\alpha_N - c}$
exists as a well-defined algebra. Non-formality means
the SC\textsuperscript{ch,top}-structure
retains genuine higher operations, reflecting the excess
intersection geometry of class~$\mathbf{M}$.
\end{remark}

\subsubsection{Complementarity constants for $\mathcal{W}_N$}
\label{subsubsec:wn-complementarity}

\begin{proposition}[Complementarity constant for $\mathcal{W}_N$]
\label{prop:wn-complementarity}
\index{complementarity constant!W-algebra}%
\index{W-algebra!complementarity constant}%
The complementarity constant of the principal $\mathcal{W}_N$
algebra is
\begin{equation}
\label{eq:wn-complementarity}
\alpha_N
\;=\; \sum_{s=2}^{N} 2(6s^2 - 6s + 1)
\;=\; 2(N-1)(2N^2 + 2N + 1).
\end{equation}
The companion central charge is $\alpha_N-c$, so the characteristic
package of $\mathcal{W}_{N,c}^!$ matches that of
$\mathcal{W}_{N,\,\alpha_N-c}$. The same-family algebra equality
requires DS/bar transport. The companion fixed point is
$c=\alpha_N/2$.
\end{proposition}

\begin{proof}
Each generator $W_s$ of spin~$s$ contributes a ghost system of
conformal weights $(s, 1-s)$ upon BV-BRST quantization of the
Khan--Zeng 3D HT action. The ghost central charge for
spin~$s$ is $c_{\mathrm{gh}}(s) = -2(6s^2 - 6s + 1)$
(the standard $bc$-ghost formula; see \cite{FMS86}).
The total ghost contribution is
$c_{\mathrm{gh}}^{\mathrm{total}}
= \sum_{s=2}^N c_{\mathrm{gh}}(s)
= -\sum_{s=2}^N 2(6s^2 - 6s + 1)
= -\alpha_N$.

For the closed-form evaluation, we compute:
\begin{align*}
\sum_{s=2}^{N}(6s^2 - 6s + 1)
&= 6\sum_{s=2}^{N} s^2 - 6\sum_{s=2}^{N} s
 + \sum_{s=2}^{N} 1 \\
&= 6\Bigl[\tfrac{N(N+1)(2N+1)}{6} - 1\Bigr]
 - 6\Bigl[\tfrac{N(N+1)}{2} - 1\Bigr]
 + (N-1) \\
&= N(N+1)(2N+1) - 3N(N+1) + (N-1) \\
&= N(N+1)(2N-2) + (N-1) \\
&= (N-1)\bigl[2N(N+1) + 1\bigr] \\
&= (N-1)(2N^2 + 2N + 1).
\end{align*}
Multiplying by~$2$ gives~\eqref{eq:wn-complementarity}.

The first values are:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcccccc}
\toprule
$N$ & $2$ & $3$ & $4$ & $5$ & $6$ & General \\
\midrule
$\alpha_N$ & $26$ & $100$ & $246$ & $488$ & $850$
 & $2(N-1)(2N^2+2N+1)$ \\
Self-dual $c$ & $13$ & $50$ & $123$ & $244$ & $425$
 & $(N-1)(2N^2+2N+1)$ \\
\bottomrule
\end{tabular}
\end{center}
The agreement with the slab central charges of
Proposition~\ref{prop:wn-slab-central-charges}
($c_{\mathrm{pair}}^{(N)} = \alpha_N$)
confirms the identity $3(2s-1)^2 - 1 = 2(6s^2 - 6s + 1)$.
\end{proof}

\begin{remark}[Complementarity sum for $\mathcal{W}_N$ vs.\
Kac--Moody]
\label{rem:wn-complementarity-nonzero}
\index{complementarity constant!non-vanishing}%
For Kac--Moody algebras $V_k(\fg)$, the Feigin--Frenkel
involution $k \mapsto -k - 2h^\vee$ ensures
$\kappa + \kappa^! = 0$. For $\mathcal{W}_N$,
the complementarity sum is \emph{not} zero:
$\kappa(\mathcal{W}_{N,c}) + \kappa(\mathcal{W}_{N,c}^!)
= (H_N - 1) \cdot \alpha_N$, where $H_N = \sum_{j=1}^N 1/j$
is the harmonic number and $\alpha_N = 2(N{-}1)(2N^2{+}2N{+}1)$.
The Koszul involution is $c \mapsto \alpha_N - c$, with
self-dual point $c = \alpha_N/2$, but the complementarity sum
is $(H_N - 1) \cdot \alpha_N$, not $\alpha_N/2$.
For Virasoro ($N=2$): $(H_2 - 1) \cdot 26 = 13$.
For $\mathcal{W}_3$: $(H_3 - 1) \cdot 100 = 250/3$.
These coincide only at $N=2$ (where $H_2 - 1 = 1/2$);
for $N \geq 3$, the complementarity sum exceeds the
self-dual central charge.
\end{remark}

\subsubsection{Chiral Hochschild cohomology of $\mathcal{W}_N$}
\label{subsubsec:wn-hochschild}

\begin{computation}[Bulk algebra for $\mathcal{W}_N$]
\label{comp:bulk-wn-stable}
\index{W-algebra!bulk algebra}%
\index{Hochschild cohomology!W-algebra}%
Let $\cA = \mathcal{W}_{N,c}$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item $H^0(C^*_{\mathrm{ch}}(\cA, \cA)) = \Bbbk$.
\item $H^1(C^*_{\mathrm{ch}}(\cA, \cA))
 = \Bbbk\langle \partial_c W_2,\, \partial_c W_3,\,
 \ldots,\, \partial_c W_N \rangle$,
 which is $(N-1)$-dimensional. Each basis element
 $\partial_c W_s$ records the infinitesimal deformation of
 the $\lambda$-brackets under $c \to c + \varepsilon$:
 \[
 \partial_c W_s \;:\;
 W_{s'} \;\longmapsto\;
 \partial_c\{W_{s'\,\lambda}\, W_s\}.
 \]
 These derivations are outer: $\partial_c$ shifts the central
 terms in the OPE without being generated by an inner
 automorphism.
\item The genus-$1$ Hessian is an $(N-1) \times (N-1)$ matrix
 \begin{equation}
 \label{eq:wn-hessian}
 H^{(1)}_N = \bigl(h_{ss'}\bigr)_{2 \le s, s' \le N},
 \end{equation}
 whose entries $h_{ss'}$ are the curvatures of the bulk
 deformation directions. For diagonal entries,
 $h_{ss} = \kappa_c + \delta_s$ where $\delta_s$ depends on
 the structure constants of the $W_s$-self-OPE.
\end{enumerate}

\emph{Explicit cases:}
\begin{itemize}
\item $N = 2$ \textup{(Virasoro):} $H^1 = \Bbbk\langle
 \partial_c\rangle$, one-dimensional
 \textup{(}Computation~\textup{\ref{comp:bulk-virasoro})}.
 Hessian: $1 \times 1$, the scalar $\kappa_c$.
\item $N = 3$ \textup{($\mathcal{W}_3$):} $H^1 = \Bbbk\langle
 \partial_c T, \partial_c W\rangle$, two-dimensional
 \textup{(}Computation~\textup{\ref{comp:bulk-w3})}.
 Hessian: $2 \times 2$, with eigenvalues
 $\kappa_c$ and $\kappa_c + 48/(5c+22)$.
\item $N = 4$ \textup{($\mathcal{W}_4$):} $H^1 = \Bbbk\langle
 \partial_c T, \partial_c W_3, \partial_c W_4\rangle$,
 three-dimensional. The Hessian is $3 \times 3$.
\item $N = 5$ \textup{($\mathcal{W}_5$):}
 $H^1$ is four-dimensional; the Hessian is $4 \times 4$.
\end{itemize}
\end{computation}

\begin{remark}[Shadow depth atlas for $\mathcal{W}_N$]
\label{rem:wn-shadow-atlas}
\index{shadow depth!W-algebra atlas}%
Under the hypotheses of Theorem~\ref{thm:wn-class-M-stable},
Proposition~\ref{prop:wn-complementarity}
extends the shadow obstruction tower atlas
(Computation~\ref{comp:shadow-tower-atlas}) by
an infinite-depth column under the KZ/DS hypotheses:

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{llcccl}
\toprule
\textbf{Family} & \textbf{Class}
 & $\alpha_N$ & Self-dual $c$ & $\dim H^1$ & \textbf{Depth} \\
\midrule
$\mathrm{Vir}_c$ ($N=2$) & $\mathbf{M}$
 & $26$ & $13$ & $1$ & $\infty$ \\
$\mathcal{W}_{3,c}$ & $\mathbf{M}$
 & $100$ & $50$ & $2$ & $\infty$ \\
$\mathcal{W}_{4,c}$ & $\mathbf{M}$
 & $246$ & $123$ & $3$ & $\infty$ \\
$\mathcal{W}_{5,c}$ & $\mathbf{M}$
 & $488$ & $244$ & $4$ & $\infty$ \\
$\mathcal{W}_{N,c}$ & $\mathbf{M}$
 & $2(N\!-\!1)(2N^2\!+\!2N\!+\!1)$
 & $(N\!-\!1)(2N^2\!+\!2N\!+\!1)$
 & $N\!-\!1$ & $\infty$ \\
\bottomrule
\end{tabular}
\end{center}

\noindent
All class-$\mathbf M$ entries in this column are read under
Theorem~\ref{thm:wn-class-M-stable}. They are chirally Koszul with
non-formal Swiss-cheese structure. The infinite depth arises from the
Virasoro sub-sector, which contributes a one-loop wheel diagram
at every degree $k \ge 3$. The higher-spin sectors contribute
additional candidate operations at higher loop orders,
but the depth is already $\infty$ from the stress tensor alone.

\emph{Two depths.}\enspace The ``Depth~$= \infty$'' column
records the \emph{perturbative depth}
$d(\mathcal{W}_N) = \sup\{r : m_r \ne 0\} = \infty$. A
complementary invariant is the \emph{$\mathcal{W}$-essential
depth} $d_{\mathcal{W}}(\mathcal{W}_N)$: the smallest degree~$r$
after which no new OPE datum enters the shadow recursion and the
master equation becomes fully self-seeding. For
$\mathcal{W}_N$: $d_{\mathcal{W}} = N$ (proved for $N = 2,3,4$;
conjectured in general), because the highest-spin self-bracket
$\{W^{(N)}{}_\lambda W^{(N)}\}$ introduces the last independent
datum at degree~$N$. The perturbative depth says ``the tower is
infinite''; the $\mathcal{W}$-essential depth says ``after
degree~$N$, the recursion is fully seeded.''
\end{remark}

%% ==================================================================
%% DS TRANSPORT FOR ALL FAMILIES
%% ==================================================================

\subsection{Universal Drinfeld--Sokolov transport:
all principal reductions}
\label{subsec:universal-ds-transport}
\index{Drinfeld--Sokolov reduction!universal transport|textbf}

The DS transport computed explicitly for
$\mathfrak{sl}_2 \to \mathrm{Vir}$ (\S\ref{subsec:gravity-shadow-tower})
and $\mathfrak{sl}_3 \to \mathcal{W}_3$ (\S\ref{subsec:ds-transport-sl3-w3})
is the specialisation of a uniform mechanism:
principal DS reduction of any simple Lie algebra $\fg$ at non-critical
level~$k$ transports the affine Swiss-cheese structure
$\mathrm{SC}^{\mathrm{ch,top}}(V_k(\fg))$ to the principal $\cW$-algebra
$\cW_k(\fg)$, escalating the pole order, manufacturing the $\Ainf$ tower,
and preserving chiral Koszulness. This subsection records the
family-by-family data.

\subsubsection{$\mathfrak{sl}_4 \to \mathcal{W}_4$:
the first octupole algebra}
\label{subsubsec:ds-sl4-w4}

\begin{computation}[$\mathcal{W}_4$ central charge
and generator structure]
\label{comp:w4-ds-data}
\index{W-algebra!W4@$\mathcal{W}_4$!DS transport}%
The principal $\mathcal{W}_4 = W_k(\mathfrak{sl}_4)$ has three
generators $T \equiv W_2$ (spin~$2$), $W_3$ (spin~$3$),
$W_4$ (spin~$4$), obtained by eliminating the $12$ weight-$1$
affine currents of $V_k(\mathfrak{sl}_4)$
($\dim(\mathfrak{sl}_4) = 15$, rank~$3$).

DS reduction introduces $|\Delta^+(\mathfrak{sl}_4)| = 6$ ghost
pairs (one per positive root), with Dynkin grades $j(\alpha)$
ranging over $\{1, 1, 1, 2, 2, 3\}$ for the six positive roots
$\alpha_{12}, \alpha_{23}, \alpha_{34}, \alpha_{13}, \alpha_{24},
\alpha_{14}$. The ghost central charge is
$c_{\mathrm{ghost}}^{\mathrm{DS}} = -6 \times 2 = -12$ at the
DS level; after recombination into spin-$(2,3,4)$ ghosts:
\[
c_{\mathrm{gh}}(2) = -26,
\qquad c_{\mathrm{gh}}(3) = -74,
\qquad c_{\mathrm{gh}}(4) = -146,
\qquad c_{\mathrm{gh}}^{\mathrm{total}} = -246 = -\alpha_4.
\]
The $\mathcal{W}_4$ central charge from DS reduction is
\begin{equation}
\label{eq:w4-central-charge}
c_{\mathcal{W}_4}(k)
\;=\; 3 - \frac{60(k+3)^2}{k+4}.
\end{equation}
This is the $N = 4$ specialisation of the general formula
$c(\mathcal{W}_N, k) = (N-1)[1 - N(N+1)(k+N-1)^2/(k+N)]$.

\emph{Verification:}
$k = -3$: $c = 3 - 0 = 3$ (the $c = 3$ free-field point,
matching $\mathrm{rank}(\mathfrak{sl}_4) = 3$);
$k = -2$: $c = 3 - 60/2 = -27$;
$k = -4 + \varepsilon$: $c \sim -60/\varepsilon \to -\infty$
(critical level $k = -h^\vee$, Sugawara undefined).

\emph{Generator fate under DS reduction:}
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lll}
\toprule
\textbf{Generators} & \textbf{Count} & \textbf{DS fate} \\
\midrule
Positive root currents
 $J^{e_\alpha}$ ($\alpha \in \Delta^+$) & $6$ &
 $Q_{\mathrm{BRST}}$-exact \\
Cartan currents $J^{h_i}$ ($i = 1,2,3$) & $3$ &
 Absorbed into $T^{\mathrm{DS}}$ (weight $1 \to 2$) \\
Negative root currents $J^{f_\alpha}$ & $6$ &
 Gauge-fixed (projected out) \\
\bottomrule
\end{tabular}
\end{center}
No weight-$1$ generator survives. The surviving generators are
$W_2 = T$ (weight~$2$), $W_3$ (weight~$3$), $W_4$ (weight~$4$).
\end{computation}

\begin{proposition}[DS complexity transport for
$\mathfrak{sl}_4 \to \mathcal{W}_4$]
\label{prop:ds-complexity-transport-sl4}
\index{Drinfeld--Sokolov reduction!complexity transport!%
sl4@$\mathfrak{sl}_4$}%
\index{complexity transport!W4@$\mathcal{W}_4$}%
Drinfeld--Sokolov reduction transports:
\[
V_k(\mathfrak{sl}_4) \;\in\; \text{Class } \mathbf{L}
\qquad\xrightarrow{\;\mathrm{DS}\;}\qquad
\mathcal{W}_{4,c(k)} \;\in\; \text{Class } \mathbf{M}.
\]
The pole escalation data:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lccc}
\toprule
\textbf{OPE} & \textbf{Max pole order}
 & \textbf{Collision residue depth}
 & \textbf{Gap position} \\
\midrule
$T \cdot T$ & $4$ & $3$ & $d = 2$ \textup{(}absent\textup{)} \\
$T \cdot W_3$ & $4$ & $3$ &; \\
$T \cdot W_4$ & $5$ & $4$ &; \\
$W_3 \cdot W_3$ & $6$ & $5$ & $d = 4$ \\
$W_3 \cdot W_4$ & $7$ & $6$ & $d = 5$ \\
$W_4 \cdot W_4$ & $\mathbf{8}$ & $\mathbf{7}$ & $d = 6$ \\
\bottomrule
\end{tabular}
\end{center}
The binding OPE $\{W_4{}_\lambda W_4\}$ has maximum $\lambda$-degree~$7$
\textup{(}octupole: order-$8$ OPE\textup{)}, with the $\lambda^6$ coefficient
absent by the vacuum selection rule
\textup{(}no weight-$1$ field in $\mathcal{W}_4$\textup{)}.
The depth gap in the $(W_4, W_4)$ sector is at
$d = 6 = 2N - 2$ for $N = 4$, consistent with the gap migration
formula $d_{\mathrm{gap}}(\mathcal{W}_N, 2) = 2N - 2$
\textup{(}Theorem~\textup{\ref{thm:gap-migration}(iv))}.
\end{proposition}

\begin{proof}
The spin-$4$ generator $W_4$ is a quartic expression in the affine
currents (the fourth-order Casimir current, plus lower-order corrections
from the DS improvement). The $W_4(z)\,W_4(w)$ OPE involves
eight-fold Wick contractions of the quartic composites, producing
the octupole from quadruple contraction of the four pairs.
The mechanism is the same as for $\mathcal{W}_3$
(Proposition~\ref{prop:ds-complexity-transport-sl3}): Sugawara-type
construction squares, cubes, and quartics the pole order.

The $\lambda^6$ coefficient would produce a field of weight
$4 + 4 - 7 = 1$, which is absent from $\mathcal{W}_4$.
The gap at $d = 6$ follows.

After $d\log$ absorption, the collision residue
$r^{W_4 W_4}(z)$ has maximum pole order~$7$ with a gap at
$1/z^7$ ($\lambda^6 = 0$), giving pole orders
$\{1, 2, 3, 4, 5, 7\}$ in the collision residue.
\end{proof}

\begin{computation}[$(W_4, W_4)$ collision residue structure]
\label{comp:w4-w4-collision}
\index{collision residue!W4W4@$(W_4, W_4)$}%
The $\{W_4{}_\lambda W_4\}$ bracket has the schematic form
\begin{align*}
\{W_{4\,\lambda} W_4\}
&= \frac{c_4}{8!}\,\lambda^7
 + 0 \cdot \lambda^6
 + a_5\,\lambda^5
 + a_4\,\lambda^4
 + a_3\,\lambda^3 \\
&\quad + a_2\,\lambda^2
 + a_1\,\lambda
 + a_0,
\end{align*}
where $c_4$ is a normalisation constant depending on the
conventions for $W_4$, and the $a_n$ are quasi-primary
composites of $T, W_3, W_4$ and their derivatives.
The $\lambda^6$ term vanishes by the vacuum selection
rule ($W_4$ has no weight-$1$ field). The $\lambda^5$ term
has coefficient proportional to $T$ (weight $4 + 4 - 6 = 2$).
The $\lambda^4$ term has coefficient proportional to $W_3$
(weight $4 + 4 - 5 = 3$). The $\lambda^3$ term receives
contributions from $W_4$ and from the quasi-primary composite
$\Lambda_4 = {:}TT{:} + \cdots$ (weight $4 + 4 - 4 = 4$).

The collision residue via Laplace transform
$\lambda^n \mapsto n!/z^{n+1}$ gives:
\[
r^{W_4 W_4}(z)
\;=\;
\frac{c_4}{z^8 \cdot \text{norm}}
+ 0 \cdot \frac{1}{z^7}
+ \frac{(\cdots)\,T}{z^6}
+ \frac{(\cdots)\,W_3}{z^5}
+ \frac{(\cdots)\,(W_4 + \Lambda_4)}{z^4}
+ \cdots
\]
The gap at $1/z^7$ is the depth-$6$ hole in the collision
residue, reflecting the weight-$1$ lacuna.
\end{computation}

\subsubsection{General principal $\mathfrak{sl}_N \to
\mathcal{W}_N$: universal formulas}
\label{subsubsec:ds-slN-wN-universal}

\begin{theorem}[Universal DS transport with wheel-survival depth clause for principal
$\mathcal{W}_N$]
\label{thm:universal-ds-transport}
\index{Drinfeld--Sokolov reduction!universal transport!%
principal slN@principal $\mathfrak{sl}_N$}%
Assume the KZ/DS realization satisfies the analytic SDR and
wheel-residue hypotheses of Theorem~\textup{\ref{thm:wn-class-M-stable}}.
For every $N \ge 2$ and non-critical level $k \ne -N$,
the principal DS reduction $V_k(\mathfrak{sl}_N) \to
\mathcal{W}_{N,c(k)}$ satisfies:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Generator census.}
 Input: $\dim(\mathfrak{sl}_N) = N^2 - 1$ currents of weight~$1$.
 Output: $N - 1$ generators $W_s$ of weights $s = 2, 3, \ldots, N$.
 Eliminated: $N(N-1)/2$ positive root currents
 \textup{(}$Q_{\mathrm{BRST}}$-exact\textup{)},
 $N - 1$ Cartan currents
 \textup{(}absorbed into $T^{\mathrm{DS}}$\textup{)},
 $N(N-1)/2$ negative root currents
 \textup{(}gauge-fixed\textup{)}.
 Total eliminated: $N^2 - 1 - (N - 1) = N^2 - N
 = N(N-1)$ currents.
\item \textbf{Ghost count.}
 $|\Delta^+(\mathfrak{sl}_N)| = N(N-1)/2$ ghost pairs
 $(b_\alpha, c_\alpha)$. Ghost central charge at the DS level:
 $c_{\mathrm{ghost}}^{\mathrm{DS}} = -N(N-1)$. After recombination
 into spin-$s$ ghosts:
 $c_{\mathrm{ghost}}^{\mathcal{W}_N} = -\alpha_N
 = -2(N-1)(2N^2 + 2N + 1)$.
\item \textbf{Central charge.}
 \begin{equation}
 \label{eq:wN-central-charge-ds}
 c_{\mathcal{W}_N}(k)
 \;=\; (N-1)\biggl[1 - \frac{N(N+1)(k + N - 1)^2}{k + N}\biggr].
 \end{equation}
 This is the Feigin--Frenkel formula, specialising to
 $c = 1 - 6(k+1)^2/(k+2)$ at $N = 2$ \textup{(Virasoro)},
 \eqref{eq:w3-central-charge} at $N = 3$, and
 \eqref{eq:w4-central-charge} at $N = 4$.
\item \textbf{Pole escalation.}
 The highest pole in the $\cW_N$ OPE is in the
 $W_N$--$W_N$ self-OPE:
 \begin{equation}
 \label{eq:wn-max-pole}
 \mathrm{ord}(\{W_{N\,\lambda} W_N\}) = 2N - 1,
 \qquad
 \text{max OPE pole order} = 2N.
 \end{equation}
 The $\lambda^{2N-2}$ coefficient vanishes by the vacuum selection
 rule \textup{(}no weight-$1$ field in $\mathcal{W}_N$\textup{)}.
 After $d\log$ absorption, the collision residue has maximum pole
 order $2N - 1$ with a gap at $1/z^{2N-1}$:
 \begin{equation}
 \label{eq:wn-collision-gap}
 d_{\mathrm{gap}}(\mathcal{W}_N,\, 2) \;=\; 2N - 2.
 \end{equation}
\item \textbf{Class transport.}
 $V_k(\mathfrak{sl}_N) \in \mathrm{Class}\;\mathbf{L}$
 \textup{(}double pole, $d_{\max} = 1$\textup{)}
 $\;\xrightarrow{\;\mathrm{DS}\;}\;$
 $\mathcal{W}_{N,c(k)} \in \mathrm{Class}\;\mathbf{M}$
 \textup{(}$2N$-fold pole, $d_{\max} = \infty$ under wheel survival\textup{)}.
 Chiral Koszulness is preserved
 \textup{(}Theorem~\textup{\ref{thm:ds-koszul-obstruction})};
 formality is destroyed for all $N \ge 2$ under the stated
 wheel-survival hypothesis.
\item \textbf{Gap migration.}
 At degree~$n$, the depth gap in the binding
 $(W_N, \ldots, W_N)$ sector is:
 \begin{equation}
 \label{eq:wn-gap-migration}
 d_{\mathrm{gap}}(\mathcal{W}_N,\, n) \;=\; 2N + n - 4.
 \end{equation}
\end{enumerate}
\end{theorem}

\begin{proof}
Parts (i)--(ii) are direct computation in the root system
$\Delta(\mathfrak{sl}_N)$. Part~(iii) is the Feigin--Frenkel
central charge formula. Part~(iv) follows from the structure
of the $W_N$ generator: $W_N$ is a degree-$N$ polynomial in
the affine currents (the $N$-th order Casimir current), so the
$W_N$--$W_N$ OPE involves $2N$-fold Wick contractions of these
polynomials, producing a pole of order $2N$ from $N$-fold
contraction. The vacuum selection rule
(Remark~\ref{rem:weight-1-vacuum-selection}) eliminates the
$\lambda^{2N-2}$ coefficient.

Part~(v) uses Theorem~\ref{thm:wn-class-M-stable}
combined with the pole-order characterisation of the depth classes:
the affine double pole places $V_k(\fg)$ in class~$\mathbf{L}$, while
the $2N$-fold pole of $\mathcal{W}_N$ gives class~$\mathbf{M}$ once the
wheel-survival hypothesis supplies $d(\mathcal{W}_N)=\infty$.

Part~(vi): the gap migrates by one unit per additional input.
At degree~$2$, the binding sector $(W_N, W_N)$ has maximum depth
$2N - 1$ with a gap at $d = 2N - 2$. Each additional input
at degree~$n$ contributes at most depth~$1$ (from the $T$-sector
propagator), shifting the gap position to $2N - 2 + (n - 2)
= 2N + n - 4$.
\end{proof}

\begin{remark}[The pole escalation cascade]
\label{rem:pole-escalation-cascade}
\index{Drinfeld--Sokolov reduction!pole escalation cascade}%
The DS reduction generates the $2N$-fold pole of $\cW_N$ from
the affine double pole by a cascade of nonlinear
constructions:
\begin{itemize}
\item $W_2 = T$ (Sugawara): quadratic in $J^a$, squares the
 pole $\Rightarrow$ order~$4$;
\item $W_3$ (cubic Casimir): cubic in $J^a$, cubes the pole
 $\Rightarrow$ order~$6$;
\item $W_s$ (degree-$s$ Casimir): degree-$s$ in $J^a$,
 $s$-tuples the pole $\Rightarrow$ order~$2s$.
\end{itemize}
The binding pole order for $\cW_N$ is therefore
$2N$ (from the $W_N$-self-OPE), giving the depth gap at
$2N - 2$ after $d\log$ absorption and the vacuum selection rule.
The Sugawara construction is the universal pole-escalation engine.
\end{remark}

%% =====================================
%% Non-simply-laced: B_2 and G_2
%% =====================================

\subsubsection{Non-simply-laced principal $\mathcal{W}$-algebras:
$B_2$ and $G_2$}
\label{subsubsec:non-simply-laced-ds}

The simply-laced formulas above extend to all simple Lie algebras.
For non-simply-laced types, two new features appear: the Casimir
tensor has root-length-dependent coefficients, and the generators
occur at the exponents of $\fg$ (which need not be $2, 3, \ldots,
\mathrm{rank} + 1$).

\begin{computation}[$W(B_2, f_{\mathrm{prin}})$:
the $\mathfrak{so}_5$ principal $\mathcal{W}$-algebra]
\label{comp:wB2-ds-data}
\index{W-algebra!B2@$B_2$ principal!DS transport}%
\index{Drinfeld--Sokolov reduction!non-simply-laced!B2@$B_2$}%
The Lie algebra $\mathfrak{so}_5 \cong \mathfrak{sp}_4$
has type $B_2$, with $\dim = 10$, rank~$2$,
$h^\vee = 3$, and exponents $1, 3$. The principal
$\mathcal{W}$-algebra has generators at weights $2$ and $4$
\textup{(}spins $= \text{exponents} + 1$\textup{)}.

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lcccc}
\toprule
& \textbf{$\mathfrak{sl}_3$ (type $A_2$)}
& \textbf{$\mathfrak{so}_5$ (type $B_2$)}
& \textbf{$\mathfrak{sp}_4$ (type $C_2$)} \\
\midrule
$\dim$ & $8$ & $10$ & $10$ \\
rank & $2$ & $2$ & $2$ \\
$h^\vee$ & $3$ & $3$ & $3$ \\
$|\Delta^+|$ & $3$ & $4$ & $4$ \\
Exponents & $1, 2$ & $1, 3$ & $1, 3$ \\
Gen.\ weights & $2, 3$ & $2, 4$ & $2, 4$ \\
Ghost pairs & $3$ & $4$ & $4$ \\
\bottomrule
\end{tabular}
\end{center}

\noindent
The ghost central charge for $W(B_2)$: spin-$2$ ghosts
contribute $c_{\mathrm{gh}}(2) = -26$, spin-$4$ ghosts contribute
$c_{\mathrm{gh}}(4) = -2(6 \cdot 16 - 6 \cdot 4 + 1) = -146$,
total $c_{\mathrm{ghost}}^{W(B_2)} = -172$. Thus
$\alpha_{B_2} = |c_{\mathrm{ghost}}| = 172$, and the Koszul
involution is $c \mapsto 172 - c$ with self-dual point
$c = 86$.

\emph{Pole escalation.}
The spin-$4$ generator $W_4$ is quartic in the affine
currents. The $W_4$--$W_4$ OPE has maximum pole
order~$8$ (octupole), matching the $A_3$ case. The vacuum
selection rule eliminates the $\lambda^6$ coefficient (no
weight-$1$ field). Depth gap at $d = 6 = 2 \cdot 4 - 2$.

The non-simply-laced novelty: the Casimir tensor
$\Omega_{B_2}$ has root-length-dependent coefficients (short
roots contribute $1$, long roots contribute $1/2$), producing a
collision residue $r^{B_2}(z) = k \cdot \Omega_{B_2}/z$ that
is \emph{not} proportional to the identity in the tensor product
of non-isomorphic root spaces. This asymmetry propagates
through DS reduction: the $(W_4, W_4)$ collision residue
inherits the root-length weighting.
\end{computation}

\begin{computation}[$W(G_2, f_{\mathrm{prin}})$:
the exceptional $G_2$ principal $\mathcal{W}$-algebra]
\label{comp:wG2-ds-data}
\index{W-algebra!G2@$G_2$ principal!DS transport}%
\index{Drinfeld--Sokolov reduction!exceptional!G2@$G_2$}%
The exceptional Lie algebra $G_2$ has $\dim = 14$, rank~$2$,
$h^\vee = 4$, and exponents $1, 5$. The principal
$\mathcal{W}$-algebra $W(G_2, f_{\mathrm{prin}})$ has
generators at weights $2$ and $6$.

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lcl}
\toprule
\textbf{Datum} & \textbf{Value} & \textbf{Notes} \\
\midrule
$\dim(G_2)$ & $14$ & \\
rank & $2$ & \\
$h^\vee$ & $4$ & \\
$|\Delta^+|$ & $6$ & $6$ ghost pairs \\
Exponents & $1, 5$ & Largest gap in rank $2$ \\
Gen.\ weights & $2, 6$ & Spin-$2$ (Virasoro) + spin-$6$ \\
\bottomrule
\end{tabular}
\end{center}

\noindent
Ghost central charge for $W(G_2)$: spin-$2$ ghosts contribute
$c_{\mathrm{gh}}(2) = -26$, spin-$6$ ghosts contribute
$c_{\mathrm{gh}}(6) = -2(6 \cdot 36 - 6 \cdot 6 + 1)
= -2 \cdot 181 = -362$, total
$c_{\mathrm{ghost}}^{W(G_2)} = -388$. Thus
$\alpha_{G_2} = 388$, and the Koszul involution is
$c \mapsto 388 - c$ with self-dual point $c = 194$.

\emph{Pole escalation.}
The spin-$6$ generator $W_6$ is degree-$6$ in the affine
currents. The $W_6$--$W_6$ OPE has maximum pole
order~$\mathbf{12}$ (dodecapole). After $d\log$ absorption,
the collision residue has maximum pole order~$11$. The vacuum
selection rule eliminates $\lambda^{10}$ (no weight-$1$ field):
\begin{equation}
\label{eq:wG2-depth-gap}
d_{\mathrm{gap}}(W(G_2),\, 2) \;=\; 2 \cdot 6 - 2 \;=\; 10.
\end{equation}
This is the largest degree-$2$ depth gap in rank~$2$: the
exponent gap ($5 - 1 = 4$, versus $2 - 1 = 1$ for $A_2$ and
$3 - 1 = 2$ for $B_2$) propagates directly to the depth gap.

The collision residue $r^{W_6 W_6}(z)$ has pole orders
$\{1, 2, 3, 4, 5, 6, 7, 8, 9, 11\}$ with the gap at
$d = 10$ ($1/z^{11}$ absent). The maximal depth of $11$
(from the $\lambda^{11}$ leading coefficient) reflects the
dodecapole structure. Class transport:
\[
V_k(G_2) \;\in\; \text{Class } \mathbf{L}
\qquad\xrightarrow{\;\mathrm{DS}\;}\qquad
W(G_2, f_{\mathrm{prin}}) \;\in\; \text{Class } \mathbf{M}.
\]
The $G_2$ principal $\mathcal{W}$-algebra has the deepest depth
gap of any rank-$2$ algebra, arising from the exceptionally large
second exponent of $G_2$.
\end{computation}

\begin{remark}[The exponent--depth correspondence]
\label{rem:exponent-depth}
\index{Drinfeld--Sokolov reduction!exponent--depth correspondence}%
For a simple Lie algebra $\fg$ with exponents
$e_1 \le e_2 \le \cdots \le e_r$ (where $r = \mathrm{rank}(\fg)$),
the principal $\mathcal{W}(\fg)$ has generators at weights
$s_i = e_i + 1$. The binding OPE is $\{W_{s_r}{}_\lambda W_{s_r}\}$
(highest-weight self-OPE), with maximum pole order $2s_r = 2(e_r + 1)$.
The degree-$2$ depth gap is at
\begin{equation}
\label{eq:exponent-depth}
d_{\mathrm{gap}}(\mathcal{W}(\fg),\, 2)
\;=\; 2\,s_r - 2
\;=\; 2\,e_r.
\end{equation}
For the classical families:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lcccc}
\toprule
\textbf{Type} & \textbf{Largest exponent $e_r$}
 & \textbf{Highest spin $s_r$}
 & \textbf{Max OPE pole $2s_r$}
 & \textbf{Depth gap $2e_r$} \\
\midrule
$A_{N-1}$ ($\mathfrak{sl}_N$) & $N - 1$ & $N$ & $2N$ & $2N - 2$ \\
$B_n$ ($\mathfrak{so}_{2n+1}$) & $2n - 1$ & $2n$ & $4n$ & $4n - 2$ \\
$C_n$ ($\mathfrak{sp}_{2n}$) & $2n - 1$ & $2n$ & $4n$ & $4n - 2$ \\
$D_n$ ($\mathfrak{so}_{2n}$) & $2n - 3$ & $2n - 2$ & $4n - 4$ & $4n - 6$ \\
$G_2$ & $5$ & $6$ & $12$ & $10$ \\
$F_4$ & $11$ & $12$ & $24$ & $22$ \\
$E_6$ & $11$ & $12$ & $24$ & $22$ \\
$E_7$ & $17$ & $18$ & $36$ & $34$ \\
$E_8$ & $29$ & $30$ & $60$ & $58$ \\
\bottomrule
\end{tabular}
\end{center}
\noindent
$E_8$ has the deepest degree-$2$ depth gap in the entire classification
($d_{\mathrm{gap}} = 58$), reflecting the Coxeter number $h = 30$.
The formula $d_{\mathrm{gap}} = 2e_r = 2(h - 1)$ relates the depth
gap to the Coxeter number for all simply-laced types. For
non-simply-laced types, $e_r = h - 1$ still holds (where $h$ is the
Coxeter number, not the dual Coxeter number $h^\vee$), so the formula
is universal.
\end{remark}

\subsubsection{Universal complexity transport formula}
\label{subsubsec:universal-complexity}

\begin{proposition}[Universal DS complexity transport]
\label{prop:universal-ds-complexity}
\index{Drinfeld--Sokolov reduction!universal complexity transport|textbf}%
Assume the principal KZ/DS realization satisfies the analytic SDR,
wheel-residue, and split-projection hypotheses of
Theorem~\textup{\ref{thm:wn-class-M-stable}} for
$\mathcal W_k(\fg)$. For every simple Lie algebra $\fg$ and every
non-critical level~$k$,
principal DS reduction effects the following transport:
\begin{align}
\label{eq:universal-transport}
&\text{Input:}\quad
V_k(\fg) \;\in\; \text{Class}\;\mathbf{L}
 \qquad(\text{double pole},\; d_{\max} = 1,\;
 \text{shadow depth } r_{\max} = 2), \\
&\text{Output:}\quad
\mathcal{W}_k(\fg) \;\in\; \text{Class}\;\mathbf{M}
 \qquad(\text{$2s_r$-fold pole},\;
 \text{$d_{\max} = \infty$ under wheel survival},\;
 r_{\max} = \infty), \notag
\end{align}
where $s_r = e_r + 1$ is the highest spin. The transport preserves:
\begin{enumerate}[label=\textup{(\alph*)}]
\item Chiral Koszulness
 \textup{(}Theorem~\textup{\ref{thm:ds-koszul-obstruction})};
\item The Koszul involution $c \mapsto \alpha_\fg - c$, where
 $\alpha_\fg = |c_{\mathrm{ghost}}(\mathcal{W}(\fg))| =
 \sum_{i=1}^r 2(6s_i^2 - 6s_i + 1)$;
\item Gravitational coproduct primitivity at all degrees
 \textup{(}Theorem~\textup{\ref{thm:gravitational-primitivity})}.
\end{enumerate}
The transport destroys formality for all $\fg$ with rank $\ge 1$ under
the stated survival hypotheses.
\end{proposition}

\begin{proof}
The proof is uniform across all types. The inputs are:
(1)~$V_k(\fg) \in \text{Class}\;\mathbf{L}$ because the affine
OPE has at most double poles;
(2)~the principal $\cW$-algebra generators $W_{s_i}$ are
degree-$s_i$ polynomials in the affine currents, so the
$W_{s_r}$-self-OPE has pole order $2s_r > 2$ for all $\fg$
with rank $\ge 1$;
(3)~the Virasoro-sector input of
Theorem~\ref{thm:wn-class-M-stable} applies once the stated SDR,
wheel-residue, and split-projection hypotheses hold for
$\cW(\fg)$, since every principal $\cW(\fg)$ contains the stress
tensor $T = W_2$.
Coproduct primitivity is
Theorem~\ref{thm:gravitational-primitivity}, which holds for
all principal DS reductions.
\end{proof}

\section{K3 base-point stable $W$-algebra}
\label{sec:was-supplement}

\begin{remark}[Stable $W$-algebras at class-$\mathcal S$ $A_1$ on $\Sigma_{0,24}$]
\label{rem:was-1}
The stable $W$-algebra at the K3 base point is the Schur-sector
chiral algebra $\mathbf H_{\Delta_5}$ of class-$\mathcal S$ $A_1$ on
$\Sigma_{0,24}$: central charge $c_{2d} = -214$
(Shapere--Tachikawa first-principles $c_{4d} = 107/6$),
Coulomb rank $21$, flavour $\mathfrak{su}(2)^{24}$. The stable-$W$ Miura transformation
carries the K3-specific $\widetilde M_{24}$ Schur cocycle of order
$6$ in $H^2(M_{24}, U(1)) = \mathbb Z/12$
\cite{Gaiotto2009,BeemRastelli2015,ChengDuncanHarvey2014}. Cross-ref
Vol.~III Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Stable-$W$ and Borcherds denominator]
\label{rem:was-2}
The stable-$W$ character at the K3 base point matches the Borcherds
1992 denominator
$\prod_{\alpha\in\Delta_+}(1-q^{r\alpha})^{c(r\alpha)}
=\Phi_{10}^{\mathrm{un}}=\Delta_5^2$.
The Schur-sector $W$-algebra character is governed by the weight-$5$
Igusa cusp form $\Delta_5$. The identity
$\mathrm{wt}(\Delta_5)=5=\kappa_{\mathrm{BKM}}(\mathfrak g_{\Delta_5})
=c_{\phi_{0,1}^{K3}}(0)/2$ is the Borcherds-weight fingerprint
\cite{Borcherds1992,Gritsenko1999}. Cross-ref
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[order-$6$ class $6A$ vs $6B$ distinguishes
the pentagon-$\hbar^3$ cocycle]
\label{rem:was-6A-6B}
The Mathieu group $M_{24}$ has two conjugacy classes of order-$6$
elements that separate the pentagon-$\hbar^3$ cocycle of the
Schur-sector stable-$W$ algebra:
the class $6A$ with cycle shape $1^2 2^2 3^2 6^2$ on the $24$-point
Golay set, umbral shift $m_{6A} = 2$ and $\chi_{23}(6A) = -1$; and
the class $6B$ with cycle shape $6^4$, umbral shift $m_{6B} = 6$ and
$\chi_{23}(6B) = +1$ \cite{ChengDuncanHarvey2014,ConwayCurtisNortonParkerWilson1985}.
Their pentagon-$\hbar^3$ cocycle restrictions lie in
$H^3(\Z/6, U(1)) = \Z/6$ at distinct classes:
$[\mathrm{coc}(6A)] = 2 \pmod{6}$ and $[\mathrm{coc}(6B)] = 3 \pmod{6}$.
The CRT decomposition $\Z/6 = \Z/2 \times \Z/3$ places $6A$ in the
$(\bmod\,2,\bmod\,3) = (0,2)$ class (a pure $\Z/3$-phase from the
$3^2$ factor of the $1^2 2^2 3^2 6^2$ shape) and $6B$ in the
$(\bmod\,2,\bmod\,3) = (1,0)$ class (a pure $\Z/2$-phase from the
sign-flip $\chi_{23}(6B) = +1$ vs $\chi_{23}(6A) = -1$). Their sum
$2 + 3 = 5 \equiv -1 \pmod 6$ matches the universal identity
$\hbar^2 \cdot K^{\kappa_{\mathrm{ch}}} = -1$ reduced to the order-$6$
sector. The finite check is the $M_{24}$ Schur-multiplier comparison
for the $6A$ and $6B$ umbral phases.
The umbral phase orders are $\mathrm{ord}(e^{2\pi i m_{6A}/24}) = 12$
for $6A$ and $\mathrm{ord}(e^{2\pi i m_{6B}/24}) = 4$ for $6B$; their
least common multiple $12$ exhausts $H^2(M_{24}, U(1)) = \Z/12$.
The $6A$ / $6B$ split is the order-$6$ refinement of the $\Z/8$ class
in Remark~\ref{rem:was-2}: $\Z/12 = \Z/8 \cdot \Z/3 / \Z/2$
absorbs both the Humbert $H_1$ order-$8$ monodromy and the order-$6$
Schur cocycle at a single Bockstein image. Cross-ref
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}
